### 2009-05-25 AffineLieAlgebras/ACMS2009/article.tex
First commit to git for cross-computer access

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}

%%%%%%%%%%%%%%% From Walton's paper
\def\Z{\Bbb Z}\def\R{\Bbb R}\def\C{\Bbb C}\def\N{\Bbb N}\def\Q{\Bbb Q}
%
\def\la{{\lambda}}\def\al{{\alpha}}\def\be{{\beta}}\def\ga{{\gamma}}
\def\ka{{\kappa}}\def\ome{{\omega}}\def\vp{{\varphi}}
%
\def\Tr{{\rm Tr}\,}\def\ad{{\rm ad}\,}\def\dim{{\rm dim}\,}\def\id{{\rm id}}
\def\ch{{\rm ch}}\def\mult{{\rm mult}\,}
\def\Ppkb{\overline{P_+^k}}
%
\def\zb{{\bar z}}
\def\pzp{{\{z\}}}
\def\di{{\partial}}
\def\h{\hat}
\def\>{{\rangle}}
\def\<{{\langle}}
\def\K{{\cal K}}
\def\T{{\cal T}}
\def\Tn{{\cal T}_\#}
\def\Nk{{{ }^{(k)}N}}\def\Vk{{{ }^{(k)}V}}
\def\Sk{{S^{(k)}}}\def\Tk{{T^{(k)}}}
\def\LR{{Littlewood-Richardson}}
\def\ie{{\rm i.e.}}\def\card{{\rm card}\,}
\def\Sp{{\rm Span}\,}

% standard tableaux
\def\b#1{\kern-0.25pt\vbox{\hrule height 0.2pt\hbox{\vrule
width 0.2pt \kern2pt\vbox{\kern2pt \hbox{#1}\kern2pt}\kern2pt\vrule
width 0.2pt}\hrule height 0.2pt}}
\def\ST#1{\matrix{\vbox{#1}}}
\def\STrow#1{\hbox{#1}\kern-1.35pt}
\def\bv{\b{\phantom{1}}}

\font\huge=cmr10 scaled \magstep2
\font\small=cmr8

% usage: surround part of equation to be boxed by \boxEq{...}
\def\boxit#1{\leavevmode\kern5pt\hbox{
	\vrule width.2pt\vtop{\vbox{\hrule height.2pt\kern5pt
        \hbox{\kern5pt{#1}\kern5pt}}
      \kern5pt\hrule height.2pt}\vrule width.2pt}\kern5pt}
\def\boxEq#1{\boxit{$\displaystyle #1$}}

% Wick contraction (upper-bracket)
\def\ubrackfill#1{$\mathsurround=0pt
	\kern2.5pt\vrule depth#1\leaders\hrule\hfill\vrule depth#1\kern2.5pt$}
\def\contract#1{\mathop{\vbox{\ialign{##\crcr\noalign{\kern3pt}
	\ubrackfill{3pt}\crcr\noalign{\kern3pt\nointerlineskip}
	$\hfil\displaystyle{#1}\hfil$\crcr}}}\limits
}

\def\ubrack#1{$\mathsurround=0pt
	\vrule depth#1\leaders\hrule\hfill\vrule depth#1$}
\def\dbrack#1{$\mathsurround=0pt
	\vrule height#1\leaders\hrule\hfill\vrule height#1$}
\def\ucontract#1#2{\mathop{\vbox{\ialign{##\crcr\noalign{\kern 4pt}
	\ubrack{#2}\crcr\noalign{\kern 4pt\nointerlineskip}
	$\hskip #1\relax$\crcr}}}\limits
}
\def\dcontract#1#2{\mathop{\vbox{\ialign{##\crcr
	$\hskip #1\relax$\crcr\noalign{\kern0pt}
	\dbrack{#2}\crcr\noalign{\kern0pt\nointerlineskip}
	}}}\limits
}

\def\ucont#1#2#3{^{\kern-#3\ucontract{#1}{#2}\kern #3\kern-#1}}
\def\dcont#1#2#3{_{\kern-#3\dcontract{#1}{#2}\kern #3\kern-#1}}

%%%%%%%%%%%%%%%%%

\title{Computational tools for representation theory of affine Lie algebras}
\author{Anton Nazarov}
\begin{document}
\maketitle
\begin{abstract}
  We describe computational algorithms for construction of
  representations of affine Lie algebras and computation of branching
  coefficients of representations of affine Lie algebra to
  representations of regular affine sub-algebra. Also we introduce the
  implementation of these algorithms as Maple package and present
  examples studied with these computational tools. 
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Affine Lie algebras constitute the simplest and most studied class of
infinite-dimesional Lie algebras \cite{wakimoto2001idl,kac1990idl}. They are connected with theory of
modular forms and other mathematical subjects, but their main
applications in physics are in conformal field theory, where they are
current algebras of WZW-models \cite{Walton:1999xc,witten1984nab}.

In this article we will describe computation algorithms for representations of affine Lie algebras by example.

Theory of affine Lie algebras is based upon the theory of simple Lie
algebras. Affine Lie algebras are infinite-dimensional, but this
infinite-dimensionality is ``along one direction''.

So in computations we limit ourselves with some finite grade. 
Then the problem is to propose algorithms with lowest growths rate
with the increase of maximal grade.

\section{Representations}
\label{sec:representations}

We consider integrable modules $L^{\mu}$ with the highest weight
$\mu$. As for simple Lie algebras the most computation-intensive task
is to find weight multiplicities (dimensions of weight subspaces). 
These multiplicities are usually encoded in form of string functions
and these functions are connected with generic theta-functions and
modular forms \cite{kac1990idl}. 
But it is easier to work with multiplicities for automated
computations.

Weight multiplicities are essential for explicit construction of
module and are also used for calculation of WZW fusion coefficients
which are sufficient for calculation of all correlation functions in
WZW-model \cite{Walton:1999xc}.

There are several recursive algorithms for computation of weight
multiplicities which are based on different recurrent relations
between weight multiplicities. These relations follow from denominator
identity and Weyl-Kac formula \cite{kac1990idl,wakimoto2001idl}.

Freudenthal formula is the most used formula for computation of weight
multiplicities of simple finite-dimensional Lie algebras:
\begin{equation}
  \label{eq:1}
   mult(\xi)=\frac{2}{(\mu+\rho|\mu+\rho)-(\xi+\rho|\xi+\rho)}\sum_{\alpha\in\Delta^{+}} mult(\alpha) \sum_{k=1}^{\infty}mult(\xi+k\alpha)(\xi+k\alpha|\alpha)
\end{equation}
Here $\xi$ is the weight in question, $\mu$ - highest weight of the
module, $\rho$ - Weyl vector of Lie algebra and $\Delta^{+}$ is the
set of positive roots of the algebra.

Algorithms, based on Freudenthal formula (\ref{eq:1}) are implemented
in several software packages, such as Coxeter/Weyl
\cite{stembridge1995mps}, LiE \cite{vanleeuwen1994lsp}, LambdaTensor
\cite{fischbacher2002ilp}.

Freudenthal formula can be used for affine Lie algebras as well. It was
the main tool for preparation of tables in the book
\cite{kass1990ala}, but the software used by the authors is not
available.

Kac-Peterson formula is less efficient and is not discussed here.

We use new method proposed in the articles
\cite{lyakhovsky1996rra,lyakhovsky2007dub,ilyin812pbc,kulish4sfa}. The
idea is to use recurrent relations for anomalous branching
coefficients based upon summation over special
set of vectors $\Gamma_{\frak{a}\subset \frak{g}} $ called ``fan''.
\begin{equation}
  \label{recurrent-relation}
  k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
    \sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
      \left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
      \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
      +\gamma }^{\left( \mu \right) }\right)   
\end{equation}

Fan doesn't depend on the module, but
is determined by the injection of sub-algebra into the algebra. If 
sub-algebra is Cartan sub-algebra, this relation gives recurrent
relation for weight multiplicities
\begin{equation}
  \label{eq:2}
  mult(\xi)=-\sum_{w\in W\backslash e}det(w)\;mult(\xi+\rho-w\rho)+\sum_{w\in W}det(w)\delta_{\xi,w(\mu+\rho)-\rho}
\end{equation}

The algorithm works as follows:
\begin{itemize}
\item Compute the set of ``anomalous'' weights as the orbit of sum of
  highest weight $\mu$ and Weyl vector $\rho$ under the action of Weyl
  group, shifted by $-\rho$.
\item Compute the set of vectors $\rho-w\rho$ for $w\in W\backslash e$
\item Set the multiplicity of highest weight equal to 1 as the initial condition.
\item Calculate multiplicities of weights grade-by-grade using formula (\ref{eq:2}).
\end{itemize}

We could illustrate the algorithm with the picture.
\begin{figure}[bh]
  \noindent\centering{
  \includegraphics[width=150mm]{A1_with_star.pdf}
  }
  \caption{Computation of weight multiplicities of level 1
    representation of algebra $A_1$}
  \label{A1 with star}
\end{figure}

Weyl group of affine Lie algebra is richer than that of simple
finite-dimensional Lie algebra. It can be presented as semi-direct
product of finite Weyl group $W_0$ of simple Lie algebra
$\frak{g}_0\subset \frak{g}$ with infinite abelian group translations
along the roots of $\frak{g}_0$ which are non-imaginary roots of $\frak{g}$: 
$W=W_0\ltimes T$.

The Weyl group orbit of highest root bounds the weights with non-zero
multiplicity.

Rich Weyl symmetry of affine Lie algebras allows further improvement
of algorithm.

It can be shown that it is enough to compute multiplicities of the
weights of the form $\lambda=(\overset{\circ }{\lambda},k,n)$ where
$\overset{\circ }{\lambda}$ is finite part, $k$ - level of the
representation and $n$ - grade only for finite number of
$\overset{\circ}{\lambda}$ lying in the intersection of main Weyl
chamber with the subspace of grade zero.
Multiplicities of all other weights could be obtained by Weyl group
action.

So all the required information can be encoded in the form of string functions:
\begin{equation}
  \label{eq:3}
  \sigma^{\mu}_{\lambda}=\sum_{k=0}^{\infty} mult(\mu-kd)q^k
\end{equation}
Where $d$ is the element dual to imaginary root $\delta$.

It is possible to ``fold'' the star, so that the summation in formula
(\ref{eq:2}) involves only weights from main Weyl chamber. Also this
computation can be rewritten as infinite set of equations on string
functions coefficient, which can be solved recursively. See
\cite{kulish4sfa} for details.

This method is theoretically more efficient than the use of Freudenthal
formula (\ref{eq:1}) \cite{Nazarov2008}, but our implementation is
rather inefficient. Also we don't have independent realisation of algorithms,
based on (\ref{eq:1}) for affine Lie algebras, so we haven't done any
practical speed comparisons yet.
\section{Branching rules}
\label{sec:branching-rules}

Say we want to obtain decomposition of module $L^{\mu}$ of algebra
$\frak{g}$ into modules of sub-algebra $\frak{a}$
\begin{equation}
  \label{eq:4}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }
\end{equation}
Here $\nu$ goes through weight lattice of $\frak{a}$.

Branching coefficients can be computed in similar way using formula
(\ref{recurrent-relation}).

Notice that to obtain the branching
rules we need only the projected singular element $\pi _{\frak{a}}\circ \Psi
^{\left( \mu\right) }$ of this module 
and the fan $\Gamma
_{\frak{a}\subset \frak{g}}$ and do not need any other properties of the module itself.

Singular element can be computed the same way as the set of ``anomalous''
weights in section \ref{sec:representations} and then projected onto
the weight lattice of $\frak{a}$.

The fan $\Gamma_{\frak{a}\subset \frak{g}}$ is computed as the
combination of projection of positive roots $\Delta^{+}$ of algebra
$\frak{g}$ using formula:

\begin{equation}
  \label{phi-d}
  \Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
      \gamma \right) \neq 0\right\} ;  
\end{equation}
\begin{equation}
  \label{fan-d}
  \prod_{\alpha \in \left( \pi _{\frak{a}}\circ \Delta ^{+}\right) }\left(
    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
      }}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset 
      \frak{g}}}s\left( \gamma \right) e^{-\gamma }.  
\end{equation}
\begin{equation}
  \label{fan-defined}
  \Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
      \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} .
\end{equation}

Then branching coefficients are computed recursively using formula
(\ref{recurrent-relation}), which gives anomalous branching
coefficients which are equal to usual branching coefficients for
weights from main Weyl chamber.

\section{Details of implementation}
\label{sec:details-implementation}

The algorithms are implemented as Maple programs. Since theory of
affine Lie algebras is based upon the theory of simple
finite-dimensional Lie algebras we use Coxeter/Weyl package
\cite{stembridge1995mps} as the foundation of our work.

This design choice imposed some performance constraints but allowed us
to keep the code concise by the lack of need of reimplementation of
algorithms for computation of roots, weights and finite Weyl
reflection. So there is less than 1000 lines of code in our package.

Currently implementation allows to calculate roots, dominant weights,
weight multiplicities and branching coefficients for non-twisted
affine Lie algebras of series $A,B,C,D$ and for twisted algebras of
series $A^{(2)}$ and $D^{(2)}$.

Our program can be freely downloaded from \url{http://anton.nazarov.name/affine}

\section{Applications}
\label{sec:applications}

Weight multiplicities, calculated with presented algorithms can be
used for explicit construction of irreducible highest-weight modules.
For example, let's consider $A_3$-module of level 2 with highest
weight $\alpha_1+\alpha_2+\alpha_3$.

String function coefficients are equal to
\begin{verbatim}
> al:=algebra_roots(A3);
              al := [e2 - e1, e3 - e2, e4 - e3, delta + e1 - e4]

> mu:=2*lambda0+sum(al[i],i=1..3);
                          mu := -e1 + e4 + 2 lambda0

> string_function(mu,mu,A3,30);
[1, 7, 32, 117, 371, 1063, 2819, 7029, 16660, 37836, 82836, 175658, 362153,

    728159, 1431447, 2757188, 5212989, 9689739, 17730751, 31977358, 56899365,

    99981354, 173632536, 298236157, 506980545, 853456334, 1423520148,

    2353697410, 3859547524, 6279119909, 10139144298]
\end{verbatim}

Weight multiplicities can be used to calculate fusion coefficients of
Wess-Zumino-Witten models, which are critical for computation of
multipoint correlation functions that determine physical quantities.

In the paper \cite{Walton:1999xc} following equation for fusion
coefficient is derived.
\begin{equation}
  \label{eq:5}
\Nk_{\la,\mu}^\nu\ =\ \sum_{w\in W}\, (\det\,w)\, 
\mult(\mu; w\nu-\la)\ .
 \end{equation}
Here $\mult(\mu; w\nu-\la)$ denotes multiplicity of weight
$w\nu-\lambda$ in the module with highest weight $\mu$.

Branching coefficients of affine Lie algebras are used
crucial for coset construction of new models from WZW-models (see
chapter 18 in \cite{difrancesco1997cft} for details).

Although the task of computation of branching coefficients by hand is
tedious, it is easily done by the computer.

For example, for branching of module $L^{[1,0,0]}$ of $A_2$ ($sl_3$
for complex algebras and $su_3$ for real) to sub-algebra $A_1$ ($sl_2$
or $su_2$) we have:
\begin{verbatim}
> wg:=weights(A2);
         e2    2 e1    e3                e2     e1    2 e3
 wg := [---- - ---- + ---- + lambda0, - ---- - ---- + ---- + lambda0, lambda0]
         3      3      3                 3      3      3

> tt1:=branching_rules(wg[-1],A2,A1,{e1=alpha[1]},15);
                                  tt1 := res

> tt1[lambda0];
           2      3      4       5       6       7       8       9       10
1 + q + 2 q  + 5 q  + 7 q  + 11 q  + 17 q  + 25 q  + 36 q  + 52 q  + 72 q

            11        12        13        14        15
     + 100 q   + 139 q   + 187 q   + 251 q   + 336 q

> tt1[lambda0+e1/2];
         2      3      4       5       6       7       8       9       10
2 q + 2 q  + 4 q  + 6 q  + 10 q  + 14 q  + 24 q  + 32 q  + 48 q  + 66 q

           11        12        13        14        15
     + 94 q   + 126 q   + 176 q   + 232 q   + 314 q  
\end{verbatim}
First several terms are in agreement with the example in section
14.7.2 of the book \cite{difrancesco1997cft}.

For branching of the same module to special sub-algebra $A_2^{(2)}$ we
get
\begin{verbatim}
> tt1:=branching_rules(wg[-1],A2,tA2,{e1=alpha[1]/2},15);
                                  tt1 := res

> tt1[lambda0];
                  4      6      8      10      12      14
             1 + q  + 2 q  + 3 q  + 4 q   + 7 q   + 8 q

> tt1[lambda0+e1/2];
                                   e1
                              res[---- + lambda0]
                                   2

> tt1[lambda0+e1];
                   3      5      7      9      11       13       15
            q + 2 q  + 2 q  + 4 q  + 5 q  + 8 q   + 11 q   + 16 q
\end{verbatim}
We see that this result is in agreement with the results from the paper \cite{ilyin812pbc}.

\section{Conclusion}
\label{sec:conclusion}
We described new algorithms for representations of affine Lie algebras
and implementation of that algorithms.

This implementation is work in progress, current version can be
downloaded from \url{http://anton.nazarov.name/affine}.

Further study is required for better performance of implementation.
Although big performance gain can be achieved for computation of
branching coefficient using the idea similar to folding of fan
\ref{sec:representations}, used
for efficient computation of string functions coefficients.

Also some additional algorithms for physical applications can be
implemented, for example for computation of fusion coefficients of
WZW-models (\ref{eq:5}). It is important to note the existence of ``Kac''
program \cite{Fuchs:1996dd} especially designed for computations in conformal field theory
models. The possibility of interoperability with ``Kac'' program
should be studied.

\bibliography{article}{}
\bibliographystyle{utphys}

\end{document}

### 2009-05-25 AffineLieAlgebras/ACMS2009/notes.tex
First commit to git for cross-computer access

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}
\begin{document}
\tableofcontents
\section{String theory}
\label{sec:string-theory}

Free relativistic particle action is equal to length of trajectory. 
\begin{equation}
  \label{eq:1}
  \begin{split}
  x^{\mu}(0)=x^{\mu}_0,\; x^{\mu}(1)=x^{\mu}_1\\
  S=\int_{0}^{1} \sqrt{\left(\frac{dx^{\mu}}{d\tau}^2\right)}d\tau
\end{split}
\end{equation}
There is Poincare invariance $x^{\mu}\to A^{\mu}_{\nu}x^{\nu}+ B^{\mu}$ and reparametrisation invariance $\tau\to f(\tau),\; x^{\mu}(\tau)\to x^{\mu}(f(\tau))$.

String action is the area of world-sheet:
\begin{equation}
  \label{eq:2}
  \begin{split}
    X^{\mu}(x^1,x^2),\; \mu=1\dots d\\
    S_N [X^{\mu}(x^1,x^2)]=\int \sqrt{det \frac{\partial X^{\mu}}{\partial x^a}\frac{\partial X^{\mu}}{\partial x^b}} dx^1 dx^2
  \end{split}
\end{equation}
This action is called Nambu action, and it is invariant under Lorenz transformations and reparametrisations.

Transition amplitude for string is given by following formula:
\begin{equation}
  \label{eq:3}
  A=\int {\cal D}X^{\mu}(x^1,x^2)e^{-S_N[X^{\mu}(x^1,x^2)]}
\end{equation}
The problem here is the definition of measure of integration. 
It is not strictly defined in most cases, so there is nothing unusual here.

We want to change ``integration variable'' in order to fix the arbitrariness connected with reparametrisations of world-sheet.

Obviously our theory should be invariant under reparametrisation:
\begin{equation}
  \label{eq:4}
  \begin{split}
    x^a \to f^a (x^1,x^2)\\
    X^{\mu}(x^1,x^2)\to \tilde{X}^{\mu}(x^1,x^2)=X^{\mu}(f^1(x^1,x^2),f^2(x^1,x^2))
  \end{split}
\end{equation}

But Nambu action is not invariant. So we will use equivalent Polyakov action, which has following form:
\begin{equation}
  \label{eq:5}
  \begin{split}
    S_P [g^{ab}(x^1,x^2), X^{\mu}(x^1,x^2)]=\int g^{ab}(x)\partial_a X^{\mu} \partial_b X^{\mu}\sqrt{g} \;d^2 x\\
    g=\det g_{ab}
  \end{split}
\end{equation}

Polyakov and Nambu actions are equivalent in the sense that equations of motion are the same after the exclusion of auxiliary field $g_{ab}$.
\begin{equation}
  \label{eq:6}
  \delta_{X}S_N=0 \Longleftrightarrow \left\{
      \begin{aligned}
        \delta_X S_P=0\\
        \delta_g S_P=0
      \end{aligned}
      \right.
\end{equation}
Polyakov action is invariant under Lorenz transformations and reparametrisations:
\begin{equation}
  \label{eq:7}
  \begin{split}
    x^a \to f^a (x^1,x^2)\\
    X^{\mu}(x^1,x^2)\to \tilde{X}^{\mu}(x^1,x^2)=X^{\mu}(f^1(x^1,x^2),f^2(x^1,x^2))\\
    g_{ab}(x)\to \tilde{g}_{ab}(x)=\frac{\partial f^{a_1}}{\partial x^{a}}\frac{\partial f^{b_1}}{\partial x^b} g_{a_1 b_1}(x)
  \end{split}  
\end{equation}

There is also one additional invariance, which is called conformal or Weyl invariance.
\begin{equation}
  \label{eq:8}
  \begin{split}
    g_{ab}(x)\to e^{\sigma(x)}g_{ab}(x)\\
    g\to e^{\sigma} g\\
    g^{ab}\to e^{-\sigma} g^{ab}\\
    S_P[e^{\sigma(x)} g_{ab}(x),X^{\mu}] = S_P[g_{ab}(x),X^{\mu}] 
  \end{split}
\end{equation}

So we have rather big freedom. For example, any metric on sphere can be obtained from one (constant) metric with reparametrisation and Weyl transformation.
\begin{equation}
  \label{eq:9}
  g_{ab}(x)=[e^{\sigma(x)}\hat{g}_{ab}]^{x^a\to f^a (x)}
\end{equation}
For surfaces of higher genus there are discrete families of equivalent metrics.

We could not preserve all the symmetries during quantization. So we choose to save Lorenz invariance and reparametrisation invariance and break conformal invariance. It is so called conformal anomaly.

\begin{equation}
  \label{eq:10}
  A=\int {\cal D}X^{\mu}(x^1,x^2)e^{-S_P[g_{ab},X^{\mu}(x^1,x^2)]}
\end{equation}

It is easy to see that norm is invariant under reparametrisations:
\begin{equation}
  \label{eq:11}
  \begin{split}
    \|\delta X^{\mu}\|^2 = \int \left(\delta X^{\mu}(x)\right)^2 \sqrt{g} d^2x\\
    \|\delta g_{ab}\|^2 = \int \delta g_{a_1 b_1}\delta g_{a_2 b_2} g^{a_1 a_2} g^{b_1 b_2} \sqrt{g}\; d^2x
  \end{split}
\end{equation}

To investigate what happens top Weyl invariance after quantization let's introduce so called effective action. We integrate out fields $X^{\mu}$ and get following result.
\begin{equation}
  \label{eq:12}
  e^{-S_X^{eff}[g_{ab}]} \overset{def}{=} \int {\cal D}X^{\mu} e^{-S_P [g_{ab},X]}
\end{equation}
\begin{equation}
  \label{eq:13}
  \begin{split}
    S^{eff}_X [e^{\sigma(x)} g_{ab}(x) ] = S_X^{eff}[g_{ab}]+\frac{d}{48\pi}W[g,\sigma]\\
    W[g,\sigma]=\int \left[ \frac{1}{2} g^{ab}\partial_a\sigma \partial_b\sigma+R[g]\sigma+\mu e^{\sigma}\right] \sqrt{g}\; d^2x
  \end{split}
\end{equation}
Here $R$ is scalar curvature of $g_{ab}$, and $\mu$ is a parameter depending on regularisation, for example for proper time regularisation $\mu=\frac{1}{4\pi\epsilon}$. The term $W[g,\sigma]$ is called Liouville's action.

{\bf Notice} $\int R[x] \sqrt{g}d^2x = 4\pi \chi_E$, $\chi_E=2-2h$, $\chi_E$ - Euler characteristic of the surface, $h$ - genus of the surface.

$W[g,\sigma]$  is called conformal anomaly.

Variance of action
\begin{equation}
  \label{eq:14}
  \begin{split}
    \delta S[g_{ab},X] = -\frac{1}{4\pi} \int  \delta g^{ab} T_{ab} \sqrt{g} \; d^2x\\
    g_{ab}\to g_{ab}+\delta g_{ab}
  \end{split}
\end{equation}
\begin{equation}
  \label{eq:15}
  \begin{split}
    g_{ab} \to e^{\sigma} g_{ab} \xrightarrow[\sigma \ll 1]{} (1+\delta\sigma) g_{ab}\\
    \delta S [g_{ab},X] = -\frac{1}{4\pi} \int \delta\sigma g^{ab} T_{ab} \sqrt{g}\, d^2 x
  \end{split}
\end{equation}
\begin{equation}
  \label{eq:16}
    \delta S =0 \Rightarrow g^{ab}T_{ab}=0
\end{equation}
We see that Weyl invariance is equivalent to tracelessness of energy-momentum tensor.

After the quantization we have
\begin{equation}
  \label{eq:17}
  g^{ab}\left< T_{ab} \right> = -\frac{d}{12} R[g]
\end{equation}
\begin{Def}
  {\bf Two dimensional conformal field theory} - is the theory that transforms as in (\ref{eq:13}).

  The factor before $W[g,\sigma]$ is called {\it central charge}.
\end{Def}

!!!!!!!!!

Why it is so? How this definition is connected with another definitions and properties of conformal field theory?

!!!!!!!!!

At this moment we have too much freedom in our Feynman integral (\ref{eq:10}). We have diffeomorphisms (\ref{eq:4}) and Weyl transformations (\ref{eq:8}). We will fix the gauge so that the metric is given by the formula 
\begin{equation}
  \label{eq:20}
  g_{ab}=[e^{\phi} \hat{g}_{ab}]^{f^a}
\end{equation}

Faddeev-Popov ghosts appear as usual after this procedure.

\begin{equation}
  \label{eq:19}
  \begin{split}
    A=\int {\cal D} X^{\mu}(x^1,x^2)e^{-S_P[g_{ab},X^{\mu}(x^1,x^2)]} = \\
    = \int {\cal D}\phi\; {\cal D}X\; \mathcal{D} B_{ab}\; \mathcal{D} C^a e^{-S_P [e^{\phi}\hat{g}_{ab},X]-
      S_{gh}[e^{\phi}\hat{g}_{ab},B,C]}
  \end{split}
\end{equation}
Here $B,C$ are ghost fields, $B_{ab}(X)$ is symmetric and traceless tensor. All the functional integrals use metric $e^{\phi}\hat{g}$. 
\begin{equation}
  \label{eq:21}
  S_{gh} = \int g^{ac} B_{ab} \nabla_c C^b \sqrt{g} \, d^2x
\end{equation}
We can fix Weyl invariance so that measures of integration over matter fields and ghosts fields in (\ref{eq:19}) don't depend on $\phi$. Then we get conformal anomaly in the exponent:
\begin{equation}
  \label{eq:22}
  A = \int \mathcal{D}_{e^{\phi} \hat{g}} \mathcal{D}_{\hat{g}} X \mathcal{D}_{\hat{g}} B_{ab} \mathcal{D}_{\hat{g}} C^a e^{-S_P [e^{\phi}\hat{g}_{ab},X]-S_{gh}[e^{\phi}\hat{g}_{ab},B,C]+\frac{d-26}{48\pi} W[\hat{g}_{ab},\phi]}
\end{equation}
$\frac{d}{48\pi}$ comes from matter fields, and $\frac{-26}{48\pi}$ from ghost fields, since both actions are actions of two-dimensional conformal field theory.

Ordinary bosonic string lives in 26-dimensional space and doesn't interact with Liouville's gravity. Such a string is called ``critical string'' since it can exist only in critical dimension. Other string models are called non-critical strings.

First integration in (\ref{eq:22}) is very inconvenient, since we integrate over $\phi$ with measure depending on $\phi$. This measure $\mathcal{D}_{e^{\phi}\hat{g}}\phi$ corresponds to interval
\begin{equation}
  \label{eq:23}
  \|\delta\phi\|^2_P = \int e^{\phi} (\delta\phi)^2 \sqrt{\hat{g}}\, d^2 x
\end{equation}
It is non-linear and is not invariant under the translations $\phi(x)\to \phi(x)+\eta(x)$.
So for some time this was a problem since nobody knew how to work with such objects.

But David-Distler-Kawai proposed to change action in order to take into account change of measure of integration to normal measure.

They conjectured that the amplitude can be written in the form
\begin{equation}
  \label{eq:24}
  A=\int \mathcal{D}_{\hat{g}}\phi\, \mathcal{D}_{\hat{g}} X\, \mathcal{D}_{\hat{g}} (B,C)\, e^{-S_P[\hat{g},X]-S_{gh}[\hat{g},B,C]-S_L[\hat{g},\phi]}
\end{equation}
where the measure $\mathcal{D}_{\hat{g}} \phi$ corresponds to the interval $\|\delta\phi\|^2_{DDK} = \int (\delta\phi)^2 \sqrt{\hat{g}}\, d^2x$ and it is invariant under the translations $\phi\to \phi+\eta$ ($\delta\phi\to \delta\phi$). 
$S_L$ here is Liouville's action with two undefined for now parameters $Q$ and $b$:
\begin{equation}
  \label{eq:25}
  S_L[\hat{g},\phi] = \frac{1}{8\pi} \int \left[ \frac{1}{2} \hat{g}^{ab} \partial_a \phi \partial_b \phi + QR\phi +\mu e^{2b\phi}\right] \sqrt{\hat{g}} \, d^2x
\end{equation}
We choose following normalization:
\begin{equation}
  \label{eq:26}
  \langle \phi(x) \phi(0) \rangle = \log |x|^2
\end{equation}
Liouville's term should be invariant under dilation $\hat{g}_{ab}\to e^{\sigma}\hat{g}_{ab}$.

After we put
\begin{equation}
  \label{eq:27}
  Q=\frac{1}{b}+b
\end{equation}
Liouville's action becomes conformal, so that
\begin{equation}
  \label{eq:28}
  \begin{split}
    \int \mathcal{D}_{\hat{g}} \phi e^{-S_L[\hat g,\phi]} = e^{-S_L^{eff}[\hat g]}\\
    S_L^{eff} [e^{\sigma}\hat{g}]=S_L^{eff}[\hat g] +\frac{C_L}{12} W[\hat g,\sigma]
  \end{split}
\end{equation}
Where
\begin{equation}
  \label{eq:29}
  C_L=1+6 Q^2
\end{equation}

Then we require total central charge to vanish:
\begin{equation}
  \label{eq:30}
  C_X+C_{gh}+C_L=C_{tot}=0
\end{equation}

Now the amplitude doesn't depend on $\hat{g}$ and parameters $Q$,$b$ are fixed.
\begin{equation}
  \label{eq:18}
  d+1+6\left(b+\frac{1}{b}\right)^2=26
\end{equation}
In some finite area we can assume
\begin{equation}
  \label{eq:31}
  \hat{g}_{ab}=\delta_{ab}
\end{equation}
There also could be additional term connected with the topology.

Let's change variables
\begin{equation}
  \label{eq:32}
  \begin{split}
    x^1+i\, x^2=z\\
    x^1-i\, x^2=\bar{z}\\
    (dx^1)^2+(dx^2)^2=dz\,d\bar{z}
  \end{split}
\end{equation}
For fields and terms of the action we have
\begin{equation}
  \label{eq:33}
  \begin{split}
    C^z=C,\; C^{\bar{z}}=\bar{C}\\
    B_{zz}=B, \; B_{\bar{z}\bar{z}}=\bar{B}\\
    S_{gh}=\int d^2z [B\bar{\partial}C+\bar{B}\partial \bar{C}]\\
    S_P[X]=\int d^2z \bar{\partial}X \partial X\\
    S_L[\phi] \propto \int d^2z \left[\bar{\partial} \phi \partial \phi+\mu e^{2 b \phi}\right] + \mbox{(topological terms)}
  \end{split}
\end{equation}
\begin{equation}
  \label{eq:34}
  e^{-S^{eff}[g]}=\int \mathcal{D} X e^{-\int g^{ab}\partial_a X \partial_b X \sqrt{g}\, d^2x} = \int \mathcal{D}_g X e^{-\int X \Delta X\sqrt{g}\, d^2x}
\end{equation}
Laplace operator depends on metric
\begin{equation}
  \label{eq:35}
  \Delta = \frac{1}{\sqrt{g}}\partial_a \sqrt{g} g^{ab}\partial_b
\end{equation}

It is self-conjugate operator.

We can represent field $X$ as combination of eigenfunctions of Laplace operator $X(x)=\sum c_n X_n,\; \Delta X_n = \lambda_n X_n,\; \lambda_n=\lambda_n[g]$. Then we will integrate over all eigenfunctions:
\begin{equation}
  \label{eq:36}
  e^{-S^{eff}[g]}=\left(\prod_{n} \lambda_n\right)^{-\frac{1}{2}}=(\det \Delta)^{-\frac{1}{2}}
\end{equation}
Obviously we could not calculate $\lambda_n$, but we can get the determinant.
\begin{equation}
  \label{eq:37}
  S^{eff}[g]=\log \det \Delta=tr \log \Delta
\end{equation}
\begin{equation}
  \label{eq:38}
  \log\frac{\lambda}{\lambda_0}=\int_0^{\infty}\frac{e^{-\lambda t}-e^{\lambda_0 t}}{t}dt
\end{equation}
\begin{equation}
  \label{eq:39}
  \delta S^{eff}[g]=tr (\log\Delta -\log\Delta_{g_0})=\delta tr \int_0^{\infty}\frac{e^{-\Delta t}}{t} dt
\end{equation}
The last integral diverges, so we need to regularise it. We will use heat kernel regularisation.
\begin{equation}
  \label{eq:40}
  \delta S^{eff}[g]=\delta tr \int_{\epsilon}^{\infty}\frac{e^{-\Delta t}}{t} dt  
\end{equation}
As we already mentioned, $\hat{g}_{ab}$ could be put equal to $\rho dz d\bar{z}$ in finite area. Then
\begin{equation}
  \label{eq:41}
  \Delta=\frac{1}{\rho}\bar{\partial}\partial
\end{equation}
For variation of effective action we have
  \begin{multline}
  \label{eq:42}
    \delta_{\rho}S^{eff}[g]=\delta_{\rho} tr \int_{\epsilon}^{\infty} e^{-\frac{1}{\rho}\bar{\partial}\partial t}\frac{dt}{t}=\\
    - tr \int_{\epsilon}^{\infty}\delta_{\Delta}e^{-\Delta t} dt=
    -tr \int_{\epsilon}^{\infty}\frac{\delta\rho}{\rho}\Delta e^{-\Delta t} dt=\\
    -tr \int_{\epsilon}^{\infty}\frac{\delta\rho}{\rho}\frac{d}{dt} e^{-\Delta t} dt=-tr \frac{\delta\rho}{\rho}e^{-\Delta \epsilon}
  \end{multline}

Let's introduce Green function for heat equation
\begin{equation}
  \label{eq:43}
  G(t,x,y)=\sum_n e^{-\lambda_n t}X_n(x) X_n(y)
\end{equation}
\begin{equation}
  \label{eq:44}
  \begin{split}
    \frac{\partial G}{\partial t}=\Delta_x G(t,x,y)\\
    G(o,x,y)=\delta^2 (x-y)\\
    G(t,x,x)=\frac{1}{4\pi t}+aR+O(t)
  \end{split}
\end{equation}
Then for variation of action we have
\begin{equation}
  \label{eq:45}
  \delta S^{eff}[g]=\int d^2x \frac{\delta\rho}{\rho}\left(\frac{1}{4\pi\epsilon}+aR\right)
\end{equation}

!!!! !!!! !!!! !!!! 
Be more elaborate here.
!!!!!!!

...
\section{CFT}
\label{sec:cft}

In Conformal Field Theory 
\begin{equation}
  \label{eq:46}
  g^{ab}\left<T_{ab}\right>=\frac{C}{12}R[g]
\end{equation}
$C$ is a central charge.

For flat metric $g_{ab}=\delta_{ab}$ we have
\begin{equation}
  \label{eq:47}
  g^{ab}\langle T_{ab} \rangle=0
\end{equation}
Then we put $T_{zz}=T,\quad T_{\bar{z}\bar{z}}=\bar{T},\quad T_{z\bar{z}}=T_{\bar{z}z}$. In flat space from continuity equation $\bar{\partial}T_{zz}+\partial T_{\bar{z}\bar{z}}=0$ we have
\begin{equation}
  \label{eq:49}
  \begin{split}
    T_{z\bar{z}}=0\\
    \bar{\partial}T_{zz}=\bar{\partial}T=0,\quad T \mbox{- holomorphic}\\
    \partial T_{\bar{z}\bar{z}}=\partial \bar{T}=0,\quad \bar{T} \mbox{- antiholomorphic}\\
  \end{split}
\end{equation}
In curved space continuity equation reads $\nabla_a T^{ab}=0$ and we can choose coordinate system where $g_{ab}dx^a dx^b = \rho dz\, d\bar{z}=e^{\sigma}dz\,d\bar{z}$. Then we introduce pseudo energy $T$:
\begin{equation}
  \label{eq:50}
  T_{zz}+\frac{C}{12}t_{zz}=T
\end{equation}
where $t_{zz}=(\partial \sigma)^2-2\partial^2 \sigma$. It is easy to check that $\bar{\partial}T=0$ in this case.

For transformations $z\to w(z)$
\begin{equation}
  \label{eq:51}
  \begin{split}
    T_{zz}\to \left(\frac{dw}{dz}\right)^2 T_{ww}(w(z))\\
    t\to \left(\frac{dw}{dz}\right)t(w)+2\{w,z\}\\
    \mbox{where}\; \{w,z\}=\left(\frac{\partial_z^3 w}{\partial_z w}-\frac{3}{2}\left(\frac{\partial_z^2 w}{\partial_z}\right)^2\right)\\
    T\to \left(\frac{dw}{dz}\right)^2 T(w)+\frac{C}{12}\{w,z\}\\
  \end{split}
\end{equation}
Energy-momentum tensor is the generator of coordinate transformations $x^a\to x^a+\epsilon^a(x)$:
\begin{equation}
  \label{eq:52}
  \delta_{\epsilon}\langle A_1(x_1)\dots A_N(x_N)\rangle = \int d^2x\, \partial_a \epsilon_b(x)\langle T_{ab}(x) A_1(x_1)\dots A_N(x_N)\rangle
\end{equation}

\begin{equation}
  \label{eq:53}
  \begin{split}
    T_{aa}=0\\
    \partial_a \epsilon_b+\partial_b \epsilon_a\sim \delta_{ab}\\
    \epsilon^a=\epsilon x^a \;\mbox{or}\; x^a\to \frac{x^a}{(\vec x)^2}
  \end{split}
\end{equation}
Correlation functions don't change under conformal transformations.
\begin{equation}
  \label{eq:54}
  \delta_{\epsilon}A(x)=\int_{\partial D} dy^a\, \epsilon^b \tilde{T}_{ab}(y)A(x)-\int_{D}d^2y\, \partial^a \epsilon^b(y)T_{ab}(y)A(x)
\end{equation}
Where $\tilde{T}_{ab}=\epsilon_{ac}T_{cb}$.

Let
\begin{equation}
  \label{eq:55}
  \begin{split}
    \partial_a \epsilon_b+\partial_b \epsilon_a\sim \delta_{ab}\\
    \bar{\partial}\epsilon=0\\
    z\to z+\epsilon(z,\bar{z})\\
    \bar{z}\to\bar{z}+\bar{\epsilon}(z,\bar{z})
  \end{split}
\end{equation}
\begin{equation}
  \label{eq:56}
  \delta_{\epsilon}A(z,\bar{z})=\oint_z du\, \epsilon(u) T(u) A(z,\bar{z})
\end{equation}
Substituting $T(z)$ in place of arbitrary operator $A$ we get 
\begin{equation}
  \label{eq:57}
  \delta_{\epsilon}T(z)=\oint_z du\, \epsilon(u)T(u)T(z)
\end{equation}

If $w(z)=z+\epsilon(z)$ where $\epsilon$ is small, $T$ transforms as following:
\begin{equation}
  \label{eq:58}
  T(z)\to \epsilon T'(z) + 2\epsilon' T(z)+\frac{C}{12}\epsilon'''
\end{equation}
\begin{equation}
  \label{eq:59}
  \delta_{\epsilon}T(z)=\oint du\, \epsilon(u) T(u) T(z) = \epsilon T'(z) + 2\epsilon' T(z)+\frac{C}{12}\epsilon'''
\end{equation}
We suppose that for full set of operators $\{A_j(x)\}$ there exists operator product expansion:
!!! How can it be proved ????
\begin{equation}
  \label{eq:60}
  A_i(x)A_j(0)=\sum C^k_{ij}(x)A_k(0)
\end{equation}
Then for product $T(u)T(z)$ we have
\begin{equation}
  \label{eq:61}
  T(u)T(z)=\sum C_k(u-z) A_k(z)
\end{equation}
We can recover the poles from formula (\ref{eq:59}):
\begin{equation}
  \label{eq:62}
  T(u)T(z)=\frac{C}{2(u-z)^4}+\frac{2T(z)}{(u-z)^2}+\frac{T'(z)}{u-z}+\mbox{non-singular terms}
\end{equation}
Now introduce the operators $L_n$:
\begin{equation}
  \label{eq:63}
  L_n A(z)\equiv \frac{}{2\pi i}\oint_{C}du\, (u-z)^{n+1}T(u)A(z)
\end{equation}
It is possible to show that for $n,m\in \mathbb{Z}$
\begin{equation}
  \label{eq:64}
  [L_n,L_m]=(n-m) L_{n+m}+\frac{C}{12}(n^3-n)\delta_{n,-m}
\end{equation}
and $\{L_n\}$ constitute Virasoro algebra.

All the fields in the theory are sums of multiplets of Virasoro algebra:
\begin{equation}
  \label{eq:65}
  \{A_j\}=\sum [\Phi_{\Delta,A}] %%% It is incorrect, fix this formula
\end{equation}

There is a primary field in every multiplet:
\begin{equation}
  \label{eq:66}
  \begin{split}
    \Phi_{\Delta}(z)\underset{z\to w(z)}{\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\Phi_{\Delta}(w(z))\\
    L_n \Phi=0,\quad n>0\\
    L_0 \Phi=\Delta \Phi\\
  \end{split}
\end{equation}
All other fields are built of primary fields and are called secondary:
\begin{equation}
  \label{eq:67}
  L_{-n_1}L_{-n_2}\dots \Phi_{\Delta}
\end{equation}

Correlation functions are expressed as combinations of correlation functions of primary fields.

The only thing that is yet undefined is the set of scaling dimensions of primary fields. So to fix the theory we should define $\Phi_a,\; \Delta_a,\; C^c_{ab}$. Then our theory is solved. If the number of primary fields is finite, such a model is called {\it minimal}.

For example, following fields are Weyl-invariant:
\begin{equation}
  \label{eq:68}
  O_a=\int \Phi_{\Delta}e^{2a\phi}\,d^2x,\quad \mbox{where}\;\Delta+a(Q-a)=1
\end{equation}
$O_a$ - is the main observable of string theory with gravitational dimension $\delta_a=-\frac{a}{b}$.
\begin{equation}
  \label{eq:69}
  \int\langle O_{a_1}\dots O_{a_n}\rangle_{\mu} e^{-\mu A}d\mu=\langle O_{a_1}\dots O_{a_n}\rangle_{A}=A^{\sum \delta_k},\quad \delta_k=\frac{a_k}{b}
\end{equation}

\subsection{Conclusion}
\label{sec:conclusion}

We can start from arbitrary conformal field theory, find $b$ from equation $C+6\left(b+\frac{1}{b}\right)^2=25$ and obtain some non-critical string theory. But for $d>1$ $b$ becomes complex and this fact leads to unsolved yet problems.

\section{Conformal Field Theory}
\label{sec:conf-field-theory}

\section{Affine Lie algebras representations}
\label{sec:affine-lie-algebras}

\subsection{Verma modules}
\label{sec:verma-modules}

Verma module is a simple thing. It can be easily understood in the framework of induced representations.

Verma module with highest weight $\lambda$ of algebra $g$ is the space $U(g)\underset{U(b_{+})}{\otimes} D_{\lambda}(b_{+})$, where $\underset{U(b_{+})}{\otimes}$ means that the action of elements of $U(b_{+})$ ``falls through'' left part of tensor product onto the right part.

Here $b_{+}$ is Borel sub-algebra ($x_{+},h$ for $sl(2)$), $D_{\lambda}(b_{+})$ is special representation of $b_{+}$, such that $D(x_{+})=0,\; D(h)=\lambda(h)$.
$g$ acts on the representation space from the left, it means that we should expand element of $g$ in some base, and then commute all the elements of $b_{+}$ to the right, so that they can act on space $D_{\lambda}(b_{+})$.

The infinite set of fields (\ref{eq:65}) corresponds to Verma module of algebra, which is Virasoro algebra in the simplest case and semidirect product of Virasoro and Kac-Moody algebra for WZW model. Also it is shown that for Wess-Zumino model the representations of the algebra are in fact the representations of current algebra only, which is Kac-Moody algebra.

Note also, that Viraso algebra belongs to universal enveloping of Kac-Moody algebra.

\subsection{Irreducible representations}
\label{sec:irred-repr}

\end{document}

### 2009-05-25 AffineLieAlgebras/ACMS2009/presentation.tex
First commit to git for cross-computer access

\documentclass{beamer} 
\usepackage{amsmath,amssymb,amsthm} 
\usepackage{pb-diagram}
\usepackage{ucs} \usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
\usepackage{graphicx}
\usepackage{multicol}

%\pagestyle{plain}

\theoremstyle{definition} \newtheorem{Def}{Definition}
\setbeamertemplate{caption}[numbered]
\newcommand{\tr}{\hat\triangleright} \newcommand{\trc}{\triangleright}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

\usetheme{AnnArbor}
\title[Affine Lie algebra computations]{Computational tools for representation theory of affine Lie algebras}
\author{Anton Nazarov}
\institute[SPbSU]{
  Department of high-energy physics\\
  Saint-Petersburg State University}

\date[ACSM 2009] % (optional, should be abbreviation of conference name)
{Workshop on Advanced Computer Simulation Methods for Junior scientists, April 2009}
\begin{document}
\maketitle
\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

\section{Representation Theory}
\label{sec:repr-theory}
\begin{frame}{Lie Algebras}
  \begin{Def}
    {\bf Lie algebra} --- linear space $g$ with Lie bracket $ \left[ \ \right]:g\times g \to g $
  \end{Def}
  \pause 
  \begin{itemize}
  \item Why Lie algebras are interesting?
    \begin{itemize}
      \pause 
    \item Infinitesimal version of continuous symmetry groups
      \pause 
    \item Connected with different areas of mathematics: differential equations, geometry, topology etc
      \pause
    \end{itemize}
  \item Classification of finite dimensional algebras
    \pause
  \item Several ways to extend the classification to infinite-dimensional Lie algebras
    \pause
  \item Affine Lie algebras --- the simplest class of infinite-dimensional Lie algebras
    \begin{itemize}
    \item Play major role in conformal field theory
    \item Are connected with modular forms
    \item Can be constructed starting from simple finite-dimensional Lie algebras
    \end{itemize}

  \end{itemize}

\end{frame}
\begin{frame}{Representations}
  \begin{Def}
    {\bf Representation} --- homomorphism from Lie algebra to linear operators on some linear space
  \end{Def}
  \begin{itemize}
  \item In physics we are interested in representations
  \item The representations can be constructed in regular way
    \begin{itemize}
    \item Integrable highest weight representations
      \begin{equation}
        \label{eq:1}
        \begin{split}
          & E^{\alpha}\left|\mu\right>=0\\
          & E^{-\alpha}\left|\mu\right>=\left|\mu-\alpha\right>\\
          & L^{\mu}=\bigoplus_{\nu\in P} V^{\nu}\\
        \end{split}
      \end{equation}
    \item The problem is to calculate weight multiplicities (subspace dimensions)
    \end{itemize}
  \item Branching --- view the representation of algebra as the sum of representations of sub-algebra
  \end{itemize}
\end{frame}
\section{Algorithms}
\label{sec:algorithms}
\begin{frame}{Main Formulae}
  \begin{itemize}
  \item Recurrent relation for weight multiplicities
    \begin{equation}
      \label{eq:2}
      mult(\xi)=-\sum_{w\in W\backslash e}det(w)\;mult(\xi+\rho-w\rho)+\sum_{w\in W}det(w)\delta_{\xi,w(\mu+\rho)-\rho}
    \end{equation}
  \item Branching of representation to representations of sub-algebra
    \begin{equation}
      \label{eq:4}
      L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
        }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }
    \end{equation}
    \begin{equation}
      \label{recurrent-relation}
      k_{\xi }^{\left( \mu \right) }=\frac{-1}{s\left( \gamma _{0}\right) }\left(
        \sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
          \left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
          \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right)   
    \end{equation}
    \begin{equation}
      \label{eq:5}
      b_{\nu }^{\left( \mu \right) }=k_{\xi }^{\left( \mu \right) } \text{ for }\nu\text{ in main Weyl chamber}
    \end{equation}
  \end{itemize}
\end{frame}
\begin{frame}{Illustration}
Computation of weight multiplicities of level 1
representation of algebra $A_1$
  \begin{figure}[bh]
  \noindent\centering{
  \includegraphics[width=110mm]{A1_with_star.pdf}
  }
  \label{A1 with star}
\end{figure}

\end{frame}
\section{Implementation}
\label{sec:implementation}
\begin{frame}{Maple Package}
  \begin{itemize}
  \item Based upon Coxeter/Weyl package which is very useful for finite dimensional Lie algebras\\
    \url{http://www.math.lsa.umich.edu/~jrs/maple.html}
  \item For untwisted $A_n,B_n,C_n,D_n$ and twisted $A_n^{(2)},D_n^{(2)}$ series of affine Lie algebras
    \begin{itemize}
    \item Explicit construction of
      \begin{itemize}
      \item algebra roots
      \item fundamental and dominant weights
      \item Weyl reflections
      \end{itemize}
    \item Computation of
      \begin{itemize}
      \item weight multiplicities
      \item branching coefficients for affine sub-algebra
      \end{itemize}
    \end{itemize}
  \item Freely available from my homepage \url{http://anton.nazarov.name/affine}
  \end{itemize}
\end{frame}
\begin{frame}[fragile]
  \frametitle{Examples}
  \begin{itemize}
  \item Weight multiplicities of level 2 representation of $A_3$ with highest weight $\alpha_1+\alpha_2+\alpha_3$
\begin{verbatim}
> al:=algebra_roots(A3);
      al := [e2 - e1, e3 - e2, e4 - e3, delta + e1 - e4]
> mu:=2*lambda0+sum(al[i],i=1..3);
      mu := -e1 + e4 + 2 lambda0
> string_function(mu,mu,A3,30);
[1, 7, 32, 117, 371, 1063, 2819, 7029, 16660, ...
\end{verbatim}
  \item Branching functions of module $L^{[1,0,0]}$ of $A_2$ to sub-algebra $A_1$ 
\begin{verbatim}
> tt1:=branching_rules(wg[-1],A2,A1,{e1=alpha[1]},15);
> tt1[lambda0];
           2      3      4       5       6       7 
1 + q + 2 q  + 5 q  + 7 q  + 11 q  + 17 q  + 25 q  + ...
> tt1[lambda0+e1/2];
         2      3      4       5       6       7   
2 q + 2 q  + 4 q  + 6 q  + 10 q  + 14 q  + 24 q  + ...
\end{verbatim}
  \end{itemize}

\end{frame}
\section{Summary}
\label{sec:summary}
\begin{frame}{Summary}
  \begin{itemize}
  \item The algorithms for representation theory of affine Lie algebra were presented
  \item Maple implementation was described
  \item \url{http://anton.nazarov.name/affine}
  \end{itemize}
  \vskip0pt plus.5fill
  \begin{itemize}
  \item
    Outlook
    \begin{itemize}
    \item
      Expand the code to cover affine extensions of exceptional Lie algebras
    \item
      Add the algorithms for computations for physical models of conformal field theory
    \end{itemize}
  \end{itemize}
\end{frame}

\bibliography{article}{}
\bibliographystyle{utphys}

\end{document}

### 2009-05-25 AffineLieAlgebras/ACMS2009/article.tex
Some textwork on folding, nothing really useful

@@
 
-Kac-Peterson formula is less efficient and is not discussed here.
-
 We use new method proposed in the articles
@@
 weights from main Weyl chamber.
+
+\subsection{Folding}
+\label{sec:folding}
+
+To facilitate computation of branching coefficients we can use the
+idea similar to one used for computation of weight multiplicities.
+There we were able to fold the star so that all the recurrent
+computation took place in main Weyl chamber.
+
+We use the formula (\ref{eq:2}). The summation in the first term of
+right-hand side goes through the set of weights $\{\xi+\pi-\omega
+\rho\;|\;\omega\in W\backslash e\}$
 

### 2009-05-26 AffineLieAlgebras/ACMS2009/article.tex
Some additions on folding

@@
 right-hand side goes through the set of weights $\{\xi+\pi-\omega
-\rho\;|\;\omega\in W\backslash e\}$
+\rho\;|\;\omega\in W\backslash e\}$.
+But for each weight $\zeta$ outside the main Weyl chamber there exists
+weight $\zeta_0$ in main Weyl chamber and $\omega\in W$ such that
+$\zeta=\omega \zeta_0$. So to calculate the multiplicity of $\xi$ we
+sum over the set of weights inside the main Weyl chamber.
+
+The question is if it is possible to introduce the same procedure for
+computation of branching coefficients.
 

### 2009-06-25 AffineLieAlgebras/SYMPHYS2009/abstract.tex
SYMPHYS abstract added

\documentclass{article}

\addtolength{\textheight}{-10mm}
\addtolength{\topmargin}{-5mm}

\pagestyle{plain}

\def\title#1{\begin{center}#1\end{center}}

\def\author#1{\centerline{\small{\textsc{#1}}}}

\def\address#1#2{\begin{center}\small\emph{#1}\\E-mail: \texttt{#2}\end{center}}

\def\refname{{\small References}}

\begin{document}
\title{\textsc{Reduction of representations of affine Lie algebra to affine sub-algebra and applications to CFT}}
%\footnote{This work is supported by etc, etc.}}

\author{A.~Nazarov}

\address{Department of High Energy and Elementary Particles Physics, \\ Saint-Petersburg State University\\
Ulyanovskaya str. 1, Petrodvorets., \\
198504 St-Petersburg, Russia}{antonnaz@gmail.com}

\bigskip

\small

   It was demonstrated \cite{ilyin812pbc} that decompositions of integrable highest weight
modules of a simple Lie algebra with respect to its reductive subalgebra
obey the set of algebraic relations leading to the recursive properties for
the corresponding branching coefficients. These properties can be used to formulate an algorithm for explicit computation of branching coefficients.

The algorithm for reduction of representation of affine Lie algebra to representation of affine sub-algebra is described. The use of Weyl symmetry allows to compute branching coefficients only in closure of main Weyk chamber. It gives the opportunity of efficient computation of branching coefficients.

Reduction of representations has several applications in two-dimensional conformal field theory. We discuss the examples of the applications of reduction of representations to construction of modular invariants of Wess-Zumino-Novikov-Witten models.

\begin{thebibliography}{5}\footnotesize

\bibitem{ilyin812pbc}
M.~Ilyin, P.~Kulish, and V.~Lyakhovsky, ``{On a property of branching
  coefficients for affine Lie algebras},'' {\em Algebra i Analiz} {\bf 21:2}

\bibitem{kulish4sfa}
P.~Kulish and V.~Lyakhovsky, ``{String Functions for Affine Lie Algebras
  Integrable Modules},'' {\em Symmetry, Integrability and Geometry: Methods and
  Applications} {\bf 4}

\bibitem{Nazarov2009}
A.~Nazarov, ``Computational tools for representation theory of affine Lie algebras,'' in {\em Workshop on Advanced Computer Simulation Methods for Junior Scientists}, Saint-Petersburg 2009.

\end{thebibliography}

\end{document}

### 2009-07-01 affine-lie-algebras/summary.tex
Symlink test

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
\usepackage{ucs} \usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
\usepackage{cmap}
\pagestyle{plain}

\theoremstyle{definition} \newtheorem{Def}{Определение}

\newcommand{\tr}{\hat\triangleright}
\newcommand{\trc}{\triangleright}
\newcommand{\adk}{a^{\dagger}_{\kappa}} 
\newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} 
\def\F{\mbox{$\cal F$}}
\begin{document}

\section{Начальные сведения}
\subsection{Про алгебры Ли}
\label{sec:Lie}

\begin{Def} {\it Внутренний автоморфизм} - который можно записать в виде $Ad(e^x),\ x\in g$
\end{Def}
\begin{Def} {\it Ранг} $g$ - размерность подалгебры Картана
\end{Def}

Присоединенное действие подалгебры Картана диагонализуемо.

Алгебра раскладывается в прямую сумму собственных подпространств относительно действия подалгебры Картана: $g=h\bigoplus_{\alpha}g_{\alpha},\ g_{\alpha}=\{X:[H.X]=\alpha(H)X\}$

$\alpha\in h^*$ - корень, $g_{\alpha}$ - корневое пространство, $X\in g_{\alpha}$ - корневой вектор
$\Delta$ - набор всех корней, $\Delta_0$ - с нулем

\begin{Def}
  $ B(X,Y)=tr_g (ad(X)ad(Y))$
\end{Def}

$h$ и $h^*$ изоморфны посредством $\left.B\right|_{h\times h}$, $H_{\alpha}\leftrightarrow \alpha:\ B(H_{\alpha},H)=\alpha(H)$

$B(X_{\alpha},X_{-\alpha})=1$
$s_{\alpha}=\mathbb{C}H_{\alpha}\oplus $

Регулярный элемент $H\in h:\ \alpha(H)\neq 0$ для всех $\alpha$.

Возьмем регулярный элемент $H_0$, тогда $\alpha(H_0)$ положительно или отрицательно, соответственно положителен или отрицателен корень $\alpha$.

$\alpha\neq \beta+\gamma \Rightarrow \alpha$ - фундаментальный или простой корень

Число фундаментальных корней $\alpha_i$ равно размерности $h$, то есть рангу $g$
$B(\alpha_i,\alpha_j)\leq 0$

\begin{Def}
$a_{ij}=\alpha_j(H_i)=\frac{2\alpha_j(H_{\alpha_i})}{\alpha_i(H_{\alpha_i})}=\frac{2B(\alpha_i,\alpha_j)}{B(\alpha_i,\alpha_i)}$ - матрица Картана, она обладает следующими свойствами:
\begin{itemize}
\item $a_{ij}$ - целые
\item $a_{ii}=2$
\item $i\neq j \Rightarrow a_{ij}\leq 0$
\item $a_{ij}=0 \Leftrightarrow a_{ji}=0$
\end{itemize}
\end{Def}

$B := B(\alpha_i,\alpha_j)$- положительно определенная симметричная матрица
$D=\frac{2\delta_{ij}}{B(\alpha_i,\alpha_i)}$ - положительная диагональная матрица
Тогда $A=DB$

В этом случае матрица Картана называется картановской матрицей конечного типа.

\begin{Def}
{\it Диаграммы Дынкина}
\begin{itemize}
\item $\alpha_1\dots \alpha_l \leftrightarrow \bigcirc$
\item для каждой пары $i,j$ соединяем $i$-ую и $j$-ую вершины $max(|\alpha_{ij}|,|\alpha_{ji}|)$ линиями
\item если $i\neq j$ и $\alpha_{ij}\leq -2$,то надо нарисовать стрелку от $j$ к $i$ 
\end{itemize}
\end{Def}

\[
a=
\left(
\begin{array}{cc}
2 & -2 \\
-1 & 2 \\
\end{array}
\right)
\]
\[
\begin{diagram}
  \node{\bigcirc} 
  \node{\bigcirc} \arrow{w,t,}{}
\end{diagram}
\]

Здесь надо нарисовать диаграммы для всех типов алгебр Ли

Что такое аффинные алгебры
\subsubsection{Матрица Картана}

\begin{Def}
  {\bf Матрица Картана} $nxn$, ранг $l$, $a_{ij}: a_{ii}=2, a_{ij}\leq 0, a_{ij}=0\Rightarrow a_{ji}=0$
\end{Def}
\begin{Def}
  {\bf Реализация матрицы $A$}: $h,\Pi,\Pi^{v}$, где $h$ -
  n-мерное комплексное векторное пространство,
  $\Pi=\{\alpha_1,\dots,\alpha_n\in h^{*}\}$,
  $\Pi^{v}=\{\alpha_1^v,\dots \alpha_n^v \in h\}$, $\Pi,\Pi^v$ -
  линейно независимы, $<\alpha_i^v,\alpha_j>=a_{ij}$, $dim\ h - n=n-l$
\end{Def}
\section{Конформная теория поля и аффинные алгебры Ли}

\subsection{Конформная теория поля}
\label{sec:--CFT-Intro}

Общий вид преобразований 
\begin{equation}
  \label{eq:1}
  g_{\mu\nu}(x)\to g'_{\mu\nu}(x')=\Omega(x)g_{\mu\nu}(x)
\end{equation}
Бесконечно малое преобразование
\begin{eqnarray}
  \label{eq:2}
  x'_{\mu}=x_{\mu}+\epsilon_{\mu}\\
  \partial_{\mu}\epsilon_{\nu}+\partial_{\nu} \epsilon_{\mu}=\frac{2}{d}(\partial\cdot \epsilon)\eta_{\mu\nu}
\end{eqnarray}
В плоском двумерном пространстве $\partial_1\epsilon_1=\partial_2\epsilon_2\;;\; \partial_2\epsilon_1=-\partial_1\epsilon_2$, поэтому можно всё переписать так: $z,\bar{z}=x_1\pm ix_2\; ; \;\epsilon(z)=\epsilon_1+i\epsilon_2\;;\; \epsilon(\bar{z})=\epsilon_1-i\epsilon_2$
Преобразования запишутся как
\begin{eqnarray}
  \label{eq:4}
  z\to f(z)\\
  \bar{z}\to f(\bar{z})\\
  ds^2=dz d\bar{z}\to \left|\frac{\partial f}{\partial z}\right|^2 dz d\bar{z}\\
  \Omega=\left|\frac{\partial f}{\partial z}\right|^2
\end{eqnarray}
Генераторы преобразований 
\begin{eqnarray}
  \label{eq:5}
  l_n=-z^{n+1}\partial_z\\
  \bar{l_n}=-\bar{z}^{n+1}\partial_{\bar{z}}\\
  \left[l_m,l_n\right]=(m-n)l_{m+n}\\
  \left[\bar{l}_m,\bar{l}_n\right]=(m-n)\bar{l}_{m+n}\\
  \left[l_m,\bar{l}_n\right]=0
\end{eqnarray}

          % \begin{diagram}
          %   \node{H} \arrow{e,t}{\epsilon} \node{k} \node{k}
          %   \arrow{e,r}{\eta} \arrow{se,r}{\eta\otimes\eta}
          %   \node{H}\\
          %   \node{H\otimes H} \arrow{n,r}{\mu}
          %   \arrow{ne,r}{\epsilon\otimes\epsilon} \node[3]{H\otimes
          %     H} \arrow{n,r}{\Delta}
          % \end{diagram}
          % \]
\begin{displaymath}
\begin{diagram}
  \node{\mbox{Топология}} \arrow{e,t}{} \node{\mbox{Действие WZW}} \\
  \node{} \arrow[2]{e,t}{\mbox{Токи, конструкция Сугавары}} \node[3]{\mbox{Алгебры Вирасоро на аффинную алгебру}}
\end{diagram}
\end{displaymath}
\begin{list}{Questions}{}
\item Связь со струнами?
\item Другие топологии?
\item В каких случаях возникают более общие алгебры Каца-Муди?
\end{list}
\subsection{Топология WZW}
Действие WZW записывается в терминах отображения $\gamma : \mathbb{R}^2\to G$, где $G$ - компактная простая группа Ли.
$G$ обладает следующим свойством: $\pi_1(G)=\pi_2(G)=0$, $\pi_3(G)=\mathbb(Z)$
\begin{Def}
  {\it Гомотопическая группа} $\pi_n(X)$ -  группа классов эквивалентности отображений $S^n\to X$. Два отображения гомотопически эквивалентны, если одно переводится в другое непрерывной деформацией, 
т.е. для $f_1,f_2, \exists \phi:S^n\times [0,1]\to G : \phi(x,0)=f_1(x), \phi(x,1)=f_2(x)$

The concept of composition that we want for the n-th homotopy group is the same, except that now the domains
that we stick together are cubes, and we must glue them along a face. We therefore define the sum of maps
 $f,g : [0,1]^n → X$ by the formula $(f + g)(t[1], t[2], ... t[n]) = f(2t[1], t[2], ... t[n])$ for t[1] in [0,1/2]
and $(f + g)(t[1], t[2], ... t[n]) = g(2t[1]-1, t[2], ... t[n]) $for t[1] in [1/2,1]. For the corresponding
definition in terms of spheres, define the sum $f + g$ of maps $f, g : S^n \to X$ to be $\psi$ composed with $h$, where $\psi$
is the map from $S^n$ to the wedge sum of two n-spheres that collapses the equator and h is the map from the
wedge sum of two n-spheres to X that is defined to be f on the first sphere and g on the second.

\end{Def}
\begin{Def}
  {\it Группа гомологий}
\end{Def}
\begin{list}{Homotopy-Homology}{}
\item По теореме Гуревича (Hurewicz) гомотопические группы связаны с гомологиями: а именно, если $\pi_k(X)$ нулевые при k меньших n, то $\pi_n(X)=H_n(X)$, либо, если $n=1$, то $\pi_1(X)/[\pi_1(X),\pi_1(X)]=H_1(X)$. 
\end{list}

   2. Далее, гомологии связаны с когомологиями -- двойственность Пуанкаре, если угодно -- в статье речь     
*     идет, кажется, о группе Ли, она ориентируема, в этом контексте двойственность Пуанкаре выглядит       
      особенно просто.                                                                                      
   3. Ранги целочисленных когомологий совпадают с размерностями вещественных когомологий.                   
   4. Последние могут быть вычислены с помощью, например, комплекса де Рама (теорема де Рама).              
   5. А по теории Ходжа (Hodge) в каждом классе когомологий де Рама есть ровно одна гармоническая форма (в  
      статье, кстати, направильное определение, правильное такое: это форма, которая зануляется оператором  
      Лапласа).

\end{document}

### 2009-07-05 AffineLieAlgebras/ACMS2009/notes.tex
Added section on WZW-models to notes, but it is in Russian.

@@
 \usepackage{ucs}
-%\usepackage[utf8x]{inputenc}
-%\usepackage[russian]{babel}
+\usepackage[utf8x]{inputenc}
+\usepackage[russian]{babel}
 \usepackage{cmap}
@@
 \end{equation}
-
 \subsection{Conclusion}
@@
 But for $d>1$ $b$ becomes complex and this fact leads to unsolved yet problems.
+
+\subsection{Модели Весса-Зумино-Новикова-Виттена}
+\label{sec:WZNW}
+Модели Весса-Зумино-Новикова-Виттена - это простейшие не минимальные модели двумерной конформной теории поля.
+Алгебра симметрии в них представляют собой полу прямое произведение алгебры Вирасоро и аффинной алгебры Ли.
+
+Эти модели допускают формулировку в терминах действия и лагранжиана, причём вид действия связан с топологией \cite{witten1984nab}.
+Кроме того, модели связаны с пределом бесконечного числа ароматов фермионов в квантовой теории поля.
+
+Модели Весса-Зумино-Новикова-Виттена подробно рассматриваются в литературе, материал этого раздела основан на обзоре \cite{Walton:1999xc} и главе 15 книги \cite{difrancesco1997cft}.
+
+Действие моделей Весса-Зумино-Новикова-Виттена записывается в виде
+\begin{equation}
+  \label{eq:2}
+  \begin{split}
+  S(\gamma)= &-\frac{k}{8\pi}\int \mathcal{K} (\gamma^{-1}\partial^{\mu}\gamma,\gamma^{-1}\partial_{\mu}\gamma) d^2x \\
+  &- \frac{k }{24\pi} \int_{B}\epsilon^{ijk} \mathcal{K}\left(
+    \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^i},\left[
+      \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^j},
+      \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^k}\right]\right) d^3y
+\end{split}
+\end{equation}
+где $\gamma$ - поле на комплексной плоскости со значениями в компактной связной группе Ли $G$ с простой алгеброй $g$, а $\mathcal{K}$ - форма Киллинга алгебры $g$, $\tilde \gamma$ - аналитическое продолжение $\gamma$ на внутренность двумерной сферы, в которую отображается комплексная плоскость.
+
+Уравнения движения имеют вид
+\begin{equation}
+  \label{eq:3}
+  \partial^{\mu}(\gamma^{-1}\partial_{\mu}\gamma)+i\epsilon_{\mu\nu}\partial^{\mu}(\gamma^{-1}\partial^{\nu}\gamma)=0
+\end{equation}
+После перехода к комплексным координатам $z,\bar z$ и введения токов $J=-k\partial_z\gamma\gamma^{-1},\; \bar J=k\gamma^{-1}\partial_{\bar z}\gamma$ уравнения принимают вид
+\begin{equation}
+  \label{eq:4}
+  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
+\end{equation}
+После квантования и разложения токов в ряд Лорана 
+\begin{equation}
+  \label{eq:8}
+  J^a_n(w)=\frac{1}{2\pi i }\oint_{w}dz (z-w)^n J^a(z)  
+\end{equation}
+для компонент токов получаются следующие коммутационные соотношения:
+\begin{equation}
+  \label{eq:5}
+  \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}
+\end{equation}
+где индексы $a,b,c$ пробегают генераторы простой алгебры $g$, $f^{abc}$ - структурные константы, а $m,n$-  целые.
+Таким образом, компоненты токов реализуют аффинную алгебру Ли $\hat g$.
+
+Компоненты тензора энергии-импульса строятся из нормально упорядоченных комбинаций компонент токов:
+\begin{equation}
+  \label{eq:6}
+  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
+\end{equation}
+Это так называемая конструкция Сугавары.
+
+Коммутационные соотношения компонент токов с генераторами алгебры Вирасоро имеют вид
+\begin{equation}
+  \label{eq:7}
+  \left[L_m,J^a_n\right]=-nJ^a_{m+n}
+\end{equation}
+Полная киральная алгебра модели представляет собой полу-прямое произведение $Vir\ltimes \hat g$
+
+Построение представлений аффинной алгебры Ли требуется для нахождения примарных полей модели Весса-Зумино-Новикова-Виттена.
+Правила ветвления представлений аффинной алгебры Ли на представления её аффинной подалгебры используются при построении новых моделей конформной теории поля путем факторизации модели Весса-Зумино-Новикова-Виттена по подмодели (так называемая орбифолд-конструкция).
 
@@
 
+\bibliography{article}{}
+\bibliographystyle{utphys}
+
 \end{document}

### 2009-07-09 AffineLieAlgebras/ACMS2009/notes.tex
Some work on WZW-models

@@
 
-\subsection{Модели Весса-Зумино-Новикова-Виттена}
+\subsection{Wess-Zumino-Novikov-Witten models}
 \label{sec:WZNW}
+
+Let's start with non-linear $\sigma$-model.
+\begin{equation}
+  \label{eq:48}
+  S_0=\frac{1}{4a^2}\int d^2x\; Tr' (\partial^{\mu}g^{-1}\partial_{\mu}g)
+\end{equation}
+Here $a^2>0$ is a positive parameter, $g(x)\in G$ - field on Lie group $G$, which we will assume to be semi-simple and by $Tr'$ we have denoted representation independent trace of Lie algebra $\mathfrak{g} $
+\begin{equation}
+  \label{eq:70}
+  Tr'=\frac{1}{x_{rep}}Tr
+\end{equation}
+$x_{rep}$ is the Dynkin index of the representation.
+
+In this model the conformal invariance is lost at the quantum level, as it can be seen along the lines of previous sections.
+!!! Show it by example !!!
+
+Also we can see that holomorphic and antiholomorphic currents aren't conserved individually. The equations of motion are
+\begin{equation}
+  \label{eq:71}
+  \partial^{\mu}(g^{-1}\partial_{\mu}g)=0
+\end{equation}
+The currents are
+\begin{equation}
+  \label{eq:currents}
+  J_{\mu}=g^{-1}\partial_{\mu}g
+\end{equation}
+or in the complex coordinates
+\begin{equation}
+  \label{eq:74}
+  \begin{matrix}
+    & \tilde{J}_z=g^{-1}\partial_z g, & \tilde{J}_{\bar{z}}=g^{-1}\partial_{\bar{z}}g\\
+    & \partial_z \tilde{J}_{\bar{z}}+\partial_{\bar{z}}\tilde{J}_z=0 & \\
+  \end{matrix}
+\end{equation}
+The terms of the equation of motion can not be null separately because $\partial_{\mu}(\epsilon^{\mu\nu}J_{\nu})\neq 0$.
+
+So we add WZ-term to the action and redefine the currents in more appropriate way
+\begin{equation}
+  \label{eq:72}
+  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
+\end{equation}
+
 Модели Весса-Зумино-Новикова-Виттена - это простейшие не минимальные модели двумерной конформной теории поля.

### 2009-07-09 AffineLieAlgebras/ACMS2009/notes.tex
Continue work on WZW models section

--- 2009-05-25 AffineLieAlgebras/ACMS2009/notes.tex
@@
 ...
-\section{CFT}
+\section{Conformal Field Theory}
 \label{sec:cft}
+
+\subsection{General properties}
+\label{sec:general-properties}
 
@@
 \end{equation}
-
-\subsection{Conclusion}
-\label{sec:conclusion}
+\subsection{Connection with string theory}
 
@@
 
-\section{Conformal Field Theory}
-\label{sec:conf-field-theory}
+\subsection{Wess-Zumino-Novikov-Witten models}
+\label{sec:WZNW}
+
+Let's start with non-linear $\sigma$-model.
+\begin{equation}
+  \label{eq:48}
+  S_0=\frac{1}{4a^2}\int d^2x\; Tr' (\partial^{\mu}g^{-1}\partial_{\mu}g)
+\end{equation}
+Here $a^2>0$ is a positive parameter, $g(x)\in G$ - field on Lie group $G$, which we will assume to be semi-simple and by $Tr'$ we have denoted representation independent trace of Lie algebra $\mathfrak{g} $
+\begin{equation}
+  \label{eq:70}
+  Tr'=\frac{1}{x_{rep}}Tr
+\end{equation}
+$x_{rep}$ is the Dynkin index of the representation.
+
+In this model the conformal invariance is lost at the quantum level, as it can be seen along the lines of previous sections.
+!!! Show it by example !!!
+
+Also we can see that holomorphic and antiholomorphic currents aren't conserved individually. The equations of motion are
+\begin{equation}
+  \label{eq:71}
+  \partial^{\mu}(g^{-1}\partial_{\mu}g)=0
+\end{equation}
+The currents are
+\begin{equation}
+  \label{eq:currents}
+  J_{\mu}=g^{-1}\partial_{\mu}g
+\end{equation}
+or in the complex coordinates
+\begin{equation}
+  \label{eq:74}
+  \begin{matrix}
+    & \tilde{J}_z=g^{-1}\partial_z g, & \tilde{J}_{\bar{z}}=g^{-1}\partial_{\bar{z}}g\\
+    & \partial_z \tilde{J}_{\bar{z}}+\partial_{\bar{z}}\tilde{J}_z=0 & \\
+  \end{matrix}
+\end{equation}
+The terms of the equation of motion can not be null separately because $\partial_{\mu}(\epsilon^{\mu\nu}J_{\nu})\neq 0$.
+
+So we add WZ-term to the action and redefine the currents in more appropriate way
+\begin{equation}
+  \label{eq:72}
+  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
+\end{equation}
+
+Wess-Zumino term has the following form
+\begin{equation}
+  \label{eq:73}
+\Gamma=  - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr'\left(
+    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+
+This term is defined on the three-dimensional manifold $B$ whose boundary is original two-dimensional space.
+By $\tilde{g}$ we have denoted the extension of the field $g$ to $B$.
+This extension isn't unique.
+In a compactified three-dimensional space a compact two-dimensional manifold delimits two three-dimensional manifolds.
+The difference between this two choices $\Delta\Gamma$ is given by the right hand side of (\ref{eq:73}) with the integration range extended over the whole compact three-dimensional space.
+Since the latter is topologically equivalent to the three-sphere we have
+\begin{equation}
+  \label{eq:75}
+\Delta\Gamma=  - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left(
+    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+$\Delta\Gamma$ is defined modulo $2\pi i$, so the Euclidean functional integral with weight $exp(-\Gamma)$ is well-defined. Clearly, any coupling constant multiplying this term must be an integer.
+
+We then consider the action
+\begin{equation}
+  \label{eq:76}
+  S=S_0+k\Gamma
+\end{equation}
+where $k$ is an integer. 
+The equation of motion for the full action (\ref{eq:76}) is
+\begin{equation}
+  \label{eq:77}
+  \partial^{\mu}(g^{-1}\partial_{\mu}g)+\frac{a^2 ik}{4\pi}\epsilon_{\mu\nu}\partial^{\mu}(g^{-1}\partial^{\nu}g)=0
+\end{equation}
+It can be rewritten using complex coordinates as
+\begin{equation}
+  \label{eq:78}
+  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
+\end{equation}
+We see that when $a^2=\frac{4\pi}{k}$ we have the desired conservation law
+\begin{equation}
+  \label{eq:79}
+  \partial_z(g^{-1}\partial{\bar z}g)=0
+\end{equation}
+For currents
+\begin{equation}
+  \label{eq:4}
+  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
+\end{equation}
+
+The solution of classical equation is
+\begin{equation}
+  \label{eq:80}
+  g(z,\bar z)=f(z)\bar f(\bar z)
+\end{equation}
+for arbitrary functions $f(z)$ and $\bar f (\bar z)$.
+
+The separate conservation of the currents $J_z,\; J_{\bar z}$ implies the invariance of the action under the transformations
+\begin{equation}
+  \label{eq:81}
+   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)
+\end{equation}
+where $\Omega,\;\bar \Omega \in G$. So we have local $G(z)\times G(\bar z)$ invariance.
+
+In order to move analysis to quantum level we rescale the currents
+\begin{equation}
+  \label{eq:82}
+  J(z)\equiv -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
+\end{equation}
+So the variation of the action under infinitesimal transformation $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ is
+\begin{equation}
+  \label{eq:83}
+  \delta_{\omega,\bar\omega}S=\frac{i}{4\pi}\oint dz Tr' (\omega(z)J(z))-\frac{i}{4\pi}\oint d\bar z Tr'(\bar\omega(\bar z)\bar J(\bar z))
+\end{equation}
+Expanding the currents as
+\begin{equation}
+  \label{eq:85}
+  \begin{aligned}
+    J=\sum J^a t^a,\bar J=\sum \bar J^a t^a \\
+    \omega=\sum \omega^a t^a\\
+  \end{aligned}
+\end{equation}
+we get
+\begin{equation}
+  \label{eq:86}
+  \delta_{\omega,\bar \omega}S=-\frac{1}{2\pi i}\oint dz \sum\omega^a J^a+\frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \bar J^a
+\end{equation}
+We can also obtain Ward identities $\delta\left< X\right>=\left<(\delta S)X\right>$
+\begin{equation}
+  \label{eq:87}
+  \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
+  \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
+\end{equation}
+Then for the currents we have
+\begin{equation}
+  \label{eq:88}
+  \delta_{\omega}J=[\omega,J]-k\partial_z\omega,\quad \delta_{\omega}J^a=\sum i f_{abc}\omega^b J^c-k\partial_z\omega^a
+\end{equation}
+The operator product expansion for currents has the form
+\begin{equation}
+  \label{eq:89}
+  J^a(z) J^b(w) \sim \frac{k\delta_{ab}}{(z-w)^2}+\sum i f_{abc}\frac{J^c(w)}{(z-w)}
+\end{equation}
+Expanding currents into series we get
+\begin{equation}
+  \label{eq:90}
+  \begin{aligned}
+    J^a(z)=\sum_{n\in \mathbb Z}z^{n-1}J^a_n\\    
+    \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}  
+  \end{aligned}
+\end{equation}
+We see that components of currents realize affine Lie algebra $\hat g$.
+
+Energy-momentum tensor is introduced with Sugawara construction as the sum of normal-ordered products of current components
+\begin{equation}
+  \label{eq:6}
+  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
+\end{equation}
+Here $h^v$ is the dual Coxeter number.
+
+Energy-momentum tensor can be expanded into modes $L_n$
+\begin{equation}
+  \label{eq:91}
+  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
+\end{equation}
+The commutation relations for the modes $L_n$ are
+\begin{equation}
+  \label{eq:92}
+  \begin{aligned}
+    \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
+    \left[L_n,J^a_m\right]=-mJ^a_{n+m}
+  \end{aligned}
+\end{equation}
+
+So the Sugawara construction is the way to embed Virasoro algebra into the universal enveloping of affine Lie algebra.
+
+Complete chiral algebra of WZW-model is equal to semidirect product $Vir\ltimes \hat g$
 

### 2009-07-09 AffineLieAlgebras/ACMS2009/notes.tex
General introduction to WZW is complete, so now I can move to modular properties

@@
 
+The primary fields are the fields that transforms covariantly with respect to $G(z)\times G(\bar z)$, such as $g(z,\bar z)$. In terms of operator product expansion this property is reformulated as
+\begin{equation}
+  \label{eq:84}
+  \begin{aligned}
+    J^a(z)g(w,\bar w)\sim \frac{-t^a g(w,\bar w)}{(z-w)}\\
+    \bar J^a(z)g(w,\bar w)\sim \frac{ g(w,\bar w)t^a}{(z-w)}
+  \end{aligned}
+\end{equation}
+Any field $\phi_{\lambda,\mu}$ transforming covariantly with respect to some representation specified by $\lambda$ in holomorphic and $\mu$ in antiholomorphic sector, will be a WZW primary field.
+
+In terms of modes this property can be written as
+\begin{equation}
+  \label{eq:93}
+  \begin{aligned}
+    & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
+    & (J^a_n\phi_{\lambda})=0\quad \mbox{for}\; n>0\\
+  \end{aligned}
+\end{equation}
+We can associate the state $\left|\phi_{\lambda}\right>$ to the field $\phi_{\lambda}$
+  \begin{equation}
+    \label{eq:94}
+    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
+  \end{equation}
+Then the conditions (\ref{eq:93}) for WZW primary field are
+\begin{equation}
+  \label{eq:95}
+  \begin{aligned}
+    & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
+    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
+  \end{aligned}
+\end{equation}
+It is easy to see that the action of the Virasoro generators is
+\begin{equation}
+  \label{eq:96}
+  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
+\end{equation}
+Here we used the explicit form of the quadratic Casimir operator eigenvalue.
+
+Primary fields live in integrable finite-dimensional representations since infinite-dimensional and non-integrable fields are decoupled from the correlation functions.
+
+All secondary states are of the form
+\begin{equation}
+  \label{eq:97}
+  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
+\end{equation}
+For the correlation functions of primary fields we can obtain Knizhnik-Zamolodchikov equations which follow from global $G\times G$ invariance
+\begin{equation}
+  \label{eq:98}
+  \left(\partial_{z_i}+\frac{1}{k+h^v}\sum_{i\neq j}\frac{\sum_a t^a_i\otimes t^a_j}{z_i-z_k}\right)
+  \left<\phi_1(z_1)\dots \phi_n(z_n)\right>=0
+\end{equation}
+So the theory is completely determined by the representations of affine Lie algebra $\hat{\mathfrak{g}} $.
+
+\subsubsection{Modular invariants}
+\label{sec:modular-invariants}
+
 \section{Affine Lie algebras representations}

### 2009-07-10 AffineLieAlgebras/ACMS2009/notes.tex
Modular invariance in WZW models is introduced, now I should write about methods of construction of modular invariants.

@@
 
+In previous section we studied holomorphic and antiholomorphic sectors of the theory separately.
+But in physically sensible theories this sectors should be entangled.
+It is required for the theory to be well-defined on the higher genus Riemann surfaces (see \cite{gaberdiel2000icf} and references therein) and also if we want our theory to describe critical behavior \cite{difrancesco1997cft}.
+In the critical point theory has conformal invariance, holomorphic and antiholomorphic sectors are decoupled, but in the vicinity of critical point there exists some large scale so the sectors should interact.
+
+!!! Expand this argumentation !!!
+
+The necessary constraint for the theory to be well-defined on higher Riemann surfaces, which is also believed to be sufficient, is that the vacuum correlator on the torus is independent of its parametrisation \cite{gaberdiel2000icf}.
+Conformal theory on the higher genus Riemann surfaces is important for the string theory since this theory describes string interaction.
+
+Two-dimensional torus is described as quotient space of $\mathbb{R}^2\approx \mathbb{C}$ by the relations $z\sim z+w_1$ and $z\sim z+w_2$, where $w_1$ and $w_2$ are not parallel.
+
+The complex structure of the torus is conformally equivalent to a torus for which the relations are $z\sim z+1$ and $z\sim z+\tau$ where $\tau$ is in the upper half plane of $\mathbb{C}$.
+It is also easy to see that $\tau$, $T(\tau)=\tau+1$ and $S(\tau)=-\frac{1}{\tau}$ describe conformally equivalent tori.
+Two maps $T$ and $S$ generate the group $SL(2,\mathbb{Z})/\mathbb{Z}_2$ that consists of matrices of the form
+\begin{equation}
+  \label{eq:99}
+  A=
+  \begin{pmatrix}
+    a & b\\
+    c & d 
+  \end{pmatrix}
+  \quad\mbox{where}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+\end{equation}
+and matrices $A$ and $-A$ have the same action on $\tau$
+\begin{equation}
+  \label{eq:100}
+  \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+\end{equation}
+The parameter $\tau$ is called the modular parameter and the group  $SL(2,\mathbb{Z})/\mathbb{Z}_2$ is called the modular group.
+
+Given a conformal field theory that is defined on the Riemann sphere, the vacuum
+correlator on the torus can be determined as follows. First, we cut the torus along one
+of its non-trivial cycles; the resulting surface is a cylinder (or an annulus) whose shape
+depends on one complex parameter $q$. Since the annulus is a subset of the sphere, the
+conformal field theory on the annulus is determined in terms of the theory on the sphere.
+In particular, the states that can propagate in the annulus are precisely the states of
+the theory as defined on the sphere.
+In order to reobtain the torus from the annulus, we have to glue the two ends of
+the annulus together; in terms of conformal field theory this means that we have to sum
+over a complete set of states. The vacuum correlator on the torus is therefore described
+by a trace over the whole space of states, the partition function of the theory,
+\begin{equation}
+  \label{eq:101}
+  \sum_{(i,j)}Tr_{\mathcal{H}_{(i,j)}}(\mathcal{O}(q,\bar q)),
+\end{equation}
+where $\mathcal{O}(q,\bar q)$ is the operator that describes the propagation of the states along the annulus,
+\begin{equation}
+  \label{eq:102}
+  \mathcal{O}(q,\bar q)=q^{L_0-\frac{c}{24}}\bar q^{\bar L_0-\frac{\bar c}{24}}
+\end{equation}
+The propagator depends on the actual shape of the annulus that is described in terms
+of the complex parameter $q$. For a given torus that is described by $\tau$ , there is a natural
+choice for how to cut the torus into an annulus, and the complex parameter $q$ that is
+associated to this annulus is $q=e^{2\pi i \tau}$. Since the tori that are described by $\tau$ and $A\tau$
+(where $A \in SL(2, \mathbb{Z})$) are equivalent, the vacuum correlator is only well-defined provided
+that (\ref{eq:101}) is invariant under this transformation. This provides strong constraints on
+the spectrum of the theory.
+
+Each of the spaces $\mathcal{H}_{(i,j)}$ is a tensor product of an irreducible representation $\mathcal{H}_j$ of chiral algebra and an irreducible representation $\bar{\mathcal{H}}_{\bar{j}}$ of antichiral algebra.
+Then the vacuum correlator on the torus (\ref{eq:101}) takes the form
+\begin{equation}
+  \label{eq:103}
+  \sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
+\end{equation}
+where $\chi_j$ is the character of the representation $\mathcal{H}_j$,
+\begin{equation}
+  \label{eq:104}
+  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{where}\; q=e^{2\pi i \tau}
+\end{equation}
+Characters transform into one another under modular transformations,
+\begin{equation}
+  \label{eq:107}
+  \chi_j(-\frac{1}{\tau})=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{and}\quad \chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
+\end{equation}
+where $S$ and $T$ are constant matrices. This fact is proved for a certain class of conformal field theories \cite{gaberdiel2000icf}.
+
+For WZW-models the representations are determined by highest weights $\hat \lambda, \hat \xi$. Then we can write
+\begin{equation}
+  \label{eq:105}
+  \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi} L_{\hat \lambda}\otimes L_{\hat \xi}
+\end{equation}
+The partition function is rewritten as
+\begin{equation}
+  \label{eq:106}
+  Z(\tau)=\sum_{\hat \lambda,\hat \xi\in P^{(k)}_{+}} \chi_{\hat \lambda}(\tau)M_{\hat \lambda\hat\xi}\bar \chi_{\hat \xi}(\bar \tau)
+\end{equation}
+$M_{\hat \lambda\hat\xi}$ can be thought of as the multiplicity of primary field with weights $\hat\lambda,\hat \xi$.
+It has following properties:$M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, it is modular invariant
+\begin{equation}
+  \label{eq:108}
+  \begin{aligned}
+    T^{\dagger}MT=S^{\dagger}MS=M,\\
+    [M,S]=[M,T]=0,
+  \end{aligned}
+\end{equation}
+and $M_{00}=1$ for the uniqueness of vacuum.
+
 \section{Affine Lie algebras representations}

### 2009-07-10 AffineLieAlgebras/ACMS2009/notes.tex
Conformal embeddings started

@@
 \end{equation}
-$M_{\hat \lambda\hat\xi}$ can be thought of as the multiplicity of primary field with weights $\hat\lambda,\hat \xi$.
+The element of the mass matrix $M_{\hat \lambda\hat\xi}$ can be thought of as the multiplicity of primary field with weights $\hat\lambda,\hat \xi$.
 It has following properties:$M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, it is modular invariant
@@
 and $M_{00}=1$ for the uniqueness of vacuum.
+
+The simplest case of diagonal matrix $M$ corresponds to equal holomorphic and antiholomorphic conformal dimensions.
+There are several ways to construct non-diagonal modular invariants from diagonal \cite{difrancesco1997cft}:
+\begin{itemize}
+\item Method of outer automorphisms
+\item Conformal embedding into bigger theory
+\item Galois-transpositions
+\end{itemize}
+Here we will discuss conformal embeddings.
+
+\subsubsection{Conformal embeddings}
+\label{sec:conformal-embeddings}
 

### 2009-07-10 AffineLieAlgebras/ACMS2009/article.tex
some minor work
Started folding for branching section

@@
 
-The question is if it is possible to introduce the same procedure for
+The question is if it is possible to introduce similar procedure for
 computation of branching coefficients.
+
+We start with the formula
+\begin{equation}
+  \label{eq:6}
+  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
+    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }
+\end{equation}
+In terms of characters it has the following form
+\begin{equation}
+  \label{eq:9}
+  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
+\end{equation}
+
+It is well-known (see for example \cite{wakimoto2001idl}, \cite{kac1990idl}) that characters are Weyl-invariant.
+\begin{equation}
+  \label{eq:8}
+  ch(L^{\omega\mu})=ch(L^{\mu})
+\end{equation}
+Also Weyl group of the subalgebra is subgroup of Weyl group of algebra $W_{\mathfrak{a}}\subset W_{\mathfrak{g}}$.
+Using Weyl-Kac character formula
+\begin{equation}
+  \label{eq:11}
+  ch(L^{\mu})=\frac{\sum_{\omega\in W}\epsilon(\omega)e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in \Delta^{+}}(1-e^{\alpha})^{mult(\alpha)}}
+\end{equation}
+the equation \eqref{eq:9} can be rewritten as
+\begin{equation}
+  \label{eq:10}
+  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\frac{\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \Psi^{(\nu)}_{\mathfrak{a}}}{R_{\mathfrak{a}}}
+\end{equation}
+where we have introduced the singular weight elements $\Psi^{(\nu)}_{\mathfrak{a}}=\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}$ for $\mathfrak{a}$-modules $L^{\nu}_{\mathfrak{a}}$ and the denominator $R_{\mathfrak{a}}=\prod_{\alpha\in \Delta^{+}_{\mathfrak{a}}}(1-e^{\alpha})^{mult_{\mathfrak{a}}(\alpha)}$.
 

### 2009-07-11 AffineLieAlgebras/ACMS2009/article.tex
More on branching
Folding for branching is written

@@
   \label{fan-defined}
-  \Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+  \Gamma_{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
       \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} .
@@
 where we have introduced the singular weight elements $\Psi^{(\nu)}_{\mathfrak{a}}=\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}$ for $\mathfrak{a}$-modules $L^{\nu}_{\mathfrak{a}}$ and the denominator $R_{\mathfrak{a}}=\prod_{\alpha\in \Delta^{+}_{\mathfrak{a}}}(1-e^{\alpha})^{mult_{\mathfrak{a}}(\alpha)}$.
+In the paper \cite{ilyin812pbc} following notation was introduced
+\begin{equation}
+  \label{eq:12}
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \Psi^{(\nu)}_{\mathfrak{a}}
+  =\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}
+  \equiv\sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda}
+\end{equation}
+The numbers $k_{\lambda}^{(\mu)}$ are called anomalous branching coefficients and are equal to the multiplicities of the submodules $L^{\nu}_{\mathfrak{a}}$ times the determinants $\epsilon(\omega)$.
 
+Now we can rewrite formula \eqref{eq:10} as
+\begin{equation}
+  \label{eq:13}
+  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
+  \frac{\sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}}{e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}}}
+\end{equation}
+Here we have multiplied the numerator and the denominator by $e^{\rho_{\mathfrak{a}}}$. Now we multiply both sides of equation by ${e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}}}$.
+\begin{equation}
+  \label{eq:14}
+   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}}=
+  \sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}
+\end{equation}
+Then left-hand side of equation is anti-invariant under Weyl transformations of group $W_{\mathfrak{a}}$, since the character of $L^{\mu}_{\mathfrak{g}}$ is invariant, projection $\pi_{\mathfrak{a}}$ is orthogonal and $e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}}$ is anti-invariant ($\omega(e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}})=\epsilon(\omega)e^{\rho_{\mathfrak{a}}}R_{\mathfrak{a}}$, see \cite{wakimoto2001idl} for the proof).
+So we have
+\begin{equation}
+  \label{eq:15}
+  \omega\left(\sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}\right)=
+  \epsilon(\omega)\sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}
+\end{equation}
+It can be rewritten as
+\begin{equation}
+  \label{eq:16}
+ \sum_{\lambda\in P_{\mathfrak{a}}}k_{\omega^{-1}(\lambda+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}=
+  \epsilon(\omega)\sum_{\lambda\in P_{\mathfrak{a}}}k_{\lambda}^{(\mu)}e^{\lambda+\rho_{\mathfrak{a}}}
+\end{equation}
+Then we can equate coefficients of identical exponents
+\begin{equation}
+  \label{eq:17}
+  k_{\lambda}^{(\mu)}=\epsilon(\omega)k_{\omega(\lambda+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}^{(\mu)}
+\end{equation}
+We see that Weyl symmetry gives us all the values of $k_{\lambda}^{(\mu)}$ from the values inside the shifted by $-\rho_{\mathfrak{a}}$ fundamental Weyl chamber $C_{\mathfrak{a}}-\rho_{\mathfrak{a}}$.
+
+In the paper \cite{ilyin812pbc} following recurrent formula for computation of $k_{\lambda}^{(\mu)}$ was proved
+\begin{equation}
+  \label{recurrent-relation}
+  k_{\lambda }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{w\in W}\epsilon \left( w\right) \delta _{\lambda ,\pi _{\frak{a}}\circ
+\left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
+\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\lambda
++\gamma }^{\left( \mu \right) }\right)   
+\end{equation}
+Here $k_{\lambda}^{(\mu)}$ is computed as the sum over special set $\Gamma _{\frak{a}\subset \frak{g}}$ \eqref{fan-defined}.
+
+Using relation \eqref{eq:17} we can restrict computation to the shifted by $-\rho_{\mathfrak{a}}$ fundamental Weyl chamber $C_{\mathfrak{a}}-\rho_{\mathfrak{a}}$.
+Then branching coefficients inside the fundamental Weyl chamber are given by anomalous branching coefficients $b_{\lambda}^{(\mu)}=k_{\lambda}^{(\mu)}\;\mbox{for}\;\lambda\in C_{\mathfrak{a}}$ \cite{ilyin812pbc}.
 \section{Details of implementation}

### 2009-07-11 AffineLieAlgebras/ACMS2009/notes.tex
More work on conformal embeddings

@@
 \label{sec:conformal-embeddings}
+Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory. !!! Provide an explanation !!!
 
+The states for the theory that corresponds to the algebra $\mathfrak{g}$
+\begin{equation}
+  \label{eq:109}
+  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq\dots>0
+\end{equation}
+For sub-algebra $\mathfrak{p}\subset\mathfrak{g}$
+\begin{equation}
+  \label{eq:110}
+  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\mathcal{P}\lambda\right>
+\end{equation}
+Here $\tilde{J}^{a'_j}_{-n_j}$ are the generators of $\mathfrak{p}$ and $\mathcal{P}$ is the projection of $\mathfrak{g}$ to $\mathfrak{p}$.
+$\mathfrak{g}$-invariance of vacuum entails its $\mathfrak{p}$-invariance, but it is not the case for energy-momentum tensor.
+So energy-momentum tensor of bigger theory should consist only of generators of $\hat{\mathfrak{p}}$.
+Then $T_{\hat{\mathfrak{g}}}=T_{\hat{\mathfrak{p}}}\Rightarrow c(\hat{\mathfrak{g}})=c(\hat{\mathfrak{p}})$.
+This leads to equation
+\begin{equation}
+  \label{eq:111}
+  \frac{k\;dim\mathfrak{g}}{k+g}=\frac{x_e k\; dim\mathfrak{p}}{x_ek+p}
+\end{equation}
+Here $x_e$ is the embedding index and $g$, $p$ are dual Coxeter numbers of corresponding algebras. !!! Prove and expand !!!
+
+It can be shown that solutions of equation (\ref{eq:111}) exist only for level 1 $k=1$. 
 \section{Affine Lie algebras representations}

### 2009-07-13 AffineLieAlgebras/ACMS2009/notes.tex
Section on modular invariants is finished

@@
 It can be shown that solutions of equation (\ref{eq:111}) exist only for level 1 $k=1$.
+
+There exist only finite number of such embeddings.
+
+{\bf Examples}
+\begin{itemize}
+\item $su(2)\subset su(3),\; x_e=4$
+\item $\hat{su}(2)_{10}\subset\hat{sp}(4)_1$
+\item $\hat{su}(2)_{28}\subset(\hat{G_2})_1$
+\item $\hat{su}(2)_{16}\oplus\hat{su}(3)\subset (\hat{E_8})_1$
+\end{itemize}
+
+Branching $\hat{\lambda}\to \bigoplus_{\hat{\mu}}b_{\hat{\lambda}\hat{\mu}}\hat{\mu}$
+\begin{equation}
+  \label{eq:112}
+  h_{\hat{\lambda}}+n=h_{\hat{\mu}},\quad \frac{(\lambda,\lambda+2\rho)}{2(1+g)}+n=\frac{(\mu,\mu+2\rho)}{2(x_e+p)}
+\end{equation}
+The simple way is to calculate the dimensions of all the representations of simple finite-dimensional Lie algebras $\mathfrak{g},\mathfrak{p}$ and find all the triples $(\lambda,\mu,n)$, satisfying (\ref{eq:112}).
+Then investigate the representation $L_{\hat{\lambda}}$ of level $n$ as the sum of irreducible representations of $\mathfrak{g}$ and write out all the branching rules of these representations in representations of subalgebra $\mathfrak{p}$.
+The number of times the representation with highest weight $\mu$ appears in this listing is the required branching coefficient $b_{\hat{\lambda},\hat{\mu}}$.
+
+  Then non-diagonal modular invariants are obtained by substitution of character relations. For example, having calculated branching coefficients for $\hat{su}(2)_{28}\subset (\hat{G_2})_1$
+  \begin{equation}
+    \label{eq:113}
+    \begin{aligned}
+      & [1,0,0]\to [28,0]\oplus [18,10]\oplus [10,18]\oplus [0,28]\\
+      & [0,0,1]\to [22,6]\oplus [16,12]\oplus [12,16]\oplus [6,22]\\
+    \end{aligned}
+  \end{equation}
+we get following modular-invariant partition function
+\begin{equation}
+  \label{eq:114}
+  Z=\left|\chi_{[28,0]}+\chi_{[18,10]}+\chi_{[10,18]}+\chi_{[0,28]}\right|^2+\left|\chi_{[22,6]}+\chi_{[16,12]}+\chi_{[12,16]}+\chi_{[6,22]}\right|^2
+\end{equation}
+
 \section{Affine Lie algebras representations}

### 2009-07-22 AffineLieAlgebras/ACMS2009/article.tex
The introduction of the article is rewritten in more scientific style, found several papers, which should be added to the bibliography.

@@
 
-In this article we will describe computation algorithms for representations of affine Lie algebras by example.
+Since the affine Lie algebras are infinite-dimensional extensions of simple finite-dimensional Lie algebras, their representation theory is well understood \cite{kac1990idl}, \cite{wakimoto2001idl}, \cite{Wakimoto-Second-Book}.
+But infinite dimensionality poses a challenge for computational methods.
 
-Theory of affine Lie algebras is based upon the theory of simple Lie
-algebras. Affine Lie algebras are infinite-dimensional, but this
-infinite-dimensionality is ``along one direction''.
+In this paper we discuss the tasks of construction of representations which is reduced to computation of weight multiplicities and of branching of representation of affine Lie algebra to representation of affine subalgebra.
 
-So in computations we limit ourselves with some finite grade. 
-Then the problem is to propose algorithms with lowest growths rate
-with the increase of maximal grade.
+The first task is usually solved using the algorithms based on the recursive Freudenthal formula for weight multiplicities \eqref{eq:1}.
+The summation is optimized by considering of Weyl symmetry \cite{kass1990ala}, \cite{Moody-Patera}.
+While these algorithms are reasonably fast, the use of Racah-like recurrent relation \eqref{eq:2} is theoretically more efficient \cite{Nazarov2008}.
+In practice speed depends upon the realisation.
+So we describe this alternative approach in section \ref{sec:representations} and show results of practical speed comparisons.
+
+The task of calculation of branching coefficients is usually solved by the reduction to finite-dimensional case \cite{difrancesco1997cft}.
+In some physical applications this task is greatly simplified by the additional physical constraints, but for general case this approach is rather inconvenient since it is not easily formalisable for machine compuatation.
+We propose another approach based on recurrent relations for anomalous branching coefficients \cite{ilyin812pbc} in section \ref{sec:branching-rules} and discuss the method to optimize this computation.
+Then we describe our realisation of mentioned algorithms \ref{sec:details-implementation} and some applications \ref{sec:applications}.
 
@@
 modular forms \cite{kac1990idl}.
-But it is easier to work with multiplicities for automated
-computations.
+
+It is possible to write general relations for string functions in order to express them as the combination of generic theta-functions \cite{Lyakhovsky-Unwritten-String-equations-with-fans}.
+But in these paper we limit ourselves to automated computation of weight multiplicities.
 

### 2009-07-22 AffineLieAlgebras/ACMS2009/article.tex
Couple of phrases added into the first setion

@@
 \cite{kass1990ala}, but the software used by the authors is not
-available.
+available. We introduce our implementation of this algorithm in
+section \ref{sec:details-implementation} and compare it
+(~\ref{sec:applications}) to the alternative
+approach, based on the formula \eqref{eq:2}, which is described below.
 
-We use new method proposed in the articles
+We are mostly interested in the use of the new method proposed in the papers
 \cite{lyakhovsky1996rra,lyakhovsky2007dub,ilyin812pbc,kulish4sfa}. The
 idea is to use recurrent relations for anomalous branching
-coefficients based upon summation over special
+coefficients based on the summation over the special
 set of vectors $\Gamma_{\frak{a}\subset \frak{g}} $ called ``fan''.

### 2009-07-22 AffineLieAlgebras/ACMS2009/article.tex
Some text on anomalous branching coefficients and weight multiplicities

@@
 coefficients based on the summation over the special
-set of vectors $\Gamma_{\frak{a}\subset \frak{g}} $ called ``fan''.
+set of vectors $\Gamma_{\frak{a}\subset \frak{g}} $ called ``fan''. We
+need to introduce some notations. Let's consider the reduction of the
+representation of the affine Lie algebra $\mathfrak{g}$ to 
+representations of affine Lie algebra $\mathfrak{a}$. By
+$\pi_{\mathfrak{a}}$ we denote the projection of the root space
+$\frak{h}_{\frak{g}}^{\ast }$ to $\frak{h}_{\frak{a}}^{\ast }$. The
+set $\Gamma_{\frak{a}\subset \frak{g}} $ is introduced as the
+combination of projection of positive roots $\Delta^{+}$ of algebra
+$\frak{g}$ using formulae:
+\begin{equation}
+  \label{eq:7}
+  \prod_{\alpha \in \left( \pi _{\frak{a}}\circ \Delta ^{+}\right) }\left(
+    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
+      }}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset 
+      \frak{g}}}s\left( \gamma \right) e^{-\gamma }.  
+\end{equation}
+\begin{equation}
+\label{eq:18}
+  \Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
+      \gamma \right) \neq 0\right\} ;  
+\end{equation}
+
+\begin{equation}
+\label{eq:19}
+  \Gamma_{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+      \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} .
+\end{equation}
+
 \begin{equation}

### 2009-07-26 AffineLieAlgebras/ACMS2009/article.tex
Bibliography work

@@
 
-Since the affine Lie algebras are infinite-dimensional extensions of simple finite-dimensional Lie algebras, their representation theory is well understood \cite{kac1990idl}, \cite{wakimoto2001idl}, \cite{Wakimoto-Second-Book}.
+Since the affine Lie algebras are infinite-dimensional extensions of simple finite-dimensional Lie algebras, their representation theory is well understood \cite{kac1990idl}, \cite{wakimoto2001idl}, \cite{wakimoto2001lectures}.
 But infinite dimensionality poses a challenge for computational methods.
@@
 The first task is usually solved using the algorithms based on the recursive Freudenthal formula for weight multiplicities \eqref{eq:1}.
-The summation is optimized by considering of Weyl symmetry \cite{kass1990ala}, \cite{Moody-Patera}.
+The summation is optimized by considering of Weyl symmetry \cite{kass1990ala}, \cite{moody1982fast}.
 While these algorithms are reasonably fast, the use of Racah-like recurrent relation \eqref{eq:2} is theoretically more efficient \cite{Nazarov2008}.

### 2009-08-31 AffineLieAlgebras/InformalNotes/ModularInvariantsAndBranching.tex
Informal notes are moved into separate folder, backup files are now ignored in git. Start of the work on note on modular invariance in conformal field theory.

--- 2009-07-10 AffineLieAlgebras/ACMS2009/notes.tex
@@
 \tableofcontents
-\section{String theory}
-\label{sec:string-theory}
 
-Free relativistic particle action is equal to length of trajectory. 
-\begin{equation}
-  \label{eq:1}
-  \begin{split}
-  x^{\mu}(0)=x^{\mu}_0,\; x^{\mu}(1)=x^{\mu}_1\\
-  S=\int_{0}^{1} \sqrt{\left(\frac{dx^{\mu}}{d\tau}^2\right)}d\tau
-\end{split}
-\end{equation}
-There is Poincare invariance $x^{\mu}\to A^{\mu}_{\nu}x^{\nu}+ B^{\mu}$ and reparametrisation invariance $\tau\to f(\tau),\; x^{\mu}(\tau)\to x^{\mu}(f(\tau))$.
-
-String action is the area of world-sheet:
-\begin{equation}
-  \label{eq:2}
-  \begin{split}
-    X^{\mu}(x^1,x^2),\; \mu=1\dots d\\
-    S_N [X^{\mu}(x^1,x^2)]=\int \sqrt{det \frac{\partial X^{\mu}}{\partial x^a}\frac{\partial X^{\mu}}{\partial x^b}} dx^1 dx^2
-  \end{split}
-\end{equation}
-This action is called Nambu action, and it is invariant under Lorenz transformations and reparametrisations.
-
-Transition amplitude for string is given by following formula:
-\begin{equation}
-  \label{eq:3}
-  A=\int {\cal D}X^{\mu}(x^1,x^2)e^{-S_N[X^{\mu}(x^1,x^2)]}
-\end{equation}
-The problem here is the definition of measure of integration. 
-It is not strictly defined in most cases, so there is nothing unusual here.
-
-We want to change ``integration variable'' in order to fix the arbitrariness connected with reparametrisations of world-sheet.
-
-Obviously our theory should be invariant under reparametrisation:
-\begin{equation}
-  \label{eq:4}
-  \begin{split}
-    x^a \to f^a (x^1,x^2)\\
-    X^{\mu}(x^1,x^2)\to \tilde{X}^{\mu}(x^1,x^2)=X^{\mu}(f^1(x^1,x^2),f^2(x^1,x^2))
-  \end{split}
-\end{equation}
-
-But Nambu action is not invariant. So we will use equivalent Polyakov action, which has following form:
-\begin{equation}
-  \label{eq:5}
-  \begin{split}
-    S_P [g^{ab}(x^1,x^2), X^{\mu}(x^1,x^2)]=\int g^{ab}(x)\partial_a X^{\mu} \partial_b X^{\mu}\sqrt{g} \;d^2 x\\
-    g=\det g_{ab}
-  \end{split}
-\end{equation}
-
-Polyakov and Nambu actions are equivalent in the sense that equations of motion are the same after the exclusion of auxiliary field $g_{ab}$.
-\begin{equation}
-  \label{eq:6}
-  \delta_{X}S_N=0 \Longleftrightarrow \left\{
-      \begin{aligned}
-        \delta_X S_P=0\\
-        \delta_g S_P=0
-      \end{aligned}
-      \right.
-\end{equation}
-Polyakov action is invariant under Lorenz transformations and reparametrisations:
-\begin{equation}
-  \label{eq:7}
-  \begin{split}
-    x^a \to f^a (x^1,x^2)\\
-    X^{\mu}(x^1,x^2)\to \tilde{X}^{\mu}(x^1,x^2)=X^{\mu}(f^1(x^1,x^2),f^2(x^1,x^2))\\
-    g_{ab}(x)\to \tilde{g}_{ab}(x)=\frac{\partial f^{a_1}}{\partial x^{a}}\frac{\partial f^{b_1}}{\partial x^b} g_{a_1 b_1}(x)
-  \end{split}  
-\end{equation}
-
-There is also one additional invariance, which is called conformal or Weyl invariance.
-\begin{equation}
-  \label{eq:8}
-  \begin{split}
-    g_{ab}(x)\to e^{\sigma(x)}g_{ab}(x)\\
-    g\to e^{\sigma} g\\
-    g^{ab}\to e^{-\sigma} g^{ab}\\
-    S_P[e^{\sigma(x)} g_{ab}(x),X^{\mu}] = S_P[g_{ab}(x),X^{\mu}] 
-  \end{split}
-\end{equation}
-
-So we have rather big freedom. For example, any metric on sphere can be obtained from one (constant) metric with reparametrisation and Weyl transformation.
-\begin{equation}
-  \label{eq:9}
-  g_{ab}(x)=[e^{\sigma(x)}\hat{g}_{ab}]^{x^a\to f^a (x)}
-\end{equation}
-For surfaces of higher genus there are discrete families of equivalent metrics.
-
-We could not preserve all the symmetries during quantization. So we choose to save Lorenz invariance and reparametrisation invariance and break conformal invariance. It is so called conformal anomaly.
-
-\begin{equation}
-  \label{eq:10}
-  A=\int {\cal D}X^{\mu}(x^1,x^2)e^{-S_P[g_{ab},X^{\mu}(x^1,x^2)]}
-\end{equation}
-
-It is easy to see that norm is invariant under reparametrisations:
-\begin{equation}
-  \label{eq:11}
-  \begin{split}
-    \|\delta X^{\mu}\|^2 = \int \left(\delta X^{\mu}(x)\right)^2 \sqrt{g} d^2x\\
-    \|\delta g_{ab}\|^2 = \int \delta g_{a_1 b_1}\delta g_{a_2 b_2} g^{a_1 a_2} g^{b_1 b_2} \sqrt{g}\; d^2x
-  \end{split}
-\end{equation}
-
-To investigate what happens top Weyl invariance after quantization let's introduce so called effective action. We integrate out fields $X^{\mu}$ and get following result.
-\begin{equation}
-  \label{eq:12}
-  e^{-S_X^{eff}[g_{ab}]} \overset{def}{=} \int {\cal D}X^{\mu} e^{-S_P [g_{ab},X]}
-\end{equation}
-\begin{equation}
-  \label{eq:13}
-  \begin{split}
-    S^{eff}_X [e^{\sigma(x)} g_{ab}(x) ] = S_X^{eff}[g_{ab}]+\frac{d}{48\pi}W[g,\sigma]\\
-    W[g,\sigma]=\int \left[ \frac{1}{2} g^{ab}\partial_a\sigma \partial_b\sigma+R[g]\sigma+\mu e^{\sigma}\right] \sqrt{g}\; d^2x
-  \end{split}
-\end{equation}
-Here $R$ is scalar curvature of $g_{ab}$, and $\mu$ is a parameter depending on regularisation, for example for proper time regularisation $\mu=\frac{1}{4\pi\epsilon}$.
-The term $W[g,\sigma]$ is called Liouville's action.
-
-{\bf Notice} $\int R[x] \sqrt{g}d^2x = 4\pi \chi_E$, $\chi_E=2-2h$, $\chi_E$ - Euler characteristic of the surface, $h$ - genus of the surface.
-
-$W[g,\sigma]$  is called conformal anomaly.
-
-Variance of action
-\begin{equation}
-  \label{eq:14}
-  \begin{split}
-    \delta S[g_{ab},X] = -\frac{1}{4\pi} \int  \delta g^{ab} T_{ab} \sqrt{g} \; d^2x\\
-    g_{ab}\to g_{ab}+\delta g_{ab}
-  \end{split}
-\end{equation}
-\begin{equation}
-  \label{eq:15}
-  \begin{split}
-    g_{ab} \to e^{\sigma} g_{ab} \xrightarrow[\sigma \ll 1]{} (1+\delta\sigma) g_{ab}\\
-    \delta S [g_{ab},X] = -\frac{1}{4\pi} \int \delta\sigma g^{ab} T_{ab} \sqrt{g}\, d^2 x
-  \end{split}
-\end{equation}
-\begin{equation}
-  \label{eq:16}
-    \delta S =0 \Rightarrow g^{ab}T_{ab}=0
-\end{equation}
-We see that Weyl invariance is equivalent to tracelessness of energy-momentum tensor.
-
-After the quantization we have
-\begin{equation}
-  \label{eq:17}
-  g^{ab}\left< T_{ab} \right> = -\frac{d}{12} R[g]
-\end{equation}
-\begin{Def}
-  {\bf Two dimensional conformal field theory} - is the theory that transforms as in (\ref{eq:13}).
-
-  The factor before $W[g,\sigma]$ is called {\it central charge}.
-\end{Def}
-
-!!!!!!!!!
-
-Why it is so? How this definition is connected with another definitions and properties of conformal field theory?
-
-!!!!!!!!!
-
-At this moment we have too much freedom in our Feynman integral (\ref{eq:10}).
-We have diffeomorphisms (\ref{eq:4}) and Weyl transformations (\ref{eq:8}).
-We will fix the gauge so that the metric is given by the formula
-\begin{equation}
-  \label{eq:20}
-  g_{ab}=[e^{\phi} \hat{g}_{ab}]^{f^a}
-\end{equation}
-
-Faddeev-Popov ghosts appear as usual after this procedure.
-
-\begin{equation}
-  \label{eq:19}
-  \begin{split}
-    A=\int {\cal D} X^{\mu}(x^1,x^2)e^{-S_P[g_{ab},X^{\mu}(x^1,x^2)]} = \\
-    = \int {\cal D}\phi\; {\cal D}X\; \mathcal{D} B_{ab}\; \mathcal{D} C^a e^{-S_P [e^{\phi}\hat{g}_{ab},X]-
-      S_{gh}[e^{\phi}\hat{g}_{ab},B,C]}
-  \end{split}
-\end{equation}
-Here $B,C$ are ghost fields, $B_{ab}(X)$ is symmetric and traceless tensor. All the functional integrals use metric $e^{\phi}\hat{g}$. 
-\begin{equation}
-  \label{eq:21}
-  S_{gh} = \int g^{ac} B_{ab} \nabla_c C^b \sqrt{g} \, d^2x
-\end{equation}
-We can fix Weyl invariance so that measures of integration over matter fields and ghosts fields in (\ref{eq:19}) don't depend on $\phi$. Then we get conformal anomaly in the exponent:
-\begin{equation}
-  \label{eq:22}
-  A = \int \mathcal{D}_{e^{\phi} \hat{g}} \mathcal{D}_{\hat{g}} X \mathcal{D}_{\hat{g}} B_{ab} \mathcal{D}_{\hat{g}} C^a e^{-S_P [e^{\phi}\hat{g}_{ab},X]-S_{gh}[e^{\phi}\hat{g}_{ab},B,C]+\frac{d-26}{48\pi} W[\hat{g}_{ab},\phi]}
-\end{equation}
-$\frac{d}{48\pi}$ comes from matter fields, and $\frac{-26}{48\pi}$ from ghost fields, since both actions are actions of two-dimensional conformal field theory.
-
-Ordinary bosonic string lives in 26-dimensional space and doesn't interact with Liouville's gravity.
-Such a string is called ``critical string'' since it can exist only in critical dimension.
-Other string models are called non-critical strings.
-
-First integration in (\ref{eq:22}) is very inconvenient, since we integrate over $\phi$ with measure depending on $\phi$. This measure $\mathcal{D}_{e^{\phi}\hat{g}}\phi$ corresponds to interval
-\begin{equation}
-  \label{eq:23}
-  \|\delta\phi\|^2_P = \int e^{\phi} (\delta\phi)^2 \sqrt{\hat{g}}\, d^2 x
-\end{equation}
-It is non-linear and is not invariant under the translations $\phi(x)\to \phi(x)+\eta(x)$.
-So for some time this was a problem since nobody knew how to work with such objects.
-
-But David-Distler-Kawai proposed to change action in order to take into account change of measure of integration to normal measure.
-
-They conjectured that the amplitude can be written in the form
-\begin{equation}
-  \label{eq:24}
-  A=\int \mathcal{D}_{\hat{g}}\phi\, \mathcal{D}_{\hat{g}} X\, \mathcal{D}_{\hat{g}} (B,C)\, e^{-S_P[\hat{g},X]-S_{gh}[\hat{g},B,C]-S_L[\hat{g},\phi]}
-\end{equation}
-where the measure $\mathcal{D}_{\hat{g}} \phi$ corresponds to the interval $\|\delta\phi\|^2_{DDK} = \int (\delta\phi)^2 \sqrt{\hat{g}}\, d^2x$ and it is invariant under the translations $\phi\to \phi+\eta$ ($\delta\phi\to \delta\phi$).
-$S_L$ here is Liouville's action with two undefined for now parameters $Q$ and $b$:
-\begin{equation}
-  \label{eq:25}
-  S_L[\hat{g},\phi] = \frac{1}{8\pi} \int \left[ \frac{1}{2} \hat{g}^{ab} \partial_a \phi \partial_b \phi + QR\phi +\mu e^{2b\phi}\right] \sqrt{\hat{g}} \, d^2x
-\end{equation}
-We choose following normalization:
-\begin{equation}
-  \label{eq:26}
-  \langle \phi(x) \phi(0) \rangle = \log |x|^2
-\end{equation}
-Liouville's term should be invariant under dilation $\hat{g}_{ab}\to e^{\sigma}\hat{g}_{ab}$.
-
-After we put
-\begin{equation}
-  \label{eq:27}
-  Q=\frac{1}{b}+b
-\end{equation}
-Liouville's action becomes conformal, so that
-\begin{equation}
-  \label{eq:28}
-  \begin{split}
-    \int \mathcal{D}_{\hat{g}} \phi e^{-S_L[\hat g,\phi]} = e^{-S_L^{eff}[\hat g]}\\
-    S_L^{eff} [e^{\sigma}\hat{g}]=S_L^{eff}[\hat g] +\frac{C_L}{12} W[\hat g,\sigma]
-  \end{split}
-\end{equation}
-Where
-\begin{equation}
-  \label{eq:29}
-  C_L=1+6 Q^2
-\end{equation}
-
-Then we require total central charge to vanish:
-\begin{equation}
-  \label{eq:30}
-  C_X+C_{gh}+C_L=C_{tot}=0
-\end{equation}
-
-Now the amplitude doesn't depend on $\hat{g}$ and parameters $Q$,$b$ are fixed.
-\begin{equation}
-  \label{eq:18}
-  d+1+6\left(b+\frac{1}{b}\right)^2=26
-\end{equation}
-In some finite area we can assume
-\begin{equation}
-  \label{eq:31}
-  \hat{g}_{ab}=\delta_{ab}
-\end{equation}
-There also could be additional term connected with the topology.
-
-Let's change variables
-\begin{equation}
-  \label{eq:32}
-  \begin{split}
-    x^1+i\, x^2=z\\
-    x^1-i\, x^2=\bar{z}\\
-    (dx^1)^2+(dx^2)^2=dz\,d\bar{z}
-  \end{split}
-\end{equation}
-For fields and terms of the action we have
-\begin{equation}
-  \label{eq:33}
-  \begin{split}
-    C^z=C,\; C^{\bar{z}}=\bar{C}\\
-    B_{zz}=B, \; B_{\bar{z}\bar{z}}=\bar{B}\\
-    S_{gh}=\int d^2z [B\bar{\partial}C+\bar{B}\partial \bar{C}]\\
-    S_P[X]=\int d^2z \bar{\partial}X \partial X\\
-    S_L[\phi] \propto \int d^2z \left[\bar{\partial} \phi \partial \phi+\mu e^{2 b \phi}\right] + \mbox{(topological terms)}
-  \end{split}
-\end{equation}
-\begin{equation}
-  \label{eq:34}
-  e^{-S^{eff}[g]}=\int \mathcal{D} X e^{-\int g^{ab}\partial_a X \partial_b X \sqrt{g}\, d^2x} = \int \mathcal{D}_g X e^{-\int X \Delta X\sqrt{g}\, d^2x}
-\end{equation}
-Laplace operator depends on metric
-\begin{equation}
-  \label{eq:35}
-  \Delta = \frac{1}{\sqrt{g}}\partial_a \sqrt{g} g^{ab}\partial_b
-\end{equation}
-
-It is self-conjugate operator.
-
-We can represent field $X$ as combination of eigenfunctions of Laplace operator $X(x)=\sum c_n X_n,\; \Delta X_n = \lambda_n X_n,\; \lambda_n=\lambda_n[g]$.
-Then we will integrate over all eigenfunctions:
-\begin{equation}
-  \label{eq:36}
-  e^{-S^{eff}[g]}=\left(\prod_{n} \lambda_n\right)^{-\frac{1}{2}}=(\det \Delta)^{-\frac{1}{2}}
-\end{equation}
-Obviously we could not calculate $\lambda_n$, but we can get the determinant.
-\begin{equation}
-  \label{eq:37}
-  S^{eff}[g]=\log \det \Delta=tr \log \Delta
-\end{equation}
-\begin{equation}
-  \label{eq:38}
-  \log\frac{\lambda}{\lambda_0}=\int_0^{\infty}\frac{e^{-\lambda t}-e^{\lambda_0 t}}{t}dt
-\end{equation}
-\begin{equation}
-  \label{eq:39}
-  \delta S^{eff}[g]=tr (\log\Delta -\log\Delta_{g_0})=\delta tr \int_0^{\infty}\frac{e^{-\Delta t}}{t} dt
-\end{equation}
-The last integral diverges, so we need to regularise it. We will use heat kernel regularisation.
-\begin{equation}
-  \label{eq:40}
-  \delta S^{eff}[g]=\delta tr \int_{\epsilon}^{\infty}\frac{e^{-\Delta t}}{t} dt  
-\end{equation}
-As we already mentioned, $\hat{g}_{ab}$ could be put equal to $\rho dz d\bar{z}$ in finite area. Then
-\begin{equation}
-  \label{eq:41}
-  \Delta=\frac{1}{\rho}\bar{\partial}\partial
-\end{equation}
-For variation of effective action we have
-  \begin{multline}
-  \label{eq:42}
-    \delta_{\rho}S^{eff}[g]=\delta_{\rho} tr \int_{\epsilon}^{\infty} e^{-\frac{1}{\rho}\bar{\partial}\partial t}\frac{dt}{t}=\\
-    - tr \int_{\epsilon}^{\infty}\delta_{\Delta}e^{-\Delta t} dt=
-    -tr \int_{\epsilon}^{\infty}\frac{\delta\rho}{\rho}\Delta e^{-\Delta t} dt=\\
-    -tr \int_{\epsilon}^{\infty}\frac{\delta\rho}{\rho}\frac{d}{dt} e^{-\Delta t} dt=-tr \frac{\delta\rho}{\rho}e^{-\Delta \epsilon}
-  \end{multline}
-
-Let's introduce Green function for heat equation
-\begin{equation}
-  \label{eq:43}
-  G(t,x,y)=\sum_n e^{-\lambda_n t}X_n(x) X_n(y)
-\end{equation}
-\begin{equation}
-  \label{eq:44}
-  \begin{split}
-    \frac{\partial G}{\partial t}=\Delta_x G(t,x,y)\\
-    G(o,x,y)=\delta^2 (x-y)\\
-    G(t,x,x)=\frac{1}{4\pi t}+aR+O(t)
-  \end{split}
-\end{equation}
-Then for variation of action we have
-\begin{equation}
-  \label{eq:45}
-  \delta S^{eff}[g]=\int d^2x \frac{\delta\rho}{\rho}\left(\frac{1}{4\pi\epsilon}+aR\right)
-\end{equation}
-
-!!!! !!!! !!!! !!!! 
-Be more elaborate here.
-!!!!!!!
-
-...
-\section{Conformal Field Theory}
-\label{sec:cft}
-
-\subsection{General properties}
-\label{sec:general-properties}
-
-In Conformal Field Theory 
-\begin{equation}
-  \label{eq:46}
-  g^{ab}\left<T_{ab}\right>=\frac{C}{12}R[g]
-\end{equation}
-$C$ is a central charge.
-
-For flat metric $g_{ab}=\delta_{ab}$ we have
-\begin{equation}
-  \label{eq:47}
-  g^{ab}\langle T_{ab} \rangle=0
-\end{equation}
-Then we put $T_{zz}=T,\quad T_{\bar{z}\bar{z}}=\bar{T},\quad T_{z\bar{z}}=T_{\bar{z}z}$. In flat space from continuity equation $\bar{\partial}T_{zz}+\partial T_{\bar{z}\bar{z}}=0$ we have
-\begin{equation}
-  \label{eq:49}
-  \begin{split}
-    T_{z\bar{z}}=0\\
-    \bar{\partial}T_{zz}=\bar{\partial}T=0,\quad T \mbox{- holomorphic}\\
-    \partial T_{\bar{z}\bar{z}}=\partial \bar{T}=0,\quad \bar{T} \mbox{- antiholomorphic}\\
-  \end{split}
-\end{equation}
-In curved space continuity equation reads $\nabla_a T^{ab}=0$ and we can choose coordinate system where $g_{ab}dx^a dx^b = \rho dz\, d\bar{z}=e^{\sigma}dz\,d\bar{z}$.
-Then we introduce pseudo energy $T$:
-\begin{equation}
-  \label{eq:50}
-  T_{zz}+\frac{C}{12}t_{zz}=T
-\end{equation}
-where $t_{zz}=(\partial \sigma)^2-2\partial^2 \sigma$. It is easy to check that $\bar{\partial}T=0$ in this case.
-
-For transformations $z\to w(z)$
-\begin{equation}
-  \label{eq:51}
-  \begin{split}
-    T_{zz}\to \left(\frac{dw}{dz}\right)^2 T_{ww}(w(z))\\
-    t\to \left(\frac{dw}{dz}\right)t(w)+2\{w,z\}\\
-    \mbox{where}\; \{w,z\}=\left(\frac{\partial_z^3 w}{\partial_z w}-\frac{3}{2}\left(\frac{\partial_z^2 w}{\partial_z}\right)^2\right)\\
-    T\to \left(\frac{dw}{dz}\right)^2 T(w)+\frac{C}{12}\{w,z\}\\
-  \end{split}
-\end{equation}
-Energy-momentum tensor is the generator of coordinate transformations $x^a\to x^a+\epsilon^a(x)$:
-\begin{equation}
-  \label{eq:52}
-  \delta_{\epsilon}\langle A_1(x_1)\dots A_N(x_N)\rangle = \int d^2x\, \partial_a \epsilon_b(x)\langle T_{ab}(x) A_1(x_1)\dots A_N(x_N)\rangle
-\end{equation}
-
-\begin{equation}
-  \label{eq:53}
-  \begin{split}
-    T_{aa}=0\\
-    \partial_a \epsilon_b+\partial_b \epsilon_a\sim \delta_{ab}\\
-    \epsilon^a=\epsilon x^a \;\mbox{or}\; x^a\to \frac{x^a}{(\vec x)^2}
-  \end{split}
-\end{equation}
-Correlation functions don't change under conformal transformations.
-\begin{equation}
-  \label{eq:54}
-  \delta_{\epsilon}A(x)=\int_{\partial D} dy^a\, \epsilon^b \tilde{T}_{ab}(y)A(x)-\int_{D}d^2y\, \partial^a \epsilon^b(y)T_{ab}(y)A(x)
-\end{equation}
-Where $\tilde{T}_{ab}=\epsilon_{ac}T_{cb}$.
-
-Let
-\begin{equation}
-  \label{eq:55}
-  \begin{split}
-    \partial_a \epsilon_b+\partial_b \epsilon_a\sim \delta_{ab}\\
-    \bar{\partial}\epsilon=0\\
-    z\to z+\epsilon(z,\bar{z})\\
-    \bar{z}\to\bar{z}+\bar{\epsilon}(z,\bar{z})
-  \end{split}
-\end{equation}
-\begin{equation}
-  \label{eq:56}
-  \delta_{\epsilon}A(z,\bar{z})=\oint_z du\, \epsilon(u) T(u) A(z,\bar{z})
-\end{equation}
-Substituting $T(z)$ in place of arbitrary operator $A$ we get 
-\begin{equation}
-  \label{eq:57}
-  \delta_{\epsilon}T(z)=\oint_z du\, \epsilon(u)T(u)T(z)
-\end{equation}
-
-If $w(z)=z+\epsilon(z)$ where $\epsilon$ is small, $T$ transforms as following:
-\begin{equation}
-  \label{eq:58}
-  T(z)\to \epsilon T'(z) + 2\epsilon' T(z)+\frac{C}{12}\epsilon'''
-\end{equation}
-\begin{equation}
-  \label{eq:59}
-  \delta_{\epsilon}T(z)=\oint du\, \epsilon(u) T(u) T(z) = \epsilon T'(z) + 2\epsilon' T(z)+\frac{C}{12}\epsilon'''
-\end{equation}
-We suppose that for full set of operators $\{A_j(x)\}$ there exists operator product expansion:
-!!! How can it be proved ????
-\begin{equation}
-  \label{eq:60}
-  A_i(x)A_j(0)=\sum C^k_{ij}(x)A_k(0)
-\end{equation}
-Then for product $T(u)T(z)$ we have
-\begin{equation}
-  \label{eq:61}
-  T(u)T(z)=\sum C_k(u-z) A_k(z)
-\end{equation}
-We can recover the poles from formula (\ref{eq:59}):
-\begin{equation}
-  \label{eq:62}
-  T(u)T(z)=\frac{C}{2(u-z)^4}+\frac{2T(z)}{(u-z)^2}+\frac{T'(z)}{u-z}+\mbox{non-singular terms}
-\end{equation}
-Now introduce the operators $L_n$:
-\begin{equation}
-  \label{eq:63}
-  L_n A(z)\equiv \frac{}{2\pi i}\oint_{C}du\, (u-z)^{n+1}T(u)A(z)
-\end{equation}
-It is possible to show that for $n,m\in \mathbb{Z}$
-\begin{equation}
-  \label{eq:64}
-  [L_n,L_m]=(n-m) L_{n+m}+\frac{C}{12}(n^3-n)\delta_{n,-m}
-\end{equation}
-and $\{L_n\}$ constitute Virasoro algebra.
-
-All the fields in the theory are sums of multiplets of Virasoro algebra:
-\begin{equation}
-  \label{eq:65}
-  \{A_j\}=\sum [\Phi_{\Delta,A}] %%% It is incorrect, fix this formula
-\end{equation}
-
-There is a primary field in every multiplet:
-\begin{equation}
-  \label{eq:66}
-  \begin{split}
-    \Phi_{\Delta}(z)\underset{z\to w(z)}{\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\Phi_{\Delta}(w(z))\\
-    L_n \Phi=0,\quad n>0\\
-    L_0 \Phi=\Delta \Phi\\
-  \end{split}
-\end{equation}
-All other fields are built of primary fields and are called secondary:
-\begin{equation}
-  \label{eq:67}
-  L_{-n_1}L_{-n_2}\dots \Phi_{\Delta}
-\end{equation}
-
-Correlation functions are expressed as combinations of correlation functions of primary fields.
-
-The only thing that is yet undefined is the set of scaling dimensions of primary fields.
-So to fix the theory we should define $\Phi_a,\; \Delta_a,\; C^c_{ab}$.
-Then our theory is solved.
-If the number of primary fields is finite, such a model is called {\it minimal}.
-
-For example, following fields are Weyl-invariant:
-\begin{equation}
-  \label{eq:68}
-  O_a=\int \Phi_{\Delta}e^{2a\phi}\,d^2x,\quad \mbox{where}\;\Delta+a(Q-a)=1
-\end{equation}
-$O_a$ - is the main observable of string theory with gravitational dimension $\delta_a=-\frac{a}{b}$.
-\begin{equation}
-  \label{eq:69}
-  \int\langle O_{a_1}\dots O_{a_n}\rangle_{\mu} e^{-\mu A}d\mu=\langle O_{a_1}\dots O_{a_n}\rangle_{A}=A^{\sum \delta_k},\quad \delta_k=\frac{a_k}{b}
-\end{equation}
-\subsection{Connection with string theory}
-
-We can start from arbitrary conformal field theory, find $b$ from equation $C+6\left(b+\frac{1}{b}\right)^2=25$ and obtain some non-critical string theory.
-But for $d>1$ $b$ becomes complex and this fact leads to unsolved yet problems.
-
-\subsection{Wess-Zumino-Novikov-Witten models}
-\label{sec:WZNW}
-
-Let's start with non-linear $\sigma$-model.
-\begin{equation}
-  \label{eq:48}
-  S_0=\frac{1}{4a^2}\int d^2x\; Tr' (\partial^{\mu}g^{-1}\partial_{\mu}g)
-\end{equation}
-Here $a^2>0$ is a positive parameter, $g(x)\in G$ - field on Lie group $G$, which we will assume to be semi-simple and by $Tr'$ we have denoted representation independent trace of Lie algebra $\mathfrak{g} $
-\begin{equation}
-  \label{eq:70}
-  Tr'=\frac{1}{x_{rep}}Tr
-\end{equation}
-$x_{rep}$ is the Dynkin index of the representation.
-
-In this model the conformal invariance is lost at the quantum level, as it can be seen along the lines of previous sections.
-!!! Show it by example !!!
-
-Also we can see that holomorphic and antiholomorphic currents aren't conserved individually. The equations of motion are
-\begin{equation}
-  \label{eq:71}
-  \partial^{\mu}(g^{-1}\partial_{\mu}g)=0
-\end{equation}
-The currents are
-\begin{equation}
-  \label{eq:currents}
-  J_{\mu}=g^{-1}\partial_{\mu}g
-\end{equation}
-or in the complex coordinates
-\begin{equation}
-  \label{eq:74}
-  \begin{matrix}
-    & \tilde{J}_z=g^{-1}\partial_z g, & \tilde{J}_{\bar{z}}=g^{-1}\partial_{\bar{z}}g\\
-    & \partial_z \tilde{J}_{\bar{z}}+\partial_{\bar{z}}\tilde{J}_z=0 & \\
-  \end{matrix}
-\end{equation}
-The terms of the equation of motion can not be null separately because $\partial_{\mu}(\epsilon^{\mu\nu}J_{\nu})\neq 0$.
-
-So we add WZ-term to the action and redefine the currents in more appropriate way
-\begin{equation}
-  \label{eq:72}
-  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
-\end{equation}
-
-Wess-Zumino term has the following form
-\begin{equation}
-  \label{eq:73}
-\Gamma=  - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr'\left(
-    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
-\end{equation}
-
-This term is defined on the three-dimensional manifold $B$ whose boundary is original two-dimensional space.
-By $\tilde{g}$ we have denoted the extension of the field $g$ to $B$.
-This extension isn't unique.
-In a compactified three-dimensional space a compact two-dimensional manifold delimits two three-dimensional manifolds.
-The difference between this two choices $\Delta\Gamma$ is given by the right hand side of (\ref{eq:73}) with the integration range extended over the whole compact three-dimensional space.
-Since the latter is topologically equivalent to the three-sphere we have
-\begin{equation}
-  \label{eq:75}
-\Delta\Gamma=  - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left(
-    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
-\end{equation}
-$\Delta\Gamma$ is defined modulo $2\pi i$, so the Euclidean functional integral with weight $exp(-\Gamma)$ is well-defined. Clearly, any coupling constant multiplying this term must be an integer.
-
-We then consider the action
-\begin{equation}
-  \label{eq:76}
-  S=S_0+k\Gamma
-\end{equation}
-where $k$ is an integer. 
-The equation of motion for the full action (\ref{eq:76}) is
-\begin{equation}
-  \label{eq:77}
-  \partial^{\mu}(g^{-1}\partial_{\mu}g)+\frac{a^2 ik}{4\pi}\epsilon_{\mu\nu}\partial^{\mu}(g^{-1}\partial^{\nu}g)=0
-\end{equation}
-It can be rewritten using complex coordinates as
-\begin{equation}
-  \label{eq:78}
-  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
-\end{equation}
-We see that when $a^2=\frac{4\pi}{k}$ we have the desired conservation law
-\begin{equation}
-  \label{eq:79}
-  \partial_z(g^{-1}\partial{\bar z}g)=0
-\end{equation}
-For currents
-\begin{equation}
-  \label{eq:4}
-  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
-\end{equation}
-
-The solution of classical equation is
-\begin{equation}
-  \label{eq:80}
-  g(z,\bar z)=f(z)\bar f(\bar z)
-\end{equation}
-for arbitrary functions $f(z)$ and $\bar f (\bar z)$.
-
-The separate conservation of the currents $J_z,\; J_{\bar z}$ implies the invariance of the action under the transformations
-\begin{equation}
-  \label{eq:81}
-   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)
-\end{equation}
-where $\Omega,\;\bar \Omega \in G$. So we have local $G(z)\times G(\bar z)$ invariance.
-
-In order to move analysis to quantum level we rescale the currents
-\begin{equation}
-  \label{eq:82}
-  J(z)\equiv -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
-\end{equation}
-So the variation of the action under infinitesimal transformation $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ is
-\begin{equation}
-  \label{eq:83}
-  \delta_{\omega,\bar\omega}S=\frac{i}{4\pi}\oint dz Tr' (\omega(z)J(z))-\frac{i}{4\pi}\oint d\bar z Tr'(\bar\omega(\bar z)\bar J(\bar z))
-\end{equation}
-Expanding the currents as
-\begin{equation}
-  \label{eq:85}
-  \begin{aligned}
-    J=\sum J^a t^a,\bar J=\sum \bar J^a t^a \\
-    \omega=\sum \omega^a t^a\\
-  \end{aligned}
-\end{equation}
-we get
-\begin{equation}
-  \label{eq:86}
-  \delta_{\omega,\bar \omega}S=-\frac{1}{2\pi i}\oint dz \sum\omega^a J^a+\frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \bar J^a
-\end{equation}
-We can also obtain Ward identities $\delta\left< X\right>=\left<(\delta S)X\right>$
-\begin{equation}
-  \label{eq:87}
-  \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
-  \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
-\end{equation}
-Then for the currents we have
-\begin{equation}
-  \label{eq:88}
-  \delta_{\omega}J=[\omega,J]-k\partial_z\omega,\quad \delta_{\omega}J^a=\sum i f_{abc}\omega^b J^c-k\partial_z\omega^a
-\end{equation}
-The operator product expansion for currents has the form
-\begin{equation}
-  \label{eq:89}
-  J^a(z) J^b(w) \sim \frac{k\delta_{ab}}{(z-w)^2}+\sum i f_{abc}\frac{J^c(w)}{(z-w)}
-\end{equation}
-Expanding currents into series we get
-\begin{equation}
-  \label{eq:90}
-  \begin{aligned}
-    J^a(z)=\sum_{n\in \mathbb Z}z^{n-1}J^a_n\\    
-    \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}  
-  \end{aligned}
-\end{equation}
-We see that components of currents realize affine Lie algebra $\hat g$.
-
-Energy-momentum tensor is introduced with Sugawara construction as the sum of normal-ordered products of current components
-\begin{equation}
-  \label{eq:6}
-  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
-\end{equation}
-Here $h^v$ is the dual Coxeter number.
-
-Energy-momentum tensor can be expanded into modes $L_n$
-\begin{equation}
-  \label{eq:91}
-  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
-\end{equation}
-The commutation relations for the modes $L_n$ are
-\begin{equation}
-  \label{eq:92}
-  \begin{aligned}
-    \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
-    \left[L_n,J^a_m\right]=-mJ^a_{n+m}
-  \end{aligned}
-\end{equation}
-
-So the Sugawara construction is the way to embed Virasoro algebra into the universal enveloping of affine Lie algebra.
-
-Complete chiral algebra of WZW-model is equal to semidirect product $Vir\ltimes \hat g$
-
-The primary fields are the fields that transforms covariantly with respect to $G(z)\times G(\bar z)$, such as $g(z,\bar z)$. In terms of operator product expansion this property is reformulated as
-\begin{equation}
-  \label{eq:84}
-  \begin{aligned}
-    J^a(z)g(w,\bar w)\sim \frac{-t^a g(w,\bar w)}{(z-w)}\\
-    \bar J^a(z)g(w,\bar w)\sim \frac{ g(w,\bar w)t^a}{(z-w)}
-  \end{aligned}
-\end{equation}
-Any field $\phi_{\lambda,\mu}$ transforming covariantly with respect to some representation specified by $\lambda$ in holomorphic and $\mu$ in antiholomorphic sector, will be a WZW primary field.
-
-In terms of modes this property can be written as
-\begin{equation}
-  \label{eq:93}
-  \begin{aligned}
-    & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
-    & (J^a_n\phi_{\lambda})=0\quad \mbox{for}\; n>0\\
-  \end{aligned}
-\end{equation}
-We can associate the state $\left|\phi_{\lambda}\right>$ to the field $\phi_{\lambda}$
-  \begin{equation}
-    \label{eq:94}
-    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
-  \end{equation}
-Then the conditions (\ref{eq:93}) for WZW primary field are
-\begin{equation}
-  \label{eq:95}
-  \begin{aligned}
-    & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
-    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
-  \end{aligned}
-\end{equation}
-It is easy to see that the action of the Virasoro generators is
-\begin{equation}
-  \label{eq:96}
-  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
-\end{equation}
-Here we used the explicit form of the quadratic Casimir operator eigenvalue.
-
-Primary fields live in integrable finite-dimensional representations since infinite-dimensional and non-integrable fields are decoupled from the correlation functions.
-
-All secondary states are of the form
-\begin{equation}
-  \label{eq:97}
-  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
-\end{equation}
-For the correlation functions of primary fields we can obtain Knizhnik-Zamolodchikov equations which follow from global $G\times G$ invariance
-\begin{equation}
-  \label{eq:98}
-  \left(\partial_{z_i}+\frac{1}{k+h^v}\sum_{i\neq j}\frac{\sum_a t^a_i\otimes t^a_j}{z_i-z_k}\right)
-  \left<\phi_1(z_1)\dots \phi_n(z_n)\right>=0
-\end{equation}
-So the theory is completely determined by the representations of affine Lie algebra $\hat{\mathfrak{g}} $.
-
-\subsubsection{Modular invariants}
-\label{sec:modular-invariants}
-
-In previous section we studied holomorphic and antiholomorphic sectors of the theory separately.
-But in physically sensible theories this sectors should be entangled.
-It is required for the theory to be well-defined on the higher genus Riemann surfaces (see \cite{gaberdiel2000icf} and references therein) and also if we want our theory to describe critical behavior \cite{difrancesco1997cft}.
-In the critical point theory has conformal invariance, holomorphic and antiholomorphic sectors are decoupled, but in the vicinity of critical point there exists some large scale so the sectors should interact.
-
-!!! Expand this argumentation !!!
-
-The necessary constraint for the theory to be well-defined on higher Riemann surfaces, which is also believed to be sufficient, is that the vacuum correlator on the torus is independent of its parametrisation \cite{gaberdiel2000icf}.
-Conformal theory on the higher genus Riemann surfaces is important for the string theory since this theory describes string interaction.
-
-Two-dimensional torus is described as quotient space of $\mathbb{R}^2\approx \mathbb{C}$ by the relations $z\sim z+w_1$ and $z\sim z+w_2$, where $w_1$ and $w_2$ are not parallel.
-
-The complex structure of the torus is conformally equivalent to a torus for which the relations are $z\sim z+1$ and $z\sim z+\tau$ where $\tau$ is in the upper half plane of $\mathbb{C}$.
-It is also easy to see that $\tau$, $T(\tau)=\tau+1$ and $S(\tau)=-\frac{1}{\tau}$ describe conformally equivalent tori.
-Two maps $T$ and $S$ generate the group $SL(2,\mathbb{Z})/\mathbb{Z}_2$ that consists of matrices of the form
-\begin{equation}
-  \label{eq:99}
-  A=
-  \begin{pmatrix}
-    a & b\\
-    c & d 
-  \end{pmatrix}
-  \quad\mbox{where}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
-\end{equation}
-and matrices $A$ and $-A$ have the same action on $\tau$
-\begin{equation}
-  \label{eq:100}
-  \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
-\end{equation}
-The parameter $\tau$ is called the modular parameter and the group  $SL(2,\mathbb{Z})/\mathbb{Z}_2$ is called the modular group.
-
-Given a conformal field theory that is defined on the Riemann sphere, the vacuum
-correlator on the torus can be determined as follows. First, we cut the torus along one
-of its non-trivial cycles; the resulting surface is a cylinder (or an annulus) whose shape
-depends on one complex parameter $q$. Since the annulus is a subset of the sphere, the
-conformal field theory on the annulus is determined in terms of the theory on the sphere.
-In particular, the states that can propagate in the annulus are precisely the states of
-the theory as defined on the sphere.
-In order to reobtain the torus from the annulus, we have to glue the two ends of
-the annulus together; in terms of conformal field theory this means that we have to sum
-over a complete set of states. The vacuum correlator on the torus is therefore described
-by a trace over the whole space of states, the partition function of the theory,
-\begin{equation}
-  \label{eq:101}
-  \sum_{(i,j)}Tr_{\mathcal{H}_{(i,j)}}(\mathcal{O}(q,\bar q)),
-\end{equation}
-where $\mathcal{O}(q,\bar q)$ is the operator that describes the propagation of the states along the annulus,
-\begin{equation}
-  \label{eq:102}
-  \mathcal{O}(q,\bar q)=q^{L_0-\frac{c}{24}}\bar q^{\bar L_0-\frac{\bar c}{24}}
-\end{equation}
-The propagator depends on the actual shape of the annulus that is described in terms
-of the complex parameter $q$. For a given torus that is described by $\tau$ , there is a natural
-choice for how to cut the torus into an annulus, and the complex parameter $q$ that is
-associated to this annulus is $q=e^{2\pi i \tau}$. Since the tori that are described by $\tau$ and $A\tau$
-(where $A \in SL(2, \mathbb{Z})$) are equivalent, the vacuum correlator is only well-defined provided
-that (\ref{eq:101}) is invariant under this transformation. This provides strong constraints on
-the spectrum of the theory.
-
-Each of the spaces $\mathcal{H}_{(i,j)}$ is a tensor product of an irreducible representation $\mathcal{H}_j$ of chiral algebra and an irreducible representation $\bar{\mathcal{H}}_{\bar{j}}$ of antichiral algebra.
-Then the vacuum correlator on the torus (\ref{eq:101}) takes the form
-\begin{equation}
-  \label{eq:103}
-  \sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
-\end{equation}
-where $\chi_j$ is the character of the representation $\mathcal{H}_j$,
-\begin{equation}
-  \label{eq:104}
-  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{where}\; q=e^{2\pi i \tau}
-\end{equation}
-Characters transform into one another under modular transformations,
-\begin{equation}
-  \label{eq:107}
-  \chi_j(-\frac{1}{\tau})=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{and}\quad \chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
-\end{equation}
-where $S$ and $T$ are constant matrices. This fact is proved for a certain class of conformal field theories \cite{gaberdiel2000icf}.
-
-For WZW-models the representations are determined by highest weights $\hat \lambda, \hat \xi$. Then we can write
-\begin{equation}
-  \label{eq:105}
-  \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi} L_{\hat \lambda}\otimes L_{\hat \xi}
-\end{equation}
-The partition function is rewritten as
-\begin{equation}
-  \label{eq:106}
-  Z(\tau)=\sum_{\hat \lambda,\hat \xi\in P^{(k)}_{+}} \chi_{\hat \lambda}(\tau)M_{\hat \lambda\hat\xi}\bar \chi_{\hat \xi}(\bar \tau)
-\end{equation}
-The element of the mass matrix $M_{\hat \lambda\hat\xi}$ can be thought of as the multiplicity of primary field with weights $\hat\lambda,\hat \xi$.
-It has following properties:$M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, it is modular invariant
-\begin{equation}
-  \label{eq:108}
-  \begin{aligned}
-    T^{\dagger}MT=S^{\dagger}MS=M,\\
-    [M,S]=[M,T]=0,
-  \end{aligned}
-\end{equation}
-and $M_{00}=1$ for the uniqueness of vacuum.
-
-The simplest case of diagonal matrix $M$ corresponds to equal holomorphic and antiholomorphic conformal dimensions.
-There are several ways to construct non-diagonal modular invariants from diagonal \cite{difrancesco1997cft}:
-\begin{itemize}
-\item Method of outer automorphisms
-\item Conformal embedding into bigger theory
-\item Galois-transpositions
-\end{itemize}
-Here we will discuss conformal embeddings.
-
-\subsubsection{Conformal embeddings}
-\label{sec:conformal-embeddings}
-
-\section{Affine Lie algebras representations}
-\label{sec:affine-lie-algebras}
-
-\subsection{Verma modules}
-\label{sec:verma-modules}
-
-Verma module is a simple thing. It can be easily understood in the framework of induced representations.
-
-Verma module with highest weight $\lambda$ of algebra $g$ is the space $U(g)\underset{U(b_{+})}{\otimes} D_{\lambda}(b_{+})$, where $\underset{U(b_{+})}{\otimes}$ means that the action of elements of $U(b_{+})$ ``falls through'' left part of tensor product onto the right part.
-
-Here $b_{+}$ is Borel sub-algebra ($x_{+},h$ for $sl(2)$), $D_{\lambda}(b_{+})$ is special representation of $b_{+}$, such that $D(x_{+})=0,\; D(h)=\lambda(h)$.
-$g$ acts on the representation space from the left, it means that we should expand element of $g$ in some base, and then commute all the elements of $b_{+}$ to the right, so that they can act on space $D_{\lambda}(b_{+})$.
-
-The infinite set of fields (\ref{eq:65}) corresponds to Verma module of algebra, which is Virasoro algebra in the simplest case and semidirect product of Virasoro and Kac-Moody algebra for WZW model.
-Also it is shown that for Wess-Zumino model the representations of the algebra are in fact the representations of current algebra only, which is Kac-Moody algebra.
-
-Note also, that Viraso algebra belongs to universal enveloping of Kac-Moody algebra.
-
-\subsection{Irreducible representations}
-\label{sec:irred-repr}
-
-\bibliography{article}{}
+\bibliography{CFTNotes}{}
 \bibliographystyle{utphys}

### 2009-08-31 AffineLieAlgebras/InformalNotes/ModularInvariantsAndBranching.tex
Preliminaries on modular invariants are completed, time to move to conformal embeddings

@@
 
+\section{Модулярная инвариантность}
+\label{sec:modular-invariance}
+
+Если мы изучаем конформную теорию поля на плоскости или на сфере, то мы можем рассматривать голоморфный и антиголоморфный сектора независимо.
+Если говорить о WZW-моделях, то примарные поля принадлежат тензорному произведению неприводимых представлений аффинной алгебры.
+
+Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать взаимодействия струн.
+Считается, что для этого необходимо (и, возможно, достаточно \cite{gaberdiel2000icf}) чтобы теория была определена на торе.
+
+В теории критического поведения конформная инвариантность имеет место только в критической точке, где голоморфный и антиголоморфный сектора расцеплены.
+Но вблизи критической точки эти сектора должны быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве параметров, то эта связь должна сохраняться и в критической точке.
+Физический спектр теории должен плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической точке.
+Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния \cite{difrancesco1997cft}.
+Здесь естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории на торе.
+
+Если мы наложили периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$, то статсумма записывается в виде
+\begin{equation}
+  \label{eq:1}
+  Z(\tau)=Tr \exp 2\pi i (\tau (L_0-c/24)-\bar{\tau} (\bar{L}_0-c/24))
+\end{equation}
+Или, если ввести $q=\exp 2\pi i \tau$
+\begin{equation}
+  \label{eq:2}
+  Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
+\end{equation}
+Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
+
+Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование модулярной инвариантности статсуммы.
+
+Комплексная структура такого тора конформно эквивалентна тору, для которого соотношения эквивалентности записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости $\mathbb{C}$.
+
+Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают конформно-эквивалентные торы.
+Отображения $T$ и $S$ порождают группу  $SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
+\begin{equation}
+  \label{eq:99}
+  A=
+  \begin{pmatrix}
+    a & b\\
+    c & d 
+  \end{pmatrix}
+  \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+\end{equation}
+и матрицы $A$ и $-A$ действуют одинаково на $\tau$
+\begin{equation}
+  \label{eq:100}
+  \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+\end{equation}
+ $\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ --- модулярной группой.
+
+Конформная теория поля задаётся примарными полями $\Phi_a$ с конформными размерностями $\Delta_a$:
+\begin{equation}
+  \label{eq:3}
+  \begin{split}
+    \Phi_{a}(z)\underset{z\to w(z)}{\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta_a}\Phi_{a}(w(z))\\
+    L_n \Phi_a=0,\quad n>0\\
+    L_0 \Phi_a=\Delta_a \Phi_a\\
+  \end{split}
+\end{equation}
+
+Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные произведения неприводимого представления  $\mathcal{H}_j$ киральной алгебры и неприводимого представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры.
+Тогда статсуммы на торе (\ref{eq:2}) может быть переписана в виде
+\begin{equation}
+  \label{eq:4}
+  \sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
+\end{equation}
+где $\chi_j$ --- характер пердставления $\mathcal{H}_j$,
+\begin{equation}
+  \label{eq:5}
+  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i \tau}
+\end{equation}
+Характеры переходят друг в друга при модулярных преобразованиях:
+\begin{equation}
+  \label{eq:107}
+  \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad \chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
+\end{equation}
+где $S$ и $T$ --- постоянные матрицы. Это верно для большого класса конформных теорий поля \cite{gaberdiel2000icf}.
+
+Для WZW-моделей представления определяются старшими весами $\hat \lambda, \hat \xi$. Тогда
+\begin{equation}
+  \label{eq:6}
+  \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi} L_{\hat \lambda}\otimes L_{\hat \xi}
+\end{equation}
+Статсумма даётся выражением
+\begin{equation}
+  \label{eq:7}
+  Z(\tau)=\sum_{\hat \lambda,\hat \xi\in P^{(k)}_{+}} \chi_{\hat \lambda}(\tau)M_{\hat \lambda\hat\xi}\bar \chi_{\hat \xi}(\bar \tau)
+\end{equation}
+Элементы так называемой матрицы масс $M_{\hat \lambda\hat\xi}$ можно рассматривать как кратности примарных полей с весами $\hat\lambda,\hat \xi$.
+У них есть следующие свойства: $M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, модулярная инвариантность
+\begin{equation}
+  \label{eq:8}
+  \begin{aligned}
+    T^{\dagger}MT=S^{\dagger}MS=M,\\
+    [M,S]=[M,T]=0,
+  \end{aligned}
+\end{equation}
+и $M_{00}=1$ для единственности вакуума.
+
+Простейший случай диагональной матрицы $M$ соответствует равным голоморфным и антиголоморфным конформным размерностям.
+Есть несколько способов построения недиагональных модулярных инвариантов из диагональных \cite{difrancesco1997cft}:
+\begin{itemize}
+\item Метод внешних автоморфизмов
+\item Конформное вложение в большую теорию
+\item Перестановки Галуа
+\end{itemize}
+Мы будем обсуждать только конформные вложения.
+
+\section{Конформные вложения}
+\label{sec:conformal-embeddings}
+Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory. !!! Provide an explanation !!!
+
+The states for the theory that corresponds to the algebra $\mathfrak{g}$
+\begin{equation}
+  \label{eq:109}
+  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq\dots>0
+\end{equation}
+For sub-algebra $\mathfrak{p}\subset\mathfrak{g}$
+\begin{equation}
+  \label{eq:110}
+  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\mathcal{P}\lambda\right>
+\end{equation}
+Here $\tilde{J}^{a'_j}_{-n_j}$ are the generators of $\mathfrak{p}$ and $\mathcal{P}$ is the projection of $\mathfrak{g}$ to $\mathfrak{p}$.
+$\mathfrak{g}$-invariance of vacuum entails its $\mathfrak{p}$-invariance, but it is not the case for energy-momentum tensor.
+So energy-momentum tensor of bigger theory should consist only of generators of $\hat{\mathfrak{p}}$.
+Then $T_{\hat{\mathfrak{g}}}=T_{\hat{\mathfrak{p}}}\Rightarrow c(\hat{\mathfrak{g}})=c(\hat{\mathfrak{p}})$.
+This leads to equation
+\begin{equation}
+  \label{eq:111}
+  \frac{k\;dim\mathfrak{g}}{k+g}=\frac{x_e k\; dim\mathfrak{p}}{x_ek+p}
+\end{equation}
+Here $x_e$ is the embedding index and $g$, $p$ are dual Coxeter numbers of corresponding algebras. !!! Prove and expand !!!
+
+It can be shown that solutions of equation (\ref{eq:111}) exist only for level 1 $k=1$.
+
+There exist only finite number of such embeddings.
+
+{\bf Examples}
+\begin{itemize}
+\item $su(2)\subset su(3),\; x_e=4$
+\item $\hat{su}(2)_{10}\subset\hat{sp}(4)_1$
+\item $\hat{su}(2)_{28}\subset(\hat{G_2})_1$
+\item $\hat{su}(2)_{16}\oplus\hat{su}(3)\subset (\hat{E_8})_1$
+\end{itemize}
+
+Branching $\hat{\lambda}\to \bigoplus_{\hat{\mu}}b_{\hat{\lambda}\hat{\mu}}\hat{\mu}$
+\begin{equation}
+  \label{eq:112}
+  h_{\hat{\lambda}}+n=h_{\hat{\mu}},\quad \frac{(\lambda,\lambda+2\rho)}{2(1+g)}+n=\frac{(\mu,\mu+2\rho)}{2(x_e+p)}
+\end{equation}
+The simple way is to calculate the dimensions of all the representations of simple finite-dimensional Lie algebras $\mathfrak{g},\mathfrak{p}$ and find all the triples $(\lambda,\mu,n)$, satisfying (\ref{eq:112}).
+Then investigate the representation $L_{\hat{\lambda}}$ of level $n$ as the sum of irreducible representations of $\mathfrak{g}$ and write out all the branching rules of these representations in representations of subalgebra $\mathfrak{p}$.
+The number of times the representation with highest weight $\mu$ appears in this listing is the required branching coefficient $b_{\hat{\lambda},\hat{\mu}}$.
+
+  Then non-diagonal modular invariants are obtained by substitution of character relations. For example, having calculated branching coefficients for $\hat{su}(2)_{28}\subset (\hat{G_2})_1$
+  \begin{equation}
+    \label{eq:113}
+    \begin{aligned}
+      & [1,0,0]\to [28,0]\oplus [18,10]\oplus [10,18]\oplus [0,28]\\
+      & [0,0,1]\to [22,6]\oplus [16,12]\oplus [12,16]\oplus [6,22]\\
+    \end{aligned}
+  \end{equation}
+we get following modular-invariant partition function
+\begin{equation}
+  \label{eq:114}
+  Z=\left|\chi_{[28,0]}+\chi_{[18,10]}+\chi_{[10,18]}+\chi_{[0,28]}\right|^2+\left|\chi_{[22,6]}+\chi_{[16,12]}+\chi_{[12,16]}+\chi_{[6,22]}\right|^2
+\end{equation}
+
 \bibliography{CFTNotes}{}

### 2009-08-31 AffineLieAlgebras/InformalNotes/ModularInvariantsAndBranching.tex
Note on modular invariants is almost completed.

@@
 \label{sec:conformal-embeddings}
-Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory. !!! Provide an explanation !!!
 
-The states for the theory that corresponds to the algebra $\mathfrak{g}$
+Состояния в теории соответствующей алгебре $g$ (с киральной алгеброй $Vir\ltimes \hat g$) имеют вид
 \begin{equation}
-  \label{eq:109}
+  \label{eq:9}
   J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq\dots>0
 \end{equation}
-For sub-algebra $\mathfrak{p}\subset\mathfrak{g}$
+А для подалгебры $\mathfrak{p}\subset\mathfrak{g}$
 \begin{equation}
-  \label{eq:110}
+  \label{eq:10}
   \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\mathcal{P}\lambda\right>
 \end{equation}
-Here $\tilde{J}^{a'_j}_{-n_j}$ are the generators of $\mathfrak{p}$ and $\mathcal{P}$ is the projection of $\mathfrak{g}$ to $\mathfrak{p}$.
-$\mathfrak{g}$-invariance of vacuum entails its $\mathfrak{p}$-invariance, but it is not the case for energy-momentum tensor.
-So energy-momentum tensor of bigger theory should consist only of generators of $\hat{\mathfrak{p}}$.
-Then $T_{\hat{\mathfrak{g}}}=T_{\hat{\mathfrak{p}}}\Rightarrow c(\hat{\mathfrak{g}})=c(\hat{\mathfrak{p}})$.
-This leads to equation
+Здесь $\tilde{J}^{a'_j}_{-n_j}$ --- генераторы $\mathfrak{p}$, а $\mathcal{P}$ --- проекция $\mathfrak{g}$ на $\mathfrak{p}$.
+Очевидно, что $\mathfrak{g}$-инвариантность вакуума ведёт к его $\mathfrak{p}$-инвариантности, но нет оснований считать, что проекция сохраняет конформную инвариантность.
+Это легко увидеть из рассмотрения тензора энергии - импульса.
+Действительно, в тензоре энергии - импульса в виде Сугавары можно выделить часть, составленную из тех комбинаций генераторов $g$, которые входят в $p$.
+Но есть ещё и остаток.
+Из-за него действие генераторов Вирасоро на состояния (\ref{eq:10}) будет выводить из этого набора.
+Таким образом в ситуации общего положения конформная инвариантность нарушается.
+
+Однако есть исключения.
+Так для представлений уровня 1 simply-laced алгебр тензор энергии - импульса в форме Сугавары состоит только из генераторов Картана.
+В этом случае он может быть пере-выражен через генераторы подалгебры и конформная инвариантность сохраняется.
+Тогда $T_{\hat{\mathfrak{g}}_k}=T_{\hat{\mathfrak{p}}_{\tilde k}}\Rightarrow c(\hat{\mathfrak{g}}_k)=c(\hat{\mathfrak{p}}_{\tilde k})$.
+Это можно переписать в виде равенства
 \begin{equation}
-  \label{eq:111}
+  \label{eq:11}
   \frac{k\;dim\mathfrak{g}}{k+g}=\frac{x_e k\; dim\mathfrak{p}}{x_ek+p}
 \end{equation}
-Here $x_e$ is the embedding index and $g$, $p$ are dual Coxeter numbers of corresponding algebras. !!! Prove and expand !!!
+Где $x_e$ - индекс вложения, а $g$, $p$ - дуальные числа Кокстера соответствующих алгебр и было использовано равенство $\tilde k=x_e k$.
+\begin{equation}
+  \label{eq:12}
+  x_e=\frac{\left|\mathcal{P}\Theta_g\right|^2}{\left| \Theta_p\right|^2},\quad
+  x_e=\sum_{\mu\in P_{+}}b_{\lambda\mu}\frac{x_{\mu}}{x_{\lambda}}
+\end{equation}
+(Здесь $x_{\lambda}$ - индекс представления со старшим весом $\lambda$:
+\begin{equation}
+  \label{eq:13}
+  x_{\lambda}=\frac{dim \left|\lambda\right|(\lambda,\lambda+\rho)}{2 dim g}
+\end{equation})
 
-It can be shown that solutions of equation (\ref{eq:111}) exist only for level 1 $k=1$.
+Вложения, которые удовлетворяют условию (\ref{eq:11}), называются конформными.
 
-There exist only finite number of such embeddings.
+Нетрудно показать, что решения уравнения (\ref{eq:11}) существуют только для уровня $k=1$.
 
-{\bf Examples}
+(Существует конечное число конформных вложений, они классифицированы).
+
+{\bf Примеры}
 \begin{itemize}

### 2009-08-31 AffineLieAlgebras/InformalNotes/ModularInvariantsAndBranching.tex
Text on modular invariants is completed.

@@
 
-Branching $\hat{\lambda}\to \bigoplus_{\hat{\mu}}b_{\hat{\lambda}\hat{\mu}}\hat{\mu}$
+\section{Конформные коэффициенты ветвления}
+\label{sec:conformal-branching-rules}
+
+Для ветвления аффинных алгебр $\hat{\lambda}\to \bigoplus_{\hat{\mu}}b_{\hat{\lambda}\hat{\mu}}\hat{\mu}$ существуют разные алгоритмы, однако мы можем существенно сократить работу при рассмотрении конформных вложений.
+
+Во-первых, заметим, что если коэффициент $b_{\hat\lambda\hat\mu}$ отличен от нуля, то конечная часть старшего веса $\mu$ модуля $L_{\hat\mu}$ находится в некотором грейде $n$  бесконечномерного модуля $L_{\hat\lambda}$ уровня 1.
+Сохранение конформной инвариантности ведет к соотношению для конформных размерностей соответствующих полей
 \begin{equation}
-  \label{eq:112}
-  h_{\hat{\lambda}}+n=h_{\hat{\mu}},\quad \frac{(\lambda,\lambda+2\rho)}{2(1+g)}+n=\frac{(\mu,\mu+2\rho)}{2(x_e+p)}
+  \label{eq:14}
+  \Delta_{\hat\lambda}+n=\Delta_{\hat\mu},
 \end{equation}
-The simple way is to calculate the dimensions of all the representations of simple finite-dimensional Lie algebras $\mathfrak{g},\mathfrak{p}$ and find all the triples $(\lambda,\mu,n)$, satisfying (\ref{eq:112}).
-Then investigate the representation $L_{\hat{\lambda}}$ of level $n$ as the sum of irreducible representations of $\mathfrak{g}$ and write out all the branching rules of these representations in representations of subalgebra $\mathfrak{p}$.
-The number of times the representation with highest weight $\mu$ appears in this listing is the required branching coefficient $b_{\hat{\lambda},\hat{\mu}}$.
+которое переписывается в виде
 
-  Then non-diagonal modular invariants are obtained by substitution of character relations. For example, having calculated branching coefficients for $\hat{su}(2)_{28}\subset (\hat{G_2})_1$
 \begin{equation}
-    \label{eq:113}
+  \label{eq:15}
+  \frac{(\lambda,\lambda+2\rho)}{2(1+g)}+n=\frac{(\mu,\mu+2\rho)}{2(x_e+p)}
+\end{equation}
+
+Используя этот факт можно  легко вычислять правила ветвления.
+Для этого надо вычислить размерности интегрируемых представлений обеих алгебр  $\mathfrak{g},\mathfrak{p}$ и найти все тройки  $(\lambda,\mu,n)$, удовлетворяющие соотношению (\ref{eq:15}).
+Затем рассматриваем разложения представления $L_{\hat\lambda}$ в грейде $n$ в сумму неприводимых представлений конечномерной алгебры $\mathfrak{g}$ и выписываем правила ветвления этих представлений на представления подалгебры $\mathfrak{p}$.
+Коэффициент ветвления $b_{\hat{\lambda},\hat{\mu}}$ --- это сколько раз представление со старшим весом $\mu$ появляется в этом списке.
+
+{\bf Пример}
+
+$\hat{su}(2)_4\subset \hat{su}(3)_1$.
+Список конформных размерностей:
+\begin{equation}
+  \label{eq:16}
+  \begin{aligned}
+    \hat{su}(2)_4&: h_{[4,0]}=0, h_{[3,1]}=\frac{1}{8}, h_{[2,2]}=\frac{1}{3}, h_{[1,3]}=\frac{5}{8}, h_{[0,4]}=1\\
+    \hat{su}(3)_1&: h_{[1,0,0]}=0, h_{[0,1,0]}=h_{[0,0,1]}=\frac{1}{3}    
+  \end{aligned}
+\end{equation}
+Отсюда видно, что
+\begin{equation}
+  \label{eq:17}
+  \begin{aligned}
+    \left[1,0,0\right] &\to c_1 [4,0]_0\oplus c_2 [0,4]_1\\
+    [0,1,0] &\to c_3 [2,2]_0\\
+    [0,0,1] &\to c_4 [2,2]_0
+  \end{aligned}
+\end{equation}
+Где $c_1, c_2, c_3, c_4$ - коэффициенты, которые надо найти, а нижний индекс указывает грейд $n$.
+
+Коэффициенты $c_1, c_3, c_4$ вычисляются из правил ветвления в нулевом грейде. В этом грейде $L_{\hat\lambda}$ содержит только $L_{\lambda}$. Из правил ветвления
+\begin{equation}
+  \label{eq:18}
+  (0,0)\to (0),\quad (1,0)\to (2),\quad (0,1)\to (2)
+\end{equation}
+мы получаем, что $c_1=c_3=c_4=1$. $c_2$ вычисляется из представления грейда 1, содержащего конечномерное представление $(1,1)$ с правилом ветвления
+\begin{equation}
+  \label{eq:19}
+  (1,1)\to (4)\oplus (2)
+\end{equation}
+То есть $c_2$ тоже равен 1.
+
+После нахождения коэффициентов ветвления, недиагональные модулярные инварианты строятся путем подстановки соотношений для характеров.
+Например, зная коэффициенты ветвления для вложения $\hat{su}(2)_{28}\subset (\hat{G_2})_1$
+  \begin{equation}
+    \label{eq:20}
     \begin{aligned}
@@
   \end{equation}
-we get following modular-invariant partition function
+мы получаем следующую модулярно-инвариантную статсумму:
 \begin{equation}
-  \label{eq:114}
+  \label{eq:21}
   Z=\left|\chi_{[28,0]}+\chi_{[18,10]}+\chi_{[10,18]}+\chi_{[0,28]}\right|^2+\left|\chi_{[22,6]}+\chi_{[16,12]}+\chi_{[12,16]}+\chi_{[6,22]}\right|^2

### 2009-10-11 AffineLieAlgebras/InformalNotes/BranchingProblems.tex
Some work

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}
\begin{document}
Мы хотим раскладывать представление $L^{\mu}$ алгебры
$\frak{g}$ на представления подалгебры $\frak{a}$
\begin{equation}
  \label{eq:1}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }
\end{equation}
Верна следующая формула для характеров:
\begin{equation}
  \label{eq:2}
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
Произведение характеров модулей старшего веса равно характеру тензорного произведения модулей.

Характеры инвариантны относительно группы Вейля.
\begin{equation}
  \label{eq:3}
  ch(L^{\omega\mu})=ch(L^{\mu})
\end{equation}

Явное выражение для формальных характеров даётся формулой Вейля-Каца:
\begin{equation}
  \label{eq:4}
  ch(L^{\mu})=\frac{\sum_{\omega\in W}\epsilon(\omega)e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in \Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}}
\end{equation}
Эту формулу также можно записать в виде
\begin{equation}
  \label{eq:5}
  ch(L^{\mu})=\sum_{\omega\in W}\epsilon(\omega)e^{\omega(\mu+\rho)-\rho} \left(\prod_{\alpha\in \Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}\right)^{-1}
\end{equation}
Обратный элемент для монома $(1-e^{-\alpha})$ - это бесконечный формальный ряд
\begin{equation}
  \label{eq:6}
  1+e^{-\alpha}+e^{-2\alpha}+e^{-3\alpha}+\dots
\end{equation}

\end{document}

### 2009-10-16 AffineLieAlgebras/InformalNotes/BranchingProblems.tex
Planning on the upcoming article on branching for affine lie algebras.

@@
   \label{eq:5}
-  ch(L^{\mu})=\sum_{\omega\in W}\epsilon(\omega)e^{\omega(\mu+\rho)-\rho} \left(\prod_{\alpha\in \Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}\right)^{-1}
+  ch(L^{\mu})=\left( \sum_{\omega\in W}\epsilon(\omega)e^{\omega(\mu+\rho)-\rho} \right) \left(\prod_{\alpha\in \Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}\right)^{-1}
 \end{equation}
@@
 \end{equation}
+В работе \cite{ilyin812pbc} рекуррентное соотношение для коэффициентов ветвления выводилось следующим образом.
+Бралось соотношение \eqref{eq:2}, характеры расписывались по формуле Вейля-Каца \eqref{eq:5}.
+\begin{multline}
+  \label{eq:7}
+  \pi_{\mathfrak{a}}\left(\left(\sum_{\omega\in W}\epsilon(\omega)e^{\omega(\mu+\rho)-\rho}\right) \left(\prod_{\alpha\in \Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}\right)^{-1}\right)= \\
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
+  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
+\end{multline}
+Затем обе стороны соотношения умножались на $\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}\right)$.
+Так как умножение на моном коммутирует с проектором, то $\prod_{\alpha\in \Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}$ сокращалось в левой части.
+
+Однако в случае, если $\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}\right)=0$, получить содержательное рекуррентное соотношение не удается, так как обе стороны равенства \eqref{eq:7} умножаются на ноль.
+
+Это происходит в том случае, если среди положительных корней алгебры $\mathfrak{g}$ есть ортогональные корневой системе вложенной подалгебры $\mathfrak{a}$.
+Обозначим набор таких корней через $\Delta_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
+Решить эту проблему можно если умножать не на $\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}\right)$, а на $\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}\right)$.
+
+Тогда
+\begin{multline}
+  \label{eq:9}
+  \pi_{\mathfrak{a}}\left(\left(\sum_{\omega\in W}\epsilon(\omega)e^{\omega(\mu+\rho)-\rho}\right) \left(\prod_{\alpha\in \Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}\right)^{-1}\right)= \\
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
+  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
+\end{multline}
+
+\bibliography{CFTNotes}{}
+\bibliographystyle{utphys}
 

### 2009-10-19 AffineLieAlgebras/InformalNotes/article.tex
Started work on paper on branching.

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}
\begin{document}
Plan:

\section{Introduction}
\label{sec:introduction}

\subsection{Notation}
\label{sec:notation}

Consider the affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
underlying finite-dimensional subalgebras $\overset{\circ }{\frak{g}}$ and $%
\overset{\circ }{\frak{a}}$ and an injection $\frak{a}\longrightarrow \frak{g%
}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
}}^{\ast }$ and $\frak{h}_{\overset{\circ }{\frak{a}}}^{\ast }\subset \frak{h%
}_{\overset{\circ }{\frak{g}}}^{\ast }$\ .

We use the following notations adopted from the paper \cite{ilyin812pbc}.

$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ -- the integrable module
of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
-module with the highest weight $\nu $ );

$r$ , $\left( r_{\frak{a}}\right) $ -- the rank of the algebra $\frak{g}$ $%
\left( \text{resp. }\frak{a}\right) $ ;

$\Delta $ $\left( \Delta _{\frak{a}}\right) $-- the root system; $\Delta
^{+} $ $\left( \text{resp. }\Delta _{\frak{a}}^{+}\right) $-- the positive
root system (of $\frak{g}$ and $\frak{a}$ respectively);

$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
\alpha \right) \right) $ -- the multiplicity of the root $\alpha$ in $\Delta 
$ (resp. in $\left( \Delta _{\frak{a}}\right) $);

$\overset{\circ }{\Delta }$ , $\left( \overset{\circ }{\Delta _{\frak{a}}}%
\right) $ -- the finite root system of the subalgebra $\overset{\circ }{%
\frak{g}}$ (resp. $\overset{\circ }{\frak{a}}$);

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ -- the
weight diagram of $L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) 
$ ;

$W$ , $\left( W_{\frak{a}}\right) $-- the corresponding Weyl group;

$C$ , $\left( C_{\frak{a}}\right) $-- the fundamental Weyl chamber;

$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ -- the Weyl vector;

$\epsilon \left( w\right) :=\det \left( w\right) $ ;

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ -- the $i
$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \text{resp. }\frak{a}%
\right) $; $i=0,\ldots ,r$ ,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$\delta $ -- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);

$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
}\right) $-- the basic coroot for $\frak{g}$ $\left( \text{resp. }\frak{a}%
\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$\overset{\circ }{\xi }$ , $\overset{\circ }{\xi _{\left( \frak{a}\right) }}$
-- the finite (classical) part of the weight $\xi \in P$ , $\left( \text{%
resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $\ ;

$\lambda =\left( \overset{\circ }{\lambda };k;n\right) $ -- the
decomposition of an affine weight indicating the finite part $\overset{\circ 
}{\lambda }$, level $k$ and grade $n$\ .

$P$ $\left( \text{resp. } P_{\frak{a}}\right) $ \ -- the weight lattice;

$M \left( \text{resp. }M_{\frak{a}}\right) :=$

\noindent $=\left\{ 
\begin{array}{c}
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\text{ }\left( \text{resp. }%
\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \frak{a}\right) i}^{\vee }\right) 
\text{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\ 
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\text{ }\left( \text{resp. }\sum_{i=1}^{r}%
\mathbf{Z}\alpha _{\left( \frak{a}\right) i}\right) \text{for }A_{r}^{\left(
u\geq 2\right) }\text{ and }A\neq A_{2r}^{\left( 2\right) },
\end{array}
\right\} ;$

$\mathcal{E}$\ , $\left( \mathcal{E}_{\frak{a}}\right) $-- the group algebra
of the group $P$ (resp. $P_{\frak{a}} $);

$\Theta _{\lambda }:=e^{-\frac{\left| \lambda \right| ^{2}}{2k}\delta
}\sum\limits_{\alpha \in M}e^{t_{\alpha }\circ \lambda }$ -- the classical
theta-function;

$\Theta _{\left( \frak{a}\right) \nu }:=e^{-\frac{\left| \nu \right| ^{2}}{%
2k_{\frak{a}}}\delta }\sum\limits_{\beta \in M_{\frak{a}}}e^{t_{\beta }\circ
\nu }$;\newline
notice that when the injection is considered the level $k_{\frak{a}}$ must
be correlated with the corresponding rescaling of roots;

$A_{\lambda }:=\sum\limits_{s\in \overset{\circ }{W}}\epsilon (s)\Theta
_{s\circ \lambda }$ $\left( \text{resp. }A_{\left( \frak{a}\right) \nu
}:=\sum\limits_{s\in \overset{\circ }{W_{\frak{a}}}}\epsilon (s)\Theta
_{\left( \frak{a}\right) s\circ \nu }\right) $;

$\Psi ^{\left( \mu \right) }:=e^{\frac{\left| \mu +\rho \right| ^{2}}{2k}%
\delta \ -\ \rho }A_{\mu +\rho }=e^{\frac{\left| \mu +\rho \right| ^{2}}{2k}%
\delta \ -\ \rho }\sum\limits_{s\in \overset{\circ }{W}}\epsilon (s)\Theta
_{s\circ \left( \mu +\rho \right) }=$

\noindent $=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$
-- the singular weight element for the $\frak{g}$-module $L^{\mu }$;

$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }:=e^{\frac{\left| \nu
+\rho _{_{\frak{a}}}\right| ^{2}}{2k_{\frak{a}}}\delta \ -\ \rho _{_{\frak{a}%
}}}A_{\left( \frak{a}\right) \nu +\rho _{_{\frak{a}}}}=e^{\frac{\left| \nu
+\rho _{_{\frak{a}}}\right| ^{2}}{2k_{\frak{a}}}\delta \ -\ \rho _{_{\frak{a}%
}}}\sum\limits_{s\in \overset{\circ }{W_{\frak{a}}}}\epsilon (s)\Theta
_{\left( \frak{a}\right) s\circ \left( \nu +\rho _{_{\frak{a}}}\right) }=$

\noindent $=\sum\limits_{w\in W_{\frak{a}}}\epsilon (w)e^{w\circ (\nu +\rho
_{_{\frak{a}}})-\rho _{_{\frak{a}}}}$ -- the corresponding singular weight
element for the $\frak{a}$-module $L_{\frak{a}}^{\nu }$;

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ -- the set of singular weights $%
\xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \overset{\circ }{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \overset{\circ }{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ ), (this set is similar to $P_{\mathrm{%
nice}}^{\prime }\left( \mu \right) $ in \cite{Wak1})

$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
}\right) $ -- the multiplicity of the weight $\xi \in P$ \ $\left( \text{%
resp. }\in P_{\frak{a}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
L_{\frak{a}}^{\nu } $);

$ch\left( L^{\mu }\right) $ $\left( \text{resp. }ch\left( L_{\frak{a}}^{\nu
}\right) \right) $-- the formal character of $L^{\mu }$ $\left( \text{resp. }%
L_{\frak{a}}^{\nu }\right) $;

$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
\mathrm{{mult}\left( \alpha \right) }}}=\frac{\Psi ^{\left( \mu \right) }}{%
\Psi ^{\left( 0\right) }}$ -- the Weyl-Kac formula.

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}=\Psi ^{\left( 0\right) }\quad $

\noindent $\left( \text{resp. }R_{\frak{a}}:=\prod_{\alpha \in \Delta _{%
\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{%
\left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $-- the
denominator.

\section{Recurrent formula for branching coefficients}
\label{sec:recurr-form-branch}

\begin{equation}
  \label{eq:1}
  k_{\nu}=\sum_{w\in W_a} k_{\rho_a-w(\nu+\rho_a)} + \sum_{w\in W}dim_{w(\mu+\rho)-\rho} \delta_{\nu,w(\mu+\rho)-\rho}
\end{equation}

\subsection{Proof}
\label{sec:proof}
Proof of the formula.

We start with the Weyl-Kac formula for the character of the module. 
\begin{equation}
  \label{eq:2}
  ch L^{\mu}=\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}}
\end{equation}
Proof of the irreducibility of factor-modules.

\section{Algorithm}
\label{sec:algorithm}

\section{Examples}
\label{sec:examples}

\subsection{Finite dimensional Lie algebras}
\label{sec:finite-dimens-lie}

B2->A1 etc.

\subsection{Affine Lie algebras}
\label{sec:affine-lie-algebras}

Branching of affine to affine and affine to classical.
\subsection{Physical applications}
\label{sec:phys-appl}

Modular invariants of WZW-models, partition functions etc.

\section{Conclusion}
\label{sec:conclusion}

\bibliography{CFTNotes}{}
\bibliographystyle{utphys}

\end{document}

### 2009-10-19 AffineLieAlgebras/InformalNotes/article.tex
Beginning of the proof

@@
 
-We start with the Weyl-Kac formula for the character of the module. 
+The decomposition of the representation of the algebra to the representations of the subalgebra can be symbolically written using formal characters and projection operator:
+\begin{equation}
+  \label{eq:3}
+  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
+    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
+  \Longrightarrow\quad
+  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
+\end{equation}
+Now using the Weyl-Kac formula for the character of the module
 \begin{equation}
@@
 \end{equation}
+we obtain the equality
+\begin{equation}
+  \label{eq:4}
+  \frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}} = 
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
+  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
+\end{equation}
+
+It is important to mention that the projection of some of the positive roots of the algebra $\mathfrak{g}$ can be equal to zero.
+These roots are orthogonal to the root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the algebra $\mathfrak{g}$.
+Let's denote the subset of these roots by $\Delta_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
+
 Proof of the irreducibility of factor-modules.

### 2009-10-21 AffineLieAlgebras/InformalNotes/article.tex
First draft of the formula

@@
 \theoremstyle{definition} \newtheorem{Def}{Definition}
+%\usepackage{verbatim} 
+\newenvironment{comment}
+{\par\noindent{\bf TODO}\\}
+{\\\hfill$\scriptstyle\blacksquare$\par}
+
 \begin{document}
@@
   \label{eq:4}
-  \frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}} = 
+  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = 
   \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
@@
 Let's denote the subset of these roots by $\Delta_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
+
+\begin{comment}
+  When such a subset does exist?  
+\end{comment}
+
+Now we can multiply the equation (\ref{eq:4}) by the term
+\begin{equation}
+  \label{eq:5}
+  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)
+\end{equation}
+This term is non-zero.
+
+Also we can see that 
+\begin{equation}
+  \label{eq:6}
+  \pi_{\mathfrak{a}} (P) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(P\cdot (1-e^{-\alpha})\right)
+\end{equation}
+The equation (\ref{eq:4}) takes the form
+\begin{multline}
+  \label{eq:7}
+  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
+  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
+  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
+\end{multline}
+The right-hand side of this equation can be reorganised as in the paper \cite{ilyin812pbc}. We introduce anomalous branching coefficients $k_{\lambda}$.
+\begin{equation}
+  \label{eq:10}
+  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
+        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
+  }^{\left( \mu \right) }e^{\lambda } 
+\end{equation}
+Also we multiply the equation (\ref{eq:7}) by the denominator of the right-hand side and get
+\begin{multline}
+  \label{eq:12}
+  \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
+  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)
+\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
+}^{\left( \mu \right) }e^{\lambda } 
+\end{multline}
+
+Now we should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
+
+\begin{comment}
+  Prove it  
+\end{comment}
+
+Then we can reorganise the summation on the left-hand side of the equation (\ref{eq:12}) in the following way
+\begin{multline}
+  \label{eq:13}
+   \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}  \;\pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
+   \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}  \;\pi_{\mathfrak{a}}\left(\sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right)
+\end{multline}
+
+Let's denote the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.
+\begin{comment}
+  Shouldn't we prove that such a subalgebra exists and is tractable?
+\end{comment}
+Then we see that
+\begin{multline}
+  \label{eq:14}
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}} =\\
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}=\\
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
+\end{multline}
+The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by $e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}})}$
+  \begin{multline}
+    \label{eq:15}
+    \pi_{\mathfrak{a}}\left(\sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
+    \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
+  \end{multline}
+These dimensions of the modules could be easily calculated using Weyl formula.
 

### 2009-10-23 AffineLieAlgebras/InformalNotes/article.tex
Description of regular embeddings

@@
 \begin{document}
-Plan:
+\title{\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}}
+\author{Vladimir Lyakhovsky\\
+Theoretical Department, SPb State University,\\
+198904, Sankt-Petersburg, Russia \\
+e-mail:lyakh1507@nm.ru \\
+[5mm] Anton Nazarov \\
+%EndAName
+Theoretical Department, SPb State University,\\
+198904, Sankt-Petersburg, Russia \\
+e-mail:antonnaz@gmail.com\\
+}
+\maketitle
+
+\begin{abstract}
+
+\end{abstract}
 
@@
 \circ (\nu +\rho _{a})-\rho _{a}}$ ), (this set is similar to $P_{\mathrm{%
-nice}}^{\prime }\left( \mu \right) $ in \cite{Wak1})
+nice}}^{\prime }\left( \mu \right) $ in \cite{wakimoto2001idl})
 
@@
 
+Now we should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
+
+Let's denote the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.
+
+Now we should discuss when the subset $\Delta_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
+
+If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta_{\bot}$ is empty.
+Then the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the formula (11) from the paper \cite{ilyin812pbc}.
+
+Non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
+Also the maximal regular embeddings are constructed by the exclusion of one or two roots from the extended Dynkin diagram of the algebra.
+Since this process can give us non-connected Dynkin diagrams we can see which roots are orthogonal to the root space of non-maximal regular subalgebra $\mathfrak{a}$.
+
+Consider for example regular embedding of $A_1\subset B_2$ ($su(2)\subset so(5)$).
+
+The extended Dynkin diagram of $B_2$ 
+\begin{equation}
+  \label{eq:8}
+  \begin{diagram}
+    \node{\circ}\arrow{e}{}\node{\circ}\arrow{e}{}\node{\circ}\\ \\
+    \node{\circ}\node[2]{\circ}
+  \end{diagram}
+\end{equation}
+We then drop central node and get the embedding $A_1\otimes A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
 \begin{comment}
-  When such a subset does exist?  
+  Consider special embeddings
 \end{comment}
@@
 
-Now we should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
+If the set $\Delta_{\bot}$ is non-empty then Weyl reflections corresponding to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
 
-\begin{comment}
-  Prove it  
-\end{comment}
+We have denoted the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.
 
@@
 
-Let's denote the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.
-\begin{comment}
-  Shouldn't we prove that such a subalgebra exists and is tractable?
-\end{comment}
 Then we see that

### 2009-10-23 AffineLieAlgebras/InformalNotes/article.tex
Proof is almost complete

@@
 \end{equation}
-Also we multiply the equation (\ref{eq:7}) by the denominator of the right-hand side and get
+Also we extract the common denominator of  the right-hand side of the equation (\ref{eq:7})
 \begin{multline}
   \label{eq:12}
-  \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
-  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)
+  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
+  \frac{\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)}
+  {  \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
 \sum_{\lambda \in P_{\frak{a}}}k_{\lambda
@@
   \label{eq:13}
-   \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}  \;\pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
-   \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}  \;\pi_{\mathfrak{a}}\left(\sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right)
+ \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
+ \pi_{\mathfrak{a}}\left(\sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right)
 \end{multline}
@@
 
-Proof of the irreducibility of factor-modules.
+Thus we have the equality
+\begin{multline}
+  \label{eq:9}
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+   \frac{\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)}
+   {   \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
+\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
+}^{\left( \mu \right) }e^{\lambda } 
+\end{multline}
+
+We can rewrite the fraction on the right-hand side as in the paper \cite{ilyin812pbc}.
+\begin{multline}
+  \label{eq:11}
+    \frac{\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)}
+    {   \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}=
+    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})} \left(1-e^{-\alpha}\right)^{mult(\alpha)-mult_{\mathfrak{a}}(\alpha)}=\\
+    = -\sum_{\gamma\in P_{\mathfrak{a}}} s(\gamma)e^{-\gamma}
+\end{multline}
+
+For the coefficient function $s\left( \gamma \right) $ define $\Phi _{\frak{a%
+}\subset \frak{g}}\subset P_{\frak{a}}$ as its carrier: 
+\begin{equation}
+\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
+\gamma \right) \neq 0\right\} ;  \label{phi-d}
+\end{equation}
+\begin{equation}
+\prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})}\left(
+1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
+}}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset 
+\frak{g}}}s\left( \gamma \right) e^{-\gamma }.  \label{fan-d}
+\end{equation}
+
+So we get the equation
+\begin{multline}
+  \label{eq:16}
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+  = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
+  k_{\lambda }^{\left( \mu \right) }e^{\lambda } \\
+  =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma }
+\end{multline}
+From the equality of the coefficients of the equal formal exponents we get
+\begin{equation}
+  \label{eq:17}
+   \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\quad \xi\in P_{\mathfrak{a}}
+\end{equation}
+
+To get the recurrent relation for the anomalous branching coefficients we should use the following procedure, introduced in the paper \cite{ilyin812pbc}.
+
+In $\left( \Phi _{\frak{a}\subset \frak{g}}\right) _{n=0}$ let $\gamma
+_{0} $ be the lowest vector with respect to the natural ordering in $%
+\overset{\circ }{\Delta _{\frak{a}}}$ . Decomposing the defining relation 
+\begin{equation}
+  \label{eq:18}
+  \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})}\left(
+    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
+      }}\mathrm{\left( \alpha \right) }}=-s\left( \gamma _{0}\right) e^{-\gamma
+    _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \gamma
+    _{0}}s\left( \gamma \right) e^{-\gamma },  
+\end{equation}
+in (\ref{eq:17}) we obtain
+
+\begin{equation}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+\sum_{\gamma \in
+\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
++\gamma }^{\left( \mu \right) }\right)   \label{recurrent relation}
+\end{equation}
+where the set 
+\begin{equation}
+\Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} .
+\label{fan-defined}
+\end{equation}
 

### 2009-10-23 AffineLieAlgebras/InformalNotes/article.tex
More work

@@
 
+\begin{comment}
+  Fix this discussion of natural ordering
+\end{comment}
+
 In $\left( \Phi _{\frak{a}\subset \frak{g}}\right) _{n=0}$ let $\gamma
@@
 \end{equation}
+\begin{comment}
+  Say something about the end of the proof
+\end{comment}
 
@@
 \label{sec:algorithm}
+\begin{enumerate}
+\item Construct the set of anomalous points of the algebra $\mathfrak{g}$
+\item Calculate the dimensions of the corresponding modules $L_{\mathfrak{a}_{\bot}}$.
+\item Calculate anomalous branching coefficients in the main Weyl chamber of the subalgebra $\mathfrak{a}$
+\item \dots
+\item PROFIT !!!
+\end{enumerate}
 
@@
 
-B2->A1 etc.
+\subsubsection{Regular embedding of $A_1$ into $B_2$}
+\label{sec:regul-embedd-a_1}
+
+\subsubsection{Something high-dimensional}
+\label{sec:someth-high-dimens}
 
@@
 
-Branching of affine to affine and affine to classical.
+\subsection{Embedding of finite-dimensional algebra into affine algebra}
+\label{sec:embedd-finite-dimens}
+
+\subsection{Embedding of the affine algebra into affine algebra}
+\label{sec:embedd-affine-algebr}
+
 \subsection{Physical applications}

### 2009-10-23 AffineLieAlgebras/InformalNotes/article.tex
Added chunk on physical applications. It should be completely rewritten.

@@
 \begin{abstract}
-
+  We present the recurrent relation for the branching coefficients of affine Lie algebras. Then we describe the algorithm for the decomposition of  integrable highest weight modules
+of a simple Lie algebra with respect to its reductive subalgebra which is based upon this recurrent relation and present some examples.
+Also we discuss the appearance of branching coefficients in the physical models.
 \end{abstract}
@@
 \label{sec:introduction}
+
+\begin{comment}
+  The problem of computation of the branching coefficients is very important. Why else would we study it??
+  It has major applications in physics of which nobody is aware. Blah-blah-blah.
+\end{comment}
+
+The paper is organised as follows.
+In the next subsection of the introduction we fix the notation used throughout the paper.
+Then in section \ref{sec:recurr-form-branch} we derive the central recurrent formula for the anomalous branching coefficients and describe the algorithm for the decomposition integrable highest weight modules of algebra $\mathfrak{g}$ to the modules of reductive subalgebra $\mathfrak{a}$ \ref{sec:algorithm}.
+In the next section \ref{sec:examples} we present several examples and discuss some applications in the physical models \ref{sec:phys-appl}.
+We conclude the paper with the review of results and the discussion of possible future developments \ref{sec:conclusion}.
 
@@
 
+Character reduction
+\begin{equation}
+  \label{eq:19}
+  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
+    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
+  \Longrightarrow\quad
+  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
+\end{equation}
+Numbers $b^{(\mu)}_{\nu}$ are called branching coefficients.
+
+The anomalous branching coefficients $k_{\lambda}$ are defined as follows
+\begin{equation}
+  \label{eq:21}
+  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
+        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
+  }^{\left( \mu \right) }e^{\lambda } 
+\end{equation}
+
+It is important to mention that
+\begin{equation}
+  \label{eq:20}
+  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in C_{\mathfrak{a}}
+\end{equation}
+
 \section{Recurrent formula for branching coefficients}
@@
 
+Here we present the final recurrent relation for the anomalous branching coefficients \eqref{eq:21}. 
 \begin{equation}
-  \label{eq:1}
-  k_{\nu}=\sum_{w\in W_a} k_{\rho_a-w(\nu+\rho_a)} + \sum_{w\in W}dim_{w(\mu+\rho)-\rho} \delta_{\nu,w(\mu+\rho)-\rho}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+\sum_{\gamma \in
+\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
++\gamma }^{\left( \mu \right) }\right)
 \end{equation}
+The proof of the formula and definitions of $\mathfrak{a}_{\bot},\; W_{\bot},\; s(\gamma),\; \Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ are in the following subsection.
 
-\subsection{Proof}
+In the next section we describe the algorithm for the computation of branching coefficients based upon this formula and then present some example and discuss physical meaning.
+
+\subsection{Proof of the recurrent formula}
 \label{sec:proof}
-Proof of the formula.
 
@@
 
-\begin{comment}
-  Fix this discussion of natural ordering
-\end{comment}
-
-In $\left( \Phi _{\frak{a}\subset \frak{g}}\right) _{n=0}$ let $\gamma
+Let $\gamma
 _{0} $ be the lowest vector with respect to the natural ordering in $%
-\overset{\circ }{\Delta _{\frak{a}}}$ . Decomposing the defining relation 
+\overset{\circ }{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$. Decomposing the defining relation 
 \begin{equation}
@@
 \end{equation}
-\begin{comment}
-  Say something about the end of the proof
-\end{comment}
+
+So we've obtained recurrent relation for the anomalous branching coefficients.
+In the next section we describe the algorithm for the computation of branching coefficients using the relation \eqref{recurrent relation}.
 
@@
 
-\subsection{Physical applications}
+\section{Physical applications}
 \label{sec:phys-appl}
+
+\subsection{Wess-Zumino-Novikov-Witten models}
+\label{sec:WZNW}
+
+Let's start with non-linear $\sigma$-model.
+\begin{equation}
+  \label{eq:48}
+  S_0=\frac{1}{4a^2}\int d^2x\; Tr' (\partial^{\mu}g^{-1}\partial_{\mu}g)
+\end{equation}
+Here $a^2>0$ is a positive parameter, $g(x)\in G$ - field on Lie group $G$, which we will assume to be semi-simple and by $Tr'$ we have denoted representation independent trace of Lie algebra $\mathfrak{g} $
+\begin{equation}
+  \label{eq:70}
+  Tr'=\frac{1}{x_{rep}}Tr
+\end{equation}
+$x_{rep}$ is the Dynkin index of the representation.
+
+In this model the conformal invariance is lost at the quantum level, as it can be seen along the lines of previous sections.
+!!! Show it by example !!!
+
+Also we can see that holomorphic and antiholomorphic currents aren't conserved individually. The equations of motion are
+\begin{equation}
+  \label{eq:71}
+  \partial^{\mu}(g^{-1}\partial_{\mu}g)=0
+\end{equation}
+The currents are
+\begin{equation}
+  \label{eq:currents}
+  J_{\mu}=g^{-1}\partial_{\mu}g
+\end{equation}
+or in the complex coordinates
+\begin{equation}
+  \label{eq:74}
+  \begin{matrix}
+    & \tilde{J}_z=g^{-1}\partial_z g, & \tilde{J}_{\bar{z}}=g^{-1}\partial_{\bar{z}}g\\
+    & \partial_z \tilde{J}_{\bar{z}}+\partial_{\bar{z}}\tilde{J}_z=0 & \\
+  \end{matrix}
+\end{equation}
+The terms of the equation of motion can not be null separately because $\partial_{\mu}(\epsilon^{\mu\nu}J_{\nu})\neq 0$.
+
+So we add WZ-term to the action and redefine the currents in more appropriate way
+\begin{equation}
+  \label{eq:72}
+  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
+\end{equation}
+
+Wess-Zumino term has the following form
+\begin{equation}
+  \label{eq:73}
+\Gamma=  - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr'\left(
+    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+
+This term is defined on the three-dimensional manifold $B$ whose boundary is original two-dimensional space.
+By $\tilde{g}$ we have denoted the extension of the field $g$ to $B$.
+This extension isn't unique.
+In a compactified three-dimensional space a compact two-dimensional manifold delimits two three-dimensional manifolds.
+The difference between this two choices $\Delta\Gamma$ is given by the right hand side of (\ref{eq:73}) with the integration range extended over the whole compact three-dimensional space.
+Since the latter is topologically equivalent to the three-sphere we have
+\begin{equation}
+  \label{eq:75}
+\Delta\Gamma=  - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left(
+    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+$\Delta\Gamma$ is defined modulo $2\pi i$, so the Euclidean functional integral with weight $exp(-\Gamma)$ is well-defined. Clearly, any coupling constant multiplying this term must be an integer.
+
+We then consider the action
+\begin{equation}
+  \label{eq:76}
+  S=S_0+k\Gamma
+\end{equation}
+where $k$ is an integer. 
+The equation of motion for the full action (\ref{eq:76}) is
+\begin{equation}
+  \label{eq:77}
+  \partial^{\mu}(g^{-1}\partial_{\mu}g)+\frac{a^2 ik}{4\pi}\epsilon_{\mu\nu}\partial^{\mu}(g^{-1}\partial^{\nu}g)=0
+\end{equation}
+It can be rewritten using complex coordinates as
+\begin{equation}
+  \label{eq:78}
+  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
+\end{equation}
+We see that when $a^2=\frac{4\pi}{k}$ we have the desired conservation law
+\begin{equation}
+  \label{eq:79}
+  \partial_z(g^{-1}\partial{\bar z}g)=0
+\end{equation}
+For currents
+\begin{equation}
+  \label{eq:4}
+  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
+\end{equation}
+
+The solution of classical equation is
+\begin{equation}
+  \label{eq:80}
+  g(z,\bar z)=f(z)\bar f(\bar z)
+\end{equation}
+for arbitrary functions $f(z)$ and $\bar f (\bar z)$.
+
+The separate conservation of the currents $J_z,\; J_{\bar z}$ implies the invariance of the action under the transformations
+\begin{equation}
+  \label{eq:81}
+   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)
+\end{equation}
+where $\Omega,\;\bar \Omega \in G$. So we have local $G(z)\times G(\bar z)$ invariance.
+
+In order to move analysis to quantum level we rescale the currents
+\begin{equation}
+  \label{eq:82}
+  J(z)\equiv -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
+\end{equation}
+So the variation of the action under infinitesimal transformation $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ is
+\begin{equation}
+  \label{eq:83}
+  \delta_{\omega,\bar\omega}S=\frac{i}{4\pi}\oint dz Tr' (\omega(z)J(z))-\frac{i}{4\pi}\oint d\bar z Tr'(\bar\omega(\bar z)\bar J(\bar z))
+\end{equation}
+Expanding the currents as
+\begin{equation}
+  \label{eq:85}
+  \begin{aligned}
+    J=\sum J^a t^a,\bar J=\sum \bar J^a t^a \\
+    \omega=\sum \omega^a t^a\\
+  \end{aligned}
+\end{equation}
+we get
+\begin{equation}
+  \label{eq:86}
+  \delta_{\omega,\bar \omega}S=-\frac{1}{2\pi i}\oint dz \sum\omega^a J^a+\frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \bar J^a
+\end{equation}
+We can also obtain Ward identities $\delta\left< X\right>=\left<(\delta S)X\right>$
+\begin{equation}
+  \label{eq:87}
+  \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
+  \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
+\end{equation}
+Then for the currents we have
+\begin{equation}
+  \label{eq:88}
+  \delta_{\omega}J=[\omega,J]-k\partial_z\omega,\quad \delta_{\omega}J^a=\sum i f_{abc}\omega^b J^c-k\partial_z\omega^a
+\end{equation}
+The operator product expansion for currents has the form
+\begin{equation}
+  \label{eq:89}
+  J^a(z) J^b(w) \sim \frac{k\delta_{ab}}{(z-w)^2}+\sum i f_{abc}\frac{J^c(w)}{(z-w)}
+\end{equation}
+Expanding currents into series we get
+\begin{equation}
+  \label{eq:90}
+  \begin{aligned}
+    J^a(z)=\sum_{n\in \mathbb Z}z^{n-1}J^a_n\\    
+    \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}  
+  \end{aligned}
+\end{equation}
+We see that components of currents realize affine Lie algebra $\hat g$.
+
+Energy-momentum tensor is introduced with Sugawara construction as the sum of normal-ordered products of current components
+\begin{equation}
+  \label{eq:6}
+  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
+\end{equation}
+Here $h^v$ is the dual Coxeter number.
+
+Energy-momentum tensor can be expanded into modes $L_n$
+\begin{equation}
+  \label{eq:91}
+  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
+\end{equation}
+The commutation relations for the modes $L_n$ are
+\begin{equation}
+  \label{eq:92}
+  \begin{aligned}
+    \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
+    \left[L_n,J^a_m\right]=-mJ^a_{n+m}
+  \end{aligned}
+\end{equation}
+
+So the Sugawara construction is the way to embed Virasoro algebra into the universal enveloping of affine Lie algebra.
+
+Complete chiral algebra of WZW-model is equal to semidirect product $Vir\ltimes \hat g$
+
+The primary fields are the fields that transforms covariantly with respect to $G(z)\times G(\bar z)$, such as $g(z,\bar z)$. In terms of operator product expansion this property is reformulated as
+\begin{equation}
+  \label{eq:84}
+  \begin{aligned}
+    J^a(z)g(w,\bar w)\sim \frac{-t^a g(w,\bar w)}{(z-w)}\\
+    \bar J^a(z)g(w,\bar w)\sim \frac{ g(w,\bar w)t^a}{(z-w)}
+  \end{aligned}
+\end{equation}
+Any field $\phi_{\lambda,\mu}$ transforming covariantly with respect to some representation specified by $\lambda$ in holomorphic and $\mu$ in antiholomorphic sector, will be a WZW primary field.
+
+In terms of modes this property can be written as
+\begin{equation}
+  \label{eq:93}
+  \begin{aligned}
+    & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
+    & (J^a_n\phi_{\lambda})=0\quad \mbox{for}\; n>0\\
+  \end{aligned}
+\end{equation}
+We can associate the state $\left|\phi_{\lambda}\right>$ to the field $\phi_{\lambda}$
+  \begin{equation}
+    \label{eq:94}
+    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
+  \end{equation}
+Then the conditions (\ref{eq:93}) for WZW primary field are
+\begin{equation}
+  \label{eq:95}
+  \begin{aligned}
+    & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
+    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
+  \end{aligned}
+\end{equation}
+It is easy to see that the action of the Virasoro generators is
+\begin{equation}
+  \label{eq:96}
+  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
+\end{equation}
+Here we used the explicit form of the quadratic Casimir operator eigenvalue.
+
+Primary fields live in integrable finite-dimensional representations since infinite-dimensional and non-integrable fields are decoupled from the correlation functions.
+
+All secondary states are of the form
+\begin{equation}
+  \label{eq:97}
+  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
+\end{equation}
+For the correlation functions of primary fields we can obtain Knizhnik-Zamolodchikov equations which follow from global $G\times G$ invariance
+\begin{equation}
+  \label{eq:98}
+  \left(\partial_{z_i}+\frac{1}{k+h^v}\sum_{i\neq j}\frac{\sum_a t^a_i\otimes t^a_j}{z_i-z_k}\right)
+  \left<\phi_1(z_1)\dots \phi_n(z_n)\right>=0
+\end{equation}
+So the theory is completely determined by the representations of affine Lie algebra $\hat{\mathfrak{g}} $.
+
+\subsubsection{Modular invariants}
+\label{sec:modular-invariants}
+
+In previous section we studied holomorphic and antiholomorphic sectors of the theory separately.
+But in physically sensible theories this sectors should be entangled.
+It is required for the theory to be well-defined on the higher genus Riemann surfaces (see \cite{gaberdiel2000icf} and references therein) and also if we want our theory to describe critical behavior \cite{difrancesco1997cft}.
+In the critical point theory has conformal invariance, holomorphic and antiholomorphic sectors are decoupled, but in the vicinity of critical point there exists some large scale so the sectors should interact.
+
+!!! Expand this argumentation !!!
+
+The necessary constraint for the theory to be well-defined on higher Riemann surfaces, which is also believed to be sufficient, is that the vacuum correlator on the torus is independent of its parametrisation \cite{gaberdiel2000icf}.
+Conformal theory on the higher genus Riemann surfaces is important for the string theory since this theory describes string interaction.
+
+Two-dimensional torus is described as quotient space of $\mathbb{R}^2\approx \mathbb{C}$ by the relations $z\sim z+w_1$ and $z\sim z+w_2$, where $w_1$ and $w_2$ are not parallel.
+
+The complex structure of the torus is conformally equivalent to a torus for which the relations are $z\sim z+1$ and $z\sim z+\tau$ where $\tau$ is in the upper half plane of $\mathbb{C}$.
+It is also easy to see that $\tau$, $T(\tau)=\tau+1$ and $S(\tau)=-\frac{1}{\tau}$ describe conformally equivalent tori.
+Two maps $T$ and $S$ generate the group $SL(2,\mathbb{Z})/\mathbb{Z}_2$ that consists of matrices of the form
+\begin{equation}
+  \label{eq:99}
+  A=
+  \begin{pmatrix}
+    a & b\\
+    c & d 
+  \end{pmatrix}
+  \quad\mbox{where}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+\end{equation}
+and matrices $A$ and $-A$ have the same action on $\tau$
+\begin{equation}
+  \label{eq:100}
+  \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+\end{equation}
+The parameter $\tau$ is called the modular parameter and the group  $SL(2,\mathbb{Z})/\mathbb{Z}_2$ is called the modular group.
+
+Given a conformal field theory that is defined on the Riemann sphere, the vacuum
+correlator on the torus can be determined as follows. First, we cut the torus along one
+of its non-trivial cycles; the resulting surface is a cylinder (or an annulus) whose shape
+depends on one complex parameter $q$. Since the annulus is a subset of the sphere, the
+conformal field theory on the annulus is determined in terms of the theory on the sphere.
+In particular, the states that can propagate in the annulus are precisely the states of
+the theory as defined on the sphere.
+In order to reobtain the torus from the annulus, we have to glue the two ends of
+the annulus together; in terms of conformal field theory this means that we have to sum
+over a complete set of states. The vacuum correlator on the torus is therefore described
+by a trace over the whole space of states, the partition function of the theory,
+\begin{equation}
+  \label{eq:101}
+  \sum_{(i,j)}Tr_{\mathcal{H}_{(i,j)}}(\mathcal{O}(q,\bar q)),
+\end{equation}
+where $\mathcal{O}(q,\bar q)$ is the operator that describes the propagation of the states along the annulus,
+\begin{equation}
+  \label{eq:102}
+  \mathcal{O}(q,\bar q)=q^{L_0-\frac{c}{24}}\bar q^{\bar L_0-\frac{\bar c}{24}}
+\end{equation}
+The propagator depends on the actual shape of the annulus that is described in terms
+of the complex parameter $q$. For a given torus that is described by $\tau$ , there is a natural
+choice for how to cut the torus into an annulus, and the complex parameter $q$ that is
+associated to this annulus is $q=e^{2\pi i \tau}$. Since the tori that are described by $\tau$ and $A\tau$
+(where $A \in SL(2, \mathbb{Z})$) are equivalent, the vacuum correlator is only well-defined provided
+that (\ref{eq:101}) is invariant under this transformation. This provides strong constraints on
+the spectrum of the theory.
+
+Each of the spaces $\mathcal{H}_{(i,j)}$ is a tensor product of an irreducible representation $\mathcal{H}_j$ of chiral algebra and an irreducible representation $\bar{\mathcal{H}}_{\bar{j}}$ of antichiral algebra.
+Then the vacuum correlator on the torus (\ref{eq:101}) takes the form
+\begin{equation}
+  \label{eq:103}
+  \sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
+\end{equation}
+where $\chi_j$ is the character of the representation $\mathcal{H}_j$,
+\begin{equation}
+  \label{eq:104}
+  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{where}\; q=e^{2\pi i \tau}
+\end{equation}
+Characters transform into one another under modular transformations,
+\begin{equation}
+  \label{eq:107}
+  \chi_j(-\frac{1}{\tau})=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{and}\quad \chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
+\end{equation}
+where $S$ and $T$ are constant matrices. This fact is proved for a certain class of conformal field theories \cite{gaberdiel2000icf}.
+
+For WZW-models the representations are determined by highest weights $\hat \lambda, \hat \xi$. Then we can write
+\begin{equation}
+  \label{eq:105}
+  \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi} L_{\hat \lambda}\otimes L_{\hat \xi}
+\end{equation}
+The partition function is rewritten as
+\begin{equation}
+  \label{eq:106}
+  Z(\tau)=\sum_{\hat \lambda,\hat \xi\in P^{(k)}_{+}} \chi_{\hat \lambda}(\tau)M_{\hat \lambda\hat\xi}\bar \chi_{\hat \xi}(\bar \tau)
+\end{equation}
+The element of the mass matrix $M_{\hat \lambda\hat\xi}$ can be thought of as the multiplicity of primary field with weights $\hat\lambda,\hat \xi$.
+It has following properties:$M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, it is modular invariant
+\begin{equation}
+  \label{eq:108}
+  \begin{aligned}
+    T^{\dagger}MT=S^{\dagger}MS=M,\\
+    [M,S]=[M,T]=0,
+  \end{aligned}
+\end{equation}
+and $M_{00}=1$ for the uniqueness of vacuum.
+
+The simplest case of diagonal matrix $M$ corresponds to equal holomorphic and antiholomorphic conformal dimensions.
+There are several ways to construct non-diagonal modular invariants from diagonal \cite{difrancesco1997cft}:
+\begin{itemize}
+\item Method of outer automorphisms
+\item Conformal embedding into bigger theory
+\item Galois-transpositions
+\end{itemize}
+Here we will discuss conformal embeddings.
+
+\subsubsection{Conformal embeddings}
+\label{sec:conformal-embeddings}
+Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory. !!! Provide an explanation !!!
+
+The states for the theory that corresponds to the algebra $\mathfrak{g}$
+\begin{equation}
+  \label{eq:109}
+  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq\dots>0
+\end{equation}
+For sub-algebra $\mathfrak{p}\subset\mathfrak{g}$
+\begin{equation}
+  \label{eq:110}
+  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\mathcal{P}\lambda\right>
+\end{equation}
+Here $\tilde{J}^{a'_j}_{-n_j}$ are the generators of $\mathfrak{p}$ and $\mathcal{P}$ is the projection of $\mathfrak{g}$ to $\mathfrak{p}$.
+$\mathfrak{g}$-invariance of vacuum entails its $\mathfrak{p}$-invariance, but it is not the case for energy-momentum tensor.
+So energy-momentum tensor of bigger theory should consist only of generators of $\hat{\mathfrak{p}}$.
+Then $T_{\hat{\mathfrak{g}}}=T_{\hat{\mathfrak{p}}}\Rightarrow c(\hat{\mathfrak{g}})=c(\hat{\mathfrak{p}})$.
+This leads to equation
+\begin{equation}
+  \label{eq:111}
+  \frac{k\;dim\mathfrak{g}}{k+g}=\frac{x_e k\; dim\mathfrak{p}}{x_ek+p}
+\end{equation}
+Here $x_e$ is the embedding index and $g$, $p$ are dual Coxeter numbers of corresponding algebras. !!! Prove and expand !!!
+
+It can be shown that solutions of equation (\ref{eq:111}) exist only for level 1 $k=1$.
+
+There exist only finite number of such embeddings.
+
+{\bf Examples}
+\begin{itemize}
+\item $su(2)\subset su(3),\; x_e=4$
+\item $\hat{su}(2)_{10}\subset\hat{sp}(4)_1$
+\item $\hat{su}(2)_{28}\subset(\hat{G_2})_1$
+\item $\hat{su}(2)_{16}\oplus\hat{su}(3)\subset (\hat{E_8})_1$
+\end{itemize}
+
+Branching $\hat{\lambda}\to \bigoplus_{\hat{\mu}}b_{\hat{\lambda}\hat{\mu}}\hat{\mu}$
+\begin{equation}
+  \label{eq:112}
+  h_{\hat{\lambda}}+n=h_{\hat{\mu}},\quad \frac{(\lambda,\lambda+2\rho)}{2(1+g)}+n=\frac{(\mu,\mu+2\rho)}{2(x_e+p)}
+\end{equation}
+The simple way is to calculate the dimensions of all the representations of simple finite-dimensional Lie algebras $\mathfrak{g},\mathfrak{p}$ and find all the triples $(\lambda,\mu,n)$, satisfying (\ref{eq:112}).
+Then investigate the representation $L_{\hat{\lambda}}$ of level $n$ as the sum of irreducible representations of $\mathfrak{g}$ and write out all the branching rules of these representations in representations of subalgebra $\mathfrak{p}$.
+The number of times the representation with highest weight $\mu$ appears in this listing is the required branching coefficient $b_{\hat{\lambda},\hat{\mu}}$.
+
+  Then non-diagonal modular invariants are obtained by substitution of character relations. For example, having calculated branching coefficients for $\hat{su}(2)_{28}\subset (\hat{G_2})_1$
+  \begin{equation}
+    \label{eq:113}
+    \begin{aligned}
+      & [1,0,0]\to [28,0]\oplus [18,10]\oplus [10,18]\oplus [0,28]\\
+      & [0,0,1]\to [22,6]\oplus [16,12]\oplus [12,16]\oplus [6,22]\\
+    \end{aligned}
+  \end{equation}
+we get following modular-invariant partition function
+\begin{equation}
+  \label{eq:114}
+  Z=\left|\chi_{[28,0]}+\chi_{[18,10]}+\chi_{[10,18]}+\chi_{[0,28]}\right|^2+\left|\chi_{[22,6]}+\chi_{[16,12]}+\chi_{[12,16]}+\chi_{[6,22]}\right|^2
+\end{equation}
 
@@
 
-\bibliography{CFTNotes}{}
+\bibliography{article}{}
 \bibliographystyle{utphys}

### 2009-10-24 AffineLieAlgebras/InformalNotes/article.tex
Example of A_1\subset B_2 is completed.

@@
 
+Consider the regular embedding of $A_1$ into $B_2$.
+Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the thick vectors at the figure \ref{fig:B2_A1}.
+We denote the corresponding Weyl reflections by $\omega_1, \omega_2$.
+Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+\alpha_2$.
+
+Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$.
+\begin{figure}[ph]
+  \noindent\centering{
+    \includegraphics[width=80mm]{B2_A1.pdf}
+  }
+  \caption{Regular embedding of $A_1$ into $B_2$}
+  \label{fig:B2_A1}
+\end{figure}
+On the figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
+Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W/W_{\bot}$:
+\begin{figure}[ph]
+  \noindent\centering{
+    \includegraphics[width=80mm]{B2_A1_2.pdf}
+  }
+  \caption{Anomalous points and the corresponding modules}
+  \label{fig:B2_A1_2}
+\end{figure}
+We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
+\begin{equation}
+  \label{eq:1}
+  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
+\end{equation}
+For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
+\begin{equation}
+  \label{eq:22}
+  (0,1),\; (1,2),\; (2,-1)
+\end{equation}
+Here the second component denotes the value of $s(\gamma)$.
+
+Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent relation}) gives us
+\begin{equation}
+  \label{eq:23}
+  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0}_1 - 3\cdot \delta_{0,0} = 1
+\end{equation}
+So we've computed the branching coefficients.
 \subsubsection{Something high-dimensional}

### 2009-10-26 AffineLieAlgebras/InformalNotes/article.tex
Minor fix
B4 example added to the article

@@
       }}\mathrm{\left( \alpha \right) }}=-s\left( \gamma _{0}\right) e^{-\gamma
-    _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \gamma
-    _{0}}s\left( \gamma \right) e^{-\gamma },  
+    _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \left\{\gamma_{0}\right\}}s\left( \gamma \right) e^{-\gamma },  
 \end{equation}
@@
 k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
 \sum_{\gamma \in
@@
 \item Calculate the dimensions of the corresponding modules $L_{\mathfrak{a}_{\bot}}$.
-\item Calculate anomalous branching coefficients in the main Weyl chamber of the subalgebra $\mathfrak{a}$
-\item \dots
-\item PROFIT !!!
+\item Calculate anomalous branching coefficients in the main Weyl
+  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent relation}).
 \end{enumerate}
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{B2_A1.pdf}
+    \includegraphics[width=90mm]{B2_A1.pdf}
   }
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{B2_A1_2.pdf}
+    \includegraphics[width=90mm]{B2_A1_2.pdf}
   }
-  \caption{Anomalous points and the corresponding modules}
+  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
   \label{fig:B2_A1_2}
@@
 So we've computed the branching coefficients.
-\subsubsection{Something high-dimensional}
+\subsubsection{Embedding of $B_2$ into $B_4$}
 \label{sec:someth-high-dimens}
+Consider the the regular embedding of the subalgebra $B_2$ into the algebra $B_4$.
+We calculate the branching coefficients for the fundamental representation of $B_4$.
+The corresponding Dynkin diagrams are in the figure.
+\begin{figure}[ph]
+  \centering
+  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
+  \caption{Dynkin diagrams}
+  \label{fig:dynkin}
+\end{figure}
+
+In the orthogonal basis $e_1,\dots,e_4$ simple roots of $B_4$ are
+\begin{equation}
+  \label{eq:1}
+  (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4)
+\end{equation}
+Positive roots are
+\begin{multline}
+  \label{eq:2}
+  (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\\
+    e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2)
+\end{multline}
+Simple roots of the embedded subalgebra $\mathfrak{a}=B_2$ are
+\begin{equation}
+  \label{eq:3}
+  (e_3-e_4,e_4)
+\end{equation}
+
+The set $\Delta_{\bot}$ is equal to
+\begin{equation}
+  \label{eq:4}
+  \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
+\end{equation}
+
+We see that this is the set of positive roots of the algebra $\mathfrak{a}_{\bot}=B_2$.
+
+To find the branching coefficients we need to compute the anomalous points of $B_4$, select point lying in the main Weyl chamber of $\mathfrak{a}_{\bot}$ and compute the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.
+
+We consider the $B_4$-module with the highest weight $\mu=(0,1,0,2)=2
+e_1 + 2 e_2 + e_3 + e_4$.
+
+The set of the anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W$
+consists of 384 points. We don't show it here.
+
+We need to select those points $\omega(\mu+\rho)$  which are projected into the main chamber of the embedded algebra $\mathfrak{a}_{\bot}$.
+It means that scalar product of these points with all the roots from $\Delta_{\bot}$ is non-negative.
+
+To compute dimensions of the corresponding
+$\mathfrak{a}_{\bot}$-modules we need to project each selected point
+onto the root space $\Delta_{\bot}$ and substract
+$\rho_{\mathfrak{a}_{\bot}}$, then use Weyl dimension formula.
+
+We show the result of this procedure on the figure \ref{fig:B4B2anom}.
+\begin{figure}[ph]
+    \includegraphics[width=170mm]{B4_B2_anom_points.pdf}
+  \caption{Anomalous points with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
+  \label{fig:B4B2anom}
+\end{figure}
+
+Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
+
+Using the definition (\ref{fan-defined}) we get the following set of
+the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$
+\begin{figure}[ph]
+  \includegraphics[width=150mm]{B4_B2_fan.pdf}
+  \caption{Fan for $B_2\subset B_4$}
+  \label{fig:B4B2Fan}
+\end{figure}
+We use the recurrent relation (\ref{recurrent relation}) and get
+following branching coefficients:
+\begin{equation}
+  \label{eq:24}
+  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
+  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
+  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
+\end{equation}
+The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
+is equal to 2772. It is easy to see, that right-hand side of the
+equation (\ref{eq:24}) gives the same result.
 

### 2009-10-26 AffineLieAlgebras/InformalNotes/article.tex
Universal literate program for classical branching

@@
 
-\subsection{Wess-Zumino-Novikov-Witten models}
-\label{sec:WZNW}
+Branching coefficients for the embedding of affine Lie subalgebra into
+affine Lie algebra can be used to construct modular invariant
+partition functions of Wess-Zumino-Novikov-Witten models.
 
-Let's start with non-linear $\sigma$-model.
-\begin{equation}
-  \label{eq:48}
-  S_0=\frac{1}{4a^2}\int d^2x\; Tr' (\partial^{\mu}g^{-1}\partial_{\mu}g)
-\end{equation}
-Here $a^2>0$ is a positive parameter, $g(x)\in G$ - field on Lie group $G$, which we will assume to be semi-simple and by $Tr'$ we have denoted representation independent trace of Lie algebra $\mathfrak{g} $
-\begin{equation}
-  \label{eq:70}
-  Tr'=\frac{1}{x_{rep}}Tr
-\end{equation}
-$x_{rep}$ is the Dynkin index of the representation.
-
-In this model the conformal invariance is lost at the quantum level, as it can be seen along the lines of previous sections.
-!!! Show it by example !!!
-
-Also we can see that holomorphic and antiholomorphic currents aren't conserved individually. The equations of motion are
-\begin{equation}
-  \label{eq:71}
-  \partial^{\mu}(g^{-1}\partial_{\mu}g)=0
-\end{equation}
-The currents are
-\begin{equation}
-  \label{eq:currents}
-  J_{\mu}=g^{-1}\partial_{\mu}g
-\end{equation}
-or in the complex coordinates
-\begin{equation}
-  \label{eq:74}
-  \begin{matrix}
-    & \tilde{J}_z=g^{-1}\partial_z g, & \tilde{J}_{\bar{z}}=g^{-1}\partial_{\bar{z}}g\\
-    & \partial_z \tilde{J}_{\bar{z}}+\partial_{\bar{z}}\tilde{J}_z=0 & \\
-  \end{matrix}
-\end{equation}
-The terms of the equation of motion can not be null separately because $\partial_{\mu}(\epsilon^{\mu\nu}J_{\nu})\neq 0$.
-
-So we add WZ-term to the action and redefine the currents in more appropriate way
-\begin{equation}
-  \label{eq:72}
-  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
-\end{equation}
-
-Wess-Zumino term has the following form
-\begin{equation}
-  \label{eq:73}
-\Gamma=  - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr'\left(
-    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
-\end{equation}
-
-This term is defined on the three-dimensional manifold $B$ whose boundary is original two-dimensional space.
-By $\tilde{g}$ we have denoted the extension of the field $g$ to $B$.
-This extension isn't unique.
-In a compactified three-dimensional space a compact two-dimensional manifold delimits two three-dimensional manifolds.
-The difference between this two choices $\Delta\Gamma$ is given by the right hand side of (\ref{eq:73}) with the integration range extended over the whole compact three-dimensional space.
-Since the latter is topologically equivalent to the three-sphere we have
-\begin{equation}
-  \label{eq:75}
-\Delta\Gamma=  - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left(
-    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
-\end{equation}
-$\Delta\Gamma$ is defined modulo $2\pi i$, so the Euclidean functional integral with weight $exp(-\Gamma)$ is well-defined. Clearly, any coupling constant multiplying this term must be an integer.
-
-We then consider the action
-\begin{equation}
-  \label{eq:76}
-  S=S_0+k\Gamma
-\end{equation}
-where $k$ is an integer. 
-The equation of motion for the full action (\ref{eq:76}) is
-\begin{equation}
-  \label{eq:77}
-  \partial^{\mu}(g^{-1}\partial_{\mu}g)+\frac{a^2 ik}{4\pi}\epsilon_{\mu\nu}\partial^{\mu}(g^{-1}\partial^{\nu}g)=0
-\end{equation}
-It can be rewritten using complex coordinates as
-\begin{equation}
-  \label{eq:78}
-  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
-\end{equation}
-We see that when $a^2=\frac{4\pi}{k}$ we have the desired conservation law
-\begin{equation}
-  \label{eq:79}
-  \partial_z(g^{-1}\partial{\bar z}g)=0
-\end{equation}
-For currents
-\begin{equation}
-  \label{eq:4}
-  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
-\end{equation}
-
-The solution of classical equation is
-\begin{equation}
-  \label{eq:80}
-  g(z,\bar z)=f(z)\bar f(\bar z)
-\end{equation}
-for arbitrary functions $f(z)$ and $\bar f (\bar z)$.
-
-The separate conservation of the currents $J_z,\; J_{\bar z}$ implies the invariance of the action under the transformations
-\begin{equation}
-  \label{eq:81}
-   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)
-\end{equation}
-where $\Omega,\;\bar \Omega \in G$. So we have local $G(z)\times G(\bar z)$ invariance.
-
-In order to move analysis to quantum level we rescale the currents
-\begin{equation}
-  \label{eq:82}
-  J(z)\equiv -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
-\end{equation}
-So the variation of the action under infinitesimal transformation $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ is
-\begin{equation}
-  \label{eq:83}
-  \delta_{\omega,\bar\omega}S=\frac{i}{4\pi}\oint dz Tr' (\omega(z)J(z))-\frac{i}{4\pi}\oint d\bar z Tr'(\bar\omega(\bar z)\bar J(\bar z))
-\end{equation}
-Expanding the currents as
-\begin{equation}
-  \label{eq:85}
-  \begin{aligned}
-    J=\sum J^a t^a,\bar J=\sum \bar J^a t^a \\
-    \omega=\sum \omega^a t^a\\
-  \end{aligned}
-\end{equation}
-we get
-\begin{equation}
-  \label{eq:86}
-  \delta_{\omega,\bar \omega}S=-\frac{1}{2\pi i}\oint dz \sum\omega^a J^a+\frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \bar J^a
-\end{equation}
-We can also obtain Ward identities $\delta\left< X\right>=\left<(\delta S)X\right>$
-\begin{equation}
-  \label{eq:87}
-  \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
-  \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
-\end{equation}
-Then for the currents we have
-\begin{equation}
-  \label{eq:88}
-  \delta_{\omega}J=[\omega,J]-k\partial_z\omega,\quad \delta_{\omega}J^a=\sum i f_{abc}\omega^b J^c-k\partial_z\omega^a
-\end{equation}
-The operator product expansion for currents has the form
-\begin{equation}
-  \label{eq:89}
-  J^a(z) J^b(w) \sim \frac{k\delta_{ab}}{(z-w)^2}+\sum i f_{abc}\frac{J^c(w)}{(z-w)}
-\end{equation}
-Expanding currents into series we get
-\begin{equation}
-  \label{eq:90}
-  \begin{aligned}
-    J^a(z)=\sum_{n\in \mathbb Z}z^{n-1}J^a_n\\    
-    \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}  
-  \end{aligned}
-\end{equation}
-We see that components of currents realize affine Lie algebra $\hat g$.
-
-Energy-momentum tensor is introduced with Sugawara construction as the sum of normal-ordered products of current components
-\begin{equation}
-  \label{eq:6}
-  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
-\end{equation}
-Here $h^v$ is the dual Coxeter number.
-
-Energy-momentum tensor can be expanded into modes $L_n$
-\begin{equation}
-  \label{eq:91}
-  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
-\end{equation}
-The commutation relations for the modes $L_n$ are
-\begin{equation}
-  \label{eq:92}
-  \begin{aligned}
-    \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
-    \left[L_n,J^a_m\right]=-mJ^a_{n+m}
-  \end{aligned}
-\end{equation}
-
-So the Sugawara construction is the way to embed Virasoro algebra into the universal enveloping of affine Lie algebra.
-
-Complete chiral algebra of WZW-model is equal to semidirect product $Vir\ltimes \hat g$
-
-The primary fields are the fields that transforms covariantly with respect to $G(z)\times G(\bar z)$, such as $g(z,\bar z)$. In terms of operator product expansion this property is reformulated as
-\begin{equation}
-  \label{eq:84}
-  \begin{aligned}
-    J^a(z)g(w,\bar w)\sim \frac{-t^a g(w,\bar w)}{(z-w)}\\
-    \bar J^a(z)g(w,\bar w)\sim \frac{ g(w,\bar w)t^a}{(z-w)}
-  \end{aligned}
-\end{equation}
-Any field $\phi_{\lambda,\mu}$ transforming covariantly with respect to some representation specified by $\lambda$ in holomorphic and $\mu$ in antiholomorphic sector, will be a WZW primary field.
-
-In terms of modes this property can be written as
-\begin{equation}
-  \label{eq:93}
-  \begin{aligned}
-    & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
-    & (J^a_n\phi_{\lambda})=0\quad \mbox{for}\; n>0\\
-  \end{aligned}
-\end{equation}
-We can associate the state $\left|\phi_{\lambda}\right>$ to the field $\phi_{\lambda}$
-  \begin{equation}
-    \label{eq:94}
-    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
-  \end{equation}
-Then the conditions (\ref{eq:93}) for WZW primary field are
-\begin{equation}
-  \label{eq:95}
-  \begin{aligned}
-    & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
-    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
-  \end{aligned}
-\end{equation}
-It is easy to see that the action of the Virasoro generators is
-\begin{equation}
-  \label{eq:96}
-  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
-\end{equation}
-Here we used the explicit form of the quadratic Casimir operator eigenvalue.
-
-Primary fields live in integrable finite-dimensional representations since infinite-dimensional and non-integrable fields are decoupled from the correlation functions.
-
-All secondary states are of the form
-\begin{equation}
-  \label{eq:97}
-  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
-\end{equation}
-For the correlation functions of primary fields we can obtain Knizhnik-Zamolodchikov equations which follow from global $G\times G$ invariance
-\begin{equation}
-  \label{eq:98}
-  \left(\partial_{z_i}+\frac{1}{k+h^v}\sum_{i\neq j}\frac{\sum_a t^a_i\otimes t^a_j}{z_i-z_k}\right)
-  \left<\phi_1(z_1)\dots \phi_n(z_n)\right>=0
-\end{equation}
-So the theory is completely determined by the representations of affine Lie algebra $\hat{\mathfrak{g}} $.
-
-\subsubsection{Modular invariants}
-\label{sec:modular-invariants}
-
-In previous section we studied holomorphic and antiholomorphic sectors of the theory separately.
-But in physically sensible theories this sectors should be entangled.
-It is required for the theory to be well-defined on the higher genus Riemann surfaces (see \cite{gaberdiel2000icf} and references therein) and also if we want our theory to describe critical behavior \cite{difrancesco1997cft}.
-In the critical point theory has conformal invariance, holomorphic and antiholomorphic sectors are decoupled, but in the vicinity of critical point there exists some large scale so the sectors should interact.
-
-!!! Expand this argumentation !!!
+ In physically sensible theories holomorphic and antiholomorphic
+ sectors should be entangled. It is required for the theory to be
+ well-defined on the higher genus Riemann surfaces (see
+ \cite{gaberdiel2000icf} and references therein) and also if we want
+ our theory to describe critical behavior \cite{difrancesco1997cft}.
+ In the critical point theory has conformal invariance, holomorphic
+ and antiholomorphic sectors are decoupled, but in the vicinity of
+ critical point there exists some large scale so the sectors should
+ interact \cite{difrancesco1997cft},
 
@@
 \label{sec:conformal-embeddings}
-Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory. !!! Provide an explanation !!!
+Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory.
 
@@
 
-It can be shown that solutions of equation (\ref{eq:111}) exist only for level 1 $k=1$.
+It can be shown that solutions of equation (\ref{eq:111}) exist only
+for level 1 $k=1$ \cite{difrancesco1997cft}.
 

### 2009-10-26 AffineLieAlgebras/InformalNotes/article.tex
One picture added

@@
 \begin{comment}
-  The problem of computation of the branching coefficients is very important. Why else would we study it??
-  It has major applications in physics of which nobody is aware. Blah-blah-blah.
+  Write here about the problem and possible applications in physics.
 \end{comment}
@@
 The extended Dynkin diagram of $B_2$ 
-\begin{equation}
-  \label{eq:8}
-  \begin{diagram}
-    \node{\circ}\arrow{e}{}\node{\circ}\arrow{e}{}\node{\circ}\\ \\
-    \node{\circ}\node[2]{\circ}
-  \end{diagram}
-\end{equation}
+\begin{figure}[ph]
+  \centering
+  \includegraphics[width=40mm]{B2_A1_diagram.pdf}
+  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
+  \label{fig:B2Dynkin}
+\end{figure}
 We then drop central node and get the embedding $A_1\otimes A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
@@
 
+\begin{comment}
+  Another examples?
+\end{comment}
 \subsection{Affine Lie algebras}
 \label{sec:affine-lie-algebras}
-
-\subsection{Embedding of finite-dimensional algebra into affine algebra}
+\begin{comment}
+  What examples should we include here?
+\end{comment}
+\subsubsection{Embedding of finite-dimensional algebra into affine algebra}
 \label{sec:embedd-finite-dimens}
 
-\subsection{Embedding of the affine algebra into affine algebra}
+\subsubsection{Embedding of the affine algebra into affine algebra}
 \label{sec:embedd-affine-algebr}
@@
 \label{sec:phys-appl}
-
+\begin{comment}
+  Rewrite it in more scientific style or drop this section.
+\end{comment}
 Branching coefficients for the embedding of affine Lie subalgebra into
@@
 
+\begin{comment}
+  We need some real examples
+\end{comment}
 \section{Conclusion}
 \label{sec:conclusion}
-
+\begin{comment}
+  Write it
+\end{comment}
+\begin{comment}
+  What about acknowledgements? 
+\end{comment}
 \bibliography{article}{}

### 2009-10-29 AffineLieAlgebras/InformalNotes/article.tex
Equations labels fixed.

@@
 \begin{equation}
-  \label{eq:19}
+  \label{eq:28}
   L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
@@
 \begin{equation}
+  \label{eq:1}
 k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
 \sum_{\gamma \in
@@
 Now we should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
+To prove it we should show that for any two positive roots $\alpha,\; \beta\in \Delta_{\bot}$ and corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$ there exists Weyl reflection $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}\in W_{\bot}$ and the corresponding positive root $\gamma\in \Delta_{\bot}$.
+Since root space of the subalgebra $\mathfrak{a}$ is invariant under $\omega_{\alpha}, \; \omega_{\beta}$ it is also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
+Then the positive root $\gamma in \Delta^{+}$ which corresponds to $\omega_{\gamma}$ is orthogonal to the root space of $\mathfrak{a}$ and hence $\gamma\in \Delta_{\bot}$.
 
-Let's denote the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.
+Since $W_{\bot}$ is the subgroup of $W$ and the space spanned over the set $\Delta_{\bot}$ is invariant under its action there exists a  subalgebra with the root space spanned over the set $\Delta_{\bot}$ which we denote by $\mathfrak{a}_{\bot}$.
 
@@
 \begin{equation}
-  \label{eq:1}
+  \label{eq:25}
   (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
@@
 \begin{equation}
-  \label{eq:1}
+  \label{eq:8}
   (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4)
@@
 \begin{multline}
-  \label{eq:2}
+  \label{eq:19}
   (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\\
@@
 \begin{equation}
-  \label{eq:3}
+  \label{eq:26}
   (e_3-e_4,e_4)
@@
 \begin{equation}
-  \label{eq:4}
+  \label{eq:27}
   \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}

### 2009-10-31 AffineLieAlgebras/InformalNotes/article.tex
Some fixes

@@
 
-$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ -- the integrable module
+$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
 of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
@@
 
-$r$ , $\left( r_{\frak{a}}\right) $ -- the rank of the algebra $\frak{g}$ $%
+$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
 \left( \text{resp. }\frak{a}\right) $ ;
 
-$\Delta $ $\left( \Delta _{\frak{a}}\right) $-- the root system; $\Delta
-^{+} $ $\left( \text{resp. }\Delta _{\frak{a}}^{+}\right) $-- the positive
+$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
+^{+} $ $\left( \text{resp. }\Delta _{\frak{a}}^{+}\right) $--- the positive
 root system (of $\frak{g}$ and $\frak{a}$ respectively);
@@
 $\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
-\alpha \right) \right) $ -- the multiplicity of the root $\alpha$ in $\Delta 
+\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $\Delta 
 $ (resp. in $\left( \Delta _{\frak{a}}\right) $);
@@
 $\overset{\circ }{\Delta }$ , $\left( \overset{\circ }{\Delta _{\frak{a}}}%
-\right) $ -- the finite root system of the subalgebra $\overset{\circ }{%
+\right) $ --- the finite root system of the subalgebra $\overset{\circ }{%
 \frak{g}}$ (resp. $\overset{\circ }{\frak{a}}$);
 
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ -- the
+$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ --- the
 weight diagram of $L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) 
@@
 
-$W$ , $\left( W_{\frak{a}}\right) $-- the corresponding Weyl group;
+$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
 
-$C$ , $\left( C_{\frak{a}}\right) $-- the fundamental Weyl chamber;
+$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
 
-$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ -- the Weyl vector;
+$\bar{C}, \left(\bar{C_{\mathfrak{a}}}\right)$ --- the closure of the fundamental Weyl chamber;
+
+$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
 
@@
 
-$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ -- the $i
+$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $i
 $-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \text{resp. }\frak{a}%
@@
 
-$\delta $ -- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);
+$\delta $ --- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);
 
 $\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
-}\right) $-- the basic coroot for $\frak{g}$ $\left( \text{resp. }\frak{a}%
+}\right) $--- the basic coroot for $\frak{g}$ $\left( \text{resp. }\frak{a}%
 \right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
@@
 $\overset{\circ }{\xi }$ , $\overset{\circ }{\xi _{\left( \frak{a}\right) }}$
--- the finite (classical) part of the weight $\xi \in P$ , $\left( \text{%
-resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $\ ;
+--- the finite (classical) part of the weight $\xi \in P$ , $\left( \text{%
+resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $;
 
-$\lambda =\left( \overset{\circ }{\lambda };k;n\right) $ -- the
+$\lambda =\left( \overset{\circ }{\lambda };k;n\right) $ --- the
 decomposition of an affine weight indicating the finite part $\overset{\circ 
@@
 
-$P$ $\left( \text{resp. } P_{\frak{a}}\right) $ \ -- the weight lattice;
+$P$ $\left( \text{resp. } P_{\frak{a}}\right) $ \ --- the weight lattice;
 
@@
 \right\} ;$
-
-$\mathcal{E}$\ , $\left( \mathcal{E}_{\frak{a}}\right) $-- the group algebra
-of the group $P$ (resp. $P_{\frak{a}} $);
-
-$\Theta _{\lambda }:=e^{-\frac{\left| \lambda \right| ^{2}}{2k}\delta
-}\sum\limits_{\alpha \in M}e^{t_{\alpha }\circ \lambda }$ -- the classical
-theta-function;
-
-$\Theta _{\left( \frak{a}\right) \nu }:=e^{-\frac{\left| \nu \right| ^{2}}{%
-2k_{\frak{a}}}\delta }\sum\limits_{\beta \in M_{\frak{a}}}e^{t_{\beta }\circ
-\nu }$;\newline
-notice that when the injection is considered the level $k_{\frak{a}}$ must
-be correlated with the corresponding rescaling of roots;
-
-$A_{\lambda }:=\sum\limits_{s\in \overset{\circ }{W}}\epsilon (s)\Theta
-_{s\circ \lambda }$ $\left( \text{resp. }A_{\left( \frak{a}\right) \nu
-}:=\sum\limits_{s\in \overset{\circ }{W_{\frak{a}}}}\epsilon (s)\Theta
-_{\left( \frak{a}\right) s\circ \nu }\right) $;
-
-$\Psi ^{\left( \mu \right) }:=e^{\frac{\left| \mu +\rho \right| ^{2}}{2k}%
-\delta \ -\ \rho }A_{\mu +\rho }=e^{\frac{\left| \mu +\rho \right| ^{2}}{2k}%
-\delta \ -\ \rho }\sum\limits_{s\in \overset{\circ }{W}}\epsilon (s)\Theta
-_{s\circ \left( \mu +\rho \right) }=$
-
-\noindent $=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$
--- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
-
-$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }:=e^{\frac{\left| \nu
-+\rho _{_{\frak{a}}}\right| ^{2}}{2k_{\frak{a}}}\delta \ -\ \rho _{_{\frak{a}%
-}}}A_{\left( \frak{a}\right) \nu +\rho _{_{\frak{a}}}}=e^{\frac{\left| \nu
-+\rho _{_{\frak{a}}}\right| ^{2}}{2k_{\frak{a}}}\delta \ -\ \rho _{_{\frak{a}%
-}}}\sum\limits_{s\in \overset{\circ }{W_{\frak{a}}}}\epsilon (s)\Theta
-_{\left( \frak{a}\right) s\circ \left( \nu +\rho _{_{\frak{a}}}\right) }=$
-
-\noindent $=\sum\limits_{w\in W_{\frak{a}}}\epsilon (w)e^{w\circ (\nu +\rho
-_{_{\frak{a}}})-\rho _{_{\frak{a}}}}$ -- the corresponding singular weight
+$\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
+$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}}}\epsilon (w)e^{w\circ (\nu +\rho
+_{_{\frak{a}}})-\rho _{_{\frak{a}}}}$ --- the corresponding singular weight
 element for the $\frak{a}$-module $L_{\frak{a}}^{\nu }$;
@@
 $\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
-a}\right) }^{\left( \nu \right) }}\right) $ -- the set of singular weights $%
+a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
 \xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
@@
 $m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
-}\right) $ -- the multiplicity of the weight $\xi \in P$ \ $\left( \text{%
+}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \text{%
 resp. }\in P_{\frak{a}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
@@
 $ch\left( L^{\mu }\right) $ $\left( \text{resp. }ch\left( L_{\frak{a}}^{\nu
-}\right) \right) $-- the formal character of $L^{\mu }$ $\left( \text{resp. }%
+}\right) \right) $--- the formal character of $L^{\mu }$ $\left( \text{resp. }%
 L_{\frak{a}}^{\nu }\right) $;
@@
 \mathrm{{mult}\left( \alpha \right) }}}=\frac{\Psi ^{\left( \mu \right) }}{%
-\Psi ^{\left( 0\right) }}$ -- the Weyl-Kac formula.
+\Psi ^{\left( 0\right) }}$ --- the Weyl-Kac formula.
 
@@
 \frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{%
-\left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $-- the
+\left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $--- the
 denominator.
 
-Character reduction
-\begin{equation}
-  \label{eq:28}
-  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
-    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
-  \Longrightarrow\quad
-  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
-\end{equation}
-Numbers $b^{(\mu)}_{\nu}$ are called branching coefficients.
+$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ --- the reduction of the representation;
 
-The anomalous branching coefficients $k_{\lambda}$ are defined as follows
+$b^{(\mu)}_{\nu}$ --- the branching coefficients;
+
 \begin{equation}
   \label{eq:21}
-  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
+  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
         a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
@@
 
+ $k_{\lambda}$ --- the anomalous branching coefficients;
+
 It is important to mention that
@@
   \label{eq:20}
-  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in C_{\mathfrak{a}}
+  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}
 \end{equation}
@@
 k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
 \sum_{\gamma \in
@@
 \end{equation}
-Now using the Weyl-Kac formula for the character of the module
-\begin{equation}
-  \label{eq:2}
-  ch L^{\mu}=\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}}
-\end{equation}
+Using the Weyl-Kac formula for the character of the module
 we obtain the equality
@@
 
-Now we should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
+We should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
 To prove it we should show that for any two positive roots $\alpha,\; \beta\in \Delta_{\bot}$ and corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$ there exists Weyl reflection $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}\in W_{\bot}$ and the corresponding positive root $\gamma\in \Delta_{\bot}$.
-Since root space of the subalgebra $\mathfrak{a}$ is invariant under $\omega_{\alpha}, \; \omega_{\beta}$ it is also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
+Since roots of the subalgebra $\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
 Then the positive root $\gamma in \Delta^{+}$ which corresponds to $\omega_{\gamma}$ is orthogonal to the root space of $\mathfrak{a}$ and hence $\gamma\in \Delta_{\bot}$.
@@
 \end{figure}
-We then drop central node and get the embedding $A_1\otimes A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
+We then drop central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
 \begin{comment}
@@
 
-Now we can multiply the equation (\ref{eq:4}) by the term
+We can multiply the equation (\ref{eq:4}) by the term
 \begin{equation}
@@
 
-Also we can see that 
+Also we can see that for any formal polynomial or series $Q$
 \begin{equation}
   \label{eq:6}
-  \pi_{\mathfrak{a}} (P) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(P\cdot (1-e^{-\alpha})\right)
+  \pi_{\mathfrak{a}} (Q) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(Q\cdot (1-e^{-\alpha})\right)
 \end{equation}
+
 The equation (\ref{eq:4}) takes the form
@@
 \end{multline}
-The right-hand side of this equation can be reorganised as in the paper \cite{ilyin812pbc}. We introduce anomalous branching coefficients $k_{\lambda}$.
+The right-hand side of this equation can be reorganised as in the paper \cite{ilyin812pbc}. We introduce the anomalous branching coefficients $k_{\lambda}$.
 \begin{equation}
@@
   \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
-  \frac{\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)}
-  {  \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
-\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
-}^{\left( \mu \right) }e^{\lambda } 
+  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
+    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda } 
 \end{multline}
 
-If the set $\Delta_{\bot}$ is non-empty then Weyl reflections corresponding to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
+If the set $\Delta_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
 
@@
 
-Then we can reorganise the summation on the left-hand side of the equation (\ref{eq:12}) in the following way
+Then we can reorganise the summation on the left-hand side of the equation (\ref{eq:12}) in the following way.
+\begin{comment}
+  We consider the factor-group $W/W_{\bot}$ and left conjugate classes.
+  Write it and check factor-group notation
+\end{comment}
 \begin{multline}
@@
   \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
-   \frac{\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)}
-   {   \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
-\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
-}^{\left( \mu \right) }e^{\lambda } 
+  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
+  \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda } 
 \end{multline}
 
-We can rewrite the fraction on the right-hand side as in the paper \cite{ilyin812pbc}.
-\begin{multline}
+We can rewrite the multiplier of the right-hand side as in the paper \cite{ilyin812pbc}.
+\begin{equation}
   \label{eq:11}
-    \frac{\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)}
-    {   \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}=
-    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})} \left(1-e^{-\alpha}\right)^{mult(\alpha)-mult_{\mathfrak{a}}(\alpha)}=\\
-    = -\sum_{\gamma\in P_{\mathfrak{a}}} s(\gamma)e^{-\gamma}
-\end{multline}
+    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})} \left(1-e^{-\alpha}\right)^{mult(\alpha)-mult_{\mathfrak{a}}(\alpha)}=
+     -\sum_{\gamma\in P_{\mathfrak{a}}} s(\gamma)e^{-\gamma}
+\end{equation}
 

### 2009-10-31 AffineLieAlgebras/InformalNotes/article.tex
Fix of factor-group

@@
   \label{eq:4}
-  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = 
+  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = 
   \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
+  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
 \end{equation}
@@
   \label{eq:5}
-  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)
+  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
 \end{equation}
@@
   \label{eq:7}
-  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
-  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
+  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
+  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
 \end{multline}
@@
   \label{eq:12}
-  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
+  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
   \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
@@
 Then we can reorganise the summation on the left-hand side of the equation (\ref{eq:12}) in the following way.
-\begin{comment}
-  We consider the factor-group $W/W_{\bot}$ and left conjugate classes.
-  Write it and check factor-group notation
-\end{comment}
+We consider the factor-group $W_{\bot}\backslash W$ and the left conjugate classes.
+For the class $\tilde{\omega}\in W_{\bot}\backslash W$ we choose the representative $\omega \in \tilde{\omega}$ in such a way that $\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$.
+Then
 \begin{multline}
   \label{eq:13}
- \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
- \pi_{\mathfrak{a}}\left(\sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right)
+ \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+ \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
 \end{multline}
 
+We see that the fraction on the right-hand side of the equation looks like the character of some representation. 
+\begin{comment}
+  Write here about $h+a_{\bot}$
+\end{comment}
 Then we see that
@@
   \label{eq:14}
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}} =\\
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}=\\
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
+  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
   \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
@@
   \label{eq:11}
-    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})} \left(1-e^{-\alpha}\right)^{mult(\alpha)-mult_{\mathfrak{a}}(\alpha)}=
+    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})} \left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}=
      -\sum_{\gamma\in P_{\mathfrak{a}}} s(\gamma)e^{-\gamma}
@@
 \begin{equation}
-\prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})}\left(
-1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
-}}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset 
+\prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})}\left(1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}_{\frak{a}}}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset
 \frak{g}}}s\left( \gamma \right) e^{-\gamma }.  \label{fan-d}

### 2009-10-31 AffineLieAlgebras/InformalNotes/article.tex
Some changes in pictures.

@@
 k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
 \sum_{\gamma \in
@@
 
-We see that the fraction on the right-hand side of the equation looks like the character of some representation. 
-\begin{comment}
-  Write here about $h+a_{\bot}$
-\end{comment}
-Then we see that
+We see that the fraction on the right-hand side of the equation looks like the character of some representation of the algebra $\mathfrak{a}_{\bot}$. 
+In order to write it explicitly we rewrite $\nu\cdot\omega(\mu+\rho)-\rho$ as
+\begin{equation}
+  \label{eq:30}
+  \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}+\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho
+\end{equation}
+
+Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we get
 \begin{multline}
   \label{eq:14}
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
 \end{multline}
-The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by $e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}})}$
+The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by the identity element of the algebra of formal exponents.
+So we have
   \begin{multline}
     \label{eq:15}
-    \pi_{\mathfrak{a}}\left(\sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
-    \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
+    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
+    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
   \end{multline}
 These dimensions of the modules could be easily calculated using Weyl formula.
+
+This explicit calculation to get the character of the $\mathfrak{a}_{\bot}$ representation can be thought as the calculation of the character of the $\mathfrak{a}_{\bot}\oplus \mathfrak{h}$-module with the highest weight $\omega(\mu+\rho)$, where $\mathfrak{h}$ is the Cartan subalgebra of $\mathfrak{g}$.
 
@@
   \label{eq:9}
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
   \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
@@
   \label{eq:16}
-  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
   = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
@@
   \label{eq:17}
-   \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
    \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\quad \xi\in P_{\mathfrak{a}}
@@
 On the figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
-Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W/W_{\bot}$:
+Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
 \begin{figure}[ph]

### 2009-11-02 AffineLieAlgebras/InformalNotes/article.tex
Some work on program for affine branching

@@
 \begin{equation}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-\sum_{\gamma \in
-\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
-+\gamma }^{\left( \mu \right) }\right)   \label{recurrent relation}
+  k_{\xi }^{\left( \mu \right) }=
+  -\frac{1}{s\left( \gamma _{0}\right) }
+  \left(
+    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}
+    \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+    \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+    \sum_{\gamma \in \Gamma _{\frak{a}\subset \frak{g}}} s\left( \gamma +\gamma _{0}\right) k_{\xi+\gamma }^{\left( \mu \right) }
+  \right)   
+\label{recurrent relation}
 \end{equation}
@@
 
-\section{Algorithm}
+\subsection{Algorithm for the recursive computation of the branching coefficients}
 \label{sec:algorithm}
+
+We use the recurrent relation \eqref{recurrent relation} to formulate the algorithm for recursive computation of the branching coefficients.
+It is important to mention that the computation of the branching coefficients is organised without the  explicit construction of the module $L^{(\mu)}_{\mathfrak{g}}$ and any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
+
+The algorithm is divided into the following steps.
 \begin{enumerate}
-\item Construct the set of anomalous points of the algebra $\mathfrak{g}$
-\item Calculate the dimensions of the corresponding modules $L_{\mathfrak{a}_{\bot}}$.
+\item Construct the set $\Delta^{+}$ of the positive roots of the algebra $\mathfrak{g}$.
+\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of the subalgebra $\mathfrak{a}$ and form the set $\Delta_{\bot}$.
+\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous points of the $\mathfrak{g}$-module $L^{(\mu)}$.
+\item Select those weights $\lambda=\omega(\mu+\rho)$ which lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$.
+Since we have constructed the set $\Delta_{\bot}$ we can easily check if the weight $\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ checking that the scalar product of $\lambda$ with the roots of $\Delta_{\bot}$ is non-negative.
+\item For $\lambda=\omega(\mu+\rho),\; \lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta_{\bot}$.
+\item Construct the set $\Gamma$ \eqref{fan-defined}.
 \item Calculate anomalous branching coefficients in the main Weyl
@@
 \end{enumerate}
+
+If we are interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous points up to required grade and use steps 4-7 of the algorithm for each grade.
+We can also speed up the algorithm by one-time computation of the representatives of the conjugate classes $W_{\bot}\backslash W$.
+
+The next section consists of several examples computed with this algorithm.
 

### 2009-11-06 AffineLieAlgebras/InformalNotes/article.tex
Some work on affine branching

@@
 
-\begin{comment}
-  Another examples?
-\end{comment}
 \subsection{Affine Lie algebras}
 \label{sec:affine-lie-algebras}
-\begin{comment}
-  What examples should we include here?
-\end{comment}
 \subsubsection{Embedding of finite-dimensional algebra into affine algebra}
@@
 
+The maximal embeddings of the finite-dimensional Lie algebras into the affine Lie algebras were thoroughly studied and the tables of the branching coefficients are given in the book \cite{kass1990ala}.
+The task of the study of non-maximal embeddings is then can be reduced to the well-known task of branching of the finite-dimensional Lie algebras.
+Thus here we show the simplest possible example of reduction of affine $\widehat{A_1}$ to $A_1$ in order to demonstrate some traits of our method and show that we eliminate the need of slice-by-slice study discussed in \cite{kass1990ala}.
+
+The simple roots for the affine $\widehat{A_1}$ are
+\begin{equation}
+  \label{eq:2}
+  (\alpha,\delta-\alpha)
+\end{equation}
+We consider the embedding with the root $\beta=\delta-\alpha$.
+
+Positive roots of the $\widehat{A_1}$ are $\alpha,\; \alpha+n\delta,\; n\delta,\; -\alpha+n\delta;\; n=1,2,3,\dots$.
+The set of the
+
 \subsubsection{Embedding of the affine algebra into affine algebra}
 \label{sec:embedd-affine-algebr}
+
+Consider the affine extension of the example \ref{sec:regul-embedd-a_1}. 
+Since this embedding is regular, the level of the representations of the subalgebra is equal to the level of the representation of the algebra.
+
+The set $\Delta_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\widehat{A_1}$ is the same as in the finite-dimensional case.
+
+Consider the level one representation of the algebra $\mathfrak{g}=\widehat{B_2}$ with the highest weight $(1,0,1,0)$, where the first to components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.
+
+The set of the anomalous points of this representation up to sixth grade is depicted in the figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the figure \ref{fig:B2_A1}.
+
+\begin{figure}[ph]
+  \centering
+  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
+  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\widehat{B_2}$}
+  \label{fig:affine_B2_anom_point}
+\end{figure}
 

### 2009-11-06 AffineLieAlgebras/InformalNotes/article.tex
Affine A1 to B2 example is completed.

@@
 The task of the study of non-maximal embeddings is then can be reduced to the well-known task of branching of the finite-dimensional Lie algebras.
-Thus here we show the simplest possible example of reduction of affine $\widehat{A_1}$ to $A_1$ in order to demonstrate some traits of our method and show that we eliminate the need of slice-by-slice study discussed in \cite{kass1990ala}.
+Thus here we show the simplest possible example of reduction of affine $\hat{A_1}$ to $A_1$ in order to demonstrate some traits of our method and show that we eliminate the need of slice-by-slice study discussed in \cite{kass1990ala}.
 
-The simple roots for the affine $\widehat{A_1}$ are
+The simple roots for the affine $\hat{A_1}$ are
 \begin{equation}
@@
 
-Positive roots of the $\widehat{A_1}$ are $\alpha,\; \alpha+n\delta,\; n\delta,\; -\alpha+n\delta;\; n=1,2,3,\dots$.
+Positive roots of the $\hat{A_1}$ are $\alpha,\; \alpha+n\delta,\; n\delta,\; -\alpha+n\delta;\; n=1,2,3,\dots$.
 The set of the
@@
 
-The set $\Delta_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\widehat{A_1}$ is the same as in the finite-dimensional case.
+The set $\Delta_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.
 
-Consider the level one representation of the algebra $\mathfrak{g}=\widehat{B_2}$ with the highest weight $(1,0,1,0)$, where the first to components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.
+Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first to components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.
 
@@
 \begin{figure}[ph]
-  \centering
   \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
-  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\widehat{B_2}$}
+  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
   \label{fig:affine_B2_anom_point}
@@
 
+As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+The result of this computation up to the twelfth grade is presented at the figure
+\begin{figure}[ph]
+  \centering
+  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
+  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \label{fig:AffineB2_A1_anom_proj}
+\end{figure}
+
+Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
+
+Using the definition (\ref{fan-defined}) we get the following set of
+the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$. 
+Here we restricted the computation to the twelfth grade.
+\begin{figure}[ph]
+  \includegraphics[width=150mm]{AffineB2_A1_fan.pdf}
+  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
+  \label{fig:B4B2Fan}
+\end{figure}
+
+Also we should mention that the lowest vector of the fan $\gamma_0$ is equal to zero, since we have excluded all the roots of $\Delta_{\bot}$ from the defining relation (\ref{fan-defined}).
+
+Using the recurrent relation for the anomalous branching coefficients we get the following result
+\begin{figure}[ph]
+  \includegraphics[width=150mm]{AffineB2_A1_branching.pdf}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
+  \label{fig:AffineB2_A1_branching}
+\end{figure}
+
+Selecting the points inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
+\begin{multline}
+  \label{eq:28}
+  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
+    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
+    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
+    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
+    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
+    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
+    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
+    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
+    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
+    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
+    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
+    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
+    1180 L_{\hat{A_1}}^{w_0}(-12)
+\end{multline}
+This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
+\begin{eqnarray}
+  \label{eq:29}
+  \begin{array}{cc}
+    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
+     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
+  \end{array}\\
+  \begin{array}{cc}
+    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
+    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
+  \end{array}
+\end{eqnarray}
+Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
 \section{Physical applications}

### 2009-11-07 AffineLieAlgebras/InformalNotes/article.tex
New items in the bibliography, some work on the physical applications and placement of the figures.

@@
 We show the result of this procedure on the figure \ref{fig:B4B2anom}.
-\begin{figure}[ph]
+\begin{figure}[h]
     \includegraphics[width=170mm]{B4_B2_anom_points.pdf}
@@
 the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$
-\begin{figure}[ph]
+\begin{figure}[h]
   \includegraphics[width=150mm]{B4_B2_fan.pdf}
@@
 
-\begin{figure}[ph]
+\begin{figure}[h!tb]
   \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
@@
 The result of this computation up to the twelfth grade is presented at the figure
-\begin{figure}[ph]
+\begin{figure}[h!tb]
   \centering
@@
 \begin{figure}[ph]
-  \includegraphics[width=150mm]{AffineB2_A1_fan.pdf}
+  \centering
+  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
   \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
@@
 \begin{figure}[ph]
-  \includegraphics[width=150mm]{AffineB2_A1_branching.pdf}
+  \centering
+  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
   \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
@@
 Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
+
+\newpage
 \section{Physical applications}
 \label{sec:phys-appl}
-\begin{comment}
-  Rewrite it in more scientific style or drop this section.
-\end{comment}
+Here we want to discuss possible applications of the described techniques in physical models.
+
 Branching coefficients for the embedding of affine Lie subalgebra into
 affine Lie algebra can be used to construct modular invariant
-partition functions of Wess-Zumino-Novikov-Witten models.
+partition functions of Wess-Zumino-Novikov-Witten models (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
+
+But for this construction to work the embedding is required to be conformal, which means that the central charge of the subalgebra is equal to the central charge of the algebra.
+\begin{equation}
+  \label{eq:31}
+  c(\mathfrak{a})=c(\mathfrak{g})
+\end{equation}
+
+ The class of the conformal embeddings is rather small, the complete classification is given in the paper \cite{schellekens1986conformal}. 
+The requirement (\ref{eq:31}) allows to reduce the task of the computation of the branching coefficients of affine Lie algebras to the computation of the branching coefficients of the finite-dimensional Lie algebras.
+
+Here we describe this procedure and discuss how the requirement (\ref{eq:31}) can be used to simplify the algorithm \ref{sec:algorithm}.
 

### 2009-11-07 AffineLieAlgebras/InformalNotes/article.tex
Some work on the introduction, bibliography and physical applications.

@@
 
-\begin{comment}
-  Write here about the problem and possible applications in physics.
-\end{comment}
+The problem of the reduction of Lie algebra representation to the representations of the subalgebra is studied for several decades and has various applications in physics.
+In the context of finite-dimensional algebras it is important for the study of great unification models whilst the problem of the branching of the affine Lie algebras emerges in conformal field theory, for example, in the construction of the modular-invariant partition functions \cite{difrancesco1997cft}.
+
+There exist several approaches to the computation of the branching coefficients which use the BGG
+resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in 
+\cite{kac1990idl},\cite{wakimoto2001idl}), the Schure function series \cite{fauser2006new}, the BRST
+cohomology \cite{hwang1994general}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
+combinatorial methods applied in \cite{feigin707principal}.
+
+Usually only the embedding of the maximal reductive subalgebras is considered since the case of non-maximal subalgebra can be obtained using the chain of maximal subalgebras.
+In this paper we present the recurrent formula for the branching coefficients which generalises the recurrent relation of the paper \cite{ilyin812pbc} to the case of non-maximal reductive subalgebra.
+Using this relation we formulate simple explicit algorithm for the computation of the branching coefficients which is applicable to the non-maximal subalgebras of finite-dimensional and affine Lie algebras.
+
+We show that our algorithm can be used in the study of the conformal embeddings where the central charge of the conformal field theory is preserved, but the computation in this case is simplified using physical requirements.
 
@@
 
-\newpage
 \section{Physical applications}
@@
 
- In physically sensible theories holomorphic and antiholomorphic
- sectors should be entangled. It is required for the theory to be
- well-defined on the higher genus Riemann surfaces (see
- \cite{gaberdiel2000icf} and references therein) and also if we want
- our theory to describe critical behavior \cite{difrancesco1997cft}.
- In the critical point theory has conformal invariance, holomorphic
- and antiholomorphic sectors are decoupled, but in the vicinity of
- critical point there exists some large scale so the sectors should
- interact \cite{difrancesco1997cft},
-
-The necessary constraint for the theory to be well-defined on higher Riemann surfaces, which is also believed to be sufficient, is that the vacuum correlator on the torus is independent of its parametrisation \cite{gaberdiel2000icf}.
-Conformal theory on the higher genus Riemann surfaces is important for the string theory since this theory describes string interaction.
-
-Two-dimensional torus is described as quotient space of $\mathbb{R}^2\approx \mathbb{C}$ by the relations $z\sim z+w_1$ and $z\sim z+w_2$, where $w_1$ and $w_2$ are not parallel.
-
-The complex structure of the torus is conformally equivalent to a torus for which the relations are $z\sim z+1$ and $z\sim z+\tau$ where $\tau$ is in the upper half plane of $\mathbb{C}$.
-It is also easy to see that $\tau$, $T(\tau)=\tau+1$ and $S(\tau)=-\frac{1}{\tau}$ describe conformally equivalent tori.
-Two maps $T$ and $S$ generate the group $SL(2,\mathbb{Z})/\mathbb{Z}_2$ that consists of matrices of the form
-\begin{equation}
-  \label{eq:99}
-  A=
-  \begin{pmatrix}
-    a & b\\
-    c & d 
-  \end{pmatrix}
-  \quad\mbox{where}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
-\end{equation}
-and matrices $A$ and $-A$ have the same action on $\tau$
-\begin{equation}
-  \label{eq:100}
-  \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
-\end{equation}
-The parameter $\tau$ is called the modular parameter and the group  $SL(2,\mathbb{Z})/\mathbb{Z}_2$ is called the modular group.
-
-Given a conformal field theory that is defined on the Riemann sphere, the vacuum
-correlator on the torus can be determined as follows. First, we cut the torus along one
-of its non-trivial cycles; the resulting surface is a cylinder (or an annulus) whose shape
-depends on one complex parameter $q$. Since the annulus is a subset of the sphere, the
-conformal field theory on the annulus is determined in terms of the theory on the sphere.
-In particular, the states that can propagate in the annulus are precisely the states of
-the theory as defined on the sphere.
-In order to reobtain the torus from the annulus, we have to glue the two ends of
-the annulus together; in terms of conformal field theory this means that we have to sum
-over a complete set of states. The vacuum correlator on the torus is therefore described
-by a trace over the whole space of states, the partition function of the theory,
-\begin{equation}
-  \label{eq:101}
-  \sum_{(i,j)}Tr_{\mathcal{H}_{(i,j)}}(\mathcal{O}(q,\bar q)),
-\end{equation}
-where $\mathcal{O}(q,\bar q)$ is the operator that describes the propagation of the states along the annulus,
-\begin{equation}
-  \label{eq:102}
-  \mathcal{O}(q,\bar q)=q^{L_0-\frac{c}{24}}\bar q^{\bar L_0-\frac{\bar c}{24}}
-\end{equation}
-The propagator depends on the actual shape of the annulus that is described in terms
-of the complex parameter $q$. For a given torus that is described by $\tau$ , there is a natural
-choice for how to cut the torus into an annulus, and the complex parameter $q$ that is
-associated to this annulus is $q=e^{2\pi i \tau}$. Since the tori that are described by $\tau$ and $A\tau$
-(where $A \in SL(2, \mathbb{Z})$) are equivalent, the vacuum correlator is only well-defined provided
-that (\ref{eq:101}) is invariant under this transformation. This provides strong constraints on
-the spectrum of the theory.
-
-Each of the spaces $\mathcal{H}_{(i,j)}$ is a tensor product of an irreducible representation $\mathcal{H}_j$ of chiral algebra and an irreducible representation $\bar{\mathcal{H}}_{\bar{j}}$ of antichiral algebra.
-Then the vacuum correlator on the torus (\ref{eq:101}) takes the form
-\begin{equation}
-  \label{eq:103}
-  \sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
-\end{equation}
-where $\chi_j$ is the character of the representation $\mathcal{H}_j$,
-\begin{equation}
-  \label{eq:104}
-  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{where}\; q=e^{2\pi i \tau}
-\end{equation}
-Characters transform into one another under modular transformations,
-\begin{equation}
-  \label{eq:107}
-  \chi_j(-\frac{1}{\tau})=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{and}\quad \chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
-\end{equation}
-where $S$ and $T$ are constant matrices. This fact is proved for a certain class of conformal field theories \cite{gaberdiel2000icf}.
-
-For WZW-models the representations are determined by highest weights $\hat \lambda, \hat \xi$. Then we can write
-\begin{equation}
-  \label{eq:105}
-  \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi} L_{\hat \lambda}\otimes L_{\hat \xi}
-\end{equation}
-The partition function is rewritten as
-\begin{equation}
-  \label{eq:106}
-  Z(\tau)=\sum_{\hat \lambda,\hat \xi\in P^{(k)}_{+}} \chi_{\hat \lambda}(\tau)M_{\hat \lambda\hat\xi}\bar \chi_{\hat \xi}(\bar \tau)
-\end{equation}
-The element of the mass matrix $M_{\hat \lambda\hat\xi}$ can be thought of as the multiplicity of primary field with weights $\hat\lambda,\hat \xi$.
-It has following properties:$M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, it is modular invariant
-\begin{equation}
-  \label{eq:108}
-  \begin{aligned}
-    T^{\dagger}MT=S^{\dagger}MS=M,\\
-    [M,S]=[M,T]=0,
-  \end{aligned}
-\end{equation}
-and $M_{00}=1$ for the uniqueness of vacuum.
-
-The simplest case of diagonal matrix $M$ corresponds to equal holomorphic and antiholomorphic conformal dimensions.
-There are several ways to construct non-diagonal modular invariants from diagonal \cite{difrancesco1997cft}:
-\begin{itemize}
-\item Method of outer automorphisms
-\item Conformal embedding into bigger theory
-\item Galois-transpositions
-\end{itemize}
-Here we will discuss conformal embeddings.
-
-\subsubsection{Conformal embeddings}
-\label{sec:conformal-embeddings}
 Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory.
@@
 for level 1 $k=1$ \cite{difrancesco1997cft}.
-
-There exist only finite number of such embeddings.
 

### 2009-11-09 AffineLieAlgebras/InformalNotes/article.tex
Some work on physics and the conclusion

@@
 We then drop central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
+
+In the case of special embeddings the set $\Delta_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $su(p)\subset su(p)\oplus su(q)\subset $
 \begin{comment}
-  Consider special embeddings
+  Well, I can't understand how the roots are embedded in the special embeddings. I need some help here.
 \end{comment}
@@
 \label{sec:affine-lie-algebras}
-\subsubsection{Embedding of finite-dimensional algebra into affine algebra}
-\label{sec:embedd-finite-dimens}
-
-The maximal embeddings of the finite-dimensional Lie algebras into the affine Lie algebras were thoroughly studied and the tables of the branching coefficients are given in the book \cite{kass1990ala}.
+%%  \subsubsection{Embedding of finite-dimensional algebra into affine algebra}
+%%  \label{sec:embedd-finite-dimens}
+%%  
+%%  The maximal embeddings of the finite-dimensional Lie algebras into the affine Lie algebras were thoroughly studied and the tables of the branching coefficients are given in the book \cite{kass1990ala}.
 The task of the study of non-maximal embeddings is then can be reduced to the well-known task of branching of the finite-dimensional Lie algebras.
-Thus here we show the simplest possible example of reduction of affine $\hat{A_1}$ to $A_1$ in order to demonstrate some traits of our method and show that we eliminate the need of slice-by-slice study discussed in \cite{kass1990ala}.
-
-The simple roots for the affine $\hat{A_1}$ are
-\begin{equation}
-  \label{eq:2}
-  (\alpha,\delta-\alpha)
-\end{equation}
-We consider the embedding with the root $\beta=\delta-\alpha$.
-
-Positive roots of the $\hat{A_1}$ are $\alpha,\; \alpha+n\delta,\; n\delta,\; -\alpha+n\delta;\; n=1,2,3,\dots$.
-The set of the
-
+%%  Thus here we show the simplest possible example of reduction of affine $\hat{A_1}$ to $A_1$ in order to demonstrate some traits of our method and show that we eliminate the need of slice-by-slice study discussed in \cite{kass1990ala}.
+%%  
+%%  The simple roots for the affine $\hat{A_1}$ are
+%%  \begin{equation}
+%%    \label{eq:2}
+%%    (\alpha,\delta-\alpha)
+%%  \end{equation}
+%%  We consider the embedding with the root $\beta=\delta-\alpha$. 
+%%  
+%%  Positive roots of the $\hat{A_1}$ are $\alpha,\; \alpha+n\delta,\; n\delta,\; -\alpha+n\delta;\; n=1,2,3,\dots$.
+%%  The set of the 
+%%  
 \subsubsection{Embedding of the affine algebra into affine algebra}
@@
 
+\newpage
 \section{Physical applications}
@@
 \end{equation}
-For sub-algebra $\mathfrak{p}\subset\mathfrak{g}$
+For sub-algebra $\mathfrak{a}\subset\mathfrak{g}$
 \begin{equation}
   \label{eq:110}
-  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\mathcal{P}\lambda\right>
+  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>
 \end{equation}
-Here $\tilde{J}^{a'_j}_{-n_j}$ are the generators of $\mathfrak{p}$ and $\mathcal{P}$ is the projection of $\mathfrak{g}$ to $\mathfrak{p}$.
-$\mathfrak{g}$-invariance of vacuum entails its $\mathfrak{p}$-invariance, but it is not the case for energy-momentum tensor.
-So energy-momentum tensor of bigger theory should consist only of generators of $\hat{\mathfrak{p}}$.
-Then $T_{\hat{\mathfrak{g}}}=T_{\hat{\mathfrak{p}}}\Rightarrow c(\hat{\mathfrak{g}})=c(\hat{\mathfrak{p}})$.
+Here $\tilde{J}^{a'_j}_{-n_j}$ are the generators of $\mathfrak{a}$ and $\pi_{\mathfrak{a}}$ is the projection of $\mathfrak{g}$ to $\mathfrak{a}$.
+$\mathfrak{g}$-invariance of vacuum entails its $\mathfrak{a}$-invariance, but it is not the case for energy-momentum tensor.
+So energy-momentum tensor of bigger theory should consist only of generators of $\mathfrak{a}$.
+Then $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow c(\mathfrak{g})=c(\mathfrak{a})$.
 This leads to equation
@@
   \label{eq:111}
-  \frac{k\;dim\mathfrak{g}}{k+g}=\frac{x_e k\; dim\mathfrak{p}}{x_ek+p}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
 \end{equation}
-Here $x_e$ is the embedding index and $g$, $p$ are dual Coxeter numbers of corresponding algebras. !!! Prove and expand !!!
+Here $x_e$ is the embedding index and $g$, $a$ are dual Coxeter numbers of corresponding algebras.
 
@@
 
-{\bf Examples}
-\begin{itemize}
-\item $su(2)\subset su(3),\; x_e=4$
-\item $\hat{su}(2)_{10}\subset\hat{sp}(4)_1$
-\item $\hat{su}(2)_{28}\subset(\hat{G_2})_1$
-\item $\hat{su}(2)_{16}\oplus\hat{su}(3)\subset (\hat{E_8})_1$
-\end{itemize}
+If we have modular-invariant partition function for the fields described by the representation of the algebra $\mathfrak{g}$ this modular invariance is preserved by the projection on the subalgebra $\mathfrak{a}$, but we need also the preservation of the conformal invariance.
+So we should select only those highest-weight modules of the subalgebra $\mathfrak{a}$ for which the relation (\ref{eq:111}) holds.
 
-Branching $\hat{\lambda}\to \bigoplus_{\hat{\mu}}b_{\hat{\lambda}\hat{\mu}}\hat{\mu}$
+Since in the decomposition (\ref{eq:3}) the highest weight $\nu$ of the subalgebra module belongs to some grade $n$ of projected algebra module $\pi_{\mathfrak{a}}\cdot L^{(\mu)}_{\mathfrak{g}}$, from the relation (\ref{eq:111}) one can obtain the following requirement on the conformal dimensions of the corresponding fields
 \begin{equation}
-  \label{eq:112}
-  h_{\hat{\lambda}}+n=h_{\hat{\mu}},\quad \frac{(\lambda,\lambda+2\rho)}{2(1+g)}+n=\frac{(\mu,\mu+2\rho)}{2(x_e+p)}
+  \label{eq:32}
+   \Delta_{\pi_{\mathfrak{a}}\mu}+n=\Delta_{\nu}
 \end{equation}
-The simple way is to calculate the dimensions of all the representations of simple finite-dimensional Lie algebras $\mathfrak{g},\mathfrak{p}$ and find all the triples $(\lambda,\mu,n)$, satisfying (\ref{eq:112}).
-Then investigate the representation $L_{\hat{\lambda}}$ of level $n$ as the sum of irreducible representations of $\mathfrak{g}$ and write out all the branching rules of these representations in representations of subalgebra $\mathfrak{p}$.
-The number of times the representation with highest weight $\mu$ appears in this listing is the required branching coefficient $b_{\hat{\lambda},\hat{\mu}}$.
+It leads to the relation on the classical parts of the corresponding weights:
+\begin{equation}
+  \label{eq:33}
+  \frac{(\overset{\circ }{\mu},\overset{\circ }{\mu}+2\rho)}{2(1+g)}+n=\frac{(\overset{\circ }{\nu},\overset{\circ }{\nu}+2\rho_{\mathfrak{a}})}{2(x_e+a)}
+\end{equation}
+There exits the finite reducibility theorem for the conformal embeddings which states that only finite number of the branching coefficients is non-zero in the case of the conformal embedding $\mathfrak{a}\subset\mathfrak{a}$.
 
-  Then non-diagonal modular invariants are obtained by substitution of character relations. For example, having calculated branching coefficients for $\hat{su}(2)_{28}\subset (\hat{G_2})_1$
+Then after we have found all such weights $\nu$ and the corresponding branching coefficients $b^{(\mu)}_{\nu}$ we can substitute the sums $\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}$ over the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules in place of the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function
 \begin{equation}
-    \label{eq:113}
-    \begin{aligned}
-      & [1,0,0]\to [28,0]\oplus [18,10]\oplus [10,18]\oplus [0,28]\\
-      & [0,0,1]\to [22,6]\oplus [16,12]\oplus [12,16]\oplus [6,22]\\
-    \end{aligned}
+  \label{eq:34}
+   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
 \end{equation}
-we get following modular-invariant partition function
+Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
 \begin{equation}
-  \label{eq:114}
-  Z=\left|\chi_{[28,0]}+\chi_{[18,10]}+\chi_{[10,18]}+\chi_{[0,28]}\right|^2+\left|\chi_{[22,6]}+\chi_{[16,12]}+\chi_{[12,16]}+\chi_{[6,22]}\right|^2
+  \label{eq:34}
+   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
 \end{equation}
 
-Modular invariants of WZW-models, partition functions etc.
+\subsection{Example}
+\label{sec:example}
+
+Consider the level ten embedding of the affine $\hat A_1$ into the level one affine $\hat C_2$. 
+The relation (\ref{eq:33}) and the finite reducibility theorem greatly simplify the calculation with the algorithm \ref{sec:algorithm}, since we know that there exists only finite number of the non-zero branching coefficients and the maximal grade of this coefficients is restricted.
 
 \begin{comment}
-  We need some real examples
+  Do the calculation, show the restriction on the grade and the final result
+  \begin{equation}
+    \label{eq:35}
+    Z=\left|\chi_{[10,0]}+\chi_{[4,6]}\right|^2+\left|\chi_{[7,3]}+\chi_{[3,7]}\right|^2+\left|\chi_{[6,4]}+\chi_{[0,10]}\right|^2
+  \end{equation}
 \end{comment}
+
 \section{Conclusion}
 \label{sec:conclusion}
-\begin{comment}
-  Write it
-\end{comment}
+We have proved the recurrent relation on the branching coefficients and proposed practical algorithm of the reduction of the representations.
+Also we have discussed the application of this algorithm to the physical problem of construction of modular-invariant partition functions in the conformal field theory.
+This method of conformal embeddings is well-known but may be actual in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
 \begin{comment}

### 2009-11-09 AffineLieAlgebras/InformalNotes/article.tex
Something

@@
 \usepackage[unicode,verbose]{hyperref}
-\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
+\usepackage{amsmath,amssymb,amsthm} 
+\usepackage{pb-diagram}
 \usepackage{ucs}
@@
 Using the definition (\ref{fan-defined}) we get the following set of
-the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$. 
+the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
 Here we restricted the computation to the twelfth grade.
@@
   \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
-  \label{fig:B4B2Fan}
+  \label{fig:AffineB2A1Fan}
 \end{figure}
@@
 \begin{equation}
-  \label{eq:34}
+  \label{eq:36}
    Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)

### 2009-11-17 AffineLieAlgebras/InformalNotes/article.tex

@@
 In the next subsection of the introduction we fix the notation used throughout the paper.
-Then in section \ref{sec:recurr-form-branch} we derive the central recurrent formula for the anomalous branching coefficients and describe the algorithm for the decomposition integrable highest weight modules of algebra $\mathfrak{g}$ to the modules of reductive subalgebra $\mathfrak{a}$ \ref{sec:algorithm}.
-In the next section \ref{sec:examples} we present several examples and discuss some applications in the physical models \ref{sec:phys-appl}.
-We conclude the paper with the review of results and the discussion of possible future developments \ref{sec:conclusion}.
+Then in Section \ref{sec:recurr-form-branch} we derive the central recurrent formula for the anomalous branching coefficients and describe the algorithm for the decomposition of the integrable highest weight modules of algebra $\mathfrak{g}$ to the modules of a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}).
+In the next Section \ref{sec:examples} we present several examples and discuss some applications in the physical models (s.
+\ref{sec:phys-appl}).
+We conclude the paper with the review of results and discussion of possible future developments (s.
+\ref{sec:conclusion}).
+\begin{comment}
+  Fix links to the sections
+\end{comment}
 
@@
 
-Consider the affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
+Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
 underlying finite-dimensional subalgebras $\overset{\circ }{\frak{g}}$ and $%
@@
 
-\section{Recurrent formula for branching coefficients}
+\section{Recurrent relation for branching coefficients}
 \label{sec:recurr-form-branch}
@@
 In the next section we describe the algorithm for the computation of branching coefficients based upon this formula and then present some example and discuss physical meaning.
-
-\subsection{Proof of the recurrent formula}
+\begin{comment}
+  Fix the relation so that the definitions are available for the reader.
+\end{comment}
+\subsection{Proof of the recurrent relation}
 \label{sec:proof}
 
-The decomposition of the representation of the algebra to the representations of the subalgebra can be symbolically written using formal characters and projection operator:
+The decomposition of the representation of the algebra to the representations of the subalgebra can be symbolically written using formal characters and projection operator $\pi_{\mathfrak{a}}$ to the weight subspace:
 \begin{equation}
@@
 Let's denote the subset of these roots by $\Delta_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
+\begin{comment}
+  Rewrite it: there are no roots associated with Weyl group element.
 
@@
 Then the positive root $\gamma in \Delta^{+}$ which corresponds to $\omega_{\gamma}$ is orthogonal to the root space of $\mathfrak{a}$ and hence $\gamma\in \Delta_{\bot}$.
-
+\end{comment}
 Since $W_{\bot}$ is the subgroup of $W$ and the space spanned over the set $\Delta_{\bot}$ is invariant under its action there exists a  subalgebra with the root space spanned over the set $\Delta_{\bot}$ which we denote by $\mathfrak{a}_{\bot}$.
@@
 Now we should discuss when the subset $\Delta_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
-
+\begin{comment}
+  Rewrite the following paragraph so that the limit is correct. Add the formula from the paper \cite{ilyin812pbc} here or near the recurrent relation (\ref{eq:1}).
+\end{comment}
 If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta_{\bot}$ is empty.
 Then the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the formula (11) from the paper \cite{ilyin812pbc}.
-
+\begin{comment}
+  Analyze all the regular embeddings and show when there exist orthogonal roots 
+\end{comment}
 Non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
@@
 We then drop central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
-
+\begin{comment}
+  Add the embedding index to the definitions
+\end{comment}
 In the case of special embeddings the set $\Delta_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $su(p)\subset su(p)\oplus su(q)\subset $
 \begin{comment}
-  Well, I can't understand how the roots are embedded in the special embeddings. I need some help here.
+  Add here the example
 \end{comment}
@@
 \end{multline}
-The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by the identity element of the algebra of formal exponents.
+The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by the unity of the algebra of formal exponents.
 So we have
@@
   \end{multline}
-These dimensions of the modules could be easily calculated using Weyl formula.
-
+These dimensions of the modules could be easily calculated using the Weyl formula.
+\begin{comment}
+  Rewrite it, so that the following paragraph begins the computation
+\end{comment}
 This explicit calculation to get the character of the $\mathfrak{a}_{\bot}$ representation can be thought as the calculation of the character of the $\mathfrak{a}_{\bot}\oplus \mathfrak{h}$-module with the highest weight $\omega(\mu+\rho)$, where $\mathfrak{h}$ is the Cartan subalgebra of $\mathfrak{g}$.
@@
 _{0} $ be the lowest vector with respect to the natural ordering in $%
-\overset{\circ }{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$. Decomposing the defining relation 
+\overset{\circ }{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$. Decomposing the defining relation (\ref{fan-d}) 
 \begin{equation}
@@
 Here the second component denotes the value of $s(\gamma)$.
+\begin{comment}
+  It seems that here $\Gamma$ should include only two points. Is it true?
 
+  Think of the pictures more.
+\end{comment}
 Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent relation}) gives us
@@
 
+\begin{comment}
+  Change ``enveloping'' into something better.
+\end{comment}
 Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory.

### 2009-11-24 AffineLieAlgebras/InformalNotes/article.tex
Some work on the physical example of the affine branching and on the new implementation in Scheme.

@@
 
+This affine embedding is the affine extension of the special embedding $A_1\subset C_2$ with the embedding index equal to 10.
+The projection of the weights of algebra $C_2$ is calculated using the projection matrix $\mathcal{P}=(3,4)$.
+The embedding index
+\begin{equation}
+  \label{eq:37}
+  x_e=\frac{\left|\mathcal{P}\Theta_{\mathfrak{g}}\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}=\frac{k_{\mathfrak{a}}}{k_{\mathfrak{g}}}=10
+\end{equation}
+If we consider this embedding in the orthogonal basis where the simple roots of $C_2$ are given by
+\begin{equation}
+  \label{eq:38}
+  \alpha_1=(1,-1),\quad \alpha_2=(0,2),
+\end{equation}
+then the simple root of the embedded $A_1$ is equal to
+\begin{equation}
+  \label{eq:39}
+  \beta=\sqrt{\frac{2}{5}}(3,1)
+\end{equation}
+It is easy to see that the set $\Delta_{\bot}$ of the $C_2$ roots orthogonal to $\beta$ is empty.
+
+Now we proceed the computation of the branching coefficients using the algorithm \ref{sec:algorithm}. 
+On the level 1 there exist three dominant weights with Dynkin labels $[1,0,0], \; [0,1,0],\; [0,0,1]$.
 \begin{comment}

### 2009-11-27 AffineLieAlgebras/InformalNotes/article.tex
LiterateLie in Scheme started, acms paper pdf added, some work on new article.

@@
 
-So we've obtained recurrent relation for the anomalous branching coefficients.
+So we have obtained recurrent relation for the anomalous branching coefficients.
 In the next section we describe the algorithm for the computation of branching coefficients using the relation \eqref{recurrent relation}.
@@
 Consider the regular embedding of $A_1$ into $B_2$.
-Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the thick vectors at the figure \ref{fig:B2_A1}.
+Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the thick vectors at the Figure \ref{fig:B2_A1}.
 We denote the corresponding Weyl reflections by $\omega_1, \omega_2$.
@@
 \end{figure}
-On the figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
+On the Figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
 Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
@@
 \end{equation}
-So we've computed the branching coefficients.
+So we have computed the branching coefficients.
 \subsubsection{Embedding of $B_2$ into $B_4$}
@@
 We calculate the branching coefficients for the fundamental representation of $B_4$.
-The corresponding Dynkin diagrams are in the figure.
+The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
 \begin{figure}[ph]
@@
 The set of the anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W$
-consists of 384 points. We don't show it here.
+consists of 384 points. We do not show it here.
 
@@
 
-We show the result of this procedure on the figure \ref{fig:B4B2anom}.
+We show the result of this procedure on the Figure \ref{fig:B4B2anom}.
 \begin{figure}[h]
@@
 
-The set of the anomalous points of this representation up to sixth grade is depicted in the figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the figure \ref{fig:B2_A1}.
+The set of the anomalous points of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.
 
@@
 As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
-The result of this computation up to the twelfth grade is presented at the figure
+The result of this computation up to the twelfth grade is presented at the Figure
 \begin{figure}[h!tb]
@@
 On the level 1 there exist three dominant weights with Dynkin labels $[1,0,0], \; [0,1,0],\; [0,0,1]$.
+
 \begin{comment}

### 2009-12-01 AffineLieAlgebras/InformalNotes/article.tex
Fixed incorrect definition of a_{\bot}

@@
 \ref{sec:conclusion}).
-\begin{comment}
-  Fix links to the sections
-\end{comment}
 
@@
 These roots are orthogonal to the root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the algebra $\mathfrak{g}$.
-Let's denote the subset of these roots by $\Delta_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
-\begin{comment}
-  Rewrite it: there are no roots associated with Weyl group element.
+Let's denote the subset of these roots by $\Delta^{+}_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
 
-We should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
-To prove it we should show that for any two positive roots $\alpha,\; \beta\in \Delta_{\bot}$ and corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$ there exists Weyl reflection $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}\in W_{\bot}$ and the corresponding positive root $\gamma\in \Delta_{\bot}$.
+We should notice that if the set $\Delta^{+}_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
+Consider any two positive roots $\alpha,\; \beta\in \Delta^{+}_{\bot}$ and corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.
 Since roots of the subalgebra $\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
-Then the positive root $\gamma in \Delta^{+}$ which corresponds to $\omega_{\gamma}$ is orthogonal to the root space of $\mathfrak{a}$ and hence $\gamma\in \Delta_{\bot}$.
-\end{comment}
-Since $W_{\bot}$ is the subgroup of $W$ and the space spanned over the set $\Delta_{\bot}$ is invariant under its action there exists a  subalgebra with the root space spanned over the set $\Delta_{\bot}$ which we denote by $\mathfrak{a}_{\bot}$.
+So the subgroup $W_{\bot}$ preserves the root system of the subalgebra $\mathfrak{a}$.
 
-Now we should discuss when the subset $\Delta_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
+The action of the Weyl subgroup $W_{\bot}$ on the set $\Delta^{+}_{\bot}$ produce the root system $\Delta_{\bot}$ which is orthogonal to the root system $\Delta_{\mathfrak{a}}$ of the subalgebra $\mathfrak{a}$.
+This root system can be considered as the root system of some subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
+
+Now we should discuss when the subset $\Delta^{+}_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
 \begin{comment}
@@
 \end{comment}
-If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta_{\bot}$ is empty.
+If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta^{+}_{\bot}$ is empty.
 Then the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the formula (11) from the paper \cite{ilyin812pbc}.
@@
 \end{comment}
-In the case of special embeddings the set $\Delta_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $su(p)\subset su(p)\oplus su(q)\subset $
+In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $su(p)\subset su(p)\oplus su(q)\subset $
 \begin{comment}
@@
   \label{eq:5}
-  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
+  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
 \end{equation}
@@
   \label{eq:7}
-  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
+  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
   \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
@@
   \label{eq:12}
-  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
+  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
     \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda } 
@@
 
-If the set $\Delta_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
+If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
 
-We have denoted the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.
+We have denoted the subalgebra with the root space spanned over the set $\Delta^{+}_{\bot}$ by $\mathfrak{a}_{\bot}$.
 
@@
   \label{eq:13}
- \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
- \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
+ \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+ \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
 \end{multline}
@@
   \label{eq:14}
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
@@
   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
-  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
+  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
   \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda } 
@@
   \label{eq:11}
-    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})} \left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}=
+    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})} \left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}=
      -\sum_{\gamma\in P_{\mathfrak{a}}} s(\gamma)e^{-\gamma}
@@
 \begin{equation}
-\prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})}\left(1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}_{\frak{a}}}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset
+\prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})}\left(1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}_{\frak{a}}}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset
 \frak{g}}}s\left( \gamma \right) e^{-\gamma }.  \label{fan-d}
@@
   \label{eq:18}
-  \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})}\left(
+  \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})}\left(
     1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
@@
 \item Construct the set $\Delta^{+}$ of the positive roots of the algebra $\mathfrak{g}$.
-\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of the subalgebra $\mathfrak{a}$ and form the set $\Delta_{\bot}$.
+\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of the subalgebra $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
 \item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous points of the $\mathfrak{g}$-module $L^{(\mu)}$.
 \item Select those weights $\lambda=\omega(\mu+\rho)$ which lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$.
-Since we have constructed the set $\Delta_{\bot}$ we can easily check if the weight $\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ checking that the scalar product of $\lambda$ with the roots of $\Delta_{\bot}$ is non-negative.
-\item For $\lambda=\omega(\mu+\rho),\; \lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta_{\bot}$.
+Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check if the weight $\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ checking that the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ is non-negative.
+\item For $\lambda=\omega(\mu+\rho),\; \lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
 \item Construct the set $\Gamma$ \eqref{fan-defined}.
@@
 
-The set $\Delta_{\bot}$ is equal to
+The set $\Delta^{+}_{\bot}$ is equal to
 \begin{equation}
@@
 We need to select those points $\omega(\mu+\rho)$  which are projected into the main chamber of the embedded algebra $\mathfrak{a}_{\bot}$.
-It means that scalar product of these points with all the roots from $\Delta_{\bot}$ is non-negative.
+It means that scalar product of these points with all the roots from $\Delta^{+}_{\bot}$ is non-negative.
 
@@
 $\mathfrak{a}_{\bot}$-modules we need to project each selected point
-onto the root space $\Delta_{\bot}$ and substract
+onto the root space $\Delta^{+}_{\bot}$ and substract
 $\rho_{\mathfrak{a}_{\bot}}$, then use Weyl dimension formula.
@@
 
-The set $\Delta_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.
+The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.
 
@@
 
-Also we should mention that the lowest vector of the fan $\gamma_0$ is equal to zero, since we have excluded all the roots of $\Delta_{\bot}$ from the defining relation (\ref{fan-defined}).
+Also we should mention that the lowest vector of the fan $\gamma_0$ is equal to zero, since we have excluded all the roots of $\Delta^{+}_{\bot}$ from the defining relation (\ref{fan-defined}).
 
@@
 \end{equation}
-It is easy to see that the set $\Delta_{\bot}$ of the $C_2$ roots orthogonal to $\beta$ is empty.
+It is easy to see that the set $\Delta^{+}_{\bot}$ of the $C_2$ roots orthogonal to $\beta$ is empty.
 

### 2009-12-05 AffineLieAlgebras/InformalNotes/article.tex
a_{\bot}\oplus h fragment is moved and slightly rewritten, it may allow better understanding of the computations

@@
 \frak{g}}$ (resp. $\overset{\circ }{\frak{a}}$);
+$\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);
 
@@
 
+$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|}{\left|\Theta_{\mathfrak{a}}\right|}$ --- the embedding index.
+
 \section{Recurrent relation for branching coefficients}
@@
 Now we should discuss when the subset $\Delta^{+}_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
-\begin{comment}
-  Rewrite the following paragraph so that the limit is correct. Add the formula from the paper \cite{ilyin812pbc} here or near the recurrent relation (\ref{eq:1}).
-\end{comment}
+
 If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta^{+}_{\bot}$ is empty.
-Then the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the formula (11) from the paper \cite{ilyin812pbc}.
 \begin{comment}
@@
 
-Consider for example regular embedding of $A_1\subset B_2$ ($su(2)\subset so(5)$).
+Consider for instance regular embedding of $A_1\subset B_2$ ($su(2)\subset so(5)$).
 
@@
 We then drop central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
-\begin{comment}
-  Add the embedding index to the definitions
-\end{comment}
+
 In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $su(p)\subset su(p)\oplus su(q)\subset $
@@
 \end{comment}
+
+Now we look at the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-module with the highest weight $\mu$. For the character of this module we get
+\begin{equation}
+  \label{eq:41}
+  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
+\end{equation}
+
+If we consider the projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ it will give us the single exponent $e^{\pi_{\mathfrak{a}}\cdot\mu}$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to the root system of $\mathfrak{a}$.
+
+Using this idea we reorganize the expression for the character of $\mathfrak{g}$-module into the sum over $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules in the following way.
 
@@
 These dimensions of the modules could be easily calculated using the Weyl formula.
-\begin{comment}
-  Rewrite it, so that the following paragraph begins the computation
-\end{comment}
-This explicit calculation to get the character of the $\mathfrak{a}_{\bot}$ representation can be thought as the calculation of the character of the $\mathfrak{a}_{\bot}\oplus \mathfrak{h}$-module with the highest weight $\omega(\mu+\rho)$, where $\mathfrak{h}$ is the Cartan subalgebra of $\mathfrak{g}$.
 
@@
 So we have obtained recurrent relation for the anomalous branching coefficients.
+
+If the set $\Delta_{\bot}^{+}$ is empty the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the following formula (11) \eqref{eq:40} from the paper \cite{ilyin812pbc}
+\begin{equation}
+  \label{eq:40}
+  k_{\xi }^{\left( \mu \right) }=-\sum_{\omega\in W\setminus e} \epsilon(\omega)\, k^{(\mu)}_{\xi-\pi_{\mathfrak{a}}\circ (\omega\circ \rho - \rho)} +
+  \sum_{\omega\in W,\; \nu\in W_{\mathfrak{a}}} \epsilon(\omega)\epsilon(\nu)\delta_{\pi_{\mathfrak{a}}\circ (\omega\circ (\mu+\rho)-\rho),\xi+\rho_{\mathfrak{a}}-\nu\circ \rho_{\mathfrak{a}}}
+\end{equation}
+
   In the next section we describe the algorithm for the computation of branching coefficients using the relation \eqref{recurrent relation}.

### 2009-12-08 AffineLieAlgebras/InformalNotes/article.tex
Added some text on the construction of $\mathfrak{a}_{\bot}$

@@
 If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta^{+}_{\bot}$ is empty.
-\begin{comment}
-  Analyze all the regular embeddings and show when there exist orthogonal roots 
-\end{comment}
-Non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
+On the other hand 
+non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
 Also the maximal regular embeddings are constructed by the exclusion of one or two roots from the extended Dynkin diagram of the algebra.
@@
 
-Consider for instance regular embedding of $A_1\subset B_2$ ($su(2)\subset so(5)$).
+Consider for instance regular embedding of $A_1\subset B_2$.
 
@@
 
-In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $su(p)\subset su(p)\oplus su(q)\subset $
-\begin{comment}
-  Add here the example
-\end{comment}
+Note that when we study the regular embedding obtained by the dropping of the nodes of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the subalgebra $\mathfrak{a}$ is one of the connected components, the subalgebra $\mathfrak{a}_{\bot}$ may be broader than the algebra generated by the other connected components.
+See for example the figure \ref{fig:dynkin} for the embedding of $B_2\subset B_4$.
+In this case the extended Dynkin diagram of $B_4$ is broken by the dropping of simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras.
+But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to $A_1\oplus A_1$ but to $B_2$.
+This fact is due to the existence of positive root $e_2=s_{\alpha_2}\cdot s_{\alpha_3}\cdot\alpha_4$ in the root system of $B_4$.
+
+In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows.
+Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$.
+This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such a subgroups.
+
+In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
+\begin{figure}[ph]
+  \centering
+  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
+  \caption{Special embedding $A_1\subset A_2\subset A_3$.\\ Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, \\dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
+  \label{fig:a1a2a3}
+\end{figure}
+
+The construction of the subalgebra $\mathfrak{a}_{\bot}$ is not obvious from the Dynkin diagrams of $\mathfrak{g}$ and $\mathfrak{a}$ but for the needs of calculation of the branching coefficients $b^{(\mu)}_{\nu}$ it is sufficient to select the positive roots $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$ in the set of positive roots of $\mathfrak{g}$.
 
@@
   \label{eq:22}
-  (0,1),\; (1,2),\; (2,-1)
+  (1,2),\; (2,-1)
 \end{equation}
@@
   \label{eq:23}
-  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0}_1 - 3\cdot \delta_{0,0} = 1
+  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1
 \end{equation}

### 2009-12-08 AffineLieAlgebras/InformalNotes/article.tex
Some work with the placement of the pictures.

@@
 In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
-\begin{figure}[ph]
-  \centering
-  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
-  \caption{Special embedding $A_1\subset A_2\subset A_3$.\\ Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, \\dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
+\begin{figure}[bh]
+\noindent  \centering{
+  \includegraphics[width=90mm]{special_A1_A2_A3.pdf}
+  \caption{Special embedding $A_1\subset A_2\subset A_3$.
+Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
+}
   \label{fig:a1a2a3}
@@
 Here the second component denotes the value of $s(\gamma)$.
-\begin{comment}
-  It seems that here $\Gamma$ should include only two points. Is it true?
 
-  Think of the pictures more.
-\end{comment}
 Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent relation}) gives us
@@
 So we have computed the branching coefficients.
+\newpage
 \subsubsection{Embedding of $B_2$ into $B_4$}
@@
 Using the definition (\ref{fan-defined}) we get the following set of
-the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$
+the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
 \begin{figure}[h]
@@
 
-\begin{comment}
-  Change ``enveloping'' into something better.
-\end{comment}
-Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory.
+Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for the original and the embedded theory.
 

### 2009-12-08 AffineLieAlgebras/InformalNotes/article.tex
The definitions of the objects are added after the first introduction of the recurrent relation

@@
 
-Here we present the final recurrent relation for the anomalous branching coefficients \eqref{eq:21}. 
+We present the final recurrent relation for the anomalous branching coefficients \eqref{eq:21}. 
 \begin{equation}
@@
 \end{equation}
-The proof of the formula and definitions of $\mathfrak{a}_{\bot},\; W_{\bot},\; s(\gamma),\; \Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ are in the following subsection.
+Here $\mathfrak{a}_{\bot}$ is the subalgebra generated by the roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group, $\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$ is the coefficient of $e^{\gamma}$ in this expansion.
+The proof of the formula and more formal definitions of $\mathfrak{a}_{\bot},\; W_{\bot},\; s(\gamma),\; \Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ are in the following subsection.
 
 In the next section we describe the algorithm for the computation of branching coefficients based upon this formula and then present some example and discuss physical meaning.
-\begin{comment}
-  Fix the relation so that the definitions are available for the reader.
-\end{comment}
+
 \subsection{Proof of the recurrent relation}

### 2009-12-10 AffineLieAlgebras/InformalNotes/article.tex
Analysis of a_{\bot} for the embeddings a\subset g is almost completed, I need to add only a table.

@@
 \begin{document}
-\title{\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}}
+\title{\textbf{{\Large {Recursive algorithm for the computation of branching coefficients of affine Lie algebras with applications in CFT}}}}
 \author{Vladimir Lyakhovsky\\
@@
 
+\newpage
 \section{Introduction}
@@
   \centering
-  \includegraphics[width=40mm]{B2_A1_diagram.pdf}
+  \includegraphics[width=50mm]{B2_A1_diagram.pdf}
   \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
@@
 
+Here we give the simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for the regular embedding $\mathfrak{a}\subset \mathfrak{g}$ for simple $\mathfrak{a}$ and $\mathfrak{g}$.
+If Dynkin diagram of $\mathfrak{g}$ can be split into the unconnected diagrams of $\mathfrak{a}$ and some other subalgebras $\{\mathfrak{\bar{a}}_j\}$ then the subset $\Delta_{\bot}$ is non-empty, subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the $\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.
+
 Note that when we study the regular embedding obtained by the dropping of the nodes of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the subalgebra $\mathfrak{a}$ is one of the connected components, the subalgebra $\mathfrak{a}_{\bot}$ may be broader than the algebra generated by the other connected components.
 See for example the figure \ref{fig:dynkin} for the embedding of $B_2\subset B_4$.
-In this case the extended Dynkin diagram of $B_4$ is broken by the dropping of simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras.
+In this case the extended Dynkin diagram of $B_4$ is split by dropping of simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras.
 But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to $A_1\oplus A_1$ but to $B_2$.
@@
 
+We should analyze the case when the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$ for the simple Lie algebras $\mathfrak{a},\,\mathfrak{g}$ and the regular embedding $\mathfrak{a}\subset \mathfrak{g}$.
+ We drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the rest nodes of the diagram of $\mathfrak{g}$ and consider the remaining diagram.
+This diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ of $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$.
+It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$.
+So the question is if $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them.
+It is possible when the set of the angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we the additional roots of $\mathfrak{a}_{\bot}$.
+
+All the cases are listed in the following table.
+
+\begin{tabular}{|l|l|}
+
+\end{tabular}
+
 In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows.
-Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$.
+Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$.
 This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such a subgroups.
@@
 In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
-\begin{figure}[bh]
+\begin{figure}[ph]
 \noindent  \centering{
-  \includegraphics[width=90mm]{special_A1_A2_A3.pdf}
+  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
   \caption{Special embedding $A_1\subset A_2\subset A_3$.

### 2009-12-15 AffineLieAlgebras/InformalNotes/article.tex
Table with the analysis of the suablgebras added

@@
 All the cases are listed in the following table.
-
-\begin{tabular}{|l|l|}
-
+\begin{figure}[ph]
+\label{fig:table}
+\noindent  \centering{
+\begin{tabular}{|l|l|l|l|}
+  \hline
+  $\mathfrak{g}$ & Extended diagram of the algebra $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
+  \hline
+  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
+  \hline
+  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\  
+  \hline
+  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
+  \hline
+  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
+  \hline
 \end{tabular}
-
+\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
+\end{figure}
 In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows.

### 2009-12-16 AffineLieAlgebras/InformalNotes/article.tex
Added one paper to the bibliography

@@
 
-All the cases are listed in the following table.
-\begin{figure}[ph]
-\label{fig:table}
+All the cases are listed in the table \ref{tab:diagrams}.
+\begin{table}[ph]
+\label{tab:diagrams}
 \noindent  \centering{
@@
 \caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
-\end{figure}
+\end{table}
 In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows.

### 2009-12-17 AffineLieAlgebras/InformalNotes/article.tex
More work on special embeddings. Simplier example of conformal embedding is proposed.

@@
 \end{table}
+
+The exceptional Lie algebras require tedious case-by-case analysis.
+
 In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows.
@@
 \end{figure}
+
+Using the existing classification of maximal special subalgebras \cite{dynkin1952semisimple} we immediately have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$ 
+\begin{equation}
+  \label{eq:42}
+  \begin{array}{lll}
+      su(p)\oplus su(q) & \subset su(pq) &\\
+      so(p)\oplus so(q) & \subset so(pq) &\\
+      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
+      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
+      so(p)\oplus so(q) & \subset so(p+q)& \text{for}\;p\;\text{and}\;q\;\text{odd}\\
+  \end{array}
+\end{equation}
+Exceptional Lie algebras and other non-maximal subalgebras require lengthy analysis which is not important for the needs of computation of the branching coefficients.
 
@@
 
-Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first to components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.
+Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.
 
@@
 
+\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
+\label{sec:spec-embedd-hata_1s}
+Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ built as the affine extension of the special embedding $su(2)\subset su(3)$ with the embedding index $x_e=4$.
+The level of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the subalgebra $\tilde{k}=kx_e=4$.
+
+\begin{enumerate}
+\item Construct the set $\Delta^{+}$ of the positive roots of the algebra $\mathfrak{g}$.
+\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of the subalgebra $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
+\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous points of the $\mathfrak{g}$-module $L^{(\mu)}$.
+\item Select those weights $\lambda=\omega(\mu+\rho)$ which lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$.
+Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check if the weight $\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ checking that the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ is non-negative.
+\item For $\lambda=\omega(\mu+\rho),\; \lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
+\item Construct the set $\Gamma$ \eqref{fan-defined}.
+\item Calculate anomalous branching coefficients in the main Weyl
+  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent relation}).
+\end{enumerate}
+
+There exist three level one dominant weights $[1,0,0],\;[0,1,0],\;[0,0,1]$ in the weight space of $\hat{A}_2$.
+It is easy to see that the set $\Delta_{\bot}$ is trivial. 
+\subsubsection{Special embedding $\hat{su}(2)\subset \hat{sp}(4)$.}
+\label{sec:spec-embedd-wideh}
+
 Consider the level ten embedding of the affine $\hat A_1$ into the level one affine $\hat C_2$. 

### 2009-12-20 AffineLieAlgebras/InformalNotes/article.tex
Physical example is completed

@@
 \end{equation}
-Exceptional Lie algebras and other non-maximal subalgebras require lengthy analysis which is not important for the needs of computation of the branching coefficients.
+It is also possible to study regular subalgebras of this special subalgebras and get new non-maximal special embeddings, such as the special embedding at the Figure \ref{fig:a1a2a3}, with the orthogonal subalgebra obtained by the combination of \eqref{eq:42} and Table \ref{tab:diagrams}.
+
+Exceptional Lie algebras subalgebras require lengthy analysis which is not important for the needs of computation of the branching coefficients.
 
@@
 
-Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.
+Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is is the level of the weight and the fourth the grade.
 
@@
 
-\begin{enumerate}
-\item Construct the set $\Delta^{+}$ of the positive roots of the algebra $\mathfrak{g}$.
-\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of the subalgebra $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous points of the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item Select those weights $\lambda=\omega(\mu+\rho)$ which lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$.
-Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check if the weight $\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ checking that the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ is non-negative.
-\item For $\lambda=\omega(\mu+\rho),\; \lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\Gamma$ \eqref{fan-defined}.
-\item Calculate anomalous branching coefficients in the main Weyl
-  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent relation}).
-\end{enumerate}
+There exist three level one dominant weights $[1,0,0],\;[0,1,0],\;[0,0,1]$ in the weight space of $\hat{A}_2$.
+It is easy to see that the set $\Delta_{\bot}$ is empty.
 
-There exist three level one dominant weights $[1,0,0],\;[0,1,0],\;[0,0,1]$ in the weight space of $\hat{A}_2$.
-It is easy to see that the set $\Delta_{\bot}$ is trivial. 
-\subsubsection{Special embedding $\hat{su}(2)\subset \hat{sp}(4)$.}
-\label{sec:spec-embedd-wideh}
+Here we view the representation with the highest weight
+$w_0=(1,0,0)$ in detail.
 
-Consider the level ten embedding of the affine $\hat A_1$ into the level one affine $\hat C_2$. 
-The relation (\ref{eq:33}) and the finite reducibility theorem greatly simplify the calculation with the algorithm \ref{sec:algorithm}, since we know that there exists only finite number of the non-zero branching coefficients and the maximal grade of this coefficients is restricted.
+The set of the anomalous points of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}.
+We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration.
 
-This affine embedding is the affine extension of the special embedding $A_1\subset C_2$ with the embedding index equal to 10.
+\begin{figure}[h!tb]
+  \includegraphics[width=160mm]{AffineA2_A1_anom.pdf}
+  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{A_2}$}
+  \label{fig:affine_A2_anom_point}
+\end{figure}
+
+As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+The result of this computation up to the twelfth grade is presented at the Figure
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
+  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \label{fig:AffineA2_A1_anom_proj}
+\end{figure}
+
+Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
+
+Using the definition (\ref{fan-defined}) we get the following set of
+the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineA2A1Fan}.
+Here we restricted the computation to the twelfth grade.
+\begin{figure}[ph]
+  \centering
+  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
+  \caption{Fan for $\hat{A_1}\subset \hat{A_2}$}
+  \label{fig:AffineA2A1Fan}
+\end{figure}
+
+Using the recurrent relation for the anomalous branching coefficients we get the following result
+\begin{figure}[ph]
+  \centering
+  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
+  \label{fig:AffineA2_A1_branching}
+\end{figure}
+
+We see that only two anomalous branching coefficients inside the main
+Weyl chamber of $\hat{A}_1$ are non-zero and equal to the branching
+coefficients. So the finite reducibility theorem holds and we get
+\begin{equation}
+  \label{eq:43}
+  L^{[1,0,0]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[0,4]}\oplus L_{\hat{A_1}}^{[4,0]}
+\end{equation}
+
+For the other level one dominant weights of $\hat{A}_2$ we get trivial
+branching rules
+\begin{eqnarray}
+  \label{eq:44}
+   L^{[0,1,0]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[2,2]}\\
+   L^{[0,0,1]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[2,2]}
+\end{eqnarray}
+
+Using this result we can construct modular-invariant partition function
+\begin{equation}
+  \label{eq:45}
+  Z=\left|\chi_{[4,0]}+\chi_{[0,4]}\right|^2+2\chi_{[2,2]}^2
+\end{equation}
+
+%%  \subsubsection{Special embedding $\hat{su}(2)\subset \hat{sp}(4)$.}
+%%  \label{sec:spec-embedd-wideh}
+%%  
+%%  Consider the level ten embedding of the affine $\hat A_1$ into the level one affine $\hat C_2$. 
+%%  The relation (\ref{eq:33}) and the finite reducibility theorem greatly simplify the calculation with the algorithm \ref{sec:algorithm}, since we know that there exists only finite number of the non-zero branching coefficients and the maximal grade of this coefficients is restricted.
+%%  
+%%  This affine embedding is the affine extension of the special embedding $A_1\subset C_2$ with the embedding index equal to 10.
 The projection of the weights of algebra $C_2$ is calculated using the projection matrix $\mathcal{P}=(3,4)$.
 The embedding index
-\begin{equation}
-  \label{eq:37}
-  x_e=\frac{\left|\mathcal{P}\Theta_{\mathfrak{g}}\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}=\frac{k_{\mathfrak{a}}}{k_{\mathfrak{g}}}=10
-\end{equation}
-If we consider this embedding in the orthogonal basis where the simple roots of $C_2$ are given by
-\begin{equation}
-  \label{eq:38}
-  \alpha_1=(1,-1),\quad \alpha_2=(0,2),
-\end{equation}
-then the simple root of the embedded $A_1$ is equal to
-\begin{equation}
-  \label{eq:39}
-  \beta=\sqrt{\frac{2}{5}}(3,1)
-\end{equation}
-It is easy to see that the set $\Delta^{+}_{\bot}$ of the $C_2$ roots orthogonal to $\beta$ is empty.
-
-Now we proceed the computation of the branching coefficients using the algorithm \ref{sec:algorithm}. 
-On the level 1 there exist three dominant weights with Dynkin labels $[1,0,0], \; [0,1,0],\; [0,0,1]$.
-
-\begin{comment}
-  Do the calculation, show the restriction on the grade and the final result
-  \begin{equation}
-    \label{eq:35}
-    Z=\left|\chi_{[10,0]}+\chi_{[4,6]}\right|^2+\left|\chi_{[7,3]}+\chi_{[3,7]}\right|^2+\left|\chi_{[6,4]}+\chi_{[0,10]}\right|^2
-  \end{equation}
-\end{comment}
-
+%%  \begin{equation}
+%%    \label{eq:37}
+%%    x_e=\frac{\left|\mathcal{P}\Theta_{\mathfrak{g}}\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}=\frac{k_{\mathfrak{a}}}{k_{\mathfrak{g}}}=10
+%%  \end{equation}
+%%  If we consider this embedding in the orthogonal basis where the simple roots of $C_2$ are given by
+%%  \begin{equation}
+%%    \label{eq:38}
+%%    \alpha_1=(1,-1),\quad \alpha_2=(0,2),
+%%  \end{equation}
+%%  then the simple root of the embedded $A_1$ is equal to
+%%  \begin{equation}
+%%    \label{eq:39}
+%%    \beta=\sqrt{\frac{2}{5}}(3,1)
+%%  \end{equation}
+%%  It is easy to see that the set $\Delta^{+}_{\bot}$ of the $C_2$ roots orthogonal to $\beta$ is empty.
+%%  
+%%  Now we proceed the computation of the branching coefficients using the algorithm \ref{sec:algorithm}. 
+%%  On the level 1 there exist three dominant weights with Dynkin labels $[1,0,0], \; [0,1,0],\; [0,0,1]$.
+%%  
+%%  \begin{comment}
+%%    Do the calculation, show the restriction on the grade and the final result
+%%    \begin{equation}
+%%      \label{eq:35}
+%%      Z=\left|\chi_{[10,0]}+\chi_{[4,6]}\right|^2+\left|\chi_{[7,3]}+\chi_{[3,7]}\right|^2+\left|\chi_{[6,4]}+\chi_{[0,10]}\right|^2
+%%    \end{equation}
+%%  \end{comment}
+%%  
 \section{Conclusion}

### 2009-12-25 AffineLieAlgebras/InformalNotes/article.tex
test
Added V.D. notes

--- 2009-12-17 AffineLieAlgebras/InformalNotes/article.tex
@@
 \theoremstyle{definition} \newtheorem{Def}{Definition}
-%\usepackage{verbatim} 
-\newenvironment{comment}
-{\par\noindent{\bf TODO}\\}
-{\\\hfill$\scriptstyle\blacksquare$\par}
 
 \begin{document} 
-\title{\textbf{{\Large {Recursive algorithm for the computation of branching coefficients of affine Lie algebras with applications in CFT}}}}
-\author{Vladimir Lyakhovsky\\
+\thispagestyle{empty}
+
+\begin{center}
+{\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
+\end{center}
+\vskip 1 cm
+\begin{flushright}
+{\large \bf SPbU-IP-09-0?}
+\end{flushright}
+\hfill {}
+\vskip 1 cm
+\begin{center}
+{\Huge \bf Recursive algorithms, branching coefficients \\ for affine algebras and applications\\[0.5cm]
+}
+\end{center}
+\vskip 1.0 cm
+\begin{center}
+{\Large \bf
+Vladimir Lyakhovsky\\[2mm]
+Anton Nazarov}
+\end{center}
+\vfill
+\begin{center}
+{\large Department of Theoretical Physics\\
+}
+\end{center}
+\vfill
+\begin{center}
+SAINT-PETERSBURG \\
+2009
+\end{center}
+
+\newpage
+
+\title{\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}}
+\author{Vladimir Lyakhovsky \thanks{ Supported by 
+ RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
 Theoretical Department, SPb State University,\\
@@
 e-mail:lyakh1507@nm.ru \\
-[5mm] Anton Nazarov \\
-%EndAName
+[5mm] Anton Nazarov \thanks{ Supported by
+the National Project RNP.2.1.1./1575 }\\
 Theoretical Department, SPb State University,\\
 198904, Sankt-Petersburg, Russia \\
-e-mail:antonnaz@gmail.com\\
+e-mail:antonnaz@gmail.com
 }
@@
 \begin{abstract}
-  We present the recurrent relation for the branching coefficients of affine Lie algebras. Then we describe the algorithm for the decomposition of  integrable highest weight modules
-of a simple Lie algebra with respect to its reductive subalgebra which is based upon this recurrent relation and present some examples.
-Also we discuss the appearance of branching coefficients in the physical models.
+  Recurrent relations for branching coefficients in affine Lie algebras highest weight modules are studied.
+The decomposition algorithm for  integrable highest weight modules reduction based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive  subalgebra.
+We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original one.
+The possible applications of subtracted fans in CFT models are considered.
 \end{abstract}
@@
 
-The problem of the reduction of Lie algebra representation to the representations of the subalgebra is studied for several decades and has various applications in physics.
-In the context of finite-dimensional algebras it is important for the study of great unification models whilst the problem of the branching of the affine Lie algebras emerges in conformal field theory, for example, in the construction of the modular-invariant partition functions \cite{difrancesco1997cft}.
+The problem of reduction of a Lie algebra representation to a  subalgebra is studied for several decades and has various applications in physics.
+In the context of finite-dimensional algebras it is important for the study of great unification models whilst the branching problem for affine Lie algebras emerges in conformal field theory, for example, in the construction of the modular-invariant partition functions \cite{difrancesco1997cft}.
 
-There exist several approaches to the computation of the branching coefficients which use the BGG
+There exist several approaches to the computation of the branching coefficients. Some of them use the BGG
 resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in 
@@
 
-Usually only the embedding of the maximal reductive subalgebras is considered since the case of non-maximal subalgebra can be obtained using the chain of maximal subalgebras.
-In this paper we present the recurrent formula for the branching coefficients which generalises the recurrent relation of the paper \cite{ilyin812pbc} to the case of non-maximal reductive subalgebra.
-Using this relation we formulate simple explicit algorithm for the computation of the branching coefficients which is applicable to the non-maximal subalgebras of finite-dimensional and affine Lie algebras.
+Usually only the embedding of the maximal reductive subalgebras is considered since the case of non-maximal subalgebra can be obtained using the chain of maximal injections.
+In this paper we study the recurrent properties for branching coefficients which generalise the recurrent relations obtained earlier (see the paper \cite{ilyin812pbc}and the references therein) to the cases of non-maximal reductive subalgebras.
+The result is formulated by an introduction of a new injection fan called "subtracted fan".
+Using this new tools we formulate simple and explicit algorithm for the computation of branching coefficients which is applicable to the non-maximal subalgebras of finite-dimensional and affine Lie algebras.
 
-We show that our algorithm can be used in the study of the conformal embeddings where the central charge of the conformal field theory is preserved, but the computation in this case is simplified using physical requirements.
+We show that our algorithm can be used in a study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified taking into account some  physical limitations.
 
 The paper is organised as follows.
-In the next subsection of the introduction we fix the notation used throughout the paper.
-Then in Section \ref{sec:recurr-form-branch} we derive the central recurrent formula for the anomalous branching coefficients and describe the algorithm for the decomposition of the integrable highest weight modules of algebra $\mathfrak{g}$ to the modules of a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}).
-In the next Section \ref{sec:examples} we present several examples and discuss some applications in the physical models (s.
+In the next subsection  we fix the notations used throughout the paper.
+In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules of algebra $\mathfrak{g}$ with respect to a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}).
+In the next Section \ref{sec:examples} we present several examples and discuss some applications in CFT models (s.
 \ref{sec:phys-appl}).
-We conclude the paper with the review of results and discussion of possible future developments (s.
+We conclude the paper with a review of obtained results.
+Possible future developments are discussed (s.
 \ref{sec:conclusion}).
@@
 
-\section{Recurrent relation for branching coefficients}
+\section{Recurrent relation for branching coefficients. Singularities and subtractions}
 \label{sec:recurr-form-branch}
 
-We present the final recurrent relation for the anomalous branching coefficients \eqref{eq:21}. 
+Our aim is to demonstrate that despite possible singularities in the Weyl denominator projected to the subalgebra root space injection fan technique can be properly modified.
+as a result of such modification the generalized recurrent relations for anomalous branching coefficients \eqref{eq:21} will appear in the following form:
 \begin{equation}
   \label{eq:1}
+  \begin{array}{c}
       k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-\sum_{\gamma \in
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
+\left.
++\sum_{\gamma \in
 \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
 +\gamma }^{\left( \mu \right) }\right)
+  \end{array}
    \end{equation}
-Here $\mathfrak{a}_{\bot}$ is the subalgebra generated by the roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group, $\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$ is the coefficient of $e^{\gamma}$ in this expansion.
-The proof of the formula and more formal definitions of $\mathfrak{a}_{\bot},\; W_{\bot},\; s(\gamma),\; \Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ are in the following subsection.
+Here $\mathfrak{a}_{\bot}$ is the subalgebra generated by the roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group, $\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion of the denominator $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$ is the coefficient of $e^{\gamma}$ in this expansion.
+In the next subsection we study the situation in details and prove the validity of this relation.
 
-In the next section we describe the algorithm for the computation of branching coefficients based upon this formula and then present some example and discuss physical meaning.
+In the next section we  shall describe the  computational algorithm for  branching coefficients based on this formula and present some examples.
 
@@
 
-The decomposition of the representation of the algebra to the representations of the subalgebra can be symbolically written using formal characters and projection operator $\pi_{\mathfrak{a}}$ to the weight subspace:
+The branching of a module can be symbolically written using formal characters and projection operators $\pi_{\mathfrak{a}}$ that bring the roots of $\mathfrak{g}$ to the weight subspace of $\mathfrak{a}$:
 \begin{equation}
@@
 \end{equation}
-Using the Weyl-Kac formula for the character of the module
-we obtain the equality
+The Weyl-Kac character formula leads to
+the equality
 \begin{equation}
@@
 
-It is important to mention that the projection of some of the positive roots of the algebra $\mathfrak{g}$ can be equal to zero.
+It is important to keep in mind that the projection of some of positive roots of the algebra $\mathfrak{g}$ can be equal to zero.
 These roots are orthogonal to the root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the algebra $\mathfrak{g}$.
-Let's denote the subset of these roots by $\Delta^{+}_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
+Let's denote the subset of such roots by $\Delta^{+}_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
 
-We should notice that if the set $\Delta^{+}_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
-Consider any two positive roots $\alpha,\; \beta\in \Delta^{+}_{\bot}$ and corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.
+Notice that if the set $\Delta^{+}_{\bot}$ is non-empty the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of the Weyl group $W$.
+Consider any two positive roots $\alpha,\; \beta\in \Delta^{+}_{\bot}$ and the corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.
 Since roots of the subalgebra $\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
@@
 
-The action of the Weyl subgroup $W_{\bot}$ on the set $\Delta^{+}_{\bot}$ produce the root system $\Delta_{\bot}$ which is orthogonal to the root system $\Delta_{\mathfrak{a}}$ of the subalgebra $\mathfrak{a}$.
-This root system can be considered as the root system of some subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
+Thus we have obtained the root system $\Delta_{\bot}$ which is orthogonal to the root system $\Delta_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$ .
+This root system can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
 
-Now we should discuss when the subset $\Delta^{+}_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
+Now we should find out when the subset $\Delta^{+}_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
 
-If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta^{+}_{\bot}$ is empty.
+If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta^{+}_{\bot}$ is empty.
 On the other hand 
 non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
-Also the maximal regular embeddings are constructed by the exclusion of one or two roots from the extended Dynkin diagram of the algebra.
+The maximal regular embeddings are constructed by the exclusion of one or two roots from the extended Dynkin diagram of the algebra.
 Since this process can give us non-connected Dynkin diagrams we can see which roots are orthogonal to the root space of non-maximal regular subalgebra $\mathfrak{a}$.
 
-Consider for instance regular embedding of $A_1\subset B_2$.
+Consider for instance regular the embedding of $A_1\subset B_2$.
 
-The extended Dynkin diagram of $B_2$ 
+The extended Dynkin diagram of $B_2$ is presented in the Figure 1.
 \begin{figure}[ph]
@@
 \end{figure}
-We then drop central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
+When we drop the central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
 
-Here we give the simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for the regular embedding $\mathfrak{a}\subset \mathfrak{g}$ for simple $\mathfrak{a}$ and $\mathfrak{g}$.
-If Dynkin diagram of $\mathfrak{g}$ can be split into the unconnected diagrams of $\mathfrak{a}$ and some other subalgebras $\{\mathfrak{\bar{a}}_j\}$ then the subset $\Delta_{\bot}$ is non-empty, subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the $\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.
+Here we present the simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple.
+If the Dynkin diagram of $\mathfrak{g}$ can be split into the disconnected diagrams of $\mathfrak{a}$ and some other subalgebras $\{\mathfrak{\bar{a}}_j\}$ then the subset $\Delta_{\bot}$ is non-empty, subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the $\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.
 
-Note that when we study the regular embedding obtained by the dropping of the nodes of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the subalgebra $\mathfrak{a}$ is one of the connected components, the subalgebra $\mathfrak{a}_{\bot}$ may be broader than the algebra generated by the other connected components.
+Note that when we study the regular embedding obtained by dropping the nodes of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the subalgebra $\mathfrak{a}$ is one of the connected components, the subalgebra $\mathfrak{a}_{\bot}$ may be broader than the algebra generated by the other connected components.
 See for example the figure \ref{fig:dynkin} for the embedding of $B_2\subset B_4$.
-In this case the extended Dynkin diagram of $B_4$ is split by dropping of simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras.
+In this case the extended Dynkin diagram of $B_4$ is split by dropping the simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras.
 But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to $A_1\oplus A_1$ but to $B_2$.
-This fact is due to the existence of positive root $e_2=s_{\alpha_2}\cdot s_{\alpha_3}\cdot\alpha_4$ in the root system of $B_4$.
+This fact is due to the existence of the positive root $e_2=s_{\alpha_2}\cdot s_{\alpha_3}\cdot\alpha_4$ in the root system of $B_4$.
 
@@
 So the question is if $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them.
-It is possible when the set of the angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we the additional roots of $\mathfrak{a}_{\bot}$.
+It is possible when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.
 
@@
 
-In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows.
+In terms of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows.
 Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$.
-This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such a subgroups.
+This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such subgroups.
 
-In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
+In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the 
+special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
 \begin{figure}[ph]
@@
 
-\subsection{Affine Lie algebras}
-\label{sec:affine-lie-algebras}
-%%  \subsubsection{Embedding of finite-dimensional algebra into affine algebra}
-%%  \label{sec:embedd-finite-dimens}
-%%  
-%%  The maximal embeddings of the finite-dimensional Lie algebras into the affine Lie algebras were thoroughly studied and the tables of the branching coefficients are given in the book \cite{kass1990ala}.
-The task of the study of non-maximal embeddings is then can be reduced to the well-known task of branching of the finite-dimensional Lie algebras.
-%%  Thus here we show the simplest possible example of reduction of affine $\hat{A_1}$ to $A_1$ in order to demonstrate some traits of our method and show that we eliminate the need of slice-by-slice study discussed in \cite{kass1990ala}.
-%%  
-%%  The simple roots for the affine $\hat{A_1}$ are
-%%  \begin{equation}
-%%    \label{eq:2}
-%%    (\alpha,\delta-\alpha)
-%%  \end{equation}
-%%  We consider the embedding with the root $\beta=\delta-\alpha$. 
-%%  
-%%  Positive roots of the $\hat{A_1}$ are $\alpha,\; \alpha+n\delta,\; n\delta,\; -\alpha+n\delta;\; n=1,2,3,\dots$.
-%%  The set of the 
-%%  
-\subsubsection{Embedding of the affine algebra into affine algebra}
-\label{sec:embedd-affine-algebr}
-
-Consider the affine extension of the example \ref{sec:regul-embedd-a_1}. 
-Since this embedding is regular, the level of the representations of the subalgebra is equal to the level of the representation of the algebra.
-
-The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.
-
-Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.
-
-The set of the anomalous points of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.
-
-\begin{figure}[h!tb]
-  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
-  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
-  \label{fig:affine_B2_anom_point}
-\end{figure}
-
-As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
-The result of this computation up to the twelfth grade is presented at the Figure
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
-  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
-  \label{fig:AffineB2_A1_anom_proj}
-\end{figure}
-
-Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
-
-Using the definition (\ref{fan-defined}) we get the following set of
-the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
-Here we restricted the computation to the twelfth grade.
-\begin{figure}[ph]
-  \centering
-  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
-  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
-  \label{fig:AffineB2A1Fan}
-\end{figure}
-
-Also we should mention that the lowest vector of the fan $\gamma_0$ is equal to zero, since we have excluded all the roots of $\Delta^{+}_{\bot}$ from the defining relation (\ref{fan-defined}).
-
-Using the recurrent relation for the anomalous branching coefficients we get the following result
-\begin{figure}[ph]
-  \centering
-  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
-  \label{fig:AffineB2_A1_branching}
-\end{figure}
-
-Selecting the points inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
-\begin{multline}
-  \label{eq:28}
-  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
-    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
-    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
-    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
-    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
-    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
-    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
-    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
-    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
-    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
-    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
-    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
-    1180 L_{\hat{A_1}}^{w_0}(-12)
-\end{multline}
-This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
-\begin{eqnarray}
-  \label{eq:29}
-  \begin{array}{cc}
-    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
-     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
-  \end{array}\\
-  \begin{array}{cc}
-    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
-    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
-  \end{array}
-\end{eqnarray}
-Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
-
 \newpage
@@
 
-\begin{comment}
 Do the calculation, show the restriction on the grade and the final result
@@
   \end{equation}
-\end{comment}
 
@@
 \label{sec:conclusion}
-We have proved the recurrent relation on the branching coefficients and proposed practical algorithm of the reduction of the representations.
-Also we have discussed the application of this algorithm to the physical problem of construction of modular-invariant partition functions in the conformal field theory.
+We have constructed the recurrent relation for branching coefficients and proposed practical algorithm for the reduction procedure.
+Also we have discussed the application of this algorithm to the physical problem of construction the modular-invariant partition functions in the conformal field theory.
 This method of conformal embeddings is well-known but may be actual in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
-\begin{comment}
-  What about acknowledgements? 
-\end{comment}
+
+\section{Acknowledgements}
+The work was supported in
+part by RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575.
+
 \bibliography{article}{}

### 2009-12-25 AffineLieAlgebras/InformalNotes/article.tex
Merge of physical example and notes of Vladimir Dmitrievich

@@
 
+\pagenumbering{arabic}
 \title{\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}}
@@
 
-\newpage
 \section{Introduction}
@@
 
-The extended Dynkin diagram of $B_2$ is presented in the Figure 1.
+The extended Dynkin diagram of $B_2$ is presented in the Figure \ref{fig:B2Dynkin}.
 \begin{figure}[ph]
@@
 So we have computed the branching coefficients.
-\newpage
+
 \subsubsection{Embedding of $B_2$ into $B_4$}
@@
 We show the result of this procedure on the Figure \ref{fig:B4B2anom}.
-\begin{figure}[h]
-    \includegraphics[width=170mm]{B4_B2_anom_points.pdf}
+\begin{figure}[h!tb]
+    \includegraphics[width=130mm]{B4_B2_anom_points.pdf}
   \caption{Anomalous points with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
@@
 the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
-\begin{figure}[h]
-  \includegraphics[width=150mm]{B4_B2_fan.pdf}
+\begin{figure}[h!tb]
+  \includegraphics[width=130mm]{B4_B2_fan.pdf}
   \caption{Fan for $B_2\subset B_4$}
@@
 
-\newpage
+\subsection{Affine Lie algebras}
+\label{sec:affine-lie-algebras}
+\subsubsection{Embedding of the affine algebra into affine algebra}
+\label{sec:embedd-affine-algebr}
+
+Consider the affine extension of the example \ref{sec:regul-embedd-a_1}. 
+Since this embedding is regular, the level of the representations of the subalgebra is equal to the level of the representation of the algebra.
+
+The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.
+
+Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is is the level of the weight and the fourth the grade.
+
+The set of the anomalous points of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.
+
+\begin{figure}[h!tb]
+  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
+  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
+  \label{fig:affine_B2_anom_point}
+\end{figure}
+
+As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+The result of this computation up to the twelfth grade is presented at the Figure
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
+  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \label{fig:AffineB2_A1_anom_proj}
+\end{figure}
+
+Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
+
+Using the definition (\ref{fan-defined}) we get the following set of
+the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
+Here we restricted the computation to the twelfth grade.
+\begin{figure}[ph]
+  \centering
+  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
+  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
+  \label{fig:AffineB2A1Fan}
+\end{figure}
+
+Also we should mention that the lowest vector of the fan $\gamma_0$ is equal to zero, since we have excluded all the roots of $\Delta^{+}_{\bot}$ from the defining relation (\ref{fan-defined}).
+
+Using the recurrent relation for the anomalous branching coefficients we get the following result
+\begin{figure}[ph]
+  \centering
+  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
+  \label{fig:AffineB2_A1_branching}
+\end{figure}
+
+Selecting the points inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
+\begin{multline}
+  \label{eq:28}
+  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
+    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
+    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
+    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
+    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
+    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
+    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
+    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
+    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
+    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
+    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
+    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
+    1180 L_{\hat{A_1}}^{w_0}(-12)
+\end{multline}
+This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
+\begin{eqnarray}
+  \label{eq:29}
+  \begin{array}{cc}
+    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
+     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
+  \end{array}\\
+  \begin{array}{cc}
+    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
+    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
+  \end{array}
+\end{eqnarray}
+Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
+
 \section{Physical applications}
@@
 
-\begin{enumerate}
-\item Construct the set $\Delta^{+}$ of the positive roots of the algebra $\mathfrak{g}$.
-\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of the subalgebra $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous points of the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item Select those weights $\lambda=\omega(\mu+\rho)$ which lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$.
-Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check if the weight $\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ checking that the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ is non-negative.
-\item For $\lambda=\omega(\mu+\rho),\; \lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\Gamma$ \eqref{fan-defined}.
-\item Calculate anomalous branching coefficients in the main Weyl
-  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent relation}).
-\end{enumerate}
+There exist three level one dominant weights $[1,0,0],\;[0,1,0],\;[0,0,1]$ in the weight space of $\hat{A}_2$.
+It is easy to see that the set $\Delta_{\bot}$ is empty.
 
-There exist three level one dominant weights $[1,0,0],\;[0,1,0],\;[0,0,1]$ in the weight space of $\hat{A}_2$.
-It is easy to see that the set $\Delta_{\bot}$ is trivial. 
-\subsubsection{Special embedding $\hat{su}(2)\subset \hat{sp}(4)$.}
-\label{sec:spec-embedd-wideh}
+Here we view the representation with the highest weight
+$w_0=(1,0,0)$ in detail.
 
-Consider the level ten embedding of the affine $\hat A_1$ into the level one affine $\hat C_2$. 
-The relation (\ref{eq:33}) and the finite reducibility theorem greatly simplify the calculation with the algorithm \ref{sec:algorithm}, since we know that there exists only finite number of the non-zero branching coefficients and the maximal grade of this coefficients is restricted.
+The set of the anomalous points of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}.
+We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration.
 
-This affine embedding is the affine extension of the special embedding $A_1\subset C_2$ with the embedding index equal to 10.
-The projection of the weights of algebra $C_2$ is calculated using the projection matrix $\mathcal{P}=(3,4)$.
-The embedding index
+\begin{figure}[h!tb]
+  \includegraphics[width=160mm]{AffineA2_A1_anom.pdf}
+  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{A_2}$}
+  \label{fig:affine_A2_anom_point}
+\end{figure}
+
+As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+The result of this computation up to the twelfth grade is presented at the Figure \ref{fig:AffineA2_A1_anom_proj}
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
+  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \label{fig:AffineA2_A1_anom_proj}
+\end{figure}
+
+Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
+
+Using the definition (\ref{fan-defined}) we get the following set of
+the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:AffineA2A1Fan}.
+Here we restricted the computation to the twelfth grade.
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
+  \caption{Fan for $\hat{A_1}\subset \hat{A_2}$}
+  \label{fig:AffineA2A1Fan}
+\end{figure}
+
+Using the recurrent relation for the anomalous branching coefficients we get the following result
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
+  \label{fig:AffineA2_A1_branching}
+\end{figure}
+
+We see that only two anomalous branching coefficients inside the main
+Weyl chamber of $\hat{A}_1$ are non-zero and equal to the branching
+coefficients. So the finite reducibility theorem holds and we get
 \begin{equation}
-  \label{eq:37}
-  x_e=\frac{\left|\mathcal{P}\Theta_{\mathfrak{g}}\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}=\frac{k_{\mathfrak{a}}}{k_{\mathfrak{g}}}=10
+  \label{eq:43}
+  L^{[1,0,0]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[0,4]}\oplus L_{\hat{A_1}}^{[4,0]}
 \end{equation}
-If we consider this embedding in the orthogonal basis where the simple roots of $C_2$ are given by
+
+For the other level one dominant weights of $\hat{A}_2$ we get trivial
+branching rules
+\begin{eqnarray}
+  \label{eq:44}
+   L^{[0,1,0]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[2,2]}\\
+   L^{[0,0,1]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[2,2]}
+\end{eqnarray}
+
+Using this result we can construct modular-invariant partition function
 \begin{equation}
-  \label{eq:38}
-  \alpha_1=(1,-1),\quad \alpha_2=(0,2),
-\end{equation}
-then the simple root of the embedded $A_1$ is equal to
-\begin{equation}
-  \label{eq:39}
-  \beta=\sqrt{\frac{2}{5}}(3,1)
-\end{equation}
-It is easy to see that the set $\Delta^{+}_{\bot}$ of the $C_2$ roots orthogonal to $\beta$ is empty.
-
-Now we proceed the computation of the branching coefficients using the algorithm \ref{sec:algorithm}. 
-On the level 1 there exist three dominant weights with Dynkin labels $[1,0,0], \; [0,1,0],\; [0,0,1]$.
-
-Do the calculation, show the restriction on the grade and the final result
-  \begin{equation}
-    \label{eq:35}
-    Z=\left|\chi_{[10,0]}+\chi_{[4,6]}\right|^2+\left|\chi_{[7,3]}+\chi_{[3,7]}\right|^2+\left|\chi_{[6,4]}+\chi_{[0,10]}\right|^2
+  \label{eq:45}
+  Z=\left|\chi_{[4,0]}+\chi_{[0,4]}\right|^2+2\chi_{[2,2]}^2
 \end{equation}

### 2010-01-01 AffineLieAlgebras/InformalNotes/article.tex
Preprint number added
Misspelling fixed
Added V.D. notes

@@
 \usepackage{cmap}
+\usepackage{color}
 \usepackage[pdftex]{graphicx}
@@
 \begin{flushright}
-{\large \bf SPbU-IP-09-0?}
+{\large \bf SPbU-IP-09-08}
 \end{flushright}
@@
 
-We show that our algorithm can be used in a study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified taking into account some  physical limitations.
+We show that our algorithm can be used in a study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some  physical limitations.
 
@@
 
-Our aim is to demonstrate that despite possible singularities in the Weyl denominator projected to the subalgebra root space injection fan technique can be properly modified.
-as a result of such modification the generalized recurrent relations for anomalous branching coefficients \eqref{eq:21} will appear in the following form:
+Our aim is to demonstrate that despite possible singularities arriving in the Weyl denominator
+when it is projected to the subalgebra root space injection fan technique can be properly modified.
+The result of such modification is that the generalized recurrent relations for anomalous branching
+coefficients \eqref{eq:21} must be reformulated in the following form:
 \begin{equation}
@@
    \end{equation}
-Here $\mathfrak{a}_{\bot}$ is the subalgebra generated by the roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group, $\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion of the denominator $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$ is the coefficient of $e^{\gamma}$ in this expansion.
+Here $\mathfrak{a}_{\bot}$ is the subalgebra described by the roots of $\mathfrak{g}$
+orthogonal to the root subsystem of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group,
+$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
+of the denominator $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
+(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
+is the coefficient of $e^{\gamma}$ in this expansion.
 In the next subsection we study the situation in details and prove the validity of this relation.
 
-In the next section we  shall describe the  computational algorithm for  branching coefficients based on this formula and present some examples.
+In the section \ref{sec:algorithm} we  shall describe the  computational algorithm for  branching coefficients
+based on this formula and present some examples.
 
@@
 
-The branching of a module can be symbolically written using formal characters and projection operators $\pi_{\mathfrak{a}}$ that bring the roots of $\mathfrak{g}$ to the weight subspace of $\mathfrak{a}$:
+Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
+projection operators $\pi_{\mathfrak{a}}$ that bring the roots of $\mathfrak{g}$ to the
+weight subspace of $\mathfrak{a}$:
 \begin{equation}
@@
   \Longrightarrow\quad
-  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
+  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
 \end{equation}
@@
   \label{eq:4}
-  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = 
+  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
+  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
   \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
+  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
+  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
+  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
 \end{equation}
 
-It is important to keep in mind that the projection of some of positive roots of the algebra $\mathfrak{g}$ can be equal to zero.
-These roots are orthogonal to the root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the algebra $\mathfrak{g}$.
-Let's denote the subset of such roots by $\Delta^{+}_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
+It is important to keep in mind that the projection of some of positive roots of
+the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the
+root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the
+algebra $\mathfrak{g}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}
+=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
+\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
 
-Notice that if the set $\Delta^{+}_{\bot}$ is non-empty the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of the Weyl group $W$.
-Consider any two positive roots $\alpha,\; \beta\in \Delta^{+}_{\bot}$ and the corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.
-Since roots of the subalgebra $\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
+Notice that if the set $\Delta^{+}_{\bot}$ is non-empty the Weyl reflections
+corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup
+$W_{\bot}$ of the Weyl group $W$. Consider any two positive roots $\alpha,\;
+\beta\in \Delta^{+}_{\bot}$ and the corresponding Weyl reflections
+$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since roots of the subalgebra
+$\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they
+are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
 So the subgroup $W_{\bot}$ preserves the root system of the subalgebra $\mathfrak{a}$.
 
-Thus we have obtained the root system $\Delta_{\bot}$ which is orthogonal to the root system $\Delta_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$ .
-This root system can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
+Thus we have obtained the root system $\Delta_{\bot}$ which is orthogonal to the root
+system $\Delta_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$ . This root system
+can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
 
-Now we should find out when the subset $\Delta^{+}_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
+Now we are to find out when the subset $\Delta^{+}_{\bot}$ is non-empty
+and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
 
-If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta^{+}_{\bot}$ is empty.
+If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then
+the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and
+it is clear that $\Delta^{+}_{\bot}$ is empty.
 On the other hand
-non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
-The maximal regular embeddings are constructed by the exclusion of one or two roots from the extended Dynkin diagram of the algebra.
-Since this process can give us non-connected Dynkin diagrams we can see which roots are orthogonal to the root space of non-maximal regular subalgebra $\mathfrak{a}$.
+non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
+through the chain of maximal embeddings
+$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
+The maximal regular embeddings are constructed by the exclusion of one or two roots
+from the extended Dynkin diagram of the algebra. Since this process can give us
+non-connected Dynkin diagrams we can see which roots are orthogonal to the root
+space of non-maximal regular subalgebra $\mathfrak{a}$.
 
@@
 \end{figure}
-When we drop the central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
+Drop the central node to describe the embedding $A_1\oplus A_1\subset B_2$.
+In this case we have: $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
 
-Here we present the simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple.
-If the Dynkin diagram of $\mathfrak{g}$ can be split into the disconnected diagrams of $\mathfrak{a}$ and some other subalgebras $\{\mathfrak{\bar{a}}_j\}$ then the subset $\Delta_{\bot}$ is non-empty, subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the $\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.
+The simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for a regular
+embedding $\mathfrak{a}\subset \mathfrak{g}$
+when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple can be formulated
+as follows:
+if the Dynkin diagram of $\mathfrak{g}$ can be split into the disconnected
+diagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
+then the subset $\Delta_{\bot}$ is non-empty,
+subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the
+$\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.
 
-Note that when we study the regular embedding obtained by dropping the nodes of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the subalgebra $\mathfrak{a}$ is one of the connected components, the subalgebra $\mathfrak{a}_{\bot}$ may be broader than the algebra generated by the other connected components.
-See for example the figure \ref{fig:dynkin} for the embedding of $B_2\subset B_4$.
-In this case the extended Dynkin diagram of $B_4$ is split by dropping the simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras.
-But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to $A_1\oplus A_1$ but to $B_2$.
-This fact is due to the existence of the positive root $e_2=s_{\alpha_2}\cdot s_{\alpha_3}\cdot\alpha_4$ in the root system of $B_4$.
+Note that when we study the regular embedding obtained by dropping the nodes
+of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the
+subalgebra $\mathfrak{a}$ is one of the connected components,
+the subalgebra $\mathfrak{a}_{\bot}$ may be larger than the algebra
+generated by the remaining connected components.
+Consider for example the embedding of $B_2\subset B_4$ (the figure \ref{fig:dynkin}).
+In this case by eliminating
+the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
+into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
+sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to
+$A_1\oplus A_1$ but to $B_2$ (the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).
 
-We should analyze the case when the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$ for the simple Lie algebras $\mathfrak{a},\,\mathfrak{g}$ and the regular embedding $\mathfrak{a}\subset \mathfrak{g}$.
- We drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the rest nodes of the diagram of $\mathfrak{g}$ and consider the remaining diagram.
+Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$ must not form a direct sum in $\mathfrak{g}$.  
+Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
+ Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the remaining nodes of the diagram of $\mathfrak{g}$.
+Consider the remaining diagram.
 This diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ of $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$.
 It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$.
-So the question is if $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them.
+So the question is whether $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them.
 It is possible when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.
@@
 
-The exceptional Lie algebras require tedious case-by-case analysis.
+In Weyl group terms to construct $\Delta _{\mathfrak{a}_{\bot}} $ means the following: given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}} \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer {\color{red} (not the centralizer?, no proof)} of $W_{\mathfrak{a}}$ in $W$, (such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$  {\color{red}(?) and if so where is the proof?}).
+This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} (but we are unaware of any publication with the exhaustive tables of such subgroups {\color{red}(drop it in the final text?)}).
 
-In terms of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows.
-Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$.
-This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such subgroups.
-
-In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the 
+(In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
 special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
+{\color{red}(This is for us!)})
 \begin{figure}[ph]
@@
 \end{equation}
-Exceptional Lie algebras and other non-maximal subalgebras require lengthy analysis which is not important for the needs of computation of the branching coefficients.
+{\color{blue} Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.}
 
-The construction of the subalgebra $\mathfrak{a}_{\bot}$ is not obvious from the Dynkin diagrams of $\mathfrak{g}$ and $\mathfrak{a}$ but for the needs of calculation of the branching coefficients $b^{(\mu)}_{\nu}$ it is sufficient to select the positive roots $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$ in the set of positive roots of $\mathfrak{g}$.
+{\color{blue} Up to this point we considered the problem of $\mathfrak{a}_{\bot}$-construction given $\mathfrak{a}\in\mathfrak{g}$ for regular injections in terms of Dynkin diagrams.
+When the root systems $ \Delta$ and $\Delta_{\mathfrak{a}}$ are known explicitly all that we need is to select the roots
+$\Delta_{\bot}=\left\{\alpha\in \Delta:\alpha\bot \Delta_{\mathfrak{a}}\right\}$ and correspondingly the positive roots
+$\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$. }
 
-Now we look at the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-module with the highest weight $\mu$. For the character of this module we get
+Now consider the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-module 
+{\color{red} What is $\mathfrak{h}$? If it is the Cartan of $\mathfrak{g}$ then there are too many Cartans! It must be $\mathfrak{h}_{\mathfrak{a}}$.}
+with the highest weight $\mu$. For the character of this module we have
 \begin{equation}
@@
 \end{equation}
+If we perform the projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ this will give us the single element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
 
-If we consider the projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ it will give us the single exponent $e^{\pi_{\mathfrak{a}}\cdot\mu}$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to the root system of $\mathfrak{a}$.
-
-Using this idea we reorganize the expression for the character of $\mathfrak{g}$-module into the sum over $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules in the following way.
-
-We can multiply the equation (\ref{eq:4}) by the term
+Using this property we can reconsider the expression for the $\mathfrak{g}$-module character as the character of the direct sum of $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules.
+Multiply the equation (\ref{eq:4}) by the element
 \begin{equation}
@@
 \end{equation}
-This term is non-zero.
-
-Also we can see that for any formal polynomial or series $Q$
+{\color{red}(This term is non-zero.) --This is for us.}
+{\color{blue}Taking into account that for any formal series $Q$ and the polynomial the projection commutes with the multiplication,
 \begin{equation}
   \label{eq:6}
-  \pi_{\mathfrak{a}} (Q) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(Q\cdot (1-e^{-\alpha})\right)
+  \pi_{\mathfrak{a}} (Q) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(Q\cdot (1-e^{-\alpha})\right),
 \end{equation}
-
-The equation (\ref{eq:4}) takes the form
+we can rewrite the 
+the product of (\ref{eq:4}) and (\ref{eq:5}) in the form:}
 \begin{multline}
@@
 \end{multline}
-The right-hand side of this equation can be reorganised as in the paper \cite{ilyin812pbc}. We introduce the anomalous branching coefficients $k_{\lambda}$.
+The right-hand side of this equation can be reorganised similarly to what was performed in the paper \cite{ilyin812pbc}. Introduce the anomalous branching coefficients $k_{\lambda}$.
 \begin{equation}
@@
 \end{equation}
-Also we extract the common denominator of  the right-hand side of the equation (\ref{eq:7})
+and cancel the denominator in the right-hand side of the equation (\ref{eq:7})
 \begin{multline}
@@
   \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
+  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
     \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
@@
 
-If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.
-
-We have denoted the subalgebra with the root space spanned over the set $\Delta^{+}_{\bot}$ by $\mathfrak{a}_{\bot}$.
+If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of the Weyl group $W$.
+{\color{red} (We have denoted the subalgebra with the root space spanned over the set $\Delta^{+}_{\bot}$ by $\mathfrak{a}_{\bot}$) we are well acquainted with this!}
 

### 2010-01-02 AffineLieAlgebras/InformalNotes/article.tex
Pdf update

@@
 \pagestyle{plain}
+
+%\usepackage{verbatim} 
+\newenvironment{comment}
+{\par\noindent{\bf TODO}\\}
+{\\\hfill$\scriptstyle\blacksquare$\par}
+
 \theoremstyle{definition} \newtheorem{Def}{Definition}
@@
 This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} (but we are unaware of any publication with the exhaustive tables of such subgroups {\color{red}(drop it in the final text?)}).
+
+\begin{comment}
+  We need to proof the following:
+  For the Weyl group $W_{\mathfrak{a}}$ any element $\omega in W$ such that $\omega\cdot W_{\mathfrak{a}} \cdot \omega = W_{\mathfrak{a}}$ has the form $\omega=r_1^{s_1} r_2^{s_2}\dots r_k^{s_k}$ where $r_1\dots r_k$ are the generators corresponding to the nodes of non-connected component if $\mathfrak{g}=A_n, C_n, D_n$.
+  For $\mathfrak{g}=B_n$ there exist additional elements $\{\omega=r_1^{s_1} r_2^{s_2}\dots r_k^{s_k}\cdot r_{k+1}^{s_{k+1}} r_{k+2}^{s_{k+2}}\}$. 
+\end{comment}
 

### 2010-01-07 AffineLieAlgebras/InformalNotes/article.tex
Added some computer-programming related publications.

@@
 
+\newtheorem{statement}{Statement}
 \theoremstyle{definition} \newtheorem{Def}{Definition}
@@
 \end{comment}
+
+For the series $A_n$ the statement has the following form:
+\begin{statement}
+  Consider subalgebra $\mathfrak{a}$ with the simple roots $\{\alpha_i, i=1\dots k,\; k<n\}$.
+Then every root $\alpha\bot \beta\in \Delta_{\mathfrak{a}}$ is the linear combination of the simple roots $\alpha_{k+2}\dots \alpha_n$ or equivalently in the language of Weyl groups, for $\forall \omega\in W: \omega\cdot W_{\mathfrak{a}}\cdot \omega=W_{\mathfrak{a}},\; \omega=r_{k+2}^{s_{k+2}}\dots r_n^{s_n}$, where $\{r_i\}$ are the Weyl reflections corresponding to simple roots $\{\alpha_i\}$.
+
+\end{statement}
+  \begin{proof}
+    Assume the opposite. It is clear that it is enough to check that $r_i\cdot \omega\cdot r_i\neq \omega,\; i=1\dots k$.  
+  \end{proof}
 

### 2010-01-11 AffineLieAlgebras/InformalNotes/article.tex
New improvements from Vladimir Dmitrievich.

@@
 \end{equation}
-If we perform the projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ this will give us the single element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
-
-Using this property we can reconsider the expression for the $\mathfrak{g}$-module character as the character of the direct sum of $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules.
+The projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ gives us the single element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
+
+Using this property we can reconsider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules.
 Multiply the equation (\ref{eq:4}) by the element
@@
 {\color{red}(This term is non-zero.) --This is for us.}
-{\color{blue}Taking into account that for any formal series $Q$ and the polynomial the projection commutes with the multiplication,
+{\color{blue}Taking into account that for any formal series $Q \in {\cal E}$ and the binomial the projection commutes with the multiplication,
 \begin{equation}
@@
 we can rewrite the 
-the product of (\ref{eq:4}) and (\ref{eq:5}) in the form:}
+product of (\ref{eq:4}) and (\ref{eq:5}) in the form:}
 \begin{multline}
@@
 \end{multline}
-The right-hand side of this equation can be reorganised similarly to what was performed in the paper \cite{ilyin812pbc}. Introduce the anomalous branching coefficients $k_{\lambda}$.
+The right-hand side of this equation can be reorganised similarly to what was performed in the paper \cite{ilyin812pbc}, by introducing the anomalous branching coefficients $k_{\lambda}$,
 \begin{equation}
@@
 \end{equation}
-and cancel the denominator in the right-hand side of the equation (\ref{eq:7})
+and simplifying the multiplier:
 \begin{multline}
@@
 {\color{red} (We have denoted the subalgebra with the root space spanned over the set $\Delta^{+}_{\bot}$ by $\mathfrak{a}_{\bot}$) we are well acquainted with this!}
-
-Then we can reorganise the summation on the left-hand side of the equation (\ref{eq:12}) in the following way.
-We consider the factor-group $W_{\bot}\backslash W$ and the left conjugate classes.
-For the class $\tilde{\omega}\in W_{\bot}\backslash W$ we choose the representative $\omega \in \tilde{\omega}$ in such a way that $\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$.
-Then
+Let us reorganise the summation in the left-hand side of (\ref{eq:12}).
+Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that 
+{\color{red} $\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$.
+This is a mistake.
+Such a transformation may not exist.
+We can only insist on } $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
 \begin{multline}
@@
 \end{multline}
-
-We see that the fraction on the right-hand side of the equation looks like the character of some representation of the algebra $\mathfrak{a}_{\bot}$.
-In order to write it explicitly we rewrite $\nu\cdot\omega(\mu+\rho)-\rho$ as
+The fraction in the right-hand side of the equation is similar to the character of some  $\mathfrak{a}_{\bot}$-module.
+Let us rewrite the shifted weights
 \begin{equation}
@@
   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
 \end{multline}
-The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by the unity of the algebra of formal exponents.
-So we have
+The projector $\pi_{\mathfrak{a}}$ transforms the character of the module ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ into an element equal to the dimension of the module multiplied by the unit element {\color{red}" of the algebra of formal exponents" (for us)}:
   \begin{multline}
     \label{eq:15}
-    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
+    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
     \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
   \end{multline}
-These dimensions of the modules could be easily calculated using the Weyl formula.
+{\color{red} These dimensions of the modules could be easily calculated using the Weyl formula. (for us)}
 
@@
   \label{eq:9}
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
   \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
@@
 \end{multline}
-
-We can rewrite the multiplier of the right-hand side as in the paper \cite{ilyin812pbc}.
+Following the transformations performed in \cite{ilyin812pbc} we rewrite the multiplier in the right-hand side:
 \begin{equation}
@@
 
-For the coefficient function $s\left( \gamma \right) $ define $\Phi _{\frak{a%
-}\subset \frak{g}}\subset P_{\frak{a}}$ as its carrier:
+For the coefficient function $s\left( \gamma \right) $ define the carrier $\Phi _{\frak{a%
+}\subset \frak{g}}\subset P_{\frak{a}}$:
 \begin{equation}
@@
 \end{equation}
-\begin{equation}
-\prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})}\left(1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}_{\frak{a}}}\mathrm{\left( \alpha \right) }}=-\sum_{\gamma \in \Phi _{\frak{a}\subset
-\frak{g}}}s\left( \gamma \right) e^{-\gamma }.  \label{fan-d}
-\end{equation}
-
-So we get the equation
+In these terms the equation for the formal elements,
 \begin{multline}
   \label{eq:16}
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
   = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
@@
 \end{multline}
-From the equality of the coefficients of the equal formal exponents we get
+leads to the following equality 
 \begin{equation}
   \label{eq:17}
-   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
    \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\quad \xi\in P_{\mathfrak{a}}
@@
 
-To get the recurrent relation for the anomalous branching coefficients we should use the following procedure, introduced in the paper \cite{ilyin812pbc}.
-
-Let $\gamma
-_{0} $ be the lowest vector with respect to the natural ordering in $%
-\overset{\circ }{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$. Decomposing the defining relation (\ref{fan-d})
+To get the recurrent relations for the anomalous branching coefficients we use the following procedure  (similar to that in \cite{ilyin812pbc}).
+Let $\gamma_{0} $ be the lowest vector with respect to the natural ordering in $%
+\overset{\circ }{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$ and decompose the defining relation (\ref{eq:11}),
 \begin{equation}
@@
 \end{equation}
-in (\ref{eq:17}) we obtain
-
-\begin{equation}
+then the equality (\ref{eq:17}) leads to the desired recurrent  relation for the anomalous branching coefficients:
+\begin{multline}
   k_{\xi }^{\left( \mu \right) }=
@@
     \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+    \right.\\
+    \left. +
     \sum_{\gamma \in \Gamma _{\frak{a}\subset \frak{g}}} s\left( \gamma +\gamma _{0}\right) k_{\xi+\gamma }^{\left( \mu \right) }
@@
 \label{recurrent relation}
-\end{equation}
+\end{multline}
 where the set
@@
 \Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} .
+\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} 
 \label{fan-defined}
 \end{equation}
-
-So we have obtained recurrent relation for the anomalous branching coefficients.
-
-If the set $\Delta_{\bot}^{+}$ is empty the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the following formula (11) \eqref{eq:40} from the paper \cite{ilyin812pbc}
-\begin{equation}
-  \label{eq:40}
-  k_{\xi }^{\left( \mu \right) }=-\sum_{\omega\in W\setminus e} \epsilon(\omega)\, k^{(\mu)}_{\xi-\pi_{\mathfrak{a}}\circ (\omega\circ \rho - \rho)} +
-  \sum_{\omega\in W,\; \nu\in W_{\mathfrak{a}}} \epsilon(\omega)\epsilon(\nu)\delta_{\pi_{\mathfrak{a}}\circ (\omega\circ (\mu+\rho)-\rho),\xi+\rho_{\mathfrak{a}}-\nu\circ \rho_{\mathfrak{a}}}
-\end{equation}
-
-  In the next section we describe the algorithm for the computation of branching coefficients using the relation \eqref{recurrent relation}.
+ was introduced that is called the injection fan.
+
+{\color{red}(If the set $\Delta_{\bot}^{+}$ is empty the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the following formula (11) \eqref{eq:40} from the paper \cite{ilyin812pbc}) This is not true!
+And the formula presented is not the one that was thus generalized.}
+{\color{blue} Now let the set $\Delta_{\bot}^{+}$ be empty.
+There are three different reasons for $\Delta_{\bot}^{+}=0$: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$, ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
+Both the first and the second cases can be treated as corresponding to the trivial orthogonal subalgebra:
+$\mathfrak{a}_{\bot}=0$. In any of these cases instead of the formal characters in the right-hand side of (\ref{eq:13}) we obtain the formal element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$
+In the first two cases (equivalent to $\mathfrak{a}_{\bot}=0$) the projection operator retains its purely geometrical meaning: the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
+It is clear that in any of the three variants the final vector $\pi_{\mathfrak{a}}\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)$ leads to the unit of the formal algebra
+$\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty we get the more simple recurrent relation: 
+\begin{equation}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
+\left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
+\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
++\gamma }^{\left( \mu \right) }\right)   \label{recurrent relation special}
+\end{equation}
+It coinsides with the one obtained in \cite{ilyin812pbc} (formula (16)). }
+
+  In the next section we describe an algorithm for the computation of branching coefficients based on the relation \eqref{recurrent relation}.
 
@@
 
-We use the recurrent relation \eqref{recurrent relation} to formulate the algorithm for recursive computation of the branching coefficients.
-It is important to mention that the computation of the branching coefficients is organised without the  explicit construction of the module $L^{(\mu)}_{\mathfrak{g}}$ and any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
-
-The algorithm is divided into the following steps.
+We use the recurrent relation \eqref{recurrent relation} to formulate an algorithm for recursive computation of the branching coefficients.
+It is important to mention that the computation of the branching coefficients is performed without the  explicit construction of the module $L^{(\mu)}_{\mathfrak{g}}$ and any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
+
+The algorithm contains the following steps.
 \begin{enumerate}
-\item Construct the set $\Delta^{+}$ of the positive roots of the algebra $\mathfrak{g}$.
-\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of the subalgebra $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous points of the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item Select those weights $\lambda=\omega(\mu+\rho)$ which lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$.
-Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check if the weight $\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ checking that the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ is non-negative.
-\item For $\lambda=\omega(\mu+\rho),\; \lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
+\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{a} \subset \mathfrak{g}$.
+\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
+\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
+\item {\color{red}"Select those weights $\lambda=\omega(\mu+\rho)$ which lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$."
+ for  lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$.
+The same mistake!} Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
+\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
 \item Construct the set $\Gamma$ \eqref{fan-defined}.
-\item Calculate anomalous branching coefficients in the main Weyl
+\item Calculate the anomalous branching coefficients in the main Weyl
   chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent relation}).
@@
 
-If we are interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous points up to required grade and use steps 4-7 of the algorithm for each grade.
+If we are interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous weights up to the required grade and use the steps 4-7 of the algorithm for each grade.
 We can also speed up the algorithm by one-time computation of the representatives of the conjugate classes $W_{\bot}\backslash W$.
 
-The next section consists of several examples computed with this algorithm.
+The next section contains several examples computed using this algorithm.
 

### 2010-01-12 AffineLieAlgebras/InformalNotes/article.tex
Proof for $\mathfrak{a}_{\bot}$ using case-by-case analysis.

@@
 
-In Weyl group terms to construct $\Delta _{\mathfrak{a}_{\bot}} $ means the following: given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}} \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer {\color{red} (not the centralizer?, no proof)} of $W_{\mathfrak{a}}$ in $W$, (such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$  {\color{red}(?) and if so where is the proof?}).
-This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} (but we are unaware of any publication with the exhaustive tables of such subgroups {\color{red}(drop it in the final text?)}).
-
-\begin{comment}
-  We need to proof the following:
-  For the Weyl group $W_{\mathfrak{a}}$ any element $\omega in W$ such that $\omega\cdot W_{\mathfrak{a}} \cdot \omega = W_{\mathfrak{a}}$ has the form $\omega=r_1^{s_1} r_2^{s_2}\dots r_k^{s_k}$ where $r_1\dots r_k$ are the generators corresponding to the nodes of non-connected component if $\mathfrak{g}=A_n, C_n, D_n$.
-  For $\mathfrak{g}=B_n$ there exist additional elements $\{\omega=r_1^{s_1} r_2^{s_2}\dots r_k^{s_k}\cdot r_{k+1}^{s_{k+1}} r_{k+2}^{s_{k+2}}\}$. 
-\end{comment}
-
-For the series $A_n$ the statement has the following form:
-\begin{statement}
-  Consider subalgebra $\mathfrak{a}$ with the simple roots $\{\alpha_i, i=1\dots k,\; k<n\}$.
-Then every root $\alpha\bot \beta\in \Delta_{\mathfrak{a}}$ is the linear combination of the simple roots $\alpha_{k+2}\dots \alpha_n$ or equivalently in the language of Weyl groups, for $\forall \omega\in W: \omega\cdot W_{\mathfrak{a}}\cdot \omega=W_{\mathfrak{a}},\; \omega=r_{k+2}^{s_{k+2}}\dots r_n^{s_n}$, where $\{r_i\}$ are the Weyl reflections corresponding to simple roots $\{\alpha_i\}$.
-
-\end{statement}
-  \begin{proof}
-    Assume the opposite. It is clear that it is enough to check that $r_i\cdot \omega\cdot r_i\neq \omega,\; i=1\dots k$.  
-  \end{proof}
+For the algebra $\mathfrak{g}$ from the series $A_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r+1\}$ are $\Delta=\{\alpha_{ i j}= e_i- e_j,\; 1\leq i, j\leq r+1\}$, $\Delta^{+}=\{\alpha_{ij},\; i<j\}$ and the set of simple roots consists of $\alpha_{1,2},\alpha_{2,3},\dots,\alpha_{r,r+1}$.
+So for the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consisting of first $r_{\mathfrak{a}}$ simple roots we get $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{ i j},\; r_{\mathfrak{a}}+1<i,j\leq r+1\}$ and $\mathfrak{a}_{\bot}=A_{r-r_{\mathfrak{a}}-1}$.
+
+For the algebra $\mathfrak{g}$ from the series $B_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;i<j;\; \alpha_{\pm j}=\pm e_{ j},\; 1\leq j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; \alpha_j;\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_r$.
+So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}-1}$.
+Otherwise if $\mathfrak{a}=B_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_r$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
+It is the only case when simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.
+
+For the algebra $\mathfrak{g}$ from the series $C_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;i<j;\; \alpha_{\pm j}=\pm 2e_{ j},\; 1\leq j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; \alpha_j;\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_r$.
+So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=C_{r-r_{\mathfrak{a}}-1}$.
+Otherwise if $\mathfrak{a}=C_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_r$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=C_{r-r_{\mathfrak{a}}}$.
+
+For the algebra $\mathfrak{g}$ from the series $D_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;1\leq i<j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_{r-1,r}$.
+So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=D_{r-r_{\mathfrak{a}}-1}$.
+Otherwise if $\mathfrak{a}=D_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_{r-1,r}$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=D_{r-r_{\mathfrak{a}}}$.
 

### 2010-01-12 AffineLieAlgebras/InformalNotes/article.tex
Coloring discarded.

@@
 
-(In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
+In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
 special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}. 
-{\color{red}(This is for us!)})
 \begin{figure}[ph]
@@
 \end{equation}
-{\color{blue} Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.}
+Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.
 
-{\color{blue} Up to this point we considered the problem of $\mathfrak{a}_{\bot}$-construction given $\mathfrak{a}\in\mathfrak{g}$ for regular injections in terms of Dynkin diagrams.
+Up to this point we considered the problem of $\mathfrak{a}_{\bot}$-construction given $\mathfrak{a}\in\mathfrak{g}$ for regular injections in terms of Dynkin diagrams.
 When the root systems $ \Delta$ and $\Delta_{\mathfrak{a}}$ are known explicitly all that we need is to select the roots
 $\Delta_{\bot}=\left\{\alpha\in \Delta:\alpha\bot \Delta_{\mathfrak{a}}\right\}$ and correspondingly the positive roots
-$\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$. }
+$\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$.
 
-Now consider the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-module 
-{\color{red} What is $\mathfrak{h}$? If it is the Cartan of $\mathfrak{g}$ then there are too many Cartans! It must be $\mathfrak{h}_{\mathfrak{a}}$.}
+Now consider the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$-module 
 with the highest weight $\mu$. For the character of this module we have
@@
 \end{equation}
-{\color{red}(This term is non-zero.) --This is for us.}
-{\color{blue}Taking into account that for any formal series $Q \in {\cal E}$ and the binomial the projection commutes with the multiplication,
+Taking into account that for any formal series $Q \in {\cal E}$ and the binomial the projection commutes with the multiplication,
 \begin{equation}
@@
 we can rewrite the 
-product of (\ref{eq:4}) and (\ref{eq:5}) in the form:}
+product of (\ref{eq:4}) and (\ref{eq:5}) in the form:
 \begin{multline}
@@
 If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of the Weyl group $W$.
-{\color{red} (We have denoted the subalgebra with the root space spanned over the set $\Delta^{+}_{\bot}$ by $\mathfrak{a}_{\bot}$) we are well acquainted with this!}
 Let us reorganise the summation in the left-hand side of (\ref{eq:12}).
-Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that 
-{\color{red} $\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$.
-This is a mistake.
-Such a transformation may not exist.
-We can only insist on } $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
+Consider the factor-space $W_{\bot}\backslash W$.
+For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
 \begin{multline}
@@
 \end{multline}
-The projector $\pi_{\mathfrak{a}}$ transforms the character of the module ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ into an element equal to the dimension of the module multiplied by the unit element {\color{red}" of the algebra of formal exponents" (for us)}:
+The projector $\pi_{\mathfrak{a}}$ transforms the character of the module ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ into an element equal to the dimension of the module multiplied by the unit element:
   \begin{multline}
@@
   \end{multline}
-{\color{red} These dimensions of the modules could be easily calculated using the Weyl formula. (for us)}
 
@@
 
-{\color{red}(If the set $\Delta_{\bot}^{+}$ is empty the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the following formula (11) \eqref{eq:40} from the paper \cite{ilyin812pbc}) This is not true!
-And the formula presented is not the one that was thus generalized.}
-{\color{blue} Now let the set $\Delta_{\bot}^{+}$ be empty.
+Now let the set $\Delta_{\bot}^{+}$ be empty.
 There are three different reasons for $\Delta_{\bot}^{+}=0$: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$, ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
@@
 \end{equation}
-It coinsides with the one obtained in \cite{ilyin812pbc} (formula (16)). }
+It coinsides with the one obtained in \cite{ilyin812pbc} (formula (16)).
 
@@
 \item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item {\color{red}"Select those weights $\lambda=\omega(\mu+\rho)$ which lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$."
- for  lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$.
-The same mistake!} Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
+\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
 \item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.

### 2010-01-14 AffineLieAlgebras/InformalNotes/article.tex
Fixed missed case of $B_r$ subalgebras

@@
 It is the only case when simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.
+There exists the third possibility to get the pair of subalgebras $\mathfrak{a},\mathfrak{a}_{\bot}$ with the regular subalgebra $\mathfrak{a}$ by dropping single node from the extended Dynkin diagram of $B_r$.
+It can be done by taking as the set of simple roots of $\mathfrak{a}$ the set $\{\alpha_{1,-2},\alpha_{1,2},\alpha_{2,-3},\dots,\alpha_{r_{\mathfrak{a}}-1,-r_{\mathfrak{a}}}\}$.
+Then $\mathfrak{a}=D_{r_{\mathfrak{a}}}$, $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
 

### 2010-01-14 AffineLieAlgebras/SchemePrograms/LiterateLie.tex
TeX created

\documentclass[a4paper,10pt]{article}% ===> this file was generated automatically by noweave --- better not edit it
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
\usepackage{ucs}
\usepackage{noweb}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}
%\usepackage{verbatim} 
\newenvironment{comment}
{\par\noindent{\bf TODO}\\}
{\\\hfill$\scriptstyle\blacksquare$\par}

\begin{document}
\nwfilename{LiterateLie.nw}\nwbegindocs{1}\nwdocspar
\title{Finite dimensional Lie algebras}
\author{Anton Nazarov}
\maketitle
\begin{abstract}
  We present concise introduction to the representation theory of finite-dimensional Lie algebras and illustrate it with the computational algorithms implemented in Scheme. 
\end{abstract}
\section{Introduction}
\label{sec:introduction}
Representation theory of finite-dimensional Lie algebras is central to the study of continuous symmetries in physics. This theory is well-understood and there exist standard courses and textbooks on the subject \cite{carter2005lie}, [humphreys]. Nevertheless some problems of the representation theory require extensive computation and no standard textbook on the computational algorithms is known to the author of this notes. There exists a volume \cite{belinfante1989survey}, but it was written in 1970-es and have not been updated since, so its contents are limited to the early approaches and implementations on the old hardware which is unavailable now. Also some progress was made in the computational algorithms of the representation theory since the publication of \cite{belinfante1989survey}. It is important to mention series of papers by Patera et al. (see \cite{moody1982fast} and references therein) and books \cite{kass1990ala}, \cite{bremner1985tables} which introduce new and optimised algorithms although do not discuss the implementations.
There exist several solid implementation of the core algorithms. We want to mention Maple package Coxeter/Weyl \cite{stembridge1995mps} and standalone programs LiE \cite{vanleeuwen1994lsp} and LambdaTensor \cite{fischbacher2002ilp}. These programs are solid and rather fast but have not seen any updates in last several years. Also they are not always convenient to use since they lack graphical user interface and interoperability with the popular programming languages and mathematical programs such as Mathematica, Python or Fortran.
We want to summarise some basic notions and algorithms of representation theory in order to stimulate the emergence of more modern and universal software or at least give some tools to the scientists who by some reasons can not use the existing software.

Our implementation use programming language Scheme and is presented as the Literate program \cite{knuth1992literate}. The choice of the language is due to high portability of its implementations \footnote{There exist Scheme implementations for UNIX, Windows, Linux, Mac OS, Palm OS, Windows CE/Pocket PC/Windows Mobile, Java platform and even micro-controllers, see [some website] for the details}, wide use of Scheme for the teaching \cite{abelson1996structure} and personal preferences of the author.

\section{Lie algebras}
\label{sec:lie-algebras}

\begin{Def}
  {\bf Lie algebra $\mathfrak{g}$} is a linear space with the bilinear operation
  \begin{equation}
    \label{eq:1}
    \left[\;,\;\right]:\mathfrak{g}\otimes \mathfrak{g}\to \mathfrak{g}
  \end{equation}
  with the additional property that Jacoby identity holds
  \begin{equation}
    \label{eq:2}
    [x,[y,z]]+\text{(cyclic permutations)}=0
  \end{equation}
\end{Def}
Lie algebras can be finite- or infinite-dimensional. Finite-dimensional Lie algebras are classified.

We will represent Lie algebra in the code as the object of class {\Tt{}lie-algebra\nwendquote}. We use very simple class system, which is described in the Appendix \ref{sec:object-system}. So {\Tt{}lie-algebra\nwendquote} is really an interface, but since our object system doesn't have interfaces we make it an abstract class and concrete classes such as {\Tt{}semisimple-lie-algebra\nwendquote} inherit it.
Lie algebra is a vector space, so we really should create class for the vector space which contains methods for the change of basis. But for now we use only one standard basis for Lie algebras and {\Tt{}lie-algebra\nwendquote} is the subclass of the most genral class {\Tt{}object\nwendquote}.
\nwenddocs{}\nwbegincode{2}\sublabel{NW1VK18x-4dzmez-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-4dzmez-1}}}\moddef{Lie algebra class .scm~{\nwtagstyle{}\subpageref{NW1VK18x-4dzmez-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
(class 'lie-algebra 'object
       \LA{}Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-4X6QTQ-1}}\RA{})
\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{3}\nwdocspar
We need to add several definitions and describe a structure of Lie algebra in order to discuss fields and methods of {\Tt{}lie-algebra\nwendquote} class.
\begin{Def}
  {\bf Ideal} $\mathfrak{e}\subset\mathfrak{g}$: $[\mathfrak{g},\mathfrak{e}]\subset \mathfrak{e}$
\end{Def}

\begin{Def}
  $\mathfrak{g}$ is a {\bf simple Lie algebra} if $\mathfrak{g}$ has no proper ideal (except $\mathfrak{g}$ and $\left\{0\right\}$).
\end{Def}

\begin{Def}
  A Lie algebra $\mathfrak{g}$ is called {\bf soluble} if $\mathfrak{g}^{(n)}=\left\{0\right\}$, where $\mathfrak{g}^{(n)}=[\mathfrak{g}^{(n-1)},\mathfrak{g}^{(n-1)}]$.
\end{Def}
\begin{Def}
  $\mathfrak{g}$ is semisimple if its maximal soluble ideal $R\subset\mathfrak{g}$ is equal to $\left\{0\right\}$.
\end{Def}
Semisimple Lie algebra is a direct sum of simple Lie algebras.

Since Lie algebra is a linear space, it can be specified by a set of generators $J_a\in \mathfrak{g}$ with the commutation relations $[J_a,J_b]=if_{ab}^cJ_c$. $f_{ab}^c$ are called {\bf structure constants}. The number of generators is equal to the dimension of Lie algebra.

Now we need to discuss internal structre of Lie algebras, which can be representated with the code constructs and used for the study of algebra properties.

\begin{Def}
  {\bf Cartan subalgebra $\mathfrak{h}\subset\mathfrak{g}$} - is the maximal commutative subalgebra of $\mathfrak{g}$. The dimension of the Cartan subalgebra $\mathfrak{h}$ is called {\bf rank} of Lie algebra $\mathfrak{g}$.
\end{Def}
\nwenddocs{}\nwbegincode{4}\sublabel{NW1VK18x-4X6QTQ-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-4X6QTQ-1}}}\moddef{Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-4X6QTQ-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-4dzmez-1}}\nwenddeflinemarkup
`(rank ,(lambda (self)
              (error "Abstract class!")))
`(dimension ,(lambda (self)
              (error "Abstract class!")))
`(cartan-subalgebra ,(lambda (self) 
              (error "Abstract class!")))

\nwused{\\{NW1VK18x-4dzmez-1}}\nwendcode{}\nwbegindocs{5}\nwdocspar
Commutative algebras constitute first concrete class of Lie algebras.
\nwenddocs{}\nwbegincode{6}\sublabel{NW1VK18x-I1QOi-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-I1QOi-1}}}\moddef{Commutative algebra .scm~{\nwtagstyle{}\subpageref{NW1VK18x-I1QOi-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
(class 'commutative-algebra 'lie-algebra
       '(dim 1)
       `(rank ,(lambda (self) (send self 'dim)))
       `(dimension ,(lambda (self) (send self 'dim)))
       `(cartan-subalgebra ,(lambda (self) self)))

;; The constructor
(define (make-commutative-algebra dim)
  (new 'commutative-algebra `(dim ,dim)))
\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{7}\nwdocspar
\begin{comment}
It can be interesting and useful to add a method which show commutation relatons of the algebra in the symbolic form, but this task is left for the future  
\end{comment}
\nwenddocs{}\nwbegindocs{8}\nwdocspar

\section{Semisimple Lie algebras}
\label{sec:semis-lie-algebra}
The structure of simple and semisimple Lie algebras can be encoded by the set of simple roots. 
\nwenddocs{}\nwbegincode{9}\sublabel{NW1VK18x-1QMleH-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1QMleH-1}}}\moddef{Semisimple Lie algebra .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1QMleH-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
(class 'semisimple-lie-algebra 'lie-algebra
       '(simple-roots ())
       \LA{}Semisimple Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1pDr9o-1}}\RA{})
;; The constructor
(define (make-semisimple-lie-algebra simple-roots)
  (new 'semisimple-lie-algebra `(simple-roots ,simple-roots)))

\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{10}\nwdocspar

\subsection{Root systems}
\label{sec:root-systems}
\begin{Def}
  In the {\bf Cartan-Weyl} basis the genrators are constructed as follows.
  First we choose the genrators $H_i\in \mathfrak{h}$ of the Cartan subalgebra. All these generators commute $[H_i,H_j]=0$ and their representations can be diagonalised simultaneously. The remaining generators $E_{\alpha}$ are chosen to be a linear combinations of $J_a$ such that
  \begin{equation}
    \label{eq:4}
    [H_i,E_{\alpha}]=\alpha_i E_{\alpha}
  \end{equation}
  The vector $\alpha=(\alpha_1,\dots,\alpha_r),\; r=rank(\mathfrak{g})$ is called a {\bf root} and the corresponding operator $E_{\alpha}$ is called {\bf ladder operator}.
\end{Def}
The root $\alpha$ maps $H_i$ to the number $\alpha(H_i)=\alpha_i$ hence $\alpha\in \mathfrak{h}^{*}$ - element of the dual to the Cartan subalgebra. The set of all the roos $\alpha$ is denoted by $\Delta=\{\alpha,\; \alpha \text{ - root}\}$. So it is natural for the {\Tt{}lie-algebra\nwendquote} class to have a method which lists all the roots.
\nwenddocs{}\nwbegincode{11}\sublabel{NW1VK18x-1pDr9o-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1pDr9o-1}}}\moddef{Semisimple Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1pDr9o-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1QMleH-1}}\nwenddeflinemarkup
`(rank ,(lambda (self)
    (length (send self 'simple-roots))))

`(cartan-subalgebra ,(lambda (self)
    (make-commutative-algebra (send self 'rank))))
\LA{}Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}\RA{}
\nwused{\\{NW1VK18x-1QMleH-1}}\nwendcode{}\nwbegindocs{12}\nwdocspar
All the roots are the linear combinations of simple roots with the integral coefficients. There exists discrete group of symmetry called {\bf Weyl group} which can be used to produce all the roots from the set of simple roots. 
\begin{Def}
  \label{weyl-group-def}
  {\bf Weyl group $W$} of finite-dimension Lie algebra is a finite reflection group of $\mathfrak{h}^*$ generated by the basic reflections corresponding to the simple roots. 
  Each simple root $\alpha_i$ corresponds to the reflection $r_{i}$ in hyperplane orthogonal to $\alpha$.
  \begin{equation}
    \label{eq:5}
    r_{i}\lambda=\lambda-\frac{(\lambda,\alpha_i)}{(\alpha_i,\alpha_i)}\alpha_i
  \end{equation}
  For $w\in W$ there exists several equivalent realizations of the form $w=r_{i_1}\cdot r_{i_2}\dots r_{i_k},\; i_1\dots i_k=1..r$. The expression of the smallest {\it length} is called {\it reduced}. 
\end{Def}
We will implement represent Weyl group elements as the lists of numbers of basic reflection
\begin{equation}
  \label{eq:6}
  w=r_{i_1}\cdot r_{i_2}\dots r_{i_k} \leftrightarrow (i_1, i_2,\dots,i_k)
\end{equation}
Then we will implement action of Weyl group elements on $\mathfrak{h}^*$ using the recipies from \cite{stembridge2001computational}, \cite{casselman1994machine}, but it will be done in the future. For now we are not implementing abstract construction of Weyl group since it is enough to be able to construct Weyl group orbits of $\mathfrak{h}^*$ elements.

So we need just two following general functions:
\nwenddocs{}\nwbegincode{13}\sublabel{NW1VK18x-10zTlp-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}}\moddef{Functions for root systems .scm~{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
(define (co-root r)
  (div (mul 2 r) (prod r r)))

(define (reflect weight root)
  (sub weight (mul (prod weight (co-root root)) root)))
\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{14}\nwdocspar
Here {\it co-root} $\alpha^{\vee}$ is the element of the dual space $(\mathfrak{h}^*)^*$ which is identified with $\mathfrak{h}^*\approx \mathfrak{h}$ since we have scalar product on $\mathfrak{h}$.

Now we can implement wide range of root system related methods of {\Tt{}semisimple-lie-algebra\nwendquote} class
\nwenddocs{}\nwbegincode{15}\sublabel{NW1VK18x-1H68wy-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{\relax}{NW1VK18x-1H68wy-2}\nwenddeflinemarkup
`(simple-co-roots ,(lambda (self)
              (map co-root (send self 'simple-roots))))
\nwalsodefined{\\{NW1VK18x-1H68wy-2}\\{NW1VK18x-1H68wy-3}\\{NW1VK18x-1H68wy-4}\\{NW1VK18x-1H68wy-5}\\{NW1VK18x-1H68wy-6}}\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{16}\nwdocspar
\begin{Def}
  {\bf Cartan matrix} with the elements
  \begin{equation}
    \label{eq:7}
    a_{ij}=(\alpha_i,\alpha_j^{\vee})=\frac{2(\alpha_i,\alpha_j)}{(\alpha_j,\alpha_j)}
  \end{equation}
  completely determines the set of simple roots and is useful for the classification and compact description of Lie algebras.
\end{Def}
\nwenddocs{}\nwbegincode{17}\sublabel{NW1VK18x-1H68wy-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-2}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-1}{NW1VK18x-1H68wy-3}\nwenddeflinemarkup
`(cartan-matrix
  ,(lambda (self)
     (map (lambda (a)
            (map (lambda (av) (prod a av)) (send self 'simple-co-roots)))
         (send self 'simple-roots))))
\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{18}\nwdocspar
We have already introduced Weyl group of reflections \ref{weyl-group-def}, now we implement procedure which constructs the union of Weyl group orbits of the set of weights.
\nwenddocs{}\nwbegincode{19}\sublabel{NW1VK18x-1H68wy-3}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-3}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-2}{NW1VK18x-1H68wy-4}\nwenddeflinemarkup
`(orbit ,
  (lambda (self weights)
    (let ((addon 
           (filter (lambda (x) (not (element-of-set? x weights)))
                   (fold-right union-set '() 
                               (map (lambda (w)
                                      (map
                                       (lambda (x) (reflect w x))
                                       (send self 'simple-roots)))
                                    weights)))))
      (if (null? addon)
          weights
          (send self 'orbit (union-set weights addon) )))))
\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{20}\nwdocspar
\begin{Def}
  {\bf Fundamental weights} form a basis $w_1,\dots,w_r$ dual to the basis of simple co-roots $\alpha_1^{\vee},\dots,\alpha_r^{\vee}$.
\end{Def}
\nwenddocs{}\nwbegincode{21}\sublabel{NW1VK18x-1H68wy-4}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-4}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-3}{NW1VK18x-1H68wy-5}\nwenddeflinemarkup
`(fundamental-weights
  ,(lambda (self)
     (map (lambda (x)
            (sum (map-n (lambda (y z) (mul y z)) x (send self 'simple-roots))))
          (matrix-inverse (send self 'cartan-matrix)))))
\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{22}\nwdocspar
{\bf Weyl vector} $\rho=\sum_i w_i=\frac{1}{2}\sum_{\alpha\in \Delta^{+}}\alpha$.
\nwenddocs{}\nwbegincode{23}\sublabel{NW1VK18x-1H68wy-5}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-5}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-4}{NW1VK18x-1H68wy-6}\nwenddeflinemarkup
`(rho ,(lambda (self)
         (sum (send self 'fundamental-weights))))

\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{24}\nwdocspar
We can construct the full set of Lie algebra roots using Weyl symmetry.
\nwenddocs{}\nwbegincode{25}\sublabel{NW1VK18x-1H68wy-6}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-6}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-5}{\relax}\nwenddeflinemarkup
`(roots ,(lambda (self)
           (send self 'orbit (send self 'simple-roots))))
\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{26}\nwdocspar

\subsection{Simple Lie algebras}
\label{sec:simple-lie-algebras}

Simple Lie algebras are classified by the use of Dynkin diagrams (which we will draw in the upcoming versions of this program) \cite{carter2005lie}.

Here we explicitly construct simple roots for the classical series of finite-dimensional Lie algebras
\nwenddocs{}\nwbegincode{27}\sublabel{NW1VK18x-379yCw-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-379yCw-1}}}\moddef{Simple Lie algebras .scm~{\nwtagstyle{}\subpageref{NW1VK18x-379yCw-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
(define (make-simple-lie-algebra series rank)
  (define (simple-roots series rank)
    (cond ((eq? series 'A)
           (do ((i 0 (+ i 1))
                (base '()
                      (cons 
                       (do ((j 0 (+ j 1))
                            (v '()
                               (cons
                                (cond ((= j i) 1)
                                      ((= j (+ i 1)) -1)
                                      (else 0))
                                v)))
                           ((> j rank) (reverse v)))
                       base)))
               ((= i rank) (reverse base))))
          ((eq? series 'B)
           (do ((i 0 (+ i 1))
                (base '()
                      (cons 
                       (do ((j 0 (+ j 1))
                            (v '()
                               (cons
                                (cond ((= j i) 1)
                                      ((= j (+ i 1)) -1)
                                      (else 0))
                                v)))
                           ((= j rank) (reverse v)))
                       base)))
               ((= i rank) (reverse base))))
          ((eq? series 'C)
           (do ((i 0 (+ i 1))
                (base '()
                      (cons 
                       (do ((j 0 (+ j 1))
                            (v '()
                               (cons
                                (cond ((and (= i (- rank 1)) (= i j)) 2)
                                      ((= j i) 1)
                                      ((= j (+ i 1)) -1)
                                      (else 0))
                                v)))
                           ((= j rank) (reverse v)))
                       base)))
               ((= i rank) (reverse base))))
          ((eq? series 'D)
           (do ((i 0 (+ i 1))
                (base '()
                      (cons 
                       (do ((j 0 (+ j 1))
                            (v '()
                               (cons
                                (cond ((and (= i (- rank 1)) (= (- i 1) j)) 1)
                                      ((= j i) 1)
                                      ((= j (+ i 1)) -1)
                                      (else 0))
                                v)))
                           ((= j rank) (reverse v)))
                       base)))
               ((= i rank) (reverse base))))))
  (make-semisimple-lie-algebra (simple-roots series rank)))
\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{28}\nwdocspar
\section{Representations}
\label{sec:representations}

\begin{Def}
  {\bf Representation} of Lie algebra $\mathfrak{g}$ on a linear space $L$ is a homomorphism $V:\mathfrak{g}\to Aut L$. It has the property
  \begin{equation}
    \label{eq:3}
    V([g,h])v=V(g)(V(h)v)-V(h)(V(g)v), \;\text{for}\; g,h\in \mathfrak{g};\; v\in L
  \end{equation}
\end{Def}
There exists a classification of finite-dimensional representations of Lie algebras.

For the finite-dimensional representations we introduce abstract class {\Tt{}representation\nwendquote} and concrete class {\Tt{}highest-weight-representation\nwendquote}. Then we can describe  tensor product of two highest weight representations as the object of class {\Tt{}representation\nwendquote} (but not of class {\Tt{}highest-weight-representation\nwendquote}.
\nwenddocs{}\nwbegincode{29}\sublabel{NW1VK18x-2w9Axe-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-1}}}\moddef{Representations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwprevnextdefs{\relax}{NW1VK18x-2w9Axe-2}\nwenddeflinemarkup
(class 'representation 'object
       `(dim ())
       `(multiplicity , (lambda (self weight)
                          (error "Class is abstract!")))
       '(lie-algebra ())
       )
\nwalsodefined{\\{NW1VK18x-2w9Axe-2}}\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{30}\nwdocspar

\nwenddocs{}\nwbegincode{31}\sublabel{NW1VK18x-2w9Axe-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-2}}}\moddef{Representations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwprevnextdefs{NW1VK18x-2w9Axe-1}{\relax}\nwenddeflinemarkup
(class 'highest-weight-representation 'representation
       '(highest-weight ())
       \LA{}Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}\RA{}
       \LA{}Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}\RA{})
`(multiplicity , (lambda (self weight)
\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{32}\nwdocspar
We use the recurrent method of calculation of weight multiplicities described in \cite{lyakhovsky1996rra}, \cite{kulish4sfa}. Weight multiplicities are determined using the set of anomalous points, which is constructed by the code below.
\nwenddocs{}\nwbegincode{33}\sublabel{NW1VK18x-1y2eh2-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}}\moddef{Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2w9Axe-2}}\nwenddeflinemarkup
       `(anomalous-weights , 
         (lambda (self)
           (let* ((algebra (send self 'lie-algebra))
                  (rho (send algebra 'rho)))
             (map (lambda (x)
                    (sub x rho))
                  (send algebra 'orbit (add (send self 'highest-weight) rho))))))
\nwused{\\{NW1VK18x-2w9Axe-2}}\nwendcode{}\nwbegindocs{34}\nwdocspar

\nwenddocs{}\nwbegincode{35}\sublabel{NW1VK18x-46EOV9-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}}\moddef{Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2w9Axe-2}}\nwenddeflinemarkup

\nwused{\\{NW1VK18x-2w9Axe-2}}\nwendcode{}\nwbegindocs{36}\nwdocspar
\section{General outline of the code}
\label{sec:general-outline-code}

The code goes to several files of which {\Tt{}library.scm\nwendquote} is a compatibility layer which consists of auxiliary functions and allows portability between different Scheme implementations on different OS-es and hardware platforms. {\Tt{}library.scm\nwendquote} is described in the appendix \ref{sec:library}.
All the mathematical code which is connected with Lie theory is collected in the file {\Tt{}lie-algebra.scm\nwendquote}.
\nwenddocs{}\nwbegincode{37}\sublabel{NW1VK18x-3yKaW-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-3yKaW-1}}}\moddef{lie-algebra.scm~{\nwtagstyle{}\subpageref{NW1VK18x-3yKaW-1}}}\endmoddef\let\nwnotused=\nwoutput{}\nwstartdeflinemarkup\nwenddeflinemarkup
\LA{}Lie algebra class .scm~{\nwtagstyle{}\subpageref{NW1VK18x-4dzmez-1}}\RA{}
\LA{}Commutative algebra .scm~{\nwtagstyle{}\subpageref{NW1VK18x-I1QOi-1}}\RA{}
\LA{}Semisimple Lie algebra .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1QMleH-1}}\RA{}
\LA{}Functions for root systems .scm~{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}\RA{}
\LA{}Simple Lie algebras .scm~{\nwtagstyle{}\subpageref{NW1VK18x-379yCw-1}}\RA{}
\LA{}Representations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-1}}\RA{}
\nwnotused{lie-algebra.scm}\nwendcode{}\nwbegindocs{38}\nwdocspar
\appendix

\section{Library}
\label{sec:library}
Since one of our target implementations of Scheme is LispMe, which is only partially R4RS-compliant, we create compatibility layer of common functions.
Also this library can be used to port the code for Lie algebras to other Scheme implementations.

\nwenddocs{}\nwbegincode{39}\sublabel{NW1VK18x-15DMjX-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-15DMjX-1}}}\moddef{library.scm~{\nwtagstyle{}\subpageref{NW1VK18x-15DMjX-1}}}\endmoddef\let\nwnotused=\nwoutput{}\nwstartdeflinemarkup\nwenddeflinemarkup
\LA{}Semi-standard Scheme procedures .scm~{\nwtagstyle{}\subpageref{NW1VK18x-16zbNk-1}}\RA{}
\LA{}Sets .scm~{\nwtagstyle{}\subpageref{NW1VK18x-3j9Egk-1}}\RA{}
\LA{}Vector and matrix tools .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2tcrGt-1}}\RA{}
\LA{}LispMe Objects .scm~{\nwtagstyle{}\subpageref{NW1VK18x-26RKW4-1}}\RA{}
\nwnotused{library.scm}\nwendcode{}\nwbegindocs{40}\nwdocspar

\subsection{Commonly used Scheme procedures}
\label{sec:commonly-used-scheme}

\nwenddocs{}\nwbegindocs{41}\nwdocspar
Due to the limitations of Palm OS platform functions such as {\Tt{}map\nwendquote} or {\Tt{}fold-left\nwendquote} in LispMe are in the separate library, which should be loaded by hand. Also function {\Tt{}map\nwendquote} accepts only 1-argument function and list, so we add these functions to our library. 
\nwenddocs{}\nwbegincode{42}\sublabel{NW1VK18x-16zbNk-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-16zbNk-1}}}\moddef{Semi-standard Scheme procedures .scm~{\nwtagstyle{}\subpageref{NW1VK18x-16zbNk-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-15DMjX-1}}\nwenddeflinemarkup
(define nil ())
(define true #t)
(define false #f)

(define (zero? v)
        (= v 0))

(define (map op list)
        (if (null? list) ()
                (cons (op (car list)) (map op (cdr list)))))

(define (map-n op . lists) 
    (define (map-n0 op  lists)
        (if (or (null? lists) (null? (car lists))) '()
        (cons (apply op (map car lists))
                (map-n0 op  (map cdr lists)))))
    (map-n0 op lists))

(define (accumulate op initial sequence)
  (if (null? sequence)
      initial
      (op (car sequence)
          (accumulate op initial (cdr sequence)))))

(define (filter predicate sequence)
  (cond ((null? sequence) ())
        ((predicate (car sequence))
         (cons (car sequence)
               (filter predicate (cdr sequence))))
        (else (filter predicate (cdr sequence)))))

(define (fold-left op initial sequence)
  (define (iter result rest)
    (if (null? rest)
        result
        (iter (op result (car rest))
              (cdr rest))))
  (iter initial sequence))

(define (fold-right op init s) (accumulate op init s))
\nwused{\\{NW1VK18x-15DMjX-1}}\nwendcode{}\nwbegindocs{43}\nwdocspar
We need couple of functions for sets. We represent set as list.
\nwenddocs{}\nwbegincode{44}\sublabel{NW1VK18x-3j9Egk-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-3j9Egk-1}}}\moddef{Sets .scm~{\nwtagstyle{}\subpageref{NW1VK18x-3j9Egk-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-15DMjX-1}}\nwenddeflinemarkup
(define (element-of-set? x set)
  (cond ((null? set) false)
        ((equal? x (car set)) true)
        (else (element-of-set? x (cdr set)))))

(define (adjoin-set x set)
  (if (element-of-set? x set)
      set
      (cons x set)))

(define (intersection-set set1 set2)
  (cond ((or (null? set1) (null? set2)) '())
        ((element-of-set? (car set1) set2)        
         (cons (car set1)
               (intersection-set (cdr set1) set2)))
        (else (intersection-set (cdr set1) set2))))

(define (union-set set1 set2)
        (if (null? set1) set2
                (union-set (cdr set1)
                           (adjoin-set (car set1) set2))
        )
)

\nwused{\\{NW1VK18x-15DMjX-1}}\nwendcode{}\nwbegindocs{45}\nwdocspar

\subsection{Object system}
\label{sec:object-system}

It is natural to represent Lie algebras, root systems and representation as objects, so we need a class system. Since standard Scheme class systems such as TinyCLOS, GOOPS, SOS can not be used on LispMe due to the lack of hygienic macros, we use the minimal class system called LispMeObjects.

Here is the original documentation:
\begin{verbatim}

; Classes

 ; LispMeObjects
 ; http://c2.com/cgi/wiki?LispMeObjects
 ; written by Don Wells
 ; Create a new class with (class name super '(slot value)... '(method function)).
 ; Always use 'object as the super
 ; class at the very least.
 ; a function used as a method 
 ; will take at least one argument 
 ; self, the object that originally
 ; received the method.
 ; Invoke a function by sending the 
 ; name and arguments to an
 ; object. (e.g. (send anObject 'add 'sum 10))
 ; where add is the method and sum and 10
 ; are arguments)
 ; Get the value of a slot by sending
 ; the slot's name.
 ; (e.g. (send anObject 'sum))
 ; Set the value of a slot by sending
 ; the set method defined on object.
 ; (e.g. (send anObject 'set 'sum 20))
 ; Always evaluate (clearClasses) before
 ; doing anything.

 ; an object is (superName (slotname value)... (methodName closure)...)
 ; a class is (className . object)

\end{verbatim}

New classes are created with 
\begin{verbatim}
(class '<classname> '<superclass> (list '<fieldname> <default-value>) ...)
\end{verbatim}
Instances of classes:
\begin{verbatim}
(define <instance-name> (new '<classname> (list '<fieldname> <value>) ...))
\end{verbatim}

\nwenddocs{}\nwbegincode{46}\sublabel{NW1VK18x-26RKW4-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-26RKW4-1}}}\moddef{LispMe Objects .scm~{\nwtagstyle{}\subpageref{NW1VK18x-26RKW4-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-15DMjX-1}}\nwenddeflinemarkup

(define *classes* '())

 (define (clearClasses)
  (set! *classes* 
    `((object #f 
      (set ,setSlot)
      (super
         ,(lambda (self)
            (getClass (car self))))))))

 (define (setSlot self aSlotName aValue)
  (let ((slot (assoc aSlotName (cdr self))))
    (cond
      ((not slot) 
        (set-cdr! self 
          (cons 
            (list aSlotName  aValue) 
            (cdr self))))
      (else
        (set-car! (cdr slot) aValue))))
  aValue)

 (define (getClass aClass)
  (let ((class (assoc aClass *classes*)))
      (cond
        ((not class) #f)
        (else (cdr class)))))

 (define (class aName aSuperName . aDefinition)
  (set! *classes* 
    (cons 
      (cons aName (cons aSuperName aDefinition))
      *classes*))
  aName)

 (define (new aSuperName . args)
  (cons aSuperName args))

 (define (send anObject aMessage . args)
  (sendWithSelf anObject anObject aMessage args))

 (define (sendWithSelf self anObject aMessage args)
  (let 
    ((superName (car anObject))
     (slot (assoc aMessage (cdr anObject))))
    (cond
      (slot (valueOfSlot self slot args))
      ((not superName) #f)
      (else 
        (let ((superClass (getClass superName)))
          (cond
            ((not superClass) #f)
            (else
              (sendWithSelf self superClass aMessage args))))))))

 (define (valueOfSlot self theSlot args)
  (let ((value (cadr theSlot)))
    (cond
      ((procedure? value)
        (apply value (cons self args)))
      (else value))))

\nwused{\\{NW1VK18x-15DMjX-1}}\nwendcode{}\nwbegindocs{47}\nwdocspar

\subsection{Vector and matrix manipulation}
\label{sec:vect-matr-manip}
Here we have colleced simple tools for manipulation with vectors and matrices. They are important for the portability, since one of our target Scheme implementations doesn't support full R5RS-Scheme (\cite{R5RS}) and portable Scheme libraries such as SLIB. 
\nwenddocs{}\nwbegincode{48}\sublabel{NW1VK18x-2tcrGt-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-2tcrGt-1}}}\moddef{Vector and matrix tools .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2tcrGt-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-15DMjX-1}}\nwenddeflinemarkup
\LA{}Vector operations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-14pT7v-1}}\RA{}
\LA{}Matrix inverse .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1qnsIb-1}}\RA{}
\nwused{\\{NW1VK18x-15DMjX-1}}\nwendcode{}\nwbegindocs{49}\nwdocspar
We represent vectors with lists since for now we don't want to have object system \ref{sec:object-system} overhead. It can be changed in the future.
\nwenddocs{}\nwbegincode{50}\sublabel{NW1VK18x-14pT7v-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-14pT7v-1}}}\moddef{Vector operations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-14pT7v-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2tcrGt-1}}\nwenddeflinemarkup
(define (add a b)
  (map-n + a b))

(define (sum list)
  (fold-left add (car list) (cdr list)))

(define (sub a b)
  (map-n - a b))

(define (mul a b)
  (cond ((and (list? a) (number? b)) (map (lambda (x) (* x b)) a))
        ((and (number? a) (list? b)) (mul b a))
        ((and (number? a) (number? b)) (* a b))
        (else (error "Can not multiply"))))

(define (div a b)
  (map (lambda (x) (/ x b)) a))

(define (prod a b)
  (fold-left + 0 (map-n * a b)))
\nwused{\\{NW1VK18x-2tcrGt-1}}\nwendcode{}\nwbegindocs{51}\nwdocspar

For the matrix inverse and determinant we use the implementation with the cofactors extracted from the SLIB. It is not the fastest and should be replaced with the Gaussian elimination.
\nwenddocs{}\nwbegincode{52}\sublabel{NW1VK18x-1qnsIb-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1qnsIb-1}}}\moddef{Matrix inverse .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1qnsIb-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2tcrGt-1}}\nwenddeflinemarkup
(define (matrix-cofactor mat i j)
  (define (butnth n lst)
    (if (<= n 1)
        (cdr lst)
        (cons (car lst)
              (butnth (+ -1 n) (cdr lst)))))
  (define (minor matrix i j)
    (map (lambda (x)
           (butnth j x))
         (butnth i mat)))
  (* (if (odd? (+ i j)) -1 1)
     (matrix-determinant (minor mat i j))))

(define (matrix-determinant mat)
  (let ((n (length mat)))
    (if (eqv? 1 n) (caar mat)
        (do ((j n (+ -1 j))
             (ans 0 (+ ans (* (list-ref (car mat) (+ -1 j))
                              (matrix-cofactor mat 1 j)))))
            ((<= j 0) ans)))))

(define (matrix-inverse mat)
  (let* ((det (matrix-determinant mat))
         (rank (length mat)))
    (and (not (zero? det))
         (do ((i rank (+ -1 i))
              (inv '() (cons
                        (do ((j rank (+ -1 j))
                             (row '()
                                  (cons (/ (matrix-cofactor mat j i) det) row)))
                            ((<= j 0) row))
                        inv)))
             ((<= i 0) inv)))))

\nwused{\\{NW1VK18x-2tcrGt-1}}\nwendcode{}

\nwixlogsorted{c}{{Anomalous weights computation .scm}{NW1VK18x-1y2eh2-1}{\nwixu{NW1VK18x-2w9Axe-2}\nwixd{NW1VK18x-1y2eh2-1}}}%
\nwixlogsorted{c}{{Commutative algebra .scm}{NW1VK18x-I1QOi-1}{\nwixd{NW1VK18x-I1QOi-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Functions for root systems .scm}{NW1VK18x-10zTlp-1}{\nwixd{NW1VK18x-10zTlp-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{library.scm}{NW1VK18x-15DMjX-1}{\nwixd{NW1VK18x-15DMjX-1}}}%
\nwixlogsorted{c}{{Lie algebra class .scm}{NW1VK18x-4dzmez-1}{\nwixd{NW1VK18x-4dzmez-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Lie algebra methods .scm}{NW1VK18x-4X6QTQ-1}{\nwixu{NW1VK18x-4dzmez-1}\nwixd{NW1VK18x-4X6QTQ-1}}}%
\nwixlogsorted{c}{{lie-algebra.scm}{NW1VK18x-3yKaW-1}{\nwixd{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{LispMe Objects .scm}{NW1VK18x-26RKW4-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-26RKW4-1}}}%
\nwixlogsorted{c}{{Matrix inverse .scm}{NW1VK18x-1qnsIb-1}{\nwixu{NW1VK18x-2tcrGt-1}\nwixd{NW1VK18x-1qnsIb-1}}}%
\nwixlogsorted{c}{{Representations .scm}{NW1VK18x-2w9Axe-1}{\nwixd{NW1VK18x-2w9Axe-1}\nwixd{NW1VK18x-2w9Axe-2}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Root system methods .scm}{NW1VK18x-1H68wy-1}{\nwixu{NW1VK18x-1pDr9o-1}\nwixd{NW1VK18x-1H68wy-1}\nwixd{NW1VK18x-1H68wy-2}\nwixd{NW1VK18x-1H68wy-3}\nwixd{NW1VK18x-1H68wy-4}\nwixd{NW1VK18x-1H68wy-5}\nwixd{NW1VK18x-1H68wy-6}}}%
\nwixlogsorted{c}{{Semi-standard Scheme procedures .scm}{NW1VK18x-16zbNk-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-16zbNk-1}}}%
\nwixlogsorted{c}{{Semisimple Lie algebra .scm}{NW1VK18x-1QMleH-1}{\nwixd{NW1VK18x-1QMleH-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Semisimple Lie algebra methods .scm}{NW1VK18x-1pDr9o-1}{\nwixu{NW1VK18x-1QMleH-1}\nwixd{NW1VK18x-1pDr9o-1}}}%
\nwixlogsorted{c}{{Sets .scm}{NW1VK18x-3j9Egk-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-3j9Egk-1}}}%
\nwixlogsorted{c}{{Simple Lie algebras .scm}{NW1VK18x-379yCw-1}{\nwixd{NW1VK18x-379yCw-1}\nwixu{NW1VK18x-3yKaW-1}}}%
\nwixlogsorted{c}{{Vector and matrix tools .scm}{NW1VK18x-2tcrGt-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-2tcrGt-1}}}%
\nwixlogsorted{c}{{Vector operations .scm}{NW1VK18x-14pT7v-1}{\nwixu{NW1VK18x-2tcrGt-1}\nwixd{NW1VK18x-14pT7v-1}}}%
\nwixlogsorted{c}{{Weight multiplicities computation .scm}{NW1VK18x-46EOV9-1}{\nwixu{NW1VK18x-2w9Axe-2}\nwixd{NW1VK18x-46EOV9-1}}}%
\nwbegindocs{53}\nwdocspar

\bibliography{LiterateLie}{}
\bibliographystyle{utphys}

\end{document}

\nwenddocs{}

### 2010-01-18 AffineLieAlgebras/InformalNotes/article.tex
Pictures in the first example are fixed.

@@
 Consider the regular embedding of $A_1$ into $B_2$.
-Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the thick vectors at the Figure \ref{fig:B2_A1}.
+Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the dashed vectors at the Figure \ref{fig:B2_A1}.
 We denote the corresponding Weyl reflections by $\omega_1, \omega_2$.
-Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+\alpha_2$.
+Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+\alpha_2$ and is drawn as grey vector.
 
-Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$.
+Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$, which is drawn as the black vector at the Figure \ref{fig:B2_A1}.
 \begin{figure}[ph]

### 2010-01-23 AffineLieAlgebras/InformalNotes/article.tex
Prettified some pictures
V.D. comments added

@@
 \documentclass[a4paper,12pt]{article}
+\usepackage{ucs}
 \usepackage[unicode,verbose]{hyperref}
@@
 \usepackage{pb-diagram}
-\usepackage{ucs}
+
 %\usepackage[utf8x]{inputenc}
@@
 \begin{figure}[h!tb]
-    \includegraphics[width=130mm]{B4_B2_anom_points.pdf}
+    \includegraphics[width=150mm]{B4_B2_anom_points.pdf}
   \caption{Anomalous points with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
@@
 \label{sec:phys-appl}
-Here we want to discuss possible applications of the described techniques in physical models.
-
-Branching coefficients for the embedding of affine Lie subalgebra into
+(This part must be changed considerably.
+First it is necessary to restore our notations instead of the Di Francesco notations.
+Starting with $J^{a_j}_{-n_j}$ which is too archaic!
+Second but much more important: the example that you had presented refers to the case where the initial injection fan method remains unmodified.
+Are there any other cases where the modified fan method is necessary?
+Fourth, you write "we should select only those highest-weight modules of the subalgebra $\mathfrak{a}$ for which the relation (\ref{eq:111}) holds", where does this selection happens and where is it in the example?
+Fifth, again the notations, it is of no use to indicate the Dynkin indices of the fund.
+weights ("three level one dominant weights $[1,0,0],\;[0,1,0],\;[0,0,1]$" ) for the reader it is interesting what are they like here; we never place the level indices in the first place as in "with the highest weight $w_0=(1,0,0)$" see the section Notations.
+In the Figure 12 the irrep is written to be (1,0,1,0) -- very strange!
+Sixth,
+in all the figures it is difficult to see anything and at the same time there are almost no explanations, even the boxes and dots are not commented.
+Some other corrections are made directly in the text.)
+
+Here we want to discuss possible applications of the described techniques in physical (?) models.
+
+Branching coefficients for an embedding of affine Lie subalgebra into
 affine Lie algebra can be used to construct modular invariant
-partition functions of Wess-Zumino-Novikov-Witten models (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
-
-But for this construction to work the embedding is required to be conformal, which means that the central charge of the subalgebra is equal to the central charge of the algebra.
+partition functions for Wess-Zumino-Novikov-Witten models (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
+For the construction to be valid the embedding is required to be conformal, which means that the central charge of the subalgebra is equal to the central charge of the algebra:
 \begin{equation}
@@
 
- The class of the conformal embeddings is rather small, the complete classification is given in the paper \cite{schellekens1986conformal}.
-The requirement (\ref{eq:31}) allows to reduce the task of the computation of the branching coefficients of affine Lie algebras to the computation of the branching coefficients of the finite-dimensional Lie algebras.
+ The class of conformal embeddings is not rich, the complete classification is given in the paper \cite{schellekens1986conformal}.
+The requirement (\ref{eq:31}) allows to reduce the problem of finding the branching coefficients for affine Lie algebras to the computation of branching coefficients for finite-dimensional Lie algebras.
 
@@
 
-Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for the original and the embedded theory.
-
-The states for the theory that corresponds to the algebra $\mathfrak{g}$
+Let $J^{a_j}_{-n_j}$ and $\tilde{J}^{a'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and of $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
+Let $\pi_{\mathfrak{a}}$ be the projection operator of $\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$.
+In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$ the states can be described as
 \begin{equation}
   \label{eq:109}
-  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq\dots>0
-\end{equation}
-For sub-algebra $\mathfrak{a}\subset\mathfrak{g}$
+  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+\end{equation}
+And for the sub-algebra $\mathfrak{a}$ the corresponding states are
 \begin{equation}
   \label{eq:110}
-  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>
-\end{equation}
-Here $\tilde{J}^{a'_j}_{-n_j}$ are the generators of $\mathfrak{a}$ and $\pi_{\mathfrak{a}}$ is the projection of $\mathfrak{g}$ to $\mathfrak{a}$.
-$\mathfrak{g}$-invariance of vacuum entails its $\mathfrak{a}$-invariance, but it is not the case for energy-momentum tensor.
-So energy-momentum tensor of bigger theory should consist only of generators of $\mathfrak{a}$.
+  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
+\end{equation}
+The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance, but it is not the case for the energy-momentum tensor.
+So the energy-momentum tensor of the larger theory should consist only of generators of $\tilde{J}$.
 Then $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow c(\mathfrak{g})=c(\mathfrak{a})$.
-This leads to equation
+This leads to the equation
 \begin{equation}
@@
 \end{equation}
-Here $x_e$ is the embedding index and $g$, $a$ are dual Coxeter numbers of corresponding algebras.
-
-It can be shown that solutions of equation (\ref{eq:111}) exist only
-for level 1 $k=1$ \cite{difrancesco1997cft}.
-
-If we have modular-invariant partition function for the fields described by the representation of the algebra $\mathfrak{g}$ this modular invariance is preserved by the projection on the subalgebra $\mathfrak{a}$, but we need also the preservation of the conformal invariance.
+Here $x_e$ is the embedding index and $g$, $a$ are the dual Coxeter numbers for the  corresponding algebras.
+
+It can be demonstrated that the solutions of the equation (\ref{eq:111}) exist only
+for level $k=1$ \cite{difrancesco1997cft}.
+
+If we have modular-invariant partition function for the fields described by a representation of the algebra $\mathfrak{g}$ this modular invariance is preserved by the projection on the subalgebra $\mathfrak{a}$, but we need also the preservation of the conformal invariance.
 So we should select only those highest-weight modules of the subalgebra $\mathfrak{a}$ for which the relation (\ref{eq:111}) holds.
 
-Since in the decomposition (\ref{eq:3}) the highest weight $\nu$ of the subalgebra module belongs to some grade $n$ of projected algebra module $\pi_{\mathfrak{a}}\cdot L^{(\mu)}_{\mathfrak{g}}$, from the relation (\ref{eq:111}) one can obtain the following requirement on the conformal dimensions of the corresponding fields
+In the decomposition (\ref{eq:3}) let the highest weight $\nu$ of the subalgebra module belong to the grade $n$ of the projected  module $\pi_{\mathfrak{a}}\cdot L^{(\mu)}_{\mathfrak{g}}$.
+Then the relation (\ref{eq:111}) implies the following requirement on the conformal dimensions of the corresponding fields
 \begin{equation}
@@
 \end{equation}
-It leads to the relation on the classical parts of the corresponding weights:
+It leads to a restriction imposed on the classical parts of the corresponding weights:
 \begin{equation}
@@
 \end{equation}
-There exits the finite reducibility theorem for the conformal embeddings which states that only finite number of the branching coefficients is non-zero in the case of the conformal embedding $\mathfrak{a}\subset\mathfrak{a}$.
-
-Then after we have found all such weights $\nu$ and the corresponding branching coefficients $b^{(\mu)}_{\nu}$ we can substitute the sums $\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}$ over the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules in place of the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function
+The finite reducibility theorem states that for conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
+
+Then after we have found all such weights $\nu$ and the corresponding branching coefficients $b^{(\mu)}_{\nu}$ we can replace the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function
 \begin{equation}
@@
 \end{equation}
+by the decompositions   $\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}$ containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules.
 Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
@@
 \end{equation}
+\begin{comment}
+The problem is also considered in the \cite{coquereaux2008conformal}.  
+\end{comment}
 
@@
 \label{sec:spec-embedd-hata_1s}
-Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ built as the affine extension of the special embedding $su(2)\subset su(3)$ with the embedding index $x_e=4$.
-The level of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the subalgebra $\tilde{k}=kx_e=4$.
+Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $su(2)\subset su(3)$ with the embedding index $x_e=4$.
+The level of the algebra (what is it ?) $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the subalgebra $\tilde{k}=kx_e=4$.
 
 There exist three level one dominant weights $[1,0,0],\;[0,1,0],\;[0,0,1]$ in the weight space of $\hat{A}_2$.
-It is easy to see that the set $\Delta_{\bot}$ is empty.
-
-Here we view the representation with the highest weight
-$w_0=(1,0,0)$ in detail.
-
-The set of the anomalous points of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}.
+It is easy to see that the set $\Delta_{\bot}$ is empty. (Not only this set is empty but the orthogonal algebra is empty!)
+
+Let us consider the representation with the highest weight
+$w_0=(1,0,0)$ in details.
+
+The set of the anomalous points of this representation up to the sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}.
 We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration.
+(Where, how?
+What are the coordinates, it is very difficult to see anything even in the zero grade!)
 
@@
 
-As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
-The result of this computation up to the twelfth grade is presented at the Figure \ref{fig:AffineA2_A1_anom_proj}
+According to our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules (there are no such subalgebra here!)$L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+The result of these caculations up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
 \begin{figure}[h!tb]
@@
 
-Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
+Then we construct ``the fan'' and use the recurrent relations to compute the anomalous branching coefficients.
 
 Using the definition (\ref{fan-defined}) we get the following set of
-the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:AffineA2A1Fan}.
-Here we restricted the computation to the twelfth grade.
+the weights $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:AffineA2A1Fan}.
+Here we restricted the calculations to the first twelve grades.
 \begin{figure}[p]
@@
 
-Using the recurrent relation for the anomalous branching coefficients we get the following result
+Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}.
+(Isn't it obvious that all the zeros there make the picture unreadable?)
 \begin{figure}[p]
@@
 
-We see that only two anomalous branching coefficients inside the main
-Weyl chamber of $\hat{A}_1$ are non-zero and equal to the branching
-coefficients. So the finite reducibility theorem holds and we get
+We see that inside the main
+Weyl chamber of $\hat{A}_1$ there are only two non-zero anomalous weights.
+(Show the Weyl chambers on the Figure.) These are the branching coefficients.
+So the finite reducibility theorem holds and we get the decomposition
 \begin{equation}
   \label{eq:43}
-  L^{[1,0,0]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[0,4]}\oplus L_{\hat{A_1}}^{[4,0]}
-\end{equation}
-
-For the other level one dominant weights of $\hat{A}_2$ we get trivial
-branching rules
+  L^{[1,0,0]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[0,4]}\oplus L_{\hat{A_1}}^{[4,0]}.
+\end{equation}
+
+For the other level one dominant weights of $\hat{A}_2$ we get the trivial
+branching 
 \begin{eqnarray}
   \label{eq:44}
-   L^{[0,1,0]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[2,2]}\\
-   L^{[0,0,1]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[2,2]}
+   L^{[0,1,0]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[2,2]},\\
+   L^{[0,0,1]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[2,2]}.
 \end{eqnarray}
 
-Using this result we can construct modular-invariant partition function
+Using this result the modular-invariant partition function is easily found,
 \begin{equation}
   \label{eq:45}
-  Z=\left|\chi_{[4,0]}+\chi_{[0,4]}\right|^2+2\chi_{[2,2]}^2
+  Z=\left|\chi_{[4,0]}+\chi_{[0,4]}\right|^2+2\chi_{[2,2]}^2.
 \end{equation}
@@
 \label{sec:conclusion}
-We have constructed the recurrent relation for branching coefficients and proposed practical algorithm for the reduction procedure.
-Also we have discussed the application of this algorithm to the physical problem of construction the modular-invariant partition functions in the conformal field theory.
-This method of conformal embeddings is well-known but may be actual in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
+We have proved that the injection fan technique can be used to deal with the nonmaximal subalgebras.
+It was demonstrated that in such cases in the set of positive roots $\Delta_{\mathfrak{g}}^{+}$ it is necessary to  separate an additional subset $\Delta^{+}_{\bot}$.
+The injection fan is formed by the weights $\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+} \setminus \Delta^{+}_{\bot}$ and the additional role of the subset $\Delta^{+}_{\bot}$ is to modify the anomalous weights of the initial module.
+This modification reduces to a simple procedure: the anomalous weights are to be substituted by the dimensions of the corresponding ${\mathfrak{a}}_{\bot}$-modules.
+
+We have demonstrated the effectiveness of the proposed generalizations of the injection fan algorithm and discussed its possible application to some physical problems.
+In particular we considered the construction modular-invariant partition functions in the conformal field theory in the framework of conformal embedding method.
+This  method is widely used in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
 

### 2010-02-18 AffineLieAlgebras/InformalNotes/article.tex
Some work on semisimple algebras

@@
 
-$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|}{\left|\Theta_{\mathfrak{a}}\right|}$ --- the embedding index.
+$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$ --- the embedding index.
 
@@
 \end{figure}
-On the Figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
-Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
+On the Figure \ref{fig:B2_A1} we have also shown the set of weights $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
+Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
 \begin{figure}[ph]
@@
   }
-  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
+  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
   \label{fig:B2_A1_2}
@@
 We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
-Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
+Then we project these weights and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous weights in fundamental weights basis with corresponding multiplicities:
 \begin{equation}
@@
 
-To find the branching coefficients we need to compute the anomalous points of $B_4$, select point lying in the main Weyl chamber of $\mathfrak{a}_{\bot}$ and compute the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.
+To find the branching coefficients we need to compute the anomalous weights of $B_4$, select weights lying in the main Weyl chamber of $\mathfrak{a}_{\bot}$ and compute the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.
 
@@
 
-The set of the anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W$
-consists of 384 points. We do not show it here.
-
-We need to select those points $\omega(\mu+\rho)$  which are projected into the main chamber of the embedded algebra $\mathfrak{a}_{\bot}$.
-It means that scalar product of these points with all the roots from $\Delta^{+}_{\bot}$ is non-negative.
+The set of the anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W$
+consists of 384 elements. We do not show it here.
+
+We need to select those weights $\omega(\mu+\rho)$  which are projected into the main chamber of the embedded algebra $\mathfrak{a}_{\bot}$.
+It means that scalar product of these weights with all the roots from $\Delta^{+}_{\bot}$ is non-negative.
 
 To compute dimensions of the corresponding
-$\mathfrak{a}_{\bot}$-modules we need to project each selected point
+$\mathfrak{a}_{\bot}$-modules we need to project each selected weight
 onto the root space $\Delta^{+}_{\bot}$ and substract
@@
     \includegraphics[width=150mm]{B4_B2_anom_points.pdf}
-  \caption{Anomalous points with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
+  \caption{Anomalous weights with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
   \label{fig:B4B2anom}
@@
 
-Using the definition (\ref{fan-defined}) we get the following set of
-the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
+Using the definition (\ref{fan-defined}) we get the following set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
 \begin{figure}[h!tb]
@@
 
-The set of the anomalous points of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.
+The set of the anomalous weights of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.
 
@@
   \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
-  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
+  \caption{The anomalous weights of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
   \label{fig:affine_B2_anom_point}
@@
 
-As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+As the next step of our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
 The result of this computation up to the twelfth grade is presented at the Figure
@@
   \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
-  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
   \label{fig:AffineB2_A1_anom_proj}
@@
 
-Using the definition (\ref{fan-defined}) we get the following set of
-the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
+Using the definition (\ref{fan-defined}) we get the following $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
 Here we restricted the computation to the twelfth grade.
@@
 
-Selecting the points inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
+Selecting the elements inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
 \begin{multline}
@@
 
-\subsection{Example}
+For the maximal conformal embedding $\mathfrak{a}\subset\mathfrak{g}$ it is easy to see that $\mathfrak{a}_{\bot}$ is trivial, otherwise it would be non-maximal, since $\mathfrak{a}\subset\mathfrak{a}\oplus\mathfrak{a}_{\bot}\subset\mathfrak{g}$.
+We can get non-maximal conformal embeddings through the chain of maximal $\mathfrak{a}\subset\mathfrak{g}_1\subset\mathfrak{g}_2$.
+In this case the representations of $\mathfrak{g}_1,\mathfrak{g}_2$ have to be of level one, due to the equation \eqref{eq:111}.
+If we limit the consideration by the affine extensions of simple classical Lie algebras, the number of possible non-maximal conformal embeddings is rather small \cite{schellekens1986conformal}.
+We study the example of $\hat{A}_1\subset \hat{A}_2\subset\hat{A}_{?}$ in the section \ref{sec:non-maxim-conf}.
+
+\subsection{Examples}
 \label{sec:example}
@@
 
-The set of the anomalous points of this representation up to the sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}.
+The set of the anomalous weights of this representation up to the sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}.
 We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration.
@@
   \includegraphics[width=160mm]{AffineA2_A1_anom.pdf}
-  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{A_2}$}
+  \caption{The anomalous weights of the $(1,0,1,0)$ representation of the algebra $\hat{A_2}$}
   \label{fig:affine_A2_anom_point}
@@
 
-According to our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules (there are no such subalgebra here!)$L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+According to our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules (there are no such subalgebra here!)$L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
 The result of these caculations up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
@@
   \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
-  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
   \label{fig:AffineA2_A1_anom_proj}
@@
 
+\subsubsection{Embedding of semisimple subalgebras}
+\label{sec:embedd-semis-subalg}
+
+Embedding of affine extensions of semisimple subalgebras to affine lie algebras allows additional construction of modular invariants \cite{difrancesco1997cft}, \cite{walton1989conformal}.
+Consider the conformal embedding constructed as the affine extension  $\mathfrak{a}_{1}\oplus\mathfrak{a}_{2}\subset \mathfrak{g}$ of the embedding of semisimple subalgebra $\overset{\circ}{\mathfrak{a}}_1\oplus\overset{\circ}{\mathfrak{a}}_2$ into simple Lie algebra $\overset{\circ}{\mathfrak{g}}$.
+
+Substituting the branching rules into \eqref{eq:34} we get non-diagonal mass matrix
+\begin{equation}
+  \label{eq:2}
+  M_{\lambda\xi,\mu\eta}
+\end{equation}
+where $\lambda,\mu$ are the highest weights of the representations of $\mathfrak{a}_1$ and $\xi,\eta$ of $\mathfrak{a}_2$.
+A new $\mathfrak{a}_1$-invariant mass matrix can be found by the contraction of $M_{\lambda\xi,\mu\eta}$ with some known $\mathfrak{a}_2$-invariant mass matrix $M^{(2)}_{\xi\eta}$:
+\begin{equation}
+  \label{eq:35}
+  M^{(1)}_{\lambda\mu}=\sum_{\xi,\eta\in P_{\mathfrak{a}}^{+}}M_{\lambda\xi,\mu\eta}M^{(2)}_{\xi\eta}
+\end{equation}
+
+Consider the embedding $\widehat{su(2)\oplus su(2)}\subset \hat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$.
+Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}.
+We start with 4-dimensional representation of $su(2)\oplus su(2)$ with the highest weight $(1,1)$.
+
+, depicted at the Figure \ref{fig:a1a2a3}.
+This embedding is characterised by the embedding indexes $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
+
+Four dominant weights of level one have the following coordinates in the orthogonal basis: 
+\begin{equation}
+  \begin{array}{lll}
+     \omega_0 & = & (0,0,0,0;1;0)\\
+     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
+     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
+     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
+  \end{array}
+\end{equation}
+We limit our computation by the fifth grade.
+The set of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements.
+
+\subsubsection{Non-maximal conformal embedding}
+\label{sec:non-maxim-conf}
+
+The example of the previous subsection \ref{sec:spec-embedd-hata_1s} has not demonstrated the features of our approach since the orthogonal subalgebra $\mathfrak{a}_{\bot}$ has been empty.
+
+But we can consider the chain of embeddings $\mathfrak{a}\subset\mathfrak{g}_1\subset\mathfrak{g}_2$.
+We can use the embedding $\hat{A}_1\subset\hat{A}_2\subset\hat{A}_{?}$.
+Modular invariant partition function for this case could be obtained in two steps.
+First one can compute branching coefficients for $\hat{A}_2\subset\hat{A}_{?}$ and get partition function for $\hat{A}_2$ and then substitute the results of the previous section \ref{sec:spec-embedd-hata_1s} into it to get the new partition function for $\hat{A}_1$.
+
+The algorithm of the section \ref{sec:algorithm} can be used to skip the intermediate computation.
+
 \section{Conclusion}

### 2010-03-15 AffineLieAlgebras/SchemePrograms/LiterateLie.tex

@@
-\documentclass[a4paper,10pt]{article}% ===> this file was generated automatically by noweave --- better not edit it
+\documentclass[a4paper,10pt]{article}
 \usepackage[unicode,verbose]{hyperref}
@@
 
-We will represent Lie algebra in the code as the object of class {\Tt{}lie-algebra\nwendquote}.
+We will represent Lie algebra in the code as the object of class {\tt{}lie-algebra}.
 We use very simple class system, which is described in the Appendix \ref{sec:object-system}.
-So {\Tt{}lie-algebra\nwendquote} is really an interface, but since our object system doesn't have interfaces we make it an abstract class and concrete classes such as {\Tt{}semisimple-lie-algebra\nwendquote} inherit it.
+So {\tt{}lie-algebra} is really an interface, but since our object system doesn't have interfaces we make it an abstract class and concrete classes such as {\tt{}semisimple-lie-algebra} inherit it.
 Lie algebra is a vector space, so we really should create class for the vector space which contains methods for the change of basis.
-But for now we use only one standard basis for Lie algebras and {\Tt{}lie-algebra\nwendquote} is the subclass of the most genral class {\Tt{}object\nwendquote}.
-\nwenddocs{}\nwbegincode{2}\sublabel{NW1VK18x-4dzmez-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-4dzmez-1}}}\moddef{Lie algebra class .scm~{\nwtagstyle{}\subpageref{NW1VK18x-4dzmez-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
+But for now we use only one standard basis for Lie algebras and {\tt{}lie-algebra} is the subclass of the most genral class {\tt{}object}.
+\nwenddocs{}\nwbegincode{2}\sublabel{NWLitE-LieM-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-LieM-1}}}\moddef{Lie algebra class .scm~{\nwtagstyle{}\subpageref{NWLitE-LieM-1}}}\endmoddef
 (class 'lie-algebra 'object
-       \LA{}Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-4X6QTQ-1}}\RA{})
-\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{3}\nwdocspar
-We need to add several definitions and describe a structure of Lie algebra in order to discuss fields and methods of {\Tt{}lie-algebra\nwendquote} class.
+       \LA{}Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NWLitE-LieO-1}}\RA{})
+\nwused{\\{NWLitE-lieF-1}}\nwendcode{}\nwbegindocs{3}\nwdocspar
+We need to add several definitions and describe a structure of Lie algebra in order to discuss fields and methods of {\tt{}lie-algebra} class.
 \begin{Def}
@@
 \end{Def}
-\nwenddocs{}\nwbegincode{4}\sublabel{NW1VK18x-4X6QTQ-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-4X6QTQ-1}}}\moddef{Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-4X6QTQ-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-4dzmez-1}}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{4}\sublabel{NWLitE-LieO-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-LieO-1}}}\moddef{Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NWLitE-LieO-1}}}\endmoddef
 `(rank ,(lambda (self)
@@
 
-\nwused{\\{NW1VK18x-4dzmez-1}}\nwendcode{}\nwbegindocs{5}\nwdocspar
+\nwused{\\{NWLitE-LieM-1}}\nwendcode{}\nwbegindocs{5}\nwdocspar
 Commutative algebras constitute first concrete class of Lie algebras.
-\nwenddocs{}\nwbegincode{6}\sublabel{NW1VK18x-I1QOi-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-I1QOi-1}}}\moddef{Commutative algebra .scm~{\nwtagstyle{}\subpageref{NW1VK18x-I1QOi-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{6}\sublabel{NWLitE-ComO-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-ComO-1}}}\moddef{Commutative algebra .scm~{\nwtagstyle{}\subpageref{NWLitE-ComO-1}}}\endmoddef
 (class 'commutative-algebra 'lie-algebra
@@
   (new 'commutative-algebra `(dim ,dim)))
-\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{7}\nwdocspar
+\nwused{\\{NWLitE-lieF-1}}\nwendcode{}\nwbegindocs{7}\nwdocspar
 \begin{comment}
@@
 The structure of simple and semisimple Lie algebras can be encoded by the set of simple roots. 
-\nwenddocs{}\nwbegincode{9}\sublabel{NW1VK18x-1QMleH-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1QMleH-1}}}\moddef{Semisimple Lie algebra .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1QMleH-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{9}\sublabel{NWLitE-SemR-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-SemR-1}}}\moddef{Semisimple Lie algebra .scm~{\nwtagstyle{}\subpageref{NWLitE-SemR-1}}}\endmoddef
 (class 'semisimple-lie-algebra 'lie-algebra
        '(simple-roots ())
-       \LA{}Semisimple Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1pDr9o-1}}\RA{})
+       \LA{}Semisimple Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NWLitE-SemZ-1}}\RA{})
 ;; The constructor
@@
 
-\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{10}\nwdocspar
+\nwused{\\{NWLitE-lieF-1}}\nwendcode{}\nwbegindocs{10}\nwdocspar
 
@@
 The set of all the roos $\alpha$ is denoted by $\Delta=\{\alpha,\; \alpha \text{ - root}\}$.
-So it is natural for the {\Tt{}lie-algebra\nwendquote} class to have a method which lists all the roots.
-\nwenddocs{}\nwbegincode{11}\sublabel{NW1VK18x-1pDr9o-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1pDr9o-1}}}\moddef{Semisimple Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1pDr9o-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1QMleH-1}}\nwenddeflinemarkup
+So it is natural for the {\tt{}lie-algebra} class to have a method which lists all the roots.
+\nwenddocs{}\nwbegincode{11}\sublabel{NWLitE-SemZ-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-SemZ-1}}}\moddef{Semisimple Lie algebra methods .scm~{\nwtagstyle{}\subpageref{NWLitE-SemZ-1}}}\endmoddef
 `(rank ,(lambda (self)
@@
     (make-commutative-algebra (send self 'rank))))
-\LA{}Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}\RA{}
-\nwused{\\{NW1VK18x-1QMleH-1}}\nwendcode{}\nwbegindocs{12}\nwdocspar
+\LA{}Root system methods .scm~{\nwtagstyle{}\subpageref{NWLitE-RooO-1}}\RA{}
+\nwused{\\{NWLitE-SemR-1}}\nwendcode{}\nwbegindocs{12}\nwdocspar
 All the roots are the linear combinations of simple roots with the integral coefficients.
@@
 
-So we need just two following general functions:
-\nwenddocs{}\nwbegincode{13}\sublabel{NW1VK18x-10zTlp-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}}\moddef{Functions for root systems .scm~{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
+Also sometimes we need to know the determinant of Weyl group element and we can take it into account using the following version of the {\tt{}reflect} function, called {\tt{}reflect-with-eps}.
+
+\nwenddocs{}\nwbegincode{13}\sublabel{NWLitE-FunV-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-FunV-1}}}\moddef{Functions for root systems .scm~{\nwtagstyle{}\subpageref{NWLitE-FunV-1}}}\endmoddef
 (define (co-root r)
@@
   (sub weight (mul (prod weight (co-root root)) root)))
-\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{14}\nwdocspar
+
+(define (reflect-with-eps weight root)
+  (if (or (null? (cdr weight))
+          (pair? (cdr weight)))
+      (let ((v (reflect weight root)))
+        (cons v (if (equal? weight v) 1 -1)))
+      (let ((v (reflect (car weight) root)))
+        (cons v (if (equal? (car weight) v) (cdr weight) (- (cdr weight)))))))
+
+(define (eps weight)
+  (if (or (null? (cdr weight))
+          (pair? (cdr weight)))
+      1
+      (cdr weight)))
+
+(define (no-eps weight)
+  (if (or (null? (cdr weight))
+          (pair? (cdr weight)))
+      weight
+      (car weight)))
+\nwused{\\{NWLitE-lieF-1}}\nwendcode{}\nwbegindocs{14}\nwdocspar
 Here {\it co-root} $\alpha^{\vee}$ is the element of the dual space $(\mathfrak{h}^*)^*$ which is identified with $\mathfrak{h}^*\approx \mathfrak{h}$ since we have scalar product on $\mathfrak{h}$.
 
-Now we can implement wide range of root system related methods of {\Tt{}semisimple-lie-algebra\nwendquote} class
-\nwenddocs{}\nwbegincode{15}\sublabel{NW1VK18x-1H68wy-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{\relax}{NW1VK18x-1H68wy-2}\nwenddeflinemarkup
+Now we can implement wide range of root system related methods of {\tt{}semisimple-lie-algebra} class
+\nwenddocs{}\nwbegincode{15}\sublabel{NWLitE-RooO-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-RooO-1}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NWLitE-RooO-1}}}\endmoddef
 `(simple-co-roots ,(lambda (self)
               (map co-root (send self 'simple-roots))))
-\nwalsodefined{\\{NW1VK18x-1H68wy-2}\\{NW1VK18x-1H68wy-3}\\{NW1VK18x-1H68wy-4}\\{NW1VK18x-1H68wy-5}\\{NW1VK18x-1H68wy-6}}\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{16}\nwdocspar
+\nwalsodefined{\\{NWLitE-RooO-2}\\{NWLitE-RooO-3}\\{NWLitE-RooO-4}\\{NWLitE-RooO-5}\\{NWLitE-RooO-6}}\nwused{\\{NWLitE-SemZ-1}}\nwendcode{}\nwbegindocs{16}\nwdocspar
 \begin{Def}
@@
 \end{Def}
-\nwenddocs{}\nwbegincode{17}\sublabel{NW1VK18x-1H68wy-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-2}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-1}{NW1VK18x-1H68wy-3}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{17}\sublabel{NWLitE-RooO-2}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-RooO-2}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NWLitE-RooO-1}}}\plusendmoddef
 `(cartan-matrix
@@
          (send self 'simple-roots))))
-\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{18}\nwdocspar
+\nwendcode{}\nwbegindocs{18}\nwdocspar
 We have already introduced Weyl group of reflections \ref{weyl-group-def}, now we implement procedure which constructs the union of Weyl group orbits of the set of weights.
-\nwenddocs{}\nwbegincode{19}\sublabel{NW1VK18x-1H68wy-3}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-3}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-2}{NW1VK18x-1H68wy-4}\nwenddeflinemarkup
-`(orbit ,
-  (lambda (self weights)
+\nwenddocs{}\nwbegincode{19}\sublabel{NWLitE-RooO-3}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-RooO-3}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NWLitE-RooO-1}}}\plusendmoddef
+`(general-orbit , (lambda (self weights reflect)
     (let ((addon 
@@
           weights
-          (send self 'orbit (union-set weights addon) )))))
-\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{20}\nwdocspar
+          (send self 'general-orbit (union-set weights addon) reflect )))))
+
+`(orbit ,
+  (lambda (self weights)
+    (send self 'general-orbit weights reflect)))
+
+`(orbit-with-eps ,
+  (lambda (self weights)
+    (send self 'general-orbit weights reflect-with-eps)))
+\nwendcode{}\nwbegindocs{20}\nwdocspar
 \begin{Def}
@@
 \end{Def}
-\nwenddocs{}\nwbegincode{21}\sublabel{NW1VK18x-1H68wy-4}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-4}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-3}{NW1VK18x-1H68wy-5}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{21}\sublabel{NWLitE-RooO-4}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-RooO-4}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NWLitE-RooO-1}}}\plusendmoddef
 `(fundamental-weights
@@
           (matrix-inverse (send self 'cartan-matrix)))))
-\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{22}\nwdocspar
+\nwendcode{}\nwbegindocs{22}\nwdocspar
 {\bf Weyl vector} $\rho=\sum_i w_i=\frac{1}{2}\sum_{\alpha\in \Delta^{+}}\alpha$.
-\nwenddocs{}\nwbegincode{23}\sublabel{NW1VK18x-1H68wy-5}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-5}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-4}{NW1VK18x-1H68wy-6}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{23}\sublabel{NWLitE-RooO-5}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-RooO-5}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NWLitE-RooO-1}}}\plusendmoddef
 `(rho ,(lambda (self)
@@
 
-\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{24}\nwdocspar
+\nwendcode{}\nwbegindocs{24}\nwdocspar
 We can construct the full set of Lie algebra roots using Weyl symmetry.
-\nwenddocs{}\nwbegincode{25}\sublabel{NW1VK18x-1H68wy-6}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-6}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-5}{\relax}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{25}\sublabel{NWLitE-RooO-6}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-RooO-6}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NWLitE-RooO-1}}}\plusendmoddef
 `(roots ,(lambda (self)
            (send self 'orbit (send self 'simple-roots))))
-\nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{26}\nwdocspar
+\nwendcode{}\nwbegindocs{26}\nwdocspar
 
@@
 Here we explicitly construct simple roots for the classical series of finite-dimensional Lie algebras
-\nwenddocs{}\nwbegincode{27}\sublabel{NW1VK18x-379yCw-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-379yCw-1}}}\moddef{Simple Lie algebras .scm~{\nwtagstyle{}\subpageref{NW1VK18x-379yCw-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{27}\sublabel{NWLitE-SimO-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-SimO-1}}}\moddef{Simple Lie algebras .scm~{\nwtagstyle{}\subpageref{NWLitE-SimO-1}}}\endmoddef
 (define (make-simple-lie-algebra series rank)
@@
   (make-semisimple-lie-algebra (simple-roots series rank)))
-\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{28}\nwdocspar
+\nwused{\\{NWLitE-lieF-1}}\nwendcode{}\nwbegindocs{28}\nwdocspar
 \section{Representations}
@@
 
-For the finite-dimensional representations we introduce abstract class {\Tt{}representation\nwendquote} and concrete class {\Tt{}highest-weight-representation\nwendquote}.
-Then we can describe  tensor product of two highest weight representations as the object of class {\Tt{}representation\nwendquote} (but not of class {\Tt{}highest-weight-representation\nwendquote}.
-\nwenddocs{}\nwbegincode{29}\sublabel{NW1VK18x-2w9Axe-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-1}}}\moddef{Representations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwprevnextdefs{\relax}{NW1VK18x-2w9Axe-2}\nwenddeflinemarkup
+For the finite-dimensional representations we introduce abstract class {\tt{}representation} and concrete class {\tt{}highest-weight-representation}.
+Then we can describe  tensor product of two highest weight representations as the object of class {\tt{}representation} (but not of class {\tt{}highest-weight-representation}.
+\nwenddocs{}\nwbegincode{29}\sublabel{NWLitE-RepK-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-RepK-1}}}\moddef{Representations .scm~{\nwtagstyle{}\subpageref{NWLitE-RepK-1}}}\endmoddef
 (class 'representation 'object
@@
        )
-\nwalsodefined{\\{NW1VK18x-2w9Axe-2}}\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{30}\nwdocspar
+\nwalsodefined{\\{NWLitE-RepK-2}}\nwused{\\{NWLitE-lieF-1}}\nwendcode{}\nwbegindocs{30}\nwdocspar
 
-\nwenddocs{}\nwbegincode{31}\sublabel{NW1VK18x-2w9Axe-2}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-2}}}\moddef{Representations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwprevnextdefs{NW1VK18x-2w9Axe-1}{\relax}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{31}\sublabel{NWLitE-RepK-2}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-RepK-2}}}\moddef{Representations .scm~{\nwtagstyle{}\subpageref{NWLitE-RepK-1}}}\plusendmoddef
 (class 'highest-weight-representation 'representation
        '(highest-weight ())
-       \LA{}Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}\RA{}
-       \LA{}Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}\RA{})
-`(multiplicity , (lambda (self weight)
-\nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{32}\nwdocspar
+       \LA{}Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NWLitE-AnoY-1}}\RA{}
+       \LA{}Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NWLitE-Weic-1}}\RA{})
+\nwendcode{}\nwbegindocs{32}\nwdocspar
 We use the recurrent method of calculation of weight multiplicities described in \cite{lyakhovsky1996rra}, \cite{kulish4sfa}.
 Weight multiplicities are determined using the set of anomalous points, which is constructed by the code below.
-\nwenddocs{}\nwbegincode{33}\sublabel{NW1VK18x-1y2eh2-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}}\moddef{Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2w9Axe-2}}\nwenddeflinemarkup
+We use the recurrent relation
+\begin{equation}
+  \label{eq:8}
+  m_{\xi }^{\left( \mu \right) }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
+-\left( w\cdot\rho-\rho \right) }^{\left( \mu \right) }+\sum_{w\in W}\epsilon
+(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.  \label{gen-mult-form}
+\end{equation}
+The second term on the right-hand side is constructed with the code:
+\nwenddocs{}\nwbegincode{33}\sublabel{NWLitE-AnoY-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-AnoY-1}}}\moddef{Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NWLitE-AnoY-1}}}\endmoddef
        `(anomalous-weights , 
@@
                   (send algebra 'orbit (add (send self 'highest-weight) rho))))))
-\nwused{\\{NW1VK18x-2w9Axe-2}}\nwendcode{}\nwbegindocs{34}\nwdocspar
+\nwused{\\{NWLitE-RepK-2}}\nwendcode{}\nwbegindocs{34}\nwdocspar
+Then multiplicity of the weight $\xi$ is calculated as the sum over the set $\omega\rho-\rho$, which we call ``star''
 
-\nwenddocs{}\nwbegincode{35}\sublabel{NW1VK18x-46EOV9-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}}\moddef{Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2w9Axe-2}}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{35}\sublabel{NWLitE-Weic-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-Weic-1}}}\moddef{Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NWLitE-Weic-1}}}\endmoddef
+`(multiplicity , (lambda (self weight)
+                   (let ((star \LA{}Construct star .scm~{\nwtagstyle{}\subpageref{nw@notdef}}\RA{}))
+                     (-
+                      (sum (map (lambda (wg) (* (eps wg) (delta weight wg)))))
+                      (sum (map (lambda (wg)
+                                    (* (eps wg)
+                                       (send self 'multiplicity (sub weight wg))))
+                                  star))))))
 
-\nwused{\\{NW1VK18x-2w9Axe-2}}\nwendcode{}\nwbegindocs{36}\nwdocspar
+\nwused{\\{NWLitE-RepK-2}}\nwendcode{}\nwbegindocs{36}\nwdocspar
 \section{General outline of the code}
@@
 
-The code goes to several files of which {\Tt{}library.scm\nwendquote} is a compatibility layer which consists of auxiliary functions and allows portability between different Scheme implementations on different OS-es and hardware platforms.
-{\Tt{}library.scm\nwendquote} is described in the appendix \ref{sec:library}.
-All the mathematical code which is connected with Lie theory is collected in the file {\Tt{}lie-algebra.scm\nwendquote}.
-\nwenddocs{}\nwbegincode{37}\sublabel{NW1VK18x-3yKaW-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-3yKaW-1}}}\moddef{lie-algebra.scm~{\nwtagstyle{}\subpageref{NW1VK18x-3yKaW-1}}}\endmoddef\let\nwnotused=\nwoutput{}\nwstartdeflinemarkup\nwenddeflinemarkup
-\LA{}Lie algebra class .scm~{\nwtagstyle{}\subpageref{NW1VK18x-4dzmez-1}}\RA{}
-\LA{}Commutative algebra .scm~{\nwtagstyle{}\subpageref{NW1VK18x-I1QOi-1}}\RA{}
-\LA{}Semisimple Lie algebra .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1QMleH-1}}\RA{}
-\LA{}Functions for root systems .scm~{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}\RA{}
-\LA{}Simple Lie algebras .scm~{\nwtagstyle{}\subpageref{NW1VK18x-379yCw-1}}\RA{}
-\LA{}Representations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2w9Axe-1}}\RA{}
+The code goes to several files of which {\tt{}library.scm} is a compatibility layer which consists of auxiliary functions and allows portability between different Scheme implementations on different OS-es and hardware platforms.
+{\tt{}library.scm} is described in the appendix \ref{sec:library}.
+All the mathematical code which is connected with Lie theory is collected in the file {\tt{}lie-algebra.scm}.
+\nwenddocs{}\nwbegincode{37}\sublabel{NWLitE-lieF-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-lieF-1}}}\moddef{lie-algebra.scm~{\nwtagstyle{}\subpageref{NWLitE-lieF-1}}}\endmoddef\let\nwnotused=\nwoutput{}
+\LA{}Lie algebra class .scm~{\nwtagstyle{}\subpageref{NWLitE-LieM-1}}\RA{}
+\LA{}Commutative algebra .scm~{\nwtagstyle{}\subpageref{NWLitE-ComO-1}}\RA{}
+\LA{}Semisimple Lie algebra .scm~{\nwtagstyle{}\subpageref{NWLitE-SemR-1}}\RA{}
+\LA{}Functions for root systems .scm~{\nwtagstyle{}\subpageref{NWLitE-FunV-1}}\RA{}
+\LA{}Simple Lie algebras .scm~{\nwtagstyle{}\subpageref{NWLitE-SimO-1}}\RA{}
+\LA{}Representations .scm~{\nwtagstyle{}\subpageref{NWLitE-RepK-1}}\RA{}
 \nwnotused{lie-algebra.scm}\nwendcode{}\nwbegindocs{38}\nwdocspar
@@
 
-\nwenddocs{}\nwbegincode{39}\sublabel{NW1VK18x-15DMjX-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-15DMjX-1}}}\moddef{library.scm~{\nwtagstyle{}\subpageref{NW1VK18x-15DMjX-1}}}\endmoddef\let\nwnotused=\nwoutput{}\nwstartdeflinemarkup\nwenddeflinemarkup
-\LA{}Semi-standard Scheme procedures .scm~{\nwtagstyle{}\subpageref{NW1VK18x-16zbNk-1}}\RA{}
-\LA{}Sets .scm~{\nwtagstyle{}\subpageref{NW1VK18x-3j9Egk-1}}\RA{}
-\LA{}Vector and matrix tools .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2tcrGt-1}}\RA{}
-\LA{}LispMe Objects .scm~{\nwtagstyle{}\subpageref{NW1VK18x-26RKW4-1}}\RA{}
+\nwenddocs{}\nwbegincode{39}\sublabel{NWLitE-libB-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-libB-1}}}\moddef{library.scm~{\nwtagstyle{}\subpageref{NWLitE-libB-1}}}\endmoddef\let\nwnotused=\nwoutput{}
+\LA{}Semi-standard Scheme procedures .scm~{\nwtagstyle{}\subpageref{NWLitE-Sema-1}}\RA{}
+\LA{}Sets .scm~{\nwtagstyle{}\subpageref{NWLitE-Set9-1}}\RA{}
+\LA{}Vector and matrix tools .scm~{\nwtagstyle{}\subpageref{NWLitE-VecS-1}}\RA{}
+\LA{}LispMe Objects .scm~{\nwtagstyle{}\subpageref{NWLitE-LisJ-1}}\RA{}
 \nwnotused{library.scm}\nwendcode{}\nwbegindocs{40}\nwdocspar
@@
 \nwenddocs{}\nwbegindocs{41}\nwdocspar
-Due to the limitations of Palm OS platform functions such as {\Tt{}map\nwendquote} or {\Tt{}fold-left\nwendquote} in LispMe are in the separate library, which should be loaded by hand.
-Also function {\Tt{}map\nwendquote} accepts only 1-argument function and list, so we add these functions to our library.
-\nwenddocs{}\nwbegincode{42}\sublabel{NW1VK18x-16zbNk-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-16zbNk-1}}}\moddef{Semi-standard Scheme procedures .scm~{\nwtagstyle{}\subpageref{NW1VK18x-16zbNk-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-15DMjX-1}}\nwenddeflinemarkup
+Due to the limitations of Palm OS platform functions such as {\tt{}map} or {\tt{}fold-left} in LispMe are in the separate library, which should be loaded by hand.
+Also function {\tt{}map} accepts only 1-argument function and list, so we add these functions to our library.
+\nwenddocs{}\nwbegincode{42}\sublabel{NWLitE-Sema-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-Sema-1}}}\moddef{Semi-standard Scheme procedures .scm~{\nwtagstyle{}\subpageref{NWLitE-Sema-1}}}\endmoddef
 (define nil ())
@@
 (define (fold-right op init s) (accumulate op init s))
-\nwused{\\{NW1VK18x-15DMjX-1}}\nwendcode{}\nwbegindocs{43}\nwdocspar
+\nwused{\\{NWLitE-libB-1}}\nwendcode{}\nwbegindocs{43}\nwdocspar
 We need couple of functions for sets. We represent set as list.
-\nwenddocs{}\nwbegincode{44}\sublabel{NW1VK18x-3j9Egk-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-3j9Egk-1}}}\moddef{Sets .scm~{\nwtagstyle{}\subpageref{NW1VK18x-3j9Egk-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-15DMjX-1}}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{44}\sublabel{NWLitE-Set9-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-Set9-1}}}\moddef{Sets .scm~{\nwtagstyle{}\subpageref{NWLitE-Set9-1}}}\endmoddef
 (define (element-of-set? x set)
@@
 
-\nwused{\\{NW1VK18x-15DMjX-1}}\nwendcode{}\nwbegindocs{45}\nwdocspar
+\nwused{\\{NWLitE-libB-1}}\nwendcode{}\nwbegindocs{45}\nwdocspar
 
@@
 
-\nwenddocs{}\nwbegincode{46}\sublabel{NW1VK18x-26RKW4-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-26RKW4-1}}}\moddef{LispMe Objects .scm~{\nwtagstyle{}\subpageref{NW1VK18x-26RKW4-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-15DMjX-1}}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{46}\sublabel{NWLitE-LisJ-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-LisJ-1}}}\moddef{LispMe Objects .scm~{\nwtagstyle{}\subpageref{NWLitE-LisJ-1}}}\endmoddef
 
@@
 
-\nwused{\\{NW1VK18x-15DMjX-1}}\nwendcode{}\nwbegindocs{47}\nwdocspar
+\nwused{\\{NWLitE-libB-1}}\nwendcode{}\nwbegindocs{47}\nwdocspar
 
@@
 They are important for the portability, since one of our target Scheme implementations doesn't support full R5RS-Scheme (\cite{R5RS}) and portable Scheme libraries such as SLIB.
-\nwenddocs{}\nwbegincode{48}\sublabel{NW1VK18x-2tcrGt-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-2tcrGt-1}}}\moddef{Vector and matrix tools .scm~{\nwtagstyle{}\subpageref{NW1VK18x-2tcrGt-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-15DMjX-1}}\nwenddeflinemarkup
-\LA{}Vector operations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-14pT7v-1}}\RA{}
-\LA{}Matrix inverse .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1qnsIb-1}}\RA{}
-\nwused{\\{NW1VK18x-15DMjX-1}}\nwendcode{}\nwbegindocs{49}\nwdocspar
+\nwenddocs{}\nwbegincode{48}\sublabel{NWLitE-VecS-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-VecS-1}}}\moddef{Vector and matrix tools .scm~{\nwtagstyle{}\subpageref{NWLitE-VecS-1}}}\endmoddef
+\LA{}Vector operations .scm~{\nwtagstyle{}\subpageref{NWLitE-VecM-1}}\RA{}
+\LA{}Matrix inverse .scm~{\nwtagstyle{}\subpageref{NWLitE-MatJ-1}}\RA{}
+\nwused{\\{NWLitE-libB-1}}\nwendcode{}\nwbegindocs{49}\nwdocspar
 We represent vectors with lists since for now we don't want to have object system \ref{sec:object-system} overhead. It can be changed in the future.
-\nwenddocs{}\nwbegincode{50}\sublabel{NW1VK18x-14pT7v-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-14pT7v-1}}}\moddef{Vector operations .scm~{\nwtagstyle{}\subpageref{NW1VK18x-14pT7v-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2tcrGt-1}}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{50}\sublabel{NWLitE-VecM-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-VecM-1}}}\moddef{Vector operations .scm~{\nwtagstyle{}\subpageref{NWLitE-VecM-1}}}\endmoddef
 (define (add a b)
@@
   (fold-left + 0 (map-n * a b)))
-\nwused{\\{NW1VK18x-2tcrGt-1}}\nwendcode{}\nwbegindocs{51}\nwdocspar
+\nwused{\\{NWLitE-VecS-1}}\nwendcode{}\nwbegindocs{51}\nwdocspar
 
 For the matrix inverse and determinant we use the implementation with the cofactors extracted from the SLIB. It is not the fastest and should be replaced with the Gaussian elimination.
-\nwenddocs{}\nwbegincode{52}\sublabel{NW1VK18x-1qnsIb-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1qnsIb-1}}}\moddef{Matrix inverse .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1qnsIb-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2tcrGt-1}}\nwenddeflinemarkup
+\nwenddocs{}\nwbegincode{52}\sublabel{NWLitE-MatJ-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-MatJ-1}}}\moddef{Matrix inverse .scm~{\nwtagstyle{}\subpageref{NWLitE-MatJ-1}}}\endmoddef
 (define (matrix-cofactor mat i j)
@@
 
-\nwused{\\{NW1VK18x-2tcrGt-1}}\nwendcode{}
+\nwused{\\{NWLitE-VecS-1}}\nwendcode{}\nwbegindocs{53}\nwdocspar
 
-\nwixlogsorted{c}{{Anomalous weights computation .scm}{NW1VK18x-1y2eh2-1}{\nwixu{NW1VK18x-2w9Axe-2}\nwixd{NW1VK18x-1y2eh2-1}}}%
-\nwixlogsorted{c}{{Commutative algebra .scm}{NW1VK18x-I1QOi-1}{\nwixd{NW1VK18x-I1QOi-1}\nwixu{NW1VK18x-3yKaW-1}}}%
-\nwixlogsorted{c}{{Functions for root systems .scm}{NW1VK18x-10zTlp-1}{\nwixd{NW1VK18x-10zTlp-1}\nwixu{NW1VK18x-3yKaW-1}}}%
-\nwixlogsorted{c}{{library.scm}{NW1VK18x-15DMjX-1}{\nwixd{NW1VK18x-15DMjX-1}}}%
-\nwixlogsorted{c}{{Lie algebra class .scm}{NW1VK18x-4dzmez-1}{\nwixd{NW1VK18x-4dzmez-1}\nwixu{NW1VK18x-3yKaW-1}}}%
-\nwixlogsorted{c}{{Lie algebra methods .scm}{NW1VK18x-4X6QTQ-1}{\nwixu{NW1VK18x-4dzmez-1}\nwixd{NW1VK18x-4X6QTQ-1}}}%
-\nwixlogsorted{c}{{lie-algebra.scm}{NW1VK18x-3yKaW-1}{\nwixd{NW1VK18x-3yKaW-1}}}%
-\nwixlogsorted{c}{{LispMe Objects .scm}{NW1VK18x-26RKW4-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-26RKW4-1}}}%
-\nwixlogsorted{c}{{Matrix inverse .scm}{NW1VK18x-1qnsIb-1}{\nwixu{NW1VK18x-2tcrGt-1}\nwixd{NW1VK18x-1qnsIb-1}}}%
-\nwixlogsorted{c}{{Representations .scm}{NW1VK18x-2w9Axe-1}{\nwixd{NW1VK18x-2w9Axe-1}\nwixd{NW1VK18x-2w9Axe-2}\nwixu{NW1VK18x-3yKaW-1}}}%
-\nwixlogsorted{c}{{Root system methods .scm}{NW1VK18x-1H68wy-1}{\nwixu{NW1VK18x-1pDr9o-1}\nwixd{NW1VK18x-1H68wy-1}\nwixd{NW1VK18x-1H68wy-2}\nwixd{NW1VK18x-1H68wy-3}\nwixd{NW1VK18x-1H68wy-4}\nwixd{NW1VK18x-1H68wy-5}\nwixd{NW1VK18x-1H68wy-6}}}%
-\nwixlogsorted{c}{{Semi-standard Scheme procedures .scm}{NW1VK18x-16zbNk-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-16zbNk-1}}}%
-\nwixlogsorted{c}{{Semisimple Lie algebra .scm}{NW1VK18x-1QMleH-1}{\nwixd{NW1VK18x-1QMleH-1}\nwixu{NW1VK18x-3yKaW-1}}}%
-\nwixlogsorted{c}{{Semisimple Lie algebra methods .scm}{NW1VK18x-1pDr9o-1}{\nwixu{NW1VK18x-1QMleH-1}\nwixd{NW1VK18x-1pDr9o-1}}}%
-\nwixlogsorted{c}{{Sets .scm}{NW1VK18x-3j9Egk-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-3j9Egk-1}}}%
-\nwixlogsorted{c}{{Simple Lie algebras .scm}{NW1VK18x-379yCw-1}{\nwixd{NW1VK18x-379yCw-1}\nwixu{NW1VK18x-3yKaW-1}}}%
-\nwixlogsorted{c}{{Vector and matrix tools .scm}{NW1VK18x-2tcrGt-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-2tcrGt-1}}}%
-\nwixlogsorted{c}{{Vector operations .scm}{NW1VK18x-14pT7v-1}{\nwixu{NW1VK18x-2tcrGt-1}\nwixd{NW1VK18x-14pT7v-1}}}%
-\nwixlogsorted{c}{{Weight multiplicities computation .scm}{NW1VK18x-46EOV9-1}{\nwixu{NW1VK18x-2w9Axe-2}\nwixd{NW1VK18x-46EOV9-1}}}%
-\nwbegindocs{53}\nwdocspar
+\subsection{Supplementary mathematical functions}
+\label{sec:suppl-math-funct}
 
+\nwenddocs{}\nwbegincode{54}\sublabel{NWLitE-SupN-1}\nwmargintag{{\nwtagstyle{}\subpageref{NWLitE-SupN-1}}}\moddef{Supplementary math .scm~{\nwtagstyle{}\subpageref{NWLitE-SupN-1}}}\endmoddef
+
+(define (delta weight1 weight2)
+  (equal? (no-eps weight1) (no-eps weight2)))
+\nwnotused{Supplementary\ math\ .scm}\nwendcode{}
+
+\nwixlogsorted{c}{{Anomalous weights computation .scm}{NWLitE-AnoY-1}{\nwixu{NWLitE-RepK-2}\nwixd{NWLitE-AnoY-1}}}%
+\nwixlogsorted{c}{{Commutative algebra .scm}{NWLitE-ComO-1}{\nwixd{NWLitE-ComO-1}\nwixu{NWLitE-lieF-1}}}%
+\nwixlogsorted{c}{{Construct star .scm}{nw@notdef}{\nwixu{NWLitE-Weic-1}}}%
+\nwixlogsorted{c}{{Functions for root systems .scm}{NWLitE-FunV-1}{\nwixd{NWLitE-FunV-1}\nwixu{NWLitE-lieF-1}}}%
+\nwixlogsorted{c}{{Lie algebra class .scm}{NWLitE-LieM-1}{\nwixd{NWLitE-LieM-1}\nwixu{NWLitE-lieF-1}}}%
+\nwixlogsorted{c}{{Lie algebra methods .scm}{NWLitE-LieO-1}{\nwixu{NWLitE-LieM-1}\nwixd{NWLitE-LieO-1}}}%
+\nwixlogsorted{c}{{LispMe Objects .scm}{NWLitE-LisJ-1}{\nwixu{NWLitE-libB-1}\nwixd{NWLitE-LisJ-1}}}%
+\nwixlogsorted{c}{{Matrix inverse .scm}{NWLitE-MatJ-1}{\nwixu{NWLitE-VecS-1}\nwixd{NWLitE-MatJ-1}}}%
+\nwixlogsorted{c}{{Representations .scm}{NWLitE-RepK-1}{\nwixd{NWLitE-RepK-1}\nwixd{NWLitE-RepK-2}\nwixu{NWLitE-lieF-1}}}%
+\nwixlogsorted{c}{{Root system methods .scm}{NWLitE-RooO-1}{\nwixu{NWLitE-SemZ-1}\nwixd{NWLitE-RooO-1}\nwixd{NWLitE-RooO-2}\nwixd{NWLitE-RooO-3}\nwixd{NWLitE-RooO-4}\nwixd{NWLitE-RooO-5}\nwixd{NWLitE-RooO-6}}}%
+\nwixlogsorted{c}{{Semisimple Lie algebra methods .scm}{NWLitE-SemZ-1}{\nwixu{NWLitE-SemR-1}\nwixd{NWLitE-SemZ-1}}}%
+\nwixlogsorted{c}{{Semisimple Lie algebra .scm}{NWLitE-SemR-1}{\nwixd{NWLitE-SemR-1}\nwixu{NWLitE-lieF-1}}}%
+\nwixlogsorted{c}{{Semi-standard Scheme procedures .scm}{NWLitE-Sema-1}{\nwixu{NWLitE-libB-1}\nwixd{NWLitE-Sema-1}}}%
+\nwixlogsorted{c}{{Sets .scm}{NWLitE-Set9-1}{\nwixu{NWLitE-libB-1}\nwixd{NWLitE-Set9-1}}}%
+\nwixlogsorted{c}{{Simple Lie algebras .scm}{NWLitE-SimO-1}{\nwixd{NWLitE-SimO-1}\nwixu{NWLitE-lieF-1}}}%
+\nwixlogsorted{c}{{Supplementary math .scm}{NWLitE-SupN-1}{\nwixd{NWLitE-SupN-1}}}%
+\nwixlogsorted{c}{{Vector and matrix tools .scm}{NWLitE-VecS-1}{\nwixu{NWLitE-libB-1}\nwixd{NWLitE-VecS-1}}}%
+\nwixlogsorted{c}{{Vector operations .scm}{NWLitE-VecM-1}{\nwixu{NWLitE-VecS-1}\nwixd{NWLitE-VecM-1}}}%
+\nwixlogsorted{c}{{Weight multiplicities computation .scm}{NWLitE-Weic-1}{\nwixu{NWLitE-RepK-2}\nwixd{NWLitE-Weic-1}}}%
+\nwixlogsorted{c}{{library.scm}{NWLitE-libB-1}{\nwixd{NWLitE-libB-1}}}%
+\nwixlogsorted{c}{{lie-algebra.scm}{NWLitE-lieF-1}{\nwixd{NWLitE-lieF-1}}}%
+\nwbegindocs{55}\nwdocspar
 \bibliography{LiterateLie}{}

### 2010-03-16 AffineLieAlgebras/InformalNotes/article.tex
Some work on semisimple affine algebras

@@
 \usepackage{pb-diagram}
-
+\usepackage{multicol}
 %\usepackage[utf8x]{inputenc}
@@
 \theoremstyle{definition} \newtheorem{Def}{Definition}
+\newcommand{\go}{\overset{\circ }{\frak{g}}}
+\newcommand{\ao}{\overset{\circ }{\frak{a}}}
+\newcommand{\co}[1]{\overset{\circ }{#1}}
 
@@
 Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
-underlying finite-dimensional subalgebras $\overset{\circ }{\frak{g}}$ and $%
-\overset{\circ }{\frak{a}}$ and an injection $\frak{a}\longrightarrow \frak{g%
+underlying finite-dimensional subalgebras $\go$ and $%
+\ao$ and an injection $\frak{a}\longrightarrow \frak{g%
 }$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
 correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
-}}^{\ast }$ and $\frak{h}_{\overset{\circ }{\frak{a}}}^{\ast }\subset \frak{h%
-}_{\overset{\circ }{\frak{g}}}^{\ast }$\ .
+}}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
+}_{\go}^{\ast }$\ .
 
@@
 
-$\overset{\circ }{\Delta }$ , $\left( \overset{\circ }{\Delta _{\frak{a}}}%
-\right) $ --- the finite root system of the subalgebra $\overset{\circ }{%
-\frak{g}}$ (resp. $\overset{\circ }{\frak{a}}$);
+$\co{\Delta}$ , $\left( \co{\Delta _{\frak{a}}}%
+\right)$ --- the finite root system of the subalgebra $\co{%
+\frak{g}}$ (resp. $\co{\frak{a}}$);
 $\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);
@@
 
-$\overset{\circ }{\xi }$ , $\overset{\circ }{\xi _{\left( \frak{a}\right) }}$
+$\co{\xi }$ , $\co{\xi _{\left( \frak{a}\right) }}$
 --- the finite (classical) part of the weight $\xi \in P$ , $\left( \text{%
@@
 
-$\lambda =\left( \overset{\circ }{\lambda };k;n\right) $ --- the
-decomposition of an affine weight indicating the finite part $\overset{\circ
-}{\lambda }$, level $k$ and grade $n$\ .
+$\lambda =\left( \co{\lambda };k;n\right) $ --- the
+decomposition of an affine weight indicating the finite part $\co{\lambda }$, level $k$ and grade $n$\ .
 
@@
 L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
-coordinates $\left( \overset{\circ }{\xi },k,n,\epsilon \left( w\left( \xi
+coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
 \right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
-)-\rho },$ (resp. $\left( \overset{\circ }{\xi },k,n,\epsilon \left(
+)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
 w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
@@
 Let $\gamma_{0} $ be the lowest vector with respect to the natural ordering in $%
-\overset{\circ }{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$ and decompose the defining relation (\ref{eq:11}),
+\co{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$ and decompose the defining relation (\ref{eq:11}),
 \begin{equation}
@@
   \right)
-\label{recurrent relation}
+\label{recurrent-relation}
 \end{multline}
@@
 
-We use the recurrent relation \eqref{recurrent relation} to formulate an algorithm for recursive computation of the branching coefficients.
+We use the recurrent relation \eqref{recurrent-relation} to formulate an algorithm for recursive computation of the branching coefficients.
 It is important to mention that the computation of the branching coefficients is performed without the  explicit construction of the module $L^{(\mu)}_{\mathfrak{g}}$ and any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
@@
 \item Calculate the anomalous branching coefficients in the main Weyl
-  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent relation}).
+  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent-relation}).
 \end{enumerate}
@@
 \end{figure}
-We use the recurrent relation (\ref{recurrent relation}) and get
+We use the recurrent relation (\ref{recurrent-relation}) and get
 following branching coefficients:
@@
   \label{eq:33}
-  \frac{(\overset{\circ }{\mu},\overset{\circ }{\mu}+2\rho)}{2(1+g)}+n=\frac{(\overset{\circ }{\nu},\overset{\circ }{\nu}+2\rho_{\mathfrak{a}})}{2(x_e+a)}
+  \frac{(\co{\mu},\co{\mu}+2\rho)}{2(1+g)}+n=\frac{(\co{\nu},\co{\nu}+2\rho_{\mathfrak{a}})}{2(x_e+a)}
 \end{equation}
@@
 Embedding of affine extensions of semisimple subalgebras to affine lie algebras allows additional construction of modular invariants \cite{difrancesco1997cft}, \cite{walton1989conformal}.
-Consider the conformal embedding constructed as the affine extension  $\mathfrak{a}_{1}\oplus\mathfrak{a}_{2}\subset \mathfrak{g}$ of the embedding of semisimple subalgebra $\overset{\circ}{\mathfrak{a}}_1\oplus\overset{\circ}{\mathfrak{a}}_2$ into simple Lie algebra $\overset{\circ}{\mathfrak{g}}$.
+Consider the conformal embedding constructed as the affine extension  $\mathfrak{a}_{1}\oplus\mathfrak{a}_{2}\subset \mathfrak{g}$ of the embedding of semisimple subalgebra $\ao_1\oplus\ao_2$ into simple Lie algebra $\go$.
 
@@
 
-Consider the embedding $\widehat{su(2)\oplus su(2)}\subset \hat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$.
+Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\widehat{su(2)\oplus su(2)}$ and $\mathfrak{g}= \widehat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$.
 Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}.
 We start with 4-dimensional representation of $su(2)\oplus su(2)$ with the highest weight $(1,1)$.
-
-, depicted at the Figure \ref{fig:a1a2a3}.
+The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1), \nu_2=(-1,1), \nu_3=(1,-1), \nu_4=(-1,-1)$.
+
+\begin{figure}[t]
+  \begin{multicols}{2}
+    \hfill
+    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
+    \hfill
+    \caption{Representation for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
+    \label{fig:A_1+A_1_to_A3}
+    \hfill
+    \includegraphics[width=50mm]{A1+A1-A3.pdf}
+    \hfill
+    \caption{Embedded roots for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
+    \label{fig:A1+A1-A3}
+  \end{multicols}
+\end{figure}
+
+Then for the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method}, so $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
+The embedded roots $\alpha_1,\alpha_2$ of $su(2)\oplus su(2)$ in terms of roots $\tilde{\alpha}_i$ of $su(4)$ are
+\begin{equation}
+  \label{eq:37}
+  \begin{array}{l}
+     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
+     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
+  \end{array}
+\end{equation}
+They are depicted at the Figure \ref{fig:A1+A1-A3}.
+
 This embedding is characterised by the embedding indexes $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
 
+We are interested in the reduction of the fundamental representations of $\widehat{su(4)}$.
 Four dominant weights of level one have the following coordinates in the orthogonal basis: 
@@
 \end{equation}
+
+These representation could be easily reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras, but we use our general method and discuss its features.
+
+For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
+\begin{equation}
+  \label{eq:38}
+  \begin{array}{lll}
+    \Delta^{+} &=&\left\{\co{\Delta}^{+};\; \co{\Delta}-n\delta;\;     -n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right. \\
+    & & \quad\left.\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\}\right\}\\
+    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm \alpha_2-n\delta;\; -n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
+  \end{array}
+\end{equation}
+
+The set $\Delta^{+}_{\bot}$ is empty. 
+\begin{enumerate}
+\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
+\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
+\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
+\item Construct the set $\Gamma$ \eqref{fan-defined}.
+\item Calculate the anomalous branching coefficients in the main Weyl
+  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent-relation}).
+\end{enumerate}
+
 We limit our computation by the fifth grade.

### 2010-03-16 AffineLieAlgebras/SchemePrograms/LiterateLie.tex
Minor fixes

--- 2010-01-14 AffineLieAlgebras/SchemePrograms/LiterateLie.tex
@@
 
-So we need just two following general functions:
+Also sometimes we need to know the determinant of Weyl group element and we can take it into account using the following version of the {\Tt{}reflect\nwendquote} function, called {\Tt{}reflect-with-eps\nwendquote}.
+
 \nwenddocs{}\nwbegincode{13}\sublabel{NW1VK18x-10zTlp-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}}\moddef{Functions for root systems .scm~{\nwtagstyle{}\subpageref{NW1VK18x-10zTlp-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-3yKaW-1}}\nwenddeflinemarkup
@@
   (sub weight (mul (prod weight (co-root root)) root)))
+
+(define (reflect-with-eps weight root)
+  (if (or (null? (cdr weight))
+          (pair? (cdr weight)))
+      (let ((v (reflect weight root)))
+        (cons v (if (equal? weight v) 1 -1)))
+      (let ((v (reflect (car weight) root)))
+        (cons v (if (equal? (car weight) v) (cdr weight) (- (cdr weight)))))))
+
+(define (eps weight)
+  (if (or (null? (cdr weight))
+          (pair? (cdr weight)))
+      1
+      (cdr weight)))
+
+(define (no-eps weight)
+  (if (or (null? (cdr weight))
+          (pair? (cdr weight)))
+      weight
+      (car weight)))
 \nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{14}\nwdocspar
@@
 \nwenddocs{}\nwbegincode{19}\sublabel{NW1VK18x-1H68wy-3}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-3}}}\moddef{Root system methods .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1H68wy-1}}}\plusendmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-1pDr9o-1}}\nwprevnextdefs{NW1VK18x-1H68wy-2}{NW1VK18x-1H68wy-4}\nwenddeflinemarkup
-`(orbit ,
-  (lambda (self weights)
+`(general-orbit , (lambda (self weights reflect)
     (let ((addon 
@@
           weights
-          (send self 'orbit (union-set weights addon) )))))
+          (send self 'general-orbit (union-set weights addon) reflect )))))
+
+`(orbit ,
+  (lambda (self weights)
+    (send self 'general-orbit weights reflect)))
+
+`(orbit-with-eps ,
+  (lambda (self weights)
+    (send self 'general-orbit weights reflect-with-eps)))
 \nwused{\\{NW1VK18x-1pDr9o-1}}\nwendcode{}\nwbegindocs{20}\nwdocspar
@@
        \LA{}Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}\RA{})
-`(multiplicity , (lambda (self weight)
 \nwused{\\{NW1VK18x-3yKaW-1}}\nwendcode{}\nwbegindocs{32}\nwdocspar
@@
 Weight multiplicities are determined using the set of anomalous points, which is constructed by the code below.
+We use the recurrent relation
+\begin{equation}
+  m_{\xi }^{\left( \mu \right) }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
+-\left( w\cdot\rho-\rho \right) }^{\left( \mu \right) }+\sum_{w\in W}\epsilon
+(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.  \label{gen-mult-form}
+\end{equation}
+The second term on the right-hand side is constructed with the code:
 \nwenddocs{}\nwbegincode{33}\sublabel{NW1VK18x-1y2eh2-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}}\moddef{Anomalous weights computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1y2eh2-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2w9Axe-2}}\nwenddeflinemarkup
@@
 \nwused{\\{NW1VK18x-2w9Axe-2}}\nwendcode{}\nwbegindocs{34}\nwdocspar
+Then multiplicity of the weight $\xi$ is calculated as the sum over the set $\omega\rho-\rho$, which we call ``star''
 
 \nwenddocs{}\nwbegincode{35}\sublabel{NW1VK18x-46EOV9-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}}\moddef{Weight multiplicities computation .scm~{\nwtagstyle{}\subpageref{NW1VK18x-46EOV9-1}}}\endmoddef\nwstartdeflinemarkup\nwusesondefline{\\{NW1VK18x-2w9Axe-2}}\nwenddeflinemarkup
+`(multiplicity , (lambda (self weight)
+                   (let ((star \LA{}Construct star .scm~{\nwtagstyle{}\subpageref{nw@notdef}}\RA{}))
+                     (-
+                      (sum (map (lambda (wg) (* (eps wg) (delta weight wg)))))
+                      (sum (map (lambda (wg)
+                                    (* (eps wg)
+                                       (send self 'multiplicity (sub weight wg))))
+                                  star))))))
 
@@
 
-\nwused{\\{NW1VK18x-2tcrGt-1}}\nwendcode{}
+\nwused{\\{NW1VK18x-2tcrGt-1}}\nwendcode{}\nwbegindocs{53}\nwdocspar
+
+\subsection{Supplementary mathematical functions}
+\label{sec:suppl-math-funct}
+
+\nwenddocs{}\nwbegincode{54}\sublabel{NW1VK18x-1tnUC5-1}\nwmargintag{{\nwtagstyle{}\subpageref{NW1VK18x-1tnUC5-1}}}\moddef{Supplementary math .scm~{\nwtagstyle{}\subpageref{NW1VK18x-1tnUC5-1}}}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
+
+(define (delta weight1 weight2)
+  (equal? (no-eps weight1) (no-eps weight2)))
+\nwnotused{Supplementary math .scm}\nwendcode{}
 
@@
 \nwixlogsorted{c}{{Commutative algebra .scm}{NW1VK18x-I1QOi-1}{\nwixd{NW1VK18x-I1QOi-1}\nwixu{NW1VK18x-3yKaW-1}}}%
+\nwixlogsorted{c}{{Construct star .scm}{nw@notdef}{\nwixu{NW1VK18x-46EOV9-1}}}%
 \nwixlogsorted{c}{{Functions for root systems .scm}{NW1VK18x-10zTlp-1}{\nwixd{NW1VK18x-10zTlp-1}\nwixu{NW1VK18x-3yKaW-1}}}%
@@
 \nwixlogsorted{c}{{Simple Lie algebras .scm}{NW1VK18x-379yCw-1}{\nwixd{NW1VK18x-379yCw-1}\nwixu{NW1VK18x-3yKaW-1}}}%
+\nwixlogsorted{c}{{Supplementary math .scm}{NW1VK18x-1tnUC5-1}{\nwixd{NW1VK18x-1tnUC5-1}}}%
 \nwixlogsorted{c}{{Vector and matrix tools .scm}{NW1VK18x-2tcrGt-1}{\nwixu{NW1VK18x-15DMjX-1}\nwixd{NW1VK18x-2tcrGt-1}}}%
@@
 \nwixlogsorted{c}{{Weight multiplicities computation .scm}{NW1VK18x-46EOV9-1}{\nwixu{NW1VK18x-2w9Axe-2}\nwixd{NW1VK18x-46EOV9-1}}}%
-\nwbegindocs{53}\nwdocspar
-
+\nwbegindocs{55}\nwdocspar
 \bibliography{LiterateLie}{}

### 2010-03-16 AffineLieAlgebras/InformalNotes/article.tex
More work on affine semisimple Lie algebras

@@
 The set $\Delta^{+}_{\bot}$ is empty.
+
+We limit our computation by the fifth grade.
+The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_1$ is shown at the Figure.
+We omit similar pictures for $\omega_0, \omega_2,\omega_3$ and include only the branching coefficients for these modules to save the space.
+
 \begin{enumerate}
@@
 
-We limit our computation by the fifth grade.
-The set of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements.
-
 \subsubsection{Non-maximal conformal embedding}

### 2010-03-30 AffineLieAlgebras/InformalNotes/article.tex
Some minor changes.

--- 2010-03-16 AffineLieAlgebras/InformalNotes/article.tex
@@
 
-  In the next section we describe an algorithm for the computation of branching coefficients based on the relation \eqref{recurrent relation}.
+  In the next section we describe an algorithm for the computation of branching coefficients based on the relation \eqref{recurrent-relation}.
 
@@
 
-Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent relation}) gives us
+Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent-relation}) gives us
 \begin{equation}
@@
 The set $\Delta^{+}_{\bot}$ is empty. 
+The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}.
+\begin{figure}[h!tb]
+  \includegraphics[width=150mm]{A1+A1-A3_fan.pdf}
+  \caption{Fan for the special embedding $\widehat{su(2)\oplus su(2)}\subset \widehat{su(4)}$}
+  \label{fig:A1+A1-A3_fan}
+\end{figure}
+
+We limit our computation by the fifth grade.
+
+\begin{figure}[h!tb]
+  \includegraphics[width=150mm]{A1+A1-A3_anom.pdf}
+  \caption{Projected anomalous weights $\pi_{\mathfrak{a}}\left(\widehat{\Psi ^{\left( \mu \right) }}\right)$ for $L^{(\omega_1)}_{A_3}$}
+  \label{fig:A1+A1-A3_anom}
+\end{figure}
+
+The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_1$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
+We omit similar pictures for $\omega_0, \omega_2,\omega_3$ and include only the branching coefficients for these modules to save the space.
+
 \begin{enumerate}
-\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
-\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\Gamma$ \eqref{fan-defined}.
 \item Calculate the anomalous branching coefficients in the main Weyl
@@
 \end{enumerate}
-
-We limit our computation by the fifth grade.
-The set of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements.
 

### 2010-04-28 AffineLieAlgebras/InformalNotes/article.tex
The example A1+A1\subset A3 is completed. Although Maple code is broken.

@@
 
-$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ --- the reduction of the representation;
+$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ --- the reduction of the module;
 
@@
 
-Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is is the level of the weight and the fourth the grade.
+Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0;1;0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the level of the weight and the fourth is the grade.
 
@@
   \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
-  \caption{The anomalous weights of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
+  \caption{The anomalous weights of the $(1,0;1;0)$ representation of the algebra $\hat{B_2}$}
   \label{fig:affine_B2_anom_point}
@@
 
-\section{Physical applications}
+\section{Applications to conformal field theory}
 \label{sec:phys-appl}
@@
 
-Here we want to discuss possible applications of the described techniques in physical (?) models.
-
 Branching coefficients for an embedding of affine Lie subalgebra into
 affine Lie algebra can be used to construct modular invariant
-partition functions for Wess-Zumino-Novikov-Witten models (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
+partition functions for Wess-Zumino-Novikov-Witten models of conformal field theory (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
+In these models currents algebras are affine Lie algebras.
 For the construction to be valid the embedding is required to be conformal, which means that the central charge of the subalgebra is equal to the central charge of the algebra:
@@
 
- The class of conformal embeddings is not rich, the complete classification is given in the paper \cite{schellekens1986conformal}.
-The requirement (\ref{eq:31}) allows to reduce the problem of finding the branching coefficients for affine Lie algebras to the computation of branching coefficients for finite-dimensional Lie algebras.
-
-Here we describe this procedure and discuss how the requirement (\ref{eq:31}) can be used to simplify the algorithm \ref{sec:algorithm}.
-
-Let $J^{a_j}_{-n_j}$ and $\tilde{J}^{a'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and of $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
+Let $X^{a_j}_{-n_j}$ and $\tilde{X}^{a'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and of $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
 Let $\pi_{\mathfrak{a}}$ be the projection operator of $\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$.
@@
   \label{eq:109}
-  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+  X^{a_1}_{-n_1}X^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
 \end{equation}
@@
   \label{eq:110}
-  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
+  \tilde{X}^{a'_1}_{-n_1}\tilde{X}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
 \end{equation}
@@
 
+The class of conformal embeddings is not rich, the complete classification is given in the paper \cite{schellekens1986conformal}.
+The requirement (\ref{eq:31}) allows to reduce the problem of finding the branching coefficients for affine Lie algebras to the computation of branching coefficients for finite-dimensional Lie algebras.
+
 If we have modular-invariant partition function for the fields described by a representation of the algebra $\mathfrak{g}$ this modular invariance is preserved by the projection on the subalgebra $\mathfrak{a}$, but we need also the preservation of the conformal invariance.
@@
 \end{equation}
-\begin{comment}
-The problem is also considered in the \cite{coquereaux2008conformal}.  
-\end{comment}
+Recently the problem of the conformal embeddings was considered in the paper \cite{coquereaux2008conformal}.
 
@@
 Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $su(2)\subset su(3)$ with the embedding index $x_e=4$.
-The level of the algebra (what is it ?) $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the subalgebra $\tilde{k}=kx_e=4$.
-
-There exist three level one dominant weights $[1,0,0],\;[0,1,0],\;[0,0,1]$ in the weight space of $\hat{A}_2$.
-It is easy to see that the set $\Delta_{\bot}$ is empty. (Not only this set is empty but the orthogonal algebra is empty!)
-
-Let us consider the representation with the highest weight
-$w_0=(1,0,0)$ in details.
+The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.
+
+There exist three level one dominant weights in the weight space of $\hat{A}_2$.
+It is easy to see that the set $\Delta_{\bot}$ and the algebra $\mathfrak{a}_{\bot}$ are empty.
+
+Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details.
+Here the first two components are the Dynkin indices (coordinates in the fundamental weights basis) of the finite part of the weight.
 
 The set of the anomalous weights of this representation up to the sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}.
-We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration.
-(Where, how?
-What are the coordinates, it is very difficult to see anything even in the zero grade!)
+We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.
 
 \begin{figure}[h!tb]
-  \includegraphics[width=160mm]{AffineA2_A1_anom.pdf}
-  \caption{The anomalous weights of the $(1,0,1,0)$ representation of the algebra $\hat{A_2}$}
+  \includegraphics[width=180mm]{AffineA2_A1_anom.pdf}
+  \caption{The anomalous weights of the $(0,0;1;0)$ representation of the algebra $\hat{A_2}$}
   \label{fig:affine_A2_anom_point}
@@
 
-According to our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules (there are no such subalgebra here!)$L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
-The result of these caculations up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
+According to our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$.
+The result of these calculations up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
 \begin{figure}[h!tb]
@@
 Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
-(Isn't it obvious that all the zeros there make the picture unreadable?)
 \begin{figure}[p]
@@
 
-We see that inside the main
-Weyl chamber of $\hat{A}_1$ there are only two non-zero anomalous weights.
+We see that inside the main Weyl chamber of $\hat{A}_1$ there are only two non-zero anomalous weights.
 (Show the Weyl chambers on the Figure.) These are the branching coefficients.
@@
   \label{eq:43}
-  L^{[1,0,0]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[0,4]}\oplus L_{\hat{A_1}}^{[4,0]}.
+  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)]}.
 \end{equation}
@@
   \label{eq:44}
-   L^{[0,1,0]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[2,2]},\\
-   L^{[0,0,1]}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{[2,2]}.
+   L^{(1,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)},\\
+   L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
 \end{eqnarray}
@@
   \label{eq:45}
-  Z=\left|\chi_{[4,0]}+\chi_{[0,4]}\right|^2+2\chi_{[2,2]}^2.
+  Z=\left|\chi_{(4;4;0)}+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
 \end{equation}
@@
 
-Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\widehat{su(2)\oplus su(2)}$ and $\mathfrak{g}= \widehat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$.
+Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\widehat{su(2)}\oplus \widehat{su(2)}$ and $\mathfrak{g}= \widehat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$.
 Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}.
 We start with 4-dimensional representation of $su(2)\oplus su(2)$ with the highest weight $(1,1)$.
-The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1), \nu_2=(-1,1), \nu_3=(1,-1), \nu_4=(-1,-1)$.
+The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
 
@@
 The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}.
+Coordinates of fan element's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$.
+Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
 \begin{figure}[h!tb]
   \includegraphics[width=150mm]{A1+A1-A3_fan.pdf}
-  \caption{Fan for the special embedding $\widehat{su(2)\oplus su(2)}\subset \widehat{su(4)}$}
+  \caption{Fan for the special embedding $\widehat{su(2)}\oplus\widehat{su(2)}\subset \widehat{su(4)}$}
   \label{fig:A1+A1-A3_fan}
@@
   \includegraphics[width=150mm]{A1+A1-A3_anom.pdf}
-  \caption{Projected anomalous weights $\pi_{\mathfrak{a}}\left(\widehat{\Psi ^{\left( \mu \right) }}\right)$ for $L^{(\omega_1)}_{A_3}$}
+  \caption{Projected anomalous weights for $L^{\omega_1}_{A_3}$}
   \label{fig:A1+A1-A3_anom}
@@
 
-The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_1$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
-We omit similar pictures for $\omega_0, \omega_2,\omega_3$ and include only the branching coefficients for these modules to save the space.
-
-\begin{enumerate}
-\item Calculate the anomalous branching coefficients in the main Weyl
-  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent-relation}).
-\end{enumerate}
+The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,0,1;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
+Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$.
+Weight $g$ are shown by cross if the corresponding value $\epsilon(\omega)=1$ and by diamond otherwise.
+
+We omit similar pictures for $\omega_0, \omega_1,\omega_3$ and include only the branching coefficients for these modules to save the space.
+
+The anomalous branching coefficients for the module $L^{(\omega_1)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
+\begin{figure}[h!tb]
+  \includegraphics[width=180mm]{A1+A1-A3_branching.pdf}
+  \caption{Anomalous branching coefficients for $L^{(0,0,1;1;0)}_{A_3}$}
+  \label{fig:A1+A1-A3_branching}
+\end{figure}
+
+ We get the following branching rules
+ \begin{equation}
+   \label{eq:39}
+   \begin{array}{ll}
+     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
+     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
+     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
+     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
+   \end{array}
+ \end{equation}
+
+The branching functions are constant and the finite reducibility theorem holds.
 
@@
 But we can consider the chain of embeddings $\mathfrak{a}\subset\mathfrak{g}_1\subset\mathfrak{g}_2$.
-We can use the embedding $\hat{A}_1\subset\hat{A}_2\subset\hat{A}_{?}$.
+We can use the embedding $\hat{A}_1\subset\hat{A}_1\oplus\hat{A}_1\subset\hat{A}_{3}$.
 Modular invariant partition function for this case could be obtained in two steps.
-First one can compute branching coefficients for $\hat{A}_2\subset\hat{A}_{?}$ and get partition function for $\hat{A}_2$ and then substitute the results of the previous section \ref{sec:spec-embedd-hata_1s} into it to get the new partition function for $\hat{A}_1$.
+First one can compute branching coefficients for $\hat{A}_1\oplus\hat{A}_1\subset\hat{A}_{3}$ and get partition function for $\hat{A}_1\oplus\hat{A_1}$ and then substitute the results of the previous section \ref{sec:spec-embedd-hata_1s} into it to get the new partition function for $\hat{A}_1$.
 

### 2010-04-30 AffineLieAlgebras/InformalNotes/article.tex
The physical section is completed.

@@
 \label{sec:phys-appl}
-(This part must be changed considerably.
-First it is necessary to restore our notations instead of the Di Francesco notations.
-Starting with $J^{a_j}_{-n_j}$ which is too archaic!
-Second but much more important: the example that you had presented refers to the case where the initial injection fan method remains unmodified.
-Are there any other cases where the modified fan method is necessary?
-Fourth, you write "we should select only those highest-weight modules of the subalgebra $\mathfrak{a}$ for which the relation (\ref{eq:111}) holds", where does this selection happens and where is it in the example?
-Fifth, again the notations, it is of no use to indicate the Dynkin indices of the fund.
-weights ("three level one dominant weights $[1,0,0],\;[0,1,0],\;[0,0,1]$" ) for the reader it is interesting what are they like here; we never place the level indices in the first place as in "with the highest weight $w_0=(1,0,0)$" see the section Notations.
-In the Figure 12 the irrep is written to be (1,0,1,0) -- very strange!
-Sixth,
-in all the figures it is difficult to see anything and at the same time there are almost no explanations, even the boxes and dots are not commented.
-Some other corrections are made directly in the text.)
 
@@
 The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance, but it is not the case for the energy-momentum tensor.
-So the energy-momentum tensor of the larger theory should consist only of generators of $\tilde{J}$.
+So the energy-momentum tensor of the larger theory should consist only of generators of $\tilde{X}$.
 Then $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow c(\mathfrak{g})=c(\mathfrak{a})$.
@@
 
-For the maximal conformal embedding $\mathfrak{a}\subset\mathfrak{g}$ it is easy to see that $\mathfrak{a}_{\bot}$ is trivial, otherwise it would be non-maximal, since $\mathfrak{a}\subset\mathfrak{a}\oplus\mathfrak{a}_{\bot}\subset\mathfrak{g}$.
-We can get non-maximal conformal embeddings through the chain of maximal $\mathfrak{a}\subset\mathfrak{g}_1\subset\mathfrak{g}_2$.
-In this case the representations of $\mathfrak{g}_1,\mathfrak{g}_2$ have to be of level one, due to the equation \eqref{eq:111}.
-If we limit the consideration by the affine extensions of simple classical Lie algebras, the number of possible non-maximal conformal embeddings is rather small \cite{schellekens1986conformal}.
-We study the example of $\hat{A}_1\subset \hat{A}_2\subset\hat{A}_{?}$ in the section \ref{sec:non-maxim-conf}.
+It is important to note that the orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
+It can be seen from the following consideration.
+In the case of the conformal embedding energy-momentum tensors are to be equal
+\begin{equation}
+  \label{eq:46}
+  T_{\mathfrak{a}}(z)=T_{\mathfrak{g}}(z)
+\end{equation}
+The energy-momentum tensor can be expanded into the modes $L_n$
+\begin{equation}
+\label{eq:47}
+  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
+\end{equation}
+The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
+\begin{equation}
+\label{eq:48}
+  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
+\end{equation}
+The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$.
+But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
 
@@
 \begin{figure}[h!tb]
+  \centering
   \includegraphics[width=180mm]{AffineA2_A1_anom.pdf}
@@
 the weights $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:AffineA2A1Fan}.
-Here we restricted the calculations to the first twelve grades.
+Here we restricted the calculations to the first eight grades.
 \begin{figure}[p]
@@
 
-The branching functions are constant and the finite reducibility theorem holds.
-
-\subsubsection{Non-maximal conformal embedding}
-\label{sec:non-maxim-conf}
-
-The example of the previous subsection \ref{sec:spec-embedd-hata_1s} has not demonstrated the features of our approach since the orthogonal subalgebra $\mathfrak{a}_{\bot}$ has been empty.
-
-But we can consider the chain of embeddings $\mathfrak{a}\subset\mathfrak{g}_1\subset\mathfrak{g}_2$.
-We can use the embedding $\hat{A}_1\subset\hat{A}_1\oplus\hat{A}_1\subset\hat{A}_{3}$.
-Modular invariant partition function for this case could be obtained in two steps.
-First one can compute branching coefficients for $\hat{A}_1\oplus\hat{A}_1\subset\hat{A}_{3}$ and get partition function for $\hat{A}_1\oplus\hat{A_1}$ and then substitute the results of the previous section \ref{sec:spec-embedd-hata_1s} into it to get the new partition function for $\hat{A}_1$.
-
-The algorithm of the section \ref{sec:algorithm} can be used to skip the intermediate computation.
+Now we can obtain modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
+\begin{multline}
+  \label{eq:40}
+  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
+  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
+\end{multline}
 

### 2010-05-12 AffineLieAlgebras/InformalNotes/article.tex
Illustrations regenerated

@@
 
-Using the recurrent relation for the anomalous branching coefficients we get the following result
+Using the recurrent relation for the anomalous branching coefficients we get the following result, presented at the Figure \ref{fig:AffineB2_A1_branching}.
+Dotted area represents the main Weyl chamber of the algebra $\hat{A}_1$.
 \begin{figure}[ph]
   \centering
-  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
+  \includegraphics[width=110mm]{AffineB2_A1_branching.pdf}
   \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
@@
 
-Selecting the elements inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
+Selecting the elements inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get for the branching coefficients up to twelfth grade
 \begin{multline}
@@
 Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details.
-Here the first two components are the Dynkin indices (coordinates in the fundamental weights basis) of the finite part of the weight.
+Here the first two components are the Dynkin indexes (coordinates in the fundamental weights basis) of the finite part of the weight.
 
@@
 Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
-\begin{figure}[p]
+\begin{figure}[ph]
   \centering
-  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
+  \includegraphics[width=110mm]{AffineA2_A1_branching.pdf}
   \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
@@
 
-We see that inside the main Weyl chamber of $\hat{A}_1$ there are only two non-zero anomalous weights.
-(Show the Weyl chambers on the Figure.) These are the branching coefficients.
+We see that inside the main Weyl chamber of $\hat{A}_1$, which is dotted at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights.
+These are the branching coefficients.
 So the finite reducibility theorem holds and we get the decomposition
@@
 We limit our computation by the fifth grade.
-
 \begin{figure}[h!tb]
-  \includegraphics[width=150mm]{A1+A1-A3_anom.pdf}
+  \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
   \caption{Projected anomalous weights for $L^{\omega_1}_{A_3}$}

### 2010-05-12 GeneralOverview/IntegrableSystems.tex

--- 2009-07-10 AffineLieAlgebras/ACMS2009/notes.tex
@@
 \begin{document}
-\tableofcontents
-\section{String theory}
-\label{sec:string-theory}
+\section{Интегрируемые системы}
+\label{sec:IntSys}
 
-Free relativistic particle action is equal to length of trajectory. 
-\begin{equation}
-  \label{eq:1}
-  \begin{split}
-  x^{\mu}(0)=x^{\mu}_0,\; x^{\mu}(1)=x^{\mu}_1\\
-  S=\int_{0}^{1} \sqrt{\left(\frac{dx^{\mu}}{d\tau}^2\right)}d\tau
-\end{split}
-\end{equation}
-There is Poincare invariance $x^{\mu}\to A^{\mu}_{\nu}x^{\nu}+ B^{\mu}$ and reparametrisation invariance $\tau\to f(\tau),\; x^{\mu}(\tau)\to x^{\mu}(f(\tau))$.
+\subsection{Интегируемые системы}
+\label{sec:-}
 
-String action is the area of world-sheet:
-\begin{equation}
-  \label{eq:2}
-  \begin{split}
-    X^{\mu}(x^1,x^2),\; \mu=1\dots d\\
-    S_N [X^{\mu}(x^1,x^2)]=\int \sqrt{det \frac{\partial X^{\mu}}{\partial x^a}\frac{\partial X^{\mu}}{\partial x^b}} dx^1 dx^2
-  \end{split}
-\end{equation}
-This action is called Nambu action, and it is invariant under Lorenz transformations and reparametrisations.
+Введение в квантовые интегрируемые системы и метод квантовой обратной задачи рассеяния.
 
-Transition amplitude for string is given by following formula:
-\begin{equation}
-  \label{eq:3}
-  A=\int {\cal D}X^{\mu}(x^1,x^2)e^{-S_N[X^{\mu}(x^1,x^2)]}
-\end{equation}
-The problem here is the definition of measure of integration. 
-It is not strictly defined in most cases, so there is nothing unusual here.
+Литература:
+  \begin{itemize}
+  \item Faddeev L.D. How Algebraic Bethe Ansatz works for integrable model. Arxiv preprint hep-th/9605187.
+  \item Korepin, VE and Bogoliubov, NM and Izergin, AG. Quantum inverse scattering method and correlation functions. Cambridge Univ Pr 1997.
+  \end{itemize}
 
-We want to change ``integration variable'' in order to fix the arbitrariness connected with reparametrisations of world-sheet.
+1.Квантовые интегрируемые системы. Анзац Бете. Квантовый метод обратной задачи рассеяния.
 
-Obviously our theory should be invariant under reparametrisation:
-\begin{equation}
-  \label{eq:4}
-  \begin{split}
-    x^a \to f^a (x^1,x^2)\\
-    X^{\mu}(x^1,x^2)\to \tilde{X}^{\mu}(x^1,x^2)=X^{\mu}(f^1(x^1,x^2),f^2(x^1,x^2))
-  \end{split}
-\end{equation}
-
-But Nambu action is not invariant. So we will use equivalent Polyakov action, which has following form:
-\begin{equation}
-  \label{eq:5}
-  \begin{split}
-    S_P [g^{ab}(x^1,x^2), X^{\mu}(x^1,x^2)]=\int g^{ab}(x)\partial_a X^{\mu} \partial_b X^{\mu}\sqrt{g} \;d^2 x\\
-    g=\det g_{ab}
-  \end{split}
-\end{equation}
-
-Polyakov and Nambu actions are equivalent in the sense that equations of motion are the same after the exclusion of auxiliary field $g_{ab}$.
-\begin{equation}
-  \label{eq:6}
-  \delta_{X}S_N=0 \Longleftrightarrow \left\{
-      \begin{aligned}
-        \delta_X S_P=0\\
-        \delta_g S_P=0
-      \end{aligned}
-      \right.
-\end{equation}
-Polyakov action is invariant under Lorenz transformations and reparametrisations:
-\begin{equation}
-  \label{eq:7}
-  \begin{split}
-    x^a \to f^a (x^1,x^2)\\
-    X^{\mu}(x^1,x^2)\to \tilde{X}^{\mu}(x^1,x^2)=X^{\mu}(f^1(x^1,x^2),f^2(x^1,x^2))\\
-    g_{ab}(x)\to \tilde{g}_{ab}(x)=\frac{\partial f^{a_1}}{\partial x^{a}}\frac{\partial f^{b_1}}{\partial x^b} g_{a_1 b_1}(x)
-  \end{split}  
-\end{equation}
-
-There is also one additional invariance, which is called conformal or Weyl invariance.
-\begin{equation}
-  \label{eq:8}
-  \begin{split}
-    g_{ab}(x)\to e^{\sigma(x)}g_{ab}(x)\\
-    g\to e^{\sigma} g\\
-    g^{ab}\to e^{-\sigma} g^{ab}\\
-    S_P[e^{\sigma(x)} g_{ab}(x),X^{\mu}] = S_P[g_{ab}(x),X^{\mu}] 
-  \end{split}
-\end{equation}
-
-So we have rather big freedom. For example, any metric on sphere can be obtained from one (constant) metric with reparametrisation and Weyl transformation.
-\begin{equation}
-  \label{eq:9}
-  g_{ab}(x)=[e^{\sigma(x)}\hat{g}_{ab}]^{x^a\to f^a (x)}
-\end{equation}
-For surfaces of higher genus there are discrete families of equivalent metrics.
-
-We could not preserve all the symmetries during quantization. So we choose to save Lorenz invariance and reparametrisation invariance and break conformal invariance. It is so called conformal anomaly.
-
-\begin{equation}
-  \label{eq:10}
-  A=\int {\cal D}X^{\mu}(x^1,x^2)e^{-S_P[g_{ab},X^{\mu}(x^1,x^2)]}
-\end{equation}
-
-It is easy to see that norm is invariant under reparametrisations:
-\begin{equation}
-  \label{eq:11}
-  \begin{split}
-    \|\delta X^{\mu}\|^2 = \int \left(\delta X^{\mu}(x)\right)^2 \sqrt{g} d^2x\\
-    \|\delta g_{ab}\|^2 = \int \delta g_{a_1 b_1}\delta g_{a_2 b_2} g^{a_1 a_2} g^{b_1 b_2} \sqrt{g}\; d^2x
-  \end{split}
-\end{equation}
-
-To investigate what happens top Weyl invariance after quantization let's introduce so called effective action. We integrate out fields $X^{\mu}$ and get following result.
-\begin{equation}
-  \label{eq:12}
-  e^{-S_X^{eff}[g_{ab}]} \overset{def}{=} \int {\cal D}X^{\mu} e^{-S_P [g_{ab},X]}
-\end{equation}
-\begin{equation}
-  \label{eq:13}
-  \begin{split}
-    S^{eff}_X [e^{\sigma(x)} g_{ab}(x) ] = S_X^{eff}[g_{ab}]+\frac{d}{48\pi}W[g,\sigma]\\
-    W[g,\sigma]=\int \left[ \frac{1}{2} g^{ab}\partial_a\sigma \partial_b\sigma+R[g]\sigma+\mu e^{\sigma}\right] \sqrt{g}\; d^2x
-  \end{split}
-\end{equation}
-Here $R$ is scalar curvature of $g_{ab}$, and $\mu$ is a parameter depending on regularisation, for example for proper time regularisation $\mu=\frac{1}{4\pi\epsilon}$.
-The term $W[g,\sigma]$ is called Liouville's action.
-
-{\bf Notice} $\int R[x] \sqrt{g}d^2x = 4\pi \chi_E$, $\chi_E=2-2h$, $\chi_E$ - Euler characteristic of the surface, $h$ - genus of the surface.
-
-$W[g,\sigma]$  is called conformal anomaly.
-
-Variance of action
-\begin{equation}
-  \label{eq:14}
-  \begin{split}
-    \delta S[g_{ab},X] = -\frac{1}{4\pi} \int  \delta g^{ab} T_{ab} \sqrt{g} \; d^2x\\
-    g_{ab}\to g_{ab}+\delta g_{ab}
-  \end{split}
-\end{equation}
-\begin{equation}
-  \label{eq:15}
-  \begin{split}
-    g_{ab} \to e^{\sigma} g_{ab} \xrightarrow[\sigma \ll 1]{} (1+\delta\sigma) g_{ab}\\
-    \delta S [g_{ab},X] = -\frac{1}{4\pi} \int \delta\sigma g^{ab} T_{ab} \sqrt{g}\, d^2 x
-  \end{split}
-\end{equation}
-\begin{equation}
-  \label{eq:16}
-    \delta S =0 \Rightarrow g^{ab}T_{ab}=0
-\end{equation}
-We see that Weyl invariance is equivalent to tracelessness of energy-momentum tensor.
-
-After the quantization we have
-\begin{equation}
-  \label{eq:17}
-  g^{ab}\left< T_{ab} \right> = -\frac{d}{12} R[g]
-\end{equation}
-\begin{Def}
-  {\bf Two dimensional conformal field theory} - is the theory that transforms as in (\ref{eq:13}).
-
-  The factor before $W[g,\sigma]$ is called {\it central charge}.
-\end{Def}
-
-!!!!!!!!!
-
-Why it is so? How this definition is connected with another definitions and properties of conformal field theory?
-
-!!!!!!!!!
-
-At this moment we have too much freedom in our Feynman integral (\ref{eq:10}).
-We have diffeomorphisms (\ref{eq:4}) and Weyl transformations (\ref{eq:8}).
-We will fix the gauge so that the metric is given by the formula
-\begin{equation}
-  \label{eq:20}
-  g_{ab}=[e^{\phi} \hat{g}_{ab}]^{f^a}
-\end{equation}
-
-Faddeev-Popov ghosts appear as usual after this procedure.
-
-\begin{equation}
-  \label{eq:19}
-  \begin{split}
-    A=\int {\cal D} X^{\mu}(x^1,x^2)e^{-S_P[g_{ab},X^{\mu}(x^1,x^2)]} = \\
-    = \int {\cal D}\phi\; {\cal D}X\; \mathcal{D} B_{ab}\; \mathcal{D} C^a e^{-S_P [e^{\phi}\hat{g}_{ab},X]-
-      S_{gh}[e^{\phi}\hat{g}_{ab},B,C]}
-  \end{split}
-\end{equation}
-Here $B,C$ are ghost fields, $B_{ab}(X)$ is symmetric and traceless tensor. All the functional integrals use metric $e^{\phi}\hat{g}$. 
-\begin{equation}
-  \label{eq:21}
-  S_{gh} = \int g^{ac} B_{ab} \nabla_c C^b \sqrt{g} \, d^2x
-\end{equation}
-We can fix Weyl invariance so that measures of integration over matter fields and ghosts fields in (\ref{eq:19}) don't depend on $\phi$. Then we get conformal anomaly in the exponent:
-\begin{equation}
-  \label{eq:22}
-  A = \int \mathcal{D}_{e^{\phi} \hat{g}} \mathcal{D}_{\hat{g}} X \mathcal{D}_{\hat{g}} B_{ab} \mathcal{D}_{\hat{g}} C^a e^{-S_P [e^{\phi}\hat{g}_{ab},X]-S_{gh}[e^{\phi}\hat{g}_{ab},B,C]+\frac{d-26}{48\pi} W[\hat{g}_{ab},\phi]}
-\end{equation}
-$\frac{d}{48\pi}$ comes from matter fields, and $\frac{-26}{48\pi}$ from ghost fields, since both actions are actions of two-dimensional conformal field theory.
-
-Ordinary bosonic string lives in 26-dimensional space and doesn't interact with Liouville's gravity.
-Such a string is called ``critical string'' since it can exist only in critical dimension.
-Other string models are called non-critical strings.
-
-First integration in (\ref{eq:22}) is very inconvenient, since we integrate over $\phi$ with measure depending on $\phi$. This measure $\mathcal{D}_{e^{\phi}\hat{g}}\phi$ corresponds to interval
-\begin{equation}
-  \label{eq:23}
-  \|\delta\phi\|^2_P = \int e^{\phi} (\delta\phi)^2 \sqrt{\hat{g}}\, d^2 x
-\end{equation}
-It is non-linear and is not invariant under the translations $\phi(x)\to \phi(x)+\eta(x)$.
-So for some time this was a problem since nobody knew how to work with such objects.
-
-But David-Distler-Kawai proposed to change action in order to take into account change of measure of integration to normal measure.
-
-They conjectured that the amplitude can be written in the form
-\begin{equation}
-  \label{eq:24}
-  A=\int \mathcal{D}_{\hat{g}}\phi\, \mathcal{D}_{\hat{g}} X\, \mathcal{D}_{\hat{g}} (B,C)\, e^{-S_P[\hat{g},X]-S_{gh}[\hat{g},B,C]-S_L[\hat{g},\phi]}
-\end{equation}
-where the measure $\mathcal{D}_{\hat{g}} \phi$ corresponds to the interval $\|\delta\phi\|^2_{DDK} = \int (\delta\phi)^2 \sqrt{\hat{g}}\, d^2x$ and it is invariant under the translations $\phi\to \phi+\eta$ ($\delta\phi\to \delta\phi$).
-$S_L$ here is Liouville's action with two undefined for now parameters $Q$ and $b$:
-\begin{equation}
-  \label{eq:25}
-  S_L[\hat{g},\phi] = \frac{1}{8\pi} \int \left[ \frac{1}{2} \hat{g}^{ab} \partial_a \phi \partial_b \phi + QR\phi +\mu e^{2b\phi}\right] \sqrt{\hat{g}} \, d^2x
-\end{equation}
-We choose following normalization:
-\begin{equation}
-  \label{eq:26}
-  \langle \phi(x) \phi(0) \rangle = \log |x|^2
-\end{equation}
-Liouville's term should be invariant under dilation $\hat{g}_{ab}\to e^{\sigma}\hat{g}_{ab}$.
-
-After we put
-\begin{equation}
-  \label{eq:27}
-  Q=\frac{1}{b}+b
-\end{equation}
-Liouville's action becomes conformal, so that
-\begin{equation}
-  \label{eq:28}
-  \begin{split}
-    \int \mathcal{D}_{\hat{g}} \phi e^{-S_L[\hat g,\phi]} = e^{-S_L^{eff}[\hat g]}\\
-    S_L^{eff} [e^{\sigma}\hat{g}]=S_L^{eff}[\hat g] +\frac{C_L}{12} W[\hat g,\sigma]
-  \end{split}
-\end{equation}
-Where
-\begin{equation}
-  \label{eq:29}
-  C_L=1+6 Q^2
-\end{equation}
-
-Then we require total central charge to vanish:
-\begin{equation}
-  \label{eq:30}
-  C_X+C_{gh}+C_L=C_{tot}=0
-\end{equation}
-
-Now the amplitude doesn't depend on $\hat{g}$ and parameters $Q$,$b$ are fixed.
-\begin{equation}
-  \label{eq:18}
-  d+1+6\left(b+\frac{1}{b}\right)^2=26
-\end{equation}
-In some finite area we can assume
-\begin{equation}
-  \label{eq:31}
-  \hat{g}_{ab}=\delta_{ab}
-\end{equation}
-There also could be additional term connected with the topology.
-
-Let's change variables
-\begin{equation}
-  \label{eq:32}
-  \begin{split}
-    x^1+i\, x^2=z\\
-    x^1-i\, x^2=\bar{z}\\
-    (dx^1)^2+(dx^2)^2=dz\,d\bar{z}
-  \end{split}
-\end{equation}
-For fields and terms of the action we have
-\begin{equation}
-  \label{eq:33}
-  \begin{split}
-    C^z=C,\; C^{\bar{z}}=\bar{C}\\
-    B_{zz}=B, \; B_{\bar{z}\bar{z}}=\bar{B}\\
-    S_{gh}=\int d^2z [B\bar{\partial}C+\bar{B}\partial \bar{C}]\\
-    S_P[X]=\int d^2z \bar{\partial}X \partial X\\
-    S_L[\phi] \propto \int d^2z \left[\bar{\partial} \phi \partial \phi+\mu e^{2 b \phi}\right] + \mbox{(topological terms)}
-  \end{split}
-\end{equation}
-\begin{equation}
-  \label{eq:34}
-  e^{-S^{eff}[g]}=\int \mathcal{D} X e^{-\int g^{ab}\partial_a X \partial_b X \sqrt{g}\, d^2x} = \int \mathcal{D}_g X e^{-\int X \Delta X\sqrt{g}\, d^2x}
-\end{equation}
-Laplace operator depends on metric
-\begin{equation}
-  \label{eq:35}
-  \Delta = \frac{1}{\sqrt{g}}\partial_a \sqrt{g} g^{ab}\partial_b
-\end{equation}
-
-It is self-conjugate operator.
-
-We can represent field $X$ as combination of eigenfunctions of Laplace operator $X(x)=\sum c_n X_n,\; \Delta X_n = \lambda_n X_n,\; \lambda_n=\lambda_n[g]$.
-Then we will integrate over all eigenfunctions:
-\begin{equation}
-  \label{eq:36}
-  e^{-S^{eff}[g]}=\left(\prod_{n} \lambda_n\right)^{-\frac{1}{2}}=(\det \Delta)^{-\frac{1}{2}}
-\end{equation}
-Obviously we could not calculate $\lambda_n$, but we can get the determinant.
-\begin{equation}
-  \label{eq:37}
-  S^{eff}[g]=\log \det \Delta=tr \log \Delta
-\end{equation}
-\begin{equation}
-  \label{eq:38}
-  \log\frac{\lambda}{\lambda_0}=\int_0^{\infty}\frac{e^{-\lambda t}-e^{\lambda_0 t}}{t}dt
-\end{equation}
-\begin{equation}
-  \label{eq:39}
-  \delta S^{eff}[g]=tr (\log\Delta -\log\Delta_{g_0})=\delta tr \int_0^{\infty}\frac{e^{-\Delta t}}{t} dt
-\end{equation}
-The last integral diverges, so we need to regularise it. We will use heat kernel regularisation.
-\begin{equation}
-  \label{eq:40}
-  \delta S^{eff}[g]=\delta tr \int_{\epsilon}^{\infty}\frac{e^{-\Delta t}}{t} dt  
-\end{equation}
-As we already mentioned, $\hat{g}_{ab}$ could be put equal to $\rho dz d\bar{z}$ in finite area. Then
-\begin{equation}
-  \label{eq:41}
-  \Delta=\frac{1}{\rho}\bar{\partial}\partial
-\end{equation}
-For variation of effective action we have
-  \begin{multline}
-  \label{eq:42}
-    \delta_{\rho}S^{eff}[g]=\delta_{\rho} tr \int_{\epsilon}^{\infty} e^{-\frac{1}{\rho}\bar{\partial}\partial t}\frac{dt}{t}=\\
-    - tr \int_{\epsilon}^{\infty}\delta_{\Delta}e^{-\Delta t} dt=
-    -tr \int_{\epsilon}^{\infty}\frac{\delta\rho}{\rho}\Delta e^{-\Delta t} dt=\\
-    -tr \int_{\epsilon}^{\infty}\frac{\delta\rho}{\rho}\frac{d}{dt} e^{-\Delta t} dt=-tr \frac{\delta\rho}{\rho}e^{-\Delta \epsilon}
-  \end{multline}
-
-Let's introduce Green function for heat equation
-\begin{equation}
-  \label{eq:43}
-  G(t,x,y)=\sum_n e^{-\lambda_n t}X_n(x) X_n(y)
-\end{equation}
-\begin{equation}
-  \label{eq:44}
-  \begin{split}
-    \frac{\partial G}{\partial t}=\Delta_x G(t,x,y)\\
-    G(o,x,y)=\delta^2 (x-y)\\
-    G(t,x,x)=\frac{1}{4\pi t}+aR+O(t)
-  \end{split}
-\end{equation}
-Then for variation of action we have
-\begin{equation}
-  \label{eq:45}
-  \delta S^{eff}[g]=\int d^2x \frac{\delta\rho}{\rho}\left(\frac{1}{4\pi\epsilon}+aR\right)
-\end{equation}
-
-!!!! !!!! !!!! !!!! 
-Be more elaborate here.
-!!!!!!!
-
-...
-\section{Conformal Field Theory}
-\label{sec:cft}
-
-\subsection{General properties}
-\label{sec:general-properties}
-
-In Conformal Field Theory 
-\begin{equation}
-  \label{eq:46}
-  g^{ab}\left<T_{ab}\right>=\frac{C}{12}R[g]
-\end{equation}
-$C$ is a central charge.
-
-For flat metric $g_{ab}=\delta_{ab}$ we have
-\begin{equation}
-  \label{eq:47}
-  g^{ab}\langle T_{ab} \rangle=0
-\end{equation}
-Then we put $T_{zz}=T,\quad T_{\bar{z}\bar{z}}=\bar{T},\quad T_{z\bar{z}}=T_{\bar{z}z}$. In flat space from continuity equation $\bar{\partial}T_{zz}+\partial T_{\bar{z}\bar{z}}=0$ we have
-\begin{equation}
-  \label{eq:49}
-  \begin{split}
-    T_{z\bar{z}}=0\\
-    \bar{\partial}T_{zz}=\bar{\partial}T=0,\quad T \mbox{- holomorphic}\\
-    \partial T_{\bar{z}\bar{z}}=\partial \bar{T}=0,\quad \bar{T} \mbox{- antiholomorphic}\\
-  \end{split}
-\end{equation}
-In curved space continuity equation reads $\nabla_a T^{ab}=0$ and we can choose coordinate system where $g_{ab}dx^a dx^b = \rho dz\, d\bar{z}=e^{\sigma}dz\,d\bar{z}$.
-Then we introduce pseudo energy $T$:
-\begin{equation}
-  \label{eq:50}
-  T_{zz}+\frac{C}{12}t_{zz}=T
-\end{equation}
-where $t_{zz}=(\partial \sigma)^2-2\partial^2 \sigma$. It is easy to check that $\bar{\partial}T=0$ in this case.
-
-For transformations $z\to w(z)$
-\begin{equation}
-  \label{eq:51}
-  \begin{split}
-    T_{zz}\to \left(\frac{dw}{dz}\right)^2 T_{ww}(w(z))\\
-    t\to \left(\frac{dw}{dz}\right)t(w)+2\{w,z\}\\
-    \mbox{where}\; \{w,z\}=\left(\frac{\partial_z^3 w}{\partial_z w}-\frac{3}{2}\left(\frac{\partial_z^2 w}{\partial_z}\right)^2\right)\\
-    T\to \left(\frac{dw}{dz}\right)^2 T(w)+\frac{C}{12}\{w,z\}\\
-  \end{split}
-\end{equation}
-Energy-momentum tensor is the generator of coordinate transformations $x^a\to x^a+\epsilon^a(x)$:
-\begin{equation}
-  \label{eq:52}
-  \delta_{\epsilon}\langle A_1(x_1)\dots A_N(x_N)\rangle = \int d^2x\, \partial_a \epsilon_b(x)\langle T_{ab}(x) A_1(x_1)\dots A_N(x_N)\rangle
-\end{equation}
-
-\begin{equation}
-  \label{eq:53}
-  \begin{split}
-    T_{aa}=0\\
-    \partial_a \epsilon_b+\partial_b \epsilon_a\sim \delta_{ab}\\
-    \epsilon^a=\epsilon x^a \;\mbox{or}\; x^a\to \frac{x^a}{(\vec x)^2}
-  \end{split}
-\end{equation}
-Correlation functions don't change under conformal transformations.
-\begin{equation}
-  \label{eq:54}
-  \delta_{\epsilon}A(x)=\int_{\partial D} dy^a\, \epsilon^b \tilde{T}_{ab}(y)A(x)-\int_{D}d^2y\, \partial^a \epsilon^b(y)T_{ab}(y)A(x)
-\end{equation}
-Where $\tilde{T}_{ab}=\epsilon_{ac}T_{cb}$.
-
-Let
-\begin{equation}
-  \label{eq:55}
-  \begin{split}
-    \partial_a \epsilon_b+\partial_b \epsilon_a\sim \delta_{ab}\\
-    \bar{\partial}\epsilon=0\\
-    z\to z+\epsilon(z,\bar{z})\\
-    \bar{z}\to\bar{z}+\bar{\epsilon}(z,\bar{z})
-  \end{split}
-\end{equation}
-\begin{equation}
-  \label{eq:56}
-  \delta_{\epsilon}A(z,\bar{z})=\oint_z du\, \epsilon(u) T(u) A(z,\bar{z})
-\end{equation}
-Substituting $T(z)$ in place of arbitrary operator $A$ we get 
-\begin{equation}
-  \label{eq:57}
-  \delta_{\epsilon}T(z)=\oint_z du\, \epsilon(u)T(u)T(z)
-\end{equation}
-
-If $w(z)=z+\epsilon(z)$ where $\epsilon$ is small, $T$ transforms as following:
-\begin{equation}
-  \label{eq:58}
-  T(z)\to \epsilon T'(z) + 2\epsilon' T(z)+\frac{C}{12}\epsilon'''
-\end{equation}
-\begin{equation}
-  \label{eq:59}
-  \delta_{\epsilon}T(z)=\oint du\, \epsilon(u) T(u) T(z) = \epsilon T'(z) + 2\epsilon' T(z)+\frac{C}{12}\epsilon'''
-\end{equation}
-We suppose that for full set of operators $\{A_j(x)\}$ there exists operator product expansion:
-!!! How can it be proved ????
-\begin{equation}
-  \label{eq:60}
-  A_i(x)A_j(0)=\sum C^k_{ij}(x)A_k(0)
-\end{equation}
-Then for product $T(u)T(z)$ we have
-\begin{equation}
-  \label{eq:61}
-  T(u)T(z)=\sum C_k(u-z) A_k(z)
-\end{equation}
-We can recover the poles from formula (\ref{eq:59}):
-\begin{equation}
-  \label{eq:62}
-  T(u)T(z)=\frac{C}{2(u-z)^4}+\frac{2T(z)}{(u-z)^2}+\frac{T'(z)}{u-z}+\mbox{non-singular terms}
-\end{equation}
-Now introduce the operators $L_n$:
-\begin{equation}
-  \label{eq:63}
-  L_n A(z)\equiv \frac{}{2\pi i}\oint_{C}du\, (u-z)^{n+1}T(u)A(z)
-\end{equation}
-It is possible to show that for $n,m\in \mathbb{Z}$
-\begin{equation}
-  \label{eq:64}
-  [L_n,L_m]=(n-m) L_{n+m}+\frac{C}{12}(n^3-n)\delta_{n,-m}
-\end{equation}
-and $\{L_n\}$ constitute Virasoro algebra.
-
-All the fields in the theory are sums of multiplets of Virasoro algebra:
-\begin{equation}
-  \label{eq:65}
-  \{A_j\}=\sum [\Phi_{\Delta,A}] %%% It is incorrect, fix this formula
-\end{equation}
-
-There is a primary field in every multiplet:
-\begin{equation}
-  \label{eq:66}
-  \begin{split}
-    \Phi_{\Delta}(z)\underset{z\to w(z)}{\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\Phi_{\Delta}(w(z))\\
-    L_n \Phi=0,\quad n>0\\
-    L_0 \Phi=\Delta \Phi\\
-  \end{split}
-\end{equation}
-All other fields are built of primary fields and are called secondary:
-\begin{equation}
-  \label{eq:67}
-  L_{-n_1}L_{-n_2}\dots \Phi_{\Delta}
-\end{equation}
-
-Correlation functions are expressed as combinations of correlation functions of primary fields.
-
-The only thing that is yet undefined is the set of scaling dimensions of primary fields.
-So to fix the theory we should define $\Phi_a,\; \Delta_a,\; C^c_{ab}$.
-Then our theory is solved.
-If the number of primary fields is finite, such a model is called {\it minimal}.
-
-For example, following fields are Weyl-invariant:
-\begin{equation}
-  \label{eq:68}
-  O_a=\int \Phi_{\Delta}e^{2a\phi}\,d^2x,\quad \mbox{where}\;\Delta+a(Q-a)=1
-\end{equation}
-$O_a$ - is the main observable of string theory with gravitational dimension $\delta_a=-\frac{a}{b}$.
-\begin{equation}
-  \label{eq:69}
-  \int\langle O_{a_1}\dots O_{a_n}\rangle_{\mu} e^{-\mu A}d\mu=\langle O_{a_1}\dots O_{a_n}\rangle_{A}=A^{\sum \delta_k},\quad \delta_k=\frac{a_k}{b}
-\end{equation}
-\subsection{Connection with string theory}
-
-We can start from arbitrary conformal field theory, find $b$ from equation $C+6\left(b+\frac{1}{b}\right)^2=25$ and obtain some non-critical string theory.
-But for $d>1$ $b$ becomes complex and this fact leads to unsolved yet problems.
-
-\subsection{Wess-Zumino-Novikov-Witten models}
-\label{sec:WZNW}
-
-Let's start with non-linear $\sigma$-model.
-\begin{equation}
-  \label{eq:48}
-  S_0=\frac{1}{4a^2}\int d^2x\; Tr' (\partial^{\mu}g^{-1}\partial_{\mu}g)
-\end{equation}
-Here $a^2>0$ is a positive parameter, $g(x)\in G$ - field on Lie group $G$, which we will assume to be semi-simple and by $Tr'$ we have denoted representation independent trace of Lie algebra $\mathfrak{g} $
-\begin{equation}
-  \label{eq:70}
-  Tr'=\frac{1}{x_{rep}}Tr
-\end{equation}
-$x_{rep}$ is the Dynkin index of the representation.
-
-In this model the conformal invariance is lost at the quantum level, as it can be seen along the lines of previous sections.
-!!! Show it by example !!!
-
-Also we can see that holomorphic and antiholomorphic currents aren't conserved individually. The equations of motion are
-\begin{equation}
-  \label{eq:71}
-  \partial^{\mu}(g^{-1}\partial_{\mu}g)=0
-\end{equation}
-The currents are
-\begin{equation}
-  \label{eq:currents}
-  J_{\mu}=g^{-1}\partial_{\mu}g
-\end{equation}
-or in the complex coordinates
-\begin{equation}
-  \label{eq:74}
-  \begin{matrix}
-    & \tilde{J}_z=g^{-1}\partial_z g, & \tilde{J}_{\bar{z}}=g^{-1}\partial_{\bar{z}}g\\
-    & \partial_z \tilde{J}_{\bar{z}}+\partial_{\bar{z}}\tilde{J}_z=0 & \\
-  \end{matrix}
-\end{equation}
-The terms of the equation of motion can not be null separately because $\partial_{\mu}(\epsilon^{\mu\nu}J_{\nu})\neq 0$.
-
-So we add WZ-term to the action and redefine the currents in more appropriate way
-\begin{equation}
-  \label{eq:72}
-  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
-\end{equation}
-
-Wess-Zumino term has the following form
-\begin{equation}
-  \label{eq:73}
-\Gamma=  - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr'\left(
-    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
-\end{equation}
-
-This term is defined on the three-dimensional manifold $B$ whose boundary is original two-dimensional space.
-By $\tilde{g}$ we have denoted the extension of the field $g$ to $B$.
-This extension isn't unique.
-In a compactified three-dimensional space a compact two-dimensional manifold delimits two three-dimensional manifolds.
-The difference between this two choices $\Delta\Gamma$ is given by the right hand side of (\ref{eq:73}) with the integration range extended over the whole compact three-dimensional space.
-Since the latter is topologically equivalent to the three-sphere we have
-\begin{equation}
-  \label{eq:75}
-\Delta\Gamma=  - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left(
-    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
-\end{equation}
-$\Delta\Gamma$ is defined modulo $2\pi i$, so the Euclidean functional integral with weight $exp(-\Gamma)$ is well-defined. Clearly, any coupling constant multiplying this term must be an integer.
-
-We then consider the action
-\begin{equation}
-  \label{eq:76}
-  S=S_0+k\Gamma
-\end{equation}
-where $k$ is an integer. 
-The equation of motion for the full action (\ref{eq:76}) is
-\begin{equation}
-  \label{eq:77}
-  \partial^{\mu}(g^{-1}\partial_{\mu}g)+\frac{a^2 ik}{4\pi}\epsilon_{\mu\nu}\partial^{\mu}(g^{-1}\partial^{\nu}g)=0
-\end{equation}
-It can be rewritten using complex coordinates as
-\begin{equation}
-  \label{eq:78}
-  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
-\end{equation}
-We see that when $a^2=\frac{4\pi}{k}$ we have the desired conservation law
-\begin{equation}
-  \label{eq:79}
-  \partial_z(g^{-1}\partial{\bar z}g)=0
-\end{equation}
-For currents
-\begin{equation}
-  \label{eq:4}
-  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
-\end{equation}
-
-The solution of classical equation is
-\begin{equation}
-  \label{eq:80}
-  g(z,\bar z)=f(z)\bar f(\bar z)
-\end{equation}
-for arbitrary functions $f(z)$ and $\bar f (\bar z)$.
-
-The separate conservation of the currents $J_z,\; J_{\bar z}$ implies the invariance of the action under the transformations
-\begin{equation}
-  \label{eq:81}
-   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)
-\end{equation}
-where $\Omega,\;\bar \Omega \in G$. So we have local $G(z)\times G(\bar z)$ invariance.
-
-In order to move analysis to quantum level we rescale the currents
-\begin{equation}
-  \label{eq:82}
-  J(z)\equiv -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
-\end{equation}
-So the variation of the action under infinitesimal transformation $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ is
-\begin{equation}
-  \label{eq:83}
-  \delta_{\omega,\bar\omega}S=\frac{i}{4\pi}\oint dz Tr' (\omega(z)J(z))-\frac{i}{4\pi}\oint d\bar z Tr'(\bar\omega(\bar z)\bar J(\bar z))
-\end{equation}
-Expanding the currents as
-\begin{equation}
-  \label{eq:85}
-  \begin{aligned}
-    J=\sum J^a t^a,\bar J=\sum \bar J^a t^a \\
-    \omega=\sum \omega^a t^a\\
-  \end{aligned}
-\end{equation}
-we get
-\begin{equation}
-  \label{eq:86}
-  \delta_{\omega,\bar \omega}S=-\frac{1}{2\pi i}\oint dz \sum\omega^a J^a+\frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \bar J^a
-\end{equation}
-We can also obtain Ward identities $\delta\left< X\right>=\left<(\delta S)X\right>$
-\begin{equation}
-  \label{eq:87}
-  \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
-  \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
-\end{equation}
-Then for the currents we have
-\begin{equation}
-  \label{eq:88}
-  \delta_{\omega}J=[\omega,J]-k\partial_z\omega,\quad \delta_{\omega}J^a=\sum i f_{abc}\omega^b J^c-k\partial_z\omega^a
-\end{equation}
-The operator product expansion for currents has the form
-\begin{equation}
-  \label{eq:89}
-  J^a(z) J^b(w) \sim \frac{k\delta_{ab}}{(z-w)^2}+\sum i f_{abc}\frac{J^c(w)}{(z-w)}
-\end{equation}
-Expanding currents into series we get
-\begin{equation}
-  \label{eq:90}
-  \begin{aligned}
-    J^a(z)=\sum_{n\in \mathbb Z}z^{n-1}J^a_n\\    
-    \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}  
-  \end{aligned}
-\end{equation}
-We see that components of currents realize affine Lie algebra $\hat g$.
-
-Energy-momentum tensor is introduced with Sugawara construction as the sum of normal-ordered products of current components
-\begin{equation}
-  \label{eq:6}
-  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
-\end{equation}
-Here $h^v$ is the dual Coxeter number.
-
-Energy-momentum tensor can be expanded into modes $L_n$
-\begin{equation}
-  \label{eq:91}
-  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
-\end{equation}
-The commutation relations for the modes $L_n$ are
-\begin{equation}
-  \label{eq:92}
-  \begin{aligned}
-    \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
-    \left[L_n,J^a_m\right]=-mJ^a_{n+m}
-  \end{aligned}
-\end{equation}
-
-So the Sugawara construction is the way to embed Virasoro algebra into the universal enveloping of affine Lie algebra.
-
-Complete chiral algebra of WZW-model is equal to semidirect product $Vir\ltimes \hat g$
-
-The primary fields are the fields that transforms covariantly with respect to $G(z)\times G(\bar z)$, such as $g(z,\bar z)$. In terms of operator product expansion this property is reformulated as
-\begin{equation}
-  \label{eq:84}
-  \begin{aligned}
-    J^a(z)g(w,\bar w)\sim \frac{-t^a g(w,\bar w)}{(z-w)}\\
-    \bar J^a(z)g(w,\bar w)\sim \frac{ g(w,\bar w)t^a}{(z-w)}
-  \end{aligned}
-\end{equation}
-Any field $\phi_{\lambda,\mu}$ transforming covariantly with respect to some representation specified by $\lambda$ in holomorphic and $\mu$ in antiholomorphic sector, will be a WZW primary field.
-
-In terms of modes this property can be written as
-\begin{equation}
-  \label{eq:93}
-  \begin{aligned}
-    & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
-    & (J^a_n\phi_{\lambda})=0\quad \mbox{for}\; n>0\\
-  \end{aligned}
-\end{equation}
-We can associate the state $\left|\phi_{\lambda}\right>$ to the field $\phi_{\lambda}$
-  \begin{equation}
-    \label{eq:94}
-    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
-  \end{equation}
-Then the conditions (\ref{eq:93}) for WZW primary field are
-\begin{equation}
-  \label{eq:95}
-  \begin{aligned}
-    & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
-    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
-  \end{aligned}
-\end{equation}
-It is easy to see that the action of the Virasoro generators is
-\begin{equation}
-  \label{eq:96}
-  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
-\end{equation}
-Here we used the explicit form of the quadratic Casimir operator eigenvalue.
-
-Primary fields live in integrable finite-dimensional representations since infinite-dimensional and non-integrable fields are decoupled from the correlation functions.
-
-All secondary states are of the form
-\begin{equation}
-  \label{eq:97}
-  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
-\end{equation}
-For the correlation functions of primary fields we can obtain Knizhnik-Zamolodchikov equations which follow from global $G\times G$ invariance
-\begin{equation}
-  \label{eq:98}
-  \left(\partial_{z_i}+\frac{1}{k+h^v}\sum_{i\neq j}\frac{\sum_a t^a_i\otimes t^a_j}{z_i-z_k}\right)
-  \left<\phi_1(z_1)\dots \phi_n(z_n)\right>=0
-\end{equation}
-So the theory is completely determined by the representations of affine Lie algebra $\hat{\mathfrak{g}} $.
-
-\subsubsection{Modular invariants}
-\label{sec:modular-invariants}
-
-In previous section we studied holomorphic and antiholomorphic sectors of the theory separately.
-But in physically sensible theories this sectors should be entangled.
-It is required for the theory to be well-defined on the higher genus Riemann surfaces (see \cite{gaberdiel2000icf} and references therein) and also if we want our theory to describe critical behavior \cite{difrancesco1997cft}.
-In the critical point theory has conformal invariance, holomorphic and antiholomorphic sectors are decoupled, but in the vicinity of critical point there exists some large scale so the sectors should interact.
-
-!!! Expand this argumentation !!!
-
-The necessary constraint for the theory to be well-defined on higher Riemann surfaces, which is also believed to be sufficient, is that the vacuum correlator on the torus is independent of its parametrisation \cite{gaberdiel2000icf}.
-Conformal theory on the higher genus Riemann surfaces is important for the string theory since this theory describes string interaction.
-
-Two-dimensional torus is described as quotient space of $\mathbb{R}^2\approx \mathbb{C}$ by the relations $z\sim z+w_1$ and $z\sim z+w_2$, where $w_1$ and $w_2$ are not parallel.
-
-The complex structure of the torus is conformally equivalent to a torus for which the relations are $z\sim z+1$ and $z\sim z+\tau$ where $\tau$ is in the upper half plane of $\mathbb{C}$.
-It is also easy to see that $\tau$, $T(\tau)=\tau+1$ and $S(\tau)=-\frac{1}{\tau}$ describe conformally equivalent tori.
-Two maps $T$ and $S$ generate the group $SL(2,\mathbb{Z})/\mathbb{Z}_2$ that consists of matrices of the form
-\begin{equation}
-  \label{eq:99}
-  A=
-  \begin{pmatrix}
-    a & b\\
-    c & d 
-  \end{pmatrix}
-  \quad\mbox{where}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
-\end{equation}
-and matrices $A$ and $-A$ have the same action on $\tau$
-\begin{equation}
-  \label{eq:100}
-  \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
-\end{equation}
-The parameter $\tau$ is called the modular parameter and the group  $SL(2,\mathbb{Z})/\mathbb{Z}_2$ is called the modular group.
-
-Given a conformal field theory that is defined on the Riemann sphere, the vacuum
-correlator on the torus can be determined as follows. First, we cut the torus along one
-of its non-trivial cycles; the resulting surface is a cylinder (or an annulus) whose shape
-depends on one complex parameter $q$. Since the annulus is a subset of the sphere, the
-conformal field theory on the annulus is determined in terms of the theory on the sphere.
-In particular, the states that can propagate in the annulus are precisely the states of
-the theory as defined on the sphere.
-In order to reobtain the torus from the annulus, we have to glue the two ends of
-the annulus together; in terms of conformal field theory this means that we have to sum
-over a complete set of states. The vacuum correlator on the torus is therefore described
-by a trace over the whole space of states, the partition function of the theory,
-\begin{equation}
-  \label{eq:101}
-  \sum_{(i,j)}Tr_{\mathcal{H}_{(i,j)}}(\mathcal{O}(q,\bar q)),
-\end{equation}
-where $\mathcal{O}(q,\bar q)$ is the operator that describes the propagation of the states along the annulus,
-\begin{equation}
-  \label{eq:102}
-  \mathcal{O}(q,\bar q)=q^{L_0-\frac{c}{24}}\bar q^{\bar L_0-\frac{\bar c}{24}}
-\end{equation}
-The propagator depends on the actual shape of the annulus that is described in terms
-of the complex parameter $q$. For a given torus that is described by $\tau$ , there is a natural
-choice for how to cut the torus into an annulus, and the complex parameter $q$ that is
-associated to this annulus is $q=e^{2\pi i \tau}$. Since the tori that are described by $\tau$ and $A\tau$
-(where $A \in SL(2, \mathbb{Z})$) are equivalent, the vacuum correlator is only well-defined provided
-that (\ref{eq:101}) is invariant under this transformation. This provides strong constraints on
-the spectrum of the theory.
-
-Each of the spaces $\mathcal{H}_{(i,j)}$ is a tensor product of an irreducible representation $\mathcal{H}_j$ of chiral algebra and an irreducible representation $\bar{\mathcal{H}}_{\bar{j}}$ of antichiral algebra.
-Then the vacuum correlator on the torus (\ref{eq:101}) takes the form
-\begin{equation}
-  \label{eq:103}
-  \sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
-\end{equation}
-where $\chi_j$ is the character of the representation $\mathcal{H}_j$,
-\begin{equation}
-  \label{eq:104}
-  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{where}\; q=e^{2\pi i \tau}
-\end{equation}
-Characters transform into one another under modular transformations,
-\begin{equation}
-  \label{eq:107}
-  \chi_j(-\frac{1}{\tau})=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{and}\quad \chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
-\end{equation}
-where $S$ and $T$ are constant matrices. This fact is proved for a certain class of conformal field theories \cite{gaberdiel2000icf}.
-
-For WZW-models the representations are determined by highest weights $\hat \lambda, \hat \xi$. Then we can write
-\begin{equation}
-  \label{eq:105}
-  \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi} L_{\hat \lambda}\otimes L_{\hat \xi}
-\end{equation}
-The partition function is rewritten as
-\begin{equation}
-  \label{eq:106}
-  Z(\tau)=\sum_{\hat \lambda,\hat \xi\in P^{(k)}_{+}} \chi_{\hat \lambda}(\tau)M_{\hat \lambda\hat\xi}\bar \chi_{\hat \xi}(\bar \tau)
-\end{equation}
-The element of the mass matrix $M_{\hat \lambda\hat\xi}$ can be thought of as the multiplicity of primary field with weights $\hat\lambda,\hat \xi$.
-It has following properties:$M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, it is modular invariant
-\begin{equation}
-  \label{eq:108}
-  \begin{aligned}
-    T^{\dagger}MT=S^{\dagger}MS=M,\\
-    [M,S]=[M,T]=0,
-  \end{aligned}
-\end{equation}
-and $M_{00}=1$ for the uniqueness of vacuum.
-
-The simplest case of diagonal matrix $M$ corresponds to equal holomorphic and antiholomorphic conformal dimensions.
-There are several ways to construct non-diagonal modular invariants from diagonal \cite{difrancesco1997cft}:
-\begin{itemize}
-\item Method of outer automorphisms
-\item Conformal embedding into bigger theory
-\item Galois-transpositions
-\end{itemize}
-Here we will discuss conformal embeddings.
-
-\subsubsection{Conformal embeddings}
-\label{sec:conformal-embeddings}
-
-\section{Affine Lie algebras representations}
-\label{sec:affine-lie-algebras}
-
-\subsection{Verma modules}
-\label{sec:verma-modules}
-
-Verma module is a simple thing. It can be easily understood in the framework of induced representations.
-
-Verma module with highest weight $\lambda$ of algebra $g$ is the space $U(g)\underset{U(b_{+})}{\otimes} D_{\lambda}(b_{+})$, where $\underset{U(b_{+})}{\otimes}$ means that the action of elements of $U(b_{+})$ ``falls through'' left part of tensor product onto the right part.
-
-Here $b_{+}$ is Borel sub-algebra ($x_{+},h$ for $sl(2)$), $D_{\lambda}(b_{+})$ is special representation of $b_{+}$, such that $D(x_{+})=0,\; D(h)=\lambda(h)$.
-$g$ acts on the representation space from the left, it means that we should expand element of $g$ in some base, and then commute all the elements of $b_{+}$ to the right, so that they can act on space $D_{\lambda}(b_{+})$.
-
-The infinite set of fields (\ref{eq:65}) corresponds to Verma module of algebra, which is Virasoro algebra in the simplest case and semidirect product of Virasoro and Kac-Moody algebra for WZW model.
-Also it is shown that for Wess-Zumino model the representations of the algebra are in fact the representations of current algebra only, which is Kac-Moody algebra.
-
-Note also, that Viraso algebra belongs to universal enveloping of Kac-Moody algebra.
-
-\subsection{Irreducible representations}
-\label{sec:irred-repr}
-
-\bibliography{article}{}
+2.Матрица монодромии. Интегралы движения.
+\bibliography{program}{}
 \bibliographystyle{utphys}
-
 \end{document}

### 2010-05-12 GeneralOverview/WZW-CS.tex

--- 2009-07-10 AffineLieAlgebras/ACMS2009/notes.tex
@@
 \theoremstyle{definition} \newtheorem{Def}{Definition}
+\title{WZW-модели и теория Черна-Саймонса}
+\author{Антон Назаров\\ antonnaz@gmail.com}
 \begin{document}
-\tableofcontents
-\section{String theory}
-\label{sec:string-theory}
+\maketitle
+\begin{abstract}
+WZW-модель - это сигма-модель с дополнительным членом Весса-Зумино, связанным с топологией.
+Существует связь таких моделей с пределом бесконечного числа цветов в калибровочных теориях.
+WZW-модели также связаны с моделями топологической теории поля - моделями Черна-Саймонса-Виттена в трех измерениях.
+Квантовые состояния в теории Черна-Саймонса с уровнем $k$ ($SU(2)_k$) эквивалентны квантовым состояниям WZW-модели, связанной с представлениями уровня $k$ аффинной алгебры Ли $\widehat{su(2)}$.
+\end{abstract}
 
-Free relativistic particle action is equal to length of trajectory. 
+\section{Конформная инвариантность}
+\label{sec:conformal-invariance}
+
+Откуда берется конформная инвариантность в физике конденсированного состояния и в теории струн?
+
+Конформные преобразования:
+
+    \begin{align} & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\ &P_\mu \equiv-i\partial_\mu \,, \\ &D \equiv-ix_\mu\partial^\mu \,, \\ &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,, \end{align}
+
+Конформная инвариантность тесно связана с масштабной инвариантностью и иногда даже прямо из нее следует.
+В физике конденсированного состояния масштабная инвариантность имеет место при фазовом переходе (стремление параметра порядка к бесконечности).
+Флуктуации при фазовом переходе конформно-инвариантны, что позволяет классифицировать фазовые переходы в терминах конформной теории поля \cite{Polyakov:1970xd}, \cite{belavin1984ics}.
+
+В теории струн действие инвариантно относительно репараметризаций мировой поверхности, в том числе конформных преобразований. 
+Однако эта инвариантность не может быть сохранена при квантовании, поэтому возникает конформная аномалия и центральный заряд алгебры Вирасоро.
+
+В двумерной теории поля локальная конформная группа бесконечномерна, хотя глобальная конформная группа конечномерна.
+Например, в конформной теории поля на сфере Римана глобальные конформные преобразования образуют группу Мебиуса $PSL(2,\mathbb{C})$.
+Алгебра же инфинитезимальных преобразований в классической теории --- это алгебра Витта, при квантовании возникает конформная аномалия, что соответствует центральному расширению алгебры.
+Так появляется алгебра Вирасоро.
+
+\subsection{Конформная инвариантность в теории струн}
+\label{sec:conformal-invariance-strings}
+
+Действие свободной релятивистской частицы --- это длина траектории.
 \begin{equation}
@@
 \end{equation}
-There is Poincare invariance $x^{\mu}\to A^{\mu}_{\nu}x^{\nu}+ B^{\mu}$ and reparametrisation invariance $\tau\to f(\tau),\; x^{\mu}(\tau)\to x^{\mu}(f(\tau))$.
+Оно Пуанкаре-инвариантно $x^{\mu}\to A^{\mu}_{\nu}x^{\nu}+ B^{\mu}$ и не зависит от репараметризаций $\tau\to f(\tau),\; x^{\mu}(\tau)\to x^{\mu}(f(\tau))$.
 
-String action is the area of world-sheet:
+Аналогично, струнное действие дается площадью мировой поверхности
 \begin{equation}
@@
 \end{equation}
-This action is called Nambu action, and it is invariant under Lorenz transformations and reparametrisations.
+Такое действие называется действием Намбу. Оно инвариантно относительно преобразований Лоренца и репараметризаций.
 
-Transition amplitude for string is given by following formula:
+Амплитуда перехода для струны дается следующей формулой:
 \begin{equation}
@@
 \end{equation}
-The problem here is the definition of measure of integration. 
-It is not strictly defined in most cases, so there is nothing unusual here.
+Сложность, как всегда, состоит в определении меры интегрирования. Она плохо определена как и в большинстве случаев, так что теория струн здесь не выделяется.
 
-We want to change ``integration variable'' in order to fix the arbitrariness connected with reparametrisations of world-sheet.
+Мы хотим сделать замену ``переменных интегрирования'', чтобы избавиться от произвола в выборе параметризации мировой поверхности.
 
-Obviously our theory should be invariant under reparametrisation:
+Теория должна быть инвариантна относительно репараметризаций:
 \begin{equation}
@@
 \end{equation}
-
-But Nambu action is not invariant. So we will use equivalent Polyakov action, which has following form:
+Но в действии Намбу эта инвариантность не видна, поэтому мы перейдем к эквивалентному действию Полякова:
 \begin{equation}
@@
 
-Polyakov and Nambu actions are equivalent in the sense that equations of motion are the same after the exclusion of auxiliary field $g_{ab}$.
+Действия Полякова и Намбу эквивалентны в том смысле, что уравнения движения совпадают после исключения вспомогательного поля $g_{ab}$.
 \begin{equation}
@@
 \end{equation}
-Polyakov action is invariant under Lorenz transformations and reparametrisations:
+Действие Полякова инвариантно относительно преобразований Лоренца и репараметризаций мировой поверхности:
 \begin{equation}
@@
 \end{equation}
-
-There is also one additional invariance, which is called conformal or Weyl invariance.
+Кроме того, есть дополнительная симметрия, которая называется вейлевской или конформной инвариантностью:
 \begin{equation}
@@
 
-So we have rather big freedom. For example, any metric on sphere can be obtained from one (constant) metric with reparametrisation and Weyl transformation.
+То есть у нас довольно большая свобода --- мы можем, например, получить произвольную метрику на сфере из постоянной метрики путем репараметризации и преобразования Вейля
 \begin{equation}
@@
 \end{equation}
-For surfaces of higher genus there are discrete families of equivalent metrics.
+Для поверхностей большего рода существуют дискретные семейства эквивалентных метрик.
 
@@
 \end{Def}
-
-!!!!!!!!!
-
-Why it is so? How this definition is connected with another definitions and properties of conformal field theory?
-
-!!!!!!!!!
 
@@
 
-!!!! !!!! !!!! !!!! 
-Be more elaborate here.
-!!!!!!!
-
-...
-\section{Conformal Field Theory}
-\label{sec:cft}
-
-\subsection{General properties}
-\label{sec:general-properties}
-
 In Conformal Field Theory 
@@
 
-\subsection{Wess-Zumino-Novikov-Witten models}
+\subsection{Глобальная конформная инвариантность и уравнения Книжника-Замолодчикова}
+\label{sec:knizhnik-zamolodchikov}
+
+\subsection{Модулярные преобразования}
+\label{sec:modular}
+
+Конформная инвариантность в квантовой и классической теории поля.
+Глобальная конформная инвариантность.
+Уравнения Книжника-Замолодчикова.
+Локальная конформная инвариантность. Бесследовость тензора энергии-импульса.
+Голоморфная факторизация.
+
+\section{Модели Весса-Зумино-Новикова-Виттена}
 \label{sec:WZNW}
 
-Let's start with non-linear $\sigma$-model.
+Связь WZW-моделей с топологией, обоснование с точки зрения предела калибровочной теории.
+
+Стартуем с нелинейной $\sigma$-модели.
 \begin{equation}
@@
 \end{equation}
-Here $a^2>0$ is a positive parameter, $g(x)\in G$ - field on Lie group $G$, which we will assume to be semi-simple and by $Tr'$ we have denoted representation independent trace of Lie algebra $\mathfrak{g} $
+Здесь $a^2>0$ - положительный параметр, $g(x)\in G$ - поле со значениями в группе $G$, которую мы будем считать полупростой, а через $Tr'$ мы обозначили след, не зависящий от выбора представления алгебры Ли $\mathfrak{g} $
 \begin{equation}
@@
 \end{equation}
-$x_{rep}$ is the Dynkin index of the representation.
+$x_{rep}$ - индекс Дынкина представления.
 
-In this model the conformal invariance is lost at the quantum level, as it can be seen along the lines of previous sections.
-!!! Show it by example !!!
-
-Also we can see that holomorphic and antiholomorphic currents aren't conserved individually. The equations of motion are
+В нелинейной $\sigma$-модели конформная инвариантность теряется на квантовом уровне.
+Голоморфный и антиголоморфный токи не сохраняются по отдельности. Уравнения движения имеют вид    
 \begin{equation}
@@
 \end{equation}
-The currents are
+Токи задаются выражением
 \begin{equation}
@@
 \end{equation}
-or in the complex coordinates
+или в комплексных координатах
 \begin{equation}
@@
 \end{equation}
-The terms of the equation of motion can not be null separately because $\partial_{\mu}(\epsilon^{\mu\nu}J_{\nu})\neq 0$.
+Члены в уравнении движения не разделяются, так как  $\partial_{\mu}(\epsilon^{\mu\nu}J_{\nu})\neq 0$.
 
-So we add WZ-term to the action and redefine the currents in more appropriate way
+Поэтому мы добавляем член Весса-Зумино к действию и переопределяем токи:
 \begin{equation}
@@
 
-Wess-Zumino term has the following form
+Член Весса-Зумино имеет вид
 \begin{equation}
@@
 
-This term is defined on the three-dimensional manifold $B$ whose boundary is original two-dimensional space.
-By $\tilde{g}$ we have denoted the extension of the field $g$ to $B$.
-This extension isn't unique.
-In a compactified three-dimensional space a compact two-dimensional manifold delimits two three-dimensional manifolds.
-The difference between this two choices $\Delta\Gamma$ is given by the right hand side of (\ref{eq:73}) with the integration range extended over the whole compact three-dimensional space.
-Since the latter is topologically equivalent to the three-sphere we have
+Он определен на трехмерном многообразии $B$, ограниченном исходным двумерным пространством. 
+Через $\tilde{g}$ мы обозначили продолжение поля  $g$ на $B$.
+Такое продолжение не единственно.
+В компактифицированном трехмерном пространстве компактное двумерное многообразие разделяет два трехмерных многообразия.
+Разность значений члена Весса-Зумино  $\Delta\Gamma$ на этих многообразиях дается правой частью уравнения (\ref{eq:73}) с интегралом, продолженным на все компактное трехмерное пространство.
+Так как оно топологически эквивалентно три-сфере, получаем
 \begin{equation}
@@
 \end{equation}
-$\Delta\Gamma$ is defined modulo $2\pi i$, so the Euclidean functional integral with weight $exp(-\Gamma)$ is well-defined. Clearly, any coupling constant multiplying this term must be an integer.
+$\Delta\Gamma$ определен по модулю $2\pi i$, поэтому Евклидов функциональный интеграл с весом  $exp(-\Gamma)$ хорошо определен.
+Значит константа связи, умножаемая на этот член, должна быть целочисленной.
 
-We then consider the action
+Теперь мы рассматриваем действи
 \begin{equation}
@@
 \end{equation}
-where $k$ is an integer. 
-The equation of motion for the full action (\ref{eq:76}) is
+где $k$ - целое.
+Уравнение движения для полного действия (\ref{eq:76}):
 \begin{equation}
@@
 \end{equation}
-It can be rewritten using complex coordinates as
+В комплексных координатах оно записывается в виде
 \begin{equation}
@@
 \end{equation}
-We see that when $a^2=\frac{4\pi}{k}$ we have the desired conservation law
+Видно, что при $a^2=\frac{4\pi}{k}$ у нас имеются интересующие нас законы сохранения
 \begin{equation}
@@
 \end{equation}
-For currents
+Для токов
 \begin{equation}
@@
 
-The solution of classical equation is
+Решение классического уравнения движения имеет вид
 \begin{equation}
@@
 \end{equation}
-for arbitrary functions $f(z)$ and $\bar f (\bar z)$.
+при произвольных $f(z)$ и $\bar f (\bar z)$.
 
-The separate conservation of the currents $J_z,\; J_{\bar z}$ implies the invariance of the action under the transformations
+Сохранение по отдельности токов $J_z,\; J_{\bar z}$ приводит к инвариантности действия при преобразованиях
 \begin{equation}
@@
 \end{equation}
-where $\Omega,\;\bar \Omega \in G$. So we have local $G(z)\times G(\bar z)$ invariance.
+где $\Omega,\;\bar \Omega \in G$. То есть мы получили локальную $G(z)\times G(\bar z)$-инвариантность.
 
-In order to move analysis to quantum level we rescale the currents
+Для перехода к квантовому случаю мы переопределяем токи
 \begin{equation}
@@
 \end{equation}
-So the variation of the action under infinitesimal transformation $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ is
+Тогда вариация действия при инфинитезимальных преобразованиях $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ дается выражением
 \begin{equation}
@@
 \end{equation}
-Expanding the currents as
+Раскладывая токи
 \begin{equation}
@@
 \end{equation}
-we get
+получаем
 \begin{equation}
@@
 \end{equation}
-We can also obtain Ward identities $\delta\left< X\right>=\left<(\delta S)X\right>$
+Мы также получили тождества Уорда $\delta\left< X\right>=\left<(\delta S)X\right>$
 \begin{equation}
@@
 \end{equation}
-Then for the currents we have
+Для токов имеем
 \begin{equation}
@@
 \end{equation}
-The operator product expansion for currents has the form
+Операторное разложение для токов имеет вид 
 \begin{equation}
@@
 \end{equation}
-Expanding currents into series we get
+Раскладывая токи в ряд, получаем
 \begin{equation}
@@
 \end{equation}
-We see that components of currents realize affine Lie algebra $\hat g$.
+Теперь мы видим, что компоненты токов образуют аффинную алгебру Ли $\hat g$.
 
-Energy-momentum tensor is introduced with Sugawara construction as the sum of normal-ordered products of current components
+Тензор энергии-импульса вводится при помощи конструкции Сугавары как сумма нормально упорядоченных компонент токов
 \begin{equation}
@@
 \end{equation}
-Here $h^v$ is the dual Coxeter number.
+Здесь $h^v$ - дуальное число Кокстера.
 
-Energy-momentum tensor can be expanded into modes $L_n$
+Тензор энергии-импульса можно разложить на моды $L_n$
 \begin{equation}
@@
 \end{equation}
-The commutation relations for the modes $L_n$ are
+Тогда коммутационные соотношения для мод  $L_n$ имеют вид
 \begin{equation}
@@
 
-So the Sugawara construction is the way to embed Virasoro algebra into the universal enveloping of affine Lie algebra.
+Таким образом, конструкция Сугавары --- это способ вложения алгебры Вирасоро в универсальную обертывающую аффинной алгебры Ли $\hat{g}$
 
-Complete chiral algebra of WZW-model is equal to semidirect product $Vir\ltimes \hat g$
+Полная киральная алгебра модели Весса-Зумино-Виттена равна полупрямому произведению $Vir\ltimes \hat g$
 
-The primary fields are the fields that transforms covariantly with respect to $G(z)\times G(\bar z)$, such as $g(z,\bar z)$. In terms of operator product expansion this property is reformulated as
+Примарными называются поля, которые преобразуются ковариантно под действием $G(z)\times G(\bar z)$, как $g(z,\bar z)$.
+В терминах операторного разложения это свойство переформулируется следующим образом:
 \begin{equation}
@@
 \end{equation}
-Any field $\phi_{\lambda,\mu}$ transforming covariantly with respect to some representation specified by $\lambda$ in holomorphic and $\mu$ in antiholomorphic sector, will be a WZW primary field.
+Любое поле $\phi_{\lambda,\mu}$, преобразующееся ковариантно по отношению к некоторому представлению, заданному весом  $\lambda$ в голоморфном секторе и весом $\mu$ в антиголоморфном, является примарным полем WZW-модели.
 
-In terms of modes this property can be written as
+В модах это свойство записывается в виде
 \begin{equation}
@@
     & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
-    & (J^a_n\phi_{\lambda})=0\quad \mbox{for}\; n>0\\
+    & (J^a_n\phi_{\lambda})=0\quad \mbox{для}\; n>0\\
   \end{aligned}
 \end{equation}
-We can associate the state $\left|\phi_{\lambda}\right>$ to the field $\phi_{\lambda}$
+Мы можем сопоставить состояние $\left|\phi_{\lambda}\right>$ полю $\phi_{\lambda}$
   \begin{equation}
@@
   \end{equation}
-Then the conditions (\ref{eq:93}) for WZW primary field are
+Тогда условия  (\ref{eq:93}) для примарных полей  дают
 \begin{equation}
@@
     & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
-    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
+    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{для}\; n>0 \\
   \end{aligned}
 \end{equation}
-It is easy to see that the action of the Virasoro generators is
+Легко видеть, что действие генераторов алгебры Вирасоро имеет вид
 \begin{equation}
@@
 \end{equation}
-Here we used the explicit form of the quadratic Casimir operator eigenvalue.
+Здесь использовано явное выражение для собственных значений квадратичного оператора Казимира.
 
-Primary fields live in integrable finite-dimensional representations since infinite-dimensional and non-integrable fields are decoupled from the correlation functions.
+Примарные поля живут в интегрируемых конечномерных представлениях, так как бесконечномерные и неинтегрируемые поля отщепляются в корреляционных функциях.
 
-All secondary states are of the form
+Все вторичные состояния имеют вид
 \begin{equation}
@@
 \end{equation}
-For the correlation functions of primary fields we can obtain Knizhnik-Zamolodchikov equations which follow from global $G\times G$ invariance
+Для корреляционных функций примарных полей можно получить уравнения Книжника-Замолодчикова, которые следуют из глобальной $G\times G$-инвариантности
 \begin{equation}
@@
 \end{equation}
-So the theory is completely determined by the representations of affine Lie algebra $\hat{\mathfrak{g}} $.
+Таким образом, теория полностью определяется представлениями аффинной алгебры Ли $\hat{\mathfrak{g}} $.
 
-\subsubsection{Modular invariants}
-\label{sec:modular-invariants}
+\subsection{Литература}
+\label{sec:wzw-literature}
 
-In previous section we studied holomorphic and antiholomorphic sectors of the theory separately.
-But in physically sensible theories this sectors should be entangled.
-It is required for the theory to be well-defined on the higher genus Riemann surfaces (see \cite{gaberdiel2000icf} and references therein) and also if we want our theory to describe critical behavior \cite{difrancesco1997cft}.
-In the critical point theory has conformal invariance, holomorphic and antiholomorphic sectors are decoupled, but in the vicinity of critical point there exists some large scale so the sectors should interact.
+Эта часть написана по книге \cite{difrancesco1997cft}, так же стоит отметить обзор \cite{Walton:1999xc}.
 
-!!! Expand this argumentation !!!
+\subsection{Калибровочная WZW-модель}
+\label{sec:gauged-wzw}
 
-The necessary constraint for the theory to be well-defined on higher Riemann surfaces, which is also believed to be sufficient, is that the vacuum correlator on the torus is independent of its parametrisation \cite{gaberdiel2000icf}.
-Conformal theory on the higher genus Riemann surfaces is important for the string theory since this theory describes string interaction.
+Добавить сюда действие G-WZW, обсудить связь с coset construction и branching functions.
 
-Two-dimensional torus is described as quotient space of $\mathbb{R}^2\approx \mathbb{C}$ by the relations $z\sim z+w_1$ and $z\sim z+w_2$, where $w_1$ and $w_2$ are not parallel.
+(Добавить статью Gawedzki в ссылки и перевести оттуда содержательную часть).
 
-The complex structure of the torus is conformally equivalent to a torus for which the relations are $z\sim z+1$ and $z\sim z+\tau$ where $\tau$ is in the upper half plane of $\mathbb{C}$.
-It is also easy to see that $\tau$, $T(\tau)=\tau+1$ and $S(\tau)=-\frac{1}{\tau}$ describe conformally equivalent tori.
-Two maps $T$ and $S$ generate the group $SL(2,\mathbb{Z})/\mathbb{Z}_2$ that consists of matrices of the form
+Теперь мы знаем, что такое conformal blocks, так что это надо здесь объяснить при обсуждении G-WZW и coset construction.
+
+\section{Теория Черна-Саймонса}
+\label{sec:Chern-Simons}
+
+Теория Черна-Саймонса --- это калибровочная теория, то есть классические полевые конфигурации в теории на $M$ с калибровочной группой $G$ описываются главным $G$-расслоением над $M$.
+Форму связности главного $G$-расслоения над $M$ обозначим через $A:M\to g$, она принимает значения в $g$.
+В общем случае связность $A$ определяется на отдельных картах, значения $A$ на разных картах связаны калибровочными преобразованиями.
+Калибровочные преобразования характеризуются тем, что ковариантная производная $D=d+\frac{1}{2}[A,\cdot]$ преобразуется в присоединенном представлении $G$.
+
+Тогда действие записывается в виде:
 \begin{equation}
-  \label{eq:99}
-  A=
-  \begin{pmatrix}
-    a & b\\
-    c & d 
-  \end{pmatrix}
-  \quad\mbox{where}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+  \label{eq:1}
+  S=\frac{k}{4\pi}\int_M \mathrm{tr}(A\wedge dA+\frac{2}{3}A\wedge A\wedge A)
 \end{equation}
-and matrices $A$ and $-A$ have the same action on $\tau$
+
+Кривизна связности
 \begin{equation}
-  \label{eq:100}
-  \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+  \label{eq:2}
+  F=DA=dA+A\wedge A\in \Omega^2(M,g)
 \end{equation}
-The parameter $\tau$ is called the modular parameter and the group  $SL(2,\mathbb{Z})/\mathbb{Z}_2$ is called the modular group.
+Уравнение движения
+\begin{equation}
+  \label{eq:3}
+  \frac{\delta S}{\delta A}=0=\frac{k}{2\pi}F
+\end{equation}
+Решениями являются плоские связности, которые определяются голономиями вокруг нестягиваемых циклов на $M$.
+Плоские связности находятся в однозначном соответствии с классами эквивалентности гомоморфизмов из фундаментальной группы $M$ в калибровочную группу $G$.
+Также говорят о том, что плоские связности определяются своими голономиями и
+\begin{equation}
+  \label{eq:8}
+  \mbox{критические значения}/\mbox{калибровочным преобразованиям}\leftrightarrow \mathrm{Hom}(\pi_1(M),G)/G
+\end{equation}
 
-Given a conformal field theory that is defined on the Riemann sphere, the vacuum
-correlator on the torus can be determined as follows. First, we cut the torus along one
-of its non-trivial cycles; the resulting surface is a cylinder (or an annulus) whose shape
-depends on one complex parameter $q$. Since the annulus is a subset of the sphere, the
-conformal field theory on the annulus is determined in terms of the theory on the sphere.
-In particular, the states that can propagate in the annulus are precisely the states of
-the theory as defined on the sphere.
-In order to reobtain the torus from the annulus, we have to glue the two ends of
-the annulus together; in terms of conformal field theory this means that we have to sum
-over a complete set of states. The vacuum correlator on the torus is therefore described
-by a trace over the whole space of states, the partition function of the theory,
+Действие зависит только от топологии $M$, метрика нигде явно не появляется. Корреляторы тоже зависят только от топологии. 
+Хотя действие и зависит от калибровки, статсумма в квантовой теории хорошо определена при целом $k$ и напряженность калибровочного поля обнуляется на границах $M$.
+
+Если у $M$ есть граница $N=\partial M$, то есть дополнительные данные, которые описывают выбор тривиализации главного $G$-расслоения на $N$.
+Такой выбор задает отображение из $N$ в $G$.
+Динамика этого отображения описывается WZW-моделью на $N$ с уровнем $k$.
+
+Рассматриваем калибровочное преобразование действия Черна-Саймонса.
+При калибровочном преобразовании $g$ $A$ преобразуется как
 \begin{equation}
-  \label{eq:101}
-  \sum_{(i,j)}Tr_{\mathcal{H}_{(i,j)}}(\mathcal{O}(q,\bar q)),
+  \label{eq:5}
+  A_{\mu}\to g^* A= g^{-1}A_{\mu}g+g^{-1}\partial_{\mu}g
 \end{equation}
-where $\mathcal{O}(q,\bar q)$ is the operator that describes the propagation of the states along the annulus,
+Для действия Черна-Саймонса имеем
 \begin{equation}
-  \label{eq:102}
-  \mathcal{O}(q,\bar q)=q^{L_0-\frac{c}{24}}\bar q^{\bar L_0-\frac{\bar c}{24}}
+  \label{eq:7}
+  S(g^* A)=S(A) +\frac{k}{4\pi}\int_{\partial M}\mathrm{Tr} (A\wedge dg \; g^{-1})-2\pi k\int_M g^* \sigma
 \end{equation}
-The propagator depends on the actual shape of the annulus that is described in terms
-of the complex parameter $q$. For a given torus that is described by $\tau$ , there is a natural
-choice for how to cut the torus into an annulus, and the complex parameter $q$ that is
-associated to this annulus is $q=e^{2\pi i \tau}$. Since the tori that are described by $\tau$ and $A\tau$
-(where $A \in SL(2, \mathbb{Z})$) are equivalent, the vacuum correlator is only well-defined provided
-that (\ref{eq:101}) is invariant under this transformation. This provides strong constraints on
-the spectrum of the theory.
+Здесь
 
-Each of the spaces $\mathcal{H}_{(i,j)}$ is a tensor product of an irreducible representation $\mathcal{H}_j$ of chiral algebra and an irreducible representation $\bar{\mathcal{H}}_{\bar{j}}$ of antichiral algebra.
-Then the vacuum correlator on the torus (\ref{eq:101}) takes the form
 \begin{equation}
-  \label{eq:103}
-  \sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
+  \label{eq:4}
+  \sigma=\frac{1}{24\pi^2} \mathrm{Tr} (\mu\wedge\mu\wedge\mu)
 \end{equation}
-where $\chi_j$ is the character of the representation $\mathcal{H}_j$,
+где $\mu=X^{-1} dX, X\in G$ - форма Маурера-Картана.
+
+Получаем добавку в \eqref{eq:7}, определенную на границе.
+Она выглядит как член Весса-Зумино.
+Из требования калибровочной инвариантности квантовых корреляторов  получаем квантование $k$, так как функциональный интеграл должен быть однозначно определен.
+
+\subsection{Квантование}
+\label{sec:quantization}
+
+\subsubsection{Задача квантования}
+\label{sec:task}
+
+При каноническом квантовании теории Черна-Саймонса состояние определяется на каждой двумерной поверхности $\Sigma\subset M$.
+Как в любой квантовой теории поля, состояния соответствуют лучам в гильбертовом пространстве.
+Так как мы имеем дело с топологической теорией поля типа Шварца, то у нас нет предопределенного выделенного времени, поэтому $\Sigma$ - произвольная поверхность Коши.
+
+Коразмерность $\Sigma$ равна 1, поэтому можно разрезать $M$ вдоль $\Sigma$ и получить многообразие с границей, на котором классическая динамика описывается WZW-моделью \ref{sec:Chern-Simons}.
+Виттен показал, что это соответствие сохраняется и в квантовой механике.
+То есть гильбертово пространство состояний всегда конечномерно и может быть отождествлено с пространством конформных блоков $G$-WZW-модели с уровнем $k$.
+Конформные блоки - это локально голоморфные и антиголоморфные множители, произведения которых складываются в корреляционные функции двумерной конформной теории поля.
+
+Например, если $\Sigma=S^2$, то гильбертово пространство одномерно и существует только одно состояние.
+При $\Sigma=T^2$ состояния соответствуют интегрируемым представлениям уровня $k$  аффинного расширения алгебры Ли $g$.
+Рассмотрение поверхностей более высокого рода не требуется для решения теории Черна-Саймонса.
+
+\subsubsection{Наблюдаемые}
+\label{sec:observables}
+
+Наблюдаемые в теории Черна-Саймонса - это $n$-точечные функции калибровочно-инвариантных операторов, чаще всего рассматривают петли Вильсона.
+Петля Вильсона - это голономия вокруг кольца в $M$, вычисленная в некотором представлении $R$ группы $G$.
+Так как мы будем рассматривать произведения петель Вильсона, то мы можем считать представления неприводимыми.
 \begin{equation}
-  \label{eq:104}
-  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{where}\; q=e^{2\pi i \tau}
+  \label{eq:33}
+    \langle W_R(K) \rangle =\text{Tr}_R \, P \, \exp{i \oint_K A}  
 \end{equation}
-Characters transform into one another under modular transformations,
+Здесь $A$- 1-форма связности, мы берем главное значение интеграла по Коши, $P \exp$ - экспонента, упорядоченная вдоль пути.
+
+Рассмотрим зацепление $L$ в $M$, которое представляет собой набор из $l$ несвязных циклов.
+Особенно интересна $l$-точечная корреляционная функция, представляющая собой произведение петель Вильсона в фундаментальном представлении $G$ вокруг этих циклов.
+Эту корреляционную функцию можно нормировать, разделив ее на 0-точечную функцию (статсумму $Z$).
+
+Если $M$ - сфера, то такие нормированные функции пропорциональны известным полиномам (инвариантам) узлов. Например, при $G=U(N)$ теория Черна-Саймонса с уровнем $k$ дает
 \begin{equation}
-  \label{eq:107}
-  \chi_j(-\frac{1}{\tau})=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{and}\quad \chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
+  \label{eq:34}
+      \frac{\sin(\pi/(k+N))}{\sin(\pi N/(k+N))}\times\;\mbox{полином HOMFLY}
 \end{equation}
-where $S$ and $T$ are constant matrices. This fact is proved for a certain class of conformal field theories \cite{gaberdiel2000icf}.
+При $N=2$ полином HOMFLY переходит в полином Джонса. В случае $SO(N)$ получается полином Кауффмана.
 
-For WZW-models the representations are determined by highest weights $\hat \lambda, \hat \xi$. Then we can write
+\subsubsection{Связь с G/G WZW-моделями}
+\label{sec:gg-wzw}
+
+Задача квантования сводится к вычислению функциональных интегралов вида
 \begin{equation}
-  \label{eq:105}
-  \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi} L_{\hat \lambda}\otimes L_{\hat \xi}
+  \label{eq:9}
+  \left< F \right> = \frac{\int \mathcal{D} A F[A] e^{i S(A)}}{\int \mathcal{D} A e^{iS(A)}}
 \end{equation}
-The partition function is rewritten as
+В первую очередь нас интересует производящий функционал (статсумма, partition function)
 \begin{equation}
-  \label{eq:106}
-  Z(\tau)=\sum_{\hat \lambda,\hat \xi\in P^{(k)}_{+}} \chi_{\hat \lambda}(\tau)M_{\hat \lambda\hat\xi}\bar \chi_{\hat \xi}(\bar \tau)
+  \label{eq:14}
+  Z_{\Sigma\times I}=\int \mathcal{D} A e^{iS(A)}
 \end{equation}
-The element of the mass matrix $M_{\hat \lambda\hat\xi}$ can be thought of as the multiplicity of primary field with weights $\hat\lambda,\hat \xi$.
-It has following properties:$M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, it is modular invariant
+
+Если многообразие $M$ имеет вид $M=\Sigma\times S^1$, то функциональный интеграл можно строго определить и явно вычислить.
+В противном случае можно вычислять его по теории возмущений.
+Как явное вычисление для многообразий специального вида так и вычисление по теории возмущений показывают связь теории Черна-Саймонса с WZW-моделями.
+Мы начнем с рассмотрения случая $M=\Sigma\times S^1$, где $\Sigma$ - компактная двумерная поверхность.
+Рассмотрение такого функционального интеграла можно свести к анализу теории Черна-Саймонса на пространстве $\Sigma\times I$, где $I=[0,1]$, с заданными граничными условиями в точках $\{0\}, \{1\}$.
+
+В случае $M=\Sigma\times S^1$ существует такой выбор калибровки, при котором функциональный интеграл имеет гауссову форму. 
+Сначала разделим поле $A$ на компоненты:
 \begin{equation}
-  \label{eq:108}
-  \begin{aligned}
-    T^{\dagger}MT=S^{\dagger}MS=M,\\
-    [M,S]=[M,T]=0,
-  \end{aligned}
+  \label{eq:10}
+  A=A+A_0 dt
 \end{equation}
-and $M_{00}=1$ for the uniqueness of vacuum.
+Для вычисления функционального интеграла зафиксируем следующую калибровку
+\begin{equation}
+  \label{eq:11}
+  \partial_0 A_0 =0
+\end{equation}
+Это условие устраняет не весь произвол, так как остаются ещё не зависящие от времени калибровочные преобразования. Обозначим через $\gamma$ голономию $A_0$ вокруг $S^1$, то есть
+\begin{equation}
+  \label{eq:12}
+  \gamma=P \exp\left(\oint A_0\right)
+\end{equation}
+При калибровочном преобразовании $h: A_0\to A_0^h\equiv h^{-1} A_0 h+h^{-1}\partial_0 h$ $\gamma$ переходит в сопряженный элемент:
+\begin{equation}
+  \label{eq:13}
+  \gamma\to h^{-1} \gamma h
+\end{equation}
+Мы можем наложить калибровочное условие, потребовав нахождения $\gamma$ в максимальном торе $T\subset G$.
 
-The simplest case of diagonal matrix $M$ corresponds to equal holomorphic and antiholomorphic conformal dimensions.
-There are several ways to construct non-diagonal modular invariants from diagonal \cite{difrancesco1997cft}:
-\begin{itemize}
-\item Method of outer automorphisms
-\item Conformal embedding into bigger theory
-\item Galois-transpositions
-\end{itemize}
-Here we will discuss conformal embeddings.
+Покажем, как мы можем получить действие калибровочной WZW-модели в результате вычисления функционального интеграла. 
+Действие калибровочной WZW-модели отличается от действия \eqref{eq:76} наличием дополнительного члена, зависящего от калибровочного поля
+\begin{equation}
+  \label{eq:15}
+  S_{/H}(g,A)=-\frac{1}{2\pi}\int_{\Sigma}d^2z (A_z\partial_{\bar z} g g^{-1}-A_{\bar z} g^{-1}\partial_z g+ A_z A_{\bar z} - g^{-1}A_z g A_{\bar z})
+\end{equation}
+Если исходное действие \eqref{eq:76} обладает глобальной инвариантностью относительно группы $G=G_L\times G_R: g\to a g b^{-1}$, то здесь калибровочная группа $H\subset G$ - это достаточно хорошая ее подгруппа, например, $H\subset G_{adj}(g\to a g a^{-1})$.
+Итоговое действие калибровочной WZW-модели
+\begin{equation}
+  \label{eq:16}
+  S_{G/H}(g,A)=S_{WZW}(g)+S_{/H}(g,A)
+\end{equation}
+При $H=G$
+\begin{equation}
+  \label{eq:17}
+  S_{G/G}(g,A)=-\frac{1}{8\pi}\int_{\Sigma} \mathrm{tr} g^{-1} d_A g * g^{-1} d_a g-i\Gamma(g,A)
+\end{equation}
+\begin{equation}
+  \label{eq:18}
+  \Gamma(g,A)=\frac{1}{12\pi}\int_{M:\partial M=\Sigma}\mathrm{tr}(g^{-1}dg)^3-\frac{1}{4\pi}\int_{\Sigma}\mathrm{tr}\left(A(dg\; g^{-1}+g^{-1} dg)+Ag^{-1} A g\right)
+\end{equation}
 
-\subsubsection{Conformal embeddings}
-\label{sec:conformal-embeddings}
+Возвращаясь к действию Черна-Саймонса на $\Sigma\times I$, мы фиксируем калибровку \eqref{eq:11} и вводим
+\begin{equation}
+  \label{eq:19}
+  \gamma_t\equiv P\exp\int_0^t A_0=\exp tA_0
+\end{equation}
+При этом $\gamma_0=1,\; \gamma_1=\gamma$ и $A^{(\gamma^{-1})}_0=0$.
 
-\section{Affine Lie algebras representations}
-\label{sec:affine-lie-algebras}
+Вводим духи Фаддева-Попова, при этом к действию добавляются члены, фиксирующие калибровку:
+\begin{equation}
+  \label{eq:20}
+  \int_{\Sigma\times S^1}\mathrm{tr}(BA_0+\bar{c}D_0c),\quad \mbox{где} \; D_0=\partial_0+A_0
+\end{equation}
+и накладываем условия
+\begin{equation}
+  \label{eq:21}
+  \oint B=\oint c=\oint \bar{c}=0
+\end{equation}
+Мы можем проинтегрировать по $A_t$, тогда $A_0$ останется только как внешнее фиксированное поле, а в интеграле появится множитель $\mathrm{Det}'D_0$.
+Обозначим оставшиеся компоненты через $B$ и зафиксируем граничные условия:
+\begin{equation}
+  \label{eq:22}
+  B_z|_{\Sigma\times \{0\}}=A_z,\quad B_{\bar{z}}|_{\Sigma\times\{1\}}=A_{\bar z}
+\end{equation}
+Тогда надо добавить граничные члены к действию:
+\begin{equation}
+  \label{eq:23}
+  S_{CS}(A_0,B)\to S_{CS}(A_0,B)-\frac{1}{4\pi}\int_{\Sigma\times \{0\}}B_z B_{\bar z}-\frac{1}{4\pi}\int_{\Sigma\times \{1\}}B_z B_{\bar z}
+\end{equation}
+Тогда нам надо вычислить
+\begin{equation}
+  \label{eq:24}
+  Z_{\Sigma\times S^1}=\int \mathcal{D}A_0\mathcal{D}A \mathrm{Det}'D_0 Z_{\Sigma\times I}[A_0; A_z, A_{\bar z}]\exp\left(\frac{ik}{2\pi}\int_{\Sigma}A_z A_{\bar z}\right) 
+\end{equation}
+Последний член - Кэлеров потенциал, необходимый для голоморфного представления граничных членов \eqref{eq:23}.
 
-\subsection{Verma modules}
-\label{sec:verma-modules}
+На многообразии с границами $\exp iS_{CS}$ не инвариантна относительно произвольных калибровочных преобразований \eqref{eq:7}
+\begin{equation}
+  \label{eq:25}
+  \exp iS_{CS}(A^g)=\Theta(A,g)^k \exp iS_{CS}(A)
+\end{equation}
+\begin{equation}
+  \label{eq:26}
+  \Theta(A,g)=\exp \left(-\frac{i}{12\pi}\int_M(g^{-1}dg)^3+\frac{i}{4\pi}\int_{\partial M} A dg g^{-1}\right)
+\end{equation}
 
-Verma module is a simple thing. It can be easily understood in the framework of induced representations.
+Тогда для амплитуды $Z_{\Sigma\times I}[A_0;A_z,A_{\bar z}]$ при преобразовании $\gamma_t=\exp tA_0$
+\begin{equation}
+  \label{eq:27}
+  Z_{\Sigma\times I}[A_0;A_z,A_{\bar z}^{\gamma}]=Z_{\Sigma\times I}[A_0^{(\gamma_t^{-1})}=0;A_z,A_{\bar z}] C[A_{\bar z},\gamma]
+\end{equation}
+где $C[A_{\bar z},\gamma]$ - коцикл Полякова-Вигманна:
+\begin{equation}
+  \label{eq:28}
+  C[A_{\bar z},\gamma]=\exp iS_{G/G}(\gamma^{-1},A_z=0,A_{\bar z})
+\end{equation}
 
-Verma module with highest weight $\lambda$ of algebra $g$ is the space $U(g)\underset{U(b_{+})}{\otimes} D_{\lambda}(b_{+})$, where $\underset{U(b_{+})}{\otimes}$ means that the action of elements of $U(b_{+})$ ``falls through'' left part of tensor product onto the right part.
+Нам надо также перейти от меры $\mathcal{D}A_0$ на алгебре Ли к мере Хаара $\mathcal{D}\gamma$ на группе, при этом получается множитель, который сокращает член $Det'$. Имеем:
+\begin{equation}
+  \label{eq:29}
+   Z_{\Sigma\times S^1}=\int \mathcal{D}\gamma\mathcal{D}A Z_{\Sigma\times I}[A_0=0; A_z, A_{\bar z}] C[A_{\bar z},\gamma] \exp\left(\frac{ik}{2\pi}\int_{\Sigma}A_z A_{\bar z}^{\gamma}\right) 
+\end{equation}
 
-Here $b_{+}$ is Borel sub-algebra ($x_{+},h$ for $sl(2)$), $D_{\lambda}(b_{+})$ is special representation of $b_{+}$, such that $D(x_{+})=0,\; D(h)=\lambda(h)$.
-$g$ acts on the representation space from the left, it means that we should expand element of $g$ in some base, and then commute all the elements of $b_{+}$ to the right, so that they can act on space $D_{\lambda}(b_{+})$.
+Осталось вычислить обычный интеграл $Z_{\Sigma\times I}[A_0;A_z,A_{\bar z}]$, только нужно быть аккуратными с граничными условиями:
+\begin{equation}
+  \label{eq:30}
+  Z_{\Sigma\times I}[A_0;A_z,A_{\bar z}]= N \exp \left( -\frac{ik}{2\pi}\int_{\Sigma\times\{0\}} A_z A_{\bar z}\right)
+\end{equation}
+Подставляя, получаем для функционального интеграла
+\begin{equation}
+  \label{eq:31}
+    Z_{\Sigma\times S^1}\propto\int \mathcal{D}\gamma\mathcal{D}A \exp ik\left(\frac{1}{k}S_{WZW}(\gamma^{-1})-\frac{1}{2\pi}\int_{\Sigma}d^2z (A_{\bar z}\partial_z \gamma \gamma^{-1}+A_zA_{\bar z}-A_z A_{\bar z}^{\gamma})\right)
+\end{equation}
+\begin{equation}
+  \label{eq:32}
+  Z_{\Sigma\times S^1}\propto\int \mathcal{D}\gamma\mathcal{D}A \exp iS_{G/G}(\gamma^{-1},A)
+\end{equation}
 
-The infinite set of fields (\ref{eq:65}) corresponds to Verma module of algebra, which is Virasoro algebra in the simplest case and semidirect product of Virasoro and Kac-Moody algebra for WZW model.
-Also it is shown that for Wess-Zumino model the representations of the algebra are in fact the representations of current algebra only, which is Kac-Moody algebra.
+При рассмотрении специальных видов поверхности $\Sigma$ (диск, тор) удается перейти к чистой WZW-модели.
 
-Note also, that Viraso algebra belongs to universal enveloping of Kac-Moody algebra.
+\subsection{Литература}
+\label{sec:cs-literature}
 
-\subsection{Irreducible representations}
-\label{sec:irred-repr}
+Оригинальные результаты по квантованию теории Черна-Саймонса и связь с WZW впервые опубликованы в работе \cite{witten1989quantum}.
+Существуют записки с лекций Виттена \cite{hu2001lecture}, но они не очень понятные.
+С более математической точки зрения вопрос о связи конформной теории поля и теории Черна-Саймонса обсуждается в книге \cite{kohno2002conformal}.
+Теория Черна-Саймонса допускает также геометрическое квантование, чему посвящена диссертация \cite{axelrod1991geometric}.
+Материал секции \ref{sec:quantization} написан по работе \cite{blau1993derivation}, а разделы \ref{sec:task}, \ref{sec:observables} представляют собой перевод английской статьи в Википедии (\url{http://en.wikipedia.org/wiki/Chern-Simons_theory}).
 
-\bibliography{article}{}
+\bibliography{program,wzw}{}
 \bibliographystyle{utphys}

### 2010-05-12 GeneralOverview/program.tex

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}
\begin{document}
\section{Программа}
Программа кандидатского экзамена по теоретической физике (01.04.02), специальная
часть, по кафедре физики высоких энергий и элементарных частиц
аспиранта 2-го года обучения Назарова Антона Андреевича.

\subsection{Интегируемые системы}
\label{sec:-}

Введение в квантовые интегрируемые системы и метод квантовой обратной задачи рассеяния.

Литература:
  \begin{itemize}
  \item Faddeev L.D. How Algebraic Bethe Ansatz works for integrable model. Arxiv preprint hep-th/9605187.
  \item Korepin, VE and Bogoliubov, NM and Izergin, AG. Quantum inverse scattering method and correlation functions. Cambridge Univ Pr 1997.
  \end{itemize}

1.Квантовые интегрируемые системы. Анзац Бете. Квантовый метод обратной задачи рассеяния.

2.Матрица монодромии. Интегралы движения.

\subsection{Алгебры Ли}
\label{sec:Lie}
Общие вещи про конечномерные и бесконечномерные алгебры Ли, книжек множество, все что надо есть в 
 \cite{kac1988modular}, \cite{difrancesco1997cft},

3.Алгебры Ли. Универсальная обертывающая алгебра. Теория представлений.

4.Алгебры Каца-Муди. Аффинные алгебры Ли. Алгебра Вирасоро.

\subsection{Квантовые группы}
\label{sec:Quantum-groups}

Общая теория по квантовым группам (без приложений).
  \begin{itemize}
  \item Etingof, P. and Schiffmann, O. Lectures on quantum groups. International press 1997
  \item Chari V., Pressley A. A guide to quantum groups. Cambridge Univ Press 1995.
  \item Majid S. Foundations of quantum group theory. Cambridge Univ Press 2000.
  \end{itemize}

5.Квантовые группы. Алгебры Хопфа.

6.Квантование Дринфельда-Джимбо.

7.Уравнение Янга-Бакстера. R-матрица.

\subsection{Теория струн, конформная теория поля}
\label{sec:CFT}

Введение в теорию струн и CFT, приложение теории из раздела \ref{sec:Lie}.

Литература:
Zweibach B. A first course in string theory. Cambridge Univ Press 2004, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{gaberdiel2000icf}

9.Теория струн. Действие струны Намбу, Полякова.

10.Критические струны и двумерная конформная теория поля.

11.Двумерная конформная теория поля. Конформная инвариантность. Уравнения Книжника-Замолодчикова.

12.Модели Весса-Зумино-Новикова-Виттена в двумерной конформной теории поля.

13.Алгебра токов в моделях Весса-Зумино-Новикова-Виттена. Конструкция Сугавары.

\subsection{AdS/CFT}
\label{sec:adscft}

Приложение всей предыдущей теории к актуальным современным проблемам :)

Литература:
\cite{Aharony:1999ti}, \cite{D'Hoker:2002aw}, Minahan, J.A. and Zarembo, K. The Bethe-ansatz for= 4 super Yang-Mills. //Journal of High Energy Physics, v 2003, 2003, \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky}

14.Суперсимметричная теория Янга-Миллса. Модель N=4. Конформная инвариантность.

8.Интегрируемые системы в N=4 SYM.

15.AdS/CFT-соответствие.

16.Интегрируемость в суперсимметричной калибровочной теории поля.

17.Струны на пространстве анти-Де-Ситтера и модели Весса-Зумино-Виттена.

\bibliography{program}{}
\bibliographystyle{utphys}
\end{document}

### 2010-05-12 AffineLieAlgebras/InformalNotes/article.tex
Pdf regenrated

--- 2010-04-28 AffineLieAlgebras/InformalNotes/article.tex
@@
 
+The modular-invariant partition function is constructed using (\ref{eq:39}):
+\begin{equation}
+  \label{eq:45}
+  Z=\left|\chi_{(0;2;0)}\chi+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
+\end{equation}
+
 \subsubsection{Non-maximal conformal embedding}

### 2010-05-13 GeneralOverview/WZW-CS.tex
String theory notes translation is completed.

@@
 
-We could not preserve all the symmetries during quantization. So we choose to save Lorenz invariance and reparametrisation invariance and break conformal invariance. It is so called conformal anomaly.
-
+При квантовании невозможно сохранить все симметрии.
+Поэтому мы сохраняем Лоренц-инвариантность и инвариантность относительно репараметризаций, но нарушаем конформную инвариантность.
+Возникает так называемая конформная аномалия.
+
+Поясним это для амплитуды перехода
 \begin{equation}
@@
 
-It is easy to see that norm is invariant under reparametrisations:
+Легко видеть, что норма инвариантна относительно репараметризаций:
 \begin{equation}
@@
 
-To investigate what happens top Weyl invariance after quantization let's introduce so called effective action. We integrate out fields $X^{\mu}$ and get following result.
-\begin{equation}
-  \label{eq:12}
-  e^{-S_X^{eff}[g_{ab}]} \overset{def}{=} \int {\cal D}X^{\mu} e^{-S_P [g_{ab},X]}
+Чтобы понять, что происходит с Вейлевской инвариантностью при квантовании, введем эффективное действие. Мы интегрируем по полям $X^{\mu}$ и получаем следующий результат.
+\begin{equation}
+  \label{eq:12} e^{-S_X^{eff}[g_{ab}]} \overset{def}{=} \int {\cal D}X^{\mu} e^{-S_P [g_{ab},X]}
 \end{equation}
@@
   \end{split}
-\end{equation}
-Here $R$ is scalar curvature of $g_{ab}$, and $\mu$ is a parameter depending on regularisation, for example for proper time regularisation $\mu=\frac{1}{4\pi\epsilon}$.
-The term $W[g,\sigma]$ is called Liouville's action.
-
-{\bf Notice} $\int R[x] \sqrt{g}d^2x = 4\pi \chi_E$, $\chi_E=2-2h$, $\chi_E$ - Euler characteristic of the surface, $h$ - genus of the surface.
-
-$W[g,\sigma]$  is called conformal anomaly.
-
-Variance of action
+\end{equation} Здесь $R$ - скалярная кривизна $g_{ab}$, а $\mu$ - параметр, зависящий от выбора регуляризации.
+Например, в регуляризации собственного времени $\mu=\frac{1}{4\pi\epsilon}$.
+Член $W[g,\sigma]$ имеет вид действия Лиувилля.
+
+{\bf Замечание} $\int R[x] \sqrt{g}d^2x = 4\pi \chi_E$, $\chi_E=2-2h$, $\chi_E$ - характеристика Эйлера поверхности, $h$ - род поверхности.
+
+$W[g,\sigma]$ называют конформной аномалией.
+
+Вариация действия
 \begin{equation}
@@
 \end{equation}
-We see that Weyl invariance is equivalent to tracelessness of energy-momentum tensor.
-
-After the quantization we have
+Видно, что Вейлевская инвариантность эквивалентна бесследовости тензора энергии-импульса.
+
+После квантования получаем 
 \begin{equation}
@@
 \begin{Def}
-  {\bf Two dimensional conformal field theory} - is the theory that transforms as in (\ref{eq:13}).
-
-  The factor before $W[g,\sigma]$ is called {\it central charge}.
+  {\bf Двумерная конформная теория поля} --- это теория, в которой действие преобразуется как в (\ref{eq:13}).
+
+  Множитель при $W[g,\sigma]$ называется {\it центральным зарядом}.
 \end{Def}
 
-At this moment we have too much freedom in our Feynman integral (\ref{eq:10}).
-We have diffeomorphisms (\ref{eq:4}) and Weyl transformations (\ref{eq:8}).
-We will fix the gauge so that the metric is given by the formula
+Сейчас у нас слишком много свободы в функциональном интеграле (\ref{eq:10}) --- диффеоморфизмы (\ref{eq:4})  и преобразования Вейля (\ref{eq:8}).
+Мы хотим зафиксировать калибровку так, чтобы метрика давалась формулой
 \begin{equation}
@@
 
-Faddeev-Popov ghosts appear as usual after this procedure.
-
+В результате этой процедуры возникают духи Фаддеева-Попова.
 \begin{equation}
@@
 \end{equation}
-Here $B,C$ are ghost fields, $B_{ab}(X)$ is symmetric and traceless tensor. All the functional integrals use metric $e^{\phi}\hat{g}$. 
+Здесь $B,C$ - поля духов, $B_{ab}(X)$ - симметричный бесследовый тензор. Все функциональные интегралы используют метрику $e^{\phi}\hat{g}$.
 \begin{equation}
@@
 \end{equation}
-We can fix Weyl invariance so that measures of integration over matter fields and ghosts fields in (\ref{eq:19}) don't depend on $\phi$. Then we get conformal anomaly in the exponent:
+Теперь мы можем зафиксировать вейлевскую инвариантность так, чтобы мера интегрирования по полям материи и полям духов  (\ref{eq:19}) не зависела от $\phi$.
+Тогда в экспоненте возникает конформная аномалия:
 \begin{equation}
@@
 \end{equation}
-$\frac{d}{48\pi}$ comes from matter fields, and $\frac{-26}{48\pi}$ from ghost fields, since both actions are actions of two-dimensional conformal field theory.
-
-Ordinary bosonic string lives in 26-dimensional space and doesn't interact with Liouville's gravity.
-Such a string is called ``critical string'' since it can exist only in critical dimension.
-Other string models are called non-critical strings.
-
-First integration in (\ref{eq:22}) is very inconvenient, since we integrate over $\phi$ with measure depending on $\phi$. This measure $\mathcal{D}_{e^{\phi}\hat{g}}\phi$ corresponds to interval
+$\frac{d}{48\pi}$ возникает из полей материи, а  $\frac{-26}{48\pi}$ --- из полей духов, так как оба эффективных действия являются действиями двумерной конформной теории поля.
+
+Обычная бозонная струна живет в 26 измерениях и не взаимодействует с гравитацией Лиувилля.
+Такая струна называется ``критической'', так как может существовать при критическом значении размерности пространства.
+Другие струнные модели называются некритическими струнами.
+
+Первое интегрирование в (\ref{eq:22}) очень неудобно, так как приходится интегрировать по $\phi$ с мерой, зависящей от $\phi$. Эта мера $\mathcal{D}_{e^{\phi}\hat{g}}\phi$ соответствует интервалу
+
 \begin{equation}
@@
 \end{equation}
-It is non-linear and is not invariant under the translations $\phi(x)\to \phi(x)+\eta(x)$.
-So for some time this was a problem since nobody knew how to work with such objects.
-
-But David-Distler-Kawai proposed to change action in order to take into account change of measure of integration to normal measure.
-
-They conjectured that the amplitude can be written in the form
+Он не линеен и не инвариантен относительно сдвигов $\phi(x)\to \phi(x)+\eta(x)$.
+В течении некоторого времени это было существенной проблемой, так как никто не знал, как работать с такими объектами.
+
+Но Дэвид, Дистлер и Каваи предложили изменить действие так, чтобы учесть изменение меры интегрирования к нормированной.
+
+Они предположили, что амплитуда может быть записана в виде
 \begin{equation}
@@
 \end{equation}
-where the measure $\mathcal{D}_{\hat{g}} \phi$ corresponds to the interval $\|\delta\phi\|^2_{DDK} = \int (\delta\phi)^2 \sqrt{\hat{g}}\, d^2x$ and it is invariant under the translations $\phi\to \phi+\eta$ ($\delta\phi\to \delta\phi$).
-$S_L$ here is Liouville's action with two undefined for now parameters $Q$ and $b$:
+где мера интегрирования  $\mathcal{D}_{\hat{g}} \phi$ соответствует интервалу $\|\delta\phi\|^2_{DDK} = \int (\delta\phi)^2 \sqrt{\hat{g}}\, d^2x$ и инвариантна относительно сдвигов $\phi\to \phi+\eta$ ($\delta\phi\to \delta\phi$).
+$S_L$ здесь - действие Лиувилля с двумя пока не определенными параметрами $Q$ и $b$:
 \begin{equation}
@@
 \end{equation}
-We choose following normalization:
+Мы выбираем следую нормировку:
 \begin{equation}
@@
 \end{equation}
-Liouville's term should be invariant under dilation $\hat{g}_{ab}\to e^{\sigma}\hat{g}_{ab}$.
-
-After we put
+Член Лиувилля должен быть инвариантен при дилатациях $\hat{g}_{ab}\to e^{\sigma}\hat{g}_{ab}$.
+
+После того, как мы положили
 \begin{equation}
@@
 \end{equation}
-Liouville's action becomes conformal, so that
+действие Лиувилля становится конформным, так что
 \begin{equation}
@@
 \end{equation}
-Where
+Где
 \begin{equation}
@@
 \end{equation}
-
-Then we require total central charge to vanish:
+Теперь мы требуем сокращения суммарного центрального заряда:
 \begin{equation}
@@
 \end{equation}
-
-Now the amplitude doesn't depend on $\hat{g}$ and parameters $Q$,$b$ are fixed.
+В результате амплитуда не зависит от  $\hat{g}$ и параметры  $Q$,$b$ фиксированы.
 \begin{equation}
@@
 \end{equation}
-In some finite area we can assume
+Мы можем положить
 \begin{equation}
@@
 \end{equation}
-There also could be additional term connected with the topology.
-
-Let's change variables
+в некоторой конечной области. Кроме того, могут возникать топологические члены.
+
+Сделаем замену переменных
 \begin{equation}
@@
 \end{equation}
-For fields and terms of the action we have
+Для полей и членов действия имеем
 \begin{equation}
@@
     S_P[X]=\int d^2z \bar{\partial}X \partial X\\
-    S_L[\phi] \propto \int d^2z \left[\bar{\partial} \phi \partial \phi+\mu e^{2 b \phi}\right] + \mbox{(topological terms)}
+    S_L[\phi] \propto \int d^2z \left[\bar{\partial} \phi \partial \phi+\mu e^{2 b \phi}\right] + \mbox{(топологические члены)}
   \end{split}
@@
 \end{equation}
-Laplace operator depends on metric
+Оператор Лапласа зависит от метрики
 \begin{equation}
@@
 \end{equation}
-
-It is self-conjugate operator.
-
-We can represent field $X$ as combination of eigenfunctions of Laplace operator $X(x)=\sum c_n X_n,\; \Delta X_n = \lambda_n X_n,\; \lambda_n=\lambda_n[g]$.
-Then we will integrate over all eigenfunctions:
+Это самосопряженный оператор.
+
+Поле $X$ может быть разложено по собственным функциям оператора Лапласа $X(x)=\sum c_n X_n,\; \Delta X_n = \lambda_n X_n,\; \lambda_n=\lambda_n[g]$.
+Тогда от интегрирования по всем полям $X$ мы перейдем к интегрированию по всем собственным функциям.
+Этот интеграл может быть (условно) записан в виде произведения собственных значений оператора Лапласа или как его детерминант
 \begin{equation}
@@
 \end{equation}
-Obviously we could not calculate $\lambda_n$, but we can get the determinant.
+Очевидно, что мы не можем вычислить все  $\lambda_n$, но мы можем получить детерминант.
 \begin{equation}
@@
 \end{equation}
-The last integral diverges, so we need to regularise it. We will use heat kernel regularisation.
+Последний интеграл расходится, поэтому его необходимо регуляризовать. Мы используем регуляризацию теплового ядра.
 \begin{equation}
@@
 \end{equation}
-As we already mentioned, $\hat{g}_{ab}$ could be put equal to $\rho dz d\bar{z}$ in finite area. Then
+Как уже отмечалось, $\hat{g}_{ab}$ можно положить равным $\rho dz d\bar{z}$ в конечной области. Тогда
 \begin{equation}
@@
 \end{equation}
-For variation of effective action we have
+Для вариации эффективного действия имеем:
   \begin{multline}
@@
   \end{multline}
-
-Let's introduce Green function for heat equation
+Введем функцию Грина для уравнения теплопроводности
 \begin{equation}
@@
 \end{equation}
-Then for variation of action we have
+Теперь вариация действия имеет вид
 \begin{equation}
@@
 
-In Conformal Field Theory 
+Здесь не хватает какого-то вывода.
+
+В конформной теории поля
 \begin{equation}
@@
 \end{equation}
-$C$ is a central charge.
-
-For flat metric $g_{ab}=\delta_{ab}$ we have
+$C$ --- центральный заряд.
+
+Для плоской метрики $g_{ab}=\delta_{ab}$ имеем
 \begin{equation}
@@
 \end{equation}
-Then we put $T_{zz}=T,\quad T_{\bar{z}\bar{z}}=\bar{T},\quad T_{z\bar{z}}=T_{\bar{z}z}$. In flat space from continuity equation $\bar{\partial}T_{zz}+\partial T_{\bar{z}\bar{z}}=0$ we have
+Положим $T_{zz}=T,\quad T_{\bar{z}\bar{z}}=\bar{T},\quad T_{z\bar{z}}=T_{\bar{z}z}$. В плоском пространстве из уравнения неразрывности $\bar{\partial}T_{zz}+\partial T_{\bar{z}\bar{z}}=0$ следует
 \begin{equation}
@@
     T_{z\bar{z}}=0\\
-    \bar{\partial}T_{zz}=\bar{\partial}T=0,\quad T \mbox{- holomorphic}\\
-    \partial T_{\bar{z}\bar{z}}=\partial \bar{T}=0,\quad \bar{T} \mbox{- antiholomorphic}\\
-  \end{split}
-\end{equation}
-In curved space continuity equation reads $\nabla_a T^{ab}=0$ and we can choose coordinate system where $g_{ab}dx^a dx^b = \rho dz\, d\bar{z}=e^{\sigma}dz\,d\bar{z}$.
-Then we introduce pseudo energy $T$:
+    \bar{\partial}T_{zz}=\bar{\partial}T=0,\quad T \mbox{- голоморфная}\\
+    \partial T_{\bar{z}\bar{z}}=\partial \bar{T}=0,\quad \bar{T} \mbox{- антиголоморфная}\\
+  \end{split}
+\end{equation}
+
+В искривленном пространстве уравнение неразрывности имеет вид $\nabla_a T^{ab}=0$ и мы можем выбрать такую систему координат, в которой $g_{ab}dx^a dx^b = \rho dz\, d\bar{z}=e^{\sigma}dz\,d\bar{z}$.
+Теперь введем псевдоэнергию $T$:
 \begin{equation}
@@
 \end{equation}
-where $t_{zz}=(\partial \sigma)^2-2\partial^2 \sigma$. It is easy to check that $\bar{\partial}T=0$ in this case.
-
-For transformations $z\to w(z)$
+где $t_{zz}=(\partial \sigma)^2-2\partial^2 \sigma$. Легко проверить, что в этом случае $\bar{\partial}T=0$.
+
+При преобразованиях $z\to w(z)$ величины преобразуются следующим образом
 \begin{equation}
@@
     t\to \left(\frac{dw}{dz}\right)t(w)+2\{w,z\}\\
-    \mbox{where}\; \{w,z\}=\left(\frac{\partial_z^3 w}{\partial_z w}-\frac{3}{2}\left(\frac{\partial_z^2 w}{\partial_z}\right)^2\right)\\
+    \mbox{где}\; \{w,z\}=\left(\frac{\partial_z^3 w}{\partial_z w}-\frac{3}{2}\left(\frac{\partial_z^2 w}{\partial_z}\right)^2\right)\\
     T\to \left(\frac{dw}{dz}\right)^2 T(w)+\frac{C}{12}\{w,z\}\\
@@
 \end{equation}
-Energy-momentum tensor is the generator of coordinate transformations $x^a\to x^a+\epsilon^a(x)$:
+
+Тензор энергии-импульса является генератором преобразований координат $x^a\to x^a+\epsilon^a(x)$:
 \begin{equation}
@@
 \end{equation}
-
+Выполняются следующие требования:
 \begin{equation}
@@
 \end{equation}
-Correlation functions don't change under conformal transformations.
+Корреляционные функции не меняются при конформных преобразованиях
 \begin{equation}
@@
 \end{equation}
-Where $\tilde{T}_{ab}=\epsilon_{ac}T_{cb}$.
-
-Let
+Здесь $\tilde{T}_{ab}=\epsilon_{ac}T_{cb}$.
+
+Пусть
 \begin{equation}
@@
 \end{equation}
-Substituting $T(z)$ in place of arbitrary operator $A$ we get 
+Подставляя $T(z)$ на место произвольного оператора $A$ получаем
 \begin{equation}
@@
 
-If $w(z)=z+\epsilon(z)$ where $\epsilon$ is small, $T$ transforms as following:
+Если $w(z)=z+\epsilon(z)$, где $\epsilon$ мало, $T$ преобразуется следующим образом:
 \begin{equation}
@@
 \end{equation}
-We suppose that for full set of operators $\{A_j(x)\}$ there exists operator product expansion:
-!!! How can it be proved ????
+
+Предположим, что для полного набора операторов  $\{A_j(x)\}$ существует операторное разложение:
 \begin{equation}
@@
 \end{equation}
-Then for product $T(u)T(z)$ we have
+Тогда для произведения $T(u)T(z)$ получаем
 \begin{equation}
@@
 \end{equation}
-We can recover the poles from formula (\ref{eq:59}):
+Полюса можно восстановить из формулы (\ref{eq:59}):
 \begin{equation}
   \label{eq:62}
-  T(u)T(z)=\frac{C}{2(u-z)^4}+\frac{2T(z)}{(u-z)^2}+\frac{T'(z)}{u-z}+\mbox{non-singular terms}
-\end{equation}
-Now introduce the operators $L_n$:
+  T(u)T(z)=\frac{C}{2(u-z)^4}+\frac{2T(z)}{(u-z)^2}+\frac{T'(z)}{u-z}+\mbox{несингулярные члены}
+\end{equation}
+Теперь введем операторы $L_n$:
 \begin{equation}
@@
 \end{equation}
-It is possible to show that for $n,m\in \mathbb{Z}$
+Можно показать, что для $n,m\in \mathbb{Z}$
 \begin{equation}
@@
 \end{equation}
-and $\{L_n\}$ constitute Virasoro algebra.
-
-All the fields in the theory are sums of multiplets of Virasoro algebra:
+и операторы $\{L_n\}$ образуют алгебру Вирасоро.
+
+Все поля в теории оказываются суммами мультиплетов алгебры Вирасоро:
 \begin{equation}
@@
 
-There is a primary field in every multiplet:
+В каждом мультиплете есть одно примарное поле, которое преобразуется так:
 \begin{equation}
@@
 \end{equation}
-All other fields are built of primary fields and are called secondary:
+Все остальные поля называются вторичными и получаются из примарного действием операторов $L_{-n}$:
 \begin{equation}
@@
 
-Correlation functions are expressed as combinations of correlation functions of primary fields.
-
-The only thing that is yet undefined is the set of scaling dimensions of primary fields.
-So to fix the theory we should define $\Phi_a,\; \Delta_a,\; C^c_{ab}$.
-Then our theory is solved.
-If the number of primary fields is finite, such a model is called {\it minimal}.
-
-For example, following fields are Weyl-invariant:
+Например, следующие поля инвариантны относительно преобразований Вейля
 \begin{equation}
   \label{eq:68}
-  O_a=\int \Phi_{\Delta}e^{2a\phi}\,d^2x,\quad \mbox{where}\;\Delta+a(Q-a)=1
-\end{equation}
-$O_a$ - is the main observable of string theory with gravitational dimension $\delta_a=-\frac{a}{b}$.
+  O_a=\int \Phi_{\Delta}e^{2a\phi}\,d^2x,\quad \mbox{где}\;\Delta+a(Q-a)=1
+\end{equation}
+$O_a$ - главная наблюдаемая теории струн с гравитационной размерностью $\delta_a=-\frac{a}{b}$.
 \begin{equation}
@@
 \end{equation}
-\subsection{Connection with string theory}
-
-We can start from arbitrary conformal field theory, find $b$ from equation $C+6\left(b+\frac{1}{b}\right)^2=25$ and obtain some non-critical string theory.
-But for $d>1$ $b$ becomes complex and this fact leads to unsolved yet problems.
+
+Корреляционные функции выражаются как комбинации корреляционных функций примарных полей.
+
+Осталось определить только скейлинговые размерности примарных полей.
+Чтобы определить теорию полностью надо задать $\Phi_a,\; \Delta_a,\; C^c_{ab}$.
+Если число примарных полей конечно, то теория называется {\it минимальной}.
 
@@
 \begin{equation}
-  \label{eq:4}
+  \label{eq:100}
   \partial_{\bar z}J=0,\quad \partial_z \bar J=0
@@
 \begin{equation}
-  \label{eq:6}
+  \label{eq:102}
   T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
@@
 \begin{equation}
-  \label{eq:1}
+  \label{eq:103}
   S=\frac{k}{4\pi}\int_M \mathrm{tr}(A\wedge dA+\frac{2}{3}A\wedge A\wedge A)
@@
 \begin{equation}
-  \label{eq:2}
+  \label{eq:104}
   F=DA=dA+A\wedge A\in \Omega^2(M,g)
@@
 \begin{equation}
-  \label{eq:4}
+  \label{eq:101}
   \sigma=\frac{1}{24\pi^2} \mathrm{Tr} (\mu\wedge\mu\wedge\mu)
@@
 \begin{equation}
-  \label{eq:10}
+  \label{eq:105}
   A=A+A_0 dt
@@
 \begin{equation}
-  \label{eq:13}
+  \label{eq:99}
   \gamma\to h^{-1} \gamma h

### 2010-05-21 GeneralOverview/WZW-CS.tex
Conformal blocks are described

@@
 
-\subsection{Глобальная конформная инвариантность и уравнения Книжника-Замолодчикова}
-\label{sec:knizhnik-zamolodchikov}
+\subsection{Конформные блоки}
+\label{sec:conformal-blocks}
+
+Примарные поля преобразуются по формуле \eqref{eq:66} в голоморфной и антиголоморфной части, то есть полностью
+\begin{equation}
+  \label{eq:106}
+  \Phi_{\Delta,\bar{\Delta}}(z,\bar{z})\to \left(\frac{\partial w}{\partial z}\right)^{\Delta}
+  \left(\frac{\partial \bar{w}}{\partial \bar{z}}\right)^{\bar{\Delta}}\Phi_{\Delta,\bar{\Delta}}(w,\bar{w})
+\end{equation}
+Операторное разложение примарных полей
+\begin{equation}
+  \label{eq:108}
+  \Phi_{\Delta_1,\bar{\Delta_1}}(z,\bar{z})\Phi_{\Delta_2,\bar{\Delta_2}}(0,0)=\sum_i A_i z^{\Delta_i-\Delta_1-\Delta_2}\bar{z}^{\bar{\Delta_i}-\bar{\Delta_1}-\bar{\Delta_2}}\left[\Phi_{\Delta_i,\bar{\Delta_i}(z,\bar{z})\right]
+\end{equation}
+Здесь выражение в квадратных скобках обозначает вклад всех полей конформного семейства $\Phi_{\Delta_i,\bar{\Delta_i}}$. Рассмотрим четырехточечную корреляционную функцию.
+\begin{equation}
+  \label{eq:109}
+  \left< \Phi_{\Delta_4,\bar{\Delta_4}}(z_4,\bar{z_4}) \Phi_{\Delta_3,\bar{\Delta_3}}(z_3,\bar{z_3}) \Phi_{\Delta_2,\bar{\Delta_2}}(z_2,\bar{z_2})  \Phi_{\Delta_1,\bar{\Delta_1}}(z_1,\bar{z_1})\right>
+\end{equation}
+При помощи проективного преобразования комплексной плоскости можно поместить три из четырех операторов в заданные точки, например $z_1=0,z_2=z,z_3=1,z_4=\infty$, так что корреляционная функция зависит от одной комплексной переменной
+\begin{equation}
+  \label{eq:110}
+  z=\frac{(z_2-z_1)(z_4-z_3)}{(z_3-z_1)(z_4-z_2)}
+\end{equation}
+Используя разложение \eqref{eq:108}, получаем для корреляционной функции
+\begin{equation}
+  \label{eq:111}
+   \left< \Phi_{\delta_4,\bar{\delta_4}}(\infty,\infty) \Phi_{\delta_3,\bar{\delta_3}}(1,1) \Phi_{\delta_2,\bar{\delta_2}}(z,\bar{z})  \Phi_{\delta_1,\bar{\delta_1}}(0,0)\right>=\sum_i G_i \mathcal{F}(c,\Delta_i,\delta_k,z)\mathcal{F}(c,\bar \Delta_i,\bar \delta_k,\bar z)
+\end{equation}
+Функция $\mathcal{F}$ называется конформным блоком, а константы $G_i$ выражаются через $A_i$.
+
+Аналогично для случая многочастичных разложений.
+
+Из требований конформной инвариантности и предположения о существовании операторного разложения получаем требование голоморфной факторизации
+\begin{equation}
+  \label{eq:107}
+  \left< \Phi_{\Delta_1,\bar{\Delta_1}}(z_1,\bar{z_1})\dots \Phi_{\Delta_N,\bar{\Delta_N}}(z_N,\bar{z_N})\right>=
+  \sum C^{ab} \mathcal{F}_a(z_1,\dots,z_N)\overline{\mathcal{F}_b(z_1,\dots,z_N)}
+\end{equation}
+Функции $\mathcal{F},\bar{\mathcal{F}}$ называются конформными блоками.
+
+В WZW-моделях на уравнения Книжника-Замолодчикова можно переписать в терминах конформных блоков. 
+Вообще если известно пространство конформных блоков, то можно найти все константы в операторных разложениях.
+
+При изучении теории на поверхностях рода больше единицы основной вопрос состоит именно в построении пространства конформных блоков.
 
@@
 \end{equation}
-Для корреляционных функций примарных полей можно получить уравнения Книжника-Замолодчикова, которые следуют из глобальной $G\times G$-инвариантности
+\subsection{Глобальная инвариантность и уравнения Книжника-Замолодчикова}
+\label{sec:knizhnik-zamolodchikov}
+Подставив в тождества Уорда коррелятор $\left<J(z)\phi_1(z_1)\dots \phi_n(z_n)\right>$ 
+для корреляционных функций примарных полей можно получить уравнения Книжника-Замолодчикова, которые следуют из глобальной $G\times G$-инвариантности
 \begin{equation}

### 2010-05-21 AffineLieAlgebras/DualFunctions/article.tex
Some files added, pdf regenerated

--- 2010-04-30 AffineLieAlgebras/InformalNotes/article.tex
@@
 \begin{document}
-\thispagestyle{empty}
-
-\begin{center}
-{\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
-\end{center}
-\vskip 1 cm
-\begin{flushright}
-{\large \bf SPbU-IP-09-08}
-\end{flushright}
-\hfill {}
-\vskip 1 cm
-\begin{center}
-{\Huge \bf Recursive algorithms, branching coefficients \\ for affine algebras and applications\\[0.5cm]
-}
-\end{center}
-\vskip 1.0 cm
-\begin{center}
-{\Large \bf
-Vladimir Lyakhovsky\\[2mm]
-Anton Nazarov}
-\end{center}
-\vfill
-\begin{center}
-{\large Department of Theoretical Physics\\
-}
-\end{center}
-\vfill
-\begin{center}
-SAINT-PETERSBURG \\
-2009
-\end{center}
-
-\newpage
-
-\pagenumbering{arabic}
-\title{\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}}
+\title{\textbf{{\Large {System of dual functions in the reduction of affine Lie algebra representations}}}}
 \author{Vladimir Lyakhovsky \thanks{ Supported by
@@
 \begin{abstract}
-  Recurrent relations for branching coefficients in affine Lie algebras highest weight modules are studied.
-The decomposition algorithm for  integrable highest weight modules reduction based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive  subalgebra.
-We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original one.
-The possible applications of subtracted fans in CFT models are considered.
+  Using the recurrent relation for the series expansion of the affine Lie algebra branching functions we construct the dual set of the functions, which can be completely described using Weyl symmetry of affine Lie algebra.
+Explicit construction of the dual functions can be carried out using the geometric finite automata approach.
+The task of the explicit construction of the branching functions is then rewritten as the procedure of the inversion of matrix of dual functions.
+Finally we study the properties of the dual functions under modular and conformal transformations and discuss possible applications in two-dimensional conformal field theory.
 \end{abstract}
-
-\section{Introduction}
-\label{sec:introduction}
-
-The problem of reduction of a Lie algebra representation to a  subalgebra is studied for several decades and has various applications in physics.
-In the context of finite-dimensional algebras it is important for the study of great unification models whilst the branching problem for affine Lie algebras emerges in conformal field theory, for example, in the construction of the modular-invariant partition functions \cite{difrancesco1997cft}.
-
-There exist several approaches to the computation of the branching coefficients. Some of them use the BGG
-resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
-\cite{kac1990idl},\cite{wakimoto2001idl}), the Schure function series \cite{fauser2006new}, the BRST
-cohomology \cite{hwang1994general}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
-combinatorial methods applied in \cite{feigin707principal}.
-
-Usually only the embedding of the maximal reductive subalgebras is considered since the case of non-maximal subalgebra can be obtained using the chain of maximal injections.
-In this paper we study the recurrent properties for branching coefficients which generalise the recurrent relations obtained earlier (see the paper \cite{ilyin812pbc}and the references therein) to the cases of non-maximal reductive subalgebras.
-The result is formulated by an introduction of a new injection fan called "subtracted fan".
-Using this new tools we formulate simple and explicit algorithm for the computation of branching coefficients which is applicable to the non-maximal subalgebras of finite-dimensional and affine Lie algebras.
-
-We show that our algorithm can be used in a study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some  physical limitations.
-
-The paper is organised as follows.
-In the next subsection  we fix the notations used throughout the paper.
-In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules of algebra $\mathfrak{g}$ with respect to a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}).
-In the next Section \ref{sec:examples} we present several examples and discuss some applications in CFT models (s.
-\ref{sec:phys-appl}).
-We conclude the paper with a review of obtained results.
-Possible future developments are discussed (s.
-\ref{sec:conclusion}).
-
-\subsection{Notation}
-\label{sec:notation}
-
-Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
-underlying finite-dimensional subalgebras $\go$ and $%
-\ao$ and an injection $\frak{a}\longrightarrow \frak{g%
-}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
-correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
-}}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
-}_{\go}^{\ast }$\ .
-
-We use the following notations adopted from the paper \cite{ilyin812pbc}.
-
-$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
-of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
--module with the highest weight $\nu $ );
-
-$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
-\left( \text{resp. }\frak{a}\right) $ ;
-
-$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
-^{+} $ $\left( \text{resp. }\Delta _{\frak{a}}^{+}\right) $--- the positive
-root system (of $\frak{g}$ and $\frak{a}$ respectively);
-
-$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
-\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $\Delta
-$ (resp. in $\left( \Delta _{\frak{a}}\right) $);
-
-$\co{\Delta}$ , $\left( \co{\Delta _{\frak{a}}}%
-\right)$ --- the finite root system of the subalgebra $\co{%
-\frak{g}}$ (resp. $\co{\frak{a}}$);
-$\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);
-
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ --- the
-weight diagram of $L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right)
-$ ;
-
-$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
-
-$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
-
-$\bar{C}, \left(\bar{C_{\mathfrak{a}}}\right)$ --- the closure of the fundamental Weyl chamber;
-
-$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
-
-$\epsilon \left( w\right) :=\det \left( w\right) $ ;
-
-$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $i
-$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \text{resp. }\frak{a}%
-\right) $; $i=0,\ldots ,r$ ,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
-
-$\delta $ --- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);
-
-$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
-}\right) $--- the basic coroot for $\frak{g}$ $\left( \text{resp. }\frak{a}%
-\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
-
-$\co{\xi }$ , $\co{\xi _{\left( \frak{a}\right) }}$
---- the finite (classical) part of the weight $\xi \in P$ , $\left( \text{%
-resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $;
-
-$\lambda =\left( \co{\lambda };k;n\right) $ --- the
-decomposition of an affine weight indicating the finite part $\co{\lambda }$, level $k$ and grade $n$\ .
-
-$P$ $\left( \text{resp. } P_{\frak{a}}\right) $ \ --- the weight lattice;
-
-$M \left( \text{resp. }M_{\frak{a}}\right) :=$
-
-\noindent $=\left\{
-\begin{array}{c}
-\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\text{ }\left( \text{resp. }%
-\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \frak{a}\right) i}^{\vee }\right)
-\text{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
-\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\text{ }\left( \text{resp. }\sum_{i=1}^{r}%
-\mathbf{Z}\alpha _{\left( \frak{a}\right) i}\right) \text{for }A_{r}^{\left(
-u\geq 2\right) }\text{ and }A\neq A_{2r}^{\left( 2\right) },
-\end{array}
-\right\} ;$
-$\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
-$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}}}\epsilon (w)e^{w\circ (\nu +\rho
-_{_{\frak{a}}})-\rho _{_{\frak{a}}}}$ --- the corresponding singular weight
-element for the $\frak{a}$-module $L_{\frak{a}}^{\nu }$;
-
-$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
-a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
-\xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
-L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
-coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
-\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
-)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
-w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
-\circ (\nu +\rho _{a})-\rho _{a}}$ ), (this set is similar to $P_{\mathrm{%
-nice}}^{\prime }\left( \mu \right) $ in \cite{wakimoto2001idl})
-
-$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
-}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \text{%
-resp. }\in P_{\frak{a}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
-L_{\frak{a}}^{\nu } $);
-
-$ch\left( L^{\mu }\right) $ $\left( \text{resp. }ch\left( L_{\frak{a}}^{\nu
-}\right) \right) $--- the formal character of $L^{\mu }$ $\left( \text{resp. }%
-L_{\frak{a}}^{\nu }\right) $;
-
-$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
-+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
-\mathrm{{mult}\left( \alpha \right) }}}=\frac{\Psi ^{\left( \mu \right) }}{%
-\Psi ^{\left( 0\right) }}$ --- the Weyl-Kac formula.
-
-$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
-mult}\left( \alpha \right) }}=\Psi ^{\left( 0\right) }\quad $
-
-\noindent $\left( \text{resp. }R_{\frak{a}}:=\prod_{\alpha \in \Delta _{%
-\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{%
-\left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $--- the
-denominator.
-
-$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ --- the reduction of the module;
-
-$b^{(\mu)}_{\nu}$ --- the branching coefficients;
-
-\begin{equation}
-  \label{eq:21}
-  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
-        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
-  }^{\left( \mu \right) }e^{\lambda }
-\end{equation}
-
- $k_{\lambda}$ --- the anomalous branching coefficients;
-
-It is important to mention that
-\begin{equation}
-  \label{eq:20}
-  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}
-\end{equation}
-
-$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$ --- the embedding index.
-
-\section{Recurrent relation for branching coefficients. Singularities and subtractions}
-\label{sec:recurr-form-branch}
-
-Our aim is to demonstrate that despite possible singularities arriving in the Weyl denominator
-when it is projected to the subalgebra root space injection fan technique can be properly modified.
-The result of such modification is that the generalized recurrent relations for anomalous branching
-coefficients \eqref{eq:21} must be reformulated in the following form:
-\begin{equation}
-  \label{eq:1}
-  \begin{array}{c}
-      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
-\left.
-+\sum_{\gamma \in
-\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
-+\gamma }^{\left( \mu \right) }\right)
-  \end{array}
-   \end{equation}
-Here $\mathfrak{a}_{\bot}$ is the subalgebra described by the roots of $\mathfrak{g}$
-orthogonal to the root subsystem of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group,
-$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
-of the denominator $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
-(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
-is the coefficient of $e^{\gamma}$ in this expansion.
-In the next subsection we study the situation in details and prove the validity of this relation.
-
-In the section \ref{sec:algorithm} we  shall describe the  computational algorithm for  branching coefficients
-based on this formula and present some examples.
-
-\subsection{Proof of the recurrent relation}
-\label{sec:proof}
-
-Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
-projection operators $\pi_{\mathfrak{a}}$ that bring the roots of $\mathfrak{g}$ to the
-weight subspace of $\mathfrak{a}$:
-\begin{equation}
-  \label{eq:3}
-  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
-    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
-  \Longrightarrow\quad
-  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
-  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
-\end{equation}
-The Weyl-Kac character formula leads to
-the equality
-\begin{equation}
-  \label{eq:4}
-  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
-  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
-  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
-  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
-  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
-\end{equation}
-
-It is important to keep in mind that the projection of some of positive roots of
-the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the
-root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the
-algebra $\mathfrak{g}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}
-=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
-\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
-
-Notice that if the set $\Delta^{+}_{\bot}$ is non-empty the Weyl reflections
-corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup
-$W_{\bot}$ of the Weyl group $W$. Consider any two positive roots $\alpha,\;
-\beta\in \Delta^{+}_{\bot}$ and the corresponding Weyl reflections
-$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since roots of the subalgebra
-$\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they
-are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
-So the subgroup $W_{\bot}$ preserves the root system of the subalgebra $\mathfrak{a}$.
-
-Thus we have obtained the root system $\Delta_{\bot}$ which is orthogonal to the root
-system $\Delta_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$ . This root system
-can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
-
-Now we are to find out when the subset $\Delta^{+}_{\bot}$ is non-empty
-and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
-
-If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then
-the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and
-it is clear that $\Delta^{+}_{\bot}$ is empty.
-On the other hand
-non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
-through the chain of maximal embeddings
-$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
-The maximal regular embeddings are constructed by the exclusion of one or two roots
-from the extended Dynkin diagram of the algebra. Since this process can give us
-non-connected Dynkin diagrams we can see which roots are orthogonal to the root
-space of non-maximal regular subalgebra $\mathfrak{a}$.
-
-Consider for instance regular the embedding of $A_1\subset B_2$.
-
-The extended Dynkin diagram of $B_2$ is presented in the Figure \ref{fig:B2Dynkin}.
-\begin{figure}[ph]
-  \centering
-  \includegraphics[width=50mm]{B2_A1_diagram.pdf}
-  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
-  \label{fig:B2Dynkin}
-\end{figure}
-Drop the central node to describe the embedding $A_1\oplus A_1\subset B_2$.
-In this case we have: $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
-
-The simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for a regular
-embedding $\mathfrak{a}\subset \mathfrak{g}$
-when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple can be formulated
-as follows:
-if the Dynkin diagram of $\mathfrak{g}$ can be split into the disconnected
-diagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
-then the subset $\Delta_{\bot}$ is non-empty,
-subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the
-$\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.
-
-Note that when we study the regular embedding obtained by dropping the nodes
-of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the
-subalgebra $\mathfrak{a}$ is one of the connected components,
-the subalgebra $\mathfrak{a}_{\bot}$ may be larger than the algebra
-generated by the remaining connected components.
-Consider for example the embedding of $B_2\subset B_4$ (the figure \ref{fig:dynkin}).
-In this case by eliminating
-the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
-into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
-sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to
-$A_1\oplus A_1$ but to $B_2$ (the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).
-
-Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$ must not form a direct sum in $\mathfrak{g}$.  
-Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
- Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the remaining nodes of the diagram of $\mathfrak{g}$.
-Consider the remaining diagram.
-This diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ of $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$.
-It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$.
-So the question is whether $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them.
-It is possible when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.
-
-All the cases are listed in the table \ref{tab:diagrams}.
-\begin{table}[ph]
-\label{tab:diagrams}
-\noindent  \centering{
-\begin{tabular}{|l|l|l|l|}
-  \hline
-  $\mathfrak{g}$ & Extended diagram of the algebra $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
-  \hline
-  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
-  \hline
-  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\
-  \hline
-  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
-  \hline
-  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
-  \hline
-\end{tabular}
-\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
-\end{table}
-
-For the algebra $\mathfrak{g}$ from the series $A_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r+1\}$ are $\Delta=\{\alpha_{ i j}= e_i- e_j,\; 1\leq i, j\leq r+1\}$, $\Delta^{+}=\{\alpha_{ij},\; i<j\}$ and the set of simple roots consists of $\alpha_{1,2},\alpha_{2,3},\dots,\alpha_{r,r+1}$.
-So for the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consisting of first $r_{\mathfrak{a}}$ simple roots we get $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{ i j},\; r_{\mathfrak{a}}+1<i,j\leq r+1\}$ and $\mathfrak{a}_{\bot}=A_{r-r_{\mathfrak{a}}-1}$.
-
-For the algebra $\mathfrak{g}$ from the series $B_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;i<j;\; \alpha_{\pm j}=\pm e_{ j},\; 1\leq j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; \alpha_j;\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_r$.
-So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}-1}$.
-Otherwise if $\mathfrak{a}=B_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_r$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
-It is the only case when simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.
-There exists the third possibility to get the pair of subalgebras $\mathfrak{a},\mathfrak{a}_{\bot}$ with the regular subalgebra $\mathfrak{a}$ by dropping single node from the extended Dynkin diagram of $B_r$.
-It can be done by taking as the set of simple roots of $\mathfrak{a}$ the set $\{\alpha_{1,-2},\alpha_{1,2},\alpha_{2,-3},\dots,\alpha_{r_{\mathfrak{a}}-1,-r_{\mathfrak{a}}}\}$.
-Then $\mathfrak{a}=D_{r_{\mathfrak{a}}}$, $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
-
-For the algebra $\mathfrak{g}$ from the series $C_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;i<j;\; \alpha_{\pm j}=\pm 2e_{ j},\; 1\leq j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; \alpha_j;\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_r$.
-So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=C_{r-r_{\mathfrak{a}}-1}$.
-Otherwise if $\mathfrak{a}=C_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_r$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=C_{r-r_{\mathfrak{a}}}$.
-
-For the algebra $\mathfrak{g}$ from the series $D_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;1\leq i<j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_{r-1,r}$.
-So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=D_{r-r_{\mathfrak{a}}-1}$.
-Otherwise if $\mathfrak{a}=D_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_{r-1,r}$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=D_{r-r_{\mathfrak{a}}}$.
-
-In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
-special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}. 
-\begin{figure}[ph]
-\noindent  \centering{
-  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
-  \caption{Special embedding $A_1\subset A_2\subset A_3$.
-Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
-}
-  \label{fig:a1a2a3}
-\end{figure}
-
-Using the existing classification of maximal special subalgebras \cite{dynkin1952semisimple} we immediately have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
-\begin{equation}
-  \label{eq:42}
-  \begin{array}{lll}
-      su(p)\oplus su(q) & \subset su(pq) &\\
-      so(p)\oplus so(q) & \subset so(pq) &\\
-      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
-      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
-      so(p)\oplus so(q) & \subset so(p+q)& \text{for}\;p\;\text{and}\;q\;\text{odd}\\
-  \end{array}
-\end{equation}
-Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.
-
-Up to this point we considered the problem of $\mathfrak{a}_{\bot}$-construction given $\mathfrak{a}\in\mathfrak{g}$ for regular injections in terms of Dynkin diagrams.
-When the root systems $ \Delta$ and $\Delta_{\mathfrak{a}}$ are known explicitly all that we need is to select the roots
-$\Delta_{\bot}=\left\{\alpha\in \Delta:\alpha\bot \Delta_{\mathfrak{a}}\right\}$ and correspondingly the positive roots
-$\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$.
-
-Now consider the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$-module 
-with the highest weight $\mu$. For the character of this module we have
-\begin{equation}
-  \label{eq:41}
-  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
-\end{equation}
-The projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ gives us the single element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
-
-Using this property we can reconsider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules.
-Multiply the equation (\ref{eq:4}) by the element
-\begin{equation}
-  \label{eq:5}
-  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
-\end{equation}
-Taking into account that for any formal series $Q \in {\cal E}$ and the binomial the projection commutes with the multiplication,
-\begin{equation}
-  \label{eq:6}
-  \pi_{\mathfrak{a}} (Q) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(Q\cdot (1-e^{-\alpha})\right),
-\end{equation}
-we can rewrite the 
-product of (\ref{eq:4}) and (\ref{eq:5}) in the form:
-\begin{multline}
-  \label{eq:7}
-  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
-\end{multline}
-The right-hand side of this equation can be reorganised similarly to what was performed in the paper \cite{ilyin812pbc}, by introducing the anomalous branching coefficients $k_{\lambda}$,
-\begin{equation}
-  \label{eq:10}
-  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
-        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
-  }^{\left( \mu \right) }e^{\lambda }
-\end{equation}
-and simplifying the multiplier:
-\begin{multline}
-  \label{eq:12}
-  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
-    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
-\end{multline}
-
-If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of the Weyl group $W$.
-Let us reorganise the summation in the left-hand side of (\ref{eq:12}).
-Consider the factor-space $W_{\bot}\backslash W$.
-For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
-\begin{multline}
-  \label{eq:13}
- \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
- \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
-\end{multline}
-The fraction in the right-hand side of the equation is similar to the character of some  $\mathfrak{a}_{\bot}$-module.
-Let us rewrite the shifted weights
-\begin{equation}
-  \label{eq:30}
-  \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}+\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho
-\end{equation}
-
-Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we get
-\begin{multline}
-  \label{eq:14}
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
-\end{multline}
-The projector $\pi_{\mathfrak{a}}$ transforms the character of the module ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ into an element equal to the dimension of the module multiplied by the unit element:
-  \begin{multline}
-    \label{eq:15}
-    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
-    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
-  \end{multline}
-
-Thus we have the equality
-\begin{multline}
-  \label{eq:9}
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
-  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
-  \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
-\end{multline}
-Following the transformations performed in \cite{ilyin812pbc} we rewrite the multiplier in the right-hand side:
-\begin{equation}
-  \label{eq:11}
-    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})} \left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}=
-     -\sum_{\gamma\in P_{\mathfrak{a}}} s(\gamma)e^{-\gamma}
-\end{equation}
-
-For the coefficient function $s\left( \gamma \right) $ define the carrier $\Phi _{\frak{a%
-}\subset \frak{g}}\subset P_{\frak{a}}$:
-\begin{equation}
-\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
-\gamma \right) \neq 0\right\} ;  \label{phi-d}
-\end{equation}
-In these terms the equation for the formal elements,
-\begin{multline}
-  \label{eq:16}
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
-  = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
-  k_{\lambda }^{\left( \mu \right) }e^{\lambda } \\
-  =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma }
-\end{multline}
-leads to the following equality 
-\begin{equation}
-  \label{eq:17}
-   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\quad \xi\in P_{\mathfrak{a}}
-\end{equation}
-
-To get the recurrent relations for the anomalous branching coefficients we use the following procedure  (similar to that in \cite{ilyin812pbc}).
-Let $\gamma_{0} $ be the lowest vector with respect to the natural ordering in $%
-\co{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$ and decompose the defining relation (\ref{eq:11}),
-\begin{equation}
-  \label{eq:18}
-  \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})}\left(
-    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
-      }}\mathrm{\left( \alpha \right) }}=-s\left( \gamma _{0}\right) e^{-\gamma
-    _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \left\{\gamma_{0}\right\}}s\left( \gamma \right) e^{-\gamma },
-\end{equation}
-then the equality (\ref{eq:17}) leads to the desired recurrent  relation for the anomalous branching coefficients:
-\begin{multline}
-  k_{\xi }^{\left( \mu \right) }=
-  -\frac{1}{s\left( \gamma _{0}\right) }
-  \left(
-    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}
-    \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-    \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-    \right.\\
-    \left. +
-    \sum_{\gamma \in \Gamma _{\frak{a}\subset \frak{g}}} s\left( \gamma +\gamma _{0}\right) k_{\xi+\gamma }^{\left( \mu \right) }
-  \right)
-\label{recurrent-relation}
-\end{multline}
-where the set
-\begin{equation}
-\Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} 
-\label{fan-defined}
-\end{equation}
- was introduced that is called the injection fan.
-
-Now let the set $\Delta_{\bot}^{+}$ be empty.
-There are three different reasons for $\Delta_{\bot}^{+}=0$: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$, ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
-Both the first and the second cases can be treated as corresponding to the trivial orthogonal subalgebra:
-$\mathfrak{a}_{\bot}=0$. In any of these cases instead of the formal characters in the right-hand side of (\ref{eq:13}) we obtain the formal element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$
-In the first two cases (equivalent to $\mathfrak{a}_{\bot}=0$) the projection operator retains its purely geometrical meaning: the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
-It is clear that in any of the three variants the final vector $\pi_{\mathfrak{a}}\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)$ leads to the unit of the formal algebra
-$\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty we get the more simple recurrent relation: 
-\begin{equation}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
-\left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
-\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
-+\gamma }^{\left( \mu \right) }\right)   \label{recurrent relation special}
-\end{equation}
-It coinsides with the one obtained in \cite{ilyin812pbc} (formula (16)).
-
-  In the next section we describe an algorithm for the computation of branching coefficients based on the relation \eqref{recurrent-relation}.
-
-\subsection{Algorithm for the recursive computation of the branching coefficients}
-\label{sec:algorithm}
-
-We use the recurrent relation \eqref{recurrent-relation} to formulate an algorithm for recursive computation of the branching coefficients.
-It is important to mention that the computation of the branching coefficients is performed without the  explicit construction of the module $L^{(\mu)}_{\mathfrak{g}}$ and any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
-
-The algorithm contains the following steps.
-\begin{enumerate}
-\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{a} \subset \mathfrak{g}$.
-\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
-\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\Gamma$ \eqref{fan-defined}.
-\item Calculate the anomalous branching coefficients in the main Weyl
-  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent-relation}).
-\end{enumerate}
-
-If we are interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous weights up to the required grade and use the steps 4-7 of the algorithm for each grade.
-We can also speed up the algorithm by one-time computation of the representatives of the conjugate classes $W_{\bot}\backslash W$.
-
-The next section contains several examples computed using this algorithm.
-
-\section{Examples}
-\label{sec:examples}
-
-\subsection{Finite dimensional Lie algebras}
-\label{sec:finite-dimens-lie}
-
-\subsubsection{Regular embedding of $A_1$ into $B_2$}
-\label{sec:regul-embedd-a_1}
-
-Consider the regular embedding of $A_1$ into $B_2$.
-Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the dashed vectors at the Figure \ref{fig:B2_A1}.
-We denote the corresponding Weyl reflections by $\omega_1, \omega_2$.
-Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+\alpha_2$ and is drawn as grey vector.
-
-Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$, which is drawn as the black vector at the Figure \ref{fig:B2_A1}.
-\begin{figure}[ph]
-  \noindent\centering{
-    \includegraphics[width=90mm]{B2_A1.pdf}
-  }
-  \caption{Regular embedding of $A_1$ into $B_2$}
-  \label{fig:B2_A1}
-\end{figure}
-On the Figure \ref{fig:B2_A1} we have also shown the set of weights $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
-Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
-\begin{figure}[ph]
-  \noindent\centering{
-    \includegraphics[width=90mm]{B2_A1_2.pdf}
-  }
-  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
-  \label{fig:B2_A1_2}
-\end{figure}
-We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
-Then we project these weights and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous weights in fundamental weights basis with corresponding multiplicities:
-\begin{equation}
-  \label{eq:25}
-  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
-\end{equation}
-For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
-\begin{equation}
-  \label{eq:22}
-  (1,2),\; (2,-1)
-\end{equation}
-Here the second component denotes the value of $s(\gamma)$.
-
-Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent-relation}) gives us
-\begin{equation}
-  \label{eq:23}
-  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1
-\end{equation}
-So we have computed the branching coefficients.
-
-\subsubsection{Embedding of $B_2$ into $B_4$}
-\label{sec:someth-high-dimens}
-Consider the the regular embedding of the subalgebra $B_2$ into the algebra $B_4$.
-We calculate the branching coefficients for the fundamental representation of $B_4$.
-The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
-\begin{figure}[ph]
-  \centering
-  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
-  \caption{Dynkin diagrams}
-  \label{fig:dynkin}
-\end{figure}
-
-In the orthogonal basis $e_1,\dots,e_4$ simple roots of $B_4$ are
-\begin{equation}
-  \label{eq:8}
-  (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4)
-\end{equation}
-Positive roots are
-\begin{multline}
-  \label{eq:19}
-  (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\\
-    e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2)
-\end{multline}
-Simple roots of the embedded subalgebra $\mathfrak{a}=B_2$ are
-\begin{equation}
-  \label{eq:26}
-  (e_3-e_4,e_4)
-\end{equation}
-
-The set $\Delta^{+}_{\bot}$ is equal to
-\begin{equation}
-  \label{eq:27}
-  \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
-\end{equation}
-
-We see that this is the set of positive roots of the algebra $\mathfrak{a}_{\bot}=B_2$.
-
-To find the branching coefficients we need to compute the anomalous weights of $B_4$, select weights lying in the main Weyl chamber of $\mathfrak{a}_{\bot}$ and compute the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.
-
-We consider the $B_4$-module with the highest weight $\mu=(0,1,0,2)=2
-e_1 + 2 e_2 + e_3 + e_4$.
-
-The set of the anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W$
-consists of 384 elements. We do not show it here.
-
-We need to select those weights $\omega(\mu+\rho)$  which are projected into the main chamber of the embedded algebra $\mathfrak{a}_{\bot}$.
-It means that scalar product of these weights with all the roots from $\Delta^{+}_{\bot}$ is non-negative.
-
-To compute dimensions of the corresponding
-$\mathfrak{a}_{\bot}$-modules we need to project each selected weight
-onto the root space $\Delta^{+}_{\bot}$ and substract
-$\rho_{\mathfrak{a}_{\bot}}$, then use Weyl dimension formula.
-
-We show the result of this procedure on the Figure \ref{fig:B4B2anom}.
-\begin{figure}[h!tb]
-    \includegraphics[width=150mm]{B4_B2_anom_points.pdf}
-  \caption{Anomalous weights with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
-  \label{fig:B4B2anom}
-\end{figure}
-
-Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
-
-Using the definition (\ref{fan-defined}) we get the following set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
-\begin{figure}[h!tb]
-  \includegraphics[width=130mm]{B4_B2_fan.pdf}
-  \caption{Fan for $B_2\subset B_4$}
-  \label{fig:B4B2Fan}
-\end{figure}
-We use the recurrent relation (\ref{recurrent-relation}) and get
-following branching coefficients:
-\begin{equation}
-  \label{eq:24}
-  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
-  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
-  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
-\end{equation}
-The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
-is equal to 2772. It is easy to see, that right-hand side of the
-equation (\ref{eq:24}) gives the same result.
-
-\subsection{Affine Lie algebras}
-\label{sec:affine-lie-algebras}
-\subsubsection{Embedding of the affine algebra into affine algebra}
-\label{sec:embedd-affine-algebr}
-
-Consider the affine extension of the example \ref{sec:regul-embedd-a_1}.
-Since this embedding is regular, the level of the representations of the subalgebra is equal to the level of the representation of the algebra.
-
-The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.
-
-Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0;1;0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the level of the weight and the fourth is the grade.
-
-The set of the anomalous weights of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.
-
-\begin{figure}[h!tb]
-  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
-  \caption{The anomalous weights of the $(1,0;1;0)$ representation of the algebra $\hat{B_2}$}
-  \label{fig:affine_B2_anom_point}
-\end{figure}
-
-As the next step of our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
-The result of this computation up to the twelfth grade is presented at the Figure
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
-  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
-  \label{fig:AffineB2_A1_anom_proj}
-\end{figure}
-
-Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
-
-Using the definition (\ref{fan-defined}) we get the following $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
-Here we restricted the computation to the twelfth grade.
-\begin{figure}[ph]
-  \centering
-  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
-  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
-  \label{fig:AffineB2A1Fan}
-\end{figure}
-
-Also we should mention that the lowest vector of the fan $\gamma_0$ is equal to zero, since we have excluded all the roots of $\Delta^{+}_{\bot}$ from the defining relation (\ref{fan-defined}).
-
-Using the recurrent relation for the anomalous branching coefficients we get the following result
-\begin{figure}[ph]
-  \centering
-  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
-  \label{fig:AffineB2_A1_branching}
-\end{figure}
-
-Selecting the elements inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
-\begin{multline}
-  \label{eq:28}
-  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
-    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
-    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
-    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
-    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
-    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
-    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
-    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
-    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
-    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
-    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
-    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
-    1180 L_{\hat{A_1}}^{w_0}(-12)
-\end{multline}
-This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
-\begin{eqnarray}
-  \label{eq:29}
-  \begin{array}{cc}
-    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
-     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
-  \end{array}\\
-  \begin{array}{cc}
-    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
-    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
-  \end{array}
-\end{eqnarray}
-Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
-
-\section{Applications to conformal field theory}
-\label{sec:phys-appl}
-
-Branching coefficients for an embedding of affine Lie subalgebra into
-affine Lie algebra can be used to construct modular invariant
-partition functions for Wess-Zumino-Novikov-Witten models of conformal field theory (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
-In these models currents algebras are affine Lie algebras.
-For the construction to be valid the embedding is required to be conformal, which means that the central charge of the subalgebra is equal to the central charge of the algebra:
-\begin{equation}
-  \label{eq:31}
-  c(\mathfrak{a})=c(\mathfrak{g})
-\end{equation}
-
-Let $X^{a_j}_{-n_j}$ and $\tilde{X}^{a'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and of $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
-Let $\pi_{\mathfrak{a}}$ be the projection operator of $\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$.
-In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$ the states can be described as
-\begin{equation}
-  \label{eq:109}
-  X^{a_1}_{-n_1}X^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
-\end{equation}
-And for the sub-algebra $\mathfrak{a}$ the corresponding states are
-\begin{equation}
-  \label{eq:110}
-  \tilde{X}^{a'_1}_{-n_1}\tilde{X}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
-\end{equation}
-The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance, but it is not the case for the energy-momentum tensor.
-So the energy-momentum tensor of the larger theory should consist only of generators of $\tilde{X}$.
-Then $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow c(\mathfrak{g})=c(\mathfrak{a})$.
-This leads to the equation
-\begin{equation}
-  \label{eq:111}
-  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
-\end{equation}
-Here $x_e$ is the embedding index and $g$, $a$ are the dual Coxeter numbers for the  corresponding algebras.
-
-It can be demonstrated that the solutions of the equation (\ref{eq:111}) exist only
-for level $k=1$ \cite{difrancesco1997cft}.
-
-The class of conformal embeddings is not rich, the complete classification is given in the paper \cite{schellekens1986conformal}.
-The requirement (\ref{eq:31}) allows to reduce the problem of finding the branching coefficients for affine Lie algebras to the computation of branching coefficients for finite-dimensional Lie algebras.
-
-If we have modular-invariant partition function for the fields described by a representation of the algebra $\mathfrak{g}$ this modular invariance is preserved by the projection on the subalgebra $\mathfrak{a}$, but we need also the preservation of the conformal invariance.
-So we should select only those highest-weight modules of the subalgebra $\mathfrak{a}$ for which the relation (\ref{eq:111}) holds.
-
-In the decomposition (\ref{eq:3}) let the highest weight $\nu$ of the subalgebra module belong to the grade $n$ of the projected  module $\pi_{\mathfrak{a}}\cdot L^{(\mu)}_{\mathfrak{g}}$.
-Then the relation (\ref{eq:111}) implies the following requirement on the conformal dimensions of the corresponding fields
-\begin{equation}
-  \label{eq:32}
-   \Delta_{\pi_{\mathfrak{a}}\mu}+n=\Delta_{\nu}
-\end{equation}
-It leads to a restriction imposed on the classical parts of the corresponding weights:
-\begin{equation}
-  \label{eq:33}
-  \frac{(\co{\mu},\co{\mu}+2\rho)}{2(1+g)}+n=\frac{(\co{\nu},\co{\nu}+2\rho_{\mathfrak{a}})}{2(x_e+a)}
-\end{equation}
-The finite reducibility theorem states that for conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
-
-Then after we have found all such weights $\nu$ and the corresponding branching coefficients $b^{(\mu)}_{\nu}$ we can replace the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function
-\begin{equation}
-  \label{eq:34}
-   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
-\end{equation}
-by the decompositions   $\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}$ containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules.
-Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
-\begin{equation}
-  \label{eq:36}
-   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
-\end{equation}
-Recently the problem of the conformal embeddings was considered in the paper \cite{coquereaux2008conformal}.
-
-It is important to note that the orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
-It can be seen from the following consideration.
-In the case of the conformal embedding energy-momentum tensors are to be equal
-\begin{equation}
-  \label{eq:46}
-  T_{\mathfrak{a}}(z)=T_{\mathfrak{g}}(z)
-\end{equation}
-The energy-momentum tensor can be expanded into the modes $L_n$
-\begin{equation}
-\label{eq:47}
-  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
-\end{equation}
-The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
-\begin{equation}
-\label{eq:48}
-  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
-\end{equation}
-The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$.
-But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
-
-\subsection{Examples}
-\label{sec:example}
-
-\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
-\label{sec:spec-embedd-hata_1s}
-Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $su(2)\subset su(3)$ with the embedding index $x_e=4$.
-The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.
-
-There exist three level one dominant weights in the weight space of $\hat{A}_2$.
-It is easy to see that the set $\Delta_{\bot}$ and the algebra $\mathfrak{a}_{\bot}$ are empty.
-
-Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details.
-Here the first two components are the Dynkin indices (coordinates in the fundamental weights basis) of the finite part of the weight.
-
-The set of the anomalous weights of this representation up to the sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}.
-We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.
-
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=180mm]{AffineA2_A1_anom.pdf}
-  \caption{The anomalous weights of the $(0,0;1;0)$ representation of the algebra $\hat{A_2}$}
-  \label{fig:affine_A2_anom_point}
-\end{figure}
-
-According to our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$.
-The result of these calculations up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
-  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
-  \label{fig:AffineA2_A1_anom_proj}
-\end{figure}
-
-Then we construct ``the fan'' and use the recurrent relations to compute the anomalous branching coefficients.
-
-Using the definition (\ref{fan-defined}) we get the following set of
-the weights $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:AffineA2A1Fan}.
-Here we restricted the calculations to the first eight grades.
-\begin{figure}[p]
-  \centering
-  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
-  \caption{Fan for $\hat{A_1}\subset \hat{A_2}$}
-  \label{fig:AffineA2A1Fan}
-\end{figure}
-
-Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
-\begin{figure}[p]
-  \centering
-  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
-  \label{fig:AffineA2_A1_branching}
-\end{figure}
-
-We see that inside the main Weyl chamber of $\hat{A}_1$ there are only two non-zero anomalous weights.
-(Show the Weyl chambers on the Figure.) These are the branching coefficients.
-So the finite reducibility theorem holds and we get the decomposition
-\begin{equation}
-  \label{eq:43}
-  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)]}.
-\end{equation}
-
-For the other level one dominant weights of $\hat{A}_2$ we get the trivial
-branching 
-\begin{eqnarray}
-  \label{eq:44}
-   L^{(1,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)},\\
-   L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
-\end{eqnarray}
-
-Using this result the modular-invariant partition function is easily found,
-\begin{equation}
-  \label{eq:45}
-  Z=\left|\chi_{(4;4;0)}+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
-\end{equation}
-
-\subsubsection{Embedding of semisimple subalgebras}
-\label{sec:embedd-semis-subalg}
-
-Embedding of affine extensions of semisimple subalgebras to affine lie algebras allows additional construction of modular invariants \cite{difrancesco1997cft}, \cite{walton1989conformal}.
-Consider the conformal embedding constructed as the affine extension  $\mathfrak{a}_{1}\oplus\mathfrak{a}_{2}\subset \mathfrak{g}$ of the embedding of semisimple subalgebra $\ao_1\oplus\ao_2$ into simple Lie algebra $\go$.
-
-Substituting the branching rules into \eqref{eq:34} we get non-diagonal mass matrix
-\begin{equation}
-  \label{eq:2}
-  M_{\lambda\xi,\mu\eta}
-\end{equation}
-where $\lambda,\mu$ are the highest weights of the representations of $\mathfrak{a}_1$ and $\xi,\eta$ of $\mathfrak{a}_2$.
-A new $\mathfrak{a}_1$-invariant mass matrix can be found by the contraction of $M_{\lambda\xi,\mu\eta}$ with some known $\mathfrak{a}_2$-invariant mass matrix $M^{(2)}_{\xi\eta}$:
-\begin{equation}
-  \label{eq:35}
-  M^{(1)}_{\lambda\mu}=\sum_{\xi,\eta\in P_{\mathfrak{a}}^{+}}M_{\lambda\xi,\mu\eta}M^{(2)}_{\xi\eta}
-\end{equation}
-
-Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\widehat{su(2)}\oplus \widehat{su(2)}$ and $\mathfrak{g}= \widehat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$.
-Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}.
-We start with 4-dimensional representation of $su(2)\oplus su(2)$ with the highest weight $(1,1)$.
-The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
-
-\begin{figure}[t]
-  \begin{multicols}{2}
-    \hfill
-    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
-    \hfill
-    \caption{Representation for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
-    \label{fig:A_1+A_1_to_A3}
-    \hfill
-    \includegraphics[width=50mm]{A1+A1-A3.pdf}
-    \hfill
-    \caption{Embedded roots for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
-    \label{fig:A1+A1-A3}
-  \end{multicols}
-\end{figure}
-
-Then for the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method}, so $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
-The embedded roots $\alpha_1,\alpha_2$ of $su(2)\oplus su(2)$ in terms of roots $\tilde{\alpha}_i$ of $su(4)$ are
-\begin{equation}
-  \label{eq:37}
-  \begin{array}{l}
-     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
-     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
-  \end{array}
-\end{equation}
-They are depicted at the Figure \ref{fig:A1+A1-A3}.
-
-This embedding is characterised by the embedding indexes $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
-
-We are interested in the reduction of the fundamental representations of $\widehat{su(4)}$.
-Four dominant weights of level one have the following coordinates in the orthogonal basis: 
-\begin{equation}
-  \begin{array}{lll}
-     \omega_0 & = & (0,0,0,0;1;0)\\
-     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
-     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
-     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
-  \end{array}
-\end{equation}
-
-These representation could be easily reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras, but we use our general method and discuss its features.
-
-For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
-\begin{equation}
-  \label{eq:38}
-  \begin{array}{lll}
-    \Delta^{+} &=&\left\{\co{\Delta}^{+};\; \co{\Delta}-n\delta;\;     -n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right. \\
-    & & \quad\left.\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\}\right\}\\
-    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm \alpha_2-n\delta;\; -n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
-  \end{array}
-\end{equation}
-
-The set $\Delta^{+}_{\bot}$ is empty. 
-The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}.
-Coordinates of fan element's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$.
-Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
-\begin{figure}[h!tb]
-  \includegraphics[width=150mm]{A1+A1-A3_fan.pdf}
-  \caption{Fan for the special embedding $\widehat{su(2)}\oplus\widehat{su(2)}\subset \widehat{su(4)}$}
-  \label{fig:A1+A1-A3_fan}
-\end{figure}
-
-We limit our computation by the fifth grade.
-
-\begin{figure}[h!tb]
-  \includegraphics[width=150mm]{A1+A1-A3_anom.pdf}
-  \caption{Projected anomalous weights for $L^{\omega_1}_{A_3}$}
-  \label{fig:A1+A1-A3_anom}
-\end{figure}
-
-The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,0,1;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
-Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$.
-Weight $g$ are shown by cross if the corresponding value $\epsilon(\omega)=1$ and by diamond otherwise.
-
-We omit similar pictures for $\omega_0, \omega_1,\omega_3$ and include only the branching coefficients for these modules to save the space.
-
-The anomalous branching coefficients for the module $L^{(\omega_1)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
-\begin{figure}[h!tb]
-  \includegraphics[width=180mm]{A1+A1-A3_branching.pdf}
-  \caption{Anomalous branching coefficients for $L^{(0,0,1;1;0)}_{A_3}$}
-  \label{fig:A1+A1-A3_branching}
-\end{figure}
-
- We get the following branching rules
- \begin{equation}
-   \label{eq:39}
-   \begin{array}{ll}
-     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
-     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
-     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
-     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
-   \end{array}
- \end{equation}
-
-Now we can obtain modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
-\begin{multline}
-  \label{eq:40}
-  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
-  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
-\end{multline}
-
-\section{Conclusion}
-\label{sec:conclusion}
-We have proved that the injection fan technique can be used to deal with the nonmaximal subalgebras.
-It was demonstrated that in such cases in the set of positive roots $\Delta_{\mathfrak{g}}^{+}$ it is necessary to  separate an additional subset $\Delta^{+}_{\bot}$.
-The injection fan is formed by the weights $\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+} \setminus \Delta^{+}_{\bot}$ and the additional role of the subset $\Delta^{+}_{\bot}$ is to modify the anomalous weights of the initial module.
-This modification reduces to a simple procedure: the anomalous weights are to be substituted by the dimensions of the corresponding ${\mathfrak{a}}_{\bot}$-modules.
-
-We have demonstrated the effectiveness of the proposed generalizations of the injection fan algorithm and discussed its possible application to some physical problems.
-In particular we considered the construction modular-invariant partition functions in the conformal field theory in the framework of conformal embedding method.
-This  method is widely used in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
-
-\section{Acknowledgements}
-The work was supported in
-part by RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575.
 

### 2010-05-24 AffineLieAlgebras/InformalNotes/talk.tex
Conformal and WZW sections are completed, bulk of modular section is added.

--- 2009-08-31 AffineLieAlgebras/InformalNotes/ModularInvariantsAndBranching.tex
@@
 \documentclass[a4paper,12pt]{article}
+\usepackage{ucs}
 \usepackage[unicode,verbose]{hyperref}
-\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
-\usepackage{ucs}
+\usepackage{amsmath,amssymb,amsthm}
+\usepackage{pb-diagram}
+\usepackage{multicol}
 \usepackage[utf8x]{inputenc}
@@
 \usepackage{cmap}
-\usepackage{graphicx}
+\usepackage{color}
+\usepackage[pdftex]{graphicx}
 \pagestyle{plain}
+
+%\usepackage{verbatim} 
+\newenvironment{comment}
+{\par\noindent{\bf TODO}\\}
+{\\\hfill$\scriptstyle\blacksquare$\par}
+
+\newtheorem{statement}{Statement}
 \theoremstyle{definition} \newtheorem{Def}{Definition}
+\newcommand{\go}{\overset{\circ }{\frak{g}}}
+\newcommand{\ao}{\overset{\circ }{\frak{a}}}
+\newcommand{\co}[1]{\overset{\circ }{#1}}
+
 \begin{document}
-\tableofcontents
+\thispagestyle{empty}
 
-\section{Модулярная инвариантность}
+\begin{center}
+{\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
+\end{center}
+\vskip 1 cm
+\begin{flushright}
+{\large \bf SPbU-IP-09-08}
+\end{flushright}
+\hfill {}
+\vskip 1 cm
+\begin{center}
+{\Huge \bf Recursive algorithms, branching coefficients \\ for affine algebras and applications\\[0.5cm]
+}
+\end{center}
+\vskip 1.0 cm
+\begin{center}
+{\Large \bf
+Vladimir Lyakhovsky\\[2mm]
+Anton Nazarov}
+\end{center}
+\vfill
+\begin{center}
+{\large Department of Theoretical Physics\\
+}
+\end{center}
+\vfill
+\begin{center}
+SAINT-PETERSBURG \\
+2009
+\end{center}
+
+\newpage
+
+\pagenumbering{arabic}
+\title{\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}}
+\author{Vladimir Lyakhovsky \thanks{ Supported by
+ RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
+Theoretical Department, SPb State University,\\
+198904, Sankt-Petersburg, Russia \\
+e-mail:lyakh1507@nm.ru \\
+[5mm] Anton Nazarov \thanks{ Supported by
+the National Project RNP.2.1.1./1575 }\\
+Theoretical Department, SPb State University,\\
+198904, Sankt-Petersburg, Russia \\
+e-mail:antonnaz@gmail.com
+}
+\maketitle
+
+\begin{abstract}
+\end{abstract}
+
+\section{Постановка задачи}
+\label{sec:task}
+
+Здравствуйте!
+Сегодня я хочу рассказать о работе ``Рекуррентные алгоритмы, коэффициенты ветвления аффинных алгебр
+Ли и приложения''. В этой работе мы решали следующую задачу.
+
+Даны две аффинные алгебры Ли $\mathfrak{a}\subset \mathfrak{g}$. Неприводимое представление
+$L^{(\mu)}_{\mathfrak{g}}$ алгебры $\mathfrak{g}$ со старшим весом $\mu$ может быть разложено на
+представления подалгебры $\mathfrak{a}$. Наша задача --- придумать практический алгоритм вычисления
+коэффициентов этого разложения.
+
+Я начну с физической мотивации этой задачи в двумерной конформной теории поля, напомню некоторые
+факты из теории представлений аффинных алгебр Ли, кратко опишу предложенное нами решение проблемы и
+расскажу про физические примеры в нашей статье.
+
+\section{Физическая мотивация}
+\label{sec:physics}
+
+\subsection{Напоминание про двумерную конформную теорию поля}
+\label{sec:CFT}
+
+В теории струн двумерная конформная теория поля описывает динамику на мировой поверхности, а в
+теории критических явлений --- фазовые переходы в двумерных системах.
+
+Двумерная конформная теория поля --- это теория поля, определенная на двумерном пространстве-времени
+и обладающая инвариантностью относительно следующих преобразований:
+\begin{align}
+  \label{eq:1}
+  & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\
+  &P_\mu \equiv-i\partial_\mu \,, \\
+  &D \equiv-ix_\mu\partial^\mu \,, \\
+  &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,,
+\end{align}
+
+На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
+В этом случае конформная группа --- это набор всех аналитических функций $w(z)$ на плоскости.
+
+В двумерной конформной теории поля тензор энергии-импульса бесследовый.
+
+Для классической теории алгебра конформных преобразований --- это алгебра Витта, которая порождается
+генераторами $\{L_n, n\in \mathbb{Z}\}$ --- модами разложения оператора энергии-импульса $T$, с
+коммутационными соотношениями
+\begin{equation}
+  \label{eq:2}
+  [L_m,L_n]=(m-n)L_{m+n}
+\end{equation}
+При квантовании возникает конформная аномалия, что соответствует центральному расширению алгебры (то
+есть появлению центрального заряда $c$). В коммутационные соотношения надо добавить член
+$\frac{c}{12}(m^3-m)\delta_{m+n,0}$. В результате получаем алгебру Вирасоро.
+
+Поля теории $\phi(z,\bar z)$ должны преобразовываться определенным образом при конформных преобразованиях.
+Оказывается, что все поля группируются в конформные семейства, в которых есть одно примарное поле
+\begin{equation}
+  \label{eq:3}
+  \begin{split}
+    \phi_{\Delta,\bar \Delta}(z,\bar z)\underset{
+      \genfrac{}{}{0pt}{}{z\to w(z)}
+        {\bar z \to \bar w(\bar z)}
+    }
+    {\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\left(\frac{d\bar w}{d\bar
+        z}\right)^{\bar\Delta}\phi_{\Delta,\bar \Delta}(w(z),\bar w(\bar z))\\
+    L_n \phi=0,\quad n>0\\
+    L_0 \phi=\Delta \phi\\
+  \end{split}
+\end{equation}
+$\Delta, \bar \Delta$ называются конформными размерностями поля.
+Все остальные поля называются вторичными и получаются из примарного действием операторов $L_{-n}$:
+\begin{equation}
+  \label{eq:67}
+  L_{-n_1}L_{-n_2}\dots \phi_{\Delta}
+\end{equation}
+Все поля в теории оказываются суммами мультиплетов алгебры Вирасоро.
+
+При некоторых дополнительных предположениях двумерную конформную теорию можно построить и решить
+полностью, если определен набор примарных полей и аномальных размерностей.
+
+Существуют различные подходы к аксиоматизации двумерной конформной теории поля. В общем случае нам
+не нужно знать действие, если мы полный знаем набор примарных полей и операторные разложения их
+произведений.
+
+В том случае, если в теории конечное число примарных полей, такая теория называется минимальной.
+Кроме того, теории классифицируются по значениям центрального заряда $c$. Теории с рациональным
+центральным зарядом называются рациональными. Оказывается, что все такие теории могут быть получены
+факторизацией так называемых моделей Весса-Зумино-Новикова-Виттена.
+
+\subsection{WZW-модели}
+\label{sec:wzw}
+
+WZW-модели обладают дополнительной симметрией. Алгебра токов в них --- это алгебра Каца-Муди
+(аффинная алгебра Ли $\mathfrak{g}$), а полная киральная алгебра --- полупрямое произведение
+$Vir\ltimes \mathfrak{g}$.
+
+Сейчас я поясню, что все это значит и как строятся такие модели.
+
+Модели Весса-Зумино-Виттена можно строить начиная со следующего действия:
+\begin{equation}
+\label{eq:4}
+  S=S_0+k\Gamma
+\end{equation}
+где $k$ - целое.
+Здесь $S_0$ --- действие нелинейной $\sigma$-модели.
+\begin{equation}
+  \label{eq:5}
+  S_0=\frac{1}{4a^2}\int_{\partial B} d^2x\; Tr (\partial^{\mu}g^{-1}\partial_{\mu}g),
+\end{equation}
+где $a^2>0$ - положительный параметр, $g(x)\in G$ - поле со значениями в группе $G$, которую мы
+будем считать полупростой.
+
+В нелинейной $\sigma$-модели конформная инвариантность теряется на квантовом уровне.
+Голоморфный и антиголоморфный токи не сохраняются по отдельности.
+Поэтому мы добавляем член Весса-Зумино $\Gamma$ к действию
+\begin{equation}
+  \label{eq:73}
+\Gamma= - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr\left(
+    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+Он определен на трехмерном многообразии $B$, ограниченном исходным двумерным пространством.
+Через $\tilde{g}$ мы обозначили продолжение поля $g$ на $B$. Такое продолжение не единственно. В
+компактифицированном трехмерном пространстве компактное двумерное многообразие разделяет два
+трехмерных многообразия. Разность значений члена Весса-Зумино $\Delta\Gamma$ на этих многообразиях
+дается правой частью уравнения (\ref{eq:73}) с интегралом, продолженным на все компактное трехмерное
+пространство. Так как оно топологически эквивалентно три-сфере, получаем
+\begin{equation}
+  \label{eq:75} \Delta\Gamma= - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left( \tilde
+g^{-1}\frac{\partial \tilde g}{\partial y^i} \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+\tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+$\Delta\Gamma$ определен по модулю $2\pi i$, поэтому Евклидов функциональный интеграл
+с весом $exp(-\Gamma)$ хорошо определен. Значит константа связи, умножаемая на этот член, должна
+быть целочисленной.
+
+Уравнение движения для полного действия (\ref{eq:4}):
+\begin{equation}
+  \label{eq:77}
+  \partial^{\mu}(g^{-1}\partial_{\mu}g)+\frac{a^2 ik}{4\pi}\epsilon_{\mu\nu}\partial^{\mu}(g^{-1}\partial^{\nu}g)=0
+\end{equation}
+В комплексных координатах оно записывается в виде
+\begin{equation}
+  \label{eq:78}
+  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
+\end{equation}
+Видно, что при $a^2=\frac{4\pi}{k}$ у нас имеются законы сохранения
+\begin{equation}
+  \label{eq:79}
+  \partial_z(g^{-1}\partial{\bar z}g)=0
+\end{equation}
+Для токов
+\begin{equation}
+  \label{eq:72}
+  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
+\end{equation}
+
+\begin{equation}
+  \label{eq:100}
+  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
+\end{equation}
+То есть голоморфная и антиголоморфная части отщепляются, что является указанием на наличие
+конформной инвариантности.
+
+Решение классического уравнения движения имеет вид
+\begin{equation}
+  \label{eq:80}
+  g(z,\bar z)=f(z)\bar f(\bar z)
+\end{equation}
+при произвольных $f(z)$ и $\bar f (\bar z)$.
+
+Сохранение по отдельности токов $J_z,\; J_{\bar z}$ приводит к инвариантности действия при преобразованиях
+\begin{equation}
+  \label{eq:81}
+   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)
+\end{equation}
+где $\Omega,\;\bar \Omega \in G$. То есть мы получили локальную $G(z)\times G(\bar z)$-инвариантность.
+
+Для перехода к квантовому случаю мы переопределяем токи
+\begin{equation}
+  \label{eq:82}
+  J(z)\equiv -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
+\end{equation}
+Тогда вариация действия при инфинитезимальных преобразованиях $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ дается выражением
+\begin{equation}
+  \label{eq:83}
+  \delta_{\omega,\bar\omega}S=\frac{i}{4\pi}\oint dz Tr (\omega(z)J(z))-\frac{i}{4\pi}\oint d\bar z Tr(\bar\omega(\bar z)\bar J(\bar z))
+\end{equation}
+Раскладывая токи
+\begin{equation}
+  \label{eq:85}
+  \begin{aligned}
+    J=\sum J^a t^a,\bar J=\sum \bar J^a t^a \\
+    \omega=\sum \omega^a t^a\\
+  \end{aligned}
+\end{equation}
+получаем
+\begin{equation}
+  \label{eq:86}
+  \delta_{\omega,\bar \omega}S=-\frac{1}{2\pi i}\oint dz \sum\omega^a J^a+\frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \bar J^a
+\end{equation}
+Мы также получили тождества Уорда $\delta\left< X\right>=\left<(\delta S)X\right>$
+\begin{equation}
+  \label{eq:87}
+  \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
+  \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
+\end{equation}
+Для токов имеем
+\begin{equation}
+  \label{eq:88}
+  \delta_{\omega}J=[\omega,J]-k\partial_z\omega,\quad \delta_{\omega}J^a=\sum i f_{abc}\omega^b J^c-k\partial_z\omega^a
+\end{equation}
+Операторное разложение для токов имеет вид
+\begin{equation}
+  \label{eq:89}
+  J^a(z) J^b(w) \sim \frac{k\delta_{ab}}{(z-w)^2}+\sum i f_{abc}\frac{J^c(w)}{(z-w)}
+\end{equation}
+Раскладывая токи в ряд, получаем
+\begin{equation}
+  \label{eq:90}
+  \begin{aligned}
+    J^a(z)=\sum_{n\in \mathbb Z}z^{n-1}J^a_n\\
+    \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}
+  \end{aligned}
+\end{equation}
+Теперь мы видим, что компоненты токов образуют аффинную алгебру Ли $\hat g$.
+
+Тензор энергии-импульса вводится при помощи конструкции Сугавары как сумма нормально упорядоченных компонент токов
+\begin{equation}
+  \label{eq:102}
+  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
+\end{equation}
+Здесь $h^v$ - дуальное число Кокстера.
+
+Тензор энергии-импульса можно разложить на моды $L_n$
+\begin{equation}
+  \label{eq:91}
+  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
+\end{equation}
+Тогда коммутационные соотношения для мод $L_n$ имеют вид
+\begin{equation}
+  \label{eq:92}
+  \begin{aligned}
+    \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
+    \left[L_n,J^a_m\right]=-mJ^a_{n+m}
+  \end{aligned}
+\end{equation}
+
+Таким образом, конструкция Сугавары --- это способ вложения алгебры Вирасоро в универсальную обертывающую аффинной алгебры Ли $\hat{g}$
+
+Полная киральная алгебра модели Весса-Зумино-Виттена равна полупрямому произведению $Vir\ltimes \hat g$
+
+Примарными оказываются поля, которые преобразуются ковариантно под действием $G(z)\times G(\bar z)$,
+как $g(z,\bar z)$. В терминах операторного разложения это свойство переформулируется следующим
+образом:
+\begin{equation}
+  \label{eq:84}
+  \begin{aligned}
+    J^a(z)g(w,\bar w)\sim \frac{-t^a g(w,\bar w)}{(z-w)}\\
+    \bar J^a(z)g(w,\bar w)\sim \frac{ g(w,\bar w)t^a}{(z-w)}
+  \end{aligned}
+\end{equation}
+Любое поле $\phi_{\lambda,\mu}$, преобразующееся ковариантно по отношению к некоторому
+представлению, заданному весом $\lambda$ в голоморфном секторе и весом $\mu$ в антиголоморфном,
+является примарным полем WZW-модели.
+
+В модах это свойство записывается в виде
+\begin{equation}
+  \label{eq:93}
+  \begin{aligned}
+    & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
+    & (J^a_n\phi_{\lambda})=0\quad \mbox{для}\; n>0\\
+  \end{aligned}
+\end{equation}
+Мы можем сопоставить состояние $\left|\phi_{\lambda}\right>$ полю $\phi_{\lambda}$
+  \begin{equation}
+    \label{eq:94}
+    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
+  \end{equation}
+Тогда условия (\ref{eq:93}) для примарных полей дают
+\begin{equation}
+  \label{eq:95}
+  \begin{aligned}
+    & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
+    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{для}\; n>0 \\
+  \end{aligned}
+\end{equation}
+Легко видеть, что действие генераторов алгебры Вирасоро имеет вид
+\begin{equation}
+  \label{eq:96}
+  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
+\end{equation}
+Здесь использовано явное выражение для собственных значений квадратичного оператора Казимира.
+
+Примарные поля живут в интегрируемых конечномерных представлениях, так как бесконечномерные и
+неинтегрируемые поля отщепляются в корреляционных функциях.
+
+Все вторичные состояния имеют вид
+\begin{equation}
+  \label{eq:97}
+  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
+\end{equation}
+
+\subsection{Конформные вложения и модулярно-инвариантные статсуммы}
 \label{sec:modular-invariance}
 
-Если мы изучаем конформную теорию поля на плоскости или на сфере, то мы можем рассматривать голоморфный и антиголоморфный сектора независимо.
-Если говорить о WZW-моделях, то примарные поля принадлежат тензорному произведению неприводимых представлений аффинной алгебры.
+Если мы изучаем конформную теорию поля на плоскости или на сфере, то мы можем рассматривать
+голоморфный и антиголоморфный сектора независимо. Если говорить о WZW-моделях, то примарные поля
+принадлежат тензорному произведению неприводимых представлений аффинной алгебры.
 
-Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать взаимодействия струн.
-Считается, что для этого необходимо (и, возможно, достаточно \cite{gaberdiel2000icf}) чтобы теория была определена на торе.
+Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть
+определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать
+взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно
+\cite{gaberdiel2000icf}) чтобы теория была определена на торе.
 
-В теории критического поведения конформная инвариантность имеет место только в критической точке, где голоморфный и антиголоморфный сектора расцеплены.
-Но вблизи критической точки эти сектора должны быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве параметров, то эта связь должна сохраняться и в критической точке.
-Физический спектр теории должен плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической точке.
-Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния \cite{difrancesco1997cft}.
-Здесь естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории на торе.
+В теории критического поведения конформная инвариантность имеет место только в критической точке,
+где голоморфный и антиголоморфный сектора расцеплены. Но вблизи критической точки эти сектора должны
+быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве
+параметров, то эта связь должна сохраняться и в критической точке. Физический спектр теории должен
+плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного
+сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической
+точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния
+\cite{difrancesco1997cft}. Здесь естественно рассматривать периодические граничные условия, которые
+эквивалентны рассмотрению теории на торе.
 
@@
 
-\bibliography{CFTNotes}{}
-\bibliographystyle{utphys}
+\section{Рекуррентные соотношения для коэффициентов ветвления}
+\label{sec:branching}
+
+\subsection{Примеры}
+\label{sec:examples}
+
+\section{Заключение. Обсуждение перспектив.}
+\label{sec:conlusion}
 

### 2010-05-26 AffineLieAlgebras/InformalNotes/article.tex
Some work on physics section

--- 2010-05-12 AffineLieAlgebras/InformalNotes/article.tex
@@
 We denote the corresponding Weyl reflections by $\omega_1, \omega_2$.
-Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+\alpha_2$ and is drawn as grey vector.
+Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+2\alpha_2$ and is drawn as grey vector.
 
@@
 \end{figure}
-On the Figure \ref{fig:B2_A1} we have also shown the set of weights $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
+On the Figure \ref{fig:B2_A1} we have also shown the set of weights $\omega(\mu+\rho)-\rho,\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
 Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
@@
 where $\lambda,\mu$ are the highest weights of the representations of $\mathfrak{a}_1$ and $\xi,\eta$ of $\mathfrak{a}_2$.
-A new $\mathfrak{a}_1$-invariant mass matrix can be found by the contraction of $M_{\lambda\xi,\mu\eta}$ with some known $\mathfrak{a}_2$-invariant mass matrix $M^{(2)}_{\xi\eta}$:
-\begin{equation}
-  \label{eq:35}
-  M^{(1)}_{\lambda\mu}=\sum_{\xi,\eta\in P_{\mathfrak{a}}^{+}}M_{\lambda\xi,\mu\eta}M^{(2)}_{\xi\eta}
-\end{equation}
 

### 2010-05-26 AffineLieAlgebras/InformalNotes/talk.tex
Talk translation is completed.

@@
 \end{align}
+=====
+Подробнее обсудить бесконечномерность.
+=====
 
@@
 определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать
-взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно
-\cite{gaberdiel2000icf}) чтобы теория была определена на торе.
+взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно) чтобы теория была определена на торе.
 
@@
 сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической
-точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния
-\cite{difrancesco1997cft}. Здесь естественно рассматривать периодические граничные условия, которые
-эквивалентны рассмотрению теории на торе.
+точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния. Здесь
+естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории
+на торе.
 
-Если мы наложили периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$, то статсумма записывается в виде
+Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
+Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
+выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
+вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
+обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
+параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
+Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
+параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
+статсумма дается следом оператора сдвига в степени $m$:
 \begin{equation}
-  \label{eq:1}
-  Z(\tau)=Tr \exp 2\pi i (\tau (L_0-c/24)-\bar{\tau} (\bar{L}_0-c/24))
+  \label{eq:6}
+  Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
+\end{equation}
+Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
+конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
+$H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
+$L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
+$P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
+можно записать в виде
+\begin{equation}
+  \label{eq:7}
+  \begin{split}
+      Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
+      L_0)\}\\
+      =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
+  \end{split}
 \end{equation}
@@
 \end{equation}
-Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
+Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
 
-Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование модулярной инвариантности статсуммы.
+Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
+эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
 
-Комплексная структура такого тора конформно эквивалентна тору, для которого соотношения эквивалентности записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости $\mathbb{C}$.
+Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
+модулярной инвариантности статсуммы.
 
-Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают конформно-эквивалентные торы.
-Отображения $T$ и $S$ порождают группу  $SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
+Комплексная структура такого тора конформно эквивалентна тору, для которого соотношения
+эквивалентности записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
+$\mathbb{C}$.
+
+Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
+конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
+$SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
 \begin{equation}
-  \label{eq:99}
-  A=
-  \begin{pmatrix}
-    a & b\\
-    c & d 
-  \end{pmatrix}
-  \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+  \label{eq:99} A=
+  \begin{pmatrix} a & b\\ c & d
+  \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
 \end{equation}
@@
 \begin{equation}
-  \label{eq:100}
-  \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+  \label{eq:100} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
 \end{equation}
- $\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ --- модулярной группой.
+$\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
+модулярной группой.
 
@@
   \label{eq:3}
-  \begin{split}
-    \Phi_{a}(z)\underset{z\to w(z)}{\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta_a}\Phi_{a}(w(z))\\
-    L_n \Phi_a=0,\quad n>0\\
-    L_0 \Phi_a=\Delta_a \Phi_a\\
+  \begin{split} \Phi_{a}(z)\underset{z\to w(z)}{\longrightarrow}
+\left(\frac{dw}{dz}\right)^{\Delta_a}\Phi_{a}(w(z))\\ L_n \Phi_a=0,\quad n>0\\ L_0 \Phi_a=\Delta_a
+\Phi_a\\
   \end{split}
@@
 
-Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные произведения неприводимого представления  $\mathcal{H}_j$ киральной алгебры и неприводимого представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры.
-Тогда статсуммы на торе (\ref{eq:2}) может быть переписана в виде
+Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
+произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
+представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсуммы на торе
+(\ref{eq:2}) может быть переписана в виде
 \begin{equation}
   \label{eq:4}
-  \sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
+    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
 \end{equation}
-где $\chi_j$ --- характер пердставления $\mathcal{H}_j$,
+где $\chi_j$ --- характер представления $\mathcal{H}_j$,
 \begin{equation}
-  \label{eq:5}
-  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i \tau}
+  \label{eq:5} \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i
+\tau}
 \end{equation}
@@
 \begin{equation}
-  \label{eq:107}
-  \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad \chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
+  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
+\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
 \end{equation}
-где $S$ и $T$ --- постоянные матрицы. Это верно для большого класса конформных теорий поля \cite{gaberdiel2000icf}.
+где $S$ и $T$ --- постоянные матрицы. Это верно для большого класса конформных теорий
+поля.
 
-Для WZW-моделей представления определяются старшими весами $\hat \lambda, \hat \xi$. Тогда
+Для WZW-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$. Тогда
 \begin{equation}
-  \label{eq:6}
-  \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi} L_{\hat \lambda}\otimes L_{\hat \xi}
+  \label{eq:6} \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi}
+L_{\hat \lambda}\otimes L_{\hat \xi}
 \end{equation}
-Статсумма даётся выражением
+
+Коэффициенты ветвления для вложения аффинной подалгебры Ли в аффинную алгебру можно использовать для
+построения модулярно-инвариантной статсуммы в соответствующей WZW-модели. Когда рассматривается
+теория на торе,  набор физически допустимых полей ограничен требованиями модулярной инвариантности.
+
+Простейшим модулярный инвариант можно записать следующим образом:
 \begin{equation}
-  \label{eq:7}
-  Z(\tau)=\sum_{\hat \lambda,\hat \xi\in P^{(k)}_{+}} \chi_{\hat \lambda}(\tau)M_{\hat \lambda\hat\xi}\bar \chi_{\hat \xi}(\bar \tau)
+  \label{eq:34}
+   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
 \end{equation}
-Элементы так называемой матрицы масс $M_{\hat \lambda\hat\xi}$ можно рассматривать как кратности примарных полей с весами $\hat\lambda,\hat \xi$.
-У них есть следующие свойства: $M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, модулярная инвариантность
+Здесь суммирование ведется по всем конформным семействам (то есть по всем представлениям алгебры
+$\mathfrak{g}$). Представления алгебры можно рассматривать как сумму представлений подалгебры.
+
+Если мы рассмотрим редукцию характеров
 \begin{equation}
   \label{eq:8}
-  \begin{aligned}
-    T^{\dagger}MT=S^{\dagger}MS=M,\\
-    [M,S]=[M,T]=0,
-  \end{aligned}
+   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
 \end{equation}
-и $M_{00}=1$ для единственности вакуума.
+и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится. 
+Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
+ней конформная инвариантность.
 
-Простейший случай диагональной матрицы $M$ соответствует равным голоморфным и антиголоморфным конформным размерностям.
-Есть несколько способов построения недиагональных модулярных инвариантов из диагональных \cite{difrancesco1997cft}:
-\begin{itemize}
-\item Метод внешних автоморфизмов
-\item Конформное вложение в большую теорию
-\item Перестановки Галуа
-\end{itemize}
-Мы будем обсуждать только конформные вложения.
-
-\section{Конформные вложения}
-\label{sec:conformal-embeddings}
-
-Состояния в теории соответствующей алгебре $g$ (с киральной алгеброй $Vir\ltimes \hat g$) имеют вид
+Для этого требуется, чтобы вложение подалгебры было ``конформным'', то есть центральные заряды
+теорий должны совпадать.
 \begin{equation}
-  \label{eq:9}
-  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq\dots>0
-\end{equation}
-А для подалгебры $\mathfrak{p}\subset\mathfrak{g}$
-\begin{equation}
-  \label{eq:10}
-  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\mathcal{P}\lambda\right>
-\end{equation}
-Здесь $\tilde{J}^{a'_j}_{-n_j}$ --- генераторы $\mathfrak{p}$, а $\mathcal{P}$ --- проекция $\mathfrak{g}$ на $\mathfrak{p}$.
-Очевидно, что $\mathfrak{g}$-инвариантность вакуума ведёт к его $\mathfrak{p}$-инвариантности, но нет оснований считать, что проекция сохраняет конформную инвариантность.
-Это легко увидеть из рассмотрения тензора энергии - импульса.
-Действительно, в тензоре энергии - импульса в виде Сугавары можно выделить часть, составленную из тех комбинаций генераторов $g$, которые входят в $p$.
-Но есть ещё и остаток.
-Из-за него действие генераторов Вирасоро на состояния (\ref{eq:10}) будет выводить из этого набора.
-Таким образом в ситуации общего положения конформная инвариантность нарушается.
-
-Однако есть исключения.
-Так для представлений уровня 1 simply-laced алгебр тензор энергии - импульса в форме Сугавары состоит только из генераторов Картана.
-В этом случае он может быть пере-выражен через генераторы подалгебры и конформная инвариантность сохраняется.
-Тогда $T_{\hat{\mathfrak{g}}_k}=T_{\hat{\mathfrak{p}}_{\tilde k}}\Rightarrow c(\hat{\mathfrak{g}}_k)=c(\hat{\mathfrak{p}}_{\tilde k})$.
-Это можно переписать в виде равенства
-\begin{equation}
-  \label{eq:11}
-  \frac{k\;dim\mathfrak{g}}{k+g}=\frac{x_e k\; dim\mathfrak{p}}{x_ek+p}
-\end{equation}
-Где $x_e$ - индекс вложения, а $g$, $p$ - дуальные числа Кокстера соответствующих алгебр и было использовано равенство $\tilde k=x_e k$.
-\begin{equation}
-  \label{eq:12}
-  x_e=\frac{\left|\mathcal{P}\Theta_g\right|^2}{\left| \Theta_p\right|^2},\quad
-  x_e=\sum_{\mu\in P_{+}}b_{\lambda\mu}\frac{x_{\mu}}{x_{\lambda}}
-\end{equation}
-(Здесь $x_{\lambda}$ - индекс представления со старшим весом $\lambda$:
-\begin{equation}
-  \label{eq:13}
-  x_{\lambda}=\frac{dim \left|\lambda\right|(\lambda,\lambda+\rho)}{2 dim g}
-\end{equation})
-
-Вложения, которые удовлетворяют условию (\ref{eq:11}), называются конформными.
-
-Нетрудно показать, что решения уравнения (\ref{eq:11}) существуют только для уровня $k=1$.
-
-(Существует конечное число конформных вложений, они классифицированы).
-
-{\bf Примеры}
-\begin{itemize}
-\item $su(2)\subset su(3),\; x_e=4$
-\item $\hat{su}(2)_{10}\subset\hat{sp}(4)_1$
-\item $\hat{su}(2)_{28}\subset(\hat{G_2})_1$
-\item $\hat{su}(2)_{16}\oplus\hat{su}(3)\subset (\hat{E_8})_1$
-\end{itemize}
-
-\section{Конформные коэффициенты ветвления}
-\label{sec:conformal-branching-rules}
-
-Для ветвления аффинных алгебр $\hat{\lambda}\to \bigoplus_{\hat{\mu}}b_{\hat{\lambda}\hat{\mu}}\hat{\mu}$ существуют разные алгоритмы, однако мы можем существенно сократить работу при рассмотрении конформных вложений.
-
-Во-первых, заметим, что если коэффициент $b_{\hat\lambda\hat\mu}$ отличен от нуля, то конечная часть старшего веса $\mu$ модуля $L_{\hat\mu}$ находится в некотором грейде $n$  бесконечномерного модуля $L_{\hat\lambda}$ уровня 1.
-Сохранение конформной инвариантности ведет к соотношению для конформных размерностей соответствующих полей
-\begin{equation}
-  \label{eq:14}
-  \Delta_{\hat\lambda}+n=\Delta_{\hat\mu},
-\end{equation}
-которое переписывается в виде
-
-\begin{equation}
-  \label{eq:15}
-  \frac{(\lambda,\lambda+2\rho)}{2(1+g)}+n=\frac{(\mu,\mu+2\rho)}{2(x_e+p)}
+  \label{eq:31}
+  c(\mathfrak{a})=c(\mathfrak{g})
 \end{equation}
 
-Используя этот факт можно  легко вычислять правила ветвления.
-Для этого надо вычислить размерности интегрируемых представлений обеих алгебр  $\mathfrak{g},\mathfrak{p}$ и найти все тройки  $(\lambda,\mu,n)$, удовлетворяющие соотношению (\ref{eq:15}).
-Затем рассматриваем разложения представления $L_{\hat\lambda}$ в грейде $n$ в сумму неприводимых представлений конечномерной алгебры $\mathfrak{g}$ и выписываем правила ветвления этих представлений на представления подалгебры $\mathfrak{p}$.
-Коэффициент ветвления $b_{\hat{\lambda},\hat{\mu}}$ --- это сколько раз представление со старшим весом $\mu$ появляется в этом списке.
+Пусть $X^{a_j}_{-n_j}$ и $\tilde{X}^{a'_j}_{-n_j}$ --- понижающие операторы алгебр  $\mathfrak{g}$ и
+$\mathfrak{a}\subset\mathfrak{g}$.  $\pi_{\mathfrak{a}}$ --- проекционный оператор
+$\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$. В теории, связанной с  $\mathfrak{g}$
+с вакуумом $\left|\lambda\right>$ будут следующие состояния:
+\begin{equation}
+  \label{eq:109}
+  X^{a_1}_{-n_1}X^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+\end{equation}
+Вакуум $\mathfrak{g}$-инвариантен, то есть $X_0^a\left|0\right>=0$. При проекции на подалгебру
+$\mathfrak{a}$ состояния примут вид
+\begin{equation}
+  \label{eq:110}
+  \tilde{X}^{a'_1}_{-n_1}\tilde{X}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
+\end{equation}
+Из $\mathfrak{g}$-ивариантности вакуума следует его $\mathfrak{a}$-инвариантность, но для тензора
+энергии-импульса в общем случае это не так. Поэтому тензор энергии-импульса большей теории должен
+состоять только из генераторов $\tilde{X}$. Тогда $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow
+c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению
+\begin{equation}
+  \label{eq:111}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
+\end{equation}
+Здесь $x_e$ --- индекс вложения, а  $g$, $a$ --- дуальные числа Кокстера, которые характеризуют алгебры.
 
-{\bf Пример}
+Можно показать, что только для представлений уровня 1 это равенство удовлетворяется. То есть класс
+конформных вложений не слишком широк и существует полная их классификация. Кроме того, для
+конформных вложений существуют специальные методы разложения представлений.
 
-$\hat{su}(2)_4\subset \hat{su}(3)_1$.
-Список конформных размерностей:
+Модулярная инвариантность статсуммы для полей, принадлежащих представлениям алгебры  $\mathfrak{g}$,
+сохраняется при проекции на подалгебру $\mathfrak{a}$. Если все представления $\mathfrak{g}$ в теории
+удовлетворяют описанным требованиям, то при проекции мы получаем конформную теорию поля.
+
+Существует теорема о том, что для конформного вложения  $\mathfrak{a}\subset\mathfrak{g}$ только
+конечное число коэффициентов ветвления отлично от нуля. Поэтому после того, как мы разложили все
+представления $\mathfrak{g}$ мы подставляем результаты в выражение для статсуммы и получаем
+модулярно-инвариантную статсумму для вложенной теории. Такая статсумма уже не будет иметь
+диагональный вид:
 \begin{equation}
-  \label{eq:16}
-  \begin{aligned}
-    \hat{su}(2)_4&: h_{[4,0]}=0, h_{[3,1]}=\frac{1}{8}, h_{[2,2]}=\frac{1}{3}, h_{[1,3]}=\frac{5}{8}, h_{[0,4]}=1\\
-    \hat{su}(3)_1&: h_{[1,0,0]}=0, h_{[0,1,0]}=h_{[0,0,1]}=\frac{1}{3}    
-  \end{aligned}
+  \label{eq:36}
+   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
 \end{equation}
-Отсюда видно, что
-\begin{equation}
-  \label{eq:17}
-  \begin{aligned}
-    \left[1,0,0\right] &\to c_1 [4,0]_0\oplus c_2 [0,4]_1\\
-    [0,1,0] &\to c_3 [2,2]_0\\
-    [0,0,1] &\to c_4 [2,2]_0
-  \end{aligned}
-\end{equation}
-Где $c_1, c_2, c_3, c_4$ - коэффициенты, которые надо найти, а нижний индекс указывает грейд $n$.
+Наша работа посвящена разработке общего метода редукции представлений аффинных алгебр Ли, поэтому
+случай конформных вложений --- лишь один из примеров применения нашего метода. Однако в этом случае
+физический смысл наиболее очевиден.
 
-Коэффициенты $c_1, c_3, c_4$ вычисляются из правил ветвления в нулевом грейде. В этом грейде $L_{\hat\lambda}$ содержит только $L_{\lambda}$. Из правил ветвления
-\begin{equation}
-  \label{eq:18}
-  (0,0)\to (0),\quad (1,0)\to (2),\quad (0,1)\to (2)
-\end{equation}
-мы получаем, что $c_1=c_3=c_4=1$. $c_2$ вычисляется из представления грейда 1, содержащего конечномерное представление $(1,1)$ с правилом ветвления
-\begin{equation}
-  \label{eq:19}
-  (1,1)\to (4)\oplus (2)
-\end{equation}
-То есть $c_2$ тоже равен 1.
-
-После нахождения коэффициентов ветвления, недиагональные модулярные инварианты строятся путем подстановки соотношений для характеров.
-Например, зная коэффициенты ветвления для вложения $\hat{su}(2)_{28}\subset (\hat{G_2})_1$
-  \begin{equation}
-    \label{eq:20}
-    \begin{aligned}
-      & [1,0,0]\to [28,0]\oplus [18,10]\oplus [10,18]\oplus [0,28]\\
-      & [0,0,1]\to [22,6]\oplus [16,12]\oplus [12,16]\oplus [6,22]\\
-    \end{aligned}
-  \end{equation}
-мы получаем следующую модулярно-инвариантную статсумму:
-\begin{equation}
-  \label{eq:21}
-  Z=\left|\chi_{[28,0]}+\chi_{[18,10]}+\chi_{[10,18]}+\chi_{[0,28]}\right|^2+\left|\chi_{[22,6]}+\chi_{[16,12]}+\chi_{[12,16]}+\chi_{[6,22]}\right|^2
-\end{equation}
+Теперь я перейду к краткому объяснению метода и примерам вычислений.
 
@@
 
+Ранее для вычисления коэффициентов ветвления был предложен способ, основанный на преобразовании
+формулы Вейля-Каца для характеров представлений аффинных алгебр Ли в рекуррентное соотношение для
+коэффициентов ветвления. Однако исходный алгоритм не работал для не максимальных вложений. В данной
+работе была решена данная проблема и предложено обобщение рекуррентных соотношений на данный случай.
+
+В результате рекуррентные соотношения имеют вид
+\begin{equation}
+  \label{eq:1}
+  \begin{array}{c}
+      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
+\left.
++\sum_{\gamma \in
+\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
++\gamma }^{\left( \mu \right) }\right)
+  \end{array}
+\end{equation}
+Здесь $\mathfrak{a}_{\bot}$ --- это подалгебра, ``натянутая'' на корни $\mathfrak{g}$, ортогональные
+к корневой системе подалгебры  $\mathfrak{a}$, $W_{\bot}$ --- соответствующая этим корням группа Вейля,
+$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ --- набор весов в разложении знаменателя $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
+(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$, а $s(\gamma)$ ---
+коэффициент при  $e^{\gamma}$ в этом разложении.
+
+Это рекуррентное соотношение позволяет нам сформулировать следующий алгоритм вычисления
+коэффициентов ветвления, который осуществляется без явного построения исходного представления или
+представлений, входящих в разложение.
+\begin{enumerate}
+\item Построить наборы положительных корней $\Delta^{+}$ и $\Delta_{\mathfrak{a}}^{+}$.
+\item Выбрать те положительные корни $\alpha\in \Delta^{+}$, которые ортогональны корневому
+  подпространству  $\mathfrak{a}$ и собрать их в набор $\Delta^{+}_{\bot}$.
+\item Построить множество весов $\Gamma$, которое мы называем ``веером''.
+\item Найти множество $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$
+  аномальных весов представления $L^{(\mu)}_{\mathfrak{g}}$.
+\item Выбрать в нем веса $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in
+    \bar{C}_{\mathfrak{a}_{\bot}} \right\}$. Это можно легко сделать, так как у нас есть набор
+  $\Delta^{+}_{\bot}$ и мы можем проверить, лежит ли вес $\pi_{\mathfrak{a}_{\bot}}\lambda$ в
+  главной камере Вейля алгебры $\mathfrak{a}_{\bot}$. Для этого все скалярные произведения этого
+  веса $\lambda$ с корнями из  $\Delta^{+}_{\bot}$ должны быть неотрицательны.
+\item Далее для весов $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in
+  \bar{C}_{\mathfrak{a}_{\bot}}$ мы вычисляем размерность соответствующих представлений
+  $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$
+  при помощи формулы Вейля и набора $\Delta^{+}_{\bot}$.
+\item Далее рекуррентно вычисляются аномальные коэффициенты ветвления, а внутри главной камеры Вейля
+  алгебры $\mathfrak{a}$ аномальные коэффициенты совпадают с настоящими коэффициентами ветвления.
+\end{enumerate}
+
 \subsection{Примеры}
 \label{sec:examples}
+
+Я начну с примера вычисления в случае конечномерных простых алгебр Ли, так как его легко нарисовать.
+
+Рассмотрим регулярное вложение  $A_1$ в $B_2$. Вот на рисунке корневая системы алгебры $B_2=so(5)$.
+Корень  $\beta$ вложенной алгебры $A_1$ равен $\alpha_1+2\alpha_2$.
+
+Функция $s(\gamma)$ и веер $\Gamma$ строятся исходя из корневых систем $\mathfrak{g}, \mathfrak{a}$
+$\frac{\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}_{\mathfrak{g}}\setminus
+      \Delta^{+}_{\mathfrak{a}}} \left(1-e^{-\alpha}\right) \right)}{\prod_{\beta\in
+    \Delta^{+}_{\mathfrak{a}}} \left(1-e^{-\beta}\right) }$ и получается
+\begin{equation}
+  \label{eq:22}
+  (1,2),\; (2,-1)
+\end{equation}
+Вторая компонента - значение $s(\gamma)$.
+
+Опишем редукцию первого фундаментального представления $B_2$. Старший вес изображен на рисунке.
+\begin{figure}[ph]
+  \noindent\centering{
+    \includegraphics[width=90mm]{B2_A1.pdf}
+  }
+  \caption{Regular embedding of $A_1$ into $B_2$}
+  \label{fig:B2_A1}
+\end{figure}
+Вот набор аномальных весов $\omega(\mu+\rho)-\rho,\; \omega\in W$ с соответствующими четностями
+отражений $\epsilon(\omega)$.
+Теперь мы факторизуем группу Вейля $W$ по подгруппе $W_{\bot}=\left\{\omega_1\right\}$. Получаем
+следующий набор весов и размерностей представлений  $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$:
+\begin{figure}[h!tb]
+  \noindent\centering{
+    \includegraphics[width=90mm]{B2_A1_2.pdf}
+  }
+  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
+  \label{fig:B2_A1_2}
+\end{figure}
+
+Затем мы проектируем эти веса и размерности на корневое подпространство подалгебры
+$\mathfrak{a}=A_1$ и получаем следующие аномальные веса и их кратности:
+\begin{equation}
+  \label{eq:25}
+  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
+\end{equation}
+
+Аномальный коэффициент ветвления  $k^{(1,0)}_{1}=2$, для коэффициента $k^{(1,0)}_{0}$ из
+рекуррентного соотношения получаем
+\begin{equation}
+  \label{eq:23}
+  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1
+\end{equation}
+
+В работе рассмотрено большое число примеров вложений аффинных алгебр Ли. На самом деле мы написали
+программу, которая может строить такие примеры автоматически для алгебр Ли не слишком большого
+ранга.
+
+Я сейчас покажу результаты применения нашего алгоритма для одного из примеров конформных вложений.
+
+Рассмотрим такое вложение $\mathfrak{a}\subset \mathfrak{g}$, где
+$\mathfrak{a}=\widehat{su(2)}\oplus \widehat{su(2)}$, а $\mathfrak{g}= \widehat{su(4)}$. Это
+вложение является аффинным расширением специального вложения конечномерных алгебр Ли $su(2)\oplus
+su(2)\subset su(4)$. Это специальное вложение строится следующим образом: берем четырехмерное
+представление $su(2)\oplus su(2)$ со старшим весом $(1,1)$. Вот веса этого представления
+\ref{fig:A_1+A_1_to_A3}, их координаты в базисе фундаментальных весов: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
+
+\begin{figure}[h]
+  \begin{multicols}{2}
+    \hfill
+    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
+    \hfill
+    \caption{Representation for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
+    \label{fig:A_1+A_1_to_A3}
+    \hfill
+    \includegraphics[width=50mm]{A1+A1-A3.pdf}
+    \hfill
+    \caption{Embedded roots for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
+    \label{fig:A1+A1-A3}
+  \end{multicols}
+\end{figure}
+
+Тогда матричные элементы представления генераторов подалгебры Картана $b_1,b_2$ в базисе Вейля
+даются выражениями
+$d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$, так что $d(b_1)=\mathrm{diag}(1,-1,1,-1),\;
+d(b_2)=\mathrm{diag}(1,1,-1,-1)$.  Отсюда вложенные корни $\alpha_1,\alpha_2$ of $su(2)\oplus su(2)$
+выражаются через корни $\tilde{\alpha}_i$ алгебры  $su(4)$
+\begin{equation}
+  \label{eq:37}
+  \begin{array}{l}
+     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
+     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
+  \end{array}
+\end{equation}
+Они изображены на рисунке \ref{fig:A1+A1-A3}.
+
+Вложение имеет индексы  $(2,2)$ и является конформным, так как $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
+
+Для построения модулярно-инвариантной статсуммы нам нужно знать редукцию фундаментальных
+представлений $\widehat{su(4)}$. Фундаментальные веса имеют следующие координаты в ортогональном базисе
+\begin{equation}
+  \begin{array}{lll}
+     \omega_0 & = & (0,0,0,0;1;0)\\
+     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
+     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
+     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
+  \end{array}
+\end{equation}
+
+Множества положительных корней  $\Delta^{+}$ и $\Delta_{\mathfrak{a}}^{+}$:
+\begin{equation}
+  \label{eq:38}
+  \begin{array}{lll}
+    \Delta^{+} &=&\left\{\co{\Delta}^{+};\; \co{\Delta}-n\delta;\;     -n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right. \\
+    & & \quad\left.\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\}\right\}\\
+    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm \alpha_2-n\delta;\; -n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
+  \end{array}
+\end{equation}
+
+Набор $\Delta^{+}_{\bot}$ пуст.
+Веер  $\Gamma _{\frak{a}\subset \frak{g}}$ показан на рисунке \ref{fig:A1+A1-A3_fan}. Конечные координаты
+даны в базисе фундаментальных весов $su(2)\oplus su(2)$. Элемент $\gamma$ обозначен крестом, если
+$s(\gamma)=1$ и кругом, если $s(\gamma)=-1$.
+\begin{figure}[h!tb]
+  \includegraphics[width=150mm]{A1+A1-A3_fan.pdf}
+  \caption{Fan for the special embedding $\widehat{su(2)}\oplus\widehat{su(2)}\subset \widehat{su(4)}$}
+  \label{fig:A1+A1-A3_fan}
+\end{figure}
+
+Мы ограничимся вычислениями до пятого грейда.
+\begin{figure}[h!tb]
+  \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
+  \caption{Projected anomalous weights for $L^{\omega_1}_{A_3}$}
+  \label{fig:A1+A1-A3_anom}
+\end{figure}
+
+Множество аномальных весов  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in
+  W\right\}$ представления алгебры $\hat{A}_3$ состоит из 192 элементов, их проекции
+$\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ показаны на рисунке  \ref{fig:A1+A1-A3_anom}
+для $\mu=\omega_2=(0,0,1;1;0)$.
+
+Аналогичные картинки для $\omega_0, \omega_1,\omega_3$ я не показываю.
+
+Аномальные коэффициенты ветвления для представления  $L^{(\omega_1)}$ вычислены при помощи
+рекуррентных соотношений и показаны на рисунке \ref{fig:A1+A1-A3_branching}. 
+\begin{figure}[h!tb]
+  \includegraphics[width=180mm]{A1+A1-A3_branching.pdf}
+  \caption{Anomalous branching coefficients for $L^{(0,0,1;1;0)}_{A_3}$}
+  \label{fig:A1+A1-A3_branching}
+\end{figure}
+
+Получаются следующие правила ветвления:
+ \begin{equation}
+   \label{eq:39}
+   \begin{array}{ll}
+     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
+     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
+     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
+     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
+   \end{array}
+ \end{equation}
+
+В результате мы получаем модулярно-инвариантную статсумму для WZW-модели с киральной алгеброй $\hat{A}_1\oplus \hat{A}_1$.
+\begin{multline}
+  \label{eq:40}
+  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
+  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
+\end{multline}
 
@@
 
+Недавно мы заметили, что струнные функции, которые описывают представления, модулярные функции,
+которые описывают редукцию представлений и функции слияния, которые описывают разложение тензорных
+произведений представлений на неприводимые, допускают построение дуальных систем функций. Эти
+дуальные функции могут быть построены просто из анализа соответствующих групп Вейля, при этом многие
+известные результаты могут быть перенесены на них, например, результаты Каца о модулярных свойствах
+струнных функций и функций ветвления. И наоборот.
+
+В настоящее время мы начали исследовать эти системы дуальных функций.
+
+Среди других возможных приложений полученных методов можно отметить также приложения в интегрируемых
+цепочках, а также в приложения дуальных функций теории модулярных форм.
+
 \end{document}

### 2010-05-26 AffineLieAlgebras/InformalNotes/article.tex
Some artifacts are removed
V.D. improvements included.

@@
 \begin{center}
-{\Huge \bf Recursive algorithms, branching coefficients \\ for affine algebras and applications\\[0.5cm]
+{\Huge \bf Recursive algorithms, branching coefficients \\ and applications\\[0.5cm]
 }
@@
 \pagenumbering{arabic}
-\title{\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}}
+\title{\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}}
 \author{Vladimir Lyakhovsky \thanks{ Supported by
@@
 \begin{abstract}
-  Recurrent relations for branching coefficients in affine Lie algebras highest weight modules are studied.
-The decomposition algorithm for  integrable highest weight modules reduction based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive  subalgebra.
-We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original one.
-The possible applications of subtracted fans in CFT models are considered.
+  Recurrent relations for branching coefficients in affine Lie algebras integrable highest weight modules are studied.
+The decomposition algorithm based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive subalgebra.
+We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original ones.
+Possible applications of subtracted fans in CFT models are considered.
 \end{abstract}
@@
 
-The problem of reduction of a Lie algebra representation to a  subalgebra is studied for several decades and has various applications in physics.
-In the context of finite-dimensional algebras it is important for the study of great unification models whilst the branching problem for affine Lie algebras emerges in conformal field theory, for example, in the construction of the modular-invariant partition functions \cite{difrancesco1997cft}.
-
-There exist several approaches to the computation of the branching coefficients. Some of them use the BGG
+The branching problem for affine Lie algebras emerges in conformal field theory, for example, in the construction of modular-invariant partition functions \cite{difrancesco1997cft}.
+Recently the problem of the conformal embeddings was considered in the paper \cite{coquereaux2008conformal}.
+
+There exist several approaches to deal with the branching coefficients. Some of them use the BGG
 resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
@@
 
-Usually only the embedding of the maximal reductive subalgebras is considered since the case of non-maximal subalgebra can be obtained using the chain of maximal injections.
-In this paper we study the recurrent properties for branching coefficients which generalise the recurrent relations obtained earlier (see the paper \cite{ilyin812pbc}and the references therein) to the cases of non-maximal reductive subalgebras.
-The result is formulated by an introduction of a new injection fan called "subtracted fan".
-Using this new tools we formulate simple and explicit algorithm for the computation of branching coefficients which is applicable to the non-maximal subalgebras of finite-dimensional and affine Lie algebras.
-
-We show that our algorithm can be used in a study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some  physical limitations.
+Usually only the maximal reductive subalgebras are considered since the case of non-maximal subalgebra can be obtained using the chain of maximal injections.
+In this paper we find the recurrent properties for branching coefficients that generalise the relations obtained earlier (see the paper \cite{ilyin812pbc} and the references therein) to the case of non-maximal reductive subalgebra.
+The result is formulated in terms of new injection fan called "the subtracted fan".
+Using this new tools we formulate simple and explicit algorithm for computations of branching coefficients which is applicable to the non-maximal subalgebras of finite-dimensional and affine Lie algebras.
+
+We demonstrate that our algorithm can be used in the study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some physical limitations.
 
 The paper is organised as follows.
-In the next subsection  we fix the notations used throughout the paper.
+In the subsection \ref{sec:notation}  we fix the notations used throughout the paper.
 In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules of algebra $\mathfrak{g}$ with respect to a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}).
-In the next Section \ref{sec:examples} we present several examples and discuss some applications in CFT models (s.
-\ref{sec:phys-appl}).
+In the Section \ref{sec:examples} we present several examples and discuss some applications in CFT models (Section \ref{sec:phys-appl}).
 We conclude the paper with a review of obtained results.
-Possible future developments are discussed (s.
-\ref{sec:conclusion}).
+Possible future developments are discussed (Section \ref{sec:conclusion}).
 
@@
 
-$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ --- the reduction of the module;
+$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ --- the module decomposition with respect to $\frak{a}\longrightarrow \frak{g}$;
 
@@
 
- $k_{\lambda}$ --- the anomalous branching coefficients;
-
-It is important to mention that
+ $k_{\lambda}$ --- the anomalous branching coefficients, notice that
 \begin{equation}
@@
 
-Our aim is to demonstrate that despite possible singularities arriving in the Weyl denominator
-when it is projected to the subalgebra root space injection fan technique can be properly modified.
-The result of such modification is that the generalized recurrent relations for anomalous branching
-coefficients \eqref{eq:21} must be reformulated in the following form:
+Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator
+(when it is projected to the subalgebra root space) the injection fan technique can be properly modified.
+The result of this modification is that the generalized recurrent relations for anomalous branching
+coefficients \eqref{eq:21} is to be formulated in the following form:
 \begin{equation}
@@
    \end{equation}
-Here $\mathfrak{a}_{\bot}$ is the subalgebra described by the roots of $\mathfrak{g}$
+Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by the roots of $\mathfrak{g}$
 orthogonal to the root subsystem of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group,
@@
 
-In the section \ref{sec:algorithm} we  shall describe the  computational algorithm for  branching coefficients
+In the subsection \ref{sec:algorithm} we  shall describe the  computational algorithm for  branching coefficients
 based on this formula and present some examples.
@@
 Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
-projection operators $\pi_{\mathfrak{a}}$ that bring the roots of $\mathfrak{g}$ to the
-weight subspace of $\mathfrak{a}$:
+projection operators $\pi_{\mathfrak{a}}$ that bring the weights of $\mathfrak{g}$ to the weight subspace of $\mathfrak{a}$:
 \begin{equation}
@@
 
-It is important to keep in mind that the projection of some of positive roots of
+It is important that the projection of some of positive roots of
 the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the
@@
 
-Consider for instance regular the embedding of $A_1\subset B_2$.
-
+Consider for instance the regular embedding of $A_1\subset B_2$.
 The extended Dynkin diagram of $B_2$ is presented in the Figure \ref{fig:B2Dynkin}.
@@
 
-Note that when we study the regular embedding obtained by dropping the nodes
+Notice that when we study the regular embedding obtained by dropping the nodes
 of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the
@@
 generated by the remaining connected components.
-Consider for example the embedding of $B_2\subset B_4$ (the figure \ref{fig:dynkin}).
+Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
 In this case by eliminating
@@
 So the question is whether $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them.
-It is possible when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.
+The answer is positive  when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$.
+Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.
 
@@
 Otherwise if $\mathfrak{a}=B_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_r$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
-It is the only case when simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.
-There exists the third possibility to get the pair of subalgebras $\mathfrak{a},\mathfrak{a}_{\bot}$ with the regular subalgebra $\mathfrak{a}$ by dropping single node from the extended Dynkin diagram of $B_r$.
-It can be done by taking as the set of simple roots of $\mathfrak{a}$ the set $\{\alpha_{1,-2},\alpha_{1,2},\alpha_{2,-3},\dots,\alpha_{r_{\mathfrak{a}}-1,-r_{\mathfrak{a}}}\}$.
+This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.
+There exists the third possibility to get the pair of subalgebras $\mathfrak{a},\mathfrak{a}_{\bot}$ with the regular subalgebra $\mathfrak{a}$ by dropping the single node from the extended Dynkin diagram of $B_r$.
+This can be done by choosing the set of simple roots of $\mathfrak{a}$ in the form $\{\alpha_{1,-2},\alpha_{1,2},\alpha_{2,-3},\dots,\alpha_{r_{\mathfrak{a}}-1,-r_{\mathfrak{a}}}\}$.
 Then $\mathfrak{a}=D_{r_{\mathfrak{a}}}$, $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
@@
 
-Up to this point we considered the problem of $\mathfrak{a}_{\bot}$-construction given $\mathfrak{a}\in\mathfrak{g}$ for regular injections in terms of Dynkin diagrams.
+Up to this point we considered the problem of constructing the subalgebra $\mathfrak{a}_{\bot}$ for a given regular injection $\mathfrak{a}\in\mathfrak{g}$  in terms of Dynkin diagrams.
 When the root systems $ \Delta$ and $\Delta_{\mathfrak{a}}$ are known explicitly all that we need is to select the roots
@@
 
-Now consider the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$-module 
-with the highest weight $\mu$. For the character of this module we have
+Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
+with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$ can be written as
 \begin{equation}
   \label{eq:41}
-  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
-\end{equation}
-The projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ gives us the single element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
-
-Using this property we can reconsider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules.
+  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
+\end{equation}
+Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ is the single element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
+
+Using this property we can consider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
 Multiply the equation (\ref{eq:4}) by the element
@@
 \end{equation}
-Taking into account that for any formal series $Q \in {\cal E}$ and the binomial the projection commutes with the multiplication,
+Taking into account that the projection commutes with the multiplication,
 \begin{equation}
@@
 we can rewrite the
-product of (\ref{eq:4}) and (\ref{eq:5}) in the form:
+product of (\ref{eq:4}) and (\ref{eq:5}):
 \begin{multline}
@@
   \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
+  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
 \end{multline}
@@
 \end{multline}
-The projector $\pi_{\mathfrak{a}}$ transforms the character of the module ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ into an element equal to the dimension of the module multiplied by the unit element:
+The projector $\pi_{\mathfrak{a}}$ transforms the character ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ into the unit element of $\cal{E}$ multiplied by ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$  :
   \begin{multline}
@@
   \end{multline}
-
-Thus we have the equality
+Thus we obtained  the relation
 \begin{multline}
@@
   \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
-  \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
+  \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
 \end{multline}
-Following the transformations performed in \cite{ilyin812pbc} we rewrite the multiplier in the right-hand side:
+Let us rewrite the multiplier in the right-hand side:
 \begin{equation}
@@
 \Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
-\gamma \right) \neq 0\right\} ;  \label{phi-d}
-\end{equation}
-In these terms the equation for the formal elements,
+\gamma \right) \neq 0\right\} .  \label{phi-d}
+\end{equation}
+From the obtained equation for the formal elements,
 \begin{multline}
@@
 \end{multline}
-leads to the following equality 
+we can deduce the following property of the anomalous branching coefficients,
 \begin{equation}
@@
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\quad \xi\in P_{\mathfrak{a}}
-\end{equation}
-
-To get the recurrent relations for the anomalous branching coefficients we use the following procedure  (similar to that in \cite{ilyin812pbc}).
+   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\quad \xi\in P_{\mathfrak{a}}.
+\end{equation}
+
+To get the recurrent relations for the coefficients $k^{(\mu)}_{\xi+\gamma}$ we use the following procedure  (similar to that in \cite{ilyin812pbc}).
 Let $\gamma_{0} $ be the lowest vector with respect to the natural ordering in $%
@@
 
-Now let the set $\Delta_{\bot}^{+}$ be empty.
-There are three different reasons for $\Delta_{\bot}^{+}=0$: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$, ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
+Now consider the case  $\Delta_{\bot}^{+} = 0$.
+There are three different reasons for $\Delta_{\bot}^{+}$ to be empty: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$, ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
 Both the first and the second cases can be treated as corresponding to the trivial orthogonal subalgebra:
-$\mathfrak{a}_{\bot}=0$. In any of these cases instead of the formal characters in the right-hand side of (\ref{eq:13}) we obtain the formal element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$
+$\mathfrak{a}_{\bot}=0$. In any of these cases instead of the formal characters in the right-hand side of (\ref{eq:13}) we obtain the formal element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$.
 In the first two cases (equivalent to $\mathfrak{a}_{\bot}=0$) the projection operator retains its purely geometrical meaning: the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
 It is clear that in any of the three variants the final vector $\pi_{\mathfrak{a}}\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)$ leads to the unit of the formal algebra
-$\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty we get the more simple recurrent relation: 
+$\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty the  recurrent relation is simplified:
 \begin{equation}
@@
 \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
-+\gamma }^{\left( \mu \right) }\right)   \label{recurrent relation special}
-\end{equation}
-It coinsides with the one obtained in \cite{ilyin812pbc} (formula (16)).
-
-  In the next section we describe an algorithm for the computation of branching coefficients based on the relation \eqref{recurrent-relation}.
++\gamma }^{\left( \mu \right) }\right),  \label{recurrent relation special}
+\end{equation}
+the latter coinsides with the one obtained in \cite{ilyin812pbc} (formula (16)).
+
+  In the next section we describe a computation algorithm for branching coefficients based on the relation \eqref{recurrent-relation}.
 
@@
 
-We use the recurrent relation \eqref{recurrent-relation} to formulate an algorithm for recursive computation of the branching coefficients.
-It is important to mention that the computation of the branching coefficients is performed without the  explicit construction of the module $L^{(\mu)}_{\mathfrak{g}}$ and any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
-
-The algorithm contains the following steps.
+The recurrent relation \eqref{recurrent-relation} allows us to formulate an algorithm for recursive computation of the branching coefficients.
+In this algorithm there is no need to  construct the module $L^{(\mu)}_{\mathfrak{g}}$ or any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
+
+It contains the following steps:
 \begin{enumerate}
@@
 \item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
+\item Construct the set $\Gamma$ \eqref{fan-defined}.
 \item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
+\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$, it must be non-negative.
 \item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\Gamma$ \eqref{fan-defined}.
 \item Calculate the anomalous branching coefficients in the main Weyl
-  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent-relation}).
+  chamber of the subalgebra $\mathfrak{a}$ using the recurrent relation (\ref{recurrent-relation}).
 \end{enumerate}
@@
 We denote the corresponding Weyl reflections by $\omega_1, \omega_2$.
-Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+2\alpha_2$ and is drawn as grey vector.
-
-Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$, which is drawn as the black vector at the Figure \ref{fig:B2_A1}.
+Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+2\alpha_2$ and is drawn as the grey vector.
+
+Let's describe the reduction of the fundamental representation of $B_2$ with the highest weight equal to $(1,0)$ (in the fundamental weight basis), it is drawn as the black vector in the Figure \ref{fig:B2_A1}.
 \begin{figure}[ph]
@@
 \end{figure}
-On the Figure \ref{fig:B2_A1} we have also shown the set of weights $\omega(\mu+\rho)-\rho,\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
+There we have also shown the set of weights $\omega(\mu+\rho)-\rho,\; \omega\in W$ of the fundamental representation of $B_2$ with the corresponding determinants $\epsilon(\omega)$ of Weyl transformations.
 Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
@@
 \end{equation}
-For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
+For the function $s(\gamma)$ and the set $\Gamma$ (using the definition (\ref{phi-d},\ref{fan-defined})) we have
 \begin{equation}
@@
 
-Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent-relation}) gives us
+As far as the anomalous branching coefficient $k^{(1,0)}_{1}=2$ for the coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent-relation}) gives the value
 \begin{equation}
   \label{eq:23}
-  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1
-\end{equation}
-So we have computed the branching coefficients.
+  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1.
+\end{equation}
+The recurrence property defines the branching.
 
@@
 \label{sec:someth-high-dimens}
-Consider the the regular embedding of the subalgebra $B_2$ into the algebra $B_4$.
-We calculate the branching coefficients for the fundamental representation of $B_4$.
+Consider the regular embedding $B_2 \longrightarrow B_4$.
+We calculate the branching coefficients for the fundamental vector representation of $B_4$.
 The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
@@
 
-In the orthogonal basis $e_1,\dots,e_4$ simple roots of $B_4$ are
+In the orthogonal basis $e_1,\dots,e_4$ the simple roots of $B_4$ are
 \begin{equation}
@@
 \end{equation}
-Positive roots are
+The positive roots are
 \begin{multline}
@@
 \end{multline}
-Simple roots of the embedded subalgebra $\mathfrak{a}=B_2$ are
+The simple roots of the embedded subalgebra $\mathfrak{a}=B_2$ are
 \begin{equation}
@@
 
-The set $\Delta^{+}_{\bot}$ is equal to
+The set $\Delta^{+}_{\bot}$ contains the roots
 \begin{equation}
@@
 \end{equation}
-
-We see that this is the set of positive roots of the algebra $\mathfrak{a}_{\bot}=B_2$.
-
-To find the branching coefficients we need to compute the anomalous weights of $B_4$, select weights lying in the main Weyl chamber of $\mathfrak{a}_{\bot}$ and compute the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.
-
-We consider the $B_4$-module with the highest weight $\mu=(0,1,0,2)=2
-e_1 + 2 e_2 + e_3 + e_4$.
-
-The set of the anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W$
-consists of 384 elements. We do not show it here.
-
-We need to select those weights $\omega(\mu+\rho)$  which are projected into the main chamber of the embedded algebra $\mathfrak{a}_{\bot}$.
-It means that scalar product of these weights with all the roots from $\Delta^{+}_{\bot}$ is non-negative.
-
-To compute dimensions of the corresponding
+and is the set of positive roots for the algebra $\mathfrak{a}_{\bot}=B_2$.
+
+Firstly we construct the fan for this injection.
+Using the definition (\ref{fan-defined}) we obtain the set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
+
+To find the branching coefficients we need to compute the anomalous weights of $B_4$, select the weights belonging to $C^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$ and compute the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.
+
+Consider the $B_4$-module $L^{\mu}$ with the highest weight $\mu=(0,1,0,2)=2
+e_1 + 2 e_2 + e_3 + e_4$; $dim(L^{(0,1,0,2)})=2772$.
+
+The set of the anomalous weights $\left\{ \omega(\mu+\rho)-\rho,\; \omega\in W\right\}$
+contains of 384 vectors.
+
+We need to select the weights $\psi \in \omega(\mu+\rho)$  with the property $\pi_{\mathfrak{a}_{\bot}} \left(  \psi \right) \in C^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$.
+It means that the scalar product of these weights with all the roots in $\Delta^{+}_{\bot}$ is non-negative.
+
+To compute the dimensions of the corresponding
 $\mathfrak{a}_{\bot}$-modules we need to project each selected weight
-onto the root space $\Delta^{+}_{\bot}$ and substract
-$\rho_{\mathfrak{a}_{\bot}}$, then use Weyl dimension formula.
-
-We show the result of this procedure on the Figure \ref{fig:B4B2anom}.
+onto the root space $\Delta^{+}_{\bot}$, substract
+$\rho_{\mathfrak{a}_{\bot}}$ and apply the Weyl dimension formula.
+
+The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.
 \begin{figure}[h!tb]
     \includegraphics[width=150mm]{B4_B2_anom_points.pdf}
-  \caption{Anomalous weights with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
+  \caption{Anomalous weights with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
   \label{fig:B4B2anom}
@@
 
-Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
-
-Using the definition (\ref{fan-defined}) we get the following set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
 \begin{figure}[h!tb]
@@
 \end{figure}
-We use the recurrent relation (\ref{recurrent-relation}) and get
+Applying the recurrent relation (\ref{recurrent-relation}) we obtain the
 following branching coefficients:
@@
   \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
-  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
-\end{equation}
-The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
-is equal to 2772. It is easy to see, that right-hand side of the
-equation (\ref{eq:24}) gives the same result.
+  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}.
+\end{equation}
 
@@
 \label{sec:affine-lie-algebras}
-\subsubsection{Embedding of the affine algebra into affine algebra}
+\subsubsection{Affine into affine embedding}
 \label{sec:embedd-affine-algebr}
@@
 Consider the affine extension of the example \ref{sec:regul-embedd-a_1}.
-Since this embedding is regular, the level of the representations of the subalgebra is equal to the level of the representation of the algebra.
+Since this embedding is regular, the level of the  subalgebra modules is equal to that of the initial module.
 
@@
 
-Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0;1;0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the level of the weight and the fourth is the grade.
-
-The set of the anomalous weights of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.
-
-\begin{figure}[h!tb]
-  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
-  \caption{The anomalous weights of the $(1,0;1;0)$ representation of the algebra $\hat{B_2}$}
-  \label{fig:affine_B2_anom_point}
-\end{figure}
-
-As the next step of our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
-The result of this computation up to the twelfth grade is presented at the Figure
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
-  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
-  \label{fig:AffineB2_A1_anom_proj}
-\end{figure}
-
-Then we should construct ``the fan'' and use the recurrent relation for the computation of anomalous branching coefficients.
-
-Using the definition (\ref{fan-defined}) we get the following $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
+Using the definition (\ref{fan-defined}) we get the fan $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
 Here we restricted the computation to the twelfth grade.
@@
 
-Also we should mention that the lowest vector of the fan $\gamma_0$ is equal to zero, since we have excluded all the roots of $\Delta^{+}_{\bot}$ from the defining relation (\ref{fan-defined}).
-
-Using the recurrent relation for the anomalous branching coefficients we get the following result, presented at the Figure \ref{fig:AffineB2_A1_branching}.
-Dotted area represents the main Weyl chamber of the algebra $\hat{A}_1$.
+Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $w_1=(1,0;1;0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the level of the weight and the fourth is the grade.
+
+The set of the anomalous weights for this module up to the sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade its form is similar to that in the  Figure \ref{fig:B2_A1}.
+
+\begin{figure}[h!tb]
+  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
+  \caption{The anomalous weights of the $(1,0;1;0)$ representation of the algebra $\hat{B_2}$}
+  \label{fig:affine_B2_anom_point}
+\end{figure}
+
+Performing the next step of the algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and find the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+The result of this computation up to the twelfth grade is presented in the Figure
+\ref{fig:AffineB2_A1_anom_proj}.
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
+  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \label{fig:AffineB2_A1_anom_proj}
+\end{figure}
+
+Notice that here the lowest weight  $\gamma_0$ of the fan  is zero, since we have excluded all the roots of $\Delta^{+}_{\bot}$ from the defining relation (\ref{fan-defined}).
+
 \begin{figure}[ph]
   \centering
-  \includegraphics[width=110mm]{AffineB2_A1_branching.pdf}
+  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
   \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
@@
 
-Selecting the elements inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get for the branching coefficients up to twelfth grade
+Selecting the elements inside the  Weyl chamber
+$\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
+we get the following results for the branching coefficients up to twelfth grade
 \begin{multline}
@@
 \end{multline}
-This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
+This result can be presented as the set of branching functions \cite{kac1990idl}.
 \begin{eqnarray}
@@
 \end{eqnarray}
-Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
-
-\section{Applications to conformal field theory}
+Here the lower index enumerates the branching function according to their highest weights in $P^+_{\hat{A_1}}$, these are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
+
+\section{Applications to the conformal field theory}
 \label{sec:phys-appl}
@@
 
-Let $X^{a_j}_{-n_j}$ and $\tilde{X}^{a'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and of $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
+Let $X^{a_j}_{-n_j}$ and $\tilde{X}^{a'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and for $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
 Let $\pi_{\mathfrak{a}}$ be the projection operator of $\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$.
@@
 \end{equation}
-The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance, but it is not the case for the energy-momentum tensor.
-So the energy-momentum tensor of the larger theory should consist only of generators of $\tilde{X}$.
+The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance, but this is not the case for the energy-momentum tensor.
+So the energy-momentum tensor of the larger theory should consist only of the generators of $\tilde{X}$.
 Then $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow c(\mathfrak{g})=c(\mathfrak{a})$.
@@
 It can be demonstrated that the solutions of the equation (\ref{eq:111}) exist only
-for level $k=1$ \cite{difrancesco1997cft}.
-
-The class of conformal embeddings is not rich, the complete classification is given in the paper \cite{schellekens1986conformal}.
+for the level $k=1$ \cite{difrancesco1997cft}.
+
+The complete classification of conformal embeddings is given in the paper \cite{schellekens1986conformal}.
 The requirement (\ref{eq:31}) allows to reduce the problem of finding the branching coefficients for affine Lie algebras to the computation of branching coefficients for finite-dimensional Lie algebras.
@@
 If we have modular-invariant partition function for the fields described by a representation of the algebra $\mathfrak{g}$ this modular invariance is preserved by the projection on the subalgebra $\mathfrak{a}$, but we need also the preservation of the conformal invariance.
-So we should select only those highest-weight modules of the subalgebra $\mathfrak{a}$ for which the relation (\ref{eq:111}) holds.
-
-In the decomposition (\ref{eq:3}) let the highest weight $\nu$ of the subalgebra module belong to the grade $n$ of the projected  module $\pi_{\mathfrak{a}}\cdot L^{(\mu)}_{\mathfrak{g}}$.
-Then the relation (\ref{eq:111}) implies the following requirement on the conformal dimensions of the corresponding fields
-\begin{equation}
-  \label{eq:32}
-   \Delta_{\pi_{\mathfrak{a}}\mu}+n=\Delta_{\nu}
-\end{equation}
-It leads to a restriction imposed on the classical parts of the corresponding weights:
-\begin{equation}
-  \label{eq:33}
-  \frac{(\co{\mu},\co{\mu}+2\rho)}{2(1+g)}+n=\frac{(\co{\nu},\co{\nu}+2\rho_{\mathfrak{a}})}{2(x_e+a)}
-\end{equation}
-The finite reducibility theorem states that for conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
-
-Then after we have found all such weights $\nu$ and the corresponding branching coefficients $b^{(\mu)}_{\nu}$ we can replace the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function
+So we should select only those highest-weight modules of the algebra $\mathfrak{g}$ for which the relation (\ref{eq:111}) holds.
+
+This relation and the asymptotics of the branching functions can be used to prove the finite reducibility theorem.
+It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
+
+Having found all such weights $\nu$ and the corresponding branching coefficients $b^{(\mu)}_{\nu}$ we can replace the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function
 \begin{equation}
@@
 \end{equation}
-Recently the problem of the conformal embeddings was considered in the paper \cite{coquereaux2008conformal}.
 
@@
 But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
+
+If we limit the consideration by the affine extensions of simple classical Lie algebras, the number of possible non-maximal conformal embeddings is rather small \cite{schellekens1986conformal}.
+We study the example of $\hat{A}_1\subset \hat{A}_2\subset\hat{A}_{3}$ in the section \ref{sec:non-maxim-conf}.
 
@@
 Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details.
-Here the first two components are the Dynkin indexes (coordinates in the fundamental weights basis) of the finite part of the weight.
+Here the first two components are the Dynkin indices (coordinates in the fundamental weights basis) of the finite part of the weight.
 
@@
 
-Embedding of affine extensions of semisimple subalgebras to affine lie algebras allows additional construction of modular invariants \cite{difrancesco1997cft}, \cite{walton1989conformal}.
 Consider the conformal embedding constructed as the affine extension  $\mathfrak{a}_{1}\oplus\mathfrak{a}_{2}\subset \mathfrak{g}$ of the embedding of semisimple subalgebra $\ao_1\oplus\ao_2$ into simple Lie algebra $\go$.

### 2010-05-26 AffineLieAlgebras/InformalNotes/article.tex
More notes from V.D.

@@
 If we limit the consideration by the affine extensions of simple classical Lie algebras, the number of possible non-maximal conformal embeddings is rather small \cite{schellekens1986conformal}.
-We study the example of $\hat{A}_1\subset \hat{A}_2\subset\hat{A}_{3}$ in the section \ref{sec:non-maxim-conf}.
 
@@
 \label{sec:spec-embedd-hata_1s}
-Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $su(2)\subset su(3)$ with the embedding index $x_e=4$.
+Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $A_1\subset A_2$ with the embedding index $x_e=4$.
 The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.
@@
 There exist three level one dominant weights in the weight space of $\hat{A}_2$.
-It is easy to see that the set $\Delta_{\bot}$ and the algebra $\mathfrak{a}_{\bot}$ are empty.
+It is easy to see that the set $\Delta_{\bot}$ is empty and the subalgebra $\mathfrak{a}_{\bot}=0$.
 
@@
 
-The set of the anomalous weights of this representation up to the sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}.
+The set of the anomalous weights of this representation  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade.
 We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.
@@
   \includegraphics[width=180mm]{AffineA2_A1_anom.pdf}
-  \caption{The anomalous weights of the $(0,0;1;0)$ representation of the algebra $\hat{A_2}$}
+  \caption{The anomalous weights of the module $L^{(0,0;1;0)}_{\hat{A_2}}$}
   \label{fig:affine_A2_anom_point}
@@
 
-According to our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$.
-The result of these calculations up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
+Using the definition (\ref{fan-defined})  we construct ``the fan'' $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).
+Here we restricted the calculations to the first eight grades.
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
+  \caption{The fan $\Gamma_{\hat{A_1}\subset \hat{A_2}}$}
+  \label{fig:AffineA2A1Fan}
+\end{figure}
+
+The next step is to project the anomalous weights to $P_{\aht A_1}$.
+The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
 \begin{figure}[h!tb]
@@
   \label{fig:AffineA2_A1_anom_proj}
-\end{figure}
-
-Then we construct ``the fan'' and use the recurrent relations to compute the anomalous branching coefficients.
-
-Using the definition (\ref{fan-defined}) we get the following set of
-the weights $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:AffineA2A1Fan}.
-Here we restricted the calculations to the first eight grades.
-\begin{figure}[p]
-  \centering
-  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
-  \caption{Fan for $\hat{A_1}\subset \hat{A_2}$}
-  \label{fig:AffineA2A1Fan}
 \end{figure}
@@
   \label{eq:43}
-  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)]}.
-\end{equation}
-
-For the other level one dominant weights of $\hat{A}_2$ we get the trivial
+  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
+\end{equation}
+
+For the other level one irreducible modules of $\hat{A}_2$ we get the trivial
 branching 
@@
 
-Using this result the modular-invariant partition function is easily found,
+Using these results the modular-invariant partition function is easily found,
 \begin{equation}

### 2010-05-31 AffineLieAlgebras/InformalNotes/article.tex
pdf regen
Some changes
Minor changes

@@
 }
-\maketitle
+%\maketitle
 
@@
 
-It is important that the projection of some of positive roots of
+It is important that the ion of some of positive roots of
 the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the
@@
 \item Calculate the anomalous branching coefficients in the main Weyl
-  chamber of the subalgebra $\mathfrak{a}$ using the recurrent relation (\ref{recurrent-relation}).
+  chamber $\bar{C_{\mathfrak{a}}}$ of the subalgebra $\mathfrak{a}$ using the recurrent relation (\ref{recurrent-relation}).
 \end{enumerate}
@@
 
-\subsection{Affine Lie algebras}
-\label{sec:affine-lie-algebras}
-\subsubsection{Affine into affine embedding}
+\subsection{Affine into affine embedding}
 \label{sec:embedd-affine-algebr}
@@
 Here we restricted the computation to the twelfth grade.
-\begin{figure}[ph]
+\begin{figure}[h!tb]
   \centering
   \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
-  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
+  \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
   \label{fig:AffineB2A1Fan}
@@
 \ref{fig:AffineB2_A1_anom_proj}.
-\begin{figure}[h!tb]
+\begin{figure}[p]
   \centering
-  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
-  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \includegraphics[width=120mm]{AffineB2_A1_proj_anom.pdf}
+  \caption{The projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
   \label{fig:AffineB2_A1_anom_proj}
@@
 
-\begin{figure}[ph]
+\begin{figure}[p]
   \centering
-  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
+  \includegraphics[width=120mm]{AffineB2_A1_branching.pdf}
   \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
@@
 
+%\newpage
 \section{Applications to the conformal field theory}
@@
 
-The set of the anomalous weights of this representation  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade.
+The set $\widehat{\Psi^{(\omega_0)}}$  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade.
 We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.
@@
 Here we restricted the calculations to the first eight grades.
-\begin{figure}[p]
+\begin{figure}[h!tb]
   \centering
@@
 
-The next step is to project the anomalous weights to $P_{\aht A_1}$.
+The next step is to project the anomalous weights to $P_{\hat A_1}$.
 The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
@@
 Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
-\begin{figure}[ph]
+\begin{figure}[h!tb]
   \centering
@@
 
-We see that inside the main Weyl chamber of $\hat{A}_1$, which is dotted at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights.
+We see that inside $\bar{C}_{\hat{A}_1}$, which is shown at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights.
 These are the branching coefficients.
@@
 
-\begin{figure}[t]
+\begin{figure}[h!tb]
   \begin{multicols}{2}

### 2010-05-31 AffineLieAlgebras/InformalNotes/article.tex
Minor changes
Image work+typo fixes

@@
   \hline
-  $\mathfrak{g}$ & Extended diagram of the algebra $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
+  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
   \hline
@@
 we can deduce the following property of the anomalous branching coefficients,
-\begin{equation}
+\begin{multline}
   \label{eq:17}
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\quad \xi\in P_{\mathfrak{a}}.
-\end{equation}
+   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\\ \xi\in P_{\mathfrak{a}}.
+\end{multline}
 
@@
   \includegraphics[width=60mm]{B4_B2_2A1.pdf}
-  \caption{Dynkin diagrams}
+  \caption{Dynkin diagrams for the regular embedding $B_2\subset B_4$. Note the dropped node and the roots of $\mathfrak{a}_{\bot}$. }
   \label{fig:dynkin}
@@
 \begin{figure}[h!tb]
-    \includegraphics[width=150mm]{B4_B2_anom_points.pdf}
-  \caption{Anomalous weights with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
+  \centering
+    \includegraphics[width=100mm]{B4_B2_anom_points.pdf}
+  \caption{Projected weights of $\pi_{B_2}\left(\Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
   \label{fig:B4B2anom}
@@
 \begin{figure}[h!tb]
-  \includegraphics[width=130mm]{B4_B2_fan.pdf}
-  \caption{Fan for $B_2\subset B_4$}
+  \centering
+  \includegraphics[width=80mm]{B4_B2_fan.pdf}
+  \caption{The fan for $B_2\subset B_4$}
   \label{fig:B4B2Fan}
@@
 following branching coefficients:
-\begin{equation}
+\begin{multline}
   \label{eq:24}
   \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
-  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
+  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+\\
   40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}.
-\end{equation}
+\end{multline}
 
@@
 Consider the affine extension of the example \ref{sec:regul-embedd-a_1}.
-Since this embedding is regular, the level of the  subalgebra modules is equal to that of the initial module.
+Since this embedding is regular and $x_e=1$, the level of the  subalgebra modules is equal to that of the initial module.
 
@@
   \centering
-  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
+  \includegraphics[width=135mm]{AffineB2_A1_fan.pdf}
   \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
@@
 \begin{figure}[h!tb]
-  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
+  \hspace*{-2cm}
+  \includegraphics[width=200mm]{AffineB2_A1_Anom.pdf}
   \caption{The anomalous weights of the $(1,0;1;0)$ representation of the algebra $\hat{B_2}$}
@@
   \includegraphics[width=120mm]{AffineB2_A1_proj_anom.pdf}
-  \caption{The projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$ and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
   \label{fig:AffineB2_A1_anom_proj}
@@
 
-There exist three level one dominant weights in the weight space of $\hat{A}_2$.
+There exist three level one fundamental weights in the weight space of $\hat{A}_2$.
 It is easy to see that the set $\Delta_{\bot}$ is empty and the subalgebra $\mathfrak{a}_{\bot}=0$.
@@
 \begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=180mm]{AffineA2_A1_anom.pdf}
+%  \hspace*{-2cm}
+  \includegraphics[width=140mm]{AffineA2_A1_anom.pdf}
   \caption{The anomalous weights of the module $L^{(0,0;1;0)}_{\hat{A_2}}$}
@@
   \centering
-  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
-  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \includegraphics[width=130mm]{AffineA2_A1_proj_anom.pdf}
+  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$.}
   \label{fig:AffineA2_A1_anom_proj}
@@
   \centering
-  \includegraphics[width=110mm]{AffineA2_A1_branching.pdf}
+  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
   \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
@@
 
-Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\widehat{su(2)}\oplus \widehat{su(2)}$ and $\mathfrak{g}= \widehat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$.
+Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$.
 Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}.
@@
 
-We are interested in the reduction of the fundamental representations of $\widehat{su(4)}$.
-Four dominant weights of level one have the following coordinates in the orthogonal basis: 
+We are interested in the reduction of the fundamental modules of $\widehat{su(4)}$.
+Four fundamental weights of level one have the following coordinates in the orthogonal basis: 
 \begin{equation}
@@
 
-These representation could be easily reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras, but we use our general method and discuss its features.
+These modules could be easily reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras, but we use our general method and discuss its features.
 
@@
 \begin{figure}[h!tb]
-  \includegraphics[width=150mm]{A1+A1-A3_fan.pdf}
-  \caption{Fan for the special embedding $\widehat{su(2)}\oplus\widehat{su(2)}\subset \widehat{su(4)}$}
+  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
+  \caption{Fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
   \label{fig:A1+A1-A3_fan}
@@
 \begin{figure}[h!tb]
+  \hspace*{-1cm}
   \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
-  \caption{Projected anomalous weights for $L^{\omega_1}_{A_3}$}
+  \caption{Projected anomalous weights for $L^{\omega_1}_{\hat A_3}$}
   \label{fig:A1+A1-A3_anom}
@@
 
-The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,0,1;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
+The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the module of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,0,1;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
 Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$.
@@
 \begin{figure}[h!tb]
-  \includegraphics[width=180mm]{A1+A1-A3_branching.pdf}
-  \caption{Anomalous branching coefficients for $L^{(0,0,1;1;0)}_{A_3}$}
+%  \hspace*{-1cm}
+  \includegraphics[width=135mm]{A1+A1-A3_branching.pdf}
+  \caption{Anomalous branching coefficients for $L^{(0,0,1;1;0)}_{\hat A_3}$}
   \label{fig:A1+A1-A3_branching}

### 2010-05-31 AffineLieAlgebras/InformalNotes/article.tex
More pictures and typos work

@@
 
-This embedding is characterised by the embedding indexes $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
-
-We are interested in the reduction of the fundamental modules of $\widehat{su(4)}$.
+This embedding is characterised by the embedding indices $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
+
+We are interested in the reduction of the fundamental modules of $\hat A_3$.
 Four fundamental weights of level one have the following coordinates in the orthogonal basis: 
@@
   \begin{array}{lll}
-     \omega_0 & = & (0,0,0,0;1;0)\\
-     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
-     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
-     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
+     \omega_0 & = & (0,0,0,0;1;0),\\
+     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
+     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
+     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
   \end{array}
@@
   \begin{array}{lll}
-    \Delta^{+} &=&\left\{\co{\Delta}^{+};\; \co{\Delta}-n\delta;\;     -n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right. \\
-    & & \quad\left.\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\}\right\}\\
+    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
+    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
     \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm \alpha_2-n\delta;\; -n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
@@
 \label{sec:conclusion}
-We have proved that the injection fan technique can be used to deal with the nonmaximal subalgebras.
+We have shown that the injection fan technique can be used to deal with the nonmaximal subalgebras.
 It was demonstrated that in such cases in the set of positive roots $\Delta_{\mathfrak{g}}^{+}$ it is necessary to  separate an additional subset $\Delta^{+}_{\bot}$.
@@
 In particular we considered the construction modular-invariant partition functions in the conformal field theory in the framework of conformal embedding method.
-This  method is widely used in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
+This  method is useful in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
+
+The proposed general approach to the reduction problem has the additional applications in the study of the integrable chains. We will consider those in the upcoming publications.
 

### 2010-06-01 AffineLieAlgebras/InformalNotes/talk.tex
Modular section decreased

@@
 \begin{document}
-\thispagestyle{empty}
-
-\begin{center}
-{\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
-\end{center}
-\vskip 1 cm
-\begin{flushright}
-{\large \bf SPbU-IP-09-08}
-\end{flushright}
-\hfill {}
-\vskip 1 cm
-\begin{center}
-{\Huge \bf Recursive algorithms, branching coefficients \\ for affine algebras and applications\\[0.5cm]
-}
-\end{center}
-\vskip 1.0 cm
-\begin{center}
-{\Large \bf
-Vladimir Lyakhovsky\\[2mm]
-Anton Nazarov}
-\end{center}
-\vfill
-\begin{center}
-{\large Department of Theoretical Physics\\
-}
-\end{center}
-\vfill
-\begin{center}
-SAINT-PETERSBURG \\
-2009
-\end{center}
-
-\newpage
 
@@
 \begin{abstract}
+Примерный текст доклада на семинаре кафедры ФВЭиЭЧ по работе ``Recursive algorithms, branching coefficients and applications''.
 \end{abstract}
@@
 коэффициентов этого разложения.
+Конечно же эта задача уже решалась, существует способ решения ``в лоб'', требующий построения всех представлений и различные способы, которые работают для частных случаев, например, многое упрощается в физически интересном случае конформных вложений.
+Мы предлагаем общий метод, но иллюстрировать его будем физическими примерами (которые можно вычислять и другими способами).
 
@@
 
-Двумерная конформная теория поля --- это теория поля, определенная на двумерном пространстве-времени
-и обладающая инвариантностью относительно следующих преобразований:
+Конформное преобразование --- это преобразование, меняющее только масштаб у метрического тензора:
+\begin{equation}
+  \label{eq:10}
+  g'_{\mu\nu}(x')=\Lambda(x)g_{\mu\nu}(x)
+\end{equation}
+
+Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований. В $D$-мерном случае генераторы у таких преобразований следующие:
 \begin{align}
@@
 \end{align}
-=====
-Подробнее обсудить бесконечномерность.
-=====
+На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
+В двумерном случае существует бесконечное число локально-конформных преобразований.
+Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это условие эквивалентно уравнению Коши-Римана для голоморфных функций.
 
-На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
 В этом случае конформная группа --- это набор всех аналитических функций $w(z)$ на плоскости.
-
-В двумерной конформной теории поля тензор энергии-импульса бесследовый.
 
@@
 $\frac{c}{12}(m^3-m)\delta_{m+n,0}$. В результате получаем алгебру Вирасоро.
+В двумерной конформной теории поля тензор энергии-импульса бесследовый.
 
@@
 Если мы изучаем конформную теорию поля на плоскости или на сфере, то мы можем рассматривать
-голоморфный и антиголоморфный сектора независимо. Если говорить о WZW-моделях, то примарные поля
+голоморфный и антиголоморфный сектора независимо. В WZW-моделях примарные поля
 принадлежат тензорному произведению неприводимых представлений аффинной алгебры.
@@
 
-Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
-Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
-выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
-вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
-обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
-параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
-Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
-параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
-статсумма дается следом оператора сдвига в степени $m$:
-\begin{equation}
-  \label{eq:6}
-  Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
-\end{equation}
-Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
-конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
-$H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
-$L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
-$P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
-можно записать в виде
-\begin{equation}
-  \label{eq:7}
-  \begin{split}
-      Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
-      L_0)\}\\
-      =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
-  \end{split}
-\end{equation}
-Или, если ввести $q=\exp 2\pi i \tau$
-\begin{equation}
-  \label{eq:2}
-  Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
-\end{equation}
-Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
-
-Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
-эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
-
+%% Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
+%% Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
+%% выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
+%% вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
+%% обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
+%% параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
+%% Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
+%% параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
+%% статсумма дается следом оператора сдвига в степени $m$:
+%% \begin{equation}
+%%   \label{eq:6}
+%%   Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
+%% \end{equation}
+%% Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
+%% конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
+%% $H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
+%% $L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
+%% $P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
+%% можно записать в виде
+%% \begin{equation}
+%%   \label{eq:7}
+%%   \begin{split}
+%%       Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
+%%       L_0)\}\\
+%%       =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
+%%   \end{split}
+%% \end{equation}
+%% Или, если ввести $q=\exp 2\pi i \tau$
+%% \begin{equation}
+%%   \label{eq:2}
+%%   Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
+%% \end{equation}
+%% Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
+%% 
+%% Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
+%% эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
+%% 
 Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
@@
 
-Комплексная структура такого тора конформно эквивалентна тору, для которого соотношения
+Комплексная структура тора конформно эквивалентна тору, для которого соотношения
 эквивалентности записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
 $\mathbb{C}$.
-
-Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
-конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
-$SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
-\begin{equation}
-  \label{eq:99} A=
-  \begin{pmatrix} a & b\\ c & d
-  \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
-\end{equation}
-и матрицы $A$ и $-A$ действуют одинаково на $\tau$
-\begin{equation}
-  \label{eq:100} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
-\end{equation}
-$\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
-модулярной группой.
-
+%% 
+%% Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
+%% конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
+%% $SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
+%% \begin{equation}
+%%   \label{eq:99} A=
+%%   \begin{pmatrix} a & b\\ c & d
+%%   \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+%% \end{equation}
+%% и матрицы $A$ и $-A$ действуют одинаково на $\tau$
+%% \begin{equation}
+%%   \label{eq:100} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+%% \end{equation}
+%% $\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
+%% модулярной группой.
+%% 
 Конформная теория поля задаётся примарными полями $\Phi_a$ с конформными размерностями $\Delta_a$:
@@
 представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсуммы на торе
-(\ref{eq:2}) может быть переписана в виде
+(\ref{eq:2}) может быть записана в виде
 \begin{equation}
@@
 
-Простейшим модулярный инвариант можно записать следующим образом:
+Простейший модулярный инвариант можно записать следующим образом:
 \begin{equation}
@@
 Здесь суммирование ведется по всем конформным семействам (то есть по всем представлениям алгебры
-$\mathfrak{g}$). Представления алгебры можно рассматривать как сумму представлений подалгебры.
+$\mathfrak{g}$).
+
+Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно.
+(Я сейчас поясню, что это значит).
+
+Представления алгебры можно рассматривать как сумму представлений подалгебры.
 
@@
 и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится.
+То есть из диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый не диагональный инвариант для подалгебры $\mathfrak{a}$.
 Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
@@
 работе была решена данная проблема и предложено обобщение рекуррентных соотношений на данный случай.
+
+Общая идея метода в следующем:
 
@@
 
+\section{Замечания}
+\label{sec:notes}
+
+1. Модулярную инвариантность рассказать удовлетворительно не удастся,
+и по времени тоже не удастся. Следовательно, её кратко помянуть и
+постулировать выражение (46). Все, что до стр 10, рассказать.
+Слушатель должен быть убежден в том, что модули афф. алгебры
+фигурируют в искомом выражении.
+2. Нуждается в обосновании сама постановка вопроса о редукции в
+этих теориях. Иначе появление подалгебры ничем не обосновано.
+3. Необходимо сказать об общей идеологии веера вложений.
+Ведь дотошно объяснить все на примере формулы (53) вряд ли
+возможно. Значит надо объяснить идею.
+
+Мелкие замечания:
+1.стр.1
+"Наша задача   придумать практический алгоритм
+вычисления коэффициентов этого разложения."
+
+Придется 2 слова сказать о том, что мы не первые
+решаем эту задачу, мы решаем её новыми методами,
+эффективность таких методов выше и т.п.
+
+2.стр.2
+"В этом случае конформная группа   это набор всех ана-
+литических функций w(z) на плоскости."
+
+Как это понимать?
+
+3.стр.3
+"Все поля в теории оказываются суммами мультиплетов алгебры Вирасо-
+ро."
+
+Все поля в теории вполне приводимы и разлагаются в прямую сумму
+подпространств, инвариантных относительно алгебры Вирасо-
+ро.
+
+4.стр.3
+Про "аномальные размерности" ничего не было сказано.
+
+5.стр.
+"Он определен на трехмерном многообразии B, ограниченном исходным
+двумерным пространством."
+Это должно быть сказано в начале параграфа.
+
+6.стр.4
+"Разность значений члена Весса-
+Зумино на этих многообразиях дается правой частью уравнения (10)
+с интегралом, продолженным на все компактное трехмерное простран-
+ство."
+
+Осталось неясно, может нарисовать?
+
+7.стр.5
+"для полного действия (42):"
+
+Уж наверное не 42, а 8?
+
+8.стр.6
+
+формулы (30) и (31) непонятны.
+
+9.стр.
+"hv - дуальное число Кокстера."
+
+Дать явное выражение.
+
+10.стр.7
+"бесконечномерные и неинтегрируемые поля отщепляют-
+ся в корреляционных функциях."
+
+Что это значит?
+
+11.
+"Представления алгебры можно рас-
+сматривать как сумму представлений подалгебры."
+
+Откуда взялась подалгебра?
+
 \end{document}

### 2010-06-01 AffineLieAlgebras/InformalNotes/article.tex

@@
 Let's describe the reduction of the fundamental representation of $B_2$ with the highest weight equal to $(1,0)$ (in the fundamental weight basis), it is drawn as the black vector in the Figure \ref{fig:B2_A1}.
-\begin{figure}[ph]
+\begin{figure}[th]
   \noindent\centering{
-    \includegraphics[width=90mm]{B2_A1.pdf}
+    \includegraphics[width=80mm]{B2_A1.pdf}
   }
@@
 Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
-\begin{figure}[ph]
+\begin{figure}[t]
   \noindent\centering{
-    \includegraphics[width=90mm]{B2_A1_2.pdf}
+    \includegraphics[width=80mm]{B2_A1_2.pdf}
   }
-  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
+  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules for the embedding $A_1\subset B_2$}
   \label{fig:B2_A1_2}
@@
 The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
-\begin{figure}[ph]
+\begin{figure}[h]
   \centering
-  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
+  \includegraphics[width=50mm]{B4_B2_2A1.pdf}
   \caption{Dynkin diagrams for the regular embedding $B_2\subset B_4$. Note the dropped node and the roots of $\mathfrak{a}_{\bot}$. }
@@
 The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.
-\begin{figure}[h!tb]
+\begin{figure}[p]
   \centering
-    \includegraphics[width=100mm]{B4_B2_anom_points.pdf}
+    \includegraphics[width=90mm,height=90mm]{B4_B2_anom_points.pdf}
   \caption{Projected weights of $\pi_{B_2}\left(\Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
@@
 
-\begin{figure}[h!tb]
+\begin{figure}[p]
   \centering
-  \includegraphics[width=80mm]{B4_B2_fan.pdf}
+  \includegraphics[width=80mm,height=80mm]{B4_B2_fan.pdf}
   \caption{The fan for $B_2\subset B_4$}

### 2010-06-01 AffineLieAlgebras/InformalNotes/talk.tex

@@
 
-Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований. В $D$-мерном случае генераторы у таких преобразований следующие:
-\begin{align}
-  \label{eq:1}
-  & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\
-  &P_\mu \equiv-i\partial_\mu \,, \\
-  &D \equiv-ix_\mu\partial^\mu \,, \\
-  &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,,
-\end{align}
+Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований.
+
+%% В $D$-мерном случае генераторы у таких преобразований следующие:
+%% \begin{align}
+%%   \label{eq:1}
+%%   & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\
+%%   &P_\mu \equiv-i\partial_\mu \,, \\
+%%   &D \equiv-ix_\mu\partial^\mu \,, \\
+%%   &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,,
+%% \end{align}
+%% 
 На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
 В двумерном случае существует бесконечное число локально-конформных преобразований.
-Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это условие эквивалентно уравнению Коши-Римана для голоморфных функций.
+Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это условие эквивалентно уравнению Коши-Римана для голоморфных функций ($\partial_{\bar z}w(z,\bar z)=0$).
 
@@
 \begin{equation}
-  \label{eq:4}
+  \label{eq:9}
     Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)

### 2010-06-03 AffineLieAlgebras/InformalNotes/talk.tex
PDF added to git
Some work on text

@@
 
-Даны две аффинные алгебры Ли $\mathfrak{a}\subset \mathfrak{g}$. Неприводимое представление
-$L^{(\mu)}_{\mathfrak{g}}$ алгебры $\mathfrak{g}$ со старшим весом $\mu$ может быть разложено на
-представления подалгебры $\mathfrak{a}$. Наша задача --- придумать практический алгоритм вычисления
-коэффициентов этого разложения.
-Конечно же эта задача уже решалась, существует способ решения ``в лоб'', требующий построения всех представлений и различные способы, которые работают для частных случаев, например, многое упрощается в физически интересном случае конформных вложений.
-Мы предлагаем общий метод, но иллюстрировать его будем физическими примерами (которые можно вычислять и другими способами).
+Даны две аффинные алгебры Ли $\mathfrak{a}\subset \mathfrak{g}$. Аффинные алгебры Ли --- это особый
+класс бесконечномерных алгебр, которые строятся из конечномерных (полу)простых алгебр Ли, как
+центральные расширения алгебр петель. Более подробное определение будет дано позже. Неприводимое
+представление $L^{(\mu)}_{\mathfrak{g}}$ аффинной алгебры $\mathfrak{g}$ со старшим весом $\mu$
+может быть разложено на представления подалгебры $\mathfrak{a}$. Наша задача --- придумать
+практический алгоритм вычисления коэффициентов этого разложения. Конечно же эта задача уже решалась,
+например, существует способ решения ``в лоб'', требующий построения всех представлений и различные способы,
+которые работают для частных случаев, например, многое упрощается в физически интересном случае
+конформных вложений. Мы предлагаем общий метод, но иллюстрировать его будем как-раз физическими
+примерами конформных вложений.
 
@@
 
-В теории струн двумерная конформная теория поля описывает динамику на мировой поверхности, а в
-теории критических явлений --- фазовые переходы в двумерных системах.
-
 Конформное преобразование --- это преобразование, меняющее только масштаб у метрического тензора:
@@
 Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований.
+
+В теории струн двумерная конформная теория поля описывает динамику на мировой поверхности, а в
+теории критических явлений --- фазовые переходы в двумерных системах.
 
@@
 В двумерном случае существует бесконечное число локально-конформных преобразований.
-Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это условие эквивалентно уравнению Коши-Римана для голоморфных функций ($\partial_{\bar z}w(z,\bar z)=0$).
+Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это
+условие эквивалентно уравнению Коши-Римана для голоморфных функций ($\partial_{\bar z}w(z,\bar
+z)=0$).
 
-В этом случае конформная группа --- это набор всех аналитических функций $w(z)$ на плоскости.
+Таким образом локально-конформные преобразования находятся в однозначном соответствии с множеством
+всех аналитических функций $w(z)$ на плоскости.
 
-Для классической теории алгебра конформных преобразований --- это алгебра Витта, которая порождается
-генераторами $\{L_n, n\in \mathbb{Z}\}$ --- модами разложения оператора энергии-импульса $T$, с
+Глобальные конформные преобразования имеют вид $f(z)=\frac{az+b}{cz+d},\; ad-bc=1$.
+
+Рассмотрим инфинитезимальные преобразования $w(z)=z+\epsilon(z),\quad
+\epsilon(z)=\sum_{-\infty}^{\infty}c_nz^{n+1}$. 
+Тогда для без-спинового поля $\phi(z,\bar z)$ верно следующее: $\phi'(z',\bar z')=\phi(z,\bar z)$,
+$\delta\phi=-\epsilon(z)\partial\phi-\bar \epsilon(\bar z)\bar \partial \phi=\sum_n(c_n L_n\phi+\bar
+c_n\bar L_n\phi)$, где $L_n=-z^{n+1}\partial_z,\quad \bar L_n=-\bar z^{n+1}\partial_{\bar z}$
+
+Мы видим, что в классической теории алгебра конформных преобразований --- это алгебра Витта, которая
+порождается генераторами $\{L_n, n\in \mathbb{Z}\}$ --- модами разложения оператора энергии-импульса $T$, с
 коммутационными соотношениями
@@
 $\frac{c}{12}(m^3-m)\delta_{m+n,0}$. В результате получаем алгебру Вирасоро.
-В двумерной конформной теории поля тензор энергии-импульса бесследовый.
+
+(Про тензор энергии-импульса:
+$x^{\mu}\to x^{\mu}+\epsilon^{\mu}\Rightarrow \delta S=\int d^2 x
+T^{\mu\nu}\partial_{\mu}\epsilon_{\nu}=
+\frac{1}{2}\int d^2 xT_{\mu}^{\mu}\partial_{\rho}\epsilon^{\rho}$
+В двумерной конформной теории поля тензор энергии-импульса бесследовый).
 
@@
 \end{equation}
-Все поля в теории оказываются суммами мультиплетов алгебры Вирасоро.
+Все поля в теории оказываются суммами произведений элементов мультиплетов алгебры Вирасоро.
 
 При некоторых дополнительных предположениях двумерную конформную теорию можно построить и решить
-полностью, если определен набор примарных полей и аномальных размерностей.
+полностью, если определен набор примарных полей и конформных размерностей.
 
@@
 WZW-модели обладают дополнительной симметрией. Алгебра токов в них --- это алгебра Каца-Муди
-(аффинная алгебра Ли $\mathfrak{g}$), а полная киральная алгебра --- полупрямое произведение
-$Vir\ltimes \mathfrak{g}$.
+(аффинная алгебра Ли $\mathfrak{g}$), полная киральная алгебра --- полупрямое произведение
+$Vir\ltimes \mathfrak{g}$, примарные поля преобразуются по неприводимым представлениям алгебры $\mathfrak{g}$.
 
@@
 компактифицированном трехмерном пространстве компактное двумерное многообразие разделяет два
-трехмерных многообразия. Разность значений члена Весса-Зумино $\Delta\Gamma$ на этих многообразиях
+трехмерных многообразия.
+\begin{figure}[h]
+ \centering
+  \includegraphics[width=100mm]{fig3.pdf}  
+  \caption{Два продолжения поля на трехмерное многообразие}
+  \label{fig:1}
+\end{figure}
+
+Разность значений члена Весса-Зумино $\Delta\Gamma$ на этих многообразиях
 дается правой частью уравнения (\ref{eq:73}) с интегралом, продолженным на все компактное трехмерное
@@
 \end{equation}
-Тогда вариация действия при инфинитезимальных преобразованиях $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ дается выражением
+ При инфинитезимальных преобразованиях $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ вариация
+ $\delta_{\omega}g=\omega g$, а вариация действия
+ \begin{equation}
+   \label{eq:11}
+   \delta S=-\frac{1}{2\pi}\int d^2 x \left(\partial_{\bar z}Tr(\omega(z)J(z))+\partial_z Tr(\bar
+     \omega(\bar z)\bar J(\bar z))\right)
+ \end{equation}
+Заменяем $d^2 x=-\frac{i}{2} dz d\bar z$, интегрируем по частям и переходим к интегралу по контуру, замыкая
+контур в разных направлениях для голоморфной и антиголоморфной частей.
+Тогда вариация действия
 \begin{equation}
@@
 \end{equation}
-Для токов имеем
+Для токов из явного вида тока и формулы для преобразования $g$ имеем
 \begin{equation}
@@
 \end{equation}
-Операторное разложение для токов имеет вид
+Если это подставить в тождество Уорда, то получаем операторное разложение для токов, которое имеет
+вид 
 \begin{equation}
@@
 \end{equation}
-Здесь $h^v$ - дуальное число Кокстера.
+Здесь $h^v$ - дуальное число Кокстера. $h^v=\sum_i \alpha_i^v +1=\frac{1}{2}(\Theta,\Theta+2\rho)$
 
@@
 \end{equation}
-Легко видеть, что действие генераторов алгебры Вирасоро имеет вид
+Все вторичные состояния имеют вид
+\begin{equation}
+  \label{eq:97}
+  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
+\end{equation}
+
+Легко видеть, что действие генераторов алгебры Вирасоро на примарные поляимеет вид
 \begin{equation}
@@
 
-Примарные поля живут в интегрируемых конечномерных представлениях, так как бесконечномерные и
-неинтегрируемые поля отщепляются в корреляционных функциях.
-
-Все вторичные состояния имеют вид
-\begin{equation}
-  \label{eq:97}
-  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
-\end{equation}
+Примарные поля преобразуются  интегрируемыми конечномерными представлениями, а бесконечномерные и
+неинтегрируемые поля зануляют корреляционные функции.
+В WZW-моделях примарные поля
+принадлежат тензорному произведению неприводимых представлений аффинной алгебры, так как есть
+голоморфный и антиголоморфный сектора.
 
@@
 
-Если мы изучаем конформную теорию поля на плоскости или на сфере, то мы можем рассматривать
-голоморфный и антиголоморфный сектора независимо. В WZW-моделях примарные поля
-принадлежат тензорному произведению неприводимых представлений аффинной алгебры.
-
+При изучении конформной теории поля на плоскости или на сфере 
+голоморфный и антиголоморфный сектора можно рассматривать независимо. 
 Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть
@@
 взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно) чтобы теория была определена на торе.
+
+(Нарисовать картинку штанов).
 
@@
 
-Комплексная структура тора конформно эквивалентна тору, для которого соотношения
-эквивалентности записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
+При помощи конформных преобразований можно перейти к таким координатам, в которых
+эквивалентности для тора (граничные условия) записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
 $\mathbb{C}$.
@@
 \end{equation}
+Здесь имеется в виду перечисление полей по мультиплетам алгебры Вирасоро и характеры, которые
+связаны с ее генераторами. В WZW-моделях, однако, поля можно перечислять по мультиплетам аффинной
+алгебры. Это нам будет полезно в дальнейшем.
+
 Характеры переходят друг в друга при модулярных преобразованиях:
@@
 \end{equation}
-где $S$ и $T$ --- постоянные матрицы. Это верно для большого класса конформных теорий
-поля.
+где $S$ и $T$ --- постоянные матрицы.
 
@@
 
-Если мы рассмотрим редукцию характеров
+Если мы рассмотрим редукцию характеров аффинной алгебры
 \begin{equation}
@@
 \end{equation}
-и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится.
-То есть из диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый не диагональный инвариант для подалгебры $\mathfrak{a}$.
-Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
+и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится. То есть из
+диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый не диагональный инвариант для
+подалгебры $\mathfrak{a}$. Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
 ней конформная инвариантность.
@@
 
-Пусть $X^{a_j}_{-n_j}$ и $\tilde{X}^{a'_j}_{-n_j}$ --- понижающие операторы алгебр  $\mathfrak{g}$ и
+Пусть $J^{a_j}_{-n_j}$ и $\tilde{J}^{a'_j}_{-n_j}$ --- понижающие операторы алгебр  $\mathfrak{g}$ и
 $\mathfrak{a}\subset\mathfrak{g}$.  $\pi_{\mathfrak{a}}$ --- проекционный оператор
@@
   \label{eq:109}
-  X^{a_1}_{-n_1}X^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
 \end{equation}
-Вакуум $\mathfrak{g}$-инвариантен, то есть $X_0^a\left|0\right>=0$. При проекции на подалгебру
+Вакуум $\mathfrak{g}$-инвариантен, то есть $J_0^a\left|0\right>=0$. При проекции на подалгебру
 $\mathfrak{a}$ состояния примут вид
@@
   \label{eq:110}
-  \tilde{X}^{a'_1}_{-n_1}\tilde{X}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
+  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
 \end{equation}
@@
 энергии-импульса в общем случае это не так. Поэтому тензор энергии-импульса большей теории должен
-состоять только из генераторов $\tilde{X}$. Тогда $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow
+состоять только из генераторов $\tilde{J}$. Тогда $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow
 c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению

### 2010-06-04 AffineLieAlgebras/InformalNotes/talk.tex
2 strings of text added :)
Old notes removed

@@
 
-Общая идея метода в следующем:
+Общая идея метода состоит в том, чтобы разделить описание ветвления на две части --- описание
+вложения и описание представления, которое раскладывается. Затем каждая из частей описывается
 
@@
 +\gamma }^{\left( \mu \right) }\right)
+
   \end{array}
@@
 
-1. Модулярную инвариантность рассказать удовлетворительно не удастся,
-и по времени тоже не удастся. Следовательно, её кратко помянуть и
-постулировать выражение (46). Все, что до стр 10, рассказать.
-Слушатель должен быть убежден в том, что модули афф. алгебры
-фигурируют в искомом выражении.
-2. Нуждается в обосновании сама постановка вопроса о редукции в
-этих теориях. Иначе появление подалгебры ничем не обосновано.
 3. Необходимо сказать об общей идеологии веера вложений.
@@
 Мелкие замечания:
-1.стр.1
-"Наша задача   придумать практический алгоритм
-вычисления коэффициентов этого разложения."
-
-Придется 2 слова сказать о том, что мы не первые
-решаем эту задачу, мы решаем её новыми методами,
-эффективность таких методов выше и т.п.
-
-2.стр.2
-"В этом случае конформная группа   это набор всех ана-
-литических функций w(z) на плоскости."
-
-Как это понимать?
 
@@
 ро.
-
-4.стр.3
-Про "аномальные размерности" ничего не было сказано.
-
-5.стр.
-"Он определен на трехмерном многообразии B, ограниченном исходным
-двумерным пространством."
-Это должно быть сказано в начале параграфа.
-
-6.стр.4
-"Разность значений члена Весса-
-Зумино на этих многообразиях дается правой частью уравнения (10)
-с интегралом, продолженным на все компактное трехмерное простран-
-ство."
-
-Осталось неясно, может нарисовать?
-
-7.стр.5
-"для полного действия (42):"
-
-Уж наверное не 42, а 8?
-
 8.стр.6
@@
 формулы (30) и (31) непонятны.
-
-9.стр.
-"hv - дуальное число Кокстера."
-
-Дать явное выражение.
-
-10.стр.7
-"бесконечномерные и неинтегрируемые поля отщепляют-
-ся в корреляционных функциях."
-
-Что это значит?
-
-11.
-"Представления алгебры можно рас-
-сматривать как сумму представлений подалгебры."
-
-Откуда взялась подалгебра?
-
 \end{document}

### 2010-06-06 AffineLieAlgebras/InformalNotes/talk.tex
Text mostly completed, picture work is required

@@
 
-%\usepackage{verbatim} 
-\newenvironment{comment}
-{\par\noindent{\bf TODO}\\}
-{\\\hfill$\scriptstyle\blacksquare$\par}
+\usepackage{verbatim} 
+%\newenvironment{comment}
+%{\par\noindent{\bf Для заинтересованных читателей}\\}
+%{\\\setlength{10cm}\\\hfill$\scriptstyle\blacksquare$\par}
 
@@
 коэффициентов ветвления. Однако исходный алгоритм не работал для не максимальных вложений. В данной
-работе была решена данная проблема и предложено обобщение рекуррентных соотношений на данный случай.
+работе была решена данная проблема и предложено обобщение рекуррентных соотношений.
 
-Общая идея метода состоит в том, чтобы разделить описание ветвления на две части --- описание
-вложения и описание представления, которое раскладывается. Затем каждая из частей описывается
+Используя формулу Вейля-Каца мы выделяем два набора элементов в весовом пространстве. Первый набор $\Gamma$
+называется веером и описывает вложение подалгебры $\mathfrak{a}$ в алгебру $\mathfrak{g}$. Веер
+универсален, в том смысле, что он может быть использован для разложения любого из представлений.
+Другой набор элементов весового пространства $\Psi ^{\left( \mu \right) }$ называется набором
+аномальных весов. Он описывает раскладываемое представление без явного его построения.
 
-В результате рекуррентные соотношения имеют вид
+После этого процесс вычисления коэффициентов ветвления можно реализовать при помощи следующей
+рекуррентной формулы:
 \begin{equation}
@@
 к корневой системе подалгебры  $\mathfrak{a}$, $W_{\bot}$ --- соответствующая этим корням группа Вейля,
-$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ --- набор весов в разложении знаменателя $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
+$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ --- веер --- набор весов в разложении знаменателя $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
 (1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$, а $s(\gamma)$ ---
 коэффициент при  $e^{\gamma}$ в этом разложении.
+
+Набор аномальных весов $\Psi^{(\mu)}$ дает член с $\delta$-символом.
 
@@
 \end{enumerate}
+
+Сейчас я поясню всю процедуру на примере редукции представления простой алгебры $B_2$ ($so(5)$) на
+подалгебру $A_1$ ($so(3)$), а потом расскажу про аффинные алгебры Ли.
 
@@
 вложение является аффинным расширением специального вложения конечномерных алгебр Ли $su(2)\oplus
-su(2)\subset su(4)$. Это специальное вложение строится следующим образом: берем четырехмерное
+su(2)\subset su(4)$.
+\begin{comment}
+ Это специальное вложение строится следующим образом: берем четырехмерное
 представление $su(2)\oplus su(2)$ со старшим весом $(1,1)$. Вот веса этого представления
@@
 даются выражениями
-$d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$, так что $d(b_1)=\mathrm{diag}(1,-1,1,-1),\;
-d(b_2)=\mathrm{diag}(1,1,-1,-1)$.  Отсюда вложенные корни $\alpha_1,\alpha_2$ of $su(2)\oplus su(2)$
+\begin{equation}
+  d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right),
+\end{equation}
+так что $d(b_1)=\mathrm{diag}(1,-1,1,-1),\;
+  d(b_2)=\mathrm{diag}(1,1,-1,-1).$
+\end{comment}
+Вложенные корни $\alpha_1,\alpha_2$ of $su(2)\oplus su(2)$
 выражаются через корни $\tilde{\alpha}_i$ алгебры  $su(4)$
@@
 \end{equation}
+\begin{comment}
 Они изображены на рисунке \ref{fig:A1+A1-A3}.
+\end{comment}
 
@@
 
-\section{Замечания}
-\label{sec:notes}
-
-3. Необходимо сказать об общей идеологии веера вложений.
-Ведь дотошно объяснить все на примере формулы (53) вряд ли
-возможно. Значит надо объяснить идею.
-
-Мелкие замечания:
-
-3.стр.3
-"Все поля в теории оказываются суммами мультиплетов алгебры Вирасо-
-ро."
-
-Все поля в теории вполне приводимы и разлагаются в прямую сумму
-подпространств, инвариантных относительно алгебры Вирасо-
-ро.
-8.стр.6
-
-формулы (30) и (31) непонятны.
 \end{document}

### 2010-06-07 AffineLieAlgebras/InformalNotes/talk.tex
Talk is completed, but too long, so the shorter veriosn is to appear.

@@
 \usepackage{color}
-\usepackage[pdftex]{graphicx}
+%\usepackage[pdftex]{graphicx}
+\usepackage{graphicx}
 \pagestyle{plain}
@@
   \label{eq:5}
-  S_0=\frac{1}{4a^2}\int_{\partial B} d^2x\; Tr (\partial^{\mu}g^{-1}\partial_{\mu}g),
+  S_0=\frac{1}{4a^2}\int_{S^2} d^2x\; Tr (\partial^{\mu}g^{-1}\partial_{\mu}g),
 \end{equation}
 где $a^2>0$ - положительный параметр, $g(x)\in G$ - поле со значениями в группе $G$, которую мы
-будем считать полупростой.
+будем считать полупростой. Действие задается на комплексной плоскости с бесконечностью, которая
+топологически эквивалентна 2-сфере.
 
@@
     \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
-    \left[L_n,J^a_m\right]=-mJ^a_{n+m}
+    c=\frac{k\;\mathrm{dim}g}{k+h^v}\\
+    \left[L_n,J^a_m\right]=-mJ^a_{n+m}.
   \end{aligned}
@@
 
-При помощи конформных преобразований можно перейти к таким координатам, в которых
+При помощи конформных преобразований можно перейти к таким координатам, в которых соотношения
 эквивалентности для тора (граничные условия) записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
@@
 %% 
-Конформная теория поля задаётся примарными полями $\Phi_a$ с конформными размерностями $\Delta_a$:
-\begin{equation}
-  \label{eq:3}
-  \begin{split} \Phi_{a}(z)\underset{z\to w(z)}{\longrightarrow}
-\left(\frac{dw}{dz}\right)^{\Delta_a}\Phi_{a}(w(z))\\ L_n \Phi_a=0,\quad n>0\\ L_0 \Phi_a=\Delta_a
-\Phi_a\\
-  \end{split}
-\end{equation}
+Конформная теория поля задаётся примарными полями $\Phi_a$ с конформными размерностями $\Delta_a$.
 
@@
 произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
-представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсуммы на торе
+представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсумма на торе
 (\ref{eq:2}) может быть записана в виде
@@
 \end{equation}
-где $\chi_j$ --- характер представления $\mathcal{H}_j$,
+где $\chi_j$ --- нормализованный характер представления $\mathcal{H}_j$,
 \begin{equation}
@@
 \end{equation}
-Здесь имеется в виду перечисление полей по мультиплетам алгебры Вирасоро и характеры, которые
-связаны с ее генераторами. В WZW-моделях, однако, поля можно перечислять по мультиплетам аффинной
-алгебры. Это нам будет полезно в дальнейшем.
 
@@
 Здесь суммирование ведется по всем конформным семействам (то есть по всем представлениям алгебры
-$\mathfrak{g}$).
+$\mathfrak{a}$).
 
-Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно.
-(Я сейчас поясню, что это значит).
+Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует
+алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно. (Я сейчас поясню, что это
+значит).
 
@@
 ней конформная инвариантность.
-
-Для этого требуется, чтобы вложение подалгебры было ``конформным'', то есть центральные заряды
-теорий должны совпадать.
-\begin{equation}
-  \label{eq:31}
-  c(\mathfrak{a})=c(\mathfrak{g})
-\end{equation}
 
@@
 к корневой системе подалгебры  $\mathfrak{a}$, $W_{\bot}$ --- соответствующая этим корням группа Вейля,
-$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ --- веер --- набор весов в разложении знаменателя $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
-(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$, а $s(\gamma)$ ---
+$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ --- веер --- набор весов в разложении знаменателя $$\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
+(1-e^{-\pi_{\mathfrak{a}}(\alpha)})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\pi_{\mathfrak{a}}(\alpha))}$$, а $s(\gamma)$ ---
 коэффициент при  $e^{\gamma}$ в этом разложении.
@@
   }
-  \caption{Regular embedding of $A_1$ into $B_2$}
+  \caption{Регулярное вложение $A_1$ в $B_2$}
   \label{fig:B2_A1}
@@
   }
-  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
+  \caption{Аномальные веса и соответствующие $\mathfrak{a}_{\bot}=A_1$-модули}
   \label{fig:B2_A1_2}
@@
 Рассмотрим такое вложение $\mathfrak{a}\subset \mathfrak{g}$, где
-$\mathfrak{a}=\widehat{su(2)}\oplus \widehat{su(2)}$, а $\mathfrak{g}= \widehat{su(4)}$. Это
-вложение является аффинным расширением специального вложения конечномерных алгебр Ли $su(2)\oplus
-su(2)\subset su(4)$.
+$\mathfrak{a}=\hat{A_1}\oplus \hat{A_1}$, а $\mathfrak{g}= \hat{A_3}$. Это
+вложение является аффинным расширением специального вложения конечномерных алгебр Ли $A_1\oplus
+A_1\subset A3$. ($su(2)\oplus su(2)\subset su(4)$).
 \begin{comment}
  Это специальное вложение строится следующим образом: берем четырехмерное
-представление $su(2)\oplus su(2)$ со старшим весом $(1,1)$. Вот веса этого представления
+представление $A_1\oplus A_1$ со старшим весом $(1,1)$. Вот веса этого представления
 \ref{fig:A_1+A_1_to_A3}, их координаты в базисе фундаментальных весов: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
@@
     \hfill
-    \caption{Representation for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
+    \caption{Представление для специального вложения $A_1\oplus A_1\subset A3$}
     \label{fig:A_1+A_1_to_A3}
@@
     \hfill
-    \caption{Embedded roots for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
+    \caption{Вложенные корни $A_1\oplus A_1\subset A3$}
     \label{fig:A1+A1-A3}
@@
 \end{comment}
-Вложенные корни $\alpha_1,\alpha_2$ of $su(2)\oplus su(2)$
-выражаются через корни $\tilde{\alpha}_i$ алгебры  $su(4)$
+Вложенные корни $\alpha_1,\alpha_2$ подалгебры $A_1\oplus A_1$
+выражаются через корни $\tilde{\alpha}_i$ алгебры  $A_3$
 \begin{equation}
@@
   \begin{array}{lll}
-    \Delta^{+} &=&\left\{\co{\Delta}^{+};\; \co{\Delta}-n\delta;\;     -n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right. \\
-    & & \quad\left.\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\}\right\}\\
-    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm \alpha_2-n\delta;\; -n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
+    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
+    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{с кратностью}\; 3;\; n=1,2,\dots,\right\}\\
+    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm
+    \alpha_2-n\delta;\; -n\delta\; \mbox{с кратностью} \; 2;\; n=1,2,\dots\}\\
   \end{array}
@@
   \includegraphics[width=150mm]{A1+A1-A3_fan.pdf}
-  \caption{Fan for the special embedding $\widehat{su(2)}\oplus\widehat{su(2)}\subset \widehat{su(4)}$}
+  \caption{Веер для специального вложения $\hat A_1\oplus\hat A_1\subset\hat A_3$}
   \label{fig:A1+A1-A3_fan}
@@
   \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
-  \caption{Projected anomalous weights for $L^{\omega_1}_{A_3}$}
+  \caption{Спроектированные аномальные веса $L^{\omega_2}_{A_3}$}
   \label{fig:A1+A1-A3_anom}
@@
 
-Аномальные коэффициенты ветвления для представления  $L^{(\omega_1)}$ вычислены при помощи
+Аномальные коэффициенты ветвления для представления  $L^{(\omega_2)}$ вычислены при помощи
 рекуррентных соотношений и показаны на рисунке \ref{fig:A1+A1-A3_branching}. 
 \begin{figure}[h!tb]
-  \includegraphics[width=180mm]{A1+A1-A3_branching.pdf}
-  \caption{Anomalous branching coefficients for $L^{(0,0,1;1;0)}_{A_3}$}
+  \hspace*{-2cm}\includegraphics[width=180mm]{A1+A1-A3_branching.pdf}
+  \caption{Аномальные коэффициенты ветвления для представления $L^{(0,1,0;1;0)}_{A_3}$}
   \label{fig:A1+A1-A3_branching}
@@
 
-Недавно мы заметили, что струнные функции, которые описывают представления, модулярные функции,
-которые описывают редукцию представлений и функции слияния, которые описывают разложение тензорных
+Функции ветвления играют важную роль в coset-моделях. Эти модели строятся путем факторизации
+WZW-модели с алгеброй $\mathfrak{g}$ по отношению к модели с подалгеброй $\mathfrak{a}$. Тут функции
+ветвления фактически описывают состояния в системе.
+
+Недавно мы заметили, что струнные функции, которые описывают представления, функции ветвления,
+описывающие редукцию представлений и функции слияния, которые описывают разложение тензорных
 произведений представлений на неприводимые, допускают построение дуальных систем функций. Эти
-дуальные функции могут быть построены просто из анализа соответствующих групп Вейля, при этом многие
-известные результаты могут быть перенесены на них, например, результаты Каца о модулярных свойствах
-струнных функций и функций ветвления. И наоборот.
-
+дуальные функции могут быть построены просто из анализа соответствующих групп и камер Вейля. 
+Задача явного построения струнных функций или функций ветвления тогда сведется к обращению матрицы.
+Явный вид функций ветвления полезен при изучении coset-моделей. Кроме того, многие
+известные результаты могут быть перенесены на дуальные функции, например, результаты Каца о модулярных свойствах
+струнных функций и функций ветвления.
 В настоящее время мы начали исследовать эти системы дуальных функций.

### 2010-06-07 AffineLieAlgebras/InformalNotes/talk.tex
Talk completed, pdf regen

@@
 
-\usepackage{verbatim} 
-%\newenvironment{comment}
-%{\par\noindent{\bf Для заинтересованных читателей}\\}
-%{\\\setlength{10cm}\\\hfill$\scriptstyle\blacksquare$\par}
+%\usepackage{verbatim} 
+\newenvironment{comment}
+{\par\noindent{\bf Для заинтересованных читателей}\\}
+{\\\setlength{10cm}\\\hfill$\scriptstyle\blacksquare$\par}
 
@@
 \epsilon(z)=\sum_{-\infty}^{\infty}c_nz^{n+1}$. 
-Тогда для без-спинового поля $\phi(z,\bar z)$ верно следующее: $\phi'(z',\bar z')=\phi(z,\bar z)$,
+Тогда для бесспинового поля $\phi(z,\bar z)$ верно следующее: $\phi'(z',\bar z')=\phi(z,\bar z)$,
 $\delta\phi=-\epsilon(z)\partial\phi-\bar \epsilon(\bar z)\bar \partial \phi=\sum_n(c_n L_n\phi+\bar
@@
 \end{equation}
-Здесь $h^v$ - дуальное число Кокстера. $h^v=\sum_i \alpha_i^v +1=\frac{1}{2}(\Theta,\Theta+2\rho)$
+Здесь $h^v$ - дуальное число Кокстера. $h^v=\sum_i \alpha_i^v +1=\frac{1}{2}(\Theta,\Theta+2\rho)$,
+а нормальное упорядочение вводится следующим образом: 
+\begin{equation}
+  \label{eq:12}
+  N(AB)(w)=\frac{1}{2\pi i}\oint\frac{dz}{z-w}A(z)B(w)
+\end{equation}
 
@@
 
-Легко видеть, что действие генераторов алгебры Вирасоро на примарные поляимеет вид
+Легко видеть, что действие генераторов алгебры Вирасоро на примарные поля имеет вид
 \begin{equation}
@@
 Веер  $\Gamma _{\frak{a}\subset \frak{g}}$ показан на рисунке \ref{fig:A1+A1-A3_fan}. Конечные координаты
-даны в базисе фундаментальных весов $su(2)\oplus su(2)$. Элемент $\gamma$ обозначен крестом, если
+даны в базисе фундаментальных весов $A_1 \oplus A_1$. Элемент $\gamma$ обозначен крестом, если
 $s(\gamma)=1$ и кругом, если $s(\gamma)=-1$.
@@
 $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ показаны на рисунке  \ref{fig:A1+A1-A3_anom}
-для $\mu=\omega_2=(0,0,1;1;0)$.
+для $\mu=\omega_2=(0,1,0;1;0)$.
 

### 2010-06-11 AffineLieAlgebras/InformalNotes/article.tex
Talk completed, pdf regen

@@
 special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}. 
-\begin{figure}[ph]
+\begin{figure}[h]
 \noindent  \centering{
-  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
+  \includegraphics[width=80mm]{special_A1_A2_A3.pdf}
   \caption{Special embedding $A_1\subset A_2\subset A_3$.
@@
   \centering
-  \includegraphics[width=80mm,height=80mm]{B4_B2_fan.pdf}
+  \includegraphics[height=80mm]{B4_B2_fan2.pdf}
   \caption{The fan for $B_2\subset B_4$}
@@
 
-Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $w_1=(1,0;1;0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the level of the weight and the fourth is the grade.
+Consider the level 1 module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $w_1=(1,0;1;0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the level of the weight and the fourth is the grade.
 
@@
   \includegraphics[width=200mm]{AffineB2_A1_Anom.pdf}
-  \caption{The anomalous weights of the $(1,0;1;0)$ representation of the algebra $\hat{B_2}$}
+  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$}.
   \label{fig:affine_B2_anom_point}
@@
 partition functions for Wess-Zumino-Novikov-Witten models of conformal field theory (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
-In these models currents algebras are affine Lie algebras.
+In these models current algebras are affine Lie algebras.
 For the construction to be valid the embedding is required to be conformal, which means that the central charge of the subalgebra is equal to the central charge of the algebra:
@@
 The complete classification of conformal embeddings is given in the paper \cite{schellekens1986conformal}.
-The requirement (\ref{eq:31}) allows to reduce the problem of finding the branching coefficients for affine Lie algebras to the computation of branching coefficients for finite-dimensional Lie algebras.
 
@@
 
-This relation and the asymptotics of the branching functions can be used to prove the finite reducibility theorem.
+This relation and the asymptotics of the branching functions can be used to prove the finite reducibility theorem \cite{kac1988modular}.
 It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
@@
 \end{equation}
-by the decompositions   $\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}$ containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules.
+by the decompositions
+\begin{equation}
+  \label{eq:32}
+\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}  
+\end{equation}
+ containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules.
 Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
@@
 But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
-
-If we limit the consideration by the affine extensions of simple classical Lie algebras, the number of possible non-maximal conformal embeddings is rather small \cite{schellekens1986conformal}.
 
@@
 
-There exist three level one fundamental weights in the weight space of $\hat{A}_2$.
+There exist three level 1 fundamental weights in the weight space of $\hat{A}_2$.
 It is easy to see that the set $\Delta_{\bot}$ is empty and the subalgebra $\mathfrak{a}_{\bot}=0$.
@@
 
-Using the definition (\ref{fan-defined})  we construct ``the fan'' $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).
+Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).
 Here we restricted the calculations to the first eight grades.
@@
 
-For the other level one irreducible modules of $\hat{A}_2$ we get the trivial
+For the other level 1 irreducible modules of $\hat{A}_2$ we get the trivial
 branching 
@@
 
-Consider the conformal embedding constructed as the affine extension  $\mathfrak{a}_{1}\oplus\mathfrak{a}_{2}\subset \mathfrak{g}$ of the embedding of semisimple subalgebra $\ao_1\oplus\ao_2$ into simple Lie algebra $\go$.
-
-Substituting the branching rules into \eqref{eq:34} we get non-diagonal mass matrix
-\begin{equation}
-  \label{eq:2}
-  M_{\lambda\xi,\mu\eta}
-\end{equation}
-where $\lambda,\mu$ are the highest weights of the representations of $\mathfrak{a}_1$ and $\xi,\eta$ of $\mathfrak{a}_2$.
-
-Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$.
-Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}.
-We start with 4-dimensional representation of $su(2)\oplus su(2)$ with the highest weight $(1,1)$.
+Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$, which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
+Let's construct the special embedding $A_1\oplus A_1\subset A_3$ using the method of \cite{vasilevich1986method}.
+We start with 4-dimensional representation of $A_1\oplus A_1$ with the highest weight $(1,1)$.
 The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
@@
     \hfill
-    \caption{Representation for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
+    \caption{Representation for the special embedding  $A_1\oplus A_1\subset A_3$}
     \label{fig:A_1+A_1_to_A3}
@@
     \hfill
-    \caption{Embedded roots for the special embedding  $su(2)\oplus su(2)\subset su(4)$}
+    \caption{Embedded roots for the special embedding  $A_1\oplus A_1\subset A_3$}
     \label{fig:A1+A1-A3}
@@
 Then for the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method}, so $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
-The embedded roots $\alpha_1,\alpha_2$ of $su(2)\oplus su(2)$ in terms of roots $\tilde{\alpha}_i$ of $su(4)$ are
+The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
 \begin{equation}
@@
 We are interested in the reduction of the fundamental modules of $\hat A_3$.
-Four fundamental weights of level one have the following coordinates in the orthogonal basis: 
+Four fundamental weights of level 1 have the following coordinates in the orthogonal basis: 
 \begin{equation}
@@
 
-These modules could be easily reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras, but we use our general method and discuss its features.
-
 For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
@@
     &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
-    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm \alpha_2-n\delta;\; -n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
+    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1+n\delta,\pm \alpha_2+n\delta;\; +n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
   \end{array}
@@
 The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}.
-Coordinates of fan element's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$.
+Coordinates of fan element's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
 Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
@@
 
-We limit our computation by the fifth grade.
+We limit our calculations by the first 5 grades.
 \begin{figure}[h!tb]
@@
   \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
-  \caption{Projected anomalous weights for $L^{\omega_1}_{\hat A_3}$}
+  \caption{Projected anomalous weights for $L^{\omega_2}_{\hat A_3}$}
   \label{fig:A1+A1-A3_anom}
@@
 
-The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the module of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,0,1;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
-Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$.
-Weight $g$ are shown by cross if the corresponding value $\epsilon(\omega)=1$ and by diamond otherwise.
-
-We omit similar pictures for $\omega_0, \omega_1,\omega_3$ and include only the branching coefficients for these modules to save the space.
-
-The anomalous branching coefficients for the module $L^{(\omega_1)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
+The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{\omega_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,1,0;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
+Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
+The weights are shown by crosses if the determinant has the value $\epsilon(\omega)=1$ and by diamonds otherwise.
+
+The diagrams for  $L^{\omega_0}_{\hat A_3}, L^{\omega_1}_{\hat A_3}, L^{\omega_1}_{\hat A_3}$ are similar to that of $L^{\omega_2}_{\hat A_3}$.
+
+The anomalous branching coefficients for the module $L^{(\omega_2)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
 \begin{figure}[h!tb]
@@
   \includegraphics[width=135mm]{A1+A1-A3_branching.pdf}
-  \caption{Anomalous branching coefficients for $L^{(0,0,1;1;0)}_{\hat A_3}$}
+  \caption{Anomalous branching coefficients for $L^{(0,1,0;1;0)}_{\hat A_3}$}
   \label{fig:A1+A1-A3_branching}
@@
 
+We have chosen this example to illustrate the mechanism of out algorithm. 
+In this case the modules could be reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras.
+We must stress that our method is universal and can be applied for an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.
+
 \section{Conclusion}
@@
 It was demonstrated that in such cases in the set of positive roots $\Delta_{\mathfrak{g}}^{+}$ it is necessary to  separate an additional subset $\Delta^{+}_{\bot}$.
-The injection fan is formed by the weights $\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+} \setminus \Delta^{+}_{\bot}$ and the additional role of the subset $\Delta^{+}_{\bot}$ is to modify the anomalous weights of the initial module.
+The injection fan is formed by the weights $\left(\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+}\right) \setminus \Delta^{+}_{\bot}$ and the additional role of the subset $\Delta^{+}_{\bot}$ is to modify the anomalous weights of the initial module.
 This modification reduces to a simple procedure: the anomalous weights are to be substituted by the dimensions of the corresponding ${\mathfrak{a}}_{\bot}$-modules.
@@
 We have demonstrated the effectiveness of the proposed generalizations of the injection fan algorithm and discussed its possible application to some physical problems.
-In particular we considered the construction modular-invariant partition functions in the conformal field theory in the framework of conformal embedding method.
+In particular we considered the construction of modular-invariant partition functions in the conformal field theory in the framework of conformal embedding method.
 This  method is useful in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
 
-The proposed general approach to the reduction problem has the additional applications in the study of the integrable chains. We will consider those in the upcoming publications.
+The proposed general approach to the reduction problem has the additional applications in the study of integrable chains.
 

### 2010-06-15 AffineLieAlgebras/InformalNotes/article.tex
Conformal embeddings rewritten. Text rearranged for the future incorporation of coset models.

@@
 \usepackage{ucs}
-\usepackage[unicode,verbose]{hyperref}
 \usepackage{amsmath,amssymb,amsthm}
@@
 \usepackage{color}
-\usepackage[pdftex]{graphicx}
+%\usepackage[pdftex]{graphicx}
+\usepackage{graphicx}
 \pagestyle{plain}
+\usepackage[unicode,verbose,plainpages=false]{hyperref}
 
@@
 \begin{document}
+\pagenumbering{alph}
 \thispagestyle{empty}
@@
 
-\section{Examples}
-\label{sec:examples}
-
-\subsection{Finite dimensional Lie algebras}
+\section{Finite dimensional Lie algebras}
 \label{sec:finite-dimens-lie}
 
-\subsubsection{Regular embedding of $A_1$ into $B_2$}
+\subsection{Regular embedding of $A_1$ into $B_2$}
 \label{sec:regul-embedd-a_1}
@@
 
-\subsubsection{Embedding of $B_2$ into $B_4$}
+\subsection{Embedding of $B_2$ into $B_4$}
 \label{sec:someth-high-dimens}
@@
   \centering
-  \includegraphics[height=80mm]{B4_B2_fan2.pdf}
+  \includegraphics[height=80mm]{B4_B2_fan.pdf}
   \caption{The fan for $B_2\subset B_4$}
@@
 
-\subsection{Affine into affine embedding}
-\label{sec:embedd-affine-algebr}
+\section{Applications to the conformal field theory}
+\label{sec:phys-appl}
+
+\subsection{Conformal embeddings}
+\label{sec:conformal-embeddings}
+
+Branching coefficients for an embedding of affine Lie subalgebra into
+affine Lie algebra can be used to construct modular invariant
+partition functions for Wess-Zumino-Novikov-Witten models of conformal field theory (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
+In these models current algebras are affine Lie algebras.
+
+The modular invariant partition function is crucial for the conformal theory to be valid on the torus and higher genus Riemann surfaces.
+It is important for the applications of CFT to the string theory and to the critical phenomena description.
+
+The simplest modular-invariant partition function has the diagonal form:
+\begin{equation}
+  \label{eq:34}
+   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
+\end{equation}
+Here the sum is over the set of the highest weights of integrable modules of WZW-model and $\chi_{\mu}(\tau)$ are the modified characters of these modules.
+
+The task of the construction of non-diagonal modular invariants is not easy. 
+Consider the Wess-Zumino-Witten model with the affine Lie algebra $\mathfrak{a}$.
+Non-diagonal modular invariants for this model can be constructed from the diagonal invariant if there exists affine algebra $\mathfrak{g}$ such that $\mathfrak{a}\subset\mathfrak{g}$.
+Then we can replace the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function (\ref{eq:36})
+by the decompositions
+\begin{equation}
+  \label{eq:32}
+\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}  
+\end{equation}
+containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules.
+Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
+\begin{equation}
+  \label{eq:36}
+   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
+\end{equation}
+The reduction of the representations is crucial in this construction.
+
+For the construction to be valid the embedding is required to preserve conformal invariance.
+Let $X^{a_j}_{-n_j}$ and $\tilde{X}^{a'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and for $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
+Let $\pi_{\mathfrak{a}}$ be the projection operator of $\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$.
+In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$ the states can be described as
+\begin{equation}
+  \label{eq:109}
+  X^{a_1}_{-n_1}X^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+\end{equation}
+And for the sub-algebra $\mathfrak{a}$ the corresponding states are
+\begin{equation}
+  \label{eq:110}
+  \tilde{X}^{a'_1}_{-n_1}\tilde{X}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
+\end{equation}
+The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance, but this is not the case for the energy-momentum tensor.
+So the energy-momentum tensor of the larger theory should consist only of the generators of $\tilde{X}$.
+Then
+\begin{equation}
+  \label{eq:2}
+  T_{\mathfrak{g}}(z)=T_{\mathfrak{a}}(z),  
+\end{equation}
+which leads to the equality of the central charges 
+\begin{equation}
+  \label{eq:33}
+  c(\mathfrak{g})=c(\mathfrak{a}).
+\end{equation}
+This leads to the equation
+\begin{equation}
+  \label{eq:111}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
+\end{equation}
+Here $x_e$ is the embedding index and $g$, $a$ are the dual Coxeter numbers for the  corresponding algebras.
+
+It can be demonstrated that the solutions of the equation (\ref{eq:111}) exist only
+for the level $k=1$ \cite{difrancesco1997cft}.
+
+The complete classification of conformal embeddings is given in the paper \cite{schellekens1986conformal}.
+
+The relation (\ref{eq:111}) and the asymptotics of the branching functions can be used to prove the finite reducibility theorem \cite{kac1988modular}.
+It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
+
+It is important to note that the orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
+It can be seen from the following consideration.
+In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
+The energy-momentum tensor can be expanded into the modes $L_n$
+\begin{equation}
+\label{eq:47}
+  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
+\end{equation}
+The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
+\begin{equation}
+\label{eq:48}
+  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
+\end{equation}
+The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$.
+But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
+
+\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
+\label{sec:spec-embedd-hata_1s}
+Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $A_1\subset A_2$ with the embedding index $x_e=4$.
+The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.
+
+There exist three level 1 fundamental weights in the weight space of $\hat{A}_2$.
+It is easy to see that the set $\Delta_{\bot}$ is empty and the subalgebra $\mathfrak{a}_{\bot}=0$.
+
+Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details.
+Here the first two components are the Dynkin indices (coordinates in the fundamental weights basis) of the finite part of the weight.
+
+The set $\widehat{\Psi^{(\omega_0)}}$  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade.
+We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.
+
+\begin{figure}[h!tb]
+%  \hspace*{-2cm}
+  \includegraphics[width=140mm]{AffineA2_A1_anom.pdf}
+  \caption{The anomalous weights of the module $L^{(0,0;1;0)}_{\hat{A_2}}$}
+  \label{fig:affine_A2_anom_point}
+\end{figure}
+
+Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).
+Here we restricted the calculations to the first eight grades.
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
+  \caption{The fan $\Gamma_{\hat{A_1}\subset \hat{A_2}}$}
+  \label{fig:AffineA2A1Fan}
+\end{figure}
+
+The next step is to project the anomalous weights to $P_{\hat A_1}$.
+The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=130mm]{AffineA2_A1_proj_anom.pdf}
+  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$.}
+  \label{fig:AffineA2_A1_anom_proj}
+\end{figure}
+
+Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
+  \label{fig:AffineA2_A1_branching}
+\end{figure}
+
+We see that inside $\bar{C}_{\hat{A}_1}$, which is shown at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights.
+These are the branching coefficients.
+So the finite reducibility theorem holds and we get the decomposition
+\begin{equation}
+  \label{eq:43}
+  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
+\end{equation}
+
+For the other level 1 irreducible modules of $\hat{A}_2$ we get the trivial
+branching 
+\begin{eqnarray}
+  \label{eq:44}
+   L^{(1,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)},\\
+   L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
+\end{eqnarray}
+
+Using these results the modular-invariant partition function is easily found,
+\begin{equation}
+  \label{eq:45}
+  Z=\left|\chi_{(4;4;0)}+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
+\end{equation}
+
+\subsubsection{Embedding of semisimple subalgebras}
+\label{sec:embedd-semis-subalg}
+
+Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$, which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
+Let's construct the special embedding $A_1\oplus A_1\subset A_3$ using the method of \cite{vasilevich1986method}.
+We start with 4-dimensional representation of $A_1\oplus A_1$ with the highest weight $(1,1)$.
+The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
+
+\begin{figure}[h!tb]
+  \begin{multicols}{2}
+    \hfill
+    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
+    \hfill
+    \caption{Representation for the special embedding  $A_1\oplus A_1\subset A_3$}
+    \label{fig:A_1+A_1_to_A3}
+    \hfill
+    \includegraphics[width=50mm]{A1+A1-A3.pdf}
+    \hfill
+    \caption{Embedded roots for the special embedding  $A_1\oplus A_1\subset A_3$}
+    \label{fig:A1+A1-A3}
+  \end{multicols}
+\end{figure}
+
+Then for the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method}, so $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
+The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
+\begin{equation}
+  \label{eq:37}
+  \begin{array}{l}
+     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
+     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
+  \end{array}
+\end{equation}
+They are depicted at the Figure \ref{fig:A1+A1-A3}.
+
+This embedding is characterised by the embedding indices $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
+
+We are interested in the reduction of the fundamental modules of $\hat A_3$.
+Four fundamental weights of level 1 have the following coordinates in the orthogonal basis: 
+\begin{equation}
+  \begin{array}{lll}
+     \omega_0 & = & (0,0,0,0;1;0),\\
+     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
+     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
+     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
+  \end{array}
+\end{equation}
+
+For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
+\begin{equation}
+  \label{eq:38}
+  \begin{array}{lll}
+    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
+    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
+    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1+n\delta,\pm \alpha_2+n\delta;\; +n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
+  \end{array}
+\end{equation}
+
+The set $\Delta^{+}_{\bot}$ is empty. 
+The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}.
+Coordinates of fan element's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
+Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
+\begin{figure}[h!tb]
+  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
+  \caption{Fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
+  \label{fig:A1+A1-A3_fan}
+\end{figure}
+
+We limit our calculations by the first 5 grades.
+\begin{figure}[h!tb]
+  \hspace*{-1cm}
+  \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
+  \caption{Projected anomalous weights for $L^{\omega_2}_{\hat A_3}$}
+  \label{fig:A1+A1-A3_anom}
+\end{figure}
+
+The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{\omega_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,1,0;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
+Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
+The weights are shown by crosses if the determinant has the value $\epsilon(\omega)=1$ and by diamonds otherwise.
+
+The diagrams for  $L^{\omega_0}_{\hat A_3}, L^{\omega_1}_{\hat A_3}, L^{\omega_1}_{\hat A_3}$ are similar to that of $L^{\omega_2}_{\hat A_3}$.
+
+The anomalous branching coefficients for the module $L^{(\omega_2)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
+\begin{figure}[h!tb]
+%  \hspace*{-1cm}
+  \includegraphics[width=135mm]{A1+A1-A3_branching.pdf}
+  \caption{Anomalous branching coefficients for $L^{(0,1,0;1;0)}_{\hat A_3}$}
+  \label{fig:A1+A1-A3_branching}
+\end{figure}
+
+ We get the following branching rules
+ \begin{equation}
+   \label{eq:39}
+   \begin{array}{ll}
+     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
+     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
+     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
+     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
+   \end{array}
+ \end{equation}
+
+Now we can obtain modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
+\begin{multline}
+  \label{eq:40}
+  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
+  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
+\end{multline}
+
+We have chosen this example to illustrate the mechanism of out algorithm. 
+In this case the modules could be reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras.
+We must stress that our method is universal and can be applied for an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.
+
+\subsection{Coset models}
+\label{sec:coset-models}
 
@@
 
-%\newpage
-\section{Applications to the conformal field theory}
-\label{sec:phys-appl}
-
-Branching coefficients for an embedding of affine Lie subalgebra into
-affine Lie algebra can be used to construct modular invariant
-partition functions for Wess-Zumino-Novikov-Witten models of conformal field theory (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
-In these models current algebras are affine Lie algebras.
-For the construction to be valid the embedding is required to be conformal, which means that the central charge of the subalgebra is equal to the central charge of the algebra:
-\begin{equation}
-  \label{eq:31}
-  c(\mathfrak{a})=c(\mathfrak{g})
-\end{equation}
-
-Let $X^{a_j}_{-n_j}$ and $\tilde{X}^{a'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and for $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
-Let $\pi_{\mathfrak{a}}$ be the projection operator of $\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$.
-In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$ the states can be described as
-\begin{equation}
-  \label{eq:109}
-  X^{a_1}_{-n_1}X^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
-\end{equation}
-And for the sub-algebra $\mathfrak{a}$ the corresponding states are
-\begin{equation}
-  \label{eq:110}
-  \tilde{X}^{a'_1}_{-n_1}\tilde{X}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
-\end{equation}
-The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance, but this is not the case for the energy-momentum tensor.
-So the energy-momentum tensor of the larger theory should consist only of the generators of $\tilde{X}$.
-Then $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow c(\mathfrak{g})=c(\mathfrak{a})$.
-This leads to the equation
-\begin{equation}
-  \label{eq:111}
-  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
-\end{equation}
-Here $x_e$ is the embedding index and $g$, $a$ are the dual Coxeter numbers for the  corresponding algebras.
-
-It can be demonstrated that the solutions of the equation (\ref{eq:111}) exist only
-for the level $k=1$ \cite{difrancesco1997cft}.
-
-The complete classification of conformal embeddings is given in the paper \cite{schellekens1986conformal}.
-
-If we have modular-invariant partition function for the fields described by a representation of the algebra $\mathfrak{g}$ this modular invariance is preserved by the projection on the subalgebra $\mathfrak{a}$, but we need also the preservation of the conformal invariance.
-So we should select only those highest-weight modules of the algebra $\mathfrak{g}$ for which the relation (\ref{eq:111}) holds.
-
-This relation and the asymptotics of the branching functions can be used to prove the finite reducibility theorem \cite{kac1988modular}.
-It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
-
-Having found all such weights $\nu$ and the corresponding branching coefficients $b^{(\mu)}_{\nu}$ we can replace the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function
-\begin{equation}
-  \label{eq:34}
-   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
-\end{equation}
-by the decompositions
-\begin{equation}
-  \label{eq:32}
-\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}  
-\end{equation}
- containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules.
-Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
-\begin{equation}
-  \label{eq:36}
-   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
-\end{equation}
-
-It is important to note that the orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
-It can be seen from the following consideration.
-In the case of the conformal embedding energy-momentum tensors are to be equal
-\begin{equation}
-  \label{eq:46}
-  T_{\mathfrak{a}}(z)=T_{\mathfrak{g}}(z)
-\end{equation}
-The energy-momentum tensor can be expanded into the modes $L_n$
-\begin{equation}
-\label{eq:47}
-  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
-\end{equation}
-The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
-\begin{equation}
-\label{eq:48}
-  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
-\end{equation}
-The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$.
-But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
-
-\subsection{Examples}
-\label{sec:example}
-
-\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
-\label{sec:spec-embedd-hata_1s}
-Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $A_1\subset A_2$ with the embedding index $x_e=4$.
-The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.
-
-There exist three level 1 fundamental weights in the weight space of $\hat{A}_2$.
-It is easy to see that the set $\Delta_{\bot}$ is empty and the subalgebra $\mathfrak{a}_{\bot}=0$.
-
-Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details.
-Here the first two components are the Dynkin indices (coordinates in the fundamental weights basis) of the finite part of the weight.
-
-The set $\widehat{\Psi^{(\omega_0)}}$  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade.
-We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.
-
-\begin{figure}[h!tb]
-%  \hspace*{-2cm}
-  \includegraphics[width=140mm]{AffineA2_A1_anom.pdf}
-  \caption{The anomalous weights of the module $L^{(0,0;1;0)}_{\hat{A_2}}$}
-  \label{fig:affine_A2_anom_point}
-\end{figure}
-
-Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).
-Here we restricted the calculations to the first eight grades.
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
-  \caption{The fan $\Gamma_{\hat{A_1}\subset \hat{A_2}}$}
-  \label{fig:AffineA2A1Fan}
-\end{figure}
-
-The next step is to project the anomalous weights to $P_{\hat A_1}$.
-The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=130mm]{AffineA2_A1_proj_anom.pdf}
-  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$.}
-  \label{fig:AffineA2_A1_anom_proj}
-\end{figure}
-
-Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
-  \label{fig:AffineA2_A1_branching}
-\end{figure}
-
-We see that inside $\bar{C}_{\hat{A}_1}$, which is shown at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights.
-These are the branching coefficients.
-So the finite reducibility theorem holds and we get the decomposition
-\begin{equation}
-  \label{eq:43}
-  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
-\end{equation}
-
-For the other level 1 irreducible modules of $\hat{A}_2$ we get the trivial
-branching 
-\begin{eqnarray}
-  \label{eq:44}
-   L^{(1,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)},\\
-   L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
-\end{eqnarray}
-
-Using these results the modular-invariant partition function is easily found,
-\begin{equation}
-  \label{eq:45}
-  Z=\left|\chi_{(4;4;0)}+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
-\end{equation}
-
-\subsubsection{Embedding of semisimple subalgebras}
-\label{sec:embedd-semis-subalg}
-
-Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$, which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
-Let's construct the special embedding $A_1\oplus A_1\subset A_3$ using the method of \cite{vasilevich1986method}.
-We start with 4-dimensional representation of $A_1\oplus A_1$ with the highest weight $(1,1)$.
-The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
-
-\begin{figure}[h!tb]
-  \begin{multicols}{2}
-    \hfill
-    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
-    \hfill
-    \caption{Representation for the special embedding  $A_1\oplus A_1\subset A_3$}
-    \label{fig:A_1+A_1_to_A3}
-    \hfill
-    \includegraphics[width=50mm]{A1+A1-A3.pdf}
-    \hfill
-    \caption{Embedded roots for the special embedding  $A_1\oplus A_1\subset A_3$}
-    \label{fig:A1+A1-A3}
-  \end{multicols}
-\end{figure}
-
-Then for the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method}, so $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
-The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
-\begin{equation}
-  \label{eq:37}
-  \begin{array}{l}
-     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
-     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
-  \end{array}
-\end{equation}
-They are depicted at the Figure \ref{fig:A1+A1-A3}.
-
-This embedding is characterised by the embedding indices $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
-
-We are interested in the reduction of the fundamental modules of $\hat A_3$.
-Four fundamental weights of level 1 have the following coordinates in the orthogonal basis: 
-\begin{equation}
-  \begin{array}{lll}
-     \omega_0 & = & (0,0,0,0;1;0),\\
-     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
-     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
-     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
-  \end{array}
-\end{equation}
-
-For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
-\begin{equation}
-  \label{eq:38}
-  \begin{array}{lll}
-    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
-    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
-    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1+n\delta,\pm \alpha_2+n\delta;\; +n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
-  \end{array}
-\end{equation}
-
-The set $\Delta^{+}_{\bot}$ is empty. 
-The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}.
-Coordinates of fan element's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
-Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
-\begin{figure}[h!tb]
-  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
-  \caption{Fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
-  \label{fig:A1+A1-A3_fan}
-\end{figure}
-
-We limit our calculations by the first 5 grades.
-\begin{figure}[h!tb]
-  \hspace*{-1cm}
-  \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
-  \caption{Projected anomalous weights for $L^{\omega_2}_{\hat A_3}$}
-  \label{fig:A1+A1-A3_anom}
-\end{figure}
-
-The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{\omega_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,1,0;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
-Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
-The weights are shown by crosses if the determinant has the value $\epsilon(\omega)=1$ and by diamonds otherwise.
-
-The diagrams for  $L^{\omega_0}_{\hat A_3}, L^{\omega_1}_{\hat A_3}, L^{\omega_1}_{\hat A_3}$ are similar to that of $L^{\omega_2}_{\hat A_3}$.
-
-The anomalous branching coefficients for the module $L^{(\omega_2)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
-\begin{figure}[h!tb]
-%  \hspace*{-1cm}
-  \includegraphics[width=135mm]{A1+A1-A3_branching.pdf}
-  \caption{Anomalous branching coefficients for $L^{(0,1,0;1;0)}_{\hat A_3}$}
-  \label{fig:A1+A1-A3_branching}
-\end{figure}
-
- We get the following branching rules
- \begin{equation}
-   \label{eq:39}
-   \begin{array}{ll}
-     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
-     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
-     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
-     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
-   \end{array}
- \end{equation}
-
-Now we can obtain modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
-\begin{multline}
-  \label{eq:40}
-  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
-  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
-\end{multline}
-
-We have chosen this example to illustrate the mechanism of out algorithm. 
-In this case the modules could be reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras.
-We must stress that our method is universal and can be applied for an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.
-
 \section{Conclusion}

### 2010-06-16 AffineLieAlgebras/InformalNotes/article.tex
Bibliography work, some text on coset construction is partially written.

@@
 \cite{kac1990idl},\cite{wakimoto2001idl}), the Schure function series \cite{fauser2006new}, the BRST
-cohomology \cite{hwang1994general}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
+cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
 combinatorial methods applied in \cite{feigin707principal}.
@@
 It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
+\begin{comment}
+  There exists a classification of modular invariant partition functions for some cases, see . [116, 219, 117, 119, 46] in \cite{Fuchs:2009iz}.
+\end{comment}
+\begin{comment}
+  Formulate this as lemma
 
@@
 But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
+\end{comment}
 
@@
 \label{sec:coset-models}
+
+Another natural setting where the reduction problem for affine Lie algebras appears is the coset construction of rational conformal field theories \cite{Goddard198588}.
+Coset models are tightly connected with the gauged WZW-models and are actively studied in string theory especially in string models on anti-de-Sitter space \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}.
+The characters of the coset model are connected with the branching functions in the following way:
+\begin{equation}
+  \label{eq:31}
+  \chi
+\end{equation}
+The problem of the branching functions construction in coset models was considered in the papers \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.
+The results were mostly given in rather cumbersome form and could not be easily used in computations.
+The method of calculation of the branching coefficients proposed in this text can be used to get power series expansion of the branching functions up to any required degree.
+In future work we are going to write complete expansion of the branching functions.
+
+In this section we present the example of the computation of branching functions power series expansion for the embedding $A_1\subset B_2$.
 
@@
 
+This expansion can be used to compute the conformal dimensions of the primary fields of $B_2/A_1$ coset model in the following way:
+\begin{equation}
+  \label{eq:35}
+  \Delta_{\mu}=
+\end{equation}
+
 \section{Conclusion}

### 2010-06-21 AffineLieAlgebras/InformalNotes/article.tex
Article is almost finished.

@@
 \newtheorem{statement}{Statement}
+\newtheorem{note}{Note}[section]
 \theoremstyle{definition} \newtheorem{Def}{Definition}
@@
 We demonstrate that our algorithm can be used in the study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some physical limitations.
+In the study of the coset construction of rational conformal field theory the algorithm is useful for the computation of the characters and states.
 
@@
 In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules of algebra $\mathfrak{g}$ with respect to a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}).
-In the Section \ref{sec:examples} we present several examples and discuss some applications in CFT models (Section \ref{sec:phys-appl}).
+In the Section \ref{sec:finite-dimens-lie} we present several simple examples for finite-dimensional Lie algebras to illustrate the algorithm.
+Then we consider the affine Lie algebras with the applications in CFT models (Section \ref{sec:phys-appl}).
 We conclude the paper with a review of obtained results.
@@
 \end{array}
-\right\} ;$
+\right\} ;$\\
 $\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
@@
 non-connected Dynkin diagrams we can see which roots are orthogonal to the root
-space of non-maximal regular subalgebra $\mathfrak{a}$.
+space of non-maximal regular subalgebra $\mathfrak{a}$.  The complete classification of the regular subalgebras of affine Lie algebras can be found in the recent paper \cite{JPhysA2008}.
 
@@
   \centering
-  \includegraphics[width=50mm]{B2_A1_diagram.pdf}
+  \includegraphics[width=40mm]{B2_A1_diagram.pdf}
   \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
@@
 
-The task of the construction of non-diagonal modular invariants is not easy. 
+The task of the construction of non-diagonal modular invariants is not easy, although the complete classification of modular invariants for some models is known [116, 219, 117, 119, 46] in \cite{Fuchs:2009iz}.
+
 Consider the Wess-Zumino-Witten model with the affine Lie algebra $\mathfrak{a}$.
@@
 It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
-\begin{comment}
-  There exists a classification of modular invariant partition functions for some cases, see . [116, 219, 117, 119, 46] in \cite{Fuchs:2009iz}.
-\end{comment}
-\begin{comment}
-  Formulate this as lemma
-
-It is important to note that the orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
-It can be seen from the following consideration.
-In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
+
+\begin{note} The orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
+\begin{proof} It can be seen from the following consideration. In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
 The energy-momentum tensor can be expanded into the modes $L_n$
@@
 But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
-\end{comment}
-
+\end{proof}
+\end{note}
 \subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
@@
 
+Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).
+
+\begin{figure}[h!bt]
+  \centering
+  \includegraphics[width=135mm]{AffineA2_A1_fan.pdf}
+  \caption{The fan for $\hat{A_1}\subset \hat{A_2}$}
+  \label{fig:AffineA2A1Fan}
+\end{figure}
+
 Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details.
@@
 
-The set $\widehat{\Psi^{(\omega_0)}}$  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade.
-We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration as the dotted diagonal plane.
+The set $\widehat{\Psi^{(w_0)}}$  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade.
+The weights $\omega (w_0+\rho)-\rho$ is shown as cross if $\epsilon(\omega)=1$ and by diamond if $\epsilon(\omega)=-1$.
+Simple roots of classical subalgebra $A_2$ are shown in grey and grey diagonal plane is the Cartan subalgebra of the embedded algebra $\hat{A}_1$.
 
@@
   \label{fig:affine_A2_anom_point}
-\end{figure}
-
-Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).
-Here we restricted the calculations to the first eight grades.
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=130mm]{AffineA2_A1_fan.pdf}
-  \caption{The fan $\Gamma_{\hat{A_1}\subset \hat{A_2}}$}
-  \label{fig:AffineA2A1Fan}
 \end{figure}
@@
   \begin{array}{lll}
-     \omega_0 & = & (0,0,0,0;1;0),\\
-     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
-     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
-     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
+     w_0 & = & (0,0,0,0;1;0),\\
+     w_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
+     w_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
+     w_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
   \end{array}
@@
 The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}.
-Coordinates of fan element's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
+Coordinates of fan element's finite part are given in the basis of fundamental roots of $A_1\oplus A_1$.
 Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
@@
 We limit our calculations by the first 5 grades.
-\begin{figure}[h!tb]
-  \hspace*{-1cm}
-  \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
-  \caption{Projected anomalous weights for $L^{\omega_2}_{\hat A_3}$}
+%\begin{figure}[h!tb]
+\begin{figure}[p]
+%  \hspace*{-1cm}
+  \includegraphics[width=135mm]{A1+A1-A3_anom.pdf}
+  \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3}$}
   \label{fig:A1+A1-A3_anom}
@@
 
-The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{\omega_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,1,0;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
+The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{w_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=w_2=(0,1,0;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
 Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
@@
 
-The diagrams for  $L^{\omega_0}_{\hat A_3}, L^{\omega_1}_{\hat A_3}, L^{\omega_1}_{\hat A_3}$ are similar to that of $L^{\omega_2}_{\hat A_3}$.
-
-The anomalous branching coefficients for the module $L^{(\omega_2)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
-\begin{figure}[h!tb]
+The diagrams for  $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_1}_{\hat A_3}$ are similar to that of $L^{w_2}_{\hat A_3}$.
+
+The anomalous branching coefficients for the module $L^{(w_2)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
+The anomalous branching coefficients in the $C_{\frak{a}}$ are equal to the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$ and are shown by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
+%\begin{figure}[h!tb]
+\begin{figure}[p]
 %  \hspace*{-1cm}
-  \includegraphics[width=135mm]{A1+A1-A3_branching.pdf}
-  \caption{Anomalous branching coefficients for $L^{(0,1,0;1;0)}_{\hat A_3}$}
+  \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.pdf}
+  \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3}$}
   \label{fig:A1+A1-A3_branching}
@@
   \label{eq:31}
-  \chi
-\end{equation}
-The problem of the branching functions construction in coset models was considered in the papers \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.
+  \chi^{(\mu)}_{\nu}(\tau)=e^{2\pi i \tau (m_{\mu}-m_{\nu})} b^{(\mu)}_{\nu}(\tau),
+\end{equation}
+where
+\begin{equation}
+  \label{eq:46}
+  m_{\mu}=\frac{\left|\mu+\rho\right|^2}{2(k+g)}-\frac{\left|\rho\right|^2}{2g}.
+\end{equation}
+
+The problem of the branching functions construction in the coset models was considered in the papers \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.
 The results were mostly given in rather cumbersome form and could not be easily used in computations.
@@
 Here we restricted the computation to the twelfth grade.
-\begin{figure}[h!tb]
+\begin{figure}[h!bt]
   \centering
@@
 
-The set of the anomalous weights for this module up to the sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade its form is similar to that in the  Figure \ref{fig:B2_A1}.
+The set of the anomalous weights for this module up to the sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point}.
+In the grade 0 it is exactly the set of the anomalous weights for the embedding of the classical Lie algebras $A_1\subset B_2$ depicted in the  Figure \ref{fig:B2_A1}.
+The weights $\omega (w_1+\rho)-\rho$ is shown as cross if $\epsilon(\omega)=1$ and by circle otherwise.
+Simple roots of classical subalgebra $B_2$ are shown in grey and grey diagonal plane is the Cartan subalgebra of the embedded algebra $\hat{A}_1$.
 
 \begin{figure}[h!tb]
-  \hspace*{-2cm}
-  \includegraphics[width=200mm]{AffineB2_A1_Anom.pdf}
-  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$}.
+%  \hspace*{-2cm}
+  \includegraphics[width=140mm]{AffineB2_A1_Anom.pdf}
+  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$. The weights of the grade 0 are depicted at the Figure \ref{fig:B2_A1}}.
   \label{fig:affine_B2_anom_point}
@@
 \end{eqnarray}
-Here the lower index enumerates the branching function according to their highest weights in $P^+_{\hat{A_1}}$, these are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
-
-This expansion can be used to compute the conformal dimensions of the primary fields of $B_2/A_1$ coset model in the following way:
+Here the lower index enumerates the branching function according to their highest weights in $P^+_{\hat{A_1}}$, these are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$, and $q=\exp (2\pi i \tau)$.
+
+Now we can use the equation \eqref{eq:31} to get the expansion of the $B_2/A_1$-coset theory characters:
 \begin{equation}
   \label{eq:35}
-  \Delta_{\mu}=
-\end{equation}
+  \begin{array}{cc}
+    \chi^{(w_1)}_{1}(q)= & q^{\frac{7}{12}}\left( 2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\right. \\
+    & \left. 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots \right)\\
+    \chi^{(w_1)}_{0}(q) = & q^{\frac{5}{6}}\left(1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\right. \\
+    &\left. 222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\right)
+  \end{array}
+\end{equation}
+
+The folded fan technique \cite{IKL2010}  can be used to get the explicit expression for the branching functions and the corresponding coset conformal field theory characters.
+This subject will be discussed in the future works.
 
@@
 We have demonstrated the effectiveness of the proposed generalizations of the injection fan algorithm and discussed its possible application to some physical problems.
-In particular we considered the construction of modular-invariant partition functions in the conformal field theory in the framework of conformal embedding method.
-This  method is useful in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
+In particular we considered the construction of modular-invariant partition functions in the conformal field theory in the framework of conformal embedding method and the coset construction of the rational conformal field theory.
+This construction is useful in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
 

### 2010-06-21 AffineLieAlgebras/InformalNotes/article.tex
Bibliography fixed

@@
 non-connected Dynkin diagrams we can see which roots are orthogonal to the root
-space of non-maximal regular subalgebra $\mathfrak{a}$.  The complete classification of the regular subalgebras of affine Lie algebras can be found in the recent paper \cite{JPhysA2008}.
+space of non-maximal regular subalgebra $\mathfrak{a}$.  The complete classification of the regular subalgebras of affine Lie algebras can be found in the recent paper \cite{1751-8121-41-36-365204}.
 
@@
 and is the set of positive roots for the algebra $\mathfrak{a}_{\bot}=B_2$.
-
-Firstly we construct the fan for this injection.
-Using the definition (\ref{fan-defined}) we obtain the set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
-
-To find the branching coefficients we need to compute the anomalous weights of $B_4$, select the weights belonging to $C^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$ and compute the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.
-
-Consider the $B_4$-module $L^{\mu}$ with the highest weight $\mu=(0,1,0,2)=2
-e_1 + 2 e_2 + e_3 + e_4$; $dim(L^{(0,1,0,2)})=2772$.
-
-The set of the anomalous weights $\left\{ \omega(\mu+\rho)-\rho,\; \omega\in W\right\}$
-contains of 384 vectors.
-
-We need to select the weights $\psi \in \omega(\mu+\rho)$  with the property $\pi_{\mathfrak{a}_{\bot}} \left(  \psi \right) \in C^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$.
-It means that the scalar product of these weights with all the roots in $\Delta^{+}_{\bot}$ is non-negative.
-
-To compute the dimensions of the corresponding
-$\mathfrak{a}_{\bot}$-modules we need to project each selected weight
-onto the root space $\Delta^{+}_{\bot}$, substract
-$\rho_{\mathfrak{a}_{\bot}}$ and apply the Weyl dimension formula.
-
-The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.
 \begin{figure}[p]
@@
 \end{figure}
+
+Firstly we construct the fan for this injection.
+Using the definition (\ref{fan-defined}) we obtain the set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
+
+To find the branching coefficients we need to compute the anomalous weights of $B_4$, select the weights belonging to $C^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$ and compute the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.
+
+Consider the $B_4$-module $L^{\mu}$ with the highest weight $\mu=(0,1,0,2)=2
+e_1 + 2 e_2 + e_3 + e_4$; $dim(L^{(0,1,0,2)})=2772$.
+
+The set of the anomalous weights $\left\{ \omega(\mu+\rho)-\rho,\; \omega\in W\right\}$
+contains of 384 vectors.
+
+We need to select the weights $\psi \in \omega(\mu+\rho)$  with the property $\pi_{\mathfrak{a}_{\bot}} \left(  \psi \right) \in C^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$.
+It means that the scalar product of these weights with all the roots in $\Delta^{+}_{\bot}$ is non-negative.
+
+To compute the dimensions of the corresponding
+$\mathfrak{a}_{\bot}$-modules we need to project each selected weight
+onto the root space $\Delta^{+}_{\bot}$, substract
+$\rho_{\mathfrak{a}_{\bot}}$ and apply the Weyl dimension formula.
+
+The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.
+
 Applying the recurrent relation (\ref{recurrent-relation}) we obtain the
@@
 
-The task of the construction of non-diagonal modular invariants is not easy, although the complete classification of modular invariants for some models is known [116, 219, 117, 119, 46] in \cite{Fuchs:2009iz}.
+The task of the construction of non-diagonal modular invariants is not easy, although the complete classification of modular invariants for some models is known \cite{1994hepthGannon,1995JMPGannon}.
 
@@
 
-The folded fan technique \cite{IKL2010}  can be used to get the explicit expression for the branching functions and the corresponding coset conformal field theory characters.
+The folded fan technique \cite{il2010folded} can be used to get the explicit expression for the branching functions and the corresponding coset conformal field theory characters.
 This subject will be discussed in the future works.

### 2010-06-21 AffineLieAlgebras/InformalNotes/article.tex
Some misprints fixed

@@
 In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
-special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}. 
+special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted in the Figure \ref{fig:a1a2a3}. 
 \begin{figure}[h]
@@
 Consider the regular embedding of $A_1$ into $B_2$.
-Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the dashed vectors at the Figure \ref{fig:B2_A1}.
+Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the dashed vectors in the Figure \ref{fig:B2_A1}.
 We denote the corresponding Weyl reflections by $\omega_1, \omega_2$.
@@
 Firstly we construct the fan for this injection.
-Using the definition (\ref{fan-defined}) we obtain the set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
+Using the definition (\ref{fan-defined}) we obtain the set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted in the Figure \ref{fig:B4B2Fan}.
 
@@
 
-We see that inside $\bar{C}_{\hat{A}_1}$, which is shown at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights.
+We see that inside $\bar{C}_{\hat{A}_1}$, which is shown in the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights.
 These are the branching coefficients.
@@
 We start with 4-dimensional representation of $A_1\oplus A_1$ with the highest weight $(1,1)$.
-The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
+The weights of this representation are numbered as depicted in the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
 
@@
 \end{equation}
-They are depicted at the Figure \ref{fig:A1+A1-A3}.
+They are depicted in the Figure \ref{fig:A1+A1-A3}.
 
@@
 The set $\Delta^{+}_{\bot}$ is empty. 
-The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}.
+The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown in the Figure \ref{fig:A1+A1-A3_fan}.
 Coordinates of fan element's finite part are given in the basis of fundamental roots of $A_1\oplus A_1$.
@@
 
-The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{w_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=w_2=(0,1,0;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}.
+The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{w_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}.
 Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
@@
 
-The anomalous branching coefficients for the module $L^{(w_2)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
+The anomalous branching coefficients for the module $L^{(w_2)}$ are shown in the Figure  \ref{fig:A1+A1-A3_branching}.
 The anomalous branching coefficients in the $C_{\frak{a}}$ are equal to the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$ and are shown by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
@@
   \includegraphics[width=140mm]{AffineB2_A1_Anom.pdf}
-  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$. The weights of the grade 0 are depicted at the Figure \ref{fig:B2_A1}}.
+  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$. The weights of the grade 0 are depicted in the Figure \ref{fig:B2_A1}}.
   \label{fig:affine_B2_anom_point}

### 2010-06-25 AffineLieAlgebras/InformalNotes/article.tex
More changes from V.D. New preprint number.

@@
 \begin{flushright}
-{\large \bf SPbU-IP-09-08}
+{\large \bf SPbU-IP-10-03}
 \end{flushright}
@@
 SAINT-PETERSBURG \\
-2009
+2010
 \end{center}
@@
 We demonstrate that our algorithm can be used in the study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some physical limitations.
-In the study of the coset construction of rational conformal field theory the algorithm is useful for the computation of the characters and states.
+In the study of the coset construction of rational conformal field theory the algorithm is useful for the computation of characters and states.
 
@@
 We conclude the paper with a review of obtained results.
-Possible future developments are discussed (Section \ref{sec:conclusion}).
+Possible further developments are discussed (Section \ref{sec:conclusion}).
 
@@
 $-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \text{resp. }\frak{a}%
-\right) $; $i=0,\ldots ,r$ ,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
 
@@
 non-connected Dynkin diagrams we can see which roots are orthogonal to the root
-space of non-maximal regular subalgebra $\mathfrak{a}$.  The complete classification of the regular subalgebras of affine Lie algebras can be found in the recent paper \cite{1751-8121-41-36-365204}.
+space of non-maximal regular subalgebra $\mathfrak{a}$.  The complete classification of the regular subalgebras for affine Lie algebras can be found in the recent paper \cite{1751-8121-41-36-365204}.
 
@@
 Coset models are tightly connected with the gauged WZW-models and are actively studied in string theory especially in string models on anti-de-Sitter space \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}.
-The characters of the coset model are connected with the branching functions in the following way:
+The characters of the coset model are connected with the branching functions,
 \begin{equation}
@@
 The problem of the branching functions construction in the coset models was considered in the papers \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.
-The results were mostly given in rather cumbersome form and could not be easily used in computations.
-The method of calculation of the branching coefficients proposed in this text can be used to get power series expansion of the branching functions up to any required degree.
-In future work we are going to write complete expansion of the branching functions.
-
-In this section we present the example of the computation of branching functions power series expansion for the embedding $A_1\subset B_2$.
-
-Consider the affine extension of the example \ref{sec:regul-embedd-a_1}.
+It was shown that the branching functions results in cumbersome calculations.
+In what follows we shall demonstrate that these calculations can be simplified by applying the injection fan method.
+
+Let us return to the example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection $A_1 \to  B_2$.
 Since this embedding is regular and $x_e=1$, the level of the  subalgebra modules is equal to that of the initial module.
@@
 
-Consider the level 1 module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $w_1=(1,0;1;0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the level of the weight and the fourth is the grade.
-
-The set of the anomalous weights for this module up to the sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point}.
+Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $w_1=(1,0;1;0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the level of the weight and the fourth is the grade.
+
+The set of the anomalous weights for this module up to the sixth grade is presented in the Figure \ref{fig:affine_B2_anom_point}.
 In the grade 0 it is exactly the set of the anomalous weights for the embedding of the classical Lie algebras $A_1\subset B_2$ depicted in the  Figure \ref{fig:B2_A1}.
-The weights $\omega (w_1+\rho)-\rho$ is shown as cross if $\epsilon(\omega)=1$ and by circle otherwise.
-Simple roots of classical subalgebra $B_2$ are shown in grey and grey diagonal plane is the Cartan subalgebra of the embedded algebra $\hat{A}_1$.
+The weights $\omega (w_1+\rho)-\rho$ are marked by crosses if $\epsilon(\omega)=1$ and by circles otherwise.
+Simple roots of classical subalgebra $B_2$ are indicated by grey arrows while the grey diagonal plane is the Cartan subalgebra of the embedded algebra $\hat{A}_1$.
 
@@
 $\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
-we get the following results for the branching coefficients up to twelfth grade
+we get the branching coefficients up to twelfth grade
 \begin{multline}
@@
 \end{eqnarray}
-Here the lower index enumerates the branching function according to their highest weights in $P^+_{\hat{A_1}}$, these are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$, and $q=\exp (2\pi i \tau)$.
-
-Now we can use the equation \eqref{eq:31} to get the expansion of the $B_2/A_1$-coset theory characters:
+Here $q=\exp (2\pi i \tau)$, the lower index enumerates the branching function according to their highest weights in $P^+_{\hat{A_1}}$, these are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
+
+Now we can use the relation \eqref{eq:31} to get the expansion of the $B_2/A_1$-coset characters:
 \begin{equation}
@@
 \end{equation}
-
-The folded fan technique \cite{il2010folded} can be used to get the explicit expression for the branching functions and the corresponding coset conformal field theory characters.
-This subject will be discussed in the future works.
+Further amelioration of the construction can be achieved using the folded fan technique \cite{il2010folded}.
+The explicit expression for the branching functions and the corresponding coset characters can be obtained.
 
@@
 We have shown that the injection fan technique can be used to deal with the nonmaximal subalgebras.
-It was demonstrated that in such cases in the set of positive roots $\Delta_{\mathfrak{g}}^{+}$ it is necessary to  separate an additional subset $\Delta^{+}_{\bot}$.
-The injection fan is formed by the weights $\left(\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+}\right) \setminus \Delta^{+}_{\bot}$ and the additional role of the subset $\Delta^{+}_{\bot}$ is to modify the anomalous weights of the initial module.
-This modification reduces to a simple procedure: the anomalous weights are to be substituted by the dimensions of the corresponding ${\mathfrak{a}}_{\bot}$-modules.
-
-We have demonstrated the effectiveness of the proposed generalizations of the injection fan algorithm and discussed its possible application to some physical problems.
-In particular we considered the construction of modular-invariant partition functions in the conformal field theory in the framework of conformal embedding method and the coset construction of the rational conformal field theory.
+It was demonstrated that for such injections it is necessary to extract from the set of positive roots $\Delta_{\mathfrak{g}}^{+}$ the auxiliary subset $\Delta^{+}_{\bot}$.
+The injection fan is formed by the weights $\left(\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+}\right) \setminus \Delta^{+}_{\bot}$ and the role of the subset $\Delta^{+}_{\bot}$ is to modify the set of anomalous weights of the initial module.
+This modification reduces to a simple procedure: the anomalous weight multiplicities are to be substituted by the dimensions of the corresponding ${\mathfrak{a}}_{\bot}$-modules.
+
+We have demonstrated the efficiency of the proposed generalizations of the injection fan algorithm.
+Its possible applications to some physical problems were discussed.
+In particular we considered the construction of modular-invariant partition functions  in the framework of conformal embedding method and the coset construction of the rational conformal field theory.
 This construction is useful in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
 
-The proposed general approach to the reduction problem has the additional applications in the study of integrable chains.
+The proposed general approach to the reduction problem also has applications in the study of integrable spin chains.
 

### 2010-07-01 AffineLieAlgebras/InformalNotes/article.tex
Mergerd V.D. changes

@@
 We demonstrate that our algorithm can be used in the study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some physical limitations.
-In the study of the coset construction of rational conformal field theory the algorithm is useful for the computation of characters and states.
+In the study of the coset construction of rational conformal field theory the algorithm is useful for the computation of the characters and states.
 
@@
 \label{sec:spec-embedd-hata_1s}
-Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $A_1\subset A_2$ with the embedding index $x_e=4$.
-The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.
+Consider the case where both $\mathfrak{g}$ and $\mathfrak{a}$ are affine Lie algebras:
+$\hat{A}_1 \longrightarrow \hat{A}_2$ and the injection is the affine extension of the
+special injection $A_1 \longrightarrow A_2$ with the embedding index $x_e=4$.
+As far as the $\mathfrak{g}$-modules to be considered are of level one,
+the $\mathfrak{g}$-modules will be of level $\tilde{k}=kx_e=4$.
 
@@
 
-Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).
+Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$
+and the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).
 
@@
   \includegraphics[width=135mm]{AffineA2_A1_fan.pdf}
-  \caption{The fan for $\hat{A_1}\subset \hat{A_2}$}
+  \caption{The fan and $s(\gamma+\gamma_0)$ for $\hat{A_1}\longrightarrow \hat{A_2}$}
   \label{fig:AffineA2A1Fan}
@@
 
-Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details.
-Here the first two components are the Dynkin indices (coordinates in the fundamental weights basis) of the finite part of the weight.
-
-The set $\widehat{\Psi^{(w_0)}}$  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade.
-The weights $\omega (w_0+\rho)-\rho$ is shown as cross if $\epsilon(\omega)=1$ and by diamond if $\epsilon(\omega)=-1$.
-Simple roots of classical subalgebra $A_2$ are shown in grey and grey diagonal plane is the Cartan subalgebra of the embedded algebra $\hat{A}_1$.
+Let us consider the module $L^{w_0=(0,0;1;0)}$. Here we use the (finite part; level; grade)
+presentation (see section(\ref{sec:notation})) of the highest weight and the finite part
+coordinates are the Dynkin indices.
+
+The set $\widehat{\Psi^{(w_0)}}$  is depicted in the Figure
+\ref{fig:affine_A2_anom_point} up to the sixth grade.
+The weights $\omega (w_0+\rho)-\rho$ are marked by crosses when $\epsilon(\omega)=1$ and
+by diamond when $\epsilon(\omega)=-1$. Simple roots of the classical subalgebra $A_2$ are
+grey and the grey diagonal plane corresponds to the Cartan subalgebra of
+the embedded algebra $\hat{A}_1$.
 
@@
 The next step is to project the anomalous weights to $P_{\hat A_1}$.
-The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
+The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}.
 \begin{figure}[h!tb]
@@
 \end{figure}
-
-We see that inside $\bar{C}_{\hat{A}_1}$, which is shown in the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights.
-These are the branching coefficients.
-So the finite reducibility theorem holds and we get the decomposition
+There we see that inside the chamber $\bar{C}_{\hat{A}_1}$, which is isolated in the
+Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights
+both with multiplicities 1.
+These are the highest weights of the $\mathfrak{a}$-submodules and their branching
+coefficients. So the finite reducibility theorem holds and we get the decomposition
 \begin{equation}
@@
 
-\subsubsection{Embedding of semisimple subalgebras}
+\subsubsection{Embeddings of semisimple subalgebras}
 \label{sec:embedd-semis-subalg}
 
-Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$, which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
-Let's construct the special embedding $A_1\oplus A_1\subset A_3$ using the method of \cite{vasilevich1986method}.
-We start with 4-dimensional representation of $A_1\oplus A_1$ with the highest weight $(1,1)$.
-The weights of this representation are numbered as depicted in the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
+Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where
+$\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$,
+which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
+To construct this injection we use the method presented in \cite{vasilevich1986method}.
+We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$.
+Its diagram $\mathcal{N}_{A_1\oplus A_1}^{(1,1)}
+= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$
+is presented in Figure \ref{fig:A_1+A_1_to_A3}.
 
@@
     \hfill
-    \caption{Representation for the special embedding  $A_1\oplus A_1\subset A_3$}
+    \caption{The special embedding  $A_1\oplus A_1\subset A_3$ is based on this module}
     \label{fig:A_1+A_1_to_A3}
@@
 
-Then for the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method}, so $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
+For the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in
+the Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}
+{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},
+\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}
+{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method},
+thus $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
 The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
@@
 \end{equation}
-They are depicted in the Figure \ref{fig:A1+A1-A3}.
-
-This embedding is characterised by the embedding indices $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
+(See Figure \ref{fig:A1+A1-A3}.)
+
+This injection is characterised by the embedding indices $(2,2)$ and is conformal,
+since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
 
@@
 \end{equation}
-
 The set $\Delta^{+}_{\bot}$ is empty.
 The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown in the Figure \ref{fig:A1+A1-A3_fan}.
-Coordinates of fan element's finite part are given in the basis of fundamental roots of $A_1\oplus A_1$.
-Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
+The coordinates of fan element finite part are given in the basis of $A_1\oplus A_1$ fundamental roots.
+The fan elements $\gamma$ are marked by crosses if  $s(\gamma)=1$ and by diamonds if $s(\gamma)=-1$.
 \begin{figure}[h!tb]
   \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
-  \caption{Fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
+  \caption{The fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
   \label{fig:A1+A1-A3_fan}
@@
   \includegraphics[width=135mm]{A1+A1-A3_anom.pdf}
-  \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3}$}
+  \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
   \label{fig:A1+A1-A3_anom}
@@
 
-The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{w_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}.
-Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
-The weights are shown by crosses if the determinant has the value $\epsilon(\omega)=1$ and by diamonds otherwise.
-
-The diagrams for  $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_1}_{\hat A_3}$ are similar to that of $L^{w_2}_{\hat A_3}$.
+The set of anomalous weights $\widehat{\Psi_{\hat A_3}^{(\mu)}}$
+and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for
+$\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}.
+Coordinates of the finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
+The weights are marked by crosses if $\epsilon(\omega)=1$ and by diamonds otherwise.
 
 The anomalous branching coefficients for the module $L^{(w_2)}$ are shown in the Figure  \ref{fig:A1+A1-A3_branching}.
-The anomalous branching coefficients in the $C_{\frak{a}}$ are equal to the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$ and are shown by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
+Inside the chamber $\bar{C_{\mathfrak{a}}}$ the anomalous branching coefficients coinside with
+the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$
+and are marked by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
 %\begin{figure}[h!tb]
@@
   \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.pdf}
-  \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3}$}
+  \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
   \label{fig:A1+A1-A3_branching}
@@
 
- We get the following branching rules
+Treating analogously the modules $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_3}_{\hat A_3}$
+we get the following set of branching rules
  \begin{equation}
@@
 
-Now we can obtain modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
+Now we can construct the modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
 \begin{multline}
@@
 
-We have chosen this example to illustrate the mechanism of out algorithm. 
-In this case the modules could be reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras.
-We must stress that our method is universal and can be applied for an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.
+By this example we have illustrated the mechanism of our algorithm.
+We want to remind that the proposed method is universal and can be applied to
+an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.
 
@@
 
-Another natural setting where the reduction problem for affine Lie algebras appears is the coset construction of rational conformal field theories \cite{Goddard198588}.
-Coset models are tightly connected with the gauged WZW-models and are actively studied in string theory especially in string models on anti-de-Sitter space \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}.
+Another natural setting where the reduction problem for affine Lie algebras appears is
+the coset construction in rational conformal field theories \cite{Goddard198588}.
+Coset models are tightly connected with the gauged WZW-models and are actively studied
+in string theory especially in string models on anti-de-Sitter space
+\cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}.
 The characters of the coset model are connected with the branching functions,
@@
 
-The problem of the branching functions construction in the coset models was considered in the papers \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.
-It was shown that the branching functions results in cumbersome calculations.
-In what follows we shall demonstrate that these calculations can be simplified by applying the injection fan method.
-
-Let us return to the example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection $A_1 \to  B_2$.
+The problem of the branching functions construction in the coset models was considered
+in  \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.
+
+Let us return to the example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
+$A_1\subset B_2$.
 Since this embedding is regular and $x_e=1$, the level of the  subalgebra modules is equal to that of the initial module.
-
-The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.
-
-Using the definition (\ref{fan-defined}) we get the fan $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
-Here we restricted the computation to the twelfth grade.
+The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection
+on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.
+
+Using the definition (\ref{fan-defined}) we get the fan
+$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$
+with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
+We restricted the computation to the twelfth grade.
 \begin{figure}[h!bt]
@@
 
-Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $w_1=(1,0;1;0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the level of the weight and the fourth is the grade.
-
-The set of the anomalous weights for this module up to the sixth grade is presented in the Figure \ref{fig:affine_B2_anom_point}.
-In the grade 0 it is exactly the set of the anomalous weights for the embedding of the classical Lie algebras $A_1\subset B_2$ depicted in the  Figure \ref{fig:B2_A1}.
+Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $w_1=(1,0;1;0)$,
+where the finite part coordinates are in the orthogonal basis $e_1,e_2$.
+
+The set of anomalous weights for this module up to the sixth grade is presented in the Figure \ref{fig:affine_B2_anom_point}.
+In the grade zero it is exactly the set of the anomalous weights for the embedding of
+the classical Lie algebras $A_1\subset B_2$ depicted in the  Figure \ref{fig:B2_A1}.
 The weights $\omega (w_1+\rho)-\rho$ are marked by crosses if $\epsilon(\omega)=1$ and by circles otherwise.
-Simple roots of classical subalgebra $B_2$ are indicated by grey arrows while the grey diagonal plane is the Cartan subalgebra of the embedded algebra $\hat{A}_1$.
+Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
+of the embedded algebra $\hat{A}_1$.
 
@@
   \includegraphics[width=140mm]{AffineB2_A1_Anom.pdf}
-  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$. The weights of the grade 0 are depicted in the Figure \ref{fig:B2_A1}}.
+  \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$.
+  The weights in the zero grade can be seen in the Figure \ref{fig:B2_A1}}.
   \label{fig:affine_B2_anom_point}
@@
 
-Performing the next step of the algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and find the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
-The result of this computation up to the twelfth grade is presented in the Figure
+Performing the next step of the algorithm \ref{sec:algorithm} we project the anomalous weights to
+$P_{\hat{A_1}}$ and find the dimensions of the corresponding
+$\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+The result is presented in the Figure
+\ref{fig:AffineB2_A1_anom_proj} up to the twelfth grade.
 \ref{fig:AffineB2_A1_anom_proj}.
@@
 $\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
-we get the branching coefficients up to twelfth grade
+we get the branching coefficients up to the twelfth grade,
 \begin{multline}
@@
 \end{multline}
-This result can be presented as the set of branching functions \cite{kac1990idl}.
+This result can be presented as the set of branching functions \cite{kac1990idl}:
 \begin{eqnarray}
@@
 \end{eqnarray}
-Here $q=\exp (2\pi i \tau)$, the lower index enumerates the branching function according to their highest weights in $P^+_{\hat{A_1}}$, these are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
+Here $q=\exp (2\pi i \tau)$, the lower index enumerates the branching functions according
+to their highest weights in $P^+_{\hat{A_1}}$,
+these are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
 
@@
 \end{equation}
-Further amelioration of the construction can be achieved using the folded fan technique \cite{il2010folded}.
-The explicit expression for the branching functions and the corresponding coset characters can be obtained.
+
+Further amelioration of the algorithm can be achieved by using
+the folded fan technique \cite{il2010folded} to get the explicit expression
+for the branching functions and the corresponding coset characters in conformal field theory.
 
@@
 We have shown that the injection fan technique can be used to deal with the nonmaximal subalgebras.
-It was demonstrated that for such injections it is necessary to extract from the set of positive roots $\Delta_{\mathfrak{g}}^{+}$ the auxiliary subset $\Delta^{+}_{\bot}$.
-The injection fan is formed by the weights $\left(\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+}\right) \setminus \Delta^{+}_{\bot}$ and the role of the subset $\Delta^{+}_{\bot}$ is to modify the set of anomalous weights of the initial module.
-This modification reduces to a simple procedure: the anomalous weight multiplicities are to be substituted by the dimensions of the corresponding ${\mathfrak{a}}_{\bot}$-modules.
+It was demonstrated that for such subalgebras an auxiliary subset $\Delta^{+}_{\bot}$ must be extracted
+from the set of positive roots $\Delta_{\mathfrak{g}}^{+}$.
+The role of the subset $\Delta^{+}_{\bot}$ is to modify both the injection fan (formed here by the
+weights $\left(\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+}\right) \setminus \Delta^{+}_{\bot}$)
+and the anomalous weights of the initial module.
+This modification reduces to a simple procedure:
+the anomalous weights multiplicities are to be substituted by the dimensions of the corresponding ${\mathfrak{a}}_{\bot}$-modules.
 
@@
 Its possible applications to some physical problems were discussed.
-In particular we considered the construction of modular-invariant partition functions  in the framework of conformal embedding method and the coset construction of the rational conformal field theory.
-This construction is useful in the study of WZW-models emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
-
-The proposed general approach to the reduction problem also has applications in the study of integrable spin chains.
+In particular we considered the construction of modular-invariant partition functions
+in the framework of conformal embedding method and the coset construction in the rational conformal field theory.
+This construction is useful in the study of WZW-models
+emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
+
+The presented technique to the reduction problem can also be applied in the study of integrable spin-chains.
 

### 2010-07-01 AffineLieAlgebras/InformalNotes/article.tex
All the V.D.'s changes merged, images improved, paper size greatly reduced (to 30 pages).

@@
 
-We demonstrate that our algorithm can be used in the study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some physical limitations.
-In the study of the coset construction of rational conformal field theory the algorithm is useful for the computation of the characters and states.
+We demonstrate that our algorithm can be used in studies of conformal embeddings and coset constructions in rational conformal field theory.
 
 The paper is organised as follows.
-In the subsection \ref{sec:notation}  we fix the notations used throughout the paper.
-In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules of algebra $\mathfrak{g}$ with respect to a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}).
-In the Section \ref{sec:finite-dimens-lie} we present several simple examples for finite-dimensional Lie algebras to illustrate the algorithm.
-Then we consider the affine Lie algebras with the applications in CFT models (Section \ref{sec:phys-appl}).
+In the subsection \ref{sec:notation}  we fix the notations.
+In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules $L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$ (subsection \ref{sec:algorithm}).
+In the Section \ref{sec:finite-dimens-lie} we present several simple examples for finite-dimensional Lie algebras.
+The affine Lie algebras and their applications in CFT models are considered in Section \ref{sec:phys-appl}.
 We conclude the paper with a review of obtained results.
@@
 w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
-\circ (\nu +\rho _{a})-\rho _{a}}$ ), (this set is similar to $P_{\mathrm{%
-nice}}^{\prime }\left( \mu \right) $ in \cite{wakimoto2001idl})
+\circ (\nu +\rho _{a})-\rho _{a}}$ ),
 
@@
 
-Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator
-(when it is projected to the subalgebra root space) the injection fan technique can be properly modified.
-The result of this modification is that the generalized recurrent relations for anomalous branching
-coefficients \eqref{eq:21} is to be formulated in the following form:
+Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator $R$
+(when it is projected to the $P_{\mathfrak{a}}$) the injection fan technique \cite{ilyin812pbc} can be properly modified.
+The result is the generalized recurrent relation for anomalous branching
+coefficients \eqref{eq:21}:
 \begin{equation}
@@
    \end{equation}
-Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by the roots of $\mathfrak{g}$
-orthogonal to the root subsystem of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group,
+Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by those roots of $\mathfrak{g}$ that are
+orthogonal $P_{\mathfrak{a}}$, $W_{\bot}$ is the corresponding Weyl group,
 $\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
-of the denominator $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
+of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
 (1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
-is the coefficient of $e^{\gamma}$ in this expansion.
-In the next subsection we study the situation in details and prove the validity of this relation.
-
-In the subsection \ref{sec:algorithm} we  shall describe the  computational algorithm for  branching coefficients
-based on this formula and present some examples.
+is the multiplicity of $e^{\gamma}$ in this expansion.
+In the next subsection we study the situation in details and prove the relation \eqref{eq:1}.
 
@@
 Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
-projection operators $\pi_{\mathfrak{a}}$ that bring the weights of $\mathfrak{g}$ to the weight subspace of $\mathfrak{a}$:
+projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
 \begin{equation}
@@
 The Weyl-Kac character formula leads to
-the equality
+the relation
 \begin{equation}
@@
 
-It is important that the ion of some of positive roots of
-the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the
-root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the
-algebra $\mathfrak{g}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}
+It is important whether there exist the positive roots $\alpha\in \Delta$ such that $\pi_{\mathfrak{a}}\alpha=0$.
+These roots are orthogonal to $P_{\mathfrak{a}}$.
+Let's denote the subset of such roots by $\Delta^{+}_{\bot}
 =\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
@@
 
-Notice that if the set $\Delta^{+}_{\bot}$ is non-empty the Weyl reflections
+Notice that if $\Delta^{+}_{\bot}\neq \emptyset$ the Weyl reflections
 corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup
@@
 \beta\in \Delta^{+}_{\bot}$ and the corresponding Weyl reflections
-$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since roots of the subalgebra
-$\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they
+$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since roots $\beta\in \Delta_{\mathfrak{a}}$ are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$ they
 are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
-So the subgroup $W_{\bot}$ preserves the root system of the subalgebra $\mathfrak{a}$.
-
-Thus we have obtained the root system $\Delta_{\bot}$ which is orthogonal to the root
-system $\Delta_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$ . This root system
+So the subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$.
+
+Thus we have obtained the system $\Delta_{\bot}$ orthogonal $P_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$. It
 can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
 
-Now we are to find out when the subset $\Delta^{+}_{\bot}$ is non-empty
-and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
-
-If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then
-the rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and
-it is clear that $\Delta^{+}_{\bot}$ is empty.
+Now we are to find out when the subset $\Delta^{+}_{\bot}$ is non-empty with the non-trivial subgroup $W_{\bot}$ and the subalgebra $\mathfrak{a}_{\bot}$.
+
+If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then $r_{\mathfrak{a}}=r$ and
+ $\Delta^{+}_{\bot}$ is empty.
 On the other hand
@@
 $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
-The maximal regular embeddings are constructed by the exclusion of one or two roots
-from the extended Dynkin diagram of the algebra. Since this process can give us
-non-connected Dynkin diagrams we can see which roots are orthogonal to the root
-space of non-maximal regular subalgebra $\mathfrak{a}$.  The complete classification of the regular subalgebras for affine Lie algebras can be found in the recent paper \cite{1751-8121-41-36-365204}.
-
-Consider for instance the regular embedding of $A_1\subset B_2$.
-The extended Dynkin diagram of $B_2$ is presented in the Figure \ref{fig:B2Dynkin}.
-\begin{figure}[ph]
-  \centering
-  \includegraphics[width=40mm]{B2_A1_diagram.pdf}
-  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
-  \label{fig:B2Dynkin}
-\end{figure}
-Drop the central node to describe the embedding $A_1\oplus A_1\subset B_2$.
-In this case we have: $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
-
-The simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for a regular
-embedding $\mathfrak{a}\subset \mathfrak{g}$
-when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple can be formulated
-as follows:
-if the Dynkin diagram of $\mathfrak{g}$ can be split into the disconnected
-diagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
+The maximal regular embeddings can be described by the elimination of one or two roots
+from the extended Dynkin diagram of the algebra. When the process gives us
+non-connected diagrams we immediately fix the roots orthogonal to $P_{\mathfrak{a}}$.
+The complete classification of the regular subalgebras for affine Lie algebras can be found in the recent paper \cite{1751-8121-41-36-365204}.
+
+For a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple the sufficient condition for $\Delta^{+}_{\bot}$ to be nontrivial can be formulated as follows:
+if the Dynkin diagram of $\mathfrak{g}$ contains the disconnected
+subdiagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
 then the subset $\Delta_{\bot}$ is non-empty,
-subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the
-$\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.
+subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and
+$\left\{\mathfrak{\bar{a}}_j\right\}$ are the subalgebras of $\mathfrak{a}_{\bot}$.
 
@@
 the subalgebra $\mathfrak{a}_{\bot}$ may be larger than the algebra
-generated by the remaining connected components.
+generated by the remaining connected components of the diagram.
 Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
@@
 into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
-sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to
-$A_1\oplus A_1$ but to $B_2$ (the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).
+sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal to $B_2$ (the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).
 
@@
  Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the remaining nodes of the diagram of $\mathfrak{g}$.
-Consider the remaining diagram.
-This diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ of $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$.
+The remaining diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ with $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$.
 It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$.
-So the question is whether $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them.
+So the question is whether $\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\mathfrak{\bar{a}}$ but the linear combinations of them.
 The answer is positive  when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$.
 Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.
-
-All the cases are listed in the table \ref{tab:diagrams}.
 \begin{table}[ph]
@@
 \end{table}
-
-For the algebra $\mathfrak{g}$ from the series $A_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r+1\}$ are $\Delta=\{\alpha_{ i j}= e_i- e_j,\; 1\leq i, j\leq r+1\}$, $\Delta^{+}=\{\alpha_{ij},\; i<j\}$ and the set of simple roots consists of $\alpha_{1,2},\alpha_{2,3},\dots,\alpha_{r,r+1}$.
-So for the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consisting of first $r_{\mathfrak{a}}$ simple roots we get $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{ i j},\; r_{\mathfrak{a}}+1<i,j\leq r+1\}$ and $\mathfrak{a}_{\bot}=A_{r-r_{\mathfrak{a}}-1}$.
-
-For the algebra $\mathfrak{g}$ from the series $B_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;i<j;\; \alpha_{\pm j}=\pm e_{ j},\; 1\leq j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; \alpha_j;\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_r$.
-So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}-1}$.
-Otherwise if $\mathfrak{a}=B_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_r$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
+If $\mathfrak{a}=B_{r_{\mathfrak{a}}}$  we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
 This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.
-There exists the third possibility to get the pair of subalgebras $\mathfrak{a},\mathfrak{a}_{\bot}$ with the regular subalgebra $\mathfrak{a}$ by dropping the single node from the extended Dynkin diagram of $B_r$.
-This can be done by choosing the set of simple roots of $\mathfrak{a}$ in the form $\{\alpha_{1,-2},\alpha_{1,2},\alpha_{2,-3},\dots,\alpha_{r_{\mathfrak{a}}-1,-r_{\mathfrak{a}}}\}$.
-Then $\mathfrak{a}=D_{r_{\mathfrak{a}}}$, $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
-
-For the algebra $\mathfrak{g}$ from the series $C_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;i<j;\; \alpha_{\pm j}=\pm 2e_{ j},\; 1\leq j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; \alpha_j;\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_r$.
-So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=C_{r-r_{\mathfrak{a}}-1}$.
-Otherwise if $\mathfrak{a}=C_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_r$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=C_{r-r_{\mathfrak{a}}}$.
-
-For the algebra $\mathfrak{g}$ from the series $D_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;1\leq i<j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_{r-1,r}$.
-So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=D_{r-r_{\mathfrak{a}}-1}$.
-Otherwise if $\mathfrak{a}=D_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_{r-1,r}$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=D_{r-r_{\mathfrak{a}}}$.
-
-In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
-special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted in the Figure \ref{fig:a1a2a3}. 
-\begin{figure}[h]
-\noindent  \centering{
-  \includegraphics[width=80mm]{special_A1_A2_A3.pdf}
-  \caption{Special embedding $A_1\subset A_2\subset A_3$.
-Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
-}
-  \label{fig:a1a2a3}
-\end{figure}
-
-Using the existing classification of maximal special subalgebras \cite{dynkin1952semisimple} we immediately have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
+
+Using the existing classification of maximal special subalgebras in classical Lie algebras \cite{dynkin1952semisimple} we have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
 \begin{equation}
@@
 
-Up to this point we considered the problem of constructing the subalgebra $\mathfrak{a}_{\bot}$ for a given regular injection $\mathfrak{a}\in\mathfrak{g}$  in terms of Dynkin diagrams.
-When the root systems $ \Delta$ and $\Delta_{\mathfrak{a}}$ are known explicitly all that we need is to select the roots
-$\Delta_{\bot}=\left\{\alpha\in \Delta:\alpha\bot \Delta_{\mathfrak{a}}\right\}$ and correspondingly the positive roots
-$\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$.
-
 Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
@@
 \end{equation}
-Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ is the single element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
+Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
 
@@
 \end{equation}
-Taking into account that the projection commutes with the multiplication,
-\begin{equation}
-  \label{eq:6}
-  \pi_{\mathfrak{a}} (Q) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(Q\cdot (1-e^{-\alpha})\right),
-\end{equation}
-we can rewrite the
-product of (\ref{eq:4}) and (\ref{eq:5}):
+and take into account that the projection commutes with the multiplication:
 \begin{multline}
@@
 \end{multline}
-The right-hand side of this equation can be reorganised similarly to what was performed in the paper \cite{ilyin812pbc}, by introducing the anomalous branching coefficients $k_{\lambda}$,
+Similarly to the transformation proposed in \cite{ilyin812pbc} we introduce the anomalous branching coefficients $k_{\lambda}$,
 \begin{equation}
@@
 \end{equation}
-and simplifying the multiplier:
+and simplify the first factor,
 \begin{multline}
@@
 
-If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of the Weyl group $W$.
-Let us reorganise the summation in the left-hand side of (\ref{eq:12}).
+If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}\subset W$.
 Consider the factor-space $W_{\bot}\backslash W$.
@@
 \end{multline}
-The fraction in the right-hand side of the equation is similar to the character of some  $\mathfrak{a}_{\bot}$-module.
-Let us rewrite the shifted weights
+The fraction in the right-hand side of the equation looks like the character of some  $\mathfrak{a}_{\bot}$-module.
+Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we can rewrite the shifted weights
 \begin{equation}
   \label{eq:30}
-  \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}+\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho
-\end{equation}
-
-Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we get
+  \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}+\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho
+\end{equation}
+
 \begin{multline}
@@
 \end{multline}
-The projector $\pi_{\mathfrak{a}}$ transforms the character ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ into the unit element of $\cal{E}$ multiplied by ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$  :
+The projector $\pi_{\mathfrak{a}}$ sends the character ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ to the unit element of $\cal{E}$ multiplied by ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$  :
   \begin{multline}
@@
   \end{multline}
-Thus we obtained  the relation
+Thus we obtain the relation
 \begin{multline}
@@
 \end{multline}
-Let us rewrite the multiplier in the right-hand side:
+Let us rewrite the factor in the right-hand side:
 \begin{equation}
@@
 \end{equation}
-From the obtained equation for the formal elements,
+From the relation \eqref{eq:9} the obtained equation for the formal elements,
 \begin{multline}
@@
   = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
-  k_{\lambda }^{\left( \mu \right) }e^{\lambda } \\
+  k_{\lambda }^{\left( \mu \right) }e^{\lambda } =\\
   =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma }
@@
 \end{equation}
-then the equality (\ref{eq:17}) leads to the desired recurrent  relation for the anomalous branching coefficients:
+the equality (\ref{eq:17}) leads to the desired recurrent  relation for the anomalous branching coefficients:
 \begin{multline}
@@
 
-Now consider the case  $\Delta_{\bot}^{+} = 0$.
+Consider the case  $\Delta_{\bot}^{+} = 0$.
 There are three different reasons for $\Delta_{\bot}^{+}$ to be empty: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$, ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
 Both the first and the second cases can be treated as corresponding to the trivial orthogonal subalgebra:
-$\mathfrak{a}_{\bot}=0$. In any of these cases instead of the formal characters in the right-hand side of (\ref{eq:13}) we obtain the formal element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$.
-In the first two cases (equivalent to $\mathfrak{a}_{\bot}=0$) the projection operator retains its purely geometrical meaning: the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
+$\mathfrak{a}_{\bot}=0$. In any of these cases the formal characters in the right-hand side of (\ref{eq:13}) reduces to the formal element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$.
+In the first two cases the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
 It is clear that in any of the three variants the final vector $\pi_{\mathfrak{a}}\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)$ leads to the unit of the formal algebra
@@
 
-  In the next section we describe a computation algorithm for branching coefficients based on the relation \eqref{recurrent-relation}.
-
 \subsection{Algorithm for the recursive computation of the branching coefficients}
@@
 \begin{enumerate}
-\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{a} \subset \mathfrak{g}$.
-\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
+\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{g} \supset \mathfrak{a}$.
+\item Select the positive roots $\alpha\in \Delta^{+}$ orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
 \item Construct the set $\Gamma$ \eqref{fan-defined}.
-\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$, it must be non-negative.
+\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights for the $\mathfrak{g}$-module $L^{(\mu)}$.
+\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$.
 \item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
@@
 
-If we are interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous weights up to the required grade and use the steps 4-7 of the algorithm for each grade.
+When are interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous weights up to the required grade and use the steps 4-7 of the algorithm for each grade.
 We can also speed up the algorithm by one-time computation of the representatives of the conjugate classes $W_{\bot}\backslash W$.
@@
 
-\section{Finite dimensional Lie algebras}
+\section{Branching for finite dimensional Lie algebras}
 \label{sec:finite-dimens-lie}
@@
 
-Consider the regular embedding of $A_1$ into $B_2$.
-Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the dashed vectors in the Figure \ref{fig:B2_A1}.
+Consider the regular embedding of $A_1\to B_2$.
+Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors in the Figure \ref{fig:B2_A1}.
 We denote the corresponding Weyl reflections by $\omega_1, \omega_2$.
-Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+2\alpha_2$ and is drawn as the grey vector.
-
-Let's describe the reduction of the fundamental representation of $B_2$ with the highest weight equal to $(1,0)$ (in the fundamental weight basis), it is drawn as the black vector in the Figure \ref{fig:B2_A1}.
+The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
+
+Let's describe the reduction of the fundamental representation of $L^{(1,0)=w_1}_{B_2}$ (the black vector in Figure \ref{fig:B2_A1}).
 \begin{figure}[th]
@@
 \end{figure}
-There we have also shown the set of weights $\omega(\mu+\rho)-\rho,\; \omega\in W$ of the fundamental representation of $B_2$ with the corresponding determinants $\epsilon(\omega)$ of Weyl transformations.
-Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
+Circles indicate the weights of the singular element $\Psi^{(w_1)}$.
+Now we are to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$ and to construct the set $\left\{\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W\right\}$. 
 \begin{figure}[t]
@@
 \end{figure}
-We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
-Then we project these weights and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous weights in fundamental weights basis with corresponding multiplicities:
+On the Figure \ref{fig:B2_A1_2} the weights of  the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ are indicated.
+Projecting them onto the root space of the subalgebra $\mathfrak{a}=A_1$ we get the anomalous weights with the corresponding multiplicities:
 \begin{equation}
@@
 \end{equation}
-For the function $s(\gamma)$ and the set $\Gamma$ (using the definition (\ref{phi-d},\ref{fan-defined})) we have
+For the set $\Gamma$ (using the definition (\ref{phi-d},\ref{fan-defined})) we have
 \begin{equation}
   \label{eq:22}
-  (1,2),\; (2,-1)
+  \Gamma_{A_1\subset B_2}=\left\{ (1,2),\; (2,-1) \right\}.
 \end{equation}
 Here the second component denotes the value of $s(\gamma)$.
-
-As far as the anomalous branching coefficient $k^{(1,0)}_{1}=2$ for the coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent-relation}) gives the value
+Applying this fan inside the $\bar{C}^{(0)}_{\mathfrak{a}}$ we get zeros for the weights greater than the first anomalous vector $(1)$, here $k^{(1,0)}_1=2$.
+For the last weight in $\bar{C}^{(0)}_{\mathfrak{a}}$ the formula (\ref{recurrent-relation}) gives
 \begin{equation}
@@
 Consider the regular embedding $B_2 \longrightarrow B_4$.
-We calculate the branching coefficients for the fundamental vector representation of $B_4$.
-The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
+The corresponding Dynkin diagrams are presented in the Figure \ref{fig:dynkin}.
 \begin{figure}[h]
@@
   \includegraphics[width=50mm]{B4_B2_2A1.pdf}
-  \caption{Dynkin diagrams for the regular embedding $B_2\subset B_4$. Note the dropped node and the roots of $\mathfrak{a}_{\bot}$. }
+  \caption{The regular embedding $B_2\subset B_4$ described by dropping the node.}
   \label{fig:dynkin}
@@
 
-In the orthogonal basis $e_1,\dots,e_4$ the simple roots of $B_4$ are
+In the orthogonal basis $\left\{e_1,\dots,e_4\right\}$ the simple roots and the positive roots of $B_4$ are
 \begin{equation}
   \label{eq:8}
-  (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4)
-\end{equation}
-The positive roots are
+ S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\}
+\end{equation}
 \begin{multline}
   \label{eq:19}
-  (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\\
-    e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2)
-\end{multline}
-The simple roots of the embedded subalgebra $\mathfrak{a}=B_2$ are
+ \Delta^+_{B_4}=\left\{ (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\right.\\
+ \left. e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2\right\}
+\end{multline}
+Correspondingly for the embedded subalgebra $\mathfrak{a}=B_2$ we have
 \begin{equation}
   \label{eq:26}
-  (e_3-e_4,e_4)
-\end{equation}
-
-The set $\Delta^{+}_{\bot}$ contains the roots
+ S_{B_2}=\{e_3-e_4,e_4\}
+\end{equation}
 \begin{equation}
   \label{eq:27}
-  \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
+ \Delta^{+}_{\bot}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
 \end{equation}
@@
   \centering
-    \includegraphics[width=90mm,height=90mm]{B4_B2_anom_points.pdf}
-  \caption{Projected weights of $\pi_{B_2}\left(\Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
+    \includegraphics[width=100mm,height=90mm]{B4_B2_anom_points.pdf}
+  \caption{Projected weights $-\frac{1}{s(\gamma_0)}\pi_{B_2}\left(\hat \Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
   \label{fig:B4B2anom}
@@
 
-Firstly we construct the fan for this injection.
-Using the definition (\ref{fan-defined}) we obtain the set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted in the Figure \ref{fig:B4B2Fan}.
-
-To find the branching coefficients we need to compute the anomalous weights of $B_4$, select the weights belonging to $C^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$ and compute the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.
+Using the definition (\ref{fan-defined}) we obtain the fan $\Gamma_{B_2\subset B_4}$ with the corresponding values $s(\gamma+\gamma_0)$, depicted in the Figure \ref{fig:B4B2Fan}.
 
 Consider the $B_4$-module $L^{\mu}$ with the highest weight $\mu=(0,1,0,2)=2
-e_1 + 2 e_2 + e_3 + e_4$; $dim(L^{(0,1,0,2)})=2772$.
-
+e_1 + 2 e_2 + e_3 + e_4$; $\mathrm{dim}(L^{(0,1,0,2)})=2772$.
+
+To find the branching coefficients we need to compute the anomalous weights of $L^{\mu}_{B_4}$, select the weights belonging to $\bar{C}^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$ and compute the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.
 The set of the anomalous weights $\left\{ \omega(\mu+\rho)-\rho,\; \omega\in W\right\}$
-contains of 384 vectors.
+contains 384 vectors.
 
@@
 onto the root space $\Delta^{+}_{\bot}$, substract
-$\rho_{\mathfrak{a}_{\bot}}$ and apply the Weyl dimension formula.
-
-The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.
+$\rho_{\mathfrak{a}_{\bot}}$ and apply the Weyl dimension formula. The result is shown in the Figure \ref{fig:B4B2anom}.
 
@@
 \end{multline}
-
+\newpage
 \section{Applications to the conformal field theory}
@@
 \end{equation}
-Here the sum is over the set of the highest weights of integrable modules of WZW-model and $\chi_{\mu}(\tau)$ are the modified characters of these modules.
-
-The task of the construction of non-diagonal modular invariants is not easy, although the complete classification of modular invariants for some models is known \cite{1994hepthGannon,1995JMPGannon}.
+Here the sum is over the set of the highest weights of integrable modules of WZW-model and $\chi_{\mu}(\tau)$ are the normalized characters of these modules.
+
+To construct the non-diagonal modular invariants is not an easy problem, although for some model the complete classification of modular invariants is known \cite{1994hepthGannon,1995JMPGannon}.
 
@@
 containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules.
-Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$.
+Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$,
 \begin{equation}
@@
 \end{equation}
-The reduction of the representations is crucial in this construction.
-
-For the construction to be valid the embedding is required to preserve conformal invariance.
-Let $X^{a_j}_{-n_j}$ and $\tilde{X}^{a'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and for $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
+The effective reduction procedure is crucial for this construction.
+
+The embedding is required to preserve the conformal invariance.
+Let $X^{\alpha_j}_{-n_j}$ and $\tilde{X}^{\alpha'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and for $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
 Let $\pi_{\mathfrak{a}}$ be the projection operator of $\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$.
@@
   \label{eq:109}
-  X^{a_1}_{-n_1}X^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+  X^{\alpha_1}_{-n_1}X^{\alpha_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
 \end{equation}
@@
   \label{eq:110}
-  \tilde{X}^{a'_1}_{-n_1}\tilde{X}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
+  \tilde{X}^{\alpha'_1}_{-n_1}\tilde{X}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
 \end{equation}
@@
 \end{equation}
-which leads to the equality of the central charges 
+leads to the equality of the central charges 
 \begin{equation}
   \label{eq:33}
-  c(\mathfrak{g})=c(\mathfrak{a}).
-\end{equation}
-This leads to the equation
+  c(\mathfrak{g})=c(\mathfrak{a})
+\end{equation}
+and to the equation
 \begin{equation}
@@
 
-The complete classification of conformal embeddings is given in the paper \cite{schellekens1986conformal}.
+The complete classification of conformal embeddings is given in \cite{schellekens1986conformal}.
 
@@
 \begin{note} The orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
-\begin{proof} It can be seen from the following consideration. In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
-The energy-momentum tensor can be expanded into the modes $L_n$
+\begin{proof} 
+Consider the modes expansion of the energy-momentum tensor
 \begin{equation}
@@
 \end{equation}
-The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
+
+The modes $L_n$ are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
 \begin{equation}
 \label{eq:48}
-  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
-\end{equation}
-The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$.
-But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
+  L_n=\frac{1}{2(k+h^v)}\sum_{\alpha}\sum_m:X^{\alpha}_m X^{\alpha}_{n-m}:
+\end{equation}
+In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
+
+The substitution of the generators of $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations  should give the energy-momentum tensor $T_{\mathfrak{g}}$.
+But if the set of the generators $\Delta_{\bot}$ is not empty this is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$.
 \end{proof}
@@
 We limit our calculations by the first 5 grades.
-%\begin{figure}[h!tb]
-\begin{figure}[p]
+\begin{figure}[h!tb]
+%\begin{figure}[p]
 %  \hspace*{-1cm}
@@
 and are marked by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
-%\begin{figure}[h!tb]
-\begin{figure}[p]
+\begin{figure}[h!tb]
+%\begin{figure}[p]
 %  \hspace*{-1cm}

### 2010-07-01 AffineLieAlgebras/InformalNotes/article.tex
PDF regen

@@
 To construct this injection we use the method presented in \cite{vasilevich1986method}.
-We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$.
-Its diagram $\mathcal{N}_{A_1\oplus A_1}^{(1,1)}
-= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$
+We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$. Its diagram
+$$\mathcal{N}_{A_1\oplus A_1}^{(1,1)}= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$$
 is presented in Figure \ref{fig:A_1+A_1_to_A3}.

### 2010-07-05 AffineLieAlgebras/InformalNotes/article.tex
pdf insured for pdflatex
Update to arXiv version
Compilation to dvi with eps images in IOP style is successful, paper size is 24 pages. Note that the renaming of figures is required.

@@
-\documentclass[a4paper,12pt]{article}
+\documentclass[12pt]{iopart}
 \usepackage{ucs}
-\usepackage{amsmath,amssymb,amsthm}
-\usepackage{pb-diagram}
+%\usepackage{amsmath,amssymb,amsthm}
+\usepackage{iopams,amssymb,amsthm}
+%\usepackage{pb-diagram}
 \usepackage{multicol}
@@
 \usepackage{graphicx}
-\pagestyle{plain}
-\usepackage[unicode,verbose,plainpages=false]{hyperref}
+%\pagestyle{plain}
+%\usepackage[unicode,verbose,plainpages=false]{hyperref}
+\usepackage{hyperref}
 
 %\usepackage{verbatim} 
-\newenvironment{comment}
-{\par\noindent{\bf TODO}\\}
-{\\\hfill$\scriptstyle\blacksquare$\par}
+%\newenvironment{comment}
+%{\par\noindent{\bf TODO}\\}
+%{\\\hfill$\scriptstyle\blacksquare$\par}
 
 \newtheorem{statement}{Statement}
-\newtheorem{note}{Note}[section]
-\theoremstyle{definition} \newtheorem{Def}{Definition}
-\newcommand{\go}{\overset{\circ }{\frak{g}}}
-\newcommand{\ao}{\overset{\circ }{\frak{a}}}
-\newcommand{\co}[1]{\overset{\circ }{#1}}
+\newtheorem{mynote}{Note}[section]
+%\theoremstyle{definition} \newtheorem{Def}{Definition}
+\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
+\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
+\newcommand{\co}[1]{\stackrel{\circ }{#1}}
 
 \begin{document}
-\pagenumbering{alph}
-\thispagestyle{empty}
-
-\begin{center}
-{\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
-\end{center}
-\vskip 1 cm
-\begin{flushright}
-{\large \bf SPbU-IP-10-03}
-\end{flushright}
-\hfill {}
-\vskip 1 cm
-\begin{center}
-{\Huge \bf Recursive algorithms, branching coefficients \\ and applications\\[0.5cm]
-}
-\end{center}
-\vskip 1.0 cm
-\begin{center}
-{\Large \bf
-Vladimir Lyakhovsky\\[2mm]
-Anton Nazarov}
-\end{center}
-\vfill
-\begin{center}
-{\large Department of Theoretical Physics\\
-}
-\end{center}
-\vfill
-\begin{center}
-SAINT-PETERSBURG \\
-2010
-\end{center}
-
-\newpage
-
-\pagenumbering{arabic}
-\title{\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}}
-\author{Vladimir Lyakhovsky \thanks{ Supported by
- RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
-Theoretical Department, SPb State University,\\
-198904, Sankt-Petersburg, Russia \\
-e-mail:lyakh1507@nm.ru \\
-[5mm] Anton Nazarov \thanks{ Supported by
-the National Project RNP.2.1.1./1575 }\\
-Theoretical Department, SPb State University,\\
-198904, Sankt-Petersburg, Russia \\
-e-mail:antonnaz@gmail.com
-}
-%\maketitle
+% \pagenumbering{alph}
+% \thispagestyle{empty}
+% 
+% \begin{center}
+% {\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
+% \end{center}
+% \vskip 1 cm
+% \begin{flushright}
+% {\large \bf SPbU-IP-10-03}
+% \end{flushright}
+% \hfill {}
+% \vskip 1 cm
+% \begin{center}
+% {\Huge \bf Recursive algorithms, branching coefficients \\ and applications\\[0.5cm]
+% }
+% \end{center}
+% \vskip 1.0 cm
+% \begin{center}
+% {\Large \bf
+% Vladimir Lyakhovsky\\[2mm]
+% Anton Nazarov}
+% \end{center}
+% \vfill
+% \begin{center}
+% {\large Department of Theoretical Physics\\
+% }
+% \end{center}
+% \vfill
+% \begin{center}
+% SAINT-PETERSBURG \\
+% 2010
+% \end{center}
+% 
+% \newpage
+% 
+% \pagenumbering{arabic}
+\title{Recursive algorithms, branching coefficients and applications}
+\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$} 
+\address{$^{1,2}$ Theoretical Department, SPb State University,
+198904, Sankt-Petersburg, Russia }
+\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}
+% \thanks{ Supported by
+%  RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
+% 
+% \thanks{ Supported by
+% the National Project RNP.2.1.1./1575 }
 
@@
 \end{abstract}
+\submitto{\JPA}
+%\maketitle
 
@@
 $r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
-\left( \text{resp. }\frak{a}\right) $ ;
+\left( \mbox{resp. }\frak{a}\right) $ ;
 
 $\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
-^{+} $ $\left( \text{resp. }\Delta _{\frak{a}}^{+}\right) $--- the positive
+^{+} $ $\left( \mbox{resp. }\Delta _{\frak{a}}^{+}\right) $--- the positive
 root system (of $\frak{g}$ and $\frak{a}$ respectively);
@@
 $\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ --- the
-weight diagram of $L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right)
+weight diagram of $L^{\mu }$ $\left( \mbox{resp. }L_{\frak{a}}^{\nu }\right)
 $ ;
@@
 $\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $i
-$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \text{resp. }\frak{a}%
+$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\frak{a}%
 \right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
@@
 $\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
-}\right) $--- the basic coroot for $\frak{g}$ $\left( \text{resp. }\frak{a}%
+}\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\frak{a}%
 \right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
@@
 $\co{\xi }$ , $\co{\xi _{\left( \frak{a}\right) }}$
---- the finite (classical) part of the weight $\xi \in P$ , $\left( \text{%
+--- the finite (classical) part of the weight $\xi \in P$ , $\left( \mbox{%
 resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $;
@@
 
-$P$ $\left( \text{resp. } P_{\frak{a}}\right) $ \ --- the weight lattice;
-
-$M \left( \text{resp. }M_{\frak{a}}\right) :=$
+$P$ $\left( \mbox{resp. } P_{\frak{a}}\right) $ \ --- the weight lattice;
+
+$M \left( \mbox{resp. }M_{\frak{a}}\right) :=$
 
@@
 \begin{array}{c}
-\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\text{ }\left( \text{resp. }%
+\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\mbox{ }\left( \mbox{resp. }%
 \sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \frak{a}\right) i}^{\vee }\right)
-\text{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
-\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\text{ }\left( \text{resp. }\sum_{i=1}^{r}%
-\mathbf{Z}\alpha _{\left( \frak{a}\right) i}\right) \text{for }A_{r}^{\left(
-u\geq 2\right) }\text{ and }A\neq A_{2r}^{\left( 2\right) },
+\mbox{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
+\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\mbox{ }\left( \mbox{resp. }\sum_{i=1}^{r}%
+\mathbf{Z}\alpha _{\left( \frak{a}\right) i}\right) \mbox{for }A_{r}^{\left(
+u\geq 2\right) }\mbox{ and }A\neq A_{2r}^{\left( 2\right) },
 \end{array}
@@
 a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
-\xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
-L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
+\xi \in P$ $\left( \mbox{resp. }\in P_{\frak{a}}\right) $ for the module $%
+L^{\mu }$ $\left( \mbox{resp. }L_{\frak{a}}^{\nu }\right) $ with the
 coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
@@
 $m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
-}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \text{%
+}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mbox{%
 resp. }\in P_{\frak{a}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
@@
 
-$ch\left( L^{\mu }\right) $ $\left( \text{resp. }ch\left( L_{\frak{a}}^{\nu
-}\right) \right) $--- the formal character of $L^{\mu }$ $\left( \text{resp. }%
+$ch\left( L^{\mu }\right) $ $\left( \mbox{resp. }ch\left( L_{\frak{a}}^{\nu
+}\right) \right) $--- the formal character of $L^{\mu }$ $\left( \mbox{resp. }%
 L_{\frak{a}}^{\nu }\right) $;
@@
 
-\noindent $\left( \text{resp. }R_{\frak{a}}:=\prod_{\alpha \in \Delta _{%
+\noindent $\left( \mbox{resp. }R_{\frak{a}}:=\prod_{\alpha \in \Delta _{%
 \frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{%
@@
 The result is the generalized recurrent relation for anomalous branching
-coefficients \eqref{eq:21}:
+coefficients \ref{eq:21}:
 \begin{equation}
@@
 is the multiplicity of $e^{\gamma}$ in this expansion.
-In the next subsection we study the situation in details and prove the relation \eqref{eq:1}.
+In the next subsection we study the situation in details and prove the relation \ref{eq:1}.
 
@@
   \hline
-  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
+  $A_n$ & \includegraphics{A_series_ext_diag.eps} & \includegraphics{A_series_ext_split.eps} \\
   \hline
-  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\
+  $B_n$ & \includegraphics{B_series_ext_diag.eps} & \includegraphics{B_series_ext_split.eps} \\
   \hline
-  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
+  $C_n$ & \includegraphics{C_series_ext_diag.eps} & \includegraphics{C_series_ext_split.eps} \\
   \hline
-  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
+  $D_n$ & \includegraphics{D_series_ext_diag.eps} & \includegraphics{D_series_ext_split.eps} \\
   \hline
@@
       sp(2p)\oplus so(q) & \subset sp(2pq)&\\
-      so(p)\oplus so(q) & \subset so(p+q)& \text{for}\;p\;\text{and}\;q\;\text{odd}\\
+      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}\\
   \end{array}
@@
 and take into account that the projection commutes with the multiplication:
-\begin{multline}
+\begin{eqnarray*}
   \label{eq:7}
@@
   \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
-\end{multline}
+\end{eqnarray*}
 Similarly to the transformation proposed in \cite{ilyin812pbc} we introduce the anomalous branching coefficients $k_{\lambda}$,
@@
 and simplify the first factor,
-\begin{multline}
+\begin{eqnarray*}
   \label{eq:12}
@@
     \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
-\end{multline}
+\end{eqnarray*}
 
@@
 For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
-\begin{multline}
+\begin{eqnarray*}
   \label{eq:13}
@@
  \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
-\end{multline}
+\end{eqnarray*}
 The fraction in the right-hand side of the equation looks like the character of some  $\mathfrak{a}_{\bot}$-module.
@@
 
-\begin{multline}
+\begin{eqnarray*}
   \label{eq:14}
@@
   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
-\end{multline}
+\end{eqnarray*}
 The projector $\pi_{\mathfrak{a}}$ sends the character ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ to the unit element of $\cal{E}$ multiplied by ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$  :
-  \begin{multline}
+  \begin{eqnarray*}
     \label{eq:15}
@@
     \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
-  \end{multline}
+  \end{eqnarray*}
 Thus we obtain the relation
-\begin{multline}
+\begin{eqnarray*}
   \label{eq:9}
@@
   \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
-\end{multline}
+\end{eqnarray*}
 Let us rewrite the factor in the right-hand side:
@@
 \end{equation}
-From the relation \eqref{eq:9} the obtained equation for the formal elements,
-\begin{multline}
+From the relation \ref{eq:9} the obtained equation for the formal elements,
+\begin{eqnarray*}
   \label{eq:16}
@@
   =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma }
-\end{multline}
+\end{eqnarray*}
 we can deduce the following property of the anomalous branching coefficients,
-\begin{multline}
+\begin{eqnarray*}
   \label{eq:17}
@@
    \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\\ \xi\in P_{\mathfrak{a}}.
-\end{multline}
+\end{eqnarray*}
 
@@
 the equality (\ref{eq:17}) leads to the desired recurrent  relation for the anomalous branching coefficients:
-\begin{multline}
+\begin{eqnarray*}
   k_{\xi }^{\left( \mu \right) }=
@@
 \label{recurrent-relation}
-\end{multline}
+\end{eqnarray*}
 where the set
@@
 
-The recurrent relation \eqref{recurrent-relation} allows us to formulate an algorithm for recursive computation of the branching coefficients.
+The recurrent relation \ref{recurrent-relation} allows us to formulate an algorithm for recursive computation of the branching coefficients.
 In this algorithm there is no need to  construct the module $L^{(\mu)}_{\mathfrak{g}}$ or any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
@@
 \item Select the positive roots $\alpha\in \Delta^{+}$ orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\Gamma$ \eqref{fan-defined}.
+\item Construct the set $\Gamma$ \ref{fan-defined}.
 \item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights for the $\mathfrak{g}$-module $L^{(\mu)}$.
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{B2_A1.pdf}
+    \includegraphics[width=80mm]{B2_A1.eps}
   }
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{B2_A1_2.pdf}
+    \includegraphics[width=80mm]{B2_A1_2.eps}
   }
@@
   \centering
-  \includegraphics[width=50mm]{B4_B2_2A1.pdf}
+  \includegraphics[width=50mm]{B4_B2_2A1.eps}
   \caption{The regular embedding $B_2\subset B_4$ described by dropping the node.}
@@
 \end{equation}
-\begin{multline}
+\begin{eqnarray*}
   \label{eq:19}
@@
  \left. e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2\right\}
-\end{multline}
+\end{eqnarray*}
 Correspondingly for the embedded subalgebra $\mathfrak{a}=B_2$ we have
@@
 and is the set of positive roots for the algebra $\mathfrak{a}_{\bot}=B_2$.
-\begin{figure}[p]
+\begin{figure}[t]
   \centering
-    \includegraphics[width=100mm,height=90mm]{B4_B2_anom_points.pdf}
+    \includegraphics[width=100mm,height=90mm]{B4_B2_anom_points.eps}
   \caption{Projected weights $-\frac{1}{s(\gamma_0)}\pi_{B_2}\left(\hat \Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
@@
 
-\begin{figure}[p]
+\begin{figure}[b]
   \centering
-  \includegraphics[height=80mm]{B4_B2_fan.pdf}
+  \includegraphics[height=80mm]{B4_B2_fan.eps}
   \caption{The fan for $B_2\subset B_4$}
@@
 following branching coefficients:
-\begin{multline}
+\begin{eqnarray*}
   \label{eq:24}
@@
   40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}.
-\end{multline}
-\newpage
+\end{eqnarray*}
+%\newpage
 \section{Applications to the conformal field theory}
@@
 
-\begin{note} The orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
+\begin{mynote} The orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
 \begin{proof} 
@@
 \end{proof}
-\end{note}
+\end{mynote}
 \subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
@@
   \centering
-  \includegraphics[width=135mm]{AffineA2_A1_fan.pdf}
+  \includegraphics[width=135mm]{AffineA2_A1_fan.eps}
   \caption{The fan and $s(\gamma+\gamma_0)$ for $\hat{A_1}\longrightarrow \hat{A_2}$}
@@
 %  \hspace*{-2cm}
-  \includegraphics[width=140mm]{AffineA2_A1_anom.pdf}
+  \includegraphics[width=140mm]{AffineA2_A1_anom.eps}
   \caption{The anomalous weights of the module $L^{(0,0;1;0)}_{\hat{A_2}}$}
@@
   \centering
-  \includegraphics[width=130mm]{AffineA2_A1_proj_anom.pdf}
+  \includegraphics[width=130mm]{AffineA2_A1_proj_anom.eps}
   \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$.}
@@
   \centering
-  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
+  \includegraphics[width=130mm]{AffineA2_A1_branching.eps}
   \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
@@
     \hfill
-    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
+    \includegraphics[width=50mm]{A_1+A_1_to_A3.eps}
     \hfill
@@
     \hfill
-    \includegraphics[width=50mm]{A1+A1-A3.pdf}
+    \includegraphics[width=50mm]{A1+A1-A3.eps}
     \hfill
@@
 \begin{figure}[h!tb]
-  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
+  \includegraphics[width=135mm]{A1+A1-A3_fan.eps}
   \caption{The fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
@@
 We limit our calculations by the first 5 grades.
-\begin{figure}[h!tb]
+\begin{figure}[t]
 %\begin{figure}[p]
 %  \hspace*{-1cm}
-  \includegraphics[width=135mm]{A1+A1-A3_anom.pdf}
+  \includegraphics[width=135mm]{A1+A1-A3_anom.eps}
   \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
@@
 and are marked by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
-\begin{figure}[h!tb]
+\begin{figure}[b]
 %\begin{figure}[p]
 %  \hspace*{-1cm}
-  \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.pdf}
+  \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.eps}
   \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
@@
      L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
-     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
+     L^{(0,1,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
      L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
@@
 Now we can construct the modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
-\begin{multline}
+\begin{eqnarray*}
   \label{eq:40}
@@
   \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
-\end{multline}
+\end{eqnarray*}
 
@@
   \centering
-  \includegraphics[width=135mm]{AffineB2_A1_fan.pdf}
+  \includegraphics[width=135mm]{AffineB2_A1_fan.eps}
   \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
@@
 %  \hspace*{-2cm}
-  \includegraphics[width=140mm]{AffineB2_A1_Anom.pdf}
+  \includegraphics[width=140mm]{AffineB2_A1_Anom.eps}
   \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$.
@@
 \ref{fig:AffineB2_A1_anom_proj}.
-\begin{figure}[p]
+\begin{figure}[h!tb]
   \centering
-  \includegraphics[width=120mm]{AffineB2_A1_proj_anom.pdf}
+  \includegraphics[width=120mm]{AffineB2_A1_proj_anom.eps}
   \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$ and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
@@
 
-\begin{figure}[p]
+\begin{figure}[h!bt]
   \centering
-  \includegraphics[width=120mm]{AffineB2_A1_branching.pdf}
+  \includegraphics[width=120mm]{AffineB2_A1_branching.eps}
   \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
@@
 we get the branching coefficients up to the twelfth grade,
-\begin{multline}
+\begin{eqnarray*}
   \label{eq:28}
-  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
-    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
-    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
-    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
-    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
-    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
-    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
-    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
-    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
-    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
-    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
-    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
-    1180 L_{\hat{A_1}}^{w_0}(-12)
-\end{multline}
+  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}\oplus 1 L_{\hat{A_1}}^{w_0}\oplus 4 L_{\hat{A_1}}^{w_0-\delta}\oplus\\
+    2 L_{\hat{A_1}}^{w_1-\delta}\oplus 8 L_{\hat{A_1}}^{w_0-2\delta}\oplus
+    8 L_{\hat{A_1}}^{w_1-2\delta}\oplus 15 L_{\hat{A_1}}^{w_0-3\delta}\oplus\\
+    12 L_{\hat{A_1}}^{w_1-3\delta}\oplus 26 L_{\hat{A_1}}^{w_1-4\delta}\oplus
+    29 L_{\hat{A_1}}^{w_0-4\delta}\oplus 51 L_{\hat{A_1}}^{w_0-5\delta}\oplus\\
+    42 L_{\hat{A_1}}^{w_1-5\delta}\oplus 78 L_{\hat{A_1}}^{w_1-6\delta}\oplus
+    85 L_{\hat{A_1}}^{w_0-6\delta}\oplus 120 L_{\hat{A_1}}^{w_1-7\delta}\oplus\\
+    139 L_{\hat{A_1}}^{w_0-7\delta}\oplus 202 L_{\hat{A_1}}^{w_1-8\delta}\oplus
+    222 L_{\hat{A_1}}^{w_0-8\delta}\oplus 306 L_{\hat{A_1}}^{w_1-9\delta}\oplus\\
+    346 L_{\hat{A_1}}^{w_0-9\delta}\oplus 530 L_{\hat{A_1}}^{w_0-10\delta}\oplus
+    482 L_{\hat{A_1}}^{w_1-10\delta}\oplus 714 L_{\hat{A_1}}^{w_1-11\delta}\oplus\\
+    797 L_{\hat{A_1}}^{w_0-11\delta}\oplus 1080 L_{\hat{A_1}}^{w_1-12\delta}\oplus
+    1180 L_{\hat{A_1}}^{w_0-12\delta}
+\end{eqnarray*}
 This result can be presented as the set of branching functions \cite{kac1990idl}:
@@
 
-Now we can use the relation \eqref{eq:31} to get the expansion of the $B_2/A_1$-coset characters:
+Now we can use the relation \ref{eq:31} to get the expansion of the $B_2/A_1$-coset characters:
 \begin{equation}
@@
 \bibliography{article}{}
-\bibliographystyle{utphys}
+\bibliographystyle{unsrt}
 

### 2010-07-06 AffineLieAlgebras/InformalNotes/article.tex
Merged V.D. changes - section on conformal embeddings of semisimple subalgebras is left out.

@@
 
-Usually only the maximal reductive subalgebras are considered since the case of non-maximal subalgebra can be obtained using the chain of maximal injections.
-In this paper we find the recurrent properties for branching coefficients that generalise the relations obtained earlier (see the paper \cite{ilyin812pbc} and the references therein) to the case of non-maximal reductive subalgebra.
-The result is formulated in terms of new injection fan called "the subtracted fan".
-Using this new tools we formulate simple and explicit algorithm for computations of branching coefficients which is applicable to the non-maximal subalgebras of finite-dimensional and affine Lie algebras.
-
-We demonstrate that our algorithm can be used in studies of conformal embeddings and coset constructions in rational conformal field theory.
-
-The paper is organised as follows.
-In the subsection \ref{sec:notation}  we fix the notations.
-In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous branching coefficients and describe the decomposition algorithm for integrable highest weight modules $L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$ (subsection \ref{sec:algorithm}).
-In the Section \ref{sec:finite-dimens-lie} we present several simple examples for finite-dimensional Lie algebras.
-The affine Lie algebras and their applications in CFT models are considered in Section \ref{sec:phys-appl}.
-We conclude the paper with a review of obtained results.
+Usually only the maximal reductive subalgebras are considered since the case of non-maximal subalgebra
+can be obtained using the chain of maximal injections. In this paper we find the recurrent properties
+for branching coefficients that generalise the relations obtained earlier (see the paper \cite{ilyin812pbc}
+and the references therein) to the case of non-maximal reductive subalgebra. The result is formulated in
+terms of the new injection fan called "the subtracted fan". Using this new tools we formulate a simple and
+explicit algorithm for computations of branching coefficients which is applicable to the non-maximal
+subalgebras of finite-dimensional and affine Lie algebras.
+
+We demonstrate that our algorithm can be used in studies of conformal embeddings and coset constructions
+in rational conformal field theory.
+
+The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the notations.
+In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous
+branching coefficients and describe the decomposition algorithm for integrable highest weight modules
+$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
+(subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several
+simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in
+CFT models are considered in Section \ref{sec:phys-appl}.
 Possible further developments are discussed (Section \ref{sec:conclusion}).
@@
 
-We use the following notations adopted from the paper \cite{ilyin812pbc}.
+We use the following notations:
 
@@
 
-It is important whether there exist the positive roots $\alpha\in \Delta$ such that $\pi_{\mathfrak{a}}\alpha=0$.
-These roots are orthogonal to $P_{\mathfrak{a}}$.
-Let's denote the subset of such roots by $\Delta^{+}_{\bot}
+Consider the positive roots $\alpha\in \Delta$ orthogonal to $P_{\mathfrak{a}}$. Denote the subset of such roots by $\Delta^{+}_{\bot}
 =\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
 \forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
-
-Notice that if $\Delta^{+}_{\bot}\neq \emptyset$ the Weyl reflections
-corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup
-$W_{\bot}$ of the Weyl group $W$. Consider any two positive roots $\alpha,\;
-\beta\in \Delta^{+}_{\bot}$ and the corresponding Weyl reflections
-$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since roots $\beta\in \Delta_{\mathfrak{a}}$ are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$ they
-are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$.
-So the subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$.
-
-Thus we have obtained the system $\Delta_{\bot}$ orthogonal $P_{\mathfrak{a}}$ and invariant with respect to  $W_{\bot}$. It
+Notice that if $\Delta^{+}_{\bot}\neq \emptyset$ the corresponding Weyl reflections
+generate a subgroup $W_{\bot}$ of the group $W$. Consider the roots $\alpha,\;
+\beta\in \Delta^{+}_{\bot}$ and the corresponding reflections
+$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since the roots in $\Delta_{\mathfrak{a}}$
+are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$ they
+are also invariant under the product $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$
+and the subgroup $W_{\bot}$ preserves the roots in $\Delta_{\mathfrak{a}}$.
+The system $\Delta_{\bot}$
 can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
@@
 
-\subsection{Algorithm for the recursive computation of the branching coefficients}
+\subsection{Algorithm for recursive computation of branching coefficients}
 \label{sec:algorithm}
@@
 
-\subsubsection{Embeddings of semisimple subalgebras}
-\label{sec:embedd-semis-subalg}
-
-Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where
-$\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$,
-which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
-To construct this injection we use the method presented in \cite{vasilevich1986method}.
-We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$. Its diagram
-$$\mathcal{N}_{A_1\oplus A_1}^{(1,1)}= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$$
-is presented in Figure \ref{fig:A_1+A_1_to_A3}.
-
-\begin{figure}[h!tb]
-  \begin{multicols}{2}
-    \hfill
-    \includegraphics[width=50mm]{A_1+A_1_to_A3.eps}
-    \hfill
-    \caption{The special embedding  $A_1\oplus A_1\subset A_3$ is based on this module}
-    \label{fig:A_1+A_1_to_A3}
-    \hfill
-    \includegraphics[width=50mm]{A1+A1-A3.eps}
-    \hfill
-    \caption{Embedded roots for the special embedding  $A_1\oplus A_1\subset A_3$}
-    \label{fig:A1+A1-A3}
-  \end{multicols}
-\end{figure}
-
-For the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in
-the Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}
-{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},
-\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}
-{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method},
-thus $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
-The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
-\begin{equation}
-  \label{eq:37}
-  \begin{array}{l}
-     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
-     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
-  \end{array}
-\end{equation}
-(See Figure \ref{fig:A1+A1-A3}.)
-
-This injection is characterised by the embedding indices $(2,2)$ and is conformal,
-since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
-
-We are interested in the reduction of the fundamental modules of $\hat A_3$.
-Four fundamental weights of level 1 have the following coordinates in the orthogonal basis: 
-\begin{equation}
-  \begin{array}{lll}
-     w_0 & = & (0,0,0,0;1;0),\\
-     w_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
-     w_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
-     w_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
-  \end{array}
-\end{equation}
-
-For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
-\begin{equation}
-  \label{eq:38}
-  \begin{array}{lll}
-    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
-    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
-    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1+n\delta,\pm \alpha_2+n\delta;\; +n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
-  \end{array}
-\end{equation}
-The set $\Delta^{+}_{\bot}$ is empty.
-The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown in the Figure \ref{fig:A1+A1-A3_fan}.
-The coordinates of fan element finite part are given in the basis of $A_1\oplus A_1$ fundamental roots.
-The fan elements $\gamma$ are marked by crosses if  $s(\gamma)=1$ and by diamonds if $s(\gamma)=-1$.
-\begin{figure}[h!tb]
-  \includegraphics[width=135mm]{A1+A1-A3_fan.eps}
-  \caption{The fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
-  \label{fig:A1+A1-A3_fan}
-\end{figure}
-
-We limit our calculations by the first 5 grades.
-\begin{figure}[t]
-%\begin{figure}[p]
-%  \hspace*{-1cm}
-  \includegraphics[width=135mm]{A1+A1-A3_anom.eps}
-  \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
-  \label{fig:A1+A1-A3_anom}
-\end{figure}
-
-The set of anomalous weights $\widehat{\Psi_{\hat A_3}^{(\mu)}}$
-and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for
-$\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}.
-Coordinates of the finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
-The weights are marked by crosses if $\epsilon(\omega)=1$ and by diamonds otherwise.
-
-The anomalous branching coefficients for the module $L^{(w_2)}$ are shown in the Figure  \ref{fig:A1+A1-A3_branching}.
-Inside the chamber $\bar{C_{\mathfrak{a}}}$ the anomalous branching coefficients coinside with
-the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$
-and are marked by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
-\begin{figure}[b]
-%\begin{figure}[p]
-%  \hspace*{-1cm}
-  \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.eps}
-  \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
-  \label{fig:A1+A1-A3_branching}
-\end{figure}
-
-Treating analogously the modules $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_3}_{\hat A_3}$
-we get the following set of branching rules
- \begin{equation}
-   \label{eq:39}
-   \begin{array}{ll}
-     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
-     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
-     L^{(0,1,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
-     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
-   \end{array}
- \end{equation}
-
-Now we can construct the modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
-\begin{eqnarray*}
-  \label{eq:40}
-  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
-  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
-\end{eqnarray*}
-
-By this example we have illustrated the mechanism of our algorithm.
-We want to remind that the proposed method is universal and can be applied to
-an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.
-
+% \subsubsection{Embeddings of semisimple subalgebras}
+% \label{sec:embedd-semis-subalg}
+% 
+% Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where
+% $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$,
+% which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
+% To construct this injection we use the method presented in \cite{vasilevich1986method}.
+% We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$. Its diagram
+% $$\mathcal{N}_{A_1\oplus A_1}^{(1,1)}= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$$
+% is presented in Figure \ref{fig:A_1+A_1_to_A3}.
+% 
+% \begin{figure}[h!tb]
+%   \begin{multicols}{2}
+%     \hfill
+%     \includegraphics[width=50mm]{A_1+A_1_to_A3.eps}
+%     \hfill
+%     \caption{The special embedding  $A_1\oplus A_1\subset A_3$ is based on this module}
+%     \label{fig:A_1+A_1_to_A3}
+%     \hfill
+%     \includegraphics[width=50mm]{A1+A1-A3.eps}
+%     \hfill
+%     \caption{Embedded roots for the special embedding  $A_1\oplus A_1\subset A_3$}
+%     \label{fig:A1+A1-A3}
+%   \end{multicols}
+% \end{figure}
+% 
+% For the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in
+% the Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}
+% {(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},
+% \frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}
+% {(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method},
+% thus $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
+% The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
+% \begin{equation}
+%   \label{eq:37}
+%   \begin{array}{l}
+%      \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
+%      \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
+%   \end{array}
+% \end{equation}
+% (See Figure \ref{fig:A1+A1-A3}.)
+% 
+% This injection is characterised by the embedding indices $(2,2)$ and is conformal,
+% since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
+% 
+% We are interested in the reduction of the fundamental modules of $\hat A_3$.
+% Four fundamental weights of level 1 have the following coordinates in the orthogonal basis: 
+% \begin{equation}
+%   \begin{array}{lll}
+%      w_0 & = & (0,0,0,0;1;0),\\
+%      w_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
+%      w_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
+%      w_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
+%   \end{array}
+% \end{equation}
+% 
+% For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
+% \begin{equation}
+%   \label{eq:38}
+%   \begin{array}{lll}
+%     \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
+%     &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
+%     \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1+n\delta,\pm \alpha_2+n\delta;\; +n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
+%   \end{array}
+% \end{equation}
+% The set $\Delta^{+}_{\bot}$ is empty.
+% The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown in the Figure \ref{fig:A1+A1-A3_fan}.
+% The coordinates of fan element finite part are given in the basis of $A_1\oplus A_1$ fundamental roots.
+% The fan elements $\gamma$ are marked by crosses if  $s(\gamma)=1$ and by diamonds if $s(\gamma)=-1$.
+% \begin{figure}[h!tb]
+%   \includegraphics[width=135mm]{A1+A1-A3_fan.eps}
+%   \caption{The fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
+%   \label{fig:A1+A1-A3_fan}
+% \end{figure}
+% 
+% We limit our calculations by the first 5 grades.
+% \begin{figure}[t]
+% %\begin{figure}[p]
+% %  \hspace*{-1cm}
+%   \includegraphics[width=135mm]{A1+A1-A3_anom.eps}
+%   \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
+%   \label{fig:A1+A1-A3_anom}
+% \end{figure}
+% 
+% The set of anomalous weights $\widehat{\Psi_{\hat A_3}^{(\mu)}}$
+% and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for
+% $\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}.
+% Coordinates of the finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
+% The weights are marked by crosses if $\epsilon(\omega)=1$ and by diamonds otherwise.
+% 
+% 
+% The anomalous branching coefficients for the module $L^{(w_2)}$ are shown in the Figure  \ref{fig:A1+A1-A3_branching}.
+% Inside the chamber $\bar{C_{\mathfrak{a}}}$ the anomalous branching coefficients coinside with
+% the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$
+% and are marked by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
+% \begin{figure}[b]
+% %\begin{figure}[p]
+% %  \hspace*{-1cm}
+%   \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.eps}
+%   \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
+%   \label{fig:A1+A1-A3_branching}
+% \end{figure}
+% 
+% Treating analogously the modules $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_3}_{\hat A_3}$
+% we get the following set of branching rules
+%  \begin{equation}
+%    \label{eq:39}
+%    \begin{array}{ll}
+%      L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
+%      L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
+%      L^{(0,1,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
+%      L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
+%    \end{array}
+%  \end{equation}
+% 
+% Now we can construct the modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
+% \begin{eqnarray*}
+%   \label{eq:40}
+%   Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
+%   \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
+% \end{eqnarray*}
+% 
+% By this example we have illustrated the mechanism of our algorithm.
+% We want to remind that the proposed method is universal and can be applied to
+% an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.
+% 
 \subsection{Coset models}

### 2010-07-06 AffineLieAlgebras/InformalNotes/article.tex
Paper is shortened for JPhysA submission, figures are converted to eps and renamed according to IOP LaTeX Guidelines.

@@
   \hline
-  $A_n$ & \includegraphics{A_series_ext_diag.eps} & \includegraphics{A_series_ext_split.eps} \\
+  $A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps} \\
   \hline                                                                     
-  $B_n$ & \includegraphics{B_series_ext_diag.eps} & \includegraphics{B_series_ext_split.eps} \\
+  $B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps} \\
   \hline                                                                     
-  $C_n$ & \includegraphics{C_series_ext_diag.eps} & \includegraphics{C_series_ext_split.eps} \\
+  $C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps} \\
   \hline                                                                     
-  $D_n$ & \includegraphics{D_series_ext_diag.eps} & \includegraphics{D_series_ext_split.eps} \\
+  $D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps} \\
   \hline
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{B2_A1.eps}
+    \includegraphics[width=80mm]{figure1.eps}
   }
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{B2_A1_2.eps}
+    \includegraphics[width=80mm]{figure2.eps}
   }
@@
   \centering
-  \includegraphics[width=50mm]{B4_B2_2A1.eps}
+  \includegraphics[width=50mm]{figure3.eps}
   \caption{The regular embedding $B_2\subset B_4$ described by dropping the node.}
@@
   \centering
-    \includegraphics[width=100mm,height=90mm]{B4_B2_anom_points.eps}
+    \includegraphics[width=100mm,height=90mm]{figure4.eps}
   \caption{Projected weights $-\frac{1}{s(\gamma_0)}\pi_{B_2}\left(\hat \Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
@@
   \centering
-  \includegraphics[height=80mm]{B4_B2_fan.eps}
+  \includegraphics[height=80mm]{figure5.eps}
   \caption{The fan for $B_2\subset B_4$}
@@
   \centering
-  \includegraphics[width=135mm]{AffineA2_A1_fan.eps}
+  \includegraphics[width=135mm]{figure6.eps}
   \caption{The fan and $s(\gamma+\gamma_0)$ for $\hat{A_1}\longrightarrow \hat{A_2}$}
@@
 %  \hspace*{-2cm}
-  \includegraphics[width=140mm]{AffineA2_A1_anom.eps}
+  \includegraphics[width=140mm]{figure7.eps}
   \caption{The anomalous weights of the module $L^{(0,0;1;0)}_{\hat{A_2}}$}
@@
   \centering
-  \includegraphics[width=130mm]{AffineA2_A1_proj_anom.eps}
+  \includegraphics[width=130mm]{figure8.eps}
   \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$.}
@@
   \centering
-  \includegraphics[width=130mm]{AffineA2_A1_branching.eps}
+  \includegraphics[width=130mm]{figure9.eps}
   \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
@@
   \centering
-  \includegraphics[width=135mm]{AffineB2_A1_fan.eps}
+  \includegraphics[width=135mm]{figure10.eps}
   \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
@@
 %  \hspace*{-2cm}
-  \includegraphics[width=140mm]{AffineB2_A1_Anom.eps}
+  \includegraphics[width=140mm]{figure11.eps}
   \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$.
@@
   \centering
-  \includegraphics[width=120mm]{AffineB2_A1_proj_anom.eps}
+  \includegraphics[width=120mm]{figure12.eps}
   \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$ and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
@@
   \centering
-  \includegraphics[width=120mm]{AffineB2_A1_branching.eps}
+  \includegraphics[width=120mm]{figure13.eps}
   \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}

### 2010-07-06 AffineLieAlgebras/InformalNotes/article.tex
Equation numbering simplified

@@
  $k_{\lambda}$ --- the anomalous branching coefficients, notice that
-\begin{equation}
-  \label{eq:20}
+\begin{equation*}
+%  \label{eq:20}
   b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}
-\end{equation}
+\end{equation*}
 
@@
 projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
-\begin{equation}
-  \label{eq:3}
+\begin{equation*}
+%  \label{eq:3}
   L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
@@
   \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
-\end{equation}
+\end{equation*}
 The Weyl-Kac character formula leads to
@@
 Using the existing classification of maximal special subalgebras in classical Lie algebras \cite{dynkin1952semisimple} we have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
-\begin{equation}
-  \label{eq:42}
+\begin{equation*}
+%  \label{eq:42}
   \begin{array}{lll}
@@
   \end{array}
-\end{equation}
+\end{equation*}
 Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.
@@
 with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$ can be written as
-\begin{equation}
-  \label{eq:41}
+\begin{equation*}
+%  \label{eq:41}
   ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
-\end{equation}
+\end{equation*}
 Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
@@
 Multiply the equation (\ref{eq:4}) by the element
-\begin{equation}
-  \label{eq:5}
+\begin{equation*}
+%  \label{eq:5}
   \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
-\end{equation}
+\end{equation*}
 and take into account that the projection commutes with the multiplication:
@@
 Similarly to the transformation proposed in \cite{ilyin812pbc} we introduce the anomalous branching coefficients $k_{\lambda}$,
-\begin{equation}
+\begin{equation*}
   \label{eq:10}
@@
   }^{\left( \mu \right) }e^{\lambda }
-\end{equation}
+\end{equation*}
 and simplify the first factor,
@@
 For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
-\begin{eqnarray*}
+\begin{equation}
   \label{eq:13}
- \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
- \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
-\end{eqnarray*}
+  \begin{array}{c}
+\fl \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+= \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
+  \end{array}
+\end{equation}
 The fraction in the right-hand side of the equation looks like the character of some  $\mathfrak{a}_{\bot}$-module.
 Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we can rewrite the shifted weights
-\begin{equation}
+\begin{equation*}
   \label{eq:30}
   \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}+\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho
-\end{equation}
+\end{equation*}
 
@@
   \label{eq:14}
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
+\fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
@@
     \label{eq:15}
-    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
+\fl    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
     \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
@@
 Thus we obtain the relation
-\begin{eqnarray*}
+\begin{equation}
   \label{eq:9}
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+  \begin{array}{c}
+\fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
   \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
   \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
-\end{eqnarray*}
+  \end{array}
+\end{equation}
 Let us rewrite the factor in the right-hand side:
@@
 we can deduce the following property of the anomalous branching coefficients,
-\begin{eqnarray*}
+\begin{eqnarray}
   \label{eq:17}
@@
    \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\\ \xi\in P_{\mathfrak{a}}.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 \co{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$ and decompose the defining relation (\ref{eq:11}),
-\begin{equation}
+\begin{equation*}
   \label{eq:18}
@@
     _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \left\{\gamma_{0}\right\}}s\left( \gamma \right) e^{-\gamma },
-\end{equation}
+\end{equation*}
 the equality (\ref{eq:17}) leads to the desired recurrent  relation for the anomalous branching coefficients:
@@
 $\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty the  recurrent relation is simplified:
-\begin{equation}
+\begin{equation*}
 k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
@@
 +\gamma }^{\left( \mu \right) }\right),  \label{recurrent relation special}
-\end{equation}
+\end{equation*}
 the latter coinsides with the one obtained in \cite{ilyin812pbc} (formula (16)).
@@
 Projecting them onto the root space of the subalgebra $\mathfrak{a}=A_1$ we get the anomalous weights with the corresponding multiplicities:
-\begin{equation}
+\begin{equation*}
   \label{eq:25}
   (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
-\end{equation}
+\end{equation*}
 For the set $\Gamma$ (using the definition (\ref{phi-d},\ref{fan-defined})) we have
-\begin{equation}
+\begin{equation*}
   \label{eq:22}
   \Gamma_{A_1\subset B_2}=\left\{ (1,2),\; (2,-1) \right\}.
-\end{equation}
+\end{equation*}
 Here the second component denotes the value of $s(\gamma)$.
@@
 For the last weight in $\bar{C}^{(0)}_{\mathfrak{a}}$ the formula (\ref{recurrent-relation}) gives
-\begin{equation}
+\begin{equation*}
   \label{eq:23}
   k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1.
-\end{equation}
+\end{equation*}
 The recurrence property defines the branching.
@@
 In the orthogonal basis $\left\{e_1,\dots,e_4\right\}$ the simple roots and the positive roots of $B_4$ are
-\begin{equation}
+\begin{equation*}
   \label{eq:8}
  S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\}
-\end{equation}
+\end{equation*}
 \begin{eqnarray*}
@@
 Correspondingly for the embedded subalgebra $\mathfrak{a}=B_2$ we have
-\begin{equation}
+\begin{equation*}
   \label{eq:26}
  S_{B_2}=\{e_3-e_4,e_4\}
-\end{equation}
-\begin{equation}
+\end{equation*}
+\begin{equation*}
   \label{eq:27}
  \Delta^{+}_{\bot}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
-\end{equation}
+\end{equation*}
 and is the set of positive roots for the algebra $\mathfrak{a}_{\bot}=B_2$.
@@
 The simplest modular-invariant partition function has the diagonal form:
-\begin{equation}
+\begin{equation*}
   \label{eq:34}
    Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
-\end{equation}
+\end{equation*}
 Here the sum is over the set of the highest weights of integrable modules of WZW-model and $\chi_{\mu}(\tau)$ are the normalized characters of these modules.
@@
 by the decompositions
-\begin{equation}
+\begin{equation*}
   \label{eq:32}
 \sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}  
-\end{equation}
+\end{equation*}
 containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules.
@@
 In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$ the states can be described as
-\begin{equation}
+\begin{equation*}
   \label{eq:109}
   X^{\alpha_1}_{-n_1}X^{\alpha_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
-\end{equation}
+\end{equation*}
 And for the sub-algebra $\mathfrak{a}$ the corresponding states are
-\begin{equation}
+\begin{equation*}
   \label{eq:110}
   \tilde{X}^{\alpha'_1}_{-n_1}\tilde{X}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
-\end{equation}
+\end{equation*}
 The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance, but this is not the case for the energy-momentum tensor.
@@
 leads to the equality of the central charges 
-\begin{equation}
+\begin{equation*}
   \label{eq:33}
   c(\mathfrak{g})=c(\mathfrak{a})
-\end{equation}
+\end{equation*}
 and to the equation
@@
 Consider the modes expansion of the energy-momentum tensor
-\begin{equation}
+\begin{equation*}
 \label{eq:47}
   T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
-\end{equation}
+\end{equation*}
 
 The modes $L_n$ are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
-\begin{equation}
+\begin{equation*}
 \label{eq:48}
   L_n=\frac{1}{2(k+h^v)}\sum_{\alpha}\sum_m:X^{\alpha}_m X^{\alpha}_{n-m}:
-\end{equation}
+\end{equation*}
 In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
@@
 coefficients. So the finite reducibility theorem holds and we get the decomposition
-\begin{equation}
+\begin{equation*}
   \label{eq:43}
   L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
-\end{equation}
+\end{equation*}
 
@@
 branching 
-\begin{eqnarray}
+\begin{equation*}
   \label{eq:44}
@@
    L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
-\end{eqnarray}
+\end{equation*}
 
 Using these results the modular-invariant partition function is easily found,
-\begin{equation}
+\begin{equation*}
   \label{eq:45}
   Z=\left|\chi_{(4;4;0)}+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
-\end{equation}
-
-% \subsubsection{Embeddings of semisimple subalgebras}
-% \label{sec:embedd-semis-subalg}
-% 
-% Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where
-% $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$,
-% which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
-% To construct this injection we use the method presented in \cite{vasilevich1986method}.
-% We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$. Its diagram
-% $$\mathcal{N}_{A_1\oplus A_1}^{(1,1)}= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$$
-% is presented in Figure \ref{fig:A_1+A_1_to_A3}.
-% 
-% \begin{figure}[h!tb]
-%   \begin{multicols}{2}
-%     \hfill
-%     \includegraphics[width=50mm]{A_1+A_1_to_A3.eps}
-%     \hfill
-%     \caption{The special embedding  $A_1\oplus A_1\subset A_3$ is based on this module}
-%     \label{fig:A_1+A_1_to_A3}
-%     \hfill
-%     \includegraphics[width=50mm]{A1+A1-A3.eps}
-%     \hfill
-%     \caption{Embedded roots for the special embedding  $A_1\oplus A_1\subset A_3$}
-%     \label{fig:A1+A1-A3}
-%   \end{multicols}
-% \end{figure}
-% 
-% For the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in
-% the Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}
-% {(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},
-% \frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}
-% {(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method},
-% thus $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
-% The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
-% \begin{equation}
-%   \label{eq:37}
-%   \begin{array}{l}
-%      \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
-%      \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
-%   \end{array}
-% \end{equation}
-% (See Figure \ref{fig:A1+A1-A3}.)
-% 
-% This injection is characterised by the embedding indices $(2,2)$ and is conformal,
-% since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
-% 
-% We are interested in the reduction of the fundamental modules of $\hat A_3$.
-% Four fundamental weights of level 1 have the following coordinates in the orthogonal basis: 
-% \begin{equation}
-%   \begin{array}{lll}
-%      w_0 & = & (0,0,0,0;1;0),\\
-%      w_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0),\\
-%      w_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0),\\
-%      w_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0). \\
-%   \end{array}
-% \end{equation}
-% 
-% For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
-% \begin{equation}
-%   \label{eq:38}
-%   \begin{array}{lll}
-%     \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
-%     &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
-%     \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1+n\delta,\pm \alpha_2+n\delta;\; +n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
-%   \end{array}
-% \end{equation}
-% The set $\Delta^{+}_{\bot}$ is empty.
-% The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown in the Figure \ref{fig:A1+A1-A3_fan}.
-% The coordinates of fan element finite part are given in the basis of $A_1\oplus A_1$ fundamental roots.
-% The fan elements $\gamma$ are marked by crosses if  $s(\gamma)=1$ and by diamonds if $s(\gamma)=-1$.
-% \begin{figure}[h!tb]
-%   \includegraphics[width=135mm]{A1+A1-A3_fan.eps}
-%   \caption{The fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
-%   \label{fig:A1+A1-A3_fan}
-% \end{figure}
-% 
-% We limit our calculations by the first 5 grades.
-% \begin{figure}[t]
-% %\begin{figure}[p]
-% %  \hspace*{-1cm}
-%   \includegraphics[width=135mm]{A1+A1-A3_anom.eps}
-%   \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
-%   \label{fig:A1+A1-A3_anom}
-% \end{figure}
-% 
-% The set of anomalous weights $\widehat{\Psi_{\hat A_3}^{(\mu)}}$
-% and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for
-% $\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}.
-% Coordinates of the finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
-% The weights are marked by crosses if $\epsilon(\omega)=1$ and by diamonds otherwise.
-% 
-% 
-% The anomalous branching coefficients for the module $L^{(w_2)}$ are shown in the Figure  \ref{fig:A1+A1-A3_branching}.
-% Inside the chamber $\bar{C_{\mathfrak{a}}}$ the anomalous branching coefficients coinside with
-% the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$
-% and are marked by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
-% \begin{figure}[b]
-% %\begin{figure}[p]
-% %  \hspace*{-1cm}
-%   \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.eps}
-%   \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
-%   \label{fig:A1+A1-A3_branching}
-% \end{figure}
-% 
-% Treating analogously the modules $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_3}_{\hat A_3}$
-% we get the following set of branching rules
-%  \begin{equation}
-%    \label{eq:39}
-%    \begin{array}{ll}
-%      L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
-%      L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
-%      L^{(0,1,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
-%      L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
-%    \end{array}
-%  \end{equation}
-% 
-% Now we can construct the modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
-% \begin{eqnarray*}
-%   \label{eq:40}
-%   Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
-%   \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
-% \end{eqnarray*}
-% 
-% By this example we have illustrated the mechanism of our algorithm.
-% We want to remind that the proposed method is universal and can be applied to
-% an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.
-% 
+\end{equation*}
+
 \subsection{Coset models}
@@
 where
-\begin{equation}
+\begin{equation*}
   \label{eq:46}
   m_{\mu}=\frac{\left|\mu+\rho\right|^2}{2(k+g)}-\frac{\left|\rho\right|^2}{2g}.
-\end{equation}
+\end{equation*}
 
@@
 This result can be presented as the set of branching functions \cite{kac1990idl}:
-\begin{eqnarray}
+\begin{eqnarray*}
   \label{eq:29}
@@
   \end{array}
-\end{eqnarray}
+\end{eqnarray*}
 Here $q=\exp (2\pi i \tau)$, the lower index enumerates the branching functions according
@@
 Now we can use the relation \ref{eq:31} to get the expansion of the $B_2/A_1$-coset characters:
-\begin{equation}
+\begin{equation*}
   \label{eq:35}
@@
   \end{array}
-\end{equation}
+\end{equation*}
 

### 2010-07-09 AffineLieAlgebras/InformalNotes/article.tex
IOP work

@@
 \documentclass[12pt]{iopart}
-\usepackage{ucs}
+%\usepackage{ucs}
 %\usepackage{amsmath,amssymb,amsthm}
@@
 \begin{document}
-% \pagenumbering{alph}
-% \thispagestyle{empty}
-% 
-% \begin{center}
-% {\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
-% \end{center}
-% \vskip 1 cm
-% \begin{flushright}
-% {\large \bf SPbU-IP-10-03}
-% \end{flushright}
-% \hfill {}
-% \vskip 1 cm
-% \begin{center}
-% {\Huge \bf Recursive algorithms, branching coefficients \\ and applications\\[0.5cm]
-% }
-% \end{center}
-% \vskip 1.0 cm
-% \begin{center}
-% {\Large \bf
-% Vladimir Lyakhovsky\\[2mm]
-% Anton Nazarov}
-% \end{center}
-% \vfill
-% \begin{center}
-% {\large Department of Theoretical Physics\\
-% }
-% \end{center}
-% \vfill
-% \begin{center}
-% SAINT-PETERSBURG \\
-% 2010
-% \end{center}
-% 
-% \newpage
-% 
-% \pagenumbering{arabic}
+
 \title{Recursive algorithms, branching coefficients and applications}
@@
 \eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}
-% \thanks{ Supported by
-%  RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
-% 
-% \thanks{ Supported by
-% the National Project RNP.2.1.1./1575 }
 
@@
 
-The branching problem for affine Lie algebras emerges in conformal field theory, for example, in the construction of modular-invariant partition functions \cite{difrancesco1997cft}.
-Recently the problem of the conformal embeddings was considered in the paper \cite{coquereaux2008conformal}.
+The branching problem for affine Lie algebras emerges in conformal field theory, for example,
+in the construction of modular-invariant partition functions \cite{difrancesco1997cft}.
+Recently the problem of conformal embeddings was considered in the paper \cite{coquereaux2008conformal}.
 
@@
 can be obtained using the chain of maximal injections. In this paper we find the recurrent properties
-for branching coefficients that generalise the relations obtained earlier (see the paper \cite{ilyin812pbc}
+for branching coefficients that generalize the relations obtained earlier (see the paper \cite{ilyin812pbc}
 and the references therein) to the case of non-maximal reductive subalgebra. The result is formulated in
@@
 $\lambda =\left( \co{\lambda };k;n\right) $ --- the
-decomposition of an affine weight indicating the finite part $\co{\lambda }$, level $k$ and grade $n$\ .
+decomposition of an affine weight indicating the finite part $\co{\lambda }$, level $k$ and grade $n$;
 
@@
 w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
-\circ (\nu +\rho _{a})-\rho _{a}}$ ),
+\circ (\nu +\rho _{a})-\rho _{a}}$ );
 
@@
 \mathrm{{mult}\left( \alpha \right) }}}=\frac{\Psi ^{\left( \mu \right) }}{%
-\Psi ^{\left( 0\right) }}$ --- the Weyl-Kac formula.
+\Psi ^{\left( 0\right) }}$ --- the Weyl-Kac formula;
 
 $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
-mult}\left( \alpha \right) }}=\Psi ^{\left( 0\right) }\quad $
+mult}\left( \alpha \right) }}=\Psi ^{\left( 0\right) }\quad $;
 
@@
 \left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $--- the
-denominator.
-
-$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ --- the module decomposition with respect to $\frak{a}\longrightarrow \frak{g}$;
-
-$b^{(\mu)}_{\nu}$ --- the branching coefficients;
+denominator;
+
+$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus
+\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$
+ --- the module decomposition with respect to $\frak{a}\longrightarrow \frak{g}$;
+
+$b^{(\mu)}_{\nu}$ --- the branching coefficients,
 
@@
         a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
-  }^{\left( \mu \right) }e^{\lambda }
+  }^{\left( \mu \right) }e^{\lambda };
 \end{equation}
@@
 %  \label{eq:20}
-  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}
+  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}};
 \end{equation*}
@@
 Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator $R$
-(when it is projected to the $P_{\mathfrak{a}}$) the injection fan technique \cite{ilyin812pbc} can be properly modified.
+(when it is projected to $P_{\mathfrak{a}}$) the injection fan technique \cite{ilyin812pbc} can be properly modified.
 The result is the generalized recurrent relation for anomalous branching
-coefficients \ref{eq:21}:
+coefficients (\ref{eq:21}):
 \begin{equation}
@@
       k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
+  {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+  \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
 \left.
@@
 \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
-+\gamma }^{\left( \mu \right) }\right)
++\gamma }^{\left( \mu \right) }\right).
   \end{array}
@@
 Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by those roots of $\mathfrak{g}$ that are
-orthogonal $P_{\mathfrak{a}}$, $W_{\bot}$ is the corresponding Weyl group,
+orthogonal to $P_{\mathfrak{a}}$, $W_{\bot}$ is the corresponding Weyl group,
 $\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
@@
 is the multiplicity of $e^{\gamma}$ in this expansion.
-In the next subsection we study the situation in details and prove the relation \ref{eq:1}.
+In the next subsection we study the situation in details and prove the relation (\ref{eq:1}).
 
@@
   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
-  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
 \end{equation*}
@@
   e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
-  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
-\end{equation}
-
-Consider the positive roots $\alpha\in \Delta$ orthogonal to $P_{\mathfrak{a}}$. Denote the subset of such roots by $\Delta^{+}_{\bot}
+  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
+\end{equation}
+
+Consider the positive roots $\alpha\in \Delta$ orthogonal to $P_{\mathfrak{a}}$.
+Denote the subset of such roots by $\Delta^{+}_{\bot}
 =\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
@@
 $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since the roots in $\Delta_{\mathfrak{a}}$
-are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$ they
-are also invariant under the product $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$
-and the subgroup $W_{\bot}$ preserves the roots in $\Delta_{\mathfrak{a}}$.
-The system $\Delta_{\bot}$
+are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$
+and $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$
+the subgroup $W_{\bot}$ preserves the roots in $\Delta_{\mathfrak{a}}$.
+The subsystem $\Delta_{\bot}$
 can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
 
-Now we are to find out when the subset $\Delta^{+}_{\bot}$ is non-empty with the non-trivial subgroup $W_{\bot}$ and the subalgebra $\mathfrak{a}_{\bot}$.
+Now we are to find out when the subset $\Delta^{+}_{\bot}$ is nonempty
+with the nontrivial subgroup $W_{\bot}$ and the subalgebra $\mathfrak{a}_{\bot}$.
 
@@
 On the other hand
-non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
+nonmaximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
 through the chain of maximal embeddings
@@
 from the extended Dynkin diagram of the algebra. When the process gives us
-non-connected diagrams we immediately fix the roots orthogonal to $P_{\mathfrak{a}}$.
-The complete classification of the regular subalgebras for affine Lie algebras can be found in the recent paper \cite{1751-8121-41-36-365204}.
-
-For a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple the sufficient condition for $\Delta^{+}_{\bot}$ to be nontrivial can be formulated as follows:
+nonconnected diagrams we immediately fix the roots orthogonal to $P_{\mathfrak{a}}$.
+The complete classification of the regular subalgebras for affine Lie algebras can be
+found in the recent paper \cite{1751-8121-41-36-365204}.
+
+For a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$
+and $\mathfrak{g}$ are simple the sufficient condition for $\Delta^{+}_{\bot}$ to be
+nontrivial can be formulated as follows:
 if the Dynkin diagram of $\mathfrak{g}$ contains the disconnected
 subdiagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
-then the subset $\Delta_{\bot}$ is non-empty,
-subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and
+then the subset $\Delta_{\bot}$ is not empty,
+subalgebra $\mathfrak{a}_{\bot}$ is nontrivial and
 $\left\{\mathfrak{\bar{a}}_j\right\}$ are the subalgebras of $\mathfrak{a}_{\bot}$.
@@
 into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
-sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal to $B_2$ (the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).
-
-Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$ must not form a direct sum in $\mathfrak{g}$.  
-Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
- Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the remaining nodes of the diagram of $\mathfrak{g}$.
-The remaining diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ with $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$.
-It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$.
-So the question is whether $\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\mathfrak{\bar{a}}$ but the linear combinations of them.
-The answer is positive  when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$.
-Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.
+sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal to $B_2$
+(the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).
+
+Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$
+must not form a direct sum in $\mathfrak{g}$.
+Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both
+algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a
+subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
+Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with
+the remaining nodes of the diagram of $\mathfrak{g}$. The result is the diagram of
+the algebra $\bar{\mathfrak{a}}$ with $\mathrm{rank}(\bar{\mathfrak{a}}) =
+\mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that
+$\bar{\mathfrak{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether
+$\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\bar{\mathfrak{a}}$
+but the linear combinations of them. The answer is positive  when the set of angles
+between the roots of $\bar{\mathfrak{a}}$ does not contain all the angles between
+the roots of $\mathfrak{a}$.
+Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional
+roots of $\mathfrak{a}_{\bot}$.
 \begin{table}[ph]
@@
   \hline
-  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
+  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ &
+  Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
   \hline
@@
 \end{table}
-If $\mathfrak{a}=B_{r_{\mathfrak{a}}}$  we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
-This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.
-
-Using the existing classification of maximal special subalgebras in classical Lie algebras \cite{dynkin1952semisimple} we have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
+If $\mathfrak{a}=B_{r_{\mathfrak{a}}}$  we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\;
+1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
+This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be
+obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.
+
+Using the existing classification of maximal special subalgebras in classical Lie algebras
+\cite{dynkin1952semisimple} we have the following pairs of the orthogonal
+subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
 \begin{equation*}
@@
       sp(2p)\oplus so(q) & \subset sp(2pq)&\\
-      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}\\
+      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}.\\
   \end{array}
 \end{equation*}
-Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.
-
-Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
-with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$ can be written as
+
+Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and
+its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
+with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
+can be written as
 \begin{equation*}
 %  \label{eq:41}
-  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
-\end{equation*}
-Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
-
-Using this property we can consider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
+  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}=
+  \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega)
+  e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}
+  {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
+\end{equation*}
+Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$
+is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$
+with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
+since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
+
+Using this property we can consider the restriction
+$ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
+that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
 Multiply the equation (\ref{eq:4}) by the element
@@
 %  \label{eq:5}
-  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
+  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}
+  (1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
 \end{equation*}
@@
   \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
-    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
+    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
 \end{eqnarray*}
 
-If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}\subset W$.
-Consider the factor-space $W_{\bot}\backslash W$.
-For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
+If the set $\Delta^{+}_{\bot}$ is nonempty then the Weyl reflections corresponding to the
+positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}\subset W$.
+Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in
+W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$
+such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
 \begin{equation}
@@
   \begin{array}{c}
-\fl \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-= \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
+\fl \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
+{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+= \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
+\frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}
+{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right).
   \end{array}
@@
 The fraction in the right-hand side of the equation looks like the character of some  $\mathfrak{a}_{\bot}$-module.
-Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we can rewrite the shifted weights
+Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and
+$\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$,
+we can rewrite the shifted weights
 \begin{equation*}
   \label{eq:30}
-  \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}+\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho
+  \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}
+  (\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}
+  +\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho,
 \end{equation*}
@@
   \label{eq:14}
-\fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
+\fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu)
+e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
+=\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}
+  \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot
+  (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})
+  -\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
+  =\\
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}
+  e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+  -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}.
 \end{eqnarray*}
-The projector $\pi_{\mathfrak{a}}$ sends the character ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ to the unit element of $\cal{E}$ multiplied by ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$  :
+The projector $\pi_{\mathfrak{a}}$ sends the character
+${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$
+to the unit element of $\cal{E}$ multiplied by
+${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ :
   \begin{eqnarray*}
     \label{eq:15}
-\fl    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
-    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
+\fl    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
+e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch}
+L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+= \\
+    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
+    \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+    -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}.
   \end{eqnarray*}
@@
 \end{equation}
-
-For the coefficient function $s\left( \gamma \right) $ define the carrier $\Phi _{\frak{a%
+and for the coefficient function $s\left( \gamma \right) $ define the carrier $\Phi _{\frak{a%
 }\subset \frak{g}}\subset P_{\frak{a}}$:
@@
 \end{equation}
-From the relation \ref{eq:9} the obtained equation for the formal elements,
+From the relation (\ref{eq:9}) the corresponding equation in terms of formal elements,
 \begin{eqnarray*}
@@
   k_{\lambda }^{\left( \mu \right) }e^{\lambda } =\\
-  =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma }
+  =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda
+  \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma },
 \end{eqnarray*}
-we can deduce the following property of the anomalous branching coefficients,
-\begin{eqnarray}
+leads to the following property of the anomalous branching coefficients,
+\begin{equation}
 \label{eq:17}
-   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\\ \xi\in P_{\mathfrak{a}}.
-\end{eqnarray}
+\begin{array}{c}
+\fl \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}
+\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+\delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\;
+k^{(\mu)}_{\xi+\gamma}=0;
+\\
+\xi\in P_{\mathfrak{a}}.
+\end{array}
+\end{equation}
 
@@
     \sum_{\gamma \in \Gamma _{\frak{a}\subset \frak{g}}} s\left( \gamma +\gamma _{0}\right) k_{\xi+\gamma }^{\left( \mu \right) }
-  \right)
+  \right),
 \label{recurrent-relation}
@@
 
-Consider the case  $\Delta_{\bot}^{+} = 0$.
-There are three different reasons for $\Delta_{\bot}^{+}$ to be empty: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$, ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
+Consider the case  $\Delta_{\bot}^{+} = 0$. There are three different reasons for $\Delta_{\bot}^{+}$
+to be empty: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$,
+ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
 Both the first and the second cases can be treated as corresponding to the trivial orthogonal subalgebra:
-$\mathfrak{a}_{\bot}=0$. In any of these cases the formal characters in the right-hand side of (\ref{eq:13}) reduces to the formal element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$.
+$\mathfrak{a}_{\bot}=0$. In any of these cases the formal characters in the right-hand side of (\ref{eq:13})
+are reduced to the element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$.
 In the first two cases the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
@@
 \end{equation*}
-the latter coinsides with the one obtained in \cite{ilyin812pbc} (formula (16)).
+the latter coincides with the one obtained in \cite{ilyin812pbc} (formula (16)).
 
@@
 
-The recurrent relation \ref{recurrent-relation} allows us to formulate an algorithm for recursive computation of the branching coefficients.
+The recurrent relation (\ref{recurrent-relation}) allows us to formulate an algorithm for recursive computation of branching coefficients.
 In this algorithm there is no need to  construct the module $L^{(\mu)}_{\mathfrak{g}}$ or any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
@@
 \item Select the positive roots $\alpha\in \Delta^{+}$ orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\Gamma$ \ref{fan-defined}.
+\item Construct the set $\Gamma$ (\ref{fan-defined}).
 \item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights for the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$.
-\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
+\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$.
+Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies
+in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$.
+\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate
+the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$.
 \item Calculate the anomalous branching coefficients in the main Weyl
@@
 
-When are interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous weights up to the required grade and use the steps 4-7 of the algorithm for each grade.
+When being interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous weights up to the required grade and use the steps 4-7 of the algorithm for each grade.
 We can also speed up the algorithm by one-time computation of the representatives of the conjugate classes $W_{\bot}\backslash W$.
 
-The next section contains several examples computed using this algorithm.
+The next section contains examples illustrating the application of this algorithm.
 
@@
 
-Consider the regular embedding of $A_1\to B_2$.
+Consider the regular embedding $A_1\to B_2$.
 Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors in the Figure \ref{fig:B2_A1}.
@@
 
-Let's describe the reduction of the fundamental representation of $L^{(1,0)=w_1}_{B_2}$ (the black vector in Figure \ref{fig:B2_A1}).
+Let's describe the reduction of the fundamental representation $L^{(1,0)=w_1}_{B_2}$ (the black vector in Figure \ref{fig:B2_A1}).
 \begin{figure}[th]
@@
 Circles indicate the weights of the singular element $\Psi^{(w_1)}$.
-Now we are to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$ and to construct the set $\left\{\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W\right\}$. 
+Now we are to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$
+and to construct the set $\left\{\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W\right\}$.
 \begin{figure}[t]
@@
 \end{figure}
-On the Figure \ref{fig:B2_A1_2} the weights of  the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ are indicated.
-Projecting them onto the root space of the subalgebra $\mathfrak{a}=A_1$ we get the anomalous weights with the corresponding multiplicities:
+In the Figure \ref{fig:B2_A1_2} the weights of the corresponding
+$\left(\mathfrak{a}_{\bot}=A_1\right)$-modules
+$L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$
+are indicated. Projecting them onto the root space of the subalgebra $\mathfrak{a}=A_1$
+we get the anomalous weights and their multiplicities:
 \begin{equation*}
   \label{eq:25}
-  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
+  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2).
 \end{equation*}
@@
 Here the second component denotes the value of $s(\gamma)$.
-Applying this fan inside the $\bar{C}^{(0)}_{\mathfrak{a}}$ we get zeros for the weights greater than the first anomalous vector $(1)$, here $k^{(1,0)}_1=2$.
-For the last weight in $\bar{C}^{(0)}_{\mathfrak{a}}$ the formula (\ref{recurrent-relation}) gives
+Applying this fan inside the $\bar{C}^{(0)}_{\mathfrak{a}}$ we get zeros for the weights
+greater than the first anomalous vector $(1)$, here $k^{(1,0)}_1=2$. For the last weight in $\bar{C}^{(0)}_{\mathfrak{a}}$ the formula (\ref{recurrent-relation}) gives
 \begin{equation*}
@@
 \end{equation*}
+and
 \begin{equation*}
@@
 \end{equation*}
-and is the set of positive roots for the algebra $\mathfrak{a}_{\bot}=B_2$.
+is the set of positive roots for the algebra $\mathfrak{a}_{\bot}=B_2$.
 \begin{figure}[t]
@@
     \includegraphics[width=100mm,height=90mm]{figure4.eps}
-  \caption{Projected weights $-\frac{1}{s(\gamma_0)}\pi_{B_2}\left(\hat \Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
+  \caption{Projected weights $-\frac{1}{s(\gamma_0)}\pi_{B_2}\left(\hat \Psi^{(0,1,0,2)}_{B_4}\right)$
+  with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
   \label{fig:B4B2anom}
@@
 \end{figure}
-
-Using the definition (\ref{fan-defined}) we obtain the fan $\Gamma_{B_2\subset B_4}$ with the corresponding values $s(\gamma+\gamma_0)$, depicted in the Figure \ref{fig:B4B2Fan}.
+Using the definition (\ref{fan-defined}) we obtain the fan
+$\Gamma_{B_2\subset B_4}$ with the corresponding values $s(\gamma+\gamma_0)$,
+depicted in the Figure \ref{fig:B4B2Fan}.
 
@@
 e_1 + 2 e_2 + e_3 + e_4$; $\mathrm{dim}(L^{(0,1,0,2)})=2772$.
-
-To find the branching coefficients we need to compute the anomalous weights of $L^{\mu}_{B_4}$, select the weights belonging to $\bar{C}^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$ and compute the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.
+To find the branching coefficients we need to compute the anomalous weights of
+$L^{\mu}_{B_4}$, select the weights belonging to $\bar{C}^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$
+and compute the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.
 The set of the anomalous weights $\left\{ \omega(\mu+\rho)-\rho,\; \omega\in W\right\}$
@@
 
-We need to select the weights $\psi \in \omega(\mu+\rho)$  with the property $\pi_{\mathfrak{a}_{\bot}} \left(  \psi \right) \in C^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$.
-It means that the scalar product of these weights with all the roots in $\Delta^{+}_{\bot}$ is non-negative.
+We are to select the weights $\psi \in \omega(\mu+\rho)$  with the property
+$\pi_{\mathfrak{a}_{\bot}} \left(  \psi \right) \in \bar{C}^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$.
+It means that the scalar product of these weights with all the roots in $\Delta^{+}_{\bot}$ is nonnegative.
 
@@
 $\mathfrak{a}_{\bot}$-modules we need to project each selected weight
-onto the root space $\Delta^{+}_{\bot}$, substract
+onto the root space $\Delta^{+}_{\bot}$, subtract
 $\rho_{\mathfrak{a}_{\bot}}$ and apply the Weyl dimension formula. The result is shown in the Figure \ref{fig:B4B2anom}.
@@
 
-Branching coefficients for an embedding of affine Lie subalgebra into
+Branching coefficients for an embedding of affine Lie algebra into
 affine Lie algebra can be used to construct modular invariant
-partition functions for Wess-Zumino-Novikov-Witten models of conformal field theory (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
+partition functions for Wess-Zumino-Novikov-Witten models in conformal field theory
+(\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
 In these models current algebras are affine Lie algebras.
 
-The modular invariant partition function is crucial for the conformal theory to be valid on the torus and higher genus Riemann surfaces.
-It is important for the applications of CFT to the string theory and to the critical phenomena description.
+The modular invariant partition function is crucial for the conformal theory to be valid
+on the torus and higher genus Riemann surfaces. It is important for the applications of
+CFT to the string theory and to the critical phenomena description.
 
@@
 \end{equation*}
-Here the sum is over the set of the highest weights of integrable modules of WZW-model and $\chi_{\mu}(\tau)$ are the normalized characters of these modules.
-
-To construct the non-diagonal modular invariants is not an easy problem, although for some model the complete classification of modular invariants is known \cite{1994hepthGannon,1995JMPGannon}.
+Here the sum is over the set of the highest weights of integrable modules in a WZW-model
+and $\chi_{\mu}(\tau)$ are the normalized characters of these modules.
+
+To construct the nondiagonal modular invariants is not an easy problem,
+although for some models the complete classification of modular invariants is known \cite{1994hepthGannon,1995JMPGannon}.
 
 Consider the Wess-Zumino-Witten model with the affine Lie algebra $\mathfrak{a}$.
-Non-diagonal modular invariants for this model can be constructed from the diagonal invariant if there exists affine algebra $\mathfrak{g}$ such that $\mathfrak{a}\subset\mathfrak{g}$.
-Then we can replace the characters of the $\mathfrak{g}$-modules in the diagonal modular-invariant partition function (\ref{eq:36})
+Nondiagonal modular invariants for this model can be constructed from the diagonal
+invariant if there exists an affine algebra $\mathfrak{g}$ such that $\mathfrak{a}\subset\mathfrak{g}$.
+Then we can replace the characters of the $\mathfrak{g}$-modules in the diagonal
+modular invariant partition function (\ref{eq:36})
 by the decompositions
@@
 containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules.
-Thus we obtain the non-diagonal modular-invariant  partition function for the theory with the current algebra $\mathfrak{a}$,
+Thus we obtain the nondiagonal modular-invariant  partition function for the theory with
+the current algebra $\mathfrak{a}$,
 \begin{equation}
   \label{eq:36}
-   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
-\end{equation}
+   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau).
+\end{equation}
+
 The effective reduction procedure is crucial for this construction.
-
 The embedding is required to preserve the conformal invariance.
-Let $X^{\alpha_j}_{-n_j}$ and $\tilde{X}^{\alpha'_j}_{-n_j}$ be the lowering generators for $\mathfrak{g}$ and for $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
-Let $\pi_{\mathfrak{a}}$ be the projection operator of $\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$.
-In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$ the states can be described as
+Let $X^{\alpha_j}_{-n_j}$ and $\tilde{X}^{\alpha'_j}_{-n_j}$ be the lowering generators for
+$\mathfrak{g}$ and for $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
+Let $\pi_{\mathfrak{a}}$ be the projection operator of
+$\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$.
+In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$
+the states can be described as
 \begin{equation*}
@@
 \end{equation*}
-The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance, but this is not the case for the energy-momentum tensor.
-So the energy-momentum tensor of the larger theory should consist only of the generators of $\tilde{X}$.
-Then
+The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance,
+but this is not the case for the energy-momentum tensor. So the energy-momentum tensor of the larger theory
+should contain only the generators $\tilde{X}$. Then the relation
 \begin{equation}
   \label{eq:2}
-  T_{\mathfrak{g}}(z)=T_{\mathfrak{a}}(z),  
+  T_{\mathfrak{g}}(z)=T_{\mathfrak{a}}(z)
 \end{equation}
@@
   \label{eq:111}
-  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}.
 \end{equation}
@@
 
-The relation (\ref{eq:111}) and the asymptotics of the branching functions can be used to prove the finite reducibility theorem \cite{kac1988modular}.
-It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$ only finite number of branching coefficients have non-zero values.
+The relation (\ref{eq:111}) and the asymptotics of the branching functions can be used
+to prove the finite reducibility theorem \cite{kac1988modular}.
+It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$
+only finite number of branching coefficients have nonzero values.
 
@@
 \label{eq:47}
-  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
-\end{equation*}
-
-The modes $L_n$ are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
+  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n.
+\end{equation*}
+The modes $L_n$ are constructed as combination of normally-ordered products of the generators of $\mathfrak{g}$,
 \begin{equation*}
 \label{eq:48}
-  L_n=\frac{1}{2(k+h^v)}\sum_{\alpha}\sum_m:X^{\alpha}_m X^{\alpha}_{n-m}:
-\end{equation*}
-In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
+  L_n=\frac{1}{2(k+h^v)}\sum_{\alpha}\sum_m:X^{\alpha}_m X^{\alpha}_{n-m}: \; .
+\end{equation*}
+In the case of a conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
 
@@
 
-There exist three level 1 fundamental weights in the weight space of $\hat{A}_2$.
+There exist three level one fundamental weights in the weight space of $\hat{A}_2$.
 It is easy to see that the set $\Delta_{\bot}$ is empty and the subalgebra $\mathfrak{a}_{\bot}=0$.
@@
 Let us consider the module $L^{w_0=(0,0;1;0)}$. Here we use the (finite part; level; grade)
-presentation (see section(\ref{sec:notation})) of the highest weight and the finite part
-coordinates are the Dynkin indices.
+presentation of the highest weight and the finite part
+coordinates are the Dynkin indices (see section(\ref{sec:notation})).
 
@@
 The next step is to project the anomalous weights to $P_{\hat A_1}$.
-The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}.
+The result is presented in the Figure \ref{fig:AffineA2_A1_anom_proj} up to the twelfth grade.
 \begin{figure}[h!tb]
@@
 
-Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
+Using the recurrent relation for the anomalous branching coefficients
+we get the result presented in Figure \ref{fig:AffineA2_A1_branching}.
 \begin{figure}[h!tb]
@@
 \end{figure}
-There we see that inside the chamber $\bar{C}_{\hat{A}_1}$, which is isolated in the
-Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights
-both with multiplicities 1.
-These are the highest weights of the $\mathfrak{a}$-submodules and their branching
+Inside the Weyl chamber $\bar{C}_{\hat{A}_1}$
+(its boundaries are indicated in the Figure \ref{fig:AffineA2_A1_branching})
+there are only two nonzero anomalous weights and both have multiplicity 1.
+These are the highest weights of $\mathfrak{a}$-submodules and their branching
 coefficients. So the finite reducibility theorem holds and we get the decomposition
@@
 
-For the other level 1 irreducible modules of $\hat{A}_2$ we get the trivial
+For the other irreducible modules of level one  we get the trivial
 branching
@@
 
-Another natural setting where the reduction problem for affine Lie algebras appears is
-the coset construction in rational conformal field theories \cite{Goddard198588}.
-Coset models are tightly connected with the gauged WZW-models and are actively studied
-in string theory especially in string models on anti-de-Sitter space
+Coset models \cite{Goddard198588} tightly connected with the gauged WZW-models are actively studied
+in string theory, especially in string models on anti-de-Sitter space
 \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}.
-The characters of the coset model are connected with the branching functions,
+The characters in coset models are proportional to the branching functions,
 \begin{equation}
@@
 \end{equation}
-where
+with
 \begin{equation*}
@@
 \end{equation*}
-
 The problem of the branching functions construction in the coset models was considered
@@
 Let us return to the example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
-$A_1\subset B_2$.
-Since this embedding is regular and $x_e=1$, the level of the  subalgebra modules is equal to that of the initial module.
+$A_1 \longrightarrow B_2$.
+Since this embedding is regular and $x_e=1$, the subalgebra modules and the initial module are of the same level.
 The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection
@@
 $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$
-with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
+with the corresponding values $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineB2A1Fan}).
 We restricted the computation to the twelfth grade.
@@
 where the finite part coordinates are in the orthogonal basis $e_1,e_2$.
-
 The set of anomalous weights for this module up to the sixth grade is presented in the Figure \ref{fig:affine_B2_anom_point}.
 In the grade zero it is exactly the set of the anomalous weights for the embedding of
-the classical Lie algebras $A_1\subset B_2$ depicted in the  Figure \ref{fig:B2_A1}.
+the classical Lie algebras $A_1\subset B_2$ that can be seen in the  Figure \ref{fig:B2_A1}.
 The weights $\omega (w_1+\rho)-\rho$ are marked by crosses if $\epsilon(\omega)=1$ and by circles otherwise.
@@
 
-Performing the next step of the algorithm \ref{sec:algorithm} we project the anomalous weights to
+According to the algorithm \ref{sec:algorithm} we project the anomalous weights to
 $P_{\hat{A_1}}$ and find the dimensions of the corresponding
@@
 \ref{fig:AffineB2_A1_anom_proj} up to the twelfth grade.
-\ref{fig:AffineB2_A1_anom_proj}.
 \begin{figure}[h!tb]
@@
 
-Selecting the elements inside the  Weyl chamber
+The multiplicities of the weights inside the  Weyl chamber
 $\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
-we get the branching coefficients up to the twelfth grade,
+are the branching coefficients (up to the twelfth grade),
 \begin{eqnarray*}
@@
     797 L_{\hat{A_1}}^{w_0-11\delta}\oplus 1080 L_{\hat{A_1}}^{w_1-12\delta}\oplus
-    1180 L_{\hat{A_1}}^{w_0-12\delta}
+    1180 L_{\hat{A_1}}^{w_0-12\delta}\oplus \dots
 \end{eqnarray*}
-This result can be presented as the set of branching functions \cite{kac1990idl}:
+This result can be presented as the set of branching functions:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-Here $q=\exp (2\pi i \tau)$, the lower index enumerates the branching functions according
-to their highest weights in $P^+_{\hat{A_1}}$,
-these are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
-
-Now we can use the relation \ref{eq:31} to get the expansion of the $B_2/A_1$-coset characters:
+Here $q=\exp (2\pi i \tau)$ and the lower index enumerates the branching functions according
+to their highest weights in $P^+_{\hat{A_1}}$.
+These are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
+
+Now we can use the relation (\ref{eq:31}) to get the expansion of the $B_2/A_1$-coset characters:
 \begin{equation*}
@@
 \label{sec:conclusion}
-We have shown that the injection fan technique can be used to deal with the nonmaximal subalgebras.
-It was demonstrated that for such subalgebras an auxiliary subset $\Delta^{+}_{\bot}$ must be extracted
+We have demonstrated that the injection fan technique can be used to deal with the nonmaximal subalgebras.
+It was found out that for such subalgebras an auxiliary subset $\Delta^{+}_{\bot}$ must be extracted
 from the set of positive roots $\Delta_{\mathfrak{g}}^{+}$.
@@
 
-We have demonstrated the efficiency of the proposed generalizations of the injection fan algorithm.
+The efficiency of the injection fan algorithm was verified.
 Its possible applications to some physical problems were discussed.
@@
 
-The presented technique to the reduction problem can also be applied in the study of integrable spin-chains.
-
 \section{Acknowledgements}
@@
 
+\section*{References}
 \bibliography{article}{}
-\bibliographystyle{unsrt}
+\bibliographystyle{iopart-num}
 

### 2010-07-09 AffineLieAlgebras/DualFunctions/ModularProperties.tex
Submission to JPhysA completed

--- 2010-05-21 AffineLieAlgebras/DualFunctions/article.tex
@@
 \begin{document}
-\title{\textbf{{\Large {System of dual functions in the reduction of affine Lie algebra representations}}}}
+\title{Modular transformations in representation theory of affine Lie algebras}
 \author{Vladimir Lyakhovsky \thanks{ Supported by
@@
 \begin{abstract}
-  Using the recurrent relation for the series expansion of the affine Lie algebra branching functions we construct the dual set of the functions, which can be completely described using Weyl symmetry of affine Lie algebra.
-Explicit construction of the dual functions can be carried out using the geometric finite automata approach.
-The task of the explicit construction of the branching functions is then rewritten as the procedure of the inversion of matrix of dual functions.
-Finally we study the properties of the dual functions under modular and conformal transformations and discuss possible applications in two-dimensional conformal field theory.
+  We review the appearance of modular transformation in the representation theory of affine Lie algebras, especially the modular properties of branching and string function.
 \end{abstract}
+\begin{Def}
+  Modular form is the analytic function on the upper half plane which transforms in the following way under the modular transformations
+  \begin{equation}
+    \label{eq:1}
+    A=
+    \begin{pmatrix} a & b\\ c & d
+    \end{pmatrix} \quad\mbox{where}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+  \end{equation}
+  \begin{equation}
+    \label{eq:2}
+    z\to A z=\frac{az+b}{cz+d}
+  \end{equation}
+\end{Def}
+
+{\bf Questions}
+\begin{itemize}
+\item The modular properties of WZW models are naturally connected with the problem of theory definition on the torus.
+What can we say about the pure representation theory?
+What is the analogue of the torus?
+\item What kind of constrains on the stars and fans follow from the modular invariance?
+\item The modular invariance is important in the number theory. What problems of number theory are connected through the modular transformations with the representation theory?
+\item I need to write about the Hecke algebras
+\item How are Hecke algebras connected to the modular forms?
+\item Are there any kind of modular invariance analogues for the finite-dimensional Lie algebras? There exists the lattice.
+\item What become of modular invariance during the quantization? Are there any properties of quantum integrable systems that follow from the modular invariance?
+\end{itemize}
 

### 2010-07-09 AffineLieAlgebras/DualFunctions/ModularProperties.tex
Empty file added

--- 2010-05-21 AffineLieAlgebras/DualFunctions/article.tex
@@
 \begin{document}
-\title{\textbf{{\Large {System of dual functions in the reduction of affine Lie algebra representations}}}}
+\title{Modular properties of string, branching and dual functions}
 \author{Vladimir Lyakhovsky \thanks{ Supported by
@@
 \begin{abstract}
-  Using the recurrent relation for the series expansion of the affine Lie algebra branching functions we construct the dual set of the functions, which can be completely described using Weyl symmetry of affine Lie algebra.
-Explicit construction of the dual functions can be carried out using the geometric finite automata approach.
-The task of the explicit construction of the branching functions is then rewritten as the procedure of the inversion of matrix of dual functions.
-Finally we study the properties of the dual functions under modular and conformal transformations and discuss possible applications in two-dimensional conformal field theory.
+  We review modular forms and discuss modular properties of string, branching and dual functions.
 \end{abstract}
 
-\bibliography{article}{}
-\bibliographystyle{utphys}
-
 \end{document}

### 2010-07-12 AffineLieAlgebras/DualFunctions/ModularProperties.tex
Some work on text about modular properties.

--- 2010-07-09 AffineLieAlgebras/DualFunctions/ModularProperties.tex
@@
 \usepackage{color}
-\usepackage[pdftex]{graphicx}
+\usepackage{graphicx}
 \pagestyle{plain}
@@
 \newenvironment{comment}
-{\par\noindent{\bf TODO}\\}
+{\par\noindent{\bf Comment}\\}
 {\\\hfill$\scriptstyle\blacksquare$\par}
@@
 \begin{document}
-\title{Modular transformations in representation theory of affine Lie algebras}
+
+\title{Modular properties of string, branching and dual functions}
+
 \author{Vladimir Lyakhovsky \thanks{ Supported by
@@
 \begin{Def}
-  Modular form is the analytic function on the upper half plane which transforms in the following way under the modular transformations
+  {\bf Modular transformation}
   \begin{equation}
@@
 \end{Def}
+\begin{Def}
+  {\bf Modular form} of weight $k$ is the analytic function $F$ on the upper half plane with infinity ( $F(i\infty)$ is holomorphic) which transforms in the following way under the modular transformations
+  \begin{equation}
+    \label{eq:3}
+    F(Az)=(cz+d)^k F(z)
+  \end{equation}
+\end{Def}
 
-{\bf Questions}
+This definition can be reformulated as the requirement for the modular form to be the function of lattices. 
+Consider the general lattice on the complex plane.
+It consists of the points $(pv,qw)$ where $p,q\in \mathbb{Z},\; w,v\in \mathbb{C}$.
+This lattice can be generated by $(z,1), \; z=v/w$ or by $(az+b,cz+d), \; a,b,c,d\in\mathbb{Z},\; ad-bc=1$.
+It is denoted by $\Lambda_z$.
+\begin{equation}
+  \label{eq:4}
+  \frac{1}{cz+d}\Lambda_z=\Lambda_{Az}
+\end{equation}
+Then we can say that the modular form of weight $k$ is the function $f$ of lattices such that $f(\alpha\Lambda)=\alpha^{-k}f(\Lambda)$.
+
+For $k\geq 4$ we have the following example (Eisenstein series):
+\begin{equation}
+  \label{eq:5}
+  G_k(\Lambda)=\sum_{\lambda\in \Lambda, \lambda\neq 0} \lambda^{-k}
+\end{equation}
+Vector space of weight $k$ modular forms is finite dimensional.
+
+The quotient of the complex numbers by a lattice is an elliptic curve and every elliptic curve arises in this way. ($y^2=f(x)$, $f$ - cubic polynomial).
+
+For the $d$-dimensional lattice $L$ with the non-degenerate form $(\cdot,\cdot)$ we can define theta-functions
+\begin{equation}
+  \label{eq:8}
+  \Theta_L (\tau)=\sum_{x\in L}e^{\pi i \tau (x,x)}
+\end{equation}
+$\Theta_L$ is modular of weight $d/2$.
+
+\begin{comment}
+  How can we link the $d$-dimensional lattice $L$ with the lattice $\Lambda_{\tau}$?
+\end{comment}
+
+Now we can consider the weight lattice of the affine Lie algebra $\mathfrak{g}$.
+Cartan subalgebra:
+\begin{equation}
+  \label{eq:6}
+  \mathfrak{h}=\mathbb{C}\Lambda_0\oplus \co{\mathfrak{h}}\oplus \mathbb{C}\delta
+\end{equation}
+$h\in \mathfrak{h}$
+\begin{equation}
+  \label{eq:7}
+  h=(z;\tau;t)=2\pi i (-\tau \Lambda_0 +z + t\delta)\quad (\tau,t\in \mathbb{Z}, z\in \co{\mathfrak{h}})
+\end{equation}
+
+It is known that string functions
+\begin{eqnarray}
+  \label{eq:9}
+  \sigma^{(\mu)}_{\lambda}=\sum_n mult^{(\mu)}(\lambda-n\delta)e^{\lambda-n\delta}\\
+  \sigma^{(\mu)}_{\lambda}(\tau)=\sigma^{(\mu)}_{\lambda}|(0;\tau;0)=\sum_n mult^{(\mu)}(\lambda-n\delta)e^{2\pi i n\tau}
+\end{eqnarray}
+can be rescaled to become modular forms:
+\begin{equation}
+  \label{eq:10}
+  c^{(\mu)}_{\lambda}=e^{2\pi i s(\mu,\lambda)}\sum_n mult^{(\mu)}(\lambda-n\delta)e^{2\pi i n\tau}
+\end{equation}
+where
+\begin{equation}
+  \label{eq:11}
+  s(\mu,\lambda)=\frac{(\mu+\rho,\mu+\rho)}{2(k+g)}-\frac{(\rho,\rho)}{2g}-\frac{(\lambda,\lambda)}{2k}.
+\end{equation}
+(Here $k$ - level of the representation, $g$ - dual Coxeter number).
+
+See Kac, Peterson 1984 for the original proof.
+\section{Questions}
+\label{sec:questions}
 \begin{itemize}

### 2010-07-18 AffineLieAlgebras/DualFunctions/ModularProperties.tex
Some work

@@
 \begin{Def}
-  {\bf Modular form} of weight $k$ is the analytic function $F$ on the upper half plane with infinity ( $F(i\infty)$ is holomorphic) which transforms in the following way under the modular transformations
+  {\bf Modular form} of weight $k$ is the function $F$ on the upper half plane with infinity which transforms in the following way under the modular transformations
   \begin{equation}
@@
 \end{equation}
-Vector space of weight $k$ modular forms is finite dimensional.
+\begin{comment}
+Eisenstein series are important in the discussion of $\Gamma_n$-modular forms, see later.
+\end{comment}
 
+This requirement is not really strong, additional requirement of $F$ being holomorphic function at the upper half-plane with infinity is really powerful.
+It is well-known that the space of the (holomorphic) modular forms of weight $k$ is finite-dimensional.
+We discuss it later in the connection with the cusp forms and forms of weight $k$ over $\Gamma(N)$.
+
+\begin{comment}
 The quotient of the complex numbers by a lattice is an elliptic curve and every elliptic curve arises in this way. ($y^2=f(x)$, $f$ - cubic polynomial).  
+\end{comment}
 
-For the $d$-dimensional lattice $L$ with the non-degenerate form $(\cdot,\cdot)$ we can define theta-functions
+\begin{Def}
+  {\bf Index} of a subgroup $H\subset G$ is the number of cosets of $H$ in $G$, it is denoted by $\left|G:H\right|$.
+\end{Def}.
+
+Let $\Gamma \subset \mathrm{SL}(2,\mathbb{Z})$ be a subgroup of finite index.
+Given a positive integer $k$, a modular form $F$ for $\Gamma$ of weight $k$ is a holomorphic function on the upper half-plane which transforms as in \eqref{eq:3} and is also holomorphic at the cusps of $\Gamma$.
+
+For $N\in \mathbb{N},$ define
+\begin{equation}
+  \label{eq:12}
+  \Gamma(N)=\left\{
+      \begin{pmatrix} a & b \\ c & d
+      \end{pmatrix}
+      \equiv
+      \begin{pmatrix}
+        1 & 0 \\
+        0 & 1
+      \end{pmatrix} (\text{mod}\; N)
+      \right|\left.
+        \begin{matrix}
+          a,b,c,d\in \mathbb{Z},\quad ad-bc=1\\
+          a\equiv d\equiv 1\; \text{mod}\; N,\quad b\equiv c\equiv 0\; \text{mod}\; N
+        \end{matrix}
+      \right\}
+  \end{equation}
+The subgroup $\Gamma(N)$ has {\it finite index} in $\Gamma(1)=SL(2,\mathbb{Z})$. For any $\tau\in \mathbb{C}$ there exists element of $SL(2,\mathbb{Z})$, which transforms it to the fundamental domain.
+
+For $A\in SL(2,\mathbb{Z})$ define
+\begin{equation}
+  \label{eq:13}
+  j(A,\tau)=c\tau+d.
+\end{equation}
+Note that
+\begin{equation}
+  \label{eq:14}
+  j(BA,\tau)=j(B,A\tau)j(A,\tau).
+\end{equation}
+For any subgroup $\Gamma$ of finite index define a {\bf multiplier system} $\chi$ as a mapping
+\begin{equation}
+  \label{eq:15}
+  \chi:\Gamma\to U(1).
+\end{equation}
+Let $k\in \mathbb{R}$.
+A complex valued holomorphic function $f$ on the upper half-plane of the complex plane is a modular form of weight $k$ with respect to $\Gamma$ if there exists a multiplier system $\chi$ for $\Gamma$ with
+\begin{equation}
+  \label{eq:16}
+  f(\tau)=\chi(A) j(A,\tau)^{-k} f(A\tau),
+\end{equation}
+for all $\tau$ in the upper half-plane and $A\in \Gamma$.
+
+For the $d$-dimensional lattice $L$ with the non-degenerate form $(\cdot,\cdot)$ we can define theta functions
 \begin{equation}
@@
 
-Now we can consider the weight lattice of the affine Lie algebra $\mathfrak{g}$.
-Cartan subalgebra:
+Since this construction gives us the modular forms from any lattice it is natural to introduce theta functions on the weight lattice of affine Lie algebra.
+
+The connection between the theta functions and the string/branching functions is revealed in the papers \cite{kac1984infinite,kac1988modular}.
+Here we briefly describe this connection using the text of the book \cite{kass1990ala} (see pages 212-218).
+
+Now we consider the weight lattice of the affine Lie algebra $\mathfrak{g}$.
+Its Cartan subalgebra has the following decomposition:
 \begin{equation}
@@
 
-See Kac, Peterson 1984 for the original proof.
 \section{Questions}

### 2010-08-01 AffineLieAlgebras/DualFunctions/ModularProperties.tex
Mod prop

--- 2010-07-12 AffineLieAlgebras/DualFunctions/ModularProperties.tex
@@
 
+For $N\in \mathbb{N},$ define
+\begin{equation}
+  \label{eq:12}
+  \Gamma(N)=\left\{
+      \begin{pmatrix} a & b \\ c & d
+      \end{pmatrix}
+      \right|\left.
+        \begin{matrix}
+          a,b,c,d\in \mathbb{Z},\quad ad-bc=1\\
+          a\equiv d\equiv 1\; \text{mod}\; N,\quad b\equiv c\equiv 0\; \text{mod}\; N
+        \end{matrix}
+      \right\}
+  \end{equation}
+The subgroup $\Gamma(N)$ has {\it finite index} (define!) in $\Gamma(1)=SL(2,\mathbb{Z})$.
+For any $\tau\in \mathbb{C}$ there exists element of $SL(2,\mathbb{Z})$, which transforms it to the fundamental domain.
+
+For $A\in SL(2,\mathbb{Z})$ define
+\begin{equation}
+  \label{eq:13}
+  j(A,\tau)=c\tau+d.
+\end{equation}
+Note that
+\begin{equation}
+  \label{eq:14}
+  j(BA,\tau)=j(B,A\tau)j(A,\tau).
+\end{equation}
+For any subgroup $\Gamma$ of finite index define a {\bf multiplier system} $\chi$ as a mapping
+\begin{equation}
+  \label{eq:15}
+  \chi:\Gamma\to U(1).
+\end{equation}
+Let $k\in \mathbb{R}$.
+A complex valued holomorphic function $f$ on the upper half-plane of the complex plane is a modular form of weight $k$ with respect to $\Gamma$ if there exists a multiplier system $\chi$ for $\Gamma$ with
+\begin{equation}
+  \label{eq:16}
+  f(\tau)=\chi(A) j(A,\tau)^{-k} f(A\tau),
+\end{equation}
+for all $\tau$ in the upper half-plane and $A\in \Gamma$.
+
 For the $d$-dimensional lattice $L$ with the non-degenerate form $(\cdot,\cdot)$ we can define theta-functions

### 2010-08-01 GeneralOverview/IntegrableSystems.tex
*** empty log message ***

@@
 \usepackage{ucs}
-\usepackage[utf8x]{inputenc}
-\usepackage[russian]{babel}
+%\usepackage[utf8x]{inputenc}
+%\usepackage[russian]{babel}
 \usepackage{cmap}
@@
 \theoremstyle{definition} \newtheorem{Def}{Definition}
+\newenvironment{comment}
+{\par\noindent{\bf Comment}\\}
+{\\\hfill$\scriptstyle\blacksquare$\par}
+
+\newtheorem{statement}{Statement}
+\theoremstyle{definition} \newtheorem{Def}{Definition}
+\newcommand{\go}{\overset{\circ }{\frak{g}}}
+\newcommand{\ao}{\overset{\circ }{\frak{a}}}
+\newcommand{\co}[1]{\overset{\circ }{#1}}
+
 \begin{document}
-\section{Интегрируемые системы}
-\label{sec:IntSys}
 
-\subsection{Интегируемые системы}
-\label{sec:-}
+\title{Introduction to quantum integrable systems and quantum groups}
+
+\begin{abstract}
+  We review quantum integrable systems and discuss the connection with the representation theory of finite-dimensional and affine Lie algebras.
+Then we consider the quantum groups which are constructed as the deformations of the universal enveloping algebras.
+\end{abstract}
+
+\section{Introduction. Historical overview.}
+\label{sec:intr-hist-overv}
 

### 2010-08-01 AffineLieAlgebras/DualFunctions/article.tex

@@
 
+\section{Introduction}
+\label{sec:introduction}
+
+We consider the following problems.
+\begin{itemize}
+\item Calculation of the weight multiplicities in the (irreducible highest-weight) module of (simple) finite-dimensional Lie algebra.
+\item Calculation of the branching coefficients for the decomposition of the module of finite-dimensional algebra to the modules of the sub-algebra.
+\item Calculation of the weight multiplicities in the (irreducible highest-weight) module of (affine) Kac-Moody algebra.
+\item Calculation of the branching coefficients for the decomposition of the module of affine Lie algebra to the modules of the affine sub-algebra.
+\end{itemize}
+
+All these problems are solved using the recurrent relations, such as Freudenthal or Racah formula. 
+The recurrent relations can be written in matrix form if one introduces the ordering on the weight lattice (or fundamental domain of it).
+
+If we consider these problems not for one selected module but for all possible modules, we get the infinite multi-diagonal matrix.
+It is similar to the Jacobi matrices, which give rise to the systems of orthogonal functions.
+
+Studying the recurrent relations in matrix form in more details we can find out that there exists two tightly connected systems of the orthogonal functions.
+These systems are dual in the sense that they correspond to the mutually inverse (infinite) matrices.
+
+In this paper we describe the construction of these systems of functions and study their properties.
+
+The paper is organised as follows.
+In section \ref{sec:finite-dimens-lie} we describe the recurrent process that gives rise to the systems of the orthogonal polynomials.
+This construction in some sense is not new (e.g.
+see \cite{2010arXiv1001.3683N}), but we explicitly describe the dual system of functions.
+The section \ref{sec:affine-lie-algebras} is devoted to the systems of special functions connected with the affine Lie algebras.
+We establish the modular properties of the dual functions.
+Possible applications in physics are described in the next section \ref{sec:poss-appl}.
+We discuss the importance of the tensor product decompositions for the integrable systems which follows from the Hecke duality.
+Also we consider conformal field theory.
+In the conclusion \ref{sec:conclusion} we overview the results and state some open questions.
+
+\section{Finite-dimensional Lie algebras}
+\label{sec:finite-dimens-lie}
+
+\section{Affine Lie algebras}
+\label{sec:affine-lie-algebras}
+
+\subsection{Modular properties of the dual functions}
+\label{sec:modul-prop-dual}
+
+\section{Possible applications}
+\label{sec:poss-appl}
+
+\section{Conclusion}
+\label{sec:conclusion}
+
 \bibliography{article}{}

### 2010-08-01 AffineLieAlgebras/DualFunctions/article.tex
Start of the section on finite-dimensional Lie algebras.

@@
 \label{sec:finite-dimens-lie}
+Consider the irreducible highest-weight module $L^{(\mu)}_{\mathfrak{g}}$ of the simple Lie algebra $\mathfrak{g}$. 
+The recurrent relation for the weight multiplicities can be written from the Weyl character formula \cite{lyakhovsky1996rra}:
+\begin{equation}
+  \label{eq:1}
+  \mathrm{ch} L^{(\mu)}_{\mathfrak{g}}=\frac{\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w \rho -\rho}}
+\end{equation}
+Let us limit our consideration to the fundamental domain (main Weyl chamber). The left side of this equation can be written as
+\begin{equation}
+  \label{eq:2}
+   \mathrm{ch} L^{(\mu)}_{\mathfrak{g}}=\sum_{\lambda\in \bar{C}_{\mathfrak{g}}} m^{(\mu)}_{\lambda} e^{\lambda}
+\end{equation}
+Multiplying the equation \eqref{eq:1} by the denominator we get the recurrent relation for the weight multiplicities $m^{(\mu)}_{\lambda}$:
+\begin{equation}
+  \label{eq:3}
 
+\end{equation}
 \section{Affine Lie algebras}

### 2010-08-02 AffineLieAlgebras/DualFunctions/article.tex
One formula added

@@
 \end{equation}
-Multiplying the equation \eqref{eq:1} by the denominator we get the recurrent relation for the weight multiplicities $m^{(\mu)}_{\lambda}$:
+Multiplying the equation \eqref{eq:1} by the denominator  and collecting the common terms we get the recurrent relation for the weight multiplicities $m^{(\mu)}_{\lambda}$:
 \begin{equation}
   \label{eq:3}
-
+  \sum_{w\in W} \epsilon(w) m^{(\mu)}_{\lambda-w\rho+\rho}=\sum_{w\in W}\epsilon(w) \delta_{\lambda,w(\mu+\rho)-\rho}
 \end{equation}

### 2010-08-03 AffineLieAlgebras/DualFunctions/article.tex
The problem is how to enumerate weights inside the main Weyl chamber?

@@
 \end{equation}
+If we consider the weights inside the main Weyl chamber the sum on the right-hand side is reduced to the single term $\delta_{\lambda,\mu}$.
+For the weight $\lambda-w\rho+\rho\not\in \bar{C}_{\mathfrak{g}}$ there exists weight $\xi\in \bar{C}_{\mathfrak{g}}$ and Weyl group element $v\in W$ such that $v\xi=\lambda-w\rho+\rho$, so we can limit the computation of weight multiplicities by the main Weyl chamber.
+This procedure was called ``folding of the fan'' in \cite{il2010folded}.
+Now we want to rewrite the equation \eqref{eq:3} in matrix form similarly to \cite{2010arXiv1001.3683N}.
+We need to choose the ordering on the set of weights in the closure of fundamental domain $\bar{C}_{\mathfrak{g}}$.
+We use the following procedure.
+Consider some ordering of the simple roots (e.g.
+the numbering of nodes of Dynkin diagram from left to right).
+Then the weight with the Dynkin labels $[0,\dots,0]$ get the index 1, $[0,\dots,0,1]$ the index 2, $[0,\dots,0,1,0]$ - 3 etc.
 \section{Affine Lie algebras}

### 2010-09-12 AffineLieAlgebras/DualFunctions/article.tex
Some minor addition to dual functions

@@
 
+\subsection{Notation}
+\label{sec:notation}
+We use the following notation in this paper.
+
+Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
+underlying finite-dimensional subalgebras $\go$ and $%
+\ao$ and an injection $\frak{a}\longrightarrow \frak{g%
+}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
+correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
+}}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
+}_{\go}^{\ast }$\ .
+
+We use the following notations:
+
+$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
+of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
+-module with the highest weight $\nu $ );
+
+$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
+\left( \mbox{resp. }\frak{a}\right) $ ;
+
+$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
+^{+} $ $\left( \mbox{resp. }\Delta _{\frak{a}}^{+}\right) $--- the positive
+root system (of $\frak{g}$ and $\frak{a}$ respectively);
+
+$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
+\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $\Delta
+$ (resp. in $\left( \Delta _{\frak{a}}\right) $);
+
+$\co{\Delta}$ , $\left( \co{\Delta _{\frak{a}}}%
+\right)$ --- the finite root system of the subalgebra $\co{%
+\frak{g}}$ (resp. $\co{\frak{a}}$);
+$\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);
+
+$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ --- the
+weight diagram of $L^{\mu }$ $\left( \mbox{resp. }L_{\frak{a}}^{\nu }\right)
+$ ;
+
+$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
+
+$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
+
+$\bar{C}, \left(\bar{C_{\mathfrak{a}}}\right)$ --- the closure of the fundamental Weyl chamber;
+
+$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
+
+$\epsilon \left( w\right) :=\det \left( w\right) $ ;
+
+$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $i
+$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\frak{a}%
+\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+
+$\delta $ --- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);
+
+$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
+}\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\frak{a}%
+\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+
+$\co{\xi }$ , $\co{\xi _{\left( \frak{a}\right) }}$
+--- the finite (classical) part of the weight $\xi \in P$ , $\left( \mbox{%
+resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $;
+
+$\lambda =\left( \co{\lambda };k;n\right) $ --- the
+decomposition of an affine weight indicating the finite part $\co{\lambda }$, level $k$ and grade $n$;
+
+$P$ $\left( \mbox{resp. } P_{\frak{a}}\right) $ \ --- the weight lattice;
+
+$M \left( \mbox{resp. }M_{\frak{a}}\right) :=$
+
+\noindent $=\left\{
+\begin{array}{c}
+\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\mbox{ }\left( \mbox{resp. }%
+\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \frak{a}\right) i}^{\vee }\right)
+\mbox{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
+\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\mbox{ }\left( \mbox{resp. }\sum_{i=1}^{r}%
+\mathbf{Z}\alpha _{\left( \frak{a}\right) i}\right) \mbox{for }A_{r}^{\left(
+u\geq 2\right) }\mbox{ and }A\neq A_{2r}^{\left( 2\right) },
+\end{array}
+\right\} ;$\\
+$\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
+$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}}}\epsilon (w)e^{w\circ (\nu +\rho
+_{_{\frak{a}}})-\rho _{_{\frak{a}}}}$ --- the corresponding singular weight
+element for the $\frak{a}$-module $L_{\frak{a}}^{\nu }$;
+
+$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
+a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
+\xi \in P$ $\left( \mbox{resp. }\in P_{\frak{a}}\right) $ for the module $%
+L^{\mu }$ $\left( \mbox{resp. }L_{\frak{a}}^{\nu }\right) $ with the
+coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
+\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
+)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
+w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
+\circ (\nu +\rho _{a})-\rho _{a}}$ );
+
+$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
+}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mbox{%
+resp. }\in P_{\frak{a}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
+L_{\frak{a}}^{\nu } $);
+
+$ch\left( L^{\mu }\right) $ $\left( \mbox{resp. }ch\left( L_{\frak{a}}^{\nu
+}\right) \right) $--- the formal character of $L^{\mu }$ $\left( \mbox{resp. }%
+L_{\frak{a}}^{\nu }\right) $;
+
+$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
++\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
+\mathrm{{mult}\left( \alpha \right) }}}=\frac{\Psi ^{\left( \mu \right) }}{%
+\Psi ^{\left( 0\right) }}$ --- the Weyl-Kac formula;
+
+$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
+mult}\left( \alpha \right) }}=\Psi ^{\left( 0\right) }\quad $;
+
+\noindent $\left( \mbox{resp. }R_{\frak{a}}:=\prod_{\alpha \in \Delta _{%
+\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{%
+\left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $--- the
+denominator;
+
+$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus
+\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$
+ --- the module decomposition with respect to $\frak{a}\longrightarrow \frak{g}$;
+
+$b^{(\mu)}_{\nu}$ --- the branching coefficients,
+
+\begin{equation}
+  \label{eq:21}
+  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
+        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
+  }^{\left( \mu \right) }e^{\lambda };
+\end{equation}
+
+ $k_{\lambda}$ --- the anomalous branching coefficients, notice that
+\begin{equation*}
+%  \label{eq:20}
+  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}};
+\end{equation*}
+
+$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$ --- the embedding index.
+
 \section{Finite-dimensional Lie algebras}
@@
 We need to choose the ordering on the set of weights in the closure of fundamental domain $\bar{C}_{\mathfrak{g}}$.
-We use the following procedure.
+We use the following natural procedure.
 Consider some ordering of the simple roots (e.g.
 the numbering of nodes of Dynkin diagram from left to right).
-Then the weight with the Dynkin labels $[0,\dots,0]$ get the index 1, $[0,\dots,0,1]$ the index 2, $[0,\dots,0,1,0]$ - 3 etc.
+Let's denote the weights by the Dynkin labels.
+Then the task is to enumerate the set $\{0\}\cup Z_{+}^r$.
+$[0,\dots,0]$ get the index 1, $[0,\dots,0,1]$ the index 2, $[0,\dots,0,1,0]$ - 3 etc.
 \section{Affine Lie algebras}

### 2010-09-12 AffineLieAlgebras/InformalNotes/article.tex
New definitions are introduced, the proof is rewritten.

@@
 \newtheorem{statement}{Statement}
+\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}
+\theoremstyle{definition}
+\newtheorem{corollary}{Corollary}[theorem]
+\theoremstyle{definition}
 \newtheorem{mynote}{Note}[section]
-%\theoremstyle{definition} \newtheorem{Def}{Definition}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
 \end{abstract}
+\ams{17B67, 17B10}
 \submitto{\JPA}
@@
 
-Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator $R$
-(when it is projected to $P_{\mathfrak{a}}$) the injection fan technique \cite{ilyin812pbc} can be properly modified.
-The result is the generalized recurrent relation for anomalous branching
-coefficients (\ref{eq:21}):
-\begin{equation}
-  \label{eq:1}
-  \begin{array}{c}
-      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
-  {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-  \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
-\left.
-+\sum_{\gamma \in
-\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
-+\gamma }^{\left( \mu \right) }\right).
-  \end{array}
-   \end{equation}
-Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by those roots of $\mathfrak{g}$ that are
-orthogonal to $P_{\mathfrak{a}}$, $W_{\bot}$ is the corresponding Weyl group,
-$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
-of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
-(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
-is the multiplicity of $e^{\gamma}$ in this expansion.
-In the next subsection we study the situation in details and prove the relation (\ref{eq:1}).
-
-\subsection{Proof of the recurrent relation}
-\label{sec:proof}
-
-Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
-projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
-\begin{equation*}
-%  \label{eq:3}
-  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
-    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
-  \Longrightarrow\quad
-  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
-  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
-\end{equation*}
-The Weyl-Kac character formula leads to
-the relation
-\begin{equation}
-  \label{eq:4}
-  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
-  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
-  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
-  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
-  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
-\end{equation}
-
-Consider the positive roots $\alpha\in \Delta$ orthogonal to $P_{\mathfrak{a}}$.
-Denote the subset of such roots by $\Delta^{+}_{\bot}
-=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
-\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
-Notice that if $\Delta^{+}_{\bot}\neq \emptyset$ the corresponding Weyl reflections
-generate a subgroup $W_{\bot}$ of the group $W$. Consider the roots $\alpha,\;
-\beta\in \Delta^{+}_{\bot}$ and the corresponding reflections
-$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since the roots in $\Delta_{\mathfrak{a}}$
-are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$
-and $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$
-the subgroup $W_{\bot}$ preserves the roots in $\Delta_{\mathfrak{a}}$.
-The subsystem $\Delta_{\bot}$
-can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
-
-Now we are to find out when the subset $\Delta^{+}_{\bot}$ is nonempty
-with the nontrivial subgroup $W_{\bot}$ and the subalgebra $\mathfrak{a}_{\bot}$.
-
-If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then $r_{\mathfrak{a}}=r$ and
- $\Delta^{+}_{\bot}$ is empty.
-On the other hand
-nonmaximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
-through the chain of maximal embeddings
-$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
-The maximal regular embeddings can be described by the elimination of one or two roots
-from the extended Dynkin diagram of the algebra. When the process gives us
-nonconnected diagrams we immediately fix the roots orthogonal to $P_{\mathfrak{a}}$.
+We consider an injection of affine Lie algebras $\frak{a}\longrightarrow \frak{g%
+}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$.
+In this section we deduce the general recurrent relation (\ref{eq:1}) for the anomalous branching coefficients (\ref{eq:21}).
+This relation is then used to formulate the practical computational algorithm (Subsection \ref{sec:algorithm}).
+In the earlier paper \cite{ilyin812pbc} the following limited setup was considered: $\mathfrak{a}$ was required to be the maximal subalgebra of $\mathfrak{g}$ so that no zeros arrive in the Weyl denominator $R$.
+Here we raise this limitation and study the general case $\mathfrak{a}\subset\mathfrak{g}$.
+
+\subsection{Some definitions}
+\label{sec:some-definitions}
+
+We need to introduce several additional definitions and state some technical results to formulate and prove the recurrent relation (\ref{eq:1}).
+
+\begin{definition}
+  Denote by $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\mathfrak{a}} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$.
+\end{definition}
+
+\begin{definition}
+  Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
+\end{definition}
+\begin{mynote}
+  The subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\mathfrak{a}}$.
+\end{mynote}
+\begin{definition}
+  The subsystem $\Delta_{\bot}=\Delta^{+}_{\bot}\cup \left(-\delta^{+}_{\bot}\right)$ determines the subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
+\end{definition}
+
+We need to know when the subset $\Delta^{+}_{\bot}$ is non-empty and $W_{\bot},\mathfrak{a}_{\bot}$ are non-trivial. So we state several simple lemmas.
+
+For the simple finite-dimensional Lie algebras $\ao,\go$ all the regular embeddings can be obtained by the successive elimination of the nodes in the extended Dynkin diagram of $\go$.
+This leads to the lemma
+\begin{lemma}
+  For the regular embedding $\ao\subset \go$ 
+  \renewcommand{\theenumi}{\alph{enumi}}
+  \begin{enumerate}
+  \item $\Delta^{+}_{\bot}=\emptyset$ if $\ao$ is maximal
+  \item If the extended Dynkin diagram of $\go$ contains the disconnected subdiagrams of $\ao$ and some subalgebras $\left\{\co{\mathfrak{a}_j}\right\}$ then $\Delta^{+}_{\bot}\neq \emptyset$ and $\co{\mathfrak{a}_j}\subset \mathfrak{a}_{\bot}$.
+  \end{enumerate}
+\end{lemma}
+\begin{mynote}
   The complete classification of the regular subalgebras for affine Lie algebras can be
   found in the recent paper \cite{1751-8121-41-36-365204}.
-
-For a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$
-and $\mathfrak{g}$ are simple the sufficient condition for $\Delta^{+}_{\bot}$ to be
-nontrivial can be formulated as follows:
-if the Dynkin diagram of $\mathfrak{g}$ contains the disconnected
-subdiagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
-then the subset $\Delta_{\bot}$ is not empty,
-subalgebra $\mathfrak{a}_{\bot}$ is nontrivial and
-$\left\{\mathfrak{\bar{a}}_j\right\}$ are the subalgebras of $\mathfrak{a}_{\bot}$.
-
-Notice that when we study the regular embedding obtained by dropping the nodes
-of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the
-subalgebra $\mathfrak{a}$ is one of the connected components,
-the subalgebra $\mathfrak{a}_{\bot}$ may be larger than the algebra
-generated by the remaining connected components of the diagram.
+\end{mynote}
+\begin{mynote}
+  $\mathfrak{a}_{\bot}$ may be larger than the algebra $\bigoplus_j \co{\mathfrak{a}_j}$.
+\end{mynote}
 Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
@@
 roots of $\mathfrak{a}_{\bot}$.
-\begin{table}[ph]
+Case-by-case analysis illustrated by the table \ref{tab:diagrams} leads us to the following lemma.
+
+\begin{table}[h!tb]
 \label{tab:diagrams}
@@
 \end{table}
-If $\mathfrak{a}=B_{r_{\mathfrak{a}}}$  we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\;
-1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
-This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be
-obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.
-
-Using the existing classification of maximal special subalgebras in classical Lie algebras
-\cite{dynkin1952semisimple} we have the following pairs of the orthogonal
-subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
+
+\begin{lemma}
+  \renewcommand{\theenumi}{\alph{enumi}}
+  \begin{enumerate}
+  \item If $\go,\ao\neq B_r$ the Dynkin diagram of $\mathfrak{a}_{\bot}$ is obtained from the extended Dynkin diagram of $\go$ by dropping the subdiagram of $\ao$ and the adjacent nodes
+  \item If $\go=B_r$ and $\ao=B_{r_{\mathfrak{a}}}$ then $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
+  \end{enumerate}
+\end{lemma}
+The complete classification of maximal special subalgebras in classical Lie algebras
+\cite{dynkin1952semisimple} allows us to formulate
+\begin{lemma}
+  For the special embeddings there exist the following set of pairs of orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$:
 \begin{equation*}
@@
 \end{equation*}
-
-Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and
+\end{lemma}
+We are almost ready to state and prove the recurrent relation for the anomalous branching coefficients.
+\begin{definition}
+  \label{fan-definition}
+  For affine $\mathfrak{a}\subset\mathfrak{g}$ expand the product
+  \begin{equation*}
+    \label{eq:6}
+    \prod_{\alpha\in \Delta^{+}\setminus\Delta^{+}_{\bot}}
+    \left(1-e^{-\pi_{\mathfrak{a}}\alpha}\right)^{
+        \mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\pi_{\mathfrak{a}}\alpha)}=
+      -\sum_{\gamma\in P_{\mathfrak{a}}}e^{-\gamma}
+  \end{equation*}
+  Denote by $\Phi_{\mathfrak{a}\subset\mathfrak{g}}\subset P_{\mathfrak{a}}$ the carrier of the coefficient function $s(\gamma)$. 
+  \begin{equation*}
+    \label{eq:37}
+    \Phi_{\mathfrak{a}\subset\mathfrak{g}}=\left\{\gamma\in P_{\mathfrak{a}}|s(\gamma)\neq 0\right\}
+  \end{equation*}
+
+  The ordering of roots in $\co{\Delta_{\mathfrak{a}}}$ induce the natural ordering on the weights of $\mathfrak{a}$.
+Denote by $\gamma_0$ the lowest vector of $    \Phi_{\mathfrak{a}\subset\mathfrak{g}}$ according to this ordering.
+  The set 
+  \begin{equation}
+    \Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+        \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
+    \label{fan-defined}
+  \end{equation}
+  is called the {\it injection fan}.
+\end{definition}
+
+\subsection{Proof of the recurrent relation}
+\label{sec:proof}
+\begin{theorem}
+  For the anomalous branching coefficients (\ref{eq:21}) holds the recurrent relation
+  \begin{equation}
+    \label{eq:1}
+    \begin{array}{c}
+      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
+        {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
+      \left.
+        +\sum_{\gamma \in
+          \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+          +\gamma }^{\left( \mu \right) }\right).
+    \end{array}
+  \end{equation}
+  \begin{proof}
+    Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
+    projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
+    \begin{equation*}
+      % \label{eq:3}
+      L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
+        }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
+      \Longrightarrow\quad
+      \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
+      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
+    \end{equation*}
+    The Weyl-Kac character formula leads to
+    the relation
+    \begin{equation}
+      \label{eq:4}
+      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
+        {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
+      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
+      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
+        e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
+      {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
+    \end{equation}
+
+    Consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and
     its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
@@
     \end{eqnarray*}
-Similarly to the transformation proposed in \cite{ilyin812pbc} we introduce the anomalous branching coefficients $k_{\lambda}$,
-\begin{equation*}
-  \label{eq:10}
-  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
-        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
-  }^{\left( \mu \right) }e^{\lambda }
-\end{equation*}
-and simplify the first factor,
+    Rewriting this relation in terms of the anomalous branching coefficients (\ref{eq:21}) and simplifying the first factor we get
     \begin{eqnarray*}
@@
     \end{equation}
-Let us rewrite the factor in the right-hand side:
-\begin{equation}
-  \label{eq:11}
-    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})} \left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}=
-     -\sum_{\gamma\in P_{\mathfrak{a}}} s(\gamma)e^{-\gamma}
-\end{equation}
-and for the coefficient function $s\left( \gamma \right) $ define the carrier $\Phi _{\frak{a%
-}\subset \frak{g}}\subset P_{\frak{a}}$:
-\begin{equation}
-\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
-\gamma \right) \neq 0\right\} .  \label{phi-d}
-\end{equation}
-From the relation (\ref{eq:9}) the corresponding equation in terms of formal elements,
+    Rewriting the factor in the right-hand side in terms of formal elements as in the definition \ref{fan-definition}
     \begin{eqnarray*}
@@
     \end{eqnarray*}
-leads to the following property of the anomalous branching coefficients,
+    we get the following property of the anomalous branching coefficients,
     \begin{equation}
@@
 
-To get the recurrent relations for the coefficients $k^{(\mu)}_{\xi+\gamma}$ we use the following procedure  (similar to that in \cite{ilyin812pbc}).
-Let $\gamma_{0} $ be the lowest vector with respect to the natural ordering in $%
-\co{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$ and decompose the defining relation (\ref{eq:11}),
-\begin{equation*}
-  \label{eq:18}
-  \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})}\left(
-    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
-      }}\mathrm{\left( \alpha \right) }}=-s\left( \gamma _{0}\right) e^{-\gamma
-    _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \left\{\gamma_{0}\right\}}s\left( \gamma \right) e^{-\gamma },
-\end{equation*}
-the equality (\ref{eq:17}) leads to the desired recurrent  relation for the anomalous branching coefficients:
+    Using the definition \ref{fan-definition} we finally get the recurrent relation
     \begin{eqnarray*}
@@
     \end{eqnarray*}
-where the set
-\begin{equation}
-\Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
-\label{fan-defined}
-\end{equation}
- was introduced that is called the injection fan.
-
+\end{proof}
+\end{theorem}
+\begin{corollary}
+  Since $b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu}\;\mbox{for}\;\nu\in \bar{C_{\mathfrak{a}}}$ the recurrent relation gives the values of the branching coefficients inside the main Weyl chamber.
+\end{corollary}
+\begin{corollary}
   Consider the case  $\Delta_{\bot}^{+} = 0$. There are three different reasons for $\Delta_{\bot}^{+}$
@@
 the latter coincides with the one obtained in \cite{ilyin812pbc} (formula (16)).
-
+\end{corollary}
 \subsection{Algorithm for recursive computation of branching coefficients}
@@
 \end{equation*}
-For the set $\Gamma$ (using the definition (\ref{phi-d},\ref{fan-defined})) we have
+For the set $\Gamma$ (using the definition \ref{fan-definition}) we have
 \begin{equation*}

### 2010-09-29 AffineLieAlgebras/InformalNotes/article.tex
Internal references are fixed
Minor changes

@@
 \usepackage{color}
-%\usepackage[pdftex]{graphicx}
-\usepackage{graphicx}
+\usepackage[pdftex]{graphicx}
+\usepackage{epstopdf}
+%\usepackage{graphicx}
 %\pagestyle{plain}
@@
 
-There exist several approaches to deal with the branching coefficients. Some of them use the BGG
+There exist several different approaches to deal with the branching coefficients. Some of them use the BGG
 resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
-\cite{kac1990idl},\cite{wakimoto2001idl}), the Schure function series \cite{fauser2006new}, the BRST
+\cite{kac1990idl},\cite{wakimoto2001idl}), the Schur function series \cite{fauser2006new}, the BRST
 cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
@@
 }}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
-}_{\go}^{\ast }$\ .
-
+}_{\go}^{\ast }$\ 
+.
 We use the following notations:
@@
     \label{eq:1}
+    \label{recurrent-relation}
     \begin{array}{c}
@@
       \right),
-      \label{recurrent-relation}
     \end{eqnarray*}
@@
 \label{sec:spec-embedd-hata_1s}
+
 Consider the case where both $\mathfrak{g}$ and $\mathfrak{a}$ are affine Lie algebras:

### 2010-09-30 AffineLieAlgebras/DualFunctions/article.tex
Lemma started

@@
 \usepackage{color}
-\usepackage{graphicx}
+\usepackage[pdftex]{graphicx}
+\usepackage{epstopdf}
 \pagestyle{plain}
@@
 \newtheorem{statement}{Statement}
-\theoremstyle{definition} \newtheorem{Def}{Definition}
-\newcommand{\go}{\overset{\circ }{\frak{g}}}
-\newcommand{\ao}{\overset{\circ }{\frak{a}}}
-\newcommand{\co}[1]{\overset{\circ }{#1}}
+\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}
+\theoremstyle{definition}
+\newtheorem{corollary}{Corollary}[theorem]
+\theoremstyle{definition}
+\newtheorem{mynote}{Note}[section]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
+\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
+\newcommand{\co}[1]{\stackrel{\circ }{#1}}
 
@@
 \label{sec:affine-lie-algebras}
+Consider the (affine) Lie algebra $\mathfrak{g}$  and its reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$. Introduce the following objects.
+\begin{definition}
+  Denote by $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\mathfrak{a}} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$.
+\end{definition}
 
+\begin{definition}
+  Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
+\end{definition}
+\begin{mynote}
+  The subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\mathfrak{a}}$.
+\end{mynote}
+\begin{definition}
+  The subsystem $\Delta_{\bot}=\Delta^{+}_{\bot}\cup \left(-\delta^{+}_{\bot}\right)$ determines the subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
+\end{definition}
+
+Let us state the following lemma.
+\begin{lemma}
+The quotient of the singular weights element $\Psi^{(\mu)}$ by the denominator $R_{\mathfrak{a}_{\bot}}$ is given by the formal element corresponding to the modified set of the singular weights of $L_{\mathfrak{a}\oplus\mathfrak{h}_d}^{(\pi_{\mathfrak{a}\oplus\mathfrak{h}_d}\mu)}$ with the multiplicities given by the dimensions of $\mathfrak{a}_{\bot}$-modules.
+\end{lemma}
 \subsection{Modular properties of the dual functions}

### 2010-09-30 GeneralOverview/IntegrableSystems.tex
some changes in integrable systems

--- 2010-05-12 GeneralOverview/IntegrableSystems.tex
@@
 \usepackage{ucs}
-\usepackage[utf8x]{inputenc}
-\usepackage[russian]{babel}
 \usepackage{cmap}
@@
 \theoremstyle{definition} \newtheorem{Def}{Definition}
+\newenvironment{comment}
+{\par\noindent{\bf Comment}\\}
+{\\\hfill$\scriptstyle\blacksquare$\par}
+
+\newtheorem{statement}{Statement}
+\theoremstyle{definition} \newtheorem{Def}{Definition}
+\newcommand{\go}{\overset{\circ }{\frak{g}}}
+\newcommand{\ao}{\overset{\circ }{\frak{a}}}
+\newcommand{\co}[1]{\overset{\circ }{#1}}
+
 \begin{document}
-\section{Интегрируемые системы}
-\label{sec:IntSys}
 
-\subsection{Интегируемые системы}
-\label{sec:-}
+\title{Integrable systems and representation theory}
+\begin{abstract}
+  We review basic notions of quantum integrable systems and then discuss the applications of the representation theory of finite-dimensional and affine Lie algebras.
+\end{abstract}
+\begin{document}
 
-Введение в квантовые интегрируемые системы и метод квантовой обратной задачи рассеяния.
-
-Литература:
-  \begin{itemize}
-  \item Faddeev L.D. How Algebraic Bethe Ansatz works for integrable model. Arxiv preprint hep-th/9605187.
-  \item Korepin, VE and Bogoliubov, NM and Izergin, AG. Quantum inverse scattering method and correlation functions. Cambridge Univ Pr 1997.
-  \end{itemize}
-
-1.Квантовые интегрируемые системы. Анзац Бете. Квантовый метод обратной задачи рассеяния.
-
-2.Матрица монодромии. Интегралы движения.
 \bibliography{program}{}

### 2010-09-30 AffineLieAlgebras/DualFunctions/article.tex
Lemma completed

--- 2010-09-12 AffineLieAlgebras/DualFunctions/article.tex
@@
 \usepackage{graphicx}
+\usepackage{epstopdf}
 \pagestyle{plain}
@@
 \newtheorem{statement}{Statement}
-\theoremstyle{definition} \newtheorem{Def}{Definition}
-\newcommand{\go}{\overset{\circ }{\frak{g}}}
-\newcommand{\ao}{\overset{\circ }{\frak{a}}}
-\newcommand{\co}[1]{\overset{\circ }{#1}}
-
+\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}
+\theoremstyle{definition}
+\newtheorem{corollary}{Corollary}[theorem]
+\theoremstyle{definition}
+\newtheorem{mynote}{Note}[section]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
+\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
+\newcommand{\co}[1]{\stackrel{\circ }{#1}}
+\newcommand{\pia}{\pi_{\mathfrak{a}}}
+\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
+\newcommand{\af}{\mathfrak{a}}
+\newcommand{\afb}{\mathfrak{a}_{\bot}}
 \begin{document}
@@
 \frak{g}}$ (resp. $\co{\frak{a}}$);
-$\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);
+$\Theta$, $(\Theta_{\af})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\af$);
 
@@
 
-$\bar{C}, \left(\bar{C_{\mathfrak{a}}}\right)$ --- the closure of the fundamental Weyl chamber;
+$\bar{C}, \left(\bar{C_{\af}}\right)$ --- the closure of the fundamental Weyl chamber;
 
@@
   \label{eq:21}
-  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
+  \sum_{\nu \in \bar{C_{\af}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
         a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
@@
 %  \label{eq:20}
-  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}};
+  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\af};
 \end{equation*}
 
-$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$ --- the embedding index.
+$x_e=\frac{\left|\pia \Theta\right|^2}{\left|\Theta_{\af}\right|^2}$ --- the embedding index.
 
@@
 \label{sec:affine-lie-algebras}
+Consider the (affine) Lie algebra $\mathfrak{g}$  and its reductive subalgebra $\af\subset \mathfrak{g}$. Introduce the following objects.
+\begin{definition}
+  Denote by $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\af} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\af$.
+\end{definition}
 
+\begin{definition}
+  Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
+\end{definition}
+\begin{mynote}
+  The subgroup $W_{\bot}$ preserves $\Delta_{\af}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\af}$.
+\end{mynote}
+\begin{definition}
+  The subsystem $\Delta_{\bot}=\Delta^{+}_{\bot}\cup \left(-\delta^{+}_{\bot}\right)$ determines the subalgebra $\af_{\bot}\subset \mathfrak{g}$.
+\end{definition}
+
+Let us state the following lemma.
+\begin{lemma}
+Denote by $\mathcal{D}=\rho_{\af_{\bot}}-\pi_{\mathfrak{a}_{\bot}}\rho$ the difference between the Weyl vector of orthogonal subalgebra $\af_{\bot}$ and the projection of the Weyl vector of the algebra $\mathfrak{g}$.
+Then
+the quotient of the singular weights element $\Psi^{(\mu)}$ by the denominator $R_{\af_{\bot}}$ is given by the formal element corresponding to the modified set of the singular weights of $L_{\af\oplus\mathfrak{h}_d}^{(\pi_{\af\oplus\mathfrak{h}_d}\mu)}$ with the multiplicities given by the dimensions of $\af_{\bot}$-modules.
+\begin{equation}
+  \label{eq:4}
+  \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\prod_{\alpha\in \Delta^{+}_{\bot}}\left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=
+    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{\af\oplus\mathfrak{h}_d}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \mathrm{ch}_{\af_{\bot}}
+      L^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}
+\end{equation}
+\begin{proof}
+  Consider $\Psi^{(\mu)}_{\mathfrak{g}}$. It is given by the sum over the Weyl group.
+  \begin{equation}
+    \label{eq:6}
+    \Psi^{(\mu)}_{\mathfrak{g}}=\sum_{w\in W}\epsilon(w)e^{w(\mu+\rho)-\rho}
+  \end{equation}
+  We can divide the summation to the sum over $W_{\bot}$ and sum over all the classes of $W/W_{\bot}$: $w=vu,\; v\in W_{\bot},\; u \in W/W_{\bot}$.
+We have the following obvious property of the projections:
+  \begin{equation}
+    \label{eq:5}
+    u(\mu+\rho)=\pia(u(\mu+\rho))+\piab(u(\mu+\rho))+\pi_{(\mathfrak{h}\setminus
+      (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}))^*}(u(\mu+\rho))
+  \end{equation}
+  Let's denote $\mathfrak{h}\setminus (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}})$ by $\mathfrak{h}_d$,
+  $\mathfrak{h}=\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}+\mathfrak{h}_d$. Since $\mathfrak{h}_{\af}^*,\mathfrak{h}_d^*$ are invariant under the action of $v\in W_{\bot}$, we have
+  \begin{equation}
+    \label{eq:8}
+    vu(\mu+\rho)-\rho=v\cdot(\piab(u(\mu+\rho))-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}+\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\mathfrak{h}_d^*}(u(\mu+\rho))
+  \end{equation}
+  Only the first term depends on $v$. So
+  \begin{equation}
+    \label{eq:9}
+    \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\mathrm{R}_{\afb}}=
+    \frac{\sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\mathfrak{h}_d^*}(u(\mu+\rho))}\cdot
+      \sum_{v\in W_{\bot}}\epsilon(v)e^{v(\piab u(\mu+\rho)-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}}}{\mathrm{R}_{\afb}}
+  \end{equation}
+  We can rewrite the r.h.s. as
+  \begin{equation}
+    \label{eq:10}
+    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{(\af\oplus\mathfrak{h}_d)}\left[u(\mu+\rho)-\rho\right]+\pi_{(\af\oplus \mathfrak{h}_d)}\cdot \rho-\rho+\rho_{\afb}}\cdot
+    \mathrm{ch}_{\afb}L^{\pi_{\afb}u(\mu+\rho)-\rho_{\afb}}.
+  \end{equation}
+  Since $\pi_{\afb}(u(\mu+\rho)-\rho)-(\rho_{\afb}-\pi_{\afb}\rho)=\pi_{\afb}(u(\mu+\rho)-\rho)-\mathcal{D}$ and $\pi_{(\af\oplus\mathfrak{h}_d)}\rho-\rho=-\pi_{\afb}\rho$ we get the statement of the Lemma.
+
+\end{proof}
+\end{lemma}
 \subsection{Modular properties of the dual functions}

### 2010-10-01 AffineLieAlgebras/InformalNotes/article.tex
Lemma added

@@
 \usepackage{color}
-\usepackage[pdftex]{graphicx}
+\usepackage{graphicx}
 \usepackage{epstopdf}
@@
 \newcommand{\co}[1]{\stackrel{\circ }{#1}}
+\newcommand{\pia}{\pi_{\mathfrak{a}}}
+\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
+\newcommand{\af}{\mathfrak{a}}
+\newcommand{\afb}{\mathfrak{a}_{\bot}}
 
@@
 \label{sec:proof}
+First we prove the lemma
+\begin{lemma}
+Denote by $\mathcal{D}=\rho_{\af_{\bot}}-\pi_{\mathfrak{a}_{\bot}}\rho$ the difference between the Weyl vector of orthogonal subalgebra $\af_{\bot}$ and the projection of the Weyl vector of the algebra $\mathfrak{g}$.
+Then
+the quotient of the singular weights element $\Psi^{(\mu)}$ by the denominator $R_{\af_{\bot}}$ is given by the formal element corresponding to the modified set of the singular weights of $L_{\af\oplus\mathfrak{h}_d}^{(\pi_{\af\oplus\mathfrak{h}_d}\mu)}$ with the multiplicities given by the dimensions of $\af_{\bot}$-modules.
+\begin{equation*}
+  \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\prod_{\alpha\in \Delta^{+}_{\bot}}\left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=
+    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{\af\oplus\mathfrak{h}_d}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \mathrm{ch}_{\af_{\bot}}
+      L^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}
+\end{equation*}
+\begin{proof}
+  Consider $\Psi^{(\mu)}_{\mathfrak{g}}$. It is given by the sum over the Weyl group.
+  \begin{equation*}
+    \Psi^{(\mu)}_{\mathfrak{g}}=\sum_{w\in W}\epsilon(w)e^{w(\mu+\rho)-\rho}
+  \end{equation*}
+  We can divide the summation to the sum over $W_{\bot}$ and sum over all the classes of $W/W_{\bot}$: $w=vu,\; v\in W_{\bot},\; u \in W/W_{\bot}$.
+We have the following obvious property of the projections:
+  \begin{equation*}
+    \label{eq:5}
+    u(\mu+\rho)=\pia(u(\mu+\rho))+\piab(u(\mu+\rho))+\pi_{(\mathfrak{h}\setminus
+      (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}))^*}(u(\mu+\rho))
+  \end{equation*}
+  Let's denote $\mathfrak{h}\setminus (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}})$ by $\mathfrak{h}_d$,
+  $\mathfrak{h}=\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}+\mathfrak{h}_d$. Since $\mathfrak{h}_{\af}^*,\mathfrak{h}_d^*$ are invariant under the action of $v\in W_{\bot}$, we have
+  \begin{equation*}
+    \begin{array}{cc}
+      vu(\mu+\rho)-\rho & = v\cdot(\piab(u(\mu+\rho))-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}+\\
+      & \pia(u(\mu+\rho))-\rho+\rho_{\afb}+
+      \pi_{\mathfrak{h}_d^*}(u(\mu+\rho))
+    \end{array}
+  \end{equation*}
+ Only the first term depends on $v$. So
+  \begin{equation*}
+    \begin{array}{cc}
+    \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\mathrm{R}_{\afb}}= &
+    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\mathfrak{h}_d^*}(u(\mu+\rho))}\cdot\\
+
+    &\cdot\frac{
+      \sum_{v\in W_{\bot}}\epsilon(v)e^{v(\piab u(\mu+\rho)-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}}}{\mathrm{R}_{\afb}}
+  \end{array}
+\end{equation*}
+  We can rewrite the r.h.s. as
+  \begin{equation*}
+    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{(\af\oplus\mathfrak{h}_d)}\left[u(\mu+\rho)-\rho\right]+\pi_{(\af\oplus \mathfrak{h}_d)}\cdot \rho-\rho+\rho_{\afb}}\cdot
+    \mathrm{ch}_{\afb}L^{\pi_{\afb}u(\mu+\rho)-\rho_{\afb}}.
+  \end{equation*}
+  Since $\pi_{\afb}(u(\mu+\rho)-\rho)-(\rho_{\afb}-\pi_{\afb}\rho)=\pi_{\afb}(u(\mu+\rho)-\rho)-\mathcal{D}$ and $\pi_{(\af\oplus\mathfrak{h}_d)}\rho-\rho=-\pi_{\afb}\rho$ we get the statement of the Lemma.
+
+\end{proof}
+\end{lemma}
+
 \begin{theorem}

### 2010-10-01 GeneralOverview/Lectures/2dqft.tex
Lecture notes on 2d QFT are added

\documentclass[a4paper,12pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
\usepackage{ucs}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{pb-diagram}
\usepackage{multicol}
\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
\usepackage{epstopdf}
\pagestyle{plain}

%\usepackage{verbatim} 
\newenvironment{comment}
{\par\noindent{\bf TODO}\\}
{\\\hfill$\scriptstyle\blacksquare$\par}

\newtheorem{statement}{Statement}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{corollary}{Corollary}[theorem]
\theoremstyle{definition}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}

\title{Лекции по теории поля в двух измерениях\\
\small{Академический университет, кафедра теоретической физики}
}
\author{Антон Назаров\\
  \small{СПбГУ, физический факультет}\\
  \small{кафедра физики высоких энергий и элементарных частиц}\\
  \texttt{antonnaz@gmail.com}
}
\date{Осенний семестр 2010 года}

\begin{document}
\maketitle
\begin{abstract}
  Текст представляет собой конспект лекций по квантовой теории поля в двух измерениях. Лекции читаются в осеннем семестре 2010 года в Академическом университете для магистрантов 6 курса, группа теории твердого тела. 
\end{abstract}

\section{Программа курса}
\label{sec:program}
\begin{enumerate}
\item Введение.
  \begin{itemize}
  \item Двумерные модели
  \item Фазовые переходы, критические индексы
  \item Универсальность
  \item Методы квантовой теории поля в статистической физике
  \end{itemize}
\item Перенормировки, ренормгруппа
\item Решение модели Изинга
  \begin{itemize}
  \item Интегрируемость
  \item Подход Каданова
  \end{itemize}
\item Конформная инвариантность
  \begin{itemize}
  \item Глобальная конформная инвариантность
  \item Ограничения на корреляционные функции
  \item Локальная конформная инвариантность в двух измерениях
  \item Алгебра Витта и алгебра Вирасоро.
  \end{itemize}
\item Конформная теория поля
  \begin{itemize}
  \item Примарные и вторичные поля
  \item Минимальные модели
  \end{itemize}
\end{enumerate}

\section{Лекция 1}
\label{sec:lecture-1}

\subsection{Введение}
\label{sec:intro}
Чем интересны двумерные системы? Во-первых, они существуют в природе. Например, критическое поведение на поверхности металлов напоминает поведение модели Изинга в двух измерениях \cite{campuzano1985110}. Во-вторых, в двух измерениях даже в простых моделях есть фазовые переходы. Это не так, например,  в одномерной модели Изинга. В простых двумерных моделях можно вычислить критические индексы и изучать поведение системы при фазовых переходах. Гипотеза универсальности утверждает, что все системы в критической точке разбиваются на небольшое число классов. Системы из одного класса ведут себя одинаково, имеют одинаковые критические индексы. Благодаря гипотезе универсальности существует лишь небольшое число типов критического поведения, поэтому значения индексов, вычисленные теоретически в простых моделях соответствуют гораздо более сложным реальным системам.
В критической точке наблюдается масштабная инвариантность, что ведет к конформной инвариантности \cite{Polyakov:1970xd}. В двух измерениях конформная инвариантность дает очень много сведений о системе, так как алгебра конформных преобразований бесконечномерна. В результате поведение системы может быть описано строго математически методами двумерной конформной теории поля. Двумерная конформная теория поля имеет и другое применение, не связанное с описанием фазовых переходов --- это теория струн, которая считается перспективным кандидатом на роль квантовой теории гравитации.

\subsection{Фазовые переходы. Основные понятия}
\label{sec:phase-transitions}
Напомним некоторые основные понятия теории фазовых переходов на примере двумерной модели Изинга.
Двумерная модель Изинга --- это простейшая модель магнетика. Она формулируется на решетке, которую мы будем, для простоты, считать прямоугольной. Вершины решетки нумеруются латинскими индексами $i,j$. В вершинах решетки находятся частицы со спинами $s_j$ равными $\pm 1$ (вверх или вниз). Взаимодействуют только ближайшие соседи, константу взаимодействия обозначим через $J$. Для энергии системы имеем
\begin{equation}
  \label{eq:1}
  E=J\sum_{\left<i,j\right>} s_i\cdot s_j-h\sum_i s_i
\end{equation}
Суммирование в первом члене ведется только по парам ближайших соседей, второй член --- это взаимодействие со внешним полем $h$.

Существует несколько точных решений двумерной модели Изинга в отсутствие внешнего поля. Решений со внешним полем и в большем числе измерений пока не известно. Недавнее достижение Станислава Смирнова, за которое он получил в этом году премию Филдса, непосредственно связано с темой наших лекций. В своих работах Станислав Смирнов впервые строго доказал наличие конформного предела в двумерной модели Изинга \cite{smirnov2007conformal,smirnov2001critical}.

Мы рассматриваем статистические системы. Все макроскопические характеристики таких систем вычисляются из статсуммы, которая связана с микроскопическим описанием системы. Для больцмановского распределения вероятность системы находиться в состоянии с номером $i$ с энергией $E_i$
\begin{equation}
  \label{eq:2}
  P_i=\frac{1}{Z}e^{-\beta E_i}, \quad \beta=\frac{1}{T}
\end{equation}
\begin{equation}
  \label{eq:3}
  Z=\sum_i e^{-\beta E_i}
\end{equation}
Свободная энергия
\begin{equation}
  \label{eq:4}
  F=-T\ln Z
\end{equation}
Внутренняя энергия
\begin{equation}
  \label{eq:5}
  U=-\frac{1}{Z}\frac{\partial Z}{\partial \beta}=-T^2 \frac{\partial}{\partial T}\left(\frac{F}{T}\right)
\end{equation}
Телоемкость равна производной внутренней энергии по температуре при заданном объеме
\begin{equation}
  \label{eq:6}
  C=\left(\frac{\partial U}{\partial T}\right)_V=-T\frac{\partial^2 F}{\partial T^2}
\end{equation}
Таким образом статсумма является производящей функцией всех термодинамических величин. Вычисление статсуммы в реальных системах --- это сложная задача.
Макроскопическое описание имеет смысл только в термодинамическом пределе, когда число частиц стремится к бесконечности $N\to \infty$. Фазовые переходы в модели Изинга наблюдаются только в этом пределе, при конечных размерах системы никаких переходов нет.
\bibliography{2dqft}{}
\bibliographystyle{utphys}

\end{document}

### 2010-10-02 GeneralOverview/Lectures/2dqft.tex
More work on lecture notes

@@
 \usepackage[russian]{babel}
-\usepackage{ucs}
+%\usepackage{ucs}
 \usepackage[unicode,verbose]{hyperref}
@@
 \usepackage{multicol}
-\usepackage{cmap}
+%\usepackage{cmap}
 \usepackage{color}
-\usepackage{graphicx}
-\usepackage{epstopdf}
+%\usepackage{graphicx}
+%\usepackage{epstopdf}
 \pagestyle{plain}
@@
 \label{sec:phase-transitions}
+
 Напомним некоторые основные понятия теории фазовых переходов на примере двумерной модели Изинга.
-Двумерная модель Изинга --- это простейшая модель магнетика.
-Она формулируется на решетке, которую мы будем, для простоты, считать прямоугольной.
-Вершины решетки нумеруются латинскими индексами $i,j$.
-В вершинах решетки находятся частицы со спинами $s_j$ равными $\pm 1$ (вверх или вниз).
-Взаимодействуют только ближайшие соседи, константу взаимодействия обозначим через $J$.
-Для энергии системы имеем
-\begin{equation}
-  \label{eq:1}
-  E=J\sum_{\left<i,j\right>} s_i\cdot s_j-h\sum_i s_i
-\end{equation}
-Суммирование в первом члене ведется только по парам ближайших соседей, второй член --- это взаимодействие со внешним полем $h$.
-
-Существует несколько точных решений двумерной модели Изинга в отсутствие внешнего поля.
-Решений со внешним полем и в большем числе измерений пока не известно.
-Недавнее достижение Станислава Смирнова, за которое он получил в этом году премию Филдса, непосредственно связано с темой наших лекций.
-В своих работах Станислав Смирнов впервые строго доказал наличие конформного предела в двумерной модели Изинга \cite{smirnov2007conformal,smirnov2001critical}.
 
@@
 \end{equation}
+Мы используем систему единиц, в которой постоянная Больцмана равна единице $k_B=1$, введем $\beta=\frac{1}{T}$. Статсумма:
 \begin{equation}
   \label{eq:3}
-  Z=\sum_i e^{-\beta E_i}
+  Z=\sum_i e^{-\beta E_i}.
 \end{equation}
@@
 Макроскопическое описание имеет смысл только в термодинамическом пределе, когда число частиц стремится к бесконечности $N\to \infty$.
+
+Двумерная модель Изинга --- это простейшая модель магнетика.
+Она формулируется на решетке, которую мы будем, для простоты, считать прямоугольной.
+Вершины решетки нумеруются латинскими индексами $i,j$.
+В вершинах решетки находятся частицы со спинами $\sigma_j$ равными $\pm 1$ (вверх или вниз).
+Взаимодействуют только ближайшие соседи, константу взаимодействия обозначим через $J$.
+Для энергии системы имеем
+\begin{equation}
+  \label{eq:1}
+  E=J\sum_{\left<i,j\right>} \sigma_i\cdot \sigma_j-h\sum_i \sigma_i
+\end{equation}
+Суммирование в первом члене ведется только по парам ближайших соседей, второй член --- это взаимодействие со внешним полем $h$.
+Пусть система состоит из $N$ вершин. Она имеет $2^N$ различных конфигураций. Случай $J>0$ соответствует ферромагнетику, $J<0$ --- антиферромагнетику. 
+При $h=0$ низшее энергетическое состояние двукратно вырождено --- это состояние, в котором все спины направлены вверх или вниз.
+
+Существует несколько точных решений двумерной модели Изинга в отсутствие внешнего поля.
+Решений со внешним полем и в большем числе измерений пока не известно.
+Недавнее достижение Станислава Смирнова, за которое он получил в этом году премию Филдса, непосредственно связано с темой наших лекций.
+В своих работах Станислав Смирнов впервые строго доказал наличие конформного предела в двумерной модели Изинга \cite{smirnov2007conformal,smirnov2001critical}.
 Фазовые переходы в модели Изинга наблюдаются только в этом пределе, при конечных размерах системы никаких переходов нет.
+
+При исследовании магнетиков нас интересуют следующие термодинамически величины.
+Намагниченность, которая равна среднему значению спина по всем конфигурациям $[\sigma]$:
+\begin{equation}
+  \label{eq:7}
+  M=\left<\sigma_j\right>=\frac{1}{NZ}\sum_{[\sigma]}\left(\sum_i\sigma_i\right)e^{-\beta E[\sigma]}=-\frac{1}{N}\frac{\partial F}{\partial h}.
+\end{equation}
+Магнитная восприимчивость
+\begin{equation}
+  \label{eq:8}
+  \chi=\left.\frac{\partial M}{\partial h}\right|_{h=0}=\frac{1}{N}\frac{\partial}{\partial h}\left(\frac{1}{Z}\sum_{[\sigma]}\left(\sum_i \sigma_i\right)e^{-\beta E[\sigma]}\right)=\frac{1}{NT}\left(\left<\sigma_{\mathrm{tot}}^2\right>-\left<\sigma_{\mathrm{tot}}\right>^2\right)
+\end{equation}
+Здесь мы ввели обозначение $\sigma_{\mathrm{tot}}=\sum_i \sigma_i$. Видно, что магнитная восприимчивость пропорциональна дисперсии полного спина. Введем парную корреляционную функцию
+\begin{equation}
+  \label{eq:9}
+  \Gamma(i-j)=\left<\sigma_i-\sigma_j\right>.
+\end{equation}
+Из-за вращательной и трансляционной инвариантности $\Gamma$ зависит только от расстояния между вершинами $\left|i-j\right|$. Связная корреляционная функция
+\begin{equation}
+  \label{eq:10}
+  \Gamma_c(i-j)=\left<\sigma_i-\sigma_j\right>_c=\left<\sigma_i\sigma_j\right>-\left<\sigma_i\right>\left<\sigma_j\right>.
+\end{equation}
+Можно показать, что
+\begin{equation}
+  \label{eq:11}
+  \chi=\beta\sum_i\Gamma(i)_c.
+\end{equation}
+То есть магнитная восприимчивость --- это мера статистической когерентности системы, она растет с ростом зависимости спинов между собой.
+
+Распределение Больцмана инвариантно относительно сдвига энергии на константу, поэтому можно переписать гамильтониан в более удобном для обобщения виде:
+\begin{equation}
+  \label{eq:12}
+  \begin{array}{l}
+    \sigma_i\sigma_j=2\delta_{\sigma_i\sigma_j}-1\\
+    E[\sigma]=-2J\sum_{\left<ij\right>}\delta_{\sigma_i\sigma_j}-h\sum_i \sigma_i
+  \end{array}
+\end{equation}
+Обсудим некоторые обобщения модели Изинга и проиллюстрируем сходство статистической механики с теорией поля.
+Если $\sigma_i$ может принимать значения не $-1,1$, а $1,2\dots,q$, то мы получаем модель Поттса с $q$ состояниями.
+Подобным образом получаются и модели Ашкина-Теллера.
+Другой класс дискретных моделей отличается более существенно.
+Если в модели Изинга переменные (спины) живут в вершинах, а энергия --- на ребрах, то в вершинных моделях все наоборот.
+В качестве переменных берутся направленные ребра (стрелки), а энергия в вершине зависит от числа входящих и выходящих из нее стрелок.
+Пусть ребра, входящие в вершину имеют значения $0,1$ в зависимости от направления стрелки.
+Тогда энергия вершины обозначается через $R_{\alpha\mu}^{\beta\nu},\; \alpha,\beta,\mu,\nu=0,1$.
+Бывает 16 таких членов.
+В зависимости от того, сколько из них не равны нулю выделяют 6-вершинную и 8-вершинную модели.
+8-вершинная модель --- ненулевой вклад только когда входит четное число стрелок.
+
+Другой класс статистических моделей --- это модели с непрерывными степенями свободы.
 \bibliography{2dqft}{}

### 2010-10-03 GeneralOverview/Lectures/2dqft.tex
Lecture 1 is completed.

@@
 \usepackage[russian]{babel}
-%\usepackage{ucs}
+\usepackage{ucs}
 \usepackage[unicode,verbose]{hyperref}
@@
 \usepackage{multicol}
-%\usepackage{cmap}
+\usepackage{cmap}
 \usepackage{color}
@@
 
+\subsection{Классические статистические модели. Связь с теорией поля.}
+\label{sec:statistical-models-qft}
+
 Распределение Больцмана инвариантно относительно сдвига энергии на константу, поэтому можно переписать гамильтониан в более удобном для обобщения виде:
@@
 
-Другой класс статистических моделей --- это модели с непрерывными степенями свободы.
+Другой класс статистических моделей --- это модели с непрерывными степенями свободы. Например, заменим спины $\sigma_i$ в \eqref{eq:1} на единичные вектора в $m$-мерном пространстве $\vec n_i$.
+\begin{equation}
+  \label{eq:14}
+  \left|\vec n\right|^2=1
+\end{equation}
+В результате получим гамильтониан
+\begin{equation}
+  \label{eq:13}
+  E[\vec n]=J\sum_{\left<ij\right>}\vec n_i\cdot \vec n_j-\sum_i \vec h\cdot \vec n_i
+\end{equation}
+Это гамильтониан классической $O(m)$-модели Гейзенберга.
+
+В критической точке параметр порядка системы стремится к бесконечности, кроме того, фазовый переход в дискретных моделях наблюдается только в термодинамическом пределе числа вершин стремящегося к бесконечности ($N\to \infty$).
+Поэтому при описании фазового перехода имеет смысл перейти модели с дискретным пространством  к непрерывному пространству $d$-мерному пространству.
+В дальнейшем $d$ будет равно двум, но сейчас мы пишем в самом общем виде, чтобы указать аналогию с теорией поля.
+При переходе к непрерывному пространству гамильтониан \eqref{eq:13} принимает вид
+\begin{equation}
+  \label{eq:15}
+  E[\vec n]=\int d^d x \left(J\partial_kn_i\partial_k  n_i-h_i\cdot n_i\right)
+\end{equation}
+Здесь подразумевается суммирование по повторяющимся индексам.
+(Легко понять обратный переход, если заменить производные разностями по ближайшим соседям, а потом отбросить в энергии постоянный член $J\sum_i \left|\vec n_i\right|^2=JN$).
+Условие $\vec n^2(x)=1$ сложно использовать, поэтому мы заменим его на другое аналогичное.
+Первый вариант такой замены --- это $\frac{1}{V}\int d^dx\; \vec n^2=1$.
+В результате получается так называемая сферическая модель.
+Другая возможность --- добавить в гамильтониан \eqref{eq:15} потенциал $V(\left|\vec n\right|)$ с минимумом в $\left|\vec n\right|=1$ и устремить константу связи к бесконечности.
+Простейший вид такого потенциала --- $V(\left|\vec n\right|)=a\vec n^2+b\left(\vec n^2\right)^2$.
+Добавим его в гамильтониан и изменим нормировку $\vec n$ так, чтобы константа $J$ ушла.
+Получим
+\begin{equation}
+  \label{eq:16}
+  E[\vec n]=\int d^d x \left(\frac{1}{2}\partial_k n_i\cdot \partial_k n_i-\frac{1}{2}\mu^2 \vec n^2+\frac{1}{4}u\left(\vec n^2\right)^2\right)
+\end{equation}
+Если у $\vec n$ всего одна компонента $\varphi$, то мы получаем скалярную модели $\varphi^4$. Если $u=0$, то такая модель называется Гауссовой и допускает точное решение.
+\begin{equation}
+  \label{eq:17}
+  E[\varphi]=\int d^d x (\frac{1}{2}(\nabla \varphi)^2+\frac{1}{2}\mu^2 \varphi^2)
+\end{equation}
+Статсумма --- это сумма $e^{-\beta E[\varphi]}$ по всем конфигурациям поля $\varphi$, то есть она записывается при помощи функционального интеграла:
+\begin{equation}
+  \label{eq:18}
+  Z=\int \mathcal{D}\varphi e^{-\beta E[\varphi]}
+\end{equation}
+В гауссовой модели функциональный интеграл имеет гауссовский вид, поэтому он хорошо определен и легко вычисляется.
+Значит можно вычислить статсумму и все корреляционные функции.
+Величины в модели $\varphi^4$ можно получать по теории возмущений вокруг решения гауссовой модели.
+Это и есть вычисление функционального интеграла как суммы по фейнмановским диаграммам.
+
+\section{Лекция 2. }
+\label{sec:lecture-2}
+
+\subsection{Квантовые статистические модели}
+\label{sec:quantum-statistical-models}
+
 \bibliography{2dqft}{}

### 2010-10-03 GeneralOverview/Lectures/2dqft.tex
Half of Lecture 2 is ready.

@@
 
+Микросостояния квантовых статистических систем описываются при помощи матрицы плотности
+\begin{equation}
+  \label{eq:19}
+  \rho=e^{-\beta H}
+\end{equation}
+Статсумма дается суммой по собственным состояниям гамильтониана или следом матрицы плотности:
+\begin{equation}
+  \label{eq:20}
+  Z=\sum_n e^{-\beta E_n}=\mathrm{Tr} \rho
+\end{equation}
+Значение физической величины определим как среднее по состояниям:
+\begin{equation}
+  \label{eq:21}
+  \left< A\right>=\sum_n \left< n\right| e^{-\beta H}A\left| n \right>=\mathrm{Tr}(\rho A)
+\end{equation}
+$e^{-\beta H}$ похоже на оператор эволюции $e^{-i H t}$, то есть его тоже можно записать через функциональный интеграл.
+Покажем, как это делается на примере системы с одной степенью свободы.
+В этом случае ядро оператора плотности имеет вид
+\begin{equation}
+  \label{eq:22}
+  \rho(x_f,x_i)=\left<x_f\right|e^{-\beta H} \left|x_i\right>
+\end{equation}
+Вспомним, что в квантовой механике оператор эволюции имеет вид $U(t)=e^{-i H t}$, а его ядро --- амплитуда перехода из состояния $\left|x_i\right>$ в $\left<x_f\right|$ дается интегралом по траекториям
+\begin{equation}
+  \label{eq:23}
+  \left<x_f\right| U(t)\left| x_i\right>=\int_{(x_i,0)}^{(x_f,t)} [dx] e^{i S[x]}
+\end{equation}
+Заменой $t\to i\tau, \; \tau\in [0,\beta]$ (виковским поворотом) переходим к евклидову действию $S[x(t)]\to iS_E[x(\tau)]$. Для ядра оператора плотности получаем
+\begin{equation}
+  \label{eq:24}
+  \rho(x_f,x_i)=\int_{(x_i,0)}^{(x_f,\beta)} [dx] e^{-S_E[x]}
+\end{equation}
+Статсумма
+\begin{equation}
+  \label{eq:25}
+  Z=\int dx \rho(x,x)=\int [dx] e^{-S_E[x]}
+\end{equation}
+Среднее значение $A$
+\begin{equation}
+  \label{eq:26}
+  \begin{array}{l}
+    \left<A\right>=\frac{1}{Z}\int dx \left<x\right|\rho A\left|x\right>=\frac{1}{Z}\int dx\; dy \left<x\right|\rho\left|y\right>\left<y\right|A\left|x\right>=    \\
+    =\frac{1}{Z}\int dx\; dy \int_{(x,0)}^{(y,\beta)} [dx] \left<y\right| A\left| x\right> e^{-S_E[x]}=\frac{1}{Z}\int dx\; dy\int_{(x,0)}^{(y,\beta)} [dx] A(x) \delta(x-y) e^{-S_E[x]}=\\
+    =\frac{1}{Z}\int [dx] A(x(0))e^{-S_E[x]}
+  \end{array}
+\end{equation}
+Здесь мы предположили, что $A$ зависит только от $x$, то есть $\left<y\right| A\left|x\right>=A(x)\delta(x-y)$.
+Мы видим, что значение $A$ дается функциональным интегралом, но $A$ вычисляется в точке $\tau=0$.
+
+Обобщение на систему с континуумом степеней свободы и многочастичные функции естественно.
+Статсумма квантовой системы получается из обычного интеграла по траекториям путем викова поворота и ограничения евклидова времени на конечный промежуток $[0,\beta]$.
+При нулевой температуре ($\beta\to \infty$) мы получаем обычный производящий функционал в евклидовом времени, то есть теорию поля.
+При конечных температурах статсумма квантовой $d$-мерной системы напоминает статсумму $d+1$-мерной классической системы на полосе шириной $\beta$.
+
+\subsection{Критические явления}
+\label{sec:critical-phenomena}
+
+Фазовые переходы характеризуются скачком в макроскопических характеристиках системы.
+При переходах первого рода скачком меняется внутренняя энергия (например, при переходе жидкость-газ).
+При переходах второго рода наблюдается скачок производных макроскопических термодинамических величин (теплоемкость, магнитная восприимчивость).
+
+Строго говоря, фазовые переходы бывают только в термодинамическом пределе.
+Это легко понять для систем типа модели Изинга в нулевом поле, где энергия любой конфигурации кратна энергетическому масштабу $\epsilon=-J$, а статсумма представляет собой полином от $z=e^{-\beta\epsilon}$.
+В модели Изинга наибольшая энергия $E=2N\epsilon$, $Z$- полином степени $2N$ от $z$ с единичными коэффициентами.
+Корни этого полинома лежат вне положительной вещественной оси и комплексно сопряжены.
+Сингулярности свободной энергии или ее производных могут быть только в корнях, которые находятся вне физической области при $N<\infty$.
+При $N\to \infty$ число корней становится бесконечным, они лежат на дугах, которые могут касаться положительной вещественной оси.
+В этих точках поведение термодинамических величин и становится сингулярным.
+
+Нас будут интересовать переходы второго рода. Именно в них имеет место конформная инвариантность. 
+Перечислим основные результаты для модели Изинга в двух измерениях.
+
+Здесь есть один фазовый переход при конечной температуре. 
+Критическая температура
+\begin{equation}
+  \label{eq:27}
+  T_C:\quad \sh \frac{2J}{T_C}=1
+\end{equation}
+При $T>T_C$ спонтанная намагниченность исчезает.
+При $T<T_C$ она не равна нулю и стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_C$.
+Это ферромагнитная фаза.
+Около критической точки спонтанная намагниченность ведет себя как
+\begin{equation}
+  \label{eq:28}
+  M\sim \left|T_C-T\right|^{\frac{1}{8}}
+\end{equation}
+
 \bibliography{2dqft}{}

### 2010-10-04 GeneralOverview/Lectures/2dqft.tex
More work on Lectures on 2D QFT. Table of contents and bibliography added.

@@
 \maketitle
+\thispagestyle{empty}
 \begin{abstract}
@@
 \end{abstract}
-
+\tableofcontents
 \section{Программа курса}
@@
 \end{enumerate}
+
+\subsection{Литература}
+\label{sec:literature}
+В первых лекциях \ref{sec:lecture-1},\ref{sec:lecture-2} мы опираемся на вводные главы книги \cite{difrancesco1997cft}.
+Подробно решение  модели Изинга в двух измерениях рассмотрено в книге  \cite{belavin2001lect}.
+Последовательное изложение техники функционального интеграла в статистической физике можно найти в книге А.Н.
+Васильева \cite{vasiliev1976}.
+
+В лекции 3 \ref{sec:lecture-3} мы обсуждаем применение ренормгруппы к описанию критического поведения, более подробно и достаточно педагогически этот вопрос рассматривается в книге \cite{ma1980} (\cite{ma2000modern}).
+Исчерпывающую информацию содержит моногорафия \cite{vasiliev1998} (английский вариант \cite{Vasilev:1027193}).
+
+Изложение конформной теории поля в двух измерениях опирается на оригинальную статью \cite{belavin1984ics}, книгу \cite{difrancesco1997cft} и обзор \cite{zamolodchikov1989rus,zamolodchikov1989conformal}, недавно переизданный в виде книги.
 
@@
 Недавнее достижение Станислава Смирнова, за которое он получил в этом году премию Филдса, непосредственно связано с темой наших лекций.
-В своих работах Станислав Смирнов впервые строго доказал наличие конформного предела в двумерной модели Изинга \cite{smirnov2007conformal,smirnov2001critical}.
+В своих работах Станислав Смирнов впервые строго доказал наличие конформного предела в двумерной модели Изинга \cite{smirnov2007conformal,smirnov2006towards,smirnov2001critical}.
 Фазовые переходы в модели Изинга наблюдаются только в этом пределе, при конечных размерах системы никаких переходов нет.
@@
   \label{eq:27}
-  T_C:\quad \sh \frac{2J}{T_C}=1
+  T_c:\quad \sh \frac{2J}{T_c}=1
 \end{equation}
-При $T>T_C$ спонтанная намагниченность исчезает.
-При $T<T_C$ она не равна нулю и стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_C$.
+При $T>T_c$ спонтанная намагниченность исчезает.
+При $T<T_c$ она не равна нулю и стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_c$.
 Это ферромагнитная фаза.
@@
   \label{eq:28}
-  M\sim \left|T_C-T\right|^{\frac{1}{8}}
+  M\sim \left|T_c-T\right|^{\frac{1}{8}}
 \end{equation}
+Направление намагниченности определяется тем, куда было направлено внешнее поле до того, как его устремили к $0$.
+
+При подходе к критической точке магнитная восприимчивость расходится
+\begin{equation}
+  \label{eq:29}
+  \chi=\frac{\partial M}{\partial h}\sim \left|T-T_c \right|^{-\frac{7}{4}}.
+\end{equation}
+Вдали от критической точки корреляторы $\Gamma_c(i)$ убывают экспоненциально с расстоянием. Характерная длина убывания $\xi$ называется корреляционной длиной
+\begin{equation}
+  \label{eq:30}
+  \left<\sigma_i\sigma_j\right>_c\sim e^{-\frac{\left|i-j\right|}{\xi(T)}}\quad \left|i-j\right|>>1.
+\end{equation}
+При $T\to T_c$ корреляционная длина расходится
+\begin{equation}
+  \label{eq:31}
+  \xi(T)\sim \frac{1}{\left|T-T_c\right|}.
+\end{equation}
+Такое поведение характеризует переходы второго рода и наблюдается в критических точках фазовой диаграммы.
+
+Около критической точки система состоит из доменов разной намагниченности.
+Существуют домены всевозможных размеров от шага решетки до корреляционной длины $\xi$.
+Свободная энергия $F$ получает вклады от доменных стенок.
+Сингулярное поведение возникает из-за вкладов доменов большого размера, оно определяется флуктуациями и не может быть правильно учтено в теории среднего поля.
+Вблизи критической температуры $\xi$ больше физических размеров системы.
+Свободная энергия перестает зависеть от $\xi$.
+
+\subsection{Процедура Каданова}
+\label{sec:kadanoff-procedure}
+
+\section{Лекция 3}
+\label{sec:lecture-3}
+
+\subsection{Ренормгруппа в решеточных моделях}
+\label{sec:renormgroup-lattice-models}
+
+\subsection{Ренормгруппа в непрерывных моделях}
+\label{sec:renormgroup-general}
 

### 2010-10-07 GeneralOverview/Lectures/2dqft.tex
More work on lecture notes

@@
 
+Парная корреляционная функция ведет себя как
+\begin{equation}
+  \label{eq:32}
+  \Gamma(\vec n)\sim \frac{1}{\left|\vec n\right|^{d-2+\eta}}
+\end{equation}
+Поведение термодинамических величин определяется критическими индексами. Перечислим их вместе со значениями в двумерной модели Изинга. Эти значения получены из точных решений модели.
+\begin{table}[h!tb]
+\label{tab:diagrams}
+\noindent  \centering{
+\begin{tabular}{|l|l|l|}
+  \hline
+  Критический индекс & Термодинамическая величина & Значение индекса в двумерной модели Изинга\\
+  \hline
+  $\alpha$ & $C\sim \frac{1}{\left|T-T_c\right|^{\alpha}}$ & $0$\\
+  $\beta$ & $M\sim \left|T-T_c\right|^{\beta}$ & $\frac{1}{8}$\\
+  $\gamma$ & $\chi\sim \frac{1}{\left|T-T_c\right|^{\gamma}}$ & $\frac{7}{4}$\\
+  $\delta$ & $M\sim h^{\frac{1}{\delta}}$ & $15$ \\
+  $\nu$ & $\xi\sim \frac{1}{\left|T-T_c\right|^{\nu}}$ & $1$\\
+  $\eta$ & $\Gamma(\vec n)\sim \left|\vec n\right|^{2-d-\eta}$ & $\frac{1}{4}$\\
+  \hline
+\end{tabular}
+\caption{Критические индексы и их значения в модели Изинга в 2 измерениях}
+\end{table}
+
+Заметим, что систему можно описывать классической статистической механикой (обычной квантовой теорией поля с неограниченным временем) когда корреляционная длина больше характерной длины волны де Бройля.
+Если характерная скорость $v$ (скорость света, скорость Ферми или скорость какого-либо возбуждения), то $\lambda_T=\frac{v\hbar}{k_B T}\sim \beta$.
+То есть классическая статистика применима при больших температурах или вблизи критической точки, если $T_c\neq 0$.
+
+\subsection{Скейлинг или масштабная инвариантность}
+\label{sec:scaling}
+
+Гипотеза подобия связывает между собой критические индексы.
+Ее можно сформулировать так: плотность свободной энергии $f(t,h)=\frac{F}{N}$ около критической точки является однородной функцией $h$ и безразмерной температуры $t=\frac{T}{T_c}-1$.
+То есть существуют $a,b$:
+\begin{equation}
+  \label{eq:33}
+  f(\lambda^a t,\lambda^b h)=\lambda f(t,h)
+\end{equation}
+В следующих лекциях мы обоснуем эту гипотезу при помощи ренормгруппы.
+
+Покажем теперь, какие условия накладывает гипотеза подобия на критические индексы. Заметим, что $t^{-\frac{1}{a}}f$ инвариантна при преобразовании $t\to \lambda^a t, h\to \lambda^b h$. Введем
+\begin{equation}
+  \label{eq:34}
+  y=\frac{h}{t^{\frac{b}{a}}}
+\end{equation}
+Тогда
+\begin{equation}
+  \label{eq:35}
+  f(t,h)=t^{\frac{1}{a}}g(y).
+\end{equation}
+Для намагниченности имеем
+\begin{equation}
+  \label{eq:36}
+  M=-\left\frac{\partial f}{\partial h}\right|_{h=0}=t^{\frac{1-b}{a}}g'(0),
+\end{equation}
+а для  магнитной восприимчивости
+\begin{equation}
+  \label{eq:37}
+  \chi=\left.\frac{\partial^2 f}{\partail h^2}\right|_{h=0}=t^{\frac{1-2b}{a}}g''(0).
+\end{equation}
+Аналогично для удельной теплоемкости получаем
+\begin{equation}
+  \label{eq:38}
+  c=-T\left.\frac{\partial^2 f}{\partial T^2}\right|_{h=0}=-\frac{1}{T_c}t^{\frac{1}{a-2}}g''(0)
+\end{equation}
+
 \subsection{Процедура Каданова}

### 2010-10-08 GeneralOverview/Lectures/2dqft.tex
Bibtex encoding specified, latex errors corrected
More work on lecture notes

@@
 \caption{Критические индексы и их значения в модели Изинга в 2 измерениях}
+}
 \end{table}
@@
 \end{equation}
-Для намагниченности имеем
+Для спонтанной намагниченности имеем
 \begin{equation}
   \label{eq:36}
-  M=-\left\frac{\partial f}{\partial h}\right|_{h=0}=t^{\frac{1-b}{a}}g'(0),
+  M=-\left.\frac{\partial f}{\partial h}\right|_{h=0}=t^{\frac{1-b}{a}}g'(0),
 \end{equation}
@@
   \label{eq:37}
-  \chi=\left.\frac{\partial^2 f}{\partail h^2}\right|_{h=0}=t^{\frac{1-2b}{a}}g''(0).
+  \chi=\left.\frac{\partial^2 f}{\partial h^2}\right|_{h=0}=t^{\frac{1-2b}{a}}g''(0).
 \end{equation}
@@
 \end{equation}
-
+В пределе $t\to 0$ $M\sim h^{\frac{1}{\delta}$, поэтому $g'(y)\sim y^{\frac{1}{\delta}}$ при $y\to \infty$.
+А значит, если в критической точке намагниченность $M$ конечна и не равна нулю, должно выполняться равенство $1-b-\frac{b}{\delta}=0$.
+Подставляя выражение для $\delta$ через $b$ в (\ref{eq:36},\ref{eq:37},\ref{eq:38}), мы получаем связь критических индексов
+  \begin{eqnarray}
+    \label{eq:39}
+    \alpha=2-\frac{1}{a}\\
+    \beta=\frac{1-b}{a}\\
+    \gamma=-\frac{1-2b}{a}\\
+    \delta=\frac{b}{1-b}
+  \end{eqnarray}
 \subsection{Процедура Каданова}
 \label{sec:kadanoff-procedure}
-
+Теперь обоснуем гипотезу подобия в модели Изинга при помощи процедуры Каданова и свяжем индексы $a,b$ с $\nu,\eta$.
+Рассмотрим кубическую $d$-мерную модель Изинга.
+\begin{equation}
+  \label{eq:40}
+  H=-J\sum_{\left<ij\right>}\sigma_i \sigma_j-h\sum_i \sigma_i
+\end{equation}
+Разбиваем решетку на блоки со стороной в $r$ ячеек. Будем нумеровать блоки большими латинскими буквами $I,J$ и понимать под записью $i\in I$ перечисление вершин в $I$-том блоке.
+Сумма спинов в блоке принимает значения от $r^{-d}$ до $r^d$. Введем блочный спин
+\begin{equation}
+  \label{eq:41}
+  \Sigma_I=\frac{1}{R}\sum_{i\in I}\sigma_i
+\end{equation}
+$R$ - нормировочный множитель, который выбирается так, чтобы блочный спин мог принимать значения $\pm 1$.
 \section{Лекция 3}

### 2010-10-12 GeneralOverview/Lectures/2dqft.tex
More work on lecture notes

@@
 \end{equation}
-$R$ - нормировочный множитель, который выбирается так, чтобы блочный спин мог принимать значения $\pm 1$.
+$R$ - нормировочный множитель, который выбирается так, чтобы блочный спин мог принимать значения $\pm 1$. Если бы спины были всегда в одном направлении, то $R$ имел бы значение $r^d$.
+
+Мы предполагаем, что поведение вблизи критической точки описывается в терминах блочных спинов, так как корреляционная длина $\xi>>r$. Гамильтониан для блочных спинов имеет вид
+\begin{equation}
+  \label{eq:42}
+  H'=-J' \sum_{\left<IJ\right> \Sigma_I \Sigma_J-h' \sum_I \Sigma_I
+\end{equation}
+Так как корреляционная длина для блоков
+\begin{equation}
+  \label{eq:43}
+  \xi'=\frac{\xi}{r},
+\end{equation}
+то из (\ref{eq:31}) для температуры имеем
+\begin{equation}
+  \label{eq:44}
+  t'=r^{\frac{1}{\nu} t.
+\end{equation}
+Суммарная энергия взаимодействия со внешним полем должна оставаться неизменной, то есть
+\begin{equation}
+  \label{eq:45}
+  h\sum_i \sigma_i=h' \sum_I \Sigma_I=\frac{h'}{R}\sum_i \sigma_i\quad\Longrightarrow\quad h'= Rh
+\end{equation}
+Так как общая свободная энергия тоже не должна меняться, то свободная энергия на блок $\sim r^d f$, то есть
+\begin{equation}
+  \label{eq:46}
+  f(t',h')=r^d f(t,h)
+\end{equation}
+или
+\begin{equation}
+  \label{eq:47}
+  f(t,h)=r^{-d} f(r^{\frac{1}{\nu}} t, Rh)
+\end{equation}
+Осталось вычислить $R$ как функцию от $r$, чтобы оправдать гипотезу подобия. Смотрим на парный коррелятор в критической точке
+\begin{multline}
+  \label{eq:48}
+  \Gamma'(\vec n)=\left< \Sigma_I\Sigma_J\right>-\left< \Sigma_I\right>\left<\Sigma_J\right>=\frac{1}{R^2}\sum_{i\in I}\sum_{j\in J}\left(\left<\sigma_i \sigma_j\right>-\left<\sigma_i\right>\left<\sigma_j\right>\right) =\\
+  = \frac{r^{2d}}{R^2}\Gamma(r\vec n)=\frac{R^{-2}r^{2d}}{\left|r\vec n\right|^{d-2+\eta}}=\frac{R^{-2}r^{d+2-\eta}}{\left|\vec n\right|^{d-2+\eta}}
+\end{multline}
+Отсюда
+\begin{equation}
+  \label{eq:49}
+  R=r^{\frac{d+2-\eta}{2}}, \quad h'=r^{\frac{d+2-\eta}{2}}h
+\end{equation}
+Подставляя в (\ref{eq:33}) $r=\lambda^{\frac{1}{d}}$ получаем выражение для скейлинговых параметров $a,b$:
+\begin{eqnarray}
+  \label{eq:50}
+  a=\frac{1}{\nu d}\\
+  b=\frac{d+2-\eta}{2d}
+\end{eqnarray}
+Для критических индексов имеем
+\begin{eqnarray}
+  \label{eq:51}
+  \alpha=2-\nu d\\
+  \beta=\frac{1}{2}\nu (d-2+\eta)\\
+  \gamma=\nu (2-\eta)\\
+  \delta=\frac{d+2-\eta}{d-2+\eta}
+\end{eqnarray}
+
 \section{Лекция 3}

### 2010-10-12 GeneralOverview/Lectures/2dqft.tex
Lecture 3 started

@@
   \hline
-  Критический индекс & Термодинамическая величина & Значение индекса в двумерной модели Изинга\\
+  Критический индекс & Термодинамическая величина & Значение индекса в \\
+  &  & двумерной модели Изинга\\
   \hline
@@
 \end{equation}
-В пределе $t\to 0$ $M\sim h^{\frac{1}{\delta}$, поэтому $g'(y)\sim y^{\frac{1}{\delta}}$ при $y\to \infty$.
+В пределе $t\to 0$ $M\sim h^{\frac{1}{\delta}}$, поэтому $g'(y)\sim y^{\frac{1}{\delta}}$ при $y\to \infty$.
 А значит, если в критической точке намагниченность $M$ конечна и не равна нулю, должно выполняться равенство $1-b-\frac{b}{\delta}=0$.
@@
   \label{eq:42}
-  H'=-J' \sum_{\left<IJ\right> \Sigma_I \Sigma_J-h' \sum_I \Sigma_I
+  H'=-J' \sum_{\left<IJ\right>} \Sigma_I \Sigma_J-h' \sum_I \Sigma_I
 \end{equation}
@@
   \label{eq:44}
-  t'=r^{\frac{1}{\nu} t.
+  t'=r^{\frac{1}{\nu}} t.
 \end{equation}
@@
 \label{sec:lecture-3}
+В прошлой лекции мы обосновали гипотезу подобия при помощи рассмотрения блочных спинов и введения эффективного гамильтониана, имеющего ту же форму, но другие константы связи.
+Эта процедура является перенормировкой в координатном пространстве, она определяет отображение гамильтониана $H\to H'$.
+Последовательное применение такой процедуры порождает так называемую ренормгруппу.
+Строго говоря, ренормгруппа является не группой, полугруппой, так как у преобразования нет обратного, ведь при переходе к блокам большего размера мы теряем информацию.
+Опишем ренормгруппу для решеточных моделей.
 
@@
 \label{sec:renormgroup-lattice-models}
+Рассматриваем решеточную модель, состоящую из $N$ спинов $\sigma_i$ на $d$-мерной решетке. Общий вид гамильтониана таких моделей
+\begin{equation}
+  \label{eq:55}
+  H(\vec J,[\sigma],N)=J_0 + J_1\sum_i \sigma_i +J_2\overset{(1)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j+J_3\overset{(2)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j + \dots
+\end{equation}
+Здесь мы явно указали на зависимость гамильтониана от констант связи, которые собраны в вектор $\vec J=(J_0,J_1,J_2,J_3,\dots)$.
+Сумма $\overset{(1)}{\sum_{\left<ij\right>}}$ - это сумма по ближайшим соседям, $\overset{(2)}{\sum_{\left<ij\right>}}$ - сумма по вершинам, разделенным двумя ребрами (через одного) и так далее.
+Статсумма
+\begin{equation}
+  \label{eq:56}
+  Z(\vec J,N)=\sum_{[\sigma]}e^{-H(\vec J,[\sigma],N)}
+\end{equation}
+Мы так переопределили константы связи, чтобы избавиться от множителя $\beta$.
+
+Теперь мы вводим блочные переменные с блоком со стороной в $r$ ячеек решетки, содержащим $r^d$ вершин.
+$\Sigma_I$ - блочные спины, $\xi_i$ - переменные внутри блока.
+В таких переменных статсумма переписывается так:
+\begin{equation}
+  \label{eq:57}
+  Z(\vec J,N)=\sum_{[\Sigma][\sigma]}e^{-H(\vec J,[\Sigma],[\sigma],N)}
+\end{equation}
+Если мы просуммируем по внутриблочным степеням свободы $\xi$, то получится перенормированный гамильтониан $H'(\vec J,[\Sigma],Nr^{-d})$.
+\begin{equation}
+  \label{eq:58}
+  e^{-H'(\vec J',[\Sigma],Nr^{-d})}=\sum_{[\xi]}e^{-H(\vec J,[\Sigma],[\xi],N)}
+\end{equation}
+Вблизи критической точки можно предполагать что у $H'$ такой же вид, как и у $H$, так как параметр порядка расходится и поведение определяется дальними корреляциями.
+Описания поведения системы в терминах $H'$ и $H$ эквивалентны, поэтому соответствующие выражения для статсуммы должны совпадать (с точностью до умножения на константу):
+\begin{equation}
+\label{eq:52}
+  Z(\vec J,N)=\sum_{[\Sigma]}e^{-H'(\vec J',[\Sigma],Nr^{-d})}=Z(\vec J',Nr^{-d})
+\end{equation}
+Удельная свободная энергия отображается как $f(\vec J)=r^{-d} f(\vec J')$.
+
+Отображение констант связи $\vec J\to\vec J'$ и порождает ренормгруппу. Будем его записывать как
+\begin{equation}
+  \label{eq:53}
+  \vec J'=T(\vec J)
+\end{equation}
+Последовательное применение таких преобразований порождает в пространстве констант связи некоторый набор точек, который называется траекторией ренормгруппы.
+
+На каждом шаге корреляционная длина уменьшается в $r$ раз, поэтому траектория уводит систему из окрестности критической точки.
+Но в самой критической точке корреляционная длина бесконечна, поэтому эта точка неподвижна относительно действия ренормгруппы.
+
+В общем случае критическое поведение наблюдается на некоторой критической поверхности в пространстве $\vec J$. Под действием ренормгруппы точки двигаются по ней. Стационарная точка
+\begin{equation}
+  \label{eq:54}
+  \vec J_c=T(\vec J_c)
+\end{equation}
+называется фиксированной точной ренормгруппы.
 

### 2010-10-13 GeneralOverview/Lectures/2dqft.tex
Lecture 3 completed

@@
 
+Вообще говоря, преобразование $T$ нелинейно, однако в окрестности фиксированной точки его можно линеаризовать.
+Вводим переменную $\delta\vec J=\vec J-\vec J_c$ и раскладываем $T$ в ряд Тейлора по $\delta\vec J$.
+Тогда
+\begin{equation}
+  \label{eq:59}
+  \delta\vec J'=A\delta\vec J,
+\end{equation}
+где $A$ - матрица, $A_{ij}=\frac{\partial T_i}{\partial J_j}$.
+Мы можем диагонализовать матрицу $A$, ее собственные значения мы обозначим через $\lambda_i$, собственные векторы через $\vec u_i$.
+Тогда для точки в пространстве констант связи мы можем написать (в окрестности  критической точки):
+\begin{equation}
+  \label{eq:60}
+  \vec J=\vec J_c+\sum_i t_i \vec u_i
+\end{equation}
+Переменные $t_i$ под действием ренормгруппы преобразуются так:
+\begin{equation}
+  \label{eq:61}
+  t'_i=\lambda_i t_i=r^{y_i} t_i
+\end{equation}
+Здесь мы ввели обозначение $y_i$ для критических индексов. В примере из раздела \ref{sec:kadanoff-procedure} такими индексами были $a$ и $b$. 
+Для свободной энергии имеем
+\begin{equation}
+  \label{eq:62}
+  f(t_1,t_2,\dots)=r^{-d} f(r^{y_1}t_1,r^{y_2}t_2,\dots)
+\end{equation}
+Таким образом, критические индексы получаются из собственных значений линеаризованной ренормгруппы в фиксированной точки.
+
+Если часть собственных значений $\lambda_i$ положительна, а часть - отрицательная, то фиксированная точка называется гиперболической. 
+Критической поверхностью называются такие точки $\vec J$, что
+\begin{equation}
+  \label{eq:63}
+  \lim_{n\to \infty}T^n (\vec J)=\vec J_c
+\end{equation}
+Около точки $\vec J_c$ она представляет собой векторное пространство, натянутое на те векторы $\vec u_i$, для которых соответствующие собственные значения $\lambda_i<1$.
+
+Параметры $t_i$, которые соответствуют $\lambda_i>1$ называются релевантными, так как они растут под действием ренормгруппы.
+Параметры с $y_i<0 \; (\lambda_i<1)$ --- иррелевантные, с $y_i=0$ --- маргинальные.
+
+Существование критической поверхности объясняет универсальность критических индексов в разных моделях.
+Статистические системы разбиваются на классы универсальности, члены которых имеют одинаковое критическое поведение.
+Это так, если разные системы живут на подмногообразиях в пространстве констант связи, которые пересекают одну и ту же критическую поверхность.
+Тогда критическая точка у них общая.
+
 \subsection{Ренормгруппа в непрерывных моделях}
 \label{sec:renormgroup-general}
+В непрерывных моделях перенормировка осуществляется в импульсном пространстве. Рассмотрим скалярное поле $\varphi(\vec x)$, где $\vec x\in \mathbb{R}^d$. Проведем преобразование Фурье
+\begin{equation}
+  \label{eq:64}
+  \varphi(\vec x)=\int \frac{d^d \vec k}{(2\pi)^d}\tilde \varphi(\vec k) e^{i\vec k\cdot \vec x}
+\end{equation}
+Функционал действия может быть переписан в виде, зависящем только от $\tilde\varphi$: $S[\varphi]\to S[\tilde\varphi]$. Например, для модели $\varphi^4$ \eqref{eq:16} получается
+\begin{multline}
+  \label{eq:65}
+  S[\varphi,r,u]=\int  \frac{d^d \vec k}{(2\pi)^d} \frac{1}{2} \tilde\varphi(-\vec k)\tilde\varphi(\vec k)(\vec k^2+r)+\\
+  \frac{1}{4}u\int  \frac{d^d \vec k_1}{(2\pi)^d} \frac{d^d \vec k_2}{(2\pi)^d} \frac{d^d \vec k_3}{(2\pi)^d} \tilde\varphi(-\vec k_1-\vec k_2 -\vec k_3)\tilde \varphi(\vec k_1)\tilde\varphi (\vec k_2)\tilde\varphi(\vec k_3).
+\end{multline}
+В общем случае функционал действия зависит от поля $\varphi$ и параметров $u_i$ в плотности Лагранжиана (констант связи).
+
+Квантовая теория поля всегда содержит расходящиеся интегралы, поэтому нужна регуляризация.
+Будем считать, что в качестве такой регуляризации используется обрезание по импульсам $\left|\vec k\right|<\Lambda$.
+После преобразования Фурье мера в функциональном интеграле переписывается как
+\begin{equation}
+  \label{eq:66}
+  [d\varphi]_{\Lambda}=\prod_x d\varphi(x)=\prod_{\left|\vec k\right|<\Lambda}d\tilde\varphi(\vec k)
+\end{equation}
+Теперь опишем перенормировку Вильсона-Каданова.
+Она проводится в два этапа.
+Сначала мы интегрируем по $\tilde\varphi(\vec k): \Lambda/s<\left|k\right|<\Lambda$.
+То есть мы исключаем быстрые моды, так как критическое поведение описывается медленными модами.
+$s$-масштабный фактор.
+В результате мы получаем новое обрезание $\Lambda/s$ и действие $S'[\varphi,\{u_i\}]$.
+\begin{equation}
+  \label{eq:67}
+  e^{-S'[\varphi,\{u_i\}]}=\int \prod_{\Lambda/s<\left|\vec k\right|<\Lambda}d\varphi(\vec k)e^{-S[\varphi,\{u_i\}]}
+\end{equation}
+Пока нас интересую только медленные моды, действие $S'$ эквивалентно $S$. Вторым шагом осуществим масштабное преобразование
+\begin{eqnarray}
+  \label{eq:68}
+  \vec k \to \vec k'=s \vec k\\
+  \vec x\to \vec x'=\vec x/s
+\end{eqnarray}
+При этом поле преобразуется так:
+\begin{eqnarray}
+  \label{eq:69}
+  \varphi(\vec x)\to \varphi'(\vec x/s)=s^{\Delta}\varphi (\vec x)\\
+  \tilde\varphi'(s\vec k)=s^{\Delta-d}\tilde\varphi (\vec k)
+\end{eqnarray}
+Здесь $\Delta$- скейлинговая размерность поля $\varphi$, она связана с индексом $\eta$: $\Delta=\eta/2$.
+Мера в функциональном интеграле при масштабном преобразовании умножится на константу.
+Теперь можно сравнить $S'$ и $S$, так как масштаб обрезания и там и там равен $\Lambda$ и те же степени свободы.
+Эти два действия описывают одинаковое поведение на больших расстояниях.
+Поэтому вид действия $S'$ должен быть тот же, что и у $S$, но с другими константами связи $u_i'$.
+\begin{equation}
+  \label{eq:70}
+  S'[\varphi,\{u_i\}]=S[\varphi,\{u_i'\}]
+\end{equation}
+Последовательным действием таких преборазований мы получаем кривую $u_i(s)$ в пространстве параметров лагранжиана.  Мы можем записать уравнение этой кривой как
+\begin{equation}
+  \label{eq:71}
+  \frac{du_i}{d(\ln s)}=\beta_i(\{u_i\})
+\end{equation}
+$\beta_i$ называется $\beta$-функцией параметра $u_i$. 
+Фиксированная точка $u_j^{*}$:
+\begin{equation}
+  \label{eq:72}
+  \beta_i(\{u^{*}_j\})=0
+\end{equation}
+Эта точка неподвижна относительно преобразований ренормгруппы. В фиксированной точке теория масштабно-инвариантна на квантовом уровне.
 

### 2010-10-25 GeneralOverview/Lectures/2dqft.tex
Started lecture 4.

@@
 
+\section{Лекция 4. Ренормгруппа в двух измерениях.}
+\label{sec:lecture-4}
+
+Вообще говоря, квантовая теория поля может быть не масштабно-инвариантна из-за наличия размерных параметров на классическом уровне или возникающих при перенормировке. Действие
+\begin{equation}
+  \label{eq:73}
+  S=\int d^dx \mathcal{L}
+\end{equation}
+зависит от полей $\varphi$ и констант связи $\vec u=(u_1,\dots,u_n)$.
+Рассмотрим инфинитезимальное масштабное преобразование $\lambda=1+\omega$.
+При этом вариация $x_{\nu}$ будет $\delta_{\omega}x_{\nu}=\omega x_{\nu}$.
+Такое преобразование, в соответствии с предыдущей лекцией,  можно рассматривать как преобразование констант связи $\vec u\to \vec u'$.
+При наличии масштабной инвариантности $\vec u = \vec u'$.
+Вариация плотности лагранжиана дается Нётеровским током:
+\begin{equation}
+  \label{eq:74}
+  \delta_{\omega}\mathcal{L}=\partial_{\mu}J^{\mu}\omega
+\end{equation}
+\begin{equation}
+  \label{eq:75}
+  J^{\mu}=x_{\nu}T^{\mu\nu}
+\end{equation}
+Здесь $T^{\mu\nu}$ - тензор энергии-импульса.
+Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$.
+Через $\Theta$ мы обозначили след тензора энергии-импульса.
+В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
+Напомним, что
+\begin{equation}
+  \label{eq:76}
+  \beta_{i}(\vec u)=\frac{du_i}{d\ln s}
+\end{equation}
+Если в точке $u$ $\beta_i(\vec u)>0$, то $u_i(\ln s)$ растет, $\beta_i (\vec u)<0$ - убывает.
+В фиксированной точке $u^*$ $\beta_i(\vec u^*)=0$.
+Пространство действий делится фиксированной точкой на регионы.
+Константы связи ``заперты'' в одном из этих регионов.
+Фиксированная точка может достигаться при $\ln s\to \pm \infty$.
+Если $u(\ln s)\to u^*$ при $\ln s\to +\infty$, то такая точка называется инфракрасной, если $u(\ln s)\to u^*$ при $\ln s\to -\infty$, то ультрафиолетовой.
+Введем функции $\Phi_i$:
+\begin{equation}
+  \label{eq:77}
+  \Phi_i=\frac{\partial \mathcal{L}}{\partial u_i}
+\end{equation}
+Вариация $\delta \mathcal{L}$ дается их линейной комбинацией.
+\begin{equation}
+  \label{eq:78}
+  \Theta(x)=\frac{\partial \mathcal{L}}{\partial (\ln s)}=\sum_i \frac{\partial \mathcal{L}}{\partial u_i}\frac{d u_i}{d(\ln s)}=\sum_i\beta_i(\vec u)\Phi_i(\vec u)
+\end{equation}
+$\Theta=0$ тогда и только тогда, когда $\beta_i(\vec u)=0$, значит в фиксированной точке ренормгруппы есть масштабная инвариантность.
 \bibliography{2dqft}{}

### 2010-10-26 GeneralOverview/Lectures/2dqft.tex
Lecture 4 completed

@@
 
-\section{Лекция 4. Ренормгруппа в двух измерениях.}
+\section{Лекция 4. Уравнение Каллана-Симанчика. Ренормгруппа в двух измерениях.}
 \label{sec:lecture-4}
@@
 При наличии масштабной инвариантности $\vec u = \vec u'$.
-Вариация плотности лагранжиана дается Нётеровским током:
+При инфинитезимальных преобразованиях $x\to x+dl x$ вариация плотности лагранжиана дается Нётеровским током:
 \begin{equation}
   \label{eq:74}
-  \delta_{\omega}\mathcal{L}=\partial_{\mu}J^{\mu}\omega
+  \delta\mathcal{L}=\partial_{\mu}J^{\mu}dl
 \end{equation}
@@
 \end{equation}
-Здесь $T^{\mu\nu}$ - тензор энергии-импульса.
-Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$.
-Через $\Theta$ мы обозначили след тензора энергии-импульса.
-В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
+Здесь $T^{\mu\nu}$ - тензор энергии-импульса.  Через $\Theta$ мы обозначим след тензора энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия
+\begin{equation}
+  \label{eq:87}
+  \delta S=dl \int d^d x \Theta(x)
+\end{equation}
+Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$. В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
+
+В классической теории вид преобразований полей при масштабных преобразованиях легко получаются из анализа размерностей.
+Напомним, что достаточно иметь одну единицу измерения - длины (или обратной длины).
+Если теория масштабно-инвариантна, то действие должно быть безразмерным.
+Канонические (классические) размерности полей легко определить из требования безразмерности слагаемых в функционале действия, если ввести соглашение, определяющее размерность координат или импульсов.
+
+Будем обозначать каноническую размерность произвольно величины $F$ через $d[F]$.
+Положим $d[p]=-d[x]=1$. Тогда $d[d^d x]=-d,\; d[\partial]=1$. Теперь легко найти размерности полей. Например, для модели $\varphi^4$
+\begin{equation}
+  \label{eq:83}
+  S[\varphi]=\int d^d x\left( -\frac{(\partial \varphi)^2}{2}-\frac{\mu \varphi^2}{2}-\frac{u\varphi^4}{24}+h\varphi\right),
+\end{equation}
+рассмотрим первое слагаемое. Оно должно быть безразмерным. При этом его размерность $d[\int d^d x (\partial \varphi)^2]=2d[\varphi]+2-d=0$. Отсюда $d[\varphi]=d/2-1$. Для общего действия
+\begin{equation}
+  \label{eq:84}
+  S[\varphi]=-\int d^d x\left( \frac{(\partial \varphi)^2}{2}+\sum_n u_n \frac{\varphi^n}{n!}\right)
+\end{equation}
+размерности констант связи следующие:
+\begin{equation}
+  \label{eq:85}
+  d[h=-u_1]=d/2+1,\quad d[\mu=u_2]=2,\quad d[g_4]=4-d,\quad d[g_6]=6-2d,\quad d[g_n]=n-\frac{d(n-2)}{2}
+\end{equation}
+При масштабных преобразованиях поля и константы связи ведут себя так:
+\begin{equation}
+  \label{eq:86}
+  \varphi'(x)=s^{-d[\varphi]}\varphi(x/s),\quad u_i'=s^{-d[u_i]}u_i
+\end{equation}
+
 Напомним, что
@@
 \end{equation}
-Если в точке $u$ $\beta_i(\vec u)>0$, то $u_i(\ln s)$ растет, $\beta_i (\vec u)<0$ - убывает.
+Параметр ренормгруппы $s$ связан с параметром масштабного преобразования $l$ соотношением $l=\ln s$, при этом
+\begin{equation}
+  \label{eq:79}
+   \beta_{i}(\vec u)=\frac{du_i}{dl}
+\end{equation}
+Если в точке $u$ $\beta_i(\vec u)>0$, то $u_i(l)$ растет, $\beta_i (\vec u)<0$ - убывает.
 В фиксированной точке $u^*$ $\beta_i(\vec u^*)=0$.
@@
 Константы связи ``заперты'' в одном из этих регионов.
-Фиксированная точка может достигаться при $\ln s\to \pm \infty$.
-Если $u(\ln s)\to u^*$ при $\ln s\to +\infty$, то такая точка называется инфракрасной, если $u(\ln s)\to u^*$ при $\ln s\to -\infty$, то ультрафиолетовой.
+Фиксированная точка может достигаться при $l\to \pm \infty$.
+Если $u(l)\to u^*$ при $l\to +\infty$, то такая точка называется инфракрасной, если $u(l)\to u^*$ при $l\to -\infty$, то ультрафиолетовой.
 Введем функции $\Phi_i$:
@@
   \label{eq:78}
-  \Theta(x)=\frac{\partial \mathcal{L}}{\partial (\ln s)}=\sum_i \frac{\partial \mathcal{L}}{\partial u_i}\frac{d u_i}{d(\ln s)}=\sum_i\beta_i(\vec u)\Phi_i(\vec u)
+  \Theta(x)=\frac{\partial \mathcal{L}}{\partial l}=\sum_i \frac{\partial \mathcal{L}}{\partial u_i}\frac{d u_i}{dl}=\sum_i\beta_i(\vec u)\Phi_i(\vec u)
 \end{equation}
 $\Theta=0$ тогда и только тогда, когда $\beta_i(\vec u)=0$, значит в фиксированной точке ренормгруппы есть масштабная инвариантность.
+
+Рассмотрим $N$-точечную корреляционную функцию --- среднее значение некоторого $N$-точечного локального оператора
+\begin{equation}
+  \label{eq:81}
+  \langle X\rangle =\langle A_1 (x_1)\dots A_N (x_N)\rangle
+\end{equation}
+
+Мы хотим получить уравнение для его преобразования под действием ренормгруппы. Такое уравнение называется уравнением Каллана-Симанчика.
+
+Вариация корреляционных функций при масштабных преобразованиях может описываться двумя способами.
+
+Во-первых, мы можем вычислить вариацию всех полей:
+\begin{multline}
+  \label{eq:82}
+  \delta \langle X\rangle=\delta \langle A_1(x_1)\dots A_N (x_N)\rangle = \delta \int {\cal D}\varphi A_1 \dots A_N e^{-S[\varphi]} = \\
+  \delta \int {\cal D} \varphi\; \left( \sum_k A_1 \dots \delta A_k \dots A_N e^{-S[\varphi]} -A_1\dots A_N e^{-S[\varphi]}\delta S\right)
+\end{multline}
+Вариация $A_k$ дается глобальной дилатацией координат и внутренней вариацией поля в соответствии с его канонической размерностью:
+\begin{equation}
+  \label{eq:88}
+  \delta A_k=dl (x^{\mu}_k\partial^k_{\mu}+d[A_k]) A_k
+\end{equation}
+Вариация действия определяется следом тензора энергии-импульса (\ref{eq:87}). Поэтому
+\begin{equation}
+  \label{eq:89}
+  \delta\langle X\rangle=dl \left(\sum_k (x_k^{\mu}\partial_{\mu}^k+d[A_k])\langle X\rangle-\int d^d y \Theta(y)\right)
+\end{equation}
+
+Другой способ вычисления состоит в вариации полей и действия по константам связи $u_i$:
+\begin{equation}
+  \label{eq:90}
+  \delta\langle X\rangle=dl\sum_i \beta_i(\vec u)\frac{\partial}{\partial u_i}\langle X\rangle,
+\end{equation}
+но
+\begin{equation}
+  \label{eq:91}
+  \frac{\partial}{\partial u_i}\langle X\rangle=\sum_k \langle A_1\dots \frac{\partial A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Phi_i(y)\rangle.
+\end{equation}
+Отсюда
+\begin{equation}
+  \label{eq:92}
+  \delta\langle X\rangle=dl \sum_i \sum_k\langle A_1\dots \frac{\partial A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Theta(y)\rangle
+\end{equation}
+Сравнивая это уравнение с (\ref{eq:89}) получаем уравнение Каллана-Симанчика:
+\begin{equation}
+  \label{eq:93}
+  \left[ \sum_k\left( x^{\mu}_k \frac{\partial}{\partial x^{\mu}_k}+\Gamma_k(\vec u)\right) -\sum_i \beta_i(\vec u)\frac{\partial }{\partial u_i}\right]\langle X\rangle=0,
+\end{equation}
+где $\Gamma_k$ - аномальная размерность поля $A_k(x_k)$, определяющаяся выражением
+\begin{equation}
+  \label{eq:94}
+  \Gamma_k A_k(x_k)=\left( d[A_k]+\sum_i \beta_i(\vec u) \frac{\partial }{\partial u_i}\right) A_k(x_k).
+\end{equation}
+В частности, для следа тензора энергии-импульса $\Gamma \Theta=2 \Theta$, то есть аномальная размерность равна классической.
+Это верно и для других компонент тензора энергии-импульса в силу Лоренц-инвариантности.
+
+Реноргрупповой анализ квантовой теории поля в двух измерениях дает следующий результат, известный как $c$-теорема Замолодчикова \cite{zamolodchikov1986irreversibility}.
+
+\begin{theorem}
+  Для любой унитарной квантовой теории поля в двух измерениях существует функция $c(\vec u)$ такая, что
+  \begin{itemize}
+  \item $c(\vec u)$ убывает, как функция параметра ренормгруппы
+    \begin{equation}
+      \label{eq:95}
+      \frac{dc}{dl}\leq 0
+    \end{equation}
+  \item $c(\vec u)$ стационарна в фиксированной точке $\vec u^*$ ренормгруппы, то есть
+    \begin{equation}
+      \label{eq:96}
+      \frac{dc({\vec u^*})}{dl}=0 \Leftrightarrow \beta_i(\vec u^*)=0
+    \end{equation}
+  \item 2-точечные корреляторы в фиксированной точке полностью определяются значением $c=c(\vec u^*)$.
+    Если ввести комплексные координаты $z=x_1+ix_2,\quad \bar z=x_1-ix_2$ и обозначить компоненты тензора энергии импульса через $T=T_{zz}$, $\bar T=T_{\bar z\bar z}$, $\Theta=T_{z\bar z}=T_{\bar z z}=T_{\mu\mu}=0$, то для корреляторов верно следующее выражение
+    \begin{eqnarray}
+      \label{eq:97}
+      \langle T(z,\bar z)T(0,0)\rangle=\frac{c/2}{z^4}\\
+      \langle \bar T(z,\bar z)\bar T(0,0)\rangle=\frac{c/2}{\bar z^4}\\
+      \langle T(z,\bar z) \bar T(0,0)\rangle=0
+    \end{eqnarray}
+    Число $c=\lim_{\vec u\to \vec u^*} c(\vec u)$ называется центральным зарядом. 
+  \end{itemize}
+\end{theorem}
+Для унитарных теорий из этой теоремы следует, что $c_{UV}\geq c_{IR}$.
+
+В фиксированной точке ренормгруппы имеет место масштабная инвариантность.
+Вместе с трансляционной и лоренц-инвариантностью она порождает конформную инвариантность, то есть инвариантность относительно преобразований, сохраняющих углы.
 \bibliography{2dqft}{}

### 2010-10-31 AffineLieAlgebras/InformalNotes/article.tex
Section 2 is rewritten, theorem added.

--- 2010-09-29 AffineLieAlgebras/InformalNotes/article.tex
@@
 \newtheorem{statement}{Statement}
+\theoremstyle{definition}
 \newtheorem{lemma}{Lemma}
@@
 \newtheorem{definition}{Definition}
+\newtheorem{remark}[theorem]{Remark}
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
  $k_{\lambda}$ --- the anomalous branching coefficients, notice that
-\begin{equation*}
+\begin{equation}
 %  \label{eq:20}
   b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}};
-\end{equation*}
+\label{eq:21-1}
+\end{equation}
 
@@
 
-\section{Recurrent relation for branching coefficients. Singularities and subtractions}
+\section{Recurrent relation for branching coefficients.}
 \label{sec:recurr-form-branch}
 
-We consider an injection of affine Lie algebras $\frak{a}\longrightarrow \frak{g%
-}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$.
-In this section we deduce the general recurrent relation (\ref{eq:1}) for the anomalous branching coefficients (\ref{eq:21}).
-This relation is then used to formulate the practical computational algorithm (Subsection \ref{sec:algorithm}).
-In the earlier paper \cite{ilyin812pbc} the following limited setup was considered: $\mathfrak{a}$ was required to be the maximal subalgebra of $\mathfrak{g}$ so that no zeros arrive in the Weyl denominator $R$.
-Here we raise this limitation and study the general case $\mathfrak{a}\subset\mathfrak{g}$.
-
-\subsection{Some definitions}
-\label{sec:some-definitions}
-
-We need to introduce several additional definitions and state some technical results to formulate and prove the recurrent relation (\ref{eq:1}).
+Let $\frak{a}\subset \frak{g}$ be a regular subalgebra of $\frak{g.}$
+Applying the Weyl-Kac character formula to the branching rule $\pi _{\frak{a}%
+}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu
+)}ch\left( L_{\frak{a}}^{\nu }\right) $ we get the relation connecting the
+singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{\left( \frak{a}%
+\right) }^{\left( \nu \right) }$ :
+\begin{eqnarray}
+\pi _{\frak{a}}\left( \frac{\sum_{\omega \in W}\epsilon (\omega )e^{\omega
+(\mu +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{%
+mult}(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}%
+\frac{\sum_{\omega \in W_{\frak{a}}}\epsilon (\omega )e^{\omega (\nu +\rho _{%
+\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
+}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\frak{a}}(\beta )}},  \label{eq:4} \\
+\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
+&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\left( \frak{%
+a}\right) }^{\left( \nu \right) }}{R_{\frak{a}}}.
+\end{eqnarray}
+where according to our notations $\Delta _{\frak{a}}^{+}$ is the set of
+positive roots of the subalgebra $\frak{a}$ (it is convenient to choose them
+from the positive root subspace of $\frak{g}$). Consider the root space $%
+\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to $\Delta _{\frak{a}}$,
+\begin{equation*}
+\frak{h}_{\perp \frak{a}}^{\ast }=:\left\{ \eta \in \frak{h}_{\frak{g}%
+}^{\ast }|\forall \alpha \in \Delta _{\frak{a}};\alpha \bot \eta \right\} ,
+\end{equation*}
+and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
+to $\Delta _{\frak{a}}$,
+\begin{eqnarray*}
+\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
+\alpha \in \Delta _{\frak{a}};\alpha \bot \beta \right\} , \\
+\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
+}^{+}|\forall \alpha ^{+}\in \Delta _{\frak{a}}^{+};\alpha ^{+}\bot \beta
+^{+}\right\} .
+\end{eqnarray*}
+Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
+reflections $\omega _{\beta }$ for the roots $\beta \in \Delta _{\frak{a}%
+_{\perp }}^{+}$ . The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
+subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
+_{\perp }}$. Let
+\begin{equation*}
+\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
+}|\forall \alpha \in \Delta _{\frak{a}}\cup \Delta _{\frak{a}_{\perp
+}};\alpha \bot \eta \right\}
+\end{equation*}
+and consider the subalgebras
+\begin{eqnarray*}
+\widetilde{\frak{a}_{\perp }} &:&=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\\
+\widetilde{\frak{a}} &:&=\frak{a}\oplus \frak{h}_{\perp }.
+\end{eqnarray*}
+
+The algebras $\frak{a}$ and $\frak{a}_{\perp }$ form an ''orthogonal pair''
+of subalgebras in $\frak{g}$. For the Cartan subalgebras we have the
+decomposition
+\begin{equation}
+\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
+\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
+\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
+\frak{h}_{\frak{a}}.
+\end{equation}
+For the subalgebras of the orthogonal pair $\left( \frak{a},\frak{a}_{\perp
+}\right) $ we consider the corresponding Weyl vectors, $\rho _{\frak{a}}$
+and $\rho _{\frak{a}_{\perp }}$ , and\ form the so called ''defects'' $%
+\mathcal{D}_{\frak{a}}$ and $\mathcal{D}_{\frak{a}_{\perp }}$ of the
+injection:
+\begin{equation}
+\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho ,
+\end{equation}
+\begin{equation}
+\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
+_{\perp }}\rho .
+\end{equation}
+For the highest weight module $L_{\frak{g}}^{\mu }$ consider the singular
+weights $\left( w(\mu +\rho )-\rho \right) \in \widehat{\Psi ^{\left( \mu
+\right) }}$ and their projections to $h_{\widetilde{\frak{a}_{\perp }}%
+}^{\ast }$ (additionally shifted by $-\mathcal{D}_{\frak{a}_{\perp }}$):
+\begin{equation*}
+\mu _{\widetilde{\frak{a}_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
+a}_{\perp }}}\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp
+}},\quad w\in W.
+\end{equation*}
+Among the weights $\mu _{\widetilde{\frak{a}_{\perp }}}\left( w\right)
+|_{w\in W}$ choose those located in the fundamental chamber $\overline{C_{%
+\widetilde{\frak{a}_{\perp }}}}$ and let $U$ be the set of representatives $%
+u $ for the classes $W/W_{\frak{a}_{\perp }}$ such that
+
+\begin{equation}
+U:=\left\{ u\in W|\quad \mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right)
+\in \overline{C_{\widetilde{\frak{a}_{\perp }}}}\right\} \quad .
+\label{U-def}
+\end{equation}
+For the same set $U$ introduce the weights
+\begin{equation*}
+\mu _{\frak{a}}\left( u\right) :=\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
+\right] +\mathcal{D}_{\frak{a}_{\perp }}.
+\end{equation*}
+
+To describe the recurrent properties for branching coefficients $b_{\nu
+}^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc} one of the
+main tools of which is the set of weights $\Gamma _{\frak{a}\subset \frak{g}%
+} $ called the injection fan. As far as we consider more general situation
+(where the injection is not maximal) the notion of the injection fan is
+modified:
 
 \begin{definition}
-  Denote by $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\mathfrak{a}} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$.
-\end{definition}
-
-\begin{definition}
-  Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
-\end{definition}
-\begin{mynote}
-  The subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\mathfrak{a}}$.
-\end{mynote}
-\begin{definition}
-  The subsystem $\Delta_{\bot}=\Delta^{+}_{\bot}\cup \left(-\delta^{+}_{\bot}\right)$ determines the subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
-\end{definition}
-
-We need to know when the subset $\Delta^{+}_{\bot}$ is non-empty and $W_{\bot},\mathfrak{a}_{\bot}$ are non-trivial. So we state several simple lemmas.
-
-For the simple finite-dimensional Lie algebras $\ao,\go$ all the regular embeddings can be obtained by the successive elimination of the nodes in the extended Dynkin diagram of $\go$.
-This leads to the lemma
-\begin{lemma}
-  For the regular embedding $\ao\subset \go$ 
-  \renewcommand{\theenumi}{\alph{enumi}}
-  \begin{enumerate}
-  \item $\Delta^{+}_{\bot}=\emptyset$ if $\ao$ is maximal
-  \item If the extended Dynkin diagram of $\go$ contains the disconnected subdiagrams of $\ao$ and some subalgebras $\left\{\co{\mathfrak{a}_j}\right\}$ then $\Delta^{+}_{\bot}\neq \emptyset$ and $\co{\mathfrak{a}_j}\subset \mathfrak{a}_{\bot}$.
-  \end{enumerate}
-\end{lemma}
-\begin{mynote}
-  The complete classification of the regular subalgebras for affine Lie algebras can be
-  found in the recent paper \cite{1751-8121-41-36-365204}.
-\end{mynote}
-\begin{mynote}
-  $\mathfrak{a}_{\bot}$ may be larger than the algebra $\bigoplus_j \co{\mathfrak{a}_j}$.
-\end{mynote}
-Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
-In this case by eliminating
-the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
-into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
-sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal to $B_2$
-(the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).
-
-Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$
-must not form a direct sum in $\mathfrak{g}$.
-Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both
-algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a
-subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
-Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with
-the remaining nodes of the diagram of $\mathfrak{g}$. The result is the diagram of
-the algebra $\bar{\mathfrak{a}}$ with $\mathrm{rank}(\bar{\mathfrak{a}}) =
-\mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that
-$\bar{\mathfrak{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether
-$\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\bar{\mathfrak{a}}$
-but the linear combinations of them. The answer is positive  when the set of angles
-between the roots of $\bar{\mathfrak{a}}$ does not contain all the angles between
-the roots of $\mathfrak{a}$.
-Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional
-roots of $\mathfrak{a}_{\bot}$.
-Case-by-case analysis illustrated by the table \ref{tab:diagrams} leads us to the following lemma.
-
-\begin{table}[h!tb]
-\label{tab:diagrams}
-\noindent  \centering{
-\begin{tabular}{|l|l|l|l|}
-  \hline
-  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ &
-  Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
-  \hline
-  $A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps} \\
-  \hline
-  $B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps} \\
-  \hline
-  $C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps} \\
-  \hline
-  $D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps} \\
-  \hline
-\end{tabular}
-\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
-\end{table}
-
-\begin{lemma}
-  \renewcommand{\theenumi}{\alph{enumi}}
-  \begin{enumerate}
-  \item If $\go,\ao\neq B_r$ the Dynkin diagram of $\mathfrak{a}_{\bot}$ is obtained from the extended Dynkin diagram of $\go$ by dropping the subdiagram of $\ao$ and the adjacent nodes
-  \item If $\go=B_r$ and $\ao=B_{r_{\mathfrak{a}}}$ then $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
-  \end{enumerate}
-\end{lemma}
-The complete classification of maximal special subalgebras in classical Lie algebras
-\cite{dynkin1952semisimple} allows us to formulate
-\begin{lemma}
-  For the special embeddings there exist the following set of pairs of orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$:
-\begin{equation*}
-%  \label{eq:42}
-  \begin{array}{lll}
-      su(p)\oplus su(q) & \subset su(pq) &\\
-      so(p)\oplus so(q) & \subset so(pq) &\\
-      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
-      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
-      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}.\\
-  \end{array}
-\end{equation*}
-\end{lemma}
-We are almost ready to state and prove the recurrent relation for the anomalous branching coefficients.
-\begin{definition}
-  \label{fan-definition}
-  For affine $\mathfrak{a}\subset\mathfrak{g}$ expand the product
-  \begin{equation*}
-    \label{eq:6}
-    \prod_{\alpha\in \Delta^{+}\setminus\Delta^{+}_{\bot}}
-    \left(1-e^{-\pi_{\mathfrak{a}}\alpha}\right)^{
-        \mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\pi_{\mathfrak{a}}\alpha)}=
-      -\sum_{\gamma\in P_{\mathfrak{a}}}e^{-\gamma}
-  \end{equation*}
-  Denote by $\Phi_{\mathfrak{a}\subset\mathfrak{g}}\subset P_{\mathfrak{a}}$ the carrier of the coefficient function $s(\gamma)$. 
-  \begin{equation*}
-    \label{eq:37}
-    \Phi_{\mathfrak{a}\subset\mathfrak{g}}=\left\{\gamma\in P_{\mathfrak{a}}|s(\gamma)\neq 0\right\}
-  \end{equation*}
-
-  The ordering of roots in $\co{\Delta_{\mathfrak{a}}}$ induce the natural ordering on the weights of $\mathfrak{a}$.
-Denote by $\gamma_0$ the lowest vector of $    \Phi_{\mathfrak{a}\subset\mathfrak{g}}$ according to this ordering.
-  The set 
+\label{fan-definition} For the product
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
+_{\frak{a}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\frak{a}%
+}(\pi _{\frak{a}}\alpha )}=-\sum_{\gamma \in P_{\frak{a}}}s(\gamma
+)e^{-\gamma }  \label{eq:6}
+\end{equation}
+consider the carrier $\Phi _{\frak{a}\subset \frak{g}}\subset P_{\frak{a}}$
+of the function $s(\gamma )=\det \left( \gamma \right) $ :
+\begin{equation}
+\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}|s(\gamma
+)\neq 0\right\}   \label{eq:37}
+\end{equation}
+The ordering of roots in $\co{\Delta _{\frak{a}}}$ induce the
+natural ordering of the weights in $P_{\frak{a}}$. Denote by $\gamma _{0}$
+the lowest vector of $\Phi _{\frak{a}\subset \frak{g}}$ . The set
 \begin{equation}
@@
 \end{equation}
-  is called the {\it injection fan}.
+is called the \textit{injection fan}.
 \end{definition}
 
-\subsection{Proof of the recurrent relation}
-\label{sec:proof}
+The main result is that the Weyl-Kac character formula (in terms of singular
+elements) describes the particular case of a more general relation:
+
+\begin{lemma}
+Let $\frak{a}$ and $\frak{a}_{\perp }$ be the orthogonal pair of regular
+subalgebras in $\frak{g}$, with $\widetilde{\frak{a}_{\perp }}=\frak{a}%
+_{\perp }\oplus \frak{h}_{\perp }$ and $\widetilde{\frak{a}}=\frak{a}\oplus
+\frak{h}_{\perp }$ ,
+
+$L_{\frak{g}}^{\mu }$ be the highest weight module with the singular element
+$\Psi _{\frak{g}}^{\mu }$ ,
+
+$R_{\frak{a}_{\perp }}$ be the Weyl denominator for $\frak{a}_{\perp }$.
+
+Then the element $\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{%
+\frak{a}_{\perp }}}\right) $ can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
+the singular elements $e^{\mu _{\frak{a}}\left( u\right) }$ with the
+coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\frak{a}_{\perp
+}}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right) $:
+\begin{equation}
+\quad \pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}%
+_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{\frak{a}}\left(
+u\right) }\mathrm{\dim }\left( L_{\widetilde{\frak{a}_{\perp }}}^{\mu _{%
+\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right) .
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+For $u\in $ $U$ \ perform the following decompositions:
+\begin{equation*}
+u(\mu +\rho )=\pi _{\left( \frak{a}\right) }u(\mu +\rho )+\pi _{\left(
+\widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho )
+\end{equation*}
+\begin{equation*}
+vu(\mu +\rho )-\rho =\pi _{\left( \frak{a}\right) }\left( u(\mu +\rho
+)\right) -\rho +\rho _{\frak{a}_{\perp }}+v\left( \pi _{\left( \widetilde{%
+\frak{a}_{\perp }}\right) }u(\mu +\rho )-\rho _{\frak{a}_{\perp }}+\rho _{%
+\frak{a}_{\perp }}\right) -\rho _{\frak{a}_{\perp }}
+\end{equation*}
+Use these formulas to decompose the anomalous element $\Psi _{\frak{g}}^{\mu
+}$ of the module $L_{\frak{g}}^{\mu }$ into the linear combination of
+anomalous elements $\Psi _{\widetilde{\frak{a}_{\perp }}}^{\eta }$ of the
+subalgebra $\widetilde{\frak{a}_{\perp }}$-modules $L_{\widetilde{\frak{a}%
+_{\perp }}}^{\eta }$:
+\begin{equation*}
+\begin{array}{l}
+\Psi _{\frak{g}}^{\mu }=\sum_{v\in W_{\frak{a}_{\perp }}}\sum_{u\in
+U}\epsilon (v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\frak{a}}\left( u(\mu +\rho )\right)
+-\rho +\rho _{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho
+)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}%
+_{\perp }}}= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\frak{a}}\left( u(\mu +\rho )\right) -\pi
+_{\frak{h}_{\perp }}\rho -\pi _{\frak{a}}\rho +\mathcal{D}_{\frak{a}_{\perp
+}}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon (v)e^{v\left( \pi _{\left(
+\widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho )-\rho _{\frak{a}_{\perp
+}}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho \right]
++\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho
+)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\pi _{\frak{h}%
+_{\perp }}\rho -\rho _{\frak{a}_{\perp }}}= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho \right]
++\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }\left[
+u(\mu +\rho )-\rho \right] .-\mathcal{D}_{\frak{a}_{\perp }}+\rho _{\frak{a}%
+_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
+=\sum_{u\in U}\;\epsilon (u)e^{\pi _{\left( \frak{a}\right) }\left[ u(\mu
++\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}\Psi _{\widetilde{%
+\frak{a}_{\perp }}}^{\pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }%
+\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}}
+\end{array}
+\end{equation*}
+Dividing both sides by the Weyl element $R_{\frak{a}_{\perp }}=\prod_{\beta
+\in \Delta _{\frak{a}_{\perp }}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}$ and
+projecting them to the weight space $h_{\frak{a}}^{\ast }$\ we obtain the
+desired relation
+\begin{eqnarray*}
+\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
+\right)  &=&\sum_{u\in W/W_{\frak{a}_{\perp }}}\;\epsilon (u)e^{\pi _{\frak{a%
+}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}\pi _{%
+\frak{a}}\left( \frac{\Psi _{\widetilde{\frak{a}_{\perp }}}^{\pi _{\left(
+\widetilde{\frak{a}_{\perp }}\right) }\left[ u(\mu +\rho )-\rho \right] -%
+\mathcal{D}_{\frak{a}_{\perp }}}}{\prod_{\beta \in \Delta _{\frak{a}_{\perp
+}}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}}\right)  \\
+&=&\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\frak{a}%
+_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right)
+e^{\mu _{\frak{a}}\left( u\right) }.
+\end{eqnarray*}
+\end{proof}
+
+\begin{remark}
+This relation is a kind of a generalization of the Weyl formula for singular
+element $\Psi _{\frak{g}}^{\mu }$ : the vectors $\mu _{\frak{a}}\left(
+u\right) $ play the role of singular weights while the determinants $%
+\epsilon (u)$ are changed for $\epsilon (u)\mathrm{\dim }\left( L_{%
+\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left(
+u\right) }\right) .$ In fact when $\frak{a=g}$ both $\frak{a}_{\perp }$ and $%
+\frak{h}_{\perp }$ are trivial, $U=W$ , and\ the original Weyl formula is
+easily reobtained.
+\end{remark}
+Now we can state the main theorem which gives us the instrument for the
+recurrent computation of the branching coefficients.
 \begin{theorem}
@@
   \end{equation}
+
+ As we have mentioned above (see (\ref{eq:21}) and (\ref
+{eq:21-1})) when $\zeta \in \bar{C}_{\frak{a}}$ the coefficients $k_{\zeta
+}^{(\mu )}$ coinside with the branching coefficients thus the
+equation for $k_{\zeta }^{(\mu )}$ serve as recurrent relations for branching coefficients.
 \begin{proof}
-    Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
-    projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
-    \begin{equation*}
-      % \label{eq:3}
-      L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
-        }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
-      \Longrightarrow\quad
-      \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
-      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
-    \end{equation*}
-    The Weyl-Kac character formula leads to
-    the relation
+To proof the theorem return to the relation (\ref{eq:4}) and rewrite it for the element $\quad
+\frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}$ ,
+\begin{eqnarray*}
+\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
+\right)  &=&\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot
+}^{+}}\left( 1-e^{-\pi _{\frak{a}}\alpha }\right) ^{\mathrm{mult}(\alpha )-%
+\mathrm{mult}_{\frak{a}}(\pi _{\frak{a}}\alpha )}\left( \sum_{\nu \in P_{%
+\frak{a}}^{+}}b_{\nu }^{(\mu )}\sum_{\omega \in W_{\frak{a}}}\epsilon
+(\omega )e^{\omega (\nu +\rho _{\frak{a}})-\rho _{\frak{a}}}\right) = \\
+&=&-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}s(\gamma )e^{-\gamma
+}\left( \sum_{\nu \in P_{\frak{a}}^{+},\omega \in W_{\frak{a}}}\epsilon
+(\omega )b_{\nu }^{(\mu )}e^{\omega (\nu +\rho _{\frak{a}})-\rho _{\frak{a}%
+}}\right).
+\end{eqnarray*}
+Then decompose the last sum (with respect to the formal basis in $\mathcal{E}$%
+):
+\begin{equation*}
+\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
+\right) =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}s(\gamma
+)e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}k_{\nu }^{(\mu )}e^{\lambda
+}=-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{%
+\frak{a}}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
+\end{equation*}
+Substitute the expression obtained in the Lemma (in the left-hand side),
+\begin{eqnarray*}
+\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
+\right)  &=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\frak{a}}\left( \mu _{\frak{a%
+}}\left( u\right) \right) }\dim \left( L_{\widetilde{\frak{a}_{\perp }}%
+}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right)
+\label{anom modules 2} \\
+&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
+\right] }\dim \left( L_{\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{%
+\frak{a}_{\perp }}}\left( u\right) }\right)  \\
+&=&-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{%
+\frak{a}}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma },
+\end{eqnarray*}
+Equate the coefficients of exponents in the last equality to get the following result:
 \begin{equation}
-      \label{eq:4}
-      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
-        {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
-      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
-        e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
-      {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
+\sum_{u\in U}\epsilon (u)\dim \left( L_{\widetilde{\frak{a}_{\perp }}}^{\mu
+_{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right) \delta _{\xi ,\pi _{%
+\frak{a}}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\frak{a}%
+\subset \frak{g}}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
+\frak{a}}.  \label{eq:17}
 \end{equation}
-
-    Consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and
-    its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
-    with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
-    can be written as
-    \begin{equation*}
-      % \label{eq:41}
-      ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}=
-      \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega)
-        e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}
-      {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
-    \end{equation*}
-    Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$
-    is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$
-    with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
-    since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
-
-    Using this property we can consider the restriction
-    $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
-    that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
-    Multiply the equation (\ref{eq:4}) by the element
-    \begin{equation*}
-      % \label{eq:5}
-      \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}
-        (1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
-    \end{equation*}
-    and take into account that the projection commutes with the multiplication:
-    \begin{eqnarray*}
-      \label{eq:7}
-      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-      \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
-    \end{eqnarray*}
-    Rewriting this relation in terms of the anomalous branching coefficients (\ref{eq:21}) and simplifying the first factor we get
-    \begin{eqnarray*}
-      \label{eq:12}
-      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-      \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
-      \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
-    \end{eqnarray*}
-
-    If the set $\Delta^{+}_{\bot}$ is nonempty then the Weyl reflections corresponding to the
-    positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}\subset W$.
-    Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in
-    W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$
-    such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
-    \begin{equation}
-      \label{eq:13}
-      \begin{array}{c}
-        \fl \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
-          {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-        = \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
-          \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}
-          {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right).
-      \end{array}
-    \end{equation}
-    The fraction in the right-hand side of the equation looks like the character of some  $\mathfrak{a}_{\bot}$-module.
-    Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and
-    $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$,
-    we can rewrite the shifted weights
-    \begin{equation*}
-      \label{eq:30}
-      \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}
-      (\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}
-      +\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho,
-    \end{equation*}
-
-    \begin{eqnarray*}
-      \label{eq:14}
-      \fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu)
-        e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
-      =\\
-      \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}
-      \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot
-          (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})
-          -\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
-      =\\
-      \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}
-      e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
-        -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}.
-    \end{eqnarray*}
-    The projector $\pi_{\mathfrak{a}}$ sends the character
-    ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$
-    to the unit element of $\cal{E}$ multiplied by
-    ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ :
-    \begin{eqnarray*}
-      \label{eq:15}
-      \fl    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
-        e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch}
-        L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-      = \\
-      \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
-      \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
-          -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}.
-    \end{eqnarray*}
-    Thus we obtain the relation
-    \begin{equation}
-      \label{eq:9}
-      \begin{array}{c}
-        \fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
-        \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
-        \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
-      \end{array}
-    \end{equation}
-    Rewriting the factor in the right-hand side in terms of formal elements as in the definition \ref{fan-definition}
-    \begin{eqnarray*}
-      \label{eq:16}
-      \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
-      = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
-      k_{\lambda }^{\left( \mu \right) }e^{\lambda } =\\
-      =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda
-        \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma },
-    \end{eqnarray*}
-    we get the following property of the anomalous branching coefficients,
-    \begin{equation}
-      \label{eq:17}
-      \begin{array}{c}
-        \fl \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}
-        \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
-            -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-        \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-        \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\;
-        k^{(\mu)}_{\xi+\gamma}=0;
-        \\
-        \xi\in P_{\mathfrak{a}}.
-      \end{array}
-    \end{equation}
-
-    Using the definition \ref{fan-definition} we finally get the recurrent relation
-    \begin{eqnarray*}
-      k_{\xi }^{\left( \mu \right) }=
-      -\frac{1}{s\left( \gamma _{0}\right) }
-      \left(
-        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}
-        \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-      \right.\\
-      \left. +
-        \sum_{\gamma \in \Gamma _{\frak{a}\subset \frak{g}}} s\left( \gamma +\gamma _{0}\right) k_{\xi+\gamma }^{\left( \mu \right) }
-      \right),
-    \end{eqnarray*}
+The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
+for $\gamma \in \Phi _{\frak{a}\subset \frak{g}}$ are not independent, they
+are subject to the linear relations and the form of these relations changes
+when the tested weight $\xi $ coinsides with one of \ the ''anomalous
+weights'', $\left\{ \pi _{\frak{a}}\left[ u(\mu +\rho )-\rho \right] |u\in
+U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
+}\subset \frak{g}}$ and pass to the summation over the vectors of the
+injection fan $\Gamma _{\frak{a}\subset \frak{g}}$ (see the definition \ref
+{fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
 \end{proof}
 \end{theorem}
-\begin{corollary}
-  Since $b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu}\;\mbox{for}\;\nu\in \bar{C_{\mathfrak{a}}}$ the recurrent relation gives the values of the branching coefficients inside the main Weyl chamber.
-\end{corollary}
-\begin{corollary}
-  Consider the case  $\Delta_{\bot}^{+} = 0$. There are three different reasons for $\Delta_{\bot}^{+}$
-to be empty: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$,
-ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
-Both the first and the second cases can be treated as corresponding to the trivial orthogonal subalgebra:
-$\mathfrak{a}_{\bot}=0$. In any of these cases the formal characters in the right-hand side of (\ref{eq:13})
-are reduced to the element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$.
-In the first two cases the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
+\subsection{Embeddings and orthogonal pairs in simple Lie algebras}
+
+In this subsection we discuss some properties of ''orthogonal pairs'' of
+subalgebras in simple Lie algebras of classical series.
+
+When both $\frak{g}$ and $\frak{a}$ are finite-dimensional all the regular
+embeddings can be obtained by a successive elimination of nodes in the
+extended Dynkin diagram of $\frak{g}$ (and $\Delta _{\bot }^{+}=\emptyset $
+if $\frak{a}$ is maximal). For the classical series $A$, $C$ and $D$ when
+the regular injection $\frak{a}\rightarrow \frak{g}$ is thus fixed, the
+Dynkin diagram for $\frak{a}_{\bot }$ is obtained from the extended diagram
+of $\frak{g}$ by eliminating the subdiagram of $\frak{a}$ and the adjacent
+nodes:
+\begin{table}[tbh]
+\label{tab:diagrams} \noindent \centering{\
+\begin{tabular}{|l|l|l|l|}
+\hline
+$\frak{g}$ & Extended diagram of $\frak{g}$ & Diagrams of the subalgebras $%
+\frak{a},\; \frak{a}_{\bot}$ &  \\ \hline
+$A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps}
+&  \\ \hline
+$B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps}
+&  \\ \hline
+$C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps}
+&  \\ \hline
+$D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps}
+&  \\ \hline
+\end{tabular}
+}
+\caption{Subalgebras $\frak{a},\;\frak{a}_{\bot }$ for the classical series}
+\end{table}
+(drop the case B)
+
+In the case of $B$ series the situation is different. The reason is that
+here the subalgebra $\frak{a}_{\bot }$ may be larger than the one obtained
+by elimination of the subdiagram of $\frak{a}$ and the adjacent nodes. The
+subalgebras of the orthogonal pair,$\ \frak{a}$ and $\frak{a}_{\bot }$, must
+not form a direct sum in $\frak{g}$ . It can be directly
+checked that when $\frak{g}=B_{r}$ and $\frak{a}=B_{r_{\frak{a}}}$ the
+orthogonal subalgebra is $\frak{a}_{\bot }=B_{r-r_{\frak{a}}}$. Consider the
+injection $B_{r_{\frak{a}}}\rightarrow B_{r},\quad 1<r_{\frak{a}}<r$ . By
+eliminating the simple root $\alpha _{r_{\frak{a}}-1}=e_{r_{\frak{a}%
+}-1}-e_{r_{\frak{a}}}$ one splits the extended Dynkin diagram of $B_{r}$
+into the disjoint diagrams for $\frak{a}=B_{r_{\frak{a}}}$ and $D_{r-r_{%
+\frak{a}}}$. But the system $\Delta _{\frak{a}_{\perp }}$ contains not only
+the simple roots $\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots ,e_{r_{\frak{a}%
+}-2}-e_{r_{\frak{a}}-1},e_{1}+e_{2}\right\} $ but also the root $e_{r_{\frak{%
+a}}-1}$. Thus $\Delta _{\frak{a}_{\perp }}$ forms the subsystem of the type $%
+B_{r-r_{\frak{a}}}$ and the orthogonal pair for the injection $B_{r_{\frak{a}%
+}}\rightarrow B_{r}$ is $\left( B_{r_{\frak{a}}},B_{r-r_{\frak{a}}}\right) $%
+. In the next Section the particular case of such orthogonal pair is
+presented for the injection $B_{2}\rightarrow B_{4}$ (see Figure \ref
+{fig:dynkin}).
+
+The complete classification of regular subalgebras for affine Lie algebras
+can be found in the recent paper \cite{1751-8121-41-36-365204}. From the complete
+classification of maximal special subalgebras in classical Lie algebras \cite
+{dynkin1952semisimple} we can deduce the following list of pairs of
+orthogonal subalgebras $\frak{a},\;\frak{a}_{\bot }$:
+\begin{equation*}
+\begin{array}{lll}
+su(p)\oplus su(q) & \subset su(pq) &  \\
+so(p)\oplus so(q) & \subset so(pq) &  \\
+sp(2p)\oplus sp(2q) & \subset so(4pq) &  \\
+sp(2p)\oplus so(q) & \subset sp(2pq) &  \\
+so(p)\oplus so(q) & \subset so(p+q) & \mathrm{{for}\;p\;{and}\;q\;{odd}.}
+\end{array}
+\end{equation*}
+
+\subsection{Algorithm for recursive computation of branching coefficients}
+
+\label{sec:algorithm}
+
+The recurrent relation (\ref{recurrent-relation}) allows us to formulate an
+algorithm for recursive computation of branching coefficients. In this
+algorithm there is no need to construct the module $L^{(\mu)}_{\frak{g}}$ or
+any of the modules $L^{(\nu)}_{\frak{a}}$.
+
+It contains the following steps:
+
+\begin{enumerate}
+\item  Construct the root subsystem $\Delta _{\frak{a}}$ for the embedding $%
+\frak{a}\rightarrow \frak{g}$.
+
+\item  Select the positive roots $\alpha \in \Delta ^{+}$ orthogonal to the
+roots in $\Delta _{\frak{a}}$ i.e. form the set $\Delta _{\bot }^{+}$.
+
+\item  Construct the set $\Gamma _{\frak{a}\rightarrow \frak{g}}$ (\ref
+{fan-defined}).
+
+\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ \omega (\mu +\rho
+)-\rho ;\;\omega \in W\right\} $ of the anomalous weights for the $\frak{g}$%
+-module $L^{(\mu )}$.
+
+\item  Select the weights $\left\{ \mu _{\widetilde{\frak{a}_{\perp }}%
+}\left( w\right) =\pi _{\widetilde{\frak{a}_{\perp }}}\left[ w(\mu +\rho
+)-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}\in \overline{C_{\widetilde{%
+\frak{a}_{\perp }}}}\right\} $. Since the set $\Delta _{\bot }^{+}$ is fixed
+we can easily check wether the weight $\mu _{\widetilde{\frak{a}_{\perp }}%
+}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
+\frak{a}_{\perp }}}}$ (by computing its scalar product with the roots from $%
+\Delta _{\bot }^{+}$).
+
+\item  For the weights $\mu _{\widetilde{\frak{a}_{\perp }}}\left( w\right) $
+calculate the dimensions of the corresponding modules $\mathrm{\dim }\left(
+L_{\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}%
+}\left( u\right) }\right) $.
+
+\item  Calculate the anomalous branching coefficients in the main Weyl
+chamber $\overline{C_{\frak{a}}}$ of the subalgebra $\frak{a}$ using the
+recurrent relation (\ref{recurrent-relation}).
+\end{enumerate}
+
+When being interested in the branching coefficients for the embedding of the
+finite-dimensional Lie algebra into the affine Lie algebra we can construct
+the set of the anomalous weights up to the required grade and use the steps
+4-7 of the algorithm for each grade. We can also speed up the algorithm by
+one-time computation of the representatives of the conjugate classes $%
+W/W_{\bot }$.
+
+The next section contains examples illustrating the application of this
+algorithm.
+
+%%  
+%%  
+%%  
+%%  
+%%  
+%%  We consider an injection of affine Lie algebras $\frak{a}\longrightarrow \frak{g%
+%%  }$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$.
+%%  In this section we deduce the general recurrent relation (\ref{eq:1}) for the anomalous branching coefficients (\ref{eq:21}).
+This relation is then used to formulate the practical computational algorithm (Subsection \ref{sec:algorithm}).
+%%  In the earlier paper \cite{ilyin812pbc} the following limited setup was considered: $\mathfrak{a}$ was required to be the maximal subalgebra of $\mathfrak{g}$ so that no zeros arrive in the Weyl denominator $R$.
+Here we raise this limitation and study the general case $\mathfrak{a}\subset\mathfrak{g}$.
+%%  
+%%  \subsection{Some definitions}
+%%  \label{sec:some-definitions}
+%%  
+%%  We need to introduce several additional definitions and state some technical results to formulate and prove the recurrent relation (\ref{eq:1}).
+%%  
+%%  \begin{definition}
+%%    Denote by $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\mathfrak{a}} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$.
+%%  \end{definition}
+%%  
+%%  \begin{definition}
+%%    Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
+%%  \end{definition}
+%%  \begin{mynote}
+%%    The subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\mathfrak{a}}$.
+%%  \end{mynote}
+%%  \begin{definition}
+%%    The subsystem $\Delta_{\bot}=\Delta^{+}_{\bot}\cup \left(-\delta^{+}_{\bot}\right)$ determines the subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
+%%  \end{definition}
+%%  
+%%  We need to know when the subset $\Delta^{+}_{\bot}$ is non-empty and $W_{\bot},\mathfrak{a}_{\bot}$ are non-trivial. So we state several simple lemmas.
+%%  
+%%  For the simple finite-dimensional Lie algebras $\ao,\go$ all the regular embeddings can be obtained by the successive elimination of the nodes in the extended Dynkin diagram of $\go$.
+This leads to the lemma
+%%  \begin{lemma}
+%%    For the regular embedding $\ao\subset \go$ 
+%%    \renewcommand{\theenumi}{\alph{enumi}}
+%%    \begin{enumerate}
+%%    \item $\Delta^{+}_{\bot}=\emptyset$ if $\ao$ is maximal
+%%    \item If the extended Dynkin diagram of $\go$ contains the disconnected subdiagrams of $\ao$ and some subalgebras $\left\{\co{\mathfrak{a}_j}\right\}$ then $\Delta^{+}_{\bot}\neq \emptyset$ and $\co{\mathfrak{a}_j}\subset \mathfrak{a}_{\bot}$.
+%%    \end{enumerate}
+%%  \end{lemma}
+%%  \begin{mynote}
+%%    The complete classification of the regular subalgebras for affine Lie algebras can be
+%%    found in the recent paper \cite{1751-8121-41-36-365204}.
+%%  \end{mynote}
+%%  \begin{mynote}
+%%    $\mathfrak{a}_{\bot}$ may be larger than the algebra $\bigoplus_j \co{\mathfrak{a}_j}$.
+%%  \end{mynote}
+%%  Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
+%%  In this case by eliminating
+%%  the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
+%%  into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
+%%  sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal to $B_2$
+%%  (the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).
+%%  
+%%  Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$
+%%  must not form a direct sum in $\mathfrak{g}$.
+%%  Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both
+%%  algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a
+%%  subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
+%%  Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with
+%%  the remaining nodes of the diagram of $\mathfrak{g}$. The result is the diagram of
+%%  the algebra $\bar{\mathfrak{a}}$ with $\mathrm{rank}(\bar{\mathfrak{a}}) =
+%%  \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that
+%%  $\bar{\mathfrak{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether
+%%  $\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\bar{\mathfrak{a}}$
+%%  but the linear combinations of them. The answer is positive  when the set of angles
+%%  between the roots of $\bar{\mathfrak{a}}$ does not contain all the angles between
+%%  the roots of $\mathfrak{a}$.
+%%  Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional
+%%  roots of $\mathfrak{a}_{\bot}$.
+%%  Case-by-case analysis illustrated by the table \ref{tab:diagrams} leads us to the following lemma.
+%%  
+%%  \begin{table}[h!tb]
+%%  \label{tab:diagrams}
+%%  \noindent  \centering{
+%%  \begin{tabular}{|l|l|l|l|}
+%%    \hline
+%%    $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ &
+%%    Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
+%%    \hline
+%%    $A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps} \\
+%%    \hline
+%%    $B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps} \\
+%%    \hline
+%%    $C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps} \\
+%%    \hline
+%%    $D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps} \\
+%%    \hline
+%%  \end{tabular}
+%%  \caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
+%%  \end{table}
+%%  
+%%  \begin{lemma}
+%%    \renewcommand{\theenumi}{\alph{enumi}}
+%%    \begin{enumerate}
+%%    \item If $\go,\ao\neq B_r$ the Dynkin diagram of $\mathfrak{a}_{\bot}$ is obtained from the extended Dynkin diagram of $\go$ by dropping the subdiagram of $\ao$ and the adjacent nodes
+%%    \item If $\go=B_r$ and $\ao=B_{r_{\mathfrak{a}}}$ then $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
+%%    \end{enumerate}
+%%  \end{lemma}
+%%  The complete classification of maximal special subalgebras in classical Lie algebras
+%%  \cite{dynkin1952semisimple} allows us to formulate
+%%  \begin{lemma}
+%%    For the special embeddings there exist the following set of pairs of orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$:
+%%  \begin{equation*}
+%%  %  \label{eq:42}
+%%    \begin{array}{lll}
+%%        su(p)\oplus su(q) & \subset su(pq) &\\
+%%        so(p)\oplus so(q) & \subset so(pq) &\\
+%%        sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
+%%        sp(2p)\oplus so(q) & \subset sp(2pq)&\\
+%%        so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}.\\
+%%    \end{array}
+%%  \end{equation*}
+%%  \end{lemma}
+%%  We are almost ready to state and prove the recurrent relation for the anomalous branching coefficients.
+%%  \begin{definition}
+%%    \label{fan-definition}
+%%    For affine $\mathfrak{a}\subset\mathfrak{g}$ expand the product
+%%    \begin{equation*}
+%%      \label{eq:6}
+%%      \prod_{\alpha\in \Delta^{+}\setminus\Delta^{+}_{\bot}}
+%%      \left(1-e^{-\pi_{\mathfrak{a}}\alpha}\right)^{
+%%          \mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\pi_{\mathfrak{a}}\alpha)}=
+%%        -\sum_{\gamma\in P_{\mathfrak{a}}}e^{-\gamma}
+%%    \end{equation*}
+%%    Denote by $\Phi_{\mathfrak{a}\subset\mathfrak{g}}\subset P_{\mathfrak{a}}$ the carrier of the coefficient function $s(\gamma)$. 
+%%    \begin{equation*}
+%%      \label{eq:37}
+%%      \Phi_{\mathfrak{a}\subset\mathfrak{g}}=\left\{\gamma\in P_{\mathfrak{a}}|s(\gamma)\neq 0\right\}
+%%    \end{equation*}
+%%  
+%%    The ordering of roots in $\co{\Delta_{\mathfrak{a}}}$ induce the natural ordering on the weights of $\mathfrak{a}$.
+Denote by $\gamma_0$ the lowest vector of $    \Phi_{\mathfrak{a}\subset\mathfrak{g}}$ according to this ordering.
+%%    The set 
+%%    \begin{equation}
+%%      \Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+%%          \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
+%%      \label{fan-defined}
+%%    \end{equation}
+%%    is called the {\it injection fan}.
+%%  \end{definition}
+%%  
+%%  \subsection{Proof of the recurrent relation}
+%%  \label{sec:proof}
+%%  First we prove the lemma
+%%  \begin{lemma}
+%%  Denote by $\mathcal{D}=\rho_{\af_{\bot}}-\pi_{\mathfrak{a}_{\bot}}\rho$ the difference between the Weyl vector of orthogonal subalgebra $\af_{\bot}$ and the projection of the Weyl vector of the algebra $\mathfrak{g}$.
+Then
+%%  the quotient of the singular weights element $\Psi^{(\mu)}$ by the denominator $R_{\af_{\bot}}$ is given by the formal element corresponding to the modified set of the singular weights of $L_{\af\oplus\mathfrak{h}_d}^{(\pi_{\af\oplus\mathfrak{h}_d}\mu)}$ with the multiplicities given by the dimensions of $\af_{\bot}$-modules.
+%%  \begin{equation*}
+%%    \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\prod_{\alpha\in \Delta^{+}_{\bot}}\left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=
+%%      \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{\af\oplus\mathfrak{h}_d}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \mathrm{ch}_{\af_{\bot}}
+%%        L^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}
+%%  \end{equation*}
+%%  \begin{proof}
+%%    Consider $\Psi^{(\mu)}_{\mathfrak{g}}$. It is given by the sum over the Weyl group.
+%%    \begin{equation*}
+%%      \Psi^{(\mu)}_{\mathfrak{g}}=\sum_{w\in W}\epsilon(w)e^{w(\mu+\rho)-\rho}
+%%    \end{equation*}
+%%    We can divide the summation to the sum over $W_{\bot}$ and sum over all the classes of $W/W_{\bot}$: $w=vu,\; v\in W_{\bot},\; u \in W/W_{\bot}$.
+We have the following obvious property of the projections:
+%%    \begin{equation*}
+%%      \label{eq:5}
+%%      u(\mu+\rho)=\pia(u(\mu+\rho))+\piab(u(\mu+\rho))+\pi_{(\mathfrak{h}\setminus
+%%        (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}))^*}(u(\mu+\rho))
+%%    \end{equation*}
+%%    Let's denote $\mathfrak{h}\setminus (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}})$ by $\mathfrak{h}_d$,
+%%    $\mathfrak{h}=\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}+\mathfrak{h}_d$. Since $\mathfrak{h}_{\af}^*,\mathfrak{h}_d^*$ are invariant under the action of $v\in W_{\bot}$, we have
+%%    \begin{equation*}
+%%      \begin{array}{cc}
+%%        vu(\mu+\rho)-\rho & = v\cdot(\piab(u(\mu+\rho))-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}+\\
+%%        & \pia(u(\mu+\rho))-\rho+\rho_{\afb}+
+%%        \pi_{\mathfrak{h}_d^*}(u(\mu+\rho))
+%%      \end{array}
+%%    \end{equation*}
+%%   Only the first term depends on $v$. So
+%%    \begin{equation*}
+%%      \begin{array}{cc}
+%%      \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\mathrm{R}_{\afb}}= &
+%%      \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\mathfrak{h}_d^*}(u(\mu+\rho))}\cdot\\
+%%  
+%%      &\cdot\frac{
+%%        \sum_{v\in W_{\bot}}\epsilon(v)e^{v(\piab u(\mu+\rho)-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}}}{\mathrm{R}_{\afb}}
+%%    \end{array}
+%%  \end{equation*}
+%%    We can rewrite the r.h.s. as
+%%    \begin{equation*}
+%%      \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{(\af\oplus\mathfrak{h}_d)}\left[u(\mu+\rho)-\rho\right]+\pi_{(\af\oplus \mathfrak{h}_d)}\cdot \rho-\rho+\rho_{\afb}}\cdot
+%%      \mathrm{ch}_{\afb}L^{\pi_{\afb}u(\mu+\rho)-\rho_{\afb}}.
+%%    \end{equation*}
+%%    Since $\pi_{\afb}(u(\mu+\rho)-\rho)-(\rho_{\afb}-\pi_{\afb}\rho)=\pi_{\afb}(u(\mu+\rho)-\rho)-\mathcal{D}$ and $\pi_{(\af\oplus\mathfrak{h}_d)}\rho-\rho=-\pi_{\afb}\rho$ we get the statement of the Lemma.
+%%  
+%%  \end{proof}
+%%  \end{lemma}
+%%  
+%%  \begin{theorem}
+%%    For the anomalous branching coefficients (\ref{eq:21}) holds the recurrent relation
+%%    \begin{equation}
+%%      \label{eq:1}
+%%      \label{recurrent-relation}
+%%      \begin{array}{c}
+%%        k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+%%          \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
+%%          {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+%%          \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
+%%        \left.
+%%          +\sum_{\gamma \in
+%%            \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+%%            +\gamma }^{\left( \mu \right) }\right).
+%%      \end{array}
+%%    \end{equation}
+%%    \begin{proof}
+%%      Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
+%%      projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
+%%      \begin{equation*}
+%%        % \label{eq:3}
+%%        L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
+%%          }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
+%%        \Longrightarrow\quad
+%%        \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
+%%        \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
+%%      \end{equation*}
+%%      The Weyl-Kac character formula leads to
+%%      the relation
+%%      \begin{equation}
+%%        \label{eq:4}
+%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
+%%          {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
+%%        \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
+%%        \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
+%%          e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
+%%        {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
+%%      \end{equation}
+%%  
+%%      Consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and
+%%      its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
+%%      with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
+%%      can be written as
+%%      \begin{equation*}
+%%        % \label{eq:41}
+%%        ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}=
+%%        \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega)
+%%          e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}
+%%        {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
+%%      \end{equation*}
+%%      Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$
+%%      is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$
+%%      with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
+%%      since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
+%%  
+%%      Using this property we can consider the restriction
+%%      $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
+%%      that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
+%%      Multiply the equation (\ref{eq:4}) by the element
+%%      \begin{equation*}
+%%        % \label{eq:5}
+%%        \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}
+%%          (1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
+%%      \end{equation*}
+%%      and take into account that the projection commutes with the multiplication:
+%%      \begin{eqnarray*}
+%%        \label{eq:7}
+%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+%%        \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
+%%        \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
+%%      \end{eqnarray*}
+%%      Rewriting this relation in terms of the anomalous branching coefficients (\ref{eq:21}) and simplifying the first factor we get
+%%      \begin{eqnarray*}
+%%        \label{eq:12}
+%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+%%        \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
+%%        \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
+%%      \end{eqnarray*}
+%%  
+%%      If the set $\Delta^{+}_{\bot}$ is nonempty then the Weyl reflections corresponding to the
+%%      positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}\subset W$.
+%%      Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in
+%%      W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$
+%%      such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
+%%      \begin{equation}
+%%        \label{eq:13}
+%%        \begin{array}{c}
+%%          \fl \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
+%%            {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+%%          = \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
+%%            \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}
+%%            {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right).
+%%        \end{array}
+%%      \end{equation}
+%%      The fraction in the right-hand side of the equation looks like the character of some  $\mathfrak{a}_{\bot}$-module.
+%%      Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and
+%%      $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$,
+%%      we can rewrite the shifted weights
+%%      \begin{equation*}
+%%        \label{eq:30}
+%%        \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}
+%%        (\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}
+%%        +\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho,
+%%      \end{equation*}
+%%  
+%%      \begin{eqnarray*}
+%%        \label{eq:14}
+%%        \fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu)
+%%          e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
+%%        =\\
+%%        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}
+%%        \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot
+%%            (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})
+%%            -\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
+%%        =\\
+%%        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}
+%%        e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+%%          -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}.
+%%      \end{eqnarray*}
+%%      The projector $\pi_{\mathfrak{a}}$ sends the character
+%%      ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$
+%%      to the unit element of $\cal{E}$ multiplied by
+%%      ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ :
+%%      \begin{eqnarray*}
+%%        \label{eq:15}
+%%        \fl    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
+%%          e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch}
+%%          L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+%%        = \\
+%%        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
+%%        \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+%%            -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}.
+%%      \end{eqnarray*}
+%%      Thus we obtain the relation
+%%      \begin{equation}
+%%        \label{eq:9}
+%%        \begin{array}{c}
+%%          \fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+%%          \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
+%%          \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
+%%        \end{array}
+%%      \end{equation}
+%%      Rewriting the factor in the right-hand side in terms of formal elements as in the definition \ref{fan-definition}
+%%      \begin{eqnarray*}
+%%        \label{eq:16}
+%%        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+%%        = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
+%%        k_{\lambda }^{\left( \mu \right) }e^{\lambda } =\\
+%%        =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda
+%%          \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma },
+%%      \end{eqnarray*}
+%%      we get the following property of the anomalous branching coefficients,
+%%      \begin{equation}
+%%        \label{eq:17}
+%%        \begin{array}{c}
+%%          \fl \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}
+%%          \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+%%              -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+%%          \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+%%          \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\;
+%%          k^{(\mu)}_{\xi+\gamma}=0;
+%%          \\
+%%          \xi\in P_{\mathfrak{a}}.
+%%        \end{array}
+%%      \end{equation}
+%%      
+%%      Using the definition \ref{fan-definition} we finally get the recurrent relation
+%%      \begin{eqnarray*}
+%%        k_{\xi }^{\left( \mu \right) }=
+%%        -\frac{1}{s\left( \gamma _{0}\right) }
+%%        \left(
+%%          \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}
+%%          \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+%%          \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+%%        \right.\\
+%%        \left. +
+%%          \sum_{\gamma \in \Gamma _{\frak{a}\subset \frak{g}}} s\left( \gamma +\gamma _{0}\right) k_{\xi+\gamma }^{\left( \mu \right) }
+%%        \right),
+%%      \end{eqnarray*}
+%%  \end{proof}
+%%  \end{theorem}
+%%  \begin{corollary}
+%%    Since $b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu}\;\mbox{for}\;\nu\in \bar{C_{\mathfrak{a}}}$ the recurrent relation gives the values of the branching coefficients inside the main Weyl chamber.
+%%  \end{corollary}
+%%  \begin{corollary}
+%%    Consider the case  $\Delta_{\bot}^{+} = 0$. There are three different reasons for $\Delta_{\bot}^{+}$
+%%  to be empty: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$,
+%%  ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
+%%  Both the first and the second cases can be treated as corresponding to the trivial orthogonal subalgebra:
+%%  $\mathfrak{a}_{\bot}=0$. In any of these cases the formal characters in the right-hand side of (\ref{eq:13})
+%%  are reduced to the element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$.
+%%  In the first two cases the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
 It is clear that in any of the three variants the final vector $\pi_{\mathfrak{a}}\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)$ leads to the unit of the formal algebra
-$\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty the  recurrent relation is simplified:
-\begin{equation*}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
-\left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
-\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
-+\gamma }^{\left( \mu \right) }\right),  \label{recurrent relation special}
-\end{equation*}
-the latter coincides with the one obtained in \cite{ilyin812pbc} (formula (16)).
-\end{corollary}
-\subsection{Algorithm for recursive computation of branching coefficients}
-\label{sec:algorithm}
-
-The recurrent relation (\ref{recurrent-relation}) allows us to formulate an algorithm for recursive computation of branching coefficients.
-In this algorithm there is no need to  construct the module $L^{(\mu)}_{\mathfrak{g}}$ or any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
-
-It contains the following steps:
-\begin{enumerate}
-\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{g} \supset \mathfrak{a}$.
-\item Select the positive roots $\alpha\in \Delta^{+}$ orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\Gamma$ (\ref{fan-defined}).
-\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights for the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$.
-Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies
-in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$.
-\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate
-the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
--\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$.
-\item Calculate the anomalous branching coefficients in the main Weyl
-  chamber $\bar{C_{\mathfrak{a}}}$ of the subalgebra $\mathfrak{a}$ using the recurrent relation (\ref{recurrent-relation}).
-\end{enumerate}
-
-When being interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous weights up to the required grade and use the steps 4-7 of the algorithm for each grade.
+%%  $\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty the  recurrent relation is simplified:
+%%  \begin{equation*}
+%%  k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+%%  \sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
+%%  \left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
+%%  \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+%%  +\gamma }^{\left( \mu \right) }\right),  \label{recurrent relation special}
+%%  \end{equation*}
+%%  the latter coincides with the one obtained in \cite{ilyin812pbc} (formula (16)).
+%%  \end{corollary}
+%%  \subsection{Algorithm for recursive computation of branching coefficients}
+%%  \label{sec:algorithm}
+%%  
+%%  The recurrent relation (\ref{recurrent-relation}) allows us to formulate an algorithm for recursive computation of branching coefficients.
+%%  In this algorithm there is no need to  construct the module $L^{(\mu)}_{\mathfrak{g}}$ or any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
+%%  
+%%  It contains the following steps:
+%%  \begin{enumerate}
+%%  \item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{g} \supset \mathfrak{a}$.
+%%  \item Select the positive roots $\alpha\in \Delta^{+}$ orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
+%%  \item Construct the set $\Gamma$ (\ref{fan-defined}).
+%%  \item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights for the $\mathfrak{g}$-module $L^{(\mu)}$.
+%%  \item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$.
+%%  Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies
+%%  in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$.
+%%  \item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate
+%%  the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+%%  -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$.
+%%  \item Calculate the anomalous branching coefficients in the main Weyl
+%%    chamber $\bar{C_{\mathfrak{a}}}$ of the subalgebra $\mathfrak{a}$ using the recurrent relation (\ref{recurrent-relation}).
+%%  \end{enumerate}
+%%  
+%%  When being interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous weights up to the required grade and use the steps 4-7 of the algorithm for each grade.
 We can also speed up the algorithm by one-time computation of the representatives of the conjugate classes $W_{\bot}\backslash W$.
-
-The next section contains examples illustrating the application of this algorithm.
-
+%%  
+%%  The next section contains examples illustrating the application of this algorithm.
+%%  
 \section{Branching for finite dimensional Lie algebras}

### 2010-10-31 GeneralOverview/Lectures/2dqft.tex

@@
 \tableofcontents
-\section{Программа курса}
+
+\section{Лекция 1}
+\label{sec:lecture-1}
+
+\subsection{Программа курса}
 \label{sec:program}
@@
 
-В лекции 3 \ref{sec:lecture-3} мы обсуждаем применение ренормгруппы к описанию критического поведения, более подробно и достаточно педагогически этот вопрос рассматривается в книге \cite{ma1980} (\cite{ma2000modern}).
+В следующих лекциях \ref{sec:lecture-3}, \ref{sec:lecture-4} мы обсуждаем применение ренормгруппы к описанию критического поведения, более подробно и достаточно педагогически этот вопрос рассматривается в книге \cite{ma1980} (\cite{ma2000modern}).
 Исчерпывающую информацию содержит моногорафия \cite{vasiliev1998} (английский вариант \cite{Vasilev:1027193}).
+Лекция \ref{sec:lecture-4} основана на вводной главе обзора \cite{Ravanini:2000st}.
 
 Изложение конформной теории поля в двух измерениях опирается на оригинальную статью \cite{belavin1984ics}, книгу \cite{difrancesco1997cft} и обзор \cite{zamolodchikov1989rus,zamolodchikov1989conformal}, недавно переизданный в виде книги.
-
-\section{Лекция 1}
-\label{sec:lecture-1}
 

### 2010-11-04 AffineLieAlgebras/InformalNotes/article.tex
Figures annotations are improved.

@@
 \newtheorem{statement}{Statement}
-\theoremstyle{definition}
+\newtheorem{theorem}{Theorem}
+%\newtheorem{corollary}{Corollary}[theorem]
 \newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\theoremstyle{definition}
-\newtheorem{corollary}{Corollary}[theorem]
-\theoremstyle{definition}
 \newtheorem{mynote}{Note}[section]
@@
 \newtheorem{definition}{Definition}
-\newtheorem{remark}[theorem]{Remark}
+\newtheorem{remark}{Remark}
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
 \begin{eqnarray}
-\pi _{\frak{a}}\left( \frac{\sum_{\omega \in W}\epsilon (\omega )e^{\omega
+\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w
 (\mu +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{%
 mult}(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}%
-\frac{\sum_{\omega \in W_{\frak{a}}}\epsilon (\omega )e^{\omega (\nu +\rho _{%
+\frac{\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{%
 \frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
@@
 Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
-reflections $\omega _{\beta }$ for the roots $\beta \in \Delta _{\frak{a}%
+reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\frak{a}%
 _{\perp }}^{+}$ . The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
@@
       k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
-        {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
+        \sum_{w\in W_{\bot}\backslash W} \epsilon(w)\;
+        {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(w(\mu+\rho)-\rho)}+ \right.\\
       \left.
@@
 \begin{proof}
-To proof the theorem return to the relation (\ref{eq:4}) and rewrite it for the element $\quad
+To prove the theorem return to the relation (\ref{eq:4}) and rewrite it for the element $\quad
 \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}$ ,
@@
 \mathrm{mult}_{\frak{a}}(\pi _{\frak{a}}\alpha )}\left( \sum_{\nu \in P_{%
-\frak{a}}^{+}}b_{\nu }^{(\mu )}\sum_{\omega \in W_{\frak{a}}}\epsilon
-(\omega )e^{\omega (\nu +\rho _{\frak{a}})-\rho _{\frak{a}}}\right) = \\
+\frak{a}}^{+}}b_{\nu }^{(\mu )}\sum_{w \in W_{\frak{a}}}\epsilon
+(w )e^{w (\nu +\rho _{\frak{a}})-\rho _{\frak{a}}}\right) = \\
 &=&-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}s(\gamma )e^{-\gamma
-}\left( \sum_{\nu \in P_{\frak{a}}^{+},\omega \in W_{\frak{a}}}\epsilon
-(\omega )b_{\nu }^{(\mu )}e^{\omega (\nu +\rho _{\frak{a}})-\rho _{\frak{a}%
+}\left( \sum_{\nu \in P_{\frak{a}}^{+},w \in W_{\frak{a}}}\epsilon
+(w )b_{\nu }^{(\mu )}e^{w (\nu +\rho _{\frak{a}})-\rho _{\frak{a}%
 }}\right).
@@
 &  \\ \hline
-$B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps}
-&  \\ \hline
 $C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps}
@@
 \end{table}
-(drop the case B)
 
@@
 
-\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ \omega (\mu +\rho
-)-\rho ;\;\omega \in W\right\} $ of the anomalous weights for the $\frak{g}$%
+\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
+)-\rho ;\;w \in W\right\} $ of the anomalous weights for the $\frak{g}$%
 -module $L^{(\mu )}$.
@@
 %%  \begin{definition}
-%%    Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
+%%    Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $w_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
 %%  \end{definition}
@@
 %%        k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-%%          \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
-%%          {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-%%          \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
+%%          \sum_{w\in W_{\bot}\backslash W} \epsilon(w)\;
+%%          {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+%%          \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(w(\mu+\rho)-\rho)}+ \right.\\
 %%        \left.
@@
 %%        \label{eq:4}
-%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
+%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}
 %%          {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
 %%        \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-%%        \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
-%%          e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
+%%        \frac{\sum_{w\in W_{\mathfrak{a}}}\epsilon(w)
+%%          e^{w(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
 %%        {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
@@
 %%        ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}=
-%%        \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega)
-%%          e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}
+%%        \frac{\sum_{w\in W_{\bot}} \epsilon(w)
+%%          e^{w(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}
 %%        {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
@@
 %%        \label{eq:7}
-%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
 %%        \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-%%        \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
+%%        \frac{\sum_{w\in W_{\mathfrak{a}}}\epsilon(w)e^{w(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
 %%      \end{eqnarray*}
@@
 %%        \label{eq:12}
-%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
+%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
 %%        \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
@@
 %%      positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}\subset W$.
-%%      Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in
-%%      W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$
-%%      such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
+%%      Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{w}\in
+%%      W_{\bot}\backslash W$ choose the representative $w \in \tilde{w}$
+%%      such that $\pi_{\mathfrak{a}_{\bot}}w(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
 %%      \begin{equation}
@@
 %%        \begin{array}{c}
-%%          \fl \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
+%%          \fl \pi_{\mathfrak{a}}\left(\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}
 %%            {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-%%          = \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
-%%            \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}
+%%          = \pi_{\mathfrak{a}}\left(\sum_{w\in W_{\bot}\backslash W} \epsilon(w)
+%%            \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot w(\mu+\rho)-\rho}}
 %%            {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right).
@@
 %%      The fraction in the right-hand side of the equation looks like the character of some  $\mathfrak{a}_{\bot}$-module.
-%%      Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and
-%%      $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$,
+%%      Since $\nu\cdot \pi_{\mathfrak{a}}(w(\mu+\rho))=\pi_{\mathfrak{a}}(w(\mu+\rho))$ and
+%%      $w(\mu+\rho)-\pi_{\mathfrak{a}}(w(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))$,
 %%      we can rewrite the shifted weights
@@
 %%        \label{eq:30}
-%%        \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}
-%%        (\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}
-%%        +\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho,
+%%        \nu\cdotw(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}
+%%        (w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}
+%%        +\pi_{\mathfrak{a}}(w(\mu+\rho))\bigr)-\rho,
 %%      \end{equation*}
@@
 %%        \label{eq:14}
-%%        \fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu)
-%%          e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
+%%        \fl  \sum_{w\in W_{\bot}\backslash W} \epsilon(w) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu)
+%%          e^{\nu \cdot w(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
 %%        =\\
-%%        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}
+%%        \sum_{w\in W_{\bot}\backslash W} \epsilon(w) e^{\pi_{\mathfrak{a}}(w(\mu+\rho))-\rho}
 %%        \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot
-%%            (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})
+%%            (\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})
 %%            -\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
 %%        =\\
-%%        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}
-%%        e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+%%        \sum_{w\in W_{\bot}\backslash W} \epsilon(w) e^{\pi_{\mathfrak{a}}(w(\mu+\rho))-\rho}
+%%        e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))
 %%          -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}.
@@
 %%      The projector $\pi_{\mathfrak{a}}$ sends the character
-%%      ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$
+%%      ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$
 %%      to the unit element of $\cal{E}$ multiplied by
-%%      ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ :
+%%      ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ :
 %%      \begin{eqnarray*}
 %%        \label{eq:15}
-%%        \fl    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
-%%          e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch}
-%%          L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+%%        \fl    \pi_{\mathfrak{a}}\left( \sum_{w\in W_{\bot}\backslash W} \epsilon(w)
+%%          e^{\pi_{\mathfrak{a}}(w(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch}
+%%          L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
 %%        = \\
-%%        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
-%%        \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
-%%            -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}.
+%%        \sum_{w\in W_{\bot}\backslash W} \epsilon(w)\;
+%%        \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))
+%%            -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(w(\mu+\rho)-\rho)}.
 %%      \end{eqnarray*}
@@
 %%        \begin{array}{c}
-%%          \fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+%%          \fl  \sum_{w\in W_{\bot}\backslash W} \epsilon(w) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(w(\mu+\rho)-\rho)}=\\
 %%          \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
@@
 %%        \label{eq:16}
-%%        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
+%%        \sum_{w\in W_{\bot}\backslash W} \epsilon(w) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(w(\mu+\rho)-\rho)}=\\
 %%        = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
@@
 %%        \begin{array}{c}
-%%          \fl \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}
-%%          \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+%%          \fl \sum_{w\in W_{\bot}\backslash W} \epsilon(w) \mathrm{dim}
+%%          \left(L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))
 %%              -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-%%          \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+%%          \delta_{\xi,\pi_{\mathfrak{a}}(w(\mu+\rho)-\rho)}+
 %%          \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\;
@@
 %%        \left(
-%%          \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}
-%%          \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-%%          \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
+%%          \sum_{w\in W_{\bot}\backslash W} \epsilon(w)\; \mathrm{dim}
+%%          \left(L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
+%%          \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(w(\mu+\rho)-\rho)}+
 %%        \right.\\
@@
 %%  $\mathfrak{a}_{\bot}=0$. In any of these cases the formal characters in the right-hand side of (\ref{eq:13})
-%%  are reduced to the element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$.
-%%  In the first two cases the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
-It is clear that in any of the three variants the final vector $\pi_{\mathfrak{a}}\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)$ leads to the unit of the formal algebra
+%%  are reduced to the element $e^{ \pi_{\mathfrak{a}_{\bot}}w(\mu+\rho)}$.
+%%  In the first two cases the vector $w(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
+It is clear that in any of the three variants the final vector $\pi_{\mathfrak{a}}\pi_{\mathfrak{a}_{\bot}}w(\mu+\rho)$ leads to the unit of the formal algebra
 %%  $\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty the  recurrent relation is simplified:
@@
 %%  \item Construct the set $\Gamma$ (\ref{fan-defined}).
-%%  \item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights for the $\mathfrak{g}$-module $L^{(\mu)}$.
-%%  \item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$.
+%%  \item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{w(\mu+\rho)-\rho;\; w\in W\right\}$ of the anomalous weights for the $\mathfrak{g}$-module $L^{(\mu)}$.
+%%  \item Select the weights $\left\{ \lambda=w(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$.
 %%  Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies
 %%  in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$.
-%%  \item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate
-%%  the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
+%%  \item For $\lambda=w(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate
+%%  the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))
 %%  -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$.
@@
 Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors in the Figure \ref{fig:B2_A1}.
-We denote the corresponding Weyl reflections by $\omega_1, \omega_2$.
+We denote the corresponding Weyl reflections by $w_1, w_2$.
 The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
 
-Let's describe the reduction of the fundamental representation $L^{(1,0)=w_1}_{B_2}$ (the black vector in Figure \ref{fig:B2_A1}).
-\begin{figure}[th]
+\begin{figure}[p]
   \noindent\centering{
@@
   }
-  \caption{Regular embedding of $A_1$ into $B_2$}
+  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
+    The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is shown by the black vector.
+    The weights of the singular element $\Psi^{(\omega_1)}$ are indicated by the circles and the corresponding determinants $\epsilon(w)$ are shown.}
   \label{fig:B2_A1}
-\end{figure}
-Circles indicate the weights of the singular element $\Psi^{(w_1)}$.
-Now we are to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$
-and to construct the set $\left\{\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W\right\}$.
-\begin{figure}[t]
+
+%\end{figure}
+%\begin{figure}[pb]
   \noindent\centering{
@@
   }
-  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules for the embedding $A_1\subset B_2$}
+  \caption{Regular embedding $A_1\subset B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
+    The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is shown by the black vector.
+$\mathfrak{a}_{\bot}=A_1$-modules built on the weights of the singular element $\Psi^{(\omega_1)}$ are shown by dotted lines.
+The dimensions of these modules and the signs of the corresponding determinants $\epsilon(w)$ are shown near the anomalous weights.
+Fundamental weight coordinate of $\mathfrak{a}=A_1$ is indicated on the weight subspace of $\mathfrak{a}$.
+}
   \label{fig:B2_A1_2}
 \end{figure}
+
+Let's describe the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ (the black vector in Figure \ref{fig:B2_A1}).
+
+Circles indicate the weights of the singular element $\Psi^{(\omega_1)}$.
+Now we are to factorise the Weyl group $W$ by $W_{\bot}=\left\{w_1\right\}$
+and to construct the set $\left\{w(\mu+\rho)-\rho,\; w\in W_{\bot}\backslash W\right\}$.
 In the Figure \ref{fig:B2_A1_2} the weights of the corresponding
 $\left(\mathfrak{a}_{\bot}=A_1\right)$-modules
-$L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$
+$L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$
 are indicated. Projecting them onto the root space of the subalgebra $\mathfrak{a}=A_1$
@@
   \includegraphics[width=50mm]{figure3.eps}
-  \caption{The regular embedding $B_2\subset B_4$ described by dropping the node.}
+  \caption{The regular embedding $B_2\subset B_4$ described by dropping the node from the Dynkin diagram.
+Note, that $\mathfrak{a}_{\bot}$ is equal to $B_2$, not to $A_1\oplus A_1$ seen at the diagram.}
   \label{fig:dynkin}
+\end{figure}
+
+\begin{figure}[pt]
+  \centering
+    \includegraphics[width=100mm,height=90mm]{figure4.eps}
+  \caption{Projected singular weights of $-\frac{1}{s(\gamma_0)}\pi_{B_2}\left(\hat \Psi^{(0,1,0,2)}_{B_4}\right)$
+  with the dimensions of the corresponding $\mathfrak{a}_{\bot}=B_2$-modules.}
+  \label{fig:B4B2anom}
+
+%\end{figure}
+%
+%\begin{figure}[pb]
+  \centering
+  \includegraphics[height=80mm]{figure5.eps}
+  \caption{The fan $\Gamma_{B_2\subset B_4}$ for $B_2\subset B_4$. The values $s(\gamma+\gamma_0)$ are shown in the corresponding weights $\gamma$.}
+  \label{fig:B4B2Fan}
 \end{figure}
@@
 is the set of positive roots for the algebra $\mathfrak{a}_{\bot}=B_2$.
-\begin{figure}[t]
-  \centering
-    \includegraphics[width=100mm,height=90mm]{figure4.eps}
-  \caption{Projected weights $-\frac{1}{s(\gamma_0)}\pi_{B_2}\left(\hat \Psi^{(0,1,0,2)}_{B_4}\right)$
-  with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
-  \label{fig:B4B2anom}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \includegraphics[height=80mm]{figure5.eps}
-  \caption{The fan for $B_2\subset B_4$}
-  \label{fig:B4B2Fan}
-\end{figure}
+
 Using the definition (\ref{fan-defined}) we obtain the fan
@@
 and compute the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.
-The set of the anomalous weights $\left\{ \omega(\mu+\rho)-\rho,\; \omega\in W\right\}$
+The set of the anomalous weights $\left\{ w(\mu+\rho)-\rho,\; w\in W\right\}$
 contains 384 vectors.
 
-We are to select the weights $\psi \in \omega(\mu+\rho)$  with the property
+We are to select the weights $\psi \in w(\mu+\rho)$  with the property
 $\pi_{\mathfrak{a}_{\bot}} \left(  \psi \right) \in \bar{C}^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$.
@@
   \includegraphics[width=135mm]{figure6.eps}
-  \caption{The fan and $s(\gamma+\gamma_0)$ for $\hat{A_1}\longrightarrow \hat{A_2}$}
+
+  \caption{The fan $\Gamma_{\hat{A_1}\longrightarrow \hat{A_2}}$ for $\hat{A_1}\longrightarrow \hat{A_2}$.
+Values of  $s(\gamma+\gamma_0)$ are shown for the weights $\gamma\in \Gamma_{\hat{A_1}\longrightarrow \hat{A_2}}$}
   \label{fig:AffineA2A1Fan}
@@
 
-Let us consider the module $L^{w_0=(0,0;1;0)}$. Here we use the (finite part; level; grade)
+Let us consider the module $L^{\omega_0=(0,0;1;0)}$. Here we use the (finite part; level; grade)
 presentation of the highest weight and the finite part
@@
 
-The set $\widehat{\Psi^{(w_0)}}$  is depicted in the Figure
+The set $\widehat{\Psi^{(\omega_0)}}$  is depicted in the Figure
 \ref{fig:affine_A2_anom_point} up to the sixth grade.
-The weights $\omega (w_0+\rho)-\rho$ are marked by crosses when $\epsilon(\omega)=1$ and
-by diamond when $\epsilon(\omega)=-1$. Simple roots of the classical subalgebra $A_2$ are
-grey and the grey diagonal plane corresponds to the Cartan subalgebra of
-the embedded algebra $\hat{A}_1$.
 
@@
   \includegraphics[width=140mm]{figure7.eps}
-  \caption{The anomalous weights of the module $L^{(0,0;1;0)}_{\hat{A_2}}$}
+  \caption{The anomalous weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$. The weights $w (\omega_0+\rho)-\rho$ are marked by crosses when $\epsilon(w)=1$ and
+by diamond when $\epsilon(w)=-1$. Simple roots of the classical subalgebra $A_2$ are
+grey and the grey diagonal plane corresponds to the Cartan subalgebra of
+the embedded algebra $\hat{A}_1$.}
   \label{fig:affine_A2_anom_point}
@@
   \includegraphics[width=130mm]{figure8.eps}
-  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$.}
+  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$. The multiplicities of projected weights and the corresponding signs are shown. }
   \label{fig:AffineA2_A1_anom_proj}
@@
   \includegraphics[width=130mm]{figure9.eps}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$. The boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
+ are indicated by the black lines. Two nonzero anomalous weights in the main Weyl chamber are marked by stars. Both weights have multiplicity 1, so the branching coefficients are equal to 1.}
   \label{fig:AffineA2_A1_branching}
@@
   \includegraphics[width=135mm]{figure10.eps}
-  \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
+  \caption{The fan $\Gamma_{\hat{A_1}\longrightarrow \hat{B_2}}$ for $\hat{A_1}\longrightarrow \hat{B_2}$.
+Values of  $s(\gamma+\gamma_0)$ are shown for the weights $\gamma\in \Gamma_{\hat{A_1}\longrightarrow \hat{B_2}}$}
   \label{fig:AffineB2A1Fan}
@@
 
-Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $w_1=(1,0;1;0)$,
+Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $\omega_1=(1,0;1;0)$,
 where the finite part coordinates are in the orthogonal basis $e_1,e_2$.
@@
 the classical Lie algebras $A_1\subset B_2$ that can be seen in the  Figure \ref{fig:B2_A1}.
-The weights $\omega (w_1+\rho)-\rho$ are marked by crosses if $\epsilon(\omega)=1$ and by circles otherwise.
-Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
-of the embedded algebra $\hat{A}_1$.
 
@@
   \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$.
-  The weights in the zero grade can be seen in the Figure \ref{fig:B2_A1}}.
+  The weights in the zero grade can be seen in the Figure \ref{fig:B2_A1}. The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by circles otherwise.
+Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
+of the embedded algebra $\hat{A}_1$.}
   \label{fig:affine_B2_anom_point}
@@
 $P_{\hat{A_1}}$ and find the dimensions of the corresponding
-$\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+$\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
 The result is presented in the Figure
@@
   \includegraphics[width=120mm]{figure12.eps}
-  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$ and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$.
+The dimensions of the corresponding $\mathfrak{a}_{\bot}=A_1$-modules with the signs $\epsilon(w)$ are shown.}
   \label{fig:AffineB2_A1_anom_proj}
@@
   \includegraphics[width=120mm]{figure13.eps}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$.  The boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
+ are indicated by the black lines. The anomalous branching coefficients inside the main Weyl chamber are equal to the branching coefficients of the embedding $\hat{A_1}\longrightarrow \hat{B_2}$.}
   \label{fig:AffineB2_A1_branching}
@@
   \label{eq:28}
-  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}\oplus 1 L_{\hat{A_1}}^{w_0}\oplus 4 L_{\hat{A_1}}^{w_0-\delta}\oplus\\
-    2 L_{\hat{A_1}}^{w_1-\delta}\oplus 8 L_{\hat{A_1}}^{w_0-2\delta}\oplus
-    8 L_{\hat{A_1}}^{w_1-2\delta}\oplus 15 L_{\hat{A_1}}^{w_0-3\delta}\oplus\\
-    12 L_{\hat{A_1}}^{w_1-3\delta}\oplus 26 L_{\hat{A_1}}^{w_1-4\delta}\oplus
-    29 L_{\hat{A_1}}^{w_0-4\delta}\oplus 51 L_{\hat{A_1}}^{w_0-5\delta}\oplus\\
-    42 L_{\hat{A_1}}^{w_1-5\delta}\oplus 78 L_{\hat{A_1}}^{w_1-6\delta}\oplus
-    85 L_{\hat{A_1}}^{w_0-6\delta}\oplus 120 L_{\hat{A_1}}^{w_1-7\delta}\oplus\\
-    139 L_{\hat{A_1}}^{w_0-7\delta}\oplus 202 L_{\hat{A_1}}^{w_1-8\delta}\oplus
-    222 L_{\hat{A_1}}^{w_0-8\delta}\oplus 306 L_{\hat{A_1}}^{w_1-9\delta}\oplus\\
-    346 L_{\hat{A_1}}^{w_0-9\delta}\oplus 530 L_{\hat{A_1}}^{w_0-10\delta}\oplus
-    482 L_{\hat{A_1}}^{w_1-10\delta}\oplus 714 L_{\hat{A_1}}^{w_1-11\delta}\oplus\\
-    797 L_{\hat{A_1}}^{w_0-11\delta}\oplus 1080 L_{\hat{A_1}}^{w_1-12\delta}\oplus
-    1180 L_{\hat{A_1}}^{w_0-12\delta}\oplus \dots
+  L^{\omega_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{\omega_1}\oplus 1 L_{\hat{A_1}}^{\omega_0}\oplus 4 L_{\hat{A_1}}^{\omega_0-\delta}\oplus\\
+    2 L_{\hat{A_1}}^{\omega_1-\delta}\oplus 8 L_{\hat{A_1}}^{\omega_0-2\delta}\oplus
+    8 L_{\hat{A_1}}^{\omega_1-2\delta}\oplus 15 L_{\hat{A_1}}^{\omega_0-3\delta}\oplus\\
+    12 L_{\hat{A_1}}^{\omega_1-3\delta}\oplus 26 L_{\hat{A_1}}^{\omega_1-4\delta}\oplus
+    29 L_{\hat{A_1}}^{\omega_0-4\delta}\oplus 51 L_{\hat{A_1}}^{\omega_0-5\delta}\oplus\\
+    42 L_{\hat{A_1}}^{\omega_1-5\delta}\oplus 78 L_{\hat{A_1}}^{\omega_1-6\delta}\oplus
+    85 L_{\hat{A_1}}^{\omega_0-6\delta}\oplus 120 L_{\hat{A_1}}^{\omega_1-7\delta}\oplus\\
+    139 L_{\hat{A_1}}^{\omega_0-7\delta}\oplus 202 L_{\hat{A_1}}^{\omega_1-8\delta}\oplus
+    222 L_{\hat{A_1}}^{\omega_0-8\delta}\oplus 306 L_{\hat{A_1}}^{\omega_1-9\delta}\oplus\\
+    346 L_{\hat{A_1}}^{\omega_0-9\delta}\oplus 530 L_{\hat{A_1}}^{\omega_0-10\delta}\oplus
+    482 L_{\hat{A_1}}^{\omega_1-10\delta}\oplus 714 L_{\hat{A_1}}^{\omega_1-11\delta}\oplus\\
+    797 L_{\hat{A_1}}^{\omega_0-11\delta}\oplus 1080 L_{\hat{A_1}}^{\omega_1-12\delta}\oplus
+    1180 L_{\hat{A_1}}^{\omega_0-12\delta}\oplus \dots
 \end{eqnarray*}
@@
   \begin{array}{cc}
-    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
+    b^{(\omega_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
      &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
@@
   \begin{array}{cc}
-    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
+    b^{(\omega_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
     & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
@@
 to their highest weights in $P^+_{\hat{A_1}}$.
-These are the fundamental weights $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
+These are the fundamental weights $\omega_0=\lambda_0=(0,1,0),\; \omega_1=\alpha/2=(1,1,0)$.
 
@@
   \begin{array}{cc}
-    \chi^{(w_1)}_{1}(q)= & q^{\frac{7}{12}}\left( 2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\right. \\
+    \chi^{(\omega_1)}_{1}(q)= & q^{\frac{7}{12}}\left( 2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\right. \\
     & \left. 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots \right)\\
-    \chi^{(w_1)}_{0}(q) = & q^{\frac{5}{6}}\left(1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\right. \\
+    \chi^{(\omega_1)}_{0}(q) = & q^{\frac{5}{6}}\left(1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\right. \\
     &\left. 222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\right)

### 2010-11-04 AffineLieAlgebras/InformalNotes/article.tex
Slight notation change, theorem numbering

--- 2010-10-01 AffineLieAlgebras/InformalNotes/article.tex
@@
 \newtheorem{statement}{Statement}
+\newtheorem{theorem}{Theorem}
+%\newtheorem{corollary}{Corollary}[theorem]
 \newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\theoremstyle{definition}
-\newtheorem{corollary}{Corollary}[theorem]
-\theoremstyle{definition}
 \newtheorem{mynote}{Note}[section]
@@
 \newtheorem{definition}{Definition}
+\newtheorem{remark}{Remark}
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
 
-Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
+Consider affine Lie algebras $\frak{g}$ and $\af$ with the
 underlying finite-dimensional subalgebras $\go$ and $%
-\ao$ and an injection $\frak{a}\longrightarrow \frak{g%
-}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
-correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
+\ao$ and an injection $\af\longrightarrow \frak{g%
+}$ such that $\af$ is a reductive subalgebra $\frak{a\subset g}$ with
+correlated root spaces: $\frak{h}_{\af}^{\ast }\subset \frak{h}_{\frak{g%
 }}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
@@
 
-$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
-of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
+$L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
+of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\af$
 -module with the highest weight $\nu $ );
 
-$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
-\left( \mbox{resp. }\frak{a}\right) $ ;
-
-$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
-^{+} $ $\left( \mbox{resp. }\Delta _{\frak{a}}^{+}\right) $--- the positive
-root system (of $\frak{g}$ and $\frak{a}$ respectively);
-
-$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
+$r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\frak{g}$ $%
+\left( \mbox{resp. }\af\right) $ ;
+
+$\Delta $ $\left( \Delta _{\af}\right) $--- the root system; $\Delta
+^{+} $ $\left( \mbox{resp. }\Delta _{\af}^{+}\right) $--- the positive
+root system (of $\frak{g}$ and $\af$ respectively);
+
+$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\af}\left(
 \alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $\Delta
-$ (resp. in $\left( \Delta _{\frak{a}}\right) $);
-
-$\co{\Delta}$ , $\left( \co{\Delta _{\frak{a}}}%
+$ (resp. in $\left( \Delta _{\af}\right) $);
+
+$\co{\Delta}$ , $\left( \co{\Delta _{\af}}%
 \right)$ --- the finite root system of the subalgebra $\co{%
-\frak{g}}$ (resp. $\co{\frak{a}}$);
+\frak{g}}$ (resp. $\co{\af}$);
 $\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);
 
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ --- the
-weight diagram of $L^{\mu }$ $\left( \mbox{resp. }L_{\frak{a}}^{\nu }\right)
+$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\af}^{\nu }\right) $ --- the
+weight diagram of $L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right)
 $ ;
 
-$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
-
-$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
+$W$ , $\left( W_{\af}\right) $--- the corresponding Weyl group;
+
+$C$ , $\left( C_{\af}\right) $--- the fundamental Weyl chamber;
 
@@
 
-$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
+$\rho $\ , $\left( \rho _{\af}\right) $\ --- the Weyl vector;
 
@@
 
-$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $i
-$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\frak{a}%
-\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
-
-$\delta $ --- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);
-
-$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
-}\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\frak{a}%
-\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
-
-$\co{\xi }$ , $\co{\xi _{\left( \frak{a}\right) }}$
+$\alpha _{i}$ , $\left( \alpha _{\left( \af\right) j}\right) $ --- the $i
+$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\af%
+\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
+
+$\delta $ --- the imaginary root of $\frak{g}$ (and of $\af$ if any);
+
+$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \af\right) j}^{\vee
+}\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\af%
+\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
+
+$\co{\xi }$ , $\co{\xi _{\left( \af\right) }}$
 --- the finite (classical) part of the weight $\xi \in P$ , $\left( \mbox{%
-resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $;
+resp. }\xi _{\left( \af\right) }\in P_{\af}\right) $;
 
@@
 
-$P$ $\left( \mbox{resp. } P_{\frak{a}}\right) $ \ --- the weight lattice;
-
-$M \left( \mbox{resp. }M_{\frak{a}}\right) :=$
+$P$ $\left( \mbox{resp. } P_{\af}\right) $ \ --- the weight lattice;
+
+$M \left( \mbox{resp. }M_{\af}\right) :=$
 
@@
 \sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\mbox{ }\left( \mbox{resp. }%
-\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \frak{a}\right) i}^{\vee }\right)
+\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \af\right) i}^{\vee }\right)
 \mbox{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
 \sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\mbox{ }\left( \mbox{resp. }\sum_{i=1}^{r}%
-\mathbf{Z}\alpha _{\left( \frak{a}\right) i}\right) \mbox{for }A_{r}^{\left(
+\mathbf{Z}\alpha _{\left( \af\right) i}\right) \mbox{for }A_{r}^{\left(
 u\geq 2\right) }\mbox{ and }A\neq A_{2r}^{\left( 2\right) },
@@
 $\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
-$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}}}\epsilon (w)e^{w\circ (\nu +\rho
-_{_{\frak{a}}})-\rho _{_{\frak{a}}}}$ --- the corresponding singular weight
-element for the $\frak{a}$-module $L_{\frak{a}}^{\nu }$;
+$\Psi _{\left( \af\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho
+_{_{\af}})-\rho _{_{\af}}}$ --- the corresponding singular weight
+element for the $\af$-module $L_{\af}^{\nu }$;
 
@@
 a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
-\xi \in P$ $\left( \mbox{resp. }\in P_{\frak{a}}\right) $ for the module $%
-L^{\mu }$ $\left( \mbox{resp. }L_{\frak{a}}^{\nu }\right) $ with the
+\xi \in P$ $\left( \mbox{resp. }\in P_{\af}\right) $ for the module $%
+L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right) $ with the
 coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
@@
 }\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mbox{%
-resp. }\in P_{\frak{a}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
-L_{\frak{a}}^{\nu } $);
-
-$ch\left( L^{\mu }\right) $ $\left( \mbox{resp. }ch\left( L_{\frak{a}}^{\nu
+resp. }\in P_{\af}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
+L_{\af}^{\nu } $);
+
+$ch\left( L^{\mu }\right) $ $\left( \mbox{resp. }ch\left( L_{\af}^{\nu
 }\right) \right) $--- the formal character of $L^{\mu }$ $\left( \mbox{resp. }%
-L_{\frak{a}}^{\nu }\right) $;
+L_{\af}^{\nu }\right) $;
 
@@
 
-\noindent $\left( \mbox{resp. }R_{\frak{a}}:=\prod_{\alpha \in \Delta _{%
-\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{%
-\left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $--- the
+\noindent $\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
+\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
+\left( \alpha \right) }}=\Psi _{\af}^{\left( 0\right) }\right) $--- the
 denominator;
 
-$ L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus
-\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$
- --- the module decomposition with respect to $\frak{a}\longrightarrow \frak{g}$;
+$ L_{\frak{g}\downarrow \af}^{\mu }=\bigoplus
+\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }$
+ --- the module decomposition with respect to $\af\longrightarrow \frak{g}$;
 
@@
   \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
-        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
+        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\af}}k_{\lambda
   }^{\left( \mu \right) }e^{\lambda };
@@
 
-\section{Recurrent relation for branching coefficients. Singularities and subtractions}
+\section{Recurrent relation for branching coefficients.}
 \label{sec:recurr-form-branch}
 
-We consider an injection of affine Lie algebras $\frak{a}\longrightarrow \frak{g%
-}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$.
-In this section we deduce the general recurrent relation (\ref{eq:1}) for the anomalous branching coefficients (\ref{eq:21}).
-This relation is then used to formulate the practical computational algorithm (Subsection \ref{sec:algorithm}).
-In the earlier paper \cite{ilyin812pbc} the following limited setup was considered: $\mathfrak{a}$ was required to be the maximal subalgebra of $\mathfrak{g}$ so that no zeros arrive in the Weyl denominator $R$.
-Here we raise this limitation and study the general case $\mathfrak{a}\subset\mathfrak{g}$.
-
-\subsection{Some definitions}
-\label{sec:some-definitions}
-
-We need to introduce several additional definitions and state some technical results to formulate and prove the recurrent relation (\ref{eq:1}).
+Let $\af\subset \frak{g}$ be a regular subalgebra of $\frak{g.}$
+Applying the Weyl-Kac character formula to the branching rule $\pi _{\af%
+}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu
+)}ch\left( L_{\af}^{\nu }\right) $ we get the relation connecting the
+singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{\left( \af%
+\right) }^{\left( \nu \right) }$ :
+\begin{eqnarray}
+\pi _{\af}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w
+(\mu +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{%
+mult}(\alpha )}}\right) &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}%
+\frac{\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{%
+\af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
+}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\af}(\beta )}},  \label{eq:4} \\
+\pi _{\af}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
+&=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\left( \frak{%
+a}\right) }^{\left( \nu \right) }}{R_{\af}}.
+\end{eqnarray}
+where according to our notations $\Delta _{\af}^{+}$ is the set of
+positive roots of the subalgebra $\af$ (it is convenient to choose them
+from the positive root subspace of $\frak{g}$). Consider the root space $%
+\frak{h}_{\perp \af}^{\ast }$ orthogonal to $\Delta _{\af}$,
+\begin{equation*}
+\frak{h}_{\perp \af}^{\ast }=:\left\{ \eta \in \frak{h}_{\frak{g}%
+}^{\ast }|\forall \alpha \in \Delta _{\af};\alpha \bot \eta \right\} ,
+\end{equation*}
+and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
+to $\Delta _{\af}$,
+\begin{eqnarray*}
+\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
+\alpha \in \Delta _{\af};\alpha \bot \beta \right\} , \\
+\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
+}^{+}|\forall \alpha ^{+}\in \Delta _{\af}^{+};\alpha ^{+}\bot \beta
+^{+}\right\} .
+\end{eqnarray*}
+Let $W_{\af_{\perp }}$ be the subgroup of $W$ generated by the
+reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\af%
+_{\perp }}^{+}$ . The subsystem $\Delta _{\af_{\perp }}$ determines the
+subalgebra $\af_{\perp }$ with the Cartan subalgebra $\frak{h}_{\af%
+_{\perp }}$. Let
+\begin{equation*}
+\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
+}|\forall \alpha \in \Delta _{\af}\cup \Delta _{\af_{\perp
+}};\alpha \bot \eta \right\}
+\end{equation*}
+and consider the subalgebras
+\begin{eqnarray*}
+\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
+\\
+\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
+\end{eqnarray*}
+
+The algebras $\af$ and $\af_{\perp }$ form an ''orthogonal pair''
+of subalgebras in $\frak{g}$. For the Cartan subalgebras we have the
+decomposition
+\begin{equation}
+\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\af_{\perp }}\oplus
+\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
+\af_{\perp }}=\frak{\frak{h}_{\widetilde{\af_{\perp }}}}\oplus
+\frak{h}_{\af}.
+\end{equation}
+For the subalgebras of the orthogonal pair $\left( \af,\af_{\perp
+}\right) $ we consider the corresponding Weyl vectors, $\rho _{\af}$
+and $\rho _{\af_{\perp }}$ , and\ form the so called ''defects'' $%
+\mathcal{D}_{\af}$ and $\mathcal{D}_{\af_{\perp }}$ of the
+injection:
+\begin{equation}
+\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
+\end{equation}
+\begin{equation}
+\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi _{\af%
+_{\perp }}\rho .
+\end{equation}
+For the highest weight module $L_{\frak{g}}^{\mu }$ consider the singular
+weights $\left( w(\mu +\rho )-\rho \right) \in \widehat{\Psi ^{\left( \mu
+\right) }}$ and their projections to $h_{\widetilde{\af_{\perp }}%
+}^{\ast }$ (additionally shifted by $-\mathcal{D}_{\af_{\perp }}$):
+\begin{equation*}
+\mu _{\widetilde{\af_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
+a}_{\perp }}}\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp
+}},\quad w\in W.
+\end{equation*}
+Among the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right)
+|_{w\in W}$ choose those located in the fundamental chamber $\overline{C_{%
+\widetilde{\af_{\perp }}}}$ and let $U$ be the set of representatives $%
+u $ for the classes $W/W_{\af_{\perp }}$ such that
+
+\begin{equation}
+U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
+\in \overline{C_{\widetilde{\af_{\perp }}}}\right\} \quad .
+\label{U-def}
+\end{equation}
+For the same set $U$ introduce the weights
+\begin{equation*}
+\mu _{\af}\left( u\right) :=\pi _{\af}\left[ u(\mu +\rho )-\rho %
+\right] +\mathcal{D}_{\af_{\perp }}.
+\end{equation*}
+
+To describe the recurrent properties for branching coefficients $b_{\nu
+}^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc} one of the
+main tools of which is the set of weights $\Gamma _{\af\subset \frak{g}%
+} $ called the injection fan. As far as we consider more general situation
+(where the injection is not maximal) the notion of the injection fan is
+modified:
 
 \begin{definition}
-  Denote by $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\mathfrak{a}} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$.
+\label{fan-definition} For the product
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
+_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
+}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
+)e^{-\gamma }  \label{eq:6}
+\end{equation}
+consider the carrier $\Phi _{\af\subset \frak{g}}\subset P_{\af}$
+of the function $s(\gamma )=\det \left( \gamma \right) $ :
+\begin{equation}
+\Phi _{\af\subset \frak{g}}=\left\{ \gamma \in P_{\af}|s(\gamma
+)\neq 0\right\}   \label{eq:37}
+\end{equation}
+The ordering of roots in $\co{\Delta _{\af}}$ induce the
+natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
+the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
+\begin{equation}
+\Gamma _{\af\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
+\label{fan-defined}
+\end{equation}
+is called the \textit{injection fan}.
 \end{definition}
 
-\begin{definition}
-  Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
-\end{definition}
-\begin{mynote}
-  The subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\mathfrak{a}}$.
-\end{mynote}
-\begin{definition}
-  The subsystem $\Delta_{\bot}=\Delta^{+}_{\bot}\cup \left(-\delta^{+}_{\bot}\right)$ determines the subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
-\end{definition}
-
-We need to know when the subset $\Delta^{+}_{\bot}$ is non-empty and $W_{\bot},\mathfrak{a}_{\bot}$ are non-trivial. So we state several simple lemmas.
-
-For the simple finite-dimensional Lie algebras $\ao,\go$ all the regular embeddings can be obtained by the successive elimination of the nodes in the extended Dynkin diagram of $\go$.
-This leads to the lemma
+The main result is that the Weyl-Kac character formula (in terms of singular
+elements) describes the particular case of a more general relation:
+
 \begin{lemma}
-  For the regular embedding $\ao\subset \go$ 
-  \renewcommand{\theenumi}{\alph{enumi}}
-  \begin{enumerate}
-  \item $\Delta^{+}_{\bot}=\emptyset$ if $\ao$ is maximal
-  \item If the extended Dynkin diagram of $\go$ contains the disconnected subdiagrams of $\ao$ and some subalgebras $\left\{\co{\mathfrak{a}_j}\right\}$ then $\Delta^{+}_{\bot}\neq \emptyset$ and $\co{\mathfrak{a}_j}\subset \mathfrak{a}_{\bot}$.
-  \end{enumerate}
+Let $\af$ and $\af_{\perp }$ be the orthogonal pair of regular
+subalgebras in $\frak{g}$, with $\widetilde{\af_{\perp }}=\af%
+_{\perp }\oplus \frak{h}_{\perp }$ and $\widetilde{\af}=\af\oplus
+\frak{h}_{\perp }$ ,
+
+$L_{\frak{g}}^{\mu }$ be the highest weight module with the singular element
+$\Psi _{\frak{g}}^{\mu }$ ,
+
+$R_{\af_{\perp }}$ be the Weyl denominator for $\af_{\perp }$.
+
+Then the element $\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{%
+\af_{\perp }}}\right) $ can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
+the singular elements $e^{\mu _{\af}\left( u\right) }$ with the
+coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
+}}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right) $:
+\begin{equation}
+\quad \pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af%
+_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{\af}\left(
+u\right) }\mathrm{\dim }\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
+\widetilde{\af_{\perp }}}\left( u\right) }\right) .
+\end{equation}
 \end{lemma}
-\begin{mynote}
-  The complete classification of the regular subalgebras for affine Lie algebras can be
-  found in the recent paper \cite{1751-8121-41-36-365204}.
-\end{mynote}
-\begin{mynote}
-  $\mathfrak{a}_{\bot}$ may be larger than the algebra $\bigoplus_j \co{\mathfrak{a}_j}$.
-\end{mynote}
-Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
-In this case by eliminating
-the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
-into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
-sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal to $B_2$
-(the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).
-
-Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$
-must not form a direct sum in $\mathfrak{g}$.
-Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both
-algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a
-subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
-Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with
-the remaining nodes of the diagram of $\mathfrak{g}$. The result is the diagram of
-the algebra $\bar{\mathfrak{a}}$ with $\mathrm{rank}(\bar{\mathfrak{a}}) =
-\mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that
-$\bar{\mathfrak{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether
-$\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\bar{\mathfrak{a}}$
-but the linear combinations of them. The answer is positive  when the set of angles
-between the roots of $\bar{\mathfrak{a}}$ does not contain all the angles between
-the roots of $\mathfrak{a}$.
-Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional
-roots of $\mathfrak{a}_{\bot}$.
-Case-by-case analysis illustrated by the table \ref{tab:diagrams} leads us to the following lemma.
-
-\begin{table}[h!tb]
-\label{tab:diagrams}
-\noindent  \centering{
-\begin{tabular}{|l|l|l|l|}
-  \hline
-  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ &
-  Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
-  \hline
-  $A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps} \\
-  \hline
-  $B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps} \\
-  \hline
-  $C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps} \\
-  \hline
-  $D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps} \\
-  \hline
-\end{tabular}
-\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
-\end{table}
-
-\begin{lemma}
-  \renewcommand{\theenumi}{\alph{enumi}}
-  \begin{enumerate}
-  \item If $\go,\ao\neq B_r$ the Dynkin diagram of $\mathfrak{a}_{\bot}$ is obtained from the extended Dynkin diagram of $\go$ by dropping the subdiagram of $\ao$ and the adjacent nodes
-  \item If $\go=B_r$ and $\ao=B_{r_{\mathfrak{a}}}$ then $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
-  \end{enumerate}
-\end{lemma}
-The complete classification of maximal special subalgebras in classical Lie algebras
-\cite{dynkin1952semisimple} allows us to formulate
-\begin{lemma}
-  For the special embeddings there exist the following set of pairs of orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$:
-\begin{equation*}
-%  \label{eq:42}
-  \begin{array}{lll}
-      su(p)\oplus su(q) & \subset su(pq) &\\
-      so(p)\oplus so(q) & \subset so(pq) &\\
-      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
-      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
-      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}.\\
+
+\begin{proof}
+For $u\in $ $U$ \ perform the following decompositions:
+\begin{equation*}
+u(\mu +\rho )=\pi _{\left( \af\right) }u(\mu +\rho )+\pi _{\left(
+\widetilde{\af_{\perp }}\right) }u(\mu +\rho )
+\end{equation*}
+\begin{equation*}
+vu(\mu +\rho )-\rho =\pi _{\left( \af\right) }\left( u(\mu +\rho
+)\right) -\rho +\rho _{\af_{\perp }}+v\left( \pi _{\left( \widetilde{%
+\af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
+\af_{\perp }}\right) -\rho _{\af_{\perp }}
+\end{equation*}
+Use these formulas to decompose the anomalous element $\Psi _{\frak{g}}^{\mu
+}$ of the module $L_{\frak{g}}^{\mu }$ into the linear combination of
+anomalous elements $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ of the
+subalgebra $\widetilde{\af_{\perp }}$-modules $L_{\widetilde{\af%
+_{\perp }}}^{\eta }$:
+\begin{equation*}
+\begin{array}{l}
+\Psi _{\frak{g}}^{\mu }=\sum_{v\in W_{\af_{\perp }}}\sum_{u\in
+U}\epsilon (v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left( u(\mu +\rho )\right)
+-\rho +\rho _{\af_{\perp }}}\sum_{v\in W_{\af_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{\left( \widetilde{\af_{\perp }}\right) }u(\mu +\rho
+)-\rho _{\af_{\perp }}+\rho _{\af_{\perp }}\right) -\rho _{\af%
+_{\perp }}}= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left( u(\mu +\rho )\right) -\pi
+_{\frak{h}_{\perp }}\rho -\pi _{\af}\rho +\mathcal{D}_{\af_{\perp
+}}}\sum_{v\in W_{\af_{\perp }}}\epsilon (v)e^{v\left( \pi _{\left(
+\widetilde{\af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp
+}}+\rho _{\af_{\perp }}\right) -\rho _{\af_{\perp }}}= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]
++\mathcal{D}_{\af_{\perp }}}\sum_{v\in W_{\af_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{\left( \widetilde{\af_{\perp }}\right) }u(\mu +\rho
+)-\rho _{\af_{\perp }}+\rho _{\af_{\perp }}\right) -\pi _{\frak{h}%
+_{\perp }}\rho -\rho _{\af_{\perp }}}= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]
++\mathcal{D}_{\af_{\perp }}}\sum_{v\in W_{\af_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{\left( \widetilde{\af_{\perp }}\right) }\left[
+u(\mu +\rho )-\rho \right] .-\mathcal{D}_{\af_{\perp }}+\rho _{\af%
+_{\perp }}\right) -\rho _{\af_{\perp }}}= \\
+=\sum_{u\in U}\;\epsilon (u)e^{\pi _{\left( \af\right) }\left[ u(\mu
++\rho )-\rho \right] +\mathcal{D}_{\af_{\perp }}}\Psi _{\widetilde{%
+\af_{\perp }}}^{\pi _{\left( \widetilde{\af_{\perp }}\right) }%
+\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}}
 \end{array}
 \end{equation*}
-\end{lemma}
-We are almost ready to state and prove the recurrent relation for the anomalous branching coefficients.
-\begin{definition}
-  \label{fan-definition}
-  For affine $\mathfrak{a}\subset\mathfrak{g}$ expand the product
-  \begin{equation*}
-    \label{eq:6}
-    \prod_{\alpha\in \Delta^{+}\setminus\Delta^{+}_{\bot}}
-    \left(1-e^{-\pi_{\mathfrak{a}}\alpha}\right)^{
-        \mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\pi_{\mathfrak{a}}\alpha)}=
-      -\sum_{\gamma\in P_{\mathfrak{a}}}e^{-\gamma}
-  \end{equation*}
-  Denote by $\Phi_{\mathfrak{a}\subset\mathfrak{g}}\subset P_{\mathfrak{a}}$ the carrier of the coefficient function $s(\gamma)$. 
-  \begin{equation*}
-    \label{eq:37}
-    \Phi_{\mathfrak{a}\subset\mathfrak{g}}=\left\{\gamma\in P_{\mathfrak{a}}|s(\gamma)\neq 0\right\}
-  \end{equation*}
-
-  The ordering of roots in $\co{\Delta_{\mathfrak{a}}}$ induce the natural ordering on the weights of $\mathfrak{a}$.
-Denote by $\gamma_0$ the lowest vector of $    \Phi_{\mathfrak{a}\subset\mathfrak{g}}$ according to this ordering.
-  The set 
-  \begin{equation}
-    \Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-        \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
-    \label{fan-defined}
-  \end{equation}
-  is called the {\it injection fan}.
-\end{definition}
-
-\subsection{Proof of the recurrent relation}
-\label{sec:proof}
-First we prove the lemma
-\begin{lemma}
-Denote by $\mathcal{D}=\rho_{\af_{\bot}}-\pi_{\mathfrak{a}_{\bot}}\rho$ the difference between the Weyl vector of orthogonal subalgebra $\af_{\bot}$ and the projection of the Weyl vector of the algebra $\mathfrak{g}$.
-Then
-the quotient of the singular weights element $\Psi^{(\mu)}$ by the denominator $R_{\af_{\bot}}$ is given by the formal element corresponding to the modified set of the singular weights of $L_{\af\oplus\mathfrak{h}_d}^{(\pi_{\af\oplus\mathfrak{h}_d}\mu)}$ with the multiplicities given by the dimensions of $\af_{\bot}$-modules.
-\begin{equation*}
-  \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\prod_{\alpha\in \Delta^{+}_{\bot}}\left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=
-    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{\af\oplus\mathfrak{h}_d}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \mathrm{ch}_{\af_{\bot}}
-      L^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}
-\end{equation*}
-\begin{proof}
-  Consider $\Psi^{(\mu)}_{\mathfrak{g}}$. It is given by the sum over the Weyl group.
-  \begin{equation*}
-    \Psi^{(\mu)}_{\mathfrak{g}}=\sum_{w\in W}\epsilon(w)e^{w(\mu+\rho)-\rho}
-  \end{equation*}
-  We can divide the summation to the sum over $W_{\bot}$ and sum over all the classes of $W/W_{\bot}$: $w=vu,\; v\in W_{\bot},\; u \in W/W_{\bot}$.
-We have the following obvious property of the projections:
-  \begin{equation*}
-    \label{eq:5}
-    u(\mu+\rho)=\pia(u(\mu+\rho))+\piab(u(\mu+\rho))+\pi_{(\mathfrak{h}\setminus
-      (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}))^*}(u(\mu+\rho))
-  \end{equation*}
-  Let's denote $\mathfrak{h}\setminus (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}})$ by $\mathfrak{h}_d$,
-  $\mathfrak{h}=\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}+\mathfrak{h}_d$. Since $\mathfrak{h}_{\af}^*,\mathfrak{h}_d^*$ are invariant under the action of $v\in W_{\bot}$, we have
-  \begin{equation*}
-    \begin{array}{cc}
-      vu(\mu+\rho)-\rho & = v\cdot(\piab(u(\mu+\rho))-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}+\\
-      & \pia(u(\mu+\rho))-\rho+\rho_{\afb}+
-      \pi_{\mathfrak{h}_d^*}(u(\mu+\rho))
-    \end{array}
-  \end{equation*}
- Only the first term depends on $v$. So
-  \begin{equation*}
-    \begin{array}{cc}
-    \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\mathrm{R}_{\afb}}= &
-    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\mathfrak{h}_d^*}(u(\mu+\rho))}\cdot\\
-
-    &\cdot\frac{
-      \sum_{v\in W_{\bot}}\epsilon(v)e^{v(\piab u(\mu+\rho)-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}}}{\mathrm{R}_{\afb}}
-  \end{array}
-\end{equation*}
-  We can rewrite the r.h.s. as
-  \begin{equation*}
-    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{(\af\oplus\mathfrak{h}_d)}\left[u(\mu+\rho)-\rho\right]+\pi_{(\af\oplus \mathfrak{h}_d)}\cdot \rho-\rho+\rho_{\afb}}\cdot
-    \mathrm{ch}_{\afb}L^{\pi_{\afb}u(\mu+\rho)-\rho_{\afb}}.
-  \end{equation*}
-  Since $\pi_{\afb}(u(\mu+\rho)-\rho)-(\rho_{\afb}-\pi_{\afb}\rho)=\pi_{\afb}(u(\mu+\rho)-\rho)-\mathcal{D}$ and $\pi_{(\af\oplus\mathfrak{h}_d)}\rho-\rho=-\pi_{\afb}\rho$ we get the statement of the Lemma.
-
+Dividing both sides by the Weyl element $R_{\af_{\perp }}=\prod_{\beta
+\in \Delta _{\af_{\perp }}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}$ and
+projecting them to the weight space $h_{\af}^{\ast }$\ we obtain the
+desired relation
+\begin{eqnarray*}
+\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
+\right)  &=&\sum_{u\in W/W_{\af_{\perp }}}\;\epsilon (u)e^{\pi _{\frak{a%
+}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af_{\perp }}}\pi _{%
+\af}\left( \frac{\Psi _{\widetilde{\af_{\perp }}}^{\pi _{\left(
+\widetilde{\af_{\perp }}\right) }\left[ u(\mu +\rho )-\rho \right] -%
+\mathcal{D}_{\af_{\perp }}}}{\prod_{\beta \in \Delta _{\af_{\perp
+}}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}}\right)  \\
+&=&\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af%
+_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
+e^{\mu _{\af}\left( u\right) }.
+\end{eqnarray*}
 \end{proof}
-\end{lemma}
-
+
+\begin{remark}
+This relation is a kind of a generalization of the Weyl formula for singular
+element $\Psi _{\frak{g}}^{\mu }$ : the vectors $\mu _{\af}\left(
+u\right) $ play the role of singular weights while the determinants $%
+\epsilon (u)$ are changed for $\epsilon (u)\mathrm{\dim }\left( L_{%
+\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left(
+u\right) }\right) .$ In fact when $\frak{a=g}$ both $\af_{\perp }$ and $%
+\frak{h}_{\perp }$ are trivial, $U=W$ , and\ the original Weyl formula is
+easily reobtained.
+\end{remark}
+Now we can state the main theorem which gives us the instrument for the
+recurrent computation of the branching coefficients.
 \begin{theorem}
@@
       k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
-        {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
+        \sum_{w\in W_{\afb}\backslash W} \epsilon(w)\;
+        {\rm dim}\left(L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}\right)
+        \delta_{\xi-\gamma_0,\pi_{\af}(w(\mu+\rho)-\rho)}+ \right.\\
       \left.
         +\sum_{\gamma \in
-          \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+          \Gamma _{\af\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
           +\gamma }^{\left( \mu \right) }\right).
@@
   \end{equation}
+
+ As we have mentioned above (see (\ref{eq:21}) and (\ref
+{eq:21-1})) when $\zeta \in \bar{C}_{\af}$ the coefficients $k_{\zeta
+}^{(\mu )}$ coinside with the branching coefficients thus the
+equation for $k_{\zeta }^{(\mu )}$ serve as recurrent relations for branching coefficients.
 \begin{proof}
-    Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
-    projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
-    \begin{equation*}
-      % \label{eq:3}
-      L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
-        }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
-      \Longrightarrow\quad
-      \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
-      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
-    \end{equation*}
-    The Weyl-Kac character formula leads to
-    the relation
-    \begin{equation}
-      \label{eq:4}
-      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
-        {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
-      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
-        e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
-      {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
-    \end{equation}
-
-    Consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and
-    its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
-    with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
-    can be written as
-    \begin{equation*}
-      % \label{eq:41}
-      ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}=
-      \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega)
-        e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}
-      {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
-    \end{equation*}
-    Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$
-    is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$
-    with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
-    since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
-
-    Using this property we can consider the restriction
-    $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
-    that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
-    Multiply the equation (\ref{eq:4}) by the element
-    \begin{equation*}
-      % \label{eq:5}
-      \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}
-        (1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
-    \end{equation*}
-    and take into account that the projection commutes with the multiplication:
+To prove the theorem return to the relation (\ref{eq:4}) and rewrite it for the element $\quad
+\frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ ,
 \begin{eqnarray*}
-      \label{eq:7}
-      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-      \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
-      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
+\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
+\right)  &=&\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot
+}^{+}}\left( 1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-%
+\mathrm{mult}_{\af}(\pi _{\af}\alpha )}\left( \sum_{\nu \in P_{%
+\af}^{+}}b_{\nu }^{(\mu )}\sum_{w \in W_{\af}}\epsilon
+(w )e^{w (\nu +\rho _{\af})-\rho _{\af}}\right) = \\
+&=&-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma )e^{-\gamma
+}\left( \sum_{\nu \in P_{\af}^{+},w \in W_{\af}}\epsilon
+(w )b_{\nu }^{(\mu )}e^{w (\nu +\rho _{\af})-\rho _{\af%
+}}\right).
 \end{eqnarray*}
-    Rewriting this relation in terms of the anomalous branching coefficients (\ref{eq:21}) and simplifying the first factor we get
+Then decompose the last sum (with respect to the formal basis in $\mathcal{E}$%
+):
+\begin{equation*}
+\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
+\right) =-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
+)e^{-\gamma }\sum_{\lambda \in P_{\af}}k_{\nu }^{(\mu )}e^{\lambda
+}=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
+\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
+\end{equation*}
+Substitute the expression obtained in the Lemma (in the left-hand side),
 \begin{eqnarray*}
-      \label{eq:12}
-      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-      \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
-      \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
+\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
+\right)  &=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left( \mu _{\frak{a%
+}}\left( u\right) \right) }\dim \left( L_{\widetilde{\af_{\perp }}%
+}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
+\label{anom modules 2} \\
+&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho %
+\right] }\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{%
+\af_{\perp }}}\left( u\right) }\right)  \\
+&=&-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
+\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma },
 \end{eqnarray*}
-
-    If the set $\Delta^{+}_{\bot}$ is nonempty then the Weyl reflections corresponding to the
-    positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}\subset W$.
-    Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in
-    W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$
-    such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
-    \begin{equation}
-      \label{eq:13}
-      \begin{array}{c}
-        \fl \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
-          {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
-        = \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
-          \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}
-          {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right).
-      \end{array}
-    \end{equation}
-    The fraction in the right-hand side of the equation looks like the character of some  $\mathfrak{a}_{\bot}$-module.
-    Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and
-    $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$,
-    we can rewrite the shifted weights
-    \begin{equation*}
-      \label{eq:30}
-      \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}
-      (\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}
-      +\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho,
-    \end{equation*}
-
-    \begin{eqnarray*}
-      \label{eq:14}
-      \fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu)
-        e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
-      =\\
-      \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}
-      \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot
-          (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})
-          -\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
-      =\\
-      \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}
-      e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
-        -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}.
-    \end{eqnarray*}
-    The projector $\pi_{\mathfrak{a}}$ sends the character
-    ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$
-    to the unit element of $\cal{E}$ multiplied by
-    ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ :
-    \begin{eqnarray*}
-      \label{eq:15}
-      \fl    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
-        e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch}
-        L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-      = \\
-      \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
-      \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
-          -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}.
-    \end{eqnarray*}
-    Thus we obtain the relation
-    \begin{equation}
-      \label{eq:9}
-      \begin{array}{c}
-        \fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
-        \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
-        \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
-      \end{array}
-    \end{equation}
-    Rewriting the factor in the right-hand side in terms of formal elements as in the definition \ref{fan-definition}
-    \begin{eqnarray*}
-      \label{eq:16}
-      \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
-      = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
-      k_{\lambda }^{\left( \mu \right) }e^{\lambda } =\\
-      =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda
-        \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma },
-    \end{eqnarray*}
-    we get the following property of the anomalous branching coefficients,
-    \begin{equation}
-      \label{eq:17}
-      \begin{array}{c}
-        \fl \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}
-        \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
-            -\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-        \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-        \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\;
-        k^{(\mu)}_{\xi+\gamma}=0;
-        \\
-        \xi\in P_{\mathfrak{a}}.
-      \end{array}
-    \end{equation}
-
-    Using the definition \ref{fan-definition} we finally get the recurrent relation
-    \begin{eqnarray*}
-      k_{\xi }^{\left( \mu \right) }=
-      -\frac{1}{s\left( \gamma _{0}\right) }
-      \left(
-        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}
-        \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
-        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
-      \right.\\
-      \left. +
-        \sum_{\gamma \in \Gamma _{\frak{a}\subset \frak{g}}} s\left( \gamma +\gamma _{0}\right) k_{\xi+\gamma }^{\left( \mu \right) }
-      \right),
-    \end{eqnarray*}
+Equate the coefficients of exponents in the last equality to get the following result:
+\begin{equation}
+\sum_{u\in U}\epsilon (u)\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
+_{\widetilde{\af_{\perp }}}\left( u\right) }\right) \delta _{\xi ,\pi _{%
+\af}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\af%
+\subset \frak{g}}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
+\af}.  \label{eq:17}
+\end{equation}
+The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
+for $\gamma \in \Phi _{\af\subset \frak{g}}$ are not independent, they
+are subject to the linear relations and the form of these relations changes
+when the tested weight $\xi $ coinsides with one of \ the ''anomalous
+weights'', $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in
+U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
+}\subset \frak{g}}$ and pass to the summation over the vectors of the
+injection fan $\Gamma _{\af\subset \frak{g}}$ (see the definition \ref
+{fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
 \end{proof}
 \end{theorem}
-\begin{corollary}
-  Since $b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu}\;\mbox{for}\;\nu\in \bar{C_{\mathfrak{a}}}$ the recurrent relation gives the values of the branching coefficients inside the main Weyl chamber.
-\end{corollary}
-\begin{corollary}
-  Consider the case  $\Delta_{\bot}^{+} = 0$. There are three different reasons for $\Delta_{\bot}^{+}$
-to be empty: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$,
-ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$.
-Both the first and the second cases can be treated as corresponding to the trivial orthogonal subalgebra:
-$\mathfrak{a}_{\bot}=0$. In any of these cases the formal characters in the right-hand side of (\ref{eq:13})
-are reduced to the element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$.
-In the first two cases the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$.
-It is clear that in any of the three variants the final vector $\pi_{\mathfrak{a}}\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)$ leads to the unit of the formal algebra
-$\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty the  recurrent relation is simplified:
-\begin{equation*}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
-\left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
-\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
-+\gamma }^{\left( \mu \right) }\right),  \label{recurrent relation special}
-\end{equation*}
-the latter coincides with the one obtained in \cite{ilyin812pbc} (formula (16)).
-\end{corollary}
+\subsection{Embeddings and orthogonal pairs in simple Lie algebras}
+
+In this subsection we discuss some properties of ''orthogonal pairs'' of
+subalgebras in simple Lie algebras of classical series.
+
+When both $\frak{g}$ and $\af$ are finite-dimensional all the regular
+embeddings can be obtained by a successive elimination of nodes in the
+extended Dynkin diagram of $\frak{g}$ (and $\Delta _{\bot }^{+}=\emptyset $
+if $\af$ is maximal). For the classical series $A$, $C$ and $D$ when
+the regular injection $\af\rightarrow \frak{g}$ is thus fixed, the
+Dynkin diagram for $\af_{\bot }$ is obtained from the extended diagram
+of $\frak{g}$ by eliminating the subdiagram of $\af$ and the adjacent
+nodes:
+\begin{table}[tbh]
+\label{tab:diagrams} \noindent \centering{\
+\begin{tabular}{|l|l|l|l|}
+\hline
+$\frak{g}$ & Extended diagram of $\frak{g}$ & Diagrams of the subalgebras $%
+\af,\; \afb$ &  \\ \hline
+$A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps}
+&  \\ \hline
+$C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps}
+&  \\ \hline
+$D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps}
+&  \\ \hline
+\end{tabular}
+}
+\caption{Subalgebras $\af,\;\af_{\bot }$ for the classical series}
+\end{table}
+
+In the case of $B$ series the situation is different. The reason is that
+here the subalgebra $\af_{\bot }$ may be larger than the one obtained
+by elimination of the subdiagram of $\af$ and the adjacent nodes. The
+subalgebras of the orthogonal pair,$\ \af$ and $\af_{\bot }$, must
+not form a direct sum in $\frak{g}$ . It can be directly
+checked that when $\frak{g}=B_{r}$ and $\af=B_{r_{\af}}$ the
+orthogonal subalgebra is $\af_{\bot }=B_{r-r_{\af}}$. Consider the
+injection $B_{r_{\af}}\rightarrow B_{r},\quad 1<r_{\af}<r$ . By
+eliminating the simple root $\alpha _{r_{\af}-1}=e_{r_{\af%
+}-1}-e_{r_{\af}}$ one splits the extended Dynkin diagram of $B_{r}$
+into the disjoint diagrams for $\af=B_{r_{\af}}$ and $D_{r-r_{%
+\af}}$. But the system $\Delta _{\af_{\perp }}$ contains not only
+the simple roots $\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots ,e_{r_{\af%
+}-2}-e_{r_{\af}-1},e_{1}+e_{2}\right\} $ but also the root $e_{r_{\frak{%
+a}}-1}$. Thus $\Delta _{\af_{\perp }}$ forms the subsystem of the type $%
+B_{r-r_{\af}}$ and the orthogonal pair for the injection $B_{r_{\af%
+}}\rightarrow B_{r}$ is $\left( B_{r_{\af}},B_{r-r_{\af}}\right) $%
+. In the next Section the particular case of such orthogonal pair is
+presented for the injection $B_{2}\rightarrow B_{4}$ (see Figure \ref
+{fig:dynkin}).
+
+The complete classification of regular subalgebras for affine Lie algebras
+can be found in the recent paper \cite{1751-8121-41-36-365204}. From the complete
+classification of maximal special subalgebras in classical Lie algebras \cite
+{dynkin1952semisimple} we can deduce the following list of pairs of
+orthogonal subalgebras $\af,\;\af_{\bot }$:
+\begin{equation*}
+\begin{array}{lll}
+su(p)\oplus su(q) & \subset su(pq) &  \\
+so(p)\oplus so(q) & \subset so(pq) &  \\
+sp(2p)\oplus sp(2q) & \subset so(4pq) &  \\
+sp(2p)\oplus so(q) & \subset sp(2pq) &  \\
+so(p)\oplus so(q) & \subset so(p+q) & \mathrm{{for}\;p\;{and}\;q\;{odd}.}
+\end{array}
+\end{equation*}
+
 \subsection{Algorithm for recursive computation of branching coefficients}
+
 \label{sec:algorithm}
 
-The recurrent relation (\ref{recurrent-relation}) allows us to formulate an algorithm for recursive computation of branching coefficients.
-In this algorithm there is no need to  construct the module $L^{(\mu)}_{\mathfrak{g}}$ or any of the modules $L^{(\nu)}_{\mathfrak{a}}$.
+The recurrent relation (\ref{recurrent-relation}) allows us to formulate an
+algorithm for recursive computation of branching coefficients. In this
+algorithm there is no need to construct the module $L^{(\mu)}_{\frak{g}}$ or
+any of the modules $L^{(\nu)}_{\af}$.
 
 It contains the following steps:
+
 \begin{enumerate}
-\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{g} \supset \mathfrak{a}$.
-\item Select the positive roots $\alpha\in \Delta^{+}$ orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
-\item Construct the set $\Gamma$ (\ref{fan-defined}).
-\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights for the $\mathfrak{g}$-module $L^{(\mu)}$.
-\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$.
-Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies
-in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$.
-\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate
-the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))
--\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$.
+\item  Construct the root subsystem $\Delta _{\af}$ for the embedding $%
+\af\rightarrow \frak{g}$.
+
+\item  Select the positive roots $\alpha \in \Delta ^{+}$ orthogonal to the
+roots in $\Delta _{\af}$ i.e. form the set $\Delta _{\bot }^{+}$.
+
+\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$ (\ref
+{fan-defined}).
+
+\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
+)-\rho ;\;w \in W\right\} $ of the anomalous weights for the $\frak{g}$%
+-module $L^{(\mu )}$.
+
+\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
+}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
+)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
+\af_{\perp }}}}\right\} $. Since the set $\Delta _{\bot }^{+}$ is fixed
+we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
+}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
+\af_{\perp }}}}$ (by computing its scalar product with the roots from $%
+\Delta _{\bot }^{+}$).
+
+\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
+calculate the dimensions of the corresponding modules $\mathrm{\dim }\left(
+L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
+}\left( u\right) }\right) $.
+
 \item  Calculate the anomalous branching coefficients in the main Weyl
-  chamber $\bar{C_{\mathfrak{a}}}$ of the subalgebra $\mathfrak{a}$ using the recurrent relation (\ref{recurrent-relation}).
+chamber $\overline{C_{\af}}$ of the subalgebra $\af$ using the
+recurrent relation (\ref{recurrent-relation}).
 \end{enumerate}
 
-When being interested in the branching coefficients for the embedding of the finite-dimensional Lie algebra into the affine Lie algebra we can construct the set of the anomalous weights up to the required grade and use the steps 4-7 of the algorithm for each grade.
-We can also speed up the algorithm by one-time computation of the representatives of the conjugate classes $W_{\bot}\backslash W$.
-
-The next section contains examples illustrating the application of this algorithm.
+When being interested in the branching coefficients for the embedding of the
+finite-dimensional Lie algebra into the affine Lie algebra we can construct
+the set of the anomalous weights up to the required grade and use the steps
+4-7 of the algorithm for each grade. We can also speed up the algorithm by
+one-time computation of the representatives of the conjugate classes $%
+W/W_{\afb }$.
+
+The next section contains examples illustrating the application of this
+algorithm.
 
@@
   }
-  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules for the embedding $A_1\subset B_2$}
+  \caption{Regular embedding $A_1\subset B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
+    The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is shown by the black vector.
+$\afb=A_1$-modules built on the weights of the singular element $\Psi^{(\omega_1)}$ are shown by dotted lines.
+The dimensions of these modules and the signs of the corresponding determinants $\epsilon(w)$ are shown near the anomalous weights.
+Fundamental weight coordinate of $\af=A_1$ is indicated on the weight subspace of $\af$.
+}
   \label{fig:B2_A1_2}
 \end{figure}
+
+Let's describe the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ (the black vector in Figure \ref{fig:B2_A1}).
+
+Circles indicate the weights of the singular element $\Psi^{(\omega_1)}$.
+Now we are to factorise the Weyl group $W$ by $W_{\afb}=\left\{w_1\right\}$
+and to construct the set $\left\{w(\mu+\rho)-\rho,\; w\in W_{\afb}\backslash W\right\}$.
 In the Figure \ref{fig:B2_A1_2} the weights of the corresponding
-$\left(\mathfrak{a}_{\bot}=A_1\right)$-modules
-$L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$
-are indicated. Projecting them onto the root space of the subalgebra $\mathfrak{a}=A_1$
+$\left(\afb=A_1\right)$-modules
+$L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$
+are indicated. Projecting them onto the root space of the subalgebra $\af=A_1$
 we get the anomalous weights and their multiplicities:
@@
 Here the second component denotes the value of $s(\gamma)$.
-Applying this fan inside the $\bar{C}^{(0)}_{\mathfrak{a}}$ we get zeros for the weights
-greater than the first anomalous vector $(1)$, here $k^{(1,0)}_1=2$. For the last weight in $\bar{C}^{(0)}_{\mathfrak{a}}$ the formula (\ref{recurrent-relation}) gives
+Applying this fan inside the $\bar{C}^{(0)}_{\af}$ we get zeros for the weights
+greater than the first anomalous vector $(1)$, here $k^{(1,0)}_1=2$. For the last weight in $\bar{C}^{(0)}_{\af}$ the formula (\ref{recurrent-relation}) gives
 \begin{equation*}
@@
   \includegraphics[width=50mm]{figure3.eps}
-  \caption{The regular embedding $B_2\subset B_4$ described by dropping the node.}
+  \caption{The regular embedding $B_2\subset B_4$ described by dropping the node from the Dynkin diagram. Note, that $\afb$ is equal to $B_2$, not to $A_1\oplus A_1$ seen at the diagram.}
   \label{fig:dynkin}
+\end{figure}
+
+\begin{figure}[pt]
+  \centering
+    \includegraphics[width=100mm,height=90mm]{figure4.eps}
+  \caption{Projected singular weights of $-\frac{1}{s(\gamma_0)}\pi_{B_2}\left(\hat \Psi^{(0,1,0,2)}_{B_4}\right)$
+  with the dimensions of the corresponding $\afb=B_2$-modules.}
+  \label{fig:B4B2anom}
+
+%\end{figure}
+%
+%\begin{figure}[pb]
+  \centering
+  \includegraphics[height=80mm]{figure5.eps}
+  \caption{The fan $\Gamma_{B_2\subset B_4}$ for $B_2\subset B_4$. The values $s(\gamma+\gamma_0)$ are shown in the corresponding weights $\gamma$.}
+  \label{fig:B4B2Fan}
 \end{figure}
@@
 \end{eqnarray*}
-Correspondingly for the embedded subalgebra $\mathfrak{a}=B_2$ we have
+Correspondingly for the embedded subalgebra $\af=B_2$ we have
 \begin{equation*}
@@
   \label{eq:27}
- \Delta^{+}_{\bot}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
-\end{equation*}
-is the set of positive roots for the algebra $\mathfrak{a}_{\bot}=B_2$.
-\begin{figure}[t]
-  \centering
-    \includegraphics[width=100mm,height=90mm]{figure4.eps}
-  \caption{Projected weights $-\frac{1}{s(\gamma_0)}\pi_{B_2}\left(\hat \Psi^{(0,1,0,2)}_{B_4}\right)$
-  with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
-  \label{fig:B4B2anom}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \includegraphics[height=80mm]{figure5.eps}
-  \caption{The fan for $B_2\subset B_4$}
-  \label{fig:B4B2Fan}
-\end{figure}
+ \Delta^{+}_{\afb}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
+\end{equation*}
+is the set of positive roots for the algebra $\afb=B_2$.
+
 Using the definition (\ref{fan-defined}) we obtain the fan
@@
 To find the branching coefficients we need to compute the anomalous weights of
-$L^{\mu}_{B_4}$, select the weights belonging to $\bar{C}^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$
-and compute the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.
-The set of the anomalous weights $\left\{ \omega(\mu+\rho)-\rho,\; \omega\in W\right\}$
+$L^{\mu}_{B_4}$, select the weights belonging to $\bar{C}^{\left( 0 \right)}_{\afb}$
+and compute the dimensions of the corresponding $\afb$-modules.
+The set of the anomalous weights $\left\{ w(\mu+\rho)-\rho,\; w\in W\right\}$
 contains 384 vectors.
 
-We are to select the weights $\psi \in \omega(\mu+\rho)$  with the property
-$\pi_{\mathfrak{a}_{\bot}} \left(  \psi \right) \in \bar{C}^{\left( 0 \right)}_{\mathfrak{a}_{\bot}}$.
-It means that the scalar product of these weights with all the roots in $\Delta^{+}_{\bot}$ is nonnegative.
+We are to select the weights $\psi \in w(\mu+\rho)$  with the property
+$\pi_{\afb} \left(  \psi \right) \in \bar{C}^{\left( 0 \right)}_{\afb}$.
+It means that the scalar product of these weights with all the roots in $\Delta^{+}_{\afb}$ is nonnegative.
 
 To compute the dimensions of the corresponding
-$\mathfrak{a}_{\bot}$-modules we need to project each selected weight
-onto the root space $\Delta^{+}_{\bot}$, subtract
-$\rho_{\mathfrak{a}_{\bot}}$ and apply the Weyl dimension formula. The result is shown in the Figure \ref{fig:B4B2anom}.
+$\afb$-modules we need to project each selected weight
+onto the root space $\Delta^{+}_{\afb}$, subtract
+$\rho_{\afb}$ and apply the Weyl dimension formula. The result is shown in the Figure \ref{fig:B4B2anom}.
 
@@
   \label{eq:24}
-  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
+  \pi_{\af} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
   \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+\\
@@
 
-Consider the Wess-Zumino-Witten model with the affine Lie algebra $\mathfrak{a}$.
+Consider the Wess-Zumino-Witten model with the affine Lie algebra $\af$.
 Nondiagonal modular invariants for this model can be constructed from the diagonal
-invariant if there exists an affine algebra $\mathfrak{g}$ such that $\mathfrak{a}\subset\mathfrak{g}$.
+invariant if there exists an affine algebra $\mathfrak{g}$ such that $\af\subset\mathfrak{g}$.
 Then we can replace the characters of the $\mathfrak{g}$-modules in the diagonal
@@
   \label{eq:32}
-\sum_{\nu \in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} \chi_{\nu}
-\end{equation*}
-containing the modified characters $\chi_{\nu}$ of the corresponding $\mathfrak{a}$-modules.
+\sum_{\nu \in P^{+}_{\af}}b^{(\mu)}_{\nu} \chi_{\nu}
+\end{equation*}
+containing the modified characters $\chi_{\nu}$ of the corresponding $\af$-modules.
 Thus we obtain the nondiagonal modular-invariant  partition function for the theory with
-the current algebra $\mathfrak{a}$,
+the current algebra $\af$,
 \begin{equation}
   \label{eq:36}
-   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau).
+   Z_{\af}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\af}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau).
 \end{equation}
@@
 Let $X^{\alpha_j}_{-n_j}$ and $\tilde{X}^{\alpha'_j}_{-n_j}$ be the lowering generators for
-$\mathfrak{g}$ and for $\mathfrak{a}\subset\mathfrak{g}$ correspondingly.
-Let $\pi_{\mathfrak{a}}$ be the projection operator of
-$\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$.
+$\mathfrak{g}$ and for $\af\subset\mathfrak{g}$ correspondingly.
+Let $\pi_{\af}$ be the projection operator of
+$\pi_{\af}:\mathfrak{g}\longrightarrow \af$.
 In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$
@@
 \end{equation*}
-And for the sub-algebra $\mathfrak{a}$ the corresponding states are
+And for the sub-algebra $\af$ the corresponding states are
 \begin{equation*}
   \label{eq:110}
-  \tilde{X}^{\alpha'_1}_{-n_1}\tilde{X}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
-\end{equation*}
-The $\mathfrak{g}$-invariance of the vacuum entails its $\mathfrak{a}$-invariance,
+  \tilde{X}^{\alpha'_1}_{-n_1}\tilde{X}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\af}(\lambda)\right>.
+\end{equation*}
+The $\mathfrak{g}$-invariance of the vacuum entails its $\af$-invariance,
 but this is not the case for the energy-momentum tensor. So the energy-momentum tensor of the larger theory
@@
   \label{eq:2}
-  T_{\mathfrak{g}}(z)=T_{\mathfrak{a}}(z)
+  T_{\mathfrak{g}}(z)=T_{\af}(z)
 \end{equation}
@@
   \label{eq:33}
-  c(\mathfrak{g})=c(\mathfrak{a})
+  c(\mathfrak{g})=c(\af)
 \end{equation*}
@@
   \label{eq:111}
-  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}.
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\af}{x_ek+a}.
 \end{equation}
@@
 to prove the finite reducibility theorem \cite{kac1988modular}.
-It states that for the conformal embedding  $\mathfrak{a}\subset\mathfrak{g}$
+It states that for the conformal embedding  $\af\subset\mathfrak{g}$
 only finite number of branching coefficients have nonzero values.
 
-\begin{mynote} The orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
+\begin{mynote} The orthogonal subalgebra $\afb$ is always empty for the conformal embeddings $\af\subset \mathfrak{g}$.
 \begin{proof}
@@
 
-The substitution of the generators of $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations  should give the energy-momentum tensor $T_{\mathfrak{g}}$.
-But if the set of the generators $\Delta_{\bot}$ is not empty this is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$.
+The substitution of the generators of $\af$  in terms of the generators of $\mathfrak{g}$ into these combinations  should give the energy-momentum tensor $T_{\mathfrak{g}}$.
+But if the set of the generators $\Delta_{\afb}$ is not empty this is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\afb}$.
 \end{proof}
 \end{mynote}
-\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
+\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$.}
 \label{sec:spec-embedd-hata_1s}
 
-Consider the case where both $\mathfrak{g}$ and $\mathfrak{a}$ are affine Lie algebras:
+Consider the case where both $\mathfrak{g}$ and $\af$ are affine Lie algebras:
 $\hat{A}_1 \longrightarrow \hat{A}_2$ and the injection is the affine extension of the
@@
 There exist three level one fundamental weights in the weight space of $\hat{A}_2$.
-It is easy to see that the set $\Delta_{\bot}$ is empty and the subalgebra $\mathfrak{a}_{\bot}=0$.
+It is easy to see that the set $\Delta_{\afb}$ is empty and the subalgebra $\afb=0$.
 
@@
 there are only two nonzero anomalous weights and both have multiplicity 1.
-These are the highest weights of $\mathfrak{a}$-submodules and their branching
+These are the highest weights of $\af$-submodules and their branching
 coefficients. So the finite reducibility theorem holds and we get the decomposition
@@
 Since this embedding is regular and $x_e=1$, the subalgebra modules and the initial module are of the same level.
-The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection
+The set $\Delta^{+}_{\afb}$ of the orthogonal positive roots with the zero projection
 on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.
@@
 $P_{\hat{A_1}}$ and find the dimensions of the corresponding
-$\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
+$\afb$-modules $L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$.
 The result is presented in the Figure
@@
   \includegraphics[width=120mm]{figure12.eps}
-  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$ and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
+  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$. The dimensions of the corresponding $\afb=A_1$-modules with the signs $\epsilon(w)$ are shown.}
   \label{fig:AffineB2_A1_anom_proj}
@@
 
-Notice that here the lowest weight  $\gamma_0$ of the fan  is zero, since we have excluded all the roots of $\Delta^{+}_{\bot}$ from the defining relation (\ref{fan-defined}).
+Notice that here the lowest weight  $\gamma_0$ of the fan  is zero, since we have excluded all the roots of $\Delta^{+}_{\afb}$ from the defining relation (\ref{fan-defined}).
 
@@
 We have demonstrated that the injection fan technique can be used to deal with the nonmaximal subalgebras.
-It was found out that for such subalgebras an auxiliary subset $\Delta^{+}_{\bot}$ must be extracted
+It was found out that for such subalgebras an auxiliary subset $\Delta^{+}_{\afb}$ must be extracted
 from the set of positive roots $\Delta_{\mathfrak{g}}^{+}$.
-The role of the subset $\Delta^{+}_{\bot}$ is to modify both the injection fan (formed here by the
-weights $\left(\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\mathfrak{a}}^{+}\right) \setminus \Delta^{+}_{\bot}$)
+The role of the subset $\Delta^{+}_{\afb}$ is to modify both the injection fan (formed here by the
+weights $\left(\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\af}^{+}\right) \setminus \Delta^{+}_{\afb}$)
 and the anomalous weights of the initial module.
 This modification reduces to a simple procedure:
-the anomalous weights multiplicities are to be substituted by the dimensions of the corresponding ${\mathfrak{a}}_{\bot}$-modules.
+the anomalous weights multiplicities are to be substituted by the dimensions of the corresponding $\afb$-modules.
 

### 2010-11-11 GeneralOverview/Lectures/2dqft.tex
Lecture 5 (Ising model) started.

@@
 Вместе с трансляционной и лоренц-инвариантностью она порождает конформную инвариантность, то есть инвариантность относительно преобразований, сохраняющих углы.
+
+\section{Лекция 5. Решение двумерной модели Изинга}
+\label{sec:lecture-5}
+
+Вернемся на некоторое время к модели Изинга в двух измерениях \eqref{eq:1}.
+Точного решения для модели с внешним полем до сих пор не найдено.
+Решение же для $h=0$ впервые было получено Онзагером в 1944 году.
+В этой и следующей лекциях излагается решение Вдовиченко, как наиболее короткое и простое.
+Изложение взято из книги \cite{belavin2001lect}.
+Энергия системы в отсутствие внешнего поля дается выражением
+\begin{equation}
+  \label{eq:98}
+  E[\sigma]=-J\sum_{\left<i,j\right>}\sigma_i \sigma_j .
+\end{equation}
+Введем обозначение
+\begin{equation}
+  \label{eq:99}
+  K=J/T.
+\end{equation}
+Статсумма имеет вид
+\begin{equation}
+  \label{eq:100}
+  Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}\sigma_i\sigma_j}
+\end{equation}
+Будем считать, что в наша решетка $\mathcal{L}$ состоит из $N=mn$ узлов.
+Обозначим через $M$ число пар $\left<i,j\right>$.
+$M=2N-n-m$.
+Для простоты будем накладывать тороидальные граничные условия.
+Тогда $M=2N$.
+Введем {\it дуальную решетку $\mathcal{L}^*$}, вершинами которой будут центры граней исходной решетки.
+Нам удобно будет использовать действие в следующем виде:
+\begin{equation}
+  \label{eq:101}
+  Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1+1)}=e^{KM} \sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
+\end{equation}
+
+\subsection{Низкотемпературное и высокотемпературное разложение. Дуальность Крамерса-Ванье.}
+\label{sec:low-high-temp}
+
+Обозначим выражения, входящие в сумму в последнем уравнении, через $X[\sigma]$:
+\begin{equation}
+  \label{eq:102}
+  X[\sigma]=e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
+\end{equation}
+Заметим, что все состояния можно упорядочить следующим образом:
+\begin{itemize}
+\item Основное состояние, все спины направлены в одну сторону, $X[\sigma]=1$
+\item Все спины в одну сторону, один в противоположную.
+Такому состоянию можно сопоставить контур на дуальной решетке вокруг этого спина.
+Тогда каждая сторона контура даст вклад $e^{-2K}$ в $X[\sigma]$.
+  \begin{equation}
+    \label{eq:103}
+    X[\sigma]=\left(e^{-2K}\right)^4
+  \end{equation}
+\item Два спина направлены в противоположную сторону, здесь есть два варианта контура на дуально решетке - если спины рядом, то его длина равна шести, если не рядом - то восьми.
+То есть вклады $\left(e^{-2K}\right)^6$ и $\left(e^{-2K}\right)^8$.
+\item И так далее.
+\end{itemize}
+В итоге мы можем записать все вклады $X[\sigma]$ в виде суммы по всевозможным замкнутым контурам на дуальной решетке. Если ввести обозначение
+\begin{equation}
+  \label{eq:104}
+  \kappa=e^{-2K},
+\end{equation}
+то
+\begin{equation}
+  \label{eq:105}
+  X[\sigma]=\kappa^{l[c]}.
+\end{equation}
+Здесь $l[c]$ --- длина контура $c$ на дуальной решетке, соответствующего состоянию $\sigma$. Тогда для $Z$ получаем
+\begin{equation}
+  \label{eq:106}
+  Z=e^{MK}\sum_c \kappa^{l[c]}. 
+\end{equation}
+Такое выражение называется низкотемпературным разложением, так как оно хорошо сходится при малых температурах ($K>>1$).
 \bibliography{2dqft}{}

### 2010-11-13 GeneralOverview/Lectures/2dqft.tex
More work
Lecture 5 is here

@@
 
-\section{Лекция 5. Решение двумерной модели Изинга}
+\section{Лекция 5. Двумерная модель Изинга}
 \label{sec:lecture-5}
@@
 Такое выражение называется низкотемпературным разложением, так как оно хорошо сходится при малых температурах ($K>>1$).
+
+Чтобы получить высокотемпературное разложение, воспользуемся тем, что $e^{K\sigma_i\sigma_j}=\ch K+\sigma_i\sigma_j\sh K=\ch K \left(1+\sigma_i\sigma_j \th K\right)$.
+Тогда статсумма записывается в виде
+\begin{equation}
+  \label{eq:80}
+  Z=(\ch K)^M\sum_{[\sigma]}\prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)
+\end{equation}
+Будем раскрывать скобки в произведении, сопоставляя каждому множителю $\sigma_i\sigma_j \th K$ ребро на решетке $\mathcal{L}$, соединяющее вершины $i,j$.
+Заметим, что вклад непрерывного пути, соединяющего вершины $i$ и $k$ пропорционален $(\sigma_i \sigma_{i+1}) (\sigma_{i+1}\sigma_{i+2}) (\sigma_{i+2}\sigma_{i+3})\dots (\sigma_{k-1}\sigma_k)=\sigma_{i}\sigma_k$, где мы пронумеровали вершины вдоль пути.
+То есть вклад от незамкнутого пути дается его концами, а вклад от замкнутого контура всегда равен 1.
+Тогда произведение запишется в виде
+\begin{equation}
+  \label{eq:107}
+  \prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)=1+a_1 \th K +a_2 \th^2 K+\dots,
+\end{equation}
+где $a_k$ дается суммой по всем контурам $c$ (не обязательно замкнутым или односвязным) длины $k$.
+Чтобы вычислить статсумму, нам надо просуммировать такие выражения по всем возможным конфигурациям спинов.
+Заметим, что для любого незамкнутого контура и любой конфигурации найдется другая конфигурация, куда вклад этого контура входит с противоположным знаком (так как спины направлены в другую сторону).
+А вклад замкнутого контура равен $\th^{l[c]}K$ в любой конфигурации, то есть входит в статсумму $2^N$ раз.
+В результате получаем высокотемпературное разложение статсуммы в виде суммы по всем замкнутым контурам на решетке $\mathcal{L}$:
+\begin{equation}
+  \label{eq:108}
+  Z=(\ch K)^M 2^N \sum_c (\th K)^{l[c]}=(\ch K)^M 2^N \sum_c \kappa^{l[c]}.
+\end{equation}
+Здесь мы ввели обозначение $\kappa=\th K$. Это разложение хорошо сходится при $K<<1$.
+
+\subsection{Дуальность Крамерса-Ванье}
+\label{sec:duality}
+
+У нас есть два точных разложения для статсуммы. Сравним их в термодинамическом пределе.
+\begin{equation}
+  \label{eq:109}
+  f=-\lim_{N\to \infty}\frac{Z_N}{N}.
+\end{equation}
+Решетки $\mathcal{L}$ и $\mathcal{L}^*$ отличаются только на границе, поэтому в термодинамическом пределе $M/N\to 2$ и выражения для удельной свободной энергии из высокотемпературного и низкотемпературного разложений должны совпадать.
+Если ввести функцию $\Phi(\kappa)=\lim_{N\to \infty}\frac{1}{N} \ln \left(\sum_c \kappa^{l[c]}\right)$, то свободная энергия запишется в высокотемпературном и низкотемпературном разложениях следующим образом:
+\begin{equation}
+  \label{eq:110}
+  -f(K)=2K+\Phi(e^{-2K})=\ln(2\ch^2 K)+\Phi(\th K)
+\end{equation}
+Это и есть соотношение дуальности {\it Крамерса-Ванье}.
+Если ввести $K^*$ так, что $\th K^*=e^{-2K}$ или $\sh 2K^* \sh 2K=1$, то соотношение дуальности будет связывать теорию при температуре $K$ и $K^*$:
+\begin{equation}
+  \label{eq:111}
+  f(K^*)=f(K)+2K-\ln(2\ch^2 K^*).
+\end{equation}
+Рассмотрим теперь поведение теории в критической точке $K_c$.
+В ней свободная энергия $f(K_c)$ не аналитична.
+Тогда $f$ должна быть не аналитична и при $K^*=K_c$.
+Если предположить, что критическая точка единственна, то мы можем найти ее из требования $K=K^*$, то есть $2K=\ln(2\ch^2 K)$ или
+\begin{equation}
+  \label{eq:112}
+  \sh^2 2K_c=1.
+\end{equation}
+Теперь перейдем к точному решению модели Изинга.
+\section{Лекция 6. Решение Вдовиченко.}
+\label{sec:lecture-6}
+Суть состоит в сведении вычисления статсуммы в высокотемпературном разложении к решению некоторого рекуррентного соотношения.
+Это соотношение записывается в матричном виде и его решение дается следом матрицы, который можно вычислить после преобразования Фурье.
+
 \bibliography{2dqft}{}

### 2010-11-13 GeneralOverview/Lectures/2dqft.tex
Lecture 6 started

@@
 \usepackage{color}
-%\usepackage{graphicx}
-%\usepackage{epstopdf}
+\usepackage{graphicx}
 \pagestyle{plain}
@@
 
+Заметим, что суммирование по замкнутым контурам обозначает, что в каждой вершине сходится четное число ребер.
+Поэтому мы можем перейти от суммирования по замкнутым контурам к суммированию по ``траекториям чернильной точки'' --- замкнутым путям, состоящим из компонент, которые можно нарисовать, не отрывая ручку от бумаги.
+При этом в случае контура с самопересечениями существует несколько способов нарисовать его.
+Например, ``восьмерку'' можно представить как два пути, путь без самопересечения и путь с самопересечением (Смотри рисунок \ref{fig:ising-1}).
+\begin{figure}[h!tb]
+  \centering
+    \includegraphics[width=80mm]{ising1}
+  \caption{Переход от контуров к замкнутым путям}
+  \label{fig:ising-1}
+\end{figure}
+Поэтому такие вклады надо брать с множителем $(-1)^{\nu(\Gamma)}$, где $\nu(\Gamma)$ - число самопересечений пути $\Gamma$.
+Статсумма в высокотемпературном разложении \eqref{eq:108} дается выражением
+\begin{equation}
+  \label{eq:113}
+  Z=(\ch K)^M 2^N\sum_c \kappa^{l[c]}.
+\end{equation}
+Обозначим сумму через $\Sigma=\sum_c \kappa^{l[c]}$. Перепишем её через сумму по путям
+\begin{equation}
+  \label{eq:114}
+  \Sigma=\sum_{\Gamma}(-1)^{\nu(\Gamma)} \kappa^{l[\Gamma]}
+\end{equation}
+Воспользуемся следующим утверждением, доказательство которого оставляется в качестве упражнения.
+Для любой связной замкнутой петли на плоскости с $\nu$ самоперечечениями и полным углом поворота $2\pi(n+1)$ (при ее обходе) верно равенство
+\begin{equation}
+  \label{eq:115}
+  (-1)^{\nu}=(-1)^n.
+\end{equation}
+Сопоставим каждому узлу в пути $\Gamma$ с углом поворота $\varphi$ в нем ($0,\pm \pi/2$) множитель $e^{\frac{i\varphi}{2}}$.
+Тогда после обхода петли полный множитель будет равен $(-1)^{\nu+1}$.
+Для несвязного пути, состоящего из $s$ компонент --- $(-1)^{m+s}$, где $m=\sum \nu$.
+То есть если ввести для пути $\Gamma$ общий множитель $s(\Gamma)$, то $\Sigma$ можно переписать в виде
+\begin{equation}
+  \label{eq:116}
+  \Sigma=\sum_{\Gamma}(-1)^{s(\Gamma)}\prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}\kappa^{l[\Gamma]}
+\end{equation}
+Обозначим через $F^{(1)}_l$ сумму по всем однокомпонентным петлям длины $l$, через $F^{(2)}_l$ --- двухкомпонентным и так далее.
+\begin{equation}
+  \label{eq:117}
+  F^{(1)}_l=\sum_{\Gamma:l[\Gamma]=l} \prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}.
+\end{equation}
+Тогда $F_l^{(2)}$ можно вычислить через $F^{(1)}$:
+\begin{equation}
+  \label{eq:118}
+  F^{(2)}_l=\frac{1}{2!}\sum_{l_1,l_2:l_1+l_2=l} F^{(1)}_{l_1} F^{(1)}_{l_2}
+\end{equation}
+Аналогично
+\begin{equation}
+  \label{eq:119}
+  F^{(s)}_l=\frac{1}{s!}\sum_{l_1,\dots l_s:l_1+\dots+l_s=l} F^{(1)}_{l_1}\dots F^{(1)}_{l_s}
+\end{equation}
+Теперь мы можем выразить $\Sigma$ через $F^{(1)}$:
+\begin{equation}
+  \label{eq:120}
+  \Sigma=\sum_{s=0}^{\infty}\frac{1}{s!}\sum_{l_1\dots l_s=1}^{\infty} \kappa^{l_1+\dots+l_s}F^{(1)}_{l_1} \dots F^{(1)}_{l_s}=
+  \sum_{s=0}^{\infty}\frac{1}{s!}\left(\sum_{l=1}^{\infty} \kappa^{l}F^{(1)}_{l} \right)^s =\exp\left(-\sum_{l=1}^{\infty} \kappa^l F_l\right)
+\end{equation}
+Петли с числом узлов больше $N$ не дают вклада, так как содержат повторяющиеся ребра и поэтому сократятся (Смотри рисунок \ref{fig:ising-2}).
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=40mm]{ising2}
+  \caption{Сокращение путей с повторяющимися ребрами}
+  \label{fig:ising-2}
+\end{figure}
 \bibliography{2dqft}{}

### 2010-11-14 GeneralOverview/Lectures/2dqft.tex
Lecture 6 completed

@@
 
-\subsection{Низкотемпературное и высокотемпературное разложение. Дуальность Крамерса-Ванье.}
+\subsection{Низкотемпературное и высокотемпературное разложение}
 \label{sec:low-high-temp}
@@
 \end{figure}
+Наша задача свелась к вычислению $F_l$.
+Рассмотрим произвольную вершину с координатами $(n,m)$.
+Пронумеруем направления выхода из нее индексом $\nu=1,2,3,4$ против часовой стрелки.
+Обозначим через $W_l (n,m,\nu|n_0,m_0,\nu_0)$ сумму по всем путям длины $l$, соединяющим вершины $(n_0,m_0)$ и $(n,m)$.
+Первый шаг пути в направлении $\nu_0$.
+Учитываются множители $e^{\frac{i\varphi}{2}}$ начиная с узла, следующего за $(n_0,m_0)$ и заканчивая узлом $(n,m)$.
+Последний шаг пути не должен быть в направлении, противоположном $\nu$.
+Тогда $F_l$ можно записать как сумму $W_l(n,m,\nu|n,m,\nu)$ по всем вершинам решетки.
+Каждая петля при этом будет учтена $2l$ раз, так как у нее $l$ возможных вершин начала и два возможных направления.
+\begin{equation}
+  \label{eq:121}
+  F_l=\frac{1}{2l}\sum_{(n,m)\in \mathcal{L}} \sum_{\nu=1,2,3,4} W_l(n,m,\nu|n,m,\nu)
+\end{equation}
+Если мы зафиксируем начальную вершину путей $(n_0,m_0,\nu_0)$, то сумму по путям длины $l+1$ можно выразить через сумму по путям длины $l$.
+В вершину $(n,m,1)$ пути могут входить с направлений $2,3,4$, то есть последний шаг может быть из вершины $(n-1,m)$ в направлении $1$, из вершины $(n,m-1)$ в направлении $2$ и из вершины $(n,m-1)$ в направлении $4$.
+Аналогично для других направлений. Тогда
+\begin{equation}
+  \label{eq:122}
+\begin{array}{l}
+W_{l+1}(n,m,1)=W_l(n-1,m,1)+e^{-i\pi/4} W_l(n,m-1,2)+e^{i\pi/4}W_l(n,m-1,4)\\
+W_{l+1}(n,m,2)=e^{i\pi/4}W_l(n-1,m,1)+W_l(n,m-1,2)+e^{i\pi/4}W_l(n+1,m,3)\\
+W_{l+1}(n,m,3)=e^{i\pi/4}W_l(n,m-1,2)+W_l(n+1,m,3)+e^{-i\pi/4}W_l(n,m+1,4)\\
+W_{l+1}(n,m,4)=e^{-i\pi/4}W_l(n-1,m,1)+e^{i\pi/4}W_l(n+1,m,3)+W_l(n,m+1,4)\\
+\end{array}
+\end{equation}
+Эти рекуррентные соотношения можно переписать в матричном виде, если ввести матрицу коэффициентов $\Lambda$:
+\begin{equation}
+  \label{eq:124}
+  W_{l+1}(n,m,\nu)=\sum_{p,q,\mu}\Lambda(n,m,\nu|t,u,\mu) W_l(t,u,\mu)
+\end{equation}
+Если вершины $(t,u)$ и $(n,m)$ не являются соседними, то $\Lambda(n,m,\nu|p,q,\mu)=0$.
+Матрица $\Lambda$ не зависит от начала пути.
+$W_{l+1}=\Lambda W_l$, поэтому мы $F_l$ дается следом $l$-той степени $\Lambda$:
+\begin{equation}
+  \label{eq:125}
+  F_l=\frac{1}{2l}\mathrm{Tr} W_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l W_0
+\end{equation}
+Но матрица $W_0=I$ (единичной матрице), поэтому
+\begin{equation}
+  \label{eq:126}
+  F_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l =\frac{1}{2l} \sum_k (\lambda_k)^l,
+\end{equation}
+где $\lambda_k$ - собственные значения матрицы $\Lambda$. Подставим выражение \eqref{eq:126} в формулу \eqref{eq:120}:
+\begin{multline}
+  \label{eq:127}
+  \Sigma=\exp\left(-\sum_{l=0}^{\infty} \frac{\kappa^l}{2l}\mathrm{Tr}\Lambda^l\right)=\exp\left(-\frac{1}{2}\sum_k \sum_{l=0}^{\infty} \frac{(\kappa\lambda_k)^l}{l}\right)=\\
+  \exp\left(\frac{1}{2}\sum_k \ln(1-\kappa\lambda_k)\right)=\prod_k(1-\kappa\lambda_k)^{1/2}=(\det(I-\kappa\Lambda))^{1/2}
+\end{multline}
+Чтобы вычислить детерминант сделаем дискретное преобразование Фурье:
+\begin{equation}
+  \label{eq:128}
+  W_{l}(n,m,\nu)=\sum_{p_1,p_2} \tilde{W}_l(p_1,p_2,\nu) e^{\frac{2\pi i (p_1n+p_2m)}{\sqrt N}}
+\end{equation}
+В импульсном представлении матрица $\Lambda$ будет иметь блочно-диагональный вид
+\begin{equation}
+  \label{eq:129}
+  \Lambda(p_1,p_2,\mu|q_1,q_2,\nu)=\delta_{p,q}\Lambda_p (\mu,\nu),
+\end{equation}
+где
+\begin{equation}
+  \label{eq:130}
+  \Lambda_p(\mu,\nu)=
+  \begin{pmatrix}
+    e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\
+    e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\
+    0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
+    e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i p_2}{\sqrt N}}
+  \end{pmatrix}
+\end{equation}
+Матрица $I-\kappa\Lambda$ тоже имеет блочный вид с блоками
+\begin{equation}
+  \label{eq:131}
+  \begin{pmatrix}
+    1-\kappa e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\
+    e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\
+    0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
+    e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1- \kappa e^{-\frac{2\pi i p_2}{\sqrt N}}
+  \end{pmatrix}.
+\end{equation}
+В результате вычисления детерминанта получаем
+\begin{eqnarray}
+  \label{eq:132}
+  \Sigma=\prod_{p_1,p_2} D^{1/2}_{p}\\
+  D_p=(1+\kappa^2)^2 -2\kappa (1-\kappa^2)\left( \cos \frac{2\pi p_1}{\sqrt N} +\cos \frac{2\pi p_2}{\sqrt N}\right)
+\end{eqnarray}
+В результате выражение для статсуммы имеет вид
+\begin{equation}
+  \label{eq:133}
+  Z_N=(2\ch^2 K)^N \prod_{p_1,p_2}D_p^{1/2}.
+\end{equation}
+Исследуем критическое поведение. Вычислим для этого удельную свободную энергию:
+\begin{equation}
+  \label{eq:134}
+  f=-T \lim_{N\to \infty}\frac{Z_N}{N}=-T \lim_{N\to \infty} \left(\ln (2\ch^2 K)+\frac{1}{2N}\sum_p \ln D_p\right)
+\end{equation}
+В термодинамическом пределе $N\to \infty$ значения импульса покрывают всю ось, поэтому сумма переходит в интеграл. Мы сделаем замену переменных
+\begin{eqnarray}
+  \label{eq:135}
+  w_1=\frac{2\pi p_1}{\sqrt N}\quad  w_2=\frac{2\pi p_2}{\sqrt N},\quad w_{1,2}\in [0;2\pi]\\
+  dp_1 dp_2=\frac{N}{(2\pi)^2} dw_1 dw_2
+\end{eqnarray}
+Вспомним, что $\kappa=\th K$, поэтому
+\begin{equation}
+  \label{eq:136}
+  -\ln(2\ch^2 K)=\ln\left(\frac{1-\kappa^2}{2}\right)
+\end{equation}
+Нам будет удобно переписать $D_p$  в виде
+\begin{equation}
+  \label{eq:137}
+  D_p=(\kappa^2+2\kappa -1)^2 +4\kappa (1-\kappa^2) \left(\sin^2 \frac{w_1}{2} +\sin^2 \frac{w_2}{2}\right)
+\end{equation}
+Тогда свободная энергия дается интегралом
+\begin{multline}
+  \label{eq:138}
+  f=T\ln\left(\frac{1-\kappa^2}{2}\right)-\\
+  -\frac{T}{8\pi^2}\int_0^{2\pi}\int_0^{2\pi}\ln\left((\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)\right) dw_1 \;dw_2
+\end{multline}
+В критической точке должна быть расходимость.
+Интеграл может иметь особую точку только при $(\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)=0$.
+Это выражение имеет минимум при $w_1=w_2=0$.
+Тогда при $\kappa^2+2\kappa-1=0$ интеграл расходится, что соответствует критической точке.
+\begin{equation}
+  \label{eq:139}
+  \kappa_c=\sqrt 2 -1
+\end{equation}
+В критической точке основной вклад в интеграл дает окрестность $w_1=w_2=0$, введем
+\begin{equation}
+  \label{eq:140}
+  \epsilon=\kappa-\kappa_c
+\end{equation}
+Тогда около критической точки свободная энергия ведет себя как
+\begin{equation}
+  \label{eq:141}
+  f=g(\epsilon)-\frac{T}{8\pi^2}\int_{0}^{2\pi}\int_0^{2\pi}\ln \left( c\epsilon^2 +A(\epsilon)(w_1^2+w_2^2)\right)dw_1\;dw_2.
+\end{equation}
+Здесь $g(\epsilon), A(\epsilon)$ - регулярные функции. Если взять интеграл, то
+\begin{equation}
+  \label{eq:142}
+  f\approx g_1 (\epsilon)+c\epsilon^2 \ln(e)
+\end{equation}
+Тогда для теплоемкости имеем
+\begin{equation}
+  \label{eq:143}
+  c\propto \ln|T-T_c|
+\end{equation}
+То есть мы подтвердили, что критический индекс $\alpha=0$ (см.
+таблицу \ref{tab:diagrams}).
+Вычисление других критических индексов также возможно, но сопряжено с техническими трудностями.
+Мы не будем его проделывать, так как в следующих лекциях мы легко сможем вычислить корреляторы из конформной теории поля.
+\section{Лекция 7. Конформная группа.}
+\label{sec:lecture-7}
+
+Построение Каданова-Вильсона (см.
+лекцию \ref{sec:kadanoff-procedure}) обосновало нам масштабную инвариантность модели Изинга.
+Сейчас мы обсудим, какие ограничения накладывает на теорию конформная инвариантность, а затем покажем, что в двух измерениях она следует из масштабной, трансляционной и вращательной инвариантностей.
+
 \bibliography{2dqft}{}

### 2010-11-18 AffineLieAlgebras/InformalNotes/article.tex
Incorporate V.D. changes of 12.11

@@
 %\usepackage[russian]{babel}
-\usepackage{cmap}
+%\usepackage{cmap}
 \usepackage{color}
 \usepackage{graphicx}
-\usepackage{epstopdf}
+%\usepackage{epstopdf}
 %\usepackage{graphicx}
@@
 \newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
+\newcommand{\gf}{\mathfrak{g}}
 \newcommand{\af}{\mathfrak{a}}
 \newcommand{\afb}{\mathfrak{a}_{\bot}}
+\newcommand{\hf}{\mathfrak{h}}
+\newcommand{\hfb}{\mathfrak{h}_{\bot}}
 
@@
 
-\title{Recursive algorithms, branching coefficients and applications}
+\title{Recursive algorithms and branching for nonmaximal embeddings}
 \author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
@@
 \begin{abstract}
-  Recurrent relations for branching coefficients in affine Lie algebras integrable highest weight modules are studied.
-The decomposition algorithm based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive subalgebra.
-We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original ones.
+  Recurrent relations for branching coefficients in affine Lie algebras
+  integrable highest weight modules are studied. The decomposition algorithm
+  based on the injection fan technique is developed for the case of reductive
+  subalgebra. In particular we consider the situations where
+  the Weyl denominator becomes singular with respect to the subalgebra.
+  We study the modifications of the injection fan technique and demonstrate
+  that for any reductive subalgebra it is possible to define the
+  "subtracted fan" -- the tool that describes
+  explicitly the recurrent properties of branching coefficients.
   Possible applications of subtracted fans in CFT models are considered.
@@
 
-There exist several different approaches to deal with the branching coefficients. Some of them use the BGG
+There exist different approaches to deal with the branching coefficients. Some of them use the BGG
 resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
@@
 
-Usually only the maximal reductive subalgebras are considered since the case of non-maximal subalgebra
-can be obtained using the chain of maximal injections. In this paper we find the recurrent properties
-for branching coefficients that generalize the relations obtained earlier (see the paper \cite{ilyin812pbc}
-and the references therein) to the case of non-maximal reductive subalgebra. The result is formulated in
-terms of the new injection fan called "the subtracted fan". Using this new tools we formulate a simple and
-explicit algorithm for computations of branching coefficients which is applicable to the non-maximal
+Usually only the maximal reductive subalgebras $\frak{a} \subset \frak{g} $ are considered since the case of non-maximal subalgebra
+can be obtained using the chain of maximal injections. In this paper we find out that the recurrent properties
+for branching coefficients can be explicitly formulated for an arbitrary reductive subalgebra.
+The principal point is to consider the subalgebra $\af$ together with its
+counterpart $\afb$ "orthogonal" to $\af$ with respect to the Killing form.
+For any reductive $\af$ the subalgebra $\afb \subset \frak{g} $ is a regular and reductive.
+For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
+$\left(  \af, \afb \right)$ we consider
+%In the the group algebra $\mathcal{E}\left( \frak{g} \right)$ we consider
+the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
+in the Weyl character formula
+$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite{humphreys1978rth})
+the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
+We prove that for any highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
+$\left(  \af, \afb \right)$ the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
+the set of Weyl numerators of $\afb$.
+This decomposition provides the possibility to construct the recurrent property for the branching coefficients corresponding
+to the injection $\frak{a} \longrightarrow \frak{g} $.
+This property is formulated in
+terms of a specific element of the group algebra $\mathcal{E}\left( \frak{g} \right)$ called "the subtracted injection fan".
+Using this tool we formulate a simple and
+explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or non-maximal)
 subalgebras of finite-dimensional and affine Lie algebras.
+In the case of maximal embedding the corresponding fan becomes unsubtracted and the recurrent relations described
+earlier (see the paper \cite{ilyin812pbc}
+and the references therein) are reobtained.
 
@@
 
-The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the notations.
-In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous
+The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the general notations.
+In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula for
+the subtracted recurrent formula for anomalous
 branching coefficients and describe the decomposition algorithm for integrable highest weight modules
@@
 \frak{g}}$ (resp. $\co{\af}$);
-$\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);
 
@@
 
-$M \left( \mbox{resp. }M_{\af}\right) :=$
-
-\noindent $=\left\{
-\begin{array}{c}
-\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\mbox{ }\left( \mbox{resp. }%
-\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \af\right) i}^{\vee }\right)
-\mbox{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
-\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\mbox{ }\left( \mbox{resp. }\sum_{i=1}^{r}%
-\mathbf{Z}\alpha _{\left( \af\right) i}\right) \mbox{for }A_{r}^{\left(
-u\geq 2\right) }\mbox{ and }A\neq A_{2r}^{\left( 2\right) },
-\end{array}
-\right\} ;$\\
-$\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
-$\Psi _{\left( \af\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho
-_{_{\af}})-\rho _{_{\af}}}$ --- the corresponding singular weight
-element for the $\af$-module $L_{\af}^{\nu }$;
-
-$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
-a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
-\xi \in P$ $\left( \mbox{resp. }\in P_{\af}\right) $ for the module $%
-L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right) $ with the
-coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
-\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
-)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
-w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
-\circ (\nu +\rho _{a})-\rho _{a}}$ );
+%$M \left( \mbox{resp. }M_{\af}\right) :=$
+
+%\noindent $=\left\{
+%\begin{array}{c}
+%\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\mbox{ }\left( \mbox{resp. }%
+%\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \af\right) i}^{\vee }\right)
+%\mbox{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
+%\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\mbox{ }\left( \mbox{resp. }\sum_{i=1}^{r}%
+%\mathbf{Z}\alpha _{\left( \af\right) i}\right) \mbox{for }A_{r}^{\left(
+%u\geq 2\right) }\mbox{ and }A\neq A_{2r}^{\left( 2\right) },
+%\end{array}
+%\right\} ;$\\
+
+%$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
+%a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
+%\xi \in P$ $\left( \mbox{resp. }\in P_{\af}\right) $ for the module $%
+%L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right) $ with the
+%coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
+%\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
+%)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
+%w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
+%\circ (\nu +\rho _{a})-\rho _{a}}$ );
 
@@
 +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
-\mathrm{{mult}\left( \alpha \right) }}}=\frac{\Psi ^{\left( \mu \right) }}{%
-\Psi ^{\left( 0\right) }}$ --- the Weyl-Kac formula;
+\mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;
 
 $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
-mult}\left( \alpha \right) }}=\Psi ^{\left( 0\right) }\quad $;
-
-\noindent $\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
+mult}\left( \alpha \right) }}\quad $
+$\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
 \af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
-\left( \alpha \right) }}=\Psi _{\af}^{\left( 0\right) }\right) $--- the
-denominator;
-
-$ L_{\frak{g}\downarrow \af}^{\mu }=\bigoplus
-\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }$
- --- the module decomposition with respect to $\af\longrightarrow \frak{g}$;
-
-$b^{(\mu)}_{\nu}$ --- the branching coefficients,
-
-\begin{equation}
-  \label{eq:21}
-  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
-        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\af}}k_{\lambda
-  }^{\left( \mu \right) }e^{\lambda };
-\end{equation}
-
- $k_{\lambda}$ --- the anomalous branching coefficients, notice that
-\begin{equation}
-%  \label{eq:20}
-  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}};
-\label{eq:21-1}
-\end{equation}
-
-$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$ --- the embedding index.
-
-\section{Recurrent relation for branching coefficients.}
+\left( \alpha \right) }}\right) $--- the
+denominator.
+
+\section{Recurrent relations for branching coefficients.}
 \label{sec:recurr-form-branch}
 
-Let $\af\subset \frak{g}$ be a regular subalgebra of $\frak{g.}$
-Applying the Weyl-Kac character formula to the branching rule $\pi _{\af%
-}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu
-)}ch\left( L_{\af}^{\nu }\right) $ we get the relation connecting the
-singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{\left( \af%
-\right) }^{\left( \nu \right) }$ :
+Consider the integrable module $L^{\mu }$
+of $\frak{g}$ with the highest weight $\mu $ and
+let $\af\subset \frak{g}$ be a reductive subalgebra of $\frak{g}$.
+With respect to $\af$ the module $L^{\mu }$ is completely reducible,
+\begin{equation*}
+ L_{\frak{g}\downarrow \af}^{\mu }=\bigoplus
+\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
+\end{equation*}
+Using the projection operator $\pi_{\af}$ (to the weight space $\frak{h_a}^*$)
+one can  rewrite this decomposition in terms of formal characters:
+\begin{equation}
+\label{branching1}
+ \pi _{\af}\circ ch\left( L^{\mu }\right)
+ =\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu)}ch\left( L_{\af}^{\nu }\right) .
+\end{equation}
+We are interested in branching coefficients $b^{(\mu)}_{\nu}$.
+
+\subsection{Orthogonal subalgebra and injection fan.}
+\label{subsec:branching-orthog-pair}
+
+In this subsection we shall introduce some simple constructions that will be used
+in our studies of branching and in particular the "orthogonal partner" $\afb$ for a
+reductive subalgebra $\af$  in  $\gf$.
+
+In the Weyl-Kac formula both numerator and denominator  can be considered
+as formal elements containing the singular weights of the Verma modules $V^{\xi}$
+with the highest weights $\xi=\mu$ and $\xi=0$ \cite{humphreys1978rth}.
+We attribute singular numerators to the corresponding integrable modules $L^{\mu }$
+and $L_{\af}^{\nu }$:
+\begin{equation*}
+\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho },
+\end{equation*}
+\begin{equation*}
+\Psi _{ \af}^{\left( \nu \right) }:=
+\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho
+_{_{\af}})-\rho _{_{\af}}}.
+\end{equation*}
+and use the Weyl-Kac formula in the form
+\begin{equation}
+\label{Weyl-Kac2}
+ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}
+{\Psi ^{\left( 0 \right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
+\end{equation}
+
+Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
+we get the relation connecting the
+singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{ \af}^{\left( \nu \right) }$ :
 \begin{eqnarray}
+\nonumber
 \pi _{\af}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w
@@
 \pi _{\af}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
-&=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\left( \frak{%
-a}\right) }^{\left( \nu \right) }}{R_{\af}}.
+&=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{ \frak{%
+a}}^{\left( \nu \right) }}{R_{\af}}.
 \end{eqnarray}
-where according to our notations $\Delta _{\af}^{+}$ is the set of
-positive roots of the subalgebra $\af$ (it is convenient to choose them
-from the positive root subspace of $\frak{g}$). Consider the root space $%
-\frak{h}_{\perp \af}^{\ast }$ orthogonal to $\Delta _{\af}$,
-\begin{equation*}
-\frak{h}_{\perp \af}^{\ast }=:\left\{ \eta \in \frak{h}_{\frak{g}%
-}^{\ast }|\forall \alpha \in \Delta _{\af};\alpha \bot \eta \right\} ,
+Here $\Delta _{\af}^{+}$ is the set of
+positive roots of the subalgebra $\af$ (without loss of generality we consider
+them as vectors from the positive root space $\frak{h}^{\ast  +}$ of $\frak{g}$).
+
+Consider the root subspace
+$\frak{h}_{\perp \af}^{\ast }$ orthogonal to the roots in $\Delta _{\af}$,
+\begin{equation*}
+\frak{h}_{\perp \af}^{\ast }=:\left\{ \eta \in \frak{h}^{\ast }
+|\forall \alpha \in \Delta _{\af};\alpha \bot \eta \right\} ,
 \end{equation*}
@@
 \end{eqnarray*}
-
-The algebras $\af$ and $\af_{\perp }$ form an ''orthogonal pair''
-of subalgebras in $\frak{g}$. For the Cartan subalgebras we have the
-decomposition
+Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
+$\left( \af,\af_{\perp}\right) $
+of subalgebras in $\frak{g}$.
+
+For the Cartan subalgebras we have the decomposition
 \begin{equation}
@@
 \end{equation}
-For the subalgebras of the orthogonal pair $\left( \af,\af_{\perp
+For the subalgebras of an orthogonal pair $\left( \af,\af_{\perp
 }\right) $ we consider the corresponding Weyl vectors, $\rho _{\af}$
@@
 \begin{equation}
+\label{defect-perp}
 \mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi _{\af%
-_{\perp }}\rho .
+_{\perp }}\circ\rho .
 \end{equation}
 For the highest weight module $L_{\frak{g}}^{\mu }$ consider the singular
-weights $\left( w(\mu +\rho )-\rho \right) \in \widehat{\Psi ^{\left( \mu
-\right) }}$ and their projections to $h_{\widetilde{\af_{\perp }}%
-}^{\ast }$ (additionally shifted by $-\mathcal{D}_{\af_{\perp }}$):
+weights $\left\{\left( w(\mu +\rho )-\rho \right)|w  \in W \right\}$ and
+their projections to $h_{\widetilde{\af_{\perp }}}^{\ast }$ (additionally
+shifted by the defect $-\mathcal{D}_{\af_{\perp }}$):
 \begin{equation*}
 \mu _{\widetilde{\af_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
-a}_{\perp }}}\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp
+a}_{\perp }}}\circ\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp
 }},\quad w\in W.
 \end{equation*}
-Among the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right)
-|_{w\in W}$ choose those located in the fundamental chamber $\overline{C_{%
+Among the weights $\left\{\mu _{\widetilde{\af_{\perp }}}\left( w\right)
+|w\in W\right\}$ choose those located in the fundamental chamber $\overline{C_{%
 \widetilde{\af_{\perp }}}}$ and let $U$ be the set of representatives $%
@@
 \begin{equation*}
-\mu _{\af}\left( u\right) :=\pi _{\af}\left[ u(\mu +\rho )-\rho %
+\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho %
 \right] +\mathcal{D}_{\af_{\perp }}.
 \end{equation*}
+To simplify the form of relations we shall now on omit the sign "$\circ$" in projected
+weights.
 
@@
 \end{definition}
-
-The main result is that the Weyl-Kac character formula (in terms of singular
+In the next subsection we shall see how the injection fan defines the recurrent
+properties of branching coefficients. It must be noticed that the injection fan is
+the universal instrument that depend only on the injection.
+
+\subsection{Decomposing the singular element.}
+\label{subsec:decomp-sing-element}
+
+Now we shall prove that the Weyl-Kac character formula (in terms of singular
 elements) describes the particular case of a more general relation:
@@
 \begin{lemma}
-Let $\af$ and $\af_{\perp }$ be the orthogonal pair of regular
+Let $\left( \af,\afb \right)$ be the orthogonal pair of reductive
 subalgebras in $\frak{g}$, with $\widetilde{\af_{\perp }}=\af%
@@
 
-$L_{\frak{g}}^{\mu }$ be the highest weight module with the singular element
-$\Psi _{\frak{g}}^{\mu }$ ,
+$L^{\mu }$ be the highest weight module with the singular element
+$\Psi ^{\left(\mu \right)}$ ,
 
@@
 \af_{\perp }}}\right) $ can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
-the singular elements $e^{\mu _{\af}\left( u\right) }$ with the
+the singular weights $e^{\mu _{\af}\left( u\right) }$ with the
 coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
@@
 \begin{equation}
-\quad \pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af%
-_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{\af}\left(
-u\right) }\mathrm{\dim }\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
-\widetilde{\af_{\perp }}}\left( u\right) }\right) .
+\quad \pi _{\af}\left( \frac{\Psi^{\mu }}{R_{\af%
+_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }
+\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
+\widetilde{\af_{\perp }}}\left( u\right) }\right) e^{\mu _{\af}\left( u \right) }.
 \end{equation}
@@
 \begin{proof}
-For $u\in $ $U$ \ perform the following decompositions:
-\begin{equation*}
-u(\mu +\rho )=\pi _{\left( \af\right) }u(\mu +\rho )+\pi _{\left(
-\widetilde{\af_{\perp }}\right) }u(\mu +\rho )
-\end{equation*}
-\begin{equation*}
-vu(\mu +\rho )-\rho =\pi _{\left( \af\right) }\left( u(\mu +\rho
-)\right) -\rho +\rho _{\af_{\perp }}+v\left( \pi _{\left( \widetilde{%
+With $u\in U $   and $v\in W_{\afb}$ perform the decomposition
+\begin{equation*}
+u(\mu +\rho )=\pi _{\left( \af\right) } u(\mu +\rho )+\pi _{\left(
+\widetilde{\af_{\perp }}\right) } u(\mu +\rho )
+\end{equation*}
+for the singular weight $vu(\mu +\rho )-\rho$:
+\begin{equation}
+\label{sing-decomp-1}
+\begin{array}{lcl}
+vu(\mu +\rho )-\rho &=&\pi _{\left( \af\right) }\left( u(\mu +\rho
+)\right) -\rho +\rho _{\af_{\perp }}+\pi _{\left( \hfb\right) }\rho \\
+&& + \ v\left( \pi _{\left( \widetilde{%
 \af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
-\af_{\perp }}\right) -\rho _{\af_{\perp }}
-\end{equation*}
-Use these formulas to decompose the anomalous element $\Psi _{\frak{g}}^{\mu
-}$ of the module $L_{\frak{g}}^{\mu }$ into the linear combination of
+\af_{\perp }}\right) -\rho _{\af_{\perp }} -\pi _{\left( \hfb\right) }\rho.
+\end{array}
+\end{equation}
+Use the defect $\mathcal{D}_{\afb}$ (\ref{defect-perp}) to simplify
+the first summand in (\ref{sing-decomp-1}):
+\begin{equation*}
+\begin{array}{r}
+\pi _{\left( \af\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
+\mathfrak{a}_{\perp }}+\pi _{\left( \hfb\right) }\rho = \\
+\pi _{\left( \af\right) }\left( u(\mu +\rho )\right) -\pi _{\af}\rho
+-\pi _{\afb}\rho +\rho _{\afb}= \\
+\pi _{\left( \af\right) }\left( u(\mu +\rho )-\rho \right) +%
+\mathcal{D}_{\afb},
+\end{array}
+\end{equation*}
+and the second one:
+\begin{equation*}
+\begin{array}{c}
+v\left( \pi _{\left( \widetilde{%
+\af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
+\af_{\perp }}\right) -\rho _{\af_{\perp }}-\pi _{\left( \hfb\right) }\rho=\\
+v\left( \pi _{\left( \widetilde{%
+\afb}\right) }u(\mu +\rho )
+- \mathcal{D}_{\afb} - \pi _{\left( \afb\right) }\rho-\pi _{\left( \hfb\right) }\rho
++\rho _{\afb}\right) -\rho _{\afb}=\\
+v\left( \pi _{\left( \widetilde{%
+\afb}\right) }\left[ u(\mu +\rho )-\rho\right]
+- \mathcal{D}_{\afb}
++\rho _{\afb}\right) -\rho _{\afb}.
+\end{array}
+\end{equation*}
+These expressions provide a kind of a factorization in the anomalous element $\Psi^{\mu
+}$ and we find in it the combination of
 anomalous elements $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ of the
@@
 \begin{array}{l}
-\Psi _{\frak{g}}^{\mu }=\sum_{v\in W_{\af_{\perp }}}\sum_{u\in
-U}\epsilon (v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
-=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left( u(\mu +\rho )\right)
--\rho +\rho _{\af_{\perp }}}\sum_{v\in W_{\af_{\perp }}}\epsilon
-(v)e^{v\left( \pi _{\left( \widetilde{\af_{\perp }}\right) }u(\mu +\rho
-)-\rho _{\af_{\perp }}+\rho _{\af_{\perp }}\right) -\rho _{\af%
-_{\perp }}}= \\
-=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left( u(\mu +\rho )\right) -\pi
-_{\frak{h}_{\perp }}\rho -\pi _{\af}\rho +\mathcal{D}_{\af_{\perp
-}}}\sum_{v\in W_{\af_{\perp }}}\epsilon (v)e^{v\left( \pi _{\left(
-\widetilde{\af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp
-}}+\rho _{\af_{\perp }}\right) -\rho _{\af_{\perp }}}= \\
-=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]
-+\mathcal{D}_{\af_{\perp }}}\sum_{v\in W_{\af_{\perp }}}\epsilon
-(v)e^{v\left( \pi _{\left( \widetilde{\af_{\perp }}\right) }u(\mu +\rho
-)-\rho _{\af_{\perp }}+\rho _{\af_{\perp }}\right) -\pi _{\frak{h}%
-_{\perp }}\rho -\rho _{\af_{\perp }}}= \\
+\Psi^{\mu }=\sum_{u\in U}\sum_{v\in W_{\af_{\perp }}}
+\epsilon (v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
 =\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]
@@
 (v)e^{v\left( \pi _{\left( \widetilde{\af_{\perp }}\right) }\left[
-u(\mu +\rho )-\rho \right] .-\mathcal{D}_{\af_{\perp }}+\rho _{\af%
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}+\rho _{\af%
 _{\perp }}\right) -\rho _{\af_{\perp }}}= \\
@@
 \end{equation*}
+
 Dividing both sides by the Weyl element $R_{\af_{\perp }}=\prod_{\beta
@@
 projecting them to the weight space $h_{\af}^{\ast }$\ we obtain the
-desired relation
+desired relation:
 \begin{eqnarray*}
@@
 \begin{remark}
-This relation is a kind of a generalization of the Weyl formula for singular
+This relation can be considered a generalized form of the Weyl formula for singular
 element $\Psi _{\frak{g}}^{\mu }$ : the vectors $\mu _{\af}\left(
-u\right) $ play the role of singular weights while the determinants $%
-\epsilon (u)$ are changed for $\epsilon (u)\mathrm{\dim }\left( L_{%
+u\right) $ play the role of singular weights while instead of the determinants $%
+\epsilon (u)$ we have the products $\epsilon (u)\mathrm{\dim }\left( L_{%
 \widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left(
@@
 \end{remark}
-Now we can state the main theorem which gives us the instrument for the
-recurrent computation of the branching coefficients.
+
+\subsection{Constructing recurrent relations.}
+\label{subsec:Construct-recurrent-rel}
+
+Consider the right-hand side of relation (\ref{eq:4}).
+The numerator there describes the branching in terms of singular elements and
+it is reasonable to expand it as an element of $\mathcal{E}\left( \frak{g} \right)$:
+\begin{equation}
+  \label{eq:21}
+  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
+        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\af}}k_{\lambda
+  }^{\left( \mu \right) }e^{\lambda }.
+\end{equation}
+Here the coefficients $k_{\lambda}^{\left( \mu \right) }$ are integer and their signes
+depend on the length (see \cite{humphreys1978rth})  of the Weyl group elements in
+$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }$. The important property of
+$k_{\lambda}^{\left( \mu \right) }$'s is that they coinside with the branching coefficients
+for all weights $\nu$ inside the main Weil chamber:
+\begin{equation}
+%  \label{eq:20}
+  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}.
+\label{eq:21-1}
+\end{equation}
+We call the coefficients $k_{\lambda}$ --- the anomalous branching coefficients
+(see also \cite{ilyin812pbc}).
+
+Now we can state the main theorem which gives us an instrument for the
+recurrent computation of branching coefficients.
+
 \begin{theorem}
-  For the anomalous branching coefficients (\ref{eq:21}) holds the recurrent relation
-  \begin{equation}
-    \label{eq:1}
+  For the anomalous branching coefficients $k^{(\mu)}_{\nu}$ (\ref{eq:21})
+  the following relation holds
+  \begin{equation}
     \label{recurrent-relation}
@@
   \end{equation}
-
- As we have mentioned above (see (\ref{eq:21}) and (\ref
-{eq:21-1})) when $\zeta \in \bar{C}_{\af}$ the coefficients $k_{\zeta
-}^{(\mu )}$ coinside with the branching coefficients thus the
-equation for $k_{\zeta }^{(\mu )}$ serve as recurrent relations for branching coefficients.
+\end{theorem}
 \begin{proof}
-To prove the theorem return to the relation (\ref{eq:4}) and rewrite it for the element $\quad
-\frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ ,
-\begin{eqnarray*}
+Redress the relation (\ref{eq:4}) for the element $\quad
+\frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using defenition (\ref{eq:37})
+of the carrier $\Phi _{\af\subset \frak{g}}$ ,
+\begin{equation*}
+\begin{array}{l}
 \pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
-\right)  &=&\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot
+\right)=\\[2mm]
+=\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot
 }^{+}}\left( 1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-%
@@
 \af}^{+}}b_{\nu }^{(\mu )}\sum_{w \in W_{\af}}\epsilon
-(w )e^{w (\nu +\rho _{\af})-\rho _{\af}}\right) = \\
-&=&-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma )e^{-\gamma
+(w )e^{w (\nu +\rho _{\af})-\rho _{\af}}\right) = \\[5mm]
+=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma )e^{-\gamma
 }\left( \sum_{\nu \in P_{\af}^{+},w \in W_{\af}}\epsilon
@@
 }}\right).
-\end{eqnarray*}
-Then decompose the last sum (with respect to the formal basis in $\mathcal{E}$%
+\end{array}
+\end{equation*}
+Then expand the sum in brackets (with respect to the formal basis in $\mathcal{E}$%
 ):
@@
 &=&-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
-\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma },
+\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
 \end{eqnarray*}
-Equate the coefficients of exponents in the last equality to get the following result:
+The immediate consequence of this equality is:
 \begin{equation}
@@
 are subject to the linear relations and the form of these relations changes
-when the tested weight $\xi $ coinsides with one of \ the ''anomalous
-weights'', $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in
+when the tested weight $\xi $ coinsides with one of \ the ''singular
+weights''  $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in
 U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
@@
 \end{proof}
-\end{theorem}
+
 \subsection{Embeddings and orthogonal pairs in simple Lie algebras}
@@
 orthogonal subalgebra is $\af_{\bot }=B_{r-r_{\af}}$. Consider the
-injection $B_{r_{\af}}\rightarrow B_{r},\quad 1<r_{\af}<r$ . By
+injection $B_{r_{\af}}\rightarrow B_{r},\quad 1<r_{\af}<r$. By
 eliminating the simple root $\alpha _{r_{\af}-1}=e_{r_{\af%
@@
 \begin{enumerate}
-\item  Construct the root subsystem $\Delta _{\af}$ for the embedding $%
+\item  Construct the root system $\Delta _{\af}$ for the embedding $%
 \af\rightarrow \frak{g}$.
@@
 \item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
-)-\rho ;\;w \in W\right\} $ of the anomalous weights for the $\frak{g}$%
+)-\rho ;\;w \in W\right\} $ of singular weights for the $\frak{g}$%
 -module $L^{(\mu )}$.
@@
 
-When being interested in the branching coefficients for the embedding of the
-finite-dimensional Lie algebra into the affine Lie algebra we can construct
-the set of the anomalous weights up to the required grade and use the steps
+When being interested in the branching coefficients for the embedding of a
+finite-dimensional Lie algebra into an affine Lie algebra we can construct
+the set of anomalous weights up to a required grade and use the steps
 4-7 of the algorithm for each grade. We can also speed up the algorithm by
@@
 \end{equation}
-Here $x_e$ is the embedding index and $g$, $a$ are the dual Coxeter numbers for the  corresponding algebras.
+Here $x_e$ is the so called "embedding index":
+$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$
+with $\Theta$, $\Theta_{\mathfrak{a}}$ being the highest roots of
+$\mathfrak{g}$ and $\mathfrak{a}$
+while $g$  and $a$ are the  corresponding dual Coxeter numbers.
 

### 2010-11-18 AffineLieAlgebras/DualFunctions/article.tex
I've started to write the paper from the MQFT2010 talk.

@@
 This construction in some sense is not new (e.g.
-see \cite{2010arXiv1001.3683N}), but we explicitly describe the dual system of functions.
+see \cite{2010arXiv1001}), but we explicitly describe the dual system of functions.
 The section \ref{sec:affine-lie-algebras} is devoted to the systems of special functions connected with the affine Lie algebras.
@@
 This procedure was called ``folding of the fan'' in \cite{il2010folded}.
-Now we want to rewrite the equation \eqref{eq:3} in matrix form similarly to \cite{2010arXiv1001.3683N}.
+Now we want to rewrite the equation \eqref{eq:3} in matrix form similarly to \cite{2010arXiv1001}.
 We need to choose the ordering on the set of weights in the closure of fundamental domain $\bar{C}_{\mathfrak{g}}$.

### 2010-11-18 AffineLieAlgebras/InformalNotes/article.tex
I've started to write the paper from the MQFT2010 talk.

@@
 \usepackage{graphicx}
-%\usepackage{epstopdf}
+\usepackage{epstopdf}
 %\usepackage{graphicx}
@@
 in the Weyl character formula
-$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite{humphreys1978rth})
+$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite{humphreys1997introduction})
 the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
@@
 as formal elements containing the singular weights of the Verma modules $V^{\xi}$
-with the highest weights $\xi=\mu$ and $\xi=0$ \cite{humphreys1978rth}.
+with the highest weights $\xi=\mu$ and $\xi=0$ \cite{humphreys1997introduction}.
 We attribute singular numerators to the corresponding integrable modules $L^{\mu }$
@@
 Here the coefficients $k_{\lambda}^{\left( \mu \right) }$ are integer and their signes
-depend on the length (see \cite{humphreys1978rth})  of the Weyl group elements in
+depend on the length (see \cite{humphreys1997introduction})  of the Weyl group elements in
 $\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }$. The important property of

### 2010-11-18 AffineLieAlgebras/MQFT2010/article.tex
I've started to write the paper from the MQFT2010 talk.

\documentclass[12pt]{article}
%\usepackage{ucs}
\usepackage{amsmath,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}

%\usepackage{verbatim}
%\newenvironment{comment}
%{\par\noindent{\bf TODO}\\}
%{\\\hfill$\scriptstyle\blacksquare$\par}

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}

\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}

\begin{document}
\title{Nope}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
%\address{$^{1,2}$ Theoretical Department, SPb State University,
%198904, Sankt-Petersburg, Russia }
%\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}

\begin{abstract}
\end{abstract}

\section{Introduction}
\label{sec:introduction}

\section{Regular subalgebras and generalized Verma modules}
\label{sec:regul-subalg-gener}

Consider finite-dimensional Lie algebra $\mathfrak{g}$  and its regular reductive subalgebra $\af\subset \mathfrak{g}$. Introduce the following objects.
\begin{definition}
  \label{def-1}
  Denote by $\Delta^{+}_{\afb}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\af} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\af$.
\end{definition}

\begin{definition}
  \label{def-2}
  Denote by $W_{\afb}$ the subgroup of the Weyl group $W$ generated by the reflections $w_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\afb}$.
\end{definition}
\begin{mynote}
  The subgroup $W_{\afb}$ preserves $\Delta_{\af}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\af}$.
\end{mynote}
\begin{definition}
  \label{def-3}
  The subsystem $\Delta_{\afb}=\Delta^{+}_{\afb}\cup \left(-\delta^{+}_{\afb}\right)$ determines the subalgebra $\af_{\bot}\subset \mathfrak{g}$.
\end{definition}
Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
}|\forall \alpha \in \Delta _{\af}\cup \Delta _{\af_{\perp
}};\alpha \bot \eta \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
$\left( \af,\af_{\perp}\right) $
of subalgebras in $\frak{g}$.

For the Cartan subalgebras we have the decomposition
\begin{equation}
\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\af_{\perp }}\oplus
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
\af_{\perp }}=\frak{\frak{h}_{\widetilde{\af_{\perp }}}}\oplus
\frak{h}_{\af}.
\end{equation}
For the subalgebras of an orthogonal pair $\left( \af,\af_{\perp
}\right) $ we consider the corresponding Weyl vectors, $\rho _{\af}$
and $\rho _{\af_{\perp }}$ , and\ form the so called ''defects'' $%
\mathcal{D}_{\af}$ and $\mathcal{D}_{\af_{\perp }}$ of the
injection:
\begin{equation}
\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
\end{equation}
\begin{equation}
\label{defect-perp}
\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi _{\af%
_{\perp }}\circ\rho .
\end{equation}
\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
\in \overline{C_{\widetilde{\af_{\perp }}}}\right\} \quad .
\label{U-def}
\end{equation}
For the same set $U$ introduce the weights
\begin{equation*}
\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho %
\right] +\mathcal{D}_{\af_{\perp }}.
\end{equation*}
To simplify the form of relations we shall now on omit the sign "$\circ$" in projected
weights.

Let us state the following lemma.
\begin{lemma}
\label{lemma-1}
The quotient of the singular weights element $\Psi^{(\mu)}$ by the denominator $R_{\af_{\bot}}$ is given by the formal element corresponding to the modified set of the singular weights of $L_{\af\oplus\mathfrak{h}_d}^{(\pi_{\af\oplus\mathfrak{h}_d}\mu)}$ with the multiplicities given by the dimensions of $\af_{\bot}$-modules.
\begin{equation}
  \label{eq:4}
  \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\prod_{\alpha\in \Delta^{+}_{\afb}}\left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=
    \sum_{u\in W/W_{\afb}}\epsilon(u)e^{\pi_{\tilde\af}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \mathrm{ch}_{\af_{\bot}}
      L^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}
\end{equation}
\end{lemma}  
\begin{proof}
  Consider $\Psi^{(\mu)}_{\mathfrak{g}}$. It is given by the sum over the Weyl group.
  \begin{equation}
    \label{eq:6}
    \Psi^{(\mu)}_{\mathfrak{g}}=\sum_{w\in W}\epsilon(w)e^{w(\mu+\rho)-\rho}
  \end{equation}
  We can divide the summation to the sum over $W_{\afb}$ and sum over all the classes of $W/W_{\afb}$: $w=vu,\; v\in W_{\afb},\; u \in W/W_{\afb}$. We have the following obvious property of the projections:
  \begin{equation}
    \label{eq:5}
    u(\mu+\rho)=\pia(u(\mu+\rho))+\piab(u(\mu+\rho))+\pi_{h_{\perp}^*}(u(\mu+\rho))
  \end{equation}
 Since $\mathfrak{h}_{\af}^*,\mathfrak{h}_{\perp}^*$ are invariant under the action of $v\in W_{\afb}$, we have
  \begin{equation}
    \label{eq:8}
    vu(\mu+\rho)-\rho=v\cdot(\piab(u(\mu+\rho))-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}+\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\hf_{\perp}^*}(u(\mu+\rho))
  \end{equation}
  Only the first term depends on $v$. So
  \begin{equation}
    \label{eq:9}
    \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\mathrm{R}_{\afb}}=
    \frac{\sum_{u\in W/W_{\afb}}\epsilon(u)e^{\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\mathfrak{h}_{\perp}}(u(\mu+\rho))}\cdot
      \sum_{v\in W_{\afb}}\epsilon(v)e^{v(\piab u(\mu+\rho)-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}}}{\mathrm{R}_{\afb}}
  \end{equation}
  We can rewrite the r.h.s. as
  \begin{equation}
    \label{eq:10}
    \sum_{u\in W/W_{\afb}}\epsilon(u)e^{\pi_{(\af\oplus\mathfrak{h}_d)}\left[u(\mu+\rho)-\rho\right]+\pi_{(\af\oplus \mathfrak{h}_d)}\cdot \rho-\rho+\rho_{\afb}}\cdot
    \mathrm{ch}_{\afb}L^{\pi_{\afb}u(\mu+\rho)-\rho_{\afb}}.
  \end{equation}
  Since $\pi_{\afb}(u(\mu+\rho)-\rho)-(\rho_{\afb}-\pi_{\afb}\rho)=\pi_{\afb}(u(\mu+\rho)-\rho)-\mathcal{D}$ and $\pi_{\tilde\af}\rho-\rho=-\pi_{\afb}\rho$ we get the statement of the Lemma.

\end{proof}

\begin{corollary}
  \label{sec:corollary-1}
  If we apply the projection $\pi_{\af}$ to the subalgebra $\af$ to the equation (\ref{eq:4}) we obtain the ``Lemma 1'' from the paper \cite{2010arXiv1007.0318L} in the case of regular subalgebras $\af, \afb$. However this Lemma \ref{lemma-2} is more general then Lemma \ref{lemma-1}, since it holds for the special subalgebra $\af$.
\begin{lemma}
\label{lemma-2}
Let $\af$ and $\af_{\perp }$ be the orthogonal pair of regular
subalgebras in $\frak{g}$, with $\widetilde{\af_{\perp }}=\af%
_{\perp }\oplus \frak{h}_{\perp }$ and $\widetilde{\af}=\af\oplus
\frak{h}_{\perp }$ ,

$L_{\frak{g}}^{\mu }$ be the highest weight module with the singular element
$\Psi _{\frak{g}}^{\mu }$ ,

$R_{\af_{\perp }}$ be the Weyl denominator for $\af_{\perp }$.

Then the element $\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{%
\af_{\perp }}}\right) $ can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
the singular elements $e^{\mu _{\af}\left( u\right) }$ with the
coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
}}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right) $:
\begin{equation}
\quad \pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af%
_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{\af}\left(
u\right) }\mathrm{\dim }\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
\widetilde{\af_{\perp }}}\left( u\right) }\right) .
\label{eq:11}
\end{equation}
\end{lemma}
This lemma can be used to state the recurrent relation for the branching coefficients for the reduction of $\gf$-module to $\af$-modules. (See \cite{2010arXiv1007.0318L} for the details). It will be also useful for the discussion of special subalgebras. 
\end{corollary}
\begin{corollary}
  \label{corollary-2}
  Since $\af, \afb$ are regular subalgebras the simple root system $\alpha_1,\dots, \alpha_r$ of $\gf$ can be chosen in such a way that simple roots $\beta_1,\dots,\beta_{r_{\afb}}$ of $\afb$ are contained in it. Denote the set of roots $\beta_i$ by $I$. This notation is in the agreement with the book \cite{humphreys2008representations}.
  \begin{equation*}
    I=\{\beta_1,\dots,\beta_{r_{\afb}}\}\subset \{\alpha_1,\dots,\alpha_r\}
  \end{equation*}
  Then the subset $I$ determines not only the subalgebra $\afb$, but also the minimal parabolic subalgebra $\mathfrak{p}_I$, such that $\afb\subset \mathfrak{p}$. Then we can consider the modules of the subcategory $\mathcal{O}^{\mathfrak{p}}$, for example the generalized Verma modules $M_{\mathfrak{p}}^{(\mu)}$. This modules are constructed from the irreducible highest-weight modules $L_{\pf}^{(\mu)}$ as follows
  \begin{equation}
    \label{eq:1}
    M_{\pf}^{(\mu)}=U(\gf)\otimes_{U(\pf)} L^{(\mu)}_{\pf}
  \end{equation}
  Denote by $\tilde R$ the denominator constructed of the positive roots of $\gf$ which are not the roots of $\afb$.
  \begin{equation}
    \label{eq:2}
    \tilde R = \prod_{\alpha\in \Delta^+\setminus \Delta^{+}_{\afb}} \left(1-e^{-\alpha}\right)^{\mathrm{mult}_{\gf} \alpha}
  \end{equation}
If we expand $\frac{1}{\tilde R}$ the coefficients near the terms $e^{\xi}$ are given by the Kostant partition function $p^I$ constructed from the roots of $\gf$ which are not in $I$. 
The character of the generalized Verma module then can be formally written as
\begin{equation}
  \label{eq:3}
  \mathrm{ch} M^{(\mu)}_{\pf}=\frac{1}{\tilde R} \mathrm{ch}L^{(\mu)}_{\pf}
\end{equation}
The character of the irreducible finite-dimensional $\pf$-module $L^{(\mu)}_{\pf}$ differs from the character of the irreducible finite-dimensional $\afb$-module by the factor $e^{\pi_{\tilde\af}(\mu)}$, since $\pf$ contains the full Cartan subalgebra $\hf\subset\gf$.
Now if we multiply the statement (\ref{eq:4}) of the lemma \ref{lemma-1} by $\frac{1}{\tilde R}$ we get the character of irreducible highest-weight module $L^{(\mu)}$ on the left and the sum of the characters of generalized Verma modules on the right-hand side of the equation:
\begin{multline}
  \label{eq:7}
  \mathrm{ch}L^{(\mu)}_{\gf}=
  \sum_{u\in W/W_{\afb}}\epsilon(u)e^{\pi_{\af\oplus\mathfrak{h}_d}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \frac{1}{\tilde R}\mathrm{ch} L_{\afb}^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}=\\
  \sum_{u \in W/W_{\afb}} \epsilon(u) \mathrm{ch} M^{(u(\mu+\rho)-\rho)}_{\pf}
\end{multline}
So we have recovered the Bernstein-Gelfand-Gelfand resolution \cite{bernstein1975differential} for the parabolic category ${\cal O}^{\pf}$.
\end{corollary}

\section{Generalizations}
\label{sec:generalizations}

\begin{enumerate}
\item If $\af$ is a special subalgebra of $\gf$, the equation (\ref{eq:4}) and the Lemma \ref{lemma-1} no longer holds since the module of the algebra can not be presented as the composition of the modules of the subalgebra. Only the projection of this module can be decomposed. So we have to rely on the Lemma \ref{lemma-2}, which holds in this case too \cite{2010arXiv1007.0318L}.

Again as in the Corollary \ref{corollary-2} we can multiply the equation (\ref{eq:11}) by the (projection of) the denominator $\frac{1}{\tilde R}$. This projection if well-defined due to the construction of $\afb$.
\begin{equation}
  \label{eq:12}
  \pi_{\af}\left(\mathrm{ch} L^{(\mu)}_{\gf}\right)= \sum_{u\in U}\epsilon(u) \pi_{\af}\left(\frac{1}{\tilde R}\right) e^{\mu_{\af}(u)}\mathrm{dim} \left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
\widetilde{\af_{\perp }}}\left( u\right) }\right) .
\end{equation}
Since the subalgebra $\afb$ is regular by construction,  at the right-hand side of the equation we see the generalized Verma module character projected on the root space of $\af$. So we have recovered the equation (\ref{eq:7}) in the projected form.
\begin{equation}
  \label{eq:13}
   \pi_{\af}\left(\mathrm{ch} L^{(\mu)}_{\gf}\right)= \pi_{\af}\left(  \sum_{u \in W/W_{\afb}} \epsilon(u) \mathrm{ch} M^{(u(\mu+\rho)-\rho)}_{\pf}\right)
\end{equation}
We have also lost any trace of subalgebra $\af$. But we can rewrite the left-hand side as the combination of the irreducible highest weight modules of subalgebra $\af$
\begin{equation}
  \label{eq:14}
  \sum_{\nu\in P^{+}_{\af}} b^{(\mu)}_{\nu} \mathrm{ch} L^{(\nu)}_{\af}= \sum_{u \in W/W_{\afb}} \epsilon(u) \pi_{\af}\left(   \mathrm{ch} M^{(u(\mu+\rho)-\rho)}_{\pf}\right)
\end{equation}
Using the Bernstein-Gelfand-Gelfand resolution for the subalgebra $\af$ we get the expression which links the projected characters of generalized Verma modules with the characters of Verma modules of special subalgebra:
\begin{equation}
  \label{eq:15}
  \sum_{\nu\in P^+_{\af}}b^{(\mu)}_{\nu}\sum_{ w\in W_{\af}} \epsilon(w) \mathrm{ch} M_{\af}^{w(\mu+\rho_{\af})-\rho_{\af}} =  \sum_{u \in W/W_{\afb}} \epsilon(u) \pi_{\af}\left(   \mathrm{ch} M^{(u(\mu+\rho)-\rho)}_{\pf}\right)
\end{equation}

\item Also we can generalize the whole construction to affine Lie algebras $\gf, \af$, since Weyl character formula and denominator identity have natural analogs in the theory of affine Lie algebras. The only subtle point is in the definition of projection $\pi$ to the subalgebra. The extension of the Killing form from the finite-dimensional simple Lie algebra $\co{\gf}$ to the affine Lie algebra $\gf$ is not positive-definite. For the imaginary root $\delta$ we have $(\delta,\delta)=0$. If we use this form for the projection to the root space of the affine subalgebra $\af$ we end up with $\delta\perp \beta; \beta\in \Delta_{\af}$ or $\pi_{\af}(n\delta)=0$. This is not what we want.

So we define new positive-definite bilinear form $(\cdot,\cdot)_+$ on the root lattice of $\gf$ by the requirement $(\delta,\delta)_+=1$. This form is only $\co{W}$-invariant. Then we define the projection $\pi_{\af}$ to the root space of the affine subalgebra $\af$ as the extension of the projection to the finite-dimensional subalgebra $\co{\af}$ with the requirement
\begin{equation}
  \label{eq:16}
  \pi_{\af}(\delta)=\delta.
\end{equation}
The orthogonality conditions in the definitions \ref{def-1}, \ref{def-2}, \ref{def-3} are to be understood with the respect to the form $(\cdot,\cdot)_+$. Then Lemma \ref{lemma-1} holds for the affine Lie algebras $\gf, \af$.
\end{enumerate}

\section{Applications}
\label{sec:applications}

\section{Conclusion}
\label{sec:conclusion}

\bibliography{article}{}
\bibliographystyle{utphys}

\end{document}

### 2010-11-19 GeneralOverview/Lectures/2dqft.tex
Some work on the lectures

@@
 
+Сперва рассмотрим конформную группу в произвольном числе измерений $d$.
+Метрический тензор обозначим через $g_{\mu\nu},\; \mu,\nu=1,\dots,d$.
+Конформными называются преобразования $x\to x'$, сохраняющие метрический тензор с точностью до масштаба:
+\begin{equation}
+  \label{eq:123}
+  g'_{\mu\nu}(x')=\Lambda(x) g_{\mu\nu}(x).
+\end{equation}
+Заметим, что группа Пуанкаре является подгруппой конформной группы с $\Lambda(x)=1$, а также что конформные преобразования сохраняют углы.
+
+Рассмотрим инфинитезимальные преобразования
+\begin{equation}
+  \label{eq:144}
+  x^{\mu}\to x'^{\mu}=x^{\mu}+\epsilon^{\mu}.
+\end{equation}
+Метрический тензор преобразуется следующим образом:
+\begin{equation}
+  \label{eq:145}
+  g'_{\mu\nu}=\frac{\partial x^{\alpha}}{\partial x'^{\mu}}\frac{\partial x^{\beta}}{\partial x'^{\nu}} g_{\alpha\beta}=(\delta^{\alpha}_{\mu}-\partial_{\mu}\epsilon^{\alpha})(\delta^{\beta}_{\nu}-\partial_{\nu} \epsilon^{\beta})g_{\alpha\beta}=g_{\mu\nu}-(\partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu})
+\end{equation}
+Перепишем условие (\ref{eq:123})в таком виде:
+\begin{equation}
+  \label{eq:146}
+  g'_{\mu\nu}(x')=g_{\mu\nu}(x)-f(x)g_{\mu\nu}(x)
+\end{equation}
+Отсюда вытекает условие на вид преобразований:
+\begin{equation}
+  \label{eq:147}
+  \partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu}=f(x)g_{\mu\nu}(x).
+\end{equation}
+Для простоты рассмотрим преобразования, действующие на плоскую метрику $g_{\mu\nu}(x)=\eta_{\mu\nu}$, кроме того, с учетом приложений к статистической физике, будем работать в евклидовом пространстве, а не в пространстве Минковского.
+Так что $\eta=\mathrm{diag}(1,1,\dots,1),\quad \eta_{\mu\nu}=\delta_{\mu\nu}$.
+
 \bibliography{2dqft}{}

### 2010-11-20 GeneralOverview/Lectures/2dqft.tex
More on Lecture 7
Lecture 8 started.

--- 2010-11-14 GeneralOverview/Lectures/2dqft.tex
@@
 
+Сперва рассмотрим конформную группу в произвольном числе измерений $d$.
+Метрический тензор обозначим через $g_{\mu\nu},\; \mu,\nu=1,\dots,d$.
+Конформными называются преобразования $x\to x'$, сохраняющие метрический тензор с точностью до масштаба:
+\begin{equation}
+  \label{eq:123}
+  g'_{\mu\nu}(x')=\Lambda(x) g_{\mu\nu}(x).
+\end{equation}
+Заметим, что группа Пуанкаре является подгруппой конформной группы с $\Lambda(x)=1$, а также что конформные преобразования сохраняют углы.
+
+Рассмотрим инфинитезимальные преобразования
+\begin{equation}
+  \label{eq:144}
+  x^{\mu}\to x'^{\mu}=x^{\mu}+\epsilon^{\mu}.
+\end{equation}
+Метрический тензор преобразуется следующим образом:
+\begin{equation}
+  \label{eq:145}
+  g'_{\mu\nu}=\frac{\partial x^{\alpha}}{\partial x'^{\mu}}\frac{\partial x^{\beta}}{\partial x'^{\nu}} g_{\alpha\beta}=(\delta^{\alpha}_{\mu}-\partial_{\mu}\epsilon^{\alpha})(\delta^{\beta}_{\nu}-\partial_{\nu} \epsilon^{\beta})g_{\alpha\beta}=g_{\mu\nu}-(\partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu})
+\end{equation}
+Перепишем условие (\ref{eq:123})в таком виде:
+\begin{equation}
+  \label{eq:146}
+  g'_{\mu\nu}(x')=g_{\mu\nu}(x)-f(x)g_{\mu\nu}(x)
+\end{equation}
+Отсюда вытекает условие на вид преобразований:
+\begin{equation}
+  \label{eq:147}
+  \partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu}=f(x)g_{\mu\nu}(x).
+\end{equation}
+Для простоты рассмотрим преобразования, действующие на плоскую метрику $g_{\mu\nu}(x)=\eta_{\mu\nu}$, кроме того, с учетом приложений к статистической физике, будем работать в евклидовом пространстве, а не в пространстве Минковского.
+Так что $\eta=\mathrm{diag}(1,1,\dots,1),\quad \eta_{\mu\nu}=\delta_{\mu\nu}$.
+В этом случае условие \eqref{eq:147} перепишется в простом виде
+\begin{equation}
+  \label{eq:148}
+  f(x)=\frac{2}{d}\partial_{\rho}\epsilon^{\rho}.
+\end{equation}
+Теперь подставим $g_{\mu\nu}=\eta_{\mu\nu}$ в уравнение \eqref{eq:147} и продиффернцируем:
+\begin{equation}
+  \label{eq:149}
+  \partial_{\rho} \partial_{\mu}\epsilon_{\nu}+\partial_{\rho}\partial_{\nu}\epsilon_{\mu}=\eta_{\mu\nu}\partial_{\rho} f.
+\end{equation}
+Переставим два раза значки и скомбинируем три уравнения в одно:
+\begin{equation}
+  \label{eq:150}
+  2\partial_{\mu}\partial_{\nu}\epsilon_{\rho}=\eta_{\mu\rho}\partial_{\nu} f+\eta_{\nu\rho}\partial_{\mu}f-\eta_{\mu\nu}\partial_{\rho}f
+\end{equation}
+Свернем это уравнение с $\eta^{\mu\nu}$ и получим
+\begin{equation}
+  \label{eq:151}
+  2\partial^2 \epsilon_{\rho}=(2-d)\partial_{\rho}f
+\end{equation}
+Теперь продифференцируем его по $x^{\nu}$ и поменяем значок $\rho$ на $\mu$:
+\begin{equation}
+  \label{eq:152}
+  2\partial^2 \partial_{\nu} \epsilon_{\mu}=(2-d)\partial_{\mu}\partial_{\nu} f
+\end{equation}
+Сравним полученное равенство с результатом применения оператора $\partial^2$ к уравнению \eqref{eq:149}:
+\begin{equation}
+  \label{eq:153}
+  \partial^2 \partial_{\mu}\epsilon_{\nu}+\partial^2 \partial_{\nu}\epsilon_{\mu}=\eta_{\mu\nu}\partial^2 f
+\end{equation}
+Из равенств \eqref{eq:152}, \eqref{eq:153} следует, что
+\begin{equation}
+  \label{eq:154}
+  (2-d)\partial_{\mu}\partial_{\nu}f=\eta_{\mu\nu}\partial^2 f.
+\end{equation}
+Свернув с $\eta^{\mu\nu}$ получим
+\begin{equation}
+  \label{eq:155}
+  (d-1)\partial^2 f =0.
+\end{equation}
+Сразу можно отметить, что при $d=1$ любое гладкое преобразование будет конформным. Рассмотрим случай $d\geq 3$. Функция $f(x)$ должна иметь вид
+\begin{equation}
+  \label{eq:156}
+  f(x)=A+B_{\mu}x^{\mu}.
+\end{equation}
+Тогда из \eqref{eq:148} получаем для $\epsilon$
+\begin{equation}
+  \label{eq:157}
+  \epsilon_{\mu}=a_{\mu}+b_{\mu\nu}x^{\nu} +c_{\mu\nu\rho}x^{\nu}x^{\rho},\quad c_{\mu\nu\rho}=c_{\mu\rho\nu}
+\end{equation}
+Так как равенства \eqref{eq:147}, \eqref{eq:148}, \eqref{eq:150} должны выполняться для любых $x^{\mu}$, то мономы в $\epsilon$ можно рассматривать независимо.
+На $a_{\mu}$ не возникает никаких ограничений.
+Этот член соответствует трансляциям.
+Теперь подставляем линейный член в \eqref{eq:147}, \eqref{eq:148} и получаем условие
+\begin{equation}
+  \label{eq:158}
+  b_{\mu\nu}+b_{\nu\mu}=\frac{2}{d}b^{\lambda}_{\lambda}\eta_{\mu\nu}
+\end{equation}
+То есть $b_{\mu\nu}$ можно записать в виде
+\begin{equation}
+  \label{eq:159}
+  b_{\mu\nu}=\alpha \eta_{\mu\nu} +m_{\mu\nu},\quad m_{\mu\nu}=-m_{\nu\mu}
+\end{equation}
+Первый член соответствует масштабному преобразованию, а второй - повороту. 
+В результате подстановки квадратичного члена $\epsilon$ в \eqref{eq:148}, \eqref{eq:150} получаем следующее условие на $c_{\mu\nu\rho}$:
+\begin{equation}
+  \label{eq:160}
+  c_{\mu\nu\rho}=\eta_{\mu\rho} h_{\nu} +\eta_{\mu\nu}h_{\rho}-\eta_{\nu\rho}h_{\mu}, \quad h_{\mu}=\frac{1}{d} c^{\alpha}_{\alpha\mu}
+\end{equation}
+Ему соответствует преобразование
+\begin{equation}
+  \label{eq:161}
+  x'^{\mu}=x^{\mu}+2 (x^{\nu}h_{\nu})x^{\mu} -h^{\mu} x^{\nu}x_{\nu}
+\end{equation}
+Такое преобразование называется специальным конформным преобразованием.
+Это преобразование можно естественно интерпретировать, если переписать в виде
+\begin{equation}
+  \label{eq:162}
+  \frac{x'^{\mu}}{x'^2}=\frac{x^{\mu}}{x^2}-h^{\mu}.
+\end{equation}
+Видно, что специальное конформное преобразование --- это инверсия, трансляция и обратная инверсия.
+
+Соответствующие конченые конформные преобразования имеют вид
+\begin{eqnarray}
+  \label{eq:163}
+  x'^{\mu}=x^{\mu}+a^{\mu}&\quad \mbox{--- трансляция}\\
+  x'{\mu}=\alpha x^{\mu} &\quad \mbox{--- растяжение}\\
+  x'^{\mu}=m^{\mu}_{\nu} x^{\nu} &\quad \mbox{--- поворот}\\
+  x'^{\mu}=\frac{x^{\mu}-h^{\mu}x^2}{1-2h_{\mu}x^{\mu}+h^2 x^2}  & \quad \begin{array}{c}\mbox{--- специальное конформное}\\ \mbox{ преобразование}\end{array}
+\end{eqnarray}
+
+Теперь выпишем вид генераторов конформных преобразований для скалярного поля. 
+Напомним, что при произвольном конечном преобразовании скалярное поле преобразуется как
+\begin{equation}
+  \label{eq:164}
+  \Phi'(x')=F(\Phi(x)).
+\end{equation}
+При соответствующем инфинитезимальном преобразовании
+\begin{equation}
+  \label{eq:165}
+  x'^{\mu}=x^{\mu}+\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}
+\end{equation}
+скалярное поле преобразуется так:
+\begin{equation}
+  \label{eq:166}
+  \Phi'(x')=\Phi(x)+\omega_a \frac{\delta F}{\delta \omega_a} (x).
+\end{equation}
+Генератор преобразования определяется следующим равенством:
+\begin{equation}
+  \label{eq:167}
+  \delta_{\omega} \Phi(x)=\Phi'(x)-\Phi(x)\equiv -i\omega_a G_a \Phi(x)
+\end{equation}
+(здесь нет суммирования по $a$). Из \eqref{eq:166} получаем действие генератора на скалярное поле:
+\begin{equation}
+  \label{eq:168}
+  iG_a \Phi=\frac{\delta x^{\mu}}{\delta\omega_a} \partial_{\mu}\Phi-\frac{\delta F}{\delta \omega_a}
+\end{equation}
+
+Если мы предположим, что поле $\Phi$ такое поле, которое не меняется при конформных преобразованиях, то есть $F(\Phi)=\Phi$, то мы получим следующий вид для генераторов:
+\begin{eqnarray}
+  \label{eq:169}
+  \mbox{трансляция} & \quad P_{\mu}=-i\partial_{\mu}\\
+  \mbox{поворот} & \quad L_{\mu\nu}=i(x_{\mu}\partial_{\nu}-x_{\nu}\partial{\mu})\\
+  \mbox{растяжение}& \quad D=-ix^{\mu}\partial_{\mu}\\
+  \begin{array}{r}
+  \mbox{специальное конформное}    \\
+  \mbox{преобразование}
+  \end{array}
+  & \quad K_{\mu}=-i(2x_{\mu}x^{\nu}\partial_{\nu}-x^2\partial_{\mu})
+\end{eqnarray}
+Отсюда легко найти коммутационные соотношения алгебры конформных преобразований в случае $d\geq 3$:
+\begin{eqnarray}
+  \label{eq:170}
+  \left[D,P_{\mu}\right]=i P_{\mu}\\
+  \left[D,K_{\mu}\right]=-i K_{\mu}\\
+  \left[K_{\mu},P_{\nu}\right]=2i (\eta_{\mu\nu}D - L_{\mu\nu})\\
+  \left[K_{\rho},L_{\mu\nu}\right]=i(\eta_{\rho\mu}P_{\nu}-\eta_{\rho\nu}P_{\mu})\\
+ \left[L_{\mu\nu},L_{\rho\sigma}\right]=i(\eta_{\nu\rho}L_{\mu\sigma}+\eta_{\mu\sigma}L_{\nu\rho}-\eta_{\mu\rho}L_{\nu\sigma}-\eta_{\nu\sigma}L_{\mu\rho})
+\end{eqnarray}
+Остальные коммутаторы равны нулю.
+Чтобы понять, о какой алгебре идет речь, переопределим генераторы следующим образом. Введем генераторы $J_{ab}, \; a,b=-1,0,\dots,d, J_{ab}=-J_{ba}$:
+\begin{eqnarray}
+  \label{eq:171}
+  J_{\mu\nu}=L_{\mu\nu}\\
+  J_{-1,0}=D\\
+  J_{-1,\mu}=\frac{1}{2}(P_{\mu}-K_{\mu})\\
+  J_{0,\mu}=\frac{1}{2}(P_{\mu}+K_{\mu})
+\end{eqnarray}
+Коммутационные соотношения для таких генераторов запишутся в виде
+\begin{equation}
+  \label{eq:172}
+  \left[J_{ab},J_{cd}\right]=i(\eta_{ad}J_{bc}+\eta_{bc}J_{ad}-\eta_{ac}J_{bd}-\eta_{bd}J_{ac}),
+\end{equation}
+где $\eta_{ab}=\mathrm{diag}(-1,1,\dots,1)$. Видно, что мы получили алгебру $so(d+1,1)$. В случае пространства Минковского была бы $so(d,2)$.
+\section{Лекция 8. Инварианты. Явный вид конформных преобразований полей в $d\geq 3$.}
+\label{sec:lecture-8}
+Обсудим, какой вид могут иметь простейшие инварианты --- $N$-точечные функции $\Gamma(x_1,\dots,x_N)$.
+В силу трансляционной инвариантности они могут зависеть только от модуля разности $|\vec x_i-\vec x_j|$.
+Масштабная инвариантность может сохраняться только отношениями
+\begin{equation}
+  \label{eq:173}
+  \frac{|\vec x_i-\vec x_j|}{|\vec x_k -\vec x_l|}
+\end{equation}
+Но при специальных конформных преобразованиях
+\begin{equation}
+  \label{eq:174}
+  |\vec x'_i-\vec x'_j|=\frac{|\vec x_i-\vec x_j|}{(1-2(\vec h,vec x_i)+h^2x_i^2)^{1/2} (1-2(\vec h,\vec x_j)+h^2 x_j^2)^{1/2}}
+\end{equation}
+Поэтому не обойтись двумя или тремя точками и простейшие инварианты имеют вид
+\begin{eqnarray}
+  \label{eq:175}
+  \frac{|\vec x_1-\vec x_2||\vec x_3-\vec x_4|}{|\vec x_1-\vec x_3||\vec x_{2}-\vec x_{4}|}\\
+  \frac{|\vec x_1-\vec x_2||\vec x_3-\vec x_4|}{|\vec x_2-\vec x_3||\vec x_{1}-\vec x_{4}|}
+\end{eqnarray}
+Всего $N(N-3)/2$ вариантов для $N$ точек.
+
 \bibliography{2dqft}{}

### 2010-11-20 GeneralOverview/Lectures/2dqft.tex
Lecture 8 is completed.

@@
 
+Покажем теперь, как преобразуются поля при конформных преобразованиях.
+Для этого используем метод индуцированных представлений, который можно легко объяснить на примере алгебры Пуанкаре.
+Сначала рассматриваем подалгебру, которая оставляет точку $x=0$ неподвижной.
+Это алгебра группы Лоренца или группы вращений в случае евклидова пространства.
+На поля в точке $x=0$ она действует своими матричными представлениями:
+\begin{equation}
+  \label{eq:176}
+  L_{\mu\nu}\Phi(0)=S_{\mu\nu}\Phi(0)
+\end{equation}
+Затем мы пользуемся коммутационными соотношениями алгебры Пуанкаре и формулой Хаусдорфа
+\begin{equation}
+  \label{eq:177}
+  e^{-A}B e^{A}=B+[B,A]+\frac{1}{2!}[[B,A],A]+\frac{1}{3!}[[[B,A],A],A]+\dots
+\end{equation}
+чтобы вычислить результат переноса в точку $x$:
+\begin{multline}
+  \label{eq:178}
+  L_{\mu\nu}\Phi(x)=e^{ix^{\rho}P_{\rho}}L_{\mu\nu}e^{-i x^{\rho}P_{\rho}}\Phi(x)=\\
+  (S_{\mu\nu}-x_{\mu}P_{\nu}+x_{\nu}P_{\mu})\Phi(x)=\\
+  i(x_{\mu}\partial_{\nu}-x_{\nu}\partial_{\mu})\Phi(x)+S_{\mu\nu}\Phi(x)
+\end{multline}
+Для полной конформной группы подгруппа стабильности точки $x=0$ порождается поворотами, растяжениями и специальными конформными преобразованиями.
+Обозначим представление генераторов через $S_{\mu\nu}, \tilde \Delta, k_{\mu}$ соответственно.
+Они порождают матричное представление усеченной алгебры с коммутационными соотношениями
+\begin{eqnarray}
+  \label{eq:179}
+  \left[\tilde\Delta,S_{\mu\nu}\right]=0\\
+  \left[\tilde \Delta,k_{\mu}\right]=-i k_{\mu}\\
+  \left[k_{\mu},k_{\nu}\right]=0\\
+  \left[k_{\rho},S_{\mu\nu}\right]=i(\eta_{\rho\mu}k_{\nu}-\eta_{\rho\nu}k_{\mu})\\
+  \left[S_{\mu\nu},S_{\rho\sigma}\right]=i(\eta_{\nu\rho}S_{\mu\sigma}+\eta_{\mu\sigma}S_{\nu\rho}-\eta_{\mu\rho}S_{\nu\sigma}-\eta_{\nu\sigma}S_{\mu\rho})
+\end{eqnarray}
+Транляция генераторов дилатации и специальных конформных преобразований дается равенствами
+\begin{eqnarray}
+  \label{eq:180}
+  e^{i x^{\rho}P_{\rho}}D e^{-i x^{\rho}P_{\rho}}=D+x^{\nu}P_{\nu}\\
+  e^{i x^{\rho}P_{\rho}}K_{\mu} e^{-i x^{\rho}P_{\rho}}=K_{\mu}+2x_{\mu}D -2 x^{\nu}L_{\mu\nu}+2x_{\mu}(x^{\nu}P_{\nu})-x^{2 P_{\mu}}
+\end{eqnarray}
+В результате действие этих генераторов на поле имеет вид
+\begin{eqnarray}
+  \label{eq:181}
+  D\Phi(x)=(-ix^{\nu}\partial_{\nu}+\tilde \Delta)\Phi(x)\\
+  K_{\mu}\Phi(x)=(k_{\mu}+2x_{\mu}\tilde\Delta -x^{\nu}S_{\mu\nu}-2ix_{\mu}x^{\nu}\partial_{\nu}+ix^{2} \partial_{\mu})\Phi(x)
+\end{eqnarray}
+
 \bibliography{2dqft}{}

### 2010-11-20 AffineLieAlgebras/InformalNotes/article.tex
More changes from V.D.

@@
   that for any reductive subalgebra it is possible to define the
-  "subtracted fan" -- the tool that describes
+  injection fan -- the tool that describes
   explicitly the recurrent properties of branching coefficients.
@@
 $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
-We prove that for any highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
+We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
 $\left(  \af, \afb \right)$ the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
-the set of Weyl numerators of $\afb$.
+the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
 This decomposition provides the possibility to construct the recurrent property for the branching coefficients corresponding
@@
 This property is formulated in
-terms of a specific element of the group algebra $\mathcal{E}\left( \frak{g} \right)$ called "the subtracted injection fan".
+terms of a specific element of the group algebra $\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
 Using this tool we formulate a simple and
@@
 In the case of maximal embedding the corresponding fan becomes unsubtracted and the recurrent relations described
-earlier (see the paper \cite{ilyin812pbc}
-and the references therein) are reobtained.
+earlier in \cite{ilyin812pbc} are reobtained.
 
@@
 To describe the recurrent properties for branching coefficients $b_{\nu
-}^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc} one of the
-main tools of which is the set of weights $\Gamma _{\af\subset \frak{g}%
+}^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc}. One of the
+main tools is the set of weights $\Gamma _{\af\subset \frak{g}%
 } $ called the injection fan. As far as we consider more general situation
@@
 \right)  &=&\sum_{u\in W/W_{\af_{\perp }}}\;\epsilon (u)e^{\pi _{\frak{a%
-}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af_{\perp }}}\pi _{%
+}}\left[ u(\mu +\rho )-\rho \right] }\pi _{%
 \af}\left( \frac{\Psi _{\widetilde{\af_{\perp }}}^{\pi _{\left(
@@
 _{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
-e^{\mu _{\af}\left( u\right) }.
+e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] }.
 \end{eqnarray*}
@@
       k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-        \sum_{w\in W_{\afb}\backslash W} \epsilon(w)\;
-        {\rm dim}\left(L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}\right)
-        \delta_{\xi-\gamma_0,\pi_{\af}(w(\mu+\rho)-\rho)}+ \right.\\
+        \sum_{u\in U} \epsilon(u)\;
+        \dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
+        _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
+        \delta_{\xi-\gamma_0,\pi_{\af}(u(\mu+\rho)-\rho)}+ \right.\\
       \left.
         +\sum_{\gamma \in
-          \Gamma _{\af\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+          \Gamma _{\af \longrightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi
           +\gamma }^{\left( \mu \right) }\right).
@@
 \begin{proof}
-Redress the relation (\ref{eq:4}) for the element $\quad
+Redress the relation (\ref{eq:4}) for the element $
 \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using defenition (\ref{eq:37})
@@
 \subsection{Embeddings and orthogonal pairs in simple Lie algebras}
+\label{sect-embeddings}
 
@@
     The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is shown by the black vector.
-    The weights of the singular element $\Psi^{(\omega_1)}$ are indicated by the circles and the corresponding determinants $\epsilon(w)$ are shown.}
+    The superscripts of the highest weights
+  $\af_{\perp }^{\mu_{\af_{\perp }}}\left( u\right)$ are the products $\epsilon(w)\dim\left(L_{\af_{\perp }}^{\mu
+_{\af_{\perp }}\left( u\right) }\right)$
+    The weights of the singular element $\Psi^{(\omega_1)}$ are marked by circles with superscripts indicating
+    the corresponding determinants $\epsilon(w)$.}
   \label{fig:B2_A1}
@@
   }
-  \caption{Regular embedding $A_1\subset B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
-    The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is shown by the black vector.
-$\afb=A_1$-modules built on the weights of the singular element $\Psi^{(\omega_1)}$ are shown by dotted lines.
-The dimensions of these modules and the signs of the corresponding determinants $\epsilon(w)$ are shown near the anomalous weights.
-Fundamental weight coordinate of $\af=A_1$ is indicated on the weight subspace of $\af$.
-}
+  \caption{Here in addition to the diagram presented above (Figure(\ref{fig:B2_A1}))
+  the weights of $\afb=A_1$-modules $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$
+  originating in the points $\pi _{\af}\left[ u(\mu +\rho )-\rho \right] $
+are shown by dotted lines.
+    The superscripts over the highest weights  $\mu_{\af_{\perp }}\left( u\right)$
+    are now the products $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.
+    Coordinates along the root $\beta$ are counted in terms of the fundamental weight of $\af$. }
 \label{fig:B2_A1_2}
@@
 
-Let's describe the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ (the black vector in Figure \ref{fig:B2_A1}).
-
-Circles indicate the weights of the singular element $\Psi^{(\omega_1)}$.
-Now we are to factorise the Weyl group $W$ by $W_{\afb}=\left\{w_1\right\}$
-and to construct the set $\left\{w(\mu+\rho)-\rho,\; w\in W_{\afb}\backslash W\right\}$.
-In the Figure \ref{fig:B2_A1_2} the weights of the corresponding
-$\left(\afb=A_1\right)$-modules
-$L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$
-are indicated. Projecting them onto the root space of the subalgebra $\af=A_1$
-we get the anomalous weights and their multiplicities:
-\begin{equation*}
+Let's perform the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$
+($\omega_1$ -- the black vector in Figure \ref{fig:B2_A1}). The root $\alpha_1$ is orthogonal to $\beta$,
+so we have $\Delta_{\perp}^+ = \left\{ \alpha_1 \right\}$.
+According to the defenition (\ref{fan-definition})
+the fan $\Gamma_{A_1\to B_2}$ consists of two weights:
+\begin{equation*}
+  \label{eq:22}
+  \Gamma_{A_1\to B_2}=\left\{ (1;2),\; (2;-1) \right\},
+\end{equation*}
+where the second component is the value of the sign function $s(\gamma)$.
+The singular weights  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$
+are indicated by circles with the superscript $\epsilon\left( w \right)$.
+The space $U$ is the factor $W/W_{\afb}$ where $W_{\afb}=\left\{e,w_1\right\}$.
+This means that the singular weights located above the line generated by $\beta$
+belong to the Weyl chamber $\overline{C_{\widetilde{\af_{\perp }}}}$.
+According to formula (\ref{defect-perp}) in our case $\mathcal{D}_{\af_{\perp }}=0$ and
+$\hf_{\perp }=0$, thus $\left\{ \mu _{\af_{\perp }}\left( w\right)
+=\pi _{\af_{\perp }}\left[ w(\mu +\rho)-\rho \right]\right\}$.
+We have four highest weights of $\af_{\perp }$-modules. In terms of
+$\af_{\perp }$-fundamental weight $\frac{1}{2} \alpha_1$ these highest weights
+$\left\{ \mu _{\af_{\perp }}\left( u\right)
+=\pi _{\af_{\perp }}\left[ u(\mu +\rho)-\rho \right]| u \in U \right\}$
+ are
+$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$. To
+visualize the procedure we indicate explicitly in Figure (\ref{fig:B2_A1_2}) how the
+corresponding weight diagrams
+$\left\{ \mathcal{N}_{\af_{\perp }}^{\mu _{\af_{\perp }}\left( u\right) }\right\} $
+are attached to the set of $\af$-weights
+$\left\{ \mu _{\af}\left( u\right)\right\} =\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]\right\}
+=\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$.
+In fact we do not need the
+weight diagrams but only the dimensions of the corresponding modules
+$L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ multiplied by
+$\epsilon \left( u\right) $. The obtained values are to be placed in $P_{\af}$ at the points
+$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$ to
+produce the set of singular weights with anomalous multiplicities:
+\begin{equation}
   \label{eq:25}
-  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2).
-\end{equation*}
-For the set $\Gamma$ (using the definition \ref{fan-definition}) we have
+  \left\{(1;2),\; (0;-3),\; (-4;3),\; (-5;-2)\right\}.
+\end{equation}
+According to the defenition (\ref{fan-definition})
+the fan $\Gamma_{A_1\to B_2}$ consists of two weights:
 \begin{equation*}
   \label{eq:22}
-  \Gamma_{A_1\subset B_2}=\left\{ (1,2),\; (2,-1) \right\}.
-\end{equation*}
-Here the second component denotes the value of $s(\gamma)$.
-Applying this fan inside the $\bar{C}^{(0)}_{\af}$ we get zeros for the weights
-greater than the first anomalous vector $(1)$, here $k^{(1,0)}_1=2$. For the last weight in $\bar{C}^{(0)}_{\af}$ the formula (\ref{recurrent-relation}) gives
+  \Gamma_{A_1\to B_2}=\left\{ (1;2),\; (2;-1) \right\},
+\end{equation*}
+where the second component of the weight is the value of the sign function $s(\gamma)$.
+
+Applying formula (\ref{recurrent-relation}) with the fan
+$\Gamma_{A_1\to B_2}$ to the set (\ref{eq:25})
+we get zeros for the weights
+greater than the highest anomalous vector $(1;2)$
+and $k^{(1,0)}_1=2$ for the vector $(1;2)$ itself.
+For the anomalous weight (0;-3) on the boundary of $\bar{C}^{(0)}_{\af}$ the recurrent relation gives
 \begin{equation*}
   \label{eq:23}
-  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1.
-\end{equation*}
-The recurrence property defines the branching.
-
-\subsection{Embedding of $B_2$ into $B_4$}
+  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1,
+\end{equation*}
+the branching is completed: $L_{B_2\downarrow A_1}^{\omega_1}=
+2L_{A_1}^{\omega_{\left(A_1\right)1} }
+\bigoplus
+L_{A_1}^{2\omega_{\left(A_1\right)1} }$.
+
+\subsection{Embedding $B_2$ into $B_4$}
 \label{sec:someth-high-dimens}
@@
   \includegraphics[width=50mm]{figure3.eps}
-  \caption{The regular embedding $B_2\subset B_4$ described by dropping the node from the Dynkin diagram. Note, that $\afb$ is equal to $B_2$, not to $A_1\oplus A_1$ seen at the diagram.}
+  \caption{The regular embedding $B_2 \longrightarrow B_4$ described by dropping the node from the Dynkin diagram.
+  Remember that here $\afb$ is equal to $B_2$ while the diagram
+  shows only $A_1\oplus A_1$ (see Subsection \ref{sect-embeddings}).}
   \label{fig:dynkin}
@@
     \includegraphics[width=100mm,height=90mm]{figure4.eps}
-  \caption{Projected singular weights of $-\frac{1}{s(\gamma_0)}\pi_{B_2}\left(\hat \Psi^{(0,1,0,2)}_{B_4}\right)$
-  with the dimensions of the corresponding $\afb=B_2$-modules.}
+  \caption{The weight subspace $P_{\af}$ for $\af=B_2$ with the basis $\left\{e_3,e_4\right\}$.
+  The set of projected singular weights $\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] +\gamma_0 | u \in U \right\}$
+  shifted by $\gamma_0$. Each weight is supplied by the multiplier
+  $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.}
   \label{fig:B4B2anom}
@@
   \includegraphics[height=80mm]{figure5.eps}
-  \caption{The fan $\Gamma_{B_2\subset B_4}$ for $B_2\subset B_4$. The values $s(\gamma+\gamma_0)$ are shown in the corresponding weights $\gamma$.}
+  \caption{The fan $\Gamma$ for $B_2\longrightarrow B_4$ and the values of $s(\gamma+\gamma_0)$ for the weights $\gamma$.}
   \label{fig:B4B2Fan}
@@
 
-In the orthogonal basis $\left\{e_1,\dots,e_4\right\}$ the simple roots and the positive roots of $B_4$ are
+In the orthogonal basis $\left\{e_1,\dots,e_4\right\}$ simple roots and positive roots of $B_4$ are
 \begin{equation*}
   \label{eq:8}
- S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\}
+ S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\},
 \end{equation*}
@@
 \end{eqnarray*}
-Correspondingly for the embedded subalgebra $\af=B_2$ we have
+The subalgebra $\af=B_2$ is fixed by the simple roots
 \begin{equation*}
@@
 \end{equation*}
-and
-\begin{equation*}
+Its orthogonal counterpart $\afb=B_2$ has
+\begin{eqnarray*}
   \label{eq:27}
- \Delta^{+}_{\afb}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}
-\end{equation*}
-is the set of positive roots for the algebra $\afb=B_2$.
-
-Using the definition (\ref{fan-defined}) we obtain the fan
-$\Gamma_{B_2\subset B_4}$ with the corresponding values $s(\gamma+\gamma_0)$,
-depicted in the Figure \ref{fig:B4B2Fan}.
-
-Consider the $B_4$-module $L^{\mu}$ with the highest weight $\mu=(0,1,0,2)=2
-e_1 + 2 e_2 + e_3 + e_4$; $\mathrm{dim}(L^{(0,1,0,2)})=2772$.
-To find the branching coefficients we need to compute the anomalous weights of
-$L^{\mu}_{B_4}$, select the weights belonging to $\bar{C}^{\left( 0 \right)}_{\afb}$
-and compute the dimensions of the corresponding $\afb$-modules.
-The set of the anomalous weights $\left\{ w(\mu+\rho)-\rho,\; w\in W\right\}$
-contains 384 vectors.
-
-We are to select the weights $\psi \in w(\mu+\rho)$  with the property
-$\pi_{\afb} \left(  \psi \right) \in \bar{C}^{\left( 0 \right)}_{\afb}$.
-It means that the scalar product of these weights with all the roots in $\Delta^{+}_{\afb}$ is nonnegative.
-
-To compute the dimensions of the corresponding
-$\afb$-modules we need to project each selected weight
-onto the root space $\Delta^{+}_{\afb}$, subtract
-$\rho_{\afb}$ and apply the Weyl dimension formula. The result is shown in the Figure \ref{fig:B4B2anom}.
-
-Applying the recurrent relation (\ref{recurrent-relation}) we obtain the
-following branching coefficients:
+  S_{\afb}=\{e_1-e_2,e_2\},\\
+ \Delta^{+}_{\afb}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}.
+\end{eqnarray*}
+As far as the set $\Delta^+_{B_4} \setminus \left(\Delta^{+}_{\af} \cup \Delta^{+}_{\afb}\right)$ is fixed the injection
+fan $\Gamma_{B_2 \to B_4}$ can be constructed (using formulas (\ref{eq:6},\ref{eq:37},\ref{fan-defined})).
+As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need just the factor
+ $s\left(\gamma + \gamma_0\right)$.
+The result is presented in Figure \ref{fig:B4B2Fan}.
+
+Consider the $B_4$-module $L^{\mu}$ with the highest weight $\mu=2e_1 + 2 e_2 + e_3 + e_4$; \,
+$\mathrm{dim}(L^{\left[0,1,0,2\right]})=2772$.
+The set of singular weights for $B_4$ contains 384 vectors.
+Here the defect is nontrivial, $\mathcal{D}_{\af_{\perp }}=-2\left( e_1 + e_2 \right)$,
+while $\hf_{\bot}=0$.
+Taking this into account we find among the singular weights
+48 vectors with the property $\left\{ \mu _{\af_{\perp }%
+}\left( u\right) =\pi _{\af_{\perp }}\left[ u(\mu +\rho
+)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\af_{\perp }}}\right\} $,
+scalar products of these weights with all the roots in $\Delta^{+}_{\afb}$ are nonnegative.
+The set $U=\left\{ u \right\}$ is thus fixed.
+Compute the dimensions of the corresponding $\afb$-modules with the highest weights
+$ \mu _{\af_{\perp }}\left( u\right)$ (using the Weyl dimension formula) and multiply them
+by $\epsilon\left( u \right)$. The results are shown in the Figure \ref{fig:B4B2anom}.
+
+Now one can place the fan $\Gamma$ from Figure \ref{fig:B4B2Fan} in the highest of the weights
+presented in Figure \ref{fig:B4B2anom} and start the recursive determination of the branching coefficients
+(using relation (\ref{recurrent-relation})):
 \begin{eqnarray*}
   \label{eq:24}
-  \pi_{\af} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
-  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+\\
-  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}.
+  \pi_{\af} \left(ch L^{\left[0,1,0,2\right]}_{B_4}\right) = 6 \; ch L^{\left[0,0\right]}_{B_2}+ 60
+  \; ch L_{B_2}^{\left[0,2\right]}+ 30 \; ch L_{B_2}^{\left[1,0\right]}+ 19 \; ch L_{B_2}^{\left[2,0\right]}+\\
+  40 \; ch L_{B_2}^{\left[1,2\right]}+ 10 \; ch L_{B_2}^{\left[0,4\right]}.
 \end{eqnarray*}

### 2010-11-23 AffineLieAlgebras/InformalNotes/article.tex
Some work with pictures
New changes from V.D.

@@
   integrable highest weight modules are studied. The decomposition algorithm
-  based on the injection fan technique is developed for the case of reductive
-  subalgebra. In particular we consider the situations where
+  based on the injection fan technique is developed for the case of an arbitrary
+  reductive subalgebra. In particular we consider the situation where
   the Weyl denominator becomes singular with respect to the subalgebra.
-  We study the modifications of the injection fan technique and demonstrate
+  We study the modifications of the fan technique and demonstrate
   that for any reductive subalgebra it is possible to define the
@@
   explicitly the recurrent properties of branching coefficients.
-  Possible applications of subtracted fans in CFT models are considered.
+  Possible applications of fan technique in CFT models are considered.
 \end{abstract}
@@
 
-Usually only the maximal reductive subalgebras $\frak{a} \subset \frak{g} $ are considered since the case of non-maximal subalgebra
+Usually only maximal reductive subalgebras $\frak{a} \subset \frak{g} $ are considered since the case of non-maximal subalgebra
 can be obtained using the chain of maximal injections. In this paper we find out that the recurrent properties
@@
 counterpart $\afb$ "orthogonal" to $\af$ with respect to the Killing form.
-For any reductive $\af$ the subalgebra $\afb \subset \frak{g} $ is a regular and reductive.
+For any reductive algebra $\af$ the subalgebra $\afb \subset \frak{g} $ is regular and reductive.
 For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
@@
 $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
-We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
+We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair
 $\left(  \af, \afb \right)$ the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
 the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
-This decomposition provides the possibility to construct the recurrent property for the branching coefficients corresponding
+This decomposition provides the possibility to construct the recurrent property for branching coefficients corresponding
 to the injection $\frak{a} \longrightarrow \frak{g} $.
@@
 Using this tool we formulate a simple and
-explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or non-maximal)
+explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
 subalgebras of finite-dimensional and affine Lie algebras.
@@
 The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the general notations.
-In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula for
-the subtracted recurrent formula for anomalous
-branching coefficients and describe the decomposition algorithm for integrable highest weight modules
+In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula based on
+recurrent properties of anomalous branching coefficients and describe the decomposition algorithm
+for integrable highest weight modules
 $L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
@@
 \af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
-\left( \alpha \right) }}\right) $--- the
-denominator.
+\left( \alpha \right) }}\right) $--- the Weyl denominator.
 
@@
 with the highest weights $\xi=\mu$ and $\xi=0$ \cite{humphreys1997introduction}.
-We attribute singular numerators to the corresponding integrable modules $L^{\mu }$
+We attribute singular elements to the corresponding integrable modules $L^{\mu }$
 and $L_{\af}^{\nu }$:
@@
 Consider the root subspace
-$\frak{h}_{\perp \af}^{\ast }$ orthogonal to the roots in $\Delta _{\af}$,
+$\frak{h}_{\perp \af}^{\ast }$ orthogonal to  $\af$,
 \begin{equation*}
 \frak{h}_{\perp \af}^{\ast }=:\left\{ \eta \in \frak{h}^{\ast }
-|\forall \alpha \in \Delta _{\af};\alpha \bot \eta \right\} ,
+|\forall h \in \hf_{\af};  \eta\left(h \right)=0 \right\} ,
 \end{equation*}
 and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
-to $\Delta _{\af}$,
+to $\af$,
 \begin{eqnarray*}
-\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
-\alpha \in \Delta _{\af};\alpha \bot \beta \right\} , \\
+\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|
+\forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} , \\
 \Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
-}^{+}|\forall \alpha ^{+}\in \Delta _{\af}^{+};\alpha ^{+}\bot \beta
-^{+}\right\} .
+}^{+}|\forall h \in \hf_{\af};  \beta^{+}\left(h \right)=0  \right\} .
 \end{eqnarray*}
@@
 \frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
-}|\forall \alpha \in \Delta _{\af}\cup \Delta _{\af_{\perp
-}};\alpha \bot \eta \right\}
+}|\forall h \in \hf_{\af\oplus \af_{\perp}}; \eta \left( h \right)=0 \right\}
 \end{equation*}
@@
 }^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc}. One of the
-main tools is the set of weights $\Gamma _{\af\subset \frak{g}%
-} $ called the injection fan. As far as we consider more general situation
-(where the injection is not maximal) the notion of the injection fan is
+main tools is the set of weights $\Gamma _{\af\rightarrow \frak{g}%
+} $ called the injection fan. As far as we consider the general situation
+(where the injection is not necessarily maximal) the notion of the injection fan is
 modified:
@@
 \begin{equation}
-\Gamma _{\af\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
 \af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
@@
 -\pi _{\afb}\rho +\rho _{\afb}= \\
-\pi _{\left( \af\right) }\left( u(\mu +\rho )-\rho \right) +%
+=\pi _{\left( \af\right) }\left( u(\mu +\rho )-\rho \right) +%
 \mathcal{D}_{\afb},
@@
 +\rho _{\afb}\right) -\rho _{\afb}=\\
-v\left( \pi _{\left( \widetilde{%
+=v\left( \pi _{\left( \widetilde{%
 \afb}\right) }\left[ u(\mu +\rho )-\rho\right]
@@
         +\sum_{\gamma \in
-          \Gamma _{\af \longrightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi
           +\gamma }^{\left( \mu \right) }\right).
@@
 \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using defenition (\ref{eq:37})
-of the carrier $\Phi _{\af\subset \frak{g}}$ ,
+for the carrier $\Phi _{\af\subset \frak{g}}$ ,
 \begin{equation*}
 \begin{array}{l}
-\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
-\right)=\\[2mm]
-=\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot
-}^{+}}\left( 1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-%
-\mathrm{mult}_{\af}(\pi _{\af}\alpha )}\left( \sum_{\nu \in P_{%
-\af}^{+}}b_{\nu }^{(\mu )}\sum_{w \in W_{\af}}\epsilon
-(w )e^{w (\nu +\rho _{\af})-\rho _{\af}}\right) = \\[5mm]
-=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma )e^{-\gamma
-}\left( \sum_{\nu \in P_{\af}^{+},w \in W_{\af}}\epsilon
-(w )b_{\nu }^{(\mu )}e^{w (\nu +\rho _{\af})-\rho _{\af%
-}}\right).
+\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
+\right) = \\[2mm]
+=\prod\limits_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left(
+1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{%
+\af}(\pi _{\af}\alpha )}\left( \sum\limits_{\nu \in P_{\af%
+}^{+}}b_{\nu }^{(\mu )}\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w(\nu
++\rho _{\af})-\rho _{\af}}\right) = \\[5mm]
+=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
+)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
+}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
+}}\right)  \\
+=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
+)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
+}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
+}}\right) .
 \end{array}
 \end{equation*}
+
 Then expand the sum in brackets (with respect to the formal basis in $\mathcal{E}$%
@@
 }\subset \frak{g}}$ and pass to the summation over the vectors of the
-injection fan $\Gamma _{\af\subset \frak{g}}$ (see the definition \ref
+injection fan $\Gamma _{\af\rightarrow \frak{g}}$ (see the definition \ref
 {fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
@@
 
-\item  Select the positive roots $\alpha \in \Delta ^{+}$ orthogonal to the
-roots in $\Delta _{\af}$ i.e. form the set $\Delta _{\bot }^{+}$.
+\item  Select the positive roots $\alpha \in \Delta ^{+}$ orthogonal
+to  $\af$, i.e. form the set $\Delta _{\bot }^{+}$.
 
@@
 }\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
-\af_{\perp }}}}$ (by computing its scalar product with the roots from $%
-\Delta _{\bot }^{+}$).
+\af_{\perp }}}}$ (by computing its scalar product with the fundamental
+weights of $\afb^{+}$).
 
@@
 L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
-}\left( u\right) }\right) $.
+}\left( u\right) }\right) $ using the Weyl dimension formula.
 
@@
     The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is shown by the black vector.
-    The superscripts of the highest weights
-  $\af_{\perp }^{\mu_{\af_{\perp }}}\left( u\right)$ are the products $\epsilon(w)\dim\left(L_{\af_{\perp }}^{\mu
-_{\af_{\perp }}\left( u\right) }\right)$
     The weights of the singular element $\Psi^{(\omega_1)}$ are marked by circles with superscripts indicating
@@
   \caption{Here in addition to the diagram presented above (Figure(\ref{fig:B2_A1}))
-  the weights of $\afb=A_1$-modules $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$
+  the weights of $\left( \afb=A_1 \right)$-modules $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$
   originating in the points $\pi _{\af}\left[ u(\mu +\rho )-\rho \right] $
@@
 so we have $\Delta_{\perp}^+ = \left\{ \alpha_1 \right\}$.
-According to the defenition (\ref{fan-definition})
+According to the definition (\ref{fan-definition})
 the fan $\Gamma_{A_1\to B_2}$ consists of two weights:
@@
 belong to the Weyl chamber $\overline{C_{\widetilde{\af_{\perp }}}}$.
-According to formula (\ref{defect-perp}) in our case $\mathcal{D}_{\af_{\perp }}=0$ and
+According to formula (\ref{defect-perp}) in our case we have $\mathcal{D}_{\af_{\perp }}=0$ and
 $\hf_{\perp }=0$, thus $\left\{ \mu _{\af_{\perp }}\left( w\right)
 =\pi _{\af_{\perp }}\left[ w(\mu +\rho)-\rho \right]\right\}$.
-We have four highest weights of $\af_{\perp }$-modules. In terms of
+We obtain four highest weights for $\af_{\perp }$-modules. In terms of
 $\af_{\perp }$-fundamental weight $\frac{1}{2} \alpha_1$ these highest weights
@@
 the branching is completed: $L_{B_2\downarrow A_1}^{\omega_1}=
-2L_{A_1}^{\omega_{\left(A_1\right)1} }
+2L_{A_1}^{\omega_{\left(A_1\right)} }
 \bigoplus
-L_{A_1}^{2\omega_{\left(A_1\right)1} }$.
+L_{A_1}^{2\omega_{\left(A_1\right)} }$.
 
@@
 \label{sec:someth-high-dimens}
-Consider the regular embedding $B_2 \longrightarrow B_4$.
+Consider the regular embedding $B_2 \rightarrow B_4$.
 The corresponding Dynkin diagrams are presented in the Figure \ref{fig:dynkin}.
@@
   \includegraphics[width=50mm]{figure3.eps}
-  \caption{The regular embedding $B_2 \longrightarrow B_4$ described by dropping the node from the Dynkin diagram.
+  \caption{The regular embedding $B_2 \rightarrow B_4$ described by dropping the node from the Dynkin diagram.
   Remember that here $\afb$ is equal to $B_2$ while the diagram
@@
   \includegraphics[height=80mm]{figure5.eps}
-  \caption{The fan $\Gamma$ for $B_2\longrightarrow B_4$ and the values of $s(\gamma+\gamma_0)$ for the weights $\gamma$.}
+  \caption{The fan $\Gamma$ for $B_2\rightarrow B_4$ and the values of $s(\gamma+\gamma_0)$ for the weights $\gamma$.}
   \label{fig:B4B2Fan}
@@
 
-In the orthogonal basis $\left\{e_1,\dots,e_4\right\}$ simple roots and positive roots of $B_4$ are
-\begin{equation*}
-  \label{eq:8}
- S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\},
-\end{equation*}
+In the orthonormal basis $\left\{e_1,\dots,e_4\right\}$ simple roots and positive roots of $B_4$ are
 \begin{eqnarray*}
   \label{eq:19}
+  S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\},\\[2mm]
  \Delta^+_{B_4}=\left\{ (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\right.\\
@@
 As far as the set $\Delta^+_{B_4} \setminus \left(\Delta^{+}_{\af} \cup \Delta^{+}_{\afb}\right)$ is fixed the injection
-fan $\Gamma_{B_2 \to B_4}$ can be constructed (using formulas (\ref{eq:6},\ref{eq:37},\ref{fan-defined})).
+fan $\Gamma_{B_2 \to B_4}$ can be constructed (using formulas (\ref{eq:6} -- \ref{fan-defined})).
 As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need just the factor
@@
 $ \mu _{\af_{\perp }}\left( u\right)$ (using the Weyl dimension formula) and multiply them
-by $\epsilon\left( u \right)$. The results are shown in the Figure \ref{fig:B4B2anom}.
+by $\epsilon\left( u \right)$. The results are shown in Figure \ref{fig:B4B2anom}.
 
@@
 on the torus and higher genus Riemann surfaces. It is important for the applications of
-CFT to the string theory and to the critical phenomena description.
+CFT to string theory and to critical phenomena description.
 
 The simplest modular-invariant partition function has the diagonal form:
-\begin{equation*}
+\begin{equation}
   \label{eq:34}
    Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
-\end{equation*}
+\end{equation}
 Here the sum is over the set of the highest weights of integrable modules in a WZW-model
-and $\chi_{\mu}(\tau)$ are the normalized characters of these modules.
+and $\chi_{\mu}(\tau)$ are the normalized characters (see \cite{difrancesco1997cft}) of these modules.
 
@@
 Then we can replace the characters of the $\mathfrak{g}$-modules in the diagonal
-modular invariant partition function (\ref{eq:36})
+modular invariant partition function (\ref{eq:34})
 by the decompositions
@@
 \end{equation*}
-containing the modified characters $\chi_{\nu}$ of the corresponding $\af$-modules.
-Thus we obtain the nondiagonal modular-invariant  partition function for the theory with
+containing normalized characters $\chi_{\nu}$ of the corresponding $\af$-modules.
+Thus we obtain a nondiagonal modular-invariant  partition function for the theory with
 the current algebra $\af$,
@@
 \end{equation}
-leads to the equality of the central charges
+leads to the equality of central charges
 \begin{equation*}
@@
 \end{equation*}
-and to the equation
+and to the relation
 \begin{equation}
@@
 
-It can be demonstrated that the solutions of the equation (\ref{eq:111}) exist only
+It can be demonstrated that solutions of equation (\ref{eq:111}) exist only
 for the level $k=1$ \cite{difrancesco1997cft}.
@@
 to prove the finite reducibility theorem \cite{kac1988modular}.
-It states that for the conformal embedding  $\af\subset\mathfrak{g}$
+It states that for a conformal embedding  $\af\longrightarrow\mathfrak{g}$
 only finite number of branching coefficients have nonzero values.
 
-\begin{mynote} The orthogonal subalgebra $\afb$ is always empty for the conformal embeddings $\af\subset \mathfrak{g}$.
+\begin{mynote} The orthogonal subalgebra $\afb$ is always trivial
+for conformal embeddings $\af\longrightarrow \mathfrak{g}$.
 \begin{proof}
@@
 \end{equation*}
-The modes $L_n$ are constructed as combination of normally-ordered products of the generators of $\mathfrak{g}$,
+The modes $L_n$ are constructed as combinations of normally-ordered products of the generators of $\mathfrak{g}$,
 \begin{equation*}
@@
 \end{equation*}
-In the case of a conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
-
-The substitution of the generators of $\af$  in terms of the generators of $\mathfrak{g}$ into these combinations  should give the energy-momentum tensor $T_{\mathfrak{g}}$.
-But if the set of the generators $\Delta_{\afb}$ is not empty this is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\afb}$.
+In case of a conformal embedding energy-momentum tensors $T_{\mathfrak{g}}(z)$ and $T_{\af}(z)$ are
+equal (see (\ref{eq:2})).
+
+Substituting generators of $\af$  in terms of generators of $\mathfrak{g}$ into these combinations
+we must obtain the energy-momentum tensor $T_{\mathfrak{g}}$.
+But if the set of generators attributed to $\Delta_{\afb}$ is not empty this is not possible,
+since $T_{\mathfrak{g}}$ contains generators $X^{\alpha}_n$ for $\alpha\in \Delta_{\afb}$.
 \end{proof}
 \end{mynote}
-\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$.}
+
+\subsubsection{Special embedding $\hat{A}_1\rightarrow\hat{A}_2$.}
 \label{sec:spec-embedd-hata_1s}
 
-Consider the case where both $\mathfrak{g}$ and $\af$ are affine Lie algebras:
-$\hat{A}_1 \longrightarrow \hat{A}_2$ and the injection is the affine extension of the
-special injection $A_1 \longrightarrow A_2$ with the embedding index $x_e=4$.
-As far as the $\mathfrak{g}$-modules to be considered are of level one,
-the $\mathfrak{g}$-modules will be of level $\tilde{k}=kx_e=4$.
-
-There exist three level one fundamental weights in the weight space of $\hat{A}_2$.
+Consider the case where both $\gf$ and $\af$ are affine Lie algebras:
+$\hat{A}_1 \rightarrow \hat{A}_2$ and the injection is the affine extension of the
+special injection $A_1 \rightarrow A_2$ with the embedding index $x_e=4$.
+As far as the $\gf$-modules to be considered are of level one,
+the $\af$-modules will be of level $\tilde{k}=kx_e=4$.
+
+There exist three level one fundamental weights of $\hat{A}_2$.
 It is easy to see that the set $\Delta_{\afb}$ is empty and the subalgebra $\afb=0$.
-
-Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$
-and the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).
+It is convenient to choose the classical root for $\hat{A}_1$ to be
+$\beta_1=\frac{1}{2}(\alpha_1+\alpha_2)$.
+
+Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$.
+In this case $\gamma_0 =0$ its sign $s\left( 0 \right)=-1$ thus we are to use the
+sign function $s(\gamma)$ (see Figure \ref{fig:AffineA2A1Fan}).
 
@@
   \centering
-  \includegraphics[width=135mm]{figure6.eps}
-
-  \caption{The fan $\Gamma_{\hat{A_1}\longrightarrow \hat{A_2}}$ for $\hat{A_1}\longrightarrow \hat{A_2}$.
-Values of  $s(\gamma+\gamma_0)$ are shown for the weights $\gamma\in \Gamma_{\hat{A_1}\longrightarrow \hat{A_2}}$}
+  \includegraphics[width=125mm]{figure6.eps}
+
+  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ for $\hat{A_1}\rightarrow \hat{A_2}$
+  in the basis $\left\{\beta,\delta \right\}$. Notice that $\gamma_0 =0$, so values of $s(\gamma)$
+  are prescribed to the weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$}
   \label{fig:AffineA2A1Fan}
@@
 
-Let us consider the module $L^{\omega_0=(0,0;1;0)}$. Here we use the (finite part; level; grade)
+Consider the module $L^{\omega_0=(0,0;1;0)}$. Here we use the (finite part; level; grade)
 presentation of the highest weight and the finite part
@@
 
-The set $\widehat{\Psi^{(\omega_0)}}$  is depicted in the Figure
+The set $\widehat{\Psi^{(\omega_0)}}$  is displayed in Figure
 \ref{fig:affine_A2_anom_point} up to the sixth grade.
@@
 %  \hspace*{-2cm}
-  \includegraphics[width=140mm]{figure7.eps}
-  \caption{The anomalous weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$. The weights $w (\omega_0+\rho)-\rho$ are marked by crosses when $\epsilon(w)=1$ and
+  \includegraphics[width=135mm]{figure7.eps}
+  \caption{The anomalous weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$.
+  The weights $w (\omega_0+\rho)-\rho$ are marked by crosses when $\epsilon(w)=1$ and
 by diamond when $\epsilon(w)=-1$. Simple roots of the classical subalgebra $A_2$ are
@@
 The next step is to project the anomalous weights to $P_{\hat A_1}$.
-The result is presented in the Figure \ref{fig:AffineA2_A1_anom_proj} up to the twelfth grade.
+The result is presented in Figure \ref{fig:AffineA2_A1_anom_proj} up to the twelfth grade.
 \begin{figure}[h!tb]
@@
   \includegraphics[width=130mm]{figure8.eps}
-  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$. The multiplicities of projected weights and the corresponding signs are shown. }
+  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$ in the basis $\left\{\beta,\delta \right\}$.
+  The multiplicities of projected weights and the corresponding signs are shown. }
   \label{fig:AffineA2_A1_anom_proj}
@@
 
-Using the recurrent relation for the anomalous branching coefficients
+Using the recurrent relation for anomalous branching coefficients
 we get the result presented in Figure \ref{fig:AffineA2_A1_branching}.
@@
   \includegraphics[width=130mm]{figure9.eps}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$. The boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
- are indicated by the black lines. Two nonzero anomalous weights in the main Weyl chamber are marked by stars. Both weights have multiplicity 1, so the branching coefficients are equal to 1.}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$. The boundaries
+  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
+ are indicated by black lines. Two anomalous highest weights located
+ in the main Weyl chamber are marked by stars.
+ Both have multiplicity 1, so the branching coefficients for them are equal one.}
   \label{fig:AffineA2_A1_branching}
@@
 Inside the Weyl chamber $\bar{C}_{\hat{A}_1}$
-(its boundaries are indicated in the Figure \ref{fig:AffineA2_A1_branching})
+(its boundaries are indicated in Figure \ref{fig:AffineA2_A1_branching})
 there are only two nonzero anomalous weights and both have multiplicity 1.
-These are the highest weights of $\af$-submodules and their branching
+These are the highest weights of $\af$-submodules and the multiplicities are their branching
 coefficients. So the finite reducibility theorem holds and we get the decomposition
@@
 Let us return to the example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
-$A_1 \longrightarrow B_2$.
+$A_1 \rightarrow B_2$.
 Since this embedding is regular and $x_e=1$, the subalgebra modules and the initial module are of the same level.
-The set $\Delta^{+}_{\afb}$ of the orthogonal positive roots with the zero projection
-on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.
-
-Using the definition (\ref{fan-defined}) we get the fan
-$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$
-with the corresponding values $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineB2A1Fan}).
+The set  of positive roots with zero projection
+on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case
+$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$.
+
+Using the definition (\ref{fan-defined}) we obtain the fan
+$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
+Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=0$.
+The values of the sign function $s(\gamma)$ for
+$ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ are presented in Figure \ref{fig:AffineB2A1Fan}.
 We restricted the computation to the twelfth grade.
@@
   \includegraphics[width=135mm]{figure10.eps}
-  \caption{The fan $\Gamma_{\hat{A_1}\longrightarrow \hat{B_2}}$ for $\hat{A_1}\longrightarrow \hat{B_2}$.
-Values of  $s(\gamma+\gamma_0)$ are shown for the weights $\gamma\in \Gamma_{\hat{A_1}\longrightarrow \hat{B_2}}$}
+  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$
+  for $\hat{A_1}\rightarrow \hat{B_2}$ in the basis $\left\{\beta,\delta \right\}$. Values of  $s(\gamma)$ are shown for the
+  weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$}
   \label{fig:AffineB2A1Fan}
@@
 The set of anomalous weights for this module up to the sixth grade is presented in the Figure \ref{fig:affine_B2_anom_point}.
-In the grade zero it is exactly the set of the anomalous weights for the embedding of
-the classical Lie algebras $A_1\subset B_2$ that can be seen in the  Figure \ref{fig:B2_A1}.
 
@@
   \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$.
-  The weights in the zero grade can be seen in the Figure \ref{fig:B2_A1}. The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by circles otherwise.
+  The weights in the zero grade are the same as in Figure \ref{fig:B2_A1}.
+  The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by circles otherwise.
 Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
@@
 $\afb$-modules $L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$.
+In the grade zero this is exactly the set of anomalous weights for the embedding of
+the classical Lie algebra $A_1\rightarrow B_2$, to see this compare Figures \ref{fig:B2_A1}
+and \ref{fig:AffineB2_A1_anom_proj}.
 The result is presented in the Figure
@@
 
-Notice that here the lowest weight  $\gamma_0$ of the fan  is zero, since we have excluded all the roots of $\Delta^{+}_{\afb}$ from the defining relation (\ref{fan-defined}).
-
 \begin{figure}[h!bt]
@@
   \includegraphics[width=120mm]{figure13.eps}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$.  The boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
- are indicated by the black lines. The anomalous branching coefficients inside the main Weyl chamber are equal to the branching coefficients of the embedding $\hat{A_1}\longrightarrow \hat{B_2}$.}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$.
+  The boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
+ are indicated by the black lines. The anomalous branching coefficients
+ inside the main Weyl chamber are equal to the branching coefficients of the embedding $\hat{A_1}\rightarrow \hat{B_2}$.}
   \label{fig:AffineB2_A1_branching}
@@
 
-The multiplicities of the weights inside the  Weyl chamber
+The multiplicities of the highest weights inside the  Weyl chamber
 $\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
-are the branching coefficients (up to the twelfth grade),
+define the following branching coefficients (up to the twelfth grade),
 \begin{eqnarray*}
@@
 \label{sec:conclusion}
-We have demonstrated that the injection fan technique can be used to deal with the nonmaximal subalgebras.
-It was found out that for such subalgebras an auxiliary subset $\Delta^{+}_{\afb}$ must be extracted
-from the set of positive roots $\Delta_{\mathfrak{g}}^{+}$.
-The role of the subset $\Delta^{+}_{\afb}$ is to modify both the injection fan (formed here by the
-weights $\left(\Delta_{\mathfrak{g}}^{+} \setminus  \Delta_{\af}^{+}\right) \setminus \Delta^{+}_{\afb}$)
-and the anomalous weights of the initial module.
-This modification reduces to a simple procedure:
-the anomalous weights multiplicities are to be substituted by the dimensions of the corresponding $\afb$-modules.
-
-The efficiency of the injection fan algorithm was verified.
-Its possible applications to some physical problems were discussed.
+We have demonstrated that the injection fan technique can be used to deal with an arbitrary
+reductive subalgebra $\af \subset \gf$ (maximal as well as  nonmaximal).
+To construct the branching rules we used the orthogonal pair $\left( \af,\af_{\perp
+}\right) $ of subalgebras. The orthogonal partner $\afb$ corresponds to the subset
+$\Delta^{+}_{\afb}$ of positive roots $\Delta_{\mathfrak{g}}^{+}$ that trivilize
+the Cartan subalgebra $\hf_{\afb}$.
+Both the injection fan and the set of singular weights of the $\gf$-module depend on the
+subalgebra $\afb$ and its submodules.
+Fortunately no more information on these submodules is necessary than their dimensions.
+The highest weights are fixed by the projections of singular weights of $\gf$-module:
+$\pi _{\widetilde{\frak{%
+a}_{\perp }}}\circ\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp
+}}$.
+The modification of the singular element reduces to a simple procedure:
+the anomalous weights multiplicities are to be substituted by the dimensions of the corresponding $\afb$-modules
+multiplied by the values of $\epsilon (u)$. The fan is defined by the roots that
+do not belong to $\Delta^{+}_{\afb}$ or $\Delta^{+}_{\af}$. As a result we have found
+that for any reductive subalgebra $\af$ the highest weights of submodules and their
+multiplicities are subject to the set of linear equations (\ref{eq:17}).
+This set can be redressed to the form of recurrent relations that can be solved step by step.
+
+The efficiency of the injection fan algorithm was illustrated on various examples.
 In particular we considered the construction of modular-invariant partition functions

### 2010-11-23 AffineLieAlgebras/InformalNotes/article.tex
More work on figures

@@
 It is easy to see that the set $\Delta_{\afb}$ is empty and the subalgebra $\afb=0$.
+Then ${\cal D}_{afb}=0$, $\hf_{\perp}$ is one-dimensional abelian subalgebra and the dimensions of $\tilde\afb=\afb\oplus \hf_{\perp}$ are equal to 1.
 It is convenient to choose the classical root for $\hat{A}_1$ to be
-$\beta_1=\frac{1}{2}(\alpha_1+\alpha_2)$.
+$\beta=\frac{1}{2}(\alpha_1+\alpha_2)$.
 
@@
 \begin{figure}[h!tb]
-%  \hspace*{-2cm}
-  \includegraphics[width=135mm]{figure7.eps}
+  \hspace*{-1.5cm}
+  \includegraphics[width=180mm]{figure7-2.eps}
   \caption{The anomalous weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$.
+In the classical cross-sections we use the orthogonal basis with the unit vector equal to $\alpha_1$.
   The weights $w (\omega_0+\rho)-\rho$ are marked by crosses when $\epsilon(w)=1$ and
-by diamond when $\epsilon(w)=-1$. Simple roots of the classical subalgebra $A_2$ are
+by box when $\epsilon(w)=-1$. Simple roots of the classical subalgebra $A_2$ are
 grey and the grey diagonal plane corresponds to the Cartan subalgebra of
@@
 on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case
-$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$.
+$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$. It is easy to see that $\hf_{\perp}$ is empty in this case and ${\cal D}_{\afb}=0$.
 
@@
 $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
-Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=0$.
+Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=-1$.
 The values of the sign function $s(\gamma)$ for
@@
   \includegraphics[width=140mm]{figure11.eps}
-  \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$.
+  \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$. The standard basis $\{e_1,e_2\}$ is used for the classical cross-section. 
   The weights in the zero grade are the same as in Figure \ref{fig:B2_A1}.
-  The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by circles otherwise.
+  The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by boxes otherwise.
 Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
@@
   \includegraphics[width=120mm]{figure12.eps}
-  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$. The dimensions of the corresponding $\afb=A_1$-modules with the signs $\epsilon(w)$ are shown.}
+  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$.
+The basis $\{\beta,\delta\}$ is used.
+The dimensions of the corresponding $\afb=A_1$-modules with the signs $\epsilon(w)$ are shown.}
   \label{fig:AffineB2_A1_anom_proj}
@@
   \includegraphics[width=120mm]{figure13.eps}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$.
+  \caption{Anomalous branching coefficients for $\hat{A_1}\rightarrow \hat{B_2}$. The basis $\{\beta,\delta\}$ is used.
   The boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$

### 2010-11-26 AffineLieAlgebras/InformalNotes/article.tex
Figure 7 is changed
Minor fix
Version, submitted to the journal

@@
 \usepackage{graphicx}
-\usepackage{epstopdf}
+%\usepackage{epstopdf}
 %\usepackage{graphicx}
@@
 
-\title{Recursive algorithms and branching for nonmaximal embeddings}
+\title{Recursive algorithm and branching for nonmaximal embeddings}
 \author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
@@
   the Weyl denominator becomes singular with respect to the subalgebra.
-  We study the modifications of the fan technique and demonstrate
+  We demonstrate
   that for any reductive subalgebra it is possible to define the
-  injection fan -- the tool that describes
+  injection fan and the analogue of the Weyl numerator -- the tools that describe
   explicitly the recurrent properties of branching coefficients.
-  Possible applications of fan technique in CFT models are considered.
+  Possible applications of the fan technique in CFT models are considered.
 \end{abstract}
@@
 
-There exist different approaches to deal with the branching coefficients. Some of them use the BGG
+There are different approaches to deal with the branching coefficients. Some of them use the BGG
 resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
@@
 
-Usually only maximal reductive subalgebras $\frak{a} \subset \frak{g} $ are considered since the case of non-maximal subalgebra
-can be obtained using the chain of maximal injections. In this paper we find out that the recurrent properties
-for branching coefficients can be explicitly formulated for an arbitrary reductive subalgebra.
+In this paper we prove that
+for an arbitrary reductive subalgebra the branching coefficients are subject to
+the recurrent properties that can be explicitly formulated and that there exists
+an effective and simple algorithm to solve these recurrent relations step by step.
+The basic idea is similar to the one used in \cite{ilyin812pbc} for maximal embeddings.
+In our case the algorithm is essentially different, new properties of singular weights
+are determined to deal with an arbitrary reductive injection $\frak{a} \rightarrow \frak{g}$.
+
 The principal point is to consider the subalgebra $\af$ together with its
-counterpart $\afb$ "orthogonal" to $\af$ with respect to the Killing form.
+counterpart $\afb$ orthogonal to $\af$.
 For any reductive algebra $\af$ the subalgebra $\afb \subset \frak{g} $ is regular and reductive.
@@
 $\left(  \af, \afb \right)$ we consider
-%In the the group algebra $\mathcal{E}\left( \frak{g} \right)$ we consider
 the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
 in the Weyl character formula
-$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite{humphreys1997introduction})
+$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$,
+see for example \cite{humphreys1997introduction})
 the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
-$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
 We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair
-$\left(  \af, \afb \right)$ the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
+$\left(  \af, \afb \right)$ the element
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
 the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
 This decomposition provides the possibility to construct the recurrent property for branching coefficients corresponding
-to the injection $\frak{a} \longrightarrow \frak{g} $.
-This property is formulated in
-terms of a specific element of the group algebra $\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
+to the injection $\frak{a} \rightarrow \frak{g} $.
+The property is formulated in
+terms of a specific element $\Gamma_{\af \rightarrow \gf}$ of the group algebra
+$\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
 Using this tool we formulate a simple and
 explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
-subalgebras of finite-dimensional and affine Lie algebras.
-In the case of maximal embedding the corresponding fan becomes unsubtracted and the recurrent relations described
-earlier in \cite{ilyin812pbc} are reobtained.
-
-We demonstrate that our algorithm can be used in studies of conformal embeddings and coset constructions
-in rational conformal field theory.
-
-The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the general notations.
+subalgebras of finite-dimensional or affine Lie algebras.
+In the case of maximal embedding the corresponding fan is unsubtracted, the singular element
+becomes trivial
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\Psi ^{\left( \mu \right) }_{\left(  \gf\right)}$
+and the relations described earlier in \cite{ilyin812pbc} are reobtained.
+
+We demonstrate that our algorithm is effective and can be used in studies
+of conformal embeddings and coset constructions in rational conformal field theory.
+
+The paper is organized as follows. In the subsection \ref{sec:notation}  we fix the general notations.
 In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula based on
@@
 CFT models are considered in Section \ref{sec:phys-appl}.
-Possible further developments are discussed (Section \ref{sec:conclusion}).
+The general properties of the proposed algorithm and
+possible further developments are discussed (Section \ref{sec:conclusion}).
 
@@
 
-$\alpha _{i}$ , $\left( \alpha _{\left( \af\right) j}\right) $ --- the $i
+$\alpha _{i}$ , $\left( \beta _{j}\right) $ --- the $i
 $-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\af%
@@
 $P$ $\left( \mbox{resp. } P_{\af}\right) $ \ --- the weight lattice;
-
-%$M \left( \mbox{resp. }M_{\af}\right) :=$
-
-%\noindent $=\left\{
-%\begin{array}{c}
-%\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\mbox{ }\left( \mbox{resp. }%
-%\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \af\right) i}^{\vee }\right)
-%\mbox{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
-%\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\mbox{ }\left( \mbox{resp. }\sum_{i=1}^{r}%
-%\mathbf{Z}\alpha _{\left( \af\right) i}\right) \mbox{for }A_{r}^{\left(
-%u\geq 2\right) }\mbox{ and }A\neq A_{2r}^{\left( 2\right) },
-%\end{array}
-%\right\} ;$\\
-
-%$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
-%a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
-%\xi \in P$ $\left( \mbox{resp. }\in P_{\af}\right) $ for the module $%
-%L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right) $ with the
-%coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
-%\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
-%)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
-%w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
-%\circ (\nu +\rho _{a})-\rho _{a}}$ );
 
@@
 \begin{equation*}
-\frak{h}_{\perp \af}^{\ast }=:\left\{ \eta \in \frak{h}^{\ast }
+\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }
 |\forall h \in \hf_{\af};  \eta\left(h \right)=0 \right\} ,
@@
 \begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left( 1-e^{-\pi
 _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
@@
 properties of branching coefficients. It must be noticed that the injection fan is
-the universal instrument that depend only on the injection.
+the universal instrument that depends only on the injection and doesn't depend on 
+the properties of a module.
 
@@
 \begin{lemma}
+\label{lemma}
 Let $\left( \af,\afb \right)$ be the orthogonal pair of reductive
@@
 
-Then the element $\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{%
-\af_{\perp }}}\right) $ can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
+Then the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+=\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}\right) $
+can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
 the singular weights $e^{\mu _{\af}\left( u\right) }$ with the
@@
 \begin{equation}
-\quad \pi _{\af}\left( \frac{\Psi^{\mu }}{R_{\af%
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\quad \pi _{\af}\left( \frac{\Psi^{\mu }}{R_{\af%
 _{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }
@@
 \begin{eqnarray*}
-\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
-\right)  &=&\sum_{u\in W/W_{\af_{\perp }}}\;\epsilon (u)e^{\pi _{\frak{a%
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+&=&\sum_{u\in W/W_{\af_{\perp }}}\;\epsilon (u)e^{\pi _{\frak{a%
 }}\left[ u(\mu +\rho )-\rho \right] }\pi _{%
@@
 \end{equation}
-Here the coefficients $k_{\lambda}^{\left( \mu \right) }$ are integer and their signes
+Here the coefficients $k_{\lambda}^{\left( \mu \right) }$ are integer and their signs
 depend on the length (see \cite{humphreys1997introduction})  of the Weyl group elements in
 $\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }$. The important property of
-$k_{\lambda}^{\left( \mu \right) }$'s is that they coinside with the branching coefficients
+$k_{\lambda}^{\left( \mu \right) }$'s is that they coincide with the branching coefficients
 for all weights $\nu$ inside the main Weil chamber:
@@
 Redress the relation (\ref{eq:4}) for the element $
-\frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using defenition (\ref{eq:37})
+\frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using definition (\ref{eq:37})
 for the carrier $\Phi _{\af\subset \frak{g}}$ ,
@@
 \begin{array}{l}
-\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+=\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
 \right) = \\[2mm]
-=\prod\limits_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left(
+=\prod\limits_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left(
 1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{%
@@
 \begin{equation*}
-\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
-\right) =-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
 )e^{-\gamma }\sum_{\lambda \in P_{\af}}k_{\nu }^{(\mu )}e^{\lambda
@@
 \end{equation*}
-Substitute the expression obtained in the Lemma (in the left-hand side),
+Substitute in the left-hand side the expression obtained in Lemma \ref{lemma},
 \begin{eqnarray*}
-\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
-\right)  &=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left( \mu _{\frak{a%
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left( \mu _{\frak{a%
 }}\left( u\right) \right) }\dim \left( L_{\widetilde{\af_{\perp }}%
@@
 are subject to the linear relations and the form of these relations changes
-when the tested weight $\xi $ coinsides with one of \ the ''singular
+when the tested weight $\xi $ coincides with one of \ the ''singular
 weights''  $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in
@@
 \item  Select the positive roots $\alpha \in \Delta ^{+}$ orthogonal
-to  $\af$, i.e. form the set $\Delta _{\bot }^{+}$.
-
-\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$ (\ref
-{fan-defined}).
+to  $\af$, i.e. form the set $\Delta _{\afb }^{+}$.
+
+\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. The relation
+ (\ref{eq:6}) defines the sign function
+ $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
+ $\gamma_0$ is to be subtracted to get the fan (\ref{fan-defined}):
+ $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}$.
 
@@
 L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
-}\left( u\right) }\right) $ using the Weyl dimension formula.
-
-\item  Calculate the anomalous branching coefficients in the main Weyl
-chamber $\overline{C_{\af}}$ of the subalgebra $\af$ using the
-recurrent relation (\ref{recurrent-relation}).
+}\left( u\right) }\right) $ using the Weyl dimension formula and construct
+the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
+
+\item  Calculate the anomalous branching coefficients using the
+recurrent relation (\ref{recurrent-relation}) and select among them those
+corresponding to the weights in the main Weyl
+chamber $\overline{C_{\af}}$.
 \end{enumerate}
 
-When being interested in the branching coefficients for the embedding of a
-finite-dimensional Lie algebra into an affine Lie algebra we can construct
-the set of anomalous weights up to a required grade and use the steps
-4-7 of the algorithm for each grade. We can also speed up the algorithm by
+We can speed up the algorithm by
 one-time computation of the representatives of the conjugate classes $%
@@
 $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ multiplied by
-$\epsilon \left( u\right) $. The obtained values are to be placed in $P_{\af}$ at the points
-$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$ to
-produce the set of singular weights with anomalous multiplicities:
+$\epsilon \left( u\right) $. The obtained values are to be attributed to the points
+$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$
+in $P_{\af}$. The corresponding element of ${\cal E}_{\af}$ is
+the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
+with the set of weights having anomalous multiplicities:
 \begin{equation}
@@
 \end{equation}
-According to the defenition (\ref{fan-definition})
-the fan $\Gamma_{A_1\to B_2}$ consists of two weights:
-\begin{equation*}
-  \label{eq:22}
-  \Gamma_{A_1\to B_2}=\left\{ (1;2),\; (2;-1) \right\},
-\end{equation*}
-where the second component of the weight is the value of the sign function $s(\gamma)$.
 
@@
     \includegraphics[width=100mm,height=90mm]{figure4.eps}
-  \caption{The weight subspace $P_{\af}$ for $\af=B_2$ with the basis $\left\{e_3,e_4\right\}$.
-  The set of projected singular weights $\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] +\gamma_0 | u \in U \right\}$
-  shifted by $\gamma_0$. Each weight is supplied by the multiplier
+  \caption{The singular element $e^{\gamma_0}\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
+  displayed in the weight subspace $P_{\af}$ for $\af=B_2$ with the basis $\left\{e_3,e_4\right\}$.
+  We see the projected singular weights $\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] +\gamma_0 | u \in U \right\}$
+  shifted by $\gamma_0$ and supplied by the multipliers
   $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.}
@@
 \end{eqnarray*}
-As far as the set $\Delta^+_{B_4} \setminus \left(\Delta^{+}_{\af} \cup \Delta^{+}_{\afb}\right)$ is fixed the injection
-fan $\Gamma_{B_2 \to B_4}$ can be constructed (using formulas (\ref{eq:6} -- \ref{fan-defined})).
+As far as the set $\Delta^+_{B_4} \setminus  \Delta^{+}_{\afb}$ is fixed the injection
+fan $\Gamma_{B_2 \to B_4}$ can be constructed using Definition \ref{fan-defininition}.
 As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need just the factor
@@
 $ \mu _{\af_{\perp }}\left( u\right)$ (using the Weyl dimension formula) and multiply them
-by $\epsilon\left( u \right)$. The results are shown in Figure \ref{fig:B4B2anom}.
+by $\epsilon\left( u \right)$. The result is the singular element
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ shown in Figure \ref{fig:B4B2anom}.
 
@@
 There exist three level one fundamental weights of $\hat{A}_2$.
-It is easy to see that the set $\Delta_{\afb}$ is empty and the subalgebra $\afb=0$.
-Then ${\cal D}_{afb}=0$, $\hf_{\perp}$ is one-dimensional abelian subalgebra and the dimensions of $\tilde\afb=\afb\oplus \hf_{\perp}$ are equal to 1.
+It is easy to see that the set $\Delta_{ \afb }$ is empty and the subalgebra $\afb=0$.
+Then ${\cal D}_{\afb}=0$, $\hf_{\perp}$ is one-dimensional Abelian subalgebra and the dimensions of $\tilde\afb=\afb\oplus \hf_{\perp}$ are equal to 1.
 It is convenient to choose the classical root for $\hat{A}_1$ to be
@@
 
-Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$.
-In this case $\gamma_0 =0$ its sign $s\left( 0 \right)=-1$ thus we are to use the
+Using Definition (\ref{fan-definition})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$.
+In this case $\gamma_0 =0$ and its sign $s\left( 0 \right)=-1$ thus we are to use the
 sign function $s(\gamma)$ (see Figure \ref{fig:AffineA2A1Fan}).
@@
   \hspace*{-1.5cm}
-  \includegraphics[width=180mm]{figure7-2.eps}
-  \caption{The anomalous weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$.
-In the classical cross-sections we use the orthogonal basis with the unit vector equal to $\alpha_1$.
+  \includegraphics[width=180mm]{figure7.eps}
+  \caption{The singular weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$.
+   The classical (grade zero) cross-section of the diagram is shown separately
+   in the right part of the figure.
+  We use the orthogonal basis with the unit vector equal to $\alpha_1$.
   The weights $w (\omega_0+\rho)-\rho$ are marked by crosses when $\epsilon(w)=1$ and
@@
 The next step is  to project the anomalous weights to $P_{\hat A_1}$.
-The result is presented in Figure \ref{fig:AffineA2_A1_anom_proj} up to the twelfth grade.
+The result is the element $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
+presented in Figure \ref{fig:AffineA2_A1_anom_proj} up to the twelfth grade.
 \begin{figure}[h!tb]
@@
   \includegraphics[width=130mm]{figure8.eps}
-  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$ in the basis $\left\{\beta,\delta \right\}$.
-  The multiplicities of projected weights and the corresponding signs are shown. }
+  \caption{The singular element $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
+  displayed in $P_{\hat A_1}$
+  with the basis $\left\{\beta,\delta \right\}$.}
   \label{fig:AffineA2_A1_anom_proj}
@@
 
-Using the recurrent relation for anomalous branching coefficients
-we get the result presented in Figure \ref{fig:AffineA2_A1_branching}.
+Using the recurrent relation (\ref{recurrent-relation}) with the fan
+$\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ and the singular weights in
+$\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
+we get the anomalous branching coefficients presented
+in Figure \ref{fig:AffineA2_A1_branching}.
 \begin{figure}[h!tb]
@@
  in the main Weyl chamber are marked by stars.
- Both have multiplicity 1, so the branching coefficients for them are equal one.}
+ Both have multiplicity 1, so the branching coefficients for them are equal 1.}
   \label{fig:AffineA2_A1_branching}
@@
 These are the highest weights of $\af$-submodules and the multiplicities are their branching
-coefficients. So the finite reducibility theorem holds and we get the decomposition
+coefficients. Thus we get the decomposition
 \begin{equation*}
@@
 \end{equation*}
-
-For the other irreducible modules of level one  we get the trivial
-branching
+The finite reducibility theorem holds.
+
+The same fan $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ can be used for any other highest weight
+module $L^{\mu}_{\hat{A_2}}$. In particular for the irreducible modules of level one  we get the trivial
+branching:
 \begin{equation*}
@@
 \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}.
-The characters in coset models are proportional to the branching functions,
+The characters in coset models are proportional to branching functions,
 \begin{equation}
@@
 \end{equation*}
-The problem of the branching functions construction in the coset models was considered
+The problem of branching functions construction in the coset models was considered
 in  \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.
@@
 on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case
-$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$. It is easy to see that $\hf_{\perp}$ is empty in this case and ${\cal D}_{\afb}=0$.
+$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$ and $\afb=A_1$. It is easy to see that $\hf_{\perp}$
+is trivial in this case and also ${\cal D}_{\afb}=0$.
 
@@
   \includegraphics[width=140mm]{figure11.eps}
-  \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$. The standard basis $\{e_1,e_2\}$ is used for the classical cross-section. 
+  \caption{Singular weights for $L^{(1,0;1;0)}_{\hat B_2 }$. The standard basis $\{e_1,e_2\}$ is used for the classical cross-section.
   The weights in the zero grade are the same as in Figure \ref{fig:B2_A1}.
-  The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by boxes otherwise.
+  The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by boxes for $\epsilon(w)=-1$.
 Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
@@
 $\afb$-modules $L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$.
-In the grade zero this is exactly the set of anomalous weights for the embedding of
-the classical Lie algebra $A_1\rightarrow B_2$, to see this compare Figures \ref{fig:B2_A1}
-and \ref{fig:AffineB2_A1_anom_proj}.
-The result is presented in the Figure
-\ref{fig:AffineB2_A1_anom_proj} up to the twelfth grade.
+In the grade zero this projection gives exactly the set
+$\Psi ^{\left( \mu \right) }_{\left(  A_1, A_1 \right)}$ for the embedding of
+the classical Lie algebra $A_1\rightarrow B_2$. To see this compare Figure \ref{fig:B2_A1}
+with the Figure \ref{fig:AffineB2_A1_anom_proj}
+where the singular element $\Psi ^{\left( \mu \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
+for the affine embedding $\hat{A_1}$ is presented up to the twelfth grade.
 \begin{figure}[h!tb]
@@
   \includegraphics[width=120mm]{figure12.eps}
-  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$.
-The basis $\{\beta,\delta\}$ is used.
-The dimensions of the corresponding $\afb=A_1$-modules with the signs $\epsilon(w)$ are shown.}
+  \caption{The singular element $\Psi ^{\left( \omega_1 \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
+  in the basis $\{\beta,\delta\}$. The dimensions of the corresponding $\afb=A_1$-modules
+  with the signs $\epsilon(u)$ are indicated.}
   \label{fig:AffineB2_A1_anom_proj}
@@
   \label{eq:28}
-  L^{\omega_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{\omega_1}\oplus 1 L_{\hat{A_1}}^{\omega_0}\oplus 4 L_{\hat{A_1}}^{\omega_0-\delta}\oplus\\
-    2 L_{\hat{A_1}}^{\omega_1-\delta}\oplus 8 L_{\hat{A_1}}^{\omega_0-2\delta}\oplus
+  L^{\omega_1}_{\hat{B_2}\downarrow \hat{A_1}}
+  &=&2 L_{\hat{A_1}}^{\omega_1}\oplus 1 L_{\hat{A_1}}^{\omega_0}\oplus 4 L_{\hat{A_1}}^{\omega_0-\delta}\oplus\\
+    &&2 L_{\hat{A_1}}^{\omega_1-\delta}\oplus 8 L_{\hat{A_1}}^{\omega_0-2\delta}\oplus
     8 L_{\hat{A_1}}^{\omega_1-2\delta}\oplus 15 L_{\hat{A_1}}^{\omega_0-3\delta}\oplus\\
-    12 L_{\hat{A_1}}^{\omega_1-3\delta}\oplus 26 L_{\hat{A_1}}^{\omega_1-4\delta}\oplus
+    &&12 L_{\hat{A_1}}^{\omega_1-3\delta}\oplus 26 L_{\hat{A_1}}^{\omega_1-4\delta}\oplus
     29 L_{\hat{A_1}}^{\omega_0-4\delta}\oplus 51 L_{\hat{A_1}}^{\omega_0-5\delta}\oplus\\
-    42 L_{\hat{A_1}}^{\omega_1-5\delta}\oplus 78 L_{\hat{A_1}}^{\omega_1-6\delta}\oplus
+    &&42 L_{\hat{A_1}}^{\omega_1-5\delta}\oplus 78 L_{\hat{A_1}}^{\omega_1-6\delta}\oplus
     85 L_{\hat{A_1}}^{\omega_0-6\delta}\oplus 120 L_{\hat{A_1}}^{\omega_1-7\delta}\oplus\\
-    139 L_{\hat{A_1}}^{\omega_0-7\delta}\oplus 202 L_{\hat{A_1}}^{\omega_1-8\delta}\oplus
+    &&139 L_{\hat{A_1}}^{\omega_0-7\delta}\oplus 202 L_{\hat{A_1}}^{\omega_1-8\delta}\oplus
     222 L_{\hat{A_1}}^{\omega_0-8\delta}\oplus 306 L_{\hat{A_1}}^{\omega_1-9\delta}\oplus\\
-    346 L_{\hat{A_1}}^{\omega_0-9\delta}\oplus 530 L_{\hat{A_1}}^{\omega_0-10\delta}\oplus
+    &&346 L_{\hat{A_1}}^{\omega_0-9\delta}\oplus 530 L_{\hat{A_1}}^{\omega_0-10\delta}\oplus
     482 L_{\hat{A_1}}^{\omega_1-10\delta}\oplus 714 L_{\hat{A_1}}^{\omega_1-11\delta}\oplus\\
-    797 L_{\hat{A_1}}^{\omega_0-11\delta}\oplus 1080 L_{\hat{A_1}}^{\omega_1-12\delta}\oplus
+    &&797 L_{\hat{A_1}}^{\omega_0-11\delta}\oplus 1080 L_{\hat{A_1}}^{\omega_1-12\delta}\oplus
     1180 L_{\hat{A_1}}^{\omega_0-12\delta}\oplus \dots
@@
 
-Now we can use the relation (\ref{eq:31}) to get the expansion of the $B_2/A_1$-coset characters:
+Now we can use the relation (\ref{eq:31}),
 \begin{equation*}
@@
     \chi^{(\omega_1)}_{1}(q)= & q^{\frac{7}{12}}\left( 2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\right. \\
-    & \left. 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots \right)\\
+    & \left. 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots \right),\\
     \chi^{(\omega_1)}_{0}(q) = & q^{\frac{5}{6}}\left(1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\right. \\
-    &\left. 222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\right)
+    &\left. 222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\right),
   \end{array}
 \end{equation*}
-
-Further amelioration of the algorithm can be achieved by using
-the folded fan technique \cite{il2010folded} to get the explicit expression
-for the branching functions and the corresponding coset characters in conformal field theory.
+and thus obtain the expansion of the $B_2/A_1$-coset characters.
 
@@
 We have demonstrated that the injection fan technique can be used to deal with an arbitrary
-reductive subalgebra $\af \subset \gf$ (maximal as well as  nonmaximal).
-To construct the branching rules we used the orthogonal pair $\left( \af,\af_{\perp
-}\right) $ of subalgebras. The orthogonal partner $\afb$ corresponds to the subset
-$\Delta^{+}_{\afb}$ of positive roots $\Delta_{\mathfrak{g}}^{+}$ that trivilize
+reductive subalgebra (maximal as well as  nonmaximal).
+It was shown that the branching problem for $\af \subset \gf$  is tightly connected with
+the properties of the orthogonal partner $ \af_{\perp
+} $ of $\af$. The subalgebra $\afb$ corresponds to the subset
+$\Delta^{+}_{\afb}$ of positive roots in $\Delta_{\mathfrak{g}}^{+}$ that trivialize
 the Cartan subalgebra $\hf_{\afb}$.
-Both the injection fan and the set of singular weights of the $\gf$-module depend on the
-subalgebra $\afb$ and its submodules.
-Fortunately no more information on these submodules is necessary than their dimensions.
-The highest weights are fixed by the projections of singular weights of $\gf$-module:
-$\pi _{\widetilde{\frak{%
-a}_{\perp }}}\circ\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp
-}}$.
-The modification of the singular element reduces to a simple procedure:
-the anomalous weights multiplicities are to be substituted by the dimensions of the corresponding $\afb$-modules
-multiplied by the values of $\epsilon (u)$. The fan is defined by the roots that
-do not belong to $\Delta^{+}_{\afb}$ or $\Delta^{+}_{\af}$. As a result we have found
-that for any reductive subalgebra $\af$ the highest weights of submodules and their
+Both the injection fan and the sets of singular weights for
+the highest weight $\gf$-modules depend substantially on the structure of $\afb$ and its submodules.
+For the fan $\Gamma_{\af\rightarrow \gf}$ this dependence is almost obvious:
+in the element $\Phi_{\af\rightarrow \gf}$ the factors corresponding to the roots
+of $\Delta^{+}_{\afb}$ are eliminated.
+The transformation in the set of projected singular weights is more interesting.
+We have found out that in the new singular element
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ the coefficients depend on the
+the $\afb$-submodules (their highest weights $\mu _{\widetilde{\af_{\perp }}}\left( u\right)$
+are fixed by the injection and by the weights of the initial
+element $\Psi^{\mu}$).
+Fortunately no more information on $L^{\mu _{\widetilde{\af_{\perp }}}\left( u\right)}
+_{\afb}$-submodules is necessary than their dimensions.
+In the new singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
+the weight multiplicities are equal to the dimensions
+$\dim\left(L^{\mu _{\widetilde{\af_{\perp }}}\left( u\right)}_{ \afb }\right)$
+of the corresponding $\afb$-modules
+multiplied by the values $\epsilon (u)$. As a result
+the highest weights of $\af$-submodules and their
 multiplicities are subject to the set of linear equations (\ref{eq:17}).
-This set can be redressed to the form of recurrent relations that can be solved step by step.
-
-The efficiency of the injection fan algorithm was illustrated on various examples.
+These properties are valid for any reductive subalgebra $\af\rightarrow \gf$ and
+the set can be redressed to the form of recurrent relations to be solved step by step.
+
+The efficiency of the obtained algorithm was illustrated in various examples.
 In particular we considered the construction of modular-invariant partition functions
@@
 
+Further amelioration of the algorithm can be achieved by using
+the folded fan technique \cite{il2010folded}. It must be mentioned that even in the case
+of string functions the explicit solution of the corresponding recurrent relations is
+a difficult problem (see \cite{il2010folded} for details). Nevertheless we hope that by
+developing the procedure of folding one could get explicit solutions
+for at least some of branching functions and the corresponding coset characters.
+
 \section{Acknowledgements}
@@
 \end{document}
+
+$\af \subset \gf$

### 2010-11-26 AffineLieAlgebras/InformalNotes/article.tex
Journal version + pdf regen

@@
 As far as the set $\Delta^+_{B_4} \setminus  \Delta^{+}_{\afb}$ is fixed the injection
-fan $\Gamma_{B_2 \to B_4}$ can be constructed using Definition \ref{fan-defininition}.
+fan $\Gamma_{B_2 \to B_4}$ can be constructed using Definition \ref{fan-definition}.
 As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need just the factor

### 2010-11-30 GeneralOverview/Lectures/2dqft.tex
Schur's lemma

@@
 \end{eqnarray}
-Транляция генераторов дилатации и специальных конформных преобразований дается равенствами
+Трансляция генераторов дилатации и специальных конформных преобразований дается равенствами
 \begin{eqnarray}
@@
 \end{eqnarray}
-
+Если требовать, чтобы поле $\Phi(x)$ преобразовывалось по неприводимому представлению группы Лоренца, то по лемме Шура любая матрица, коммутирующая со всеми генераторами $S_{\mu\nu}$ пропорциональна единичной.
+\begin{mynote}
+  {\it Лемма Шура}.
+Оператор, сплетающий неприводимые конечномерные представления группы Ли либо нулевой, либо обратим.
+Эта лемма доказывается в любом учебнике по теории групп Ли, например \cite{голод2001математические}.
+
+  {\it Следствие}.
+Оператор $B$, коммутирующий со всеми операторами конечномерного неприводимого представления, кратен единичному.
+{\it Доказательство}: рассмотрим оператор $B-\lambda I$, он тоже коммутирует со всеми операторами представления.
+Возьмем $\lambda=\lambda_1$, являющееся решением уравнения $\det (B-\lambda I)=0$.
+Тогда оператор $B-\lambda I$ вырожден, и по лемме Шура равен нулю.
+Следовательно $B\propto I$.
+\end{mynote}
 \bibliography{2dqft}{}

### 2010-12-03 GeneralOverview/Lectures/2dqft.tex
Minor changes

@@
 \theoremstyle{definition}
-\newtheorem{mynote}{Note}[section]
+\newtheorem{mynote}{Замечание}[section]
 \theoremstyle{definition}
@@
 \begin{mynote}
+
   {\it Лемма Шура}.
 Оператор, сплетающий неприводимые конечномерные представления группы Ли либо нулевой, либо обратим.
-Эта лемма доказывается в любом учебнике по теории групп Ли, например \cite{голод2001математические}.
-
-  {\it Следствие}.
-Оператор $B$, коммутирующий со всеми операторами конечномерного неприводимого представления, кратен единичному.
+Эта лемма доказывается в любом учебнике по теории групп Ли, например \cite{golod2001}.
+
+  {\it Следствие}. Оператор $B$, коммутирующий со всеми операторами конечномерного неприводимого представления, кратен единичному.
+
   {\it Доказательство}: рассмотрим оператор $B-\lambda I$, он тоже коммутирует со всеми операторами представления.
@@
 \end{mynote}
+
+То есть $\tilde \Delta\propto I$ и $k_{\mu}=0$.
+Тогда $\tilde \Delta =-i \Delta I$, где $\Delta$ -- скейлинговая размерность поля $\Phi$, $\Phi'(\lambda x)=\lambda^{-\Delta}\Phi(x)$.
+Закон преобразования бесспинового поля $\varphi$ при конечных конформных преобразованиях
+\begin{eqnarray}
+  \label{eq:182}
+  x\to x'\\
+  \varphi(x)\to \varphi'(x')=\left|\frac{\partial x'}{\partial x}\right|^{-\Delta/2}\varphi(x)\\
+  \left|\frac{\partial x'}{\partial x}\right|=\Lambda(x)^{-d/2}    \quad\mbox{--- якобиан преобразования}
+\end{eqnarray}
+Поля, которые так преобразуются, называются {\it квазипримарными}.
+
+Заметим, что  вариация действия при конформных преобразованиях определяется тензором энергии импульса:
+\begin{equation}
+  \label{eq:183}
+  \delta S=\int d^{d}x T^{\mu\nu}\partial_{\mu}\epsilon_{\nu}=\frac{1}{2} \int d^{d}x T^{\mu\nu}(\partial_{\mu}\epsilon_{\nu}-\partial_{\nu}\epsilon_{\mu})=\frac{1}{d}\int d^{d}x T^{\mu}_{\mu}\partial_{\rho}\epsilon^{\rho},
+\end{equation}
+где мы использовали равенства \eqref{eq:147}, \eqref{eq:148}.
+То есть бесследовость тензора энергии-импульса ведет к конформной инвариантности классической теории поля.
+В классической теории поля при наличии трансляционной, вращательной и масштабной инвариантности  тензор энергии-импульса часто можно переопределить так, чтобы он был бесследовым.
+То есть конформная инвариантность следует из трансляционной, вращательной и масштабной.
+В случае двумерной квантовой теории поля общего доказательства нет, но конформная инвариантность наблюдается во множестве моделей.
+
+\section{Лекция 9. Корреляторы квазипримарных полей. Тождества Уорда.}
+\label{sec:lecture-9}
+
+Теперь перейдем к квантовой теории поля. Рассмотрим коррелятор квазипримарных полей.
+\begin{equation}
+  \label{eq:184}
+  \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = \frac{1}{Z} \int \mathcal{D} \Phi \phi_{1}(x_{1})\phi_{2}(x_{2}) e^{-S[\Phi]}
+\end{equation}
+
 \bibliography{2dqft}{}

### 2010-12-10 AffineLieAlgebras/MQFT2010/article.tex
Some work on BGG paper

@@
 \label{sec:introduction}
+
+We consider the reduction problem for simple Lie algebra modules.
+We study the reduction of Verma and irreducible finite-dimensional modules of the algebra to the modules of the subalgebra.
+We discuss the connection of the reduction with the Bernstein-Gelfand-Gelfand resolution.
+We show that different structures appear in the process of reduction, for example modules of contracted algebra and generalized Verma modules from parabolic category $\mathcal{O}^{\mathfrak{p}}$.
+
+First of all, consider the following example. 
+Let Lie algebra $\gf$ be $so(5)$ and subalgebra $\af\subset \gf$ be $so(3)$. There are different embeddings of $so(3)\to so(5)$. Here we limit ourselves to the regular ones. 
+The root system of the algebra $so(5)$ consists of 8 roots.
+We denote simple roots by $\alpha_{1}=e_{1}-e_{2}$ and $\alpha_{2}=e_{2}$, where $e_{1},e_{2}$ form standard basis.
+The set of the positive roots is $\Delta^{+}=\left\{\alpha_{1}, \alpha_{1}+\alpha_{2}, \alpha_{1}+2\alpha_{2}, \alpha_{2}\right\}$.
+Each of these roots can be taken as the simple root of the subalgebra $so(3)$.
+At first we consider the subalgebra $so(3)$ with the root space spanned on $\beta=\alpha_{1}+2\alpha_{2}$.
+Verma module $M^{\mu}$ with the highest weight $\mu=\omega_{1}+2\omega_{2}=2\alpha_{1}+3\alpha_{2}$ is shown at Figure \ref{fig:B2_Verma}.
+\begin{figure}[h!bt]
+  \noindent\centering{
+    \includegraphics[width=120mm]{B2_Verma}
+  }
+  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}
+
+  \label{fig:B2_Verma}
+\end{figure}
+
+The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2} for the different regular embeddings $so(3)\to so(5)$.
+Here we can see that the picture depends upon the embedding and looks similar to the Verma modules of some subalgebra.
+\begin{figure}[h!bt]
+  \noindent\centering{
+    \includegraphics[width=120mm]{B2_Verma_Branch2}
+  }
+  \caption{Branching for the Verma modules}
+
+  \label{fig:B2_Verma_Branch2}
+\end{figure}
+In present paper we interpret this branching coefficients as the dimensions of the weight subspaces of the modules of contracted algebras.
+
+The formal character of Verma module is given by the expression
+\begin{equation}
+  \label{eq:17}
+  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left(1-e^{-\alpha}\right)}
+\end{equation}
+The denominator $R=\prod_{\alpha\in \Delta^{+}} \left(1-e^{-\alpha}\right)$ can be rewritten as the sum over the Weyl group of the algebra
+\begin{equation}
+  \label{eq:20}
+  R=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}.
+\end{equation}
+Since we consider the regular embeddings, all the positive roots of the subalgebra $\af$ are in the set of positive roots of the algebra $\gf$, $\Delta^{+}_{\af}\subset \Delta^{+}$.
+Then we can introduce $\tilde R$ and the carrier of its expansion $\Phi$:
+\begin{equation}
+  \label{eq:21}
+  \tilde R=\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\af}} \left( 1 - e^{-\alpha}\right)=-\sum_{\gamma\in \Phi} s(\gamma) e^{-\gamma}
+\end{equation}
+The ordering of roots in $\Delta _{\af}$ induce the
+natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
+the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
+\begin{equation}
+\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
+\label{fan-defined}
+\end{equation}
+is called the \textit{injection fan}.
+
+The root of the subalgebra is among the positive roots of the algebra. So  Verma module can be decomposed into the set of Verma modules of the subalgebra:
+\begin{equation}
+  \label{eq:18}
+  \mathrm{ch}M^{\mu}=\sum_{\nu}b^{(\mu)}_{\nu} e^{\nu-\pi_{\af}\nu} \mathrm{ch}M^{\pi_{\af}\nu}_{\af}
+\end{equation}
+Using the equation \eqref{eq:21} we can write the recurrent relation for the branching coefficients $b^{(\mu)}_{\nu}$:
+\begin{equation}
+  \label{eq:19}
+   b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+        \delta_{\xi-\gamma_0,\mu}
+        +\sum_{\gamma \in
+          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) b_{\xi
+          +\gamma }^{\left( \mu \right) }\right).
+\end{equation}
 
@@
 Then Lemma \ref{lemma-1} holds for the affine Lie algebras $\gf, \af$.
+\item Another case that we need to consider is the of $\afb$ built on the non-simple roots.
 \end{enumerate}

### 2010-12-14 AffineLieAlgebras/MQFT2010/article.tex
More work on MQFT2010 paper

@@
 \author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
-%\address{$^{1,2}$ Theoretical Department, SPb State University,
-%198904, Sankt-Petersburg, Russia }
-%\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}
 
@@
 \section{Introduction}
+
 \label{sec:introduction}
 
-We consider the reduction problem for simple Lie algebra modules.
-We study the reduction of Verma and irreducible finite-dimensional modules of the algebra to the modules of the subalgebra.
-We discuss the connection of the reduction with the Bernstein-Gelfand-Gelfand resolution.
-We show that different structures appear in the process of reduction, for example modules of contracted algebra and generalized Verma modules from parabolic category $\mathcal{O}^{\mathfrak{p}}$.
+The branching properties of Lie (affine Lie) algebras are highly important for
+applications in quantum field theory. This concernes for example the
+conformal field theory models \cite{difrancesco1997cft},\cite
+{coquereaux2008conformal}.
 
-First of all, consider the following example. 
-Let Lie algebra $\gf$ be $so(5)$ and subalgebra $\af\subset \gf$ be $so(3)$. There are different embeddings of $so(3)\to so(5)$. Here we limit ourselves to the regular ones. 
-The root system of the algebra $so(5)$ consists of 8 roots.
-We denote simple roots by $\alpha_{1}=e_{1}-e_{2}$ and $\alpha_{2}=e_{2}$, where $e_{1},e_{2}$ form standard basis.
-The set of the positive roots is $\Delta^{+}=\left\{\alpha_{1}, \alpha_{1}+\alpha_{2}, \alpha_{1}+2\alpha_{2}, \alpha_{2}\right\}$.
-Each of these roots can be taken as the simple root of the subalgebra $so(3)$.
-At first we consider the subalgebra $so(3)$ with the root space spanned on $\beta=\alpha_{1}+2\alpha_{2}$.
-Verma module $M^{\mu}$ with the highest weight $\mu=\omega_{1}+2\omega_{2}=2\alpha_{1}+3\alpha_{2}$ is shown at Figure \ref{fig:B2_Verma}.
-\begin{figure}[h!bt]
-  \noindent\centering{
-    \includegraphics[width=120mm]{B2_Verma}
-  }
-  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}
+% There are different approaches to deal with the branching coefficients. Some
+% of them use the BGG resolution \cite{bernstein1975differential} (for
+% Kac-Moody algebras the algorithm is described in \cite{kac1990idl},\cite
+% {wakimoto2001idl}).
 
-  \label{fig:B2_Verma}
-\end{figure}
+In this paper we demonstrate that for an arbitrary reductive subalgebra
+branching is directly connected with the BGG resolution and in particular
+exhibits the resolution properties in terms of the $\mathcal{O}^{p}$
+category \cite{lepowsky1977generalization} (the parabolic generalization of the cathegory $%
+\mathcal{O}$ \cite{bernstein1976category}).
 
-The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2} for the different regular embeddings $so(3)\to so(5)$.
-Here we can see that the picture depends upon the embedding and looks similar to the Verma modules of some subalgebra.
-\begin{figure}[h!bt]
-  \noindent\centering{
-    \includegraphics[width=120mm]{B2_Verma_Branch2}
-  }
-  \caption{Branching for the Verma modules}
+To show this we use the recursive approach to branching presented in [our
+preprint] (similar to the one used in \cite{ilyin812pbc} for maximal
+embeddings). We consider the subalgebra $\frak{a}$ together with its
+counterpart $\frak{a}_{\bot }$ ''orthogonal'' to $\frak{a}$ with respect to
+the Killing form and also $\widetilde{\frak{a}_{\perp }}:=\frak{a}_{\perp
+}\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus 
+\frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$. For any reductive
+algebra $\frak{a}$ the subalgebra $\frak{a}_{\bot }\hookrightarrow \frak{g}$
+is regular and reductive. For a highest weight integrable module $L^{\left(
+\mu \right) }$ and orthogonal pair of subalgebras $\left( \frak{a},\frak{a}%
+_{\bot }\right) $ we consider the singular element $\Psi ^{\left( \mu
+\right) }$ (the numerator in the Weyl character formula $ch\left( L^{\mu
+}\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see
+for example \cite{humphreys1997introduction}) the Weyl denominator $R=\Psi _{%
+\frak{a}_{\bot }}^{\left( 0\right) }$ and the projection $\Psi _{\left( 
+\frak{a},\frak{a}_{\bot }\right) }^{\left( \mu \right) }=\pi _{\frak{a}}%
+\frac{\Psi _{\frak{g}}^{\left( \mu \right) }}{\Psi _{\frak{a}_{\bot
+}}^{\left( 0\right) }}$. The element $\Psi _{\frak{g}}^{\left( \mu \right) }$
+can be decomposed with respect to the set of Weyl numerators $\Psi _{\frak{a}%
+_{\bot }}^{\left( \mu \right) }$ of $\frak{a}_{\bot }$. This decomposition
+provides the possibility to construct the set of highest weight modules $L_{%
+\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. When
+the injection \ $\frak{a}_{\bot }\hookrightarrow \frak{g}$ \ satisfies the
+''standard parabolic'' conditions these modules give rise to the parabolic
+Verma modules $M_{\left( \widetilde{\frak{a}_{\perp }}\hookrightarrow \frak{g%
+}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$ so that the initial
+character $ch\left( L^{\mu }\right) $ is finally decomposed into the
+alternating sum of such. On the other hand when the parabolic conditions are
+violated the construction survives and exhibites a decomposition with
+respect to a set of Verma modules $M_{\left( \widetilde{\frak{b}_{\perp }},%
+\frak{g}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. In such a
+situation the algebra $\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in 
+$\frak{g}$ but a contraction of $\widetilde{\frak{a}_{\perp }}$.
 
-  \label{fig:B2_Verma_Branch2}
-\end{figure}
-In present paper we interpret this branching coefficients as the dimensions of the weight subspaces of the modules of contracted algebras.
+Some general properties of the proposed decompositions are formulated in
+terms of a specific element $\Gamma _{\frak{a}\rightarrow \frak{g}}$ of the
+group algebra $\mathcal{E}\left( \frak{g}\right) $ called ''the injection
+fan''. Using this tool the simple and explicit algorithm for branching
+coefficients computations applicable for an arbitrary (maximal or
+nonmaximal) subalgebras of finite-dimensional or affine Lie algebras was
+obtained in [our preprint].
+
+Possible further developments are discussed in Section \ref{sec:conclusion}.
+
+\subsection{Notation}
+
+\label{sec:notation}
+
+Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the underlying
+finite-dimensional subalgebras $\stackrel{\circ }{\frak{g}}$ and $\stackrel{%
+\circ }{\frak{a}}$ and an injection $\frak{a}\hookrightarrow \frak{g}$ such
+that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
+correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
+}}^{\ast }$ and $\frak{h}_{\stackrel{\circ }{\frak{a}}}^{\ast }\subset \frak{%
+h}_{\stackrel{\circ }{\frak{g}}}^{\ast }$\ . We use the following notations:
+
+$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
+of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
+-module with the highest weight $\nu $ );
+
+$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
+\left( \mathrm{{resp. }\frak{a}}\right) $ ;
+
+$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
+^{+} $ $\left( \mathrm{{resp. }\Delta _{\frak{a}}^{+}}\right) $--- the
+positive root system (of $\frak{g}$ and $\frak{a}$ respectively);
+
+$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
+\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $%
+\Delta $ (resp. in $\left( \Delta _{\frak{a}}\right) $);
+
+$\stackrel{\circ }{\Delta}$ , $\left( \stackrel{\circ }{\Delta _{\frak{a}}}%
+\right)$ --- the finite root system of the subalgebra $\stackrel{\circ }{%
+\frak{g}}$ (resp. $\stackrel{\circ }{\frak{a}}$);
+
+$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
+the weight diagram of $L^{\mu }$ $\left( \mathrm{{resp. }L_{\frak{a}}^{\nu }}%
+\right) $ ;
+
+$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
+
+$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
+
+$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
+fundamental Weyl chamber;
+
+$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
+
+$\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;
+
+$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
+i $-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mathrm{{resp. }%
+\frak{a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}%
+}\right) $;
+
+$\delta $ --- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);
+
+$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
+}\right) $--- the basic coroot for $\frak{g}$ $\left( \mathrm{{resp. }\frak{a%
+}}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+
+$\stackrel{\circ }{\xi }$ , $\stackrel{\circ }{\xi _{\left( \frak{a}\right) }%
+}$ --- the finite (classical) part of the weight $\xi \in P$ , $\left( 
+\mathrm{{resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}}\right) $;
+
+$\lambda =\left( \stackrel{\circ }{\lambda };k;n\right) $ --- the
+decomposition of an affine weight indicating the finite part $\stackrel{%
+\circ }{\lambda }$, level $k$ and grade $n$;
+
+$P$ $\left( \mathrm{{resp.}P_{\frak{a}}}\right) $ \ --- the weight lattice;
+
+$P^{+}$ $\left( \mathrm{{resp.}P_{\frak{a}}^{+}}\right) $ \ --- the dominant
+weight lattice;
+
+$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
+}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
+resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
+L_{\frak{a}}^{\nu } $);
+
+$ch\left( L^{\mu }\right) $ $\left( \mathrm{{resp. }ch\left( L_{\frak{a}%
+}^{\nu }\right) }\right) $--- the formal character of $L^{\mu }$ $\left( 
+\mathrm{{resp. }L_{\frak{a}}^{\nu }}\right) $;
+
+$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
++\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
+\mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;
+
+$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
+mult}\left( \alpha \right) }}\quad $ $\left( \mathrm{resp.}R_{\frak{a}%
+}:=\prod_{\alpha \in \Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{%
+\mathrm{mult}_{\frak{a}}\mathrm{\left( \alpha \right) }}\right) $--- the
+Weyl denominator.
+
+\section{Orthogonal subalgebra and the singular element}
+
+\label{sec:recurr-form-branch}
+
+Consider the highest weight $\mu \in P^{+}$ of an integrable module $L^{\mu
+} $ of $\frak{g}$ and let $\frak{a}\subset \frak{g}$ be a reductive
+subalgebra of $\frak{g}$. Let $L^{\mu }$ be completely reducible with
+respect to $\frak{a}$, 
+\[
+L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }. 
+\]
+Using the projection operator $\pi _{\frak{a}}$ (to the weight space $\frak{%
+h_{a}}^{\ast }$) one can rewrite this decomposition in terms of formal
+characters: 
+\begin{equation}
+\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
+\label{branching1}
+\end{equation}
+The module $L^{\mu }$ has the BGG-resolution (see [BGG] and [Humphrys]). All
+the members of the filtration sequence are the direct sums of Verma modules
+and all their highest weights $\nu $ are strongly linked to $\mu $: 
+\[
+\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
+W\right\} . 
+\]
+
+\subsection{Orthogonal subalgebra}
+
+Let us introduce the ''orthogonal partner'' $\frak{a}_{\bot }$ for a
+reductive subalgebra $\frak{a}$ in $\frak{g}$.
+
+Consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to 
+$\frak{a}$, 
+\[
+\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
+h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} , 
+\]
+and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
+to $\frak{a}$, 
+\begin{eqnarray*}
+\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
+h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} , \\
+\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
+}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
+\end{eqnarray*}
+Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
+reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\frak{a}_{\perp
+}}^{+}$ . The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
+subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
+_{\perp }}$. Let 
+\[
+\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
+}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
+h\right) =0\right\} 
+\]
+so that $\frak{g}$ has the subalgebras 
+\begin{eqnarray*}
+\widetilde{\frak{a}_{\perp }} &:&=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\\
+\widetilde{\frak{a}} &:&=\frak{a}\oplus \frak{h}_{\perp }.
+\end{eqnarray*}
+Algebras $\frak{a}$ and $\frak{a}_{\perp }$ form the ''orthogonal pair'' $%
+\left( \frak{a},\frak{a}_{\perp }\right) $ of subalgebras in $\frak{g}$.
+
+For the Cartan subalgebras we have the decomposition 
+\begin{equation}
+\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus 
+\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
+\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus 
+\frak{h}_{\frak{a}}.
+\end{equation}
+For the subalgebras of an orthogonal pair $\left( \frak{a},\frak{a}_{\perp
+}\right) $ we consider the corresponding Weyl vectors, $\rho _{\frak{a}}$
+and $\rho _{\frak{a}_{\perp }}$ , and\ form the so called ''defects'' $%
+\mathcal{D}_{\frak{a}}$ and $\mathcal{D}_{\frak{a}_{\perp }}$ of the
+injection: 
+\begin{equation}
+\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho ,
+\end{equation}
+\begin{equation}
+\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
+_{\perp }}\rho .
+\end{equation}
+
+For the highest weight $\mu \in P^{+}$ consider the linked weights $\left\{
+\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections to 
+$h_{\widetilde{\frak{a}_{\perp }}}^{\ast }$ additionally shifted by the
+defect $-\mathcal{D}_{\frak{a}_{\perp }}$: 
+\[
+\mu _{\widetilde{\frak{a}_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
+a}_{\perp }}}\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp
+}},\quad w\in W. 
+\]
+In the case we do consider here among the weights $\left\{ \mu _{\widetilde{%
+\frak{a}_{\perp }}}\left( w\right) |w\in W\right\} $ one can always choose
+those located in the fundamental chamber $\overline{C_{\widetilde{\frak{a}%
+_{\perp }}}}$. Let $U$ be the set of representatives $u$ for the classes $%
+W/W_{\frak{a}_{\perp }}$ such that
+
+\begin{equation}
+U:=\left\{ u\in W|\quad \mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right)
+\in \overline{C_{\widetilde{\frak{a}_{\perp }}}}\right\} \quad .
+\label{U-def}
+\end{equation}
+For such a set $U$ introduce the weights 
+\[
+\mu _{\frak{a}}\left( u\right) :=\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
+\right] +\mathcal{D}_{\frak{a}_{\perp }}. 
+\]
+
+Note that the subalgebra $\afb$ is regular by definition since it is built on the roots of the
+algebra $\gf$.
+
+Consider the Weyl-Kac formula for $ch\left( L^{\mu }\right) $ in terms of
+singular elements \cite{humphreys1997introduction}: 
+\begin{equation}
+ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left(
+0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R},  \label{Weyl-Kac2}
+\end{equation}
+where 
+\[
+\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu
++\rho )-\rho }. 
+\]
+The same form will be used for the submodules $ch\left( L_{\frak{a}}^{\nu
+}\right) $%
+\[
+ch\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left( \nu
+\right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
+}^{\left( \nu \right) }}{R_{\frak{a}}}, 
+\]
+with 
+\[
+\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
+}}\epsilon (w)e^{w\circ (\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}. 
+\]
+
+Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
+we get the relation connecting the singular elements $\Psi ^{\left( \mu
+\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ : 
+\begin{eqnarray}
+\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
+)-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
+(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
+\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
+\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
+mult}_{\frak{a}}(\beta )}},  \nonumber  \label{eq:4} \\
+\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
+&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
+}^{\left( \nu \right) }}{R_{\frak{a}}}.
+\end{eqnarray}
+Here $\Delta _{\frak{a}}^{+}$ is the set of positive roots of the subalgebra 
+$\frak{a}$ (without loss of generality we consider them as vectors from the
+positive root space $\frak{h}^{\ast +}$ of $\frak{g}$).
+
+To describe the recurrent properties for branching coefficients $b_{\nu
+}^{(\mu )}$ we shall use the technique first proposed in \cite{ilyin812pbc}.
+One of the main tools is the set of weights $\Gamma _{\frak{a}\rightarrow 
+\frak{g}}$ called the injection fan:
+
+\begin{definition}
+\label{fan-definition} For the product 
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
+_{\frak{a}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\frak{a}%
+}(\pi _{\frak{a}}\alpha )}=-\sum_{\gamma \in P_{\frak{a}}}s(\gamma
+)e^{-\gamma }  \label{eq:6}
+\end{equation}
+consider the carrier $\Phi _{\frak{a}\subset \frak{g}}\subset P_{\frak{a}}$
+of the function $s(\gamma )=\det \left( \gamma \right) $ : 
+\begin{equation}
+\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}|s(\gamma
+)\neq 0\right\}   \label{eq:37}
+\end{equation}
+The ordering of roots in $\stackrel{\circ }{\Delta _{\frak{a}}}$ induce the
+natural ordering of the weights in $P_{\frak{a}}$. Denote by $\gamma _{0}$
+the lowest vector of $\Phi _{\frak{a}\subset \frak{g}}$ . The set 
+\begin{equation}
+\Gamma _{\frak{a}\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi
+_{\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} 
+\label{fan-defined}
+\end{equation}
+is called the \textit{injection fan}.
+\end{definition}
+
+It must be noticed that the injection fan is the universal instrument that
+depend only on the injection.
+
+\section{Branching for Verma modules}
+\label{sec:branching-verma}
 
@@
 \end{equation}
-Since we consider the regular embeddings, all the positive roots of the subalgebra $\af$ are in the set of positive roots of the algebra $\gf$, $\Delta^{+}_{\af}\subset \Delta^{+}$.
-Then we can introduce $\tilde R$ and the carrier of its expansion $\Phi$:
-\begin{equation}
-  \label{eq:21}
-  \tilde R=\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\af}} \left( 1 - e^{-\alpha}\right)=-\sum_{\gamma\in \Phi} s(\gamma) e^{-\gamma}
-\end{equation}
-The ordering of roots in $\Delta _{\af}$ induce the
-natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
-the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
-\begin{equation}
-\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
-\label{fan-defined}
-\end{equation}
-is called the \textit{injection fan}.
-
-The root of the subalgebra is among the positive roots of the algebra. So  Verma module can be decomposed into the set of Verma modules of the subalgebra:
+If we consider the regular embeddings, all the positive roots of the subalgebra $\af$ are in the set of positive roots of the algebra $\gf$, $\Delta^{+}_{\af}\subset \Delta^{+}$.
+Verma module can be decomposed into the set of Verma modules of the subalgebra:
 \begin{equation}
@@
 
+Inside the main Weyl chamber branching coefficients for Verma module coincide with the coefficients
+for reduction of irreducible representations.
+
+Now consider the following example. 
+Let Lie algebra $\gf$ be $so(5)$ and subalgebra $\af\subset \gf$ be $so(3)$. There are different embeddings of $so(3)\to so(5)$. Here we limit ourselves to the regular ones. 
+The root system of the algebra $so(5)$ consists of 8 roots.
+We denote simple roots by $\alpha_{1}=e_{1}-e_{2}$ and $\alpha_{2}=e_{2}$, where $e_{1},e_{2}$ form standard basis.
+The set of the positive roots is $\Delta^{+}=\left\{\alpha_{1}, \alpha_{1}+\alpha_{2}, \alpha_{1}+2\alpha_{2}, \alpha_{2}\right\}$.
+Each of these roots can be taken as the simple root of the subalgebra $so(3)$.
+At first we consider the subalgebra $so(3)$ with the root space spanned on $\beta=\alpha_{1}+2\alpha_{2}$.
+Verma module $M^{\mu}$ with the highest weight $\mu=\omega_{1}+2\omega_{2}=2\alpha_{1}+3\alpha_{2}$ is shown at Figure \ref{fig:B2_Verma}.
+\begin{figure}[h!bt]
+  \noindent\centering{
+    \includegraphics[width=120mm]{B2_Verma.pdf}
+  }
+  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}
+
+  \label{fig:B2_Verma}
+\end{figure}
+
+The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2} for the different regular embeddings $so(3)\to so(5)$.
+Here we can see that the picture depends upon the embedding and looks similar to the Verma modules of some subalgebra.
+\begin{figure}[h!bt]
+  \noindent\centering{
+    \includegraphics[width=120mm]{B2_Verma_Branch3}
+  }
+  \caption{Branching for the Verma modules}
+
+  \label{fig:B2_Verma_Branch2}
+\end{figure}
+In present paper we interpret this branching coefficients as the dimensions of the weight subspaces of the modules of contracted algebras.
+
 \section{Regular subalgebras and generalized Verma modules}
 \label{sec:regul-subalg-gener}
-
-Consider finite-dimensional Lie algebra $\mathfrak{g}$  and its regular reductive subalgebra $\af\subset \mathfrak{g}$. Introduce the following objects.
-\begin{definition}
-  \label{def-1}
-  Denote by $\Delta^{+}_{\afb}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\af} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\af$.
-\end{definition}
-
-\begin{definition}
-  \label{def-2}
-  Denote by $W_{\afb}$ the subgroup of the Weyl group $W$ generated by the reflections $w_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\afb}$.
-\end{definition}
-\begin{mynote}
-  The subgroup $W_{\afb}$ preserves $\Delta_{\af}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\af}$.
-\end{mynote}
-\begin{definition}
-  \label{def-3}
-  The subsystem $\Delta_{\afb}=\Delta^{+}_{\afb}\cup \left(-\delta^{+}_{\afb}\right)$ determines the subalgebra $\af_{\bot}\subset \mathfrak{g}$.
-\end{definition}
-Let
-\begin{equation*}
-\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
-}|\forall \alpha \in \Delta _{\af}\cup \Delta _{\af_{\perp
-}};\alpha \bot \eta \right\}
-\end{equation*}
-and consider the subalgebras
-\begin{eqnarray*}
-\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
-\\
-\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
-\end{eqnarray*}
-Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
-$\left( \af,\af_{\perp}\right) $
-of subalgebras in $\frak{g}$.
-
-For the Cartan subalgebras we have the decomposition
-\begin{equation}
-\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\af_{\perp }}\oplus
-\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
-\af_{\perp }}=\frak{\frak{h}_{\widetilde{\af_{\perp }}}}\oplus
-\frak{h}_{\af}.
-\end{equation}
-For the subalgebras of an orthogonal pair $\left( \af,\af_{\perp
-}\right) $ we consider the corresponding Weyl vectors, $\rho _{\af}$
-and $\rho _{\af_{\perp }}$ , and\ form the so called ''defects'' $%
-\mathcal{D}_{\af}$ and $\mathcal{D}_{\af_{\perp }}$ of the
-injection:
-\begin{equation}
-\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
-\end{equation}
-\begin{equation}
-\label{defect-perp}
-\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi _{\af%
-_{\perp }}\circ\rho .
-\end{equation}
-\begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
-\in \overline{C_{\widetilde{\af_{\perp }}}}\right\} \quad .
-\label{U-def}
-\end{equation}
-For the same set $U$ introduce the weights
-\begin{equation*}
-\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho %
-\right] +\mathcal{D}_{\af_{\perp }}.
-\end{equation*}
-To simplify the form of relations we shall now on omit the sign "$\circ$" in projected
-weights.
 
@@
   \label{corollary-2}
-  Since $\af, \afb$ are regular subalgebras the simple root system $\alpha_1,\dots, \alpha_r$ of $\gf$ can be chosen in such a way that simple roots $\beta_1,\dots,\beta_{r_{\afb}}$ of $\afb$ are contained in it.
+ If $\af, \afb$ are regular subalgebras the simple root system $\alpha_1,\dots, \alpha_r$ of $\gf$ sometimes can be chosen in such a way that simple roots $\beta_1,\dots,\beta_{r_{\afb}}$ of $\afb$ are contained in it.
 Denote the set of roots $\beta_i$ by $I$.
@@
 
+Note, that not all the examples of branching lead to the generalized Verma modules. For example,
+consider the embedding $\af_{1}=B_{4}\subset \gf=B_{6}$. As we mentioned in \cite{2010arXiv1007.0318L} the
+orthogonal subalgebra $\afb=B_{2}$. Then consider the regular subalgebra $\af=A_{1}\subset
+\af_{1}\subset \gf$ with the root system spanned over the first long root of $\af_{1}$. Its
+orthogonal subalgebra in $\gf$ contains the root systems of two algebras $B_{2}$. But those two root
+systems cannot be built on the simple roots of $\gf$.
 \section{Generalizations}
@@
 
-\item Also we can generalize the whole construction to affine Lie algebras $\gf, \af$, since Weyl character formula and denominator identity have natural analogs in the theory of affine Lie algebras.
-The only subtle point is in the definition of projection $\pi$ to the subalgebra.
-The extension of the Killing form from the finite-dimensional simple Lie algebra $\co{\gf}$ to the affine Lie algebra $\gf$ is not positive-definite.
-For the imaginary root $\delta$ we have $(\delta,\delta)=0$.
-If we use this form for the projection to the root space of the affine subalgebra $\af$ we end up with $\delta\perp \beta; \beta\in \Delta_{\af}$ or $\pi_{\af}(n\delta)=0$.
-This is not what we want.
-
-So we define new positive-definite bilinear form $(\cdot,\cdot)_+$ on the root lattice of $\gf$ by the requirement $(\delta,\delta)_+=1$.
-This form is only $\co{W}$-invariant.
-Then we define the projection $\pi_{\af}$ to the root space of the affine subalgebra $\af$ as the extension of the projection to the finite-dimensional subalgebra $\co{\af}$ with the requirement
-\begin{equation}
-  \label{eq:16}
-  \pi_{\af}(\delta)=\delta.
-\end{equation}
-The orthogonality conditions in the definitions \ref{def-1}, \ref{def-2}, \ref{def-3} are to be understood with the respect to the form $(\cdot,\cdot)_+$.
-Then Lemma \ref{lemma-1} holds for the affine Lie algebras $\gf, \af$.
-\item Another case that we need to consider is the of $\afb$ built on the non-simple roots.
 \end{enumerate}
@@
 
+\section{Acknowledgements}
+
+The work was supported in part by RFFI grant N 09-01-00504 and the National
+Project RNP.2.1.1./1575.
+
+\section*{References}
 \bibliography{article}{}
 \bibliographystyle{utphys}
-
 \end{document}

### 2010-12-14 AffineLieAlgebras/MQFT2010/article.tex
Reference to Bernstein 1971 fixed

@@
 
-To show this we use the recursive approach to branching presented in [our
-preprint] (similar to the one used in \cite{ilyin812pbc} for maximal
+To show this we use the recursive approach to branching presented in \cite{2010arXiv1007.0318L} (similar to the one used in \cite{ilyin812pbc} for maximal
 embeddings). We consider the subalgebra $\frak{a}$ together with its
@@
 nonmaximal) subalgebras of finite-dimensional or affine Lie algebras was
-obtained in [our preprint].
+obtained in \cite{2010arXiv1007.0318L}.
 
@@
 \end{equation}
-The module $L^{\mu }$ has the BGG-resolution (see [BGG] and [Humphrys]). All
+The module $L^{\mu }$ has the BGG-resolution (see
+\cite{bernstein1976category,bernstein1975differential,bernstein1971structure} and \cite{humphreys2008representations}). All
 the members of the filtration sequence are the direct sums of Verma modules
@@
 \end{multline}
-So we have recovered the Bernstein-Gelfand-Gelfand resolution \cite{bernstein1975differential} for the parabolic category ${\cal O}^{\pf}$.
+So we have recovered the Bernstein-Gelfand-Gelfand resolution \cite{bernstein1976category,bernstein1975differential,bernstein1971structure} for the parabolic category ${\cal O}^{\pf}$.
 \end{corollary}

### 2010-12-14 AffineLieAlgebras/MQFT2010/article.tex
Merge with V.D. version

@@
 \usepackage{multicol}
-\usepackage{cmap}
 \usepackage{color}
@@
 }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see
-for example \cite{humphreys1997introduction}) the Weyl denominator $R=\Psi _{%
+for example \cite{humphreys1997introduction}) the Weyl denominator $\Psi _{%
 \frak{a}_{\bot }}^{\left( 0\right) }$ and the projection $\Psi _{\left(
@@
 
-$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
-of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
--module with the highest weight $\nu $ );
+$\frak{g=n}^{-}+\frak{b}+\frak{n}^{+}$ --- the Cartan decomposition;
 
@@
 
-$\stackrel{\circ }{\Delta}$ , $\left( \stackrel{\circ }{\Delta _{\frak{a}}}%
-\right)$ --- the finite root system of the subalgebra $\stackrel{\circ }{%
+$S\quad \left( S_{\frak{a}}\right) $ --- the system of simple roots (of $%
+\frak{g}$ and $\frak{a}$ respectively);
+
+$\stackrel{\circ }{\Delta }$ , $\left( \stackrel{\circ }{\Delta _{\frak{a}}}%
+\right) $ --- the finite root system of the subalgebra $\stackrel{\circ }{%
 \frak{g}}$ (resp. $\stackrel{\circ }{\frak{a}}$);
 
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
-the weight diagram of $L^{\mu }$ $\left( \mathrm{{resp. }L_{\frak{a}}^{\nu }}%
-\right) $ ;
+$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
+i$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a%
+}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+
+$\delta $ --- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);
+
+$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
+}\right) $--- the basic coroot for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a}%
+}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
 
@@
 
+$\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;
+
 $\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
 
-$\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;
+$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
+of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
+-module with the highest weight $\nu $ );
 
-$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
-i $-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mathrm{{resp. }%
-\frak{a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}%
-}\right) $;
-
-$\delta $ --- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);
-
-$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
-}\right) $--- the basic coroot for $\frak{g}$ $\left( \mathrm{{resp. }\frak{a%
-}}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
+the weight diagram of $L^{\mu }$ $\left( \mathrm{{resp.}L_{\frak{a}}^{\nu }}%
+\right) $ ;
 
@@
 }$ --- the finite (classical) part of the weight $\xi \in P$ , $\left(
-\mathrm{{resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}}\right) $;
+\mathrm{{resp.}\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}}\right) $;
 
@@
 
-Let us introduce the ''orthogonal partner'' $\frak{a}_{\bot }$ for a
-reductive subalgebra $\frak{a}$ in $\frak{g}$.
+Now we shall show how the branching procedure naturally produces the
+generalized Verma modules.
 
-Consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to 
-$\frak{a}$, 
+Consider in $\frak{g}$ a reductive subalgebra $\frak{a}$ with the Cartan
+subalgebra $\frak{h}_{\frak{a}}$. For $\frak{a}\hookrightarrow \frak{g}$
+introduce the ''orthogonal partner'' $\frak{a}_{\bot }\hookrightarrow \frak{g%
+}$ .
+
+Firstly consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$
+orthogonal to $\frak{a}$,
 \[
@@
 \end{eqnarray*}
-Algebras $\frak{a}$ and $\frak{a}_{\perp }$ form the ''orthogonal pair'' $%
-\left( \frak{a},\frak{a}_{\perp }\right) $ of subalgebras in $\frak{g}$.
 
@@
 \end{equation}
-For the subalgebras of an orthogonal pair $\left( \frak{a},\frak{a}_{\perp
-}\right) $ we consider the corresponding Weyl vectors, $\rho _{\frak{a}}$
-and $\rho _{\frak{a}_{\perp }}$ , and\ form the so called ''defects'' $%
-\mathcal{D}_{\frak{a}}$ and $\mathcal{D}_{\frak{a}_{\perp }}$ of the
-injection: 
+For the subalgebras $\frak{a}$ and $\frak{a}_{\perp }$ consider the
+corresponding Weyl vectors, $\rho _{\frak{a}}$ and $\rho _{\frak{a}_{\perp }}
+$ , and\ form the so called ''defects'' $\mathcal{D}_{\frak{a}}$ and $%
+\mathcal{D}_{\frak{a}_{\perp }}$ of the injection:
 \begin{equation}
@@
 \mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
-_{\perp }}\rho .
+_{\perp }}\rho .  \label{defect ort}
 \end{equation}
@@
 \]
-In the case we do consider here among the weights $\left\{ \mu _{\widetilde{%
-\frak{a}_{\perp }}}\left( w\right) |w\in W\right\} $ one can always choose
-those located in the fundamental chamber $\overline{C_{\widetilde{\frak{a}%
-_{\perp }}}}$. Let $U$ be the set of representatives $u$ for the classes $%
-W/W_{\frak{a}_{\perp }}$ such that
+For $\mu \in P^{+}$ among the weights $\left\{ \mu _{\widetilde{\frak{a}%
+_{\perp }}}\left( w\right) |w\in W\right\} $ one can always choose those
+located in the fundamental chamber $\overline{C_{\widetilde{\frak{a}_{\perp }%
+}}}$. Let $U$ be the set of representatives $u$ for the classes $W/W_{\frak{a%
+}_{\perp }}$ such that
 
@@
 \end{equation}
-For such a set $U$ introduce the weights 
-\[
+Thus we can select the following subsets:
+\begin{equation}
 \mu _{\frak{a}}\left( u\right) :=\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
-\right] +\mathcal{D}_{\frak{a}_{\perp }}. 
-\]
+\right] +\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U,  \label{mu-a}
+\end{equation}
+and
+\begin{equation}
+\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) :=\pi _{\widetilde{\frak{%
+a}_{\perp }}}\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp
+}},\quad u\in U.  \label{mu-a-tilda}
+\end{equation}
 
@@
 
-Consider the Weyl-Kac formula for $ch\left( L^{\mu }\right) $ in terms of
-singular elements \cite{humphreys1997introduction}: 
+For the modules we are interested in the Weyl-Kac formula for $ch\left( L^{\mu }\right) $ can be
+written in terms of
+singular elements \cite{humphreys1997introduction}
+\[
+\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu
++\rho )-\rho },
+\]
+namely,
 \begin{equation}
 ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left(
-0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R},  \label{Weyl-Kac2}
+0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.  \label{Weyl-Kac2}
 \end{equation}
-where 
-\[
-\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu
-+\rho )-\rho }. 
-\]
-The same form will be used for the submodules $ch\left( L_{\frak{a}}^{\nu
-}\right) $%
+The same is true for the submodules $ch\left( L_{\frak{a}}^{\nu }\right) $
+in (\ref{branching1})
 \[
@@
 
-To describe the recurrent properties for branching coefficients $b_{\nu
-}^{(\mu )}$ we shall use the technique first proposed in \cite{ilyin812pbc}.
-One of the main tools is the set of weights $\Gamma _{\frak{a}\rightarrow 
-\frak{g}}$ called the injection fan:
+\subsection{Decomposing the singular element.}
 
-\begin{definition}
-\label{fan-definition} For the product 
+\label{subsec:decomp-sing-element}
+
+Now we shall perform a decomposition of the singular element $\Psi ^{\left(
+\mu \right) }$ in terms of singular elements of the orthogonal subalgebra
+modules:
+
+\begin{lemma}
+Let $\frak{a}_{\bot }$ be the orthogonal partner of a reductive subalgebra $%
+\frak{a}\hookrightarrow \frak{g}$ with $\frak{h}=\frak{\frak{h}_{\frak{a}}}%
+\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$, $\widetilde{%
+\frak{a}_{\perp }}=\frak{a}_{\perp }\oplus \frak{h}_{\perp }$ and $%
+\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$.
+
+$L^{\mu }$ be the highest weight integrable module with $\mu \in P^{+}$ and
+
+$\Psi ^{\left( \mu \right) }$\ -- the singular element of $L^{\mu }$.
+
+Then the element $\Psi ^{\left( \mu \right) }$ can be decomposed into the
+sum over $u\in U$ (see (\ref{U-def})) of singular elements $\Psi _{%
+\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left(
+u\right) }$ with the coefficients $\epsilon (u)e^{\mu _{\frak{a}}\left(
+u\right) }$:
+\begin{equation}
+\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\frak{a}%
+}\left( u\right) }\Psi _{\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{%
+\frak{a}_{\perp }}}\left( u\right) }.  \label{sing decomp main}
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+With $u\in U$ and $v\in W_{\frak{a}_{\bot }}$ perform the decomposition
+\[
+u(\mu +\rho )=\pi _{\left( \frak{a}\right) }u(\mu +\rho )+\pi _{\left(
+\widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho )
+\]
+for the singular weight $vu(\mu +\rho )-\rho $:
+\begin{equation}
+\begin{array}{lcl}
+vu(\mu +\rho )-\rho  & = & \pi _{\left( \frak{a}\right) }\left( u(\mu +\rho
+)\right) -\rho +\rho _{\frak{a}_{\perp }}+\pi _{\left( \frak{h}_{\bot
+}\right) }\rho  \\
+&  & +\ v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }u(\mu
++\rho )-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{%
+\frak{a}_{\perp }}-\pi _{\left( \frak{h}_{\bot }\right) }\rho .
+\end{array}
+\label{sing-decomp-1}
+\end{equation}
+Use the defect $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect-perp}) to
+simplify the first summand in (\ref{sing-decomp-1}):
+\[
+\begin{array}{r}
+\pi _{\left( \frak{a}\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
+\frak{a}_{\perp }}+\pi _{\left( \frak{h}_{\bot }\right) }\rho = \\
+\pi _{\left( \frak{a}\right) }\left( u(\mu +\rho )\right) -\pi _{\frak{a}%
+}\rho -\pi _{\frak{a}_{\bot }}\rho +\rho _{\frak{a}_{\bot }}= \\
+=\pi _{\left( \frak{a}\right) }\left( u(\mu +\rho )-\rho \right) +\mathcal{D}%
+_{\frak{a}_{\bot }},
+\end{array}
+\]
+and the second one:
+\[
+\begin{array}{c}
+v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho
+)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}%
+_{\perp }}-\pi _{\left( \frak{h}_{\bot }\right) }\rho = \\
+v\left( \pi _{\left( \widetilde{\frak{a}_{\bot }}\right) }u(\mu +\rho )-%
+\mathcal{D}_{\frak{a}_{\bot }}-\pi _{\left( \frak{a}_{\bot }\right) }\rho
+-\pi _{\left( \frak{h}_{\bot }\right) }\rho +\rho _{\frak{a}_{\bot }}\right)
+-\rho _{\frak{a}_{\bot }}= \\
+=v\left( \pi _{\left( \widetilde{\frak{a}_{\bot }}\right) }\left[ u(\mu
++\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\bot }}+\rho _{\frak{a}_{\bot
+}}\right) -\rho _{\frak{a}_{\bot }}.
+\end{array}
+\]
+These expressions provide the desired factorization of the singular element $%
+\Psi ^{\mu }$ in terms of singular elements $\Psi _{\widetilde{\frak{a}%
+_{\perp }}}^{\eta }$ of the $\widetilde{\frak{a}_{\perp }}$-modules $L_{%
+\widetilde{\frak{a}_{\perp }}}^{\eta }$:
+\begin{equation}
+\begin{array}{l}
+\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
+(v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho \right]
++\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}+\rho _{\frak{a}%
+_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
+=\sum_{u\in U}\;\epsilon (u)\Psi _{\widetilde{\frak{a}_{\perp }}}^{\pi
+_{\left( \widetilde{\frak{a}_{\perp }}\right) }\left[ u(\mu +\rho )-\rho
+\right] -\mathcal{D}_{\frak{a}_{\perp }}}e^{\pi _{\left( \frak{a}\right) }%
+\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}.
+\end{array}
+\label{singular main}
+\end{equation}
+\end{proof}
+
+\bigskip
+
+\begin{remark}
+This relation can be considered as a generalized form of the Weyl formula
+for the singular element $\Psi _{\frak{g}}^{\mu }$: the vectors $\mu _{\frak{%
+a}}\left( u\right) $ play the role of singular weights while the alternating
+factors $\epsilon (u)$ are extended to $\epsilon (u)\Psi _{\widetilde{\frak{a%
+}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }$. In
+fact when $\frak{a=g}$ both $\frak{a}_{\perp }$and $\frak{h}_{\perp }$are
+zeros, $U=W$, and\ the original Weyl formula is reobtained via the
+trivilization of the singular elements: $\epsilon (u)\Psi _{\widetilde{\frak{%
+a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right)
+}=\epsilon (u)$. In the opposite limit when $\frak{a=0}$, $\Delta _{\frak{a}%
+_{\perp }}=\Delta _{\frak{g}}$, $\frak{h}_{\perp }^{\ast }=0$, $\widetilde{%
+\frak{a}_{\perp }}=\frak{g}$, $\mathcal{D}_{\frak{a}_{\perp }}=0$, $U=W/W_{%
+\frak{a}_{\perp }}=e$ and $\Psi ^{\mu }$ is again reobtained, now via the
+trivilization of the set of vectors: $\mu _{\frak{a}}\left( e\right) =0$.
+\end{remark}
+
+\begin{remark}
+In [our preprint] the decomposition analogous to (\ref{singular main}) was
+used to construct the recurrent relations for branching coefficients $k_{\xi
+}^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
+\hookrightarrow \frak{g}$:
+\[
+\begin{array}{c}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\widetilde{\frak{a}_{\perp }}%
+}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right) \delta _{\xi
+-\gamma _{0},\pi _{\frak{a}}(u(\mu +\rho )-\rho )}+\right.  \\
+\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
+\gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right) }\right) .
+\end{array}
+\]
+The recursion is goverened by the set $\Gamma _{\frak{a}\rightarrow \frak{g}}
+$ called the injection fan. The latter is defined the carrier set $\left\{
+\xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the coefficient function $%
+s(\xi )$
+\[
+\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{ \xi \in P_{%
+\frak{a}}|s(\xi )\neq 0\right\}
+\]
+appearing in the expansion
 \begin{equation}
@@
 }(\pi _{\frak{a}}\alpha )}=-\sum_{\gamma \in P_{\frak{a}}}s(\gamma
-)e^{-\gamma }  \label{eq:6}
+)e^{-\gamma };\quad
 \end{equation}
-consider the carrier $\Phi _{\frak{a}\subset \frak{g}}\subset P_{\frak{a}}$
-of the function $s(\gamma )=\det \left( \gamma \right) $ : 
+The weights in $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ are to
+be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi \right\} $
+-- and the zero element is to be eliminated:
 \begin{equation}
-\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}|s(\gamma
-)\neq 0\right\}   \label{eq:37}
+\Gamma _{\frak{a}\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in
+\left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
 \end{equation}
-The ordering of roots in $\stackrel{\circ }{\Delta _{\frak{a}}}$ induce the
-natural ordering of the weights in $P_{\frak{a}}$. Denote by $\gamma _{0}$
-the lowest vector of $\Phi _{\frak{a}\subset \frak{g}}$ . The set 
+\end{remark}
+
+\subsection{Weyl like formulas.}
+
+\bigskip By the definition the subalgebra $\widetilde{\frak{a}_{\perp }}$ is
+regular and reductive. Consider its Weyl denominator $R_{\widetilde{\frak{a}%
+_{\perp }}}:=\prod_{\alpha \in \Delta _{\widetilde{\frak{a}_{\perp }}%
+}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{\left(
+\alpha \right) }}$ and the element $R_{J}:=\prod_{\alpha \in \Delta
+^{+}\setminus \Delta _{\widetilde{\frak{a}_{\perp }}}^{+}}\left(
+1-e^{-\alpha }\right) ^{\mathrm{mult}(\alpha )}$ as the factors in $R$: $%
+\quad $%
+\[
+R=R_{J}R_{\widetilde{\frak{a}_{\perp }}}.
+\]
+According to this factorization and the decomposition (\ref{sing decomp main}%
+) the character $ch\left( L^{\mu }\right) $ can be written as
+\begin{eqnarray*}
+\mathrm{ch}\left( L^{\mu }\right) &=&\left( R_{J}\right) ^{-1}\left( R_{%
+\widetilde{\frak{a}_{\perp }}}\right) ^{-1}\Psi ^{\mu }=\left( R_{J}\right)
+^{-1}\sum_{u\in U}\;e^{\mu _{\frak{a}}\left( u\right) }\epsilon (u)\left( R_{%
+\widetilde{\frak{a}_{\perp }}}\right) ^{-1}\Psi _{\widetilde{\frak{a}_{\perp
+}}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) } \\
+&=&\left( R_{J}\right) ^{-1}\sum_{u\in U}\;e^{\mu _{\frak{a}}\left( u\right)
+}\epsilon (u)L_{\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}%
+_{\perp }}}\left( u\right) },
+\end{eqnarray*}
+where $\left\{ L_{\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}%
+_{\perp }}}\left( u\right) }|u\in U\right\} $ is the set of
+finite-dimensional $\widetilde{\frak{a}_{\perp }}$-modules with the highest
+weights $\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) $.
+
+Now remember that the subalgebra $\widetilde{\frak{a}_{\perp }}$ is regular
+and reductive. We are interested in nontrivial subalgebras $\frak{a}$ and
+correspondingly in nontrivial $\widetilde{\frak{a}_{\perp }}$ (the case of a
+trivial orthogonal subalgebra arise when $\frak{a}=\frak{g}$ and was
+considered above (see Remark 1)). This means that $r_{\frak{a}}\geq 1$ and $%
+r_{\widetilde{\frak{a}_{\perp }}}<r$. Due to the fact that any maximal
+regular subalgebra has the Dynkin scheme obtained by one or two node
+subtractions from the extended Dynkin scheme and the extended scheme has at
+most one dependent root (the highest root) the set of roots $\Delta _{%
+\widetilde{\frak{a}_{\perp }}}^{+}$ is always equivalent to the one $\Delta
+_{I}^{+}$ generated\ by some subset $I\subset S$ of simple roots.
+
+It follows that we can (by redefining the set $\Delta ^{+}$) identify $%
+\Delta _{\widetilde{\frak{a}_{\perp }}}^{+}$ with the subset $\Delta _{I}^{+}
+$ \ where $I\subset S$ . This allows us to introduce the elements necessary
+to compose the generalized Verma modules [Lepowsky,Hamphrys]. We have two
+sets of root vectors $\left\{ x_{\xi }\in \frak{g}_{\xi }|\xi \in \Delta
+_{I}^{+}\right\} $ and $\left\{ x_{\eta }\in \frak{g}_{\eta }|\eta \in
+\Delta ^{+}\setminus \Delta _{I}^{+}\right\} $ . They generate nilpotent
+subalgebras of $\frak{n}^{+}$:
+\[
+\frak{n}_{I}^{+}:=\sum_{\xi \in \Delta _{I}^{+}}\frak{g}_{\xi },\quad \frak{u%
+}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\frak{g}%
+_{\eta }.
+\]
+The first subalgebra together with its negative counterpart $\frak{n}_{I}^{-}
+$ generates a simple subalgebra
+\[
+\frak{s}_{I}=\frak{n}_{I}^{-}+\frak{h}_{I}+\frak{n}_{I}^{+}.
+\]
+We enlarge it with the remaining Cartan generators and introduce the
+subalgebra:
+\[
+\frak{l}_{I}=\frak{n}_{I}^{-}+\frak{h}+\frak{n}_{I}^{+}.
+\]
+The semidirect product of subalgebras $\frak{l}_{I}$ and $\frak{u}_{I}^{+}$
+gives a parabolic subalgebra in $\frak{g}$ :
 \begin{equation}
-\Gamma _{\frak{a}\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi
-_{\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} 
-\label{fan-defined}
+\frak{p}_{I}=\frak{l}_{I}\vartriangleright \frak{u}_{I}^{+},
+\label{paralolic subalg}
 \end{equation}
-is called the \textit{injection fan}.
-\end{definition}
+Its universal enveloping $U\left( \frak{p}_{I}\right) $ is a subalgebra in $%
+U\left( \frak{g}\right) $. According to the obtained structure (\ref
+{paralolic subalg}) the $\frak{l}_{I}$-modules $L_{\widetilde{\frak{a}%
+_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }$ can be
+easily lifted to $\frak{p}_{I}$-modules using the trivial action of the
+nilradical $\frak{u}_{I}^{+}$ . The latter induce $U\left( \frak{g}\right) $%
+-modules in a standard way:
+\[
+M_{I}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }=U\left( \frak{g}%
+\right) \otimes _{U\left( \frak{p}_{I}\right) }L_{\widetilde{\frak{a}_{\perp
+}}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }.
+\]
+According to the defenition presented in [Lepowsky] this is a \textit{%
+generalized Verma module} generated by the highest weight $\mu _{\widetilde{%
+\frak{a}_{\perp }}}\left( u\right) $. As $U\left( \frak{u}_{I}^{-}\right) $%
+-module $M_{I}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }$ is
+isomorphic to $U\left( \frak{u}_{I}^{-}\right) \otimes $ $L_{\widetilde{%
+\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }$
+and thus its character can be written with the help of Kostant-Heckman
+function \{KostantHeckman1982\} corresponding to the injection of the
+orthogonal subalgebra $\widetilde{\frak{a}_{\perp }}\hookrightarrow \frak{g}$%
+:
+\[
+\mathrm{ch}M_{I}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }=%
+\mathcal{KH}_{\widetilde{\frak{a}_{\perp }}\hookrightarrow \frak{g}}\mathrm{%
+ch}L_{\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}%
+}\left( u\right) }.
+\]
+As far as function $\mathcal{KH}_{\widetilde{\frak{a}_{\perp }}%
+\hookrightarrow \frak{g}}$ is generated by the denominator $R_{I}$ the last
+expression can be rewritten in the form
+\[
+\mathrm{ch}M_{I}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }=%
+\frac{1}{R_{I}}\mathrm{ch}L_{\widetilde{\frak{a}_{\perp }}}^{\mu _{%
+\widetilde{\frak{a}_{\perp }}}\left( u\right) }.
+\]
+This means that we have obtained the decomposition of $\mathrm{ch}\left(
+L^{\mu }\right) $ in terms of generalized Verma modules characters:
+\begin{equation}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\frak{a}}\left(
+u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\widetilde{\frak{a}_{\perp }}%
+}\left( u\right) }.  \label{char in gen verma mod}
+\end{equation}
 
-It must be noticed that the injection fan is the universal instrument that
-depend only on the injection.
+As it was proved in [Humphrys] (see Proposition 9.6 ) characters of the
+generalized Verma modules $M_{I}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left(
+u\right) }$  can be described as a linear combination of ordinary Verma
+modules corresponding to $\frak{g}$:
+\[
+\mathrm{ch}M_{I}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right)
+}=\sum_{w\in W_{\frak{a}_{\perp }}}\epsilon \left( w\right) \mathrm{ch}%
+M^{w\left( \mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) +\rho _{%
+\widetilde{\frak{a}_{\perp }}}\right) -\rho _{\widetilde{\frak{a}_{\perp }}}}
+\]
+Substituting this expression in\ (\ref{char in gen verma mod}) and using the
+definitions (\ref{mu-a},\ref{mu-a-tilda}) and (\ref{defect ort}) we reobtain
+the standard decomposition of the character:
+\[
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{w\in W}\;\epsilon (u)\mathrm{ch}%
+M^{w\left( \mu +\rho \right) -\rho }.
+\]
+
+\bigskip
+
+\bigskip Supplements:
+
+\bigskip $\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast
+}|\forall h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} ,$
+
+$\Delta _{\frak{a}_{\perp }}:=\left\{ \beta \in \Delta _{\frak{g}}|\forall
+h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,$
+
+$\Delta _{\frak{a}_{\perp }}^{+}:=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
+}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\}
+. $
+
+$\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
+}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
+h\right) =0\right\} $
+
+$\widetilde{\frak{a}_{\perp }}:=\frak{a}_{\perp }\oplus \frak{h}_{\perp };%
+\widetilde{\frak{a}}:=\frak{a}\oplus \frak{h}_{\perp }.$
+
+$\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp
+}}\oplus \frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus
+\frak{h}_{\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}%
+\oplus \frak{h}_{\frak{a}}.$
+
+$\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
+_{\perp }}\rho .$
+
+$U=W/W_{\frak{a}_{\perp }};U:=\left\{ u\in W|\quad \mu _{\widetilde{\frak{a}%
+_{\perp }}}\left( u\right) \in \overline{C_{\widetilde{\frak{a}_{\perp }}}}%
+\right\} $
+
+$\mu _{\frak{a}}\left( u\right) :=\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
+\right] +\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U,$
+
+$\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) :=\pi _{\widetilde{%
+\frak{a}_{\perp }}}\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}%
+_{\perp }},\quad u\in U.$
+
+$\Psi ^{\mu }=\sum_{u\in U}\;\epsilon (u)\Psi _{\widetilde{\frak{a}_{\perp }}%
+}^{\pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }\left[ u(\mu +\rho
+)-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}}e^{\pi _{\left( \frak{a}%
+\right) }\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp
+}}}. $
+
+$\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\frak{a}%
+}\left( u\right) }\Psi _{\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{%
+\frak{a}_{\perp }}}\left( u\right) }.$
+
+$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
+mult}\left( \alpha \right) }}\quad $ $\left( \mathrm{resp.}R_{\frak{a}%
+}:=\prod_{\alpha \in \Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{%
+\mathrm{mult}_{\frak{a}}\mathrm{\left( \alpha \right) }}\right) $
+
+Proof of the final result:
+
+$\sum_{u\in U}\;e^{\mu _{\frak{a}}\left( u\right) }\epsilon (u)\sum_{w\in W_{%
+\frak{a}_{\perp }}}\epsilon \left( w\right) \mathrm{ch}M^{w\left( \mu _{%
+\widetilde{\frak{a}_{\perp }}}\left( u\right) +\rho _{\frak{a}_{\perp
+}}\right) -\rho _{\frak{a}_{\perp }}}=$
+
+$=\sum_{u\in U}\sum_{w\in W_{\frak{a}_{\perp }}}\;\epsilon \left( w\right)
+\epsilon (u)e^{\mu _{\frak{a}}\left( u\right) }\mathrm{ch}M^{w\left( \mu _{%
+\widetilde{\frak{a}_{\perp }}}\left( u\right) +\rho _{\frak{a}_{\perp
+}}\right) -\rho _{\frak{a}_{\perp }}}=$
+
+$=\sum_{u\in U}\sum_{w\in W_{\frak{a}_{\perp }}}\;\epsilon \left( w\right)
+\epsilon (u)e^{\mu _{\frak{a}}\left( u\right) }\mathrm{ch}M^{w\left( \mu _{%
+\widetilde{\frak{a}_{\perp }}}\left( u\right) +\rho _{\frak{a}_{\perp
+}}\right) -\rho _{\frak{a}_{\perp }}}$
+
+$w\left( \mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) +\rho _{%
+\widetilde{\frak{a}_{\perp }}}\right) -\rho _{\widetilde{\frak{a}_{\perp }}%
+}=w\left( \pi _{\widetilde{\frak{a}_{\perp }}}\left[ u(\mu +\rho )-\rho %
+\right] -\rho _{\widetilde{\frak{a}_{\perp }}}+\pi _{\widetilde{\frak{a}%
+_{\perp }}}\rho +\rho _{\widetilde{\frak{a}_{\perp }}}\right) -\rho _{%
+\widetilde{\frak{a}_{\perp }}}$
+
+$=w\left( \pi _{\widetilde{\frak{a}_{\perp }}}\left[ u(\mu +\rho )-\rho %
+\right] +\pi _{\widetilde{\frak{a}_{\perp }}}\rho \right) -\rho _{\widetilde{%
+\frak{a}_{\perp }}}=w\left( \pi _{\widetilde{\frak{a}_{\perp }}}\left[ u(\mu
++\rho )\right] \right) -\rho _{\widetilde{\frak{a}_{\perp }}}=$
+
+$=\left( \pi _{\widetilde{\frak{a}_{\perp }}}\left[ wu(\mu +\rho )\right]
+\right) -\rho _{\widetilde{\frak{a}_{\perp }}};$
+
+$e^{\mu _{\frak{a}}\left( u\right) }=e^{\pi _{\frak{a}}\left[ u(\mu +\rho
+)-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}=e^{\pi _{\frak{a}}\left[
+wu(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}=e^{\pi _{\frak{%
+a}}\left[ wu(\mu +\rho )\right] -\left( \pi _{\frak{a}}\rho +\pi _{%
+\widetilde{\frak{a}_{\perp }}}\rho \right) +\rho _{\widetilde{\frak{a}%
+_{\perp }}}}=$
+
+$=e^{\pi _{\frak{a}}\left[ wu(\mu +\rho )\right] -\rho +\rho _{\widetilde{%
+\frak{a}_{\perp }}}};$
+
+$e^{\left( \pi _{\widetilde{\frak{a}_{\perp }}}\left[ wu(\mu +\rho )\right]
+\right) -\rho _{\widetilde{\frak{a}_{\perp }}}}e^{\pi _{\frak{a}}\left[
+wu(\mu +\rho )\right] -\rho +\rho _{\widetilde{\frak{a}_{\perp }}%
+}}=e^{wu(\mu +\rho )-\rho };$
+
+$\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) :=\pi _{\widetilde{%
+\frak{a}_{\perp }}}\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}%
+_{\perp }}$
 
@@
 
-\section{Applications}
-\label{sec:applications}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-\section{Acknowledgements}
-
-The work was supported in part by RFFI grant N 09-01-00504 and the National
-Project RNP.2.1.1./1575.
-
+% \section{Applications}
+% \label{sec:applications}
+% 
+% \section{Conclusion}
+% \label{sec:conclusion}
+% 
+% 
+% \section{Acknowledgements}
+% 
+% The work was supported in part by RFFI grant N 09-01-00504 and the National
+% Project RNP.2.1.1./1575.
+% 
 \section*{References}

### 2010-12-15 GeneralOverview/Lectures/2dqft.tex
Lecture 9 is (almost) completed.

@@
   \label{eq:174}
-  |\vec x'_i-\vec x'_j|=\frac{|\vec x_i-\vec x_j|}{(1-2(\vec h,vec x_i)+h^2x_i^2)^{1/2} (1-2(\vec h,\vec x_j)+h^2 x_j^2)^{1/2}}
+  |\vec x'_i-\vec x'_j|=\frac{|\vec x_i-\vec x_j|}{(1-2(\vec h,\vec x_i)+h^2x_i^2)^{1/2} (1-2(\vec h,\vec x_j)+h^2 x_j^2)^{1/2}}
 \end{equation}
@@
   x\to x'\\
-  \varphi(x)\to \varphi'(x')=\left|\frac{\partial x'}{\partial x}\right|^{-\Delta/2}\varphi(x)\\
+  \varphi(x)\to \varphi'(x')=\left|\frac{\partial x'}{\partial x}\right|^{-\Delta/d}\varphi(x)\\
   \left|\frac{\partial x'}{\partial x}\right|=\Lambda(x)^{-d/2}    \quad\mbox{--- якобиан преобразования}
@@
 \end{equation}
+Мы знаем, как преобразуется поле при конформных преобразованиях \eqref{eq:182}, поэтому коррелятор должен вести себя так:
+\begin{equation}
+  \label{eq:185}
+  \langle \phi_{1}(x_{1})\phi_{2}(x_{2})\rangle = \left|\frac{\partial x'_{1}}{\partial x_{1}}\right|^{\frac{\Delta_{1}}{d}}\left| \frac{\partial x'_{2}}{\partial x_{2}}\right|^{\frac{\Delta_{1}}{d}} \langle \phi_{1}(x'_{1})\phi_{2}(x'_{2})\rangle .
+\end{equation}
+Из требования инвариантности коррелятора при поворотах и трансляциях получаем, что коррелятор может зависеть только от модуля разности $\left|x_{1}-x_{2}\right|$:
+\begin{equation}
+  \label{eq:186}
+  \langle \phi_{1}(x_{1}) \phi_{2}(x_{2})\rangle = f(\left|x_{1}-x_{2}\right|)
+\end{equation}
+При масштабных преобразованиях $x\to \lambda x$ из \eqref{eq:185} получаем
+\begin{equation}
+  \label{eq:187}
+   \langle \phi_{1}(x_{1}) \phi_{2}(x_{2})\rangle=\lambda^{\Delta_{1}+\Delta_{2}}  \langle \phi_{1}(\lambda x_{1}) \phi_{2}(\lambda x_{2})\rangle .
+\end{equation}
+То есть мы видим, что $ \langle \phi_{1}(x_{1}) \phi_{2}(x_{2})\rangle$ - однородная функция, $f(x)=\lambda^{\Delta_{1}+\Delta_{2}} f(\lambda x)$. Отсюда
+\begin{equation}
+  \label{eq:188}
+   \langle \phi_{1}(x_{1}) \phi_{2}(x_{2})\rangle = \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}.
+\end{equation}
+Однако мы ещё не воспользовались инвариантностью коррелятора относительно специальных конформных преобразований.
+Подставим явный вид преобразований $\left|x_{1}-x_{2}\right|$ из \eqref{eq:174} и введем обозначение $\gamma_{i}=\left(1-2(h,x_{i})+h^{2}x_{i}^{2}\right)$, тогда
+\begin{equation}
+  \label{eq:189}
+  \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}=\frac{C_{12}(\gamma_{1}\gamma_{2})^{(\Delta_{1}+\Delta_{2})/2}}{\gamma_{1}^{\Delta_{1}}\gamma_{2}^{\Delta_{2}} \left|x_{1}-x_{2}\right|}.
+\end{equation}
+Это равенство может выполняться только при $\Delta_{1}=\Delta_{2}$. В итоге для коррелятора
+\begin{equation}
+  \label{eq:190}
+   \langle \phi_{1}(x_{1}) \phi_{2}(x_{2})\rangle =
+   \begin{cases}
+     \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{2\Delta_{1}}} & \Delta_{1}=\Delta_{2}\\
+     0 & \Delta_{1}\neq \Delta_{2}
+   \end{cases}
+\end{equation}
+Вспомним, что для парной корреляционной функции мы вводили критический индекс $\eta$: $\Gamma(\vec n)\sim |\vec n|^{2-d-\eta}$. То есть для коррелятора квазипримарых полей
+\begin{equation}
+  \label{eq:191}
+  \eta=2\Delta +2 -d.
+\end{equation}
+
+Аналогичный анализ можно провести для трехточечных функций. Из требований трансляционной и вращательной инвариантности имеем
+\begin{equation}
+  \label{eq:192}
+  \langle \phi_{1}(x_{1})\phi_{2}(x_{2})\phi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}},\quad a+b+c=\Delta_{1}+\Delta_{2}+\Delta_{3}.
+\end{equation}
+Здесь введено обозначение $x_{ij}=|x_{i}-x_{j}|$.
+Из требования инвариантности при специальных конформных преобразованиях получаем
+\begin{equation}
+  \label{eq:193}
+  \frac{C^{abc}_{123}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}}=\frac{C^{abc}_{123}}{\gamma_{1}^{\Delta_{1}}\gamma_{2}^{\Delta_{2}}\gamma_{3}^{\Delta_{3}}}\frac{(\gamma_{1}\gamma_{2})^{a/2}(\gamma_{2}\gamma_{3})^{b/2}(\gamma_{1}\gamma_{3})^{c/2}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}}
+\end{equation}
+Это равенство может выполняться только при
+\begin{equation}
+  \label{eq:194}
+  \begin{array}{l}
+    a+c=2\Delta_{1}\\
+    a+b=2\Delta_{2}\\
+    b+c=2\Delta_{3}
+  \end{array}
+\end{equation}
+Отсюда сразу получаем, сто
+\begin{equation}
+  \label{eq:195}
+  \begin{array}{l}
+    a=\Delta_{1}+\Delta_{2}-\Delta_{3}\\
+    b=\Delta_{2}+\Delta_{3}-\Delta_{1}\\
+    c=\Delta_{3}+\Delta_{1}-\Delta_{2}.
+  \end{array}
+\end{equation}
+В итоге для трехточечных функций имеем:
+\begin{equation}
+  \label{eq:196}
+   \langle \phi_{1}(x_{1})\phi_{2}(x_{2})\phi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{\Delta_{1}+\Delta_{2}-\Delta_{3}} x_{23}^{\Delta_{2}+\Delta_{3}-\Delta_{1}}x_{13}^{\Delta_{3}+\Delta_{1}-\Delta_{2}}}.
+\end{equation}
+Из четырех точек уже можно собрать инварианты \eqref{eq:175}, поэтому из требований конформной инвариантности для четырехточечной функции можно написать только
+\begin{equation}
+  \label{eq:197}
+  \langle \phi_{1}(x_{1})\phi_{2}(x_{2})\phi_{3}(x_{3})\phi_{4}(x_{4})\rangle=f\left(\frac{x_{12}x_{34}}{x_{13}x_{24}}; \frac{x_{12}x_{34}}{x_{23}x_{14}}\right) \prod_{i<j}^{4}x_{ij}^{\Delta/3-\Delta_{i}-\Delta_{j}},\quad \Delta=\sum_{i=1}^{4}\Delta_{i}.
+\end{equation}
+
+\subsection{Тождества Уорда}
+\label{sec:ward-identities}
+
+Напомним, о чем идет речь. В произвольной теории поля с полями $\Phi(x)$ инфинитезимальное преобразование может быть записано при помощи генераторов
+\begin{equation}
+  \label{eq:198}
+  \Phi'(x)=\Phi(x)-i\omega_{a} G_{a} \Phi(x)
+\end{equation}
+Вариация действия вычисляется через ток, соответствующий данному преобразовании:
+\begin{equation}
+  \label{eq:199}
+  j^{\mu}_{a}=\left(\frac{\partial \mathcal{L} }{\partial (\partial_{\mu}\Phi)} \partial_{\nu}\Phi -\delta^{\mu}_{\nu}\mathcal{L}\right) \frac{\delta x^{\nu}}{\delta \omega_{a}} - \frac{\partial \mathcal{L} }{\partial (\partial_{\mu} \Phi)}\frac{\delta F}{\delta \omega_{a}}
+\end{equation}
+\begin{equation}
+  \label{eq:200}
+  \delta S =\int d^{d}x \partial_{\mu}j^{\mu}_{a} \omega_{a}
+\end{equation}
+Обозначим через $X$ произведение локальных полей, входящих в коррелятор
+\begin{equation}
+  \label{eq:201}
+  X=\Phi(x_{1})\dots \Phi(x_{n}).
+\end{equation}
+Коррелятор дается функциональным интегралом
+\begin{equation}
+  \label{eq:202}
+  \langle X\rangle = \frac{1}{Z}\int \mathcal{D} \Phi X e^{-S[\Phi]}
+\end{equation}
+Сделаем замену переменных $\Phi\to \Phi'$ в функциональном интеграле. При этом можно предполагать, что ``мера интегрирования'' не меняется $\mathcal{D}\Phi'=\mathcal{D}\Phi$ \cite{difrancesco1997cft}:
+\begin{equation}
+  \label{eq:203}
+  \langle X\rangle = \frac{1}{Z} \int \mathcal{D} \Phi' (X+\delta X)e^{-S[\Phi]-\int d^{d}x \partial_{\mu}j^{\mu}_{a}\omega_{a}(x)}
+\end{equation}
+Раскладываем выражение в ряд до первого порядка по $\omega_{a}(x)$:
+\begin{equation}
+  \label{eq:204}
+  \langle X\rangle=\frac{1}{Z} \left( \int \mathcal{D} \Phi X e^{-S[\Phi]}+\int \mathcal{D} \Phi \delta X e^{-S[\Phi]} -\int \mathcal{D}\Phi \int d^{d}x \partial_{\mu}j^{\mu}_{a}\omega_{a}(x) X e^{-S[\Phi]}\right)
+\end{equation}
+В результате имеем
+\begin{equation}
+  \label{eq:205}
+  \langle \delta X\rangle=\int d^{d}x \partial_{\mu}\langle j^{\mu}_{a}(x) X\rangle \omega_{a}(x)
+\end{equation}
+С другой стороны, мы можем вычислить $\langle\delta X\rangle$ используя \eqref{eq:198}:
+\begin{multline}
+  \label{eq:206}
+  \langle\delta X\rangle=-i\sum_{i=1}^{n}\langle \Phi(x_{1})\dots G_{a} \Phi(x_{i}) \dots \Phi(x_{n})\rangle \omega_{a}(x_{i})=\\
+  -i \int d^{d}x \omega_{a}(x) \sum_{i=1}^{n} \langle \Phi(x_{1}) \dots G_{a} \Phi(x_{i}) \dots \Phi(x_{n})\rangle \delta (x-x_{i})
+\end{multline}
+Окончательно общий вид тождеств Уорда выглядит следующим образом:
+\begin{equation}
+  \label{eq:207}
+  \partial_{\mu}\langle j^{\mu}_{a}\Phi(x_{1}) \dots \Phi(x_{n})\rangle=-i\sum_{i=1}^{n}\delta (x-x_{i}) \langle\Phi(x_{1})\dots G_{a} \Phi(x_{i})\dots \Phi(x_{n})\rangle
+\end{equation}
+Рассмотрим некоторые примеры, которые понадобятся нам для конформной теории. Мы используем полученный нами явный вид генераторов \eqref{eq:169}.
+
+Тождество Уорда для трансляций:
+\begin{equation}
+  \label{eq:208}
+  \partial_{\mu}\langle T^{\mu}_{\nu} X\rangle =-i \sum_{i} \delta(x-x_{i}) \frac{\partial}{\partial x_{i}^{\nu}} \langle X \rangle
+\end{equation}
+Теперь рассмотрим вращения. Если тензор энергии-импульса симметризован (это можно сделать в большинстве случаев), то отвечающий вращениям ток дается выражением
+\begin{equation}
+  \label{eq:209}
+  j^{\mu\nu\rho}=T^{\mu\nu}x^{\rho}-T^{\mu\rho}x^{\nu}.
+\end{equation}
+Тогда тождество Уорда может быть записано в виде
+\begin{equation}
+  \label{eq:210}
+  \partial_{\mu}\langle (T^{\mu\nu}x^{\rho}-T^{\mu\rho}x^{\nu}) X\rangle=\sum_{i }\delta(x-x_{i}) \left( (x^{\nu}_{i}\partial^{\rho}_{i}-x^{\rho}_{i}\partial^{\nu}_{i})\langle X\rangle-i S^{\nu\rho}_{i}\langle X\rangle\right).
+\end{equation}
+Его можно упростить с использованием тождества для трансляций \eqref{eq:208}:
+\begin{equation}
+  \label{eq:211}
+  \langle (T^{\rho\nu}-T^{\nu\rho}) X\rangle=-i \sum_{i} \delta(x-x_{i}) S^{\nu\rho}_{i}\langle X\rangle.
+\end{equation}
+Тензор энергии-импульса в квантовой теории симметричен в корреляционных функциях, если его положение не совпадает с положениями других полей в корреляторе.
+
+Наконец, для масштабных преобразований ток имеет вид $T^{\mu}_{\nu}x^{\nu}$, действие генератора дается выражением \eqref{eq:181} и тождества Уорда выглядят так:
+\begin{equation}
+  \label{eq:212}
+  \partial_{\mu}\langle T^{\mu}_{\nu} x^{\nu} X\rangle=-\sum_{i} \delta(x-x_{i}) \left( x^{\nu}_{i}\frac{\partial}{\partial x^{\nu}_{i}} \langle X\rangle+\Delta_{i} \langle X\rangle\right) 
+\end{equation}
+Его тоже можно упростить:
+\begin{equation}
+  \label{eq:213}
+  \langle T^{\mu}_{\mu} X \rangle = -i \sum_{i} \delta(x-x_{i}) \Delta_{i}\langle X\rangle
+\end{equation}
+
+\subsection{О бесследовости тензора энергии-импульса.}
+\label{sec:tracelessness}
+
+В некоторых теориях из масштабной, вращательной и трансляционной инвариантности автоматически следует конформная инвариантность.
+Как мы знаем, конформная инвариантность соответствует бесследовости тензора энергии-импульса.
+Общего доказательства конформной инвариантности для масштабно-, трансляционно- и вращательно-инвариантных теорий не существует даже для двумерного случая, однако мы можем показать, что вакуумное среднее квадрата следа тензора энергии-импульса в этом случае равно нулю.
+
+Для этого рассмотрим функцию Швингера
+\begin{equation}
+  \label{eq:214}
+  S_{\mu\nu\rho\sigma}=\langle T_{\mu\nu}(x) T_{\rho\sigma}(0)\rangle.
+\end{equation}
+Из симметричности тензора энергии-импульса
+\begin{equation}
+  \label{eq:215}
+  S_{\mu\nu\rho\sigma}=S_{\nu\mu\rho\sigma}=S_{\mu\nu\sigma\rho}=S_{\nu\mu\sigma\rho}
+\end{equation}
 

### 2010-12-17 AffineLieAlgebras/MQFT2010/article.tex
More work on MQFT2010 paper - new changes from V.D., some examples, images and bibliography entries.

--- 2010-12-14 AffineLieAlgebras/MQFT2010/article.tex
@@
-\documentclass[12pt]{article}
 %\usepackage{ucs}
-\usepackage{amsmath,amssymb,amsthm}
 %\usepackage{pb-diagram}
-\usepackage{multicol}
-\usepackage{cmap}
-\usepackage{color}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-\usepackage{hyperref}
-
+%\usepackage{epstopdf}
 %\usepackage{verbatim}
@@
 %{\\\hfill$\scriptstyle\blacksquare$\par}
+
+\documentclass[12pt]{article}
+\usepackage{amssymb}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{amsmath}
+\usepackage{amsmath,amssymb,amsthm}
+\usepackage{multicol}
+\usepackage{color}
+\usepackage{graphicx}
+\usepackage{hyperref}
+
+%TCIDATA{OutputFilter=Latex.dll}
+%TCIDATA{LastRevised=Wed Dec 15 21:36:06 2010}
+%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
+%TCIDATA{CSTFile=article.cst}
 
@@
 \newtheorem{mynote}{Note}[section]
+%\newtheorem{proof}{Proof}
 \theoremstyle{definition}
@@
 \newtheorem{remark}{Remark}
+\newtheorem{example}{Example}
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
 \newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
-
 \newcommand{\gf}{\mathfrak{g}}
 \newcommand{\af}{\mathfrak{a}}
+\newcommand{\aft}{\widetilde{\mathfrak{a}}}
 \newcommand{\afb}{\mathfrak{a}_{\bot}}
@@
 \newcommand{\pf}{\mathfrak{p}}
+%\input{tcilatex}
 
 \begin{document}
-\title{Nope}
+
+\title{Recursive properties of branching and Weyl-Verma formulas}
 \author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
 
+\maketitle
+
 \begin{abstract}
+Recurrent relations for branching coefficients are based on a special type of
+singular element decomposition. We show that this decomposition can be used to
+construct the parabolic Verma modules and finally to obtain the generalized
+Weyl-Verma formulas for characters.
+These Weyl-Verma formulas explicitly exhibit how branching and the generalized
+BGG-resolution properties are connected.
 \end{abstract}
@@
 
-The branching properties of Lie (affine Lie) algebras are highly important for
-applications in quantum field theory. This concernes for example the
-conformal field theory models \cite{difrancesco1997cft},\cite
-{coquereaux2008conformal}.
-
-% There are different approaches to deal with the branching coefficients. Some
-% of them use the BGG resolution \cite{bernstein1975differential} (for
-% Kac-Moody algebras the algorithm is described in \cite{kac1990idl},\cite
-% {wakimoto2001idl}).
-
-In this paper we demonstrate that for an arbitrary reductive subalgebra
+Branching properties of Lie (affine Lie) algebras are highly important for
+applications in quantum field theory (see for example the conformal field
+theory models \cite{difrancesco1997cft},\cite{coquereaux2008conformal}). In
+this paper we demonstrate that for an arbitrary reductive subalgebra
 branching is directly connected with the BGG resolution and in particular
 exhibits the resolution properties in terms of the $\mathcal{O}^{p}$
-category \cite{lepowsky1977generalization} (the parabolic generalization of the cathegory $%
-\mathcal{O}$ \cite{bernstein1976category}).
+category \cite{lepowsky1977generalization} (the parabolic generalization of
+the cathegory $\mathcal{O}$ \cite{bernstein1976category}).
 
-To show this we use the recursive approach to branching presented in \cite{2010arXiv1007.0318L} (similar to the one used in \cite{ilyin812pbc} for maximal
-embeddings). We consider the subalgebra $\frak{a}$ together with its
-counterpart $\frak{a}_{\bot }$ ''orthogonal'' to $\frak{a}$ with respect to
-the Killing form and also $\widetilde{\frak{a}_{\perp }}:=\frak{a}_{\perp
-}\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus 
-\frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$. For any reductive
-algebra $\frak{a}$ the subalgebra $\frak{a}_{\bot }\hookrightarrow \frak{g}$
-is regular and reductive. For a highest weight integrable module $L^{\left(
-\mu \right) }$ and orthogonal pair of subalgebras $\left( \frak{a},\frak{a}%
-_{\bot }\right) $ we consider the singular element $\Psi ^{\left( \mu
-\right) }$ (the numerator in the Weyl character formula $ch\left( L^{\mu
-}\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see
-for example \cite{humphreys1997introduction}) the Weyl denominator $R=\Psi _{%
-\frak{a}_{\bot }}^{\left( 0\right) }$ and the projection $\Psi _{\left( 
-\frak{a},\frak{a}_{\bot }\right) }^{\left( \mu \right) }=\pi _{\frak{a}}%
-\frac{\Psi _{\frak{g}}^{\left( \mu \right) }}{\Psi _{\frak{a}_{\bot
-}}^{\left( 0\right) }}$. The element $\Psi _{\frak{g}}^{\left( \mu \right) }$
-can be decomposed with respect to the set of Weyl numerators $\Psi _{\frak{a}%
-_{\bot }}^{\left( \mu \right) }$ of $\frak{a}_{\bot }$. This decomposition
-provides the possibility to construct the set of highest weight modules $L_{%
-\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. When
-the injection \ $\frak{a}_{\bot }\hookrightarrow \frak{g}$ \ satisfies the
-''standard parabolic'' conditions these modules give rise to the parabolic
-Verma modules $M_{\left( \widetilde{\frak{a}_{\perp }}\hookrightarrow \frak{g%
-}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$ so that the initial
-character $ch\left( L^{\mu }\right) $ is finally decomposed into the
-alternating sum of such. On the other hand when the parabolic conditions are
-violated the construction survives and exhibites a decomposition with
-respect to a set of Verma modules $M_{\left( \widetilde{\frak{b}_{\perp }},%
-\frak{g}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. In such a
-situation the algebra $\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in 
-$\frak{g}$ but a contraction of $\widetilde{\frak{a}_{\perp }}$.
+The resolution of the irreducible modules in terms of infinite-dimensional ones is important for the
+theory of integrable spin chains \cite{derk1008}. In the Baxter $\mathcal{Q}$-operator approach the generic transfer
+matrices corresponding to the (generalized) Verma modules are factorized into the product of Baxter
+operator. Then the resolution allows to calculate the transfer matrices for finite-dimensional
+auxiliary spaces.
+
+To show the connection of the BGG resolution with the branching we use the recursive approach presented in \cite
+{2010arXiv1007.0318L} (similar to the one used in \cite{ilyin812pbc} for
+maximal embeddings). We consider the subalgebra $\af$ together with its
+counterpart $\afb$ ''orthogonal'' to $\af$ with respect to
+the Killing form and also $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\af}}\oplus
+\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. For any reductive
+algebra $\af$ the subalgebra $\afb\hookrightarrow \gf$
+is regular and reductive. For a highest weight integrable module $%
+L^{\left(\mu \right) }$ and orthogonal subalgebra $\af_{\bot }$ we
+consider the singular element $\Psi ^{\left( \mu \right) }$ (the numerator
+in the Weyl character formula $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
+\mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite
+{humphreys1997introduction}) the Weyl denominator $\Psi _{\af_{\bot
+}}^{\left( 0\right) }$ for the orthogonal subalgebra and the projection $%
+\Psi _{\left( \af,\af_{\bot }\right) }^{\left( \mu \right) }=\pi _{%
+\af}\frac{\Psi _{\gf}^{\left( \mu \right) }}{\Psi _{\af_{\bot
+}}^{\left( 0\right) }}$. It is shown that the element $\Psi _{\gf%
+}^{\left( \mu \right) }$ can be decomposed into a combination of Weyl
+numerators $\Psi _{\af_{\bot }}^{\left( \nu \right) }$ with $\nu \in P_{%
+\mathfrak{a}_{\bot}}^{+}$. This decomposition provides the possibility to
+construct the set of highest weight modules $L_{\widetilde{\afb}%
+}^{\mu _{\widetilde{\afb}}}$. When the injection \ $\af%
+_{\bot }\hookrightarrow \gf$ \ satisfies the ''standard parabolic''
+conditions these modules give rise to the parabolic Verma modules $M_{\left(
+\widetilde{\afb}\hookrightarrow \gf\right) }^{\mu _{%
+\widetilde{\afb}}}$ so that the initial character $ch\left(
+L^{\mu }\right) $ is finally decomposed into the alternating sum of such. On
+the other hand when the parabolic conditions are violated the construction
+survives and exhibits a decomposition with respect to a set of Verma
+modules $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
+\widetilde{\afb}}}$. In such a situation the algebra $%
+\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in $\gf$ but a
+contraction of $\widetilde{\afb}$.
 
 Some general properties of the proposed decompositions are formulated in
-terms of a specific element $\Gamma _{\frak{a}\rightarrow \frak{g}}$ of the
-group algebra $\mathcal{E}\left( \frak{g}\right) $ called ''the injection
+terms of a specific element $\Gamma _{\af\rightarrow \gf}$ of the
+group algebra $\mathcal{E}\left( \gf\right) $ called ''the injection
 fan''. Using this tool the simple and explicit algorithm for branching
@@
 
-Possible further developments are discussed in Section \ref{sec:conclusion}.
+Possible further developments are presented in Section \ref{sec:conclusions}.
 
@@
 
-Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the underlying
-finite-dimensional subalgebras $\stackrel{\circ }{\frak{g}}$ and $\stackrel{%
-\circ }{\frak{a}}$ and an injection $\frak{a}\hookrightarrow \frak{g}$ such
-that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
-correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
-}}^{\ast }$ and $\frak{h}_{\stackrel{\circ }{\frak{a}}}^{\ast }\subset \frak{%
-h}_{\stackrel{\circ }{\frak{g}}}^{\ast }$\ . We use the following notations:
+Consider Lie algebras (affine Lie algebras) $\gf$ and $\af$ and an
+injection $\af\hookrightarrow \gf$ such that $\af$ is a
+reductive subalgebra $\frak{a\subset g}$ with correlated root spaces: $\frak{%
+h}_{\af}^{\ast }\subset \frak{h}_{\gf}^{\ast }$. We use the
+following notations:
 
-$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
-of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
--module with the highest weight $\nu $ );
+$\frak{g=n}^{-}+\frak{b}+\frak{n}^{+}$ --- the Cartan decomposition;
 
-$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
-\left( \mathrm{{resp. }\frak{a}}\right) $ ;
+$r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\gf$ $%
+\left( \mathrm{{resp. }\af}\right) $ ;
 
-$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
-^{+} $ $\left( \mathrm{{resp. }\Delta _{\frak{a}}^{+}}\right) $--- the
-positive root system (of $\frak{g}$ and $\frak{a}$ respectively);
+$\Delta $ $\left( \Delta _{\af}\right) $--- the root system; $\Delta
+^{+} $ $\left( \mathrm{{resp. }\Delta _{\af}^{+}}\right) $--- the
+positive root system (of $\gf$ and $\af$ respectively);
 
-$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
+$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\af}\left(
 \alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $%
-\Delta $ (resp. in $\left( \Delta _{\frak{a}}\right) $);
+\Delta $ (resp. in $\left( \Delta _{\af}\right) $);
 
-$\stackrel{\circ }{\Delta}$ , $\left( \stackrel{\circ }{\Delta _{\frak{a}}}%
-\right)$ --- the finite root system of the subalgebra $\stackrel{\circ }{%
-\frak{g}}$ (resp. $\stackrel{\circ }{\frak{a}}$);
+$S\quad \left( S_{\af}\right) $ --- the system of simple roots (of $%
+\gf$ and $\af$ respectively);
 
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
-the weight diagram of $L^{\mu }$ $\left( \mathrm{{resp. }L_{\frak{a}}^{\nu }}%
-\right) $ ;
+$\alpha _{i}$ , $\left( \alpha _{\left( \af\right) j}\right) $ --- the $%
+i$-th (resp. $j$-th) basic root for $\gf$ $\left( \mathrm{{resp.}\frak{a%
+}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
 
-$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
+$\delta $ --- the imaginary root of $\gf$ (and of $\af$ if any);
 
-$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
+$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \af\right) j}^{\vee
+}\right) $--- the basic coroot for $\gf$ $\left( \mathrm{{resp.}\af%
+}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
 
-$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
+$W$ , $\left( W_{\af}\right) $--- the corresponding Weyl group;
+
+$C$ , $\left( C_{\af}\right) $--- the fundamental Weyl chamber;
+
+$\bar{C}, \left(\bar{C_{\af}}\right)$ --- the closure of the
 fundamental Weyl chamber;
-
-$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
 
@@
 
-$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
-i $-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mathrm{{resp. }%
-\frak{a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}%
-}\right) $;
+$\rho $\ , $\left( \rho _{\af}\right) $\ --- the Weyl vector;
 
-$\delta $ --- the imaginary root of $\frak{g}$ (and of $\frak{a}$ if any);
+$L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
+of $\gf$ with the highest weight $\mu $\ ; (resp. integrable $\af$
+-module with the highest weight $\nu $ );
 
-$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
-}\right) $--- the basic coroot for $\frak{g}$ $\left( \mathrm{{resp. }\frak{a%
-}}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\af}^{\nu }\right) $ ---
+the weight diagram of $L^{\mu }$ (resp. ${}L_{\af}^{\nu }$ );
 
-$\stackrel{\circ }{\xi }$ , $\stackrel{\circ }{\xi _{\left( \frak{a}\right) }%
-}$ --- the finite (classical) part of the weight $\xi \in P$ , $\left( 
-\mathrm{{resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}}\right) $;
+$P$ (resp. $P_{\af} $) \ --- the weight lattice;
 
-$\lambda =\left( \stackrel{\circ }{\lambda };k;n\right) $ --- the
-decomposition of an affine weight indicating the finite part $\stackrel{%
-\circ }{\lambda }$, level $k$ and grade $n$;
-
-$P$ $\left( \mathrm{{resp.}P_{\frak{a}}}\right) $ \ --- the weight lattice;
-
-$P^{+}$ $\left( \mathrm{{resp.}P_{\frak{a}}^{+}}\right) $ \ --- the dominant
-weight lattice;
+$P^{+}$ (resp. $P_{\af}^{+} $) \ --- the dominant weight lattice;
 
@@
 }\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
-resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
-L_{\frak{a}}^{\nu } $);
+resp. }\in P_{\af}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
+L_{\af}^{\nu } $);
 
-$ch\left( L^{\mu }\right) $ $\left( \mathrm{{resp. }ch\left( L_{\frak{a}%
-}^{\nu }\right) }\right) $--- the formal character of $L^{\mu }$ $\left( 
-\mathrm{{resp. }L_{\frak{a}}^{\nu }}\right) $;
+$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\af}^{\nu
+}\right) $)--- the formal character of $L^{\mu }$ (resp. $L_{\af}^{\nu
+} $);
 
@@
 $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
-mult}\left( \alpha \right) }}\quad $ $\left( \mathrm{resp.}R_{\frak{a}%
-}:=\prod_{\alpha \in \Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{%
-\mathrm{mult}_{\frak{a}}\mathrm{\left( \alpha \right) }}\right) $--- the
-Weyl denominator.
+mult}\left( \alpha \right) }}\quad $ (resp. $R_{\af}:=\prod_{\alpha \in
+\Delta _{\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af%
+}\left( \alpha \right) } $)--- the Weyl denominator.
 
-\section{Orthogonal subalgebra and the singular element}
+\section{Orthogonal subalgebra and singular elements}
 
@@
 
-Consider the highest weight $\mu \in P^{+}$ of an integrable module $L^{\mu
-} $ of $\frak{g}$ and let $\frak{a}\subset \frak{g}$ be a reductive
-subalgebra of $\frak{g}$. Let $L^{\mu }$ be completely reducible with
-respect to $\frak{a}$, 
-\[
-L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
-}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }. 
-\]
-Using the projection operator $\pi _{\frak{a}}$ (to the weight space $\frak{%
+In this section we shall show how the recurrent approach to branching
+problem leads naturally to a presentation of the formal character in terms
+of parabolic (generalized) Verma modules. Consider a reductive Lie algebra $%
+\gf$ and its reductive subalgebra $\af\subset \gf$. Let $%
+L^{\mu} $ be the highest weight integrable module of $\gf$, $\mu \in
+P^{+}$. Let $L^{\mu }$ be completely reducible with respect to $\af$,
+\begin{equation*}
+L_{\gf\downarrow \af}^{\mu }=\bigoplus\limits_{\nu \in P_{\af%
+}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
+\end{equation*}
+Using the projection operator $\pi _{\af}$ (to the weight space $\frak{%
 h_{a}}^{\ast }$) one can rewrite this decomposition in terms of formal
@@
 \begin{equation}
-\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
-}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
+\pi _{\af}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\af%
+}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\af}^{\nu }\right) .
 \label{branching1}
 \end{equation}
-The module $L^{\mu }$ has the BGG-resolution (see
-\cite{bernstein1976category,bernstein1975differential,bernstein1971structure} and \cite{humphreys2008representations}). All
-the members of the filtration sequence are the direct sums of Verma modules
-and all their highest weights $\nu $ are strongly linked to $\mu $: 
-\[
+The module $L^{\mu }$ has the BGG-resolution (see \cite
+{bernstein1976category,bernstein1975differential,bernstein1971structure} and
+\cite{humphreys2008representations}). All the members of the filtration
+sequence are the direct sums of Verma modules and all their highest weights $%
+\nu $ are strongly linked to $\mu $:
+\begin{equation*}
 \left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
 W\right\} .
-\]
+\end{equation*}
 
@@
 
-Let us introduce the ''orthogonal partner'' $\frak{a}_{\bot }$ for a
-reductive subalgebra $\frak{a}$ in $\frak{g}$.
+Let $\frak{h}_{\af}$ be a Cartan subalgebra of $\mathfrak{g}$. For $%
+\mathfrak{a}\hookrightarrow \gf$ introduce the ''orthogonal partner'' $%
+\mathfrak{a}_{\bot }\hookrightarrow \gf$ .
 
-Consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to 
-$\frak{a}$, 
-\[
-\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
-h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} , 
-\]
-and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
-to $\frak{a}$, 
+Consider the root subspace $\frak{h}_{\perp \af}^{\ast }$ orthogonal to
+$\af$,
+\begin{equation*}
+\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
+h\in \frak{h}_{\af};\eta \left( h\right) =0\right\} ,
+\end{equation*}
+and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
+to $\af$,
+\begin{eqnarray}
+\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
+h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
+\label{delta a ort} \\
+\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
+}^{+}|\forall h\in \frak{h}_{\af};\beta ^{+}\left( h\right) =0\right\} .
+\notag
+\end{eqnarray}
+Let $W_{\afb}$ be the subgroup of $W$ generated by the
+reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\afb}^{+}$ . The subsystem $\Delta _{\afb}$ determines the
+subalgebra $\afb$ with the Cartan subalgebra $\frak{h}_{\af%
+_{\perp }}$. Let
+\begin{equation*}
+\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
+}|\forall h\in \frak{h}_{\af\oplus \afb};\eta \left(
+h\right) =0\right\}
+\end{equation*}
+so that $\gf$ has the subalgebras
 \begin{eqnarray*}
-\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
-h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} , \\
-\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
-}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
+\widetilde{\afb} &:&=\afb\oplus \frak{h}_{\perp }
+\\
+\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
 \end{eqnarray*}
-Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
-reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\frak{a}_{\perp
-}}^{+}$ . The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
-subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
-_{\perp }}$. Let 
-\[
-\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
-}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
-h\right) =0\right\} 
-\]
-so that $\frak{g}$ has the subalgebras 
-\begin{eqnarray*}
-\widetilde{\frak{a}_{\perp }} &:&=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
-\\
-\widetilde{\frak{a}} &:&=\frak{a}\oplus \frak{h}_{\perp }.
-\end{eqnarray*}
-Algebras $\frak{a}$ and $\frak{a}_{\perp }$ form the ''orthogonal pair'' $%
-\left( \frak{a},\frak{a}_{\perp }\right) $ of subalgebras in $\frak{g}$.
+Notice that $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ in general is not a
+subalgebra of $\mathfrak{g}$
 
@@
 \begin{equation}
-\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus 
-\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
-\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus 
-\frak{h}_{\frak{a}}.
+\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\afb}\oplus
+\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
+\afb}=\frak{\frak{h}_{\widetilde{\afb}}}\oplus
+\frak{h}_{\af}.
 \end{equation}
-For the subalgebras of an orthogonal pair $\left( \frak{a},\frak{a}_{\perp
-}\right) $ we consider the corresponding Weyl vectors, $\rho _{\frak{a}}$
-and $\rho _{\frak{a}_{\perp }}$ , and\ form the so called ''defects'' $%
-\mathcal{D}_{\frak{a}}$ and $\mathcal{D}_{\frak{a}_{\perp }}$ of the
-injection: 
+For the subalgebras $\af$ and $\afb$ consider the
+corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\afb} $ . Form the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
+D}_{\afb}$ of the injection:
 \begin{equation}
-\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho ,
+\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
 \end{equation}
 \begin{equation}
-\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
-_{\perp }}\rho .
+\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
+_{\perp }}\rho .  \label{defect ort}
 \end{equation}
@@
 \left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections to
-$h_{\widetilde{\frak{a}_{\perp }}}^{\ast }$ additionally shifted by the
-defect $-\mathcal{D}_{\frak{a}_{\perp }}$: 
-\[
-\mu _{\widetilde{\frak{a}_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
-a}_{\perp }}}\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp
-}},\quad w\in W. 
-\]
-In the case we do consider here among the weights $\left\{ \mu _{\widetilde{%
-\frak{a}_{\perp }}}\left( w\right) |w\in W\right\} $ one can always choose
-those located in the fundamental chamber $\overline{C_{\widetilde{\frak{a}%
-_{\perp }}}}$. Let $U$ be the set of representatives $u$ for the classes $%
-W/W_{\frak{a}_{\perp }}$ such that
+$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
+\mathcal{D}_{\afb}$:
+\begin{equation*}
+\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
+w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
+\end{equation*}
+For $\mu \in P^{+}$ among the weights $\left\{ \mu _{\afb}\left( w\right) |w\in W\right\} $ one can always choose those located in
+the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
+set of representatives $u$ for the classes $W/W_{\afb}$ such
+that
 
 \begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right)
-\in \overline{C_{\widetilde{\frak{a}_{\perp }}}}\right\} \quad .
-\label{U-def}
+U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
+\overline{C_{\afb}}\right\} \quad .  \label{U-def}
 \end{equation}
-For such a set $U$ introduce the weights 
-\[
-\mu _{\frak{a}}\left( u\right) :=\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
-\right] +\mathcal{D}_{\frak{a}_{\perp }}. 
-\]
+Thus we can select the following subsets:
+\begin{equation}
+\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
+\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
+_{\perp }},\quad u\in U,  \label{mu-a}
+\end{equation}
+and
+\begin{equation}
+\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
+\label{mu-a-tilda}
+\end{equation}
 
-Note that the subalgebra $\afb$ is regular by definition since it is built on the roots of the
-algebra $\gf$.
+Note that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
+since it is built on the roots of the algebra $\mathfrak{g}$.
 
-Consider the Weyl-Kac formula for $ch\left( L^{\mu }\right) $ in terms of
-singular elements \cite{humphreys1997introduction}: 
+For the modules we are interested in the Weyl-Kac formula for $\mathrm{ch}%
+\left( L^{\mu }\right) $ can be written in terms of singular elements \cite
+{humphreys1997introduction}
+\begin{equation*}
+\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
+)-\rho },
+\end{equation*}
+namely,
 \begin{equation}
-ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left(
-0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R},  \label{Weyl-Kac2}
+\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
+^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
+\label{Weyl-Kac2}
 \end{equation}
-where 
-\[
-\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu
-+\rho )-\rho }. 
-\]
-The same form will be used for the submodules $ch\left( L_{\frak{a}}^{\nu
-}\right) $%
-\[
-ch\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left( \nu
-\right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
-}^{\left( \nu \right) }}{R_{\frak{a}}}, 
-\]
+The same is true for the submodules $\mathrm{ch}\left( L_{\af}^{\nu
+}\right) $ in (\ref{branching1})
+\begin{equation*}
+\mathrm{ch}\left( L_{\af}^{\nu }\right) =\frac{\Psi _{\af}^{\left(
+\nu \right) }}{\Psi _{\af}^{\left( 0\right) }}=\frac{\Psi _{\af%
+}^{\left( \nu \right) }}{R_{\af}},
+\end{equation*}
 with
-\[
-\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
-}}\epsilon (w)e^{w\circ (\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}. 
-\]
+\begin{equation*}
+\Psi _{\af}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\af%
+}}\epsilon (w)e^{w(\nu +\rho _{_{\af}})-\rho _{_{\af}}}.
+\end{equation*}
 
@@
 we get the relation connecting the singular elements $\Psi ^{\left( \mu
-\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ : 
+\right) }$ and $\Psi _{\af}^{\left( \nu \right) }$ :
 \begin{eqnarray}
-\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
+\pi _{\af}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
 )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
-(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
-\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
-\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
-mult}_{\frak{a}}(\beta )}},  \nonumber  \label{eq:4} \\
-\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
-&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
-}^{\left( \nu \right) }}{R_{\frak{a}}}.
+(\alpha )}}\right) &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{%
+\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{\af})-\rho _{%
+\af}}}{\prod_{\beta \in \Delta _{\af}^{+}}(1-e^{-\beta })^{\mathrm{%
+mult}_{\af}(\beta )}},  \notag  \label{eq:4} \\
+\pi _{\af}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
+&=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\af%
+}^{\left( \nu \right) }}{R_{\af}}.
 \end{eqnarray}
-Here $\Delta _{\frak{a}}^{+}$ is the set of positive roots of the subalgebra 
-$\frak{a}$ (without loss of generality we consider them as vectors from the
-positive root space $\frak{h}^{\ast +}$ of $\frak{g}$).
 
-To describe the recurrent properties for branching coefficients $b_{\nu
-}^{(\mu )}$ we shall use the technique first proposed in \cite{ilyin812pbc}.
-One of the main tools is the set of weights $\Gamma _{\frak{a}\rightarrow 
-\frak{g}}$ called the injection fan:
+\subsection{Decomposing the singular element.}
 
-\begin{definition}
-\label{fan-definition} For the product 
+\label{subsec:decomp-sing-element}
+
+Now we shall perform a decomposition of the singular element $\Psi ^{\left(
+\mu \right) }$ in terms of singular elements of the orthogonal subalgebra
+modules:
+
+\begin{lemma}
+Let $\af_{\bot }$ be the orthogonal partner of a reductive subalgebra $%
+\af\hookrightarrow \gf$ with $\frak{h}=\frak{\frak{h}_{\af}}%
+\oplus \frak{h}_{\afb}\oplus \frak{h}_{\perp }$, $\widetilde{%
+\afb}=\afb\oplus \frak{h}_{\perp }$ and $%
+\widetilde{\af}=\af\oplus \frak{h}_{\perp }$.
+
+$L^{\mu }$ be the highest weight integrable module with $\mu \in P^{+}$ and
+
+$\Psi ^{\left( \mu \right) }$\ -- the singular element of $L^{\mu }$.
+
+Then the element $\Psi ^{\left( \mu \right) }$ can be decomposed into the
+sum over $u\in U$ (see (\ref{U-def})) of singular elements $\Psi _{\af%
+_{\perp }}^{\mu _{\afb}\left( u\right) }$ with the coefficients
+$\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
 \begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
-_{\frak{a}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\frak{a}%
-}(\pi _{\frak{a}}\alpha )}=-\sum_{\gamma \in P_{\frak{a}}}s(\gamma
-)e^{-\gamma }  \label{eq:6}
+\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\widetilde{%
+\mathfrak{a}}}\left( u\right) }\Psi _{\afb}^{\mu _{\af%
+_{\perp }}\left( u\right) }.  \label{sing decomp main}
 \end{equation}
-consider the carrier $\Phi _{\frak{a}\subset \frak{g}}\subset P_{\frak{a}}$
-of the function $s(\gamma )=\det \left( \gamma \right) $ : 
+\end{lemma}
+
+\begin{proof}
+With $u\in U$ and $v\in W_{\af_{\bot }}$ perform the decomposition
+\[
+u(\mu +\rho )=\pi _{\left( \aft\right) }u(\mu +\rho )+\pi _{\left(
+\afb\right) }u(\mu +\rho )
+\]
+for the singular weight $vu(\mu +\rho )-\rho $:
 \begin{equation}
-\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}|s(\gamma
-)\neq 0\right\}   \label{eq:37}
+\begin{array}{lcl}
+vu(\mu +\rho )-\rho  & = & \pi _{\left( \af\right) }\left( u(\mu +\rho
+)\right) -\rho +\rho _{\afb}
+\\
+&  & +\ v\left( \pi _{\left( \aft_{\perp }\right) }u(\mu
++\rho )-\rho _{\afb}+\rho _{\afb}\right) -\rho _{%
+\afb} .
+\end{array}
+\label{sing-decomp-1}
 \end{equation}
-The ordering of roots in $\stackrel{\circ }{\Delta _{\frak{a}}}$ induce the
-natural ordering of the weights in $P_{\frak{a}}$. Denote by $\gamma _{0}$
-the lowest vector of $\Phi _{\frak{a}\subset \frak{g}}$ . The set 
+Use the defect $\mathcal{D}_{\af_{\bot }}$ (\ref{defect ort}) to
+simplify the first line in (\ref{sing-decomp-1}):
+\[
+\begin{array}{r}
+\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
+\afb}= \\
+\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\pi _{\aft%
+}\rho -\pi _{\af_{\bot }}\rho +\rho _{\af_{\bot }}= \\
+=\pi _{\left( \aft\right) }\left( u(\mu +\rho )-\rho \right) +\mathcal{D}%
+_{\af_{\bot }},
+\end{array}
+\]
+and the second one:
+\[
+\begin{array}{c}
+v\left( \pi _{\left( \afb\right) }u(\mu +\rho
+)-\rho _{\afb}+\rho _{\afb}\right) -\rho _{\af%
+_{\perp }}= \\
+v\left( \pi _{\left( \af_{\bot }\right) }u(\mu +\rho )-%
+\mathcal{D}_{\af_{\bot }}-\pi _{\left( \af_{\bot }\right) }\rho
++\rho _{\af_{\bot }}\right)
+-\rho _{\af_{\bot }}= \\
+=v\left( \pi _{\left( \af_{\bot }\right) }\left[ u(\mu
++\rho )-\rho \right] -\mathcal{D}_{\af_{\bot }}+\rho _{\af_{\bot
+}}\right) -\rho _{\af_{\bot }}.
+\end{array}
+\]
+These expressions provide the desired decomposition of the singular element $%
+\Psi ^{\mu }$ in terms of singular elements $\Psi _{\af%
+_{\perp }}^{\eta }$ of the $\afb$-modules $L_{%
+\afb}^{\eta }$:
 \begin{equation}
-\Gamma _{\frak{a}\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi
-_{\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} 
-\label{fan-defined}
+\begin{array}{l}
+\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\afb}}\epsilon
+(v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\aft}\left[ u(\mu +\rho )-\rho \right]
++\mathcal{D}_{\afb}}\sum_{v\in W_{\afb}}\epsilon
+(v)e^{v\left( \pi _{\left( \afb\right) }\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb}+\rho _{\af%
+_{\perp }}\right) -\rho _{\afb}}= \\
+=\sum_{u\in U}\;\epsilon (u)\Psi _{\afb}^{\pi
+_{\left( \afb\right) }\left[ u(\mu +\rho )-\rho
+\right] -\mathcal{D}_{\afb}}e^{\pi _{\left( \aft\right) }%
+\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}}.
+\end{array}
+\label{singular main}
 \end{equation}
-is called the \textit{injection fan}.
-\end{definition}
+\end{proof}
 
-It must be noticed that the injection fan is the universal instrument that
-depend only on the injection.
+\bigskip
 
-\section{Branching for Verma modules}
-\label{sec:branching-verma}
+\begin{remark}
+This relation can be considered as a generalized form of the Weyl formula
+for the singular element $\Psi _{\gf}^{\mu }$: the vectors $\mu _{%
+\widetilde{\mathfrak{a}}}\left( u\right) $ play the role of singular weights
+while the alternating factors $\epsilon (u)$ are extended to $\epsilon
+(u)\Psi _{\afb}^{\mu _{\afb}\left( u\right) }$. In
+fact when $\frak{a=g}$ both $\afb$and $\frak{h}_{\perp }$are
+zeros, $U=W$, and\ the original Weyl formula is reobtained via the
+trivilization of the singular elements: $\epsilon (u)\Psi _{\afb}^{\mu _{\afb}\left( u\right) }=\epsilon (u)$. In the opposite
+limit when $\frak{a=0}$, $\Delta _{\afb}=\Delta _{\gf}$, $%
+\frak{h}_{\perp }^{\ast }=0$, $\afb=\gf$, $\mathcal{D}_{%
+\afb}=0$, $U=W/W_{\afb}=e$ and $\Psi ^{\mu }$ is
+again reobtained, now via the trivilization of the set of vectors: $\mu _{%
+\af}\left( e\right) =0$.
+\end{remark}
 
-The formal character of Verma module is given by the expression
+\subsection{Reduction of Verma modules}
+
+In \cite{2010arXiv1007.0318L} the decomposition analogous to (\ref{singular main}) was
+used to construct the recurrent relations for branching coefficients $k_{\xi
+}^{\left( \mu \right) }$ corresponding to the injection $\af%
+\hookrightarrow \gf$:
 \begin{equation}
-  \label{eq:17}
-  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left(1-e^{-\alpha}\right)}
+\begin{array}{c}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
+_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{\af%
+}(u(\mu +\rho )-\rho )}+\right.  \\
+\left. +\sum_{\gamma \in \Gamma _{\af\rightarrow \gf}}s\left(
+\gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right) }\right) .
+\end{array}
+\label{recurrent rel}
 \end{equation}
-The denominator $R=\prod_{\alpha\in \Delta^{+}} \left(1-e^{-\alpha}\right)$ can be rewritten as the sum over the Weyl group of the algebra
+The recursion is goverened by the set $\Gamma _{\af\rightarrow \gf}
+$ called the injection fan. The later is defined as the carrier set $\left\{
+\xi \right\} _{\af\rightarrow \gf}$ for the coefficient function $%
+s(\xi )$
+\begin{equation*}
+\left\{ \xi \right\} _{\af\rightarrow \gf}:=\left\{ \xi \in P_{%
+\af}|s(\xi )\neq 0\right\}
+\end{equation*}
+appearing in the expansion
 \begin{equation}
-  \label{eq:20}
-  R=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}.
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left( 1-e^{-\pi
+_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
+}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
+)e^{-\gamma };\quad
 \end{equation}
-If we consider the regular embeddings, all the positive roots of the subalgebra $\af$ are in the set of positive roots of the algebra $\gf$, $\Delta^{+}_{\af}\subset \Delta^{+}$.
-Verma module can be decomposed into the set of Verma modules of the subalgebra:
+The weights in $\left\{ \xi \right\} _{\af\rightarrow \gf}$ are to
+be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi \right\} $
+-- and the zero element is to be eliminated:
 \begin{equation}
-  \label{eq:18}
-  \mathrm{ch}M^{\mu}=\sum_{\nu}b^{(\mu)}_{\nu} e^{\nu-\pi_{\af}\nu} \mathrm{ch}M^{\pi_{\af}\nu}_{\af}
-\end{equation}
-Using the equation \eqref{eq:21} we can write the recurrent relation for the branching coefficients $b^{(\mu)}_{\nu}$:
-\begin{equation}
-  \label{eq:19}
-   b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-        \delta_{\xi-\gamma_0,\mu}
-        +\sum_{\gamma \in
-          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) b_{\xi
-          +\gamma }^{\left( \mu \right) }\right).
+\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in
+\left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
 \end{equation}
 
-Inside the main Weyl chamber branching coefficients for Verma module coincide with the coefficients
-for reduction of irreducible representations.
+The recursion relation (\ref{recurrent rel}) was originally used to
+described branchings for integrable modules. There exists an important class
+of modules that also can be reduced with the help of an injection fan --
+these are the Verma modules.
 
-Now consider the following example. 
-Let Lie algebra $\gf$ be $so(5)$ and subalgebra $\af\subset \gf$ be $so(3)$. There are different embeddings of $so(3)\to so(5)$. Here we limit ourselves to the regular ones. 
-The root system of the algebra $so(5)$ consists of 8 roots.
-We denote simple roots by $\alpha_{1}=e_{1}-e_{2}$ and $\alpha_{2}=e_{2}$, where $e_{1},e_{2}$ form standard basis.
-The set of the positive roots is $\Delta^{+}=\left\{\alpha_{1}, \alpha_{1}+\alpha_{2}, \alpha_{1}+2\alpha_{2}, \alpha_{2}\right\}$.
-Each of these roots can be taken as the simple root of the subalgebra $so(3)$.
-At first we consider the subalgebra $so(3)$ with the root space spanned on $\beta=\alpha_{1}+2\alpha_{2}$.
-Verma module $M^{\mu}$ with the highest weight $\mu=\omega_{1}+2\omega_{2}=2\alpha_{1}+3\alpha_{2}$ is shown at Figure \ref{fig:B2_Verma}.
+For a regular embedding $\af\hookrightarrow \gf$ we have the
+corresponding embedding for the root systems $\Delta _{\mathfrak{a}%
+}^{+}\hookrightarrow \Delta ^{+}$ . Moreover, in this case it is reasonable
+to enlarge the subalgebra $\af$ and consider $\frak{b}=\af\oplus
+\frak{h}_{\perp \af}$ . In this case the weights of a $\frak{b}$-module
+can be considered in $\frak{h}^{\ast }$ . Verma module is decomposable for
+any highest weight:
+\begin{equation}
+\mathrm{ch}M^{\mu }=\sum_{\nu }b_{\nu }^{(\mu )}\mathrm{ch}M_{\frak{b}}^{\nu
+}.
+\end{equation}
+Verma module $\mathrm{ch}M^{\mu }$ have one singular weight $\mu $ with the
+multiplicity ($+1$). The Weyl groups can be considered to be trivial. The
+orthogonal partner $\afb$ is also trivial and the recursion
+relation is simplified:
+\begin{equation*}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }%
+\;\left( \delta _{\xi -\gamma _{0},\mu }+\sum_{\gamma \in \Gamma _{\af%
+\rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma
+}^{\left( \mu \right) }\right) .
+\end{equation*}
+
+\begin{remark}
+Notice that inside the main Weyl chamber branching coefficients $k_{\xi
+}^{\left( \mu \right) }$ for Verma modules reduction coincide with the
+coefficients for reduction of integrable simple modules.
+\end{remark}
+
+\begin{example}
+\label{example:reduct-verma-modul}
+ Let $\mathfrak{g}=B_{2}$ be and consider $A_{1}=\mathfrak{a}%
+\hookrightarrow \mathfrak{g}$. There are different embeddings  $%
+A_{1}\hookrightarrow B_{2}$. Here we limit ourselves by the regular ones.
+The root system $\Delta _{B_{2}}$ consists of 8 roots. Let $%
+S_{B_{2}}=\left\{ \alpha _{1}=e_{1}-e_{2},\alpha _{2}=e_{2}\right\} $ where $%
+e_{1},e_{2}$ form the standard basis in $\mathbf{R}^{2}$. The set of the
+positive roots is $\Delta ^{+}=\left\{ \alpha _{1},\alpha _{1}+\alpha
+_{2},\alpha _{1}+2\alpha _{2},\alpha _{2}\right\} $. Each of these roots can
+be taken as the simple root of the $A_{1}-$subalgebra. Firstly  we consider
+the subalgebra $A_{1}$ with the simple root $\beta =\alpha _{1}+2\alpha _{2}$%
+. Consider the Verma module $M^{\mu }$ with the highest weight $\mu =\omega
+_{1}+2\omega _{2}=2\alpha _{1}+3\alpha _{2}$ as it is shown at Figure \ref
+{fig:B2_Verma}.
+
 \begin{figure}[h!bt]
  \noindent\centering{
-    \includegraphics[width=120mm]{B2_Verma.pdf}
+   \includegraphics[width=120mm]{B2_Verma}
   }
  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}
-
+    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
+Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}
   \label{fig:B2_Verma}
@@
 
-The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2} for the different regular embeddings $so(3)\to so(5)$.
-Here we can see that the picture depends upon the embedding and looks similar to the Verma modules of some subalgebra.
+The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2}
+for the regular embedding $A_{1}\rightarrow B_{2}$. Here we can
+see that the picture depends upon the embedding and looks similar to the
+Verma modules of some subalgebra.
+
 \begin{figure}[h!bt]
   \noindent\centering{
-    \includegraphics[width=120mm]{B2_Verma_Branch3}
+   \includegraphics[width=120mm]{B2_Verma_Branch4.pdf}
   }
-  \caption{Branching for the Verma modules}
-
+  \caption{Branching of the Verma module $M^{(1,2)}$ for the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
+    Branching coefficients for Verma module of the subalgebra are shown. Dashed line indicates the
+    direction of subalgebra modules.}
  \label{fig:B2_Verma_Branch2}
 \end{figure}
-In present paper we interpret this branching coefficients as the dimensions of the weight subspaces of the modules of contracted algebras.
+\end{example}
+In the present paper we interpret this branching coefficients as the dimensions
+of the weight subspaces of modules of contracted algebras.
 
-\section{Regular subalgebras and generalized Verma modules}
-\label{sec:regul-subalg-gener}
+\subsection{Weyl-Verma formulas.}
 
-Let us state the following lemma.
-\begin{lemma}
-\label{lemma-1}
-The quotient of the singular weights element $\Psi^{(\mu)}$ by the denominator $R_{\af_{\bot}}$ is given by the formal element corresponding to the modified set of the singular weights of $L_{\af\oplus\mathfrak{h}_d}^{(\pi_{\af\oplus\mathfrak{h}_d}\mu)}$ with the multiplicities given by the dimensions of $\af_{\bot}$-modules.
+\begin{statement}
+\bigskip For an orthogonal subalgebra $\afb$ in $\gf$
+(orthogonal partner of reductive $\af\hookrightarrow \gf$) the
+character of an integrable highest weight module $L^{\mu }$ can be presented
+as a combination (with integral coefficients) of parabolic Verma modules
+distributed by the set of weights $e^{\mu _{\aft}\left( u\right) }$:
+\begin{equation*}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{%
+\widetilde{\af}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\af%
+_{\perp }}\left( u\right) },
+\end{equation*}
+where $U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
+\overline{C_{\afb}}\right\} $ and $\Delta _{I}^{+}$ is
+equivalent to $\Delta _{\afb}^{+}$.
+\end{statement}
+
+\bigskip
+\begin{proof}
+By the definition (\ref{delta a ort}) the subalgebra $%
+\mathfrak{a}_{\bot }$ is regular and reductive. Consider its Weyl
+denominator $R_{\afb}:=\prod_{\alpha \in \Delta _{\af%
+_{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}%
+\mathrm{\left( \alpha \right) }}$ and the element $R_{J}:=\prod_{\alpha \in
+\Delta ^{+}\setminus \Delta _{\afb}^{+}}\left( 1-e^{-\alpha
+}\right) ^{\mathrm{mult}(\alpha )}$ as the factors in $R$: $\quad $%
+\begin{equation*}
+R=R_{J}R_{\afb}.
+\end{equation*}
+According to this factorization and the decomposition (\ref{sing decomp main}%
+) the character $\mathrm{ch}\left( L^{\mu }\right) $ can be written as
+\begin{eqnarray*}
+\mathrm{ch}\left( L^{\mu }\right) &=&\left( R_{J}\right) ^{-1}\left( R_{%
+\afb}\right) ^{-1}\Psi ^{\mu }=\left( R_{J}\right)
+^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\af}}\left( u\right) }\epsilon
+(u)\left( R_{\afb}\right) ^{-1}\Psi _{\afb}^{\mu _{%
+\afb}\left( u\right) } \\
+&=&\left( R_{J}\right) ^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\af}%
+}\left( u\right) }\epsilon (u)L_{\afb}^{\mu _{\afb}\left( u\right) },
+\end{eqnarray*}
+where $\left\{ L_{\afb}^{\mu _{\afb}\left(
+u\right) }|u\in U\right\} $ is the set of finite-dimensional $\af%
+_{\perp }$-modules with the highest weights $\mu _{\afb}\left(
+u\right) $. We are interested in nontrivial subalgebras $\af$ and
+correspondingly in nontrivial $\afb$ (the case of a trivial
+orthogonal subalgebra arise when $\af=\gf$ and was considered
+above (see Remark 1)). This means that $r_{\af}\geq 1$ and $r_{\af%
+_{\perp }}<r$. Due to the fact that any maximal regular subalgebra has the
+Dynkin scheme obtained by one or two node subtractions from the extended
+Dynkin scheme and the extended scheme has at most one dependent root (the
+highest root) the set of roots $\Delta _{\afb}^{+}$ is always
+equivalent to the one $\Delta _{I}^{+}$ generated\ by some subset $I\subset
+S $ of simple roots.
+
+It follows that we can (by redefining the set $\Delta ^{+}$) identify $%
+\Delta _{\afb}^{+}$ with the subset $\Delta _{I}^{+}$ \ where $%
+I\subset S$ . This allows us to introduce the elements necessary to compose
+the generalized Verma modules
+\cite{lepowsky1977generalization,humphreys2008representations}.
+We have two sets of root
+vectors $\left\{ x_{\xi }\in \gf_{\xi }|\xi \in \Delta _{I}^{+}\right\}
+$ and $\left\{ x_{\eta }\in \gf_{\eta }|\eta \in \Delta ^{+}\setminus
+\Delta _{I}^{+}\right\} $. They generate nilpotent subalgebras of $\frak{n}%
+^{+}$:
+\begin{equation*}
+\frak{n}_{I}^{+}:=\sum_{\xi \in \Delta _{I}^{+}}\gf_{\xi },\quad
+\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\gf%
+_{\eta }.
+\end{equation*}
+The first subalgebra together with its negative counterpart $\frak{n}%
+_{I}^{-} $ generates a simple subalgebra
+\begin{equation*}
+\frak{s}_{I}=\frak{n}_{I}^{-}+\frak{h}_{I}+\frak{n}_{I}^{+}.
+\end{equation*}
+We enlarge it with the remaining Cartan generators and introduce the
+subalgebra:
+\begin{equation*}
+\frak{l}_{I}=\frak{n}_{I}^{-}+\frak{h}+\frak{n}_{I}^{+}.
+\end{equation*}
+The semidirect product of subalgebras $\frak{l}_{I}$ and $\frak{u}_{I}^{+}$
+gives a parabolic subalgebra $\frak{p}_{I}\hookrightarrow \gf$ :
 \begin{equation}
-  \label{eq:4}
-  \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\prod_{\alpha\in \Delta^{+}_{\afb}}\left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=
-    \sum_{u\in W/W_{\afb}}\epsilon(u)e^{\pi_{\tilde\af}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \mathrm{ch}_{\af_{\bot}}
-      L^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}
+\frak{p}_{I}=\frak{l}_{I}\vartriangleright \frak{u}_{I}^{+},
+\label{paralolic subalg}
 \end{equation}
-\end{lemma}  
-\begin{proof}
-  Consider $\Psi^{(\mu)}_{\mathfrak{g}}$. It is given by the sum over the Weyl group.
+Its universal enveloping $U\left( \frak{p}_{I}\right) $ is a subalgebra in $%
+U\left( \gf\right) $. According to the obtained structure (\ref
+{paralolic subalg}) the $\frak{l}_{I}$-modules $L_{\afb}^{\mu _{%
+\afb}\left( u\right) }$ can be easily lifted to $\frak{p}_{I}$%
+-modules using the trivial action of the nilradical $\frak{u}_{I}^{+}$. The
+latter induce $U\left( \gf\right) $-modules in a standard way:
+\begin{equation*}
+M_{I}^{\mu _{\afb}\left( u\right) }=U\left( \gf\right)
+\otimes _{U\left( \frak{p}_{I}\right) }L_{\afb}^{\mu _{\af%
+_{\perp }}\left( u\right) }.
+\end{equation*}
+According to the defenition presented in \cite{lepowsky1977generalization}
+these are the \textit{generalized Verma modules}
+generated by the highest weights $\mu _{\af%
+_{\perp }}\left( u\right) $. As a $U\left( \frak{u}_{I}^{-}\right) $-module
+each $M_{I}^{\mu _{\afb}\left( u\right) }$ is isomorphic to $%
+U\left( \frak{u}_{I}^{-}\right) \otimes $ $L_{\afb}^{\mu _{%
+\afb}\left( u\right) }$ and thus its character can be written
+with the help of Kostant-Heckman function \cite{KostantHeckman1982} corresponding
+to the injection of the orthogonal subalgebra $\afb\hookrightarrow \gf$:
+\begin{equation*}
+\mathrm{ch}M_{I}^{\mu _{\afb}\left( u\right) }=\mathcal{KH}_{%
+\afb\hookrightarrow \gf}\mathrm{ch}L_{\afb}^{\mu _{\afb}\left( u\right) }.
+\end{equation*}
+As far as the function $\mathcal{KH}_{\afb\hookrightarrow \frak{%
+g}}$ is generated by the denominator $R_{I}$ the last expression can be
+rewritten in the form
+\begin{equation*}
+\mathrm{ch}M_{I}^{\mu _{\afb}\left( u\right) }=\frac{1}{R_{I}}%
+\mathrm{ch}L_{\afb}^{\mu _{\afb}\left( u\right) }.
+\end{equation*}
+This means that we have obtained the generalized Weyl-Verma character formula
+-- the decomposition of $\mathrm{ch}\left(
+L^{\mu }\right) $ in terms of generalized Verma modules characters:
 \begin{equation}
-    \label{eq:6}
-    \Psi^{(\mu)}_{\mathfrak{g}}=\sum_{w\in W}\epsilon(w)e^{w(\mu+\rho)-\rho}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
+u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\afb}\left(
+u\right) }.  \label{char in gen verma mod}
 \end{equation}
-  We can divide the summation to the sum over $W_{\afb}$ and sum over all the classes of $W/W_{\afb}$: $w=vu,\; v\in W_{\afb},\; u \in W/W_{\afb}$.
-We have the following obvious property of the projections:
-  \begin{equation}
-    \label{eq:5}
-    u(\mu+\rho)=\pia(u(\mu+\rho))+\piab(u(\mu+\rho))+\pi_{h_{\perp}^*}(u(\mu+\rho))
-  \end{equation}
- Since $\mathfrak{h}_{\af}^*,\mathfrak{h}_{\perp}^*$ are invariant under the action of $v\in W_{\afb}$, we have
-  \begin{equation}
-    \label{eq:8}
-    vu(\mu+\rho)-\rho=v\cdot(\piab(u(\mu+\rho))-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}+\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\hf_{\perp}^*}(u(\mu+\rho))
-  \end{equation}
-  Only the first term depends on $v$. So
-  \begin{equation}
-    \label{eq:9}
-    \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\mathrm{R}_{\afb}}=
-    \frac{\sum_{u\in W/W_{\afb}}\epsilon(u)e^{\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\mathfrak{h}_{\perp}}(u(\mu+\rho))}\cdot
-      \sum_{v\in W_{\afb}}\epsilon(v)e^{v(\piab u(\mu+\rho)-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}}}{\mathrm{R}_{\afb}}
-  \end{equation}
-  We can rewrite the r.h.s. as
-  \begin{equation}
-    \label{eq:10}
-    \sum_{u\in W/W_{\afb}}\epsilon(u)e^{\pi_{(\af\oplus\mathfrak{h}_d)}\left[u(\mu+\rho)-\rho\right]+\pi_{(\af\oplus \mathfrak{h}_d)}\cdot \rho-\rho+\rho_{\afb}}\cdot
-    \mathrm{ch}_{\afb}L^{\pi_{\afb}u(\mu+\rho)-\rho_{\afb}}.
-  \end{equation}
-  Since $\pi_{\afb}(u(\mu+\rho)-\rho)-(\rho_{\afb}-\pi_{\afb}\rho)=\pi_{\afb}(u(\mu+\rho)-\rho)-\mathcal{D}$ and $\pi_{\tilde\af}\rho-\rho=-\pi_{\afb}\rho$ we get the statement of the Lemma.
-
 \end{proof}
 
-\begin{corollary}
-  \label{sec:corollary-1}
-  If we apply the projection $\pi_{\af}$ to the subalgebra $\af$ to the equation (\ref{eq:4}) we obtain the ``Lemma 1'' from the paper \cite{2010arXiv1007.0318L} in the case of regular subalgebras $\af, \afb$.
-However this Lemma \ref{lemma-2} is more general then Lemma \ref{lemma-1}, since it holds for the special subalgebra $\af$.
-\begin{lemma}
-\label{lemma-2}
-Let $\af$ and $\af_{\perp }$ be the orthogonal pair of regular
-subalgebras in $\frak{g}$, with $\widetilde{\af_{\perp }}=\af%
-_{\perp }\oplus \frak{h}_{\perp }$ and $\widetilde{\af}=\af\oplus
-\frak{h}_{\perp }$ ,
+\begin{remark}
+Here the generalized Weyl-Verma character formula appear in a detailed
+form: the weights $\mu _{\aft}$ and the generalized Verma modules highest weights
+$\mu _{\afb}$ are indicated separately. The reason is that the
+highest weight of $M_{I}$-module is not equal to the projection of the maximal
+weight to $h^*_{\afb}$ (but must be additionally shifted by the defect).
+\end{remark}
 
-$L_{\frak{g}}^{\mu }$ be the highest weight module with the singular element
-$\Psi _{\frak{g}}^{\mu }$ ,
+\begin{example}
+  Continuing Example \ref{example:reduct-verma-modul} we consider the generalized Verma modules for the
+  embedding  $A_{1}\hookrightarrow B_{2}$ with the subalgebra $\afb$ built on the root $\alpha_{1}$
+  of $B_{2}$. The generalized Verma module $M^{\omega_{1}}_{I}$ with the highest weight
+  $\omega_{1}=e_{1}$ is shown in Figure \ref{fig:B2_Verma_Decomp}. The decomposition of the corresponding irreducible module
+  $L^{\omega_{1}}$ is indicated by the set of dashed contours of the involved generalized Verma
+  modules. 
+   \begin{figure}[h!bt]
+  \noindent\centering{
+   \includegraphics[width=120mm]{B2_Gen_Verma_Decomp}
+  }
+  \caption{Generalized Verma module  for the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. The
+    decomposition of $L^{\omega_{1}}$ is indicated by the set of dashed contours of the involved generalized Verma
+  modules. Dashed contours correspond to positive $\epsilon(u)$ and dotted to negative.}
 
-$R_{\af_{\perp }}$ be the Weyl denominator for $\af_{\perp }$.
+ \label{fig:B2_Verma_Decomp}
+\end{figure}
 
-Then the element $\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{%
-\af_{\perp }}}\right) $ can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
-the singular elements $e^{\mu _{\af}\left( u\right) }$ with the
-coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
-}}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right) $:
-\begin{equation}
-\quad \pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af%
-_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{\af}\left(
-u\right) }\mathrm{\dim }\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
-\widetilde{\af_{\perp }}}\left( u\right) }\right) .
-\label{eq:11}
-\end{equation}
-\end{lemma}
-This lemma can be used to state the recurrent relation for the branching coefficients for the reduction of $\gf$-module to $\af$-modules.
-(See \cite{2010arXiv1007.0318L} for the details).
-It will be also useful for the discussion of special subalgebras.
-\end{corollary}
-\begin{corollary}
-  \label{corollary-2}
- If $\af, \afb$ are regular subalgebras the simple root system $\alpha_1,\dots, \alpha_r$ of $\gf$ sometimes can be chosen in such a way that simple roots $\beta_1,\dots,\beta_{r_{\afb}}$ of $\afb$ are contained in it.
-Denote the set of roots $\beta_i$ by $I$.
-This notation is in the agreement with the book \cite{humphreys2008representations}.
+\end{example}
+
+\begin{remark}
+As it was proved in \cite{humphreys2008representations} (see Proposition 9.6 ) the characters of the
+generalized Verma modules $M_{I}^{\mu _{\afb}\left( u\right) }$
+can be described as linear combinations of ordinary Verma modules of $\frak{g%
+}$:
 \begin{equation*}
-    I=\{\beta_1,\dots,\beta_{r_{\afb}}\}\subset \{\alpha_1,\dots,\alpha_r\}
+\mathrm{ch}M_{I}^{\mu _{\afb}\left( u\right) }=\sum_{w\in W_{%
+\afb}}\epsilon \left( w\right) \mathrm{ch}M^{w\left( \mu _{%
+\afb}\left( u\right) +\rho _{\afb}\right) -\rho _{%
+\afb}}
 \end{equation*}
-  Then the subset $I$ determines not only the subalgebra $\afb$, but also the minimal parabolic subalgebra $\mathfrak{p}_I$, such that $\afb\subset \mathfrak{p}$.
-Then we can consider the modules of the subcategory $\mathcal{O}^{\mathfrak{p}}$, for example the generalized Verma modules $M_{\mathfrak{p}}^{(\mu)}$.
-This modules are constructed from the irreducible highest-weight modules $L_{\pf}^{(\mu)}$ as follows
-  \begin{equation}
-    \label{eq:1}
-    M_{\pf}^{(\mu)}=U(\gf)\otimes_{U(\pf)} L^{(\mu)}_{\pf}
-  \end{equation}
-  Denote by $\tilde R$ the denominator constructed of the positive roots of $\gf$ which are not the roots of $\afb$.
-  \begin{equation}
-    \label{eq:2}
-    \tilde R = \prod_{\alpha\in \Delta^+\setminus \Delta^{+}_{\afb}} \left(1-e^{-\alpha}\right)^{\mathrm{mult}_{\gf} \alpha}
-  \end{equation}
-If we expand $\frac{1}{\tilde R}$ the coefficients near the terms $e^{\xi}$ are given by the Kostant partition function $p^I$ constructed from the roots of $\gf$ which are not in $I$. 
-The character of the generalized Verma module then can be formally written as
-\begin{equation}
-  \label{eq:3}
-  \mathrm{ch} M^{(\mu)}_{\pf}=\frac{1}{\tilde R} \mathrm{ch}L^{(\mu)}_{\pf}
-\end{equation}
-The character of the irreducible finite-dimensional $\pf$-module $L^{(\mu)}_{\pf}$ differs from the character of the irreducible finite-dimensional $\afb$-module by the factor $e^{\pi_{\tilde\af}(\mu)}$, since $\pf$ contains the full Cartan subalgebra $\hf\subset\gf$.
-Now if we multiply the statement (\ref{eq:4}) of the lemma \ref{lemma-1} by $\frac{1}{\tilde R}$ we get the character of irreducible highest-weight module $L^{(\mu)}$ on the left and the sum of the characters of generalized Verma modules on the right-hand side of the equation:
-\begin{multline}
-  \label{eq:7}
-  \mathrm{ch}L^{(\mu)}_{\gf}=
-  \sum_{u\in W/W_{\afb}}\epsilon(u)e^{\pi_{\af\oplus\mathfrak{h}_d}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \frac{1}{\tilde R}\mathrm{ch} L_{\afb}^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}=\\
-  \sum_{u \in W/W_{\afb}} \epsilon(u) \mathrm{ch} M^{(u(\mu+\rho)-\rho)}_{\pf}
-\end{multline}
-So we have recovered the Bernstein-Gelfand-Gelfand resolution \cite{bernstein1976category,bernstein1975differential,bernstein1971structure} for the parabolic category ${\cal O}^{\pf}$.
-\end{corollary}
+Substituting this expression in\ (\ref{char in gen verma mod}) and using the
+definitions (\ref{mu-a},\ref{mu-a-tilda}) and (\ref{defect ort}) we reobtain
+the standard Weyl-Verma decomposition of the character:
+\begin{equation*}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{w\in W}\;\epsilon (u)\mathrm{ch}%
+M^{w\left( \mu +\rho \right) -\rho }.
+\end{equation*}
+\end{remark}
 
-Note, that not all the examples of branching lead to the generalized Verma modules. For example,
-consider the embedding $\af_{1}=B_{4}\subset \gf=B_{6}$. As we mentioned in \cite{2010arXiv1007.0318L} the
-orthogonal subalgebra $\afb=B_{2}$. Then consider the regular subalgebra $\af=A_{1}\subset
-\af_{1}\subset \gf$ with the root system spanned over the first long root of $\af_{1}$. Its
-orthogonal subalgebra in $\gf$ contains the root systems of two algebras $B_{2}$. But those two root
-systems cannot be built on the simple roots of $\gf$.
-\section{Generalizations}
-\label{sec:generalizations}
+%\bigskip
 
-\begin{enumerate}
-\item If $\af$ is a special subalgebra of $\gf$, the equation (\ref{eq:4}) and the Lemma \ref{lemma-1} no longer holds since the module of the algebra can not be presented as the composition of the modules of the subalgebra.
-Only the projection of this module can be decomposed.
-So we have to rely on the Lemma \ref{lemma-2}, which holds in this case too \cite{2010arXiv1007.0318L}.
+\section{Conclusions}
 
-Again as in the Corollary \ref{corollary-2} we can multiply the equation (\ref{eq:11}) by the (projection of) the denominator $\frac{1}{\tilde R}$.
-This projection if well-defined due to the construction of $\afb$.
-\begin{equation}
-  \label{eq:12}
-  \pi_{\af}\left(\mathrm{ch} L^{(\mu)}_{\gf}\right)= \sum_{u\in U}\epsilon(u) \pi_{\af}\left(\frac{1}{\tilde R}\right) e^{\mu_{\af}(u)}\mathrm{dim} \left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
-\widetilde{\af_{\perp }}}\left( u\right) }\right) .
-\end{equation}
-Since the subalgebra $\afb$ is regular by construction,  at the right-hand side of the equation we see the generalized Verma module character projected on the root space of $\af$.
-So we have recovered the equation (\ref{eq:7}) in the projected form.
-\begin{equation}
-  \label{eq:13}
-   \pi_{\af}\left(\mathrm{ch} L^{(\mu)}_{\gf}\right)= \pi_{\af}\left(  \sum_{u \in W/W_{\afb}} \epsilon(u) \mathrm{ch} M^{(u(\mu+\rho)-\rho)}_{\pf}\right)
-\end{equation}
-We have also lost any trace of subalgebra $\af$. But we can rewrite the left-hand side as the combination of the irreducible highest weight modules of subalgebra $\af$
-\begin{equation}
-  \label{eq:14}
-  \sum_{\nu\in P^{+}_{\af}} b^{(\mu)}_{\nu} \mathrm{ch} L^{(\nu)}_{\af}= \sum_{u \in W/W_{\afb}} \epsilon(u) \pi_{\af}\left(   \mathrm{ch} M^{(u(\mu+\rho)-\rho)}_{\pf}\right)
-\end{equation}
-Using the Bernstein-Gelfand-Gelfand resolution for the subalgebra $\af$ we get the expression which links the projected characters of generalized Verma modules with the characters of Verma modules of special subalgebra:
-\begin{equation}
-  \label{eq:15}
-  \sum_{\nu\in P^+_{\af}}b^{(\mu)}_{\nu}\sum_{ w\in W_{\af}} \epsilon(w) \mathrm{ch} M_{\af}^{w(\mu+\rho_{\af})-\rho_{\af}} =  \sum_{u \in W/W_{\afb}} \epsilon(u) \pi_{\af}\left(   \mathrm{ch} M^{(u(\mu+\rho)-\rho)}_{\pf}\right)
-\end{equation}
+\label{sec:conclusions}
 
-\end{enumerate}
+In \cite{2010arXiv1007.0318L} it was demonstrated that the injection fan recursive mechanism
+works also for special injections. Here we must stress that the Weyl-Verma decomposition
+can be obtained in this case. The Weyl-Verma relations corresponding to the special
+subalgebras will describe the projections of characters of the initial module in terms
+of generalized Verma modules distributed in the subspace of $h^*$.
 
-\section{Applications}
-\label{sec:applications}
+Consider the situation where the simple roots are prescribed by some external
+forces (originating in physical applications conditions, for example). In this case
+the orthogonal partner cannot be generated by simple root vectors only.  The elements
+$\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\gf%
+_{\eta }$ do not form a subalgebra in $\gf$ because some nonsimple roots are lost in
+$\Delta ^{+}\setminus \Delta _{I}^{+}$. It is important to indicate that in this case
+the Weyl-Verma formula still exists. In it the generalized Verma modules correspond to
+the contractions \cite{Doebner1967Melsheimer} of the algebra $\frak{n}^{+}$ and the
+Weyl-Verma relations describes the decomposition of the representation space of $L^{\mu}$
+into the set of generalized Verma modules of contracted algebra
+$U\left(\frak{n}_c^{+}\right)$. The weight vectors are formed by the PBW-basis
+of $U\left(\frak{n}_c^{+}\right)$ and of $U\left( \afb \right)$. To consider such space
+as a $\gf$-module we must perform the deformation \cite{Nijenhuis1966Richardson} of
+the algebra $\frak{n}_c^{+}$ (restore the initial composition law). The space survives
+and after such a deformation the initial
+algebra generators will act properly on it.
 
-\section{Conclusion}
-\label{sec:conclusion}
+\section{Acknowledgments}
+The authors express their sincere gratitude to all those who prepared and performed the
+III International Conference "Models in Quantum Field Theory - 2010" dedicated to 70-th
+anniversary of A. N. Vassiliev.
 
-\section{Acknowledgements}
+The work was supported in part by the RFFI grant N 09-01-00504.
 
-The work was supported in part by RFFI grant N 09-01-00504 and the National
-Project RNP.2.1.1./1575.
+% \section{Applications}
+% \label{sec:applications}
+%
+% \section{Conclusion}
+% \label{sec:conclusion}
+%
+%
+% \section{Acknowledgements}
+%
+% The work was supported in part by RFFI grant N 09-01-00504 and the National
+% Project RNP.2.1.1./1575.
+%
 
-\section*{References}
-\bibliography{article}{}
 \bibliographystyle{utphys}
+\bibliography{article}
+{}
+
 \end{document}

### 2010-12-18 AffineLieAlgebras/MQFT2010/article.tex
New figures for MQFT paper, half of the Lecture 10.

@@
  \noindent\centering{
-   \includegraphics[width=120mm]{B2_Verma}
+   \includegraphics[width=140mm]{B2_Decomp}
  }
- \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
-Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}
-  \label{fig:B2_Verma}
+ \caption{Character decomposition of generalized Verma module $M^{\mu=\omega_{1}}_{I}$ to the
+   characters of the irreducible modules. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. The
+    highest weight $\mu$ is shown by the black arrow. }
 \end{figure}
 
+\begin{figure}[h!bt]
+ \noindent\centering{
+   \includegraphics[width=140mm]{B2_Exact}}
+ \caption{Part of the exact sequence
+   $M_{I}^{\mu(u_{(1)})}/\left(M_{I}^{\mu(w_{(2)})}/M_{I}^{\mu(w_{(3)})}\right)\to M^{\mu}_{I}\to
+   L^{\mu}\to 0 $ for Lie algebra $B_2$. Here $w_{(i)}\in  U$ is Weyl reflection of the length $i$, $\mu=\omega_{1}$.}
+
+\end{figure}
+
+%%  \begin{figure}[h!bt]
+%%   \noindent\centering{
+%%     \includegraphics[width=120mm]{B2_Verma}
+%%    }
+%%   \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+%%      The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
+%%  Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}
+%%    \label{fig:B2_Verma}
+%%  \end{figure}
+%%  
 The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2}
@@
 
-\begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=120mm]{B2_Verma_Branch4.pdf}
-  }
-  \caption{Branching of the Verma module $M^{(1,2)}$ for the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
-    Branching coefficients for Verma module of the subalgebra are shown. Dashed line indicates the
-    direction of subalgebra modules.}
- \label{fig:B2_Verma_Branch2}
-\end{figure}
+%%  
+%%  \begin{figure}[h!bt]
+%%    \noindent\centering{
+%%     \includegraphics[width=120mm]{B2_Verma_Branch4.pdf}
+%%    }
+%%    \caption{Branching of the Verma module $M^{(1,2)}$ for the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+%%      The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
+%%      Branching coefficients for Verma module of the subalgebra are shown. Dashed line indicates the
+%%      direction of subalgebra modules.}
+%%   \label{fig:B2_Verma_Branch2}
+%%  \end{figure}
+%%  
 \end{example}
@@
   modules. 
-   \begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=120mm]{B2_Gen_Verma_Decomp}
-  }
-  \caption{Generalized Verma module  for the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. The
-    decomposition of $L^{\omega_{1}}$ is indicated by the set of dashed contours of the involved generalized Verma
-  modules. Dashed contours correspond to positive $\epsilon(u)$ and dotted to negative.}
-
- \label{fig:B2_Verma_Decomp}
-\end{figure}
+%%     \begin{figure}[h!bt]
+%%    \noindent\centering{
+%%     \includegraphics[width=120mm]{B2_Gen_Verma_Decomp}
+%%    }
+%%    \caption{Generalized Verma module  for the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+%%      The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. The
+%%      decomposition of $L^{\omega_{1}}$ is indicated by the set of dashed contours of the involved generalized Verma
+%%    modules. Dashed contours correspond to positive $\epsilon(u)$ and dotted to negative.}
+%%  
+%%   \label{fig:B2_Verma_Decomp}
+%%  \end{figure}
 

### 2010-12-18 GeneralOverview/Lectures/2dqft.tex
New figures for MQFT paper, half of the Lecture 10.

@@
   \hline
-  Критический индекс & Термодинамическая величина & Значение индекса в \\
-  &  & двумерной модели Изинга\\
+  Критический  & Термодинамическая & Значение индекса в \\
+  индекс &  величина  & двумерной модели Изинга\\
   \hline
@@
 \end{equation}
+Теперь воспользуемся трансляционной инвариантностью:
+\begin{equation}
+  \label{eq:216}
+  S_{\mu\nu\rho\sigma}=\langle T_{\mu\nu}(0)T_{\rho\sigma}(-x)\rangle =\langle T_{\rho\sigma}(-x) T_{\mu\nu}(0)\rangle = S_{\rho\sigma\mu\nu}(-x).
+\end{equation}
+Если в теории сохраняется четность, то $S_{\mu\nu\rho\sigma}(x)=S_{\rho\sigma\mu\nu}(x)$.
+В силу масштабной инвариантности $T_{\mu\nu}$ имеет скейлинговую размерность 2, так как является плотностью.
+Следовательно функция Швингера при масштабных преобразованиях ведет себя так:
+\begin{equation}
+  \label{eq:217}
+  S_{\mu\nu\rho\sigma}(\lambda x)=\lambda^{-4} S_{\mu\nu\rho\sigma}(x)
+\end{equation}
+Теперь можно записать общий вид функции Швингера:
+\begin{multline}
+  \label{eq:218}
+  S_{\mu\nu\rho\sigma}(x)=(x^{2})^{-4} \left( A_{1}g_{\mu\nu} g_{\rho\sigma} (x^{2})^{2} + A_{2} (g_{\mu\rho}g_{\nu\sigma}\right. +\\
+  \left. g_{\mu\sigma}g_{\nu\rho}) (x^{2})^{2} +A_{3} (g_{\mu\nu} x_{\rho}x_{\sigma} +g_{\rho\sigma}x_{\mu}x_{\nu})x^{2} +A_{4} x_{\mu}x_{\nu}x_{\rho}x_{\sigma}\right)
+\end{multline}
+Кроме того, у нас имеется закон сохранения $\partial^{\mu} T_{\mu\nu}=0$, поэтому
+\begin{multline}
+  \label{eq:219}
+  \partial^{\mu}  S_{\mu\nu\rho\sigma}(x)=-(x^{2})^{-4} \left( 3(A_{4}+2 A_{3}) x_{\nu}x_{\rho}x_{\sigma}\right. +\\
+  \left. (4 A_{1}+3 A_{3}) g_{\rho\sigma} x_{\nu} x^{2} +(4 A_{2} - A_{3}) (g_{\rho\nu}x_{\sigma}+g_{\nu\sigma}x_{\rho}) x^{2}\right)=0
+\end{multline}
+Это равенство может выполняться для любого $x$ только если все коэффициенты в скобках равны нулю. То есть
+\begin{eqnarray}
+  \label{eq:220}
+  A_{1}=3 A\\
+  A_{2}=-A\\
+  A_{3}=-4 A\\
+  A_{4}=8 A
+\end{eqnarray}
+Окончательно получаем для функции Швингера
+\begin{multline}
+  \label{eq:221}
+  S_{\mu\nu\rho\sigma}(x)=\frac{A}{(x^{2})^{4}} \left( (3g_{\mu\nu} g_{\rho\sigma}-g_{\mu\rho}g_{\nu\sigma}-g_{\mu\sigma}g_{\nu\rho}) (x^{2})^{2} 
+  \right. \\
+  \left.-4 x^{2} (g_{\mu\nu} x_{\rho}x_{\sigma} +g_{\rho\sigma}x_{\mu}x_{\nu}) +8 x_{\mu}x_{\nu}x_{\rho}x_{\sigma}\right)
+\end{multline}
+Теперь прямой подстановкой можно проверить, что
+\begin{equation}
+  \label{eq:222}
+  S^{\mu\sigma}_{\mu\sigma}=\langle T^{\mu}_{\mu}(x) T^{\sigma}_{\sigma}(0)\rangle=0
+\end{equation}
+при любых значениях $x$. В частности $\langle T^{\mu}_{\mu}(0)\rangle=0$, то есть у оператора следа тензора энергии-импульса нулевое матожидание и среднеквадратичное отклонение в основном состоянии.
+
+\section{Лекция 10. Конформная инвариантность в двумерной теории.}
+\label{sec:lecture-10}
+
+В лекции \ref{sec:lecture-7} мы получили общее условие на вид инфинитезимальных конформных преобразований:
+\begin{equation}
+  \label{eq:223}
+  \partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu}=\frac{2}{d} \partial_{\rho}\epsilon^{\rho} \eta_{\mu\nu}.
+\end{equation}
+Теперь у нас $d=2$, $\mu,\nu=0,1$ и $\eta_{\mu\nu}=\delta_{\mu\nu}$, так как мы работаем в евклидовой теории. Расписывая компоненты уравнения \eqref{eq:223}, получаем
+\begin{eqnarray}
+  \label{eq:224}
+  \partial_{0} \epsilon_{1}+ \partial_{1}\epsilon_{0}=0& \Rightarrow & \quad\partial_{0} \epsilon_{1}=- \partial_{1}\epsilon_{0}\\
+  2\partial_{0}\epsilon_{0}=\partial_{0}\epsilon_{0}+\partial_{1}\epsilon_{1}& \Rightarrow& \quad \partial_{0} \epsilon_{0}= \partial_{1}\epsilon_{1}
+\end{eqnarray}
+То есть мы получили уравнения Коши-Римана. Введем комплексные координаты
+\begin{eqnarray}
+  \label{eq:225}
+  z=x_{0}+i x_{1}\\
+  \bar z = x_{0}-i x_{1}\\
+  \partial = \partial_{z}=\frac{1}{2}(\partial_{0}-i\partial_{1}) \\
+  \bar \partial=\partial_{\bar z}=\frac{1}{2} (\partial_{0}+i \partial_{1})\\
+  \epsilon=\epsilon_{0}+i \epsilon_{1}\\
+  \bar \epsilon=\epsilon_{0}-i \epsilon_{1}, 
+\end{eqnarray}
+тогда уравнения \eqref{eq:224} можно переписать в виде
+\begin{eqnarray}
+  \label{eq:226}
+  \partial \epsilon=0\\
+  \bar \partial \bar \epsilon=0.
+\end{eqnarray}
+Решениями будут любые голоморфные и антиголоморфные функции: $\epsilon=\epsilon(z)$ -- голоморфная функция и $\bar \epsilon=\bar \epsilon(\bar z)$ -- антиголоморфная.
+Таким образом мы видим, что алгебра локальных конформных преобразований в двумерном случае оказывается бесконечномерной алгеброй преобразований
+\begin{eqnarray}
+  \label{eq:227}
+  z\to f(z)\\
+  \bar z \to \bar f(\bar z)
+\end{eqnarray}
+Введем в алгебре конформых преобразований следующий базис:
+\begin{eqnarray}
+  \label{eq:228}
+  z'=z+\epsilon_{n}(z)\\
+  \bar z'=\bar z+\bar \epsilon_{n}(\bar z)\\
+  \epsilon_{n}(z)= -z^{n+1}\\
+  \bar \epsilon_{n}(\bar z)=-\bar z^{n+1}
+\end{eqnarray}
+Тогда соответствующие генераторы будут равны
+\begin{eqnarray}
+  \label{eq:229}
+  l_{n}=-z^{n+1}\partial\\
+  \bar l_{n}=-\bar z^{n+1}\bar \partial 
+\end{eqnarray}
+Легко видеть, что коммутационные соотношения имеют вид
+\begin{eqnarray}
+  \label{eq:230}
+  \left[l_{m},l_{n}\right]=(m-n) l_{m+n}\\
+  \left[\bar l_{m},\bar l_{n}\right]=(m-n) \bar l_{m+n}\\  
+  \left[l_{n},\bar l_{m}\right]=0
+\end{eqnarray}
+Мы видим, что алгебра распадается в прямую сумму $\mathcal{A} \oplus \bar{\mathcal{A}}$, каждая компонента --- это алгебра Витта (Witt algebra).
+Оказывается удобно продолжить теорию на случай независимых $z,\bar z$.
+Тогда теория распадется на два независимых сектора.
+Условие же $z^{*}=\bar z$ можно наложить в самом конце.
+Такая процедура соответствует комплексному продолжению всех функций от $x_{0},x_{1}$ на $x_{0},x_{1}\in \mathbb{C}^{2}$.
+Заметим, что вещественная плоскость сохраняется подалгеброй, натянутой на генераторы $l_{n}+\bar l_{n}$ и $i(l_{n}-\bar l_{n})$.
+
+\subsection{Глобальные конформные преобразования}
+\label{sec:global-conformal}
+
+Глобальными называются те преобразования, которые определены на всей сфере Римана $S^{2}=\mathbb{C}^{2}\cup \{\infty\}$.
+Понятно, что это может быть только при $n\geq -1$.
+Кроме того, чтобы рассмотреть окрестность точки $z=\infty$ можно сделать преобразование координат $z=-\frac{1}{w}$.
+Тогда
+\begin{equation}
+  \label{eq:231}
+  l_{n}=-z^{n+1}\partial = - \left(-\frac{1}{w}\right)^{n+1}\left(\frac{\partial z}{\partial w}\right) \partial_{w}=-\left(-\frac{1}{w}\right)^{n-1}\partial_{w}.
+\end{equation}
+Это выражение должно быть хорошо определено при $w\to 0$, то есть $n\leq 1$.
+Значит глобальные конформные преобразования генерируются $l_{\pm 1},l_{0},\bar l_{\pm 1},\bar l_{0}$.
+Заметим, что генераторы $l_{-1},\bar l_{-1}$ порождают трансляции, $i(l_{0}-\bar l_{0})$ -- вращения, $l_{0}+\bar l_{0}$ -- масштабные преобразования.
+Конечные глобальные преобразования имеют вид
+\begin{equation}
+  \label{eq:232}
+  z\to \frac{az+b}{cz+d}, \quad ad-bc=1,\quad a,b,c,d\in \mathbb{C}
+\end{equation}
+(И аналогично для $\bar z$).
+Если собрать коэффициенты $a,b,c,d$ в матрицу $A=
+\begin{pmatrix}
+  a & b\\
+  c & d
+\end{pmatrix}$, то ясно, что мы имеем дело с группой $SL_{2}(\mathbb{C})/Z_{2}\approx SO(3,1)$.
+Факторизация по $Z_{2}$ соответствует тому, что изменение знака у $a,b,c,d$ разом не меняет преобразования.
+Эта группа называется также группой проективных конформных преобразований.
+
+Трансляции, дилатации и вращения в матричном виде записываются следующим образом:
+\begin{eqnarray}
+  \label{eq:233}
+  &\mbox{трансляции} \quad x\to x+a, B=a^{0}+i a^{1},\quad &
+  \begin{pmatrix}
+    1 & B\\
+    0 & 1
+  \end{pmatrix}\\
+  &\mbox{вращения}\quad &
+  \begin{pmatrix}
+    e^{i \Theta/2} & 0\\
+    0 & e^{-i \Theta/2}
+  \end{pmatrix}\\
+  & \mbox{дилатации}\quad &
+  \begin{pmatrix}
+    \lambda & 0\\
+    0 & \lambda^{-1}
+  \end{pmatrix}\\
+  &\begin{array}{r}
+  \mbox{специальные конформные}    \\
+  \mbox{преобразования}
+  \end{array} 
+  \quad
+  C=h_{0}-i h_{1}\quad &
+  \begin{pmatrix}
+    1 & 0\\
+    C & 1
+  \end{pmatrix}
+\end{eqnarray}
+
+Глобальные конформные преобразования образуют группу, локальные же преобразования не обратимы, поэтому по отношению к ним говорят только об алгебре.
+
+Глобальные преобразования полезны для описания физических состояний.
+Допустим, мы работаем в базисе собственных состояний операторов $l_{0}, \bar l_{0}$, соответствующие собственные значения $h,\bar h$ -- независимые, вещественные, называются конформными весами или голоморфной и антиголоморфной размерностями.
+Так как $l_{0}+\bar l_{0}$ -- генератор дилатации, то скейлинговая размерность $\Delta=h+\bar h$, а поскольку $i(l_{0}-\bar l_{0})$ порождает вращения, то спин $s=h-\bar h$.
+
+Квазипримарное поле $\phi(z,\bar z)$ \eqref{eq:182} со спином $s$ при преобразованиях $z\to w(z), \bar z\to \bar w(\bar z)$ преобразуется так:
+\begin{equation}
+  \label{eq:234}
+  \phi'(w,\bar w)=\left( \frac{d w}{d z}\right)^{-h}\left( \frac{d \bar w}{d \bar z}\right)^{-\bar h} \phi(z,\bar z)
+\end{equation}
+Вариация квазипримарного поля при инфинитезимальных преобразованиях $w=z+\epsilon, \bar w =\bar z +\bar \epsilon$ имеет вид
+\begin{equation}
+  \label{eq:235}
+  \delta_{\epsilon,\bar \epsilon} \phi=\phi'(z,\bar z)-\phi(z,\bar z)=-(h\phi \partial \epsilon +\epsilon \partial \phi) - (\bar h \phi\bar \partial \bar \epsilon+\bar \epsilon \bar \partial \phi)
+\end{equation}
+Если поле ведет себя так не только при глобальных, но и при локальных преобразованиях, то оно называется {\it примарным}.
+
+\subsection{Тождества Уорда в двумерной конформной теории}
+\label{sec:ward-2d-cft}
 

### 2010-12-18 GeneralOverview/Lectures/2dqft.tex
Lecture 10 is completed

@@
 \label{sec:ward-2d-cft}
+В прошлой лекции мы получили общий вид тождеств Уорда для трансляций, поворотов и масштабных преобразований. Выпишем их здесь.
+\begin{eqnarray}
+  \label{eq:236}
+  \partial_{\mu}\langle T^{\mu}_{\nu} X\rangle = -\sum_{i} \delta(x-x_{i}) \partial_{\nu}^{(i)}\langle X\rangle\\
+  \langle (T^{\mu\nu}-T^{\nu\mu}) X\rangle =i\sum_{i}\delta(x-x_{i}) S^{\mu\nu}_{(i)}\langle X\rangle\\
+  \langle T^{\mu}_{\mu} X\rangle=-\sum_{i}\delta(x-x_{i}) \Delta_{(i)} \langle X\rangle
+\end{eqnarray}
+Прежде чем мы начнем переписывать тождества в комплексных координатах обсудим следующий вспомогательный математический факт: для голоморфных (антиголоморфных) функций можно использовать следующее представление для $\delta$-функции:
+\begin{equation}
+  \label{eq:237}
+  \delta(x)=\frac{1}{\pi} \bar \partial \frac{1}{z} = \frac{1}{\pi}\partial \frac{1}{\bar z}
+\end{equation}
+Заметим, что
+\begin{equation}
+  \label{eq:238}
+  \int_{M} d^{2}x \partial_{\mu}F^{\mu}=\int_{\partial M} d\xi_{\mu} F^{\mu}=\frac{1}{2i} \oint_{\partial M} (-dz F^{\bar z}+d\bar z F^{z})
+\end{equation}
+Для голоморфной функции
+\begin{equation}
+  \label{eq:239}
+  \frac{1}{\pi}\int_{M} d^{2}x \bar \partial\left( \frac{f(z)}{z}\right)=\frac{1}{2\pi i} \int_{\partial M} dz \frac{f(z)}{z}=f(0)=\int_{M} d^{2}x \delta(x) f(z)
+\end{equation}
+Теперь перепишем тождества Уорда \eqref{eq:236} в комплексных координатах:
+\begin{eqnarray}
+  \label{eq:240}
+  2\pi \partial \langle T_{\bar z z } X\rangle +2\pi \bar \partial \langle T_{zz}X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X \rangle\\
+  2\pi \partial \langle T_{\bar z \bar z } X\rangle +2\pi \bar \partial \langle T_{z\bar z}X\rangle = -\sum_{i} \bar \partial \frac{1}{\bar z-w_{i}} \partial_{\bar w_{i}} \langle X \rangle\\
+  2 \langle T_{z\bar z} X 1\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) \Delta_{i} \langle X\rangle\\
+  -2 \langle T_{z\bar z} X 1\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) s_{i} \langle X\rangle\\
+\end{eqnarray}
+Если сложить и вычесть два последних равенства и вспомнить определение $h, \bar h$, то получим
+\begin{eqnarray}
+  \label{eq:241}
+  2\pi \langle T_{\bar z z} X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}} h_{i} \langle X\rangle\\
+  2\pi \langle T_{z \bar z} X\rangle = -\sum_{i}  \partial \frac{1}{\bar z-\bar w_{i}} \bar h_{i} \langle X\rangle
+\end{eqnarray}
+Введем обозачения
+\begin{eqnarray}
+  \label{eq:242}
+  T=-2\pi T_{zz}\\
+  \bar T = -2 \pi T_{\bar z \bar z},
+\end{eqnarray}
+и подставим уравнения \eqref{eq:241} в первые два уравнения \eqref{eq:240}:
+\begin{eqnarray}
+  \label{eq:243}
+  \bar \partial \left( \langle T X\rangle -\sum_{i} \left( \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X\rangle + \frac{h_{i}}{(z-w_{i})^{2}} \langle X\rangle \right) \right) =0\\
+  \partial \left( \langle \bar T X\rangle -\sum_{i} \left( \frac{1}{\bar z-\bar w_{i}} \partial_{\bar w_{i}} \langle X\rangle + \frac{\bar h_{i}}{(\bar z-\bar w_{i})^{2}} \langle X\rangle \right) \right) =0
+\end{eqnarray}
+То есть выражения в скобках (анти)голоморфны. Следовательно
+\begin{equation}
+  \label{eq:244}
+  \langle T X\rangle =\sum_{i} \left( \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X\rangle + \frac{h_{i}}{(z-w_{i})^{2}} \langle X\rangle \right) +\mbox{регулярные члены}
+\end{equation}
+Это пример операторного разложения, которое мы будем обсуждать далее.
+
+Заметим, что вариация коррелятора при конформных преобразованиях дается тензором энергии-импульса:
+\begin{equation}
+  \label{eq:245}
+  \delta_{\epsilon}\langle X\rangle =\int_{M} d^{2}x \partial_{\mu} \langle T^{\mu\nu}(x)\epsilon_{\nu}(x) X \rangle
+\end{equation}
+В комплексных координатах она перепишется так:
+\begin{equation}
+  \label{eq:246}
+  \delta_{\epsilon,\bar \epsilon} \langle X\rangle = \frac{1}{2\pi i} \oint_{C} dz \epsilon(z) \langle T(z) X\rangle +\frac{1}{2\pi i} \oint_{C}  d\bar z \bar \epsilon(\bar z) \langle \bar T(\bar z) X\rangle
+\end{equation}
+Здесь интеграл берется по контуру, внутри которого находятся все аргументы $X$.
+Вообще говоря, это выражение для вариации верно для коррелятора любых полей, не только примарных.
+
+Применимость тождеств Уорда основывается на регулярности тензора энергии-импульса.
+Он должен быть везде хорошо определен.
+В частности, $T(0)$ должен быть конечен.
+Кроме того, если вычислить вариацию постоянного поля в точке $z=\infty$:
+\begin{equation}
+  \label{eq:247}
+  \delta_{\epsilon} \langle 1\rangle =-\frac{1}{2\pi i} \oint_{C}dz \epsilon(z) \langle T(z)\rangle =0
+\end{equation}
+где контур обходит точку $\infty$. Для специальных конформных преобразований $\epsilon(z)\sim z^{2}$, поэтому $T(z)\sim z^{-4},\quad z\to \infty$.
+
+\section{Лекция 11. Алгебра локальных полей. Операторное разложение. Алгебра Вирасоро}
+\label{sec:lecture-11}
 

### 2010-12-20 GeneralOverview/Lectures/2dqft.tex
Lecture 11 is completed.

@@
 \usepackage{amsmath,amssymb,amsthm}
+\usepackage{mathtools}
 \usepackage{pb-diagram}
@@
   Для любой унитарной квантовой теории поля в двух измерениях существует функция $c(\vec u)$ такая, что
+  \label{c-theorem}
   \begin{itemize}
@@
   \label{eq:184}
-  \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = \frac{1}{Z} \int \mathcal{D} \Phi \phi_{1}(x_{1})\phi_{2}(x_{2}) e^{-S[\Phi]}
+  \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = \frac{1}{Z} \int \mathcal{D} \Phi \varphi_{1}(x_{1})\varphi_{2}(x_{2}) e^{-S[\Phi]}
 \end{equation}
@@
   \label{eq:185}
-  \langle \phi_{1}(x_{1})\phi_{2}(x_{2})\rangle = \left|\frac{\partial x'_{1}}{\partial x_{1}}\right|^{\frac{\Delta_{1}}{d}}\left| \frac{\partial x'_{2}}{\partial x_{2}}\right|^{\frac{\Delta_{1}}{d}} \langle \phi_{1}(x'_{1})\phi_{2}(x'_{2})\rangle .
+  \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\rangle = \left|\frac{\partial x'_{1}}{\partial x_{1}}\right|^{\frac{\Delta_{1}}{d}}\left| \frac{\partial x'_{2}}{\partial x_{2}}\right|^{\frac{\Delta_{1}}{d}} \langle \varphi_{1}(x'_{1})\varphi_{2}(x'_{2})\rangle .
 \end{equation}
@@
   \label{eq:186}
-  \langle \phi_{1}(x_{1}) \phi_{2}(x_{2})\rangle = f(\left|x_{1}-x_{2}\right|)
+  \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = f(\left|x_{1}-x_{2}\right|)
 \end{equation}
@@
   \label{eq:187}
-   \langle \phi_{1}(x_{1}) \phi_{2}(x_{2})\rangle=\lambda^{\Delta_{1}+\Delta_{2}}  \langle \phi_{1}(\lambda x_{1}) \phi_{2}(\lambda x_{2})\rangle .
-\end{equation}
-То есть мы видим, что $ \langle \phi_{1}(x_{1}) \phi_{2}(x_{2})\rangle$ - однородная функция, $f(x)=\lambda^{\Delta_{1}+\Delta_{2}} f(\lambda x)$. Отсюда
+   \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle=\lambda^{\Delta_{1}+\Delta_{2}}  \langle \varphi_{1}(\lambda x_{1}) \varphi_{2}(\lambda x_{2})\rangle .
+\end{equation}
+То есть мы видим, что $ \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle$ - однородная функция, $f(x)=\lambda^{\Delta_{1}+\Delta_{2}} f(\lambda x)$. Отсюда
 \begin{equation}
   \label{eq:188}
-   \langle \phi_{1}(x_{1}) \phi_{2}(x_{2})\rangle = \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}.
+   \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}.
 \end{equation}
@@
   \label{eq:190}
-   \langle \phi_{1}(x_{1}) \phi_{2}(x_{2})\rangle =
+   \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle =
    \begin{cases}
@@
   \label{eq:192}
-  \langle \phi_{1}(x_{1})\phi_{2}(x_{2})\phi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}},\quad a+b+c=\Delta_{1}+\Delta_{2}+\Delta_{3}.
+  \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}},\quad a+b+c=\Delta_{1}+\Delta_{2}+\Delta_{3}.
 \end{equation}
@@
   \label{eq:196}
-   \langle \phi_{1}(x_{1})\phi_{2}(x_{2})\phi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{\Delta_{1}+\Delta_{2}-\Delta_{3}} x_{23}^{\Delta_{2}+\Delta_{3}-\Delta_{1}}x_{13}^{\Delta_{3}+\Delta_{1}-\Delta_{2}}}.
+   \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{\Delta_{1}+\Delta_{2}-\Delta_{3}} x_{23}^{\Delta_{2}+\Delta_{3}-\Delta_{1}}x_{13}^{\Delta_{3}+\Delta_{1}-\Delta_{2}}}.
 \end{equation}
@@
   \label{eq:197}
-  \langle \phi_{1}(x_{1})\phi_{2}(x_{2})\phi_{3}(x_{3})\phi_{4}(x_{4})\rangle=f\left(\frac{x_{12}x_{34}}{x_{13}x_{24}}; \frac{x_{12}x_{34}}{x_{23}x_{14}}\right) \prod_{i<j}^{4}x_{ij}^{\Delta/3-\Delta_{i}-\Delta_{j}},\quad \Delta=\sum_{i=1}^{4}\Delta_{i}.
+  \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\varphi_{4}(x_{4})\rangle=f\left(\frac{x_{12}x_{34}}{x_{13}x_{24}}; \frac{x_{12}x_{34}}{x_{23}x_{14}}\right) \prod_{i<j}^{4}x_{ij}^{\Delta/3-\Delta_{i}-\Delta_{j}},\quad \Delta=\sum_{i=1}^{4}\Delta_{i}.
 \end{equation}
@@
 
-Квазипримарное поле $\phi(z,\bar z)$ \eqref{eq:182} со спином $s$ при преобразованиях $z\to w(z), \bar z\to \bar w(\bar z)$ преобразуется так:
+Квазипримарное поле $\varphi(z,\bar z)$ \eqref{eq:182} со спином $s$ при преобразованиях $z\to w(z), \bar z\to \bar w(\bar z)$ преобразуется так:
 \begin{equation}
   \label{eq:234}
-  \phi'(w,\bar w)=\left( \frac{d w}{d z}\right)^{-h}\left( \frac{d \bar w}{d \bar z}\right)^{-\bar h} \phi(z,\bar z)
+  \varphi'(w,\bar w)=\left( \frac{d w}{d z}\right)^{-h}\left( \frac{d \bar w}{d \bar z}\right)^{-\bar h} \varphi(z,\bar z)
 \end{equation}
@@
   \label{eq:235}
-  \delta_{\epsilon,\bar \epsilon} \phi=\phi'(z,\bar z)-\phi(z,\bar z)=-(h\phi \partial \epsilon +\epsilon \partial \phi) - (\bar h \phi\bar \partial \bar \epsilon+\bar \epsilon \bar \partial \phi)
+  \delta_{\epsilon,\bar \epsilon} \varphi=\varphi'(z,\bar z)-\varphi(z,\bar z)=-(h\varphi \partial \epsilon +\epsilon \partial \varphi) - (\bar h \varphi\bar \partial \bar \epsilon+\bar \epsilon \bar \partial \varphi)
 \end{equation}
@@
 
-\section{Лекция 11. Алгебра локальных полей. Операторное разложение. Алгебра Вирасоро}
+\section{Лекция 11}
 \label{sec:lecture-11}
+
+\subsection{Алгебра локальных полей. Операторное разложение}
+\label{sec:ope}
+
+В набор локальных полей теории входят не только те поля, которые входят в плотность лагранжиана, но и их производные, произведения и так далее.
+Мы предполагаем, что набор локальных полей $A$ является полным, то есть существует некий базис $\{ A_{j}\}$, по которому можно разложить любое поле. Локальные поля образуют линейное пространство.
+
+Кроме того, мы предполагаем, что имеет место операторное разложение
+\begin{equation}
+  \label{eq:248}
+  A_{i}(x)A_{j}(y) =\sum_{k} C^{k}_{ij} (x,y) A_{k}(y),
+\end{equation}
+здесь $C_{ij}^{k}(x,y)$ -- функция. Равенство \eqref{eq:248} надо понимать в смысле корреляционных функций
+\begin{equation}
+  \label{eq:249}
+  \langle A_{i}(x) A_{j}(y) X\rangle = \sum_{k} C^{k}_{ij} (x,y) \langle A_{k}(y) X\rangle.
+\end{equation}
+Тогда набор локальных полей образует алгебру.
+
+Рассмотрим четырехточечную функцию и воспользуемся операторным разложением \eqref{eq:248}:
+\begin{equation}
+  \label{eq:250}
+  \langle A_{1}(x_{1}) A_{2}(x_{2}) A_{3}(x_{3}) A_{4}(x_{4}) \rangle =\sum_{k,l} C^{k}_{12} (x_{1}-x_{2}) D_{kl}(x_{2}-x_{4}) C^{l}_{34}(x_{3}-x_{4}) 
+\end{equation}
+Здесь мы воспользовались трансляционной инвариантностью, а также ввели обозначение для пропагатора
+\begin{equation}
+  \label{eq:251}
+  \langle A_{i}(x_{i}) A_{j}(x_{j}) \rangle =D_{ij}(x_{i}-x_{j}).
+\end{equation}
+Однако операторным разложением можно воспользоваться и в другом порядке, тогда для четырехточечной функции получим:
+\begin{equation}
+  \label{eq:252}
+  \langle A_{1}(x_{1}) A_{2}(x_{2}) A_{3}(x_{3}) A_{4}(x_{4}) \rangle =\sum_{k,l} C^{k}_{13} (x_{1}-x_{3}) D_{kl}(x_{3}-x_{4}) C^{l}_{24}(x_{2}-x_{4})   
+\end{equation}
+Приравняв правые части уравнений \eqref{eq:252},\eqref{eq:250} можно получить систему уравнений на коэффициенты $C^{k}_{ij}$.
+Если решить эти уравнения, то в принципе можно вычислять любые корреляторы, если известен набор полей и их конформных размерностей.
+Такой подход называется конформным бутстрапом.
+
+Корреляционные функции имеют особенности при совпадении положений полей. Именно характер этих особенностей важен при описании критического поведения (критические индексы и т.п.).
+Для произведения $T$ и примарного поля $\varphi$ с конформными размерностями $h,\bar h$ имеет место операторное разложение \eqref{eq:244}:
+\begin{eqnarray}
+  \label{eq:253}
+  T(z) \varphi(w,\bar w)\sim \frac{h}{(z-w)^{2}} \varphi(w,\bar w)+\frac{1}{z-w} \partial_{w} \varphi(w,\bar w)\\
+  \bar T(\bar z) \varphi(w,\bar w)\sim \frac{\bar h}{(\bar z-\bar w)^{2}} \varphi(w,\bar w)+\frac{1}{\bar z-\bar w} \partial_{\bar w} \varphi(w,\bar w)  
+\end{eqnarray}
+
+\subsection{Свободный бозон}
+\label{sec:free-boson}
+
+В качестве примера конформной теории рассмотрим свободное бозонное поле $\varphi$. Действие имеет вид
+\begin{equation}
+  \label{eq:254}
+  S=\frac{1}{2} g \int d^{2}x \partial_{\mu}\varphi \partial^{\mu}\varphi,
+\end{equation}
+а пропагатор дается равенством
+\begin{equation}
+  \label{eq:255}
+  \langle\varphi(x) \varphi(y)\rangle =-\frac{1}{4\pi g} \ln (x-y)^{2}+\text{const}
+\end{equation}
+В комплексных координатах пропагатор запишется следующим образом:
+\begin{equation}
+  \label{eq:256}
+  \langle \varphi(z,\bar z) \varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \left( \ln(z-w) + \ln(\bar z -\bar w)\right) +\text{const}
+\end{equation}
+Дифференцируя получаем
+\begin{eqnarray}
+  \label{eq:257}
+  \langle\partial_{z} \varphi(z,\bar z) \partial_{w}\varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \frac{1}{(z-w)^{2}}\\
+  \langle\partial_{\bar z} \varphi(z,\bar z) \partial_{\bar w}\varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \frac{1}{(\bar z-\bar w)^{2}}  
+\end{eqnarray}
+То есть имеет место операторное разложение полей $\partial \varphi$:
+\begin{equation}
+  \label{eq:259}
+  \partial \varphi(z) \partial \varphi(w) \sim -\frac{1}{4 \pi g} \frac{1}{(z-w)^{2}}
+\end{equation}
+
+Тензор энергии-импульса:
+\begin{equation}
+  \label{eq:258}
+  T_{\mu\nu}=g \left(\partial_{\mu}\varphi \partial_{\nu} \varphi -\frac{1}{2} \eta_{\mu\nu}\partial_{\rho}\varphi \partial^{\rho} \varphi \right)
+\end{equation}
+После квантования получаем для оператора $T(z)$ следующее выражение:
+\begin{equation}
+  \label{eq:260}
+  T(z) =-2\pi g :\partial \varphi \partial \varphi : =-2\pi g \lim_{w\to z} \left(\partial \varphi(z) \partial \varphi(w) -\langle\partial \varphi(z) \partial \varphi(w)\rangle\right)
+\end{equation}
+Теперь мы можем вычислить операторное разложение тензора энергии-импульса и локального поля $\partial \varphi$:
+\begin{equation}
+  \label{eq:261}
+  T(z)\partial \varphi(w)=-2\pi g :\partial \varphi(z) \partial \varphi(z): \partial \varphi(w) \sim -4\pi g:\partial \varphi(z)  \partial \overbracket{ \varphi(z): \partial \varphi } (w) \sim \frac{\partial \varphi (z)}{(z-w)^{2}}
+\end{equation}
+Для вычисления мы использовали теорему Вика (см. \cite{vasiliev1998}, \cite{difrancesco1997cft}). Раскладывая в ряд по $(z-w)$ получаем окончательно для сингулярной части операторного разложения
+\begin{equation}
+  \label{eq:262}
+  T(z) \partial \varphi(w) \sim \frac{\partial \varphi(w) }{(z-w)^{2}} +\frac{\partial_{w}^{2} \varphi(w)}{z-w}
+\end{equation}
+Теперь мы видим, что поле $\partial \varphi$ -- примарное, с конформной размерностью $h=1$.
+
+Аналогично вычислим операторное разложение $T$  с самим собой.
+\begin{multline}
+  \label{eq:263}
+  T(z) T(w) =4 \pi^{2}g^{2}:\partial \varphi(z) \partial \varphi(z): :\partial \varphi(w)\partial \varphi(w): \\
+  \sim \frac{1/2}{(z-w)^{4}} -\frac{4\pi g:\partial \varphi(z) \partial \varphi(w):}{(z-w)^{2}} \\
+  \sim \frac{1/2}{(z-w)^{4}}+ \frac{2T(w)}{(z-w)^{2}} +\frac{\partial T(w)}{z-w}
+\end{multline}
+
+\subsection{Центральный заряд. Алгебра Вирасоро}
+\label{sec:virasoro}
+
+В силу обсуждения после формулы \eqref{eq:247}, ренормгруппового анализа \ref{c-theorem} и вычисления функции Швингера  \eqref{eq:221} мы имеем следующий общий вид операторного разложения для $T(z)T(w)$:
+\begin{equation}
+  \label{eq:264}
+  T(z)T(w) \sim \frac{c/2}{(z-w)^{4}}+ \frac{2T(w)}{(z-w)^{2}} +\frac{\partial T(w)}{z-w}
+\end{equation}
+Здесь $c$ -- параметр теории, называемый центральным зарядом.
+Он зависит от физической природы теории и не определяется из соображений конформной инвариантности.
+В теории свободного бозона $c=1$, для фермиона $c=1/2$.
+Член $\frac{c/2}{(z-w)^{4}}$ называется аномальным.
+Если этого члена нет, то $T$--квазипримарное поле c $h=2$.
+
+Сравнивая выражение \eqref{eq:264} и \eqref{eq:221} мы видим, что константа $A$ в функции Швингера
+\begin{equation}
+  \label{eq:265}
+  A=\frac{c}{4\pi^{2}}
+\end{equation}
+Покажем, как преобразуется тензор энергии-импульса при конформных преобразованиях. Используем формулу \eqref{eq:246}:
+\begin{multline}
+  \label{eq:266}
+  \delta_{\epsilon} T(w) =-\frac{1}{2\pi i} \oint_{C} dz \epsilon(z) T(z) T(w) =-\frac{1}{12} c \partial_{w}^{3}\epsilon(w) -2 T(w) \partial_{w} \epsilon(w) -\epsilon(w) \partial_{w}T(w) 
+\end{multline}
+Соответствующее конечное преобразование $z\to w(z)$ имеет вид
+\begin{eqnarray}
+  \label{eq:267}
+  T\to T'(w) =\left(\frac{dw}{dz}\right)^{-2} \left(T(z) -\frac{c}{12} \left\{ w,z\right\}\right)\\
+  \left\{ w,z\right\}=\frac{\left(\frac{d^{3}w}{dz^{3}}\right) } {\frac{dw}{dz}} -\frac{3}{2}\left(\frac{\frac{d^{2}w}{dz^{2}}}{\frac{dw}{dz}}\right)^{2}
+\end{eqnarray}
+В качестве упражнения предлагаем проверить это выражение обратным переходом к инфинитезимальному преобразованию.
+
+Разложим $T(z)$ в ряд Лорана.
+\begin{eqnarray}
+  \label{eq:268}
+  T(z)=\sum_{n\in \mathbb{z}}z^{-n-2}L_{n}\\
+  T(z)=\sum_{n\in \mathbb{z}}\bar z^{-n-2}\bar L_{n}
+\end{eqnarray}
+При масштабном преобразовании $z\to z/\lambda$ оператор $T(z)\to \lambda^{2}T(z/\lambda)$, соответственно компоненты $L_{-n}\to \lambda^{n}L_{-n}$.
+\begin{equation}
+  \label{eq:269}
+  L_{n}=\oint \frac{dz}{2\pi i} z^{n+1} T(z)
+\end{equation}
+Выведем коммутационные соотношения для операторов $L_{n}$:
+\begin{equation}
+  \label{eq:270}
+  [L_{n},L_{m}]=\left( \oint \frac{dz}{2\pi i}\oint \frac{dw}{2\pi i}-\oint \frac{dw}{2\pi i}\oint \frac{dz}{2\pi i}\right) z^{n+1} T(z)w^{m+1}T(w)
+\end{equation}
+Используем операторное разложение \eqref{eq:264}:
+\begin{multline}
+  \label{eq:271}
+  [L_{n},L_{m}]=\oint \frac{dz}{2\pi i} \oint \frac{dw}{2\pi i} z^{n+1} w^{m+1}\left( \frac{c/2}{(z-w)^{4}} +\frac{2T(w)}{(z-w)^{2}}+\frac{\partial T(w) }{z-w} +\mbox{рег. члены}\right) =\\
+  \oint \frac{dw}{2\pi i} \left(\frac{c}{12} (n+1)n(n-1)w^{n-2}w^{m+1} + 2(n+1)w^{n}w^{m+1}T(w)+w^{n+1}w^{m+1}\partial T(w)\right)
+\end{multline}
+Интегрируем последний член по частям, внеинтегральный член зануляется, а под интегралом остается $(n-m)w^{n+m+1}T(w)$:
+\begin{equation}
+  \label{eq:272}
+    [L_{n},L_{m}]=\oint \frac{dw}{2\pi i} \left(\frac{c}{12} (n+1)n(n-1)w^{m+n-1}+ (n-m)w^{n+m+1}T(w)\right)
+\end{equation}
+Используя определение \eqref{eq:269} и вычисляя вычет подинтегрального выражения при $n=-m$, в итоге получаем коммутационное соотношение
+\begin{equation}
+  \label{eq:273}
+    [L_{n},L_{m}]=(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}
+\end{equation}
+Это коммутационные соотношения алгебры Вирасоро.
+
+Легко показать, что в результате действия оператора $L_{-n}$ на поле $\varphi$  с конформной размерностью $(h,\bar h)$ получается поле с размерностью $(h-n,\bar h)$.
+Все поля в теории разбиваются на конформные семейства, соответствующие примарным полям:
+\begin{equation}
+  \label{eq:274}
+  [\varphi]=\{L_{-n_{1}}L_{-n_{2}}\dots L_{-n_{N}}\bar L_{-m_{1}}\dots \bar L_{-m_{M}}\varphi\}
+\end{equation}
+Вычисление корреляторов вторичных полей сводится к корреляторам примарных. Алгебра локальных полей оказывается прямой суммой конформных семейств
+\begin{equation}
+  \label{eq:275}
+  \mathcal{A} =\bigoplus_{\alpha}[\varphi_{\alpha}]
+\end{equation}
+{\it Минимальными} называются теории с конечным числом примарных полей. Чтобы полностью задать такую теорию нужно определить примарные поля и их конформные размерности.
+
+\section{Лекция 12. Конформный предел модели Изинга}
+\label{sec:lecture-12}
 

### 2010-12-20 GeneralOverview/Lectures/2dqft.tex
PDF regen

@@
 
+Рассмотрим теорию с центральным зарядом $c=\frac{1}{2}$, $\bar c=c$ и примарными полями с конформными размерностями
+\begin{equation}
+  \label{eq:276}
+  \Phi_{1}: (0,0),\quad \Phi_{2}: \left(\frac{1}{2},\frac{1}{2}\right),\quad \Phi_{3}\left(\frac{1}{16},\frac{1}{16}\right)
+\end{equation}
+Первое из этих полей соответствует единичному оператору.
+
+В модели Изинга $\sigma$ -- параметр порядка. $\langle\sigma\rangle=0$ при большой температуре и $\langle \sigma\rangle\neq 0$ при малой. Как мы знаем,
+\begin{equation}
+  \label{eq:277}
+  \langle \sigma_{n} \sigma_{0}\rangle\sim e^{-\frac{|n|}{\xi}}
+\end{equation}
+Где $\xi$ --- корреляционная длина. $\xi^{-1}$ можно рассматривать как массу в теопии. В критической точке $\xi$ расходится и теория становится безмассовой.
+\begin{equation}
+  \label{eq:278}
+  \langle\sigma_{n}\sigma_{0}\rangle\sim\frac{1}{|n|^{d-2+\eta}}
+\end{equation}
+Для оператора энергии верно
+\begin{equation}
+  \label{eq:279}
+  \langle \varepsilon_{n} \varepsilon_{0}\rangle \sim \langle\sigma_{n}\sigma_{n+1}\sigma_{0}\sigma_{1}\rangle\sim\frac{1}{|n|^{\frac{2d-2}{\nu}}}
+\end{equation}
+Это выражение не совсем точное, так как при вычислении $\varepsilon_{n}$ надо брать среднее по всем соседям, но сейчас нам это не очень важно.
+В любом случае коррелятор оператора энергии соответствует цетырехточечной функции.
+
+Мы знаем (см. Лекции \ref{sec:lecture-2}, \ref{sec:lecture-5}, \ref{sec:lecture-6}) значения критических индексов в модели Изинга --- $\eta=\frac{1}{4}, \nu=1$. Тогда для двухточечной функции
+\begin{equation}
+  \label{eq:280}
+  \langle \sigma_{n} \sigma_{0} \rangle\sim \frac{1}{|n|^{\frac{1}{4}}} \sim\frac{1}{r^{2\Delta_{\sigma}}},
+\end{equation}
+так как мы помним, что двухточечная функция ведет себя как $\langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle=\frac{C_{12}}{r_{12}^{\Delta_{1}+\Delta_{2}}}$.
+Отсюда $\Delta_{\sigma}=h_{\sigma}+\bar h_{\sigma}=\frac{1}{8}$, $s_{\sigma}=h_{\sigma}-\bar h_{\sigma}=0$, то есть поле $\Phi_{3}$ соответствует спину в модели Изинга.
+
+Для оператора энергии мы видим, что
+\begin{equation}
+  \label{eq:281}
+  \langle\varepsilon_{n}\varepsilon_{0}\rangle\sim \frac{1}{|n|^{2\Delta_{\varepsilon}}},
+\end{equation}
+$\nu=1$, $d-1/\nu=1=\Delta_{\varepsilon}=h_{\varepsilon}+\bar h_{\varepsilon}$, то есть $h_{\varepsilon}=\frac{1}{2}$ и поле $\Phi_{2}$ соответствует оператору энергии в модели Изинга.
+
+Заметим, что другая простая физическая система с центральным зарядом $(c,\bar c)=\left(\frac{1}{2},\frac{1}{2}\right)$ --- это свободный фермион. Его действие
+\begin{equation}
+  \label{eq:282}
+  S=\frac{1}{2} g \int d^{2}x\Psi^{+}\gamma^{0}\gamma^{\mu}\partial_{\mu}\Psi,
+\end{equation}
+где
+\begin{equation}
+  \label{eq:283}
+  \Psi=
+  \begin{pmatrix}
+    \psi\\ \bar \psi
+  \end{pmatrix}
+\end{equation}
+и для гамма-матриц выполняется
+\begin{equation}
+  \label{eq:284}
+  \gamma^{\mu}\gamma^{n}+\gamma^{\nu}\gamma^{\mu}=2\eta^{\mu\nu},\quad \gamma^{0}=
+  \begin{pmatrix}
+    0 & 1\\
+    1 & 0
+  \end{pmatrix}, \quad
+  \gamma^{1}=
+  \begin{pmatrix}
+    0 & -i\\
+    i & 0
+  \end{pmatrix}
+\end{equation}
+Вводим комплексные координаты \eqref{eq:225} и получаем
+\begin{equation}
+  \label{eq:285}
+  \gamma^{0}(\gamma^{0}\partial_{0}+\gamma^{1}\partial_{1})=2
+  \begin{pmatrix}
+    \bar \partial & 0\\
+    0 & \partial
+  \end{pmatrix}
+\end{equation}
+Тогда действие в компонентах \eqref{eq:283} будет
+\begin{equation}
+  \label{eq:286}
+  S=g\int d^{2}x (\bar \psi \partial \bar \psi + \psi\bar \partial \psi)
+\end{equation}
+Классические уравнения движения
+\begin{eqnarray}
+  \label{eq:287}
+  \partial \bar \psi=0\\
+  \bar \partial \psi=0, 
+\end{eqnarray}
+следовательно $\psi=\psi(x)$ и $\bar \psi=\bar \psi(\bar z)$. 
 \bibliography{2dqft}{}

### 2010-12-21 GeneralOverview/Lectures/2dqft.tex
Lecture 12 is completed

@@
 следовательно $\psi=\psi(x)$ и $\bar \psi=\bar \psi(\bar z)$.
+
+Мы хотим вычислить двухточечные корреляционные функции (пропагаторы).
+Они имеют вид $\langle \psi_i(x)\psi_j(x)\rangle, i,j=1,2$ (в координатах $x_1,x_2$).
+Для этого перепишем действие в матричном виде
+\begin{equation}
+  \label{eq:288}
+  S=\frac{1}{2}\int d^2x d^2 y \psi_i (x) A_{ij}(x,y) \psi_j(y),
+\end{equation}
+где мы ввели ядро
+\begin{equation}
+  \label{eq:289}
+  A_{ij}(x,y)=g \delta(x-y) (\gamma^0 \gamma^{\mu})_{ij} \partial_{\mu}.
+\end{equation}
+ Корреляторы можно собрать в матрицу $K_{ij}(x,y)=\langle \psi_i(x)\psi_j(y)\rangle$. Если вычислить гауссов функциональный интеграл, то получается, что
+ \begin{equation}
+   \label{eq:290}
+   K_{ij}(x,y)=\left(A^{-1}\right)_{ij}(x,y).
+ \end{equation}
+То есть $K$ удовлетворяет следующему уравнению:
+\begin{equation}
+  \label{eq:291}
+  g \delta (x-y) (\gamma^0 \gamma^{\mu})_{ik} \frac{\partial}{\partial x^{\mu}} K_{kj}(x,y)=\delta(x-y)\delta_{ij}
+\end{equation}
+В наших комплексных координатах это уравнение имеет очень простой вид
+\begin{equation}
+  \label{eq:292}
+  2g
+  \begin{pmatrix}
+    \bar \partial & 0\\
+    0 & \partial
+  \end{pmatrix}
+  \begin{pmatrix}
+    \langle \psi(z,\bar z) \psi(w,\bar w) \rangle & \langle\psi(z,\bar z)\bar \psi(w,\bar w) \rangle \\
+    \langle \bar \psi(z,\bar z) \psi(w,\bar w) \rangle & \langle\bar\psi(z,\bar z)\bar \psi(w,\bar w) \rangle \\    
+  \end{pmatrix}=
+  \frac{1}{\pi}
+  \begin{pmatrix}
+    \bar \partial\frac{1}{z-w} & 0\\
+    0 & \partial \frac{1}{\bar z-\bar w}
+  \end{pmatrix}
+\end{equation}
+Решением этого уравнения будут
+\begin{eqnarray}
+  \label{eq:293}
+  \langle \psi(z,\bar z) \psi(w,\bar w) \rangle=\frac{1}{2\pi g} \frac{1}{z-w}\\
+  \langle\bar\psi(z,\bar z) \bar \psi(w,\bar w) \rangle =\frac{1}{2\pi g} \frac{1}{\bar z-\bar w}\\
+  \langle\psi(z,\bar z) \bar \psi(w,\bar w) \rangle =0
+\end{eqnarray}
+Если их продифференцировать, получаем
+\begin{eqnarray}
+  \label{eq:294}
+  \langle \partial_z \psi(z,\bar z) \psi(w,\bar w) \rangle=-\frac{1}{2\pi g} \frac{1}{(z-w)^2}\\
+  \langle \partial_z \psi(z,\bar z) \partial_w \psi(w,\bar w) \rangle=-\frac{1}{\pi g} \frac{1}{(z-w)^3}
+\end{eqnarray}
+То есть имеет место операторное разложение
+\begin{equation}
+  \label{eq:295}
+  \psi(z)\psi(w)\sim \frac{1}{2\pi g} \frac{1}{z-w}
+\end{equation}
+Для компонент тензора энергии-импульса имеем
+\begin{eqnarray}
+  \label{eq:296}
+  T^{\bar z\bar z} =2g\psi\partial \psi\\
+  T^{ z z} =2g\bar \psi\bar\partial \bar \psi\\
+  T^{ z\bar z} =-2g\psi\bar\partial \psi\neq 0
+\end{eqnarray}
+Однако $T^{z\bar z}$ исчезает на классических траекториях, то есть теория является конформной.
+Вводим привычное обозначение и квантуем:
+\begin{equation}
+  \label{eq:297}
+  T(z)=-2\pi T_{zz}=-\pi g :\psi(z) \partial \psi(z):=-\pi g\lim_{w\to z}(\psi(z)\partial \psi(w) -\langle\psi(z) \partial \psi(w)\rangle)
+\end{equation}
+Используем теорему Вика и вычисляем операторное разложение
+\begin{equation}
+  \label{eq:298}
+  T(z) \psi(w)=-\pi g:\psi(z)\partial \psi(z) :\psi(w) \sim \frac{1}{2}\frac{\partial \psi(z)}{z-w} +\frac{1}{2}\frac{\psi(z)}{(z-w)^2} \sim \frac{\frac{1}{2} \psi(w)}{(z-w)^2} +\frac{\partial \psi(w)}{z-w}
+\end{equation}
+Мы видим, что у фермионного поля $\psi$ конформная размерность $h=\frac{1}{2}$.
+
+Теперь аналогично вычисляем операторное разложение $T$ с собой:
+\begin{equation}
+  \label{eq:299}
+  T(z)T(w)=\pi^2 g^2 :\psi(z)\partial \psi(z)::\psi(w)\partial \psi(w): \sim \frac{\frac{1}{4}}{(z-w)^4} +\frac{2T(w)}{(z-w)^2} +\frac{\partial T(w)}{z-w}
+\end{equation}
+Мы видим, что центральный заряд в теории свободного фермиона $c=\frac{1}{2}$.
+
+Ненулевые операторные разложения между членами конформных семейств определяются разложениями примарных полей. Поэтому можно писать сразу для семейств
+\begin{equation}
+  \label{eq:300}
+  [\varphi_i][\varphi_j]=\sum_k C_{ijk} [\varphi_k]
+\end{equation}
+В модели Изинга у нас есть три семейства $[1], [\sigma], [\varepsilon]$. Из наличия симметрий ($\sigma\to - \sigma$ и $\varepsilon\to -\varepsilon$ (дуальность Крамерса-Ванье)) имеем:
+\begin{eqnarray}
+  \label{eq:301}
+  \left[\sigma\right]\left[\sigma\right]=1+\left[\varepsilon\right]\\
+  \left[\sigma\right]\left[\varepsilon\right]=\left[\sigma\right]\\
+  \left[\varepsilon\right]\left[\varepsilon\right]=1
+\end{eqnarray}
+Отсюда можно вычислять все корреляционные функции. Например, для четырехточечной функции получается:
+\begin{equation}
+  \label{eq:302}
+  G^{(4)} =\langle \sigma(z_1,\bar z_1)\dots \sigma(z_4,\bar z_4)\rangle = \frac{1}{2} \left|\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right|^{\frac{1}{4}}\left(\left|1+\sqrt{1-x}\right| + \left|1-\sqrt{1-x}\right|\right)
+\end{equation}
+
 \bibliography{2dqft}{}

### 2010-12-21 GeneralOverview/Lectures/2dqft.tex
Some literature added

@@
 
-Изложение конформной теории поля в двух измерениях опирается на оригинальную статью \cite{belavin1984ics}, книгу \cite{difrancesco1997cft} и обзор \cite{zamolodchikov1989rus,zamolodchikov1989conformal}, недавно переизданный в виде книги.
+Изложение конформной теории поля в двух измерениях опирается на оригинальную статью \cite{belavin1984ics}, книгу \cite{difrancesco1997cft}, обзор \cite{zamolodchikov1989rus,zamolodchikov1989conformal}, недавно переизданный в виде книги.
+В последних лекциях \ref{sec:lecture-10}, \ref{sec:lecture-11}, \ref{sec:lecture-12} использовались также материалы из обзора \cite{Ginsparg:1988ui}, хотя логика изложения ближе к книге \cite{difrancesco1997cft}.
+Некоторые алгебраические сведения о представлениях алгебры Вирасоро  могут быть найдены в книге \cite{golod2001}.
 

### 2010-12-22 AffineLieAlgebras/InformalNotes/article.tex
V.D. changes merged

--- 2010-11-26 AffineLieAlgebras/InformalNotes/article.tex
@@
   the Weyl denominator becomes singular with respect to the subalgebra.
-  We demonstrate
+  We study the modifications of the fan technique and demonstrate
   that for any reductive subalgebra it is possible to define the
-  injection fan and the analogue of the Weyl numerator -- the tools that describe
+  injection fan -- the tool that describes
   explicitly the recurrent properties of branching coefficients.
-  Possible applications of the fan technique in CFT models are considered.
+  Possible applications of fan technique in CFT models are considered.
 \end{abstract}
@@
 in the construction of modular-invariant partition functions \cite{difrancesco1997cft}.
-Recently the problem of conformal embeddings was considered in the paper \cite{coquereaux2008conformal}.
-
-There are different approaches to deal with the branching coefficients. Some of them use the BGG
+Recently the problem of conformal embeddings was considered in \cite{coquereaux2008conformal}.
+
+There are different approaches to deal with branching coefficients. Some of them use the BGG
 resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
 \cite{kac1990idl},\cite{wakimoto2001idl}), the Schur function series \cite{fauser2006new}, the BRST
-cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
+cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or some
 combinatorial methods applied in \cite{feigin707principal}.
@@
 In this paper we prove that
-for an arbitrary reductive subalgebra the branching coefficients are subject to
-the recurrent properties that can be explicitly formulated and that there exists
+for an arbitrary reductive subalgebra branching coefficients are subject to
+a set of recurrent properties that can be explicitly formulated and that there exists
 an effective and simple algorithm to solve these recurrent relations step by step.
@@
 the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
-This decomposition provides the possibility to construct the recurrent property for branching coefficients corresponding
+This decomposition provides the possibility to construct a recurrent property for branching coefficients corresponding
 to the injection $\frak{a} \rightarrow \frak{g} $.
 The property is formulated in
-terms of a specific element $\Gamma_{\af \rightarrow \gf}$ of the group algebra
+terms of the specific element $\Gamma_{\af \rightarrow \gf}$ of the group algebra
 $\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
@@
 explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
-subalgebras of finite-dimensional or affine Lie algebras.
+subalgebra of finite-dimensional or affine Lie algebra.
 In the case of maximal embedding the corresponding fan is unsubtracted, the singular element
@@
 $L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
-(subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several
-simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in
+(subsection \ref{sec:algorithm}). In Section \ref{sec:finite-dimens-lie} we present several
+simple examples for finite-dimensional Lie algebras. Affine Lie algebras and their applications in
 CFT models are considered in Section \ref{sec:phys-appl}.
-The general properties of the proposed algorithm and
-possible further developments are discussed (Section \ref{sec:conclusion}).
+General properties of the proposed algorithm and
+possible further developments are also discussed (Section \ref{sec:conclusion}).
 
@@
 
-Consider affine Lie algebras $\frak{g}$ and $\af$ with the
+Consider affine Lie algebras $\frak{g}$ and $\af$ with
 underlying finite-dimensional subalgebras $\go$ and $%
@@
 
-$\lambda =\left( \co{\lambda };k;n\right) $ --- the
-decomposition of an affine weight indicating the finite part $\co{\lambda }$, level $k$ and grade $n$;
+$\lambda =\left( \co{\lambda };k;n\right) $ ---
+decomposition of the affine weight $\lambda$ indicating the finite
+part $\co{\lambda }$, the level $k$ and the grade $n$;
 
@@
 
-Consider the integrable module $L^{\mu }$
+Consider an integrable module $L^{\mu }$
 of $\frak{g}$ with the highest weight $\mu $ and
@@
 
-For the Cartan subalgebras we have the decomposition
+For the Cartan subalgebra we have the decomposition
 \begin{equation}
@@
 \widetilde{\af_{\perp }}}}$ and let $U$ be the set of representatives $%
-u $ for the classes $W/W_{\af_{\perp }}$ such that
+u $ for classes $W/W_{\af_{\perp }}$ such that
 
@@
 properties of branching coefficients. It must be noticed that the injection fan is
-the universal instrument that depends only on the injection and doesn't depend on 
-the properties of a module.
+the universal instrument that depends only on the injection.
 
@@
 can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
-the singular weights $e^{\mu _{\af}\left( u\right) }$ with the
+singular weights $e^{\mu _{\af}\left( u\right) }$ with the
 coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
@@
 \begin{proof}
-With $u\in U $   and $v\in W_{\afb}$ perform the decomposition
-\begin{equation*}
-u(\mu +\rho )=\pi _{\left( \af\right) } u(\mu +\rho )+\pi _{\left(
-\widetilde{\af_{\perp }}\right) } u(\mu +\rho )
-\end{equation*}
-for the singular weight $vu(\mu +\rho )-\rho$:
+With $u\in U $   and $v\in W_{\afb}$ apply the decomposition
+\begin{equation*}
+u(\mu +\rho )=\pi _{\af } u(\mu +\rho )+\pi _{
+\widetilde{\af_{\perp }} } u(\mu +\rho )
+\end{equation*}
+to the singular weight
 \begin{equation}
@@
 \begin{array}{lcl}
-vu(\mu +\rho )-\rho &=&\pi _{\left( \af\right) }\left( u(\mu +\rho
-)\right) -\rho +\rho _{\af_{\perp }}+\pi _{\left( \hfb\right) }\rho \\
-&& + \ v\left( \pi _{\left( \widetilde{%
-\af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
-\af_{\perp }}\right) -\rho _{\af_{\perp }} -\pi _{\left( \hfb\right) }\rho.
+vu(\mu +\rho )-\rho &=&\pi _{ \af }\left( u(\mu +\rho
+)\right) -\rho +\rho _{\af_{\perp }}+\pi _{ \hfb }\rho \\
+&& + \ v\left( \pi _{ \widetilde{%
+\af_{\perp }} }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
+\af_{\perp }}\right) -\rho _{\af_{\perp }} -\pi _{ \hfb }\rho.
 \end{array}
@@
 \begin{array}{r}
-\pi _{\left( \af\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
-\mathfrak{a}_{\perp }}+\pi _{\left( \hfb\right) }\rho = \\
-\pi _{\left( \af\right) }\left( u(\mu +\rho )\right) -\pi _{\af}\rho
+\pi _{ \af }\left( u(\mu +\rho )\right) -\rho +\rho _{%
+\mathfrak{a}_{\perp }}+\pi _{ \hfb }\rho = \\
+\pi _{ \af }\left( u(\mu +\rho )\right) -\pi _{\af}\rho
 -\pi _{\afb}\rho +\rho _{\afb}= \\
-=\pi _{\left( \af\right) }\left( u(\mu +\rho )-\rho \right) +%
+=\pi _{ \af }\left( u(\mu +\rho )-\rho \right) +%
 \mathcal{D}_{\afb},
@@
 \begin{array}{c}
-v\left( \pi _{\left( \widetilde{%
-\af_{\perp }}\right) }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
-\af_{\perp }}\right) -\rho _{\af_{\perp }}-\pi _{\left( \hfb\right) }\rho=\\
-v\left( \pi _{\left( \widetilde{%
-\afb}\right) }u(\mu +\rho )
-- \mathcal{D}_{\afb} - \pi _{\left( \afb\right) }\rho-\pi _{\left( \hfb\right) }\rho
+v\left( \pi _{ \widetilde{%
+\af_{\perp }} }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
+\af_{\perp }}\right) -\rho _{\af_{\perp }}-\pi _{ \hfb }\rho=\\
+v\left( \pi _{ \widetilde{%
+\afb} }u(\mu +\rho )
+- \mathcal{D}_{\afb} - \pi _{ \afb }\rho-\pi _{ \hfb }\rho
 +\rho _{\afb}\right) -\rho _{\afb}=\\
-=v\left( \pi _{\left( \widetilde{%
-\afb}\right) }\left[ u(\mu +\rho )-\rho\right]
+=v\left( \pi _{ \widetilde{%
+\afb} }\left[ u(\mu +\rho )-\rho\right]
 - \mathcal{D}_{\afb}
@@
 +\mathcal{D}_{\af_{\perp }}}\sum_{v\in W_{\af_{\perp }}}\epsilon
-(v)e^{v\left( \pi _{\left( \widetilde{\af_{\perp }}\right) }\left[
+(v)e^{v\left( \pi _{ \widetilde{\af_{\perp }} }\left[
 u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}+\rho _{\af%
 _{\perp }}\right) -\rho _{\af_{\perp }}}= \\
-=\sum_{u\in U}\;\epsilon (u)e^{\pi _{\left( \af\right) }\left[ u(\mu
+=\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af }\left[ u(\mu
 +\rho )-\rho \right] +\mathcal{D}_{\af_{\perp }}}\Psi _{\widetilde{%
-\af_{\perp }}}^{\pi _{\left( \widetilde{\af_{\perp }}\right) }%
+\af_{\perp }}}^{\pi _{ \widetilde{\af_{\perp }} }%
 \left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}}
@@
 }}\left[ u(\mu +\rho )-\rho \right] }\pi _{%
-\af}\left( \frac{\Psi _{\widetilde{\af_{\perp }}}^{\pi _{\left(
-\widetilde{\af_{\perp }}\right) }\left[ u(\mu +\rho )-\rho \right] -%
+\af}\left( \frac{\Psi _{\widetilde{\af_{\perp }}}^{\pi _{
+\widetilde{\af_{\perp }} }\left[ u(\mu +\rho )-\rho \right] -%
 \mathcal{D}_{\af_{\perp }}}}{\prod_{\beta \in \Delta _{\af_{\perp
@@
 \begin{proof}
-Redress the relation (\ref{eq:4}) for the element $
+Redress relation (\ref{eq:4}) for the element $
 \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using definition (\ref{eq:37})
@@
 \end{equation*}
-Substitute in the left-hand side the expression obtained in Lemma \ref{lemma},
+Substitute the expression obtained in Lemma \ref{lemma} (in the left-hand side),
 \begin{eqnarray*}
@@
 for $\gamma \in \Phi _{\af\subset \frak{g}}$ are not independent, they
-are subject to the linear relations and the form of these relations changes
+are subject to linear relations and the form of these relations changes
 when the tested weight $\xi $ coincides with one of \ the ''singular
@@
 U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
-}\subset \frak{g}}$ and pass to the summation over the vectors of the
-injection fan $\Gamma _{\af\rightarrow \frak{g}}$ (see the definition \ref
+}\subset \frak{g}}$ and pass to a summation over the vectors of the
+injection fan $\Gamma _{\af\rightarrow \frak{g}}$ (see definition \ref
 {fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
@@
 
-When both $\frak{g}$ and $\af$ are finite-dimensional all the regular
+When both $\frak{g}$ and $\af$ are finite-dimensional all regular
 embeddings can be obtained by a successive elimination of nodes in the
-extended Dynkin diagram of $\frak{g}$ (and $\Delta _{\bot }^{+}=\emptyset $
+extended Dynkin diagram of $\frak{g}$ (and $\Delta_{\afb }^{+}=\emptyset $
 if $\af$ is maximal). For the classical series $A$, $C$ and $D$ when
@@
 }}\rightarrow B_{r}$ is $\left( B_{r_{\af}},B_{r-r_{\af}}\right) $%
-. In the next Section the particular case of such orthogonal pair is
+. In the next Section a particular case of such orthogonal pair is
 presented for the injection $B_{2}\rightarrow B_{4}$ (see Figure \ref
@@
 
-\item  Select the positive roots $\alpha \in \Delta ^{+}$ orthogonal
-to  $\af$, i.e. form the set $\Delta _{\afb }^{+}$.
-
-\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. The relation
+\item  Select all positive roots $\alpha \in \Delta ^{+}$ orthogonal
+to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
+
+\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. Relation
  (\ref{eq:6}) defines the sign function
@@
 )-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
-\af_{\perp }}}}\right\} $. Since the set $\Delta _{\bot }^{+}$ is fixed
+\af_{\perp }}}}\right\} $. Since the set $\Delta_{\afb }^{+}$ is fixed
 we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
@@
 \item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
-calculate the dimensions of the corresponding modules $\mathrm{\dim }\left(
+calculate dimensions of the corresponding modules, $\mathrm{\dim }\left(
 L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
-}\left( u\right) }\right) $ using the Weyl dimension formula and construct
+}\left( u\right) }\right) $, using the Weyl dimension formula and construct
 the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
@@
 
-Consider the regular embedding $A_1\to B_2$.
-Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors in the Figure \ref{fig:B2_A1}.
-We denote the corresponding Weyl reflections by $w_1, w_2$.
-The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
+Consider the regular embedding $A_1\to B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$
+are presented as dashed vectors in Figure \ref{fig:B2_A1}. We denote the corresponding
+Weyl reflections by $w_1, w_2$. The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is
+grey.
 
@@
   }
-  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
-    The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is shown by the black vector.
-    The weights of the singular element $\Psi^{(\omega_1)}$ are marked by circles with superscripts indicating
-    the corresponding determinants $\epsilon(w)$.}
+  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$
+  are presented as dashed vectors.
+  The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is grey.
+  The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is black.
+  The weights of the singular element $\Psi^{(\omega_1)}$ are marked by circles with
+  superscripts indicating the corresponding determinants $\epsilon(w)$.}
   \label{fig:B2_A1}
@@
 Let's perform the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$
-($\omega_1$ -- the black vector in Figure \ref{fig:B2_A1}). The root $\alpha_1$ is orthogonal to $\beta$,
-so we have $\Delta_{\perp}^+ = \left\{ \alpha_1 \right\}$.
-According to the definition (\ref{fan-definition})
-the fan $\Gamma_{A_1\to B_2}$ consists of two weights:
+($\omega_1$ -- the black vector in Figure \ref{fig:B2_A1}) according to the steps of the algorithm.
+The root $\alpha_1$ is orthogonal to $\beta$,
+so we have $\Delta_{\afb}^+ = \left\{ \alpha_1 \right\}$ (step (ii)).
+According to (\ref{fan-definition})
+the fan $\Gamma_{A_1\to B_2}$ (step (iii)) consists of two weights:
 \begin{equation*}
@@
 where the second component is the value of the sign function $s(\gamma)$.
-The singular weights  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$
+Singular weights  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$ (step (iv))
 are indicated by circles with the superscript $\epsilon\left( w \right)$.
 The space $U$ is the factor $W/W_{\afb}$ where $W_{\afb}=\left\{e,w_1\right\}$.
-This means that the singular weights located above the line generated by $\beta$
+This means that singular weights located above the $\beta$-line
 belong to the Weyl chamber $\overline{C_{\widetilde{\af_{\perp }}}}$.
-According to formula (\ref{defect-perp}) in our case we have $\mathcal{D}_{\af_{\perp }}=0$ and
+According to formula (\ref{defect-perp}) we have $\mathcal{D}_{\af_{\perp }}=0$ and
 $\hf_{\perp }=0$, thus $\left\{ \mu _{\af_{\perp }}\left( w\right)
@@
  are
-$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$. To
-visualize the procedure we indicate explicitly in Figure (\ref{fig:B2_A1_2}) how the
-corresponding weight diagrams
+$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$ (step v).
+In Figure (\ref{fig:B2_A1_2}) the corresponding weight diagrams
 $\left\{ \mathcal{N}_{\af_{\perp }}^{\mu _{\af_{\perp }}\left( u\right) }\right\} $
@@
 In fact we do not need the
-weight diagrams but only the dimensions of the corresponding modules
+weight diagrams but only the dimensions of modules
 $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ multiplied by
-$\epsilon \left( u\right) $. The obtained values are to be attributed to the points
+$\epsilon \left( u\right) $ (step vi). Obtained values are to be attributed to the points
 $\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$
-in $P_{\af}$. The corresponding element of ${\cal E}_{\af}$ is
-the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
-with the set of weights having anomalous multiplicities:
+in $P_{\af}$. The singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
+has the set of weights with anomalous multiplicities:
 \begin{equation}
@@
 Applying formula (\ref{recurrent-relation}) with the fan
-$\Gamma_{A_1\to B_2}$ to the set (\ref{eq:25})
+$\Gamma_{A_1\to B_2}$ to the set (\ref{eq:25}) (step vii)
 we get zeros for the weights
@@
   \centering
-  \includegraphics[width=50mm]{figure3.eps}
+  \includegraphics[width=100mm]{figure3.eps}
   \caption{The regular embedding $B_2 \rightarrow B_4$ described by dropping the node from the Dynkin diagram.
@@
   We see the projected singular weights $\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] +\gamma_0 | u \in U \right\}$
-  shifted by $\gamma_0$ and supplied by the multipliers
+  shifted by $\gamma_0$ and supplied by multipliers
   $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.}
@@
   \includegraphics[height=80mm]{figure5.eps}
-  \caption{The fan $\Gamma$ for $B_2\rightarrow B_4$ and the values of $s(\gamma+\gamma_0)$ for the weights $\gamma$.}
+  \caption{The fan $\Gamma$ for $B_2\rightarrow B_4$ with values of $s(\gamma+\gamma_0)$ attributed to each $\gamma \in \Gamma$.}
   \label{fig:B4B2Fan}
@@
   \label{eq:26}
- S_{B_2}=\{e_3-e_4,e_4\}
+ S_{B_2}=\{e_3-e_4,e_4\}.
 \end{equation*}
@@
 \end{eqnarray*}
-As far as the set $\Delta^+_{B_4} \setminus  \Delta^{+}_{\afb}$ is fixed the injection
-fan $\Gamma_{B_2 \to B_4}$ can be constructed using Definition \ref{fan-defininition}.
-As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need just the factor
+As far as the set $\Delta^+_{B_4} \setminus \left(\Delta^{+}_{\af} \cup \Delta^{+}_{\afb}\right)$ is fixed the injection
+fan $\Gamma_{B_2 \to B_4}$ can be constructed (using formulas (\ref{eq:6} -- \ref{fan-defined})).
+As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need only the factor
  $s\left(\gamma + \gamma_0\right)$.
@@
 $\mathrm{dim}(L^{\left[0,1,0,2\right]})=2772$.
-The set of singular weights for $B_4$ contains 384 vectors.
 Here the defect is nontrivial, $\mathcal{D}_{\af_{\perp }}=-2\left( e_1 + e_2 \right)$,
-while $\hf_{\bot}=0$.
-Taking this into account we find among the singular weights
+while $\hf_{\bot}=0$. Among the singular weights there are
 48 vectors with the property $\left\{ \mu _{\af_{\perp }%
 }\left( u\right) =\pi _{\af_{\perp }}\left[ u(\mu +\rho
-)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\af_{\perp }}}\right\} $,
-scalar products of these weights with all the roots in $\Delta^{+}_{\afb}$ are nonnegative.
+)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\af_{\perp }}}\right\} $.
 The set $U=\left\{ u \right\}$ is thus fixed.
@@
 
-Now one can place the fan $\Gamma$ from Figure \ref{fig:B4B2Fan} in the highest of the weights
+Now one can place the fan $\Gamma$ (see Figure \ref{fig:B4B2Fan}) in the highest of the weights
 presented in Figure \ref{fig:B4B2anom} and start the recursive determination of the branching coefficients
@@
 %\newpage
-\section{Applications to the conformal field theory}
+\section{Applications to conformal field theory}
 \label{sec:phys-appl}
@@
 \end{equation}
-Here the sum is over the set of the highest weights of integrable modules in a WZW-model
+Here the sum is over the set of highest weights for integrable modules in a WZW-model
 and $\chi_{\mu}(\tau)$ are the normalized characters (see \cite{difrancesco1997cft}) of these modules.
 
-To construct the nondiagonal modular invariants is not an easy problem,
+To construct nondiagonal modular invariants is not an easy problem,
 although for some models the complete classification of modular invariants is known \cite{1994hepthGannon,1995JMPGannon}.
@@
 \end{equation*}
-The modes $L_n$ are constructed as combinations of normally-ordered products of the generators of $\mathfrak{g}$,
+The modes $L_n$ are constructed as combinations of normally-ordered products of $\gf$-algebra generators,
 \begin{equation*}
@@
 
-Substituting generators of $\af$  in terms of generators of $\mathfrak{g}$ into these combinations
-we must obtain the energy-momentum tensor $T_{\mathfrak{g}}$.
+In these combinations we are to substitute  $\af$-generators in terms of $\mathfrak{g}$-generators
+and obtain the energy-momentum tensor $T_{\mathfrak{g}}$.
 But if the set of generators attributed to $\Delta_{\afb}$ is not empty this is not possible,
@@
 special injection $A_1 \rightarrow A_2$ with the embedding index $x_e=4$.
-As far as the $\gf$-modules to be considered are of level one,
-the $\af$-modules will be of level $\tilde{k}=kx_e=4$.
+As far as $\gf$-modules to be considered are of level one,
+the necessary $\af$-modules will be of level $\tilde{k}=kx_e=4$.
 
@@
 It is easy to see that the set $\Delta_{ \afb }$ is empty and the subalgebra $\afb=0$.
-Then ${\cal D}_{\afb}=0$, $\hf_{\perp}$ is one-dimensional Abelian subalgebra and the dimensions of $\tilde\afb=\afb\oplus \hf_{\perp}$ are equal to 1.
+Then ${\cal D}_{\afb}=0$, $\hf_{\perp}$ is one-dimensional abelian subalgebra and
+the dimension of $\tilde\afb=\afb\oplus \hf_{\perp}$ is also 1.
 It is convenient to choose the classical root for $\hat{A}_1$ to be
@@
 
-Using Definition (\ref{fan-definition})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$.
-In this case $\gamma_0 =0$ and its sign $s\left( 0 \right)=-1$ thus we are to use the
+Using the defining relation (\ref{fan-defined}) we construct the
+fan $\Gamma_{\hat A_1\to\hat A_2}$.
+In this case $\gamma_0 =0$ its sign is minus, $s\left( 0 \right)=-1$, thus we are to use the
 sign function $s(\gamma)$ (see Figure \ref{fig:AffineA2A1Fan}).
@@
   \includegraphics[width=180mm]{figure7.eps}
-  \caption{The singular weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$.
+  \caption{Singular weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$.
    The classical (grade zero) cross-section of the diagram is shown separately
@@
 \end{equation*}
-The finite reducibility theorem holds.
+Notice that the finite reducibility theorem holds.
 
 The same fan $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ can be used for any other highest weight
-module $L^{\mu}_{\hat{A_2}}$. In particular for the irreducible modules of level one  we get the trivial
+module $L^{\mu}_{\hat{A_2}}$. In particular for irreducible modules of level one  we get the trivial
 branching:
@@
 
-Let us return to the example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
+Let us return to our example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
 $A_1 \rightarrow B_2$.
@@
 The set  of positive roots with zero projection
-on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case
-$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$ and $\afb=A_1$. It is easy to see that $\hf_{\perp}$
-is trivial in this case and also ${\cal D}_{\afb}=0$.
-
-Using the definition (\ref{fan-defined}) we obtain the fan
+on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case:
+$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$ and $\afb=A_1$. It is easy to see that here $\hf_{\perp}$
+is trivial and ${\cal D}_{\afb}=0$.
+
+Using (\ref{fan-defined}) we obtain the fan
 $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
 Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=-1$.
-The values of the sign function $s(\gamma)$ for
+Values of the sign function $s(\gamma)$ for
 $ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ are presented in Figure \ref{fig:AffineB2A1Fan}.
@@
 where the finite part coordinates are in the orthogonal basis $e_1,e_2$.
-The set of anomalous weights for this module up to the sixth grade is presented in the Figure \ref{fig:affine_B2_anom_point}.
+The set of anomalous weights for this module up to the sixth grade is presented in Figure \ref{fig:affine_B2_anom_point}.
 
@@
 
-According to the algorithm \ref{sec:algorithm} we project the anomalous weights to
+According to the recursive algorithm \ref{sec:algorithm} we project these anomalous weights to
 $P_{\hat{A_1}}$ and find the dimensions of the corresponding
@@
 the classical Lie algebra $A_1\rightarrow B_2$. To see this compare Figure \ref{fig:B2_A1}
-with the Figure \ref{fig:AffineB2_A1_anom_proj}
+with Figure \ref{fig:AffineB2_A1_anom_proj}
 where the singular element $\Psi ^{\left( \mu \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
@@
   \includegraphics[width=120mm]{figure12.eps}
-  \caption{The singular element $\Psi ^{\left( \omega_1 \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
-  in the basis $\{\beta,\delta\}$. The dimensions of the corresponding $\afb=A_1$-modules
+  \caption{Singular element $\Psi ^{\left( \omega_1 \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
+  in the basis $\{\beta,\delta\}$. Dimensions of the corresponding $\afb=A_1$-modules
   with the signs $\epsilon(u)$ are indicated.}
@@
   \caption{Anomalous branching coefficients for $\hat{A_1}\rightarrow \hat{B_2}$. The basis $\{\beta,\delta\}$ is used.
-  The boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
- are indicated by the black lines. The anomalous branching coefficients
- inside the main Weyl chamber are equal to the branching coefficients of the embedding $\hat{A_1}\rightarrow \hat{B_2}$.}
+ Boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
+ are indicated by black lines. Anomalous branching coefficients
+ inside the main Weyl chamber are equal to branching coefficients of the embedding $\hat{A_1}\rightarrow \hat{B_2}$.}
   \label{fig:AffineB2_A1_branching}
@@
 
-The multiplicities of the highest weights inside the  Weyl chamber
+Multiplicities of the highest weights inside the  Weyl chamber
 $\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
@@
 
-Now we can use the relation (\ref{eq:31}),
+Now we can return to (\ref{eq:31}),
 \begin{equation*}
@@
 \end{equation*}
-and thus obtain the expansion of the $B_2/A_1$-coset characters.
+and finally obtain expansions for the $B_2/A_1$-coset characters.
 
@@
 \label{sec:conclusion}
-We have demonstrated that the injection fan technique can be used to deal with an arbitrary
-reductive subalgebra (maximal as well as  nonmaximal).
+We have demonstrated that the injection fan technique can be used to deal with arbitrary
+reductive subalgebras (maximal as well as  nonmaximal).
 It was shown that the branching problem for $\af \subset \gf$  is tightly connected with
@@
 Both the injection fan and the sets of singular weights for
-the highest weight $\gf$-modules depend substantially on the structure of $\afb$ and its submodules.
+highest weight $\gf$-modules depend substantially on the structure of $\afb$ and its submodules.
 For the fan $\Gamma_{\af\rightarrow \gf}$ this dependence is almost obvious:
@@
 We have found out that in the new singular element
-$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ the coefficients depend on the
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ the coefficients depend on
 the $\afb$-submodules (their highest weights $\mu _{\widetilde{\af_{\perp }}}\left( u\right)$
@@
 Fortunately no more information on $L^{\mu _{\widetilde{\af_{\perp }}}\left( u\right)}
-_{\afb}$-submodules is necessary than their dimensions.
+_{\left\{ \afb \right\}}$-submodules is necessary than their dimensions.
 In the new singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
-the weight multiplicities are equal to the dimensions
-$\dim\left(L^{\mu _{\widetilde{\af_{\perp }}}\left( u\right)}_{ \afb }\right)$
+weight multiplicities are equal to dimensions
+$\dim\left(L^{\mu _{\widetilde{\af_{\perp }}}\left( u\right)}_{\left\{ \afb \right\}}\right)$
 of the corresponding $\afb$-modules
@@
 In particular we considered the construction of modular-invariant partition functions
-in the framework of conformal embedding method and the coset construction in the rational conformal field theory.
+in the framework of conformal embedding method and the coset construction in rational conformal field theory.
 This construction is useful in the study of WZW-models

### 2010-12-25 AffineLieAlgebras/InformalNotes/article.tex
Spelling
Figure 3 fixed, PDF regenerated.
List of changes is prepared.

@@
   the Weyl denominator becomes singular with respect to the subalgebra.
-  We study the modifications of the fan technique and demonstrate
+  We demonstrate
   that for any reductive subalgebra it is possible to define the
-  injection fan -- the tool that describes
+  injection fan and the analogue of the Weyl numerator -- the tools that describe
   explicitly the recurrent properties of branching coefficients.
@@
 explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
-subalgebra of finite-dimensional or affine Lie algebra.
+subalgebras of finite-dimensional or affine Lie algebras.
 In the case of maximal embedding the corresponding fan is unsubtracted, the singular element
@@
 
-$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \af\right) j}^{\vee
+$\alpha _{i}^{\vee }$ , $\left( \beta _{j}^{\vee
 }\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\af%
@@
 }\subset \frak{g}}$ and pass to a summation over the vectors of the
-injection fan $\Gamma _{\af\rightarrow \frak{g}}$ (see definition \ref
+injection fan $\Gamma _{\af\rightarrow \frak{g}}$ (see Definition \ref
 {fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
@@
 so we have $\Delta_{\afb}^+ = \left\{ \alpha_1 \right\}$ (step (ii)).
-According to (\ref{fan-definition})
+According to Definition \ref{fan-definition}
 the fan $\Gamma_{A_1\to B_2}$ (step (iii)) consists of two weights:
@@
 \end{eqnarray*}
-As far as the set $\Delta^+_{B_4} \setminus \left(\Delta^{+}_{\af} \cup \Delta^{+}_{\afb}\right)$ is fixed the injection
-fan $\Gamma_{B_2 \to B_4}$ can be constructed (using formulas (\ref{eq:6} -- \ref{fan-defined})).
+As far as the set $\Delta^+_{B_4} \setminus  \Delta^{+}_{\afb}$ is fixed the injection
+fan $\Gamma_{B_2 \to B_4}$ can be constructed using Definition \ref{fan-definition}.
 As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need only the factor
@@
 
-Using the defining relation (\ref{fan-defined}) we construct the
-fan $\Gamma_{\hat A_1\to\hat A_2}$.
-In this case $\gamma_0 =0$ its sign is minus, $s\left( 0 \right)=-1$, thus we are to use the
+Using Definition (\ref{fan-definition})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$.
+In this case $\gamma_0 =0$ and its sign $s\left( 0 \right)=-1$ thus we are to use the
 sign function $s(\gamma)$ (see Figure \ref{fig:AffineA2A1Fan}).
@@
 
-Using (\ref{fan-defined}) we obtain the fan
+Using Definition (\ref{fan-definition}) we obtain the fan
 $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
@@
 \end{document}
-
-$\af \subset \gf$

### 2011-01-18 GeneralOverview/Lectures/2dqft.tex
Caption changed, three papers added to bibliography, some changes in subsection captions and introduction.

@@
 
-\title{Лекции по теории поля в двух измерениях\\
+\title{Конформная теория поля и критические явления\\
 \small{Академический университет, кафедра теоретической физики}
@@
   Текст представляет собой конспект лекций по квантовой теории поля в двух измерениях.
-Лекции читаются в осеннем семестре 2010 года в Академическом университете для магистрантов 6 курса, группа теории твердого тела.
+Лекции читались в осеннем семестре 2010 года в Академическом университете для магистрантов 6 курса (группа теории конденсированного состояния).
 \end{abstract}
@@
 \label{sec:literature}
-В первых лекциях \ref{sec:lecture-1},\ref{sec:lecture-2} мы опираемся на вводные главы книги \cite{difrancesco1997cft}.
-Подробно решение  модели Изинга в двух измерениях рассмотрено в книге  \cite{belavin2001lect}.
+В \ref{sec:lecture-1} и \ref{sec:lecture-2} лекциях  мы опираемся на вводные главы книги \cite{difrancesco1997cft}.
+Мы уделяем большое внимание использованию математического аппарата квантовой теории поля в моделях статистической физики.
+При этом мы пользуемся знакомством слушателей с функциональным интегралом.
 Последовательное изложение техники функционального интеграла в статистической физике можно найти в книге А.Н.
@@
 
+Лекции \ref{sec:lecture-5}, \ref{sec:lecture-6} посвящены  точному решению модели Изинга в двух измерениях.
+Подробно решение  модели Изинга в двух измерениях рассмотрено в книге  \cite{belavin2001lect}, на материале которой и основано изложение в данных лекциях.
+
 Изложение конформной теории поля в двух измерениях опирается на оригинальную статью \cite{belavin1984ics}, книгу \cite{difrancesco1997cft}, обзор \cite{zamolodchikov1989rus,zamolodchikov1989conformal}, недавно переизданный в виде книги.
@@
 
+Дополнительные сведения о приложениях конформной теории поля и ее связи с теорией суперструн можно найти в подробных лекциях \cite{springerlink:10.1134/S1063778810050108} и обзорах \cite{Walton:1999xc}, \cite{gaberdiel2000icf}.
+
 \subsection{Введение}
@@
 Чем интересны двумерные системы?
-Во-первых, они существуют в природе.
-Например, критическое поведение на поверхности металлов напоминает поведение модели Изинга в двух измерениях \cite{campuzano1985110}.
+
+Во-первых, они существуют в природе. Например, критическое поведение на поверхности металлов напоминает поведение модели Изинга в двух измерениях \cite{campuzano1985110}.
+
 Во-вторых, в двух измерениях даже в простых моделях есть фазовые переходы.
@@
 В простых двумерных моделях можно вычислить критические индексы и изучать поведение системы при фазовых переходах.
+
 Гипотеза универсальности утверждает, что все системы в критической точке разбиваются на небольшое число классов.
@@
 Благодаря гипотезе универсальности существует лишь небольшое число типов критического поведения, поэтому значения индексов, вычисленные теоретически в простых моделях соответствуют гораздо более сложным реальным системам.
+
 В критической точке наблюдается масштабная инвариантность, что ведет к конформной инвариантности \cite{Polyakov:1970xd}.
@@
 В результате поведение системы может быть описано строго математически методами двумерной конформной теории поля.
+
 Двумерная конформная теория поля имеет и другое применение, не связанное с описанием фазовых переходов --- это теория струн, которая считается перспективным кандидатом на роль квантовой теории гравитации.
+
+В данных лекциях мы займемся проблемой описания фазовых переходов в двумерных системах.
+Основной для нас будет двумерная модель Изинга.
+Мы обсудим обоснование гипотез подобия и универсальности в рамках ренормгруппового подхода, покажем наличие конформной инвариантности в критической точке и продемонстрируем на примере применение конформной теории поля для вычисления критических индексов и корреляторов.
 
@@
 \end{equation}
+Намагниченность является параметром порядка --- в (анти)ферромагнитной фазе она отлична от нуля.
+
 Магнитная восприимчивость
@@
 
-\section{Лекция 4. Уравнение Каллана-Симанчика. Ренормгруппа в двух измерениях.}
+\section{Лекция 4 }
 \label{sec:lecture-4}
+\subsection{Уравнение Каллана-Симанчика}
 
@@
 Это верно и для других компонент тензора энергии-импульса в силу Лоренц-инвариантности.
+
+\subsection{Ренормгруппа в двух измерениях}
+\label{sec:renormgroup-in-2d}
 
@@
 где $\eta_{ab}=\mathrm{diag}(-1,1,\dots,1)$. Видно, что мы получили алгебру $so(d+1,1)$. В случае пространства Минковского была бы $so(d,2)$.
-\section{Лекция 8. Инварианты. Явный вид конформных преобразований полей в $d\geq 3$.}
+\section{Лекция 8}
 \label{sec:lecture-8}
+
+\subsection{Инварианты}
+\label{sec:invariants}
+
 Обсудим, какой вид могут иметь простейшие инварианты --- $N$-точечные функции $\Gamma(x_1,\dots,x_N)$.
@@
 Всего $N(N-3)/2$ вариантов для $N$ точек.
+
+\subsection{Явный вид конформных преобразований полей в $d\geq 3$.}
+\label{sec:conformal-transforms-explicit}
 
@@
 
-\section{Лекция 9. Корреляторы квазипримарных полей. Тождества Уорда.}
+\section{Лекция 9}
 \label{sec:lecture-9}
+
+\subsection{Корреляторы квазипримарных полей}
+\label{sec:quasiprimary-correlators}
 
@@
 
-\section{Лекция 12. Конформный предел модели Изинга}
+\section{Лекция 12}
 \label{sec:lecture-12}
+
+\subsection{Конформный предел модели Изинга}
+\label{sec:ising-conformal-limit}
 
@@
 $\nu=1$, $d-1/\nu=1=\Delta_{\varepsilon}=h_{\varepsilon}+\bar h_{\varepsilon}$, то есть $h_{\varepsilon}=\frac{1}{2}$ и поле $\Phi_{2}$ соответствует оператору энергии в модели Изинга.
+
+\subsection{Свободный фермион}
+\label{sec:free-fermion}
 
@@
 
+\section{Заключение}
+\label{sec:conclusion}
+
 \bibliography{2dqft}{}

### 2011-01-27 AffineLieAlgebras/Mathematica/lie.m
Mathematica code initial commit

@@ -1,0 +1,515 @@
+clear[standardBase]
+
+makeSimpleRootSystem[A,rank_Integer]:=standardBase @@@ Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank},{j,1,rank+1}];
+makeSimpleRootSystem[B,rank_Integer]:=standardBase @@@ Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],1]];
+makeSimpleRootSystem[C,rank_Integer]:=standardBase @@@ Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],2]];
+makeSimpleRootSystem[D,rank_Integer]:=standardBase @@@ Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Append[Table[0,{rank-2}],1],1]];
+
+Unprotect[Dot];
+Dot[x_standardBase,y_standardBase]:=standardBase @@ Dot[List@@x,List@@y]
+
+Unprotect[Plus];
+Plus[x_standardBase,y_standardBase]:=standardBase @@ Plus[List@@x,List@@y]
+
+Unprotect[Times];
+Times[x_,y_standardBase]:=standardBase @@ Times[x,List@@y]
+
+reflection[x_standardBase]:=Function[y, y-2*(x.y)/(x.x)*x]
+
+coroot[x_standardBase]:=2*x/(x.x)
+
+cartanMatrix[{x__standardBase}]:=Transpose[Outer[Dot,{x},coroot/@{x}]]
+
+weights[
+coroot[b2[[2]]]
+
+coroot/@b2
+
+
+
+coroot/@makeSimpleRootSystem[D,5]
+
+Out[113]= {standardBase[1, -1, 0, 0, 0, 0], standardBase[0, 1, -1, 0, 0, 0], 
+ 
+>    standardBase[0, 0, 1, -1, 0, 0], standardBase[0, 0, 0, 1, -1, 0], 
+ 
+>    standardBase[0, 0, 0, 0, 1, 1]}
+
+Out[111]= {standardBase[1, -1, 0, 0, 0, 0], standardBase[0, 1, -1, 0, 0, 0], 
+ 
+>    standardBase[0, 0, 1, -1, 0, 0], standardBase[0, 0, 0, 1, -1, 0], 
+ 
[…]

### 2011-01-27 GeneralOverview/Lectures/2dqft.tex
Bibliography + lectures compactified

@@
 \newcommand{\afb}{\mathfrak{a}_{\bot}}
+
+\topmargin=-3.5cm
+\oddsidemargin=-1.5cm
+\evensidemargin=-1.5cm
+\textwidth=19cm
+\textheight=28cm
 
@@
 \end{equation}
-Намагниченность является параметром порядка --- в (анти)ферромагнитной фазе она отлична от нуля.
+Намагниченность является параметром порядка --- в упорядоченной (анти)ферромагнитной фазе она отлична от нуля.
 
@@
 Обсудим некоторые обобщения модели Изинга и проиллюстрируем сходство статистической механики с теорией поля.
+
 Если $\sigma_i$ может принимать значения не $-1,1$, а $1,2\dots,q$, то мы получаем модель Поттса с $q$ состояниями.
-Подобным образом получаются и модели Ашкина-Теллера.
+Подобным образом получаются и модели Ашкина-Теллера \cite{difrancesco1997cft}.
+
 Другой класс дискретных моделей отличается более существенно.
@@
 Бывает 16 таких членов.
-В зависимости от того, сколько из них не равны нулю выделяют 6-вершинную и 8-вершинную модели.
-8-вершинная модель --- ненулевой вклад только когда входит четное число стрелок.
+В зависимости от того, сколько из них не равны нулю, выделяют 6-вершинную и 8-вершинную модели.
+8-вершинная модель --- ненулевой вклад только когда входит четное число стрелок (0 входит, 4 выходит; 4 входит, 0 выходит; 6 способов выбрать две входящие стрелки -- итого 8 отличных от нуля членов $R_{\alpha\mu}^{\beta\nu}$).
 
@@
 В критической точке параметр порядка системы стремится к бесконечности, кроме того, фазовый переход в дискретных моделях наблюдается только в термодинамическом пределе числа вершин стремящегося к бесконечности ($N\to \infty$).
-Поэтому при описании фазового перехода имеет смысл перейти модели с дискретным пространством  к непрерывному пространству $d$-мерному пространству.
+Поэтому при описании фазового перехода имеет смысл перейти от модели с дискретным пространством  к непрерывному $d$-мерному пространству.
 В дальнейшем $d$ будет равно двум, но сейчас мы пишем в самом общем виде, чтобы указать аналогию с теорией поля.
@@
 Условие $\vec n^2(x)=1$ сложно использовать, поэтому мы заменим его на другое аналогичное.
-Первый вариант такой замены --- это $\frac{1}{V}\int d^dx\; \vec n^2=1$.
+Первый вариант такой замены --- это наложить требование $\frac{1}{V}\int d^dx\; \vec n^2=1$.
 В результате получается так называемая сферическая модель.

### 2011-02-10 AffineLieAlgebras/Mathematica/lie.m
Freudenthal, not working

@@ -17,9 +17,633 @@ cartanMatrix[{x__standardBase}]:=Transpose[Outer[Dot,{x},coroot/@{x}]];
 clear[weylGroupElement];
 revApply[x_,f_]:=f[x];
 weylGroupElement[x__Integer][{y__standardBase}]:=Function[z,Fold[revApply,z,reflection /@ Part[{y},{x}]]];
-fundamentalWeights[{simpleRoots__standardBase}]:=Plus@@(Inverse[cartanMatrix[{simpleRoots}]]*{simpleRoots})
+fundamentalWeights[{simpleRoots__standardBase}]:=Plus@@(Inverse[cartanMatrix[{simpleRoots}]]*{simpleRoots});
+rho[{simpleRoots__standardBase}]:=Plus@@fundamentalWeights[{simpleRoots}];
+toFundamentalChamber[{simpleRoots__standardBase}][vec_standardBase]:=
+    First[NestWhile[Function[v,
+		       reflection[Scan[If[#.v<0,Return[#]]&,{simpleRoots}]][v]],
+	      vec,
+	      Head[#]=!=reflection[Null]&]];
+orbit[{simpleRoots__standardBase}][{weights__standardBase}]:=
+    Module[{total={}},
+	   NestWhileList[
+	       Function[x,
+			Union[Flatten[Map[Function[y,
+						   Map[reflection[#][y]&,Cases[{simpleRoots},z_ /; z.y>0]]],x]]]],
+	       {weights},
+	       Function[y,
+			Module[{t=y=!={}},total=Union[total,y];t]
+		       ]]];
+orbit[{simpleRoots__standardBase}][weight_standardBase]:=orbit[{simpleRoots}][{toFundamentalChamber[{simpleRoots}][weight]}];
+positiveRoots[{simpleRoots__standardBase}]:=Map[-#&,Flatten[orbit[{simpleRoots}][Map[-#&,{simpleRoots}]]]];
+weightSystem[{simpleRoots__standardBase}][higestWeight_standardBase]:=Module[{minusPosRoots=-positiveRoots[{simpleRoots}]},
+									     NestWhileList[Function[x,Complement[
+										 Cases[Flatten[Outer[Plus,minusPosRoots,x]],y_/;And@@(#.y>=0&/@{simpleRoots})]
+										 ,x]],{higestWeight},#=!={}&]]
 
[…]

### 2011-02-10 AffineLieAlgebras/MQFT2010/article-ru.tex
arXiv version (1102.1702v1) added, Russian translation for TMPh started

\documentclass[12pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsthm}
\usepackage{color}
\usepackage{graphicx}
\usepackage{ucs}
\usepackage[unicode,verbose]{hyperref}

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
%\input{tcilatex}

\begin{document}

\title{Рекурсивные свойства ветвления и БГГ резольвента}
\author{В Д Ляховский$^1$, А А Назаров$^2$\\
Теоретический отдел,\\ Санкт - Петербургский государственный университет\\
198904, Санкт - Петербург, Россия\\
$^1$e-mail: lyakh1507@nm.ru, $^2$ antonnaz@gmail.com}

\maketitle

\begin{abstract}
Рекуррентные соотношения для коэффициентов ветвления основываются на определенном разложении сингулярного элемента. Мы показываем, что такое разложение может использоваться для построения параболических модулей Верма и получения обобщенных формул Вейля-Верма для характеров. Также мы демонстрируем, что коэффициенты ветвления определяют обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда. 
\end{abstract}

\section{Введение}

\label{sec:introduction}
Свойства ветвления (аффинных) алгебр Ли важны для приложений в квантовой теории поля (смотри, например, модели конформной теории поля \cite{difrancesco1997cft},\cite{coquereaux2008conformal}). В данной работе мы показываем, что ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и проявляет свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).

Резольвента для неприводимых модулей в терминах бесконечномерных модулей важна для теории интегрируемых спиновых цепочек \cite{derk1008}. В подходе  $\mathcal{Q}$-оператора Бакстера \cite{derk09} общие трансфер-матрицы, соответствующие (обобщенным) модулям Верма, факторизуются в произведение операторов Бакстера. Резольвента позволяет вычислить трансфер-матрицы для конечномерных вспомогательных пространств.

Чтобы продемонстрировать связь БГГ резольвенты с ветвлением мы используем рекурсивный подход, представленный в работе \cite
{2010arXiv1007.0318L} (похожий подход для максимальных вложений использовался в работе \cite{ilyin812pbc}). Мы рассматриваем подалгебру $\af \hookrightarrow \gf$ вместе с $\afb$ -- ``ортогональным партнером'' $\af$ по отношению к форме Киллинга, а также  $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$, где $\frak{h}=\frak{\frak{h}_{\af}}\oplus
\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. Для любой редуктивной подалгебры $\af$ подалгебра $\afb\hookrightarrow \gf$ регулярна и редуктивна. Для интегрируемого модуля старшего веса $%
L^{\left(\mu \right) }$ и ортогональной подалгебры  $\af_{\bot }$ мы рассматриваем сингулярный элемент $\Psi ^{\left( \mu \right) }$ (числитель в формуле Вейля для характеров $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
\mu \right) }}{\Psi ^{\left( 0\right) }}$, см., например,  \cite
{humphreys1997introduction}) и знаменатель Вейля $\Psi _{\af_{\bot
  }}^{\left( 0\right) }$ для ортогонального партнера. В работе показано, что элемент  $\Psi _{\gf%
}^{\left( \mu \right) }$ может быть разложен в комбинацию числителей Вейля $\Psi _{\af_{\bot }}^{\left( \nu \right) }$, где $\nu \in P_{%
\mathfrak{a}_{\bot}}^{+}$. Это разложение дает возможность построить множество модулей старшего веса $L_{\afb}%
^{\mu _{\afb}}$. В том случае, если вложение\ $\af%
_{\bot }\hookrightarrow \gf$ \ удовлетворяет ``стандартным параболическим'' условиям, эти модули порождают параболические модули Верма $M_{\left(
\afb \hookrightarrow \gf\right) }^{\mu _{%
\afb}}$, так что исходный характер $ch\left(
L^{\mu }\right) $ в итоге раскладывается в чередующуюся сумму таких модулей. С другой стороны, если параболическое условие нарушено, конструкция сохраняется и порождает разложение по отношению к набору обобщенных модулей Верма  $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
\widetilde{\afb}}}$, где $%
\widetilde{\frak{b}_{\perp }}$ уже не является подалгеброй в $\gf$, а оказывается сжатием $\widetilde{\afb}$.

Некоторые общие свойства предложенного разложения формулируются в терминах определенного формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''. Использование этого инструмента позволило сформулировать простой и явный алгоритм для вычисления правил ветвления, подходящий для произвольной (максимальной или не максимальной) подалгебры в аффинной алгебре Ли \cite{2010arXiv1007.0318L}.

Возможные обобщения полученных результатов обсуждаются в Разделе \ref{sec:conclusions}.

\subsection{Обозначения}

\label{sec:notation}

Consider Lie algebras (affine Lie algebras) $\frak{g}$ and $\frak{a}$ and an
injection $\frak{a}\hookrightarrow \frak{g}$ such that $\frak{a}$ is a
reductive subalgebra $\frak{a\subset g}$ with correlated root spaces: $\frak{%
h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g}}^{\ast }$. We use the
following notations:

$\frak{g=n}^{-}+\frak{h}+\frak{n}^{+}$ --- the Cartan decomposition;

$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
\left( \mathrm{{resp. }\frak{a}}\right) $ ;

$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
^{+} $ $\left( \mathrm{{resp. }\Delta _{\frak{a}}^{+}}\right) $--- the
positive root system (of $\frak{g}$ and $\frak{a}$ respectively);

$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $%
\Delta $ (resp. in $\left( \Delta _{\frak{a}}\right) $);

$S\quad \left( S_{\frak{a}}\right) $ --- the set of simple roots (for
$\gf$ and $\af$ respectively);

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a%
}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
}\right) $-- the simple coroot for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a}%
}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$W$ , $\left( W_{\frak{a}}\right) $--- the Weyl group;

$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;

$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
fundamental Weyl chamber;

$\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;

$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;

$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\af$-module
with the highest weight $\nu $);

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
the weight diagram of $L^{\mu }$ (resp. ${}L_{\frak{a}}^{\nu }$ );

$P$ (resp. $P_{\frak{a}} $) \ --- the weight lattice;

$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight lattice;

$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\zeta }^{\left( \nu \right)
}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
resp. }\in P_{\frak{a}}}\right) $ in $L^{\mu }$, (resp. in $\zeta \in
L_{\frak{a}}^{\nu } $);

$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\frak{a}}^{\nu
}\right) $)--- the formal character of $L^{\mu }$ (resp. of $L_{\frak{a}}^{\nu
} $);

$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
\mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}\quad $ (resp. $R_{\frak{a}}:=\prod_{\alpha \in
\Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}%
}\left( \alpha \right) } $)--- the Weyl denominator.

\section{Orthogonal subalgebra and\\ singular elements}

\label{sec:recurr-form-branch}

In this section we shall show how the recurrent approach to branching
problem leads naturally to a presentation of a formal character of
$\frak{g}$-module in terms characters corresponding to a set
of parabolic (generalized) Verma modules. Consider a reductive
Lie algebra $\frak{g}$ and its reductive subalgebra $\frak{a}\subset \frak{g}$.
Let $L^{\mu} $ be the highest weight integrable module of $\frak{g}$, $\mu \in
P^{+}$. Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
\begin{equation*}
L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
\end{equation*}
Using the projection operator $\pi _{\frak{a}}$ (to the weight space $\frak{%
h_{a}}^{\ast }$) one can write this decomposition in terms of formal
characters:
\begin{equation}
\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
\label{branching1}
\end{equation}
The module $L^{\mu }$ has the BGG resolution (see \cite
{bernstein1976category,bernstein1975differential,bernstein1971structure} and
\cite{humphreys2008representations}). All the members of the filtration
sequence are the direct sums of Verma modules and all their highest weights $%
\nu $ are strongly linked to $\mu $:
\begin{equation*}
\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
W\right\} .
\end{equation*}

\subsection{Orthogonal subalgebra}

Let $\frak{h}_{\frak{a}}$ be a Cartan subalgebra of $\mathfrak{g}$. For $%
\mathfrak{a}\hookrightarrow \frak{g}$ introduce the ''orthogonal partner'' $%
\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$ .

Consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to
$\frak{a}$,
\begin{equation*}
\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\frak{a}$,
\begin{eqnarray}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
\label{delta a ort} \\
\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
\notag
\end{eqnarray}
Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\frak{a}_{\perp
}}^{+}$. The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
h\right) =0\right\}
\end{equation*}
so that $\frak{g}$ has the subalgebras
\begin{eqnarray}
\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\qquad
\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
\end{eqnarray}
Notice that $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ in general is not a
subalgebra in $\mathfrak{g}$.

For the Cartan subalgebras we have the decomposition
\begin{equation}
\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
\frak{h}_{\frak{a}}.
\end{equation}
For $\frak{a}$ and $\frak{a}_{\perp }$ consider the
corresponding Weyl vectors, $\rho _{\frak{a}}$ and $\rho _{\frak{a}_{\perp
}} $. Form the so called ''defects'' $\mathcal{D}_{\frak{a}}$ and $\mathcal{%
D}_{\frak{a}_{\perp }}$ of the injection:
\begin{equation}
\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho , \qquad
\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
_{\perp }}\rho .  \label{defect ort}
\end{equation}

For $\mu \in P^{+}$ consider the linked weights $\left\{
\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $. Consider the projections to
$h_{\frak{a}_{\perp }}^{\ast }$ additionally shifted by the defect $-%
\mathcal{D}_{\frak{a}_{\perp }}$:
\begin{equation*}
\mu _{\frak{a}_{\perp }}\left( w\right) :=\pi _{\frak{a}_{\perp }}\left[
w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad w\in W.
\end{equation*}
Among the weights $\left\{ \mu _{\frak{a}_{\perp
}}\left( w\right) |w\in W\right\} $ one can always choose those located in
the fundamental chamber $\overline{C_{\frak{a}_{\perp }}}$. Let $U$ be the
set of representatives $u$ for the classes $W/W_{\frak{a}_{\perp }}$ such
that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
\overline{C_{\frak{a}_{\perp }}}\right\} \quad .  \label{U-def}
\end{equation}
Thus we can form the subsets:
\begin{equation}
\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}%
_{\perp }},\quad u\in U,  \label{mu-a}
\end{equation}
and
\begin{equation}
\mu _{\frak{a}_{\perp }}\left( u\right) :=\pi _{\frak{a}_{\perp }}\left[
u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U.
\label{mu-a-tilda}
\end{equation}

Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
since it is built on a subset of roots of the algebra $\mathfrak{g}$.

For the modules we are interested in the Weyl-Kac formula for $\mathrm{ch}%
\left( L^{\mu }\right) $ can be written in terms of singular elements \cite
{humphreys1997introduction},
\begin{equation*}
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
)-\rho },
\end{equation*}
namely,
\begin{equation}
\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
\label{Weyl-Kac2}
\end{equation}
The same is true for the submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
}\right) $ in (\ref{branching1})
\begin{equation*}
\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}},
\end{equation*}
with
\begin{equation*}
\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
\end{equation*}

Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
we get the relation connecting the singular elements $\Psi ^{\left( \mu
\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
\begin{eqnarray}
\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
)-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
mult}_{\frak{a}}(\beta )}},  \notag  \label{eq:4} \\
\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}}.
\end{eqnarray}

\subsection{Decomposing the singular element.}

\label{subsec:decomp-sing-element}

Now we shall perform a decomposition of the singular element $\Psi ^{\left(
\mu \right) }$ in terms of singular elements of the orthogonal partner
modules:

\begin{lemma}
Let $\frak{a}_{\bot }$ be the orthogonal partner of a reductive subalgebra $%
\frak{a}\hookrightarrow \frak{g}$ with $\frak{h}=\frak{\frak{h}_{\frak{a}}}%
\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$, $\widetilde{%
\frak{a}_{\perp }}=\frak{a}_{\perp }\oplus \frak{h}_{\perp }$ and $%
\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$.

$L^{\mu }$ be the highest weight integrable module with $\mu \in P^{+}$ and

$\Psi ^{\left( \mu \right) }$\ -- the singular element of $L^{\mu }$.

Then the element $\Psi ^{\left( \mu \right) }$ can be decomposed into the
sum over $u\in U$ (see (\ref{U-def})) of singular elements $\Psi _{\frak{a}%
_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ with the coefficients
$\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
\begin{equation}
\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\widetilde{%
\mathfrak{a}}}\left( u\right) }\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) }.  \label{sing decomp main}
\end{equation}
\label{Psi-decomp-lemma}
\end{lemma}

\begin{proof}
Let
\[
u(\mu +\rho )=\pi _{\left( \aft\right) }u(\mu +\rho )+\pi _{\left(
\frak{a}_{\perp }\right) }u(\mu +\rho )
\]
with $u\in U$. For any $v\in W_{\frak{a}_{\bot }}$ consider
the singular weight $vu(\mu +\rho )-\rho $ and perform the decomposition:
\begin{equation}
\begin{array}{lcl}
vu(\mu +\rho )-\rho  & = & \pi _{\left( \frak{a}\right) }\left( u(\mu +\rho
)\right) -\rho +\rho _{\frak{a}_{\perp }}
\\
&  & +\ v\left( \pi _{\left( \aft_{\perp }\right) }u(\mu
+\rho )-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{%
\frak{a}_{\perp }} .
\end{array}
\label{sing-decomp-1}
\end{equation}
Use the defect $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}) to
simplify the first line in (\ref{sing-decomp-1}):
\[
\begin{array}{r}
\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
\frak{a}_{\perp }}= \\
\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\pi _{\aft%
}\rho -\pi _{\af_{\bot }}\rho +\rho _{\frak{a}_{\bot }}= \\
=\pi _{\left( \aft\right) }\left( u(\mu +\rho )-\rho \right) +\mathcal{D}%
_{\frak{a}_{\bot }},
\end{array}
\]
and the second one:
\[
\begin{array}{c}
v\left( \pi _{\left( \frak{a}_{\perp }\right) }u(\mu +\rho
)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}%
_{\perp }}= \\
v\left( \pi _{\left( \frak{a}_{\bot }\right) }u(\mu +\rho )-%
\mathcal{D}_{\frak{a}_{\bot }}-\pi _{\left( \frak{a}_{\bot }\right) }\rho
+\rho _{\frak{a}_{\bot }}\right)
-\rho _{\frak{a}_{\bot }}= \\
=v\left( \pi _{\left( \frak{a}_{\bot }\right) }\left[ u(\mu
+\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\bot }}+\rho _{\frak{a}_{\bot
}}\right) -\rho _{\frak{a}_{\bot }}.
\end{array}
\]
This provides the desired decomposition of the singular element $%
\Psi ^{\mu }$ in terms of singular elements $\Psi _{\frak{a}%
_{\perp }}^{\eta }$ of the $\frak{a}_{\perp }$-modules $L_{%
\frak{a}_{\perp }}^{\eta }$:
\begin{equation}
\begin{array}{l}
\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
(v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
=\sum_{u\in U}\epsilon (u)e^{\pi _{\aft}\left[ u(\mu +\rho )-\rho \right]
+\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
(v)e^{v\left( \pi _{\left( \frak{a}_{\perp }\right) }\left[
u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}+\rho _{\frak{a}%
_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
=\sum_{u\in U}\;\epsilon (u)\Psi _{\af_{\perp }}^{\pi
_{\left( \frak{a}_{\perp }\right) }\left[ u(\mu +\rho )-\rho
\right] -\mathcal{D}_{\frak{a}_{\perp }}}e^{\pi _{\left( \aft\right) }%
\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}.
\end{array}
\label{singular main}
\end{equation}
\end{proof}

\bigskip

\begin{remark}
This relation can be considered as a generalized form of the Weyl formula
for the singular element $\Psi _{\frak{g}}^{\mu }$: the vectors $\mu _{%
\widetilde{\mathfrak{a}}}\left( u\right) $ play the role of singular weights
while the alternating factors $\epsilon (u)$ are extended to $\epsilon
(u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$. In
fact when $\frak{a=g}$ both $\frak{a}_{\perp }$and $\frak{h}_{\perp }$are
zeros, $U=W$, and\ the original Weyl formula is reobtained so far as the singular elements $\epsilon (u)\Psi _{\frak{a}_{\perp
}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\epsilon (u)$ become trivial.
 In the opposite
limit when $\frak{a=0}$, $\Delta _{\frak{a}_{\perp }}=\Delta _{\frak{g}}$, $%
\frak{h}_{\perp }^{\ast }=0$, $\frak{a}_{\perp }=\frak{g}$, $\mathcal{D}_{%
\frak{a}_{\perp }}=0$ and $U=W/W_{\frak{a}_{\perp }}=e$ the singular element
 $\Psi ^{\mu }$ is again reobtained, now via the trivilization of the set of
 vectors $\mu _{\af}\left( e\right) =0$.
\end{remark}

\begin{remark}

In \cite
{2010arXiv1007.0318L} the decomposition analogous to (\ref{singular main}) was
used to construct the recurrent relations for branching coefficients $k_{\xi
}^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
\hookrightarrow \frak{g}$:
\begin{equation}
\begin{array}{c}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right.  \\
\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
}\right) .
\end{array}
\label{recurrent rel}
\end{equation}
The recursion is goverened by the set $\Gamma _{\widetilde{\frak{a}}%
\rightarrow \frak{g}}$ called the injection fan. The latter is defined by the
carrier set $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the
coefficient function $s(\xi )$
\begin{equation*}
\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{g}}:=\left\{
\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\}
\end{equation*}
appearing in the expansion
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\widetilde{\frak{a}}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
_{\frak{a}}(\pi _{\widetilde{\frak{a}}}\alpha )}=-\sum_{\gamma \in P_{%
\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma };\quad
\end{equation}
The weights in $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
g}}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
\right\} $ -- and the zero element is to be eliminated:
\begin{equation}
\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}=\left\{ \xi -\gamma
_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
\end{equation}

The recursion relation (\ref{recurrent rel}) was originally used to
describe branchings for integrable modules. Notice that there exists an
important class of modules that also can be reduced with the help of the
injection fan --
these are Verma modules.
\end{remark}

\subsection{Weyl-Verma formulas.}

\begin{statement}
\bigskip For an orthogonal subalgebra $\frak{a}_{\perp }$ in $\frak{g}$ (an
orthogonal partner of a reductive $\frak{a}\hookrightarrow \frak{g}$) the
character of an integrable highest weight module $L^{\mu }$ can be presented
as a combination (with integral coefficients) of parabolic Verma modules
distributed by the set of weights $e^{\mu _{\widetilde{\mathfrak{a}}}\left(
u\right) }$:
\begin{equation}
\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{%
\widetilde{\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) },  \label{gen Weyl-Verma}
\end{equation}
where $U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
\overline{C_{\frak{a}_{\perp }}}\right\} $ and $I$ is such a subset of $S$ that
$\Delta _{I}^{+}$ is
equivalent to $\Delta _{\frak{a}_{\perp }}^{+}$.
\end{statement}

\bigskip
\begin{proof}
By the definition (\ref{delta a ort}) the subalgebra $%
\mathfrak{a}_{\bot }$ is regular and reductive. Consider its Weyl
denominator $R_{\frak{a}_{\perp }}:=\prod_{\alpha \in \Delta _{\frak{a}%
_{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}%
\mathrm{\left( \alpha \right) }}$ and the element $R_{J}:=\prod_{\alpha \in
\Delta ^{+}\setminus \Delta _{\frak{a}_{\perp }}^{+}}\left( 1-e^{-\alpha
}\right) ^{\mathrm{mult}(\alpha )}$ as the factors in $R$: $\quad $%
\begin{equation*}
R=R_{J}R_{\frak{a}_{\perp }}.
\end{equation*}
According to this factorization and the decomposition (\ref{sing decomp main}%
) the character $\mathrm{ch}\left( L^{\mu }\right) $ can be written as
\begin{eqnarray*}
\mathrm{ch}\left( L^{\mu }\right) &=&\left( R_{J}\right) ^{-1}\left( R_{%
\frak{a}_{\perp }}\right) ^{-1}\Psi ^{\mu }=\left( R_{J}\right)
^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}}\left( u\right) }\epsilon
(u)\left( R_{\frak{a}_{\perp }}\right) ^{-1}\Psi _{\frak{a}_{\perp }}^{\mu _{%
\frak{a}_{\perp }}\left( u\right) } \\
&=&\left( R_{J}\right) ^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}%
}\left( u\right) }\epsilon (u)\mathrm{ch}\left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
}}\left( u\right) }\right),
\end{eqnarray*}
where $\left\{ L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left(
u\right) }|u\in U\right\} $ is the set of finite-dimensional $\frak{a}%
_{\perp }$-modules with the highest weights $\mu _{\frak{a}_{\perp }}\left(
u\right) $. We are interested in nontrivial subalgebras $\frak{a}$ and
correspondingly in nontrivial $\frak{a}_{\perp }$ (the case of a trivial
orthogonal subalgebra was considered above (see Remark 1)). This means that $r_{\frak{a}}\geq 1$ and $r_{\frak{a}%
_{\perp }}<r$. Due to the fact that any maximal regular subalgebra has the
Dynkin scheme obtained by one or two node subtractions from the extended
Dynkin scheme and the extended scheme has at most one dependent root (the
highest root) the set of roots $\Delta _{\frak{a}_{\perp }}^{+}$ is always
equivalent to the one $\Delta _{I}^{+}$ generated\ by some subset $I\subset
S $ of simple roots.

It follows that we can (by redefining the set $\Delta ^{+}$) identify $%
\Delta _{\frak{a}_{\perp }}^{+}$ with the subset $\Delta _{I}^{+}$ \ where $%
I\subset S$ . This allows us to introduce the elements necessary to compose
the generalized Verma modules
\cite{lepowsky1977generalization,humphreys2008representations}.
We have two sets of root
vectors $\left\{ x_{\xi }\in \frak{g}_{\xi }|\xi \in \Delta _{I}^{+}\right\}
$ and $\left\{ x_{\eta }\in \frak{g}_{\eta }|\eta \in \Delta ^{+}\setminus
\Delta _{I}^{+}\right\} $ and the corresponding nilpotent subalgebras in $\frak{n}%
^{+}$:
\begin{equation*}
\frak{n}_{I}^{+}:=\sum_{\xi \in \Delta _{I}^{+}}\frak{g}_{\xi },\quad
\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\frak{g}%
_{\eta }.
\end{equation*}
The first subalgebra together with its negative counterpart $\frak{n}%
_{I}^{-} $ generates a simple subalgebra
\begin{equation*}
\frak{s}_{I}=\frak{n}_{I}^{-}+\frak{h}_{I}+\frak{n}_{I}^{+}.
\end{equation*}
We enlarge it with the remaining Cartan generators:
\begin{equation*}
\frak{l}_{I}=\frak{n}_{I}^{-}+\frak{h}+\frak{n}_{I}^{+}.
\end{equation*}
The semidirect product of $\frak{l}_{I}$ and $\frak{u}_{I}^{+}$
gives a parabolic subalgebra $\frak{p}_{I}\hookrightarrow \frak{g}$ :
\begin{equation}
\frak{p}_{I}=\frak{l}_{I}\vartriangleright \frak{u}_{I}^{+}.
\label{paralolic subalg}
\end{equation}
Its universal enveloping $U\left( \frak{p}_{I}\right) $ is a subalgebra in $%
U\left( \frak{g}\right) $. The $\frak{l}_{I}$-modules $L_{\frak{a}_{\perp }}^{\mu _{%
\frak{a}_{\perp }}\left( u\right) }$ can be easily lifted to $\frak{p}_{I}$%
-modules using the trivial action of the nilradical $\frak{u}_{I}^{+}$. The
latter induce $U\left( \frak{g}\right) $-modules in a standard way:
\begin{equation*}
M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=U\left( \frak{g}\right)
\otimes _{U\left( \frak{p}_{I}\right) }L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) }.
\end{equation*}

These are the \textit{generalized Verma modules}  \cite{lepowsky1977generalization}
generated by the highest weights $\mu _{\frak{a}%
_{\perp }}\left( u\right) $. As a $U\left( \frak{u}_{I}^{-}\right) $-module
each $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ is isomorphic to $%
U\left( \frak{u}_{I}^{-}\right) \otimes $ $L_{\frak{a}_{\perp }}^{\mu _{%
\frak{a}_{\perp }}\left( u\right) }$ and thus its character can be written
in terms of Kostant-Heckman function \cite{KostantHeckman1982} corresponding
to the injection of the orthogonal partner $\frak{a}_{\perp
}\hookrightarrow \frak{g}$:
\begin{equation*}
\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\mathcal{KH}_{%
\frak{a}_{\perp }\hookrightarrow \frak{g}}\mathrm{ch}L_{\frak{a}_{\perp
}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
\end{equation*}
The function $\mathcal{KH}_{\frak{a}_{\perp }\hookrightarrow \frak{%
g}}$ is generated by the denominator $R_{I}$ thus the last expression can be
written in the form
\begin{equation*}
\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\frac{1}{R_{I}}%
\mathrm{ch}L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
\end{equation*}
This means that we have obtained the generalized Weyl-Verma character formula
 -- the decomposition of $\mathrm{ch}\left(
L^{\mu }\right) $ in terms of generalized Verma module characters:
\begin{equation}
\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
u\right) }.  \label{char in gen verma mod}
\end{equation}
\end{proof}

\begin{remark}
Here the generalized Weyl-Verma character formula (called the alternating sum
formula in \cite{humphreys2008representations}) appears in a special
form: the weights $\mu _{\aft}$ and the generalized Verma module highest weights
$\mu _{\afb}$ are separated. The reason is that the
highest weight of $M_{I}$-module is not equal to the projection of its maximal
weight to $h^*_{\afb}$ (but must be additionally shifted by the defect).
\end{remark}

\begin{example}
  Consider the generalized Verma modules for the
  embedding  $A_{1}\hookrightarrow B_{2}$ with the subalgebra $\afb$ attributed to the
  root $\alpha_{1}$
  of $B_{2}$. The generalized Verma module $M^{\omega_{1}}_{I}$ with the highest weight
  $\omega_{1}=e_{1}$ is shown in Figure \ref{fig:B2_Verma_Decomp}.
  \begin{figure}[h!bt]
  \noindent\centering{
   \includegraphics[width=120mm]{B2_Gen_Verma_Decomp.pdf}
  }
  \caption{Generalized Verma modules  for the regular embedding of $A_1$ into $B_2$.
  Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. The
    decomposition of $L^{\omega_{1}}$ is indicated by
    the set of contours of the involved generalized Verma
  modules. Dashed contours correspond to positive $\epsilon(u)$ and dotted to negative.}

 \label{fig:B2_Verma_Decomp}
\end{figure}

\end{example}

\begin{remark}
As it was proved in \cite{humphreys2008representations} (see Proposition 9.6
) characters of the generalized Verma modules $M_{I}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) }$ can be described as linear combinations of
ordinary Verma modules of $\frak{g}$:
\begin{equation*}
\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\sum_{w\in W_{%
\frak{a}_{\perp }}}\epsilon \left( w\right) \mathrm{ch}M^{w\left( \mu _{%
\frak{a}_{\perp }}\left( u\right) +\rho _{\frak{a}_{\perp }}\right) -\rho _{%
\frak{a}_{\perp }}}
\end{equation*}
Substituting this expression in\ (\ref{char in gen verma mod}) and using the
definitions (\ref{mu-a},\ref{mu-a-tilda}) and (\ref{defect ort}) we reconstruct
the standard Weyl-Verma decomposition of the character:
\begin{equation*}
\mathrm{ch}\left( L^{\mu }\right) =\sum_{w\in W}\;\epsilon (u)\mathrm{ch}%
M^{w\left( \mu +\rho \right) -\rho }.
\end{equation*}
\end{remark}

\section{BGG resolution and branching}

In \cite{lepowsky1977generalization} it was demonstrated that for the
highest weight module $L^{\mu }$ with $\mu \in P^{+}$ the sequence

\begin{equation}
0\rightarrow M_{r}^{I}\overset{\delta _{r}}{\rightarrow }M_{r-1}^{I}\overset{%
\delta _{r-1}}{\rightarrow }\ldots \overset{\delta _{1}}{\rightarrow }%
M_{0}^{I}\overset{\varepsilon }{\rightarrow }L^{\mu }\rightarrow 0,
\label{resolution sequence}
\end{equation}
with
\begin{equation}
M_{k}^{I}=\bigoplus_{u\in U,\;\mathrm{length}\left( u\right)
=k}M_{I}^{u\left( \mu +\rho \right) -\rho },\quad M_{0}^{I}=M_{I}^{\mu }
\label{Verma elements sequence}
\end{equation}
(the generalized BGG resolution) is exact and formula (\ref{gen Weyl-Verma}%
) is a cosequence of this resolution.

\begin{figure}[h!bt]
 \noindent\centering{
   \includegraphics[width=140mm]{B2_Exact.pdf}}
 \caption{Injection $A_1\hookrightarrow B_2$ (see Figure \ref{fig:B2_Verma_Decomp}).
 The orthogonal partner is $A_1$ corresponding to the root $\alpha_1$.
 The resolution of the simple module $L^{\omega_1}$.
 Presented is the central part of the exact sequence
   $0 \to Im(\delta_2) \to \left( e^{\mu _{\widetilde{%
\frak{a}}}\left( e\right) }\mathrm{ch}M_{I}^{\pi _{\afb}\left[ \omega_1 \right] -%
\mathcal{D}_{\afb} }=M^{\omega_1}_{I}\right) \to
   L^{\omega_1}\to 0 $.  Here $\mu _{\widetilde{\frak{a}}}\left( e\right) =\pi _{\aft}\left[ \mu \right] + \mathcal{D}_{\afb}$.
   }
\end{figure}

\begin{statement}

Let $L^{\mu }$ be the highest weight $\frak{g}$-module with $\mu \in P^{+}$
,let its regular subalgebra $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$
be orthogonal to a reductive subalgebra $\frak{a}\hookrightarrow \frak{g}$.
Then the decomposition (\ref{sing decomp main}) defines both the generalized
resolution of $L^{\mu }$ with respect to $\frak{a}_{\perp }$ and the
branching rules for $L^{\mu }$ with respect to $\frak{a}$ .
\end{statement}

\begin{proof}
Put
\begin{equation*}
\mathrm{ch}M_{I}^{u\left( \mu +\rho \right) -\rho }=e^{\mu _{\widetilde{%
\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
u\right) },\mathrm{ch}M_{I}^{\mu }=e^{\mu _{\widetilde{\frak{a}}}\left(
e\right) }\mathrm{ch}M_{I}^{\pi _{\frak{a}_{\perp }}\left[ \mu \right] -%
\mathcal{D}_{\frak{a}_{\perp }}}
\end{equation*}
with\ $\mu _{\widetilde{\frak{a}}}\left( u\right) ,\mu _{\frak{a}_{\perp
}}\left( u\right) $ and $\mathcal{D}_{\frak{a}_{\perp }}$ as in Lemma \ref{Psi-decomp-lemma} and $%
u\in U$ defined by (\ref{U-def}). This gives the elements of the filtration
sequence (\ref{resolution sequence}).

Consider the set $\left\{ \mu _{\frak{a}_{\perp }}\left( u\right) |u\in
U\right\} $ as the highest weights for the simple modules $L_{\frak{a}%
_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ and evaluate their
dimensions. Together with
$\left\{ \mu _{\widetilde{\mathfrak{a}}}\left( u\right) |u\in
U\right\} $ this gives the set of singular weights
\begin{equation*}
\left\{ \epsilon (u)\;
e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }
\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
}}\left( u\right) }\right) \right\} .
\end{equation*}
The branching $L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu
\in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ is
then fixed by the injection fan $\Gamma _{\frak{a}\rightarrow \frak{g}}$ and
the relation (\ref{recurrent rel}). The latter gives us the coefficients $k_{\xi
}^{\left( \mu \right) }$ and thus defines $b_{\nu }^{\left( \mu \right) }$
due to the property $b_{\nu }^{\left( \mu \right) }=k_{\nu }^{\left( \mu
\right) }$ for $\nu \in \overline{C_{\frak{a}}}$ .
\end{proof}

\begin{corollary}

Let $L^{\mu }$ be the highest weight $\frak{g}$-module with $\mu \in P^{+}$
and $\frak{a}\hookrightarrow \frak{g}$ -- a reductive subalgebra in $\frak{g}
$. Let $\frak{a}_{\perp }$, the orthogonal partner for $\frak{a}$, be
equivalent to $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, and $\widetilde{%
\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ with $\frak{h=\frak{h}_{\frak{a}}%
}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$. Let $L_{%
\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }=\bigoplus\limits_{\nu \in P_{%
\widetilde{\frak{a}}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\widetilde{\frak{a%
}}}^{\nu }$ be the branching of $L^{\mu }$ with respect to $\widetilde{\frak{%
a}}$. Then the branching coefficients $b_{\nu }^{\left( \mu \right) }$
define the generalized resolution (\ref{resolution sequence}) of $L^{\mu }$
with respect to $\frak{a}_{\perp }$.
\end{corollary}

\begin{proof}
Let $\alpha $ be the simple root of $A_{1}$. Use the Weyl transformations
to identify it with some simple root of $\frak{g}$, say $\alpha _{1}$.
Construct the singular element for the module $L_{\frak{g}\downarrow
\widetilde{\frak{a}}}^{\mu }$, i.e. the $\Psi _{\widetilde{\frak{a}}%
}^{\left( L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }\right)
}=\sum_{\nu \in P_{\widetilde{\frak{a}}}^{+},b_{\nu }^{\left( \mu \right)
}>0}b_{\nu }^{\left( \mu \right) }\Psi _{\widetilde{\frak{a}}}^{\left( \nu
\right) }$ , and decompose it $\Psi _{\widetilde{\frak{a}}}^{\left( L_{\frak{%
g}\downarrow \widetilde{\frak{a}}}^{\mu }\right) }=k_{\xi }^{\left( \mu
\right) }e^{\xi }$. In our case the representatives $u$ in the
recurrent relation (\ref{recurrent rel}) are uniquely determined by the weight $\xi $:
\begin{equation*}
\epsilon (u\left( \xi \right) )\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{%
\frak{a}_{\perp }}\left( u\left( \xi \right) \right) }\right) =-s\left(
\gamma _{0}\right) k_{\xi }^{\left( \mu \right) }-\sum_{\gamma \in \Gamma _{%
\widetilde{\frak{a}}\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right)
k_{\xi +\gamma }^{\left( \mu \right) }.
\end{equation*}
We have
\begin{equation*}
\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\left(
\xi \right) \right) }\right) =\left| s\left( \gamma _{0}\right) k_{\xi
}^{\left( \mu \right) }+\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}%
\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma
}^{\left( \mu \right) }\right|
\end{equation*}
and
\begin{equation*}
\mu _{\frak{a}_{\perp }}\left( u\left( \xi \right) \right) =\frac{1}{2}%
\left( \dim \left( L_{A_{1}}^{\mu \left( \xi \right) }\right) -1\right)
\alpha _{1}
\end{equation*}
The set of generalized Verma modules $e^{\xi +\mathcal{D}%
_{\frak{a}_{\perp }}}\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
u\left( \xi \right) \right) }$ is thus fixed:
\begin{equation*}
\left\{ e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }\mathrm{ch}%
M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }|u\in U\right\} .
\end{equation*}
Classifying these modules according to the length of $u$
we get the components (\ref{Verma elements sequence}) of the resolution (\ref{resolution sequence}).
\end{proof}

\section{Conclusions}

\label{sec:conclusions}

In \cite{2010arXiv1007.0318L} it was demonstrated that the injection fan
recursive mechanism works also for special injections. It must be mentioned
that in this case the Weyl-Verma decompositions can also be obtained. The
resolutions corresponding to special subalgebras describe the relations
between the projections of characters of the initial module and the generalized
Verma modules with highest weights in the subspace of $h^*$.

Consider the situation where the simple roots are prescribed by some
external factors (originating in physical applications conditions, for
example). In this case the orthogonal partner cannot be generated by simple
root vectors only. The elements $\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta
^{+}\setminus \Delta _{I}^{+}}\frak{g}_{\eta }$ do not form a subalgebra in $%
\mathfrak{g}$ because some nonsimple roots are lost in $\Delta ^{+}\setminus
\Delta _{I}^{+}$. It is important to indicate that in this case the
Weyl-Verma formula still exists. In it the generalized Verma modules
correspond to the contractions \cite{Doebner1967Melsheimer} of the algebra $%
\frak{n}^{+}$ and the Weyl-Verma relations describe the decomposition of
the representation space of $L^{\mu}$ into the set of generalized Verma
modules of contracted algebra $U\left(\frak{n}_c^{+}\right)$. The weight
vectors are formed by the PBW-basis of $U\left(\frak{n}_c^{+}\right)$ and of
$U\left( \mathfrak{a}_{\bot} \right)$. To consider such space as a $%
\mathfrak{g}$-module we must perform the deformation \cite
{Nijenhuis1966Richardson} of the algebra $\frak{n}_c^{+}$ (and thus restore the
initial composition law). The space survives and after such a deformation
the initial algebra generators will act properly on it.

\section{Acknowledgments}

The authors express their sincere gratitude to all those who prepared and
performed the III International Conference "Models in Quantum Field Theory -
2010" dedicated to 70-th anniversary of A. N. Vassiliev.

The work was supported in part by the RFFI grant N 09-01-00504 and by the Chebyshev Laboratory
(Department of Mathematics and Mechanics, Saint-Petersburg State
University) under the grant 11.G34.31.2006 of the Government of the
Russian Federation.

\bibliographystyle{plain}
\bibliography{article-ru}
{}

\end{document}

### 2011-02-10 AffineLieAlgebras/MQFT2010/article.tex
arXiv version (1102.1702v1) added, Russian translation for TMPh started

--- 2010-12-17 AffineLieAlgebras/MQFT2010/article.tex
@@
-%\usepackage{ucs}
-%\usepackage{pb-diagram}
-%\usepackage{epstopdf}
-%\usepackage{verbatim}
-%\newenvironment{comment}
-%{\par\noindent{\bf TODO}\\}
-%{\\\hfill$\scriptstyle\blacksquare$\par}
-
 \documentclass[12pt]{article}
@@
 
-%TCIDATA{OutputFilter=Latex.dll}
-%TCIDATA{LastRevised=Wed Dec 15 21:36:06 2010}
-%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
-%TCIDATA{CSTFile=article.cst}
-
 \newtheorem{statement}{Statement}
@@
 \newtheorem{mynote}{Note}[section]
-%\newtheorem{proof}{Proof}
 \theoremstyle{definition}
@@
 
-\title{Recursive properties of branching and Weyl-Verma formulas}
-\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
+\title{Recursive properties of branching and BGG resolution}
+\author{V D Lyakhovsky$^1$ and A A Nazarov$^{2,3}$\\
+{\small $^1$ Theoretical Department, SPb State University}\\
+{\small 198904, Sankt-Petersburg, Russia}\\
+{\small e-mail: lyakh1507@nm.ru}\\
+{\small $^2$ Theoretical Department, SPb State University}\\
+{\small 198904, Sankt-Petersburg, Russia}\\
+{\small$^{3}$ Chebyshev Laboratory,}\\
+{\small Department of Mathematics and Mechanics, SPb State University}\\
+{\small 199178, Saint-Petersburg, Russia}\\
+{\small email: antonnaz@gmail.com}}
 
@@
 \begin{abstract}
-Recurrent relations for branching coefficients are based on a special type of
-singular element decomposition. We show that this decomposition can be used to
-construct the parabolic Verma modules and finally to obtain the generalized
-Weyl-Verma formulas for characters.
-These Weyl-Verma formulas explicitly exhibit how branching and the generalized
-BGG-resolution properties are connected.
+Recurrent relations for branching coefficients are based on a special type
+of singular element decomposition. We show that this decomposition can be
+used to construct the parabolic Verma modules and finally to obtain the
+generalized Weyl-Verma formulas for characters. We demonstrate how branching coefficients can determine the generalized BGG resolution sequence.
 \end{abstract}
@@
 
-The resolution of the irreducible modules in terms of infinite-dimensional ones is important for the
-theory of integrable spin chains \cite{derk1008}. In the Baxter $\mathcal{Q}$-operator approach the generic transfer
+The resolution of irreducible modules in terms of infinite-dimensional ones is important for the
+theory of integrable spin chains \cite{derk1008}. In the Baxter $\mathcal{Q}$-operator approach \cite{derk09} the generic transfer
 matrices corresponding to the (generalized) Verma modules are factorized into the product of Baxter
-operator. Then the resolution allows to calculate the transfer matrices for finite-dimensional
+operators. The resolution allows to calculate the transfer matrices for finite-dimensional
 auxiliary spaces.
@@
 {2010arXiv1007.0318L} (similar to the one used in \cite{ilyin812pbc} for
-maximal embeddings). We consider the subalgebra $\af$ together with its
+maximal embeddings). We consider the subalgebra $\af \hookrightarrow \gf$ together with its
 counterpart $\afb$ ''orthogonal'' to $\af$ with respect to
@@
 \frak{h}_{\afb}\oplus \frak{h}_{\perp }$. For any reductive
-algebra $\af$ the subalgebra $\afb\hookrightarrow \gf$
+subalgebra $\af$ the subalgebra $\afb\hookrightarrow \gf$
 is regular and reductive. For a highest weight integrable module $%
@@
 \mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite
-{humphreys1997introduction}) the Weyl denominator $\Psi _{\af_{\bot
-}}^{\left( 0\right) }$ for the orthogonal subalgebra and the projection $%
-\Psi _{\left( \af,\af_{\bot }\right) }^{\left( \mu \right) }=\pi _{%
-\af}\frac{\Psi _{\gf}^{\left( \mu \right) }}{\Psi _{\af_{\bot
-}}^{\left( 0\right) }}$. It is shown that the element $\Psi _{\gf%
+{humphreys1997introduction}) and the Weyl denominator $\Psi _{\af_{\bot
+}}^{\left( 0\right) }$ for the orthogonal partner. It is shown that the element $\Psi _{\gf%
 }^{\left( \mu \right) }$ can be decomposed into a combination of Weyl
@@
 \mathfrak{a}_{\bot}}^{+}$. This decomposition provides the possibility to
-construct the set of highest weight modules $L_{\widetilde{\afb}%
-}^{\mu _{\widetilde{\afb}}}$. When the injection \ $\af%
+construct the set of highest weight modules $L_{\afb}%
+^{\mu _{\afb}}$. When the injection \ $\af%
 _{\bot }\hookrightarrow \gf$ \ satisfies the ''standard parabolic''
 conditions these modules give rise to the parabolic Verma modules $M_{\left(
-\widetilde{\afb}\hookrightarrow \gf\right) }^{\mu _{%
-\widetilde{\afb}}}$ so that the initial character $ch\left(
+\afb \hookrightarrow \gf\right) }^{\mu _{%
+\afb}}$ so that the initial character $ch\left(
 L^{\mu }\right) $ is finally decomposed into the alternating sum of such. On
 the other hand when the parabolic conditions are violated the construction
-survives and exhibits a decomposition with respect to a set of Verma
+survives and exhibits a decomposition with respect to a set of generalized Verma
 modules $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
-\widetilde{\afb}}}$. In such a situation the algebra $%
+\widetilde{\afb}}}$ where $%
 \widetilde{\frak{b}_{\perp }}$ is not a subalgebra in $\gf$ but a
@@
 Some general properties of the proposed decompositions are formulated in
-terms of a specific element $\Gamma _{\af\rightarrow \gf}$ of the
-group algebra $\mathcal{E}\left( \gf\right) $ called ''the injection
-fan''. Using this tool the simple and explicit algorithm for branching
-coefficients computations applicable for an arbitrary (maximal or
-nonmaximal) subalgebras of finite-dimensional or affine Lie algebras was
-obtained in \cite{2010arXiv1007.0318L}.
+terms of a specific formal element $\Gamma _{\af\rightarrow \gf}$  called ''the injection fan''. Using this tool a simple and explicit algorithm for branching
+rules applicable for an arbitrary (maximal or
+nonmaximal) subalgebra in affine Lie algebras was
+proposed in \cite{2010arXiv1007.0318L}.
 
-Possible further developments are presented in Section \ref{sec:conclusions}.
+Possible further developments are discussed in Section \ref{sec:conclusions}.
 
@@
 
-Consider Lie algebras (affine Lie algebras) $\gf$ and $\af$ and an
-injection $\af\hookrightarrow \gf$ such that $\af$ is a
+Consider Lie algebras (affine Lie algebras) $\frak{g}$ and $\frak{a}$ and an
+injection $\frak{a}\hookrightarrow \frak{g}$ such that $\frak{a}$ is a
 reductive subalgebra $\frak{a\subset g}$ with correlated root spaces: $\frak{%
-h}_{\af}^{\ast }\subset \frak{h}_{\gf}^{\ast }$. We use the
+h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g}}^{\ast }$. We use the
 following notations:
 
-$\frak{g=n}^{-}+\frak{b}+\frak{n}^{+}$ --- the Cartan decomposition;
+$\frak{g=n}^{-}+\frak{h}+\frak{n}^{+}$ --- the Cartan decomposition;
 
-$r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\gf$ $%
-\left( \mathrm{{resp. }\af}\right) $ ;
+$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
+\left( \mathrm{{resp. }\frak{a}}\right) $ ;
 
-$\Delta $ $\left( \Delta _{\af}\right) $--- the root system; $\Delta
-^{+} $ $\left( \mathrm{{resp. }\Delta _{\af}^{+}}\right) $--- the
-positive root system (of $\gf$ and $\af$ respectively);
+$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
+^{+} $ $\left( \mathrm{{resp. }\Delta _{\frak{a}}^{+}}\right) $--- the
+positive root system (of $\frak{g}$ and $\frak{a}$ respectively);
 
-$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\af}\left(
+$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
 \alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $%
-\Delta $ (resp. in $\left( \Delta _{\af}\right) $);
+\Delta $ (resp. in $\left( \Delta _{\frak{a}}\right) $);
 
-$S\quad \left( S_{\af}\right) $ --- the system of simple roots (of $%
-\gf$ and $\af$ respectively);
+$S\quad \left( S_{\frak{a}}\right) $ --- the set of simple roots (for
+$\gf$ and $\af$ respectively);
 
-$\alpha _{i}$ , $\left( \alpha _{\left( \af\right) j}\right) $ --- the $%
-i$-th (resp. $j$-th) basic root for $\gf$ $\left( \mathrm{{resp.}\frak{a%
-}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
+$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
+i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a%
+}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
 
-$\delta $ --- the imaginary root of $\gf$ (and of $\af$ if any);
+$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
+}\right) $-- the simple coroot for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a}%
+}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
 
-$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \af\right) j}^{\vee
-}\right) $--- the basic coroot for $\gf$ $\left( \mathrm{{resp.}\af%
-}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
+$W$ , $\left( W_{\frak{a}}\right) $--- the Weyl group;
 
-$W$ , $\left( W_{\af}\right) $--- the corresponding Weyl group;
+$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
 
-$C$ , $\left( C_{\af}\right) $--- the fundamental Weyl chamber;
-
-$\bar{C}, \left(\bar{C_{\af}}\right)$ --- the closure of the
+$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
 fundamental Weyl chamber;
@@
 
-$\rho $\ , $\left( \rho _{\af}\right) $\ --- the Weyl vector;
+$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
 
-$L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
-of $\gf$ with the highest weight $\mu $\ ; (resp. integrable $\af$
--module with the highest weight $\nu $ );
+$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
+of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\af$-module
+with the highest weight $\nu $);
 
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\af}^{\nu }\right) $ ---
-the weight diagram of $L^{\mu }$ (resp. ${}L_{\af}^{\nu }$ );
+$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
+the weight diagram of $L^{\mu }$ (resp. ${}L_{\frak{a}}^{\nu }$ );
 
-$P$ (resp. $P_{\af} $) \ --- the weight lattice;
+$P$ (resp. $P_{\frak{a}} $) \ --- the weight lattice;
 
-$P^{+}$ (resp. $P_{\af}^{+} $) \ --- the dominant weight lattice;
+$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight lattice;
 
-$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
+$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\zeta }^{\left( \nu \right)
 }\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
-resp. }\in P_{\af}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
-L_{\af}^{\nu } $);
+resp. }\in P_{\frak{a}}}\right) $ in $L^{\mu }$, (resp. in $\zeta \in
+L_{\frak{a}}^{\nu } $);
 
-$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\af}^{\nu
-}\right) $)--- the formal character of $L^{\mu }$ (resp. $L_{\af}^{\nu
+$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $)--- the formal character of $L^{\mu }$ (resp. of $L_{\frak{a}}^{\nu
 } $);
@@
 $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
-mult}\left( \alpha \right) }}\quad $ (resp. $R_{\af}:=\prod_{\alpha \in
-\Delta _{\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af%
+mult}\left( \alpha \right) }}\quad $ (resp. $R_{\frak{a}}:=\prod_{\alpha \in
+\Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}%
 }\left( \alpha \right) } $)--- the Weyl denominator.
 
-\section{Orthogonal subalgebra and singular elements}
+\section{Orthogonal subalgebra and\\ singular elements}
 
@@
 In this section we shall show how the recurrent approach to branching
-problem leads naturally to a presentation of the formal character in terms
-of parabolic (generalized) Verma modules. Consider a reductive Lie algebra $%
-\gf$ and its reductive subalgebra $\af\subset \gf$. Let $%
-L^{\mu} $ be the highest weight integrable module of $\gf$, $\mu \in
-P^{+}$. Let $L^{\mu }$ be completely reducible with respect to $\af$,
+problem leads naturally to a presentation of a formal character of
+$\frak{g}$-module in terms characters corresponding to a set
+of parabolic (generalized) Verma modules. Consider a reductive
+Lie algebra $\frak{g}$ and its reductive subalgebra $\frak{a}\subset \frak{g}$.
+Let $L^{\mu} $ be the highest weight integrable module of $\frak{g}$, $\mu \in
+P^{+}$. Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
 \begin{equation*}
-L_{\gf\downarrow \af}^{\mu }=\bigoplus\limits_{\nu \in P_{\af%
-}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
+L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
 \end{equation*}
-Using the projection operator $\pi _{\af}$ (to the weight space $\frak{%
-h_{a}}^{\ast }$) one can rewrite this decomposition in terms of formal
+Using the projection operator $\pi _{\frak{a}}$ (to the weight space $\frak{%
+h_{a}}^{\ast }$) one can write this decomposition in terms of formal
 characters:
 \begin{equation}
-\pi _{\af}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\af%
-}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\af}^{\nu }\right) .
+\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
 \label{branching1}
 \end{equation}
-The module $L^{\mu }$ has the BGG-resolution (see \cite
+The module $L^{\mu }$ has the BGG resolution (see \cite
 {bernstein1976category,bernstein1975differential,bernstein1971structure} and
@@
 
-Let $\frak{h}_{\af}$ be a Cartan subalgebra of $\mathfrak{g}$. For $%
-\mathfrak{a}\hookrightarrow \gf$ introduce the ''orthogonal partner'' $%
-\mathfrak{a}_{\bot }\hookrightarrow \gf$ .
+Let $\frak{h}_{\frak{a}}$ be a Cartan subalgebra of $\mathfrak{g}$. For $%
+\mathfrak{a}\hookrightarrow \frak{g}$ introduce the ''orthogonal partner'' $%
+\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$ .
 
-Consider the root subspace $\frak{h}_{\perp \af}^{\ast }$ orthogonal to
-$\af$,
+Consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to
+$\frak{a}$,
 \begin{equation*}
-\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
-h\in \frak{h}_{\af};\eta \left( h\right) =0\right\} ,
+\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
+h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} ,
 \end{equation*}
-and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
-to $\af$,
+and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
+to $\frak{a}$,
 \begin{eqnarray}
-\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
-h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
+\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
+h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
 \label{delta a ort} \\
-\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
-}^{+}|\forall h\in \frak{h}_{\af};\beta ^{+}\left( h\right) =0\right\} .
+\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
+}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
 \notag
 \end{eqnarray}
-Let $W_{\afb}$ be the subgroup of $W$ generated by the
-reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\afb}^{+}$ . The subsystem $\Delta _{\afb}$ determines the
-subalgebra $\afb$ with the Cartan subalgebra $\frak{h}_{\af%
+Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
+reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\frak{a}_{\perp
+}}^{+}$. The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
+subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
 _{\perp }}$. Let
 \begin{equation*}
-\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
-}|\forall h\in \frak{h}_{\af\oplus \afb};\eta \left(
+\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
+}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
 h\right) =0\right\}
 \end{equation*}
-so that $\gf$ has the subalgebras
-\begin{eqnarray*}
-\widetilde{\afb} &:&=\afb\oplus \frak{h}_{\perp }
-\\
-\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
-\end{eqnarray*}
+so that $\frak{g}$ has the subalgebras
+\begin{eqnarray}
+\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\qquad
+\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
+\end{eqnarray}
 Notice that $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ in general is not a
-subalgebra of $\mathfrak{g}$
+subalgebra in $\mathfrak{g}$.
 
@@
 \begin{equation}
-\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\afb}\oplus
-\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
-\afb}=\frak{\frak{h}_{\widetilde{\afb}}}\oplus
-\frak{h}_{\af}.
+\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
+\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
+\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
+\frak{h}_{\frak{a}}.
 \end{equation}
-For the subalgebras $\af$ and $\afb$ consider the
-corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\afb} $ . Form the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
-D}_{\afb}$ of the injection:
+For $\frak{a}$ and $\frak{a}_{\perp }$ consider the
+corresponding Weyl vectors, $\rho _{\frak{a}}$ and $\rho _{\frak{a}_{\perp
+}} $. Form the so called ''defects'' $\mathcal{D}_{\frak{a}}$ and $\mathcal{%
+D}_{\frak{a}_{\perp }}$ of the injection:
 \begin{equation}
-\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
-\end{equation}
-\begin{equation}
-\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
+\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho , \qquad
+\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
 _{\perp }}\rho .  \label{defect ort}
@@
 
-For the highest weight $\mu \in P^{+}$ consider the linked weights $\left\{
-\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections to
-$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
-\mathcal{D}_{\afb}$:
+For $\mu \in P^{+}$ consider the linked weights $\left\{
+\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $. Consider the projections to
+$h_{\frak{a}_{\perp }}^{\ast }$ additionally shifted by the defect $-%
+\mathcal{D}_{\frak{a}_{\perp }}$:
 \begin{equation*}
-\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
-w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
+\mu _{\frak{a}_{\perp }}\left( w\right) :=\pi _{\frak{a}_{\perp }}\left[
+w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad w\in W.
 \end{equation*}
-For $\mu \in P^{+}$ among the weights $\left\{ \mu _{\afb}\left( w\right) |w\in W\right\} $ one can always choose those located in
-the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
-set of representatives $u$ for the classes $W/W_{\afb}$ such
+Among the weights $\left\{ \mu _{\frak{a}_{\perp
+}}\left( w\right) |w\in W\right\} $ one can always choose those located in
+the fundamental chamber $\overline{C_{\frak{a}_{\perp }}}$. Let $U$ be the
+set of representatives $u$ for the classes $W/W_{\frak{a}_{\perp }}$ such
 that
@@
 \begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
-\overline{C_{\afb}}\right\} \quad .  \label{U-def}
+U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
+\overline{C_{\frak{a}_{\perp }}}\right\} \quad .  \label{U-def}
 \end{equation}
-Thus we can select the following subsets:
+Thus we can form the subsets:
 \begin{equation}
 \mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
-\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
+\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}%
 _{\perp }},\quad u\in U,  \label{mu-a}
@@
 \begin{equation}
-\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
+\mu _{\frak{a}_{\perp }}\left( u\right) :=\pi _{\frak{a}_{\perp }}\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U.
 \label{mu-a-tilda}
@@
 
-Note that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
-since it is built on the roots of the algebra $\mathfrak{g}$.
+Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
+since it is built on a subset of roots of the algebra $\mathfrak{g}$.
 
@@
 \left( L^{\mu }\right) $ can be written in terms of singular elements \cite
-{humphreys1997introduction}
+{humphreys1997introduction},
 \begin{equation*}
@@
 \end{equation}
-The same is true for the submodules $\mathrm{ch}\left( L_{\af}^{\nu
+The same is true for the submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
 }\right) $ in (\ref{branching1})
 \begin{equation*}
-\mathrm{ch}\left( L_{\af}^{\nu }\right) =\frac{\Psi _{\af}^{\left(
-\nu \right) }}{\Psi _{\af}^{\left( 0\right) }}=\frac{\Psi _{\af%
-}^{\left( \nu \right) }}{R_{\af}},
+\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
+\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
+}^{\left( \nu \right) }}{R_{\frak{a}}},
 \end{equation*}
@@
 \begin{equation*}
-\Psi _{\af}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\af%
-}}\epsilon (w)e^{w(\nu +\rho _{_{\af}})-\rho _{_{\af}}}.
+\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
+}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
 \end{equation*}
@@
 we get the relation connecting the singular elements $\Psi ^{\left( \mu
-\right) }$ and $\Psi _{\af}^{\left( \nu \right) }$ :
+\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
 \begin{eqnarray}
-\pi _{\af}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
+\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
 )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
-(\alpha )}}\right) &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{%
-\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{\af})-\rho _{%
-\af}}}{\prod_{\beta \in \Delta _{\af}^{+}}(1-e^{-\beta })^{\mathrm{%
-mult}_{\af}(\beta )}},  \notag  \label{eq:4} \\
-\pi _{\af}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
-&=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\af%
-}^{\left( \nu \right) }}{R_{\af}}.
+(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
+\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
+\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
+mult}_{\frak{a}}(\beta )}},  \notag  \label{eq:4} \\
+\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
+&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
+}^{\left( \nu \right) }}{R_{\frak{a}}}.
 \end{eqnarray}
@@
 Now we shall perform a decomposition of the singular element $\Psi ^{\left(
-\mu \right) }$ in terms of singular elements of the orthogonal subalgebra
+\mu \right) }$ in terms of singular elements of the orthogonal partner
 modules:
@@
 \begin{lemma}
-Let $\af_{\bot }$ be the orthogonal partner of a reductive subalgebra $%
-\af\hookrightarrow \gf$ with $\frak{h}=\frak{\frak{h}_{\af}}%
-\oplus \frak{h}_{\afb}\oplus \frak{h}_{\perp }$, $\widetilde{%
-\afb}=\afb\oplus \frak{h}_{\perp }$ and $%
-\widetilde{\af}=\af\oplus \frak{h}_{\perp }$.
+Let $\frak{a}_{\bot }$ be the orthogonal partner of a reductive subalgebra $%
+\frak{a}\hookrightarrow \frak{g}$ with $\frak{h}=\frak{\frak{h}_{\frak{a}}}%
+\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$, $\widetilde{%
+\frak{a}_{\perp }}=\frak{a}_{\perp }\oplus \frak{h}_{\perp }$ and $%
+\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$.
 
@@
 Then the element $\Psi ^{\left( \mu \right) }$ can be decomposed into the
-sum over $u\in U$ (see (\ref{U-def})) of singular elements $\Psi _{\af%
-_{\perp }}^{\mu _{\afb}\left( u\right) }$ with the coefficients
+sum over $u\in U$ (see (\ref{U-def})) of singular elements $\Psi _{\frak{a}%
+_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ with the coefficients
 $\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
@@
 \Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\widetilde{%
-\mathfrak{a}}}\left( u\right) }\Psi _{\afb}^{\mu _{\af%
+\mathfrak{a}}}\left( u\right) }\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}%
 _{\perp }}\left( u\right) }.  \label{sing decomp main}
 \end{equation}
+\label{Psi-decomp-lemma}
 \end{lemma}
@@
 \begin{proof}
-With $u\in U$ and $v\in W_{\af_{\bot }}$ perform the decomposition
+Let
 \[
 u(\mu +\rho )=\pi _{\left( \aft\right) }u(\mu +\rho )+\pi _{\left(
-\afb\right) }u(\mu +\rho )
+\frak{a}_{\perp }\right) }u(\mu +\rho )
 \]
-for the singular weight $vu(\mu +\rho )-\rho $:
+with $u\in U$. For any $v\in W_{\frak{a}_{\bot }}$ consider
+the singular weight $vu(\mu +\rho )-\rho $ and perform the decomposition:
 \begin{equation}
 \begin{array}{lcl}
-vu(\mu +\rho )-\rho  & = & \pi _{\left( \af\right) }\left( u(\mu +\rho
-)\right) -\rho +\rho _{\afb}
+vu(\mu +\rho )-\rho  & = & \pi _{\left( \frak{a}\right) }\left( u(\mu +\rho
+)\right) -\rho +\rho _{\frak{a}_{\perp }}
 \\
 &  & +\ v\left( \pi _{\left( \aft_{\perp }\right) }u(\mu
-+\rho )-\rho _{\afb}+\rho _{\afb}\right) -\rho _{%
-\afb} .
++\rho )-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{%
+\frak{a}_{\perp }} .
 \end{array}
@@
 \end{equation}
-Use the defect $\mathcal{D}_{\af_{\bot }}$ (\ref{defect ort}) to
+Use the defect $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}) to
 simplify the first line in (\ref{sing-decomp-1}):
@@
 \pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
-\afb}= \\
+\frak{a}_{\perp }}= \\
 \pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\pi _{\aft%
-}\rho -\pi _{\af_{\bot }}\rho +\rho _{\af_{\bot }}= \\
+}\rho -\pi _{\af_{\bot }}\rho +\rho _{\frak{a}_{\bot }}= \\
 =\pi _{\left( \aft\right) }\left( u(\mu +\rho )-\rho \right) +\mathcal{D}%
-_{\af_{\bot }},
+_{\frak{a}_{\bot }},
 \end{array}
@@
 \begin{array}{c}
-v\left( \pi _{\left( \afb\right) }u(\mu +\rho
-)-\rho _{\afb}+\rho _{\afb}\right) -\rho _{\af%
+v\left( \pi _{\left( \frak{a}_{\perp }\right) }u(\mu +\rho
+)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}%
 _{\perp }}= \\
-v\left( \pi _{\left( \af_{\bot }\right) }u(\mu +\rho )-%
-\mathcal{D}_{\af_{\bot }}-\pi _{\left( \af_{\bot }\right) }\rho
-+\rho _{\af_{\bot }}\right)
--\rho _{\af_{\bot }}= \\
-=v\left( \pi _{\left( \af_{\bot }\right) }\left[ u(\mu
-+\rho )-\rho \right] -\mathcal{D}_{\af_{\bot }}+\rho _{\af_{\bot
-}}\right) -\rho _{\af_{\bot }}.
+v\left( \pi _{\left( \frak{a}_{\bot }\right) }u(\mu +\rho )-%
+\mathcal{D}_{\frak{a}_{\bot }}-\pi _{\left( \frak{a}_{\bot }\right) }\rho
++\rho _{\frak{a}_{\bot }}\right)
+-\rho _{\frak{a}_{\bot }}= \\
+=v\left( \pi _{\left( \frak{a}_{\bot }\right) }\left[ u(\mu
++\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\bot }}+\rho _{\frak{a}_{\bot
+}}\right) -\rho _{\frak{a}_{\bot }}.
 \end{array}
 \]
-These expressions provide the desired decomposition of the singular element $%
-\Psi ^{\mu }$ in terms of singular elements $\Psi _{\af%
-_{\perp }}^{\eta }$ of the $\afb$-modules $L_{%
-\afb}^{\eta }$:
+This provides the desired decomposition of the singular element $%
+\Psi ^{\mu }$ in terms of singular elements $\Psi _{\frak{a}%
+_{\perp }}^{\eta }$ of the $\frak{a}_{\perp }$-modules $L_{%
+\frak{a}_{\perp }}^{\eta }$:
 \begin{equation}
 \begin{array}{l}
-\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\afb}}\epsilon
+\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
 (v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
 =\sum_{u\in U}\epsilon (u)e^{\pi _{\aft}\left[ u(\mu +\rho )-\rho \right]
-+\mathcal{D}_{\afb}}\sum_{v\in W_{\afb}}\epsilon
-(v)e^{v\left( \pi _{\left( \afb\right) }\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb}+\rho _{\af%
-_{\perp }}\right) -\rho _{\afb}}= \\
-=\sum_{u\in U}\;\epsilon (u)\Psi _{\afb}^{\pi
-_{\left( \afb\right) }\left[ u(\mu +\rho )-\rho
-\right] -\mathcal{D}_{\afb}}e^{\pi _{\left( \aft\right) }%
-\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}}.
++\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{\left( \frak{a}_{\perp }\right) }\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}+\rho _{\frak{a}%
+_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
+=\sum_{u\in U}\;\epsilon (u)\Psi _{\af_{\perp }}^{\pi
+_{\left( \frak{a}_{\perp }\right) }\left[ u(\mu +\rho )-\rho
+\right] -\mathcal{D}_{\frak{a}_{\perp }}}e^{\pi _{\left( \aft\right) }%
+\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}.
 \end{array}
@@
 This relation can be considered as a generalized form of the Weyl formula
-for the singular element $\Psi _{\gf}^{\mu }$: the vectors $\mu _{%
+for the singular element $\Psi _{\frak{g}}^{\mu }$: the vectors $\mu _{%
 \widetilde{\mathfrak{a}}}\left( u\right) $ play the role of singular weights
 while the alternating factors $\epsilon (u)$ are extended to $\epsilon
-(u)\Psi _{\afb}^{\mu _{\afb}\left( u\right) }$. In
-fact when $\frak{a=g}$ both $\afb$and $\frak{h}_{\perp }$are
-zeros, $U=W$, and\ the original Weyl formula is reobtained via the
-trivilization of the singular elements: $\epsilon (u)\Psi _{\afb}^{\mu _{\afb}\left( u\right) }=\epsilon (u)$. In the opposite
-limit when $\frak{a=0}$, $\Delta _{\afb}=\Delta _{\gf}$, $%
-\frak{h}_{\perp }^{\ast }=0$, $\afb=\gf$, $\mathcal{D}_{%
-\afb}=0$, $U=W/W_{\afb}=e$ and $\Psi ^{\mu }$ is
-again reobtained, now via the trivilization of the set of vectors: $\mu _{%
-\af}\left( e\right) =0$.
+(u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$. In
+fact when $\frak{a=g}$ both $\frak{a}_{\perp }$and $\frak{h}_{\perp }$are
+zeros, $U=W$, and\ the original Weyl formula is reobtained so far as the singular elements $\epsilon (u)\Psi _{\frak{a}_{\perp
+}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\epsilon (u)$ become trivial.
+ In the opposite
+limit when $\frak{a=0}$, $\Delta _{\frak{a}_{\perp }}=\Delta _{\frak{g}}$, $%
+\frak{h}_{\perp }^{\ast }=0$, $\frak{a}_{\perp }=\frak{g}$, $\mathcal{D}_{%
+\frak{a}_{\perp }}=0$ and $U=W/W_{\frak{a}_{\perp }}=e$ the singular element
+ $\Psi ^{\mu }$ is again reobtained, now via the trivilization of the set of
+ vectors $\mu _{\af}\left( e\right) =0$.
 \end{remark}
 
-\subsection{Reduction of Verma modules}
+\begin{remark}
 
-In \cite{2010arXiv1007.0318L} the decomposition analogous to (\ref{singular main}) was
+In \cite
+{2010arXiv1007.0318L} the decomposition analogous to (\ref{singular main}) was
 used to construct the recurrent relations for branching coefficients $k_{\xi
-}^{\left( \mu \right) }$ corresponding to the injection $\af%
-\hookrightarrow \gf$:
+}^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
+\hookrightarrow \frak{g}$:
 \begin{equation}
@@
 k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
-_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{\af%
-}(u(\mu +\rho )-\rho )}+\right.  \\
-\left. +\sum_{\gamma \in \Gamma _{\af\rightarrow \gf}}s\left(
-\gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right) }\right) .
+\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
+\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right.  \\
+\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
+}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
+}\right) .
 \end{array}
@@
 \end{equation}
-The recursion is goverened by the set $\Gamma _{\af\rightarrow \gf}
-$ called the injection fan. The later is defined as the carrier set $\left\{
-\xi \right\} _{\af\rightarrow \gf}$ for the coefficient function $%
-s(\xi )$
+The recursion is goverened by the set $\Gamma _{\widetilde{\frak{a}}%
+\rightarrow \frak{g}}$ called the injection fan. The latter is defined by the
+carrier set $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the
+coefficient function $s(\xi )$
 \begin{equation*}
-\left\{ \xi \right\} _{\af\rightarrow \gf}:=\left\{ \xi \in P_{%
-\af}|s(\xi )\neq 0\right\}
+\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{g}}:=\left\{
+\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\}
 \end{equation*}
@@
 \begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left( 1-e^{-\pi
-_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
-}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
-)e^{-\gamma };\quad
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
+_{\widetilde{\frak{a}}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
+_{\frak{a}}(\pi _{\widetilde{\frak{a}}}\alpha )}=-\sum_{\gamma \in P_{%
+\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma };\quad
 \end{equation}
-The weights in $\left\{ \xi \right\} _{\af\rightarrow \gf}$ are to
-be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi \right\} $
--- and the zero element is to be eliminated:
+The weights in $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
+g}}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
+\right\} $ -- and the zero element is to be eliminated:
 \begin{equation}
-\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in
-\left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
+\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}=\left\{ \xi -\gamma
+_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
 \end{equation}
@@
 The recursion relation (\ref{recurrent rel}) was originally used to
-described branchings for integrable modules. There exists an important class
-of modules that also can be reduced with the help of an injection fan --
-these are the Verma modules.
-
-For a regular embedding $\af\hookrightarrow \gf$ we have the
-corresponding embedding for the root systems $\Delta _{\mathfrak{a}%
-}^{+}\hookrightarrow \Delta ^{+}$ . Moreover, in this case it is reasonable
-to enlarge the subalgebra $\af$ and consider $\frak{b}=\af\oplus
-\frak{h}_{\perp \af}$ . In this case the weights of a $\frak{b}$-module
-can be considered in $\frak{h}^{\ast }$ . Verma module is decomposable for
-any highest weight:
-\begin{equation}
-\mathrm{ch}M^{\mu }=\sum_{\nu }b_{\nu }^{(\mu )}\mathrm{ch}M_{\frak{b}}^{\nu
-}.
-\end{equation}
-Verma module $\mathrm{ch}M^{\mu }$ have one singular weight $\mu $ with the
-multiplicity ($+1$). The Weyl groups can be considered to be trivial. The
-orthogonal partner $\afb$ is also trivial and the recursion
-relation is simplified:
-\begin{equation*}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }%
-\;\left( \delta _{\xi -\gamma _{0},\mu }+\sum_{\gamma \in \Gamma _{\af%
-\rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma
-}^{\left( \mu \right) }\right) .
-\end{equation*}
-
-\begin{remark}
-Notice that inside the main Weyl chamber branching coefficients $k_{\xi
-}^{\left( \mu \right) }$ for Verma modules reduction coincide with the
-coefficients for reduction of integrable simple modules.
+describe branchings for integrable modules. Notice that there exists an
+important class of modules that also can be reduced with the help of the
+injection fan --
+these are Verma modules.
 \end{remark}
-
-\begin{example}
-\label{example:reduct-verma-modul}
- Let $\mathfrak{g}=B_{2}$ be and consider $A_{1}=\mathfrak{a}%
-\hookrightarrow \mathfrak{g}$. There are different embeddings  $%
-A_{1}\hookrightarrow B_{2}$. Here we limit ourselves by the regular ones.
-The root system $\Delta _{B_{2}}$ consists of 8 roots. Let $%
-S_{B_{2}}=\left\{ \alpha _{1}=e_{1}-e_{2},\alpha _{2}=e_{2}\right\} $ where $%
-e_{1},e_{2}$ form the standard basis in $\mathbf{R}^{2}$. The set of the
-positive roots is $\Delta ^{+}=\left\{ \alpha _{1},\alpha _{1}+\alpha
-_{2},\alpha _{1}+2\alpha _{2},\alpha _{2}\right\} $. Each of these roots can
-be taken as the simple root of the $A_{1}-$subalgebra. Firstly  we consider
-the subalgebra $A_{1}$ with the simple root $\beta =\alpha _{1}+2\alpha _{2}$%
-. Consider the Verma module $M^{\mu }$ with the highest weight $\mu =\omega
-_{1}+2\omega _{2}=2\alpha _{1}+3\alpha _{2}$ as it is shown at Figure \ref
-{fig:B2_Verma}.
-
-\begin{figure}[h!bt]
- \noindent\centering{
-   \includegraphics[width=120mm]{B2_Verma}
-  }
- \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
-Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}
-  \label{fig:B2_Verma}
-\end{figure}
-
-The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2}
-for the regular embedding $A_{1}\rightarrow B_{2}$. Here we can
-see that the picture depends upon the embedding and looks similar to the
-Verma modules of some subalgebra.
-
-\begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=120mm]{B2_Verma_Branch4.pdf}
-  }
-  \caption{Branching of the Verma module $M^{(1,2)}$ for the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
-    Branching coefficients for Verma module of the subalgebra are shown. Dashed line indicates the
-    direction of subalgebra modules.}
- \label{fig:B2_Verma_Branch2}
-\end{figure}
-\end{example}
-In the present paper we interpret this branching coefficients as the dimensions
-of the weight subspaces of modules of contracted algebras.
 
@@
 \begin{statement}
-\bigskip For an orthogonal subalgebra $\afb$ in $\gf$
-(orthogonal partner of reductive $\af\hookrightarrow \gf$) the
+\bigskip For an orthogonal subalgebra $\frak{a}_{\perp }$ in $\frak{g}$ (an
+orthogonal partner of a reductive $\frak{a}\hookrightarrow \frak{g}$) the
 character of an integrable highest weight module $L^{\mu }$ can be presented
 as a combination (with integral coefficients) of parabolic Verma modules
-distributed by the set of weights $e^{\mu _{\aft}\left( u\right) }$:
-\begin{equation*}
+distributed by the set of weights $e^{\mu _{\widetilde{\mathfrak{a}}}\left(
+u\right) }$:
+\begin{equation}
 \mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{%
-\widetilde{\af}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\af%
-_{\perp }}\left( u\right) },
-\end{equation*}
-where $U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
-\overline{C_{\afb}}\right\} $ and $\Delta _{I}^{+}$ is
-equivalent to $\Delta _{\afb}^{+}$.
+\widetilde{\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) },  \label{gen Weyl-Verma}
+\end{equation}
+where $U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
+\overline{C_{\frak{a}_{\perp }}}\right\} $ and $I$ is such a subset of $S$ that
+$\Delta _{I}^{+}$ is
+equivalent to $\Delta _{\frak{a}_{\perp }}^{+}$.
 \end{statement}
@@
 \mathfrak{a}_{\bot }$ is regular and reductive. Consider its Weyl
-denominator $R_{\afb}:=\prod_{\alpha \in \Delta _{\af%
-_{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}%
+denominator $R_{\frak{a}_{\perp }}:=\prod_{\alpha \in \Delta _{\frak{a}%
+_{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}%
 \mathrm{\left( \alpha \right) }}$ and the element $R_{J}:=\prod_{\alpha \in
-\Delta ^{+}\setminus \Delta _{\afb}^{+}}\left( 1-e^{-\alpha
+\Delta ^{+}\setminus \Delta _{\frak{a}_{\perp }}^{+}}\left( 1-e^{-\alpha
 }\right) ^{\mathrm{mult}(\alpha )}$ as the factors in $R$: $\quad $%
 \begin{equation*}
-R=R_{J}R_{\afb}.
+R=R_{J}R_{\frak{a}_{\perp }}.
 \end{equation*}
@@
 \mathrm{ch}\left( L^{\mu }\right) &=&\left( R_{J}\right) ^{-1}\left( R_{%
-\afb}\right) ^{-1}\Psi ^{\mu }=\left( R_{J}\right)
-^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\af}}\left( u\right) }\epsilon
-(u)\left( R_{\afb}\right) ^{-1}\Psi _{\afb}^{\mu _{%
-\afb}\left( u\right) } \\
-&=&\left( R_{J}\right) ^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\af}%
-}\left( u\right) }\epsilon (u)L_{\afb}^{\mu _{\afb}\left( u\right) },
+\frak{a}_{\perp }}\right) ^{-1}\Psi ^{\mu }=\left( R_{J}\right)
+^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}}\left( u\right) }\epsilon
+(u)\left( R_{\frak{a}_{\perp }}\right) ^{-1}\Psi _{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) } \\
+&=&\left( R_{J}\right) ^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}%
+}\left( u\right) }\epsilon (u)\mathrm{ch}\left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
+}}\left( u\right) }\right),
 \end{eqnarray*}
-where $\left\{ L_{\afb}^{\mu _{\afb}\left(
-u\right) }|u\in U\right\} $ is the set of finite-dimensional $\af%
-_{\perp }$-modules with the highest weights $\mu _{\afb}\left(
-u\right) $. We are interested in nontrivial subalgebras $\af$ and
-correspondingly in nontrivial $\afb$ (the case of a trivial
-orthogonal subalgebra arise when $\af=\gf$ and was considered
-above (see Remark 1)). This means that $r_{\af}\geq 1$ and $r_{\af%
+where $\left\{ L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left(
+u\right) }|u\in U\right\} $ is the set of finite-dimensional $\frak{a}%
+_{\perp }$-modules with the highest weights $\mu _{\frak{a}_{\perp }}\left(
+u\right) $. We are interested in nontrivial subalgebras $\frak{a}$ and
+correspondingly in nontrivial $\frak{a}_{\perp }$ (the case of a trivial
+orthogonal subalgebra was considered above (see Remark 1)). This means that $r_{\frak{a}}\geq 1$ and $r_{\frak{a}%
 _{\perp }}<r$. Due to the fact that any maximal regular subalgebra has the
@@
 Dynkin scheme and the extended scheme has at most one dependent root (the
-highest root) the set of roots $\Delta _{\afb}^{+}$ is always
+highest root) the set of roots $\Delta _{\frak{a}_{\perp }}^{+}$ is always
 equivalent to the one $\Delta _{I}^{+}$ generated\ by some subset $I\subset
@@
 It follows that we can (by redefining the set $\Delta ^{+}$) identify $%
-\Delta _{\afb}^{+}$ with the subset $\Delta _{I}^{+}$ \ where $%
+\Delta _{\frak{a}_{\perp }}^{+}$ with the subset $\Delta _{I}^{+}$ \ where $%
 I\subset S$ . This allows us to introduce the elements necessary to compose
@@
 We have two sets of root
-vectors $\left\{ x_{\xi }\in \gf_{\xi }|\xi \in \Delta _{I}^{+}\right\}
-$ and $\left\{ x_{\eta }\in \gf_{\eta }|\eta \in \Delta ^{+}\setminus
-\Delta _{I}^{+}\right\} $. They generate nilpotent subalgebras of $\frak{n}%
+vectors $\left\{ x_{\xi }\in \frak{g}_{\xi }|\xi \in \Delta _{I}^{+}\right\}
+$ and $\left\{ x_{\eta }\in \frak{g}_{\eta }|\eta \in \Delta ^{+}\setminus
+\Delta _{I}^{+}\right\} $ and the corresponding nilpotent subalgebras in $\frak{n}%
 ^{+}$:
 \begin{equation*}
-\frak{n}_{I}^{+}:=\sum_{\xi \in \Delta _{I}^{+}}\gf_{\xi },\quad
-\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\gf%
+\frak{n}_{I}^{+}:=\sum_{\xi \in \Delta _{I}^{+}}\frak{g}_{\xi },\quad
+\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\frak{g}%
 _{\eta }.
@@
 \end{equation*}
-We enlarge it with the remaining Cartan generators and introduce the
-subalgebra:
+We enlarge it with the remaining Cartan generators:
 \begin{equation*}
@@
 \end{equation*}
-The semidirect product of subalgebras $\frak{l}_{I}$ and $\frak{u}_{I}^{+}$
-gives a parabolic subalgebra $\frak{p}_{I}\hookrightarrow \gf$ :
+The semidirect product of $\frak{l}_{I}$ and $\frak{u}_{I}^{+}$
+gives a parabolic subalgebra $\frak{p}_{I}\hookrightarrow \frak{g}$ :
 \begin{equation}
-\frak{p}_{I}=\frak{l}_{I}\vartriangleright \frak{u}_{I}^{+},
+\frak{p}_{I}=\frak{l}_{I}\vartriangleright \frak{u}_{I}^{+}.
 \label{paralolic subalg}
@@
 Its universal enveloping $U\left( \frak{p}_{I}\right) $ is a subalgebra in $%
-U\left( \gf\right) $. According to the obtained structure (\ref
-{paralolic subalg}) the $\frak{l}_{I}$-modules $L_{\afb}^{\mu _{%
-\afb}\left( u\right) }$ can be easily lifted to $\frak{p}_{I}$%
+U\left( \frak{g}\right) $. The $\frak{l}_{I}$-modules $L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) }$ can be easily lifted to $\frak{p}_{I}$%
 -modules using the trivial action of the nilradical $\frak{u}_{I}^{+}$. The
-latter induce $U\left( \gf\right) $-modules in a standard way:
+latter induce $U\left( \frak{g}\right) $-modules in a standard way:
 \begin{equation*}
-M_{I}^{\mu _{\afb}\left( u\right) }=U\left( \gf\right)
-\otimes _{U\left( \frak{p}_{I}\right) }L_{\afb}^{\mu _{\af%
+M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=U\left( \frak{g}\right)
+\otimes _{U\left( \frak{p}_{I}\right) }L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
 _{\perp }}\left( u\right) }.
 \end{equation*}
-According to the defenition presented in \cite{lepowsky1977generalization}
-these are the \textit{generalized Verma modules}
-generated by the highest weights $\mu _{\af%
+
+These are the \textit{generalized Verma modules}  \cite{lepowsky1977generalization}
+generated by the highest weights $\mu _{\frak{a}%
 _{\perp }}\left( u\right) $. As a $U\left( \frak{u}_{I}^{-}\right) $-module
-each $M_{I}^{\mu _{\afb}\left( u\right) }$ is isomorphic to $%
-U\left( \frak{u}_{I}^{-}\right) \otimes $ $L_{\afb}^{\mu _{%
-\afb}\left( u\right) }$ and thus its character can be written
-with the help of Kostant-Heckman function \cite{KostantHeckman1982} corresponding
-to the injection of the orthogonal subalgebra $\afb\hookrightarrow \gf$:
+each $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ is isomorphic to $%
+U\left( \frak{u}_{I}^{-}\right) \otimes $ $L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) }$ and thus its character can be written
+in terms of Kostant-Heckman function \cite{KostantHeckman1982} corresponding
+to the injection of the orthogonal partner $\frak{a}_{\perp
+}\hookrightarrow \frak{g}$:
 \begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\afb}\left( u\right) }=\mathcal{KH}_{%
-\afb\hookrightarrow \gf}\mathrm{ch}L_{\afb}^{\mu _{\afb}\left( u\right) }.
+\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\mathcal{KH}_{%
+\frak{a}_{\perp }\hookrightarrow \frak{g}}\mathrm{ch}L_{\frak{a}_{\perp
+}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
 \end{equation*}
-As far as the function $\mathcal{KH}_{\afb\hookrightarrow \frak{%
-g}}$ is generated by the denominator $R_{I}$ the last expression can be
-rewritten in the form
+The function $\mathcal{KH}_{\frak{a}_{\perp }\hookrightarrow \frak{%
+g}}$ is generated by the denominator $R_{I}$ thus the last expression can be
+written in the form
 \begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\afb}\left( u\right) }=\frac{1}{R_{I}}%
-\mathrm{ch}L_{\afb}^{\mu _{\afb}\left( u\right) }.
+\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\frac{1}{R_{I}}%
+\mathrm{ch}L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
 \end{equation*}
@@
  -- the decomposition of $\mathrm{ch}\left(
-L^{\mu }\right) $ in terms of generalized Verma modules characters:
+L^{\mu }\right) $ in terms of generalized Verma module characters:
 \begin{equation}
 \mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
-u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\afb}\left(
+u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
 u\right) }.  \label{char in gen verma mod}
@@
 \begin{remark}
-Here the generalized Weyl-Verma character formula appear in a detailed
-form: the weights $\mu _{\aft}$ and the generalized Verma modules highest weights
-$\mu _{\afb}$ are indicated separately. The reason is that the
-highest weight of $M_{I}$-module is not equal to the projection of the maximal
+Here the generalized Weyl-Verma character formula (called the alternating sum
+formula in \cite{humphreys2008representations}) appears in a special
+form: the weights $\mu _{\aft}$ and the generalized Verma module highest weights
+$\mu _{\afb}$ are separated. The reason is that the
+highest weight of $M_{I}$-module is not equal to the projection of its maximal
 weight to $h^*_{\afb}$ (but must be additionally shifted by the defect).
@@
 \begin{example}
-  Continuing Example \ref{example:reduct-verma-modul} we consider the generalized Verma modules for the
-  embedding  $A_{1}\hookrightarrow B_{2}$ with the subalgebra $\afb$ built on the root $\alpha_{1}$
+  Consider the generalized Verma modules for the
+  embedding  $A_{1}\hookrightarrow B_{2}$ with the subalgebra $\afb$ attributed to the
+  root $\alpha_{1}$
   of $B_{2}$. The generalized Verma module $M^{\omega_{1}}_{I}$ with the highest weight
-  $\omega_{1}=e_{1}$ is shown in Figure \ref{fig:B2_Verma_Decomp}. The decomposition of the corresponding irreducible module
-  $L^{\omega_{1}}$ is indicated by the set of dashed contours of the involved generalized Verma
-  modules. 
+  $\omega_{1}=e_{1}$ is shown in Figure \ref{fig:B2_Verma_Decomp}.
   \begin{figure}[h!bt]
@@
   }
-  \caption{Generalized Verma module  for the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
+  \caption{Generalized Verma modules  for the regular embedding of $A_1$ into $B_2$.
+  Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
     The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. The
-    decomposition of $L^{\omega_{1}}$ is indicated by the set of dashed contours of the involved generalized Verma
+    decomposition of $L^{\omega_{1}}$ is indicated by
+    the set of contours of the involved generalized Verma
   modules. Dashed contours correspond to positive $\epsilon(u)$ and dotted to negative.}
@@
 \begin{remark}
-As it was proved in \cite{humphreys2008representations} (see Proposition 9.6 ) the characters of the
-generalized Verma modules $M_{I}^{\mu _{\afb}\left( u\right) }$
-can be described as linear combinations of ordinary Verma modules of $\frak{g%
-}$:
+As it was proved in \cite{humphreys2008representations} (see Proposition 9.6
+) characters of the generalized Verma modules $M_{I}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) }$ can be described as linear combinations of
+ordinary Verma modules of $\frak{g}$:
 \begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\afb}\left( u\right) }=\sum_{w\in W_{%
-\afb}}\epsilon \left( w\right) \mathrm{ch}M^{w\left( \mu _{%
-\afb}\left( u\right) +\rho _{\afb}\right) -\rho _{%
-\afb}}
+\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\sum_{w\in W_{%
+\frak{a}_{\perp }}}\epsilon \left( w\right) \mathrm{ch}M^{w\left( \mu _{%
+\frak{a}_{\perp }}\left( u\right) +\rho _{\frak{a}_{\perp }}\right) -\rho _{%
+\frak{a}_{\perp }}}
 \end{equation*}
 Substituting this expression in\ (\ref{char in gen verma mod}) and using the
-definitions (\ref{mu-a},\ref{mu-a-tilda}) and (\ref{defect ort}) we reobtain
+definitions (\ref{mu-a},\ref{mu-a-tilda}) and (\ref{defect ort}) we reconstruct
 the standard Weyl-Verma decomposition of the character:
@@
 
-%\bigskip
+\section{BGG resolution and branching}
+
+In \cite{lepowsky1977generalization} it was demonstrated that for the
+highest weight module $L^{\mu }$ with $\mu \in P^{+}$ the sequence
+
+\begin{equation}
+0\rightarrow M_{r}^{I}\overset{\delta _{r}}{\rightarrow }M_{r-1}^{I}\overset{%
+\delta _{r-1}}{\rightarrow }\ldots \overset{\delta _{1}}{\rightarrow }%
+M_{0}^{I}\overset{\varepsilon }{\rightarrow }L^{\mu }\rightarrow 0,
+\label{resolution sequence}
+\end{equation}
+with
+\begin{equation}
+M_{k}^{I}=\bigoplus_{u\in U,\;\mathrm{length}\left( u\right)
+=k}M_{I}^{u\left( \mu +\rho \right) -\rho },\quad M_{0}^{I}=M_{I}^{\mu }
+\label{Verma elements sequence}
+\end{equation}
+(the generalized BGG resolution) is exact and formula (\ref{gen Weyl-Verma}%
+) is a cosequence of this resolution.
+
+\begin{figure}[h!bt]
+ \noindent\centering{
+   \includegraphics[width=140mm]{B2_Exact}}
+ \caption{Injection $A_1\hookrightarrow B_2$ (see Figure \ref{fig:B2_Verma_Decomp}).
+ The orthogonal partner is $A_1$ corresponding to the root $\alpha_1$.
+ The resolution of the simple module $L^{\omega_1}$.
+ Presented is the central part of the exact sequence
+   $0 \to Im(\delta_2) \to \left( e^{\mu _{\widetilde{%
+\frak{a}}}\left( e\right) }\mathrm{ch}M_{I}^{\pi _{\afb}\left[ \omega_1 \right] -%
+\mathcal{D}_{\afb} }=M^{\omega_1}_{I}\right) \to
+   L^{\omega_1}\to 0 $.  Here $\mu _{\widetilde{\frak{a}}}\left( e\right) =\pi _{\aft}\left[ \mu \right] + \mathcal{D}_{\afb}$.
+   }
+\end{figure}
+
+\begin{statement}
+
+Let $L^{\mu }$ be the highest weight $\frak{g}$-module with $\mu \in P^{+}$
+,let its regular subalgebra $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$
+be orthogonal to a reductive subalgebra $\frak{a}\hookrightarrow \frak{g}$.
+Then the decomposition (\ref{sing decomp main}) defines both the generalized
+resolution of $L^{\mu }$ with respect to $\frak{a}_{\perp }$ and the
+branching rules for $L^{\mu }$ with respect to $\frak{a}$ .
+\end{statement}
+
+\begin{proof}
+Put
+\begin{equation*}
+\mathrm{ch}M_{I}^{u\left( \mu +\rho \right) -\rho }=e^{\mu _{\widetilde{%
+\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
+u\right) },\mathrm{ch}M_{I}^{\mu }=e^{\mu _{\widetilde{\frak{a}}}\left(
+e\right) }\mathrm{ch}M_{I}^{\pi _{\frak{a}_{\perp }}\left[ \mu \right] -%
+\mathcal{D}_{\frak{a}_{\perp }}}
+\end{equation*}
+with\ $\mu _{\widetilde{\frak{a}}}\left( u\right) ,\mu _{\frak{a}_{\perp
+}}\left( u\right) $ and $\mathcal{D}_{\frak{a}_{\perp }}$ as in Lemma \ref{Psi-decomp-lemma} and $%
+u\in U$ defined by (\ref{U-def}). This gives the elements of the filtration
+sequence (\ref{resolution sequence}).
+
+Consider the set $\left\{ \mu _{\frak{a}_{\perp }}\left( u\right) |u\in
+U\right\} $ as the highest weights for the simple modules $L_{\frak{a}%
+_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ and evaluate their
+dimensions. Together with
+$\left\{ \mu _{\widetilde{\mathfrak{a}}}\left( u\right) |u\in
+U\right\} $ this gives the set of singular weights
+\begin{equation*}
+\left\{ \epsilon (u)\;
+e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }
+\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
+}}\left( u\right) }\right) \right\} .
+\end{equation*}
+The branching $L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu
+\in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ is
+then fixed by the injection fan $\Gamma _{\frak{a}\rightarrow \frak{g}}$ and
+the relation (\ref{recurrent rel}). The latter gives us the coefficients $k_{\xi
+}^{\left( \mu \right) }$ and thus defines $b_{\nu }^{\left( \mu \right) }$
+due to the property $b_{\nu }^{\left( \mu \right) }=k_{\nu }^{\left( \mu
+\right) }$ for $\nu \in \overline{C_{\frak{a}}}$ .
+\end{proof}
+
+\begin{corollary}
+
+Let $L^{\mu }$ be the highest weight $\frak{g}$-module with $\mu \in P^{+}$
+and $\frak{a}\hookrightarrow \frak{g}$ -- a reductive subalgebra in $\frak{g}
+$. Let $\frak{a}_{\perp }$, the orthogonal partner for $\frak{a}$, be
+equivalent to $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, and $\widetilde{%
+\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ with $\frak{h=\frak{h}_{\frak{a}}%
+}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$. Let $L_{%
+\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }=\bigoplus\limits_{\nu \in P_{%
+\widetilde{\frak{a}}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\widetilde{\frak{a%
+}}}^{\nu }$ be the branching of $L^{\mu }$ with respect to $\widetilde{\frak{%
+a}}$. Then the branching coefficients $b_{\nu }^{\left( \mu \right) }$
+define the generalized resolution (\ref{resolution sequence}) of $L^{\mu }$
+with respect to $\frak{a}_{\perp }$.
+\end{corollary}
+
+\begin{proof}
+Let $\alpha $ be the simple root of $A_{1}$. Use the Weyl transformations
+to identify it with some simple root of $\frak{g}$, say $\alpha _{1}$.
+Construct the singular element for the module $L_{\frak{g}\downarrow
+\widetilde{\frak{a}}}^{\mu }$, i.e. the $\Psi _{\widetilde{\frak{a}}%
+}^{\left( L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }\right)
+}=\sum_{\nu \in P_{\widetilde{\frak{a}}}^{+},b_{\nu }^{\left( \mu \right)
+}>0}b_{\nu }^{\left( \mu \right) }\Psi _{\widetilde{\frak{a}}}^{\left( \nu
+\right) }$ , and decompose it $\Psi _{\widetilde{\frak{a}}}^{\left( L_{\frak{%
+g}\downarrow \widetilde{\frak{a}}}^{\mu }\right) }=k_{\xi }^{\left( \mu
+\right) }e^{\xi }$. In our case the representatives $u$ in the
+recurrent relation (\ref{recurrent rel}) are uniquely determined by the weight $\xi $:
+\begin{equation*}
+\epsilon (u\left( \xi \right) )\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\left( \xi \right) \right) }\right) =-s\left(
+\gamma _{0}\right) k_{\xi }^{\left( \mu \right) }-\sum_{\gamma \in \Gamma _{%
+\widetilde{\frak{a}}\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right)
+k_{\xi +\gamma }^{\left( \mu \right) }.
+\end{equation*}
+We have
+\begin{equation*}
+\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\left(
+\xi \right) \right) }\right) =\left| s\left( \gamma _{0}\right) k_{\xi
+}^{\left( \mu \right) }+\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}%
+\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma
+}^{\left( \mu \right) }\right|
+\end{equation*}
+and
+\begin{equation*}
+\mu _{\frak{a}_{\perp }}\left( u\left( \xi \right) \right) =\frac{1}{2}%
+\left( \dim \left( L_{A_{1}}^{\mu \left( \xi \right) }\right) -1\right)
+\alpha _{1}
+\end{equation*}
+The set of generalized Verma modules $e^{\xi +\mathcal{D}%
+_{\frak{a}_{\perp }}}\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
+u\left( \xi \right) \right) }$ is thus fixed:
+\begin{equation*}
+\left\{ e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }\mathrm{ch}%
+M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }|u\in U\right\} .
+\end{equation*}
+Classifying these modules according to the length of $u$
+we get the components (\ref{Verma elements sequence}) of the resolution (\ref{resolution sequence}).
+\end{proof}
 
@@
 
-In \cite{2010arXiv1007.0318L} it was demonstrated that the injection fan recursive mechanism
-works also for special injections. Here we must stress that the Weyl-Verma decomposition
-can be obtained in this case. The Weyl-Verma relations corresponding to the special
-subalgebras will describe the projections of characters of the initial module in terms
-of generalized Verma modules distributed in the subspace of $h^*$.
+In \cite{2010arXiv1007.0318L} it was demonstrated that the injection fan
+recursive mechanism works also for special injections. It must be mentioned
+that in this case the Weyl-Verma decompositions can also be obtained. The
+resolutions corresponding to special subalgebras describe the relations
+between the projections of characters of the initial module and the generalized
+Verma modules with highest weights in the subspace of $h^*$.
 
-Consider the situation where the simple roots are prescribed by some external
-forces (originating in physical applications conditions, for example). In this case
-the orthogonal partner cannot be generated by simple root vectors only.  The elements
-$\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\gf%
-_{\eta }$ do not form a subalgebra in $\gf$ because some nonsimple roots are lost in
-$\Delta ^{+}\setminus \Delta _{I}^{+}$. It is important to indicate that in this case
-the Weyl-Verma formula still exists. In it the generalized Verma modules correspond to
-the contractions \cite{Doebner1967Melsheimer} of the algebra $\frak{n}^{+}$ and the
-Weyl-Verma relations describes the decomposition of the representation space of $L^{\mu}$
-into the set of generalized Verma modules of contracted algebra
-$U\left(\frak{n}_c^{+}\right)$. The weight vectors are formed by the PBW-basis
-of $U\left(\frak{n}_c^{+}\right)$ and of $U\left( \afb \right)$. To consider such space
-as a $\gf$-module we must perform the deformation \cite{Nijenhuis1966Richardson} of
-the algebra $\frak{n}_c^{+}$ (restore the initial composition law). The space survives
-and after such a deformation the initial
-algebra generators will act properly on it.
+Consider the situation where the simple roots are prescribed by some
+external factors (originating in physical applications conditions, for
+example). In this case the orthogonal partner cannot be generated by simple
+root vectors only. The elements $\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta
+^{+}\setminus \Delta _{I}^{+}}\frak{g}_{\eta }$ do not form a subalgebra in $%
+\mathfrak{g}$ because some nonsimple roots are lost in $\Delta ^{+}\setminus
+\Delta _{I}^{+}$. It is important to indicate that in this case the
+Weyl-Verma formula still exists. In it the generalized Verma modules
+correspond to the contractions \cite{Doebner1967Melsheimer} of the algebra $%
+\frak{n}^{+}$ and the Weyl-Verma relations describe the decomposition of
+the representation space of $L^{\mu}$ into the set of generalized Verma
+modules of contracted algebra $U\left(\frak{n}_c^{+}\right)$. The weight
+vectors are formed by the PBW-basis of $U\left(\frak{n}_c^{+}\right)$ and of
+$U\left( \mathfrak{a}_{\bot} \right)$. To consider such space as a $%
+\mathfrak{g}$-module we must perform the deformation \cite
+{Nijenhuis1966Richardson} of the algebra $\frak{n}_c^{+}$ (and thus restore the
+initial composition law). The space survives and after such a deformation
+the initial algebra generators will act properly on it.
 
 \section{Acknowledgments}
-The authors express their sincere gratitude to all those who prepared and performed the
-III International Conference "Models in Quantum Field Theory - 2010" dedicated to 70-th
-anniversary of A. N. Vassiliev.
 
-The work was supported in part by the RFFI grant N 09-01-00504.
+The authors express their sincere gratitude to all those who prepared and
+performed the III International Conference "Models in Quantum Field Theory -
+2010" dedicated to 70-th anniversary of A. N. Vassiliev.
 
-% \section{Applications}
-% \label{sec:applications}
-%
-% \section{Conclusion}
-% \label{sec:conclusion}
-%
-%
-% \section{Acknowledgements}
-%
-% The work was supported in part by RFFI grant N 09-01-00504 and the National
-% Project RNP.2.1.1./1575.
-%
+The work was supported in part by the RFFI grant N 09-01-00504 and by the Chebyshev Laboratory
+(Department of Mathematics and Mechanics, Saint-Petersburg State
+University) under the grant 11.G34.31.2006 of the Government of the
+Russian Federation.
 
-\bibliographystyle{utphys}
+\bibliographystyle{plain}
 \bibliography{article}

### 2011-02-10 AffineLieAlgebras/MQFT2010/article-ru.tex
Work on translation

@@
 \label{sec:notation}
+Пусть $\frak{g}$ и $\frak{a}$ -- (аффинные) алгебры Ли, а вложение  $\frak{a}\hookrightarrow \frak{g}$ таково, что  $\frak{a}$ -- редуктивная подалгебра в  $\frak{a\subset g}$ с согласованным корневым пространством: $\frak{%
+h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g}}^{\ast }$. Мы используем следующие обозначения:
 
-Consider Lie algebras (affine Lie algebras) $\frak{g}$ and $\frak{a}$ and an
-injection $\frak{a}\hookrightarrow \frak{g}$ such that $\frak{a}$ is a
-reductive subalgebra $\frak{a\subset g}$ with correlated root spaces: $\frak{%
-h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g}}^{\ast }$. We use the
-following notations:
+$\frak{g=n}^{-}+\frak{h}+\frak{n}^{+}$ --- разложение Картана;
 
-$\frak{g=n}^{-}+\frak{h}+\frak{n}^{+}$ --- the Cartan decomposition;
+$r$ , $\left( r_{\frak{a}}\right) $ --- ранг алгебра $\frak{g}$ $%
+\left( \mathrm{\text{соотв., }\frak{a}}\right) $ ;
 
-$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
-\left( \mathrm{{resp. }\frak{a}}\right) $ ;
-
-$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
-^{+} $ $\left( \mathrm{{resp. }\Delta _{\frak{a}}^{+}}\right) $--- the
-positive root system (of $\frak{g}$ and $\frak{a}$ respectively);
+$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- корневая система; $\Delta
+^{+} $ $\left( \mathrm{\text{соотв., }\Delta _{\frak{a}}^{+}}\right) $--- набор положительных корней (алгебр $\frak{g}$ и $\frak{a}$ соответственно);
 
 $\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
-\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $%
-\Delta $ (resp. in $\left( \Delta _{\frak{a}}\right) $);
+\alpha \right) \right) $ --- кратность корня $\alpha$ в $%
+\Delta $ (соотв., в $\left( \Delta _{\frak{a}}\right) $);
 
-$S\quad \left( S_{\frak{a}}\right) $ --- the set of simple roots (for
-$\gf$ and $\af$ respectively);
+$S\quad \left( S_{\frak{a}}\right) $ --- множество простых корней (для 
+$\gf$ и $\af$ соответственно);
 
-$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
-i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a%
+$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ ---  $%
+i$-й (соотв., $j$-й) простой корень алгебры $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a%
 }}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
@@
 $\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
-}\right) $-- the simple coroot for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a}%
+}\right) $-- простой кокорень для $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a}%
 }\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
 
-$W$ , $\left( W_{\frak{a}}\right) $--- the Weyl group;
+$W$ , $\left( W_{\frak{a}}\right) $--- группа Вейля;
 
-$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
+$C$ , $\left( C_{\frak{a}}\right) $--- фундаментальная камера Вейля;
 
-$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
-fundamental Weyl chamber;
+$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- замыкание фундаментальной камеры Вейля;
 
@@
 
-$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
+$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- вектор Вейля;
 
-$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
-of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\af$-module
-with the highest weight $\nu $);
+$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- интегрируемый модуль  $\frak{g}$ со старшим весом $\mu $\ ; (соотв., интегрируемый $\af$-модуль старшего веса $\nu $);
 
 $\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
-the weight diagram of $L^{\mu }$ (resp. ${}L_{\frak{a}}^{\nu }$ );
+весовая диаграмма модуля $L^{\mu }$ (соотв., ${}L_{\frak{a}}^{\nu }$ );
 
-$P$ (resp. $P_{\frak{a}} $) \ --- the weight lattice;
+$P$ (соотв., $P_{\frak{a}} $) \ --- весовая решетка;
 
-$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight lattice;
+$P^{+}$ (соотв., $P_{\frak{a}}^{+} $) \ --- решетка доминантных весов;
 
 $m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\zeta }^{\left( \nu \right)
-}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
-resp. }\in P_{\frak{a}}}\right) $ in $L^{\mu }$, (resp. in $\zeta \in
+}\right) $ --- кратность веса $\xi \in P$ \ $\left( \mathrm{\text{соотв., }\in P_{\frak{a}}}\right) $ в $L^{\mu }$, (соотв., в $\zeta \in
 L_{\frak{a}}^{\nu } $);
 
-$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\frak{a}}^{\nu
-}\right) $)--- the formal character of $L^{\mu }$ (resp. of $L_{\frak{a}}^{\nu
+$ch\left( L^{\mu }\right) $ (соотв., $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $)--- формальный характер $L^{\mu }$ (соответственно, $L_{\frak{a}}^{\nu
 } $);
@@
 +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
-\mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;
+\mathrm{{mult}\left( \alpha \right) }}}$ --- формула Вейля-Каца;
 
 $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
-mult}\left( \alpha \right) }}\quad $ (resp. $R_{\frak{a}}:=\prod_{\alpha \in
+mult}\left( \alpha \right) }}\quad $ (соотв., $R_{\frak{a}}:=\prod_{\alpha \in
 \Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}%
-}\left( \alpha \right) } $)--- the Weyl denominator.
+}\left( \alpha \right) } $)--- знаменатель Вейля.
 
-\section{Orthogonal subalgebra and\\ singular elements}
+\section{Ортогональная подалгебра и сингулярные элементы}
 

### 2011-02-11 AffineLieAlgebras/MQFT2010/article-ru.tex
Translation in progress

@@
 
-\newtheorem{statement}{Statement}
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{lemma}{Lemma}
-\newtheorem{mynote}{Note}[section]
+\newtheorem{statement}{Утверждение}
+\newtheorem{theorem}{Теорема}
+\newtheorem{corollary}{Следствие}[theorem]
+\newtheorem{lemma}{Лемма}
+\newtheorem{mynote}{Замечание}[section]
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
+\newtheorem{definition}{Определение}
+\newtheorem{remark}{Ремарка}
+\newtheorem{example}{Пример}
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
 $\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
-}\right) $-- простой кокорень для $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a}%
+}\right) $-- простой ко-корень для $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a}%
 }\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
@@
 
-In this section we shall show how the recurrent approach to branching
-problem leads naturally to a presentation of a formal character of
-$\frak{g}$-module in terms characters corresponding to a set
-of parabolic (generalized) Verma modules. Consider a reductive
-Lie algebra $\frak{g}$ and its reductive subalgebra $\frak{a}\subset \frak{g}$.
-Let $L^{\mu} $ be the highest weight integrable module of $\frak{g}$, $\mu \in
-P^{+}$. Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
+В этом разделе мы покажем, как рекуррентный подход к проблеме ветвления естественным образом приводит к представлению формального характера $\frak{g}$-модуля в виде комбинации характеров, соответствующих параболическим (обобщенным) модулям Верма.
+Рассмотрим редуктивную алгебру Ли  $\frak{g}$ и ее редуктивную подалгебру $\frak{a}\subset \frak{g}$.
+Пусть  $L^{\mu} $ -- интегрируемый модуль старшего веса алгебры  $\frak{g}$, $\mu \in P^{+}$.  Будем считать  $L^{\mu}$ полностью приводимым по отношению к подалгебре $\frak{a}$,
 \begin{equation*}
@@
 \end{equation*}
-Using the projection operator $\pi _{\frak{a}}$ (to the weight space $\frak{%
-h_{a}}^{\ast }$) one can write this decomposition in terms of formal
-characters:
+Это разложение может быть записано в терминах формальных характеров с использованием оператора проекции  $\pi _{\frak{a}}$ (на весовое пространство $\frak{h_{a}}^{\ast }$):
 \begin{equation}
@@
 \end{equation}
-The module $L^{\mu }$ has the BGG resolution (see \cite
-{bernstein1976category,bernstein1975differential,bernstein1971structure} and
-\cite{humphreys2008representations}). All the members of the filtration
-sequence are the direct sums of Verma modules and all their highest weights $%
-\nu $ are strongly linked to $\mu $:
+Для модуля  $L^{\mu }$ существует БГГ резольвента (см. \cite
+{bernstein1976category,bernstein1975differential,bernstein1971structure} и
+\cite{humphreys2008representations}). Все члены фильтрующей последовательности представляются суммами модулей Верма со старшими весами $\nu$, сильно связанными с $\mu$:
 \begin{equation*}
@@
 
-\subsection{Orthogonal subalgebra}
+\subsection{Ортогональная подалгебра}
 
-Let $\frak{h}_{\frak{a}}$ be a Cartan subalgebra of $\mathfrak{g}$. For $%
-\mathfrak{a}\hookrightarrow \frak{g}$ introduce the ''orthogonal partner'' $%
-\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$ .
+Пусть  $\frak{h}_{\frak{a}}$ -- подалгебра Картана в  $\mathfrak{g}$. Для  $\mathfrak{a}\hookrightarrow \frak{g}$ введем ``ортогонального партнера''  $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$.
 
-Consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to
-$\frak{a}$,
+Рассмотрим корневое подпространство  $\frak{h}_{\perp \frak{a}}^{\ast }$, ортогональное к $\frak{a}$,
 \begin{equation*}
@@
 \end{equation*}
-and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
-to $\frak{a}$,
+и корни  $\frak{g}$ (соответственно, положительные корни)  ортогональные к $\frak{a}$,
 \begin{eqnarray}
@@
 \end{eqnarray}
-Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
-reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\frak{a}_{\perp
-}}^{+}$. The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
-subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
-_{\perp }}$. Let
+Обозначим через  $W_{\frak{a}_{\perp }}$ подгруппу  $W$, порожденную отражениями  $w_{\beta }$ с корнями  $\beta \in \Delta_{\frak{a}_{\perp}}^{+}$.
+Корневая подсистема  $\Delta _{\frak{a}_{\perp }}$ определяет подалгебру  $\frak{a}_{\perp }$, имеющую подалгебру Картана $\frak{h}_{\frak{a}_{\perp }}$.
+Пусть
 \begin{equation*}
@@
 \end{equation*}
-so that $\frak{g}$ has the subalgebras
+и у  $\frak{g}$ есть подалгебры
 \begin{eqnarray}
@@
 \end{eqnarray}
-Notice that $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ in general is not a
-subalgebra in $\mathfrak{g}$.
+Заметим, что  $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ в общем случае не является подалгеброй в $\mathfrak{g}$.
 
-For the Cartan subalgebras we have the decomposition
+Для подалгебр Картана имеет место разложение
 \begin{equation}
@@
 \end{equation}
-For $\frak{a}$ and $\frak{a}_{\perp }$ consider the
-corresponding Weyl vectors, $\rho _{\frak{a}}$ and $\rho _{\frak{a}_{\perp
-}} $. Form the so called ''defects'' $\mathcal{D}_{\frak{a}}$ and $\mathcal{%
-D}_{\frak{a}_{\perp }}$ of the injection:
+Рассмотрим векторы Вейля  $\rho _{\frak{a}}$ и $\rho _{\frak{a}_{\perp}} $, соответствующие  $\frak{a}$ и $\frak{a}_{\perp }$.
+Введем так называемые ``дефекты'' вложения  $\mathcal{D}_{\frak{a}}$ и $\mathcal{D}_{\frak{a}_{\perp }}$:
 \begin{equation}
@@
 \end{equation}
-
-For $\mu \in P^{+}$ consider the linked weights $\left\{
-\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $. Consider the projections to
-$h_{\frak{a}_{\perp }}^{\ast }$ additionally shifted by the defect $-%
-\mathcal{D}_{\frak{a}_{\perp }}$:
+Для  $\mu \in P^{+}$ рассмотрим связанные веса  $\left\{\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ и их проекции на $h_{\frak{a}_{\perp }}^{\ast }$, дополнительно сдвинутые на дефект $-\mathcal{D}_{\frak{a}_{\perp }}$:
 \begin{equation*}
@@
 \end{equation*}
-Among the weights $\left\{ \mu _{\frak{a}_{\perp
-}}\left( w\right) |w\in W\right\} $ one can always choose those located in
-the fundamental chamber $\overline{C_{\frak{a}_{\perp }}}$. Let $U$ be the
-set of representatives $u$ for the classes $W/W_{\frak{a}_{\perp }}$ such
-that
 
+Среди весов  $\left\{ \mu _{\frak{a}_{\perp
+}}\left( w\right) |w\in W\right\} $ всегда можно выбрать те, которые попадают в фундаментальную камеру $\overline{C_{\frak{a}_{\perp }}}$.
+Пусть $U$ -- множество представителей $u$ классов  $W/W_{\frak{a}_{\perp }}$, таких что
 \begin{equation}
@@
 \end{equation}
-Thus we can form the subsets:
+Тогда можно выделить подмножества:
 \begin{equation}
@@
 \end{equation}
-and
+и
 \begin{equation}
@@
 
-Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
-since it is built on a subset of roots of the algebra $\mathfrak{g}$.
+Заметим, что подалгебра  $\mathfrak{a}_{\bot}$ по определению регулярна, так как она построена на подмножестве корней алгебры $\mathfrak{g}$.
 
-For the modules we are interested in the Weyl-Kac formula for $\mathrm{ch}%
-\left( L^{\mu }\right) $ can be written in terms of singular elements \cite
-{humphreys1997introduction},
+Для интересующих нас модулей формула Вейля-Каца для  $\mathrm{ch}\left( L^{\mu }\right) $ может быть записана через сингулярные элементы \cite{humphreys1997introduction},
 \begin{equation*}
@@
 \end{equation*}
-namely,
+а именно,
 \begin{equation}
@@
 \end{equation}
-The same is true for the submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
-}\right) $ in (\ref{branching1})
+То же верно и для подмодулей $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $ в формуле (\ref{branching1})
 \begin{equation*}
@@
 \end{equation*}
-with
+где
 \begin{equation*}
@@
 \end{equation*}
-
-Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
-we get the relation connecting the singular elements $\Psi ^{\left( \mu
-\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
+Применяя формулу  (\ref{Weyl-Kac2}) к правилу ветвления  (\ref{branching1}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu
+\right) }$ и $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
 \begin{eqnarray}
@@
 
-\subsection{Decomposing the singular element.}
+\subsection{Разложение сингулярного элемента.}
 
@@
 
-Now we shall perform a decomposition of the singular element $\Psi ^{\left(
-\mu \right) }$ in terms of singular elements of the orthogonal partner
-modules:
+Теперь мы выполним разложение сингулярного элемента  $\Psi ^{\left(\mu \right) }$ на сингулярные элементы модулей ортогонального партнера:
 
 \begin{lemma}
-Let $\frak{a}_{\bot }$ be the orthogonal partner of a reductive subalgebra $%
-\frak{a}\hookrightarrow \frak{g}$ with $\frak{h}=\frak{\frak{h}_{\frak{a}}}%
-\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$, $\widetilde{%
-\frak{a}_{\perp }}=\frak{a}_{\perp }\oplus \frak{h}_{\perp }$ and $%
+
+Пусть  $\frak{a}_{\bot }$ -- ортогональный партнер редуктивной подалгебры  $\frak{a}\hookrightarrow \frak{g}$ и $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$, $\widetilde{%
+\frak{a}_{\perp }}=\frak{a}_{\perp }\oplus \frak{h}_{\perp }$, $%
 \widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$.
 
-$L^{\mu }$ be the highest weight integrable module with $\mu \in P^{+}$ and
+Пусть $L^{\mu }$ -- интегрируемый модуль старшего веса  $\mu \in P^{+}$ и
 
-$\Psi ^{\left( \mu \right) }$\ -- the singular element of $L^{\mu }$.
+$\Psi ^{\left( \mu \right) }$\ -- сингулярный элемент $L^{\mu }$.
 
-Then the element $\Psi ^{\left( \mu \right) }$ can be decomposed into the
-sum over $u\in U$ (see (\ref{U-def})) of singular elements $\Psi _{\frak{a}%
-_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ with the coefficients
+Тогда элемент  $\Psi ^{\left( \mu \right) }$ может быть разложен в сумму по  $u\in U$ (см.
+(\ref{U-def})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
 $\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
@@
 \begin{proof}
-Let
+Пусть
 \[
 u(\mu +\rho )=\pi _{\left( \aft\right) }u(\mu +\rho )+\pi _{\left(
-\frak{a}_{\perp }\right) }u(\mu +\rho )
+\frak{a}_{\perp }\right) }u(\mu +\rho ),
 \]
-with $u\in U$. For any $v\in W_{\frak{a}_{\bot }}$ consider
-the singular weight $vu(\mu +\rho )-\rho $ and perform the decomposition:
+где $u\in U$. Для произвольного  $v\in W_{\frak{a}_{\bot }}$ рассмотрим сингулярный вес  $vu(\mu +\rho )-\rho $ и выполним разложение:
 \begin{equation}
@@
 \end{equation}
-Use the defect $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}) to
-simplify the first line in (\ref{sing-decomp-1}):
+Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}), чтобы упростить первую строчку в формуле (\ref{sing-decomp-1}):
 \[
@@
 \]
-and the second one:
+и вторую
 \[
@@
 \]
-This provides the desired decomposition of the singular element $%
-\Psi ^{\mu }$ in terms of singular elements $\Psi _{\frak{a}%
-_{\perp }}^{\eta }$ of the $\frak{a}_{\perp }$-modules $L_{%
-\frak{a}_{\perp }}^{\eta }$:
+В результате получаем требуемое разложение сингулярного элемента $\Psi ^{\mu }$ на сингулярные элементы $\Psi_{\frak{a}_{\perp}}^{\eta}$ модулей $L_{\frak{a}_{\perp }}^{\eta }$ подалгебры $\frak{a}_{\perp }$:
 \begin{equation}

### 2011-02-11 AffineLieAlgebras/MQFT2010/article-ru.tex
More work on translation

@@
 \begin{remark}
-This relation can be considered as a generalized form of the Weyl formula
-for the singular element $\Psi _{\frak{g}}^{\mu }$: the vectors $\mu _{%
-\widetilde{\mathfrak{a}}}\left( u\right) $ play the role of singular weights
-while the alternating factors $\epsilon (u)$ are extended to $\epsilon
-(u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$. In
-fact when $\frak{a=g}$ both $\frak{a}_{\perp }$and $\frak{h}_{\perp }$are
-zeros, $U=W$, and\ the original Weyl formula is reobtained so far as the singular elements $\epsilon (u)\Psi _{\frak{a}_{\perp
-}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\epsilon (u)$ become trivial.
- In the opposite
-limit when $\frak{a=0}$, $\Delta _{\frak{a}_{\perp }}=\Delta _{\frak{g}}$, $%
+Это соотношение можно рассматривать как обобщенную форму формулы Вейля для сингулярного элемента $\Psi _{\frak{g}}^{\mu }$: векторы $\mu _{%
+\widetilde{\mathfrak{a}}}\left( u\right) $ играют роль сингулярных весов, а чередующиеся множители  $\epsilon (u)$ расширены до $\epsilon
+(u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$.
+
+Действительно, при  $\frak{a=g}$ подалгебры  $\frak{a}_{\perp }$, и $\frak{h}_{\perp }$ тривиальны, $U=W$ и оригинальная формула Вейля восстанавливается, так как сингулярные элементы $\epsilon (u)\Psi _{\frak{a}_{\perp %
+}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\epsilon (u)$ становятся  тривиальными.
+
+В противоположном пределе, когда $\frak{a}=0$, $\Delta _{\frak{a}_{\perp }}=\Delta _{\frak{g}}$, $%
 \frak{h}_{\perp }^{\ast }=0$, $\frak{a}_{\perp }=\frak{g}$, $\mathcal{D}_{%
-\frak{a}_{\perp }}=0$ and $U=W/W_{\frak{a}_{\perp }}=e$ the singular element
- $\Psi ^{\mu }$ is again reobtained, now via the trivilization of the set of
- vectors $\mu _{\af}\left( e\right) =0$.
+\frak{a}_{\perp }}=0$ и $U=W/W_{\frak{a}_{\perp }}=e$, опять восстанавливается сингулярный элемент
+ $\Psi ^{\mu }$, теперь в результате тривиализации множества векторов $\mu _{\af}\left( e\right) =0$.
 \end{remark}
@@
 
-In \cite
-{2010arXiv1007.0318L} the decomposition analogous to (\ref{singular main}) was
-used to construct the recurrent relations for branching coefficients $k_{\xi
-}^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
-\hookrightarrow \frak{g}$:
+В работе \cite{2010arXiv1007.0318L} разложение, аналогичное формуле (\ref{singular main}) было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
 \begin{equation}
@@
 \end{equation}
-The recursion is goverened by the set $\Gamma _{\widetilde{\frak{a}}%
-\rightarrow \frak{g}}$ called the injection fan. The latter is defined by the
-carrier set $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the
-coefficient function $s(\xi )$
+Рекурсия задается множеством  $\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}$, называемом веером вложения.
+Это множество определяется как носитель  $\left\{ \xi \right\}_{\frak{a}\rightarrow \frak{g}}$  коэффициентной функции $s(\xi )$
 \begin{equation*}
 \left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{g}}:=\left\{
-\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\}
+\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\},
 \end{equation*}
-appearing in the expansion
+возникающей в разложении 
 \begin{equation}
@@
 \end{equation}
-The weights in $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
-g}}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
-\right\} $ -- and the zero element is to be eliminated:
+Веса из множества $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
+g}}$ сдвигаются на $\gamma _{0}$ -- младший вектор в $\left\{ \xi
+\right\} $ -- и исключается нулевой элемент:
 \begin{equation}
@@
 
-The recursion relation (\ref{recurrent rel}) was originally used to
-describe branchings for integrable modules. Notice that there exists an
-important class of modules that also can be reduced with the help of the
-injection fan --
-these are Verma modules.
+Рекуррентное соотношение (\ref{recurrent rel}) первоначально использовалось для описания ветвления интегрируемых модулей.
+Заметим, что существует важный класс модулей, которые также могут быть редуцированы при помощи веера вложения -- это модули Верма.
 \end{remark}
 
-\subsection{Weyl-Verma formulas.}
+\subsection{Фомулы Вейля-Верма.}
 

### 2011-02-12 AffineLieAlgebras/MQFT2010/article-ru.tex
More translation

@@
 \begin{statement}
-\bigskip For an orthogonal subalgebra $\frak{a}_{\perp }$ in $\frak{g}$ (an
-orthogonal partner of a reductive $\frak{a}\hookrightarrow \frak{g}$) the
-character of an integrable highest weight module $L^{\mu }$ can be presented
-as a combination (with integral coefficients) of parabolic Verma modules
-distributed by the set of weights $e^{\mu _{\widetilde{\mathfrak{a}}}\left(
+\bigskip
+Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характера интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) параболических модулей Верма, распределенных по множеству весов $e^{\mu _{\widetilde{\mathfrak{a}}}\left(
 u\right) }$:
@@
 \end{equation}
-where $U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
-\overline{C_{\frak{a}_{\perp }}}\right\} $ and $I$ is such a subset of $S$ that
-$\Delta _{I}^{+}$ is
-equivalent to $\Delta _{\frak{a}_{\perp }}^{+}$.
+где  $U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
+\overline{C_{\frak{a}_{\perp }}}\right\} $ и $I$ -- такое подмножество в  $S$, что $\Delta _{I}^{+}$ эквивалентно $\Delta _{\frak{a}_{\perp }}^{+}$.
 \end{statement}
@@
 \begin{proof}
-By the definition (\ref{delta a ort}) the subalgebra $%
-\mathfrak{a}_{\bot }$ is regular and reductive. Consider its Weyl
-denominator $R_{\frak{a}_{\perp }}:=\prod_{\alpha \in \Delta _{\frak{a}%
+Подалгебра  $\mathfrak{a}_{\bot }$ регулярна и редуктивна по определению  (\ref{delta a ort}). Рассмотрим её знаменатель Вейля   $R_{\frak{a}_{\perp }}:=\prod_{\alpha \in \Delta _{\frak{a}%
 _{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}%
-\mathrm{\left( \alpha \right) }}$ and the element $R_{J}:=\prod_{\alpha \in
+\mathrm{\left( \alpha \right) }}$ и элемент  $R_{J}:=\prod_{\alpha \in
 \Delta ^{+}\setminus \Delta _{\frak{a}_{\perp }}^{+}}\left( 1-e^{-\alpha
-}\right) ^{\mathrm{mult}(\alpha )}$ as the factors in $R$: $\quad $%
+}\right) ^{\mathrm{mult}(\alpha )}$ как сомножители в $R$:
 \begin{equation*}
@@
 \end{equation*}
-According to this factorization and the decomposition (\ref{sing decomp main}%
-) the character $\mathrm{ch}\left( L^{\mu }\right) $ can be written as
+Согласно этой факторизации и разложению  (\ref{sing decomp main}) характер $\mathrm{ch}\left( L^{\mu }\right) $ можно переписать в виде
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-where $\left\{ L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left(
-u\right) }|u\in U\right\} $ is the set of finite-dimensional $\frak{a}%
-_{\perp }$-modules with the highest weights $\mu _{\frak{a}_{\perp }}\left(
-u\right) $. We are interested in nontrivial subalgebras $\frak{a}$ and
-correspondingly in nontrivial $\frak{a}_{\perp }$ (the case of a trivial
-orthogonal subalgebra was considered above (see Remark 1)). This means that $r_{\frak{a}}\geq 1$ and $r_{\frak{a}%
-_{\perp }}<r$. Due to the fact that any maximal regular subalgebra has the
-Dynkin scheme obtained by one or two node subtractions from the extended
-Dynkin scheme and the extended scheme has at most one dependent root (the
-highest root) the set of roots $\Delta _{\frak{a}_{\perp }}^{+}$ is always
-equivalent to the one $\Delta _{I}^{+}$ generated\ by some subset $I\subset
-S $ of simple roots.
+где  $\left\{ L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left(
+u\right) }|u\in U\right\} $ -- множество конечномерных $\frak{a}%
+_{\perp }$-модулей со старшими весами   $\mu _{\frak{a}_{\perp }}\left(
+u\right) $.
+Нас интересуют нетривиальные подалгебры $\frak{a}$ и, соответственно, нетривиальные  $\frak{a}_{\perp }$ (случай тривиальной ортогональной подалгебры рассматривался выше в (см.
+Замечание 1)).
+Значит $r_{\frak{a}}\geq 1$ и $r_{\frak{a}%
+_{\perp }}<r$.
+Так как диаграмма Дынкина для любой регулярной подалгебры получается в результате исключения одной, двух или более вершин из расширенной диаграммы Дынкина алгебры, а расширенная диаграмма содержит не более одного зависимого корня (старший корень), множество корней $\Delta _{\frak{a}_{\perp }}^{+}$ всегда эквивалентно некоторому множеству $\Delta _{I}^{+}$, порожденному набором  простых корней $I\subset S $.
 
-It follows that we can (by redefining the set $\Delta ^{+}$) identify $%
-\Delta _{\frak{a}_{\perp }}^{+}$ with the subset $\Delta _{I}^{+}$ \ where $%
-I\subset S$ . This allows us to introduce the elements necessary to compose
-the generalized Verma modules
-\cite{lepowsky1977generalization,humphreys2008representations}.
-We have two sets of root
-vectors $\left\{ x_{\xi }\in \frak{g}_{\xi }|\xi \in \Delta _{I}^{+}\right\}
-$ and $\left\{ x_{\eta }\in \frak{g}_{\eta }|\eta \in \Delta ^{+}\setminus
-\Delta _{I}^{+}\right\} $ and the corresponding nilpotent subalgebras in $\frak{n}%
+Следовательно мы можем (переопределяя множество  $\Delta ^{+}$) отождествить $\Delta _{\frak{a}_{\perp }}^{+}$ с подмножеством  $\Delta _{I}^{+}$, где $I\subset S$.
+В результате мы можем определить объекты, необходимые для построения обобщенных модулей Верма \cite{lepowsky1977generalization,humphreys2008representations}.
+У нас есть два множества корневых векторов $\left\{ x_{\xi }\in \frak{g}_{\xi }|\xi \in \Delta _{I}^{+}\right\}
+$ и $\left\{ x_{\eta }\in \frak{g}_{\eta }|\eta \in \Delta ^{+}\setminus
+\Delta _{I}^{+}\right\} $, и соответствующие нильпотентные подалгбры в  $\frak{n}%
 ^{+}$:
@@
 \end{equation*}
-The first subalgebra together with its negative counterpart $\frak{n}%
-_{I}^{-} $ generates a simple subalgebra
+Первая подалгебра, вместе со своей отрицательной копией  $\frak{n}%
+_{I}^{-} $ порождает простую подалгебру 
 \begin{equation*}
@@
 \end{equation*}
-We enlarge it with the remaining Cartan generators:
+Мы расширяем ее оставшимися картановскими генераторами:
 \begin{equation*}
@@
 \end{equation*}
-The semidirect product of $\frak{l}_{I}$ and $\frak{u}_{I}^{+}$
-gives a parabolic subalgebra $\frak{p}_{I}\hookrightarrow \frak{g}$ :
+Полупрямое произведение  $\frak{l}_{I}$ и $\frak{u}_{I}^{+}$ дает параболическую подалгебры $\frak{p}_{I}\hookrightarrow \frak{g}$ :
 \begin{equation}
@@
 \end{equation}
-Its universal enveloping $U\left( \frak{p}_{I}\right) $ is a subalgebra in $%
-U\left( \frak{g}\right) $. The $\frak{l}_{I}$-modules $L_{\frak{a}_{\perp }}^{\mu _{%
-\frak{a}_{\perp }}\left( u\right) }$ can be easily lifted to $\frak{p}_{I}$%
--modules using the trivial action of the nilradical $\frak{u}_{I}^{+}$. The
-latter induce $U\left( \frak{g}\right) $-modules in a standard way:
+Ее универсальная обертывающая $U\left( \frak{p}_{I}\right) $ является подалгеброй в  $%
+U\left( \frak{g}\right) $. Модули  $L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) }$ алгебры  $\frak{l}_{I}$ легко поднимаются до  $\frak{p}_{I}$-модулей при помощи тривиального действия нильрадикала $\frak{u}_{I}^{+}$.
+Последний стандартным образом индуцирует $U\left( \frak{g}\right) $-модули:
 \begin{equation*}
@@
 
-These are the \textit{generalized Verma modules}  \cite{lepowsky1977generalization}
-generated by the highest weights $\mu _{\frak{a}%
-_{\perp }}\left( u\right) $. As a $U\left( \frak{u}_{I}^{-}\right) $-module
-each $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ is isomorphic to $%
-U\left( \frak{u}_{I}^{-}\right) \otimes $ $L_{\frak{a}_{\perp }}^{\mu _{%
-\frak{a}_{\perp }}\left( u\right) }$ and thus its character can be written
-in terms of Kostant-Heckman function \cite{KostantHeckman1982} corresponding
-to the injection of the orthogonal partner $\frak{a}_{\perp
+Это  \textit{обобщенные модули Верма}  \cite{lepowsky1977generalization}
+порожденные старшими весами  $\mu _{\frak{a}%
+_{\perp }}\left( u\right) $. Как  $U\left( \frak{u}_{I}^{-}\right) $-модуль каждый  $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ изоморфен  $%
+U\left( \frak{u}_{I}^{-}\right) \otimes L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) }$ и его характер можно записать при помощи функции Костанта-Хекмана \cite{KostantHeckman1982}, соответствующей вложению ортогонального партнера $\frak{a}_{\perp
 }\hookrightarrow \frak{g}$:
@@
 \end{equation*}
-The function $\mathcal{KH}_{\frak{a}_{\perp }\hookrightarrow \frak{%
-g}}$ is generated by the denominator $R_{I}$ thus the last expression can be
-written in the form
+Функция  $\mathcal{KH}_{\frak{a}_{\perp }\hookrightarrow \frak{%
+g}}$ генерируется знаменателем  $R_{I}$, так что последнее выражение можно переписать следующим образом
 \begin{equation*}
@@
 \end{equation*}
-This means that we have obtained the generalized Weyl-Verma character formula
- -- the decomposition of $\mathrm{ch}\left(
-L^{\mu }\right) $ in terms of generalized Verma module characters:
+Значит мы получили обобщенную формулу Вейля-Верма для характеров -- разложение  $\mathrm{ch}\left(
+L^{\mu }\right) $ на характеры обобщенных модулей Верма:
 \begin{equation}

### 2011-02-13 AffineLieAlgebras/MQFT2010/article-ru.tex
Translation completed

@@
 \title{Рекурсивные свойства ветвления и БГГ резольвента}
-\author{В Д Ляховский$^1$, А А Назаров$^2$\\
-Теоретический отдел,\\ Санкт - Петербургский государственный университет\\
-198904, Санкт - Петербург, Россия\\
-$^1$e-mail: lyakh1507@nm.ru, $^2$ antonnaz@gmail.com}
+\author{В Д Ляховский$^1$, А А Назаров$^{2,3}$\\
+  {\small $^1$ Теоретический отдел,}\\
+  {\small Санкт - Петербургский государственный университет}\\
+  {\small 198904, Санкт - Петербург, Россия}\\
+  {\small e-mail: lyakh1507@nm.ru}\\
+  {\small $^2$ Теоретический отдел,}\\
+  {\small Санкт - Петербургский государственный университет}\\
+  {\small 198904, Санкт - Петербург, Россия}\\
+  {\small $^2$ Лаборатория имени Чебышева,}\\
+  {\small математико-механический факультет,}\\ 
+  {\small Санкт - Петербургский государственный университет}\\
+  {\small 199178, Санкт - Петербург, Россия}\\
+  {\small email: antonnaz@gmail.com}}
 
@@
 
-\bigskip
+%\bigskip
 
@@
 \begin{statement}
-\bigskip
+%\bigskip
 Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характера интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) параболических модулей Верма, распределенных по множеству весов $e^{\mu _{\widetilde{\mathfrak{a}}}\left(
@@
 
-\bigskip
+%\bigskip
 \begin{proof}
@@
 \begin{remark}
-Here the generalized Weyl-Verma character formula (called the alternating sum
-formula in \cite{humphreys2008representations}) appears in a special
-form: the weights $\mu _{\aft}$ and the generalized Verma module highest weights
-$\mu _{\afb}$ are separated. The reason is that the
-highest weight of $M_{I}$-module is not equal to the projection of its maximal
-weight to $h^*_{\afb}$ (but must be additionally shifted by the defect).
+Здесь обобщенная формула Вейля-Верма для характеров (называемая формулой переменного суммирования в книге \cite{humphreys2008representations}) имеет специальный вид: веса $\mu _{\aft}$ и старшие веса обобщенных модулей Верма $\mu _{\afb}$ разделены.
+Причина в том, что старший вес $M_{I}$-модуля не равен проекции его максимального веса на  $h^*_{\afb}$ (а должен быть дополнительно сдвинут на дефект).
 \end{remark}
@@
 \begin{example}
-  Consider the generalized Verma modules for the
-  embedding  $A_{1}\hookrightarrow B_{2}$ with the subalgebra $\afb$ attributed to the
-  root $\alpha_{1}$
-  of $B_{2}$. The generalized Verma module $M^{\omega_{1}}_{I}$ with the highest weight
-  $\omega_{1}=e_{1}$ is shown in Figure \ref{fig:B2_Verma_Decomp}.
+  Рассмотрим обобщенные модули Верма для вложения $A_{1}\hookrightarrow B_{2}$, где подалгебра  $\afb$ связана с корнем  $\alpha_{1}$ алгебры  $B_{2}$.
+Обобщенный модуль Верма $M^{\omega_{1}}_{I}$ со старшим весом   $\omega_{1}=e_{1}$ показан на Рисунке \ref{fig:B2_Verma_Decomp}.
   \begin{figure}[h!bt]
@@
   }
-  \caption{Generalized Verma modules  for the regular embedding of $A_1$ into $B_2$.
-  Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. The
-    decomposition of $L^{\omega_{1}}$ is indicated by
-    the set of contours of the involved generalized Verma
-  modules. Dashed contours correspond to positive $\epsilon(u)$ and dotted to negative.}
+  \caption{Обобщенные модули Верма для регулярного вложения  $A_1$ в $B_2$. 
+    Простые корни $\alpha_1, \alpha_2$ алгебры $B_2$ показаны пунктирными стрелками.
+Простой корень  $\beta = \alpha_1+2\alpha_2$ алгебры $A_1$ показан серым вектором.
+Разложение $L^{\omega_{1}}$ представлено набором контуров входящих в него обобщенных модулей Верма.
+Пунктирные контуры соответствуют положительным значениям  $\epsilon(u)$, а точечные -- отрицательным.
+}
 
@@
 \begin{remark}
-As it was proved in \cite{humphreys2008representations} (see Proposition 9.6
-) characters of the generalized Verma modules $M_{I}^{\mu _{\frak{a}%
-_{\perp }}\left( u\right) }$ can be described as linear combinations of
-ordinary Verma modules of $\frak{g}$:
+Как доказано, например, в книге  \cite{humphreys2008representations} (см.
+утверждение 9.6), характеры обобщенных модулей Верма $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ могут также описываться как линейные комбинации обычных модулей Верма алгебры $\frak{g}$:
 \begin{equation*}
@@
 \end{equation*}
-Substituting this expression in\ (\ref{char in gen verma mod}) and using the
-definitions (\ref{mu-a},\ref{mu-a-tilda}) and (\ref{defect ort}) we reconstruct
-the standard Weyl-Verma decomposition of the character:
+Подставляя это выражение в формулу (\ref{char in gen verma mod}) и используя определения  (\ref{mu-a},\ref{mu-a-tilda}) и (\ref{defect ort}), мы восстанавливаем стандартное разложение Вейля-Верма для характера:
 \begin{equation*}
@@
 
-\section{BGG resolution and branching}
-
-In \cite{lepowsky1977generalization} it was demonstrated that for the
-highest weight module $L^{\mu }$ with $\mu \in P^{+}$ the sequence
-
+\section{БГГ резольвента и ветвление}
+В работе \cite{lepowsky1977generalization} показано, что для модуля старшего веса $L^{\mu }$, где $\mu \in P^{+}$, последовательность
 \begin{equation}
@@
 \end{equation}
-with
+где
 \begin{equation}
@@
 \end{equation}
-(the generalized BGG resolution) is exact and formula (\ref{gen Weyl-Verma}%
-) is a cosequence of this resolution.
+(обобщенная БГГ резольвента), является точной и формула (\ref{gen Weyl-Verma}%
+) следует из этого разложения.
 
@@
    \includegraphics[width=140mm]{B2_Exact.pdf}}
- \caption{Injection $A_1\hookrightarrow B_2$ (see Figure \ref{fig:B2_Verma_Decomp}).
- The orthogonal partner is $A_1$ corresponding to the root $\alpha_1$.
- The resolution of the simple module $L^{\omega_1}$.
- Presented is the central part of the exact sequence
+ \caption{Вложение $A_1\hookrightarrow B_2$ (см. Рисунок \ref{fig:B2_Verma_Decomp}). Ортогональный партнер -- это подалгебра $A_1$, соответствующая корню $\alpha_1$.
+   Резольвента простого модуля $L^{\omega_1}$. Показана центральная часть точной последовательности
    $0 \to Im(\delta_2) \to \left( e^{\mu _{\widetilde{%
@@
 \mathcal{D}_{\afb} }=M^{\omega_1}_{I}\right) \to
-   L^{\omega_1}\to 0 $.  Here $\mu _{\widetilde{\frak{a}}}\left( e\right) =\pi _{\aft}\left[ \mu \right] + \mathcal{D}_{\afb}$.
+   L^{\omega_1}\to 0 $.  Здесь $\mu _{\widetilde{\frak{a}}}\left( e\right) =\pi _{\aft}\left[ \mu \right] + \mathcal{D}_{\afb}$.
    }
@@
 \begin{statement}
-
-Let $L^{\mu }$ be the highest weight $\frak{g}$-module with $\mu \in P^{+}$
-,let its regular subalgebra $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$
-be orthogonal to a reductive subalgebra $\frak{a}\hookrightarrow \frak{g}$.
-Then the decomposition (\ref{sing decomp main}) defines both the generalized
-resolution of $L^{\mu }$ with respect to $\frak{a}_{\perp }$ and the
-branching rules for $L^{\mu }$ with respect to $\frak{a}$ .
+Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра $\mu \in P^{+}$ ортогональна редуктивной подалгебре $\frak{a}\hookrightarrow \frak{g}$.
+Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}$ .
 \end{statement}
@@
 \begin{proof}
-Put
+Положим
 \begin{equation*}
@@
 \end{equation*}
-with\ $\mu _{\widetilde{\frak{a}}}\left( u\right) ,\mu _{\frak{a}_{\perp
-}}\left( u\right) $ and $\mathcal{D}_{\frak{a}_{\perp }}$ as in Lemma \ref{Psi-decomp-lemma} and $%
-u\in U$ defined by (\ref{U-def}). This gives the elements of the filtration
-sequence (\ref{resolution sequence}).
+где \ $\mu _{\widetilde{\frak{a}}}\left( u\right) ,\mu _{\frak{a}_{\perp
+}}\left( u\right) $ и $\mathcal{D}_{\frak{a}_{\perp }}$ определены как в Лемме \ref{Psi-decomp-lemma}, а  $%
+u\in U$ определено формулой (\ref{U-def}). Тогда мы получаем элементы фильтрующей последовательности (\ref{resolution sequence}).
 
-Consider the set $\left\{ \mu _{\frak{a}_{\perp }}\left( u\right) |u\in
-U\right\} $ as the highest weights for the simple modules $L_{\frak{a}%
-_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ and evaluate their
-dimensions. Together with
+Рассмотрим множество $\left\{ \mu _{\frak{a}_{\perp }}\left( u\right) |u\in U\right\} $ как множество старших весов простых модулей $L_{\frak{a}%
+_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ и вычислим размерности этих модулей. Вместе с 
 $\left\{ \mu _{\widetilde{\mathfrak{a}}}\left( u\right) |u\in
-U\right\} $ this gives the set of singular weights
+U\right\} $ мы получим набор сингулярных весов
 \begin{equation*}
@@
 \end{equation*}
-The branching $L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu
-\in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ is
-then fixed by the injection fan $\Gamma _{\frak{a}\rightarrow \frak{g}}$ and
-the relation (\ref{recurrent rel}). The latter gives us the coefficients $k_{\xi
-}^{\left( \mu \right) }$ and thus defines $b_{\nu }^{\left( \mu \right) }$
-due to the property $b_{\nu }^{\left( \mu \right) }=k_{\nu }^{\left( \mu
-\right) }$ for $\nu \in \overline{C_{\frak{a}}}$ .
+Ветвление  $L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu
+\in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$  определяется веером вложения  $\Gamma _{\frak{a}\rightarrow \frak{g}}$ и соотношением (\ref{recurrent rel}), которое дает нам коэффициенты  $k_{\xi
+}^{\left( \mu \right) }$, а значит определяет и  $b_{\nu }^{\left( \mu \right) }$, так как  $b_{\nu }^{\left( \mu \right) }=k_{\nu }^{\left( \mu
+\right) }$ при $\nu \in \overline{C_{\frak{a}}}$ .
 \end{proof}
@@
 \begin{corollary}
-
-Let $L^{\mu }$ be the highest weight $\frak{g}$-module with $\mu \in P^{+}$
-and $\frak{a}\hookrightarrow \frak{g}$ -- a reductive subalgebra in $\frak{g}
-$. Let $\frak{a}_{\perp }$, the orthogonal partner for $\frak{a}$, be
-equivalent to $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, and $\widetilde{%
-\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ with $\frak{h=\frak{h}_{\frak{a}}%
-}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$. Let $L_{%
-\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }=\bigoplus\limits_{\nu \in P_{%
-\widetilde{\frak{a}}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\widetilde{\frak{a%
-}}}^{\nu }$ be the branching of $L^{\mu }$ with respect to $\widetilde{\frak{%
-a}}$. Then the branching coefficients $b_{\nu }^{\left( \mu \right) }$
-define the generalized resolution (\ref{resolution sequence}) of $L^{\mu }$
-with respect to $\frak{a}_{\perp }$.
+Пусть  $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$ и  $\frak{a}\hookrightarrow \frak{g}$ -- редуктивная подалгебры $\frak{g}$.
+Пусть $\frak{a}_{\perp }$ -- ортогональный партнер для $\frak{a}$, -- эквивалентен  $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, и $\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ с $\frak{h=\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$.
+Пусть $L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }=\bigoplus\limits_{\nu \in P_{\widetilde{\frak{a}}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\widetilde{\frak{a}}}^{\nu }$ -- ветвление модуля $L^{\mu }$ относительно подалгебры $\widetilde{\frak{%
+a}}$. Тогда коэффициенты $b_{\nu }^{\left( \mu \right) }$ определяют обобщенную резольвенту (\ref{resolution sequence}) модуля $L^{\mu }$
+по отношению к  $\frak{a}_{\perp }$.
 \end{corollary}
@@
 \begin{proof}
-Let $\alpha $ be the simple root of $A_{1}$. Use the Weyl transformations
-to identify it with some simple root of $\frak{g}$, say $\alpha _{1}$.
-Construct the singular element for the module $L_{\frak{g}\downarrow
-\widetilde{\frak{a}}}^{\mu }$, i.e. the $\Psi _{\widetilde{\frak{a}}%
+Пусть $\alpha $ -- простой корень  $A_{1}$.
+Используем преобразования из группы Вейля чтобы перевести его в некоторый простой корень алгебры $\frak{g}$, например $\alpha _{1}$.
+Построим сингулярный элемент для модуля  $L_{\frak{g}\downarrow
+\widetilde{\frak{a}}}^{\mu }$, то есть  $\Psi _{\widetilde{\frak{a}}%
 }^{\left( L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }\right)
@@
 }>0}b_{\nu }^{\left( \mu \right) }\Psi _{\widetilde{\frak{a}}}^{\left( \nu
-\right) }$ , and decompose it $\Psi _{\widetilde{\frak{a}}}^{\left( L_{\frak{%
+\right) }$, и разложим его $\Psi _{\widetilde{\frak{a}}}^{\left( L_{\frak{%
 g}\downarrow \widetilde{\frak{a}}}^{\mu }\right) }=k_{\xi }^{\left( \mu
-\right) }e^{\xi }$. In our case the representatives $u$ in the
-recurrent relation (\ref{recurrent rel}) are uniquely determined by the weight $\xi $:
+\right) }e^{\xi }$. В нашем случае представители $u$ в рекуррентном соотношении (\ref{recurrent rel}) определяются весом $\xi $ однозначно:
 \begin{equation*}
@@
 \end{equation*}
-We have
+Тогда
 \begin{equation*}
@@
 \end{equation*}
-and
+и
 \begin{equation*}
@@
 \end{equation*}
-The set of generalized Verma modules $e^{\xi +\mathcal{D}%
+Таким образом, множество обобщенных модулей Верма  $e^{\xi +\mathcal{D}%
 _{\frak{a}_{\perp }}}\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
-u\left( \xi \right) \right) }$ is thus fixed:
+u\left( \xi \right) \right) }$ теперь определено:
 \begin{equation*}
@@
 \end{equation*}
-Classifying these modules according to the length of $u$
-we get the components (\ref{Verma elements sequence}) of the resolution (\ref{resolution sequence}).
+Упорядочивая эти модули по длине $u$ мы получаем компоненты (\ref{Verma elements sequence}) резольвенты (\ref{resolution sequence}).
 \end{proof}
 
-\section{Conclusions}
+\section{Заключение}
 
 \label{sec:conclusions}
+В работе \cite{2010arXiv1007.0318L} было показано, что метод веера вложения работает также и для специальных вложений.
+Надо заметить, что в этом случае разложения Вейля-Верма тоже могут быть получены.
+Резольвенты, соответствующие специальным подалгебрам, описывают соотношения между проекциями характера начального модуля и обобщенными модулями Верма со старшими весами в подпространстве $h^*$.
 
-In \cite{2010arXiv1007.0318L} it was demonstrated that the injection fan
-recursive mechanism works also for special injections. It must be mentioned
-that in this case the Weyl-Verma decompositions can also be obtained. The
-resolutions corresponding to special subalgebras describe the relations
-between the projections of characters of the initial module and the generalized
-Verma modules with highest weights in the subspace of $h^*$.
+Рассмотрим ситуацию, когда выбор простых корней зафиксирован какими-то внешними факторами (возникающими, например, из требований физических приложений).
+В этом случае ортогональный партнер не может порождаться только простыми корнями.
+Элементы   $\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta
+^{+}\setminus \Delta _{I}^{+}}\frak{g}_{\eta }$ не образуют подалгебру в  $%
+\mathfrak{g}$, так как некоторые не простые корни отсутствуют в  $\Delta ^{+}\setminus
+\Delta _{I}^{+}$. Важно отметить, что в этом случае формула Вейля-Верма по-прежнему существует. В ней обобщенные модули Верма соответствуют сжатиями \cite{Doebner1967Melsheimer} алгебры $%
+\frak{n}^{+}$ и соотношения Вейля-Верма описывают разложение пространства представления $L^{\mu}$ в набор обобщенных модулей Верма сжатой алгебры  $U\left(\frak{n}_c^{+}\right)$.
+Весовые векторы образованы базисом Пуанкаре-Биркгофа-Витта алгебр $U\left(\frak{n}_c^{+}\right)$ и
+$U\left( \mathfrak{a}_{\bot} \right)$. Чтобы рассмотреть такое пространство как  $%
+\mathfrak{g}$-модуль мы должны выполнить деформацию \cite
+{Nijenhuis1966Richardson} алгебры $\frak{n}_c^{+}$ (то есть восстановить первоначальный закон композиции).
+Пространство сохраняется и после такой деформации генераторы начальной алгебры будут действовать на нем правильным образом.
 
-Consider the situation where the simple roots are prescribed by some
-external factors (originating in physical applications conditions, for
-example). In this case the orthogonal partner cannot be generated by simple
-root vectors only. The elements $\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta
-^{+}\setminus \Delta _{I}^{+}}\frak{g}_{\eta }$ do not form a subalgebra in $%
-\mathfrak{g}$ because some nonsimple roots are lost in $\Delta ^{+}\setminus
-\Delta _{I}^{+}$. It is important to indicate that in this case the
-Weyl-Verma formula still exists. In it the generalized Verma modules
-correspond to the contractions \cite{Doebner1967Melsheimer} of the algebra $%
-\frak{n}^{+}$ and the Weyl-Verma relations describe the decomposition of
-the representation space of $L^{\mu}$ into the set of generalized Verma
-modules of contracted algebra $U\left(\frak{n}_c^{+}\right)$. The weight
-vectors are formed by the PBW-basis of $U\left(\frak{n}_c^{+}\right)$ and of
-$U\left( \mathfrak{a}_{\bot} \right)$. To consider such space as a $%
-\mathfrak{g}$-module we must perform the deformation \cite
-{Nijenhuis1966Richardson} of the algebra $\frak{n}_c^{+}$ (and thus restore the
-initial composition law). The space survives and after such a deformation
-the initial algebra generators will act properly on it.
+\section{Благодарности}
+Авторы выражают свою искреннюю благодарность всем, кто подготовил и организовал III международную конференцию ``Модели квантовой теории поля 2010'', посвященную 70-летию А.Н. Васильева.
 
-\section{Acknowledgments}
-
-The authors express their sincere gratitude to all those who prepared and
-performed the III International Conference "Models in Quantum Field Theory -
-2010" dedicated to 70-th anniversary of A. N. Vassiliev.
-
-The work was supported in part by the RFFI grant N 09-01-00504 and by the Chebyshev Laboratory
-(Department of Mathematics and Mechanics, Saint-Petersburg State
-University) under the grant 11.G34.31.2006 of the Government of the
-Russian Federation.
+Данная работа была частично поддержана грантом РФФИ № 09-01-00504 и лабораторией имени Чебышева (математико-механический факультет СПбГУ) из средств гранта 11.G34.31.2006 правительства Российской Федерации.
 

### 2011-02-13 AffineLieAlgebras/MQFT2010/article-ru.tex
Translation sent.

@@
 \newtheorem{lemma}{Лемма}
-\newtheorem{mynote}{Замечание}[section]
 \theoremstyle{definition}
 \newtheorem{definition}{Определение}
-\newtheorem{remark}{Ремарка}
+\newtheorem{remark}{Замечание}
 \newtheorem{example}{Пример}
@@
 \end{equation*}
-а именно,
+а именно:
 \begin{equation}
@@
 
-В работе \cite{2010arXiv1007.0318L} разложение, аналогичное формуле (\ref{singular main}) было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
+В работе \cite{2010arXiv1007.0318L} разложение, аналогичное формуле (\ref{singular main}), было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
 \begin{equation}
@@
 g}}$ сдвигаются на $\gamma _{0}$ -- младший вектор в $\left\{ \xi
-\right\} $ -- и исключается нулевой элемент:
+\right\} $, и исключается нулевой элемент:
 \begin{equation}
@@
 %\bigskip
-Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характера интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) параболических модулей Верма, распределенных по множеству весов $e^{\mu _{\widetilde{\mathfrak{a}}}\left(
+Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характер интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) характеров параболических модулей Верма, распределенных по множеству весов $e^{\mu _{\widetilde{\mathfrak{a}}}\left(
 u\right) }$:
@@
 $ и $\left\{ x_{\eta }\in \frak{g}_{\eta }|\eta \in \Delta ^{+}\setminus
-\Delta _{I}^{+}\right\} $, и соответствующие нильпотентные подалгбры в  $\frak{n}%
+\Delta _{I}^{+}\right\} $, и соответствующие нильпотентные подалгебры в  $\frak{n}%
 ^{+}$:
@@
 \end{equation*}
-Первая подалгебра, вместе со своей отрицательной копией  $\frak{n}%
+Первая подалгебра вместе со своей отрицательной копией  $\frak{n}%
 _{I}^{-} $ порождает простую подалгебру 
@@
 \end{equation*}
-Полупрямое произведение  $\frak{l}_{I}$ и $\frak{u}_{I}^{+}$ дает параболическую подалгебры $\frak{p}_{I}\hookrightarrow \frak{g}$ :
+Полупрямое произведение  $\frak{l}_{I}$ и $\frak{u}_{I}^{+}$ дает параболическую подалгебру $\frak{p}_{I}\hookrightarrow \frak{g}$ :
 \begin{equation}
@@
 
-Это  \textit{обобщенные модули Верма}  \cite{lepowsky1977generalization}
+Это  \textit{обобщенные модули Верма}  \cite{lepowsky1977generalization},
 порожденные старшими весами  $\mu _{\frak{a}%
@@
 Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра $\mu \in P^{+}$ ортогональна редуктивной подалгебре $\frak{a}\hookrightarrow \frak{g}$.
-Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}$ .
+Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к подалгебре $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}$ .
 \end{statement}
@@
 \begin{corollary}
-Пусть  $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$ и  $\frak{a}\hookrightarrow \frak{g}$ -- редуктивная подалгебры $\frak{g}$.
+Пусть  $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$ и  $\frak{a}\hookrightarrow \frak{g}$ -- редуктивная подалгебра $\frak{g}$.
 Пусть $\frak{a}_{\perp }$ -- ортогональный партнер для $\frak{a}$, -- эквивалентен  $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, и $\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ с $\frak{h=\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$.
@@
 \end{equation*}
-Упорядочивая эти модули по длине $u$ мы получаем компоненты (\ref{Verma elements sequence}) резольвенты (\ref{resolution sequence}).
+Упорядочивая эти модули по длине $u$, мы получаем компоненты (\ref{Verma elements sequence}) резольвенты (\ref{resolution sequence}).
 \end{proof}
@@
 В работе \cite{2010arXiv1007.0318L} было показано, что метод веера вложения работает также и для специальных вложений.
-Надо заметить, что в этом случае разложения Вейля-Верма тоже могут быть получены.
+Надо заметить, что  разложения Вейля-Верма также могут быть получены в этом случае.
 Резольвенты, соответствующие специальным подалгебрам, описывают соотношения между проекциями характера начального модуля и обобщенными модулями Верма со старшими весами в подпространстве $h^*$.

### 2011-02-15 AffineLieAlgebras/MQFT2010/article-ru.tex
Translation corrected

@@
 \newtheorem{theorem}{Теорема}
-\newtheorem{corollary}{Следствие}[theorem]
+\newtheorem{corollary}{Следствие}
 \newtheorem{lemma}{Лемма}
@@
 \title{Рекурсивные свойства ветвления и БГГ резольвента}
-\author{В Д Ляховский$^1$, А А Назаров$^{2,3}$\\
+\author{В Д Ляховский$^1$, А А Назаров$^{1,2}$\\
   {\small $^1$ Теоретический отдел,}\\
-  {\small Санкт - Петербургский государственный университет}\\
-  {\small 198904, Санкт - Петербург, Россия}\\
-  {\small e-mail: lyakh1507@nm.ru}\\
-  {\small $^2$ Теоретический отдел,}\\
   {\small Санкт - Петербургский государственный университет}\\
@@
   {\small Санкт - Петербургский государственный университет}\\
-  {\small 199178, Санкт - Петербург, Россия}\\
-  {\small email: antonnaz@gmail.com}}
+  {\small 199178, Санкт - Петербург, Россия}\\[5mm]
+  {\small e-mails: lyakh1507@nm.ru \quad antonnaz@gmail.com}}
 
@@
 Свойства ветвления (аффинных) алгебр Ли важны для приложений в квантовой теории поля (смотри, например, модели конформной теории поля \cite{difrancesco1997cft},\cite{coquereaux2008conformal}).
-В данной работе мы показываем, что ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и проявляет свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).
+В данной работе мы показываем, что ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и демонстрирует свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).
 
@@
 Чтобы продемонстрировать связь БГГ резольвенты с ветвлением мы используем рекурсивный подход, представленный в работе \cite
-{2010arXiv1007.0318L} (похожий подход для максимальных вложений использовался в работе \cite{ilyin812pbc}).
-Мы рассматриваем подалгебру $\af \hookrightarrow \gf$ вместе с $\afb$ -- ``ортогональным партнером'' $\af$ по отношению к форме Киллинга, а также  $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$, где $\frak{h}=\frak{\frak{h}_{\af}}\oplus
-\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. Для любой редуктивной подалгебры $\af$ подалгебра $\afb\hookrightarrow \gf$ регулярна и редуктивна. Для интегрируемого модуля старшего веса $%
+{2010arXiv1007.0318L} (аналогичный подход для максимальных вложений использовался в работе \cite{ilyin812pbc}).
+Мы рассматриваем подалгебру $\af \hookrightarrow \gf$ вместе с $\afb$ -- ``ортогональным партнером'' $\af$ по отношению к форме Киллинга, а также подалгебру $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$, где $\frak{h}=\frak{\frak{h}_{\af}}\oplus
+\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. Для любой редуктивной подалгебры $\af$ алгебра $\afb\hookrightarrow \gf$ регулярна и редуктивна. Для интегрируемого модуля старшего веса $%
 L^{\left(\mu \right) }$ и ортогональной подалгебры  $\af_{\bot }$ мы рассматриваем сингулярный элемент $\Psi ^{\left( \mu \right) }$ (числитель в формуле Вейля для характеров $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
@@
 \afb}}$, так что исходный характер $ch\left(
-L^{\mu }\right) $ в итоге раскладывается в чередующуюся сумму таких модулей.
+L^{\mu }\right) $ в итоге раскладывается в знакопеременную сумму таких модулей.
 С другой стороны, если параболическое условие нарушено, конструкция сохраняется и порождает разложение по отношению к набору обобщенных модулей Верма  $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
@@
 
-Некоторые общие свойства предложенного разложения формулируются в терминах определенного формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''.
+Некоторые общие свойства предложенного разложения формулируются в терминах  формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''.
 Использование этого инструмента позволило сформулировать простой и явный алгоритм для вычисления правил ветвления, подходящий для произвольной (максимальной или не максимальной) подалгебры в аффинной алгебре Ли \cite{2010arXiv1007.0318L}.
@@
 \label{sec:notation}
-Пусть $\frak{g}$ и $\frak{a}$ -- (аффинные) алгебры Ли, а вложение  $\frak{a}\hookrightarrow \frak{g}$ таково, что  $\frak{a}$ -- редуктивная подалгебра в  $\frak{a\subset g}$ с согласованным корневым пространством: $\frak{%
+Пусть $\frak{g}$ и $\frak{a}$ -- (аффинные) алгебры Ли, и существует вложение  $\frak{a}\hookrightarrow \frak{g}$ такое, что  $\frak{a}$ -- редуктивная подалгебра в $\frak{g}$ с согласованным корневым пространством: $\frak{%
 h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g}}^{\ast }$. Мы используем следующие обозначения:
@@
 Рассмотрим редуктивную алгебру Ли  $\frak{g}$ и ее редуктивную подалгебру $\frak{a}\subset \frak{g}$.
-Пусть  $L^{\mu} $ -- интегрируемый модуль старшего веса алгебры  $\frak{g}$, $\mu \in P^{+}$.  Будем считать  $L^{\mu}$ полностью приводимым по отношению к подалгебре $\frak{a}$,
+Пусть  $L^{\mu} $ -- интегрируемый модуль старшего веса алгебры  $\frak{g}$, $\mu \in P^{+}$.  Будем считать  $L^{\mu}$ вполне приводимым по отношению к подалгебре $\frak{a}$,
 \begin{equation*}
@@
 \end{equation*}
-и корни  $\frak{g}$ (соответственно, положительные корни)  ортогональные к $\frak{a}$,
+и корни  $\frak{g}$ (соответственно, положительные корни),  ортогональные к $\frak{a}$,
 \begin{eqnarray}
@@
 \end{eqnarray}
-Обозначим через  $W_{\frak{a}_{\perp }}$ подгруппу  $W$, порожденную отражениями  $w_{\beta }$ с корнями  $\beta \in \Delta_{\frak{a}_{\perp}}^{+}$.
+Обозначим символом  $W_{\frak{a}_{\perp }}$ подгруппу  $W$, порожденную отражениями  $w_{\beta }$ с корнями  $\beta \in \Delta_{\frak{a}_{\perp}}^{+}$.
 Корневая подсистема  $\Delta _{\frak{a}_{\perp }}$ определяет подалгебру  $\frak{a}_{\perp }$, имеющую подалгебру Картана $\frak{h}_{\frak{a}_{\perp }}$.
@@
 }|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
-h\right) =0\right\}
+h\right) =0\right\};
 \end{equation*}
-и у  $\frak{g}$ есть подалгебры
+выделим в  $\frak{g}$  подалгебры
 \begin{eqnarray}
-\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp },
 \qquad
@@
 \end{equation}
-Для  $\mu \in P^{+}$ рассмотрим связанные веса  $\left\{\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ и их проекции на $h_{\frak{a}_{\perp }}^{\ast }$, дополнительно сдвинутые на дефект $-\mathcal{D}_{\frak{a}_{\perp }}$:
+Для  $\mu \in P^{+}$ рассмотрим связанные веса  $\left\{\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ и их проекции на $h_{\frak{a}_{\perp }}^{\ast }$, дополнительно сдвинутые на вектор дефекта $-\mathcal{D}_{\frak{a}_{\perp }}$:
 \begin{equation*}
@@
 \end{equation}
-Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}), чтобы упростить первую строчку в формуле (\ref{sing-decomp-1}):
+Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}), чтобы упростить первую строку в формуле (\ref{sing-decomp-1}):
 \[
@@
 \]
-и вторую
+и вторую строку
 \[
@@
 \begin{remark}
-Это соотношение можно рассматривать как обобщенную форму формулы Вейля для сингулярного элемента $\Psi _{\frak{g}}^{\mu }$: векторы $\mu _{%
-\widetilde{\mathfrak{a}}}\left( u\right) $ играют роль сингулярных весов, а чередующиеся множители  $\epsilon (u)$ расширены до $\epsilon
+Это соотношение можно рассматривать как обобщение формулы Вейля для сингулярного элемента $\Psi _{\frak{g}}^{\mu }$: векторы $\mu _{%
+\widetilde{\mathfrak{a}}}\left( u\right) $ играют роль сингулярных весов, в то время как множители  $\epsilon (u)$ расширены до $\epsilon
 (u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$.
@@
 \frak{h}_{\perp }^{\ast }=0$, $\frak{a}_{\perp }=\frak{g}$, $\mathcal{D}_{%
-\frak{a}_{\perp }}=0$ и $U=W/W_{\frak{a}_{\perp }}=e$, опять восстанавливается сингулярный элемент
- $\Psi ^{\mu }$, теперь в результате тривиализации множества векторов $\mu _{\af}\left( e\right) =0$.
+\frak{a}_{\perp }}=0$ и $U=W/W_{\frak{a}_{\perp }}=e$, вновь приходим к выражению для  сингулярного элемента
+ $\Psi ^{\mu }$, теперь -- в результате тривиализации множества векторов $\mu _{\af}\left( e\right) =0$.
 \end{remark}
@@
 \end{equation}
-Рекурсия задается множеством  $\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}$, называемом веером вложения.
+Рекурсия задается множеством  $\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}$, которое носит название веера вложения.
 Это множество определяется как носитель  $\left\{ \xi \right\}_{\frak{a}\rightarrow \frak{g}}$  коэффициентной функции $s(\xi )$
@@
 _{\frak{a}}(\pi _{\widetilde{\frak{a}}}\alpha )}=-\sum_{\gamma \in P_{%
-\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma };\quad
+\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma }.\quad
 \end{equation}
@@
 %\bigskip
-Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характер интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) характеров параболических модулей Верма, распределенных по множеству весов $e^{\mu _{\widetilde{\mathfrak{a}}}\left(
-u\right) }$:
+Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характер интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) характеров параболических модулей Верма, распределенных по множеству весов $\mu _{\widetilde{\mathfrak{a}}}\left(
+u\right)$:
 \begin{equation}
@@
 \end{equation*}
-Значит мы получили обобщенную формулу Вейля-Верма для характеров -- разложение  $\mathrm{ch}\left(
+Таким образом мы получили обобщенную формулу Вейля-Верма для характеров -- разложение  $\mathrm{ch}\left(
 L^{\mu }\right) $ на характеры обобщенных модулей Верма:
@@
 \begin{remark}
-Здесь обобщенная формула Вейля-Верма для характеров (называемая формулой переменного суммирования в книге \cite{humphreys2008representations}) имеет специальный вид: веса $\mu _{\aft}$ и старшие веса обобщенных модулей Верма $\mu _{\afb}$ разделены.
-Причина в том, что старший вес $M_{I}$-модуля не равен проекции его максимального веса на  $h^*_{\afb}$ (а должен быть дополнительно сдвинут на дефект).
+Здесь обобщенная формула Вейля-Верма для характеров (называемая формулой переменного суммирования в книге \cite{humphreys2008representations}) имеет специальный вид: веса $\mu _{\aft}$ отличны от старших весов обобщенных модулей Верма $\mu _{\afb}$.
+Причина в том, что старший вес $M_{I}$-модуля не равен проекции его максимального веса на  $h^*_{\afb}$ (он должен быть дополнительно сдвинут на дефект).
 \end{remark}
@@
     Простые корни $\alpha_1, \alpha_2$ алгебры $B_2$ показаны пунктирными стрелками.
-Простой корень  $\beta = \alpha_1+2\alpha_2$ алгебры $A_1$ показан серым вектором.
+Простой корень  $\beta = \alpha_1+2\alpha_2$ алгебры $A_1$ изображен серым вектором.
 Разложение $L^{\omega_{1}}$ представлено набором контуров входящих в него обобщенных модулей Верма.
@@
 \section{БГГ резольвента и ветвление}
-В работе \cite{lepowsky1977generalization} показано, что для модуля старшего веса $L^{\mu }$, где $\mu \in P^{+}$, последовательность
+В работе \cite{lepowsky1977generalization} показано, что для модуля старшего веса $L^{\mu }$, где $\mu \in P^{+}$, последовательность (обобщенная БГГ резольвента)
 \begin{equation}
@@
 \end{equation}
-(обобщенная БГГ резольвента), является точной и формула (\ref{gen Weyl-Verma}%
+является точной и формула (\ref{gen Weyl-Verma}%
 ) следует из этого разложения.
@@
    \includegraphics[width=140mm]{B2_Exact.pdf}}
- \caption{Вложение $A_1\hookrightarrow B_2$ (см. Рисунок \ref{fig:B2_Verma_Decomp}). Ортогональный партнер -- это подалгебра $A_1$, соответствующая корню $\alpha_1$.
+ \caption{Вложение $A_1\hookrightarrow B_2$ (см. Рисунок \ref{fig:B2_Verma_Decomp}). Ортогональный партнер, подалгебра $A_1$, соответствует корню $\alpha_1$.
    Резольвента простого модуля $L^{\omega_1}$. Показана центральная часть точной последовательности
@@
 \begin{statement}
-Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра $\mu \in P^{+}$ ортогональна редуктивной подалгебре $\frak{a}\hookrightarrow \frak{g}$.
-Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к подалгебре $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}$ .
+Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра  $\afb\hookrightarrow \frak{g}$ ортогональна редуктивной подалгебре $\frak{a}\hookrightarrow \frak{g}$.
+Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\afb$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к подалгебре $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}$ .
 \end{statement}
@@
 e\right) }\mathrm{ch}M_{I}^{\pi _{\frak{a}_{\perp }}\left[ \mu \right] -%
-\mathcal{D}_{\frak{a}_{\perp }}}
+\mathcal{D}_{\frak{a}_{\perp }}},
 \end{equation*}
 где \ $\mu _{\widetilde{\frak{a}}}\left( u\right) ,\mu _{\frak{a}_{\perp
-}}\left( u\right) $ и $\mathcal{D}_{\frak{a}_{\perp }}$ определены как в Лемме \ref{Psi-decomp-lemma}, а  $%
-u\in U$ определено формулой (\ref{U-def}). Тогда мы получаем элементы фильтрующей последовательности (\ref{resolution sequence}).
+}}\left( u\right) $ и $\mathcal{D}_{\frak{a}_{\perp }}$ заданы как в Лемме \ref{Psi-decomp-lemma}, $%
+u\in U$ определено формулой (\ref{U-def}). В результате получим элементы фильтрующей последовательности (\ref{resolution sequence}).
 
@@
 Пусть  $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$ и  $\frak{a}\hookrightarrow \frak{g}$ -- редуктивная подалгебра $\frak{g}$.
-Пусть $\frak{a}_{\perp }$ -- ортогональный партнер для $\frak{a}$, -- эквивалентен  $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, и $\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ с $\frak{h=\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$.
+Пусть $\frak{a}_{\perp }$, ортогональный партнер для $\frak{a}$, эквивалентен  $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, и $\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ с $\frak{h=\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$.
 Пусть $L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }=\bigoplus\limits_{\nu \in P_{\widetilde{\frak{a}}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\widetilde{\frak{a}}}^{\nu }$ -- ветвление модуля $L^{\mu }$ относительно подалгебры $\widetilde{\frak{%
@@
 _{\frak{a}_{\perp }}}\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
-u\left( \xi \right) \right) }$ теперь определено:
+u\left( \xi \right) \right) }$ полностью фиксировано:
 \begin{equation*}
@@
 {Nijenhuis1966Richardson} алгебры $\frak{n}_c^{+}$ (то есть восстановить первоначальный закон композиции).
-Пространство сохраняется и после такой деформации генераторы начальной алгебры будут действовать на нем правильным образом.
+Пространство сохраняется, и после такой деформации генераторы начальной алгебры будут действовать на нем правильным образом.
 

### 2011-02-16 AffineLieAlgebras/CPC/article.tex
CPC paper started

--- 2010-12-17 AffineLieAlgebras/MQFT2010/article.tex
@@
 
-\title{Recursive properties of branching and Weyl-Verma formulas}
-\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
+\title{{\bf Affine.m} -- {\it Mathematica} package for Lie algebras of finite, affine and extended affine type}
+\author{A A Nazarov$^{1,2}$\\
+{\small $^1$ Theoretical Department, SPb State University}\\
+{\small 198904, Sankt-Petersburg, Russia}\\
+{\small$^{2}$ Chebyshev Laboratory,}\\
+{\small Department of Mathematics and Mechanics, SPb State University}\\
+{\small 199178, Saint-Petersburg, Russia}\\
+{\small email: antonnaz@gmail.com}}
 
@@
 \begin{abstract}
-Recurrent relations for branching coefficients are based on a special type of
-singular element decomposition. We show that this decomposition can be used to
-construct the parabolic Verma modules and finally to obtain the generalized
-Weyl-Verma formulas for characters.
-These Weyl-Verma formulas explicitly exhibit how branching and the generalized
-BGG-resolution properties are connected.
+  We present {\it Mathematica} package for computations in the representation theory of Lie algebras of finite, affine and extended affine types. 
 \end{abstract}
@@
 \section{Introduction}
-
-\label{sec:introduction}
-
-Branching properties of Lie (affine Lie) algebras are highly important for
-applications in quantum field theory (see for example the conformal field
-theory models \cite{difrancesco1997cft},\cite{coquereaux2008conformal}). In
-this paper we demonstrate that for an arbitrary reductive subalgebra
-branching is directly connected with the BGG resolution and in particular
-exhibits the resolution properties in terms of the $\mathcal{O}^{p}$
-category \cite{lepowsky1977generalization} (the parabolic generalization of
-the cathegory $\mathcal{O}$ \cite{bernstein1976category}).
-
-The resolution of the irreducible modules in terms of infinite-dimensional ones is important for the
-theory of integrable spin chains \cite{derk1008}. In the Baxter $\mathcal{Q}$-operator approach the generic transfer
-matrices corresponding to the (generalized) Verma modules are factorized into the product of Baxter
-operator. Then the resolution allows to calculate the transfer matrices for finite-dimensional
-auxiliary spaces.
-
-To show the connection of the BGG resolution with the branching we use the recursive approach presented in \cite
-{2010arXiv1007.0318L} (similar to the one used in \cite{ilyin812pbc} for
-maximal embeddings). We consider the subalgebra $\af$ together with its
-counterpart $\afb$ ''orthogonal'' to $\af$ with respect to
-the Killing form and also $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\af}}\oplus
-\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. For any reductive
-algebra $\af$ the subalgebra $\afb\hookrightarrow \gf$
-is regular and reductive. For a highest weight integrable module $%
-L^{\left(\mu \right) }$ and orthogonal subalgebra $\af_{\bot }$ we
-consider the singular element $\Psi ^{\left( \mu \right) }$ (the numerator
-in the Weyl character formula $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
-\mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite
-{humphreys1997introduction}) the Weyl denominator $\Psi _{\af_{\bot
-}}^{\left( 0\right) }$ for the orthogonal subalgebra and the projection $%
-\Psi _{\left( \af,\af_{\bot }\right) }^{\left( \mu \right) }=\pi _{%
-\af}\frac{\Psi _{\gf}^{\left( \mu \right) }}{\Psi _{\af_{\bot
-}}^{\left( 0\right) }}$. It is shown that the element $\Psi _{\gf%
-}^{\left( \mu \right) }$ can be decomposed into a combination of Weyl
-numerators $\Psi _{\af_{\bot }}^{\left( \nu \right) }$ with $\nu \in P_{%
-\mathfrak{a}_{\bot}}^{+}$. This decomposition provides the possibility to
-construct the set of highest weight modules $L_{\widetilde{\afb}%
-}^{\mu _{\widetilde{\afb}}}$. When the injection \ $\af%
-_{\bot }\hookrightarrow \gf$ \ satisfies the ''standard parabolic''
-conditions these modules give rise to the parabolic Verma modules $M_{\left(
-\widetilde{\afb}\hookrightarrow \gf\right) }^{\mu _{%
-\widetilde{\afb}}}$ so that the initial character $ch\left(
-L^{\mu }\right) $ is finally decomposed into the alternating sum of such. On
-the other hand when the parabolic conditions are violated the construction
-survives and exhibits a decomposition with respect to a set of Verma
-modules $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
-\widetilde{\afb}}}$. In such a situation the algebra $%
-\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in $\gf$ but a
-contraction of $\widetilde{\afb}$.
-
-Some general properties of the proposed decompositions are formulated in
-terms of a specific element $\Gamma _{\af\rightarrow \gf}$ of the
-group algebra $\mathcal{E}\left( \gf\right) $ called ''the injection
-fan''. Using this tool the simple and explicit algorithm for branching
-coefficients computations applicable for an arbitrary (maximal or
-nonmaximal) subalgebras of finite-dimensional or affine Lie algebras was
-obtained in \cite{2010arXiv1007.0318L}.
-
-Possible further developments are presented in Section \ref{sec:conclusions}.
-
-\subsection{Notation}
-
-\label{sec:notation}
-
-Consider Lie algebras (affine Lie algebras) $\gf$ and $\af$ and an
-injection $\af\hookrightarrow \gf$ such that $\af$ is a
-reductive subalgebra $\frak{a\subset g}$ with correlated root spaces: $\frak{%
-h}_{\af}^{\ast }\subset \frak{h}_{\gf}^{\ast }$. We use the
-following notations:
-
-$\frak{g=n}^{-}+\frak{b}+\frak{n}^{+}$ --- the Cartan decomposition;
-
-$r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\gf$ $%
-\left( \mathrm{{resp. }\af}\right) $ ;
-
-$\Delta $ $\left( \Delta _{\af}\right) $--- the root system; $\Delta
-^{+} $ $\left( \mathrm{{resp. }\Delta _{\af}^{+}}\right) $--- the
-positive root system (of $\gf$ and $\af$ respectively);
-
-$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\af}\left(
-\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $%
-\Delta $ (resp. in $\left( \Delta _{\af}\right) $);
-
-$S\quad \left( S_{\af}\right) $ --- the system of simple roots (of $%
-\gf$ and $\af$ respectively);
-
-$\alpha _{i}$ , $\left( \alpha _{\left( \af\right) j}\right) $ --- the $%
-i$-th (resp. $j$-th) basic root for $\gf$ $\left( \mathrm{{resp.}\frak{a%
-}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
-
-$\delta $ --- the imaginary root of $\gf$ (and of $\af$ if any);
-
-$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \af\right) j}^{\vee
-}\right) $--- the basic coroot for $\gf$ $\left( \mathrm{{resp.}\af%
-}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
-
-$W$ , $\left( W_{\af}\right) $--- the corresponding Weyl group;
-
-$C$ , $\left( C_{\af}\right) $--- the fundamental Weyl chamber;
-
-$\bar{C}, \left(\bar{C_{\af}}\right)$ --- the closure of the
-fundamental Weyl chamber;
-
-$\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;
-
-$\rho $\ , $\left( \rho _{\af}\right) $\ --- the Weyl vector;
-
-$L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
-of $\gf$ with the highest weight $\mu $\ ; (resp. integrable $\af$
--module with the highest weight $\nu $ );
-
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\af}^{\nu }\right) $ ---
-the weight diagram of $L^{\mu }$ (resp. ${}L_{\af}^{\nu }$ );
-
-$P$ (resp. $P_{\af} $) \ --- the weight lattice;
-
-$P^{+}$ (resp. $P_{\af}^{+} $) \ --- the dominant weight lattice;
-
-$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
-}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
-resp. }\in P_{\af}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
-L_{\af}^{\nu } $);
-
-$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\af}^{\nu
-}\right) $)--- the formal character of $L^{\mu }$ (resp. $L_{\af}^{\nu
-} $);
-
-$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
-+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
-\mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;
-
-$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
-mult}\left( \alpha \right) }}\quad $ (resp. $R_{\af}:=\prod_{\alpha \in
-\Delta _{\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af%
-}\left( \alpha \right) } $)--- the Weyl denominator.
-
-\section{Orthogonal subalgebra and singular elements}
-
-\label{sec:recurr-form-branch}
-
-In this section we shall show how the recurrent approach to branching
-problem leads naturally to a presentation of the formal character in terms
-of parabolic (generalized) Verma modules. Consider a reductive Lie algebra $%
-\gf$ and its reductive subalgebra $\af\subset \gf$. Let $%
-L^{\mu} $ be the highest weight integrable module of $\gf$, $\mu \in
-P^{+}$. Let $L^{\mu }$ be completely reducible with respect to $\af$,
-\begin{equation*}
-L_{\gf\downarrow \af}^{\mu }=\bigoplus\limits_{\nu \in P_{\af%
-}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
-\end{equation*}
-Using the projection operator $\pi _{\af}$ (to the weight space $\frak{%
-h_{a}}^{\ast }$) one can rewrite this decomposition in terms of formal
-characters:
-\begin{equation}
-\pi _{\af}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\af%
-}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\af}^{\nu }\right) .
-\label{branching1}
-\end{equation}
-The module $L^{\mu }$ has the BGG-resolution (see \cite
-{bernstein1976category,bernstein1975differential,bernstein1971structure} and
-\cite{humphreys2008representations}). All the members of the filtration
-sequence are the direct sums of Verma modules and all their highest weights $%
-\nu $ are strongly linked to $\mu $:
-\begin{equation*}
-\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
-W\right\} .
-\end{equation*}
-
-\subsection{Orthogonal subalgebra}
-
-Let $\frak{h}_{\af}$ be a Cartan subalgebra of $\mathfrak{g}$. For $%
-\mathfrak{a}\hookrightarrow \gf$ introduce the ''orthogonal partner'' $%
-\mathfrak{a}_{\bot }\hookrightarrow \gf$ .
-
-Consider the root subspace $\frak{h}_{\perp \af}^{\ast }$ orthogonal to
-$\af$,
-\begin{equation*}
-\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
-h\in \frak{h}_{\af};\eta \left( h\right) =0\right\} ,
-\end{equation*}
-and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
-to $\af$,
-\begin{eqnarray}
-\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
-h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
-\label{delta a ort} \\
-\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
-}^{+}|\forall h\in \frak{h}_{\af};\beta ^{+}\left( h\right) =0\right\} .
-\notag
-\end{eqnarray}
-Let $W_{\afb}$ be the subgroup of $W$ generated by the
-reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\afb}^{+}$ . The subsystem $\Delta _{\afb}$ determines the
-subalgebra $\afb$ with the Cartan subalgebra $\frak{h}_{\af%
-_{\perp }}$. Let
-\begin{equation*}
-\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
-}|\forall h\in \frak{h}_{\af\oplus \afb};\eta \left(
-h\right) =0\right\}
-\end{equation*}
-so that $\gf$ has the subalgebras
-\begin{eqnarray*}
-\widetilde{\afb} &:&=\afb\oplus \frak{h}_{\perp }
-\\
-\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
-\end{eqnarray*}
-Notice that $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ in general is not a
-subalgebra of $\mathfrak{g}$
-
-For the Cartan subalgebras we have the decomposition
-\begin{equation}
-\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\afb}\oplus
-\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
-\afb}=\frak{\frak{h}_{\widetilde{\afb}}}\oplus
-\frak{h}_{\af}.
-\end{equation}
-For the subalgebras $\af$ and $\afb$ consider the
-corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\afb} $ . Form the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
-D}_{\afb}$ of the injection:
-\begin{equation}
-\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
-\end{equation}
-\begin{equation}
-\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
-_{\perp }}\rho .  \label{defect ort}
-\end{equation}
-
-For the highest weight $\mu \in P^{+}$ consider the linked weights $\left\{
-\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections to
-$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
-\mathcal{D}_{\afb}$:
-\begin{equation*}
-\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
-w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
-\end{equation*}
-For $\mu \in P^{+}$ among the weights $\left\{ \mu _{\afb}\left( w\right) |w\in W\right\} $ one can always choose those located in
-the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
-set of representatives $u$ for the classes $W/W_{\afb}$ such
-that
-
-\begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
-\overline{C_{\afb}}\right\} \quad .  \label{U-def}
-\end{equation}
-Thus we can select the following subsets:
-\begin{equation}
-\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
-\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
-_{\perp }},\quad u\in U,  \label{mu-a}
-\end{equation}
-and
-\begin{equation}
-\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
-\label{mu-a-tilda}
-\end{equation}
-
-Note that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
-since it is built on the roots of the algebra $\mathfrak{g}$.
-
-For the modules we are interested in the Weyl-Kac formula for $\mathrm{ch}%
-\left( L^{\mu }\right) $ can be written in terms of singular elements \cite
-{humphreys1997introduction}
-\begin{equation*}
-\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
-)-\rho },
-\end{equation*}
-namely,
-\begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
-^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
-\label{Weyl-Kac2}
-\end{equation}
-The same is true for the submodules $\mathrm{ch}\left( L_{\af}^{\nu
-}\right) $ in (\ref{branching1})
-\begin{equation*}
-\mathrm{ch}\left( L_{\af}^{\nu }\right) =\frac{\Psi _{\af}^{\left(
-\nu \right) }}{\Psi _{\af}^{\left( 0\right) }}=\frac{\Psi _{\af%
-}^{\left( \nu \right) }}{R_{\af}},
-\end{equation*}
-with
-\begin{equation*}
-\Psi _{\af}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\af%
-}}\epsilon (w)e^{w(\nu +\rho _{_{\af}})-\rho _{_{\af}}}.
-\end{equation*}
-
-Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
-we get the relation connecting the singular elements $\Psi ^{\left( \mu
-\right) }$ and $\Psi _{\af}^{\left( \nu \right) }$ :
-\begin{eqnarray}
-\pi _{\af}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
-)-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
-(\alpha )}}\right) &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{%
-\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{\af})-\rho _{%
-\af}}}{\prod_{\beta \in \Delta _{\af}^{+}}(1-e^{-\beta })^{\mathrm{%
-mult}_{\af}(\beta )}},  \notag  \label{eq:4} \\
-\pi _{\af}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
-&=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\af%
-}^{\left( \nu \right) }}{R_{\af}}.
-\end{eqnarray}
-
-\subsection{Decomposing the singular element.}
-
-\label{subsec:decomp-sing-element}
-
-Now we shall perform a decomposition of the singular element $\Psi ^{\left(
-\mu \right) }$ in terms of singular elements of the orthogonal subalgebra
-modules:
-
-\begin{lemma}
-Let $\af_{\bot }$ be the orthogonal partner of a reductive subalgebra $%
-\af\hookrightarrow \gf$ with $\frak{h}=\frak{\frak{h}_{\af}}%
-\oplus \frak{h}_{\afb}\oplus \frak{h}_{\perp }$, $\widetilde{%
-\afb}=\afb\oplus \frak{h}_{\perp }$ and $%
-\widetilde{\af}=\af\oplus \frak{h}_{\perp }$.
-
-$L^{\mu }$ be the highest weight integrable module with $\mu \in P^{+}$ and
-
-$\Psi ^{\left( \mu \right) }$\ -- the singular element of $L^{\mu }$.
-
-Then the element $\Psi ^{\left( \mu \right) }$ can be decomposed into the
-sum over $u\in U$ (see (\ref{U-def})) of singular elements $\Psi _{\af%
-_{\perp }}^{\mu _{\afb}\left( u\right) }$ with the coefficients
-$\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
-\begin{equation}
-\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\widetilde{%
-\mathfrak{a}}}\left( u\right) }\Psi _{\afb}^{\mu _{\af%
-_{\perp }}\left( u\right) }.  \label{sing decomp main}
-\end{equation}
-\end{lemma}
-
-\begin{proof}
-With $u\in U$ and $v\in W_{\af_{\bot }}$ perform the decomposition
-\[
-u(\mu +\rho )=\pi _{\left( \aft\right) }u(\mu +\rho )+\pi _{\left(
-\afb\right) }u(\mu +\rho )
-\]
-for the singular weight $vu(\mu +\rho )-\rho $:
-\begin{equation}
-\begin{array}{lcl}
-vu(\mu +\rho )-\rho  & = & \pi _{\left( \af\right) }\left( u(\mu +\rho
-)\right) -\rho +\rho _{\afb}
-\\
-&  & +\ v\left( \pi _{\left( \aft_{\perp }\right) }u(\mu
-+\rho )-\rho _{\afb}+\rho _{\afb}\right) -\rho _{%
-\afb} .
-\end{array}
-\label{sing-decomp-1}
-\end{equation}
-Use the defect $\mathcal{D}_{\af_{\bot }}$ (\ref{defect ort}) to
-simplify the first line in (\ref{sing-decomp-1}):
-\[
-\begin{array}{r}
-\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
-\afb}= \\
-\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\pi _{\aft%
-}\rho -\pi _{\af_{\bot }}\rho +\rho _{\af_{\bot }}= \\
-=\pi _{\left( \aft\right) }\left( u(\mu +\rho )-\rho \right) +\mathcal{D}%
-_{\af_{\bot }},
-\end{array}
-\]
-and the second one:
-\[
-\begin{array}{c}
-v\left( \pi _{\left( \afb\right) }u(\mu +\rho
-)-\rho _{\afb}+\rho _{\afb}\right) -\rho _{\af%
-_{\perp }}= \\
-v\left( \pi _{\left( \af_{\bot }\right) }u(\mu +\rho )-%
-\mathcal{D}_{\af_{\bot }}-\pi _{\left( \af_{\bot }\right) }\rho
-+\rho _{\af_{\bot }}\right)
--\rho _{\af_{\bot }}= \\
-=v\left( \pi _{\left( \af_{\bot }\right) }\left[ u(\mu
-+\rho )-\rho \right] -\mathcal{D}_{\af_{\bot }}+\rho _{\af_{\bot
-}}\right) -\rho _{\af_{\bot }}.
-\end{array}
-\]
-These expressions provide the desired decomposition of the singular element $%
-\Psi ^{\mu }$ in terms of singular elements $\Psi _{\af%
-_{\perp }}^{\eta }$ of the $\afb$-modules $L_{%
-\afb}^{\eta }$:
-\begin{equation}
-\begin{array}{l}
-\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\afb}}\epsilon
-(v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
-=\sum_{u\in U}\epsilon (u)e^{\pi _{\aft}\left[ u(\mu +\rho )-\rho \right]
-+\mathcal{D}_{\afb}}\sum_{v\in W_{\afb}}\epsilon
-(v)e^{v\left( \pi _{\left( \afb\right) }\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb}+\rho _{\af%
-_{\perp }}\right) -\rho _{\afb}}= \\
-=\sum_{u\in U}\;\epsilon (u)\Psi _{\afb}^{\pi
-_{\left( \afb\right) }\left[ u(\mu +\rho )-\rho
-\right] -\mathcal{D}_{\afb}}e^{\pi _{\left( \aft\right) }%
-\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}}.
-\end{array}
-\label{singular main}
-\end{equation}
-\end{proof}
-
-\bigskip
-
-\begin{remark}
-This relation can be considered as a generalized form of the Weyl formula
-for the singular element $\Psi _{\gf}^{\mu }$: the vectors $\mu _{%
-\widetilde{\mathfrak{a}}}\left( u\right) $ play the role of singular weights
-while the alternating factors $\epsilon (u)$ are extended to $\epsilon
-(u)\Psi _{\afb}^{\mu _{\afb}\left( u\right) }$. In
-fact when $\frak{a=g}$ both $\afb$and $\frak{h}_{\perp }$are
-zeros, $U=W$, and\ the original Weyl formula is reobtained via the
-trivilization of the singular elements: $\epsilon (u)\Psi _{\afb}^{\mu _{\afb}\left( u\right) }=\epsilon (u)$. In the opposite
-limit when $\frak{a=0}$, $\Delta _{\afb}=\Delta _{\gf}$, $%
-\frak{h}_{\perp }^{\ast }=0$, $\afb=\gf$, $\mathcal{D}_{%
-\afb}=0$, $U=W/W_{\afb}=e$ and $\Psi ^{\mu }$ is
-again reobtained, now via the trivilization of the set of vectors: $\mu _{%
-\af}\left( e\right) =0$.
-\end{remark}
-
-\subsection{Reduction of Verma modules}
-
-In \cite{2010arXiv1007.0318L} the decomposition analogous to (\ref{singular main}) was
-used to construct the recurrent relations for branching coefficients $k_{\xi
-}^{\left( \mu \right) }$ corresponding to the injection $\af%
-\hookrightarrow \gf$:
-\begin{equation}
-\begin{array}{c}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
-_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{\af%
-}(u(\mu +\rho )-\rho )}+\right.  \\
-\left. +\sum_{\gamma \in \Gamma _{\af\rightarrow \gf}}s\left(
-\gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right) }\right) .
-\end{array}
-\label{recurrent rel}
-\end{equation}
-The recursion is goverened by the set $\Gamma _{\af\rightarrow \gf}
-$ called the injection fan. The later is defined as the carrier set $\left\{
-\xi \right\} _{\af\rightarrow \gf}$ for the coefficient function $%
-s(\xi )$
-\begin{equation*}
-\left\{ \xi \right\} _{\af\rightarrow \gf}:=\left\{ \xi \in P_{%
-\af}|s(\xi )\neq 0\right\}
-\end{equation*}
-appearing in the expansion
-\begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left( 1-e^{-\pi
-_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
-}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
-)e^{-\gamma };\quad
-\end{equation}
-The weights in $\left\{ \xi \right\} _{\af\rightarrow \gf}$ are to
-be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi \right\} $
--- and the zero element is to be eliminated:
-\begin{equation}
-\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in
-\left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
-\end{equation}
-
-The recursion relation (\ref{recurrent rel}) was originally used to
-described branchings for integrable modules. There exists an important class
-of modules that also can be reduced with the help of an injection fan --
-these are the Verma modules.
-
-For a regular embedding $\af\hookrightarrow \gf$ we have the
-corresponding embedding for the root systems $\Delta _{\mathfrak{a}%
-}^{+}\hookrightarrow \Delta ^{+}$ . Moreover, in this case it is reasonable
-to enlarge the subalgebra $\af$ and consider $\frak{b}=\af\oplus
-\frak{h}_{\perp \af}$ . In this case the weights of a $\frak{b}$-module
-can be considered in $\frak{h}^{\ast }$ . Verma module is decomposable for
-any highest weight:
-\begin{equation}
-\mathrm{ch}M^{\mu }=\sum_{\nu }b_{\nu }^{(\mu )}\mathrm{ch}M_{\frak{b}}^{\nu
-}.
-\end{equation}
-Verma module $\mathrm{ch}M^{\mu }$ have one singular weight $\mu $ with the
-multiplicity ($+1$). The Weyl groups can be considered to be trivial. The
-orthogonal partner $\afb$ is also trivial and the recursion
-relation is simplified:
-\begin{equation*}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }%
-\;\left( \delta _{\xi -\gamma _{0},\mu }+\sum_{\gamma \in \Gamma _{\af%
-\rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma
-}^{\left( \mu \right) }\right) .
-\end{equation*}
-
-\begin{remark}
-Notice that inside the main Weyl chamber branching coefficients $k_{\xi
-}^{\left( \mu \right) }$ for Verma modules reduction coincide with the
-coefficients for reduction of integrable simple modules.
-\end{remark}
-
-\begin{example}
-\label{example:reduct-verma-modul}
- Let $\mathfrak{g}=B_{2}$ be and consider $A_{1}=\mathfrak{a}%
-\hookrightarrow \mathfrak{g}$. There are different embeddings  $%
-A_{1}\hookrightarrow B_{2}$. Here we limit ourselves by the regular ones.
-The root system $\Delta _{B_{2}}$ consists of 8 roots. Let $%
-S_{B_{2}}=\left\{ \alpha _{1}=e_{1}-e_{2},\alpha _{2}=e_{2}\right\} $ where $%
-e_{1},e_{2}$ form the standard basis in $\mathbf{R}^{2}$. The set of the
-positive roots is $\Delta ^{+}=\left\{ \alpha _{1},\alpha _{1}+\alpha
-_{2},\alpha _{1}+2\alpha _{2},\alpha _{2}\right\} $. Each of these roots can
-be taken as the simple root of the $A_{1}-$subalgebra. Firstly  we consider
-the subalgebra $A_{1}$ with the simple root $\beta =\alpha _{1}+2\alpha _{2}$%
-. Consider the Verma module $M^{\mu }$ with the highest weight $\mu =\omega
-_{1}+2\omega _{2}=2\alpha _{1}+3\alpha _{2}$ as it is shown at Figure \ref
-{fig:B2_Verma}.
-
-\begin{figure}[h!bt]
- \noindent\centering{
-   \includegraphics[width=120mm]{B2_Verma}
-  }
- \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
-Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}
-  \label{fig:B2_Verma}
-\end{figure}
-
-The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2}
-for the regular embedding $A_{1}\rightarrow B_{2}$. Here we can
-see that the picture depends upon the embedding and looks similar to the
-Verma modules of some subalgebra.
-
-\begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=120mm]{B2_Verma_Branch4.pdf}
-  }
-  \caption{Branching of the Verma module $M^{(1,2)}$ for the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector.
-    Branching coefficients for Verma module of the subalgebra are shown. Dashed line indicates the
-    direction of subalgebra modules.}
- \label{fig:B2_Verma_Branch2}
-\end{figure}
-\end{example}
-In the present paper we interpret this branching coefficients as the dimensions
-of the weight subspaces of modules of contracted algebras.
-
-\subsection{Weyl-Verma formulas.}
-
-\begin{statement}
-\bigskip For an orthogonal subalgebra $\afb$ in $\gf$
-(orthogonal partner of reductive $\af\hookrightarrow \gf$) the
-character of an integrable highest weight module $L^{\mu }$ can be presented
-as a combination (with integral coefficients) of parabolic Verma modules
-distributed by the set of weights $e^{\mu _{\aft}\left( u\right) }$:
-\begin{equation*}
-\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{%
-\widetilde{\af}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\af%
-_{\perp }}\left( u\right) },
-\end{equation*}
-where $U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
-\overline{C_{\afb}}\right\} $ and $\Delta _{I}^{+}$ is
-equivalent to $\Delta _{\afb}^{+}$.
-\end{statement}
-
-\bigskip
-\begin{proof}
-By the definition (\ref{delta a ort}) the subalgebra $%
-\mathfrak{a}_{\bot }$ is regular and reductive. Consider its Weyl
-denominator $R_{\afb}:=\prod_{\alpha \in \Delta _{\af%
-_{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}%
-\mathrm{\left( \alpha \right) }}$ and the element $R_{J}:=\prod_{\alpha \in
-\Delta ^{+}\setminus \Delta _{\afb}^{+}}\left( 1-e^{-\alpha
-}\right) ^{\mathrm{mult}(\alpha )}$ as the factors in $R$: $\quad $%
-\begin{equation*}
-R=R_{J}R_{\afb}.
-\end{equation*}
-According to this factorization and the decomposition (\ref{sing decomp main}%
-) the character $\mathrm{ch}\left( L^{\mu }\right) $ can be written as
-\begin{eqnarray*}
-\mathrm{ch}\left( L^{\mu }\right) &=&\left( R_{J}\right) ^{-1}\left( R_{%
-\afb}\right) ^{-1}\Psi ^{\mu }=\left( R_{J}\right)
-^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\af}}\left( u\right) }\epsilon
-(u)\left( R_{\afb}\right) ^{-1}\Psi _{\afb}^{\mu _{%
-\afb}\left( u\right) } \\
-&=&\left( R_{J}\right) ^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\af}%
-}\left( u\right) }\epsilon (u)L_{\afb}^{\mu _{\afb}\left( u\right) },
-\end{eqnarray*}
-where $\left\{ L_{\afb}^{\mu _{\afb}\left(
-u\right) }|u\in U\right\} $ is the set of finite-dimensional $\af%
-_{\perp }$-modules with the highest weights $\mu _{\afb}\left(
-u\right) $. We are interested in nontrivial subalgebras $\af$ and
-correspondingly in nontrivial $\afb$ (the case of a trivial
-orthogonal subalgebra arise when $\af=\gf$ and was considered
-above (see Remark 1)). This means that $r_{\af}\geq 1$ and $r_{\af%
-_{\perp }}<r$. Due to the fact that any maximal regular subalgebra has the
-Dynkin scheme obtained by one or two node subtractions from the extended
-Dynkin scheme and the extended scheme has at most one dependent root (the
-highest root) the set of roots $\Delta _{\afb}^{+}$ is always
-equivalent to the one $\Delta _{I}^{+}$ generated\ by some subset $I\subset
-S $ of simple roots.
-
-It follows that we can (by redefining the set $\Delta ^{+}$) identify $%
-\Delta _{\afb}^{+}$ with the subset $\Delta _{I}^{+}$ \ where $%
-I\subset S$ . This allows us to introduce the elements necessary to compose
-the generalized Verma modules
-\cite{lepowsky1977generalization,humphreys2008representations}.
-We have two sets of root
-vectors $\left\{ x_{\xi }\in \gf_{\xi }|\xi \in \Delta _{I}^{+}\right\}
-$ and $\left\{ x_{\eta }\in \gf_{\eta }|\eta \in \Delta ^{+}\setminus
-\Delta _{I}^{+}\right\} $. They generate nilpotent subalgebras of $\frak{n}%
-^{+}$:
-\begin{equation*}
-\frak{n}_{I}^{+}:=\sum_{\xi \in \Delta _{I}^{+}}\gf_{\xi },\quad
-\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\gf%
-_{\eta }.
-\end{equation*}
-The first subalgebra together with its negative counterpart $\frak{n}%
-_{I}^{-} $ generates a simple subalgebra
-\begin{equation*}
-\frak{s}_{I}=\frak{n}_{I}^{-}+\frak{h}_{I}+\frak{n}_{I}^{+}.
-\end{equation*}
-We enlarge it with the remaining Cartan generators and introduce the
-subalgebra:
-\begin{equation*}
-\frak{l}_{I}=\frak{n}_{I}^{-}+\frak{h}+\frak{n}_{I}^{+}.
-\end{equation*}
-The semidirect product of subalgebras $\frak{l}_{I}$ and $\frak{u}_{I}^{+}$
-gives a parabolic subalgebra $\frak{p}_{I}\hookrightarrow \gf$ :
-\begin{equation}
-\frak{p}_{I}=\frak{l}_{I}\vartriangleright \frak{u}_{I}^{+},
-\label{paralolic subalg}
-\end{equation}
-Its universal enveloping $U\left( \frak{p}_{I}\right) $ is a subalgebra in $%
-U\left( \gf\right) $. According to the obtained structure (\ref
-{paralolic subalg}) the $\frak{l}_{I}$-modules $L_{\afb}^{\mu _{%
-\afb}\left( u\right) }$ can be easily lifted to $\frak{p}_{I}$%
--modules using the trivial action of the nilradical $\frak{u}_{I}^{+}$. The
-latter induce $U\left( \gf\right) $-modules in a standard way:
-\begin{equation*}
-M_{I}^{\mu _{\afb}\left( u\right) }=U\left( \gf\right)
-\otimes _{U\left( \frak{p}_{I}\right) }L_{\afb}^{\mu _{\af%
-_{\perp }}\left( u\right) }.
-\end{equation*}
-According to the defenition presented in \cite{lepowsky1977generalization}
-these are the \textit{generalized Verma modules}
-generated by the highest weights $\mu _{\af%
-_{\perp }}\left( u\right) $. As a $U\left( \frak{u}_{I}^{-}\right) $-module
-each $M_{I}^{\mu _{\afb}\left( u\right) }$ is isomorphic to $%
-U\left( \frak{u}_{I}^{-}\right) \otimes $ $L_{\afb}^{\mu _{%
-\afb}\left( u\right) }$ and thus its character can be written
-with the help of Kostant-Heckman function \cite{KostantHeckman1982} corresponding
-to the injection of the orthogonal subalgebra $\afb\hookrightarrow \gf$:
-\begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\afb}\left( u\right) }=\mathcal{KH}_{%
-\afb\hookrightarrow \gf}\mathrm{ch}L_{\afb}^{\mu _{\afb}\left( u\right) }.
-\end{equation*}
-As far as the function $\mathcal{KH}_{\afb\hookrightarrow \frak{%
-g}}$ is generated by the denominator $R_{I}$ the last expression can be
-rewritten in the form
-\begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\afb}\left( u\right) }=\frac{1}{R_{I}}%
-\mathrm{ch}L_{\afb}^{\mu _{\afb}\left( u\right) }.
-\end{equation*}
-This means that we have obtained the generalized Weyl-Verma character formula
--- the decomposition of $\mathrm{ch}\left(
-L^{\mu }\right) $ in terms of generalized Verma modules characters:
-\begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
-u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\afb}\left(
-u\right) }.  \label{char in gen verma mod}
-\end{equation}
-\end{proof}
-
-\begin{remark}
-Here the generalized Weyl-Verma character formula appear in a detailed
-form: the weights $\mu _{\aft}$ and the generalized Verma modules highest weights
-$\mu _{\afb}$ are indicated separately. The reason is that the
-highest weight of $M_{I}$-module is not equal to the projection of the maximal
-weight to $h^*_{\afb}$ (but must be additionally shifted by the defect).
-\end{remark}
-
-\begin{example}
-  Continuing Example \ref{example:reduct-verma-modul} we consider the generalized Verma modules for the
-  embedding  $A_{1}\hookrightarrow B_{2}$ with the subalgebra $\afb$ built on the root $\alpha_{1}$
-  of $B_{2}$. The generalized Verma module $M^{\omega_{1}}_{I}$ with the highest weight
-  $\omega_{1}=e_{1}$ is shown in Figure \ref{fig:B2_Verma_Decomp}. The decomposition of the corresponding irreducible module
-  $L^{\omega_{1}}$ is indicated by the set of dashed contours of the involved generalized Verma
-  modules. 
-   \begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=120mm]{B2_Gen_Verma_Decomp}
-  }
-  \caption{Generalized Verma module  for the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
-    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. The
-    decomposition of $L^{\omega_{1}}$ is indicated by the set of dashed contours of the involved generalized Verma
-  modules. Dashed contours correspond to positive $\epsilon(u)$ and dotted to negative.}
-
- \label{fig:B2_Verma_Decomp}
-\end{figure}
-
-\end{example}
-
-\begin{remark}
-As it was proved in \cite{humphreys2008representations} (see Proposition 9.6 ) the characters of the
-generalized Verma modules $M_{I}^{\mu _{\afb}\left( u\right) }$
-can be described as linear combinations of ordinary Verma modules of $\frak{g%
-}$:
-\begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\afb}\left( u\right) }=\sum_{w\in W_{%
-\afb}}\epsilon \left( w\right) \mathrm{ch}M^{w\left( \mu _{%
-\afb}\left( u\right) +\rho _{\afb}\right) -\rho _{%
-\afb}}
-\end{equation*}
-Substituting this expression in\ (\ref{char in gen verma mod}) and using the
-definitions (\ref{mu-a},\ref{mu-a-tilda}) and (\ref{defect ort}) we reobtain
-the standard Weyl-Verma decomposition of the character:
-\begin{equation*}
-\mathrm{ch}\left( L^{\mu }\right) =\sum_{w\in W}\;\epsilon (u)\mathrm{ch}%
-M^{w\left( \mu +\rho \right) -\rho }.
-\end{equation*}
-\end{remark}
-
-%\bigskip
-
-\section{Conclusions}
-
-\label{sec:conclusions}
-
-In \cite{2010arXiv1007.0318L} it was demonstrated that the injection fan recursive mechanism
-works also for special injections. Here we must stress that the Weyl-Verma decomposition
-can be obtained in this case. The Weyl-Verma relations corresponding to the special
-subalgebras will describe the projections of characters of the initial module in terms
-of generalized Verma modules distributed in the subspace of $h^*$.
-
-Consider the situation where the simple roots are prescribed by some external
-forces (originating in physical applications conditions, for example). In this case
-the orthogonal partner cannot be generated by simple root vectors only.  The elements
-$\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\gf%
-_{\eta }$ do not form a subalgebra in $\gf$ because some nonsimple roots are lost in
-$\Delta ^{+}\setminus \Delta _{I}^{+}$. It is important to indicate that in this case
-the Weyl-Verma formula still exists. In it the generalized Verma modules correspond to
-the contractions \cite{Doebner1967Melsheimer} of the algebra $\frak{n}^{+}$ and the
-Weyl-Verma relations describes the decomposition of the representation space of $L^{\mu}$
-into the set of generalized Verma modules of contracted algebra
-$U\left(\frak{n}_c^{+}\right)$. The weight vectors are formed by the PBW-basis
-of $U\left(\frak{n}_c^{+}\right)$ and of $U\left( \afb \right)$. To consider such space
-as a $\gf$-module we must perform the deformation \cite{Nijenhuis1966Richardson} of
-the algebra $\frak{n}_c^{+}$ (restore the initial composition law). The space survives
-and after such a deformation the initial
-algebra generators will act properly on it.
-
-\section{Acknowledgments}
-The authors express their sincere gratitude to all those who prepared and performed the
-III International Conference "Models in Quantum Field Theory - 2010" dedicated to 70-th
-anniversary of A. N. Vassiliev.
-
-The work was supported in part by the RFFI grant N 09-01-00504.
-
-% \section{Applications}
-% \label{sec:applications}
-%
-% \section{Conclusion}
-% \label{sec:conclusion}
-%
-%
-% \section{Acknowledgements}
-%
-% The work was supported in part by RFFI grant N 09-01-00504 and the National
-% Project RNP.2.1.1./1575.
-%
-
-\bibliographystyle{utphys}
-\bibliography{article}
-{}
-
 \end{document}

### 2011-02-17 AffineLieAlgebras/Mathematica/datastructures.m
Mathematica code rework - datatypes for finite and affine weights are proposed, start of code rework for typed operations.

@@ -1,0 +1,204 @@
+(* 
+
+   finiteWeight[dimension]=dimension_Integer
+   finiteWeight[standardBase]=List[x__Integer]
+   
+   affineWeight[finitePart]=x_finiteWeight
+   affineWeight[grade]=grade_Integer
+   affineWeight[level]=level_Integer
+   
+
+   Finite Weight: finiteWeight[dimension][<id>][dimension]
+                                              [standardBase]
+   Affine Weight: affineWeight[dimension][<id>][finitePart]
+   Affine Weight: affineWeight[dimension][<id>][level]
+   Affine Weight: affineWeight[dimension][<id>][grade]
+   
+   *)
+
+clear[finiteWeight,affineWeight,dimension,standardBase,simpleRootBase,level,grade];
+
+clear[Expect];
+
+Expect[ description_, val_, expr_ ] := 
+If[
+    val != expr,
+    Throw[
+        StringJoin[ "GOT UNEXPECTED VALUE ", ToString[expr], 
+        " INSTEAD OF ", ToString[val] ]
+        , "assertion exception"
+    ]
+]
+
+
+makeFiniteWeight[{coordinates__?NumberQ}]:=Module[{uniq=finiteWeight[Unique[]]},
+				      uniq[dimension]=Length[{coordinates}];
+				      uniq[standardBase]={coordinates};
+				      uniq]
+
+Expect["Dimension equals to length",3,makeFiniteWeight[{1,2,3}][dimension]]
+
+finiteWeight/:x_finiteWeight . y_finiteWeight/;x[dimension]==y[dimension]:=x[standardBase].y[standardBase]
+
+Expect["Scalar product for vectors from weigth space of finite-dimensional Lie algebras",10,makeFiniteWeight[{1,2,3}].makeFiniteWeight[{3,2,1}]]
+
+
+Expect["Scalar product for vectors from different spaces are left unevaluated",True,
+       MatchQ[makeFiniteWeight[{1,2,3}].makeFiniteWeight[{3,2,1,2}],finiteWeight[x_] . finiteWeight[y_]]]
+
[…]

### 2011-02-17 AffineLieAlgebras/Mathematica/lie.m

@@ -2,7 +2,6 @@ ExpandNCM[(h : NonCommutativeMultiply)[a___, b_Plus, c___]] :=  Distribute[h[a, 
 ExpandNCM[a_] := ExpandAll[a];
 ExpandNCM[(a + b) ** (a + b) ** (a + b)];
 keys = DownValues[#,Sort->False][[All,1,1,1]]&;
-
 clear[standardBase];
 makeSimpleRootSystem[A,rank_Integer]:=standardBase @@@ Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank},{j,1,rank+1}];
 makeSimpleRootSystem[B,rank_Integer]:=standardBase @@@ Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],1]];
@@ -35,8 +34,7 @@ orbit[{simpleRoots__standardBase}][{weights__standardBase}]:=
 		 Union[Flatten[Map[Function[y,
 					    Map[reflection[#][y]&,Cases[{simpleRoots},z_ /; z.y>0]]],x]]]],
 	{weights},
-	#=!={}&]
-
+	#=!={}&];
 orbit[{simpleRoots__standardBase}][weight_standardBase]:=orbit[{simpleRoots}][{toFundamentalChamber[{simpleRoots}][weight]}];
 positiveRoots[{simpleRoots__standardBase}]:=Map[-#&,Flatten[orbit[{simpleRoots}][Map[-#&,{simpleRoots}]]]];
 weightSystem[{simpleRoots__standardBase}][higestWeight_standardBase]:=Module[{minusPosRoots=-positiveRoots[{simpleRoots}]},
@@ -46,6 +44,41 @@ weightSystem[{simpleRoots__standardBase}][higestWeight_standardBase]:=Module[{mi
 freudenthalMultiplicities[{simpleRoots__standardBase}][highestWeight_standardBase]:=
     Module[{rh=rho[{simpleRoots}],weights,mults,c,insideQ,
[…]

### 2011-02-17 AffineLieAlgebras/Mathematica/datastructures.m
More data structures - finiteRootSystem. MakeSimpleRootsSystem, reflection for finite weights.

@@ -38,6 +38,17 @@ makeFiniteWeight[{coordinates__?NumberQ}]:=Module[{uniq=finiteWeight[Unique[]]},
 
 Expect["Dimension equals to length",3,makeFiniteWeight[{1,2,3}][dimension]]
 
+finiteWeight/:Print[x_finiteWeight]:=Print[x,x[standardBase]]
+
+
+(*
+
+Print[makeFiniteWeight[{1,2,3}]]
+
+finiteWeight[$114]{1, 2, 3}
+
+*)
+
 finiteWeight/:x_finiteWeight . y_finiteWeight/;x[dimension]==y[dimension]:=x[standardBase].y[standardBase]
 
 Expect["Scalar product for vectors from weigth space of finite-dimensional Lie algebras",10,makeFiniteWeight[{1,2,3}].makeFiniteWeight[{3,2,1}]]
@@ -126,21 +137,32 @@ ExpandNCM[a_] := ExpandAll[a];
 ExpandNCM[(a + b) ** (a + b) ** (a + b)];
 keys = DownValues[#,Sort->False][[All,1,1,1]]&;
 
+makeFiniteWeight/@Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,3},{j,1,3+1}]
 
+makeRootSystem[{roots__finiteWeight}]:=Module[{rs=finiteRootSystem[Unique[]]},
+					      rs[simpleRoots]={roots};
+					      rs[rank]=Length[{roots}];
+					      rs]
 
-makeSimpleRootSystem[A,rank_Integer]:=standardBase @@@ Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank},{j,1,rank+1}];
-makeSimpleRootSystem[B,rank_Integer]:=standardBase @@@ Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],1]];
-makeSimpleRootSystem[C,rank_Integer]:=standardBase @@@ Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],2]];
-makeSimpleRootSystem[D,rank_Integer]:=standardBase @@@ Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Append[Table[0,{rank-2}],1],1]];
[…]

### 2011-02-18 AffineLieAlgebras/Mathematica/datastructures.m
Some work on finite-dimensional root systems

@@ -137,22 +137,19 @@ ExpandNCM[a_] := ExpandAll[a];
 ExpandNCM[(a + b) ** (a + b) ** (a + b)];
 keys = DownValues[#,Sort->False][[All,1,1,1]]&;
 
-makeFiniteWeight/@Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,3},{j,1,3+1}]
-
-makeRootSystem[{roots__finiteWeight}]:=Module[{rs=finiteRootSystem[Unique[]]},
+makeFiniteRootSystem[{roots__finiteWeight}]:=Module[{rs=finiteRootSystem[Unique[]]},
 					      rs[simpleRoots]={roots};
 					      rs[rank]=Length[{roots}];
+					      rs[simpleRoot][n_Integer]:=rs[simpleRoots][[n]];
 					      rs]
 
-makeRootSystem[{roots__List}]:=Module[{rs=finiteRootSystem[Unique[]]},
-					      rs[simpleRoots]=makeFiniteWeight/@{roots};
-					      rs[rank]=Length[{roots}];
-					      rs]
+makeFiniteRootSystem[{roots__List}]:=makeFiniteRootSystem[makeFiniteWeight/@{roots}]
 
-makeSimpleRootSystem[A,r_Integer]:=makeRootSystem[makeFiniteWeight /@ Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,r},{j,1,r+1}]];
-makeSimpleRootSystem[B,rank_Integer]:=makeRootSystem[Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],1]]];
-makeSimpleRootSystem[C,rank_Integer]:=makeRootSystem[Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],2]]];
-makeSimpleRootSystem[D,rank_Integer]:=makeRootSystem[Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Append[Table[0,{rank-2}],1],1]]];
+makeSimpleRootSystem[A,1]:=makeFiniteRootSystem[{{1}}];
[…]

### 2011-02-18 AffineLieAlgebras/Mathematica/datastructures.m
to fundamental chamber

@@ -201,12 +201,26 @@ Out[86]= {Null, Null}
 
 Out[85]= {finiteWeight[$159], finiteWeight[$160]}
 
-rho[{simpleRoots__standardBase}]:=Plus@@fundamentalWeights[{simpleRoots}];
-toFundamentalChamber[{simpleRoots__standardBase}][vec_standardBase]:=
+rho[rs_finiteRootSystem]:=Plus@@fundamentalWeights[rs];
+
+Expect["Weyl vector for B2",True,makeFiniteWeight[{3/2,1/2}]==rho[makeSimpleRootSystem[B,2]]]
+
+toFundamentalChamber[rs_finiteRootSystem][vec_finiteWeight]:=
     First[NestWhile[Function[v,
-		       reflection[Scan[If[#.v<0,Return[#]]&,{simpleRoots}]][v]],
+		       reflection[Scan[If[#.v<0,Return[#]]&,rs[simpleRoots]]][v]],
 	      vec,
 	      Head[#]=!=reflection[Null]&]];
+
+Print[toFundamentalChamber[makeSimpleRootSystem[B,2]][makeFiniteWeight[{-1,0}]]]
+
+finiteWeight[$211]{1, 0}
+
+Out[97]= finiteWeight[$203]
+
+Out[93]= toFundamentalChamber[makeFiniteRootSystem[B, 2]][finiteWeight[$186]]
+
+Out[91]= toFundamentalChamber[makeFiniteRootSystem[B, 2]][finiteWeight[$185]]
+
 orbit[{simpleRoots__standardBase}][{weights__standardBase}]:=
     NestWhileList[
 	Function[x,

### 2011-02-18 AffineLieAlgebras/Mathematica/datastructures.m
Orbit

@@ -172,11 +172,7 @@ clear[weylGroupElement];
 
 revApply[x_,f_]:=f[x];
 
-t[s]={1,2,3}
-
-t[s][0]=1
-
-Print[makeSimpleRootSystem[B,2][simpleRoot][2]]
+(* Print[makeSimpleRootSystem[B,2][simpleRoot][2]] *)
 
 rootSystemQ[rs_]:=MatchQ[rs,x_finiteRootSystem|x_affineRootSystem]
 
@@ -188,8 +184,9 @@ Expect["Weyl reflection s1 s2 s1 in algebra B2",True,
        weylGroupElement[1,2,1][makeSimpleRootSystem[B,2]][makeFiniteWeight[{1,0}]]==
        makeFiniteWeight[{-1,0}]]
 
-fundamentalWeights[rs_finiteRootSystem]:=Plus@@(Inverse[cartanMatrix[rs[simpleRoots]]]*rs[simpleRoots]);
+fundamentalWeights[rs_finiteRootSystem]:=Plus@@(Inverse[cartanMatrix[rs]]*rs[simpleRoots]);
 
+(*
 Print/@fundamentalWeights[makeSimpleRootSystem[B,2]]
 
 finiteWeight[$166]{1, 0}
@@ -200,8 +197,12 @@ finiteWeight[$167]{-, -}
 Out[86]= {Null, Null}
 
 Out[85]= {finiteWeight[$159], finiteWeight[$160]}
+*)
+
 
 rho[rs_finiteRootSystem]:=Plus@@fundamentalWeights[rs];
+
+Print[rho[makeSimpleRootSystem[B,2]]]
 
 Expect["Weyl vector for B2",True,makeFiniteWeight[{3/2,1/2}]==rho[makeSimpleRootSystem[B,2]]]
 
@@ -209,9 +210,21 @@ toFundamentalChamber[rs_finiteRootSystem][vec_finiteWeight]:=
     First[NestWhile[Function[v,
 		       reflection[Scan[If[#.v<0,Return[#]]&,rs[simpleRoots]]][v]],
 	      vec,
-	      Head[#]=!=reflection[Null]&]];
+	      Head[#]=!=reflection[Null]&]]
 
-Print[toFundamentalChamber[makeSimpleRootSystem[B,2]][makeFiniteWeight[{-1,0}]]]
+Print[toFundamentalChamber[makeSimpleRootSystem[B,2]][makeFiniteWeight[{-1,1/2}]]]
+
+                      1
[…]

### 2011-02-19 AffineLieAlgebras/Mathematica/datastructures.m
Prepare to change datastructures from hashes to lists

@@ -30,6 +30,11 @@ If[
     ]
 ]
 
+(* finiteWeight[dimension,coordinates] *)
+
+finiteWeight/:x_finiteWeight[dimension]:=x[[1]];
+finiteWeight/:x_finiteWeight[standardBase]:=x[[2]];
+
 
 makeFiniteWeight[{coordinates__?NumberQ}]:=Module[{uniq=finiteWeight[Unique[]]},
 				      uniq[dimension]=Length[{coordinates}];
@@ -252,6 +257,8 @@ Print/@positiveRoots[makeSimpleRootSystem[B,2]]
 
 Map[Print,orbit[makeSimpleRootSystem[B, 2]][rho[makeSimpleRootSystem[B, 2]]],2]
 
+SubValues[finiteWeight]
+
 
 Out[91]= {{finiteWeight[$342]}, {finiteWeight[$344], finiteWeight[$346]}, 
  
@@ -260,6 +267,10 @@ Out[91]= {{finiteWeight[$342]}, {finiteWeight[$344], finiteWeight[$346]},
 >    {finiteWeight[$352], finiteWeight[$354]}, 
  
 >    {finiteWeight[$356], finiteWeight[$358]}, {}}
+
+Clear[finiteWeight[$99]]
+
+Print[finiteWeight[$99]]
 
 weightSystem[{simpleRoots__standardBase}][higestWeight_standardBase]:=Module[{minusPosRoots=-positiveRoots[{simpleRoots}]},
 									     NestWhileList[Function[x,Complement[

### 2011-02-19 AffineLieAlgebras/Mathematica/datastructures.m
Racah and Freudenthal are working again.
I need to write unit tests for them though.
Also I think that rootSystem[rho] and rootSystem[orbit][weight] are better than rho[rootSystem] and orbit[rootSystem][weight]

@@ -16,9 +16,7 @@
    
    *)
 
-clear[finiteWeight,affineWeight,dimension,standardBase,simpleRootBase,level,grade];
-
-clear[Expect];
+Clear[finiteWeight,affineWeight,dimension,standardBase,simpleRootBase,level,grade,Expect];
 
 Expect[ description_, val_, expr_ ] := 
 If[
@@ -35,24 +33,9 @@ If[
 finiteWeight/:x_finiteWeight[dimension]:=x[[1]];
 finiteWeight/:x_finiteWeight[standardBase]:=x[[2]];
 
-
-makeFiniteWeight[{coordinates__?NumberQ}]:=Module[{uniq=finiteWeight[Unique[]]},
-				      uniq[dimension]=Length[{coordinates}];
-				      uniq[standardBase]={coordinates};
-				      uniq]
+makeFiniteWeight[{coordinates__?NumberQ}]:=finiteWeight @@ {Length[{coordinates}],{coordinates}}
 
 Expect["Dimension equals to length",3,makeFiniteWeight[{1,2,3}][dimension]]
-
-finiteWeight/:Print[x_finiteWeight]:=Print[x,x[standardBase]]
-
-
-(*
-
-Print[makeFiniteWeight[{1,2,3}]]
-
-finiteWeight[$114]{1, 2, 3}
-
-*)
 
 finiteWeight/:x_finiteWeight . y_finiteWeight/;x[dimension]==y[dimension]:=x[standardBase].y[standardBase]
 
@@ -60,16 +43,16 @@ Expect["Scalar product for vectors from weigth space of finite-dimensional Lie a
 
 
 Expect["Scalar product for vectors from different spaces are left unevaluated",True,
-       MatchQ[makeFiniteWeight[{1,2,3}].makeFiniteWeight[{3,2,1,2}],finiteWeight[x_] . finiteWeight[y_]]]
+       MatchQ[makeFiniteWeight[{1,2,3}].makeFiniteWeight[{3,2,1,2}],x_finiteWeight . y_finiteWeight]]
 
 finiteWeight/:x_finiteWeight+y_finiteWeight/;x[dimension]==y[dimension]:=makeFiniteWeight[x[standardBase]+y[standardBase]]
 
[…]

### 2011-02-20 AffineLieAlgebras/CPC/article.tex
Some work on affine Lie algebras and introduction to the paper.

@@
 \section{Introduction}
+
+Representation theory of finite, affine and extended affine Lie algebras is of central importance for different areas of mathematical and theoretical physics.
+Simple Lie algebras appear as the symmetries of classical and quantum systems, e.g.
+of gauge quantum field theories.
+Tensor product decomposition problem for simple Lie algebras appears in classification of particles, branching problem -- in the study of symmetry breaking, for example in great unification models.
+
+Major role of representation theory for the study of quantum and classical integrable systems is well known.
+Here, for example, tensor product decomposition is required for the computation of spectra and eigenstates of Hamiltonian.
+Quantum deformation of simple Lie algebras appears naturally in the study of integrable systems.
+It is possible to introduce $q$-analogues of multiplicities and branching coefficients.
+If $q$ is not root of unity category of $U_{q}(\gf)$-modules is equivalent to the non-deformed case.
+Since Weyl character formula is preserved by $q$-deformation in this case, recurrent approach is applicable.
+
+Affine Lie algebras, WZW and coset models.
+
+Extended affine Lie algebras currently attract a lot of attention. These algebras has applications in supergravity 
 \end{document}

### 2011-02-20 AffineLieAlgebras/Mathematica/datastructures.m

@@ -173,6 +173,12 @@ Expect["Weyl reflection s1 s2 s1 in algebra B2",True,
 
 fundamentalWeights[rs_finiteRootSystem]:=Plus@@(Inverse[cartanMatrix[rs]]*rs[simpleRoots]);
 
+Expect["Fundamental weights for B2", True, {makeFiniteWeight[{1,0}],makeFiniteWeight[{1/2,1/2}]}==fundamentalWeights[makeSimpleRootSystem[B,2]]]
+
+Expect["Fundamental weights for A1", True, {makeFiniteWeight[{1/2}]}==fundamentalWeights[makeSimpleRootSystem[A,1]]]
+
+Expect["Fundamental weights for A2", True, {makeFiniteWeight[{2/3,-1/3,-1/3}],makeFiniteWeight[{1/3,1/3,-2/3}]}==fundamentalWeights[makeSimpleRootSystem[A,2]]]
+
 (*
 Print/@fundamentalWeights[makeSimpleRootSystem[B,2]]
 
@@ -188,12 +194,6 @@ Out[85]= {finiteWeight[$159], finiteWeight[$160]}
 
 
 rho[rs_finiteRootSystem]:=Plus@@fundamentalWeights[rs];
-
-Print[rho[makeSimpleRootSystem[B,2]]]
-
-                 3  1
-finiteWeight[2, {-, -}]
-                 2  2
 
 Expect["Weyl vector for B2",True,makeFiniteWeight[{3/2,1/2}]==rho[makeSimpleRootSystem[B,2]]]
 
@@ -351,13 +351,225 @@ Out[108]= orbitWithEps[finiteRootSystem[2,
  
 >      {finiteWeight[2, {1, -1}], finiteWeight[2, {0, 1}]}]][]
 
-makeUntwistedAffineRootSystem[fs_finiteRootSystem]:=Module[{rs=affineRootSystem[Unique[]],ar},
-							   rs[finiteRootSystem]=fs;
-							   ar=makeAffineWeight[#,1,0]&/@fs[simpleRoots];
-							   rs[simpleRoots]=Append[ar,makeAffineWeight[-highestRoot[fs],1,1]];
-							   rs[simpleRoot][0]=rs[[-1]];
[…]

### 2011-02-21 AffineLieAlgebras/Mathematica/datastructures.m
Some work on affine root systems

@@ -229,17 +229,7 @@ weightSystem[rs_finiteRootSystem][higestWeight_finiteWeight]:=Module[{minusPosRo
 										 Cases[Flatten[Outer[Plus,minusPosRoots,x]],y_/;And@@(#.y>=0&/@rs[simpleRoots])]
 										 ,x]],{higestWeight},#=!={}&]];
 
-weightSystem[makeSimpleRootSystem[B,2]][makeFiniteWeight[{2,2}]]
-
-Out[88]= {{finiteWeight[2, {2, 2}]}, 
- 
->    {finiteWeight[2, {1, 1}], finiteWeight[2, {2, 1}]}, 
- 
->    {finiteWeight[2, {0, 0}], finiteWeight[2, {1, 0}], 
- 
->     finiteWeight[2, {2, 0}]}, {finiteWeight[2, {1, 1}]}, 
- 
->    {finiteWeight[2, {0, 0}], finiteWeight[2, {1, 0}]}, {}}
+(* weightSystem[makeSimpleRootSystem[B,2]][makeFiniteWeight[{2,2}]] *)
 
 freudenthalMultiplicities[rs_finiteRootSystem][highestWeight_finiteWeight]:=
     Module[{rh=rho[rs],weights,mults,c,insideQ,
@@ -262,23 +252,7 @@ freudenthalMultiplicities[rs_finiteRootSystem][highestWeight_finiteWeight]:=
 		weights];
 	   mults];
 
-freudenthalMultiplicities[makeSimpleRootSystem[B,2]][makeFiniteWeight[{5,5}]]
-
-Out[94]= mults$98
-
-Out[90]= mults$96
-
-Out[94][finiteWeight[2, {0, 0}]]
-
-Out[96]= 6
-
-Out[95]= 1
-
-Out[93]= 1
-
-Out[92]= 1
-
-Out[91]= {finiteWeight[2, {1, 0}], finiteWeight[2, {0, 0}]}
+(* freudenthalMultiplicities[makeSimpleRootSystem[B,2]][makeFiniteWeight[{5,5}]] *)
 
 orbitWithEps[rs_finiteRootSystem][weight_finiteWeight]:=Flatten[Most[MapIndexed[Function[{x,i},Map[{#,(-1)^(i[[1]]+1)}&,x]],orbit[rs][weight]]],1];
 
[…]

### 2011-02-21 AffineLieAlgebras/CPC/article.tex
Thesis file added :) Some work on CPC paper introduction and code.

@@
 
+Example.
+
 Major role of representation theory for the study of quantum and classical integrable systems is well known.
@@
 It is possible to introduce $q$-analogues of multiplicities and branching coefficients.
-If $q$ is not root of unity category of $U_{q}(\gf)$-modules is equivalent to the non-deformed case.
-Since Weyl character formula is preserved by $q$-deformation in this case, recurrent approach is applicable.
 
-Affine Lie algebras, WZW and coset models.
+Definition.
+
+Example.
+
+Affine Lie algebras, WZW and coset models. Denominator identity
 
 Extended affine Lie algebras currently attract a lot of attention. These algebras has applications in supergravity
+
+Reference.
+
+Multiplicities, branching and tensor product problems are essentially different faces of the same problem.
+One possible solution is recurrent computation from corresponding generalization of Weyl character formula.
+Such a solution is applicable in many cases.
+For example if $q$ is not root of unity category of $U_{q}(\gf)$-modules is equivalent to the non-deformed case.
+Since Weyl character formula is preserved by $q$-deformation in this case, recurrent approach is applicable to quantum groups.
+etc.
+
+General recurrent relations for branching coefficients of non-maximal embeddings were proposed in [1007].
+It [1102] it was shown that these relations demonstrate the connection of branching problem with BGG resolution.
+Also it was noticed, that weight multiplicities and tensor product decomposition coefficients can be obtained in the special cases of Lie algebra embeddings ($\hf\subset\gf$ and $\gf\subset\gf\otimes\gf$ correspondingly).
+
+Example.
+
+In this paper we present {\it Mathematica} package for computations in representation theory of affine Lie algebras.
+
+Main features:
+\begin{itemize}
+\item Root systems, fundamental weights, Weyl reflections for finite dimensional and affine semi-simple Lie algebras.
+\item Recurrent calculation of weight multiplicities and branching coefficients for irreducible representations.
+\item Construction of closed algebraic expressions for string and branching functions for low-rank affine Lie algebras.
+\end{itemize}
+
+Methods and algorithms.
+For (1) we use fairly standard algorithms.
+For simple finite-dimensional Lie algebras these algorithms were already implemented in several software packages (\cite{vanleeuwen1994lsp}, \cite{stembridge2001computational}, \cite{fischbacher2002ilp}, \cite{simplie}).
+We have made them available to the users of popular computer algebra system {\it Mathematica}.
+Flexibility of {\it Mathematica} language has allowed us to represent Weyl group elements in the form convenient for simplification with rules [].
+
+There exists well-known fast recursive formula for recurrent computation of weight multiplicities of Freudenthal \cite{moody1982fast}.
+It is used in most software packages (\cite{vanleeuwen1994lsp}, \cite{stembridge2001computational}, \cite{fischbacher2002ilp}).
+We present our own implementation.
+Also we present another recurrent computation routine based on general approach to branching [1007].
+In case of finite-dimensional Lie algebras this procedure is equivalent to Racah formula, which is faster for weight multiplicities in case of low rank algebras and big representations.
+(See the table with run times).
+
+Branching and tensor-product decomposition is carried out by the same recurrent process, which is implemented for arbitrary pair of algebra $\gf$ and subalgebra $\af$.
+
+For tensor product decompositions it is sometimes possible to give close algebraic answer for arbitrary tensor powers (see [Lyakhovsky, Postnova]). This formulae are also included in our package.
+
+\bibliography{bibliography}{}
+\bibliographystyle{utphys}
+
 \end{document}

### 2011-02-21 AffineLieAlgebras/Mathematica/datastructures.m

@@ -60,6 +60,7 @@ Expect["Equal for finite weights compares standard base representations", True,m
 
 Expect["Equal for finite weights compares standard base representations", False,makeFiniteWeight[{1,2,3}]==makeFiniteWeight[{1,2,3,4}]]
 
+finiteWeight/:0*y_finiteWeight:=makeFiniteWeight[0*y[standardBase]];
 finiteWeight/:x_?NumberQ*y_finiteWeight:=makeFiniteWeight[x*y[standardBase]]
 
 Expect["Multiplication by scalar", True,makeFiniteWeight[{1,2,3}]*2==makeFiniteWeight[{2,4,6}]]
@@ -296,10 +297,10 @@ affineRootSystem/:rs_affineRootSystem[realRoots]:=rs[[4]]
 
 affineRootSystem/:rs_affineRootSystem[imaginaryRoot]:=rs[[3]]
 
-affineRootSystem/:rs_affineRootSystem[simpleRoots]:=Prepend[rs[[4]],rs[[3]]]Out[302]= {1, 1, 1}
+affineRootSystem/:rs_affineRootSystem[simpleRoots]:=Prepend[rs[[4]],rs[[3]]]
 
 affineRootSystem/:rs_affineRootSystem[simpleRoot][0]:=rs[[3]];
-affineRootSystem/:rs_affineRootSystem[simpleRoot][n_?NumberQ]/;n<=rs[rank]:=rs[simpleRoots][[n]];Out[293]= {1, 1, 2}
+affineRootSystem/:rs_affineRootSystem[simpleRoot][n_?NumberQ]/;n<=rs[rank]:=rs[simpleRoots][[n]];
 
 toFundamentalChamber[rs_affineRootSystem][vec_affineWeight]:=
     First[NestWhile[Function[v,
@@ -313,10 +314,13 @@ comarks[rs_affineRootSystem]:=marks[rs]*Map[#.#/2&,rs[simpleRoots]]
 
 b2a=makeAffineExtension[makeSimpleRootSystem[B,2]]
 
-fundamentalWeights[rs_affineRootSystem]:=Map[makeAffineWeight[#1,#2,0]&,
-					     Transpose[{Prepend[fundamentalWeights[rs[finitePart]],
-								0*rs[finitePart][simpleRoot][[1]]],
+
[…]

### 2011-02-25 AffineLieAlgebras/Mathematica/datastructures.m
Some work on help for Mathematica code

@@ -18,6 +18,7 @@
 
 Clear[finiteWeight,affineWeight,dimension,standardBase,simpleRootBase,level,grade,Expect];
 
+Expect::"usage"="Expect[comment,value,expression] is used for unit tests. If expression != value it throws exception.";
 Expect[ description_, val_, expr_ ] := 
 If[
     val != expr,
@@ -28,23 +29,28 @@ If[
     ]
 ]
 
+standardBase::"usage"="standardBase[coordinates] represents weight vector in standard (Bourbaki) coordinates. E.g. simple roots for B2 are standardBase[1,-1] and standardBase[0,1]"
+
 (* finiteWeight[dimension,coordinates] *)
+finiteWeight::"usage"="finiteWeight[dimension_?NomberQ,coordinates_standardBase] represents vector in weight space of finite-dimensional Lie algebra.\n finiteWeight[dimension] returns dimension of the space, where weight vector is embedded (i.e. for sl_n it is n+1.\n finiteWeight[standardBase] returns standard base coordinates of weight of finite-dimensional Lie algebra";
 
 finiteWeight/:x_finiteWeight[dimension]:=x[[1]];
 finiteWeight/:x_finiteWeight[standardBase]:=x[[2]];
 
+makeFiniteWeight::"usage"="makeFiniteWeight[{coordinates__?NumberQ}] creates finiteWeight with given coordinates in standard base"
 makeFiniteWeight[{coordinates__?NumberQ}]:=finiteWeight @@ {Length[{coordinates}],{coordinates}}
 
 Expect["Dimension equals to length",3,makeFiniteWeight[{1,2,3}][dimension]]
 
+Dot::"usage"=Dot::"usage" <> "\n It is defined for weights of finite and affine Lie algebras";
 finiteWeight/:x_finiteWeight . y_finiteWeight/;x[dimension]==y[dimension]:=x[standardBase].y[standardBase]
 
 Expect["Scalar product for vectors from weigth space of finite-dimensional Lie algebras",10,makeFiniteWeight[{1,2,3}].makeFiniteWeight[{3,2,1}]]
 
-
 Expect["Scalar product for vectors from different spaces are left unevaluated",True,
[…]

### 2011-02-25 AffineLieAlgebras/Mathematica/testd.m

@@ -1,0 +1,728 @@
+AppendTo[$Path,"/home/anton/study/2011/Articles/AffineLieAlgebras/Mathematica/"];
+
+<<datastructures.m;
+
+?finiteWeight
+
+?==
+
+orbit[b2][{makeFiniteWeight[{2,-1}]}]
+
+ChebyshevU[5,x]
+
+5!
+
+M[p_,k_]/;Mod[p,2]==Mod[k,2]:=p!(k+1)/((p-k)/2)!/((p+k+2)/2)!;
+M[p_,k_]/;Mod[p,2]!=Mod[k,2]:=0
+
+Clear[M]
+
+MM:=Table[M[i,j],{i,10},{j,10}]
+
+MM//MatrixForm
+
+Out[53]//MatrixForm= 1   0   0   0   0
+
+                     0   1   0   0   0
+
+                     2   0   1   0   0
+
+                     0   3   0   1   0
+
+                     5   0   4   0   1
+
+Inverse[MM].((2*x)^Range[10])
+
+                  2            3       2       4            3       5
+Out[69]= {2 x, 4 x , -4 x + 8 x , -12 x  + 16 x , 6 x - 32 x  + 32 x , 
+ 
+         2       4       6             3        5        7
+>    24 x  - 80 x  + 64 x , -8 x + 80 x  - 192 x  + 128 x , 
+ 
+          2        4        6        8
+>    -40 x  + 240 x  - 448 x  + 256 x , 
+ 
+                 3        5         7        9
+>    10 x - 160 x  + 672 x  - 1024 x  + 512 x , 
+ 
+         2        4         6         8         10
+>    60 x  - 560 x  + 1792 x  - 2304 x  + 1024 x  }
+
+                          2            3          2       4
+Out[66]= {1, 2 x, -2 + 4 x , -6 x + 8 x , 3 - 16 x  + 16 x }
+
+Range[0,5]
+
+Out[65]= {0, 1, 2, 3, 4, 5}
+
+                  2            3       2       4            3       5
+Out[57]= {2 x, 4 x , -4 x + 8 x , -12 x  + 16 x , 6 x - 32 x  + 32 x }
+
+ChebyshevU[#,x]&/@ Range[10]
+
+                       2            3          2       4
+Out[70]= {2 x, -1 + 4 x , -4 x + 8 x , 1 - 12 x  + 16 x , 
+ 
+               3       5           2       4       6
[…]

### 2011-02-27 AffineLieAlgebras/Mathematica/datastructures.m
Some documentation added

@@ -29,29 +29,44 @@ If[
     ]
 ]
 
-standardBase::"usage"="standardBase[coordinates] represents weight vector in standard (Bourbaki) coordinates. E.g. simple roots for B2 are standardBase[1,-1] and standardBase[0,1]"
+standardBase::"usage"=
+    "standardBase[coordinates] represents weight vector in standard (Bourbaki) coordinates.\
+    E.g. simple roots for B2 are standardBase[1,-1] and standardBase[0,1]"
 
 (* finiteWeight[dimension,coordinates] *)
-finiteWeight::"usage"="finiteWeight[dimension_?NomberQ,coordinates_standardBase] represents vector in weight space of finite-dimensional Lie algebra.\n finiteWeight[dimension] returns dimension of the space, where weight vector is embedded (i.e. for sl_n it is n+1.\n finiteWeight[standardBase] returns standard base coordinates of weight of finite-dimensional Lie algebra";
+
+finiteWeight::"usage"=
+    "finiteWeight[dimension_?NumberQ,coordinates_standardBase] represents\ 
+    vector in weight space of finite-dimensional Lie algebra.\n 
+    finiteWeight[dimension] returns dimension of the space, where weight vector is embedded\ 
+    (i.e. for sl_n it is n+1).\n 
+     finiteWeight[standardBase] returns standard base coordinates of weight of finite-dimensional Lie algebra";
 
 finiteWeight/:x_finiteWeight[dimension]:=x[[1]];
 finiteWeight/:x_finiteWeight[standardBase]:=x[[2]];
 
-makeFiniteWeight::"usage"="makeFiniteWeight[{coordinates__?NumberQ}] creates finiteWeight with given coordinates in standard base"
+makeFiniteWeight::"usage"=
+    "makeFiniteWeight[{coordinates__?NumberQ}] creates finiteWeight with given coordinates in standard base"
+
 makeFiniteWeight[{coordinates__?NumberQ}]:=finiteWeight @@ {Length[{coordinates}],{coordinates}}
 
 Expect["Dimension equals to length",3,makeFiniteWeight[{1,2,3}][dimension]]
 
 Dot::"usage"=Dot::"usage" <> "\n It is defined for weights of finite and affine Lie algebras";
+
[…]

### 2011-03-13 AffineLieAlgebras/Mathematica/testd.m
Some test file changes

@@ -2,7 +2,1094 @@ AppendTo[$Path,"/home/anton/study/2011/Articles/AffineLieAlgebras/Mathematica/"]
 
 <<datastructures.m;
 
+
+
+Module[{b2=makeSimpleRootSystem[B,2]},
+       Expect["Partial orbit test", True, partialOrbit[b2][{rho[b2]}]==
+	      {{makeFiniteWeight[{3/2,1/2}]},{makeFiniteWeight[{1/2,3/2}],makeFiniteWeight[{3/2,-1/2}]},
+	       {makeFiniteWeight[{-1/2,3/2}],makeFiniteWeight[{1/2,-3/2}]},
+	       {makeFiniteWeight[{-3/2,1/2}],makeFiniteWeight[{-1/2,-3/2}]},
+	       {makeFiniteWeight[{-3/2,-1/2}]}}]]
+
+Throw::nocatch: 
+   Uncaught Throw[Partial orbit test: GOT UNEXPECTED VALUE False INSTEAD OF
+      True, assertion exception] returned to top level.
+
+Out[1]= Hold[Throw[Partial orbit test: GOT UNEXPECTED VALUE False INSTEAD OF\
+ 
+>      True, assertion exception]]
+
+Throw::nocatch: 
+   Uncaught Throw[Weights of [1,1] module of B2: GOT UNEXPECTED VALUE False
+      INSTEAD OF True, assertion exception] returned to top level.
+
+Out[16]= Hold[Throw[Weights of [1,1] module of B2: GOT UNEXPECTED VALUE False\
+ 
+>      INSTEAD OF True, assertion exception]]
+
+b2=makeSimpleRootSystem[B,2]
+
+Out[6]= finiteRootSystem[2, {finiteWeight[2, {1, -1}], 
+ 
+>     finiteWeight[2, {0, 1}]}]
+
+partialOrbit[b2][{rho[b2]}]
+
+                            3  1
+Out[16]= {{finiteWeight[2, {-, -}]}, 
+                            2  2
+ 
+                       1  3                     3    1
+>    {finiteWeight[2, {-, -}], finiteWeight[2, {-, -(-)}]}, 
[…]

### 2011-03-13 AffineLieAlgebras/Mathematica/lie.m
Some computations

@@ -142,9 +142,19 @@ Out[97]= weights[{standardBase[1, -1, 0, 0, 0, 0, 0, 0],
 
 freudenthalMultiplicities[b8][wg[[-1]]*2]//Timing
 
+Out[14]= {1.24008, mults$101}
+
+Out[9]= {1.26008, mults$99}
+
 Out[4]= {0.776049, mults$89}
 
-Out[4][[2]][standardBase[0,0,0,0,0,0,0,1]]
+Out[9][[2]][standardBase[0,0,0,0,0,0,0,0]]
+
+Out[12]= 70
+
+Out[11]= mults$99[standardBase[0, 0, 0, 0, 0, 0, 0, 1]]
+
+Out[10]= mults$89[standardBase[0, 0, 0, 0, 0, 0, 0, 1]]
 
 Out[6]= mults$89[standardBase[0, 0, 0, 0, 0, 0, 0, 1]]
 

### 2011-03-14 GeneralOverview/Lectures/2dqft.tex
Section on Noether's theorem is written.

@@
 
+\subsection*{Классическая и квантовая теория поля}
+\label{sec:qft}
+Напоминание про теорию поля.
+
+Лагранжева формулировка классической теории поля.
+
+ Действие
+\begin{equation}
+  S=\int d^dx \mathcal{L}
+\end{equation}
+зависит от полей $\varphi$ и констант связи $\vec u=(u_1,\dots,u_n)$.
+Например:
+\begin{equation}
+  S[\varphi]=\int d^d x\left( -\frac{(\partial \varphi)^2}{2}-\frac{\mu \varphi^2}{2}-\frac{u\varphi^4}{24}+h\varphi\right),
+\end{equation}
+
+\subsubsection*{Симметрии}
+\label{sec:symmetry}
+
+При преобразованиях координат
+\begin{equation}
+  \label{eq:303}
+  x\to x'
+\end{equation}
+поля тоже преобразуются, то есть у них не только меняется аргумент, но и само поле. Тип поля (скалярное, векторное, спинорное) -- это вид такого преобразования.
+\begin{equation}
+  \label{eq:304}
+  \varphi(x)\to \varphi'(x')=F(\varphi(x))
+\end{equation}
+
+При этом действие тоже преобразуется:
+\begin{equation}
+  \label{eq:305}
+  S'=\int d^{d}x' \mathcal{L}(\varphi'(x'),\partial_{\mu} \varphi'(x'))=\int d^{d}x \left|\frac{\partial x'}{\partial x}\right| \mathcal{L}(F(\varphi(x)),\frac{\partial x^{\nu}}{\partial x'^{\mu}} \partial_{\nu}F(\varphi(x)))
+\end{equation}
+{\bf Примеры.}
+
+Трансляции:
+
+\begin{equation*}
+  \label{eq:306}
+  x'^{\mu}=x^{\mu}+a^{\mu},\quad \varphi'(x+a)=\varphi(x),\quad S'=S
+\end{equation*}
+
+Поворот (преобразования Лоренца):
+\begin{equation*}
+  x'^{\mu}=m^{\mu}_{\nu} x^{\nu}, \quad \varphi'(m x)=\Lambda \varphi(x),\quad \Lambda \mbox{--представление группы} 
+\end{equation*}
+
+Теперь рассмотрим инфинитезимальные преобразования.
+Если действие инвариантно относительно каких-либо преобразований, то говорят, что в теории есть симметрия.
+В этом случае действие должно быть стационарно по отношению к инфинитезимальным преобразованиям.
+
+\begin{equation}
+  \label{eq:165}
+  x'^{\mu}=x^{\mu}+\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}
+\end{equation}
+($\omega_{a}$ -- бесконечно малые параметры).
+
+Наше поле преобразуется так:
+\begin{equation}
+  \label{eq:166}
+  \varphi'(x')=\varphi(x)+\omega_a \frac{\delta F}{\delta \omega_a} (x).
+\end{equation}
+Генератор преобразования определяется следующим равенством:
+\begin{equation}
+  \label{eq:167}
+  \delta_{\omega} \varphi(x)=\varphi'(x)-\varphi(x)\equiv -i\omega_a G_a \varphi(x)
+\end{equation}
+(здесь нет суммирования по $a$). Действие генератора на поле:
+\begin{equation}
+  \label{eq:168}
+  iG_a \varphi=\frac{\delta x^{\mu}}{\delta\omega_a} \partial_{\mu}\varphi-\frac{\delta F}{\delta \omega_a}
+\end{equation}
+
+Примеры генераторов:
+Если мы предположим, что поле $\varphi$ -- такое поле, которое не меняется при конформных преобразованиях, то есть $F(\varphi)=\varphi$, то мы получим следующий вид для генераторов:
+\begin{eqnarray}
+  \label{eq:169}
+  \mbox{трансляция}  & x'^{\mu}=x^{\mu}+\omega^{\mu}& \quad P_{\mu}=-i\partial_{\mu}\\
+  \mbox{поворот} & x'^{\mu}=x^{\mu}+\omega^{\mu}_{\nu}x^{\nu} & \quad L_{\mu\nu}=i(x_{\mu}\partial_{\nu}-x_{\nu}\partial{\mu})
+\end{eqnarray}
+Если же при поворотах поле преобразуется $\varphi'(x')=\Lambda\varphi(x)$, то при инфинитезимальных преобразованиях $\varphi'(x')=\varphi(x)-\frac{i}{2}\omega_{\mu\nu}S^{\mu\nu}$ и генератор принимает вид
+\begin{equation*}
+  L_{\mu\nu}=i(x_{\mu}\partial_{\nu}-x_{\nu}\partial{\mu})+S_{\mu\nu}
+\end{equation*}
+
+\subsubsection*{Теорема Нётер}
+\label{sec:noether}
+
+Теперь рассмотрим произвольные инфинитезимальные преобразования, при которых действие не меняется.
+Якобиан такого преобразования
+\begin{eqnarray*}
+  \frac{\partial x'^{\nu}}{\partial x^{\mu}} = \delta^{\mu}_{\nu}+\partial_{\mu}\left(\omega_a \frac{\delta x^{\nu}}{\delta \omega_a}\right)\\
+  \frac{\partial x^{\nu}}{\partial x'^{\mu}} = \delta^{\mu}_{\nu}-\partial_{\mu}\left(\omega_a \frac{\delta x^{\nu}}{\delta \omega_a}\right)
+\end{eqnarray*}
+\begin{equation*}
+  \left|\frac{\partial x'^{\nu}}{\partial x^{\mu}}\right| = 1+\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)
+\end{equation*}
+Вариация действия
+\begin{multline*}
+  0=\delta_{\omega} S=\int \mathcal{L}(\varphi',\partial_{\mu}\varphi',x'^{\mu})dx'-\int \mathcal{L}(\varphi,\partial_{\mu}\varphi,x)dx=\\
+  \int d^{d}x\left[ \left( 1+\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)\right) \mathcal{L} \left(\varphi+\delta_{\omega}\varphi,
+    \partial_{\mu}\varphi+\partial_{\mu}\delta_{\omega}\varphi\right)\right]-\mathcal{L}(\varphi,\partial_{\mu}\varphi)=
+\end{multline*}
+\begin{multline*}
+      \int d^{d}x\left( \frac{\partial \mathcal{L}}{\partial \varphi} \delta_{\omega}\varphi +\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\partial_{\mu}\varphi +\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)\mathcal{L}\right)
+\end{multline*}
+Первые два члена переписываются с использованием уравнений Эйлера-Лагранжа и интегрирования по частям:
+\begin{equation*}
+  \partial_{\mu}\left(\frac{\partial \mathcal{L}}{\partial (\partial_{\mu}\varphi)}\right)\delta_{\omega}\varphi+\frac{\partial \mathcal{L}}{\partial (\partial_{\mu}\varphi)}\delta_{\omega}\partial_{\mu}\varphi=
+    \partial_{\mu}\left(\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\varphi\right)
+\end{equation*}
+В итоге имеем:
+\begin{equation*}
+  0=\int d^{d}x \partial_{\mu}\left(\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\varphi +\delta^{\mu}_{\nu}\mathcal{L} \frac{\delta x^{\nu}}{\delta \omega_{a}}\right)
+\end{equation*}
+Если подставить явный вид вариации поля и ввести обозначение
+\begin{equation*}
+  j^{\mu}_{a}=\left(\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\partial_{\nu}\varphi -\delta^{\mu}_{\nu}\mathcal{L}\right) \frac{\delta x^{\nu}}{\delta \omega_{a}}-\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\frac{\delta F}{\delta w_{a}},
+\end{equation*}
+то для вариации действия выходит:
+\begin{equation*}
+  \delta_{\omega}S=-\int d^{d}x j^{\mu}_{a}\partial_{\mu}\omega_{a}
+\end{equation*}
+$j^{\mu}_{a}$ называется нетеровским током, соответствующим данной симметрии. 
+Если $\delta_{\omega} S=0$, то
+\begin{equation*}
+  \partial_{\mu}j^{\mu}_{a}=0
+\end{equation*}
+Сохраняющийся заряд:
+\begin{equation*}
+  Q_{a}=\int d^{d-1}x\; j^{0}_{a}
+\end{equation*}
+
+ Рассмотрим инфинитезимальное масштабное преобразование $\lambda=1+\omega$.
+При этом вариация $x_{\nu}$ будет $\delta_{\omega}x_{\nu}=\omega x_{\nu}$.
+При инфинитезимальных преобразованиях $x\to x+dl x$ вариация плотности лагранжиана дается Нётеровским током:
+\begin{equation}
+  \label{eq:74}
+  \delta\mathcal{L}=\partial_{\mu}J^{\mu}dl
+\end{equation}
+\begin{equation}
+  \label{eq:75}
+  J^{\mu}=x_{\nu}T^{\mu\nu}
+\end{equation}
+Здесь $T^{\mu\nu}$ - тензор энергии-импульса.  Через $\Theta$ мы обозначим след тензора энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия
+\begin{equation}
+  \label{eq:87}
+  \delta S=dl \int d^d x \Theta(x)
+\end{equation}
+Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$. В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
+
 \section{Лекция 2. }

### 2011-03-14 GeneralOverview/Lectures/talk.tex
Talk added

--- 2011-03-14 GeneralOverview/Lectures/2dqft.tex
@@
 
-\title{Конформная теория поля и критические явления\\
-\small{Академический университет, кафедра теоретической физики}
-}
-\author{Антон Назаров\\
-  \small{СПбГУ, физический факультет}\\
-  \small{кафедра физики высоких энергий и элементарных частиц}\\
-  \texttt{antonnaz@gmail.com}
-}
-\date{Осенний семестр 2010 года}
-
 \begin{document}
-\maketitle
-\thispagestyle{empty}
-\begin{abstract}
-  Текст представляет собой конспект лекций по квантовой теории поля в двух измерениях.
-Лекции читались в осеннем семестре 2010 года в Академическом университете для магистрантов 6 курса (группа теории конденсированного состояния).
-\end{abstract}
-\tableofcontents
-
-\section{Лекция 1}
-\label{sec:lecture-1}
-
-\subsection{Программа курса}
-\label{sec:program}
-\begin{enumerate}
-\item Введение.
-  \begin{itemize}
-  \item Двумерные модели
-  \item Фазовые переходы, критические индексы
-  \item Универсальность
-  \item Методы квантовой теории поля в статистической физике
-  \end{itemize}
-\item Перенормировки, ренормгруппа
-\item Решение модели Изинга
-  \begin{itemize}
-  \item Интегрируемость
-  \item Подход Каданова
-  \end{itemize}
-\item Конформная инвариантность
-  \begin{itemize}
-  \item Глобальная конформная инвариантность
-  \item Ограничения на корреляционные функции
-  \item Локальная конформная инвариантность в двух измерениях
-  \item Алгебра Витта и алгебра Вирасоро.
-  \end{itemize}
-\item Конформная теория поля
-  \begin{itemize}
-  \item Примарные и вторичные поля
-  \item Минимальные модели
-  \end{itemize}
-\end{enumerate}
-
-\subsection{Литература}
-\label{sec:literature}
-В \ref{sec:lecture-1} и \ref{sec:lecture-2} лекциях  мы опираемся на вводные главы книги \cite{difrancesco1997cft}.
-Мы уделяем большое внимание использованию математического аппарата квантовой теории поля в моделях статистической физики.
-При этом мы пользуемся знакомством слушателей с функциональным интегралом.
-Последовательное изложение техники функционального интеграла в статистической физике можно найти в книге А.Н.
-Васильева \cite{vasiliev1976}.
-
-В следующих лекциях \ref{sec:lecture-3}, \ref{sec:lecture-4} мы обсуждаем применение ренормгруппы к описанию критического поведения, более подробно и достаточно педагогически этот вопрос рассматривается в книге \cite{ma1980} (\cite{ma2000modern}).
-Исчерпывающую информацию содержит моногорафия \cite{vasiliev1998} (английский вариант \cite{Vasilev:1027193}).
-Лекция \ref{sec:lecture-4} основана на вводной главе обзора \cite{Ravanini:2000st}.
-
-Лекции \ref{sec:lecture-5}, \ref{sec:lecture-6} посвящены  точному решению модели Изинга в двух измерениях.
-Подробно решение  модели Изинга в двух измерениях рассмотрено в книге  \cite{belavin2001lect}, на материале которой и основано изложение в данных лекциях.
-
-Изложение конформной теории поля в двух измерениях опирается на оригинальную статью \cite{belavin1984ics}, книгу \cite{difrancesco1997cft}, обзор \cite{zamolodchikov1989rus,zamolodchikov1989conformal}, недавно переизданный в виде книги.
-В последних лекциях \ref{sec:lecture-10}, \ref{sec:lecture-11}, \ref{sec:lecture-12} использовались также материалы из обзора \cite{Ginsparg:1988ui}, хотя логика изложения ближе к книге \cite{difrancesco1997cft}.
-Некоторые алгебраические сведения о представлениях алгебры Вирасоро  могут быть найдены в книге \cite{golod2001}.
-
-Дополнительные сведения о приложениях конформной теории поля и ее связи с теорией суперструн можно найти в подробных лекциях \cite{springerlink:10.1134/S1063778810050108} и обзорах \cite{Walton:1999xc}, \cite{gaberdiel2000icf}.
-
-\subsection{Введение}
-\label{sec:intro}
-Чем интересны двумерные системы?
-
-Во-первых, они существуют в природе. Например, критическое поведение на поверхности металлов напоминает поведение модели Изинга в двух измерениях \cite{campuzano1985110}.
-
-Во-вторых, в двух измерениях даже в простых моделях есть фазовые переходы.
-Это не так, например,  в одномерной модели Изинга.
-В простых двумерных моделях можно вычислить критические индексы и изучать поведение системы при фазовых переходах.
-
-Гипотеза универсальности утверждает, что все системы в критической точке разбиваются на небольшое число классов.
-Системы из одного класса ведут себя одинаково, имеют одинаковые критические индексы.
-Благодаря гипотезе универсальности существует лишь небольшое число типов критического поведения, поэтому значения индексов, вычисленные теоретически в простых моделях соответствуют гораздо более сложным реальным системам.
-
-В критической точке наблюдается масштабная инвариантность, что ведет к конформной инвариантности \cite{Polyakov:1970xd}.
-В двух измерениях конформная инвариантность дает очень много сведений о системе, так как алгебра конформных преобразований бесконечномерна.
-В результате поведение системы может быть описано строго математически методами двумерной конформной теории поля.
-
-Двумерная конформная теория поля имеет и другое применение, не связанное с описанием фазовых переходов --- это теория струн, которая считается перспективным кандидатом на роль квантовой теории гравитации.
-
-В данных лекциях мы займемся проблемой описания фазовых переходов в двумерных системах.
-Основной для нас будет двумерная модель Изинга.
-Мы обсудим обоснование гипотез подобия и универсальности в рамках ренормгруппового подхода, покажем наличие конформной инвариантности в критической точке и продемонстрируем на примере применение конформной теории поля для вычисления критических индексов и корреляторов.
-
-\subsection{Фазовые переходы. Основные понятия}
-\label{sec:phase-transitions}
-
-Напомним некоторые основные понятия теории фазовых переходов на примере двумерной модели Изинга.
-
-Мы рассматриваем статистические системы.
-Все макроскопические характеристики таких систем вычисляются из статсуммы, которая связана с микроскопическим описанием системы.
-Для больцмановского распределения вероятность системы находиться в состоянии с номером $i$ с энергией $E_i$
-\begin{equation}
-  \label{eq:2}
-  P_i=\frac{1}{Z}e^{-\beta E_i}, \quad \beta=\frac{1}{T}
-\end{equation}
-Мы используем систему единиц, в которой постоянная Больцмана равна единице $k_B=1$, введем $\beta=\frac{1}{T}$. Статсумма:
-\begin{equation}
-  \label{eq:3}
-  Z=\sum_i e^{-\beta E_i}.
-\end{equation}
-Свободная энергия
-\begin{equation}
-  \label{eq:4}
-  F=-T\ln Z
-\end{equation}
-Внутренняя энергия
-\begin{equation}
-  \label{eq:5}
-  U=-\frac{1}{Z}\frac{\partial Z}{\partial \beta}=-T^2 \frac{\partial}{\partial T}\left(\frac{F}{T}\right)
-\end{equation}
-Телоемкость равна производной внутренней энергии по температуре при заданном объеме
-\begin{equation}
-  \label{eq:6}
-  C=\left(\frac{\partial U}{\partial T}\right)_V=-T\frac{\partial^2 F}{\partial T^2}
-\end{equation}
-Таким образом статсумма является производящей функцией всех термодинамических величин. Вычисление статсуммы в реальных системах --- это сложная задача.
-Макроскопическое описание имеет смысл только в термодинамическом пределе, когда число частиц стремится к бесконечности $N\to \infty$.
-
-Двумерная модель Изинга --- это простейшая модель магнетика.
-Она формулируется на решетке, которую мы будем, для простоты, считать прямоугольной.
-Вершины решетки нумеруются латинскими индексами $i,j$.
-В вершинах решетки находятся частицы со спинами $\sigma_j$ равными $\pm 1$ (вверх или вниз).
-Взаимодействуют только ближайшие соседи, константу взаимодействия обозначим через $J$.
-Для энергии системы имеем
-\begin{equation}
-  \label{eq:1}
-  E=J\sum_{\left<i,j\right>} \sigma_i\cdot \sigma_j-h\sum_i \sigma_i
-\end{equation}
-Суммирование в первом члене ведется только по парам ближайших соседей, второй член --- это взаимодействие со внешним полем $h$.
-Пусть система состоит из $N$ вершин. Она имеет $2^N$ различных конфигураций. Случай $J>0$ соответствует ферромагнетику, $J<0$ --- антиферромагнетику. 
-При $h=0$ низшее энергетическое состояние двукратно вырождено --- это состояние, в котором все спины направлены вверх или вниз.
-
-Существует несколько точных решений двумерной модели Изинга в отсутствие внешнего поля.
-Решений со внешним полем и в большем числе измерений пока не известно.
-Недавнее достижение Станислава Смирнова, за которое он получил в этом году премию Филдса, непосредственно связано с темой наших лекций.
-В своих работах Станислав Смирнов впервые строго доказал наличие конформного предела в двумерной модели Изинга \cite{smirnov2007conformal,smirnov2006towards,smirnov2001critical}.
-Фазовые переходы в модели Изинга наблюдаются только в этом пределе, при конечных размерах системы никаких переходов нет.
-
-При исследовании магнетиков нас интересуют следующие термодинамически величины.
-Намагниченность, которая равна среднему значению спина по всем конфигурациям $[\sigma]$:
-\begin{equation}
-  \label{eq:7}
-  M=\left<\sigma_j\right>=\frac{1}{NZ}\sum_{[\sigma]}\left(\sum_i\sigma_i\right)e^{-\beta E[\sigma]}=-\frac{1}{N}\frac{\partial F}{\partial h}.
-\end{equation}
-Намагниченность является параметром порядка --- в упорядоченной (анти)ферромагнитной фазе она отлична от нуля.
-
-Магнитная восприимчивость
-\begin{equation}
-  \label{eq:8}
-  \chi=\left.\frac{\partial M}{\partial h}\right|_{h=0}=\frac{1}{N}\frac{\partial}{\partial h}\left(\frac{1}{Z}\sum_{[\sigma]}\left(\sum_i \sigma_i\right)e^{-\beta E[\sigma]}\right)=\frac{1}{NT}\left(\left<\sigma_{\mathrm{tot}}^2\right>-\left<\sigma_{\mathrm{tot}}\right>^2\right)
-\end{equation}
-Здесь мы ввели обозначение $\sigma_{\mathrm{tot}}=\sum_i \sigma_i$. Видно, что магнитная восприимчивость пропорциональна дисперсии полного спина. Введем парную корреляционную функцию
-\begin{equation}
-  \label{eq:9}
-  \Gamma(i-j)=\left<\sigma_i-\sigma_j\right>.
-\end{equation}
-Из-за вращательной и трансляционной инвариантности $\Gamma$ зависит только от расстояния между вершинами $\left|i-j\right|$. Связная корреляционная функция
-\begin{equation}
-  \label{eq:10}
-  \Gamma_c(i-j)=\left<\sigma_i-\sigma_j\right>_c=\left<\sigma_i\sigma_j\right>-\left<\sigma_i\right>\left<\sigma_j\right>.
-\end{equation}
-Можно показать, что
-\begin{equation}
-  \label{eq:11}
-  \chi=\beta\sum_i\Gamma(i)_c.
-\end{equation}
-То есть магнитная восприимчивость --- это мера статистической когерентности системы, она растет с ростом зависимости спинов между собой.
-
-\subsection{Классические статистические модели. Связь с теорией поля.}
-\label{sec:statistical-models-qft}
-
-Распределение Больцмана инвариантно относительно сдвига энергии на константу, поэтому можно переписать гамильтониан в более удобном для обобщения виде:
-\begin{equation}
-  \label{eq:12}
-  \begin{array}{l}
-    \sigma_i\sigma_j=2\delta_{\sigma_i\sigma_j}-1\\
-    E[\sigma]=-2J\sum_{\left<ij\right>}\delta_{\sigma_i\sigma_j}-h\sum_i \sigma_i
-  \end{array}
-\end{equation}
-Обсудим некоторые обобщения модели Изинга и проиллюстрируем сходство статистической механики с теорией поля.
-
-Если $\sigma_i$ может принимать значения не $-1,1$, а $1,2\dots,q$, то мы получаем модель Поттса с $q$ состояниями.
-Подобным образом получаются и модели Ашкина-Теллера \cite{difrancesco1997cft}.
-
-Другой класс дискретных моделей отличается более существенно.
-Если в модели Изинга переменные (спины) живут в вершинах, а энергия --- на ребрах, то в вершинных моделях все наоборот.
-В качестве переменных берутся направленные ребра (стрелки), а энергия в вершине зависит от числа входящих и выходящих из нее стрелок.
-Пусть ребра, входящие в вершину имеют значения $0,1$ в зависимости от направления стрелки.
-Тогда энергия вершины обозначается через $R_{\alpha\mu}^{\beta\nu},\; \alpha,\beta,\mu,\nu=0,1$.
-Бывает 16 таких членов.
-В зависимости от того, сколько из них не равны нулю, выделяют 6-вершинную и 8-вершинную модели.
-8-вершинная модель --- ненулевой вклад только когда входит четное число стрелок (0 входит, 4 выходит; 4 входит, 0 выходит; 6 способов выбрать две входящие стрелки -- итого 8 отличных от нуля членов $R_{\alpha\mu}^{\beta\nu}$).
-
-Другой класс статистических моделей --- это модели с непрерывными степенями свободы. Например, заменим спины $\sigma_i$ в \eqref{eq:1} на единичные вектора в $m$-мерном пространстве $\vec n_i$.
-\begin{equation}
-  \label{eq:14}
-  \left|\vec n\right|^2=1
-\end{equation}
-В результате получим гамильтониан
-\begin{equation}
-  \label{eq:13}
-  E[\vec n]=J\sum_{\left<ij\right>}\vec n_i\cdot \vec n_j-\sum_i \vec h\cdot \vec n_i
-\end{equation}
-Это гамильтониан классической $O(m)$-модели Гейзенберга.
-
-В критической точке параметр порядка системы стремится к бесконечности, кроме того, фазовый переход в дискретных моделях наблюдается только в термодинамическом пределе числа вершин стремящегося к бесконечности ($N\to \infty$).
-Поэтому при описании фазового перехода имеет смысл перейти от модели с дискретным пространством  к непрерывному $d$-мерному пространству.
-В дальнейшем $d$ будет равно двум, но сейчас мы пишем в самом общем виде, чтобы указать аналогию с теорией поля.
-При переходе к непрерывному пространству гамильтониан \eqref{eq:13} принимает вид
-\begin{equation}
-  \label{eq:15}
-  E[\vec n]=\int d^d x \left(J\partial_kn_i\partial_k  n_i-h_i\cdot n_i\right)
-\end{equation}
-Здесь подразумевается суммирование по повторяющимся индексам.
-(Легко понять обратный переход, если заменить производные разностями по ближайшим соседям, а потом отбросить в энергии постоянный член $J\sum_i \left|\vec n_i\right|^2=JN$).
-Условие $\vec n^2(x)=1$ сложно использовать, поэтому мы заменим его на другое аналогичное.
-Первый вариант такой замены --- это наложить требование $\frac{1}{V}\int d^dx\; \vec n^2=1$.
-В результате получается так называемая сферическая модель.
-Другая возможность --- добавить в гамильтониан \eqref{eq:15} потенциал $V(\left|\vec n\right|)$ с минимумом в $\left|\vec n\right|=1$ и устремить константу связи к бесконечности.
-Простейший вид такого потенциала --- $V(\left|\vec n\right|)=a\vec n^2+b\left(\vec n^2\right)^2$.
-Добавим его в гамильтониан и изменим нормировку $\vec n$ так, чтобы константа $J$ ушла.
-Получим
-\begin{equation}
-  \label{eq:16}
-  E[\vec n]=\int d^d x \left(\frac{1}{2}\partial_k n_i\cdot \partial_k n_i-\frac{1}{2}\mu^2 \vec n^2+\frac{1}{4}u\left(\vec n^2\right)^2\right)
-\end{equation}
-Если у $\vec n$ всего одна компонента $\varphi$, то мы получаем скалярную модели $\varphi^4$. Если $u=0$, то такая модель называется Гауссовой и допускает точное решение.
-\begin{equation}
-  \label{eq:17}
-  E[\varphi]=\int d^d x (\frac{1}{2}(\nabla \varphi)^2+\frac{1}{2}\mu^2 \varphi^2)
-\end{equation}
-Статсумма --- это сумма $e^{-\beta E[\varphi]}$ по всем конфигурациям поля $\varphi$, то есть она записывается при помощи функционального интеграла:
-\begin{equation}
-  \label{eq:18}
-  Z=\int \mathcal{D}\varphi e^{-\beta E[\varphi]}
-\end{equation}
-В гауссовой модели функциональный интеграл имеет гауссовский вид, поэтому он хорошо определен и легко вычисляется.
-Значит можно вычислить статсумму и все корреляционные функции.
-Величины в модели $\varphi^4$ можно получать по теории возмущений вокруг решения гауссовой модели.
-Это и есть вычисление функционального интеграла как суммы по фейнмановским диаграммам.
-
 \subsection*{Классическая и квантовая теория поля}
@@
 
-\section{Лекция 2. }
-\label{sec:lecture-2}
-
-\subsection{Квантовые статистические модели}
-\label{sec:quantum-statistical-models}
-
-Микросостояния квантовых статистических систем описываются при помощи матрицы плотности
-\begin{equation}
-  \label{eq:19}
-  \rho=e^{-\beta H}
-\end{equation}
-Статсумма дается суммой по собственным состояниям гамильтониана или следом матрицы плотности:
-\begin{equation}
-  \label{eq:20}
-  Z=\sum_n e^{-\beta E_n}=\mathrm{Tr} \rho
-\end{equation}
-Значение физической величины определим как среднее по состояниям:
-\begin{equation}
-  \label{eq:21}
-  \left< A\right>=\sum_n \left< n\right| e^{-\beta H}A\left| n \right>=\mathrm{Tr}(\rho A)
-\end{equation}
-$e^{-\beta H}$ похоже на оператор эволюции $e^{-i H t}$, то есть его тоже можно записать через функциональный интеграл.
-Покажем, как это делается на примере системы с одной степенью свободы.
-В этом случае ядро оператора плотности имеет вид
-\begin{equation}
-  \label{eq:22}
-  \rho(x_f,x_i)=\left<x_f\right|e^{-\beta H} \left|x_i\right>
-\end{equation}
-Вспомним, что в квантовой механике оператор эволюции имеет вид $U(t)=e^{-i H t}$, а его ядро --- амплитуда перехода из состояния $\left|x_i\right>$ в $\left<x_f\right|$ дается интегралом по траекториям
-\begin{equation}
-  \label{eq:23}
-  \left<x_f\right| U(t)\left| x_i\right>=\int_{(x_i,0)}^{(x_f,t)} [dx] e^{i S[x]}
-\end{equation}
-Заменой $t\to i\tau, \; \tau\in [0,\beta]$ (виковским поворотом) переходим к евклидову действию $S[x(t)]\to iS_E[x(\tau)]$. Для ядра оператора плотности получаем
-\begin{equation}
-  \label{eq:24}
-  \rho(x_f,x_i)=\int_{(x_i,0)}^{(x_f,\beta)} [dx] e^{-S_E[x]}
-\end{equation}
-Статсумма
-\begin{equation}
-  \label{eq:25}
-  Z=\int dx \rho(x,x)=\int [dx] e^{-S_E[x]}
-\end{equation}
-Среднее значение $A$
-\begin{equation}
-  \label{eq:26}
-  \begin{array}{l}
-    \left<A\right>=\frac{1}{Z}\int dx \left<x\right|\rho A\left|x\right>=\frac{1}{Z}\int dx\; dy \left<x\right|\rho\left|y\right>\left<y\right|A\left|x\right>=    \\
-    =\frac{1}{Z}\int dx\; dy \int_{(x,0)}^{(y,\beta)} [dx] \left<y\right| A\left| x\right> e^{-S_E[x]}=\frac{1}{Z}\int dx\; dy\int_{(x,0)}^{(y,\beta)} [dx] A(x) \delta(x-y) e^{-S_E[x]}=\\
-    =\frac{1}{Z}\int [dx] A(x(0))e^{-S_E[x]}
-  \end{array}
-\end{equation}
-Здесь мы предположили, что $A$ зависит только от $x$, то есть $\left<y\right| A\left|x\right>=A(x)\delta(x-y)$.
-Мы видим, что значение $A$ дается функциональным интегралом, но $A$ вычисляется в точке $\tau=0$.
-
-Обобщение на систему с континуумом степеней свободы и многочастичные функции естественно.
-Статсумма квантовой системы получается из обычного интеграла по траекториям путем викова поворота и ограничения евклидова времени на конечный промежуток $[0,\beta]$.
-При нулевой температуре ($\beta\to \infty$) мы получаем обычный производящий функционал в евклидовом времени, то есть теорию поля.
-При конечных температурах статсумма квантовой $d$-мерной системы напоминает статсумму $d+1$-мерной классической системы на полосе шириной $\beta$.
-
-\subsection{Критические явления}
-\label{sec:critical-phenomena}
-
-Фазовые переходы характеризуются скачком в макроскопических характеристиках системы.
-При переходах первого рода скачком меняется внутренняя энергия (например, при переходе жидкость-газ).
-При переходах второго рода наблюдается скачок производных макроскопических термодинамических величин (теплоемкость, магнитная восприимчивость).
-
-Строго говоря, фазовые переходы бывают только в термодинамическом пределе.
-Это легко понять для систем типа модели Изинга в нулевом поле, где энергия любой конфигурации кратна энергетическому масштабу $\epsilon=-J$, а статсумма представляет собой полином от $z=e^{-\beta\epsilon}$.
-В модели Изинга наибольшая энергия $E=2N\epsilon$, $Z$- полином степени $2N$ от $z$ с единичными коэффициентами.
-Корни этого полинома лежат вне положительной вещественной оси и комплексно сопряжены.
-Сингулярности свободной энергии или ее производных могут быть только в корнях, которые находятся вне физической области при $N<\infty$.
-При $N\to \infty$ число корней становится бесконечным, они лежат на дугах, которые могут касаться положительной вещественной оси.
-В этих точках поведение термодинамических величин и становится сингулярным.
-
-Нас будут интересовать переходы второго рода. Именно в них имеет место конформная инвариантность. 
-Перечислим основные результаты для модели Изинга в двух измерениях.
-
-Здесь есть один фазовый переход при конечной температуре. 
-Критическая температура
-\begin{equation}
-  \label{eq:27}
-  T_c:\quad \sh \frac{2J}{T_c}=1
-\end{equation}
-При $T>T_c$ спонтанная намагниченность исчезает.
-При $T<T_c$ она не равна нулю и стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_c$.
-Это ферромагнитная фаза.
-Около критической точки спонтанная намагниченность ведет себя как
-\begin{equation}
-  \label{eq:28}
-  M\sim \left|T_c-T\right|^{\frac{1}{8}}
-\end{equation}
-Направление намагниченности определяется тем, куда было направлено внешнее поле до того, как его устремили к $0$.
-
-При подходе к критической точке магнитная восприимчивость расходится
-\begin{equation}
-  \label{eq:29}
-  \chi=\frac{\partial M}{\partial h}\sim \left|T-T_c \right|^{-\frac{7}{4}}.
-\end{equation}
-Вдали от критической точки корреляторы $\Gamma_c(i)$ убывают экспоненциально с расстоянием. Характерная длина убывания $\xi$ называется корреляционной длиной
-\begin{equation}
-  \label{eq:30}
-  \left<\sigma_i\sigma_j\right>_c\sim e^{-\frac{\left|i-j\right|}{\xi(T)}}\quad \left|i-j\right|>>1.
-\end{equation}
-При $T\to T_c$ корреляционная длина расходится
-\begin{equation}
-  \label{eq:31}
-  \xi(T)\sim \frac{1}{\left|T-T_c\right|}.
-\end{equation}
-Такое поведение характеризует переходы второго рода и наблюдается в критических точках фазовой диаграммы.
-
-Около критической точки система состоит из доменов разной намагниченности.
-Существуют домены всевозможных размеров от шага решетки до корреляционной длины $\xi$.
-Свободная энергия $F$ получает вклады от доменных стенок.
-Сингулярное поведение возникает из-за вкладов доменов большого размера, оно определяется флуктуациями и не может быть правильно учтено в теории среднего поля.
-Вблизи критической температуры $\xi$ больше физических размеров системы.
-Свободная энергия перестает зависеть от $\xi$.
-
-Парная корреляционная функция ведет себя как
-\begin{equation}
-  \label{eq:32}
-  \Gamma(\vec n)\sim \frac{1}{\left|\vec n\right|^{d-2+\eta}}
-\end{equation}
-Поведение термодинамических величин определяется критическими индексами. Перечислим их вместе со значениями в двумерной модели Изинга. Эти значения получены из точных решений модели.
-\begin{table}[h!tb]
-\label{tab:diagrams}
-\noindent  \centering{
-\begin{tabular}{|l|l|l|}
-  \hline
-  Критический  & Термодинамическая & Значение индекса в \\
-  индекс &  величина  & двумерной модели Изинга\\
-  \hline
-  $\alpha$ & $C\sim \frac{1}{\left|T-T_c\right|^{\alpha}}$ & $0$\\
-  $\beta$ & $M\sim \left|T-T_c\right|^{\beta}$ & $\frac{1}{8}$\\
-  $\gamma$ & $\chi\sim \frac{1}{\left|T-T_c\right|^{\gamma}}$ & $\frac{7}{4}$\\
-  $\delta$ & $M\sim h^{\frac{1}{\delta}}$ & $15$ \\
-  $\nu$ & $\xi\sim \frac{1}{\left|T-T_c\right|^{\nu}}$ & $1$\\
-  $\eta$ & $\Gamma(\vec n)\sim \left|\vec n\right|^{2-d-\eta}$ & $\frac{1}{4}$\\
-  \hline
-\end{tabular}
-\caption{Критические индексы и их значения в модели Изинга в 2 измерениях}
-}
-\end{table}
-
-Заметим, что систему можно описывать классической статистической механикой (обычной квантовой теорией поля с неограниченным временем) когда корреляционная длина больше характерной длины волны де Бройля.
-Если характерная скорость $v$ (скорость света, скорость Ферми или скорость какого-либо возбуждения), то $\lambda_T=\frac{v\hbar}{k_B T}\sim \beta$.
-То есть классическая статистика применима при больших температурах или вблизи критической точки, если $T_c\neq 0$.
-
-\subsection{Скейлинг или масштабная инвариантность}
-\label{sec:scaling}
-
-Гипотеза подобия связывает между собой критические индексы.
-Ее можно сформулировать так: плотность свободной энергии $f(t,h)=\frac{F}{N}$ около критической точки является однородной функцией $h$ и безразмерной температуры $t=\frac{T}{T_c}-1$.
-То есть существуют $a,b$:
-\begin{equation}
-  \label{eq:33}
-  f(\lambda^a t,\lambda^b h)=\lambda f(t,h)
-\end{equation}
-В следующих лекциях мы обоснуем эту гипотезу при помощи ренормгруппы.
-
-Покажем теперь, какие условия накладывает гипотеза подобия на критические индексы. Заметим, что $t^{-\frac{1}{a}}f$ инвариантна при преобразовании $t\to \lambda^a t, h\to \lambda^b h$. Введем
-\begin{equation}
-  \label{eq:34}
-  y=\frac{h}{t^{\frac{b}{a}}}
-\end{equation}
-Тогда
-\begin{equation}
-  \label{eq:35}
-  f(t,h)=t^{\frac{1}{a}}g(y).
-\end{equation}
-Для спонтанной намагниченности имеем
-\begin{equation}
-  \label{eq:36}
-  M=-\left.\frac{\partial f}{\partial h}\right|_{h=0}=t^{\frac{1-b}{a}}g'(0),
-\end{equation}
-а для  магнитной восприимчивости
-\begin{equation}
-  \label{eq:37}
-  \chi=\left.\frac{\partial^2 f}{\partial h^2}\right|_{h=0}=t^{\frac{1-2b}{a}}g''(0).
-\end{equation}
-Аналогично для удельной теплоемкости получаем
-\begin{equation}
-  \label{eq:38}
-  c=-T\left.\frac{\partial^2 f}{\partial T^2}\right|_{h=0}=-\frac{1}{T_c}t^{\frac{1}{a-2}}g''(0)
-\end{equation}
-В пределе $t\to 0$ $M\sim h^{\frac{1}{\delta}}$, поэтому $g'(y)\sim y^{\frac{1}{\delta}}$ при $y\to \infty$.
-А значит, если в критической точке намагниченность $M$ конечна и не равна нулю, должно выполняться равенство $1-b-\frac{b}{\delta}=0$.
-Подставляя выражение для $\delta$ через $b$ в (\ref{eq:36},\ref{eq:37},\ref{eq:38}), мы получаем связь критических индексов
-  \begin{eqnarray}
-    \label{eq:39}
-    \alpha=2-\frac{1}{a}\\
-    \beta=\frac{1-b}{a}\\
-    \gamma=-\frac{1-2b}{a}\\
-    \delta=\frac{b}{1-b}
-  \end{eqnarray}
-\subsection{Процедура Каданова}
-\label{sec:kadanoff-procedure}
-Теперь обоснуем гипотезу подобия в модели Изинга при помощи процедуры Каданова и свяжем индексы $a,b$ с $\nu,\eta$.
-Рассмотрим кубическую $d$-мерную модель Изинга.
-\begin{equation}
-  \label{eq:40}
-  H=-J\sum_{\left<ij\right>}\sigma_i \sigma_j-h\sum_i \sigma_i
-\end{equation}
-Разбиваем решетку на блоки со стороной в $r$ ячеек. Будем нумеровать блоки большими латинскими буквами $I,J$ и понимать под записью $i\in I$ перечисление вершин в $I$-том блоке.
-Сумма спинов в блоке принимает значения от $r^{-d}$ до $r^d$. Введем блочный спин
-\begin{equation}
-  \label{eq:41}
-  \Sigma_I=\frac{1}{R}\sum_{i\in I}\sigma_i
-\end{equation}
-$R$ - нормировочный множитель, который выбирается так, чтобы блочный спин мог принимать значения $\pm 1$. Если бы спины были всегда в одном направлении, то $R$ имел бы значение $r^d$.
-
-Мы предполагаем, что поведение вблизи критической точки описывается в терминах блочных спинов, так как корреляционная длина $\xi>>r$. Гамильтониан для блочных спинов имеет вид
-\begin{equation}
-  \label{eq:42}
-  H'=-J' \sum_{\left<IJ\right>} \Sigma_I \Sigma_J-h' \sum_I \Sigma_I
-\end{equation}
-Так как корреляционная длина для блоков
-\begin{equation}
-  \label{eq:43}
-  \xi'=\frac{\xi}{r},
-\end{equation}
-то из (\ref{eq:31}) для температуры имеем
-\begin{equation}
-  \label{eq:44}
-  t'=r^{\frac{1}{\nu}} t.
-\end{equation}
-Суммарная энергия взаимодействия со внешним полем должна оставаться неизменной, то есть
-\begin{equation}
-  \label{eq:45}
-  h\sum_i \sigma_i=h' \sum_I \Sigma_I=\frac{h'}{R}\sum_i \sigma_i\quad\Longrightarrow\quad h'= Rh
-\end{equation}
-Так как общая свободная энергия тоже не должна меняться, то свободная энергия на блок $\sim r^d f$, то есть
-\begin{equation}
-  \label{eq:46}
-  f(t',h')=r^d f(t,h)
-\end{equation}
-или
-\begin{equation}
-  \label{eq:47}
-  f(t,h)=r^{-d} f(r^{\frac{1}{\nu}} t, Rh)
-\end{equation}
-Осталось вычислить $R$ как функцию от $r$, чтобы оправдать гипотезу подобия. Смотрим на парный коррелятор в критической точке
-\begin{multline}
-  \label{eq:48}
-  \Gamma'(\vec n)=\left< \Sigma_I\Sigma_J\right>-\left< \Sigma_I\right>\left<\Sigma_J\right>=\frac{1}{R^2}\sum_{i\in I}\sum_{j\in J}\left(\left<\sigma_i \sigma_j\right>-\left<\sigma_i\right>\left<\sigma_j\right>\right) =\\
-  = \frac{r^{2d}}{R^2}\Gamma(r\vec n)=\frac{R^{-2}r^{2d}}{\left|r\vec n\right|^{d-2+\eta}}=\frac{R^{-2}r^{d+2-\eta}}{\left|\vec n\right|^{d-2+\eta}}
-\end{multline}
-Отсюда
-\begin{equation}
-  \label{eq:49}
-  R=r^{\frac{d+2-\eta}{2}}, \quad h'=r^{\frac{d+2-\eta}{2}}h
-\end{equation}
-Подставляя в (\ref{eq:33}) $r=\lambda^{\frac{1}{d}}$ получаем выражение для скейлинговых параметров $a,b$:
-\begin{eqnarray}
-  \label{eq:50}
-  a=\frac{1}{\nu d}\\
-  b=\frac{d+2-\eta}{2d}
-\end{eqnarray}
-Для критических индексов имеем
-\begin{eqnarray}
-  \label{eq:51}
-  \alpha=2-\nu d\\
-  \beta=\frac{1}{2}\nu (d-2+\eta)\\
-  \gamma=\nu (2-\eta)\\
-  \delta=\frac{d+2-\eta}{d-2+\eta}
-\end{eqnarray}
-
-\section{Лекция 3}
-\label{sec:lecture-3}
-В прошлой лекции мы обосновали гипотезу подобия при помощи рассмотрения блочных спинов и введения эффективного гамильтониана, имеющего ту же форму, но другие константы связи.
-Эта процедура является перенормировкой в координатном пространстве, она определяет отображение гамильтониана $H\to H'$.
-Последовательное применение такой процедуры порождает так называемую ренормгруппу.
-Строго говоря, ренормгруппа является не группой, полугруппой, так как у преобразования нет обратного, ведь при переходе к блокам большего размера мы теряем информацию.
-Опишем ренормгруппу для решеточных моделей.
-
-\subsection{Ренормгруппа в решеточных моделях}
-\label{sec:renormgroup-lattice-models}
-Рассматриваем решеточную модель, состоящую из $N$ спинов $\sigma_i$ на $d$-мерной решетке. Общий вид гамильтониана таких моделей
-\begin{equation}
-  \label{eq:55}
-  H(\vec J,[\sigma],N)=J_0 + J_1\sum_i \sigma_i +J_2\overset{(1)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j+J_3\overset{(2)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j + \dots
-\end{equation}
-Здесь мы явно указали на зависимость гамильтониана от констант связи, которые собраны в вектор $\vec J=(J_0,J_1,J_2,J_3,\dots)$.
-Сумма $\overset{(1)}{\sum_{\left<ij\right>}}$ - это сумма по ближайшим соседям, $\overset{(2)}{\sum_{\left<ij\right>}}$ - сумма по вершинам, разделенным двумя ребрами (через одного) и так далее.
-Статсумма
-\begin{equation}
-  \label{eq:56}
-  Z(\vec J,N)=\sum_{[\sigma]}e^{-H(\vec J,[\sigma],N)}
-\end{equation}
-Мы так переопределили константы связи, чтобы избавиться от множителя $\beta$.
-
-Теперь мы вводим блочные переменные с блоком со стороной в $r$ ячеек решетки, содержащим $r^d$ вершин.
-$\Sigma_I$ - блочные спины, $\xi_i$ - переменные внутри блока.
-В таких переменных статсумма переписывается так:
-\begin{equation}
-  \label{eq:57}
-  Z(\vec J,N)=\sum_{[\Sigma][\sigma]}e^{-H(\vec J,[\Sigma],[\sigma],N)}
-\end{equation}
-Если мы просуммируем по внутриблочным степеням свободы $\xi$, то получится перенормированный гамильтониан $H'(\vec J,[\Sigma],Nr^{-d})$.
-\begin{equation}
-  \label{eq:58}
-  e^{-H'(\vec J',[\Sigma],Nr^{-d})}=\sum_{[\xi]}e^{-H(\vec J,[\Sigma],[\xi],N)}
-\end{equation}
-Вблизи критической точки можно предполагать что у $H'$ такой же вид, как и у $H$, так как параметр порядка расходится и поведение определяется дальними корреляциями.
-Описания поведения системы в терминах $H'$ и $H$ эквивалентны, поэтому соответствующие выражения для статсуммы должны совпадать (с точностью до умножения на константу):
-\begin{equation}
-\label{eq:52}
-  Z(\vec J,N)=\sum_{[\Sigma]}e^{-H'(\vec J',[\Sigma],Nr^{-d})}=Z(\vec J',Nr^{-d})
-\end{equation}
-Удельная свободная энергия отображается как $f(\vec J)=r^{-d} f(\vec J')$.
-
-Отображение констант связи $\vec J\to\vec J'$ и порождает ренормгруппу. Будем его записывать как
-\begin{equation}
-  \label{eq:53}
-  \vec J'=T(\vec J)
-\end{equation}
-Последовательное применение таких преобразований порождает в пространстве констант связи некоторый набор точек, который называется траекторией ренормгруппы.
-
-На каждом шаге корреляционная длина уменьшается в $r$ раз, поэтому траектория уводит систему из окрестности критической точки.
-Но в самой критической точке корреляционная длина бесконечна, поэтому эта точка неподвижна относительно действия ренормгруппы.
-
-В общем случае критическое поведение наблюдается на некоторой критической поверхности в пространстве $\vec J$. Под действием ренормгруппы точки двигаются по ней. Стационарная точка
-\begin{equation}
-  \label{eq:54}
-  \vec J_c=T(\vec J_c)
-\end{equation}
-называется фиксированной точной ренормгруппы.
-
-Вообще говоря, преобразование $T$ нелинейно, однако в окрестности фиксированной точки его можно линеаризовать.
-Вводим переменную $\delta\vec J=\vec J-\vec J_c$ и раскладываем $T$ в ряд Тейлора по $\delta\vec J$.
-Тогда
-\begin{equation}
-  \label{eq:59}
-  \delta\vec J'=A\delta\vec J,
-\end{equation}
-где $A$ - матрица, $A_{ij}=\frac{\partial T_i}{\partial J_j}$.
-Мы можем диагонализовать матрицу $A$, ее собственные значения мы обозначим через $\lambda_i$, собственные векторы через $\vec u_i$.
-Тогда для точки в пространстве констант связи мы можем написать (в окрестности  критической точки):
-\begin{equation}
-  \label{eq:60}
-  \vec J=\vec J_c+\sum_i t_i \vec u_i
-\end{equation}
-Переменные $t_i$ под действием ренормгруппы преобразуются так:
-\begin{equation}
-  \label{eq:61}
-  t'_i=\lambda_i t_i=r^{y_i} t_i
-\end{equation}
-Здесь мы ввели обозначение $y_i$ для критических индексов. В примере из раздела \ref{sec:kadanoff-procedure} такими индексами были $a$ и $b$. 
-Для свободной энергии имеем
-\begin{equation}
-  \label{eq:62}
-  f(t_1,t_2,\dots)=r^{-d} f(r^{y_1}t_1,r^{y_2}t_2,\dots)
-\end{equation}
-Таким образом, критические индексы получаются из собственных значений линеаризованной ренормгруппы в фиксированной точки.
-
-Если часть собственных значений $\lambda_i$ положительна, а часть - отрицательная, то фиксированная точка называется гиперболической. 
-Критической поверхностью называются такие точки $\vec J$, что
-\begin{equation}
-  \label{eq:63}
-  \lim_{n\to \infty}T^n (\vec J)=\vec J_c
-\end{equation}
-Около точки $\vec J_c$ она представляет собой векторное пространство, натянутое на те векторы $\vec u_i$, для которых соответствующие собственные значения $\lambda_i<1$.
-
-Параметры $t_i$, которые соответствуют $\lambda_i>1$ называются релевантными, так как они растут под действием ренормгруппы.
-Параметры с $y_i<0 \; (\lambda_i<1)$ --- иррелевантные, с $y_i=0$ --- маргинальные.
-
-Существование критической поверхности объясняет универсальность критических индексов в разных моделях.
-Статистические системы разбиваются на классы универсальности, члены которых имеют одинаковое критическое поведение.
-Это так, если разные системы живут на подмногообразиях в пространстве констант связи, которые пересекают одну и ту же критическую поверхность.
-Тогда критическая точка у них общая.
-
-\subsection{Ренормгруппа в непрерывных моделях}
-\label{sec:renormgroup-general}
-В непрерывных моделях перенормировка осуществляется в импульсном пространстве. Рассмотрим скалярное поле $\varphi(\vec x)$, где $\vec x\in \mathbb{R}^d$. Проведем преобразование Фурье
-\begin{equation}
-  \label{eq:64}
-  \varphi(\vec x)=\int \frac{d^d \vec k}{(2\pi)^d}\tilde \varphi(\vec k) e^{i\vec k\cdot \vec x}
-\end{equation}
-Функционал действия может быть переписан в виде, зависящем только от $\tilde\varphi$: $S[\varphi]\to S[\tilde\varphi]$. Например, для модели $\varphi^4$ \eqref{eq:16} получается
-\begin{multline}
-  \label{eq:65}
-  S[\varphi,r,u]=\int  \frac{d^d \vec k}{(2\pi)^d} \frac{1}{2} \tilde\varphi(-\vec k)\tilde\varphi(\vec k)(\vec k^2+r)+\\
-  \frac{1}{4}u\int  \frac{d^d \vec k_1}{(2\pi)^d} \frac{d^d \vec k_2}{(2\pi)^d} \frac{d^d \vec k_3}{(2\pi)^d} \tilde\varphi(-\vec k_1-\vec k_2 -\vec k_3)\tilde \varphi(\vec k_1)\tilde\varphi (\vec k_2)\tilde\varphi(\vec k_3).
-\end{multline}
-В общем случае функционал действия зависит от поля $\varphi$ и параметров $u_i$ в плотности Лагранжиана (констант связи).
-
-Квантовая теория поля всегда содержит расходящиеся интегралы, поэтому нужна регуляризация.
-Будем считать, что в качестве такой регуляризации используется обрезание по импульсам $\left|\vec k\right|<\Lambda$.
-После преобразования Фурье мера в функциональном интеграле переписывается как
-\begin{equation}
-  \label{eq:66}
-  [d\varphi]_{\Lambda}=\prod_x d\varphi(x)=\prod_{\left|\vec k\right|<\Lambda}d\tilde\varphi(\vec k)
-\end{equation}
-Теперь опишем перенормировку Вильсона-Каданова.
-Она проводится в два этапа.
-Сначала мы интегрируем по $\tilde\varphi(\vec k): \Lambda/s<\left|k\right|<\Lambda$.
-То есть мы исключаем быстрые моды, так как критическое поведение описывается медленными модами.
-$s$-масштабный фактор.
-В результате мы получаем новое обрезание $\Lambda/s$ и действие $S'[\varphi,\{u_i\}]$.
-\begin{equation}
-  \label{eq:67}
-  e^{-S'[\varphi,\{u_i\}]}=\int \prod_{\Lambda/s<\left|\vec k\right|<\Lambda}d\varphi(\vec k)e^{-S[\varphi,\{u_i\}]}
-\end{equation}
-Пока нас интересую только медленные моды, действие $S'$ эквивалентно $S$. Вторым шагом осуществим масштабное преобразование
-\begin{eqnarray}
-  \label{eq:68}
-  \vec k \to \vec k'=s \vec k\\
-  \vec x\to \vec x'=\vec x/s
-\end{eqnarray}
-При этом поле преобразуется так:
-\begin{eqnarray}
-  \label{eq:69}
-  \varphi(\vec x)\to \varphi'(\vec x/s)=s^{\Delta}\varphi (\vec x)\\
-  \tilde\varphi'(s\vec k)=s^{\Delta-d}\tilde\varphi (\vec k)
-\end{eqnarray}
-Здесь $\Delta$- скейлинговая размерность поля $\varphi$, она связана с индексом $\eta$: $\Delta=\eta/2$.
-Мера в функциональном интеграле при масштабном преобразовании умножится на константу.
-Теперь можно сравнить $S'$ и $S$, так как масштаб обрезания и там и там равен $\Lambda$ и те же степени свободы.
-Эти два действия описывают одинаковое поведение на больших расстояниях.
-Поэтому вид действия $S'$ должен быть тот же, что и у $S$, но с другими константами связи $u_i'$.
-\begin{equation}
-  \label{eq:70}
-  S'[\varphi,\{u_i\}]=S[\varphi,\{u_i'\}]
-\end{equation}
-Последовательным действием таких преборазований мы получаем кривую $u_i(s)$ в пространстве параметров лагранжиана.  Мы можем записать уравнение этой кривой как
-\begin{equation}
-  \label{eq:71}
-  \frac{du_i}{d(\ln s)}=\beta_i(\{u_i\})
-\end{equation}
-$\beta_i$ называется $\beta$-функцией параметра $u_i$. 
-Фиксированная точка $u_j^{*}$:
-\begin{equation}
-  \label{eq:72}
-  \beta_i(\{u^{*}_j\})=0
-\end{equation}
-Эта точка неподвижна относительно преобразований ренормгруппы. В фиксированной точке теория масштабно-инвариантна на квантовом уровне.
-
-\section{Лекция 4 }
-\label{sec:lecture-4}
-\subsection{Уравнение Каллана-Симанчика}
-
-Вообще говоря, квантовая теория поля может быть не масштабно-инвариантна из-за наличия размерных параметров на классическом уровне или возникающих при перенормировке. Действие
-\begin{equation}
-  \label{eq:73}
-  S=\int d^dx \mathcal{L}
-\end{equation}
-зависит от полей $\varphi$ и констант связи $\vec u=(u_1,\dots,u_n)$.
-Рассмотрим инфинитезимальное масштабное преобразование $\lambda=1+\omega$.
-При этом вариация $x_{\nu}$ будет $\delta_{\omega}x_{\nu}=\omega x_{\nu}$.
-Такое преобразование, в соответствии с предыдущей лекцией,  можно рассматривать как преобразование констант связи $\vec u\to \vec u'$.
-При наличии масштабной инвариантности $\vec u = \vec u'$.
-При инфинитезимальных преобразованиях $x\to x+dl x$ вариация плотности лагранжиана дается Нётеровским током:
-\begin{equation}
-  \label{eq:74}
-  \delta\mathcal{L}=\partial_{\mu}J^{\mu}dl
-\end{equation}
-\begin{equation}
-  \label{eq:75}
-  J^{\mu}=x_{\nu}T^{\mu\nu}
-\end{equation}
-Здесь $T^{\mu\nu}$ - тензор энергии-импульса.  Через $\Theta$ мы обозначим след тензора энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия
-\begin{equation}
-  \label{eq:87}
-  \delta S=dl \int d^d x \Theta(x)
-\end{equation}
-Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$. В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
-
-В классической теории вид преобразований полей при масштабных преобразованиях легко получаются из анализа размерностей.
-Напомним, что достаточно иметь одну единицу измерения - длины (или обратной длины).
-Если теория масштабно-инвариантна, то действие должно быть безразмерным.
-Канонические (классические) размерности полей легко определить из требования безразмерности слагаемых в функционале действия, если ввести соглашение, определяющее размерность координат или импульсов.
-
-Будем обозначать каноническую размерность произвольно величины $F$ через $d[F]$.
-Положим $d[p]=-d[x]=1$. Тогда $d[d^d x]=-d,\; d[\partial]=1$. Теперь легко найти размерности полей. Например, для модели $\varphi^4$
-\begin{equation}
-  \label{eq:83}
-  S[\varphi]=\int d^d x\left( -\frac{(\partial \varphi)^2}{2}-\frac{\mu \varphi^2}{2}-\frac{u\varphi^4}{24}+h\varphi\right),
-\end{equation}
-рассмотрим первое слагаемое. Оно должно быть безразмерным. При этом его размерность $d[\int d^d x (\partial \varphi)^2]=2d[\varphi]+2-d=0$. Отсюда $d[\varphi]=d/2-1$. Для общего действия
-\begin{equation}
-  \label{eq:84}
-  S[\varphi]=-\int d^d x\left( \frac{(\partial \varphi)^2}{2}+\sum_n u_n \frac{\varphi^n}{n!}\right)
-\end{equation}
-размерности констант связи следующие:
-\begin{equation}
-  \label{eq:85}
-  d[h=-u_1]=d/2+1,\quad d[\mu=u_2]=2,\quad d[g_4]=4-d,\quad d[g_6]=6-2d,\quad d[g_n]=n-\frac{d(n-2)}{2}
-\end{equation}
-При масштабных преобразованиях поля и константы связи ведут себя так:
-\begin{equation}
-  \label{eq:86}
-  \varphi'(x)=s^{-d[\varphi]}\varphi(x/s),\quad u_i'=s^{-d[u_i]}u_i
-\end{equation}
-
-Напомним, что
-\begin{equation}
-  \label{eq:76}
-  \beta_{i}(\vec u)=\frac{du_i}{d\ln s}
-\end{equation}
-Параметр ренормгруппы $s$ связан с параметром масштабного преобразования $l$ соотношением $l=\ln s$, при этом
-\begin{equation}
-  \label{eq:79}
-   \beta_{i}(\vec u)=\frac{du_i}{dl}
-\end{equation}
-Если в точке $u$ $\beta_i(\vec u)>0$, то $u_i(l)$ растет, $\beta_i (\vec u)<0$ - убывает.
-В фиксированной точке $u^*$ $\beta_i(\vec u^*)=0$.
-Пространство действий делится фиксированной точкой на регионы.
-Константы связи ``заперты'' в одном из этих регионов.
-Фиксированная точка может достигаться при $l\to \pm \infty$.
-Если $u(l)\to u^*$ при $l\to +\infty$, то такая точка называется инфракрасной, если $u(l)\to u^*$ при $l\to -\infty$, то ультрафиолетовой.
-Введем функции $\Phi_i$:
-\begin{equation}
-  \label{eq:77}
-  \Phi_i=\frac{\partial \mathcal{L}}{\partial u_i}
-\end{equation}
-Вариация $\delta \mathcal{L}$ дается их линейной комбинацией.
-\begin{equation}
-  \label{eq:78}
-  \Theta(x)=\frac{\partial \mathcal{L}}{\partial l}=\sum_i \frac{\partial \mathcal{L}}{\partial u_i}\frac{d u_i}{dl}=\sum_i\beta_i(\vec u)\Phi_i(\vec u)
-\end{equation}
-$\Theta=0$ тогда и только тогда, когда $\beta_i(\vec u)=0$, значит в фиксированной точке ренормгруппы есть масштабная инвариантность.
-
-Рассмотрим $N$-точечную корреляционную функцию --- среднее значение некоторого $N$-точечного локального оператора
-\begin{equation}
-  \label{eq:81}
-  \langle X\rangle =\langle A_1 (x_1)\dots A_N (x_N)\rangle
-\end{equation}
-
-Мы хотим получить уравнение для его преобразования под действием ренормгруппы. Такое уравнение называется уравнением Каллана-Симанчика.
-
-Вариация корреляционных функций при масштабных преобразованиях может описываться двумя способами.
-
-Во-первых, мы можем вычислить вариацию всех полей:
-\begin{multline}
-  \label{eq:82}
-  \delta \langle X\rangle=\delta \langle A_1(x_1)\dots A_N (x_N)\rangle = \delta \int {\cal D}\varphi A_1 \dots A_N e^{-S[\varphi]} = \\
-  \delta \int {\cal D} \varphi\; \left( \sum_k A_1 \dots \delta A_k \dots A_N e^{-S[\varphi]} -A_1\dots A_N e^{-S[\varphi]}\delta S\right)
-\end{multline}
-Вариация $A_k$ дается глобальной дилатацией координат и внутренней вариацией поля в соответствии с его канонической размерностью:
-\begin{equation}
-  \label{eq:88}
-  \delta A_k=dl (x^{\mu}_k\partial^k_{\mu}+d[A_k]) A_k
-\end{equation}
-Вариация действия определяется следом тензора энергии-импульса (\ref{eq:87}). Поэтому
-\begin{equation}
-  \label{eq:89}
-  \delta\langle X\rangle=dl \left(\sum_k (x_k^{\mu}\partial_{\mu}^k+d[A_k])\langle X\rangle-\int d^d y \Theta(y)\right)
-\end{equation}
-
-Другой способ вычисления состоит в вариации полей и действия по константам связи $u_i$:
-\begin{equation}
-  \label{eq:90}
-  \delta\langle X\rangle=dl\sum_i \beta_i(\vec u)\frac{\partial}{\partial u_i}\langle X\rangle,
-\end{equation}
-но
-\begin{equation}
-  \label{eq:91}
-  \frac{\partial}{\partial u_i}\langle X\rangle=\sum_k \langle A_1\dots \frac{\partial A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Phi_i(y)\rangle.
-\end{equation}
-Отсюда
-\begin{equation}
-  \label{eq:92}
-  \delta\langle X\rangle=dl \sum_i \sum_k\langle A_1\dots \frac{\partial A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Theta(y)\rangle
-\end{equation}
-Сравнивая это уравнение с (\ref{eq:89}) получаем уравнение Каллана-Симанчика:
-\begin{equation}
-  \label{eq:93}
-  \left[ \sum_k\left( x^{\mu}_k \frac{\partial}{\partial x^{\mu}_k}+\Gamma_k(\vec u)\right) -\sum_i \beta_i(\vec u)\frac{\partial }{\partial u_i}\right]\langle X\rangle=0,
-\end{equation}
-где $\Gamma_k$ - аномальная размерность поля $A_k(x_k)$, определяющаяся выражением
-\begin{equation}
-  \label{eq:94}
-  \Gamma_k A_k(x_k)=\left( d[A_k]+\sum_i \beta_i(\vec u) \frac{\partial }{\partial u_i}\right) A_k(x_k).
-\end{equation}
-В частности, для следа тензора энергии-импульса $\Gamma \Theta=2 \Theta$, то есть аномальная размерность равна классической.
-Это верно и для других компонент тензора энергии-импульса в силу Лоренц-инвариантности.
-
-\subsection{Ренормгруппа в двух измерениях}
-\label{sec:renormgroup-in-2d}
-
-Реноргрупповой анализ квантовой теории поля в двух измерениях дает следующий результат, известный как $c$-теорема Замолодчикова \cite{zamolodchikov1986irreversibility}.
-
-\begin{theorem}
-  Для любой унитарной квантовой теории поля в двух измерениях существует функция $c(\vec u)$ такая, что
-  \label{c-theorem}
-  \begin{itemize}
-  \item $c(\vec u)$ убывает, как функция параметра ренормгруппы
-    \begin{equation}
-      \label{eq:95}
-      \frac{dc}{dl}\leq 0
-    \end{equation}
-  \item $c(\vec u)$ стационарна в фиксированной точке $\vec u^*$ ренормгруппы, то есть
-    \begin{equation}
-      \label{eq:96}
-      \frac{dc({\vec u^*})}{dl}=0 \Leftrightarrow \beta_i(\vec u^*)=0
-    \end{equation}
-  \item 2-точечные корреляторы в фиксированной точке полностью определяются значением $c=c(\vec u^*)$.
-    Если ввести комплексные координаты $z=x_1+ix_2,\quad \bar z=x_1-ix_2$ и обозначить компоненты тензора энергии импульса через $T=T_{zz}$, $\bar T=T_{\bar z\bar z}$, $\Theta=T_{z\bar z}=T_{\bar z z}=T_{\mu\mu}=0$, то для корреляторов верно следующее выражение
-    \begin{eqnarray}
-      \label{eq:97}
-      \langle T(z,\bar z)T(0,0)\rangle=\frac{c/2}{z^4}\\
-      \langle \bar T(z,\bar z)\bar T(0,0)\rangle=\frac{c/2}{\bar z^4}\\
-      \langle T(z,\bar z) \bar T(0,0)\rangle=0
-    \end{eqnarray}
-    Число $c=\lim_{\vec u\to \vec u^*} c(\vec u)$ называется центральным зарядом. 
-  \end{itemize}
-\end{theorem}
-Для унитарных теорий из этой теоремы следует, что $c_{UV}\geq c_{IR}$.
-
-В фиксированной точке ренормгруппы имеет место масштабная инвариантность.
-Вместе с трансляционной и лоренц-инвариантностью она порождает конформную инвариантность, то есть инвариантность относительно преобразований, сохраняющих углы.
-
-\section{Лекция 5. Двумерная модель Изинга}
-\label{sec:lecture-5}
-
-Вернемся на некоторое время к модели Изинга в двух измерениях \eqref{eq:1}.
-Точного решения для модели с внешним полем до сих пор не найдено.
-Решение же для $h=0$ впервые было получено Онзагером в 1944 году.
-В этой и следующей лекциях излагается решение Вдовиченко, как наиболее короткое и простое.
-Изложение взято из книги \cite{belavin2001lect}.
-Энергия системы в отсутствие внешнего поля дается выражением
-\begin{equation}
-  \label{eq:98}
-  E[\sigma]=-J\sum_{\left<i,j\right>}\sigma_i \sigma_j .
-\end{equation}
-Введем обозначение
-\begin{equation}
-  \label{eq:99}
-  K=J/T.
-\end{equation}
-Статсумма имеет вид
-\begin{equation}
-  \label{eq:100}
-  Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}\sigma_i\sigma_j}
-\end{equation}
-Будем считать, что в наша решетка $\mathcal{L}$ состоит из $N=mn$ узлов.
-Обозначим через $M$ число пар $\left<i,j\right>$.
-$M=2N-n-m$.
-Для простоты будем накладывать тороидальные граничные условия.
-Тогда $M=2N$.
-Введем {\it дуальную решетку $\mathcal{L}^*$}, вершинами которой будут центры граней исходной решетки.
-Нам удобно будет использовать действие в следующем виде:
-\begin{equation}
-  \label{eq:101}
-  Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1+1)}=e^{KM} \sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
-\end{equation}
-
-\subsection{Низкотемпературное и высокотемпературное разложение}
-\label{sec:low-high-temp}
-
-Обозначим выражения, входящие в сумму в последнем уравнении, через $X[\sigma]$:
-\begin{equation}
-  \label{eq:102}
-  X[\sigma]=e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
-\end{equation}
-Заметим, что все состояния можно упорядочить следующим образом:
-\begin{itemize}
-\item Основное состояние, все спины направлены в одну сторону, $X[\sigma]=1$
-\item Все спины в одну сторону, один в противоположную.
-Такому состоянию можно сопоставить контур на дуальной решетке вокруг этого спина.
-Тогда каждая сторона контура даст вклад $e^{-2K}$ в $X[\sigma]$.
-  \begin{equation}
-    \label{eq:103}
-    X[\sigma]=\left(e^{-2K}\right)^4
-  \end{equation}
-\item Два спина направлены в противоположную сторону, здесь есть два варианта контура на дуально решетке - если спины рядом, то его длина равна шести, если не рядом - то восьми.
-То есть вклады $\left(e^{-2K}\right)^6$ и $\left(e^{-2K}\right)^8$.
-\item И так далее.
-\end{itemize}
-В итоге мы можем записать все вклады $X[\sigma]$ в виде суммы по всевозможным замкнутым контурам на дуальной решетке. Если ввести обозначение
-\begin{equation}
-  \label{eq:104}
-  \kappa=e^{-2K},
-\end{equation}
-то
-\begin{equation}
-  \label{eq:105}
-  X[\sigma]=\kappa^{l[c]}.
-\end{equation}
-Здесь $l[c]$ --- длина контура $c$ на дуальной решетке, соответствующего состоянию $\sigma$. Тогда для $Z$ получаем
-\begin{equation}
-  \label{eq:106}
-  Z=e^{MK}\sum_c \kappa^{l[c]}. 
-\end{equation}
-Такое выражение называется низкотемпературным разложением, так как оно хорошо сходится при малых температурах ($K>>1$).
-
-Чтобы получить высокотемпературное разложение, воспользуемся тем, что $e^{K\sigma_i\sigma_j}=\ch K+\sigma_i\sigma_j\sh K=\ch K \left(1+\sigma_i\sigma_j \th K\right)$.
-Тогда статсумма записывается в виде
-\begin{equation}
-  \label{eq:80}
-  Z=(\ch K)^M\sum_{[\sigma]}\prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)
-\end{equation}
-Будем раскрывать скобки в произведении, сопоставляя каждому множителю $\sigma_i\sigma_j \th K$ ребро на решетке $\mathcal{L}$, соединяющее вершины $i,j$.
-Заметим, что вклад непрерывного пути, соединяющего вершины $i$ и $k$ пропорционален $(\sigma_i \sigma_{i+1}) (\sigma_{i+1}\sigma_{i+2}) (\sigma_{i+2}\sigma_{i+3})\dots (\sigma_{k-1}\sigma_k)=\sigma_{i}\sigma_k$, где мы пронумеровали вершины вдоль пути.
-То есть вклад от незамкнутого пути дается его концами, а вклад от замкнутого контура всегда равен 1.
-Тогда произведение запишется в виде
-\begin{equation}
-  \label{eq:107}
-  \prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)=1+a_1 \th K +a_2 \th^2 K+\dots,
-\end{equation}
-где $a_k$ дается суммой по всем контурам $c$ (не обязательно замкнутым или односвязным) длины $k$.
-Чтобы вычислить статсумму, нам надо просуммировать такие выражения по всем возможным конфигурациям спинов.
-Заметим, что для любого незамкнутого контура и любой конфигурации найдется другая конфигурация, куда вклад этого контура входит с противоположным знаком (так как спины направлены в другую сторону).
-А вклад замкнутого контура равен $\th^{l[c]}K$ в любой конфигурации, то есть входит в статсумму $2^N$ раз.
-В результате получаем высокотемпературное разложение статсуммы в виде суммы по всем замкнутым контурам на решетке $\mathcal{L}$:
-\begin{equation}
-  \label{eq:108}
-  Z=(\ch K)^M 2^N \sum_c (\th K)^{l[c]}=(\ch K)^M 2^N \sum_c \kappa^{l[c]}.
-\end{equation}
-Здесь мы ввели обозначение $\kappa=\th K$. Это разложение хорошо сходится при $K<<1$.
-
-\subsection{Дуальность Крамерса-Ванье}
-\label{sec:duality}
-
-У нас есть два точных разложения для статсуммы. Сравним их в термодинамическом пределе.
-\begin{equation}
-  \label{eq:109}
-  f=-\lim_{N\to \infty}\frac{Z_N}{N}.
-\end{equation}
-Решетки $\mathcal{L}$ и $\mathcal{L}^*$ отличаются только на границе, поэтому в термодинамическом пределе $M/N\to 2$ и выражения для удельной свободной энергии из высокотемпературного и низкотемпературного разложений должны совпадать.
-Если ввести функцию $\Phi(\kappa)=\lim_{N\to \infty}\frac{1}{N} \ln \left(\sum_c \kappa^{l[c]}\right)$, то свободная энергия запишется в высокотемпературном и низкотемпературном разложениях следующим образом:
-\begin{equation}
-  \label{eq:110}
-  -f(K)=2K+\Phi(e^{-2K})=\ln(2\ch^2 K)+\Phi(\th K)
-\end{equation}
-Это и есть соотношение дуальности {\it Крамерса-Ванье}.
-Если ввести $K^*$ так, что $\th K^*=e^{-2K}$ или $\sh 2K^* \sh 2K=1$, то соотношение дуальности будет связывать теорию при температуре $K$ и $K^*$:
-\begin{equation}
-  \label{eq:111}
-  f(K^*)=f(K)+2K-\ln(2\ch^2 K^*).
-\end{equation}
-Рассмотрим теперь поведение теории в критической точке $K_c$.
-В ней свободная энергия $f(K_c)$ не аналитична.
-Тогда $f$ должна быть не аналитична и при $K^*=K_c$.
-Если предположить, что критическая точка единственна, то мы можем найти ее из требования $K=K^*$, то есть $2K=\ln(2\ch^2 K)$ или
-\begin{equation}
-  \label{eq:112}
-  \sh^2 2K_c=1.
-\end{equation}
-Теперь перейдем к точному решению модели Изинга.
-\section{Лекция 6. Решение Вдовиченко.}
-\label{sec:lecture-6}
-Суть состоит в сведении вычисления статсуммы в высокотемпературном разложении к решению некоторого рекуррентного соотношения.
-Это соотношение записывается в матричном виде и его решение дается следом матрицы, который можно вычислить после преобразования Фурье.
-
-Заметим, что суммирование по замкнутым контурам обозначает, что в каждой вершине сходится четное число ребер.
-Поэтому мы можем перейти от суммирования по замкнутым контурам к суммированию по ``траекториям чернильной точки'' --- замкнутым путям, состоящим из компонент, которые можно нарисовать, не отрывая ручку от бумаги.
-При этом в случае контура с самопересечениями существует несколько способов нарисовать его.
-Например, ``восьмерку'' можно представить как два пути, путь без самопересечения и путь с самопересечением (Смотри рисунок \ref{fig:ising-1}).
-\begin{figure}[h!tb]
-  \centering
-    \includegraphics[width=80mm]{ising1}
-  \caption{Переход от контуров к замкнутым путям}
-  \label{fig:ising-1}
-\end{figure}
-Поэтому такие вклады надо брать с множителем $(-1)^{\nu(\Gamma)}$, где $\nu(\Gamma)$ - число самопересечений пути $\Gamma$.
-Статсумма в высокотемпературном разложении \eqref{eq:108} дается выражением
-\begin{equation}
-  \label{eq:113}
-  Z=(\ch K)^M 2^N\sum_c \kappa^{l[c]}.
-\end{equation}
-Обозначим сумму через $\Sigma=\sum_c \kappa^{l[c]}$. Перепишем её через сумму по путям
-\begin{equation}
-  \label{eq:114}
-  \Sigma=\sum_{\Gamma}(-1)^{\nu(\Gamma)} \kappa^{l[\Gamma]}
-\end{equation}
-Воспользуемся следующим утверждением, доказательство которого оставляется в качестве упражнения.
-Для любой связной замкнутой петли на плоскости с $\nu$ самоперечечениями и полным углом поворота $2\pi(n+1)$ (при ее обходе) верно равенство
-\begin{equation}
-  \label{eq:115}
-  (-1)^{\nu}=(-1)^n.
-\end{equation}
-Сопоставим каждому узлу в пути $\Gamma$ с углом поворота $\varphi$ в нем ($0,\pm \pi/2$) множитель $e^{\frac{i\varphi}{2}}$.
-Тогда после обхода петли полный множитель будет равен $(-1)^{\nu+1}$.
-Для несвязного пути, состоящего из $s$ компонент --- $(-1)^{m+s}$, где $m=\sum \nu$.
-То есть если ввести для пути $\Gamma$ общий множитель $s(\Gamma)$, то $\Sigma$ можно переписать в виде
-\begin{equation}
-  \label{eq:116}
-  \Sigma=\sum_{\Gamma}(-1)^{s(\Gamma)}\prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}\kappa^{l[\Gamma]}
-\end{equation}
-Обозначим через $F^{(1)}_l$ сумму по всем однокомпонентным петлям длины $l$, через $F^{(2)}_l$ --- двухкомпонентным и так далее.
-\begin{equation}
-  \label{eq:117}
-  F^{(1)}_l=\sum_{\Gamma:l[\Gamma]=l} \prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}.
-\end{equation}
-Тогда $F_l^{(2)}$ можно вычислить через $F^{(1)}$:
-\begin{equation}
-  \label{eq:118}
-  F^{(2)}_l=\frac{1}{2!}\sum_{l_1,l_2:l_1+l_2=l} F^{(1)}_{l_1} F^{(1)}_{l_2}
-\end{equation}
-Аналогично
-\begin{equation}
-  \label{eq:119}
-  F^{(s)}_l=\frac{1}{s!}\sum_{l_1,\dots l_s:l_1+\dots+l_s=l} F^{(1)}_{l_1}\dots F^{(1)}_{l_s}
-\end{equation}
-Теперь мы можем выразить $\Sigma$ через $F^{(1)}$:
-\begin{equation}
-  \label{eq:120}
-  \Sigma=\sum_{s=0}^{\infty}\frac{1}{s!}\sum_{l_1\dots l_s=1}^{\infty} \kappa^{l_1+\dots+l_s}F^{(1)}_{l_1} \dots F^{(1)}_{l_s}=
-  \sum_{s=0}^{\infty}\frac{1}{s!}\left(\sum_{l=1}^{\infty} \kappa^{l}F^{(1)}_{l} \right)^s =\exp\left(-\sum_{l=1}^{\infty} \kappa^l F_l\right)
-\end{equation}
-Петли с числом узлов больше $N$ не дают вклада, так как содержат повторяющиеся ребра и поэтому сократятся (Смотри рисунок \ref{fig:ising-2}).
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=40mm]{ising2}
-  \caption{Сокращение путей с повторяющимися ребрами}
-  \label{fig:ising-2}
-\end{figure}
-Наша задача свелась к вычислению $F_l$.
-Рассмотрим произвольную вершину с координатами $(n,m)$.
-Пронумеруем направления выхода из нее индексом $\nu=1,2,3,4$ против часовой стрелки.
-Обозначим через $W_l (n,m,\nu|n_0,m_0,\nu_0)$ сумму по всем путям длины $l$, соединяющим вершины $(n_0,m_0)$ и $(n,m)$.
-Первый шаг пути в направлении $\nu_0$.
-Учитываются множители $e^{\frac{i\varphi}{2}}$ начиная с узла, следующего за $(n_0,m_0)$ и заканчивая узлом $(n,m)$.
-Последний шаг пути не должен быть в направлении, противоположном $\nu$.
-Тогда $F_l$ можно записать как сумму $W_l(n,m,\nu|n,m,\nu)$ по всем вершинам решетки.
-Каждая петля при этом будет учтена $2l$ раз, так как у нее $l$ возможных вершин начала и два возможных направления.
-\begin{equation}
-  \label{eq:121}
-  F_l=\frac{1}{2l}\sum_{(n,m)\in \mathcal{L}} \sum_{\nu=1,2,3,4} W_l(n,m,\nu|n,m,\nu)
-\end{equation}
-Если мы зафиксируем начальную вершину путей $(n_0,m_0,\nu_0)$, то сумму по путям длины $l+1$ можно выразить через сумму по путям длины $l$.
-В вершину $(n,m,1)$ пути могут входить с направлений $2,3,4$, то есть последний шаг может быть из вершины $(n-1,m)$ в направлении $1$, из вершины $(n,m-1)$ в направлении $2$ и из вершины $(n,m-1)$ в направлении $4$.
-Аналогично для других направлений. Тогда
-\begin{equation}
-  \label{eq:122}
-\begin{array}{l}
-W_{l+1}(n,m,1)=W_l(n-1,m,1)+e^{-i\pi/4} W_l(n,m-1,2)+e^{i\pi/4}W_l(n,m-1,4)\\
-W_{l+1}(n,m,2)=e^{i\pi/4}W_l(n-1,m,1)+W_l(n,m-1,2)+e^{i\pi/4}W_l(n+1,m,3)\\
-W_{l+1}(n,m,3)=e^{i\pi/4}W_l(n,m-1,2)+W_l(n+1,m,3)+e^{-i\pi/4}W_l(n,m+1,4)\\
-W_{l+1}(n,m,4)=e^{-i\pi/4}W_l(n-1,m,1)+e^{i\pi/4}W_l(n+1,m,3)+W_l(n,m+1,4)\\
-\end{array}
-\end{equation}
-Эти рекуррентные соотношения можно переписать в матричном виде, если ввести матрицу коэффициентов $\Lambda$:
-\begin{equation}
-  \label{eq:124}
-  W_{l+1}(n,m,\nu)=\sum_{p,q,\mu}\Lambda(n,m,\nu|t,u,\mu) W_l(t,u,\mu)
-\end{equation}
-Если вершины $(t,u)$ и $(n,m)$ не являются соседними, то $\Lambda(n,m,\nu|p,q,\mu)=0$.
-Матрица $\Lambda$ не зависит от начала пути.
-$W_{l+1}=\Lambda W_l$, поэтому мы $F_l$ дается следом $l$-той степени $\Lambda$:
-\begin{equation}
-  \label{eq:125}
-  F_l=\frac{1}{2l}\mathrm{Tr} W_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l W_0
-\end{equation}
-Но матрица $W_0=I$ (единичной матрице), поэтому
-\begin{equation}
-  \label{eq:126}
-  F_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l =\frac{1}{2l} \sum_k (\lambda_k)^l,
-\end{equation}
-где $\lambda_k$ - собственные значения матрицы $\Lambda$. Подставим выражение \eqref{eq:126} в формулу \eqref{eq:120}:
-\begin{multline}
-  \label{eq:127}
-  \Sigma=\exp\left(-\sum_{l=0}^{\infty} \frac{\kappa^l}{2l}\mathrm{Tr}\Lambda^l\right)=\exp\left(-\frac{1}{2}\sum_k \sum_{l=0}^{\infty} \frac{(\kappa\lambda_k)^l}{l}\right)=\\
-  \exp\left(\frac{1}{2}\sum_k \ln(1-\kappa\lambda_k)\right)=\prod_k(1-\kappa\lambda_k)^{1/2}=(\det(I-\kappa\Lambda))^{1/2}
-\end{multline}
-Чтобы вычислить детерминант сделаем дискретное преобразование Фурье:
-\begin{equation}
-  \label{eq:128}
-  W_{l}(n,m,\nu)=\sum_{p_1,p_2} \tilde{W}_l(p_1,p_2,\nu) e^{\frac{2\pi i (p_1n+p_2m)}{\sqrt N}}
-\end{equation}
-В импульсном представлении матрица $\Lambda$ будет иметь блочно-диагональный вид
-\begin{equation}
-  \label{eq:129}
-  \Lambda(p_1,p_2,\mu|q_1,q_2,\nu)=\delta_{p,q}\Lambda_p (\mu,\nu),
-\end{equation}
-где
-\begin{equation}
-  \label{eq:130}
-  \Lambda_p(\mu,\nu)=
-  \begin{pmatrix}
-    e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\
-    0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i p_2}{\sqrt N}}
-  \end{pmatrix}
-\end{equation}
-Матрица $I-\kappa\Lambda$ тоже имеет блочный вид с блоками
-\begin{equation}
-  \label{eq:131}
-  \begin{pmatrix}
-    1-\kappa e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\
-    0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1- \kappa e^{-\frac{2\pi i p_2}{\sqrt N}}
-  \end{pmatrix}.
-\end{equation}
-В результате вычисления детерминанта получаем
-\begin{eqnarray}
-  \label{eq:132}
-  \Sigma=\prod_{p_1,p_2} D^{1/2}_{p}\\
-  D_p=(1+\kappa^2)^2 -2\kappa (1-\kappa^2)\left( \cos \frac{2\pi p_1}{\sqrt N} +\cos \frac{2\pi p_2}{\sqrt N}\right)
-\end{eqnarray}
-В результате выражение для статсуммы имеет вид
-\begin{equation}
-  \label{eq:133}
-  Z_N=(2\ch^2 K)^N \prod_{p_1,p_2}D_p^{1/2}.
-\end{equation}
-Исследуем критическое поведение. Вычислим для этого удельную свободную энергию:
-\begin{equation}
-  \label{eq:134}
-  f=-T \lim_{N\to \infty}\frac{Z_N}{N}=-T \lim_{N\to \infty} \left(\ln (2\ch^2 K)+\frac{1}{2N}\sum_p \ln D_p\right)
-\end{equation}
-В термодинамическом пределе $N\to \infty$ значения импульса покрывают всю ось, поэтому сумма переходит в интеграл. Мы сделаем замену переменных
-\begin{eqnarray}
-  \label{eq:135}
-  w_1=\frac{2\pi p_1}{\sqrt N}\quad  w_2=\frac{2\pi p_2}{\sqrt N},\quad w_{1,2}\in [0;2\pi]\\
-  dp_1 dp_2=\frac{N}{(2\pi)^2} dw_1 dw_2
-\end{eqnarray}
-Вспомним, что $\kappa=\th K$, поэтому
-\begin{equation}
-  \label{eq:136}
-  -\ln(2\ch^2 K)=\ln\left(\frac{1-\kappa^2}{2}\right)
-\end{equation}
-Нам будет удобно переписать $D_p$  в виде
-\begin{equation}
-  \label{eq:137}
-  D_p=(\kappa^2+2\kappa -1)^2 +4\kappa (1-\kappa^2) \left(\sin^2 \frac{w_1}{2} +\sin^2 \frac{w_2}{2}\right)
-\end{equation}
-Тогда свободная энергия дается интегралом
-\begin{multline}
-  \label{eq:138}
-  f=T\ln\left(\frac{1-\kappa^2}{2}\right)-\\
-  -\frac{T}{8\pi^2}\int_0^{2\pi}\int_0^{2\pi}\ln\left((\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)\right) dw_1 \;dw_2
-\end{multline}
-В критической точке должна быть расходимость.
-Интеграл может иметь особую точку только при $(\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)=0$.
-Это выражение имеет минимум при $w_1=w_2=0$.
-Тогда при $\kappa^2+2\kappa-1=0$ интеграл расходится, что соответствует критической точке.
-\begin{equation}
-  \label{eq:139}
-  \kappa_c=\sqrt 2 -1
-\end{equation}
-В критической точке основной вклад в интеграл дает окрестность $w_1=w_2=0$, введем
-\begin{equation}
-  \label{eq:140}
-  \epsilon=\kappa-\kappa_c
-\end{equation}
-Тогда около критической точки свободная энергия ведет себя как
-\begin{equation}
-  \label{eq:141}
-  f=g(\epsilon)-\frac{T}{8\pi^2}\int_{0}^{2\pi}\int_0^{2\pi}\ln \left( c\epsilon^2 +A(\epsilon)(w_1^2+w_2^2)\right)dw_1\;dw_2.
-\end{equation}
-Здесь $g(\epsilon), A(\epsilon)$ - регулярные функции. Если взять интеграл, то
-\begin{equation}
-  \label{eq:142}
-  f\approx g_1 (\epsilon)+c\epsilon^2 \ln(e)
-\end{equation}
-Тогда для теплоемкости имеем
-\begin{equation}
-  \label{eq:143}
-  c\propto \ln|T-T_c|
-\end{equation}
-То есть мы подтвердили, что критический индекс $\alpha=0$ (см.
-таблицу \ref{tab:diagrams}).
-Вычисление других критических индексов также возможно, но сопряжено с техническими трудностями.
-Мы не будем его проделывать, так как в следующих лекциях мы легко сможем вычислить корреляторы из конформной теории поля.
-\section{Лекция 7. Конформная группа.}
-\label{sec:lecture-7}
-
-Построение Каданова-Вильсона (см.
-лекцию \ref{sec:kadanoff-procedure}) обосновало нам масштабную инвариантность модели Изинга.
+\subsection*{Конформная алгебра}
+\label{sec:conformal}
+
  Сейчас мы обсудим, какие ограничения накладывает на теорию конформная инвариантность, а затем покажем, что в двух измерениях она следует из масштабной, трансляционной и вращательной инвариантностей.
@@
 где $\eta_{ab}=\mathrm{diag}(-1,1,\dots,1)$. Видно, что мы получили алгебру $so(d+1,1)$. В случае пространства Минковского была бы $so(d,2)$.
-\section{Лекция 8}
-\label{sec:lecture-8}
-
-\subsection{Инварианты}
-\label{sec:invariants}
-
-Обсудим, какой вид могут иметь простейшие инварианты --- $N$-точечные функции $\Gamma(x_1,\dots,x_N)$.
-В силу трансляционной инвариантности они могут зависеть только от модуля разности $|\vec x_i-\vec x_j|$.
-Масштабная инвариантность может сохраняться только отношениями
-\begin{equation}
-  \label{eq:173}
-  \frac{|\vec x_i-\vec x_j|}{|\vec x_k -\vec x_l|}
-\end{equation}
-Но при специальных конформных преобразованиях
-\begin{equation}
-  \label{eq:174}
-  |\vec x'_i-\vec x'_j|=\frac{|\vec x_i-\vec x_j|}{(1-2(\vec h,\vec x_i)+h^2x_i^2)^{1/2} (1-2(\vec h,\vec x_j)+h^2 x_j^2)^{1/2}}
-\end{equation}
-Поэтому не обойтись двумя или тремя точками и простейшие инварианты имеют вид
-\begin{eqnarray}
-  \label{eq:175}
-  \frac{|\vec x_1-\vec x_2||\vec x_3-\vec x_4|}{|\vec x_1-\vec x_3||\vec x_{2}-\vec x_{4}|}\\
-  \frac{|\vec x_1-\vec x_2||\vec x_3-\vec x_4|}{|\vec x_2-\vec x_3||\vec x_{1}-\vec x_{4}|}
-\end{eqnarray}
-Всего $N(N-3)/2$ вариантов для $N$ точек.
-
-\subsection{Явный вид конформных преобразований полей в $d\geq 3$.}
-\label{sec:conformal-transforms-explicit}
-
-Покажем теперь, как преобразуются поля при конформных преобразованиях.
-Для этого используем метод индуцированных представлений, который можно легко объяснить на примере алгебры Пуанкаре.
-Сначала рассматриваем подалгебру, которая оставляет точку $x=0$ неподвижной.
-Это алгебра группы Лоренца или группы вращений в случае евклидова пространства.
-На поля в точке $x=0$ она действует своими матричными представлениями:
-\begin{equation}
-  \label{eq:176}
-  L_{\mu\nu}\Phi(0)=S_{\mu\nu}\Phi(0)
-\end{equation}
-Затем мы пользуемся коммутационными соотношениями алгебры Пуанкаре и формулой Хаусдорфа
-\begin{equation}
-  \label{eq:177}
-  e^{-A}B e^{A}=B+[B,A]+\frac{1}{2!}[[B,A],A]+\frac{1}{3!}[[[B,A],A],A]+\dots
-\end{equation}
-чтобы вычислить результат переноса в точку $x$:
-\begin{multline}
-  \label{eq:178}
-  L_{\mu\nu}\Phi(x)=e^{ix^{\rho}P_{\rho}}L_{\mu\nu}e^{-i x^{\rho}P_{\rho}}\Phi(x)=\\
-  (S_{\mu\nu}-x_{\mu}P_{\nu}+x_{\nu}P_{\mu})\Phi(x)=\\
-  i(x_{\mu}\partial_{\nu}-x_{\nu}\partial_{\mu})\Phi(x)+S_{\mu\nu}\Phi(x)
-\end{multline}
-Для полной конформной группы подгруппа стабильности точки $x=0$ порождается поворотами, растяжениями и специальными конформными преобразованиями.
-Обозначим представление генераторов через $S_{\mu\nu}, \tilde \Delta, k_{\mu}$ соответственно.
-Они порождают матричное представление усеченной алгебры с коммутационными соотношениями
-\begin{eqnarray}
-  \label{eq:179}
-  \left[\tilde\Delta,S_{\mu\nu}\right]=0\\
-  \left[\tilde \Delta,k_{\mu}\right]=-i k_{\mu}\\
-  \left[k_{\mu},k_{\nu}\right]=0\\
-  \left[k_{\rho},S_{\mu\nu}\right]=i(\eta_{\rho\mu}k_{\nu}-\eta_{\rho\nu}k_{\mu})\\
-  \left[S_{\mu\nu},S_{\rho\sigma}\right]=i(\eta_{\nu\rho}S_{\mu\sigma}+\eta_{\mu\sigma}S_{\nu\rho}-\eta_{\mu\rho}S_{\nu\sigma}-\eta_{\nu\sigma}S_{\mu\rho})
-\end{eqnarray}
-Трансляция генераторов дилатации и специальных конформных преобразований дается равенствами
-\begin{eqnarray}
-  \label{eq:180}
-  e^{i x^{\rho}P_{\rho}}D e^{-i x^{\rho}P_{\rho}}=D+x^{\nu}P_{\nu}\\
-  e^{i x^{\rho}P_{\rho}}K_{\mu} e^{-i x^{\rho}P_{\rho}}=K_{\mu}+2x_{\mu}D -2 x^{\nu}L_{\mu\nu}+2x_{\mu}(x^{\nu}P_{\nu})-x^{2 P_{\mu}}
-\end{eqnarray}
-В результате действие этих генераторов на поле имеет вид
-\begin{eqnarray}
-  \label{eq:181}
-  D\Phi(x)=(-ix^{\nu}\partial_{\nu}+\tilde \Delta)\Phi(x)\\
-  K_{\mu}\Phi(x)=(k_{\mu}+2x_{\mu}\tilde\Delta -x^{\nu}S_{\mu\nu}-2ix_{\mu}x^{\nu}\partial_{\nu}+ix^{2} \partial_{\mu})\Phi(x)
-\end{eqnarray}
-Если требовать, чтобы поле $\Phi(x)$ преобразовывалось по неприводимому представлению группы Лоренца, то по лемме Шура любая матрица, коммутирующая со всеми генераторами $S_{\mu\nu}$ пропорциональна единичной.
-\begin{mynote}
-
-  {\it Лемма Шура}.
-Оператор, сплетающий неприводимые конечномерные представления группы Ли либо нулевой, либо обратим.
-Эта лемма доказывается в любом учебнике по теории групп Ли, например \cite{golod2001}.
-
-  {\it Следствие}. Оператор $B$, коммутирующий со всеми операторами конечномерного неприводимого представления, кратен единичному.
-
-  {\it Доказательство}: рассмотрим оператор $B-\lambda I$, он тоже коммутирует со всеми операторами представления.
-Возьмем $\lambda=\lambda_1$, являющееся решением уравнения $\det (B-\lambda I)=0$.
-Тогда оператор $B-\lambda I$ вырожден, и по лемме Шура равен нулю.
-Следовательно $B\propto I$.
-\end{mynote}
-
-То есть $\tilde \Delta\propto I$ и $k_{\mu}=0$.
-Тогда $\tilde \Delta =-i \Delta I$, где $\Delta$ -- скейлинговая размерность поля $\Phi$, $\Phi'(\lambda x)=\lambda^{-\Delta}\Phi(x)$.
-Закон преобразования бесспинового поля $\varphi$ при конечных конформных преобразованиях
-\begin{eqnarray}
-  \label{eq:182}
-  x\to x'\\
-  \varphi(x)\to \varphi'(x')=\left|\frac{\partial x'}{\partial x}\right|^{-\Delta/d}\varphi(x)\\
-  \left|\frac{\partial x'}{\partial x}\right|=\Lambda(x)^{-d/2}    \quad\mbox{--- якобиан преобразования}
-\end{eqnarray}
-Поля, которые так преобразуются, называются {\it квазипримарными}.
-
-Заметим, что  вариация действия при конформных преобразованиях определяется тензором энергии импульса:
-\begin{equation}
-  \label{eq:183}
-  \delta S=\int d^{d}x T^{\mu\nu}\partial_{\mu}\epsilon_{\nu}=\frac{1}{2} \int d^{d}x T^{\mu\nu}(\partial_{\mu}\epsilon_{\nu}-\partial_{\nu}\epsilon_{\mu})=\frac{1}{d}\int d^{d}x T^{\mu}_{\mu}\partial_{\rho}\epsilon^{\rho},
-\end{equation}
-где мы использовали равенства \eqref{eq:147}, \eqref{eq:148}.
-То есть бесследовость тензора энергии-импульса ведет к конформной инвариантности классической теории поля.
-В классической теории поля при наличии трансляционной, вращательной и масштабной инвариантности  тензор энергии-импульса часто можно переопределить так, чтобы он был бесследовым.
-То есть конформная инвариантность следует из трансляционной, вращательной и масштабной.
-В случае двумерной квантовой теории поля общего доказательства нет, но конформная инвариантность наблюдается во множестве моделей.
-
-\section{Лекция 9}
-\label{sec:lecture-9}
-
-\subsection{Корреляторы квазипримарных полей}
-\label{sec:quasiprimary-correlators}
-
-Теперь перейдем к квантовой теории поля. Рассмотрим коррелятор квазипримарных полей.
-\begin{equation}
-  \label{eq:184}
-  \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = \frac{1}{Z} \int \mathcal{D} \Phi \varphi_{1}(x_{1})\varphi_{2}(x_{2}) e^{-S[\Phi]}
-\end{equation}
-Мы знаем, как преобразуется поле при конформных преобразованиях \eqref{eq:182}, поэтому коррелятор должен вести себя так:
-\begin{equation}
-  \label{eq:185}
-  \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\rangle = \left|\frac{\partial x'_{1}}{\partial x_{1}}\right|^{\frac{\Delta_{1}}{d}}\left| \frac{\partial x'_{2}}{\partial x_{2}}\right|^{\frac{\Delta_{1}}{d}} \langle \varphi_{1}(x'_{1})\varphi_{2}(x'_{2})\rangle .
-\end{equation}
-Из требования инвариантности коррелятора при поворотах и трансляциях получаем, что коррелятор может зависеть только от модуля разности $\left|x_{1}-x_{2}\right|$:
-\begin{equation}
-  \label{eq:186}
-  \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = f(\left|x_{1}-x_{2}\right|)
-\end{equation}
-При масштабных преобразованиях $x\to \lambda x$ из \eqref{eq:185} получаем
-\begin{equation}
-  \label{eq:187}
-   \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle=\lambda^{\Delta_{1}+\Delta_{2}}  \langle \varphi_{1}(\lambda x_{1}) \varphi_{2}(\lambda x_{2})\rangle .
-\end{equation}
-То есть мы видим, что $ \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle$ - однородная функция, $f(x)=\lambda^{\Delta_{1}+\Delta_{2}} f(\lambda x)$. Отсюда
-\begin{equation}
-  \label{eq:188}
-   \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}.
-\end{equation}
-Однако мы ещё не воспользовались инвариантностью коррелятора относительно специальных конформных преобразований.
-Подставим явный вид преобразований $\left|x_{1}-x_{2}\right|$ из \eqref{eq:174} и введем обозначение $\gamma_{i}=\left(1-2(h,x_{i})+h^{2}x_{i}^{2}\right)$, тогда
-\begin{equation}
-  \label{eq:189}
-  \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}=\frac{C_{12}(\gamma_{1}\gamma_{2})^{(\Delta_{1}+\Delta_{2})/2}}{\gamma_{1}^{\Delta_{1}}\gamma_{2}^{\Delta_{2}} \left|x_{1}-x_{2}\right|}.
-\end{equation}
-Это равенство может выполняться только при $\Delta_{1}=\Delta_{2}$. В итоге для коррелятора
-\begin{equation}
-  \label{eq:190}
-   \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle =
-   \begin{cases}
-     \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{2\Delta_{1}}} & \Delta_{1}=\Delta_{2}\\
-     0 & \Delta_{1}\neq \Delta_{2}
-   \end{cases}
-\end{equation}
-Вспомним, что для парной корреляционной функции мы вводили критический индекс $\eta$: $\Gamma(\vec n)\sim |\vec n|^{2-d-\eta}$. То есть для коррелятора квазипримарых полей
-\begin{equation}
-  \label{eq:191}
-  \eta=2\Delta +2 -d.
-\end{equation}
-
-Аналогичный анализ можно провести для трехточечных функций. Из требований трансляционной и вращательной инвариантности имеем
-\begin{equation}
-  \label{eq:192}
-  \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}},\quad a+b+c=\Delta_{1}+\Delta_{2}+\Delta_{3}.
-\end{equation}
-Здесь введено обозначение $x_{ij}=|x_{i}-x_{j}|$.
-Из требования инвариантности при специальных конформных преобразованиях получаем
-\begin{equation}
-  \label{eq:193}
-  \frac{C^{abc}_{123}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}}=\frac{C^{abc}_{123}}{\gamma_{1}^{\Delta_{1}}\gamma_{2}^{\Delta_{2}}\gamma_{3}^{\Delta_{3}}}\frac{(\gamma_{1}\gamma_{2})^{a/2}(\gamma_{2}\gamma_{3})^{b/2}(\gamma_{1}\gamma_{3})^{c/2}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}}
-\end{equation}
-Это равенство может выполняться только при
-\begin{equation}
-  \label{eq:194}
-  \begin{array}{l}
-    a+c=2\Delta_{1}\\
-    a+b=2\Delta_{2}\\
-    b+c=2\Delta_{3}
-  \end{array}
-\end{equation}
-Отсюда сразу получаем, сто
-\begin{equation}
-  \label{eq:195}
-  \begin{array}{l}
-    a=\Delta_{1}+\Delta_{2}-\Delta_{3}\\
-    b=\Delta_{2}+\Delta_{3}-\Delta_{1}\\
-    c=\Delta_{3}+\Delta_{1}-\Delta_{2}.
-  \end{array}
-\end{equation}
-В итоге для трехточечных функций имеем:
-\begin{equation}
-  \label{eq:196}
-   \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{\Delta_{1}+\Delta_{2}-\Delta_{3}} x_{23}^{\Delta_{2}+\Delta_{3}-\Delta_{1}}x_{13}^{\Delta_{3}+\Delta_{1}-\Delta_{2}}}.
-\end{equation}
-Из четырех точек уже можно собрать инварианты \eqref{eq:175}, поэтому из требований конформной инвариантности для четырехточечной функции можно написать только
-\begin{equation}
-  \label{eq:197}
-  \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\varphi_{4}(x_{4})\rangle=f\left(\frac{x_{12}x_{34}}{x_{13}x_{24}}; \frac{x_{12}x_{34}}{x_{23}x_{14}}\right) \prod_{i<j}^{4}x_{ij}^{\Delta/3-\Delta_{i}-\Delta_{j}},\quad \Delta=\sum_{i=1}^{4}\Delta_{i}.
-\end{equation}
-
-\subsection{Тождества Уорда}
-\label{sec:ward-identities}
-
-Напомним, о чем идет речь. В произвольной теории поля с полями $\Phi(x)$ инфинитезимальное преобразование может быть записано при помощи генераторов
-\begin{equation}
-  \label{eq:198}
-  \Phi'(x)=\Phi(x)-i\omega_{a} G_{a} \Phi(x)
-\end{equation}
-Вариация действия вычисляется через ток, соответствующий данному преобразовании:
-\begin{equation}
-  \label{eq:199}
-  j^{\mu}_{a}=\left(\frac{\partial \mathcal{L} }{\partial (\partial_{\mu}\Phi)} \partial_{\nu}\Phi -\delta^{\mu}_{\nu}\mathcal{L}\right) \frac{\delta x^{\nu}}{\delta \omega_{a}} - \frac{\partial \mathcal{L} }{\partial (\partial_{\mu} \Phi)}\frac{\delta F}{\delta \omega_{a}}
-\end{equation}
-\begin{equation}
-  \label{eq:200}
-  \delta S =\int d^{d}x \partial_{\mu}j^{\mu}_{a} \omega_{a}
-\end{equation}
-Обозначим через $X$ произведение локальных полей, входящих в коррелятор
-\begin{equation}
-  \label{eq:201}
-  X=\Phi(x_{1})\dots \Phi(x_{n}).
-\end{equation}
-Коррелятор дается функциональным интегралом
-\begin{equation}
-  \label{eq:202}
-  \langle X\rangle = \frac{1}{Z}\int \mathcal{D} \Phi X e^{-S[\Phi]}
-\end{equation}
-Сделаем замену переменных $\Phi\to \Phi'$ в функциональном интеграле. При этом можно предполагать, что ``мера интегрирования'' не меняется $\mathcal{D}\Phi'=\mathcal{D}\Phi$ \cite{difrancesco1997cft}:
-\begin{equation}
-  \label{eq:203}
-  \langle X\rangle = \frac{1}{Z} \int \mathcal{D} \Phi' (X+\delta X)e^{-S[\Phi]-\int d^{d}x \partial_{\mu}j^{\mu}_{a}\omega_{a}(x)}
-\end{equation}
-Раскладываем выражение в ряд до первого порядка по $\omega_{a}(x)$:
-\begin{equation}
-  \label{eq:204}
-  \langle X\rangle=\frac{1}{Z} \left( \int \mathcal{D} \Phi X e^{-S[\Phi]}+\int \mathcal{D} \Phi \delta X e^{-S[\Phi]} -\int \mathcal{D}\Phi \int d^{d}x \partial_{\mu}j^{\mu}_{a}\omega_{a}(x) X e^{-S[\Phi]}\right)
-\end{equation}
-В результате имеем
-\begin{equation}
-  \label{eq:205}
-  \langle \delta X\rangle=\int d^{d}x \partial_{\mu}\langle j^{\mu}_{a}(x) X\rangle \omega_{a}(x)
-\end{equation}
-С другой стороны, мы можем вычислить $\langle\delta X\rangle$ используя \eqref{eq:198}:
-\begin{multline}
-  \label{eq:206}
-  \langle\delta X\rangle=-i\sum_{i=1}^{n}\langle \Phi(x_{1})\dots G_{a} \Phi(x_{i}) \dots \Phi(x_{n})\rangle \omega_{a}(x_{i})=\\
-  -i \int d^{d}x \omega_{a}(x) \sum_{i=1}^{n} \langle \Phi(x_{1}) \dots G_{a} \Phi(x_{i}) \dots \Phi(x_{n})\rangle \delta (x-x_{i})
-\end{multline}
-Окончательно общий вид тождеств Уорда выглядит следующим образом:
-\begin{equation}
-  \label{eq:207}
-  \partial_{\mu}\langle j^{\mu}_{a}\Phi(x_{1}) \dots \Phi(x_{n})\rangle=-i\sum_{i=1}^{n}\delta (x-x_{i}) \langle\Phi(x_{1})\dots G_{a} \Phi(x_{i})\dots \Phi(x_{n})\rangle
-\end{equation}
-Рассмотрим некоторые примеры, которые понадобятся нам для конформной теории. Мы используем полученный нами явный вид генераторов \eqref{eq:169}.
-
-Тождество Уорда для трансляций:
-\begin{equation}
-  \label{eq:208}
-  \partial_{\mu}\langle T^{\mu}_{\nu} X\rangle =-i \sum_{i} \delta(x-x_{i}) \frac{\partial}{\partial x_{i}^{\nu}} \langle X \rangle
-\end{equation}
-Теперь рассмотрим вращения. Если тензор энергии-импульса симметризован (это можно сделать в большинстве случаев), то отвечающий вращениям ток дается выражением
-\begin{equation}
-  \label{eq:209}
-  j^{\mu\nu\rho}=T^{\mu\nu}x^{\rho}-T^{\mu\rho}x^{\nu}.
-\end{equation}
-Тогда тождество Уорда может быть записано в виде
-\begin{equation}
-  \label{eq:210}
-  \partial_{\mu}\langle (T^{\mu\nu}x^{\rho}-T^{\mu\rho}x^{\nu}) X\rangle=\sum_{i }\delta(x-x_{i}) \left( (x^{\nu}_{i}\partial^{\rho}_{i}-x^{\rho}_{i}\partial^{\nu}_{i})\langle X\rangle-i S^{\nu\rho}_{i}\langle X\rangle\right).
-\end{equation}
-Его можно упростить с использованием тождества для трансляций \eqref{eq:208}:
-\begin{equation}
-  \label{eq:211}
-  \langle (T^{\rho\nu}-T^{\nu\rho}) X\rangle=-i \sum_{i} \delta(x-x_{i}) S^{\nu\rho}_{i}\langle X\rangle.
-\end{equation}
-Тензор энергии-импульса в квантовой теории симметричен в корреляционных функциях, если его положение не совпадает с положениями других полей в корреляторе.
-
-Наконец, для масштабных преобразований ток имеет вид $T^{\mu}_{\nu}x^{\nu}$, действие генератора дается выражением \eqref{eq:181} и тождества Уорда выглядят так:
-\begin{equation}
-  \label{eq:212}
-  \partial_{\mu}\langle T^{\mu}_{\nu} x^{\nu} X\rangle=-\sum_{i} \delta(x-x_{i}) \left( x^{\nu}_{i}\frac{\partial}{\partial x^{\nu}_{i}} \langle X\rangle+\Delta_{i} \langle X\rangle\right) 
-\end{equation}
-Его тоже можно упростить:
-\begin{equation}
-  \label{eq:213}
-  \langle T^{\mu}_{\mu} X \rangle = -i \sum_{i} \delta(x-x_{i}) \Delta_{i}\langle X\rangle
-\end{equation}
-
-\subsection{О бесследовости тензора энергии-импульса.}
-\label{sec:tracelessness}
-
-В некоторых теориях из масштабной, вращательной и трансляционной инвариантности автоматически следует конформная инвариантность.
-Как мы знаем, конформная инвариантность соответствует бесследовости тензора энергии-импульса.
-Общего доказательства конформной инвариантности для масштабно-, трансляционно- и вращательно-инвариантных теорий не существует даже для двумерного случая, однако мы можем показать, что вакуумное среднее квадрата следа тензора энергии-импульса в этом случае равно нулю.
-
-Для этого рассмотрим функцию Швингера
-\begin{equation}
-  \label{eq:214}
-  S_{\mu\nu\rho\sigma}=\langle T_{\mu\nu}(x) T_{\rho\sigma}(0)\rangle.
-\end{equation}
-Из симметричности тензора энергии-импульса
-\begin{equation}
-  \label{eq:215}
-  S_{\mu\nu\rho\sigma}=S_{\nu\mu\rho\sigma}=S_{\mu\nu\sigma\rho}=S_{\nu\mu\sigma\rho}
-\end{equation}
-Теперь воспользуемся трансляционной инвариантностью:
-\begin{equation}
-  \label{eq:216}
-  S_{\mu\nu\rho\sigma}=\langle T_{\mu\nu}(0)T_{\rho\sigma}(-x)\rangle =\langle T_{\rho\sigma}(-x) T_{\mu\nu}(0)\rangle = S_{\rho\sigma\mu\nu}(-x).
-\end{equation}
-Если в теории сохраняется четность, то $S_{\mu\nu\rho\sigma}(x)=S_{\rho\sigma\mu\nu}(x)$.
-В силу масштабной инвариантности $T_{\mu\nu}$ имеет скейлинговую размерность 2, так как является плотностью.
-Следовательно функция Швингера при масштабных преобразованиях ведет себя так:
-\begin{equation}
-  \label{eq:217}
-  S_{\mu\nu\rho\sigma}(\lambda x)=\lambda^{-4} S_{\mu\nu\rho\sigma}(x)
-\end{equation}
-Теперь можно записать общий вид функции Швингера:
-\begin{multline}
-  \label{eq:218}
-  S_{\mu\nu\rho\sigma}(x)=(x^{2})^{-4} \left( A_{1}g_{\mu\nu} g_{\rho\sigma} (x^{2})^{2} + A_{2} (g_{\mu\rho}g_{\nu\sigma}\right. +\\
-  \left. g_{\mu\sigma}g_{\nu\rho}) (x^{2})^{2} +A_{3} (g_{\mu\nu} x_{\rho}x_{\sigma} +g_{\rho\sigma}x_{\mu}x_{\nu})x^{2} +A_{4} x_{\mu}x_{\nu}x_{\rho}x_{\sigma}\right)
-\end{multline}
-Кроме того, у нас имеется закон сохранения $\partial^{\mu} T_{\mu\nu}=0$, поэтому
-\begin{multline}
-  \label{eq:219}
-  \partial^{\mu}  S_{\mu\nu\rho\sigma}(x)=-(x^{2})^{-4} \left( 3(A_{4}+2 A_{3}) x_{\nu}x_{\rho}x_{\sigma}\right. +\\
-  \left. (4 A_{1}+3 A_{3}) g_{\rho\sigma} x_{\nu} x^{2} +(4 A_{2} - A_{3}) (g_{\rho\nu}x_{\sigma}+g_{\nu\sigma}x_{\rho}) x^{2}\right)=0
-\end{multline}
-Это равенство может выполняться для любого $x$ только если все коэффициенты в скобках равны нулю. То есть
-\begin{eqnarray}
-  \label{eq:220}
-  A_{1}=3 A\\
-  A_{2}=-A\\
-  A_{3}=-4 A\\
-  A_{4}=8 A
-\end{eqnarray}
-Окончательно получаем для функции Швингера
-\begin{multline}
-  \label{eq:221}
-  S_{\mu\nu\rho\sigma}(x)=\frac{A}{(x^{2})^{4}} \left( (3g_{\mu\nu} g_{\rho\sigma}-g_{\mu\rho}g_{\nu\sigma}-g_{\mu\sigma}g_{\nu\rho}) (x^{2})^{2} 
-  \right. \\
-  \left.-4 x^{2} (g_{\mu\nu} x_{\rho}x_{\sigma} +g_{\rho\sigma}x_{\mu}x_{\nu}) +8 x_{\mu}x_{\nu}x_{\rho}x_{\sigma}\right)
-\end{multline}
-Теперь прямой подстановкой можно проверить, что
-\begin{equation}
-  \label{eq:222}
-  S^{\mu\sigma}_{\mu\sigma}=\langle T^{\mu}_{\mu}(x) T^{\sigma}_{\sigma}(0)\rangle=0
-\end{equation}
-при любых значениях $x$. В частности $\langle T^{\mu}_{\mu}(0)\rangle=0$, то есть у оператора следа тензора энергии-импульса нулевое матожидание и среднеквадратичное отклонение в основном состоянии.
-
-\section{Лекция 10. Конформная инвариантность в двумерной теории.}
-\label{sec:lecture-10}
-
-В лекции \ref{sec:lecture-7} мы получили общее условие на вид инфинитезимальных конформных преобразований:
+
+Мы получили общее условие на вид инфинитезимальных конформных преобразований:
 \begin{equation}
@@
 Так как $l_{0}+\bar l_{0}$ -- генератор дилатации, то скейлинговая размерность $\Delta=h+\bar h$, а поскольку $i(l_{0}-\bar l_{0})$ порождает вращения, то спин $s=h-\bar h$.
-
-Квазипримарное поле $\varphi(z,\bar z)$ \eqref{eq:182} со спином $s$ при преобразованиях $z\to w(z), \bar z\to \bar w(\bar z)$ преобразуется так:
-\begin{equation}
-  \label{eq:234}
-  \varphi'(w,\bar w)=\left( \frac{d w}{d z}\right)^{-h}\left( \frac{d \bar w}{d \bar z}\right)^{-\bar h} \varphi(z,\bar z)
-\end{equation}
-Вариация квазипримарного поля при инфинитезимальных преобразованиях $w=z+\epsilon, \bar w =\bar z +\bar \epsilon$ имеет вид
-\begin{equation}
-  \label{eq:235}
-  \delta_{\epsilon,\bar \epsilon} \varphi=\varphi'(z,\bar z)-\varphi(z,\bar z)=-(h\varphi \partial \epsilon +\epsilon \partial \varphi) - (\bar h \varphi\bar \partial \bar \epsilon+\bar \epsilon \bar \partial \varphi)
-\end{equation}
-Если поле ведет себя так не только при глобальных, но и при локальных преобразованиях, то оно называется {\it примарным}.
-
-\subsection{Тождества Уорда в двумерной конформной теории}
-\label{sec:ward-2d-cft}
-В прошлой лекции мы получили общий вид тождеств Уорда для трансляций, поворотов и масштабных преобразований. Выпишем их здесь.
-\begin{eqnarray}
-  \label{eq:236}
-  \partial_{\mu}\langle T^{\mu}_{\nu} X\rangle = -\sum_{i} \delta(x-x_{i}) \partial_{\nu}^{(i)}\langle X\rangle\\
-  \langle (T^{\mu\nu}-T^{\nu\mu}) X\rangle =i\sum_{i}\delta(x-x_{i}) S^{\mu\nu}_{(i)}\langle X\rangle\\
-  \langle T^{\mu}_{\mu} X\rangle=-\sum_{i}\delta(x-x_{i}) \Delta_{(i)} \langle X\rangle
-\end{eqnarray}
-Прежде чем мы начнем переписывать тождества в комплексных координатах обсудим следующий вспомогательный математический факт: для голоморфных (антиголоморфных) функций можно использовать следующее представление для $\delta$-функции:
-\begin{equation}
-  \label{eq:237}
-  \delta(x)=\frac{1}{\pi} \bar \partial \frac{1}{z} = \frac{1}{\pi}\partial \frac{1}{\bar z}
-\end{equation}
-Заметим, что
-\begin{equation}
-  \label{eq:238}
-  \int_{M} d^{2}x \partial_{\mu}F^{\mu}=\int_{\partial M} d\xi_{\mu} F^{\mu}=\frac{1}{2i} \oint_{\partial M} (-dz F^{\bar z}+d\bar z F^{z})
-\end{equation}
-Для голоморфной функции
-\begin{equation}
-  \label{eq:239}
-  \frac{1}{\pi}\int_{M} d^{2}x \bar \partial\left( \frac{f(z)}{z}\right)=\frac{1}{2\pi i} \int_{\partial M} dz \frac{f(z)}{z}=f(0)=\int_{M} d^{2}x \delta(x) f(z)
-\end{equation}
-Теперь перепишем тождества Уорда \eqref{eq:236} в комплексных координатах:
-\begin{eqnarray}
-  \label{eq:240}
-  2\pi \partial \langle T_{\bar z z } X\rangle +2\pi \bar \partial \langle T_{zz}X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X \rangle\\
-  2\pi \partial \langle T_{\bar z \bar z } X\rangle +2\pi \bar \partial \langle T_{z\bar z}X\rangle = -\sum_{i} \bar \partial \frac{1}{\bar z-w_{i}} \partial_{\bar w_{i}} \langle X \rangle\\
-  2 \langle T_{z\bar z} X 1\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) \Delta_{i} \langle X\rangle\\
-  -2 \langle T_{z\bar z} X 1\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) s_{i} \langle X\rangle\\
-\end{eqnarray}
-Если сложить и вычесть два последних равенства и вспомнить определение $h, \bar h$, то получим
-\begin{eqnarray}
-  \label{eq:241}
-  2\pi \langle T_{\bar z z} X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}} h_{i} \langle X\rangle\\
-  2\pi \langle T_{z \bar z} X\rangle = -\sum_{i}  \partial \frac{1}{\bar z-\bar w_{i}} \bar h_{i} \langle X\rangle
-\end{eqnarray}
-Введем обозачения
-\begin{eqnarray}
-  \label{eq:242}
-  T=-2\pi T_{zz}\\
-  \bar T = -2 \pi T_{\bar z \bar z},
-\end{eqnarray}
-и подставим уравнения \eqref{eq:241} в первые два уравнения \eqref{eq:240}:
-\begin{eqnarray}
-  \label{eq:243}
-  \bar \partial \left( \langle T X\rangle -\sum_{i} \left( \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X\rangle + \frac{h_{i}}{(z-w_{i})^{2}} \langle X\rangle \right) \right) =0\\
-  \partial \left( \langle \bar T X\rangle -\sum_{i} \left( \frac{1}{\bar z-\bar w_{i}} \partial_{\bar w_{i}} \langle X\rangle + \frac{\bar h_{i}}{(\bar z-\bar w_{i})^{2}} \langle X\rangle \right) \right) =0
-\end{eqnarray}
-То есть выражения в скобках (анти)голоморфны. Следовательно
-\begin{equation}
-  \label{eq:244}
-  \langle T X\rangle =\sum_{i} \left( \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X\rangle + \frac{h_{i}}{(z-w_{i})^{2}} \langle X\rangle \right) +\mbox{регулярные члены}
-\end{equation}
-Это пример операторного разложения, которое мы будем обсуждать далее.
-
-Заметим, что вариация коррелятора при конформных преобразованиях дается тензором энергии-импульса:
-\begin{equation}
-  \label{eq:245}
-  \delta_{\epsilon}\langle X\rangle =\int_{M} d^{2}x \partial_{\mu} \langle T^{\mu\nu}(x)\epsilon_{\nu}(x) X \rangle
-\end{equation}
-В комплексных координатах она перепишется так:
-\begin{equation}
-  \label{eq:246}
-  \delta_{\epsilon,\bar \epsilon} \langle X\rangle = \frac{1}{2\pi i} \oint_{C} dz \epsilon(z) \langle T(z) X\rangle +\frac{1}{2\pi i} \oint_{C}  d\bar z \bar \epsilon(\bar z) \langle \bar T(\bar z) X\rangle
-\end{equation}
-Здесь интеграл берется по контуру, внутри которого находятся все аргументы $X$.
-Вообще говоря, это выражение для вариации верно для коррелятора любых полей, не только примарных.
-
-Применимость тождеств Уорда основывается на регулярности тензора энергии-импульса.
-Он должен быть везде хорошо определен.
-В частности, $T(0)$ должен быть конечен.
-Кроме того, если вычислить вариацию постоянного поля в точке $z=\infty$:
-\begin{equation}
-  \label{eq:247}
-  \delta_{\epsilon} \langle 1\rangle =-\frac{1}{2\pi i} \oint_{C}dz \epsilon(z) \langle T(z)\rangle =0
-\end{equation}
-где контур обходит точку $\infty$. Для специальных конформных преобразований $\epsilon(z)\sim z^{2}$, поэтому $T(z)\sim z^{-4},\quad z\to \infty$.
-
-\section{Лекция 11}
-\label{sec:lecture-11}
-
-\subsection{Алгебра локальных полей. Операторное разложение}
-\label{sec:ope}
-
-В набор локальных полей теории входят не только те поля, которые входят в плотность лагранжиана, но и их производные, произведения и так далее.
-Мы предполагаем, что набор локальных полей $A$ является полным, то есть существует некий базис $\{ A_{j}\}$, по которому можно разложить любое поле. Локальные поля образуют линейное пространство.
-
-Кроме того, мы предполагаем, что имеет место операторное разложение
-\begin{equation}
-  \label{eq:248}
-  A_{i}(x)A_{j}(y) =\sum_{k} C^{k}_{ij} (x,y) A_{k}(y),
-\end{equation}
-здесь $C_{ij}^{k}(x,y)$ -- функция. Равенство \eqref{eq:248} надо понимать в смысле корреляционных функций
-\begin{equation}
-  \label{eq:249}
-  \langle A_{i}(x) A_{j}(y) X\rangle = \sum_{k} C^{k}_{ij} (x,y) \langle A_{k}(y) X\rangle.
-\end{equation}
-Тогда набор локальных полей образует алгебру.
-
-Рассмотрим четырехточечную функцию и воспользуемся операторным разложением \eqref{eq:248}:
-\begin{equation}
-  \label{eq:250}
-  \langle A_{1}(x_{1}) A_{2}(x_{2}) A_{3}(x_{3}) A_{4}(x_{4}) \rangle =\sum_{k,l} C^{k}_{12} (x_{1}-x_{2}) D_{kl}(x_{2}-x_{4}) C^{l}_{34}(x_{3}-x_{4}) 
-\end{equation}
-Здесь мы воспользовались трансляционной инвариантностью, а также ввели обозначение для пропагатора
-\begin{equation}
-  \label{eq:251}
-  \langle A_{i}(x_{i}) A_{j}(x_{j}) \rangle =D_{ij}(x_{i}-x_{j}).
-\end{equation}
-Однако операторным разложением можно воспользоваться и в другом порядке, тогда для четырехточечной функции получим:
-\begin{equation}
-  \label{eq:252}
-  \langle A_{1}(x_{1}) A_{2}(x_{2}) A_{3}(x_{3}) A_{4}(x_{4}) \rangle =\sum_{k,l} C^{k}_{13} (x_{1}-x_{3}) D_{kl}(x_{3}-x_{4}) C^{l}_{24}(x_{2}-x_{4})   
-\end{equation}
-Приравняв правые части уравнений \eqref{eq:252},\eqref{eq:250} можно получить систему уравнений на коэффициенты $C^{k}_{ij}$.
-Если решить эти уравнения, то в принципе можно вычислять любые корреляторы, если известен набор полей и их конформных размерностей.
-Такой подход называется конформным бутстрапом.
-
-Корреляционные функции имеют особенности при совпадении положений полей. Именно характер этих особенностей важен при описании критического поведения (критические индексы и т.п.).
-Для произведения $T$ и примарного поля $\varphi$ с конформными размерностями $h,\bar h$ имеет место операторное разложение \eqref{eq:244}:
-\begin{eqnarray}
-  \label{eq:253}
-  T(z) \varphi(w,\bar w)\sim \frac{h}{(z-w)^{2}} \varphi(w,\bar w)+\frac{1}{z-w} \partial_{w} \varphi(w,\bar w)\\
-  \bar T(\bar z) \varphi(w,\bar w)\sim \frac{\bar h}{(\bar z-\bar w)^{2}} \varphi(w,\bar w)+\frac{1}{\bar z-\bar w} \partial_{\bar w} \varphi(w,\bar w)  
-\end{eqnarray}
-
-\subsection{Свободный бозон}
-\label{sec:free-boson}
-
-В качестве примера конформной теории рассмотрим свободное бозонное поле $\varphi$. Действие имеет вид
-\begin{equation}
-  \label{eq:254}
-  S=\frac{1}{2} g \int d^{2}x \partial_{\mu}\varphi \partial^{\mu}\varphi,
-\end{equation}
-а пропагатор дается равенством
-\begin{equation}
-  \label{eq:255}
-  \langle\varphi(x) \varphi(y)\rangle =-\frac{1}{4\pi g} \ln (x-y)^{2}+\text{const}
-\end{equation}
-В комплексных координатах пропагатор запишется следующим образом:
-\begin{equation}
-  \label{eq:256}
-  \langle \varphi(z,\bar z) \varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \left( \ln(z-w) + \ln(\bar z -\bar w)\right) +\text{const}
-\end{equation}
-Дифференцируя получаем
-\begin{eqnarray}
-  \label{eq:257}
-  \langle\partial_{z} \varphi(z,\bar z) \partial_{w}\varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \frac{1}{(z-w)^{2}}\\
-  \langle\partial_{\bar z} \varphi(z,\bar z) \partial_{\bar w}\varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \frac{1}{(\bar z-\bar w)^{2}}  
-\end{eqnarray}
-То есть имеет место операторное разложение полей $\partial \varphi$:
-\begin{equation}
-  \label{eq:259}
-  \partial \varphi(z) \partial \varphi(w) \sim -\frac{1}{4 \pi g} \frac{1}{(z-w)^{2}}
-\end{equation}
-
-Тензор энергии-импульса:
-\begin{equation}
-  \label{eq:258}
-  T_{\mu\nu}=g \left(\partial_{\mu}\varphi \partial_{\nu} \varphi -\frac{1}{2} \eta_{\mu\nu}\partial_{\rho}\varphi \partial^{\rho} \varphi \right)
-\end{equation}
-После квантования получаем для оператора $T(z)$ следующее выражение:
-\begin{equation}
-  \label{eq:260}
-  T(z) =-2\pi g :\partial \varphi \partial \varphi : =-2\pi g \lim_{w\to z} \left(\partial \varphi(z) \partial \varphi(w) -\langle\partial \varphi(z) \partial \varphi(w)\rangle\right)
-\end{equation}
-Теперь мы можем вычислить операторное разложение тензора энергии-импульса и локального поля $\partial \varphi$:
-\begin{equation}
-  \label{eq:261}
-  T(z)\partial \varphi(w)=-2\pi g :\partial \varphi(z) \partial \varphi(z): \partial \varphi(w) \sim -4\pi g:\partial \varphi(z)  \partial \overbracket{ \varphi(z): \partial \varphi } (w) \sim \frac{\partial \varphi (z)}{(z-w)^{2}}
-\end{equation}
-Для вычисления мы использовали теорему Вика (см. \cite{vasiliev1998}, \cite{difrancesco1997cft}). Раскладывая в ряд по $(z-w)$ получаем окончательно для сингулярной части операторного разложения
-\begin{equation}
-  \label{eq:262}
-  T(z) \partial \varphi(w) \sim \frac{\partial \varphi(w) }{(z-w)^{2}} +\frac{\partial_{w}^{2} \varphi(w)}{z-w}
-\end{equation}
-Теперь мы видим, что поле $\partial \varphi$ -- примарное, с конформной размерностью $h=1$.
-
-Аналогично вычислим операторное разложение $T$  с самим собой.
-\begin{multline}
-  \label{eq:263}
-  T(z) T(w) =4 \pi^{2}g^{2}:\partial \varphi(z) \partial \varphi(z): :\partial \varphi(w)\partial \varphi(w): \\
-  \sim \frac{1/2}{(z-w)^{4}} -\frac{4\pi g:\partial \varphi(z) \partial \varphi(w):}{(z-w)^{2}} \\
-  \sim \frac{1/2}{(z-w)^{4}}+ \frac{2T(w)}{(z-w)^{2}} +\frac{\partial T(w)}{z-w}
-\end{multline}
-
-\subsection{Центральный заряд. Алгебра Вирасоро}
-\label{sec:virasoro}
-
-В силу обсуждения после формулы \eqref{eq:247}, ренормгруппового анализа \ref{c-theorem} и вычисления функции Швингера  \eqref{eq:221} мы имеем следующий общий вид операторного разложения для $T(z)T(w)$:
-\begin{equation}
-  \label{eq:264}
-  T(z)T(w) \sim \frac{c/2}{(z-w)^{4}}+ \frac{2T(w)}{(z-w)^{2}} +\frac{\partial T(w)}{z-w}
-\end{equation}
-Здесь $c$ -- параметр теории, называемый центральным зарядом.
-Он зависит от физической природы теории и не определяется из соображений конформной инвариантности.
-В теории свободного бозона $c=1$, для фермиона $c=1/2$.
-Член $\frac{c/2}{(z-w)^{4}}$ называется аномальным.
-Если этого члена нет, то $T$--квазипримарное поле c $h=2$.
-
-Сравнивая выражение \eqref{eq:264} и \eqref{eq:221} мы видим, что константа $A$ в функции Швингера
-\begin{equation}
-  \label{eq:265}
-  A=\frac{c}{4\pi^{2}}
-\end{equation}
-Покажем, как преобразуется тензор энергии-импульса при конформных преобразованиях. Используем формулу \eqref{eq:246}:
-\begin{multline}
-  \label{eq:266}
-  \delta_{\epsilon} T(w) =-\frac{1}{2\pi i} \oint_{C} dz \epsilon(z) T(z) T(w) =-\frac{1}{12} c \partial_{w}^{3}\epsilon(w) -2 T(w) \partial_{w} \epsilon(w) -\epsilon(w) \partial_{w}T(w) 
-\end{multline}
-Соответствующее конечное преобразование $z\to w(z)$ имеет вид
-\begin{eqnarray}
-  \label{eq:267}
-  T\to T'(w) =\left(\frac{dw}{dz}\right)^{-2} \left(T(z) -\frac{c}{12} \left\{ w,z\right\}\right)\\
-  \left\{ w,z\right\}=\frac{\left(\frac{d^{3}w}{dz^{3}}\right) } {\frac{dw}{dz}} -\frac{3}{2}\left(\frac{\frac{d^{2}w}{dz^{2}}}{\frac{dw}{dz}}\right)^{2}
-\end{eqnarray}
-В качестве упражнения предлагаем проверить это выражение обратным переходом к инфинитезимальному преобразованию.
-
-Разложим $T(z)$ в ряд Лорана.
-\begin{eqnarray}
-  \label{eq:268}
-  T(z)=\sum_{n\in \mathbb{z}}z^{-n-2}L_{n}\\
-  T(z)=\sum_{n\in \mathbb{z}}\bar z^{-n-2}\bar L_{n}
-\end{eqnarray}
-При масштабном преобразовании $z\to z/\lambda$ оператор $T(z)\to \lambda^{2}T(z/\lambda)$, соответственно компоненты $L_{-n}\to \lambda^{n}L_{-n}$.
-\begin{equation}
-  \label{eq:269}
-  L_{n}=\oint \frac{dz}{2\pi i} z^{n+1} T(z)
-\end{equation}
-Выведем коммутационные соотношения для операторов $L_{n}$:
-\begin{equation}
-  \label{eq:270}
-  [L_{n},L_{m}]=\left( \oint \frac{dz}{2\pi i}\oint \frac{dw}{2\pi i}-\oint \frac{dw}{2\pi i}\oint \frac{dz}{2\pi i}\right) z^{n+1} T(z)w^{m+1}T(w)
-\end{equation}
-Используем операторное разложение \eqref{eq:264}:
-\begin{multline}
-  \label{eq:271}
-  [L_{n},L_{m}]=\oint \frac{dz}{2\pi i} \oint \frac{dw}{2\pi i} z^{n+1} w^{m+1}\left( \frac{c/2}{(z-w)^{4}} +\frac{2T(w)}{(z-w)^{2}}+\frac{\partial T(w) }{z-w} +\mbox{рег. члены}\right) =\\
-  \oint \frac{dw}{2\pi i} \left(\frac{c}{12} (n+1)n(n-1)w^{n-2}w^{m+1} + 2(n+1)w^{n}w^{m+1}T(w)+w^{n+1}w^{m+1}\partial T(w)\right)
-\end{multline}
-Интегрируем последний член по частям, внеинтегральный член зануляется, а под интегралом остается $(n-m)w^{n+m+1}T(w)$:
-\begin{equation}
-  \label{eq:272}
-    [L_{n},L_{m}]=\oint \frac{dw}{2\pi i} \left(\frac{c}{12} (n+1)n(n-1)w^{m+n-1}+ (n-m)w^{n+m+1}T(w)\right)
-\end{equation}
-Используя определение \eqref{eq:269} и вычисляя вычет подинтегрального выражения при $n=-m$, в итоге получаем коммутационное соотношение
-\begin{equation}
-  \label{eq:273}
-    [L_{n},L_{m}]=(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}
-\end{equation}
-Это коммутационные соотношения алгебры Вирасоро.
-
-Легко показать, что в результате действия оператора $L_{-n}$ на поле $\varphi$  с конформной размерностью $(h,\bar h)$ получается поле с размерностью $(h-n,\bar h)$.
-Все поля в теории разбиваются на конформные семейства, соответствующие примарным полям:
-\begin{equation}
-  \label{eq:274}
-  [\varphi]=\{L_{-n_{1}}L_{-n_{2}}\dots L_{-n_{N}}\bar L_{-m_{1}}\dots \bar L_{-m_{M}}\varphi\}
-\end{equation}
-Вычисление корреляторов вторичных полей сводится к корреляторам примарных. Алгебра локальных полей оказывается прямой суммой конформных семейств
-\begin{equation}
-  \label{eq:275}
-  \mathcal{A} =\bigoplus_{\alpha}[\varphi_{\alpha}]
-\end{equation}
-{\it Минимальными} называются теории с конечным числом примарных полей. Чтобы полностью задать такую теорию нужно определить примарные поля и их конформные размерности.
-
-\section{Лекция 12}
-\label{sec:lecture-12}
-
-\subsection{Конформный предел модели Изинга}
-\label{sec:ising-conformal-limit}
-
-Рассмотрим теорию с центральным зарядом $c=\frac{1}{2}$, $\bar c=c$ и примарными полями с конформными размерностями
-\begin{equation}
-  \label{eq:276}
-  \Phi_{1}: (0,0),\quad \Phi_{2}: \left(\frac{1}{2},\frac{1}{2}\right),\quad \Phi_{3}\left(\frac{1}{16},\frac{1}{16}\right)
-\end{equation}
-Первое из этих полей соответствует единичному оператору.
-
-В модели Изинга $\sigma$ -- параметр порядка. $\langle\sigma\rangle=0$ при большой температуре и $\langle \sigma\rangle\neq 0$ при малой. Как мы знаем,
-\begin{equation}
-  \label{eq:277}
-  \langle \sigma_{n} \sigma_{0}\rangle\sim e^{-\frac{|n|}{\xi}}
-\end{equation}
-Где $\xi$ --- корреляционная длина. $\xi^{-1}$ можно рассматривать как массу в теопии. В критической точке $\xi$ расходится и теория становится безмассовой.
-\begin{equation}
-  \label{eq:278}
-  \langle\sigma_{n}\sigma_{0}\rangle\sim\frac{1}{|n|^{d-2+\eta}}
-\end{equation}
-Для оператора энергии верно
-\begin{equation}
-  \label{eq:279}
-  \langle \varepsilon_{n} \varepsilon_{0}\rangle \sim \langle\sigma_{n}\sigma_{n+1}\sigma_{0}\sigma_{1}\rangle\sim\frac{1}{|n|^{\frac{2d-2}{\nu}}}
-\end{equation}
-Это выражение не совсем точное, так как при вычислении $\varepsilon_{n}$ надо брать среднее по всем соседям, но сейчас нам это не очень важно.
-В любом случае коррелятор оператора энергии соответствует цетырехточечной функции.
-
-Мы знаем (см. Лекции \ref{sec:lecture-2}, \ref{sec:lecture-5}, \ref{sec:lecture-6}) значения критических индексов в модели Изинга --- $\eta=\frac{1}{4}, \nu=1$. Тогда для двухточечной функции
-\begin{equation}
-  \label{eq:280}
-  \langle \sigma_{n} \sigma_{0} \rangle\sim \frac{1}{|n|^{\frac{1}{4}}} \sim\frac{1}{r^{2\Delta_{\sigma}}},
-\end{equation}
-так как мы помним, что двухточечная функция ведет себя как $\langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle=\frac{C_{12}}{r_{12}^{\Delta_{1}+\Delta_{2}}}$.
-Отсюда $\Delta_{\sigma}=h_{\sigma}+\bar h_{\sigma}=\frac{1}{8}$, $s_{\sigma}=h_{\sigma}-\bar h_{\sigma}=0$, то есть поле $\Phi_{3}$ соответствует спину в модели Изинга.
-
-Для оператора энергии мы видим, что
-\begin{equation}
-  \label{eq:281}
-  \langle\varepsilon_{n}\varepsilon_{0}\rangle\sim \frac{1}{|n|^{2\Delta_{\varepsilon}}},
-\end{equation}
-$\nu=1$, $d-1/\nu=1=\Delta_{\varepsilon}=h_{\varepsilon}+\bar h_{\varepsilon}$, то есть $h_{\varepsilon}=\frac{1}{2}$ и поле $\Phi_{2}$ соответствует оператору энергии в модели Изинга.
-
-\subsection{Свободный фермион}
-\label{sec:free-fermion}
-
-Заметим, что другая простая физическая система с центральным зарядом $(c,\bar c)=\left(\frac{1}{2},\frac{1}{2}\right)$ --- это свободный фермион. Его действие
-\begin{equation}
-  \label{eq:282}
-  S=\frac{1}{2} g \int d^{2}x\Psi^{+}\gamma^{0}\gamma^{\mu}\partial_{\mu}\Psi,
-\end{equation}
-где
-\begin{equation}
-  \label{eq:283}
-  \Psi=
-  \begin{pmatrix}
-    \psi\\ \bar \psi
-  \end{pmatrix}
-\end{equation}
-и для гамма-матриц выполняется
-\begin{equation}
-  \label{eq:284}
-  \gamma^{\mu}\gamma^{n}+\gamma^{\nu}\gamma^{\mu}=2\eta^{\mu\nu},\quad \gamma^{0}=
-  \begin{pmatrix}
-    0 & 1\\
-    1 & 0
-  \end{pmatrix}, \quad
-  \gamma^{1}=
-  \begin{pmatrix}
-    0 & -i\\
-    i & 0
-  \end{pmatrix}
-\end{equation}
-Вводим комплексные координаты \eqref{eq:225} и получаем
-\begin{equation}
-  \label{eq:285}
-  \gamma^{0}(\gamma^{0}\partial_{0}+\gamma^{1}\partial_{1})=2
-  \begin{pmatrix}
-    \bar \partial & 0\\
-    0 & \partial
-  \end{pmatrix}
-\end{equation}
-Тогда действие в компонентах \eqref{eq:283} будет
-\begin{equation}
-  \label{eq:286}
-  S=g\int d^{2}x (\bar \psi \partial \bar \psi + \psi\bar \partial \psi)
-\end{equation}
-Классические уравнения движения
-\begin{eqnarray}
-  \label{eq:287}
-  \partial \bar \psi=0\\
-  \bar \partial \psi=0, 
-\end{eqnarray}
-следовательно $\psi=\psi(x)$ и $\bar \psi=\bar \psi(\bar z)$.
-
-Мы хотим вычислить двухточечные корреляционные функции (пропагаторы).
-Они имеют вид $\langle \psi_i(x)\psi_j(x)\rangle, i,j=1,2$ (в координатах $x_1,x_2$).
-Для этого перепишем действие в матричном виде
-\begin{equation}
-  \label{eq:288}
-  S=\frac{1}{2}\int d^2x d^2 y \psi_i (x) A_{ij}(x,y) \psi_j(y),
-\end{equation}
-где мы ввели ядро
-\begin{equation}
-  \label{eq:289}
-  A_{ij}(x,y)=g \delta(x-y) (\gamma^0 \gamma^{\mu})_{ij} \partial_{\mu}.
-\end{equation}
- Корреляторы можно собрать в матрицу $K_{ij}(x,y)=\langle \psi_i(x)\psi_j(y)\rangle$. Если вычислить гауссов функциональный интеграл, то получается, что
- \begin{equation}
-   \label{eq:290}
-   K_{ij}(x,y)=\left(A^{-1}\right)_{ij}(x,y).
- \end{equation}
-То есть $K$ удовлетворяет следующему уравнению:
-\begin{equation}
-  \label{eq:291}
-  g \delta (x-y) (\gamma^0 \gamma^{\mu})_{ik} \frac{\partial}{\partial x^{\mu}} K_{kj}(x,y)=\delta(x-y)\delta_{ij}
-\end{equation}
-В наших комплексных координатах это уравнение имеет очень простой вид
-\begin{equation}
-  \label{eq:292}
-  2g
-  \begin{pmatrix}
-    \bar \partial & 0\\
-    0 & \partial
-  \end{pmatrix}
-  \begin{pmatrix}
-    \langle \psi(z,\bar z) \psi(w,\bar w) \rangle & \langle\psi(z,\bar z)\bar \psi(w,\bar w) \rangle \\
-    \langle \bar \psi(z,\bar z) \psi(w,\bar w) \rangle & \langle\bar\psi(z,\bar z)\bar \psi(w,\bar w) \rangle \\    
-  \end{pmatrix}=
-  \frac{1}{\pi}
-  \begin{pmatrix}
-    \bar \partial\frac{1}{z-w} & 0\\
-    0 & \partial \frac{1}{\bar z-\bar w}
-  \end{pmatrix}
-\end{equation}
-Решением этого уравнения будут
-\begin{eqnarray}
-  \label{eq:293}
-  \langle \psi(z,\bar z) \psi(w,\bar w) \rangle=\frac{1}{2\pi g} \frac{1}{z-w}\\
-  \langle\bar\psi(z,\bar z) \bar \psi(w,\bar w) \rangle =\frac{1}{2\pi g} \frac{1}{\bar z-\bar w}\\
-  \langle\psi(z,\bar z) \bar \psi(w,\bar w) \rangle =0
-\end{eqnarray}
-Если их продифференцировать, получаем
-\begin{eqnarray}
-  \label{eq:294}
-  \langle \partial_z \psi(z,\bar z) \psi(w,\bar w) \rangle=-\frac{1}{2\pi g} \frac{1}{(z-w)^2}\\
-  \langle \partial_z \psi(z,\bar z) \partial_w \psi(w,\bar w) \rangle=-\frac{1}{\pi g} \frac{1}{(z-w)^3}
-\end{eqnarray}
-То есть имеет место операторное разложение
-\begin{equation}
-  \label{eq:295}
-  \psi(z)\psi(w)\sim \frac{1}{2\pi g} \frac{1}{z-w}
-\end{equation}
-Для компонент тензора энергии-импульса имеем
-\begin{eqnarray}
-  \label{eq:296}
-  T^{\bar z\bar z} =2g\psi\partial \psi\\
-  T^{ z z} =2g\bar \psi\bar\partial \bar \psi\\
-  T^{ z\bar z} =-2g\psi\bar\partial \psi\neq 0
-\end{eqnarray}
-Однако $T^{z\bar z}$ исчезает на классических траекториях, то есть теория является конформной.
-Вводим привычное обозначение и квантуем:
-\begin{equation}
-  \label{eq:297}
-  T(z)=-2\pi T_{zz}=-\pi g :\psi(z) \partial \psi(z):=-\pi g\lim_{w\to z}(\psi(z)\partial \psi(w) -\langle\psi(z) \partial \psi(w)\rangle)
-\end{equation}
-Используем теорему Вика и вычисляем операторное разложение
-\begin{equation}
-  \label{eq:298}
-  T(z) \psi(w)=-\pi g:\psi(z)\partial \psi(z) :\psi(w) \sim \frac{1}{2}\frac{\partial \psi(z)}{z-w} +\frac{1}{2}\frac{\psi(z)}{(z-w)^2} \sim \frac{\frac{1}{2} \psi(w)}{(z-w)^2} +\frac{\partial \psi(w)}{z-w}
-\end{equation}
-Мы видим, что у фермионного поля $\psi$ конформная размерность $h=\frac{1}{2}$.
-
-Теперь аналогично вычисляем операторное разложение $T$ с собой:
-\begin{equation}
-  \label{eq:299}
-  T(z)T(w)=\pi^2 g^2 :\psi(z)\partial \psi(z)::\psi(w)\partial \psi(w): \sim \frac{\frac{1}{4}}{(z-w)^4} +\frac{2T(w)}{(z-w)^2} +\frac{\partial T(w)}{z-w}
-\end{equation}
-Мы видим, что центральный заряд в теории свободного фермиона $c=\frac{1}{2}$.
-
-Ненулевые операторные разложения между членами конформных семейств определяются разложениями примарных полей. Поэтому можно писать сразу для семейств
-\begin{equation}
-  \label{eq:300}
-  [\varphi_i][\varphi_j]=\sum_k C_{ijk} [\varphi_k]
-\end{equation}
-В модели Изинга у нас есть три семейства $[1], [\sigma], [\varepsilon]$. Из наличия симметрий ($\sigma\to - \sigma$ и $\varepsilon\to -\varepsilon$ (дуальность Крамерса-Ванье)) имеем:
-\begin{eqnarray}
-  \label{eq:301}
-  \left[\sigma\right]\left[\sigma\right]=1+\left[\varepsilon\right]\\
-  \left[\sigma\right]\left[\varepsilon\right]=\left[\sigma\right]\\
-  \left[\varepsilon\right]\left[\varepsilon\right]=1
-\end{eqnarray}
-Отсюда можно вычислять все корреляционные функции. Например, для четырехточечной функции получается:
-\begin{equation}
-  \label{eq:302}
-  G^{(4)} =\langle \sigma(z_1,\bar z_1)\dots \sigma(z_4,\bar z_4)\rangle = \frac{1}{2} \left|\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right|^{\frac{1}{4}}\left(\left|1+\sqrt{1-x}\right| + \left|1-\sqrt{1-x}\right|\right)
-\end{equation}
-
-\section{Заключение}
-\label{sec:conclusion}
-
-\bibliography{2dqft}{}
-\bibliographystyle{utphys}
-
 \end{document}
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2011-03-14 GeneralOverview/Lectures/talk.tex
Added notes from Dima. They are to be rewritten.

@@
 \label{sec:noether}
+From: Dmitry Chicherin <tchitcherin@gmail.com>
+Subject: теорема Нётер
+To: Anton Nazarov <antonnaz@gmail.com>
+Date: Mon, 14 Mar 2011 23:08:53 +0300
+
+Привет!
+
+Я хочу сказать про злосчастную теорему Нётер, если ты ещё не
+посмотрел. Доказательство из Дифранческо работает для симметрий именно
+действия. Его доказательство тоже, что и у Вайнберга и идейно
+отличается от Боголюбова. Он сначала формально продолжает
+преобразования глобальной симметрии до локальных, т.е. его
+инфинитезимальные параметры становятся функциями. С такими
+преобразованиями он считает вариацию, раскладывается до первого
+порядка по параметру преобразования, но не ограничивается полями на
+уравнениях движения! Затем он выкидывает под интегралом те члены,
+которые не содержат производных от параметров преобразования в силу
+глобальной симметрии(здесь и есть отличие от Боголюбова и иже с ним).
+В итоге как и положено остаётся только первая производная от
+параметров преобразования на ток. При этом параметр преобразований всё
+время произвольная функция. Далее он говорит, что если сесть на
+уравнения движения, то вариация даст нуль и опять же параметр
+преобразования всё время постоянная функция. Короче говоря,
+рассуждение совсем отличается от Боголюбовского, хотя промежуточные
+формулы и похожи.
+
+Удачи,
+Дима
 

### 2011-03-21 GeneralOverview/Lectures/talk.tex
Notes for talks of 14th and 21st of March 2011

--- 2011-03-14 GeneralOverview/Lectures/talk.tex
@@
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}
+\newtheorem{definition}{Определение}
+\newtheorem{exercise}{Упражнение}
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
 \newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
+\newcommand{\gf}{\mathfrak{g}}
 \newcommand{\af}{\mathfrak{a}}
@@
 
-\topmargin=-3.5cm
-\oddsidemargin=-1.5cm
-\evensidemargin=-1.5cm
-\textwidth=19cm
-\textheight=28cm
+\title{Записки с семинара ``Конформная теория поля''}
+\author{Антон Назаров}
 
 \begin{document}
-\subsection*{Классическая и квантовая теория поля}
+\maketitle
+\tableofcontents
+\section{14 марта 2011}
+\label{sec:14--2011}
+
+\subsection{Классическая теория поля}
 \label{sec:qft}
@@
 
-\subsubsection*{Симметрии}
+\subsection{Симметрии и генераторы}
 \label{sec:symmetry}
@@
 
-\begin{equation*}
+\begin{equation}
   \label{eq:306}
   x'^{\mu}=x^{\mu}+a^{\mu},\quad \varphi'(x+a)=\varphi(x),\quad S'=S
-\end{equation*}
+\end{equation}
 
 Поворот (преобразования Лоренца):
-\begin{equation*}
+\begin{equation}
   x'^{\mu}=m^{\mu}_{\nu} x^{\nu}, \quad \varphi'(m x)=\Lambda \varphi(x),\quad \Lambda \mbox{--представление группы} 
-\end{equation*}
+\end{equation}
 
@@
 В этом случае действие должно быть стационарно по отношению к инфинитезимальным преобразованиям.
+Мы будем считать, что инфинитезимальные параметры преобразований зависят от координат, то есть рассматривать не только глобальные, но и локальные преобразования.
 
@@
 Если же при поворотах поле преобразуется $\varphi'(x')=\Lambda\varphi(x)$, то при инфинитезимальных преобразованиях $\varphi'(x')=\varphi(x)-\frac{i}{2}\omega_{\mu\nu}S^{\mu\nu}$ и генератор принимает вид
-\begin{equation*}
+\begin{equation}
   L_{\mu\nu}=i(x_{\mu}\partial_{\nu}-x_{\nu}\partial{\mu})+S_{\mu\nu}
-\end{equation*}
+\end{equation}
 
-\subsubsection*{Теорема Нётер}
+\subsection{Теорема Нётер}
 \label{sec:noether}
@@
 Теперь рассмотрим произвольные инфинитезимальные преобразования, при которых действие не меняется.
+Инфинитезимальные параметры зависят от точки в пространстве, то есть мы рассматриваем локальные преобразования.
+Преобразования, для которых такой зависимости нет, называются глобальными.
 Якобиан такого преобразования
-\begin{eqnarray*}
+\begin{eqnarray}
   \frac{\partial x'^{\nu}}{\partial x^{\mu}} = \delta^{\mu}_{\nu}+\partial_{\mu}\left(\omega_a \frac{\delta x^{\nu}}{\delta \omega_a}\right)\\
   \frac{\partial x^{\nu}}{\partial x'^{\mu}} = \delta^{\mu}_{\nu}-\partial_{\mu}\left(\omega_a \frac{\delta x^{\nu}}{\delta \omega_a}\right)
-\end{eqnarray*}
-\begin{equation*}
+\end{eqnarray}
+\begin{equation}
   \left|\frac{\partial x'^{\nu}}{\partial x^{\mu}}\right| = 1+\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)
-\end{equation*}
+\end{equation}
 Вариация действия
-\begin{multline*}
+\begin{multline}
   0=\delta_{\omega} S=\int \mathcal{L}(\varphi',\partial_{\mu}\varphi',x'^{\mu})dx'-\int \mathcal{L}(\varphi,\partial_{\mu}\varphi,x)dx=\\
@@
     \partial_{\mu}\varphi+\partial_{\mu}\delta_{\omega}\varphi\right)\right]-\mathcal{L}(\varphi,\partial_{\mu}\varphi)=
-\end{multline*}
-\begin{multline*}
+\end{multline}
+\begin{multline}
       \int d^{d}x\left( \frac{\partial \mathcal{L}}{\partial \varphi} \delta_{\omega}\varphi +\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\partial_{\mu}\varphi +\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)\mathcal{L}\right)
-\end{multline*}
+\end{multline}
+
+Члены, не содержащие производных от $\omega_{a}$ зануляются в случае наличия глобальной симметрии.
+
 Первые два члена переписываются с использованием уравнений Эйлера-Лагранжа и интегрирования по частям:
-\begin{equation*}
+\begin{equation}
   \partial_{\mu}\left(\frac{\partial \mathcal{L}}{\partial (\partial_{\mu}\varphi)}\right)\delta_{\omega}\varphi+\frac{\partial \mathcal{L}}{\partial (\partial_{\mu}\varphi)}\delta_{\omega}\partial_{\mu}\varphi=
     \partial_{\mu}\left(\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\varphi\right)
-\end{equation*}
+\end{equation}
 В итоге имеем:
-\begin{equation*}
+\begin{equation}
   0=\int d^{d}x \partial_{\mu}\left(\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\varphi +\delta^{\mu}_{\nu}\mathcal{L} \frac{\delta x^{\nu}}{\delta \omega_{a}}\right)
-\end{equation*}
+\end{equation}
 Если подставить явный вид вариации поля и ввести обозначение
-\begin{equation*}
+\begin{equation}
   j^{\mu}_{a}=\left(\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\partial_{\nu}\varphi -\delta^{\mu}_{\nu}\mathcal{L}\right) \frac{\delta x^{\nu}}{\delta \omega_{a}}-\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\frac{\delta F}{\delta w_{a}},
-\end{equation*}
+\end{equation}
 то для вариации действия выходит:
-\begin{equation*}
+\begin{equation}
   \delta_{\omega}S=-\int d^{d}x j^{\mu}_{a}\partial_{\mu}\omega_{a}
-\end{equation*}
-$j^{\mu}_{a}$ называется нетеровским током, соответствующим данной симметрии. 
-Если $\delta_{\omega} S=0$, то
-\begin{equation*}
+\end{equation}
+$j^{\mu}_{a}$ называется Нётеровским током, соответствующим данной симметрии. Проинтегрируем по частям и получим:
+\begin{equation}
+    \delta_{\omega}S=\int d^{d}x (\partial_{\mu} j^{\mu}_{a})\omega_{a}
+\end{equation}
+Если поля удовлетворяют уравнениям движения, то действие инвариантно относительно любой вариации полей, то есть вариация действия должна зануляться для любого $\omega(x)$. Тогда
+\begin{equation}
   \partial_{\mu}j^{\mu}_{a}=0
-\end{equation*}
-Сохраняющийся заряд:
-\begin{equation*}
+\end{equation}
+Таким образом каждой симметрии соответствует ток $j_{\mu}^{a}$ и сохраняющийся заряд:
+\begin{equation}
   Q_{a}=\int d^{d-1}x\; j^{0}_{a}
-\end{equation*}
+\end{equation}
+
+{\bf Пример}
 
@@
 
-\subsection*{Конформная алгебра}
+\section{21 марта 2011}
+\label{sec:21--2011-1}
+
+\subsection{Конформная алгебра в $d\geq 3$}
 \label{sec:conformal}
@@
 
+\subsection{Локальные конформные преобразования в двумерной теории}
+\label{sec:2d-cft}
+
 Мы получили общее условие на вид инфинитезимальных конформных преобразований:
@@
   \label{eq:226}
-  \partial \epsilon=0\\
-  \bar \partial \bar \epsilon=0.
+   \bar \partial \epsilon=0\\
+  \partial\bar \epsilon=0.
 \end{eqnarray}
@@
 Так как $l_{0}+\bar l_{0}$ -- генератор дилатации, то скейлинговая размерность $\Delta=h+\bar h$, а поскольку $i(l_{0}-\bar l_{0})$ порождает вращения, то спин $s=h-\bar h$.
+
+\subsection{Центральное расширение алгебры Витта}
+\label{sec:witt-algebra-central-extension}
+
+Напомним несколько определений (см \cite{fuks1986cohomology}, \cite{feigin1988}).
+\begin{definition}
+Будем рассматривать алгебру Ли $\gf$ над полем $k=\mathbb{C},\mathbb{R}$.
+Векторное пространство $A$ над полем $k$ называется {\it модулем над $\gf$} или {\it $\gf$-модулем}, если задано билинейное отображение $\mu:\gf\times A\to A$, такое что $\mu([X,Y],a)=\mu(X,\mu(Y,a))-\mu(Y,\mu(X,a))$ для $X,Y\in \gf, a\in A$.
+Далее мы будем опускать символ $\mu$ и писать $X a= \mu(X,a)$.
+\end{definition}
+\begin{definition}
+  {\it $n$-мерная коцепь с коэффициентами в $A$} -- это кососимметричный $n$-линейный функционал на $\gf$ со значениями в $A$. Пространство $n$-коцепей $C^{n}(\gf;A)=\mathrm{Hom}(\wedge^{n}\gf;A)$.
+\end{definition}
+Заметим, что элементы $\gf$ действуют на $C^{n}(\gf;A)$.
+\begin{definition}
+  Внешний дифференциал $d=d_{n}:C^{n}(\gf;A)\to C^{n+1}(\gf;A)$ определяется формулой
+  \begin{multline}
+    \label{eq:1}
+    (dc) (X_{1},\dots, X_{n+1})=\sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} c([X_{s},X_{t}],X_{1},\dots,\hat X_{s},\dots,\hat X_{t},\dots X_{n+1})\\
+    +\sum_{1\leq s\leq n+1} (-1)^{s}X_{s} c(X_{1},\dots \hat X_{s},\dots X_{n+1})
+  \end{multline}
+\end{definition}
+Оставляем в качестве упражнения проверку того факта, что последовательность
+\begin{equation}
+  \label{eq:2}
+  \dots\stackrel{d_{n}}{\longleftarrow} C^{n}(g;A)\stackrel{d_{n-1}}{\longleftarrow} C^{n-1}(\gf;A)\leftarrow \dots \leftarrow C^{1}(\gf;A) \stackrel{d_{0}}{\longleftarrow} C^{0}(\gf;A)\leftarrow 0
+\end{equation}
+точна.Тогда $\{C^{n}(\gf;A),d_{n}\}=C^{*}(\gf;A)$ есть комплекс.
+\begin{definition}
+Соответствующие когомологии называются {\it когомологиями алгебры $\gf$ с коэффициентами в $A$} и обозначаются через $H^{n}(\gf;A)=\mathrm{Ker}\; d_{n}/\mathrm{Im}\; d_{n-1}$.
+
+\end{definition}
+Заметим, что поле $k$ может рассматриваться как тривиальный $\gf$-модуль. В этом случае второй член в формуле \eqref{eq:1} исчезает и используют сокращенные обозначения $C^{n}(\gf), H^{n}(\gf)$.
+\begin{definition}
+  Определим, заодно, и гомологии. Пространство $n$-мерных цепей $C_{n}(\gf;A)=A\otimes \wedge^{n}\gf$, дифференциал $\partial=\partial_{n}:C_{n}(\gf;A)\to C_{n-1}(\gf;A)$ определяется формулой
+  \begin{multline}
+    \label{eq:3}
+    \partial(a\otimes (X_{1}\wedge \dots \wedge X_{n})) =\\ \sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} a\otimes ([X_{s},X_{t}]\wedge X_{1} \wedge\dots\wedge\hat X_{s}\wedge \dots\wedge \hat X_{t}\wedge \dots\wedge X_{n+1})\\
+    +\sum_{1\leq s\leq n+1} (-1)^{s}(X_{s} a)\otimes (X_{1}\wedge\dots\wedge \hat X_{s}\wedge\dots\wedge X_{n+1})
+  \end{multline}
+  Аналогично определяется точная последовательность, комплекс и группа гомологий $H_{n}(\gf;A)$.
+\end{definition}
+\begin{definition}
+  {\it Одномерным центральным расширением алгебры $\gf$ } называется точная последовательность
+  \begin{equation}
+    \label{eq:4}
+    0\to k \to \tilde \gf\to \gf\to 0,
+  \end{equation}
+  такая что образ $k\to \tilde\gf$ содержится в центре $\tilde\gf$.
+\end{definition}
+Заметим, что всякий 2-коцикл $c\in C^{2}(\gf;A)$ определяет центральное расширение $\gf$:
+\begin{equation}
+  \label{eq:5}
+  0\to k\stackrel{\lambda\to (0,\lambda)}{\longrightarrow}\tilde\gf=\gf\oplus k \stackrel{(X,\lambda)\to X}{\longrightarrow} \gf\to 0
+\end{equation}
+Скобка Ли в алгебре $\tilde\gf$, которая равна $\gf\oplus k$ как векторное пространство, определяется равенством
+\begin{equation}
+  \label{eq:6}
+  [(X,\lambda),(Y,\mu)]=([X,Y],c(X,Y))
+\end{equation}
+Тождество Якоби для такой скобки равносильно тому, что $c$-- 2-коцикл. Когомологичным коциклам отвечают эквивалентные расширения.
+
+Два расширения $\tilde \gf$ и $\tilde{\tilde\gf}$ называются эквивалентными, если существует изоморфизм $I:\tilde\gf\to \tilde{\tilde \gf}$ такой, что диаграмма коммутирует:
+\begin{equation}
+  \label{eq:7}
+  \begin{diagram}
+    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \arrow{s,l}{id} \node{\tilde\gf}\arrow{s,l}{I} \arrow{e,t}{} \node{k}\arrow{s,r}{id} \arrow{e,t}{} \node{0}\\
+    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \node{\tilde{\tilde\gf}} \arrow{e,t}{} \node{k} \arrow{e,t}{} \node{0}
+  \end{diagram}
+\end{equation}
+\begin{exercise}
+ Построить изоморфизм $I$.   
+\end{exercise}
+
+Таким образом пространство $H^{2}(\gf)$ -- это множество классов 1-мерных центральных расширений $\gf$. Нуль в $H^{2}(\gf)$  соответствует тривиальному расширению.
+
+Вернемся к алгебре Витта \eqref{eq:230}. Существует коцикл
+\begin{equation}
+  \label{eq:8}
+  c(l_{n},l_{m})=\frac{1}{12}(m^{3}-m)\delta_{-n,m}
+\end{equation}
+\begin{exercise}
+  Проверить, что $c$ -- коцикл алгебры Витта. 
+\end{exercise}
+Соответствующее центральное расширение алгебры Витта называется алгеброй Вирасоро. Коммутационные соотношения этой алгебры имеют вид
+\begin{eqnarray}
+  \label{eq:9}
+  [L_{n},c]=0\\
+  \left[L_{n},L_{m}\right]=(n-m)L_{n+m} +\frac{c}{12} (m^{3}-m) \delta_{-n,m}
+\end{eqnarray}
+Можно показать, что $H^{2}(Witt)\cong \mathbb{C}$ и все нетривиальные коциклы пропорциональны $c$. 
+(Доказательство есть в \cite{fuks1986cohomology}, \cite{schottenloher2008mathematical}).
+\bibliography{talk}{}
+\bibliographystyle{utphys}
+
 \end{document}

### 2011-03-21 GeneralOverview/Lectures/talk.tex
PDF regen

@@
 \newtheorem{exercise}{Упражнение}
+\newtheorem{example}{Пример}
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
 \end{equation}
-{\bf Примеры.}
 
+\begin{example}
 Трансляции:
@@
 
+\end{example}
+\begin{example}
+
 Поворот (преобразования Лоренца):
@@
 
+\end{example}
 Теперь рассмотрим инфинитезимальные преобразования. 
@@
 
-Примеры генераторов:
+\begin{example}
 Если мы предположим, что поле $\varphi$ -- такое поле, которое не меняется при конформных преобразованиях, то есть $F(\varphi)=\varphi$, то мы получим следующий вид для генераторов:
@@
 \end{equation}
+
+\end{example}
 
@@
 
-{\bf Пример}
+\begin{example}
 
@@
 Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$. В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
+\end{example}
 
@@
 \begin{equation}
-  \label{eq:165}
+  \label{eq:10}
   x'^{\mu}=x^{\mu}+\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}
@@
 \begin{equation}
-  \label{eq:166}
+  \label{eq:11}
   \Phi'(x')=\Phi(x)+\omega_a \frac{\delta F}{\delta \omega_a} (x).
@@
 \begin{equation}
-  \label{eq:167}
+  \label{eq:12}
   \delta_{\omega} \Phi(x)=\Phi'(x)-\Phi(x)\equiv -i\omega_a G_a \Phi(x)
@@
 \begin{equation}
-  \label{eq:168}
+  \label{eq:13}
   iG_a \Phi=\frac{\delta x^{\mu}}{\delta\omega_a} \partial_{\mu}\Phi-\frac{\delta F}{\delta \omega_a}
@@
 \begin{eqnarray}
-  \label{eq:169}
+  \label{eq:14}
   \mbox{трансляция} & \quad P_{\mu}=-i\partial_{\mu}\\
@@
 
-Напомним несколько определений (см \cite{fuks1986cohomology}, \cite{feigin1988}).
+Напомним несколько определений (см \cite{fuks1986cohomology},\cite{fuks1984}, \cite{feigin1988}).
 \begin{definition}

### 2011-03-28 AffineLieAlgebras/CPC/article.tex
Some work on help for Mathematica code
Some work on CPC paper. lstlisting package is added to preamble. Sum of finite root systems needs to be implemented.

@@
 \usepackage{hyperref}
+\usepackage{listings}
+\usepackage{textcomp}
+\definecolor{listinggray}{gray}{0.9}
+\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
+\lstset{
+%	backgroundcolor=\color{lbcolor},
+        language=Mathematica,
+	tabsize=2,
+	rulecolor=,
+        basicstyle=\scriptsize,
+        upquote=true,
+%        aboveskip={1.5\baselineskip},
+        columns=fixed,
+        showstringspaces=false,
+        extendedchars=true,
+%        breaklines=true,
+        prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
+%        frame=single,
+        showtabs=false,
+        showspaces=false,
+        showstringspaces=false,
+        identifierstyle=\ttfamily,
+        keywordstyle=\color[rgb]{0,0,1},
+        commentstyle=\color[rgb]{0.133,0.545,0.133},
+        stringstyle=\color[rgb]{0.627,0.126,0.941},
+}
 
@@
 
-Extended affine Lie algebras currently attract a lot of attention. These algebras has applications in supergravity
-
-Reference.
-
 Multiplicities, branching and tensor product problems are essentially different faces of the same problem.
@@
 
-General recurrent relations for branching coefficients of non-maximal embeddings were proposed in [1007].
-It [1102] it was shown that these relations demonstrate the connection of branching problem with BGG resolution.
+General recurrent relations for branching coefficients of non-maximal embeddings were proposed in \cite{2010arXiv1007.0318L}.
+In \cite{2011arXiv1102.1702L} it was shown that these relations demonstrate the connection of branching problem with BGG resolution.
 Also it was noticed, that weight multiplicities and tensor product decomposition coefficients can be obtained in the special cases of Lie algebra embeddings ($\hf\subset\gf$ and $\gf\subset\gf\otimes\gf$ correspondingly).
@@
 
-Methods and algorithms.
 For (1) we use fairly standard algorithms.
@@
 
+\section{Core algorithms and data structures}
+\label{sec:core-algorithms}
+
+Consider Lie algebra $\gf$ of finite or affine type.
+We denote its root system by $\Delta$.
+Roots and weights of the algebra are represented by the data-structures \lstinline{finiteWeight} and \lstinline{affineWeight} of {\it Affine.m} package.
+Root system is determined by the set of simple roots $\alpha_{1}, \dots, \alpha_{r}$, where $r$ is the rank of the algebra.
+So to specify an algebra it is enough to have simple roots.
+The set of simple roots can be created using different methods.
+The coordinates of simple roots can be entered by hand, for example direct sum $sl_{2}\oplus sl_{2}$ can be constructed by the code
+\begin{lstlisting}
+  makeFiniteRootSystem[{{1,0}, {0,1}}]
+\end{lstlisting}
+For simple finite-dimensional Lie algebras there are built-in constructors
+\begin{lstlisting}
+  b2=makeSimpleRootSystem[B,2]
+
+  Out[6]= finiteRootSystem[2, {finiteWeight[2, {1, -1}], finiteWeight[2, {0, 1}]}]
+\end{lstlisting}
+
+Central data structures of our package are {\it finiteWeight} and {\it affineWeight}.
+These structures are used to represent weights of finite-dimensional and affine Lie algebras.
+We have implemented several constructors for convenience of users, so weights can be specified by the coordinates in standard orthogonal basis, Dynkin labels or coefficients of decomposition to the sum of simple roots.
+We introduce arithmetic operations on the structures of weight and inner product (Killing form) is represented by a built-in dot-product operation.
+
+\section{Examples}
+\label{sec:examples}
+
+\subsection{Finite-dimensional Lie algebras}
+\label{sec:finite-dimens-lie}
+
+Consider the algebra $B_{4}$ and regular subalgebra $B_{2}$. This embedding can be specified by the following code:
+\begin{equation}
+  \label{eq:1}
+  B_{2}\subset B_{4}
+\end{equation}
+
+Branching coefficients can be calculated using the formula () with the code:
+\begin{equation}
+  \label{eq:2}
+  calculate_{branching}
+\end{equation}
+
+It is interesting to note that the subalgebra $\afb$ is equal to $B_{2}$ in this case and not to $A_{1}$ as it can be thought from the Dynkin diagram.
+To visualize the diagrams and branching coefficients the following instructions were used:
+\begin{equation}
+  \label{eq:3}
+  plot
+\end{equation}
+\section{Conclusion}
+\label{sec:conclusion}
+
 \bibliography{bibliography}{}

### 2011-03-28 AffineLieAlgebras/Mathematica/datastructures.m

@@ -191,6 +191,7 @@ makeFiniteRootSystem[{roots__finiteWeight}]:=finiteRootSystem[Length[{roots}],{r
 finiteRootSystem/:x_finiteRootSystem[rank]:=x[[1]];
 finiteRootSystem/:x_finiteRootSystem[simpleRoots]:=x[[2]];
 finiteRootSystem/:x_finiteRootSystem[simpleRoot][n_Integer]:=x[[2]][[n]];
+finiteRootSystem/:x_finiteRootSystem+y_finiteRootSystem:=
 
 makeFiniteRootSystem[{roots__List}]:=makeFiniteRootSystem[makeFiniteWeight/@{roots}]
 
@@ -344,7 +345,7 @@ positiveRoots::"usage"=
 (* Ugly hack *)
 positiveRoots[rs_affineRootSystem]:=Join[Map[-#&,Flatten[partialOrbit[rs][Map[-#&,rs[simpleRoots]]]]],
 					 Join@@Table[NestWhileList[#+makeAffineWeight[zeroWeight[rs[finiteRootSystem]],0,1]&,zeroWeight[rs],checkGrade[rs][#]&],{rs[rank]}]];
-positiveroots[rs_?rootSystemQ]:=Map[-#&,Flatten[partialOrbit[rs][Map[-#&,rs[simpleRoots]]]]]
+positiveRoots[rs_?rootSystemQ]:=Map[-#&,Flatten[partialOrbit[rs][Map[-#&,rs[simpleRoots]]]]]
 
 
 Module[{b2=makeSimpleRootSystem[B,2]},
@@ -368,7 +369,6 @@ weightSystem[rs_?rootSystemQ][higestWeight_?weightQ]:=Module[{minusPosRoots=-pos
 										 Cases[Flatten[Outer[Plus,minusPosRoots,x]],y_/;
 										       And[checkGrade[rs][y],And@@(#.y>=0&/@rs[simpleRoots])]]
 										 ,x]],{higestWeight},#=!={}&]]];
-
 
 Module[{b2=makeSimpleRootSystem[B,2]},
        Expect["Weights of [2,1] module of B2",True, weightSystem[b2][makeFiniteWeight[{2,1}]]==
@@ -409,6 +409,10 @@ Module[{b2=makeSimpleRootSystem[B,2],fm},
 orbitWithEps::"usage"="returns orbit with the determinants of Weyl reflections";
[…]

### 2011-03-29 AffineLieAlgebras/CPC/article.tex
Some text on Weyl group, start of representation theory section

@@
 Consider Lie algebra $\gf$ of finite or affine type.
-We denote its root system by $\Delta$.
-Roots and weights of the algebra are represented by the data-structures \lstinline{finiteWeight} and \lstinline{affineWeight} of {\it Affine.m} package.
-Root system is determined by the set of simple roots $\alpha_{1}, \dots, \alpha_{r}$, where $r$ is the rank of the algebra.
-So to specify an algebra it is enough to have simple roots.
-The set of simple roots can be created using different methods.
-The coordinates of simple roots can be entered by hand, for example direct sum $sl_{2}\oplus sl_{2}$ can be constructed by the code
+We denote its Cartan subalgebra by $\hf$ and root system by $\Delta$.
+Roots $\alpha_i\in \Delta$ and weights $\mu,\nu\in \hf^*$ of the algebra are represented by the data-structures \lstinline{finiteWeight} and \lstinline{affineWeight} of {\it Affine.m} package.
+Root system can be reconstructed from the set of simple roots $\alpha_{1}, \dots, \alpha_{r}$, where $r$ is the rank of the algebra, by the action of Weyl group $W_{\gf}$.
+
+The set of simple roots can be created using different methods. The coordinates of simple roots can be entered by hand, for example direct sum $sl_{2}\oplus sl_{2}$ can be constructed by the code
 \begin{lstlisting}
@@
 
-  Out[6]= finiteRootSystem[2, {finiteWeight[2, {1, -1}], finiteWeight[2, {0, 1}]}]
+  Out[6]= finiteRootSystem[2, 2, {finiteWeight[2, {1, -1}], finiteWeight[2, {0, 1}]}]
+\end{lstlisting}
+
+It is possible to specify direct sum of algebras:
+\begin{lstlisting}
+  b2+b2
+
+  Out[6]= finiteRootSystem[4, 4, {finiteWeight[4, {1, -1, 0, 0}], finiteWeight[2, {0, 1}]}]
+\end{lstlisting}
+
+Addition, multiplication by number and scalar product are defined for roots and weights:
+\begin{lstlisting}
+  makeFiniteWeight[{1,1}]+2*makeFiniteWeight[{1,-1}]
+
+  Out[7]=finiteWeight[2, {3, -1}]
+\end{lstlisting}
+
+It is possible to compute Cartan matrix or draw Dynkin diagram of the algebra or specify an algebra with Cartan matrix or Dynkin diagram. TODO
+
+Action of Weyl group $W_{\gf}$ generated by simple reflections $s_{\alpha}, \alpha\in \Delta$ is important for computations.
+We denote by $C_{\gf}\subset \hf^*$ the main Weyl chamber (fundamental domain for the action of $W_{\gf}$) and its closure by $\bar C_{\gf}$.
+In many computations it is possible to work inside the main Weyl chamber due to Weyl symmetry.
+
+Sometimes it can be helpful to consider Weyl group elements abstractly withouth the reference to root system.
+For example, there exists package for rule-based simplification of Weyl group elements based on finite automata [cite!].
+We offer the function \lstinline{weylGroupElement[x__Integer][rs_?rootSystemQ]} which produces the object, representing element of Weyl group encoded by the set of reflections, that can act upon the weights.
+It can be used as follows:
+\begin{lstlisting}
+  <<simplification.m;
+  (weylGroupElement @@ simplify[s[1,2,3,1,3,1,2,1,4,2,1]])[b2+b2][makeFiniteWeight[{1,1,0,0}]]
+
+  Out[7]= finiteWeight[4, {-1, 1, 0, 0}]
+\end{lstlisting}
+
+Following functions can be used to compute objects related to Weyl group and its action on roots and weights
+ \begin{itemize}
+ \item   $\forall \mu\in \hf^* \exists \lambda\in \bar C_{\gf}, w\in W_{\gf}: \mu=w \lambda$, the function \lstinline{toFundamentalChamber} can be used to find such $\lambda$.
+ \item Orbit of weight under the action of Weyl group is computed with the function \lstinline{orbit}, the elements of the orbit are grouped by the length of Weyl group element.
+ \end{itemize}
+
+\subsection{Representation theory}
+\label{sec:repr-theory}
+
+Weights of the irreducible highest weight representation are calculated using the function \lstinline{weightSystem}
+\begin{lstlisting}
+  weightSystem[b2][fundamentalWeights[b2][[1]]*2]
 \end{lstlisting}

### 2011-04-04 AffineLieAlgebras/CPC/article.tex
Projection, Dynkin indices, orthogonal subsystem and some documentation in datastructures.m Sections in thesis. Small example in CPC paper.

@@
 
+Weights can be specified by coordinates in standard basis or by Dynkin labels. The latter way is preferable. 
+\begin{lstlisting}
+  makeFiniteWeight[{1,0}]
+
+  weight[b2][1,1]
+
+  weight[b2a][1,0,1]
+\end{lstlisting}
+
 Addition, multiplication by number and scalar product are defined for roots and weights:
@@
 
-Central data structures of our package are {\it finiteWeight} and {\it affineWeight}.
-These structures are used to represent weights of finite-dimensional and affine Lie algebras.
-We have implemented several constructors for convenience of users, so weights can be specified by the coordinates in standard orthogonal basis, Dynkin labels or coefficients of decomposition to the sum of simple roots.
-We introduce arithmetic operations on the structures of weight and inner product (Killing form) is represented by a built-in dot-product operation.
-
 \section{Examples}

### 2011-04-04 AffineLieAlgebras/Mathematica/datastructures.m

@@ -194,14 +194,28 @@ finiteRootSystem/:x_finiteRootSystem[dimension]:=x[[2]];
 finiteRootSystem/:x_finiteRootSystem[simpleRoots]:=x[[3]];
 finiteRootSystem/:x_finiteRootSystem[simpleRoot][n_Integer]:=x[[3]][[n]];
 
+
+prependZeros::"usage"=
+    "prependZeros[num_Integer,vec_finiteWeight] embeds vec to bigger space by prepending num zeros to its coordinates";
 prependZeros[num_Integer,vec_finiteWeight]:=makeFiniteWeight[Join[Table[0,{num}],vec[standardBase]]];
+
+Expect["prependZeros",0,"__TODO__"]
+
+appendZeros::"usage"=
+    "appendZeros[num_Integer,vec_finiteWeight] embeds vec to bigger space by appending num zeros to its coordinates";
 appendZeros[num_Integer,vec_finiteWeight]:=makeFiniteWeight[Join[vec[standardBase],Table[0,{num}]]];
 
+Expect["appendZeros",0,"__TODO__"]
+
+Plus::"usage"=Plus::"usage" <> "\n Direct sum of finite-dimensional and affine Lie algebras can be specified as sum of root systems";
 finiteRootSystem/:x_finiteRootSystem+y_finiteRootSystem:=makeFiniteRootSystem[Join[Map[appendZeros[y[dimension],#]&,x[simpleRoots]],
 										   Map[prependZeros[x[dimension],#]&,y[simpleRoots]]]];
 
+Expect["Direct sum of finite-dimensional Lie algebras",0,"__TODO__"]
+
 affineRootSystem/:x_affineRootSystem+y_affineRootSystem+y:=makeAffineExtension[x[finiteRootSystem]+y[finiteRootSystem]];
 
+Expect["Direct sum of affine Lie algebras",0,"__TODO__"]
 
 makeFiniteRootSystem[{roots__List}]:=makeFiniteRootSystem[makeFiniteWeight/@{roots}]
 
@@ -464,6 +478,18 @@ Append[makeAffineExtension[makeSimpleRootSystem[B,2]][simpleRoots],makeAffineExt
 
 (* makeAffineExtension[makeSimpleRootSystem[B,2]][simpleRoot][0] *)
 
+
+affineRootSystem::"usage"=
[…]

### 2011-04-04 AffineLieAlgebras/Mathematica/testd.m

@@ -2,6 +2,107 @@ AppendTo[$Path,"/home/anton/study/2011/Articles/AffineLieAlgebras/Mathematica/"]
 
 <<datastructures.m;
 
+b2Out[45]= finiteRootSystem[2, {finiteWeight[2, {1, -1}], 
+ 
+>     finiteWeight[2, {0, 1}]}]
+
+Out[46]= {}
+
+orthogonalSubsystem[b2,makeFiniteRootSystem[{makeFiniteWeight[{1,1}]}]]
+
+marks::"usage"="comarks[rs_affineRootSystem] returns comarks of affine Lie algebra";
+comarks[rs_affineRootSystem]:=marks[rs]*Map[#.#/2&,rs[simpleRoots]]
+
+fundamentalWeights[b2].{3,2}                                                    1  1
+Out[74]= {finiteWeight[2, {1, 0}], finiteWeight[2, {-, -}]}
+                                                    2  2
+
+fundamentalWeights[b2]
+
+makeWeight[rs_?rootSystemQ][labels__Integer]:=fundamentalWeights[rs].{labels}
+
+makeWeight[makeAffineExtension[b2]][0,0,1]
+
+weight[rs_?rootSystemQ][labels__Integer]:=fundamentalWeights[rs].{labels}
+
+ww=weight[A2][1,0]
+
+
+
+
+Clear[A2]
+
+A2=makeSimpleRootSystem[A,2]
+
+[Calculating...]
+
+[Calculating...]
+
+Out[87]= finiteRootSystem[2, {finiteWeight[3, {1, -1, 0}], 
+ 
+>     finiteWeight[3, {0, 1, -1}]}]
+
+Out[86]= weight[A2][1, 0]
+
+[Calculating...]
+
+                                          1  1
+Out[83]= affineWeight[2, finiteWeight[2, {-, -}], 1, 0]
+                                          2  2
+
+Out[82]= affineWeight[2, finiteWeight[2, {0, 0}], 1, 0]
+
+[Calculating...]
+
+                          7  5
+Out[78]= finiteWeight[2, {-, -}]
+                          2  2
+
+                          3  1
+Out[77]= finiteWeight[2, {-, -}]
+                          2  2
+
[…]

### 2011-04-08 AffineLieAlgebras/CPC/article.tex
Program summary template created

@@
 \end{abstract}
+
+{\footnotesize
+\section*{Program summary}
+\textit{Title of program:} Affine.m
+\\
+\textit{Catalogue identifier:}
+\\
+\textit{Program obtainable from:} (submitted to Computer Physics Communications) \\
+%CPC Program Library, Queen's University of Belfast, N. Ireland. Also from
+\mbox{}\qquad \texttt{http://github.com/naa/Articles/AffineLieAlgebras/Mathematica/}
+\\
+\textit{Reference in CPC to previous version:} 
+\\
+\textit{Catalogue identifier of previous version:}
+\\
+\textit{Does the new version supersede the original program?:}
+\\
+\textit{Computers:} Any computer running Mathematica
+\\
+\textit{Operating systems under which the new version has been
+tested:} Linux, Unix, Windows XP, MacOS
+\\
+\textit{Programming language:} Mathematica (version 7.0 or higher)
+\\
+\textit{Memory required to execute with typical data:} 20 Mbyte
+\\
+\textit{No. of bits in a word:} 64 or 32
+\\
+\textit{No. of processors used:} 1
+\\
+\textit{No. of bytes in distributed program, including test data,
+etc.:} 0.15 Mbyte
+\\
+\textit{Distribution format:} Unencoded compressed tar file
+\\
+\textit{Nature of physical problem:} 
+TODO: Finite dimensional Lie algebras are important for physics. Affine for CFT/
+
+Symmetry has been a very important fundamental principle under-
+lying human knowledge about our physical world. Among several
+mathematical formulations of symmetry, the Lie algebras and their
+corresponding Lie groups are probably the ones most explored.
+They were discovered by Sophus Lie and Wilhelm Killing during
+the last two decades of the 19th century. Lie’s work on Lie groups
+was inspired by Galois’ work in 1832 in which he discovered the
+ﬁnite groups. Independently, Killing had started a classiﬁcation of
+Lie groups which was the starting point to the Élie Cartan’s doctoral
+thesis in the beginning at the 20th century. Cartan was able to make
+a complete classiﬁcation of Lie groups. Since Cartan’s classiﬁca-
+tion, the theory of Lie groups has been utilized in many branches
+of physics, including molecular physics, atomic physics, nuclear
+physics and particle physics.
+\\
+\textit{Method of solution:} The Butler-Portugal algorithm.
+\\
+\textit{Restrictions on the complexity of the problem:}
+Calculations up to finite grade
+\\
+\textit{Typical running time:} A few seconds with generic expressions
+
+%
+}
 

### 2011-04-18 AffineLieAlgebras/Mathematica/datastructures.m
Fine typography introduced

@@ -686,6 +686,9 @@ fan[rs_?rootSystemQ,subs_?rootSystemQ]:=
 ourBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
     Module[{anomPoints,fn},
 	   anomPoints=1]
+
+
+
     
 (*
 fan[rs_?rootSystemQ,subs_?rootSystemQ]:=

### 2011-04-18 AffineLieAlgebras/Mathematica/testd.m
Testing

@@ -2,6 +2,4051 @@ AppendTo[$Path,"/home/anton/study/2011/Articles/AffineLieAlgebras/Mathematica/"]
 
 <<datastructures.m;
 
+fn=fan[makeSimpleRootSystem[B,2],makeFiniteRootSystem[{makeFiniteWeight[{1,1}]}]]
+
+                  1  1
+{finiteWeight[2, {-, -}], finiteWeight[2, {1, 1}]}
+                  2  2
+{2, 0}
+
+Out[97]= formalElement[table$910]
+
+                  1  1
+{finiteWeight[2, {-, -}], finiteWeight[2, {1, 1}]}
+                  2  2
+{2, 0}
+
+makeFormalElement[{makeFiniteWeight[{1/2,1/2}],makeFiniteWeight[{1/2,1/2}]}]
+
+Expand[makeFormalElement[{zeroWeight[makeFiniteRootSystem[{makeFiniteWeight[{1,1}]}]]},{1}]*(1-Exp[makeFiniteWeight[{1/2,1/2}]])^2][multiplicities]
+
+Out[78]= {1, 0, 0}
+
+ze=makeFormalElement[{zeroWeight[makeFiniteRootSystem[{makeFiniteWeight[{1,1}]}]]}]
+
+
+                                                    1  1
+Out[77]= {finiteWeight[2, {0, 0}], finiteWeight[2, {-, -}], 
+                                                    2  2
+ 
+>    finiteWeight[2, {1, 1}]}
+
+(Expand[(1-Exp[makeFiniteWeight[{1/2,1/2}]])^2][[2]]*ze)[multiplicities]
+
+Out[96]= {-2}
+
+(2*ze*Exp[makeFiniteWeight[{1/2,1/2}]])[multiplicities]
+
+Out[95]= {2}
+
+ze[makeFiniteWeight[{0,0}]]
+
+?MapAt
+
+MapAt[f, expr, n] applies f to the element at position n
+      in expr. If n is negative, the position is counted from the end. 
+
+        MapAt[f, expr, {i, j, ...}]
+         applies f to the part of expr
+           at position {i, j, ...}
+           . MapAt[f, expr, {{i , j , ...}, {i , j , ...}, ...}]
+                               1   1          2   2
+             applies f to parts of expr at several positions. 
+
+Out[92]= 1
+
+Out[91]= 0
+
+Out[90]= {0}
+
+Out[89]= {2}
+
+Out[88]= formalElement[table$851]
+
[…]

### 2011-04-20 GeneralOverview/IntegrableSystems.tex
Part of summary of integrable spin chains lectures.

@@
 \usepackage{ucs}
+%\usepackage[utf8x]{inputenc}
+%\usepackage[russian]{babel}
 \usepackage{cmap}
@@
 
-\title{Integrable systems and representation theory}
+\title{Интегрируемые спиновые цепочки}
+
 \begin{abstract}
-  We review basic notions of quantum integrable systems and then discuss the applications of the representation theory of finite-dimensional and affine Lie algebras.
 \end{abstract}
-\begin{document}
+
+\section{Лекция 1. 13 февраля 2011}
+
+Лекция началась с формулировки двух примеров интегрируемых спиновых цепочек -- XXX-цепочки со спином 1/2 и цепочки со спином, равным -1.
+
+XXX-цепочка -- это одномерная квантовая система, представляющая собой набор из N частиц со спинами.
+Спины могут быть как полуцелыми, так и в общем положении.
+Гамильтониан системы раскладывающимся в сумму взаимодействий ближайших соседей.
+Члены этой суммы представляют собой тензорные произведения спинов в соседних узлах.
+Пространство состояний представляет собой N-ую тензорную степень пространства представления алгебры sl(2), соответствующего данному значению спина.
+В случае спина 1/2 пространство представления -- это двумерное комплексное векторное пространство, а для спина -1 -- бесконечномерное пространство.
+
+Задача состоит в точном решении квантовой системы, то есть нахождении спектра и собственных состояний гамильтониана.
+
+Из sl(2)-инвариантности гамильтониана XXX-цепочки следует, что пространство состояний разбивается на sl(2)-инвариантные подпространства меньшей размерности, так как в результате действия генераторов алгебры sl(2) на собственные состояния гамильтониана будут опять получаться собственные состояния гамильтониана.
+Таким образом задача диагонализации гамильтониана упростилась.
+То есть чтобы диагонализовать гамильтониан, надо разложить N-ую тензорную степень пространства представления алгебры sl(2), соответствующего спину, в прямую сумму инвариантных подпространств неприводимых представлений, и диагонализовать гамильтониан на этих подпространствах меньшей размерности.
+
+\section{Лекция 2. 17 февраля 2011}
+
+Лекция была посвящена обсуждению цепочки со спинами в общем положении.
+В этом случае в качестве реализации пространства представления, соответствующего спину, можно взять пространство полиномов, тогда все пространство состояний будет пространством полиномов N переменных.
+Действие генераторов алгебры sl(2) на таком пространстве реализуется дифференциальными операторами.
+Однако в случае спина в общем положении частные производные в этом операторе не обязательно будут в целых степенях.
+Чтобы правильно интерпретировать такие операторы, их нужно переписать через гамма-функции и представить в интегральном виде.
+Гамильтониан представляет собой сумму членов, отвечающих взаимодействию ближайших соседей.
+Такие члены даются интегральным оператором.
+Была представлена явная реализация представлений алгебры sl(2) в виде дифференциальных операторов на пространстве полиномов.
+Показано, что в случае полуцелого спина возникает инвариантное конечномерное подпространство, на котором действует неприводимое представление алгебры sl(2).
+
+\section{Лекция 3. 24 февраля 2011}
+
+Мы проверяем sl(2)-инвариантность гамильтониана, представляющего собой интегральный оператор.
+Для этого мы вычисляем действие экспонент генераторов алгебры sl(2) на функции.
+Вычисление можно свести к решению уравнения, имеющего тот же вид, что и уравнения ренормгруппы в квантовой теории поля.
+Так как в данном случае пространство состояний бесконечномерное, то sl(2)-инвариантность гамильтониана не упрощает задачу так же сильно, как в случае спина 1/2.
+
+Затем мы начинаем рассмотрение общей конструкции интегрируемых спиновых цепочек. 
+\section{Лекция 4. 3 марта 2011}
+
+\section{Лекция 5. 10 марта 2011}
+
+\section{Лекция 6. 17 марта 2011}
+
+\section{Лекция 7. 24 марта 2011}
+
+\section{Лекция 8. 31 марта 2011}
+
+\section{Лекция 9. 7 апреля 2011}
+
+\section{Лекция 10. 14 апреля 2011}
 

### 2011-04-20 AffineLieAlgebras/Mathematica/datastructures.m
Outline of branching function. Anomalous points.

@@ -506,7 +506,9 @@ Module[{b2=makeSimpleRootSystem[B,2],fm},
 
 (* freudenthalMultiplicities[makeSimpleRootSystem[B,2]][makeFiniteWeight[{5,5}]] *)
 orbitWithEps::"usage"="returns orbit with the determinants of Weyl reflections";
-orbitWithEps[rs_?rootSystemQ][weight_?weightQ]:=Flatten[Most[MapIndexed[Function[{x,i},Map[{#,(-1)^(i[[1]]+1)}&,x]],orbit[rs][weight]]],1];
+orbitWithEps[rs_?rootSystemQ][weight_?weightQ]:=Flatten[MapIndexed[Function[{x,i},Map[{#,(-1)^(i[[1]]+1)}&,x]],orbit[rs][weight]],1];
+
+Expect["orbitWithEps __TODO__",False,True]
 
 racahMultiplicities::"usage"=
     "racahMultiplicities[rs_?rootSystemQ] returns hashtable with the multiplicities of 
@@ -673,7 +675,10 @@ branching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
 	   wgs=Select[Sort[pmults[weights],#1.rh>#2.rh&],mainChamberQ[subs]];
 	   Scan[(res[hashtable][#]=pmults[#];pmults=pmults - pmults[#]*makeFormalElement[freudenthalMultiplicities[subs][#]])&, wgs];
 	   res];
-	   
+
+anomalousWeights[rs_?rootSystemQ][hweight_?weightQ]:=
+    makeFormalElement @@ Transpose[{#[[1]]-rho[rs],#[[2]]}& /@ orbitWithEps[rs][hweight+rho[rs]]]
+
 
 fan::"usage"=
     "Constructs fan of the embedding";
@@ -684,8 +689,15 @@ fan[rs_?rootSystemQ,subs_?rootSystemQ]:=
 		  Fold[Expand[#1*(1-Exp[#2])^(pr[#2])]&,makeFormalElement[{zeroWeight[subs]}],pr[weights]]];
 
 ourBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
-    Module[{anomPoints,fn},
-	   anomPoints=1]
+    Module[{anomPoints,fn,reprw,orth},
+	   anomPoints=projection[subs][anomalousWeights[rs][highestWeight]];
[…]

### 2011-04-20 AffineLieAlgebras/Mathematica/testd.m
orbitWithEps, anomalousWeights

@@ -2,6 +2,111 @@ AppendTo[$Path,"/home/anton/study/2011/Articles/AffineLieAlgebras/Mathematica/"]
 
 <<datastructures.m;
 
+orbitWithEps[rs_?rootSystemQ][weight_?weightQ]:=Flatten[MapIndexed[Function[{x,i},Map[{#,(-1)^(i[[1]]+1)}&,x]],orbit[rs][weight]],1];
+
+anomalousWeights[makeSimpleRootSystem[B,2]][makeFiniteWeight[{2,1}]][weights]
+
+Out[21]= {finiteWeight[2, {2, 1}], finiteWeight[2, {0, 3}], 
+ 
+>    finiteWeight[2, {2, -2}], finiteWeight[2, {-3, 3}], 
+ 
+>    finiteWeight[2, {0, -4}], finiteWeight[2, {-5, 1}], 
+ 
+>    finiteWeight[2, {-3, -4}], finiteWeight[2, {-5, -2}]}
+
+Out[20]= {1, -1, -1, 1, 1, -1, -1, 1}
+
+anomalousWeights[rs_?rootSystemQ][hweight_?weightQ]:=
+    makeFormalElement @@ Transpose[{#[[1]]-rho[rs],#[[2]]}& /@ orbitWithEps[rs][hweight+rho[rs]]]
+
+
+Out[18]= {1, -1, -1, 1, 1, -1, -1, 1}
+
+Out[17]= {finiteWeight[2, {2, 1}], finiteWeight[2, {1, 2}], 
+ 
+>    finiteWeight[2, {2, -1}], finiteWeight[2, {-1, 2}], 
+ 
+>    finiteWeight[2, {1, -2}], finiteWeight[2, {-2, 1}], 
+ 
+>    finiteWeight[2, {-1, -2}], finiteWeight[2, {-2, -1}]}
+
+Out[11]= {finiteWeight[2, {2, 1}], finiteWeight[2, {1, 2}], 
+ 
+>    finiteWeight[2, {2, -1}], finiteWeight[2, {-1, 2}], 
+ 
+>    finiteWeight[2, {1, -2}], finiteWeight[2, {-2, 1}], 
+ 
+>    finiteWeight[2, {-1, -2}]}
+
+Out[10]= {1, -1, -1, 1, 1, -1, -1}
+
+Rest[orbit[makeSimpleRootSystem[B,2]][makeFiniteWeight[{2,1}]]]
[…]

### 2011-06-26 GeneralOverview/Lectures/talk.tex
Some work on CPC paper. lstlisting package is added to preamble. Sum of finite root systems needs to be implemented.
Talk

@@
 
+\section{28 марта 2011}
+\label{sec:28--2011}
+\begin{itemize}
+\item Броуновское движение
+\item Интеграл по путям
+\item Квантовая механика
+\item Статистическая физика
+\item Функциональный интеграл в квантовой теории поля
+\item Тождества Уорда
+\item Конформная аномалия.
+\end{itemize}
+
+\section{11 апреля 2011}
+\label{sec:11--2011}
+
+\subsection{Тождества Уорда}
+\label{sec:ward-identities}
+
+Напомним, о чем идет речь. В произвольной теории поля с полями $\Phi(x)$ инфинитезимальное преобразование может быть записано при помощи генераторов
+\begin{equation}
+  \label{eq:198}
+  \Phi'(x)=\Phi(x)-i\omega_{a} G_{a} \Phi(x)
+\end{equation}
+Вариация действия вычисляется через ток, соответствующий данному преобразовании:
+\begin{equation}
+  \label{eq:199}
+  j^{\mu}_{a}=\left(\frac{\partial \mathcal{L} }{\partial (\partial_{\mu}\Phi)} \partial_{\nu}\Phi -\delta^{\mu}_{\nu}\mathcal{L}\right) \frac{\delta x^{\nu}}{\delta \omega_{a}} - \frac{\partial \mathcal{L} }{\partial (\partial_{\mu} \Phi)}\frac{\delta F}{\delta \omega_{a}}
+\end{equation}
+\begin{equation}
+  \label{eq:200}
+  \delta S =\int d^{d}x \partial_{\mu}j^{\mu}_{a} \omega_{a}
+\end{equation}
+Обозначим через $X$ произведение локальных полей, входящих в коррелятор
+\begin{equation}
+  \label{eq:201}
+  X=\Phi(x_{1})\dots \Phi(x_{n}).
+\end{equation}
+Коррелятор дается функциональным интегралом
+\begin{equation}
+  \label{eq:202}
+  \langle X\rangle = \frac{1}{Z}\int \mathcal{D} \Phi X e^{-S[\Phi]}
+\end{equation}
+Сделаем замену переменных $\Phi\to \Phi'$ в функциональном интеграле. При этом можно предполагать, что ``мера интегрирования'' не меняется $\mathcal{D}\Phi'=\mathcal{D}\Phi$ \cite{difrancesco1997cft}:
+\begin{equation}
+  \label{eq:203}
+  \langle X\rangle = \frac{1}{Z} \int \mathcal{D} \Phi' (X+\delta X)e^{-S[\Phi]-\int d^{d}x \partial_{\mu}j^{\mu}_{a}\omega_{a}(x)}
+\end{equation}
+Раскладываем выражение в ряд до первого порядка по $\omega_{a}(x)$:
+\begin{equation}
+  \label{eq:204}
+  \langle X\rangle=\frac{1}{Z} \left( \int \mathcal{D} \Phi X e^{-S[\Phi]}+\int \mathcal{D} \Phi \delta X e^{-S[\Phi]} -\int \mathcal{D}\Phi \int d^{d}x \partial_{\mu}j^{\mu}_{a}\omega_{a}(x) X e^{-S[\Phi]}\right)
+\end{equation}
+В результате имеем
+\begin{equation}
+  \label{eq:205}
+  \langle \delta X\rangle=\int d^{d}x \partial_{\mu}\langle j^{\mu}_{a}(x) X\rangle \omega_{a}(x)
+\end{equation}
+С другой стороны, мы можем вычислить $\langle\delta X\rangle$ используя \eqref{eq:198}:
+\begin{multline}
+  \label{eq:206}
+  \langle\delta X\rangle=-i\sum_{i=1}^{n}\langle \Phi(x_{1})\dots G_{a} \Phi(x_{i}) \dots \Phi(x_{n})\rangle \omega_{a}(x_{i})=\\
+  -i \int d^{d}x \omega_{a}(x) \sum_{i=1}^{n} \langle \Phi(x_{1}) \dots G_{a} \Phi(x_{i}) \dots \Phi(x_{n})\rangle \delta (x-x_{i})
+\end{multline}
+Окончательно общий вид тождеств Уорда выглядит следующим образом:
+\begin{equation}
+  \label{eq:207}
+  \partial_{\mu}\langle j^{\mu}_{a}\Phi(x_{1}) \dots \Phi(x_{n})\rangle=-i\sum_{i=1}^{n}\delta (x-x_{i}) \langle\Phi(x_{1})\dots G_{a} \Phi(x_{i})\dots \Phi(x_{n})\rangle
+\end{equation}
+Рассмотрим некоторые примеры, которые понадобятся нам для конформной теории. Мы используем полученный нами явный вид генераторов \eqref{eq:169}.
+
+Тождество Уорда для трансляций:
+\begin{equation}
+  \label{eq:208}
+  \partial_{\mu}\langle T^{\mu}_{\nu} X\rangle =-i \sum_{i} \delta(x-x_{i}) \frac{\partial}{\partial x_{i}^{\nu}} \langle X \rangle
+\end{equation}
+Теперь рассмотрим вращения. Если тензор энергии-импульса симметризован (это можно сделать в большинстве случаев), то отвечающий вращениям ток дается выражением
+\begin{equation}
+  \label{eq:209}
+  j^{\mu\nu\rho}=T^{\mu\nu}x^{\rho}-T^{\mu\rho}x^{\nu}.
+\end{equation}
+Тогда тождество Уорда может быть записано в виде
+\begin{equation}
+  \label{eq:210}
+  \partial_{\mu}\langle (T^{\mu\nu}x^{\rho}-T^{\mu\rho}x^{\nu}) X\rangle=\sum_{i }\delta(x-x_{i}) \left( (x^{\nu}_{i}\partial^{\rho}_{i}-x^{\rho}_{i}\partial^{\nu}_{i})\langle X\rangle-i S^{\nu\rho}_{i}\langle X\rangle\right).
+\end{equation}
+Его можно упростить с использованием тождества для трансляций \eqref{eq:208}:
+\begin{equation}
+  \label{eq:211}
+  \langle (T^{\rho\nu}-T^{\nu\rho}) X\rangle=-i \sum_{i} \delta(x-x_{i}) S^{\nu\rho}_{i}\langle X\rangle.
+\end{equation}
+Тензор энергии-импульса в квантовой теории симметричен в корреляционных функциях, если его положение не совпадает с положениями других полей в корреляторе.
+
+Наконец, для масштабных преобразований ток имеет вид $T^{\mu}_{\nu}x^{\nu}$, действие генератора дается выражением \eqref{eq:181} и тождества Уорда выглядят так:
+\begin{equation}
+  \label{eq:212}
+  \partial_{\mu}\langle T^{\mu}_{\nu} x^{\nu} X\rangle=-\sum_{i} \delta(x-x_{i}) \left( x^{\nu}_{i}\frac{\partial}{\partial x^{\nu}_{i}} \langle X\rangle+\Delta_{i} \langle X\rangle\right) 
+\end{equation}
+Его тоже можно упростить:
+\begin{equation}
+  \label{eq:213}
+  \langle T^{\mu}_{\mu} X \rangle = -i \sum_{i} \delta(x-x_{i}) \Delta_{i}\langle X\rangle
+\end{equation}
+
+\subsection{Тождества Уорда в двумерной конформной теории}
+\label{sec:ward-2d-cft}
+В прошлой лекции мы получили общий вид тождеств Уорда для трансляций, поворотов и масштабных преобразований. Выпишем их здесь.
+\begin{eqnarray}
+  \label{eq:236}
+  \partial_{\mu}\langle T^{\mu}_{\nu} X\rangle = -\sum_{i} \delta(x-x_{i}) \partial_{\nu}^{(i)}\langle X\rangle\\
+  \langle (T^{\mu\nu}-T^{\nu\mu}) X\rangle =i\sum_{i}\delta(x-x_{i}) S^{\mu\nu}_{(i)}\langle X\rangle\\
+  \langle T^{\mu}_{\mu} X\rangle=-\sum_{i}\delta(x-x_{i}) \Delta_{(i)} \langle X\rangle
+\end{eqnarray}
+Прежде чем мы начнем переписывать тождества в комплексных координатах обсудим следующий вспомогательный математический факт: для голоморфных (антиголоморфных) функций можно использовать следующее представление для $\delta$-функции:
+\begin{equation}
+  \label{eq:237}
+  \delta(x)=\frac{1}{\pi} \bar \partial \frac{1}{z} = \frac{1}{\pi}\partial \frac{1}{\bar z}
+\end{equation}
+Заметим, что
+\begin{equation}
+  \label{eq:238}
+  \int_{M} d^{2}x \partial_{\mu}F^{\mu}=\int_{\partial M} d\xi_{\mu} F^{\mu}=\frac{1}{2i} \oint_{\partial M} (-dz F^{\bar z}+d\bar z F^{z})
+\end{equation}
+Для голоморфной функции
+\begin{equation}
+  \label{eq:239}
+  \frac{1}{\pi}\int_{M} d^{2}x \bar \partial\left( \frac{f(z)}{z}\right)=\frac{1}{2\pi i} \int_{\partial M} dz \frac{f(z)}{z}=f(0)=\int_{M} d^{2}x \delta(x) f(z)
+\end{equation}
+Теперь перепишем тождества Уорда \eqref{eq:236} в комплексных координатах:
+\begin{eqnarray}
+  \label{eq:240}
+  2\pi \partial \langle T_{\bar z z } X\rangle +2\pi \bar \partial \langle T_{zz}X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X \rangle\\
+  2\pi \partial \langle T_{\bar z \bar z } X\rangle +2\pi \bar \partial \langle T_{z\bar z}X\rangle = -\sum_{i} \bar \partial \frac{1}{\bar z-w_{i}} \partial_{\bar w_{i}} \langle X \rangle\\
+  2 \langle T_{z\bar z} X 1\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) \Delta_{i} \langle X\rangle\\
+  -2 \langle T_{z\bar z} X 1\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) s_{i} \langle X\rangle\\
+\end{eqnarray}
+Если сложить и вычесть два последних равенства и вспомнить определение $h, \bar h$, то получим
+\begin{eqnarray}
+  \label{eq:241}
+  2\pi \langle T_{\bar z z} X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}} h_{i} \langle X\rangle\\
+  2\pi \langle T_{z \bar z} X\rangle = -\sum_{i}  \partial \frac{1}{\bar z-\bar w_{i}} \bar h_{i} \langle X\rangle
+\end{eqnarray}
+Введем обозачения
+\begin{eqnarray}
+  \label{eq:242}
+  T=-2\pi T_{zz}\\
+  \bar T = -2 \pi T_{\bar z \bar z},
+\end{eqnarray}
+и подставим уравнения \eqref{eq:241} в первые два уравнения \eqref{eq:240}:
+\begin{eqnarray}
+  \label{eq:243}
+  \bar \partial \left( \langle T X\rangle -\sum_{i} \left( \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X\rangle + \frac{h_{i}}{(z-w_{i})^{2}} \langle X\rangle \right) \right) =0\\
+  \partial \left( \langle \bar T X\rangle -\sum_{i} \left( \frac{1}{\bar z-\bar w_{i}} \partial_{\bar w_{i}} \langle X\rangle + \frac{\bar h_{i}}{(\bar z-\bar w_{i})^{2}} \langle X\rangle \right) \right) =0
+\end{eqnarray}
+То есть выражения в скобках (анти)голоморфны. Следовательно
+\begin{equation}
+  \label{eq:244}
+  \langle T X\rangle =\sum_{i} \left( \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X\rangle + \frac{h_{i}}{(z-w_{i})^{2}} \langle X\rangle \right) +\mbox{регулярные члены}
+\end{equation}
+Это пример операторного разложения, которое мы будем обсуждать далее.
+
+Заметим, что вариация коррелятора при конформных преобразованиях дается тензором энергии-импульса:
+\begin{equation}
+  \label{eq:245}
+  \delta_{\epsilon}\langle X\rangle =\int_{M} d^{2}x \partial_{\mu} \langle T^{\mu\nu}(x)\epsilon_{\nu}(x) X \rangle
+\end{equation}
+В комплексных координатах она перепишется так:
+\begin{equation}
+  \label{eq:246}
+  \delta_{\epsilon,\bar \epsilon} \langle X\rangle = \frac{1}{2\pi i} \oint_{C} dz \epsilon(z) \langle T(z) X\rangle +\frac{1}{2\pi i} \oint_{C}  d\bar z \bar \epsilon(\bar z) \langle \bar T(\bar z) X\rangle
+\end{equation}
+Здесь интеграл берется по контуру, внутри которого находятся все аргументы $X$.
+Вообще говоря, это выражение для вариации верно для коррелятора любых полей, не только примарных.
+
+Применимость тождеств Уорда основывается на регулярности тензора энергии-импульса.
+Он должен быть везде хорошо определен.
+В частности, $T(0)$ должен быть конечен.
+Кроме того, если вычислить вариацию постоянного поля в точке $z=\infty$:
+\begin{equation}
+  \label{eq:247}
+  \delta_{\epsilon} \langle 1\rangle =-\frac{1}{2\pi i} \oint_{C}dz \epsilon(z) \langle T(z)\rangle =0
+\end{equation}
+где контур обходит точку $\infty$. Для специальных конформных преобразований $\epsilon(z)\sim z^{2}$, поэтому $T(z)\sim z^{-4},\quad z\to \infty$.
+
+\subsection{Алгебра локальных полей. Операторное разложение}
+\label{sec:ope}
+
+В набор локальных полей теории входят не только те поля, которые входят в плотность лагранжиана, но и их производные, произведения и так далее.
+Мы предполагаем, что набор локальных полей $A$ является полным, то есть существует некий базис $\{ A_{j}\}$, по которому можно разложить любое поле. Локальные поля образуют линейное пространство.
+
+Кроме того, мы предполагаем, что имеет место операторное разложение
+\begin{equation}
+  \label{eq:248}
+  A_{i}(x)A_{j}(y) =\sum_{k} C^{k}_{ij} (x,y) A_{k}(y),
+\end{equation}
+здесь $C_{ij}^{k}(x,y)$ -- функция. Равенство \eqref{eq:248} надо понимать в смысле корреляционных функций
+\begin{equation}
+  \label{eq:249}
+  \langle A_{i}(x) A_{j}(y) X\rangle = \sum_{k} C^{k}_{ij} (x,y) \langle A_{k}(y) X\rangle.
+\end{equation}
+Тогда набор локальных полей образует алгебру.
+
+Рассмотрим четырехточечную функцию и воспользуемся операторным разложением \eqref{eq:248}:
+\begin{equation}
+  \label{eq:250}
+  \langle A_{1}(x_{1}) A_{2}(x_{2}) A_{3}(x_{3}) A_{4}(x_{4}) \rangle =\sum_{k,l} C^{k}_{12} (x_{1}-x_{2}) D_{kl}(x_{2}-x_{4}) C^{l}_{34}(x_{3}-x_{4}) 
+\end{equation}
+Здесь мы воспользовались трансляционной инвариантностью, а также ввели обозначение для пропагатора
+\begin{equation}
+  \label{eq:251}
+  \langle A_{i}(x_{i}) A_{j}(x_{j}) \rangle =D_{ij}(x_{i}-x_{j}).
+\end{equation}
+Однако операторным разложением можно воспользоваться и в другом порядке, тогда для четырехточечной функции получим:
+\begin{equation}
+  \label{eq:252}
+  \langle A_{1}(x_{1}) A_{2}(x_{2}) A_{3}(x_{3}) A_{4}(x_{4}) \rangle =\sum_{k,l} C^{k}_{13} (x_{1}-x_{3}) D_{kl}(x_{3}-x_{4}) C^{l}_{24}(x_{2}-x_{4})   
+\end{equation}
+Приравняв правые части уравнений \eqref{eq:252},\eqref{eq:250} можно получить систему уравнений на коэффициенты $C^{k}_{ij}$.
+Если решить эти уравнения, то в принципе можно вычислять любые корреляторы, если известен набор полей и их конформных размерностей.
+Такой подход называется конформным бутстрапом.
+
+Корреляционные функции имеют особенности при совпадении положений полей. Именно характер этих особенностей важен при описании критического поведения (критические индексы и т.п.).
+Для произведения $T$ и примарного поля $\varphi$ с конформными размерностями $h,\bar h$ имеет место операторное разложение \eqref{eq:244}:
+\begin{eqnarray}
+  \label{eq:253}
+  T(z) \varphi(w,\bar w)\sim \frac{h}{(z-w)^{2}} \varphi(w,\bar w)+\frac{1}{z-w} \partial_{w} \varphi(w,\bar w)\\
+  \bar T(\bar z) \varphi(w,\bar w)\sim \frac{\bar h}{(\bar z-\bar w)^{2}} \varphi(w,\bar w)+\frac{1}{\bar z-\bar w} \partial_{\bar w} \varphi(w,\bar w)  
+\end{eqnarray}
+
+\subsection{Свободный бозон}
+\label{sec:free-boson}
+
+В качестве примера конформной теории рассмотрим свободное бозонное поле $\varphi$. Действие имеет вид
+\begin{equation}
+  \label{eq:254}
+  S=\frac{1}{2} g \int d^{2}x \partial_{\mu}\varphi \partial^{\mu}\varphi,
+\end{equation}
+а пропагатор дается равенством
+\begin{equation}
+  \label{eq:255}
+  \langle\varphi(x) \varphi(y)\rangle =-\frac{1}{4\pi g} \ln (x-y)^{2}+\text{const}
+\end{equation}
+В комплексных координатах пропагатор запишется следующим образом:
+\begin{equation}
+  \label{eq:256}
+  \langle \varphi(z,\bar z) \varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \left( \ln(z-w) + \ln(\bar z -\bar w)\right) +\text{const}
+\end{equation}
+Дифференцируя получаем
+\begin{eqnarray}
+  \label{eq:257}
+  \langle\partial_{z} \varphi(z,\bar z) \partial_{w}\varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \frac{1}{(z-w)^{2}}\\
+  \langle\partial_{\bar z} \varphi(z,\bar z) \partial_{\bar w}\varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \frac{1}{(\bar z-\bar w)^{2}}  
+\end{eqnarray}
+То есть имеет место операторное разложение полей $\partial \varphi$:
+\begin{equation}
+  \label{eq:259}
+  \partial \varphi(z) \partial \varphi(w) \sim -\frac{1}{4 \pi g} \frac{1}{(z-w)^{2}}
+\end{equation}
+
+Тензор энергии-импульса:
+\begin{equation}
+  \label{eq:258}
+  T_{\mu\nu}=g \left(\partial_{\mu}\varphi \partial_{\nu} \varphi -\frac{1}{2} \eta_{\mu\nu}\partial_{\rho}\varphi \partial^{\rho} \varphi \right)
+\end{equation}
+После квантования получаем для оператора $T(z)$ следующее выражение:
+\begin{equation}
+  \label{eq:260}
+  T(z) =-2\pi g :\partial \varphi \partial \varphi : =-2\pi g \lim_{w\to z} \left(\partial \varphi(z) \partial \varphi(w) -\langle\partial \varphi(z) \partial \varphi(w)\rangle\right)
+\end{equation}
+Теперь мы можем вычислить операторное разложение тензора энергии-импульса и локального поля $\partial \varphi$:
+\begin{equation}
+  \label{eq:261}
+  T(z)\partial \varphi(w)=-2\pi g :\partial \varphi(z) \partial \varphi(z): \partial \varphi(w) \sim -4\pi g:\partial \varphi(z)  \partial \overbracket{ \varphi(z): \partial \varphi } (w) \sim \frac{\partial \varphi (z)}{(z-w)^{2}}
+\end{equation}
+Для вычисления мы использовали теорему Вика (см. \cite{vasiliev1998}, \cite{difrancesco1997cft}). Раскладывая в ряд по $(z-w)$ получаем окончательно для сингулярной части операторного разложения
+\begin{equation}
+  \label{eq:262}
+  T(z) \partial \varphi(w) \sim \frac{\partial \varphi(w) }{(z-w)^{2}} +\frac{\partial_{w}^{2} \varphi(w)}{z-w}
+\end{equation}
+Теперь мы видим, что поле $\partial \varphi$ -- примарное, с конформной размерностью $h=1$.
+
+Аналогично вычислим операторное разложение $T$  с самим собой.
+\begin{multline}
+  \label{eq:263}
+  T(z) T(w) =4 \pi^{2}g^{2}:\partial \varphi(z) \partial \varphi(z): :\partial \varphi(w)\partial \varphi(w): \\
+  \sim \frac{1/2}{(z-w)^{4}} -\frac{4\pi g:\partial \varphi(z) \partial \varphi(w):}{(z-w)^{2}} \\
+  \sim \frac{1/2}{(z-w)^{4}}+ \frac{2T(w)}{(z-w)^{2}} +\frac{\partial T(w)}{z-w}
+\end{multline}
+
+\subsection{Центральный заряд. Алгебра Вирасоро}
+\label{sec:virasoro}
+
+В силу обсуждения после формулы \eqref{eq:247}, ренормгруппового анализа \ref{c-theorem} и вычисления функции Швингера  \eqref{eq:221} мы имеем следующий общий вид операторного разложения для $T(z)T(w)$:
+\begin{equation}
+  \label{eq:264}
+  T(z)T(w) \sim \frac{c/2}{(z-w)^{4}}+ \frac{2T(w)}{(z-w)^{2}} +\frac{\partial T(w)}{z-w}
+\end{equation}
+Здесь $c$ -- параметр теории, называемый центральным зарядом.
+Он зависит от физической природы теории и не определяется из соображений конформной инвариантности.
+В теории свободного бозона $c=1$, для фермиона $c=1/2$.
+Член $\frac{c/2}{(z-w)^{4}}$ называется аномальным.
+Если этого члена нет, то $T$--квазипримарное поле c $h=2$.
+
+Сравнивая выражение \eqref{eq:264} и \eqref{eq:221} мы видим, что константа $A$ в функции Швингера
+\begin{equation}
+  \label{eq:265}
+  A=\frac{c}{4\pi^{2}}
+\end{equation}
+Покажем, как преобразуется тензор энергии-импульса при конформных преобразованиях. Используем формулу \eqref{eq:246}:
+\begin{multline}
+  \label{eq:266}
+  \delta_{\epsilon} T(w) =-\frac{1}{2\pi i} \oint_{C} dz \epsilon(z) T(z) T(w) =-\frac{1}{12} c \partial_{w}^{3}\epsilon(w) -2 T(w) \partial_{w} \epsilon(w) -\epsilon(w) \partial_{w}T(w) 
+\end{multline}
+Соответствующее конечное преобразование $z\to w(z)$ имеет вид
+\begin{eqnarray}
+  \label{eq:267}
+  T\to T'(w) =\left(\frac{dw}{dz}\right)^{-2} \left(T(z) -\frac{c}{12} \left\{ w,z\right\}\right)\\
+  \left\{ w,z\right\}=\frac{\left(\frac{d^{3}w}{dz^{3}}\right) } {\frac{dw}{dz}} -\frac{3}{2}\left(\frac{\frac{d^{2}w}{dz^{2}}}{\frac{dw}{dz}}\right)^{2}
+\end{eqnarray}
+В качестве упражнения предлагаем проверить это выражение обратным переходом к инфинитезимальному преобразованию.
+
+Разложим $T(z)$ в ряд Лорана.
+\begin{eqnarray}
+  \label{eq:268}
+  T(z)=\sum_{n\in \mathbb{z}}z^{-n-2}L_{n}\\
+  T(z)=\sum_{n\in \mathbb{z}}\bar z^{-n-2}\bar L_{n}
+\end{eqnarray}
+При масштабном преобразовании $z\to z/\lambda$ оператор $T(z)\to \lambda^{2}T(z/\lambda)$, соответственно компоненты $L_{-n}\to \lambda^{n}L_{-n}$.
+\begin{equation}
+  \label{eq:269}
+  L_{n}=\oint \frac{dz}{2\pi i} z^{n+1} T(z)
+\end{equation}
+Выведем коммутационные соотношения для операторов $L_{n}$:
+\begin{equation}
+  \label{eq:270}
+  [L_{n},L_{m}]=\left( \oint \frac{dz}{2\pi i}\oint \frac{dw}{2\pi i}-\oint \frac{dw}{2\pi i}\oint \frac{dz}{2\pi i}\right) z^{n+1} T(z)w^{m+1}T(w)
+\end{equation}
+Используем операторное разложение \eqref{eq:264}:
+\begin{multline}
+  \label{eq:271}
+  [L_{n},L_{m}]=\oint \frac{dz}{2\pi i} \oint \frac{dw}{2\pi i} z^{n+1} w^{m+1}\left( \frac{c/2}{(z-w)^{4}} +\frac{2T(w)}{(z-w)^{2}}+\frac{\partial T(w) }{z-w} +\mbox{рег. члены}\right) =\\
+  \oint \frac{dw}{2\pi i} \left(\frac{c}{12} (n+1)n(n-1)w^{n-2}w^{m+1} + 2(n+1)w^{n}w^{m+1}T(w)+w^{n+1}w^{m+1}\partial T(w)\right)
+\end{multline}
+Интегрируем последний член по частям, внеинтегральный член зануляется, а под интегралом остается $(n-m)w^{n+m+1}T(w)$:
+\begin{equation}
+  \label{eq:272}
+    [L_{n},L_{m}]=\oint \frac{dw}{2\pi i} \left(\frac{c}{12} (n+1)n(n-1)w^{m+n-1}+ (n-m)w^{n+m+1}T(w)\right)
+\end{equation}
+Используя определение \eqref{eq:269} и вычисляя вычет подинтегрального выражения при $n=-m$, в итоге получаем коммутационное соотношение
+\begin{equation}
+  \label{eq:273}
+    [L_{n},L_{m}]=(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}
+\end{equation}
+Это коммутационные соотношения алгебры Вирасоро.
+
+Легко показать, что в результате действия оператора $L_{-n}$ на поле $\varphi$  с конформной размерностью $(h,\bar h)$ получается поле с размерностью $(h-n,\bar h)$.
+Все поля в теории разбиваются на конформные семейства, соответствующие примарным полям:
+\begin{equation}
+  \label{eq:274}
+  [\varphi]=\{L_{-n_{1}}L_{-n_{2}}\dots L_{-n_{N}}\bar L_{-m_{1}}\dots \bar L_{-m_{M}}\varphi\}
+\end{equation}
+Вычисление корреляторов вторичных полей сводится к корреляторам примарных. Алгебра локальных полей оказывается прямой суммой конформных семейств
+\begin{equation}
+  \label{eq:275}
+  \mathcal{A} =\bigoplus_{\alpha}[\varphi_{\alpha}]
+\end{equation}
+{\it Минимальными} называются теории с конечным числом примарных полей. Чтобы полностью задать такую теорию нужно определить примарные поля и их конформные размерности.
+
+\bibliography{2dqft}{}
+\bibliographystyle{utphys}
+
 \end{document}

### 2011-06-27 GeneralOverview/IntegrableSystems.tex
Lecture 5 minor changes

@@
 \newtheorem{statement}{Statement}
-\theoremstyle{definition} \newtheorem{Def}{Definition}
+\theoremstyle{definition} 
 \newcommand{\go}{\overset{\circ }{\frak{g}}}
@@
 Вычисление можно свести к решению уравнения, имеющего тот же вид, что и уравнения ренормгруппы в квантовой теории поля.
-Так как в данном случае пространство состояний бесконечномерное, то sl(2)-инвариантность гамильтониана не упрощает задачу так же сильно, как в случае спина 1/2.
+Из sl(2)-инвариантности гамильтониана следует, что собственные функции можно искать на пространстве однородных полиномов.
 
 Затем мы начинаем рассмотрение общей конструкции интегрируемых спиновых цепочек.
+Идея состоит в построении набора из N-1 операторов Q, коммутирующих с гамильтонианом и между собой.
+Трансфер-матрица -- это производящая функция таких операторов.
+Она дается следом по вспомогательному пространству от произведения операторов Лакса, действующих в тензорном произведении пространств, связанных с узлами и вспомогательного пространства.
+Оператор Лакса и трансфер-матрица зависят от спектрального параметра u.
+Коэффициенты разложения трансфер-матрицы по степеням спектрального параметра являются операторами, коммутирующими с гамильтонианом.
+
 \section{Лекция 4. 3 марта 2011}
+
+Рассматриваем, какие требования на трансфер-матрицу и оператор Лакса накладывает sl(2)-инвариантность и требования коммутативности операторов Q.
+Оказывается, что трансфер-матрицы при разных значениях спектрального параметра должны коммутировать.
+Оператор Лакса должен являться оператором Казимира алгебры sl(2) и удовлетворять RLL-соотношениям, из которых следует коммутативность трансфер- матрицы.
+
+В RLL-соотношения входит новый объект -- R-матрица, которая удовлетворяет уравнению Янга-Бакстера.
+Мы используем R-матрицу, представляющую собой сумму спектрального параметра (умноженного на единичный оператор) и оператора перестановки.
+Для такого вида R-матрицы мы получаем выражение для L-оператора.
 
@@
 
+Теперь нам необходимо проверить коммутативность трансфер-матрицы. 
+Сначала мы проверяем ее для случая двух узлов.
+В этом случае условие коммутативности легко следует из RLL-соотношений.
+Для большего числа узлов можно доказать из коммутативности L-операторов для разных узлов при различных значениях спектрального параметра.
+
+После того, как мы доказали необходимые свойства трансфер-матрицы, мы можем ввести оставшиеся ингредиенты алгебраического анзаца Бете.
+Для этого запишем трансфер-матрицу в виде матрицы 2x2 с компонентами A, B, C, D.
 \section{Лекция 6. 17 марта 2011}

### 2011-08-21 AffineLieAlgebras/Mathematica/testd.m
Minor changes + some bibliography additions

@@ -2,6 +2,57 @@ AppendTo[$Path,"/home/anton/study/2011/Articles/AffineLieAlgebras/Mathematica/"]
 
 <<datastructures.m;
 
+ourBranching[b2,makeFiniteRootSystem[{makeFiniteWeight[{1,1}]}]][makeFiniteWeight[{2,1}]]
+
+Out[11]= ourBranching[finiteRootSystem[2, 2, 
+ 
+>      {finiteWeight[2, {1, -1}], finiteWeight[2, {0, 1}]}], 
+ 
+>     makeFiniteRootSystem[finiteWeight[2, {1, 1}]]][finiteWeight[2, {2, 1}]]
+
+Throw::nocatch: 
+   Uncaught Throw[orbitWithEps __TODO__: GOT UNEXPECTED VALUE True INSTEAD OF
+      False, assertion exception] returned to top level.
+
+Out[9]= Hold[Throw[orbitWithEps __TODO__: GOT UNEXPECTED VALUE True INSTEAD\
+ 
+>      OF False, assertion exception]]
+
+b2=makeSimpleRootSystem[B,2]
+
+weightSystem[b2][makeFiniteWeight[{2,1}]]
+
+positiveRoots[b2]
+
+Out[7]= {{finiteWeight[2, {2, 1}]}}
+
+       Expect["Weights of [2,1] module of B2",True, weightSystem[b2][makeFiniteWeight[{2,1}]]==
+	      {{makeFiniteWeight[{2,1}]},
+	      {makeFiniteWeight[{1,0}],makeFiniteWeight[{1,1}],makeFiniteWeight[{2,0}]},
+	      {makeFiniteWeight[{0,0}]}}]]
+
+
+Throw::nocatch: 
+   Uncaught Throw[Weights of [2,1] module of B2: GOT UNEXPECTED VALUE False
+      INSTEAD OF True, assertion exception] returned to top level.
+
+Out[5]= Hold[Throw[Weights of [2,1] module of B2: GOT UNEXPECTED VALUE False\
+ 
+>      INSTEAD OF True, assertion exception]]
+
+makeAffineWeight[{1,2,3},1,1][finitePart]
+
+makeFiniteWeight[{1,2,3}][finitePart]
+
+Out[4]= finiteWeight[3, {1, 2, 3}][finitePart]
+
+Out[3]= finiteWeight[3, {1, 2, 3}]
+
[…]

### 2011-08-21 AffineLieAlgebras/SLE/article.tex

\documentclass[12pt]{article}
\usepackage{amssymb}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\usepackage{amsmath}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{multicol}
\usepackage{color}
\usepackage{graphicx}
\usepackage{hyperref}

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\tr}{\hat\triangleright} \newcommand{\trc}{\triangleright}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

\begin{document}

\title{Algebraic properties of CFT coset construction and Schramm-Loewner evolution}
\author{A A Nazarov$^{1,2}$\\
  {\small $^1$ Theoretical Department, SPb State University}\\
  {\small 198904, Sankt-Petersburg, Russia}\\
  {\small$^{2}$ Chebyshev Laboratory,}\\
  {\small Department of Mathematics and Mechanics, SPb State University}\\
  {\small 199178, Saint-Petersburg, Russia}\\
  {\small email: antonnaz@gmail.com}}

\maketitle

\begin{abstract}
  Schramm-Loewner evolution appears naturally as the scaling limit of interfaces in lattice models at critical point. Critical behavior of these models can be described by minimal models of conformal field theory.

  SLE with additional Brownian motion on Lie group $G$ was proposed as generalization to WZNW models of CFT. Martingale property of SLE observables is related to Virasoro null vector conditions for CFT fields and KZ-equations for correlation functions.

  Minimal models can be obtained from WZNW models by coset construction. Then it is natural to study SLE with additional Brownian motion on coset space $G/H$. We discuss algebraic properties of coset fields and correlation functions which correspond to SLE observables. 
\end{abstract}

\section{Introduction}
\subsection{Schramm-Loewner evolution}
To remind of Schramm-Loewner evolution we first describe simple example.

Consider Ising model on triangular lattice on upper half plane (see Fig. \ref{fig:sle}). We impose following boundary condition: all spins are down on one half of the boundary and all spins are up on another half. Then in any configuration we get an interface delimiting two clusters and connecting zero and infinity.

\begin{figure}[h]
  \centering{
    \includegraphics[height=25mm]{explore.pdf}
    \caption{SLE -- continuous limit of interfaces}}
  \label{fig:sle}
\end{figure}

Next we consider continuous limit of lattice model. Interface in random configuration of the model tends to random curve. We can think of this curve as of trace of stochastic process which satisfy some stochastic equation.

In papers [Smirnov, Schramm ... ] it was shown that this equation is
\begin{equation*}
  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} \quad \text{or} \quad       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}
\end{equation*}
The stochastic process which satisfy this equation is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.

Here $g_{t}(z)$ is a conformal map from $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$ to $\mathbb{H}$ (see Fig. \ref{fig:sle2}).
\begin{figure}[h]
  \centering{
    \includegraphics[width=50mm]{loewner.pdf}
    \caption{Conformal map}}
  \label{fig:sle2}
\end{figure}

Schramm-Loewner evolution provides conformally-invariant probability measure on trajectories $\gamma_{t}$ in $\mathbb{H}$.

\subsection{Correspondence between SLE and minimal models of CFT}

Now we can look at the observables in the presence of SLE trace. Expectation value of lattice observable on upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace up to some time $t$ multiplied by the probability of this trajectory.

Consider lattice observable $\mathcal{O}$, then it expectation value can be calculated as
\begin{equation*}
  \prec \mathcal{O} \succ_{\mathbb{H}}=\mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=\sum_{\gamma_{t}} P\left[C_{\gamma_{t}}\right] \prec \mathcal{O} \succ_{\gamma_{t}}
\end{equation*}
Since lattice observable  $\prec \mathcal{O} \succ_{\mathbb{H}}$ does not depend on $t$, hence $\prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale.

In continuous limit lattice observable tends to CFT correlation function. Since we consider the theory with the boundary, CFT correlation function has following form:
\begin{equation*}
  \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}=
  \frac{\left< ^{g_{t}}\mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
\end{equation*}
We assume that $\mathcal{F}$ contains some set of primary fields $\phi_{\lambda_{i}}$ with conformal weights $\lambda_{i}$. Also we have boundary condition changing operators  $\phi$ at the tip of SLE trace and in the infinity.  We can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite this expression in upper half plane:

\begin{equation}
  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
  \label{eq:1}
\end{equation}

Now we want to consider evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
\begin{equation*}
  -\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}.
\end{equation*}
For transformation of primary fields $\phi_{\lambda_{i}}$ we have 
\begin{equation}
  \label{eq:2}
  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\phi_{\lambda_{i}}(w_{i}) 
\end{equation}
We denote generator of this transform by $\mathcal{G}_{i}$.

Continuous limit in critical point leads to CFT correlation function

Now for expectation value of martingale we have this expression.
\begin{equation*}
  \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=    \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t+dt}}\right], \quad \mathbb{E}\left[d \prec\mathcal{O}\succ_{\gamma_{t}}\right]=0
\end{equation*}

Now we use Ito calculus to calculate increment of our correlation function. It should be zero so we get the equation:
\begin{equation*}
  \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{-h_{i}}\right)\mathbb{E}\left[d 
    \mathcal{F}_{\mathbb{H}_{t}}\right]=\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\mathbb{E}\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}
\end{equation*}
Then use explicit form of conformal map and obtain
\begin{equation*}
  \left( \sum_{i}\left[-\frac{2h_{i}}{w_{i}^{2}} +\frac{2}{w_{i}}\partial_{w_{i}}\right]+\frac{\kappa}{2}\sum_{i,j}\partial_{w_{i}} \partial_{w_{j}}\right)\mathcal{F}(\left\{z_{i}\right\})=0
\end{equation*}

We can rewrite it as the necessary condition on b.c.c. operator $\phi$:
\begin{equation*}
  (L_{-2}-\frac{\kappa}{2}L_{-1}^{2})\phi=0 \Longrightarrow \phi \left|0\right>  \text{has level 2 null state}, \phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}
\end{equation*}
We can see that it can be rewritten as the action of Virasoro generators. Since we have arbitrary observable, this equation is equivalent to the requirement for boundary condition changing operator to have level two null state. 
In case of minimal model we can see that boundary condition chaining operator is primary field $\phi_{1,2}$ or $\phi_{2,1}$.

\section{SLE and WZNW models}
\label{sec:sle-wzw-models}
Now we want to generalize this analysis to rational conformal field theories. First we consider Wess-Zumino-Novikov-Witten model.
\subsection{WZNW models}

 The action for this model can be written in terms of map $g:\mathbb{C}\cup \{\infty\}\sim S^{2}\to G$ from complex plane with infinity or two-sphere to some Lie group $G$:
\begin{multline}
  S=-\frac{k}{8\pi}\int d^2x\; \mathcal{K} (g^{-1}\partial^{\mu}g, g^{-1} \partial_{\mu}g)  
  \\
  - \frac{k }{24\pi^{2}} \int_{B}\epsilon_{ijk} \mathcal{K}\left(
    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i},\left[
      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right]\right) d^3y
\end{multline}
The first term is just non-linear sigma-model.

 Here $\mathcal{K}$ is Killing form on Lie algebra $\gf$ of Lie group $G$. The second term is written in terms of continuation from two-sphere $S^{2}$ to three-dimensional manifold $B$ which has two-sphere as the boundary. Since this continuation is non-unique we get the requirement for $k$ to be integer.

Currents of this model have following form:
  \begin{eqnarray}
    J(z)= -k \partial_zg g^{-1}
    \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
  \end{eqnarray}

Model possess gauge invariance under gauge transformations:
  \begin{equation*}
    g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z),
  \end{equation*}
  where $\Omega,\;\bar \Omega \in G$.
Here $\Omega$ and $\bar \Omega$ are independent.

If we consider infinitesimal gauge transformation $\Omega=1+\omega$ we get Ward identities:
  \begin{equation}
    \label{eq:87}
    \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
    \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
  \end{equation}

 Then we can get operator product expansion for currents. 
 \begin{equation}
   \label{eq:3}
   <J\phi>\sim \dots
 \end{equation}

If we expand currents to modes
\begin{equation*}
  J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n 
\end{equation*}
and use operator product expansion \eqref{eq:3} we get commutation relations of affine Lie algebra $\gfh$:
\begin{equation}
  \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0} 
\end{equation}

This model has conformal invariance which can be seen from 
Sugawara construction. This is way to embed Virasoro algebra into the universal enveloping algebra of affine Lie algebra $\gfh$ ($Vir\subset U(\gfh)$):
\begin{equation}
  \label{eq:4}
  L_n=\frac{1}{2(k+h^v)}\sum\limits_a\sum\limits_m:J^a_m J^a_{n-m}:
\end{equation}

Full chiral algebra of the model is semidirect product of affine and Virasoro algebra $\gfh \ltimes Vir$.

Its commutation relations are
  \begin{equation}
    \label{eq:92}
    \begin{aligned}
      \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
      \left[L_n,J^a_m\right]=-mJ^a_{n+m}
    \end{aligned}
  \end{equation}

Primary fields  $\phi_{\lambda}$ are labeled by highest weights of affine Lie algebra representations. Here we see how Virasoro and affine Lie algebra generators act on primary fields:
  \begin{equation*}
    \begin{aligned}
      & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>  \quad    J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
      & L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>=h_{\lambda} \left|\phi_{\lambda}\right>
    \end{aligned}
  \end{equation*}

\subsection{SLE and WZNW models}
Now we want to study Schramm-Loewner evolution in WZNW-models.

Similarly to minimal models we consider observable
\begin{equation*}
  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
  \frac{\left<\phi_{\Lambda}(z_{t}) \phi_{\lambda_1}(z_{1}) \dots \phi_{\lambda_n}(z_{n}) \phi_{\lambda^{*}_1}(\bar z_{1}) \dots \phi_{\lambda^{*}_n}(\bar z_{n})
      \phi_{\Lambda^{*}}(\infty)\right>}{\left<\phi_{\Lambda}(z_{t})\phi_{\Lambda^{*}}(\infty)\right>}
\end{equation*}
Again we can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite it on the whole upper half-plane. 
\begin{equation*}
  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
\end{equation*}

Consider evolution from $t$ to $t+dt$.
First factor gives us $-\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}$.

 For fields we have
\begin{equation*}
  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i})
\end{equation*}
When we consider fields we need to add random gauge transformation (random motion in $G$) to stochastic evolution \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}:
\begin{equation*}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)
\end{equation*}
Since we have boundary we are working with boundary CFT so we have only half of gauge transformations due to Cardy conditions.

\subsection{SLE martingales in WZNW models}
We use Ito calculus to get the equation from martingale condition:
\begin{equation*}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0
\end{equation*}
\begin{equation*}
  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{\lambda_{i}}}{(w_{i}-z)^{n}}-\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right);\quad \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}}
\end{equation*}
Again we can rewrite it as algebraic requirement for  field  which 
correspond to boundary condition changing operator.
\begin{equation*}
  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
\end{equation*}
is level two null state and if we act on this state with raising operators we should get zero.
\begin{equation*}
  J^{a}_{1} \left|\psi\right>=0, J^{a}_{2}\left|\psi\right>=0.
\end{equation*}
 We use commutation relations and get equations which connects parameters of random motion with level of affine Lie algebra representation.

We can see that $\kappa+\tau h^{v}=4$ and it is possible to derive additional relations connecting $\kappa, \tau, k$:
\begin{equation*}
  \kappa=\frac{2(h^{v}-2k)}{2h_{\Lambda}h^{v}-k},\quad \tau=\frac{8 h_{\Lambda}-2}{2h_{\Lambda}h^{v}-k}  \quad\text{for}\; k\neq 2h_{\Lambda}h^{v}
\end{equation*}
 Also we get some constraints on possible boundary condition changing operators. 
To get complete classification use Knizhnik-Zamolodchikov equations.

\section{Coset models}
\label{sec:coset-models}

\subsection{Gauged WZNW-models and coset construction}
Add gauge fields $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action:
\begin{multline*}
  S(g,A)=S_{WZNW}(g)+\\
  \frac{k}{4\pi}\int d^{2}z \left(\mathcal{K}(A, g^{-1}\bar \partial g)-\mathcal{K}(\bar A, (\partial g ) g^{-1})+\mathcal{K}(A,g^{-1}\bar A g)-\mathcal{K}(A,\bar A)\right)
\end{multline*}

Now current is
\begin{equation*}
  J_{(\gf,\af)}=-k\partial g g^{-1} -k g A g^{-1}
\end{equation*}

From Ward identities we get
\begin{equation*}
  \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{v}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
\end{equation*}
Remember that for WZNW current we have OPE $J_{\gf}^{a}(z)\phi_{i}(w)\sim \frac{-t^{a}_{i}\phi(w)}{z-w}$.
%% Commutation relations for current components are preserved.

Algebraic structure is connected with two affine Lie algebras $\gfh, \afh: \afh\subset\gfh$.

Virasoro generators are given by difference of Sugawara expressions:
\begin{equation*}
  L_{n}=L_{n}^{\gf}-L_{n}^{\af}
\end{equation*}

\subsection{Primary fields}

Primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$. But some pairs are equivalent. This equivalence is given by the action of simple currents $(J,\tilde{J})$ such that $h_{J}-h_{\tilde{J}}=0$.

Conformal weight of primary field
\begin{multline}
  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^v)}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
  \left|\phi_{\lambda}\right>=\\
  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^v)}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^v)}\right)\left|\phi_{(\mu,\nu)}\right>
\end{multline}

%% So $G/A$-coset theory is related to $\gf\oplus \bar{\af}$-theory.

It is possible to obtain analogues of KZ-equations:
\begin{equation*}
  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{v}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{v}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
\end{equation*}

\subsection{SLE on coset space}
For  $\gf\oplus \af$ WZNW-model we can write SLE generator of primary field transformation under stochastic evolution as
\begin{equation*}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)+\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
\end{equation*}
%% \begin{equation*}
%%   \mathcal{G}_{i}^{L,R}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)\pm\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
%% \end{equation*}

and get martingale condition
\begin{equation*}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0
\end{equation*}

which can be rewritten as the requirement for
\begin{equation*}
  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}
\end{equation*}
to be level two null-field.

\subsection{Parafermions}
$\mathbb{Z}(N)$ parafermions are equivalent to $SU(2)_{N}/U(1)$ coset theory.

Parafermionic field decomposes as
\begin{equation*}
  \Phi^{j}=\phi_{j}(z) \exp\left( -i \frac{j}{\sqrt{N}}\phi(z)\right)
\end{equation*}
where $\phi_{j}(z)$ is field of $SU(2)$-WZNW model with spin $j$, $\phi(z)$ -- $U(1)$ bosonic field.

For parafermionic current we have
\begin{equation*}
  \Psi^{\pm}=\frac{1}{\sqrt{N}} J^{\pm}\exp\left(\mp i \frac{1}{\sqrt{N}}\phi(z)\right)
\end{equation*}
%% Its action in terms of primary fields of $su(2)\oplus u(1)$ WZNW-model is equivalent to $J^{\pm}\pm \tilde{J}^{\pm}$.

Martingale condition can be rewritten as
\begin{equation*}
  \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[\Psi^{+}_{-1}\Psi^{-}_{-1}+\Psi^{-}_{-1}\Psi^{+}_{-1}\right]\right) \left|\Phi\right>=0
\end{equation*}
which coincides with the result of Santachiara [arXiv:0705.2749].

\subsection{Next steps}
\begin{itemize}
\item Act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations connecting $\kappa, \tau, k$. 
\item Use Knizhnik-Zamolodchikov equations to simplify them.
\item Get conditions on boundary condition changing operator
\item Compare these conditions with results of  the study of boundary states with fusion algebra (Verlinde formula for Cardy states)
\end{itemize}

\section{Conclusion}
\label{sec:conclusion}

\subsection{Conclusion}
\begin{itemize}
\item It is possible to match SLE observables and CFT correlators
\item Martingale conditions are equivalent to Verma module of affine Lie algebra having singular weights at level two.
\item Primary fields of $\gf\oplus \af$ WZNW-model with equivalence relations can be used to study coset theory
\item Study of martingale conditions in coset theory is parallel to the study of boundary states with fusion algebra
\end{itemize}

\subsection{Thank you for your attention!}

Now we want to generalize this analysis even further and study coset models of conformal field theory. This models can be realized as gauged Wess-Zumino-Novikov-Witten models. We add gauge fields taking values in subalgebra a of Lie algebra g. The term which describes interaction with gauge fields has this form. 
The current of this model is here. 
We have this expression for the product of gauge field and primary fields. Here hv is dual Coxeter number of Lie algebra h.
Remember that for Wess-Zumino-Witten model current we have this operator product expansion. So we see that algebraic structure is connected with the pair of algebras g and a. Virasoro generators are given by the difference of Sugawara expressions for this algebras. 
Primary fields are labeled by pairs of weights of algebra and subalgebra, but some pairs are equivalent. This equivalence relation is given by the action of simple currents corresponding to affine Lie algebras g and a such, that their conformal weights are equal. 
For conformal weight of primary fields we have this expression. 
One can also write analogues of Knizhnik-Zamolodchikov equations.

So for SLE transformation we get direct sum of random gauge transformation in algebras g and a. Martingale condition can be written in this form. So again we get algebraic relation on boundary condition changing operator.

We can compare this result with the simplest possible coset model su two divided by u one. It is parafermion theory. It is well-known that parafermionic field can be written as product of su two primary field and Vertex operator of bosonic field. 
Parafermionic current can be seen as the combination of su(2) and u(1) currents and the martingale equation from previous slide can be written in this form. This relation coincide with the relation which can be obtained from the study SLE in  parafermionic models.

Next steps in the study of SLE martingales for coset models  are the following. We need to act on the relation with raising operators and get relations which connects level of representation and parameters of random motion. Then we use Knizhnik-Zamolodchikov equations to rewrite the relations in simpler form and get conditions on possible boundary condition changing operators. 
Boundary states in coset models were actively studied. One of the ideas is to consider direct sum WZNW-model and use equivalence relations. This study is essentially the study representation of fusion algebra, Verlinde formula is one of key ingredients in this study. So we hope to compare the classification of boundary states obtained in this way with our condition on boundary condition changing operator.

Now we see that it is possible to match SLE observables and CFT correlation functions. Martingale conditions can be seen as the constraints on possible Verma modules of affine Lie algebra corresponding to boundary condition changing operator. This Verma module must have level two null state. 
We can use primary fields of direct sum WZNW model and equivalence relations to study coset models. 
Martingale conditions should be compared with the classification of boundary states with other methods.

Thank you for your attention.

\section{Introduction}
SLE for WZW models are actively studied. KZ-equations allow to show that certain functions are martingales. 
In coset models of CFT it is possible to write analogues of KZ equations from null vector conditions. 
Corresponding SLE should have natural interpretation in case of coset construction of minimal models.

SLE is interpreted as limit of interfaces in lattice models. So SLE observable should have the form of boundary correlation function with boundary condition changing operator inserted. There is some condition on spin of boundary condition changing operator in Kostya's paper.  Classification of boundary condition changing operators is given in papers in CFT folder.

What to do:
Simplest coset model: $su(2)_{1}\oplus su(2)_{1}/su(2)_{2}$ $k=1, c=1/2$.

Schramm-Loewner evolution is conformally-invariant probability measure on the continuous curves in complex domain. We work with upper half-plane. SLEs are limits of critical interfaces in lattice models such as Ising model, percolation, FK-model. 
SLE can be used to make a connection with boundary conformal field theory. Observables in presence of SLE (probabilities) are identified with certain correlators in BCFT.

Rational conformal field theories have description in terms of coset models. These models have geometric formulation as gauged WZNW models. Minimal models of CFT can be realized as coset models. So (at least) some of coset models can be seen as the limit of lattice models. 
\section{WZW-models and SLE}
\label{sec:wzw-models-sle}

$SLE_{\kappa,\tau}$ appears in WZW [cite: Gruzberg, Alekseev-Bytsko-Izurov]. Brownian motion on Lie group.

Boundary conditions. Boundary condition changing operators.

\section{Parafermions}
\label{sec:parafermions}

Parafermions are fields in coset $\hat{su}(2)/\hat{u}(1)$. Generalization of Brownian motion. Possible boundary conditions. D-branes.

\section{Coset models}
\label{sec:coset-models}

Boundary conditions??

Ishikava paper - method to get boundary operators.

Ising model - boundary condition changing operator should be known (find).

Generalizations of Brownian motion??

\section{Conclusion}
\label{sec:conclusion}

\bibliography{bibliography}{}
\bibliographystyle{utphys}

\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2011-08-21 AffineLieAlgebras/SLE/talk.tex

--- 2011-08-21 AffineLieAlgebras/SLE/article.tex
@@
-\documentclass[12pt]{article}
-\usepackage{amssymb}
+\documentclass{article}
+\begin{document}
+Hello!
+It's a pleasure for me to be here in Prague.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\usepackage{amsmath}
-\usepackage{amsmath,amssymb,amsthm}
-\usepackage{multicol}
-\usepackage{color}
-\usepackage{graphicx}
-\usepackage{hyperref}
+My talk is devoted to the correspondence between Schramm-Loewner evolution and conformal field theory.
 
-\newtheorem{statement}{Statement}
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{lemma}{Lemma}
-\newtheorem{mynote}{Note}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
-\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
-\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
-\newcommand{\co}[1]{\stackrel{\circ }{#1}}
-\newcommand{\pia}{\pi_{\mathfrak{a}}}
-\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
-\newcommand{\gf}{\mathfrak{g}}
-\newcommand{\af}{\mathfrak{a}}
-\newcommand{\aft}{\widetilde{\mathfrak{a}}}
-\newcommand{\afb}{\mathfrak{a}_{\bot}}
-\newcommand{\hf}{\mathfrak{h}}
-\newcommand{\hfb}{\mathfrak{h}_{\bot}}
-\newcommand{\pf}{\mathfrak{p}}
-\newcommand{\gfh}{\hat{\mathfrak{g}}}
-\newcommand{\afh}{\hat{\mathfrak{a}}}
-\newcommand{\bff}{\mathfrak{b}}
-\newcommand{\hfg}{\hf_{\gf}}
-
-\theoremstyle{definition} \newtheorem{Def}{Definition}
-\newcommand{\tr}{\hat\triangleright} \newcommand{\trc}{\triangleright}
-\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
-\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}
-
-\begin{document}
-
-\title{Algebraic properties of CFT coset construction and Schramm-Loewner evolution}
-\author{A A Nazarov$^{1,2}$\\
-  {\small $^1$ Theoretical Department, SPb State University}\\
-  {\small 198904, Sankt-Petersburg, Russia}\\
-  {\small$^{2}$ Chebyshev Laboratory,}\\
-  {\small Department of Mathematics and Mechanics, SPb State University}\\
-  {\small 199178, Saint-Petersburg, Russia}\\
-  {\small email: antonnaz@gmail.com}}
-
-\maketitle
-
-\begin{abstract}
-  Schramm-Loewner evolution appears naturally as the scaling limit of interfaces in lattice models at critical point.
-Critical behavior of these models can be described by minimal models of conformal field theory.
-
-  SLE with additional Brownian motion on Lie group $G$ was proposed as generalization to WZNW models of CFT.
-Martingale property of SLE observables is related to Virasoro null vector conditions for CFT fields and KZ-equations for correlation functions.
-
-  Minimal models can be obtained from WZNW models by coset construction.
-Then it is natural to study SLE with additional Brownian motion on coset space $G/H$.
-We discuss algebraic properties of coset fields and correlation functions which correspond to SLE observables.
-\end{abstract}
-
-\section{Introduction}
-\subsection{Schramm-Loewner evolution}
-To remind of Schramm-Loewner evolution we first describe simple example.
-
-Consider Ising model on triangular lattice on upper half plane (see Fig.
-\ref{fig:sle}).
-We impose following boundary condition: all spins are down on one half of the boundary and all spins are up on another half.
+First of all I need to remind you of Schramm-Loewner evolution.
+Consider Ising model on triangular lattice on upper half plane.
+Let we have spins down on one half of the boundary and spins up on another half.
 Then in any configuration we get an interface delimiting two clusters and connecting zero and infinity.
-
-\begin{figure}[h]
-  \centering{
-    \includegraphics[height=25mm]{explore.pdf}
-    \caption{SLE -- continuous limit of interfaces}}
-  \label{fig:sle}
-\end{figure}
-
 Next we consider continuous limit of lattice model.
-Interface in random configuration of the model tends to random curve.
-We can think of this curve as of trace of stochastic process which satisfy some stochastic equation.
-
-In papers [Smirnov, Schramm ... ] it was shown that this equation is
-\begin{equation*}
-  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} \quad \text{or} \quad       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}
-\end{equation*}
-The stochastic process which satisfy this equation is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.
-
-Here $g_{t}(z)$ is a conformal map from $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$ to $\mathbb{H}$ (see Fig. \ref{fig:sle2}).
-\begin{figure}[h]
-  \centering{
-    \includegraphics[width=50mm]{loewner.pdf}
-    \caption{Conformal map}}
-  \label{fig:sle2}
-\end{figure}
-
-Schramm-Loewner evolution provides conformally-invariant probability measure on trajectories $\gamma_{t}$ in $\mathbb{H}$.
-
-\subsection{Correspondence between SLE and minimal models of CFT}
-
+We can think of it as of stochastic process which satisfy this stochastic equation.
+Here gt or wt is conformal map which maps SLE trace up to time t to the boundary.
 Now we can look at the observables in the presence of SLE trace.
-Expectation value of lattice observable on upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace up to some time $t$ multiplied by the probability of this trajectory.
-
-Consider lattice observable $\mathcal{O}$, then it expectation value can be calculated as
-\begin{equation*}
-  \prec \mathcal{O} \succ_{\mathbb{H}}=\mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=\sum_{\gamma_{t}} P\left[C_{\gamma_{t}}\right] \prec \mathcal{O} \succ_{\gamma_{t}}
-\end{equation*}
-Since lattice observable  $\prec \mathcal{O} \succ_{\mathbb{H}}$ does not depend on $t$, hence $\prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale.
-
-In continuous limit lattice observable tends to CFT correlation function. Since we consider the theory with the boundary, CFT correlation function has following form:
-\begin{equation*}
-  \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
-  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}=
-  \frac{\left< ^{g_{t}}\mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
-\end{equation*}
-We assume that $\mathcal{F}$ contains some set of primary fields $\phi_{\lambda_{i}}$ with conformal weights $\lambda_{i}$.
-Also we have boundary condition changing operators  $\phi$ at the tip of SLE trace and in the infinity.
-We can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite this expression in upper half plane:
-
-\begin{equation}
-  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
-  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
-  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
-  \label{eq:1}
-\end{equation}
-
-Now we want to consider evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
-\begin{equation*}
-  -\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}.
-\end{equation*}
-For transformation of primary fields $\phi_{\lambda_{i}}$ we have 
-\begin{equation}
-  \label{eq:2}
-  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\phi_{\lambda_{i}}(w_{i}) 
-\end{equation}
-We denote generator of this transform by $\mathcal{G}_{i}$.
-
-Continuous limit in critical point leads to CFT correlation function
-
-Now for expectation value of martingale we have this expression.
-\begin{equation*}
-  \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=    \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t+dt}}\right], \quad \mathbb{E}\left[d \prec\mathcal{O}\succ_{\gamma_{t}}\right]=0
-\end{equation*}
-
-Now we use Ito calculus to calculate increment of our correlation function. It should be zero so we get the equation:
-\begin{equation*}
-  \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{-h_{i}}\right)\mathbb{E}\left[d 
-    \mathcal{F}_{\mathbb{H}_{t}}\right]=\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\mathbb{E}\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
-      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}
-\end{equation*}
-Then use explicit form of conformal map and obtain
-\begin{equation*}
-  \left( \sum_{i}\left[-\frac{2h_{i}}{w_{i}^{2}} +\frac{2}{w_{i}}\partial_{w_{i}}\right]+\frac{\kappa}{2}\sum_{i,j}\partial_{w_{i}} \partial_{w_{j}}\right)\mathcal{F}(\left\{z_{i}\right\})=0
-\end{equation*}
-
-We can rewrite it as the necessary condition on b.c.c. operator $\phi$:
-\begin{equation*}
-  (L_{-2}-\frac{\kappa}{2}L_{-1}^{2})\phi=0 \Longrightarrow \phi \left|0\right>  \text{has level 2 null state}, \phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}
-\end{equation*}
+Expectation value of lattice observable on upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace multiplied by the probability of this trajectory.
+Since lattice observable does not depend on the choice of time t, observables in presence of SLE trace should be martingales. 
+In continuous limit lattice observable tends to CFT correlation function of this form.
+It contains some set of primary fields.
+And we have boundary condition changing operators at the tip of SLE trace and in the infinity.
+We can use conformal map w of z to rewrite this expression in upper half plane. 
+Now we want to consider evolution from t to t plus dt. First factor give us this expression. Primary field under conformal map are changed in this way.
+We denote generator of this transform by gi.
+Now for expectation value of martingale we have this expression. We use Ito calculus to calculate increment of our correlation function. It should be zero so we get this equation.
 We can see that it can be rewritten as the action of Virasoro generators.
 Since we have arbitrary observable, this equation is equivalent to the requirement for boundary condition changing operator to have level two null state.
-In case of minimal model we can see that boundary condition chaining operator is primary field $\phi_{1,2}$ or $\phi_{2,1}$.
+In case of minimal model we can see that boundary condition chaining operator is primary field phi one two or phi two one. 
+Now we want to generalize this analysis to rational conformal field theories.
+First we consider Wess-Zumino-Novikov-Witten model.
+The action for this model can be written in terms of map from complex plane with infinity or two-sphere to some Lie group G.
+The first term is just non-linear sigma-model.
+Here K is Killing form on algebra g.
+The second term is written in terms of continuation from two sphere to three-dimensional manifold which has two sphere as the boundary.
+Since this continuation is non-unique we get the requirement for k to be integer.
+Currents of this model have this form. 
+Model possess gauge invariance with omega and omega bar in dependant.
+If we consider infinitesimal gauge transformation we get this Ward identities.
+Then we can get operator product expansion for currents.
+If we expand currents to modes we get commutation relations of affine Lie algebra g hat. 
+This model has conformal invariance which can be seen from 
+Sugawara construction. This is way to embed Virasoro algebra into the universal enveloping algebra of affine Lie algebra g hat. 
+Full chiral algebra of the model is semidirect product of affine and Virasoro algebra. Its commutation relations are here. 
+Primary fields are labeled by highest weights of affine Lie algebra representations. Here we see how Virasoro and affine Lie algebra generators act on primary fields.
 
-\section{SLE and WZNW models}
-\label{sec:sle-wzw-models}
-Now we want to generalize this analysis to rational conformal field theories. First we consider Wess-Zumino-Novikov-Witten model.
-\subsection{WZNW models}
-
- The action for this model can be written in terms of map $g:\mathbb{C}\cup \{\infty\}\sim S^{2}\to G$ from complex plane with infinity or two-sphere to some Lie group $G$:
-\begin{multline}
-  S=-\frac{k}{8\pi}\int d^2x\; \mathcal{K} (g^{-1}\partial^{\mu}g, g^{-1} \partial_{\mu}g)  
-  \\
-  - \frac{k }{24\pi^{2}} \int_{B}\epsilon_{ijk} \mathcal{K}\left(
-    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i},\left[
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right]\right) d^3y
-\end{multline}
-The first term is just non-linear sigma-model.
-
- Here $\mathcal{K}$ is Killing form on Lie algebra $\gf$ of Lie group $G$.
-The second term is written in terms of continuation from two-sphere $S^{2}$ to three-dimensional manifold $B$ which has two-sphere as the boundary.
-Since this continuation is non-unique we get the requirement for $k$ to be integer.
-
-Currents of this model have following form:
-  \begin{eqnarray}
-    J(z)= -k \partial_zg g^{-1}
-    \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
-  \end{eqnarray}
-
-Model possess gauge invariance under gauge transformations:
-  \begin{equation*}
-    g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z),
-  \end{equation*}
-  where $\Omega,\;\bar \Omega \in G$.
-Here $\Omega$ and $\bar \Omega$ are independent.
-
-If we consider infinitesimal gauge transformation $\Omega=1+\omega$ we get Ward identities:
-  \begin{equation}
-    \label{eq:87}
-    \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
-    \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
-  \end{equation}
-
- Then we can get operator product expansion for currents. 
- \begin{equation}
-   \label{eq:3}
-   <J\phi>\sim \dots
- \end{equation}
-
-If we expand currents to modes
-\begin{equation*}
-  J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n 
-\end{equation*}
-and use operator product expansion \eqref{eq:3} we get commutation relations of affine Lie algebra $\gfh$:
-\begin{equation}
-  \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0} 
-\end{equation}
-
-This model has conformal invariance which can be seen from 
-Sugawara construction. This is way to embed Virasoro algebra into the universal enveloping algebra of affine Lie algebra $\gfh$ ($Vir\subset U(\gfh)$):
-\begin{equation}
-  \label{eq:4}
-  L_n=\frac{1}{2(k+h^v)}\sum\limits_a\sum\limits_m:J^a_m J^a_{n-m}:
-\end{equation}
-
-Full chiral algebra of the model is semidirect product of affine and Virasoro algebra $\gfh \ltimes Vir$.
-
-Its commutation relations are
-  \begin{equation}
-    \label{eq:92}
-    \begin{aligned}
-      \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
-      \left[L_n,J^a_m\right]=-mJ^a_{n+m}
-    \end{aligned}
-  \end{equation}
-
-Primary fields  $\phi_{\lambda}$ are labeled by highest weights of affine Lie algebra representations. Here we see how Virasoro and affine Lie algebra generators act on primary fields:
-  \begin{equation*}
-    \begin{aligned}
-      & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>  \quad    J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
-      & L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>=h_{\lambda} \left|\phi_{\lambda}\right>
-    \end{aligned}
-  \end{equation*}
-
-\subsection{SLE and WZNW models}
-Now we want to study Schramm-Loewner evolution in WZNW-models.
-
-Similarly to minimal models we consider observable
-\begin{equation*}
-  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
-  \frac{\left<\phi_{\Lambda}(z_{t}) \phi_{\lambda_1}(z_{1}) \dots \phi_{\lambda_n}(z_{n}) \phi_{\lambda^{*}_1}(\bar z_{1}) \dots \phi_{\lambda^{*}_n}(\bar z_{n})
-      \phi_{\Lambda^{*}}(\infty)\right>}{\left<\phi_{\Lambda}(z_{t})\phi_{\Lambda^{*}}(\infty)\right>}
-\end{equation*}
-Again we can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite it on the whole upper half-plane. 
-\begin{equation*}
-  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
-  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
-  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
-\end{equation*}
-
-Consider evolution from $t$ to $t+dt$.
-First factor gives us $-\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}$.
-
- For fields we have
-\begin{equation*}
-  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i})
-\end{equation*}
-When we consider fields we need to add random gauge transformation (random motion in $G$) to stochastic evolution \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}:
-\begin{equation*}
-  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)
-\end{equation*}
+Now we want to study Schramm-Loewner evolution in this case. Similarly to minimal case we need to study this correlation function. 
+Again we can use conformal map w of z to rewrite it on the whole upper half-plane. 
+We consider evolution from time t to t plus dt. We get the same expression from the first factor. But when we consider fields we need to add random gauge transformation. 
 Since we have boundary we are working with boundary CFT so we have only half of gauge transformations due to Cardy conditions.
-
-\subsection{SLE martingales in WZNW models}
-We use Ito calculus to get the equation from martingale condition:
-\begin{equation*}
-  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0
-\end{equation*}
-\begin{equation*}
-  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{\lambda_{i}}}{(w_{i}-z)^{n}}-\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right);\quad \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}}
-\end{equation*}
-Again we can rewrite it as algebraic requirement for  field  which 
-correspond to boundary condition changing operator.
-\begin{equation*}
-  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
-\end{equation*}
-is level two null state and if we act on this state with raising operators we should get zero.
-\begin{equation*}
-  J^{a}_{1} \left|\psi\right>=0, J^{a}_{2}\left|\psi\right>=0.
-\end{equation*}
+The generator of field transformation have this form.
+We can interpret last term as Brownian motion in Lie group G.
+Then we use Ito calculus to get this equation from martingale condition. Again we can rewrite it as algebraic requirement for  field  which correspond to boundary condition changing operator.
+If we act on this state with raising operators we should get zero.
 We use commutation relations and get equations which connects parameters of random motion with level of affine Lie algebra representation.
-
-We can see that $\kappa+\tau h^{v}=4$ and it is possible to derive additional relations connecting $\kappa, \tau, k$:
-\begin{equation*}
-  \kappa=\frac{2(h^{v}-2k)}{2h_{\Lambda}h^{v}-k},\quad \tau=\frac{8 h_{\Lambda}-2}{2h_{\Lambda}h^{v}-k}  \quad\text{for}\; k\neq 2h_{\Lambda}h^{v}
-\end{equation*}
+To study this equations we need to use Knizhnik-Zamolodchikov equations.
 Also we get some constraints on possible boundary condition changing operators.
-To get complete classification use Knizhnik-Zamolodchikov equations.
-
-\section{Coset models}
-\label{sec:coset-models}
-
-\subsection{Gauged WZNW-models and coset construction}
-Add gauge fields $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action:
-\begin{multline*}
-  S(g,A)=S_{WZNW}(g)+\\
-  \frac{k}{4\pi}\int d^{2}z \left(\mathcal{K}(A, g^{-1}\bar \partial g)-\mathcal{K}(\bar A, (\partial g ) g^{-1})+\mathcal{K}(A,g^{-1}\bar A g)-\mathcal{K}(A,\bar A)\right)
-\end{multline*}
-
-Now current is
-\begin{equation*}
-  J_{(\gf,\af)}=-k\partial g g^{-1} -k g A g^{-1}
-\end{equation*}
-
-From Ward identities we get
-\begin{equation*}
-  \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{v}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
-\end{equation*}
-Remember that for WZNW current we have OPE $J_{\gf}^{a}(z)\phi_{i}(w)\sim \frac{-t^{a}_{i}\phi(w)}{z-w}$.
-%% Commutation relations for current components are preserved.
-
-Algebraic structure is connected with two affine Lie algebras $\gfh, \afh: \afh\subset\gfh$.
-
-Virasoro generators are given by difference of Sugawara expressions:
-\begin{equation*}
-  L_{n}=L_{n}^{\gf}-L_{n}^{\af}
-\end{equation*}
-
-\subsection{Primary fields}
-
-Primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
-But some pairs are equivalent.
-This equivalence is given by the action of simple currents $(J,\tilde{J})$ such that $h_{J}-h_{\tilde{J}}=0$.
-
-Conformal weight of primary field
-\begin{multline}
-  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^v)}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
-  \left|\phi_{\lambda}\right>=\\
-  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^v)}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^v)}\right)\left|\phi_{(\mu,\nu)}\right>
-\end{multline}
-
-%% So $G/A$-coset theory is related to $\gf\oplus \bar{\af}$-theory.
-
-It is possible to obtain analogues of KZ-equations:
-\begin{equation*}
-  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{v}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{v}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
-\end{equation*}
-
-\subsection{SLE on coset space}
-For  $\gf\oplus \af$ WZNW-model we can write SLE generator of primary field transformation under stochastic evolution as
-\begin{equation*}
-  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)+\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
-\end{equation*}
-%% \begin{equation*}
-%%   \mathcal{G}_{i}^{L,R}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)\pm\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
-%% \end{equation*}
-
-and get martingale condition
-\begin{equation*}
-  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
-      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0
-\end{equation*}
-
-which can be rewritten as the requirement for
-\begin{equation*}
-  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}
-\end{equation*}
-to be level two null-field.
-
-\subsection{Parafermions}
-$\mathbb{Z}(N)$ parafermions are equivalent to $SU(2)_{N}/U(1)$ coset theory.
-
-Parafermionic field decomposes as
-\begin{equation*}
-  \Phi^{j}=\phi_{j}(z) \exp\left( -i \frac{j}{\sqrt{N}}\phi(z)\right)
-\end{equation*}
-where $\phi_{j}(z)$ is field of $SU(2)$-WZNW model with spin $j$, $\phi(z)$ -- $U(1)$ bosonic field.
-
-For parafermionic current we have
-\begin{equation*}
-  \Psi^{\pm}=\frac{1}{\sqrt{N}} J^{\pm}\exp\left(\mp i \frac{1}{\sqrt{N}}\phi(z)\right)
-\end{equation*}
-%% Its action in terms of primary fields of $su(2)\oplus u(1)$ WZNW-model is equivalent to $J^{\pm}\pm \tilde{J}^{\pm}$.
-
-Martingale condition can be rewritten as
-\begin{equation*}
-  \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[\Psi^{+}_{-1}\Psi^{-}_{-1}+\Psi^{-}_{-1}\Psi^{+}_{-1}\right]\right) \left|\Phi\right>=0
-\end{equation*}
-which coincides with the result of Santachiara [arXiv:0705.2749].
-
-\subsection{Next steps}
-\begin{itemize}
-\item Act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations connecting $\kappa, \tau, k$.
-\item Use Knizhnik-Zamolodchikov equations to simplify them.
-\item Get conditions on boundary condition changing operator
-\item Compare these conditions with results of  the study of boundary states with fusion algebra (Verlinde formula for Cardy states)
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-\subsection{Conclusion}
-\begin{itemize}
-\item It is possible to match SLE observables and CFT correlators
-\item Martingale conditions are equivalent to Verma module of affine Lie algebra having singular weights at level two.
-\item Primary fields of $\gf\oplus \af$ WZNW-model with equivalence relations can be used to study coset theory
-\item Study of martingale conditions in coset theory is parallel to the study of boundary states with fusion algebra
-\end{itemize}
-
-\subsection{Thank you for your attention!}
 
@@
 
-\section{Introduction}
-SLE for WZW models are actively studied. KZ-equations allow to show that certain functions are martingales. 
-In coset models of CFT it is possible to write analogues of KZ equations from null vector conditions. 
-Corresponding SLE should have natural interpretation in case of coset construction of minimal models.
-
-SLE is interpreted as limit of interfaces in lattice models.
-So SLE observable should have the form of boundary correlation function with boundary condition changing operator inserted.
-There is some condition on spin of boundary condition changing operator in Kostya's paper.
-Classification of boundary condition changing operators is given in papers in CFT folder.
-
-What to do:
-Simplest coset model: $su(2)_{1}\oplus su(2)_{1}/su(2)_{2}$ $k=1, c=1/2$.
-
-Schramm-Loewner evolution is conformally-invariant probability measure on the continuous curves in complex domain.
-We work with upper half-plane.
-SLEs are limits of critical interfaces in lattice models such as Ising model, percolation, FK-model.
-SLE can be used to make a connection with boundary conformal field theory. Observables in presence of SLE (probabilities) are identified with certain correlators in BCFT.
-
-Rational conformal field theories have description in terms of coset models.
-These models have geometric formulation as gauged WZNW models.
-Minimal models of CFT can be realized as coset models.
-So (at least) some of coset models can be seen as the limit of lattice models.
-\section{WZW-models and SLE}
-\label{sec:wzw-models-sle}
-
-$SLE_{\kappa,\tau}$ appears in WZW [cite: Gruzberg, Alekseev-Bytsko-Izurov]. Brownian motion on Lie group.
-
-Boundary conditions. Boundary condition changing operators.
-
-\section{Parafermions}
-\label{sec:parafermions}
-
-Parafermions are fields in coset $\hat{su}(2)/\hat{u}(1)$. Generalization of Brownian motion. Possible boundary conditions. D-branes.
-
-\section{Coset models}
-\label{sec:coset-models}
-
-Boundary conditions??
-
-Ishikava paper - method to get boundary operators.
-
-Ising model - boundary condition changing operator should be known (find).
-
-Generalizations of Brownian motion??
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-\bibliography{bibliography}{}
-\bibliographystyle{utphys}
-
 \end{document}
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2011-08-21 AffineLieAlgebras/SLE/article.tex
Text of the talk is mixed with the transparencies

@@
 \label{sec:coset-models}
+Now we want to generalize analysis of correspondence between SLE and CFT even further and study coset models of conformal field theory.
 
 \subsection{Gauged WZNW-models and coset construction}
-Add gauge fields $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action:
+
+Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models. We add gauge fields  $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action:
 \begin{multline*}
@@
 \end{multline*}
-
 Now current is
@@
 
-From Ward identities we get
+From Ward identities we get following expression for the product of gauge field and primary fields:
 \begin{equation*}
@@
 \end{equation*}
-Remember that for WZNW current we have OPE $J_{\gf}^{a}(z)\phi_{i}(w)\sim \frac{-t^{a}_{i}\phi(w)}{z-w}$.
-%% Commutation relations for current components are preserved.
+Here $h_{\af}^{v}$ is the dual Coxeter number of Lie algebra $\af$.
 
-Algebraic structure is connected with two affine Lie algebras $\gfh, \afh: \afh\subset\gfh$.
+Remember that for WZNW current we have OPE $J_{\gf}^{a}(z)\phi_{i}(w)\sim \frac{-t^{a}_{i}\phi(w)}{z-w}$,  so we see that algebraic structure is connected with the pair of algebras $\gf$ and $\af$, such that $\afh\subset\gfh$.
 
@@
 
-Primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
+Primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra and subalgebra, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
 But some pairs are equivalent.
-This equivalence is given by the action of simple currents $(J,\tilde{J})$ such that $h_{J}-h_{\tilde{J}}=0$.
+This equivalence is given by the action of simple currents $(J,\tilde{J})$ such that their conformal weights are equal:  $h_{J}-h_{\tilde{J}}=0$.
 
-Conformal weight of primary field
+Conformal weight of primary field are equal to
 \begin{multline}
@@
 
+We can compare this result with the simplest possible coset model $su(2)/u(1)$ --  parafermion theory.
+
 \subsection{Parafermions}
+
 $\mathbb{Z}(N)$ parafermions are equivalent to $SU(2)_{N}/U(1)$ coset theory.
 
-Parafermionic field decomposes as
+It is well-known that parafermionic field can be written as product of $su(2)$-primary field and vertex operator of bosonic field. 
 \begin{equation*}
@@
 \subsection{Next steps}
-\begin{itemize}
-\item Act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations connecting $\kappa, \tau, k$.
-\item Use Knizhnik-Zamolodchikov equations to simplify them.
-\item Get conditions on boundary condition changing operator
-\item Compare these conditions with results of  the study of boundary states with fusion algebra (Verlinde formula for Cardy states)
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-\subsection{Conclusion}
-\begin{itemize}
-\item It is possible to match SLE observables and CFT correlators
-\item Martingale conditions are equivalent to Verma module of affine Lie algebra having singular weights at level two.
-\item Primary fields of $\gf\oplus \af$ WZNW-model with equivalence relations can be used to study coset theory
-\item Study of martingale conditions in coset theory is parallel to the study of boundary states with fusion algebra
-\end{itemize}
-
-\subsection{Thank you for your attention!}
-
-Now we want to generalize this analysis even further and study coset models of conformal field theory.
-This models can be realized as gauged Wess-Zumino-Novikov-Witten models.
-We add gauge fields taking values in subalgebra a of Lie algebra g.
-The term which describes interaction with gauge fields has this form.
-The current of this model is here. 
-We have this expression for the product of gauge field and primary fields. Here hv is dual Coxeter number of Lie algebra h.
-Remember that for Wess-Zumino-Witten model current we have this operator product expansion.
-So we see that algebraic structure is connected with the pair of algebras g and a.
-Virasoro generators are given by the difference of Sugawara expressions for this algebras.
-Primary fields are labeled by pairs of weights of algebra and subalgebra, but some pairs are equivalent.
-This equivalence relation is given by the action of simple currents corresponding to affine Lie algebras g and a such, that their conformal weights are equal.
-For conformal weight of primary fields we have this expression. 
-One can also write analogues of Knizhnik-Zamolodchikov equations.
-
-So for SLE transformation we get direct sum of random gauge transformation in algebras g and a.
-Martingale condition can be written in this form.
-So again we get algebraic relation on boundary condition changing operator.
-
-We can compare this result with the simplest possible coset model su two divided by u one.
-It is parafermion theory.
-It is well-known that parafermionic field can be written as product of su two primary field and Vertex operator of bosonic field.
-Parafermionic current can be seen as the combination of su(2) and u(1) currents and the martingale equation from previous slide can be written in this form.
-This relation coincide with the relation which can be obtained from the study SLE in  parafermionic models.
 
 Next steps in the study of SLE martingales for coset models  are the following.
-We need to act on the relation with raising operators and get relations which connects level of representation and parameters of random motion.
+
+At first we act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with  raising operators $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations which connects level of representation and parameters of random motion $\kappa, \tau$.
+
 Then we use Knizhnik-Zamolodchikov equations to rewrite the relations in simpler form and get conditions on possible boundary condition changing operators.
+
 Boundary states in coset models were actively studied.
@@
 
+\section{Conclusion}
+\label{sec:conclusion}
+
 Now we see that it is possible to match SLE observables and CFT correlation functions.
 Martingale conditions can be seen as the constraints on possible Verma modules of affine Lie algebra corresponding to boundary condition changing operator.
-This Verma module must have level two null state.
+These Verma modules must have level two null state.
+
 We can use primary fields of direct sum WZNW model and equivalence relations to study coset models.
+
 Martingale conditions should be compared with the classification of boundary states with other methods.
-
-Thank you for your attention.
-
-\section{Introduction}
-SLE for WZW models are actively studied. KZ-equations allow to show that certain functions are martingales. 
-In coset models of CFT it is possible to write analogues of KZ equations from null vector conditions. 
-Corresponding SLE should have natural interpretation in case of coset construction of minimal models.
-
-SLE is interpreted as limit of interfaces in lattice models.
-So SLE observable should have the form of boundary correlation function with boundary condition changing operator inserted.
-There is some condition on spin of boundary condition changing operator in Kostya's paper.
-Classification of boundary condition changing operators is given in papers in CFT folder.
-
-What to do:
-Simplest coset model: $su(2)_{1}\oplus su(2)_{1}/su(2)_{2}$ $k=1, c=1/2$.
-
-Schramm-Loewner evolution is conformally-invariant probability measure on the continuous curves in complex domain.
-We work with upper half-plane.
-SLEs are limits of critical interfaces in lattice models such as Ising model, percolation, FK-model.
-SLE can be used to make a connection with boundary conformal field theory. Observables in presence of SLE (probabilities) are identified with certain correlators in BCFT.
-
-Rational conformal field theories have description in terms of coset models.
-These models have geometric formulation as gauged WZNW models.
-Minimal models of CFT can be realized as coset models.
-So (at least) some of coset models can be seen as the limit of lattice models.
-\section{WZW-models and SLE}
-\label{sec:wzw-models-sle}
-
-$SLE_{\kappa,\tau}$ appears in WZW [cite: Gruzberg, Alekseev-Bytsko-Izurov]. Brownian motion on Lie group.
-
-Boundary conditions. Boundary condition changing operators.
-
-\section{Parafermions}
-\label{sec:parafermions}
-
-Parafermions are fields in coset $\hat{su}(2)/\hat{u}(1)$. Generalization of Brownian motion. Possible boundary conditions. D-branes.
-
-\section{Coset models}
-\label{sec:coset-models}
-
-Boundary conditions??
-
-Ishikava paper - method to get boundary operators.
-
-Ising model - boundary condition changing operator should be known (find).
-
-Generalizations of Brownian motion??
-
-\section{Conclusion}
-\label{sec:conclusion}
 

### 2011-09-19 AffineLieAlgebras/SLE/abstract.tex
Abstract for the talk in laboratory on September 28 2011 added.

\documentclass[a4paper,12pt]{article}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}

\usepackage{latexsym}
\usepackage{amssymb}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}

\topmargin=-1.5cm
\oddsidemargin=-1.5cm
\textwidth=17cm
\textheight=28cm

\author{Антон Назаров}
\title{Эволюция Шрамма-Лёвнера и coset-модели конформной теории поля}
\date{28 сентября 2011, 15:00}

\begin{document}
\pagestyle{empty}
\maketitle

  Эволюция Шрамма-Лёвнера описывает непрерывный предел интерфейсов в критической точке решеточных
  моделей. При этом значения корреляционных функций вычисляются в области с разрезом, порожденным
  эволюцией Шрамма-Лёвнера. С другой стороны существует описание в терминах минимальных моделей
  конформной теории поля. Там значения вычисляются как корреляторы некоторых наборов примарных
  операторов с добавлением оператора смены граничного условия на конце разреза. Условие, что
  определенная величина является мартингалом можно записать как дифференциальное уравнение на
  коррелятор, которое, в свою очередь, можно переписать как набор алгебраических соотношений,
  наложенных на оператор смены граничного условия. Если решить эти соотношения, получится набор
  возможных операторов смены граничных условий, который совпадает с предсказаниями граничной
  конформной теории поля, следующими из физических соображений.

  Помимо минимальных моделей конформной теории поля существуют и более сложные. Важный класс таких
  моделей -- это модели Весса-Зумино-Новикова-Виттена, которые обладают дополнительной симметрией,
  связанной с алгебрами Каца-Муди. Для таких моделей не известно решеточной реализации, однако можно
  рассмотреть эволюцию Шрамма-Лёвнера с дополнительным случайным движением по группе Ли, записать и
  решить условия на мартингалы. Это было сделано в работе Антона Алексеева, Андрея Быцко и
  Константина Изъюрова \cite{alekseev2010sle}.

  Coset-конструкция конформной теории поля позволяет строить еще более широкий класс моделей на
  основе моделей Весса-Зумино-Новикова-Виттена. В частности, таким образом можно реализовать все
  минимальные модели конформной теории поля. В данном докладе мы попробуем обобщить эволюцию
  Шрамма-Лёвнера на этот случай путем рассмотрения дополнительного случайного блуждания на
  фактор-группе группы Ли. Так как этот подход должен воспроизводить известные результаты для
  минимальных моделей, мы рассмотрим в качестве примера coset-модели, соответствующие модели Изинга
  и парафермионам, эволюция Шрамма-Лёвнера для которых была рассмотрена Раулем Сантачиарой в работе
  \cite{santachiara2008sle}.

\bibliography{bibliography}{}
\bibliographystyle{utphys}

\end{document}

### 2011-09-19 AffineLieAlgebras/SLE/article.tex
Abstract for the talk in laboratory on September 28 2011 added.

@@
 \subsection{SLE on coset space}
+Consider gauge transformation in gauged WZNW model:
+\begin{eqnarray*}
+  \delta \phi_{i}=(\epsilon_{L}^{a} t^{a}_{i}+\epsilon^{b}_{R}\tilde{t}^{b})\phi_{i}\\
+  \delta A = -\partial \epsilon_{R}-[\epsilon_{R},A]
+\end{eqnarray*}
+Here $\epsilon_{L}, \epsilon_{R}$ are arbitrary holomorphic functions $\bar\partial\epsilon_{L,R}=0$. 
 For  $\gf\oplus \af$ WZNW-model we can write SLE generator of primary field transformation under stochastic evolution as
@@
 %% Its action in terms of primary fields of $su(2)\oplus u(1)$ WZNW-model is equivalent to $J^{\pm}\pm \tilde{J}^{\pm}$.
-
+%% !!! TODO
 Martingale condition can be rewritten as
@@
 
-At first we act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with  raising operators $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations which connects level of representation and parameters of random motion $\kappa, \tau$.
+%At first we act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with  raising operators $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations which connects level of representation and parameters of random motion $\kappa, \tau$.
+% !!! This is wrong !!!
+% We can act by Sugawara generators
 

### 2011-09-19 GeneralOverview/IntegrableSystems.tex
Abstract for the talk in laboratory on September 28 2011 added.

@@
 
+\title{Интегрируемые спиновые цепочки}
+\date{}
 \begin{document}
 
-\title{Интегрируемые спиновые цепочки}
-
-\begin{abstract}
-\end{abstract}
+\maketitle
 
@@
 
+Произведение операторов Лакса по всем узлам называется матрицей монодромии. Трансфер-матрица - это ее след.
+
 \section{Лекция 4. 3 марта 2011}
@@
 Для этого запишем трансфер-матрицу в виде матрицы 2x2 с компонентами A, B, C, D.
+При этом A,B,C,D - операторы, зависящие от спектрального параметра.
+
+Алгебраический анзац Бете основан на предположении о существовании особого состояния в спектре трансфер-матрицы, называющегося псевдовакуумом.
+Это состояние обнуляется оператором B.
+Все остальные состояния порождаются действием оператора C на псевдовакуум.
+Таким образом B выполняет роль оператора уничтожения, а C - рождения.
+
+Далее мы рассматриваем действие трансфер-матрицы на состояния, порожденные из псевдовакуума и получаем уравнения Бете.
 \section{Лекция 6. 17 марта 2011}
+
+Лекция посвящена рассмотрению примера уравнений Бете-анзаца для случая цепочки из двух узлов.
+Явно выписывается вид и действие операторов, составляющих матрицу монодромии.
+Затем выводятся уравнения Бете.
+Уравнения Бете - это алгебраические уравнения на функции q(u), через которые выражается спектр трансфер-матрицы, а значит и всех интегралов движения, включая гамильтониан.
 
@@
 
+В этой лекции приводится способ построения гамильтониана из трансфер-матрицы и вычисление его спектра из уравнений Бете-анзаца.
+Оказывается, что гамильтониан в виде суммы операторов перестановки, который приводился в первых лекциях в качестве примера, можно получить из трансфер-матрицы путем дифференцирования ее логарифма по спектральному параметру в точке 1/2.
+Зная вид и коммутационные соотношения для трансфер-матрицы мы теперь можем предъявить набор коммутирующих с гамильтонианом операторов и доказать интегрируемость.
+
 \section{Лекция 8. 31 марта 2011}
 
+Теперь мы демонстрируем возможность получения гамильтониана для спиновой цепочки со спином -1, который был приведен в первой лекции в интегральном представлении, из явного вида R-матрицы и оператора Лакса.
+Для этого выводится явный вид операторов перестановки, проверяются их свойства и выписывается выражение для действия R-матрицы.
+Она зависит только от разности спектральных параметров.
+Двухчастичный гамильтониан дается произведением производной R-матрицы и обратного к R-матрице оператора в точке 0.
 \section{Лекция 9. 7 апреля 2011}
 
+Завершая доказательство, начатое в предыдущей лекции, мы получаем интегральный вид для гамильтониана.
+После этого, в принципе, можно находить его спектр при помощи анзаца Бете.
+Но этот метод не всегда работает, так как зависит от наличия особого состояния - псевдовакуума.
+
+Поэтому мы переходим к описанию альтернативного подхода, связанного с построением Q-оператора Бакстера.
+В этом подходе нам не требуется предположение о существовании псевдовакуума.
+Q-оператор должен зависеть от спектрального параметра и коммутировать с трансфер-матрицей и сам с собой.
+Вид и соотношения для Q-оператора должны следовать из уравнений Янга-Бакстера для R-матрицы.
 \section{Лекция 10. 14 апреля 2011}
+Q-оператор состоит из блоков, условия на вид которых находятся из требуемых коммутационных соотношений с трансфер-матрицей.
+Оказывается, что блоки можно получить из явного вида для R-матрицы.
+В данной лекции мы используем явный вид, подходящий для бесконечномерных представлений алгебры sl(s) - модулей Верма.
+После получения выражения для блоков, мы видим, что Q-оператор дается (нормированным) произведением по всем узлам.
+Затем определяется действие полученного оператора на полиномах.
+
+\section{Лекция 11. 21 апреля 2011}
+
+В этой лекции мы проверяем, что коммутационные соотношения для Q-оператора с трансфер-матрицей, полученного в прошлой лекции, эквивалентны RLL-соотношениям, связывающим R-матрицу и оператор Лакса или уравнениям Янга-Бакстера.
+Теперь нам остается доказать коммутативность Q-оператора с собой при разных значениях спектрального параметра.
+Для этого нам нужно начать с представления оператора в виде произведения блоков, выражающихся через R-матрицу и рассмотреть действие коммутатора Q-оператора на произвольные функции.
+
+\section{Лекция 12. 5 мая 2011}
+Завершая вычисление, начатое в прошлой лекции, мы получаем уравнение на собственные функции Q-оператора.
+Оказывается, что собственная функция эквивалентна функции q(u), возникающей в уравнениях Бете-анзаца.
+
+Далее мы показываем, что гамильтониан дается разностью производных от логарифма Q-оператора в при противоположных значениях спектрального параметра.
+В результате из подхода с Q-оператором удается извлечь те же результаты для спектра, что и при использовании Бете-анзаца.
+
+\section{Лекция 13. 12 мая 2011}
+
+В этой лекции мы обсуждаем проблему построения решений методом Q-оператора для случая конечномерных представлений алгебры sl(2).
+Конечномерные представления связаны с бесконечномерными модулями Верма резольвентой Бернштейна-Гельфанда-Гельфанда.
+Оказывается, что перенос конструкции на Q-операторы сопряжен с некоторыми техническими сложностями.
 

### 2011-09-28 AffineLieAlgebras/Thesis/3.tex
Copied two papers to thesis, which is recreated with disser style.

\chapter{Конформная теория поля}
\label{cha:cft}

Подробное изложение \cite{difrancesco1997cft}.

\section{Общие свойства}
\label{sec:cft-general}
Алгебра Вирасоро. Представления алгебры Вирасоро. Модулярная инвариантность.

\section{Модели Весса-Зумино-Новикова-Виттена}
\label{sec:wzw}
Связь с аффинными алгебрами Ли.
Конформные вложения и недиагональные модулярные инварианты.

\section{Coset-модели}
\label{sec:coset-models}
Ветвления. Функции ветвления и статсуммы. 
Калибровочные WZW-модели.

\section{SLE}
\label{sec:sle}
SLE на WZW-моделях. Граничные условия. Парафермионы. SLE на coset-моделях.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2011-09-28 AffineLieAlgebras/Thesis/1.tex
Copied two papers to thesis, which is recreated with disser style.

--- 2011-02-15 AffineLieAlgebras/MQFT2010/article-ru.tex
@@
-\documentclass[12pt]{article}
-\usepackage[utf8x]{inputenc}
-\usepackage[russian]{babel}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{amsmath,amssymb,amsthm}
-\usepackage{color}
-\usepackage{graphicx}
-\usepackage{ucs}
-\usepackage[unicode,verbose]{hyperref}
+\chapter{Аффинные алгебры Ли}
+\label{cha:affine-lie-algebras}
 
-\newtheorem{statement}{Утверждение}
-\newtheorem{theorem}{Теорема}
-\newtheorem{corollary}{Следствие}
-\newtheorem{lemma}{Лемма}
-\theoremstyle{definition}
-\newtheorem{definition}{Определение}
-\newtheorem{remark}{Замечание}
-\newtheorem{example}{Пример}
-\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
-\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
-\newcommand{\co}[1]{\stackrel{\circ }{#1}}
-\newcommand{\pia}{\pi_{\mathfrak{a}}}
-\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
-\newcommand{\gf}{\mathfrak{g}}
-\newcommand{\af}{\mathfrak{a}}
-\newcommand{\aft}{\widetilde{\mathfrak{a}}}
-\newcommand{\afb}{\mathfrak{a}_{\bot}}
-\newcommand{\hf}{\mathfrak{h}}
-\newcommand{\hfb}{\mathfrak{h}_{\bot}}
-\newcommand{\pf}{\mathfrak{p}}
-%\input{tcilatex}
-
-\begin{document}
-
-\title{Рекурсивные свойства ветвления и БГГ резольвента}
-\author{В Д Ляховский$^1$, А А Назаров$^{1,2}$\\
-  {\small $^1$ Теоретический отдел,}\\
-  {\small Санкт - Петербургский государственный университет}\\
-  {\small 198904, Санкт - Петербург, Россия}\\
-  {\small $^2$ Лаборатория имени Чебышева,}\\
-  {\small математико-механический факультет,}\\ 
-  {\small Санкт - Петербургский государственный университет}\\
-  {\small 199178, Санкт - Петербург, Россия}\\[5mm]
-  {\small e-mails: lyakh1507@nm.ru \quad antonnaz@gmail.com}}
-
-\maketitle
-
-\begin{abstract}
-Рекуррентные соотношения для коэффициентов ветвления основываются на определенном разложении сингулярного элемента.
-Мы показываем, что такое разложение может использоваться для построения параболических модулей Верма и получения обобщенных формул Вейля-Верма для характеров.
-Также мы демонстрируем, что коэффициенты ветвления определяют обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда.
-\end{abstract}
-
-\section{Введение}
-
-\label{sec:introduction}
-Свойства ветвления (аффинных) алгебр Ли важны для приложений в квантовой теории поля (смотри, например, модели конформной теории поля \cite{difrancesco1997cft},\cite{coquereaux2008conformal}).
-В данной работе мы показываем, что ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и демонстрирует свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).
-
-Резольвента для неприводимых модулей в терминах бесконечномерных модулей важна для теории интегрируемых спиновых цепочек \cite{derk1008}.
-В подходе  $\mathcal{Q}$-оператора Бакстера \cite{derk09} общие трансфер-матрицы, соответствующие (обобщенным) модулям Верма, факторизуются в произведение операторов Бакстера.
-Резольвента позволяет вычислить трансфер-матрицы для конечномерных вспомогательных пространств.
-
-Чтобы продемонстрировать связь БГГ резольвенты с ветвлением мы используем рекурсивный подход, представленный в работе \cite
-{2010arXiv1007.0318L} (аналогичный подход для максимальных вложений использовался в работе \cite{ilyin812pbc}).
-Мы рассматриваем подалгебру $\af \hookrightarrow \gf$ вместе с $\afb$ -- ``ортогональным партнером'' $\af$ по отношению к форме Киллинга, а также подалгебру $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$, где $\frak{h}=\frak{\frak{h}_{\af}}\oplus
-\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. Для любой редуктивной подалгебры $\af$ алгебра $\afb\hookrightarrow \gf$ регулярна и редуктивна. Для интегрируемого модуля старшего веса $%
-L^{\left(\mu \right) }$ и ортогональной подалгебры  $\af_{\bot }$ мы рассматриваем сингулярный элемент $\Psi ^{\left( \mu \right) }$ (числитель в формуле Вейля для характеров $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
-\mu \right) }}{\Psi ^{\left( 0\right) }}$, см., например,  \cite
-{humphreys1997introduction}) и знаменатель Вейля $\Psi _{\af_{\bot
-  }}^{\left( 0\right) }$ для ортогонального партнера. В работе показано, что элемент  $\Psi _{\gf%
-}^{\left( \mu \right) }$ может быть разложен в комбинацию числителей Вейля $\Psi _{\af_{\bot }}^{\left( \nu \right) }$, где $\nu \in P_{%
-\mathfrak{a}_{\bot}}^{+}$. Это разложение дает возможность построить множество модулей старшего веса $L_{\afb}%
-^{\mu _{\afb}}$. В том случае, если вложение\ $\af%
-_{\bot }\hookrightarrow \gf$ \ удовлетворяет ``стандартным параболическим'' условиям, эти модули порождают параболические модули Верма $M_{\left(
-\afb \hookrightarrow \gf\right) }^{\mu _{%
-\afb}}$, так что исходный характер $ch\left(
-L^{\mu }\right) $ в итоге раскладывается в знакопеременную сумму таких модулей.
-С другой стороны, если параболическое условие нарушено, конструкция сохраняется и порождает разложение по отношению к набору обобщенных модулей Верма  $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
-\widetilde{\afb}}}$, где $%
-\widetilde{\frak{b}_{\perp }}$ уже не является подалгеброй в $\gf$, а оказывается сжатием $\widetilde{\afb}$.
-
-Некоторые общие свойства предложенного разложения формулируются в терминах  формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''.
-Использование этого инструмента позволило сформулировать простой и явный алгоритм для вычисления правил ветвления, подходящий для произвольной (максимальной или не максимальной) подалгебры в аффинной алгебре Ли \cite{2010arXiv1007.0318L}.
-
-Возможные обобщения полученных результатов обсуждаются в Разделе \ref{sec:conclusions}.
-
-\subsection{Обозначения}
+ \section{Обозначения}
 
@@
  }\left( \alpha \right) } $)--- знаменатель Вейля.
+
+\section{Конечномерные алгебры Ли}
+\label{sec:finite-dimensional}
+Основные определения: корни, веса, кратности.
+
+\section{Теория представлений аффинных алгебр Ли}
+\label{sec:representation-theory}
+Определение аффинных алгебр. Корни, веса, кратности. Категория О.
+
+\section{Ветвления}
+\label{sec:branching}
+Веер вложения. Алгоритм.
+
+\section{БГГ-резольвента}
+\label{sec:bgg}
+Категория О.
+Резольвента Бернштейна-Гельфанда-Гельфанда для представлений аффинных алгебр Ли. Параболические модули и их связь с подалгебрами и ветвлением.
+
+\begin{abstract}
+Рекуррентные соотношения для коэффициентов ветвления основываются на определенном разложении сингулярного элемента.
+Мы показываем, что такое разложение может использоваться для построения параболических модулей Верма и получения обобщенных формул Вейля-Верма для характеров.
+Также мы демонстрируем, что коэффициенты ветвления определяют обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда.
+\end{abstract}
+
+\section{Введение}
+
+\label{sec:introduction}
+Свойства ветвления (аффинных) алгебр Ли важны для приложений в квантовой теории поля (смотри, например, модели конформной теории поля \cite{difrancesco1997cft},\cite{coquereaux2008conformal}).
+В данной работе мы показываем, что ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и демонстрирует свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).
+
+Резольвента для неприводимых модулей в терминах бесконечномерных модулей важна для теории интегрируемых спиновых цепочек \cite{derk1008}.
+В подходе  $\mathcal{Q}$-оператора Бакстера \cite{derk09} общие трансфер-матрицы, соответствующие (обобщенным) модулям Верма, факторизуются в произведение операторов Бакстера.
+Резольвента позволяет вычислить трансфер-матрицы для конечномерных вспомогательных пространств.
+
+Чтобы продемонстрировать связь БГГ резольвенты с ветвлением мы используем рекурсивный подход, представленный в работе \cite
+{2010arXiv1007.0318L} (аналогичный подход для максимальных вложений использовался в работе \cite{ilyin812pbc}).
+Мы рассматриваем подалгебру $\af \hookrightarrow \gf$ вместе с $\afb$ -- ``ортогональным партнером'' $\af$ по отношению к форме Киллинга, а также подалгебру $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$, где $\frak{h}=\frak{\frak{h}_{\af}}\oplus
+\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. Для любой редуктивной подалгебры $\af$ алгебра $\afb\hookrightarrow \gf$ регулярна и редуктивна. Для интегрируемого модуля старшего веса $%
+L^{\left(\mu \right) }$ и ортогональной подалгебры  $\af_{\bot }$ мы рассматриваем сингулярный элемент $\Psi ^{\left( \mu \right) }$ (числитель в формуле Вейля для характеров $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
+\mu \right) }}{\Psi ^{\left( 0\right) }}$, см., например,  \cite
+{humphreys1997introduction}) и знаменатель Вейля $\Psi _{\af_{\bot
+  }}^{\left( 0\right) }$ для ортогонального партнера. В работе показано, что элемент  $\Psi _{\gf%
+}^{\left( \mu \right) }$ может быть разложен в комбинацию числителей Вейля $\Psi _{\af_{\bot }}^{\left( \nu \right) }$, где $\nu \in P_{%
+\mathfrak{a}_{\bot}}^{+}$. Это разложение дает возможность построить множество модулей старшего веса $L_{\afb}%
+^{\mu _{\afb}}$. В том случае, если вложение\ $\af%
+_{\bot }\hookrightarrow \gf$ \ удовлетворяет ``стандартным параболическим'' условиям, эти модули порождают параболические модули Верма $M_{\left(
+\afb \hookrightarrow \gf\right) }^{\mu _{%
+\afb}}$, так что исходный характер $ch\left(
+L^{\mu }\right) $ в итоге раскладывается в знакопеременную сумму таких модулей.
+С другой стороны, если параболическое условие нарушено, конструкция сохраняется и порождает разложение по отношению к набору обобщенных модулей Верма  $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
+\widetilde{\afb}}}$, где $%
+\widetilde{\frak{b}_{\perp }}$ уже не является подалгеброй в $\gf$, а оказывается сжатием $\widetilde{\afb}$.
+
+Некоторые общие свойства предложенного разложения формулируются в терминах  формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''.
+Использование этого инструмента позволило сформулировать простой и явный алгоритм для вычисления правил ветвления, подходящий для произвольной (максимальной или не максимальной) подалгебры в аффинной алгебре Ли \cite{2010arXiv1007.0318L}.
+
+Возможные обобщения полученных результатов обсуждаются в Разделе \ref{sec:conclusions}.
 
@@
 
-\section{Благодарности}
-Авторы выражают свою искреннюю благодарность всем, кто подготовил и организовал III международную конференцию ``Модели квантовой теории поля 2010'', посвященную 70-летию А.Н. Васильева.
+\section{Выводы к первой главе}
 
-Данная работа была частично поддержана грантом РФФИ № 09-01-00504 и лабораторией имени Чебышева (математико-механический факультет СПбГУ) из средств гранта 11.G34.31.2006 правительства Российской Федерации.
-
-\bibliographystyle{plain}
-\bibliography{article-ru}
-{}
-
-\end{document}
+%%
+%% End of file
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "thesis"
+%%% End:

### 2011-09-28 AffineLieAlgebras/Thesis/2.tex
Copied two papers to thesis, which is recreated with disser style.

%% \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
%% \newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
%% \newcommand{\co}[1]{\stackrel{\circ }{#1}}
%% \newcommand{\pia}{\pi_{\mathfrak{a}}}
%% \newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
%% \newcommand{\gf}{\mathfrak{g}}
%% \newcommand{\af}{\mathfrak{a}}
\newcommand{\bff}{\mathfrak{b}}
%% \newcommand{\afb}{\mathfrak{a}_{\bot}}
%% \newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfg}{\hf_{\gf}}
%% \newcommand{\hfb}{\mathfrak{h}_{\bot}}
%% \newcommand{\pf}{\mathfrak{p}}
%% \newcommand{\aft}{\widetilde{\mathfrak{a}}}

\begin{abstract}
%% Text of abstract
In this paper we present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.  Algorithms are based on the properties of weights and Weyl symmetry. The most important problems for us are the ones, concerning computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition. These problems have numerous applications in physics and we provide some examples of these applications. The program is implemented in popular computer algebra system {\it Mathematica} and works with finite-dimensional and affine Lie algebras.

% A submitted program is expected to be of benefit to other physicists or physical chemists, or be an exemplar of good programming practice, or illustrate new or novel programming techniques which are of importance to some branch of computational physics or physical chemistry.
%
% Acceptable program descriptions can take different forms. The following Long Write-Up structure is a suggested structure but it is not obligatory. Actual structure will depend on the length of the program, the extent to which the algorithms or software have already been described in literature, and the detail provided in the user manual.

%Your manuscript and figure sources should be submitted through the Elsevier Editorial System (EES) by using the online submission tool at \\
% http://www.ees.elsevier.com/cpc.

%In addition to the manuscript you must supply: the program source code; job control scripts, where applicable; a README file giving the names and a brief description of all the files that make up the package and clear instructions on the installation and execution of the program; sample input and output data for at least one comprehensive test run; and, where appropriate, a user manual. These should be sent, via email as a compressed archive file, to the CPC Program Librarian at cpc@qub.ac.uk.

\end{abstract}

%%
%% Start line numbering here if you want
%%
% \linenumbers

% Computer program descriptions should contain the following
% PROGRAM SUMMARY.

{\bf PROGRAM SUMMARY}%/NEW VERSION PROGRAM SUMMARY}
  %Delete as appropriate.

\begin{small}
\noindent
{\em Manuscript Title:}{\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of finite-dimensional and affine Lie algebras                                       \\
{\em Authors:}Anton Nazarov                                                \\
{\em Program Title:}Affine.m                                          \\
{\em Journal Reference:}                                      \\
  %Leave blank, supplied by Elsevier.
{\em Catalogue identifier:}                                   \\
  %Leave blank, supplied by Elsevier.
{\em Licensing provisions:}none                                   \\
  %enter "none" if CPC non-profit use license is sufficient.
{\em Programming language:}Mathematica                                   \\
{\em Computer:}i386-i686, x86\textunderscore 64                                               \\
  %Computer(s) for which program has been designed.
{\em Operating system:} Linux, Windows, MacOS, Solaris                                       \\
  %Operating system(s) for which program has been designed.
{\em RAM:} 5-500 Mb                                              \\
  %RAM in bytes required to execute program with typical data.
%{\em Number of processors used:}                              \\
  %If more than one processor.
%{\em Supplementary material:}                                 \\
  % Fill in if necessary, otherwise leave out.
{\em Keywords:} Mathematica; Lie algebra; affine Lie algebra; Kac-Moody algebra; root system; weights; irreducible modules, CFT, Integrable systems\\
  % Please give some freely chosen keywords that we can use in a
  % cumulative keyword index.
{\em Classification:} 5 Computer Algebra, 4.2 Other algebras and groups                                         \\
  %Classify using CPC Program Library Subject Index, see (
  % http://cpc.cs.qub.ac.uk/subjectIndex/SUBJECT_index.html)
  %e.g. 4.4 Feynman diagrams, 5 Computer Algebra.
%{\em External routines/libraries:}                            \\
  % Fill in if necessary, otherwise leave out.
%{\em Subprograms used:}                                       \\
  %Fill in if necessary, otherwise leave out.
%{\em Catalogue identifier of previous version:}*              \\
  %Only required for a New Version summary, otherwise leave out.
%{\em Journal reference of previous version:}*                  \\
  %Only required for a New Version summary, otherwise leave out.
%{\em Does the new version supersede the previous version?:}*   \\
  %Only required for a New Version summary, otherwise leave out.
{\em Nature of problem:}\\
  %Describe the nature of the problem here.
Representation theory of finite-dimensional Lie algebras has many applications in different branches of physics, including elementary particle physics, molecular physics, nuclear physics. Representations of affine Lie algebras appear in string theories and two-dimensional conformal field theory used for the description of critical phenomena in two-dimensional systems. Also Lie symmetries play major role in study of quantum integrable systems.
   \\
{\em Solution method:}\\
  %Describe the method solution here.
We work with weights and roots of finite-dimensional and affine Lie algebras and use Weyl symmetry extensively. Central problems which are the computations of weight multiplicities, branching and fusion coefficients are solved using one general recurrent algorithm based on generalization of Weyl character formula. We also offer alternative implementation based on Freudenthal multiplicity formula which can be faster in some cases.
   \\
%{\em Reasons for the new version:}*\\
  %Only required for a New Version summary, otherwise leave out.
%   \\
%{\em Summary of revisions:}*\\
  %Only required for a New Version summary, otherwise leave out.
%   \\
{\em Restrictions:}\\
  %Describe any restrictions on the complexity of the problem here.
Computational complexity grows fast  with the rank of algebra, so computations for algebra of rank greater than 8 are non practical.
   \\
{\em Unusual features:}\\
  %Describe any unusual features of the program/problem here.
We offer the possibility to use traditional mathematical notation for objects in representation theory of Lie algebras in computations if {\bf Affine.m} is used in {\it Mathematica} notebook interface.
   \\
%{\em Additional comments:}\\
  %Provide any additional comments here.
%   \\
{\em Running time:}\\
  %Give an indication of the typical running time here.
From seconds to days depending on rank of algebra and complexity of representations.
   \\

% \begin{thebibliography}{0}
% \bibitem{1}Reference 1         % This list should only contain those items referenced in the
% \bibitem{2}Reference 2         % Program Summary section.
% \bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
%                                % This list is different from the bibliography at the end of
%                                % the Long Write-Up.
% \end{thebibliography}
% * Items marked with an asterisk are only required for new versions
% of programs previously published in the CPC Program Library.\\
\end{small}

%% main text
\section{Introduction}
\label{intro}

Representation theory of Lie algebras is of central importance for different areas of physics and mathematics. In physics Lie algebras are used to describe symmetries of quantum and classical systems. Computational methods in representation theory have a long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.

Most popular programs \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{fischbacher2002ilp}, \cite{coxweyl} are created to study representation theory of simple finite-dimensional Lie algebras. The main computational problems are the following:
\begin{enumerate}
\item Construction of root system which determine the properties of Lie algebra including its commutation relations.
\item Weyl group traversal which is important due to Weyl symmetry of root system and characters of representations.
\item Calculation of weight multiplicities, branching and fusion coefficients, which are essential for construction and study of representations.
\end{enumerate}
There are well-known algorithms for these tasks \cite{moody1982fast}, \cite{stembridge2001computational}, \cite{belinfante1989survey}, \cite{casselman1994machine}.
The third problem is most computation-intensive. There are two different recurrent algorithms which are based on the Weyl character formula and the Freudenthal multiplicity formula. In this paper we analyze them both.

Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and in a study of  integrable systems. But infinite-dimensional algebras are much harder to investigate and the number of available computer programs is much smaller in this case.

Affine Lie algebras \cite{kac1990idl} constitute important and tractable class of infinite-dimensional Lie algebras. They are constructed as central extensions of loop algebras of (semi-simple) finite-dimensional Lie algebras and appear naturally in a study of Wess-Zumino-Witten and coset models in conformal field theory \cite{Walton:1999xc}, \cite{difrancesco1997cft}, \cite{Goddard198588}, \cite{Dunbar:1992gh}.

The structure of affine Lie algebras allows to adapt for them computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}. The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of affine Lie algebras and representations was published in 1990. But we are not aware of software packages for popular computer algebra systems which can be used to extend these results.
We address this issue and present {\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.  We describe the features and limitations of the package in the present paper.  We also provide representation-theoretical background of implemented algorithms and present examples of computations relevant to physical applications.

The paper starts with an overview of Lie algebras and their representation theory (Sec. \ref{sec:theor-backgr}). Then we describe datastructures of {\bf Affine.m} used to present different objects related to Lie algebras and representations (Sec. \ref{sec:core-datastructures}) and discuss implemented algorithms (Sec. \ref{sec:comp-algor}). Next section consists of physically interesting examples (Sec. \ref{sec:examples}). The paper is concluded with the discussion of possible extensions and refinements (Sec. \ref{sec:conclusion}).

\section{Theoretical background}
\label{sec:theor-backgr}

In this section we remind necessary definitions and present formulae used in computations.

\subsection{Lie algebras of finite and affine types}
\label{sec:lie-algebras-finite}

{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it Lie bracket}. If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
\begin{equation}
  \label{eq:1}
  [X^{i},X^{j}]=\sum_{k} C^{ij}_{k} X^{k}
\end{equation}
Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to commutator. {\it Semisimple} Lie algebra is a direct sum of simple Lie algebras. In the present paper we treat simple and semisimple Lie algebras.

{\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
We denote the elements of basis of $\hfg$ by $H^{i}$.

Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$. {\it Weights} are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$

Special choice of basis gives compact description of commutation relations (\ref{eq:1}). This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).

{\it Loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
\begin{equation}
  \label{eq:6}
  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
\end{equation}
Central extension leads to the appearance of an additional term
\begin{equation}
  \label{eq:7}
   [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
\end{equation}
This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.

We do not treat twisted affine Lie algebras in the present paper.

\subsection{Modules, weights and roots}
\label{sec:weights-roots}

Let $\gf$ be a inite-dimensional or an affine Lie algebra.

Then $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
\begin{equation}
  \label{eq:2}
  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
\end{equation}
Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms of the  vector space $V$ with the commutator as a bracket.

For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by a special choice of basis $\{v_{j}\}$ in $V$:
\begin{equation}
  \label{eq:3}
  H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
\end{equation}
Eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$. Vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$. The  weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$. The weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of the weight subspace.

The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
\begin{equation}
  \label{eq:5}
  E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
\end{equation}
Module structure can be encoded by the formal character of a module
\begin{equation}
  \label{eq:10}
  \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
\end{equation}
Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
A character can be specialized by taking its value on some element $\xi$ of $\hf$.

Lie algebra is its own module with respect to a special kind of representation. The action that
defines this representation is called adjoint and is given by the bracket $ad_{X} Y=[X,Y]$. 
{\it Roots} are weights of the adjoint representation of $\gf$. They encode the commutation relations of algebra in the following way. Denote by $\Delta$ the set of roots. For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and the generators $E^{\alpha}, E^{-\alpha}$ such that
\begin{align}
  \label{eq:4}
  &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
  &\left[E^{\alpha},E^{\beta}\right]=
  \begin{cases}
    N_{\alpha,\beta} E^{\alpha+\beta}, & \mbox{if}\; \alpha+\beta\in \Delta\\
    \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
    0,&\mbox{otherwise}
  \end{cases}
\end{align}

Given the root system $\Delta$ we can choose the set of positive roots. This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
Elements of $-\Delta^{+}$ are called negative roots.

A positive root is {\it simple} if it cannot be written as a sum of positive roots. The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis in $\hfg^{*}$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive simultaneously. In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$. By numbering simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$. Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}. $\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}). {\it Comarcs} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.

Although for affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$. The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$. The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- the highest root of the algebra $\go$.
Note that root multiplicity $\mathrm{mult}(\alpha)$ for an affine Lie algebra root can be greater than one.

Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called the Borel subalgebra.

{\it Parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$. It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .

The {\it Weyl group} $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
\begin{equation}
  \label{eq:8}
  s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
\end{equation}
Root system and characters of representation are invariant with respect to the Weyl group  action. Root system can be reconstructed from the set of simple roots by the Weyl group transformations.

Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.

Consider an action of the element $s_{\alpha}s_{\alpha+\delta}$ of the Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ being a simple root of the underlying finite-dimensional Lie algebra $\gf$. Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$. So the Weyl group can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to roots of $\gf$.

A Weyl group element can be presented as a product of elementary reflections in multiple ways. Number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$. We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for the parity of the number of Weyl reflections generating $w$.

Fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$. It is called a {\it main Weyl chamber}.

The {\it Cartan matrix} $A$ is defined by products of simple roots
\begin{equation}
  \label{eq:9}
  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}
\end{equation}
and can be used for a compact description of Lie algebra commutation relations in the Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.

Form \eqref{eq:9} induces a basis dual  to the simple
roots basis. It is called the {\it fundamental weights basis}. We denote
its elements by $\omega_i$:
\begin{equation}
  \label{eq:20}
  \langle\omega_i,\alpha_j\rangle=\frac{2(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
\end{equation}
For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$. For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$. Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.

 The sum of fundamental weights $\rho=\sum_{i} \omega_{i}$ is called a {\it Weyl vector}. It is an important tool in representation theory.

\subsection{Highest weight modules}
\label{sec:high-weight-modul}

We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e. if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).

Highest weight module $V^{\mu}$ contains a single highest weight $\mu$, all the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.

The most simple type of highest weight modules is the Verma module
$M^{\mu}$. Its space can be defined as a module
\begin{equation}
  \label{eq:17}
  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}),
\end{equation}
with respect to a multiplication in $U(\gf)$ and
$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part. Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D^{\lambda}(\bff_{+})$.

Weight multiplicities in Verma modules can be found by applying the Weyl
character formula
\begin{equation}
  \label{eq:11}
  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
\end{equation}
Here we have used the Weyl denominator identity
\begin{equation}
  \label{eq:12}
  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
\end{equation}
and $\epsilon \left( w\right) :=\det \left( w\right)$ is equal to 
the parity of the sequence of Weyl reflections generating $w$.

Verma module $M^{\mu}$ has the unique maximal submodule and the
unique nontrivial simple quotient $L^{\mu}$ which is an
{\it irreducible highest weight module}.

Irreducible highest weight modules have no non-trivial submodules. 
The Weyl character formula for
irreducible highest weight modules is
\begin{equation}
  \label{eq:13}
  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
\end{equation}
Thus the character of an irreducible highest weight module can be
seen as a combination of characters of Verma modules. ( This
fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
(\cite{bernstein1976category,bernstein1971structure}, see also
\cite{humphreys2008representations}).)

Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
%% !!! \Delta_{p}?!
\begin{equation*}
M_{I}^{\mu}=U\left( \gf\right)\otimes _{U\left( \pf_{I}\right) }L_{\pf_{I}}^{\mu}.
\end{equation*}
Introduce a formal element $R_{I}:=\prod_{\alpha \in \Delta
^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
^{\mathrm{mult}(\alpha )}$. Then the character of a generalized
Verma module can be written as
\begin{equation}
  \label{eq:18}
  \mathrm{ch}M_{I}^{\mu}=\frac{1}{R_{I}}\mathrm{ch}L_{\pf_{I}}^{\mu }.
\end{equation}

%% Define external border of irreducible representation here

We can use the Weyl character formula to obtain recurrent relations for weight multiplicities -- important tools for calculations \cite{il2010folded,kulish4sfa}.

For irreducible highest-weight modules recurrent relations have the following form
\begin{equation}
\label{eq:14}
m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
-\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
\end{equation}
Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side. In case of Verma module it is just $\delta_{\xi,\mu}$. For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.

Other recurrent formula can be obtained from a study of Casimir
elements action on irreducible highest weight modules
\cite{humphreys1997introduction}:
\begin{equation}
  \label{eq:15}
  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
\end{equation}
It is called the Freudenthal multiplicity formula.
Note that it is applicable only to irreducible modules.

We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.

Now consider an algebra $\gf$ and a reductive subalgebra
$\af\subset \gf$. Simple roots $\beta_{i}$ of the subalgebra $\af$
can be presented as linear combinations of $\gf$-algebra roots
$\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j}
\alpha_{j},\ j=1,\dots,r_{\af}$.

Each irreducible $\gf$-module is also an $\af$-module, although
$L^{\mu}_{\gf}$ is in general not irreducible as $\af$-module. 
It can be
decomposed into a direct sum of irreducible $\af$-modules:
\begin{equation}
  \label{eq:16}
  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
\end{equation}
Coefficients in such a decomposition are called branching
coefficients.

It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. 
This traditional approach has serious limitations especially in case of affine Lie algebras. We discuss them in the end of section \ref{sec:comp-algor}.

Now we describe an alternative approach which is based on recurrent properties of branching coefficients. 
But before we proceed to these recurrent relations we need several additional definitions.

For a subalgebra $\af\subset \gf$ we introduce the subalgebra
$\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
orthogonal to $\hf_{\af}$,
\begin{equation*}
\hf_{\perp \af}^{\ast }:=\left\{ \eta \in \hf^{\ast }|\forall
h\in \hf_{\af};\eta \left( h\right) =0\right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
to roots of $\af$,
\begin{eqnarray}
\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
h\in \hf_{\af};\beta \left( h\right) =0\right\} ,
\label{delta a ort} \\
\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
}^{+}|\forall h\in \hf_{\af};\beta ^{+}\left( h\right) =0\right\} .
\notag
\end{eqnarray}
Let $W_{\afb}$ be a subgroup of $W$ generated by
reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
}}^{+}$. The subsystem $\Delta _{\afb}$ determines a 
subalgebra $\afb$ with the Cartan subalgebra $\hf_{\af%
_{\perp }}$.

The Cartan subalgebra $\frak{h}$ can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
\frak{h}_{\afb}\oplus \frak{h}_{\perp }$

We also introduce the notations
\begin{eqnarray}
\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\qquad
\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
\end{eqnarray}

For $\af$ and $\afb$ we consider the
corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\af_{\perp
}} $ and compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
D}_{\afb}$ of the injection:
\begin{equation}
\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho , \qquad
\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
_{\perp }}\rho .  \label{defect-ort}
\end{equation}

%%!!! Define P^+
For $\mu \in P^{+}$ consider the linked weights $\left\{ \left(
w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections
to
$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
\mathcal{D}_{\afb}$:
\begin{equation*}
\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
\end{equation*}
Among the weights $\left\{ \mu _{\af_{\perp
}}\left( w\right) |w\in W\right\} $ one can always choose those located in
the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
set of representatives $u$ for the classes $W/W_{\afb}$ such
that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
\overline{C_{\afb}}\right\} \quad .  \label{U-def}
\end{equation}
Thus we can form the subsets:
\begin{equation}
\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
_{\perp }},\quad u\in U,  \label{mu-a}
\end{equation}
and
\begin{equation}
\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
\label{mu-a-tilda}
\end{equation}

Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
since it is built on a subset of roots of the algebra $\mathfrak{g}$.

Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients. If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.

Now we can use the Weyl character formula to write a
recurrent relation \cite{2010arXiv1007.0318L} for signed branching
coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
injection $\af\hookrightarrow \gf$:
\begin{equation}
\begin{array}{c}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right.  \\
\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
}\right) .
\end{array}
\label{recurrent-rel}
\end{equation}
The recursion is governed by the set $\Gamma _{\af\rightarrow \gf}$ called the injection fan. The latter is defined by the
carrier set $\left\{ \xi \right\} _{\af\rightarrow \gf}$ for the
coefficient function $s(\xi )$
\begin{equation*}
\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}:=\left\{
\xi \in P_{\widetilde{\af}}|s(\xi )\neq 0\right\}
\end{equation*}
appearing in the expansion
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\widetilde{\af}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
_{\af}(\pi _{\widetilde{\af}}\alpha )}=-\sum_{\gamma \in P_{%
\widetilde{\af}}}s(\gamma )e^{-\gamma };\quad
\end{equation}
The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
\right\} $ -- and the zero element is to be eliminated:
\begin{equation}
\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma
_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
\end{equation}
Formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.

If the root system of $\afb$ is generated by some subset of $\gf$
simple roots $\alpha_{1},\dots,\alpha_{r}$ then the recurrent
relation (\ref{recurrent-rel}) is connected with the generalized
Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules
\cite{2011arXiv1102.1702L}.

Another particular case of this formula is connected with tensor
product decompositions. Consider the tensor product of two
irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$. It is also a
$\gf$-module but not irreducible in general. So
\begin{equation}
  \label{eq:19}
  L^{\mu}\otimes L^{\nu}=\bigoplus_{\gamma} f^{\mu\nu}_{\gamma}L^{\gamma}
\end{equation}
The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion
coefficients. The problem of computation of fusion coefficients is
equivalent to branching problem for the diagonal subalgebra
$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).

In the case of affine Lie algebras $\gf, \af$  the multiplicities
$m_{\nu}$ and the corresponding branching coefficients $b_{\nu}$
can be regarded as the coefficients in power series decomposition
of string and branching functions correspondingly:
\begin{align}
  \label{eq:21}
  &\sigma_{\nu}(q)=\sum_{n=0}^{\infty} m_{\nu-n\delta} q^n, \quad \nu=\sum_j c_j \omega_j,\quad c_j\geq 0\\
  & b_{\nu}(q)=\sum_{n=0}^{\infty} b_{\nu-n\delta} q^n,\quad  \nu=\sum_j c_j \omega_j, \quad c_j\geq 0
\end{align}
String and branching functions have  modular and analytic properties which are important for conformal field theory, especially in  coset models and the study of CFT on higher genus surfaces \cite{kac1988modular}, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}.

{\bf Affine.m}  calculates weight multiplicities and branching coefficients for affine Lie algebras up to some finite grade. We present examples of computations in Sections \ref{sec:string-funct-affine}, \ref{sec:branch-funct-coset}. Now we proceed to the description of datastructures and algorithms implemented in {\bf Affine.m}.

\section{Core datastructures}
\label{sec:core-datastructures} Having introduced necessary
mathematical objects, problems and relations we now describe the
related datastructures of {\bf Affine.m}. Although {\it
Mathematica} is untyped language it is possible to create
structured objects and do type checks with patterns
\cite{shifrinmathematica}, \cite{maeder2000computer}.
\subsection{Weights}
\label{sec:weights}

Weights are represented  by two data-structures: \lstinline{finiteWeight} for finite-dimensional Lie algebras and \lstinline{affineWeight}  for affine.

Internally the finite weight is a \lstinline{List} with the
\lstinline{Head} \lstinline{finiteWeight}, its components are the
coordinates of the weight in the orthogonal Bourbaki  basis
\cite{bourbaki2002lie}.

Affine weight is an extension of a finite weight by supplying it
with level and grade coordinates. There is a set of functions
defined for finite and affine weights. The complete list can be
found in  online help of the package. The most important
are definitions of addition, multiplication by a number and a
scalar product (bilinear form) for weights. These definitions
allow to use traditional notation when working with {\bf
Affine.m}:
\begin{lstlisting}
  w=makeFiniteWeight[{1,0,3}];
  v=makeFiniteWeight[{3,2,1}];
  2*w+v==makeFiniteWeight[{5,2,7}]
  w.v==6
\end{lstlisting}

The use of orthogonal basis in the internal structure of weights allows us to work with weights without complete specification of root system which is useful for study of branching, since roots of the subalgebra can be specified by hand.

\subsection{Root systems}
\label{sec:root-systems}

To specify an algebra of finite or affine type it is enough to fix
its root system. Root systems are represented by two datatypes
\lstinline{finiteRootSystem} and \lstinline{affineRootSystem}. The
latter is an extension of the former. We offer several different
constructors for these datastructures. It is possible to specify
the set of simple roots explicitly, for example to study the
subalgebra $B_2\subset B_4$ we can use the definition
\begin{lstlisting}
  b2b4=makeFiniteRootSystem[ { {1,-1,0,0}, {0,1,0,0} } ]
\end{lstlisting}
There are constructors for root systems of simple finite-dimensional Lie algebras:
\begin{lstlisting}
  b2=makeSimpleRootSystem[B,2]
\end{lstlisting}
We use typographic features of {\it Mathematica} frontend to offer mathematical notation for simple Lie algebras:

\begin{lstlisting}[mathescape=true]
  $B_2$ == makeFiniteRootSystem[ { {1, -1}, {0, 1} }]
\end{lstlisting}

Non-twisted affine root systems can be created as affine extensions of finte root systems, e.g.
\begin{lstlisting}
  b2affine = makeAffineExtension[b2]
\end{lstlisting}
In notebook interface this can be written simply as $\hat{B}_2$.

Semisimple Lie algebras can be created as sums of simple:
\begin{lstlisting}[mathescape=true]
  $A_1\oplus A_1$ == finiteRootSystem[2, 2, {finiteWeight[2, {1, 0}], finiteWeight[2, {0, 1}]}]
\end{lstlisting}
%% The problem is here

Predicate \lstinline{rootSystemQ} checks if the object is root systems of finite or affine type.

List of simple roots is the property of root system so it is accessed as \lstinline{rs[simpleRoots]}.

We have implemented several functions to get major properties of root systems. Weyl vector is given by the function \lstinline{rho[rs_?rootSystemQ]}:
\begin{lstlisting}[label=list:1]
  In[1]  =  rho[b2]
  Out[1]  =  finiteWeight[2, {3/2, 1/2}]
\end{lstlisting}
Positive roots can be constructed with \lstinline{positiveRoots[rs_?rootSystemQ]}. For an affine Lie algebra this and related functions return the list up to fixed grade. This grade limit is set through the value of \lstinline{rs[gradeLimit]} which is equal to 10 by default. List of roots (up to \lstinline{gradeLimit}) is returned by \lstinline{roots[rs]}. Cartan matrix and fundamental weights are calculated by the functions \lstinline{cartanMatrix} and \lstinline{fundamentalWeights} correspondingly.

It is possible to specify a weight of a Lie algebra by its Dynkin labels
\begin{lstlisting}
  weight[b2][1,2] == makeFiniteWeight[{2, 1}]
\end{lstlisting}
The function \lstinline{dynkinLabels[rs_?rootSystemQ][wg_?weightQ]} returns Dynkin labels of weight \lstinline{wg} in the root system \lstinline{rs}.

Elements of Weyl group are specified by the set of indices of reflections, so the element  $w=s_{1}s_{2}s_{1}$ of the Weyl group of algebra $B_{2}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}. Then it can be applied to the weights:
\begin{lstlisting}
  w = weylGroupElement[b2][1,2,1];
  w @ makeFiniteWeight[{1,0}] == makeFiniteWeight[{-1,0}]
\end{lstlisting}

Computation of lexicographically minimal form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching in {\it Mathematica}. In \cite{KallenShortlex} rewrite rules for simple finite dimensional and affine Lie algebras are presented as {\it Mathematica} patterns. Our presentation of Weyl group elements is compatible with the code of \cite{KallenShortlex}
\begin{lstlisting}[mathescape=true]
  In[1]  = $<<$A3reduce;
           reduce[s[1,2,1,2,1,3,2,1,1]]
  Out[1] = s[2, 3, 2]

  In[2]  = (weylGroupElement[$A_{3}$] @@ reduce[s[1,2,1,2,1,3,2,1,1]]) @ weight[$A_{3}$][-1,-2,-1]
  Out[2] = finiteWeight[4, {-2, 2, 1, -1}]

  In[3]  = dynkinLabels[$A_{3}$][Out[2]]
  Out[3] = {-4, 1, 2}
\end{lstlisting}

\subsection{Formal elements}
\label{sec:formal-elements}

We represent formal characters of representations by special structure \lstinline{formalElement}. This structure is a hash-table implemented with \lstinline{DownValues}. The keys are weights at the exponents and the values are the  corresponding multiplicities. \lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]! creates data-structure which represents the element $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ of the formal algebra $\mathcal{E}$. The operations in $\mathcal{E}$ are implemented for \lstinline{formalElement} data-type: formal elements can be added, multiplied by a number or by an exponent of a weight. There exists also a multiplication of formal elements but no division.
\begin{lstlisting}[mathescape=true]
  In[1]  = makeFormalElement[{makeFiniteWeight[{1,1}],makeFiniteWeight[{0,0}]},{1,2}] *
             (2 * Exp[makeFiniteWeight[{1,0}]] *
             makeFormalElement[{makeFiniteWeight[{1,1}],makeFiniteWeight[{0,0}]},{1,2}]);
  In[2]  = In[1][weights]
  Out[2] = {finiteWeight[2, {1, 0}], finiteWeight[2, {2, 1}], finiteWeight[2, {3, 2}]}

  In[3]  = In[1][multiplicities]
  Out[3] = {8, 8, 2}
\end{lstlisting}

\subsection{Modules}
\label{sec:modules}

{\bf Affine.m} can be used to study different kinds of modules, i.e. Verma modules, irreducible modules and parabolic Verma modules.  We need datastructure \lstinline{module} to represent generic module of Lie algebra $\gf$. Module properties can be deduced from its set of singular weights using Weyl character formulae \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}. Set of singular weights can have Weyl symmetry. It can be a symmetry with respect to the Weyl group $W_{\gf}$ or with respect to some subalgebra $W_{\af}$ as in the case of parabolic Verma modules. Then it is possible to study only the main Weyl chamber $C_{\af}$. To use this symmetry generic constructor for \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],limit:10}. Here \lstinline{rs} is the root system of the Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is the root system corresponding to the Weyl group $W_{\af}$ which is the (anti-)symmetry of the set of singular weights. Parameter \lstinline{limit} limits computation for infinite-dimensional modules such as Verma or parabolic Verma.
There are several specialized constructors for different types of highest weight modules:
\begin{lstlisting}[mathescape=true]
vm=makeVermaModule[$B_{2}$][{2,1}];
pm=makeParabolicVermaModule[$B_{2}$][weight[$B_{2}$][2,1],{1}];
im=makeIrreducibleModule[$B_{2}$][2,1];
GraphicsRow[textPlot/@{im,vm,pm}]
$\includegraphics[width=130mm]{figures/irrep-verma-pverma.pdf}$
\end{lstlisting}

As we already stated properties of a module are encoded by its singular element. Function \lstinline{singularElement[m_module]} returns singular element of a module as \lstinline{formalElement} datastructure. Character (up to \lstinline{limit} for (parabolic) Verma modules) is returned by the function \lstinline{character[m_module]}. Direct sum of modules is a module and we use natural notation
\begin{lstlisting}[mathescape=true]
im1=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
im2=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][1,2]];
textPlot[im1$\oplus$ im2]
$\includegraphics[width=60mm]{figures/irrep-sum.pdf}$
\end{lstlisting}

The tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
\begin{lstlisting}[mathescape=true]
textPlot[makeIrreducibleModule[$A_{1}$][5]$\otimes$ makeIrreducibleModule[$A_{1}$][3]];
$\includegraphics[width=60mm]{figures/tensor-product.pdf}$
\end{lstlisting}
\section{Computational algorithms}
\label{sec:comp-algor}

As we have already stated in section \ref{sec:high-weight-modul} there exist two recurrent relations which can be used to calculate weight multiplicities in irreducible modules. Both algorithms proceed in the following way to calculate weight multiplicities:
\begin{enumerate}
\item Create the list of weights in the main Weyl chamber by subtracting all possible combinations of simple roots from the highest weight (e.g. for finite-dimensional algebra subtract $\alpha_{1}$ from $\mu$ while inside $\bar C$, then subtract $\alpha_{2}$ from all the weights already obtained etc).
\item Sort the list of weights by their product with the Weyl vector.
\item Use a recurrent formula. If the weight required for recurrent computation is outside the main chamber use the Weyl symmetry.
\end{enumerate}
The difference in the performance of algorithms is in the number of previous values required to get the multiplicity of weight under consideration. For  the Weyl formula based recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in the Weyl group (if we are far from the boundary of representation diagram). When the Freudenthal formula \eqref{eq:15} is used number of previous values grows with the distance from the external border of representation. So the Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
Note that the Freudenthal formula is valid for irreducible modules only, so it can not be used to study (generalized) Verma modules.

We have made some experiments with our implementations of the Freudenthal formula and formula \eqref{eq:15} and have got Figure  \ref{fig:freudenthal-racah-times}, which depicts the dependence of the computation time on the number of weights in a module.

\begin{figure}[h]
  \noindent\centering{
    \includegraphics[width=80mm]{figures/timing.pdf}
  }
  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{eq:14} (solid) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
\label{fig:freudenthal-racah-times}

\end{figure}

In the calculation of branching coefficients the application of the Freudenthal formula requires a complete construction of formal characters of an algebra module and all the representations of a subalgebra. It is impractical when the rank of algebra and subalgebra are big, for example for maximal subalgebras.

Alternative algorithm which was presented in the paper \cite{2010arXiv1007.0318L}  contains the following steps:

\begin{enumerate}
\item  Construct the root system $\Delta _{\af}$ for the embedding $%
\af\rightarrow \frak{g}$.

\item  Select all the positive roots $\alpha \in \Delta ^{+}$ orthogonal
to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.

\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. Relation
 (\ref{eq:6}) defines the sign function
 $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
 $\gamma_0$ is to be subtracted to get the fan:
 $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}$.

\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
)-\rho ;\;w \in W\right\} $ of singular weights for the $\frak{g}$%
-module $L^{(\mu )}$.

\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
\af_{\perp }}}}\right\} $. Since the set $\Delta_{\afb }^{+}$ is fixed
we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
\af_{\perp }}}}$ (by computing its scalar product with the fundamental
weights of $\afb^{+}$).

\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
calculate dimensions of the corresponding modules, $\mathrm{\dim }\left(
L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
}\left( u\right) }\right) $, using the Weyl dimension formula and construct
the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.

\item  Calculate the anomalous branching coefficients using 
recurrent relation (\ref{recurrent-rel}) and select among them those
corresponding to the weights in the main Weyl
chamber $\overline{C_{\af}}$.
\end{enumerate}

We can speed up the algorithm by
one-time computation of the representatives of the conjugate classes $%
W/W_{\afb }$.

Consider the regular embedding $B_{2}\subset B_{4}$. In this case the fan consists of 24 elements. In order to decompose $B_{4}$ module we need to construct the subset of singular weights of the module which projects to the main Weyl chamber of the subalgebra $B_{2}$. The full set of singular weights consists of 384 elements. The required subset contains at most 48 elements. So the time for the construction of this required subset is negligible if the number of branching coefficients is greater than that. We may estimate the total number of required operations for the computation of branching coefficients as the product of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients and the number of elements in the fan. In the case of a direct algorithm we need to compute the multiplicities for each module in the decomposition, so the number of operations grows faster than the square of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients.

To further illustrate this performance issue we include Figure \ref{fig:branching} where we show the time required for computations of branching coefficients for $B_{3}\subset B_{4}$.

\begin{figure}[h]
  \noindent\centering{
   \includegraphics[width=100mm]{figures/branching-timing.pdf}
  }
  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{recurrent-rel} (solid) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
  \label{fig:branching}
\end{figure}

\section{Examples}
\label{sec:examples}
In this section we present some examples of computations available with {\bf Affine.m} with the code required to produce these results.

\subsection{Tensor product decompositon for finite-dimensional Lie algebras}
\label{sec:tens-prod-decomp}

Computation of fusion coefficients for the decomposition of tensor product of highest-weight modules to the direct sum of irreducible modules has numerous applications in physics. For example, we can consider the spin of a composite system such as an atom. Another interesting example is integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of a Lie algebra $\gf$ with a $\gf$-invariant Hamiltonian $H$, describing the nearest-neighbour spin-spin interaction. In order to solve such a system, i.e. to find eigenstates of the Hamiltonian, we need to decompose $L^{\otimes N}$ into the direct sum of irreducible $\gf$-modules of lower dimension and diagonalize the Hamiltonian on these modules.

For fundamental representations of simple Lie algebras it is sometimes possible to get an analytic result describing the dependence of decomposition coefficients on $N$ (See \cite{LyakhovskyPostnova2011}). Our code provides numerical values and can be used to check this analytic results.

Consider a tensor power of $B_{2}$ the first fundamental representation $\left(L^{[1,0]}\right)^{\otimes 4}$. Decomposition coefficients are just the branching
 coefficients for the tensor power module reduced to the diagonal subalgebra $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$. So the following code calculates these coefficients:
\begin{lstlisting}[mathescape=true]
fm = makeIrreducibleModule[$B_{2}$][1, 0];
tp = ((fm$\otimes$ ]fm)$\otimes$ fm)$\otimes$]fm;
subs = makeFiniteRootSystem[
  {1/4*{1, -1, 1, -1, 1, -1, 1, -1}, 
   1/4*{0, 1, 0, 1, 0, 1, 0, 1}}];
bc = branching[tp, subs];
{bc[#], dynkinLabels[subs][#]} & /@ bc[weights]
\end{lstlisting}
It produces a list of highest weights and tensor product decomposition coefficients:
\begin{lstlisting}
{{1, {4, 0}}, {3, {2, 2}}, {0, {3, 0}}, 
{2, {0, 4}}, {3, {1, 2}}, {6, {2, 0}}, 
{6, {0, 2}}, {1, {1, 0}}, {3, {0, 0}}}]
\end{lstlisting}

Returning to the problem of spin chain Hamiltonian diagonalization we can see that instead of diagonalizing operator in space of dimension $625$ we can diagonalize operators in the spaces of dimensions $55, 81, 30, 35, 35, 14, 10, 5, 1$.

\subsection{Branching and parabolic Verma modules}
\label{sec:branch-parab-verma}

We illustrate the generalized BGG-resolution by the diagrams of $G_{2}$ parabolic Verma modules which appear in the decomposition of irreducible module $L^{[1,1]}_{G_{2}}$:
\begin{equation}
\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
u\right) }.  \label{char-in-gen-verma-mod}
\end{equation}
The character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, characters of the generalized Verma modules in decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}. Characters in the upper row appear in \eqref{char-in-gen-verma-mod} with positive sign and in the lower row -- with negative.

\begin{figure}[h]
  \noindent\centering{
    \includegraphics[width=80mm]{figures/G2-irrep.pdf}
  }
  \caption{Character of the irreducible $G_{2}$-module $L^{[1,1]}$}
  \label{branching-bgg}
\end{figure}
\begin{figure}[h]
  \noindent\centering{
    \includegraphics[width=150mm]{figures/G2-pverma.pdf}
  }
  \caption{Characters of $G_{2}$ generalized Verma modules appearing in the decomposition of $L^{[1,1]}$. Parabolic Verma modules in the upper row appear in the decomposition with a positive sign, in the lower row -- with a negative.}
  \label{g2-pverma}
\end{figure}

\subsection{String functions of affine Lie algebras and CFT models}
\label{sec:string-funct-affine}

String functions can be used to present formal characters of affine Lie algebra highest weight representation. They have interesting analytic and modular properties \cite{kac1990idl,kac1988modular,kac1984infinite}.

{\bf Affine.m} produces power series decomposition for string functions. Consider an affine Lie algebra $\hat{sl(3)}=\hat A_{2}$ and its highest weight module $L^{(1,0,0)}$. To get the string functions we can use the code:
\begin{lstlisting}[mathescape=true]
stringFunctions[$\hat A_2$,{1,1,2}]
{{0, 0, 4}, 
  $2 q + 10 q^2 + 40 q^3 + 133 q^4 + 398 q^5 + 1084 q^6 + 2760 q^7 + 6632 q^8 + 15214 q^9 + 33508 q^{10}$}, 
{{0, 3, 1}, 
  $2 q + 12 q^2 + 49 q^3 + 166 q^4 + 494 q^5 + 1340 q^6 + 3387 q^7 + 8086 q^8 + 18415 q^9 + 40302 q^{10}$}, 
{{1, 1, 2}, 
  $1 + 6 q + 27 q^2 + 96 q^3 + 298 q^4 + 836 q^5 + 2173 q^6 + 5310 q^7 + 12341 q^8 + 27486 q^9 + 59029 q^{10}$}, 
{{2, 2, 0}, 
  $1 + 8 q + 35 q^2 + 124 q^3 + 379 q^4 + 1052 q^5 + 2700 q^6 + 6536 q^7 + 15047 q^8 + 33248 q^9 + 70877 q^{10}$}, 
{{3, 0, 1}, 
  $2 + 12 q + 49 q^2 + 166 q^3 + 494 q^4 + 1340 q^5 + 3387 q^6 + 8086 q^7 + 18415 q^8 + 40302 q^9 + 85226 q^{10}$}
\end{lstlisting}
Similarly for the affine Lie algebra $\hat G_{2}$ we get
\begin{lstlisting}[mathescape=true]
stringFunctions[$\hat G_2$,{1,1,0}]
{{2, 0, 0}, 
  $1 + 8 q + 37 q^2 + 138 q^3 + 431 q^4 + 1227 q^5 + 3208 q^6 + 7901 q^7$}, 
{{0, 0, 1}, 
  $3 q + 18 q^2 + 73 q^3 + 247 q^4 + 736 q^5 + 2000 q^6 + 5070 q^7$}, 
{{1, 1, 0},
  $1 + 7 q + 32 q^2 + 117 q^3 + 370 q^4 + 1055 q^5 + 2780 q^6 + 6880 q^7$}, 
{{0, 2, 0}, 
  $3 q + 15 q^2 + 63 q^3 + 210 q^4 + 633 q^5 + 1725 q^6 + 4407 q^7$}
\end{lstlisting}

\subsection{Branching functions and coset models of conformal field theory}
\label{sec:branch-funct-coset}

It is believed that most rational models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$. These models can be studied as gauge theories \cite{Hwang:1994yr, hwang1993brst}.

Branching functions for an embedding $\af\subset\gf$ are the partition functions of CFT on the torus (see \cite{difrancesco1997cft}).

As a first example we show how to construct branching functions for the embedding $\hat A_{1}\to \hat B_{2}$ up to the tenth grade:
\begin{lstlisting}[mathescape=true]
branchingFunctions[$\hat B_{2}$,makeAffineExtension[makeFiniteRootSystem[{{1, 1}}]], {1, 1, 1}]

 {{3, 0}, 
  $2 + 14 q + 52 q^2 + 154 q^3 + 410 q^4 + 994 q^5 + 2248 q^6 + 4832 q^7 + 9934 q^8 + 19680 q^9 + 37802 q^{10}$},
 {{2, 1}, 
  $4 + 20 q + 72 q^2 + 220 q^3 + 584 q^4 + 1424 q^5 + 3248 q^6 + 7012 q^7 + 14488 q^8 + 28844 q^9 + 55616 q^{10}$},
 {{0, 3}, 
  $4 q + 20 q^2 + 68 q^3 + 200 q^4 + 516 q^5 + 1224 q^6 + 2736 q^7 + 5808 q^8 + 11820 q^9 + 23236 q^{10}$},
 {{1, 2}, 
  $2 + 14 q + 54 q^2 + 168 q^3 + 462 q^4 + 1148 q^5 + 2656 q^6 + 5812 q^7 + 12130 q^8 + 24358 q^9 + 47328 q^{10}$}
\end{lstlisting}

Another example demonstrates the computation of branching functions for the regular embedding $\hat B_{2}\subset \hat C_{3}$:
\begin{lstlisting}[mathescape=true]
sub=makeAffineExtension[parabolicSubalgebra[$C_{3}$][2,3]];
branchingFunctions[$\hat C_{3}$,sub, {2, 0, 0, 0}]

{{0, 1, 0}, 
  $2 q - 20 q^3 + 24 q^4 + 82 q^5 - 320 q^6 + 108 q^7$}, 
{{1, 0, 0}, 
  $1 - q - 8 q^2 + 19 q^3 + 16 q^4 - 156 q^5 + 205 q^6 + 640 q^7$}, 
{{0, 0, 1}, 
  $q - 5 q^3 + 7 q^5$}
\end{lstlisting}

\section{Conclusion}
\label{sec:conclusion}
We have presented the package {\bf Affine.m} for computations in representation theory of finite-dimensional and affine Lie algebras. It can be used to study Weyl symmetry, root systems, irreducible, Verma and parabolic Verma modules of finite-dimensional and affine Lie algebras.  In the present paper we have also discussed main ideas used for an implementation of the package and described most important notions of representation theory required to use {\bf Affine.m}.

We have demonstrated that recurrent approach based on the Weyl character formula is not only useful for calculations but also allows to establish connections with the (generalized) Bernstein-Bernstein-Gelfand resolution.

Also we have presented examples of computations with this package connected with problems of physics and mathematics.

In future versions of our software we are going to treat twisted affine Lie algebras, extended affine Lie algebras and provide more direct support for tensor product decompositions.

\section*{Acknowledgements}
\label{sec:acknowledgements}
I thank V.D. Lyakhovsky and O.Postnova for discussions and helpful comments.

The work is supported by the Chebyshev Laboratory
(Department of Mathematics and Mechanics, Saint-Petersburg State
University) under the grant 11.G34.31.0026 of the Government of the
Russian Federation.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix

\section{Software package}
\label{package}
The package can be freely downloaded from \url{http://github.com/naa/Affine}. To get the development code use the command
\begin{lstlisting}[language=bash]
 git clone git://github.com/naa/Affine.git
\end{lstlisting}

Contents of the package:
\begin{verbatim}
    Affine/                                root folder
      demo/                                  demonstrations
        demo.nb                                demo notebook
        paper.nb                               code for the paper
      doc/                                 documentation folder
        figures/                             figures in paper 
          timing.pdf                           diagram showing performance
          branching-timing.pdf                 ...  for branching coefficients  
          irrep-sum.pdf                        sum of B2 irreps
          irrep-verma-pverma.pdf               irrep, Verma, (p)Verma for B2
          G2-irrep.pdf                         irrep for G2
          G2-pverma.pdf                        parabolic Verma for G2
          tensor-product.pdf                   tensor product of A1-modules
        bibliography.bib                     bibliographic database
        paper.pdf                            present paper
        paper.tex                            paper source
        TODO.org                             list of issues
      src/                                 source folder
        affine.m                             main software package
      tests/                               unit tests folder
        tests.m                              unit tests
      README.markdown                      installation and usage notes
\end{verbatim}

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}         ==>>  [#]
%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
%%

%% References with bibTeX database:

  %   \section*{References}
  %   \label{sec:references}
  %   
  %   
  %   \bibliography{bibliography}
  %   \bibliographystyle{phcpc}
  %   %\bibliographystyle{model1-num-names}
  %   
  %   
  %   %% Authors are advised to submit their bibtex database files. They are
  %   %% requested to list a bibtex style file in the manuscript if they do
  %   %% not want to use elsarticle-num.bst.
  %   
  %   %% References without bibTeX database:
  %   
  %   % \begin{thebibliography}{00}
  %   
  %   %% \bibitem must have the following form:
  %   %%   \bibitem{key}...
  %   %%
  %   
  %   % \bibitem{}
  %   
  %   % \end{thebibliography}
  %   
  %   
  %

%%
%% End of file
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:

### 2011-09-28 AffineLieAlgebras/Thesis/common.tex
Copied two papers to thesis, which is recreated with disser style.

% Общие поля титульного листа диссертации и автореферата
\institution{Санкт-Петербургский Государственный Университет}

\topic{Бесконечномерные алгебры симметрии в моделях квантовой теории поля}

\author{Назаров Антон Андреевич}

\specnum{01.04.02}
\spec{Теоретическая физика}

\sa{Ляховский Владимир Дмитриевич}
\sastatus{д.~ф.-м.~н., проф.}

\city{Санкт-Петербург}
\date{\number\year}

% Общие разделы автореферата и диссертации
\mkcommonsect{actuality}{Актуальность работы}{%
Текст раздела. Ссылка~\cite{Yoffe_1993_AP_42_173}.
}

\mkcommonsect{objective}{Цель диссертационной работы}{%
Текст раздела
}

\mkcommonsect{novelty}{Научная новизна}{%
Текст раздела
}

\mkcommonsect{value}{Практическая значимость}{%
Текст раздела
}

\mkcommonsect{results}{%
На защиту выносятся следующие основные результаты и положения:}{%
Текст раздела
}

\mkcommonsect{approbation}{Апробация работы}{%
Текст раздела
}

\mkcommonsect{pub}{Публикации.}{%
Материалы диссертации опубликованы в $N$ печатных работах, из них $n_1$ статей в
рецензируемых журналах~\citemy{Ivanov_1999_Journal_17_173,
Petrov_2001_Journal_23_12321,Sidorov_2002_Journal_32_1531}, $n_2$ статей в
сборниках трудов конференций и $n_3$ тезисов докладов.
}

\mkcommonsect{contrib}{Личный вклад автора}{%
Текст раздела
}

\mkcommonsect{struct}{Структура и объем диссертации}{%
Текст раздела
}

### 2011-09-28 AffineLieAlgebras/Thesis/intro.tex
Copied two papers to thesis, which is recreated with disser style.

\intro

%
% Используемые далее команды определяются в файле common.tex.
%

% Актуальность работы
\actualitysection
\actualitytext

% Цель диссертационной работы
\objectivesection
\objectivetext

% Научная новизна
\noveltysection
\noveltytext

% Практическая ценность
\valuesection
\valuetext

% Результаты и положения, выносимые на защиту
\resultssection
\resultstext

% Апробация работы
\approbationsection
\approbationtext

% Публикации
\pubsection
\pubtext

% Личный вклад автора
\contribsection
\contribtext

% Структура и объем диссертации
\structsection
\structtext
Диссертация состоит из трех глав. В первой главе рассматривается теория представлений аффинных алгебр Ли. Обсуждаются проблемы построения представлений и вычисления правил ветвлений представлений алгебры на представления подалгебры. В разделе \ref{sec:branching}  выводятся рекуррентные соотношения для коэффициентов ветвления, в разделе \ref{sec:bgg} обсуждается связь ветвлений представлений с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда. Во второй главе рассматриваются практические алгоритмы для вычисления кратностей и коэффициентов ветвления и описывается пакет {\bf Affine.m} для системы компьютерной алгебры {\it Mathematica}, разработанный с использованием этих алгоритмов. В третьей главе рассмотрены приложения к моделям конформной теории поля. 
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:

### 2011-10-10 AffineLieAlgebras/Splints/paper.tex
Splints paper added to git

\documentclass[12pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsmath,amssymb,amsthm}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}

\newtheorem{Def}{Definition}[section]
\newtheorem{Cnj}[Def]{Conjecture}
\newtheorem{Prop}[Def]{Property}
\newtheorem{example}{Example}
\begin{document}

\title{Fan, splint and branching rules.}

\author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$ \\
  {\small $^1$ Department of High-energy and elementary particle physics, SPb State University}\\
  {\small 198904, Saint-Petersburg, Russia}\\
  {\small e-mail: lyakh1507@nm.ru}\\
  {\small$^{2}$ Chebyshev Laboratory,}\\
  {\small Department of Mathematics and Mechanics, SPb State University}\\
  {\small 199178, Saint-Petersburg, Russia}\\
  {\small email: antonnaz@gmail.com}}
\maketitle

\begin{abstract}
Splint of root system of simple Lie algebra appears naturally in the study of (regular) embedding of reductive subalgebra. It can be used to derive branching rules. We show that the use of splint drastically simplifies the derivation of branching functions. 
\end{abstract}

\section{Introduction}
\label{sec:Introduction} 
Splint $\phi$ of root system $\Delta_1$ to root system $\Delta$ is a bijective map of roots of $\Delta_{1}$ to (proper) subset of $\Delta$ which commutes with the addition in $\Delta_{1}$ and $\Delta$. 
\begin{equation*}
\phi:\Delta_1 \longrightarrow \Delta
\end{equation*}
\begin{equation*}
\phi \circ \alpha + \beta =\phi \circ \alpha + \phi \circ \beta,
\,\,\, \alpha,\beta \in \Delta_1
\end{equation*}

Note that image $Im(\phi)$ is not required to have the properties of root system except the addition rules equivalent to the addition rules in $\Delta_{1}$ (for pre-images). The term {\it splint} was introduce in paper \cite{richter2008splints} where the classification of splints for simple Lie algebras was obtained. The conjecture of the connection splint with injection fan was stated in the same paper. 
The fan $\Gamma \subset \Delta$ as the subset of root system describing recurrent properties of branching coefficients for maximal embeddings  was introduced in \cite{lyakhovsky1996rra}. Injection fan is an efficient tool for the study of branching rules. This construction was generalized to non-maximal embeddings and infinite-dimensional Lie algebras in  \cite{2010arXiv1007.0318L, ilyin812pbc}.

In present paper we study the connection of splint with the injection fan of regular embedding of reductive subalgebra ${\mathfrak a}$. We show that (under certain conditions described in section \ref{sec:stems and multiplicity functions}) splint is a natural tool for the reduction of simple Lie algebra $\gf$-modules to the modules of subalgebra $\af\rightarrow\gf$. The use of this tool allows us to state the main result of the present paper -- the one-to-one relationship between weight multiplicities of irreducible modules of splint and branching coefficients for the reduction $L^{\mu}_{{\mathfrak g}\downarrow {\mathfrak a}}$.

\section{Injections and splints}
\label{sec:Injections and splints}

Consider a simple Lie algebra $\mathfrak{g}$ and its regular
subalgebra $\mathfrak{a}\longrightarrow \mathfrak{g%
}$ such that $\mathfrak{a}$ is a reductive subalgebra $\mathfrak{a
\subset g}$ with correlated root spaces:
$\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset
\mathfrak{h}_{\mathfrak{g }}^{\ast }$. Let $\mathfrak{a}^S$ be a
semisimple summand of $\mathfrak{a}$, this means that
$\mathfrak{a}=\mathfrak{a}^S \oplus \mathfrak{a}(1)\oplus
\mathfrak{a}(1)\oplus \dots$. We shall consider $\mathfrak{a}^S$
to be a proper regular subalgebra and $\mathfrak{a}$ to be the
maximal subalgebra with $\mathfrak{a}^S$ fixed that is the rank
$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.

$r$ , $\left( r_{\mathfrak{a}^S}\right) $ --- the rank of
$\frak{g}$ $\left( \mathrm{{resp. }\mathfrak{a}^S}\right) $ ;

$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system;
$\Delta ^{+} $ $\left( \mathrm{{resp. }\Delta
_{\frak{a}}^{+}}\right) $--- the positive root system (of
$\frak{g}$ and $\frak{a}$ respectively);

$S\quad \left( S_{\frak{a}}\right) $ --- the system of simple roots (of $%
\frak{g}$ and $\frak{a}$ respectively);

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a%
}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots
,r_{\mathfrak{a}^S}\right) $;

$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl
group;

$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl
chamber;

$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
fundamental Weyl chamber;

$\epsilon \left( w\right) :=\left( -1\right)
^{\mathrm{length}(w)}$;

$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;

$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the
integrable module of $\frak{g}$ with the highest weight $\mu $\ ;
(resp. integrable $\frak{a}$ -module with the highest weight $\nu
$ );

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu
}\right) $ --- the weight diagram of $L^{\mu }$ (resp.
${}L_{\frak{a}}^{\nu }$ );

$P$ (resp. $P_{\frak{a}} $) \ --- the weight lattice;

$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight
lattice;

$\cal{E}$ (resp. $\cal{E}_{\frak{a}} $) \ --- the formal algebra;

$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu
\right)
}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ ,
(resp. $\xi \in L_{\frak{a}}^{\nu } $);

$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left(
L_{\frak{a}}^{\nu }\right) $)--- the formal character of $L^{\mu
}$ (resp. $L_{\frak{a}}^{\nu } $);

$ch\left( L^{\mu }\right)
 =\frac{\sum_{w\in W}\epsilon
(w)e^{w\circ (\mu +\rho )-\rho }}
{\prod_{\alpha \in \Delta
^{+}}
\left( 1-e^{-\alpha }\right) }
$ --- the Weyl formula;

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right)
\quad
$
(resp.
$
R_{\frak{a}}:
=\prod_{\alpha \in \Delta_{\frak{a}}^{+}}
\left( 1-e^{-\alpha }\right)
$
) --- the Weyl
denominator.

Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
\begin{equation*}
L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
\end{equation*}
\begin{equation}
\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
\label{branching1}
\end{equation}
For the modules we are interested in the Weyl formula for $\mathrm{ch}%
\left( L^{\mu }\right) $ can be written in terms of singular
elements \cite {humphreys1997introduction}
\begin{equation*}
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon
(w)e^{w(\mu +\rho )-\rho },
\end{equation*}
namely,
\begin{equation}
\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right)
}}{\Psi ^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right)
}}{R}. \label{Weyl-Kac2}
\end{equation}
The same is true for submodules $\mathrm{ch}\left(
L_{\frak{a}}^{\nu }\right) $ in (\ref{branching1})
\begin{equation*}
\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi
_{\frak{a}}^{\left(
\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}},
\end{equation*}
with
\begin{equation*}
\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
\end{equation*}

Applying formula (\ref{Weyl-Kac2}) to the branching rule
(\ref{branching1}) we get the relation connecting the singular
elements $\Psi ^{\left( \mu \right) }$ and $\Psi
_{\frak{a}}^{\left( \nu \right) }$ :
\begin{eqnarray}
 \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu
+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })}
&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })},
\notag  \label{eq:4} \\
\frac{\Psi ^{\left( \mu \right) }}{R}
&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}}.
\label{singular main}
\end{eqnarray}

In \cite
{2010arXiv1007.0318L} it was proven that branching coefficients $b_{\xi
}^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
\hookrightarrow \frak{g}$ are subject to the set of recurrent relations:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right.  \\
\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
}\right) .
\end{array}
\label{recurrent rel}
\end{equation}
where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $\frak{g}$ orthogonal to roots of $\frak{a}$
\begin{eqnarray}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
\label{delta a ort}
\end{eqnarray}
\begin{eqnarray}
\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\qquad
\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }
\end{eqnarray}
and $\pi$ is the projection operator. When the injection is maximal the projection becomes trivial and the relation (\ref{recurrent rel}) is simplified:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho }+\right.  \\
\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}%
}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
}\right) .
\end{array}
\label{recurrent relation max}
\end{equation}
The recursion is goverened by the set $\Gamma _{\frak{a}%
\rightarrow \frak{g}}$ called the injection fan. The latter is defined by the
carrier set $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the
coefficient function $s(\xi )$
\begin{equation*}
\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{
\xi \in P_{\frak{a}}|s(\xi )\neq 0\right\}
\end{equation*}
appearing in the expansion
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\frak{a}}^{+}}\left( 1-e^{
-\alpha }\right) =-\sum_{\gamma \in P_{%
\frak{a}}}s(\gamma )e^{-\gamma };\quad
\label{product}
\end{equation}

Now we remind two definitions introduced in \cite{richter2008splints}
\begin{Def}
Suppose $\Delta_0$ and $\Delta$ are root systems with the corresponding weight lattices $P_0$ and $P$.  Then $\phi$ is an ``embedding'', 
\begin{equation}
\phi:\left\{
\begin{array}{l}
\Delta_0\hookrightarrow\Delta,\\
P_0 \hookrightarrow P,
 \end{array}
\right.
\end{equation}
if \\
\noindent
(a) it injects $\Delta_0$ in $\Delta$, and \\
\noindent
(b) acts homomorphically with respect to the vector groups in $P_0$ and $P$:
$$\phi(\gamma)=\phi(\alpha)+\phi(\beta)$$
for any triple $\alpha,\beta,\gamma\in P_0$ such that $\gamma=\alpha+\beta$.
\end{Def}
$\phi$ induces an injection of formal algebras $ :{\cal{E}}_0 \longrightarrow \cal{E}$ and for the image ${\cal{E}}_i=Im_{\phi}\left( {\cal{E}}_0\right)$ one can consider its inverse
$\phi^{-1}:{\cal{E}}_i \longrightarrow {\cal{E}}_0$.

 Notice that one must distinguish two classes of embeddings: when the scalar product (defined by the Killing form) in the root space $P_0$ is invariant with respect to $\phi$ and when it is not $\phi$-invariant. The first embedding is called "metric" 
, the second -- "nonmetric". 
\begin{Def}
A root system $\Delta$ "splinters'' as $(\Delta_1,\Delta_2)$ if there are two embeddings
$\phi_1:\Delta_1\hookrightarrow\Delta$ and $\phi_2:\Delta_2\hookrightarrow\Delta$
where (a) $\Delta$ is the disjoint union of the images of $\phi_1$ and $\phi_2$ and
(b) neither the rank of $\Delta_1$ nor the rank of $\Delta_2$ exceeds the rank of $\Delta$.
\end{Def}
It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$.
Each component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $(\Delta_1,\Delta_2)$.

In \cite{richter2008splints} it was indicated that the injection fan technique used in \cite{lyakhovsky1996rra} is close to that of splints.

To demonstrate the relations between these instruments consider the case where
one of the stems $\Delta_1=\Delta_{\frak{a}}$ is a root system of a regular reductive subalgebra  $\frak{a}\hookrightarrow\frak{g}$. Then the second stem is $\Delta_{\frak{s}}:=\Delta_2=\Delta \setminus \Delta _{\frak{a}}$ can be translated into the product (\ref{product}) and defines the injection fan $\Gamma_{\frak{a}\hookrightarrow\frak{g}}$.

Thus we see that
\begin{Cnj}
Each splint of the type $\Delta \approx (\Delta_{\frak{a}},\Delta_{\frak{s}})$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ fixed by the product
\begin{equation}
\prod_{\beta \in  \Delta _{\frak{s}}^{+}}\left( 1-e^{
-\beta }\right) =-\sum_{\gamma \in P} s(\gamma )e^{-\gamma }\quad
\label{splint product}
\end{equation}
\end{Cnj}
In this case we say that the subalgebra $\frak{a}\hookrightarrow\frak{g}$ splinters $\Delta$ (and call $\frak{a}$ the "splinting subalgebra" of $\frak{g}$). In
\cite{richter2008splints} the splints are classified (see Appendix) and in the first three types one can easily see that one of the stems corresponds to a splinting subalgebra.

\section{How stems define multiplicity functions}
\label{sec:stems and multiplicity functions}

In this Section we consider the situation where  the splinting subalgebra is "larger"
than the Lie algebra $\frak{s}$ defined by the root system $\Delta_{\frak{s}\,0}=CoIm_{\phi} \left( \Delta_{\frak{s}}\right)$
(the details will be given below). In such a case to find branching coefficients for a splinting 
injection $\frak{a}\hookrightarrow\frak{g}$ means to find weight multiplicities for an irreducible $\frak{s}$-module $L^{\nu}_{\frak{s}}$ with 
the fixed highest weight $\nu$. Notice that $\frak{s}$ must not be a subalgebra of $\frak{g}$.

Let us return to relation (\ref{singular main}) and multiply both sides by $R_{\frak{a}}$: 
\begin{eqnarray}
 \frac{1}{\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })}\Psi_{\frak{g}} ^{\left( \mu \right) }
&=&
\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\Psi _{\frak{a}%
}^{\left( \nu \right) }.
\label{singular main-2}
\end{eqnarray}
Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{\frak{a}%
\rightarrow \frak{g}}$. 
Consider the highest weight module $L^{\nu}_{\frak{s}}$. An embedding
$\phi:\Delta_{\frak{s}\,0} \longrightarrow \Delta_{\frak{g}} $  sends the singular element         $\Psi_{\frak{s}} ^{\left( \nu \right)}$ into $ \Psi_{\frak{g}} ^{\left( \mu \right) }$.
Applying the inverse morphism $\phi^{-1}$ to the product 
$\left(\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })\right)^{-1}\phi\left(\Psi_{\frak{s}} ^{\left( \nu \right)}\right)$  
 one obtains the character of the module $L^{\nu}_{\frak{s}}$,

\begin{equation}
 \phi^{-1}\left( \frac{1}{\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })}\phi\left(\Psi_{\frak{s}} ^{\left( \nu \right)}\right)\right)
 =
 \frac{1}{\prod_{\beta \in \Delta_{\frak{s}\left(0\right)} ^{+}}(1-e^{-\beta })}\Psi_{\frak{s}} ^{\left( \nu \right)}
 =
 \mathrm{ch}\left( L_{\frak{s}}^{\nu }\right).
\label{inverse for stem}
\end{equation}
Our task is to prove that the singular element $\Psi_{\frak{g}} ^{\left( \mu \right) }$ contains the element $\Psi_{\frak{g}} ^{\left( \xi \right) }$ for a module $L^{\xi}_{\frak{s}}$ uniquely defined by $L^{\mu}_{\frak{g}}$ and that the branching coefficients $b_{\nu }^{(\mu )}$ in the r.h.s. of (\ref{singular main-2})  coincide with multiplicities $m_{\zeta}^{\left( \xi \right) }$ of the weights of $L^{\xi}_{\frak{s}}$.

For a highest weight irreducible module $L^{\mu}_{\frak{g}}$ the singular element $\Psi_{\frak{g}} ^{\left( \mu \right) }$ is an element of $\cal{E}$ corresponding to the shifted Weyl-orbit of the weight $\left( \mu + \rho \right) \in P^+$ and the sign function $\epsilon\left( w \right)$. It is convenient to use also unshifted singular elements  
\begin{equation}
 \Phi^{\left( \mu \right)}:= \Psi^{\left( \mu \right) }e^{\rho}.
 \label{definition Phi}
\end{equation}
In these terms the relation (\ref{singular main-2}) looks like
\begin{equation}
 \frac{e^{\rho_{\frak{g}}-\rho_{\frak{a}}}}{\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })}\Phi_{\frak{g}} ^{\left( \mu \right) }
=
\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\Phi _{\frak{a}%
}^{\left( \nu \right) }.
\label{singular main-3}
\end{equation}
The orbit that corresponds to $\Phi_{\frak{g}} ^{\left( \mu \right) }$ is completely defined by 
the set of edges $\left\{ \lambda_{i}\right\}_{i=1,\dots,r}$ adjusted to the end of the highest weight vector $\mu + \rho$. Let $\mu=\sum m_i \omega_i$ then 
\begin{equation}
 \lambda_i=-\left( m_i +1\right)\alpha_i .\quad i=1,\dots,r
\label{edge}
\end{equation}
Each weight $\mu + \rho + \lambda_i $ bears the sign coefficient $(-)$ in the singular element. The defining property of $\Phi_{\frak{g}} ^{\left( \mu \right) }$ is as follows. Consider any pair of edges $\lambda_i,\lambda_j$ and the corresponding weights $\mu + \rho $, $\mu + \rho + \lambda_i $ and $\mu + \rho + \lambda_j $. Apply the reflection $s_{\alpha_i}$ (or $s_{\alpha_j}$),  
\begin{equation}
 s_{\alpha_i}\circ
 \left\{
\begin{array}{l}
\left( \mu + \rho  \right)\\
\left( \mu + \rho + \lambda_i \right)\\
\left( \mu + \rho + \lambda_j \right)
 \end{array}
\right.
= 
  \left\{
\begin{array}{l}
\left( \mu + \rho + \lambda_i \right)\\
\left( \mu + \rho  \right)\\
\left( \mu + \rho + \lambda_i -  (m_j + 1) s_{\alpha_i}\circ \alpha_j\right)
 \end{array}
\right.
 \label{reflected triple}
\end{equation}

\begin{Prop}
 The edge $\lambda_{i,j}$ of $\Phi_{\frak{g}} ^{\left( \mu \right) }$ starting at the weight $\left( \mu + \rho + \lambda_i \right)$ along the root $- s_{\alpha_i}\circ \alpha_j$ has the same length in $( s_{\alpha_i}\circ \alpha_j )$ as $\lambda_j$ has in $\alpha_j$.
(The same is true for the edge $\lambda_{i,j}$, its length in $( s_{\alpha_j}\circ \alpha_i )$  is equal to the length of $\lambda_i$ in $\alpha_i$.)
\label{diagram property}
\end{Prop}
  In $\Phi_{\frak{g}} ^{\left( \mu \right) }$ the elements $e^{\left( \mu + \rho + \lambda_i -  (m_j + 1) s_{\alpha_i}\circ \alpha_j\right)}$ and  $e^{\left( \mu + \rho + \lambda_j -  (m_i + 1) s_{\alpha_j}\circ \alpha_i\right)}$
have the sign $(+)$.

From now on we consider splints for simple Lie algebras of the first three types according to the classification in \cite{richter2008splints}: 
$$\begin{array}{c c||c|c}
\hbox{type}
& \hspace{0.25 in}\Delta\hspace{0.25 in} & \hspace{0.25 in}\Delta_{\frak{a} }\hspace{0.25 in} & \hspace{0.25 in}\Delta _{\frak{s}}\hspace{0.25 in} \\
\hline
\hline
\hbox{(i)}     & G_2 & A_2 & A_2 \\
& F_4 & D_4 & D_4 \\
\hline
\hbox{(ii)} & B_r (r\geq 2) & D_r & rA_1 \\
    & C_r (r\geq 3) & D_r  & rA_1 \\
\hline
\hbox{(iii)}    & A_r (r\geq 2) & A_{r-1} & r A_1 \\
    & B_2 & A_1 & A_2 \\
\end{array}$$

Each row in the table gives a splint $(\Delta_{\frak{a} },\Delta_{\frak{s} })$ of the simple root system $\Delta$.
For these types:  
(i) Both $\Delta_{\frak{a} }$ and $\Delta_{\frak{s} }$ are embedded metrically, and $\Delta_{\frak{a} }\cong\Delta_{\frak{s} }$. 
(ii) Both $\Delta_{\frak{a} }$ and $\Delta_{\frak{s} }$ are embedded metrically, but $\Delta_{\frak{a} }$ and $\Delta_{\frak{s} }$ are not isomorphic.
(iii) Only $\Delta_{\frak{a} }$ is embedded metrically.

Splints induce a decomposition of the set $S=S_{\frak{c}} \cup S_{\frak{d}}$ where $S_{\frak{c}}=S \cap S_{\frak{a}}$ and $S_{\frak{d}}=S \cap S_{\frak{s}}$. It is easy to check that for all the splints we are interested in   the subset $S_{\frak{d}}$ is nonempty. It follows that in the set $\left\{ \lambda_{i}\right\}_{i=1,\dots,r}$ one can always find simple roots $\beta_k \in \Delta_{\frak{s}}$ and that the orbit corresponding to $\Phi_{\frak{g}} ^{\left( \mu \right) }$ contains edges 
\begin{equation}
 \lambda_k=-\left( m_k +1\right)\beta_k 
\label{beta edge}
\end{equation}
attached to the weight $\mu + \rho$. As far as $\Delta_{\frak{a}} $ is a root system and for any pair of simple roots from $S_{\frak{c}}$ the singular element $\Phi_{\frak{g}} ^{\left( \mu \right) }$ is a singular element for a set of $\frak{a}$-modules the property \ref{diagram property} is fulfilled. Consider $\alpha_l \in S_{\frak{c}}$ with the corresponding edge $ \lambda_l=-\left( m_l +1\right)\alpha_l $ and a root $\beta_l \in \Delta_{\frak{s}}$ whose  coimage in $\Delta_{\frak{s}0}$ is simple. The root $\beta_l $ is not simple in $\Delta$. Firstly suppose that $\beta_l =\alpha_l + \beta_k$. It is easily seen that the corresponding edge intersects the boundary plane of the fundamental chamber $\bar{C_{\frak{a}}}$ orthogonal  to the root  $\alpha_l$:
\begin{equation}
s_{\alpha_l}\left( \mu + \rho - p\beta_l\right)=s_{\alpha_l}\left( \mu + \rho \right) - p s_{\alpha_l}\beta_l=\mu + \rho - p\beta_l
\label{intersection}
\end{equation}
\begin{equation}
\mu + \rho - s_{\alpha_l}\left( \mu + \rho \right)=\left( m_l +1\right)\alpha_l =\left( m_l +1\right)\beta_l - \left( m_l +1\right)\beta_k=p\beta_l  - ps_{\alpha_l}\beta_l
\label{intersection}
\end{equation}
It follows that $p=\left( m_l +1\right)$ and $s_{\alpha_l}\beta_l=\beta_k$. Now apply the operator $s_{\beta_k}$ and find that the edge along the root $s_{\beta_k}\alpha_l$ attached at the weight $s_{\beta_k}(\mu + \rho)$ is also equal to $ -p s_{\beta_k}\alpha_l$. This means that for the triple of roots $\beta_k,\beta_l$ and $s_{\beta_k}\alpha_l$ in $\Delta_{\frak{s}}$ the edges $\lambda_k=-\left( m_k +1\right)\beta_k  $, $\lambda_l=-\left( m_l +1\right)\beta_l$ and $\lambda_{kl}=-\left( m_l +1\right)s_{\beta_k}\alpha_l$ have the property \ref{diagram property}. One can continue this procedure further in the 2-dimensional subspace    fixed by the roots $\beta_k$ and $beta_l$ and find the set of formal exponents that being supplied with the corresponding sign factors compose the coimage of the singular element of a module for the subalgebra in $\frak{s}$ (this subalgebra has rank $r=2$).

The same can be proven for any positive root $\beta_l \in \Delta$ that is simple in $\Delta_{\frak{s}0}$ and correspondingly for any $r=2$ subalgebra in $\frak{s}$. The latter means that to "find" a singular element of $\frak{s}$-module in $\Phi_{\frak{g}} ^{\left( \mu \right) }$ it is necessary to incorporate in it additional formal elements corresponding to the weights belonging to the boundary of the chamber $\bar{C_{\frak{a}}}$.

Now let us return to the relation (\ref{singular main-3}). One can add to $\Phi_{\frak{g}} ^{\left( \mu \right) }$ pairs of necessary formal elements with the opposite  signs.  Notice that all the additional weights belong to the boundaries of $\bar{C_{\frak{a}}}$. To form a singular element for an $\frak{s}$-module one must attribute to these weights the fixed signs. The same elements with the opposite signs are to be referred to the neighbor Weyl chambers of $\bar{C^{(l)}_{\frak{a}}}$ (the latter are connected with the main one by simple reflections $s_{\alpha_l}$). In fact one can repeat the procedure of finding additional singular weights in any Weyl chamber $\bar{C^{(m)}_{\frak{a}}}$ and in them additional singular weights always have the signs opposite to that in their neighbors. Thus without changing in fact the element $\Phi_{\frak{g}} ^{\left( \mu \right) }$ one can present it as a sum  
\begin{equation}
\Phi_{\frak{g}} ^{\left( \mu \right) }=\sum_{w \in W_{\frak{a}}} w \circ \left(e^{\rho_{\frak{a}}}\Psi^{\widetilde{\mu} + \rho_{\frak{s}}}\right)
\label{singular final}
\end{equation}
where the weight $\widetilde{\mu}=\sum m_k \omega_{\frak{s}}^k$ has the same Dynkin labels $m_k$ as in the corresponding decomposition $\mu=\sum m_k \omega_{\frak{g}}^k$. 
The decomposition (\ref{singular final}) provides the possibility to apply the factor
$\left(\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })\right)^{-1}$ to each summand of the singular element $\Phi_{\frak{g}} ^{\left( \mu \right) }$ separately because the sets of weights from different Weyl summands do not intersect. Taking into account the isomorphism $\phi$ one can see that in the main Weyl chamber $\bar{C_{\frak{a}}}$ the set of weights generated by the factor $\left(\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })\right)^{-1}$ is isomorphic with the weight diagram of the $\frak{s}$-module $L^{\widetilde{\mu}}_{\frak{s}}$. Finally one must restrict relation (\ref{singular main-3}) to 
$\bar{C_{\frak{a}}}$ and obtain the main result:
\begin{Prop}
\begin{equation}
 \frac{e^{\rho_{\frak{g}}}}{\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })}\left(\Psi^{\widetilde{\mu} + \rho_{\frak{s}}}\right)
=e^{\rho_{\frak{g}}}\left( \phi^{-1}\left( \mathcal{N}_{\frak{a}}^{\widetilde{\mu}
}\right)  \right)
=
\sum b_{\nu }^{(\mu )}e^{\nu}.
\label{singular main-4}
\end{equation}
\end{Prop}

\section{Examples}
\label{sec:examples}
\begin{example}
  Consider Lie algebra $A_{2} (\bf{sl}(3))$ and branching of its irreducible module $L^{(3,2)}$ into the modules of reductive subalgebra $A_{1}\oplus u(1)$ with root system spanned by first simple root of $A_{2}$. Singular element of $L^{(3,2)}$ is decomposition into the sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules and branching coefficients coincide weight multiplicities of $A_{1}\oplus A_{1}$-module (see Fig. \ref{fig:a2_splint}).

  \begin{figure}[h!bt]
  \noindent\centering{
   \includegraphics[width=120mm]{a2-a1}
  }
  \caption{Weyl group orbit (dotted) producing singular element of $A_{2}$-module $L^{(3,2)}$ and its decomposition into the sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules (dashed). Weight multiplicities of $A_{1}\oplus A_{1}$-module coincide with branching coefficients for the reduction $L^{(3,2)}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}

 \label{fig:a2_splint}
\end{figure}
\end{example}
\begin{example}
  Now consider Lie algebra $B_{2} (\bf{so}(5))$ and branching of its irreducible module $L^{(3,2)}$ into the modules of reductive subalgebra $A_{1}\oplus u(1)$ with root system spanned by first simple root of $B_{2}$. Singular element of $L^{(3,2)}$ is decomposition into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide weight multiplicities of $A_{2}$-module (see Fig. \ref{fig:b2_splint}).

  \begin{figure}[h!bt]
  \hspace*{-1.5cm}

   \includegraphics[width=75mm]{b2}
   \includegraphics[width=75mm]{b2-a2-a1}
  \caption{$B_{2}$-module $L^{(3,2)}$ is shown on the left. Weight multiplicities are indicated. Contour of singular element is shown by dotted line. Right figure represents the decomposition of  $L^{(3,2)}$-singular element into the sum of splint images of singular elements of $A_{2}$-modules (dashed). Weight multiplicities of $A_{2}$-module coincide with branching coefficients for the reduction $L^{(3,2)}_{B_{2}\downarrow A_{1}\oplus u(1)}$.}

 \label{fig:b2_splint}
\end{figure}
\end{example}
\begin{example}
   Lie algebra $G_{2}$ has regular subalgebra $A_{2}$ with root system built on long roots of $G_{2}$. Consider branching of its irreducible module $L^{(3,2)}$ into the modules of reductive subalgebra $A_{2}$. Singular element of $L^{(3,2)}$ is decomposition into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide weight multiplicities of $A_{2}$-module (see Fig. \ref{fig:g2_splint}).

  \begin{figure}[h!bt]
  \noindent\centering{
   \includegraphics[width=120mm]{g2}
  }

  \caption{Weyl group orbit (dotted) producing singular element of $G_{2}$-module $L^{(3,2)}$ and its decomposition into the sum of splint images of singular elements of $A_{2}$-modules (dashed). Weight multiplicities of $A_{2}$-module coincide with branching coefficients for the reduction $L^{(3,2)}_{G_{2}\downarrow A_{2}}$.}

 \label{fig:g2_splint}
\end{figure}

\end{example}

\section{Conclusions}
\label{sec:conclusions}

\section*{Acknowledgements}
\label{sec:acknowledgements}

The work of A.A.~Nazarov is supported by the Chebyshev Laboratory
(Department of Mathematics and Mechanics, Saint-Petersburg State
University) under the grant 11.G34.31.0026 of the Government of the
Russian Federation.

\bibliography{bibliography}{}
\bibliographystyle{utphys}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\begin{thebibliography}{99}
%%\bibitem{2010arXiv1007.0318L}
%%V. Lyakhovsky and A. Nazarov, ТRecursive algorithm and branching
%%for nonmaximal embeddingsУ, J. Phys. A: Math. Theor. 44 (2011),
%%075205. arXiv:1007.0318 [math.RT].
%%
%%\bibitem{Richter}D. A. Richter,"Splints of classical root systems",
%%arXiv:0807.0640v1 [math.RT].
%%
%%\bibitem{LyakhMel} V. D. Lyakhovsky and S. Yu Melnikov, "Recursion relations and branching rules for simple Lie algebras", J. Phys. A: Math. Gen. 29 (1996) 1075-1087.
%%
%%\end{thebibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2011-10-10 AffineLieAlgebras/SLE/article.tex
Bibliography on SLE is added.

@@
 
-  SLE with additional Brownian motion on Lie group $G$ was proposed as generalization to WZNW models of CFT.
+  We generalize Schramm-Loewner evolution with additional Brownian motion on Lie group to the case of direct product of two groups.
+We then study connection between SLE description of critical behavior with coset models of conformal field theory.
+In order to be consistent such construction should give minimal models for certain choice of groups.
+
+%%    SLE with additional Brownian motion on Lie group $G$ was proposed as generalization to WZNW models of CFT.
 Martingale property of SLE observables is related to Virasoro null vector conditions for CFT fields and KZ-equations for correlation functions.
-
-  Minimal models can be obtained from WZNW models by coset construction.
+%%  
+%%    Minimal models can be obtained from WZNW models by coset construction.
 Then it is natural to study SLE with additional Brownian motion on coset space $G/H$.
@@
 \section{Introduction}
+Schramm-Loewner evolution, introduced by Oded Schramm in papers \cite{schramm2000scaling} is
+
 \subsection{Schramm-Loewner evolution}

### 2011-10-13 AffineLieAlgebras/Splints/paper.tex

@@
 \documentclass[12pt]{article}
+\usepackage{amsfonts}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{amsmath,amssymb,amsthm}
@@
 \usepackage{graphicx}
-\usepackage[utf8]{inputenc}
 \usepackage[english]{babel}
 
-\newcommand{\gf}{\mathfrak{g}}
-\newcommand{\af}{\mathfrak{a}}
+%TCIDATA{OutputFilter=Latex.dll}
+%TCIDATA{LastRevised=Mon Oct 10 18:16:16 2011}
+%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
+%TCIDATA{CSTFile=article.cst}
 
@@
 \newtheorem{Prop}[Def]{Property}
-\newtheorem{example}{Example}
+\newtheorem{example}{Example}[section]
+
+%\input{tcilatex}
+
 \begin{document}
-
 \title{Fan, splint and branching rules.}
@@
 \begin{abstract}
-Splint of root system of simple Lie algebra appears naturally in the study of (regular) embedding of reductive subalgebra.
-It can be used to derive branching rules.
-We show that the use of splint drastically simplifies the derivation of branching functions.
+Splint of root system of simple Lie algebra appears naturally in
+the study of (regular) embeddings of reductive subalgebras. It can
+be used to derive branching rules. We show that application of
+splint properties drastically simplifies calculations of
+branching coefficients.
 \end{abstract}
@@
 \section{Introduction}
-\label{sec:Introduction} 
-Splint $\phi$ of root system $\Delta_1$ to root system $\Delta$ is a bijective map of roots of $\Delta_{1}$ to (proper) subset of $\Delta$ which commutes with the addition in $\Delta_{1}$ and $\Delta$.
+\label{sec:Introduction} Splint $\phi$ of a root system $\Delta_1$
+into a root system $\Delta$ is a bijective map of roots of
+$\Delta_{1}$ to (proper) subset of $\Delta$ which commutes with
+vector composition law in $\Delta_{1}$ and $\Delta$.
 \begin{equation*}
@@
 \begin{equation*}
-\phi \circ \alpha + \beta =\phi \circ \alpha + \phi \circ \beta,
+\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
 \,\,\, \alpha,\beta \in \Delta_1
@@
 
-Note that image $Im(\phi)$ is not required to have the properties of root system except the addition rules equivalent to the addition rules in $\Delta_{1}$ (for pre-images).
-The term {\it splint} was introduce in paper \cite{richter2008splints} where the classification of splints for simple Lie algebras was obtained.
-The conjecture of the connection splint with injection fan was stated in the same paper.
-The fan $\Gamma \subset \Delta$ as the subset of root system describing recurrent properties of branching coefficients for maximal embeddings  was introduced in \cite{lyakhovsky1996rra}.
-Injection fan is an efficient tool for the study of branching rules.
-This construction was generalized to non-maximal embeddings and infinite-dimensional Lie algebras in  \cite{2010arXiv1007.0318L, ilyin812pbc}.
+Note that the image $Im(\phi)$ must not inherit the root system
+properties except the addition rules equivalent to the addition
+rules in $\Delta_{1}$ (for pre-images). The term {\it splint} was
+introduced by D. Richter in  \cite{richter2008splints} where the
+classification of splints for simple Lie algebras was obtained.
+There was also mentioned that the notion of splint must have tight
+connections with the injection fan approach. The fan $\Gamma
+\subset \Delta$ was
+introduced in \cite{lyakhovsky1996rra} as the subset of root system describing recurrent
+properties of branching coefficients for maximal embeddings  . Injection fan is an
+efficient tool to study branching rules. Later this construction
+was generalized to non-maximal embeddings and infinite-dimensional
+Lie algebras in \cite{2010arXiv1007.0318L, ilyin812pbc}.
 
-In present paper we study the connection of splint with the injection fan of regular embedding of reductive subalgebra ${\mathfrak a}$.
-We show that (under certain conditions described in section \ref{sec:stems and multiplicity functions}) splint is a natural tool for the reduction of simple Lie algebra $\gf$-modules to the modules of subalgebra $\af\rightarrow\gf$.
-The use of this tool allows us to state the main result of the present paper -- the one-to-one relationship between weight multiplicities of irreducible modules of splint and branching coefficients for the reduction $L^{\mu}_{{\mathfrak g}\downarrow {\mathfrak a}}$.
+In the present paper we study the connection of splint with
+injection fan for regular embeddings of reductive subalgebras
+${\mathfrak a}\longrightarrow {\mathfrak g}$. We show that (under
+certain conditions described in section \ref{sec:stems and
+multiplicity functions}) splint is a natural tool to study
+reduction properties of simple Lie algebra ${\mathfrak g}$-modules
+with respect to a subalgebra ${\mathfrak a}\longrightarrow
+{\mathfrak g}$. Using this tool we obtain the main result of the
+present paper -- the one-to-one correspondence between weight
+multiplicities in irreducible modules of splint and branching
+coefficients for a reduced module $L^{\mu}_{{\mathfrak
+g}\downarrow {\mathfrak a}}$.
 
 \section{Injections and splints}
+
 \label{sec:Injections and splints}
 
-Consider a simple Lie algebra $\mathfrak{g}$ and its regular
-subalgebra $\mathfrak{a}\longrightarrow \mathfrak{g%
-}$ such that $\mathfrak{a}$ is a reductive subalgebra $\mathfrak{a
-\subset g}$ with correlated root spaces:
-$\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset
-\mathfrak{h}_{\mathfrak{g }}^{\ast }$. Let $\mathfrak{a}^S$ be a
-semisimple summand of $\mathfrak{a}$, this means that
-$\mathfrak{a}=\mathfrak{a}^S \oplus \mathfrak{a}(1)\oplus
-\mathfrak{a}(1)\oplus \dots$. We shall consider $\mathfrak{a}^S$
-to be a proper regular subalgebra and $\mathfrak{a}$ to be the
-maximal subalgebra with $\mathfrak{a}^S$ fixed that is the rank
-$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
+Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
+\mathfrak{a}\longrightarrow \mathfrak{g}$ such that $\mathfrak{a}$ is a
+reductive subalgebra $\mathfrak{a
+\subset g}$ with correlated root spaces: $\mathfrak{h}_{\mathfrak{a}}^{\ast
+}\subset \mathfrak{h}_{\mathfrak{g }}^{\ast }$. Let $\mathfrak{a}^S$ be a
+semisimple summand of $\mathfrak{a}$, this means that $\mathfrak{a}=%
+\mathfrak{a}^S \oplus \mathfrak{u}(1)\oplus \mathfrak{u}(1)\oplus \dots$. We
+shall consider $\mathfrak{a}^S$ to be a proper regular subalgebra and $%
+\mathfrak{a}$ to be the maximal subalgebra with $\mathfrak{a}^S$ fixed that
+is the rank $r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
 
-$r$ , $\left( r_{\mathfrak{a}^S}\right) $ --- the rank of
-$\frak{g}$ $\left( \mathrm{{resp. }\mathfrak{a}^S}\right) $ ;
+$r$ , $\left( r_{\mathfrak{a}^S}\right) $ --- the rank of $\frak{g}$ $\left(
+\mathrm{{resp. }\mathfrak{a}^S}\right) $ ;
 
-$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system;
-$\Delta ^{+} $ $\left( \mathrm{{resp. }\Delta
-_{\frak{a}}^{+}}\right) $--- the positive root system (of
-$\frak{g}$ and $\frak{a}$ respectively);
+$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
+^{+} $ $\left( \mathrm{{resp. }\Delta _{\frak{a}}^{+}}\right) $--- the
+positive root system (of $\frak{g}$ and $\frak{a}$ respectively);
 
@@
 $\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
-i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a%
-}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots
-,r_{\mathfrak{a}^S}\right) $;
+i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{%
+a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
+^S}\right) $;
 
-$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl
-group;
+$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
 
-$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl
-chamber;
+$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
 
@@
 
-$\epsilon \left( w\right) :=\left( -1\right)
-^{\mathrm{length}(w)}$;
+$\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;
 
@@
 
-$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the
-integrable module of $\frak{g}$ with the highest weight $\mu $\ ;
-(resp. integrable $\frak{a}$ -module with the highest weight $\nu
-$ );
+$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
+of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
+-module with the highest weight $\nu $ );
 
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu
-}\right) $ --- the weight diagram of $L^{\mu }$ (resp.
-${}L_{\frak{a}}^{\nu }$ );
+$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
+the weight diagram of $L^{\mu }$ (resp. ${}L_{\frak{a}}^{\nu }$ );
 
@@
 
-$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight
-lattice;
+$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight lattice;
 
-$\cal{E}$ (resp. $\cal{E}_{\frak{a}} $) \ --- the formal algebra;
+$\mathcal{E}$ (resp. $\mathcal{E}_{\frak{a}} $) \ --- the formal algebra;
 
-$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu
-\right)
+$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
 }\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
-resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ ,
-(resp. $\xi \in L_{\frak{a}}^{\nu } $);
+resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
+L_{\frak{a}}^{\nu } $);
 
-$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left(
-L_{\frak{a}}^{\nu }\right) $)--- the formal character of $L^{\mu
-}$ (resp. $L_{\frak{a}}^{\nu } $);
+$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $)--- the formal character of $L^{\mu }$ (resp. $L_{\frak{a}}^{\nu
+} $);
 
-$ch\left( L^{\mu }\right)
- =\frac{\sum_{w\in W}\epsilon
-(w)e^{w\circ (\mu +\rho )-\rho }}
-{\prod_{\alpha \in \Delta
-^{+}}
-\left( 1-e^{-\alpha }\right) }
-$ --- the Weyl formula;
+$ch\left( L^{\mu }\right)  =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
++\rho )-\rho }} {\prod_{\alpha \in \Delta ^{+}} \left( 1-e^{-\alpha }\right)
+} $ --- the Weyl formula;
 
-$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right)
-\quad
-$
-(resp.
-$
-R_{\frak{a}}:
-=\prod_{\alpha \in \Delta_{\frak{a}}^{+}}
-\left( 1-e^{-\alpha }\right)
-$
-) --- the Weyl
-denominator.
+$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) \quad $
+(resp. $R_{\frak{a}}: =\prod_{\alpha \in \Delta_{\frak{a}}^{+}} \left(
+1-e^{-\alpha }\right) $ ) --- the Weyl denominator.
 
 Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
-\begin{equation*}
+\[
 L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
 }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
-\end{equation*}
+\]
 \begin{equation}
@@
 \end{equation}
-For the modules we are interested in the Weyl formula for $\mathrm{ch}%
-\left( L^{\mu }\right) $ can be written in terms of singular
-elements \cite {humphreys1997introduction}
-\begin{equation*}
-\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon
-(w)e^{w(\mu +\rho )-\rho },
-\end{equation*}
+For the modules we are interested in the Weyl formula for $\mathrm{ch}\left(
+L^{\mu }\right) $ can be written in terms of singular elements \cite
+{humphreys1997introduction}
+\[
+\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
+)-\rho },
+\]
 namely,
 \begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right)
-}}{\Psi ^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right)
-}}{R}. \label{Weyl-Kac2}
+\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
+^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
+\label{Weyl-Kac2}
 \end{equation}
-The same is true for submodules $\mathrm{ch}\left(
-L_{\frak{a}}^{\nu }\right) $ in (\ref{branching1})
-\begin{equation*}
-\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi
-_{\frak{a}}^{\left(
+The same is true for submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $ in (\ref{branching1})
+\[
+\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
 \nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
 }^{\left( \nu \right) }}{R_{\frak{a}}},
-\end{equation*}
+\]
 with
-\begin{equation*}
+\[
 \Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
 }}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
-\end{equation*}
+\]
 
-Applying formula (\ref{Weyl-Kac2}) to the branching rule
-(\ref{branching1}) we get the relation connecting the singular
-elements $\Psi ^{\left( \mu \right) }$ and $\Psi
-_{\frak{a}}^{\left( \nu \right) }$ :
+Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
+we get the relation connecting the singular elements $\Psi ^{\left( \mu
+\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
 \begin{eqnarray}
- \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu
-+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })}
-&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
-\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
-\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })},
-\notag  \label{eq:4} \\
-\frac{\Psi ^{\left( \mu \right) }}{R}
-&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
-}^{\left( \nu \right) }}{R_{\frak{a}}}.
-\label{singular main}
+\frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho )-\rho }}{\prod_{\alpha \in
+\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
+}^{(\mu )}\frac{\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{%
+\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
+}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:4} \\
+\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}}^{\left( \nu \right) }}{R_{%
+\frak{a}}}.  \label{singular main}
 \end{eqnarray}
 
-In \cite
-{2010arXiv1007.0318L} it was proven that branching coefficients $b_{\xi
-}^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
+In \cite{2010arXiv1007.0318L} it was proven that branching coefficients $%
+b_{\xi }^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
 \hookrightarrow \frak{g}$ are subject to the set of recurrent relations:
@@
 \end{equation}
-where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $\frak{g}$ orthogonal to roots of $\frak{a}$
+where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $%
+\frak{g}$ orthogonal to roots of $\frak{a}$
 \begin{eqnarray}
@@
 \widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
-\qquad
-\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }
+\qquad \widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }
 \end{eqnarray}
-and $\pi$ is the projection operator. When the injection is maximal the projection becomes trivial and the relation (\ref{recurrent rel}) is simplified:
+and $\pi$ is the projection operator. When the injection is maximal the
+projection becomes trivial and the relation (\ref{recurrent rel}) is
+simplified:
 \begin{equation}
@@
 b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho }+\right.  \\
-\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}%
-}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
-}\right) .
+\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
+}+\right. \\
+\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
+\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
 \end{array}
@@
 \end{equation}
-The recursion is goverened by the set $\Gamma _{\frak{a}%
-\rightarrow \frak{g}}$ called the injection fan. The latter is defined by the
-carrier set $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the
-coefficient function $s(\xi )$
-\begin{equation*}
-\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{
-\xi \in P_{\frak{a}}|s(\xi )\neq 0\right\}
-\end{equation*}
+The recursion is goverened by the set $\Gamma _{\frak{a}\rightarrow \frak{g}}
+$ called the injection fan. The latter is defined by the carrier set $%
+\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the coefficient
+function $s(\xi )$
+\[
+\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{ \xi \in P_{%
+\frak{a}}|s(\xi )\neq 0\right\}
+\]
 appearing in the expansion
@@
 \prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\frak{a}}^{+}}\left( 1-e^{
--\alpha }\right) =-\sum_{\gamma \in P_{%
-\frak{a}}}s(\gamma )e^{-\gamma };\quad
+-\alpha }\right) =-\sum_{\gamma \in P_{\frak{a}}}s(\gamma )e^{-\gamma };\quad
 \label{product}
@@
 Now we remind two definitions introduced in \cite{richter2008splints}
+
 \begin{Def}
-Suppose $\Delta_0$ and $\Delta$ are root systems with the corresponding weight lattices $P_0$ and $P$.  Then $\phi$ is an ``embedding'', 
+Suppose $\Delta _{0}$ and $\Delta $ are root systems with the corresponding
+weight lattices $P_{0}$ and $P$. Then $\phi $ is an ``embedding'',
 \begin{equation}
-\phi:\left\{
+\phi :\left\{
 \begin{array}{l}
-\Delta_0\hookrightarrow\Delta,\\
-P_0 \hookrightarrow P,
+\Delta _{0}\hookrightarrow \Delta , \\
+P_{0}\hookrightarrow P,
 \end{array}
@@
 \end{equation}
-if \\
-\noindent
-(a) it injects $\Delta_0$ in $\Delta$, and \\
-\noindent
-(b) acts homomorphically with respect to the vector groups in $P_0$ and $P$:
-$$\phi(\gamma)=\phi(\alpha)+\phi(\beta)$$
-for any triple $\alpha,\beta,\gamma\in P_0$ such that $\gamma=\alpha+\beta$.
+if \newline
+\noindent (a) it injects $\Delta _{0}$ in $\Delta $, and \newline
+\noindent (b) acts homomorphically with respect to the vector groups in $%
+P_{0}$ and $P$:
+\[
+\phi (\gamma )=\phi (\alpha )+\phi (\beta )
+\]
+for any triple $\alpha ,\beta ,\gamma \in P_{0}$ such that $\gamma =\alpha
++\beta $.
 \end{Def}
-$\phi$ induces an injection of formal algebras $ :{\cal{E}}_0 \longrightarrow \cal{E}$ and for the image ${\cal{E}}_i=Im_{\phi}\left( {\cal{E}}_0\right)$ one can consider its inverse
-$\phi^{-1}:{\cal{E}}_i \longrightarrow {\cal{E}}_0$.
 
- Notice that one must distinguish two classes of embeddings: when the scalar product (defined by the Killing form) in the root space $P_0$ is invariant with respect to $\phi$ and when it is not $\phi$-invariant.
-The first embedding is called "metric"
-, the second -- "nonmetric". 
+$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
+\longrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
+_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
+\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+
+Notice that one must distinguish two classes of embeddings: when the scalar
+product (defined by the Killing form) in the root space $P_0$ is invariant
+with respect to $\phi$ and when it is not $\phi$-invariant. The first
+embedding is called "metric" , the second -- "nonmetric".
+
 \begin{Def}
-A root system $\Delta$ "splinters'' as $(\Delta_1,\Delta_2)$ if there are two embeddings
-$\phi_1:\Delta_1\hookrightarrow\Delta$ and $\phi_2:\Delta_2\hookrightarrow\Delta$
-where (a) $\Delta$ is the disjoint union of the images of $\phi_1$ and $\phi_2$ and
-(b) neither the rank of $\Delta_1$ nor the rank of $\Delta_2$ exceeds the rank of $\Delta$.
+A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if
+there are two embeddings $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
+\phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the
+disjoint union of the images of $\phi _{1}$ and $\phi _{2}$ and (b) neither
+the rank of $\Delta _{1}$ nor the rank of $\Delta _{2}$ exceeds the rank of $%
+\Delta $.
 \end{Def}
-It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$.
-Each component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $(\Delta_1,\Delta_2)$.
 
-In \cite{richter2008splints} it was indicated that the injection fan technique used in \cite{lyakhovsky1996rra} is close to that of splints.
+It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$
+and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$. Each
+component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $%
+(\Delta_1,\Delta_2)$.
 
-To demonstrate the relations between these instruments consider the case where
-one of the stems $\Delta_1=\Delta_{\frak{a}}$ is a root system of a regular reductive subalgebra  $\frak{a}\hookrightarrow\frak{g}$.
-Then the second stem is $\Delta_{\frak{s}}:=\Delta_2=\Delta \setminus \Delta _{\frak{a}}$ can be translated into the product (\ref{product}) and defines the injection fan $\Gamma_{\frak{a}\hookrightarrow\frak{g}}$.
+In \cite{richter2008splints} it was indicated that the injection fan technique used in
+\cite{lyakhovsky1996rra} is close to that of splints.
+
+To demonstrate the relations between these instruments consider the case
+where one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem
+in $\Delta $.
+
+Splint $\Delta \approx (\Delta _{1},\Delta _{2})$ is called ''injective'' if
+one of its stems, say $\Delta _{1}=\Delta _{\frak{a}}$ , is a root subsystem
+in $\Delta $ corresponding to a regular reductive subalgebra $\frak{a}%
+\hookrightarrow \frak{g}$.
+
+In case of injective splint the second stem $\Delta _{\frak{s}}:=\Delta
+_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product (%
+\ref{product}) and defines an injection fan $\Gamma _{\frak{a}%
+\hookrightarrow \frak{g}}$.
 
 Thus we see that
+
 \begin{Cnj}
-Each splint of the type $\Delta \approx (\Delta_{\frak{a}},\Delta_{\frak{s}})$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ fixed by the product
+Each injective splint $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
+$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\frak{a}%
+\rightarrow \frak{g}}$ fixed by the product
 \begin{equation}
-\prod_{\beta \in  \Delta _{\frak{s}}^{+}}\left( 1-e^{
--\beta }\right) =-\sum_{\gamma \in P} s(\gamma )e^{-\gamma }\quad
-\label{splint product}
+\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)
+=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
 \end{equation}
 \end{Cnj}
-In this case we say that the subalgebra $\frak{a}\hookrightarrow\frak{g}$ splinters $\Delta$ (and call $\frak{a}$ the "splinting subalgebra" of $\frak{g}$). In
-\cite{richter2008splints} the splints are classified (see Appendix) and in the first three types one can easily see that one of the stems corresponds to a splinting subalgebra.
+
+In this case we say that the subalgebra $\frak{a}\hookrightarrow \frak{g}$
+splinters $\Delta $ (and call $\frak{a}$ the ''splinting subalgebra'' of $%
+\frak{g}$). In \cite{richter2008splints} splints are classified (see Appendix there)
+and the first three types of them are injective.
 
 \section{How stems define multiplicity functions}
+
 \label{sec:stems and multiplicity functions}
 
-In this Section we consider the situation where  the splinting subalgebra is "larger"
-than the Lie algebra $\frak{s}$ defined by the root system $\Delta_{\frak{s}\,0}=CoIm_{\phi} \left( \Delta_{\frak{s}}\right)$
-(the details will be given below). In such a case to find branching coefficients for a splinting 
-injection $\frak{a}\hookrightarrow\frak{g}$ means to find weight multiplicities for an irreducible $\frak{s}$-module $L^{\nu}_{\frak{s}}$ with 
-the fixed highest weight $\nu$. Notice that $\frak{s}$ must not be a subalgebra of $\frak{g}$.
+In this Section we consider the situation where the splinting subalgebra is
+''larger'' than the Lie algebra $\frak{s}$ defined by the root system $%
+\Delta _{\frak{s}\,0}=CoIm_{\phi }\left( \Delta _{\frak{s}}\right) $ (the
+details will be given below). In such a case to find branching coefficients
+for a splinting injection $\frak{a}\hookrightarrow \frak{g}$ means to find
+weight multiplicities for an irreducible $\frak{s}$-module $L_{\frak{s}%
+}^{\nu }$ with fixed highest weight $\nu $. Notice that $\frak{s}$ must not
+be a subalgebra of $\frak{g}$.
 
-Let us return to relation (\ref{singular main}) and multiply both sides by $R_{\frak{a}}$: 
-\begin{eqnarray}
- \frac{1}{\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })}\Psi_{\frak{g}} ^{\left( \mu \right) }
-&=&
-\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\Psi _{\frak{a}%
-}^{\left( \nu \right) }.
+Let us return to relation (\ref{singular main}) and multiply both sides by $%
+R_{\frak{a}}$:
+\begin{equation}
+\frac{1}{\prod_{\beta \in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })}\Psi _{%
+\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
+}^{(\mu )}\Psi _{\frak{a}}^{\left( \nu \right) }.
 \label{singular main-2}
-\end{eqnarray}
-Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{\frak{a}%
-\rightarrow \frak{g}}$. 
-Consider the highest weight module $L^{\nu}_{\frak{s}}$. An embedding
-$\phi:\Delta_{\frak{s}\,0} \longrightarrow \Delta_{\frak{g}} $  sends the singular element         $\Psi_{\frak{s}} ^{\left( \nu \right)}$ into $ \Psi_{\frak{g}} ^{\left( \mu \right) }$.
-Applying the inverse morphism $\phi^{-1}$ to the product 
-$\left(\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })\right)^{-1}\phi\left(\Psi_{\frak{s}} ^{\left( \nu \right)}\right)$  
- one obtains the character of the module $L^{\nu}_{\frak{s}}$,
+\end{equation}
+Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{%
+\frak{a}\rightarrow \frak{g}}$. Consider the highest weight module $L_{\frak{%
+s}}^{\nu }$. An embedding $\phi :\Delta _{\frak{s}\,0}\longrightarrow \Delta
+_{\frak{g}}$ sends the singular element $\Psi _{\frak{s}}^{\left( \nu
+\right) }$ into $\Psi _{\frak{g}}^{\left( \mu \right) }$. Applying the
+inverse morphism $\phi ^{-1}$ to the product $\left( \prod_{\beta \in \Delta
+_{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\frak{s}%
+}^{\left( \nu \right) }\right) $ one gets the character of the module $L_{%
+\frak{s}}^{\nu }$,
 
 \begin{equation}
- \phi^{-1}\left( \frac{1}{\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })}\phi\left(\Psi_{\frak{s}} ^{\left( \nu \right)}\right)\right)
- =
- \frac{1}{\prod_{\beta \in \Delta_{\frak{s}\left(0\right)} ^{+}}(1-e^{-\beta })}\Psi_{\frak{s}} ^{\left( \nu \right)}
- =
- \mathrm{ch}\left( L_{\frak{s}}^{\nu }\right).
-\label{inverse for stem}
+\phi ^{-1}\left( \frac{1}{\prod_{\beta \in \Delta _{\frak{s}%
+}^{+}}(1-e^{-\beta })}\phi \left( \Psi _{\frak{s}}^{\left( \nu \right)
+}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\frak{s}\left( 0\right)
+}^{+}}(1-e^{-\beta })}\Psi _{\frak{s}}^{\left( \nu \right) }=\mathrm{ch}%
+\left( L_{\frak{s}}^{\nu }\right) .  \label{inverse for stem}
 \end{equation}
-Our task is to prove that the singular element $\Psi_{\frak{g}} ^{\left( \mu \right) }$ contains the element $\Psi_{\frak{g}} ^{\left( \xi \right) }$ for a module $L^{\xi}_{\frak{s}}$ uniquely defined by $L^{\mu}_{\frak{g}}$ and that the branching coefficients $b_{\nu }^{(\mu )}$ in the r.h.s.
-of (\ref{singular main-2})  coincide with multiplicities $m_{\zeta}^{\left( \xi \right) }$ of the weights of $L^{\xi}_{\frak{s}}$.
+Our task is to prove that the singular element $\Psi _{\frak{g}}^{\left( \mu
+\right) }$ contains the element $\Psi _{\frak{s}}^{\left( \xi \right) }$ for
+a module $L_{\frak{s}}^{\xi }$ uniquely defined by $L_{\frak{g}}^{\mu }$ and
+that the branching coefficients $b_{\nu }^{(\mu )}$ in the r.h.s. of (\ref
+{singular main-2}) coincide with multiplicities $m_{\zeta }^{\left( \xi
+\right) }$ of the corresponding weights in $\mathcal{N}_{\frak{s}}^{\xi }$ .
 
-For a highest weight irreducible module $L^{\mu}_{\frak{g}}$ the singular element $\Psi_{\frak{g}} ^{\left( \mu \right) }$ is an element of $\cal{E}$ corresponding to the shifted Weyl-orbit of the weight $\left( \mu + \rho \right) \in P^+$ and the sign function $\epsilon\left( w \right)$.
-It is convenient to use also unshifted singular elements
+For a highest weight irreducible module $L_{\frak{g}}^{\mu }$ the singular
+element $\Psi _{\frak{g}}^{\left( \mu \right) }$ is an element of $\mathcal{E%
+}$ corresponding to the shifted Weyl-orbit of the weight $\left( \mu +\rho
+\right) \in P^{+}$ with the sign function $\epsilon \left( w\right) $. It is
+convenient to use also unshifted singular elements
 \begin{equation}
- \Phi^{\left( \mu \right)}:= \Psi^{\left( \mu \right) }e^{\rho}.
+\Phi ^{\left( \mu \right) }:=\Psi ^{\left( \mu \right) }e^{\rho }.
 \label{definition Phi}
@@
 \begin{equation}
- \frac{e^{\rho_{\frak{g}}-\rho_{\frak{a}}}}{\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })}\Phi_{\frak{g}} ^{\left( \mu \right) }
-=
-\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\Phi _{\frak{a}%
-}^{\left( \nu \right) }.
+\frac{e^{\rho _{\frak{g}}-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{%
+s}}^{+}}(1-e^{-\beta })}\Phi _{\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in
+P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\Phi _{\frak{a}}^{\left( \nu \right) }.
 \label{singular main-3}
 \end{equation}
-The orbit that corresponds to $\Phi_{\frak{g}} ^{\left( \mu \right) }$ is completely defined by 
-the set of edges $\left\{ \lambda_{i}\right\}_{i=1,\dots,r}$ adjusted to the end of the highest weight vector $\mu + \rho$. Let $\mu=\sum m_i \omega_i$ then 
+The orbit related to $\Phi _{\frak{g}}^{\left( \mu \right) }$ is completely
+defined by the set of edges $\left\{ \lambda _{i}\right\} _{i=1,\dots ,r}$
+adjusted to the end of the highest weight vector $\mu +\rho $. Let $\mu
+=\sum m_{i}\omega _{i}$ then these edges are
 \begin{equation}
- \lambda_i=-\left( m_i +1\right)\alpha_i .\quad i=1,\dots,r
+\lambda _{i}=-\left( m_{i}+1\right) \alpha _{i}.\quad i=1,\dots ,r
 \label{edge}
 \end{equation}
-Each weight $\mu + \rho + \lambda_i $ bears the sign coefficient $(-)$ in the singular element.
-The defining property of $\Phi_{\frak{g}} ^{\left( \mu \right) }$ is as follows.
-Consider any pair of edges $\lambda_i,\lambda_j$ and the corresponding weights $\mu + \rho $, $\mu + \rho + \lambda_i $ and $\mu + \rho + \lambda_j $.
-Apply the reflection $s_{\alpha_i}$ (or $s_{\alpha_j}$),
+Each formal exponent $e^{\mu +\rho +\lambda _{i}}$ in $\Phi _{\frak{g}%
+}^{\left( \mu \right) }$ bears the sign coefficient $\epsilon =(-)$. The
+defining property of $\Phi _{\frak{g}}^{\left( \mu \right) }$ is as follows.
+Consider any pair of edges $\lambda _{i},\lambda _{j}$ and the corresponding
+weights $\mu +\rho $, $\mu +\rho +\lambda _{i}$ and $\mu +\rho +\lambda _{j}$%
+. Apply the reflection $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
 \begin{equation}
- s_{\alpha_i}\circ
- \left\{
+s_{\alpha _{i}}\circ \left\{
 \begin{array}{l}
-\left( \mu + \rho  \right)\\
-\left( \mu + \rho + \lambda_i \right)\\
-\left( \mu + \rho + \lambda_j \right)
+\left( \mu +\rho \right)  \\
+\left( \mu +\rho +\lambda _{i}\right)  \\
+\left( \mu +\rho +\lambda _{j}\right)
 \end{array}
-\right.
-= 
-  \left\{
+\right. =\left\{
 \begin{array}{l}
-\left( \mu + \rho + \lambda_i \right)\\
-\left( \mu + \rho  \right)\\
-\left( \mu + \rho + \lambda_i -  (m_j + 1) s_{\alpha_i}\circ \alpha_j\right)
+\left( \mu +\rho +\lambda _{i}\right)  \\
+\left( \mu +\rho \right)  \\
+\left( \mu +\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha
+_{j}\right)
 \end{array}
-\right.
- \label{reflected triple}
+\right.   \label{reflected triple}
 \end{equation}
@@
 \begin{Prop}
- The edge $\lambda_{i,j}$ of $\Phi_{\frak{g}} ^{\left( \mu \right) }$ starting at the weight $\left( \mu + \rho + \lambda_i \right)$ along the root $- s_{\alpha_i}\circ \alpha_j$ has the same length in $( s_{\alpha_i}\circ \alpha_j )$ as $\lambda_j$ has in $\alpha_j$.
-(The same is true for the edge $\lambda_{i,j}$, its length in $( s_{\alpha_j}\circ \alpha_i )$  is equal to the length of $\lambda_i$ in $\alpha_i$.)
+The edge $\lambda _{i,j}$ of $\Phi _{\frak{g}}^{\left( \mu \right) }$
+starting at the weight $\left( \mu +\rho +\lambda _{i}\right) $ along the
+root $-s_{\alpha _{i}}\circ \alpha _{j}$ has the same length in $(s_{\alpha
+_{i}}\circ \alpha _{j})$ as $\lambda _{j}$ has in $\alpha _{j}$. (The same
+is true for the edge $\lambda _{j,i}$, its length in $(s_{\alpha _{j}}\circ
+\alpha _{i})$ is equal to the length of $\lambda _{i}$ in $\alpha _{i}$.)
 \label{diagram property}
 \end{Prop}
-  In $\Phi_{\frak{g}} ^{\left( \mu \right) }$ the elements $e^{\left( \mu + \rho + \lambda_i -  (m_j + 1) s_{\alpha_i}\circ \alpha_j\right)}$ and  $e^{\left( \mu + \rho + \lambda_j -  (m_i + 1) s_{\alpha_j}\circ \alpha_i\right)}$
-have the sign $(+)$.
 
-From now on we consider splints for simple Lie algebras of the first three types according to the classification in \cite{richter2008splints}: 
-$$\begin{array}{c c||c|c}
-\hbox{type}
-& \hspace{0.25 in}\Delta\hspace{0.25 in} & \hspace{0.25 in}\Delta_{\frak{a} }\hspace{0.25 in} & \hspace{0.25 in}\Delta _{\frak{s}}\hspace{0.25 in} \\
-\hline
-\hline
-\hbox{(i)}     & G_2 & A_2 & A_2 \\
-& F_4 & D_4 & D_4 \\
-\hline
-\hbox{(ii)} & B_r (r\geq 2) & D_r & rA_1 \\
-    & C_r (r\geq 3) & D_r  & rA_1 \\
-\hline
-\hbox{(iii)}    & A_r (r\geq 2) & A_{r-1} & r A_1 \\
-    & B_2 & A_1 & A_2 \\
-\end{array}$$
+In $\Phi _{\frak{g}}^{\left( \mu \right) }$ the elements $e^{\left( \mu
++\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha _{j}\right) }$ and $%
+e^{\left( \mu +\rho +\lambda _{j}-(m_{i}+1)s_{\alpha _{j}}\circ \alpha
+_{i}\right) }$ have the sign coefficient  $\epsilon =(+)$.
 
-Each row in the table gives a splint $(\Delta_{\frak{a} },\Delta_{\frak{s} })$ of the simple root system $\Delta$.
-For these types:  
-(i) Both $\Delta_{\frak{a} }$ and $\Delta_{\frak{s} }$ are embedded metrically, and $\Delta_{\frak{a} }\cong\Delta_{\frak{s} }$. 
-(ii) Both $\Delta_{\frak{a} }$ and $\Delta_{\frak{s} }$ are embedded metrically, but $\Delta_{\frak{a} }$ and $\Delta_{\frak{s} }$ are not isomorphic.
-(iii) Only $\Delta_{\frak{a} }$ is embedded metrically.
+Remember that only the first three types in Richter classification are
+injective splints and thus are naturally connected with branching. Below we
+reproduce the part of the splints table from \cite{richter2008splints} corresponding to
+injective splints:
+\[
+\begin{array}{cc||c|c}
+\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
+_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
+\\ \hline\hline
+\hbox{(i)} & G_{2} & A_{2} & A_{2} \\
+& F_{4} & D_{4} & D_{4} \\ \hline
+\hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
+& C_{r}(r\geq 3) & D_{r} & \oplus ^{r}A_{1} \\ \hline
+\hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
+^{r}A_{1} \\
+& B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
+\end{array}
+\]
+Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\frak{s}})
+$ of the simple root system $\Delta $. In the first two types both $\Delta _{%
+\frak{a}}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
+first type splints are equivalent and in the second are not. In the third
+type splints only $\Delta _{\frak{a}}$ is embedded metrically. the summands $%
+u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$ . This does not change
+the principle properties of branching but makes it possible to use the
+multiplicities of $\frak{s}$ -modules without further projecting their
+weights.
 
-Splints induce a decomposition of the set $S=S_{\frak{c}} \cup S_{\frak{d}}$ where $S_{\frak{c}}=S \cap S_{\frak{a}}$ and $S_{\frak{d}}=S \cap S_{\frak{s}}$.
-It is easy to check that for all the splints we are interested in   the subset $S_{\frak{d}}$ is nonempty.
-It follows that in the set $\left\{ \lambda_{i}\right\}_{i=1,\dots,r}$ one can always find simple roots $\beta_k \in \Delta_{\frak{s}}$ and that the orbit corresponding to $\Phi_{\frak{g}} ^{\left( \mu \right) }$ contains edges
+Splints induce a decomposition of the set $S=S_{\frak{c}}\cup S_{\frak{d}}$
+with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}}$%
+. It is easy to check that for all the injective splints the subset $S_{%
+\frak{d}}$ is nonempty. It follows that in the set $\left\{ \lambda
+_{i}\right\} _{i=1,\dots ,r}$ one can always find simple roots $\beta
+_{k}\in \Delta _{\frak{s}}$ and that the orbit corresponding to $\Phi _{%
+\frak{g}}^{\left( \mu \right) }$ contains the edges
 \begin{equation}
- \lambda_k=-\left( m_k +1\right)\beta_k 
-\label{beta edge}
+\lambda _{k}=-\left( m_{k}+1\right) \beta _{k}  \label{beta edge}
 \end{equation}
-attached to the weight $\mu + \rho$.
-As far as $\Delta_{\frak{a}} $ is a root system and for any pair of simple roots from $S_{\frak{c}}$ the singular element $\Phi_{\frak{g}} ^{\left( \mu \right) }$ is a singular element for a set of $\frak{a}$-modules the property \ref{diagram property} is fulfilled.
-Consider $\alpha_l \in S_{\frak{c}}$ with the corresponding edge $ \lambda_l=-\left( m_l +1\right)\alpha_l $ and a root $\beta_l \in \Delta_{\frak{s}}$ whose  coimage in $\Delta_{\frak{s}0}$ is simple.
-The root $\beta_l $ is not simple in $\Delta$.
-Firstly suppose that $\beta_l =\alpha_l + \beta_k$.
-It is easily seen that the corresponding edge intersects the boundary plane of the fundamental chamber $\bar{C_{\frak{a}}}$ orthogonal  to the root  $\alpha_l$:
+attached to the weight $\mu +\rho $. As far as $\Delta _{\frak{a}}$ is a
+root system and for any pair of simple roots from $S_{\frak{c}}$ the
+property \ref{diagram property} is fulfilled, the element $\Phi _{\frak{g}%
+}^{\left( \mu \right) }$ being a singular element for a set of $\frak{a}$%
+-modules. Consider $\beta _{l}\in \Delta _{\frak{s}}$ whose coimage in $%
+\Delta _{\frak{s}0}$ is simple. In Appendix it is shown that for any such $%
+\beta _{l}$ there corresponds a root $\alpha _{l}\in S_{\frak{c}}$ such that
+$\beta _{l}=\alpha _{l}+\beta _{k}$. It is easily seen that the
+corresponding edge intersects the boundary plane of the fundamental chamber $%
+\bar{C_{\frak{a}}}$ orthogonal to the root $\alpha _{l}$,
 \begin{equation}
-s_{\alpha_l}\left( \mu + \rho - p\beta_l\right)=s_{\alpha_l}\left( \mu + \rho \right) - p s_{\alpha_l}\beta_l=\mu + \rho - p\beta_l
+s_{\alpha _{l}}\left( \mu +\rho -p\beta _{l}\right) =s_{\alpha _{l}}\left(
+\mu +\rho \right) -ps_{\alpha _{l}}\beta _{l}=\mu +\rho -p\beta _{l}
 \label{intersection}
@@
 \begin{equation}
-\mu + \rho - s_{\alpha_l}\left( \mu + \rho \right)=\left( m_l +1\right)\alpha_l =\left( m_l +1\right)\beta_l - \left( m_l +1\right)\beta_k=p\beta_l  - ps_{\alpha_l}\beta_l
-\label{intersection}
+\mu +\rho -s_{\alpha _{l}}\left( \mu +\rho \right) =\left( m_{l}+1\right)
+\alpha _{l}=\left( m_{l}+1\right) \beta _{l}-\left( m_{l}+1\right) \beta
+_{k}=p\beta _{l}-ps_{\alpha _{l}}\beta _{l}  \label{intersection-2}
 \end{equation}
-It follows that $p=\left( m_l +1\right)$ and $s_{\alpha_l}\beta_l=\beta_k$.
-Now apply the operator $s_{\beta_k}$ and find that the edge along the root $s_{\beta_k}\alpha_l$ attached at the weight $s_{\beta_k}(\mu + \rho)$ is also equal to $ -p s_{\beta_k}\alpha_l$.
-This means that for the triple of roots $\beta_k,\beta_l$ and $s_{\beta_k}\alpha_l$ in $\Delta_{\frak{s}}$ the edges $\lambda_k=-\left( m_k +1\right)\beta_k  $, $\lambda_l=-\left( m_l +1\right)\beta_l$ and $\lambda_{kl}=-\left( m_l +1\right)s_{\beta_k}\alpha_l$ have the property \ref{diagram property}.
-One can continue this procedure further in the 2-dimensional subspace    fixed by the roots $\beta_k$ and $beta_l$ and find the set of formal exponents that being supplied with the corresponding sign factors compose the coimage of the singular element of a module for the subalgebra in $\frak{s}$ (this subalgebra has rank $r=2$).
+It follows that $p=\left( m_{l}+1\right) $ and $s_{\alpha _{l}}\beta
+_{l}=\beta _{k}$. Now apply the operator $s_{\beta _{k}}$ and find that the
+edge along the root $s_{\beta _{k}}\alpha _{l}$ attached at the weight $%
+s_{\beta _{k}}(\mu +\rho )$ is also equal to $-ps_{\beta _{k}}\alpha _{l}$.
+This means that for the triple of roots $\beta _{k},\beta _{l}$ and $%
+s_{\beta _{k}}\alpha _{l}$ in $\Delta _{\frak{s}}$ the edges $\lambda
+_{k}=-\left( m_{k}+1\right) \beta _{k}$, $\lambda _{l}=-\left(
+m_{l}+1\right) \beta _{l}$ and $\lambda _{kl}=-\left( m_{l}+1\right)
+s_{\beta _{k}}\alpha _{l}$ demonstrate the property \ref{diagram property}.
+One can continue this procedure further in the 2-dimensional subspace fixed
+by the roots $\beta _{k}$ and $\beta _{l}$ and find the set of formal
+exponents that being supplied with the corresponding sign factors compose
+the coimage of the singular element of a module for the subalgebra in $\frak{%
+s}$ (this subalgebra has rank $r=2$).
 
-The same can be proven for any positive root $\beta_l \in \Delta$ that is simple in $\Delta_{\frak{s}0}$ and correspondingly for any $r=2$ subalgebra in $\frak{s}$.
-The latter means that to "find" a singular element of $\frak{s}$-module in $\Phi_{\frak{g}} ^{\left( \mu \right) }$ it is necessary to incorporate in it additional formal elements corresponding to the weights belonging to the boundary of the chamber $\bar{C_{\frak{a}}}$.
+The same can be proven for any positive root $\beta _{l}\in \Delta $ that is
+simple in $\Delta _{\frak{s}0}$ and correspondingly for any $r=2$ subalgebra
+in $\frak{s}$. The latter means that to ''find'' a singular element of $%
+\frak{s}$-module in $\Phi _{\frak{g}}^{\left( \mu \right) }$ it is necessary
+to incorporate in it additional formal elements $\left\{ -e^{\mu +\rho
+-\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\} $ This
+fixes the starting edges of the diagram $\phi ^{-1}\left( \Phi _{\frak{s}}^{%
+\widetilde{\mu }}\right) $. As it follows from the reconstruction procedure
+the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $%
+, they have the same Dynkin numbers:
+\begin{equation}
+\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
+m_{k}\widetilde{\omega }_{k}  \label{new h weight}
+\end{equation}
+The next step is to construct the full $W_{\frak{s}}$-orbit $\Phi _{\frak{s}%
+}^{\left( \widetilde{\mu }\right) }$  in $P_{\frak{s}}$. It is easily seen
+that its coimage belongs to $\bar{C_{\frak{a}}}$. and that the set $\phi
+^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) \setminus \Phi _{%
+\frak{g}}^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ corresponds to the
+weights belonging to the boundary $\bar{C_{\frak{a}}}$ (including the subset
+$\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{%
+\frak{c}}\right\} $). Thus we have constructed all the formal elements\ with
+the appropriate sing factors that after being added to $\Phi _{\frak{g}%
+}^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ form the diagram $\phi
+^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) $ in $\bar{C_{\frak{a}%
+}}$.
 
-Now let us return to the relation (\ref{singular main-3}).
-One can add to $\Phi_{\frak{g}} ^{\left( \mu \right) }$ pairs of necessary formal elements with the opposite  signs.
-Notice that all the additional weights belong to the boundaries of $\bar{C_{\frak{a}}}$.
-To form a singular element for an $\frak{s}$-module one must attribute to these weights the fixed signs.
-The same elements with the opposite signs are to be referred to the neighbor Weyl chambers of $\bar{C^{(l)}_{\frak{a}}}$ (the latter are connected with the main one by simple reflections $s_{\alpha_l}$).
-In fact one can repeat the procedure of finding additional singular weights in any Weyl chamber $\bar{C^{(m)}_{\frak{a}}}$ and in them additional singular weights always have the signs opposite to that in their neighbors.
-Thus without changing in fact the element $\Phi_{\frak{g}} ^{\left( \mu \right) }$ one can present it as a sum
+Now let us return to the relation (\ref{singular main-3}). One can add to $%
+\Phi _{\frak{g}}^{\left( \mu \right) }$ pairs of additional formal elements
+constructed above  with the opposite signs: $\epsilon \left( w\right)
+|_{w\in W_{\frak{s}}}$ and $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$%
+. Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ to
+the elements whose weights we shall consider beloning to $\bar{C_{\frak{a}}}$%
+. The same elements with the opposite signs are to be referred to the
+neighbor Weyl chambers of $\bar{C_{\frak{a}}^{(l)}}$ (the latter are
+connected with the main one via simple reflections $s_{\alpha _{l}}$ so the
+signes $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ are natural for
+them). In fact one can repeat the procedure of finding additional singular
+weights in any Weyl chamber $\bar{C_{\frak{a}}^{(m)}}$ and in them
+additional singular weights always have the signs opposite to that in their
+nearest neighbors. Thus without changing in fact the element $\Phi _{\frak{g}%
+}^{\left( \mu \right) }$ one can present it as a sum
 \begin{equation}
-\Phi_{\frak{g}} ^{\left( \mu \right) }=\sum_{w \in W_{\frak{a}}} w \circ \left(e^{\rho_{\frak{a}}}\Psi^{\widetilde{\mu} + \rho_{\frak{s}}}\right)
+\Phi _{\frak{g}}^{\left( \mu \right) }=\sum_{w\in W_{\frak{a}}}w\circ \left(
+e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho _{\frak{s}}}\right)
 \label{singular final}
 \end{equation}
-where the weight $\widetilde{\mu}=\sum m_k \omega_{\frak{s}}^k$ has the same Dynkin labels $m_k$ as in the corresponding decomposition $\mu=\sum m_k \omega_{\frak{g}}^k$. 
-The decomposition (\ref{singular final}) provides the possibility to apply the factor
-$\left(\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })\right)^{-1}$ to each summand of the singular element $\Phi_{\frak{g}} ^{\left( \mu \right) }$ separately because the sets of weights from different Weyl summands do not intersect.
-Taking into account the isomorphism $\phi$ one can see that in the main Weyl chamber $\bar{C_{\frak{a}}}$ the set of weights generated by the factor $\left(\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })\right)^{-1}$ is isomorphic with the weight diagram of the $\frak{s}$-module $L^{\widetilde{\mu}}_{\frak{s}}$.
-Finally one must restrict relation (\ref{singular main-3}) to
-$\bar{C_{\frak{a}}}$ and obtain the main result:
+where the weight $\widetilde{\mu }=\sum m_{k}\omega _{\frak{s}}^{k}$ was
+defined above. The decomposition (\ref{singular final}) provides the
+possibility to apply the factor $\left( \prod_{\beta \in \Delta _{\frak{s}%
+}^{+}}(1-e^{-\beta })\right) ^{-1}$ to each summand of the singular element $%
+\Phi _{\frak{g}}^{\left( \mu \right) }$ separately because the sets of
+weights from different Weyl summands do not intersect. Taking into account
+the isomorphism $\phi $ one can see that in the main Weyl chamber $\bar{C_{%
+\frak{a}}}$ the set of weights generated by the factor $\left( \prod_{\beta
+\in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}$ is isomorphic to
+the weight diagram $\mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ of the $\frak{%
+s}$-module $L_{\frak{s}}^{\widetilde{\mu }}$. Finally one must restrict
+relation (\ref{singular main-3}) to $\bar{C_{\frak{a}}}$ and obtain the main
+result:
+
 \begin{Prop}
 \begin{equation}
- \frac{e^{\rho_{\frak{g}}}}{\prod_{\beta \in \Delta_{\frak{s}} ^{+}}(1-e^{-\beta })}\left(\Psi^{\widetilde{\mu} + \rho_{\frak{s}}}\right)
-=e^{\rho_{\frak{g}}}\left( \phi^{-1}\left( \mathcal{N}_{\frak{a}}^{\widetilde{\mu}
-}\right)  \right)
-=
-\sum b_{\nu }^{(\mu )}e^{\nu}.
+\frac{e^{\rho _{\frak{g}}}}{\prod_{\beta \in \Delta _{\frak{s}%
+}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
+}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }%
+}}M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
+\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}=\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
 \label{singular main-4}
 \end{equation}
+Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
+highest weights in the decomposition. The multiplicity $M_{\left( \frak{s}%
+\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
+}\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ defines the branching
+coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
+-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
+\[
+b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}.
+\]
 \end{Prop}
@@
   Consider Lie algebra $A_{2} (\bf{sl}(3))$ and branching of its irreducible module $L^{(3,2)}$ into the modules of reductive subalgebra $A_{1}\oplus u(1)$ with root system spanned by first simple root of $A_{2}$.
-Singular element of $L^{(3,2)}$ is decomposition into the sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules and branching coefficients coincide weight multiplicities of $A_{1}\oplus A_{1}$-module (see Fig.
+Singular element of $L^{(3,2)}$ is decomposed into the sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules and branching coefficients coincide with weight multiplicities of $A_{1}\oplus A_{1}$-module (see Fig.
 \ref{fig:a2_splint}).
@@
   Now consider Lie algebra $B_{2} (\bf{so}(5))$ and branching of its irreducible module $L^{(3,2)}$ into the modules of reductive subalgebra $A_{1}\oplus u(1)$ with root system spanned by first simple root of $B_{2}$.
-Singular element of $L^{(3,2)}$ is decomposition into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide weight multiplicities of $A_{2}$-module (see Fig.
+Singular element of $L^{(3,2)}$ is decomposed into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide with weight multiplicities of $A_{2}$-module (see Fig.
 \ref{fig:b2_splint}).
@@
 Consider branching of its irreducible module $L^{(3,2)}$ into the modules of reductive subalgebra $A_{2}$.
-Singular element of $L^{(3,2)}$ is decomposition into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide weight multiplicities of $A_{2}$-module (see Fig.
+Singular element of $L^{(3,2)}$ is decomposed into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide with weight multiplicities of $A_{2}$-module (see Fig.
 \ref{fig:g2_splint}).
@@
 \section{Conclusions}
+
 \label{sec:conclusions}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\begin{thebibliography}{99}
-%%\bibitem{2010arXiv1007.0318L}
-%%V. Lyakhovsky and A. Nazarov, ТRecursive algorithm and branching
-%%for nonmaximal embeddingsУ, J. Phys. A: Math. Theor. 44 (2011),
-%%075205. arXiv:1007.0318 [math.RT].
-%%
-%%\bibitem{Richter}D. A. Richter,"Splints of classical root systems",
-%%arXiv:0807.0640v1 [math.RT].
-%%
-%%\bibitem{LyakhMel} V. D. Lyakhovsky and S. Yu Melnikov, "Recursion relations and branching rules for simple Lie algebras", J. Phys. A: Math. Gen. 29 (1996) 1075-1087.
-%%
-%%\end{thebibliography}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Appendix}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Let us demonstrate that the injection splints
+ \begin{figure}[h!bt]
+  \noindent\centering{
+   \includegraphics[width=100mm]{g2-roots}
+  }
+  \caption{Weyl group orbit (dotted) producing singular element of $A_{2}$-module $L^{(3,2)}$ and its decomposition into the sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules (dashed).
+Weight multiplicities of $A_{1}\oplus A_{1}$-module coincide with branching coefficients for the reduction $L^{(3,2)}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2011-10-13 AffineLieAlgebras/Splints/paper.tex
Paper almost finished

@@
 \section{Introduction}
-\label{sec:Introduction} Splint $\phi$ of a root system $\Delta_1$
-into a root system $\Delta$ is a bijective map of roots of
-$\Delta_{1}$ to (proper) subset of $\Delta$ which commutes with
-vector composition law in $\Delta_{1}$ and $\Delta$.
+\label{sec:Introduction}
+
+Splint $\phi$ of a root system $\Delta_1$ into a root system
+$\Delta$ is a bijective map of roots of $\Delta_{1}$ to (proper)
+subset of $\Delta$ which commutes with vector composition law in
+$\Delta_{1}$ and $\Delta$.
 \begin{equation*}
@@
 Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
-\mathfrak{a}\longrightarrow \mathfrak{g}$ such that $\mathfrak{a}$ is a
-reductive subalgebra $\mathfrak{a
-\subset g}$ with correlated root spaces: $\mathfrak{h}_{\mathfrak{a}}^{\ast
-}\subset \mathfrak{h}_{\mathfrak{g }}^{\ast }$. Let $\mathfrak{a}^S$ be a
-semisimple summand of $\mathfrak{a}$, this means that $\mathfrak{a}=%
-\mathfrak{a}^S \oplus \mathfrak{u}(1)\oplus \mathfrak{u}(1)\oplus \dots$. We
-shall consider $\mathfrak{a}^S$ to be a proper regular subalgebra and $%
-\mathfrak{a}$ to be the maximal subalgebra with $\mathfrak{a}^S$ fixed that
-is the rank $r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
+\mathfrak{a}\longrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
+is a
+reductive subalgebra $\mathfrak{a \subset g}$ with correlated root spaces: $%
+\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset \mathfrak{h}_{\mathfrak{g }%
+}^{\ast }$. Let $\mathfrak{a}^S$ be a semisimple summand of
+$\mathfrak{a}$,
+this means that $\mathfrak{a}=\mathfrak{a}^S \oplus \mathfrak{u}(1)\oplus %
+\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^S$
+to be a proper regular subalgebra and $\mathfrak{a}$ to be the
+maximal subalgebra with $\mathfrak{a}^S$ fixed that is the rank
+$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
 
-$r$ , $\left( r_{\mathfrak{a}^S}\right) $ --- the rank of $\frak{g}$ $\left(
-\mathrm{{resp. }\mathfrak{a}^S}\right) $ ;
+$r$ , $\left( r_{\mathfrak{a}^S}\right) $ --- the rank of
+$\frak{g}$ $\left( \mathrm{{resp. }\mathfrak{a}^S}\right) $ ;
 
-$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
-^{+} $ $\left( \mathrm{{resp. }\Delta _{\frak{a}}^{+}}\right) $--- the
-positive root system (of $\frak{g}$ and $\frak{a}$ respectively);
+$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system;
+$\Delta ^{+} $ $\left( \mathrm{{resp. }\Delta
+_{\frak{a}}^{+}}\right) $--- the positive root system (of
+$\frak{g}$ and $\frak{a}$ respectively);
 
@@
 
-In this Section we consider the situation where the splinting subalgebra is
-''larger'' than the Lie algebra $\frak{s}$ defined by the root system $%
-\Delta _{\frak{s}\,0}=CoIm_{\phi }\left( \Delta _{\frak{s}}\right) $ (the
-details will be given below). In such a case to find branching coefficients
-for a splinting injection $\frak{a}\hookrightarrow \frak{g}$ means to find
-weight multiplicities for an irreducible $\frak{s}$-module $L_{\frak{s}%
-}^{\nu }$ with fixed highest weight $\nu $. Notice that $\frak{s}$ must not
-be a subalgebra of $\frak{g}$.
+In this Section we study properties of injective splints. It will
+be demonstrated that provided such splint exists to find branching
+coefficients for a splinting injection $\frak{a}\hookrightarrow
+\frak{g}$ means to find weight multiplicities of an irreducible
+$\frak{s}$-module $L_{\frak{s}}^{\nu }$ with fixed highest weight
+$\nu $. Notice that $\frak{s}$ must not be a subalgebra of
+$\frak{g}$.
 
@@
 
-\label{sec:conclusions}
+\label{sec:conclusions}It is explicitly demonstrated that splint
+presents a very effective tool to find branching coefficients. In
+particular injective splints provide a possibility to reduce
+branching rules calculations for highest weight modules to a
+determination of weight multiplicities for a module with the same
+Dynkin labels referred to a different Lie algebra. This algebra
+$\frak{s}$ must not be a subalgebra in the initial $\frak{g}$ , it
+has the same rank $r_{\frak{s}}=r$\ , but as a rule is less
+complicated than $\frak{g}$ .
+
+It is significant that for the injections $D_{r}\hookrightarrow B_{r}$ , $%
+D_{r}\hookrightarrow C_{r}$ and $A_{r}\hookrightarrow
+A_{r-1}\oplus u\left( 1\right) $ splint technique shows
+immediately Gelfand-Tzeytlin rules for branching: the nonzero
+branching coefficients are equal to 1, the reduction is
+multiplicity free. Here it is an immediate consequence of the
+structure of the second stem being a direct sum of $A_{1}$
+algebras and the fact that the corresponding module
+$L_{\frak{s}}^{\mu }$ is irreducible.
 
@@
 \label{sec:acknowledgements}
-
-The work of A.A.~Nazarov is supported by the Chebyshev Laboratory
-(Department of Mathematics and Mechanics, Saint-Petersburg State
-University) under the grant 11.G34.31.0026 of the Government of the
-Russian Federation.
+The work was supported in part by the
+RFFI grant N 09-01-00504. The work of A.A.~Nazarov is supported by
+the Chebyshev Laboratory (Department of Mathematics and Mechanics,
+Saint-Petersburg State University) under the grant 11.G34.31.0026
+of the Government of the Russian Federation.
 
@@
 
-\section{Appendix}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Appendix}
 
@@
 
-Let us demonstrate that the injection splints
+Let us demonstrate that for injective splints of classical Lie
+algebras the following property is valid:
+
+Let $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})$ be an
+injective
+splint with the decomposition of simple roots $S=S_{\frak{c}}\cup S_{\frak{d}%
+}$ with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}%
+}$.
+
+Then for any simple root $\beta \in S_{\frak{s}}$ there exists the
+pair of
+roots ( $\alpha $ ,$\beta ^{\prime }$) with $\alpha \in $ $S_{\frak{c}%
+},\beta ^{\prime }\in S_{\frak{s}}$ such that $\alpha =\beta
+-\beta ^{\prime }$
+
+Type 1. $\Delta _{G_{2}}\approx (\Delta _{A_{2}},\Delta
+_{A_{2}}).$
+
  \begin{figure}[h!bt]
@@
 \end{figure}
+Here both stems are metric and the corresponding root systems are
+equivalent. In Figure 4 a part of the singular element $\Phi
+_{G_{2}}^{\left( 0\right) }$ is presented. The boundaries of $\bar{C_{\frak{a%
+}}}$ are the dashed lines starting in the center of the singular
+element. It
+contains the edge $\lambda _{2}=-\alpha _{2}=-\beta _{2}$ and the roots $%
+-\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3}$ , $-\beta _{3}$
+($\beta _{3}$ is indicated as $\beta _{l}$). For this root $\beta
+_{1}$ the necessary pair
+is ( $\alpha _{1}$ ,$\beta _{2}$): $\alpha _{1}=\beta _{1}-\beta _{2}$. The $%
+\lambda _{2,3}^{\frak{s}}=\beta _{3}$ edge is equal to $\lambda _{1}^{\frak{s%
+}}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ and $m_{1}$ indice
+is aquired by the $\frak{s}$-module that inherit the second
+indice. In this particular
+case they are $m_{1}=m_{2}=0$. The general case with the initial module $%
+L^{\mu }$ and $\mu =m_{1}\omega _{1}+m_{2}\omega _{2}$.can be
+treated in the same way: one finds an edge $\lambda _{2}=-\left(
+m_{2}+1\right) \beta _{2}$ and put $\lambda
+_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$, its end
+belongs to the boundary $\bar{C_{\frak{a}}}$ . The reflection
+$s_{\beta
+_{2}} $ sends $\beta _{1}$ to $\beta _{3}$ and the corresponding edge $%
+\lambda _{2,3}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{3}$ has
+the same length. Now consider $\lambda _{1}^{\frak{s}}$ (or
+$\lambda _{2,3}^{\frak{s}} $) and $\lambda _{1,3}^{\frak{s}}$ (or
+$\lambda _{2,3,1}^{\frak{s}}$) edges to find that they belong to
+the boundary $\bar{C_{\frak{a}}}$ and the Weyl symmetry predicts
+that $\lambda _{1,3}^{\frak{s}}=-\left( m_{2}+1\right)
+\beta _{3}$ ($\lambda _{2,3,1}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{1}$%
+) . Finally the edge $\lambda _{1,3,2}^{\frak{s}}=-\left(
+m_{1}+1\right) \beta _{2}$ close the polytop . The latter
+corresponds to the singular
+element $\Phi _{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{%
+\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
+\widetilde{\mu }+\rho
+_{\frak{s}}\right) }$ of the module $L_{\frak{s}}^{\left( \widetilde{\mu }%
+\right) }$ with $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}%
+\widetilde{\omega }_{2}$ . Notice that in this case the sign
+factors can be obtained directly in the initial weight system as
+far as the stem is metric.
+
+Type 1. $\Delta _{F_{4}}\approx (\Delta _{D_{4}},\Delta
+_{D_{4}}).$
+
+Both stems are metric and the corresponding root systems are
+equivalent. The system $\Delta _{D_{4}}$ of the subalgebra
+$\frak{a=}D_{4}$ is formed by the set $\left\{ \pm e_{i},\pm
+e_{j}\right\} _{|i,j=1,\ldots 4,\quad i\neq j}$ . The simple roots
+$S_{\frak{c}}$ are $\left\{ e_{2}-e_{3},e_{3}-e_{4}\right\} $ and
+$S_{\frak{d}}=\left\{ e_{4},\frac{1}{2}\left(
+e_{1}-e_{2}-e_{3}-e_{4}\right) \right\} $.
+
+For a module $L^{\mu }$ with $\mu =\sum m_{k}\omega _{k}$ consider the edge $%
+\lambda _{3}=-\left( m_{3}+1\right) e_{4}=-\left( m_{3}+1\right)
+\beta _{3}$
+\ Compose an edge $\lambda _{2}^{\frak{s}}=-\left( \widetilde{m}%
+_{2}+1\right) \beta _{2}$ . Now the necessary pair is $\left(
+\alpha
+_{2}=e_{3}-e_{4},\beta _{3}\right) $. The intersection of $\lambda _{2}^{%
+\frak{s}}$ with the $\alpha _{2}$ -boundary of
+$\bar{C_{\frak{a}}}$ fixes
+its length to be $\lambda _{2}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{2}$%
+\ and the length of the edge $\lambda _{3,2}^{\frak{s}}$ is equal
+to that of
+$\lambda _{2}^{\frak{s}}$. Next consider the edge $\lambda _{2}^{\frak{s}%
+}=-\left( m_{2}+1\right) \beta _{2}$ and the pair $\left( \alpha
+_{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $ \ The length of the
+edge $\lambda _{1}^{\frak{s}}$ becomes equal to $\lambda
+_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$ and so on. The
+edges along the roots like $\alpha _{4}=\beta
+_{4}=\frac{1}{2}\left( e_{1}-e_{2}-e_{3}-e_{4}\right) $ are
+treated similarly and finally the singular element $\Phi
+_{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in
+W_{\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
+\widetilde{\mu }+\rho _{\frak{s}}\right) }$ of the module
+$L_{\frak{s}}^{\left( \widetilde{\mu }\right) }$ with
+$\widetilde{\mu }=\sum m_{k}\widetilde{\omega }_{k}$ is formed in
+$\bar{C_{\frak{a}}}$.
+
+Type 2. $\Delta _{B_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
+^{r}A_{1}}). $
+
+Both stems are metric. The injection is fixed by the stem $\Delta
+_{D_{r}}$ with simple roots $S_{\frak{a}}=\left\{
+e_{1}-e_{2},e_{2}-e_{3},\ldots
+,e_{r-1}-e_{r},e_{r-1}+e_{r}\right\} $ . The second stem
+corresponds to a
+direct sum of algebras $A_{1}$ and has the simple roots $S_{\frak{s}%
+}=\left\{ e_{1},e_{2},\ldots ,e_{r-1},e_{r}\right\} $. Consider the edge $%
+\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ (here $\beta
+_{r}=e_{r}$) and .$\lambda _{r-1}=-\left(
+\widetilde{m}_{r-1}+1\right) \beta _{r-1}$
+attached to it (here $\beta _{r-1}=e_{r-1}$). The corresponding pair is $%
+\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta _{r-1}=e_{r-1}\right) $
+.\ The intersection condition fixes the second edge to be $\lambda
+_{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ , it is orthogonal
+to $\beta _{r}$ so the opposite edge has the same length. The
+Dynkin indice $m_{r-1}$ now refers
+also to the\ simple root $\beta _{r-1}$ . Next consider the obtained edge $%
+\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and $\lambda
+_{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$ to
+obtain the indice $\widetilde{m}_{r-2}=m_{r-2}$ and the edge
+$\lambda _{r-2}=-\left( m_{r-2}+1\right) \beta _{r-2}$ and so on
+till all the pairs of edges are properly fixed. Finally in
+$\bar{C_{D_{r}}}$ the element $\Phi _{\oplus ^{r}A_{1}}^{\left(
+\widetilde{\mu }\right) }=\sum_{w\in W_{\oplus
+^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+%
+\frac{1}{2}\sum e_{k}\right) }$ can be constructed for the module
+$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
+$\widetilde{\mu }=\sum m_{k}\frac{1}{2}e_{k}$ .
+
+Type 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
+^{r}A_{1}}). $
+
+The situation in this case is eqivalent to the previous one and
+the additional edges are constructed similarly.
+
+Type 3 $\Delta _{A_{r}}\approx (\Delta _{A_{r-1}\oplus
+u_{1}},\Delta _{\oplus ^{r}A_{1}}).$
+
+Here only the first stem is metric and it fixes the injection with
+simple roots $S_{\frak{a}}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots
+,e_{r-1}-e_{r}\right\} $ . The second stem corresponding to a direct sum of $%
+r$ copies of $A_{1}$ has the simple roots $S_{\frak{s}}=\left\{
+e_{1}-e_{r+1},e_{2}-e_{r+1},\ldots ,e_{r}-e_{r+1}\right\} $.
+Consider the edge $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$
+with $\beta
+_{r}=e_{r}-e_{r+1}$ and .$\lambda _{r-1}=-\left( \widetilde{m}%
+_{r-1}+1\right) \beta _{r-1}$ \ with $\beta
+_{r-1}=e_{r-1}-e_{r+1}$ attached to it . Then the corresponding
+pair is $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta
+_{r-1}=e_{r-1}-e_{r+1}\right) $ .\ The intersection with the
+boundary of $\bar{C_{A_{r-1}}}$ orthogonal to $\alpha _{r-1}$
+fixes the second edge to be $\lambda _{r-1}=-\left(
+m_{r-1}+1\right) \beta _{r-1}$. The Dynkin indice $m_{r-1}$ is to
+be used for the fundamental weight  $\omega _{r-1}$ . The\
+reflection $s_{\beta _{r}}$ sends $\lambda _{r-1}=-\left(
+m_{r-1}+1\right) \beta _{r-1}$ to $\lambda _{r,r-1}=-\left(
+m_{r-1}+1\right) \beta _{r-1}$\ . Next consider the obtained edge
+$\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and
+$\lambda _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$
+with $\beta _{r-2}=e_{r-2}-e_{r+1} $ to obtain the indice
+$\widetilde{m}_{r-2}=m_{r-2}$ and the edge $\lambda _{r-2}=-\left(
+m_{r-2}+1\right) \beta _{r-2}$ and so on till all the pairs of
+edges are properly fixed. Finally in $\bar{C_{D_{r}}}$ the element
+$\Phi _{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right)
+}=\sum_{w\in W_{\oplus
+^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+%
+\widetilde{\rho }\right) }$ can be constructed for the module
+$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
+$\widetilde{\mu }=\sum m_{k}\beta _{k}$ . The simplest case
+$\Delta _{A_{2}}\approx (\Delta _{A_{1}\oplus u_{1}},\Delta
+_{A_{1}\oplus A_{1}})$ is presented in Example 4.1 and Figure 1.
+
+Type 3 $\Delta _{B_{2}}\approx (\Delta _{A_{1}},\Delta _{A_{2}}).$
+
+The necessary elements are presented in Example 4.1 and Figure 1 , $%
+S_{A\_1}=\left\{ e_{1}-e_{2}\right\} $ , $S_{A\_2}=\left\{
+e_{1},e_{2}\right\} $.The edge $\lambda _{\alpha _{2}}=\lambda
+_{\beta _{2}}=-\left( m_{2}+1\right) \beta _{2}$ has an edge
+$\lambda _{\beta _{1}}=-\left( \widetilde{m}_{1}+1\right) \beta
+_{1}$ attached to it. Consider the pair $\left( \alpha
+_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right) $ .The end of the edge
+$\lambda _{\beta _{1}}$ is to define a weight
+invariant under the reflexion $s_{\alpha _{1}}$ . This defines its length: $%
+\lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$ . In the
+coimage of
+the second stem, that is in the $A_{2}$ root system, the reflection $%
+s_{\beta _{2}}$ sends $\lambda _{\beta _{1}}=-\left(
+m_{1}+1\right) \beta
+_{1}$ to $\lambda _{2,3}$\ ., thus the latter edge has the same length in $%
+\beta _{3}=e_{1}+e_{3}$ , we have $\lambda _{2,3}=-\left(
+m_{1}+1\right)
+\beta _{3}$ with $\beta _{3}=e_{1}+e_{3}$ . The irreducible $\frak{s}$%
+-module has the highest weight $\widetilde{\mu }=m_{1}\widetilde{\omega }%
+_{1}+m_{2}\widetilde{\omega }_{2}$ . In Figure 1 we see the
+details of these relations in a particular case where
+$L_{B_{2}}^{\left[ 3,2\right] }$ is reduced to a subalgebra
+$A_{1}\oplus u\left( 1\right) $ and the
+corresponding highest weights with their multiplicities form the diagram $%
+\mathcal{N}_{A\_2}^{\left[ 3,2\right] }$ .
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2011-10-14 AffineLieAlgebras/Splints/paper.tex
Misprints fixed

@@
 injection fan for regular embeddings of reductive subalgebras
-${\mathfrak a}\longrightarrow {\mathfrak g}$. We show that (under
+${\mathfrak a}\longrightarrow {\mathfrak g}$ of simple Lie algebra $\mathfrak{g}$. We show that (under
 certain conditions described in section \ref{sec:stems and
 multiplicity functions}) splint is a natural tool to study
-reduction properties of simple Lie algebra ${\mathfrak g}$-modules
+reduction properties of ${\mathfrak g}$-modules
 with respect to a subalgebra ${\mathfrak a}\longrightarrow
@@
 \mathfrak{h}_{\mathfrak{a}}^{\ast }\subset \mathfrak{h}_{\mathfrak{g }%
-}^{\ast }$. Let $\mathfrak{a}^S$ be a semisimple summand of
+}^{\ast }$. Let $\mathfrak{a}^{\mathfrak{s}}$ be a semisimple summand of
 $\mathfrak{a}$,
-this means that $\mathfrak{a}=\mathfrak{a}^S \oplus \mathfrak{u}(1)\oplus %
-\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^S$
+this means that $\mathfrak{a}=\mathfrak{a}^{\mathfrak{s}} \oplus \mathfrak{u}(1)\oplus %
+\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^{\mathfrak{s}}$
 to be a proper regular subalgebra and $\mathfrak{a}$ to be the
@@
 
-$r$ , $\left( r_{\mathfrak{a}^S}\right) $ --- the rank of
-$\frak{g}$ $\left( \mathrm{{resp. }\mathfrak{a}^S}\right) $ ;
+We use the following notations:
+$r$ , $\left( r_{\mathfrak{a}^{\mathfrak{s}}}\right) $ --- the rank of
+$\frak{g}$ $\left( \mathrm{{resp. }\mathfrak{a}^{\mathfrak{s}}}\right) $ ;
 
@@
 i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{%
+a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
+^S}\right) $;
+
+$\omega _{i}$ , $\left( \omega _{\left( \frak{a}\right) j}\right) $ --- the $%
+i$-th (resp. $j$-th) fundamental weight for $\frak{g}$ $\left( \mathrm{{resp.}\frak{%
 a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
@@
 b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+\sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
 _{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
@@
 where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $%
-\frak{g}$ orthogonal to roots of $\frak{a}$
+\frak{g}$ orthogonal to roots of $\frak{a}$, $W_{\perp}$ is a Weyl group of $\mathfrak{a}_{\perp}$
 \begin{eqnarray}
@@
 _{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product (%
-\ref{product}) and defines an injection fan $\Gamma _{\frak{a}%
-\hookrightarrow \frak{g}}$.
+\ref{product}) and it defines an injection fan $\Gamma _{\frak{a}%
+\hookrightarrow \frak{g}}$. Denote by $\Delta_{\mathfrak{s}0}$ the coimage of the second embedding $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\mathfrak{g}}$.
 
@@
 
-In this Section we study properties of injective splints. It will
-be demonstrated that provided such splint exists to find branching
+In this Section we study properties of injective splints  $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
+$. It will
+be demonstrated that in this case to find branching
 coefficients for a splinting injection $\frak{a}\hookrightarrow
@@
 \frak{a}\rightarrow \frak{g}}$. Consider the highest weight module $L_{\frak{%
-s}}^{\nu }$. An embedding $\phi :\Delta _{\frak{s}\,0}\longrightarrow \Delta
+s}}^{\nu }$. The embedding $\phi :\Delta _{\frak{s}\,0}\longrightarrow \Delta
 _{\frak{g}}$ sends the singular element $\Psi _{\frak{s}}^{\left( \nu
@@
 }^{+}}(1-e^{-\beta })}\phi \left( \Psi _{\frak{s}}^{\left( \nu \right)
-}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\frak{s}\left( 0\right)
+}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\frak{s}0
 }^{+}}(1-e^{-\beta })}\Psi _{\frak{s}}^{\left( \nu \right) }=\mathrm{ch}%
@@
 first type splints are equivalent and in the second are not. In the third
-type splints only $\Delta _{\frak{a}}$ is embedded metrically. the summands $%
+type splints only $\Delta _{\frak{a}}$ is embedded metrically. The summands $%
 u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$ . This does not change
@@
 \Delta _{\frak{s}0}$ is simple. In Appendix it is shown that for any such $%
-\beta _{l}$ there corresponds a root $\alpha _{l}\in S_{\frak{c}}$ such that
+\beta _{l}$ there exists a root $\alpha _{l}\in S_{\frak{c}}$ such that
 $\beta _{l}=\alpha _{l}+\beta _{k}$. It is easily seen that the
@@
 to incorporate in it additional formal elements $\left\{ -e^{\mu +\rho
--\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\} $ This
+-\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\}.$ This
 fixes the starting edges of the diagram $\phi ^{-1}\left( \Phi _{\frak{s}}^{%
@@
 \frak{c}}\right\} $). Thus we have constructed all the formal elements\ with
-the appropriate sing factors that after being added to $\Phi _{\frak{g}%
+the appropriate sign factors that after being added to $\Phi _{\frak{g}%
 }^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ form the diagram $\phi
@@
 It is significant that for the injections $D_{r}\hookrightarrow B_{r}$ , $%
-D_{r}\hookrightarrow C_{r}$ and $A_{r}\hookrightarrow
-A_{r-1}\oplus u\left( 1\right) $ splint technique shows
+D_{r}\hookrightarrow C_{r}$ and $A_{r-1}\oplus u\left( 1\right) \hookrightarrow A_{r}$ splint technique shows
 immediately Gelfand-Tzeytlin rules for branching: the nonzero
@@
   }
-  \caption{Weyl group orbit (dotted) producing singular element of $A_{2}$-module $L^{(3,2)}$ and its decomposition into the sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules (dashed).
-Weight multiplicities of $A_{1}\oplus A_{1}$-module coincide with branching coefficients for the reduction $L^{(3,2)}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}
+  \caption{Positive roots of $G_{2}$ and formation of singular element $\Phi^{(0)}_{\mathfrak{s}}$ in the main Weyl chamber of $\mathfrak{a}=A_{2}$.}
 \end{figure}
@@
 contains the edge $\lambda _{2}=-\alpha _{2}=-\beta _{2}$ and the roots $%
--\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3}$ , $-\beta _{3}$
+-\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3},\; -\beta _{3}$
 ($\beta _{3}$ is indicated as $\beta _{l}$). For this root $\beta
 _{1}$ the necessary pair
-is ( $\alpha _{1}$ ,$\beta _{2}$): $\alpha _{1}=\beta _{1}-\beta _{2}$. The $%
+is  $(\alpha _{1}, \beta _{2})$: $\alpha _{1}=\beta _{1}-\beta _{2}$. The $%
 \lambda _{2,3}^{\frak{s}}=\beta _{3}$ edge is equal to $\lambda _{1}^{\frak{s%
-}}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ and $m_{1}$ indice
+}}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ and $m_{1}$ index
 is aquired by the $\frak{s}$-module that inherit the second
@@
 ) . Finally the edge $\lambda _{1,3,2}^{\frak{s}}=-\left(
-m_{1}+1\right) \beta _{2}$ close the polytop . The latter
+m_{1}+1\right) \beta _{2}$ close the polytope. The latter
 corresponds to the singular
@@
 $\frak{a=}D_{4}$ is formed by the set $\left\{ \pm e_{i},\pm
-e_{j}\right\} _{|i,j=1,\ldots 4,\quad i\neq j}$ . The simple roots
+e_{j}\right\} _{|i,j=1,\ldots 4,\; i\neq j}.$ The simple roots
 $S_{\frak{c}}$ are $\left\{ e_{2}-e_{3},e_{3}-e_{4}\right\} $ and
@@
 \lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ (here $\beta
-_{r}=e_{r}$) and .$\lambda _{r-1}=-\left(
+_{r}=e_{r}$) and $\lambda _{r-1}=-\left(
 \widetilde{m}_{r-1}+1\right) \beta _{r-1}$
@@
 to $\beta _{r}$ so the opposite edge has the same length. The
-Dynkin indice $m_{r-1}$ now refers
+Dynkin index $m_{r-1}$ now refers
 also to the\ simple root $\beta _{r-1}$ . Next consider the obtained edge $%
@@
 _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$ to
-obtain the indice $\widetilde{m}_{r-2}=m_{r-2}$ and the edge
+obtain the index $\widetilde{m}_{r-2}=m_{r-2}$ and the edge
 $\lambda _{r-2}=-\left( m_{r-2}+1\right) \beta _{r-2}$ and so on
 till all the pairs of edges are properly fixed. Finally in
-$\bar{C_{D_{r}}}$ the element $\Phi _{\oplus ^{r}A_{1}}^{\left(
+$\bar{C}_{D_{r}}$ the element $\Phi _{\oplus ^{r}A_{1}}^{\left(
 \widetilde{\mu }\right) }=\sum_{w\in W_{\oplus
@@
 with $\beta
-_{r}=e_{r}-e_{r+1}$ and .$\lambda _{r-1}=-\left( \widetilde{m}%
+_{r}=e_{r}-e_{r+1}$ and $\lambda _{r-1}=-\left( \widetilde{m}%
 _{r-1}+1\right) \beta _{r-1}$ \ with $\beta
@@
 pair is $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta
-_{r-1}=e_{r-1}-e_{r+1}\right) $ .\ The intersection with the
-boundary of $\bar{C_{A_{r-1}}}$ orthogonal to $\alpha _{r-1}$
+_{r-1}=e_{r-1}-e_{r+1}\right).$ The intersection with the
+boundary of $\bar{C}_{A_{r-1}}$ orthogonal to $\alpha _{r-1}$
 fixes the second edge to be $\lambda _{r-1}=-\left(
-m_{r-1}+1\right) \beta _{r-1}$. The Dynkin indice $m_{r-1}$ is to
-be used for the fundamental weight  $\omega _{r-1}$ . The\
+m_{r-1}+1\right) \beta _{r-1}$. The Dynkin index $m_{r-1}$ is to
+be used for the fundamental weight  $\omega _{r-1}.$ The\
 reflection $s_{\beta _{r}}$ sends $\lambda _{r-1}=-\left(
 m_{r-1}+1\right) \beta _{r-1}$ to $\lambda _{r,r-1}=-\left(
-m_{r-1}+1\right) \beta _{r-1}$\ . Next consider the obtained edge
+m_{r-1}+1\right) \beta _{r-1}.$ Next consider the obtained edge
 $\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and
 $\lambda _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$
-with $\beta _{r-2}=e_{r-2}-e_{r+1} $ to obtain the indice
+with $\beta _{r-2}=e_{r-2}-e_{r+1} $ to obtain the index
 $\widetilde{m}_{r-2}=m_{r-2}$ and the edge $\lambda _{r-2}=-\left(
 m_{r-2}+1\right) \beta _{r-2}$ and so on till all the pairs of
-edges are properly fixed. Finally in $\bar{C_{D_{r}}}$ the element
+edges are properly fixed. Finally in $\bar{C}_{D_{r}}$ the element
 $\Phi _{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right)
@@
 $L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
-$\widetilde{\mu }=\sum m_{k}\beta _{k}$ . The simplest case
+$\widetilde{\mu }=\sum m_{k}\beta _{k}.$ The simplest case
 $\Delta _{A_{2}}\approx (\Delta _{A_{1}\oplus u_{1}},\Delta
@@
 _{1}$ attached to it. Consider the pair $\left( \alpha
-_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right) $ .The end of the edge
+_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right).$ The end of the edge
 $\lambda _{\beta _{1}}$ is to define a weight
-invariant under the reflexion $s_{\alpha _{1}}$ . This defines its length: $%
+invariant under the reflexion $s_{\alpha _{1}}.$ This defines its length: $%
 \lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$ . In the
@@
 m_{1}+1\right) \beta
-_{1}$ to $\lambda _{2,3}$\ ., thus the latter edge has the same length in $%
+_{1}$ to $\lambda _{2,3}$, thus the latter edge has the same length in $%
 \beta _{3}=e_{1}+e_{3}$ , we have $\lambda _{2,3}=-\left(

### 2011-10-17 AffineLieAlgebras/SLE/article.tex
Minor changes in sle paper

@@
 
+\subsection{Semisimple Lie algebras and coset construction}
+\label{sec:semis-lie-algebr}
+
+It is well known that unitary minimal models with central charge $c=1-\frac{6}{m(m+1)}$ can be obtained from coset construction starting with $su(2)_{m}\oplus su(2)_{1}$ WZW-model and factorizing it by $su(2)_{m+1}$.
+Here lower index represents level of affine Lie algebra representation.
+
+In this case the dimension of Lie algebra $\gf=su(s)\oplus su(2)$ is 6, dual Coxeter number $h^{v}=2+2=4$.
+
+\begin{equation*}
+  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
+\end{equation*}
+
+SLE and factorization by equivalence relations.
+
 \subsection{Parafermions}

### 2011-10-17 AffineLieAlgebras/SLE/article.tex
Couple more formulas in SLE paper

@@
 
+\begin{equation}
+  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
+\label{eq:6}
+\end{equation}
+
+For semisimple Lie algebra $\gf=\gf_{1}+\gf_{2}$ with generators $J^{a}$ and $\tilde{J}^{b}$ correspondingly we can more explicitly write the relation \eqref{eq:6} as
+
 \begin{equation*}
-  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
+  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\left(\sum_{a} J^{a}_{-1} J^{a}_{-1}+\sum_{b}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right) \right) \left|\phi_{\Lambda}\right>
 \end{equation*}
 
+This vector should be null vector of level two, so $L_{2}\left|\psi\right>=L_{1}\left|\psi\right>=0$. Then we get following algebraic relations for semisimple Lie algebra:
+\begin{equation}
+  \label{eq:7}
+  \left( 3\kappa h_{\Lambda} +\frac{1}{2} \tau (k_{1} \mathrm{dim} \gf_{1}+k_{2}\mathrm{dim} \gf_{2}) -8 h_{\Lambda} - c\right)\phi_{\Lambda}=0
+\end{equation}
 SLE and factorization by equivalence relations.

### 2011-10-20 AffineLieAlgebras/SLE/article.tex
Added (almost) all texts and figures to thesis. Some work on SLE paper.

@@
 Schramm-Loewner evolution, introduced by Oded Schramm in papers \cite{schramm2000scaling} is
+
+The connection of SLE with CFT was studied in papers \cite{bauer2004conformal,bauer2004cfts,bauer2003sle,bauer2002sle}.
+
+Reviews \cite{rohde2005basic}, \cite{bauer20062d}, \cite{Cardy:2005kh}.
+
+SLE and conformal field theories with additional symmetries \cite{alekseev2010sle}, \cite{santachiara2008sle,picco2008numerical}, \cite{bettelheim2005stochastic}, \cite{Rasmussen:2004xr}.
 
@@
 Now we use Ito calculus to calculate increment of our correlation function. It should be zero so we get the equation:
-\begin{equation*}
+\begin{equation}
   \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{-h_{i}}\right)\mathbb{E}\left[d 
@@
       \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}
-\end{equation*}
+\label{eq:8}
+\end{equation}
 Then use explicit form of conformal map and obtain
@@
 \subsection{Primary fields}
-
+\label{sec:primary-fields}
 Primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra and subalgebra, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
@@
 
-Conformal weight of primary field are equal to
+Conformal weight of primary field is equal to
 \begin{multline}
@@
 \subsection{SLE on coset space}
+Consider Lie (semi-)simple group $G$ with Lie algebra $\gf$ and (semi-)simple subgroup $A\subset G$ with Lie algebra $\af\subset \gf$. 
+The simplest way to study SLE on $G/A$ coset space is to restrict random walk on group manifold to the coset space by the choice of basis in $\gf$.
+Assume that generators $\{J^{a};\; a=1\dots \mathrm{dim}\gf\}$ are chosen in such way that $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\; a=\mathrm{dim}\gf-\mathrm{dim}\af\dots \mathrm{dim}\gf\}$ are the generators of subalgebra $\af\subset \gf$.
+Now we can consider $\mathrm{dim}\gf-\mathrm{dim}\af$-dimensional Brownian motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \; d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\mathrm{dim}\gf-\mathrm{dim}\af$.
+
+Then for generator of field transformation we can write 
+\begin{equation}
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}\left(d \theta ^{a} t^{a}_{i}\right)\right)
+\label{eq:5}
+\end{equation}
+Substituting to equation \eqref{eq:8} we get martingale condition
+
+\begin{equation}
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0
+\label{eq:9}
+\end{equation}
+
+which can be rewritten as the requirement for
+\begin{equation}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}J^{a}_{-1}J^{a}_{-1}\right)\right) \phi_{\Lambda}
+\label{eq:10}
+\end{equation}
+to be level two null-field. Here primary field $\phi_{\Lambda}$ is indexed by the pair $\Lambda=(\mu,\nu)$ with the equivalence relations \ref{sec:primary-fields}.
+
+Consider the simplest possible example.
+Let $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$.
+Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
+The equation \eqref{eq:10} is now
+\begin{equation}
+  \label{eq:11}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{\Lambda}
+\end{equation}
+If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\; J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
+\begin{equation}
+ \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{\Lambda}
+\label{eq:12}
+\end{equation}
+which coincides with the equation for parafermionic fields introduced in paper \cite{santachiara2008sle}.
+
+Central charge in this case is equal to
+\begin{equation}
+  \label{eq:14}
+  c=\frac{2(k-1)}{k+2}
+\end{equation}
+
+Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
+\begin{equation}
+  \label{eq:13}
+  L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{\Lambda}=0\quad \Longrightarrow\quad  (3\kappa-8) h_{\Lambda}+\frac{2(k-1)}{k+2}+\tau k =0
+\end{equation}
+Another equation can be obtained by action of $L_{1}^{2}$
+\begin{equation}
+  \label{eq:15}
+  L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{\Lambda}=0
+\end{equation}
+or
+\begin{equation}
+  \label{eq:16}
+  \left(12 h_{\Lambda}+2\kappa h_{\Lambda} (2h_{\Lambda}+1) + 2 \tau J^{3}_{0}J^{3}_{0}\right) \phi_{\Lambda}=0
+\end{equation}
+
+Alternative approach is to study $\gf\oplus \af$ WZNW-model and then impose equivalence relations on the solutions. 
+So we need to generalize the analysis of \cite{alekseev2010sle} to the case of semisimple Lie algebras.
+
+From equation
+
+Now consider as an example $\frac{SU(2)_{k}\times SU(2)_{1}}{SU(2)_{k+1}}$ -- another coset realization for minimal unitary models.
+
+We get following relations on $\kappa,\tau$ and primary fields. So we see that the solutions at level $k$ are
+
+Now we need to impose equivalence relations.
+
+We get
+
 Consider gauge transformation in gauged WZNW model:
@@
 \end{equation*}
-which coincides with the result of Santachiara [arXiv:0705.2749].
+which coincides with the result of Santachiara \cite{santachiara2008sle}.
 

### 2011-10-20 AffineLieAlgebras/Thesis/1.tex
Added (almost) all texts and figures to thesis. Some work on SLE paper.

@@
 \label{sec:representation-theory}
+
+\subsection{Алгебра петель и центральное расширение}
+\label{sec:loop-algebra-central-extension}
+
 Определение аффинных алгебр. Корни, веса, кратности. Категория О.
+
+\subsection{Представления аффинных алгебр Ли}
+\label{sec:affine-lie-algebra-representations}
 
@@
 Веер вложения. Алгоритм.
+
+\begin{abstract}
+  Recurrent relations for branching coefficients in affine Lie algebras
+  integrable highest weight modules are studied. The decomposition algorithm
+  based on the injection fan technique is developed for the case of an arbitrary
+  reductive subalgebra. In particular we consider the situation where
+  the Weyl denominator becomes singular with respect to the subalgebra.
+  We demonstrate
+  that for any reductive subalgebra it is possible to define the
+  injection fan and the analogue of the Weyl numerator -- the tools that describe
+  explicitly the recurrent properties of branching coefficients.
+  Possible applications of fan technique in CFT models are considered.
+\end{abstract}
+
+\subsection{Introduction}
+\label{sec:introduction}
+
+The branching problem for affine Lie algebras emerges in conformal field theory, for example,
+in the construction of modular-invariant partition functions \cite{difrancesco1997cft}.
+Recently the problem of conformal embeddings was considered in \cite{coquereaux2008conformal}.
+
+There are different approaches to deal with branching coefficients. Some of them use the BGG
+resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
+\cite{kac1990idl},\cite{wakimoto2001idl}), the Schur function series \cite{fauser2006new}, the BRST
+cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or some
+combinatorial methods applied in \cite{feigin707principal}.
+
+In this paper we prove that
+for an arbitrary reductive subalgebra branching coefficients are subject to
+a set of recurrent properties that can be explicitly formulated and that there exists
+an effective and simple algorithm to solve these recurrent relations step by step.
+The basic idea is similar to the one used in \cite{ilyin812pbc} for maximal embeddings.
+In our case the algorithm is essentially different, new properties of singular weights
+are determined to deal with an arbitrary reductive injection $\frak{a} \rightarrow \frak{g}$.
+
+The principal point is to consider the subalgebra $\af$ together with its
+counterpart $\afb$ orthogonal to $\af$.
+For any reductive algebra $\af$ the subalgebra $\afb \subset \frak{g} $ is regular and reductive.
+For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
+$\left(  \af, \afb \right)$ we consider
+the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
+in the Weyl character formula
+$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$,
+see for example \cite{humphreys1997introduction})
+the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
+We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair
+$\left(  \af, \afb \right)$ the element
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
+the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
+This decomposition provides the possibility to construct a recurrent property for branching coefficients corresponding
+to the injection $\frak{a} \rightarrow \frak{g} $.
+The property is formulated in
+terms of the specific element $\Gamma_{\af \rightarrow \gf}$ of the group algebra
+$\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
+Using this tool we formulate a simple and
+explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
+subalgebras of finite-dimensional or affine Lie algebras.
+In the case of maximal embedding the corresponding fan is unsubtracted, the singular element
+becomes trivial
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\Psi ^{\left( \mu \right) }_{\left(  \gf\right)}$
+and the relations described earlier in \cite{ilyin812pbc} are reobtained.
+
+We demonstrate that our algorithm is effective and can be used in studies
+of conformal embeddings and coset constructions in rational conformal field theory.
+
+The paper is organized as follows. In the subsection \ref{sec:notation}  we fix the general notations.
+In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula based on
+recurrent properties of anomalous branching coefficients and describe the decomposition algorithm
+for integrable highest weight modules
+$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
+(subsection \ref{sec:algorithm}). In Section \ref{sec:finite-dimens-lie} we present several
+simple examples for finite-dimensional Lie algebras. Affine Lie algebras and their applications in
+CFT models are considered in Section \ref{sec:phys-appl}.
+General properties of the proposed algorithm and
+possible further developments are also discussed (Section \ref{sec:conclusion}).
+
+\subsubsection{Notation}
+\label{sec:notation}
+
+Consider affine Lie algebras $\frak{g}$ and $\af$ with
+underlying finite-dimensional subalgebras $\go$ and $%
+\ao$ and an injection $\af\longrightarrow \frak{g%
+}$ such that $\af$ is a reductive subalgebra $\frak{a\subset g}$ with
+correlated root spaces: $\frak{h}_{\af}^{\ast }\subset \frak{h}_{\frak{g%
+}}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
+}_{\go}^{\ast }$\
+.
+We use the following notations:
+
+$L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
+of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\af$
+-module with the highest weight $\nu $ );
+
+$r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\frak{g}$ $%
+\left( \mbox{resp. }\af\right) $ ;
+
+$\Delta $ $\left( \Delta _{\af}\right) $--- the root system; $\Delta
+^{+} $ $\left( \mbox{resp. }\Delta _{\af}^{+}\right) $--- the positive
+root system (of $\frak{g}$ and $\af$ respectively);
+
+$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\af}\left(
+\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $\Delta
+$ (resp. in $\left( \Delta _{\af}\right) $);
+
+$\co{\Delta}$ , $\left( \co{\Delta _{\af}}%
+\right)$ --- the finite root system of the subalgebra $\co{%
+\frak{g}}$ (resp. $\co{\af}$);
+
+$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\af}^{\nu }\right) $ --- the
+weight diagram of $L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right)
+$ ;
+
+$W$ , $\left( W_{\af}\right) $--- the corresponding Weyl group;
+
+$C$ , $\left( C_{\af}\right) $--- the fundamental Weyl chamber;
+
+$\bar{C}, \left(\bar{C_{\mathfrak{a}}}\right)$ --- the closure of the fundamental Weyl chamber;
+
+$\rho $\ , $\left( \rho _{\af}\right) $\ --- the Weyl vector;
+
+$\epsilon \left( w\right) :=\det \left( w\right) $ ;
+
+$\alpha _{i}$ , $\left( \beta _{j}\right) $ --- the $i
+$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\af%
+\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
+
+$\delta $ --- the imaginary root of $\frak{g}$ (and of $\af$ if any);
+
+$\alpha _{i}^{\vee }$ , $\left( \beta _{j}^{\vee
+}\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\af%
+\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
+
+$\co{\xi }$ , $\co{\xi _{\left( \af\right) }}$
+--- the finite (classical) part of the weight $\xi \in P$ , $\left( \mbox{%
+resp. }\xi _{\left( \af\right) }\in P_{\af}\right) $;
+
+$\lambda =\left( \co{\lambda };k;n\right) $ ---
+decomposition of the affine weight $\lambda$ indicating the finite
+part $\co{\lambda }$, the level $k$ and the grade $n$;
+
+$P$ $\left( \mbox{resp. } P_{\af}\right) $ \ --- the weight lattice;
+
+$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
+}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mbox{%
+resp. }\in P_{\af}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
+L_{\af}^{\nu } $);
+
+$ch\left( L^{\mu }\right) $ $\left( \mbox{resp. }ch\left( L_{\af}^{\nu
+}\right) \right) $--- the formal character of $L^{\mu }$ $\left( \mbox{resp. }%
+L_{\af}^{\nu }\right) $;
+
+$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
++\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
+\mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;
+
+$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
+mult}\left( \alpha \right) }}\quad $
+$\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
+\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
+\left( \alpha \right) }}\right) $--- the Weyl denominator.
+
+\subsection{Recurrent relations for branching coefficients.}
+\label{sec:recurr-form-branch}
+
+Consider an integrable module $L^{\mu }$
+of $\frak{g}$ with the highest weight $\mu $ and
+let $\af\subset \frak{g}$ be a reductive subalgebra of $\frak{g}$.
+With respect to $\af$ the module $L^{\mu }$ is completely reducible,
+\begin{equation*}
+ L_{\frak{g}\downarrow \af}^{\mu }=\bigoplus
+\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
+\end{equation*}
+Using the projection operator $\pi_{\af}$ (to the weight space $\frak{h_a}^*$)
+one can  rewrite this decomposition in terms of formal characters:
+\begin{equation}
+\label{branching1}
+ \pi _{\af}\circ ch\left( L^{\mu }\right)
+ =\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu)}ch\left( L_{\af}^{\nu }\right) .
+\end{equation}
+We are interested in branching coefficients $b^{(\mu)}_{\nu}$.
+
+\subsubsection{Orthogonal subalgebra and injection fan.}
+\label{subsec:branching-orthog-pair}
+
+In this subsection we shall introduce some simple constructions that will be used
+in our studies of branching and in particular the "orthogonal partner" $\afb$ for a
+reductive subalgebra $\af$  in  $\gf$.
+
+In the Weyl-Kac formula both numerator and denominator  can be considered
+as formal elements containing the singular weights of the Verma modules $V^{\xi}$
+with the highest weights $\xi=\mu$ and $\xi=0$ \cite{humphreys1997introduction}.
+We attribute singular elements to the corresponding integrable modules $L^{\mu }$
+and $L_{\af}^{\nu }$:
+\begin{equation*}
+\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho },
+\end{equation*}
+\begin{equation*}
+\Psi _{ \af}^{\left( \nu \right) }:=
+\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho
+_{_{\af}})-\rho _{_{\af}}}.
+\end{equation*}
+and use the Weyl-Kac formula in the form
+\begin{equation}
+\label{Weyl-Kac2}
+ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}
+{\Psi ^{\left( 0 \right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
+\end{equation}
+
+Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
+we get the relation connecting the
+singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{ \af}^{\left( \nu \right) }$ :
+\begin{eqnarray}
+\nonumber
+\pi _{\af}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w
+(\mu +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{%
+mult}(\alpha )}}\right) &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}%
+\frac{\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{%
+\af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
+}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\af}(\beta )}},  \label{eq:4} \\
+\pi _{\af}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
+&=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{ \frak{%
+a}}^{\left( \nu \right) }}{R_{\af}}.
+\end{eqnarray}
+Here $\Delta _{\af}^{+}$ is the set of
+positive roots of the subalgebra $\af$ (without loss of generality we consider
+them as vectors from the positive root space $\frak{h}^{\ast  +}$ of $\frak{g}$).
+
+Consider the root subspace
+$\frak{h}_{\perp \af}^{\ast }$ orthogonal to  $\af$,
+\begin{equation*}
+\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }
+|\forall h \in \hf_{\af};  \eta\left(h \right)=0 \right\} ,
+\end{equation*}
+and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
+to $\af$,
+\begin{eqnarray*}
+\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|
+\forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} , \\
+\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
+}^{+}|\forall h \in \hf_{\af};  \beta^{+}\left(h \right)=0  \right\} .
+\end{eqnarray*}
+Let $W_{\af_{\perp }}$ be the subgroup of $W$ generated by the
+reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\af%
+_{\perp }}^{+}$ . The subsystem $\Delta _{\af_{\perp }}$ determines the
+subalgebra $\af_{\perp }$ with the Cartan subalgebra $\frak{h}_{\af%
+_{\perp }}$. Let
+\begin{equation*}
+\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
+}|\forall h \in \hf_{\af\oplus \af_{\perp}}; \eta \left( h \right)=0 \right\}
+\end{equation*}
+and consider the subalgebras
+\begin{eqnarray*}
+\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
+\\
+\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
+\end{eqnarray*}
+Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
+$\left( \af,\af_{\perp}\right) $
+of subalgebras in $\frak{g}$.
+
+For the Cartan subalgebra we have the decomposition
+\begin{equation}
+\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\af_{\perp }}\oplus
+\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
+\af_{\perp }}=\frak{\frak{h}_{\widetilde{\af_{\perp }}}}\oplus
+\frak{h}_{\af}.
+\end{equation}
+For the subalgebras of an orthogonal pair $\left( \af,\af_{\perp
+}\right) $ we consider the corresponding Weyl vectors, $\rho _{\af}$
+and $\rho _{\af_{\perp }}$ , and\ form the so called ''defects'' $%
+\mathcal{D}_{\af}$ and $\mathcal{D}_{\af_{\perp }}$ of the
+injection:
+\begin{equation}
+\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
+\end{equation}
+\begin{equation}
+\label{defect-perp}
+\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi _{\af%
+_{\perp }}\circ\rho .
+\end{equation}
+For the highest weight module $L_{\frak{g}}^{\mu }$ consider the singular
+weights $\left\{\left( w(\mu +\rho )-\rho \right)|w  \in W \right\}$ and
+their projections to $h_{\widetilde{\af_{\perp }}}^{\ast }$ (additionally
+shifted by the defect $-\mathcal{D}_{\af_{\perp }}$):
+\begin{equation*}
+\mu _{\widetilde{\af_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
+a}_{\perp }}}\circ\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp
+}},\quad w\in W.
+\end{equation*}
+Among the weights $\left\{\mu _{\widetilde{\af_{\perp }}}\left( w\right)
+|w\in W\right\}$ choose those located in the fundamental chamber $\overline{C_{%
+\widetilde{\af_{\perp }}}}$ and let $U$ be the set of representatives $%
+u $ for classes $W/W_{\af_{\perp }}$ such that
+
+\begin{equation}
+U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
+\in \overline{C_{\widetilde{\af_{\perp }}}}\right\} \quad .
+\label{U-def}
+\end{equation}
+For the same set $U$ introduce the weights
+\begin{equation*}
+\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho %
+\right] +\mathcal{D}_{\af_{\perp }}.
+\end{equation*}
+To simplify the form of relations we shall now on omit the sign "$\circ$" in projected
+weights.
+
+To describe the recurrent properties for branching coefficients $b_{\nu
+}^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc}. One of the
+main tools is the set of weights $\Gamma _{\af\rightarrow \frak{g}%
+} $ called the injection fan. As far as we consider the general situation
+(where the injection is not necessarily maximal) the notion of the injection fan is
+modified:
+
+\begin{definition}
+\label{fan-definition} For the product
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left( 1-e^{-\pi
+_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
+}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
+)e^{-\gamma }  \label{eq:6}
+\end{equation}
+consider the carrier $\Phi _{\af\subset \frak{g}}\subset P_{\af}$
+of the function $s(\gamma )=\det \left( \gamma \right) $ :
+\begin{equation}
+\Phi _{\af\subset \frak{g}}=\left\{ \gamma \in P_{\af}|s(\gamma
+)\neq 0\right\}   \label{eq:37}
+\end{equation}
+The ordering of roots in $\co{\Delta _{\af}}$ induce the
+natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
+the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
+\begin{equation}
+\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
+\label{fan-defined}
+\end{equation}
+is called the \textit{injection fan}.
+\end{definition}
+In the next subsection we shall see how the injection fan defines the recurrent
+properties of branching coefficients. It must be noticed that the injection fan is
+the universal instrument that depends only on the injection.
+
+\subsubsection{Decomposing the singular element.}
+\label{subsec:decomp-sing-element}
+
+Now we shall prove that the Weyl-Kac character formula (in terms of singular
+elements) describes the particular case of a more general relation:
+
+\begin{lemma}
+\label{lemma}
+Let $\left( \af,\afb \right)$ be the orthogonal pair of reductive
+subalgebras in $\frak{g}$, with $\widetilde{\af_{\perp }}=\af%
+_{\perp }\oplus \frak{h}_{\perp }$ and $\widetilde{\af}=\af\oplus
+\frak{h}_{\perp }$ ,
+
+$L^{\mu }$ be the highest weight module with the singular element
+$\Psi ^{\left(\mu \right)}$ ,
+
+$R_{\af_{\perp }}$ be the Weyl denominator for $\af_{\perp }$.
+
+Then the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+=\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}\right) $
+can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
+singular weights $e^{\mu _{\af}\left( u\right) }$ with the
+coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
+}}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right) $:
+\begin{equation}
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\quad \pi _{\af}\left( \frac{\Psi^{\mu }}{R_{\af%
+_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }
+\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
+\widetilde{\af_{\perp }}}\left( u\right) }\right) e^{\mu _{\af}\left( u \right) }.
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+With $u\in U $   and $v\in W_{\afb}$ apply the decomposition
+\begin{equation*}
+u(\mu +\rho )=\pi _{\af } u(\mu +\rho )+\pi _{
+\widetilde{\af_{\perp }} } u(\mu +\rho )
+\end{equation*}
+to the singular weight
+\begin{equation}
+\label{sing-decomp-1}
+\begin{array}{lcl}
+vu(\mu +\rho )-\rho &=&\pi _{ \af }\left( u(\mu +\rho
+)\right) -\rho +\rho _{\af_{\perp }}+\pi _{ \hfb }\rho \\
+&& + \ v\left( \pi _{ \widetilde{%
+\af_{\perp }} }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
+\af_{\perp }}\right) -\rho _{\af_{\perp }} -\pi _{ \hfb }\rho.
+\end{array}
+\end{equation}
+Use the defect $\mathcal{D}_{\afb}$ (\ref{defect-perp}) to simplify
+the first summand in (\ref{sing-decomp-1}):
+\begin{equation*}
+\begin{array}{r}
+\pi _{ \af }\left( u(\mu +\rho )\right) -\rho +\rho _{%
+\mathfrak{a}_{\perp }}+\pi _{ \hfb }\rho = \\
+\pi _{ \af }\left( u(\mu +\rho )\right) -\pi _{\af}\rho
+-\pi _{\afb}\rho +\rho _{\afb}= \\
+=\pi _{ \af }\left( u(\mu +\rho )-\rho \right) +%
+\mathcal{D}_{\afb},
+\end{array}
+\end{equation*}
+and the second one:
+\begin{equation*}
+\begin{array}{c}
+v\left( \pi _{ \widetilde{%
+\af_{\perp }} }u(\mu +\rho )-\rho _{\af_{\perp }}+\rho _{%
+\af_{\perp }}\right) -\rho _{\af_{\perp }}-\pi _{ \hfb }\rho=\\
+v\left( \pi _{ \widetilde{%
+\afb} }u(\mu +\rho )
+- \mathcal{D}_{\afb} - \pi _{ \afb }\rho-\pi _{ \hfb }\rho
++\rho _{\afb}\right) -\rho _{\afb}=\\
+=v\left( \pi _{ \widetilde{%
+\afb} }\left[ u(\mu +\rho )-\rho\right]
+- \mathcal{D}_{\afb}
++\rho _{\afb}\right) -\rho _{\afb}.
+\end{array}
+\end{equation*}
+These expressions provide a kind of a factorization in the anomalous element $\Psi^{\mu
+}$ and we find in it the combination of
+anomalous elements $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ of the
+subalgebra $\widetilde{\af_{\perp }}$-modules $L_{\widetilde{\af%
+_{\perp }}}^{\eta }$:
+\begin{equation*}
+\begin{array}{l}
+\Psi^{\mu }=\sum_{u\in U}\sum_{v\in W_{\af_{\perp }}}
+\epsilon (v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]
++\mathcal{D}_{\af_{\perp }}}\sum_{v\in W_{\af_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{ \widetilde{\af_{\perp }} }\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}+\rho _{\af%
+_{\perp }}\right) -\rho _{\af_{\perp }}}= \\
+=\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af }\left[ u(\mu
++\rho )-\rho \right] +\mathcal{D}_{\af_{\perp }}}\Psi _{\widetilde{%
+\af_{\perp }}}^{\pi _{ \widetilde{\af_{\perp }} }%
+\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp }}}
+\end{array}
+\end{equation*}
+
+Dividing both sides by the Weyl element $R_{\af_{\perp }}=\prod_{\beta
+\in \Delta _{\af_{\perp }}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}$ and
+projecting them to the weight space $h_{\af}^{\ast }$\ we obtain the
+desired relation:
+\begin{eqnarray*}
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+&=&\sum_{u\in W/W_{\af_{\perp }}}\;\epsilon (u)e^{\pi _{\frak{a%
+}}\left[ u(\mu +\rho )-\rho \right] }\pi _{%
+\af}\left( \frac{\Psi _{\widetilde{\af_{\perp }}}^{\pi _{
+\widetilde{\af_{\perp }} }\left[ u(\mu +\rho )-\rho \right] -%
+\mathcal{D}_{\af_{\perp }}}}{\prod_{\beta \in \Delta _{\af_{\perp
+}}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}}\right)  \\
+&=&\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af%
+_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
+e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] }.
+\end{eqnarray*}
+\end{proof}
+
+\begin{remark}
+This relation can be considered a generalized form of the Weyl formula for singular
+element $\Psi _{\frak{g}}^{\mu }$ : the vectors $\mu _{\af}\left(
+u\right) $ play the role of singular weights while instead of the determinants $%
+\epsilon (u)$ we have the products $\epsilon (u)\mathrm{\dim }\left( L_{%
+\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left(
+u\right) }\right) .$ In fact when $\frak{a=g}$ both $\af_{\perp }$ and $%
+\frak{h}_{\perp }$ are trivial, $U=W$ , and\ the original Weyl formula is
+easily reobtained.
+\end{remark}
+
+\subsubsection{Constructing recurrent relations.}
+\label{subsec:Construct-recurrent-rel}
+
+Consider the right-hand side of relation (\ref{eq:4}).
+The numerator there describes the branching in terms of singular elements and
+it is reasonable to expand it as an element of $\mathcal{E}\left( \frak{g} \right)$:
+\begin{equation}
+  \label{eq:21}
+  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
+        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\af}}k_{\lambda
+  }^{\left( \mu \right) }e^{\lambda }.
+\end{equation}
+Here the coefficients $k_{\lambda}^{\left( \mu \right) }$ are integer and their signs
+depend on the length (see \cite{humphreys1997introduction})  of the Weyl group elements in
+$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }$. The important property of
+$k_{\lambda}^{\left( \mu \right) }$'s is that they coincide with the branching coefficients
+for all weights $\nu$ inside the main Weil chamber:
+\begin{equation}
+%  \label{eq:20}
+  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}.
+\label{eq:21-1}
+\end{equation}
+We call the coefficients $k_{\lambda}$ --- the anomalous branching coefficients
+(see also \cite{ilyin812pbc}).
+
+Now we can state the main theorem which gives us an instrument for the
+recurrent computation of branching coefficients.
+
+\begin{theorem}
+  For the anomalous branching coefficients $k^{(\mu)}_{\nu}$ (\ref{eq:21})
+  the following relation holds
+  \begin{equation}
+    \label{recurrent-relation}
+    \begin{array}{c}
+      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+        \sum_{u\in U} \epsilon(u)\;
+        \dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
+        _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
+        \delta_{\xi-\gamma_0,\pi_{\af}(u(\mu+\rho)-\rho)}+ \right.\\
+      \left.
+        +\sum_{\gamma \in
+          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+          +\gamma }^{\left( \mu \right) }\right).
+    \end{array}
+  \end{equation}
+\end{theorem}
+\begin{proof}
+Redress relation (\ref{eq:4}) for the element $
+\frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using definition (\ref{eq:37})
+for the carrier $\Phi _{\af\subset \frak{g}}$ ,
+\begin{equation*}
+\begin{array}{l}
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+=\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
+\right) = \\[2mm]
+=\prod\limits_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left(
+1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{%
+\af}(\pi _{\af}\alpha )}\left( \sum\limits_{\nu \in P_{\af%
+}^{+}}b_{\nu }^{(\mu )}\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w(\nu
++\rho _{\af})-\rho _{\af}}\right) = \\[5mm]
+=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
+)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
+}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
+}}\right)  \\
+=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
+)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
+}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
+}}\right) .
+\end{array}
+\end{equation*}
+
+Then expand the sum in brackets (with respect to the formal basis in $\mathcal{E}$%
+):
+\begin{equation*}
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
+)e^{-\gamma }\sum_{\lambda \in P_{\af}}k_{\nu }^{(\mu )}e^{\lambda
+}=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
+\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
+\end{equation*}
+Substitute the expression obtained in Lemma \ref{lemma} (in the left-hand side),
+\begin{eqnarray*}
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left( \mu _{\frak{a%
+}}\left( u\right) \right) }\dim \left( L_{\widetilde{\af_{\perp }}%
+}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
+\label{anom modules 2} \\
+&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho %
+\right] }\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{%
+\af_{\perp }}}\left( u\right) }\right)  \\
+&=&-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
+\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
+\end{eqnarray*}
+The immediate consequence of this equality is:
+\begin{equation}
+\sum_{u\in U}\epsilon (u)\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
+_{\widetilde{\af_{\perp }}}\left( u\right) }\right) \delta _{\xi ,\pi _{%
+\af}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\af%
+\subset \frak{g}}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
+\af}.  \label{eq:17}
+\end{equation}
+The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
+for $\gamma \in \Phi _{\af\subset \frak{g}}$ are not independent, they
+are subject to linear relations and the form of these relations changes
+when the tested weight $\xi $ coincides with one of \ the ''singular
+weights''  $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in
+U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
+}\subset \frak{g}}$ and pass to a summation over the vectors of the
+injection fan $\Gamma _{\af\rightarrow \frak{g}}$ (see Definition \ref
+{fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
+\end{proof}
+
+\subsubsection{Embeddings and orthogonal pairs in simple Lie algebras}
+\label{sect-embeddings}
+
+In this subsection we discuss some properties of ''orthogonal pairs'' of
+subalgebras in simple Lie algebras of classical series.
+
+When both $\frak{g}$ and $\af$ are finite-dimensional all regular
+embeddings can be obtained by a successive elimination of nodes in the
+extended Dynkin diagram of $\frak{g}$ (and $\Delta_{\afb }^{+}=\emptyset $
+if $\af$ is maximal). For the classical series $A$, $C$ and $D$ when
+the regular injection $\af\rightarrow \frak{g}$ is thus fixed, the
+Dynkin diagram for $\af_{\bot }$ is obtained from the extended diagram
+of $\frak{g}$ by eliminating the subdiagram of $\af$ and the adjacent
+nodes:
+\begin{table}[tbh]
+\label{tab:diagrams} \noindent \centering{\
+\begin{tabular}{|l|l|l|l|}
+\hline
+$\frak{g}$ & Extended diagram of $\frak{g}$ & Diagrams of the subalgebras $%
+\af,\; \afb$ &  \\ \hline
+$A_n$ & \includegraphics{table1_1(l)} & \includegraphics{table1_1(r)}
+&  \\ \hline
+$C_n$ & \includegraphics{table1_3(l)} & \includegraphics{table1_3(r)}
+&  \\ \hline
+$D_n$ & \includegraphics{table1_4(l)} & \includegraphics{table1_4(r)}
+&  \\ \hline
+\end{tabular}
+}
+\caption{Subalgebras $\af,\;\af_{\bot }$ for the classical series}
+\end{table}
+
+In the case of $B$ series the situation is different. The reason is that
+here the subalgebra $\af_{\bot }$ may be larger than the one obtained
+by elimination of the subdiagram of $\af$ and the adjacent nodes. The
+subalgebras of the orthogonal pair,$\ \af$ and $\af_{\bot }$, must
+not form a direct sum in $\frak{g}$ . It can be directly
+checked that when $\frak{g}=B_{r}$ and $\af=B_{r_{\af}}$ the
+orthogonal subalgebra is $\af_{\bot }=B_{r-r_{\af}}$. Consider the
+injection $B_{r_{\af}}\rightarrow B_{r},\quad 1<r_{\af}<r$. By
+eliminating the simple root $\alpha _{r_{\af}-1}=e_{r_{\af%
+}-1}-e_{r_{\af}}$ one splits the extended Dynkin diagram of $B_{r}$
+into the disjoint diagrams for $\af=B_{r_{\af}}$ and $D_{r-r_{%
+\af}}$. But the system $\Delta _{\af_{\perp }}$ contains not only
+the simple roots $\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots ,e_{r_{\af%
+}-2}-e_{r_{\af}-1},e_{1}+e_{2}\right\} $ but also the root $e_{r_{\frak{%
+a}}-1}$. Thus $\Delta _{\af_{\perp }}$ forms the subsystem of the type $%
+B_{r-r_{\af}}$ and the orthogonal pair for the injection $B_{r_{\af%
+}}\rightarrow B_{r}$ is $\left( B_{r_{\af}},B_{r-r_{\af}}\right) $%
+. In the next Section a particular case of such orthogonal pair is
+presented for the injection $B_{2}\rightarrow B_{4}$ (see Figure \ref
+{fig:dynkin}).
+
+The complete classification of regular subalgebras for affine Lie algebras
+can be found in the recent paper \cite{1751-8121-41-36-365204}. From the complete
+classification of maximal special subalgebras in classical Lie algebras \cite
+{dynkin1952semisimple} we can deduce the following list of pairs of
+orthogonal subalgebras $\af,\;\af_{\bot }$:
+\begin{equation*}
+\begin{array}{lll}
+su(p)\oplus su(q) & \subset su(pq) &  \\
+so(p)\oplus so(q) & \subset so(pq) &  \\
+sp(2p)\oplus sp(2q) & \subset so(4pq) &  \\
+sp(2p)\oplus so(q) & \subset sp(2pq) &  \\
+so(p)\oplus so(q) & \subset so(p+q) & \mathrm{{for}\;p\;{and}\;q\;{odd}.}
+\end{array}
+\end{equation*}
+
+\subsubsection{Algorithm for recursive computation of branching coefficients}
+
+\label{sec:algorithm}
+
+The recurrent relation (\ref{recurrent-relation}) allows us to formulate an
+algorithm for recursive computation of branching coefficients. In this
+algorithm there is no need to construct the module $L^{(\mu)}_{\frak{g}}$ or
+any of the modules $L^{(\nu)}_{\af}$.
+
+It contains the following steps:
+
+\begin{enumerate}
+\item  Construct the root system $\Delta _{\af}$ for the embedding $%
+\af\rightarrow \frak{g}$.
+
+\item  Select all positive roots $\alpha \in \Delta ^{+}$ orthogonal
+to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
+
+\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. Relation
+ (\ref{eq:6}) defines the sign function
+ $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
+ $\gamma_0$ is to be subtracted to get the fan (\ref{fan-defined}):
+ $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}$.
+
+\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
+)-\rho ;\;w \in W\right\} $ of singular weights for the $\frak{g}$%
+-module $L^{(\mu )}$.
+
+\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
+}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
+)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
+\af_{\perp }}}}\right\} $. Since the set $\Delta_{\afb }^{+}$ is fixed
+we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
+}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
+\af_{\perp }}}}$ (by computing its scalar product with the fundamental
+weights of $\afb^{+}$).
+
+\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
+calculate dimensions of the corresponding modules, $\mathrm{\dim }\left(
+L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
+}\left( u\right) }\right) $, using the Weyl dimension formula and construct
+the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
+
+\item  Calculate the anomalous branching coefficients using the
+recurrent relation (\ref{recurrent-relation}) and select among them those
+corresponding to the weights in the main Weyl
+chamber $\overline{C_{\af}}$.
+\end{enumerate}
+
+We can speed up the algorithm by
+one-time computation of the representatives of the conjugate classes $%
+W/W_{\afb }$.
+
+The next section contains examples illustrating the application of this
+algorithm.
+
+\subsection{Branching for finite dimensional Lie algebras}
+\label{sec:finite-dimens-lie}
+
+\subsubsection{Regular embedding of $A_1$ into $B_2$}
+\label{sec:regul-embedd-a_1}
+
+Consider the regular embedding $A_1\to B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$
+are presented as dashed vectors in Figure \ref{fig:B2_A1}. We denote the corresponding
+Weyl reflections by $w_1, w_2$. The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is
+grey.
+
+\begin{figure}[p]
+  \noindent\centering{
+    \includegraphics[width=80mm]{figure1}
+  }
+  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$
+  are presented as dashed vectors.
+  The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is grey.
+  The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is black.
+  The weights of the singular element $\Psi^{(\omega_1)}$ are marked by circles with
+  superscripts indicating the corresponding determinants $\epsilon(w)$.}
+  \label{fig:B2_A1}
+
+%\end{figure}
+%\begin{figure}[pb]
+  \noindent\centering{
+    \includegraphics[width=80mm]{figure2}
+  }
+  \caption{Here in addition to the diagram presented above (Figure(\ref{fig:B2_A1}))
+  the weights of $\left( \afb=A_1 \right)$-modules $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$
+  originating in the points $\pi _{\af}\left[ u(\mu +\rho )-\rho \right] $
+are shown by dotted lines.
+    The superscripts over the highest weights  $\mu_{\af_{\perp }}\left( u\right)$
+    are now the products $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.
+    Coordinates along the root $\beta$ are counted in terms of the fundamental weight of $\af$. }
+\label{fig:B2_A1_2}
+\end{figure}
+
+Let's perform the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$
+($\omega_1$ -- the black vector in Figure \ref{fig:B2_A1}) according to the steps of the algorithm.
+The root $\alpha_1$ is orthogonal to $\beta$,
+so we have $\Delta_{\afb}^+ = \left\{ \alpha_1 \right\}$ (step (ii)).
+According to Definition \ref{fan-definition}
+the fan $\Gamma_{A_1\to B_2}$ (step (iii)) consists of two weights:
+\begin{equation*}
+  \label{eq:22}
+  \Gamma_{A_1\to B_2}=\left\{ (1;2),\; (2;-1) \right\},
+\end{equation*}
+where the second component is the value of the sign function $s(\gamma)$.
+Singular weights  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$ (step (iv))
+are indicated by circles with the superscript $\epsilon\left( w \right)$.
+The space $U$ is the factor $W/W_{\afb}$ where $W_{\afb}=\left\{e,w_1\right\}$.
+This means that singular weights located above the $\beta$-line
+belong to the Weyl chamber $\overline{C_{\widetilde{\af_{\perp }}}}$.
+According to formula (\ref{defect-perp}) we have $\mathcal{D}_{\af_{\perp }}=0$ and
+$\hf_{\perp }=0$, thus $\left\{ \mu _{\af_{\perp }}\left( w\right)
+=\pi _{\af_{\perp }}\left[ w(\mu +\rho)-\rho \right]\right\}$.
+We obtain four highest weights for $\af_{\perp }$-modules. In terms of
+$\af_{\perp }$-fundamental weight $\frac{1}{2} \alpha_1$ these highest weights
+$\left\{ \mu _{\af_{\perp }}\left( u\right)
+=\pi _{\af_{\perp }}\left[ u(\mu +\rho)-\rho \right]| u \in U \right\}$
+ are
+$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$ (step v).
+In Figure (\ref{fig:B2_A1_2}) the corresponding weight diagrams
+$\left\{ \mathcal{N}_{\af_{\perp }}^{\mu _{\af_{\perp }}\left( u\right) }\right\} $
+are attached to the set of $\af$-weights
+$\left\{ \mu _{\af}\left( u\right)\right\} =\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]\right\}
+=\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$.
+In fact we do not need the
+weight diagrams but only the dimensions of modules
+$L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ multiplied by
+$\epsilon \left( u\right) $ (step vi). Obtained values are to be attributed to the points
+$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$
+in $P_{\af}$. The singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
+has the set of weights with anomalous multiplicities:
+\begin{equation}
+  \label{eq:25}
+  \left\{(1;2),\; (0;-3),\; (-4;3),\; (-5;-2)\right\}.
+\end{equation}
+
+Applying formula (\ref{recurrent-relation}) with the fan
+$\Gamma_{A_1\to B_2}$ to the set (\ref{eq:25}) (step vii)
+we get zeros for the weights
+greater than the highest anomalous vector $(1;2)$
+and $k^{(1,0)}_1=2$ for the vector $(1;2)$ itself.
+For the anomalous weight (0;-3) on the boundary of $\bar{C}^{(0)}_{\af}$ the recurrent relation gives
+\begin{equation*}
+  \label{eq:23}
+  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1,
+\end{equation*}
+the branching is completed: $L_{B_2\downarrow A_1}^{\omega_1}=
+2L_{A_1}^{\omega_{\left(A_1\right)} }
+\bigoplus
+L_{A_1}^{2\omega_{\left(A_1\right)} }$.
+
+\subsubsection{Embedding $B_2$ into $B_4$}
+\label{sec:someth-high-dimens}
+Consider the regular embedding $B_2 \rightarrow B_4$.
+The corresponding Dynkin diagrams are presented in the Figure \ref{fig:dynkin}.
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=100mm]{figure3}
+  \caption{The regular embedding $B_2 \rightarrow B_4$ described by dropping the node from the Dynkin diagram.
+  Remember that here $\afb$ is equal to $B_2$ while the diagram
+  shows only $A_1\oplus A_1$ (see Subsection \ref{sect-embeddings}).}
+  \label{fig:dynkin}
+\end{figure}
+
+\begin{figure}[pt]
+  \centering
+    \includegraphics[width=100mm,height=90mm]{figure4}
+  \caption{The singular element $e^{\gamma_0}\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
+  displayed in the weight subspace $P_{\af}$ for $\af=B_2$ with the basis $\left\{e_3,e_4\right\}$.
+  We see the projected singular weights $\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] +\gamma_0 | u \in U \right\}$
+  shifted by $\gamma_0$ and supplied by multipliers
+  $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.}
+  \label{fig:B4B2anom}
+
+%\end{figure}
+%
+%\begin{figure}[pb]
+  \centering
+  \includegraphics[height=80mm]{figure5}
+  \caption{The fan $\Gamma$ for $B_2\rightarrow B_4$ with values of $s(\gamma+\gamma_0)$ attributed to each $\gamma \in \Gamma$.}
+  \label{fig:B4B2Fan}
+\end{figure}
+
+In the orthonormal basis $\left\{e_1,\dots,e_4\right\}$ simple roots and positive roots of $B_4$ are
+\begin{eqnarray*}
+  \label{eq:19}
+  S_{B_4}= \{e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4\},\\[2mm]
+ \Delta^+_{B_4}=\left\{ (e_1 - e_2,\; e_2 - e_3,\; e_3 - e_4,\; e_4,\; e_1 - e_3,\; e_2 - e_4,\; e_3 + e_4,\; e_3,\; e_1 - e_4,\;\right.\\
+ \left. e_2 + e_4,\; e_2,\; e_1 + e_4,\; e_2 + e_3,\; e_1,\; e_1 + e_3,\; e_1 + e_2\right\}
+\end{eqnarray*}
+The subalgebra $\af=B_2$ is fixed by the simple roots
+\begin{equation*}
+  \label{eq:26}
+ S_{B_2}=\{e_3-e_4,e_4\}.
+\end{equation*}
+Its orthogonal counterpart $\afb=B_2$ has
+\begin{eqnarray*}
+  \label{eq:27}
+  S_{\afb}=\{e_1-e_2,e_2\},\\
+ \Delta^{+}_{\afb}= \left\{e_1-e_2,e_1+e_2,e_1,e_2\right\}.
+\end{eqnarray*}
+As far as the set $\Delta^+_{B_4} \setminus  \Delta^{+}_{\afb}$ is fixed the injection
+fan $\Gamma_{B_2 \to B_4}$ can be constructed using Definition \ref{fan-definition}.
+As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need only the factor
+ $s\left(\gamma + \gamma_0\right)$.
+The result is presented in Figure \ref{fig:B4B2Fan}.
+
+Consider the $B_4$-module $L^{\mu}$ with the highest weight $\mu=2e_1 + 2 e_2 + e_3 + e_4$; \,
+$\mathrm{dim}(L^{\left[0,1,0,2\right]})=2772$.
+Here the defect is nontrivial, $\mathcal{D}_{\af_{\perp }}=-2\left( e_1 + e_2 \right)$,
+while $\hf_{\bot}=0$. Among the singular weights there are
+48 vectors with the property $\left\{ \mu _{\af_{\perp }%
+}\left( u\right) =\pi _{\af_{\perp }}\left[ u(\mu +\rho
+)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\af_{\perp }}}\right\} $.
+The set $U=\left\{ u \right\}$ is thus fixed.
+Compute the dimensions of the corresponding $\afb$-modules with the highest weights
+$ \mu _{\af_{\perp }}\left( u\right)$ (using the Weyl dimension formula) and multiply them
+by $\epsilon\left( u \right)$. The result is the singular element
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ shown in Figure \ref{fig:B4B2anom}.
+
+Now one can place the fan $\Gamma$ (see Figure \ref{fig:B4B2Fan}) in the highest of the weights
+presented in Figure \ref{fig:B4B2anom} and start the recursive determination of the branching coefficients
+(using relation (\ref{recurrent-relation})):
+\begin{eqnarray*}
+  \label{eq:24}
+  \pi_{\af} \left(ch L^{\left[0,1,0,2\right]}_{B_4}\right) = 6 \; ch L^{\left[0,0\right]}_{B_2}+ 60
+  \; ch L_{B_2}^{\left[0,2\right]}+ 30 \; ch L_{B_2}^{\left[1,0\right]}+ 19 \; ch L_{B_2}^{\left[2,0\right]}+\\
+  40 \; ch L_{B_2}^{\left[1,2\right]}+ 10 \; ch L_{B_2}^{\left[0,4\right]}.
+\end{eqnarray*}
+%\newpage
+\subsection{Applications to conformal field theory}
+\label{sec:phys-appl}
+
+\subsubsection{Conformal embeddings}
+\label{sec:conformal-embeddings}
+
+Branching coefficients for an embedding of affine Lie algebra into
+affine Lie algebra can be used to construct modular invariant
+partition functions for Wess-Zumino-Novikov-Witten models in conformal field theory
+(\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
+In these models current algebras are affine Lie algebras.
+
+The modular invariant partition function is crucial for the conformal theory to be valid
+on the torus and higher genus Riemann surfaces. It is important for the applications of
+CFT to string theory and to critical phenomena description.
+
+The simplest modular-invariant partition function has the diagonal form:
+\begin{equation}
+  \label{eq:34}
+   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
+\end{equation}
+Here the sum is over the set of highest weights for integrable modules in a WZW-model
+and $\chi_{\mu}(\tau)$ are the normalized characters (see \cite{difrancesco1997cft}) of these modules.
+
+To construct nondiagonal modular invariants is not an easy problem,
+although for some models the complete classification of modular invariants is known \cite{1994hepthGannon,1995JMPGannon}.
+
+Consider the Wess-Zumino-Witten model with the affine Lie algebra $\af$.
+Nondiagonal modular invariants for this model can be constructed from the diagonal
+invariant if there exists an affine algebra $\mathfrak{g}$ such that $\af\subset\mathfrak{g}$.
+Then we can replace the characters of the $\mathfrak{g}$-modules in the diagonal
+modular invariant partition function (\ref{eq:34})
+by the decompositions
+\begin{equation*}
+  \label{eq:32}
+\sum_{\nu \in P^{+}_{\af}}b^{(\mu)}_{\nu} \chi_{\nu}
+\end{equation*}
+containing normalized characters $\chi_{\nu}$ of the corresponding $\af$-modules.
+Thus we obtain a nondiagonal modular-invariant  partition function for the theory with
+the current algebra $\af$,
+\begin{equation}
+  \label{eq:36}
+   Z_{\af}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\af}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau).
+\end{equation}
+
+The effective reduction procedure is crucial for this construction.
+The embedding is required to preserve the conformal invariance.
+Let $X^{\alpha_j}_{-n_j}$ and $\tilde{X}^{\alpha'_j}_{-n_j}$ be the lowering generators for
+$\mathfrak{g}$ and for $\af\subset\mathfrak{g}$ correspondingly.
+Let $\pi_{\af}$ be the projection operator of
+$\pi_{\af}:\mathfrak{g}\longrightarrow \af$.
+In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$
+the states can be described as
+\begin{equation*}
+  \label{eq:109}
+  X^{\alpha_1}_{-n_1}X^{\alpha_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+\end{equation*}
+And for the sub-algebra $\af$ the corresponding states are
+\begin{equation*}
+  \label{eq:110}
+  \tilde{X}^{\alpha'_1}_{-n_1}\tilde{X}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\af}(\lambda)\right>.
+\end{equation*}
+The $\mathfrak{g}$-invariance of the vacuum entails its $\af$-invariance,
+but this is not the case for the energy-momentum tensor. So the energy-momentum tensor of the larger theory
+should contain only the generators $\tilde{X}$. Then the relation
+\begin{equation}
+  \label{eq:2}
+  T_{\mathfrak{g}}(z)=T_{\af}(z)
+\end{equation}
+leads to the equality of central charges
+\begin{equation*}
+  \label{eq:33}
+  c(\mathfrak{g})=c(\af)
+\end{equation*}
+and to the relation
+\begin{equation}
+  \label{eq:111}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\af}{x_ek+a}.
+\end{equation}
+Here $x_e$ is the so called "embedding index":
+$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$
+with $\Theta$, $\Theta_{\mathfrak{a}}$ being the highest roots of
+$\mathfrak{g}$ and $\mathfrak{a}$
+while $g$  and $a$ are the  corresponding dual Coxeter numbers.
+
+It can be demonstrated that solutions of equation (\ref{eq:111}) exist only
+for the level $k=1$ \cite{difrancesco1997cft}.
+
+The complete classification of conformal embeddings is given in \cite{schellekens1986conformal}.
+
+The relation (\ref{eq:111}) and the asymptotics of the branching functions can be used
+to prove the finite reducibility theorem \cite{kac1988modular}.
+It states that for a conformal embedding  $\af\longrightarrow\mathfrak{g}$
+only finite number of branching coefficients have nonzero values.
+
+\begin{mynote} The orthogonal subalgebra $\afb$ is always trivial
+for conformal embeddings $\af\longrightarrow \mathfrak{g}$.
+\begin{proof}
+Consider the modes expansion of the energy-momentum tensor
+\begin{equation*}
+\label{eq:47}
+  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n.
+\end{equation*}
+The modes $L_n$ are constructed as combinations of normally-ordered products of $\gf$-algebra generators,
+\begin{equation*}
+\label{eq:48}
+  L_n=\frac{1}{2(k+h^v)}\sum_{\alpha}\sum_m:X^{\alpha}_m X^{\alpha}_{n-m}: \; .
+\end{equation*}
+In case of a conformal embedding energy-momentum tensors $T_{\mathfrak{g}}(z)$ and $T_{\af}(z)$ are
+equal (see (\ref{eq:2})).
+
+In these combinations we are to substitute  $\af$-generators in terms of $\mathfrak{g}$-generators
+and obtain the energy-momentum tensor $T_{\mathfrak{g}}$.
+But if the set of generators attributed to $\Delta_{\afb}$ is not empty this is not possible,
+since $T_{\mathfrak{g}}$ contains generators $X^{\alpha}_n$ for $\alpha\in \Delta_{\afb}$.
+\end{proof}
+\end{mynote}
+
+\subsubsection{Special embedding $\hat{A}_1\rightarrow\hat{A}_2$.}
+\label{sec:spec-embedd-hata_1s}
+
+Consider the case where both $\gf$ and $\af$ are affine Lie algebras:
+$\hat{A}_1 \rightarrow \hat{A}_2$ and the injection is the affine extension of the
+special injection $A_1 \rightarrow A_2$ with the embedding index $x_e=4$.
+As far as $\gf$-modules to be considered are of level one,
+the necessary $\af$-modules will be of level $\tilde{k}=kx_e=4$.
+
+There exist three level one fundamental weights of $\hat{A}_2$.
+It is easy to see that the set $\Delta_{ \afb }$ is empty and the subalgebra $\afb=0$.
+Then ${\cal D}_{\afb}=0$, $\hf_{\perp}$ is one-dimensional abelian subalgebra and
+the dimension of $\tilde\afb=\afb\oplus \hf_{\perp}$ is also 1.
+It is convenient to choose the classical root for $\hat{A}_1$ to be
+$\beta=\frac{1}{2}(\alpha_1+\alpha_2)$.
+
+Using Definition (\ref{fan-definition})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$.
+In this case $\gamma_0 =0$ and its sign $s\left( 0 \right)=-1$ thus we are to use the
+sign function $s(\gamma)$ (see Figure \ref{fig:AffineA2A1Fan}).
+
+\begin{figure}[h!bt]
+  \centering
+  \includegraphics[width=125mm]{figure6}
+
+  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ for $\hat{A_1}\rightarrow \hat{A_2}$
+  in the basis $\left\{\beta,\delta \right\}$. Notice that $\gamma_0 =0$, so values of $s(\gamma)$
+  are prescribed to the weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$}
+  \label{fig:AffineA2A1Fan}
+\end{figure}
+
+Consider the module $L^{\omega_0=(0,0;1;0)}$. Here we use the (finite part; level; grade)
+presentation of the highest weight and the finite part
+coordinates are the Dynkin indices (see section(\ref{sec:notation})).
+
+The set $\widehat{\Psi^{(\omega_0)}}$  is displayed in Figure
+\ref{fig:affine_A2_anom_point} up to the sixth grade.
+
+\begin{figure}[h!tb]
+  \hspace*{-1.5cm}
+  \includegraphics[width=180mm]{figure7}
+  \caption{Singular weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$.
+   The classical (grade zero) cross-section of the diagram is shown separately
+   in the right part of the figure.
+  We use the orthogonal basis with the unit vector equal to $\alpha_1$.
+  The weights $w (\omega_0+\rho)-\rho$ are marked by crosses when $\epsilon(w)=1$ and
+by box when $\epsilon(w)=-1$. Simple roots of the classical subalgebra $A_2$ are
+grey and the grey diagonal plane corresponds to the Cartan subalgebra of
+the embedded algebra $\hat{A}_1$.}
+  \label{fig:affine_A2_anom_point}
+\end{figure}
+
+The next step is  to project the anomalous weights to $P_{\hat A_1}$.
+The result is the element $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
+presented in Figure \ref{fig:AffineA2_A1_anom_proj} up to the twelfth grade.
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=130mm]{figure8}
+  \caption{The singular element $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
+  displayed in $P_{\hat A_1}$
+  with the basis $\left\{\beta,\delta \right\}$.}
+  \label{fig:AffineA2_A1_anom_proj}
+\end{figure}
+
+Using the recurrent relation (\ref{recurrent-relation}) with the fan
+$\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ and the singular weights in
+$\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
+we get the anomalous branching coefficients presented
+in Figure \ref{fig:AffineA2_A1_branching}.
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=130mm]{figure9}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$. The boundaries
+  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
+ are indicated by black lines. Two anomalous highest weights located
+ in the main Weyl chamber are marked by stars.
+ Both have multiplicity 1, so the branching coefficients for them are equal 1.}
+  \label{fig:AffineA2_A1_branching}
+\end{figure}
+Inside the Weyl chamber $\bar{C}_{\hat{A}_1}$
+(its boundaries are indicated in Figure \ref{fig:AffineA2_A1_branching})
+there are only two nonzero anomalous weights and both have multiplicity 1.
+These are the highest weights of $\af$-submodules and the multiplicities are their branching
+coefficients. Thus we get the decomposition
+\begin{equation*}
+  \label{eq:43}
+  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
+\end{equation*}
+Notice that the finite reducibility theorem holds.
+
+The same fan $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ can be used for any other highest weight
+module $L^{\mu}_{\hat{A_2}}$. In particular for irreducible modules of level one  we get the trivial
+branching:
+\begin{equation*}
+  \label{eq:44}
+   L^{(1,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)},\\
+   L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
+\end{equation*}
+
+Using these results the modular-invariant partition function is easily found,
+\begin{equation*}
+  \label{eq:45}
+  Z=\left|\chi_{(4;4;0)}+\chi_{(0;4;0)}\right|^2+2\chi_{(2;4;0)}^2.
+\end{equation*}
+
+\subsubsection{Coset models}
+\label{sec:coset-models}
+
+Coset models \cite{Goddard198588} tightly connected with the gauged WZW-models are actively studied
+in string theory, especially in string models on anti-de-Sitter space
+\cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}.
+The characters in coset models are proportional to branching functions,
+\begin{equation}
+  \label{eq:31}
+  \chi^{(\mu)}_{\nu}(\tau)=e^{2\pi i \tau (m_{\mu}-m_{\nu})} b^{(\mu)}_{\nu}(\tau),
+\end{equation}
+with
+\begin{equation*}
+  \label{eq:46}
+  m_{\mu}=\frac{\left|\mu+\rho\right|^2}{2(k+g)}-\frac{\left|\rho\right|^2}{2g}.
+\end{equation*}
+The problem of branching functions construction in the coset models was considered
+in  \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.
+
+Let us return to our example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
+$A_1 \rightarrow B_2$.
+Since this embedding is regular and $x_e=1$, the subalgebra modules and the initial module are of the same level.
+The set  of positive roots with zero projection
+on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case:
+$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$ and $\afb=A_1$. It is easy to see that here $\hf_{\perp}$
+is trivial and ${\cal D}_{\afb}=0$.
+
+Using Definition (\ref{fan-definition}) we obtain the fan
+$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
+Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=-1$.
+Values of the sign function $s(\gamma)$ for
+$ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ are presented in Figure \ref{fig:AffineB2A1Fan}.
+We restricted the computation to the twelfth grade.
+\begin{figure}[h!bt]
+  \centering
+  \includegraphics[width=135mm]{figure10}
+  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$
+  for $\hat{A_1}\rightarrow \hat{B_2}$ in the basis $\left\{\beta,\delta \right\}$. Values of  $s(\gamma)$ are shown for the
+  weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$}
+  \label{fig:AffineB2A1Fan}
+\end{figure}
+
+Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $\omega_1=(1,0;1;0)$,
+where the finite part coordinates are in the orthogonal basis $e_1,e_2$.
+The set of anomalous weights for this module up to the sixth grade is presented in Figure \ref{fig:affine_B2_anom_point}.
+
+\begin{figure}[h!tb]
+%  \hspace*{-2cm}
+  \includegraphics[width=140mm]{figure11}
+  \caption{Singular weights for $L^{(1,0;1;0)}_{\hat B_2 }$. The standard basis $\{e_1,e_2\}$ is used for the classical cross-section.
+  The weights in the zero grade are the same as in Figure \ref{fig:B2_A1}.
+  The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by boxes for $\epsilon(w)=-1$.
+Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
+of the embedded algebra $\hat{A}_1$.}
+  \label{fig:affine_B2_anom_point}
+\end{figure}
+
+According to the recursive algorithm \ref{sec:algorithm} we project these anomalous weights to
+$P_{\hat{A_1}}$ and find the dimensions of the corresponding
+$\afb$-modules $L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$.
+In the grade zero this projection gives exactly the set
+$\Psi ^{\left( \mu \right) }_{\left(  A_1, A_1 \right)}$ for the embedding of
+the classical Lie algebra $A_1\rightarrow B_2$. To see this compare Figure \ref{fig:B2_A1}
+with Figure \ref{fig:AffineB2_A1_anom_proj}
+where the singular element $\Psi ^{\left( \mu \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
+for the affine embedding $\hat{A_1}$ is presented up to the twelfth grade.
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=120mm]{figure12}
+  \caption{Singular element $\Psi ^{\left( \omega_1 \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
+  in the basis $\{\beta,\delta\}$. Dimensions of the corresponding $\afb=A_1$-modules
+  with the signs $\epsilon(u)$ are indicated.}
+  \label{fig:AffineB2_A1_anom_proj}
+\end{figure}
+
+\begin{figure}[h!bt]
+  \centering
+  \includegraphics[width=120mm]{figure13}
+  \caption{Anomalous branching coefficients for $\hat{A_1}\rightarrow \hat{B_2}$. The basis $\{\beta,\delta\}$ is used.
+ Boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
+ are indicated by black lines. Anomalous branching coefficients
+ inside the main Weyl chamber are equal to branching coefficients of the embedding $\hat{A_1}\rightarrow \hat{B_2}$.}
+  \label{fig:AffineB2_A1_branching}
+\end{figure}
+
+Multiplicities of the highest weights inside the  Weyl chamber
+$\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
+define the following branching coefficients (up to the twelfth grade),
+\begin{eqnarray*}
+  \label{eq:28}
+  L^{\omega_1}_{\hat{B_2}\downarrow \hat{A_1}}
+  &=&2 L_{\hat{A_1}}^{\omega_1}\oplus 1 L_{\hat{A_1}}^{\omega_0}\oplus 4 L_{\hat{A_1}}^{\omega_0-\delta}\oplus\\
+    &&2 L_{\hat{A_1}}^{\omega_1-\delta}\oplus 8 L_{\hat{A_1}}^{\omega_0-2\delta}\oplus
+    8 L_{\hat{A_1}}^{\omega_1-2\delta}\oplus 15 L_{\hat{A_1}}^{\omega_0-3\delta}\oplus\\
+    &&12 L_{\hat{A_1}}^{\omega_1-3\delta}\oplus 26 L_{\hat{A_1}}^{\omega_1-4\delta}\oplus
+    29 L_{\hat{A_1}}^{\omega_0-4\delta}\oplus 51 L_{\hat{A_1}}^{\omega_0-5\delta}\oplus\\
+    &&42 L_{\hat{A_1}}^{\omega_1-5\delta}\oplus 78 L_{\hat{A_1}}^{\omega_1-6\delta}\oplus
+    85 L_{\hat{A_1}}^{\omega_0-6\delta}\oplus 120 L_{\hat{A_1}}^{\omega_1-7\delta}\oplus\\
+    &&139 L_{\hat{A_1}}^{\omega_0-7\delta}\oplus 202 L_{\hat{A_1}}^{\omega_1-8\delta}\oplus
+    222 L_{\hat{A_1}}^{\omega_0-8\delta}\oplus 306 L_{\hat{A_1}}^{\omega_1-9\delta}\oplus\\
+    &&346 L_{\hat{A_1}}^{\omega_0-9\delta}\oplus 530 L_{\hat{A_1}}^{\omega_0-10\delta}\oplus
+    482 L_{\hat{A_1}}^{\omega_1-10\delta}\oplus 714 L_{\hat{A_1}}^{\omega_1-11\delta}\oplus\\
+    &&797 L_{\hat{A_1}}^{\omega_0-11\delta}\oplus 1080 L_{\hat{A_1}}^{\omega_1-12\delta}\oplus
+    1180 L_{\hat{A_1}}^{\omega_0-12\delta}\oplus \dots
+\end{eqnarray*}
+This result can be presented as the set of branching functions:
+\begin{eqnarray*}
+  \label{eq:29}
+  \begin{array}{cc}
+    b^{(\omega_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
+     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
+  \end{array}\\
+  \begin{array}{cc}
+    b^{(\omega_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
+    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
+  \end{array}
+\end{eqnarray*}
+Here $q=\exp (2\pi i \tau)$ and the lower index enumerates the branching functions according
+to their highest weights in $P^+_{\hat{A_1}}$.
+These are the fundamental weights $\omega_0=\lambda_0=(0,1,0),\; \omega_1=\alpha/2=(1,1,0)$.
+
+Now we can return to (\ref{eq:31}),
+\begin{equation*}
+  \label{eq:35}
+  \begin{array}{cc}
+    \chi^{(\omega_1)}_{1}(q)= & q^{\frac{7}{12}}\left( 2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\right. \\
+    & \left. 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots \right),\\
+    \chi^{(\omega_1)}_{0}(q) = & q^{\frac{5}{6}}\left(1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\right. \\
+    &\left. 222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\right),
+  \end{array}
+\end{equation*}
+and finally obtain expansions for the $B_2/A_1$-coset characters.
+
+\subsection{Conclusion}
+\label{sec:conclusion}
+We have demonstrated that the injection fan technique can be used to deal with arbitrary
+reductive subalgebras (maximal as well as  nonmaximal).
+It was shown that the branching problem for $\af \subset \gf$  is tightly connected with
+the properties of the orthogonal partner $ \af_{\perp
+} $ of $\af$. The subalgebra $\afb$ corresponds to the subset
+$\Delta^{+}_{\afb}$ of positive roots in $\Delta_{\mathfrak{g}}^{+}$ that trivialize
+the Cartan subalgebra $\hf_{\afb}$.
+Both the injection fan and the sets of singular weights for
+highest weight $\gf$-modules depend substantially on the structure of $\afb$ and its submodules.
+For the fan $\Gamma_{\af\rightarrow \gf}$ this dependence is almost obvious:
+in the element $\Phi_{\af\rightarrow \gf}$ the factors corresponding to the roots
+of $\Delta^{+}_{\afb}$ are eliminated.
+The transformation in the set of projected singular weights is more interesting.
+We have found out that in the new singular element
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ the coefficients depend on
+the $\afb$-submodules (their highest weights $\mu _{\widetilde{\af_{\perp }}}\left( u\right)$
+are fixed by the injection and by the weights of the initial
+element $\Psi^{\mu}$).
+Fortunately no more information on $L^{\mu _{\widetilde{\af_{\perp }}}\left( u\right)}
+_{\left\{ \afb \right\}}$-submodules is necessary than their dimensions.
+In the new singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
+weight multiplicities are equal to dimensions
+$\dim\left(L^{\mu _{\widetilde{\af_{\perp }}}\left( u\right)}_{\left\{ \afb \right\}}\right)$
+of the corresponding $\afb$-modules
+multiplied by the values $\epsilon (u)$. As a result
+the highest weights of $\af$-submodules and their
+multiplicities are subject to the set of linear equations (\ref{eq:17}).
+These properties are valid for any reductive subalgebra $\af\rightarrow \gf$ and
+the set can be redressed to the form of recurrent relations to be solved step by step.
+
+The efficiency of the obtained algorithm was illustrated in various examples.
+In particular we considered the construction of modular-invariant partition functions
+in the framework of conformal embedding method and the coset construction in rational conformal field theory.
+This construction is useful in the study of WZW-models
+emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
+
+Further amelioration of the algorithm can be achieved by using
+the folded fan technique \cite{il2010folded}. It must be mentioned that even in the case
+of string functions the explicit solution of the corresponding recurrent relations is
+a difficult problem (see \cite{il2010folded} for details). Nevertheless we hope that by
+developing the procedure of folding one could get explicit solutions
+for at least some of branching functions and the corresponding coset characters.
 
@@
 
-\section{Введение}
+\subsection{Введение}
 
@@
 
-\section{Ортогональная подалгебра и сингулярные элементы}
+\subsection{Ортогональная подалгебра и сингулярные элементы}
 
@@
 
-\subsection{Ортогональная подалгебра}
+\subsubsection{Ортогональная подалгебра}
 
@@
 
-\subsection{Разложение сингулярного элемента.}
+\subsubsection{Разложение сингулярного элемента.}
 
@@
 
-\subsection{Фомулы Вейля-Верма.}
+\subsubsection{Фомулы Вейля-Верма.}
 
@@
   \noindent\centering{
-   \includegraphics[width=120mm]{B2_Gen_Verma_Decomp.pdf}
+   \includegraphics[width=120mm]{B2_Gen_Verma_Decomp}
   }
@@
 
-\section{БГГ резольвента и ветвление}
+\subsection{БГГ резольвента и ветвление}
 В работе \cite{lepowsky1977generalization} показано, что для модуля старшего веса $L^{\mu }$, где $\mu \in P^{+}$, последовательность (обобщенная БГГ резольвента)
@@
  \noindent\centering{
-   \includegraphics[width=140mm]{B2_Exact.pdf}}
+   \includegraphics[width=140mm]{B2_Exact}}
  \caption{Вложение $A_1\hookrightarrow B_2$ (см. Рисунок \ref{fig:B2_Verma_Decomp}). Ортогональный партнер, подалгебра $A_1$, соответствует корню $\alpha_1$.
@@
 
-\section{Заключение}
+\subsection{Заключение}
 
@@
 
+\section{Сплинты и ветвления}
+\label{sec:splints}
+
+%%\newtheorem{Def}{Definition}[section]
+%%\newtheorem{Cnj}[Def]{Conjecture}
+%%\newtheorem{Prop}[Def]{Property}
+%%\newtheorem{example}{Example}[section]
+%%
+%\input{tcilatex}
+
+\begin{abstract}
+Splint of root system for simple Lie algebra appears naturally in
+studies of (regular) embeddings of reductive subalgebras. Splint can
+be used to construct branching rules. We demonstrate that 
+splint properties implementation drastically simplify calculations of
+branching coefficients.
+\end{abstract}
+
+\section{Introduction}
+\label{sec:Introduction}
+
+Embedding $\phi$ of a root system $\Delta_1$ into a root system
+$\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
+subset of $\Delta$ that commutes with vector composition law in
+$\Delta_{1}$ and $\Delta$.
+\begin{equation*}
+\phi:\Delta_1 \longrightarrow \Delta
+\end{equation*}
+\begin{equation*}
+\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
+\,\,\, \alpha,\beta \in \Delta_1
+\end{equation*}
+
+Note that the image $Im(\phi)$ must not inherit the root system
+properties except the addition rules equivalent to the addition
+rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
+can splinter $\Delta$  when the latter can be presented 
+as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.   
+The term {\it splint} was
+introduced by D. Richter in  \cite{richter2008splints} where the
+classification of splints for simple Lie algebras was obtained.
+There was also mentioned that splint must have tight
+connections with the injection fan construction. The fan $\Gamma
+\subset \Delta$ was
+introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent
+properties of branching coefficients for maximal embeddings. Injection fan is an
+efficient tool to study branching rules. Later this construction
+was generalized to non-maximal embeddings and infinite-dimensional
+Lie algebras in \cite{2010arXiv1007.0318L, ilyin812pbc}.
+
+In the present paper we study connections between splint and
+injection fan for regular embedding of reductive subalgebras
+${\mathfrak a}$ in simple Lie algebra $\mathfrak{g}$. We show that (under
+certain conditions described in section \ref{sec:stems and
+multiplicity functions}) splint is a natural tool to study
+reduction properties of ${\mathfrak g}$-modules
+with respect to a subalgebra ${\mathfrak a}\longrightarrow
+{\mathfrak g}$. Using this tool we obtain the main result -- the one-to-one correspondence between weight
+multiplicities in irreducible modules of splint and branching
+coefficients for a reduced module $L^{\mu}_{{\mathfrak
+g}\downarrow {\mathfrak a}}$.
+
+\section{Injections and splints}
+
+\label{sec:Injections and splints}
+
+Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
+\mathfrak{a}\hookrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
+is a
+reductive subalgebra $\mathfrak{a \subset g}$ with correlated root spaces: $%
+\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset \mathfrak{h}_{\mathfrak{g }%
+}^{\ast }$. Let $\mathfrak{a}^{\mathfrak{s}}$ be a semisimple summand of
+$\mathfrak{a}$,
+this means that $\mathfrak{a}=\mathfrak{a}^{\mathfrak{s}} \oplus \mathfrak{u}(1)\oplus %
+\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^{\mathfrak{s}}$
+to be a proper regular subalgebra and $\mathfrak{a}$ to be the
+maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed that is the rank
+$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
+
+The following notations are used:
+
+$r$ , $\left( r_{\mathfrak{a}^{\mathfrak{s}}}\right) $ --- the rank of
+$\frak{g}$ $\left( \mathrm{{resp. }\mathfrak{a}^{\mathfrak{s}}}\right) $ ;
+
+$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system;
+$\Delta ^{+} $ $\left( \mathrm{{resp. }\Delta
+_{\frak{a}}^{+}}\right) $--- the positive root system (of
+$\frak{g}$ and $\frak{a}$ respectively);
+
+$S \, ,\quad \left( S_{\frak{a}}\right) $ --- the system of simple roots (of $%
+\frak{g}$ and $\frak{a}$ respectively);
+
+$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
+i$-th (resp. $j$-th) simple root for $\frak{g}$  $\left( \mathrm{{resp. \,} \frak{%
+a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
+^S}\right) $;
+
+$\omega _{i}$ , $\left( \omega _{\left( \frak{a}\right) j}\right) $ --- the $%
+i$-th (resp. $j$-th) fundamental weight for $\frak{g}$ $\left( \mathrm{{resp. \,}\frak{%
+a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
+^S}\right) $;
+
+$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
+
+$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
+
+$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
+fundamental Weyl chamber;
+
+$\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;
+
+$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
+
+$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
+of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
+-module with the highest weight $\nu $ );
+
+$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
+the weight diagram of $L^{\mu }$ (resp. ${}L_{\frak{a}}^{\nu }$ );
+
+$P$ (resp. $P_{\frak{a}} $) \ --- the weight lattice;
+
+$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight lattice;
+
+$\mathcal{E}$ (resp. $\mathcal{E}_{\frak{a}} $) \ --- the formal algebra;
+
+$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
+}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
+resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
+L_{\frak{a}}^{\nu } $);
+
+$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $)--- the formal character of $L^{\mu }$ (resp. $L_{\frak{a}}^{\nu
+} $);
+
+$ch\left( L^{\mu }\right)  =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
++\rho )-\rho }} {\prod_{\alpha \in \Delta ^{+}} \left( 1-e^{-\alpha }\right)
+} $ --- the Weyl formula;
+
+$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) \quad $
+(resp. $R_{\frak{a}}: =\prod_{\alpha \in \Delta_{\frak{a}}^{+}} \left(
+1-e^{-\alpha }\right) $ ) --- the Weyl denominator.
+
+Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
+\[
+L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
+\]
+\begin{equation}
+\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
+\label{branching1}
+\end{equation}
+For the modules we are interested in the Weyl formula for $\mathrm{ch}\left(
+L^{\mu }\right) $ can be written in terms of singular elements \cite
+{humphreys1997introduction}
+\[
+\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
+)-\rho },
+\]
+namely,
+\begin{equation}
+\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
+^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
+\label{Weyl-Kac2}
+\end{equation}
+The same is true for submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $ in (\ref{branching1})
+\[
+\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
+\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
+}^{\left( \nu \right) }}{R_{\frak{a}}},
+\]
+with
+\[
+\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
+}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
+\]
+
+Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
+we get a relation connecting the singular elements $\Psi ^{\left( \mu
+\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
+\begin{eqnarray}
+\frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho )-\rho }}{\prod_{\alpha \in
+\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
+}^{(\mu )}\frac{\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{%
+\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
+}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:4} \\
+\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}}^{\left( \nu \right) }}{R_{%
+\frak{a}}}.  \label{singular main}
+\end{eqnarray}
+
+In \cite{2010arXiv1007.0318L} it was proven that branching coefficients $%
+b_{\xi }^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
+\hookrightarrow \frak{g}$ are subject to the set of recurrent relations:
+\begin{equation}
+\begin{array}{c}
+b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
+\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right. \\
+\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
+}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
+}\right) .
+\end{array}
+\label{recurrent rel}
+\end{equation}
+where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $%
+\frak{g}$ orthogonal to roots of $\frak{a}$ and $W_{\perp}$ is a Weyl group of $\mathfrak{a}_{\perp}$
+\begin{eqnarray}
+\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
+h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
+\label{delta a ort}
+\end{eqnarray}
+\begin{eqnarray}
+\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\qquad \widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }
+\end{eqnarray}
+and $\pi$ is the projection operator. When an injection is maximal the
+projection becomes trivial and the relation (\ref{recurrent rel}) is
+simplified:
+\begin{equation}
+\begin{array}{c}
+b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
+}+\right. \\
+\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
+\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
+\end{array}
+\label{recurrent relation max}
+\end{equation}
+The recursion is goverened by the set $\Gamma _{\frak{a}\rightarrow \frak{g}}
+$ called the injection fan. The latter is defined by the carrier set $%
+\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the coefficient
+function $s(\xi )$
+\[
+\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{ \xi \in P_{%
+\frak{a}}|s(\xi )\neq 0\right\}
+\]
+appearing in the expansion
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\frak{a}}^{+}}\left( 1-e^{
+-\alpha }\right) =-\sum_{\gamma \in P_{\frak{a}}}s(\gamma )e^{-\gamma };\quad
+\label{product}
+\end{equation}
+
+Now we remind two definitions introduced in \cite{richter2008splints}
+
+\begin{Def}
+Suppose $\Delta _{0}$ and $\Delta $ are root systems with corresponding
+weight lattices $P_{0}$ and $P$. Then $\phi $ is an ``embedding'',
+\begin{equation}
+\phi :\left\{
+\begin{array}{l}
+\Delta _{0}\hookrightarrow \Delta , \\
+P_{0}\hookrightarrow P,
+\end{array}
+\right.
+\end{equation}
+if \newline
+\noindent (a) it injects $\Delta _{0}$ in $\Delta $, and \newline
+\noindent (b) acts homomorphically with respect to the vector groups in $%
+P_{0}$ and $P$:
+\[
+\phi (\gamma )=\phi (\alpha )+\phi (\beta )
+\]
+for any triple $\alpha ,\beta ,\gamma \in P_{0}$ such that $\gamma =\alpha
++\beta $.
+\end{Def}
+
+$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
+\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
+_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
+\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+
+Notice that one must distinguish two classes of embeddings: when the scalar
+product (defined by the Killing form) in the root space $P_0$ is invariant
+with respect to $\phi$ and when it is not $\phi$-invariant. The first
+embedding is called "metric" , the second -- "nonmetric".
+
+\begin{Def}
+A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if
+there are two embeddings $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
+\phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the
+disjoint union of the images of $\phi _{1}$ and $\phi _{2}$ and (b) neither
+the rank of $\Delta _{1}$ nor the rank of $\Delta _{2}$ exceeds the rank of $%
+\Delta $.
+\end{Def}
+
+It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$
+and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$. Each
+component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $%
+(\Delta_1,\Delta_2)$.
+
+To study relations between injection fan technique and splint let us 
+consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ 
+is a root subsystem.
+
+Splint $\Delta \approx (\Delta _{1},\Delta _{2})$ is called ''injective'' if
+$\Delta _{1}=\Delta _{\frak{a}}$, is a root subsystem
+in $\Delta $ corresponding to a regular reductive subalgebra $\frak{a}%
+\hookrightarrow \frak{g}$.
+
+In case of injective splint the second stem $\Delta _{\frak{s}}:=\Delta
+_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product (%
+\ref{product}) and it defines an injection fan $\Gamma _{\frak{a}%
+\hookrightarrow \frak{g}}$. Denote by $\Delta_{\mathfrak{s}0}$ the coimage of the second embedding $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\mathfrak{g}}$.
+The following conjecture follows.
+
+\begin{Cnj}
+Each injective splint $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
+$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\frak{a}%
+\rightarrow \frak{g}}$ fixed by the product
+\begin{equation}
+\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)
+=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
+\end{equation}
+\end{Cnj}
+
+In case of injective splint we say that subalgebra $\frak{a}\hookrightarrow \frak{g}$
+splinters $\Delta $ (and call $\frak{a}$ the ''splinting subalgebra'' of $%
+\frak{g}$). In \cite{richter2008splints} splints are classified (see Appendix there)
+and the first three types of them are injective.
+
+\section{How stems define multiplicity functions}
+
+\label{sec:stems and multiplicity functions}
+
+In this Section we study properties of injective splints  $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
+$. It will
+be demonstrated that in this case to find branching
+coefficients for a splinting injection $\frak{a}\hookrightarrow
+\frak{g}$ means to find weight multiplicities of an irreducible
+$\frak{s}$-module $L_{\frak{s}}^{\nu }$ with fixed highest weight
+$\nu $. Notice that $\frak{s}$ must not be a subalgebra of
+$\frak{g}$.
+
+Let us return to relation (\ref{singular main}) and multiply both sides by $%
+R_{\frak{a}}$:
+\begin{equation}
+\frac{1}{\prod_{\beta \in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })}\Psi _{%
+\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
+}^{(\mu )}\Psi _{\frak{a}}^{\left( \nu \right) }.
+\label{singular main-2}
+\end{equation}
+Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{%
+\frak{a}\rightarrow \frak{g}}$. Consider the highest weight module $L_{\frak{%
+s}}^{\nu }$. The embedding $\phi :\Delta _{\frak{s}\,0}\longrightarrow \Delta
+_{\frak{g}}$ sends the singular element $\Psi _{\frak{s}}^{\left( \nu
+\right) }$ into $\Psi _{\frak{g}}^{\left( \mu \right) }$. Applying the
+inverse morphism $\phi ^{-1}$ to the product $\left( \prod_{\beta \in \Delta
+_{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\frak{s}%
+}^{\left( \nu \right) }\right) $ one gets the character of the module $L_{%
+\frak{s}}^{\nu }$,
+
+\begin{equation}
+\phi ^{-1}\left( \frac{1}{\prod_{\beta \in \Delta _{\frak{s}%
+}^{+}}(1-e^{-\beta })}\phi \left( \Psi _{\frak{s}}^{\left( \nu \right)
+}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\frak{s}0
+}^{+}}(1-e^{-\beta })}\Psi _{\frak{s}}^{\left( \nu \right) }=\mathrm{ch}%
+\left( L_{\frak{s}}^{\nu }\right) .  \label{inverse for stem}
+\end{equation}
+Our task is to prove that the singular element $\Psi _{\frak{g}}^{\left( \mu
+\right) }$ contains the element $\Psi _{\frak{s}}^{\left( \xi \right) }$ for
+a module $L_{\frak{s}}^{\xi }$ uniquely defined by $L_{\frak{g}}^{\mu }$ and
+that the branching coefficients $b_{\nu }^{(\mu )}$ in the r.h.s. of (\ref
+{singular main-2}) coincide with multiplicities $m_{\zeta }^{\left( \xi
+\right) }$ of the corresponding weights in $\mathcal{N}_{\frak{s}}^{\xi }$ .
+
+For a highest weight irreducible module $L_{\frak{g}}^{\mu }$ the singular
+element $\Psi _{\frak{g}}^{\left( \mu \right) }$ is an element of $\mathcal{E%
+}$ corresponding to the shifted Weyl-orbit of the weight $\left( \mu +\rho
+\right) \in P^{+}$ with the sign function $\epsilon \left( w\right) $. It is
+convenient to use also unshifted singular elements
+\begin{equation}
+\Phi ^{\left( \mu \right) }:=\Psi ^{\left( \mu \right) }e^{\rho }.
+\label{definition Phi}
+\end{equation}
+In these terms the relation (\ref{singular main-2}) looks like
+\begin{equation}
+\frac{e^{\rho _{\frak{g}}-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{%
+s}}^{+}}(1-e^{-\beta })}\Phi _{\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in
+P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\Phi _{\frak{a}}^{\left( \nu \right) }.
+\label{singular main-3}
+\end{equation}
+The orbit related to $\Phi _{\frak{g}}^{\left( \mu \right) }$ is completely
+defined by the set of edges $\left\{ \lambda _{i}\right\} _{i=1,\dots ,r}$
+adjusted to the end of the highest weight vector $\mu +\rho $. For $\mu
+=\sum m_{i}\omega _{i}$ these edges are
+\begin{equation}
+\lambda _{i}=-\left( m_{i}+1\right) \alpha _{i},\quad i=1,\dots ,r.
+\label{edge}
+\end{equation}
+Each formal exponent $e^{\mu +\rho +\lambda _{i}}$ in $\Phi _{\frak{g}%
+}^{\left( \mu \right) }$ bears the sign coefficient $\epsilon =(-)$. The
+defining property of $\Phi _{\frak{g}}^{\left( \mu \right) }$ is as follows.
+Consider any pair of edges $\lambda _{i},\lambda _{j}$ and the corresponding
+weights $\mu +\rho $, $\mu +\rho +\lambda _{i}$ and $\mu +\rho +\lambda _{j}$. 
+Apply the reflection $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
+\begin{equation}
+s_{\alpha _{i}}\circ \left\{
+\begin{array}{l}
+\left( \mu +\rho \right)  \\
+\left( \mu +\rho +\lambda _{i}\right)  \\
+\left( \mu +\rho +\lambda _{j}\right)
+\end{array}
+\right. =\left\{
+\begin{array}{l}
+\left( \mu +\rho +\lambda _{i}\right)  \\
+\left( \mu +\rho \right)  \\
+\left( \mu +\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha
+_{j}\right)
+\end{array}
+\right.   \label{reflected triple}
+\end{equation}
+
+\begin{Prop}
+The edge $\lambda _{i,j}$ of $\Phi _{\frak{g}}^{\left( \mu \right) }$
+starting at the weight $\left( \mu +\rho +\lambda _{i}\right) $ along the
+root $-s_{\alpha _{i}}\circ \alpha _{j}$ has the same length in $(s_{\alpha
+_{i}}\circ \alpha _{j})$ as $\lambda _{j}$ has in $\alpha _{j}$. (The same
+is true for the edge $\lambda _{j,i}$, its length in $(s_{\alpha _{j}}\circ
+\alpha _{i})$ is equal to the length of $\lambda _{i}$ in $\alpha _{i}$.)
+\label{diagram property}
+\end{Prop}
+
+In $\Phi _{\frak{g}}^{\left( \mu \right) }$ the elements $e^{\left( \mu
++\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha _{j}\right) }$ and $%
+e^{\left( \mu +\rho +\lambda _{j}-(m_{i}+1)s_{\alpha _{j}}\circ \alpha
+_{i}\right) }$ have the sign coefficient  $\epsilon =(+)$.
+
+Remember that only three types of splints are
+injective and thus are naturally connected with branching. Below we
+reproduce the part of the splints table from \cite{richter2008splints} corresponding to
+injective splints:
+\[
+\begin{array}{cc||c|c}
+\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
+_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
+\\ \hline\hline
+\hbox{(i)} & G_{2} & A_{2} & A_{2} \\
+& F_{4} & D_{4} & D_{4} \\ \hline
+\hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
+& C_{r}(r\geq 3) & D_{r} & \oplus ^{r}A_{1} \\ \hline
+\hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
+^{r}A_{1} \\
+& B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
+\end{array}
+\]
+Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\frak{s}})
+$ of the simple root system $\Delta $. In the first two types both $\Delta _{%
+\frak{a}}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
+first type splints are equivalent and in the second are not. In the third
+type splints only $\Delta _{\frak{a}}$ is embedded metrically. The summands $%
+u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$. This does not change
+the principle properties of branching but makes it possible to use the
+multiplicities of $\frak{s}$-modules without further projecting their
+weights.
+
+Splints induce a decomposition of the set $S=S_{\frak{c}}\cup S_{\frak{d}}$
+with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}}$. 
+It is easy to check that for any injective splint the subset $S_{%
+\frak{d}}$ is nonempty. It follows that in the set $\left\{ \lambda
+_{i}\right\} _{i=1,\dots ,r}$ one can always find simple roots $\beta
+_{k}\in \Delta _{\frak{s}}$ and that the orbit corresponding to $\Phi _{%
+\frak{g}}^{\left( \mu \right) }$ contains the edges
+\begin{equation}
+\lambda _{k}=-\left( m_{k}+1\right) \beta _{k}  \label{beta edge}
+\end{equation}
+attached to the weight $\mu +\rho $. As far as $\Delta _{\frak{a}}$ is a
+root system and for any pair of simple roots from $S_{\frak{c}}$ the
+property \ref{diagram property} is fulfilled, the element $\Phi _{\frak{g}%
+}^{\left( \mu \right) }$ being a singular element for a set of $\frak{a}$%
+-modules. Consider $\beta _{l}\in \Delta _{\frak{s}}$ whose coimage in $%
+\Delta _{\frak{s}0}$ is simple. In Appendix it is shown that for any such $%
+\beta _{l}$ there exists a root $\alpha _{l}\in S_{\frak{c}}$ such that
+$\beta _{l}=\alpha _{l}+\beta _{k}$. It is easily seen that the
+corresponding edge intersects the boundary plane of the fundamental chamber $%
+\bar{C_{\frak{a}}}$ orthogonal to the root $\alpha _{l}$,
+\begin{equation}
+s_{\alpha _{l}}\left( \mu +\rho -p\beta _{l}\right) =s_{\alpha _{l}}\left(
+\mu +\rho \right) -ps_{\alpha _{l}}\beta _{l}=\mu +\rho -p\beta _{l},
+\label{intersection}
+\end{equation}
+\begin{equation}
+\mu +\rho -s_{\alpha _{l}}\left( \mu +\rho \right) =\left( m_{l}+1\right)
+\alpha _{l}=\left( m_{l}+1\right) \beta _{l}-\left( m_{l}+1\right) \beta
+_{k}=p\beta _{l}-ps_{\alpha _{l}}\beta _{l}.  
+\label{intersection-2}
+\end{equation}
+It follows that $p=\left( m_{l}+1\right) $ and $s_{\alpha _{l}}\beta
+_{l}=\beta _{k}$. Now apply the operator $s_{\beta _{k}}$ and find that the
+edge along the root $s_{\beta _{k}}\alpha _{l}$ attached at the weight $%
+s_{\beta _{k}}(\mu +\rho )$ is also equal to $-ps_{\beta _{k}}\alpha _{l}$.
+This means that for the triple of roots $\beta _{k},\beta _{l}$ and $%
+s_{\beta _{k}}\alpha _{l}$ in $\Delta _{\frak{s}}$ the edges $\lambda
+_{k}=-\left( m_{k}+1\right) \beta _{k}$, $\lambda _{l}=-\left(
+m_{l}+1\right) \beta _{l}$ and $\lambda _{kl}=-\left( m_{l}+1\right)
+s_{\beta _{k}}\alpha _{l}$ demonstrate the property \ref{diagram property}.
+One can continue this procedure further in the 2-dimensional subspace fixed
+by the roots $\beta _{k}$ and $\beta _{l}$ and find the set of formal
+exponents that being supplied with the corresponding sign factors compose
+the coimage of the singular element of a module for the subalgebra in $\frak{%
+s}$ (this subalgebra has rank $r=2$).
+
+The same can be proven for any positive root $\beta _{l}\in \Delta $ that is
+simple in $\Delta _{\frak{s}0}$ and correspondingly for any $r=2$ subalgebra
+in $\frak{s}$. The latter means that to ''find'' a singular element of $%
+\frak{s}$-module in $\Phi _{\frak{g}}^{\left( \mu \right) }$ it is necessary
+to incorporate in it additional formal elements $\left\{ -e^{\mu +\rho
+-\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\}.$ This
+fixes the starting edges of the diagram $\phi ^{-1}\left( \Phi _{\frak{s}}^{%
+\widetilde{\mu }}\right) $. As it follows from the reconstruction procedure
+the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $%
+, they have the same Dynkin numbers:
+\begin{equation}
+\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
+m_{k}\widetilde{\omega }_{k} . \label{new h weight}
+\end{equation}
+The next step is to construct the full $W_{\frak{s}}$-orbit $\Phi _{\frak{s}%
+}^{\left( \widetilde{\mu }\right) }$  in $P_{\frak{s}}$. It is easily seen
+that its coimage belongs to $\bar{C_{\frak{a}}}$ and that the set $\phi
+^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) \setminus \Phi _{%
+\frak{g}}^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ corresponds to the
+weights belonging to the boundary $\bar{C_{\frak{a}}}$ (including the subset
+$\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{%
+\frak{c}}\right\} $). Thus we have constructed all the formal elements\ with
+the appropriate sign factors that after being added to $\Phi _{\frak{g}%
+}^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ form the diagram $\phi
+^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) $ in $\bar{C_{\frak{a}%
+}}$.
+
+Now let us return to relation (\ref{singular main-3}). One can add to $%
+\Phi _{\frak{g}}^{\left( \mu \right) }$ pairs of formal elements
+constructed above  with the opposite signs: $\epsilon \left( w\right)
+|_{w\in W_{\frak{s}}}$ and $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$. 
+Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ to
+the elements whose weights we shall attribute to $\bar{C_{\frak{a}}}$. 
+The same elements with the opposite signs are to be referred to the
+neighboring Weyl chambers of $\bar{C_{\frak{a}}^{(l)}}$ (the latter are
+connected with the main one via simple reflections $s_{\alpha _{l}}$ so the
+signes $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ are natural for
+them). In fact one can repeat the procedure and find additional singular
+weights in any Weyl chamber $\bar{C_{\frak{a}}^{(m)}}$ and in them
+additional singular weights always have the signs opposite to that in their
+nearest neighbors. Thus without changing the element $\Phi _{\frak{g}%
+}^{\left( \mu \right) }$ one can present it as a sum
+\begin{equation}
+\Phi _{\frak{g}}^{\left( \mu \right) }=\sum_{w\in W_{\frak{a}}}w\circ \left(
+e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho _{\frak{s}}}\right)
+\label{singular final}
+\end{equation}
+where the weight $\widetilde{\mu }=\sum m_{k}\omega _{\frak{s}}^{k}$ was
+defined above. The decomposition (\ref{singular final}) provides the
+possibility to apply the factor $\left( \prod_{\beta \in \Delta _{\frak{s}%
+}^{+}}(1-e^{-\beta })\right) ^{-1}$ to each summand of the singular element $%
+\Phi _{\frak{g}}^{\left( \mu \right) }$ separately because the sets of
+weights from different Weyl summands do not intersect. Taking into account
+the isomorphism $\phi $ one can see that in the main Weyl chamber $\bar{C_{%
+\frak{a}}}$ the set of weights generated by the factor $\left( \prod_{\beta
+\in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}$ is isomorphic to
+the weight diagram $\mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ of the $\frak{%
+s}$-module $L_{\frak{s}}^{\widetilde{\mu }}$. Now one can restrict
+relation (\ref{singular main-3}) to $\bar{C_{\frak{a}}}$ and obtain the main
+result:
+\begin{Prop}
+\begin{equation}
+\frac{e^{\rho _{\frak{g}}}}{\prod_{\beta \in \Delta _{\frak{s}%
+}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
+}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }%
+}}M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
+\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}=\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
+\label{singular main-4}
+\end{equation}
+Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
+highest weights in the decomposition. The multiplicity $M_{\left( \frak{s}%
+\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
+}\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ defines the branching
+coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
+-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
+\[
+b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}.
+\]
+\end{Prop}
+
+\section{Examples}
+\label{sec:examples}
+\begin{example}
+  Consider the Lie algebra $A_{2} =\bf{sl}(3)$ and branching of its irreducible module $L^{[3,2]}_{A_{2}}$ with respect to the reductive subalgebra $A_{1}\oplus u(1)$.
+The root system  $\Delta _{\frak{a}}= \Delta_{A_{1}\oplus u(1)}$ contains the simple root of $\alpha_1=e_1-e_2$ of $A_{2}$.
+The singular element $\Psi^{[3,2]}_{\frak{a}}$ is decomposed into a sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules.
+Branching coefficients $b_{\nu }^{[ 3,2 ] }$ coincide with weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module (see Fig.
+\ref{fig:a2_splint}).
+
+  \begin{figure}[h!bt]
+  \noindent\centering{
+   \includegraphics[width=80mm]{a2-a1}
+  }
+  \caption{Weyl group orbit (dotted) producing singular element of $L^{[3,2]}_{A_{2}}$ and its decomposition into the sum of splint images of singular elements of modules  $L^{[3,2]}_{A_{1}\oplus A_{1}}$ (dashed).
+Weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}
+
+ \label{fig:a2_splint}
+\end{figure}
+\end{example}
+\begin{example}
+  For the Lie algebra $B_{2}= \bf{so}(5)$ branching of its irreducible module $L^{[3,2]}$ into  modules of a reductive subalgebra $A_{1}\oplus u(1)$ with the root system spanned by the first simple root $\alpha_1=e_1-e_2$ of $B_{2}$.
+Singular element of $\Psi^{[3,2]}_{B_{2}}$ is decomposed into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide with weight multiplicities of $A_{2}$-module (see Fig.
+\ref{fig:b2_splint}).
+
+  \begin{figure}[h!bt]
+  \hspace*{-1.2cm}
+
+   \includegraphics[width=65mm]{b2}
+   \includegraphics[width=65mm]{b2-a2-a1}
+  \caption{Weights of the $B_{2}$-module $L^{[3,2]}$ are indicated by dots in the left picture (their multiplicities are also indicated).
+Contour of the singular element is shown by dotted line.
+The right picture presents the decomposition of  $\Psi_{B_{2}}(L^{[3,2]}_{B_{2}})$-singular element into the sum of splint images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ (dashed).
+Weight multiplicities of $L^{[3,2]}_{A_{2}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{B_{2}\downarrow A_{1}\oplus u(1)}$.}
+
+ \label{fig:b2_splint}
+\end{figure}
+\end{example}
+
+\vspace{10mm}
+\begin{example}
+   Lie algebra $G_{2}$ has a regular subalgebra $A_{2}$ with root system $\Delta_{\mathfrak{a}}=\Delta_{A_{2}}$ containing the $G_{2}$ long roots.
+Consider branching of an irreducible module $L_{G_{2}}^{(3,2)}$ into the $A_{2}$-modules.
+Singular element $\Psi_{G_{2}}(L^{[3,2]})$ is decomposed into the sum of splint images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ and the corresponding branching coefficients coincide with weight multiplicities of $L^{[3,2]}_{A_{2}}$-module (see Fig.
+\ref{fig:g2_splint}).
+
+  \begin{figure}[h!bt]
+  \noindent\centering{
+   \includegraphics[width=120mm]{g2}
+  }
+
+  \caption{Weyl group orbit (dotted) for the singular element $\Psi_{G_{2}}(L^{[3,2]})$ and its decomposition into the sum of splint images of singular elements of $A_{2}$-modules (dashed).
+Weight multiplicities of $L^{[3,2]}_{A_{2}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{G_{2}\downarrow A_{2}}$.}
+
+ \label{fig:g2_splint}
+\end{figure}
+
+\end{example}
+
+\section{Conclusions}
+
+\label{sec:conclusions}It is explicitly demonstrated that splint
+presents a very effective tool to find branching coefficients. In
+particular injective splints provide a possibility to reduce
+branching rules calculations for highest weight modules to a
+determination of weight multiplicities for a module with the same
+Dynkin labels referred to the Lie algebra $\mathfrak{s}$. This algebra
+$\mathfrak{s}$ must not be a subalgebra in the initial $\mathfrak{g}$ , it
+has the same rank $r_{\mathfrak{s}}=r$\ , but obviously less
+"complicated" than $\mathfrak{g}$ -- only a subset of the initial root system is involved in the second stem $\Delta_{\mathfrak{s}}$.
+
+It is significant that for the injections $D_{r}\hookrightarrow B_{r}$ , $%
+D_{r}\hookrightarrow C_{r}$ and $A_{r-1}\oplus u\left( 1\right) \hookrightarrow A_{r}$ splint technique shows
+transparently Gelfand-Tzeytlin rules for branching:  the reduction is
+multiplicity free (all nonzero
+branching coefficients are equal to 1). Here it is an immediate consequence of the
+structure of the second stem being a direct sum of $A_{1}$
+algebras and the fact that the corresponding module
+$L_{\frak{s}}^{\mu }$ is irreducible.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Appendix}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Let us demonstrate that for injective splints of classical Lie
+algebras the following property is valid:
+\begin{Prop}
+Let $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})$ be an
+injective
+splint with the decomposition of simple roots $S=S_{\frak{c}}\cup S_{\frak{d}%
+}$ with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}%
+}$.
+\end{Prop}
+Thus for any simple root $\beta \in S_{\frak{s}}$ there exists the
+pair of
+roots ( $\alpha $ ,$\beta ^{\prime }$) with $\alpha \in $ $S_{\frak{c}%
+},\beta ^{\prime }\in S_{\frak{s}}$ such that $\alpha =\beta
+-\beta ^{\prime }$
+
+\begin{itemize}
+\item
+Type 1. $\Delta _{G_{2}}\approx (\Delta _{A_{2}},\Delta
+_{A_{2}}).$
+
+ \begin{figure}[h!bt]
+  \noindent\centering{
+   \includegraphics[width=100mm]{g2-roots}
+  }
+  \caption{Positive roots of $G_{2}$ and formation of singular element $\Phi^{(0)}_{\mathfrak{s}}$ in the main Weyl chamber of $\mathfrak{a}=A_{2}$.}
+\end{figure}
+Here both stems are metric and the corresponding root systems are
+equivalent. In Figure 4 a part of the singular element $\Phi
+_{G_{2}}^{\left( 0\right) }$ is presented. The boundaries of $\bar{C_{\frak{a%
+}}}$ are the dashed lines starting at the center of the singular
+element. It
+contains the edge $\lambda _{2}=-\alpha _{2}=-\beta _{2}$ and the roots $%
+-\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3}$ and $ -\beta _{3}$
+($\beta _{3}$ is indicated as $\beta _{l}$). For the root $\beta
+_{1}$ the necessary pair
+is  $(\alpha _{1}, \beta _{2})$: $\alpha _{1}=\beta _{1}-\beta _{2}$. The $%
+\lambda _{2,3}^{\frak{s}}=\beta _{3}$ edge is equal to $\lambda _{1}^{\frak{s%
+}}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ and $m_{1}$ index
+is aquired by the $\frak{s}$-module that also inherit the second
+index $m_{2}$. In this particular
+case they are $m_{1}=m_{2}=0$. The general case with the initial module $%
+L^{\mu }$ and $\mu =m_{1}\omega _{1}+m_{2}\omega _{2}$ can be
+treated in the same way: one finds an edge $\lambda _{2}=-\left(
+m_{2}+1\right) \beta _{2}$ and put $\lambda
+_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$, its end
+belongs to the boundary $\bar{C_{\frak{a}}}$. The reflection
+$s_{\beta
+_{2}} $ sends $\beta _{1}$ to $\beta _{3}$ and the corresponding edge 
+$\lambda _{2,3}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{3}$ has
+the length $\left( m_{1}+1\right) $. Now consider $\lambda _{1}^{\frak{s}}$ (or
+$\lambda _{2,3}^{\frak{s}} $) and $\lambda _{1,3}^{\frak{s}}$ (or
+$\lambda _{2,3,1}^{\frak{s}}$) edges to find that they belong to
+the boundary $\bar{C_{\frak{a}}}$ and the Weyl symmetry predicts
+that $\lambda _{1,3}^{\frak{s}}=-\left( m_{2}+1\right)
+\beta _{3}$ ($\lambda _{2,3,1}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{1}$%
+) . Finally the edge $\lambda _{1,3,2}^{\frak{s}}=-\left(
+m_{1}+1\right) \beta _{2}$ closes the polytope. Its vertices
+correspond to weights of the singular
+element $\Phi _{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{%
+\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
+\widetilde{\mu }+\rho
+_{\frak{s}}\right) }$ of the module $L_{\frak{s}}^{\left( \widetilde{\mu }%
+\right) }$ with $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}%
+\widetilde{\omega }_{2}$. Notice that in this case the sign
+factors can be obtained directly in the initial weight system as
+far as the stem is metric.
+\item
+Type 1. $\Delta _{F_{4}}\approx (\Delta _{D_{4}},\Delta
+_{D_{4}}).$
+
+Both stems are metric here and the corresponding root systems are
+equivalent. The system $\Delta _{D_{4}}$ of the subalgebra
+$\frak{a=}D_{4}$ is formed by the set $\left\{ \pm e_{i}\pm
+e_{j}\right\} _{|i,j=1,\ldots 4,\; i\neq j}.$ The simple roots
+$S_{\frak{c}}$ are $\left\{ e_{2}-e_{3},e_{3}-e_{4}\right\} $ and
+$S_{\frak{d}}=\left\{ e_{4},\frac{1}{2}\left(
+e_{1}-e_{2}-e_{3}-e_{4}\right) \right\} $.
+For a module $L^{\mu }$ with $\mu =\sum m_{k}\omega _{k}$ consider the edge $%
+\lambda _{3}=-\left( m_{3}+1\right) e_{4}=-\left( m_{3}+1\right)
+\beta _{3}$.
+ Compose an edge $\lambda _{2}^{\frak{s}}=-\left( \widetilde{m}%
+_{2}+1\right) \beta _{2}$. The necessary pair of roots is $\left(
+\alpha
+_{2}=e_{3}-e_{4},\beta _{3}\right) $. The intersection of $\lambda _{2}^{%
+\frak{s}}$ with the $\alpha _{2}$-boundary of
+$\bar{C_{\frak{a}}}$ fixes
+its length to be $\lambda _{2}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{2}$%
+\ and the length of the edge $\lambda _{3,2}^{\frak{s}}$ is equal
+to that of
+$\lambda _{2}^{\frak{s}}$. Next consider the edge $\lambda _{2}^{\frak{s}%
+}=-\left( m_{2}+1\right) \beta _{2}$ and the pair $\left( \alpha
+_{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $. The length of  
+$\lambda _{1}^{\frak{s}}$ becomes equal to $\lambda
+_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$. Proceed further till the closure of the polytope. 
+The edges looking along the roots of the $\alpha_4$-type, $\alpha _{4}=\beta
+_{4}=$ $\frac{1}{2}\left( e_{1}-e_{2}-e_{3}-e_{4}\right) $, are
+treated similarly and finally the singular element $\Phi
+_{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in
+W_{\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
+\widetilde{\mu }+\rho _{\frak{s}}\right) }$ for the module
+$L_{\frak{s}}^{\left( \widetilde{\mu }\right) }$ with
+$\widetilde{\mu }=\sum m_{k}\widetilde{\omega }_{k}$ is formed in
+$\bar{C_{\frak{a}}}$.
+\item
+Type 2. $\Delta _{B_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
+^{r}A_{1}}). $
+
+Both stems are metric. An injection is fixed by the stem $\Delta
+_{D_{r}}$ simple roots $S_{\frak{a}}=\left\{
+e_{1}-e_{2},e_{2}-e_{3},\ldots
+,e_{r-1}-e_{r},e_{r-1}+e_{r}\right\} $. The second stem
+corresponds to a
+direct sum of algebras $A_{1}$ with the simple roots $S_{\frak{s}%
+}=\left\{ e_{1},e_{2},\ldots ,e_{r-1},e_{r}\right\} $. Consider the edge $%
+\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ (here $\beta
+_{r}=e_{r}$) and $\lambda _{r-1}=-\left(
+\widetilde{m}_{r-1}+1\right) \beta _{r-1}$
+attached to it (here $\beta _{r-1}=e_{r-1}$). The corresponding pair is $%
+\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta _{r-1}=e_{r-1}\right) $.
+ The intersection condition fixes the second edge to be $\lambda
+_{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ , it is orthogonal
+to $\beta _{r}$ so the opposite edge has the same length. The
+Dynkin index $m_{r-1}$ now refers
+also to the\ simple root $\beta _{r-1}$. Next consider the obtained edge $%
+\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and $\lambda
+_{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$ to
+fix the index $\widetilde{m}_{r-2}=m_{r-2}$ and the edge
+$\lambda _{r-2}=-\left( m_{r-2}+1\right) \beta _{r-2}$ and so on
+till all the pairs of edges are properly fixed. Finally in
+$\bar{C}_{D_{r}}$ the element $\Phi _{\oplus ^{r}A_{1}}^{\left(
+\widetilde{\mu }\right) }=\sum_{w\in W_{\oplus
+^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+%
+\frac{1}{2}\sum e_{k}\right) }$ can be constructed for the module
+$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
+$\widetilde{\mu }=\sum m_{k}\frac{1}{2}e_{k}$.
+
+\item
+Type 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
+^{r}A_{1}}). $
+
+The situation in this case is eqivalent to the previous one and
+the additional edges are constructed similarly.
+\item
+Type 3 $\Delta _{A_{r}}\approx (\Delta _{A_{r-1}\oplus
+u_{1}},\Delta _{\oplus ^{r}A_{1}}).$
+
+Here only the first stem is metric and it fixes the injection with
+simple roots $S_{\frak{a}}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots
+,e_{r-1}-e_{r}\right\} $. The second stem corresponding to a direct sum of $%
+r$ copies of $A_{1}$ has the simple roots $S_{\frak{s}}=\left\{
+e_{1}-e_{r+1},e_{2}-e_{r+1},\ldots ,e_{r}-e_{r+1}\right\} $.
+Consider the edge $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$
+with $\beta
+_{r}=e_{r}-e_{r+1}$ and $\lambda _{r-1}=-\left( \widetilde{m}%
+_{r-1}+1\right) \beta _{r-1}$ \ with $\beta
+_{r-1}=e_{r-1}-e_{r+1}$ attached to it. Then the corresponding
+pair is $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta
+_{r-1}=e_{r-1}-e_{r+1}\right)$. The intersection with the
+boundary of $\bar{C}_{A_{r-1}}$ orthogonal to $\alpha _{r-1}$
+fixes the second edge to be $\lambda _{r-1}=-\left(
+m_{r-1}+1\right) \beta _{r-1}$. The Dynkin index $m_{r-1}$ is to
+be used for the fundamental weight  $\omega _{r-1}.$ The\
+reflection $s_{\beta _{r}}$ sends $\lambda _{r-1}=-\left(
+m_{r-1}+1\right) \beta _{r-1}$ to $\lambda _{r,r-1}=-\left(
+m_{r-1}+1\right) \beta _{r-1}.$ Next consider the obtained edge
+$\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and
+$\lambda _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$
+with $\beta _{r-2}=e_{r-2}-e_{r+1} $ to obtain the index
+$\widetilde{m}_{r-2}=m_{r-2}$ and the edge $\lambda _{r-2}=-\left(
+m_{r-2}+1\right) \beta _{r-2}$ and so on till all the pairs of
+edges are properly fixed. Finally in $\bar{C}_{D_{r}}$ the element
+$\Phi _{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right)
+}=\sum_{w\in W_{\oplus
+^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+%
+\widetilde{\rho }\right) }$ can be constructed for the module
+$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
+$\widetilde{\mu }=\sum m_{k}\beta _{k}.$ The simplest case
+$\Delta _{A_{2}}\approx (\Delta _{A_{1}\oplus u_{1}},\Delta
+_{A_{1}\oplus A_{1}})$ is presented in Example 4.1 and Figure 1.
+\item
+Type 3 $\Delta _{B_{2}}\approx (\Delta _{A_{1}},\Delta _{A_{2}}).$
+
+This splint is illustrated in Example 4.1 and Figure 1, 
+$S_{A\_1}=\left\{ e_{1}-e_{2}\right\} $, $S_{A\_2}=\left\{
+e_{1},e_{2}\right\} $. The edge $\lambda _{\alpha _{2}}=\lambda
+_{\beta _{2}}=-\left( m_{2}+1\right) \beta _{2}$ is followed by
+$\lambda _{\beta _{1}}=-\left( \widetilde{m}_{1}+1\right) \beta
+_{1}$. Consider the pair $\left( \alpha
+_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right)$. The end of the edge
+$\lambda _{\beta _{1}}$ must indicate a weight
+invariant under the reflexion $s_{\alpha _{1}}$.  Its length is thus fixed: 
+$\lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$. In the
+coimage of
+the second stem, that is in the root system $\Delta_{A_{2}}$, the reflection 
+$s_{\beta _{2}}$ sends $\lambda _{\beta _{1}}=-\left(
+m_{1}+1\right) \beta
+_{1}$ to $\lambda _{2,3}$, thus the latter edge has the same length in $%
+\beta _{3}=e_{1}+e_{3}$, we have $\lambda _{2,3}=-\left(
+m_{1}+1\right)
+\beta _{3}$ with $\beta _{3}=e_{1}+e_{3}$. The irreducible $\frak{s}$%
+-module has the highest weight $\widetilde{\mu }=m_{1}\widetilde{\omega }%
+_{1}+m_{2}\widetilde{\omega }_{2}$. In Figure 1 we see the
+details of these relations in a particular case where
+$L_{B_{2}}^{\left[ 3,2\right] }$ is reduced to a subalgebra
+$A_{1}\oplus u\left( 1\right) $ and the
+corresponding highest weights (with their multiplicities) form the diagram $%
+\mathcal{N}_{A_2}^{\left[ 3,2\right] }$ .
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Выводы к первой главе}

### 2011-10-20 AffineLieAlgebras/Thesis/2.tex
Added (almost) all texts and figures to thesis. Some work on SLE paper.

@@
+\chapter{Вычислительные методы для теории представлений аффинных алгебр Ли}
+\label{cha:computational-methods}
 %% \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
 %% \newcommand{\af}{\mathfrak{a}}
-\newcommand{\bff}{\mathfrak{b}}
+%\newcommand{\bff}{\mathfrak{b}}
 %% \newcommand{\afb}{\mathfrak{a}_{\bot}}
 %% \newcommand{\hf}{\mathfrak{h}}
-\newcommand{\hfg}{\hf_{\gf}}
+%\newcommand{\hfg}{\hf_{\gf}}
 %% \newcommand{\hfb}{\mathfrak{h}_{\bot}}
@@
 GraphicsRow[textPlot/@{im,vm,pm}]
-$\includegraphics[width=130mm]{figures/irrep-verma-pverma.pdf}$
+$\includegraphics[width=130mm]{figures/irrep-verma-pverma}$
 \end{lstlisting}
@@
 textPlot[im1$\oplus$ im2]
-$\includegraphics[width=60mm]{figures/irrep-sum.pdf}$
+$\includegraphics[width=60mm]{figures/irrep-sum}$
 \end{lstlisting}
@@
 textPlot[makeIrreducibleModule[$A_{1}$][5]$\otimes$ makeIrreducibleModule[$A_{1}$][3]];
-$\includegraphics[width=60mm]{figures/tensor-product.pdf}$
+$\includegraphics[width=60mm]{figures/tensor-product}$
 \end{lstlisting}
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{figures/timing.pdf}
+    \includegraphics[width=80mm]{figures/timing}
   }
@@
   \noindent\centering{
-   \includegraphics[width=100mm]{figures/branching-timing.pdf}
+   \includegraphics[width=100mm]{figures/branching-timing}
   }
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{figures/G2-irrep.pdf}
+    \includegraphics[width=80mm]{figures/G2-irrep}
   }
@@
   \noindent\centering{
-    \includegraphics[width=150mm]{figures/G2-pverma.pdf}
+    \includegraphics[width=150mm]{figures/G2-pverma}
   }
@@
 %% appendix sections are then done as normal sections
-\appendix
+%\appendix
 

### 2011-10-20 AffineLieAlgebras/Thesis/3.tex
Added (almost) all texts and figures to thesis. Some work on SLE paper.

@@
 
+%\usepackage{verbatim} 
+\newenvironment{comment}
+{\par\noindent{\bf Для заинтересованных читателей}\\}
+{\\\setlength{10cm}\\\hfill$\scriptstyle\blacksquare$\par}
+
+\begin{abstract}
+Примерный текст доклада на семинаре кафедры ФВЭиЭЧ по работе ``Recursive algorithms, branching coefficients and applications''.
+\end{abstract}
+
+\section{Постановка задачи}
+\label{sec:task}
+
+Здравствуйте!
+Сегодня я хочу рассказать о работе ``Рекуррентные алгоритмы, коэффициенты ветвления аффинных алгебр
+Ли и приложения''. В этой работе мы решали следующую задачу.
+
+Даны две аффинные алгебры Ли $\mathfrak{a}\subset \mathfrak{g}$. Аффинные алгебры Ли --- это особый
+класс бесконечномерных алгебр, которые строятся из конечномерных (полу)простых алгебр Ли, как
+центральные расширения алгебр петель. Более подробное определение будет дано позже. Неприводимое
+представление $L^{(\mu)}_{\mathfrak{g}}$ аффинной алгебры $\mathfrak{g}$ со старшим весом $\mu$
+может быть разложено на представления подалгебры $\mathfrak{a}$. Наша задача --- придумать
+практический алгоритм вычисления коэффициентов этого разложения. Конечно же эта задача уже решалась,
+например, существует способ решения ``в лоб'', требующий построения всех представлений и различные способы,
+которые работают для частных случаев, например, многое упрощается в физически интересном случае
+конформных вложений. Мы предлагаем общий метод, но иллюстрировать его будем как-раз физическими
+примерами конформных вложений.
+
+Я начну с физической мотивации этой задачи в двумерной конформной теории поля, напомню некоторые
+факты из теории представлений аффинных алгебр Ли, кратко опишу предложенное нами решение проблемы и
+расскажу про физические примеры в нашей статье.
+
+\section{Физическая мотивация}
+\label{sec:physics}
+
+\subsection{Напоминание про двумерную конформную теорию поля}
+\label{sec:CFT}
+
+Конформное преобразование --- это преобразование, меняющее только масштаб у метрического тензора:
+\begin{equation}
+  \label{eq:10}
+  g'_{\mu\nu}(x')=\Lambda(x)g_{\mu\nu}(x)
+\end{equation}
+
+Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований.
+
+В теории струн двумерная конформная теория поля описывает динамику на мировой поверхности, а в
+теории критических явлений --- фазовые переходы в двумерных системах.
+
+%% В $D$-мерном случае генераторы у таких преобразований следующие:
+%% \begin{align}
+%%   \label{eq:1}
+%%   & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\
+%%   &P_\mu \equiv-i\partial_\mu \,, \\
+%%   &D \equiv-ix_\mu\partial^\mu \,, \\
+%%   &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,,
+%% \end{align}
+%% 
+На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
+В двумерном случае существует бесконечное число локально-конформных преобразований.
+Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это
+условие эквивалентно уравнению Коши-Римана для голоморфных функций ($\partial_{\bar z}w(z,\bar
+z)=0$).
+
+Таким образом локально-конформные преобразования находятся в однозначном соответствии с множеством
+всех аналитических функций $w(z)$ на плоскости.
+
+Глобальные конформные преобразования имеют вид $f(z)=\frac{az+b}{cz+d},\; ad-bc=1$.
+
+Рассмотрим инфинитезимальные преобразования $w(z)=z+\epsilon(z),\quad
+\epsilon(z)=\sum_{-\infty}^{\infty}c_nz^{n+1}$. 
+Тогда для бесспинового поля $\phi(z,\bar z)$ верно следующее: $\phi'(z',\bar z')=\phi(z,\bar z)$,
+$\delta\phi=-\epsilon(z)\partial\phi-\bar \epsilon(\bar z)\bar \partial \phi=\sum_n(c_n L_n\phi+\bar
+c_n\bar L_n\phi)$, где $L_n=-z^{n+1}\partial_z,\quad \bar L_n=-\bar z^{n+1}\partial_{\bar z}$
+
+Мы видим, что в классической теории алгебра конформных преобразований --- это алгебра Витта, которая
+порождается генераторами $\{L_n, n\in \mathbb{Z}\}$ --- модами разложения оператора энергии-импульса $T$, с
+коммутационными соотношениями
+\begin{equation}
+  \label{eq:2}
+  [L_m,L_n]=(m-n)L_{m+n}
+\end{equation}
+При квантовании возникает конформная аномалия, что соответствует центральному расширению алгебры (то
+есть появлению центрального заряда $c$). В коммутационные соотношения надо добавить член
+$\frac{c}{12}(m^3-m)\delta_{m+n,0}$. В результате получаем алгебру Вирасоро.
+
+(Про тензор энергии-импульса:
+$x^{\mu}\to x^{\mu}+\epsilon^{\mu}\Rightarrow \delta S=\int d^2 x
+T^{\mu\nu}\partial_{\mu}\epsilon_{\nu}=
+\frac{1}{2}\int d^2 xT_{\mu}^{\mu}\partial_{\rho}\epsilon^{\rho}$
+В двумерной конформной теории поля тензор энергии-импульса бесследовый).
+
+Поля теории $\phi(z,\bar z)$ должны преобразовываться определенным образом при конформных преобразованиях.
+Оказывается, что все поля группируются в конформные семейства, в которых есть одно примарное поле
+\begin{equation}
+  \label{eq:3}
+  \begin{split}
+    \phi_{\Delta,\bar \Delta}(z,\bar z)\underset{
+      \genfrac{}{}{0pt}{}{z\to w(z)}
+        {\bar z \to \bar w(\bar z)}
+    }
+    {\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\left(\frac{d\bar w}{d\bar
+        z}\right)^{\bar\Delta}\phi_{\Delta,\bar \Delta}(w(z),\bar w(\bar z))\\
+    L_n \phi=0,\quad n>0\\
+    L_0 \phi=\Delta \phi\\
+  \end{split}
+\end{equation}
+$\Delta, \bar \Delta$ называются конформными размерностями поля.
+Все остальные поля называются вторичными и получаются из примарного действием операторов $L_{-n}$:
+\begin{equation}
+  \label{eq:67}
+  L_{-n_1}L_{-n_2}\dots \phi_{\Delta}
+\end{equation}
+Все поля в теории оказываются суммами произведений элементов мультиплетов алгебры Вирасоро.
+
+При некоторых дополнительных предположениях двумерную конформную теорию можно построить и решить
+полностью, если определен набор примарных полей и конформных размерностей.
+
+Существуют различные подходы к аксиоматизации двумерной конформной теории поля. В общем случае нам
+не нужно знать действие, если мы полный знаем набор примарных полей и операторные разложения их
+произведений.
+
+В том случае, если в теории конечное число примарных полей, такая теория называется минимальной.
+Кроме того, теории классифицируются по значениям центрального заряда $c$. Теории с рациональным
+центральным зарядом называются рациональными. Оказывается, что все такие теории могут быть получены
+факторизацией так называемых моделей Весса-Зумино-Новикова-Виттена.
+
+\subsection{WZW-модели}
+\label{sec:wzw}
+
+WZW-модели обладают дополнительной симметрией. Алгебра токов в них --- это алгебра Каца-Муди
+(аффинная алгебра Ли $\mathfrak{g}$), полная киральная алгебра --- полупрямое произведение
+$Vir\ltimes \mathfrak{g}$, примарные поля преобразуются по неприводимым представлениям алгебры $\mathfrak{g}$.
+
+Сейчас я поясню, что все это значит и как строятся такие модели.
+
+Модели Весса-Зумино-Виттена можно строить начиная со следующего действия:
+\begin{equation}
+\label{eq:4}
+  S=S_0+k\Gamma
+\end{equation}
+где $k$ - целое.
+Здесь $S_0$ --- действие нелинейной $\sigma$-модели.
+\begin{equation}
+  \label{eq:5}
+  S_0=\frac{1}{4a^2}\int_{S^2} d^2x\; Tr (\partial^{\mu}g^{-1}\partial_{\mu}g),
+\end{equation}
+где $a^2>0$ - положительный параметр, $g(x)\in G$ - поле со значениями в группе $G$, которую мы
+будем считать полупростой. Действие задается на комплексной плоскости с бесконечностью, которая
+топологически эквивалентна 2-сфере.
+
+В нелинейной $\sigma$-модели конформная инвариантность теряется на квантовом уровне.
+Голоморфный и антиголоморфный токи не сохраняются по отдельности.
+Поэтому мы добавляем член Весса-Зумино $\Gamma$ к действию
+\begin{equation}
+  \label{eq:73}
+\Gamma= - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr\left(
+    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+Он определен на трехмерном многообразии $B$, ограниченном исходным двумерным пространством.
+Через $\tilde{g}$ мы обозначили продолжение поля $g$ на $B$. Такое продолжение не единственно. В
+компактифицированном трехмерном пространстве компактное двумерное многообразие разделяет два
+трехмерных многообразия.
+\begin{figure}[h]
+ \centering
+  \includegraphics[width=100mm]{fig3}  
+  \caption{Два продолжения поля на трехмерное многообразие}
+  \label{fig:1}
+\end{figure}
+
+Разность значений члена Весса-Зумино $\Delta\Gamma$ на этих многообразиях
+дается правой частью уравнения (\ref{eq:73}) с интегралом, продолженным на все компактное трехмерное
+пространство. Так как оно топологически эквивалентно три-сфере, получаем
+\begin{equation}
+  \label{eq:75} \Delta\Gamma= - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left( \tilde
+g^{-1}\frac{\partial \tilde g}{\partial y^i} \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+\tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+$\Delta\Gamma$ определен по модулю $2\pi i$, поэтому Евклидов функциональный интеграл
+с весом $exp(-\Gamma)$ хорошо определен. Значит константа связи, умножаемая на этот член, должна
+быть целочисленной.
+
+Уравнение движения для полного действия (\ref{eq:4}):
+\begin{equation}
+  \label{eq:77}
+  \partial^{\mu}(g^{-1}\partial_{\mu}g)+\frac{a^2 ik}{4\pi}\epsilon_{\mu\nu}\partial^{\mu}(g^{-1}\partial^{\nu}g)=0
+\end{equation}
+В комплексных координатах оно записывается в виде
+\begin{equation}
+  \label{eq:78}
+  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
+\end{equation}
+Видно, что при $a^2=\frac{4\pi}{k}$ у нас имеются законы сохранения
+\begin{equation}
+  \label{eq:79}
+  \partial_z(g^{-1}\partial{\bar z}g)=0
+\end{equation}
+Для токов
+\begin{equation}
+  \label{eq:72}
+  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
+\end{equation}
+
+\begin{equation}
+  \label{eq:100}
+  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
+\end{equation}
+То есть голоморфная и антиголоморфная части отщепляются, что является указанием на наличие
+конформной инвариантности.
+
+Решение классического уравнения движения имеет вид
+\begin{equation}
+  \label{eq:80}
+  g(z,\bar z)=f(z)\bar f(\bar z)
+\end{equation}
+при произвольных $f(z)$ и $\bar f (\bar z)$.
+
+Сохранение по отдельности токов $J_z,\; J_{\bar z}$ приводит к инвариантности действия при преобразованиях
+\begin{equation}
+  \label{eq:81}
+   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)
+\end{equation}
+где $\Omega,\;\bar \Omega \in G$. То есть мы получили локальную $G(z)\times G(\bar z)$-инвариантность.
+
+Для перехода к квантовому случаю мы переопределяем токи
+\begin{equation}
+  \label{eq:82}
+  J(z)\equiv -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
+\end{equation}
+ При инфинитезимальных преобразованиях $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ вариация
+ $\delta_{\omega}g=\omega g$, а вариация действия
+ \begin{equation}
+   \label{eq:11}
+   \delta S=-\frac{1}{2\pi}\int d^2 x \left(\partial_{\bar z}Tr(\omega(z)J(z))+\partial_z Tr(\bar
+     \omega(\bar z)\bar J(\bar z))\right)
+ \end{equation}
+Заменяем $d^2 x=-\frac{i}{2} dz d\bar z$, интегрируем по частям и переходим к интегралу по контуру, замыкая
+контур в разных направлениях для голоморфной и антиголоморфной частей.
+Тогда вариация действия
+\begin{equation}
+  \label{eq:83}
+  \delta_{\omega,\bar\omega}S=\frac{i}{4\pi}\oint dz Tr (\omega(z)J(z))-\frac{i}{4\pi}\oint d\bar z Tr(\bar\omega(\bar z)\bar J(\bar z))
+\end{equation}
+Раскладывая токи
+\begin{equation}
+  \label{eq:85}
+  \begin{aligned}
+    J=\sum J^a t^a,\bar J=\sum \bar J^a t^a \\
+    \omega=\sum \omega^a t^a\\
+  \end{aligned}
+\end{equation}
+получаем
+\begin{equation}
+  \label{eq:86}
+  \delta_{\omega,\bar \omega}S=-\frac{1}{2\pi i}\oint dz \sum\omega^a J^a+\frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \bar J^a
+\end{equation}
+Мы также получили тождества Уорда $\delta\left< X\right>=\left<(\delta S)X\right>$
+\begin{equation}
+  \label{eq:87}
+  \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
+  \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
+\end{equation}
+Для токов из явного вида тока и формулы для преобразования $g$ имеем
+\begin{equation}
+  \label{eq:88}
+  \delta_{\omega}J=[\omega,J]-k\partial_z\omega,\quad \delta_{\omega}J^a=\sum i f_{abc}\omega^b J^c-k\partial_z\omega^a
+\end{equation}
+Если это подставить в тождество Уорда, то получаем операторное разложение для токов, которое имеет
+вид 
+\begin{equation}
+  \label{eq:89}
+  J^a(z) J^b(w) \sim \frac{k\delta_{ab}}{(z-w)^2}+\sum i f_{abc}\frac{J^c(w)}{(z-w)}
+\end{equation}
+Раскладывая токи в ряд, получаем
+\begin{equation}
+  \label{eq:90}
+  \begin{aligned}
+    J^a(z)=\sum_{n\in \mathbb Z}z^{n-1}J^a_n\\
+    \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}
+  \end{aligned}
+\end{equation}
+Теперь мы видим, что компоненты токов образуют аффинную алгебру Ли $\hat g$.
+
+Тензор энергии-импульса вводится при помощи конструкции Сугавары как сумма нормально упорядоченных компонент токов
+\begin{equation}
+  \label{eq:102}
+  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
+\end{equation}
+Здесь $h^v$ - дуальное число Кокстера. $h^v=\sum_i \alpha_i^v +1=\frac{1}{2}(\Theta,\Theta+2\rho)$,
+а нормальное упорядочение вводится следующим образом: 
+\begin{equation}
+  \label{eq:12}
+  N(AB)(w)=\frac{1}{2\pi i}\oint\frac{dz}{z-w}A(z)B(w)
+\end{equation}
+
+Тензор энергии-импульса можно разложить на моды $L_n$
+\begin{equation}
+  \label{eq:91}
+  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
+\end{equation}
+Тогда коммутационные соотношения для мод $L_n$ имеют вид
+\begin{equation}
+  \label{eq:92}
+  \begin{aligned}
+    \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
+    c=\frac{k\;\mathrm{dim}g}{k+h^v}\\
+    \left[L_n,J^a_m\right]=-mJ^a_{n+m}.
+  \end{aligned}
+\end{equation}
+
+Таким образом, конструкция Сугавары --- это способ вложения алгебры Вирасоро в универсальную обертывающую аффинной алгебры Ли $\hat{g}$
+
+Полная киральная алгебра модели Весса-Зумино-Виттена равна полупрямому произведению $Vir\ltimes \hat g$
+
+Примарными оказываются поля, которые преобразуются ковариантно под действием $G(z)\times G(\bar z)$,
+как $g(z,\bar z)$. В терминах операторного разложения это свойство переформулируется следующим
+образом:
+\begin{equation}
+  \label{eq:84}
+  \begin{aligned}
+    J^a(z)g(w,\bar w)\sim \frac{-t^a g(w,\bar w)}{(z-w)}\\
+    \bar J^a(z)g(w,\bar w)\sim \frac{ g(w,\bar w)t^a}{(z-w)}
+  \end{aligned}
+\end{equation}
+Любое поле $\phi_{\lambda,\mu}$, преобразующееся ковариантно по отношению к некоторому
+представлению, заданному весом $\lambda$ в голоморфном секторе и весом $\mu$ в антиголоморфном,
+является примарным полем WZW-модели.
+
+В модах это свойство записывается в виде
+\begin{equation}
+  \label{eq:93}
+  \begin{aligned}
+    & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
+    & (J^a_n\phi_{\lambda})=0\quad \mbox{для}\; n>0\\
+  \end{aligned}
+\end{equation}
+Мы можем сопоставить состояние $\left|\phi_{\lambda}\right>$ полю $\phi_{\lambda}$
+  \begin{equation}
+    \label{eq:94}
+    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
+  \end{equation}
+Тогда условия (\ref{eq:93}) для примарных полей дают
+\begin{equation}
+  \label{eq:95}
+  \begin{aligned}
+    & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
+    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{для}\; n>0 \\
+  \end{aligned}
+\end{equation}
+Все вторичные состояния имеют вид
+\begin{equation}
+  \label{eq:97}
+  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
+\end{equation}
+
+Легко видеть, что действие генераторов алгебры Вирасоро на примарные поля имеет вид
+\begin{equation}
+  \label{eq:96}
+  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
+\end{equation}
+Здесь использовано явное выражение для собственных значений квадратичного оператора Казимира.
+
+Примарные поля преобразуются  интегрируемыми конечномерными представлениями, а бесконечномерные и
+неинтегрируемые поля зануляют корреляционные функции.
+В WZW-моделях примарные поля
+принадлежат тензорному произведению неприводимых представлений аффинной алгебры, так как есть
+голоморфный и антиголоморфный сектора.
+
+\subsection{Конформные вложения и модулярно-инвариантные статсуммы}
+\label{sec:modular-invariance}
+
+При изучении конформной теории поля на плоскости или на сфере 
+голоморфный и антиголоморфный сектора можно рассматривать независимо. 
+Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть
+определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать
+взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно) чтобы теория была определена на торе.
+
+(Нарисовать картинку штанов).
+
+В теории критического поведения конформная инвариантность имеет место только в критической точке,
+где голоморфный и антиголоморфный сектора расцеплены. Но вблизи критической точки эти сектора должны
+быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве
+параметров, то эта связь должна сохраняться и в критической точке. Физический спектр теории должен
+плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного
+сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической
+точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния. Здесь
+естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории
+на торе.
+
+%% Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
+%% Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
+%% выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
+%% вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
+%% обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
+%% параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
+%% Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
+%% параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
+%% статсумма дается следом оператора сдвига в степени $m$:
+%% \begin{equation}
+%%   \label{eq:6}
+%%   Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
+%% \end{equation}
+%% Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
+%% конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
+%% $H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
+%% $L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
+%% $P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
+%% можно записать в виде
+%% \begin{equation}
+%%   \label{eq:7}
+%%   \begin{split}
+%%       Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
+%%       L_0)\}\\
+%%       =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
+%%   \end{split}
+%% \end{equation}
+%% Или, если ввести $q=\exp 2\pi i \tau$
+%% \begin{equation}
+%%   \label{eq:2}
+%%   Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
+%% \end{equation}
+%% Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
+%% 
+%% Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
+%% эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
+%% 
+Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
+модулярной инвариантности статсуммы.
+
+При помощи конформных преобразований можно перейти к таким координатам, в которых соотношения
+эквивалентности для тора (граничные условия) записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
+$\mathbb{C}$.
+%% 
+%% Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
+%% конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
+%% $SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
+%% \begin{equation}
+%%   \label{eq:99} A=
+%%   \begin{pmatrix} a & b\\ c & d
+%%   \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+%% \end{equation}
+%% и матрицы $A$ и $-A$ действуют одинаково на $\tau$
+%% \begin{equation}
+%%   \label{eq:100} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+%% \end{equation}
+%% $\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
+%% модулярной группой.
+%% 
+Конформная теория поля задаётся примарными полями $\Phi_a$ с конформными размерностями $\Delta_a$.
+
+Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
+произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
+представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсумма на торе
+(\ref{eq:2}) может быть записана в виде
+\begin{equation}
+  \label{eq:9}
+    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
+\end{equation}
+где $\chi_j$ --- нормализованный характер представления $\mathcal{H}_j$,
+\begin{equation}
+  \label{eq:5} \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i
+\tau}
+\end{equation}
+
+Характеры переходят друг в друга при модулярных преобразованиях:
+\begin{equation}
+  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
+\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
+\end{equation}
+где $S$ и $T$ --- постоянные матрицы.
+
+Для WZW-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$. Тогда
+\begin{equation}
+  \label{eq:6} \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi}
+L_{\hat \lambda}\otimes L_{\hat \xi}
+\end{equation}
+
+Коэффициенты ветвления для вложения аффинной подалгебры Ли в аффинную алгебру можно использовать для
+построения модулярно-инвариантной статсуммы в соответствующей WZW-модели. Когда рассматривается
+теория на торе,  набор физически допустимых полей ограничен требованиями модулярной инвариантности.
+
+Простейший модулярный инвариант можно записать следующим образом:
+\begin{equation}
+  \label{eq:34}
+   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
+\end{equation}
+Здесь суммирование ведется по всем конформным семействам (то есть по всем представлениям алгебры
+$\mathfrak{a}$).
+
+Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует
+алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно. (Я сейчас поясню, что это
+значит).
+
+Представления алгебры можно рассматривать как сумму представлений подалгебры.
+
+Если мы рассмотрим редукцию характеров аффинной алгебры
+\begin{equation}
+  \label{eq:8}
+   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
+\end{equation}
+и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится. То есть из
+диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый не диагональный инвариант для
+подалгебры $\mathfrak{a}$. Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
+ней конформная инвариантность.
+
+Пусть $J^{a_j}_{-n_j}$ и $\tilde{J}^{a'_j}_{-n_j}$ --- понижающие операторы алгебр  $\mathfrak{g}$ и
+$\mathfrak{a}\subset\mathfrak{g}$.  $\pi_{\mathfrak{a}}$ --- проекционный оператор
+$\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$. В теории, связанной с  $\mathfrak{g}$
+с вакуумом $\left|\lambda\right>$ будут следующие состояния:
+\begin{equation}
+  \label{eq:109}
+  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+\end{equation}
+Вакуум $\mathfrak{g}$-инвариантен, то есть $J_0^a\left|0\right>=0$. При проекции на подалгебру
+$\mathfrak{a}$ состояния примут вид
+\begin{equation}
+  \label{eq:110}
+  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
+\end{equation}
+Из $\mathfrak{g}$-ивариантности вакуума следует его $\mathfrak{a}$-инвариантность, но для тензора
+энергии-импульса в общем случае это не так. Поэтому тензор энергии-импульса большей теории должен
+состоять только из генераторов $\tilde{J}$. Тогда $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow
+c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению
+\begin{equation}
+  \label{eq:111}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
+\end{equation}
+Здесь $x_e$ --- индекс вложения, а  $g$, $a$ --- дуальные числа Кокстера, которые характеризуют алгебры.
+
+Можно показать, что только для представлений уровня 1 это равенство удовлетворяется. То есть класс
+конформных вложений не слишком широк и существует полная их классификация. Кроме того, для
+конформных вложений существуют специальные методы разложения представлений.
+
+Модулярная инвариантность статсуммы для полей, принадлежащих представлениям алгебры  $\mathfrak{g}$,
+сохраняется при проекции на подалгебру $\mathfrak{a}$. Если все представления $\mathfrak{g}$ в теории
+удовлетворяют описанным требованиям, то при проекции мы получаем конформную теорию поля.
+
+Существует теорема о том, что для конформного вложения  $\mathfrak{a}\subset\mathfrak{g}$ только
+конечное число коэффициентов ветвления отлично от нуля. Поэтому после того, как мы разложили все
+представления $\mathfrak{g}$ мы подставляем результаты в выражение для статсуммы и получаем
+модулярно-инвариантную статсумму для вложенной теории. Такая статсумма уже не будет иметь
+диагональный вид:
+\begin{equation}
+  \label{eq:36}
+   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
+\end{equation}
+Наша работа посвящена разработке общего метода редукции представлений аффинных алгебр Ли, поэтому
+случай конформных вложений --- лишь один из примеров применения нашего метода. Однако в этом случае
+физический смысл наиболее очевиден.
+
+Теперь я перейду к краткому объяснению метода и примерам вычислений.
+
+\section{Рекуррентные соотношения для коэффициентов ветвления}
+\label{sec:branching}
+
+Ранее для вычисления коэффициентов ветвления был предложен способ, основанный на преобразовании
+формулы Вейля-Каца для характеров представлений аффинных алгебр Ли в рекуррентное соотношение для
+коэффициентов ветвления. Однако исходный алгоритм не работал для не максимальных вложений. В данной
+работе была решена данная проблема и предложено обобщение рекуррентных соотношений.
+
+Используя формулу Вейля-Каца мы выделяем два набора элементов в весовом пространстве. Первый набор $\Gamma$
+называется веером и описывает вложение подалгебры $\mathfrak{a}$ в алгебру $\mathfrak{g}$. Веер
+универсален, в том смысле, что он может быть использован для разложения любого из представлений.
+Другой набор элементов весового пространства $\Psi ^{\left( \mu \right) }$ называется набором
+аномальных весов. Он описывает раскладываемое представление без явного его построения.
+
+После этого процесс вычисления коэффициентов ветвления можно реализовать при помощи следующей
+рекуррентной формулы:
+\begin{equation}
+  \label{eq:1}
+  \begin{array}{c}
+      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
+\left.
++\sum_{\gamma \in
+\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
++\gamma }^{\left( \mu \right) }\right)
+
+  \end{array}
+\end{equation}
+Здесь $\mathfrak{a}_{\bot}$ --- это подалгебра, ``натянутая'' на корни $\mathfrak{g}$, ортогональные
+к корневой системе подалгебры  $\mathfrak{a}$, $W_{\bot}$ --- соответствующая этим корням группа Вейля,
+$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ --- веер --- набор весов в разложении знаменателя $$\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
+(1-e^{-\pi_{\mathfrak{a}}(\alpha)})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\pi_{\mathfrak{a}}(\alpha))}$$, а $s(\gamma)$ ---
+коэффициент при  $e^{\gamma}$ в этом разложении.
+
+Набор аномальных весов $\Psi^{(\mu)}$ дает член с $\delta$-символом.
+
+Это рекуррентное соотношение позволяет нам сформулировать следующий алгоритм вычисления
+коэффициентов ветвления, который осуществляется без явного построения исходного представления или
+представлений, входящих в разложение.
+\begin{enumerate}
+\item Построить наборы положительных корней $\Delta^{+}$ и $\Delta_{\mathfrak{a}}^{+}$.
+\item Выбрать те положительные корни $\alpha\in \Delta^{+}$, которые ортогональны корневому
+  подпространству  $\mathfrak{a}$ и собрать их в набор $\Delta^{+}_{\bot}$.
+\item Построить множество весов $\Gamma$, которое мы называем ``веером''.
+\item Найти множество $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$
+  аномальных весов представления $L^{(\mu)}_{\mathfrak{g}}$.
+\item Выбрать в нем веса $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in
+    \bar{C}_{\mathfrak{a}_{\bot}} \right\}$. Это можно легко сделать, так как у нас есть набор
+  $\Delta^{+}_{\bot}$ и мы можем проверить, лежит ли вес $\pi_{\mathfrak{a}_{\bot}}\lambda$ в
+  главной камере Вейля алгебры $\mathfrak{a}_{\bot}$. Для этого все скалярные произведения этого
+  веса $\lambda$ с корнями из  $\Delta^{+}_{\bot}$ должны быть неотрицательны.
+\item Далее для весов $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in
+  \bar{C}_{\mathfrak{a}_{\bot}}$ мы вычисляем размерность соответствующих представлений
+  $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$
+  при помощи формулы Вейля и набора $\Delta^{+}_{\bot}$.
+\item Далее рекуррентно вычисляются аномальные коэффициенты ветвления, а внутри главной камеры Вейля
+  алгебры $\mathfrak{a}$ аномальные коэффициенты совпадают с настоящими коэффициентами ветвления.
+\end{enumerate}
+
+Сейчас я поясню всю процедуру на примере редукции представления простой алгебры $B_2$ ($so(5)$) на
+подалгебру $A_1$ ($so(3)$), а потом расскажу про аффинные алгебры Ли.
+
+\subsection{Примеры}
+\label{sec:examples}
+
+Я начну с примера вычисления в случае конечномерных простых алгебр Ли, так как его легко нарисовать.
+
+Рассмотрим регулярное вложение  $A_1$ в $B_2$. Вот на рисунке корневая системы алгебры $B_2=so(5)$.
+Корень  $\beta$ вложенной алгебры $A_1$ равен $\alpha_1+2\alpha_2$.
+
+Функция $s(\gamma)$ и веер $\Gamma$ строятся исходя из корневых систем $\mathfrak{g}, \mathfrak{a}$
+$\frac{\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}_{\mathfrak{g}}\setminus
+      \Delta^{+}_{\mathfrak{a}}} \left(1-e^{-\alpha}\right) \right)}{\prod_{\beta\in
+    \Delta^{+}_{\mathfrak{a}}} \left(1-e^{-\beta}\right) }$ и получается
+\begin{equation}
+  \label{eq:22}
+  (1,2),\; (2,-1)
+\end{equation}
+Вторая компонента - значение $s(\gamma)$.
+
+Опишем редукцию первого фундаментального представления $B_2$. Старший вес изображен на рисунке.
+\begin{figure}[ph]
+  \noindent\centering{
+    \includegraphics[width=90mm]{B2_A1}
+  }
+  \caption{Регулярное вложение $A_1$ в $B_2$}
+  \label{fig:B2_A1}
+\end{figure}
+Вот набор аномальных весов $\omega(\mu+\rho)-\rho,\; \omega\in W$ с соответствующими четностями
+отражений $\epsilon(\omega)$.
+Теперь мы факторизуем группу Вейля $W$ по подгруппе $W_{\bot}=\left\{\omega_1\right\}$. Получаем
+следующий набор весов и размерностей представлений  $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$:
+\begin{figure}[h!tb]
+  \noindent\centering{
+    \includegraphics[width=90mm]{B2_A1_2}
+  }
+  \caption{Аномальные веса и соответствующие $\mathfrak{a}_{\bot}=A_1$-модули}
+  \label{fig:B2_A1_2}
+\end{figure}
+
+Затем мы проектируем эти веса и размерности на корневое подпространство подалгебры
+$\mathfrak{a}=A_1$ и получаем следующие аномальные веса и их кратности:
+\begin{equation}
+  \label{eq:25}
+  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
+\end{equation}
+
+Аномальный коэффициент ветвления  $k^{(1,0)}_{1}=2$, для коэффициента $k^{(1,0)}_{0}$ из
+рекуррентного соотношения получаем
+\begin{equation}
+  \label{eq:23}
+  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1
+\end{equation}
+
+В работе рассмотрено большое число примеров вложений аффинных алгебр Ли. На самом деле мы написали
+программу, которая может строить такие примеры автоматически для алгебр Ли не слишком большого
+ранга.
+
+Я сейчас покажу результаты применения нашего алгоритма для одного из примеров конформных вложений.
+
+Рассмотрим такое вложение $\mathfrak{a}\subset \mathfrak{g}$, где
+$\mathfrak{a}=\hat{A_1}\oplus \hat{A_1}$, а $\mathfrak{g}= \hat{A_3}$. Это
+вложение является аффинным расширением специального вложения конечномерных алгебр Ли $A_1\oplus
+A_1\subset A3$. ($su(2)\oplus su(2)\subset su(4)$).
+\begin{comment}
+ Это специальное вложение строится следующим образом: берем четырехмерное
+представление $A_1\oplus A_1$ со старшим весом $(1,1)$. Вот веса этого представления
+\ref{fig:A_1+A_1_to_A3}, их координаты в базисе фундаментальных весов: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
+
+\begin{figure}[h]
+  \begin{multicols}{2}
+    \hfill
+    \includegraphics[width=50mm]{A_1+A_1_to_A3}
+    \hfill
+    \caption{Представление для специального вложения $A_1\oplus A_1\subset A3$}
+    \label{fig:A_1+A_1_to_A3}
+    \hfill
+    \includegraphics[width=50mm]{A1+A1-A3}
+    \hfill
+    \caption{Вложенные корни $A_1\oplus A_1\subset A3$}
+    \label{fig:A1+A1-A3}
+  \end{multicols}
+\end{figure}
+
+Тогда матричные элементы представления генераторов подалгебры Картана $b_1,b_2$ в базисе Вейля
+даются выражениями
+\begin{equation}
+  d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right),
+\end{equation}
+так что $d(b_1)=\mathrm{diag}(1,-1,1,-1),\;
+  d(b_2)=\mathrm{diag}(1,1,-1,-1).$
+\end{comment}
+Вложенные корни $\alpha_1,\alpha_2$ подалгебры $A_1\oplus A_1$
+выражаются через корни $\tilde{\alpha}_i$ алгебры  $A_3$
+\begin{equation}
+  \label{eq:37}
+  \begin{array}{l}
+     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
+     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
+  \end{array}
+\end{equation}
+\begin{comment}
+Они изображены на рисунке \ref{fig:A1+A1-A3}.
+\end{comment}
+
+Вложение имеет индексы  $(2,2)$ и является конформным, так как $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
+
+Для построения модулярно-инвариантной статсуммы нам нужно знать редукцию фундаментальных
+представлений $\widehat{su(4)}$. Фундаментальные веса имеют следующие координаты в ортогональном базисе
+\begin{equation}
+  \begin{array}{lll}
+     \omega_0 & = & (0,0,0,0;1;0)\\
+     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
+     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
+     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
+  \end{array}
+\end{equation}
+
+Множества положительных корней  $\Delta^{+}$ и $\Delta_{\mathfrak{a}}^{+}$:
+\begin{equation}
+  \label{eq:38}
+  \begin{array}{lll}
+    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
+    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{с кратностью}\; 3;\; n=1,2,\dots,\right\}\\
+    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm
+    \alpha_2-n\delta;\; -n\delta\; \mbox{с кратностью} \; 2;\; n=1,2,\dots\}\\
+  \end{array}
+\end{equation}
+
+Набор $\Delta^{+}_{\bot}$ пуст.
+Веер  $\Gamma _{\frak{a}\subset \frak{g}}$ показан на рисунке \ref{fig:A1+A1-A3_fan}. Конечные координаты
+даны в базисе фундаментальных весов $A_1 \oplus A_1$. Элемент $\gamma$ обозначен крестом, если
+$s(\gamma)=1$ и кругом, если $s(\gamma)=-1$.
+\begin{figure}[h!tb]
+  \includegraphics[width=150mm]{A1+A1-A3_fan}
+  \caption{Веер для специального вложения $\hat A_1\oplus\hat A_1\subset\hat A_3$}
+  \label{fig:A1+A1-A3_fan}
+\end{figure}
+
+Мы ограничимся вычислениями до пятого грейда.
+\begin{figure}[h!tb]
+  \includegraphics[width=170mm]{A1+A1-A3_anom}
+  \caption{Спроектированные аномальные веса $L^{\omega_2}_{A_3}$}
+  \label{fig:A1+A1-A3_anom}
+\end{figure}
+
+Множество аномальных весов  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in
+  W\right\}$ представления алгебры $\hat{A}_3$ состоит из 192 элементов, их проекции
+$\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ показаны на рисунке  \ref{fig:A1+A1-A3_anom}
+для $\mu=\omega_2=(0,1,0;1;0)$.
+
+Аналогичные картинки для $\omega_0, \omega_1,\omega_3$ я не показываю.
+
+Аномальные коэффициенты ветвления для представления  $L^{(\omega_2)}$ вычислены при помощи
+рекуррентных соотношений и показаны на рисунке \ref{fig:A1+A1-A3_branching}. 
+\begin{figure}[h!tb]
+  \hspace*{-2cm}\includegraphics[width=180mm]{A1+A1-A3_branching}
+  \caption{Аномальные коэффициенты ветвления для представления $L^{(0,1,0;1;0)}_{A_3}$}
+  \label{fig:A1+A1-A3_branching}
+\end{figure}
+
+Получаются следующие правила ветвления:
+ \begin{equation}
+   \label{eq:39}
+   \begin{array}{ll}
+     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
+     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
+     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
+     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
+   \end{array}
+ \end{equation}
+
+В результате мы получаем модулярно-инвариантную статсумму для WZW-модели с киральной алгеброй $\hat{A}_1\oplus \hat{A}_1$.
+\begin{multline}
+  \label{eq:40}
+  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
+  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
+\end{multline}
+
+\section{Заключение. Обсуждение перспектив.}
+\label{sec:conlusion}
+
+Функции ветвления играют важную роль в coset-моделях. Эти модели строятся путем факторизации
+WZW-модели с алгеброй $\mathfrak{g}$ по отношению к модели с подалгеброй $\mathfrak{a}$. Тут функции
+ветвления фактически описывают состояния в системе.
+
+Недавно мы заметили, что струнные функции, которые описывают представления, функции ветвления,
+описывающие редукцию представлений и функции слияния, которые описывают разложение тензорных
+произведений представлений на неприводимые, допускают построение дуальных систем функций. Эти
+дуальные функции могут быть построены просто из анализа соответствующих групп и камер Вейля. 
+Задача явного построения струнных функций или функций ветвления тогда сведется к обращению матрицы.
+Явный вид функций ветвления полезен при изучении coset-моделей. Кроме того, многие
+известные результаты могут быть перенесены на дуальные функции, например, результаты Каца о модулярных свойствах
+струнных функций и функций ветвления.
+В настоящее время мы начали исследовать эти системы дуальных функций.
+
+Среди других возможных приложений полученных методов можно отметить также приложения в интегрируемых
+цепочках, а также в приложения дуальных функций теории модулярных форм.
+
 \section{Coset-модели}
@@
 
+\begin{abstract}
+  Schramm-Loewner evolution appears naturally as the scaling limit of interfaces in lattice models at critical point.
+Critical behavior of these models can be described by minimal models of conformal field theory.
+
+  We generalize Schramm-Loewner evolution with additional Brownian motion on Lie group to the case of direct product of two groups.
+We then study connection between SLE description of critical behavior with coset models of conformal field theory.
+In order to be consistent such construction should give minimal models for certain choice of groups.
+
+%%    SLE with additional Brownian motion on Lie group $G$ was proposed as generalization to WZNW models of CFT.
+Martingale property of SLE observables is related to Virasoro null vector conditions for CFT fields and KZ-equations for correlation functions.
+%%  
+%%    Minimal models can be obtained from WZNW models by coset construction.
+Then it is natural to study SLE with additional Brownian motion on coset space $G/H$.
+We discuss algebraic properties of coset fields and correlation functions which correspond to SLE observables.
+\end{abstract}
+
+\section{Introduction}
+Schramm-Loewner evolution, introduced by Oded Schramm in papers \cite{schramm2000scaling} is
+
+The connection of SLE with CFT was studied in papers \cite{bauer2004conformal,bauer2004cfts,bauer2003sle,bauer2002sle}.
+
+Reviews \cite{rohde2005basic}, \cite{bauer20062d}, \cite{Cardy:2005kh}.
+
+SLE and conformal field theories with additional symmetries \cite{alekseev2010sle}, \cite{santachiara2008sle,picco2008numerical}, \cite{bettelheim2005stochastic}, \cite{Rasmussen:2004xr}.
+
+\subsection{Schramm-Loewner evolution}
+To remind of Schramm-Loewner evolution we first describe simple example.
+
+Consider Ising model on triangular lattice on upper half plane (see Fig.
+\ref{fig:sle}).
+We impose following boundary condition: all spins are down on one half of the boundary and all spins are up on another half.
+Then in any configuration we get an interface delimiting two clusters and connecting zero and infinity.
+
+\begin{figure}[h]
+  \centering{
+    \includegraphics[height=25mm]{explore}
+    \caption{SLE -- continuous limit of interfaces}}
+  \label{fig:sle}
+\end{figure}
+
+Next we consider continuous limit of lattice model.
+Interface in random configuration of the model tends to random curve.
+We can think of this curve as of trace of stochastic process which satisfy some stochastic equation.
+
+In papers [Smirnov, Schramm ... ] it was shown that this equation is
+\begin{equation*}
+  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} \quad \text{or} \quad       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}
+\end{equation*}
+The stochastic process which satisfy this equation is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.
+
+Here $g_{t}(z)$ is a conformal map from $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$ to $\mathbb{H}$ (see Fig. \ref{fig:sle2}).
+\begin{figure}[h]
+  \centering{
+    \includegraphics[width=50mm]{loewner}
+    \caption{Conformal map}}
+  \label{fig:sle2}
+\end{figure}
+
+Schramm-Loewner evolution provides conformally-invariant probability measure on trajectories $\gamma_{t}$ in $\mathbb{H}$.
+
+\subsection{Correspondence between SLE and minimal models of CFT}
+
+Now we can look at the observables in the presence of SLE trace.
+Expectation value of lattice observable on upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace up to some time $t$ multiplied by the probability of this trajectory.
+
+Consider lattice observable $\mathcal{O}$, then it expectation value can be calculated as
+\begin{equation*}
+  \prec \mathcal{O} \succ_{\mathbb{H}}=\mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=\sum_{\gamma_{t}} P\left[C_{\gamma_{t}}\right] \prec \mathcal{O} \succ_{\gamma_{t}}
+\end{equation*}
+Since lattice observable  $\prec \mathcal{O} \succ_{\mathbb{H}}$ does not depend on $t$, hence $\prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale.
+
+In continuous limit lattice observable tends to CFT correlation function. Since we consider the theory with the boundary, CFT correlation function has following form:
+\begin{equation*}
+  \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
+  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}=
+  \frac{\left< ^{g_{t}}\mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
+\end{equation*}
+We assume that $\mathcal{F}$ contains some set of primary fields $\phi_{\lambda_{i}}$ with conformal weights $\lambda_{i}$.
+Also we have boundary condition changing operators  $\phi$ at the tip of SLE trace and in the infinity.
+We can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite this expression in upper half plane:
+
+\begin{equation}
+  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
+  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
+  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
+  \label{eq:1}
+\end{equation}
+
+Now we want to consider evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
+\begin{equation*}
+  -\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}.
+\end{equation*}
+For transformation of primary fields $\phi_{\lambda_{i}}$ we have 
+\begin{equation}
+  \label{eq:2}
+  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\phi_{\lambda_{i}}(w_{i}) 
+\end{equation}
+We denote generator of this transform by $\mathcal{G}_{i}$.
+
+Continuous limit in critical point leads to CFT correlation function
+
+Now for expectation value of martingale we have this expression.
+\begin{equation*}
+  \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=    \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t+dt}}\right], \quad \mathbb{E}\left[d \prec\mathcal{O}\succ_{\gamma_{t}}\right]=0
+\end{equation*}
+
+Now we use Ito calculus to calculate increment of our correlation function. It should be zero so we get the equation:
+\begin{equation}
+  \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{-h_{i}}\right)\mathbb{E}\left[d 
+    \mathcal{F}_{\mathbb{H}_{t}}\right]=\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\mathbb{E}\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
+      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}
+\label{eq:8}
+\end{equation}
+Then use explicit form of conformal map and obtain
+\begin{equation*}
+  \left( \sum_{i}\left[-\frac{2h_{i}}{w_{i}^{2}} +\frac{2}{w_{i}}\partial_{w_{i}}\right]+\frac{\kappa}{2}\sum_{i,j}\partial_{w_{i}} \partial_{w_{j}}\right)\mathcal{F}(\left\{z_{i}\right\})=0
+\end{equation*}
+
+We can rewrite it as the necessary condition on b.c.c. operator $\phi$:
+\begin{equation*}
+  (L_{-2}-\frac{\kappa}{2}L_{-1}^{2})\phi=0 \Longrightarrow \phi \left|0\right>  \text{has level 2 null state}, \phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}
+\end{equation*}
+We can see that it can be rewritten as the action of Virasoro generators.
+Since we have arbitrary observable, this equation is equivalent to the requirement for boundary condition changing operator to have level two null state.
+In case of minimal model we can see that boundary condition chaining operator is primary field $\phi_{1,2}$ or $\phi_{2,1}$.
+
+\section{SLE and WZNW models}
+\label{sec:sle-wzw-models}
+Now we want to generalize this analysis to rational conformal field theories. First we consider Wess-Zumino-Novikov-Witten model.
+\subsection{WZNW models}
+
+ The action for this model can be written in terms of map $g:\mathbb{C}\cup \{\infty\}\sim S^{2}\to G$ from complex plane with infinity or two-sphere to some Lie group $G$:
+\begin{multline}
+  S=-\frac{k}{8\pi}\int d^2x\; \mathcal{K} (g^{-1}\partial^{\mu}g, g^{-1} \partial_{\mu}g)  
+  \\
+  - \frac{k }{24\pi^{2}} \int_{B}\epsilon_{ijk} \mathcal{K}\left(
+    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i},\left[
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right]\right) d^3y
+\end{multline}
+The first term is just non-linear sigma-model.
+
+ Here $\mathcal{K}$ is Killing form on Lie algebra $\gf$ of Lie group $G$.
+The second term is written in terms of continuation from two-sphere $S^{2}$ to three-dimensional manifold $B$ which has two-sphere as the boundary.
+Since this continuation is non-unique we get the requirement for $k$ to be integer.
+
+Currents of this model have following form:
+  \begin{eqnarray}
+    J(z)= -k \partial_zg g^{-1}
+    \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
+  \end{eqnarray}
+
+Model possess gauge invariance under gauge transformations:
+  \begin{equation*}
+    g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z),
+  \end{equation*}
+  where $\Omega,\;\bar \Omega \in G$.
+Here $\Omega$ and $\bar \Omega$ are independent.
+
+If we consider infinitesimal gauge transformation $\Omega=1+\omega$ we get Ward identities:
+  \begin{equation}
+    \label{eq:87}
+    \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
+    \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
+  \end{equation}
+
+ Then we can get operator product expansion for currents. 
+ \begin{equation}
+   \label{eq:3}
+   <J\phi>\sim \dots
+ \end{equation}
+
+If we expand currents to modes
+\begin{equation*}
+  J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n 
+\end{equation*}
+and use operator product expansion \eqref{eq:3} we get commutation relations of affine Lie algebra $\gfh$:
+\begin{equation}
+  \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0} 
+\end{equation}
+
+This model has conformal invariance which can be seen from 
+Sugawara construction. This is way to embed Virasoro algebra into the universal enveloping algebra of affine Lie algebra $\gfh$ ($Vir\subset U(\gfh)$):
+\begin{equation}
+  \label{eq:4}
+  L_n=\frac{1}{2(k+h^v)}\sum\limits_a\sum\limits_m:J^a_m J^a_{n-m}:
+\end{equation}
+
+Full chiral algebra of the model is semidirect product of affine and Virasoro algebra $\gfh \ltimes Vir$.
+
+Its commutation relations are
+  \begin{equation}
+    \label{eq:92}
+    \begin{aligned}
+      \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
+      \left[L_n,J^a_m\right]=-mJ^a_{n+m}
+    \end{aligned}
+  \end{equation}
+
+Primary fields  $\phi_{\lambda}$ are labeled by highest weights of affine Lie algebra representations. Here we see how Virasoro and affine Lie algebra generators act on primary fields:
+  \begin{equation*}
+    \begin{aligned}
+      & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>  \quad    J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
+      & L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>=h_{\lambda} \left|\phi_{\lambda}\right>
+    \end{aligned}
+  \end{equation*}
+
+\subsection{SLE and WZNW models}
+Now we want to study Schramm-Loewner evolution in WZNW-models.
+
+Similarly to minimal models we consider observable
+\begin{equation*}
+  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
+  \frac{\left<\phi_{\Lambda}(z_{t}) \phi_{\lambda_1}(z_{1}) \dots \phi_{\lambda_n}(z_{n}) \phi_{\lambda^{*}_1}(\bar z_{1}) \dots \phi_{\lambda^{*}_n}(\bar z_{n})
+      \phi_{\Lambda^{*}}(\infty)\right>}{\left<\phi_{\Lambda}(z_{t})\phi_{\Lambda^{*}}(\infty)\right>}
+\end{equation*}
+Again we can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite it on the whole upper half-plane. 
+\begin{equation*}
+  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
+  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
+  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
+\end{equation*}
+
+Consider evolution from $t$ to $t+dt$.
+First factor gives us $-\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}$.
+
+ For fields we have
+\begin{equation*}
+  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i})
+\end{equation*}
+When we consider fields we need to add random gauge transformation (random motion in $G$) to stochastic evolution \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}:
+\begin{equation*}
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)
+\end{equation*}
+Since we have boundary we are working with boundary CFT so we have only half of gauge transformations due to Cardy conditions.
+
+\subsection{SLE martingales in WZNW models}
+We use Ito calculus to get the equation from martingale condition:
+\begin{equation*}
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0
+\end{equation*}
+\begin{equation*}
+  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{\lambda_{i}}}{(w_{i}-z)^{n}}-\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right);\quad \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}}
+\end{equation*}
+Again we can rewrite it as algebraic requirement for  field  which 
+correspond to boundary condition changing operator.
+\begin{equation*}
+  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
+\end{equation*}
+is level two null state and if we act on this state with raising operators we should get zero.
+\begin{equation*}
+  J^{a}_{1} \left|\psi\right>=0, J^{a}_{2}\left|\psi\right>=0.
+\end{equation*}
+ We use commutation relations and get equations which connects parameters of random motion with level of affine Lie algebra representation.
+
+We can see that $\kappa+\tau h^{v}=4$ and it is possible to derive additional relations connecting $\kappa, \tau, k$:
+\begin{equation*}
+  \kappa=\frac{2(h^{v}-2k)}{2h_{\Lambda}h^{v}-k},\quad \tau=\frac{8 h_{\Lambda}-2}{2h_{\Lambda}h^{v}-k}  \quad\text{for}\; k\neq 2h_{\Lambda}h^{v}
+\end{equation*}
+ Also we get some constraints on possible boundary condition changing operators. 
+To get complete classification use Knizhnik-Zamolodchikov equations.
+
+\section{Coset models}
+\label{sec:coset-models}
+Now we want to generalize analysis of correspondence between SLE and CFT even further and study coset models of conformal field theory.
+
+\subsection{Gauged WZNW-models and coset construction}
+
+Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models. We add gauge fields  $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action:
+\begin{multline*}
+  S(g,A)=S_{WZNW}(g)+\\
+  \frac{k}{4\pi}\int d^{2}z \left(\mathcal{K}(A, g^{-1}\bar \partial g)-\mathcal{K}(\bar A, (\partial g ) g^{-1})+\mathcal{K}(A,g^{-1}\bar A g)-\mathcal{K}(A,\bar A)\right)
+\end{multline*}
+Now current is
+\begin{equation*}
+  J_{(\gf,\af)}=-k\partial g g^{-1} -k g A g^{-1}
+\end{equation*}
+
+From Ward identities we get following expression for the product of gauge field and primary fields:
+\begin{equation*}
+  \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{v}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
+\end{equation*}
+Here $h_{\af}^{v}$ is the dual Coxeter number of Lie algebra $\af$.
+
+Remember that for WZNW current we have OPE $J_{\gf}^{a}(z)\phi_{i}(w)\sim \frac{-t^{a}_{i}\phi(w)}{z-w}$,  so we see that algebraic structure is connected with the pair of algebras $\gf$ and $\af$, such that $\afh\subset\gfh$.
+
+Virasoro generators are given by difference of Sugawara expressions:
+\begin{equation*}
+  L_{n}=L_{n}^{\gf}-L_{n}^{\af}
+\end{equation*}
+
+\subsection{Primary fields}
+\label{sec:primary-fields}
+Primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra and subalgebra, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
+But some pairs are equivalent.
+This equivalence is given by the action of simple currents $(J,\tilde{J})$ such that their conformal weights are equal:  $h_{J}-h_{\tilde{J}}=0$.
+
+Conformal weight of primary field is equal to
+\begin{multline}
+  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^v)}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
+  \left|\phi_{\lambda}\right>=\\
+  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^v)}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^v)}\right)\left|\phi_{(\mu,\nu)}\right>
+\end{multline}
+
+%% So $G/A$-coset theory is related to $\gf\oplus \bar{\af}$-theory.
+
+It is possible to obtain analogues of KZ-equations:
+\begin{equation*}
+  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{v}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{v}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
+\end{equation*}
+
+\subsection{SLE on coset space}
+Consider Lie (semi-)simple group $G$ with Lie algebra $\gf$ and (semi-)simple subgroup $A\subset G$ with Lie algebra $\af\subset \gf$. 
+The simplest way to study SLE on $G/A$ coset space is to restrict random walk on group manifold to the coset space by the choice of basis in $\gf$.
+Assume that generators $\{J^{a};\; a=1\dots \mathrm{dim}\gf\}$ are chosen in such way that $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\; a=\mathrm{dim}\gf-\mathrm{dim}\af\dots \mathrm{dim}\gf\}$ are the generators of subalgebra $\af\subset \gf$.
+Now we can consider $\mathrm{dim}\gf-\mathrm{dim}\af$-dimensional Brownian motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \; d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\mathrm{dim}\gf-\mathrm{dim}\af$.
+
+Then for generator of field transformation we can write 
+\begin{equation}
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}\left(d \theta ^{a} t^{a}_{i}\right)\right)
+\label{eq:5}
+\end{equation}
+Substituting to equation \eqref{eq:8} we get martingale condition
+
+\begin{equation}
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0
+\label{eq:9}
+\end{equation}
+
+which can be rewritten as the requirement for
+\begin{equation}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}J^{a}_{-1}J^{a}_{-1}\right)\right) \phi_{\Lambda}
+\label{eq:10}
+\end{equation}
+to be level two null-field. Here primary field $\phi_{\Lambda}$ is indexed by the pair $\Lambda=(\mu,\nu)$ with the equivalence relations \ref{sec:primary-fields}.
+
+Consider the simplest possible example.
+Let $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$.
+Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
+The equation \eqref{eq:10} is now
+\begin{equation}
+  \label{eq:11}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{\Lambda}
+\end{equation}
+If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\; J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
+\begin{equation}
+ \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{\Lambda}
+\label{eq:12}
+\end{equation}
+which coincides with the equation for parafermionic fields introduced in paper \cite{santachiara2008sle}.
+
+Central charge in this case is equal to
+\begin{equation}
+  \label{eq:14}
+  c=\frac{2(k-1)}{k+2}
+\end{equation}
+
+Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
+\begin{equation}
+  \label{eq:13}
+  L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{\Lambda}=0\quad \Longrightarrow\quad  (3\kappa-8) h_{\Lambda}+\frac{2(k-1)}{k+2}+\tau k =0
+\end{equation}
+Another equation can be obtained by action of $L_{1}^{2}$
+\begin{equation}
+  \label{eq:15}
+  L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{\Lambda}=0
+\end{equation}
+or
+\begin{equation}
+  \label{eq:16}
+  \left(12 h_{\Lambda}+2\kappa h_{\Lambda} (2h_{\Lambda}+1) + 2 \tau J^{3}_{0}J^{3}_{0}\right) \phi_{\Lambda}=0
+\end{equation}
+
+Alternative approach is to study $\gf\oplus \af$ WZNW-model and then impose equivalence relations on the solutions. 
+So we need to generalize the analysis of \cite{alekseev2010sle} to the case of semisimple Lie algebras.
+
+From equation
+
+Now consider as an example $\frac{SU(2)_{k}\times SU(2)_{1}}{SU(2)_{k+1}}$ -- another coset realization for minimal unitary models.
+
+We get following relations on $\kappa,\tau$ and primary fields. So we see that the solutions at level $k$ are
+
+Now we need to impose equivalence relations.
+
+We get
+
+Consider gauge transformation in gauged WZNW model:
+\begin{eqnarray*}
+  \delta \phi_{i}=(\epsilon_{L}^{a} t^{a}_{i}+\epsilon^{b}_{R}\tilde{t}^{b})\phi_{i}\\
+  \delta A = -\partial \epsilon_{R}-[\epsilon_{R},A]
+\end{eqnarray*}
+Here $\epsilon_{L}, \epsilon_{R}$ are arbitrary holomorphic functions $\bar\partial\epsilon_{L,R}=0$. 
+For  $\gf\oplus \af$ WZNW-model we can write SLE generator of primary field transformation under stochastic evolution as
+\begin{equation*}
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)+\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
+\end{equation*}
+%% \begin{equation*}
+%%   \mathcal{G}_{i}^{L,R}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)\pm\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
+%% \end{equation*}
+
+and get martingale condition
+\begin{equation*}
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
+      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0
+\end{equation*}
+
+which can be rewritten as the requirement for
+\begin{equation*}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}
+\end{equation*}
+to be level two null-field.
+
+We can compare this result with the simplest possible coset model $su(2)/u(1)$ --  parafermion theory.
+
+\subsection{Semisimple Lie algebras and coset construction}
+\label{sec:semis-lie-algebr}
+
+It is well known that unitary minimal models with central charge $c=1-\frac{6}{m(m+1)}$ can be obtained from coset construction starting with $su(2)_{m}\oplus su(2)_{1}$ WZW-model and factorizing it by $su(2)_{m+1}$.
+Here lower index represents level of affine Lie algebra representation.
+
+In this case the dimension of Lie algebra $\gf=su(s)\oplus su(2)$ is 6, dual Coxeter number $h^{v}=2+2=4$.
+
+\begin{equation}
+  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
+\label{eq:6}
+\end{equation}
+
+For semisimple Lie algebra $\gf=\gf_{1}+\gf_{2}$ with generators $J^{a}$ and $\tilde{J}^{b}$ correspondingly we can more explicitly write the relation \eqref{eq:6} as
+
+\begin{equation*}
+  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\left(\sum_{a} J^{a}_{-1} J^{a}_{-1}+\sum_{b}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right) \right) \left|\phi_{\Lambda}\right>
+\end{equation*}
+
+This vector should be null vector of level two, so $L_{2}\left|\psi\right>=L_{1}\left|\psi\right>=0$. Then we get following algebraic relations for semisimple Lie algebra:
+\begin{equation}
+  \label{eq:7}
+  \left( 3\kappa h_{\Lambda} +\frac{1}{2} \tau (k_{1} \mathrm{dim} \gf_{1}+k_{2}\mathrm{dim} \gf_{2}) -8 h_{\Lambda} - c\right)\phi_{\Lambda}=0
+\end{equation}
+SLE and factorization by equivalence relations.
+
+\subsection{Parafermions}
+
+$\mathbb{Z}(N)$ parafermions are equivalent to $SU(2)_{N}/U(1)$ coset theory.
+
+It is well-known that parafermionic field can be written as product of $su(2)$-primary field and vertex operator of bosonic field. 
+\begin{equation*}
+  \Phi^{j}=\phi_{j}(z) \exp\left( -i \frac{j}{\sqrt{N}}\phi(z)\right)
+\end{equation*}
+where $\phi_{j}(z)$ is field of $SU(2)$-WZNW model with spin $j$, $\phi(z)$ -- $U(1)$ bosonic field.
+
+For parafermionic current we have
+\begin{equation*}
+  \Psi^{\pm}=\frac{1}{\sqrt{N}} J^{\pm}\exp\left(\mp i \frac{1}{\sqrt{N}}\phi(z)\right)
+\end{equation*}
+%% Its action in terms of primary fields of $su(2)\oplus u(1)$ WZNW-model is equivalent to $J^{\pm}\pm \tilde{J}^{\pm}$.
+%% !!! TODO
+Martingale condition can be rewritten as
+\begin{equation*}
+  \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[\Psi^{+}_{-1}\Psi^{-}_{-1}+\Psi^{-}_{-1}\Psi^{+}_{-1}\right]\right) \left|\Phi\right>=0
+\end{equation*}
+which coincides with the result of Santachiara \cite{santachiara2008sle}.
+
+\subsection{Next steps}
+
+Next steps in the study of SLE martingales for coset models  are the following.
+
+%At first we act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with  raising operators $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations which connects level of representation and parameters of random motion $\kappa, \tau$.
+% !!! This is wrong !!!
+% We can act by Sugawara generators
+
+Then we use Knizhnik-Zamolodchikov equations to rewrite the relations in simpler form and get conditions on possible boundary condition changing operators.
+
+Boundary states in coset models were actively studied.
+One of the ideas is to consider direct sum WZNW-model and use equivalence relations.
+This study is essentially the study representation of fusion algebra, Verlinde formula is one of key ingredients in this study.
+So we hope to compare the classification of boundary states obtained in this way with our condition on boundary condition changing operator.
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+Now we see that it is possible to match SLE observables and CFT correlation functions.
+Martingale conditions can be seen as the constraints on possible Verma modules of affine Lie algebra corresponding to boundary condition changing operator.
+These Verma modules must have level two null state.
+
+We can use primary fields of direct sum WZNW model and equivalence relations to study coset models.
+
+Martingale conditions should be compared with the classification of boundary states with other methods.
+
+\bibliography{bibliography}{}
+\bibliographystyle{utphys}
+
+%%
+%% End of file
 %%% Local Variables: 
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "thesis"
 %%% End:

### 2011-10-26 AffineLieAlgebras/SLE/article.tex
Introduction is written.

@@
 \section{Introduction}
-Schramm-Loewner evolution, introduced by Oded Schramm in papers \cite{schramm2000scaling} is
+Schramm-Loewner evolution (SLE) was introduced by Oded Schramm  \cite{schramm2000scaling} to describe scaling limit of critical interfaces in two-dimensional statistical lattice models.
+This approach to the critical systems has lead to numerous strict results in the study of critical behavior (see reviews  \cite{rohde2005basic}, \cite{bauer20062d}, \cite{Cardy:2005kh}).
+We give some basics of SLE in Section \ref{sec:schr-loewn-evol}.
 
-The connection of SLE with CFT was studied in papers \cite{bauer2004conformal,bauer2004cfts,bauer2003sle,bauer2002sle}.
+Probability measure induced by Schramm-Loewner evolution on random curves is conformally invariant.
+Since conformal field theory (CFT) gives us another tool-set for the study of two-dimensional critical systems, it is natural to discuss its connection with SLE.
+This connection  was studied in \cite{bauer2004conformal,bauer2004cfts,bauer2003sle,bauer2002sle} and many other papers mostly in case of unitary minimal models.
+The idea is to consider certain observables in the domain with the cut. This construction is briefly discussed in Section \ref{sec:corr-betw-sle}.
 
-Reviews \cite{rohde2005basic}, \cite{bauer20062d}, \cite{Cardy:2005kh}.
+More general models of CFT has additional symmetries.
+For example Kac-Moody algebras  appear in Wess-Zumino-Novikov-Witten models.
+To introduce such symmetry in SLE approach one considers additional random motion on Lie group \cite{bettelheim2005stochastic}, \cite{Rasmussen:2004xr}.
+This construction is described in Section \ref{sec:sle-wzw-models}.
+The correspondence between SLE martingales in this model and WZNW-correlation functions was studied in \cite{alekseev2010sle}.
+Similar generalization to $\mathbb{Z}(N)$-parafermionic models were considered in \cite{santachiara2008sle,picco2008numerical}.
 
-SLE and conformal field theories with additional symmetries \cite{alekseev2010sle}, \cite{santachiara2008sle,picco2008numerical}, \cite{bettelheim2005stochastic}, \cite{Rasmussen:2004xr}.
+Main task of present paper is to generalize SLE with additional random walk on Lie group to the case of factor space $G/H$ and to study the relation with coset conformal field theory.
+We remind some details of CFT coset construction in Section  \ref{sec:coset-models} then introduce SLE on factor space (Section \ref{sec:sle-coset-space} and relate it to conformal field theory (Section \ref{sec:semis-lie-algebr}).
+Similarly to WZNW-case we obtain the system of algebraic equations on boundary condition changing operators from martingale condition.
+Coset construction of CFT can be used to obtain minimal models and parafermions (see \cite{difrancesco1997cft}) so we compare our classification of boundary condition changing operators with the results of paper \cite{santachiara2008sle} (Section \ref{sec:parafermions}).
+
+In the conclusion we compare classification of boundary condition changing operators which follows from martingale condition with general classification of b.c.c.
+operators in boundary conformal field theory related to D-brane solutions \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,Maldacena:2001ky,felder1999geometry,alekseev1999d}.
 
 \subsection{Schramm-Loewner evolution}
+\label{sec:schr-loewn-evol}
 To remind of Schramm-Loewner evolution we first describe simple example.
@@
 \subsection{Correspondence between SLE and minimal models of CFT}
+\label{sec:corr-betw-sle}
 
@@
 \subsection{SLE on coset space}
+\label{sec:sle-coset-space}
+
 Consider Lie (semi-)simple group $G$ with Lie algebra $\gf$ and (semi-)simple subgroup $A\subset G$ with Lie algebra $\af\subset \gf$. 
@@
 \end{equation}
-or
+Since $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$ we have
+
+\begin{equation}
+  \label{eq:17}
+  12 h_{\Lambda}+2\kappa h_{\Lambda} (2h_{\Lambda}+1) +  \tau (C_{\Lambda}-\tilde{C}_{\Lambda})=0
+\end{equation}
+
 \begin{equation}
   \label{eq:16}
-  \left(12 h_{\Lambda}+2\kappa h_{\Lambda} (2h_{\Lambda}+1) + 2 \tau J^{3}_{0}J^{3}_{0}\right) \phi_{\Lambda}=0
+  \left(12 h_{\Lambda}+2\kappa h_{\Lambda} (2h_{\Lambda}+1) +  \tau (C_{\Lambda}-\Lambda^{2}\right) \phi_{\Lambda}=0
+\end{equation}
+
+We need to get one more equation since we have three variables $\kappa,\tau,h_{\Lambda}$. We can use that $\psi$ is singular vector so $L_{1}\psi=0$ and then
+\begin{equation}
+  \label{eq:18}
+  J_{1}^{a}L_{1}\psi=0
 \end{equation}
@@
 \subsection{Parafermions}
+\label{sec:parafermions}
 

### 2011-10-27 AffineLieAlgebras/SLE/article.tex
IOP JPhys Conference series style applied, Mathematica code added.

@@
-\documentclass[12pt]{article}
+\documentclass[a4paper]{jpconf}
+
+%\documentclass[12pt]{article}
 \usepackage{amssymb}
@@
 \theoremstyle{definition} \newtheorem{Def}{Definition}
-\newcommand{\tr}{\hat\triangleright} \newcommand{\trc}{\triangleright}
 \newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
@@
 \title{Algebraic properties of CFT coset construction and Schramm-Loewner evolution}
-\author{A A Nazarov$^{1,2}$\\
-  {\small $^1$ Theoretical Department, SPb State University}\\
-  {\small 198904, Sankt-Petersburg, Russia}\\
-  {\small$^{2}$ Chebyshev Laboratory,}\\
-  {\small Department of Mathematics and Mechanics, SPb State University}\\
-  {\small 199178, Saint-Petersburg, Russia}\\
-  {\small email: antonnaz@gmail.com}}
+\author{A A Nazarov$^{1,2}$}
+\address{
+  $^1$ Department of High-Energy and Elementary Particle Physics, 
+  Faculty of Physics, \\ SPb State University
+  198904, Saint-Petersburg, Russia}
+\address{
+  $^{2}$ Chebyshev Laboratory,
+  Faculty of Mathematics and Mechanics, \\ SPb State University
+  199178, Saint-Petersburg, Russia}
 
-\maketitle
+\ead{antonnaz@gmail.com}
 
@@
 \label{sec:schr-loewn-evol}
-To remind of Schramm-Loewner evolution we first describe simple example.
-
 Consider Ising model on triangular lattice on upper half plane (see Fig.
@@
 We impose following boundary condition: all spins are down on one half of the boundary and all spins are up on another half.
-Then in any configuration we get an interface delimiting two clusters and connecting zero and infinity.
+Then in any spin configuration we get an interface delimiting two clusters and connecting zero and infinity (see Figure \ref{fig:sle}).
 
@@
 \bibliography{bibliography}{}
-\bibliographystyle{utphys}
+\bibliographystyle{iopart-num}
 

### 2011-10-27 AffineLieAlgebras/SLE/computations.m

@@ -1,0 +1,87 @@
+ExpandNCM[(h : NonCommutativeMultiply)[a___, b_Plus, c___]] :=  Distribute[h[a, b, c], Plus, h, Plus, ExpandNCM[h[##]] &];
+ExpandNCM[a_] := ExpandAll[a];
+
+L/:NonCommutativeMultiply[L[0],phi] := h*phi;
+L/:NonCommutativeMultiply[L[n_Integer],phi]/;n>0 := 0;
+L/:NonCommutativeMultiply[L[n_Integer],phi]/;n>0 := 0;
+J/:NonCommutativeMultiply[J[n_Integer][a_Integer],phi]/;n>0 := 0;
+J/:NonCommutativeMultiply[J[0][3],phi] := j*phi;
+L/:NonCommutativeMultiply[L[n_Integer],L[m_Integer]]/;And[n>=0, m<=0, n==-m] := c/12*(n^3-n);
+L/:NonCommutativeMultiply[L[n_Integer],L[m_Integer]]/;And[n>=0, m<=0] := (n-m)*L[n+m];
+L/:NonCommutativeMultiply[L[n_Integer],J[m_Integer][a_Integer]]:=-m*J[n+m][a];
+J/:NonCommutativeMultiply[J[m_Integer][a_Integer],J[n_Integer][b_Integer]]/;And[m>=0,n==-m,a==b] := J[n][a]**J[m][a]+k*m;
+J/:NonCommutativeMultiply[J[m_Integer][a_Integer],J[n_Integer][b_Integer]]/;And[m>=0,n<=0] := Sum[I*Signature[a,b,c]*J[m+n][c],{c,3}];
+L/:NonCommutativeMultiply[q_?NumericQ,L[n_Integer]]:=q*L[n];
+J/:NonCommutativeMultiply[q_?NumericQ,J[n_Integer][a_Integer]]:=q*J[n][a];
+phi/:NonCommutativeMultiply[q_?NumericQ,phi]:=q*psi;
+psi=(-2*L[-2]+1/2*kappa*L[-1]**L[-1]+1/2*tau*Sum[J[-1][a]**J[-1][a],{a,3}])**phi;
+
+ExpandNCM[L[2]**psi]
+
+                                              kappa L[-1] ** L[-1]
+Out[11]= L[2] ** (-2 L[-2]) ** phi + L[2] ** (--------------------) ** phi + 
+                                                       2
+ 
[…]

### 2011-10-27 AffineLieAlgebras/SLE/article.tex
Some changes in first sections

@@
     \includegraphics[height=25mm]{explore.pdf}
-    \caption{SLE -- continuous limit of interfaces}}
+    \caption{Interface in Ising model on triangular lattice}}
   \label{fig:sle}
 \end{figure}
+We can impose the condition of existence of certain interface of some finite length and study statistical model with this condition.
+Obviously it is equivalent to the model in the slit domain with the cut along an interface.
 
-Next we consider continuous limit of lattice model.
-Interface in random configuration of the model tends to random curve.
-We can think of this curve as of trace of stochastic process which satisfy some stochastic equation.
+Now we consider continuous limit of lattice model with a (part of) interface of finite length.
+Interface in random configuration of the model tends to random curve in this case.
+Old hypothesis \cite{Polyakov:1970xd} of conformal invariance at critical point was recently strictly proved for some lattice models (See \cite{smirnov2007towards}, \cite{duminil2011conformal} for a review).
+We assume conformal invariance at critical point and consider upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$.
+We denote this slit domain by $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$.
+Conformal map from $\mathbb{H}_{t}$ to $\mathbb{H}$ is denoted by $g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ (See Figure \ref{fig:sle2}).
 
-In papers [Smirnov, Schramm ... ] it was shown that this equation is
-\begin{equation*}
-  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} \quad \text{or} \quad       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}
-\end{equation*}
-The stochastic process which satisfy this equation is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.
-
-Here $g_{t}(z)$ is a conformal map from $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$ to $\mathbb{H}$ (see Fig. \ref{fig:sle2}).
 \begin{figure}[h]
@@
     \includegraphics[width=50mm]{loewner.pdf}
-    \caption{Conformal map}}
+    \caption{Conformal map $g_{t}(z):\mathbb{H}_{t}\to \mathbb{H}$.}}
   \label{fig:sle2}
@@
 
-Schramm-Loewner evolution provides conformally-invariant probability measure on trajectories $\gamma_{t}$ in $\mathbb{H}$.
+In paper \cite{schramm2000scaling} it was shown that $g_{t}(z)$ satisfies stochastic differential equation 
+\begin{equation}
+\label{eq:19}
+  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
+\end{equation}
+where $\xi_{t}$ is the Brownian motion.
 
-\subsection{Correspondence between SLE and minimal models of CFT}
+The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
+
+This stochastic process which satisfy is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.
+In the sequel it is more convenient to use map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
+\begin{equation}
+  \label{eq:20}
+       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}  
+\end{equation}
+Schramm-Loewner evolution provides conformally-invariant probability measure on curves $\gamma_{t}$ in $\mathbb{H}$.
+
+\subsection{SLE martingales and CFT correlation functions}
 \label{sec:corr-betw-sle}
@@
 Now we can look at the observables in the presence of SLE trace.
-Expectation value of lattice observable on upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace up to some time $t$ multiplied by the probability of this trajectory.
-
-Consider lattice observable $\mathcal{O}$, then it expectation value can be calculated as
+Expectation value of lattice observable $\mathcal{O}$ on the upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace $\gamma_{t}$ up to some time $t$ multiplied by the probability of this trajectory:
 \begin{equation*}
@@
 \end{equation*}
-Since lattice observable  $\prec \mathcal{O} \succ_{\mathbb{H}}$ does not depend on $t$, hence $\prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale.
+Lattice observable  $\prec \mathcal{O} \succ_{\mathbb{H}}$ does not depend on $t$, hence $\prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale.
 
-In continuous limit lattice observable tends to CFT correlation function. Since we consider the theory with the boundary, CFT correlation function has following form:
-\begin{equation*}
+In continuous limit lattice observable tends to CFT correlation function \cite{bauer2003sle,bauer2003conformal,bauer2002sle}.
+We need to take into account the change of boundary conditions on the tip of SLE trace and at the infinity, so the expression is
+\begin{equation}
   \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
   \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}=
-  \frac{\left< ^{g_{t}}\mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
-\end{equation*}
+  \frac{\left< ^{g_{t}}\mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
+\label{eq:21}
+\end{equation}
+
+Here $\phi(z_{t})$ is a primary field corresponding to boundary condition changing operator. We've used the conformal map $g_{t}$ to get the expression on the whole plane in equation \eqref{eq:21}.
+
+We consider the theory with the boundary, so in principle we need to use boundary conformal field theory here and impose proper consistency conditions \cite{cardy1984conformal,cardy1989boundary,cardy1991bulk}.
+In the case of upper half-plane boundary CFT correlation functions can be rewritten as the correlation functions of the theory on the whole plane but with doubled number of bulk fields.
+Here we are interested mainly in properties of boundary condition changing operator $\phi$.
+
 We assume that $\mathcal{F}$ contains some set of primary fields $\phi_{\lambda_{i}}$ with conformal weights $\lambda_{i}$.
+Since we work with boundary CFT we need to add bulk fields in conjugate points $\bar z_{i}$.
+For future use in WZNW models we denote the conformal weights of these duplicate fields by $h_{\lambda_{i}^{*}}$.
 Also we have boundary condition changing operators  $\phi$ at the tip of SLE trace and in the infinity.
-We can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite this expression in upper half plane:
+We use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite this expression in upper half plane:
 
@@
 
-Now we want to consider evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
+Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
 \begin{equation*}
@@
 
-Continuous limit in critical point leads to CFT correlation function
-
-Now for expectation value of martingale we have this expression.
-\begin{equation*}
-  \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=    \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t+dt}}\right], \quad \mathbb{E}\left[d \prec\mathcal{O}\succ_{\gamma_{t}}\right]=0
-\end{equation*}
-
-Now we use Ito calculus to calculate increment of our correlation function. It should be zero so we get the equation:
+Since $ \prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale, the expectation value of its increment during the evolution from $t$ to $t+dt$ is zero
 \begin{equation}
-  \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{-h_{i}}\right)\mathbb{E}\left[d 
-    \mathcal{F}_{\mathbb{H}_{t}}\right]=\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\mathbb{E}\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
-      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}
+  \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=    \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t+dt}}\right], \quad d\mathbb{E}\left[ \prec\mathcal{O}\succ_{\gamma_{t}}\right]=0
+\label{eq:22}
+\end{equation}
+By using Ito calculus we get the expression for the differential of $\mathcal{F}$:
+\begin{equation}
+d \mathcal{F}_{\mathbb{H}_{t}}= \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
+      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}=0
 \label{eq:8}
 \end{equation}
-Then use explicit form of conformal map and obtain
+We substitute \eqref{eq:2} and obtain the equation
+\begin{equation}
+  \left( \sum_{i}\left[-\frac{2h_{i}}{w_{i}^{2}} +\frac{2}{w_{i}}\partial_{w_{i}}\right]+\frac{\kappa}{2}\sum_{i,j}\partial_{w_{i}} \partial_{w_{j}}\right)\mathcal{F}(\left\{z_{i}\right\})=0
+\label{eq:23}
+\end{equation}
+
+For the correlation functions of secondary fields $L_{-n}\phi$ we have the equation 
+\begin{equation}
+\left< (L_{-n}\phi)(z) \varphi_{1}\dots \varphi_{N}\right>=\mathcal{L}_{-n}\left<\phi\varphi_{1}\dots\varphi_{N}\right>,
+\end{equation}
+ where $n\geq 1$ and
 \begin{equation*}
-  \left( \sum_{i}\left[-\frac{2h_{i}}{w_{i}^{2}} +\frac{2}{w_{i}}\partial_{w_{i}}\right]+\frac{\kappa}{2}\sum_{i,j}\partial_{w_{i}} \partial_{w_{j}}\right)\mathcal{F}(\left\{z_{i}\right\})=0
+  \mathcal{L}_{-n}=\sum_{i=1}^{N} \left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}} -\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right)
 \end{equation*}
+(See \cite{difrancesco1997cft}). So we can rewrite the differential equation \eqref{eq:23} as the algebraic equation on the field $\phi$ corresponding to boundary condition changing operator:
+\begin{equation}
+  \label{eq:24}
+   (L_{-2}-\frac{\kappa}{2}L_{-1}^{2})\phi=0.
+\end{equation}
 
+In case of minimal models the set of primary fields is finite and all the states are obtained through field-state correspondence \cite{belavin1984ics}, \cite{difrancesco1997cft}
+This equation means that 
 We can rewrite it as the necessary condition on b.c.c. operator $\phi$:
 \begin{equation*}
-  (L_{-2}-\frac{\kappa}{2}L_{-1}^{2})\phi=0 \Longrightarrow \phi \left|0\right>  \text{has level 2 null state}, \phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}
+ \Longrightarrow \phi \left|0\right>  \text{has level 2 null state}, \phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}
 \end{equation*}

### 2011-10-28 AffineLieAlgebras/SLE/article.tex
More work on text

@@
 Main task of present paper is to generalize SLE with additional random walk on Lie group to the case of factor space $G/H$ and to study the relation with coset conformal field theory.
-We remind some details of CFT coset construction in Section  \ref{sec:coset-models} then introduce SLE on factor space (Section \ref{sec:sle-coset-space} and relate it to conformal field theory (Section \ref{sec:semis-lie-algebr}).
+We remind some details of CFT coset construction in Section  \ref{sec:coset-models} then introduce SLE on factor space (Section \ref{sec:sle-coset-space}) and relate it to conformal field theory (Section \ref{sec:semis-lie-algebr}).
 Similarly to WZNW-case we obtain the system of algebraic equations on boundary condition changing operators from martingale condition.
@@
 
-We assume that $\mathcal{F}$ contains some set of primary fields $\phi_{\lambda_{i}}$ with conformal weights $\lambda_{i}$.
+We assume that $\mathcal{F}$ contains some set of primary fields $\varphi_{\lambda_{i}}$ with conformal weights $\lambda_{i}$.
 Since we work with boundary CFT we need to add bulk fields in conjugate points $\bar z_{i}$.
@@
 \end{equation*}
-For transformation of primary fields $\phi_{\lambda_{i}}$ we have 
+For transformation of primary fields $\varphi_{\lambda_{i}}$ we have 
 \begin{equation}
   \label{eq:2}
-  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\phi_{\lambda_{i}}(w_{i}) 
+  d\varphi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\varphi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\varphi_{\lambda_{i}}(w_{i}) 
 \end{equation}
@@
   \label{eq:24}
-   (L_{-2}-\frac{\kappa}{2}L_{-1}^{2})\phi=0.
+   \left<\left([L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi\right)(0)\; \varphi_{\lambda_{1}}\dots \varphi_{\lambda_{{2N}}}\right>=0.
 \end{equation}
+In the case of minimal models the set of primary fields is finite and all the states are obtained through field-state correspondence \cite{belavin1984ics}, \cite{difrancesco1997cft}. 
+Equation \eqref{eq:24}  holds for arbitrary observable $\mathcal{O}$ and arbitrary primary fields $\varphi_{i}$, so $[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ is level two null field and $[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi(0)\left|0\right>$ is level two null-state.
+There exist only two primary fields in minimal unitary models which give rise to Verma modules of Virasoro algebra with level two null-states.
+They are $\phi_{1,2}$ and $\phi_{2,1}$, so $\phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}$.
 
-In case of minimal models the set of primary fields is finite and all the states are obtained through field-state correspondence \cite{belavin1984ics}, \cite{difrancesco1997cft}
-This equation means that 
-We can rewrite it as the necessary condition on b.c.c. operator $\phi$:
-\begin{equation*}
- \Longrightarrow \phi \left|0\right>  \text{has level 2 null state}, \phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}
-\end{equation*}
-We can see that it can be rewritten as the action of Virasoro generators.
-Since we have arbitrary observable, this equation is equivalent to the requirement for boundary condition changing operator to have level two null state.
-In case of minimal model we can see that boundary condition chaining operator is primary field $\phi_{1,2}$ or $\phi_{2,1}$.
+\section{Wess-Zumino-Novikov-Witten models}
+\label{sec:sle-wzw-models}
+To generalize the analysis of previous section \ref{sec:corr-betw-sle} to non-minimal models we need to take additional symmetries into account.
+Wess-Zumino-Novikov-Witten models has Kac-Moody symmetry in addition to Virasoro algebra.
+At first we remind well-known properties of the model \cite{difrancesco1997cft} which are useful to study SLE martingales.
 
-\section{SLE and WZNW models}
-\label{sec:sle-wzw-models}
-Now we want to generalize this analysis to rational conformal field theories. First we consider Wess-Zumino-Novikov-Witten model.
-\subsection{WZNW models}
-
- The action for this model can be written in terms of map $g:\mathbb{C}\cup \{\infty\}\sim S^{2}\to G$ from complex plane with infinity or two-sphere to some Lie group $G$:
+ The action of WZNW model can be written in terms of map $g:\mathbb{C}\cup \{\infty\}\sim S^{2}\to G$ from complex plane with infinity or two-sphere to some (simple) Lie group $G$:
 \begin{multline}
   S=-\frac{k}{8\pi}\int d^2x\; \mathcal{K} (g^{-1}\partial^{\mu}g, g^{-1} \partial_{\mu}g)  
-  \\
   - \frac{k }{24\pi^{2}} \int_{B}\epsilon_{ijk} \mathcal{K}\left(
@@
 \end{multline}
-The first term is just non-linear sigma-model.
-
  Here $\mathcal{K}$ is Killing form on Lie algebra $\gf$ of Lie group $G$.
-The second term is written in terms of continuation from two-sphere $S^{2}$ to three-dimensional manifold $B$ which has two-sphere as the boundary.
+The first term is just non-linear sigma-model and the second term is written using the continuation $\tilde{g}$ from two-sphere $S^{2}$ to three-dimensional manifold $B$ which has two-sphere as the boundary.
 Since this continuation is non-unique we get the requirement for $k$ to be integer.
 
-Currents of this model have following form:
+Conserved currents of this model have following form:
   \begin{eqnarray}
@@
 
-Model possess gauge invariance under gauge transformations:
-  \begin{equation*}
-    g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z),
-  \end{equation*}
-  where $\Omega,\;\bar \Omega \in G$.
-Here $\Omega$ and $\bar \Omega$ are independent.
-
-If we consider infinitesimal gauge transformation $\Omega=1+\omega$ we get Ward identities:
+Model possess gauge invariance under gauge transformations
+  $g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)$, 
+where $\Omega,\;\bar \Omega \in G$ are are independent. If we consider infinitesimal gauge transformation $\Omega=1+\omega$ we get Ward identities 
   \begin{equation}
@@
     \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
-    \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
+    \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>,
   \end{equation}
-
- Then we can get operator product expansion for currents. 
+which can be used to get operator product expansion for currents:
  \begin{equation}
    \label{eq:3}
-   <J\phi>\sim \dots
+   J^{a}(z)J^{b}(w)\sim \frac{k\delta_{ab}}{(z-w)^{2}}+\sum_{c}i f_{abc}\frac{J^{c}}{z-w},
  \end{equation}
+where $f_{abc}$ are the structure constants of Lie algebra $\gf$.
 
-If we expand currents to modes
-\begin{equation*}
-  J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n 
-\end{equation*}
-and use operator product expansion \eqref{eq:3} we get commutation relations of affine Lie algebra $\gfh$:
-\begin{equation}
-  \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0} 
-\end{equation}
+Expanding currents to modes
+$J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n $
+and using operator product expansion \eqref{eq:3} we get commutation relations of affine Lie algebra $\gfh$:
+$ \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0} $.
 
-This model has conformal invariance which can be seen from 
-Sugawara construction. This is way to embed Virasoro algebra into the universal enveloping algebra of affine Lie algebra $\gfh$ ($Vir\subset U(\gfh)$):
+Conformal invariance of the model can  be seen from 
+Sugawara construction, which is a way to embed Virasoro algebra into the universal enveloping algebra of affine Lie algebra $\gfh$ ($Vir\subset U(\gfh)$):
 \begin{equation}
   \label{eq:4}
-  L_n=\frac{1}{2(k+h^v)}\sum\limits_a\sum\limits_m:J^a_m J^a_{n-m}:
+  L_n=\frac{1}{2(k+h^{\vee})}\left(\sum\limits_a\sum\limits_{m\leq -1}J^a_m J^a_{n-m}+\sum_{m\geq 0} J^{a}_{n-m}J^{a}_{m}\right), 
 \end{equation}
-
-Full chiral algebra of the model is semidirect product of affine and Virasoro algebra $\gfh \ltimes Vir$.
-
-Its commutation relations are
+ where $h^{\vee}$ is the dual Coxeter number of Lie algebra $\gf$. 
+Full chiral algebra of the model is semidirect product of affine and Virasoro algebra $\gfh \ltimes Vir$ with commutation relations 
   \begin{equation}
@@
     \begin{aligned}
+      \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0} \\
       \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
@@
   \end{equation}
-
-Primary fields  $\phi_{\lambda}$ are labeled by highest weights of affine Lie algebra representations. Here we see how Virasoro and affine Lie algebra generators act on primary fields:
+Here central charge $c$ of Virasoro algebra is given by expression
+\begin{equation}
+  \label{eq:25}
+  c=\frac{k\;\mathrm{dim}\gf}{k+h^{\vee}}
+\end{equation}
+There is infinite number of Virasoro primary fields, but they are organized into highest weight modules of affine Lie algebra $\gfh$. 
+Primary fields of full chiral algebra $\phi_{\lambda}$ are labeled by highest weights of affine Lie algebra $\gfh$ modules.
+Here we see how Virasoro and affine Lie algebra generators act on primary fields:
   \begin{equation*}
@@
       & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>  \quad    J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
-      & L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>=h_{\lambda} \left|\phi_{\lambda}\right>
+      & L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^{\vee})}\left|\phi_{\lambda}\right>=h_{\lambda} \left|\phi_{\lambda}\right>,
     \end{aligned}
   \end{equation*}
+where $\rho$ is Weyl vector of $\gf$.
 
-\subsection{SLE and WZNW models}
 Now we want to study Schramm-Loewner evolution in WZNW-models.
-
 Similarly to minimal models we consider observable
@@
 
-Consider evolution from $t$ to $t+dt$.
-First factor gives us $-\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}$.
+Under the evolution from $t$ to $t+dt$ first factor gives us $-\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}$.
 
+When we consider fields we need to add random gauge transformation (random motion in $G$) to stochastic evolution \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}. 
 For fields we have
 \begin{equation*}
-  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i})
+  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i}),
 \end{equation*}
-When we consider fields we need to add random gauge transformation (random motion in $G$) to stochastic evolution \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}:
+so additional term appears in the generator of field transformation. 
 \begin{equation*}
@@
 \end{equation*}
-Since we have boundary we are working with boundary CFT so we have only half of gauge transformations due to Cardy conditions.
+Here $d\theta^{a}$ are the generators of $\mathrm{dim}\gf$-dimensional Brownian motion and $\mathbb{E}[d\theta^{a}d\theta^{b}]=\delta_{ab}dt$.
+We assume that $t^{a}$ is a basis of $\gf$ orthogonal with respect to Killing form $\mathcal{K}$, $\mathcal{K}(t^{a},t^{b})=\delta_{ab}$.
 
-\subsection{SLE martingales in WZNW models}
-We use Ito calculus to get the equation from martingale condition:
+Using formula \eqref{eq:8} we get the equation from martingale condition:
 \begin{equation*}
-  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0,
 \end{equation*}
+where
 \begin{equation*}
@@
 \end{equation*}
-Again we can rewrite it as algebraic requirement for  field  which 
-correspond to boundary condition changing operator.
+Again we can rewrite it as algebraic requirement for  field  which corresponds to boundary condition changing operator. Now
 \begin{equation*}
@@
 is level two null state and if we act on this state with raising operators we should get zero.
-\begin{equation*}
-  J^{a}_{1} \left|\psi\right>=0, J^{a}_{2}\left|\psi\right>=0.
-\end{equation*}
- We use commutation relations and get equations which connects parameters of random motion with level of affine Lie algebra representation.
-
-We can see that $\kappa+\tau h^{v}=4$ and it is possible to derive additional relations connecting $\kappa, \tau, k$:
-\begin{equation*}
-  \kappa=\frac{2(h^{v}-2k)}{2h_{\Lambda}h^{v}-k},\quad \tau=\frac{8 h_{\Lambda}-2}{2h_{\Lambda}h^{v}-k}  \quad\text{for}\; k\neq 2h_{\Lambda}h^{v}
-\end{equation*}
- Also we get some constraints on possible boundary condition changing operators. 
-To get complete classification use Knizhnik-Zamolodchikov equations.
+\begin{eqnarray}
+  J^{a}_{1} \left|\psi\right>=0\\
+  J^{a}_{2}\left|\psi\right>=0\\
+  L_{2}\left|\psi\right>=0\\
+  L_{1}\left|\psi\right>=0
+\end{eqnarray}
+Using commutation relations \eqref{eq:92} these equations can be rewritten as algebraic equations connecting parameters of random motion $\kappa, \tau$ with the level $k$ of affine Lie algebra representation.
+Rigorous analysis of these equations is given in the paper \cite{alekseev2010sle}.
 
@@
 \label{sec:coset-models}
-Now we want to generalize analysis of correspondence between SLE and CFT even further and study coset models of conformal field theory.
-
-\subsection{Gauged WZNW-models and coset construction}
-
-Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models. We add gauge fields  $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action:
-\begin{multline*}
-  S(g,A)=S_{WZNW}(g)+\\
-  \frac{k}{4\pi}\int d^{2}z \left(\mathcal{K}(A, g^{-1}\bar \partial g)-\mathcal{K}(\bar A, (\partial g ) g^{-1})+\mathcal{K}(A,g^{-1}\bar A g)-\mathcal{K}(A,\bar A)\right)
-\end{multline*}
-Now current is
-\begin{equation*}
-  J_{(\gf,\af)}=-k\partial g g^{-1} -k g A g^{-1}
-\end{equation*}
-
-From Ward identities we get following expression for the product of gauge field and primary fields:
-\begin{equation*}
-  \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{v}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
-\end{equation*}
-Here $h_{\af}^{v}$ is the dual Coxeter number of Lie algebra $\af$.
-
-Remember that for WZNW current we have OPE $J_{\gf}^{a}(z)\phi_{i}(w)\sim \frac{-t^{a}_{i}\phi(w)}{z-w}$,  so we see that algebraic structure is connected with the pair of algebras $\gf$ and $\af$, such that $\afh\subset\gfh$.
-
-Virasoro generators are given by difference of Sugawara expressions:
+Now we want to generalize analysis of correspondence between SLE and CFT even further and study coset models of conformal field theory\cite{Goddard198588}.
+Such models are specified by  Lie algebra $\gf$ and its subalgebra $\af$.
+Virasoro generators in coset models are given by difference of Sugawara expressions of $\gf$ and $\af$-WZNW models:
 \begin{equation*}
@@
 
-\subsection{Primary fields}
-\label{sec:primary-fields}
-Primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra and subalgebra, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
+Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields  $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}.
+Here we are not interested in the details of this construction.
+For us it is only important that it is possible to obtain primary fields of coset model by field identification in WZNW-model with algebra $\gf\oplus \af$ \cite{fuchs1996resolution,schellekens1990field}.
+So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
 But some pairs are equivalent.
@@
 \begin{multline}
-  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^v)}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
-  \left|\phi_{\lambda}\right>=\\
-  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^v)}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^v)}\right)\left|\phi_{(\mu,\nu)}\right>
+  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^v)}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
+  \left|\phi_{\lambda}\right>=
+  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
 \end{multline}
@@
 
-It is possible to obtain analogues of KZ-equations:
+It is possible to obtain analogues of KZ-equations \cite{kogan1997knizhnik}:
 \begin{equation*}
-  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{v}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{v}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
+  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
 \end{equation*}
 
-\subsection{SLE on coset space}
-\label{sec:sle-coset-space}
+The idea is to constrain additional Brownian motion on group manifold to the factor space $G/A$.
 
-Consider Lie (semi-)simple group $G$ with Lie algebra $\gf$ and (semi-)simple subgroup $A\subset G$ with Lie algebra $\af\subset \gf$. 
+First we consider simple example. Let $G=SU(2)$ and $A=U(1)$, and corresponding Lie algebras $\gf=su(2)$, $\af=u(1)$, $\af\subset\gf$.
 The simplest way to study SLE on $G/A$ coset space is to restrict random walk on group manifold to the coset space by the choice of basis in $\gf$.
 Assume that generators $\{J^{a};\; a=1\dots \mathrm{dim}\gf\}$ are chosen in such way that $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\; a=\mathrm{dim}\gf-\mathrm{dim}\af\dots \mathrm{dim}\gf\}$ are the generators of subalgebra $\af\subset \gf$.
-Now we can consider $\mathrm{dim}\gf-\mathrm{dim}\af$-dimensional Brownian motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \; d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\mathrm{dim}\gf-\mathrm{dim}\af$.
+Now we can consider $(\mathrm{dim}\gf-\mathrm{dim}\af)$-dimensional Brownian motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \; d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\mathrm{dim}\gf-\mathrm{dim}\af$.
 
@@
 \end{equation}
-to be level two null-field. Here primary field $\phi_{\Lambda}$ is indexed by the pair $\Lambda=(\mu,\nu)$ with the equivalence relations \ref{sec:primary-fields}.
+to be level two null-field.
 
-Consider the simplest possible example.
-Let $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$.
-Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
-The equation \eqref{eq:10} is now
+Here $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$. The equation \eqref{eq:10} is now
 \begin{equation}
@@
 
+\subsection{SLE on coset space}
+\label{sec:sle-coset-space}
+
 Alternative approach is to study $\gf\oplus \af$ WZNW-model and then impose equivalence relations on the solutions. 
@@
 \end{equation*}
+
 %% \begin{equation*}
@@
 
-In this case the dimension of Lie algebra $\gf=su(s)\oplus su(2)$ is 6, dual Coxeter number $h^{v}=2+2=4$.
+In this case the dimension of Lie algebra $\gf=su(s)\oplus su(2)$ is 6, dual Coxeter number $h^{\vee}=2+2=4$.
 

### 2011-10-28 AffineLieAlgebras/SLE/article.tex
Coset models-coset models

@@
 Main task of present paper is to generalize SLE with additional random walk on Lie group to the case of factor space $G/H$ and to study the relation with coset conformal field theory.
-We remind some details of CFT coset construction in Section  \ref{sec:coset-models} then introduce SLE on factor space (Section \ref{sec:sle-coset-space}) and relate it to conformal field theory (Section \ref{sec:semis-lie-algebr}).
+We remind some details of CFT coset construction in Section  \ref{sec:coset-models} then introduce SLE on factor space (Section \ref{sec:coset-models}) and relate it to conformal field theory.
 Similarly to WZNW-case we obtain the system of algebraic equations on boundary condition changing operators from martingale condition.
-Coset construction of CFT can be used to obtain minimal models and parafermions (see \cite{difrancesco1997cft}) so we compare our classification of boundary condition changing operators with the results of paper \cite{santachiara2008sle} (Section \ref{sec:parafermions}).
+Coset construction of CFT can be used to obtain minimal models and parafermions (see \cite{difrancesco1997cft}) so we compare our classification of boundary condition changing operators with the results of paper \cite{santachiara2008sle}.
 
@@
 Such models are specified by  Lie algebra $\gf$ and its subalgebra $\af$.
+Denote by $J_{n}^{a}$ the generators of affine Lie algebra $\gfh$ and by $\tilde{J}_{n}^{b}$ the generators of $\afh$, so that $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b} J^{a}_{n}$.
 Virasoro generators in coset models are given by difference of Sugawara expressions of $\gf$ and $\af$-WZNW models:
@@
 \end{equation*}
+Commutation relations of Virasoro generators with generators of subalgebra $\afh$ are trivial
+\begin{equation}
+  \label{eq:26}
+  \left[L_{n},\tilde{J}^{b}_{m}\right]=0
+\end{equation}
 
@@
 Here we are not interested in the details of this construction.
+
+Looking at equation \eqref{eq:26} it is natural to think that we need to identify fields of $\gf$-model which differ by the action of $\afh$ generators $\tilde{J}_{n}^{b}$ to obtain primary fields of coset model.
+But the situation is not so simple since fields obtained in this way are equivalent if branching functions
+
 For us it is only important that it is possible to obtain primary fields of coset model by field identification in WZNW-model with algebra $\gf\oplus \af$ \cite{fuchs1996resolution,schellekens1990field}.
+
+(Field identification group here)
+
 So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
@@
 
+Let us introduce Schramm-Loewner evolution corresponding to coset models. 
 The idea is to constrain additional Brownian motion on group manifold to the factor space $G/A$.
@@
 
-\subsection{SLE on coset space}
-\label{sec:sle-coset-space}
+We can solve this equations.
 
@@
 
-\subsection{Parafermions}
-\label{sec:parafermions}
+%% \subsection{Parafermions}
+%% \label{sec:parafermions}
+%% 
+%% $\mathbb{Z}(N)$ parafermions are equivalent to $SU(2)_{N}/U(1)$ coset theory.
+%% 
+%% It is well-known that parafermionic field can be written as product of $su(2)$-primary field and vertex operator of bosonic field. 
+%% \begin{equation*}
+%%   \Phi^{j}=\phi_{j}(z) \exp\left( -i \frac{j}{\sqrt{N}}\phi(z)\right)
+%% \end{equation*}
+%% where $\phi_{j}(z)$ is field of $SU(2)$-WZNW model with spin $j$, $\phi(z)$ -- $U(1)$ bosonic field.
+%% 
+%% For parafermionic current we have
+%% \begin{equation*}
+%%   \Psi^{\pm}=\frac{1}{\sqrt{N}} J^{\pm}\exp\left(\mp i \frac{1}{\sqrt{N}}\phi(z)\right)
+%% \end{equation*}
+%% %% Its action in terms of primary fields of $su(2)\oplus u(1)$ WZNW-model is equivalent to $J^{\pm}\pm \tilde{J}^{\pm}$.
+%% %% !!! TODO
+%% Martingale condition can be rewritten as
+%% \begin{equation*}
+%%   \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[\Psi^{+}_{-1}\Psi^{-}_{-1}+\Psi^{-}_{-1}\Psi^{+}_{-1}\right]\right) \left|\Phi\right>=0
+%% \end{equation*}
+%% which coincides with the result of Santachiara \cite{santachiara2008sle}.
+%% 
+%%
 
-$\mathbb{Z}(N)$ parafermions are equivalent to $SU(2)_{N}/U(1)$ coset theory.
-
-It is well-known that parafermionic field can be written as product of $su(2)$-primary field and vertex operator of bosonic field. 
-\begin{equation*}
-  \Phi^{j}=\phi_{j}(z) \exp\left( -i \frac{j}{\sqrt{N}}\phi(z)\right)
-\end{equation*}
-where $\phi_{j}(z)$ is field of $SU(2)$-WZNW model with spin $j$, $\phi(z)$ -- $U(1)$ bosonic field.
-
-For parafermionic current we have
-\begin{equation*}
-  \Psi^{\pm}=\frac{1}{\sqrt{N}} J^{\pm}\exp\left(\mp i \frac{1}{\sqrt{N}}\phi(z)\right)
-\end{equation*}
-%% Its action in terms of primary fields of $su(2)\oplus u(1)$ WZNW-model is equivalent to $J^{\pm}\pm \tilde{J}^{\pm}$.
-%% !!! TODO
-Martingale condition can be rewritten as
-\begin{equation*}
-  \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[\Psi^{+}_{-1}\Psi^{-}_{-1}+\Psi^{-}_{-1}\Psi^{+}_{-1}\right]\right) \left|\Phi\right>=0
-\end{equation*}
-which coincides with the result of Santachiara \cite{santachiara2008sle}.
-
-\subsection{Next steps}
-
-Next steps in the study of SLE martingales for coset models  are the following.
-
-%At first we act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with  raising operators $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations which connects level of representation and parameters of random motion $\kappa, \tau$.
-% !!! This is wrong !!!
-% We can act by Sugawara generators
-
-Then we use Knizhnik-Zamolodchikov equations to rewrite the relations in simpler form and get conditions on possible boundary condition changing operators.
-
-Boundary states in coset models were actively studied.
+%% \subsection{Next steps}
+%% 
+%% Next steps in the study of SLE martingales for coset models  are the following. 
+%% 
+%% %At first we act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with  raising operators $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations which connects level of representation and parameters of random motion $\kappa, \tau$.
+%% % !!! This is wrong !!!
+%% % We can act by Sugawara generators 
+%% 
+%% Then we use Knizhnik-Zamolodchikov equations to rewrite the relations in simpler form and get conditions on possible boundary condition changing operators. 
+%% 
+%% Boundary states in coset models were actively studied.
 One of the ideas is to consider direct sum WZNW-model and use equivalence relations.
@@
 So we hope to compare the classification of boundary states obtained in this way with our condition on boundary condition changing operator.
-
+%% 
 \section{Conclusion}

### 2011-10-30 AffineLieAlgebras/SLE/article.tex
Text is finished, proofreading is required.

@@
 
-In the conclusion we compare classification of boundary condition changing operators which follows from martingale condition with general classification of b.c.c.
+In the conclusion we discuss the need to compare classification of boundary condition changing operators which follows from martingale condition with general classification of b.c.c.
 operators in boundary conformal field theory related to D-brane solutions \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,Maldacena:2001ky,felder1999geometry,alekseev1999d}.
@@
 so additional term appears in the generator of field transformation. 
-\begin{equation*}
+\begin{equation}
   \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)
-\end{equation*}
+\label{eq:18}
+\end{equation}
 Here $d\theta^{a}$ are the generators of $\mathrm{dim}\gf$-dimensional Brownian motion and $\mathbb{E}[d\theta^{a}d\theta^{b}]=\delta_{ab}dt$.
@@
 Using formula \eqref{eq:8} we get the equation from martingale condition:
-\begin{equation*}
+\begin{equation}
   \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0,
-\end{equation*}
+  \label{eq:27}
+\end{equation}
 where
@@
 Again we can rewrite it as algebraic requirement for  field  which corresponds to boundary condition changing operator. Now
-\begin{equation*}
+\begin{equation}
   \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
-\end{equation*}
+  \label{eq:16}
+\end{equation}
 is level two null state and if we act on this state with raising operators we should get zero.
@@
 Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields  $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}.
-Here we are not interested in the details of this construction.
-
-Looking at equation \eqref{eq:26} it is natural to think that we need to identify fields of $\gf$-model which differ by the action of $\afh$ generators $\tilde{J}_{n}^{b}$ to obtain primary fields of coset model.
-But the situation is not so simple since fields obtained in this way are equivalent if branching functions
-
-For us it is only important that it is possible to obtain primary fields of coset model by field identification in WZNW-model with algebra $\gf\oplus \af$ \cite{fuchs1996resolution,schellekens1990field}.
-
-(Field identification group here)
+Then fields are labeled by pairs of weights $(\mu,\nu)$, where $\mu$ is the weight of $\gfh$ and $\nu$ is the weight of $\afh$ correspondingly.
+But there are selection rules, i.e.
+the branching functions for certain pairs of weights $(\mu,\nu)$ vanish.
+There is also a redundancy, i.e.
+non-vanishing branching functions for distinct pairs $(\mu,\nu)$ turn out to be identical \cite{fuchs1996resolution,schellekens1990field}.
 
 So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
-But some pairs are equivalent.
-This equivalence is given by the action of simple currents $(J,\tilde{J})$ such that their conformal weights are equal:  $h_{J}-h_{\tilde{J}}=0$.
+Some pairs are equivalent.
+This equivalence is given by the action of so called ``simple currents'' $(J,\tilde{J})$, which are certain elements of outer  automorphisms group $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ of $\gfh\times\afh$, where $B(G)$ is center of Lie group G.
+We can think of simple currents as of primary fields and their action on fields of theory are given by fusion product \cite{difrancesco1997cft}.
+Then we must primary fields of coset model are given by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where $(J,\tilde J)$ such that their conformal weights are equal:  $h_{J}-h_{\tilde{J}}=0$.
 
@@
 \begin{multline}
-  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^v)}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
-  \left|\phi_{\lambda}\right>=
+  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
+  \left|\phi_{(\mu,\nu)}\right>=\\
   \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
 \end{multline}
-
-%% So $G/A$-coset theory is related to $\gf\oplus \bar{\af}$-theory.
-
-It is possible to obtain analogues of KZ-equations \cite{kogan1997knizhnik}:
+It is possible to obtain analogues of KZ-equations for coset models \cite{kogan1997knizhnik}:
 \begin{equation*}
@@
 \begin{equation}
-  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}J^{a}_{-1}J^{a}_{-1}\right)\right) \phi_{\Lambda}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}J^{a}_{-1}J^{a}_{-1}\right)\right) \phi_{(\mu,\nu)}
 \label{eq:10}
@@
 
-Here $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$. The equation \eqref{eq:10} is now
+Here $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$.
+Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
+We label weights by Dynkin labels, so $J^{3}_{0}\phi_{(\mu,\nu)}=\frac{\mu}{2} \phi_{(\mu,\nu)}$.
+
+ The equation \eqref{eq:10} is now
 \begin{equation}
   \label{eq:11}
-  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{\Lambda}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
 \end{equation}
@@
 \begin{equation}
- \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{\Lambda}
+ \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{(\mu,\nu)}
 \label{eq:12}
 \end{equation}
-which coincides with the equation for parafermionic fields introduced in paper \cite{santachiara2008sle}.
+which are similar to the equations for parafermionic fields introduced in paper \cite{santachiara2008sle}.
 
@@
   \label{eq:13}
-  L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{\Lambda}=0\quad \Longrightarrow\quad  (3\kappa-8) h_{\Lambda}+\frac{2(k-1)}{k+2}+\tau k =0
+  L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{(\mu,\nu)}=0,
+\end{equation}
+and obtain
+\begin{equation}
+  \label{eq:28}
+  (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
 \end{equation}
@@
   \label{eq:15}
-  L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{\Lambda}=0
+  L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{(\mu,\nu)}=0
 \end{equation}
 Since $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$ we have
-
 \begin{equation}
   \label{eq:17}
-  12 h_{\Lambda}+2\kappa h_{\Lambda} (2h_{\Lambda}+1) +  \tau (C_{\Lambda}-\tilde{C}_{\Lambda})=0
+  12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) +  \tau (C_{\mu}-\tilde{C}_{\nu})=0,
+\end{equation}
+where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator $\sum_{a}t^{a}t^{a}$. For $u(1)$ it is just $\nu^{2}$.
+We need to get one more equation since we have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so $L_{1}\psi=0$ and then $J_{1}^{3}L_{1}\psi=0$, so
+\begin{equation}
+  \label{eq:29}
+  \left(-6  + \kappa +  \tau +  2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0} \phi_{(\mu,\nu)}=0
 \end{equation}
 
-\begin{equation}
-  \label{eq:16}
-  \left(12 h_{\Lambda}+2\kappa h_{\Lambda} (2h_{\Lambda}+1) +  \tau (C_{\Lambda}-\Lambda^{2}\right) \phi_{\Lambda}=0
-\end{equation}
+Turn to the case $k=2, \;c=1/2$ which corresponds to square lattice Ising model.
+We have three non-equivalent fields numbered by the pairs of $su(2)$ and $u(1)$ weights, which are $\phi_{(0,0)}, \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$.
+The equation \eqref{eq:29} is trivial for $\phi_{(0,0)}$ and $\phi_{(0,2)}$, so the equations \eqref{eq:17}, \eqref{eq:28} are consistent although we do not know how to interpret $\tau$ in context of the Ising model.
+If we consider the field $\phi_{(1,1)}$ we have no solution for $\kappa,\tau$, so we see that not every primary field correspond to some boundary condition changing operator.
 
-We need to get one more equation since we have three variables $\kappa,\tau,h_{\Lambda}$. We can use that $\psi$ is singular vector so $L_{1}\psi=0$ and then
-\begin{equation}
-  \label{eq:18}
-  J_{1}^{a}L_{1}\psi=0
-\end{equation}
-
-We can solve this equations.
-
-Alternative approach is to study $\gf\oplus \af$ WZNW-model and then impose equivalence relations on the solutions. 
-So we need to generalize the analysis of \cite{alekseev2010sle} to the case of semisimple Lie algebras.
-
-From equation
-
-Now consider as an example $\frac{SU(2)_{k}\times SU(2)_{1}}{SU(2)_{k+1}}$ -- another coset realization for minimal unitary models.
-
-We get following relations on $\kappa,\tau$ and primary fields. So we see that the solutions at level $k$ are
-
-Now we need to impose equivalence relations.
-
-We get
-
-Consider gauge transformation in gauged WZNW model:
-\begin{eqnarray*}
-  \delta \phi_{i}=(\epsilon_{L}^{a} t^{a}_{i}+\epsilon^{b}_{R}\tilde{t}^{b})\phi_{i}\\
-  \delta A = -\partial \epsilon_{R}-[\epsilon_{R},A]
-\end{eqnarray*}
-Here $\epsilon_{L}, \epsilon_{R}$ are arbitrary holomorphic functions $\bar\partial\epsilon_{L,R}=0$. 
-For  $\gf\oplus \af$ WZNW-model we can write SLE generator of primary field transformation under stochastic evolution as
+Now let us generalize to arbitrary coset model.
+It is not always convenient to work with generators orthogonal with respect to Killing form $\mathcal{K}$, sometimes it is preferable to use Chevalley or Cartan-Weyl basis.
+So we introduce additional $\mathrm{dim}\gf$-dimensional Brownian motion \eqref{eq:18} with the normalization condition $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
+We need to consider Brownian motion on factor space $G/A$, the generator of field transformation \eqref{eq:2} is
 \begin{equation*}
-  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)+\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right)
 \end{equation*}
-
-%% \begin{equation*}
-%%   \mathcal{G}_{i}^{L,R}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)\pm\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
-%% \end{equation*}
-
-and get martingale condition
+and we get \eqref{eq:8} martingale condition, which can be written as
 \begin{equation*}
   \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
-      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0
+      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0.
 \end{equation*}
-
-which can be rewritten as the requirement for
-\begin{equation*}
-  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}
-\end{equation*}
+This equation can be rewritten as the requirement for
+\begin{equation}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\mu,\nu)}
+\label{eq:30}
+\end{equation}
 to be level two null-field.
 
-We can compare this result with the simplest possible coset model $su(2)/u(1)$ --  parafermion theory.
+Acting on \eqref{eq:30} with $L_{2}$ and $L_{1}^{2}$ we can obtain equations \eqref{eq:28} and \eqref{eq:17}.
+To get more equations we can act by $\afh$-generators $\tilde{J}^{b}_{1}$ and $L_{1}$ similarly to what was done with $J^{3}_{1}$ to get equation \eqref{eq:29}.
 
-\subsection{Semisimple Lie algebras and coset construction}
-\label{sec:semis-lie-algebr}
+To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} as was done for WZNW-models in paper \cite{alekseev2010sle}.
 
-It is well known that unitary minimal models with central charge $c=1-\frac{6}{m(m+1)}$ can be obtained from coset construction starting with $su(2)_{m}\oplus su(2)_{1}$ WZW-model and factorizing it by $su(2)_{m+1}$.
-Here lower index represents level of affine Lie algebra representation.
-
-In this case the dimension of Lie algebra $\gf=su(s)\oplus su(2)$ is 6, dual Coxeter number $h^{\vee}=2+2=4$.
-
-\begin{equation}
-  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
-\label{eq:6}
-\end{equation}
-
-For semisimple Lie algebra $\gf=\gf_{1}+\gf_{2}$ with generators $J^{a}$ and $\tilde{J}^{b}$ correspondingly we can more explicitly write the relation \eqref{eq:6} as
-
-\begin{equation*}
-  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\left(\sum_{a} J^{a}_{-1} J^{a}_{-1}+\sum_{b}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right) \right) \left|\phi_{\Lambda}\right>
-\end{equation*}
-
-This vector should be null vector of level two, so $L_{2}\left|\psi\right>=L_{1}\left|\psi\right>=0$. Then we get following algebraic relations for semisimple Lie algebra:
-\begin{equation}
-  \label{eq:7}
-  \left( 3\kappa h_{\Lambda} +\frac{1}{2} \tau (k_{1} \mathrm{dim} \gf_{1}+k_{2}\mathrm{dim} \gf_{2}) -8 h_{\Lambda} - c\right)\phi_{\Lambda}=0
-\end{equation}
-SLE and factorization by equivalence relations.
-
-%% \subsection{Parafermions}
-%% \label{sec:parafermions}
-%% 
-%% $\mathbb{Z}(N)$ parafermions are equivalent to $SU(2)_{N}/U(1)$ coset theory.
-%% 
-%% It is well-known that parafermionic field can be written as product of $su(2)$-primary field and vertex operator of bosonic field. 
-%% \begin{equation*}
-%%   \Phi^{j}=\phi_{j}(z) \exp\left( -i \frac{j}{\sqrt{N}}\phi(z)\right)
-%% \end{equation*}
-%% where $\phi_{j}(z)$ is field of $SU(2)$-WZNW model with spin $j$, $\phi(z)$ -- $U(1)$ bosonic field.
-%% 
-%% For parafermionic current we have
-%% \begin{equation*}
-%%   \Psi^{\pm}=\frac{1}{\sqrt{N}} J^{\pm}\exp\left(\mp i \frac{1}{\sqrt{N}}\phi(z)\right)
-%% \end{equation*}
-%% %% Its action in terms of primary fields of $su(2)\oplus u(1)$ WZNW-model is equivalent to $J^{\pm}\pm \tilde{J}^{\pm}$.
-%% %% !!! TODO
-%% Martingale condition can be rewritten as
-%% \begin{equation*}
-%%   \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[\Psi^{+}_{-1}\Psi^{-}_{-1}+\Psi^{-}_{-1}\Psi^{+}_{-1}\right]\right) \left|\Phi\right>=0
-%% \end{equation*}
-%% which coincides with the result of Santachiara \cite{santachiara2008sle}.
-%% 
-%%
-
-%% \subsection{Next steps}
-%% 
-%% Next steps in the study of SLE martingales for coset models  are the following. 
-%% 
-%% %At first we act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with  raising operators $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations which connects level of representation and parameters of random motion $\kappa, \tau$.
-%% % !!! This is wrong !!!
-%% % We can act by Sugawara generators 
-%% 
-%% Then we use Knizhnik-Zamolodchikov equations to rewrite the relations in simpler form and get conditions on possible boundary condition changing operators. 
-%% 
-%% Boundary states in coset models were actively studied.
-One of the ideas is to consider direct sum WZNW-model and use equivalence relations.
-This study is essentially the study representation of fusion algebra, Verlinde formula is one of key ingredients in this study.
-So we hope to compare the classification of boundary states obtained in this way with our condition on boundary condition changing operator.
-%% 
 \section{Conclusion}
@@
 
-Now we see that it is possible to match SLE observables and CFT correlation functions.
-Martingale conditions can be seen as the constraints on possible Verma modules of affine Lie algebra corresponding to boundary condition changing operator.
-These Verma modules must have level two null state.
+We proposed a way to generalize Schramm-Loewner evolution to obtain observables which can be studied by methods of coset conformal field theory.
+The description of fields in coset models is not very simple due to field identification \cite{schellekens1990field} and the need of resolution of fixed points \cite{Fuchs:1996dd,fuchs1996resolution} which we have not discussed here.
+This subtleties can complicate the solution of equations  \eqref{eq:28}, \eqref{eq:17} and analogues of equation \eqref{eq:29}.
+On the other hand the use of Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} for correlation functions in the spirit of \cite{alekseev2010sle} lead to matrix algebraic relations which are similar to NIM-representations for boundary states \cite{ishikawa2003novel}.
+The study of this subject can reveal deep algebraic connection of martingale conditions with boundary states classification.
 
-We can use primary fields of direct sum WZNW model and equivalence relations to study coset models.
-
-Martingale conditions should be compared with the classification of boundary states with other methods.
+Physical interpretation of the solutions of martingale conditions is not clear, but there is also no lattice interpretation of Schramm-Loewner evolution with additional Brownian motion on group manifold \cite{bettelheim2005stochastic} and no lattice interpretation of WZNW-models.
+We think that these questions are closely related.
+\newpage
 

### 2011-10-30 AffineLieAlgebras/SLE/article.tex
Paper submitted to proceedings, acknowledgements were added, some computations made, pdf is now in git

@@
 \begin{abstract}
-  Schramm-Loewner evolution appears naturally as the scaling limit of interfaces in lattice models at critical point.
+  Schramm-Loewner evolution appears as the scaling limit of interfaces in lattice models at critical point.
 Critical behavior of these models can be described by minimal models of conformal field theory.
-
-  We generalize Schramm-Loewner evolution with additional Brownian motion on Lie group to the case of direct product of two groups.
+Certain CFT correlation functions are martingales with respect to SLE.
+  We generalize Schramm-Loewner evolution with additional Brownian motion on Lie group $G$ to the case of factor space $G/A$.
 We then study connection between SLE description of critical behavior with coset models of conformal field theory.
@@
 
-%%    SLE with additional Brownian motion on Lie group $G$ was proposed as generalization to WZNW models of CFT.
-Martingale property of SLE observables is related to Virasoro null vector conditions for CFT fields and KZ-equations for correlation functions.
 %%  
@@
 Since conformal field theory (CFT) gives us another tool-set for the study of two-dimensional critical systems, it is natural to discuss its connection with SLE.
-This connection  was studied in \cite{bauer2004conformal,bauer2004cfts,bauer2003sle,bauer2002sle} and many other papers mostly in case of unitary minimal models.
+This connection  was studied in \cite{bauer2004conformal,bauer2004cfts,bauer2003sle,bauer2002sle} and many other papers mostly for unitary minimal models.
 The idea is to consider certain observables in the domain with the cut. This construction is briefly discussed in Section \ref{sec:corr-betw-sle}.
@@
 The correspondence between SLE martingales in this model and WZNW-correlation functions was studied in \cite{alekseev2010sle}.
-Similar generalization to $\mathbb{Z}(N)$-parafermionic models were considered in \cite{santachiara2008sle,picco2008numerical}.
+Similar generalization to $\mathbb{Z}(N)$-parafermionic models was proposed in \cite{santachiara2008sle,picco2008numerical}.
 
-Main task of present paper is to generalize SLE with additional random walk on Lie group to the case of factor space $G/H$ and to study the relation with coset conformal field theory.
-We remind some details of CFT coset construction in Section  \ref{sec:coset-models} then introduce SLE on factor space (Section \ref{sec:coset-models}) and relate it to conformal field theory.
+Main task of present paper is to generalize SLE with additional random walk on Lie group to the case of factor space $G/H$ and to study the connection with coset construction  of conformal field theory.
+We remind some details of coset construction, introduce SLE on factor space and relate it to conformal field theory in Section  \ref{sec:coset-models}.
 Similarly to WZNW-case we obtain the system of algebraic equations on boundary condition changing operators from martingale condition.
-Coset construction of CFT can be used to obtain minimal models and parafermions (see \cite{difrancesco1997cft}) so we compare our classification of boundary condition changing operators with the results of paper \cite{santachiara2008sle}.
+Coset construction of CFT can be used to obtain minimal models and parafermions (see \cite{difrancesco1997cft}) so we compare our equations on boundary condition changing operators with the results of paper \cite{santachiara2008sle}.
 
-In the conclusion we discuss the need to compare classification of boundary condition changing operators which follows from martingale condition with general classification of b.c.c.
+In Conclusion \ref{sec:conclusion} we discuss the need to compare classification of boundary condition changing operators which follows from martingale condition with general classification of b.c.c.
 operators in boundary conformal field theory related to D-brane solutions \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,Maldacena:2001ky,felder1999geometry,alekseev1999d}.
@@
   \centering{
-    \includegraphics[height=25mm]{explore.pdf}
+    \includegraphics[height=50mm]{explore.pdf}
     \caption{Interface in Ising model on triangular lattice}}
@@
 \end{figure}
-We can impose the condition of existence of certain interface of some finite length and study statistical model with this condition.
+We can impose the condition of the existence of finite-length part of interface and study statistical model with this condition.
 Obviously it is equivalent to the model in the slit domain with the cut along an interface.
 
-Now we consider continuous limit of lattice model with a (part of) interface of finite length.
-Interface in random configuration of the model tends to random curve in this case.
+Now consider continuous limit of lattice model with a (part of) interface of finite length.
+Interface in random configuration of the model tends to random curve.
 Old hypothesis \cite{Polyakov:1970xd} of conformal invariance at critical point was recently strictly proved for some lattice models (See \cite{smirnov2007towards}, \cite{duminil2011conformal} for a review).
@@
   \centering{
-    \includegraphics[width=50mm]{loewner.pdf}
+    \includegraphics[width=60mm]{loewner.pdf}
     \caption{Conformal map $g_{t}(z):\mathbb{H}_{t}\to \mathbb{H}$.}}
@@
 \end{equation}
-where $\xi_{t}$ is the Brownian motion.
+where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
 
-The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
-
-This stochastic process which satisfy is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.
-In the sequel it is more convenient to use map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
+Stochastic process which satisfies \eqref{eq:19} is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.
+For us it is more convenient to use map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
 \begin{equation}
@@
   \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
-  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}=
-  \frac{\left< ^{g_{t}}\mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
+  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}
+%% =
+%%   \frac{\left<^{g_{t}}
+%% \mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
 \label{eq:21}
@@
 
-Here $\phi(z_{t})$ is a primary field corresponding to boundary condition changing operator. We've used the conformal map $g_{t}$ to get the expression on the whole plane in equation \eqref{eq:21}.
+%% Here $\phi(z_{t})$ is a primary field corresponding to boundary condition changing operator.
+%% We've used the conformal map $g_{t}$ to get the expression on the whole plane in equation \eqref{eq:21}.
 
 We consider the theory with the boundary, so in principle we need to use boundary conformal field theory here and impose proper consistency conditions \cite{cardy1984conformal,cardy1989boundary,cardy1991bulk}.
-In the case of upper half-plane boundary CFT correlation functions can be rewritten as the correlation functions of the theory on the whole plane but with doubled number of bulk fields.
-Here we are interested mainly in properties of boundary condition changing operator $\phi$.
+In the case of upper half-plane correlation functions of boundary CFT can be rewritten as the correlation functions of the theory on the whole plane but with doubled number of bulk fields.
 
-We assume that $\mathcal{F}$ contains some set of primary fields $\varphi_{\lambda_{i}}$ with conformal weights $\lambda_{i}$.
+% Here we are interested mainly in properties of boundary condition changing operator $\phi$.
+
+We assume that $\mathcal{F}$ contains some set of primary fields $\varphi_{\lambda_{i}}$ with conformal weights $h_{\lambda_{i}}$.
 Since we work with boundary CFT we need to add bulk fields in conjugate points $\bar z_{i}$.
 For future use in WZNW models we denote the conformal weights of these duplicate fields by $h_{\lambda_{i}^{*}}$.
-Also we have boundary condition changing operators  $\phi$ at the tip of SLE trace and in the infinity.
-We use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite this expression in upper half plane:
+Also we have boundary condition changing operators  $\phi$ at the tip of SLE trace and at the infinity.
+We use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite expression \eqref{eq:21} in the whole upper half plane:
 
@@
 \end{equation}
-By using Ito calculus we get the expression for the differential of $\mathcal{F}$:
+Using Ito calculus we get the expression for the differential of $\mathcal{F}$:
 \begin{equation}
@@
 \end{equation}
-We substitute \eqref{eq:2} and obtain the equation
+We substitute formula \eqref{eq:2} and obtain the equation
 \begin{equation}
@@
 In the case of minimal models the set of primary fields is finite and all the states are obtained through field-state correspondence \cite{belavin1984ics}, \cite{difrancesco1997cft}. 
-Equation \eqref{eq:24}  holds for arbitrary observable $\mathcal{O}$ and arbitrary primary fields $\varphi_{i}$, so $[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ is level two null field and $[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi(0)\left|0\right>$ is level two null-state.
+Equation \eqref{eq:24}  holds for arbitrary observable $\mathcal{O}$ and arbitrary primary fields $\varphi_{\lambda_{i}}$, so $\psi=[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ is level two null field and $\psi(0)\left|0\right>$ is level two null-state.
 There exist only two primary fields in minimal unitary models which give rise to Verma modules of Virasoro algebra with level two null-states.
@@
 \label{sec:sle-wzw-models}
-To generalize the analysis of previous section \ref{sec:corr-betw-sle} to non-minimal models we need to take additional symmetries into account.
-Wess-Zumino-Novikov-Witten models has Kac-Moody symmetry in addition to Virasoro algebra.
-At first we remind well-known properties of the model \cite{difrancesco1997cft} which are useful to study SLE martingales.
+To generalize the analysis of previous section \ref{sec:corr-betw-sle} to non-minimal models we need to take into account extra symmetries.
+Wess-Zumino-Novikov-Witten models has Kac-Moody symmetry in addition to conformal invariance leading to the appearance of Virasoro algebra.
+At first we remind well-known properties of WZNW-models \cite{difrancesco1997cft} which are useful to study SLE martingales.
 
@@
 
-Conserved currents of this model have following form:
+Conserved currents of this model have the following form:
   \begin{eqnarray}
@@
 
-Model possess gauge invariance under gauge transformations
+The model possesses gauge invariance under the transformations
   $g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)$, 
@@
 
-Expanding currents to modes
+Expanding the currents to modes
 $J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n $
 and using operator product expansion \eqref{eq:3} we get commutation relations of affine Lie algebra $\gfh$:
-$ \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0} $.
+\begin{equation*}
+ \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}.  
+\end{equation*}
 
@@
 There is infinite number of Virasoro primary fields, but they are organized into highest weight modules of affine Lie algebra $\gfh$. 
-Primary fields of full chiral algebra $\phi_{\lambda}$ are labeled by highest weights of affine Lie algebra $\gfh$ modules.
-Here we see how Virasoro and affine Lie algebra generators act on primary fields:
+Primary fields of full chiral algebra $\phi_{\lambda}$ are labeled by highest weights of  $\gfh$-modules. Here we see how Virasoro and affine Lie algebra generators act on primary fields:
   \begin{equation*}
@@
 \end{eqnarray}
-Using commutation relations \eqref{eq:92} these equations can be rewritten as algebraic equations connecting parameters of random motion $\kappa, \tau$ with the level $k$ of affine Lie algebra representation.
+Using commutation relations \eqref{eq:92} these equations can be rewritten as the algebraic equations connecting parameters of random motion $\kappa, \tau$ with the level $k$ of affine Lie algebra representation.
 Rigorous analysis of these equations is given in the paper \cite{alekseev2010sle}.
@@
 Denote by $J_{n}^{a}$ the generators of affine Lie algebra $\gfh$ and by $\tilde{J}_{n}^{b}$ the generators of $\afh$, so that $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b} J^{a}_{n}$.
-Virasoro generators in coset models are given by difference of Sugawara expressions of $\gf$ and $\af$-WZNW models:
+Virasoro generators in coset models are given by the difference of Sugawara expressions of $\gf$ and $\af$-WZNW models:
 \begin{equation*}
@@
 This equivalence is given by the action of so called ``simple currents'' $(J,\tilde{J})$, which are certain elements of outer  automorphisms group $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ of $\gfh\times\afh$, where $B(G)$ is center of Lie group G.
-We can think of simple currents as of primary fields and their action on fields of theory are given by fusion product \cite{difrancesco1997cft}.
-Then we must primary fields of coset model are given by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where $(J,\tilde J)$ such that their conformal weights are equal:  $h_{J}-h_{\tilde{J}}=0$.
+We can think of simple currents as of primary fields and their action on fields of theory are then given by fusion product \cite{difrancesco1997cft}.
+So primary fields of coset model are given by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where $(J,\tilde J)$ such that their conformal weights are equal:  $h_{J}-h_{\tilde{J}}=0$.
 
-Conformal weight of primary field is equal to
+Conformal weight of coset primary field is equal to
 \begin{multline}
@@
 \end{multline}
-It is possible to obtain analogues of KZ-equations for coset models \cite{kogan1997knizhnik}:
-\begin{equation*}
+It is possible to obtain analogues of Knizhnik-Zamolodchikov equations for coset models \cite{kogan1997knizhnik}:
+\begin{equation}
   \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
-\end{equation*}
+  \label{eq:6}
+\end{equation}
 
@@
 
-First we consider simple example. Let $G=SU(2)$ and $A=U(1)$, and corresponding Lie algebras $\gf=su(2)$, $\af=u(1)$, $\af\subset\gf$.
-The simplest way to study SLE on $G/A$ coset space is to restrict random walk on group manifold to the coset space by the choice of basis in $\gf$.
+To study SLE on $G/A$ factor space we restrict random walk on group manifold by the choice of basis in $\gf$.
 Assume that generators $\{J^{a};\; a=1\dots \mathrm{dim}\gf\}$ are chosen in such way that $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\; a=\mathrm{dim}\gf-\mathrm{dim}\af\dots \mathrm{dim}\gf\}$ are the generators of subalgebra $\af\subset \gf$.
@@
 
-Here $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$.
-Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
-We label weights by Dynkin labels, so $J^{3}_{0}\phi_{(\mu,\nu)}=\frac{\mu}{2} \phi_{(\mu,\nu)}$.
+Now consider simple example. Let $G=SU(2)$ and $A=U(1)$, and corresponding Lie algebras $\gf=\mathrm{su}(2)$
+with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$, $\af\subset\gf$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$. 
+%%We label weights by Dynkin labels, so $J^{3}_{0}\phi_{(\mu,\nu)}=\frac{\mu}{2} \phi_{(\mu,\nu)}$.
 
@@
 \end{equation}
-which are similar to the equations for parafermionic fields introduced in paper \cite{santachiara2008sle}.
+which is similar to the equations for parafermionic fields introduced in paper \cite{santachiara2008sle}.
 
@@
 The equation \eqref{eq:29} is trivial for $\phi_{(0,0)}$ and $\phi_{(0,2)}$, so the equations \eqref{eq:17}, \eqref{eq:28} are consistent although we do not know how to interpret $\tau$ in context of the Ising model.
-If we consider the field $\phi_{(1,1)}$ we have no solution for $\kappa,\tau$, so we see that not every primary field correspond to some boundary condition changing operator.
+If we consider the field $\phi_{(1,1)}$ we have no solution for $\kappa,\tau$, so we see that not every primary field corresponds to some boundary condition changing operator.
 
@@
 It is not always convenient to work with generators orthogonal with respect to Killing form $\mathcal{K}$, sometimes it is preferable to use Chevalley or Cartan-Weyl basis.
-So we introduce additional $\mathrm{dim}\gf$-dimensional Brownian motion \eqref{eq:18} with the normalization condition $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
-We need to consider Brownian motion on factor space $G/A$, the generator of field transformation \eqref{eq:2} is
+So we change normalization condition of additional $\mathrm{dim}\gf$-dimensional Brownian motion \eqref{eq:5} to $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation \eqref{eq:2} is
 \begin{equation*}
-  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right)
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right).
 \end{equation*}
-and we get \eqref{eq:8} martingale condition, which can be written as
+ Martingale condition  \eqref{eq:8} can be written as
 \begin{equation*}
@@
 \end{equation*}
-This equation can be rewritten as the requirement for
+This equation can again be rewritten as the requirement for
 \begin{equation}
@@
 
-To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} as was done for WZNW-models in paper \cite{alekseev2010sle}.
+To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov equations \eqref{eq:6} as was done for WZNW-models in paper \cite{alekseev2010sle}.
 
@@
 We proposed a way to generalize Schramm-Loewner evolution to obtain observables which can be studied by methods of coset conformal field theory.
-The description of fields in coset models is not very simple due to field identification \cite{schellekens1990field} and the need of resolution of fixed points \cite{Fuchs:1996dd,fuchs1996resolution} which we have not discussed here.
-This subtleties can complicate the solution of equations  \eqref{eq:28}, \eqref{eq:17} and analogues of equation \eqref{eq:29}.
-On the other hand the use of Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} for correlation functions in the spirit of \cite{alekseev2010sle} lead to matrix algebraic relations which are similar to NIM-representations for boundary states \cite{ishikawa2003novel}.
+The description of fields in coset models is not very simple due to field identification \cite{schellekens1990field} and the need of  fixed points resolution \cite{Fuchs:1996dd,fuchs1996resolution} which we have not discussed here.
+These subtleties can complicate the solution of equations  \eqref{eq:28}, \eqref{eq:17} and analogues of equation \eqref{eq:29}.
+On the other hand the use of Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} for correlation functions in the spirit of \cite{alekseev2010sle} leads to matrix algebraic relations which are similar to NIM-representations for boundary states \cite{ishikawa2003novel}.
 The study of this subject can reveal deep algebraic connection of martingale conditions with boundary states classification.
@@
 We think that these questions are closely related.
-\newpage
+
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+I thank the organizers of The Seventh International Conference ``Quantum Theory and Symmetries'' (QTS-7) for the opportunity to present this work and especially professor C.
+Burdik for his attention.
+I am grateful to A.
+Bytsko, K.
+Izyurov, D.
+Chelkak and R.
+Santachiara for the discussions on SLE and WZNW models.
+This work  is supported by
+the Chebyshev Laboratory (Department of Mathematics and Mechanics,
+Saint-Petersburg State University) under the grant 11.G34.31.0026
+of the Government of the Russian Federation.
 

### 2011-11-10 AffineLieAlgebras/Thesis/review.tex
Work on CFT section (axiomatics) + wzw moved to chapter 1

--- 2011-09-28 AffineLieAlgebras/Thesis/2.tex
@@
-%% \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
-%% \newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
-%% \newcommand{\co}[1]{\stackrel{\circ }{#1}}
-%% \newcommand{\pia}{\pi_{\mathfrak{a}}}
-%% \newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
-%% \newcommand{\gf}{\mathfrak{g}}
-%% \newcommand{\af}{\mathfrak{a}}
-\newcommand{\bff}{\mathfrak{b}}
-%% \newcommand{\afb}{\mathfrak{a}_{\bot}}
-%% \newcommand{\hf}{\mathfrak{h}}
-\newcommand{\hfg}{\hf_{\gf}}
-%% \newcommand{\hfb}{\mathfrak{h}_{\bot}}
-%% \newcommand{\pf}{\mathfrak{p}}
-%% \newcommand{\aft}{\widetilde{\mathfrak{a}}}
-
-\begin{abstract}
-%% Text of abstract
-In this paper we present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
-Algorithms are based on the properties of weights and Weyl symmetry.
-The most important problems for us are the ones, concerning computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition.
-These problems have numerous applications in physics and we provide some examples of these applications.
-The program is implemented in popular computer algebra system {\it Mathematica} and works with finite-dimensional and affine Lie algebras.
-
-% A submitted program is expected to be of benefit to other physicists or physical chemists, or be an exemplar of good programming practice, or illustrate new or novel programming techniques which are of importance to some branch of computational physics or physical chemistry.
-%
-% Acceptable program descriptions can take different forms.
-The following Long Write-Up structure is a suggested structure but it is not obligatory.
-Actual structure will depend on the length of the program, the extent to which the algorithms or software have already been described in literature, and the detail provided in the user manual.
-
-%Your manuscript and figure sources should be submitted through the Elsevier Editorial System (EES) by using the online submission tool at \\
-% http://www.ees.elsevier.com/cpc.
-
-%In addition to the manuscript you must supply: the program source code; job control scripts, where applicable; a README file giving the names and a brief description of all the files that make up the package and clear instructions on the installation and execution of the program; sample input and output data for at least one comprehensive test run; and, where appropriate, a user manual.
-These should be sent, via email as a compressed archive file, to the CPC Program Librarian at cpc@qub.ac.uk.
-
-\end{abstract}
-
-%%
-%% Start line numbering here if you want
-%%
-% \linenumbers
-
-% Computer program descriptions should contain the following
-% PROGRAM SUMMARY.
-
-{\bf PROGRAM SUMMARY}%/NEW VERSION PROGRAM SUMMARY}
-  %Delete as appropriate.
-
-\begin{small}
-\noindent
-{\em Manuscript Title:}{\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of finite-dimensional and affine Lie algebras                                       \\
-{\em Authors:}Anton Nazarov                                                \\
-{\em Program Title:}Affine.m                                          \\
-{\em Journal Reference:}                                      \\
-  %Leave blank, supplied by Elsevier.
-{\em Catalogue identifier:}                                   \\
-  %Leave blank, supplied by Elsevier.
-{\em Licensing provisions:}none                                   \\
-  %enter "none" if CPC non-profit use license is sufficient.
-{\em Programming language:}Mathematica                                   \\
-{\em Computer:}i386-i686, x86\textunderscore 64                                               \\
-  %Computer(s) for which program has been designed.
-{\em Operating system:} Linux, Windows, MacOS, Solaris                                       \\
-  %Operating system(s) for which program has been designed.
-{\em RAM:} 5-500 Mb                                              \\
-  %RAM in bytes required to execute program with typical data.
-%{\em Number of processors used:}                              \\
-  %If more than one processor.
-%{\em Supplementary material:}                                 \\
-  % Fill in if necessary, otherwise leave out.
-{\em Keywords:} Mathematica; Lie algebra; affine Lie algebra; Kac-Moody algebra; root system; weights; irreducible modules, CFT, Integrable systems\\
-  % Please give some freely chosen keywords that we can use in a
-  % cumulative keyword index.
-{\em Classification:} 5 Computer Algebra, 4.2 Other algebras and groups                                         \\
-  %Classify using CPC Program Library Subject Index, see (
-  % http://cpc.cs.qub.ac.uk/subjectIndex/SUBJECT_index.html)
-  %e.g. 4.4 Feynman diagrams, 5 Computer Algebra.
-%{\em External routines/libraries:}                            \\
-  % Fill in if necessary, otherwise leave out.
-%{\em Subprograms used:}                                       \\
-  %Fill in if necessary, otherwise leave out.
-%{\em Catalogue identifier of previous version:}*              \\
-  %Only required for a New Version summary, otherwise leave out.
-%{\em Journal reference of previous version:}*                  \\
-  %Only required for a New Version summary, otherwise leave out.
-%{\em Does the new version supersede the previous version?:}*   \\
-  %Only required for a New Version summary, otherwise leave out.
-{\em Nature of problem:}\\
-  %Describe the nature of the problem here.
-Representation theory of finite-dimensional Lie algebras has many applications in different branches of physics, including elementary particle physics, molecular physics, nuclear physics.
-Representations of affine Lie algebras appear in string theories and two-dimensional conformal field theory used for the description of critical phenomena in two-dimensional systems.
-Also Lie symmetries play major role in study of quantum integrable systems.
-   \\
-{\em Solution method:}\\
-  %Describe the method solution here.
-We work with weights and roots of finite-dimensional and affine Lie algebras and use Weyl symmetry extensively.
-Central problems which are the computations of weight multiplicities, branching and fusion coefficients are solved using one general recurrent algorithm based on generalization of Weyl character formula.
-We also offer alternative implementation based on Freudenthal multiplicity formula which can be faster in some cases.
-   \\
-%{\em Reasons for the new version:}*\\
-  %Only required for a New Version summary, otherwise leave out.
-%   \\
-%{\em Summary of revisions:}*\\
-  %Only required for a New Version summary, otherwise leave out.
-%   \\
-{\em Restrictions:}\\
-  %Describe any restrictions on the complexity of the problem here.
-Computational complexity grows fast  with the rank of algebra, so computations for algebra of rank greater than 8 are non practical.
-   \\
-{\em Unusual features:}\\
-  %Describe any unusual features of the program/problem here.
-We offer the possibility to use traditional mathematical notation for objects in representation theory of Lie algebras in computations if {\bf Affine.m} is used in {\it Mathematica} notebook interface.
-   \\
-%{\em Additional comments:}\\
-  %Provide any additional comments here.
-%   \\
-{\em Running time:}\\
-  %Give an indication of the typical running time here.
-From seconds to days depending on rank of algebra and complexity of representations.
-   \\
-
-% \begin{thebibliography}{0}
-% \bibitem{1}Reference 1         % This list should only contain those items referenced in the
-% \bibitem{2}Reference 2         % Program Summary section.
-% \bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
-%                                % This list is different from the bibliography at the end of
-%                                % the Long Write-Up.
-% \end{thebibliography}
-% * Items marked with an asterisk are only required for new versions
-% of programs previously published in the CPC Program Library.\\
-\end{small}
-
-%% main text
-\section{Introduction}
-\label{intro}
-
-Representation theory of Lie algebras is of central importance for different areas of physics and mathematics.
-In physics Lie algebras are used to describe symmetries of quantum and classical systems.
-Computational methods in representation theory have a long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
-
-Most popular programs \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{fischbacher2002ilp}, \cite{coxweyl} are created to study representation theory of simple finite-dimensional Lie algebras.
-The main computational problems are the following:
-\begin{enumerate}
-\item Construction of root system which determine the properties of Lie algebra including its commutation relations.
-\item Weyl group traversal which is important due to Weyl symmetry of root system and characters of representations.
-\item Calculation of weight multiplicities, branching and fusion coefficients, which are essential for construction and study of representations.
-\end{enumerate}
-There are well-known algorithms for these tasks \cite{moody1982fast}, \cite{stembridge2001computational}, \cite{belinfante1989survey}, \cite{casselman1994machine}.
-The third problem is most computation-intensive.
-There are two different recurrent algorithms which are based on the Weyl character formula and the Freudenthal multiplicity formula.
-In this paper we analyze them both.
-
-Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and in a study of  integrable systems.
-But infinite-dimensional algebras are much harder to investigate and the number of available computer programs is much smaller in this case.
-
-Affine Lie algebras \cite{kac1990idl} constitute important and tractable class of infinite-dimensional Lie algebras.
-They are constructed as central extensions of loop algebras of (semi-simple) finite-dimensional Lie algebras and appear naturally in a study of Wess-Zumino-Witten and coset models in conformal field theory \cite{Walton:1999xc}, \cite{difrancesco1997cft}, \cite{Goddard198588}, \cite{Dunbar:1992gh}.
-
-The structure of affine Lie algebras allows to adapt for them computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
-The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of affine Lie algebras and representations was published in 1990.
-But we are not aware of software packages for popular computer algebra systems which can be used to extend these results.
-We address this issue and present {\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.
-We describe the features and limitations of the package in the present paper.
-We also provide representation-theoretical background of implemented algorithms and present examples of computations relevant to physical applications.
-
-The paper starts with an overview of Lie algebras and their representation theory (Sec.
-\ref{sec:theor-backgr}).
-Then we describe datastructures of {\bf Affine.m} used to present different objects related to Lie algebras and representations (Sec.
-\ref{sec:core-datastructures}) and discuss implemented algorithms (Sec.
-\ref{sec:comp-algor}).
-Next section consists of physically interesting examples (Sec.
-\ref{sec:examples}).
-The paper is concluded with the discussion of possible extensions and refinements (Sec.
-\ref{sec:conclusion}).
-
-\section{Theoretical background}
-\label{sec:theor-backgr}
-
-In this section we remind necessary definitions and present formulae used in computations.
-
-\subsection{Lie algebras of finite and affine types}
-\label{sec:lie-algebras-finite}
-
-{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it Lie bracket}.
-If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
-\begin{equation}
-  \label{eq:1}
-  [X^{i},X^{j}]=\sum_{k} C^{ij}_{k} X^{k}
-\end{equation}
-Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to commutator.
-{\it Semisimple} Lie algebra is a direct sum of simple Lie algebras.
-In the present paper we treat simple and semisimple Lie algebras.
-
-{\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
-We denote the elements of basis of $\hfg$ by $H^{i}$.
-
-Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
-{\it Weights} are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
-
-Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
-This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).
-
-{\it Loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
-\begin{equation}
-  \label{eq:6}
-  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
-\end{equation}
-Central extension leads to the appearance of an additional term
-\begin{equation}
-  \label{eq:7}
-   [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
-\end{equation}
-This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
-
-We do not treat twisted affine Lie algebras in the present paper.
-
-\subsection{Modules, weights and roots}
-\label{sec:weights-roots}
-
-Let $\gf$ be a inite-dimensional or an affine Lie algebra.
-
-Then $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
-\begin{equation}
-  \label{eq:2}
-  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
-\end{equation}
-Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms of the  vector space $V$ with the commutator as a bracket.
-
-For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by a special choice of basis $\{v_{j}\}$ in $V$:
-\begin{equation}
-  \label{eq:3}
-  H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
-\end{equation}
-Eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
-Vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
-The  weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
-The weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of the weight subspace.
-
-The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
-\begin{equation}
-  \label{eq:5}
-  E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
-\end{equation}
-Module structure can be encoded by the formal character of a module
-\begin{equation}
-  \label{eq:10}
-  \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
-\end{equation}
-Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
-A character can be specialized by taking its value on some element $\xi$ of $\hf$.
-
-Lie algebra is its own module with respect to a special kind of representation. The action that
-defines this representation is called adjoint and is given by the bracket $ad_{X} Y=[X,Y]$. 
-{\it Roots} are weights of the adjoint representation of $\gf$.
-They encode the commutation relations of algebra in the following way.
-Denote by $\Delta$ the set of roots.
-For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and the generators $E^{\alpha}, E^{-\alpha}$ such that
-\begin{align}
-  \label{eq:4}
-  &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
-  &\left[E^{\alpha},E^{\beta}\right]=
-  \begin{cases}
-    N_{\alpha,\beta} E^{\alpha+\beta}, & \mbox{if}\; \alpha+\beta\in \Delta\\
-    \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
-    0,&\mbox{otherwise}
-  \end{cases}
-\end{align}
-
-Given the root system $\Delta$ we can choose the set of positive roots.
-This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
-Elements of $-\Delta^{+}$ are called negative roots.
-
-A positive root is {\it simple} if it cannot be written as a sum of positive roots.
-The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis in $\hfg^{*}$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive simultaneously.
-In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
-By numbering simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
-Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
-$\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}).
-{\it Comarcs} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
-
-Although for affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
-The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.
-The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- the highest root of the algebra $\go$.
-Note that root multiplicity $\mathrm{mult}(\alpha)$ for an affine Lie algebra root can be greater than one.
-
-Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called the Borel subalgebra.
-
-{\it Parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
-It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
-{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .
-
-The {\it Weyl group} $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
-\begin{equation}
-  \label{eq:8}
-  s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
-\end{equation}
-Root system and characters of representation are invariant with respect to the Weyl group  action. Root system can be reconstructed from the set of simple roots by the Weyl group transformations.
-
-Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
-
-Consider an action of the element $s_{\alpha}s_{\alpha+\delta}$ of the Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ being a simple root of the underlying finite-dimensional Lie algebra $\gf$.
-Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
-So the Weyl group can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to roots of $\gf$.
-
-A Weyl group element can be presented as a product of elementary reflections in multiple ways.
-Number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$.
-We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for the parity of the number of Weyl reflections generating $w$.
-
-Fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
-It is called a {\it main Weyl chamber}.
-
-The {\it Cartan matrix} $A$ is defined by products of simple roots
-\begin{equation}
-  \label{eq:9}
-  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}
-\end{equation}
-and can be used for a compact description of Lie algebra commutation relations in the Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
-
-Form \eqref{eq:9} induces a basis dual  to the simple
-roots basis. It is called the {\it fundamental weights basis}. We denote
-its elements by $\omega_i$:
-\begin{equation}
-  \label{eq:20}
-  \langle\omega_i,\alpha_j\rangle=\frac{2(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
-\end{equation}
-For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
-For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
-Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
-
- The sum of fundamental weights $\rho=\sum_{i} \omega_{i}$ is called a {\it Weyl vector}. It is an important tool in representation theory.
-
-\subsection{Highest weight modules}
-\label{sec:high-weight-modul}
-
-We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e.
-if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
-
-Highest weight module $V^{\mu}$ contains a single highest weight $\mu$, all the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
-
-The most simple type of highest weight modules is the Verma module
-$M^{\mu}$. Its space can be defined as a module
-\begin{equation}
-  \label{eq:17}
-  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}),
-\end{equation}
-with respect to a multiplication in $U(\gf)$ and
-$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
-Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
-Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D^{\lambda}(\bff_{+})$.
-
-Weight multiplicities in Verma modules can be found by applying the Weyl
-character formula
-\begin{equation}
-  \label{eq:11}
-  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
-\end{equation}
-Here we have used the Weyl denominator identity
-\begin{equation}
-  \label{eq:12}
-  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
-\end{equation}
-and $\epsilon \left( w\right) :=\det \left( w\right)$ is equal to 
-the parity of the sequence of Weyl reflections generating $w$.
-
-Verma module $M^{\mu}$ has the unique maximal submodule and the
-unique nontrivial simple quotient $L^{\mu}$ which is an
-{\it irreducible highest weight module}.
-
-Irreducible highest weight modules have no non-trivial submodules. 
-The Weyl character formula for
-irreducible highest weight modules is
-\begin{equation}
-  \label{eq:13}
-  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
-\end{equation}
-Thus the character of an irreducible highest weight module can be
-seen as a combination of characters of Verma modules. ( This
-fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
-(\cite{bernstein1976category,bernstein1971structure}, see also
-\cite{humphreys2008representations}).)
-
-Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
-%% !!! \Delta_{p}?!
-\begin{equation*}
-M_{I}^{\mu}=U\left( \gf\right)\otimes _{U\left( \pf_{I}\right) }L_{\pf_{I}}^{\mu}.
-\end{equation*}
-Introduce a formal element $R_{I}:=\prod_{\alpha \in \Delta
-^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
-^{\mathrm{mult}(\alpha )}$. Then the character of a generalized
-Verma module can be written as
-\begin{equation}
-  \label{eq:18}
-  \mathrm{ch}M_{I}^{\mu}=\frac{1}{R_{I}}\mathrm{ch}L_{\pf_{I}}^{\mu }.
-\end{equation}
-
-%% Define external border of irreducible representation here
-
-We can use the Weyl character formula to obtain recurrent relations for weight multiplicities -- important tools for calculations \cite{il2010folded,kulish4sfa}.
-
-For irreducible highest-weight modules recurrent relations have the following form
-\begin{equation}
-\label{eq:14}
-m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
--\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
-(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
-\end{equation}
-Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side.
-In case of Verma module it is just $\delta_{\xi,\mu}$.
-For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
-
-Other recurrent formula can be obtained from a study of Casimir
-elements action on irreducible highest weight modules
-\cite{humphreys1997introduction}:
-\begin{equation}
-  \label{eq:15}
-  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
-\end{equation}
-It is called the Freudenthal multiplicity formula.
-Note that it is applicable only to irreducible modules.
-
-We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.
-
-Now consider an algebra $\gf$ and a reductive subalgebra
-$\af\subset \gf$. Simple roots $\beta_{i}$ of the subalgebra $\af$
-can be presented as linear combinations of $\gf$-algebra roots
-$\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j}
-\alpha_{j},\ j=1,\dots,r_{\af}$.
-
-Each irreducible $\gf$-module is also an $\af$-module, although
-$L^{\mu}_{\gf}$ is in general not irreducible as $\af$-module. 
-It can be
-decomposed into a direct sum of irreducible $\af$-modules:
-\begin{equation}
-  \label{eq:16}
-  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
-\end{equation}
-Coefficients in such a decomposition are called branching
-coefficients.
-
-It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. 
-This traditional approach has serious limitations especially in case of affine Lie algebras. We discuss them in the end of section \ref{sec:comp-algor}.
-
-Now we describe an alternative approach which is based on recurrent properties of branching coefficients. 
-But before we proceed to these recurrent relations we need several additional definitions.
-
-For a subalgebra $\af\subset \gf$ we introduce the subalgebra
-$\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
-orthogonal to $\hf_{\af}$,
-\begin{equation*}
-\hf_{\perp \af}^{\ast }:=\left\{ \eta \in \hf^{\ast }|\forall
-h\in \hf_{\af};\eta \left( h\right) =0\right\} ,
-\end{equation*}
-and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
-to roots of $\af$,
-\begin{eqnarray}
-\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
-h\in \hf_{\af};\beta \left( h\right) =0\right\} ,
-\label{delta a ort} \\
-\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
-}^{+}|\forall h\in \hf_{\af};\beta ^{+}\left( h\right) =0\right\} .
-\notag
-\end{eqnarray}
-Let $W_{\afb}$ be a subgroup of $W$ generated by
-reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
-}}^{+}$. The subsystem $\Delta _{\afb}$ determines a 
-subalgebra $\afb$ with the Cartan subalgebra $\hf_{\af%
-_{\perp }}$.
-
-The Cartan subalgebra $\frak{h}$ can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
-\frak{h}_{\afb}\oplus \frak{h}_{\perp }$
-
-We also introduce the notations
-\begin{eqnarray}
-\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
-\qquad
-\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
-\end{eqnarray}
-
-For $\af$ and $\afb$ we consider the
-corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\af_{\perp
-}} $ and compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
-D}_{\afb}$ of the injection:
-\begin{equation}
-\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho , \qquad
-\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
-_{\perp }}\rho .  \label{defect-ort}
-\end{equation}
-
-%%!!! Define P^+
-For $\mu \in P^{+}$ consider the linked weights $\left\{ \left(
-w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections
-to
-$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
-\mathcal{D}_{\afb}$:
-\begin{equation*}
-\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
-w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
-\end{equation*}
-Among the weights $\left\{ \mu _{\af_{\perp
-}}\left( w\right) |w\in W\right\} $ one can always choose those located in
-the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
-set of representatives $u$ for the classes $W/W_{\afb}$ such
-that
-
-\begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
-\overline{C_{\afb}}\right\} \quad .  \label{U-def}
-\end{equation}
-Thus we can form the subsets:
-\begin{equation}
-\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
-\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
-_{\perp }},\quad u\in U,  \label{mu-a}
-\end{equation}
-and
-\begin{equation}
-\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
-\label{mu-a-tilda}
-\end{equation}
-
-Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
-since it is built on a subset of roots of the algebra $\mathfrak{g}$.
-
-Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients.
-If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.
-
-Now we can use the Weyl character formula to write a
-recurrent relation \cite{2010arXiv1007.0318L} for signed branching
-coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
-injection $\af\hookrightarrow \gf$:
-\begin{equation}
-\begin{array}{c}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
-_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
-\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right.  \\
-\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
-}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
-}\right) .
-\end{array}
-\label{recurrent-rel}
-\end{equation}
-The recursion is governed by the set $\Gamma _{\af\rightarrow \gf}$ called the injection fan. The latter is defined by the
-carrier set $\left\{ \xi \right\} _{\af\rightarrow \gf}$ for the
-coefficient function $s(\xi )$
-\begin{equation*}
-\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}:=\left\{
-\xi \in P_{\widetilde{\af}}|s(\xi )\neq 0\right\}
-\end{equation*}
-appearing in the expansion
-\begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
-_{\widetilde{\af}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
-_{\af}(\pi _{\widetilde{\af}}\alpha )}=-\sum_{\gamma \in P_{%
-\widetilde{\af}}}s(\gamma )e^{-\gamma };\quad
-\end{equation}
-The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
-\right\} $ -- and the zero element is to be eliminated:
-\begin{equation}
-\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma
-_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
-\end{equation}
-Formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
-
-If the root system of $\afb$ is generated by some subset of $\gf$
-simple roots $\alpha_{1},\dots,\alpha_{r}$ then the recurrent
-relation (\ref{recurrent-rel}) is connected with the generalized
-Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules
-\cite{2011arXiv1102.1702L}.
-
-Another particular case of this formula is connected with tensor
-product decompositions. Consider the tensor product of two
-irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$. It is also a
-$\gf$-module but not irreducible in general. So
-\begin{equation}
-  \label{eq:19}
-  L^{\mu}\otimes L^{\nu}=\bigoplus_{\gamma} f^{\mu\nu}_{\gamma}L^{\gamma}
-\end{equation}
-The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion
-coefficients. The problem of computation of fusion coefficients is
-equivalent to branching problem for the diagonal subalgebra
-$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
-
-In the case of affine Lie algebras $\gf, \af$  the multiplicities
-$m_{\nu}$ and the corresponding branching coefficients $b_{\nu}$
-can be regarded as the coefficients in power series decomposition
-of string and branching functions correspondingly:
-\begin{align}
-  \label{eq:21}
-  &\sigma_{\nu}(q)=\sum_{n=0}^{\infty} m_{\nu-n\delta} q^n, \quad \nu=\sum_j c_j \omega_j,\quad c_j\geq 0\\
-  & b_{\nu}(q)=\sum_{n=0}^{\infty} b_{\nu-n\delta} q^n,\quad  \nu=\sum_j c_j \omega_j, \quad c_j\geq 0
-\end{align}
-String and branching functions have  modular and analytic properties which are important for conformal field theory, especially in  coset models and the study of CFT on higher genus surfaces \cite{kac1988modular}, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}.
-
-{\bf Affine.m}  calculates weight multiplicities and branching coefficients for affine Lie algebras up to some finite grade.
-We present examples of computations in Sections \ref{sec:string-funct-affine}, \ref{sec:branch-funct-coset}.
-Now we proceed to the description of datastructures and algorithms implemented in {\bf Affine.m}.
-
-\section{Core datastructures}
-\label{sec:core-datastructures} Having introduced necessary
-mathematical objects, problems and relations we now describe the
-related datastructures of {\bf Affine.m}. Although {\it
-Mathematica} is untyped language it is possible to create
-structured objects and do type checks with patterns
-\cite{shifrinmathematica}, \cite{maeder2000computer}.
-\subsection{Weights}
-\label{sec:weights}
-
-Weights are represented  by two data-structures: \lstinline{finiteWeight} for finite-dimensional Lie algebras and \lstinline{affineWeight}  for affine.
-
-Internally the finite weight is a \lstinline{List} with the
-\lstinline{Head} \lstinline{finiteWeight}, its components are the
-coordinates of the weight in the orthogonal Bourbaki  basis
-\cite{bourbaki2002lie}.
-
-Affine weight is an extension of a finite weight by supplying it
-with level and grade coordinates. There is a set of functions
-defined for finite and affine weights. The complete list can be
-found in  online help of the package. The most important
-are definitions of addition, multiplication by a number and a
-scalar product (bilinear form) for weights. These definitions
-allow to use traditional notation when working with {\bf
-Affine.m}:
-\begin{lstlisting}
-  w=makeFiniteWeight[{1,0,3}];
-  v=makeFiniteWeight[{3,2,1}];
-  2*w+v==makeFiniteWeight[{5,2,7}]
-  w.v==6
-\end{lstlisting}
-
-The use of orthogonal basis in the internal structure of weights allows us to work with weights without complete specification of root system which is useful for study of branching, since roots of the subalgebra can be specified by hand.
-
-\subsection{Root systems}
-\label{sec:root-systems}
-
-To specify an algebra of finite or affine type it is enough to fix
-its root system. Root systems are represented by two datatypes
-\lstinline{finiteRootSystem} and \lstinline{affineRootSystem}. The
-latter is an extension of the former. We offer several different
-constructors for these datastructures. It is possible to specify
-the set of simple roots explicitly, for example to study the
-subalgebra $B_2\subset B_4$ we can use the definition
-\begin{lstlisting}
-  b2b4=makeFiniteRootSystem[ { {1,-1,0,0}, {0,1,0,0} } ]
-\end{lstlisting}
-There are constructors for root systems of simple finite-dimensional Lie algebras:
-\begin{lstlisting}
-  b2=makeSimpleRootSystem[B,2]
-\end{lstlisting}
-We use typographic features of {\it Mathematica} frontend to offer mathematical notation for simple Lie algebras:
-
-\begin{lstlisting}[mathescape=true]
-  $B_2$ == makeFiniteRootSystem[ { {1, -1}, {0, 1} }]
-\end{lstlisting}
-
-Non-twisted affine root systems can be created as affine extensions of finte root systems, e.g.
-\begin{lstlisting}
-  b2affine = makeAffineExtension[b2]
-\end{lstlisting}
-In notebook interface this can be written simply as $\hat{B}_2$.
-
-Semisimple Lie algebras can be created as sums of simple:
-\begin{lstlisting}[mathescape=true]
-  $A_1\oplus A_1$ == finiteRootSystem[2, 2, {finiteWeight[2, {1, 0}], finiteWeight[2, {0, 1}]}]
-\end{lstlisting}
-%% The problem is here
-
-Predicate \lstinline{rootSystemQ} checks if the object is root systems of finite or affine type.
-
-List of simple roots is the property of root system so it is accessed as \lstinline{rs[simpleRoots]}.
-
-We have implemented several functions to get major properties of root systems. Weyl vector is given by the function \lstinline{rho[rs_?rootSystemQ]}:
-\begin{lstlisting}[label=list:1]
-  In[1]  =  rho[b2]
-  Out[1]  =  finiteWeight[2, {3/2, 1/2}]
-\end{lstlisting}
-Positive roots can be constructed with \lstinline{positiveRoots[rs_?rootSystemQ]}.
-For an affine Lie algebra this and related functions return the list up to fixed grade.
-This grade limit is set through the value of \lstinline{rs[gradeLimit]} which is equal to 10 by default.
-List of roots (up to \lstinline{gradeLimit}) is returned by \lstinline{roots[rs]}.
-Cartan matrix and fundamental weights are calculated by the functions \lstinline{cartanMatrix} and \lstinline{fundamentalWeights} correspondingly.
-
-It is possible to specify a weight of a Lie algebra by its Dynkin labels
-\begin{lstlisting}
-  weight[b2][1,2] == makeFiniteWeight[{2, 1}]
-\end{lstlisting}
-The function \lstinline{dynkinLabels[rs_?rootSystemQ][wg_?weightQ]} returns Dynkin labels of weight \lstinline{wg} in the root system \lstinline{rs}.
-
-Elements of Weyl group are specified by the set of indices of reflections, so the element  $w=s_{1}s_{2}s_{1}$ of the Weyl group of algebra $B_{2}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
-Then it can be applied to the weights:
-\begin{lstlisting}
-  w = weylGroupElement[b2][1,2,1];
-  w @ makeFiniteWeight[{1,0}] == makeFiniteWeight[{-1,0}]
-\end{lstlisting}
-
-Computation of lexicographically minimal form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching in {\it Mathematica}.
-In \cite{KallenShortlex} rewrite rules for simple finite dimensional and affine Lie algebras are presented as {\it Mathematica} patterns.
-Our presentation of Weyl group elements is compatible with the code of \cite{KallenShortlex}
-\begin{lstlisting}[mathescape=true]
-  In[1]  = $<<$A3reduce;
-           reduce[s[1,2,1,2,1,3,2,1,1]]
-  Out[1] = s[2, 3, 2]
-
-  In[2]  = (weylGroupElement[$A_{3}$] @@ reduce[s[1,2,1,2,1,3,2,1,1]]) @ weight[$A_{3}$][-1,-2,-1]
-  Out[2] = finiteWeight[4, {-2, 2, 1, -1}]
-
-  In[3]  = dynkinLabels[$A_{3}$][Out[2]]
-  Out[3] = {-4, 1, 2}
-\end{lstlisting}
-
-\subsection{Formal elements}
-\label{sec:formal-elements}
-
-We represent formal characters of representations by special structure \lstinline{formalElement}.
-This structure is a hash-table implemented with \lstinline{DownValues}.
-The keys are weights at the exponents and the values are the  corresponding multiplicities.
-\lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]!
-creates data-structure which represents the element $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ of the formal algebra $\mathcal{E}$.
-The operations in $\mathcal{E}$ are implemented for \lstinline{formalElement} data-type: formal elements can be added, multiplied by a number or by an exponent of a weight.
-There exists also a multiplication of formal elements but no division.
-\begin{lstlisting}[mathescape=true]
-  In[1]  = makeFormalElement[{makeFiniteWeight[{1,1}],makeFiniteWeight[{0,0}]},{1,2}] *
-             (2 * Exp[makeFiniteWeight[{1,0}]] *
-             makeFormalElement[{makeFiniteWeight[{1,1}],makeFiniteWeight[{0,0}]},{1,2}]);
-  In[2]  = In[1][weights]
-  Out[2] = {finiteWeight[2, {1, 0}], finiteWeight[2, {2, 1}], finiteWeight[2, {3, 2}]}
-
-  In[3]  = In[1][multiplicities]
-  Out[3] = {8, 8, 2}
-\end{lstlisting}
-
-\subsection{Modules}
-\label{sec:modules}
-
-{\bf Affine.m} can be used to study different kinds of modules, i.e.
-Verma modules, irreducible modules and parabolic Verma modules.
-We need datastructure \lstinline{module} to represent generic module of Lie algebra $\gf$.
-Module properties can be deduced from its set of singular weights using Weyl character formulae \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}.
-Set of singular weights can have Weyl symmetry.
-It can be a symmetry with respect to the Weyl group $W_{\gf}$ or with respect to some subalgebra $W_{\af}$ as in the case of parabolic Verma modules.
-Then it is possible to study only the main Weyl chamber $C_{\af}$.
-To use this symmetry generic constructor for \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],limit:10}.
-Here \lstinline{rs} is the root system of the Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is the root system corresponding to the Weyl group $W_{\af}$ which is the (anti-)symmetry of the set of singular weights.
-Parameter \lstinline{limit} limits computation for infinite-dimensional modules such as Verma or parabolic Verma.
-There are several specialized constructors for different types of highest weight modules:
-\begin{lstlisting}[mathescape=true]
-vm=makeVermaModule[$B_{2}$][{2,1}];
-pm=makeParabolicVermaModule[$B_{2}$][weight[$B_{2}$][2,1],{1}];
-im=makeIrreducibleModule[$B_{2}$][2,1];
-GraphicsRow[textPlot/@{im,vm,pm}]
-$\includegraphics[width=130mm]{figures/irrep-verma-pverma.pdf}$
-\end{lstlisting}
-
-As we already stated properties of a module are encoded by its singular element.
-Function \lstinline{singularElement[m_module]} returns singular element of a module as \lstinline{formalElement} datastructure.
-Character (up to \lstinline{limit} for (parabolic) Verma modules) is returned by the function \lstinline{character[m_module]}.
-Direct sum of modules is a module and we use natural notation
-\begin{lstlisting}[mathescape=true]
-im1=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
-im2=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][1,2]];
-textPlot[im1$\oplus$ im2]
-$\includegraphics[width=60mm]{figures/irrep-sum.pdf}$
-\end{lstlisting}
-
-The tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
-\begin{lstlisting}[mathescape=true]
-textPlot[makeIrreducibleModule[$A_{1}$][5]$\otimes$ makeIrreducibleModule[$A_{1}$][3]];
-$\includegraphics[width=60mm]{figures/tensor-product.pdf}$
-\end{lstlisting}
-\section{Computational algorithms}
-\label{sec:comp-algor}
-
-As we have already stated in section \ref{sec:high-weight-modul} there exist two recurrent relations which can be used to calculate weight multiplicities in irreducible modules.
-Both algorithms proceed in the following way to calculate weight multiplicities:
-\begin{enumerate}
-\item Create the list of weights in the main Weyl chamber by subtracting all possible combinations of simple roots from the highest weight (e.g.
-for finite-dimensional algebra subtract $\alpha_{1}$ from $\mu$ while inside $\bar C$, then subtract $\alpha_{2}$ from all the weights already obtained etc).
-\item Sort the list of weights by their product with the Weyl vector.
-\item Use a recurrent formula. If the weight required for recurrent computation is outside the main chamber use the Weyl symmetry.
-\end{enumerate}
-The difference in the performance of algorithms is in the number of previous values required to get the multiplicity of weight under consideration.
-For  the Weyl formula based recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in the Weyl group (if we are far from the boundary of representation diagram).
-When the Freudenthal formula \eqref{eq:15} is used number of previous values grows with the distance from the external border of representation.
-So the Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
-Note that the Freudenthal formula is valid for irreducible modules only, so it can not be used to study (generalized) Verma modules.
-
-We have made some experiments with our implementations of the Freudenthal formula and formula \eqref{eq:15} and have got Figure  \ref{fig:freudenthal-racah-times}, which depicts the dependence of the computation time on the number of weights in a module.
-
-\begin{figure}[h]
-  \noindent\centering{
-    \includegraphics[width=80mm]{figures/timing.pdf}
-  }
-  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{eq:14} (solid) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
-\label{fig:freudenthal-racah-times}
-
-\end{figure}
-
-In the calculation of branching coefficients the application of the Freudenthal formula requires a complete construction of formal characters of an algebra module and all the representations of a subalgebra.
-It is impractical when the rank of algebra and subalgebra are big, for example for maximal subalgebras.
-
-Alternative algorithm which was presented in the paper \cite{2010arXiv1007.0318L}  contains the following steps:
-
-\begin{enumerate}
-\item  Construct the root system $\Delta _{\af}$ for the embedding $%
-\af\rightarrow \frak{g}$.
-
-\item  Select all the positive roots $\alpha \in \Delta ^{+}$ orthogonal
-to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
-
-\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. Relation
- (\ref{eq:6}) defines the sign function
- $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
- $\gamma_0$ is to be subtracted to get the fan:
- $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}$.
-
-\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
-)-\rho ;\;w \in W\right\} $ of singular weights for the $\frak{g}$%
--module $L^{(\mu )}$.
-
-\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
-}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
-)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
-\af_{\perp }}}}\right\} $. Since the set $\Delta_{\afb }^{+}$ is fixed
-we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
-}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
-\af_{\perp }}}}$ (by computing its scalar product with the fundamental
-weights of $\afb^{+}$).
-
-\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
-calculate dimensions of the corresponding modules, $\mathrm{\dim }\left(
-L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
-}\left( u\right) }\right) $, using the Weyl dimension formula and construct
-the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
-
-\item  Calculate the anomalous branching coefficients using 
-recurrent relation (\ref{recurrent-rel}) and select among them those
-corresponding to the weights in the main Weyl
-chamber $\overline{C_{\af}}$.
-\end{enumerate}
-
-We can speed up the algorithm by
-one-time computation of the representatives of the conjugate classes $%
-W/W_{\afb }$.
-
-Consider the regular embedding $B_{2}\subset B_{4}$.
-In this case the fan consists of 24 elements.
-In order to decompose $B_{4}$ module we need to construct the subset of singular weights of the module which projects to the main Weyl chamber of the subalgebra $B_{2}$.
-The full set of singular weights consists of 384 elements.
-The required subset contains at most 48 elements.
-So the time for the construction of this required subset is negligible if the number of branching coefficients is greater than that.
-We may estimate the total number of required operations for the computation of branching coefficients as the product of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients and the number of elements in the fan.
-In the case of a direct algorithm we need to compute the multiplicities for each module in the decomposition, so the number of operations grows faster than the square of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients.
-
-To further illustrate this performance issue we include Figure \ref{fig:branching} where we show the time required for computations of branching coefficients for $B_{3}\subset B_{4}$.
-
-\begin{figure}[h]
-  \noindent\centering{
-   \includegraphics[width=100mm]{figures/branching-timing.pdf}
-  }
-  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{recurrent-rel} (solid) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
-  \label{fig:branching}
-\end{figure}
-
-\section{Examples}
-\label{sec:examples}
-In this section we present some examples of computations available with {\bf Affine.m} with the code required to produce these results.
-
-\subsection{Tensor product decompositon for finite-dimensional Lie algebras}
-\label{sec:tens-prod-decomp}
-
-Computation of fusion coefficients for the decomposition of tensor product of highest-weight modules to the direct sum of irreducible modules has numerous applications in physics.
-For example, we can consider the spin of a composite system such as an atom.
-Another interesting example is integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of a Lie algebra $\gf$ with a $\gf$-invariant Hamiltonian $H$, describing the nearest-neighbour spin-spin interaction.
-In order to solve such a system, i.e.
-to find eigenstates of the Hamiltonian, we need to decompose $L^{\otimes N}$ into the direct sum of irreducible $\gf$-modules of lower dimension and diagonalize the Hamiltonian on these modules.
-
-For fundamental representations of simple Lie algebras it is sometimes possible to get an analytic result describing the dependence of decomposition coefficients on $N$ (See \cite{LyakhovskyPostnova2011}).
-Our code provides numerical values and can be used to check this analytic results.
-
-Consider a tensor power of $B_{2}$ the first fundamental representation $\left(L^{[1,0]}\right)^{\otimes 4}$. Decomposition coefficients are just the branching
- coefficients for the tensor power module reduced to the diagonal subalgebra $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$. So the following code calculates these coefficients:
-\begin{lstlisting}[mathescape=true]
-fm = makeIrreducibleModule[$B_{2}$][1, 0];
-tp = ((fm$\otimes$ ]fm)$\otimes$ fm)$\otimes$]fm;
-subs = makeFiniteRootSystem[
-  {1/4*{1, -1, 1, -1, 1, -1, 1, -1}, 
-   1/4*{0, 1, 0, 1, 0, 1, 0, 1}}];
-bc = branching[tp, subs];
-{bc[#], dynkinLabels[subs][#]} & /@ bc[weights]
-\end{lstlisting}
-It produces a list of highest weights and tensor product decomposition coefficients:
-\begin{lstlisting}
-{{1, {4, 0}}, {3, {2, 2}}, {0, {3, 0}}, 
-{2, {0, 4}}, {3, {1, 2}}, {6, {2, 0}}, 
-{6, {0, 2}}, {1, {1, 0}}, {3, {0, 0}}}]
-\end{lstlisting}
-
-Returning to the problem of spin chain Hamiltonian diagonalization we can see that instead of diagonalizing operator in space of dimension $625$ we can diagonalize operators in the spaces of dimensions $55, 81, 30, 35, 35, 14, 10, 5, 1$.
-
-\subsection{Branching and parabolic Verma modules}
-\label{sec:branch-parab-verma}
-
-We illustrate the generalized BGG-resolution by the diagrams of $G_{2}$ parabolic Verma modules which appear in the decomposition of irreducible module $L^{[1,1]}_{G_{2}}$:
-\begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
-u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
-u\right) }.  \label{char-in-gen-verma-mod}
-\end{equation}
-The character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, characters of the generalized Verma modules in decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}.
-Characters in the upper row appear in \eqref{char-in-gen-verma-mod} with positive sign and in the lower row -- with negative.
-
-\begin{figure}[h]
-  \noindent\centering{
-    \includegraphics[width=80mm]{figures/G2-irrep.pdf}
-  }
-  \caption{Character of the irreducible $G_{2}$-module $L^{[1,1]}$}
-  \label{branching-bgg}
-\end{figure}
-\begin{figure}[h]
-  \noindent\centering{
-    \includegraphics[width=150mm]{figures/G2-pverma.pdf}
-  }
-  \caption{Characters of $G_{2}$ generalized Verma modules appearing in the decomposition of $L^{[1,1]}$.
-Parabolic Verma modules in the upper row appear in the decomposition with a positive sign, in the lower row -- with a negative.}
-  \label{g2-pverma}
-\end{figure}
-
-\subsection{String functions of affine Lie algebras and CFT models}
-\label{sec:string-funct-affine}
-
-String functions can be used to present formal characters of affine Lie algebra highest weight representation.
-They have interesting analytic and modular properties \cite{kac1990idl,kac1988modular,kac1984infinite}.
-
-{\bf Affine.m} produces power series decomposition for string functions.
-Consider an affine Lie algebra $\hat{sl(3)}=\hat A_{2}$ and its highest weight module $L^{(1,0,0)}$.
-To get the string functions we can use the code:
-\begin{lstlisting}[mathescape=true]
-stringFunctions[$\hat A_2$,{1,1,2}]
-{{0, 0, 4}, 
-  $2 q + 10 q^2 + 40 q^3 + 133 q^4 + 398 q^5 + 1084 q^6 + 2760 q^7 + 6632 q^8 + 15214 q^9 + 33508 q^{10}$}, 
-{{0, 3, 1}, 
-  $2 q + 12 q^2 + 49 q^3 + 166 q^4 + 494 q^5 + 1340 q^6 + 3387 q^7 + 8086 q^8 + 18415 q^9 + 40302 q^{10}$}, 
-{{1, 1, 2}, 
-  $1 + 6 q + 27 q^2 + 96 q^3 + 298 q^4 + 836 q^5 + 2173 q^6 + 5310 q^7 + 12341 q^8 + 27486 q^9 + 59029 q^{10}$}, 
-{{2, 2, 0}, 
-  $1 + 8 q + 35 q^2 + 124 q^3 + 379 q^4 + 1052 q^5 + 2700 q^6 + 6536 q^7 + 15047 q^8 + 33248 q^9 + 70877 q^{10}$}, 
-{{3, 0, 1}, 
-  $2 + 12 q + 49 q^2 + 166 q^3 + 494 q^4 + 1340 q^5 + 3387 q^6 + 8086 q^7 + 18415 q^8 + 40302 q^9 + 85226 q^{10}$}
-\end{lstlisting}
-Similarly for the affine Lie algebra $\hat G_{2}$ we get
-\begin{lstlisting}[mathescape=true]
-stringFunctions[$\hat G_2$,{1,1,0}]
-{{2, 0, 0}, 
-  $1 + 8 q + 37 q^2 + 138 q^3 + 431 q^4 + 1227 q^5 + 3208 q^6 + 7901 q^7$}, 
-{{0, 0, 1}, 
-  $3 q + 18 q^2 + 73 q^3 + 247 q^4 + 736 q^5 + 2000 q^6 + 5070 q^7$}, 
-{{1, 1, 0},
-  $1 + 7 q + 32 q^2 + 117 q^3 + 370 q^4 + 1055 q^5 + 2780 q^6 + 6880 q^7$}, 
-{{0, 2, 0}, 
-  $3 q + 15 q^2 + 63 q^3 + 210 q^4 + 633 q^5 + 1725 q^6 + 4407 q^7$}
-\end{lstlisting}
-
-\subsection{Branching functions and coset models of conformal field theory}
-\label{sec:branch-funct-coset}
-
-It is believed that most rational models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$.
-These models can be studied as gauge theories \cite{Hwang:1994yr, hwang1993brst}.
-
-Branching functions for an embedding $\af\subset\gf$ are the partition functions of CFT on the torus (see \cite{difrancesco1997cft}).
-
-As a first example we show how to construct branching functions for the embedding $\hat A_{1}\to \hat B_{2}$ up to the tenth grade:
-\begin{lstlisting}[mathescape=true]
-branchingFunctions[$\hat B_{2}$,makeAffineExtension[makeFiniteRootSystem[{{1, 1}}]], {1, 1, 1}]
-
- {{3, 0}, 
-  $2 + 14 q + 52 q^2 + 154 q^3 + 410 q^4 + 994 q^5 + 2248 q^6 + 4832 q^7 + 9934 q^8 + 19680 q^9 + 37802 q^{10}$},
- {{2, 1}, 
-  $4 + 20 q + 72 q^2 + 220 q^3 + 584 q^4 + 1424 q^5 + 3248 q^6 + 7012 q^7 + 14488 q^8 + 28844 q^9 + 55616 q^{10}$},
- {{0, 3}, 
-  $4 q + 20 q^2 + 68 q^3 + 200 q^4 + 516 q^5 + 1224 q^6 + 2736 q^7 + 5808 q^8 + 11820 q^9 + 23236 q^{10}$},
- {{1, 2}, 
-  $2 + 14 q + 54 q^2 + 168 q^3 + 462 q^4 + 1148 q^5 + 2656 q^6 + 5812 q^7 + 12130 q^8 + 24358 q^9 + 47328 q^{10}$}
-\end{lstlisting}
-
-Another example demonstrates the computation of branching functions for the regular embedding $\hat B_{2}\subset \hat C_{3}$:
-\begin{lstlisting}[mathescape=true]
-sub=makeAffineExtension[parabolicSubalgebra[$C_{3}$][2,3]];
-branchingFunctions[$\hat C_{3}$,sub, {2, 0, 0, 0}]
-
-{{0, 1, 0}, 
-  $2 q - 20 q^3 + 24 q^4 + 82 q^5 - 320 q^6 + 108 q^7$}, 
-{{1, 0, 0}, 
-  $1 - q - 8 q^2 + 19 q^3 + 16 q^4 - 156 q^5 + 205 q^6 + 640 q^7$}, 
-{{0, 0, 1}, 
-  $q - 5 q^3 + 7 q^5$}
-\end{lstlisting}
-
-\section{Conclusion}
-\label{sec:conclusion}
-We have presented the package {\bf Affine.m} for computations in representation theory of finite-dimensional and affine Lie algebras.
-It can be used to study Weyl symmetry, root systems, irreducible, Verma and parabolic Verma modules of finite-dimensional and affine Lie algebras.
-In the present paper we have also discussed main ideas used for an implementation of the package and described most important notions of representation theory required to use {\bf Affine.m}.
-
-We have demonstrated that recurrent approach based on the Weyl character formula is not only useful for calculations but also allows to establish connections with the (generalized) Bernstein-Bernstein-Gelfand resolution.
-
-Also we have presented examples of computations with this package connected with problems of physics and mathematics.
-
-In future versions of our software we are going to treat twisted affine Lie algebras, extended affine Lie algebras and provide more direct support for tensor product decompositions.
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-I thank V.D. Lyakhovsky and O.Postnova for discussions and helpful comments.
-
-The work is supported by the Chebyshev Laboratory
-(Department of Mathematics and Mechanics, Saint-Petersburg State
-University) under the grant 11.G34.31.0026 of the Government of the
-Russian Federation.
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-\appendix
-
-\section{Software package}
-\label{package}
-The package can be freely downloaded from \url{http://github.com/naa/Affine}. To get the development code use the command
-\begin{lstlisting}[language=bash]
- git clone git://github.com/naa/Affine.git
-\end{lstlisting}
-
-Contents of the package:
-\begin{verbatim}
-    Affine/                                root folder
-      demo/                                  demonstrations
-        demo.nb                                demo notebook
-        paper.nb                               code for the paper
-      doc/                                 documentation folder
-        figures/                             figures in paper 
-          timing.pdf                           diagram showing performance
-          branching-timing.pdf                 ...  for branching coefficients  
-          irrep-sum.pdf                        sum of B2 irreps
-          irrep-verma-pverma.pdf               irrep, Verma, (p)Verma for B2
-          G2-irrep.pdf                         irrep for G2
-          G2-pverma.pdf                        parabolic Verma for G2
-          tensor-product.pdf                   tensor product of A1-modules
-        bibliography.bib                     bibliographic database
-        paper.pdf                            present paper
-        paper.tex                            paper source
-        TODO.org                             list of issues
-      src/                                 source folder
-        affine.m                             main software package
-      tests/                               unit tests folder
-        tests.m                              unit tests
-      README.markdown                      installation and usage notes
-\end{verbatim}
-
-%% References
-%%
-%% Following citation commands can be used in the body text:
-%% Usage of \cite is as follows:
-%%   \cite{key}         ==>>  [#]
-%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
-%%
-
-%% References with bibTeX database:
-
-  %   \section*{References}
-  %   \label{sec:references}
-  %   
-  %   
-  %   \bibliography{bibliography}
-  %   \bibliographystyle{phcpc}
-  %   %\bibliographystyle{model1-num-names}
-  %   
-  %   
-  %   %% Authors are advised to submit their bibtex database files. They are
-  %   %% requested to list a bibtex style file in the manuscript if they do
-  %   %% not want to use elsarticle-num.bst.
-  %   
-  %   %% References without bibTeX database:
-  %   
-  %   % \begin{thebibliography}{00}
-  %   
-  %   %% \bibitem must have the following form:
-  %   %%   \bibitem{key}...
-  %   %%
-  %   
-  %   % \bibitem{}
-  %   
-  %   % \end{thebibliography}
-  %   
-  %   
-  %
+\review
 

### 2011-11-10 AffineLieAlgebras/Thesis/1.tex
Work on CFT section (axiomatics) + wzw moved to chapter 1

@@
+\chapter{Конформная теория поля}
+\label{cha:CFT}
+
+Двумерная конформная теория поля возникла при изучении моделей критического поведения в двумерных моделях и привлекла большое внимание благодаря новым идеям и своей связи с теорией струн.
+Двумерная конформная теория поля выделяется как модель квантовой теории поля из-за того, что она может быть сформулирована аксиоматически, например, следующим образом.
+Введем пространство $S(\mathbb{R}^{n})$ тест-функций $f:\mathbb{R}^{n}\to \mathbb{C}$.
+Распределения или обобщенные функции -- это линейные функционалы на нем $T:S(\mathbb{R}^{n})\to \mathbb{C}$ со свойством непрерывности.
+Каждой функции $g:\mathbb{R}^{n}\to \mathbb{C}$ можно поставить в соответствие некоторое распределение $T_{g}$ по правилу
+\begin{equation}
+  \label{eq:30}
+  T_{g}(f)=\int_{\mathbb{R}^{n}}g(x)f(x) dx
+\end{equation}
+На пространстве обобщенных функций можно ввести операторы дифференцирования с мультииндексами $\alpha$:
+\begin{equation}
+  \label{eq:41}
+  \partial^{\alpha}:=(-1)^{|\alpha|}T(\partial^{\alpha} f)
+\end{equation}
+При этом
+\begin{equation}
+  \label{eq:42}
+  \partial^{\alpha}T_{g}=T_{\partial ^{\alpha}g}
+\end{equation}
+и для любой обобщенной функции $T$ есть $n\in \mathbb{N}$, такое что
+\begin{equation}
+  \label{eq:49}
+  T=\sum_{0\leq |\alpha|\leq n}\partial^{\alpha} T_{g_{\alpha}}.
+\end{equation}
+В квантовой теории поля должны быть поля и состояния.
+Состояния определяются как элементы некоторого гильбертова пространства $\mathbb{H}$.
+Пространство операторов на $\mathbb{H}$ мы обозначим через $\mathcal{O}$.
+Тогда поля -- это операторно-значные распределения $\varphi:S(\mathbb{R}^{n})\to \mathcal{O}$, такие, что существует плотное подпространство $D\subset \mathbb{H}$ и
+\begin{enumerate}
+\item Для любой тест-функции $f\in S(\mathbb{R}^{n})$ подпространство $D\subset D_{\varphi(f)}$, где $D_{\varphi(f)}$ -- область определения оператора $\varphi(f)$.
+\item Индуцированное отображение $f\to \varphi(f)|_{D}$ из $S(\mathbb{R}^{n})$ в $\mathrm{End}(D)$ линейно.
+\item Для любых $\nu\in D$ и $\omega\in \mathbb{H}$ отображение $f\to \left<\omega,\varphi(f)(\nu)\right>$ является распределением. 
+\end{enumerate}
+Можно определять конформную теорию поля путем задания всех полей, как делается в подходе, предложенном в работе \cite{moore1989classical}.
+Мы воспользуемся определением из работы \cite{felder1989structure}, подробно изложенном в книге \cite{schottenloher2008mathematical}.
+Чтобы определить конформную теорию поля оказывается достаточно задать все корреляционные функции.
+Обычно их понимают следующим образом.
+Пусть $\Omega\in\mathbb{H}$ -- вакуум, $n$-точечные корреляционные функции в квантовой теории поля обычно понимают, как
+\begin{equation}
+  \label{eq:50}
+  G_{i_{1},\dots ,i_{n}}(z_{1},\dots,z_{n}):=\left<\Omega|\varphi_{i_{1}}(z_{1})\dots \varphi_{i_{n}}(z_{n})|\Omega\right>, \quad |z_{n}|>\dots > |z_{1}|,
+\end{equation}
+где $\varphi_{i_{k}}$ -- поля в теории.
+$n$-точечные корреляционные функции можно аналитически продолжить на пространство $M_{n}=\{(z_{1},\dots,z_{n})\in \mathbb{C}^{n}: z_{i}\neq z_{j},\; i\neq j\}$.
+$M_{n}^{+}$ состоит из наборов, где $\mathrm{Re}\;z_{i}>0$ для любого $i$.
+Введем последовательность пространств тест-функций $S_{n}^{+}$, где $S_{0}^{+}=\mathbb{C}$, а $S_{n}^{+}=\{f\in S(\mathbb{C}^{n}): \mathrm{supp}(f)\subset M^{+}_{n}\} $.
+Теперь мы можем определить корреляционные функции не обращаясь к понятию полей.
+
+  Пусть $B_{0}$ -- индексное множество (счетное), последовательности произвольной длины $(i_{1},\dots,i_{n})\in B_{0}^{n}$ образуют пространство мультииндексов $i\in B$.
+Корреляционные функции $G_{i_{1},\dots, i_{n}}:M_{n}\to \mathbb{R}$ удовлетворяют следующим аксиомам.
+\begin{axiom}
+  (Аксиома локальности)
+  Для всех $(i_{1},\dots,i_{n})\in B_{0}^{n}$, $(z_{1},\dots, z_{n})\in M_{n}$ и $\pi\in S_{n}$ -- перестановок множества из $n$ элементов верно равенство
+  \begin{equation}
+    \label{eq:51}
+    G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n})=G_{i_{\pi(1)},\dots i_{\pi(n)}}(z_{\pi(1)},\dots, z_{\pi(n)})
+  \end{equation}
+\end{axiom}
+\begin{axiom}
+  (Аксиома ковариантности)
+  Для любого индекса $i\in B_{0}$ существуют независимые конформные веса $h_{i},\bar h_{i}\in \mathbb{R}$, такие, что
+  \begin{equation}
+    \label{eq:52}
+    G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n},\bar z_{1},\dots, \bar z_{n})=\prod_{j=1}^{n}\left(\frac{dw(z_{j})}{dz}\right)^{h_{i_{j}}}\left(\overline{\frac{dw(z_{j})}{dz}}\right)^{\bar{h}_{i_{j}}} G_{i_{\pi(1)},\dots i_{\pi(n)}}(w_{1},\dots, w_{n},\bar w_{1},\dots,\bar w_{n}),
+  \end{equation}
+где $w_{i}=w(z_{i})$, а $s_{i}=h_{i}-\bar h_{i}, d_{i}=h_{i}+\bar h_{i}$  -- конформный вес и скейлинговая размерность.
+\end{axiom}
+\begin{axiom}
+  (Положительность по отношению к отражениям).
+  Обозначим через $\Theta:\mathbb{C}\to\mathbb{C}$  отображение $z=t+i y\to \Theta(z)= -t+i y$.
+Тогда аксиома утверждает, что существует инволюция $\star:B_{0}\to B_{0}$, $\star^{2}=\mathrm{id}_{B_{0}}$, которая продолжается на $B$ ($i\to i^{*}$), и выполняются свойства
+  \begin{enumerate}
+  \item
+    \begin{equation}
+      \label{eq:53}
+      G_{i}(z)=G_{i^{*}}(\Theta(z))=G_{i^{*}}(-z^{*})
+    \end{equation}
+  \item Обозначим через $\underline{S}^{+}$ пространство последовательности тест-функций $\underline{f}=(f_{i})_{i\in B}, f_{i}\in S^{+}_{n}$. Тогда
+    \begin{multline}
+      \label{eq:54}
+      \left<\underline{f},\underline{f}\right>=\\
+      \sum_{i,j\in B}\sum_{n,m}\int_{M_{n+m}}G_{i^{*} j}(\Theta(z_{1}),\dots ,\Theta(z_{n}),w_{1},\dots,w_{m}) f_{i}(z)^{*}f_{j}(w) d^{n}z d^{m}w 
+      \geq 0,\\ \forall \underline{f}\in \underline{S}^{+}
+    \end{multline}
+  \end{enumerate}
+\end{axiom}
+Эта аксиома позволяет восстановить гильбертово пространство $\mathbb{H}$, так как она дает положительную полу-определенную форму $H$ на $\underline{S}^{+}$.
+То есть мы можем определить $\mathbb{H}$ как пополнение $\underline{S}^{+}$ факторизованное по $\mathrm{ker}\; H$ с произведением \eqref{eq:54}.
+
+\section{Модели Весса-Зумино-Новикова-Виттена и алгебры Ли}
+\label{sec:WZNW-models}
+
+\subsection{Напоминание про двумерную конформную теорию поля}
+\label{sec:CFT}
+
+Конформное преобразование --- это преобразование, меняющее только масштаб у метрического тензора:
+\begin{equation}
+  \label{eq:10}
+  g'_{\mu\nu}(x')=\Lambda(x)g_{\mu\nu}(x)
+\end{equation}
+
+Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований.
+
+В теории струн двумерная конформная теория поля описывает динамику на мировой поверхности, а в
+теории критических явлений --- фазовые переходы в двумерных системах.
+
+%% В $D$-мерном случае генераторы у таких преобразований следующие:
+%% \begin{align}
+%%   \label{eq:1}
+%%   & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\
+%%   &P_\mu \equiv-i\partial_\mu \,, \\
+%%   &D \equiv-ix_\mu\partial^\mu \,, \\
+%%   &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,,
+%% \end{align}
+%% 
+На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
+В двумерном случае существует бесконечное число локально-конформных преобразований.
+Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это
+условие эквивалентно уравнению Коши-Римана для голоморфных функций ($\partial_{\bar z}w(z,\bar
+z)=0$).
+
+Таким образом локально-конформные преобразования находятся в однозначном соответствии с множеством
+всех аналитических функций $w(z)$ на плоскости.
+
+Глобальные конформные преобразования имеют вид $f(z)=\frac{az+b}{cz+d},\; ad-bc=1$.
+
+Рассмотрим инфинитезимальные преобразования $w(z)=z+\epsilon(z),\quad
+\epsilon(z)=\sum_{-\infty}^{\infty}c_nz^{n+1}$. 
+Тогда для бесспинового поля $\phi(z,\bar z)$ верно следующее: $\phi'(z',\bar z')=\phi(z,\bar z)$,
+$\delta\phi=-\epsilon(z)\partial\phi-\bar \epsilon(\bar z)\bar \partial \phi=\sum_n(c_n L_n\phi+\bar
+c_n\bar L_n\phi)$, где $L_n=-z^{n+1}\partial_z,\quad \bar L_n=-\bar z^{n+1}\partial_{\bar z}$
+
+Мы видим, что в классической теории алгебра конформных преобразований --- это алгебра Витта, которая
+порождается генераторами $\{L_n, n\in \mathbb{Z}\}$ --- модами разложения оператора энергии-импульса $T$, с
+коммутационными соотношениями
+\begin{equation}
+  \label{eq:2}
+  [L_m,L_n]=(m-n)L_{m+n}
+\end{equation}
+При квантовании возникает конформная аномалия, что соответствует центральному расширению алгебры (то
+есть появлению центрального заряда $c$). В коммутационные соотношения надо добавить член
+$\frac{c}{12}(m^3-m)\delta_{m+n,0}$. В результате получаем алгебру Вирасоро.
+
+(Про тензор энергии-импульса:
+$x^{\mu}\to x^{\mu}+\epsilon^{\mu}\Rightarrow \delta S=\int d^2 x
+T^{\mu\nu}\partial_{\mu}\epsilon_{\nu}=
+\frac{1}{2}\int d^2 xT_{\mu}^{\mu}\partial_{\rho}\epsilon^{\rho}$
+В двумерной конформной теории поля тензор энергии-импульса бесследовый).
+
+Поля теории $\phi(z,\bar z)$ должны преобразовываться определенным образом при конформных преобразованиях.
+Оказывается, что все поля группируются в конформные семейства, в которых есть одно примарное поле
+\begin{equation}
+  \label{eq:3}
+  \begin{split}
+    \phi_{\Delta,\bar \Delta}(z,\bar z)\underset{
+      \genfrac{}{}{0pt}{}{z\to w(z)}
+        {\bar z \to \bar w(\bar z)}
+    }
+    {\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\left(\frac{d\bar w}{d\bar
+        z}\right)^{\bar\Delta}\phi_{\Delta,\bar \Delta}(w(z),\bar w(\bar z))\\
+    L_n \phi=0,\quad n>0\\
+    L_0 \phi=\Delta \phi\\
+  \end{split}
+\end{equation}
+$\Delta, \bar \Delta$ называются конформными размерностями поля.
+Все остальные поля называются вторичными и получаются из примарного действием операторов $L_{-n}$:
+\begin{equation}
+  \label{eq:67}
+  L_{-n_1}L_{-n_2}\dots \phi_{\Delta}
+\end{equation}
+Все поля в теории оказываются суммами произведений элементов мультиплетов алгебры Вирасоро.
+
+При некоторых дополнительных предположениях двумерную конформную теорию можно построить и решить
+полностью, если определен набор примарных полей и конформных размерностей.
+
+Существуют различные подходы к аксиоматизации двумерной конформной теории поля. В общем случае нам
+не нужно знать действие, если мы полный знаем набор примарных полей и операторные разложения их
+произведений.
+
+В том случае, если в теории конечное число примарных полей, такая теория называется минимальной.
+Кроме того, теории классифицируются по значениям центрального заряда $c$. Теории с рациональным
+центральным зарядом называются рациональными. Оказывается, что все такие теории могут быть получены
+факторизацией так называемых моделей Весса-Зумино-Новикова-Виттена.
+
+\subsection{WZW-модели}
+\label{sec:wzw}
+
+WZW-модели обладают дополнительной симметрией. Алгебра токов в них --- это алгебра Каца-Муди
+(аффинная алгебра Ли $\mathfrak{g}$), полная киральная алгебра --- полупрямое произведение
+$Vir\ltimes \mathfrak{g}$, примарные поля преобразуются по неприводимым представлениям алгебры $\mathfrak{g}$.
+
+Сейчас я поясню, что все это значит и как строятся такие модели.
+
+Модели Весса-Зумино-Виттена можно строить начиная со следующего действия:
+\begin{equation}
+\label{eq:4}
+  S=S_0+k\Gamma
+\end{equation}
+где $k$ - целое.
+Здесь $S_0$ --- действие нелинейной $\sigma$-модели.
+\begin{equation}
+  \label{eq:5}
+  S_0=\frac{1}{4a^2}\int_{S^2} d^2x\; Tr (\partial^{\mu}g^{-1}\partial_{\mu}g),
+\end{equation}
+где $a^2>0$ - положительный параметр, $g(x)\in G$ - поле со значениями в группе $G$, которую мы
+будем считать полупростой. Действие задается на комплексной плоскости с бесконечностью, которая
+топологически эквивалентна 2-сфере.
+
+В нелинейной $\sigma$-модели конформная инвариантность теряется на квантовом уровне.
+Голоморфный и антиголоморфный токи не сохраняются по отдельности.
+Поэтому мы добавляем член Весса-Зумино $\Gamma$ к действию
+\begin{equation}
+  \label{eq:73}
+\Gamma= - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr\left(
+    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+Он определен на трехмерном многообразии $B$, ограниченном исходным двумерным пространством.
+Через $\tilde{g}$ мы обозначили продолжение поля $g$ на $B$. Такое продолжение не единственно. В
+компактифицированном трехмерном пространстве компактное двумерное многообразие разделяет два
+трехмерных многообразия.
+\begin{figure}[h]
+ \centering
+  \includegraphics[width=100mm]{fig3}  
+  \caption{Два продолжения поля на трехмерное многообразие}
+  \label{fig:1}
+\end{figure}
+
+Разность значений члена Весса-Зумино $\Delta\Gamma$ на этих многообразиях
+дается правой частью уравнения (\ref{eq:73}) с интегралом, продолженным на все компактное трехмерное
+пространство. Так как оно топологически эквивалентно три-сфере, получаем
+\begin{equation}
+  \label{eq:75} \Delta\Gamma= - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left( \tilde
+g^{-1}\frac{\partial \tilde g}{\partial y^i} \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+\tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+$\Delta\Gamma$ определен по модулю $2\pi i$, поэтому Евклидов функциональный интеграл
+с весом $exp(-\Gamma)$ хорошо определен. Значит константа связи, умножаемая на этот член, должна
+быть целочисленной.
+
+Уравнение движения для полного действия (\ref{eq:4}):
+\begin{equation}
+  \label{eq:77}
+  \partial^{\mu}(g^{-1}\partial_{\mu}g)+\frac{a^2 ik}{4\pi}\epsilon_{\mu\nu}\partial^{\mu}(g^{-1}\partial^{\nu}g)=0
+\end{equation}
+В комплексных координатах оно записывается в виде
+\begin{equation}
+  \label{eq:78}
+  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
+\end{equation}
+Видно, что при $a^2=\frac{4\pi}{k}$ у нас имеются законы сохранения
+\begin{equation}
+  \label{eq:79}
+  \partial_z(g^{-1}\partial{\bar z}g)=0
+\end{equation}
+Для токов
+\begin{equation}
+  \label{eq:72}
+  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
+\end{equation}
+
+\begin{equation}
+  \label{eq:100}
+  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
+\end{equation}
+То есть голоморфная и антиголоморфная части отщепляются, что является указанием на наличие
+конформной инвариантности.
+
+Решение классического уравнения движения имеет вид
+\begin{equation}
+  \label{eq:80}
+  g(z,\bar z)=f(z)\bar f(\bar z)
+\end{equation}
+при произвольных $f(z)$ и $\bar f (\bar z)$.
+
+Сохранение по отдельности токов $J_z,\; J_{\bar z}$ приводит к инвариантности действия при преобразованиях
+\begin{equation}
+  \label{eq:81}
+   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)
+\end{equation}
+где $\Omega,\;\bar \Omega \in G$. То есть мы получили локальную $G(z)\times G(\bar z)$-инвариантность.
+
+Для перехода к квантовому случаю мы переопределяем токи
+\begin{equation}
+  \label{eq:82}
+  J(z)\equiv -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
+\end{equation}
+ При инфинитезимальных преобразованиях $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ вариация
+ $\delta_{\omega}g=\omega g$, а вариация действия
+ \begin{equation}
+   \label{eq:11}
+   \delta S=-\frac{1}{2\pi}\int d^2 x \left(\partial_{\bar z}Tr(\omega(z)J(z))+\partial_z Tr(\bar
+     \omega(\bar z)\bar J(\bar z))\right)
+ \end{equation}
+Заменяем $d^2 x=-\frac{i}{2} dz d\bar z$, интегрируем по частям и переходим к интегралу по контуру, замыкая
+контур в разных направлениях для голоморфной и антиголоморфной частей.
+Тогда вариация действия
+\begin{equation}
+  \label{eq:83}
+  \delta_{\omega,\bar\omega}S=\frac{i}{4\pi}\oint dz Tr (\omega(z)J(z))-\frac{i}{4\pi}\oint d\bar z Tr(\bar\omega(\bar z)\bar J(\bar z))
+\end{equation}
+Раскладывая токи
+\begin{equation}
+  \label{eq:85}
+  \begin{aligned}
+    J=\sum J^a t^a,\bar J=\sum \bar J^a t^a \\
+    \omega=\sum \omega^a t^a\\
+  \end{aligned}
+\end{equation}
+получаем
+\begin{equation}
+  \label{eq:86}
+  \delta_{\omega,\bar \omega}S=-\frac{1}{2\pi i}\oint dz \sum\omega^a J^a+\frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \bar J^a
+\end{equation}
+Мы также получили тождества Уорда $\delta\left< X\right>=\left<(\delta S)X\right>$
+\begin{equation}
+  \label{eq:87}
+  \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
+  \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
+\end{equation}
+Для токов из явного вида тока и формулы для преобразования $g$ имеем
+\begin{equation}
+  \label{eq:88}
+  \delta_{\omega}J=[\omega,J]-k\partial_z\omega,\quad \delta_{\omega}J^a=\sum i f_{abc}\omega^b J^c-k\partial_z\omega^a
+\end{equation}
+Если это подставить в тождество Уорда, то получаем операторное разложение для токов, которое имеет
+вид 
+\begin{equation}
+  \label{eq:89}
+  J^a(z) J^b(w) \sim \frac{k\delta_{ab}}{(z-w)^2}+\sum i f_{abc}\frac{J^c(w)}{(z-w)}
+\end{equation}
+Раскладывая токи в ряд, получаем
+\begin{equation}
+  \label{eq:90}
+  \begin{aligned}
+    J^a(z)=\sum_{n\in \mathbb Z}z^{n-1}J^a_n\\
+    \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}
+  \end{aligned}
+\end{equation}
+Теперь мы видим, что компоненты токов образуют аффинную алгебру Ли $\hat g$.
+
+Тензор энергии-импульса вводится при помощи конструкции Сугавары как сумма нормально упорядоченных компонент токов
+\begin{equation}
+  \label{eq:102}
+  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
+\end{equation}
+Здесь $h^v$ - дуальное число Кокстера. $h^v=\sum_i \alpha_i^v +1=\frac{1}{2}(\Theta,\Theta+2\rho)$,
+а нормальное упорядочение вводится следующим образом: 
+\begin{equation}
+  \label{eq:12}
+  N(AB)(w)=\frac{1}{2\pi i}\oint\frac{dz}{z-w}A(z)B(w)
+\end{equation}
+
+Тензор энергии-импульса можно разложить на моды $L_n$
+\begin{equation}
+  \label{eq:91}
+  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
+\end{equation}
+Тогда коммутационные соотношения для мод $L_n$ имеют вид
+\begin{equation}
+  \label{eq:92}
+  \begin{aligned}
+    \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
+    c=\frac{k\;\mathrm{dim}g}{k+h^v}\\
+    \left[L_n,J^a_m\right]=-mJ^a_{n+m}.
+  \end{aligned}
+\end{equation}
+
+Таким образом, конструкция Сугавары --- это способ вложения алгебры Вирасоро в универсальную обертывающую аффинной алгебры Ли $\hat{g}$
+
+Полная киральная алгебра модели Весса-Зумино-Виттена равна полупрямому произведению $Vir\ltimes \hat g$
+
+Примарными оказываются поля, которые преобразуются ковариантно под действием $G(z)\times G(\bar z)$,
+как $g(z,\bar z)$. В терминах операторного разложения это свойство переформулируется следующим
+образом:
+\begin{equation}
+  \label{eq:84}
+  \begin{aligned}
+    J^a(z)g(w,\bar w)\sim \frac{-t^a g(w,\bar w)}{(z-w)}\\
+    \bar J^a(z)g(w,\bar w)\sim \frac{ g(w,\bar w)t^a}{(z-w)}
+  \end{aligned}
+\end{equation}
+Любое поле $\phi_{\lambda,\mu}$, преобразующееся ковариантно по отношению к некоторому
+представлению, заданному весом $\lambda$ в голоморфном секторе и весом $\mu$ в антиголоморфном,
+является примарным полем WZW-модели.
+
+В модах это свойство записывается в виде
+\begin{equation}
+  \label{eq:93}
+  \begin{aligned}
+    & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
+    & (J^a_n\phi_{\lambda})=0\quad \mbox{для}\; n>0\\
+  \end{aligned}
+\end{equation}
+Мы можем сопоставить состояние $\left|\phi_{\lambda}\right>$ полю $\phi_{\lambda}$
+  \begin{equation}
+    \label{eq:94}
+    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
+  \end{equation}
+Тогда условия (\ref{eq:93}) для примарных полей дают
+\begin{equation}
+  \label{eq:95}
+  \begin{aligned}
+    & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
+    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{для}\; n>0 \\
+  \end{aligned}
+\end{equation}
+Все вторичные состояния имеют вид
+\begin{equation}
+  \label{eq:97}
+  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
+\end{equation}
+
+Легко видеть, что действие генераторов алгебры Вирасоро на примарные поля имеет вид
+\begin{equation}
+  \label{eq:96}
+  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
+\end{equation}
+Здесь использовано явное выражение для собственных значений квадратичного оператора Казимира.
+
+Примарные поля преобразуются  интегрируемыми конечномерными представлениями, а бесконечномерные и
+неинтегрируемые поля зануляют корреляционные функции.
+В WZW-моделях примарные поля
+принадлежат тензорному произведению неприводимых представлений аффинной алгебры, так как есть
+голоморфный и антиголоморфный сектора.
+
+\subsection{Конформные вложения и модулярно-инвариантные статсуммы}
+\label{sec:modular-invariance}
+
+При изучении конформной теории поля на плоскости или на сфере 
+голоморфный и антиголоморфный сектора можно рассматривать независимо. 
+Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть
+определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать
+взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно) чтобы теория была определена на торе.
+
+(Нарисовать картинку штанов).
+
+В теории критического поведения конформная инвариантность имеет место только в критической точке,
+где голоморфный и антиголоморфный сектора расцеплены. Но вблизи критической точки эти сектора должны
+быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве
+параметров, то эта связь должна сохраняться и в критической точке. Физический спектр теории должен
+плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного
+сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической
+точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния. Здесь
+естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории
+на торе.
+
+%% Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
+%% Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
+%% выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
+%% вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
+%% обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
+%% параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
+%% Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
+%% параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
+%% статсумма дается следом оператора сдвига в степени $m$:
+%% \begin{equation}
+%%   \label{eq:6}
+%%   Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
+%% \end{equation}
+%% Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
+%% конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
+%% $H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
+%% $L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
+%% $P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
+%% можно записать в виде
+%% \begin{equation}
+%%   \label{eq:7}
+%%   \begin{split}
+%%       Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
+%%       L_0)\}\\
+%%       =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
+%%   \end{split}
+%% \end{equation}
+%% Или, если ввести $q=\exp 2\pi i \tau$
+%% \begin{equation}
+%%   \label{eq:2}
+%%   Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
+%% \end{equation}
+%% Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
+%% 
+%% Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
+%% эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
+%% 
+Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
+модулярной инвариантности статсуммы.
+
+При помощи конформных преобразований можно перейти к таким координатам, в которых соотношения
+эквивалентности для тора (граничные условия) записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
+$\mathbb{C}$.
+%% 
+%% Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
+%% конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
+%% $SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
+%% \begin{equation}
+%%   \label{eq:99} A=
+%%   \begin{pmatrix} a & b\\ c & d
+%%   \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+%% \end{equation}
+%% и матрицы $A$ и $-A$ действуют одинаково на $\tau$
+%% \begin{equation}
+%%   \label{eq:100} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+%% \end{equation}
+%% $\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
+%% модулярной группой.
+%% 
+Конформная теория поля задаётся примарными полями $\Phi_a$ с конформными размерностями $\Delta_a$.
+
+Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
+произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
+представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсумма на торе
+(\ref{eq:2}) может быть записана в виде
+\begin{equation}
+  \label{eq:9}
+    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
+\end{equation}
+где $\chi_j$ --- нормализованный характер представления $\mathcal{H}_j$,
+\begin{equation}
+  \label{eq:5} \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i
+\tau}
+\end{equation}
+
+Характеры переходят друг в друга при модулярных преобразованиях:
+\begin{equation}
+  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
+\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
+\end{equation}
+где $S$ и $T$ --- постоянные матрицы.
+
+Для WZW-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$. Тогда
+\begin{equation}
+  \label{eq:6} \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi}
+L_{\hat \lambda}\otimes L_{\hat \xi}
+\end{equation}
+
+Коэффициенты ветвления для вложения аффинной подалгебры Ли в аффинную алгебру можно использовать для
+построения модулярно-инвариантной статсуммы в соответствующей WZW-модели. Когда рассматривается
+теория на торе,  набор физически допустимых полей ограничен требованиями модулярной инвариантности.
+
+Простейший модулярный инвариант можно записать следующим образом:
+\begin{equation}
+  \label{eq:34}
+   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
+\end{equation}
+Здесь суммирование ведется по всем конформным семействам (то есть по всем представлениям алгебры
+$\mathfrak{a}$).
+
+Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует
+алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно. (Я сейчас поясню, что это
+значит).
+
+Представления алгебры можно рассматривать как сумму представлений подалгебры.
+
+Если мы рассмотрим редукцию характеров аффинной алгебры
+\begin{equation}
+  \label{eq:8}
+   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
+\end{equation}
+и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится. То есть из
+диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый не диагональный инвариант для
+подалгебры $\mathfrak{a}$. Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
+ней конформная инвариантность.
+
+Пусть $J^{a_j}_{-n_j}$ и $\tilde{J}^{a'_j}_{-n_j}$ --- понижающие операторы алгебр  $\mathfrak{g}$ и
+$\mathfrak{a}\subset\mathfrak{g}$.  $\pi_{\mathfrak{a}}$ --- проекционный оператор
+$\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$. В теории, связанной с  $\mathfrak{g}$
+с вакуумом $\left|\lambda\right>$ будут следующие состояния:
+\begin{equation}
+  \label{eq:109}
+  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+\end{equation}
+Вакуум $\mathfrak{g}$-инвариантен, то есть $J_0^a\left|0\right>=0$. При проекции на подалгебру
+$\mathfrak{a}$ состояния примут вид
+\begin{equation}
+  \label{eq:110}
+  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
+\end{equation}
+Из $\mathfrak{g}$-ивариантности вакуума следует его $\mathfrak{a}$-инвариантность, но для тензора
+энергии-импульса в общем случае это не так. Поэтому тензор энергии-импульса большей теории должен
+состоять только из генераторов $\tilde{J}$. Тогда $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow
+c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению
+\begin{equation}
+  \label{eq:111}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
+\end{equation}
+Здесь $x_e$ --- индекс вложения, а  $g$, $a$ --- дуальные числа Кокстера, которые характеризуют алгебры.
+
+Можно показать, что только для представлений уровня 1 это равенство удовлетворяется. То есть класс
+конформных вложений не слишком широк и существует полная их классификация. Кроме того, для
+конформных вложений существуют специальные методы разложения представлений.
+
+Модулярная инвариантность статсуммы для полей, принадлежащих представлениям алгебры  $\mathfrak{g}$,
+сохраняется при проекции на подалгебру $\mathfrak{a}$. Если все представления $\mathfrak{g}$ в теории
+удовлетворяют описанным требованиям, то при проекции мы получаем конформную теорию поля.
+
+Существует теорема о том, что для конформного вложения  $\mathfrak{a}\subset\mathfrak{g}$ только
+конечное число коэффициентов ветвления отлично от нуля. Поэтому после того, как мы разложили все
+представления $\mathfrak{g}$ мы подставляем результаты в выражение для статсуммы и получаем
+модулярно-инвариантную статсумму для вложенной теории. Такая статсумма уже не будет иметь
+диагональный вид:
+\begin{equation}
+  \label{eq:36}
+   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
+\end{equation}
+Наша работа посвящена разработке общего метода редукции представлений аффинных алгебр Ли, поэтому
+случай конформных вложений --- лишь один из примеров применения нашего метода. Однако в этом случае
+физический смысл наиболее очевиден.
+
+\subsection{Центральное расширение алгебры Витта}
+\label{sec:witt-algebra-central-extension}
+
+Напомним несколько определений (см \cite{fuks1986cohomology},\cite{fuks1984}, \cite{feigin1988}).
+\begin{definition}
+Будем рассматривать алгебру Ли $\gf$ над полем $k=\mathbb{C},\mathbb{R}$.
+Векторное пространство $A$ над полем $k$ называется {\it модулем над $\gf$} или {\it $\gf$-модулем}, если задано билинейное отображение $\mu:\gf\times A\to A$, такое что $\mu([X,Y],a)=\mu(X,\mu(Y,a))-\mu(Y,\mu(X,a))$ для $X,Y\in \gf, a\in A$.
+Далее мы будем опускать символ $\mu$ и писать $X a= \mu(X,a)$.
+\end{definition}
+\begin{definition}
+  {\it $n$-мерная коцепь с коэффициентами в $A$} -- это кососимметричный $n$-линейный функционал на $\gf$ со значениями в $A$. Пространство $n$-коцепей $C^{n}(\gf;A)=\mathrm{Hom}(\wedge^{n}\gf;A)$.
+\end{definition}
+Заметим, что элементы $\gf$ действуют на $C^{n}(\gf;A)$.
+\begin{definition}
+  Внешний дифференциал $d=d_{n}:C^{n}(\gf;A)\to C^{n+1}(\gf;A)$ определяется формулой
+  \begin{multline}
+    \label{eq:1}
+    (dc) (X_{1},\dots, X_{n+1})=\sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} c([X_{s},X_{t}],X_{1},\dots,\hat X_{s},\dots,\hat X_{t},\dots X_{n+1})\\
+    +\sum_{1\leq s\leq n+1} (-1)^{s}X_{s} c(X_{1},\dots \hat X_{s},\dots X_{n+1})
+  \end{multline}
+\end{definition}
+Оставляем в качестве упражнения проверку того факта, что последовательность
+\begin{equation}
+  \label{eq:2}
+  \dots\stackrel{d_{n}}{\longleftarrow} C^{n}(g;A)\stackrel{d_{n-1}}{\longleftarrow} C^{n-1}(\gf;A)\leftarrow \dots \leftarrow C^{1}(\gf;A) \stackrel{d_{0}}{\longleftarrow} C^{0}(\gf;A)\leftarrow 0
+\end{equation}
+точна.Тогда $\{C^{n}(\gf;A),d_{n}\}=C^{*}(\gf;A)$ есть комплекс.
+\begin{definition}
+Соответствующие когомологии называются {\it когомологиями алгебры $\gf$ с коэффициентами в $A$} и обозначаются через $H^{n}(\gf;A)=\mathrm{Ker}\; d_{n}/\mathrm{Im}\; d_{n-1}$.
+
+\end{definition}
+Заметим, что поле $k$ может рассматриваться как тривиальный $\gf$-модуль. В этом случае второй член в формуле \eqref{eq:1} исчезает и используют сокращенные обозначения $C^{n}(\gf), H^{n}(\gf)$.
+\begin{definition}
+  Определим, заодно, и гомологии. Пространство $n$-мерных цепей $C_{n}(\gf;A)=A\otimes \wedge^{n}\gf$, дифференциал $\partial=\partial_{n}:C_{n}(\gf;A)\to C_{n-1}(\gf;A)$ определяется формулой
+  \begin{multline}
+    \label{eq:3}
+    \partial(a\otimes (X_{1}\wedge \dots \wedge X_{n})) =\\ \sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} a\otimes ([X_{s},X_{t}]\wedge X_{1} \wedge\dots\wedge\hat X_{s}\wedge \dots\wedge \hat X_{t}\wedge \dots\wedge X_{n+1})\\
+    +\sum_{1\leq s\leq n+1} (-1)^{s}(X_{s} a)\otimes (X_{1}\wedge\dots\wedge \hat X_{s}\wedge\dots\wedge X_{n+1})
+  \end{multline}
+  Аналогично определяется точная последовательность, комплекс и группа гомологий $H_{n}(\gf;A)$.
+\end{definition}
+\begin{definition}
+  {\it Одномерным центральным расширением алгебры $\gf$ } называется точная последовательность
+  \begin{equation}
+    \label{eq:4}
+    0\to k \to \tilde \gf\to \gf\to 0,
+  \end{equation}
+  такая что образ $k\to \tilde\gf$ содержится в центре $\tilde\gf$.
+\end{definition}
+Заметим, что всякий 2-коцикл $c\in C^{2}(\gf;A)$ определяет центральное расширение $\gf$:
+\begin{equation}
+  \label{eq:5}
+  0\to k\stackrel{\lambda\to (0,\lambda)}{\longrightarrow}\tilde\gf=\gf\oplus k \stackrel{(X,\lambda)\to X}{\longrightarrow} \gf\to 0
+\end{equation}
+Скобка Ли в алгебре $\tilde\gf$, которая равна $\gf\oplus k$ как векторное пространство, определяется равенством
+\begin{equation}
+  \label{eq:6}
+  [(X,\lambda),(Y,\mu)]=([X,Y],c(X,Y))
+\end{equation}
+Тождество Якоби для такой скобки равносильно тому, что $c$-- 2-коцикл. Когомологичным коциклам отвечают эквивалентные расширения.
+
+Два расширения $\tilde \gf$ и $\tilde{\tilde\gf}$ называются эквивалентными, если существует изоморфизм $I:\tilde\gf\to \tilde{\tilde \gf}$ такой, что диаграмма коммутирует:
+\begin{equation}
+  \label{eq:7}
+  \begin{diagram}
+    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \arrow{s,l}{id} \node{\tilde\gf}\arrow{s,l}{I} \arrow{e,t}{} \node{k}\arrow{s,r}{id} \arrow{e,t}{} \node{0}\\
+    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \node{\tilde{\tilde\gf}} \arrow{e,t}{} \node{k} \arrow{e,t}{} \node{0}
+  \end{diagram}
+\end{equation}
+\begin{exercise}
+ Построить изоморфизм $I$.   
+\end{exercise}
+
+Таким образом пространство $H^{2}(\gf)$ -- это множество классов 1-мерных центральных расширений $\gf$. Нуль в $H^{2}(\gf)$  соответствует тривиальному расширению.
+
+Вернемся к алгебре Витта \eqref{eq:230}. Существует коцикл
+\begin{equation}
+  \label{eq:8}
+  c(l_{n},l_{m})=\frac{1}{12}(m^{3}-m)\delta_{-n,m}
+\end{equation}
+\begin{exercise}
+  Проверить, что $c$ -- коцикл алгебры Витта. 
+\end{exercise}
+Соответствующее центральное расширение алгебры Витта называется алгеброй Вирасоро. Коммутационные соотношения этой алгебры имеют вид
+\begin{eqnarray}
+  \label{eq:9}
+  [L_{n},c]=0\\
+  \left[L_{n},L_{m}\right]=(n-m)L_{n+m} +\frac{c}{12} (m^{3}-m) \delta_{-n,m}
+\end{eqnarray}
+Можно показать, что $H^{2}(Witt)\cong \mathbb{C}$ и все нетривиальные коциклы пропорциональны $c$. 
+(Доказательство есть в \cite{fuks1986cohomology}, \cite{schottenloher2008mathematical}).
+
 \chapter{Аффинные алгебры Ли}
 \label{cha:affine-lie-algebras}
+Аффинные алгебры Ли - это естественное обобщение простых конечномерных алгебр Ли.
+Они возникают при изучении различных физических моделей, например, моделей Весса-Зумино-Новикова-Виттена в конформной теории поля и интегрируемых спиновых цепочек.
+\section{Введение. Простые алгебры Ли.}
+
+\label{sec:intro-simple-lie-algebras}
+
+\subsection{Lie algebras of finite and affine types}
+\label{sec:lie-algebras-finite}
+
+{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it Lie bracket}.
+If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
+\begin{equation}
+  \label{eq:1}
+  [X^{i},X^{j}]=\sum_{k} C^{ij}_{k} X^{k}
+\end{equation}
+Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to commutator.
+{\it Semisimple} Lie algebra is a direct sum of simple Lie algebras.
+In the present paper we treat simple and semisimple Lie algebras.
+
+{\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
+We denote the elements of basis of $\hfg$ by $H^{i}$.
+
+Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
+{\it Weights} are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
+
+Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
+This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).
+
+{\it Loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
+\begin{equation}
+  \label{eq:6}
+  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
+\end{equation}
+Central extension leads to the appearance of an additional term
+\begin{equation}
+  \label{eq:7}
+   [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
+\end{equation}
+This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
+
+We do not treat twisted affine Lie algebras in the present paper.
+
+\subsection{Modules, weights and roots}
+\label{sec:weights-roots}
+
+Let $\gf$ be a inite-dimensional or an affine Lie algebra.
+
+Then $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
+\begin{equation}
+  \label{eq:2}
+  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
+\end{equation}
+Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms of the  vector space $V$ with the commutator as a bracket.
+
+For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by a special choice of basis $\{v_{j}\}$ in $V$:
+\begin{equation}
+  \label{eq:3}
+  H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
+\end{equation}
+Eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
+Vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
+The  weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
+The weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of the weight subspace.
+
+The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
+\begin{equation}
+  \label{eq:5}
+  E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
+\end{equation}
+Module structure can be encoded by the formal character of a module
+\begin{equation}
+  \label{eq:10}
+  \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
+\end{equation}
+Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
+A character can be specialized by taking its value on some element $\xi$ of $\hf$.
+
+Lie algebra is its own module with respect to a special kind of representation. The action that
+defines this representation is called adjoint and is given by the bracket $ad_{X} Y=[X,Y]$. 
+{\it Roots} are weights of the adjoint representation of $\gf$.
+They encode the commutation relations of algebra in the following way.
+Denote by $\Delta$ the set of roots.
+For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and the generators $E^{\alpha}, E^{-\alpha}$ such that
+\begin{align}
+  \label{eq:4}
+  &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
+  &\left[E^{\alpha},E^{\beta}\right]=
+  \begin{cases}
+    N_{\alpha,\beta} E^{\alpha+\beta}, & \mbox{if}\; \alpha+\beta\in \Delta\\
+    \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
+    0,&\mbox{otherwise}
+  \end{cases}
+\end{align}
+
+Given the root system $\Delta$ we can choose the set of positive roots.
+This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
+Elements of $-\Delta^{+}$ are called negative roots.
+
+A positive root is {\it simple} if it cannot be written as a sum of positive roots.
+The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis in $\hfg^{*}$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive simultaneously.
+In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
+By numbering simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
+Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
+$\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}).
+{\it Comarcs} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
+
+Although for affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
+The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.
+The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- the highest root of the algebra $\go$.
+Note that root multiplicity $\mathrm{mult}(\alpha)$ for an affine Lie algebra root can be greater than one.
+
+Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called the Borel subalgebra.
+
+{\it Parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
+It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
+{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .
+
+The {\it Weyl group} $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
+\begin{equation}
+  \label{eq:8}
+  s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
+\end{equation}
+Root system and characters of representation are invariant with respect to the Weyl group  action. Root system can be reconstructed from the set of simple roots by the Weyl group transformations.
+
+Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
+
+Consider an action of the element $s_{\alpha}s_{\alpha+\delta}$ of the Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ being a simple root of the underlying finite-dimensional Lie algebra $\gf$.
+Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
+So the Weyl group can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to roots of $\gf$.
+
+A Weyl group element can be presented as a product of elementary reflections in multiple ways.
+Number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$.
+We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for the parity of the number of Weyl reflections generating $w$.
+
+Fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
+It is called a {\it main Weyl chamber}.
+
+The {\it Cartan matrix} $A$ is defined by products of simple roots
+\begin{equation}
+  \label{eq:9}
+  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}
+\end{equation}
+and can be used for a compact description of Lie algebra commutation relations in the Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
+
+Form \eqref{eq:9} induces a basis dual  to the simple
+roots basis. It is called the {\it fundamental weights basis}. We denote
+its elements by $\omega_i$:
+\begin{equation}
+  \label{eq:20}
+  \langle\omega_i,\alpha_j\rangle=\frac{2(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
+\end{equation}
+For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
+For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
+Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
+
+ The sum of fundamental weights $\rho=\sum_{i} \omega_{i}$ is called a {\it Weyl vector}. It is an important tool in representation theory.
+
+\subsection{Highest weight modules}
+\label{sec:high-weight-modul}
+
+We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e.
+if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
+
+Highest weight module $V^{\mu}$ contains a single highest weight $\mu$, all the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
+
+The most simple type of highest weight modules is the Verma module
+$M^{\mu}$. Its space can be defined as a module
+\begin{equation}
+  \label{eq:17}
+  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}),
+\end{equation}
+with respect to a multiplication in $U(\gf)$ and
+$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
+Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
+Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D^{\lambda}(\bff_{+})$.
+
+Weight multiplicities in Verma modules can be found by applying the Weyl
+character formula
+\begin{equation}
+  \label{eq:11}
+  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
+\end{equation}
+Here we have used the Weyl denominator identity
+\begin{equation}
+  \label{eq:12}
+  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
+\end{equation}
+and $\epsilon \left( w\right) :=\det \left( w\right)$ is equal to 
+the parity of the sequence of Weyl reflections generating $w$.
+
+Verma module $M^{\mu}$ has the unique maximal submodule and the
+unique nontrivial simple quotient $L^{\mu}$ which is an
+{\it irreducible highest weight module}.
+
+Irreducible highest weight modules have no non-trivial submodules. 
+The Weyl character formula for
+irreducible highest weight modules is
+\begin{equation}
+  \label{eq:13}
+  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
+\end{equation}
+Thus the character of an irreducible highest weight module can be
+seen as a combination of characters of Verma modules. ( This
+fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
+(\cite{bernstein1976category,bernstein1971structure}, see also
+\cite{humphreys2008representations}).)
+
+Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
+%% !!! \Delta_{p}?!
+\begin{equation*}
+M_{I}^{\mu}=U\left( \gf\right)\otimes _{U\left( \pf_{I}\right) }L_{\pf_{I}}^{\mu}.
+\end{equation*}
+Introduce a formal element $R_{I}:=\prod_{\alpha \in \Delta
+^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
+^{\mathrm{mult}(\alpha )}$. Then the character of a generalized
+Verma module can be written as
+\begin{equation}
+  \label{eq:18}
+  \mathrm{ch}M_{I}^{\mu}=\frac{1}{R_{I}}\mathrm{ch}L_{\pf_{I}}^{\mu }.
+\end{equation}
+
+%% Define external border of irreducible representation here
+
+We can use the Weyl character formula to obtain recurrent relations for weight multiplicities -- important tools for calculations \cite{il2010folded,kulish4sfa}.
+
+For irreducible highest-weight modules recurrent relations have the following form
+\begin{equation}
+\label{eq:14}
+m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
+-\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
+(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
+\end{equation}
+Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side.
+In case of Verma module it is just $\delta_{\xi,\mu}$.
+For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
+
+Other recurrent formula can be obtained from a study of Casimir
+elements action on irreducible highest weight modules
+\cite{humphreys1997introduction}:
+\begin{equation}
+  \label{eq:15}
+  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
+\end{equation}
+It is called the Freudenthal multiplicity formula.
+Note that it is applicable only to irreducible modules.
+
+We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.
+
+Now consider an algebra $\gf$ and a reductive subalgebra
+$\af\subset \gf$. Simple roots $\beta_{i}$ of the subalgebra $\af$
+can be presented as linear combinations of $\gf$-algebra roots
+$\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j}
+\alpha_{j},\ j=1,\dots,r_{\af}$.
+
+Each irreducible $\gf$-module is also an $\af$-module, although
+$L^{\mu}_{\gf}$ is in general not irreducible as $\af$-module. 
+It can be
+decomposed into a direct sum of irreducible $\af$-modules:
+\begin{equation}
+  \label{eq:16}
+  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
+\end{equation}
+Coefficients in such a decomposition are called branching
+coefficients.
+
+It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. 
+This traditional approach has serious limitations especially in case of affine Lie algebras. We discuss them in the end of section \ref{sec:comp-algor}.
+
+Now we describe an alternative approach which is based on recurrent properties of branching coefficients. 
+But before we proceed to these recurrent relations we need several additional definitions.
+
+For a subalgebra $\af\subset \gf$ we introduce the subalgebra
+$\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
+orthogonal to $\hf_{\af}$,
+\begin{equation*}
+\hf_{\perp \af}^{\ast }:=\left\{ \eta \in \hf^{\ast }|\forall
+h\in \hf_{\af};\eta \left( h\right) =0\right\} ,
+\end{equation*}
+and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
+to roots of $\af$,
+\begin{eqnarray}
+\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
+h\in \hf_{\af};\beta \left( h\right) =0\right\} ,
+\label{delta a ort} \\
+\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
+}^{+}|\forall h\in \hf_{\af};\beta ^{+}\left( h\right) =0\right\} .
+\notag
+\end{eqnarray}
+Let $W_{\afb}$ be a subgroup of $W$ generated by
+reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
+}}^{+}$. The subsystem $\Delta _{\afb}$ determines a 
+subalgebra $\afb$ with the Cartan subalgebra $\hf_{\af%
+_{\perp }}$.
+
+The Cartan subalgebra $\frak{h}$ can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
+\frak{h}_{\afb}\oplus \frak{h}_{\perp }$
+
+We also introduce the notations
+\begin{eqnarray}
+\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\qquad
+\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
+\end{eqnarray}
+
+For $\af$ and $\afb$ we consider the
+corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\af_{\perp
+}} $ and compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
+D}_{\afb}$ of the injection:
+\begin{equation}
+\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho , \qquad
+\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
+_{\perp }}\rho .  \label{defect-ort}
+\end{equation}
+
+%%!!! Define P^+
+For $\mu \in P^{+}$ consider the linked weights $\left\{ \left(
+w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections
+to
+$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
+\mathcal{D}_{\afb}$:
+\begin{equation*}
+\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
+w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
+\end{equation*}
+Among the weights $\left\{ \mu _{\af_{\perp
+}}\left( w\right) |w\in W\right\} $ one can always choose those located in
+the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
+set of representatives $u$ for the classes $W/W_{\afb}$ such
+that
+
+\begin{equation}
+U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
+\overline{C_{\afb}}\right\} \quad .  \label{U-def}
+\end{equation}
+Thus we can form the subsets:
+\begin{equation}
+\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
+\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
+_{\perp }},\quad u\in U,  \label{mu-a}
+\end{equation}
+and
+\begin{equation}
+\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
+\label{mu-a-tilda}
+\end{equation}
+
+Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
+since it is built on a subset of roots of the algebra $\mathfrak{g}$.
+
+Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients.
+If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.
+
+Now we can use the Weyl character formula to write a
+recurrent relation \cite{2010arXiv1007.0318L} for signed branching
+coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
+injection $\af\hookrightarrow \gf$:
+\begin{equation}
+\begin{array}{c}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
+_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
+\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right.  \\
+\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
+}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
+}\right) .
+\end{array}
+\label{recurrent-rel}
+\end{equation}
+The recursion is governed by the set $\Gamma _{\af\rightarrow \gf}$ called the injection fan. The latter is defined by the
+carrier set $\left\{ \xi \right\} _{\af\rightarrow \gf}$ for the
+coefficient function $s(\xi )$
+\begin{equation*}
+\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}:=\left\{
+\xi \in P_{\widetilde{\af}}|s(\xi )\neq 0\right\}
+\end{equation*}
+appearing in the expansion
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
+_{\widetilde{\af}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
+_{\af}(\pi _{\widetilde{\af}}\alpha )}=-\sum_{\gamma \in P_{%
+\widetilde{\af}}}s(\gamma )e^{-\gamma };\quad
+\end{equation}
+The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
+\right\} $ -- and the zero element is to be eliminated:
+\begin{equation}
+\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma
+_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
+\end{equation}
+Formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
+
+If the root system of $\afb$ is generated by some subset of $\gf$
+simple roots $\alpha_{1},\dots,\alpha_{r}$ then the recurrent
+relation (\ref{recurrent-rel}) is connected with the generalized
+Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules
+\cite{2011arXiv1102.1702L}.
+
+Another particular case of this formula is connected with tensor
+product decompositions. Consider the tensor product of two
+irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$. It is also a
+$\gf$-module but not irreducible in general. So
+\begin{equation}
+  \label{eq:19}
+  L^{\mu}\otimes L^{\nu}=\bigoplus_{\gamma} f^{\mu\nu}_{\gamma}L^{\gamma}
+\end{equation}
+The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion
+coefficients. The problem of computation of fusion coefficients is
+equivalent to branching problem for the diagonal subalgebra
+$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
+
+In the case of affine Lie algebras $\gf, \af$  the multiplicities
+$m_{\nu}$ and the corresponding branching coefficients $b_{\nu}$
+can be regarded as the coefficients in power series decomposition
+of string and branching functions correspondingly:
+\begin{align}
+  \label{eq:21}
+  &\sigma_{\nu}(q)=\sum_{n=0}^{\infty} m_{\nu-n\delta} q^n, \quad \nu=\sum_j c_j \omega_j,\quad c_j\geq 0\\
+  & b_{\nu}(q)=\sum_{n=0}^{\infty} b_{\nu-n\delta} q^n,\quad  \nu=\sum_j c_j \omega_j, \quad c_j\geq 0
+\end{align}
+String and branching functions have  modular and analytic properties which are important for conformal field theory, especially in  coset models and the study of CFT on higher genus surfaces \cite{kac1988modular}, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}.
+
+{\bf Affine.m}  calculates weight multiplicities and branching coefficients for affine Lie algebras up to some finite grade.
+We present examples of computations in Sections \ref{sec:string-funct-affine}, \ref{sec:branch-funct-coset}.
+Now we proceed to the description of datastructures and algorithms implemented in {\bf Affine.m}.
 

### 2011-11-10 AffineLieAlgebras/Thesis/3.tex
Work on CFT section (axiomatics) + wzw moved to chapter 1

@@
 \label{sec:physics}
-
-\subsection{Напоминание про двумерную конформную теорию поля}
-\label{sec:CFT}
-
-Конформное преобразование --- это преобразование, меняющее только масштаб у метрического тензора:
-\begin{equation}
-  \label{eq:10}
-  g'_{\mu\nu}(x')=\Lambda(x)g_{\mu\nu}(x)
-\end{equation}
-
-Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований.
-
-В теории струн двумерная конформная теория поля описывает динамику на мировой поверхности, а в
-теории критических явлений --- фазовые переходы в двумерных системах.
-
-%% В $D$-мерном случае генераторы у таких преобразований следующие:
-%% \begin{align}
-%%   \label{eq:1}
-%%   & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\
-%%   &P_\mu \equiv-i\partial_\mu \,, \\
-%%   &D \equiv-ix_\mu\partial^\mu \,, \\
-%%   &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,,
-%% \end{align}
-%% 
-На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
-В двумерном случае существует бесконечное число локально-конформных преобразований.
-Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это
-условие эквивалентно уравнению Коши-Римана для голоморфных функций ($\partial_{\bar z}w(z,\bar
-z)=0$).
-
-Таким образом локально-конформные преобразования находятся в однозначном соответствии с множеством
-всех аналитических функций $w(z)$ на плоскости.
-
-Глобальные конформные преобразования имеют вид $f(z)=\frac{az+b}{cz+d},\; ad-bc=1$.
-
-Рассмотрим инфинитезимальные преобразования $w(z)=z+\epsilon(z),\quad
-\epsilon(z)=\sum_{-\infty}^{\infty}c_nz^{n+1}$. 
-Тогда для бесспинового поля $\phi(z,\bar z)$ верно следующее: $\phi'(z',\bar z')=\phi(z,\bar z)$,
-$\delta\phi=-\epsilon(z)\partial\phi-\bar \epsilon(\bar z)\bar \partial \phi=\sum_n(c_n L_n\phi+\bar
-c_n\bar L_n\phi)$, где $L_n=-z^{n+1}\partial_z,\quad \bar L_n=-\bar z^{n+1}\partial_{\bar z}$
-
-Мы видим, что в классической теории алгебра конформных преобразований --- это алгебра Витта, которая
-порождается генераторами $\{L_n, n\in \mathbb{Z}\}$ --- модами разложения оператора энергии-импульса $T$, с
-коммутационными соотношениями
-\begin{equation}
-  \label{eq:2}
-  [L_m,L_n]=(m-n)L_{m+n}
-\end{equation}
-При квантовании возникает конформная аномалия, что соответствует центральному расширению алгебры (то
-есть появлению центрального заряда $c$). В коммутационные соотношения надо добавить член
-$\frac{c}{12}(m^3-m)\delta_{m+n,0}$. В результате получаем алгебру Вирасоро.
-
-(Про тензор энергии-импульса:
-$x^{\mu}\to x^{\mu}+\epsilon^{\mu}\Rightarrow \delta S=\int d^2 x
-T^{\mu\nu}\partial_{\mu}\epsilon_{\nu}=
-\frac{1}{2}\int d^2 xT_{\mu}^{\mu}\partial_{\rho}\epsilon^{\rho}$
-В двумерной конформной теории поля тензор энергии-импульса бесследовый).
-
-Поля теории $\phi(z,\bar z)$ должны преобразовываться определенным образом при конформных преобразованиях.
-Оказывается, что все поля группируются в конформные семейства, в которых есть одно примарное поле
-\begin{equation}
-  \label{eq:3}
-  \begin{split}
-    \phi_{\Delta,\bar \Delta}(z,\bar z)\underset{
-      \genfrac{}{}{0pt}{}{z\to w(z)}
-        {\bar z \to \bar w(\bar z)}
-    }
-    {\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\left(\frac{d\bar w}{d\bar
-        z}\right)^{\bar\Delta}\phi_{\Delta,\bar \Delta}(w(z),\bar w(\bar z))\\
-    L_n \phi=0,\quad n>0\\
-    L_0 \phi=\Delta \phi\\
-  \end{split}
-\end{equation}
-$\Delta, \bar \Delta$ называются конформными размерностями поля.
-Все остальные поля называются вторичными и получаются из примарного действием операторов $L_{-n}$:
-\begin{equation}
-  \label{eq:67}
-  L_{-n_1}L_{-n_2}\dots \phi_{\Delta}
-\end{equation}
-Все поля в теории оказываются суммами произведений элементов мультиплетов алгебры Вирасоро.
-
-При некоторых дополнительных предположениях двумерную конформную теорию можно построить и решить
-полностью, если определен набор примарных полей и конформных размерностей.
-
-Существуют различные подходы к аксиоматизации двумерной конформной теории поля. В общем случае нам
-не нужно знать действие, если мы полный знаем набор примарных полей и операторные разложения их
-произведений.
-
-В том случае, если в теории конечное число примарных полей, такая теория называется минимальной.
-Кроме того, теории классифицируются по значениям центрального заряда $c$. Теории с рациональным
-центральным зарядом называются рациональными. Оказывается, что все такие теории могут быть получены
-факторизацией так называемых моделей Весса-Зумино-Новикова-Виттена.
-
-\subsection{WZW-модели}
-\label{sec:wzw}
-
-WZW-модели обладают дополнительной симметрией. Алгебра токов в них --- это алгебра Каца-Муди
-(аффинная алгебра Ли $\mathfrak{g}$), полная киральная алгебра --- полупрямое произведение
-$Vir\ltimes \mathfrak{g}$, примарные поля преобразуются по неприводимым представлениям алгебры $\mathfrak{g}$.
-
-Сейчас я поясню, что все это значит и как строятся такие модели.
-
-Модели Весса-Зумино-Виттена можно строить начиная со следующего действия:
-\begin{equation}
-\label{eq:4}
-  S=S_0+k\Gamma
-\end{equation}
-где $k$ - целое.
-Здесь $S_0$ --- действие нелинейной $\sigma$-модели.
-\begin{equation}
-  \label{eq:5}
-  S_0=\frac{1}{4a^2}\int_{S^2} d^2x\; Tr (\partial^{\mu}g^{-1}\partial_{\mu}g),
-\end{equation}
-где $a^2>0$ - положительный параметр, $g(x)\in G$ - поле со значениями в группе $G$, которую мы
-будем считать полупростой. Действие задается на комплексной плоскости с бесконечностью, которая
-топологически эквивалентна 2-сфере.
-
-В нелинейной $\sigma$-модели конформная инвариантность теряется на квантовом уровне.
-Голоморфный и антиголоморфный токи не сохраняются по отдельности.
-Поэтому мы добавляем член Весса-Зумино $\Gamma$ к действию
-\begin{equation}
-  \label{eq:73}
-\Gamma= - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr\left(
-    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
-\end{equation}
-Он определен на трехмерном многообразии $B$, ограниченном исходным двумерным пространством.
-Через $\tilde{g}$ мы обозначили продолжение поля $g$ на $B$. Такое продолжение не единственно. В
-компактифицированном трехмерном пространстве компактное двумерное многообразие разделяет два
-трехмерных многообразия.
-\begin{figure}[h]
- \centering
-  \includegraphics[width=100mm]{fig3}  
-  \caption{Два продолжения поля на трехмерное многообразие}
-  \label{fig:1}
-\end{figure}
-
-Разность значений члена Весса-Зумино $\Delta\Gamma$ на этих многообразиях
-дается правой частью уравнения (\ref{eq:73}) с интегралом, продолженным на все компактное трехмерное
-пространство. Так как оно топологически эквивалентно три-сфере, получаем
-\begin{equation}
-  \label{eq:75} \Delta\Gamma= - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left( \tilde
-g^{-1}\frac{\partial \tilde g}{\partial y^i} \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
-\tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
-\end{equation}
-$\Delta\Gamma$ определен по модулю $2\pi i$, поэтому Евклидов функциональный интеграл
-с весом $exp(-\Gamma)$ хорошо определен. Значит константа связи, умножаемая на этот член, должна
-быть целочисленной.
-
-Уравнение движения для полного действия (\ref{eq:4}):
-\begin{equation}
-  \label{eq:77}
-  \partial^{\mu}(g^{-1}\partial_{\mu}g)+\frac{a^2 ik}{4\pi}\epsilon_{\mu\nu}\partial^{\mu}(g^{-1}\partial^{\nu}g)=0
-\end{equation}
-В комплексных координатах оно записывается в виде
-\begin{equation}
-  \label{eq:78}
-  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
-\end{equation}
-Видно, что при $a^2=\frac{4\pi}{k}$ у нас имеются законы сохранения
-\begin{equation}
-  \label{eq:79}
-  \partial_z(g^{-1}\partial{\bar z}g)=0
-\end{equation}
-Для токов
-\begin{equation}
-  \label{eq:72}
-  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
-\end{equation}
-
-\begin{equation}
-  \label{eq:100}
-  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
-\end{equation}
-То есть голоморфная и антиголоморфная части отщепляются, что является указанием на наличие
-конформной инвариантности.
-
-Решение классического уравнения движения имеет вид
-\begin{equation}
-  \label{eq:80}
-  g(z,\bar z)=f(z)\bar f(\bar z)
-\end{equation}
-при произвольных $f(z)$ и $\bar f (\bar z)$.
-
-Сохранение по отдельности токов $J_z,\; J_{\bar z}$ приводит к инвариантности действия при преобразованиях
-\begin{equation}
-  \label{eq:81}
-   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)
-\end{equation}
-где $\Omega,\;\bar \Omega \in G$. То есть мы получили локальную $G(z)\times G(\bar z)$-инвариантность.
-
-Для перехода к квантовому случаю мы переопределяем токи
-\begin{equation}
-  \label{eq:82}
-  J(z)\equiv -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
-\end{equation}
- При инфинитезимальных преобразованиях $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ вариация
- $\delta_{\omega}g=\omega g$, а вариация действия
- \begin{equation}
-   \label{eq:11}
-   \delta S=-\frac{1}{2\pi}\int d^2 x \left(\partial_{\bar z}Tr(\omega(z)J(z))+\partial_z Tr(\bar
-     \omega(\bar z)\bar J(\bar z))\right)
- \end{equation}
-Заменяем $d^2 x=-\frac{i}{2} dz d\bar z$, интегрируем по частям и переходим к интегралу по контуру, замыкая
-контур в разных направлениях для голоморфной и антиголоморфной частей.
-Тогда вариация действия
-\begin{equation}
-  \label{eq:83}
-  \delta_{\omega,\bar\omega}S=\frac{i}{4\pi}\oint dz Tr (\omega(z)J(z))-\frac{i}{4\pi}\oint d\bar z Tr(\bar\omega(\bar z)\bar J(\bar z))
-\end{equation}
-Раскладывая токи
-\begin{equation}
-  \label{eq:85}
-  \begin{aligned}
-    J=\sum J^a t^a,\bar J=\sum \bar J^a t^a \\
-    \omega=\sum \omega^a t^a\\
-  \end{aligned}
-\end{equation}
-получаем
-\begin{equation}
-  \label{eq:86}
-  \delta_{\omega,\bar \omega}S=-\frac{1}{2\pi i}\oint dz \sum\omega^a J^a+\frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \bar J^a
-\end{equation}
-Мы также получили тождества Уорда $\delta\left< X\right>=\left<(\delta S)X\right>$
-\begin{equation}
-  \label{eq:87}
-  \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
-  \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
-\end{equation}
-Для токов из явного вида тока и формулы для преобразования $g$ имеем
-\begin{equation}
-  \label{eq:88}
-  \delta_{\omega}J=[\omega,J]-k\partial_z\omega,\quad \delta_{\omega}J^a=\sum i f_{abc}\omega^b J^c-k\partial_z\omega^a
-\end{equation}
-Если это подставить в тождество Уорда, то получаем операторное разложение для токов, которое имеет
-вид 
-\begin{equation}
-  \label{eq:89}
-  J^a(z) J^b(w) \sim \frac{k\delta_{ab}}{(z-w)^2}+\sum i f_{abc}\frac{J^c(w)}{(z-w)}
-\end{equation}
-Раскладывая токи в ряд, получаем
-\begin{equation}
-  \label{eq:90}
-  \begin{aligned}
-    J^a(z)=\sum_{n\in \mathbb Z}z^{n-1}J^a_n\\
-    \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}
-  \end{aligned}
-\end{equation}
-Теперь мы видим, что компоненты токов образуют аффинную алгебру Ли $\hat g$.
-
-Тензор энергии-импульса вводится при помощи конструкции Сугавары как сумма нормально упорядоченных компонент токов
-\begin{equation}
-  \label{eq:102}
-  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
-\end{equation}
-Здесь $h^v$ - дуальное число Кокстера. $h^v=\sum_i \alpha_i^v +1=\frac{1}{2}(\Theta,\Theta+2\rho)$,
-а нормальное упорядочение вводится следующим образом: 
-\begin{equation}
-  \label{eq:12}
-  N(AB)(w)=\frac{1}{2\pi i}\oint\frac{dz}{z-w}A(z)B(w)
-\end{equation}
-
-Тензор энергии-импульса можно разложить на моды $L_n$
-\begin{equation}
-  \label{eq:91}
-  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
-\end{equation}
-Тогда коммутационные соотношения для мод $L_n$ имеют вид
-\begin{equation}
-  \label{eq:92}
-  \begin{aligned}
-    \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
-    c=\frac{k\;\mathrm{dim}g}{k+h^v}\\
-    \left[L_n,J^a_m\right]=-mJ^a_{n+m}.
-  \end{aligned}
-\end{equation}
-
-Таким образом, конструкция Сугавары --- это способ вложения алгебры Вирасоро в универсальную обертывающую аффинной алгебры Ли $\hat{g}$
-
-Полная киральная алгебра модели Весса-Зумино-Виттена равна полупрямому произведению $Vir\ltimes \hat g$
-
-Примарными оказываются поля, которые преобразуются ковариантно под действием $G(z)\times G(\bar z)$,
-как $g(z,\bar z)$. В терминах операторного разложения это свойство переформулируется следующим
-образом:
-\begin{equation}
-  \label{eq:84}
-  \begin{aligned}
-    J^a(z)g(w,\bar w)\sim \frac{-t^a g(w,\bar w)}{(z-w)}\\
-    \bar J^a(z)g(w,\bar w)\sim \frac{ g(w,\bar w)t^a}{(z-w)}
-  \end{aligned}
-\end{equation}
-Любое поле $\phi_{\lambda,\mu}$, преобразующееся ковариантно по отношению к некоторому
-представлению, заданному весом $\lambda$ в голоморфном секторе и весом $\mu$ в антиголоморфном,
-является примарным полем WZW-модели.
-
-В модах это свойство записывается в виде
-\begin{equation}
-  \label{eq:93}
-  \begin{aligned}
-    & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
-    & (J^a_n\phi_{\lambda})=0\quad \mbox{для}\; n>0\\
-  \end{aligned}
-\end{equation}
-Мы можем сопоставить состояние $\left|\phi_{\lambda}\right>$ полю $\phi_{\lambda}$
-  \begin{equation}
-    \label{eq:94}
-    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
-  \end{equation}
-Тогда условия (\ref{eq:93}) для примарных полей дают
-\begin{equation}
-  \label{eq:95}
-  \begin{aligned}
-    & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
-    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{для}\; n>0 \\
-  \end{aligned}
-\end{equation}
-Все вторичные состояния имеют вид
-\begin{equation}
-  \label{eq:97}
-  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
-\end{equation}
-
-Легко видеть, что действие генераторов алгебры Вирасоро на примарные поля имеет вид
-\begin{equation}
-  \label{eq:96}
-  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
-\end{equation}
-Здесь использовано явное выражение для собственных значений квадратичного оператора Казимира.
-
-Примарные поля преобразуются  интегрируемыми конечномерными представлениями, а бесконечномерные и
-неинтегрируемые поля зануляют корреляционные функции.
-В WZW-моделях примарные поля
-принадлежат тензорному произведению неприводимых представлений аффинной алгебры, так как есть
-голоморфный и антиголоморфный сектора.
-
-\subsection{Конформные вложения и модулярно-инвариантные статсуммы}
-\label{sec:modular-invariance}
-
-При изучении конформной теории поля на плоскости или на сфере 
-голоморфный и антиголоморфный сектора можно рассматривать независимо. 
-Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть
-определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать
-взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно) чтобы теория была определена на торе.
-
-(Нарисовать картинку штанов).
-
-В теории критического поведения конформная инвариантность имеет место только в критической точке,
-где голоморфный и антиголоморфный сектора расцеплены. Но вблизи критической точки эти сектора должны
-быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве
-параметров, то эта связь должна сохраняться и в критической точке. Физический спектр теории должен
-плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного
-сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической
-точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния. Здесь
-естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории
-на торе.
-
-%% Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
-%% Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
-%% выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
-%% вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
-%% обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
-%% параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
-%% Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
-%% параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
-%% статсумма дается следом оператора сдвига в степени $m$:
-%% \begin{equation}
-%%   \label{eq:6}
-%%   Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
-%% \end{equation}
-%% Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
-%% конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
-%% $H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
-%% $L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
-%% $P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
-%% можно записать в виде
-%% \begin{equation}
-%%   \label{eq:7}
-%%   \begin{split}
-%%       Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
-%%       L_0)\}\\
-%%       =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
-%%   \end{split}
-%% \end{equation}
-%% Или, если ввести $q=\exp 2\pi i \tau$
-%% \begin{equation}
-%%   \label{eq:2}
-%%   Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
-%% \end{equation}
-%% Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
-%% 
-%% Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
-%% эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
-%% 
-Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
-модулярной инвариантности статсуммы.
-
-При помощи конформных преобразований можно перейти к таким координатам, в которых соотношения
-эквивалентности для тора (граничные условия) записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
-$\mathbb{C}$.
-%% 
-%% Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
-%% конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
-%% $SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
-%% \begin{equation}
-%%   \label{eq:99} A=
-%%   \begin{pmatrix} a & b\\ c & d
-%%   \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
-%% \end{equation}
-%% и матрицы $A$ и $-A$ действуют одинаково на $\tau$
-%% \begin{equation}
-%%   \label{eq:100} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
-%% \end{equation}
-%% $\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
-%% модулярной группой.
-%% 
-Конформная теория поля задаётся примарными полями $\Phi_a$ с конформными размерностями $\Delta_a$.
-
-Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
-произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
-представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсумма на торе
-(\ref{eq:2}) может быть записана в виде
-\begin{equation}
-  \label{eq:9}
-    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
-\end{equation}
-где $\chi_j$ --- нормализованный характер представления $\mathcal{H}_j$,
-\begin{equation}
-  \label{eq:5} \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i
-\tau}
-\end{equation}
-
-Характеры переходят друг в друга при модулярных преобразованиях:
-\begin{equation}
-  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
-\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
-\end{equation}
-где $S$ и $T$ --- постоянные матрицы.
-
-Для WZW-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$. Тогда
-\begin{equation}
-  \label{eq:6} \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi}
-L_{\hat \lambda}\otimes L_{\hat \xi}
-\end{equation}
-
-Коэффициенты ветвления для вложения аффинной подалгебры Ли в аффинную алгебру можно использовать для
-построения модулярно-инвариантной статсуммы в соответствующей WZW-модели. Когда рассматривается
-теория на торе,  набор физически допустимых полей ограничен требованиями модулярной инвариантности.
-
-Простейший модулярный инвариант можно записать следующим образом:
-\begin{equation}
-  \label{eq:34}
-   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
-\end{equation}
-Здесь суммирование ведется по всем конформным семействам (то есть по всем представлениям алгебры
-$\mathfrak{a}$).
-
-Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует
-алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно. (Я сейчас поясню, что это
-значит).
-
-Представления алгебры можно рассматривать как сумму представлений подалгебры.
-
-Если мы рассмотрим редукцию характеров аффинной алгебры
-\begin{equation}
-  \label{eq:8}
-   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
-  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
-\end{equation}
-и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится. То есть из
-диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый не диагональный инвариант для
-подалгебры $\mathfrak{a}$. Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
-ней конформная инвариантность.
-
-Пусть $J^{a_j}_{-n_j}$ и $\tilde{J}^{a'_j}_{-n_j}$ --- понижающие операторы алгебр  $\mathfrak{g}$ и
-$\mathfrak{a}\subset\mathfrak{g}$.  $\pi_{\mathfrak{a}}$ --- проекционный оператор
-$\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$. В теории, связанной с  $\mathfrak{g}$
-с вакуумом $\left|\lambda\right>$ будут следующие состояния:
-\begin{equation}
-  \label{eq:109}
-  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
-\end{equation}
-Вакуум $\mathfrak{g}$-инвариантен, то есть $J_0^a\left|0\right>=0$. При проекции на подалгебру
-$\mathfrak{a}$ состояния примут вид
-\begin{equation}
-  \label{eq:110}
-  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
-\end{equation}
-Из $\mathfrak{g}$-ивариантности вакуума следует его $\mathfrak{a}$-инвариантность, но для тензора
-энергии-импульса в общем случае это не так. Поэтому тензор энергии-импульса большей теории должен
-состоять только из генераторов $\tilde{J}$. Тогда $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow
-c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению
-\begin{equation}
-  \label{eq:111}
-  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
-\end{equation}
-Здесь $x_e$ --- индекс вложения, а  $g$, $a$ --- дуальные числа Кокстера, которые характеризуют алгебры.
-
-Можно показать, что только для представлений уровня 1 это равенство удовлетворяется. То есть класс
-конформных вложений не слишком широк и существует полная их классификация. Кроме того, для
-конформных вложений существуют специальные методы разложения представлений.
-
-Модулярная инвариантность статсуммы для полей, принадлежащих представлениям алгебры  $\mathfrak{g}$,
-сохраняется при проекции на подалгебру $\mathfrak{a}$. Если все представления $\mathfrak{g}$ в теории
-удовлетворяют описанным требованиям, то при проекции мы получаем конформную теорию поля.
-
-Существует теорема о том, что для конформного вложения  $\mathfrak{a}\subset\mathfrak{g}$ только
-конечное число коэффициентов ветвления отлично от нуля. Поэтому после того, как мы разложили все
-представления $\mathfrak{g}$ мы подставляем результаты в выражение для статсуммы и получаем
-модулярно-инвариантную статсумму для вложенной теории. Такая статсумма уже не будет иметь
-диагональный вид:
-\begin{equation}
-  \label{eq:36}
-   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
-\end{equation}
-Наша работа посвящена разработке общего метода редукции представлений аффинных алгебр Ли, поэтому
-случай конформных вложений --- лишь один из примеров применения нашего метода. Однако в этом случае
-физический смысл наиболее очевиден.
 

### 2011-11-10 AffineLieAlgebras/Thesis/common.tex
Work on CFT section (axiomatics) + wzw moved to chapter 1

@@
 \mkcommonsect{actuality}{Актуальность работы}{%
-Текст раздела. Ссылка~\cite{Yoffe_1993_AP_42_173}.
+Проблема вычисления коэффициентов ветвления для представлений алгебр Ли стоит уже многие десятилетия.
+Она актуальна для различных физических приложений.
+Вместе с тем, в отличие от кратностей весов не существует особенно эффективных алгоритмов.
 }
@@
 \mkcommonsect{objective}{Цель диссертационной работы}{%
-Текст раздела
+Разработка рекуррентного подхода к функциям ветвления аффинных алгебр Ли, его связь с проблемами теории представлений и его приложения в моделях конформной теории поля.
 }
@@
 \mkcommonsect{novelty}{Научная новизна}{%
-Текст раздела
+Предложен эффективный алгоритм для вычисления коэффициентов ветвления, показана его связь с резольвентой Бернштейна-Гельфанда-Гельфанда.
 }
@@
 \mkcommonsect{value}{Практическая значимость}{%
-Текст раздела
+Результаты работы                                  
 }

### 2011-11-16 AffineLieAlgebras/Thesis/review.tex
More work on thesis (mostly introduction, axiomatic CFT and WZW)

@@
-\review
+%\review
+
+\chapter{Конформная теория поля}
+\label{cha:CFT}
+
+Двумерная конформная теория поля возникла при изучении моделей критического поведения в двумерных моделях и привлекла большое внимание благодаря новым идеям и своей связи с теорией струн.
+Двумерная конформная теория поля выделяется как модель квантовой теории поля из-за того, что она может быть сформулирована аксиоматически, например, следующим образом.
+Введем пространство $S(\mathbb{R}^{n})$ тест-функций $f:\mathbb{R}^{n}\to \mathbb{C}$.
+Распределения или обобщенные функции -- это линейные функционалы на нем $T:S(\mathbb{R}^{n})\to \mathbb{C}$ со свойством непрерывности.
+Каждой функции $g:\mathbb{R}^{n}\to \mathbb{C}$ можно поставить в соответствие некоторое распределение $T_{g}$ по правилу
+\begin{equation}
+  \label{eq:30}
+  T_{g}(f)=\int_{\mathbb{R}^{n}}g(x)f(x) dx
+\end{equation}
+На пространстве обобщенных функций можно ввести операторы дифференцирования с мультииндексами $\alpha$:
+\begin{equation}
+  \label{eq:41}
+  \partial^{\alpha}:=(-1)^{|\alpha|}T(\partial^{\alpha} f)
+\end{equation}
+При этом
+\begin{equation}
+  \label{eq:42}
+  \partial^{\alpha}T_{g}=T_{\partial ^{\alpha}g}
+\end{equation}
+и для любой обобщенной функции $T$ есть $n\in \mathbb{N}$, такое что
+\begin{equation}
+  \label{eq:49}
+  T=\sum_{0\leq |\alpha|\leq n}\partial^{\alpha} T_{g_{\alpha}}.
+\end{equation}
+В квантовой теории поля должны быть поля и состояния.
+Состояния определяются как элементы некоторого гильбертова пространства $\mathbb{H}$.
+Пространство операторов на $\mathbb{H}$ мы обозначим через $\mathcal{O}$.
+Тогда поля -- это операторно-значные распределения $\varphi:S(\mathbb{R}^{n})\to \mathcal{O}$, такие, что существует плотное подпространство $D\subset \mathbb{H}$ и
+\begin{enumerate}
+\item Для любой тест-функции $f\in S(\mathbb{R}^{n})$ подпространство $D\subset D_{\varphi(f)}$, где $D_{\varphi(f)}$ -- область определения оператора $\varphi(f)$.
+\item Индуцированное отображение $f\to \varphi(f)|_{D}$ из $S(\mathbb{R}^{n})$ в $\mathrm{End}(D)$ линейно.
+\item Для любых $\nu\in D$ и $\omega\in \mathbb{H}$ отображение $f\to \left<\omega,\varphi(f)(\nu)\right>$ является распределением. 
+\end{enumerate}
+Можно определять конформную теорию поля путем задания всех полей, как делается в подходе, предложенном в работе \cite{moore1989classical}.
+Мы воспользуемся определением из работы \cite{felder1989structure}, подробно изложенном в книге \cite{schottenloher2008mathematical}.
+Чтобы определить конформную теорию поля оказывается достаточно задать все корреляционные функции.
+Обычно их понимают следующим образом.
+Пусть $\Omega\in\mathbb{H}$ -- вакуум, $n$-точечные корреляционные функции в квантовой теории поля обычно понимают, как
+\begin{equation}
+  \label{eq:50}
+  G_{i_{1},\dots ,i_{n}}(z_{1},\dots,z_{n}):=\left<\Omega|\varphi_{i_{1}}(z_{1})\dots \varphi_{i_{n}}(z_{n})|\Omega\right>, \quad |z_{n}|>\dots > |z_{1}|,
+\end{equation}
+где $\varphi_{i_{k}}$ -- поля в теории.
+$n$-точечные корреляционные функции можно аналитически продолжить на пространство $M_{n}=\{(z_{1},\dots,z_{n})\in \mathbb{C}^{n}: z_{i}\neq z_{j},\; i\neq j\}$.
+$M_{n}^{+}$ состоит из наборов, где $\mathrm{Re}\;z_{i}>0$ для любого $i$.
+Введем последовательность пространств тест-функций $S_{n}^{+}$, где $S_{0}^{+}=\mathbb{C}$, а $S_{n}^{+}=\{f\in S(\mathbb{C}^{n}): \mathrm{supp}(f)\subset M^{+}_{n}\} $.
+Теперь мы можем определить корреляционные функции не обращаясь к понятию полей.
+
+  Пусть $B_{0}$ -- индексное множество (счетное), последовательности произвольной длины $(i_{1},\dots,i_{n})\in B_{0}^{n}$ образуют пространство мультииндексов $i\in B$.
+Корреляционные функции $G_{i_{1},\dots, i_{n}}:M_{n}\to \mathbb{R}$ удовлетворяют следующим аксиомам.
+\begin{axiom}
+  (Аксиома локальности)
+  Для всех $(i_{1},\dots,i_{n})\in B_{0}^{n}$, $(z_{1},\dots, z_{n})\in M_{n}$ и $\pi\in S_{n}$ -- перестановок множества из $n$ элементов верно равенство
+  \begin{equation}
+    \label{eq:51}
+    G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n})=G_{i_{\pi(1)},\dots i_{\pi(n)}}(z_{\pi(1)},\dots, z_{\pi(n)})
+  \end{equation}
+\end{axiom}
+Рассмотрим группу движений двумерного пространства $E_{2}$, генераторами которой являются повороты $r_{\alpha}:\mathbb{C}\to\mathbb{C}, \; z\to e^{i\alpha}z,\; \alpha\in \mathbb{R}$ и трансляции $t_{a}:\mathbb{C}\to\mathbb{C},\; z\to z+a,\; a\in\mathbb{C}$.
+\begin{axiom}
+  (Аксиома ковариантности)
+  Для любого индекса $i\in B_{0}$  существуют независимые конформные веса $h_{i},\bar h_{i}\in \mathbb{R}$, такие, что для всех преобразований $w\in E_{2}$
+  \begin{equation}
+    \label{eq:52}
+    G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n},\bar z_{1},\dots, \bar z_{n})=\prod_{j=1}^{n}\left(\frac{dw(z_{j})}{dz}\right)^{h_{i_{j}}}\left(\overline{\frac{dw(z_{j})}{dz}}\right)^{\bar{h}_{i_{j}}} G_{i_{\pi(1)},\dots i_{\pi(n)}}(w_{1},\dots, w_{n},\bar w_{1},\dots,\bar w_{n}),
+  \end{equation}
+где $w_{i}=w(z_{i})$, а $s_{i}=h_{i}-\bar h_{i}, d_{i}=h_{i}+\bar h_{i}$  -- конформный спин и скейлинговая размерность.
+\end{axiom}
+\begin{axiom}
+  (Положительность по отношению к отражениям).
+  Обозначим через $\Theta:\mathbb{C}\to\mathbb{C}$  отображение $z=t+i y\to \Theta(z)= -t+i y$.
+Тогда аксиома утверждает, что существует инволюция $\star:B_{0}\to B_{0}$, $\star^{2}=\mathrm{id}_{B_{0}}$, которая продолжается на $B$ ($i\to i^{*}$), и выполняются свойства
+  \begin{enumerate}
+  \item Верно равенство
+    \begin{equation}
+      \label{eq:53}
+      G_{i}(z)=G_{i^{*}}(\Theta(z))=G_{i^{*}}(-z^{*})
+    \end{equation}
+  \item Обозначим через $\underline{S}^{+}$ пространство последовательности тест-функций $\underline{f}=(f_{i})_{i\in B}, f_{i}\in S^{+}_{n}$. Тогда
+    \begin{multline}
+      \label{eq:54}
+      \left<\underline{f},\underline{f}\right>=\\
+      \sum_{i,j\in B}\sum_{n,m}\int_{M_{n+m}}G_{i^{*} j}(\Theta(z_{1}),\dots ,\Theta(z_{n}),w_{1},\dots,w_{m}) f_{i}(z)^{*}f_{j}(w) d^{n}z d^{m}w 
+      \geq 0,\\ \forall \underline{f}\in \underline{S}^{+}
+    \end{multline}
+  \end{enumerate}
+\end{axiom}
+Эта аксиома позволяет восстановить гильбертово пространство $\mathbb{H}$, так как она дает положительную полу-определенную форму $H$ на $\underline{S}^{+}$.
+То есть мы можем определить $\mathbb{H}$ как пополнение $\underline{S}^{+}$ факторизованное по $\mathrm{ker}\; H$ с произведением \eqref{eq:54}.
+Мы можем построить и полевые операторы.
+Для $j\in B_{0}$ определим $\varphi_{j}$ как операторно-значную обобщенную функцию.
+Пусть $f\in S^{+}$, $\underline{g}\in\underline{S}^{+}$, а через $[\underline{g}]$ обозначим класс эквивалентности $\underline{g}$ по отношению к ядру $H$.
+Определим $\varphi_{j}(f)([\underline{g}])$ как класс эквивалентности $\underline{g}\times f$, такой, что
+\begin{equation}
+  \label{eq:55}
+  \begin{array}{l}
+    \underline{g}\times f=((\underline{g}\times f)_{i_{1},\dots,i_{n+1}});\quad\quad (i_{1},\dots,i_{n+1})\in B\\
+    (\underline{g}\times f)_{i_{1},\dots,i_{n+1}}(z_{1},\dots,z_{n+1}):=g_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n})f(z_{n+1})\delta_{j,i_{n+1}}.
+  \end{array}
+\end{equation}
+Можно показать, что эта конструкция порождает унитарное представление $U$ группы $E_{2}$ евклидовых движений плоскости на гильбертовом пространстве $\mathbb{H}$.
+Кроме того, существует инвариантное плотное подпространство $D\subset \mathbb{H}$, такое, что отображения $\varphi_{j}(f):[\underline{g}]\to [\underline{g}\times f]$ определены на $D$ для всех $j\in B_{0}$ и $\varphi_{j}(f)(D)\subset D$.
+Также существует вакуум $\Omega\in\mathbb{H}: \Omega=[f];\; f_{\emptyset}=1, f_{i}=0\quad \forall i\neq \emptyset$.
+Тогда
+следующая теорема определяет структуру двумерной евклидовой теории поля
+\begin{theorem}
+  \begin{enumerate}
+  \item Для всех $j\in B_{0}$ отображения $\varphi_{j}:S^{+}\to \mathrm{End}(D)$ линейны, $\varphi_{j}$ -- полевые операторы, $\varphi_{j}(D)\subset D, \Omega\in D$ и вакуум $\Omega$ инвариантен относительно инвариантных представлений $U$ группы $E_{2}$.
+  \item Поля $\varphi_{j}$ преобразуются ковариантно по отношению к представлению $U$, для $w\in E_{2}$:
+    \begin{equation}
+      \label{eq:57}
+      U(w)\varphi_{j}(z)U(w)^{*}=\left(\frac{\partial w}{\partial z}\right)^{h_{j}}\varphi_{j}(w(z))
+    \end{equation}
+  \item Матричные коэффициенты $\left<\Omega|\varphi_{i_{1}}(z_{1})\dots \varphi_{i_{n}}(z_{n})|\Omega\right>$ представляются аналитическими функциями, которые при $\mathrm{Re}z_{n}>\dots>\mathrm{Re}z_{1}>0$ совпадают с корреляционными функциями
+  \begin{equation}
+    \label{eq:56}
+    \left<\Omega|\varphi_{i_{1}}(z_{1})\dots \varphi_{i_{n}}(z_{n})|\Omega\right>=G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n})
+  \end{equation}
+  \end{enumerate}
+\end{theorem}
+Теперь добавим аксиомы, специфичные для конформной теории поля. Во-первых введем масштабную инвариантность.
+\begin{axiom}
+  (Масштабная инвариантность)
+  Корреляционная функция $G_{i}, i\in B$ преобразуется ковариантно \eqref{eq:52} при масштабных преобразованиях $w(z)=e^{\tau}z$, то есть
+  \begin{equation}
+    \label{eq:58}
+    G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n})=\left(e^{\tau}\right)^{h_{1}+\dots+h_{n}+\bar{h}_{1}+\dots+\bar{h}_{n}} G_{i_{1},\dots,i_{n}}(e^{\tau} z_{1},\dots,e^{\tau} z_{n}),
+  \end{equation}
+  где $(z_{1},\dots,z_{n})\in M_{n},\quad h_{j}=h_{i_{j}}$
+\end{axiom}
+Из требований масштабной инвариантности можно вычислить двухточечные функции. 
+\begin{axiom}
+  (Существование тензора энергии-импульса)
+  Среди полей $\varphi_{i},\; i\in B_{0}$ есть четыре поля $T_{\mu\nu},\; \mu,\nu=0,1$, такие, что $T_{\mu\nu}=T_{\nu\mu},\quad T_{\mu\nu}^{*}=T_{\nu\mu}(\Theta(z)),\quad \partial_{0} T_{\mu 0}+\partial_{1}T_{\mu 1}=0$, скейлинговая размерность поля $d(T_{\mu\nu})=h_{\mu\nu}+\bar{h}_{\mu\nu}=2$, конформный спин $s(T_{00}-T_{11}\pm 2i T_{01})=\pm 2$.
+\end{axiom}
+Можно показать, что $\mathrm{tr} T_{\mu\nu}=0$ и $T=T_{00}-i T_{01}$ не зависит от $\bar z$, то есть $\bar \partial T=0$. Операторы 
+\begin{equation}
+  \label{eq:59}
+    L_{n}=\oint \frac{dz}{2\pi i} z^{n+1} T(z)
+\end{equation}
+удовлетворяют коммутационным соотношениям алгебры Вирасоро.
+
+Примарными называются поля $\varphi_{i}, i\in B_{0}$, такие, что
+\begin{equation}
+  \label{eq:60}
+  [L_{n}, \varphi_{i}(z)]=z^{n+1}\partial \varphi_{i}(z)+h_{i}(n+1)z^{n}\varphi_{i}(z),\quad \forall n\in\mathbb{Z}
+\end{equation}
+Для каждого примарного поля $\varphi_{i}$ можно определить конформное семейство $[\varphi_{i}]$, состоящее из полей вторичных $\varphi_{i}^{\alpha}(z)=L_{-\alpha_{1}}(z)\dots L_{-\alpha_{n}}(z)\varphi_{i}(z)$, где $L_{-n}(z)=\frac{1}{2\pi i}\oint\frac{T(\xi)}{(\xi-z)^{n+1}} d\xi$.
+Заметим, что $L_{n}(0)=L_{n}$ и корреляционные функции вторичных полей могут быть выражены через корреляционные функции примарных.
+Последняя аксиома определяет операторное разложение
+\begin{axiom}
+(Операторное разложение).
+Корреляционные функции примарных полей  при $z_{i}\to z_{j}$ удовлетворяют уравнению:
+\begin{multline}
+  \label{eq:61}
+  \left<\Omega|\varphi_{i_{1}}(z_{1})\dots\varphi_{i}(z_{i})\dots \varphi_{j}(z_{j})\dots \varphi_{i_{n}}(z_{n})|\Omega\right>=\\
+  \sum_{k\in B_{0}}C_{ijk} (z_{i}-z_{j})^{h_{k}-h_{i}-h_{j}} \left<\Omega|\varphi_{i_{1}}(z_{1})\dots\varphi_{k}(z_{k})\dots \varphi_{i_{n}}(z_{n})|\Omega\right>\\
+  +\mbox{регулярные члены}
+\end{multline}
+
+\end{axiom}
+
+Если дополнительно предположить, что операторное разложение ассоциативно (так называемый ``конформный бутстрап''), то вся теория определяется набором примарных полей $\varphi_{j}, j\in B_{0}$, их размерностями и коэффициентами операторного разложения $C_{ijk}$.
+
+Простейший класс конформных теория поля составляют минимальные модели, в которых число примарных полей конечно.
+
+\section{Модели Весса-Зумино-Новикова-Виттена и алгебры Ли}
+\label{sec:WZNW-models}
+
+\subsection{Напоминание про двумерную конформную теорию поля}
+\label{sec:CFT}
+
+Конформное преобразование --- это преобразование, меняющее только масштаб у метрического тензора:
+\begin{equation}
+  \label{eq:10}
+  g'_{\mu\nu}(x')=\Lambda(x)g_{\mu\nu}(x)
+\end{equation}
+
+Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований.
+
+В теории струн двумерная конформная теория поля описывает динамику на мировой поверхности, а в
+теории критических явлений --- фазовые переходы в двумерных системах.
+
+%% В $D$-мерном случае генераторы у таких преобразований следующие:
+%% \begin{align}
+%%   \label{eq:1}
+%%   & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\
+%%   &P_\mu \equiv-i\partial_\mu \,, \\
+%%   &D \equiv-ix_\mu\partial^\mu \,, \\
+%%   &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,,
+%% \end{align}
+%% 
+На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
+В двумерном случае существует бесконечное число локально-конформных преобразований.
+Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это
+условие эквивалентно уравнению Коши-Римана для голоморфных функций ($\partial_{\bar z}w(z,\bar
+z)=0$).
+
+Таким образом локально-конформные преобразования находятся в однозначном соответствии с множеством
+всех аналитических функций $w(z)$ на плоскости.
+
+Глобальные конформные преобразования имеют вид $f(z)=\frac{az+b}{cz+d},\; ad-bc=1$.
+
+Рассмотрим инфинитезимальные преобразования $w(z)=z+\epsilon(z),\quad
+\epsilon(z)=\sum_{-\infty}^{\infty}c_nz^{n+1}$. 
+Тогда для бесспинового поля $\phi(z,\bar z)$ верно следующее: $\phi'(z',\bar z')=\phi(z,\bar z)$,
+$\delta\phi=-\epsilon(z)\partial\phi-\bar \epsilon(\bar z)\bar \partial \phi=\sum_n(c_n L_n\phi+\bar
+c_n\bar L_n\phi)$, где $L_n=-z^{n+1}\partial_z,\quad \bar L_n=-\bar z^{n+1}\partial_{\bar z}$
+
+Мы видим, что в классической теории алгебра конформных преобразований --- это алгебра Витта, которая
+порождается генераторами $\{L_n, n\in \mathbb{Z}\}$ --- модами разложения оператора энергии-импульса $T$, с
+коммутационными соотношениями
+\begin{equation}
+  \label{eq:2}
+  [L_m,L_n]=(m-n)L_{m+n}
+\end{equation}
+При квантовании возникает конформная аномалия, что соответствует центральному расширению алгебры (то
+есть появлению центрального заряда $c$). В коммутационные соотношения надо добавить член
+$\frac{c}{12}(m^3-m)\delta_{m+n,0}$. В результате получаем алгебру Вирасоро.
+
+(Про тензор энергии-импульса:
+$x^{\mu}\to x^{\mu}+\epsilon^{\mu}\Rightarrow \delta S=\int d^2 x
+T^{\mu\nu}\partial_{\mu}\epsilon_{\nu}=
+\frac{1}{2}\int d^2 xT_{\mu}^{\mu}\partial_{\rho}\epsilon^{\rho}$
+В двумерной конформной теории поля тензор энергии-импульса бесследовый).
+
+Поля теории $\phi(z,\bar z)$ должны преобразовываться определенным образом при конформных преобразованиях.
+Оказывается, что все поля группируются в конформные семейства, в которых есть одно примарное поле
+\begin{equation}
+  \label{eq:3}
+  \begin{split}
+    \phi_{\Delta,\bar \Delta}(z,\bar z)\underset{
+      \genfrac{}{}{0pt}{}{z\to w(z)}
+        {\bar z \to \bar w(\bar z)}
+    }
+    {\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\left(\frac{d\bar w}{d\bar
+        z}\right)^{\bar\Delta}\phi_{\Delta,\bar \Delta}(w(z),\bar w(\bar z))\\
+    L_n \phi=0,\quad n>0\\
+    L_0 \phi=\Delta \phi\\
+  \end{split}
+\end{equation}
+$\Delta, \bar \Delta$ называются конформными размерностями поля.
+Все остальные поля называются вторичными и получаются из примарного действием операторов $L_{-n}$:
+\begin{equation}
+  \label{eq:67}
+  L_{-n_1}L_{-n_2}\dots \phi_{\Delta}
+\end{equation}
+Все поля в теории оказываются суммами произведений элементов мультиплетов алгебры Вирасоро.
+
+При некоторых дополнительных предположениях двумерную конформную теорию можно построить и решить
+полностью, если определен набор примарных полей и конформных размерностей.
+
+Существуют различные подходы к аксиоматизации двумерной конформной теории поля. В общем случае нам
+не нужно знать действие, если мы полный знаем набор примарных полей и операторные разложения их
+произведений.
+
+В том случае, если в теории конечное число примарных полей, такая теория называется минимальной.
+Кроме того, теории классифицируются по значениям центрального заряда $c$. Теории с рациональным
+центральным зарядом называются рациональными. Оказывается, что все такие теории могут быть получены
+факторизацией так называемых моделей Весса-Зумино-Новикова-Виттена.
+
+\subsection{WZW-модели}
+\label{sec:wzw}
+
+WZW-модели обладают дополнительной симметрией. Алгебра токов в них --- это алгебра Каца-Муди
+(аффинная алгебра Ли $\mathfrak{g}$), полная киральная алгебра --- полупрямое произведение
+$Vir\ltimes \mathfrak{g}$, примарные поля преобразуются по неприводимым представлениям алгебры $\mathfrak{g}$.
+
+Сейчас я поясню, что все это значит и как строятся такие модели.
+
+Модели Весса-Зумино-Виттена можно строить начиная со следующего действия:
+\begin{equation}
+\label{eq:4}
+  S=S_0+k\Gamma
+\end{equation}
+где $k$ - целое.
+Здесь $S_0$ --- действие нелинейной $\sigma$-модели.
+\begin{equation}
+  \label{eq:5}
+  S_0=\frac{1}{4a^2}\int_{S^2} d^2x\; Tr (\partial^{\mu}g^{-1}\partial_{\mu}g),
+\end{equation}
+где $a^2>0$ - положительный параметр, $g(x)\in G$ - поле со значениями в группе $G$, которую мы
+будем считать полупростой. Действие задается на комплексной плоскости с бесконечностью, которая
+топологически эквивалентна 2-сфере.
+
+В нелинейной $\sigma$-модели конформная инвариантность теряется на квантовом уровне.
+Голоморфный и антиголоморфный токи не сохраняются по отдельности.
+Поэтому мы добавляем член Весса-Зумино $\Gamma$ к действию
+\begin{equation}
+  \label{eq:73}
+\Gamma= - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr\left(
+    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+Он определен на трехмерном многообразии $B$, ограниченном исходным двумерным пространством.
+Через $\tilde{g}$ мы обозначили продолжение поля $g$ на $B$. Такое продолжение не единственно. В
+компактифицированном трехмерном пространстве компактное двумерное многообразие разделяет два
+трехмерных многообразия.
+\begin{figure}[h]
+ \centering
+  \includegraphics[width=100mm]{fig3}  
+  \caption{Два продолжения поля на трехмерное многообразие}
+  \label{fig:1}
+\end{figure}
+
+Разность значений члена Весса-Зумино $\Delta\Gamma$ на этих многообразиях
+дается правой частью уравнения (\ref{eq:73}) с интегралом, продолженным на все компактное трехмерное
+пространство. Так как оно топологически эквивалентно три-сфере, получаем
+\begin{equation}
+  \label{eq:75} \Delta\Gamma= - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left( \tilde
+g^{-1}\frac{\partial \tilde g}{\partial y^i} \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+\tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
+\end{equation}
+$\Delta\Gamma$ определен по модулю $2\pi i$, поэтому Евклидов функциональный интеграл
+с весом $exp(-\Gamma)$ хорошо определен. Значит константа связи, умножаемая на этот член, должна
+быть целочисленной.
+
+Уравнение движения для полного действия (\ref{eq:4}):
+\begin{equation}
+  \label{eq:77}
+  \partial^{\mu}(g^{-1}\partial_{\mu}g)+\frac{a^2 ik}{4\pi}\epsilon_{\mu\nu}\partial^{\mu}(g^{-1}\partial^{\nu}g)=0
+\end{equation}
+В комплексных координатах оно записывается в виде
+\begin{equation}
+  \label{eq:78}
+  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
+\end{equation}
+Видно, что при $a^2=\frac{4\pi}{k}$ у нас имеются законы сохранения
+\begin{equation}
+  \label{eq:79}
+  \partial_z(g^{-1}\partial{\bar z}g)=0
+\end{equation}
+Для токов
+\begin{equation}
+  \label{eq:72}
+  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
+\end{equation}
+
+\begin{equation}
+  \label{eq:100}
+  \partial_{\bar z}J=0,\quad \partial_z \bar J=0
+\end{equation}
+То есть голоморфная и антиголоморфная части отщепляются, что является указанием на наличие
+конформной инвариантности.
+
+Решение классического уравнения движения имеет вид
+\begin{equation}
+  \label{eq:80}
+  g(z,\bar z)=f(z)\bar f(\bar z)
+\end{equation}
+при произвольных $f(z)$ и $\bar f (\bar z)$.
+
+Сохранение по отдельности токов $J_z,\; J_{\bar z}$ приводит к инвариантности действия при преобразованиях
+\begin{equation}
+  \label{eq:81}
+   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)
+\end{equation}
+где $\Omega,\;\bar \Omega \in G$. То есть мы получили локальную $G(z)\times G(\bar z)$-инвариантность.
+
+Для перехода к квантовому случаю мы переопределяем токи
+\begin{equation}
+  \label{eq:82}
+  J(z)\equiv -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
+\end{equation}
+ При инфинитезимальных преобразованиях $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ вариация
+ $\delta_{\omega}g=\omega g$, а вариация действия
+ \begin{equation}
+   \label{eq:11}
+   \delta S=-\frac{1}{2\pi}\int d^2 x \left(\partial_{\bar z}Tr(\omega(z)J(z))+\partial_z Tr(\bar
+     \omega(\bar z)\bar J(\bar z))\right)
+ \end{equation}
+Заменяем $d^2 x=-\frac{i}{2} dz d\bar z$, интегрируем по частям и переходим к интегралу по контуру, замыкая
+контур в разных направлениях для голоморфной и антиголоморфной частей.
+Тогда вариация действия
+\begin{equation}
+  \label{eq:83}
+  \delta_{\omega,\bar\omega}S=\frac{i}{4\pi}\oint dz Tr (\omega(z)J(z))-\frac{i}{4\pi}\oint d\bar z Tr(\bar\omega(\bar z)\bar J(\bar z))
+\end{equation}
+Раскладывая токи
+\begin{equation}
+  \label{eq:85}
+  \begin{aligned}
+    J=\sum J^a t^a,\bar J=\sum \bar J^a t^a \\
+    \omega=\sum \omega^a t^a\\
+  \end{aligned}
+\end{equation}
+получаем
+\begin{equation}
+  \label{eq:86}
+  \delta_{\omega,\bar \omega}S=-\frac{1}{2\pi i}\oint dz \sum\omega^a J^a+\frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \bar J^a
+\end{equation}
+Мы также получили тождества Уорда $\delta\left< X\right>=\left<(\delta S)X\right>$
+\begin{equation}
+  \label{eq:87}
+  \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
+  \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
+\end{equation}
+Для токов из явного вида тока и формулы для преобразования $g$ имеем
+\begin{equation}
+  \label{eq:88}
+  \delta_{\omega}J=[\omega,J]-k\partial_z\omega,\quad \delta_{\omega}J^a=\sum i f_{abc}\omega^b J^c-k\partial_z\omega^a
+\end{equation}
+Если это подставить в тождество Уорда, то получаем операторное разложение для токов, которое имеет
+вид 
+\begin{equation}
+  \label{eq:89}
+  J^a(z) J^b(w) \sim \frac{k\delta_{ab}}{(z-w)^2}+\sum i f_{abc}\frac{J^c(w)}{(z-w)}
+\end{equation}
+Раскладывая токи в ряд, получаем
+\begin{equation}
+  \label{eq:90}
+  \begin{aligned}
+    J^a(z)=\sum_{n\in \mathbb Z}z^{n-1}J^a_n\\
+    \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}
+  \end{aligned}
+\end{equation}
+Теперь мы видим, что компоненты токов образуют аффинную алгебру Ли $\hat g$.
+
+Тензор энергии-импульса вводится при помощи конструкции Сугавары как сумма нормально упорядоченных компонент токов
+\begin{equation}
+  \label{eq:102}
+  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
+\end{equation}
+Здесь $h^v$ - дуальное число Кокстера. $h^v=\sum_i \alpha_i^v +1=\frac{1}{2}(\Theta,\Theta+2\rho)$,
+а нормальное упорядочение вводится следующим образом: 
+\begin{equation}
+  \label{eq:12}
+  N(AB)(w)=\frac{1}{2\pi i}\oint\frac{dz}{z-w}A(z)B(w)
+\end{equation}
+
+Тензор энергии-импульса можно разложить на моды $L_n$
+\begin{equation}
+  \label{eq:91}
+  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
+\end{equation}
+Тогда коммутационные соотношения для мод $L_n$ имеют вид
+\begin{equation}
+  \label{eq:92}
+  \begin{aligned}
+    \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
+    c=\frac{k\;\mathrm{dim}g}{k+h^v}\\
+    \left[L_n,J^a_m\right]=-mJ^a_{n+m}.
+  \end{aligned}
+\end{equation}
+
+Таким образом, конструкция Сугавары --- это способ вложения алгебры Вирасоро в универсальную обертывающую аффинной алгебры Ли $\hat{g}$
+
+Полная киральная алгебра модели Весса-Зумино-Виттена равна полупрямому произведению $Vir\ltimes \hat g$
+
+Примарными оказываются поля, которые преобразуются ковариантно под действием $G(z)\times G(\bar z)$,
+как $g(z,\bar z)$. В терминах операторного разложения это свойство переформулируется следующим
+образом:
+\begin{equation}
+  \label{eq:84}
+  \begin{aligned}
+    J^a(z)g(w,\bar w)\sim \frac{-t^a g(w,\bar w)}{(z-w)}\\
+    \bar J^a(z)g(w,\bar w)\sim \frac{ g(w,\bar w)t^a}{(z-w)}
+  \end{aligned}
+\end{equation}
+Любое поле $\phi_{\lambda,\mu}$, преобразующееся ковариантно по отношению к некоторому
+представлению, заданному весом $\lambda$ в голоморфном секторе и весом $\mu$ в антиголоморфном,
+является примарным полем WZW-модели.
+
+В модах это свойство записывается в виде
+\begin{equation}
+  \label{eq:93}
+  \begin{aligned}
+    & (J_0^a \phi_{\lambda})=-t^a_{\lambda}\phi_{\lambda}\\
+    & (J^a_n\phi_{\lambda})=0\quad \mbox{для}\; n>0\\
+  \end{aligned}
+\end{equation}
+Мы можем сопоставить состояние $\left|\phi_{\lambda}\right>$ полю $\phi_{\lambda}$
+  \begin{equation}
+    \label{eq:94}
+    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
+  \end{equation}
+Тогда условия (\ref{eq:93}) для примарных полей дают
+\begin{equation}
+  \label{eq:95}
+  \begin{aligned}
+    & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>\\
+    & J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{для}\; n>0 \\
+  \end{aligned}
+\end{equation}
+Все вторичные состояния имеют вид
+\begin{equation}
+  \label{eq:97}
+  J^{a_1}_{-n_1}J^{a_2}_{n_2}\dots\left|\phi_{\lambda}\right>
+\end{equation}
+
+Легко видеть, что действие генераторов алгебры Вирасоро на примарные поля имеет вид
+\begin{equation}
+  \label{eq:96}
+  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
+\end{equation}
+Здесь использовано явное выражение для собственных значений квадратичного оператора Казимира.
+
+Примарные поля преобразуются  интегрируемыми конечномерными представлениями, а бесконечномерные и
+неинтегрируемые поля зануляют корреляционные функции.
+В WZW-моделях примарные поля
+принадлежат тензорному произведению неприводимых представлений аффинной алгебры, так как есть
+голоморфный и антиголоморфный сектора.
+
+\subsection{Конформные вложения и модулярно-инвариантные статсуммы}
+\label{sec:modular-invariance}
+
+При изучении конформной теории поля на плоскости или на сфере 
+голоморфный и антиголоморфный сектора можно рассматривать независимо. 
+Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть
+определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать
+взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно) чтобы теория была определена на торе.
+
+(Нарисовать картинку штанов).
+
+В теории критического поведения конформная инвариантность имеет место только в критической точке,
+где голоморфный и антиголоморфный сектора расцеплены. Но вблизи критической точки эти сектора должны
+быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве
+параметров, то эта связь должна сохраняться и в критической точке. Физический спектр теории должен
+плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного
+сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической
+точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния. Здесь
+естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории
+на торе.
+
+%% Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
+%% Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
+%% выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
+%% вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
+%% обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
+%% параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
+%% Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
+%% параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
+%% статсумма дается следом оператора сдвига в степени $m$:
+%% \begin{equation}
+%%   \label{eq:6}
+%%   Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
+%% \end{equation}
+%% Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
+%% конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
+%% $H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
+%% $L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
+%% $P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
+%% можно записать в виде
+%% \begin{equation}
+%%   \label{eq:7}
+%%   \begin{split}
+%%       Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
+%%       L_0)\}\\
+%%       =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
+%%   \end{split}
+%% \end{equation}
+%% Или, если ввести $q=\exp 2\pi i \tau$
+%% \begin{equation}
+%%   \label{eq:2}
+%%   Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
+%% \end{equation}
+%% Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
+%% 
+%% Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
+%% эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
+%% 
+Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
+модулярной инвариантности статсуммы.
+
+При помощи конформных преобразований можно перейти к таким координатам, в которых соотношения
+эквивалентности для тора (граничные условия) записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
+$\mathbb{C}$.
+%% 
+%% Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
+%% конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
+%% $SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
+%% \begin{equation}
+%%   \label{eq:99} A=
+%%   \begin{pmatrix} a & b\\ c & d
+%%   \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+%% \end{equation}
+%% и матрицы $A$ и $-A$ действуют одинаково на $\tau$
+%% \begin{equation}
+%%   \label{eq:100} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+%% \end{equation}
+%% $\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
+%% модулярной группой.
+%% 
+Конформная теория поля задаётся примарными полями $\Phi_a$ с конформными размерностями $\Delta_a$.
+
+Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
+произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
+представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсумма на торе
+(\ref{eq:2}) может быть записана в виде
+\begin{equation}
+  \label{eq:9}
+    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
+\end{equation}
+где $\chi_j$ --- нормализованный характер представления $\mathcal{H}_j$,
+\begin{equation}
+  \label{eq:5} \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i
+\tau}
+\end{equation}
+
+Характеры переходят друг в друга при модулярных преобразованиях:
+\begin{equation}
+  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
+\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
+\end{equation}
+где $S$ и $T$ --- постоянные матрицы.
+
+Для WZW-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$. Тогда
+\begin{equation}
+  \label{eq:6} \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi}
+L_{\hat \lambda}\otimes L_{\hat \xi}
+\end{equation}
+
+Коэффициенты ветвления для вложения аффинной подалгебры Ли в аффинную алгебру можно использовать для
+построения модулярно-инвариантной статсуммы в соответствующей WZW-модели. Когда рассматривается
+теория на торе,  набор физически допустимых полей ограничен требованиями модулярной инвариантности.
+
+Простейший модулярный инвариант можно записать следующим образом:
+\begin{equation}
+  \label{eq:34}
+   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
+\end{equation}
+Здесь суммирование ведется по всем конформным семействам (то есть по всем представлениям алгебры
+$\mathfrak{a}$).
+
+Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует
+алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно. (Я сейчас поясню, что это
+значит).
+
+Представления алгебры можно рассматривать как сумму представлений подалгебры.
+
+Если мы рассмотрим редукцию характеров аффинной алгебры
+\begin{equation}
+  \label{eq:8}
+   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
+\end{equation}
+и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится. То есть из
+диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый не диагональный инвариант для
+подалгебры $\mathfrak{a}$. Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
+ней конформная инвариантность.
+
+Пусть $J^{a_j}_{-n_j}$ и $\tilde{J}^{a'_j}_{-n_j}$ --- понижающие операторы алгебр  $\mathfrak{g}$ и
+$\mathfrak{a}\subset\mathfrak{g}$.  $\pi_{\mathfrak{a}}$ --- проекционный оператор
+$\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$. В теории, связанной с  $\mathfrak{g}$
+с вакуумом $\left|\lambda\right>$ будут следующие состояния:
+\begin{equation}
+  \label{eq:109}
+  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+\end{equation}
+Вакуум $\mathfrak{g}$-инвариантен, то есть $J_0^a\left|0\right>=0$. При проекции на подалгебру
+$\mathfrak{a}$ состояния примут вид
+\begin{equation}
+  \label{eq:110}
+  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
+\end{equation}
+Из $\mathfrak{g}$-ивариантности вакуума следует его $\mathfrak{a}$-инвариантность, но для тензора
+энергии-импульса в общем случае это не так. Поэтому тензор энергии-импульса большей теории должен
+состоять только из генераторов $\tilde{J}$. Тогда $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow
+c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению
+\begin{equation}
+  \label{eq:111}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
+\end{equation}
+Здесь $x_e$ --- индекс вложения, а  $g$, $a$ --- дуальные числа Кокстера, которые характеризуют алгебры.
+
+Можно показать, что только для представлений уровня 1 это равенство удовлетворяется. То есть класс
+конформных вложений не слишком широк и существует полная их классификация. Кроме того, для
+конформных вложений существуют специальные методы разложения представлений.
+
+Модулярная инвариантность статсуммы для полей, принадлежащих представлениям алгебры  $\mathfrak{g}$,
+сохраняется при проекции на подалгебру $\mathfrak{a}$. Если все представления $\mathfrak{g}$ в теории
+удовлетворяют описанным требованиям, то при проекции мы получаем конформную теорию поля.
+
+Существует теорема о том, что для конформного вложения  $\mathfrak{a}\subset\mathfrak{g}$ только
+конечное число коэффициентов ветвления отлично от нуля. Поэтому после того, как мы разложили все
+представления $\mathfrak{g}$ мы подставляем результаты в выражение для статсуммы и получаем
+модулярно-инвариантную статсумму для вложенной теории. Такая статсумма уже не будет иметь
+диагональный вид:
+\begin{equation}
+  \label{eq:36}
+   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
+\end{equation}
+Наша работа посвящена разработке общего метода редукции представлений аффинных алгебр Ли, поэтому
+случай конформных вложений --- лишь один из примеров применения нашего метода. Однако в этом случае
+физический смысл наиболее очевиден.
+
+\subsection{Центральное расширение алгебры Витта}
+\label{sec:witt-algebra-central-extension}
+
+Напомним несколько определений (см \cite{fuks1986cohomology},\cite{fuks1984}, \cite{feigin1988}).
+\begin{definition}
+Будем рассматривать алгебру Ли $\gf$ над полем $k=\mathbb{C},\mathbb{R}$.
+Векторное пространство $A$ над полем $k$ называется {\it модулем над $\gf$} или {\it $\gf$-модулем}, если задано билинейное отображение $\mu:\gf\times A\to A$, такое что $\mu([X,Y],a)=\mu(X,\mu(Y,a))-\mu(Y,\mu(X,a))$ для $X,Y\in \gf, a\in A$.
+Далее мы будем опускать символ $\mu$ и писать $X a= \mu(X,a)$.
+\end{definition}
+\begin{definition}
+  {\it $n$-мерная коцепь с коэффициентами в $A$} -- это кососимметричный $n$-линейный функционал на $\gf$ со значениями в $A$. Пространство $n$-коцепей $C^{n}(\gf;A)=\mathrm{Hom}(\wedge^{n}\gf;A)$.
+\end{definition}
+Заметим, что элементы $\gf$ действуют на $C^{n}(\gf;A)$.
+\begin{definition}
+  Внешний дифференциал $d=d_{n}:C^{n}(\gf;A)\to C^{n+1}(\gf;A)$ определяется формулой
+  \begin{multline}
+    \label{eq:1}
+    (dc) (X_{1},\dots, X_{n+1})=\sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} c([X_{s},X_{t}],X_{1},\dots,\hat X_{s},\dots,\hat X_{t},\dots X_{n+1})\\
+    +\sum_{1\leq s\leq n+1} (-1)^{s}X_{s} c(X_{1},\dots \hat X_{s},\dots X_{n+1})
+  \end{multline}
+\end{definition}
+Оставляем в качестве упражнения проверку того факта, что последовательность
+\begin{equation}
+  \label{eq:2}
+  \dots\stackrel{d_{n}}{\longleftarrow} C^{n}(g;A)\stackrel{d_{n-1}}{\longleftarrow} C^{n-1}(\gf;A)\leftarrow \dots \leftarrow C^{1}(\gf;A) \stackrel{d_{0}}{\longleftarrow} C^{0}(\gf;A)\leftarrow 0
+\end{equation}
+точна.Тогда $\{C^{n}(\gf;A),d_{n}\}=C^{*}(\gf;A)$ есть комплекс.
+\begin{definition}
+Соответствующие когомологии называются {\it когомологиями алгебры $\gf$ с коэффициентами в $A$} и обозначаются через $H^{n}(\gf;A)=\mathrm{Ker}\; d_{n}/\mathrm{Im}\; d_{n-1}$.
+
+\end{definition}
+Заметим, что поле $k$ может рассматриваться как тривиальный $\gf$-модуль. В этом случае второй член в формуле \eqref{eq:1} исчезает и используют сокращенные обозначения $C^{n}(\gf), H^{n}(\gf)$.
+\begin{definition}
+  Определим, заодно, и гомологии. Пространство $n$-мерных цепей $C_{n}(\gf;A)=A\otimes \wedge^{n}\gf$, дифференциал $\partial=\partial_{n}:C_{n}(\gf;A)\to C_{n-1}(\gf;A)$ определяется формулой
+  \begin{multline}
+    \label{eq:3}
+    \partial(a\otimes (X_{1}\wedge \dots \wedge X_{n})) =\\ \sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} a\otimes ([X_{s},X_{t}]\wedge X_{1} \wedge\dots\wedge\hat X_{s}\wedge \dots\wedge \hat X_{t}\wedge \dots\wedge X_{n+1})\\
+    +\sum_{1\leq s\leq n+1} (-1)^{s}(X_{s} a)\otimes (X_{1}\wedge\dots\wedge \hat X_{s}\wedge\dots\wedge X_{n+1})
+  \end{multline}
+  Аналогично определяется точная последовательность, комплекс и группа гомологий $H_{n}(\gf;A)$.
+\end{definition}
+\begin{definition}
+  {\it Одномерным центральным расширением алгебры $\gf$ } называется точная последовательность
+  \begin{equation}
+    \label{eq:4}
+    0\to k \to \tilde \gf\to \gf\to 0,
+  \end{equation}
+  такая что образ $k\to \tilde\gf$ содержится в центре $\tilde\gf$.
+\end{definition}
+Заметим, что всякий 2-коцикл $c\in C^{2}(\gf;A)$ определяет центральное расширение $\gf$:
+\begin{equation}
+  \label{eq:5}
+  0\to k\stackrel{\lambda\to (0,\lambda)}{\longrightarrow}\tilde\gf=\gf\oplus k \stackrel{(X,\lambda)\to X}{\longrightarrow} \gf\to 0
+\end{equation}
+Скобка Ли в алгебре $\tilde\gf$, которая равна $\gf\oplus k$ как векторное пространство, определяется равенством
+\begin{equation}
+  \label{eq:6}
+  [(X,\lambda),(Y,\mu)]=([X,Y],c(X,Y))
+\end{equation}
+Тождество Якоби для такой скобки равносильно тому, что $c$-- 2-коцикл. Когомологичным коциклам отвечают эквивалентные расширения.
+
+Два расширения $\tilde \gf$ и $\tilde{\tilde\gf}$ называются эквивалентными, если существует изоморфизм $I:\tilde\gf\to \tilde{\tilde \gf}$ такой, что диаграмма коммутирует:
+\begin{equation}
+  \label{eq:7}
+  \begin{diagram}
+    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \arrow{s,l}{id} \node{\tilde\gf}\arrow{s,l}{I} \arrow{e,t}{} \node{k}\arrow{s,r}{id} \arrow{e,t}{} \node{0}\\
+    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \node{\tilde{\tilde\gf}} \arrow{e,t}{} \node{k} \arrow{e,t}{} \node{0}
+  \end{diagram}
+\end{equation}
+\begin{exercise}
+ Построить изоморфизм $I$.   
+\end{exercise}
+
+Таким образом пространство $H^{2}(\gf)$ -- это множество классов 1-мерных центральных расширений $\gf$. Нуль в $H^{2}(\gf)$  соответствует тривиальному расширению.
+
+Вернемся к алгебре Витта \eqref{eq:230}. Существует коцикл
+\begin{equation}
+  \label{eq:8}
+  c(l_{n},l_{m})=\frac{1}{12}(m^{3}-m)\delta_{-n,m}
+\end{equation}
+\begin{exercise}
+  Проверить, что $c$ -- коцикл алгебры Витта. 
+\end{exercise}
+Соответствующее центральное расширение алгебры Витта называется алгеброй Вирасоро. Коммутационные соотношения этой алгебры имеют вид
+\begin{eqnarray}
+  \label{eq:9}
+  [L_{n},c]=0\\
+  \left[L_{n},L_{m}\right]=(n-m)L_{n+m} +\frac{c}{12} (m^{3}-m) \delta_{-n,m}
+\end{eqnarray}
+Можно показать, что $H^{2}(Witt)\cong \mathbb{C}$ и все нетривиальные коциклы пропорциональны $c$. 
+(Доказательство есть в \cite{fuks1986cohomology}, \cite{schottenloher2008mathematical}).
 

### 2011-11-16 AffineLieAlgebras/Thesis/1.tex
More work on thesis (mostly introduction, axiomatic CFT and WZW)

--- 2011-10-20 AffineLieAlgebras/Thesis/1.tex
@@
 \label{cha:affine-lie-algebras}
+Аффинные алгебры Ли - это естественное обобщение простых конечномерных алгебр Ли.
+Они возникают при изучении различных физических моделей, например, моделей Весса-Зумино-Новикова-Виттена в конформной теории поля и интегрируемых спиновых цепочек.
+\section{Введение. Простые алгебры Ли.}
+
+\label{sec:intro-simple-lie-algebras}
+
+\subsection{Lie algebras of finite and affine types}
+\label{sec:lie-algebras-finite}
+
+{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it Lie bracket}.
+If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
+\begin{equation}
+  \label{eq:1}
+  [X^{i},X^{j}]=\sum_{k} C^{ij}_{k} X^{k}
+\end{equation}
+Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to commutator.
+{\it Semisimple} Lie algebra is a direct sum of simple Lie algebras.
+In the present paper we treat simple and semisimple Lie algebras.
+
+{\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
+We denote the elements of basis of $\hfg$ by $H^{i}$.
+
+Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
+{\it Weights} are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
+
+Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
+This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).
+
+{\it Loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
+\begin{equation}
+  \label{eq:6}
+  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
+\end{equation}
+Central extension leads to the appearance of an additional term
+\begin{equation}
+  \label{eq:7}
+   [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
+\end{equation}
+This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
+
+We do not treat twisted affine Lie algebras in the present paper.
+
+\subsection{Modules, weights and roots}
+\label{sec:weights-roots}
+
+Let $\gf$ be a inite-dimensional or an affine Lie algebra.
+
+Then $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
+\begin{equation}
+  \label{eq:2}
+  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
+\end{equation}
+Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms of the  vector space $V$ with the commutator as a bracket.
+
+For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by a special choice of basis $\{v_{j}\}$ in $V$:
+\begin{equation}
+  \label{eq:3}
+  H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
+\end{equation}
+Eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
+Vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
+The  weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
+The weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of the weight subspace.
+
+The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
+\begin{equation}
+  \label{eq:5}
+  E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
+\end{equation}
+Module structure can be encoded by the formal character of a module
+\begin{equation}
+  \label{eq:10}
+  \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
+\end{equation}
+Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
+A character can be specialized by taking its value on some element $\xi$ of $\hf$.
+
+Lie algebra is its own module with respect to a special kind of representation. The action that
+defines this representation is called adjoint and is given by the bracket $ad_{X} Y=[X,Y]$. 
+{\it Roots} are weights of the adjoint representation of $\gf$.
+They encode the commutation relations of algebra in the following way.
+Denote by $\Delta$ the set of roots.
+For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and the generators $E^{\alpha}, E^{-\alpha}$ such that
+\begin{align}
+  \label{eq:4}
+  &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
+  &\left[E^{\alpha},E^{\beta}\right]=
+  \begin{cases}
+    N_{\alpha,\beta} E^{\alpha+\beta}, & \mbox{if}\; \alpha+\beta\in \Delta\\
+    \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
+    0,&\mbox{otherwise}
+  \end{cases}
+\end{align}
+
+Given the root system $\Delta$ we can choose the set of positive roots.
+This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
+Elements of $-\Delta^{+}$ are called negative roots.
+
+A positive root is {\it simple} if it cannot be written as a sum of positive roots.
+The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis in $\hfg^{*}$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive simultaneously.
+In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
+By numbering simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
+Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
+$\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}).
+{\it Comarcs} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
+
+Although for affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
+The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.
+The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- the highest root of the algebra $\go$.
+Note that root multiplicity $\mathrm{mult}(\alpha)$ for an affine Lie algebra root can be greater than one.
+
+Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called the Borel subalgebra.
+
+{\it Parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
+It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
+{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .
+
+The {\it Weyl group} $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
+\begin{equation}
+  \label{eq:8}
+  s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
+\end{equation}
+Root system and characters of representation are invariant with respect to the Weyl group  action. Root system can be reconstructed from the set of simple roots by the Weyl group transformations.
+
+Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
+
+Consider an action of the element $s_{\alpha}s_{\alpha+\delta}$ of the Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ being a simple root of the underlying finite-dimensional Lie algebra $\gf$.
+Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
+So the Weyl group can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to roots of $\gf$.
+
+A Weyl group element can be presented as a product of elementary reflections in multiple ways.
+Number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$.
+We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for the parity of the number of Weyl reflections generating $w$.
+
+Fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
+It is called a {\it main Weyl chamber}.
+
+The {\it Cartan matrix} $A$ is defined by products of simple roots
+\begin{equation}
+  \label{eq:9}
+  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}
+\end{equation}
+and can be used for a compact description of Lie algebra commutation relations in the Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
+
+Form \eqref{eq:9} induces a basis dual  to the simple
+roots basis. It is called the {\it fundamental weights basis}. We denote
+its elements by $\omega_i$:
+\begin{equation}
+  \label{eq:20}
+  \langle\omega_i,\alpha_j\rangle=\frac{2(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
+\end{equation}
+For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
+For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
+Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
+
+ The sum of fundamental weights $\rho=\sum_{i} \omega_{i}$ is called a {\it Weyl vector}. It is an important tool in representation theory.
+
+\subsection{Highest weight modules}
+\label{sec:high-weight-modul}
+
+We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e.
+if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
+
+Highest weight module $V^{\mu}$ contains a single highest weight $\mu$, all the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
+
+The most simple type of highest weight modules is the Verma module
+$M^{\mu}$. Its space can be defined as a module
+\begin{equation}
+  \label{eq:17}
+  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}),
+\end{equation}
+with respect to a multiplication in $U(\gf)$ and
+$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
+Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
+Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D^{\lambda}(\bff_{+})$.
+
+Weight multiplicities in Verma modules can be found by applying the Weyl
+character formula
+\begin{equation}
+  \label{eq:11}
+  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
+\end{equation}
+Here we have used the Weyl denominator identity
+\begin{equation}
+  \label{eq:12}
+  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
+\end{equation}
+and $\epsilon \left( w\right) :=\det \left( w\right)$ is equal to 
+the parity of the sequence of Weyl reflections generating $w$.
+
+Verma module $M^{\mu}$ has the unique maximal submodule and the
+unique nontrivial simple quotient $L^{\mu}$ which is an
+{\it irreducible highest weight module}.
+
+Irreducible highest weight modules have no non-trivial submodules. 
+The Weyl character formula for
+irreducible highest weight modules is
+\begin{equation}
+  \label{eq:13}
+  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
+\end{equation}
+Thus the character of an irreducible highest weight module can be
+seen as a combination of characters of Verma modules. ( This
+fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
+(\cite{bernstein1976category,bernstein1971structure}, see also
+\cite{humphreys2008representations}).)
+
+Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
+%% !!! \Delta_{p}?!
+\begin{equation*}
+M_{I}^{\mu}=U\left( \gf\right)\otimes _{U\left( \pf_{I}\right) }L_{\pf_{I}}^{\mu}.
+\end{equation*}
+Introduce a formal element $R_{I}:=\prod_{\alpha \in \Delta
+^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
+^{\mathrm{mult}(\alpha )}$. Then the character of a generalized
+Verma module can be written as
+\begin{equation}
+  \label{eq:18}
+  \mathrm{ch}M_{I}^{\mu}=\frac{1}{R_{I}}\mathrm{ch}L_{\pf_{I}}^{\mu }.
+\end{equation}
+
+%% Define external border of irreducible representation here
+
+We can use the Weyl character formula to obtain recurrent relations for weight multiplicities -- important tools for calculations \cite{il2010folded,kulish4sfa}.
+
+For irreducible highest-weight modules recurrent relations have the following form
+\begin{equation}
+\label{eq:14}
+m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
+-\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
+(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
+\end{equation}
+Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side.
+In case of Verma module it is just $\delta_{\xi,\mu}$.
+For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
+
+Other recurrent formula can be obtained from a study of Casimir
+elements action on irreducible highest weight modules
+\cite{humphreys1997introduction}:
+\begin{equation}
+  \label{eq:15}
+  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
+\end{equation}
+It is called the Freudenthal multiplicity formula.
+Note that it is applicable only to irreducible modules.
+
+We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.
+
+Now consider an algebra $\gf$ and a reductive subalgebra
+$\af\subset \gf$. Simple roots $\beta_{i}$ of the subalgebra $\af$
+can be presented as linear combinations of $\gf$-algebra roots
+$\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j}
+\alpha_{j},\ j=1,\dots,r_{\af}$.
+
+Each irreducible $\gf$-module is also an $\af$-module, although
+$L^{\mu}_{\gf}$ is in general not irreducible as $\af$-module. 
+It can be
+decomposed into a direct sum of irreducible $\af$-modules:
+\begin{equation}
+  \label{eq:16}
+  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
+\end{equation}
+Coefficients in such a decomposition are called branching
+coefficients.
+
+It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. 
+This traditional approach has serious limitations especially in case of affine Lie algebras. We discuss them in the end of section \ref{sec:comp-algor}.
+
+Now we describe an alternative approach which is based on recurrent properties of branching coefficients. 
+But before we proceed to these recurrent relations we need several additional definitions.
+
+For a subalgebra $\af\subset \gf$ we introduce the subalgebra
+$\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
+orthogonal to $\hf_{\af}$,
+\begin{equation*}
+\hf_{\perp \af}^{\ast }:=\left\{ \eta \in \hf^{\ast }|\forall
+h\in \hf_{\af};\eta \left( h\right) =0\right\} ,
+\end{equation*}
+and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
+to roots of $\af$,
+\begin{eqnarray}
+\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
+h\in \hf_{\af};\beta \left( h\right) =0\right\} ,
+\label{delta a ort} \\
+\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
+}^{+}|\forall h\in \hf_{\af};\beta ^{+}\left( h\right) =0\right\} .
+\notag
+\end{eqnarray}
+Let $W_{\afb}$ be a subgroup of $W$ generated by
+reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
+}}^{+}$. The subsystem $\Delta _{\afb}$ determines a 
+subalgebra $\afb$ with the Cartan subalgebra $\hf_{\af%
+_{\perp }}$.
+
+The Cartan subalgebra $\frak{h}$ can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
+\frak{h}_{\afb}\oplus \frak{h}_{\perp }$
+
+We also introduce the notations
+\begin{eqnarray}
+\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\qquad
+\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
+\end{eqnarray}
+
+For $\af$ and $\afb$ we consider the
+corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\af_{\perp
+}} $ and compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
+D}_{\afb}$ of the injection:
+\begin{equation}
+\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho , \qquad
+\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
+_{\perp }}\rho .  \label{defect-ort}
+\end{equation}
+
+%%!!! Define P^+
+For $\mu \in P^{+}$ consider the linked weights $\left\{ \left(
+w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections
+to
+$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
+\mathcal{D}_{\afb}$:
+\begin{equation*}
+\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
+w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
+\end{equation*}
+Among the weights $\left\{ \mu _{\af_{\perp
+}}\left( w\right) |w\in W\right\} $ one can always choose those located in
+the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
+set of representatives $u$ for the classes $W/W_{\afb}$ such
+that
+
+\begin{equation}
+U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
+\overline{C_{\afb}}\right\} \quad .  \label{U-def}
+\end{equation}
+Thus we can form the subsets:
+\begin{equation}
+\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
+\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
+_{\perp }},\quad u\in U,  \label{mu-a}
+\end{equation}
+and
+\begin{equation}
+\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
+\label{mu-a-tilda}
+\end{equation}
+
+Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
+since it is built on a subset of roots of the algebra $\mathfrak{g}$.
+
+Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients.
+If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.
+
+Now we can use the Weyl character formula to write a
+recurrent relation \cite{2010arXiv1007.0318L} for signed branching
+coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
+injection $\af\hookrightarrow \gf$:
+\begin{equation}
+\begin{array}{c}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
+_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
+\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right.  \\
+\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
+}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
+}\right) .
+\end{array}
+\label{recurrent-rel}
+\end{equation}
+The recursion is governed by the set $\Gamma _{\af\rightarrow \gf}$ called the injection fan. The latter is defined by the
+carrier set $\left\{ \xi \right\} _{\af\rightarrow \gf}$ for the
+coefficient function $s(\xi )$
+\begin{equation*}
+\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}:=\left\{
+\xi \in P_{\widetilde{\af}}|s(\xi )\neq 0\right\}
+\end{equation*}
+appearing in the expansion
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
+_{\widetilde{\af}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
+_{\af}(\pi _{\widetilde{\af}}\alpha )}=-\sum_{\gamma \in P_{%
+\widetilde{\af}}}s(\gamma )e^{-\gamma };\quad
+\end{equation}
+The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
+\right\} $ -- and the zero element is to be eliminated:
+\begin{equation}
+\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma
+_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
+\end{equation}
+Formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
+
+If the root system of $\afb$ is generated by some subset of $\gf$
+simple roots $\alpha_{1},\dots,\alpha_{r}$ then the recurrent
+relation (\ref{recurrent-rel}) is connected with the generalized
+Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules
+\cite{2011arXiv1102.1702L}.
+
+Another particular case of this formula is connected with tensor
+product decompositions. Consider the tensor product of two
+irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$. It is also a
+$\gf$-module but not irreducible in general. So
+\begin{equation}
+  \label{eq:19}
+  L^{\mu}\otimes L^{\nu}=\bigoplus_{\gamma} f^{\mu\nu}_{\gamma}L^{\gamma}
+\end{equation}
+The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion
+coefficients. The problem of computation of fusion coefficients is
+equivalent to branching problem for the diagonal subalgebra
+$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
+
+In the case of affine Lie algebras $\gf, \af$  the multiplicities
+$m_{\nu}$ and the corresponding branching coefficients $b_{\nu}$
+can be regarded as the coefficients in power series decomposition
+of string and branching functions correspondingly:
+\begin{align}
+  \label{eq:21}
+  &\sigma_{\nu}(q)=\sum_{n=0}^{\infty} m_{\nu-n\delta} q^n, \quad \nu=\sum_j c_j \omega_j,\quad c_j\geq 0\\
+  & b_{\nu}(q)=\sum_{n=0}^{\infty} b_{\nu-n\delta} q^n,\quad  \nu=\sum_j c_j \omega_j, \quad c_j\geq 0
+\end{align}
+String and branching functions have  modular and analytic properties which are important for conformal field theory, especially in  coset models and the study of CFT on higher genus surfaces \cite{kac1988modular}, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}.
+
+{\bf Affine.m}  calculates weight multiplicities and branching coefficients for affine Lie algebras up to some finite grade.
+We present examples of computations in Sections \ref{sec:string-funct-affine}, \ref{sec:branch-funct-coset}.
+Now we proceed to the description of datastructures and algorithms implemented in {\bf Affine.m}.
 

### 2011-11-20 AffineLieAlgebras/Thesis/1.tex
Some translations in thesis

@@
 
-\subsection{Lie algebras of finite and affine types}
-\label{sec:lie-algebras-finite}
-
-{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it Lie bracket}.
-If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
+{\it Алгебра Ли} $\gf$ -- это векторное пространство с билинейной операцией $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, которая называется  {\it скобкой Ли или коммутатором}.
+Если выбрать некоторый  $X_{i}$ в $\gf$, то коммутационные соотношения можно задать при помощи  {\it структурных констант} $C_{ijk}$:
 \begin{equation}
@@
 \end{equation}
-Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to commutator.
-{\it Semisimple} Lie algebra is a direct sum of simple Lie algebras.
-In the present paper we treat simple and semisimple Lie algebras.
-
-{\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
-We denote the elements of basis of $\hfg$ by $H^{i}$.
-
-Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
-{\it Weights} are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
-
-Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
-This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).
-
-{\it Loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
+
+Алгебра Ли называется {\it простой} если она не содержит нетривиальных идеалов относительно коммутатора.
+{\it Полупростая} алгебра Ли -- это прямая сумма простых алгебр Ли.
+В этой работе мы рассматриваем, в основном, простые и полупростые алгебры Ли.
+
+{\it Подалгеброй Картана}  $\hfg$ называется нильпотентная подалгебра алгебры $\gf$, совпадающая со своим нормализатором. Мы обозначаем элементы базиса в $\hfg$ через $H^{i}$.
+
+Форма Киллинга на  $\gf$ порождает невырожденную билинейную форму $(\cdot,\cdot)$ на подалгебре Картана $\hfg$, позволяющую идентифицировать $\hfg$ с подпространством дуального пространства  $\hfg^{*}$ линейных функционалов на $\hfg$.
+{\it Веса}  -- это элементы  $\hfg^{*}$, мы обозначаем их греческими буквами $\mu,\nu, \omega, \lambda\dots$
+
+Коммутационные соотношения  (\ref{eq:1}) можно записать в компактной форме, если выбрать базис специальным образом.
+Такой базис описывается корневой системой, которая определяется в разделе \ref{sec:weights-roots} (Смотри также \cite{humphreys1997introduction,humphreys1992reflection}).
+
+{\it Алгебра петель} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, соответствующая полупростой алгебре Ли $\gf$, определяется коммутационными соотношениями
 \begin{equation}
@@
 \end{equation}
-Central extension leads to the appearance of an additional term
+Центральное расширение алгебры петель ведет к возникновению дополнительного члена
 \begin{equation}
@@
 \end{equation}
-This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
-
-We do not treat twisted affine Lie algebras in the present paper.
-
-\subsection{Modules, weights and roots}
+Эта алгебра $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ называется (не скрученной)  {\it аффинной алгеброй Ли} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
+
+\subsection{Модули, веса и корни}
 \label{sec:weights-roots}
 
-Let $\gf$ be a inite-dimensional or an affine Lie algebra.
-
-Then $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
+Пусть $\gf$ -- конечномерная или аффинная алгебра Ли.  $\gf$-модулем называется векторное пространство $V$ с билинейным отображением $\gf \times V\to V$, таким, что выполнено равенство
 \begin{equation}
@@
 \end{equation}
-Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms of the  vector space $V$ with the commutator as a bracket.
-
-For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by a special choice of basis $\{v_{j}\}$ in $V$:
+Представление алгебры  $\gf$ на векторном пространстве $V$ называется гомоморфизм $\gf\to gl(V)$ из $\gf$ в алгебру Ли эндоморфизмов векторного пространства $V$, где скобка задана коммутатором.
+
+В произвольном представлении операторы, соответствующие генераторам подалгебры Картана $H^{i}$ можно одновременно диагонализовать путем специального выбора базиса
+ $\{v_{j}\}$ в $V$:
 \begin{equation}
@@
 \end{equation}
-Eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
-Vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
-The  weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
-The weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of the weight subspace.
-
-The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
+Собственные значения $\nu^{i}_{j}$ генераторов Картана на элементе базиса $v_{j}$ определяют вес  $\nu_{j}\in \hfg^{*}$, такой, что $\nu_{j}(H^{i})=\nu_{j}^{i}$.
+Вектор $v\in V$ называется весовым вектором веса  $\lambda$, если $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
+Весовое подпространство состоит из всех весовых векторов $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
+Кратностью веса  $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ называется размерность весового подпространства.
+
+Структура модуля определяется набором весов, так как действие генераторов $E^{\alpha}$ на весовых векторах дается выражением
 \begin{equation}
@@
 \end{equation}
-Module structure can be encoded by the formal character of a module
+Структуру модуля можно записать в виде формального характера
 \begin{equation}
@@
 \end{equation}
-Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
-A character can be specialized by taking its value on some element $\xi$ of $\hf$.
-
-Lie algebra is its own module with respect to a special kind of representation. The action that
-defines this representation is called adjoint and is given by the bracket $ad_{X} Y=[X,Y]$. 
-{\it Roots} are weights of the adjoint representation of $\gf$.
-They encode the commutation relations of algebra in the following way.
-Denote by $\Delta$ the set of roots.
-For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and the generators $E^{\alpha}, E^{-\alpha}$ such that
+Характер  $\mathrm{ch}V\in \mathcal{E}$ -- это элемент алгебры  $\mathcal{E}$, порожденной формальными экспонентами весов.
+Характер можно специализировать --- взять его значение на некотором элементе $\xi\in\hf$.
+
+Алгебра Ли является собственным модулем по отношению к специальному представлению, называющемуся присоединенном. Действие генераторов в этом представлении дается скобкой $ad_{X} Y=[X,Y]$. 
+{\it Корни} -- это веса присоединенного представления алгебры $\gf$.
+Они определяют коммутационные соотношения в алгебре следующим образом.
+Обозначим через $\Delta$ множество корней.
+Для каждого $\alpha\in \Delta$ существует корень  $-\alpha\in \Delta$ и генераторы $E^{\alpha}, E^{-\alpha}$, такие, что
 \begin{align}
@@
     \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
-    0,&\mbox{otherwise}
+    0,&\mbox{в остальных случаях}
   \end{cases}

### 2011-11-22 AffineLieAlgebras/Thesis/1.tex
Translation of section on weights and roots

@@
 Такой базис описывается корневой системой, которая определяется в разделе \ref{sec:weights-roots} (Смотри также \cite{humphreys1997introduction,humphreys1992reflection}).
+
+Чтобы определить аффинные алгебры нам нужно обсудить процедуру центрального расширения алгебры Ли.
+Напомним несколько определений (см \cite{fuks1986cohomology},\cite{fuks1984}, \cite{feigin1988}).
+\begin{definition}
+Будем рассматривать алгебру Ли $\gf$ над полем $k=\mathbb{C},\mathbb{R}$.
+Векторное пространство $A$ над полем $k$ называется {\it модулем над $\gf$} или {\it $\gf$-модулем}, если задано билинейное отображение $\mu:\gf\times A\to A$, такое что $\mu([X,Y],a)=\mu(X,\mu(Y,a))-\mu(Y,\mu(X,a))$ для $X,Y\in \gf, a\in A$.
+Далее мы будем опускать символ $\mu$ и писать $X a= \mu(X,a)$.
+\end{definition}
+\begin{definition}
+  {\it $n$-мерная коцепь с коэффициентами в $A$} -- это кососимметричный $n$-линейный функционал на $\gf$ со значениями в $A$. Пространство $n$-коцепей $C^{n}(\gf;A)=\mathrm{Hom}(\wedge^{n}\gf;A)$.
+\end{definition}
+Заметим, что элементы $\gf$ действуют на $C^{n}(\gf;A)$.
+\begin{definition}
+  Внешний дифференциал $d=d_{n}:C^{n}(\gf;A)\to C^{n+1}(\gf;A)$ определяется формулой
+  \begin{multline}
+    \label{eq:1}
+    (dc) (X_{1},\dots, X_{n+1})=\sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} c([X_{s},X_{t}],X_{1},\dots,\hat X_{s},\dots,\hat X_{t},\dots X_{n+1})\\
+    +\sum_{1\leq s\leq n+1} (-1)^{s}X_{s} c(X_{1},\dots \hat X_{s},\dots X_{n+1})
+  \end{multline}
+\end{definition}
+Нетрудно проверить, что последовательность
+\begin{equation}
+  \label{eq:2}
+  \dots\stackrel{d_{n}}{\longleftarrow} C^{n}(g;A)\stackrel{d_{n-1}}{\longleftarrow} C^{n-1}(\gf;A)\leftarrow \dots \leftarrow C^{1}(\gf;A) \stackrel{d_{0}}{\longleftarrow} C^{0}(\gf;A)\leftarrow 0
+\end{equation}
+точна.Тогда $\{C^{n}(\gf;A),d_{n}\}=C^{*}(\gf;A)$ есть комплекс.
+\begin{definition}
+Соответствующие когомологии называются {\it когомологиями алгебры $\gf$ с коэффициентами в $A$} и обозначаются через $H^{n}(\gf;A)=\mathrm{Ker}\; d_{n}/\mathrm{Im}\; d_{n-1}$.
+
+\end{definition}
+Заметим, что поле $k$ может рассматриваться как тривиальный $\gf$-модуль. В этом случае второй член в формуле \eqref{eq:1} исчезает и используют сокращенные обозначения $C^{n}(\gf), H^{n}(\gf)$.
+\begin{definition}
+  Определим, заодно, и гомологии. Пространство $n$-мерных цепей $C_{n}(\gf;A)=A\otimes \wedge^{n}\gf$, дифференциал $\partial=\partial_{n}:C_{n}(\gf;A)\to C_{n-1}(\gf;A)$ определяется формулой
+  \begin{multline}
+    \label{eq:3}
+    \partial(a\otimes (X_{1}\wedge \dots \wedge X_{n})) =\\ \sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} a\otimes ([X_{s},X_{t}]\wedge X_{1} \wedge\dots\wedge\hat X_{s}\wedge \dots\wedge \hat X_{t}\wedge \dots\wedge X_{n+1})\\
+    +\sum_{1\leq s\leq n+1} (-1)^{s}(X_{s} a)\otimes (X_{1}\wedge\dots\wedge \hat X_{s}\wedge\dots\wedge X_{n+1})
+  \end{multline}
+  Аналогично определяется точная последовательность, комплекс и группа гомологий $H_{n}(\gf;A)$.
+\end{definition}
+\begin{definition}
+  {\it Одномерным центральным расширением алгебры $\gf$ } называется точная последовательность
+  \begin{equation}
+    \label{eq:4}
+    0\to k \to \tilde \gf\to \gf\to 0,
+  \end{equation}
+  такая что образ $k\to \tilde\gf$ содержится в центре $\tilde\gf$.
+\end{definition}
+Заметим, что всякий 2-коцикл $c\in C^{2}(\gf;A)$ определяет центральное расширение $\gf$:
+\begin{equation}
+  \label{eq:5}
+  0\to k\stackrel{\lambda\to (0,\lambda)}{\longrightarrow}\tilde\gf=\gf\oplus k \stackrel{(X,\lambda)\to X}{\longrightarrow} \gf\to 0
+\end{equation}
+Скобка Ли в алгебре $\tilde\gf$, которая равна $\gf\oplus k$ как векторное пространство, определяется равенством
+\begin{equation}
+  \label{eq:6}
+  [(X,\lambda),(Y,\mu)]=([X,Y],c(X,Y))
+\end{equation}
+Тождество Якоби для такой скобки равносильно тому, что $c$-- 2-коцикл. Когомологичным коциклам отвечают эквивалентные расширения.
+
+Два расширения $\tilde \gf$ и $\tilde{\tilde\gf}$ называются эквивалентными, если существует изоморфизм $I:\tilde\gf\to \tilde{\tilde \gf}$ такой, что диаграмма коммутирует:
+\begin{equation}
+  \label{eq:7}
+  \begin{diagram}
+    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \arrow{s,l}{id} \node{\tilde\gf}\arrow{s,l}{I} \arrow{e,t}{} \node{k}\arrow{s,r}{id} \arrow{e,t}{} \node{0}\\
+    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \node{\tilde{\tilde\gf}} \arrow{e,t}{} \node{k} \arrow{e,t}{} \node{0}
+  \end{diagram}
+\end{equation}
+%% \begin{exercise}
+%%  Построить изоморфизм $I$.   
+%% \end{exercise}
+
+Таким образом пространство $H^{2}(\gf)$ -- это множество классов 1-мерных центральных расширений $\gf$. Нуль в $H^{2}(\gf)$  соответствует тривиальному расширению.
+
+Вернемся к алгебре Витта \eqref{eq:230}. Существует коцикл
+\begin{equation}
+  \label{eq:8}
+  c(l_{n},l_{m})=\frac{1}{12}(m^{3}-m)\delta_{-n,m}
+\end{equation}
+%% \begin{exercise}
+%%   Проверить, что $c$ -- коцикл алгебры Витта. 
+%% \end{exercise}
+Соответствующее центральное расширение алгебры Витта называется алгеброй Вирасоро. Коммутационные соотношения этой алгебры имеют вид
+\begin{eqnarray}
+  \label{eq:9}
+  [L_{n},c]=0\\
+  \left[L_{n},L_{m}\right]=(n-m)L_{n+m} +\frac{c}{12} (m^{3}-m) \delta_{-n,m}
+\end{eqnarray}
+Можно показать, что $H^{2}(Witt)\cong \mathbb{C}$ и все нетривиальные коциклы пропорциональны $c$. 
+(Доказательство есть в \cite{fuks1986cohomology}, \cite{schottenloher2008mathematical}).
 
@@
 
-Given the root system $\Delta$ we can choose the set of positive roots.
-This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
-Elements of $-\Delta^{+}$ are called negative roots.
-
-A positive root is {\it simple} if it cannot be written as a sum of positive roots.
-The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis in $\hfg^{*}$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive simultaneously.
-In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
-By numbering simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
-Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
-$\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}).
-{\it Comarcs} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
-
-Although for affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
-The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.
-The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- the highest root of the algebra $\go$.
-Note that root multiplicity $\mathrm{mult}(\alpha)$ for an affine Lie algebra root can be greater than one.
-
-Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called the Borel subalgebra.
-
-{\it Parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
-It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
-{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .
-
-The {\it Weyl group} $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
+В корневой системе $\Delta$ можно выбрать множество положительных корней.
+Это подмножество  $\Delta^{+}\subset \Delta$, такое, что для любого корня $\alpha\in\Delta$ ровно один из корней $\alpha, -\alpha$ содержится $\Delta^{+}$ и для любых двух различных положительных корней $\alpha, \beta\in \Delta^{+}$, таких, что $\alpha+\beta\in \Delta$ их сумма тоже положительна $\alpha+\beta\in\Delta^{+}$.
+Элементы множества $-\Delta^{+}$ называются отрицательными корнями.
+
+Положительный корень называется {\it простым} если его нельзя представить в виде суммы положительных корней.
+Множество простых корней  $\Phi=\left\{\alpha_{i}\right\}$ является базисом в $\hfg^{*}$ и каждый корень может быть записан как сумма $\alpha=\sum_{i}n_{i}\alpha_{i}$, где все $n_{i}$ не отрицательны или не положительны одновременно.
+В случае конечномерной алгебры Ли  $\gf$ простые корни можно пронумеровать числами от  1 до ранга алгебры $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
+Такая нумерация порождает лексикографическое упорядочение корневой системы.
+Старший по отношению к этому упорядочению корень обозначается через $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, его координаты в базисе простых корней $a_i$ называются  {\it марками}.
+$\theta$ -- это старший вес присоединенного модуля (См.
+раздел \ref{sec:high-weight-modul}).
+{\it Ко-марками} называются числа, равные $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
+
+В аффинной алгебре Ли  $\hat\gf$ множество корней  $\Delta$ бесконечно, но набор простых корней  $\Phi$ конечен.
+Обозначим его элементы через $\alpha_{0},\dots \alpha_{r}$, где $r=\mathrm{rank}(\gf)$.
+Корни $\alpha_1,\dots, \alpha_r$ -- это корни соответствующей конечномерной алгебры Ли $\go$.
+Простой корень  $\alpha_0=\delta-\theta$ -- это разность  {\it мнимого корня} $\delta$ и $\theta$ -- старшего корня алгебры $\go$.
+Заметим, что кратность корня  $\mathrm{mult}(\alpha)$ в случае аффинной алгебры Ли может быть больше единицы.
+
+Подалгебра  $\bff_{+}\subset \gf$, порожденная генераторами $H^{i}, E^{\alpha}$, соответствующими положительным корням $\alpha\in \Delta^{+}$, называется подалгеброй Бореля.
+
+{\it Параболическая подалгебра}  $\pf_{I}\supset \bff_{+}$ содержит подалгебру Бореля и порождена некоторым подмножеством простых корней  $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
+Она образована подмножеством генераторов  $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
+{\it Регулярная подалгебра} $\af\subset\gf$ определяется корневой системой  $\Delta_{\af}$, множество простых корней которой  $\{\beta_{i}, i=1,\dots,r_{\af}\}$ является подмножеством множества $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ корней алгебры $\gf$.
+
+ {\it Группа Вейля} $W_{\gf}$ порождается отражениями $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$, соответствующим простым корням $\{\alpha_{i}\}$:
 \begin{equation}
@@
 \end{equation}
-Root system and characters of representation are invariant with respect to the Weyl group  action. Root system can be reconstructed from the set of simple roots by the Weyl group transformations.
-
-Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
-
-Consider an action of the element $s_{\alpha}s_{\alpha+\delta}$ of the Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ being a simple root of the underlying finite-dimensional Lie algebra $\gf$.
-Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
-So the Weyl group can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to roots of $\gf$.
-
-A Weyl group element can be presented as a product of elementary reflections in multiple ways.
-Number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$.
-We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for the parity of the number of Weyl reflections generating $w$.
-
-Fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
-It is called a {\it main Weyl chamber}.
-
-The {\it Cartan matrix} $A$ is defined by products of simple roots
+Корневая система и характеры представлений инвариантны относительно действия группы Вейля.
+Корневая система может быть восстановлена из множества простых корней в результате применения вейлевских отражений.
+
+Группа Вейля конечна для конечномерных алгебр Ли и конечно порождена для аффинных алгебр Ли.
+
+Рассмотрим действие элемента группы Вейля $s_{\alpha}s_{\alpha+\delta}$ аффинной алгебры Ли   $\hat\gf$, соответствующего простому корню  $\alpha$ конечномерной подалгебры Ли $\gf$.
+Из определения  \eqref{eq:8} легко видеть, что $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
+То есть группа Вейля для аффинной алгебры Ли может быть представлена как полупрямое произведение группы Вейля $W_{\gf}$ конечномерной подалгебры  $\gf$ и трансляций, соответствующих корням $\gf$.
+
+Элемент группы Вейля можно представить как произведение простых отражений различными способами.
+Число простых отражений в кратчайшей последовательности, представляющей элемент$w\in W_{\gf}$ называется {\it длиной}  $w$ и обозначается $l(w)$.
+Мы также используем обозначение $\epsilon(w)=(-1)^{l(w)}$ для четности числа отражений Вейля, порождающих $w$.
+
+Фундаментальная область $\bar{C}$ для действия группы Вейля $W_{\gf}$ на $\hfg^{*}$ описывается условием $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ для всех простых корней $\alpha_{i}$.
+Ее называют {\it главной камерой Вейля}.
+
+{\it Матрица Картана} $A$ строится из произведений простых корней
 \begin{equation}
   \label{eq:9}
-  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}
-\end{equation}
-and can be used for a compact description of Lie algebra commutation relations in the Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
-
-Form \eqref{eq:9} induces a basis dual  to the simple
-roots basis. It is called the {\it fundamental weights basis}. We denote
-its elements by $\omega_i$:
+  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}.
+\end{equation}
+Она может использоваться для компактного описания алгебры Ли и ее коммутационных соотношений в базисе Шевалле \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
+
+Форма, заданная матрицей Картана \eqref{eq:9} определяет базис, дуальный к базису простых корней.  Он называется  {\it базисом фундаментальных весов}. Мы обозначаем его элементы через $\omega_i$:
 \begin{equation}
@@
 \end{equation}
-For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
-For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
-Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
-
- The sum of fundamental weights $\rho=\sum_{i} \omega_{i}$ is called a {\it Weyl vector}. It is an important tool in representation theory.
-
-\subsection{Highest weight modules}
+Для конечномерной алгебры Ли существует $r$ фундаментальных весов $\omega_{i}$, $i=1,\dots, r$.
+Для аффинной алгебры Ли есть дополнительный фундаментальный вес $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
+Другие фундаментальные веса равны $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, где $\co{\omega_i}$ -- это фундаментальные веса конечномерной подалгебры Ли $\gf$.
+
+Сумма фундаментальных весов $\rho=\sum_{i} \omega_{i}$ называется {\it вектором Вейля} и играет большую роль в теории представлений.
+
+\subsection{Модули старшего веса}
 \label{sec:high-weight-modul}
 
-We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e.
-if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
-
-Highest weight module $V^{\mu}$ contains a single highest weight $\mu$, all the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
-
-The most simple type of highest weight modules is the Verma module
-$M^{\mu}$. Its space can be defined as a module
+Мы рассматриваем конечно-порожденные  $\gf$-модули $V$, такие, что $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, где каждое подпространство $V_{\xi}$ конечномерно и существует конечный набор весов $\lambda_{1},\dots \lambda_{s}$, порождающий весовую систему модуля $V$.
+То есть, если $\mathrm{dim}V_{\xi}\neq 0$, то $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$, где $n_{k}\in \mathbb{Z}_{+}$ (См.
+\cite{humphreys2008representations}, \cite{carter2005lie}).
+
+Модули старшего веса содержат единственный старший вес $\mu$ и все остальные веса в них могут быть получены вычитанием линейных комбинаций простых корней $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
+
+Самый простой тип модулей старшего веса -- это модули Верма $M^{\mu}$. Модуль Верма можно определить, как пространство
 \begin{equation}
@@
 \end{equation}
-with respect to a multiplication in $U(\gf)$ and
-$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
-Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
-Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D^{\lambda}(\bff_{+})$.
-
-Weight multiplicities in Verma modules can be found by applying the Weyl
-character formula
+где действие $\gf$ дается умножением в $U(\gf)$, а
+$\underset{U(\bff_{+})}{\otimes}$ значит, что действие элементов $U(\bff_{+})$ ``проносится'' через левую часть тензорного произведения направо.
+Здесь $\bff_{+}$ -- подалгебры Бореля, а $D^{\mu}(\bff_{+})$ -- представление $\bff_{+}$, такое, что $D(E^{\alpha})=0,\; D(H)=\mu(H)$ для любого положительного корня $\alpha$.
+Элементы  $\gf$ действуют слева и мы должны прокоммутировать все элементы $\bff_{+}$ направо, чтобы они могли подействовать на пространстве $D^{\lambda}(\bff_{+})$.
+
+Кратности весов в модуле Верма можно определить из формулы Вейля для характеров
 \begin{equation}
@@
 \end{equation}
-Here we have used the Weyl denominator identity
+Здесь мы воспользовались тождеством Вейля для знаменателей
 \begin{equation}
@@
 \end{equation}
-and $\epsilon \left( w\right) :=\det \left( w\right)$ is equal to 
-the parity of the sequence of Weyl reflections generating $w$.
-
-Verma module $M^{\mu}$ has the unique maximal submodule and the
-unique nontrivial simple quotient $L^{\mu}$ which is an
-{\it irreducible highest weight module}.
-
-Irreducible highest weight modules have no non-trivial submodules. 
-The Weyl character formula for
-irreducible highest weight modules is
+а $\epsilon \left( w\right) :=\det \left( w\right)$ равняется четности последовательности отражений Вейля, образующих $w$.
+
+У модуля Верма  $M^{\mu}$ есть единственный максимальный подмодуль и нетривиальный фактормодуль $L^{\mu}$ является 
+{\it неприводимым модулем старшего веса}.
+
+Неприводимые модули старшего веса не имеют нетривиальных подмодулей. 
+Формула Вейля для характеров неприводимых модулей старшего веса имеет вид
 \begin{equation}
@@
 \end{equation}
-Thus the character of an irreducible highest weight module can be
-seen as a combination of characters of Verma modules. ( This
-fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
-(\cite{bernstein1976category,bernstein1971structure}, see also
-\cite{humphreys2008representations}).)
-
-Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
+То есть характер неприводимого модуля старшего веса можно рассматривать как комбинацию характеров модулей Верма.
+Этот факт следует из существования резольвенты Бернштейна-Гельфанда-Гельфанда \cite{bernstein1976category,bernstein1971structure}, см.
+также
+\cite{humphreys2008representations}.
+
+Конструкция обобщенного (или параболического) модуля Верма аналогична формуле (\ref{eq:17}), но представление подалгебры Бореля заменяется на представление параболической подалгебры $\pf_{I}\supset \bff_{+}$, определяющейся некоторым подмножеством  $\{\alpha_{I}\}$ простых корней $I\subset \{1,\dots, r\}$:
 %% !!! \Delta_{p}?!
@@
 \end{equation*}
-Introduce a formal element $R_{I}:=\prod_{\alpha \in \Delta
+Введем формальный элемент $R_{I}:=\prod_{\alpha \in \Delta
 ^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
-^{\mathrm{mult}(\alpha )}$. Then the character of a generalized
-Verma module can be written as
+^{\mathrm{mult}(\alpha )}$. Тогда характер обобщенного модуля Верма можно записать в виде
 \begin{equation}

### 2011-11-22 AffineLieAlgebras/Thesis/1.tex
More translations

@@
 
-We can use the Weyl character formula to obtain recurrent relations for weight multiplicities -- important tools for calculations \cite{il2010folded,kulish4sfa}.
-
-For irreducible highest-weight modules recurrent relations have the following form
+Формула Вейля для характеров может быть использована для получения рекуррентных соотношений на кратности весов. Эти соотношения важны для вычислений \cite{il2010folded,kulish4sfa}.
+
+Для неприводимых модулей старшего веса рекуррентные соотношения имеют вид
 \begin{equation}
@@
 \end{equation}
-Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side.
-In case of Verma module it is just $\delta_{\xi,\mu}$.
-For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
-
-Other recurrent formula can be obtained from a study of Casimir
-elements action on irreducible highest weight modules
-\cite{humphreys1997introduction}:
+Формулы для модулей Верма и обобщенных модулей Верма отличаются только во вторым членом в правой части.
+В случае модулей Верма он равен $\delta_{\xi,\mu}$.
+Для обобщенного модуля Верма суммирование во втором члене в правой части равенства \eqref{eq:14} производится по элементам подгруппы Вейля порожденной отражениями, соответствующими корням $\{\alpha_{I}\}$.
+
+В разделе \ref{subsec:Construct-recurrent-rel} мы покажем, что для модулей старшего веса эти соотношения могут быть получены как частный случай рекуррентных соотношений на коэффициенты ветвления.
+
+Другая рекуррентная формула для кратностей может быть получена из рассмотрения действия элементов Казимира на неприводимых модулях старшего веса \cite{humphreys1997introduction}:
 \begin{equation}
@@
 \end{equation}
-It is called the Freudenthal multiplicity formula.
-Note that it is applicable only to irreducible modules.
-
-We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.
+Эта формула называется формулой Фрейденталя. Заметим, что она применима только для неприводимых модулей
+
+Применение рекуррентных соотношений \eqref{eq:14} и \eqref{eq:15} для вычисления кратностей весов обсуждается в разделе \ref{sec:comp-algor}.
 

### 2011-11-22 AffineLieAlgebras/Thesis/review.tex
More translation work

@@
 \label{cha:CFT}
+
+Конформная теория поля возникла как инструмент для описания критического поведения в двумерных системах \cite{Polyakov:1970xd}.
+В двух измерениях такая теория обладает богатой симметрией, так что ее даже иногда называют точно решаемой \cite{belavin1984ics}.
+На самом деле существуют разнообразные классы моделей двумерной конформной теории поля и даже задача классификации всех таких моделей до конца не решена, несмотря на первоначальный оптимизм \cite{}.
+
+\section{Общие свойства моделей конформной теории поля}
+\label{sec:conformal-field-theory-general}
 
@@
 \end{equation}
-При квантовании возникает конформная аномалия, что соответствует центральному расширению алгебры (то
+При квантовании возникает конформная аномалия, что соответствует центральному расширению \eqref{eq:9} алгебры  (то
 есть появлению центрального заряда $c$). В коммутационные соотношения надо добавить член
@@
 
-\subsection{Центральное расширение алгебры Витта}
-\label{sec:witt-algebra-central-extension}
-
-Напомним несколько определений (см \cite{fuks1986cohomology},\cite{fuks1984}, \cite{feigin1988}).
-\begin{definition}
-Будем рассматривать алгебру Ли $\gf$ над полем $k=\mathbb{C},\mathbb{R}$.
-Векторное пространство $A$ над полем $k$ называется {\it модулем над $\gf$} или {\it $\gf$-модулем}, если задано билинейное отображение $\mu:\gf\times A\to A$, такое что $\mu([X,Y],a)=\mu(X,\mu(Y,a))-\mu(Y,\mu(X,a))$ для $X,Y\in \gf, a\in A$.
-Далее мы будем опускать символ $\mu$ и писать $X a= \mu(X,a)$.
-\end{definition}
-\begin{definition}
-  {\it $n$-мерная коцепь с коэффициентами в $A$} -- это кососимметричный $n$-линейный функционал на $\gf$ со значениями в $A$. Пространство $n$-коцепей $C^{n}(\gf;A)=\mathrm{Hom}(\wedge^{n}\gf;A)$.
-\end{definition}
-Заметим, что элементы $\gf$ действуют на $C^{n}(\gf;A)$.
-\begin{definition}
-  Внешний дифференциал $d=d_{n}:C^{n}(\gf;A)\to C^{n+1}(\gf;A)$ определяется формулой
-  \begin{multline}
-    \label{eq:1}
-    (dc) (X_{1},\dots, X_{n+1})=\sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} c([X_{s},X_{t}],X_{1},\dots,\hat X_{s},\dots,\hat X_{t},\dots X_{n+1})\\
-    +\sum_{1\leq s\leq n+1} (-1)^{s}X_{s} c(X_{1},\dots \hat X_{s},\dots X_{n+1})
-  \end{multline}
-\end{definition}
-Оставляем в качестве упражнения проверку того факта, что последовательность
-\begin{equation}
-  \label{eq:2}
-  \dots\stackrel{d_{n}}{\longleftarrow} C^{n}(g;A)\stackrel{d_{n-1}}{\longleftarrow} C^{n-1}(\gf;A)\leftarrow \dots \leftarrow C^{1}(\gf;A) \stackrel{d_{0}}{\longleftarrow} C^{0}(\gf;A)\leftarrow 0
-\end{equation}
-точна.Тогда $\{C^{n}(\gf;A),d_{n}\}=C^{*}(\gf;A)$ есть комплекс.
-\begin{definition}
-Соответствующие когомологии называются {\it когомологиями алгебры $\gf$ с коэффициентами в $A$} и обозначаются через $H^{n}(\gf;A)=\mathrm{Ker}\; d_{n}/\mathrm{Im}\; d_{n-1}$.
-
-\end{definition}
-Заметим, что поле $k$ может рассматриваться как тривиальный $\gf$-модуль. В этом случае второй член в формуле \eqref{eq:1} исчезает и используют сокращенные обозначения $C^{n}(\gf), H^{n}(\gf)$.
-\begin{definition}
-  Определим, заодно, и гомологии. Пространство $n$-мерных цепей $C_{n}(\gf;A)=A\otimes \wedge^{n}\gf$, дифференциал $\partial=\partial_{n}:C_{n}(\gf;A)\to C_{n-1}(\gf;A)$ определяется формулой
-  \begin{multline}
-    \label{eq:3}
-    \partial(a\otimes (X_{1}\wedge \dots \wedge X_{n})) =\\ \sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} a\otimes ([X_{s},X_{t}]\wedge X_{1} \wedge\dots\wedge\hat X_{s}\wedge \dots\wedge \hat X_{t}\wedge \dots\wedge X_{n+1})\\
-    +\sum_{1\leq s\leq n+1} (-1)^{s}(X_{s} a)\otimes (X_{1}\wedge\dots\wedge \hat X_{s}\wedge\dots\wedge X_{n+1})
-  \end{multline}
-  Аналогично определяется точная последовательность, комплекс и группа гомологий $H_{n}(\gf;A)$.
-\end{definition}
-\begin{definition}
-  {\it Одномерным центральным расширением алгебры $\gf$ } называется точная последовательность
-  \begin{equation}
-    \label{eq:4}
-    0\to k \to \tilde \gf\to \gf\to 0,
-  \end{equation}
-  такая что образ $k\to \tilde\gf$ содержится в центре $\tilde\gf$.
-\end{definition}
-Заметим, что всякий 2-коцикл $c\in C^{2}(\gf;A)$ определяет центральное расширение $\gf$:
-\begin{equation}
-  \label{eq:5}
-  0\to k\stackrel{\lambda\to (0,\lambda)}{\longrightarrow}\tilde\gf=\gf\oplus k \stackrel{(X,\lambda)\to X}{\longrightarrow} \gf\to 0
-\end{equation}
-Скобка Ли в алгебре $\tilde\gf$, которая равна $\gf\oplus k$ как векторное пространство, определяется равенством
-\begin{equation}
-  \label{eq:6}
-  [(X,\lambda),(Y,\mu)]=([X,Y],c(X,Y))
-\end{equation}
-Тождество Якоби для такой скобки равносильно тому, что $c$-- 2-коцикл. Когомологичным коциклам отвечают эквивалентные расширения.
-
-Два расширения $\tilde \gf$ и $\tilde{\tilde\gf}$ называются эквивалентными, если существует изоморфизм $I:\tilde\gf\to \tilde{\tilde \gf}$ такой, что диаграмма коммутирует:
-\begin{equation}
-  \label{eq:7}
-  \begin{diagram}
-    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \arrow{s,l}{id} \node{\tilde\gf}\arrow{s,l}{I} \arrow{e,t}{} \node{k}\arrow{s,r}{id} \arrow{e,t}{} \node{0}\\
-    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \node{\tilde{\tilde\gf}} \arrow{e,t}{} \node{k} \arrow{e,t}{} \node{0}
-  \end{diagram}
-\end{equation}
-\begin{exercise}
- Построить изоморфизм $I$.   
-\end{exercise}
-
-Таким образом пространство $H^{2}(\gf)$ -- это множество классов 1-мерных центральных расширений $\gf$. Нуль в $H^{2}(\gf)$  соответствует тривиальному расширению.
-
-Вернемся к алгебре Витта \eqref{eq:230}. Существует коцикл
-\begin{equation}
-  \label{eq:8}
-  c(l_{n},l_{m})=\frac{1}{12}(m^{3}-m)\delta_{-n,m}
-\end{equation}
-\begin{exercise}
-  Проверить, что $c$ -- коцикл алгебры Витта. 
-\end{exercise}
-Соответствующее центральное расширение алгебры Витта называется алгеброй Вирасоро. Коммутационные соотношения этой алгебры имеют вид
-\begin{eqnarray}
-  \label{eq:9}
-  [L_{n},c]=0\\
-  \left[L_{n},L_{m}\right]=(n-m)L_{n+m} +\frac{c}{12} (m^{3}-m) \delta_{-n,m}
-\end{eqnarray}
-Можно показать, что $H^{2}(Witt)\cong \mathbb{C}$ и все нетривиальные коциклы пропорциональны $c$. 
-(Доказательство есть в \cite{fuks1986cohomology}, \cite{schottenloher2008mathematical}).
-
 %%

### 2011-11-23 AffineLieAlgebras/Thesis/common.tex
Added two papers to bibliography, minor changes in thesis text

@@
 \mkcommonsect{pub}{Публикации.}{%
-Материалы диссертации опубликованы в $N$ печатных работах, из них $n_1$ статей в
-рецензируемых журналах~\citemy{Ivanov_1999_Journal_17_173,
-Petrov_2001_Journal_23_12321,Sidorov_2002_Journal_32_1531}, $n_2$ статей в
-сборниках трудов конференций и $n_3$ тезисов докладов.
+Материалы диссертации опубликованы в $8$ печатных работах, из них $3$ статьи в
+рецензируемых журналах~\citemy{2010arXiv1007.0318L,2010LyakhovskyNazarovTMF}, $2$ статьи в
+сборниках трудов конференций, 2 препринта и $1$ тезисы доклада.
 }
@@
 }
+
+%%
+%% End of file
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "thesis"
+%%% End:

### 2011-11-23 AffineLieAlgebras/Thesis/review.tex
Added two papers to bibliography, minor changes in thesis text

@@
 В двух измерениях такая теория обладает богатой симметрией, так что ее даже иногда называют точно решаемой \cite{belavin1984ics}.
-На самом деле существуют разнообразные классы моделей двумерной конформной теории поля и даже задача классификации всех таких моделей до конца не решена, несмотря на первоначальный оптимизм \cite{}.
+На самом деле существуют разнообразные классы моделей двумерной конформной теории поля и даже задача классификации всех таких моделей до конца не решена, несмотря на первоначальный оптимизм \cite{moore1989taming}.
 
@@
   Для любого индекса $i\in B_{0}$  существуют независимые конформные веса $h_{i},\bar h_{i}\in \mathbb{R}$, такие, что для всех преобразований $w\in E_{2}$
-  \begin{equation}
+  \begin{multline}
     \label{eq:52}
-    G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n},\bar z_{1},\dots, \bar z_{n})=\prod_{j=1}^{n}\left(\frac{dw(z_{j})}{dz}\right)^{h_{i_{j}}}\left(\overline{\frac{dw(z_{j})}{dz}}\right)^{\bar{h}_{i_{j}}} G_{i_{\pi(1)},\dots i_{\pi(n)}}(w_{1},\dots, w_{n},\bar w_{1},\dots,\bar w_{n}),
-  \end{equation}
+    G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n},\bar z_{1},\dots, \bar z_{n})=\\
+\prod_{j=1}^{n}\left(\frac{dw(z_{j})}{dz}\right)^{h_{i_{j}}}\left(\overline{\frac{dw(z_{j})}{dz}}\right)^{\bar{h}_{i_{j}}} G_{i_{\pi(1)},\dots i_{\pi(n)}}(w_{1},\dots, w_{n},\bar w_{1},\dots,\bar w_{n}),
+  \end{multline}
 где $w_{i}=w(z_{i})$, а $s_{i}=h_{i}-\bar h_{i}, d_{i}=h_{i}+\bar h_{i}$  -- конформный спин и скейлинговая размерность.

### 2011-11-24 AffineLieAlgebras/Thesis/1.tex
Thesis partially structure cleaned, some translations in chapter 2.

@@
-\chapter{Аффинные алгебры Ли}
+\chapter{Рекуррентные соотношения для коэффициентов ветвления представлений аффинных алгебр Ли}
 \label{cha:affine-lie-algebras}
@@
 Они возникают при изучении различных физических моделей, например, моделей Весса-Зумино-Новикова-Виттена в конформной теории поля и интегрируемых спиновых цепочек.
-\section{Введение. Простые алгебры Ли.}
+
+\section{Введение}
+\label{sec:introduction}
+
+Как было показано в разделе \ref{sec:modular-invariance}, проблема ветвления для аффинных алгебр Ли возникает в конформной теории поля, например, при построении модулярно-инвариантных статсумм  \cite{difrancesco1997cft}.
+Недавно проблема конформных вложений рассматривалась в работе \cite{coquereaux2008conformal}.
+
+Существуют различные подходы к вычислению коэффициентов ветвления.
+Некоторые из них используют резольвенту Бернштейна-Гельфанда-Гельфанда \cite{bernstein1975differential} (См.
+главу \ref{cha:BGG}, алгоритм вычислений описан в работах \cite{kac1990idl},\cite{wakimoto2001idl}), ряды функций Шура \cite{fauser2006new}, когомологии БРСТ  \cite{Hwang:1994yr}, формулы Каца-Петерсона  \cite{kac1990idl,quella2002branching} или комбинаторные методы \cite{feigin707principal}.
+
+В этой главе мы доказываем, что для произвольной редуктивной подалгебры коэффициенты ветвления описываются набором рекуррентных соотношений и существует эффективный и простой алгоритм для пошагового решения этих соотношений.
+Общая идея похожа на подход, предложенный в работе  \cite{ilyin812pbc} для максимальных вложений.
+Но в данном случае алгоритм существенно отличается, так как использует новые свойства сингулярных весов для работы с произвольными редуктивными вложениями $\frak{a} \rightarrow \frak{g}$.
+
+При этом важно рассматривать подалгебру  $\af$ вместе с ее ``ортогональным партнером'' $\afb\subset \gf$. 
+Для любой редуктивной подалгебры $\af$ подалгебра $\afb$ регулярна и редуктивна.
+
+Для модуля старшего веса  $L^{\left( \mu \right)}$ и ортогональной пары подалгебр $\left(  \af, \afb \right)$ мы рассматриваем так называемый сингулярный элемент  $\Psi^{\left( \mu \right)}$ (числитель в формуле Вейля для характеров
+$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$,
+см., например, \cite{humphreys1997introduction}), 
+знаменатель Вейля $\Psi ^{\left( 0\right) }_{\afb}$ и проекцию
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
+=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
+
+Мы доказываем, что для произвольного $\hf$-диагонализующего модуля старшего веса $L^{\left( \mu \right)}$ и ортогональной пары $\left(  \af, \afb \right)$ элемент
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ допускает разложение на множество числителей Вейля $\Psi ^{\left( \mu \right) }_{ \afb }$ модулей подалгебры $\afb$.
+Это разложение дает возможность построить рекуррентное соотношение для коэффициентов ветвления, соответствующих вложению $\frak{a} \rightarrow \frak{g} $.
+Рекуррентное соотношение формулируется с использованием особого элемента  $\Gamma_{\af \rightarrow \gf}$ групповой алгебры
+$\mathcal{E}\left( \frak{g} \right)$, который мы называем ``веером вложения''. 
+Применение этих инструментов позволяет нам сформулировать простой и явный алгоритм для вычисления коэффициентов ветвления, который может быть использован в случае произвольных (максимальных и не максимальных) подалгебр конечномерных и аффинных алгебр Ли.
+В случае максимального вложения веер имеет простую форму, сингулярный элемент становится тривиальном $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\Psi ^{\left( \mu \right) }_{\left(  \gf\right)}$ и мы восстанавливаем соотношения, полученные ранее в работе \cite{ilyin812pbc}.
+
+Также мы показываем, что предложенный алгоритм эффективен и может использоваться при изучении конформных вложений и coset-моделей в рациональной конформной теории поля.
+
+В следующем разделе \ref{sec:intro-simple-lie-algebras} мы определяем аффинные алгебры Ли и приводим основные определения в теории представлений.
+Заодно мы фиксируем обозначения.
+Затем в разделе \ref{sec:branching} мы выводим формулы разложения, основывающиеся на аномальных коэффициентах ветвления и описываем алгоритм редукции интегрируемых модулей старшего веса $L_{\mathfrak{g}}$ по отношению к редуктивной подалгебре  $\mathfrak{a}\subset \mathfrak{g}$ (см.
+секцию \ref{sec:algorithm}).
+В разделе \ref{sec:branching-examples} мы представляем различные примеры применения алгоритма для конечномерных \ref{sec:finite-dimens-lie} и аффинных алгебр Ли и обсуждаем их роль в моделях конформной теории поля \ref{sec:phys-appl}.
+Выводы к главе изложены в разделе \ref{sec:conclusion}.
+В следующей главе \ref{cha:computational-methods} описывается реализация алгоритма на языке {\it Mathematica} и приводятся дополнительные примеры вычислений.
+
+%%  \subsubsection{Notation}
+%%  \label{sec:notation}
+%%  
+%%  Consider affine Lie algebras $\frak{g}$ and $\af$ with
+%%  underlying finite-dimensional subalgebras $\go$ and $%
+%%  \ao$ and an injection $\af\longrightarrow \frak{g%
+%%  }$ such that $\af$ is a reductive subalgebra $\frak{a\subset g}$ with
+%%  correlated root spaces: $\frak{h}_{\af}^{\ast }\subset \frak{h}_{\frak{g%
+%%  }}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
+%%  }_{\go}^{\ast }$\
+%%  .
+%%  We use the following notations:
+%%  
+%%  $L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
+%%  of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\af$
+%%  -module with the highest weight $\nu $ );
+%%  
+%%  $r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\frak{g}$ $%
+%%  \left( \mbox{resp. }\af\right) $ ;
+%%  
+%%  $\Delta $ $\left( \Delta _{\af}\right) $--- the root system; $\Delta
+%%  ^{+} $ $\left( \mbox{resp. }\Delta _{\af}^{+}\right) $--- the positive
+%%  root system (of $\frak{g}$ and $\af$ respectively);
+%%  
+%%  $\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\af}\left(
+%%  \alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $\Delta
+%%  $ (resp. in $\left( \Delta _{\af}\right) $);
+%%  
+%%  $\co{\Delta}$ , $\left( \co{\Delta _{\af}}%
+%%  \right)$ --- the finite root system of the subalgebra $\co{%
+%%  \frak{g}}$ (resp. $\co{\af}$);
+%%  
+%%  $\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\af}^{\nu }\right) $ --- the
+%%  weight diagram of $L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right)
+%%  $ ;
+%%  
+%%  $W$ , $\left( W_{\af}\right) $--- the corresponding Weyl group;
+%%  
+%%  $C$ , $\left( C_{\af}\right) $--- the fundamental Weyl chamber;
+%%  
+%%  $\bar{C}, \left(\bar{C_{\mathfrak{a}}}\right)$ --- the closure of the fundamental Weyl chamber;
+%%  
+%%  $\rho $\ , $\left( \rho _{\af}\right) $\ --- the Weyl vector;
+%%  
+%%  $\epsilon \left( w\right) :=\det \left( w\right) $ ;
+%%  
+%%  $\alpha _{i}$ , $\left( \beta _{j}\right) $ --- the $i
+%%  $-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\af%
+%%  \right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
+%%  
+%%  $\delta $ --- the imaginary root of $\frak{g}$ (and of $\af$ if any);
+%%  
+%%  $\alpha _{i}^{\vee }$ , $\left( \beta _{j}^{\vee
+%%  }\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\af%
+%%  \right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
+%%  
+%%  $\co{\xi }$ , $\co{\xi _{\left( \af\right) }}$
+%%  --- the finite (classical) part of the weight $\xi \in P$ , $\left( \mbox{%
+%%  resp. }\xi _{\left( \af\right) }\in P_{\af}\right) $;
+%%  
+%%  $\lambda =\left( \co{\lambda };k;n\right) $ ---
+%%  decomposition of the affine weight $\lambda$ indicating the finite
+%%  part $\co{\lambda }$, the level $k$ and the grade $n$;
+%%  
+%%  $P$ $\left( \mbox{resp. } P_{\af}\right) $ \ --- the weight lattice;
+%%  
+%%  $m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
+%%  }\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mbox{%
+%%  resp. }\in P_{\af}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
+%%  L_{\af}^{\nu } $);
+%%  
+%%  $ch\left( L^{\mu }\right) $ $\left( \mbox{resp. }ch\left( L_{\af}^{\nu
+%%  }\right) \right) $--- the formal character of $L^{\mu }$ $\left( \mbox{resp. }%
+%%  L_{\af}^{\nu }\right) $;
+%%  
+%%  $ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+%%  +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
+%%  \mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;
+%%  
+%%  $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
+%%  mult}\left( \alpha \right) }}\quad $
+%%  $\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
+%%  \af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
+%%  \left( \alpha \right) }}\right) $--- the Weyl denominator.
+%%  
+%%  
+%%  
+\section{Простые алгебры Ли, алгебра петель, центральные расширения и аффинные алгебры Ли}
 
@@
 
-Now consider an algebra $\gf$ and a reductive subalgebra
-$\af\subset \gf$. Simple roots $\beta_{i}$ of the subalgebra $\af$
-can be presented as linear combinations of $\gf$-algebra roots
-$\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j}
-\alpha_{j},\ j=1,\dots,r_{\af}$.
-
-Each irreducible $\gf$-module is also an $\af$-module, although
-$L^{\mu}_{\gf}$ is in general not irreducible as $\af$-module. 
-It can be
-decomposed into a direct sum of irreducible $\af$-modules:
-\begin{equation}
-  \label{eq:16}
-  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
-\end{equation}
-Coefficients in such a decomposition are called branching
-coefficients.
-
-It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. 
-This traditional approach has serious limitations especially in case of affine Lie algebras. We discuss them in the end of section \ref{sec:comp-algor}.
-
-Now we describe an alternative approach which is based on recurrent properties of branching coefficients. 
-But before we proceed to these recurrent relations we need several additional definitions.
-
-For a subalgebra $\af\subset \gf$ we introduce the subalgebra
-$\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
-orthogonal to $\hf_{\af}$,
-\begin{equation*}
-\hf_{\perp \af}^{\ast }:=\left\{ \eta \in \hf^{\ast }|\forall
-h\in \hf_{\af};\eta \left( h\right) =0\right\} ,
-\end{equation*}
-and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
-to roots of $\af$,
-\begin{eqnarray}
-\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
-h\in \hf_{\af};\beta \left( h\right) =0\right\} ,
-\label{delta a ort} \\
-\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
-}^{+}|\forall h\in \hf_{\af};\beta ^{+}\left( h\right) =0\right\} .
-\notag
-\end{eqnarray}
-Let $W_{\afb}$ be a subgroup of $W$ generated by
-reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
-}}^{+}$. The subsystem $\Delta _{\afb}$ determines a 
-subalgebra $\afb$ with the Cartan subalgebra $\hf_{\af%
-_{\perp }}$.
-
-The Cartan subalgebra $\frak{h}$ can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
-\frak{h}_{\afb}\oplus \frak{h}_{\perp }$
-
-We also introduce the notations
-\begin{eqnarray}
-\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
-\qquad
-\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
-\end{eqnarray}
-
-For $\af$ and $\afb$ we consider the
-corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\af_{\perp
-}} $ and compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
-D}_{\afb}$ of the injection:
-\begin{equation}
-\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho , \qquad
-\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
-_{\perp }}\rho .  \label{defect-ort}
-\end{equation}
-
-%%!!! Define P^+
-For $\mu \in P^{+}$ consider the linked weights $\left\{ \left(
-w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections
-to
-$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
-\mathcal{D}_{\afb}$:
-\begin{equation*}
-\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
-w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
-\end{equation*}
-Among the weights $\left\{ \mu _{\af_{\perp
-}}\left( w\right) |w\in W\right\} $ one can always choose those located in
-the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
-set of representatives $u$ for the classes $W/W_{\afb}$ such
-that
-
-\begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
-\overline{C_{\afb}}\right\} \quad .  \label{U-def}
-\end{equation}
-Thus we can form the subsets:
-\begin{equation}
-\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
-\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
-_{\perp }},\quad u\in U,  \label{mu-a}
-\end{equation}
-and
-\begin{equation}
-\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
-\label{mu-a-tilda}
-\end{equation}
-
-Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
-since it is built on a subset of roots of the algebra $\mathfrak{g}$.
-
-Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients.
-If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.
-
-Now we can use the Weyl character formula to write a
-recurrent relation \cite{2010arXiv1007.0318L} for signed branching
-coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
-injection $\af\hookrightarrow \gf$:
-\begin{equation}
-\begin{array}{c}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
-_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
-\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right.  \\
-\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
-}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
-}\right) .
-\end{array}
-\label{recurrent-rel}
-\end{equation}
-The recursion is governed by the set $\Gamma _{\af\rightarrow \gf}$ called the injection fan. The latter is defined by the
-carrier set $\left\{ \xi \right\} _{\af\rightarrow \gf}$ for the
-coefficient function $s(\xi )$
-\begin{equation*}
-\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}:=\left\{
-\xi \in P_{\widetilde{\af}}|s(\xi )\neq 0\right\}
-\end{equation*}
-appearing in the expansion
-\begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
-_{\widetilde{\af}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
-_{\af}(\pi _{\widetilde{\af}}\alpha )}=-\sum_{\gamma \in P_{%
-\widetilde{\af}}}s(\gamma )e^{-\gamma };\quad
-\end{equation}
-The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
-\right\} $ -- and the zero element is to be eliminated:
-\begin{equation}
-\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma
-_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
-\end{equation}
-Formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
-
-If the root system of $\afb$ is generated by some subset of $\gf$
-simple roots $\alpha_{1},\dots,\alpha_{r}$ then the recurrent
-relation (\ref{recurrent-rel}) is connected with the generalized
-Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules
-\cite{2011arXiv1102.1702L}.
-
-Another particular case of this formula is connected with tensor
-product decompositions. Consider the tensor product of two
-irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$. It is also a
-$\gf$-module but not irreducible in general. So
-\begin{equation}
-  \label{eq:19}
-  L^{\mu}\otimes L^{\nu}=\bigoplus_{\gamma} f^{\mu\nu}_{\gamma}L^{\gamma}
-\end{equation}
-The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion
-coefficients. The problem of computation of fusion coefficients is
-equivalent to branching problem for the diagonal subalgebra
-$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
-
-In the case of affine Lie algebras $\gf, \af$  the multiplicities
-$m_{\nu}$ and the corresponding branching coefficients $b_{\nu}$
-can be regarded as the coefficients in power series decomposition
-of string and branching functions correspondingly:
-\begin{align}
-  \label{eq:21}
-  &\sigma_{\nu}(q)=\sum_{n=0}^{\infty} m_{\nu-n\delta} q^n, \quad \nu=\sum_j c_j \omega_j,\quad c_j\geq 0\\
-  & b_{\nu}(q)=\sum_{n=0}^{\infty} b_{\nu-n\delta} q^n,\quad  \nu=\sum_j c_j \omega_j, \quad c_j\geq 0
-\end{align}
-String and branching functions have  modular and analytic properties which are important for conformal field theory, especially in  coset models and the study of CFT on higher genus surfaces \cite{kac1988modular}, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}.
-
-{\bf Affine.m}  calculates weight multiplicities and branching coefficients for affine Lie algebras up to some finite grade.
-We present examples of computations in Sections \ref{sec:string-funct-affine}, \ref{sec:branch-funct-coset}.
-Now we proceed to the description of datastructures and algorithms implemented in {\bf Affine.m}.
-
- \section{Обозначения}
-
- \label{sec:notation}
- Пусть $\frak{g}$ и $\frak{a}$ -- (аффинные) алгебры Ли, и существует вложение  $\frak{a}\hookrightarrow \frak{g}$ такое, что  $\frak{a}$ -- редуктивная подалгебра в $\frak{g}$ с согласованным корневым пространством: $\frak{%
- h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g}}^{\ast }$. Мы используем следующие обозначения:
-
- $\frak{g=n}^{-}+\frak{h}+\frak{n}^{+}$ --- разложение Картана;
-
- $r$ , $\left( r_{\frak{a}}\right) $ --- ранг алгебра $\frak{g}$ $%
- \left( \mathrm{\text{соотв., }\frak{a}}\right) $ ;
-
- $\Delta $ $\left( \Delta _{\frak{a}}\right) $--- корневая система; $\Delta
- ^{+} $ $\left( \mathrm{\text{соотв., }\Delta _{\frak{a}}^{+}}\right) $--- набор положительных корней (алгебр $\frak{g}$ и $\frak{a}$ соответственно);
-
- $\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
- \alpha \right) \right) $ --- кратность корня $\alpha$ в $%
- \Delta $ (соотв., в $\left( \Delta _{\frak{a}}\right) $);
-
- $S\quad \left( S_{\frak{a}}\right) $ --- множество простых корней (для 
- $\gf$ и $\af$ соответственно);
-
- $\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ ---  $%
- i$-й (соотв., $j$-й) простой корень алгебры $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a%
- }}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
-
- $\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
- }\right) $-- простой ко-корень для $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a}%
- }\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
-
- $W$ , $\left( W_{\frak{a}}\right) $--- группа Вейля;
-
- $C$ , $\left( C_{\frak{a}}\right) $--- фундаментальная камера Вейля;
-
- $\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- замыкание фундаментальной камеры Вейля;
-
- $\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;
-
- $\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- вектор Вейля;
-
- $L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- интегрируемый модуль  $\frak{g}$ со старшим весом $\mu $\ ; (соотв., интегрируемый $\af$-модуль старшего веса $\nu $);
-
- $\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
- весовая диаграмма модуля $L^{\mu }$ (соотв., ${}L_{\frak{a}}^{\nu }$ );
-
- $P$ (соотв., $P_{\frak{a}} $) \ --- весовая решетка;
-
- $P^{+}$ (соотв., $P_{\frak{a}}^{+} $) \ --- решетка доминантных весов;
-
- $m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\zeta }^{\left( \nu \right)
- }\right) $ --- кратность веса $\xi \in P$ \ $\left( \mathrm{\text{соотв., }\in P_{\frak{a}}}\right) $ в $L^{\mu }$, (соотв., в $\zeta \in
- L_{\frak{a}}^{\nu } $);
-
- $ch\left( L^{\mu }\right) $ (соотв., $\mathrm{ch}\left( L_{\frak{a}}^{\nu
- }\right) $)--- формальный характер $L^{\mu }$ (соответственно, $L_{\frak{a}}^{\nu
- } $);
-
- $ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
- +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
- \mathrm{{mult}\left( \alpha \right) }}}$ --- формула Вейля-Каца;
-
- $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
- mult}\left( \alpha \right) }}\quad $ (соотв., $R_{\frak{a}}:=\prod_{\alpha \in
- \Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}%
- }\left( \alpha \right) } $)--- знаменатель Вейля.
-
-\section{Конечномерные алгебры Ли}
-\label{sec:finite-dimensional}
-Основные определения: корни, веса, кратности.
-
-\section{Теория представлений аффинных алгебр Ли}
-\label{sec:representation-theory}
-
-\subsection{Алгебра петель и центральное расширение}
-\label{sec:loop-algebra-central-extension}
-
-Определение аффинных алгебр. Корни, веса, кратности. Категория О.
-
-\subsection{Представления аффинных алгебр Ли}
-\label{sec:affine-lie-algebra-representations}
-
-\section{Ветвления}
+\section{Рекуррентные соотношения для коэффициентов ветвления}
 \label{sec:branching}
-Веер вложения. Алгоритм.
-
-\begin{abstract}
-  Recurrent relations for branching coefficients in affine Lie algebras
-  integrable highest weight modules are studied. The decomposition algorithm
-  based on the injection fan technique is developed for the case of an arbitrary
-  reductive subalgebra. In particular we consider the situation where
-  the Weyl denominator becomes singular with respect to the subalgebra.
-  We demonstrate
-  that for any reductive subalgebra it is possible to define the
-  injection fan and the analogue of the Weyl numerator -- the tools that describe
-  explicitly the recurrent properties of branching coefficients.
-  Possible applications of fan technique in CFT models are considered.
-\end{abstract}
-
-\subsection{Introduction}
-\label{sec:introduction}
-
-The branching problem for affine Lie algebras emerges in conformal field theory, for example,
-in the construction of modular-invariant partition functions \cite{difrancesco1997cft}.
-Recently the problem of conformal embeddings was considered in \cite{coquereaux2008conformal}.
-
-There are different approaches to deal with branching coefficients. Some of them use the BGG
-resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
-\cite{kac1990idl},\cite{wakimoto2001idl}), the Schur function series \cite{fauser2006new}, the BRST
-cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or some
-combinatorial methods applied in \cite{feigin707principal}.
-
-In this paper we prove that
-for an arbitrary reductive subalgebra branching coefficients are subject to
-a set of recurrent properties that can be explicitly formulated and that there exists
-an effective and simple algorithm to solve these recurrent relations step by step.
-The basic idea is similar to the one used in \cite{ilyin812pbc} for maximal embeddings.
-In our case the algorithm is essentially different, new properties of singular weights
-are determined to deal with an arbitrary reductive injection $\frak{a} \rightarrow \frak{g}$.
-
-The principal point is to consider the subalgebra $\af$ together with its
-counterpart $\afb$ orthogonal to $\af$.
-For any reductive algebra $\af$ the subalgebra $\afb \subset \frak{g} $ is regular and reductive.
-For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
-$\left(  \af, \afb \right)$ we consider
-the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
-in the Weyl character formula
-$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$,
-see for example \cite{humphreys1997introduction})
-the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
-$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
-=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
-We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair
-$\left(  \af, \afb \right)$ the element
-$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
-the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
-This decomposition provides the possibility to construct a recurrent property for branching coefficients corresponding
-to the injection $\frak{a} \rightarrow \frak{g} $.
-The property is formulated in
-terms of the specific element $\Gamma_{\af \rightarrow \gf}$ of the group algebra
-$\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
-Using this tool we formulate a simple and
-explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
-subalgebras of finite-dimensional or affine Lie algebras.
-In the case of maximal embedding the corresponding fan is unsubtracted, the singular element
-becomes trivial
-$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\Psi ^{\left( \mu \right) }_{\left(  \gf\right)}$
-and the relations described earlier in \cite{ilyin812pbc} are reobtained.
-
-We demonstrate that our algorithm is effective and can be used in studies
-of conformal embeddings and coset constructions in rational conformal field theory.
-
-The paper is organized as follows. In the subsection \ref{sec:notation}  we fix the general notations.
-In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula based on
-recurrent properties of anomalous branching coefficients and describe the decomposition algorithm
-for integrable highest weight modules
-$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
-(subsection \ref{sec:algorithm}). In Section \ref{sec:finite-dimens-lie} we present several
-simple examples for finite-dimensional Lie algebras. Affine Lie algebras and their applications in
-CFT models are considered in Section \ref{sec:phys-appl}.
-General properties of the proposed algorithm and
-possible further developments are also discussed (Section \ref{sec:conclusion}).
-
-\subsubsection{Notation}
-\label{sec:notation}
-
-Consider affine Lie algebras $\frak{g}$ and $\af$ with
-underlying finite-dimensional subalgebras $\go$ and $%
-\ao$ and an injection $\af\longrightarrow \frak{g%
-}$ such that $\af$ is a reductive subalgebra $\frak{a\subset g}$ with
-correlated root spaces: $\frak{h}_{\af}^{\ast }\subset \frak{h}_{\frak{g%
-}}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
-}_{\go}^{\ast }$\
-.
-We use the following notations:
-
-$L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
-of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\af$
--module with the highest weight $\nu $ );
-
-$r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\frak{g}$ $%
-\left( \mbox{resp. }\af\right) $ ;
-
-$\Delta $ $\left( \Delta _{\af}\right) $--- the root system; $\Delta
-^{+} $ $\left( \mbox{resp. }\Delta _{\af}^{+}\right) $--- the positive
-root system (of $\frak{g}$ and $\af$ respectively);
-
-$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\af}\left(
-\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $\Delta
-$ (resp. in $\left( \Delta _{\af}\right) $);
-
-$\co{\Delta}$ , $\left( \co{\Delta _{\af}}%
-\right)$ --- the finite root system of the subalgebra $\co{%
-\frak{g}}$ (resp. $\co{\af}$);
-
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\af}^{\nu }\right) $ --- the
-weight diagram of $L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right)
-$ ;
-
-$W$ , $\left( W_{\af}\right) $--- the corresponding Weyl group;
-
-$C$ , $\left( C_{\af}\right) $--- the fundamental Weyl chamber;
-
-$\bar{C}, \left(\bar{C_{\mathfrak{a}}}\right)$ --- the closure of the fundamental Weyl chamber;
-
-$\rho $\ , $\left( \rho _{\af}\right) $\ --- the Weyl vector;
-
-$\epsilon \left( w\right) :=\det \left( w\right) $ ;
-
-$\alpha _{i}$ , $\left( \beta _{j}\right) $ --- the $i
-$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\af%
-\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
-
-$\delta $ --- the imaginary root of $\frak{g}$ (and of $\af$ if any);
-
-$\alpha _{i}^{\vee }$ , $\left( \beta _{j}^{\vee
-}\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\af%
-\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
-
-$\co{\xi }$ , $\co{\xi _{\left( \af\right) }}$
---- the finite (classical) part of the weight $\xi \in P$ , $\left( \mbox{%
-resp. }\xi _{\left( \af\right) }\in P_{\af}\right) $;
-
-$\lambda =\left( \co{\lambda };k;n\right) $ ---
-decomposition of the affine weight $\lambda$ indicating the finite
-part $\co{\lambda }$, the level $k$ and the grade $n$;
-
-$P$ $\left( \mbox{resp. } P_{\af}\right) $ \ --- the weight lattice;
-
-$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
-}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mbox{%
-resp. }\in P_{\af}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
-L_{\af}^{\nu } $);
-
-$ch\left( L^{\mu }\right) $ $\left( \mbox{resp. }ch\left( L_{\af}^{\nu
-}\right) \right) $--- the formal character of $L^{\mu }$ $\left( \mbox{resp. }%
-L_{\af}^{\nu }\right) $;
-
-$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
-+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
-\mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;
-
-$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
-mult}\left( \alpha \right) }}\quad $
-$\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
-\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
-\left( \alpha \right) }}\right) $--- the Weyl denominator.
-
-\subsection{Recurrent relations for branching coefficients.}
-\label{sec:recurr-form-branch}
 
@@
 algorithm.
+
+\section{Примеры}
+\label{sec:branching-examples}
 
@@
 
-\subsection{Conclusion}
+\section{Выводы к первой главе}
 \label{sec:conclusion}
@@
 
-\section{БГГ-резольвента}
-\label{sec:bgg}
-Категория О.
-Резольвента Бернштейна-Гельфанда-Гельфанда для представлений аффинных алгебр Ли. Параболические модули и их связь с подалгебрами и ветвлением.
-
-\begin{abstract}
-Рекуррентные соотношения для коэффициентов ветвления основываются на определенном разложении сингулярного элемента.
-Мы показываем, что такое разложение может использоваться для построения параболических модулей Верма и получения обобщенных формул Вейля-Верма для характеров.
-Также мы демонстрируем, что коэффициенты ветвления определяют обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда.
-\end{abstract}
-
-\subsection{Введение}
-
-\label{sec:introduction}
-Свойства ветвления (аффинных) алгебр Ли важны для приложений в квантовой теории поля (смотри, например, модели конформной теории поля \cite{difrancesco1997cft},\cite{coquereaux2008conformal}).
-В данной работе мы показываем, что ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и демонстрирует свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).
-
-Резольвента для неприводимых модулей в терминах бесконечномерных модулей важна для теории интегрируемых спиновых цепочек \cite{derk1008}.
-В подходе  $\mathcal{Q}$-оператора Бакстера \cite{derk09} общие трансфер-матрицы, соответствующие (обобщенным) модулям Верма, факторизуются в произведение операторов Бакстера.
-Резольвента позволяет вычислить трансфер-матрицы для конечномерных вспомогательных пространств.
-
-Чтобы продемонстрировать связь БГГ резольвенты с ветвлением мы используем рекурсивный подход, представленный в работе \cite
-{2010arXiv1007.0318L} (аналогичный подход для максимальных вложений использовался в работе \cite{ilyin812pbc}).
-Мы рассматриваем подалгебру $\af \hookrightarrow \gf$ вместе с $\afb$ -- ``ортогональным партнером'' $\af$ по отношению к форме Киллинга, а также подалгебру $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$, где $\frak{h}=\frak{\frak{h}_{\af}}\oplus
-\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. Для любой редуктивной подалгебры $\af$ алгебра $\afb\hookrightarrow \gf$ регулярна и редуктивна. Для интегрируемого модуля старшего веса $%
-L^{\left(\mu \right) }$ и ортогональной подалгебры  $\af_{\bot }$ мы рассматриваем сингулярный элемент $\Psi ^{\left( \mu \right) }$ (числитель в формуле Вейля для характеров $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
-\mu \right) }}{\Psi ^{\left( 0\right) }}$, см., например,  \cite
-{humphreys1997introduction}) и знаменатель Вейля $\Psi _{\af_{\bot
-  }}^{\left( 0\right) }$ для ортогонального партнера. В работе показано, что элемент  $\Psi _{\gf%
-}^{\left( \mu \right) }$ может быть разложен в комбинацию числителей Вейля $\Psi _{\af_{\bot }}^{\left( \nu \right) }$, где $\nu \in P_{%
-\mathfrak{a}_{\bot}}^{+}$. Это разложение дает возможность построить множество модулей старшего веса $L_{\afb}%
-^{\mu _{\afb}}$. В том случае, если вложение\ $\af%
-_{\bot }\hookrightarrow \gf$ \ удовлетворяет ``стандартным параболическим'' условиям, эти модули порождают параболические модули Верма $M_{\left(
-\afb \hookrightarrow \gf\right) }^{\mu _{%
-\afb}}$, так что исходный характер $ch\left(
-L^{\mu }\right) $ в итоге раскладывается в знакопеременную сумму таких модулей.
-С другой стороны, если параболическое условие нарушено, конструкция сохраняется и порождает разложение по отношению к набору обобщенных модулей Верма  $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
-\widetilde{\afb}}}$, где $%
-\widetilde{\frak{b}_{\perp }}$ уже не является подалгеброй в $\gf$, а оказывается сжатием $\widetilde{\afb}$.
-
-Некоторые общие свойства предложенного разложения формулируются в терминах  формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''.
-Использование этого инструмента позволило сформулировать простой и явный алгоритм для вычисления правил ветвления, подходящий для произвольной (максимальной или не максимальной) подалгебры в аффинной алгебре Ли \cite{2010arXiv1007.0318L}.
-
-Возможные обобщения полученных результатов обсуждаются в Разделе \ref{sec:conclusions}.
-
-\subsection{Ортогональная подалгебра и сингулярные элементы}
-
-\label{sec:recurr-form-branch}
-
-В этом разделе мы покажем, как рекуррентный подход к проблеме ветвления естественным образом приводит к представлению формального характера $\frak{g}$-модуля в виде комбинации характеров, соответствующих параболическим (обобщенным) модулям Верма.
-Рассмотрим редуктивную алгебру Ли  $\frak{g}$ и ее редуктивную подалгебру $\frak{a}\subset \frak{g}$.
-Пусть  $L^{\mu} $ -- интегрируемый модуль старшего веса алгебры  $\frak{g}$, $\mu \in P^{+}$.  Будем считать  $L^{\mu}$ вполне приводимым по отношению к подалгебре $\frak{a}$,
-\begin{equation*}
-L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
-}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
-\end{equation*}
-Это разложение может быть записано в терминах формальных характеров с использованием оператора проекции  $\pi _{\frak{a}}$ (на весовое пространство $\frak{h_{a}}^{\ast }$):
-\begin{equation}
-\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
-}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
-\label{branching1}
-\end{equation}
-Для модуля  $L^{\mu }$ существует БГГ резольвента (см. \cite
-{bernstein1976category,bernstein1975differential,bernstein1971structure} и
-\cite{humphreys2008representations}). Все члены фильтрующей последовательности представляются суммами модулей Верма со старшими весами $\nu$, сильно связанными с $\mu$:
-\begin{equation*}
-\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
-W\right\} .
-\end{equation*}
-
-\subsubsection{Ортогональная подалгебра}
-
-Пусть  $\frak{h}_{\frak{a}}$ -- подалгебра Картана в  $\mathfrak{g}$. Для  $\mathfrak{a}\hookrightarrow \frak{g}$ введем ``ортогонального партнера''  $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$.
-
-Рассмотрим корневое подпространство  $\frak{h}_{\perp \frak{a}}^{\ast }$, ортогональное к $\frak{a}$,
-\begin{equation*}
-\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
-h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} ,
-\end{equation*}
-и корни  $\frak{g}$ (соответственно, положительные корни),  ортогональные к $\frak{a}$,
-\begin{eqnarray}
-\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
-h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
-\label{delta a ort} \\
-\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
-}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
-\notag
-\end{eqnarray}
-Обозначим символом  $W_{\frak{a}_{\perp }}$ подгруппу  $W$, порожденную отражениями  $w_{\beta }$ с корнями  $\beta \in \Delta_{\frak{a}_{\perp}}^{+}$.
-Корневая подсистема  $\Delta _{\frak{a}_{\perp }}$ определяет подалгебру  $\frak{a}_{\perp }$, имеющую подалгебру Картана $\frak{h}_{\frak{a}_{\perp }}$.
-Пусть
-\begin{equation*}
-\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
-}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
-h\right) =0\right\};
-\end{equation*}
-выделим в  $\frak{g}$  подалгебры
-\begin{eqnarray}
-\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp },
-\qquad
-\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
-\end{eqnarray}
-Заметим, что  $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ в общем случае не является подалгеброй в $\mathfrak{g}$.
-
-Для подалгебр Картана имеет место разложение
-\begin{equation}
-\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
-\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
-\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
-\frak{h}_{\frak{a}}.
-\end{equation}
-Рассмотрим векторы Вейля  $\rho _{\frak{a}}$ и $\rho _{\frak{a}_{\perp}} $, соответствующие  $\frak{a}$ и $\frak{a}_{\perp }$.
-Введем так называемые ``дефекты'' вложения  $\mathcal{D}_{\frak{a}}$ и $\mathcal{D}_{\frak{a}_{\perp }}$:
-\begin{equation}
-\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho , \qquad
-\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
-_{\perp }}\rho .  \label{defect ort}
-\end{equation}
-Для  $\mu \in P^{+}$ рассмотрим связанные веса  $\left\{\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ и их проекции на $h_{\frak{a}_{\perp }}^{\ast }$, дополнительно сдвинутые на вектор дефекта $-\mathcal{D}_{\frak{a}_{\perp }}$:
-\begin{equation*}
-\mu _{\frak{a}_{\perp }}\left( w\right) :=\pi _{\frak{a}_{\perp }}\left[
-w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad w\in W.
-\end{equation*}
-
-Среди весов  $\left\{ \mu _{\frak{a}_{\perp
-}}\left( w\right) |w\in W\right\} $ всегда можно выбрать те, которые попадают в фундаментальную камеру $\overline{C_{\frak{a}_{\perp }}}$.
-Пусть $U$ -- множество представителей $u$ классов  $W/W_{\frak{a}_{\perp }}$, таких что
-\begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
-\overline{C_{\frak{a}_{\perp }}}\right\} \quad .  \label{U-def}
-\end{equation}
-Тогда можно выделить подмножества:
-\begin{equation}
-\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
-\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}%
-_{\perp }},\quad u\in U,  \label{mu-a}
-\end{equation}
-и
-\begin{equation}
-\mu _{\frak{a}_{\perp }}\left( u\right) :=\pi _{\frak{a}_{\perp }}\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U.
-\label{mu-a-tilda}
-\end{equation}
-
-Заметим, что подалгебра  $\mathfrak{a}_{\bot}$ по определению регулярна, так как она построена на подмножестве корней алгебры $\mathfrak{g}$.
-
-Для интересующих нас модулей формула Вейля-Каца для  $\mathrm{ch}\left( L^{\mu }\right) $ может быть записана через сингулярные элементы \cite{humphreys1997introduction},
-\begin{equation*}
-\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
-)-\rho },
-\end{equation*}
-а именно:
-\begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
-^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
-\label{Weyl-Kac2}
-\end{equation}
-То же верно и для подмодулей $\mathrm{ch}\left( L_{\frak{a}}^{\nu
-}\right) $ в формуле (\ref{branching1})
-\begin{equation*}
-\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
-\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
-}^{\left( \nu \right) }}{R_{\frak{a}}},
-\end{equation*}
-где
-\begin{equation*}
-\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
-}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
-\end{equation*}
-Применяя формулу  (\ref{Weyl-Kac2}) к правилу ветвления  (\ref{branching1}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu
-\right) }$ и $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
-\begin{eqnarray}
-\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
-)-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
-(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
-\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
-\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
-mult}_{\frak{a}}(\beta )}},  \notag  \label{eq:4} \\
-\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
-&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
-}^{\left( \nu \right) }}{R_{\frak{a}}}.
-\end{eqnarray}
-
-\subsubsection{Разложение сингулярного элемента.}
-
-\label{subsec:decomp-sing-element}
-
-Теперь мы выполним разложение сингулярного элемента  $\Psi ^{\left(\mu \right) }$ на сингулярные элементы модулей ортогонального партнера:
-
-\begin{lemma}
-
-Пусть  $\frak{a}_{\bot }$ -- ортогональный партнер редуктивной подалгебры  $\frak{a}\hookrightarrow \frak{g}$ и $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$, $\widetilde{%
-\frak{a}_{\perp }}=\frak{a}_{\perp }\oplus \frak{h}_{\perp }$, $%
-\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$.
-
-Пусть $L^{\mu }$ -- интегрируемый модуль старшего веса  $\mu \in P^{+}$ и
-
-$\Psi ^{\left( \mu \right) }$\ -- сингулярный элемент $L^{\mu }$.
-
-Тогда элемент  $\Psi ^{\left( \mu \right) }$ может быть разложен в сумму по  $u\in U$ (см.
-(\ref{U-def})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
-$\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
-\begin{equation}
-\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\widetilde{%
-\mathfrak{a}}}\left( u\right) }\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}%
-_{\perp }}\left( u\right) }.  \label{sing decomp main}
-\end{equation}
-\label{Psi-decomp-lemma}
-\end{lemma}
-
-\begin{proof}
-Пусть
-\[
-u(\mu +\rho )=\pi _{\left( \aft\right) }u(\mu +\rho )+\pi _{\left(
-\frak{a}_{\perp }\right) }u(\mu +\rho ),
-\]
-где $u\in U$. Для произвольного  $v\in W_{\frak{a}_{\bot }}$ рассмотрим сингулярный вес  $vu(\mu +\rho )-\rho $ и выполним разложение:
-\begin{equation}
-\begin{array}{lcl}
-vu(\mu +\rho )-\rho  & = & \pi _{\left( \frak{a}\right) }\left( u(\mu +\rho
-)\right) -\rho +\rho _{\frak{a}_{\perp }}
-\\
-&  & +\ v\left( \pi _{\left( \aft_{\perp }\right) }u(\mu
-+\rho )-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{%
-\frak{a}_{\perp }} .
-\end{array}
-\label{sing-decomp-1}
-\end{equation}
-Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}), чтобы упростить первую строку в формуле (\ref{sing-decomp-1}):
-\[
-\begin{array}{r}
-\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
-\frak{a}_{\perp }}= \\
-\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\pi _{\aft%
-}\rho -\pi _{\af_{\bot }}\rho +\rho _{\frak{a}_{\bot }}= \\
-=\pi _{\left( \aft\right) }\left( u(\mu +\rho )-\rho \right) +\mathcal{D}%
-_{\frak{a}_{\bot }},
-\end{array}
-\]
-и вторую строку
-\[
-\begin{array}{c}
-v\left( \pi _{\left( \frak{a}_{\perp }\right) }u(\mu +\rho
-)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}%
-_{\perp }}= \\
-v\left( \pi _{\left( \frak{a}_{\bot }\right) }u(\mu +\rho )-%
-\mathcal{D}_{\frak{a}_{\bot }}-\pi _{\left( \frak{a}_{\bot }\right) }\rho
-+\rho _{\frak{a}_{\bot }}\right)
--\rho _{\frak{a}_{\bot }}= \\
-=v\left( \pi _{\left( \frak{a}_{\bot }\right) }\left[ u(\mu
-+\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\bot }}+\rho _{\frak{a}_{\bot
-}}\right) -\rho _{\frak{a}_{\bot }}.
-\end{array}
-\]
-В результате получаем требуемое разложение сингулярного элемента $\Psi ^{\mu }$ на сингулярные элементы $\Psi_{\frak{a}_{\perp}}^{\eta}$ модулей $L_{\frak{a}_{\perp }}^{\eta }$ подалгебры $\frak{a}_{\perp }$:
-\begin{equation}
-\begin{array}{l}
-\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
-(v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
-=\sum_{u\in U}\epsilon (u)e^{\pi _{\aft}\left[ u(\mu +\rho )-\rho \right]
-+\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
-(v)e^{v\left( \pi _{\left( \frak{a}_{\perp }\right) }\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}+\rho _{\frak{a}%
-_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
-=\sum_{u\in U}\;\epsilon (u)\Psi _{\af_{\perp }}^{\pi
-_{\left( \frak{a}_{\perp }\right) }\left[ u(\mu +\rho )-\rho
-\right] -\mathcal{D}_{\frak{a}_{\perp }}}e^{\pi _{\left( \aft\right) }%
-\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}.
-\end{array}
-\label{singular main}
-\end{equation}
-\end{proof}
-
-%\bigskip
-
-\begin{remark}
-Это соотношение можно рассматривать как обобщение формулы Вейля для сингулярного элемента $\Psi _{\frak{g}}^{\mu }$: векторы $\mu _{%
-\widetilde{\mathfrak{a}}}\left( u\right) $ играют роль сингулярных весов, в то время как множители  $\epsilon (u)$ расширены до $\epsilon
-(u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$.
-
-Действительно, при  $\frak{a=g}$ подалгебры  $\frak{a}_{\perp }$, и $\frak{h}_{\perp }$ тривиальны, $U=W$ и оригинальная формула Вейля восстанавливается, так как сингулярные элементы $\epsilon (u)\Psi _{\frak{a}_{\perp %
-}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\epsilon (u)$ становятся  тривиальными.
-
-В противоположном пределе, когда $\frak{a}=0$, $\Delta _{\frak{a}_{\perp }}=\Delta _{\frak{g}}$, $%
-\frak{h}_{\perp }^{\ast }=0$, $\frak{a}_{\perp }=\frak{g}$, $\mathcal{D}_{%
-\frak{a}_{\perp }}=0$ и $U=W/W_{\frak{a}_{\perp }}=e$, вновь приходим к выражению для  сингулярного элемента
- $\Psi ^{\mu }$, теперь -- в результате тривиализации множества векторов $\mu _{\af}\left( e\right) =0$.
-\end{remark}
-
-\begin{remark}
-
-В работе \cite{2010arXiv1007.0318L} разложение, аналогичное формуле (\ref{singular main}), было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
-\begin{equation}
-\begin{array}{c}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
-_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
-\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right.  \\
-\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
-}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
-}\right) .
-\end{array}
-\label{recurrent rel}
-\end{equation}
-Рекурсия задается множеством  $\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}$, которое носит название веера вложения.
-Это множество определяется как носитель  $\left\{ \xi \right\}_{\frak{a}\rightarrow \frak{g}}$  коэффициентной функции $s(\xi )$
-\begin{equation*}
-\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{g}}:=\left\{
-\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\},
-\end{equation*}
-возникающей в разложении 
-\begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
-_{\widetilde{\frak{a}}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
-_{\frak{a}}(\pi _{\widetilde{\frak{a}}}\alpha )}=-\sum_{\gamma \in P_{%
-\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma }.\quad
-\end{equation}
-Веса из множества $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
-g}}$ сдвигаются на $\gamma _{0}$ -- младший вектор в $\left\{ \xi
-\right\} $, и исключается нулевой элемент:
-\begin{equation}
-\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}=\left\{ \xi -\gamma
-_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
-\end{equation}
-
-Рекуррентное соотношение (\ref{recurrent rel}) первоначально использовалось для описания ветвления интегрируемых модулей.
-Заметим, что существует важный класс модулей, которые также могут быть редуцированы при помощи веера вложения -- это модули Верма.
-\end{remark}
-
-\subsubsection{Фомулы Вейля-Верма.}
-
-\begin{statement}
-%\bigskip
-Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характер интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) характеров параболических модулей Верма, распределенных по множеству весов $\mu _{\widetilde{\mathfrak{a}}}\left(
-u\right)$:
-\begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{%
-\widetilde{\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}%
-_{\perp }}\left( u\right) },  \label{gen Weyl-Verma}
-\end{equation}
-где  $U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
-\overline{C_{\frak{a}_{\perp }}}\right\} $ и $I$ -- такое подмножество в  $S$, что $\Delta _{I}^{+}$ эквивалентно $\Delta _{\frak{a}_{\perp }}^{+}$.
-\end{statement}
-
-%\bigskip
-\begin{proof}
-Подалгебра  $\mathfrak{a}_{\bot }$ регулярна и редуктивна по определению  (\ref{delta a ort}). Рассмотрим её знаменатель Вейля   $R_{\frak{a}_{\perp }}:=\prod_{\alpha \in \Delta _{\frak{a}%
-_{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}%
-\mathrm{\left( \alpha \right) }}$ и элемент  $R_{J}:=\prod_{\alpha \in
-\Delta ^{+}\setminus \Delta _{\frak{a}_{\perp }}^{+}}\left( 1-e^{-\alpha
-}\right) ^{\mathrm{mult}(\alpha )}$ как сомножители в $R$:
-\begin{equation*}
-R=R_{J}R_{\frak{a}_{\perp }}.
-\end{equation*}
-Согласно этой факторизации и разложению  (\ref{sing decomp main}) характер $\mathrm{ch}\left( L^{\mu }\right) $ можно переписать в виде
-\begin{eqnarray*}
-\mathrm{ch}\left( L^{\mu }\right) &=&\left( R_{J}\right) ^{-1}\left( R_{%
-\frak{a}_{\perp }}\right) ^{-1}\Psi ^{\mu }=\left( R_{J}\right)
-^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}}\left( u\right) }\epsilon
-(u)\left( R_{\frak{a}_{\perp }}\right) ^{-1}\Psi _{\frak{a}_{\perp }}^{\mu _{%
-\frak{a}_{\perp }}\left( u\right) } \\
-&=&\left( R_{J}\right) ^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}%
-}\left( u\right) }\epsilon (u)\mathrm{ch}\left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
-}}\left( u\right) }\right),
-\end{eqnarray*}
-где  $\left\{ L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left(
-u\right) }|u\in U\right\} $ -- множество конечномерных $\frak{a}%
-_{\perp }$-модулей со старшими весами   $\mu _{\frak{a}_{\perp }}\left(
-u\right) $.
-Нас интересуют нетривиальные подалгебры $\frak{a}$ и, соответственно, нетривиальные  $\frak{a}_{\perp }$ (случай тривиальной ортогональной подалгебры рассматривался выше в (см.
-Замечание 1)).
-Значит $r_{\frak{a}}\geq 1$ и $r_{\frak{a}%
-_{\perp }}<r$.
-Так как диаграмма Дынкина для любой регулярной подалгебры получается в результате исключения одной, двух или более вершин из расширенной диаграммы Дынкина алгебры, а расширенная диаграмма содержит не более одного зависимого корня (старший корень), множество корней $\Delta _{\frak{a}_{\perp }}^{+}$ всегда эквивалентно некоторому множеству $\Delta _{I}^{+}$, порожденному набором  простых корней $I\subset S $.
-
-Следовательно мы можем (переопределяя множество  $\Delta ^{+}$) отождествить $\Delta _{\frak{a}_{\perp }}^{+}$ с подмножеством  $\Delta _{I}^{+}$, где $I\subset S$.
-В результате мы можем определить объекты, необходимые для построения обобщенных модулей Верма \cite{lepowsky1977generalization,humphreys2008representations}.
-У нас есть два множества корневых векторов $\left\{ x_{\xi }\in \frak{g}_{\xi }|\xi \in \Delta _{I}^{+}\right\}
-$ и $\left\{ x_{\eta }\in \frak{g}_{\eta }|\eta \in \Delta ^{+}\setminus
-\Delta _{I}^{+}\right\} $, и соответствующие нильпотентные подалгебры в  $\frak{n}%
-^{+}$:
-\begin{equation*}
-\frak{n}_{I}^{+}:=\sum_{\xi \in \Delta _{I}^{+}}\frak{g}_{\xi },\quad
-\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\frak{g}%
-_{\eta }.
-\end{equation*}
-Первая подалгебра вместе со своей отрицательной копией  $\frak{n}%
-_{I}^{-} $ порождает простую подалгебру 
-\begin{equation*}
-\frak{s}_{I}=\frak{n}_{I}^{-}+\frak{h}_{I}+\frak{n}_{I}^{+}.
-\end{equation*}
-Мы расширяем ее оставшимися картановскими генераторами:
-\begin{equation*}
-\frak{l}_{I}=\frak{n}_{I}^{-}+\frak{h}+\frak{n}_{I}^{+}.
-\end{equation*}
-Полупрямое произведение  $\frak{l}_{I}$ и $\frak{u}_{I}^{+}$ дает параболическую подалгебру $\frak{p}_{I}\hookrightarrow \frak{g}$ :
-\begin{equation}
-\frak{p}_{I}=\frak{l}_{I}\vartriangleright \frak{u}_{I}^{+}.
-\label{paralolic subalg}
-\end{equation}
-Ее универсальная обертывающая $U\left( \frak{p}_{I}\right) $ является подалгеброй в  $%
-U\left( \frak{g}\right) $. Модули  $L_{\frak{a}_{\perp }}^{\mu _{%
-\frak{a}_{\perp }}\left( u\right) }$ алгебры  $\frak{l}_{I}$ легко поднимаются до  $\frak{p}_{I}$-модулей при помощи тривиального действия нильрадикала $\frak{u}_{I}^{+}$.
-Последний стандартным образом индуцирует $U\left( \frak{g}\right) $-модули:
-\begin{equation*}
-M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=U\left( \frak{g}\right)
-\otimes _{U\left( \frak{p}_{I}\right) }L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
-_{\perp }}\left( u\right) }.
-\end{equation*}
-
-Это  \textit{обобщенные модули Верма}  \cite{lepowsky1977generalization},
-порожденные старшими весами  $\mu _{\frak{a}%
-_{\perp }}\left( u\right) $. Как  $U\left( \frak{u}_{I}^{-}\right) $-модуль каждый  $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ изоморфен  $%
-U\left( \frak{u}_{I}^{-}\right) \otimes L_{\frak{a}_{\perp }}^{\mu _{%
-\frak{a}_{\perp }}\left( u\right) }$ и его характер можно записать при помощи функции Костанта-Хекмана \cite{KostantHeckman1982}, соответствующей вложению ортогонального партнера $\frak{a}_{\perp
-}\hookrightarrow \frak{g}$:
-\begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\mathcal{KH}_{%
-\frak{a}_{\perp }\hookrightarrow \frak{g}}\mathrm{ch}L_{\frak{a}_{\perp
-}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
-\end{equation*}
-Функция  $\mathcal{KH}_{\frak{a}_{\perp }\hookrightarrow \frak{%
-g}}$ генерируется знаменателем  $R_{I}$, так что последнее выражение можно переписать следующим образом
-\begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\frac{1}{R_{I}}%
-\mathrm{ch}L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
-\end{equation*}
-Таким образом мы получили обобщенную формулу Вейля-Верма для характеров -- разложение  $\mathrm{ch}\left(
-L^{\mu }\right) $ на характеры обобщенных модулей Верма:
-\begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
-u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
-u\right) }.  \label{char in gen verma mod}
-\end{equation}
-\end{proof}
-
-\begin{remark}
-Здесь обобщенная формула Вейля-Верма для характеров (называемая формулой переменного суммирования в книге \cite{humphreys2008representations}) имеет специальный вид: веса $\mu _{\aft}$ отличны от старших весов обобщенных модулей Верма $\mu _{\afb}$.
-Причина в том, что старший вес $M_{I}$-модуля не равен проекции его максимального веса на  $h^*_{\afb}$ (он должен быть дополнительно сдвинут на дефект).
-\end{remark}
-
-\begin{example}
-  Рассмотрим обобщенные модули Верма для вложения $A_{1}\hookrightarrow B_{2}$, где подалгебра  $\afb$ связана с корнем  $\alpha_{1}$ алгебры  $B_{2}$.
-Обобщенный модуль Верма $M^{\omega_{1}}_{I}$ со старшим весом   $\omega_{1}=e_{1}$ показан на Рисунке \ref{fig:B2_Verma_Decomp}.
-  \begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=120mm]{B2_Gen_Verma_Decomp}
-  }
-  \caption{Обобщенные модули Верма для регулярного вложения  $A_1$ в $B_2$. 
-    Простые корни $\alpha_1, \alpha_2$ алгебры $B_2$ показаны пунктирными стрелками.
-Простой корень  $\beta = \alpha_1+2\alpha_2$ алгебры $A_1$ изображен серым вектором.
-Разложение $L^{\omega_{1}}$ представлено набором контуров входящих в него обобщенных модулей Верма.
-Пунктирные контуры соответствуют положительным значениям  $\epsilon(u)$, а точечные -- отрицательным.
-}
-
- \label{fig:B2_Verma_Decomp}
-\end{figure}
-
-\end{example}
-
-\begin{remark}
-Как доказано, например, в книге  \cite{humphreys2008representations} (см.
-утверждение 9.6), характеры обобщенных модулей Верма $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ могут также описываться как линейные комбинации обычных модулей Верма алгебры $\frak{g}$:
-\begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\sum_{w\in W_{%
-\frak{a}_{\perp }}}\epsilon \left( w\right) \mathrm{ch}M^{w\left( \mu _{%
-\frak{a}_{\perp }}\left( u\right) +\rho _{\frak{a}_{\perp }}\right) -\rho _{%
-\frak{a}_{\perp }}}
-\end{equation*}
-Подставляя это выражение в формулу (\ref{char in gen verma mod}) и используя определения  (\ref{mu-a},\ref{mu-a-tilda}) и (\ref{defect ort}), мы восстанавливаем стандартное разложение Вейля-Верма для характера:
-\begin{equation*}
-\mathrm{ch}\left( L^{\mu }\right) =\sum_{w\in W}\;\epsilon (u)\mathrm{ch}%
-M^{w\left( \mu +\rho \right) -\rho }.
-\end{equation*}
-\end{remark}
-
-\subsection{БГГ резольвента и ветвление}
-В работе \cite{lepowsky1977generalization} показано, что для модуля старшего веса $L^{\mu }$, где $\mu \in P^{+}$, последовательность (обобщенная БГГ резольвента)
-\begin{equation}
-0\rightarrow M_{r}^{I}\overset{\delta _{r}}{\rightarrow }M_{r-1}^{I}\overset{%
-\delta _{r-1}}{\rightarrow }\ldots \overset{\delta _{1}}{\rightarrow }%
-M_{0}^{I}\overset{\varepsilon }{\rightarrow }L^{\mu }\rightarrow 0,
-\label{resolution sequence}
-\end{equation}
-где
-\begin{equation}
-M_{k}^{I}=\bigoplus_{u\in U,\;\mathrm{length}\left( u\right)
-=k}M_{I}^{u\left( \mu +\rho \right) -\rho },\quad M_{0}^{I}=M_{I}^{\mu }
-\label{Verma elements sequence}
-\end{equation}
-является точной и формула (\ref{gen Weyl-Verma}%
-) следует из этого разложения.
-
-\begin{figure}[h!bt]
- \noindent\centering{
-   \includegraphics[width=140mm]{B2_Exact}}
- \caption{Вложение $A_1\hookrightarrow B_2$ (см. Рисунок \ref{fig:B2_Verma_Decomp}). Ортогональный партнер, подалгебра $A_1$, соответствует корню $\alpha_1$.
-   Резольвента простого модуля $L^{\omega_1}$. Показана центральная часть точной последовательности
-   $0 \to Im(\delta_2) \to \left( e^{\mu _{\widetilde{%
-\frak{a}}}\left( e\right) }\mathrm{ch}M_{I}^{\pi _{\afb}\left[ \omega_1 \right] -%
-\mathcal{D}_{\afb} }=M^{\omega_1}_{I}\right) \to
-   L^{\omega_1}\to 0 $.  Здесь $\mu _{\widetilde{\frak{a}}}\left( e\right) =\pi _{\aft}\left[ \mu \right] + \mathcal{D}_{\afb}$.
-   }
-\end{figure}
-
-\begin{statement}
-Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра  $\afb\hookrightarrow \frak{g}$ ортогональна редуктивной подалгебре $\frak{a}\hookrightarrow \frak{g}$.
-Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\afb$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к подалгебре $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}$ .
-\end{statement}
-
-\begin{proof}
-Положим
-\begin{equation*}
-\mathrm{ch}M_{I}^{u\left( \mu +\rho \right) -\rho }=e^{\mu _{\widetilde{%
-\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
-u\right) },\mathrm{ch}M_{I}^{\mu }=e^{\mu _{\widetilde{\frak{a}}}\left(
-e\right) }\mathrm{ch}M_{I}^{\pi _{\frak{a}_{\perp }}\left[ \mu \right] -%
-\mathcal{D}_{\frak{a}_{\perp }}},
-\end{equation*}
-где \ $\mu _{\widetilde{\frak{a}}}\left( u\right) ,\mu _{\frak{a}_{\perp
-}}\left( u\right) $ и $\mathcal{D}_{\frak{a}_{\perp }}$ заданы как в Лемме \ref{Psi-decomp-lemma}, $%
-u\in U$ определено формулой (\ref{U-def}). В результате получим элементы фильтрующей последовательности (\ref{resolution sequence}).
-
-Рассмотрим множество $\left\{ \mu _{\frak{a}_{\perp }}\left( u\right) |u\in U\right\} $ как множество старших весов простых модулей $L_{\frak{a}%
-_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ и вычислим размерности этих модулей. Вместе с 
-$\left\{ \mu _{\widetilde{\mathfrak{a}}}\left( u\right) |u\in
-U\right\} $ мы получим набор сингулярных весов
-\begin{equation*}
-\left\{ \epsilon (u)\;
-e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }
-\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
-}}\left( u\right) }\right) \right\} .
-\end{equation*}
-Ветвление  $L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu
-\in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$  определяется веером вложения  $\Gamma _{\frak{a}\rightarrow \frak{g}}$ и соотношением (\ref{recurrent rel}), которое дает нам коэффициенты  $k_{\xi
-}^{\left( \mu \right) }$, а значит определяет и  $b_{\nu }^{\left( \mu \right) }$, так как  $b_{\nu }^{\left( \mu \right) }=k_{\nu }^{\left( \mu
-\right) }$ при $\nu \in \overline{C_{\frak{a}}}$ .
-\end{proof}
-
-\begin{corollary}
-Пусть  $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$ и  $\frak{a}\hookrightarrow \frak{g}$ -- редуктивная подалгебра $\frak{g}$.
-Пусть $\frak{a}_{\perp }$, ортогональный партнер для $\frak{a}$, эквивалентен  $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, и $\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ с $\frak{h=\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$.
-Пусть $L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }=\bigoplus\limits_{\nu \in P_{\widetilde{\frak{a}}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\widetilde{\frak{a}}}^{\nu }$ -- ветвление модуля $L^{\mu }$ относительно подалгебры $\widetilde{\frak{%
-a}}$. Тогда коэффициенты $b_{\nu }^{\left( \mu \right) }$ определяют обобщенную резольвенту (\ref{resolution sequence}) модуля $L^{\mu }$
-по отношению к  $\frak{a}_{\perp }$.
-\end{corollary}
-
-\begin{proof}
-Пусть $\alpha $ -- простой корень  $A_{1}$.
-Используем преобразования из группы Вейля чтобы перевести его в некоторый простой корень алгебры $\frak{g}$, например $\alpha _{1}$.
-Построим сингулярный элемент для модуля  $L_{\frak{g}\downarrow
-\widetilde{\frak{a}}}^{\mu }$, то есть  $\Psi _{\widetilde{\frak{a}}%
-}^{\left( L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }\right)
-}=\sum_{\nu \in P_{\widetilde{\frak{a}}}^{+},b_{\nu }^{\left( \mu \right)
-}>0}b_{\nu }^{\left( \mu \right) }\Psi _{\widetilde{\frak{a}}}^{\left( \nu
-\right) }$, и разложим его $\Psi _{\widetilde{\frak{a}}}^{\left( L_{\frak{%
-g}\downarrow \widetilde{\frak{a}}}^{\mu }\right) }=k_{\xi }^{\left( \mu
-\right) }e^{\xi }$. В нашем случае представители $u$ в рекуррентном соотношении (\ref{recurrent rel}) определяются весом $\xi $ однозначно:
-\begin{equation*}
-\epsilon (u\left( \xi \right) )\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{%
-\frak{a}_{\perp }}\left( u\left( \xi \right) \right) }\right) =-s\left(
-\gamma _{0}\right) k_{\xi }^{\left( \mu \right) }-\sum_{\gamma \in \Gamma _{%
-\widetilde{\frak{a}}\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right)
-k_{\xi +\gamma }^{\left( \mu \right) }.
-\end{equation*}
-Тогда
-\begin{equation*}
-\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\left(
-\xi \right) \right) }\right) =\left| s\left( \gamma _{0}\right) k_{\xi
-}^{\left( \mu \right) }+\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}%
-\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma
-}^{\left( \mu \right) }\right|
-\end{equation*}
-и
-\begin{equation*}
-\mu _{\frak{a}_{\perp }}\left( u\left( \xi \right) \right) =\frac{1}{2}%
-\left( \dim \left( L_{A_{1}}^{\mu \left( \xi \right) }\right) -1\right)
-\alpha _{1}
-\end{equation*}
-Таким образом, множество обобщенных модулей Верма  $e^{\xi +\mathcal{D}%
-_{\frak{a}_{\perp }}}\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
-u\left( \xi \right) \right) }$ полностью фиксировано:
-\begin{equation*}
-\left\{ e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }\mathrm{ch}%
-M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }|u\in U\right\} .
-\end{equation*}
-Упорядочивая эти модули по длине $u$, мы получаем компоненты (\ref{Verma elements sequence}) резольвенты (\ref{resolution sequence}).
-\end{proof}
-
-\subsection{Заключение}
-
-\label{sec:conclusions}
-В работе \cite{2010arXiv1007.0318L} было показано, что метод веера вложения работает также и для специальных вложений.
-Надо заметить, что  разложения Вейля-Верма также могут быть получены в этом случае.
-Резольвенты, соответствующие специальным подалгебрам, описывают соотношения между проекциями характера начального модуля и обобщенными модулями Верма со старшими весами в подпространстве $h^*$.
-
-Рассмотрим ситуацию, когда выбор простых корней зафиксирован какими-то внешними факторами (возникающими, например, из требований физических приложений).
-В этом случае ортогональный партнер не может порождаться только простыми корнями.
-Элементы   $\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta
-^{+}\setminus \Delta _{I}^{+}}\frak{g}_{\eta }$ не образуют подалгебру в  $%
-\mathfrak{g}$, так как некоторые не простые корни отсутствуют в  $\Delta ^{+}\setminus
-\Delta _{I}^{+}$. Важно отметить, что в этом случае формула Вейля-Верма по-прежнему существует. В ней обобщенные модули Верма соответствуют сжатиями \cite{Doebner1967Melsheimer} алгебры $%
-\frak{n}^{+}$ и соотношения Вейля-Верма описывают разложение пространства представления $L^{\mu}$ в набор обобщенных модулей Верма сжатой алгебры  $U\left(\frak{n}_c^{+}\right)$.
-Весовые векторы образованы базисом Пуанкаре-Биркгофа-Витта алгебр $U\left(\frak{n}_c^{+}\right)$ и
-$U\left( \mathfrak{a}_{\bot} \right)$. Чтобы рассмотреть такое пространство как  $%
-\mathfrak{g}$-модуль мы должны выполнить деформацию \cite
-{Nijenhuis1966Richardson} алгебры $\frak{n}_c^{+}$ (то есть восстановить первоначальный закон композиции).
-Пространство сохраняется, и после такой деформации генераторы начальной алгебры будут действовать на нем правильным образом.
-
-\section{Сплинты и ветвления}
-\label{sec:splints}
-
-%%\newtheorem{Def}{Definition}[section]
-%%\newtheorem{Cnj}[Def]{Conjecture}
-%%\newtheorem{Prop}[Def]{Property}
-%%\newtheorem{example}{Example}[section]
-%%
-%\input{tcilatex}
-
-\begin{abstract}
-Splint of root system for simple Lie algebra appears naturally in
-studies of (regular) embeddings of reductive subalgebras. Splint can
-be used to construct branching rules. We demonstrate that 
-splint properties implementation drastically simplify calculations of
-branching coefficients.
-\end{abstract}
-
-\section{Introduction}
-\label{sec:Introduction}
-
-Embedding $\phi$ of a root system $\Delta_1$ into a root system
-$\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
-subset of $\Delta$ that commutes with vector composition law in
-$\Delta_{1}$ and $\Delta$.
-\begin{equation*}
-\phi:\Delta_1 \longrightarrow \Delta
-\end{equation*}
-\begin{equation*}
-\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
-\,\,\, \alpha,\beta \in \Delta_1
-\end{equation*}
-
-Note that the image $Im(\phi)$ must not inherit the root system
-properties except the addition rules equivalent to the addition
-rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
-can splinter $\Delta$  when the latter can be presented 
-as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.   
-The term {\it splint} was
-introduced by D. Richter in  \cite{richter2008splints} where the
-classification of splints for simple Lie algebras was obtained.
-There was also mentioned that splint must have tight
-connections with the injection fan construction. The fan $\Gamma
-\subset \Delta$ was
-introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent
-properties of branching coefficients for maximal embeddings. Injection fan is an
-efficient tool to study branching rules. Later this construction
-was generalized to non-maximal embeddings and infinite-dimensional
-Lie algebras in \cite{2010arXiv1007.0318L, ilyin812pbc}.
-
-In the present paper we study connections between splint and
-injection fan for regular embedding of reductive subalgebras
-${\mathfrak a}$ in simple Lie algebra $\mathfrak{g}$. We show that (under
-certain conditions described in section \ref{sec:stems and
-multiplicity functions}) splint is a natural tool to study
-reduction properties of ${\mathfrak g}$-modules
-with respect to a subalgebra ${\mathfrak a}\longrightarrow
-{\mathfrak g}$. Using this tool we obtain the main result -- the one-to-one correspondence between weight
-multiplicities in irreducible modules of splint and branching
-coefficients for a reduced module $L^{\mu}_{{\mathfrak
-g}\downarrow {\mathfrak a}}$.
-
-\section{Injections and splints}
-
-\label{sec:Injections and splints}
-
-Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
-\mathfrak{a}\hookrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
-is a
-reductive subalgebra $\mathfrak{a \subset g}$ with correlated root spaces: $%
-\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset \mathfrak{h}_{\mathfrak{g }%
-}^{\ast }$. Let $\mathfrak{a}^{\mathfrak{s}}$ be a semisimple summand of
-$\mathfrak{a}$,
-this means that $\mathfrak{a}=\mathfrak{a}^{\mathfrak{s}} \oplus \mathfrak{u}(1)\oplus %
-\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^{\mathfrak{s}}$
-to be a proper regular subalgebra and $\mathfrak{a}$ to be the
-maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed that is the rank
-$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
-
-The following notations are used:
-
-$r$ , $\left( r_{\mathfrak{a}^{\mathfrak{s}}}\right) $ --- the rank of
-$\frak{g}$ $\left( \mathrm{{resp. }\mathfrak{a}^{\mathfrak{s}}}\right) $ ;
-
-$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system;
-$\Delta ^{+} $ $\left( \mathrm{{resp. }\Delta
-_{\frak{a}}^{+}}\right) $--- the positive root system (of
-$\frak{g}$ and $\frak{a}$ respectively);
-
-$S \, ,\quad \left( S_{\frak{a}}\right) $ --- the system of simple roots (of $%
-\frak{g}$ and $\frak{a}$ respectively);
-
-$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
-i$-th (resp. $j$-th) simple root for $\frak{g}$  $\left( \mathrm{{resp. \,} \frak{%
-a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
-^S}\right) $;
-
-$\omega _{i}$ , $\left( \omega _{\left( \frak{a}\right) j}\right) $ --- the $%
-i$-th (resp. $j$-th) fundamental weight for $\frak{g}$ $\left( \mathrm{{resp. \,}\frak{%
-a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
-^S}\right) $;
-
-$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
-
-$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
-
-$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
-fundamental Weyl chamber;
-
-$\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;
-
-$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
-
-$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
-of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
--module with the highest weight $\nu $ );
-
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
-the weight diagram of $L^{\mu }$ (resp. ${}L_{\frak{a}}^{\nu }$ );
-
-$P$ (resp. $P_{\frak{a}} $) \ --- the weight lattice;
-
-$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight lattice;
-
-$\mathcal{E}$ (resp. $\mathcal{E}_{\frak{a}} $) \ --- the formal algebra;
-
-$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
-}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
-resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
-L_{\frak{a}}^{\nu } $);
-
-$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\frak{a}}^{\nu
-}\right) $)--- the formal character of $L^{\mu }$ (resp. $L_{\frak{a}}^{\nu
-} $);
-
-$ch\left( L^{\mu }\right)  =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
-+\rho )-\rho }} {\prod_{\alpha \in \Delta ^{+}} \left( 1-e^{-\alpha }\right)
-} $ --- the Weyl formula;
-
-$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) \quad $
-(resp. $R_{\frak{a}}: =\prod_{\alpha \in \Delta_{\frak{a}}^{+}} \left(
-1-e^{-\alpha }\right) $ ) --- the Weyl denominator.
-
-Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
-\[
-L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
-}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
-\]
-\begin{equation}
-\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
-}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
-\label{branching1}
-\end{equation}
-For the modules we are interested in the Weyl formula for $\mathrm{ch}\left(
-L^{\mu }\right) $ can be written in terms of singular elements \cite
-{humphreys1997introduction}
-\[
-\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
-)-\rho },
-\]
-namely,
-\begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
-^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
-\label{Weyl-Kac2}
-\end{equation}
-The same is true for submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
-}\right) $ in (\ref{branching1})
-\[
-\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
-\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
-}^{\left( \nu \right) }}{R_{\frak{a}}},
-\]
-with
-\[
-\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
-}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
-\]
-
-Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
-we get a relation connecting the singular elements $\Psi ^{\left( \mu
-\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
-\begin{eqnarray}
-\frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho )-\rho }}{\prod_{\alpha \in
-\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
-}^{(\mu )}\frac{\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{%
-\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
-}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:4} \\
-\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\frak{a}%
-}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}}^{\left( \nu \right) }}{R_{%
-\frak{a}}}.  \label{singular main}
-\end{eqnarray}
-
-In \cite{2010arXiv1007.0318L} it was proven that branching coefficients $%
-b_{\xi }^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
-\hookrightarrow \frak{g}$ are subject to the set of recurrent relations:
-\begin{equation}
-\begin{array}{c}
-b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
-_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
-\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right. \\
-\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
-}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
-}\right) .
-\end{array}
-\label{recurrent rel}
-\end{equation}
-where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $%
-\frak{g}$ orthogonal to roots of $\frak{a}$ and $W_{\perp}$ is a Weyl group of $\mathfrak{a}_{\perp}$
-\begin{eqnarray}
-\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
-h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
-\label{delta a ort}
-\end{eqnarray}
-\begin{eqnarray}
-\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
-\qquad \widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }
-\end{eqnarray}
-and $\pi$ is the projection operator. When an injection is maximal the
-projection becomes trivial and the relation (\ref{recurrent rel}) is
-simplified:
-\begin{equation}
-\begin{array}{c}
-b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
-}+\right. \\
-\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
-\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
-\end{array}
-\label{recurrent relation max}
-\end{equation}
-The recursion is goverened by the set $\Gamma _{\frak{a}\rightarrow \frak{g}}
-$ called the injection fan. The latter is defined by the carrier set $%
-\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the coefficient
-function $s(\xi )$
-\[
-\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{ \xi \in P_{%
-\frak{a}}|s(\xi )\neq 0\right\}
-\]
-appearing in the expansion
-\begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\frak{a}}^{+}}\left( 1-e^{
--\alpha }\right) =-\sum_{\gamma \in P_{\frak{a}}}s(\gamma )e^{-\gamma };\quad
-\label{product}
-\end{equation}
-
-Now we remind two definitions introduced in \cite{richter2008splints}
-
-\begin{Def}
-Suppose $\Delta _{0}$ and $\Delta $ are root systems with corresponding
-weight lattices $P_{0}$ and $P$. Then $\phi $ is an ``embedding'',
-\begin{equation}
-\phi :\left\{
-\begin{array}{l}
-\Delta _{0}\hookrightarrow \Delta , \\
-P_{0}\hookrightarrow P,
-\end{array}
-\right.
-\end{equation}
-if \newline
-\noindent (a) it injects $\Delta _{0}$ in $\Delta $, and \newline
-\noindent (b) acts homomorphically with respect to the vector groups in $%
-P_{0}$ and $P$:
-\[
-\phi (\gamma )=\phi (\alpha )+\phi (\beta )
-\]
-for any triple $\alpha ,\beta ,\gamma \in P_{0}$ such that $\gamma =\alpha
-+\beta $.
-\end{Def}
-
-$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
-\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
-_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
-\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
-
-Notice that one must distinguish two classes of embeddings: when the scalar
-product (defined by the Killing form) in the root space $P_0$ is invariant
-with respect to $\phi$ and when it is not $\phi$-invariant. The first
-embedding is called "metric" , the second -- "nonmetric".
-
-\begin{Def}
-A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if
-there are two embeddings $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
-\phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the
-disjoint union of the images of $\phi _{1}$ and $\phi _{2}$ and (b) neither
-the rank of $\Delta _{1}$ nor the rank of $\Delta _{2}$ exceeds the rank of $%
-\Delta $.
-\end{Def}
-
-It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$
-and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$. Each
-component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $%
-(\Delta_1,\Delta_2)$.
-
-To study relations between injection fan technique and splint let us 
-consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ 
-is a root subsystem.
-
-Splint $\Delta \approx (\Delta _{1},\Delta _{2})$ is called ''injective'' if
-$\Delta _{1}=\Delta _{\frak{a}}$, is a root subsystem
-in $\Delta $ corresponding to a regular reductive subalgebra $\frak{a}%
-\hookrightarrow \frak{g}$.
-
-In case of injective splint the second stem $\Delta _{\frak{s}}:=\Delta
-_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product (%
-\ref{product}) and it defines an injection fan $\Gamma _{\frak{a}%
-\hookrightarrow \frak{g}}$. Denote by $\Delta_{\mathfrak{s}0}$ the coimage of the second embedding $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\mathfrak{g}}$.
-The following conjecture follows.
-
-\begin{Cnj}
-Each injective splint $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
-$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\frak{a}%
-\rightarrow \frak{g}}$ fixed by the product
-\begin{equation}
-\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)
-=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
-\end{equation}
-\end{Cnj}
-
-In case of injective splint we say that subalgebra $\frak{a}\hookrightarrow \frak{g}$
-splinters $\Delta $ (and call $\frak{a}$ the ''splinting subalgebra'' of $%
-\frak{g}$). In \cite{richter2008splints} splints are classified (see Appendix there)
-and the first three types of them are injective.
-
-\section{How stems define multiplicity functions}
-
-\label{sec:stems and multiplicity functions}
-
-In this Section we study properties of injective splints  $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
-$. It will
-be demonstrated that in this case to find branching
-coefficients for a splinting injection $\frak{a}\hookrightarrow
-\frak{g}$ means to find weight multiplicities of an irreducible
-$\frak{s}$-module $L_{\frak{s}}^{\nu }$ with fixed highest weight
-$\nu $. Notice that $\frak{s}$ must not be a subalgebra of
-$\frak{g}$.
-
-Let us return to relation (\ref{singular main}) and multiply both sides by $%
-R_{\frak{a}}$:
-\begin{equation}
-\frac{1}{\prod_{\beta \in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })}\Psi _{%
-\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
-}^{(\mu )}\Psi _{\frak{a}}^{\left( \nu \right) }.
-\label{singular main-2}
-\end{equation}
-Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{%
-\frak{a}\rightarrow \frak{g}}$. Consider the highest weight module $L_{\frak{%
-s}}^{\nu }$. The embedding $\phi :\Delta _{\frak{s}\,0}\longrightarrow \Delta
-_{\frak{g}}$ sends the singular element $\Psi _{\frak{s}}^{\left( \nu
-\right) }$ into $\Psi _{\frak{g}}^{\left( \mu \right) }$. Applying the
-inverse morphism $\phi ^{-1}$ to the product $\left( \prod_{\beta \in \Delta
-_{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\frak{s}%
-}^{\left( \nu \right) }\right) $ one gets the character of the module $L_{%
-\frak{s}}^{\nu }$,
-
-\begin{equation}
-\phi ^{-1}\left( \frac{1}{\prod_{\beta \in \Delta _{\frak{s}%
-}^{+}}(1-e^{-\beta })}\phi \left( \Psi _{\frak{s}}^{\left( \nu \right)
-}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\frak{s}0
-}^{+}}(1-e^{-\beta })}\Psi _{\frak{s}}^{\left( \nu \right) }=\mathrm{ch}%
-\left( L_{\frak{s}}^{\nu }\right) .  \label{inverse for stem}
-\end{equation}
-Our task is to prove that the singular element $\Psi _{\frak{g}}^{\left( \mu
-\right) }$ contains the element $\Psi _{\frak{s}}^{\left( \xi \right) }$ for
-a module $L_{\frak{s}}^{\xi }$ uniquely defined by $L_{\frak{g}}^{\mu }$ and
-that the branching coefficients $b_{\nu }^{(\mu )}$ in the r.h.s. of (\ref
-{singular main-2}) coincide with multiplicities $m_{\zeta }^{\left( \xi
-\right) }$ of the corresponding weights in $\mathcal{N}_{\frak{s}}^{\xi }$ .
-
-For a highest weight irreducible module $L_{\frak{g}}^{\mu }$ the singular
-element $\Psi _{\frak{g}}^{\left( \mu \right) }$ is an element of $\mathcal{E%
-}$ corresponding to the shifted Weyl-orbit of the weight $\left( \mu +\rho
-\right) \in P^{+}$ with the sign function $\epsilon \left( w\right) $. It is
-convenient to use also unshifted singular elements
-\begin{equation}
-\Phi ^{\left( \mu \right) }:=\Psi ^{\left( \mu \right) }e^{\rho }.
-\label{definition Phi}
-\end{equation}
-In these terms the relation (\ref{singular main-2}) looks like
-\begin{equation}
-\frac{e^{\rho _{\frak{g}}-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{%
-s}}^{+}}(1-e^{-\beta })}\Phi _{\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in
-P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\Phi _{\frak{a}}^{\left( \nu \right) }.
-\label{singular main-3}
-\end{equation}
-The orbit related to $\Phi _{\frak{g}}^{\left( \mu \right) }$ is completely
-defined by the set of edges $\left\{ \lambda _{i}\right\} _{i=1,\dots ,r}$
-adjusted to the end of the highest weight vector $\mu +\rho $. For $\mu
-=\sum m_{i}\omega _{i}$ these edges are
-\begin{equation}
-\lambda _{i}=-\left( m_{i}+1\right) \alpha _{i},\quad i=1,\dots ,r.
-\label{edge}
-\end{equation}
-Each formal exponent $e^{\mu +\rho +\lambda _{i}}$ in $\Phi _{\frak{g}%
-}^{\left( \mu \right) }$ bears the sign coefficient $\epsilon =(-)$. The
-defining property of $\Phi _{\frak{g}}^{\left( \mu \right) }$ is as follows.
-Consider any pair of edges $\lambda _{i},\lambda _{j}$ and the corresponding
-weights $\mu +\rho $, $\mu +\rho +\lambda _{i}$ and $\mu +\rho +\lambda _{j}$. 
-Apply the reflection $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
-\begin{equation}
-s_{\alpha _{i}}\circ \left\{
-\begin{array}{l}
-\left( \mu +\rho \right)  \\
-\left( \mu +\rho +\lambda _{i}\right)  \\
-\left( \mu +\rho +\lambda _{j}\right)
-\end{array}
-\right. =\left\{
-\begin{array}{l}
-\left( \mu +\rho +\lambda _{i}\right)  \\
-\left( \mu +\rho \right)  \\
-\left( \mu +\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha
-_{j}\right)
-\end{array}
-\right.   \label{reflected triple}
-\end{equation}
-
-\begin{Prop}
-The edge $\lambda _{i,j}$ of $\Phi _{\frak{g}}^{\left( \mu \right) }$
-starting at the weight $\left( \mu +\rho +\lambda _{i}\right) $ along the
-root $-s_{\alpha _{i}}\circ \alpha _{j}$ has the same length in $(s_{\alpha
-_{i}}\circ \alpha _{j})$ as $\lambda _{j}$ has in $\alpha _{j}$. (The same
-is true for the edge $\lambda _{j,i}$, its length in $(s_{\alpha _{j}}\circ
-\alpha _{i})$ is equal to the length of $\lambda _{i}$ in $\alpha _{i}$.)
-\label{diagram property}
-\end{Prop}
-
-In $\Phi _{\frak{g}}^{\left( \mu \right) }$ the elements $e^{\left( \mu
-+\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha _{j}\right) }$ and $%
-e^{\left( \mu +\rho +\lambda _{j}-(m_{i}+1)s_{\alpha _{j}}\circ \alpha
-_{i}\right) }$ have the sign coefficient  $\epsilon =(+)$.
-
-Remember that only three types of splints are
-injective and thus are naturally connected with branching. Below we
-reproduce the part of the splints table from \cite{richter2008splints} corresponding to
-injective splints:
-\[
-\begin{array}{cc||c|c}
-\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
-_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
-\\ \hline\hline
-\hbox{(i)} & G_{2} & A_{2} & A_{2} \\
-& F_{4} & D_{4} & D_{4} \\ \hline
-\hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
-& C_{r}(r\geq 3) & D_{r} & \oplus ^{r}A_{1} \\ \hline
-\hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
-^{r}A_{1} \\
-& B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
-\end{array}
-\]
-Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\frak{s}})
-$ of the simple root system $\Delta $. In the first two types both $\Delta _{%
-\frak{a}}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
-first type splints are equivalent and in the second are not. In the third
-type splints only $\Delta _{\frak{a}}$ is embedded metrically. The summands $%
-u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$. This does not change
-the principle properties of branching but makes it possible to use the
-multiplicities of $\frak{s}$-modules without further projecting their
-weights.
-
-Splints induce a decomposition of the set $S=S_{\frak{c}}\cup S_{\frak{d}}$
-with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}}$. 
-It is easy to check that for any injective splint the subset $S_{%
-\frak{d}}$ is nonempty. It follows that in the set $\left\{ \lambda
-_{i}\right\} _{i=1,\dots ,r}$ one can always find simple roots $\beta
-_{k}\in \Delta _{\frak{s}}$ and that the orbit corresponding to $\Phi _{%
-\frak{g}}^{\left( \mu \right) }$ contains the edges
-\begin{equation}
-\lambda _{k}=-\left( m_{k}+1\right) \beta _{k}  \label{beta edge}
-\end{equation}
-attached to the weight $\mu +\rho $. As far as $\Delta _{\frak{a}}$ is a
-root system and for any pair of simple roots from $S_{\frak{c}}$ the
-property \ref{diagram property} is fulfilled, the element $\Phi _{\frak{g}%
-}^{\left( \mu \right) }$ being a singular element for a set of $\frak{a}$%
--modules. Consider $\beta _{l}\in \Delta _{\frak{s}}$ whose coimage in $%
-\Delta _{\frak{s}0}$ is simple. In Appendix it is shown that for any such $%
-\beta _{l}$ there exists a root $\alpha _{l}\in S_{\frak{c}}$ such that
-$\beta _{l}=\alpha _{l}+\beta _{k}$. It is easily seen that the
-corresponding edge intersects the boundary plane of the fundamental chamber $%
-\bar{C_{\frak{a}}}$ orthogonal to the root $\alpha _{l}$,
-\begin{equation}
-s_{\alpha _{l}}\left( \mu +\rho -p\beta _{l}\right) =s_{\alpha _{l}}\left(
-\mu +\rho \right) -ps_{\alpha _{l}}\beta _{l}=\mu +\rho -p\beta _{l},
-\label{intersection}
-\end{equation}
-\begin{equation}
-\mu +\rho -s_{\alpha _{l}}\left( \mu +\rho \right) =\left( m_{l}+1\right)
-\alpha _{l}=\left( m_{l}+1\right) \beta _{l}-\left( m_{l}+1\right) \beta
-_{k}=p\beta _{l}-ps_{\alpha _{l}}\beta _{l}.  
-\label{intersection-2}
-\end{equation}
-It follows that $p=\left( m_{l}+1\right) $ and $s_{\alpha _{l}}\beta
-_{l}=\beta _{k}$. Now apply the operator $s_{\beta _{k}}$ and find that the
-edge along the root $s_{\beta _{k}}\alpha _{l}$ attached at the weight $%
-s_{\beta _{k}}(\mu +\rho )$ is also equal to $-ps_{\beta _{k}}\alpha _{l}$.
-This means that for the triple of roots $\beta _{k},\beta _{l}$ and $%
-s_{\beta _{k}}\alpha _{l}$ in $\Delta _{\frak{s}}$ the edges $\lambda
-_{k}=-\left( m_{k}+1\right) \beta _{k}$, $\lambda _{l}=-\left(
-m_{l}+1\right) \beta _{l}$ and $\lambda _{kl}=-\left( m_{l}+1\right)
-s_{\beta _{k}}\alpha _{l}$ demonstrate the property \ref{diagram property}.
-One can continue this procedure further in the 2-dimensional subspace fixed
-by the roots $\beta _{k}$ and $\beta _{l}$ and find the set of formal
-exponents that being supplied with the corresponding sign factors compose
-the coimage of the singular element of a module for the subalgebra in $\frak{%
-s}$ (this subalgebra has rank $r=2$).
-
-The same can be proven for any positive root $\beta _{l}\in \Delta $ that is
-simple in $\Delta _{\frak{s}0}$ and correspondingly for any $r=2$ subalgebra
-in $\frak{s}$. The latter means that to ''find'' a singular element of $%
-\frak{s}$-module in $\Phi _{\frak{g}}^{\left( \mu \right) }$ it is necessary
-to incorporate in it additional formal elements $\left\{ -e^{\mu +\rho
--\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\}.$ This
-fixes the starting edges of the diagram $\phi ^{-1}\left( \Phi _{\frak{s}}^{%
-\widetilde{\mu }}\right) $. As it follows from the reconstruction procedure
-the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $%
-, they have the same Dynkin numbers:
-\begin{equation}
-\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
-m_{k}\widetilde{\omega }_{k} . \label{new h weight}
-\end{equation}
-The next step is to construct the full $W_{\frak{s}}$-orbit $\Phi _{\frak{s}%
-}^{\left( \widetilde{\mu }\right) }$  in $P_{\frak{s}}$. It is easily seen
-that its coimage belongs to $\bar{C_{\frak{a}}}$ and that the set $\phi
-^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) \setminus \Phi _{%
-\frak{g}}^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ corresponds to the
-weights belonging to the boundary $\bar{C_{\frak{a}}}$ (including the subset
-$\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{%
-\frak{c}}\right\} $). Thus we have constructed all the formal elements\ with
-the appropriate sign factors that after being added to $\Phi _{\frak{g}%
-}^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ form the diagram $\phi
-^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) $ in $\bar{C_{\frak{a}%
-}}$.
-
-Now let us return to relation (\ref{singular main-3}). One can add to $%
-\Phi _{\frak{g}}^{\left( \mu \right) }$ pairs of formal elements
-constructed above  with the opposite signs: $\epsilon \left( w\right)
-|_{w\in W_{\frak{s}}}$ and $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$. 
-Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ to
-the elements whose weights we shall attribute to $\bar{C_{\frak{a}}}$. 
-The same elements with the opposite signs are to be referred to the
-neighboring Weyl chambers of $\bar{C_{\frak{a}}^{(l)}}$ (the latter are
-connected with the main one via simple reflections $s_{\alpha _{l}}$ so the
-signes $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ are natural for
-them). In fact one can repeat the procedure and find additional singular
-weights in any Weyl chamber $\bar{C_{\frak{a}}^{(m)}}$ and in them
-additional singular weights always have the signs opposite to that in their
-nearest neighbors. Thus without changing the element $\Phi _{\frak{g}%
-}^{\left( \mu \right) }$ one can present it as a sum
-\begin{equation}
-\Phi _{\frak{g}}^{\left( \mu \right) }=\sum_{w\in W_{\frak{a}}}w\circ \left(
-e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho _{\frak{s}}}\right)
-\label{singular final}
-\end{equation}
-where the weight $\widetilde{\mu }=\sum m_{k}\omega _{\frak{s}}^{k}$ was
-defined above. The decomposition (\ref{singular final}) provides the
-possibility to apply the factor $\left( \prod_{\beta \in \Delta _{\frak{s}%
-}^{+}}(1-e^{-\beta })\right) ^{-1}$ to each summand of the singular element $%
-\Phi _{\frak{g}}^{\left( \mu \right) }$ separately because the sets of
-weights from different Weyl summands do not intersect. Taking into account
-the isomorphism $\phi $ one can see that in the main Weyl chamber $\bar{C_{%
-\frak{a}}}$ the set of weights generated by the factor $\left( \prod_{\beta
-\in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}$ is isomorphic to
-the weight diagram $\mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ of the $\frak{%
-s}$-module $L_{\frak{s}}^{\widetilde{\mu }}$. Now one can restrict
-relation (\ref{singular main-3}) to $\bar{C_{\frak{a}}}$ and obtain the main
-result:
-\begin{Prop}
-\begin{equation}
-\frac{e^{\rho _{\frak{g}}}}{\prod_{\beta \in \Delta _{\frak{s}%
-}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
-}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }%
-}}M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
-\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
-}=\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
-\label{singular main-4}
-\end{equation}
-Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
-highest weights in the decomposition. The multiplicity $M_{\left( \frak{s}%
-\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
-}\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ defines the branching
-coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
--\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
-\[
-b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
-}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}.
-\]
-\end{Prop}
-
-\section{Examples}
-\label{sec:examples}
-\begin{example}
-  Consider the Lie algebra $A_{2} =\bf{sl}(3)$ and branching of its irreducible module $L^{[3,2]}_{A_{2}}$ with respect to the reductive subalgebra $A_{1}\oplus u(1)$.
-The root system  $\Delta _{\frak{a}}= \Delta_{A_{1}\oplus u(1)}$ contains the simple root of $\alpha_1=e_1-e_2$ of $A_{2}$.
-The singular element $\Psi^{[3,2]}_{\frak{a}}$ is decomposed into a sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules.
-Branching coefficients $b_{\nu }^{[ 3,2 ] }$ coincide with weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module (see Fig.
-\ref{fig:a2_splint}).
-
-  \begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=80mm]{a2-a1}
-  }
-  \caption{Weyl group orbit (dotted) producing singular element of $L^{[3,2]}_{A_{2}}$ and its decomposition into the sum of splint images of singular elements of modules  $L^{[3,2]}_{A_{1}\oplus A_{1}}$ (dashed).
-Weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}
-
- \label{fig:a2_splint}
-\end{figure}
-\end{example}
-\begin{example}
-  For the Lie algebra $B_{2}= \bf{so}(5)$ branching of its irreducible module $L^{[3,2]}$ into  modules of a reductive subalgebra $A_{1}\oplus u(1)$ with the root system spanned by the first simple root $\alpha_1=e_1-e_2$ of $B_{2}$.
-Singular element of $\Psi^{[3,2]}_{B_{2}}$ is decomposed into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide with weight multiplicities of $A_{2}$-module (see Fig.
-\ref{fig:b2_splint}).
-
-  \begin{figure}[h!bt]
-  \hspace*{-1.2cm}
-
-   \includegraphics[width=65mm]{b2}
-   \includegraphics[width=65mm]{b2-a2-a1}
-  \caption{Weights of the $B_{2}$-module $L^{[3,2]}$ are indicated by dots in the left picture (their multiplicities are also indicated).
-Contour of the singular element is shown by dotted line.
-The right picture presents the decomposition of  $\Psi_{B_{2}}(L^{[3,2]}_{B_{2}})$-singular element into the sum of splint images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ (dashed).
-Weight multiplicities of $L^{[3,2]}_{A_{2}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{B_{2}\downarrow A_{1}\oplus u(1)}$.}
-
- \label{fig:b2_splint}
-\end{figure}
-\end{example}
-
-\vspace{10mm}
-\begin{example}
-   Lie algebra $G_{2}$ has a regular subalgebra $A_{2}$ with root system $\Delta_{\mathfrak{a}}=\Delta_{A_{2}}$ containing the $G_{2}$ long roots.
-Consider branching of an irreducible module $L_{G_{2}}^{(3,2)}$ into the $A_{2}$-modules.
-Singular element $\Psi_{G_{2}}(L^{[3,2]})$ is decomposed into the sum of splint images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ and the corresponding branching coefficients coincide with weight multiplicities of $L^{[3,2]}_{A_{2}}$-module (see Fig.
-\ref{fig:g2_splint}).
-
-  \begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=120mm]{g2}
-  }
-
-  \caption{Weyl group orbit (dotted) for the singular element $\Psi_{G_{2}}(L^{[3,2]})$ and its decomposition into the sum of splint images of singular elements of $A_{2}$-modules (dashed).
-Weight multiplicities of $L^{[3,2]}_{A_{2}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{G_{2}\downarrow A_{2}}$.}
-
- \label{fig:g2_splint}
-\end{figure}
-
-\end{example}
-
-\section{Conclusions}
-
-\label{sec:conclusions}It is explicitly demonstrated that splint
-presents a very effective tool to find branching coefficients. In
-particular injective splints provide a possibility to reduce
-branching rules calculations for highest weight modules to a
-determination of weight multiplicities for a module with the same
-Dynkin labels referred to the Lie algebra $\mathfrak{s}$. This algebra
-$\mathfrak{s}$ must not be a subalgebra in the initial $\mathfrak{g}$ , it
-has the same rank $r_{\mathfrak{s}}=r$\ , but obviously less
-"complicated" than $\mathfrak{g}$ -- only a subset of the initial root system is involved in the second stem $\Delta_{\mathfrak{s}}$.
-
-It is significant that for the injections $D_{r}\hookrightarrow B_{r}$ , $%
-D_{r}\hookrightarrow C_{r}$ and $A_{r-1}\oplus u\left( 1\right) \hookrightarrow A_{r}$ splint technique shows
-transparently Gelfand-Tzeytlin rules for branching:  the reduction is
-multiplicity free (all nonzero
-branching coefficients are equal to 1). Here it is an immediate consequence of the
-structure of the second stem being a direct sum of $A_{1}$
-algebras and the fact that the corresponding module
-$L_{\frak{s}}^{\mu }$ is irreducible.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Appendix}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Let us demonstrate that for injective splints of classical Lie
-algebras the following property is valid:
-\begin{Prop}
-Let $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})$ be an
-injective
-splint with the decomposition of simple roots $S=S_{\frak{c}}\cup S_{\frak{d}%
-}$ with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}%
-}$.
-\end{Prop}
-Thus for any simple root $\beta \in S_{\frak{s}}$ there exists the
-pair of
-roots ( $\alpha $ ,$\beta ^{\prime }$) with $\alpha \in $ $S_{\frak{c}%
-},\beta ^{\prime }\in S_{\frak{s}}$ such that $\alpha =\beta
--\beta ^{\prime }$
-
-\begin{itemize}
-\item
-Type 1. $\Delta _{G_{2}}\approx (\Delta _{A_{2}},\Delta
-_{A_{2}}).$
-
- \begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=100mm]{g2-roots}
-  }
-  \caption{Positive roots of $G_{2}$ and formation of singular element $\Phi^{(0)}_{\mathfrak{s}}$ in the main Weyl chamber of $\mathfrak{a}=A_{2}$.}
-\end{figure}
-Here both stems are metric and the corresponding root systems are
-equivalent. In Figure 4 a part of the singular element $\Phi
-_{G_{2}}^{\left( 0\right) }$ is presented. The boundaries of $\bar{C_{\frak{a%
-}}}$ are the dashed lines starting at the center of the singular
-element. It
-contains the edge $\lambda _{2}=-\alpha _{2}=-\beta _{2}$ and the roots $%
--\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3}$ and $ -\beta _{3}$
-($\beta _{3}$ is indicated as $\beta _{l}$). For the root $\beta
-_{1}$ the necessary pair
-is  $(\alpha _{1}, \beta _{2})$: $\alpha _{1}=\beta _{1}-\beta _{2}$. The $%
-\lambda _{2,3}^{\frak{s}}=\beta _{3}$ edge is equal to $\lambda _{1}^{\frak{s%
-}}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ and $m_{1}$ index
-is aquired by the $\frak{s}$-module that also inherit the second
-index $m_{2}$. In this particular
-case they are $m_{1}=m_{2}=0$. The general case with the initial module $%
-L^{\mu }$ and $\mu =m_{1}\omega _{1}+m_{2}\omega _{2}$ can be
-treated in the same way: one finds an edge $\lambda _{2}=-\left(
-m_{2}+1\right) \beta _{2}$ and put $\lambda
-_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$, its end
-belongs to the boundary $\bar{C_{\frak{a}}}$. The reflection
-$s_{\beta
-_{2}} $ sends $\beta _{1}$ to $\beta _{3}$ and the corresponding edge 
-$\lambda _{2,3}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{3}$ has
-the length $\left( m_{1}+1\right) $. Now consider $\lambda _{1}^{\frak{s}}$ (or
-$\lambda _{2,3}^{\frak{s}} $) and $\lambda _{1,3}^{\frak{s}}$ (or
-$\lambda _{2,3,1}^{\frak{s}}$) edges to find that they belong to
-the boundary $\bar{C_{\frak{a}}}$ and the Weyl symmetry predicts
-that $\lambda _{1,3}^{\frak{s}}=-\left( m_{2}+1\right)
-\beta _{3}$ ($\lambda _{2,3,1}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{1}$%
-) . Finally the edge $\lambda _{1,3,2}^{\frak{s}}=-\left(
-m_{1}+1\right) \beta _{2}$ closes the polytope. Its vertices
-correspond to weights of the singular
-element $\Phi _{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{%
-\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
-\widetilde{\mu }+\rho
-_{\frak{s}}\right) }$ of the module $L_{\frak{s}}^{\left( \widetilde{\mu }%
-\right) }$ with $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}%
-\widetilde{\omega }_{2}$. Notice that in this case the sign
-factors can be obtained directly in the initial weight system as
-far as the stem is metric.
-\item
-Type 1. $\Delta _{F_{4}}\approx (\Delta _{D_{4}},\Delta
-_{D_{4}}).$
-
-Both stems are metric here and the corresponding root systems are
-equivalent. The system $\Delta _{D_{4}}$ of the subalgebra
-$\frak{a=}D_{4}$ is formed by the set $\left\{ \pm e_{i}\pm
-e_{j}\right\} _{|i,j=1,\ldots 4,\; i\neq j}.$ The simple roots
-$S_{\frak{c}}$ are $\left\{ e_{2}-e_{3},e_{3}-e_{4}\right\} $ and
-$S_{\frak{d}}=\left\{ e_{4},\frac{1}{2}\left(
-e_{1}-e_{2}-e_{3}-e_{4}\right) \right\} $.
-For a module $L^{\mu }$ with $\mu =\sum m_{k}\omega _{k}$ consider the edge $%
-\lambda _{3}=-\left( m_{3}+1\right) e_{4}=-\left( m_{3}+1\right)
-\beta _{3}$.
- Compose an edge $\lambda _{2}^{\frak{s}}=-\left( \widetilde{m}%
-_{2}+1\right) \beta _{2}$. The necessary pair of roots is $\left(
-\alpha
-_{2}=e_{3}-e_{4},\beta _{3}\right) $. The intersection of $\lambda _{2}^{%
-\frak{s}}$ with the $\alpha _{2}$-boundary of
-$\bar{C_{\frak{a}}}$ fixes
-its length to be $\lambda _{2}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{2}$%
-\ and the length of the edge $\lambda _{3,2}^{\frak{s}}$ is equal
-to that of
-$\lambda _{2}^{\frak{s}}$. Next consider the edge $\lambda _{2}^{\frak{s}%
-}=-\left( m_{2}+1\right) \beta _{2}$ and the pair $\left( \alpha
-_{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $. The length of  
-$\lambda _{1}^{\frak{s}}$ becomes equal to $\lambda
-_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$. Proceed further till the closure of the polytope. 
-The edges looking along the roots of the $\alpha_4$-type, $\alpha _{4}=\beta
-_{4}=$ $\frac{1}{2}\left( e_{1}-e_{2}-e_{3}-e_{4}\right) $, are
-treated similarly and finally the singular element $\Phi
-_{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in
-W_{\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
-\widetilde{\mu }+\rho _{\frak{s}}\right) }$ for the module
-$L_{\frak{s}}^{\left( \widetilde{\mu }\right) }$ with
-$\widetilde{\mu }=\sum m_{k}\widetilde{\omega }_{k}$ is formed in
-$\bar{C_{\frak{a}}}$.
-\item
-Type 2. $\Delta _{B_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
-^{r}A_{1}}). $
-
-Both stems are metric. An injection is fixed by the stem $\Delta
-_{D_{r}}$ simple roots $S_{\frak{a}}=\left\{
-e_{1}-e_{2},e_{2}-e_{3},\ldots
-,e_{r-1}-e_{r},e_{r-1}+e_{r}\right\} $. The second stem
-corresponds to a
-direct sum of algebras $A_{1}$ with the simple roots $S_{\frak{s}%
-}=\left\{ e_{1},e_{2},\ldots ,e_{r-1},e_{r}\right\} $. Consider the edge $%
-\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ (here $\beta
-_{r}=e_{r}$) and $\lambda _{r-1}=-\left(
-\widetilde{m}_{r-1}+1\right) \beta _{r-1}$
-attached to it (here $\beta _{r-1}=e_{r-1}$). The corresponding pair is $%
-\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta _{r-1}=e_{r-1}\right) $.
- The intersection condition fixes the second edge to be $\lambda
-_{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ , it is orthogonal
-to $\beta _{r}$ so the opposite edge has the same length. The
-Dynkin index $m_{r-1}$ now refers
-also to the\ simple root $\beta _{r-1}$. Next consider the obtained edge $%
-\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and $\lambda
-_{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$ to
-fix the index $\widetilde{m}_{r-2}=m_{r-2}$ and the edge
-$\lambda _{r-2}=-\left( m_{r-2}+1\right) \beta _{r-2}$ and so on
-till all the pairs of edges are properly fixed. Finally in
-$\bar{C}_{D_{r}}$ the element $\Phi _{\oplus ^{r}A_{1}}^{\left(
-\widetilde{\mu }\right) }=\sum_{w\in W_{\oplus
-^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+%
-\frac{1}{2}\sum e_{k}\right) }$ can be constructed for the module
-$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
-$\widetilde{\mu }=\sum m_{k}\frac{1}{2}e_{k}$.
-
-\item
-Type 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
-^{r}A_{1}}). $
-
-The situation in this case is eqivalent to the previous one and
-the additional edges are constructed similarly.
-\item
-Type 3 $\Delta _{A_{r}}\approx (\Delta _{A_{r-1}\oplus
-u_{1}},\Delta _{\oplus ^{r}A_{1}}).$
-
-Here only the first stem is metric and it fixes the injection with
-simple roots $S_{\frak{a}}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots
-,e_{r-1}-e_{r}\right\} $. The second stem corresponding to a direct sum of $%
-r$ copies of $A_{1}$ has the simple roots $S_{\frak{s}}=\left\{
-e_{1}-e_{r+1},e_{2}-e_{r+1},\ldots ,e_{r}-e_{r+1}\right\} $.
-Consider the edge $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$
-with $\beta
-_{r}=e_{r}-e_{r+1}$ and $\lambda _{r-1}=-\left( \widetilde{m}%
-_{r-1}+1\right) \beta _{r-1}$ \ with $\beta
-_{r-1}=e_{r-1}-e_{r+1}$ attached to it. Then the corresponding
-pair is $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta
-_{r-1}=e_{r-1}-e_{r+1}\right)$. The intersection with the
-boundary of $\bar{C}_{A_{r-1}}$ orthogonal to $\alpha _{r-1}$
-fixes the second edge to be $\lambda _{r-1}=-\left(
-m_{r-1}+1\right) \beta _{r-1}$. The Dynkin index $m_{r-1}$ is to
-be used for the fundamental weight  $\omega _{r-1}.$ The\
-reflection $s_{\beta _{r}}$ sends $\lambda _{r-1}=-\left(
-m_{r-1}+1\right) \beta _{r-1}$ to $\lambda _{r,r-1}=-\left(
-m_{r-1}+1\right) \beta _{r-1}.$ Next consider the obtained edge
-$\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and
-$\lambda _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$
-with $\beta _{r-2}=e_{r-2}-e_{r+1} $ to obtain the index
-$\widetilde{m}_{r-2}=m_{r-2}$ and the edge $\lambda _{r-2}=-\left(
-m_{r-2}+1\right) \beta _{r-2}$ and so on till all the pairs of
-edges are properly fixed. Finally in $\bar{C}_{D_{r}}$ the element
-$\Phi _{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right)
-}=\sum_{w\in W_{\oplus
-^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+%
-\widetilde{\rho }\right) }$ can be constructed for the module
-$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
-$\widetilde{\mu }=\sum m_{k}\beta _{k}.$ The simplest case
-$\Delta _{A_{2}}\approx (\Delta _{A_{1}\oplus u_{1}},\Delta
-_{A_{1}\oplus A_{1}})$ is presented in Example 4.1 and Figure 1.
-\item
-Type 3 $\Delta _{B_{2}}\approx (\Delta _{A_{1}},\Delta _{A_{2}}).$
-
-This splint is illustrated in Example 4.1 and Figure 1, 
-$S_{A\_1}=\left\{ e_{1}-e_{2}\right\} $, $S_{A\_2}=\left\{
-e_{1},e_{2}\right\} $. The edge $\lambda _{\alpha _{2}}=\lambda
-_{\beta _{2}}=-\left( m_{2}+1\right) \beta _{2}$ is followed by
-$\lambda _{\beta _{1}}=-\left( \widetilde{m}_{1}+1\right) \beta
-_{1}$. Consider the pair $\left( \alpha
-_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right)$. The end of the edge
-$\lambda _{\beta _{1}}$ must indicate a weight
-invariant under the reflexion $s_{\alpha _{1}}$.  Its length is thus fixed: 
-$\lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$. In the
-coimage of
-the second stem, that is in the root system $\Delta_{A_{2}}$, the reflection 
-$s_{\beta _{2}}$ sends $\lambda _{\beta _{1}}=-\left(
-m_{1}+1\right) \beta
-_{1}$ to $\lambda _{2,3}$, thus the latter edge has the same length in $%
-\beta _{3}=e_{1}+e_{3}$, we have $\lambda _{2,3}=-\left(
-m_{1}+1\right)
-\beta _{3}$ with $\beta _{3}=e_{1}+e_{3}$. The irreducible $\frak{s}$%
--module has the highest weight $\widetilde{\mu }=m_{1}\widetilde{\omega }%
-_{1}+m_{2}\widetilde{\omega }_{2}$. In Figure 1 we see the
-details of these relations in a particular case where
-$L_{B_{2}}^{\left[ 3,2\right] }$ is reduced to a subalgebra
-$A_{1}\oplus u\left( 1\right) $ and the
-corresponding highest weights (with their multiplicities) form the diagram $%
-\mathcal{N}_{A_2}^{\left[ 3,2\right] }$ .
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Выводы к первой главе}
+%-----------------------------------------------------------------------------------------------------
 

### 2011-11-24 AffineLieAlgebras/Thesis/3.tex
Thesis partially structure cleaned, some translations in chapter 2.

--- 2011-09-28 AffineLieAlgebras/Thesis/3.tex
@@
-\chapter{Конформная теория поля}
-\label{cha:cft}
+\chapter{Коэффициенты ветвления и обобщенная резольвента Бернштейна-Гельфанда-Гельфанда}
+\label{cha:BGG}
 
-Подробное изложение \cite{difrancesco1997cft}.
+ \section{Обозначения}
 
-\section{Общие свойства}
-\label{sec:cft-general}
-Алгебра Вирасоро. Представления алгебры Вирасоро. Модулярная инвариантность.
+ \label{sec:notation}
+ Пусть $\frak{g}$ и $\frak{a}$ -- (аффинные) алгебры Ли, и существует вложение  $\frak{a}\hookrightarrow \frak{g}$ такое, что  $\frak{a}$ -- редуктивная подалгебра в $\frak{g}$ с согласованным корневым пространством: $\frak{%
+ h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g}}^{\ast }$. Мы используем следующие обозначения:
 
-\section{Модели Весса-Зумино-Новикова-Виттена}
-\label{sec:wzw}
-Связь с аффинными алгебрами Ли.
-Конформные вложения и недиагональные модулярные инварианты.
+ $\frak{g=n}^{-}+\frak{h}+\frak{n}^{+}$ --- разложение Картана;
 
-\section{Coset-модели}
-\label{sec:coset-models}
-Ветвления. Функции ветвления и статсуммы. 
-Калибровочные WZW-модели.
+ $r$ , $\left( r_{\frak{a}}\right) $ --- ранг алгебра $\frak{g}$ $%
+ \left( \mathrm{\text{соотв., }\frak{a}}\right) $ ;
 
-\section{SLE}
-\label{sec:sle}
-SLE на WZW-моделях. Граничные условия. Парафермионы. SLE на coset-моделях.
+ $\Delta $ $\left( \Delta _{\frak{a}}\right) $--- корневая система; $\Delta
+ ^{+} $ $\left( \mathrm{\text{соотв., }\Delta _{\frak{a}}^{+}}\right) $--- набор положительных корней (алгебр $\frak{g}$ и $\frak{a}$ соответственно);
 
+ $\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
+ \alpha \right) \right) $ --- кратность корня $\alpha$ в $%
+ \Delta $ (соотв., в $\left( \Delta _{\frak{a}}\right) $);
+
+ $S\quad \left( S_{\frak{a}}\right) $ --- множество простых корней (для 
+ $\gf$ и $\af$ соответственно);
+
+ $\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ ---  $%
+ i$-й (соотв., $j$-й) простой корень алгебры $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a%
+ }}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+
+ $\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
+ }\right) $-- простой ко-корень для $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a}%
+ }\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+
+ $W$ , $\left( W_{\frak{a}}\right) $--- группа Вейля;
+
+ $C$ , $\left( C_{\frak{a}}\right) $--- фундаментальная камера Вейля;
+
+ $\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- замыкание фундаментальной камеры Вейля;
+
+ $\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;
+
+ $\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- вектор Вейля;
+
+ $L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- интегрируемый модуль  $\frak{g}$ со старшим весом $\mu $\ ; (соотв., интегрируемый $\af$-модуль старшего веса $\nu $);
+
+ $\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
+ весовая диаграмма модуля $L^{\mu }$ (соотв., ${}L_{\frak{a}}^{\nu }$ );
+
+ $P$ (соотв., $P_{\frak{a}} $) \ --- весовая решетка;
+
+ $P^{+}$ (соотв., $P_{\frak{a}}^{+} $) \ --- решетка доминантных весов;
+
+ $m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\zeta }^{\left( \nu \right)
+ }\right) $ --- кратность веса $\xi \in P$ \ $\left( \mathrm{\text{соотв., }\in P_{\frak{a}}}\right) $ в $L^{\mu }$, (соотв., в $\zeta \in
+ L_{\frak{a}}^{\nu } $);
+
+ $ch\left( L^{\mu }\right) $ (соотв., $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+ }\right) $)--- формальный характер $L^{\mu }$ (соответственно, $L_{\frak{a}}^{\nu
+ } $);
+
+ $ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+ +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
+ \mathrm{{mult}\left( \alpha \right) }}}$ --- формула Вейля-Каца;
+
+ $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
+ mult}\left( \alpha \right) }}\quad $ (соотв., $R_{\frak{a}}:=\prod_{\alpha \in
+ \Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}%
+ }\left( \alpha \right) } $)--- знаменатель Вейля.
+
+\section{Конечномерные алгебры Ли}
+\label{sec:finite-dimensional}
+Основные определения: корни, веса, кратности.
+
+\section{Теория представлений аффинных алгебр Ли}
+\label{sec:representation-theory}
+
+\subsection{Алгебра петель и центральное расширение}
+\label{sec:loop-algebra-central-extension}
+
+Определение аффинных алгебр. Корни, веса, кратности. Категория О.
+
+\subsection{Представления аффинных алгебр Ли}
+\label{sec:affine-lie-algebra-representations}
+
+\section{БГГ-резольвента}
+\label{sec:bgg}
+Категория О.
+Резольвента Бернштейна-Гельфанда-Гельфанда для представлений аффинных алгебр Ли. Параболические модули и их связь с подалгебрами и ветвлением.
+
+\begin{abstract}
+Рекуррентные соотношения для коэффициентов ветвления основываются на определенном разложении сингулярного элемента.
+Мы показываем, что такое разложение может использоваться для построения параболических модулей Верма и получения обобщенных формул Вейля-Верма для характеров.
+Также мы демонстрируем, что коэффициенты ветвления определяют обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда.
+\end{abstract}
+
+\subsection{Введение}
+
+\label{sec:introduction}
+Свойства ветвления (аффинных) алгебр Ли важны для приложений в квантовой теории поля (смотри, например, модели конформной теории поля \cite{difrancesco1997cft},\cite{coquereaux2008conformal}).
+В данной работе мы показываем, что ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и демонстрирует свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).
+
+Резольвента для неприводимых модулей в терминах бесконечномерных модулей важна для теории интегрируемых спиновых цепочек \cite{derk1008}.
+В подходе  $\mathcal{Q}$-оператора Бакстера \cite{derk09} общие трансфер-матрицы, соответствующие (обобщенным) модулям Верма, факторизуются в произведение операторов Бакстера.
+Резольвента позволяет вычислить трансфер-матрицы для конечномерных вспомогательных пространств.
+
+Чтобы продемонстрировать связь БГГ резольвенты с ветвлением мы используем рекурсивный подход, представленный в работе \cite
+{2010arXiv1007.0318L} (аналогичный подход для максимальных вложений использовался в работе \cite{ilyin812pbc}).
+Мы рассматриваем подалгебру $\af \hookrightarrow \gf$ вместе с $\afb$ -- ``ортогональным партнером'' $\af$ по отношению к форме Киллинга, а также подалгебру $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$, где $\frak{h}=\frak{\frak{h}_{\af}}\oplus
+\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. Для любой редуктивной подалгебры $\af$ алгебра $\afb\hookrightarrow \gf$ регулярна и редуктивна. Для интегрируемого модуля старшего веса $%
+L^{\left(\mu \right) }$ и ортогональной подалгебры  $\af_{\bot }$ мы рассматриваем сингулярный элемент $\Psi ^{\left( \mu \right) }$ (числитель в формуле Вейля для характеров $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
+\mu \right) }}{\Psi ^{\left( 0\right) }}$, см., например,  \cite
+{humphreys1997introduction}) и знаменатель Вейля $\Psi _{\af_{\bot
+  }}^{\left( 0\right) }$ для ортогонального партнера. В работе показано, что элемент  $\Psi _{\gf%
+}^{\left( \mu \right) }$ может быть разложен в комбинацию числителей Вейля $\Psi _{\af_{\bot }}^{\left( \nu \right) }$, где $\nu \in P_{%
+\mathfrak{a}_{\bot}}^{+}$. Это разложение дает возможность построить множество модулей старшего веса $L_{\afb}%
+^{\mu _{\afb}}$. В том случае, если вложение\ $\af%
+_{\bot }\hookrightarrow \gf$ \ удовлетворяет ``стандартным параболическим'' условиям, эти модули порождают параболические модули Верма $M_{\left(
+\afb \hookrightarrow \gf\right) }^{\mu _{%
+\afb}}$, так что исходный характер $ch\left(
+L^{\mu }\right) $ в итоге раскладывается в знакопеременную сумму таких модулей.
+С другой стороны, если параболическое условие нарушено, конструкция сохраняется и порождает разложение по отношению к набору обобщенных модулей Верма  $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
+\widetilde{\afb}}}$, где $%
+\widetilde{\frak{b}_{\perp }}$ уже не является подалгеброй в $\gf$, а оказывается сжатием $\widetilde{\afb}$.
+
+Некоторые общие свойства предложенного разложения формулируются в терминах  формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''.
+Использование этого инструмента позволило сформулировать простой и явный алгоритм для вычисления правил ветвления, подходящий для произвольной (максимальной или не максимальной) подалгебры в аффинной алгебре Ли \cite{2010arXiv1007.0318L}.
+
+Возможные обобщения полученных результатов обсуждаются в Разделе \ref{sec:conclusions}.
+
+\subsection{Ортогональная подалгебра и сингулярные элементы}
+
+\label{sec:recurr-form-branch}
+
+В этом разделе мы покажем, как рекуррентный подход к проблеме ветвления естественным образом приводит к представлению формального характера $\frak{g}$-модуля в виде комбинации характеров, соответствующих параболическим (обобщенным) модулям Верма.
+Рассмотрим редуктивную алгебру Ли  $\frak{g}$ и ее редуктивную подалгебру $\frak{a}\subset \frak{g}$.
+Пусть  $L^{\mu} $ -- интегрируемый модуль старшего веса алгебры  $\frak{g}$, $\mu \in P^{+}$.  Будем считать  $L^{\mu}$ вполне приводимым по отношению к подалгебре $\frak{a}$,
+\begin{equation*}
+L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
+\end{equation*}
+Это разложение может быть записано в терминах формальных характеров с использованием оператора проекции  $\pi _{\frak{a}}$ (на весовое пространство $\frak{h_{a}}^{\ast }$):
+\begin{equation}
+\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
+\label{branching1}
+\end{equation}
+Для модуля  $L^{\mu }$ существует БГГ резольвента (см. \cite
+{bernstein1976category,bernstein1975differential,bernstein1971structure} и
+\cite{humphreys2008representations}). Все члены фильтрующей последовательности представляются суммами модулей Верма со старшими весами $\nu$, сильно связанными с $\mu$:
+\begin{equation*}
+\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
+W\right\} .
+\end{equation*}
+
+\subsubsection{Ортогональная подалгебра}
+
+Пусть  $\frak{h}_{\frak{a}}$ -- подалгебра Картана в  $\mathfrak{g}$. Для  $\mathfrak{a}\hookrightarrow \frak{g}$ введем ``ортогонального партнера''  $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$.
+
+Рассмотрим корневое подпространство  $\frak{h}_{\perp \frak{a}}^{\ast }$, ортогональное к $\frak{a}$,
+\begin{equation*}
+\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
+h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} ,
+\end{equation*}
+и корни  $\frak{g}$ (соответственно, положительные корни),  ортогональные к $\frak{a}$,
+\begin{eqnarray}
+\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
+h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
+\label{delta a ort} \\
+\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
+}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
+\notag
+\end{eqnarray}
+Обозначим символом  $W_{\frak{a}_{\perp }}$ подгруппу  $W$, порожденную отражениями  $w_{\beta }$ с корнями  $\beta \in \Delta_{\frak{a}_{\perp}}^{+}$.
+Корневая подсистема  $\Delta _{\frak{a}_{\perp }}$ определяет подалгебру  $\frak{a}_{\perp }$, имеющую подалгебру Картана $\frak{h}_{\frak{a}_{\perp }}$.
+Пусть
+\begin{equation*}
+\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
+}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
+h\right) =0\right\};
+\end{equation*}
+выделим в  $\frak{g}$  подалгебры
+\begin{eqnarray}
+\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp },
+\qquad
+\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
+\end{eqnarray}
+Заметим, что  $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ в общем случае не является подалгеброй в $\mathfrak{g}$.
+
+Для подалгебр Картана имеет место разложение
+\begin{equation}
+\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
+\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
+\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
+\frak{h}_{\frak{a}}.
+\end{equation}
+Рассмотрим векторы Вейля  $\rho _{\frak{a}}$ и $\rho _{\frak{a}_{\perp}} $, соответствующие  $\frak{a}$ и $\frak{a}_{\perp }$.
+Введем так называемые ``дефекты'' вложения  $\mathcal{D}_{\frak{a}}$ и $\mathcal{D}_{\frak{a}_{\perp }}$:
+\begin{equation}
+\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho , \qquad
+\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
+_{\perp }}\rho .  \label{defect ort}
+\end{equation}
+Для  $\mu \in P^{+}$ рассмотрим связанные веса  $\left\{\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ и их проекции на $h_{\frak{a}_{\perp }}^{\ast }$, дополнительно сдвинутые на вектор дефекта $-\mathcal{D}_{\frak{a}_{\perp }}$:
+\begin{equation*}
+\mu _{\frak{a}_{\perp }}\left( w\right) :=\pi _{\frak{a}_{\perp }}\left[
+w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad w\in W.
+\end{equation*}
+
+Среди весов  $\left\{ \mu _{\frak{a}_{\perp
+}}\left( w\right) |w\in W\right\} $ всегда можно выбрать те, которые попадают в фундаментальную камеру $\overline{C_{\frak{a}_{\perp }}}$.
+Пусть $U$ -- множество представителей $u$ классов  $W/W_{\frak{a}_{\perp }}$, таких что
+\begin{equation}
+U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
+\overline{C_{\frak{a}_{\perp }}}\right\} \quad .  \label{U-def}
+\end{equation}
+Тогда можно выделить подмножества:
+\begin{equation}
+\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
+\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}%
+_{\perp }},\quad u\in U,  \label{mu-a}
+\end{equation}
+и
+\begin{equation}
+\mu _{\frak{a}_{\perp }}\left( u\right) :=\pi _{\frak{a}_{\perp }}\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U.
+\label{mu-a-tilda}
+\end{equation}
+
+Заметим, что подалгебра  $\mathfrak{a}_{\bot}$ по определению регулярна, так как она построена на подмножестве корней алгебры $\mathfrak{g}$.
+
+Для интересующих нас модулей формула Вейля-Каца для  $\mathrm{ch}\left( L^{\mu }\right) $ может быть записана через сингулярные элементы \cite{humphreys1997introduction},
+\begin{equation*}
+\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
+)-\rho },
+\end{equation*}
+а именно:
+\begin{equation}
+\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
+^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
+\label{Weyl-Kac2}
+\end{equation}
+То же верно и для подмодулей $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $ в формуле (\ref{branching1})
+\begin{equation*}
+\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
+\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
+}^{\left( \nu \right) }}{R_{\frak{a}}},
+\end{equation*}
+где
+\begin{equation*}
+\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
+}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
+\end{equation*}
+Применяя формулу  (\ref{Weyl-Kac2}) к правилу ветвления  (\ref{branching1}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu
+\right) }$ и $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
+\begin{eqnarray}
+\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
+)-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
+(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
+\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
+\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
+mult}_{\frak{a}}(\beta )}},  \notag  \label{eq:4} \\
+\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
+&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
+}^{\left( \nu \right) }}{R_{\frak{a}}}.
+\end{eqnarray}
+
+\subsubsection{Разложение сингулярного элемента.}
+
+\label{subsec:decomp-sing-element}
+
+Теперь мы выполним разложение сингулярного элемента  $\Psi ^{\left(\mu \right) }$ на сингулярные элементы модулей ортогонального партнера:
+
+\begin{lemma}
+
+Пусть  $\frak{a}_{\bot }$ -- ортогональный партнер редуктивной подалгебры  $\frak{a}\hookrightarrow \frak{g}$ и $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$, $\widetilde{%
+\frak{a}_{\perp }}=\frak{a}_{\perp }\oplus \frak{h}_{\perp }$, $%
+\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$.
+
+Пусть $L^{\mu }$ -- интегрируемый модуль старшего веса  $\mu \in P^{+}$ и
+
+$\Psi ^{\left( \mu \right) }$\ -- сингулярный элемент $L^{\mu }$.
+
+Тогда элемент  $\Psi ^{\left( \mu \right) }$ может быть разложен в сумму по  $u\in U$ (см.
+(\ref{U-def})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
+$\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
+\begin{equation}
+\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\widetilde{%
+\mathfrak{a}}}\left( u\right) }\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) }.  \label{sing decomp main}
+\end{equation}
+\label{Psi-decomp-lemma}
+\end{lemma}
+
+\begin{proof}
+Пусть
+\[
+u(\mu +\rho )=\pi _{\left( \aft\right) }u(\mu +\rho )+\pi _{\left(
+\frak{a}_{\perp }\right) }u(\mu +\rho ),
+\]
+где $u\in U$. Для произвольного  $v\in W_{\frak{a}_{\bot }}$ рассмотрим сингулярный вес  $vu(\mu +\rho )-\rho $ и выполним разложение:
+\begin{equation}
+\begin{array}{lcl}
+vu(\mu +\rho )-\rho  & = & \pi _{\left( \frak{a}\right) }\left( u(\mu +\rho
+)\right) -\rho +\rho _{\frak{a}_{\perp }}
+\\
+&  & +\ v\left( \pi _{\left( \aft_{\perp }\right) }u(\mu
++\rho )-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{%
+\frak{a}_{\perp }} .
+\end{array}
+\label{sing-decomp-1}
+\end{equation}
+Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}), чтобы упростить первую строку в формуле (\ref{sing-decomp-1}):
+\[
+\begin{array}{r}
+\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
+\frak{a}_{\perp }}= \\
+\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\pi _{\aft%
+}\rho -\pi _{\af_{\bot }}\rho +\rho _{\frak{a}_{\bot }}= \\
+=\pi _{\left( \aft\right) }\left( u(\mu +\rho )-\rho \right) +\mathcal{D}%
+_{\frak{a}_{\bot }},
+\end{array}
+\]
+и вторую строку
+\[
+\begin{array}{c}
+v\left( \pi _{\left( \frak{a}_{\perp }\right) }u(\mu +\rho
+)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}%
+_{\perp }}= \\
+v\left( \pi _{\left( \frak{a}_{\bot }\right) }u(\mu +\rho )-%
+\mathcal{D}_{\frak{a}_{\bot }}-\pi _{\left( \frak{a}_{\bot }\right) }\rho
++\rho _{\frak{a}_{\bot }}\right)
+-\rho _{\frak{a}_{\bot }}= \\
+=v\left( \pi _{\left( \frak{a}_{\bot }\right) }\left[ u(\mu
++\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\bot }}+\rho _{\frak{a}_{\bot
+}}\right) -\rho _{\frak{a}_{\bot }}.
+\end{array}
+\]
+В результате получаем требуемое разложение сингулярного элемента $\Psi ^{\mu }$ на сингулярные элементы $\Psi_{\frak{a}_{\perp}}^{\eta}$ модулей $L_{\frak{a}_{\perp }}^{\eta }$ подалгебры $\frak{a}_{\perp }$:
+\begin{equation}
+\begin{array}{l}
+\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
+(v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\aft}\left[ u(\mu +\rho )-\rho \right]
++\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{\left( \frak{a}_{\perp }\right) }\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}+\rho _{\frak{a}%
+_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
+=\sum_{u\in U}\;\epsilon (u)\Psi _{\af_{\perp }}^{\pi
+_{\left( \frak{a}_{\perp }\right) }\left[ u(\mu +\rho )-\rho
+\right] -\mathcal{D}_{\frak{a}_{\perp }}}e^{\pi _{\left( \aft\right) }%
+\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}.
+\end{array}
+\label{singular main}
+\end{equation}
+\end{proof}
+
+%\bigskip
+
+\begin{remark}
+Это соотношение можно рассматривать как обобщение формулы Вейля для сингулярного элемента $\Psi _{\frak{g}}^{\mu }$: векторы $\mu _{%
+\widetilde{\mathfrak{a}}}\left( u\right) $ играют роль сингулярных весов, в то время как множители  $\epsilon (u)$ расширены до $\epsilon
+(u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$.
+
+Действительно, при  $\frak{a=g}$ подалгебры  $\frak{a}_{\perp }$, и $\frak{h}_{\perp }$ тривиальны, $U=W$ и оригинальная формула Вейля восстанавливается, так как сингулярные элементы $\epsilon (u)\Psi _{\frak{a}_{\perp %
+}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\epsilon (u)$ становятся  тривиальными.
+
+В противоположном пределе, когда $\frak{a}=0$, $\Delta _{\frak{a}_{\perp }}=\Delta _{\frak{g}}$, $%
+\frak{h}_{\perp }^{\ast }=0$, $\frak{a}_{\perp }=\frak{g}$, $\mathcal{D}_{%
+\frak{a}_{\perp }}=0$ и $U=W/W_{\frak{a}_{\perp }}=e$, вновь приходим к выражению для  сингулярного элемента
+ $\Psi ^{\mu }$, теперь -- в результате тривиализации множества векторов $\mu _{\af}\left( e\right) =0$.
+\end{remark}
+
+\begin{remark}
+
+В работе \cite{2010arXiv1007.0318L} разложение, аналогичное формуле (\ref{singular main}), было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
+\begin{equation}
+\begin{array}{c}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
+\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right.  \\
+\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
+}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
+}\right) .
+\end{array}
+\label{recurrent rel}
+\end{equation}
+Рекурсия задается множеством  $\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}$, которое носит название веера вложения.
+Это множество определяется как носитель  $\left\{ \xi \right\}_{\frak{a}\rightarrow \frak{g}}$  коэффициентной функции $s(\xi )$
+\begin{equation*}
+\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{g}}:=\left\{
+\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\},
+\end{equation*}
+возникающей в разложении 
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
+_{\widetilde{\frak{a}}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
+_{\frak{a}}(\pi _{\widetilde{\frak{a}}}\alpha )}=-\sum_{\gamma \in P_{%
+\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma }.\quad
+\end{equation}
+Веса из множества $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
+g}}$ сдвигаются на $\gamma _{0}$ -- младший вектор в $\left\{ \xi
+\right\} $, и исключается нулевой элемент:
+\begin{equation}
+\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}=\left\{ \xi -\gamma
+_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
+\end{equation}
+
+Рекуррентное соотношение (\ref{recurrent rel}) первоначально использовалось для описания ветвления интегрируемых модулей.
+Заметим, что существует важный класс модулей, которые также могут быть редуцированы при помощи веера вложения -- это модули Верма.
+\end{remark}
+
+\subsubsection{Фомулы Вейля-Верма.}
+
+\begin{statement}
+%\bigskip
+Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характер интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) характеров параболических модулей Верма, распределенных по множеству весов $\mu _{\widetilde{\mathfrak{a}}}\left(
+u\right)$:
+\begin{equation}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{%
+\widetilde{\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) },  \label{gen Weyl-Verma}
+\end{equation}
+где  $U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
+\overline{C_{\frak{a}_{\perp }}}\right\} $ и $I$ -- такое подмножество в  $S$, что $\Delta _{I}^{+}$ эквивалентно $\Delta _{\frak{a}_{\perp }}^{+}$.
+\end{statement}
+
+%\bigskip
+\begin{proof}
+Подалгебра  $\mathfrak{a}_{\bot }$ регулярна и редуктивна по определению  (\ref{delta a ort}). Рассмотрим её знаменатель Вейля   $R_{\frak{a}_{\perp }}:=\prod_{\alpha \in \Delta _{\frak{a}%
+_{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}%
+\mathrm{\left( \alpha \right) }}$ и элемент  $R_{J}:=\prod_{\alpha \in
+\Delta ^{+}\setminus \Delta _{\frak{a}_{\perp }}^{+}}\left( 1-e^{-\alpha
+}\right) ^{\mathrm{mult}(\alpha )}$ как сомножители в $R$:
+\begin{equation*}
+R=R_{J}R_{\frak{a}_{\perp }}.
+\end{equation*}
+Согласно этой факторизации и разложению  (\ref{sing decomp main}) характер $\mathrm{ch}\left( L^{\mu }\right) $ можно переписать в виде
+\begin{eqnarray*}
+\mathrm{ch}\left( L^{\mu }\right) &=&\left( R_{J}\right) ^{-1}\left( R_{%
+\frak{a}_{\perp }}\right) ^{-1}\Psi ^{\mu }=\left( R_{J}\right)
+^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}}\left( u\right) }\epsilon
+(u)\left( R_{\frak{a}_{\perp }}\right) ^{-1}\Psi _{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) } \\
+&=&\left( R_{J}\right) ^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}%
+}\left( u\right) }\epsilon (u)\mathrm{ch}\left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
+}}\left( u\right) }\right),
+\end{eqnarray*}
+где  $\left\{ L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left(
+u\right) }|u\in U\right\} $ -- множество конечномерных $\frak{a}%
+_{\perp }$-модулей со старшими весами   $\mu _{\frak{a}_{\perp }}\left(
+u\right) $.
+Нас интересуют нетривиальные подалгебры $\frak{a}$ и, соответственно, нетривиальные  $\frak{a}_{\perp }$ (случай тривиальной ортогональной подалгебры рассматривался выше в (см.
+Замечание 1)).
+Значит $r_{\frak{a}}\geq 1$ и $r_{\frak{a}%
+_{\perp }}<r$.
+Так как диаграмма Дынкина для любой регулярной подалгебры получается в результате исключения одной, двух или более вершин из расширенной диаграммы Дынкина алгебры, а расширенная диаграмма содержит не более одного зависимого корня (старший корень), множество корней $\Delta _{\frak{a}_{\perp }}^{+}$ всегда эквивалентно некоторому множеству $\Delta _{I}^{+}$, порожденному набором  простых корней $I\subset S $.
+
+Следовательно мы можем (переопределяя множество  $\Delta ^{+}$) отождествить $\Delta _{\frak{a}_{\perp }}^{+}$ с подмножеством  $\Delta _{I}^{+}$, где $I\subset S$.
+В результате мы можем определить объекты, необходимые для построения обобщенных модулей Верма \cite{lepowsky1977generalization,humphreys2008representations}.
+У нас есть два множества корневых векторов $\left\{ x_{\xi }\in \frak{g}_{\xi }|\xi \in \Delta _{I}^{+}\right\}
+$ и $\left\{ x_{\eta }\in \frak{g}_{\eta }|\eta \in \Delta ^{+}\setminus
+\Delta _{I}^{+}\right\} $, и соответствующие нильпотентные подалгебры в  $\frak{n}%
+^{+}$:
+\begin{equation*}
+\frak{n}_{I}^{+}:=\sum_{\xi \in \Delta _{I}^{+}}\frak{g}_{\xi },\quad
+\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\frak{g}%
+_{\eta }.
+\end{equation*}
+Первая подалгебра вместе со своей отрицательной копией  $\frak{n}%
+_{I}^{-} $ порождает простую подалгебру 
+\begin{equation*}
+\frak{s}_{I}=\frak{n}_{I}^{-}+\frak{h}_{I}+\frak{n}_{I}^{+}.
+\end{equation*}
+Мы расширяем ее оставшимися картановскими генераторами:
+\begin{equation*}
+\frak{l}_{I}=\frak{n}_{I}^{-}+\frak{h}+\frak{n}_{I}^{+}.
+\end{equation*}
+Полупрямое произведение  $\frak{l}_{I}$ и $\frak{u}_{I}^{+}$ дает параболическую подалгебру $\frak{p}_{I}\hookrightarrow \frak{g}$ :
+\begin{equation}
+\frak{p}_{I}=\frak{l}_{I}\vartriangleright \frak{u}_{I}^{+}.
+\label{paralolic subalg}
+\end{equation}
+Ее универсальная обертывающая $U\left( \frak{p}_{I}\right) $ является подалгеброй в  $%
+U\left( \frak{g}\right) $. Модули  $L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) }$ алгебры  $\frak{l}_{I}$ легко поднимаются до  $\frak{p}_{I}$-модулей при помощи тривиального действия нильрадикала $\frak{u}_{I}^{+}$.
+Последний стандартным образом индуцирует $U\left( \frak{g}\right) $-модули:
+\begin{equation*}
+M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=U\left( \frak{g}\right)
+\otimes _{U\left( \frak{p}_{I}\right) }L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) }.
+\end{equation*}
+
+Это  \textit{обобщенные модули Верма}  \cite{lepowsky1977generalization},
+порожденные старшими весами  $\mu _{\frak{a}%
+_{\perp }}\left( u\right) $. Как  $U\left( \frak{u}_{I}^{-}\right) $-модуль каждый  $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ изоморфен  $%
+U\left( \frak{u}_{I}^{-}\right) \otimes L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) }$ и его характер можно записать при помощи функции Костанта-Хекмана \cite{KostantHeckman1982}, соответствующей вложению ортогонального партнера $\frak{a}_{\perp
+}\hookrightarrow \frak{g}$:
+\begin{equation*}
+\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\mathcal{KH}_{%
+\frak{a}_{\perp }\hookrightarrow \frak{g}}\mathrm{ch}L_{\frak{a}_{\perp
+}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
+\end{equation*}
+Функция  $\mathcal{KH}_{\frak{a}_{\perp }\hookrightarrow \frak{%
+g}}$ генерируется знаменателем  $R_{I}$, так что последнее выражение можно переписать следующим образом
+\begin{equation*}
+\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\frac{1}{R_{I}}%
+\mathrm{ch}L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
+\end{equation*}
+Таким образом мы получили обобщенную формулу Вейля-Верма для характеров -- разложение  $\mathrm{ch}\left(
+L^{\mu }\right) $ на характеры обобщенных модулей Верма:
+\begin{equation}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
+u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
+u\right) }.  \label{char in gen verma mod}
+\end{equation}
+\end{proof}
+
+\begin{remark}
+Здесь обобщенная формула Вейля-Верма для характеров (называемая формулой переменного суммирования в книге \cite{humphreys2008representations}) имеет специальный вид: веса $\mu _{\aft}$ отличны от старших весов обобщенных модулей Верма $\mu _{\afb}$.
+Причина в том, что старший вес $M_{I}$-модуля не равен проекции его максимального веса на  $h^*_{\afb}$ (он должен быть дополнительно сдвинут на дефект).
+\end{remark}
+
+\begin{example}
+  Рассмотрим обобщенные модули Верма для вложения $A_{1}\hookrightarrow B_{2}$, где подалгебра  $\afb$ связана с корнем  $\alpha_{1}$ алгебры  $B_{2}$.
+Обобщенный модуль Верма $M^{\omega_{1}}_{I}$ со старшим весом   $\omega_{1}=e_{1}$ показан на Рисунке \ref{fig:B2_Verma_Decomp}.
+  \begin{figure}[h!bt]
+  \noindent\centering{
+   \includegraphics[width=120mm]{B2_Gen_Verma_Decomp}
+  }
+  \caption{Обобщенные модули Верма для регулярного вложения  $A_1$ в $B_2$. 
+    Простые корни $\alpha_1, \alpha_2$ алгебры $B_2$ показаны пунктирными стрелками.
+Простой корень  $\beta = \alpha_1+2\alpha_2$ алгебры $A_1$ изображен серым вектором.
+Разложение $L^{\omega_{1}}$ представлено набором контуров входящих в него обобщенных модулей Верма.
+Пунктирные контуры соответствуют положительным значениям  $\epsilon(u)$, а точечные -- отрицательным.
+}
+
+ \label{fig:B2_Verma_Decomp}
+\end{figure}
+
+\end{example}
+
+\begin{remark}
+Как доказано, например, в книге  \cite{humphreys2008representations} (см.
+утверждение 9.6), характеры обобщенных модулей Верма $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ могут также описываться как линейные комбинации обычных модулей Верма алгебры $\frak{g}$:
+\begin{equation*}
+\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\sum_{w\in W_{%
+\frak{a}_{\perp }}}\epsilon \left( w\right) \mathrm{ch}M^{w\left( \mu _{%
+\frak{a}_{\perp }}\left( u\right) +\rho _{\frak{a}_{\perp }}\right) -\rho _{%
+\frak{a}_{\perp }}}
+\end{equation*}
+Подставляя это выражение в формулу (\ref{char in gen verma mod}) и используя определения  (\ref{mu-a},\ref{mu-a-tilda}) и (\ref{defect ort}), мы восстанавливаем стандартное разложение Вейля-Верма для характера:
+\begin{equation*}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{w\in W}\;\epsilon (u)\mathrm{ch}%
+M^{w\left( \mu +\rho \right) -\rho }.
+\end{equation*}
+\end{remark}
+
+\subsection{БГГ резольвента и ветвление}
+В работе \cite{lepowsky1977generalization} показано, что для модуля старшего веса $L^{\mu }$, где $\mu \in P^{+}$, последовательность (обобщенная БГГ резольвента)
+\begin{equation}
+0\rightarrow M_{r}^{I}\overset{\delta _{r}}{\rightarrow }M_{r-1}^{I}\overset{%
+\delta _{r-1}}{\rightarrow }\ldots \overset{\delta _{1}}{\rightarrow }%
+M_{0}^{I}\overset{\varepsilon }{\rightarrow }L^{\mu }\rightarrow 0,
+\label{resolution sequence}
+\end{equation}
+где
+\begin{equation}
+M_{k}^{I}=\bigoplus_{u\in U,\;\mathrm{length}\left( u\right)
+=k}M_{I}^{u\left( \mu +\rho \right) -\rho },\quad M_{0}^{I}=M_{I}^{\mu }
+\label{Verma elements sequence}
+\end{equation}
+является точной и формула (\ref{gen Weyl-Verma}%
+) следует из этого разложения.
+
+\begin{figure}[h!bt]
+ \noindent\centering{
+   \includegraphics[width=140mm]{B2_Exact}}
+ \caption{Вложение $A_1\hookrightarrow B_2$ (см. Рисунок \ref{fig:B2_Verma_Decomp}). Ортогональный партнер, подалгебра $A_1$, соответствует корню $\alpha_1$.
+   Резольвента простого модуля $L^{\omega_1}$. Показана центральная часть точной последовательности
+   $0 \to Im(\delta_2) \to \left( e^{\mu _{\widetilde{%
+\frak{a}}}\left( e\right) }\mathrm{ch}M_{I}^{\pi _{\afb}\left[ \omega_1 \right] -%
+\mathcal{D}_{\afb} }=M^{\omega_1}_{I}\right) \to
+   L^{\omega_1}\to 0 $.  Здесь $\mu _{\widetilde{\frak{a}}}\left( e\right) =\pi _{\aft}\left[ \mu \right] + \mathcal{D}_{\afb}$.
+   }
+\end{figure}
+
+\begin{statement}
+Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра  $\afb\hookrightarrow \frak{g}$ ортогональна редуктивной подалгебре $\frak{a}\hookrightarrow \frak{g}$.
+Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\afb$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к подалгебре $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}$ .
+\end{statement}
+
+\begin{proof}
+Положим
+\begin{equation*}
+\mathrm{ch}M_{I}^{u\left( \mu +\rho \right) -\rho }=e^{\mu _{\widetilde{%
+\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
+u\right) },\mathrm{ch}M_{I}^{\mu }=e^{\mu _{\widetilde{\frak{a}}}\left(
+e\right) }\mathrm{ch}M_{I}^{\pi _{\frak{a}_{\perp }}\left[ \mu \right] -%
+\mathcal{D}_{\frak{a}_{\perp }}},
+\end{equation*}
+где \ $\mu _{\widetilde{\frak{a}}}\left( u\right) ,\mu _{\frak{a}_{\perp
+}}\left( u\right) $ и $\mathcal{D}_{\frak{a}_{\perp }}$ заданы как в Лемме \ref{Psi-decomp-lemma}, $%
+u\in U$ определено формулой (\ref{U-def}). В результате получим элементы фильтрующей последовательности (\ref{resolution sequence}).
+
+Рассмотрим множество $\left\{ \mu _{\frak{a}_{\perp }}\left( u\right) |u\in U\right\} $ как множество старших весов простых модулей $L_{\frak{a}%
+_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ и вычислим размерности этих модулей. Вместе с 
+$\left\{ \mu _{\widetilde{\mathfrak{a}}}\left( u\right) |u\in
+U\right\} $ мы получим набор сингулярных весов
+\begin{equation*}
+\left\{ \epsilon (u)\;
+e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }
+\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
+}}\left( u\right) }\right) \right\} .
+\end{equation*}
+Ветвление  $L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu
+\in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$  определяется веером вложения  $\Gamma _{\frak{a}\rightarrow \frak{g}}$ и соотношением (\ref{recurrent rel}), которое дает нам коэффициенты  $k_{\xi
+}^{\left( \mu \right) }$, а значит определяет и  $b_{\nu }^{\left( \mu \right) }$, так как  $b_{\nu }^{\left( \mu \right) }=k_{\nu }^{\left( \mu
+\right) }$ при $\nu \in \overline{C_{\frak{a}}}$ .
+\end{proof}
+
+\begin{corollary}
+Пусть  $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$ и  $\frak{a}\hookrightarrow \frak{g}$ -- редуктивная подалгебра $\frak{g}$.
+Пусть $\frak{a}_{\perp }$, ортогональный партнер для $\frak{a}$, эквивалентен  $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, и $\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ с $\frak{h=\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$.
+Пусть $L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }=\bigoplus\limits_{\nu \in P_{\widetilde{\frak{a}}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\widetilde{\frak{a}}}^{\nu }$ -- ветвление модуля $L^{\mu }$ относительно подалгебры $\widetilde{\frak{%
+a}}$. Тогда коэффициенты $b_{\nu }^{\left( \mu \right) }$ определяют обобщенную резольвенту (\ref{resolution sequence}) модуля $L^{\mu }$
+по отношению к  $\frak{a}_{\perp }$.
+\end{corollary}
+
+\begin{proof}
+Пусть $\alpha $ -- простой корень  $A_{1}$.
+Используем преобразования из группы Вейля чтобы перевести его в некоторый простой корень алгебры $\frak{g}$, например $\alpha _{1}$.
+Построим сингулярный элемент для модуля  $L_{\frak{g}\downarrow
+\widetilde{\frak{a}}}^{\mu }$, то есть  $\Psi _{\widetilde{\frak{a}}%
+}^{\left( L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }\right)
+}=\sum_{\nu \in P_{\widetilde{\frak{a}}}^{+},b_{\nu }^{\left( \mu \right)
+}>0}b_{\nu }^{\left( \mu \right) }\Psi _{\widetilde{\frak{a}}}^{\left( \nu
+\right) }$, и разложим его $\Psi _{\widetilde{\frak{a}}}^{\left( L_{\frak{%
+g}\downarrow \widetilde{\frak{a}}}^{\mu }\right) }=k_{\xi }^{\left( \mu
+\right) }e^{\xi }$. В нашем случае представители $u$ в рекуррентном соотношении (\ref{recurrent rel}) определяются весом $\xi $ однозначно:
+\begin{equation*}
+\epsilon (u\left( \xi \right) )\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\left( \xi \right) \right) }\right) =-s\left(
+\gamma _{0}\right) k_{\xi }^{\left( \mu \right) }-\sum_{\gamma \in \Gamma _{%
+\widetilde{\frak{a}}\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right)
+k_{\xi +\gamma }^{\left( \mu \right) }.
+\end{equation*}
+Тогда
+\begin{equation*}
+\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\left(
+\xi \right) \right) }\right) =\left| s\left( \gamma _{0}\right) k_{\xi
+}^{\left( \mu \right) }+\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}%
+\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma
+}^{\left( \mu \right) }\right|
+\end{equation*}
+и
+\begin{equation*}
+\mu _{\frak{a}_{\perp }}\left( u\left( \xi \right) \right) =\frac{1}{2}%
+\left( \dim \left( L_{A_{1}}^{\mu \left( \xi \right) }\right) -1\right)
+\alpha _{1}
+\end{equation*}
+Таким образом, множество обобщенных модулей Верма  $e^{\xi +\mathcal{D}%
+_{\frak{a}_{\perp }}}\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
+u\left( \xi \right) \right) }$ полностью фиксировано:
+\begin{equation*}
+\left\{ e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }\mathrm{ch}%
+M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }|u\in U\right\} .
+\end{equation*}
+Упорядочивая эти модули по длине $u$, мы получаем компоненты (\ref{Verma elements sequence}) резольвенты (\ref{resolution sequence}).
+\end{proof}
+
+\subsection{Заключение}
+
+\label{sec:conclusions}
+В работе \cite{2010arXiv1007.0318L} было показано, что метод веера вложения работает также и для специальных вложений.
+Надо заметить, что  разложения Вейля-Верма также могут быть получены в этом случае.
+Резольвенты, соответствующие специальным подалгебрам, описывают соотношения между проекциями характера начального модуля и обобщенными модулями Верма со старшими весами в подпространстве $h^*$.
+
+Рассмотрим ситуацию, когда выбор простых корней зафиксирован какими-то внешними факторами (возникающими, например, из требований физических приложений).
+В этом случае ортогональный партнер не может порождаться только простыми корнями.
+Элементы   $\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta
+^{+}\setminus \Delta _{I}^{+}}\frak{g}_{\eta }$ не образуют подалгебру в  $%
+\mathfrak{g}$, так как некоторые не простые корни отсутствуют в  $\Delta ^{+}\setminus
+\Delta _{I}^{+}$. Важно отметить, что в этом случае формула Вейля-Верма по-прежнему существует. В ней обобщенные модули Верма соответствуют сжатиями \cite{Doebner1967Melsheimer} алгебры $%
+\frak{n}^{+}$ и соотношения Вейля-Верма описывают разложение пространства представления $L^{\mu}$ в набор обобщенных модулей Верма сжатой алгебры  $U\left(\frak{n}_c^{+}\right)$.
+Весовые векторы образованы базисом Пуанкаре-Биркгофа-Витта алгебр $U\left(\frak{n}_c^{+}\right)$ и
+$U\left( \mathfrak{a}_{\bot} \right)$. Чтобы рассмотреть такое пространство как  $%
+\mathfrak{g}$-модуль мы должны выполнить деформацию \cite
+{Nijenhuis1966Richardson} алгебры $\frak{n}_c^{+}$ (то есть восстановить первоначальный закон композиции).
+Пространство сохраняется, и после такой деформации генераторы начальной алгебры будут действовать на нем правильным образом.
+
+%%
+%% End of file
 %%% Local Variables: 
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "thesis"
 %%% End:

### 2011-11-25 AffineLieAlgebras/Thesis/1.tex
More translation in chapter 1.

@@
 Общая идея похожа на подход, предложенный в работе  \cite{ilyin812pbc} для максимальных вложений.
-Но в данном случае алгоритм существенно отличается, так как использует новые свойства сингулярных весов для работы с произвольными редуктивными вложениями $\frak{a} \rightarrow \frak{g}$.
+Но в данном случае алгоритм существенно отличается, так как использует новые свойства сингулярных весов для работы с произвольными редуктивными вложениями $\af \rightarrow \gf$.
 
@@
 $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
-=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
+=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\gf}}{\Psi ^{\left( 0\right) }_{\afb}}$.
 
@@
 $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ допускает разложение на множество числителей Вейля $\Psi ^{\left( \mu \right) }_{ \afb }$ модулей подалгебры $\afb$.
-Это разложение дает возможность построить рекуррентное соотношение для коэффициентов ветвления, соответствующих вложению $\frak{a} \rightarrow \frak{g} $.
+Это разложение дает возможность построить рекуррентное соотношение для коэффициентов ветвления, соответствующих вложению $\af \rightarrow \gf $.
 Рекуррентное соотношение формулируется с использованием особого элемента  $\Gamma_{\af \rightarrow \gf}$ групповой алгебры
-$\mathcal{E}\left( \frak{g} \right)$, который мы называем ``веером вложения''. 
+$\mathcal{E}\left( \gf \right)$, который мы называем ``веером вложения''. 
 Применение этих инструментов позволяет нам сформулировать простой и явный алгоритм для вычисления коэффициентов ветвления, который может быть использован в случае произвольных (максимальных и не максимальных) подалгебр конечномерных и аффинных алгебр Ли.
@@
 %%  
-%%  Consider affine Lie algebras $\frak{g}$ and $\af$ with
+%%  Consider affine Lie algebras $\gf$ and $\af$ with
 %%  underlying finite-dimensional subalgebras $\go$ and $%
@@
 %%  }$ such that $\af$ is a reductive subalgebra $\frak{a\subset g}$ with
-%%  correlated root spaces: $\frak{h}_{\af}^{\ast }\subset \frak{h}_{\frak{g%
-%%  }}^{\ast }$ and $\frak{h}_{\ao}^{\ast }\subset \frak{h%
+%%  correlated root spaces: $\hf_{\af}^{\ast }\subset \hf_{\frak{g%
+%%  }}^{\ast }$ and $\hf_{\ao}^{\ast }\subset \frak{h%
 %%  }_{\go}^{\ast }$\
@@
 %%  $L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
-%%  of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\af$
+%%  of $\gf$ with the highest weight $\mu $\ ; (resp. integrable $\af$
 %%  -module with the highest weight $\nu $ );
 %%  
-%%  $r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\frak{g}$ $%
+%%  $r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\gf$ $%
 %%  \left( \mbox{resp. }\af\right) $ ;
@@
 %%  ^{+} $ $\left( \mbox{resp. }\Delta _{\af}^{+}\right) $--- the positive
-%%  root system (of $\frak{g}$ and $\af$ respectively);
+%%  root system (of $\gf$ and $\af$ respectively);
 %%  
@@
 %%  \right)$ --- the finite root system of the subalgebra $\co{%
-%%  \frak{g}}$ (resp. $\co{\af}$);
+%%  \gf}$ (resp. $\co{\af}$);
 %%  
@@
 %%  $\alpha _{i}$ , $\left( \beta _{j}\right) $ --- the $i
-%%  $-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\af%
+%%  $-th (resp. $j$-th) basic root for $\gf$ $\left( \mbox{resp. }\af%
 %%  \right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
 %%  
-%%  $\delta $ --- the imaginary root of $\frak{g}$ (and of $\af$ if any);
+%%  $\delta $ --- the imaginary root of $\gf$ (and of $\af$ if any);
 %%  
 %%  $\alpha _{i}^{\vee }$ , $\left( \beta _{j}^{\vee
-%%  }\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\af%
+%%  }\right) $--- the basic coroot for $\gf$ $\left( \mbox{resp. }\af%
 %%  \right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
@@
 
-Consider an integrable module $L^{\mu }$
-of $\frak{g}$ with the highest weight $\mu $ and
-let $\af\subset \frak{g}$ be a reductive subalgebra of $\frak{g}$.
-With respect to $\af$ the module $L^{\mu }$ is completely reducible,
-\begin{equation*}
- L_{\frak{g}\downarrow \af}^{\mu }=\bigoplus
+Рассмотрим интегрируемый модуль $L^{\mu }$ алгебры $\gf$ со старшим весом  $\mu$ и пусть  $\af\subset\gf$ -- редуктивная подалгебра $\gf$. Модуль $L^{\mu}$ полностью приводим по отношению к $\af$.
+\begin{equation*}
+ L_{\gf\downarrow \af}^{\mu }=\bigoplus
 \limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
 \end{equation*}
-Using the projection operator $\pi_{\af}$ (to the weight space $\frak{h_a}^*$)
-one can  rewrite this decomposition in terms of formal characters:
+Используем оператор проекции  $\pi_{\af}$ (на весовое пространство $\hf_{\af}^*$) и перепишем это разложение в терминах формальных характеров:
 \begin{equation}
@@
 \end{equation}
-We are interested in branching coefficients $b^{(\mu)}_{\nu}$.
-
-\subsubsection{Orthogonal subalgebra and injection fan.}
+Нас интересуют коэффициенты ветвления $b^{(\mu)}_{\nu}$.
+
+\subsubsection{Ортогональная подалгебра и веер вложения.}
 \label{subsec:branching-orthog-pair}
 
-In this subsection we shall introduce some simple constructions that will be used
-in our studies of branching and in particular the "orthogonal partner" $\afb$ for a
-reductive subalgebra $\af$  in  $\gf$.
-
-In the Weyl-Kac formula both numerator and denominator  can be considered
-as formal elements containing the singular weights of the Verma modules $V^{\xi}$
-with the highest weights $\xi=\mu$ and $\xi=0$ \cite{humphreys1997introduction}.
-We attribute singular elements to the corresponding integrable modules $L^{\mu }$
-and $L_{\af}^{\nu }$:
+В этой секции мы введем простые конструкции, которые будут полезны при изучении ветвлений. Важный объект здесь -- это ``ортогональный партнер''  $\afb$ редуктивной подалгебры $\af$ в  $\gf$.
+
+В формуле Вейля-Каца и числитель, и знаменатель могут рассматриваться как формальные элементы, содержащие сингулярные веса модулей Верма $V^{\xi}$ со старшими весами  $\xi=\mu$ и $\xi=0$ \cite{humphreys1997introduction}.
+Мы связываем сингулярные элементы с соответствующими интегрируемыми модулями  $L^{\mu }$ и $L_{\af}^{\nu }$:
 \begin{equation*}
@@
 \begin{equation*}
-\Psi _{ \af}^{\left( \nu \right) }:=
-\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho
-_{_{\af}})-\rho _{_{\af}}}.
-\end{equation*}
-and use the Weyl-Kac formula in the form
+\Psi _{ \af}^{\left( \nu \right) }:= \sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho_{_{\af}})-\rho _{_{\af}}}.
+\end{equation*}
+и используем формулы Вейля-Каца в форме
 \begin{equation}
 \label{Weyl-Kac2}
-ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}
-{\Psi ^{\left( 0 \right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
-\end{equation}
-
-Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
-we get the relation connecting the
-singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{ \af}^{\left( \nu \right) }$ :
+ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0 \right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
+\end{equation}
+
+Применим формулу  (\ref{Weyl-Kac2}) к правилу ветвления (\ref{branching1}) и получим соотношение, связывающее сингулярные элементы
+ $\Psi ^{\left( \mu \right) }$ and $\Psi _{ \af}^{\left( \nu \right) }$ :
 \begin{eqnarray}
@@
 \end{eqnarray}
-Here $\Delta _{\af}^{+}$ is the set of
-positive roots of the subalgebra $\af$ (without loss of generality we consider
-them as vectors from the positive root space $\frak{h}^{\ast  +}$ of $\frak{g}$).
-
-Consider the root subspace
-$\frak{h}_{\perp \af}^{\ast }$ orthogonal to  $\af$,
-\begin{equation*}
-\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }
+Здесь $\Delta _{\af}^{+}$ -- множество положительных корней подалгебры $\af$ (без потери общности мы можем считать их векторами из положительного корневого пространства  $\hf^{\ast  +}$ of $\gf$).
+
+Рассмотрим корневое подпространство $\hf_{\perp \af}^{\ast }$, ортогональное к  $\af$,
+\begin{equation*}
+\hf_{\perp \af}^{\ast }:=\left\{ \eta \in \hf^{\ast }
 |\forall h \in \hf_{\af};  \eta\left(h \right)=0 \right\} ,
 \end{equation*}
-and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
-to $\af$,
+и корни (соответственно -- положительные корни)  $\gf$, ортогональные
+к $\af$,
 \begin{eqnarray*}
-\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|
+\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\gf}|
 \forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} , \\
-\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
+\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
 }^{+}|\forall h \in \hf_{\af};  \beta^{+}\left(h \right)=0  \right\} .
 \end{eqnarray*}
-Let $W_{\af_{\perp }}$ be the subgroup of $W$ generated by the
-reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\af%
-_{\perp }}^{+}$ . The subsystem $\Delta _{\af_{\perp }}$ determines the
-subalgebra $\af_{\perp }$ with the Cartan subalgebra $\frak{h}_{\af%
-_{\perp }}$. Let
-\begin{equation*}
-\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
-}|\forall h \in \hf_{\af\oplus \af_{\perp}}; \eta \left( h \right)=0 \right\}
-\end{equation*}
-and consider the subalgebras
+Обозначим через $W_{\afb}$ подгруппу группы Вейля $W$, порожденную отражениями $w _{\beta }$, соответствующими корням $\beta \in \Delta _{\afb}^{+}$ .
+Подсистема  $\Delta _{\af_{\perp }}$ определяет подалгебру $\af_{\perp }$ с подалгеброй Картана $\hf_{\afb}$.
+Пусть
+\begin{equation*}
+\hf_{\perp }^{\ast }:=\left\{ \eta \in \hf_{\perp \af}^{\ast
+}|\forall h \in \hf_{\af\oplus \af_{\perp}}; \eta \left( h \right)=0 \right\},
+\end{equation*}
+рассмотрим подалгебры
 \begin{eqnarray*}
-\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
+\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \hf_{\perp }
 \\
-\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
+\widetilde{\af} &:&=\af\oplus \hf_{\perp }.
 \end{eqnarray*}
-Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
-$\left( \af,\af_{\perp}\right) $
-of subalgebras in $\frak{g}$.
-
-For the Cartan subalgebra we have the decomposition
-\begin{equation}
-\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\af_{\perp }}\oplus
-\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
-\af_{\perp }}=\frak{\frak{h}_{\widetilde{\af_{\perp }}}}\oplus
-\frak{h}_{\af}.
-\end{equation}
-For the subalgebras of an orthogonal pair $\left( \af,\af_{\perp
-}\right) $ we consider the corresponding Weyl vectors, $\rho _{\af}$
-and $\rho _{\af_{\perp }}$ , and\ form the so called ''defects'' $%
-\mathcal{D}_{\af}$ and $\mathcal{D}_{\af_{\perp }}$ of the
-injection:
+Алгебры $\af$ и $\af_{\perp }$ образуют ''ортогональную пару''
+$\left( \af,\afb\right)$ подалгебр в  $\gf$.
+
+Имеет место разложение подалгебры Картана
+\begin{equation}
+\hf=\frak{\hf_{\af}}\oplus \hf_{\af_{\perp }}\oplus
+\hf_{\perp }=\frak{\hf_{\widetilde{\af}}}\oplus \hf_{%
+\af_{\perp }}=\frak{\hf_{\widetilde{\af_{\perp }}}}\oplus
+\hf_{\af}.
+\end{equation}
+
+Для подалгебр из ортогональной пары  $\left( \af,\afb\right) $ рассмотрим соответствующие векторы Вейля $\rho _{\af}$ и $\rho _{\af_{\perp }}$, и образуем так называемые  ''дефекты'' вложения $\mathcal{D}_{\af}$ и $\mathcal{D}_{\af_{\perp }}$ :
 \begin{equation}
@@
 \end{equation}
-For the highest weight module $L_{\frak{g}}^{\mu }$ consider the singular
-weights $\left\{\left( w(\mu +\rho )-\rho \right)|w  \in W \right\}$ and
-their projections to $h_{\widetilde{\af_{\perp }}}^{\ast }$ (additionally
-shifted by the defect $-\mathcal{D}_{\af_{\perp }}$):
+
+Рассмотрим сингулярные веса  $\left\{\left( w(\mu +\rho )-\rho \right)|w  \in W \right\}$  модуля старшего веса  $L_{\gf}^{\mu }$ и их проекции на $h_{\widetilde{\af_{\perp }}}^{\ast }$ (дополнительно сдвинутые на дефект $-\mathcal{D}_{\af_{\perp }}$):
 \begin{equation*}
@@
 \end{equation*}
-Among the weights $\left\{\mu _{\widetilde{\af_{\perp }}}\left( w\right)
-|w\in W\right\}$ choose those located in the fundamental chamber $\overline{C_{%
-\widetilde{\af_{\perp }}}}$ and let $U$ be the set of representatives $%
-u $ for classes $W/W_{\af_{\perp }}$ such that
-
+Среди весов  $\left\{\mu _{\widetilde{\af_{\perp }}}\left( w\right)|w\in W\right\}$ выберем находящиеся в главной камере Вейля $\overline{C_{\widetilde{\afb}}}$ и обозначим через $U$ множество представителей $u$ классов смежности $W/W_{\af_{\perp }}$, таких что
 \begin{equation}
@@
 \end{equation}
-For the same set $U$ introduce the weights
+Для множества  $U$ введем веса
 \begin{equation*}
@@
 \end{equation*}
-To simplify the form of relations we shall now on omit the sign "$\circ$" in projected
-weights.
-
-To describe the recurrent properties for branching coefficients $b_{\nu
-}^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc}. One of the
-main tools is the set of weights $\Gamma _{\af\rightarrow \frak{g}%
-} $ called the injection fan. As far as we consider the general situation
-(where the injection is not necessarily maximal) the notion of the injection fan is
-modified:
-
+Чтобы упростить вид соотношений мы будем опускать значок "$\circ$" при записи проекций весов.
+
+Воспользуемся техникой, предложенной в работе  \cite{ilyin812pbc} для записи рекуррентных свойств коэффициентов ветвления $b_{\nu}^{(\mu )}$.
+Один из инструментов в ней -- это множество весов $\Gamma_{\af\rightarrow \gf}$, называющееся веером вложения.
+Так как мы рассматриваем общую ситуацию (где вложение не обязательно максимально) понятие веера вложения нуждается в уточнении:
 \begin{definition}
-\label{fan-definition} For the product
+\label{fan-definition} Рассмотрим произведение
 \begin{equation}
@@
 \end{equation}
-consider the carrier $\Phi _{\af\subset \frak{g}}\subset P_{\af}$
-of the function $s(\gamma )=\det \left( \gamma \right) $ :
-\begin{equation}
-\Phi _{\af\subset \frak{g}}=\left\{ \gamma \in P_{\af}|s(\gamma
+и носитель $\Phi _{\af\subset \gf}\subset P_{\af}$ функции $s(\gamma )=\det \left( \gamma \right) $ :
+\begin{equation}
+\Phi _{\af\subset \gf}=\left\{ \gamma \in P_{\af}|s(\gamma
 )\neq 0\right\}   \label{eq:37}
 \end{equation}
-The ordering of roots in $\co{\Delta _{\af}}$ induce the
-natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
-the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
-\begin{equation}
-\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
+Упорядочение корней в  $\co{\Delta _{\af}}$ индуцирует натуральное упорядочение весов в $P_{\af}$. Обозначим через $\gamma_{0}$ наименьший вектор $\Phi _{\af\subset \gf}$. Множество
+\begin{equation}
+\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \gf}\right\} \setminus \left\{ 0\right\}
 \label{fan-defined}
 \end{equation}
-is called the \textit{injection fan}.
+называется  \textit{веером вложения}.
 \end{definition}
-In the next subsection we shall see how the injection fan defines the recurrent
-properties of branching coefficients. It must be noticed that the injection fan is
-the universal instrument that depends only on the injection.
-
-\subsubsection{Decomposing the singular element.}
+В следующем разделе мы покажем, что веер вложения определяет рекуррентные свойства коэффициентов ветвления. Нужно отметить, что веер вложения универсален и зависит только от вложения.
+
+\subsubsection{Разложение сингулярного элемента.}
 \label{subsec:decomp-sing-element}
 
-Now we shall prove that the Weyl-Kac character formula (in terms of singular
-elements) describes the particular case of a more general relation:
+Теперь покажем, что формула Вейля-Каца для характеров (в терминах сингулярных элементов) представляет собой частный случай более общего соотношения:
 
@@
 \label{lemma}
-Let $\left( \af,\afb \right)$ be the orthogonal pair of reductive
-subalgebras in $\frak{g}$, with $\widetilde{\af_{\perp }}=\af%
-_{\perp }\oplus \frak{h}_{\perp }$ and $\widetilde{\af}=\af\oplus
-\frak{h}_{\perp }$ ,
-
-$L^{\mu }$ be the highest weight module with the singular element
-$\Psi ^{\left(\mu \right)}$ ,
-
-$R_{\af_{\perp }}$ be the Weyl denominator for $\af_{\perp }$.
-
-Then the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
-=\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}\right) $
-can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
-singular weights $e^{\mu _{\af}\left( u\right) }$ with the
-coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
-}}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right) $:
+Пусть $\left( \af,\afb \right)$ -- ортогональная пара редуктивных подалгебр $\gf$ и  $\widetilde{\afb}=\afb\oplus \hf_{\perp }$, $\widetilde{\af}=\af\oplus\hf_{\perp }$ ,
+
+$L^{\mu }$ -- модуль старшего веса с сингулярным элементом $\Psi ^{\left(\mu \right)}$ ,
+
+$R_{\af_{\perp }}$ -- знаменатель Вейля для подалгебры $\af_{\perp }$.
+
+Тогда элемент  $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi _{\af}\left( \frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}\right) $ можно разложить в сумму по  $u\in U$ (см.
+(\ref{U-def})) сингулярных весов $e^{\mu _{\af}\left( u\right) }$ с коэффициентами $\epsilon (u)\mathrm{\dim}\left( L_{\widetilde{\afb}}^{\mu _{\widetilde{\afb}}\left( u\right) }\right) $:
 \begin{equation}
@@
 \begin{proof}
-With $u\in U $   and $v\in W_{\afb}$ apply the decomposition
+Для $u\in U $ и $v\in W_{\afb}$ применим разложение
 \begin{equation*}
@@
 \end{equation*}
-to the singular weight
+к сингулярному весу
 \begin{equation}
@@
 \end{equation}
-Use the defect $\mathcal{D}_{\afb}$ (\ref{defect-perp}) to simplify
-the first summand in (\ref{sing-decomp-1}):
+Используем дефект $\mathcal{D}_{\afb}$ (\ref{defect-perp}) чтобы упростить в (\ref{sing-decomp-1}) первое слагаемое :
 \begin{equation*}
@@
 \end{equation*}
-and the second one:
+и второе:
 \begin{equation*}
@@
 \end{equation*}
-These expressions provide a kind of a factorization in the anomalous element $\Psi^{\mu
-}$ and we find in it the combination of
-anomalous elements $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ of the
-subalgebra $\widetilde{\af_{\perp }}$-modules $L_{\widetilde{\af%
-_{\perp }}}^{\eta }$:
+Эти выражения представляют собой факторизацию аномального элемента  $\Psi^{\mu}$ и мы видим, что они содержат комбинации сингулярных элементов $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ модулей $L_{\widetilde{\afb}}^{\eta }$ подалгебры  $\widetilde{\afb}$:
 \begin{equation*}
@@
 
-Dividing both sides by the Weyl element $R_{\af_{\perp }}=\prod_{\beta
-\in \Delta _{\af_{\perp }}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}$ and
-projecting them to the weight space $h_{\af}^{\ast }$\ we obtain the
-desired relation:
+Разделим обе части на элемент Вейля  $R_{\af_{\perp }}=\prod_{\beta \in \Delta _{\afb}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}$, спроектируем их на весовое подпространство  $h_{\af}^{\ast }$ и получим итоговое соотношение:
 \begin{eqnarray*}
@@
 \begin{remark}
-This relation can be considered a generalized form of the Weyl formula for singular
-element $\Psi _{\frak{g}}^{\mu }$ : the vectors $\mu _{\af}\left(
-u\right) $ play the role of singular weights while instead of the determinants $%
-\epsilon (u)$ we have the products $\epsilon (u)\mathrm{\dim }\left( L_{%
-\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left(
-u\right) }\right) .$ In fact when $\frak{a=g}$ both $\af_{\perp }$ and $%
-\frak{h}_{\perp }$ are trivial, $U=W$ , and\ the original Weyl formula is
-easily reobtained.
+Это соотношение можно рассматривать как обобщение формулы Вейля для сингулярного элемента  $\Psi _{\gf}^{\mu }$: векторы  $\mu_{\af}\left(u\right)$ играют роль сингулярных весов, но вместо определителей $\epsilon (u)$ появляются произведения  $\epsilon(u)\mathrm{\dim }\left( L_{\widetilde{\afb}}^{\mu _{\widetilde{\afb}}\left(u\right) }\right).$ Действительно, при  $\frak{a=g}$ подалгебры  $\afb$ и $\hf_{\perp }$ тривиальны, $U=W$ , и исходная формула Вейля с легкостью восстанавливается.
 \end{remark}
 
-\subsubsection{Constructing recurrent relations.}
+\subsubsection{Построение рекуррентных соотношений.}
 \label{subsec:Construct-recurrent-rel}
 
-Consider the right-hand side of relation (\ref{eq:4}).
-The numerator there describes the branching in terms of singular elements and
-it is reasonable to expand it as an element of $\mathcal{E}\left( \frak{g} \right)$:
+Рассмотрим правую часть равенства (\ref{eq:4}).
+Числитель описывает ветвление в терминах сингулярных элементов и, как элемент  $\mathcal{E}\left( \gf \right)$, допускает разложение в виде:
 \begin{equation}
@@
 \end{equation}
-Here the coefficients $k_{\lambda}^{\left( \mu \right) }$ are integer and their signs
-depend on the length (see \cite{humphreys1997introduction})  of the Weyl group elements in
-$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }$. The important property of
-$k_{\lambda}^{\left( \mu \right) }$'s is that they coincide with the branching coefficients
-for all weights $\nu$ inside the main Weil chamber:
+Здесь $k_{\lambda}^{\left( \mu \right) }$  -- целочисленные коэффициенты, их знаки зависят от длины элементов группы Вейля в 
+$\Psi _{\left( \af\right) }^{\left( \nu \right) }$. Важно заметить, что $k_{\lambda}^{\left( \mu \right) }$ совпадают с коэффициентами ветвления для всех весов $\nu$ в главной камере Вейля:
 \begin{equation}
@@
 \end{equation}
-We call the coefficients $k_{\lambda}$ --- the anomalous branching coefficients
-(see also \cite{ilyin812pbc}).
-
-Now we can state the main theorem which gives us an instrument for the
-recurrent computation of branching coefficients.
+Мы называем коэффициенты $k_{\lambda}$ сингулярными коэффициентами ветвления
+(см. также \cite{ilyin812pbc}).
+
+Теперь мы можем сформулировать основную в этой главе теорему, которая позволит нам рекуррентно вычислять коэффициенты ветвления.
 
 \begin{theorem}
-  For the anomalous branching coefficients $k^{(\mu)}_{\nu}$ (\ref{eq:21})
-  the following relation holds
+  Для сингулярных коэффициентов ветвления $k^{(\mu)}_{\nu}$ (\ref{eq:21}) выполняется соотношение
   \begin{equation}
@@
 \begin{proof}
+
 Redress relation (\ref{eq:4}) for the element $
-\frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using definition (\ref{eq:37})
-for the carrier $\Phi _{\af\subset \frak{g}}$ ,
+\frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}$ using definition (\ref{eq:37})
+for the carrier $\Phi _{\af\subset \gf}$ ,
 \begin{equation*}
@@
 \Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
-=\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
+=\pi _{\af}\left( \frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}%
 \right) = \\[2mm]
@@
 +\rho _{\af})-\rho _{\af}}\right) = \\[5mm]
-=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
+=-\sum\limits_{\gamma \in \Phi _{\af\subset \gf}}s(\gamma
 )e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
@@
 }}\right)  \\
-=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
+=-\sum\limits_{\gamma \in \Phi _{\af\subset \gf}}s(\gamma
 )e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
@@
 \Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
-=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
+=-\sum_{\gamma \in \Phi _{\af\subset \gf}}s(\gamma
 )e^{-\gamma }\sum_{\lambda \in P_{\af}}k_{\nu }^{(\mu )}e^{\lambda
-}=-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
+}=-\sum_{\gamma \in \Phi _{\af\subset \gf}}\sum_{\lambda \in P_{%
 \af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
@@
 \af_{\perp }}}\left( u\right) }\right)  \\
-&=&-\sum_{\gamma \in \Phi _{\af\subset \frak{g}}}\sum_{\lambda \in P_{%
+&=&-\sum_{\gamma \in \Phi _{\af\subset \gf}}\sum_{\lambda \in P_{%
 \af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
@@
 \af}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\af%
-\subset \frak{g}}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
+\subset \gf}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
 \af}.  \label{eq:17}
@@
 The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
-for $\gamma \in \Phi _{\af\subset \frak{g}}$ are not independent, they
+for $\gamma \in \Phi _{\af\subset \gf}$ are not independent, they
 are subject to linear relations and the form of these relations changes
@@
 U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
-}\subset \frak{g}}$ and pass to a summation over the vectors of the
-injection fan $\Gamma _{\af\rightarrow \frak{g}}$ (see Definition \ref
+}\subset \gf}$ and pass to a summation over the vectors of the
+injection fan $\Gamma _{\af\rightarrow \gf}$ (see Definition \ref
 {fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
@@
 
-When both $\frak{g}$ and $\af$ are finite-dimensional all regular
+When both $\gf$ and $\af$ are finite-dimensional all regular
 embeddings can be obtained by a successive elimination of nodes in the
-extended Dynkin diagram of $\frak{g}$ (and $\Delta_{\afb }^{+}=\emptyset $
+extended Dynkin diagram of $\gf$ (and $\Delta_{\afb }^{+}=\emptyset $
 if $\af$ is maximal). For the classical series $A$, $C$ and $D$ when
-the regular injection $\af\rightarrow \frak{g}$ is thus fixed, the
-Dynkin diagram for $\af_{\bot }$ is obtained from the extended diagram
-of $\frak{g}$ by eliminating the subdiagram of $\af$ and the adjacent
+the regular injection $\af\rightarrow \gf$ is thus fixed, the
+Dynkin diagram for $\afb$ is obtained from the extended diagram
+of $\gf$ by eliminating the subdiagram of $\af$ and the adjacent
 nodes:
@@
 \hline
-$\frak{g}$ & Extended diagram of $\frak{g}$ & Diagrams of the subalgebras $%
+$\gf$ & Extended diagram of $\gf$ & Diagrams of the subalgebras $%
 \af,\; \afb$ &  \\ \hline
@@
 }
-\caption{Subalgebras $\af,\;\af_{\bot }$ for the classical series}
+\caption{Subalgebras $\af,\;\afb$ for the classical series}
 \end{table}
@@
 In the case of $B$ series the situation is different. The reason is that
-here the subalgebra $\af_{\bot }$ may be larger than the one obtained
+here the subalgebra $\afb$ may be larger than the one obtained
 by elimination of the subdiagram of $\af$ and the adjacent nodes. The
-subalgebras of the orthogonal pair,$\ \af$ and $\af_{\bot }$, must
-not form a direct sum in $\frak{g}$ . It can be directly
-checked that when $\frak{g}=B_{r}$ and $\af=B_{r_{\af}}$ the
-orthogonal subalgebra is $\af_{\bot }=B_{r-r_{\af}}$. Consider the
+subalgebras of the orthogonal pair,$\ \af$ and $\afb$, must
+not form a direct sum in $\gf$ . It can be directly
+checked that when $\gf=B_{r}$ and $\af=B_{r_{\af}}$ the
+orthogonal subalgebra is $\afb=B_{r-r_{\af}}$. Consider the
 injection $B_{r_{\af}}\rightarrow B_{r},\quad 1<r_{\af}<r$. By
@@
 {dynkin1952semisimple} we can deduce the following list of pairs of
-orthogonal subalgebras $\af,\;\af_{\bot }$:
+orthogonal subalgebras $\af,\;\afb$:
 \begin{equation*}
@@
 algorithm for recursive computation of branching coefficients. In this
-algorithm there is no need to construct the module $L^{(\mu)}_{\frak{g}}$ or
+algorithm there is no need to construct the module $L^{(\mu)}_{\gf}$ or
 any of the modules $L^{(\nu)}_{\af}$.
@@
 \item  Construct the root system $\Delta _{\af}$ for the embedding $%
-\af\rightarrow \frak{g}$.
+\af\rightarrow \gf$.
 
@@
 
-\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. Relation
+\item  Construct the set $\Gamma _{\af\rightarrow \gf}$. Relation
  (\ref{eq:6}) defines the sign function
- $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
+ $s(\gamma)$ and the set $\Phi_{\af\subset \gf}$ where the lowest weight
  $\gamma_0$ is to be subtracted to get the fan (\ref{fan-defined}):
- $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}$.
+ $\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \gf}\right\} \setminus \left\{ 0\right\}$.
 
 \item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
-)-\rho ;\;w \in W\right\} $ of singular weights for the $\frak{g}$%
+)-\rho ;\;w \in W\right\} $ of singular weights for the $\gf$%
 -module $L^{(\mu )}$.

### 2011-11-25 AffineLieAlgebras/Thesis/1.tex
More translation in chapter 1.

@@
 \begin{proof}
-
-Redress relation (\ref{eq:4}) for the element $
-\frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}$ using definition (\ref{eq:37})
-for the carrier $\Phi _{\af\subset \gf}$ ,
+Перепишем соотношение (\ref{eq:4}) для элемента $\frac{\Psi _{\gf}^{\mu }}{R_{\afb}}$ используя определение (\ref{eq:37})
+для носителя $\Phi _{\af\subset \gf}$ ,
 \begin{equation*}
@@
 
-Then expand the sum in brackets (with respect to the formal basis in $\mathcal{E}$%
-):
+Затем раскроем сумму в скобках (по отношению к формальному базису в  $\mathcal{E}$):
 \begin{equation*}
@@
 \end{equation*}
-Substitute the expression obtained in Lemma \ref{lemma} (in the left-hand side),
+Подставим выражение, полученное в Лемме \ref{lemma} (в левую часть),
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-The immediate consequence of this equality is:
+Из этого равенства немедленно следует
 \begin{equation}
@@
 \end{equation}
-The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
-for $\gamma \in \Phi _{\af\subset \gf}$ are not independent, they
-are subject to linear relations and the form of these relations changes
-when the tested weight $\xi $ coincides with one of \ the ''singular
-weights''  $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in
-U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
-}\subset \gf}$ and pass to a summation over the vectors of the
-injection fan $\Gamma _{\af\rightarrow \gf}$ (see Definition \ref
-{fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
+Полученная формула означает, что коэффициенты  $k_{\xi +\gamma }^{(\mu )}$ для  $\gamma \in \Phi _{\af\subset \gf}$ не независимы, а удовлетворяют линейным соотношениям.
+Вид этих соотношений меняется если тестовый вес  $\xi $ совпадает с одним из ``сингулярных весов''   $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in U\right\} $.
+В завершение доказательства мы вычитаем наименьший вес  $\gamma _{0}\in \Phi _{\af\subset \gf}$ и переходим к суммированию по векторам веера вложения $\Gamma _{\af\rightarrow \gf}$ (см.
+определение \ref{fan-definition}).
+Итак, мы получили искомое рекуррентное соотношение  (\ref{recurrent-relation}).
 \end{proof}
 
-\subsubsection{Embeddings and orthogonal pairs in simple Lie algebras}
+\subsubsection{Вложения и ортогональные пары подалгебр простых алгебр Ли}
 \label{sect-embeddings}

### 2011-11-25 AffineLieAlgebras/Thesis/1.tex
More translations in chapter 1.

@@
 \label{sect-embeddings}
-
-In this subsection we discuss some properties of ''orthogonal pairs'' of
-subalgebras in simple Lie algebras of classical series.
-
-When both $\gf$ and $\af$ are finite-dimensional all regular
-embeddings can be obtained by a successive elimination of nodes in the
-extended Dynkin diagram of $\gf$ (and $\Delta_{\afb }^{+}=\emptyset $
-if $\af$ is maximal). For the classical series $A$, $C$ and $D$ when
-the regular injection $\af\rightarrow \gf$ is thus fixed, the
-Dynkin diagram for $\afb$ is obtained from the extended diagram
-of $\gf$ by eliminating the subdiagram of $\af$ and the adjacent
-nodes:
+В этом разделе мы обсудим некоторые свойства ``ортогональных пар'' подалгебр простых алгебр Ли классических серий.
+
+Когда  $\gf$ и $\af$ конечномерные все регулярные вложения можно получить путем последовательного удаления вершин из расширенной диаграммы Дынкина алгебры $\gf$ (и  $\Delta_{\afb }^{+}=\emptyset $ если $\af$ максимальна).
+Если регулярное вложение для классических серий $A$, $C$ и $D$ зафиксировано таким образом, то диаграмма Дынкина для $\afb$ получается из расширенной диаграммы $\gf$ путем удаления поддиаграммы $\af$ и соседних вершин:
 \begin{table}[tbh]
@@
 \hline
-$\gf$ & Extended diagram of $\gf$ & Diagrams of the subalgebras $%
-\af,\; \afb$ &  \\ \hline
+$\gf$ & Расширенная диаграмма $\gf$ & Диаграммы подалгебр $\af,\; \afb$ &  \\ \hline
 $A_n$ & \includegraphics{table1_1(l)} & \includegraphics{table1_1(r)}
@@
 }
-\caption{Subalgebras $\af,\;\afb$ for the classical series}
+\caption{Подалгебры $\af,\;\afb$ для классических серий}
 \end{table}
 
-In the case of $B$ series the situation is different. The reason is that
-here the subalgebra $\afb$ may be larger than the one obtained
-by elimination of the subdiagram of $\af$ and the adjacent nodes. The
-subalgebras of the orthogonal pair,$\ \af$ and $\afb$, must
-not form a direct sum in $\gf$ . It can be directly
-checked that when $\gf=B_{r}$ and $\af=B_{r_{\af}}$ the
-orthogonal subalgebra is $\afb=B_{r-r_{\af}}$. Consider the
-injection $B_{r_{\af}}\rightarrow B_{r},\quad 1<r_{\af}<r$. By
-eliminating the simple root $\alpha _{r_{\af}-1}=e_{r_{\af%
-}-1}-e_{r_{\af}}$ one splits the extended Dynkin diagram of $B_{r}$
-into the disjoint diagrams for $\af=B_{r_{\af}}$ and $D_{r-r_{%
-\af}}$. But the system $\Delta _{\af_{\perp }}$ contains not only
-the simple roots $\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots ,e_{r_{\af%
-}-2}-e_{r_{\af}-1},e_{1}+e_{2}\right\} $ but also the root $e_{r_{\frak{%
-a}}-1}$. Thus $\Delta _{\af_{\perp }}$ forms the subsystem of the type $%
-B_{r-r_{\af}}$ and the orthogonal pair for the injection $B_{r_{\af%
-}}\rightarrow B_{r}$ is $\left( B_{r_{\af}},B_{r-r_{\af}}\right) $%
-. In the next Section a particular case of such orthogonal pair is
-presented for the injection $B_{2}\rightarrow B_{4}$ (see Figure \ref
-{fig:dynkin}).
-
-The complete classification of regular subalgebras for affine Lie algebras
-can be found in the recent paper \cite{1751-8121-41-36-365204}. From the complete
-classification of maximal special subalgebras in classical Lie algebras \cite
-{dynkin1952semisimple} we can deduce the following list of pairs of
-orthogonal subalgebras $\af,\;\afb$:
+В случае серии $B$ ситуация отличается.
+Причина в том, что в данном случае подалгебра $\afb$ может быть больше, чем результат удаления поддиаграммы  $\af$ и соседних вершин.
+Подалгебры ортогональной пары $\ \af$ и $\afb$ не обязаны образовывать прямую сумму в $\gf$.
+Можно явно проверить, что при  $\gf=B_{r}$ и $\af=B_{r_{\af}}$ ортогональная подалгебра -- это $\afb=B_{r-r_{\af}}$.
+Рассмотрим вложение $B_{r_{\af}}\rightarrow B_{r},\quad 1<r_{\af}<r$.
+В результате удаления простого корня  $\alpha _{r_{\af}-1}=e_{r_{\af}-1}-e_{r_{\af}}$ расширенная диаграмма Дынкина для $B_{r}$ разбивается на несвязные диаграммы $\af=B_{r_{\af}}$ и $D_{r-r_{\af}}$.
+Однако корневая система  $\Delta _{\afb}$ содержит не только простые корни  $\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots ,e_{r_{\af}-2}-e_{r_{\af}-1},e_{1}+e_{2}\right\} $, но и корень $e_{r_{\af}-1}$.
+То есть  $\Delta _{\afb}$ образует систему типа  $B_{r-r_{\af}}$ и ортогональная пара для вложения $B_{r_{\af}}\rightarrow B_{r}$ -- это  $\left( B_{r_{\af}},B_{r-r_{\af}}\right) $.
+В следующем разделе мы приводим пример такой ортогональной пары для вложения $B_{2}\rightarrow B_{4}$ (см.
+Рис.
+\ref{fig:dynkin}).
+
+Полная классификация регулярных подалгебр аффинных алгебр Ли приведена в недавней работе \cite{1751-8121-41-36-365204}.
+Из полной классификации максимальных специальных подалгебр классических алгебр Ли \cite{dynkin1952semisimple} мы получаем следующий список пар ортогональных подалгебр $\af,\;\afb$:
 \begin{equation*}
@@
 sp(2p)\oplus so(q) & \subset sp(2pq) &  \\
-so(p)\oplus so(q) & \subset so(p+q) & \mathrm{{for}\;p\;{and}\;q\;{odd}.}
+so(p)\oplus so(q) & \subset so(p+q) & \text{для нечетных}\;p\;\text{и}\;q.
 \end{array}
@@
 
-\subsubsection{Algorithm for recursive computation of branching coefficients}
+\subsubsection{Алгоритм рекурсивного вычисления коэффициентов ветвления}
 
@@
 
-The recurrent relation (\ref{recurrent-relation}) allows us to formulate an
-algorithm for recursive computation of branching coefficients. In this
-algorithm there is no need to construct the module $L^{(\mu)}_{\gf}$ or
-any of the modules $L^{(\nu)}_{\af}$.
-
-It contains the following steps:
+Рекуррентные соотношения (\ref{recurrent-relation}) позволяют нам сформулировать алгоритм для рекурсивного вычисления коэффициентов ветвления.
+При этом для работы алгоритма не требуется построение модуля $L^{(\mu)}_{\gf}$ или какого-то из модулей $L^{(\nu)}_{\af}$
+
+Алгоритм состоит из следующих шагов:
 
 \begin{enumerate}
-\item  Construct the root system $\Delta _{\af}$ for the embedding $%
-\af\rightarrow \gf$.
-
-\item  Select all positive roots $\alpha \in \Delta ^{+}$ orthogonal
-to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
-
-\item  Construct the set $\Gamma _{\af\rightarrow \gf}$. Relation
- (\ref{eq:6}) defines the sign function
- $s(\gamma)$ and the set $\Phi_{\af\subset \gf}$ where the lowest weight
- $\gamma_0$ is to be subtracted to get the fan (\ref{fan-defined}):
- $\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\af\subset \gf}\right\} \setminus \left\{ 0\right\}$.
-
-\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
-)-\rho ;\;w \in W\right\} $ of singular weights for the $\gf$%
--module $L^{(\mu )}$.
-
-\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
-}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
-)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
-\af_{\perp }}}}\right\} $. Since the set $\Delta_{\afb }^{+}$ is fixed
-we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
-}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
-\af_{\perp }}}}$ (by computing its scalar product with the fundamental
-weights of $\afb^{+}$).
-
-\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
-calculate dimensions of the corresponding modules, $\mathrm{\dim }\left(
-L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
-}\left( u\right) }\right) $, using the Weyl dimension formula and construct
-the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
-
-\item  Calculate the anomalous branching coefficients using the
-recurrent relation (\ref{recurrent-relation}) and select among them those
-corresponding to the weights in the main Weyl
-chamber $\overline{C_{\af}}$.
+\item Построить корневую систему $\Delta _{\af}$ для вложения $\af\rightarrow \gf$.
+
+\item Выбрать все положительные корни $\alpha \in \Delta ^{+}$, ортогональные к  $\af$, то есть сформировать множество $\Delta_{\afb }^{+}$.
+
+\item Построить множество $\Gamma _{\af\rightarrow \gf}$.
+Соотношение  (\ref{eq:6}) определяет знаковую функцию $s(\gamma)$ и множество $\Phi_{\af\subset \gf}$.
+Вычитание наименьшего веса $\gamma_0$ дает веер вложения (\ref{fan-defined}):
+ $\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{\af\subset \gf}\right\} \setminus \left\{ 0\right\}$.
+
+\item Построить множество $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
+)-\rho ;\;w \in W\right\} $ сингулярных весов для  $\gf$-модуля $L^{(\mu )}$.
+
+\item Выбрать веса $\left\{ \mu _{\widetilde{\afb}}\left( w\right) =\pi _{\widetilde{\afb}}\left[ w(\mu +\rho
+)-\rho \right] -\mathcal{D}_{\afb}\in \overline{C_{\widetilde{\afb}}}\right\} $.
+Так как множество  $\Delta_{\afb }^{+}$ фиксировано, легко осуществить проверку принадлежности веса $\mu _{\widetilde{\afb}}\left( w\right) $ к главной камере Вейля $\overline{C_{\widetilde{\afb}}}$ (достаточно вычислить скалярные произведения с фундаментальными весами $\afb^{+}$).
+
+\item Для весов $\mu _{\widetilde{\afb}}\left( w\right) $ вычислить размерности соответствующих модулей, $\mathrm{\dim }\left(L_{\widetilde{\afb}}^{\mu _{\widetilde{\afb}}\left( u\right) }\right) $, используя формулу Вейля для размерностей.
+Затем построить сингулярный элемент $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
+
+\item Вычислить аномальные коэффициенты ветвления используя рекуррентное соотношение (\ref{recurrent-relation}) и выбрать среди них те, которые соответствуют весам в главной камере Вейля $\overline{C_{\af}}$.
 \end{enumerate}
 
-We can speed up the algorithm by
-one-time computation of the representatives of the conjugate classes $%
-W/W_{\afb }$.
-
-The next section contains examples illustrating the application of this
-algorithm.
+Можно ускорить работу алгоритмы путем однократного вычисления представителей классов смежности $W/W_{\afb }$.
+
+Следующий раздел состоит из примеров, иллюстрирующих применение данного алгоритма.
 

### 2011-11-26 AffineLieAlgebras/Thesis/1.tex
More translations in chapter 1.

@@
 
-\subsection{Branching for finite dimensional Lie algebras}
+\subsection{Ветвления модулей конечномерных алгебр Ли}
 \label{sec:finite-dimens-lie}
 
-\subsubsection{Regular embedding of $A_1$ into $B_2$}
+\subsubsection{Регулярное вложение $A_1$ в $B_2$}
 \label{sec:regul-embedd-a_1}
 
-Consider the regular embedding $A_1\to B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$
-are presented as dashed vectors in Figure \ref{fig:B2_A1}. We denote the corresponding
-Weyl reflections by $w_1, w_2$. The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is
-grey.
+Рассмотрим регулярное вложение $A_1\to B_2$.
+Простые корни $\alpha_1, \alpha_2$ алгебры $B_2$ обозначены пунктирными стрелками на Рисунке \ref{fig:B2_A1}.
+Мы обозначаем соответствующие элементарные отражения через $w_1, w_2$.
+Простой корень $\beta = \alpha_1+2\alpha_2$ алгебры $A_1$ показан серым цветом.
 
@@
   }
-  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$
-  are presented as dashed vectors.
-  The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is grey.
-  The highest weight of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$ is black.
-  The weights of the singular element $\Psi^{(\omega_1)}$ are marked by circles with
-  superscripts indicating the corresponding determinants $\epsilon(w)$.}
+  \caption{Регулярное вложение  $A_1$ в $B_2$.
+Простые корни  $\alpha_1, \alpha_2$ алгебры $B_2$ обозначены пунктирными стрелками.
+Простой корень $\beta = \alpha_1+2\alpha_2$ подалгебры $A_1$ показан серым цветом.
+Старший вес фундаментального представления $L^{(1,0)=\omega_1}_{B_2}$ выделен черным.
+Веса сингулярного элемента $\Psi^{(\omega_1)}$ отмечены кругами с подписанными значениями соответствующих определителей $\epsilon(w)$.}
   \label{fig:B2_A1}
@@
   }
-  \caption{Here in addition to the diagram presented above (Figure(\ref{fig:B2_A1}))
-  the weights of $\left( \afb=A_1 \right)$-modules $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$
-  originating in the points $\pi _{\af}\left[ u(\mu +\rho )-\rho \right] $
-are shown by dotted lines.
-    The superscripts over the highest weights  $\mu_{\af_{\perp }}\left( u\right)$
-    are now the products $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.
-    Coordinates along the root $\beta$ are counted in terms of the fundamental weight of $\af$. }
+  \caption{Здесь диаграмма, показанная выше (Рисунок \ref{fig:B2_A1}), дополнена весами $\left( \afb=A_1 \right)$-модулей $L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$, построенных в точках $\pi _{\af}\left[ u(\mu +\rho )-\rho \right] $ и показанных пунктирными линиями.
+    Подписи к старшим весам   $\mu_{\af_{\perp }}\left( u\right)$ представляют собой значения произведений $\epsilon(u)\dim\left(L_{\afb}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.
+    Координаты вдоль корня $\beta$ указаны по отношению к фундаментальному весу $\af$. }
 \label{fig:B2_A1_2}
@@
 
-Let's perform the reduction of the fundamental representation $L^{(1,0)=\omega_1}_{B_2}$
-($\omega_1$ -- the black vector in Figure \ref{fig:B2_A1}) according to the steps of the algorithm.
-The root $\alpha_1$ is orthogonal to $\beta$,
-so we have $\Delta_{\afb}^+ = \left\{ \alpha_1 \right\}$ (step (ii)).
-According to Definition \ref{fan-definition}
-the fan $\Gamma_{A_1\to B_2}$ (step (iii)) consists of two weights:
+Выполним редукцию фундаментального представления  $L^{(1,0)=\omega_1}_{B_2}$ ($\omega_1$ -- черная стрелка на Рисунке \ref{fig:B2_A1}) в соответствии с алгоритмом.
+Корень $\alpha_1$ ортогонален к $\beta$, так что  $\Delta_{\afb}^+ = \left\{ \alpha_1 \right\}$ (шаг (ii)).
+В соответствии с Определением \ref{fan-definition} веер вложения $\Gamma_{A_1\to B_2}$ (шаг (iii)) состоит из двух весов:
 \begin{equation*}
@@
 \end{equation*}
-where the second component is the value of the sign function $s(\gamma)$.
-Singular weights  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$ (step (iv))
-are indicated by circles with the superscript $\epsilon\left( w \right)$.
-The space $U$ is the factor $W/W_{\afb}$ where $W_{\afb}=\left\{e,w_1\right\}$.
-This means that singular weights located above the $\beta$-line
-belong to the Weyl chamber $\overline{C_{\widetilde{\af_{\perp }}}}$.
-According to formula (\ref{defect-perp}) we have $\mathcal{D}_{\af_{\perp }}=0$ and
-$\hf_{\perp }=0$, thus $\left\{ \mu _{\af_{\perp }}\left( w\right)
-=\pi _{\af_{\perp }}\left[ w(\mu +\rho)-\rho \right]\right\}$.
-We obtain four highest weights for $\af_{\perp }$-modules. In terms of
-$\af_{\perp }$-fundamental weight $\frac{1}{2} \alpha_1$ these highest weights
-$\left\{ \mu _{\af_{\perp }}\left( u\right)
-=\pi _{\af_{\perp }}\left[ u(\mu +\rho)-\rho \right]| u \in U \right\}$
- are
-$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$ (step v).
-In Figure (\ref{fig:B2_A1_2}) the corresponding weight diagrams
+где вторая компонента -- это значение знаковой функции  $s(\gamma)$.
+Сингулярные веса  $\left\{ w (\omega_1 +\rho)-\rho ;\;w \in W\right\}$ (шаг (iv)) показаны кругами с подписанными значениями $\epsilon\left( w \right)$.
+Пространство  $U$ представляет собой факторпространство $W/W_{\afb}$, где $W_{\afb}=\left\{e,w_1\right\}$.
+Это означает, что сингулярные веса, находящиеся над прямой, заданной корнем $\beta$, принадлежат главной камере Вейля $\overline{C_{\widetilde{\af_{\perp }}}}$.
+Из формулы (\ref{defect-perp})  мы получаем  $\mathcal{D}_{\af_{\perp }}=0$ и $\hf_{\perp }=0$, то есть $\left\{ \mu _{\afb}\left( w\right)=\pi _{\afb}\left[ w(\mu +\rho)-\rho \right]\right\}$.
+Значит есть четыре старших веса для $\af_{\perp }$-модулей.
+В базисе фундаментального веса $\frac{1}{2} \alpha_1$ алгебры $\afb$ координаты этих весов
+$\left\{ \mu _{\afb}\left( u\right)=\pi _{\afb}\left[ u(\mu +\rho)-\rho \right]| u \in U \right\}$
+равны
+$\left\{ \left( 1\right) \left( 2\right) \left( 2\right) \left( 1\right) \right\}$ (шаг v).
+На Рисунке (\ref{fig:B2_A1_2}) соответствующие весовые диаграммы
 $\left\{ \mathcal{N}_{\af_{\perp }}^{\mu _{\af_{\perp }}\left( u\right) }\right\} $
-are attached to the set of $\af$-weights
-$\left\{ \mu _{\af}\left( u\right)\right\} =\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]\right\}
-=\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$.
-In fact we do not need the
-weight diagrams but only the dimensions of modules
-$L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ multiplied by
-$\epsilon \left( u\right) $ (step vi). Obtained values are to be attributed to the points
-$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$
-in $P_{\af}$. The singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
-has the set of weights with anomalous multiplicities:
+построены из весов $\left\{ \mu _{\af}\left( u\right)\right\} =\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right]\right\}
+=\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$ подалгебры   $\af$.
+В действительности весовые диаграммы нам не нужны, достаточно знать лишь размерности модулей
+$L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }$ умноженные на
+$\epsilon \left( u\right) $ (шаг vi). Полученные значения должны быть связаны с точками
+$\left\{ \left( 1\right) \left( 0\right) \left( -4\right) \left( -5\right) \right\}$ в $P_{\af}$.
+Сингулярный элемент $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ содержит следующий набор весов и их сингулярных кратностей:
 \begin{equation}
@@
 
-Applying formula (\ref{recurrent-relation}) with the fan
-$\Gamma_{A_1\to B_2}$ to the set (\ref{eq:25}) (step vii)
-we get zeros for the weights
-greater than the highest anomalous vector $(1;2)$
-and $k^{(1,0)}_1=2$ for the vector $(1;2)$ itself.
-For the anomalous weight (0;-3) on the boundary of $\bar{C}^{(0)}_{\af}$ the recurrent relation gives
+Применяя формулу (\ref{recurrent-relation}) с веером
+$\Gamma_{A_1\to B_2}$ к множеству (\ref{eq:25}) (шаг vii)
+мы получаем нули для весов больше старшего сингулярного вектора$(1;2)$ и  $k^{(1,0)}_1=2$ для самого вектора $(1;2)$.
+Для сингулярного веса $(0;-3)$ на границе $\bar{C}^{(0)}_{\af}$ рекуррентное соотношение дает
 \begin{equation*}
@@
 \end{equation*}
-the branching is completed: $L_{B_2\downarrow A_1}^{\omega_1}=
+и редукция завершена: $L_{B_2\downarrow A_1}^{\omega_1}=
 2L_{A_1}^{\omega_{\left(A_1\right)} }
@@
 
-\subsubsection{Embedding $B_2$ into $B_4$}
+\subsubsection{Вложение  $B_2$ в $B_4$}
 \label{sec:someth-high-dimens}
-Consider the regular embedding $B_2 \rightarrow B_4$.
-The corresponding Dynkin diagrams are presented in the Figure \ref{fig:dynkin}.
+Рассмотрим регулярное вложение $B_2 \rightarrow B_4$. Соответствующие диаграммы Дынкина показаны на Рисунке \ref{fig:dynkin}.
 \begin{figure}[h]
@@
   \includegraphics[width=100mm]{figure3}
-  \caption{The regular embedding $B_2 \rightarrow B_4$ described by dropping the node from the Dynkin diagram.
-  Remember that here $\afb$ is equal to $B_2$ while the diagram
-  shows only $A_1\oplus A_1$ (see Subsection \ref{sect-embeddings}).}
+  \caption{Регулярное вложение  $B_2 \rightarrow B_4$ получается путем исключения вершины из диаграммы Дынкина. 
+    Напомним, что в данном случае $\afb$ равна $B_2$, тогда как на диаграмме видна только подалгебра $A_1\oplus A_1$ (см. раздел \ref{sect-embeddings}).}
   \label{fig:dynkin}
@@
     \includegraphics[width=100mm,height=90mm]{figure4}
-  \caption{The singular element $e^{\gamma_0}\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
-  displayed in the weight subspace $P_{\af}$ for $\af=B_2$ with the basis $\left\{e_3,e_4\right\}$.
-  We see the projected singular weights $\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] +\gamma_0 | u \in U \right\}$
-  shifted by $\gamma_0$ and supplied by multipliers
-  $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.}
+  \caption{Сингулярный элемент  $e^{\gamma_0}\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ показан в весовом подпространстве $P_{\af}$, где $\af=B_2$ и базис равен $\left\{e_3,e_4\right\}$.
+Показаны спроектированные сингулярные веса $\left\{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] +\gamma_0 | u \in U \right\}$, сдвинутые на  $\gamma_0$ и снабженные множителям  $\epsilon(u)\dim\left(L_{\af_{\perp }}^{\mu_{\af_{\perp }}\left( u\right) }\right)$.}
   \label{fig:B4B2anom}
@@
   \includegraphics[height=80mm]{figure5}
-  \caption{The fan $\Gamma$ for $B_2\rightarrow B_4$ with values of $s(\gamma+\gamma_0)$ attributed to each $\gamma \in \Gamma$.}
+  \caption{Веер $\Gamma$ для вложения $B_2\rightarrow B_4$ со значениями функции $s(\gamma+\gamma_0)$, указанными при соответствующих весах $\gamma \in \Gamma$.}
   \label{fig:B4B2Fan}
@@
 
-In the orthonormal basis $\left\{e_1,\dots,e_4\right\}$ simple roots and positive roots of $B_4$ are
+В ортогональном базисе $\left\{e_1,\dots,e_4\right\}$ простые и положительные алгебры $B_4$ равны
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-The subalgebra $\af=B_2$ is fixed by the simple roots
+Подалгебра  $\af=B_2$ задается простыми корнями
 \begin{equation*}
@@
 \end{equation*}
-Its orthogonal counterpart $\afb=B_2$ has
+Ее ортогональный партнер $\afb=B_2$ определяется корнями
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-As far as the set $\Delta^+_{B_4} \setminus  \Delta^{+}_{\afb}$ is fixed the injection
-fan $\Gamma_{B_2 \to B_4}$ can be constructed using Definition \ref{fan-definition}.
-As far as for this injection $s\left( \gamma_0\right)=-1$ in the recursion formula we need only the factor
- $s\left(\gamma + \gamma_0\right)$.
-The result is presented in Figure \ref{fig:B4B2Fan}.
-
-Consider the $B_4$-module $L^{\mu}$ with the highest weight $\mu=2e_1 + 2 e_2 + e_3 + e_4$; \,
+После определения множества $\Delta^+_{B_4} \setminus  \Delta^{+}_{\afb}$ можно построить веер вложения $\Gamma_{B_2 \to B_4}$ применяя Определение \ref{fan-definition}.
+Так как для этого вложения $s\left( \gamma_0\right)=-1$, в рекуррентном соотношении нам нужен только множитель $s\left(\gamma + \gamma_0\right)$.
+Результат построения веера показан на Рисунке \ref{fig:B4B2Fan}.
+
+Рассмотрим модуль $L^{\mu}$ алгебры  $B_4$ со старшим весом $\mu=2e_1 + 2 e_2 + e_3 + e_4$; \,
 $\mathrm{dim}(L^{\left[0,1,0,2\right]})=2772$.
-Here the defect is nontrivial, $\mathcal{D}_{\af_{\perp }}=-2\left( e_1 + e_2 \right)$,
-while $\hf_{\bot}=0$. Among the singular weights there are
-48 vectors with the property $\left\{ \mu _{\af_{\perp }%
-}\left( u\right) =\pi _{\af_{\perp }}\left[ u(\mu +\rho
-)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\af_{\perp }}}\right\} $.
-The set $U=\left\{ u \right\}$ is thus fixed.
-Compute the dimensions of the corresponding $\afb$-modules with the highest weights
-$ \mu _{\af_{\perp }}\left( u\right)$ (using the Weyl dimension formula) and multiply them
-by $\epsilon\left( u \right)$. The result is the singular element
-$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ shown in Figure \ref{fig:B4B2anom}.
-
-Now one can place the fan $\Gamma$ (see Figure \ref{fig:B4B2Fan}) in the highest of the weights
-presented in Figure \ref{fig:B4B2anom} and start the recursive determination of the branching coefficients
-(using relation (\ref{recurrent-relation})):
+В данном случае дефект не тривиален, $\mathcal{D}_{\af_{\perp }}=-2\left( e_1 + e_2 \right)$, тогда как $\hf_{\bot}=0$. Среди сингулярных весов есть 
+48 векторов со свойством $\left\{ \mu _{\afb}\left( u\right) =\pi _{\af_{\perp }}\left[ u(\mu +\rho)-\rho \right] -\mathcal{D}_{\afb}\in \overline{C_{\afb}}\right\} $.
+Таким образом мы определили множество $U=\left\{ u \right\}$.
+Вычислим размерности соответствующих  $\afb$-модулей со старшими весами $\mu_{\afb}\left( u\right)$ (используем формулу Вейля для размерностей) и умножим их на $\epsilon\left( u \right)$.
+В результате получим сингулярный элемент
+$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$, показанный на Рисунке \ref{fig:B4B2anom}.
+
+Теперь поместим веер  $\Gamma$ (см.
+Рисунок \ref{fig:B4B2Fan}) в старший из весов, показанных на Рисунке \ref{fig:B4B2anom} и проведем рекурсивное вычисление коэффициентов ветвления (с использованием соотношения (\ref{recurrent-relation})):
 \begin{eqnarray*}
@@
 %\newpage
-\subsection{Applications to conformal field theory}
+\subsection{Примеры приложений в конформной теории поля}
 \label{sec:phys-appl}
 
-\subsubsection{Conformal embeddings}
+\subsubsection{Конформные вложения}
 \label{sec:conformal-embeddings}
 
-Branching coefficients for an embedding of affine Lie algebra into
-affine Lie algebra can be used to construct modular invariant
-partition functions for Wess-Zumino-Novikov-Witten models in conformal field theory
-(\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
-In these models current algebras are affine Lie algebras.
-
-The modular invariant partition function is crucial for the conformal theory to be valid
-on the torus and higher genus Riemann surfaces. It is important for the applications of
-CFT to string theory and to critical phenomena description.
-
-The simplest modular-invariant partition function has the diagonal form:
+Как мы уже объясняли в разделе \ref{sec:modular-invariance}, коэффициенты ветвления для вложения аффинной алгебры Ли в аффинную алгебру Ли можно использовать для построения модулярно-инвариантной статсуммы для моделей Весса-Зумино-Новикова-Виттена в двумерной конформной теории поля (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).
+В этих моделях аффинные алгебры Ли являются алгебрами токов.
+
+Модулярная инвариантность статсуммы необходима для самосогласованности теории на торе и римановых поверхностях высшего рода, что важно для приложений конформной теории поля в теории струн и описании критического поведения.
+
+Простейшая модулярно-инвариантная статсумма имеет диагональный вид:
 \begin{equation}
@@
 \end{equation}
-Here the sum is over the set of highest weights for integrable modules in a WZW-model
-and $\chi_{\mu}(\tau)$ are the normalized characters (see \cite{difrancesco1997cft}) of these modules.
-
-To construct nondiagonal modular invariants is not an easy problem,
-although for some models the complete classification of modular invariants is known \cite{1994hepthGannon,1995JMPGannon}.
-
-Consider the Wess-Zumino-Witten model with the affine Lie algebra $\af$.
-Nondiagonal modular invariants for this model can be constructed from the diagonal
-invariant if there exists an affine algebra $\mathfrak{g}$ such that $\af\subset\mathfrak{g}$.
-Then we can replace the characters of the $\mathfrak{g}$-modules in the diagonal
-modular invariant partition function (\ref{eq:34})
-by the decompositions
+Здесь суммирование ведется по множеству старших весов интегрируемых модулей в ВЗНВ-модели, а $\chi_{\mu}(\tau)$ -- это нормированные характеры (см. \cite{difrancesco1997cft}) этих модулей.
+
+Построение недиагональных модулярных инвариантов -- это нетривиальная проблема, хотя для некоторых моделей известна полная классификация модулярных инвариантов \cite{1994hepthGannon,1995JMPGannon}.
+
+Рассмотрим модель Весса-Зумино-Новикова-Виттена с аффинной алгеброй Ли $\af$.
+Недиагональные модулярные инварианты этой модели могут быть построены из диагонального инварианта, если существует аффинная алгебра  $\mathfrak{g}$, такая, что $\af\subset\mathfrak{g}$.
+Тогда мы можем заменить характеры  $\mathfrak{g}$-модулей в диагональной модулярно-инвариантной статсумме (\ref{eq:34}) на разложения
 \begin{equation*}
   \label{eq:32}
-\sum_{\nu \in P^{+}_{\af}}b^{(\mu)}_{\nu} \chi_{\nu}
-\end{equation*}
-containing normalized characters $\chi_{\nu}$ of the corresponding $\af$-modules.
-Thus we obtain a nondiagonal modular-invariant  partition function for the theory with
-the current algebra $\af$,
+\sum_{\nu \in P^{+}_{\af}}b^{(\mu)}_{\nu} \chi_{\nu},
+\end{equation*}
+содержащие нормированные характеры $\chi_{\nu}$ соответствующих $\af$-модулей. В результате мы получим недиагональную модулярно-инвариантную статсумму для теории с алгеброй токов $\af$,
 \begin{equation}
@@
 
-The effective reduction procedure is crucial for this construction.
-The embedding is required to preserve the conformal invariance.
-Let $X^{\alpha_j}_{-n_j}$ and $\tilde{X}^{\alpha'_j}_{-n_j}$ be the lowering generators for
-$\mathfrak{g}$ and for $\af\subset\mathfrak{g}$ correspondingly.
-Let $\pi_{\af}$ be the projection operator of
-$\pi_{\af}:\mathfrak{g}\longrightarrow \af$.
-In the theory attributed to $\mathfrak{g}$ with the vacuum $\left|\lambda\right>$
-the states can be described as
+Эффективная процедура редукции существенна для этой конструкции.
+Вложение должно сохранять конформную инвариантность.
+Пусть $X^{\alpha_j}_{-n_j}$ и $\tilde{X}^{\alpha'_j}_{-n_j}$ -- понижающие операторы для алгебры $\mathfrak{g}$ и подалгебры $\af\subset\mathfrak{g}$ соответственно.
+Обозначим через $\pi_{\af}$ оператор проекции $\pi_{\af}:\mathfrak{g}\longrightarrow \af$.
+В теории, связанной с $\mathfrak{g}$ и вакуумом $\left|\lambda\right>$ состояния строятся как
 \begin{equation*}
@@
 \end{equation*}
-And for the sub-algebra $\af$ the corresponding states are
+А для подалгебры $\af$ соответствующие состояния имеют вид
 \begin{equation*}
@@
 \end{equation*}
-The $\mathfrak{g}$-invariance of the vacuum entails its $\af$-invariance,
-but this is not the case for the energy-momentum tensor. So the energy-momentum tensor of the larger theory
-should contain only the generators $\tilde{X}$. Then the relation
+Инвариантность вакуума под действием $\mathfrak{g}$ влечет его инвариантность относительно действия $\af$, но это неверно для тензора энергии-импульса.
+Необходимо, чтобы тензор энергии-импульса объемлющей теории содержал только генераторы $\tilde{X}$.
+Тогда соотношение
 \begin{equation}
@@
 \end{equation}
-leads to the equality of central charges
+ведет к равенству центральных зарядов
 \begin{equation*}
@@
 \end{equation*}
-and to the relation
+и к уравнению
 \begin{equation}
@@
 \end{equation}
-Here $x_e$ is the so called "embedding index":
-$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$
-with $\Theta$, $\Theta_{\mathfrak{a}}$ being the highest roots of
-$\mathfrak{g}$ and $\mathfrak{a}$
-while $g$  and $a$ are the  corresponding dual Coxeter numbers.
-
-It can be demonstrated that solutions of equation (\ref{eq:111}) exist only
-for the level $k=1$ \cite{difrancesco1997cft}.
-
-The complete classification of conformal embeddings is given in \cite{schellekens1986conformal}.
-
-The relation (\ref{eq:111}) and the asymptotics of the branching functions can be used
+Здесь $x_e$ -- так называемый ``индекс вложения'':
+$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$, где $\Theta$, $\Theta_{\mathfrak{a}}$ -- старшие корни алгебр
+$\mathfrak{g}$ и $\mathfrak{a}$, а  $g$ и $a$ -- соответствующие дуальные числа Кокстера.
+
+Можно показать, что решения уравнения (\ref{eq:111}) существуют только для уровня $k=1$ \cite{difrancesco1997cft}.
+
+Полная классификация конформных вложения дана в работе \cite{schellekens1986conformal}.
+
+Соотношение (\ref{eq:111}) и асимптотика функций  and the asymptotics of the branching functions can be used
 to prove the finite reducibility theorem \cite{kac1988modular}.

### 2011-11-26 AffineLieAlgebras/Thesis/1.tex
+tr

@@
 
-Соотношение (\ref{eq:111}) и асимптотика функций  and the asymptotics of the branching functions can be used
-to prove the finite reducibility theorem \cite{kac1988modular}.
-It states that for a conformal embedding  $\af\longrightarrow\mathfrak{g}$
-only finite number of branching coefficients have nonzero values.
+Если рассмотреть соотношение (\ref{eq:111}) и асимптотику функций ветвления, то можно доказать теорему о конечной приводимости \cite{kac1988modular}.
+Она утверждает, что для конформного вложения  $\af\longrightarrow\mathfrak{g}$ лишь конечное число коэффициентов ветвления отлично от нуля.
 

### 2011-11-27 AffineLieAlgebras/Thesis/5.tex
Thesis partially structure cleaned, some translations in chapter 2.
Chapter 2 is completely translated. Description of computational package is moved to the last chapter.

--- 2011-09-28 AffineLieAlgebras/Thesis/3.tex
@@
-\chapter{Конформная теория поля}
-\label{cha:cft}
+\section{Вычислительные методы для теории представлений аффинных алгебр Ли}
+\label{cha:computational-methods}
+%% \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
+%% \newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
+%% \newcommand{\co}[1]{\stackrel{\circ }{#1}}
+%% \newcommand{\pia}{\pi_{\mathfrak{a}}}
+%% \newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
+%% \newcommand{\gf}{\mathfrak{g}}
+%% \newcommand{\af}{\mathfrak{a}}
+%\newcommand{\bff}{\mathfrak{b}}
+%% \newcommand{\afb}{\mathfrak{a}_{\bot}}
+%% \newcommand{\hf}{\mathfrak{h}}
+%\newcommand{\hfg}{\hf_{\gf}}
+%% \newcommand{\hfb}{\mathfrak{h}_{\bot}}
+%% \newcommand{\pf}{\mathfrak{p}}
+%% \newcommand{\aft}{\widetilde{\mathfrak{a}}}
 
-Подробное изложение \cite{difrancesco1997cft}.
+\begin{abstract}
+%% Text of abstract
+In this paper we present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
+Algorithms are based on the properties of weights and Weyl symmetry.
+The most important problems for us are the ones, concerning computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition.
+These problems have numerous applications in physics and we provide some examples of these applications.
+The program is implemented in popular computer algebra system {\it Mathematica} and works with finite-dimensional and affine Lie algebras.
 
-\section{Общие свойства}
-\label{sec:cft-general}
-Алгебра Вирасоро. Представления алгебры Вирасоро. Модулярная инвариантность.
+% A submitted program is expected to be of benefit to other physicists or physical chemists, or be an exemplar of good programming practice, or illustrate new or novel programming techniques which are of importance to some branch of computational physics or physical chemistry.
+%
+% Acceptable program descriptions can take different forms.
+The following Long Write-Up structure is a suggested structure but it is not obligatory.
+Actual structure will depend on the length of the program, the extent to which the algorithms or software have already been described in literature, and the detail provided in the user manual.
 
-\section{Модели Весса-Зумино-Новикова-Виттена}
-\label{sec:wzw}
-Связь с аффинными алгебрами Ли.
-Конформные вложения и недиагональные модулярные инварианты.
+%Your manuscript and figure sources should be submitted through the Elsevier Editorial System (EES) by using the online submission tool at \\
+% http://www.ees.elsevier.com/cpc.
 
-\section{Coset-модели}
-\label{sec:coset-models}
-Ветвления. Функции ветвления и статсуммы. 
-Калибровочные WZW-модели.
+%In addition to the manuscript you must supply: the program source code; job control scripts, where applicable; a README file giving the names and a brief description of all the files that make up the package and clear instructions on the installation and execution of the program; sample input and output data for at least one comprehensive test run; and, where appropriate, a user manual.
+These should be sent, via email as a compressed archive file, to the CPC Program Librarian at cpc@qub.ac.uk.
 
-\section{SLE}
-\label{sec:sle}
-SLE на WZW-моделях. Граничные условия. Парафермионы. SLE на coset-моделях.
+\end{abstract}
 
+%%
+%% Start line numbering here if you want
+%%
+% \linenumbers
+
+% Computer program descriptions should contain the following
+% PROGRAM SUMMARY.
+
+{\bf PROGRAM SUMMARY}%/NEW VERSION PROGRAM SUMMARY}
+  %Delete as appropriate.
+
+\begin{small}
+\noindent
+{\em Manuscript Title:}{\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of finite-dimensional and affine Lie algebras                                       \\
+{\em Authors:}Anton Nazarov                                                \\
+{\em Program Title:}Affine.m                                          \\
+{\em Journal Reference:}                                      \\
+  %Leave blank, supplied by Elsevier.
+{\em Catalogue identifier:}                                   \\
+  %Leave blank, supplied by Elsevier.
+{\em Licensing provisions:}none                                   \\
+  %enter "none" if CPC non-profit use license is sufficient.
+{\em Programming language:}Mathematica                                   \\
+{\em Computer:}i386-i686, x86\textunderscore 64                                               \\
+  %Computer(s) for which program has been designed.
+{\em Operating system:} Linux, Windows, MacOS, Solaris                                       \\
+  %Operating system(s) for which program has been designed.
+{\em RAM:} 5-500 Mb                                              \\
+  %RAM in bytes required to execute program with typical data.
+%{\em Number of processors used:}                              \\
+  %If more than one processor.
+%{\em Supplementary material:}                                 \\
+  % Fill in if necessary, otherwise leave out.
+{\em Keywords:} Mathematica; Lie algebra; affine Lie algebra; Kac-Moody algebra; root system; weights; irreducible modules, CFT, Integrable systems\\
+  % Please give some freely chosen keywords that we can use in a
+  % cumulative keyword index.
+{\em Classification:} 5 Computer Algebra, 4.2 Other algebras and groups                                         \\
+  %Classify using CPC Program Library Subject Index, see (
+  % http://cpc.cs.qub.ac.uk/subjectIndex/SUBJECT_index.html)
+  %e.g. 4.4 Feynman diagrams, 5 Computer Algebra.
+%{\em External routines/libraries:}                            \\
+  % Fill in if necessary, otherwise leave out.
+%{\em Subprograms used:}                                       \\
+  %Fill in if necessary, otherwise leave out.
+%{\em Catalogue identifier of previous version:}*              \\
+  %Only required for a New Version summary, otherwise leave out.
+%{\em Journal reference of previous version:}*                  \\
+  %Only required for a New Version summary, otherwise leave out.
+%{\em Does the new version supersede the previous version?:}*   \\
+  %Only required for a New Version summary, otherwise leave out.
+{\em Nature of problem:}\\
+  %Describe the nature of the problem here.
+Representation theory of finite-dimensional Lie algebras has many applications in different branches of physics, including elementary particle physics, molecular physics, nuclear physics.
+Representations of affine Lie algebras appear in string theories and two-dimensional conformal field theory used for the description of critical phenomena in two-dimensional systems.
+Also Lie symmetries play major role in study of quantum integrable systems.
+   \\
+{\em Solution method:}\\
+  %Describe the method solution here.
+We work with weights and roots of finite-dimensional and affine Lie algebras and use Weyl symmetry extensively.
+Central problems which are the computations of weight multiplicities, branching and fusion coefficients are solved using one general recurrent algorithm based on generalization of Weyl character formula.
+We also offer alternative implementation based on Freudenthal multiplicity formula which can be faster in some cases.
+   \\
+%{\em Reasons for the new version:}*\\
+  %Only required for a New Version summary, otherwise leave out.
+%   \\
+%{\em Summary of revisions:}*\\
+  %Only required for a New Version summary, otherwise leave out.
+%   \\
+{\em Restrictions:}\\
+  %Describe any restrictions on the complexity of the problem here.
+Computational complexity grows fast  with the rank of algebra, so computations for algebra of rank greater than 8 are non practical.
+   \\
+{\em Unusual features:}\\
+  %Describe any unusual features of the program/problem here.
+We offer the possibility to use traditional mathematical notation for objects in representation theory of Lie algebras in computations if {\bf Affine.m} is used in {\it Mathematica} notebook interface.
+   \\
+%{\em Additional comments:}\\
+  %Provide any additional comments here.
+%   \\
+{\em Running time:}\\
+  %Give an indication of the typical running time here.
+From seconds to days depending on rank of algebra and complexity of representations.
+   \\
+
+% \begin{thebibliography}{0}
+% \bibitem{1}Reference 1         % This list should only contain those items referenced in the
+% \bibitem{2}Reference 2         % Program Summary section.
+% \bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
+%                                % This list is different from the bibliography at the end of
+%                                % the Long Write-Up.
+% \end{thebibliography}
+% * Items marked with an asterisk are only required for new versions
+% of programs previously published in the CPC Program Library.\\
+\end{small}
+
+%% main text
+\section{Introduction}
+\label{intro}
+
+Representation theory of Lie algebras is of central importance for different areas of physics and mathematics.
+In physics Lie algebras are used to describe symmetries of quantum and classical systems.
+Computational methods in representation theory have a long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
+
+Most popular programs \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{fischbacher2002ilp}, \cite{coxweyl} are created to study representation theory of simple finite-dimensional Lie algebras.
+The main computational problems are the following:
+\begin{enumerate}
+\item Construction of root system which determine the properties of Lie algebra including its commutation relations.
+\item Weyl group traversal which is important due to Weyl symmetry of root system and characters of representations.
+\item Calculation of weight multiplicities, branching and fusion coefficients, which are essential for construction and study of representations.
+\end{enumerate}
+There are well-known algorithms for these tasks \cite{moody1982fast}, \cite{stembridge2001computational}, \cite{belinfante1989survey}, \cite{casselman1994machine}.
+The third problem is most computation-intensive.
+There are two different recurrent algorithms which are based on the Weyl character formula and the Freudenthal multiplicity formula.
+In this paper we analyze them both.
+
+Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and in a study of  integrable systems.
+But infinite-dimensional algebras are much harder to investigate and the number of available computer programs is much smaller in this case.
+
+Affine Lie algebras \cite{kac1990idl} constitute important and tractable class of infinite-dimensional Lie algebras.
+They are constructed as central extensions of loop algebras of (semi-simple) finite-dimensional Lie algebras and appear naturally in a study of Wess-Zumino-Witten and coset models in conformal field theory \cite{Walton:1999xc}, \cite{difrancesco1997cft}, \cite{Goddard198588}, \cite{Dunbar:1992gh}.
+
+The structure of affine Lie algebras allows to adapt for them computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
+The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of affine Lie algebras and representations was published in 1990.
+But we are not aware of software packages for popular computer algebra systems which can be used to extend these results.
+We address this issue and present {\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.
+We describe the features and limitations of the package in the present paper.
+We also provide representation-theoretical background of implemented algorithms and present examples of computations relevant to physical applications.
+
+The paper starts with an overview of Lie algebras and their representation theory (Sec.
+\ref{sec:theor-backgr}).
+Then we describe datastructures of {\bf Affine.m} used to present different objects related to Lie algebras and representations (Sec.
+\ref{sec:core-datastructures}) and discuss implemented algorithms (Sec.
+\ref{sec:comp-algor}).
+Next section consists of physically interesting examples (Sec.
+\ref{sec:examples}).
+The paper is concluded with the discussion of possible extensions and refinements (Sec.
+\ref{sec:conclusion}).
+
+\section{Theoretical background}
+\label{sec:theor-backgr}
+
+In this section we remind necessary definitions and present formulae used in computations.
+
+\subsection{Lie algebras of finite and affine types}
+\label{sec:lie-algebras-finite}
+
+{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it Lie bracket}.
+If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
+\begin{equation}
+  \label{eq:1}
+  [X^{i},X^{j}]=\sum_{k} C^{ij}_{k} X^{k}
+\end{equation}
+Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to commutator.
+{\it Semisimple} Lie algebra is a direct sum of simple Lie algebras.
+In the present paper we treat simple and semisimple Lie algebras.
+
+{\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
+We denote the elements of basis of $\hfg$ by $H^{i}$.
+
+Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
+{\it Weights} are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
+
+Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
+This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).
+
+{\it Loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
+\begin{equation}
+  \label{eq:6}
+  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
+\end{equation}
+Central extension leads to the appearance of an additional term
+\begin{equation}
+  \label{eq:7}
+   [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
+\end{equation}
+This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
+
+We do not treat twisted affine Lie algebras in the present paper.
+
+\subsection{Modules, weights and roots}
+\label{sec:weights-roots}
+
+Let $\gf$ be a inite-dimensional or an affine Lie algebra.
+
+Then $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
+\begin{equation}
+  \label{eq:2}
+  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
+\end{equation}
+Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms of the  vector space $V$ with the commutator as a bracket.
+
+For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by a special choice of basis $\{v_{j}\}$ in $V$:
+\begin{equation}
+  \label{eq:3}
+  H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
+\end{equation}
+Eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
+Vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
+The  weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
+The weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of the weight subspace.
+
+The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
+\begin{equation}
+  \label{eq:5}
+  E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
+\end{equation}
+Module structure can be encoded by the formal character of a module
+\begin{equation}
+  \label{eq:10}
+  \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
+\end{equation}
+Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
+A character can be specialized by taking its value on some element $\xi$ of $\hf$.
+
+Lie algebra is its own module with respect to a special kind of representation. The action that
+defines this representation is called adjoint and is given by the bracket $ad_{X} Y=[X,Y]$. 
+{\it Roots} are weights of the adjoint representation of $\gf$.
+They encode the commutation relations of algebra in the following way.
+Denote by $\Delta$ the set of roots.
+For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and the generators $E^{\alpha}, E^{-\alpha}$ such that
+\begin{align}
+  \label{eq:4}
+  &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
+  &\left[E^{\alpha},E^{\beta}\right]=
+  \begin{cases}
+    N_{\alpha,\beta} E^{\alpha+\beta}, & \mbox{if}\; \alpha+\beta\in \Delta\\
+    \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
+    0,&\mbox{otherwise}
+  \end{cases}
+\end{align}
+
+Given the root system $\Delta$ we can choose the set of positive roots.
+This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
+Elements of $-\Delta^{+}$ are called negative roots.
+
+A positive root is {\it simple} if it cannot be written as a sum of positive roots.
+The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis in $\hfg^{*}$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive simultaneously.
+In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
+By numbering simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
+Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
+$\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}).
+{\it Comarcs} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
+
+Although for affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
+The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.
+The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- the highest root of the algebra $\go$.
+Note that root multiplicity $\mathrm{mult}(\alpha)$ for an affine Lie algebra root can be greater than one.
+
+Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called the Borel subalgebra.
+
+{\it Parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
+It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
+{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .
+
+The {\it Weyl group} $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
+\begin{equation}
+  \label{eq:8}
+  s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
+\end{equation}
+Root system and characters of representation are invariant with respect to the Weyl group  action. Root system can be reconstructed from the set of simple roots by the Weyl group transformations.
+
+Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
+
+Consider an action of the element $s_{\alpha}s_{\alpha+\delta}$ of the Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ being a simple root of the underlying finite-dimensional Lie algebra $\gf$.
+Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
+So the Weyl group can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to roots of $\gf$.
+
+A Weyl group element can be presented as a product of elementary reflections in multiple ways.
+Number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$.
+We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for the parity of the number of Weyl reflections generating $w$.
+
+Fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
+It is called a {\it main Weyl chamber}.
+
+The {\it Cartan matrix} $A$ is defined by products of simple roots
+\begin{equation}
+  \label{eq:9}
+  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}
+\end{equation}
+and can be used for a compact description of Lie algebra commutation relations in the Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
+
+Form \eqref{eq:9} induces a basis dual  to the simple
+roots basis. It is called the {\it fundamental weights basis}. We denote
+its elements by $\omega_i$:
+\begin{equation}
+  \label{eq:20}
+  \langle\omega_i,\alpha_j\rangle=\frac{2(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
+\end{equation}
+For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
+For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
+Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
+
+ The sum of fundamental weights $\rho=\sum_{i} \omega_{i}$ is called a {\it Weyl vector}. It is an important tool in representation theory.
+
+\subsection{Highest weight modules}
+\label{sec:high-weight-modul}
+
+We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e.
+if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
+
+Highest weight module $V^{\mu}$ contains a single highest weight $\mu$, all the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
+
+The most simple type of highest weight modules is the Verma module
+$M^{\mu}$. Its space can be defined as a module
+\begin{equation}
+  \label{eq:17}
+  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}),
+\end{equation}
+with respect to a multiplication in $U(\gf)$ and
+$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
+Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
+Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D^{\lambda}(\bff_{+})$.
+
+Weight multiplicities in Verma modules can be found by applying the Weyl
+character formula
+\begin{equation}
+  \label{eq:11}
+  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
+\end{equation}
+Here we have used the Weyl denominator identity
+\begin{equation}
+  \label{eq:12}
+  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
+\end{equation}
+and $\epsilon \left( w\right) :=\det \left( w\right)$ is equal to 
+the parity of the sequence of Weyl reflections generating $w$.
+
+Verma module $M^{\mu}$ has the unique maximal submodule and the
+unique nontrivial simple quotient $L^{\mu}$ which is an
+{\it irreducible highest weight module}.
+
+Irreducible highest weight modules have no non-trivial submodules. 
+The Weyl character formula for
+irreducible highest weight modules is
+\begin{equation}
+  \label{eq:13}
+  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
+\end{equation}
+Thus the character of an irreducible highest weight module can be
+seen as a combination of characters of Verma modules. ( This
+fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
+(\cite{bernstein1976category,bernstein1971structure}, see also
+\cite{humphreys2008representations}).)
+
+Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
+%% !!! \Delta_{p}?!
+\begin{equation*}
+M_{I}^{\mu}=U\left( \gf\right)\otimes _{U\left( \pf_{I}\right) }L_{\pf_{I}}^{\mu}.
+\end{equation*}
+Introduce a formal element $R_{I}:=\prod_{\alpha \in \Delta
+^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
+^{\mathrm{mult}(\alpha )}$. Then the character of a generalized
+Verma module can be written as
+\begin{equation}
+  \label{eq:18}
+  \mathrm{ch}M_{I}^{\mu}=\frac{1}{R_{I}}\mathrm{ch}L_{\pf_{I}}^{\mu }.
+\end{equation}
+
+%% Define external border of irreducible representation here
+
+We can use the Weyl character formula to obtain recurrent relations for weight multiplicities -- important tools for calculations \cite{il2010folded,kulish4sfa}.
+
+For irreducible highest-weight modules recurrent relations have the following form
+\begin{equation}
+\label{eq:14}
+m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
+-\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
+(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
+\end{equation}
+Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side.
+In case of Verma module it is just $\delta_{\xi,\mu}$.
+For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
+
+Other recurrent formula can be obtained from a study of Casimir
+elements action on irreducible highest weight modules
+\cite{humphreys1997introduction}:
+\begin{equation}
+  \label{eq:15}
+  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
+\end{equation}
+It is called the Freudenthal multiplicity formula.
+Note that it is applicable only to irreducible modules.
+
+We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.
+
+Now consider an algebra $\gf$ and a reductive subalgebra
+$\af\subset \gf$. Simple roots $\beta_{i}$ of the subalgebra $\af$
+can be presented as linear combinations of $\gf$-algebra roots
+$\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j}
+\alpha_{j},\ j=1,\dots,r_{\af}$.
+
+Each irreducible $\gf$-module is also an $\af$-module, although
+$L^{\mu}_{\gf}$ is in general not irreducible as $\af$-module. 
+It can be
+decomposed into a direct sum of irreducible $\af$-modules:
+\begin{equation}
+  \label{eq:16}
+  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
+\end{equation}
+Coefficients in such a decomposition are called branching
+coefficients.
+
+It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. 
+This traditional approach has serious limitations especially in case of affine Lie algebras. We discuss them in the end of section \ref{sec:comp-algor}.
+
+Now we describe an alternative approach which is based on recurrent properties of branching coefficients. 
+But before we proceed to these recurrent relations we need several additional definitions.
+
+For a subalgebra $\af\subset \gf$ we introduce the subalgebra
+$\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
+orthogonal to $\hf_{\af}$,
+\begin{equation*}
+\hf_{\perp \af}^{\ast }:=\left\{ \eta \in \hf^{\ast }|\forall
+h\in \hf_{\af};\eta \left( h\right) =0\right\} ,
+\end{equation*}
+and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
+to roots of $\af$,
+\begin{eqnarray}
+\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
+h\in \hf_{\af};\beta \left( h\right) =0\right\} ,
+\label{delta a ort} \\
+\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
+}^{+}|\forall h\in \hf_{\af};\beta ^{+}\left( h\right) =0\right\} .
+\notag
+\end{eqnarray}
+Let $W_{\afb}$ be a subgroup of $W$ generated by
+reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
+}}^{+}$. The subsystem $\Delta _{\afb}$ determines a 
+subalgebra $\afb$ with the Cartan subalgebra $\hf_{\af%
+_{\perp }}$.
+
+The Cartan subalgebra $\frak{h}$ can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
+\frak{h}_{\afb}\oplus \frak{h}_{\perp }$
+
+We also introduce the notations
+\begin{eqnarray}
+\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\qquad
+\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
+\end{eqnarray}
+
+For $\af$ and $\afb$ we consider the
+corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\af_{\perp
+}} $ and compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
+D}_{\afb}$ of the injection:
+\begin{equation}
+\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho , \qquad
+\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
+_{\perp }}\rho .  \label{defect-ort}
+\end{equation}
+
+%%!!! Define P^+
+For $\mu \in P^{+}$ consider the linked weights $\left\{ \left(
+w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections
+to
+$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
+\mathcal{D}_{\afb}$:
+\begin{equation*}
+\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
+w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
+\end{equation*}
+Among the weights $\left\{ \mu _{\af_{\perp
+}}\left( w\right) |w\in W\right\} $ one can always choose those located in
+the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
+set of representatives $u$ for the classes $W/W_{\afb}$ such
+that
+
+\begin{equation}
+U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
+\overline{C_{\afb}}\right\} \quad .  \label{U-def}
+\end{equation}
+Thus we can form the subsets:
+\begin{equation}
+\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
+\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
+_{\perp }},\quad u\in U,  \label{mu-a}
+\end{equation}
+and
+\begin{equation}
+\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
+\label{mu-a-tilda}
+\end{equation}
+
+Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
+since it is built on a subset of roots of the algebra $\mathfrak{g}$.
+
+Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients.
+If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.
+
+Now we can use the Weyl character formula to write a
+recurrent relation \cite{2010arXiv1007.0318L} for signed branching
+coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
+injection $\af\hookrightarrow \gf$:
+\begin{equation}
+\begin{array}{c}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
+_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
+\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right.  \\
+\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
+}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
+}\right) .
+\end{array}
+\label{recurrent-rel}
+\end{equation}
+The recursion is governed by the set $\Gamma _{\af\rightarrow \gf}$ called the injection fan. The latter is defined by the
+carrier set $\left\{ \xi \right\} _{\af\rightarrow \gf}$ for the
+coefficient function $s(\xi )$
+\begin{equation*}
+\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}:=\left\{
+\xi \in P_{\widetilde{\af}}|s(\xi )\neq 0\right\}
+\end{equation*}
+appearing in the expansion
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
+_{\widetilde{\af}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
+_{\af}(\pi _{\widetilde{\af}}\alpha )}=-\sum_{\gamma \in P_{%
+\widetilde{\af}}}s(\gamma )e^{-\gamma };\quad
+\end{equation}
+The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
+\right\} $ -- and the zero element is to be eliminated:
+\begin{equation}
+\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma
+_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
+\end{equation}
+Formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
+
+If the root system of $\afb$ is generated by some subset of $\gf$
+simple roots $\alpha_{1},\dots,\alpha_{r}$ then the recurrent
+relation (\ref{recurrent-rel}) is connected with the generalized
+Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules
+\cite{2011arXiv1102.1702L}.
+
+Another particular case of this formula is connected with tensor
+product decompositions. Consider the tensor product of two
+irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$. It is also a
+$\gf$-module but not irreducible in general. So
+\begin{equation}
+  \label{eq:19}
+  L^{\mu}\otimes L^{\nu}=\bigoplus_{\gamma} f^{\mu\nu}_{\gamma}L^{\gamma}
+\end{equation}
+The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion
+coefficients. The problem of computation of fusion coefficients is
+equivalent to branching problem for the diagonal subalgebra
+$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
+
+In the case of affine Lie algebras $\gf, \af$  the multiplicities
+$m_{\nu}$ and the corresponding branching coefficients $b_{\nu}$
+can be regarded as the coefficients in power series decomposition
+of string and branching functions correspondingly:
+\begin{align}
+  \label{eq:21}
+  &\sigma_{\nu}(q)=\sum_{n=0}^{\infty} m_{\nu-n\delta} q^n, \quad \nu=\sum_j c_j \omega_j,\quad c_j\geq 0\\
+  & b_{\nu}(q)=\sum_{n=0}^{\infty} b_{\nu-n\delta} q^n,\quad  \nu=\sum_j c_j \omega_j, \quad c_j\geq 0
+\end{align}
+String and branching functions have  modular and analytic properties which are important for conformal field theory, especially in  coset models and the study of CFT on higher genus surfaces \cite{kac1988modular}, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}.
+
+{\bf Affine.m}  calculates weight multiplicities and branching coefficients for affine Lie algebras up to some finite grade.
+We present examples of computations in Sections \ref{sec:string-funct-affine}, \ref{sec:branch-funct-coset}.
+Now we proceed to the description of datastructures and algorithms implemented in {\bf Affine.m}.
+
+\section{Core datastructures}
+\label{sec:core-datastructures} Having introduced necessary
+mathematical objects, problems and relations we now describe the
+related datastructures of {\bf Affine.m}. Although {\it
+Mathematica} is untyped language it is possible to create
+structured objects and do type checks with patterns
+\cite{shifrinmathematica}, \cite{maeder2000computer}.
+\subsection{Weights}
+\label{sec:weights}
+
+Weights are represented  by two data-structures: \lstinline{finiteWeight} for finite-dimensional Lie algebras and \lstinline{affineWeight}  for affine.
+
+Internally the finite weight is a \lstinline{List} with the
+\lstinline{Head} \lstinline{finiteWeight}, its components are the
+coordinates of the weight in the orthogonal Bourbaki  basis
+\cite{bourbaki2002lie}.
+
+Affine weight is an extension of a finite weight by supplying it
+with level and grade coordinates. There is a set of functions
+defined for finite and affine weights. The complete list can be
+found in  online help of the package. The most important
+are definitions of addition, multiplication by a number and a
+scalar product (bilinear form) for weights. These definitions
+allow to use traditional notation when working with {\bf
+Affine.m}:
+\begin{lstlisting}
+  w=makeFiniteWeight[{1,0,3}];
+  v=makeFiniteWeight[{3,2,1}];
+  2*w+v==makeFiniteWeight[{5,2,7}]
+  w.v==6
+\end{lstlisting}
+
+The use of orthogonal basis in the internal structure of weights allows us to work with weights without complete specification of root system which is useful for study of branching, since roots of the subalgebra can be specified by hand.
+
+\subsection{Root systems}
+\label{sec:root-systems}
+
+To specify an algebra of finite or affine type it is enough to fix
+its root system. Root systems are represented by two datatypes
+\lstinline{finiteRootSystem} and \lstinline{affineRootSystem}. The
+latter is an extension of the former. We offer several different
+constructors for these datastructures. It is possible to specify
+the set of simple roots explicitly, for example to study the
+subalgebra $B_2\subset B_4$ we can use the definition
+\begin{lstlisting}
+  b2b4=makeFiniteRootSystem[ { {1,-1,0,0}, {0,1,0,0} } ]
+\end{lstlisting}
+There are constructors for root systems of simple finite-dimensional Lie algebras:
+\begin{lstlisting}
+  b2=makeSimpleRootSystem[B,2]
+\end{lstlisting}
+We use typographic features of {\it Mathematica} frontend to offer mathematical notation for simple Lie algebras:
+
+\begin{lstlisting}[mathescape=true]
+  $B_2$ == makeFiniteRootSystem[ { {1, -1}, {0, 1} }]
+\end{lstlisting}
+
+Non-twisted affine root systems can be created as affine extensions of finte root systems, e.g.
+\begin{lstlisting}
+  b2affine = makeAffineExtension[b2]
+\end{lstlisting}
+In notebook interface this can be written simply as $\hat{B}_2$.
+
+Semisimple Lie algebras can be created as sums of simple:
+\begin{lstlisting}[mathescape=true]
+  $A_1\oplus A_1$ == finiteRootSystem[2, 2, {finiteWeight[2, {1, 0}], finiteWeight[2, {0, 1}]}]
+\end{lstlisting}
+%% The problem is here
+
+Predicate \lstinline{rootSystemQ} checks if the object is root systems of finite or affine type.
+
+List of simple roots is the property of root system so it is accessed as \lstinline{rs[simpleRoots]}.
+
+We have implemented several functions to get major properties of root systems. Weyl vector is given by the function \lstinline{rho[rs_?rootSystemQ]}:
+\begin{lstlisting}[label=list:1]
+  In[1]  =  rho[b2]
+  Out[1]  =  finiteWeight[2, {3/2, 1/2}]
+\end{lstlisting}
+Positive roots can be constructed with \lstinline{positiveRoots[rs_?rootSystemQ]}.
+For an affine Lie algebra this and related functions return the list up to fixed grade.
+This grade limit is set through the value of \lstinline{rs[gradeLimit]} which is equal to 10 by default.
+List of roots (up to \lstinline{gradeLimit}) is returned by \lstinline{roots[rs]}.
+Cartan matrix and fundamental weights are calculated by the functions \lstinline{cartanMatrix} and \lstinline{fundamentalWeights} correspondingly.
+
+It is possible to specify a weight of a Lie algebra by its Dynkin labels
+\begin{lstlisting}
+  weight[b2][1,2] == makeFiniteWeight[{2, 1}]
+\end{lstlisting}
+The function \lstinline{dynkinLabels[rs_?rootSystemQ][wg_?weightQ]} returns Dynkin labels of weight \lstinline{wg} in the root system \lstinline{rs}.
+
+Elements of Weyl group are specified by the set of indices of reflections, so the element  $w=s_{1}s_{2}s_{1}$ of the Weyl group of algebra $B_{2}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
+Then it can be applied to the weights:
+\begin{lstlisting}
+  w = weylGroupElement[b2][1,2,1];
+  w @ makeFiniteWeight[{1,0}] == makeFiniteWeight[{-1,0}]
+\end{lstlisting}
+
+Computation of lexicographically minimal form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching in {\it Mathematica}.
+In \cite{KallenShortlex} rewrite rules for simple finite dimensional and affine Lie algebras are presented as {\it Mathematica} patterns.
+Our presentation of Weyl group elements is compatible with the code of \cite{KallenShortlex}
+\begin{lstlisting}[mathescape=true]
+  In[1]  = $<<$A3reduce;
+           reduce[s[1,2,1,2,1,3,2,1,1]]
+  Out[1] = s[2, 3, 2]
+
+  In[2]  = (weylGroupElement[$A_{3}$] @@ reduce[s[1,2,1,2,1,3,2,1,1]]) @ weight[$A_{3}$][-1,-2,-1]
+  Out[2] = finiteWeight[4, {-2, 2, 1, -1}]
+
+  In[3]  = dynkinLabels[$A_{3}$][Out[2]]
+  Out[3] = {-4, 1, 2}
+\end{lstlisting}
+
+\subsection{Formal elements}
+\label{sec:formal-elements}
+
+We represent formal characters of representations by special structure \lstinline{formalElement}.
+This structure is a hash-table implemented with \lstinline{DownValues}.
+The keys are weights at the exponents and the values are the  corresponding multiplicities.
+\lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]!
+creates data-structure which represents the element $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ of the formal algebra $\mathcal{E}$.
+The operations in $\mathcal{E}$ are implemented for \lstinline{formalElement} data-type: formal elements can be added, multiplied by a number or by an exponent of a weight.
+There exists also a multiplication of formal elements but no division.
+\begin{lstlisting}[mathescape=true]
+  In[1]  = makeFormalElement[{makeFiniteWeight[{1,1}],makeFiniteWeight[{0,0}]},{1,2}] *
+             (2 * Exp[makeFiniteWeight[{1,0}]] *
+             makeFormalElement[{makeFiniteWeight[{1,1}],makeFiniteWeight[{0,0}]},{1,2}]);
+  In[2]  = In[1][weights]
+  Out[2] = {finiteWeight[2, {1, 0}], finiteWeight[2, {2, 1}], finiteWeight[2, {3, 2}]}
+
+  In[3]  = In[1][multiplicities]
+  Out[3] = {8, 8, 2}
+\end{lstlisting}
+
+\subsection{Modules}
+\label{sec:modules}
+
+{\bf Affine.m} can be used to study different kinds of modules, i.e.
+Verma modules, irreducible modules and parabolic Verma modules.
+We need datastructure \lstinline{module} to represent generic module of Lie algebra $\gf$.
+Module properties can be deduced from its set of singular weights using Weyl character formulae \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}.
+Set of singular weights can have Weyl symmetry.
+It can be a symmetry with respect to the Weyl group $W_{\gf}$ or with respect to some subalgebra $W_{\af}$ as in the case of parabolic Verma modules.
+Then it is possible to study only the main Weyl chamber $C_{\af}$.
+To use this symmetry generic constructor for \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],limit:10}.
+Here \lstinline{rs} is the root system of the Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is the root system corresponding to the Weyl group $W_{\af}$ which is the (anti-)symmetry of the set of singular weights.
+Parameter \lstinline{limit} limits computation for infinite-dimensional modules such as Verma or parabolic Verma.
+There are several specialized constructors for different types of highest weight modules:
+\begin{lstlisting}[mathescape=true]
+vm=makeVermaModule[$B_{2}$][{2,1}];
+pm=makeParabolicVermaModule[$B_{2}$][weight[$B_{2}$][2,1],{1}];
+im=makeIrreducibleModule[$B_{2}$][2,1];
+GraphicsRow[textPlot/@{im,vm,pm}]
+$\includegraphics[width=130mm]{figures/irrep-verma-pverma}$
+\end{lstlisting}
+
+As we already stated properties of a module are encoded by its singular element.
+Function \lstinline{singularElement[m_module]} returns singular element of a module as \lstinline{formalElement} datastructure.
+Character (up to \lstinline{limit} for (parabolic) Verma modules) is returned by the function \lstinline{character[m_module]}.
+Direct sum of modules is a module and we use natural notation
+\begin{lstlisting}[mathescape=true]
+im1=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
+im2=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][1,2]];
+textPlot[im1$\oplus$ im2]
+$\includegraphics[width=60mm]{figures/irrep-sum}$
+\end{lstlisting}
+
+The tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
+\begin{lstlisting}[mathescape=true]
+textPlot[makeIrreducibleModule[$A_{1}$][5]$\otimes$ makeIrreducibleModule[$A_{1}$][3]];
+$\includegraphics[width=60mm]{figures/tensor-product}$
+\end{lstlisting}
+\section{Computational algorithms}
+\label{sec:comp-algor}
+
+As we have already stated in section \ref{sec:high-weight-modul} there exist two recurrent relations which can be used to calculate weight multiplicities in irreducible modules.
+Both algorithms proceed in the following way to calculate weight multiplicities:
+\begin{enumerate}
+\item Create the list of weights in the main Weyl chamber by subtracting all possible combinations of simple roots from the highest weight (e.g.
+for finite-dimensional algebra subtract $\alpha_{1}$ from $\mu$ while inside $\bar C$, then subtract $\alpha_{2}$ from all the weights already obtained etc).
+\item Sort the list of weights by their product with the Weyl vector.
+\item Use a recurrent formula. If the weight required for recurrent computation is outside the main chamber use the Weyl symmetry.
+\end{enumerate}
+The difference in the performance of algorithms is in the number of previous values required to get the multiplicity of weight under consideration.
+For  the Weyl formula based recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in the Weyl group (if we are far from the boundary of representation diagram).
+When the Freudenthal formula \eqref{eq:15} is used number of previous values grows with the distance from the external border of representation.
+So the Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
+Note that the Freudenthal formula is valid for irreducible modules only, so it can not be used to study (generalized) Verma modules.
+
+We have made some experiments with our implementations of the Freudenthal formula and formula \eqref{eq:15} and have got Figure  \ref{fig:freudenthal-racah-times}, which depicts the dependence of the computation time on the number of weights in a module.
+
+\begin{figure}[h]
+  \noindent\centering{
+    \includegraphics[width=80mm]{figures/timing}
+  }
+  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{eq:14} (solid) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
+\label{fig:freudenthal-racah-times}
+
+\end{figure}
+
+In the calculation of branching coefficients the application of the Freudenthal formula requires a complete construction of formal characters of an algebra module and all the representations of a subalgebra.
+It is impractical when the rank of algebra and subalgebra are big, for example for maximal subalgebras.
+
+Alternative algorithm which was presented in the paper \cite{2010arXiv1007.0318L}  contains the following steps:
+
+\begin{enumerate}
+\item  Construct the root system $\Delta _{\af}$ for the embedding $%
+\af\rightarrow \frak{g}$.
+
+\item  Select all the positive roots $\alpha \in \Delta ^{+}$ orthogonal
+to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
+
+\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. Relation
+ (\ref{eq:6}) defines the sign function
+ $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
+ $\gamma_0$ is to be subtracted to get the fan:
+ $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}$.
+
+\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
+)-\rho ;\;w \in W\right\} $ of singular weights for the $\frak{g}$%
+-module $L^{(\mu )}$.
+
+\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
+}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
+)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
+\af_{\perp }}}}\right\} $. Since the set $\Delta_{\afb }^{+}$ is fixed
+we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
+}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
+\af_{\perp }}}}$ (by computing its scalar product with the fundamental
+weights of $\afb^{+}$).
+
+\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
+calculate dimensions of the corresponding modules, $\mathrm{\dim }\left(
+L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
+}\left( u\right) }\right) $, using the Weyl dimension formula and construct
+the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
+
+\item  Calculate the anomalous branching coefficients using 
+recurrent relation (\ref{recurrent-rel}) and select among them those
+corresponding to the weights in the main Weyl
+chamber $\overline{C_{\af}}$.
+\end{enumerate}
+
+We can speed up the algorithm by
+one-time computation of the representatives of the conjugate classes $%
+W/W_{\afb }$.
+
+Consider the regular embedding $B_{2}\subset B_{4}$.
+In this case the fan consists of 24 elements.
+In order to decompose $B_{4}$ module we need to construct the subset of singular weights of the module which projects to the main Weyl chamber of the subalgebra $B_{2}$.
+The full set of singular weights consists of 384 elements.
+The required subset contains at most 48 elements.
+So the time for the construction of this required subset is negligible if the number of branching coefficients is greater than that.
+We may estimate the total number of required operations for the computation of branching coefficients as the product of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients and the number of elements in the fan.
+In the case of a direct algorithm we need to compute the multiplicities for each module in the decomposition, so the number of operations grows faster than the square of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients.
+
+To further illustrate this performance issue we include Figure \ref{fig:branching} where we show the time required for computations of branching coefficients for $B_{3}\subset B_{4}$.
+
+\begin{figure}[h]
+  \noindent\centering{
+   \includegraphics[width=100mm]{figures/branching-timing}
+  }
+  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{recurrent-rel} (solid) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
+  \label{fig:branching}
+\end{figure}
+
+\section{Examples}
+\label{sec:examples}
+In this section we present some examples of computations available with {\bf Affine.m} with the code required to produce these results.
+
+\subsection{Tensor product decompositon for finite-dimensional Lie algebras}
+\label{sec:tens-prod-decomp}
+
+Computation of fusion coefficients for the decomposition of tensor product of highest-weight modules to the direct sum of irreducible modules has numerous applications in physics.
+For example, we can consider the spin of a composite system such as an atom.
+Another interesting example is integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of a Lie algebra $\gf$ with a $\gf$-invariant Hamiltonian $H$, describing the nearest-neighbour spin-spin interaction.
+In order to solve such a system, i.e.
+to find eigenstates of the Hamiltonian, we need to decompose $L^{\otimes N}$ into the direct sum of irreducible $\gf$-modules of lower dimension and diagonalize the Hamiltonian on these modules.
+
+For fundamental representations of simple Lie algebras it is sometimes possible to get an analytic result describing the dependence of decomposition coefficients on $N$ (See \cite{LyakhovskyPostnova2011}).
+Our code provides numerical values and can be used to check this analytic results.
+
+Consider a tensor power of $B_{2}$ the first fundamental representation $\left(L^{[1,0]}\right)^{\otimes 4}$. Decomposition coefficients are just the branching
+ coefficients for the tensor power module reduced to the diagonal subalgebra $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$. So the following code calculates these coefficients:
+\begin{lstlisting}[mathescape=true]
+fm = makeIrreducibleModule[$B_{2}$][1, 0];
+tp = ((fm$\otimes$ ]fm)$\otimes$ fm)$\otimes$]fm;
+subs = makeFiniteRootSystem[
+  {1/4*{1, -1, 1, -1, 1, -1, 1, -1}, 
+   1/4*{0, 1, 0, 1, 0, 1, 0, 1}}];
+bc = branching[tp, subs];
+{bc[#], dynkinLabels[subs][#]} & /@ bc[weights]
+\end{lstlisting}
+It produces a list of highest weights and tensor product decomposition coefficients:
+\begin{lstlisting}
+{{1, {4, 0}}, {3, {2, 2}}, {0, {3, 0}}, 
+{2, {0, 4}}, {3, {1, 2}}, {6, {2, 0}}, 
+{6, {0, 2}}, {1, {1, 0}}, {3, {0, 0}}}]
+\end{lstlisting}
+
+Returning to the problem of spin chain Hamiltonian diagonalization we can see that instead of diagonalizing operator in space of dimension $625$ we can diagonalize operators in the spaces of dimensions $55, 81, 30, 35, 35, 14, 10, 5, 1$.
+
+\subsection{Branching and parabolic Verma modules}
+\label{sec:branch-parab-verma}
+
+We illustrate the generalized BGG-resolution by the diagrams of $G_{2}$ parabolic Verma modules which appear in the decomposition of irreducible module $L^{[1,1]}_{G_{2}}$:
+\begin{equation}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
+u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
+u\right) }.  \label{char-in-gen-verma-mod}
+\end{equation}
+The character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, characters of the generalized Verma modules in decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}.
+Characters in the upper row appear in \eqref{char-in-gen-verma-mod} with positive sign and in the lower row -- with negative.
+
+\begin{figure}[h]
+  \noindent\centering{
+    \includegraphics[width=80mm]{figures/G2-irrep}
+  }
+  \caption{Character of the irreducible $G_{2}$-module $L^{[1,1]}$}
+  \label{branching-bgg}
+\end{figure}
+\begin{figure}[h]
+  \noindent\centering{
+    \includegraphics[width=150mm]{figures/G2-pverma}
+  }
+  \caption{Characters of $G_{2}$ generalized Verma modules appearing in the decomposition of $L^{[1,1]}$.
+Parabolic Verma modules in the upper row appear in the decomposition with a positive sign, in the lower row -- with a negative.}
+  \label{g2-pverma}
+\end{figure}
+
+\subsection{String functions of affine Lie algebras and CFT models}
+\label{sec:string-funct-affine}
+
+String functions can be used to present formal characters of affine Lie algebra highest weight representation.
+They have interesting analytic and modular properties \cite{kac1990idl,kac1988modular,kac1984infinite}.
+
+{\bf Affine.m} produces power series decomposition for string functions.
+Consider an affine Lie algebra $\hat{sl(3)}=\hat A_{2}$ and its highest weight module $L^{(1,0,0)}$.
+To get the string functions we can use the code:
+\begin{lstlisting}[mathescape=true]
+stringFunctions[$\hat A_2$,{1,1,2}]
+{{0, 0, 4}, 
+  $2 q + 10 q^2 + 40 q^3 + 133 q^4 + 398 q^5 + 1084 q^6 + 2760 q^7 + 6632 q^8 + 15214 q^9 + 33508 q^{10}$}, 
+{{0, 3, 1}, 
+  $2 q + 12 q^2 + 49 q^3 + 166 q^4 + 494 q^5 + 1340 q^6 + 3387 q^7 + 8086 q^8 + 18415 q^9 + 40302 q^{10}$}, 
+{{1, 1, 2}, 
+  $1 + 6 q + 27 q^2 + 96 q^3 + 298 q^4 + 836 q^5 + 2173 q^6 + 5310 q^7 + 12341 q^8 + 27486 q^9 + 59029 q^{10}$}, 
+{{2, 2, 0}, 
+  $1 + 8 q + 35 q^2 + 124 q^3 + 379 q^4 + 1052 q^5 + 2700 q^6 + 6536 q^7 + 15047 q^8 + 33248 q^9 + 70877 q^{10}$}, 
+{{3, 0, 1}, 
+  $2 + 12 q + 49 q^2 + 166 q^3 + 494 q^4 + 1340 q^5 + 3387 q^6 + 8086 q^7 + 18415 q^8 + 40302 q^9 + 85226 q^{10}$}
+\end{lstlisting}
+Similarly for the affine Lie algebra $\hat G_{2}$ we get
+\begin{lstlisting}[mathescape=true]
+stringFunctions[$\hat G_2$,{1,1,0}]
+{{2, 0, 0}, 
+  $1 + 8 q + 37 q^2 + 138 q^3 + 431 q^4 + 1227 q^5 + 3208 q^6 + 7901 q^7$}, 
+{{0, 0, 1}, 
+  $3 q + 18 q^2 + 73 q^3 + 247 q^4 + 736 q^5 + 2000 q^6 + 5070 q^7$}, 
+{{1, 1, 0},
+  $1 + 7 q + 32 q^2 + 117 q^3 + 370 q^4 + 1055 q^5 + 2780 q^6 + 6880 q^7$}, 
+{{0, 2, 0}, 
+  $3 q + 15 q^2 + 63 q^3 + 210 q^4 + 633 q^5 + 1725 q^6 + 4407 q^7$}
+\end{lstlisting}
+
+\subsection{Branching functions and coset models of conformal field theory}
+\label{sec:branch-funct-coset}
+
+It is believed that most rational models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$.
+These models can be studied as gauge theories \cite{Hwang:1994yr, hwang1993brst}.
+
+Branching functions for an embedding $\af\subset\gf$ are the partition functions of CFT on the torus (see \cite{difrancesco1997cft}).
+
+As a first example we show how to construct branching functions for the embedding $\hat A_{1}\to \hat B_{2}$ up to the tenth grade:
+\begin{lstlisting}[mathescape=true]
+branchingFunctions[$\hat B_{2}$,makeAffineExtension[makeFiniteRootSystem[{{1, 1}}]], {1, 1, 1}]
+
+ {{3, 0}, 
+  $2 + 14 q + 52 q^2 + 154 q^3 + 410 q^4 + 994 q^5 + 2248 q^6 + 4832 q^7 + 9934 q^8 + 19680 q^9 + 37802 q^{10}$},
+ {{2, 1}, 
+  $4 + 20 q + 72 q^2 + 220 q^3 + 584 q^4 + 1424 q^5 + 3248 q^6 + 7012 q^7 + 14488 q^8 + 28844 q^9 + 55616 q^{10}$},
+ {{0, 3}, 
+  $4 q + 20 q^2 + 68 q^3 + 200 q^4 + 516 q^5 + 1224 q^6 + 2736 q^7 + 5808 q^8 + 11820 q^9 + 23236 q^{10}$},
+ {{1, 2}, 
+  $2 + 14 q + 54 q^2 + 168 q^3 + 462 q^4 + 1148 q^5 + 2656 q^6 + 5812 q^7 + 12130 q^8 + 24358 q^9 + 47328 q^{10}$}
+\end{lstlisting}
+
+Another example demonstrates the computation of branching functions for the regular embedding $\hat B_{2}\subset \hat C_{3}$:
+\begin{lstlisting}[mathescape=true]
+sub=makeAffineExtension[parabolicSubalgebra[$C_{3}$][2,3]];
+branchingFunctions[$\hat C_{3}$,sub, {2, 0, 0, 0}]
+
+{{0, 1, 0}, 
+  $2 q - 20 q^3 + 24 q^4 + 82 q^5 - 320 q^6 + 108 q^7$}, 
+{{1, 0, 0}, 
+  $1 - q - 8 q^2 + 19 q^3 + 16 q^4 - 156 q^5 + 205 q^6 + 640 q^7$}, 
+{{0, 0, 1}, 
+  $q - 5 q^3 + 7 q^5$}
+\end{lstlisting}
+
+\section{Conclusion}
+\label{sec:conclusion}
+We have presented the package {\bf Affine.m} for computations in representation theory of finite-dimensional and affine Lie algebras.
+It can be used to study Weyl symmetry, root systems, irreducible, Verma and parabolic Verma modules of finite-dimensional and affine Lie algebras.
+In the present paper we have also discussed main ideas used for an implementation of the package and described most important notions of representation theory required to use {\bf Affine.m}.
+
+We have demonstrated that recurrent approach based on the Weyl character formula is not only useful for calculations but also allows to establish connections with the (generalized) Bernstein-Bernstein-Gelfand resolution.
+
+Also we have presented examples of computations with this package connected with problems of physics and mathematics.
+
+In future versions of our software we are going to treat twisted affine Lie algebras, extended affine Lie algebras and provide more direct support for tensor product decompositions.
+
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+I thank V.D. Lyakhovsky and O.Postnova for discussions and helpful comments.
+
+The work is supported by the Chebyshev Laboratory
+(Department of Mathematics and Mechanics, Saint-Petersburg State
+University) under the grant 11.G34.31.0026 of the Government of the
+Russian Federation.
+
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%\appendix
+
+\section{Software package}
+\label{package}
+The package can be freely downloaded from \url{http://github.com/naa/Affine}. To get the development code use the command
+\begin{lstlisting}[language=bash]
+ git clone git://github.com/naa/Affine.git
+\end{lstlisting}
+
+Contents of the package:
+\begin{verbatim}
+    Affine/                                root folder
+      demo/                                  demonstrations
+        demo.nb                                demo notebook
+        paper.nb                               code for the paper
+      doc/                                 documentation folder
+        figures/                             figures in paper 
+          timing.pdf                           diagram showing performance
+          branching-timing.pdf                 ...  for branching coefficients  
+          irrep-sum.pdf                        sum of B2 irreps
+          irrep-verma-pverma.pdf               irrep, Verma, (p)Verma for B2
+          G2-irrep.pdf                         irrep for G2
+          G2-pverma.pdf                        parabolic Verma for G2
+          tensor-product.pdf                   tensor product of A1-modules
+        bibliography.bib                     bibliographic database
+        paper.pdf                            present paper
+        paper.tex                            paper source
+        TODO.org                             list of issues
+      src/                                 source folder
+        affine.m                             main software package
+      tests/                               unit tests folder
+        tests.m                              unit tests
+      README.markdown                      installation and usage notes
+\end{verbatim}
+
+%% References
+%%
+%% Following citation commands can be used in the body text:
+%% Usage of \cite is as follows:
+%%   \cite{key}         ==>>  [#]
+%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
+%%
+
+%% References with bibTeX database:
+
+  %   \section*{References}
+  %   \label{sec:references}
+  %   
+  %   
+  %   \bibliography{bibliography}
+  %   \bibliographystyle{phcpc}
+  %   %\bibliographystyle{model1-num-names}
+  %   
+  %   
+  %   %% Authors are advised to submit their bibtex database files. They are
+  %   %% requested to list a bibtex style file in the manuscript if they do
+  %   %% not want to use elsarticle-num.bst.
+  %   
+  %   %% References without bibTeX database:
+  %   
+  %   % \begin{thebibliography}{00}
+  %   
+  %   %% \bibitem must have the following form:
+  %   %%   \bibitem{key}...
+  %   %%
+  %   
+  %   % \bibitem{}
+  %   
+  %   % \end{thebibliography}
+  %   
+  %   
+  %
+
+%%
+%% End of file
 %%% Local Variables: 
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "thesis"
 %%% End:

### 2011-11-27 AffineLieAlgebras/Thesis/1.tex
Chapter 2 is completely translated. Description of computational package is moved to the last chapter.

@@
 
-\begin{mynote} The orthogonal subalgebra $\afb$ is always trivial
-for conformal embeddings $\af\longrightarrow \mathfrak{g}$.
+\begin{mynote} Ортогональная подалгебра  $\afb$ всегда тривиальна в случае конформного вложения $\af\longrightarrow \mathfrak{g}$.
 \begin{proof}
-Consider the modes expansion of the energy-momentum tensor
+Рассмотрим разложение тензора энергии-импульса на моды:
 \begin{equation*}
@@
 \end{equation*}
-The modes $L_n$ are constructed as combinations of normally-ordered products of $\gf$-algebra generators,
+Моды $L_n$ представляют собой комбинации нормально упорядоченных произведений генераторов алгебры $\gf$,
 \begin{equation*}
@@
 \end{equation*}
-In case of a conformal embedding energy-momentum tensors $T_{\mathfrak{g}}(z)$ and $T_{\af}(z)$ are
-equal (see (\ref{eq:2})).
-
-In these combinations we are to substitute  $\af$-generators in terms of $\mathfrak{g}$-generators
-and obtain the energy-momentum tensor $T_{\mathfrak{g}}$.
-But if the set of generators attributed to $\Delta_{\afb}$ is not empty this is not possible,
-since $T_{\mathfrak{g}}$ contains generators $X^{\alpha}_n$ for $\alpha\in \Delta_{\afb}$.
+При конформном вложении тензоры энергии-импульса  $T_{\mathfrak{g}}(z)$ и $T_{\af}(z)$ равны (см. (\ref{eq:2})).
+
+В эти комбинации мы должны подставить генераторы подалгебры $\af$ выраженные через генераторы $\mathfrak{g}$ и получить тензор энергии-импульса $T_{\mathfrak{g}}$.
+Но если набор генераторов, связанных с  $\Delta_{\afb}$ не пуст, это не возможно, так как  $T_{\mathfrak{g}}$ содержит генераторы $X^{\alpha}_n$, где $\alpha\in \Delta_{\afb}$.
 \end{proof}
@@
 
-\subsubsection{Special embedding $\hat{A}_1\rightarrow\hat{A}_2$.}
+\subsubsection{Специальное вложение $\hat{A}_1\rightarrow\hat{A}_2$.}
 \label{sec:spec-embedd-hata_1s}
-
-Consider the case where both $\gf$ and $\af$ are affine Lie algebras:
-$\hat{A}_1 \rightarrow \hat{A}_2$ and the injection is the affine extension of the
-special injection $A_1 \rightarrow A_2$ with the embedding index $x_e=4$.
-As far as $\gf$-modules to be considered are of level one,
-the necessary $\af$-modules will be of level $\tilde{k}=kx_e=4$.
-
-There exist three level one fundamental weights of $\hat{A}_2$.
-It is easy to see that the set $\Delta_{ \afb }$ is empty and the subalgebra $\afb=0$.
-Then ${\cal D}_{\afb}=0$, $\hf_{\perp}$ is one-dimensional abelian subalgebra and
-the dimension of $\tilde\afb=\afb\oplus \hf_{\perp}$ is also 1.
-It is convenient to choose the classical root for $\hat{A}_1$ to be
-$\beta=\frac{1}{2}(\alpha_1+\alpha_2)$.
-
-Using Definition (\ref{fan-definition})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$.
-In this case $\gamma_0 =0$ and its sign $s\left( 0 \right)=-1$ thus we are to use the
-sign function $s(\gamma)$ (see Figure \ref{fig:AffineA2A1Fan}).
+Рассмотрим следующие пример аффинной алгебры Ли $\gf$ и аффинной подалгебры $\af$:
+$\hat{A}_1 \rightarrow \hat{A}_2$ и вложение является аффинным расширением специального вложения $A_1 \rightarrow A_2$ с индексом вложения $x_e=4$.
+Так как мы должны рассматривать $\gf$-модули уровня один, соответствующие  $\af$-модули будут иметь уровень $\tilde{k}=kx_e=4$.
+
+Существует три фундаментальных веса алгебры  $\hat{A}_2$ имеющих уровень один. 
+Легко видеть, что множество $\Delta_{ \afb }$ пусто и подалгебра $\afb=0$.
+Тогда ${\cal D}_{\afb}=0$, $\hf_{\perp}$ -- одномерная абелева подалгебра и размерность $\tilde\afb=\afb\oplus \hf_{\perp}$ также равна 1.
+Удобно выбрать классический корень для подалгебры $\hat{A}_1$ равным $\beta=\frac{1}{2}(\alpha_1+\alpha_2)$.
+
+Используем Определение (\ref{fan-definition}) и построим веер $\Gamma_{\hat A_1\to\hat A_2}$.
+В этом случае $\gamma_0 =0$ и знак  $s\left( 0 \right)=-1$, то есть мы используем знаковую функцию $s(\gamma)$ (см.
+Рисунок \ref{fig:AffineA2A1Fan}).
 
@@
 
-  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ for $\hat{A_1}\rightarrow \hat{A_2}$
-  in the basis $\left\{\beta,\delta \right\}$. Notice that $\gamma_0 =0$, so values of $s(\gamma)$
-  are prescribed to the weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$}
+  \caption{Веер  $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ для вложения $\hat{A_1}\rightarrow \hat{A_2}$ в базисе $\left\{\beta,\delta \right\}$.
+Заметим, что  $\gamma_0 =0$ и значения $s(\gamma)$ приписаны к весам $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$}
   \label{fig:AffineA2A1Fan}
@@
 
-Consider the module $L^{\omega_0=(0,0;1;0)}$. Here we use the (finite part; level; grade)
-presentation of the highest weight and the finite part
-coordinates are the Dynkin indices (see section(\ref{sec:notation})).
-
-The set $\widehat{\Psi^{(\omega_0)}}$  is displayed in Figure
-\ref{fig:affine_A2_anom_point} up to the sixth grade.
+Рассмотрим модуль $L^{\omega_0=(0,0;1;0)}$. Здесь мы используем обозначение (конечномерная часть; уровень; грейд)
+для старшего веса и координаты конечномерной части даются индексами Дынкина (см. раздел \ref{sec:weights-roots}).
+
+Множество весов $\widehat{\Psi^{(\omega_0)}}$ показано на Рисунке \ref{fig:affine_A2_anom_point} вплоть до шестого грейда.
 
@@
   \includegraphics[width=180mm]{figure7}
-  \caption{Singular weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$.
-   The classical (grade zero) cross-section of the diagram is shown separately
-   in the right part of the figure.
-  We use the orthogonal basis with the unit vector equal to $\alpha_1$.
-  The weights $w (\omega_0+\rho)-\rho$ are marked by crosses when $\epsilon(w)=1$ and
-by box when $\epsilon(w)=-1$. Simple roots of the classical subalgebra $A_2$ are
-grey and the grey diagonal plane corresponds to the Cartan subalgebra of
-the embedded algebra $\hat{A}_1$.}
+  \caption{Сингулярные веса модуля $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$. Классическое сечение (нулевой грейд) диаграммы показано отдельно в правой части рисунка. 
+    Мы используем ортогональный базис с единичным вектором, равным $\alpha_1$.
+Веса $w (\omega_0+\rho)-\rho$ показаны крестами, если $\epsilon(w)=1$ и квадратами при $\epsilon(w)=-1$.
+Простые корни классической подалгебры  $A_2$ показаны серым, а диагональная плоскость соответствует подалгебре Картана вложенной алгебры $\hat{A}_1$.}
   \label{fig:affine_A2_anom_point}
@@
 
-The next step is  to project the anomalous weights to $P_{\hat A_1}$.
-The result is the element $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
-presented in Figure \ref{fig:AffineA2_A1_anom_proj} up to the twelfth grade.
+Следующий шаг состоит в проектировании сингулярных весов на $P_{\hat A_1}$.
+В результате получается элемент $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$, изображенный на Рисунке \ref{fig:AffineA2_A1_anom_proj} вплоть до двенадцатого грейда.
 \begin{figure}[h!tb]
@@
   \includegraphics[width=130mm]{figure8}
-  \caption{The singular element $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
-  displayed in $P_{\hat A_1}$
-  with the basis $\left\{\beta,\delta \right\}$.}
+  \caption{Сингулярный элемент $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$ показан в $P_{\hat A_1}$ с базисом $\left\{\beta,\delta \right\}$.}
   \label{fig:AffineA2_A1_anom_proj}
@@
 
-Using the recurrent relation (\ref{recurrent-relation}) with the fan
-$\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ and the singular weights in
-$\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$
-we get the anomalous branching coefficients presented
-in Figure \ref{fig:AffineA2_A1_branching}.
+Используя рекуррентное соотношение  (\ref{recurrent-relation}) с веером
+$\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ и сингулярными весами $\Psi ^{\left( \omega_0 \right) }_{\left(  \hat A_1\, , \, \afb=0 \right)}$, мы получаем сингулярные коэффициенты ветвления, показанные на Рисунке \ref{fig:AffineA2_A1_branching}.
 \begin{figure}[h!tb]
@@
   \includegraphics[width=130mm]{figure9}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$. The boundaries
-  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
- are indicated by black lines. Two anomalous highest weights located
- in the main Weyl chamber are marked by stars.
- Both have multiplicity 1, so the branching coefficients for them are equal 1.}
+  \caption{Сингулярные коэффициенты ветвления для вложения $\hat{A_1}\subset \hat{A_2}$.
+Границы главной камеры Вейля $\bar{C}_{\hat{A}_1}$ показаны черными линиями.
+Два сингулярных веса, расположенные в главной камере Вейля, отмечены звездочками.
+Они оба имеют кратность 1, то есть соответствующие коэффициенты ветвления равны 1.}
   \label{fig:AffineA2_A1_branching}
 \end{figure}
-Inside the Weyl chamber $\bar{C}_{\hat{A}_1}$
-(its boundaries are indicated in Figure \ref{fig:AffineA2_A1_branching})
-there are only two nonzero anomalous weights and both have multiplicity 1.
-These are the highest weights of $\af$-submodules and the multiplicities are their branching
-coefficients. Thus we get the decomposition
+Внутри камеры Вейля $\bar{C}_{\hat{A}_1}$ (ее границы показаны на Рисунке \ref{fig:AffineA2_A1_branching}) находятся только два ненулевых сингулярных веса и оба они имеют кратность 1.
+Это старшие веса подмодулей $\af$ и их кратности равны коэффициентам ветвления.
+То есть мы получаем разложение
 \begin{equation*}
@@
 \end{equation*}
-Notice that the finite reducibility theorem holds.
-
-The same fan $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ can be used for any other highest weight
-module $L^{\mu}_{\hat{A_2}}$. In particular for irreducible modules of level one  we get the trivial
-branching:
+Заметим, что теорема о конечной приводимости выполняется.
+
+Тот же веер $\Gamma_{\hat{A_1}\rightarrow \hat{A_2}}$ можно использовать для других модулей старшего веса $L^{\mu}_{\hat{A_2}}$.
+В частности для неприводимых модулей уровня один мы получаем тривиальное ветвление:
 \begin{equation*}
@@
 
-Using these results the modular-invariant partition function is easily found,
+Используя эти результаты легко получить модулярно-инвариантную статсумму:
 \begin{equation*}
@@
 
-\subsubsection{Coset models}
+\subsubsection{Coset-модели}
 \label{sec:coset-models}
 
-Coset models \cite{Goddard198588} tightly connected with the gauged WZW-models are actively studied
-in string theory, especially in string models on anti-de-Sitter space
-\cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}.
-The characters in coset models are proportional to branching functions,
+Coset-модели \cite{Goddard198588} тесно связанные с калибровочными ВЗНВ-моделям активно изучаются в теории струн, особенно в струнных моделях в пространстве анти де Ситтера
+\cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}. Характера в coset-моделях пропорциональны функциям ветвления.
 \begin{equation}
@@
 \end{equation}
-with
+где
 \begin{equation*}
@@
 \end{equation*}
-The problem of branching functions construction in the coset models was considered
-in  \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.
-
-Let us return to our example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
-$A_1 \rightarrow B_2$.
-Since this embedding is regular and $x_e=1$, the subalgebra modules and the initial module are of the same level.
-The set  of positive roots with zero projection
-on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case:
-$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$ and $\afb=A_1$. It is easy to see that here $\hf_{\perp}$
-is trivial and ${\cal D}_{\afb}=0$.
-
-Using Definition (\ref{fan-definition}) we obtain the fan
-$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
-Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=-1$.
-Values of the sign function $s(\gamma)$ for
-$ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ are presented in Figure \ref{fig:AffineB2A1Fan}.
-We restricted the computation to the twelfth grade.
+Проблема построения функций ветвления для  coset-моделей рассматривалась в работах  \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.
+
+Вернемся к нашему примеру \ref{sec:regul-embedd-a_1} и рассмотрим аффинное расширение вложения $A_1 \rightarrow B_2$.
+Так как вложение регулярно и индекс $x_e=1$, модули подалгебры и исходный модуль имеют одинаковый уровень.
+Множество положительных корней с нулевой проекцией на корневое пространство подалгебры  $\hat{A_1}$ то же, что и в конечномерном случае: $\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$ и $\afb=A_1$.
+Легко видеть, что здесь $\hf_{\perp}$ тривиальна и  ${\cal D}_{\afb}=0$.
+
+Используя Определение (\ref{fan-definition}) мы получаем веер вложения $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
+Заметим, что наименьший вес веера $\gamma_0$ равен нулю и  $s\left( \gamma_0 \right)=-1$.
+Значения знаковой функции  $s(\gamma)$ для $ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ показаны на Рисунке \ref{fig:AffineB2A1Fan}.
+Мы ограничили вычисление двенадцатым грейдом. 
 \begin{figure}[h!bt]
@@
   \includegraphics[width=135mm]{figure10}
-  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$
-  for $\hat{A_1}\rightarrow \hat{B_2}$ in the basis $\left\{\beta,\delta \right\}$. Values of  $s(\gamma)$ are shown for the
-  weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$}
+  \caption{Веер $\Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$ для вложения $\hat{A_1}\rightarrow \hat{B_2}$ в базисе $\left\{\beta,\delta \right\}$.
+Значения $s(\gamma)$ показаны для весов $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$}
   \label{fig:AffineB2A1Fan}
@@
 
-Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $\omega_1=(1,0;1;0)$,
-where the finite part coordinates are in the orthogonal basis $e_1,e_2$.
-The set of anomalous weights for this module up to the sixth grade is presented in Figure \ref{fig:affine_B2_anom_point}.
+Рассмотрим модуль уровня один $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  со старшим весом  $\omega_1=(1,0;1;0)$, где координаты конечномерной части даны в ортогональном базисе $e_1,e_2$.
+Множество сингулярных весов для этого модуля вплоть до шестого грейда приведено на Рисунке \ref{fig:affine_B2_anom_point}.
 
@@
   \includegraphics[width=140mm]{figure11}
-  \caption{Singular weights for $L^{(1,0;1;0)}_{\hat B_2 }$. The standard basis $\{e_1,e_2\}$ is used for the classical cross-section.
-  The weights in the zero grade are the same as in Figure \ref{fig:B2_A1}.
-  The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by boxes for $\epsilon(w)=-1$.
-Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
-of the embedded algebra $\hat{A}_1$.}
+  \caption{Сингулярные веса модуля $L^{(1,0;1;0)}_{\hat B_2 }$.
+В классическом сечении используется стандартный базис  $\{e_1,e_2\}$.
+Веса в нулевом грейде те же, что и на Рисунке \ref{fig:B2_A1}.
+Веса  $w (\omega_1+\rho)-\rho$ отмечены крестами, если $\epsilon(w)=1$ и квадратами при $\epsilon(w)=-1$.
+Простые корни классической подалгебры  $B_2$ показаны серым, а диагональная плоскость соответствует подалгебре Картана вложенной алгебры $\hat{A}_1$.}
   \label{fig:affine_B2_anom_point}
@@
 
-According to the recursive algorithm \ref{sec:algorithm} we project these anomalous weights to
-$P_{\hat{A_1}}$ and find the dimensions of the corresponding
-$\afb$-modules $L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$.
-In the grade zero this projection gives exactly the set
-$\Psi ^{\left( \mu \right) }_{\left(  A_1, A_1 \right)}$ for the embedding of
-the classical Lie algebra $A_1\rightarrow B_2$. To see this compare Figure \ref{fig:B2_A1}
-with Figure \ref{fig:AffineB2_A1_anom_proj}
-where the singular element $\Psi ^{\left( \mu \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
-for the affine embedding $\hat{A_1}$ is presented up to the twelfth grade.
+В соответствии с рекурсивным алгоритмом  \ref{sec:algorithm} мы проектируем сингулярные веса на $P_{\hat{A_1}}$ и вычисляем размерности $\afb$-модулей $L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$.
+В нулевом грейде эта проекция дает в точности множество $\Psi ^{\left( \mu \right) }_{\left(  A_1, A_1 \right)}$, соответствующее вложению классической алгебры Ли  $A_1\rightarrow B_2$.
+Это можно заметить сравнивая Рисунок \ref{fig:B2_A1} и Рисунок \ref{fig:AffineB2_A1_anom_proj}, на котором сингулярный элемент $\Psi ^{\left( \mu \right) }_{\left(  \widehat{A_1}, A_1 \right)}$ для аффинного вложения  $\hat{A_1}\to\hat{B_{2}}$  показан вплоть до двенадцатого грейда.
 \begin{figure}[h!tb]
@@
   \includegraphics[width=120mm]{figure12}
-  \caption{Singular element $\Psi ^{\left( \omega_1 \right) }_{\left(  \widehat{A_1}, A_1 \right)}$
-  in the basis $\{\beta,\delta\}$. Dimensions of the corresponding $\afb=A_1$-modules
-  with the signs $\epsilon(u)$ are indicated.}
+  \caption{Сингулярный элемент $\Psi ^{\left( \omega_1 \right) }_{\left(  \widehat{A_1}, A_1 \right)}$ в базисе $\{\beta,\delta\}$.
+Размерности соответствующих  $\afb=A_1$-модулей со знаками  $\epsilon(u)$ представлены на рисунке.}
   \label{fig:AffineB2_A1_anom_proj}
@@
   \includegraphics[width=120mm]{figure13}
-  \caption{Anomalous branching coefficients for $\hat{A_1}\rightarrow \hat{B_2}$. The basis $\{\beta,\delta\}$ is used.
- Boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
- are indicated by black lines. Anomalous branching coefficients
- inside the main Weyl chamber are equal to branching coefficients of the embedding $\hat{A_1}\rightarrow \hat{B_2}$.}
+  \caption{Сингулярные коэффициенты ветвления для вложения $\hat{A_1}\rightarrow \hat{B_2}$.
+Использован базис $\{\beta,\delta\}$.
+Границы главной камеры Вейля $\bar{C}_{\hat{A}_1}$ показаны черными линиями.
+Сингулярные коэффициенты ветвления внутри главной камеры Вейля равны коэффициентам ветвления для вложения $\hat{A_1}\rightarrow \hat{B_2}$.}
   \label{fig:AffineB2_A1_branching}
@@
 
-Multiplicities of the highest weights inside the  Weyl chamber
-$\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$
-define the following branching coefficients (up to the twelfth grade),
+Кратности старших весов внутри главной камеры Вейля
+$\bar{C}^{\left( 0 \right)}_{\hat{A_1}}$ определяют следующие значения коэффициентов ветвления (до двенадцатого грейда):
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-This result can be presented as the set of branching functions:
+Этот результат можно представить в виде набора функций ветвления:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-Here $q=\exp (2\pi i \tau)$ and the lower index enumerates the branching functions according
-to their highest weights in $P^+_{\hat{A_1}}$.
-These are the fundamental weights $\omega_0=\lambda_0=(0,1,0),\; \omega_1=\alpha/2=(1,1,0)$.
-
-Now we can return to (\ref{eq:31}),
+Здесь $q=\exp (2\pi i \tau)$ и нижний индекс нумерует функции ветвления по их старшим весам в  $P^+_{\hat{A_1}}$, равным фундаментальным весам $\omega_0=\lambda_0=(0,1,0),\; \omega_1=\alpha/2=(1,1,0)$.
+
+Теперь мы можем вернуться к равенству (\ref{eq:31}) и получить выражение для характеров coset-модели $B_2/A_1$:
 \begin{equation*}
@@
 \end{equation*}
-and finally obtain expansions for the $B_2/A_1$-coset characters.
-
-\section{Выводы к первой главе}
+
+\section{Выводы ко второй главе}
 \label{sec:conclusion}
-We have demonstrated that the injection fan technique can be used to deal with arbitrary
-reductive subalgebras (maximal as well as  nonmaximal).
-It was shown that the branching problem for $\af \subset \gf$  is tightly connected with
-the properties of the orthogonal partner $ \af_{\perp
-} $ of $\af$. The subalgebra $\afb$ corresponds to the subset
-$\Delta^{+}_{\afb}$ of positive roots in $\Delta_{\mathfrak{g}}^{+}$ that trivialize
-the Cartan subalgebra $\hf_{\afb}$.
-Both the injection fan and the sets of singular weights for
-highest weight $\gf$-modules depend substantially on the structure of $\afb$ and its submodules.
-For the fan $\Gamma_{\af\rightarrow \gf}$ this dependence is almost obvious:
-in the element $\Phi_{\af\rightarrow \gf}$ the factors corresponding to the roots
-of $\Delta^{+}_{\afb}$ are eliminated.
-The transformation in the set of projected singular weights is more interesting.
-We have found out that in the new singular element
-$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ the coefficients depend on
-the $\afb$-submodules (their highest weights $\mu _{\widetilde{\af_{\perp }}}\left( u\right)$
-are fixed by the injection and by the weights of the initial
-element $\Psi^{\mu}$).
-Fortunately no more information on $L^{\mu _{\widetilde{\af_{\perp }}}\left( u\right)}
-_{\left\{ \afb \right\}}$-submodules is necessary than their dimensions.
-In the new singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$
-weight multiplicities are equal to dimensions
-$\dim\left(L^{\mu _{\widetilde{\af_{\perp }}}\left( u\right)}_{\left\{ \afb \right\}}\right)$
-of the corresponding $\afb$-modules
-multiplied by the values $\epsilon (u)$. As a result
-the highest weights of $\af$-submodules and their
-multiplicities are subject to the set of linear equations (\ref{eq:17}).
-These properties are valid for any reductive subalgebra $\af\rightarrow \gf$ and
-the set can be redressed to the form of recurrent relations to be solved step by step.
-
-The efficiency of the obtained algorithm was illustrated in various examples.
-In particular we considered the construction of modular-invariant partition functions
-in the framework of conformal embedding method and the coset construction in rational conformal field theory.
-This construction is useful in the study of WZW-models
-emerging in the context of the AdS/CFT correspondence \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
-
-Further amelioration of the algorithm can be achieved by using
-the folded fan technique \cite{il2010folded}. It must be mentioned that even in the case
-of string functions the explicit solution of the corresponding recurrent relations is
-a difficult problem (see \cite{il2010folded} for details). Nevertheless we hope that by
-developing the procedure of folding one could get explicit solutions
-for at least some of branching functions and the corresponding coset characters.
+
+Мы продемонстрировали, что техника веера вложения может использоваться для работы с произвольными редуктивными подалгебрами (как максимальными, так и не максимальными).
+Также показано, что проблема редукции для  $\af \subset \gf$ тесно связана со свойствами ортогонального партнера $ \afb $ подалгебры $\af$.
+Подалгебра  $\afb$ соответствует подмножеству положительных корней $\Delta^{+}_{\afb}$ в $\Delta_{\mathfrak{g}}^{+}$, которое тривиализует подалгебру Картана $\hf_{\afb}$.
+Веер вложения и множества сингулярных весов для модулей старшего веса алгебры $\gf$ существенным образом зависят от структуры  $\afb$ и ее подмодулей.
+Для веера  $\Gamma_{\af\rightarrow \gf}$ эта зависимость почти очевидна: в элементе  $\Phi_{\af\rightarrow \gf}$ исключены множители, соответствующие корням  $\Delta^{+}_{\afb}$.
+Преобразование множества спроектированных сингулярных весов более интересно.
+Мы показали, что в новом сингулярном элементе $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ коэффициенты зависят от $\afb$-подмодулей (их старшие веса $\mu _{\widetilde{\afb}}\left( u\right)$ заданы вложением и весами первоначального элемента $\Psi^{\mu}$).
+К счастью, для вычислений не требуется никакой информации о  $L^{\mu _{\widetilde{\afb}}\left( u\right)}_{\left\{ \afb \right\}}$-подмодулях, кроме их размерностей.
+В новом сингулярном элементе $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ кратности весов равны размерностям $\dim\left(L^{\mu _{\widetilde{\afb}}\left( u\right)}_{\left\{ \afb \right\}}\right)$ соответствующих  $\afb$-модулей, умноженным на значения $\epsilon (u)$.
+В результате старшие веса подмодулей $\af$ и их кратности удовлетворяют набору линейных соотношений (\ref{eq:17}).
+Эти свойства выполняются для любой редуктивной подалгебры $\af\rightarrow \gf$ и уравнения могут быть переписаны в виде рекуррентных соотношений, которые можно решать последовательно.
+
+Эффективность полученного алгоритма была продемонстрирована на различных примерах.
+В частности, мы рассмотрели построение модулярно-инвариантных статсумм в методе конформных вложений и coset-конструкцию моделей рациональной конформной теории поля.
+Эти конструкции полезны при изучении ВЗНВ-моделей, возникающих в контексте AdS/CFT соответствия \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
+
+Дальнейшее улучшение алгоритма может быть достигнуто при использовании техники сложенных вееров \cite{il2010folded}.
+Нужно отметить, что даже в случае струнных функций явное решение соответствующих рекуррентных соотношений представляет собой сложную проблему (см.
+подробности в работе\cite{il2010folded}).
+Тем не менее, мы надеемся, что развитие процедуры сложения позволит получить явные решения хотя бы для некоторых функций ветвления и соответствующих характеров coset-моделей.
 

### 2011-11-27 AffineLieAlgebras/Thesis/3.tex
Chapter 2 is completely translated. Description of computational package is moved to the last chapter.

@@
-\chapter{Коэффициенты ветвления и обобщенная резольвента Бернштейна-Гельфанда-Гельфанда}
-\label{cha:BGG}
+\chapter{Сплинты корневых систем и функции ветвления}
+\label{cha:splints}
 
- \section{Обозначения}
+\section{Сплинты и ветвления}
+\label{sec:splints}
 
- \label{sec:notation}
- Пусть $\frak{g}$ и $\frak{a}$ -- (аффинные) алгебры Ли, и существует вложение  $\frak{a}\hookrightarrow \frak{g}$ такое, что  $\frak{a}$ -- редуктивная подалгебра в $\frak{g}$ с согласованным корневым пространством: $\frak{%
- h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g}}^{\ast }$. Мы используем следующие обозначения:
+%%\newtheorem{Def}{Definition}[section]
+%%\newtheorem{Cnj}[Def]{Conjecture}
+%%\newtheorem{Prop}[Def]{Property}
+%%\newtheorem{example}{Example}[section]
+%%
+%\input{tcilatex}
 
- $\frak{g=n}^{-}+\frak{h}+\frak{n}^{+}$ --- разложение Картана;
+\begin{abstract}
+Splint of root system for simple Lie algebra appears naturally in
+studies of (regular) embeddings of reductive subalgebras. Splint can
+be used to construct branching rules. We demonstrate that 
+splint properties implementation drastically simplify calculations of
+branching coefficients.
+\end{abstract}
 
- $r$ , $\left( r_{\frak{a}}\right) $ --- ранг алгебра $\frak{g}$ $%
- \left( \mathrm{\text{соотв., }\frak{a}}\right) $ ;
+\section{Introduction}
+\label{sec:Introduction}
 
- $\Delta $ $\left( \Delta _{\frak{a}}\right) $--- корневая система; $\Delta
- ^{+} $ $\left( \mathrm{\text{соотв., }\Delta _{\frak{a}}^{+}}\right) $--- набор положительных корней (алгебр $\frak{g}$ и $\frak{a}$ соответственно);
+Embedding $\phi$ of a root system $\Delta_1$ into a root system
+$\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
+subset of $\Delta$ that commutes with vector composition law in
+$\Delta_{1}$ and $\Delta$.
+\begin{equation*}
+\phi:\Delta_1 \longrightarrow \Delta
+\end{equation*}
+\begin{equation*}
+\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
+\,\,\, \alpha,\beta \in \Delta_1
+\end{equation*}
 
- $\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
- \alpha \right) \right) $ --- кратность корня $\alpha$ в $%
- \Delta $ (соотв., в $\left( \Delta _{\frak{a}}\right) $);
+Note that the image $Im(\phi)$ must not inherit the root system
+properties except the addition rules equivalent to the addition
+rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
+can splinter $\Delta$  when the latter can be presented 
+as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.   
+The term {\it splint} was
+introduced by D. Richter in  \cite{richter2008splints} where the
+classification of splints for simple Lie algebras was obtained.
+There was also mentioned that splint must have tight
+connections with the injection fan construction. The fan $\Gamma
+\subset \Delta$ was
+introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent
+properties of branching coefficients for maximal embeddings. Injection fan is an
+efficient tool to study branching rules. Later this construction
+was generalized to non-maximal embeddings and infinite-dimensional
+Lie algebras in \cite{2010arXiv1007.0318L, ilyin812pbc}.
 
- $S\quad \left( S_{\frak{a}}\right) $ --- множество простых корней (для 
- $\gf$ и $\af$ соответственно);
+In the present paper we study connections between splint and
+injection fan for regular embedding of reductive subalgebras
+${\mathfrak a}$ in simple Lie algebra $\mathfrak{g}$. We show that (under
+certain conditions described in section \ref{sec:stems and
+multiplicity functions}) splint is a natural tool to study
+reduction properties of ${\mathfrak g}$-modules
+with respect to a subalgebra ${\mathfrak a}\longrightarrow
+{\mathfrak g}$. Using this tool we obtain the main result -- the one-to-one correspondence between weight
+multiplicities in irreducible modules of splint and branching
+coefficients for a reduced module $L^{\mu}_{{\mathfrak
+g}\downarrow {\mathfrak a}}$.
 
- $\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ ---  $%
- i$-й (соотв., $j$-й) простой корень алгебры $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a%
- }}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+\section{Injections and splints}
 
- $\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
- }\right) $-- простой ко-корень для $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a}%
- }\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;
+\label{sec:Injections and splints}
 
- $W$ , $\left( W_{\frak{a}}\right) $--- группа Вейля;
+Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
+\mathfrak{a}\hookrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
+is a
+reductive subalgebra $\mathfrak{a \subset g}$ with correlated root spaces: $%
+\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset \mathfrak{h}_{\mathfrak{g }%
+}^{\ast }$. Let $\mathfrak{a}^{\mathfrak{s}}$ be a semisimple summand of
+$\mathfrak{a}$,
+this means that $\mathfrak{a}=\mathfrak{a}^{\mathfrak{s}} \oplus \mathfrak{u}(1)\oplus %
+\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^{\mathfrak{s}}$
+to be a proper regular subalgebra and $\mathfrak{a}$ to be the
+maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed that is the rank
+$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
 
- $C$ , $\left( C_{\frak{a}}\right) $--- фундаментальная камера Вейля;
+The following notations are used:
 
- $\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- замыкание фундаментальной камеры Вейля;
+$r$ , $\left( r_{\mathfrak{a}^{\mathfrak{s}}}\right) $ --- the rank of
+$\frak{g}$ $\left( \mathrm{{resp. }\mathfrak{a}^{\mathfrak{s}}}\right) $ ;
+
+$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system;
+$\Delta ^{+} $ $\left( \mathrm{{resp. }\Delta
+_{\frak{a}}^{+}}\right) $--- the positive root system (of
+$\frak{g}$ and $\frak{a}$ respectively);
+
+$S \, ,\quad \left( S_{\frak{a}}\right) $ --- the system of simple roots (of $%
+\frak{g}$ and $\frak{a}$ respectively);
+
+$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
+i$-th (resp. $j$-th) simple root for $\frak{g}$  $\left( \mathrm{{resp. \,} \frak{%
+a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
+^S}\right) $;
+
+$\omega _{i}$ , $\left( \omega _{\left( \frak{a}\right) j}\right) $ --- the $%
+i$-th (resp. $j$-th) fundamental weight for $\frak{g}$ $\left( \mathrm{{resp. \,}\frak{%
+a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
+^S}\right) $;
+
+$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
+
+$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
+
+$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
+fundamental Weyl chamber;
 
@@
 
- $\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- вектор Вейля;
+$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
 
- $L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- интегрируемый модуль  $\frak{g}$ со старшим весом $\mu $\ ; (соотв., интегрируемый $\af$-модуль старшего веса $\nu $);
+$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
+of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
+-module with the highest weight $\nu $ );
 
 $\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
- весовая диаграмма модуля $L^{\mu }$ (соотв., ${}L_{\frak{a}}^{\nu }$ );
+the weight diagram of $L^{\mu }$ (resp. ${}L_{\frak{a}}^{\nu }$ );
 
- $P$ (соотв., $P_{\frak{a}} $) \ --- весовая решетка;
+$P$ (resp. $P_{\frak{a}} $) \ --- the weight lattice;
 
- $P^{+}$ (соотв., $P_{\frak{a}}^{+} $) \ --- решетка доминантных весов;
+$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight lattice;
 
- $m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\zeta }^{\left( \nu \right)
- }\right) $ --- кратность веса $\xi \in P$ \ $\left( \mathrm{\text{соотв., }\in P_{\frak{a}}}\right) $ в $L^{\mu }$, (соотв., в $\zeta \in
+$\mathcal{E}$ (resp. $\mathcal{E}_{\frak{a}} $) \ --- the formal algebra;
+
+$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
+}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
+resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
 L_{\frak{a}}^{\nu } $);
 
- $ch\left( L^{\mu }\right) $ (соотв., $\mathrm{ch}\left( L_{\frak{a}}^{\nu
- }\right) $)--- формальный характер $L^{\mu }$ (соответственно, $L_{\frak{a}}^{\nu
+$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $)--- the formal character of $L^{\mu }$ (resp. $L_{\frak{a}}^{\nu
 } $);
@@
 $ch\left( L^{\mu }\right)  =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
- +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
- \mathrm{{mult}\left( \alpha \right) }}}$ --- формула Вейля-Каца;
++\rho )-\rho }} {\prod_{\alpha \in \Delta ^{+}} \left( 1-e^{-\alpha }\right)
+} $ --- the Weyl formula;
 
- $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
- mult}\left( \alpha \right) }}\quad $ (соотв., $R_{\frak{a}}:=\prod_{\alpha \in
- \Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}%
- }\left( \alpha \right) } $)--- знаменатель Вейля.
+$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) \quad $
+(resp. $R_{\frak{a}}: =\prod_{\alpha \in \Delta_{\frak{a}}^{+}} \left(
+1-e^{-\alpha }\right) $ ) --- the Weyl denominator.
 
-\section{Конечномерные алгебры Ли}
-\label{sec:finite-dimensional}
-Основные определения: корни, веса, кратности.
-
-\section{Теория представлений аффинных алгебр Ли}
-\label{sec:representation-theory}
-
-\subsection{Алгебра петель и центральное расширение}
-\label{sec:loop-algebra-central-extension}
-
-Определение аффинных алгебр. Корни, веса, кратности. Категория О.
-
-\subsection{Представления аффинных алгебр Ли}
-\label{sec:affine-lie-algebra-representations}
-
-\section{БГГ-резольвента}
-\label{sec:bgg}
-Категория О.
-Резольвента Бернштейна-Гельфанда-Гельфанда для представлений аффинных алгебр Ли. Параболические модули и их связь с подалгебрами и ветвлением.
-
-\begin{abstract}
-Рекуррентные соотношения для коэффициентов ветвления основываются на определенном разложении сингулярного элемента.
-Мы показываем, что такое разложение может использоваться для построения параболических модулей Верма и получения обобщенных формул Вейля-Верма для характеров.
-Также мы демонстрируем, что коэффициенты ветвления определяют обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда.
-\end{abstract}
-
-\subsection{Введение}
-
-\label{sec:introduction}
-Свойства ветвления (аффинных) алгебр Ли важны для приложений в квантовой теории поля (смотри, например, модели конформной теории поля \cite{difrancesco1997cft},\cite{coquereaux2008conformal}).
-В данной работе мы показываем, что ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и демонстрирует свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).
-
-Резольвента для неприводимых модулей в терминах бесконечномерных модулей важна для теории интегрируемых спиновых цепочек \cite{derk1008}.
-В подходе  $\mathcal{Q}$-оператора Бакстера \cite{derk09} общие трансфер-матрицы, соответствующие (обобщенным) модулям Верма, факторизуются в произведение операторов Бакстера.
-Резольвента позволяет вычислить трансфер-матрицы для конечномерных вспомогательных пространств.
-
-Чтобы продемонстрировать связь БГГ резольвенты с ветвлением мы используем рекурсивный подход, представленный в работе \cite
-{2010arXiv1007.0318L} (аналогичный подход для максимальных вложений использовался в работе \cite{ilyin812pbc}).
-Мы рассматриваем подалгебру $\af \hookrightarrow \gf$ вместе с $\afb$ -- ``ортогональным партнером'' $\af$ по отношению к форме Киллинга, а также подалгебру $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$, где $\frak{h}=\frak{\frak{h}_{\af}}\oplus
-\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. Для любой редуктивной подалгебры $\af$ алгебра $\afb\hookrightarrow \gf$ регулярна и редуктивна. Для интегрируемого модуля старшего веса $%
-L^{\left(\mu \right) }$ и ортогональной подалгебры  $\af_{\bot }$ мы рассматриваем сингулярный элемент $\Psi ^{\left( \mu \right) }$ (числитель в формуле Вейля для характеров $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
-\mu \right) }}{\Psi ^{\left( 0\right) }}$, см., например,  \cite
-{humphreys1997introduction}) и знаменатель Вейля $\Psi _{\af_{\bot
-  }}^{\left( 0\right) }$ для ортогонального партнера. В работе показано, что элемент  $\Psi _{\gf%
-}^{\left( \mu \right) }$ может быть разложен в комбинацию числителей Вейля $\Psi _{\af_{\bot }}^{\left( \nu \right) }$, где $\nu \in P_{%
-\mathfrak{a}_{\bot}}^{+}$. Это разложение дает возможность построить множество модулей старшего веса $L_{\afb}%
-^{\mu _{\afb}}$. В том случае, если вложение\ $\af%
-_{\bot }\hookrightarrow \gf$ \ удовлетворяет ``стандартным параболическим'' условиям, эти модули порождают параболические модули Верма $M_{\left(
-\afb \hookrightarrow \gf\right) }^{\mu _{%
-\afb}}$, так что исходный характер $ch\left(
-L^{\mu }\right) $ в итоге раскладывается в знакопеременную сумму таких модулей.
-С другой стороны, если параболическое условие нарушено, конструкция сохраняется и порождает разложение по отношению к набору обобщенных модулей Верма  $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
-\widetilde{\afb}}}$, где $%
-\widetilde{\frak{b}_{\perp }}$ уже не является подалгеброй в $\gf$, а оказывается сжатием $\widetilde{\afb}$.
-
-Некоторые общие свойства предложенного разложения формулируются в терминах  формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''.
-Использование этого инструмента позволило сформулировать простой и явный алгоритм для вычисления правил ветвления, подходящий для произвольной (максимальной или не максимальной) подалгебры в аффинной алгебре Ли \cite{2010arXiv1007.0318L}.
-
-Возможные обобщения полученных результатов обсуждаются в Разделе \ref{sec:conclusions}.
-
-\subsection{Ортогональная подалгебра и сингулярные элементы}
-
-\label{sec:recurr-form-branch}
-
-В этом разделе мы покажем, как рекуррентный подход к проблеме ветвления естественным образом приводит к представлению формального характера $\frak{g}$-модуля в виде комбинации характеров, соответствующих параболическим (обобщенным) модулям Верма.
-Рассмотрим редуктивную алгебру Ли  $\frak{g}$ и ее редуктивную подалгебру $\frak{a}\subset \frak{g}$.
-Пусть  $L^{\mu} $ -- интегрируемый модуль старшего веса алгебры  $\frak{g}$, $\mu \in P^{+}$.  Будем считать  $L^{\mu}$ вполне приводимым по отношению к подалгебре $\frak{a}$,
-\begin{equation*}
+Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
+\[
 L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
 }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
-\end{equation*}
-Это разложение может быть записано в терминах формальных характеров с использованием оператора проекции  $\pi _{\frak{a}}$ (на весовое пространство $\frak{h_{a}}^{\ast }$):
+\]
 \begin{equation}
@@
 \end{equation}
-Для модуля  $L^{\mu }$ существует БГГ резольвента (см. \cite
-{bernstein1976category,bernstein1975differential,bernstein1971structure} и
-\cite{humphreys2008representations}). Все члены фильтрующей последовательности представляются суммами модулей Верма со старшими весами $\nu$, сильно связанными с $\mu$:
-\begin{equation*}
-\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
-W\right\} .
-\end{equation*}
-
-\subsubsection{Ортогональная подалгебра}
-
-Пусть  $\frak{h}_{\frak{a}}$ -- подалгебра Картана в  $\mathfrak{g}$. Для  $\mathfrak{a}\hookrightarrow \frak{g}$ введем ``ортогонального партнера''  $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$.
-
-Рассмотрим корневое подпространство  $\frak{h}_{\perp \frak{a}}^{\ast }$, ортогональное к $\frak{a}$,
-\begin{equation*}
-\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
-h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} ,
-\end{equation*}
-и корни  $\frak{g}$ (соответственно, положительные корни),  ортогональные к $\frak{a}$,
-\begin{eqnarray}
-\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
-h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
-\label{delta a ort} \\
-\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
-}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
-\notag
-\end{eqnarray}
-Обозначим символом  $W_{\frak{a}_{\perp }}$ подгруппу  $W$, порожденную отражениями  $w_{\beta }$ с корнями  $\beta \in \Delta_{\frak{a}_{\perp}}^{+}$.
-Корневая подсистема  $\Delta _{\frak{a}_{\perp }}$ определяет подалгебру  $\frak{a}_{\perp }$, имеющую подалгебру Картана $\frak{h}_{\frak{a}_{\perp }}$.
-Пусть
-\begin{equation*}
-\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
-}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
-h\right) =0\right\};
-\end{equation*}
-выделим в  $\frak{g}$  подалгебры
-\begin{eqnarray}
-\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp },
-\qquad
-\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
-\end{eqnarray}
-Заметим, что  $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ в общем случае не является подалгеброй в $\mathfrak{g}$.
-
-Для подалгебр Картана имеет место разложение
-\begin{equation}
-\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
-\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
-\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
-\frak{h}_{\frak{a}}.
-\end{equation}
-Рассмотрим векторы Вейля  $\rho _{\frak{a}}$ и $\rho _{\frak{a}_{\perp}} $, соответствующие  $\frak{a}$ и $\frak{a}_{\perp }$.
-Введем так называемые ``дефекты'' вложения  $\mathcal{D}_{\frak{a}}$ и $\mathcal{D}_{\frak{a}_{\perp }}$:
-\begin{equation}
-\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho , \qquad
-\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
-_{\perp }}\rho .  \label{defect ort}
-\end{equation}
-Для  $\mu \in P^{+}$ рассмотрим связанные веса  $\left\{\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ и их проекции на $h_{\frak{a}_{\perp }}^{\ast }$, дополнительно сдвинутые на вектор дефекта $-\mathcal{D}_{\frak{a}_{\perp }}$:
-\begin{equation*}
-\mu _{\frak{a}_{\perp }}\left( w\right) :=\pi _{\frak{a}_{\perp }}\left[
-w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad w\in W.
-\end{equation*}
-
-Среди весов  $\left\{ \mu _{\frak{a}_{\perp
-}}\left( w\right) |w\in W\right\} $ всегда можно выбрать те, которые попадают в фундаментальную камеру $\overline{C_{\frak{a}_{\perp }}}$.
-Пусть $U$ -- множество представителей $u$ классов  $W/W_{\frak{a}_{\perp }}$, таких что
-\begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
-\overline{C_{\frak{a}_{\perp }}}\right\} \quad .  \label{U-def}
-\end{equation}
-Тогда можно выделить подмножества:
-\begin{equation}
-\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
-\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}%
-_{\perp }},\quad u\in U,  \label{mu-a}
-\end{equation}
-и
-\begin{equation}
-\mu _{\frak{a}_{\perp }}\left( u\right) :=\pi _{\frak{a}_{\perp }}\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U.
-\label{mu-a-tilda}
-\end{equation}
-
-Заметим, что подалгебра  $\mathfrak{a}_{\bot}$ по определению регулярна, так как она построена на подмножестве корней алгебры $\mathfrak{g}$.
-
-Для интересующих нас модулей формула Вейля-Каца для  $\mathrm{ch}\left( L^{\mu }\right) $ может быть записана через сингулярные элементы \cite{humphreys1997introduction},
-\begin{equation*}
+For the modules we are interested in the Weyl formula for $\mathrm{ch}\left(
+L^{\mu }\right) $ can be written in terms of singular elements \cite
+{humphreys1997introduction}
+\[
 \Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
 )-\rho },
-\end{equation*}
-а именно:
+\]
+namely,
 \begin{equation}
@@
 \end{equation}
-То же верно и для подмодулей $\mathrm{ch}\left( L_{\frak{a}}^{\nu
-}\right) $ в формуле (\ref{branching1})
-\begin{equation*}
+The same is true for submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $ in (\ref{branching1})
+\[
 \mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
@@
 }^{\left( \nu \right) }}{R_{\frak{a}}},
-\end{equation*}
-где
-\begin{equation*}
+\]
+with
+\[
 \Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
 }}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
-\end{equation*}
-Применяя формулу  (\ref{Weyl-Kac2}) к правилу ветвления  (\ref{branching1}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu
-\right) }$ и $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
+\]
+
+Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
+we get a relation connecting the singular elements $\Psi ^{\left( \mu
+\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
 \begin{eqnarray}
-\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
-)-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
-(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
-\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
-\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
-mult}_{\frak{a}}(\beta )}},  \notag  \label{eq:4} \\
-\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
-&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
-}^{\left( \nu \right) }}{R_{\frak{a}}}.
+\frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho )-\rho }}{\prod_{\alpha \in
+\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
+}^{(\mu )}\frac{\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{%
+\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
+}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:4} \\
+\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}}^{\left( \nu \right) }}{R_{%
+\frak{a}}}.  \label{singular main}
 \end{eqnarray}
 
-\subsubsection{Разложение сингулярного элемента.}
-
-\label{subsec:decomp-sing-element}
-
-Теперь мы выполним разложение сингулярного элемента  $\Psi ^{\left(\mu \right) }$ на сингулярные элементы модулей ортогонального партнера:
-
-\begin{lemma}
-
-Пусть  $\frak{a}_{\bot }$ -- ортогональный партнер редуктивной подалгебры  $\frak{a}\hookrightarrow \frak{g}$ и $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$, $\widetilde{%
-\frak{a}_{\perp }}=\frak{a}_{\perp }\oplus \frak{h}_{\perp }$, $%
-\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$.
-
-Пусть $L^{\mu }$ -- интегрируемый модуль старшего веса  $\mu \in P^{+}$ и
-
-$\Psi ^{\left( \mu \right) }$\ -- сингулярный элемент $L^{\mu }$.
-
-Тогда элемент  $\Psi ^{\left( \mu \right) }$ может быть разложен в сумму по  $u\in U$ (см.
-(\ref{U-def})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
-$\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
-\begin{equation}
-\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\widetilde{%
-\mathfrak{a}}}\left( u\right) }\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}%
-_{\perp }}\left( u\right) }.  \label{sing decomp main}
-\end{equation}
-\label{Psi-decomp-lemma}
-\end{lemma}
-
-\begin{proof}
-Пусть
-\[
-u(\mu +\rho )=\pi _{\left( \aft\right) }u(\mu +\rho )+\pi _{\left(
-\frak{a}_{\perp }\right) }u(\mu +\rho ),
-\]
-где $u\in U$. Для произвольного  $v\in W_{\frak{a}_{\bot }}$ рассмотрим сингулярный вес  $vu(\mu +\rho )-\rho $ и выполним разложение:
-\begin{equation}
-\begin{array}{lcl}
-vu(\mu +\rho )-\rho  & = & \pi _{\left( \frak{a}\right) }\left( u(\mu +\rho
-)\right) -\rho +\rho _{\frak{a}_{\perp }}
-\\
-&  & +\ v\left( \pi _{\left( \aft_{\perp }\right) }u(\mu
-+\rho )-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{%
-\frak{a}_{\perp }} .
-\end{array}
-\label{sing-decomp-1}
-\end{equation}
-Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}), чтобы упростить первую строку в формуле (\ref{sing-decomp-1}):
-\[
-\begin{array}{r}
-\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
-\frak{a}_{\perp }}= \\
-\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\pi _{\aft%
-}\rho -\pi _{\af_{\bot }}\rho +\rho _{\frak{a}_{\bot }}= \\
-=\pi _{\left( \aft\right) }\left( u(\mu +\rho )-\rho \right) +\mathcal{D}%
-_{\frak{a}_{\bot }},
-\end{array}
-\]
-и вторую строку
-\[
-\begin{array}{c}
-v\left( \pi _{\left( \frak{a}_{\perp }\right) }u(\mu +\rho
-)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}%
-_{\perp }}= \\
-v\left( \pi _{\left( \frak{a}_{\bot }\right) }u(\mu +\rho )-%
-\mathcal{D}_{\frak{a}_{\bot }}-\pi _{\left( \frak{a}_{\bot }\right) }\rho
-+\rho _{\frak{a}_{\bot }}\right)
--\rho _{\frak{a}_{\bot }}= \\
-=v\left( \pi _{\left( \frak{a}_{\bot }\right) }\left[ u(\mu
-+\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\bot }}+\rho _{\frak{a}_{\bot
-}}\right) -\rho _{\frak{a}_{\bot }}.
-\end{array}
-\]
-В результате получаем требуемое разложение сингулярного элемента $\Psi ^{\mu }$ на сингулярные элементы $\Psi_{\frak{a}_{\perp}}^{\eta}$ модулей $L_{\frak{a}_{\perp }}^{\eta }$ подалгебры $\frak{a}_{\perp }$:
-\begin{equation}
-\begin{array}{l}
-\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
-(v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
-=\sum_{u\in U}\epsilon (u)e^{\pi _{\aft}\left[ u(\mu +\rho )-\rho \right]
-+\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
-(v)e^{v\left( \pi _{\left( \frak{a}_{\perp }\right) }\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}+\rho _{\frak{a}%
-_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
-=\sum_{u\in U}\;\epsilon (u)\Psi _{\af_{\perp }}^{\pi
-_{\left( \frak{a}_{\perp }\right) }\left[ u(\mu +\rho )-\rho
-\right] -\mathcal{D}_{\frak{a}_{\perp }}}e^{\pi _{\left( \aft\right) }%
-\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}.
-\end{array}
-\label{singular main}
-\end{equation}
-\end{proof}
-
-%\bigskip
-
-\begin{remark}
-Это соотношение можно рассматривать как обобщение формулы Вейля для сингулярного элемента $\Psi _{\frak{g}}^{\mu }$: векторы $\mu _{%
-\widetilde{\mathfrak{a}}}\left( u\right) $ играют роль сингулярных весов, в то время как множители  $\epsilon (u)$ расширены до $\epsilon
-(u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$.
-
-Действительно, при  $\frak{a=g}$ подалгебры  $\frak{a}_{\perp }$, и $\frak{h}_{\perp }$ тривиальны, $U=W$ и оригинальная формула Вейля восстанавливается, так как сингулярные элементы $\epsilon (u)\Psi _{\frak{a}_{\perp %
-}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\epsilon (u)$ становятся  тривиальными.
-
-В противоположном пределе, когда $\frak{a}=0$, $\Delta _{\frak{a}_{\perp }}=\Delta _{\frak{g}}$, $%
-\frak{h}_{\perp }^{\ast }=0$, $\frak{a}_{\perp }=\frak{g}$, $\mathcal{D}_{%
-\frak{a}_{\perp }}=0$ и $U=W/W_{\frak{a}_{\perp }}=e$, вновь приходим к выражению для  сингулярного элемента
- $\Psi ^{\mu }$, теперь -- в результате тривиализации множества векторов $\mu _{\af}\left( e\right) =0$.
-\end{remark}
-
-\begin{remark}
-
-В работе \cite{2010arXiv1007.0318L} разложение, аналогичное формуле (\ref{singular main}), было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
+In \cite{2010arXiv1007.0318L} it was proven that branching coefficients $%
+b_{\xi }^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
+\hookrightarrow \frak{g}$ are subject to the set of recurrent relations:
 \begin{equation}
 \begin{array}{c}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
 _{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
@@
 \left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
-}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
+}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
 }\right) .
@@
 \end{equation}
-Рекурсия задается множеством  $\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}$, которое носит название веера вложения.
-Это множество определяется как носитель  $\left\{ \xi \right\}_{\frak{a}\rightarrow \frak{g}}$  коэффициентной функции $s(\xi )$
-\begin{equation*}
-\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{g}}:=\left\{
-\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\},
-\end{equation*}
-возникающей в разложении 
+where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $%
+\frak{g}$ orthogonal to roots of $\frak{a}$ and $W_{\perp}$ is a Weyl group of $\mathfrak{a}_{\perp}$
+\begin{eqnarray}
+\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
+h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
+\label{delta a ort}
+\end{eqnarray}
+\begin{eqnarray}
+\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\qquad \widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }
+\end{eqnarray}
+and $\pi$ is the projection operator. When an injection is maximal the
+projection becomes trivial and the relation (\ref{recurrent rel}) is
+simplified:
 \begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
-_{\widetilde{\frak{a}}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
-_{\frak{a}}(\pi _{\widetilde{\frak{a}}}\alpha )}=-\sum_{\gamma \in P_{%
-\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma }.\quad
+\begin{array}{c}
+b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
+}+\right. \\
+\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
+\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
+\end{array}
+\label{recurrent relation max}
 \end{equation}
-Веса из множества $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
-g}}$ сдвигаются на $\gamma _{0}$ -- младший вектор в $\left\{ \xi
-\right\} $, и исключается нулевой элемент:
+The recursion is goverened by the set $\Gamma _{\frak{a}\rightarrow \frak{g}}
+$ called the injection fan. The latter is defined by the carrier set $%
+\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the coefficient
+function $s(\xi )$
+\[
+\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{ \xi \in P_{%
+\frak{a}}|s(\xi )\neq 0\right\}
+\]
+appearing in the expansion
 \begin{equation}
-\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}=\left\{ \xi -\gamma
-_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\frak{a}}^{+}}\left( 1-e^{
+-\alpha }\right) =-\sum_{\gamma \in P_{\frak{a}}}s(\gamma )e^{-\gamma };\quad
+\label{product}
 \end{equation}
 
-Рекуррентное соотношение (\ref{recurrent rel}) первоначально использовалось для описания ветвления интегрируемых модулей.
-Заметим, что существует важный класс модулей, которые также могут быть редуцированы при помощи веера вложения -- это модули Верма.
-\end{remark}
+Now we remind two definitions introduced in \cite{richter2008splints}
 
-\subsubsection{Фомулы Вейля-Верма.}
+\begin{Def}
+Suppose $\Delta _{0}$ and $\Delta $ are root systems with corresponding
+weight lattices $P_{0}$ and $P$. Then $\phi $ is an ``embedding'',
+\begin{equation}
+\phi :\left\{
+\begin{array}{l}
+\Delta _{0}\hookrightarrow \Delta , \\
+P_{0}\hookrightarrow P,
+\end{array}
+\right.
+\end{equation}
+if \newline
+\noindent (a) it injects $\Delta _{0}$ in $\Delta $, and \newline
+\noindent (b) acts homomorphically with respect to the vector groups in $%
+P_{0}$ and $P$:
+\[
+\phi (\gamma )=\phi (\alpha )+\phi (\beta )
+\]
+for any triple $\alpha ,\beta ,\gamma \in P_{0}$ such that $\gamma =\alpha
++\beta $.
+\end{Def}
 
-\begin{statement}
-%\bigskip
-Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характер интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) характеров параболических модулей Верма, распределенных по множеству весов $\mu _{\widetilde{\mathfrak{a}}}\left(
-u\right)$:
+$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
+\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
+_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
+\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+
+Notice that one must distinguish two classes of embeddings: when the scalar
+product (defined by the Killing form) in the root space $P_0$ is invariant
+with respect to $\phi$ and when it is not $\phi$-invariant. The first
+embedding is called "metric" , the second -- "nonmetric".
+
+\begin{Def}
+A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if
+there are two embeddings $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
+\phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the
+disjoint union of the images of $\phi _{1}$ and $\phi _{2}$ and (b) neither
+the rank of $\Delta _{1}$ nor the rank of $\Delta _{2}$ exceeds the rank of $%
+\Delta $.
+\end{Def}
+
+It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$
+and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$. Each
+component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $%
+(\Delta_1,\Delta_2)$.
+
+To study relations between injection fan technique and splint let us 
+consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ 
+is a root subsystem.
+
+Splint $\Delta \approx (\Delta _{1},\Delta _{2})$ is called ''injective'' if
+$\Delta _{1}=\Delta _{\frak{a}}$, is a root subsystem
+in $\Delta $ corresponding to a regular reductive subalgebra $\frak{a}%
+\hookrightarrow \frak{g}$.
+
+In case of injective splint the second stem $\Delta _{\frak{s}}:=\Delta
+_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product (%
+\ref{product}) and it defines an injection fan $\Gamma _{\frak{a}%
+\hookrightarrow \frak{g}}$. Denote by $\Delta_{\mathfrak{s}0}$ the coimage of the second embedding $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\mathfrak{g}}$.
+The following conjecture follows.
+
+\begin{Cnj}
+Each injective splint $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
+$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\frak{a}%
+\rightarrow \frak{g}}$ fixed by the product
 \begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{%
-\widetilde{\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}%
-_{\perp }}\left( u\right) },  \label{gen Weyl-Verma}
+\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)
+=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
 \end{equation}
-где  $U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
-\overline{C_{\frak{a}_{\perp }}}\right\} $ и $I$ -- такое подмножество в  $S$, что $\Delta _{I}^{+}$ эквивалентно $\Delta _{\frak{a}_{\perp }}^{+}$.
-\end{statement}
+\end{Cnj}
 
-%\bigskip
-\begin{proof}
-Подалгебра  $\mathfrak{a}_{\bot }$ регулярна и редуктивна по определению  (\ref{delta a ort}). Рассмотрим её знаменатель Вейля   $R_{\frak{a}_{\perp }}:=\prod_{\alpha \in \Delta _{\frak{a}%
-_{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}%
-\mathrm{\left( \alpha \right) }}$ и элемент  $R_{J}:=\prod_{\alpha \in
-\Delta ^{+}\setminus \Delta _{\frak{a}_{\perp }}^{+}}\left( 1-e^{-\alpha
-}\right) ^{\mathrm{mult}(\alpha )}$ как сомножители в $R$:
-\begin{equation*}
-R=R_{J}R_{\frak{a}_{\perp }}.
-\end{equation*}
-Согласно этой факторизации и разложению  (\ref{sing decomp main}) характер $\mathrm{ch}\left( L^{\mu }\right) $ можно переписать в виде
-\begin{eqnarray*}
-\mathrm{ch}\left( L^{\mu }\right) &=&\left( R_{J}\right) ^{-1}\left( R_{%
-\frak{a}_{\perp }}\right) ^{-1}\Psi ^{\mu }=\left( R_{J}\right)
-^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}}\left( u\right) }\epsilon
-(u)\left( R_{\frak{a}_{\perp }}\right) ^{-1}\Psi _{\frak{a}_{\perp }}^{\mu _{%
-\frak{a}_{\perp }}\left( u\right) } \\
-&=&\left( R_{J}\right) ^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}%
-}\left( u\right) }\epsilon (u)\mathrm{ch}\left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
-}}\left( u\right) }\right),
-\end{eqnarray*}
-где  $\left\{ L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left(
-u\right) }|u\in U\right\} $ -- множество конечномерных $\frak{a}%
-_{\perp }$-модулей со старшими весами   $\mu _{\frak{a}_{\perp }}\left(
-u\right) $.
-Нас интересуют нетривиальные подалгебры $\frak{a}$ и, соответственно, нетривиальные  $\frak{a}_{\perp }$ (случай тривиальной ортогональной подалгебры рассматривался выше в (см.
-Замечание 1)).
-Значит $r_{\frak{a}}\geq 1$ и $r_{\frak{a}%
-_{\perp }}<r$.
-Так как диаграмма Дынкина для любой регулярной подалгебры получается в результате исключения одной, двух или более вершин из расширенной диаграммы Дынкина алгебры, а расширенная диаграмма содержит не более одного зависимого корня (старший корень), множество корней $\Delta _{\frak{a}_{\perp }}^{+}$ всегда эквивалентно некоторому множеству $\Delta _{I}^{+}$, порожденному набором  простых корней $I\subset S $.
+In case of injective splint we say that subalgebra $\frak{a}\hookrightarrow \frak{g}$
+splinters $\Delta $ (and call $\frak{a}$ the ''splinting subalgebra'' of $%
+\frak{g}$). In \cite{richter2008splints} splints are classified (see Appendix there)
+and the first three types of them are injective.
 
-Следовательно мы можем (переопределяя множество  $\Delta ^{+}$) отождествить $\Delta _{\frak{a}_{\perp }}^{+}$ с подмножеством  $\Delta _{I}^{+}$, где $I\subset S$.
-В результате мы можем определить объекты, необходимые для построения обобщенных модулей Верма \cite{lepowsky1977generalization,humphreys2008representations}.
-У нас есть два множества корневых векторов $\left\{ x_{\xi }\in \frak{g}_{\xi }|\xi \in \Delta _{I}^{+}\right\}
-$ и $\left\{ x_{\eta }\in \frak{g}_{\eta }|\eta \in \Delta ^{+}\setminus
-\Delta _{I}^{+}\right\} $, и соответствующие нильпотентные подалгебры в  $\frak{n}%
-^{+}$:
-\begin{equation*}
-\frak{n}_{I}^{+}:=\sum_{\xi \in \Delta _{I}^{+}}\frak{g}_{\xi },\quad
-\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\frak{g}%
-_{\eta }.
-\end{equation*}
-Первая подалгебра вместе со своей отрицательной копией  $\frak{n}%
-_{I}^{-} $ порождает простую подалгебру 
-\begin{equation*}
-\frak{s}_{I}=\frak{n}_{I}^{-}+\frak{h}_{I}+\frak{n}_{I}^{+}.
-\end{equation*}
-Мы расширяем ее оставшимися картановскими генераторами:
-\begin{equation*}
-\frak{l}_{I}=\frak{n}_{I}^{-}+\frak{h}+\frak{n}_{I}^{+}.
-\end{equation*}
-Полупрямое произведение  $\frak{l}_{I}$ и $\frak{u}_{I}^{+}$ дает параболическую подалгебру $\frak{p}_{I}\hookrightarrow \frak{g}$ :
+\section{How stems define multiplicity functions}
+
+\label{sec:stems and multiplicity functions}
+
+In this Section we study properties of injective splints  $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
+$. It will
+be demonstrated that in this case to find branching
+coefficients for a splinting injection $\frak{a}\hookrightarrow
+\frak{g}$ means to find weight multiplicities of an irreducible
+$\frak{s}$-module $L_{\frak{s}}^{\nu }$ with fixed highest weight
+$\nu $. Notice that $\frak{s}$ must not be a subalgebra of
+$\frak{g}$.
+
+Let us return to relation (\ref{singular main}) and multiply both sides by $%
+R_{\frak{a}}$:
 \begin{equation}
-\frak{p}_{I}=\frak{l}_{I}\vartriangleright \frak{u}_{I}^{+}.
-\label{paralolic subalg}
+\frac{1}{\prod_{\beta \in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })}\Psi _{%
+\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
+}^{(\mu )}\Psi _{\frak{a}}^{\left( \nu \right) }.
+\label{singular main-2}
 \end{equation}
-Ее универсальная обертывающая $U\left( \frak{p}_{I}\right) $ является подалгеброй в  $%
-U\left( \frak{g}\right) $. Модули  $L_{\frak{a}_{\perp }}^{\mu _{%
-\frak{a}_{\perp }}\left( u\right) }$ алгебры  $\frak{l}_{I}$ легко поднимаются до  $\frak{p}_{I}$-модулей при помощи тривиального действия нильрадикала $\frak{u}_{I}^{+}$.
-Последний стандартным образом индуцирует $U\left( \frak{g}\right) $-модули:
-\begin{equation*}
-M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=U\left( \frak{g}\right)
-\otimes _{U\left( \frak{p}_{I}\right) }L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
-_{\perp }}\left( u\right) }.
-\end{equation*}
+Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{%
+\frak{a}\rightarrow \frak{g}}$. Consider the highest weight module $L_{\frak{%
+s}}^{\nu }$. The embedding $\phi :\Delta _{\frak{s}\,0}\longrightarrow \Delta
+_{\frak{g}}$ sends the singular element $\Psi _{\frak{s}}^{\left( \nu
+\right) }$ into $\Psi _{\frak{g}}^{\left( \mu \right) }$. Applying the
+inverse morphism $\phi ^{-1}$ to the product $\left( \prod_{\beta \in \Delta
+_{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\frak{s}%
+}^{\left( \nu \right) }\right) $ one gets the character of the module $L_{%
+\frak{s}}^{\nu }$,
 
-Это  \textit{обобщенные модули Верма}  \cite{lepowsky1977generalization},
-порожденные старшими весами  $\mu _{\frak{a}%
-_{\perp }}\left( u\right) $. Как  $U\left( \frak{u}_{I}^{-}\right) $-модуль каждый  $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ изоморфен  $%
-U\left( \frak{u}_{I}^{-}\right) \otimes L_{\frak{a}_{\perp }}^{\mu _{%
-\frak{a}_{\perp }}\left( u\right) }$ и его характер можно записать при помощи функции Костанта-Хекмана \cite{KostantHeckman1982}, соответствующей вложению ортогонального партнера $\frak{a}_{\perp
-}\hookrightarrow \frak{g}$:
-\begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\mathcal{KH}_{%
-\frak{a}_{\perp }\hookrightarrow \frak{g}}\mathrm{ch}L_{\frak{a}_{\perp
-}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
-\end{equation*}
-Функция  $\mathcal{KH}_{\frak{a}_{\perp }\hookrightarrow \frak{%
-g}}$ генерируется знаменателем  $R_{I}$, так что последнее выражение можно переписать следующим образом
-\begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\frac{1}{R_{I}}%
-\mathrm{ch}L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
-\end{equation*}
-Таким образом мы получили обобщенную формулу Вейля-Верма для характеров -- разложение  $\mathrm{ch}\left(
-L^{\mu }\right) $ на характеры обобщенных модулей Верма:
 \begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
-u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
-u\right) }.  \label{char in gen verma mod}
+\phi ^{-1}\left( \frac{1}{\prod_{\beta \in \Delta _{\frak{s}%
+}^{+}}(1-e^{-\beta })}\phi \left( \Psi _{\frak{s}}^{\left( \nu \right)
+}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\frak{s}0
+}^{+}}(1-e^{-\beta })}\Psi _{\frak{s}}^{\left( \nu \right) }=\mathrm{ch}%
+\left( L_{\frak{s}}^{\nu }\right) .  \label{inverse for stem}
 \end{equation}
-\end{proof}
+Our task is to prove that the singular element $\Psi _{\frak{g}}^{\left( \mu
+\right) }$ contains the element $\Psi _{\frak{s}}^{\left( \xi \right) }$ for
+a module $L_{\frak{s}}^{\xi }$ uniquely defined by $L_{\frak{g}}^{\mu }$ and
+that the branching coefficients $b_{\nu }^{(\mu )}$ in the r.h.s. of (\ref
+{singular main-2}) coincide with multiplicities $m_{\zeta }^{\left( \xi
+\right) }$ of the corresponding weights in $\mathcal{N}_{\frak{s}}^{\xi }$ .
 
-\begin{remark}
-Здесь обобщенная формула Вейля-Верма для характеров (называемая формулой переменного суммирования в книге \cite{humphreys2008representations}) имеет специальный вид: веса $\mu _{\aft}$ отличны от старших весов обобщенных модулей Верма $\mu _{\afb}$.
-Причина в том, что старший вес $M_{I}$-модуля не равен проекции его максимального веса на  $h^*_{\afb}$ (он должен быть дополнительно сдвинут на дефект).
-\end{remark}
+For a highest weight irreducible module $L_{\frak{g}}^{\mu }$ the singular
+element $\Psi _{\frak{g}}^{\left( \mu \right) }$ is an element of $\mathcal{E%
+}$ corresponding to the shifted Weyl-orbit of the weight $\left( \mu +\rho
+\right) \in P^{+}$ with the sign function $\epsilon \left( w\right) $. It is
+convenient to use also unshifted singular elements
+\begin{equation}
+\Phi ^{\left( \mu \right) }:=\Psi ^{\left( \mu \right) }e^{\rho }.
+\label{definition Phi}
+\end{equation}
+In these terms the relation (\ref{singular main-2}) looks like
+\begin{equation}
+\frac{e^{\rho _{\frak{g}}-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{%
+s}}^{+}}(1-e^{-\beta })}\Phi _{\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in
+P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\Phi _{\frak{a}}^{\left( \nu \right) }.
+\label{singular main-3}
+\end{equation}
+The orbit related to $\Phi _{\frak{g}}^{\left( \mu \right) }$ is completely
+defined by the set of edges $\left\{ \lambda _{i}\right\} _{i=1,\dots ,r}$
+adjusted to the end of the highest weight vector $\mu +\rho $. For $\mu
+=\sum m_{i}\omega _{i}$ these edges are
+\begin{equation}
+\lambda _{i}=-\left( m_{i}+1\right) \alpha _{i},\quad i=1,\dots ,r.
+\label{edge}
+\end{equation}
+Each formal exponent $e^{\mu +\rho +\lambda _{i}}$ in $\Phi _{\frak{g}%
+}^{\left( \mu \right) }$ bears the sign coefficient $\epsilon =(-)$. The
+defining property of $\Phi _{\frak{g}}^{\left( \mu \right) }$ is as follows.
+Consider any pair of edges $\lambda _{i},\lambda _{j}$ and the corresponding
+weights $\mu +\rho $, $\mu +\rho +\lambda _{i}$ and $\mu +\rho +\lambda _{j}$. 
+Apply the reflection $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
+\begin{equation}
+s_{\alpha _{i}}\circ \left\{
+\begin{array}{l}
+\left( \mu +\rho \right)  \\
+\left( \mu +\rho +\lambda _{i}\right)  \\
+\left( \mu +\rho +\lambda _{j}\right)
+\end{array}
+\right. =\left\{
+\begin{array}{l}
+\left( \mu +\rho +\lambda _{i}\right)  \\
+\left( \mu +\rho \right)  \\
+\left( \mu +\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha
+_{j}\right)
+\end{array}
+\right.   \label{reflected triple}
+\end{equation}
 
+\begin{Prop}
+The edge $\lambda _{i,j}$ of $\Phi _{\frak{g}}^{\left( \mu \right) }$
+starting at the weight $\left( \mu +\rho +\lambda _{i}\right) $ along the
+root $-s_{\alpha _{i}}\circ \alpha _{j}$ has the same length in $(s_{\alpha
+_{i}}\circ \alpha _{j})$ as $\lambda _{j}$ has in $\alpha _{j}$. (The same
+is true for the edge $\lambda _{j,i}$, its length in $(s_{\alpha _{j}}\circ
+\alpha _{i})$ is equal to the length of $\lambda _{i}$ in $\alpha _{i}$.)
+\label{diagram property}
+\end{Prop}
+
+In $\Phi _{\frak{g}}^{\left( \mu \right) }$ the elements $e^{\left( \mu
++\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha _{j}\right) }$ and $%
+e^{\left( \mu +\rho +\lambda _{j}-(m_{i}+1)s_{\alpha _{j}}\circ \alpha
+_{i}\right) }$ have the sign coefficient  $\epsilon =(+)$.
+
+Remember that only three types of splints are
+injective and thus are naturally connected with branching. Below we
+reproduce the part of the splints table from \cite{richter2008splints} corresponding to
+injective splints:
+\[
+\begin{array}{cc||c|c}
+\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
+_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
+\\ \hline\hline
+\hbox{(i)} & G_{2} & A_{2} & A_{2} \\
+& F_{4} & D_{4} & D_{4} \\ \hline
+\hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
+& C_{r}(r\geq 3) & D_{r} & \oplus ^{r}A_{1} \\ \hline
+\hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
+^{r}A_{1} \\
+& B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
+\end{array}
+\]
+Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\frak{s}})
+$ of the simple root system $\Delta $. In the first two types both $\Delta _{%
+\frak{a}}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
+first type splints are equivalent and in the second are not. In the third
+type splints only $\Delta _{\frak{a}}$ is embedded metrically. The summands $%
+u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$. This does not change
+the principle properties of branching but makes it possible to use the
+multiplicities of $\frak{s}$-modules without further projecting their
+weights.
+
+Splints induce a decomposition of the set $S=S_{\frak{c}}\cup S_{\frak{d}}$
+with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}}$. 
+It is easy to check that for any injective splint the subset $S_{%
+\frak{d}}$ is nonempty. It follows that in the set $\left\{ \lambda
+_{i}\right\} _{i=1,\dots ,r}$ one can always find simple roots $\beta
+_{k}\in \Delta _{\frak{s}}$ and that the orbit corresponding to $\Phi _{%
+\frak{g}}^{\left( \mu \right) }$ contains the edges
+\begin{equation}
+\lambda _{k}=-\left( m_{k}+1\right) \beta _{k}  \label{beta edge}
+\end{equation}
+attached to the weight $\mu +\rho $. As far as $\Delta _{\frak{a}}$ is a
+root system and for any pair of simple roots from $S_{\frak{c}}$ the
+property \ref{diagram property} is fulfilled, the element $\Phi _{\frak{g}%
+}^{\left( \mu \right) }$ being a singular element for a set of $\frak{a}$%
+-modules. Consider $\beta _{l}\in \Delta _{\frak{s}}$ whose coimage in $%
+\Delta _{\frak{s}0}$ is simple. In Appendix it is shown that for any such $%
+\beta _{l}$ there exists a root $\alpha _{l}\in S_{\frak{c}}$ such that
+$\beta _{l}=\alpha _{l}+\beta _{k}$. It is easily seen that the
+corresponding edge intersects the boundary plane of the fundamental chamber $%
+\bar{C_{\frak{a}}}$ orthogonal to the root $\alpha _{l}$,
+\begin{equation}
+s_{\alpha _{l}}\left( \mu +\rho -p\beta _{l}\right) =s_{\alpha _{l}}\left(
+\mu +\rho \right) -ps_{\alpha _{l}}\beta _{l}=\mu +\rho -p\beta _{l},
+\label{intersection}
+\end{equation}
+\begin{equation}
+\mu +\rho -s_{\alpha _{l}}\left( \mu +\rho \right) =\left( m_{l}+1\right)
+\alpha _{l}=\left( m_{l}+1\right) \beta _{l}-\left( m_{l}+1\right) \beta
+_{k}=p\beta _{l}-ps_{\alpha _{l}}\beta _{l}.  
+\label{intersection-2}
+\end{equation}
+It follows that $p=\left( m_{l}+1\right) $ and $s_{\alpha _{l}}\beta
+_{l}=\beta _{k}$. Now apply the operator $s_{\beta _{k}}$ and find that the
+edge along the root $s_{\beta _{k}}\alpha _{l}$ attached at the weight $%
+s_{\beta _{k}}(\mu +\rho )$ is also equal to $-ps_{\beta _{k}}\alpha _{l}$.
+This means that for the triple of roots $\beta _{k},\beta _{l}$ and $%
+s_{\beta _{k}}\alpha _{l}$ in $\Delta _{\frak{s}}$ the edges $\lambda
+_{k}=-\left( m_{k}+1\right) \beta _{k}$, $\lambda _{l}=-\left(
+m_{l}+1\right) \beta _{l}$ and $\lambda _{kl}=-\left( m_{l}+1\right)
+s_{\beta _{k}}\alpha _{l}$ demonstrate the property \ref{diagram property}.
+One can continue this procedure further in the 2-dimensional subspace fixed
+by the roots $\beta _{k}$ and $\beta _{l}$ and find the set of formal
+exponents that being supplied with the corresponding sign factors compose
+the coimage of the singular element of a module for the subalgebra in $\frak{%
+s}$ (this subalgebra has rank $r=2$).
+
+The same can be proven for any positive root $\beta _{l}\in \Delta $ that is
+simple in $\Delta _{\frak{s}0}$ and correspondingly for any $r=2$ subalgebra
+in $\frak{s}$. The latter means that to ''find'' a singular element of $%
+\frak{s}$-module in $\Phi _{\frak{g}}^{\left( \mu \right) }$ it is necessary
+to incorporate in it additional formal elements $\left\{ -e^{\mu +\rho
+-\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\}.$ This
+fixes the starting edges of the diagram $\phi ^{-1}\left( \Phi _{\frak{s}}^{%
+\widetilde{\mu }}\right) $. As it follows from the reconstruction procedure
+the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $%
+, they have the same Dynkin numbers:
+\begin{equation}
+\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
+m_{k}\widetilde{\omega }_{k} . \label{new h weight}
+\end{equation}
+The next step is to construct the full $W_{\frak{s}}$-orbit $\Phi _{\frak{s}%
+}^{\left( \widetilde{\mu }\right) }$  in $P_{\frak{s}}$. It is easily seen
+that its coimage belongs to $\bar{C_{\frak{a}}}$ and that the set $\phi
+^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) \setminus \Phi _{%
+\frak{g}}^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ corresponds to the
+weights belonging to the boundary $\bar{C_{\frak{a}}}$ (including the subset
+$\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{%
+\frak{c}}\right\} $). Thus we have constructed all the formal elements\ with
+the appropriate sign factors that after being added to $\Phi _{\frak{g}%
+}^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ form the diagram $\phi
+^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) $ in $\bar{C_{\frak{a}%
+}}$.
+
+Now let us return to relation (\ref{singular main-3}). One can add to $%
+\Phi _{\frak{g}}^{\left( \mu \right) }$ pairs of formal elements
+constructed above  with the opposite signs: $\epsilon \left( w\right)
+|_{w\in W_{\frak{s}}}$ and $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$. 
+Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ to
+the elements whose weights we shall attribute to $\bar{C_{\frak{a}}}$. 
+The same elements with the opposite signs are to be referred to the
+neighboring Weyl chambers of $\bar{C_{\frak{a}}^{(l)}}$ (the latter are
+connected with the main one via simple reflections $s_{\alpha _{l}}$ so the
+signes $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ are natural for
+them). In fact one can repeat the procedure and find additional singular
+weights in any Weyl chamber $\bar{C_{\frak{a}}^{(m)}}$ and in them
+additional singular weights always have the signs opposite to that in their
+nearest neighbors. Thus without changing the element $\Phi _{\frak{g}%
+}^{\left( \mu \right) }$ one can present it as a sum
+\begin{equation}
+\Phi _{\frak{g}}^{\left( \mu \right) }=\sum_{w\in W_{\frak{a}}}w\circ \left(
+e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho _{\frak{s}}}\right)
+\label{singular final}
+\end{equation}
+where the weight $\widetilde{\mu }=\sum m_{k}\omega _{\frak{s}}^{k}$ was
+defined above. The decomposition (\ref{singular final}) provides the
+possibility to apply the factor $\left( \prod_{\beta \in \Delta _{\frak{s}%
+}^{+}}(1-e^{-\beta })\right) ^{-1}$ to each summand of the singular element $%
+\Phi _{\frak{g}}^{\left( \mu \right) }$ separately because the sets of
+weights from different Weyl summands do not intersect. Taking into account
+the isomorphism $\phi $ one can see that in the main Weyl chamber $\bar{C_{%
+\frak{a}}}$ the set of weights generated by the factor $\left( \prod_{\beta
+\in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}$ is isomorphic to
+the weight diagram $\mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ of the $\frak{%
+s}$-module $L_{\frak{s}}^{\widetilde{\mu }}$. Now one can restrict
+relation (\ref{singular main-3}) to $\bar{C_{\frak{a}}}$ and obtain the main
+result:
+\begin{Prop}
+\begin{equation}
+\frac{e^{\rho _{\frak{g}}}}{\prod_{\beta \in \Delta _{\frak{s}%
+}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
+}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }%
+}}M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
+\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}=\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
+\label{singular main-4}
+\end{equation}
+Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
+highest weights in the decomposition. The multiplicity $M_{\left( \frak{s}%
+\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
+}\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ defines the branching
+coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
+-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
+\[
+b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}.
+\]
+\end{Prop}
+
+\section{Examples}
+\label{sec:examples}
 \begin{example}
-  Рассмотрим обобщенные модули Верма для вложения $A_{1}\hookrightarrow B_{2}$, где подалгебра  $\afb$ связана с корнем  $\alpha_{1}$ алгебры  $B_{2}$.
-Обобщенный модуль Верма $M^{\omega_{1}}_{I}$ со старшим весом   $\omega_{1}=e_{1}$ показан на Рисунке \ref{fig:B2_Verma_Decomp}.
+  Consider the Lie algebra $A_{2} =\bf{sl}(3)$ and branching of its irreducible module $L^{[3,2]}_{A_{2}}$ with respect to the reductive subalgebra $A_{1}\oplus u(1)$.
+The root system  $\Delta _{\frak{a}}= \Delta_{A_{1}\oplus u(1)}$ contains the simple root of $\alpha_1=e_1-e_2$ of $A_{2}$.
+The singular element $\Psi^{[3,2]}_{\frak{a}}$ is decomposed into a sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules.
+Branching coefficients $b_{\nu }^{[ 3,2 ] }$ coincide with weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module (see Fig.
+\ref{fig:a2_splint}).
+
   \begin{figure}[h!bt]
   \noindent\centering{
-   \includegraphics[width=120mm]{B2_Gen_Verma_Decomp}
+   \includegraphics[width=80mm]{a2-a1}
   }
-  \caption{Обобщенные модули Верма для регулярного вложения  $A_1$ в $B_2$. 
-    Простые корни $\alpha_1, \alpha_2$ алгебры $B_2$ показаны пунктирными стрелками.
-Простой корень  $\beta = \alpha_1+2\alpha_2$ алгебры $A_1$ изображен серым вектором.
-Разложение $L^{\omega_{1}}$ представлено набором контуров входящих в него обобщенных модулей Верма.
-Пунктирные контуры соответствуют положительным значениям  $\epsilon(u)$, а точечные -- отрицательным.
+  \caption{Weyl group orbit (dotted) producing singular element of $L^{[3,2]}_{A_{2}}$ and its decomposition into the sum of splint images of singular elements of modules  $L^{[3,2]}_{A_{1}\oplus A_{1}}$ (dashed).
+Weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}
+
+ \label{fig:a2_splint}
+\end{figure}
+\end{example}
+\begin{example}
+  For the Lie algebra $B_{2}= \bf{so}(5)$ branching of its irreducible module $L^{[3,2]}$ into  modules of a reductive subalgebra $A_{1}\oplus u(1)$ with the root system spanned by the first simple root $\alpha_1=e_1-e_2$ of $B_{2}$.
+Singular element of $\Psi^{[3,2]}_{B_{2}}$ is decomposed into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide with weight multiplicities of $A_{2}$-module (see Fig.
+\ref{fig:b2_splint}).
+
+  \begin{figure}[h!bt]
+  \hspace*{-1.2cm}
+
+   \includegraphics[width=65mm]{b2}
+   \includegraphics[width=65mm]{b2-a2-a1}
+  \caption{Weights of the $B_{2}$-module $L^{[3,2]}$ are indicated by dots in the left picture (their multiplicities are also indicated).
+Contour of the singular element is shown by dotted line.
+The right picture presents the decomposition of  $\Psi_{B_{2}}(L^{[3,2]}_{B_{2}})$-singular element into the sum of splint images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ (dashed).
+Weight multiplicities of $L^{[3,2]}_{A_{2}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{B_{2}\downarrow A_{1}\oplus u(1)}$.}
+
+ \label{fig:b2_splint}
+\end{figure}
+\end{example}
+
+\vspace{10mm}
+\begin{example}
+   Lie algebra $G_{2}$ has a regular subalgebra $A_{2}$ with root system $\Delta_{\mathfrak{a}}=\Delta_{A_{2}}$ containing the $G_{2}$ long roots.
+Consider branching of an irreducible module $L_{G_{2}}^{(3,2)}$ into the $A_{2}$-modules.
+Singular element $\Psi_{G_{2}}(L^{[3,2]})$ is decomposed into the sum of splint images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ and the corresponding branching coefficients coincide with weight multiplicities of $L^{[3,2]}_{A_{2}}$-module (see Fig.
+\ref{fig:g2_splint}).
+
+  \begin{figure}[h!bt]
+  \noindent\centering{
+   \includegraphics[width=120mm]{g2}
   }
 
- \label{fig:B2_Verma_Decomp}
+  \caption{Weyl group orbit (dotted) for the singular element $\Psi_{G_{2}}(L^{[3,2]})$ and its decomposition into the sum of splint images of singular elements of $A_{2}$-modules (dashed).
+Weight multiplicities of $L^{[3,2]}_{A_{2}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{G_{2}\downarrow A_{2}}$.}
+
+ \label{fig:g2_splint}
 \end{figure}
@@
 
-\begin{remark}
-Как доказано, например, в книге  \cite{humphreys2008representations} (см.
-утверждение 9.6), характеры обобщенных модулей Верма $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ могут также описываться как линейные комбинации обычных модулей Верма алгебры $\frak{g}$:
-\begin{equation*}
-\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\sum_{w\in W_{%
-\frak{a}_{\perp }}}\epsilon \left( w\right) \mathrm{ch}M^{w\left( \mu _{%
-\frak{a}_{\perp }}\left( u\right) +\rho _{\frak{a}_{\perp }}\right) -\rho _{%
-\frak{a}_{\perp }}}
-\end{equation*}
-Подставляя это выражение в формулу (\ref{char in gen verma mod}) и используя определения  (\ref{mu-a},\ref{mu-a-tilda}) и (\ref{defect ort}), мы восстанавливаем стандартное разложение Вейля-Верма для характера:
-\begin{equation*}
-\mathrm{ch}\left( L^{\mu }\right) =\sum_{w\in W}\;\epsilon (u)\mathrm{ch}%
-M^{w\left( \mu +\rho \right) -\rho }.
-\end{equation*}
-\end{remark}
+\section{Conclusions}
 
-\subsection{БГГ резольвента и ветвление}
-В работе \cite{lepowsky1977generalization} показано, что для модуля старшего веса $L^{\mu }$, где $\mu \in P^{+}$, последовательность (обобщенная БГГ резольвента)
-\begin{equation}
-0\rightarrow M_{r}^{I}\overset{\delta _{r}}{\rightarrow }M_{r-1}^{I}\overset{%
-\delta _{r-1}}{\rightarrow }\ldots \overset{\delta _{1}}{\rightarrow }%
-M_{0}^{I}\overset{\varepsilon }{\rightarrow }L^{\mu }\rightarrow 0,
-\label{resolution sequence}
-\end{equation}
-где
-\begin{equation}
-M_{k}^{I}=\bigoplus_{u\in U,\;\mathrm{length}\left( u\right)
-=k}M_{I}^{u\left( \mu +\rho \right) -\rho },\quad M_{0}^{I}=M_{I}^{\mu }
-\label{Verma elements sequence}
-\end{equation}
-является точной и формула (\ref{gen Weyl-Verma}%
-) следует из этого разложения.
+\label{sec:conclusions}It is explicitly demonstrated that splint
+presents a very effective tool to find branching coefficients. In
+particular injective splints provide a possibility to reduce
+branching rules calculations for highest weight modules to a
+determination of weight multiplicities for a module with the same
+Dynkin labels referred to the Lie algebra $\mathfrak{s}$. This algebra
+$\mathfrak{s}$ must not be a subalgebra in the initial $\mathfrak{g}$ , it
+has the same rank $r_{\mathfrak{s}}=r$\ , but obviously less
+"complicated" than $\mathfrak{g}$ -- only a subset of the initial root system is involved in the second stem $\Delta_{\mathfrak{s}}$.
+
+It is significant that for the injections $D_{r}\hookrightarrow B_{r}$ , $%
+D_{r}\hookrightarrow C_{r}$ and $A_{r-1}\oplus u\left( 1\right) \hookrightarrow A_{r}$ splint technique shows
+transparently Gelfand-Tzeytlin rules for branching:  the reduction is
+multiplicity free (all nonzero
+branching coefficients are equal to 1). Here it is an immediate consequence of the
+structure of the second stem being a direct sum of $A_{1}$
+algebras and the fact that the corresponding module
+$L_{\frak{s}}^{\mu }$ is irreducible.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Appendix}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Let us demonstrate that for injective splints of classical Lie
+algebras the following property is valid:
+\begin{Prop}
+Let $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})$ be an
+injective
+splint with the decomposition of simple roots $S=S_{\frak{c}}\cup S_{\frak{d}%
+}$ with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}%
+}$.
+\end{Prop}
+Thus for any simple root $\beta \in S_{\frak{s}}$ there exists the
+pair of
+roots ( $\alpha $ ,$\beta ^{\prime }$) with $\alpha \in $ $S_{\frak{c}%
+},\beta ^{\prime }\in S_{\frak{s}}$ such that $\alpha =\beta
+-\beta ^{\prime }$
+
+\begin{itemize}
+\item
+Type 1. $\Delta _{G_{2}}\approx (\Delta _{A_{2}},\Delta
+_{A_{2}}).$
 
@@
   \noindent\centering{
-   \includegraphics[width=140mm]{B2_Exact}}
- \caption{Вложение $A_1\hookrightarrow B_2$ (см. Рисунок \ref{fig:B2_Verma_Decomp}). Ортогональный партнер, подалгебра $A_1$, соответствует корню $\alpha_1$.
-   Резольвента простого модуля $L^{\omega_1}$. Показана центральная часть точной последовательности
-   $0 \to Im(\delta_2) \to \left( e^{\mu _{\widetilde{%
-\frak{a}}}\left( e\right) }\mathrm{ch}M_{I}^{\pi _{\afb}\left[ \omega_1 \right] -%
-\mathcal{D}_{\afb} }=M^{\omega_1}_{I}\right) \to
-   L^{\omega_1}\to 0 $.  Здесь $\mu _{\widetilde{\frak{a}}}\left( e\right) =\pi _{\aft}\left[ \mu \right] + \mathcal{D}_{\afb}$.
+   \includegraphics[width=100mm]{g2-roots}
   }
+  \caption{Positive roots of $G_{2}$ and formation of singular element $\Phi^{(0)}_{\mathfrak{s}}$ in the main Weyl chamber of $\mathfrak{a}=A_{2}$.}
 \end{figure}
+Here both stems are metric and the corresponding root systems are
+equivalent. In Figure 4 a part of the singular element $\Phi
+_{G_{2}}^{\left( 0\right) }$ is presented. The boundaries of $\bar{C_{\frak{a%
+}}}$ are the dashed lines starting at the center of the singular
+element. It
+contains the edge $\lambda _{2}=-\alpha _{2}=-\beta _{2}$ and the roots $%
+-\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3}$ and $ -\beta _{3}$
+($\beta _{3}$ is indicated as $\beta _{l}$). For the root $\beta
+_{1}$ the necessary pair
+is  $(\alpha _{1}, \beta _{2})$: $\alpha _{1}=\beta _{1}-\beta _{2}$. The $%
+\lambda _{2,3}^{\frak{s}}=\beta _{3}$ edge is equal to $\lambda _{1}^{\frak{s%
+}}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ and $m_{1}$ index
+is aquired by the $\frak{s}$-module that also inherit the second
+index $m_{2}$. In this particular
+case they are $m_{1}=m_{2}=0$. The general case with the initial module $%
+L^{\mu }$ and $\mu =m_{1}\omega _{1}+m_{2}\omega _{2}$ can be
+treated in the same way: one finds an edge $\lambda _{2}=-\left(
+m_{2}+1\right) \beta _{2}$ and put $\lambda
+_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$, its end
+belongs to the boundary $\bar{C_{\frak{a}}}$. The reflection
+$s_{\beta
+_{2}} $ sends $\beta _{1}$ to $\beta _{3}$ and the corresponding edge 
+$\lambda _{2,3}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{3}$ has
+the length $\left( m_{1}+1\right) $. Now consider $\lambda _{1}^{\frak{s}}$ (or
+$\lambda _{2,3}^{\frak{s}} $) and $\lambda _{1,3}^{\frak{s}}$ (or
+$\lambda _{2,3,1}^{\frak{s}}$) edges to find that they belong to
+the boundary $\bar{C_{\frak{a}}}$ and the Weyl symmetry predicts
+that $\lambda _{1,3}^{\frak{s}}=-\left( m_{2}+1\right)
+\beta _{3}$ ($\lambda _{2,3,1}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{1}$%
+) . Finally the edge $\lambda _{1,3,2}^{\frak{s}}=-\left(
+m_{1}+1\right) \beta _{2}$ closes the polytope. Its vertices
+correspond to weights of the singular
+element $\Phi _{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{%
+\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
+\widetilde{\mu }+\rho
+_{\frak{s}}\right) }$ of the module $L_{\frak{s}}^{\left( \widetilde{\mu }%
+\right) }$ with $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}%
+\widetilde{\omega }_{2}$. Notice that in this case the sign
+factors can be obtained directly in the initial weight system as
+far as the stem is metric.
+\item
+Type 1. $\Delta _{F_{4}}\approx (\Delta _{D_{4}},\Delta
+_{D_{4}}).$
 
-\begin{statement}
-Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра  $\afb\hookrightarrow \frak{g}$ ортогональна редуктивной подалгебре $\frak{a}\hookrightarrow \frak{g}$.
-Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\afb$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к подалгебре $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}$ .
-\end{statement}
+Both stems are metric here and the corresponding root systems are
+equivalent. The system $\Delta _{D_{4}}$ of the subalgebra
+$\frak{a=}D_{4}$ is formed by the set $\left\{ \pm e_{i}\pm
+e_{j}\right\} _{|i,j=1,\ldots 4,\; i\neq j}.$ The simple roots
+$S_{\frak{c}}$ are $\left\{ e_{2}-e_{3},e_{3}-e_{4}\right\} $ and
+$S_{\frak{d}}=\left\{ e_{4},\frac{1}{2}\left(
+e_{1}-e_{2}-e_{3}-e_{4}\right) \right\} $.
+For a module $L^{\mu }$ with $\mu =\sum m_{k}\omega _{k}$ consider the edge $%
+\lambda _{3}=-\left( m_{3}+1\right) e_{4}=-\left( m_{3}+1\right)
+\beta _{3}$.
+ Compose an edge $\lambda _{2}^{\frak{s}}=-\left( \widetilde{m}%
+_{2}+1\right) \beta _{2}$. The necessary pair of roots is $\left(
+\alpha
+_{2}=e_{3}-e_{4},\beta _{3}\right) $. The intersection of $\lambda _{2}^{%
+\frak{s}}$ with the $\alpha _{2}$-boundary of
+$\bar{C_{\frak{a}}}$ fixes
+its length to be $\lambda _{2}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{2}$%
+\ and the length of the edge $\lambda _{3,2}^{\frak{s}}$ is equal
+to that of
+$\lambda _{2}^{\frak{s}}$. Next consider the edge $\lambda _{2}^{\frak{s}%
+}=-\left( m_{2}+1\right) \beta _{2}$ and the pair $\left( \alpha
+_{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $. The length of  
+$\lambda _{1}^{\frak{s}}$ becomes equal to $\lambda
+_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$. Proceed further till the closure of the polytope. 
+The edges looking along the roots of the $\alpha_4$-type, $\alpha _{4}=\beta
+_{4}=$ $\frac{1}{2}\left( e_{1}-e_{2}-e_{3}-e_{4}\right) $, are
+treated similarly and finally the singular element $\Phi
+_{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in
+W_{\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
+\widetilde{\mu }+\rho _{\frak{s}}\right) }$ for the module
+$L_{\frak{s}}^{\left( \widetilde{\mu }\right) }$ with
+$\widetilde{\mu }=\sum m_{k}\widetilde{\omega }_{k}$ is formed in
+$\bar{C_{\frak{a}}}$.
+\item
+Type 2. $\Delta _{B_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
+^{r}A_{1}}). $
 
-\begin{proof}
-Положим
-\begin{equation*}
-\mathrm{ch}M_{I}^{u\left( \mu +\rho \right) -\rho }=e^{\mu _{\widetilde{%
-\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
-u\right) },\mathrm{ch}M_{I}^{\mu }=e^{\mu _{\widetilde{\frak{a}}}\left(
-e\right) }\mathrm{ch}M_{I}^{\pi _{\frak{a}_{\perp }}\left[ \mu \right] -%
-\mathcal{D}_{\frak{a}_{\perp }}},
-\end{equation*}
-где \ $\mu _{\widetilde{\frak{a}}}\left( u\right) ,\mu _{\frak{a}_{\perp
-}}\left( u\right) $ и $\mathcal{D}_{\frak{a}_{\perp }}$ заданы как в Лемме \ref{Psi-decomp-lemma}, $%
-u\in U$ определено формулой (\ref{U-def}). В результате получим элементы фильтрующей последовательности (\ref{resolution sequence}).
+Both stems are metric. An injection is fixed by the stem $\Delta
+_{D_{r}}$ simple roots $S_{\frak{a}}=\left\{
+e_{1}-e_{2},e_{2}-e_{3},\ldots
+,e_{r-1}-e_{r},e_{r-1}+e_{r}\right\} $. The second stem
+corresponds to a
+direct sum of algebras $A_{1}$ with the simple roots $S_{\frak{s}%
+}=\left\{ e_{1},e_{2},\ldots ,e_{r-1},e_{r}\right\} $. Consider the edge $%
+\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ (here $\beta
+_{r}=e_{r}$) and $\lambda _{r-1}=-\left(
+\widetilde{m}_{r-1}+1\right) \beta _{r-1}$
+attached to it (here $\beta _{r-1}=e_{r-1}$). The corresponding pair is $%
+\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta _{r-1}=e_{r-1}\right) $.
+ The intersection condition fixes the second edge to be $\lambda
+_{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ , it is orthogonal
+to $\beta _{r}$ so the opposite edge has the same length. The
+Dynkin index $m_{r-1}$ now refers
+also to the\ simple root $\beta _{r-1}$. Next consider the obtained edge $%
+\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and $\lambda
+_{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$ to
+fix the index $\widetilde{m}_{r-2}=m_{r-2}$ and the edge
+$\lambda _{r-2}=-\left( m_{r-2}+1\right) \beta _{r-2}$ and so on
+till all the pairs of edges are properly fixed. Finally in
+$\bar{C}_{D_{r}}$ the element $\Phi _{\oplus ^{r}A_{1}}^{\left(
+\widetilde{\mu }\right) }=\sum_{w\in W_{\oplus
+^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+%
+\frac{1}{2}\sum e_{k}\right) }$ can be constructed for the module
+$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
+$\widetilde{\mu }=\sum m_{k}\frac{1}{2}e_{k}$.
 
-Рассмотрим множество $\left\{ \mu _{\frak{a}_{\perp }}\left( u\right) |u\in U\right\} $ как множество старших весов простых модулей $L_{\frak{a}%
-_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ и вычислим размерности этих модулей. Вместе с 
-$\left\{ \mu _{\widetilde{\mathfrak{a}}}\left( u\right) |u\in
-U\right\} $ мы получим набор сингулярных весов
-\begin{equation*}
-\left\{ \epsilon (u)\;
-e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }
-\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
-}}\left( u\right) }\right) \right\} .
-\end{equation*}
-Ветвление  $L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu
-\in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$  определяется веером вложения  $\Gamma _{\frak{a}\rightarrow \frak{g}}$ и соотношением (\ref{recurrent rel}), которое дает нам коэффициенты  $k_{\xi
-}^{\left( \mu \right) }$, а значит определяет и  $b_{\nu }^{\left( \mu \right) }$, так как  $b_{\nu }^{\left( \mu \right) }=k_{\nu }^{\left( \mu
-\right) }$ при $\nu \in \overline{C_{\frak{a}}}$ .
-\end{proof}
+\item
+Type 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
+^{r}A_{1}}). $
 
-\begin{corollary}
-Пусть  $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$ и  $\frak{a}\hookrightarrow \frak{g}$ -- редуктивная подалгебра $\frak{g}$.
-Пусть $\frak{a}_{\perp }$, ортогональный партнер для $\frak{a}$, эквивалентен  $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, и $\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ с $\frak{h=\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$.
-Пусть $L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }=\bigoplus\limits_{\nu \in P_{\widetilde{\frak{a}}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\widetilde{\frak{a}}}^{\nu }$ -- ветвление модуля $L^{\mu }$ относительно подалгебры $\widetilde{\frak{%
-a}}$. Тогда коэффициенты $b_{\nu }^{\left( \mu \right) }$ определяют обобщенную резольвенту (\ref{resolution sequence}) модуля $L^{\mu }$
-по отношению к  $\frak{a}_{\perp }$.
-\end{corollary}
+The situation in this case is eqivalent to the previous one and
+the additional edges are constructed similarly.
+\item
+Type 3 $\Delta _{A_{r}}\approx (\Delta _{A_{r-1}\oplus
+u_{1}},\Delta _{\oplus ^{r}A_{1}}).$
 
-\begin{proof}
-Пусть $\alpha $ -- простой корень  $A_{1}$.
-Используем преобразования из группы Вейля чтобы перевести его в некоторый простой корень алгебры $\frak{g}$, например $\alpha _{1}$.
-Построим сингулярный элемент для модуля  $L_{\frak{g}\downarrow
-\widetilde{\frak{a}}}^{\mu }$, то есть  $\Psi _{\widetilde{\frak{a}}%
-}^{\left( L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }\right)
-}=\sum_{\nu \in P_{\widetilde{\frak{a}}}^{+},b_{\nu }^{\left( \mu \right)
-}>0}b_{\nu }^{\left( \mu \right) }\Psi _{\widetilde{\frak{a}}}^{\left( \nu
-\right) }$, и разложим его $\Psi _{\widetilde{\frak{a}}}^{\left( L_{\frak{%
-g}\downarrow \widetilde{\frak{a}}}^{\mu }\right) }=k_{\xi }^{\left( \mu
-\right) }e^{\xi }$. В нашем случае представители $u$ в рекуррентном соотношении (\ref{recurrent rel}) определяются весом $\xi $ однозначно:
-\begin{equation*}
-\epsilon (u\left( \xi \right) )\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{%
-\frak{a}_{\perp }}\left( u\left( \xi \right) \right) }\right) =-s\left(
-\gamma _{0}\right) k_{\xi }^{\left( \mu \right) }-\sum_{\gamma \in \Gamma _{%
-\widetilde{\frak{a}}\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right)
-k_{\xi +\gamma }^{\left( \mu \right) }.
-\end{equation*}
-Тогда
-\begin{equation*}
-\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\left(
-\xi \right) \right) }\right) =\left| s\left( \gamma _{0}\right) k_{\xi
-}^{\left( \mu \right) }+\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}%
-\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma
-}^{\left( \mu \right) }\right|
-\end{equation*}
-и
-\begin{equation*}
-\mu _{\frak{a}_{\perp }}\left( u\left( \xi \right) \right) =\frac{1}{2}%
-\left( \dim \left( L_{A_{1}}^{\mu \left( \xi \right) }\right) -1\right)
-\alpha _{1}
-\end{equation*}
-Таким образом, множество обобщенных модулей Верма  $e^{\xi +\mathcal{D}%
-_{\frak{a}_{\perp }}}\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
-u\left( \xi \right) \right) }$ полностью фиксировано:
-\begin{equation*}
-\left\{ e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }\mathrm{ch}%
-M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }|u\in U\right\} .
-\end{equation*}
-Упорядочивая эти модули по длине $u$, мы получаем компоненты (\ref{Verma elements sequence}) резольвенты (\ref{resolution sequence}).
-\end{proof}
+Here only the first stem is metric and it fixes the injection with
+simple roots $S_{\frak{a}}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots
+,e_{r-1}-e_{r}\right\} $. The second stem corresponding to a direct sum of $%
+r$ copies of $A_{1}$ has the simple roots $S_{\frak{s}}=\left\{
+e_{1}-e_{r+1},e_{2}-e_{r+1},\ldots ,e_{r}-e_{r+1}\right\} $.
+Consider the edge $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$
+with $\beta
+_{r}=e_{r}-e_{r+1}$ and $\lambda _{r-1}=-\left( \widetilde{m}%
+_{r-1}+1\right) \beta _{r-1}$ \ with $\beta
+_{r-1}=e_{r-1}-e_{r+1}$ attached to it. Then the corresponding
+pair is $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta
+_{r-1}=e_{r-1}-e_{r+1}\right)$. The intersection with the
+boundary of $\bar{C}_{A_{r-1}}$ orthogonal to $\alpha _{r-1}$
+fixes the second edge to be $\lambda _{r-1}=-\left(
+m_{r-1}+1\right) \beta _{r-1}$. The Dynkin index $m_{r-1}$ is to
+be used for the fundamental weight  $\omega _{r-1}.$ The\
+reflection $s_{\beta _{r}}$ sends $\lambda _{r-1}=-\left(
+m_{r-1}+1\right) \beta _{r-1}$ to $\lambda _{r,r-1}=-\left(
+m_{r-1}+1\right) \beta _{r-1}.$ Next consider the obtained edge
+$\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and
+$\lambda _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$
+with $\beta _{r-2}=e_{r-2}-e_{r+1} $ to obtain the index
+$\widetilde{m}_{r-2}=m_{r-2}$ and the edge $\lambda _{r-2}=-\left(
+m_{r-2}+1\right) \beta _{r-2}$ and so on till all the pairs of
+edges are properly fixed. Finally in $\bar{C}_{D_{r}}$ the element
+$\Phi _{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right)
+}=\sum_{w\in W_{\oplus
+^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+%
+\widetilde{\rho }\right) }$ can be constructed for the module
+$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
+$\widetilde{\mu }=\sum m_{k}\beta _{k}.$ The simplest case
+$\Delta _{A_{2}}\approx (\Delta _{A_{1}\oplus u_{1}},\Delta
+_{A_{1}\oplus A_{1}})$ is presented in Example 4.1 and Figure 1.
+\item
+Type 3 $\Delta _{B_{2}}\approx (\Delta _{A_{1}},\Delta _{A_{2}}).$
 
-\subsection{Заключение}
+This splint is illustrated in Example 4.1 and Figure 1, 
+$S_{A\_1}=\left\{ e_{1}-e_{2}\right\} $, $S_{A\_2}=\left\{
+e_{1},e_{2}\right\} $. The edge $\lambda _{\alpha _{2}}=\lambda
+_{\beta _{2}}=-\left( m_{2}+1\right) \beta _{2}$ is followed by
+$\lambda _{\beta _{1}}=-\left( \widetilde{m}_{1}+1\right) \beta
+_{1}$. Consider the pair $\left( \alpha
+_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right)$. The end of the edge
+$\lambda _{\beta _{1}}$ must indicate a weight
+invariant under the reflexion $s_{\alpha _{1}}$.  Its length is thus fixed: 
+$\lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$. In the
+coimage of
+the second stem, that is in the root system $\Delta_{A_{2}}$, the reflection 
+$s_{\beta _{2}}$ sends $\lambda _{\beta _{1}}=-\left(
+m_{1}+1\right) \beta
+_{1}$ to $\lambda _{2,3}$, thus the latter edge has the same length in $%
+\beta _{3}=e_{1}+e_{3}$, we have $\lambda _{2,3}=-\left(
+m_{1}+1\right)
+\beta _{3}$ with $\beta _{3}=e_{1}+e_{3}$. The irreducible $\frak{s}$%
+-module has the highest weight $\widetilde{\mu }=m_{1}\widetilde{\omega }%
+_{1}+m_{2}\widetilde{\omega }_{2}$. In Figure 1 we see the
+details of these relations in a particular case where
+$L_{B_{2}}^{\left[ 3,2\right] }$ is reduced to a subalgebra
+$A_{1}\oplus u\left( 1\right) $ and the
+corresponding highest weights (with their multiplicities) form the diagram $%
+\mathcal{N}_{A_2}^{\left[ 3,2\right] }$ .
+\end{itemize}
 
-\label{sec:conclusions}
-В работе \cite{2010arXiv1007.0318L} было показано, что метод веера вложения работает также и для специальных вложений.
-Надо заметить, что  разложения Вейля-Верма также могут быть получены в этом случае.
-Резольвенты, соответствующие специальным подалгебрам, описывают соотношения между проекциями характера начального модуля и обобщенными модулями Верма со старшими весами в подпространстве $h^*$.
-
-Рассмотрим ситуацию, когда выбор простых корней зафиксирован какими-то внешними факторами (возникающими, например, из требований физических приложений).
-В этом случае ортогональный партнер не может порождаться только простыми корнями.
-Элементы   $\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta
-^{+}\setminus \Delta _{I}^{+}}\frak{g}_{\eta }$ не образуют подалгебру в  $%
-\mathfrak{g}$, так как некоторые не простые корни отсутствуют в  $\Delta ^{+}\setminus
-\Delta _{I}^{+}$. Важно отметить, что в этом случае формула Вейля-Верма по-прежнему существует. В ней обобщенные модули Верма соответствуют сжатиями \cite{Doebner1967Melsheimer} алгебры $%
-\frak{n}^{+}$ и соотношения Вейля-Верма описывают разложение пространства представления $L^{\mu}$ в набор обобщенных модулей Верма сжатой алгебры  $U\left(\frak{n}_c^{+}\right)$.
-Весовые векторы образованы базисом Пуанкаре-Биркгофа-Витта алгебр $U\left(\frak{n}_c^{+}\right)$ и
-$U\left( \mathfrak{a}_{\bot} \right)$. Чтобы рассмотреть такое пространство как  $%
-\mathfrak{g}$-модуль мы должны выполнить деформацию \cite
-{Nijenhuis1966Richardson} алгебры $\frak{n}_c^{+}$ (то есть восстановить первоначальный закон композиции).
-Пространство сохраняется, и после такой деформации генераторы начальной алгебры будут действовать на нем правильным образом.
-
-%%
-%% End of file
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: "thesis"
-%%% End:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2011-11-29 AffineLieAlgebras/Splints/paper.tex
Updated to submitted version

@@
 \author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$ \\
-  {\small $^1$ Department of High-energy and elementary particle physics, SPb State University}\\
+  {\small $^1$ Department of High-Energy and Elementary Particle Physics, SPb State University}\\
   {\small 198904, Saint-Petersburg, Russia}\\
@@
 \begin{abstract}
-Splint of root system of simple Lie algebra appears naturally in
-the study of (regular) embeddings of reductive subalgebras. It can
-be used to derive branching rules. We show that application of
-splint properties drastically simplifies calculations of
+Splint of root system for simple Lie algebra appears naturally in
+studies of (regular) embeddings of reductive subalgebras. Splint can
+be used to construct branching rules. We demonstrate that 
+splint properties implementation drastically simplify calculations of
 branching coefficients.
@@
 
-Splint $\phi$ of a root system $\Delta_1$ into a root system
-$\Delta$ is a bijective map of roots of $\Delta_{1}$ to (proper)
-subset of $\Delta$ which commutes with vector composition law in
+Embedding $\phi$ of a root system $\Delta_1$ into a root system
+$\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
+subset of $\Delta$ that commutes with vector composition law in
 $\Delta_{1}$ and $\Delta$.
@@
 properties except the addition rules equivalent to the addition
-rules in $\Delta_{1}$ (for pre-images). The term {\it splint} was
+rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
+can splinter $\Delta$  when the latter can be presented 
+as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.   
+The term {\it splint} was
 introduced by D. Richter in  \cite{richter2008splints} where the
 classification of splints for simple Lie algebras was obtained.
-There was also mentioned that the notion of splint must have tight
-connections with the injection fan approach. The fan $\Gamma
+There was also mentioned that splint must have tight
+connections with the injection fan construction. The fan $\Gamma
 \subset \Delta$ was
-introduced in \cite{lyakhovsky1996rra} as the subset of root system describing recurrent
-properties of branching coefficients for maximal embeddings  . Injection fan is an
+introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent
+properties of branching coefficients for maximal embeddings. Injection fan is an
 efficient tool to study branching rules. Later this construction
@@
 
-In the present paper we study the connection of splint with
-injection fan for regular embeddings of reductive subalgebras
-${\mathfrak a}\longrightarrow {\mathfrak g}$ of simple Lie algebra $\mathfrak{g}$. We show that (under
+In the present paper we study connections between splint and
+injection fan for regular embedding of reductive subalgebras
+${\mathfrak a}$ in simple Lie algebra $\mathfrak{g}$. We show that (under
 certain conditions described in section \ref{sec:stems and
@@
 with respect to a subalgebra ${\mathfrak a}\longrightarrow
-{\mathfrak g}$. Using this tool we obtain the main result of the
-present paper -- the one-to-one correspondence between weight
+{\mathfrak g}$. Using this tool we obtain the main result -- the one-to-one correspondence between weight
 multiplicities in irreducible modules of splint and branching
@@
 Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
-\mathfrak{a}\longrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
+\mathfrak{a}\hookrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
 is a
@@
 to be a proper regular subalgebra and $\mathfrak{a}$ to be the
-maximal subalgebra with $\mathfrak{a}^S$ fixed that is the rank
+maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed that is the rank
 $r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
 
-We use the following notations:
+The following notations are used:
+
 $r$ , $\left( r_{\mathfrak{a}^{\mathfrak{s}}}\right) $ --- the rank of
@@
 
-$S\quad \left( S_{\frak{a}}\right) $ --- the system of simple roots (of $%
+$S \, ,\quad \left( S_{\frak{a}}\right) $ --- the system of simple roots (of $%
 \frak{g}$ and $\frak{a}$ respectively);
@@
 $\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
-i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{%
+i$-th (resp. $j$-th) simple root for $\frak{g}$  $\left( \mathrm{{resp. \,} \frak{%
 a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
@@
 $\omega _{i}$ , $\left( \omega _{\left( \frak{a}\right) j}\right) $ --- the $%
-i$-th (resp. $j$-th) fundamental weight for $\frak{g}$ $\left( \mathrm{{resp.}\frak{%
+i$-th (resp. $j$-th) fundamental weight for $\frak{g}$ $\left( \mathrm{{resp. \,}\frak{%
 a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
@@
 Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
-we get the relation connecting the singular elements $\Psi ^{\left( \mu
+we get a relation connecting the singular elements $\Psi ^{\left( \mu
 \right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
@@
 where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $%
-\frak{g}$ orthogonal to roots of $\frak{a}$, $W_{\perp}$ is a Weyl group of $\mathfrak{a}_{\perp}$
+\frak{g}$ orthogonal to roots of $\frak{a}$ and $W_{\perp}$ is a Weyl group of $\mathfrak{a}_{\perp}$
 \begin{eqnarray}
@@
 \end{eqnarray}
-and $\pi$ is the projection operator. When the injection is maximal the
+and $\pi$ is the projection operator. When an injection is maximal the
 projection becomes trivial and the relation (\ref{recurrent rel}) is
@@
 \begin{Def}
-Suppose $\Delta _{0}$ and $\Delta $ are root systems with the corresponding
+Suppose $\Delta _{0}$ and $\Delta $ are root systems with corresponding
 weight lattices $P_{0}$ and $P$. Then $\phi $ is an ``embedding'',
@@
 $\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
-\longrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
+\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
 _i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
@@
 
-In \cite{richter2008splints} it was indicated that the injection fan technique used in
-\cite{lyakhovsky1996rra} is close to that of splints.
-
-To demonstrate the relations between these instruments consider the case
-where one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem
-in $\Delta $.
+To study relations between injection fan technique and splint let us 
+consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ 
+is a root subsystem.
 
 Splint $\Delta \approx (\Delta _{1},\Delta _{2})$ is called ''injective'' if
-one of its stems, say $\Delta _{1}=\Delta _{\frak{a}}$ , is a root subsystem
+$\Delta _{1}=\Delta _{\frak{a}}$, is a root subsystem
 in $\Delta $ corresponding to a regular reductive subalgebra $\frak{a}%
@@
 \hookrightarrow \frak{g}}$. Denote by $\Delta_{\mathfrak{s}0}$ the coimage of the second embedding $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\mathfrak{g}}$.
-
-Thus we see that
+The following conjecture follows.
 
@@
 
-In this case we say that the subalgebra $\frak{a}\hookrightarrow \frak{g}$
+In case of injective splint we say that subalgebra $\frak{a}\hookrightarrow \frak{g}$
 splinters $\Delta $ (and call $\frak{a}$ the ''splinting subalgebra'' of $%
@@
 defined by the set of edges $\left\{ \lambda _{i}\right\} _{i=1,\dots ,r}$
-adjusted to the end of the highest weight vector $\mu +\rho $. Let $\mu
-=\sum m_{i}\omega _{i}$ then these edges are
+adjusted to the end of the highest weight vector $\mu +\rho $. For $\mu
+=\sum m_{i}\omega _{i}$ these edges are
 \begin{equation}
-\lambda _{i}=-\left( m_{i}+1\right) \alpha _{i}.\quad i=1,\dots ,r
+\lambda _{i}=-\left( m_{i}+1\right) \alpha _{i},\quad i=1,\dots ,r.
 \label{edge}
@@
 Consider any pair of edges $\lambda _{i},\lambda _{j}$ and the corresponding
-weights $\mu +\rho $, $\mu +\rho +\lambda _{i}$ and $\mu +\rho +\lambda _{j}$%
-. Apply the reflection $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
+weights $\mu +\rho $, $\mu +\rho +\lambda _{i}$ and $\mu +\rho +\lambda _{j}$. 
+Apply the reflection $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
 \begin{equation}
@@
 
-Remember that only the first three types in Richter classification are
-injective splints and thus are naturally connected with branching. Below we
+Remember that only three types of splints are
+injective and thus are naturally connected with branching. Below we
 reproduce the part of the splints table from \cite{richter2008splints} corresponding to
@@
 type splints only $\Delta _{\frak{a}}$ is embedded metrically. The summands $%
-u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$ . This does not change
+u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$. This does not change
 the principle properties of branching but makes it possible to use the
@@
 Splints induce a decomposition of the set $S=S_{\frak{c}}\cup S_{\frak{d}}$
-with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}}$%
-. It is easy to check that for all the injective splints the subset $S_{%
+with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}}$. 
+It is easy to check that for any injective splint the subset $S_{%
 \frak{d}}$ is nonempty. It follows that in the set $\left\{ \lambda
@@
 s_{\alpha _{l}}\left( \mu +\rho -p\beta _{l}\right) =s_{\alpha _{l}}\left(
-\mu +\rho \right) -ps_{\alpha _{l}}\beta _{l}=\mu +\rho -p\beta _{l}
+\mu +\rho \right) -ps_{\alpha _{l}}\beta _{l}=\mu +\rho -p\beta _{l},
 \label{intersection}
@@
 \alpha _{l}=\left( m_{l}+1\right) \beta _{l}-\left( m_{l}+1\right) \beta
-_{k}=p\beta _{l}-ps_{\alpha _{l}}\beta _{l}  \label{intersection-2}
+_{k}=p\beta _{l}-ps_{\alpha _{l}}\beta _{l}.  
+\label{intersection-2}
 \end{equation}
@@
 \mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
-m_{k}\widetilde{\omega }_{k}  \label{new h weight}
+m_{k}\widetilde{\omega }_{k} . \label{new h weight}
 \end{equation}
@@
 }^{\left( \widetilde{\mu }\right) }$  in $P_{\frak{s}}$. It is easily seen
-that its coimage belongs to $\bar{C_{\frak{a}}}$. and that the set $\phi
+that its coimage belongs to $\bar{C_{\frak{a}}}$ and that the set $\phi
 ^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) \setminus \Phi _{%
@@
 
-Now let us return to the relation (\ref{singular main-3}). One can add to $%
-\Phi _{\frak{g}}^{\left( \mu \right) }$ pairs of additional formal elements
+Now let us return to relation (\ref{singular main-3}). One can add to $%
+\Phi _{\frak{g}}^{\left( \mu \right) }$ pairs of formal elements
 constructed above  with the opposite signs: $\epsilon \left( w\right)
-|_{w\in W_{\frak{s}}}$ and $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$%
-. Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ to
-the elements whose weights we shall consider beloning to $\bar{C_{\frak{a}}}$%
-. The same elements with the opposite signs are to be referred to the
-neighbor Weyl chambers of $\bar{C_{\frak{a}}^{(l)}}$ (the latter are
+|_{w\in W_{\frak{s}}}$ and $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$. 
+Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ to
+the elements whose weights we shall attribute to $\bar{C_{\frak{a}}}$. 
+The same elements with the opposite signs are to be referred to the
+neighboring Weyl chambers of $\bar{C_{\frak{a}}^{(l)}}$ (the latter are
 connected with the main one via simple reflections $s_{\alpha _{l}}$ so the
 signes $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ are natural for
-them). In fact one can repeat the procedure of finding additional singular
+them). In fact one can repeat the procedure and find additional singular
 weights in any Weyl chamber $\bar{C_{\frak{a}}^{(m)}}$ and in them
 additional singular weights always have the signs opposite to that in their
-nearest neighbors. Thus without changing in fact the element $\Phi _{\frak{g}%
+nearest neighbors. Thus without changing the element $\Phi _{\frak{g}%
 }^{\left( \mu \right) }$ one can present it as a sum
@@
 the weight diagram $\mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ of the $\frak{%
-s}$-module $L_{\frak{s}}^{\widetilde{\mu }}$. Finally one must restrict
+s}$-module $L_{\frak{s}}^{\widetilde{\mu }}$. Now one can restrict
 relation (\ref{singular main-3}) to $\bar{C_{\frak{a}}}$ and obtain the main
 result:
-
 \begin{Prop}
@@
 \begin{example}
-  Consider Lie algebra $A_{2} (\bf{sl}(3))$ and branching of its irreducible module $L^{(3,2)}$ into the modules of reductive subalgebra $A_{1}\oplus u(1)$ with root system spanned by first simple root of $A_{2}$.
-Singular element of $L^{(3,2)}$ is decomposed into the sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules and branching coefficients coincide with weight multiplicities of $A_{1}\oplus A_{1}$-module (see Fig.
+  Consider the Lie algebra $A_{2} =\bf{sl}(3)$ and branching of its irreducible module $L^{[3,2]}_{A_{2}}$ with respect to the reductive subalgebra $A_{1}\oplus u(1)$.
+The root system  $\Delta _{\frak{a}}= \Delta_{A_{1}\oplus u(1)}$ contains the simple root of $\alpha_1=e_1-e_2$ of $A_{2}$.
+The singular element $\Psi^{[3,2]}_{\frak{a}}$ is decomposed into a sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules.
+Branching coefficients $b_{\nu }^{[ 3,2 ] }$ coincide with weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module (see Fig.
 \ref{fig:a2_splint}).
@@
   \noindent\centering{
-   \includegraphics[width=120mm]{a2-a1}
+   \includegraphics[width=80mm]{a2-a1}
   }
-  \caption{Weyl group orbit (dotted) producing singular element of $A_{2}$-module $L^{(3,2)}$ and its decomposition into the sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules (dashed).
-Weight multiplicities of $A_{1}\oplus A_{1}$-module coincide with branching coefficients for the reduction $L^{(3,2)}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}
+  \caption{Weyl group orbit (dotted) producing singular element of $L^{[3,2]}_{A_{2}}$ and its decomposition into the sum of splint images of singular elements of modules  $L^{[3,2]}_{A_{1}\oplus A_{1}}$ (dashed).
+Weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}
 
@@
 \begin{example}
-  Now consider Lie algebra $B_{2} (\bf{so}(5))$ and branching of its irreducible module $L^{(3,2)}$ into the modules of reductive subalgebra $A_{1}\oplus u(1)$ with root system spanned by first simple root of $B_{2}$.
-Singular element of $L^{(3,2)}$ is decomposed into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide with weight multiplicities of $A_{2}$-module (see Fig.
+  For the Lie algebra $B_{2}= \bf{so}(5)$ branching of its irreducible module $L^{[3,2]}$ into  modules of a reductive subalgebra $A_{1}\oplus u(1)$ with the root system spanned by the first simple root $\alpha_1=e_1-e_2$ of $B_{2}$.
+Singular element of $\Psi^{[3,2]}_{B_{2}}$ is decomposed into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide with weight multiplicities of $A_{2}$-module (see Fig.
 \ref{fig:b2_splint}).
@@
   \begin{figure}[h!bt]
-  \hspace*{-1.5cm}
+  \hspace*{-1.2cm}
 
-   \includegraphics[width=75mm]{b2}
-   \includegraphics[width=75mm]{b2-a2-a1}
-  \caption{$B_{2}$-module $L^{(3,2)}$ is shown on the left.
-Weight multiplicities are indicated.
-Contour of singular element is shown by dotted line.
-Right figure represents the decomposition of  $L^{(3,2)}$-singular element into the sum of splint images of singular elements of $A_{2}$-modules (dashed).
-Weight multiplicities of $A_{2}$-module coincide with branching coefficients for the reduction $L^{(3,2)}_{B_{2}\downarrow A_{1}\oplus u(1)}$.}
+   \includegraphics[width=65mm]{b2}
+   \includegraphics[width=65mm]{b2-a2-a1}
+  \caption{Weights of the $B_{2}$-module $L^{[3,2]}$ are indicated by dots in the left picture (their multiplicities are also indicated).
+Contour of the singular element is shown by dotted line.
+The right picture presents the decomposition of  $\Psi_{B_{2}}(L^{[3,2]}_{B_{2}})$-singular element into the sum of splint images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ (dashed).
+Weight multiplicities of $L^{[3,2]}_{A_{2}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{B_{2}\downarrow A_{1}\oplus u(1)}$.}
 
@@
 \end{example}
+
+\vspace{10mm}
 \begin{example}
-   Lie algebra $G_{2}$ has regular subalgebra $A_{2}$ with root system built on long roots of $G_{2}$.
-Consider branching of its irreducible module $L^{(3,2)}$ into the modules of reductive subalgebra $A_{2}$.
-Singular element of $L^{(3,2)}$ is decomposed into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide with weight multiplicities of $A_{2}$-module (see Fig.
+   Lie algebra $G_{2}$ has a regular subalgebra $A_{2}$ with root system $\Delta_{\mathfrak{a}}=\Delta_{A_{2}}$ containing the $G_{2}$ long roots.
+Consider branching of an irreducible module $L_{G_{2}}^{(3,2)}$ into the $A_{2}$-modules.
+Singular element $\Psi_{G_{2}}(L^{[3,2]})$ is decomposed into the sum of splint images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ and the corresponding branching coefficients coincide with weight multiplicities of $L^{[3,2]}_{A_{2}}$-module (see Fig.
 \ref{fig:g2_splint}).
@@
 
-  \caption{Weyl group orbit (dotted) producing singular element of $G_{2}$-module $L^{(3,2)}$ and its decomposition into the sum of splint images of singular elements of $A_{2}$-modules (dashed).
-Weight multiplicities of $A_{2}$-module coincide with branching coefficients for the reduction $L^{(3,2)}_{G_{2}\downarrow A_{2}}$.}
+  \caption{Weyl group orbit (dotted) for the singular element $\Psi_{G_{2}}(L^{[3,2]})$ and its decomposition into the sum of splint images of singular elements of $A_{2}$-modules (dashed).
+Weight multiplicities of $L^{[3,2]}_{A_{2}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{G_{2}\downarrow A_{2}}$.}
 
@@
 determination of weight multiplicities for a module with the same
-Dynkin labels referred to a different Lie algebra. This algebra
-$\frak{s}$ must not be a subalgebra in the initial $\frak{g}$ , it
-has the same rank $r_{\frak{s}}=r$\ , but as a rule is less
-complicated than $\frak{g}$ .
+Dynkin labels referred to the Lie algebra $\mathfrak{s}$. This algebra
+$\mathfrak{s}$ must not be a subalgebra in the initial $\mathfrak{g}$ , it
+has the same rank $r_{\mathfrak{s}}=r$\ , but obviously less
+"complicated" than $\mathfrak{g}$ -- only a subset of the initial root system is involved in the second stem $\Delta_{\mathfrak{s}}$.
 
@@
 D_{r}\hookrightarrow C_{r}$ and $A_{r-1}\oplus u\left( 1\right) \hookrightarrow A_{r}$ splint technique shows
-immediately Gelfand-Tzeytlin rules for branching: the nonzero
-branching coefficients are equal to 1, the reduction is
-multiplicity free. Here it is an immediate consequence of the
+transparently Gelfand-Tzeytlin rules for branching:  the reduction is
+multiplicity free (all nonzero
+branching coefficients are equal to 1). Here it is an immediate consequence of the
 structure of the second stem being a direct sum of $A_{1}$
@@
 The work was supported in part by the
-RFFI grant N 09-01-00504. The work of A.A.~Nazarov is supported by
+RFFI grant N 09-01-00504. A.A.N. thanks 
 the Chebyshev Laboratory (Department of Mathematics and Mechanics,
-Saint-Petersburg State University) under the grant 11.G34.31.0026
-of the Government of the Russian Federation.
+Saint-Petersburg State University) for support under the grant 11.G34.31.0026
+of the Government of Russian Federation.
 
@@
 algebras the following property is valid:
-
+\begin{Prop}
 Let $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})$ be an
@@
 }$.
-
-Then for any simple root $\beta \in S_{\frak{s}}$ there exists the
+\end{Prop}
+Thus for any simple root $\beta \in S_{\frak{s}}$ there exists the
 pair of
@@
 
+\begin{itemize}
+\item
 Type 1. $\Delta _{G_{2}}\approx (\Delta _{A_{2}},\Delta
@@
 _{G_{2}}^{\left( 0\right) }$ is presented. The boundaries of $\bar{C_{\frak{a%
-}}}$ are the dashed lines starting in the center of the singular
+}}}$ are the dashed lines starting at the center of the singular
 element. It
 contains the edge $\lambda _{2}=-\alpha _{2}=-\beta _{2}$ and the roots $%
--\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3},\; -\beta _{3}$
-($\beta _{3}$ is indicated as $\beta _{l}$). For this root $\beta
+-\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3}$ and $ -\beta _{3}$
+($\beta _{3}$ is indicated as $\beta _{l}$). For the root $\beta
 _{1}$ the necessary pair
@@
 }}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ and $m_{1}$ index
-is aquired by the $\frak{s}$-module that inherit the second
-indice. In this particular
+is aquired by the $\frak{s}$-module that also inherit the second
+index $m_{2}$. In this particular
 case they are $m_{1}=m_{2}=0$. The general case with the initial module $%
-L^{\mu }$ and $\mu =m_{1}\omega _{1}+m_{2}\omega _{2}$.can be
+L^{\mu }$ and $\mu =m_{1}\omega _{1}+m_{2}\omega _{2}$ can be
 treated in the same way: one finds an edge $\lambda _{2}=-\left(
@@
 $s_{\beta
-_{2}} $ sends $\beta _{1}$ to $\beta _{3}$ and the corresponding edge $%
-\lambda _{2,3}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{3}$ has
-the same length. Now consider $\lambda _{1}^{\frak{s}}$ (or
+_{2}} $ sends $\beta _{1}$ to $\beta _{3}$ and the corresponding edge 
+$\lambda _{2,3}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{3}$ has
+the length $\left( m_{1}+1\right) $. Now consider $\lambda _{1}^{\frak{s}}$ (or
 $\lambda _{2,3}^{\frak{s}} $) and $\lambda _{1,3}^{\frak{s}}$ (or
@@
 ) . Finally the edge $\lambda _{1,3,2}^{\frak{s}}=-\left(
-m_{1}+1\right) \beta _{2}$ close the polytope. The latter
-corresponds to the singular
+m_{1}+1\right) \beta _{2}$ closes the polytope. Its vertices
+correspond to weights of the singular
 element $\Phi _{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{%
@@
 far as the stem is metric.
-
+\item
 Type 1. $\Delta _{F_{4}}\approx (\Delta _{D_{4}},\Delta
@@
 
-Both stems are metric and the corresponding root systems are
+Both stems are metric here and the corresponding root systems are
 equivalent. The system $\Delta _{D_{4}}$ of the subalgebra
-$\frak{a=}D_{4}$ is formed by the set $\left\{ \pm e_{i},\pm
+$\frak{a=}D_{4}$ is formed by the set $\left\{ \pm e_{i}\pm
 e_{j}\right\} _{|i,j=1,\ldots 4,\; i\neq j}.$ The simple roots
@@
 e_{1}-e_{2}-e_{3}-e_{4}\right) \right\} $.
-
 For a module $L^{\mu }$ with $\mu =\sum m_{k}\omega _{k}$ consider the edge $%
 \lambda _{3}=-\left( m_{3}+1\right) e_{4}=-\left( m_{3}+1\right)
-\beta _{3}$
-\ Compose an edge $\lambda _{2}^{\frak{s}}=-\left( \widetilde{m}%
-_{2}+1\right) \beta _{2}$ . Now the necessary pair is $\left(
+\beta _{3}$.
+ Compose an edge $\lambda _{2}^{\frak{s}}=-\left( \widetilde{m}%
+_{2}+1\right) \beta _{2}$. The necessary pair of roots is $\left(
 \alpha
@@
 }=-\left( m_{2}+1\right) \beta _{2}$ and the pair $\left( \alpha
-_{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $ \ The length of the
-edge $\lambda _{1}^{\frak{s}}$ becomes equal to $\lambda
-_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$ and so on. The
-edges along the roots like $\alpha _{4}=\beta
-_{4}=\frac{1}{2}\left( e_{1}-e_{2}-e_{3}-e_{4}\right) $ are
+_{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $. The length of  
+$\lambda _{1}^{\frak{s}}$ becomes equal to $\lambda
+_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$. Proceed further till the closure of the polytope. 
+The edges looking along the roots of the $\alpha_4$-type, $\alpha _{4}=\beta
+_{4}=$ $\frac{1}{2}\left( e_{1}-e_{2}-e_{3}-e_{4}\right) $, are
 treated similarly and finally the singular element $\Phi
@@
 W_{\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
-\widetilde{\mu }+\rho _{\frak{s}}\right) }$ of the module
+\widetilde{\mu }+\rho _{\frak{s}}\right) }$ for the module
 $L_{\frak{s}}^{\left( \widetilde{\mu }\right) }$ with
@@
 $\bar{C_{\frak{a}}}$.
-
+\item
 Type 2. $\Delta _{B_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
@@
 
-Both stems are metric. The injection is fixed by the stem $\Delta
-_{D_{r}}$ with simple roots $S_{\frak{a}}=\left\{
+Both stems are metric. An injection is fixed by the stem $\Delta
+_{D_{r}}$ simple roots $S_{\frak{a}}=\left\{
 e_{1}-e_{2},e_{2}-e_{3},\ldots
@@
 corresponds to a
-direct sum of algebras $A_{1}$ and has the simple roots $S_{\frak{s}%
+direct sum of algebras $A_{1}$ with the simple roots $S_{\frak{s}%
 }=\left\{ e_{1},e_{2},\ldots ,e_{r-1},e_{r}\right\} $. Consider the edge $%
@@
 attached to it (here $\beta _{r-1}=e_{r-1}$). The corresponding pair is $%
-\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta _{r-1}=e_{r-1}\right) $
-.\ The intersection condition fixes the second edge to be $\lambda
+\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta _{r-1}=e_{r-1}\right) $.
+ The intersection condition fixes the second edge to be $\lambda
 _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ , it is orthogonal
@@
 _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$ to
-obtain the index $\widetilde{m}_{r-2}=m_{r-2}$ and the edge
+fix the index $\widetilde{m}_{r-2}=m_{r-2}$ and the edge
 $\lambda _{r-2}=-\left( m_{r-2}+1\right) \beta _{r-2}$ and so on
@@
 
+\item
 Type 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
@@
 the additional edges are constructed similarly.
-
+\item
 Type 3 $\Delta _{A_{r}}\approx (\Delta _{A_{r-1}\oplus
@@
 simple roots $S_{\frak{a}}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots
-,e_{r-1}-e_{r}\right\} $ . The second stem corresponding to a direct sum of $%
+,e_{r-1}-e_{r}\right\} $. The second stem corresponding to a direct sum of $%
 r$ copies of $A_{1}$ has the simple roots $S_{\frak{s}}=\left\{
@@
 _{r-1}+1\right) \beta _{r-1}$ \ with $\beta
-_{r-1}=e_{r-1}-e_{r+1}$ attached to it . Then the corresponding
+_{r-1}=e_{r-1}-e_{r+1}$ attached to it. Then the corresponding
 pair is $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta
-_{r-1}=e_{r-1}-e_{r+1}\right).$ The intersection with the
+_{r-1}=e_{r-1}-e_{r+1}\right)$. The intersection with the
 boundary of $\bar{C}_{A_{r-1}}$ orthogonal to $\alpha _{r-1}$
@@
 _{A_{1}\oplus A_{1}})$ is presented in Example 4.1 and Figure 1.
-
+\item
 Type 3 $\Delta _{B_{2}}\approx (\Delta _{A_{1}},\Delta _{A_{2}}).$
 
-The necessary elements are presented in Example 4.1 and Figure 1 , $%
-S_{A\_1}=\left\{ e_{1}-e_{2}\right\} $ , $S_{A\_2}=\left\{
-e_{1},e_{2}\right\} $.The edge $\lambda _{\alpha _{2}}=\lambda
-_{\beta _{2}}=-\left( m_{2}+1\right) \beta _{2}$ has an edge
+This splint is illustrated in Example 4.1 and Figure 1, 
+$S_{A\_1}=\left\{ e_{1}-e_{2}\right\} $, $S_{A\_2}=\left\{
+e_{1},e_{2}\right\} $. The edge $\lambda _{\alpha _{2}}=\lambda
+_{\beta _{2}}=-\left( m_{2}+1\right) \beta _{2}$ is followed by
 $\lambda _{\beta _{1}}=-\left( \widetilde{m}_{1}+1\right) \beta
-_{1}$ attached to it. Consider the pair $\left( \alpha
-_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right).$ The end of the edge
-$\lambda _{\beta _{1}}$ is to define a weight
-invariant under the reflexion $s_{\alpha _{1}}.$ This defines its length: $%
-\lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$ . In the
+_{1}$. Consider the pair $\left( \alpha
+_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right)$. The end of the edge
+$\lambda _{\beta _{1}}$ must indicate a weight
+invariant under the reflexion $s_{\alpha _{1}}$.  Its length is thus fixed: 
+$\lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$. In the
 coimage of
-the second stem, that is in the $A_{2}$ root system, the reflection $%
-s_{\beta _{2}}$ sends $\lambda _{\beta _{1}}=-\left(
+the second stem, that is in the root system $\Delta_{A_{2}}$, the reflection 
+$s_{\beta _{2}}$ sends $\lambda _{\beta _{1}}=-\left(
 m_{1}+1\right) \beta
@@
 $A_{1}\oplus u\left( 1\right) $ and the
-corresponding highest weights with their multiplicities form the diagram $%
-\mathcal{N}_{A\_2}^{\left[ 3,2\right] }$ .
+corresponding highest weights (with their multiplicities) form the diagram $%
+\mathcal{N}_{A_2}^{\left[ 3,2\right] }$ .
+\end{itemize}
 

### 2011-12-02 AffineLieAlgebras/Thesis/3.tex
Translation of chapter 4 started

@@
 
-\begin{abstract}
-Splint of root system for simple Lie algebra appears naturally in
-studies of (regular) embeddings of reductive subalgebras. Splint can
-be used to construct branching rules. We demonstrate that 
-splint properties implementation drastically simplify calculations of
-branching coefficients.
-\end{abstract}
+Сплинт корневой системы простой алгебры Ли возникает при изучении регулярных вложений редуктивных подалгебр.
+Сплинт можно использовать для получения правил ветвления.
+Мы показываем, что использование свойств сплинта  позволяет сильно упростить вычисление коэффициентов ветвления.
 
-\section{Introduction}
+\section{Введение}
 \label{sec:Introduction}
 
-Embedding $\phi$ of a root system $\Delta_1$ into a root system
-$\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
-subset of $\Delta$ that commutes with vector composition law in
-$\Delta_{1}$ and $\Delta$.
+Вложение  $\phi$ корневой системы $\Delta_1$ в корневую систему $\Delta$ -- это биективное отображение корней из $\Delta_{1}$ в (собственное) подмножество $\Delta$, коммутирующее с законом сложения векторов в $\Delta_{1}$ и $\Delta$.
+
 \begin{equation*}
@@
 
-Note that the image $Im(\phi)$ must not inherit the root system
-properties except the addition rules equivalent to the addition
-rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
-can splinter $\Delta$  when the latter can be presented 
-as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.   
-The term {\it splint} was
-introduced by D. Richter in  \cite{richter2008splints} where the
-classification of splints for simple Lie algebras was obtained.
-There was also mentioned that splint must have tight
-connections with the injection fan construction. The fan $\Gamma
-\subset \Delta$ was
-introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent
-properties of branching coefficients for maximal embeddings. Injection fan is an
-efficient tool to study branching rules. Later this construction
-was generalized to non-maximal embeddings and infinite-dimensional
-Lie algebras in \cite{2010arXiv1007.0318L, ilyin812pbc}.
+Заметим, что образ  $Im(\phi)$ не обязан обладать свойствами корневой системы за исключением правил сложения, эквивалентных правилам сложения в  $\Delta_{1}$ (для прообразов).
+Два вложения  $\phi_1$ и $\phi_2$  {\it расщепляют} корневую систему  $\Delta$ если она может быть представлена, как несвязное объединение образов $Im(\phi_1)$ и $Im(\phi_2)$.
+Термин {\it сплинт} (расщепление) предложил D.
+Richter в работе  \cite{richter2008splints}, где  были получены все сплинты для простых алгебр Ли.
+В работе так же упоминалось, что сплинт должен быть тесно связан с конструкцией веера вложения.
+Веер вложения  $\Gamma\subset \Delta$ был введен в работе  \cite{lyakhovsky1996rra} как подмножество корневой системы, описывающее рекуррентные свойства коэффициентов ветвления для максимальных вложений.
+Веер вложения -- это эффективный инструмент для изучения правил ветвления.
+Позднее в работах \cite{2010arXiv1007.0318L, ilyin812pbc} эта конструкция была обобщена на не-максимальные вложения и бесконечномерные алгебры Ли.
 
-In the present paper we study connections between splint and
-injection fan for regular embedding of reductive subalgebras
-${\mathfrak a}$ in simple Lie algebra $\mathfrak{g}$. We show that (under
-certain conditions described in section \ref{sec:stems and
-multiplicity functions}) splint is a natural tool to study
-reduction properties of ${\mathfrak g}$-modules
-with respect to a subalgebra ${\mathfrak a}\longrightarrow
-{\mathfrak g}$. Using this tool we obtain the main result -- the one-to-one correspondence between weight
-multiplicities in irreducible modules of splint and branching
-coefficients for a reduced module $L^{\mu}_{{\mathfrak
-g}\downarrow {\mathfrak a}}$.
+В данной главе мы изучаем связь между сплинтом и веером вложения для регулярных вложений редуктивных подалгебр ${\mathfrak a}$ в простую алгебру Ли $\mathfrak{g}$.
+Мы демонстрируем, что (при выполнении определенных условий, описанных в разделе \ref{sec:stems and multiplicity functions}) сплинт является естественным инструментом для изучения свойств редукции  $\gf$-модулей по отношению к подалгебре $\af\longrightarrow\gf$.
+Используя этот инструмент мы получаем основной результат данной главы -- однозначное соответствие между кратностями весов неприводимых модулей сплинта и коэффициентов ветвления для редуцированного модуля $L^{\mu}_{\gf\downarrow \af}$
 
-\section{Injections and splints}
+\section{Вложения и сплинты}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%
+%% End of file
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "thesis"
+%%% End:

### 2011-12-03 AffineLieAlgebras/Thesis/3.tex
Work on translation of chapter 3.

@@
 
-В данной главе мы изучаем связь между сплинтом и веером вложения для регулярных вложений редуктивных подалгебр ${\mathfrak a}$ в простую алгебру Ли $\mathfrak{g}$.
+В данной главе мы изучаем связь между сплинтом и веером вложения для регулярных вложений редуктивных подалгебр ${\mathfrak a}$ в простую алгебру Ли $\gf$.
 Мы демонстрируем, что (при выполнении определенных условий, описанных в разделе \ref{sec:stems and multiplicity functions}) сплинт является естественным инструментом для изучения свойств редукции  $\gf$-модулей по отношению к подалгебре $\af\longrightarrow\gf$.
@@
 
-Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
-\mathfrak{a}\hookrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
-is a
-reductive subalgebra $\mathfrak{a \subset g}$ with correlated root spaces: $%
-\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset \mathfrak{h}_{\mathfrak{g }%
-}^{\ast }$. Let $\mathfrak{a}^{\mathfrak{s}}$ be a semisimple summand of
-$\mathfrak{a}$,
-this means that $\mathfrak{a}=\mathfrak{a}^{\mathfrak{s}} \oplus \mathfrak{u}(1)\oplus %
-\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^{\mathfrak{s}}$
-to be a proper regular subalgebra and $\mathfrak{a}$ to be the
-maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed that is the rank
-$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
+Рассмотрим простую алгебру Ли $\gf$ и ее  регулярную подалгебру $\af \hookrightarrow \gf$, такую, что $\af$ -- редуктивную подалгебра $\af\subset \gf$ и корневые системы согласованы $\hf_{\af}^{\ast}\subset\hf_{\gf}^{\ast}$.
+Пусть $\af^{\mathfrak{s}}$ -- полупростое слагаемое в $\mathfrak{a}$, то есть  $\af=\af^{\mathfrak{s}} \oplus \uf(1)\oplus \uf(1)\oplus \dots$.
+Мы будем считать, что $\af^{\mathfrak{s}}$ -- собственная регулярная подалгебра и что $\af$ -- максимальная подалгебра с заданной  $\af^{\mathfrak{s}}$, то есть ранг $r$ подалгебры $\af$ равен рангу $\gf$.
 
-The following notations are used:
-
-$r$ , $\left( r_{\mathfrak{a}^{\mathfrak{s}}}\right) $ --- the rank of
-$\frak{g}$ $\left( \mathrm{{resp. }\mathfrak{a}^{\mathfrak{s}}}\right) $ ;
-
-$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system;
-$\Delta ^{+} $ $\left( \mathrm{{resp. }\Delta
-_{\frak{a}}^{+}}\right) $--- the positive root system (of
-$\frak{g}$ and $\frak{a}$ respectively);
-
-$S \, ,\quad \left( S_{\frak{a}}\right) $ --- the system of simple roots (of $%
-\frak{g}$ and $\frak{a}$ respectively);
-
-$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
-i$-th (resp. $j$-th) simple root for $\frak{g}$  $\left( \mathrm{{resp. \,} \frak{%
-a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
-^S}\right) $;
-
-$\omega _{i}$ , $\left( \omega _{\left( \frak{a}\right) j}\right) $ --- the $%
-i$-th (resp. $j$-th) fundamental weight for $\frak{g}$ $\left( \mathrm{{resp. \,}\frak{%
-a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
-^S}\right) $;
-
-$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;
-
-$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;
-
-$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
-fundamental Weyl chamber;
-
-$\epsilon \left( w\right) :=\left( -1\right) ^{\mathrm{length}(w)}$;
-
-$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;
-
-$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
-of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
--module with the highest weight $\nu $ );
-
-$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
-the weight diagram of $L^{\mu }$ (resp. ${}L_{\frak{a}}^{\nu }$ );
-
-$P$ (resp. $P_{\frak{a}} $) \ --- the weight lattice;
-
-$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight lattice;
-
-$\mathcal{E}$ (resp. $\mathcal{E}_{\frak{a}} $) \ --- the formal algebra;
-
-$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
-}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
-resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
-L_{\frak{a}}^{\nu } $);
-
-$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\frak{a}}^{\nu
-}\right) $)--- the formal character of $L^{\mu }$ (resp. $L_{\frak{a}}^{\nu
-} $);
-
-$ch\left( L^{\mu }\right)  =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
-+\rho )-\rho }} {\prod_{\alpha \in \Delta ^{+}} \left( 1-e^{-\alpha }\right)
-} $ --- the Weyl formula;
-
-$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) \quad $
-(resp. $R_{\frak{a}}: =\prod_{\alpha \in \Delta_{\frak{a}}^{+}} \left(
-1-e^{-\alpha }\right) $ ) --- the Weyl denominator.
-
-Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
+Пусть $L^{\mu }$ -- вполне приводимый по отношению к  $\af$ модуль алгебры $\gf$,
 \[
-L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
-}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
+L_{\gf\downarrow \af}^{\mu }=\bigoplus\limits_{\nu \in P_{\af%
+}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
 \]
 \begin{equation}
-\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
-}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
+\pi _{\af}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\af%
+}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\af}^{\nu }\right) .
 \label{branching1}
 \end{equation}
-For the modules we are interested in the Weyl formula for $\mathrm{ch}\left(
-L^{\mu }\right) $ can be written in terms of singular elements \cite
-{humphreys1997introduction}
+Для модулей, которые мы исследуем, формула Вейля для характеров $\mathrm{ch}\left(L^{\mu }\right) $ может быть записана через сингулярные элементы \cite{humphreys1997introduction}
 \[
@@
 \]
-namely,
+а именно,
 \begin{equation}
@@
 \end{equation}
-The same is true for submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
-}\right) $ in (\ref{branching1})
+Это же верно и для подмодулей $\mathrm{ch}\left( L_{\af}^{\nu}\right) $ в уравнении (\ref{branching1})
 \[
-\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
-\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
-}^{\left( \nu \right) }}{R_{\frak{a}}},
+\mathrm{ch}\left( L_{\af}^{\nu }\right) =\frac{\Psi _{\af}^{\left(
+\nu \right) }}{\Psi _{\af}^{\left( 0\right) }}=\frac{\Psi _{\af%
+}^{\left( \nu \right) }}{R_{\af}},
 \]
-with
+где
 \[
-\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
-}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
+\Psi _{\af}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\af%
+}}\epsilon (w)e^{w(\nu +\rho _{_{\af}})-\rho _{_{\af}}}.
 \]
 
-Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
-we get a relation connecting the singular elements $\Psi ^{\left( \mu
-\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
+Применяя формулу (\ref{Weyl-Kac2}) к правилам ветвления (\ref{branching1}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu\right) }$ и $\Psi _{\af}^{\left( \nu \right) }$ :
 \begin{eqnarray}
 \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho )-\rho }}{\prod_{\alpha \in
-\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
-}^{(\mu )}\frac{\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{%
-\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
+\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu
+}^{(\mu )}\frac{\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{%
+\af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
 }^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:4} \\
-\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\frak{a}%
-}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}}^{\left( \nu \right) }}{R_{%
-\frak{a}}}.  \label{singular main}
+\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\af%
+}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\af}^{\left( \nu \right) }}{R_{%
+\af}}.  \label{singular main}
 \end{eqnarray}
 
-In \cite{2010arXiv1007.0318L} it was proven that branching coefficients $%
-b_{\xi }^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
-\hookrightarrow \frak{g}$ are subject to the set of recurrent relations:
+В работе \cite{2010arXiv1007.0318L} (см.
+главу \ref{cha:affine-lie-algebras}) было доказано, что коэффициенты ветвления $b_{\xi }^{\left(\mu\right)}$, отвечающие вложению $\af\hookrightarrow \gf$, удовлетворяют следующим рекуррентным соотношениям:
 \begin{equation}
@@
 b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+\sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\af_{\perp }}^{\mu _{\af%
 _{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
-\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right. \\
-\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
+\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right. \\
+\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
 }}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
-}\right) .
+}\right) ,
 \end{array}
@@
 \end{equation}
-where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $%
-\frak{g}$ orthogonal to roots of $\frak{a}$ and $W_{\perp}$ is a Weyl group of $\mathfrak{a}_{\perp}$
+где $\afb$ -- подалгбера, задающаяся корнями  $\gf$, ортогональными ко всем корням $\af$ и $W_{\perp}$ -- подгруппа Вейля, соответствующая $\afb$,
 \begin{eqnarray}
-\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
-h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
+\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
+h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
 \label{delta a ort}
@@
 \begin{eqnarray}
-\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
-\qquad \widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }
+\widetilde{\af_{\perp }} :=\af_{\perp }\oplus \frak{h}_{\perp }
+\qquad \widetilde{\af} :=\af\oplus \frak{h}_{\perp }
 \end{eqnarray}
-and $\pi$ is the projection operator. When an injection is maximal the
-projection becomes trivial and the relation (\ref{recurrent rel}) is
-simplified:
+и $\pi$ -- оператор проекции. Если вложение максимально, то оператор проекции становится тривиальным и соотношение (\ref{recurrent rel}) упрощается:
 \begin{equation}
@@
 }+\right. \\
-\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
+\left. +\sum_{\gamma \in \Gamma _{\af\rightarrow \gf}}s\left(
 \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
@@
 \end{equation}
-The recursion is goverened by the set $\Gamma _{\frak{a}\rightarrow \frak{g}}
-$ called the injection fan. The latter is defined by the carrier set $%
-\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the coefficient
-function $s(\xi )$
+Рекурсия задается множеством  $\Gamma _{\af\rightarrow \gf}$, называющимся ``веер вложения''.
+Оно определяется как носитель $\left\{ \xi \right\} _{\af\rightarrow \gf}$ для коэффициентоной функции $s(\xi )$
 \[
-\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{ \xi \in P_{%
-\frak{a}}|s(\xi )\neq 0\right\}
+\left\{ \xi \right\} _{\af\rightarrow \gf}:=\left\{ \xi \in P_{%
+\af}|s(\xi )\neq 0\right\}
 \]
-appearing in the expansion
+возникающей в разложении
 \begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\frak{a}}^{+}}\left( 1-e^{
--\alpha }\right) =-\sum_{\gamma \in P_{\frak{a}}}s(\gamma )e^{-\gamma };\quad
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\af}^{+}}\left( 1-e^{
+-\alpha }\right) =-\sum_{\gamma \in P_{\af}}s(\gamma )e^{-\gamma };\quad
 \label{product}
@@
 
-Now we remind two definitions introduced in \cite{richter2008splints}
+Теперь мы приведем два определения, введенные в работе \cite{richter2008splints}
 
 \begin{Def}
-Suppose $\Delta _{0}$ and $\Delta $ are root systems with corresponding
-weight lattices $P_{0}$ and $P$. Then $\phi $ is an ``embedding'',
+Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$. Тогда отображение $\phi $ -- ``вложение''
 \begin{equation}
@@
 \end{equation}
-if \newline
-\noindent (a) it injects $\Delta _{0}$ in $\Delta $, and \newline
-\noindent (b) acts homomorphically with respect to the vector groups in $%
-P_{0}$ and $P$:
+если \newline
+\noindent (a) оно вкладывает $\Delta _{0}$ в $\Delta $, и \newline
+\noindent (b) $\phi$ действует гомоморфно по отношению к группам сложения векторов в $P_{0}$ и $P$:
 \[
@@
 \]
-for any triple $\alpha ,\beta ,\gamma \in P_{0}$ such that $\gamma =\alpha
-+\beta $.
+для любой тройки $\alpha ,\beta ,\gamma \in P_{0}$, такой, что $\gamma =\alpha+\beta $.
 \end{Def}
 
-$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
-\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
-_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
-\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+$\phi$ индуцирует вложение формальных алгебр: ${\mathcal{E}}_0\hookrightarrow \mathcal{E}$ и для образа ${\mathcal{E}}_i=\mathrm{Im}_{\phi}\left( {\mathcal{E}}_0\right)$ можно рассмотреть обратное отображение $\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
 
-Notice that one must distinguish two classes of embeddings: when the scalar
-product (defined by the Killing form) in the root space $P_0$ is invariant
-with respect to $\phi$ and when it is not $\phi$-invariant. The first
-embedding is called "metric" , the second -- "nonmetric".
+Заметим, что нужно различать два класса вложений: когда скалярное произведение (заданное формой Киллинга) в корневом пространстве $P_0$ инвариантно по отношению к  $\phi$ и когда оно не  $\phi$-инвариантно.
+Вложения первого класса называются ``метрическими'', второго -- ``неметрическими''.
 
 \begin{Def}
-A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if
-there are two embeddings $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
-\phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the
-disjoint union of the images of $\phi _{1}$ and $\phi _{2}$ and (b) neither
-the rank of $\Delta _{1}$ nor the rank of $\Delta _{2}$ exceeds the rank of $%
-\Delta $.
+Корневая система $\Delta$ ``расщепляется'' на  $(\Delta _{1},\Delta _{2})$, если существует два вложения  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ и $\phi _{2}:\Delta _{2}\hookrightarrow \Delta $, где (a) $\Delta $ -- несвязное объединение образов $\phi _{1}$ и $\phi _{2}$, и (b) ни ранг  $\Delta _{1}$, ни ранг  $\Delta _{2}$ не превосходит ранга $\Delta $.
 \end{Def}
 
-It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$
-and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$. Each
-component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $%
-(\Delta_1,\Delta_2)$.
+Эквивалентно, можно сказать, что  $(\Delta_1,\Delta_2)$  -- ``сплинт'' (расщепление)  $\Delta$ и мы можем обозначить его через $\Delta \approx (\Delta_1,\Delta_2)$.
+Каждая из компонент  $\Delta_1$ и $\Delta_2$ называется ``стеблем'' сплинта $(\Delta_1,\Delta_2)$.
 
 To study relations between injection fan technique and splint let us 
-consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ 
+consider the case when one of the stems $\Delta _{1}=\Delta _{\af}$ 
 is a root subsystem.
@@
 Splint $\Delta \approx (\Delta _{1},\Delta _{2})$ is called ''injective'' if
-$\Delta _{1}=\Delta _{\frak{a}}$, is a root subsystem
-in $\Delta $ corresponding to a regular reductive subalgebra $\frak{a}%
-\hookrightarrow \frak{g}$.
+$\Delta _{1}=\Delta _{\af}$, is a root subsystem
+in $\Delta $ corresponding to a regular reductive subalgebra $\af%
+\hookrightarrow \gf$.
 
 In case of injective splint the second stem $\Delta _{\frak{s}}:=\Delta
-_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product (%
-\ref{product}) and it defines an injection fan $\Gamma _{\frak{a}%
-\hookrightarrow \frak{g}}$. Denote by $\Delta_{\mathfrak{s}0}$ the coimage of the second embedding $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\mathfrak{g}}$.
+_{2}=\Delta \setminus \Delta _{\af}$ can be translated into a product (%
+\ref{product}) and it defines an injection fan $\Gamma _{\af%
+\hookrightarrow \gf}$. Denote by $\Delta_{\mathfrak{s}0}$ the coimage of the second embedding $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$.
 The following conjecture follows.
@@
 \begin{Cnj}
-Each injective splint $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
-$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\frak{a}%
-\rightarrow \frak{g}}$ fixed by the product
+Each injective splint $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})
+$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\af%
+\rightarrow \gf}$ fixed by the product
 \begin{equation}
@@
 
-In case of injective splint we say that subalgebra $\frak{a}\hookrightarrow \frak{g}$
-splinters $\Delta $ (and call $\frak{a}$ the ''splinting subalgebra'' of $%
-\frak{g}$). In \cite{richter2008splints} splints are classified (see Appendix there)
+In case of injective splint we say that subalgebra $\af\hookrightarrow \gf$
+splinters $\Delta $ (and call $\af$ the ''splinting subalgebra'' of $%
+\gf$). In \cite{richter2008splints} splints are classified (see Appendix there)
 and the first three types of them are injective.
@@
 
-In this Section we study properties of injective splints  $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
+In this Section we study properties of injective splints  $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})
 $. It will
 be demonstrated that in this case to find branching
-coefficients for a splinting injection $\frak{a}\hookrightarrow
-\frak{g}$ means to find weight multiplicities of an irreducible
+coefficients for a splinting injection $\af\hookrightarrow
+\gf$ means to find weight multiplicities of an irreducible
 $\frak{s}$-module $L_{\frak{s}}^{\nu }$ with fixed highest weight
 $\nu $. Notice that $\frak{s}$ must not be a subalgebra of
-$\frak{g}$.
+$\gf$.
 
 Let us return to relation (\ref{singular main}) and multiply both sides by $%
-R_{\frak{a}}$:
+R_{\af}$:
 \begin{equation}
 \frac{1}{\prod_{\beta \in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })}\Psi _{%
-\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
-}^{(\mu )}\Psi _{\frak{a}}^{\left( \nu \right) }.
+\gf}^{\left( \mu \right) }=\sum_{\nu \in P_{\af}^{+}}b_{\nu
+}^{(\mu )}\Psi _{\af}^{\left( \nu \right) }.
 \label{singular main-2}
@@
 Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{%
-\frak{a}\rightarrow \frak{g}}$. Consider the highest weight module $L_{\frak{%
+\af\rightarrow \gf}$. Consider the highest weight module $L_{\frak{%
 s}}^{\nu }$. The embedding $\phi :\Delta _{\frak{s}\,0}\longrightarrow \Delta
-_{\frak{g}}$ sends the singular element $\Psi _{\frak{s}}^{\left( \nu
-\right) }$ into $\Psi _{\frak{g}}^{\left( \mu \right) }$. Applying the
+_{\gf}$ sends the singular element $\Psi _{\frak{s}}^{\left( \nu
+\right) }$ into $\Psi _{\gf}^{\left( \mu \right) }$. Applying the
 inverse morphism $\phi ^{-1}$ to the product $\left( \prod_{\beta \in \Delta
@@
 \end{equation}
-Our task is to prove that the singular element $\Psi _{\frak{g}}^{\left( \mu
+Our task is to prove that the singular element $\Psi _{\gf}^{\left( \mu
 \right) }$ contains the element $\Psi _{\frak{s}}^{\left( \xi \right) }$ for
-a module $L_{\frak{s}}^{\xi }$ uniquely defined by $L_{\frak{g}}^{\mu }$ and
+a module $L_{\frak{s}}^{\xi }$ uniquely defined by $L_{\gf}^{\mu }$ and
 that the branching coefficients $b_{\nu }^{(\mu )}$ in the r.h.s. of (\ref
@@
 
-For a highest weight irreducible module $L_{\frak{g}}^{\mu }$ the singular
-element $\Psi _{\frak{g}}^{\left( \mu \right) }$ is an element of $\mathcal{E%
+For a highest weight irreducible module $L_{\gf}^{\mu }$ the singular
+element $\Psi _{\gf}^{\left( \mu \right) }$ is an element of $\mathcal{E%
 }$ corresponding to the shifted Weyl-orbit of the weight $\left( \mu +\rho
@@
 \begin{equation}
-\frac{e^{\rho _{\frak{g}}-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{%
-s}}^{+}}(1-e^{-\beta })}\Phi _{\frak{g}}^{\left( \mu \right) }=\sum_{\nu \in
-P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\Phi _{\frak{a}}^{\left( \nu \right) }.
+\frac{e^{\rho _{\gf}-\rho _{\af}}}{\prod_{\beta \in \Delta _{\frak{%
+s}}^{+}}(1-e^{-\beta })}\Phi _{\gf}^{\left( \mu \right) }=\sum_{\nu \in
+P_{\af}^{+}}b_{\nu }^{(\mu )}\Phi _{\af}^{\left( \nu \right) }.
 \label{singular main-3}
 \end{equation}
-The orbit related to $\Phi _{\frak{g}}^{\left( \mu \right) }$ is completely
+The orbit related to $\Phi _{\gf}^{\left( \mu \right) }$ is completely
 defined by the set of edges $\left\{ \lambda _{i}\right\} _{i=1,\dots ,r}$
@@
 \end{equation}
-Each formal exponent $e^{\mu +\rho +\lambda _{i}}$ in $\Phi _{\frak{g}%
+Each formal exponent $e^{\mu +\rho +\lambda _{i}}$ in $\Phi _{\gf%
 }^{\left( \mu \right) }$ bears the sign coefficient $\epsilon =(-)$. The
-defining property of $\Phi _{\frak{g}}^{\left( \mu \right) }$ is as follows.
+defining property of $\Phi _{\gf}^{\left( \mu \right) }$ is as follows.
 Consider any pair of edges $\lambda _{i},\lambda _{j}$ and the corresponding
@@
 \begin{Prop}
-The edge $\lambda _{i,j}$ of $\Phi _{\frak{g}}^{\left( \mu \right) }$
+The edge $\lambda _{i,j}$ of $\Phi _{\gf}^{\left( \mu \right) }$
 starting at the weight $\left( \mu +\rho +\lambda _{i}\right) $ along the
@@
 
-In $\Phi _{\frak{g}}^{\left( \mu \right) }$ the elements $e^{\left( \mu
+In $\Phi _{\gf}^{\left( \mu \right) }$ the elements $e^{\left( \mu
 +\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha _{j}\right) }$ and $%
@@
 \hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
-_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
+_{\af}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
 \\ \hline\hline
@@
 \]
-Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\frak{s}})
+Each row in the table gives a splint $(\Delta _{\af},\Delta _{\frak{s}})
 $ of the simple root system $\Delta $. In the first two types both $\Delta _{%
-\frak{a}}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
+\af}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
 first type splints are equivalent and in the second are not. In the third
-type splints only $\Delta _{\frak{a}}$ is embedded metrically. The summands $%
-u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$. This does not change
+type splints only $\Delta _{\af}$ is embedded metrically. The summands $%
+u\left( 1\right) $ are added to keep $r_{\af}=r$. This does not change
 the principle properties of branching but makes it possible to use the
@@
 Splints induce a decomposition of the set $S=S_{\frak{c}}\cup S_{\frak{d}}$
-with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}}$. 
+with $S_{\frak{c}}=S\cap S_{\af}$ and $S_{\frak{d}}=S\cap S_{\frak{s}}$. 
 It is easy to check that for any injective splint the subset $S_{%
@@
 _{k}\in \Delta _{\frak{s}}$ and that the orbit corresponding to $\Phi _{%
-\frak{g}}^{\left( \mu \right) }$ contains the edges
+\gf}^{\left( \mu \right) }$ contains the edges
 \begin{equation}
@@
 \end{equation}
-attached to the weight $\mu +\rho $. As far as $\Delta _{\frak{a}}$ is a
+attached to the weight $\mu +\rho $. As far as $\Delta _{\af}$ is a
 root system and for any pair of simple roots from $S_{\frak{c}}$ the
-property \ref{diagram property} is fulfilled, the element $\Phi _{\frak{g}%
-}^{\left( \mu \right) }$ being a singular element for a set of $\frak{a}$%
+property \ref{diagram property} is fulfilled, the element $\Phi _{\gf%
+}^{\left( \mu \right) }$ being a singular element for a set of $\af$%
 -modules. Consider $\beta _{l}\in \Delta _{\frak{s}}$ whose coimage in $%
@@
 corresponding edge intersects the boundary plane of the fundamental chamber $%
-\bar{C_{\frak{a}}}$ orthogonal to the root $\alpha _{l}$,
+\bar{C_{\af}}$ orthogonal to the root $\alpha _{l}$,
 \begin{equation}
@@
 in $\frak{s}$. The latter means that to ''find'' a singular element of $%
-\frak{s}$-module in $\Phi _{\frak{g}}^{\left( \mu \right) }$ it is necessary
+\frak{s}$-module in $\Phi _{\gf}^{\left( \mu \right) }$ it is necessary
 to incorporate in it additional formal elements $\left\{ -e^{\mu +\rho
@@
 }^{\left( \widetilde{\mu }\right) }$  in $P_{\frak{s}}$. It is easily seen
-that its coimage belongs to $\bar{C_{\frak{a}}}$ and that the set $\phi
+that its coimage belongs to $\bar{C_{\af}}$ and that the set $\phi
 ^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) \setminus \Phi _{%
-\frak{g}}^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ corresponds to the
-weights belonging to the boundary $\bar{C_{\frak{a}}}$ (including the subset
+\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ corresponds to the
+weights belonging to the boundary $\bar{C_{\af}}$ (including the subset
 $\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{%
 \frak{c}}\right\} $). Thus we have constructed all the formal elements\ with
-the appropriate sign factors that after being added to $\Phi _{\frak{g}%
-}^{\left( \mu \right) }|_{\bar{C_{\frak{a}}}}$ form the diagram $\phi
-^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) $ in $\bar{C_{\frak{a}%
+the appropriate sign factors that after being added to $\Phi _{\gf%
+}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ form the diagram $\phi
+^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) $ in $\bar{C_{\af%
 }}$.
@@
 Now let us return to relation (\ref{singular main-3}). One can add to $%
-\Phi _{\frak{g}}^{\left( \mu \right) }$ pairs of formal elements
+\Phi _{\gf}^{\left( \mu \right) }$ pairs of formal elements
 constructed above  with the opposite signs: $\epsilon \left( w\right)
@@
 Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ to
-the elements whose weights we shall attribute to $\bar{C_{\frak{a}}}$. 
+the elements whose weights we shall attribute to $\bar{C_{\af}}$. 
 The same elements with the opposite signs are to be referred to the
-neighboring Weyl chambers of $\bar{C_{\frak{a}}^{(l)}}$ (the latter are
+neighboring Weyl chambers of $\bar{C_{\af}^{(l)}}$ (the latter are
 connected with the main one via simple reflections $s_{\alpha _{l}}$ so the
@@
 them). In fact one can repeat the procedure and find additional singular
-weights in any Weyl chamber $\bar{C_{\frak{a}}^{(m)}}$ and in them
+weights in any Weyl chamber $\bar{C_{\af}^{(m)}}$ and in them
 additional singular weights always have the signs opposite to that in their
-nearest neighbors. Thus without changing the element $\Phi _{\frak{g}%
+nearest neighbors. Thus without changing the element $\Phi _{\gf%
 }^{\left( \mu \right) }$ one can present it as a sum
 \begin{equation}
-\Phi _{\frak{g}}^{\left( \mu \right) }=\sum_{w\in W_{\frak{a}}}w\circ \left(
-e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho _{\frak{s}}}\right)
+\Phi _{\gf}^{\left( \mu \right) }=\sum_{w\in W_{\af}}w\circ \left(
+e^{\rho _{\af}}\Psi ^{\widetilde{\mu }+\rho _{\frak{s}}}\right)
 \label{singular final}
@@
 }^{+}}(1-e^{-\beta })\right) ^{-1}$ to each summand of the singular element $%
-\Phi _{\frak{g}}^{\left( \mu \right) }$ separately because the sets of
+\Phi _{\gf}^{\left( \mu \right) }$ separately because the sets of
 weights from different Weyl summands do not intersect. Taking into account
 the isomorphism $\phi $ one can see that in the main Weyl chamber $\bar{C_{%
-\frak{a}}}$ the set of weights generated by the factor $\left( \prod_{\beta
+\af}}$ the set of weights generated by the factor $\left( \prod_{\beta
 \in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}$ is isomorphic to
@@
 s}$-module $L_{\frak{s}}^{\widetilde{\mu }}$. Now one can restrict
-relation (\ref{singular main-3}) to $\bar{C_{\frak{a}}}$ and obtain the main
+relation (\ref{singular main-3}) to $\bar{C_{\af}}$ and obtain the main
 result:
@@
 \begin{equation}
-\frac{e^{\rho _{\frak{g}}}}{\prod_{\beta \in \Delta _{\frak{s}%
+\frac{e^{\rho _{\gf}}}{\prod_{\beta \in \Delta _{\frak{s}%
 }^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
@@
 \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
-}=\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
+}=\sum_{\nu \in P_{\af}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
 \label{singular main-4}
@@
   Consider the Lie algebra $A_{2} =\bf{sl}(3)$ and branching of its irreducible module $L^{[3,2]}_{A_{2}}$ with respect to the reductive subalgebra $A_{1}\oplus u(1)$.
-The root system  $\Delta _{\frak{a}}= \Delta_{A_{1}\oplus u(1)}$ contains the simple root of $\alpha_1=e_1-e_2$ of $A_{2}$.
-The singular element $\Psi^{[3,2]}_{\frak{a}}$ is decomposed into a sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules.
+The root system  $\Delta _{\af}= \Delta_{A_{1}\oplus u(1)}$ contains the simple root of $\alpha_1=e_1-e_2$ of $A_{2}$.
+The singular element $\Psi^{[3,2]}_{\af}$ is decomposed into a sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules.
 Branching coefficients $b_{\nu }^{[ 3,2 ] }$ coincide with weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module (see Fig.
@@
 \begin{example}
-   Lie algebra $G_{2}$ has a regular subalgebra $A_{2}$ with root system $\Delta_{\mathfrak{a}}=\Delta_{A_{2}}$ containing the $G_{2}$ long roots.
+   Lie algebra $G_{2}$ has a regular subalgebra $A_{2}$ with root system $\Delta_{\af}=\Delta_{A_{2}}$ containing the $G_{2}$ long roots.
 Consider branching of an irreducible module $L_{G_{2}}^{(3,2)}$ into the $A_{2}$-modules.
@@
 Dynkin labels referred to the Lie algebra $\mathfrak{s}$. This algebra
-$\mathfrak{s}$ must not be a subalgebra in the initial $\mathfrak{g}$ , it
+$\mathfrak{s}$ must not be a subalgebra in the initial $\gf$ , it
 has the same rank $r_{\mathfrak{s}}=r$\ , but obviously less
-"complicated" than $\mathfrak{g}$ -- only a subset of the initial root system is involved in the second stem $\Delta_{\mathfrak{s}}$.
+"complicated" than $\gf$ -- only a subset of the initial root system is involved in the second stem $\Delta_{\mathfrak{s}}$.
 
@@
 \begin{Prop}
-Let $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})$ be an
+Let $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})$ be an
 injective
 splint with the decomposition of simple roots $S=S_{\frak{c}}\cup S_{\frak{d}%
-}$ with $S_{\frak{c}}=S\cap S_{\frak{a}}$ and $S_{\frak{d}}=S\cap S_{\frak{s}%
+}$ with $S_{\frak{c}}=S\cap S_{\af}$ and $S_{\frak{d}}=S\cap S_{\frak{s}%
 }$.
@@
   }
-  \caption{Positive roots of $G_{2}$ and formation of singular element $\Phi^{(0)}_{\mathfrak{s}}$ in the main Weyl chamber of $\mathfrak{a}=A_{2}$.}
+  \caption{Positive roots of $G_{2}$ and formation of singular element $\Phi^{(0)}_{\mathfrak{s}}$ in the main Weyl chamber of $\af=A_{2}$.}
 \end{figure}
@@
 _{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$, its end
-belongs to the boundary $\bar{C_{\frak{a}}}$. The reflection
+belongs to the boundary $\bar{C_{\af}}$. The reflection
 $s_{\beta
@@
 $\lambda _{2,3,1}^{\frak{s}}$) edges to find that they belong to
-the boundary $\bar{C_{\frak{a}}}$ and the Weyl symmetry predicts
+the boundary $\bar{C_{\af}}$ and the Weyl symmetry predicts
 that $\lambda _{1,3}^{\frak{s}}=-\left( m_{2}+1\right)
@@
 \frak{s}}$ with the $\alpha _{2}$-boundary of
-$\bar{C_{\frak{a}}}$ fixes
+$\bar{C_{\af}}$ fixes
 its length to be $\lambda _{2}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{2}$%
@@
 $\widetilde{\mu }=\sum m_{k}\widetilde{\omega }_{k}$ is formed in
-$\bar{C_{\frak{a}}}$.
+$\bar{C_{\af}}$.
 \item
@@
 Both stems are metric. An injection is fixed by the stem $\Delta
-_{D_{r}}$ simple roots $S_{\frak{a}}=\left\{
+_{D_{r}}$ simple roots $S_{\af}=\left\{
 e_{1}-e_{2},e_{2}-e_{3},\ldots
@@
 Here only the first stem is metric and it fixes the injection with
-simple roots $S_{\frak{a}}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots
+simple roots $S_{\af}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots
 ,e_{r-1}-e_{r}\right\} $. The second stem corresponding to a direct sum of $%

### 2011-12-03 AffineLieAlgebras/Thesis/3.tex
Translations in chapter 3.

@@
 
-To study relations between injection fan technique and splint let us 
-consider the case when one of the stems $\Delta _{1}=\Delta _{\af}$ 
-is a root subsystem.
+Чтобы показать связь веера вложения со сплинтом рассмотрим случай, когда один из стеблей $\Delta _{1}=\Delta _{\af}$  является подсистемой корневой системы.
 
-Splint $\Delta \approx (\Delta _{1},\Delta _{2})$ is called ''injective'' if
-$\Delta _{1}=\Delta _{\af}$, is a root subsystem
-in $\Delta $ corresponding to a regular reductive subalgebra $\af%
-\hookrightarrow \gf$.
+Сплинт $\Delta \approx (\Delta _{1},\Delta _{2})$ называется ``инъективным'', если $\Delta _{1}=\Delta _{\af}$, -- подсистема корневой системы $\Delta $, соответствующая регулярной редуктивной подалгебре $\af\hookrightarrow \gf$.
 
-In case of injective splint the second stem $\Delta _{\frak{s}}:=\Delta
-_{2}=\Delta \setminus \Delta _{\af}$ can be translated into a product (%
-\ref{product}) and it defines an injection fan $\Gamma _{\af%
-\hookrightarrow \gf}$. Denote by $\Delta_{\mathfrak{s}0}$ the coimage of the second embedding $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$.
-The following conjecture follows.
+В случае инъективного сплинта второй стебель $\Delta _{\frak{s}}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (\ref{product}) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$.
+Обозначим через $\Delta_{\mathfrak{s}0}$ кообраз второго вложения $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$.
+Верна следующая гипотеза.
 
 \begin{Cnj}
-Each injective splint $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})
-$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\af%
-\rightarrow \gf}$ fixed by the product
+Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением
 \begin{equation}
@@
 
-In case of injective splint we say that subalgebra $\af\hookrightarrow \gf$
-splinters $\Delta $ (and call $\af$ the ''splinting subalgebra'' of $%
-\gf$). In \cite{richter2008splints} splints are classified (see Appendix there)
-and the first three types of them are injective.
+В случае инъективного сплинты мы можем сказать, что подалгебра $\af\hookrightarrow \gf$ расщепляется $\Delta$ (и назовем $\af$ ``расщепляющей подалгеброй'' алгебры $\gf$).
+Сплинты были классифицированы в работе \cite{richter2008splints}  (см.
+Приложение в работе) и первые три класса сплинтов в этой классификации инъективны.
 
-\section{How stems define multiplicity functions}
+\section{Как стебли определяют функции кратности}
 
@@
 
-In this Section we study properties of injective splints  $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})
-$. It will
-be demonstrated that in this case to find branching
-coefficients for a splinting injection $\af\hookrightarrow
-\gf$ means to find weight multiplicities of an irreducible
-$\frak{s}$-module $L_{\frak{s}}^{\nu }$ with fixed highest weight
-$\nu $. Notice that $\frak{s}$ must not be a subalgebra of
-$\gf$.
+В этом разделе мы рассмотрим свойства инъективных сплинтов $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})$.
+Мы покажем, что в этом случае вычисление коэффициентов ветвления для расщепляющего вложения $\af\hookrightarrow\gf$ эквивалентно нахождению кратностей весов неприводимого $\frak{s}$-модуля $L_{\frak{s}}^{\nu }$ с определенным старшим весом $\nu $.
+Заметим, что алгебра $\frak{s}$ не обязательно должна быть подалгеброй $\gf$.
 

### 2011-12-03 AffineLieAlgebras/Thesis/3.tex
More translations.

@@
 
-В случае инъективного сплинта второй стебель $\Delta _{\frak{s}}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (\ref{product}) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$.
+В случае инъективного сплинта второй стебель $\Delta _{\sfr}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (\ref{product}) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$.
 Обозначим через $\Delta_{\mathfrak{s}0}$ кообраз второго вложения $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$.
@@
 \begin{Cnj}
-Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением
+Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением
 \begin{equation}
-\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)
+\prod_{\beta \in \Delta _{\sfr}^{+}}\left( 1-e^{-\beta }\right)
 =-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
@@
 
-В этом разделе мы рассмотрим свойства инъективных сплинтов $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})$.
-Мы покажем, что в этом случае вычисление коэффициентов ветвления для расщепляющего вложения $\af\hookrightarrow\gf$ эквивалентно нахождению кратностей весов неприводимого $\frak{s}$-модуля $L_{\frak{s}}^{\nu }$ с определенным старшим весом $\nu $.
-Заметим, что алгебра $\frak{s}$ не обязательно должна быть подалгеброй $\gf$.
+В этом разделе мы рассмотрим свойства инъективных сплинтов $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$.
+Мы покажем, что в этом случае вычисление коэффициентов ветвления для расщепляющего вложения $\af\hookrightarrow\gf$ эквивалентно нахождению кратностей весов неприводимого $\sfr$-модуля $L_{\sfr}^{\nu }$ с определенным старшим весом $\nu $.
+Заметим, что алгебра $\sfr$ не обязательно должна быть подалгеброй $\gf$.
 
-Let us return to relation (\ref{singular main}) and multiply both sides by $%
-R_{\af}$:
+Вернемся к соотношению  (\ref{singular main}) и домножим обе стороны на  $R_{\af}$:
 \begin{equation}
-\frac{1}{\prod_{\beta \in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })}\Psi _{%
-\gf}^{\left( \mu \right) }=\sum_{\nu \in P_{\af}^{+}}b_{\nu
-}^{(\mu )}\Psi _{\af}^{\left( \nu \right) }.
+\frac{1}{\prod_{\beta \in \Delta _{\sfr}^{+}}(1-e^{-\beta })}\Psi _{\gf}^{\left( \mu \right) }=\sum_{\nu \in P_{\af}^{+}}b_{\nu}^{(\mu )}\Psi _{\af}^{\left( \nu \right) }.
 \label{singular main-2}
 \end{equation}
-Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{%
-\af\rightarrow \gf}$. Consider the highest weight module $L_{\frak{%
-s}}^{\nu }$. The embedding $\phi :\Delta _{\frak{s}\,0}\longrightarrow \Delta
-_{\gf}$ sends the singular element $\Psi _{\frak{s}}^{\left( \nu
-\right) }$ into $\Psi _{\gf}^{\left( \mu \right) }$. Applying the
-inverse morphism $\phi ^{-1}$ to the product $\left( \prod_{\beta \in \Delta
-_{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\frak{s}%
-}^{\left( \nu \right) }\right) $ one gets the character of the module $L_{%
-\frak{s}}^{\nu }$,
+Здесь первый множитель в левой части -- это формальный элемент, обратный к вееру $\Gamma _{\af\rightarrow \gf}$.
+Рассмотрим модуль старшего веса $L_{\sfr}^{\nu }$.
+Вложение $\phi :\Delta _{\sfr\,0}\longrightarrow \Delta_{\gf}$ переводит сингулярный элемент  $\Psi _{\sfr}^{\left( \nu\right) }$ в $\Psi _{\gf}^{\left( \mu \right) }$.
+Применяя обратный морфизм $\phi ^{-1}$ к произведению $\left( \prod_{\beta \in \Delta_{\sfr}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\sfr}^{\left( \nu \right) }\right) $, мы получаем характер модуля $L_{\sfr}^{\nu }$,
 
 \begin{equation}
-\phi ^{-1}\left( \frac{1}{\prod_{\beta \in \Delta _{\frak{s}%
-}^{+}}(1-e^{-\beta })}\phi \left( \Psi _{\frak{s}}^{\left( \nu \right)
-}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\frak{s}0
-}^{+}}(1-e^{-\beta })}\Psi _{\frak{s}}^{\left( \nu \right) }=\mathrm{ch}%
-\left( L_{\frak{s}}^{\nu }\right) .  \label{inverse for stem}
+\phi ^{-1}\left( \frac{1}{\prod_{\beta \in \Delta _{\sfr%
+}^{+}}(1-e^{-\beta })}\phi \left( \Psi _{\sfr}^{\left( \nu \right)
+}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\sfr0
+}^{+}}(1-e^{-\beta })}\Psi _{\sfr}^{\left( \nu \right) }=\mathrm{ch}%
+\left( L_{\sfr}^{\nu }\right) .  \label{inverse for stem}
 \end{equation}
-Our task is to prove that the singular element $\Psi _{\gf}^{\left( \mu
-\right) }$ contains the element $\Psi _{\frak{s}}^{\left( \xi \right) }$ for
-a module $L_{\frak{s}}^{\xi }$ uniquely defined by $L_{\gf}^{\mu }$ and
-that the branching coefficients $b_{\nu }^{(\mu )}$ in the r.h.s. of (\ref
-{singular main-2}) coincide with multiplicities $m_{\zeta }^{\left( \xi
-\right) }$ of the corresponding weights in $\mathcal{N}_{\frak{s}}^{\xi }$ .
+Наша задача состоит в том, чтобы доказать, что сингулярный элемент $\Psi _{\gf}^{\left(\mu\right) }$ содержит элемент $\Psi _{\sfr}^{\left( \xi \right) }$ для модуля $L_{\sfr}^{\xi }$, однозначно определяемого модулем $L_{\gf}^{\mu }$ и что коэффициенты ветвления $b_{\nu }^{(\mu )}$ в правой части равенства (\ref{singular main-2}) совпадают с кратностями $m_{\zeta }^{\left( \xi\right) }$ соответствующих весов в $\mathcal{N}_{\sfr}^{\xi }$ .
 
-For a highest weight irreducible module $L_{\gf}^{\mu }$ the singular
-element $\Psi _{\gf}^{\left( \mu \right) }$ is an element of $\mathcal{E%
-}$ corresponding to the shifted Weyl-orbit of the weight $\left( \mu +\rho
-\right) \in P^{+}$ with the sign function $\epsilon \left( w\right) $. It is
-convenient to use also unshifted singular elements
+Для неприводимого модуля старшего веса $L_{\gf}^{\mu }$ сингулярный элемент $\Psi _{\gf}^{\left( \mu \right) }$ -- это элемент $\mathcal{E}$, соответствующий сдвинутой орбите группы веса $\left( \mu +\rho\right) \in P^{+}$, со знаковой функцией $\epsilon \left( w\right) $.
+Удобно использовать также не сдвинутые сингулярные элементы
 \begin{equation}
@@
 \end{equation}
-In these terms the relation (\ref{singular main-2}) looks like
+В этих обозначениях соотношение (\ref{singular main-2}) имеет вид
 \begin{equation}
@@
 \end{equation}
-The orbit related to $\Phi _{\gf}^{\left( \mu \right) }$ is completely
-defined by the set of edges $\left\{ \lambda _{i}\right\} _{i=1,\dots ,r}$
-adjusted to the end of the highest weight vector $\mu +\rho $. For $\mu
-=\sum m_{i}\omega _{i}$ these edges are
+Орбита, связанная с  $\Phi _{\gf}^{\left( \mu \right) }$, полностью определяется набором ребер $\left\{ \lambda _{i}\right\} _{i=1,\dots ,r}$ построенным из конца вектора старшего веса $\mu +\rho $.
+Для $\mu=\sum m_{i}\omega _{i}$ эти ребра равны
 \begin{equation}
@@
 \end{equation}
-Each formal exponent $e^{\mu +\rho +\lambda _{i}}$ in $\Phi _{\gf%
-}^{\left( \mu \right) }$ bears the sign coefficient $\epsilon =(-)$. The
-defining property of $\Phi _{\gf}^{\left( \mu \right) }$ is as follows.
-Consider any pair of edges $\lambda _{i},\lambda _{j}$ and the corresponding
-weights $\mu +\rho $, $\mu +\rho +\lambda _{i}$ and $\mu +\rho +\lambda _{j}$. 
-Apply the reflection $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
+Каждая формальная экспонента $e^{\mu +\rho +\lambda _{i}}$ in $\Phi _{\gf}^{\left( \mu \right) }$ снабжена знаковым коэффициентом  $\epsilon =(-)$.
+Можно определить $\Phi_{\gf}^{\left( \mu \right) }$ следующим свойством.
+Рассмотрим любую пару ребер $\lambda _{i},\lambda _{j}$ и соответствующие веса $\mu +\rho $, $\mu +\rho +\lambda _{i}$ и $\mu +\rho +\lambda _{j}$.
+Применим отражение $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
 \begin{equation}
@@
 \begin{Prop}
-The edge $\lambda _{i,j}$ of $\Phi _{\gf}^{\left( \mu \right) }$
-starting at the weight $\left( \mu +\rho +\lambda _{i}\right) $ along the
-root $-s_{\alpha _{i}}\circ \alpha _{j}$ has the same length in $(s_{\alpha
-_{i}}\circ \alpha _{j})$ as $\lambda _{j}$ has in $\alpha _{j}$. (The same
-is true for the edge $\lambda _{j,i}$, its length in $(s_{\alpha _{j}}\circ
-\alpha _{i})$ is equal to the length of $\lambda _{i}$ in $\alpha _{i}$.)
+Ребро  $\lambda _{i,j}$ сингулярного элемента $\Phi _{\gf}^{\left( \mu \right) }$, начинающееся в весе $\left( \mu +\rho +\lambda _{i}\right) $ и направленное вдоль корня $-s_{\alpha _{i}}\circ \alpha _{j}$ имеет такую же длину, выраженную в длинах корня $(s_{\alpha_{i}}\circ \alpha _{j})$, как и $\lambda _{j}$ в длинах $\alpha _{j}$.
+(Это же верно для ребра $\lambda _{j,i}$, его длина в единицах $(s_{\alpha _{j}}\circ\alpha _{i})$ равна длине $\lambda _{i}$ в единицах $\alpha _{i}$.)
 \label{diagram property}
@@
 
-In $\Phi _{\gf}^{\left( \mu \right) }$ the elements $e^{\left( \mu
-+\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha _{j}\right) }$ and $%
-e^{\left( \mu +\rho +\lambda _{j}-(m_{i}+1)s_{\alpha _{j}}\circ \alpha
-_{i}\right) }$ have the sign coefficient  $\epsilon =(+)$.
+В $\Phi _{\gf}^{\left( \mu \right) }$ элементы $e^{\left( \mu+\rho +\lambda_{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha _{j}\right) }$ и $e^{\left( \mu +\rho +\lambda _{j}-(m_{i}+1)s_{\alpha_{j}}\circ \alpha_{i}\right) }$ имеют знаковый коэффициент  $\epsilon =(+)$.
 
-Remember that only three types of splints are
-injective and thus are naturally connected with branching. Below we
-reproduce the part of the splints table from \cite{richter2008splints} corresponding to
-injective splints:
+Вспомним, что только три типа сплинтов инъективны и имеют естественную связь с ветвлениями.
+Ниже мы приводим часть таблицы сплинтов из работы \cite{richter2008splints}, соответствующую инъективным сплинтам:
 \[
@@
 \hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
-_{\af}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
+_{\af}\hspace{0.25in} & \hspace{0.25in}\Delta _{\sfr}\hspace{0.25in}
 \\ \hline\hline
@@
 \]
-Each row in the table gives a splint $(\Delta _{\af},\Delta _{\frak{s}})
+Each row in the table gives a splint $(\Delta _{\af},\Delta _{\sfr})
 $ of the simple root system $\Delta $. In the first two types both $\Delta _{%
-\af}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
+\af}$ and $\Delta _{\sfr}$ are embedded metrically. Stems in the
 first type splints are equivalent and in the second are not. In the third
@@
 the principle properties of branching but makes it possible to use the
-multiplicities of $\frak{s}$-modules without further projecting their
+multiplicities of $\sfr$-modules without further projecting their
 weights.
@@
 Splints induce a decomposition of the set $S=S_{\frak{c}}\cup S_{\frak{d}}$
-with $S_{\frak{c}}=S\cap S_{\af}$ and $S_{\frak{d}}=S\cap S_{\frak{s}}$. 
+with $S_{\frak{c}}=S\cap S_{\af}$ and $S_{\frak{d}}=S\cap S_{\sfr}$. 
 It is easy to check that for any injective splint the subset $S_{%
@@
 _{i}\right\} _{i=1,\dots ,r}$ one can always find simple roots $\beta
-_{k}\in \Delta _{\frak{s}}$ and that the orbit corresponding to $\Phi _{%
+_{k}\in \Delta _{\sfr}$ and that the orbit corresponding to $\Phi _{%
 \gf}^{\left( \mu \right) }$ contains the edges
@@
 }^{\left( \mu \right) }$ being a singular element for a set of $\af$%
--modules. Consider $\beta _{l}\in \Delta _{\frak{s}}$ whose coimage in $%
-\Delta _{\frak{s}0}$ is simple. In Appendix it is shown that for any such $%
+-modules. Consider $\beta _{l}\in \Delta _{\sfr}$ whose coimage in $%
+\Delta _{\sfr0}$ is simple. In Appendix it is shown that for any such $%
 \beta _{l}$ there exists a root $\alpha _{l}\in S_{\frak{c}}$ such that
@@
 This means that for the triple of roots $\beta _{k},\beta _{l}$ and $%
-s_{\beta _{k}}\alpha _{l}$ in $\Delta _{\frak{s}}$ the edges $\lambda
+s_{\beta _{k}}\alpha _{l}$ in $\Delta _{\sfr}$ the edges $\lambda
 _{k}=-\left( m_{k}+1\right) \beta _{k}$, $\lambda _{l}=-\left(
@@
 The same can be proven for any positive root $\beta _{l}\in \Delta $ that is
-simple in $\Delta _{\frak{s}0}$ and correspondingly for any $r=2$ subalgebra
-in $\frak{s}$. The latter means that to ''find'' a singular element of $%
-\frak{s}$-module in $\Phi _{\gf}^{\left( \mu \right) }$ it is necessary
+simple in $\Delta _{\sfr0}$ and correspondingly for any $r=2$ subalgebra
+in $\sfr$. The latter means that to ''find'' a singular element of $%
+\sfr$-module in $\Phi _{\gf}^{\left( \mu \right) }$ it is necessary
 to incorporate in it additional formal elements $\left\{ -e^{\mu +\rho
 -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\}.$ This
-fixes the starting edges of the diagram $\phi ^{-1}\left( \Phi _{\frak{s}}^{%
+fixes the starting edges of the diagram $\phi ^{-1}\left( \Phi _{\sfr}^{%
 \widetilde{\mu }}\right) $. As it follows from the reconstruction procedure
@@
 \end{equation}
-The next step is to construct the full $W_{\frak{s}}$-orbit $\Phi _{\frak{s}%
-}^{\left( \widetilde{\mu }\right) }$  in $P_{\frak{s}}$. It is easily seen
+The next step is to construct the full $W_{\sfr}$-orbit $\Phi _{\sfr%
+}^{\left( \widetilde{\mu }\right) }$  in $P_{\sfr}$. It is easily seen
 that its coimage belongs to $\bar{C_{\af}}$ and that the set $\phi
-^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) \setminus \Phi _{%
+^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) \setminus \Phi _{%
 \gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ corresponds to the
@@
 }^{\left( \mu \right) }|_{\bar{C_{\af}}}$ form the diagram $\phi
-^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) $ in $\bar{C_{\af%
+^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) $ in $\bar{C_{\af%
 }}$.
@@
 constructed above  with the opposite signs: $\epsilon \left( w\right)
-|_{w\in W_{\frak{s}}}$ and $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$. 
-Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ to
+|_{w\in W_{\sfr}}$ and $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$. 
+Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\sfr}}$ to
 the elements whose weights we shall attribute to $\bar{C_{\af}}$. 
@@
 connected with the main one via simple reflections $s_{\alpha _{l}}$ so the
-signes $-\epsilon \left( w\right) |_{w\in W_{\frak{s}}}$ are natural for
+signes $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$ are natural for
 them). In fact one can repeat the procedure and find additional singular
@@
 \Phi _{\gf}^{\left( \mu \right) }=\sum_{w\in W_{\af}}w\circ \left(
-e^{\rho _{\af}}\Psi ^{\widetilde{\mu }+\rho _{\frak{s}}}\right)
+e^{\rho _{\af}}\Psi ^{\widetilde{\mu }+\rho _{\sfr}}\right)
 \label{singular final}
 \end{equation}
-where the weight $\widetilde{\mu }=\sum m_{k}\omega _{\frak{s}}^{k}$ was
+where the weight $\widetilde{\mu }=\sum m_{k}\omega _{\sfr}^{k}$ was
 defined above. The decomposition (\ref{singular final}) provides the
-possibility to apply the factor $\left( \prod_{\beta \in \Delta _{\frak{s}%
+possibility to apply the factor $\left( \prod_{\beta \in \Delta _{\sfr%
 }^{+}}(1-e^{-\beta })\right) ^{-1}$ to each summand of the singular element $%
@@
 \af}}$ the set of weights generated by the factor $\left( \prod_{\beta
-\in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}$ is isomorphic to
-the weight diagram $\mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ of the $\frak{%
-s}$-module $L_{\frak{s}}^{\widetilde{\mu }}$. Now one can restrict
+\in \Delta _{\sfr}^{+}}(1-e^{-\beta })\right) ^{-1}$ is isomorphic to
+the weight diagram $\mathcal{N}_{\sfr}^{\widetilde{\mu }}$ of the $\frak{%
+s}$-module $L_{\sfr}^{\widetilde{\mu }}$. Now one can restrict
 relation (\ref{singular main-3}) to $\bar{C_{\af}}$ and obtain the main
@@
 \begin{equation}
-\frac{e^{\rho _{\gf}}}{\prod_{\beta \in \Delta _{\frak{s}%
-}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
-}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }%
-}}M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
+\frac{e^{\rho _{\gf}}}{\prod_{\beta \in \Delta _{\sfr%
+}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\sfr%
+}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\sfr}^{\widetilde{\mu }%
+}}M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
 \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
@@
 Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
-highest weights in the decomposition. The multiplicity $M_{\left( \frak{s}%
+highest weights in the decomposition. The multiplicity $M_{\left( \sfr%
 \right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
-}\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ defines the branching
+}\in \mathcal{N}_{\sfr}^{\widetilde{\mu }}$ defines the branching
 coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
@@
 b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
-}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}.
+}^{(\mu )}=M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}.
 \]
@@
 algebras and the fact that the corresponding module
-$L_{\frak{s}}^{\mu }$ is irreducible.
+$L_{\sfr}^{\mu }$ is irreducible.
 
@@
 \begin{Prop}
-Let $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})$ be an
+Let $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ be an
 injective
 splint with the decomposition of simple roots $S=S_{\frak{c}}\cup S_{\frak{d}%
-}$ with $S_{\frak{c}}=S\cap S_{\af}$ and $S_{\frak{d}}=S\cap S_{\frak{s}%
+}$ with $S_{\frak{c}}=S\cap S_{\af}$ and $S_{\frak{d}}=S\cap S_{\sfr%
 }$.
 \end{Prop}
-Thus for any simple root $\beta \in S_{\frak{s}}$ there exists the
+Thus for any simple root $\beta \in S_{\sfr}$ there exists the
 pair of
 roots ( $\alpha $ ,$\beta ^{\prime }$) with $\alpha \in $ $S_{\frak{c}%
-},\beta ^{\prime }\in S_{\frak{s}}$ such that $\alpha =\beta
+},\beta ^{\prime }\in S_{\sfr}$ such that $\alpha =\beta
 -\beta ^{\prime }$
@@
 is  $(\alpha _{1}, \beta _{2})$: $\alpha _{1}=\beta _{1}-\beta _{2}$. The $%
-\lambda _{2,3}^{\frak{s}}=\beta _{3}$ edge is equal to $\lambda _{1}^{\frak{s%
+\lambda _{2,3}^{\sfr}=\beta _{3}$ edge is equal to $\lambda _{1}^{\frak{s%
 }}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ and $m_{1}$ index
-is aquired by the $\frak{s}$-module that also inherit the second
+is aquired by the $\sfr$-module that also inherit the second
 index $m_{2}$. In this particular
@@
 m_{2}+1\right) \beta _{2}$ and put $\lambda
-_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$, its end
+_{1}^{\sfr}=-\left( m_{1}+1\right) \beta _{1}$, its end
 belongs to the boundary $\bar{C_{\af}}$. The reflection
@@
 _{2}} $ sends $\beta _{1}$ to $\beta _{3}$ and the corresponding edge 
-$\lambda _{2,3}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{3}$ has
-the length $\left( m_{1}+1\right) $. Now consider $\lambda _{1}^{\frak{s}}$ (or
-$\lambda _{2,3}^{\frak{s}} $) and $\lambda _{1,3}^{\frak{s}}$ (or
-$\lambda _{2,3,1}^{\frak{s}}$) edges to find that they belong to
+$\lambda _{2,3}^{\sfr}=-\left( m_{1}+1\right) \beta _{3}$ has
+the length $\left( m_{1}+1\right) $. Now consider $\lambda _{1}^{\sfr}$ (or
+$\lambda _{2,3}^{\sfr} $) and $\lambda _{1,3}^{\sfr}$ (or
+$\lambda _{2,3,1}^{\sfr}$) edges to find that they belong to
 the boundary $\bar{C_{\af}}$ and the Weyl symmetry predicts
-that $\lambda _{1,3}^{\frak{s}}=-\left( m_{2}+1\right)
-\beta _{3}$ ($\lambda _{2,3,1}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{1}$%
-) . Finally the edge $\lambda _{1,3,2}^{\frak{s}}=-\left(
+that $\lambda _{1,3}^{\sfr}=-\left( m_{2}+1\right)
+\beta _{3}$ ($\lambda _{2,3,1}^{\sfr}=-\left( m_{2}+1\right) \beta _{1}$%
+) . Finally the edge $\lambda _{1,3,2}^{\sfr}=-\left(
 m_{1}+1\right) \beta _{2}$ closes the polytope. Its vertices
 correspond to weights of the singular
-element $\Phi _{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{%
-\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
+element $\Phi _{\sfr}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{%
+\sfr}}\varepsilon \left( w\right) e^{w\circ \left(
 \widetilde{\mu }+\rho
-_{\frak{s}}\right) }$ of the module $L_{\frak{s}}^{\left( \widetilde{\mu }%
+_{\sfr}\right) }$ of the module $L_{\sfr}^{\left( \widetilde{\mu }%
 \right) }$ with $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}%
@@
 \beta _{3}$.
- Compose an edge $\lambda _{2}^{\frak{s}}=-\left( \widetilde{m}%
+ Compose an edge $\lambda _{2}^{\sfr}=-\left( \widetilde{m}%
 _{2}+1\right) \beta _{2}$. The necessary pair of roots is $\left(
@@
 _{2}=e_{3}-e_{4},\beta _{3}\right) $. The intersection of $\lambda _{2}^{%
-\frak{s}}$ with the $\alpha _{2}$-boundary of
+\sfr}$ with the $\alpha _{2}$-boundary of
 $\bar{C_{\af}}$ fixes
-its length to be $\lambda _{2}^{\frak{s}}=-\left( m_{2}+1\right) \beta _{2}$%
-\ and the length of the edge $\lambda _{3,2}^{\frak{s}}$ is equal
+its length to be $\lambda _{2}^{\sfr}=-\left( m_{2}+1\right) \beta _{2}$%
+\ and the length of the edge $\lambda _{3,2}^{\sfr}$ is equal
 to that of
-$\lambda _{2}^{\frak{s}}$. Next consider the edge $\lambda _{2}^{\frak{s}%
+$\lambda _{2}^{\sfr}$. Next consider the edge $\lambda _{2}^{\sfr%
 }=-\left( m_{2}+1\right) \beta _{2}$ and the pair $\left( \alpha
 _{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $. The length of  
-$\lambda _{1}^{\frak{s}}$ becomes equal to $\lambda
-_{1}^{\frak{s}}=-\left( m_{1}+1\right) \beta _{1}$. Proceed further till the closure of the polytope. 
+$\lambda _{1}^{\sfr}$ becomes equal to $\lambda
+_{1}^{\sfr}=-\left( m_{1}+1\right) \beta _{1}$. Proceed further till the closure of the polytope. 
 The edges looking along the roots of the $\alpha_4$-type, $\alpha _{4}=\beta
@@
 treated similarly and finally the singular element $\Phi
-_{\frak{s}}^{\left( \widetilde{\mu }\right) }=\sum_{w\in
-W_{\frak{s}}}\varepsilon \left( w\right) e^{w\circ \left(
-\widetilde{\mu }+\rho _{\frak{s}}\right) }$ for the module
-$L_{\frak{s}}^{\left( \widetilde{\mu }\right) }$ with
+_{\sfr}^{\left( \widetilde{\mu }\right) }=\sum_{w\in
+W_{\sfr}}\varepsilon \left( w\right) e^{w\circ \left(
+\widetilde{\mu }+\rho _{\sfr}\right) }$ for the module
+$L_{\sfr}^{\left( \widetilde{\mu }\right) }$ with
 $\widetilde{\mu }=\sum m_{k}\widetilde{\omega }_{k}$ is formed in
@@
 corresponds to a
-direct sum of algebras $A_{1}$ with the simple roots $S_{\frak{s}%
+direct sum of algebras $A_{1}$ with the simple roots $S_{\sfr%
 }=\left\{ e_{1},e_{2},\ldots ,e_{r-1},e_{r}\right\} $. Consider the edge $%
@@
 ,e_{r-1}-e_{r}\right\} $. The second stem corresponding to a direct sum of $%
-r$ copies of $A_{1}$ has the simple roots $S_{\frak{s}}=\left\{
+r$ copies of $A_{1}$ has the simple roots $S_{\sfr}=\left\{
 e_{1}-e_{r+1},e_{2}-e_{r+1},\ldots ,e_{r}-e_{r+1}\right\} $.
@@
 m_{1}+1\right)
-\beta _{3}$ with $\beta _{3}=e_{1}+e_{3}$. The irreducible $\frak{s}$%
+\beta _{3}$ with $\beta _{3}=e_{1}+e_{3}$. The irreducible $\sfr$%
 -module has the highest weight $\widetilde{\mu }=m_{1}\widetilde{\omega }%

### 2011-12-08 AffineLieAlgebras/Thesis/3.tex
Chapter 3 is translated.

@@
 \begin{array}{cc||c|c}
-\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
+\hbox{тип} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
 _{\af}\hspace{0.25in} & \hspace{0.25in}\Delta _{\sfr}\hspace{0.25in}
@@
 \]
-Each row in the table gives a splint $(\Delta _{\af},\Delta _{\sfr})
-$ of the simple root system $\Delta $. In the first two types both $\Delta _{%
-\af}$ and $\Delta _{\sfr}$ are embedded metrically. Stems in the
-first type splints are equivalent and in the second are not. In the third
-type splints only $\Delta _{\af}$ is embedded metrically. The summands $%
-u\left( 1\right) $ are added to keep $r_{\af}=r$. This does not change
-the principle properties of branching but makes it possible to use the
-multiplicities of $\sfr$-modules without further projecting their
-weights.
 
-Splints induce a decomposition of the set $S=S_{\frak{c}}\cup S_{\frak{d}}$
-with $S_{\frak{c}}=S\cap S_{\af}$ and $S_{\frak{d}}=S\cap S_{\sfr}$. 
-It is easy to check that for any injective splint the subset $S_{%
-\frak{d}}$ is nonempty. It follows that in the set $\left\{ \lambda
-_{i}\right\} _{i=1,\dots ,r}$ one can always find simple roots $\beta
-_{k}\in \Delta _{\sfr}$ and that the orbit corresponding to $\Phi _{%
-\gf}^{\left( \mu \right) }$ contains the edges
+Каждая строка в таблице соответствует сплинту  $(\Delta _{\af},\Delta _{\sfr})$  корневой системы $\Delta $.
+В случае первых двух типов и  $\Delta _{\af}$, и $\Delta _{\sfr}$ вложены метрически.
+Стебли для первого типа эквивалентны, а для второго -- нет.
+В случае третьего типа сплинтов только корневая система $\Delta _{\af}$ вложена метрически.
+Слагаемые $u\left( 1\right) $ добавлены, чтобы совпадали ранги $r_{\af}=r$.
+Такая добавка не меняет основных свойств ветвления, но позволяет использовать кратности весов $\sfr$-модулей без последующей проекции весов.
+
+Сплинт индуцирует разложение множества $S=S_{\frak{c}}\cup S_{\frak{d}}$, где $S_{\frak{c}}=S\cap S_{\af}$ и $S_{\frak{d}}=S\cap S_{\sfr}$.
+Легко проверить, что для любого инъективного сплинта подмножество  $S_{\frak{d}}$ не пусто.
+Следовательно, в множестве $\left\{ \lambda
+_{i}\right\} _{i=1,\dots ,r}$ всегда найдется простые корни $\beta_{k}\in \Delta _{\sfr}$ и орбита, соответствующая $\Phi _{\gf}^{\left( \mu \right) }$ будет содержать ребра
 \begin{equation}
-\lambda _{k}=-\left( m_{k}+1\right) \beta _{k}  \label{beta edge}
+\lambda _{k}=-\left( m_{k}+1\right) \beta _{k}  \label{beta edge},
 \end{equation}
-attached to the weight $\mu +\rho $. As far as $\Delta _{\af}$ is a
-root system and for any pair of simple roots from $S_{\frak{c}}$ the
-property \ref{diagram property} is fulfilled, the element $\Phi _{\gf%
-}^{\left( \mu \right) }$ being a singular element for a set of $\af$%
--modules. Consider $\beta _{l}\in \Delta _{\sfr}$ whose coimage in $%
-\Delta _{\sfr0}$ is simple. In Appendix it is shown that for any such $%
-\beta _{l}$ there exists a root $\alpha _{l}\in S_{\frak{c}}$ such that
-$\beta _{l}=\alpha _{l}+\beta _{k}$. It is easily seen that the
-corresponding edge intersects the boundary plane of the fundamental chamber $%
-\bar{C_{\af}}$ orthogonal to the root $\alpha _{l}$,
+построенные из веса  $\mu +\rho $.
+Так как $\Delta _{\af}$ -- корневая система и для любой пары простых корней из $S_{\frak{c}}$ выполнено свойство \ref{diagram property}, элемент  $\Phi _{\gf}^{\left( \mu \right) }$ является сингулярным элементом для набора  $\af$-модулей.
+Рассмотрим корень $\beta _{l}\in \Delta _{\sfr}$, кообраз которого в  $\Delta _{\sfr0}$  простой.
+В разделе \ref{sec:appendix} мы показываем, что для каждого такого $\beta _{l}$ существует корень  $\alpha _{l}\in S_{\frak{c}}$, такой, что $\beta _{l}=\alpha _{l}+\beta _{k}$.
+Легко видеть, что в этом случае соответствующее ребро пересекает гиперплоскость, ограничивающую главную камеру Вейля$ \bar{C_{\af}}$ и ортогональную к корню $\alpha _{l}$,
 \begin{equation}
@@
 \end{equation}
-It follows that $p=\left( m_{l}+1\right) $ and $s_{\alpha _{l}}\beta
-_{l}=\beta _{k}$. Now apply the operator $s_{\beta _{k}}$ and find that the
-edge along the root $s_{\beta _{k}}\alpha _{l}$ attached at the weight $%
-s_{\beta _{k}}(\mu +\rho )$ is also equal to $-ps_{\beta _{k}}\alpha _{l}$.
-This means that for the triple of roots $\beta _{k},\beta _{l}$ and $%
-s_{\beta _{k}}\alpha _{l}$ in $\Delta _{\sfr}$ the edges $\lambda
-_{k}=-\left( m_{k}+1\right) \beta _{k}$, $\lambda _{l}=-\left(
-m_{l}+1\right) \beta _{l}$ and $\lambda _{kl}=-\left( m_{l}+1\right)
-s_{\beta _{k}}\alpha _{l}$ demonstrate the property \ref{diagram property}.
-One can continue this procedure further in the 2-dimensional subspace fixed
-by the roots $\beta _{k}$ and $\beta _{l}$ and find the set of formal
-exponents that being supplied with the corresponding sign factors compose
-the coimage of the singular element of a module for the subalgebra in $\frak{%
-s}$ (this subalgebra has rank $r=2$).
+Следовательно,  $p=\left( m_{l}+1\right) $ и  $s_{\alpha _{l}}\beta_{l}=\beta _{k}$.
+Теперь применим оператор $s_{\beta _{k}}$ и заметим, что ребро, построенное вдоль корня $s_{\beta _{k}}\alpha _{l}$ из веса $s_{\beta _{k}}(\mu +\rho )$ тоже равно $-ps_{\beta _{k}}\alpha _{l}$.
+Значит, для тройки корней  $\beta _{k},\beta _{l}$ и $s_{\beta _{k}}\alpha _{l}$ in $\Delta _{\sfr}$ ребра $\lambda_{k}=-\left( m_{k}+1\right) \beta _{k}$, $\lambda _{l}=-\left(m_{l}+1\right) \beta _{l}$ и $\lambda _{kl}=-\left( m_{l}+1\right)s_{\beta _{k}}\alpha _{l}$ удовлетворяют свойству \ref{diagram property}.
+Эту процедуру можно продолжить далее в двумерном подпространстве, заданном корнями $\beta _{k}$ и $\beta _{l}$ и показать, что множество формальных экспонент, снабженных соответствующими знаковыми множителями, составляет кообраз сингулярного элемента модуля подалгебры в  $\frak{
+s}$ (ранг этой подалгебры $r=2$).
 
-The same can be proven for any positive root $\beta _{l}\in \Delta $ that is
-simple in $\Delta _{\sfr0}$ and correspondingly for any $r=2$ subalgebra
-in $\sfr$. The latter means that to ''find'' a singular element of $%
-\sfr$-module in $\Phi _{\gf}^{\left( \mu \right) }$ it is necessary
-to incorporate in it additional formal elements $\left\{ -e^{\mu +\rho
--\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\}.$ This
-fixes the starting edges of the diagram $\phi ^{-1}\left( \Phi _{\sfr}^{%
-\widetilde{\mu }}\right) $. As it follows from the reconstruction procedure
-the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $%
-, they have the same Dynkin numbers:
+Аналогичное рассуждение  можно провести для любого положительного корня $\beta _{l}\in \Delta $, являющегося простым в $\Delta _{\sfr0}$ и, соответственно, для любой подалгебры ранга $r=2$ в $\sfr$.
+То есть чтобы ``найти'' сингулярный элемент $\sfr$-модуля в $\Phi_{\gf}^{\left( \mu \right) }$ необходимо сгруппировать с ним дополнительные формальные элементы  $\left\{ -e^{\mu +\rho-\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\}.$ Эта процедура определяет начальные ребра диаграммы $\phi ^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) $.
+Как следует из процедуры восстановления, старший вес $\widetilde{\mu }$ полностью определяется весом $\mu $, эти веса имеют следующие индексы Дынкина:
 \begin{equation}
@@
 \end{equation}
-The next step is to construct the full $W_{\sfr}$-orbit $\Phi _{\sfr%
-}^{\left( \widetilde{\mu }\right) }$  in $P_{\sfr}$. It is easily seen
-that its coimage belongs to $\bar{C_{\af}}$ and that the set $\phi
-^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) \setminus \Phi _{%
-\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ corresponds to the
-weights belonging to the boundary $\bar{C_{\af}}$ (including the subset
-$\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{%
-\frak{c}}\right\} $). Thus we have constructed all the formal elements\ with
-the appropriate sign factors that after being added to $\Phi _{\gf%
-}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ form the diagram $\phi
-^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) $ in $\bar{C_{\af%
-}}$.
+Следующим шагом построим полную  $W_{\sfr}$-орбиту элемента $\Phi _{\sfr}^{\left( \widetilde{\mu }\right) }$  в $P_{\sfr}$.
+Легко видеть, что его кообраз принадлежит  $\bar{C_{\af}}$ и что множество $\phi^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) \setminus \Phi _{\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ соответствует весам, принадлежащим границе$\bar{C_{\af}}$ (включая подмножество $\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\} $).
+То есть мы построили все формальные элементы с соответствующими знаковыми множителями, которые после сложения с  $\Phi _{\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ образуют диаграмму $\phi^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) $ в $\bar{C_{\af}}$.
 
-Now let us return to relation (\ref{singular main-3}). One can add to $%
-\Phi _{\gf}^{\left( \mu \right) }$ pairs of formal elements
-constructed above  with the opposite signs: $\epsilon \left( w\right)
-|_{w\in W_{\sfr}}$ and $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$. 
-Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\sfr}}$ to
-the elements whose weights we shall attribute to $\bar{C_{\af}}$. 
-The same elements with the opposite signs are to be referred to the
-neighboring Weyl chambers of $\bar{C_{\af}^{(l)}}$ (the latter are
-connected with the main one via simple reflections $s_{\alpha _{l}}$ so the
-signes $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$ are natural for
-them). In fact one can repeat the procedure and find additional singular
-weights in any Weyl chamber $\bar{C_{\af}^{(m)}}$ and in them
-additional singular weights always have the signs opposite to that in their
-nearest neighbors. Thus without changing the element $\Phi _{\gf%
-}^{\left( \mu \right) }$ one can present it as a sum
+Теперь вернемся к равенству (\ref{singular main-3}).
+Можно добавить к $\Phi _{\gf}^{\left( \mu \right) }$ пары формальных элементов, построенные выше, с противоположными знаками: $\epsilon \left( w\right)|_{w\in W_{\sfr}}$ and $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$.
+Припишем знаки $\epsilon \left( w\right) |_{w\in W_{\sfr}}$ элементам, веса которых попадут в главную камеру $\bar{C_{\af}}$.
+К соседним камерам $\bar{C_{\af}^{(l)}}$ относятся те же элементы, но  с противоположным знаком  (Эти камеры связаны с главной простыми отражениями $s_{\alpha _{l}}$, так что противоположные знаки $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$ здесь естественны).
+Можно повторить эту процедуру и получить дополнительные сингулярные веса в любой камере Вейля $\bar{C_{\af}^{(m)}}$, причем эти веса будут иметь знаки, противоположные знакам в соседних камерах.
+То есть не меняя элемент $\Phi _{\gf}^{\left( \mu \right) }$ его можно представить в виде суммы
 \begin{equation}
@@
 \end{equation}
-where the weight $\widetilde{\mu }=\sum m_{k}\omega _{\sfr}^{k}$ was
-defined above. The decomposition (\ref{singular final}) provides the
-possibility to apply the factor $\left( \prod_{\beta \in \Delta _{\sfr%
-}^{+}}(1-e^{-\beta })\right) ^{-1}$ to each summand of the singular element $%
-\Phi _{\gf}^{\left( \mu \right) }$ separately because the sets of
-weights from different Weyl summands do not intersect. Taking into account
-the isomorphism $\phi $ one can see that in the main Weyl chamber $\bar{C_{%
-\af}}$ the set of weights generated by the factor $\left( \prod_{\beta
-\in \Delta _{\sfr}^{+}}(1-e^{-\beta })\right) ^{-1}$ is isomorphic to
-the weight diagram $\mathcal{N}_{\sfr}^{\widetilde{\mu }}$ of the $\frak{%
-s}$-module $L_{\sfr}^{\widetilde{\mu }}$. Now one can restrict
-relation (\ref{singular main-3}) to $\bar{C_{\af}}$ and obtain the main
-result:
+где вес $\widetilde{\mu }=\sum m_{k}\omega _{\sfr}^{k}$ был введен выше.
+Разложение (\ref{singular final}) позволяет применить множитель $\left( \prod_{\beta \in \Delta _{\sfr}^{+}}(1-e^{-\beta })\right) ^{-1}$ к каждому слагаемому сингулярного элемента  $\Phi _{\gf}^{\left( \mu \right)}$ по отдельности, так как множества весов различных слагаемых Вейля не пересекаются.
+Воспользовавшись изоморфизмом  $\phi $ мы видим, что в главной камере Вейля  $\bar{C_{\af}}$ множество весов, порожденное действием $\left( \prod_{\beta\in \Delta _{\sfr}^{+}}(1-e^{-\beta })\right)^{-1}$ изоморфно весовой диаграмме  $\mathcal{N}_{\sfr}^{\widetilde{\mu }}$  модуля  $L_{\sfr}^{\widetilde{\mu }}$ алгебры $\sfr$.
+Теперь можно ограничить равенство (\ref{singular main-3}) на главную камеру Вейля $\bar{C_{\af}}$ и получить основной результат этого раздела:
 \begin{Prop}
@@
 \end{equation}
-Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
-highest weights in the decomposition. The multiplicity $M_{\left( \sfr%
-\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
-}\in \mathcal{N}_{\sfr}^{\widetilde{\mu }}$ defines the branching
-coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
--\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
+Любой вес с ненулевой кратностью, входящий в правую часть равенства, равен одному из старших весов в разложении. Кратность $M_{\left( \sfr
+\right) \widetilde{\nu }}^{\widetilde{\mu }}$ веса  $\widetilde{\nu}\in \mathcal{N}_{\sfr}^{\widetilde{\mu }}$ определяет коэффициент ветвления  $b_{\nu }^{(\mu )}$ для старшего веса $\nu =\left( \mu-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
 \[
@@
 
-\section{Examples}
+\section{Примеры}
 \label{sec:examples}
 \begin{example}
-  Consider the Lie algebra $A_{2} =\bf{sl}(3)$ and branching of its irreducible module $L^{[3,2]}_{A_{2}}$ with respect to the reductive subalgebra $A_{1}\oplus u(1)$.
-The root system  $\Delta _{\af}= \Delta_{A_{1}\oplus u(1)}$ contains the simple root of $\alpha_1=e_1-e_2$ of $A_{2}$.
-The singular element $\Psi^{[3,2]}_{\af}$ is decomposed into a sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules.
-Branching coefficients $b_{\nu }^{[ 3,2 ] }$ coincide with weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module (see Fig.
+\label{example-1}
+Рассмотрим алгебру Ли $A_{2} =\bf{sl}(3)$ и ветвление ее неприводимого модуля $L^{[3,2]}_{A_{2}}$ по отношению к редуктивной подалгебре $A_{1}\oplus u(1)$.
+Корневая система  $\Delta _{\af}= \Delta_{A_{1}\oplus u(1)}$ содержит простой корень $\alpha_1=e_1-e_2$ алгебры $A_{2}$.
+Сингулярный элемент $\Psi^{[3,2]}_{\af}$ раскладывается в сумму образов сингулярных элементов  модулей алгебры $A_{1}\oplus A_{1}$.
+Коэффициенты ветвления $b_{\nu }^{[ 3,2 ] }$ совпадают с кратностями весов модуля $L^{[3,2]}_{A_{1}\oplus A_{1}}$ (см.
+Рисунок.
 \ref{fig:a2_splint}).
@@
   }
-  \caption{Weyl group orbit (dotted) producing singular element of $L^{[3,2]}_{A_{2}}$ and its decomposition into the sum of splint images of singular elements of modules  $L^{[3,2]}_{A_{1}\oplus A_{1}}$ (dashed).
-Weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}
+  \caption{Орбита группы Вейля (точечный контур), соответствующая сингулярному элементу $L^{[3,2]}_{A_{2}}$ и ее разложение в сумму образов сингулряных элементов модулей  $L^{[3,2]}_{A_{1}\oplus A_{1}}$ (пунктирные контуры).
+Кратности весов модуля $L^{[3,2]}_{A_{1}\oplus A_{1}}$ совпадают  с коэффициентами ветвления для редукции $L^{[3,2]}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}
 
@@
 \begin{example}
-  For the Lie algebra $B_{2}= \bf{so}(5)$ branching of its irreducible module $L^{[3,2]}$ into  modules of a reductive subalgebra $A_{1}\oplus u(1)$ with the root system spanned by the first simple root $\alpha_1=e_1-e_2$ of $B_{2}$.
-Singular element of $\Psi^{[3,2]}_{B_{2}}$ is decomposed into the sum of splint images of singular elements of $A_{2}$-modules and branching coefficients coincide with weight multiplicities of $A_{2}$-module (see Fig.
-\ref{fig:b2_splint}).
+\label{example-2}
+ Рассмотрим алгебру Ли $B_{2}= \bf{so}(5)$ и редукцию ее неприводимого модуля  $L^{[3,2]}$ на модули редуктивной подалгебры  $A_{1}\oplus u(1)$ с корневой системой, натянутой на первый простой корень $\alpha_1=e_1-e_2$ алгебры $B_{2}$.
+Сингулярный элемент $\Psi^{[3,2]}_{B_{2}}$ раскладывается в сумму образов сингулярных элементов модулей $A_{2}$ и коэффициенты ветвления совпадают с кратностями весов в модуле $A_{2}$ (см.
+Рисунок \ref{fig:b2_splint}).
 
@@
    \includegraphics[width=65mm]{b2-a2-a1}
-  \caption{Weights of the $B_{2}$-module $L^{[3,2]}$ are indicated by dots in the left picture (their multiplicities are also indicated).
-Contour of the singular element is shown by dotted line.
-The right picture presents the decomposition of  $\Psi_{B_{2}}(L^{[3,2]}_{B_{2}})$-singular element into the sum of splint images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ (dashed).
-Weight multiplicities of $L^{[3,2]}_{A_{2}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{B_{2}\downarrow A_{1}\oplus u(1)}$.}
+  \caption{Веса модуля  $L^{[3,2]}$ алгебры  $B_{2}$ показаны точками на левом рисунке (кратности подписаны).
+Контур сингулярного элемента показан коротким пунктиром.
+На правом рисунке представлено разложение сингулярного элемента $\Psi_{B_{2}}(L^{[3,2]}_{B_{2}})$ в сумму образов сингулярных элементов $\Psi_{A_{2}}(L^{[3,2]})$ (длинный пунктир).
+Кратности весов модуля $L^{[3,2]}_{A_{2}}$ совпадают с коэффициентами ветвления для редукции $L^{[3,2]}_{B_{2}\downarrow A_{1}\oplus u(1)}$.}
 
@@
 \begin{example}
-   Lie algebra $G_{2}$ has a regular subalgebra $A_{2}$ with root system $\Delta_{\af}=\Delta_{A_{2}}$ containing the $G_{2}$ long roots.
-Consider branching of an irreducible module $L_{G_{2}}^{(3,2)}$ into the $A_{2}$-modules.
-Singular element $\Psi_{G_{2}}(L^{[3,2]})$ is decomposed into the sum of splint images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ and the corresponding branching coefficients coincide with weight multiplicities of $L^{[3,2]}_{A_{2}}$-module (see Fig.
-\ref{fig:g2_splint}).
+  Алгебра Ли  $G_{2}$ содержит регулярную подалгебры  $A_{2}$ с корневой системой $\Delta_{\af}=\Delta_{A_{2}}$, содержащей длинные корни $G_{2}$.
+Рассмотрим ветвление неприводимого модуля $L_{G_{2}}^{(3,2)}$ на модули подалгебры $A_{2}$.
+Сингулярный элемент $\Psi_{G_{2}}(L^{[3,2]})$ раскладывается в сумму образов сингулярных элементов  $\Psi_{A_{2}}(L^{[3,2]})$ и коэффициенты ветвления совпадают с кратностями весов модуля $L^{[3,2]}_{A_{2}}$ (см.
+Рисунок \ref{fig:g2_splint}).
 
@@
 
-  \caption{Weyl group orbit (dotted) for the singular element $\Psi_{G_{2}}(L^{[3,2]})$ and its decomposition into the sum of splint images of singular elements of $A_{2}$-modules (dashed).
-Weight multiplicities of $L^{[3,2]}_{A_{2}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{G_{2}\downarrow A_{2}}$.}
+  \caption{Орбита группы Вейля  (короткий пунктир) для сингулярного элемента  $\Psi_{G_{2}}(L^{[3,2]})$ и его разложение в сумму образов сингулярных элементов модулей алгебры $A_{2}$ (длинный пунктир).
+Кратности весов модуля $L^{[3,2]}_{A_{2}}$ совпадают с коэффициентами ветвления для редукции $L^{[3,2]}_{G_{2}\downarrow A_{2}}$.}
 
@@
 
-\section{Conclusions}
+\section{Заключение}
 
-\label{sec:conclusions}It is explicitly demonstrated that splint
-presents a very effective tool to find branching coefficients. In
-particular injective splints provide a possibility to reduce
-branching rules calculations for highest weight modules to a
-determination of weight multiplicities for a module with the same
-Dynkin labels referred to the Lie algebra $\mathfrak{s}$. This algebra
-$\mathfrak{s}$ must not be a subalgebra in the initial $\gf$ , it
-has the same rank $r_{\mathfrak{s}}=r$\ , but obviously less
-"complicated" than $\gf$ -- only a subset of the initial root system is involved in the second stem $\Delta_{\mathfrak{s}}$.
+\label{sec:conclusions}
+Мы продемонстрировали, что сплинт представляет собой очень эффективный инструмент для вычисления коэффициентов ветвления.
+В частности, инъективные сплинты дают возможность свести определение правил ветвления модулей старшего веса к вычислению кратностей весов для модуля с теми же индексами Дынкина алгебры Ли $\mathfrak{s}$.
+Эта алгебра $\mathfrak{s}$ не обязательно является подалгеброй в  $\gf$ , ее ранг $r_{\mathfrak{s}}=r$ совпадает с рангом $\gf$, но сома она ``проще'' чем  $\gf$, так как только подмножество корней корневой системы включено во второй ``стебель''  $\Delta_{\mathfrak{s}}$.
 
-It is significant that for the injections $D_{r}\hookrightarrow B_{r}$ , $%
-D_{r}\hookrightarrow C_{r}$ and $A_{r-1}\oplus u\left( 1\right) \hookrightarrow A_{r}$ splint technique shows
-transparently Gelfand-Tzeytlin rules for branching:  the reduction is
-multiplicity free (all nonzero
-branching coefficients are equal to 1). Here it is an immediate consequence of the
-structure of the second stem being a direct sum of $A_{1}$
-algebras and the fact that the corresponding module
-$L_{\sfr}^{\mu }$ is irreducible.
+Важно отметить, что для вложений  $D_{r}\hookrightarrow B_{r}$ , $D_{r}\hookrightarrow C_{r}$ и $A_{r-1}\oplus u\left( 1\right) \hookrightarrow A_{r}$ техника сплинта ведет к появлению правил ветвления Гельфанда-Цейтлина: редукция свободна от множественности (все ненулевые коэффициенты ветвления равны 1).
+В данном случае это немедленное следствие структуры второго стебля, который является прямой суммой алгебр $A_{1}$, и того факта, что соответствующий модуль $L_{\sfr}^{\mu }$ неприводим.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Appendix}
+\section{Приложение}
+\label{sec:appendix}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Покажем, что для инъективного сплинта классической алгебры Ли выполняется следующее свойство:
+\begin{Prop}
+Пусть $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ -- инъективный сплинт с разложением множества простых корней  $S=S_{\frak{c}}\cup S_{\frak{d}}$, где $S_{\frak{c}}=S\cap S_{\af}$ и $S_{\frak{d}}=S\cap S_{\sfr}$.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Let us demonstrate that for injective splints of classical Lie
-algebras the following property is valid:
-\begin{Prop}
-Let $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ be an
-injective
-splint with the decomposition of simple roots $S=S_{\frak{c}}\cup S_{\frak{d}%
-}$ with $S_{\frak{c}}=S\cap S_{\af}$ and $S_{\frak{d}}=S\cap S_{\sfr%
-}$.
+Тогда для каждого простого корня  $\beta \in S_{\sfr}$ существует пара корней  ( $\alpha $ ,$\beta ^{\prime }$), где $\alpha \in $ $S_{\frak{c}},\beta ^{\prime }\in S_{\sfr}$, такая, что $\alpha =\beta-\beta ^{\prime }$
 \end{Prop}
-Thus for any simple root $\beta \in S_{\sfr}$ there exists the
-pair of
-roots ( $\alpha $ ,$\beta ^{\prime }$) with $\alpha \in $ $S_{\frak{c}%
-},\beta ^{\prime }\in S_{\sfr}$ such that $\alpha =\beta
--\beta ^{\prime }$
-
 \begin{itemize}
 \item
-Type 1. $\Delta _{G_{2}}\approx (\Delta _{A_{2}},\Delta
+Тип 1. $\Delta _{G_{2}}\approx (\Delta _{A_{2}},\Delta
 _{A_{2}}).$
@@
   }
-  \caption{Positive roots of $G_{2}$ and formation of singular element $\Phi^{(0)}_{\mathfrak{s}}$ in the main Weyl chamber of $\af=A_{2}$.}
+  \caption{Положительные корни $G_{2}$ и образование сингулярного элемента $\Phi^{(0)}_{\mathfrak{s}}$ в главной камере Вейля алгебры $\af=A_{2}$.}
+  \label{fig:g2-roots}
 \end{figure}
-Here both stems are metric and the corresponding root systems are
-equivalent. In Figure 4 a part of the singular element $\Phi
-_{G_{2}}^{\left( 0\right) }$ is presented. The boundaries of $\bar{C_{\frak{a%
-}}}$ are the dashed lines starting at the center of the singular
-element. It
-contains the edge $\lambda _{2}=-\alpha _{2}=-\beta _{2}$ and the roots $%
--\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3}$ and $ -\beta _{3}$
-($\beta _{3}$ is indicated as $\beta _{l}$). For the root $\beta
-_{1}$ the necessary pair
-is  $(\alpha _{1}, \beta _{2})$: $\alpha _{1}=\beta _{1}-\beta _{2}$. The $%
-\lambda _{2,3}^{\sfr}=\beta _{3}$ edge is equal to $\lambda _{1}^{\frak{s%
-}}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ and $m_{1}$ index
-is aquired by the $\sfr$-module that also inherit the second
-index $m_{2}$. In this particular
-case they are $m_{1}=m_{2}=0$. The general case with the initial module $%
-L^{\mu }$ and $\mu =m_{1}\omega _{1}+m_{2}\omega _{2}$ can be
-treated in the same way: one finds an edge $\lambda _{2}=-\left(
-m_{2}+1\right) \beta _{2}$ and put $\lambda
-_{1}^{\sfr}=-\left( m_{1}+1\right) \beta _{1}$, its end
-belongs to the boundary $\bar{C_{\af}}$. The reflection
-$s_{\beta
-_{2}} $ sends $\beta _{1}$ to $\beta _{3}$ and the corresponding edge 
-$\lambda _{2,3}^{\sfr}=-\left( m_{1}+1\right) \beta _{3}$ has
-the length $\left( m_{1}+1\right) $. Now consider $\lambda _{1}^{\sfr}$ (or
-$\lambda _{2,3}^{\sfr} $) and $\lambda _{1,3}^{\sfr}$ (or
-$\lambda _{2,3,1}^{\sfr}$) edges to find that they belong to
-the boundary $\bar{C_{\af}}$ and the Weyl symmetry predicts
-that $\lambda _{1,3}^{\sfr}=-\left( m_{2}+1\right)
-\beta _{3}$ ($\lambda _{2,3,1}^{\sfr}=-\left( m_{2}+1\right) \beta _{1}$%
-) . Finally the edge $\lambda _{1,3,2}^{\sfr}=-\left(
-m_{1}+1\right) \beta _{2}$ closes the polytope. Its vertices
-correspond to weights of the singular
-element $\Phi _{\sfr}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{%
-\sfr}}\varepsilon \left( w\right) e^{w\circ \left(
-\widetilde{\mu }+\rho
-_{\sfr}\right) }$ of the module $L_{\sfr}^{\left( \widetilde{\mu }%
-\right) }$ with $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}%
-\widetilde{\omega }_{2}$. Notice that in this case the sign
-factors can be obtained directly in the initial weight system as
-far as the stem is metric.
+Здесь оба стебля метрические и соответствующие корневые системы эквивалентны.
+На Рисунке \ref{fig:g2-roots} показана часть сингулярного элемента $\Phi_{G_{2}}^{\left( 0\right) }$.
+Границы  $\bar{C_{\frak{a}}}$ изображены пунктирными линиями, начинающимися в центре сингулярного элемента.
+Они содержат ребро $\lambda _{2}=-\alpha _{2}=-\beta _{2}$ и корни $-\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3}$ и $ -\beta _{3}$
+($\beta _{3}$ показан, как $\beta _{l}$).
+Для корня $\beta_{1}$ искомая пара -- это  $(\alpha _{1}, \beta _{2})$: $\alpha _{1}=\beta _{1}-\beta _{2}$.
+Ребро $\lambda _{2,3}^{\sfr}=\beta _{3}$ равно  $\lambda _{1}^{\frak{s}}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ и  $\sfr$-модуль получает индекс Дынкина $m_{1}$  и наследует второй индекс $m_{2}$.
+В этом частном случае  $m_{1}=m_{2}=0$.
+Общий случай с начальным модулем $L^{\mu }$, где $\mu =m_{1}\omega _{1}+m_{2}\omega _{2}$, может быть рассмотрен аналогично: необходимо найти ребро $\lambda _{2}=-\left(
+m_{2}+1\right) \beta _{2}$ и положить $\lambda_{1}^{\sfr}=-\left( m_{1}+1\right) \beta _{1}$, его конец принадлежит границе $\bar{C_{\af}}$.
+Отражение $s_{\beta_{2}} $ переводит $\beta _{1}$ в $\beta _{3}$ и соответствующее ребро
+$\lambda _{2,3}^{\sfr}=-\left( m_{1}+1\right) \beta _{3}$ имеет длину $\left( m_{1}+1\right) $.
+Теперь рассмотрим ребра $\lambda _{1}^{\sfr}$ (или $\lambda _{2,3}^{\sfr} $) и $\lambda _{1,3}^{\sfr}$ (или $\lambda _{2,3,1}^{\sfr}$), и обнаружим, что они принадлежат границе  $\bar{C_{\af}}$ и Вейлевская симметрия предсказывает, что $\lambda _{1,3}^{\sfr}=-\left( m_{2}+1\right)\beta _{3}$ ($\lambda _{2,3,1}^{\sfr}=-\left( m_{2}+1\right) \beta _{1}$) .
+Наконец, ребро $\lambda _{1,3,2}^{\sfr}=-\left(m_{1}+1\right) \beta _{2}$ замыкает многогранник.
+Его вершины соответствуют весам сингулярного элемента $\Phi _{\sfr}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{\sfr}}\varepsilon \left( w\right) e^{w\circ \left(
+\widetilde{\mu }+\rho_{\sfr}\right) }$ модуля $L_{\sfr}^{\left( \widetilde{\mu }\right) }$, где $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}\widetilde{\omega }_{2}$.
+Заметим, что в этом случае знаковые множители можно получить прямо в первоначальной весовой системе, так как стебли метрические.
 \item
-Type 1. $\Delta _{F_{4}}\approx (\Delta _{D_{4}},\Delta
-_{D_{4}}).$
+Тип 1. $\Delta _{F_{4}}\approx (\Delta _{D_{4}},\Delta_{D_{4}}).$
 
-Both stems are metric here and the corresponding root systems are
-equivalent. The system $\Delta _{D_{4}}$ of the subalgebra
-$\frak{a=}D_{4}$ is formed by the set $\left\{ \pm e_{i}\pm
-e_{j}\right\} _{|i,j=1,\ldots 4,\; i\neq j}.$ The simple roots
-$S_{\frak{c}}$ are $\left\{ e_{2}-e_{3},e_{3}-e_{4}\right\} $ and
-$S_{\frak{d}}=\left\{ e_{4},\frac{1}{2}\left(
-e_{1}-e_{2}-e_{3}-e_{4}\right) \right\} $.
-For a module $L^{\mu }$ with $\mu =\sum m_{k}\omega _{k}$ consider the edge $%
-\lambda _{3}=-\left( m_{3}+1\right) e_{4}=-\left( m_{3}+1\right)
+Оба стебля здесь метрические и соответствующие корневые системы эквивалентны.
+Система $\Delta _{D_{4}}$ подалгебры $\frak{a=}D_{4}$ формируется множеством $\left\{ \pm e_{i}\pm e_{j}\right\} _{|i,j=1,\ldots 4,\; i\neq j}.$ Простые корни $S_{\frak{c}}$ -- это $\left\{e_{2}-e_{3},e_{3}-e_{4}\right\} $ и $S_{\frak{d}}=\left\{ e_{4},\frac{1}{2}\left(e_{1}-e_{2}-e_{3}-e_{4}\right) \right\} $.
+Для модуля $L^{\mu }$, где $\mu =\sum m_{k}\omega _{k}$ рассмотрим ребро $\lambda _{3}=-\left( m_{3}+1\right) e_{4}=-\left( m_{3}+1\right)
 \beta _{3}$.
- Compose an edge $\lambda _{2}^{\sfr}=-\left( \widetilde{m}%
-_{2}+1\right) \beta _{2}$. The necessary pair of roots is $\left(
-\alpha
-_{2}=e_{3}-e_{4},\beta _{3}\right) $. The intersection of $\lambda _{2}^{%
-\sfr}$ with the $\alpha _{2}$-boundary of
-$\bar{C_{\af}}$ fixes
-its length to be $\lambda _{2}^{\sfr}=-\left( m_{2}+1\right) \beta _{2}$%
-\ and the length of the edge $\lambda _{3,2}^{\sfr}$ is equal
-to that of
-$\lambda _{2}^{\sfr}$. Next consider the edge $\lambda _{2}^{\sfr%
-}=-\left( m_{2}+1\right) \beta _{2}$ and the pair $\left( \alpha
-_{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $. The length of  
-$\lambda _{1}^{\sfr}$ becomes equal to $\lambda
-_{1}^{\sfr}=-\left( m_{1}+1\right) \beta _{1}$. Proceed further till the closure of the polytope. 
-The edges looking along the roots of the $\alpha_4$-type, $\alpha _{4}=\beta
-_{4}=$ $\frac{1}{2}\left( e_{1}-e_{2}-e_{3}-e_{4}\right) $, are
-treated similarly and finally the singular element $\Phi
-_{\sfr}^{\left( \widetilde{\mu }\right) }=\sum_{w\in
-W_{\sfr}}\varepsilon \left( w\right) e^{w\circ \left(
-\widetilde{\mu }+\rho _{\sfr}\right) }$ for the module
-$L_{\sfr}^{\left( \widetilde{\mu }\right) }$ with
-$\widetilde{\mu }=\sum m_{k}\widetilde{\omega }_{k}$ is formed in
-$\bar{C_{\af}}$.
+Построим ребро $\lambda _{2}^{\sfr}=-\left( \widetilde{m}_{2}+1\right) \beta _{2}$.
+Искомая пара корней -- это $\left(\alpha_{2}=e_{3}-e_{4},\beta _{3}\right) $.
+Пересечение  $\lambda _{2}^{\sfr}$ с  $\alpha _{2}$-границей камеры $\bar{C_{\af}}$ определяет длину $\lambda _{2}^{\sfr}=-\left( m_{2}+1\right) \beta _{2}$ и длины ребра $\lambda _{3,2}^{\sfr}$ равна длине $\lambda _{2}^{\sfr}$.
+Далее рассмотрим ребро $\lambda _{2}^{\sfr}=-\left( m_{2}+1\right) \beta _{2}$ и пару $\left( \alpha_{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $.
+Длина   $\lambda _{1}^{\sfr}$ становится равной $\lambda_{1}^{\sfr}=-\left( m_{1}+1\right) \beta _{1}$.
+Продолжаем эту процедуру, пока не замкнем многогранник.
+Ребра, направленные вдоль корней типа $\alpha_4$, $\alpha _{4}=\beta_{4}=$ $\frac{1}{2}\left( e_{1}-e_{2}-e_{3}-e_{4}\right) $, рассматриваются аналогично и, наконец, сингулярный элемент $\Phi_{\sfr}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{\sfr}}\varepsilon \left( w\right) e^{w\circ \left(\widetilde{\mu }+\rho _{\sfr}\right) }$ для модуля $L_{\sfr}^{\left( \widetilde{\mu }\right) }$, где
+$\widetilde{\mu }=\sum m_{k}\widetilde{\omega }_{k}$ возникает в камере $\bar{C_{\af}}$.
 \item
-Type 2. $\Delta _{B_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
-^{r}A_{1}}). $
+Тип 2. $\Delta _{B_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus^{r}A_{1}}). $
 
-Both stems are metric. An injection is fixed by the stem $\Delta
-_{D_{r}}$ simple roots $S_{\af}=\left\{
-e_{1}-e_{2},e_{2}-e_{3},\ldots
-,e_{r-1}-e_{r},e_{r-1}+e_{r}\right\} $. The second stem
-corresponds to a
-direct sum of algebras $A_{1}$ with the simple roots $S_{\sfr%
-}=\left\{ e_{1},e_{2},\ldots ,e_{r-1},e_{r}\right\} $. Consider the edge $%
-\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ (here $\beta
-_{r}=e_{r}$) and $\lambda _{r-1}=-\left(
-\widetilde{m}_{r-1}+1\right) \beta _{r-1}$
-attached to it (here $\beta _{r-1}=e_{r-1}$). The corresponding pair is $%
-\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta _{r-1}=e_{r-1}\right) $.
- The intersection condition fixes the second edge to be $\lambda
-_{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ , it is orthogonal
-to $\beta _{r}$ so the opposite edge has the same length. The
-Dynkin index $m_{r-1}$ now refers
-also to the\ simple root $\beta _{r-1}$. Next consider the obtained edge $%
-\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and $\lambda
-_{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$ to
-fix the index $\widetilde{m}_{r-2}=m_{r-2}$ and the edge
-$\lambda _{r-2}=-\left( m_{r-2}+1\right) \beta _{r-2}$ and so on
-till all the pairs of edges are properly fixed. Finally in
-$\bar{C}_{D_{r}}$ the element $\Phi _{\oplus ^{r}A_{1}}^{\left(
-\widetilde{\mu }\right) }=\sum_{w\in W_{\oplus
-^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+%
-\frac{1}{2}\sum e_{k}\right) }$ can be constructed for the module
-$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
+Оба стебля метрические.
+Вложения дается стеблем $\Delta_{D_{r}}$ с простыми корнями $S_{\af}=\left\{e_{1}-e_{2},e_{2}-e_{3},\ldots,e_{r-1}-e_{r},e_{r-1}+e_{r}\right\} $.
+Второй стебель соответствует прямой сумме алгебр $A_{1}$ с простыми корнями $S_{\sfr}=\left\{ e_{1},e_{2},\ldots ,e_{r-1},e_{r}\right\} $.
+Рассмотрим ребро $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ (здесь $\beta_{r}=e_{r}$) и ребро $\lambda _{r-1}=-\left(\widetilde{m}_{r-1}+1\right) \beta _{r-1}$, присоединенное к нему (здесь $\beta_{r-1}=e_{r-1}$).
+Соответствующая пара корней -- это $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta _{r-1}=e_{r-1}\right) $.
+Из условия пересечения определяется второе ребро $\lambda_{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ , оно ортогонально к  $\beta _{r}$, так что противоположное ребро имеет ту же длину.
+Индекс Дынкина $m_{r-1}$ теперь связан также с простым корнем $\beta _{r-1}$.
+Далее рассмотрим полученное ребро $\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ и $\lambda_{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$, чтобы определить индекс $\widetilde{m}_{r-2}=m_{r-2}$ и ребро $\lambda _{r-2}=-\left( m_{r-2}+1\right) \beta _{r-2}$, и так далее, пока все пары ребер не будут определены.
+Наконец, в $\bar{C}_{D_{r}}$ элемент $\Phi _{\oplus ^{r}A_{1}}^{\left(\widetilde{\mu }\right) }=\sum_{w\in W_{\oplus^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+\frac{1}{2}\sum e_{k}\right) }$ может быть построен для модуля
+$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$, где
 $\widetilde{\mu }=\sum m_{k}\frac{1}{2}e_{k}$.
@@
 \item
-Type 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
-^{r}A_{1}}). $
+Тип 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus^{r}A_{1}}). $
 
-The situation in this case is eqivalent to the previous one and
-the additional edges are constructed similarly.
+Ситуация в этом случае эквивалентна предыдущему и дополнительные ребра строятся аналогично.
+
 \item
-Type 3 $\Delta _{A_{r}}\approx (\Delta _{A_{r-1}\oplus
-u_{1}},\Delta _{\oplus ^{r}A_{1}}).$
+Тип 3 $\Delta _{A_{r}}\approx (\Delta _{A_{r-1}\oplus u_{1}},\Delta _{\oplus ^{r}A_{1}}).$
 
-Here only the first stem is metric and it fixes the injection with
-simple roots $S_{\af}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots
-,e_{r-1}-e_{r}\right\} $. The second stem corresponding to a direct sum of $%
-r$ copies of $A_{1}$ has the simple roots $S_{\sfr}=\left\{
-e_{1}-e_{r+1},e_{2}-e_{r+1},\ldots ,e_{r}-e_{r+1}\right\} $.
-Consider the edge $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$
-with $\beta
-_{r}=e_{r}-e_{r+1}$ and $\lambda _{r-1}=-\left( \widetilde{m}%
-_{r-1}+1\right) \beta _{r-1}$ \ with $\beta
-_{r-1}=e_{r-1}-e_{r+1}$ attached to it. Then the corresponding
-pair is $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta
-_{r-1}=e_{r-1}-e_{r+1}\right)$. The intersection with the
-boundary of $\bar{C}_{A_{r-1}}$ orthogonal to $\alpha _{r-1}$
-fixes the second edge to be $\lambda _{r-1}=-\left(
-m_{r-1}+1\right) \beta _{r-1}$. The Dynkin index $m_{r-1}$ is to
-be used for the fundamental weight  $\omega _{r-1}.$ The\
-reflection $s_{\beta _{r}}$ sends $\lambda _{r-1}=-\left(
-m_{r-1}+1\right) \beta _{r-1}$ to $\lambda _{r,r-1}=-\left(
-m_{r-1}+1\right) \beta _{r-1}.$ Next consider the obtained edge
-$\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ and
-$\lambda _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$
-with $\beta _{r-2}=e_{r-2}-e_{r+1} $ to obtain the index
-$\widetilde{m}_{r-2}=m_{r-2}$ and the edge $\lambda _{r-2}=-\left(
-m_{r-2}+1\right) \beta _{r-2}$ and so on till all the pairs of
-edges are properly fixed. Finally in $\bar{C}_{D_{r}}$ the element
-$\Phi _{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right)
-}=\sum_{w\in W_{\oplus
-^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+%
-\widetilde{\rho }\right) }$ can be constructed for the module
-$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$ with
-$\widetilde{\mu }=\sum m_{k}\beta _{k}.$ The simplest case
-$\Delta _{A_{2}}\approx (\Delta _{A_{1}\oplus u_{1}},\Delta
-_{A_{1}\oplus A_{1}})$ is presented in Example 4.1 and Figure 1.
+Здесь только первый стебель метрический и он определяет вложение с простыми корнями  $S_{\af}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots ,e_{r-1}-e_{r}\right\} $.
+Второй стебель, соответствующий прямой сумме  $r$ копий алгебры $A_{1}$, имеет простые корни $S_{\sfr}=\left\{
+e_{1}-e_{r+1},e_{2}-e_{r+1},\ldots ,e_{r}-e_{r+1}\right\} $. Рассмотрим ребро $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ с $\beta
+_{r}=e_{r}-e_{r+1}$ и $\lambda _{r-1}=-\left( \widetilde{m}_{r-1}+1\right) \beta _{r-1}$  с $\beta_{r-1}=e_{r-1}-e_{r+1}$ присоединенным к нему.
+Тогда соответствующая пара равна $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta_{r-1}=e_{r-1}-e_{r+1}\right)$.
+Пересечение с границей $\bar{C}_{A_{r-1}}$, ортогональной $\alpha _{r-1}$ определяет второе ребро $\lambda _{r-1}=-\left(m_{r-1}+1\right) \beta _{r-1}$.
+Индекс Дынкина $m_{r-1}$ должен использоваться для фундаментального веса  $\omega _{r-1}.$ Отражение  $s_{\beta _{r}}$ переводит $\lambda _{r-1}=-\left(m_{r-1}+1\right) \beta _{r-1}$ в $\lambda _{r,r-1}=-\left(m_{r-1}+1\right) \beta _{r-1}.$ Далее рассмотрим полученное ребро edge
+$\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ и $\lambda _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$ с  $\beta_{r-2}=e_{r-2}-e_{r+1} $ , чтобы получить индекс $\widetilde{m}_{r-2}=m_{r-2}$ и ребро $\lambda _{r-2}=-\left(m_{r-2}+1\right) \beta _{r-2}$, и так далее, пока не получим все пары ребер.
+Наконец, в  $\bar{C}_{D_{r}}$ элемент$\Phi _{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right)}=\sum_{w\in W_{\oplus^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+\widetilde{\rho }\right) }$ может быть построен для модуля $L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$, где $\widetilde{\mu }=\sum m_{k}\beta _{k}.$ Простейший случай $\Delta _{A_{2}}\approx (\Delta _{A_{1}\oplus u_{1}},\Delta_{A_{1}\oplus A_{1}})$ показан в примере \ref{example-1} и на Рисунке \ref{fig:a2_splint}.
 \item
-Type 3 $\Delta _{B_{2}}\approx (\Delta _{A_{1}},\Delta _{A_{2}}).$
+Тип 3 $\Delta _{B_{2}}\approx (\Delta _{A_{1}},\Delta _{A_{2}}).$
 
-This splint is illustrated in Example 4.1 and Figure 1, 
-$S_{A\_1}=\left\{ e_{1}-e_{2}\right\} $, $S_{A\_2}=\left\{
-e_{1},e_{2}\right\} $. The edge $\lambda _{\alpha _{2}}=\lambda
-_{\beta _{2}}=-\left( m_{2}+1\right) \beta _{2}$ is followed by
-$\lambda _{\beta _{1}}=-\left( \widetilde{m}_{1}+1\right) \beta
-_{1}$. Consider the pair $\left( \alpha
-_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right)$. The end of the edge
-$\lambda _{\beta _{1}}$ must indicate a weight
-invariant under the reflexion $s_{\alpha _{1}}$.  Its length is thus fixed: 
-$\lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$. In the
-coimage of
-the second stem, that is in the root system $\Delta_{A_{2}}$, the reflection 
-$s_{\beta _{2}}$ sends $\lambda _{\beta _{1}}=-\left(
-m_{1}+1\right) \beta
-_{1}$ to $\lambda _{2,3}$, thus the latter edge has the same length in $%
-\beta _{3}=e_{1}+e_{3}$, we have $\lambda _{2,3}=-\left(
-m_{1}+1\right)
-\beta _{3}$ with $\beta _{3}=e_{1}+e_{3}$. The irreducible $\sfr$%
--module has the highest weight $\widetilde{\mu }=m_{1}\widetilde{\omega }%
-_{1}+m_{2}\widetilde{\omega }_{2}$. In Figure 1 we see the
-details of these relations in a particular case where
-$L_{B_{2}}^{\left[ 3,2\right] }$ is reduced to a subalgebra
-$A_{1}\oplus u\left( 1\right) $ and the
-corresponding highest weights (with their multiplicities) form the diagram $%
-\mathcal{N}_{A_2}^{\left[ 3,2\right] }$ .
+Этот сплинт показан в примере \ref{example-2} и на Рисунке \ref{fig:b2_splint}, 
+$S_{A\_1}=\left\{ e_{1}-e_{2}\right\} $, $S_{A\_2}=\left\{e_{1},e_{2}\right\} $.
+Ребро $\lambda _{\alpha _{2}}=\lambda_{\beta _{2}}=-\left( m_{2}+1\right) \beta _{2}$ продолжается ребром $\lambda _{\beta _{1}}=-\left( \widetilde{m}_{1}+1\right) \beta_{1}$.
+Рассмотрим пару $\left(\alpha_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right)$.
+Конец ребра $\lambda _{\beta _{1}}$ должен указывать вес, инвариантный по отношению к отражению  $s_{\alpha _{1}}$.
+Его длина таким образом фиксирована: $\lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$ В кообразе второго стебля, то есть в корневой системе $\Delta_{A_{2}}$, отражение $s_{\beta _{2}}$ переводит $\lambda _{\beta _{1}}=-\left(m_{1}+1\right) \beta_{1}$ в $\lambda _{2,3}$, то есть это ребро имеет ту же длину в $\beta _{3}=e_{1}+e_{3}$, и $\lambda _{2,3}=-\left(m_{1}+1\right)\beta _{3}$ с $\beta_{3}=e_{1}+e_{3}$.
+Неприводимый  $\sfr$-модуль имеет старший вес $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}\widetilde{\omega }_{2}$.
+На Рисунке \ref{fig:b2_splint} мы видим детали этих соотношений и, в частности, случай, когда $L_{B_{2}}^{\left[ 3,2\right] }$ редуцируется на подалгебру $A_{1}\oplus u\left( 1\right) $ и соответствующие старшие веса (вместе с их кратностями) образуют диаграмму $\mathcal{N}_{A_2}^{\left[ 3,2\right] }$ .
 \end{itemize}

### 2011-12-09 AffineLieAlgebras/Thesis/4.tex
Chapter 2 is completely translated. Description of computational package is moved to the last chapter.
SLE translation started

--- 2011-09-28 AffineLieAlgebras/Thesis/3.tex
@@
-\chapter{Конформная теория поля}
-\label{cha:cft}
+\chapter{Практические приложения}
+\label{cha:applications}
 
-Подробное изложение \cite{difrancesco1997cft}.
+\section{Эволюция Шрамма-Левнера и алгебраические свойства предельного перехода от решеточных моделей к конформной теории поля}
+\label{sec:SLE}
 
-\section{Общие свойства}
-\label{sec:cft-general}
-Алгебра Вирасоро. Представления алгебры Вирасоро. Модулярная инвариантность.
+Эволюция Шрамма-Левнера появляется как скейлинговый предел интерфейсов в решеточных моделях в критической точке.
+Критическое поведение этих моделей можно описывать при помощи минимальных моделей конформной теории поля.
+Оказывается, что некоторые корреляционные функции в моделях конформной теории поля являются мартингалами по отношению к эволюции Шрамма-Левнера.
+В этой главе мы обобщаем эволюцию Шрамма-Левнера с дополнительным броуновским движением на группе Ли  $G$ на случай фактор-пространства $G/A$.
+Замет мы изучаем, как связано такое описание критического поведения с coset-моделями конформной теории поля.
+В качестве критерия согласованности мы используем тот факт, что минимальные модели могут быть реализованы как coset-модели при некотором выборе групп $G, A$.
 
-\section{Модели Весса-Зумино-Новикова-Виттена}
-\label{sec:wzw}
-Связь с аффинными алгебрами Ли.
-Конформные вложения и недиагональные модулярные инварианты.
+\section{Введение}
+Эволюция Шрамма-Левнера -- это стохастический процесс, который предложил Oded Schramm  \cite{schramm2000scaling} для описания скейлингового предела критических интерфейсов в двумерных статистических решеточных моделях.
+Этот подход к критическим системам дал много строгих результатов в теории критического поведения (см.
+обзоры  \cite{rohde2005basic}, \cite{bauer20062d}, \cite{Cardy:2005kh}).
+В разделе \ref{sec:schr-loewn-evol} мы приводим необходимые определения.
+
+Вероятностная мера, порожденная эволюцией Шрамма-Левнера на случайных кривых, конформно-инвариантна.
+Так как конформная теория поля представляет собой другой метод для изучения двумерных критических систем, естественно изучать ее связь с эволюцией Шрамма-Левнера.
+Такая связь изучалась, например, в работах \cite{bauer2004conformal,bauer2004cfts,bauer2003sle,bauer2002sle} (и многих других), но в основном для минимальных унитарных моделей.
+Идея состоит в рассмотрении определенных наблюдаемых в области с разрезом. Эта конструкция обсуждается в разделе \ref{sec:corr-betw-sle}.
+
+Более общие модели конформной теории поля обладают дополнительными симметриями.
+Например, алгебры Каца-Муди возникают в моделях Весса-Зумино-Новикова-Виттена.
+Чтобы реализовать такие симметрии при изучении эволюции Шрамма-Левнера нужно ввести дополнительное случайное блуждание на группе Ли \cite{bettelheim2005stochastic}, \cite{Rasmussen:2004xr}.
+Такое случайное блуждание определяется в разделе \ref{sec:sle-wzw-models}.
+Соответствие между мартингалами эволюции Шрамма-Левнера и корреляционными функциями в моделях Весса-Зумино-Новикова-Виттена изучалось в работе \cite{alekseev2010sle}.
+Аналогичное обобщение на $\mathbb{Z}(N)$-парафермионную модель было предложено в статьях \cite{santachiara2008sle,picco2008numerical}.
+
+Основная задача данной главы состоит в обобщении эволюции Шрамма-Левнера с дополнительным случайным блужданием на группе Ли на случай фактор-пространства  $G/A$ и в изучении связи с coset-конструкцией конформной теории поля.
+В разделе \ref{sec:coset-models} мы напоминаем некоторые детали coset-конструкции, вводим эволюцию Шрамма-Левнера на фактор-пространстве и связываем ее с конформной теорией поля.
+По аналогии со случаем моделей Весса-Зумино-Новикова-Виттена мы получаем систему алгебраических уравнений на оператор смены граничного условия из условия на мартингал.
+При помощи coset-конструкции можно реализовать минимальные и парафермионные модели конформной теории поля (см.
+\cite{difrancesco1997cft}), так что мы можем сравнить наши уравнения на оператор смены граничных условий с результатами работы \cite{santachiara2008sle}.
+
+В разделе  \ref{sec:conclusion} мы обсуждаем возможность сравнения классификации операторов смены граничных условий, следующей из свойства мартингалов с общей классификацией операторов смены граничных условий в граничной конформной теории поля, связанной с D-бранными решениями \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,Maldacena:2001ky,felder1999geometry,alekseev1999d}.
+
+\subsection{Эволюция Шрамма-Левнера}
+\label{sec:schr-loewn-evol}
+Рассмотрим модель Изинга на треугольной решетке в верхней полуплоскости (см.
+Рисунок \ref{fig:sle}).
+Наложим следующее граничное условие: потребуем, чтобы на одной половине границы все спины были направлены вверх, а на другой половине -- вниз.
+Тогда при любой конфигурации спинов на полуплоскости будет интерфейс, разделяющий два кластера и соединяющий точку ноль с бесконечностью (см.
+Рисунок \ref{fig:sle}).
+
+\begin{figure}[h]
+  \centering{
+    \includegraphics[height=50mm]{explore}
+    \caption{Интерфейс в модели Изинга на треугольной решетке}}
+  \label{fig:sle}
+\end{figure}
+Мы можем наложить условие существования части интерфейса конечной длины и рассмотреть конфигурации статистической модели, удовлетворяющие этому условию.
+Очевидно, такие конфигурации эквивалентны конфигурациям модели на области с разрезом вдоль интерфейса.
+
+Теперь рассмотрим непрерывный предел решеточной модели с (частью) интерфейса конечной длины.
+Интерфейсы в случайных конфигурациях модели сходятся к случайной кривой.
+Старая гипотеза \cite{Polyakov:1970xd} о конформной инвариантности в критической точке была недавно строго доказана для некоторых решеточных моделей (см.
+\cite{smirnov2007towards}, \cite{duminil2011conformal}).
+Мы предполагаем наличие конформной инвариантности в критической точке и рассматриваем верхнюю полуплоскость  $\mathbb{H}$ с разрезом вдоль критического интерфейса  $\gamma_{t}$.
+Такую область с разрезом мы обозначим через  $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$.
+Конформное отображение из $\mathbb{H}_{t}$ в $\mathbb{H}$ обозначим через $g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ (см.
+Рисунок \ref{fig:sle2}).
+
+\begin{figure}[h]
+  \centering{
+    \includegraphics[width=60mm]{loewner}
+    \caption{Конформное отображение $g_{t}(z):\mathbb{H}_{t}\to \mathbb{H}$.}}
+  \label{fig:sle2}
+\end{figure}
+
+In paper \cite{schramm2000scaling} it was shown that $g_{t}(z)$ satisfies stochastic differential equation 
+\begin{equation}
+\label{eq:19}
+  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
+\end{equation}
+where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
+
+Stochastic process which satisfies \eqref{eq:19} is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.
+For us it is more convenient to use map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
+\begin{equation}
+  \label{eq:20}
+       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}  
+\end{equation}
+Schramm-Loewner evolution provides conformally-invariant probability measure on curves $\gamma_{t}$ in $\mathbb{H}$.
+
+\subsection{SLE martingales and CFT correlation functions}
+\label{sec:corr-betw-sle}
+
+Now we can look at the observables in the presence of SLE trace.
+Expectation value of lattice observable $\mathcal{O}$ on the upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace $\gamma_{t}$ up to some time $t$ multiplied by the probability of this trajectory:
+\begin{equation*}
+  \prec \mathcal{O} \succ_{\mathbb{H}}=\mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=\sum_{\gamma_{t}} P\left[C_{\gamma_{t}}\right] \prec \mathcal{O} \succ_{\gamma_{t}}
+\end{equation*}
+Lattice observable  $\prec \mathcal{O} \succ_{\mathbb{H}}$ does not depend on $t$, hence $\prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale.
+
+In continuous limit lattice observable tends to CFT correlation function \cite{bauer2003sle,bauer2003conformal,bauer2002sle}.
+We need to take into account the change of boundary conditions on the tip of SLE trace and at the infinity, so the expression is
+\begin{equation}
+  \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
+  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}
+%% =
+%%   \frac{\left<^{g_{t}}
+%% \mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
+\label{eq:21}
+\end{equation}
+
+%% Here $\phi(z_{t})$ is a primary field corresponding to boundary condition changing operator.
+%% We've used the conformal map $g_{t}$ to get the expression on the whole plane in equation \eqref{eq:21}.
+
+We consider the theory with the boundary, so in principle we need to use boundary conformal field theory here and impose proper consistency conditions \cite{cardy1984conformal,cardy1989boundary,cardy1991bulk}.
+In the case of upper half-plane correlation functions of boundary CFT can be rewritten as the correlation functions of the theory on the whole plane but with doubled number of bulk fields.
+
+% Here we are interested mainly in properties of boundary condition changing operator $\phi$.
+
+We assume that $\mathcal{F}$ contains some set of primary fields $\varphi_{\lambda_{i}}$ with conformal weights $h_{\lambda_{i}}$.
+Since we work with boundary CFT we need to add bulk fields in conjugate points $\bar z_{i}$.
+For future use in WZNW models we denote the conformal weights of these duplicate fields by $h_{\lambda_{i}^{*}}$.
+Also we have boundary condition changing operators  $\phi$ at the tip of SLE trace and at the infinity.
+We use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite expression \eqref{eq:21} in the whole upper half plane:
+
+\begin{equation}
+  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
+  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
+  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
+  \label{eq:1}
+\end{equation}
+
+Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
+\begin{equation*}
+  -\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}.
+\end{equation*}
+For transformation of primary fields $\varphi_{\lambda_{i}}$ we have 
+\begin{equation}
+  \label{eq:2}
+  d\varphi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\varphi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\varphi_{\lambda_{i}}(w_{i}) 
+\end{equation}
+We denote generator of this transform by $\mathcal{G}_{i}$.
+
+Since $ \prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale, the expectation value of its increment during the evolution from $t$ to $t+dt$ is zero
+\begin{equation}
+  \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=    \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t+dt}}\right], \quad d\mathbb{E}\left[ \prec\mathcal{O}\succ_{\gamma_{t}}\right]=0
+\label{eq:22}
+\end{equation}
+Using Ito calculus we get the expression for the differential of $\mathcal{F}$:
+\begin{equation}
+d \mathcal{F}_{\mathbb{H}_{t}}= \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
+      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}=0
+\label{eq:8}
+\end{equation}
+We substitute formula \eqref{eq:2} and obtain the equation
+\begin{equation}
+  \left( \sum_{i}\left[-\frac{2h_{i}}{w_{i}^{2}} +\frac{2}{w_{i}}\partial_{w_{i}}\right]+\frac{\kappa}{2}\sum_{i,j}\partial_{w_{i}} \partial_{w_{j}}\right)\mathcal{F}(\left\{z_{i}\right\})=0
+\label{eq:23}
+\end{equation}
+
+For the correlation functions of secondary fields $L_{-n}\phi$ we have the equation 
+\begin{equation}
+\left< (L_{-n}\phi)(z) \varphi_{1}\dots \varphi_{N}\right>=\mathcal{L}_{-n}\left<\phi\varphi_{1}\dots\varphi_{N}\right>,
+\end{equation}
+ where $n\geq 1$ and
+\begin{equation*}
+  \mathcal{L}_{-n}=\sum_{i=1}^{N} \left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}} -\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right)
+\end{equation*}
+(See \cite{difrancesco1997cft}). So we can rewrite the differential equation \eqref{eq:23} as the algebraic equation on the field $\phi$ corresponding to boundary condition changing operator:
+\begin{equation}
+  \label{eq:24}
+   \left<\left([L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi\right)(0)\; \varphi_{\lambda_{1}}\dots \varphi_{\lambda_{{2N}}}\right>=0.
+\end{equation}
+In the case of minimal models the set of primary fields is finite and all the states are obtained through field-state correspondence \cite{belavin1984ics}, \cite{difrancesco1997cft}. 
+Equation \eqref{eq:24}  holds for arbitrary observable $\mathcal{O}$ and arbitrary primary fields $\varphi_{\lambda_{i}}$, so $\psi=[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ is level two null field and $\psi(0)\left|0\right>$ is level two null-state.
+There exist only two primary fields in minimal unitary models which give rise to Verma modules of Virasoro algebra with level two null-states.
+They are $\phi_{1,2}$ and $\phi_{2,1}$, so $\phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}$.
+
+\section{Wess-Zumino-Novikov-Witten models}
+\label{sec:sle-wzw-models}
+To generalize the analysis of previous section \ref{sec:corr-betw-sle} to non-minimal models we need to take into account extra symmetries.
+Wess-Zumino-Novikov-Witten models has Kac-Moody symmetry in addition to conformal invariance leading to the appearance of Virasoro algebra.
+At first we remind well-known properties of WZNW-models \cite{difrancesco1997cft} which are useful to study SLE martingales.
+
+ The action of WZNW model can be written in terms of map $g:\mathbb{C}\cup \{\infty\}\sim S^{2}\to G$ from complex plane with infinity or two-sphere to some (simple) Lie group $G$:
+\begin{multline}
+  S=-\frac{k}{8\pi}\int d^2x\; \mathcal{K} (g^{-1}\partial^{\mu}g, g^{-1} \partial_{\mu}g)  
+  - \frac{k }{24\pi^{2}} \int_{B}\epsilon_{ijk} \mathcal{K}\left(
+    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i},\left[
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
+      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right]\right) d^3y
+\end{multline}
+ Here $\mathcal{K}$ is Killing form on Lie algebra $\gf$ of Lie group $G$.
+The first term is just non-linear sigma-model and the second term is written using the continuation $\tilde{g}$ from two-sphere $S^{2}$ to three-dimensional manifold $B$ which has two-sphere as the boundary.
+Since this continuation is non-unique we get the requirement for $k$ to be integer.
+
+Conserved currents of this model have the following form:
+  \begin{eqnarray}
+    J(z)= -k \partial_zg g^{-1}
+    \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
+  \end{eqnarray}
+
+The model possesses gauge invariance under the transformations
+  $g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)$, 
+where $\Omega,\;\bar \Omega \in G$ are are independent. If we consider infinitesimal gauge transformation $\Omega=1+\omega$ we get Ward identities 
+  \begin{equation}
+    \label{eq:87}
+    \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
+    \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>,
+  \end{equation}
+which can be used to get operator product expansion for currents:
+ \begin{equation}
+   \label{eq:3}
+   J^{a}(z)J^{b}(w)\sim \frac{k\delta_{ab}}{(z-w)^{2}}+\sum_{c}i f_{abc}\frac{J^{c}}{z-w},
+ \end{equation}
+where $f_{abc}$ are the structure constants of Lie algebra $\gf$.
+
+Expanding the currents to modes
+$J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n $
+and using operator product expansion \eqref{eq:3} we get commutation relations of affine Lie algebra $\gfh$:
+\begin{equation*}
+ \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}.  
+\end{equation*}
+
+Conformal invariance of the model can  be seen from 
+Sugawara construction, which is a way to embed Virasoro algebra into the universal enveloping algebra of affine Lie algebra $\gfh$ ($Vir\subset U(\gfh)$):
+\begin{equation}
+  \label{eq:4}
+  L_n=\frac{1}{2(k+h^{\vee})}\left(\sum\limits_a\sum\limits_{m\leq -1}J^a_m J^a_{n-m}+\sum_{m\geq 0} J^{a}_{n-m}J^{a}_{m}\right), 
+\end{equation}
+ where $h^{\vee}$ is the dual Coxeter number of Lie algebra $\gf$. 
+Full chiral algebra of the model is semidirect product of affine and Virasoro algebra $\gfh \ltimes Vir$ with commutation relations 
+  \begin{equation}
+    \label{eq:92}
+    \begin{aligned}
+      \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0} \\
+      \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
+      \left[L_n,J^a_m\right]=-mJ^a_{n+m}
+    \end{aligned}
+  \end{equation}
+Here central charge $c$ of Virasoro algebra is given by expression
+\begin{equation}
+  \label{eq:25}
+  c=\frac{k\;\mathrm{dim}\gf}{k+h^{\vee}}
+\end{equation}
+There is infinite number of Virasoro primary fields, but they are organized into highest weight modules of affine Lie algebra $\gfh$. 
+Primary fields of full chiral algebra $\phi_{\lambda}$ are labeled by highest weights of  $\gfh$-modules. Here we see how Virasoro and affine Lie algebra generators act on primary fields:
+  \begin{equation*}
+    \begin{aligned}
+      & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>  \quad    J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
+      & L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^{\vee})}\left|\phi_{\lambda}\right>=h_{\lambda} \left|\phi_{\lambda}\right>,
+    \end{aligned}
+  \end{equation*}
+where $\rho$ is Weyl vector of $\gf$.
+
+Now we want to study Schramm-Loewner evolution in WZNW-models.
+Similarly to minimal models we consider observable
+\begin{equation*}
+  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
+  \frac{\left<\phi_{\Lambda}(z_{t}) \phi_{\lambda_1}(z_{1}) \dots \phi_{\lambda_n}(z_{n}) \phi_{\lambda^{*}_1}(\bar z_{1}) \dots \phi_{\lambda^{*}_n}(\bar z_{n})
+      \phi_{\Lambda^{*}}(\infty)\right>}{\left<\phi_{\Lambda}(z_{t})\phi_{\Lambda^{*}}(\infty)\right>}
+\end{equation*}
+Again we can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite it on the whole upper half-plane. 
+\begin{equation*}
+  \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
+  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{h_{\lambda^{*}_i}}
+  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
+\end{equation*}
+
+Under the evolution from $t$ to $t+dt$ first factor gives us $-\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}$.
+
+When we consider fields we need to add random gauge transformation (random motion in $G$) to stochastic evolution \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}. 
+For fields we have
+\begin{equation*}
+  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i}),
+\end{equation*}
+so additional term appears in the generator of field transformation. 
+\begin{equation}
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)
+\label{eq:18}
+\end{equation}
+Here $d\theta^{a}$ are the generators of $\mathrm{dim}\gf$-dimensional Brownian motion and $\mathbb{E}[d\theta^{a}d\theta^{b}]=\delta_{ab}dt$.
+We assume that $t^{a}$ is a basis of $\gf$ orthogonal with respect to Killing form $\mathcal{K}$, $\mathcal{K}(t^{a},t^{b})=\delta_{ab}$.
+
+Using formula \eqref{eq:8} we get the equation from martingale condition:
+\begin{equation}
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0,
+  \label{eq:27}
+\end{equation}
+where
+\begin{equation*}
+  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{\lambda_{i}}}{(w_{i}-z)^{n}}-\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right);\quad \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}}
+\end{equation*}
+Again we can rewrite it as algebraic requirement for  field  which corresponds to boundary condition changing operator. Now
+\begin{equation}
+  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
+  \label{eq:16}
+\end{equation}
+is level two null state and if we act on this state with raising operators we should get zero.
+\begin{eqnarray}
+  J^{a}_{1} \left|\psi\right>=0\\
+  J^{a}_{2}\left|\psi\right>=0\\
+  L_{2}\left|\psi\right>=0\\
+  L_{1}\left|\psi\right>=0
+\end{eqnarray}
+Using commutation relations \eqref{eq:92} these equations can be rewritten as the algebraic equations connecting parameters of random motion $\kappa, \tau$ with the level $k$ of affine Lie algebra representation.
+Rigorous analysis of these equations is given in the paper \cite{alekseev2010sle}.
+
+\section{Coset models}
+\label{sec:coset-models}
+Now we want to generalize analysis of correspondence between SLE and CFT even further and study coset models of conformal field theory\cite{Goddard198588}.
+Such models are specified by  Lie algebra $\gf$ and its subalgebra $\af$.
+Denote by $J_{n}^{a}$ the generators of affine Lie algebra $\gfh$ and by $\tilde{J}_{n}^{b}$ the generators of $\afh$, so that $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b} J^{a}_{n}$.
+Virasoro generators in coset models are given by the difference of Sugawara expressions of $\gf$ and $\af$-WZNW models:
+\begin{equation*}
+  L_{n}=L_{n}^{\gf}-L_{n}^{\af}
+\end{equation*}
+Commutation relations of Virasoro generators with generators of subalgebra $\afh$ are trivial
+\begin{equation}
+  \label{eq:26}
+  \left[L_{n},\tilde{J}^{b}_{m}\right]=0
+\end{equation}
+
+Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields  $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}.
+Then fields are labeled by pairs of weights $(\mu,\nu)$, where $\mu$ is the weight of $\gfh$ and $\nu$ is the weight of $\afh$ correspondingly.
+But there are selection rules, i.e.
+the branching functions for certain pairs of weights $(\mu,\nu)$ vanish.
+There is also a redundancy, i.e.
+non-vanishing branching functions for distinct pairs $(\mu,\nu)$ turn out to be identical \cite{fuchs1996resolution,schellekens1990field}.
+
+So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
+Some pairs are equivalent.
+This equivalence is given by the action of so called ``simple currents'' $(J,\tilde{J})$, which are certain elements of outer  automorphisms group $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ of $\gfh\times\afh$, where $B(G)$ is center of Lie group G.
+We can think of simple currents as of primary fields and their action on fields of theory are then given by fusion product \cite{difrancesco1997cft}.
+So primary fields of coset model are given by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where $(J,\tilde J)$ such that their conformal weights are equal:  $h_{J}-h_{\tilde{J}}=0$.
+
+Conformal weight of coset primary field is equal to
+\begin{multline}
+  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
+  \left|\phi_{(\mu,\nu)}\right>=\\
+  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
+\end{multline}
+It is possible to obtain analogues of Knizhnik-Zamolodchikov equations for coset models \cite{kogan1997knizhnik}:
+\begin{equation}
+  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
+  \label{eq:6}
+\end{equation}
+
+Let us introduce Schramm-Loewner evolution corresponding to coset models. 
+The idea is to constrain additional Brownian motion on group manifold to the factor space $G/A$.
+
+To study SLE on $G/A$ factor space we restrict random walk on group manifold by the choice of basis in $\gf$.
+Assume that generators $\{J^{a};\; a=1\dots \mathrm{dim}\gf\}$ are chosen in such way that $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\; a=\mathrm{dim}\gf-\mathrm{dim}\af\dots \mathrm{dim}\gf\}$ are the generators of subalgebra $\af\subset \gf$.
+Now we can consider $(\mathrm{dim}\gf-\mathrm{dim}\af)$-dimensional Brownian motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \; d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\mathrm{dim}\gf-\mathrm{dim}\af$.
+
+Then for generator of field transformation we can write 
+\begin{equation}
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}\left(d \theta ^{a} t^{a}_{i}\right)\right)
+\label{eq:5}
+\end{equation}
+Substituting to equation \eqref{eq:8} we get martingale condition
+
+\begin{equation}
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0
+\label{eq:9}
+\end{equation}
+
+which can be rewritten as the requirement for
+\begin{equation}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}J^{a}_{-1}J^{a}_{-1}\right)\right) \phi_{(\mu,\nu)}
+\label{eq:10}
+\end{equation}
+to be level two null-field.
+
+Now consider simple example. Let $G=SU(2)$ and $A=U(1)$, and corresponding Lie algebras $\gf=\mathrm{su}(2)$
+with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$, $\af\subset\gf$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$. 
+%%We label weights by Dynkin labels, so $J^{3}_{0}\phi_{(\mu,\nu)}=\frac{\mu}{2} \phi_{(\mu,\nu)}$.
+
+ The equation \eqref{eq:10} is now
+\begin{equation}
+  \label{eq:11}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
+\end{equation}
+If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\; J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
+\begin{equation}
+ \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{(\mu,\nu)}
+\label{eq:12}
+\end{equation}
+which is similar to the equations for parafermionic fields introduced in paper \cite{santachiara2008sle}.
+
+Central charge in this case is equal to
+\begin{equation}
+  \label{eq:14}
+  c=\frac{2(k-1)}{k+2}
+\end{equation}
+
+Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
+\begin{equation}
+  \label{eq:13}
+  L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{(\mu,\nu)}=0,
+\end{equation}
+and obtain
+\begin{equation}
+  \label{eq:28}
+  (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
+\end{equation}
+Another equation can be obtained by action of $L_{1}^{2}$
+\begin{equation}
+  \label{eq:15}
+  L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{(\mu,\nu)}=0
+\end{equation}
+Since $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$ we have
+\begin{equation}
+  \label{eq:17}
+  12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) +  \tau (C_{\mu}-\tilde{C}_{\nu})=0,
+\end{equation}
+where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator $\sum_{a}t^{a}t^{a}$. For $u(1)$ it is just $\nu^{2}$.
+We need to get one more equation since we have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so $L_{1}\psi=0$ and then $J_{1}^{3}L_{1}\psi=0$, so
+\begin{equation}
+  \label{eq:29}
+  \left(-6  + \kappa +  \tau +  2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0} \phi_{(\mu,\nu)}=0
+\end{equation}
+
+Turn to the case $k=2, \;c=1/2$ which corresponds to square lattice Ising model.
+We have three non-equivalent fields numbered by the pairs of $su(2)$ and $u(1)$ weights, which are $\phi_{(0,0)}, \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$.
+The equation \eqref{eq:29} is trivial for $\phi_{(0,0)}$ and $\phi_{(0,2)}$, so the equations \eqref{eq:17}, \eqref{eq:28} are consistent although we do not know how to interpret $\tau$ in context of the Ising model.
+If we consider the field $\phi_{(1,1)}$ we have no solution for $\kappa,\tau$, so we see that not every primary field corresponds to some boundary condition changing operator.
+
+Now let us generalize to arbitrary coset model.
+It is not always convenient to work with generators orthogonal with respect to Killing form $\mathcal{K}$, sometimes it is preferable to use Chevalley or Cartan-Weyl basis.
+So we change normalization condition of additional $\mathrm{dim}\gf$-dimensional Brownian motion \eqref{eq:5} to $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation \eqref{eq:2} is
+\begin{equation*}
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right).
+\end{equation*}
+ Martingale condition  \eqref{eq:8} can be written as
+\begin{equation*}
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
+      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0.
+\end{equation*}
+This equation can again be rewritten as the requirement for
+\begin{equation}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\mu,\nu)}
+\label{eq:30}
+\end{equation}
+to be level two null-field.
+
+Acting on \eqref{eq:30} with $L_{2}$ and $L_{1}^{2}$ we can obtain equations \eqref{eq:28} and \eqref{eq:17}.
+To get more equations we can act by $\afh$-generators $\tilde{J}^{b}_{1}$ and $L_{1}$ similarly to what was done with $J^{3}_{1}$ to get equation \eqref{eq:29}.
+
+To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov equations \eqref{eq:6} as was done for WZNW-models in paper \cite{alekseev2010sle}.
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+We proposed a way to generalize Schramm-Loewner evolution to obtain observables which can be studied by methods of coset conformal field theory.
+The description of fields in coset models is not very simple due to field identification \cite{schellekens1990field} and the need of  fixed points resolution \cite{Fuchs:1996dd,fuchs1996resolution} which we have not discussed here.
+These subtleties can complicate the solution of equations  \eqref{eq:28}, \eqref{eq:17} and analogues of equation \eqref{eq:29}.
+On the other hand the use of Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} for correlation functions in the spirit of \cite{alekseev2010sle} leads to matrix algebraic relations which are similar to NIM-representations for boundary states \cite{ishikawa2003novel}.
+The study of this subject can reveal deep algebraic connection of martingale conditions with boundary states classification.
+
+Physical interpretation of the solutions of martingale conditions is not clear, but there is also no lattice interpretation of Schramm-Loewner evolution with additional Brownian motion on group manifold \cite{bettelheim2005stochastic} and no lattice interpretation of WZNW-models.
+We think that these questions are closely related.
+
+%\usepackage{verbatim} 
+\newenvironment{comment}
+{\par\noindent{\bf Для заинтересованных читателей}\\}
+{\\\setlength{10cm}\\\hfill$\scriptstyle\blacksquare$\par}
+
+\begin{abstract}
+Примерный текст доклада на семинаре кафедры ФВЭиЭЧ по работе ``Recursive algorithms, branching coefficients and applications''.
+\end{abstract}
+
+\section{Постановка задачи}
+\label{sec:task}
+
+Здравствуйте!
+Сегодня я хочу рассказать о работе ``Рекуррентные алгоритмы, коэффициенты ветвления аффинных алгебр
+Ли и приложения''. В этой работе мы решали следующую задачу.
+
+Даны две аффинные алгебры Ли $\mathfrak{a}\subset \mathfrak{g}$. Аффинные алгебры Ли --- это особый
+класс бесконечномерных алгебр, которые строятся из конечномерных (полу)простых алгебр Ли, как
+центральные расширения алгебр петель. Более подробное определение будет дано позже. Неприводимое
+представление $L^{(\mu)}_{\mathfrak{g}}$ аффинной алгебры $\mathfrak{g}$ со старшим весом $\mu$
+может быть разложено на представления подалгебры $\mathfrak{a}$. Наша задача --- придумать
+практический алгоритм вычисления коэффициентов этого разложения. Конечно же эта задача уже решалась,
+например, существует способ решения ``в лоб'', требующий построения всех представлений и различные способы,
+которые работают для частных случаев, например, многое упрощается в физически интересном случае
+конформных вложений. Мы предлагаем общий метод, но иллюстрировать его будем как-раз физическими
+примерами конформных вложений.
+
+Я начну с физической мотивации этой задачи в двумерной конформной теории поля, напомню некоторые
+факты из теории представлений аффинных алгебр Ли, кратко опишу предложенное нами решение проблемы и
+расскажу про физические примеры в нашей статье.
+
+\section{Физическая мотивация}
+\label{sec:physics}
+
+Теперь я перейду к краткому объяснению метода и примерам вычислений.
+
+\section{Рекуррентные соотношения для коэффициентов ветвления}
+\label{sec:branching}
+
+Ранее для вычисления коэффициентов ветвления был предложен способ, основанный на преобразовании
+формулы Вейля-Каца для характеров представлений аффинных алгебр Ли в рекуррентное соотношение для
+коэффициентов ветвления. Однако исходный алгоритм не работал для не максимальных вложений. В данной
+работе была решена данная проблема и предложено обобщение рекуррентных соотношений.
+
+Используя формулу Вейля-Каца мы выделяем два набора элементов в весовом пространстве. Первый набор $\Gamma$
+называется веером и описывает вложение подалгебры $\mathfrak{a}$ в алгебру $\mathfrak{g}$. Веер
+универсален, в том смысле, что он может быть использован для разложения любого из представлений.
+Другой набор элементов весового пространства $\Psi ^{\left( \mu \right) }$ называется набором
+аномальных весов. Он описывает раскладываемое представление без явного его построения.
+
+После этого процесс вычисления коэффициентов ветвления можно реализовать при помощи следующей
+рекуррентной формулы:
+\begin{equation}
+  \label{eq:1}
+  \begin{array}{c}
+      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
+\left.
++\sum_{\gamma \in
+\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
++\gamma }^{\left( \mu \right) }\right)
+
+  \end{array}
+\end{equation}
+Здесь $\mathfrak{a}_{\bot}$ --- это подалгебра, ``натянутая'' на корни $\mathfrak{g}$, ортогональные
+к корневой системе подалгебры  $\mathfrak{a}$, $W_{\bot}$ --- соответствующая этим корням группа Вейля,
+$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ --- веер --- набор весов в разложении знаменателя $$\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
+(1-e^{-\pi_{\mathfrak{a}}(\alpha)})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\pi_{\mathfrak{a}}(\alpha))}$$, а $s(\gamma)$ ---
+коэффициент при  $e^{\gamma}$ в этом разложении.
+
+Набор аномальных весов $\Psi^{(\mu)}$ дает член с $\delta$-символом.
+
+Это рекуррентное соотношение позволяет нам сформулировать следующий алгоритм вычисления
+коэффициентов ветвления, который осуществляется без явного построения исходного представления или
+представлений, входящих в разложение.
+\begin{enumerate}
+\item Построить наборы положительных корней $\Delta^{+}$ и $\Delta_{\mathfrak{a}}^{+}$.
+\item Выбрать те положительные корни $\alpha\in \Delta^{+}$, которые ортогональны корневому
+  подпространству  $\mathfrak{a}$ и собрать их в набор $\Delta^{+}_{\bot}$.
+\item Построить множество весов $\Gamma$, которое мы называем ``веером''.
+\item Найти множество $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$
+  аномальных весов представления $L^{(\mu)}_{\mathfrak{g}}$.
+\item Выбрать в нем веса $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in
+    \bar{C}_{\mathfrak{a}_{\bot}} \right\}$. Это можно легко сделать, так как у нас есть набор
+  $\Delta^{+}_{\bot}$ и мы можем проверить, лежит ли вес $\pi_{\mathfrak{a}_{\bot}}\lambda$ в
+  главной камере Вейля алгебры $\mathfrak{a}_{\bot}$. Для этого все скалярные произведения этого
+  веса $\lambda$ с корнями из  $\Delta^{+}_{\bot}$ должны быть неотрицательны.
+\item Далее для весов $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in
+  \bar{C}_{\mathfrak{a}_{\bot}}$ мы вычисляем размерность соответствующих представлений
+  $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$
+  при помощи формулы Вейля и набора $\Delta^{+}_{\bot}$.
+\item Далее рекуррентно вычисляются аномальные коэффициенты ветвления, а внутри главной камеры Вейля
+  алгебры $\mathfrak{a}$ аномальные коэффициенты совпадают с настоящими коэффициентами ветвления.
+\end{enumerate}
+
+Сейчас я поясню всю процедуру на примере редукции представления простой алгебры $B_2$ ($so(5)$) на
+подалгебру $A_1$ ($so(3)$), а потом расскажу про аффинные алгебры Ли.
+
+\subsection{Примеры}
+\label{sec:examples}
+
+Я начну с примера вычисления в случае конечномерных простых алгебр Ли, так как его легко нарисовать.
+
+Рассмотрим регулярное вложение  $A_1$ в $B_2$. Вот на рисунке корневая системы алгебры $B_2=so(5)$.
+Корень  $\beta$ вложенной алгебры $A_1$ равен $\alpha_1+2\alpha_2$.
+
+Функция $s(\gamma)$ и веер $\Gamma$ строятся исходя из корневых систем $\mathfrak{g}, \mathfrak{a}$
+$\frac{\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}_{\mathfrak{g}}\setminus
+      \Delta^{+}_{\mathfrak{a}}} \left(1-e^{-\alpha}\right) \right)}{\prod_{\beta\in
+    \Delta^{+}_{\mathfrak{a}}} \left(1-e^{-\beta}\right) }$ и получается
+\begin{equation}
+  \label{eq:22}
+  (1,2),\; (2,-1)
+\end{equation}
+Вторая компонента - значение $s(\gamma)$.
+
+Опишем редукцию первого фундаментального представления $B_2$. Старший вес изображен на рисунке.
+\begin{figure}[ph]
+  \noindent\centering{
+    \includegraphics[width=90mm]{B2_A1}
+  }
+  \caption{Регулярное вложение $A_1$ в $B_2$}
+  \label{fig:B2_A1}
+\end{figure}
+Вот набор аномальных весов $\omega(\mu+\rho)-\rho,\; \omega\in W$ с соответствующими четностями
+отражений $\epsilon(\omega)$.
+Теперь мы факторизуем группу Вейля $W$ по подгруппе $W_{\bot}=\left\{\omega_1\right\}$. Получаем
+следующий набор весов и размерностей представлений  $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$:
+\begin{figure}[h!tb]
+  \noindent\centering{
+    \includegraphics[width=90mm]{B2_A1_2}
+  }
+  \caption{Аномальные веса и соответствующие $\mathfrak{a}_{\bot}=A_1$-модули}
+  \label{fig:B2_A1_2}
+\end{figure}
+
+Затем мы проектируем эти веса и размерности на корневое подпространство подалгебры
+$\mathfrak{a}=A_1$ и получаем следующие аномальные веса и их кратности:
+\begin{equation}
+  \label{eq:25}
+  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
+\end{equation}
+
+Аномальный коэффициент ветвления  $k^{(1,0)}_{1}=2$, для коэффициента $k^{(1,0)}_{0}$ из
+рекуррентного соотношения получаем
+\begin{equation}
+  \label{eq:23}
+  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1
+\end{equation}
+
+В работе рассмотрено большое число примеров вложений аффинных алгебр Ли. На самом деле мы написали
+программу, которая может строить такие примеры автоматически для алгебр Ли не слишком большого
+ранга.
+
+Я сейчас покажу результаты применения нашего алгоритма для одного из примеров конформных вложений.
+
+Рассмотрим такое вложение $\mathfrak{a}\subset \mathfrak{g}$, где
+$\mathfrak{a}=\hat{A_1}\oplus \hat{A_1}$, а $\mathfrak{g}= \hat{A_3}$. Это
+вложение является аффинным расширением специального вложения конечномерных алгебр Ли $A_1\oplus
+A_1\subset A3$. ($su(2)\oplus su(2)\subset su(4)$).
+\begin{comment}
+ Это специальное вложение строится следующим образом: берем четырехмерное
+представление $A_1\oplus A_1$ со старшим весом $(1,1)$. Вот веса этого представления
+\ref{fig:A_1+A_1_to_A3}, их координаты в базисе фундаментальных весов: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
+
+\begin{figure}[h]
+  \begin{multicols}{2}
+    \hfill
+    \includegraphics[width=50mm]{A_1+A_1_to_A3}
+    \hfill
+    \caption{Представление для специального вложения $A_1\oplus A_1\subset A3$}
+    \label{fig:A_1+A_1_to_A3}
+    \hfill
+    \includegraphics[width=50mm]{A1+A1-A3}
+    \hfill
+    \caption{Вложенные корни $A_1\oplus A_1\subset A3$}
+    \label{fig:A1+A1-A3}
+  \end{multicols}
+\end{figure}
+
+Тогда матричные элементы представления генераторов подалгебры Картана $b_1,b_2$ в базисе Вейля
+даются выражениями
+\begin{equation}
+  d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right),
+\end{equation}
+так что $d(b_1)=\mathrm{diag}(1,-1,1,-1),\;
+  d(b_2)=\mathrm{diag}(1,1,-1,-1).$
+\end{comment}
+Вложенные корни $\alpha_1,\alpha_2$ подалгебры $A_1\oplus A_1$
+выражаются через корни $\tilde{\alpha}_i$ алгебры  $A_3$
+\begin{equation}
+  \label{eq:37}
+  \begin{array}{l}
+     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
+     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
+  \end{array}
+\end{equation}
+\begin{comment}
+Они изображены на рисунке \ref{fig:A1+A1-A3}.
+\end{comment}
+
+Вложение имеет индексы  $(2,2)$ и является конформным, так как $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
+
+Для построения модулярно-инвариантной статсуммы нам нужно знать редукцию фундаментальных
+представлений $\widehat{su(4)}$. Фундаментальные веса имеют следующие координаты в ортогональном базисе
+\begin{equation}
+  \begin{array}{lll}
+     \omega_0 & = & (0,0,0,0;1;0)\\
+     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
+     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
+     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
+  \end{array}
+\end{equation}
+
+Множества положительных корней  $\Delta^{+}$ и $\Delta_{\mathfrak{a}}^{+}$:
+\begin{equation}
+  \label{eq:38}
+  \begin{array}{lll}
+    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
+    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{с кратностью}\; 3;\; n=1,2,\dots,\right\}\\
+    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm
+    \alpha_2-n\delta;\; -n\delta\; \mbox{с кратностью} \; 2;\; n=1,2,\dots\}\\
+  \end{array}
+\end{equation}
+
+Набор $\Delta^{+}_{\bot}$ пуст.
+Веер  $\Gamma _{\frak{a}\subset \frak{g}}$ показан на рисунке \ref{fig:A1+A1-A3_fan}. Конечные координаты
+даны в базисе фундаментальных весов $A_1 \oplus A_1$. Элемент $\gamma$ обозначен крестом, если
+$s(\gamma)=1$ и кругом, если $s(\gamma)=-1$.
+\begin{figure}[h!tb]
+  \includegraphics[width=150mm]{A1+A1-A3_fan}
+  \caption{Веер для специального вложения $\hat A_1\oplus\hat A_1\subset\hat A_3$}
+  \label{fig:A1+A1-A3_fan}
+\end{figure}
+
+Мы ограничимся вычислениями до пятого грейда.
+\begin{figure}[h!tb]
+  \includegraphics[width=170mm]{A1+A1-A3_anom}
+  \caption{Спроектированные аномальные веса $L^{\omega_2}_{A_3}$}
+  \label{fig:A1+A1-A3_anom}
+\end{figure}
+
+Множество аномальных весов  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in
+  W\right\}$ представления алгебры $\hat{A}_3$ состоит из 192 элементов, их проекции
+$\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ показаны на рисунке  \ref{fig:A1+A1-A3_anom}
+для $\mu=\omega_2=(0,1,0;1;0)$.
+
+Аналогичные картинки для $\omega_0, \omega_1,\omega_3$ я не показываю.
+
+Аномальные коэффициенты ветвления для представления  $L^{(\omega_2)}$ вычислены при помощи
+рекуррентных соотношений и показаны на рисунке \ref{fig:A1+A1-A3_branching}. 
+\begin{figure}[h!tb]
+  \hspace*{-2cm}\includegraphics[width=180mm]{A1+A1-A3_branching}
+  \caption{Аномальные коэффициенты ветвления для представления $L^{(0,1,0;1;0)}_{A_3}$}
+  \label{fig:A1+A1-A3_branching}
+\end{figure}
+
+Получаются следующие правила ветвления:
+ \begin{equation}
+   \label{eq:39}
+   \begin{array}{ll}
+     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
+     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
+     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
+     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
+   \end{array}
+ \end{equation}
+
+В результате мы получаем модулярно-инвариантную статсумму для WZW-модели с киральной алгеброй $\hat{A}_1\oplus \hat{A}_1$.
+\begin{multline}
+  \label{eq:40}
+  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
+  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
+\end{multline}
+
+\section{Заключение. Обсуждение перспектив.}
+\label{sec:conlusion}
+
+Функции ветвления играют важную роль в coset-моделях. Эти модели строятся путем факторизации
+WZW-модели с алгеброй $\mathfrak{g}$ по отношению к модели с подалгеброй $\mathfrak{a}$. Тут функции
+ветвления фактически описывают состояния в системе.
+
+Недавно мы заметили, что струнные функции, которые описывают представления, функции ветвления,
+описывающие редукцию представлений и функции слияния, которые описывают разложение тензорных
+произведений представлений на неприводимые, допускают построение дуальных систем функций. Эти
+дуальные функции могут быть построены просто из анализа соответствующих групп и камер Вейля. 
+Задача явного построения струнных функций или функций ветвления тогда сведется к обращению матрицы.
+Явный вид функций ветвления полезен при изучении coset-моделей. Кроме того, многие
+известные результаты могут быть перенесены на дуальные функции, например, результаты Каца о модулярных свойствах
+струнных функций и функций ветвления.
+В настоящее время мы начали исследовать эти системы дуальных функций.
+
+Среди других возможных приложений полученных методов можно отметить также приложения в интегрируемых
+цепочках, а также в приложения дуальных функций теории модулярных форм.
 
@@
 
+%%
+%% End of file
 %%% Local Variables: 
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "thesis"
 %%% End:

### 2011-12-09 AffineLieAlgebras/Thesis/4.tex
More translations in SLE section

@@
 
-In paper \cite{schramm2000scaling} it was shown that $g_{t}(z)$ satisfies stochastic differential equation 
+В статье \cite{schramm2000scaling} было показано, что  $g_{t}(z)$ удовлетворяет стохастическому дифференциальному уравнению
 \begin{equation}
@@
 \end{equation}
-where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
+здесь $\xi_{t}$ -- Броуновское движение. Динамика конца  $z_{t}$ критической кривой $\gamma_{t}$ (конец следа эволюции Шрамма-Левнера) описывается уравнением $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
 
-Stochastic process which satisfies \eqref{eq:19} is called     {\it Schramm-Loewner evolution} on the upper half-plane $\mathbb{H}$.
-For us it is more convenient to use map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
+Стохастический процесс, который удовлетворяет уравнению \eqref{eq:19} называется {\it эволюцией Шрамма-Левнера} на верхней полуплоскости $\mathbb{H}$.
+Для нас будет удобнее использовать отображение $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, так что уравнение \eqref{eq:19} переписывается в виде
 \begin{equation}
@@
 \end{equation}
-Schramm-Loewner evolution provides conformally-invariant probability measure on curves $\gamma_{t}$ in $\mathbb{H}$.
+Эволюция Шрамма-Левнера порождает конформно-инвариантную вероятностную меру на кривых $\gamma_{t}$ в $\mathbb{H}$.
 
-\subsection{SLE martingales and CFT correlation functions}
+\subsection{Мартингалы эволюции Шрамма-Левнера и корреляционные функции в конформной теории поля}
 \label{sec:corr-betw-sle}
 
-Now we can look at the observables in the presence of SLE trace.
-Expectation value of lattice observable $\mathcal{O}$ on the upper half-plane can be calculated as the sum of expectation values of this observable in presence of SLE trace $\gamma_{t}$ up to some time $t$ multiplied by the probability of this trajectory:
+Теперь рассмотрим наблюдаемые в присутствии следа эволюции Шрамма-Левнера.
+Математическое ожидание решеточной наблюдаемой $\mathcal{O}$ на верхней полуплоскости можно вычислить как сумму ожиданий этой наблюдаемой в присутствии (конечной части) траектории эволюции Шрамма-Левнера  $\gamma_{t}$ вплоть до некоторого времени $t$, умноженных на вероятность этой траектории:
 \begin{equation*}
@@
 \end{equation*}
-Lattice observable  $\prec \mathcal{O} \succ_{\mathbb{H}}$ does not depend on $t$, hence $\prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale.
+Решеточная наблюдаемая  $\prec \mathcal{O} \succ_{\mathbb{H}}$ не зависит от  $t$, следовательно $\prec\mathcal{O}\succ_{\gamma_{t}}$ -- мартингал.
 
-In continuous limit lattice observable tends to CFT correlation function \cite{bauer2003sle,bauer2003conformal,bauer2002sle}.
-We need to take into account the change of boundary conditions on the tip of SLE trace and at the infinity, so the expression is
+В непрерывном пределе решеточные наблюдаемые сходятся к корреляционным функциям в конформной теории поля \cite{bauer2003sle,bauer2003conformal,bauer2002sle}.
+Мы должны учесть изменение граничных условий на конце следа эволюции Шрамма-Левнера и на бесконечности, так что соотношение имеет вид:
 \begin{equation}
@@
 %% We've used the conformal map $g_{t}$ to get the expression on the whole plane in equation \eqref{eq:21}.
-
-We consider the theory with the boundary, so in principle we need to use boundary conformal field theory here and impose proper consistency conditions \cite{cardy1984conformal,cardy1989boundary,cardy1991bulk}.
-In the case of upper half-plane correlation functions of boundary CFT can be rewritten as the correlation functions of the theory on the whole plane but with doubled number of bulk fields.
+Мы рассматриваем теорию с границей, так что мы должны использовать модели граничной конформной теории поля и накладывать соответствующие граничные условия \cite{cardy1984conformal,cardy1989boundary,cardy1991bulk}.
+В случае верхней полуплоскости корреляционные функции в граничной конформной теории поля могут быть переписаны как корреляционные функции для теории на всей плоскости, но с удвоенным числом полей.
 
@@
 
-We assume that $\mathcal{F}$ contains some set of primary fields $\varphi_{\lambda_{i}}$ with conformal weights $h_{\lambda_{i}}$.
-Since we work with boundary CFT we need to add bulk fields in conjugate points $\bar z_{i}$.
-For future use in WZNW models we denote the conformal weights of these duplicate fields by $h_{\lambda_{i}^{*}}$.
-Also we have boundary condition changing operators  $\phi$ at the tip of SLE trace and at the infinity.
-We use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite expression \eqref{eq:21} in the whole upper half plane:
-
+Мы предполагаем, что $\mathcal{F}$ содержит некоторый набор примарных полей  $\varphi_{\lambda_{i}}$ с конформными весами $h_{\lambda_{i}}$.
+Так как мы рассматриваем граничную конформную теорию поля, мы должны добавить объемные поля в сопряженных точках  $\bar z_{i}$.
+Для дальнейшего использования в моделях Весса-Зумино-Новикова-Виттена мы обозначим конформные веса этих сопряженных полей через $h_{\lambda_{i}^{*}}$.
+Кроме того, у нас есть операторы смены граничного условия   $\phi$ на конце следа эволюции Шрамма-Левнера и на бесконечности.
+Воспользуемся конформным отображением   $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$, чтобы переписать выражение \eqref{eq:21} на верхней полуплоскости без разреза:
 \begin{equation}
@@
 
-Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
+Теперь нам нужно рассмотреть, как преобразуется конец следа эволюции Шрамма-Левнера  $\gamma_{t}$ при переходе от времени $t$ к $t+ dt$.
+Первый множитель в правой части уравнения  (\ref{eq:1}) дает нам
 \begin{equation*}
@@
 \end{equation*}
-For transformation of primary fields $\varphi_{\lambda_{i}}$ we have 
+Для преобразования примарных полей  $\varphi_{\lambda_{i}}$ имеет место равенство
 \begin{equation}
@@
 \end{equation}
-We denote generator of this transform by $\mathcal{G}_{i}$.
+Мы обозначим генератор этого преобразования через  $\mathcal{G}_{i}$.
 
-Since $ \prec\mathcal{O}\succ_{\gamma_{t}}$ is a martingale, the expectation value of its increment during the evolution from $t$ to $t+dt$ is zero
+Так как $ \prec\mathcal{O}\succ_{\gamma_{t}}$ --  мартингал, математическое ожидание его приращения при эволюции от  $t$ к $t+dt$ равняется нулю
 \begin{equation}
@@
 \end{equation}
-Using Ito calculus we get the expression for the differential of $\mathcal{F}$:
+Используем исчисление Ито и получим выражение для дифференциала $\mathcal{F}$:
 \begin{equation}
@@
 \end{equation}
-We substitute formula \eqref{eq:2} and obtain the equation
+Подставим формулу \eqref{eq:2} и получим уравнение
 \begin{equation}
@@
 
-For the correlation functions of secondary fields $L_{-n}\phi$ we have the equation 
+Для корреляционных функций вторичных полей  $L_{-n}\phi$ имеет место уравнение
 \begin{equation}
@@
 \end{equation}
- where $n\geq 1$ and
+где $n\geq 1$ и
 \begin{equation*}
@@
 \end{equation*}
-(See \cite{difrancesco1997cft}). So we can rewrite the differential equation \eqref{eq:23} as the algebraic equation on the field $\phi$ corresponding to boundary condition changing operator:
+(См. \cite{difrancesco1997cft}). То есть мы можем переписать дифференциальное уравнение \eqref{eq:23} как алгебраическое уравнение на поле $\phi$, соответствующее оператору смены граничных условий:
 \begin{equation}
@@
 \end{equation}
-In the case of minimal models the set of primary fields is finite and all the states are obtained through field-state correspondence \cite{belavin1984ics}, \cite{difrancesco1997cft}. 
-Equation \eqref{eq:24}  holds for arbitrary observable $\mathcal{O}$ and arbitrary primary fields $\varphi_{\lambda_{i}}$, so $\psi=[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ is level two null field and $\psi(0)\left|0\right>$ is level two null-state.
-There exist only two primary fields in minimal unitary models which give rise to Verma modules of Virasoro algebra with level two null-states.
-They are $\phi_{1,2}$ and $\phi_{2,1}$, so $\phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}$.
+В случае минимальных моделей набор примарных полей конечен и все состояния можно получить через соответствие между полями и состояниями
+\cite{belavin1984ics}, \cite{difrancesco1997cft}. 
+Равенство \eqref{eq:24} верно для произвольной наблюдаемой $\mathcal{O}$ и для произвольных примарных поле $\varphi_{\lambda_{i}}$, так что $\psi=[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ -- нулевое поле уровня два и $\psi(0)\left|0\right>$ -- нулевое состояние уровня два.
+В минимальных унитарных моделях существует только два примарных поля, порождающих модули Верма алгебры Вирасоро с нулевыми состояниями на уровне два.
+Это поля $\phi_{1,2}$ и $\phi_{2,1}$, так что $\phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}$.
 

### 2011-12-09 AffineLieAlgebras/Thesis/4.tex
More translation in SLE chapter

@@
 
-\section{Wess-Zumino-Novikov-Witten models}
+\section{Модели Весса-Зумино-Новикова-Виттена и эволюция Шрамма-Левнера}
 \label{sec:sle-wzw-models}
-To generalize the analysis of previous section \ref{sec:corr-betw-sle} to non-minimal models we need to take into account extra symmetries.
-Wess-Zumino-Novikov-Witten models has Kac-Moody symmetry in addition to conformal invariance leading to the appearance of Virasoro algebra.
-At first we remind well-known properties of WZNW-models \cite{difrancesco1997cft} which are useful to study SLE martingales.
+Чтобы обобщить анализ предыдущего раздела  \ref{sec:corr-betw-sle} на не-минимальные модели мы должны принять во внимание дополнительные симметрии.
+Модели Весса-Зумино-Новикова-Виттена обладают симметрией Каца-Муди в дополнение к конформной инвариантности, приводящей к появлению алгебры Вирасоро.
+Сначала мы напомним свойства ВЗНВ-моделей \cite{difrancesco1997cft}, которые нужны для изучения мартингалов эволюции Шрамма-Левнера.
 
- The action of WZNW model can be written in terms of map $g:\mathbb{C}\cup \{\infty\}\sim S^{2}\to G$ from complex plane with infinity or two-sphere to some (simple) Lie group $G$:
+Действие модели Весса-Зумино-Новикова-Виттена записывается в терминах отображения $g:\mathbb{C}\cup \{\infty\}\sim S^{2}\to G$ из комплексной плоскости с бесконечностью (сферы Римана) в некоторую (простую) группу Ли $G$:
 \begin{multline}
@@
 \end{multline}
- Here $\mathcal{K}$ is Killing form on Lie algebra $\gf$ of Lie group $G$.
-The first term is just non-linear sigma-model and the second term is written using the continuation $\tilde{g}$ from two-sphere $S^{2}$ to three-dimensional manifold $B$ which has two-sphere as the boundary.
-Since this continuation is non-unique we get the requirement for $k$ to be integer.
+Здесь $\mathcal{K}$ -- форма Киллинга на алгебре Ли  $\gf$ группы Ли $G$.
+Первый член -- это просто нелинейная сигма-модель, а второй записывается при помощи продолжения $\tilde{g}$ с два-сферы $S^{2}$ на трехмерное многообразие $B$, границей которого является два-сфера.
+Так как это продолжение не единственно, а экспонента действия должна быть определена однозначно, константа  $k$ должна быть целочисленной.
 
-Conserved currents of this model have the following form:
+Сохраняющиеся токи в этой модели даются выражениями:
   \begin{eqnarray}
@@
 
-The model possesses gauge invariance under the transformations
+Модель обладает калибровочной инвариантностью по отношению к преобразованиям
   $g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)$, 
-where $\Omega,\;\bar \Omega \in G$ are are independent. If we consider infinitesimal gauge transformation $\Omega=1+\omega$ we get Ward identities 
+здесь $\Omega,\;\bar \Omega \in G$ независимы. Из рассмотрения инфинитезимальных калибровочных преобразований  $\Omega=1+\omega$ получаем тождества Уорда
   \begin{equation}
@@
   \end{equation}
-which can be used to get operator product expansion for currents:
+из которых следует операторное разложение для токов:
  \begin{equation}
@@
  \end{equation}
-where $f_{abc}$ are the structure constants of Lie algebra $\gf$.
+здесь $f_{abc}$ -- структурные константы алгебры Ли $\gf$.
 
-Expanding the currents to modes
-$J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n $
-and using operator product expansion \eqref{eq:3} we get commutation relations of affine Lie algebra $\gfh$:
+Разложим токи на моды $J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n $, воспользуемся операторным разложением \eqref{eq:3} и получим коммутационные соотношения аффинной алгебры Ли $\gfh$:
 \begin{equation*}
@@
 
-Conformal invariance of the model can  be seen from 
-Sugawara construction, which is a way to embed Virasoro algebra into the universal enveloping algebra of affine Lie algebra $\gfh$ ($Vir\subset U(\gfh)$):
+Конформная инвариантность в этой модели следует из конструкции Сугавары, которая представляет собой способ вложения алгебры Вирасоро в универсальную обертывающую алгебры аффинной алгебры Ли $\gfh$ ($Vir\subset U(\gfh)$):
 \begin{equation}
@@
 \end{equation}
- where $h^{\vee}$ is the dual Coxeter number of Lie algebra $\gf$. 
-Full chiral algebra of the model is semidirect product of affine and Virasoro algebra $\gfh \ltimes Vir$ with commutation relations 
+где $h^{\vee}$ -- дуальное число Кокстера алгебры Ли $\gf$. 
+Полная киральная алгебра модели представляет собой полупрямое произведение аффинной алгебры и алгебры Вирасоро $\gfh \ltimes Vir$ с коммутационными соотношениями
   \begin{equation}
@@
   \end{equation}
-Here central charge $c$ of Virasoro algebra is given by expression
+Здесь центральный заряд  $c$ алгебры Вирасоро дается выражением
 \begin{equation}
@@
 \end{equation}
-There is infinite number of Virasoro primary fields, but they are organized into highest weight modules of affine Lie algebra $\gfh$. 
-Primary fields of full chiral algebra $\phi_{\lambda}$ are labeled by highest weights of  $\gfh$-modules. Here we see how Virasoro and affine Lie algebra generators act on primary fields:
+В модели существует бесконечное число полей, примарных по отношению к действию алгебры Вирасоро, но они организованы в модули старшего веса аффинной алгебры Ли $\gfh$.
+Примарные поля полной киральной алгебры  $\phi_{\lambda}$ нумеруются старшими весами  $\gfh$-модулей.
+Покажем, как генераторы алгебры Вирасоро и аффинной алгебры Ли действуют на примарные поля:
   \begin{equation*}
     \begin{aligned}
-      & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>  \quad    J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
+      & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>  \quad    J^a_n\left|\phi_{\lambda}\right>=0 \quad \text{для}\; n>0 \\
       & L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^{\vee})}\left|\phi_{\lambda}\right>=h_{\lambda} \left|\phi_{\lambda}\right>,
@@
   \end{equation*}
-where $\rho$ is Weyl vector of $\gf$.
+где $\rho$ -- вектор Вейля алгебры $\gf$.
 
-Now we want to study Schramm-Loewner evolution in WZNW-models.
-Similarly to minimal models we consider observable
+Теперь рассмотрим эволюцию Шрамма-Левнера в ВЗНВ-моделях. 
+Подобно минимальным моделям мы рассматриваем наблюдаемые
 \begin{equation*}
@@
 \end{equation*}
-Again we can use conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite it on the whole upper half-plane. 
+Мы опять используем конформное отображение  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ чтобы переписать формулу для наблюдаемых на всей верхней полуплоскости.
 \begin{equation*}
@@
 
-Under the evolution from $t$ to $t+dt$ first factor gives us $-\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}$.
+В результате эволюции от $t$ к $t+dt$ первый множитель дает нам $-\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}$.
 
-When we consider fields we need to add random gauge transformation (random motion in $G$) to stochastic evolution \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}. 
-For fields we have
+При рассмотрении полей нам нужно добавить случайное калибровочное преобразование  (случайное блуждание в $G$) к стохастическому процессу \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}. 
+Для полей мы имеем
 \begin{equation*}
@@
 \end{equation*}
-so additional term appears in the generator of field transformation. 
+так что в генераторе преобразования поля появляется дополнительный член
 \begin{equation}
@@
 \end{equation}
-Here $d\theta^{a}$ are the generators of $\mathrm{dim}\gf$-dimensional Brownian motion and $\mathbb{E}[d\theta^{a}d\theta^{b}]=\delta_{ab}dt$.
-We assume that $t^{a}$ is a basis of $\gf$ orthogonal with respect to Killing form $\mathcal{K}$, $\mathcal{K}(t^{a},t^{b})=\delta_{ab}$.
+Здесь  $d\theta^{a}$ -- генераторы  $\mathrm{dim}\gf$--мерного Броуновского движения, с $\mathbb{E}[d\theta^{a}d\theta^{b}]=\delta_{ab}dt$.
+Мы предполагаем, что $t^{a}$ -- это базис в $\gf$, ортогональный по отношению к форме Киллинга $\mathcal{K}$, $\mathcal{K}(t^{a},t^{b})=\delta_{ab}$.
 
-Using formula \eqref{eq:8} we get the equation from martingale condition:
+Воспользуемся формулой \eqref{eq:8} и получим следующее уравнение из условий для мартингала:
 \begin{equation}
@@
 \end{equation}
-where
+где
 \begin{equation*}
@@
 \end{equation*}
-Again we can rewrite it as algebraic requirement for  field  which corresponds to boundary condition changing operator. Now
+Мы снова перепишем уравнение в виде алгебраического соотношения на поле, соответствующее оператору смены граничного условия. Теперь
 \begin{equation}
@@
 \end{equation}
-is level two null state and if we act on this state with raising operators we should get zero.
+является нулевым состоянием уровня два и если на него подействовать повышающими операторами, мы должны получить ноль.
 \begin{eqnarray}
@@
 \end{eqnarray}
-Using commutation relations \eqref{eq:92} these equations can be rewritten as the algebraic equations connecting parameters of random motion $\kappa, \tau$ with the level $k$ of affine Lie algebra representation.
-Rigorous analysis of these equations is given in the paper \cite{alekseev2010sle}.
+Эти уравнения можно переписать как алгебраические соотношения, связывающие параметры случайного блуждания $\kappa, \tau$ с уровнем  $k$ представления аффинной алгебры Ли, если воспользоваться коммутационными соотношениями  \eqref{eq:92}.
+Строгий анализ полученных алгебраических соотношений проведен в работе \cite{alekseev2010sle}.
 
-\section{Coset models}
+\section{Coset-модели}
 \label{sec:coset-models}
-Now we want to generalize analysis of correspondence between SLE and CFT even further and study coset models of conformal field theory\cite{Goddard198588}.
-Such models are specified by  Lie algebra $\gf$ and its subalgebra $\af$.
-Denote by $J_{n}^{a}$ the generators of affine Lie algebra $\gfh$ and by $\tilde{J}_{n}^{b}$ the generators of $\afh$, so that $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b} J^{a}_{n}$.
-Virasoro generators in coset models are given by the difference of Sugawara expressions of $\gf$ and $\af$-WZNW models:
+Теперь мы обобщим анализ соответствия между эволюцией Шрамма-Левнера и конформной теорией поля на случай coset-моделей \cite{Goddard198588}.
+Такие модели задаются алгеброй Ли $\gf$ и ее подалгеброй $\af$.
+Обозначим через $J_{n}^{a}$ генераторы аффинной алгебры Ли $\gfh$, а через $\tilde{J}_{n}^{b}$ -- генераторы $\afh$, так что $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b} J^{a}_{n}$.
+Генераторы алгебры Вирасоро в coset-моделях даются разностями выражений Сугавары для ВЗНВ-моделей, соответствующих алгебрам  $\gf$ и $\af$:
 \begin{equation*}
@@
 \end{equation*}
-Commutation relations of Virasoro generators with generators of subalgebra $\afh$ are trivial
+Коммутационные соотношения между генераторам алгебры Вирасоро и генераторами подалгебры  $\afh$ тривиальны
 \begin{equation}
@@
 
-Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields  $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}.
-Then fields are labeled by pairs of weights $(\mu,\nu)$, where $\mu$ is the weight of $\gfh$ and $\nu$ is the weight of $\afh$ correspondingly.
-But there are selection rules, i.e.
-the branching functions for certain pairs of weights $(\mu,\nu)$ vanish.
-There is also a redundancy, i.e.
-non-vanishing branching functions for distinct pairs $(\mu,\nu)$ turn out to be identical \cite{fuchs1996resolution,schellekens1990field}.
+Coset-модели можно реализовать, как калибровочные модели Весса-Зумино-Новикова-Виттена, если добавить дополнительные калибровочные полями  $A, \bar{A}$, принимающие значения в алгебре Ли $\af\subset \gf$, в действие \cite{gawdzki1988g}.
+Теперь поля нумеруются парами весов  $(\mu,\nu)$, где $\mu$ -- вес  $\gfh$, а $\nu$ -- вес $\afh$, соответственно.
+Но появляются правила отбора, так как функции ветвления для некоторых пар весов  $(\mu,\nu)$ исчезают.
+Кроме того, имеется избыточность, так как функции ветвления для различных пар $(\mu,\nu)$ могут совпадать \cite{fuchs1996resolution,schellekens1990field}.
 
-So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$.
-Some pairs are equivalent.
-This equivalence is given by the action of so called ``simple currents'' $(J,\tilde{J})$, which are certain elements of outer  automorphisms group $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ of $\gfh\times\afh$, where $B(G)$ is center of Lie group G.
-We can think of simple currents as of primary fields and their action on fields of theory are then given by fusion product \cite{difrancesco1997cft}.
-So primary fields of coset model are given by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where $(J,\tilde J)$ such that their conformal weights are equal:  $h_{J}-h_{\tilde{J}}=0$.
+Итак, примарные поля нумеруются парами весов  $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ алгебры $\gfh$ и подалгебры $\afh$, такими, что соответствующие функции ветвления $b^{\mu}_{\nu}(q)\neq 0$.
+Некоторые пары эквивалентны.
+Эта эквивалентность дается действием так называемых ``простых токов'' $(J,\tilde{J})$, которые являются элементами группы внешних автоморфизмов  $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ алгебры $\gfh\times\afh$, где $B(G)$ -- это центр группы Ли $G$.
+Мы можем думать о простых токах как о примарных полях, тогда их действие на поля теории дается слиянием \cite{difrancesco1997cft}.
+Таким образом, примарные поля coset-моделей нумеруются классами эквивалентности пар весов  $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, где $(J,\tilde J)$ такие, что  конформные веса компонент равны:  $h_{J}-h_{\tilde{J}}=0$.
 
-Conformal weight of coset primary field is equal to
+Конформный вес примарного поля в coset-модели равен
 \begin{multline}
@@
 \end{multline}
-It is possible to obtain analogues of Knizhnik-Zamolodchikov equations for coset models \cite{kogan1997knizhnik}:
+Можно получить аналог уравнений Книжника-Замолодчикова для coset-моделей \cite{kogan1997knizhnik}:
 \begin{equation}
@@
 
-Let us introduce Schramm-Loewner evolution corresponding to coset models. 
-The idea is to constrain additional Brownian motion on group manifold to the factor space $G/A$.
+Теперь введем эволюцию Шрамма-Левнера, соответствующую coset-моделям.
+Суть конструкции состоит в ограничении дополнительного броуновского движения на групповом многообразии на фактор-пространство  $G/A$.
 

### 2011-12-09 AffineLieAlgebras/Thesis/4.tex
SLE paper translated

@@
 
-To study SLE on $G/A$ factor space we restrict random walk on group manifold by the choice of basis in $\gf$.
-Assume that generators $\{J^{a};\; a=1\dots \mathrm{dim}\gf\}$ are chosen in such way that $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\; a=\mathrm{dim}\gf-\mathrm{dim}\af\dots \mathrm{dim}\gf\}$ are the generators of subalgebra $\af\subset \gf$.
-Now we can consider $(\mathrm{dim}\gf-\mathrm{dim}\af)$-dimensional Brownian motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \; d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\mathrm{dim}\gf-\mathrm{dim}\af$.
+Чтобы ограничить броуновское движение на фактор-пространство $G/A$ выберем базис в $\gf$ специальным образом.
+Потребуем, чтобы генераторы $\{J^{a};\; a=1\dots \mathrm{dim}\gf\}$ были выбраны так, что $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$, а $\{J^{a};\; a=\mathrm{dim}\gf-\mathrm{dim}\af\dots \mathrm{dim}\gf\}$ -- генераторы подалгебры $\af\subset \gf$.
+Теперь мы  можем ввести  $(\mathrm{dim}\gf-\mathrm{dim}\af)$-мерное Броуновское движение с генераторами $d\theta^{a}$, такими, что $\mathbb{E}(d\theta^{a} \; d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\mathrm{dim}\gf-\mathrm{dim}\af$.
 
-Then for generator of field transformation we can write 
+Тогда для генераторов преобразования полей можно написать
 \begin{equation}
@@
 \end{equation}
-Substituting to equation \eqref{eq:8} we get martingale condition
-
+Подставляя это выражение в уравнение \eqref{eq:8} мы получаем условие мартингала
 \begin{equation}
-  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0,
 \label{eq:9}
 \end{equation}
-
-which can be rewritten as the requirement for
+которое можно переписать как требование, чтобы поле
 \begin{equation}
@@
 \end{equation}
-to be level two null-field.
+было нулевым полем уровня два.
 
-Now consider simple example. Let $G=SU(2)$ and $A=U(1)$, and corresponding Lie algebras $\gf=\mathrm{su}(2)$
-with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$, $\af\subset\gf$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$. 
+Рассмотрим простой пример.Пусть $G=SU(2)$ и $A=U(1)$, соответствующая алгебра Ли $\gf=\mathrm{su}(2)$ имеет генераторы $J^{1},J^{2},J^{3}$, а $\af=\mathrm{u}(1)$ -- генератор $J^{3}$, $\af\subset\gf$.
+Заметим, что $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
 %%We label weights by Dynkin labels, so $J^{3}_{0}\phi_{(\mu,\nu)}=\frac{\mu}{2} \phi_{(\mu,\nu)}$.
 
- The equation \eqref{eq:10} is now
+Уравнение \eqref{eq:10} теперь имеет вид
 \begin{equation}
@@
 \end{equation}
-If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\; J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
+Если перейти к базису $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\; J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$, это уравнение будет переписано в виде
 \begin{equation}
- \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{(\mu,\nu)}
+ \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{(\mu,\nu)},
 \label{eq:12}
 \end{equation}
-which is similar to the equations for parafermionic fields introduced in paper \cite{santachiara2008sle}.
+аналогичном уравнениям для парафермионных полей, выведенным в статье  \cite{santachiara2008sle}.
 
-Central charge in this case is equal to
+В данном примере центральный заряд равен
 \begin{equation}
@@
 
-Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
+Найдем решения уравнения  \eqref{eq:11}. Подействуем на  $\psi$ оператором $L_{2}$:
 \begin{equation}
@@
 \end{equation}
-and obtain
+и получим
 \begin{equation}
@@
 \end{equation}
-Another equation can be obtained by action of $L_{1}^{2}$
+Другое уравнение можно получить действием  $L_{1}^{2}$
 \begin{equation}
@@
 \end{equation}
-Since $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$ we have
+Так как $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$, мы получаем
 \begin{equation}
@@
 \end{equation}
-where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator $\sum_{a}t^{a}t^{a}$. For $u(1)$ it is just $\nu^{2}$.
-We need to get one more equation since we have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so $L_{1}\psi=0$ and then $J_{1}^{3}L_{1}\psi=0$, so
+где $C_{\mu}=(\mu,\mu+2\rho)$ -- собственное значение квадратичного оператора Казимира $\sum_{a}t^{a}t^{a}$.
+Для $u(1)$ это просто $\nu^{2}$.
+Нам необходимо еще одно уравнение, так как у нас три неизвестных $\kappa,\tau,h_{(\mu,\nu)}$.
+Чтобы его получить, мы пользуемся тем, что $\psi$ -- сингулярный вектор, так что $L_{1}\psi=0$ и следовательно $J_{1}^{3}L_{1}\psi=0$, что дает уравнение
 \begin{equation}
@@
 
-Turn to the case $k=2, \;c=1/2$ which corresponds to square lattice Ising model.
-We have three non-equivalent fields numbered by the pairs of $su(2)$ and $u(1)$ weights, which are $\phi_{(0,0)}, \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$.
-The equation \eqref{eq:29} is trivial for $\phi_{(0,0)}$ and $\phi_{(0,2)}$, so the equations \eqref{eq:17}, \eqref{eq:28} are consistent although we do not know how to interpret $\tau$ in context of the Ising model.
-If we consider the field $\phi_{(1,1)}$ we have no solution for $\kappa,\tau$, so we see that not every primary field corresponds to some boundary condition changing operator.
+Рассмотрим случай $k=2, \;c=1/2$, который соответствует модели Изинга на квадратной решетке.
+У нас есть три неэквивалентных поля, нумерующихся парами весов $su(2)$ и $u(1)$: $\phi_{(0,0)}, \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$.
+Уравнение \eqref{eq:29} тривиально для  $\phi_{(0,0)}$ и  $\phi_{(0,2)}$, так что уравнения  \eqref{eq:17}, \eqref{eq:28} непротиворечивы,  однако мы не знаем, как интерпретировать параметр  $\tau$ в контексте модели Изинга.
+Для поля  $\phi_{(1,1)}$ не существует решений уравнений на  $\kappa,\tau$, так что не каждое примарное поле соответствует оператору смены граничного условия.
 
-Now let us generalize to arbitrary coset model.
-It is not always convenient to work with generators orthogonal with respect to Killing form $\mathcal{K}$, sometimes it is preferable to use Chevalley or Cartan-Weyl basis.
-So we change normalization condition of additional $\mathrm{dim}\gf$-dimensional Brownian motion \eqref{eq:5} to $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation \eqref{eq:2} is
+Теперь обобщим анализ на произвольную  coset-модель.
+Работать с генераторами, ортогональными по отношению к форме Киллинга $\mathcal{K}$, не всегда удобно.
+Иногда предпочтительно использовать базис Шевалле или Картана-Вейля.
+Так что мы изменим условие нормировке дополнительного $\mathrm{dim}\gf$-мерного Броуновского движения \eqref{eq:5} на $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, и генератор преобразования поля  \eqref{eq:2} примет вид
 \begin{equation*}
@@
 \end{equation*}
- Martingale condition  \eqref{eq:8} can be written as
+Условие мартингала  \eqref{eq:8} запишется в виде
 \begin{equation*}
@@
 \end{equation*}
-This equation can again be rewritten as the requirement for
+Это уравнение снова может быть переписано, как требование чтобы поле
 \begin{equation}
@@
 \end{equation}
-to be level two null-field.
+было нулевым полем уровня два.
 
-Acting on \eqref{eq:30} with $L_{2}$ and $L_{1}^{2}$ we can obtain equations \eqref{eq:28} and \eqref{eq:17}.
-To get more equations we can act by $\afh$-generators $\tilde{J}^{b}_{1}$ and $L_{1}$ similarly to what was done with $J^{3}_{1}$ to get equation \eqref{eq:29}.
+Действуя на уравнение \eqref{eq:30} операторами  $L_{2}$ и $L_{1}^{2}$ мы можем получить уравнения \eqref{eq:28} и \eqref{eq:17}.
+Чтобы получить дополнительные уравнения мы можем подействовать генераторами  $\tilde{J}^{b}_{1}$ алгебры $\afh$ и оператором $L_{1}$, аналогично том, как мы делали с оператором  $J^{3}_{1}$ при выводе уравнения \eqref{eq:29}.
 
-To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov equations \eqref{eq:6} as was done for WZNW-models in paper \cite{alekseev2010sle}.
+Чтобы упростить соотношения можно использовать обобщение уравнений Книжника-Замолодчикова \eqref{eq:6}, как было сделано для ВЗНВ-моделей в статье \cite{alekseev2010sle}.
 
-\section{Conclusion}
+\section{Заключение}
 \label{sec:conclusion}
 
-We proposed a way to generalize Schramm-Loewner evolution to obtain observables which can be studied by methods of coset conformal field theory.
-The description of fields in coset models is not very simple due to field identification \cite{schellekens1990field} and the need of  fixed points resolution \cite{Fuchs:1996dd,fuchs1996resolution} which we have not discussed here.
-These subtleties can complicate the solution of equations  \eqref{eq:28}, \eqref{eq:17} and analogues of equation \eqref{eq:29}.
-On the other hand the use of Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} for correlation functions in the spirit of \cite{alekseev2010sle} leads to matrix algebraic relations which are similar to NIM-representations for boundary states \cite{ishikawa2003novel}.
-The study of this subject can reveal deep algebraic connection of martingale conditions with boundary states classification.
+Мы предложили способ обобщения эволюции Шрамма-Левнера для получения таких наблюдаемых, которые могут исследоваться методами конформной теории поля.
+Описание полей в coset-моделях нетривиально ввиду идентификации полей \cite{schellekens1990field} и необходимости в разрешении фиксированных точек \cite{Fuchs:1996dd,fuchs1996resolution}, которое не обсуждалась в данной главе.
+Эти тонкости могут усложнить решение уравнений  \eqref{eq:28}, \eqref{eq:17} и аналогов уравнения \eqref{eq:29}.
+С другой стороны, использование уравнений Книжника-Замолодчикова  \cite{kogan1997knizhnik} для корреляционных функций в духе работы \cite{alekseev2010sle} приводит к матричным алгебраическим соотношениям, которые напоминают NIM-представления для граничных состояний \cite{ishikawa2003novel}.
+Дальнейшее изучение этого предмета может выявить глубокую алгебраическую связь условия мартингала с классификацией граничных состояний.
 
-Physical interpretation of the solutions of martingale conditions is not clear, but there is also no lattice interpretation of Schramm-Loewner evolution with additional Brownian motion on group manifold \cite{bettelheim2005stochastic} and no lattice interpretation of WZNW-models.
-We think that these questions are closely related.
+Физическая интерпретация решений условий мартингала не вполне ясна, но пока не найдена и решеточная интерпретация эволюции Шрамма-Левнера с дополнительным Броуновским движением на групповом многообразии \cite{bettelheim2005stochastic} и решеточная реализация ВЗНВ-моделей.
+Кажется, что эти вопросы тесно связаны.
 

### 2011-12-09 AffineLieAlgebras/Thesis/concl.tex
Thesis work
Thesis partially structure cleaned, some translations in chapter 2.
Minor changes

--- 2011-11-10 AffineLieAlgebras/Thesis/review.tex
@@
-\review
+\conclusion
+\label{cha:conclusion1}
+
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+I thank the organizers of The Seventh International Conference ``Quantum Theory and Symmetries'' (QTS-7) for the opportunity to present this work and especially professor C.
+Burdik for his attention.
+I am grateful to A.
+Bytsko, K.
+Izyurov, D.
+Chelkak and R.
+Santachiara for the discussions on SLE and WZNW models.
+This work  is supported by
+the Chebyshev Laboratory (Department of Mathematics and Mechanics,
+Saint-Petersburg State University) under the grant 11.G34.31.0026
+of the Government of the Russian Federation.
 

### 2011-12-13 AffineLieAlgebras/Thesis/5.tex
Translation of Affine.m description started

@@
-\section{Вычислительные методы для теории представлений аффинных алгебр Ли}
+\chapter{Вычислительные методы для теории представлений аффинных алгебр Ли}
 \label{cha:computational-methods}
-%% \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
-%% \newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
-%% \newcommand{\co}[1]{\stackrel{\circ }{#1}}
-%% \newcommand{\pia}{\pi_{\mathfrak{a}}}
-%% \newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
-%% \newcommand{\gf}{\mathfrak{g}}
-%% \newcommand{\af}{\mathfrak{a}}
-%\newcommand{\bff}{\mathfrak{b}}
-%% \newcommand{\afb}{\mathfrak{a}_{\bot}}
-%% \newcommand{\hf}{\mathfrak{h}}
-%\newcommand{\hfg}{\hf_{\gf}}
-%% \newcommand{\hfb}{\mathfrak{h}_{\bot}}
-%% \newcommand{\pf}{\mathfrak{p}}
-%% \newcommand{\aft}{\widetilde{\mathfrak{a}}}
 
-\begin{abstract}
-%% Text of abstract
-In this paper we present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
-Algorithms are based on the properties of weights and Weyl symmetry.
-The most important problems for us are the ones, concerning computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition.
-These problems have numerous applications in physics and we provide some examples of these applications.
-The program is implemented in popular computer algebra system {\it Mathematica} and works with finite-dimensional and affine Lie algebras.
+В данной главе мы описываем вычислительный пакет  {\bf Affine.m}, разработанный нами на основе идей и методов, изложенных в главах \ref{cha:affine-lie-algebras}, \ref{cha:BGG}.
+Этот пакет для популярной системы компьютерной алгебры {\it Mathematica} может использоваться для вычислений в теории представлений конечномерных и аффинных алгебр Ли.
+Реализованные в пакете алгоритмы основываются на свойствах весов и симметрии Вейля.
+Основные проблемы, которые может решать данный пакет -- это вычисление кратностей весов в неприводимых модулях и модулях Верма, построение правил ветвления и функций ветвления, а также разложение тензорных произведений.
+Такие задачи важны с точки зрения физических приложений (см.
+главы \ref{cha:CFT},\ref{sec:SLE}) и в данной главе мы приводим дополнительные примеры.
 
-% A submitted program is expected to be of benefit to other physicists or physical chemists, or be an exemplar of good programming practice, or illustrate new or novel programming techniques which are of importance to some branch of computational physics or physical chemistry.
-%
-% Acceptable program descriptions can take different forms.
-The following Long Write-Up structure is a suggested structure but it is not obligatory.
-Actual structure will depend on the length of the program, the extent to which the algorithms or software have already been described in literature, and the detail provided in the user manual.
+Вычислительные методы в теории представлений имеют долгую историю \cite{belinfante1989survey}, существует большое количество программ и пакетов для вычислений, связанных с алгебрами Ли \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
 
-%Your manuscript and figure sources should be submitted through the Elsevier Editorial System (EES) by using the online submission tool at \\
-% http://www.ees.elsevier.com/cpc.
-
-%In addition to the manuscript you must supply: the program source code; job control scripts, where applicable; a README file giving the names and a brief description of all the files that make up the package and clear instructions on the installation and execution of the program; sample input and output data for at least one comprehensive test run; and, where appropriate, a user manual.
-These should be sent, via email as a compressed archive file, to the CPC Program Librarian at cpc@qub.ac.uk.
-
-\end{abstract}
-
-%%
-%% Start line numbering here if you want
-%%
-% \linenumbers
-
-% Computer program descriptions should contain the following
-% PROGRAM SUMMARY.
-
-{\bf PROGRAM SUMMARY}%/NEW VERSION PROGRAM SUMMARY}
-  %Delete as appropriate.
-
-\begin{small}
-\noindent
-{\em Manuscript Title:}{\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of finite-dimensional and affine Lie algebras                                       \\
-{\em Authors:}Anton Nazarov                                                \\
-{\em Program Title:}Affine.m                                          \\
-{\em Journal Reference:}                                      \\
-  %Leave blank, supplied by Elsevier.
-{\em Catalogue identifier:}                                   \\
-  %Leave blank, supplied by Elsevier.
-{\em Licensing provisions:}none                                   \\
-  %enter "none" if CPC non-profit use license is sufficient.
-{\em Programming language:}Mathematica                                   \\
-{\em Computer:}i386-i686, x86\textunderscore 64                                               \\
-  %Computer(s) for which program has been designed.
-{\em Operating system:} Linux, Windows, MacOS, Solaris                                       \\
-  %Operating system(s) for which program has been designed.
-{\em RAM:} 5-500 Mb                                              \\
-  %RAM in bytes required to execute program with typical data.
-%{\em Number of processors used:}                              \\
-  %If more than one processor.
-%{\em Supplementary material:}                                 \\
-  % Fill in if necessary, otherwise leave out.
-{\em Keywords:} Mathematica; Lie algebra; affine Lie algebra; Kac-Moody algebra; root system; weights; irreducible modules, CFT, Integrable systems\\
-  % Please give some freely chosen keywords that we can use in a
-  % cumulative keyword index.
-{\em Classification:} 5 Computer Algebra, 4.2 Other algebras and groups                                         \\
-  %Classify using CPC Program Library Subject Index, see (
-  % http://cpc.cs.qub.ac.uk/subjectIndex/SUBJECT_index.html)
-  %e.g. 4.4 Feynman diagrams, 5 Computer Algebra.
-%{\em External routines/libraries:}                            \\
-  % Fill in if necessary, otherwise leave out.
-%{\em Subprograms used:}                                       \\
-  %Fill in if necessary, otherwise leave out.
-%{\em Catalogue identifier of previous version:}*              \\
-  %Only required for a New Version summary, otherwise leave out.
-%{\em Journal reference of previous version:}*                  \\
-  %Only required for a New Version summary, otherwise leave out.
-%{\em Does the new version supersede the previous version?:}*   \\
-  %Only required for a New Version summary, otherwise leave out.
-{\em Nature of problem:}\\
-  %Describe the nature of the problem here.
-Representation theory of finite-dimensional Lie algebras has many applications in different branches of physics, including elementary particle physics, molecular physics, nuclear physics.
-Representations of affine Lie algebras appear in string theories and two-dimensional conformal field theory used for the description of critical phenomena in two-dimensional systems.
-Also Lie symmetries play major role in study of quantum integrable systems.
-   \\
-{\em Solution method:}\\
-  %Describe the method solution here.
-We work with weights and roots of finite-dimensional and affine Lie algebras and use Weyl symmetry extensively.
-Central problems which are the computations of weight multiplicities, branching and fusion coefficients are solved using one general recurrent algorithm based on generalization of Weyl character formula.
-We also offer alternative implementation based on Freudenthal multiplicity formula which can be faster in some cases.
-   \\
-%{\em Reasons for the new version:}*\\
-  %Only required for a New Version summary, otherwise leave out.
-%   \\
-%{\em Summary of revisions:}*\\
-  %Only required for a New Version summary, otherwise leave out.
-%   \\
-{\em Restrictions:}\\
-  %Describe any restrictions on the complexity of the problem here.
-Computational complexity grows fast  with the rank of algebra, so computations for algebra of rank greater than 8 are non practical.
-   \\
-{\em Unusual features:}\\
-  %Describe any unusual features of the program/problem here.
-We offer the possibility to use traditional mathematical notation for objects in representation theory of Lie algebras in computations if {\bf Affine.m} is used in {\it Mathematica} notebook interface.
-   \\
-%{\em Additional comments:}\\
-  %Provide any additional comments here.
-%   \\
-{\em Running time:}\\
-  %Give an indication of the typical running time here.
-From seconds to days depending on rank of algebra and complexity of representations.
-   \\
-
-% \begin{thebibliography}{0}
-% \bibitem{1}Reference 1         % This list should only contain those items referenced in the
-% \bibitem{2}Reference 2         % Program Summary section.
-% \bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
-%                                % This list is different from the bibliography at the end of
-%                                % the Long Write-Up.
-% \end{thebibliography}
-% * Items marked with an asterisk are only required for new versions
-% of programs previously published in the CPC Program Library.\\
-\end{small}
-
-%% main text
-\section{Introduction}
-\label{intro}
-
-Representation theory of Lie algebras is of central importance for different areas of physics and mathematics.
-In physics Lie algebras are used to describe symmetries of quantum and classical systems.
-Computational methods in representation theory have a long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
-
-Most popular programs \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{fischbacher2002ilp}, \cite{coxweyl} are created to study representation theory of simple finite-dimensional Lie algebras.
-The main computational problems are the following:
+Большинство популярных программ \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{fischbacher2002ilp}, \cite{coxweyl} создано для изучения теории представлений простых конечномерных алгебр Ли.
+Здесь основные вычислительные задачи это:
 \begin{enumerate}
-\item Construction of root system which determine the properties of Lie algebra including its commutation relations.
-\item Weyl group traversal which is important due to Weyl symmetry of root system and characters of representations.
-\item Calculation of weight multiplicities, branching and fusion coefficients, which are essential for construction and study of representations.
+\item Построение корневой системы, определяющей свойства алгебры Ли, в том числе коммутационные соотношения.
+\item Перечисление элементов группы Вейля, необходимое ввиду симметрии корневой системы и характеров представлений относительно группы Вейля.
+\item Вычисление кратностей весов, коэффициентов ветвления и слияния
 \end{enumerate}
-There are well-known algorithms for these tasks \cite{moody1982fast}, \cite{stembridge2001computational}, \cite{belinfante1989survey}, \cite{casselman1994machine}.
-The third problem is most computation-intensive.
-There are two different recurrent algorithms which are based on the Weyl character formula and the Freudenthal multiplicity formula.
-In this paper we analyze them both.
+Существуют различные алгоритмы для решения этих задач \cite{moody1982fast}, \cite{stembridge2001computational}, \cite{belinfante1989survey}, \cite{casselman1994machine}.
+Третья задача наиболее сложна с точки зрения вычислений.
+Существует два рекуррентных алгоритма, основывающихся на формуле Вейля для характеров и формуле Фрейденталя для кратностей.
+В данной главе мы их опишем.
 
@@
 In this section we remind necessary definitions and present formulae used in computations.
-
-\subsection{Lie algebras of finite and affine types}
-\label{sec:lie-algebras-finite}
-
-{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it Lie bracket}.
-If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
-\begin{equation}
-  \label{eq:1}
-  [X^{i},X^{j}]=\sum_{k} C^{ij}_{k} X^{k}
-\end{equation}
-Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to commutator.
-{\it Semisimple} Lie algebra is a direct sum of simple Lie algebras.
-In the present paper we treat simple and semisimple Lie algebras.
-
-{\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
-We denote the elements of basis of $\hfg$ by $H^{i}$.
-
-Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
-{\it Weights} are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
-
-Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
-This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).
-
-{\it Loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
-\begin{equation}
-  \label{eq:6}
-  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
-\end{equation}
-Central extension leads to the appearance of an additional term
-\begin{equation}
-  \label{eq:7}
-   [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
-\end{equation}
-This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
-
-We do not treat twisted affine Lie algebras in the present paper.
-
-\subsection{Modules, weights and roots}
-\label{sec:weights-roots}
-
-Let $\gf$ be a inite-dimensional or an affine Lie algebra.
-
-Then $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
-\begin{equation}
-  \label{eq:2}
-  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
-\end{equation}
-Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms of the  vector space $V$ with the commutator as a bracket.
-
-For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by a special choice of basis $\{v_{j}\}$ in $V$:
-\begin{equation}
-  \label{eq:3}
-  H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
-\end{equation}
-Eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
-Vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
-The  weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
-The weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of the weight subspace.
-
-The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
-\begin{equation}
-  \label{eq:5}
-  E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
-\end{equation}
-Module structure can be encoded by the formal character of a module
-\begin{equation}
-  \label{eq:10}
-  \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
-\end{equation}
-Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
-A character can be specialized by taking its value on some element $\xi$ of $\hf$.
-
-Lie algebra is its own module with respect to a special kind of representation. The action that
-defines this representation is called adjoint and is given by the bracket $ad_{X} Y=[X,Y]$. 
-{\it Roots} are weights of the adjoint representation of $\gf$.
-They encode the commutation relations of algebra in the following way.
-Denote by $\Delta$ the set of roots.
-For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and the generators $E^{\alpha}, E^{-\alpha}$ such that
-\begin{align}
-  \label{eq:4}
-  &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
-  &\left[E^{\alpha},E^{\beta}\right]=
-  \begin{cases}
-    N_{\alpha,\beta} E^{\alpha+\beta}, & \mbox{if}\; \alpha+\beta\in \Delta\\
-    \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
-    0,&\mbox{otherwise}
-  \end{cases}
-\end{align}
-
-Given the root system $\Delta$ we can choose the set of positive roots.
-This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
-Elements of $-\Delta^{+}$ are called negative roots.
-
-A positive root is {\it simple} if it cannot be written as a sum of positive roots.
-The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis in $\hfg^{*}$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive simultaneously.
-In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
-By numbering simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
-Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
-$\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}).
-{\it Comarcs} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
-
-Although for affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
-The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.
-The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- the highest root of the algebra $\go$.
-Note that root multiplicity $\mathrm{mult}(\alpha)$ for an affine Lie algebra root can be greater than one.
-
-Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called the Borel subalgebra.
-
-{\it Parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
-It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
-{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .
-
-The {\it Weyl group} $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
-\begin{equation}
-  \label{eq:8}
-  s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
-\end{equation}
-Root system and characters of representation are invariant with respect to the Weyl group  action. Root system can be reconstructed from the set of simple roots by the Weyl group transformations.
-
-Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
-
-Consider an action of the element $s_{\alpha}s_{\alpha+\delta}$ of the Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ being a simple root of the underlying finite-dimensional Lie algebra $\gf$.
-Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
-So the Weyl group can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to roots of $\gf$.
-
-A Weyl group element can be presented as a product of elementary reflections in multiple ways.
-Number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$.
-We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for the parity of the number of Weyl reflections generating $w$.
-
-Fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
-It is called a {\it main Weyl chamber}.
-
-The {\it Cartan matrix} $A$ is defined by products of simple roots
-\begin{equation}
-  \label{eq:9}
-  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}
-\end{equation}
-and can be used for a compact description of Lie algebra commutation relations in the Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
-
-Form \eqref{eq:9} induces a basis dual  to the simple
-roots basis. It is called the {\it fundamental weights basis}. We denote
-its elements by $\omega_i$:
-\begin{equation}
-  \label{eq:20}
-  \langle\omega_i,\alpha_j\rangle=\frac{2(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
-\end{equation}
-For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
-For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
-Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
-
- The sum of fundamental weights $\rho=\sum_{i} \omega_{i}$ is called a {\it Weyl vector}. It is an important tool in representation theory.
-
-\subsection{Highest weight modules}
-\label{sec:high-weight-modul}
-
-We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e.
-if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
-
-Highest weight module $V^{\mu}$ contains a single highest weight $\mu$, all the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
-
-The most simple type of highest weight modules is the Verma module
-$M^{\mu}$. Its space can be defined as a module
-\begin{equation}
-  \label{eq:17}
-  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}),
-\end{equation}
-with respect to a multiplication in $U(\gf)$ and
-$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
-Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
-Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D^{\lambda}(\bff_{+})$.
-
-Weight multiplicities in Verma modules can be found by applying the Weyl
-character formula
-\begin{equation}
-  \label{eq:11}
-  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
-\end{equation}
-Here we have used the Weyl denominator identity
-\begin{equation}
-  \label{eq:12}
-  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
-\end{equation}
-and $\epsilon \left( w\right) :=\det \left( w\right)$ is equal to 
-the parity of the sequence of Weyl reflections generating $w$.
-
-Verma module $M^{\mu}$ has the unique maximal submodule and the
-unique nontrivial simple quotient $L^{\mu}$ which is an
-{\it irreducible highest weight module}.
-
-Irreducible highest weight modules have no non-trivial submodules. 
-The Weyl character formula for
-irreducible highest weight modules is
-\begin{equation}
-  \label{eq:13}
-  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
-\end{equation}
-Thus the character of an irreducible highest weight module can be
-seen as a combination of characters of Verma modules. ( This
-fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
-(\cite{bernstein1976category,bernstein1971structure}, see also
-\cite{humphreys2008representations}).)
-
-Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
-%% !!! \Delta_{p}?!
-\begin{equation*}
-M_{I}^{\mu}=U\left( \gf\right)\otimes _{U\left( \pf_{I}\right) }L_{\pf_{I}}^{\mu}.
-\end{equation*}
-Introduce a formal element $R_{I}:=\prod_{\alpha \in \Delta
-^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
-^{\mathrm{mult}(\alpha )}$. Then the character of a generalized
-Verma module can be written as
-\begin{equation}
-  \label{eq:18}
-  \mathrm{ch}M_{I}^{\mu}=\frac{1}{R_{I}}\mathrm{ch}L_{\pf_{I}}^{\mu }.
-\end{equation}
 

### 2011-12-13 AffineLieAlgebras/Thesis/4.tex
Translation of Affine.m description started

@@
-\chapter{Практические приложения}
-\label{cha:applications}
+%\chapter{Практические приложения}
+%\label{cha:applications}
 
-\section{Эволюция Шрамма-Левнера и алгебраические свойства предельного перехода от решеточных моделей к конформной теории поля}
+\chapter{Эволюция Шрамма-Левнера и алгебраические свойства предельного перехода от решеточных моделей к конформной теории поля}
 \label{sec:SLE}
@@
 
-%\usepackage{verbatim} 
-\newenvironment{comment}
-{\par\noindent{\bf Для заинтересованных читателей}\\}
-{\\\setlength{10cm}\\\hfill$\scriptstyle\blacksquare$\par}
-
-\begin{abstract}
-Примерный текст доклада на семинаре кафедры ФВЭиЭЧ по работе ``Recursive algorithms, branching coefficients and applications''.
-\end{abstract}
-
-\section{Постановка задачи}
-\label{sec:task}
-
-Здравствуйте!
-Сегодня я хочу рассказать о работе ``Рекуррентные алгоритмы, коэффициенты ветвления аффинных алгебр
-Ли и приложения''. В этой работе мы решали следующую задачу.
-
-Даны две аффинные алгебры Ли $\mathfrak{a}\subset \mathfrak{g}$. Аффинные алгебры Ли --- это особый
-класс бесконечномерных алгебр, которые строятся из конечномерных (полу)простых алгебр Ли, как
-центральные расширения алгебр петель. Более подробное определение будет дано позже. Неприводимое
-представление $L^{(\mu)}_{\mathfrak{g}}$ аффинной алгебры $\mathfrak{g}$ со старшим весом $\mu$
-может быть разложено на представления подалгебры $\mathfrak{a}$. Наша задача --- придумать
-практический алгоритм вычисления коэффициентов этого разложения. Конечно же эта задача уже решалась,
-например, существует способ решения ``в лоб'', требующий построения всех представлений и различные способы,
-которые работают для частных случаев, например, многое упрощается в физически интересном случае
-конформных вложений. Мы предлагаем общий метод, но иллюстрировать его будем как-раз физическими
-примерами конформных вложений.
-
-Я начну с физической мотивации этой задачи в двумерной конформной теории поля, напомню некоторые
-факты из теории представлений аффинных алгебр Ли, кратко опишу предложенное нами решение проблемы и
-расскажу про физические примеры в нашей статье.
-
-\section{Физическая мотивация}
-\label{sec:physics}
-
-Теперь я перейду к краткому объяснению метода и примерам вычислений.
-
-\section{Рекуррентные соотношения для коэффициентов ветвления}
-\label{sec:branching}
-
-Ранее для вычисления коэффициентов ветвления был предложен способ, основанный на преобразовании
-формулы Вейля-Каца для характеров представлений аффинных алгебр Ли в рекуррентное соотношение для
-коэффициентов ветвления. Однако исходный алгоритм не работал для не максимальных вложений. В данной
-работе была решена данная проблема и предложено обобщение рекуррентных соотношений.
-
-Используя формулу Вейля-Каца мы выделяем два набора элементов в весовом пространстве. Первый набор $\Gamma$
-называется веером и описывает вложение подалгебры $\mathfrak{a}$ в алгебру $\mathfrak{g}$. Веер
-универсален, в том смысле, что он может быть использован для разложения любого из представлений.
-Другой набор элементов весового пространства $\Psi ^{\left( \mu \right) }$ называется набором
-аномальных весов. Он описывает раскладываемое представление без явного его построения.
-
-После этого процесс вычисления коэффициентов ветвления можно реализовать при помощи следующей
-рекуррентной формулы:
-\begin{equation}
-  \label{eq:1}
-  \begin{array}{c}
-      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
-\left.
-+\sum_{\gamma \in
-\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
-+\gamma }^{\left( \mu \right) }\right)
-
-  \end{array}
-\end{equation}
-Здесь $\mathfrak{a}_{\bot}$ --- это подалгебра, ``натянутая'' на корни $\mathfrak{g}$, ортогональные
-к корневой системе подалгебры  $\mathfrak{a}$, $W_{\bot}$ --- соответствующая этим корням группа Вейля,
-$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ --- веер --- набор весов в разложении знаменателя $$\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
-(1-e^{-\pi_{\mathfrak{a}}(\alpha)})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\pi_{\mathfrak{a}}(\alpha))}$$, а $s(\gamma)$ ---
-коэффициент при  $e^{\gamma}$ в этом разложении.
-
-Набор аномальных весов $\Psi^{(\mu)}$ дает член с $\delta$-символом.
-
-Это рекуррентное соотношение позволяет нам сформулировать следующий алгоритм вычисления
-коэффициентов ветвления, который осуществляется без явного построения исходного представления или
-представлений, входящих в разложение.
-\begin{enumerate}
-\item Построить наборы положительных корней $\Delta^{+}$ и $\Delta_{\mathfrak{a}}^{+}$.
-\item Выбрать те положительные корни $\alpha\in \Delta^{+}$, которые ортогональны корневому
-  подпространству  $\mathfrak{a}$ и собрать их в набор $\Delta^{+}_{\bot}$.
-\item Построить множество весов $\Gamma$, которое мы называем ``веером''.
-\item Найти множество $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$
-  аномальных весов представления $L^{(\mu)}_{\mathfrak{g}}$.
-\item Выбрать в нем веса $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in
-    \bar{C}_{\mathfrak{a}_{\bot}} \right\}$. Это можно легко сделать, так как у нас есть набор
-  $\Delta^{+}_{\bot}$ и мы можем проверить, лежит ли вес $\pi_{\mathfrak{a}_{\bot}}\lambda$ в
-  главной камере Вейля алгебры $\mathfrak{a}_{\bot}$. Для этого все скалярные произведения этого
-  веса $\lambda$ с корнями из  $\Delta^{+}_{\bot}$ должны быть неотрицательны.
-\item Далее для весов $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in
-  \bar{C}_{\mathfrak{a}_{\bot}}$ мы вычисляем размерность соответствующих представлений
-  $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$
-  при помощи формулы Вейля и набора $\Delta^{+}_{\bot}$.
-\item Далее рекуррентно вычисляются аномальные коэффициенты ветвления, а внутри главной камеры Вейля
-  алгебры $\mathfrak{a}$ аномальные коэффициенты совпадают с настоящими коэффициентами ветвления.
-\end{enumerate}
-
-Сейчас я поясню всю процедуру на примере редукции представления простой алгебры $B_2$ ($so(5)$) на
-подалгебру $A_1$ ($so(3)$), а потом расскажу про аффинные алгебры Ли.
-
-\subsection{Примеры}
-\label{sec:examples}
-
-Я начну с примера вычисления в случае конечномерных простых алгебр Ли, так как его легко нарисовать.
-
-Рассмотрим регулярное вложение  $A_1$ в $B_2$. Вот на рисунке корневая системы алгебры $B_2=so(5)$.
-Корень  $\beta$ вложенной алгебры $A_1$ равен $\alpha_1+2\alpha_2$.
-
-Функция $s(\gamma)$ и веер $\Gamma$ строятся исходя из корневых систем $\mathfrak{g}, \mathfrak{a}$
-$\frac{\pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}_{\mathfrak{g}}\setminus
-      \Delta^{+}_{\mathfrak{a}}} \left(1-e^{-\alpha}\right) \right)}{\prod_{\beta\in
-    \Delta^{+}_{\mathfrak{a}}} \left(1-e^{-\beta}\right) }$ и получается
-\begin{equation}
-  \label{eq:22}
-  (1,2),\; (2,-1)
-\end{equation}
-Вторая компонента - значение $s(\gamma)$.
-
-Опишем редукцию первого фундаментального представления $B_2$. Старший вес изображен на рисунке.
-\begin{figure}[ph]
-  \noindent\centering{
-    \includegraphics[width=90mm]{B2_A1}
-  }
-  \caption{Регулярное вложение $A_1$ в $B_2$}
-  \label{fig:B2_A1}
-\end{figure}
-Вот набор аномальных весов $\omega(\mu+\rho)-\rho,\; \omega\in W$ с соответствующими четностями
-отражений $\epsilon(\omega)$.
-Теперь мы факторизуем группу Вейля $W$ по подгруппе $W_{\bot}=\left\{\omega_1\right\}$. Получаем
-следующий набор весов и размерностей представлений  $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$:
-\begin{figure}[h!tb]
-  \noindent\centering{
-    \includegraphics[width=90mm]{B2_A1_2}
-  }
-  \caption{Аномальные веса и соответствующие $\mathfrak{a}_{\bot}=A_1$-модули}
-  \label{fig:B2_A1_2}
-\end{figure}
-
-Затем мы проектируем эти веса и размерности на корневое подпространство подалгебры
-$\mathfrak{a}=A_1$ и получаем следующие аномальные веса и их кратности:
-\begin{equation}
-  \label{eq:25}
-  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
-\end{equation}
-
-Аномальный коэффициент ветвления  $k^{(1,0)}_{1}=2$, для коэффициента $k^{(1,0)}_{0}$ из
-рекуррентного соотношения получаем
-\begin{equation}
-  \label{eq:23}
-  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1
-\end{equation}
-
-В работе рассмотрено большое число примеров вложений аффинных алгебр Ли. На самом деле мы написали
-программу, которая может строить такие примеры автоматически для алгебр Ли не слишком большого
-ранга.
-
-Я сейчас покажу результаты применения нашего алгоритма для одного из примеров конформных вложений.
-
-Рассмотрим такое вложение $\mathfrak{a}\subset \mathfrak{g}$, где
-$\mathfrak{a}=\hat{A_1}\oplus \hat{A_1}$, а $\mathfrak{g}= \hat{A_3}$. Это
-вложение является аффинным расширением специального вложения конечномерных алгебр Ли $A_1\oplus
-A_1\subset A3$. ($su(2)\oplus su(2)\subset su(4)$).
-\begin{comment}
- Это специальное вложение строится следующим образом: берем четырехмерное
-представление $A_1\oplus A_1$ со старшим весом $(1,1)$. Вот веса этого представления
-\ref{fig:A_1+A_1_to_A3}, их координаты в базисе фундаментальных весов: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.
-
-\begin{figure}[h]
-  \begin{multicols}{2}
-    \hfill
-    \includegraphics[width=50mm]{A_1+A_1_to_A3}
-    \hfill
-    \caption{Представление для специального вложения $A_1\oplus A_1\subset A3$}
-    \label{fig:A_1+A_1_to_A3}
-    \hfill
-    \includegraphics[width=50mm]{A1+A1-A3}
-    \hfill
-    \caption{Вложенные корни $A_1\oplus A_1\subset A3$}
-    \label{fig:A1+A1-A3}
-  \end{multicols}
-\end{figure}
-
-Тогда матричные элементы представления генераторов подалгебры Картана $b_1,b_2$ в базисе Вейля
-даются выражениями
-\begin{equation}
-  d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right),
-\end{equation}
-так что $d(b_1)=\mathrm{diag}(1,-1,1,-1),\;
-  d(b_2)=\mathrm{diag}(1,1,-1,-1).$
-\end{comment}
-Вложенные корни $\alpha_1,\alpha_2$ подалгебры $A_1\oplus A_1$
-выражаются через корни $\tilde{\alpha}_i$ алгебры  $A_3$
-\begin{equation}
-  \label{eq:37}
-  \begin{array}{l}
-     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
-     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
-  \end{array}
-\end{equation}
-\begin{comment}
-Они изображены на рисунке \ref{fig:A1+A1-A3}.
-\end{comment}
-
-Вложение имеет индексы  $(2,2)$ и является конформным, так как $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.
-
-Для построения модулярно-инвариантной статсуммы нам нужно знать редукцию фундаментальных
-представлений $\widehat{su(4)}$. Фундаментальные веса имеют следующие координаты в ортогональном базисе
-\begin{equation}
-  \begin{array}{lll}
-     \omega_0 & = & (0,0,0,0;1;0)\\
-     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
-     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
-     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
-  \end{array}
-\end{equation}
-
-Множества положительных корней  $\Delta^{+}$ и $\Delta_{\mathfrak{a}}^{+}$:
-\begin{equation}
-  \label{eq:38}
-  \begin{array}{lll}
-    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
-    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{с кратностью}\; 3;\; n=1,2,\dots,\right\}\\
-    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1-n\delta,\pm
-    \alpha_2-n\delta;\; -n\delta\; \mbox{с кратностью} \; 2;\; n=1,2,\dots\}\\
-  \end{array}
-\end{equation}
-
-Набор $\Delta^{+}_{\bot}$ пуст.
-Веер  $\Gamma _{\frak{a}\subset \frak{g}}$ показан на рисунке \ref{fig:A1+A1-A3_fan}. Конечные координаты
-даны в базисе фундаментальных весов $A_1 \oplus A_1$. Элемент $\gamma$ обозначен крестом, если
-$s(\gamma)=1$ и кругом, если $s(\gamma)=-1$.
-\begin{figure}[h!tb]
-  \includegraphics[width=150mm]{A1+A1-A3_fan}
-  \caption{Веер для специального вложения $\hat A_1\oplus\hat A_1\subset\hat A_3$}
-  \label{fig:A1+A1-A3_fan}
-\end{figure}
-
-Мы ограничимся вычислениями до пятого грейда.
-\begin{figure}[h!tb]
-  \includegraphics[width=170mm]{A1+A1-A3_anom}
-  \caption{Спроектированные аномальные веса $L^{\omega_2}_{A_3}$}
-  \label{fig:A1+A1-A3_anom}
-\end{figure}
-
-Множество аномальных весов  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in
-  W\right\}$ представления алгебры $\hat{A}_3$ состоит из 192 элементов, их проекции
-$\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ показаны на рисунке  \ref{fig:A1+A1-A3_anom}
-для $\mu=\omega_2=(0,1,0;1;0)$.
-
-Аналогичные картинки для $\omega_0, \omega_1,\omega_3$ я не показываю.
-
-Аномальные коэффициенты ветвления для представления  $L^{(\omega_2)}$ вычислены при помощи
-рекуррентных соотношений и показаны на рисунке \ref{fig:A1+A1-A3_branching}. 
-\begin{figure}[h!tb]
-  \hspace*{-2cm}\includegraphics[width=180mm]{A1+A1-A3_branching}
-  \caption{Аномальные коэффициенты ветвления для представления $L^{(0,1,0;1;0)}_{A_3}$}
-  \label{fig:A1+A1-A3_branching}
-\end{figure}
-
-Получаются следующие правила ветвления:
- \begin{equation}
-   \label{eq:39}
-   \begin{array}{ll}
-     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
-     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
-     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
-     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
-   \end{array}
- \end{equation}
-
-В результате мы получаем модулярно-инвариантную статсумму для WZW-модели с киральной алгеброй $\hat{A}_1\oplus \hat{A}_1$.
-\begin{multline}
-  \label{eq:40}
-  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
-  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
-\end{multline}
-
-\section{Заключение. Обсуждение перспектив.}
-\label{sec:conlusion}
-
-Функции ветвления играют важную роль в coset-моделях. Эти модели строятся путем факторизации
-WZW-модели с алгеброй $\mathfrak{g}$ по отношению к модели с подалгеброй $\mathfrak{a}$. Тут функции
-ветвления фактически описывают состояния в системе.
-
-Недавно мы заметили, что струнные функции, которые описывают представления, функции ветвления,
-описывающие редукцию представлений и функции слияния, которые описывают разложение тензорных
-произведений представлений на неприводимые, допускают построение дуальных систем функций. Эти
-дуальные функции могут быть построены просто из анализа соответствующих групп и камер Вейля. 
-Задача явного построения струнных функций или функций ветвления тогда сведется к обращению матрицы.
-Явный вид функций ветвления полезен при изучении coset-моделей. Кроме того, многие
-известные результаты могут быть перенесены на дуальные функции, например, результаты Каца о модулярных свойствах
-струнных функций и функций ветвления.
-В настоящее время мы начали исследовать эти системы дуальных функций.
-
-Среди других возможных приложений полученных методов можно отметить также приложения в интегрируемых
-цепочках, а также в приложения дуальных функций теории модулярных форм.
-
-\section{Coset-модели}
-\label{sec:coset-models}
-Ветвления. Функции ветвления и статсуммы. 
-Калибровочные WZW-модели.
-
-\section{SLE}
-\label{sec:sle}
-SLE на WZW-моделях. Граничные условия. Парафермионы. SLE на coset-моделях.
-
 %%

### 2011-12-13 AffineLieAlgebras/Splints/paper2.tex
Paper on splints of affine Lie algebras is started

\documentclass[12pt]{article}
\usepackage{amsfonts}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsthm}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[english]{babel}

%TCIDATA{OutputFilter=Latex.dll}
%TCIDATA{LastRevised=Mon Oct 10 18:16:16 2011}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{CSTFile=article.cst}

\newtheorem{Def}{Definition}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{statement}{Statement}
\newtheorem{Cnj}[Def]{Conjecture}
\newtheorem{Prop}[Def]{Property}
\newtheorem{example}{Example}[section]

\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\nfp}{\mathfrak{n}^{+}}
\newcommand{\nfm}{\mathfrak{n}^{-}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}

\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

%\input{tcilatex}

\begin{document}
\title{On affine extension of splint root systems}

\author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$ \\
  {\small $^1$ Department of High-energy and elementary particle physics, SPb State University}\\
  {\small 198904, Saint-Petersburg, Russia}\\
  {\small e-mail: lyakh1507@nm.ru}\\
  {\small$^{2}$ Chebyshev Laboratory,}\\
  {\small Department of Mathematics and Mechanics, SPb State University}\\
  {\small 199178, Saint-Petersburg, Russia}\\
  {\small email: antonnaz@gmail.com}}
\maketitle

\begin{abstract}
Splint of root system of simple Lie algebra appears naturally in
the study of (regular) embeddings of reductive subalgebras. It can
be used to derive branching rules. Application of
splint properties drastically simplifies calculations of
branching coefficients. We study affine extension of splint root system of simple Lie algebra.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Consider Lie algebra $\gf$ and its irreducible modules $L^{\mu}_{\gf}$. 
Splints of root systems were introduced by D. Richter in paper \cite{richter2008splints} to describe cases of drastic simplification of module reduction into the sum of subalgebra modules. In paper \cite{2011arXiv1111.6787L} we've proved that branching coefficients coincide with multiplicities (more details here).

In present note we generalize our analysis to affine extension of $\gf$. We consider affine Lie algebra $\gfh$ with the underlying simple finite-dimensional Lie algebra $\gf$. We assume that root system $\Delta_{\gf}$ admits splint $\Delta_{\gf}=\Delta_{\af_{1}}\cup \Delta_{\af_{2}}$. It is well-known \cite{kac1990idl} that irreducible $\gfh$-module can be decomposed into the sum of irreducible $\gf$-modules.
\begin{equation}
  \label{eq:1}
  L_{\gfh}^{\mu}=\bigoplus_{\nu=(\co{\nu},n,k)} b^{\mu}_{\co{\nu}}(n) L^{\co{\nu}}_{\gf}
\end{equation}
Then each of these $\gf$-modules in this decomposition admits decomposition to $\af_{1}$ modules with branching coefficients equal to weight multiplicities of $\af_{2}$ irreducible module \cite{2011arXiv1111.6787L}. 
\begin{equation}
  \label{eq:2}
  L^{\co{\nu}}_{\gf} = \bigoplus b^{\mu}_{\af_{1}\co{\nu}}(n) L^{\co{\nu}}_{\gf}
\end{equation}
We state that it is possible to reorganize weights in such a way that branching coefficients for the reduction $\gfh\downarrow \af_{1}$  are expressed in terms of weight multiplicities of $\hat\af_{2}$. 
\section{Main theorem}
\label{sec:main-theorem}
\begin{theorem}
  Consider reduction of affine Lie algebra $\gfh$-module $L^{\mu}_{\gfh}$ to finite-dimensional subalgebra $\af_{1}$. Then for branching coefficients following relation holds:
  \begin{equation}
    \label{eq:3}
    b^{\mu}_{\nu}=\sum_{?} m^{\nu}_{\hat\af_{2}}
  \end{equation}
\end{theorem}
\begin{proof}
  At first we use equation \eqref{eq:1}, then substitute to equation \eqref{eq:2}, reorganize weights and obtain the desired result. 
\end{proof}

\section{Examples}
\label{sec:examples}
The most simple example is constructed starting with splint $\Delta_{A_{2}}=\Delta_{A_{1}\oplus A_{1}}\cup \Delta_{A_{1}}$.

Then we consider the case $\gfh=\hat B_{2}$.
\section*{Conclusion}
\label{sec:conclusion}
Further question is to generalize this analysis to affine sublagebras and apply the results on branching coefficients to the study of CFT coset models.

%%  
%%  
%%  In the present paper we provide alternative proof of the main statement of paper [LN-2011-Splints] which uses graded commutative structure on vector space of universal enveloping algebra $U(n^{-})$. 
%%  
%%  Con
%%  
%%  
%%  Consider decomposition of simple Lie algebra $\gf=\nfp\oplus \hf \oplus \nfm$. Verma module $M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+})$. $S(\nfm)=\{x_{1}\dots x_{l}:x_{i}\in\nfm\}_{l=0}^{\infty}$
%%  \begin{theorem}
%%    Fix some ordering $\alpha_{1},\dots,\alpha_{s}$ on the set of positive roots $\Delta^{+}$ and obtain the ordering on the basis $f_{1},\dots,f_{s}$ of $\nfm$.  Then monomials $f_{1}^{n_{1}} \dots f_{s}^{n_{s}}$ form a basis in $U(\nfm)\sim M^{\lambda}$ and $U(\nfm)\sim \mathbb{Z}^{s}_{\geq 0}$. 
%%  \end{theorem}
%%  \begin{statement}
%%    Let $\Delta^{+}_{\gf}=\Delta^{+}_{\af_{1}}\cup \Delta^{+}_{\af_{2}}$ be a splint positive root system of simple Lie algebra $\gf$. Then $M^{\lambda}_{\gf}\sim M^{\lambda}_{\af_{1}}\oplus M^{\lambda}_{\af_{2}}$.
%%    \begin{proof}
%%      Basis of $M^{\lambda}_{\gf}$ is given by $f_{1}^{n_{1}}\dots f_{s_{1}}^{n_{s_{1}}} f_{s_{1}+1}^{n_{s_{1}+1}}\dots f_{s_{1}+s_{2}}^{n_{s_{1}+s_{2}}}$, where $f_{1},\dots, f_{s_{1}}\in \nfm_{\af_{1}}$ and $f_{s_{1}+1},\dots,f_{s_{1}+s_{2}}\in \nfm_{\af_{2}}$
%%    \end{proof}
%%  \end{statement}
%%  Now consider irreducible $\gf$-module $L_{\gf}^{\mu}=M^{\mu}_{\gf}/I^{\mu}_{\gf}$t
%%  
\bibliography{bibliography}{}
\bibliographystyle{utphys}

\end{document}

### 2011-12-14 AffineLieAlgebras/Thesis/5.tex
Translation on Affine.m

@@
 
-Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and in a study of  integrable systems.
-But infinite-dimensional algebras are much harder to investigate and the number of available computer programs is much smaller in this case.
+Бесконечномерные алгебры Ли гораздо сложнее исследовать и число имеющихся программ гораздо меньше. 
+Однако структура аффинных алгебр Ли позволяет адаптировать к ним вычислительные алгоритмы, предложенные для конечномерных алгебр Ли \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
+В книге \cite{kass1990ala}, изданной в 1990 году, приведены таблицы кратностей весов неприводимых представлений и другие вычисленные характеристики аффинных алгебр и их модулей.
+Однако нам на данный момент не известны пакеты для популярных систем компьютерной алгебры, которые можно было бы использовать для воспроизведения и расширения этих результатов.
 
-Affine Lie algebras \cite{kac1990idl} constitute important and tractable class of infinite-dimensional Lie algebras.
-They are constructed as central extensions of loop algebras of (semi-simple) finite-dimensional Lie algebras and appear naturally in a study of Wess-Zumino-Witten and coset models in conformal field theory \cite{Walton:1999xc}, \cite{difrancesco1997cft}, \cite{Goddard198588}, \cite{Dunbar:1992gh}.
+Чтобы исправить этот недостаток, нами был создан пакет {\bf Affine.m} для популярной системы  {\it Mathematica}.
+Возможности и ограничения этого пакета мы и описываем в этой главе.
+Кроме того, мы приводим некоторые примеры, связанные с физическими приложениями.
 
-The structure of affine Lie algebras allows to adapt for them computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
-The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of affine Lie algebras and representations was published in 1990.
-But we are not aware of software packages for popular computer algebra systems which can be used to extend these results.
-We address this issue and present {\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.
-We describe the features and limitations of the package in the present paper.
-We also provide representation-theoretical background of implemented algorithms and present examples of computations relevant to physical applications.
+Необходимые сведения из теории представлений приведены в главе \ref{cha:affine-lie-algebras}.
+Здесь мы начинаем с описания структур данных пакета  {\bf Affine.m}, использующихся для описания различных объектов теории представлений  (раздел \ref{sec:core-datastructures}), обсуждаем алгоритмы  (раздел \ref{sec:comp-algor}) и приводим примеры  (раздел \ref{sec:examples}).
 
-The paper starts with an overview of Lie algebras and their representation theory (Sec.
-\ref{sec:theor-backgr}).
-Then we describe datastructures of {\bf Affine.m} used to present different objects related to Lie algebras and representations (Sec.
-\ref{sec:core-datastructures}) and discuss implemented algorithms (Sec.
-\ref{sec:comp-algor}).
-Next section consists of physically interesting examples (Sec.
-\ref{sec:examples}).
-The paper is concluded with the discussion of possible extensions and refinements (Sec.
-\ref{sec:conclusion}).
-
-\section{Theoretical background}
-\label{sec:theor-backgr}
-
-In this section we remind necessary definitions and present formulae used in computations.
-
-%% Define external border of irreducible representation here
-
-We can use the Weyl character formula to obtain recurrent relations for weight multiplicities -- important tools for calculations \cite{il2010folded,kulish4sfa}.
-
-For irreducible highest-weight modules recurrent relations have the following form
-\begin{equation}
-\label{eq:14}
-m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
--\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
-(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
-\end{equation}
-Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side.
-In case of Verma module it is just $\delta_{\xi,\mu}$.
-For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
-
-Other recurrent formula can be obtained from a study of Casimir
-elements action on irreducible highest weight modules
-\cite{humphreys1997introduction}:
-\begin{equation}
-  \label{eq:15}
-  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
-\end{equation}
-It is called the Freudenthal multiplicity formula.
-Note that it is applicable only to irreducible modules.
-
-We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.
-
-Now consider an algebra $\gf$ and a reductive subalgebra
-$\af\subset \gf$. Simple roots $\beta_{i}$ of the subalgebra $\af$
-can be presented as linear combinations of $\gf$-algebra roots
-$\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j}
-\alpha_{j},\ j=1,\dots,r_{\af}$.
-
-Each irreducible $\gf$-module is also an $\af$-module, although
-$L^{\mu}_{\gf}$ is in general not irreducible as $\af$-module. 
-It can be
-decomposed into a direct sum of irreducible $\af$-modules:
-\begin{equation}
-  \label{eq:16}
-  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
-\end{equation}
-Coefficients in such a decomposition are called branching
-coefficients.
-
-It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. 
-This traditional approach has serious limitations especially in case of affine Lie algebras. We discuss them in the end of section \ref{sec:comp-algor}.
-
-Now we describe an alternative approach which is based on recurrent properties of branching coefficients. 
-But before we proceed to these recurrent relations we need several additional definitions.
-
-For a subalgebra $\af\subset \gf$ we introduce the subalgebra
-$\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
-orthogonal to $\hf_{\af}$,
-\begin{equation*}
-\hf_{\perp \af}^{\ast }:=\left\{ \eta \in \hf^{\ast }|\forall
-h\in \hf_{\af};\eta \left( h\right) =0\right\} ,
-\end{equation*}
-and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
-to roots of $\af$,
-\begin{eqnarray}
-\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
-h\in \hf_{\af};\beta \left( h\right) =0\right\} ,
-\label{delta a ort} \\
-\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
-}^{+}|\forall h\in \hf_{\af};\beta ^{+}\left( h\right) =0\right\} .
-\notag
-\end{eqnarray}
-Let $W_{\afb}$ be a subgroup of $W$ generated by
-reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
-}}^{+}$. The subsystem $\Delta _{\afb}$ determines a 
-subalgebra $\afb$ with the Cartan subalgebra $\hf_{\af%
-_{\perp }}$.
-
-The Cartan subalgebra $\frak{h}$ can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
-\frak{h}_{\afb}\oplus \frak{h}_{\perp }$
-
-We also introduce the notations
-\begin{eqnarray}
-\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
-\qquad
-\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
-\end{eqnarray}
-
-For $\af$ and $\afb$ we consider the
-corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\af_{\perp
-}} $ and compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
-D}_{\afb}$ of the injection:
-\begin{equation}
-\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho , \qquad
-\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
-_{\perp }}\rho .  \label{defect-ort}
-\end{equation}
-
-%%!!! Define P^+
-For $\mu \in P^{+}$ consider the linked weights $\left\{ \left(
-w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections
-to
-$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
-\mathcal{D}_{\afb}$:
-\begin{equation*}
-\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
-w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
-\end{equation*}
-Among the weights $\left\{ \mu _{\af_{\perp
-}}\left( w\right) |w\in W\right\} $ one can always choose those located in
-the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
-set of representatives $u$ for the classes $W/W_{\afb}$ such
-that
-
-\begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
-\overline{C_{\afb}}\right\} \quad .  \label{U-def}
-\end{equation}
-Thus we can form the subsets:
-\begin{equation}
-\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
-\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
-_{\perp }},\quad u\in U,  \label{mu-a}
-\end{equation}
-and
-\begin{equation}
-\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
-\label{mu-a-tilda}
-\end{equation}
-
-Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
-since it is built on a subset of roots of the algebra $\mathfrak{g}$.
-
-Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients.
-If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.
-
-Now we can use the Weyl character formula to write a
-recurrent relation \cite{2010arXiv1007.0318L} for signed branching
-coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
-injection $\af\hookrightarrow \gf$:
-\begin{equation}
-\begin{array}{c}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
-_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
-\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right.  \\
-\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
-}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
-}\right) .
-\end{array}
-\label{recurrent-rel}
-\end{equation}
-The recursion is governed by the set $\Gamma _{\af\rightarrow \gf}$ called the injection fan. The latter is defined by the
-carrier set $\left\{ \xi \right\} _{\af\rightarrow \gf}$ for the
-coefficient function $s(\xi )$
-\begin{equation*}
-\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}:=\left\{
-\xi \in P_{\widetilde{\af}}|s(\xi )\neq 0\right\}
-\end{equation*}
-appearing in the expansion
-\begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
-_{\widetilde{\af}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
-_{\af}(\pi _{\widetilde{\af}}\alpha )}=-\sum_{\gamma \in P_{%
-\widetilde{\af}}}s(\gamma )e^{-\gamma };\quad
-\end{equation}
-The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
-\right\} $ -- and the zero element is to be eliminated:
-\begin{equation}
-\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma
-_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
-\end{equation}
-Formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
-
-If the root system of $\afb$ is generated by some subset of $\gf$
-simple roots $\alpha_{1},\dots,\alpha_{r}$ then the recurrent
-relation (\ref{recurrent-rel}) is connected with the generalized
-Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules
-\cite{2011arXiv1102.1702L}.
-
-Another particular case of this formula is connected with tensor
-product decompositions. Consider the tensor product of two
-irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$. It is also a
-$\gf$-module but not irreducible in general. So
-\begin{equation}
-  \label{eq:19}
-  L^{\mu}\otimes L^{\nu}=\bigoplus_{\gamma} f^{\mu\nu}_{\gamma}L^{\gamma}
-\end{equation}
-The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion
-coefficients. The problem of computation of fusion coefficients is
-equivalent to branching problem for the diagonal subalgebra
-$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
-
-In the case of affine Lie algebras $\gf, \af$  the multiplicities
-$m_{\nu}$ and the corresponding branching coefficients $b_{\nu}$
-can be regarded as the coefficients in power series decomposition
-of string and branching functions correspondingly:
-\begin{align}
-  \label{eq:21}
-  &\sigma_{\nu}(q)=\sum_{n=0}^{\infty} m_{\nu-n\delta} q^n, \quad \nu=\sum_j c_j \omega_j,\quad c_j\geq 0\\
-  & b_{\nu}(q)=\sum_{n=0}^{\infty} b_{\nu-n\delta} q^n,\quad  \nu=\sum_j c_j \omega_j, \quad c_j\geq 0
-\end{align}
-String and branching functions have  modular and analytic properties which are important for conformal field theory, especially in  coset models and the study of CFT on higher genus surfaces \cite{kac1988modular}, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}.
-
-{\bf Affine.m}  calculates weight multiplicities and branching coefficients for affine Lie algebras up to some finite grade.
-We present examples of computations in Sections \ref{sec:string-funct-affine}, \ref{sec:branch-funct-coset}.
-Now we proceed to the description of datastructures and algorithms implemented in {\bf Affine.m}.
-
-\section{Core datastructures}
-\label{sec:core-datastructures} Having introduced necessary
-mathematical objects, problems and relations we now describe the
-related datastructures of {\bf Affine.m}. Although {\it
-Mathematica} is untyped language it is possible to create
-structured objects and do type checks with patterns
-\cite{shifrinmathematica}, \cite{maeder2000computer}.
-\subsection{Weights}
+\section{Структуры данных}
+\label{sec:core-datastructures} 
+Хотя {\it Mathematica} -- нетипизированный язык программирования, в нем можно создавать структурированные объекты и проверять их типы используя сопоставление с шаблоном (pattern matching) \cite{shifrinmathematica}, \cite{maeder2000computer}.
+\subsection{Веса}
 \label{sec:weights}
 
-Weights are represented  by two data-structures: \lstinline{finiteWeight} for finite-dimensional Lie algebras and \lstinline{affineWeight}  for affine.
+Веса представляются двумя структурами данных: \lstinline{finiteWeight} для конечномерных алгебр Ли и \lstinline{affineWeight} для аффинных алгебр Ли.
 
-Internally the finite weight is a \lstinline{List} with the
-\lstinline{Head} \lstinline{finiteWeight}, its components are the
-coordinates of the weight in the orthogonal Bourbaki  basis
-\cite{bourbaki2002lie}.
+Внутренняя структура веса конечномерной алгебры Ли представляет собой  \lstinline{List} с заголовком \lstinline{finiteWeight}, его компоненты -- это координаты веса в ортогональном базисе выбранном согласно Бурбаки \cite{bourbaki2002lie}.
+Аффинный вес представляет собой расширение конечномерного веса с добавлением уровня и грейда.
 
-Affine weight is an extension of a finite weight by supplying it
-with level and grade coordinates. There is a set of functions
-defined for finite and affine weights. The complete list can be
-found in  online help of the package. The most important
-are definitions of addition, multiplication by a number and a
-scalar product (bilinear form) for weights. These definitions
-allow to use traditional notation when working with {\bf
-Affine.m}:
+В пакете {\bf Affine.m} содержится набор функций для работы с весами конечномерных и аффинных алгебр Ли.
+Полный список доступен во встроенной справке пакета.
+Важнейшие из них -- это определение операций сложения, умножения на число и скалярного произведения (билинейной формы) для весов.
+В результате можно использовать традиционные обозначения при работе с  {\bf Affine.m}:
 \begin{lstlisting}
@@
 
-The use of orthogonal basis in the internal structure of weights allows us to work with weights without complete specification of root system which is useful for study of branching, since roots of the subalgebra can be specified by hand.
+Использование ортогонального базиса во внутренней структуре весов позволяет нам работать с весами без полного задания корневой системы.
+Это полезно при изучении редукции на подалгебры, так как корни подалгебры можно задать вручную, путем указания их координат в ортогональном базисе.
 
-\subsection{Root systems}
+\subsection{Корневые системы}
 \label{sec:root-systems}
 
-To specify an algebra of finite or affine type it is enough to fix
-its root system. Root systems are represented by two datatypes
-\lstinline{finiteRootSystem} and \lstinline{affineRootSystem}. The
-latter is an extension of the former. We offer several different
-constructors for these datastructures. It is possible to specify
-the set of simple roots explicitly, for example to study the
-subalgebra $B_2\subset B_4$ we can use the definition
+Чтобы задать конечномерную или аффинную алгебру достаточно определить ее корневую систему.
+Корневые системы представляются двумя структурами данных \lstinline{finiteRootSystem} и \lstinline{affineRootSystem}.
+Вторая структура является расширением первой.
+Мы предлагаем несколько конструкторов для этих структур данных.
+Во-первых, можно определить простое корни явно, например, при изучении вложения $B_2\subset B_4$ можно использовать определение
 \begin{lstlisting}
@@
 \end{lstlisting}
-There are constructors for root systems of simple finite-dimensional Lie algebras:
+Для корневых систем простых конечномерных алгебр Ли есть специальные конструкторы:
 \begin{lstlisting}
@@
 \end{lstlisting}
-We use typographic features of {\it Mathematica} frontend to offer mathematical notation for simple Lie algebras:
+В графическом интерфейсе {\it Mathematica} можно использовать традиционные математические обозначения для простых алгебр Ли:
 
@@
 
-Non-twisted affine root systems can be created as affine extensions of finte root systems, e.g.
+Нескрученные аффинные корневые системы могут быть созданы как аффинные расширения корневых систем конечномерных алгебр Ли, например:
 \begin{lstlisting}
@@
 \end{lstlisting}
-In notebook interface this can be written simply as $\hat{B}_2$.
+В графическом интерфейсе это же определение можно ввести просто как $\hat{B}_2$.
 
-Semisimple Lie algebras can be created as sums of simple:
+Полупростые алгебры Ли представляют собой прямые суммы простых:
 \begin{lstlisting}[mathescape=true]
@@
 
-Predicate \lstinline{rootSystemQ} checks if the object is root systems of finite or affine type.
+Предикат \lstinline{rootSystemQ} проверяет, является ли объект корневой системой конечномерной или аффинной алгебры Ли.
 
-List of simple roots is the property of root system so it is accessed as \lstinline{rs[simpleRoots]}.
+Список простых корней -- это определяющее свойство корневой системы, поэтому он доступен как \lstinline{rs[simpleRoots]}.
 
-We have implemented several functions to get major properties of root systems. Weyl vector is given by the function \lstinline{rho[rs_?rootSystemQ]}:
+В пакете реализовано несколько функций для основных характеристик корневой системы. Вектор Вейля дается функцией
+\lstinline{rho[rs_?rootSystemQ]}:
 \begin{lstlisting}[label=list:1]
@@
 \end{lstlisting}
-Positive roots can be constructed with \lstinline{positiveRoots[rs_?rootSystemQ]}.
-For an affine Lie algebra this and related functions return the list up to fixed grade.
-This grade limit is set through the value of \lstinline{rs[gradeLimit]} which is equal to 10 by default.
-List of roots (up to \lstinline{gradeLimit}) is returned by \lstinline{roots[rs]}.
-Cartan matrix and fundamental weights are calculated by the functions \lstinline{cartanMatrix} and \lstinline{fundamentalWeights} correspondingly.
+Положительные корни строятся функцией  \lstinline{positiveRoots[rs_?rootSystemQ]}.
+Для аффинной алгебры Ли эта и аналогичные функции возвращают список до некоторого фиксированного грейда.
+Это максимальное значение грейда задается как свойство \lstinline{rs[gradeLimit]} и по умолчанию равняется 10.
+Список корней  (вплоть до грейда \lstinline{gradeLimit}) строится функцией \lstinline{roots[rs]}.
+Матрица Картана и фундаментальные веса вычисляются функциями \lstinline{cartanMatrix} и \lstinline{fundamentalWeights} соответственно.
 
-It is possible to specify a weight of a Lie algebra by its Dynkin labels
+Вес алгебры Ли можно задать его индексами Дынкина
 \begin{lstlisting}
@@
 \end{lstlisting}
-The function \lstinline{dynkinLabels[rs_?rootSystemQ][wg_?weightQ]} returns Dynkin labels of weight \lstinline{wg} in the root system \lstinline{rs}.
+Функция \lstinline{dynkinLabels[rs_?rootSystemQ][wg_?weightQ]} возвращает индексы Дынкина веса \lstinline{wg} по отношению к корневой системе \lstinline{rs}.
 
-Elements of Weyl group are specified by the set of indices of reflections, so the element  $w=s_{1}s_{2}s_{1}$ of the Weyl group of algebra $B_{2}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
-Then it can be applied to the weights:
+Элементы группы Вейля задаются номерами элементарных отражение, так что элемент  $w=s_{1}s_{2}s_{1}$ группы Вейля алгебры Ли $B_{2}$ строится вызовом функции \lstinline{weylGroupElement[b2][1,2,1]}.
+После этого его можно применить к весам:
 \begin{lstlisting}
@@
 
-Computation of lexicographically minimal form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching in {\it Mathematica}.
-In \cite{KallenShortlex} rewrite rules for simple finite dimensional and affine Lie algebras are presented as {\it Mathematica} patterns.
-Our presentation of Weyl group elements is compatible with the code of \cite{KallenShortlex}
+Вычисление лексикографически минимальной формы \cite{casselman1994machine,casselman1995automata} для элементов группы Вейля можно реализовать при помощи шаблонов в  {\it Mathematica}.
+В работе \cite{KallenShortlex} представлены правила подстановки на языке {\it Mathematica} для такого вычисления в случае простых конечномерных и аффинных алгебр Ли.
+Наше представление для элементов группы Вейля совместимо с кодом \cite{KallenShortlex}:
 \begin{lstlisting}[mathescape=true]
@@
 
-\subsection{Formal elements}
+\subsection{Формальные элементы}
 \label{sec:formal-elements}
 
-We represent formal characters of representations by special structure \lstinline{formalElement}.
-This structure is a hash-table implemented with \lstinline{DownValues}.
-The keys are weights at the exponents and the values are the  corresponding multiplicities.
-\lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]!
-creates data-structure which represents the element $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ of the formal algebra $\mathcal{E}$.
-The operations in $\mathcal{E}$ are implemented for \lstinline{formalElement} data-type: formal elements can be added, multiplied by a number or by an exponent of a weight.
-There exists also a multiplication of formal elements but no division.
+Формальные элементы представляются специальной структурой данных \lstinline{formalElement}.
+Эта структура данных представляет собой хэш-таблицу, реализованную через механизм \lstinline{DownValues}.
+Ключами в таблице выступают веса, стоящие в экспонентах формального элемента, а значениями -- соответствующие кратности.
+Вызов \lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]!
+создает структуру данных, представляющую элемент $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ формальной алгебры $\mathcal{E}$.
+Операции в алгебре  $\mathcal{E}$ реализованы для структуры \lstinline{formalElement}: формальные элементы можно складывать, умножать на число или экспоненту веса.
+Кроме того, есть умножение формальных элементов, но нет операции деления.
 \begin{lstlisting}[mathescape=true]
@@
 
-\subsection{Modules}
+\subsection{Модули}
 \label{sec:modules}
 
-{\bf Affine.m} can be used to study different kinds of modules, i.e.
-Verma modules, irreducible modules and parabolic Verma modules.
-We need datastructure \lstinline{module} to represent generic module of Lie algebra $\gf$.
+{\bf Affine.m} можно использовать для изучения различных видов модулей, например, модулей Верма, неприводимых модулей и параболических модулей Верма.
+Для представления произвольного модуля используется структура данных  \lstinline{module}.
+
 Module properties can be deduced from its set of singular weights using Weyl character formulae \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}.

### 2011-12-15 AffineLieAlgebras/Thesis/5.tex
Translation of Affine.m paper completed.

@@
 Для представления произвольного модуля используется структура данных  \lstinline{module}.
-
-Module properties can be deduced from its set of singular weights using Weyl character formulae \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}.
-Set of singular weights can have Weyl symmetry.
-It can be a symmetry with respect to the Weyl group $W_{\gf}$ or with respect to some subalgebra $W_{\af}$ as in the case of parabolic Verma modules.
-Then it is possible to study only the main Weyl chamber $C_{\af}$.
-To use this symmetry generic constructor for \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],limit:10}.
-Here \lstinline{rs} is the root system of the Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is the root system corresponding to the Weyl group $W_{\af}$ which is the (anti-)symmetry of the set of singular weights.
-Parameter \lstinline{limit} limits computation for infinite-dimensional modules such as Verma or parabolic Verma.
-There are several specialized constructors for different types of highest weight modules:
+Свойства модуля можно вывести из набора его сингулярных весов используя формулы Вейля для характеров \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}.
+Множество сингулярных весов может обладать вейлевой симметрией.
+Это может быть симметрия по отношению к действию группы Вейля алгебры  $W_{\gf}$ или по отношению к действию группы Вейля некоторой подалгебры $W_{\af}$, как в случае параболических модулей Верма.
+В этом случае можно ограничиться изучением главной камеры Вейля $C_{\af}$.
+Чтобы воспользоваться такой симметрией общий конструктор для структуры данных \lstinline{module} принимает несколько параметров \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],limit:10}.
+Здесь \lstinline{rs} -- корневая система алгебры Ли $\gf$,\lstinline{singWeights} -- набор сингулярных весов,  \lstinline{subs} -- корневая система, соответствующая группе Вейля  $W_{\af}$, являющейся группой (анти-)симметрии множества сингулярных весов.
+Параметр \lstinline{limit} ограничивает вычисления в случае бесконечномерных модулей, таких, как модули Верма и параболические модули Верма.
+Существует несколько специализированных конструкторов для различных типов модулей старшего веса:
 \begin{lstlisting}[mathescape=true]
@@
 
-As we already stated properties of a module are encoded by its singular element.
-Function \lstinline{singularElement[m_module]} returns singular element of a module as \lstinline{formalElement} datastructure.
-Character (up to \lstinline{limit} for (parabolic) Verma modules) is returned by the function \lstinline{character[m_module]}.
-Direct sum of modules is a module and we use natural notation
+Как мы уже отмечали, свойства модулей определяются его сингулярным элементом.
+Функция  \lstinline{singularElement[m_module]} возвращает сингулярный элемент модуля в виде структуры данных  \lstinline{formalElement}.
+Характер  (вплоть до предела \lstinline{limit} для  (параболических) модулей Верма) вычисляется функцией \lstinline{character[m_module]}.
+Прямая сумма модулей является модулем и мы используем естественные обозначения
 \begin{lstlisting}[mathescape=true]
@@
 
-The tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
+Тензорное произведение модулей тоже реализовано, но только для модулей конечномерных алгебр Ли.
+Это связано с тем, что тензорные произведения модулей аффинных алгебр Ли приводят к возникновению различных дополнительных структур  \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2}, изучение которых пока лежит за пределами наших интересов.
 \begin{lstlisting}[mathescape=true]
@@
 \end{lstlisting}
-\section{Computational algorithms}
+\section{Основные алгоритмы}
 \label{sec:comp-algor}
 
-As we have already stated in section \ref{sec:high-weight-modul} there exist two recurrent relations which can be used to calculate weight multiplicities in irreducible modules.
-Both algorithms proceed in the following way to calculate weight multiplicities:
+Существует два рекуррентных соотношения \eqref{eq:15}, \eqref{eq:14}, которые можно использовать для вычисления кратностей весов в неприводимых модулях. Оба алгоритма состоят из следующих шагов:
 \begin{enumerate}
-\item Create the list of weights in the main Weyl chamber by subtracting all possible combinations of simple roots from the highest weight (e.g.
-for finite-dimensional algebra subtract $\alpha_{1}$ from $\mu$ while inside $\bar C$, then subtract $\alpha_{2}$ from all the weights already obtained etc).
-\item Sort the list of weights by their product with the Weyl vector.
-\item Use a recurrent formula. If the weight required for recurrent computation is outside the main chamber use the Weyl symmetry.
+\item Построение списка весов в главной камере Вейля путем вычитания всех возможных комбинаций простых корней их старшего веса (например, для конечномерной алгебры вычитаем корень  $\alpha_{1}$ из старшего веса $\mu$ до тех пор, пока остаемся внутри  $\bar C$, затем вычитаем корень $\alpha_{2}$ из всех весов полученных на перво шаге и так далее).
+\item Сортировка списка весов по значению их скалярного произведения с вектором Вейля.
+\item Рекуррентное вычисление кратностей по формуле. Если вес, необходимый для вычислений оказывается вне главной камеры Вейля, то используется симметрия относительно группы Вейля.
 \end{enumerate}
-The difference in the performance of algorithms is in the number of previous values required to get the multiplicity of weight under consideration.
-For  the Weyl formula based recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in the Weyl group (if we are far from the boundary of representation diagram).
-When the Freudenthal formula \eqref{eq:15} is used number of previous values grows with the distance from the external border of representation.
-So the Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
-Note that the Freudenthal formula is valid for irreducible modules only, so it can not be used to study (generalized) Verma modules.
+Различие в производительности алгоритмов происходит от количества предыдущих значений, требующихся для вычисления кратности веса.
+В случае рекуррентного соотношения, основанного на формуле Вейля  \eqref{eq:14} это количество постоянно и равно числу элементов в группе Вейля (если мы находимся далеко от внешнего контура диаграммы представления).
+При использовании формулы Фрейдентала \eqref{eq:15} требуемое число предыдущих значений растет с расстоянием от внешнего контура диаграммы представления.
+Поэтому формула Фрейденталя работает быстрее, если вес близок к границе или ранг алгебры и размер группы Вейля велик \cite{moody1982fast}.
+Заметим, что формула Фрейденталя работает только для неприводимых модулей и не подходит для изучения (обобщенных) модулей Верма.
 
-We have made some experiments with our implementations of the Freudenthal formula and formula \eqref{eq:15} and have got Figure  \ref{fig:freudenthal-racah-times}, which depicts the dependence of the computation time on the number of weights in a module.
+Мы осуществили тестирование производительности наших реализаций алгоритмов, основанных на формуле Фрейденталя и формуле \eqref{eq:15} и получили результаты, представленные на Рисунке  \ref{fig:freudenthal-racah-times}.
+Там показана зависимость времени вычислений от числа весов в модуле.
 
@@
   }
-  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{eq:14} (solid) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
+  \caption{Время работы алгоритмов, основанных на формуле Фрейденталя \eqref{eq:15} (пунктир) и рекуррентном соотношении \eqref{eq:14} (сплошная линия) в зависимости от количества весов в  $\bar C$ для вычисления кратностей в представлениях алгебры $B_{2}$.}
 \label{fig:freudenthal-racah-times}
@@
 
-In the calculation of branching coefficients the application of the Freudenthal formula requires a complete construction of formal characters of an algebra module and all the representations of a subalgebra.
-It is impractical when the rank of algebra and subalgebra are big, for example for maximal subalgebras.
+При вычислении коэффициентов ветвления использование формулы Фрейденталя требует полного построения формальных характеров представления алгебры и всех представлений подалгебры, входящих в его разложение.
+Такой подход становится непрактичным для большого ранга алгебры и подалгебры, например, при максимальных вложениях.
 
-Alternative algorithm which was presented in the paper \cite{2010arXiv1007.0318L}  contains the following steps:
+Альтернативный алгоритм описан в разделе \ref{sec:algorithm}.
+Рассмотренный там же пример регулярного вложения \ref{sec:someth-high-dimens}  $B_{2}\subset B_{4}$ позволяет сделать следующее сравнение числа требующихся операций.
+В данном примере веер вложения состоит из 24 элементов.
+Для разложения модуля алгебры  $B_{4}$ необходимо построить подмножество сингулярных весов модуля, проектирующихся в главную камеру Вейля подалгебры $B_{2}$.
+Полное множество сингулярных весов состоит из 384 элементов, в главную камеру Вейля проектируется не более 48, так что время на построение этого множества пренебрежимо мало, если число коэффициентов ветвления более 48.
+Мы можем оценить сверху общее число операций для вычисления коэффициентов ветвления произведением числа весов в главной камере Вейля подалгебры с ненулевыми коэффициентами ветвления на число элементов веера вложения.
+С другой стороны, при использовании алгоритма, основанного на построении всех характеров при помощи формулы Фрейденталя мы должны вычислить кратности для каждого модуля в разложении, так что общее количество операций растет с ростом числа весов в представлении быстрее, чем квадрат числа весов в главной камере Вейля подалгебры с ненулевыми коэффициентами ветвления.
 
-\begin{enumerate}
-\item  Construct the root system $\Delta _{\af}$ for the embedding $%
-\af\rightarrow \frak{g}$.
-
-\item  Select all the positive roots $\alpha \in \Delta ^{+}$ orthogonal
-to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
-
-\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. Relation
- (\ref{eq:6}) defines the sign function
- $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
- $\gamma_0$ is to be subtracted to get the fan:
- $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}$.
-
-\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
-)-\rho ;\;w \in W\right\} $ of singular weights for the $\frak{g}$%
--module $L^{(\mu )}$.
-
-\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
-}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
-)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
-\af_{\perp }}}}\right\} $. Since the set $\Delta_{\afb }^{+}$ is fixed
-we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
-}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
-\af_{\perp }}}}$ (by computing its scalar product with the fundamental
-weights of $\afb^{+}$).
-
-\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
-calculate dimensions of the corresponding modules, $\mathrm{\dim }\left(
-L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
-}\left( u\right) }\right) $, using the Weyl dimension formula and construct
-the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
-
-\item  Calculate the anomalous branching coefficients using 
-recurrent relation (\ref{recurrent-rel}) and select among them those
-corresponding to the weights in the main Weyl
-chamber $\overline{C_{\af}}$.
-\end{enumerate}
-
-We can speed up the algorithm by
-one-time computation of the representatives of the conjugate classes $%
-W/W_{\afb }$.
-
-Consider the regular embedding $B_{2}\subset B_{4}$.
-In this case the fan consists of 24 elements.
-In order to decompose $B_{4}$ module we need to construct the subset of singular weights of the module which projects to the main Weyl chamber of the subalgebra $B_{2}$.
-The full set of singular weights consists of 384 elements.
-The required subset contains at most 48 elements.
-So the time for the construction of this required subset is negligible if the number of branching coefficients is greater than that.
-We may estimate the total number of required operations for the computation of branching coefficients as the product of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients and the number of elements in the fan.
-In the case of a direct algorithm we need to compute the multiplicities for each module in the decomposition, so the number of operations grows faster than the square of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients.
-
-To further illustrate this performance issue we include Figure \ref{fig:branching} where we show the time required for computations of branching coefficients for $B_{3}\subset B_{4}$.
+Чтобы проиллюстрировать эту разницу в производительности алгоритмов, мы приводим Рисунок \ref{fig:branching}, на котором показано время, необходимое для вычисления коэффициентов ветвления для вложения $B_{3}\subset B_{4}$.
 
@@
   }
-  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{recurrent-rel} (solid) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
+  \caption{Время работы алгоритмов, основанных на применении формулы Фрейденталя \eqref{eq:15} (пунктиром)  и рекуррентного соотношения \eqref{recurrent-rel} (сплошная линия) с ростом числа весов в  $\bar C$ при вычислении коэффициентов ветвления для вложения $B_{3}\subset B_{4}$.}
   \label{fig:branching}
@@
 
-\section{Examples}
+\section{Примеры}
 \label{sec:examples}
-In this section we present some examples of computations available with {\bf Affine.m} with the code required to produce these results.
+В этом разделе мы приводим примеры вычислений, проведенных с использованием {\bf Affine.m} и код, который для этого потребовался.
 
-\subsection{Tensor product decompositon for finite-dimensional Lie algebras}
+\subsection{Разложение тензорных произведений модулей конечномерных алгебр Ли на неприводимые}
 \label{sec:tens-prod-decomp}
 
-Computation of fusion coefficients for the decomposition of tensor product of highest-weight modules to the direct sum of irreducible modules has numerous applications in physics.
-For example, we can consider the spin of a composite system such as an atom.
-Another interesting example is integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of a Lie algebra $\gf$ with a $\gf$-invariant Hamiltonian $H$, describing the nearest-neighbour spin-spin interaction.
-In order to solve such a system, i.e.
-to find eigenstates of the Hamiltonian, we need to decompose $L^{\otimes N}$ into the direct sum of irreducible $\gf$-modules of lower dimension and diagonalize the Hamiltonian on these modules.
+Вычисление коэффициентов слияния для разложения тензорного произведения модулей старшего веса в прямую сумму неприводимых модулей важно для различных приложений в физике.
+Например, мы можем рассматривать спин составной системы, такой как атом.
+Другой интересный пример -- это интегрируемые спиновые цепочки, состоящие из  $N$ частиц со спинами, живущими в некотором представлении  $L$ алгебры Ли $\gf$, с  $\gf$-инвариантным гамильтонианом $H$, описывающим спин-спиновое взаимодействие ближайших соседей.
+Чтобы решить такую систему, то есть найти собственные состояния гамильтониана, мы должны разложить  $L^{\otimes N}$ в прямую сумму неприводимых $\gf$-модулей меньшей размерности и диагонализовывать гамильтониан на этих модулях.
 
-For fundamental representations of simple Lie algebras it is sometimes possible to get an analytic result describing the dependence of decomposition coefficients on $N$ (See \cite{LyakhovskyPostnova2011}).
-Our code provides numerical values and can be used to check this analytic results.
+Для фундаментальных представлений простых алгебр Ли иногда можно написать аналитический ответ, описывающий зависимость коэффициентов разложения от  $N$ (См.
+работу \cite{LyakhovskyPostnova2011}).
+Наш код позволяет получать численные ответы, которые можно использовать для проверки этих аналитических результатов.
 
-Consider a tensor power of $B_{2}$ the first fundamental representation $\left(L^{[1,0]}\right)^{\otimes 4}$. Decomposition coefficients are just the branching
- coefficients for the tensor power module reduced to the diagonal subalgebra $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$. So the following code calculates these coefficients:
+Рассмотрим тензорную степень $\left(L^{[1,0]}\right)^{\otimes 4}$ первого фундаментального представления алгебры $B_{2}$.
+Коэффициенты разложения тензорной степени на неприводимые модули -- это коэффициенты ветвления модуля алгебры $B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$ на диагональную подалгебру $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$.
+Следующий код осуществляет необходимые вычисления:
 \begin{lstlisting}[mathescape=true]
@@
 \end{lstlisting}
-It produces a list of highest weights and tensor product decomposition coefficients:
+Он выдает в результате следующий набор старших весов и коэффициентов разложения:
 \begin{lstlisting}
@@
 
-Returning to the problem of spin chain Hamiltonian diagonalization we can see that instead of diagonalizing operator in space of dimension $625$ we can diagonalize operators in the spaces of dimensions $55, 81, 30, 35, 35, 14, 10, 5, 1$.
+Возвращаясь к проблеме диагонализации гамильтониана спиновой цепочке, мы можем заметить, что вместо диагонализации оператора в пространстве размерности  $625$ мы можем диагонализовывать операторы в пространствах размерностей $55, 81, 30, 35, 35, 14, 10, 5, 1$.
 
-\subsection{Branching and parabolic Verma modules}
+\subsection{Ветвления и параболические модули Верма}
 \label{sec:branch-parab-verma}
 
-We illustrate the generalized BGG-resolution by the diagrams of $G_{2}$ parabolic Verma modules which appear in the decomposition of irreducible module $L^{[1,1]}_{G_{2}}$:
+Мы иллюстрируем обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда (см.
+главу \ref{cha:BGG}) диаграммами параболических модулей Верма алгебры $G_{2}$, возникающих в разложении неприводимого модуля $L^{[1,1]}_{G_{2}}$:
 \begin{equation}
@@
 \end{equation}
-The character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, characters of the generalized Verma modules in decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}.
-Characters in the upper row appear in \eqref{char-in-gen-verma-mod} with positive sign and in the lower row -- with negative.
+Характер  $L^{[1,1]}$ представлен на Рисунке \ref{branching-bgg}, характеры обобщенных модулей Верма в разложении  \eqref{char-in-gen-verma-mod} показаны на Рисунке  \ref{g2-pverma}.
+Характеры в верхнем ряду входят в формулу \eqref{char-in-gen-verma-mod} со знаком плюс, в нижнем -- со знаком минус.
 
@@
   }
-  \caption{Character of the irreducible $G_{2}$-module $L^{[1,1]}$}
+  \caption{Характер неприводимого модуля  $L^{[1,1]}$ алгебры $G_{2}$}
   \label{branching-bgg}
@@
   }
-  \caption{Characters of $G_{2}$ generalized Verma modules appearing in the decomposition of $L^{[1,1]}$.
-Parabolic Verma modules in the upper row appear in the decomposition with a positive sign, in the lower row -- with a negative.}
+  \caption{Характеры обобщенных модулей Верма алгебры $G_{2}$, входящие в разложение характера $L^{[1,1]}$.
+Параболические модули Верма в верхнем ряду входят в разложение со знаком плюс, в нижнем -- со знаком минус.}
   \label{g2-pverma}
@@
 
-\subsection{String functions of affine Lie algebras and CFT models}
+\subsection{Струнные функции аффинных алгебр Ли и модели конформной теории поля}
 \label{sec:string-funct-affine}
+Струнные функции можно использовать для описания формальных характеров представлений старшего веса аффинных алгебр Ли.
+Эти функции обладают интересными аналитическими и модулярными свойствами \cite{kac1990idl,kac1988modular,kac1984infinite}.
 
-String functions can be used to present formal characters of affine Lie algebra highest weight representation.
-They have interesting analytic and modular properties \cite{kac1990idl,kac1988modular,kac1984infinite}.
-
-{\bf Affine.m} produces power series decomposition for string functions.
-Consider an affine Lie algebra $\hat{sl(3)}=\hat A_{2}$ and its highest weight module $L^{(1,0,0)}$.
-To get the string functions we can use the code:
+{\bf Affine.m} позволяет вычислять степенное разложение для струнных функций.
+Рассмотрим аффинную алгебру Ли $\hat{sl(3)}=\hat A_{2}$ и ее модуль старшего веса $L^{(1,0,0)}$.
+Чтобы получить струнные функции используем следующий код:
 \begin{lstlisting}[mathescape=true]
@@
 \end{lstlisting}
-Similarly for the affine Lie algebra $\hat G_{2}$ we get
+Аналогично для аффинной алгебры Ли $\hat G_{2}$ получаем
 \begin{lstlisting}[mathescape=true]
@@
 
-\subsection{Branching functions and coset models of conformal field theory}
+\subsection{Функции ветвления и  coset-модели конформной теории поля}
 \label{sec:branch-funct-coset}
 
-It is believed that most rational models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$.
-These models can be studied as gauge theories \cite{Hwang:1994yr, hwang1993brst}.
+Считается, что рациональные модели конформной теории поля могут быть получены как  $G/A$ coset-модели, соответствующие вложениям $\af\subset\gf$.
+Эти модели можно реализовать как калибровочные теории  \cite{Hwang:1994yr, hwang1993brst} (см.
+раздел \ref{sec:coset-models-cft}).
 
-Branching functions for an embedding $\af\subset\gf$ are the partition functions of CFT on the torus (see \cite{difrancesco1997cft}).
+Функции ветвления для вложения  $\af\subset\gf$ являются статсуммами для моделей конформной теории поля на торе (см. \cite{difrancesco1997cft}).
 
-As a first example we show how to construct branching functions for the embedding $\hat A_{1}\to \hat B_{2}$ up to the tenth grade:
+В качестве первого примера мы демонстрируем вычисление функций ветвления для вложения $\hat A_{1}\to \hat B_{2}$ до десятого грейда:
 \begin{lstlisting}[mathescape=true]
@@
 
-Another example demonstrates the computation of branching functions for the regular embedding $\hat B_{2}\subset \hat C_{3}$:
+Второй пример -- это вычисление функций ветвления для регулярного вложения  $\hat B_{2}\subset \hat C_{3}$:
 \begin{lstlisting}[mathescape=true]
@@
 
-\section{Conclusion}
+\section{Заключение}
 \label{sec:conclusion}
-We have presented the package {\bf Affine.m} for computations in representation theory of finite-dimensional and affine Lie algebras.
-It can be used to study Weyl symmetry, root systems, irreducible, Verma and parabolic Verma modules of finite-dimensional and affine Lie algebras.
-In the present paper we have also discussed main ideas used for an implementation of the package and described most important notions of representation theory required to use {\bf Affine.m}.
+В данной главе мы представили пакет {\bf Affine.m} для вычислений в теории представлений конечномерных и аффинных алгебр Ли.
+Он может использоваться для изучения групп Вейля, корневых систем, неприводимых модулей, модулей Верма и параболических модулей Верма конечномерных и аффинных алгебр Ли.
+Кроме того, мы обсудили основные идеи в реализации пакета  {\bf Affine.m}.
 
-We have demonstrated that recurrent approach based on the Weyl character formula is not only useful for calculations but also allows to establish connections with the (generalized) Bernstein-Bernstein-Gelfand resolution.
+Мы показали, что рекуррентный подход, основанный на формуле Вейля для характеров полезен не только для вычислений, но и позволяет прояснить связь с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
 
-Also we have presented examples of computations with this package connected with problems of physics and mathematics.
+Также мы представили примеры вычислений с применением нашего пакета, полезных для различных физических и математических проблем.
 
-In future versions of our software we are going to treat twisted affine Lie algebras, extended affine Lie algebras and provide more direct support for tensor product decompositions.
+В следующих версиях программы мы планируем реализовать работу со скрученными аффинными алгебрами Ли, расширенными аффинными алгебрами и реализовать более полную поддержку вычислений коэффициентов разложения тензорных произведений.
 
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-I thank V.D. Lyakhovsky and O.Postnova for discussions and helpful comments.
+\appendix
 
-The work is supported by the Chebyshev Laboratory
-(Department of Mathematics and Mechanics, Saint-Petersburg State
-University) under the grant 11.G34.31.0026 of the Government of the
-Russian Federation.
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%\appendix
-
-\section{Software package}
+\section{Описание пакета}
 \label{package}
-The package can be freely downloaded from \url{http://github.com/naa/Affine}. To get the development code use the command
+Пакет может быть бесплатно загружен с сайта \url{http://github.com/naa/Affine}. Чтобы получить разрабатываемую версию кода можно использовать систему управления версиями {\it git} и команду
 \begin{lstlisting}[language=bash]
@@
 
-Contents of the package:
+Содержимое пакета:
 \begin{verbatim}
-    Affine/                                root folder
-      demo/                                  demonstrations
-        demo.nb                                demo notebook
-        paper.nb                               code for the paper
-      doc/                                 documentation folder
-        figures/                             figures in paper 
-          timing.pdf                           diagram showing performance
-          branching-timing.pdf                 ...  for branching coefficients  
-          irrep-sum.pdf                        sum of B2 irreps
-          irrep-verma-pverma.pdf               irrep, Verma, (p)Verma for B2
-          G2-irrep.pdf                         irrep for G2
-          G2-pverma.pdf                        parabolic Verma for G2
-          tensor-product.pdf                   tensor product of A1-modules
-        bibliography.bib                     bibliographic database
-        paper.pdf                            present paper
-        paper.tex                            paper source
-        TODO.org                             list of issues
-      src/                                 source folder
-        affine.m                             main software package
-      tests/                               unit tests folder
-        tests.m                              unit tests
-      README.markdown                      installation and usage notes
+    Affine/                              Корневой каталог
+      demo/                               Демонстрации
+        demo.nb                                Демонстрационный файл
+        paper.nb                               Код, содержащийся в статье 
+      doc/                                 Каталог документации
+        figures/                             рисунки в статье
+          timing.pdf                           диаграмма, показывающая производительность
+          branching-timing.pdf                 ...  для коэффициентов ветвления
+          irrep-sum.pdf                        сумма неприводимых представлений B2
+          irrep-verma-pverma.pdf               неприводимое представлений, модуль Верма и обобщенный модуль Верма для B2
+          G2-irrep.pdf                         неприводимое представление G2
+          G2-pverma.pdf                        параболический модуль Верма для G2
+          tensor-product.pdf                   тензорное произведение модулей  A1
+        bibliography.bib                     Библиографическая база
+        paper.pdf                            Статья, описывающая пакет
+        paper.tex                            Исходный LaTeX-файл статьи
+        TODO.org                             Список доработок
+      src/                                 Каталог исходного кода
+        affine.m                             основной пакет
+      tests/                               Каталог тестов
+        tests.m                              тесты
+      README.markdown                    Инструкция по установке и использованию
 \end{verbatim}

### 2011-12-17 AffineLieAlgebras/Splints/paper2.tex
Some text in new paper on affine splints

@@
 \newcommand{\af}{\mathfrak{a}}
+\newcommand{\uf}{\mathfrak{u}}
+\newcommand{\sfr}{\mathfrak{s}}
 \newcommand{\aft}{\widetilde{\mathfrak{a}}}
@@
 \newcommand{\afh}{\hat{\mathfrak{a}}}
+\newcommand{\sfh}{\hat{\mathfrak{s}}}
 \newcommand{\bff}{\mathfrak{b}}
@@
 
+The term {\it splint} was
+introduced by D. Richter in  \cite{richter2008splints} where the
+classification of splints for simple Lie algebras was obtained.
+There was also mentioned that splint must have tight
+connections with the injection fan construction. The fan $\Gamma
+\subset \Delta$ was
+introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent
+properties of branching coefficients for maximal embeddings. Injection fan is an
+efficient tool to study branching rules. Later this construction
+was generalized to non-maximal embeddings and affine Lie algebras
+Lie algebras in \cite{2010arXiv1007.0318L, ilyin812pbc}.
+
+In paper \cite{2011arXiv1111.6787L} we have shown that existence of splint of root system of simple Lie algebra leads to simplification of reduction of Lie algebra module to modules of subalgebra.
+This statement is based upon the properties of injection fan and singular element of Lie algebra module.
+
+In present note we discuss the poss applications of splint of root system of simple Lie algebra to representation theory of affine Lie algebras.
+We discuss the structure of injection fan for affine Lie algebras and show that it admits decomposition similar to that used in \cite{2011arXiv1111.6787L} for simple Lie algebras.
+But there is no such decomposition for singular elements due to semidirect product structure of Weyl group of affine Lie algebras.
+So there is no straightforward generalization of the coincidence of branching coefficients to weight multiplicities, and branching functions for affine Lie algebras in general do not coincide with string functions of other algebras.
+
+Then we study graded branching of affine Lie algebra module to finite-dimensional subalgebras and discuss the consequences of splint existence on branching functions in this case.
+
+\section{Definitions}
+\label{sec:definitions}
+
+Consider simple Lie algebra $\gf$ with root system $\Delta$.
+Let $\af_{1}\subset \gf$ be its reductive subalgebra, such that $\Delta_{1}\subset\Delta$.
+Irreducible highest-weight modules of $\gf$ and $\af$ are denoted by $L^{\mu}$ and $L^{\nu}_{\af}$ correspondingly.
+Weyl character formula for irreducible modules is $\mathrm{ch}L^{\mu}=\frac{\Psi^{(\mu)}}{\prod_{\alpha\in\Delta}(1-e^{-\alpha})}$, where $\Psi^{(\mu)}=\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}$ is singular element of the module and $W$ -- Weyl group of $\gf$.
+Formal character of irreducible module admits decomposition
+\begin{equation}
+  \label{eq:4}
+  \mathrm{ch} L^{\mu}=\sum_{\nu\in P_{\af}} b^{\mu}_{\nu} \mathrm{ch} L^{\nu}_{\af},
+\end{equation}
+where $P$, $P_{\af}$ are weight lattices of $\gf$ and $\af$.
+We want to study affine extension of this situation: $\gf\subset\gfh,\; \af\subset\afh$, $\afh\subset\gfh$, $\hat{\Delta}\subset\hat{\Delta}$ and $\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{\hat{\nu}} b^{\hat{\mu}}_{\hat{\nu}} \mathrm{ch} L^{\hat{\nu}}_{\afh}$.
+For weights of affine Lie algebra $\gfh$ we have $\hat{\mu}=(\mu,k,n)$, where $\mu$ is a weight of $\gf$, $k$ -- level of module and $n$ -- grade of weight $\hat{\mu}$
+
+\begin{Def}
+Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper) 
+subset of $\Delta$ that commutes with vector composition law in $\Delta_{1}$ and $\Delta$.
+\begin{equation*}
+\phi:\Delta_1 \longrightarrow \Delta
+\end{equation*}
+\begin{equation*}
+\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
+\,\,\, \alpha,\beta \in \Delta_1
+\end{equation*}
+
+\end{Def}
+
+Note that the image $Im(\phi)$ must not inherit the root system properties except the addition rules equivalent to the addition
+rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  can splinter $\Delta$  when the latter can be presented as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.
+
+$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
+\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
+_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
+\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+
+\begin{Def}
+A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if there are two embeddings $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
+\phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the disjoint union of the images of $\phi _{1}$ and $\phi _{2}$ and (b) neither the rank of $\Delta _{1}$ nor the rank of $\Delta _{2}$ exceeds the rank of $%
+\Delta $.
+\end{Def}
+
+It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$.
+Each component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $%
+(\Delta_1,\Delta_2)$.
+
+We consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem. As shown in paper \cite{2011arXiv1111.6787L} the second stem $\Delta _{\frak{s}}:=\Delta
+_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product 
+$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}$
+and it defines an injection fan $\Gamma _{\frak{a}%
+\hookrightarrow \frak{g}}$ \cite{lyakhovsky1996rra,ilyin812pbc,2010arXiv1007.0318L}.
+
+Since singular element of $\gf$-module $L^{\mu}$ can be written as $\Psi _{\frak{g}}^{\left( \mu \right) }=e^{-\rho } \sum_{w\in W_{\frak{a}}}w\circ \left(
+e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho _{\frak{s}}}\right)$  for branching coefficients we get the identity $b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}$  \cite{2011arXiv1111.6787L}.
+
+Now we consider affine extension of this setup, $\afh\subset\gfh$. Since $\mathrm{rank}\gf\leq \mathrm{rank} \af+\mathrm{rank}\sfr$
+for Weyl denominators we get
+ \[
+\prod_{\alpha\in\hat{\Delta}_{1}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}\prod_{\beta\in\hat{\Delta}_{2}}(1-e^{\phi\circ \beta})^{\mathrm{mult}(\beta)}=\prod_{\gamma\in\hat{\Delta}}(1-e^{-\gamma})^{\mathrm{mult}(\gamma)}\prod_{n=0}^{\infty}(1-e^{-n\delta})^{\mathrm{rank}\af+\mathrm{rank}\sfr-\mathrm{rank}\gf}
+\]
+
+This decomposition can lead to the conjecture that branching coefficients for the embedding $\afh\subset\gfh$ coincide with branching coefficients for the embedding $\widehat{\uf(1)\oplus\dots\oplus\uf(1)}\subset\sfh$ but we have no corresponding decomposition of singular elements.
+It can be seen from the following counterexample.
+
+\begin{example}
+  Consider affine extension of splint 
+  Consider the Lie algebra $A_{2} =\bf{sl}(3)$ and branching of its irreducible module $L^{[3,2]}_{A_{2}}$ with respect to the reductive subalgebra $A_{1}\oplus u(1)$.
+The root system  $\Delta _{\frak{a}}= \Delta_{A_{1}\oplus u(1)}$ contains the simple root of $\alpha_1=e_1-e_2$ of $A_{2}$.
+The singular element $\Psi^{[3,2]}_{\frak{a}}$ is decomposed into a sum of splint images of singular elements of $A_{1}\oplus A_{1}$-modules.
+Branching coefficients $b_{\nu }^{[ 3,2 ] }$ coincide with weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module (see Fig.
+\ref{fig:a2_splint}).
+
+  \begin{figure}[h!bt]
+  \noindent\centering{
+   \includegraphics[width=80mm]{a2-a1}
+  }
+  \caption{Weyl group orbit (dotted) producing singular element of $L^{[3,2]}_{A_{2}}$ and its decomposition into the sum of splint images of singular elements of modules  $L^{[3,2]}_{A_{1}\oplus A_{1}}$ (dashed).
+Weight multiplicities of $L^{[3,2]}_{A_{1}\oplus A_{1}}$-module coincide with branching coefficients for the reduction $L^{[3,2]}_{A_{2}\downarrow A_{1}\oplus u(1)}$.}
+
+ \label{fig:a2_splint}
+\end{figure}
+\end{example}
+
 Consider Lie algebra $\gf$ and its irreducible modules $L^{\mu}_{\gf}$. 
@@
 Richter in paper \cite{richter2008splints} to describe cases of drastic simplification of module reduction into the sum of subalgebra modules.
-In paper \cite{2011arXiv1111.6787L} we've proved that branching coefficients coincide with multiplicities (more details here).
+In paper \cite{2011arXiv1111.6787L} we've proved that branching coefficients coincide with multiplicities of the representation of second stem algebra.
 
@@
 \end{equation}
+
 Then each of these $\gf$-modules in this decomposition admits decomposition to $\af_{1}$ modules with branching coefficients equal to weight multiplicities of $\af_{2}$ irreducible module \cite{2011arXiv1111.6787L}.
@@
 \label{sec:main-theorem}
+
+When an injection is maximal the
+projection becomes trivial and the relation (\ref{recurrent rel}) is
+simplified:
+\begin{equation}
+\begin{array}{c}
+b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
+}+\right. \\
+\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
+\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
+\end{array}
+\label{recurrent relation max}
+\end{equation}
+The recursion is goverened by the set $\Gamma _{\frak{a}\rightarrow \frak{g}}
+$ called the injection fan. The latter is defined by the carrier set $%
+\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the coefficient
+function $s(\xi )$
+\[
+\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{ \xi \in P_{%
+\frak{a}}|s(\xi )\neq 0\right\}
+\]
+appearing in the expansion
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\frak{a}}^{+}}\left( 1-e^{
+-\alpha }\right) =-\sum_{\gamma \in P_{\frak{a}}}s(\gamma )e^{-\gamma };\quad
+\label{product}
+\end{equation}
+
 \begin{theorem}
+
+ So following statement holds:
+\begin{statement}
+\label{statement-1}
+\begin{equation}
+\frac{e^{\rho _{\frak{g}}}}{\prod_{\beta \in \Delta _{\frak{s}%
+}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
+}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }%
+}}M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
+\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}=\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
+\label{singular main-4}
+\end{equation}
+Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
+highest weights in the decomposition. The multiplicity $M_{\left( \frak{s}%
+\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
+}\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ defines the branching
+coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
+-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
+\[
+b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}.
+\]
+\end{statement}
+
+The extension to the case of non-twisted affine Lie algebras is not straightforward.
+The statement \ref{statement-1} is based upon the decomposition of the injection fan and the possibility to present the singular element of the algebra module as the linear combination of singular elements of second stem algebra modules.
+
   Consider reduction of affine Lie algebra $\gfh$-module $L^{\mu}_{\gfh}$ to finite-dimensional subalgebra $\af_{1}$. Then for branching coefficients following relation holds:

### 2011-12-21 GeneralOverview/Lectures/CFT-APTU-2011.tex
Added last lecture to 2011 course

--- 2011-03-14 GeneralOverview/Lectures/2dqft.tex
@@
   \label{eq:109}
-  f=-\lim_{N\to \infty}\frac{Z_N}{N}.
+  f=-\lim_{N\to \infty}\frac{\ln Z_N}{N}.
 \end{equation}
@@
 
+\section{Лекция 13. Уравнения на корреляционные функции в минимальных моделях}
+\label{sec:lecture-13}
+
+Чтобы окончательно зафиксировать структуру двумерной конформной теории поля введем два дополнительных предположения.
+Во-первых, мы предполагаем, что локальные поля образуют алгебру $\mathcal{A}$ по отношению к операторному разложению \eqref{eq:248}\eqref{eq:249}.
+
 Ненулевые операторные разложения между членами конформных семейств определяются разложениями примарных полей. Поэтому можно писать сразу для семейств
@@
 \end{equation}
-В модели Изинга у нас есть три семейства $[1], [\sigma], [\varepsilon]$. Из наличия симметрий ($\sigma\to - \sigma$ и $\varepsilon\to -\varepsilon$ (дуальность Крамерса-Ванье)) имеем:
+
+При этом в минимальных моделях, где число примарных полей конечно, сумма \eqref{eq:300} оказывается конечной.
+Например, в модели Изинга у нас есть три семейства $[1], [\sigma], [\varepsilon]$. Из наличия симметрий ($\sigma\to - \sigma$ и $\varepsilon\to -\varepsilon$ (дуальность Крамерса-Ванье)) имеем:
 \begin{eqnarray}
@@
 \end{eqnarray}
-Отсюда можно вычислять все корреляционные функции. Например, для четырехточечной функции получается:
+
+Кроме того, потребуем, чтобы все состояния в гильбертовом пространстве порождались полями из алгебры локальных полей $\mathcal{A}$ из вакуума (state-field correspondence):
+\begin{equation}
+  \label{eq:307}
+  \forall \left| a\right> \in \mathbb{H}\quad \exists \varphi\in\mathcal{A}:\quad \lim_{z\to 0}\varphi(z)\left|0\right>=\left|a\right>
+\end{equation}
+Для примарного поля $\varphi$ с размерностью $h$ соответствующее состояние будем обозначать через $\left|h\right>$. 
+Из определения \eqref{eq:307} и операторного разложения \eqref{eq:253} легко видеть, что $L_{0}\left|h\right>=h\left|h\right>$.
+Заметим, что $L_{0} L_{n}\left|h\right> = L_{n} L_{0}\left|h\right> + [L_{0},L_{n}]\left|h\right> = (h-n) L_{n}\left|h\right>$. 
+Гамильтониан $H=L_{0}+\bar L_{0}$ должен иметь спектр, ограниченный снизу, поэтому для любого состояния $\left|h\right>$ должно существовать $n>0$, такое что $L_{n}\left|h\right> =0 $.
+Так как все состояния порождаются полями, а все поля получаются из примарных действием понижающих операторов $L_{-n}$, то все состояния должны разбиваться на модули старшего веса алгебры Вирасоро -- так называемые модули Верма.
+В минимальных моделях число таких модулей конечно.
+
+Рассмотрим действие $L_{n}$ на состояние $\left|h\right>$ и получим ограничение на значения конформного веса. Возьмем свертку с сопряженным состоянием $\left<h\right|$, $L^{+}_{m}=L_{-m}$:
+\begin{equation}
+  \label{eq:308}
+  \left<h\right|L^{+}_{-n}L_{n}\left|h\right>=\left<h\right| [L_{n},L_{-n}]\left|h\right> = \left(2nh +\frac{c}{12}(n^{3}-n)\right) \left<h|h\right>
+\end{equation}
+Норма состояний должна быть положительна.
+Устремим $n$ к бесконечности.
+Отсюда сразу получаем ограничение $c\geq 0$.
+Если положить $n=1$, то $h\geq 0$.
+При $h=0$ имеем $L_{1}\left|0\right>=0$, то есть вакуум $sl_{2}$-инвариантен, так как комбинации генераторов $L_{0,\pm_{1}}$ образуют подалгебру $sl_{2}$.
+
+Теперь опишем структуру модуля Верма со старшим весом $h$.
+
+\begin{table}[tbh]
+\label{tab:diagrams} \noindent \centering{\
+\begin{tabular}{|l|l|l|l|}
+\hline
+уровень & конформный вес & поле & состояние   \\ \hline
+0 & h & $\varphi$ & $\left|h\right>$  \\
+1 & h+1 & $L_{-1}\varphi$ & $L_{-1}\left|h\right>$  \\
+2 & h+2 & $L_{-2}\varphi$, $L_{-1}^{2}\varphi$ & $L_{-2}\left|h\right>$, $L_{-1}^{2}\left|h\right>$  \\
+3 & h+3 & $L_{-3}\varphi$,$L_{-1}L_{-2}\varphi$, $L_{-1}^{3}\varphi$ & $L_{-3}\left|h\right>$, $L_{-1}L_{-2}\left|h\right>$, $L_{-1}^{3}\left|h\right>$  \\
+\dots & \dots & \dots & \dots  \\
+N & h+N & $P(N)$ полей & $P(N)$ состояний  \\ \hline
+\end{tabular}
+}
+\caption{Структура модуля Верма}
+\end{table}
+
+Здесь $P(N)$ -- число разбиений числа $N$, для него имеет место следующая производящая функция:
+\begin{equation}
+  \label{eq:309}
+  \frac{1}{\prod_{n=1}^{\infty} (1-q^{n})} = \sum_{n=0}^{\infty} P(n) q^{n}
+\end{equation}
+
+В модуле Верма может оказаться такое состояние $\left|\omega\right>$, что $L_{n}\left|\omega\right>=0, \quad \forall n>0$.
+Действие понижающих операторов на такие состояния порождает инвариантное подпространство, то есть модуль Верма оказывается приводимым.
+Такие состояния обладают нулевой нормой и исключаются.
+Их иногда называют нулевыми состояниями (null-state).
+Как искать такие состояния?
+
+На уровне один  $L_{1}\left(L_{-1}\left|h\right>\right)=0\Longrightarrow h=0$, то есть все состояния, полученные из вакуума понижающим оператором являются нефизическими состояниями с нулевой нормой, как и должно быть.
+
+На уровне два будем искать нулевое состояние в виде $\left|\omega\right>=(L_{-2}+a L_{-1}^{2})\left| h \right> $. Из $L_{1}\left|\omega\right>=0$ получаем
+\begin{equation}
+  \label{eq:310}
+  0=([L_{1},L_{-2}] +a [L_{1},L_{-1}^{2}])\left|h\right> = (3+2a(2h+1))L_{-1}\left|h\right>
+\end{equation}
+То есть
+\begin{equation}
+  \label{eq:311}
+  a=-\frac{3}{2}(2h+1)
+\end{equation}
+Аналогично, действуя $L_{2}$ получаем условие
+\begin{equation}
+  \label{eq:312}
+  c=2h\frac{5-8h}{2h+1}
+\end{equation}
+Так как состояние $(L_{-2}-\frac{3}{2(2h+1)} L_{-1}^{2})\left|h\right>$ имеет нулевую норму, для корреляторов получаем $\left<(L_{-2}+aL_{1}^{2})\phi_{1}(w_{1}) \dots \phi_{n}(w_{n}) \right>=0$. 
+Используем тождества Уорда \eqref{eq:243}, \eqref{eq:244} и определение $L_{n}$ \eqref{eq:269} и перепишем это условие в виде дифференциального уравнения:
+\begin{equation}
+  \label{eq:313}
+\left[  a \frac{\partial^{2}}{\partial w_{1}^{2}} +\sum_{j\neq 1} \left(\frac{h_{j}}{(w_{1}-w_{j})^{2}}+\frac{1}{w_{1}-w_{j}} \frac{\partial}{\partial w_{j}}\right)\right] \left< \phi_{1}(w_{1}) \dots \phi_{n}(w_{n}) \right> =0
+\end{equation}
+То есть мы получили дифференциальные уравнения на корреляционные функции.
+
+Рассмотрим в качестве примера модель Изинга.
+Ей соответствует конформная теория поля с тремя примарными полями \eqref{eq:276} и центральным зарядом $1/2$.
+Заметим, что для поля спина $\Phi_{3}$ с конформной размерностью $h=1/16$ выполнено условие \eqref{eq:312}.
+То есть мы можем записать уравнение \eqref{eq:313} для корреляционных функций спинов.
+Рассмотрим для примера четырехточечную функцию
+\begin{equation}
+  \label{eq:314}
+   G^{(4)} =\langle \sigma(z_1,\bar z_1)\dots \sigma(z_4,\bar z_4)\rangle
+\end{equation}
+Из лекции \ref{sec:lecture-9} и формулы \eqref{eq:197} можно переписать $G^{(4)}$ в виде
+\begin{equation}
+  \label{eq:315}
+   G^{(4)} = \mathrm{const}\cdot \left(\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right)^{\frac{1}{8}} \overline{ \left(\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right)}^{\frac{1}{8}}F(x,\bar x),
+\end{equation}
+где $x=\frac{z_{12}z_{34}}{z_{13}z_{24}}, z_{ij}=\left| z_{i}-z_{j}\right|$. Тогда дифференциальное уравнение на $F$ примет вид
+\begin{equation}
+  \label{eq:316}
+  \left( x(1-x) \frac{\partial^{2}}{\partial x^{2}} +(\frac{1}{2}-x)\frac{\partial}{\partial x}+\frac{1}{16}\right) F(x,\bar x)=0
+\end{equation}
+и аналогично для $\bar x$.
+Решение этого уравнения дается гипергеометрической функцией.
+В данном случае она упрощается до $f_{1,2}(x)=(1\pm \sqrt{1-x})^{\frac{1}{2}}$.
+Тогда  четырехточечную функцию можно записать в виде комбинации решений
+\begin{equation}
+  \label{eq:317}
+  G^{(4)} =  \left|\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right|^{\frac{1}{4}}\sum_{i,j=1}^{2}a_{ij}f_{i}(x)f_{j}(\bar x)
+\end{equation}
+Возвращаясь к физической системе мы должны положить $\bar x= x^{*}$, тогда из однозначности четырехточечной функции комбинация может быть только $a(|f_{1}(x)|^{2}+|f_{2}(x)|^{2})$.
+Из сравнения с операторным разложением для $\sigma(z)\sigma(w)$ нетрудно получить, что $a=1/2$.
+
+В итоге для четырехточечной функции получается следующее выражение:
 \begin{equation}
@@
 
+Таким образом конформная теория поля позволяет не только находить критические индексы, но и получать явные выражения для корреляционных функций статистических моделей в критической точке.
+
 \section{Заключение}
@@
 
-\bibliography{2dqft}{}
+С момента своего создания в 1984 году двумерная конформная теория поля бурно развивалась и новые результаты не вошли в данный курс.
+В качестве обзора можно предложить книги \cite{difrancesco1997cft}, \cite{schottenloher2008mathematical}.
+Большое развитие получили и решеточные модели, в том числе и строгие математические методы, не связанные напрямую с конформной теорией поля.
+В частности, много приложений нашла эволюция Шрамма-Левнера \cite{schramm2000scaling}, при помощи которой удалось строго показать конформную инвариантность некоторых критических моделей \cite{chelkak2009universality,smirnov2001critical}.
+Надеюсь, что данный курс лекций послужит введением в эти области исследований.
+
+\bibliography{CFT-APTU-2011}{}
 \bibliographystyle{utphys}

### 2011-12-21 GeneralOverview/Lectures/CFT-APTU-2011.tex
Order of lectures now coincides with the text

@@
 \label{sec:literature}
-В \ref{sec:lecture-1} и \ref{sec:lecture-2} лекциях  мы опираемся на вводные главы книги \cite{difrancesco1997cft}.
+В \ref{sec:lecture-1} лекции  мы опираемся на вводные главы книги \cite{difrancesco1997cft}.
 Мы уделяем большое внимание использованию математического аппарата квантовой теории поля в моделях статистической физики.
@@
 
+Лекции \ref{sec:lecture-5}, \ref{sec:lecture-6} посвящены  точному решению модели Изинга в двух измерениях.
+Подробно решение  модели Изинга в двух измерениях рассмотрено в книге  \cite{belavin2001lect}, на материале которой и основано изложение в данных лекциях.
+
 В следующих лекциях \ref{sec:lecture-3}, \ref{sec:lecture-4} мы обсуждаем применение ренормгруппы к описанию критического поведения, более подробно и достаточно педагогически этот вопрос рассматривается в книге \cite{ma1980} (\cite{ma2000modern}).
@@
 Лекция \ref{sec:lecture-4} основана на вводной главе обзора \cite{Ravanini:2000st}.
-
-Лекции \ref{sec:lecture-5}, \ref{sec:lecture-6} посвящены  точному решению модели Изинга в двух измерениях.
-Подробно решение  модели Изинга в двух измерениях рассмотрено в книге  \cite{belavin2001lect}, на материале которой и основано изложение в данных лекциях.
 
@@
 
+\subsection*{Квантовые статистические модели}
+\label{sec:quantum-statistical-models}
+
+Микросостояния квантовых статистических систем описываются при помощи матрицы плотности
+\begin{equation}
+  \label{eq:19}
+  \rho=e^{-\beta H}
+\end{equation}
+Статсумма дается суммой по собственным состояниям гамильтониана или следом матрицы плотности:
+\begin{equation}
+  \label{eq:20}
+  Z=\sum_n e^{-\beta E_n}=\mathrm{Tr} \rho
+\end{equation}
+Значение физической величины определим как среднее по состояниям:
+\begin{equation}
+  \label{eq:21}
+  \left< A\right>=\sum_n \left< n\right| e^{-\beta H}A\left| n \right>=\mathrm{Tr}(\rho A)
+\end{equation}
+$e^{-\beta H}$ похоже на оператор эволюции $e^{-i H t}$, то есть его тоже можно записать через функциональный интеграл.
+Покажем, как это делается на примере системы с одной степенью свободы.
+В этом случае ядро оператора плотности имеет вид
+\begin{equation}
+  \label{eq:22}
+  \rho(x_f,x_i)=\left<x_f\right|e^{-\beta H} \left|x_i\right>
+\end{equation}
+Вспомним, что в квантовой механике оператор эволюции имеет вид $U(t)=e^{-i H t}$, а его ядро --- амплитуда перехода из состояния $\left|x_i\right>$ в $\left<x_f\right|$ дается интегралом по траекториям
+\begin{equation}
+  \label{eq:23}
+  \left<x_f\right| U(t)\left| x_i\right>=\int_{(x_i,0)}^{(x_f,t)} [dx] e^{i S[x]}
+\end{equation}
+Заменой $t\to i\tau, \; \tau\in [0,\beta]$ (виковским поворотом) переходим к евклидову действию $S[x(t)]\to iS_E[x(\tau)]$. Для ядра оператора плотности получаем
+\begin{equation}
+  \label{eq:24}
+  \rho(x_f,x_i)=\int_{(x_i,0)}^{(x_f,\beta)} [dx] e^{-S_E[x]}
+\end{equation}
+Статсумма
+\begin{equation}
+  \label{eq:25}
+  Z=\int dx \rho(x,x)=\int [dx] e^{-S_E[x]}
+\end{equation}
+Среднее значение $A$
+\begin{equation}
+  \label{eq:26}
+  \begin{array}{l}
+    \left<A\right>=\frac{1}{Z}\int dx \left<x\right|\rho A\left|x\right>=\frac{1}{Z}\int dx\; dy \left<x\right|\rho\left|y\right>\left<y\right|A\left|x\right>=    \\
+    =\frac{1}{Z}\int dx\; dy \int_{(x,0)}^{(y,\beta)} [dx] \left<y\right| A\left| x\right> e^{-S_E[x]}=\frac{1}{Z}\int dx\; dy\int_{(x,0)}^{(y,\beta)} [dx] A(x) \delta(x-y) e^{-S_E[x]}=\\
+    =\frac{1}{Z}\int [dx] A(x(0))e^{-S_E[x]}
+  \end{array}
+\end{equation}
+Здесь мы предположили, что $A$ зависит только от $x$, то есть $\left<y\right| A\left|x\right>=A(x)\delta(x-y)$.
+Мы видим, что значение $A$ дается функциональным интегралом, но $A$ вычисляется в точке $\tau=0$.
+
+Обобщение на систему с континуумом степеней свободы и многочастичные функции естественно.
+Статсумма квантовой системы получается из обычного интеграла по траекториям путем викова поворота и ограничения евклидова времени на конечный промежуток $[0,\beta]$.
+При нулевой температуре ($\beta\to \infty$) мы получаем обычный производящий функционал в евклидовом времени, то есть теорию поля.
+При конечных температурах статсумма квантовой $d$-мерной системы напоминает статсумму $d+1$-мерной классической системы на полосе шириной $\beta$.
+
 \subsection*{Классическая и квантовая теория поля}
@@
 \end{equation}
+
+Классическое уравнение движения получается из принципа экстремальности действия (равенства нулю вариации действия).
 
@@
 
-\section{Лекция 2. }
-\label{sec:lecture-2}
-
-\subsection{Квантовые статистические модели}
-\label{sec:quantum-statistical-models}
-
-Микросостояния квантовых статистических систем описываются при помощи матрицы плотности
-\begin{equation}
-  \label{eq:19}
-  \rho=e^{-\beta H}
-\end{equation}
-Статсумма дается суммой по собственным состояниям гамильтониана или следом матрицы плотности:
-\begin{equation}
-  \label{eq:20}
-  Z=\sum_n e^{-\beta E_n}=\mathrm{Tr} \rho
-\end{equation}
-Значение физической величины определим как среднее по состояниям:
-\begin{equation}
-  \label{eq:21}
-  \left< A\right>=\sum_n \left< n\right| e^{-\beta H}A\left| n \right>=\mathrm{Tr}(\rho A)
-\end{equation}
-$e^{-\beta H}$ похоже на оператор эволюции $e^{-i H t}$, то есть его тоже можно записать через функциональный интеграл.
-Покажем, как это делается на примере системы с одной степенью свободы.
-В этом случае ядро оператора плотности имеет вид
-\begin{equation}
-  \label{eq:22}
-  \rho(x_f,x_i)=\left<x_f\right|e^{-\beta H} \left|x_i\right>
-\end{equation}
-Вспомним, что в квантовой механике оператор эволюции имеет вид $U(t)=e^{-i H t}$, а его ядро --- амплитуда перехода из состояния $\left|x_i\right>$ в $\left<x_f\right|$ дается интегралом по траекториям
-\begin{equation}
-  \label{eq:23}
-  \left<x_f\right| U(t)\left| x_i\right>=\int_{(x_i,0)}^{(x_f,t)} [dx] e^{i S[x]}
-\end{equation}
-Заменой $t\to i\tau, \; \tau\in [0,\beta]$ (виковским поворотом) переходим к евклидову действию $S[x(t)]\to iS_E[x(\tau)]$. Для ядра оператора плотности получаем
-\begin{equation}
-  \label{eq:24}
-  \rho(x_f,x_i)=\int_{(x_i,0)}^{(x_f,\beta)} [dx] e^{-S_E[x]}
-\end{equation}
-Статсумма
-\begin{equation}
-  \label{eq:25}
-  Z=\int dx \rho(x,x)=\int [dx] e^{-S_E[x]}
-\end{equation}
-Среднее значение $A$
-\begin{equation}
-  \label{eq:26}
-  \begin{array}{l}
-    \left<A\right>=\frac{1}{Z}\int dx \left<x\right|\rho A\left|x\right>=\frac{1}{Z}\int dx\; dy \left<x\right|\rho\left|y\right>\left<y\right|A\left|x\right>=    \\
-    =\frac{1}{Z}\int dx\; dy \int_{(x,0)}^{(y,\beta)} [dx] \left<y\right| A\left| x\right> e^{-S_E[x]}=\frac{1}{Z}\int dx\; dy\int_{(x,0)}^{(y,\beta)} [dx] A(x) \delta(x-y) e^{-S_E[x]}=\\
-    =\frac{1}{Z}\int [dx] A(x(0))e^{-S_E[x]}
-  \end{array}
-\end{equation}
-Здесь мы предположили, что $A$ зависит только от $x$, то есть $\left<y\right| A\left|x\right>=A(x)\delta(x-y)$.
-Мы видим, что значение $A$ дается функциональным интегралом, но $A$ вычисляется в точке $\tau=0$.
-
-Обобщение на систему с континуумом степеней свободы и многочастичные функции естественно.
-Статсумма квантовой системы получается из обычного интеграла по траекториям путем викова поворота и ограничения евклидова времени на конечный промежуток $[0,\beta]$.
-При нулевой температуре ($\beta\to \infty$) мы получаем обычный производящий функционал в евклидовом времени, то есть теорию поля.
-При конечных температурах статсумма квантовой $d$-мерной системы напоминает статсумму $d+1$-мерной классической системы на полосе шириной $\beta$.
-
 \subsection{Критические явления}
@@
 
-\subsection{Скейлинг или масштабная инвариантность}
-\label{sec:scaling}
-
-Гипотеза подобия связывает между собой критические индексы.
-Ее можно сформулировать так: плотность свободной энергии $f(t,h)=\frac{F}{N}$ около критической точки является однородной функцией $h$ и безразмерной температуры $t=\frac{T}{T_c}-1$.
-То есть существуют $a,b$:
-\begin{equation}
-  \label{eq:33}
-  f(\lambda^a t,\lambda^b h)=\lambda f(t,h)
-\end{equation}
-В следующих лекциях мы обоснуем эту гипотезу при помощи ренормгруппы.
-
-Покажем теперь, какие условия накладывает гипотеза подобия на критические индексы. Заметим, что $t^{-\frac{1}{a}}f$ инвариантна при преобразовании $t\to \lambda^a t, h\to \lambda^b h$. Введем
-\begin{equation}
-  \label{eq:34}
-  y=\frac{h}{t^{\frac{b}{a}}}
-\end{equation}
-Тогда
-\begin{equation}
-  \label{eq:35}
-  f(t,h)=t^{\frac{1}{a}}g(y).
-\end{equation}
-Для спонтанной намагниченности имеем
-\begin{equation}
-  \label{eq:36}
-  M=-\left.\frac{\partial f}{\partial h}\right|_{h=0}=t^{\frac{1-b}{a}}g'(0),
-\end{equation}
-а для  магнитной восприимчивости
-\begin{equation}
-  \label{eq:37}
-  \chi=\left.\frac{\partial^2 f}{\partial h^2}\right|_{h=0}=t^{\frac{1-2b}{a}}g''(0).
-\end{equation}
-Аналогично для удельной теплоемкости получаем
-\begin{equation}
-  \label{eq:38}
-  c=-T\left.\frac{\partial^2 f}{\partial T^2}\right|_{h=0}=-\frac{1}{T_c}t^{\frac{1}{a-2}}g''(0)
-\end{equation}
-В пределе $t\to 0$ $M\sim h^{\frac{1}{\delta}}$, поэтому $g'(y)\sim y^{\frac{1}{\delta}}$ при $y\to \infty$.
-А значит, если в критической точке намагниченность $M$ конечна и не равна нулю, должно выполняться равенство $1-b-\frac{b}{\delta}=0$.
-Подставляя выражение для $\delta$ через $b$ в (\ref{eq:36},\ref{eq:37},\ref{eq:38}), мы получаем связь критических индексов
-  \begin{eqnarray}
-    \label{eq:39}
-    \alpha=2-\frac{1}{a}\\
-    \beta=\frac{1-b}{a}\\
-    \gamma=-\frac{1-2b}{a}\\
-    \delta=\frac{b}{1-b}
-  \end{eqnarray}
-\subsection{Процедура Каданова}
-\label{sec:kadanoff-procedure}
-Теперь обоснуем гипотезу подобия в модели Изинга при помощи процедуры Каданова и свяжем индексы $a,b$ с $\nu,\eta$.
-Рассмотрим кубическую $d$-мерную модель Изинга.
-\begin{equation}
-  \label{eq:40}
-  H=-J\sum_{\left<ij\right>}\sigma_i \sigma_j-h\sum_i \sigma_i
-\end{equation}
-Разбиваем решетку на блоки со стороной в $r$ ячеек. Будем нумеровать блоки большими латинскими буквами $I,J$ и понимать под записью $i\in I$ перечисление вершин в $I$-том блоке.
-Сумма спинов в блоке принимает значения от $r^{-d}$ до $r^d$. Введем блочный спин
-\begin{equation}
-  \label{eq:41}
-  \Sigma_I=\frac{1}{R}\sum_{i\in I}\sigma_i
-\end{equation}
-$R$ - нормировочный множитель, который выбирается так, чтобы блочный спин мог принимать значения $\pm 1$. Если бы спины были всегда в одном направлении, то $R$ имел бы значение $r^d$.
-
-Мы предполагаем, что поведение вблизи критической точки описывается в терминах блочных спинов, так как корреляционная длина $\xi>>r$. Гамильтониан для блочных спинов имеет вид
-\begin{equation}
-  \label{eq:42}
-  H'=-J' \sum_{\left<IJ\right>} \Sigma_I \Sigma_J-h' \sum_I \Sigma_I
-\end{equation}
-Так как корреляционная длина для блоков
-\begin{equation}
-  \label{eq:43}
-  \xi'=\frac{\xi}{r},
-\end{equation}
-то из (\ref{eq:31}) для температуры имеем
-\begin{equation}
-  \label{eq:44}
-  t'=r^{\frac{1}{\nu}} t.
-\end{equation}
-Суммарная энергия взаимодействия со внешним полем должна оставаться неизменной, то есть
-\begin{equation}
-  \label{eq:45}
-  h\sum_i \sigma_i=h' \sum_I \Sigma_I=\frac{h'}{R}\sum_i \sigma_i\quad\Longrightarrow\quad h'= Rh
-\end{equation}
-Так как общая свободная энергия тоже не должна меняться, то свободная энергия на блок $\sim r^d f$, то есть
-\begin{equation}
-  \label{eq:46}
-  f(t',h')=r^d f(t,h)
-\end{equation}
-или
-\begin{equation}
-  \label{eq:47}
-  f(t,h)=r^{-d} f(r^{\frac{1}{\nu}} t, Rh)
-\end{equation}
-Осталось вычислить $R$ как функцию от $r$, чтобы оправдать гипотезу подобия. Смотрим на парный коррелятор в критической точке
-\begin{multline}
-  \label{eq:48}
-  \Gamma'(\vec n)=\left< \Sigma_I\Sigma_J\right>-\left< \Sigma_I\right>\left<\Sigma_J\right>=\frac{1}{R^2}\sum_{i\in I}\sum_{j\in J}\left(\left<\sigma_i \sigma_j\right>-\left<\sigma_i\right>\left<\sigma_j\right>\right) =\\
-  = \frac{r^{2d}}{R^2}\Gamma(r\vec n)=\frac{R^{-2}r^{2d}}{\left|r\vec n\right|^{d-2+\eta}}=\frac{R^{-2}r^{d+2-\eta}}{\left|\vec n\right|^{d-2+\eta}}
-\end{multline}
-Отсюда
-\begin{equation}
-  \label{eq:49}
-  R=r^{\frac{d+2-\eta}{2}}, \quad h'=r^{\frac{d+2-\eta}{2}}h
-\end{equation}
-Подставляя в (\ref{eq:33}) $r=\lambda^{\frac{1}{d}}$ получаем выражение для скейлинговых параметров $a,b$:
-\begin{eqnarray}
-  \label{eq:50}
-  a=\frac{1}{\nu d}\\
-  b=\frac{d+2-\eta}{2d}
-\end{eqnarray}
-Для критических индексов имеем
-\begin{eqnarray}
-  \label{eq:51}
-  \alpha=2-\nu d\\
-  \beta=\frac{1}{2}\nu (d-2+\eta)\\
-  \gamma=\nu (2-\eta)\\
-  \delta=\frac{d+2-\eta}{d-2+\eta}
-\end{eqnarray}
-
-\section{Лекция 3}
-\label{sec:lecture-3}
-В прошлой лекции мы обосновали гипотезу подобия при помощи рассмотрения блочных спинов и введения эффективного гамильтониана, имеющего ту же форму, но другие константы связи.
-Эта процедура является перенормировкой в координатном пространстве, она определяет отображение гамильтониана $H\to H'$.
-Последовательное применение такой процедуры порождает так называемую ренормгруппу.
-Строго говоря, ренормгруппа является не группой, полугруппой, так как у преобразования нет обратного, ведь при переходе к блокам большего размера мы теряем информацию.
-Опишем ренормгруппу для решеточных моделей.
-
-\subsection{Ренормгруппа в решеточных моделях}
-\label{sec:renormgroup-lattice-models}
-Рассматриваем решеточную модель, состоящую из $N$ спинов $\sigma_i$ на $d$-мерной решетке. Общий вид гамильтониана таких моделей
-\begin{equation}
-  \label{eq:55}
-  H(\vec J,[\sigma],N)=J_0 + J_1\sum_i \sigma_i +J_2\overset{(1)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j+J_3\overset{(2)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j + \dots
-\end{equation}
-Здесь мы явно указали на зависимость гамильтониана от констант связи, которые собраны в вектор $\vec J=(J_0,J_1,J_2,J_3,\dots)$.
-Сумма $\overset{(1)}{\sum_{\left<ij\right>}}$ - это сумма по ближайшим соседям, $\overset{(2)}{\sum_{\left<ij\right>}}$ - сумма по вершинам, разделенным двумя ребрами (через одного) и так далее.
-Статсумма
-\begin{equation}
-  \label{eq:56}
-  Z(\vec J,N)=\sum_{[\sigma]}e^{-H(\vec J,[\sigma],N)}
-\end{equation}
-Мы так переопределили константы связи, чтобы избавиться от множителя $\beta$.
-
-Теперь мы вводим блочные переменные с блоком со стороной в $r$ ячеек решетки, содержащим $r^d$ вершин.
-$\Sigma_I$ - блочные спины, $\xi_i$ - переменные внутри блока.
-В таких переменных статсумма переписывается так:
-\begin{equation}
-  \label{eq:57}
-  Z(\vec J,N)=\sum_{[\Sigma][\sigma]}e^{-H(\vec J,[\Sigma],[\sigma],N)}
-\end{equation}
-Если мы просуммируем по внутриблочным степеням свободы $\xi$, то получится перенормированный гамильтониан $H'(\vec J,[\Sigma],Nr^{-d})$.
-\begin{equation}
-  \label{eq:58}
-  e^{-H'(\vec J',[\Sigma],Nr^{-d})}=\sum_{[\xi]}e^{-H(\vec J,[\Sigma],[\xi],N)}
-\end{equation}
-Вблизи критической точки можно предполагать что у $H'$ такой же вид, как и у $H$, так как параметр порядка расходится и поведение определяется дальними корреляциями.
-Описания поведения системы в терминах $H'$ и $H$ эквивалентны, поэтому соответствующие выражения для статсуммы должны совпадать (с точностью до умножения на константу):
-\begin{equation}
-\label{eq:52}
-  Z(\vec J,N)=\sum_{[\Sigma]}e^{-H'(\vec J',[\Sigma],Nr^{-d})}=Z(\vec J',Nr^{-d})
-\end{equation}
-Удельная свободная энергия отображается как $f(\vec J)=r^{-d} f(\vec J')$.
-
-Отображение констант связи $\vec J\to\vec J'$ и порождает ренормгруппу. Будем его записывать как
-\begin{equation}
-  \label{eq:53}
-  \vec J'=T(\vec J)
-\end{equation}
-Последовательное применение таких преобразований порождает в пространстве констант связи некоторый набор точек, который называется траекторией ренормгруппы.
-
-На каждом шаге корреляционная длина уменьшается в $r$ раз, поэтому траектория уводит систему из окрестности критической точки.
-Но в самой критической точке корреляционная длина бесконечна, поэтому эта точка неподвижна относительно действия ренормгруппы.
-
-В общем случае критическое поведение наблюдается на некоторой критической поверхности в пространстве $\vec J$. Под действием ренормгруппы точки двигаются по ней. Стационарная точка
-\begin{equation}
-  \label{eq:54}
-  \vec J_c=T(\vec J_c)
-\end{equation}
-называется фиксированной точной ренормгруппы.
-
-Вообще говоря, преобразование $T$ нелинейно, однако в окрестности фиксированной точки его можно линеаризовать.
-Вводим переменную $\delta\vec J=\vec J-\vec J_c$ и раскладываем $T$ в ряд Тейлора по $\delta\vec J$.
-Тогда
-\begin{equation}
-  \label{eq:59}
-  \delta\vec J'=A\delta\vec J,
-\end{equation}
-где $A$ - матрица, $A_{ij}=\frac{\partial T_i}{\partial J_j}$.
-Мы можем диагонализовать матрицу $A$, ее собственные значения мы обозначим через $\lambda_i$, собственные векторы через $\vec u_i$.
-Тогда для точки в пространстве констант связи мы можем написать (в окрестности  критической точки):
-\begin{equation}
-  \label{eq:60}
-  \vec J=\vec J_c+\sum_i t_i \vec u_i
-\end{equation}
-Переменные $t_i$ под действием ренормгруппы преобразуются так:
-\begin{equation}
-  \label{eq:61}
-  t'_i=\lambda_i t_i=r^{y_i} t_i
-\end{equation}
-Здесь мы ввели обозначение $y_i$ для критических индексов. В примере из раздела \ref{sec:kadanoff-procedure} такими индексами были $a$ и $b$. 
-Для свободной энергии имеем
-\begin{equation}
-  \label{eq:62}
-  f(t_1,t_2,\dots)=r^{-d} f(r^{y_1}t_1,r^{y_2}t_2,\dots)
-\end{equation}
-Таким образом, критические индексы получаются из собственных значений линеаризованной ренормгруппы в фиксированной точки.
-
-Если часть собственных значений $\lambda_i$ положительна, а часть - отрицательная, то фиксированная точка называется гиперболической. 
-Критической поверхностью называются такие точки $\vec J$, что
-\begin{equation}
-  \label{eq:63}
-  \lim_{n\to \infty}T^n (\vec J)=\vec J_c
-\end{equation}
-Около точки $\vec J_c$ она представляет собой векторное пространство, натянутое на те векторы $\vec u_i$, для которых соответствующие собственные значения $\lambda_i<1$.
-
-Параметры $t_i$, которые соответствуют $\lambda_i>1$ называются релевантными, так как они растут под действием ренормгруппы.
-Параметры с $y_i<0 \; (\lambda_i<1)$ --- иррелевантные, с $y_i=0$ --- маргинальные.
-
-Существование критической поверхности объясняет универсальность критических индексов в разных моделях.
-Статистические системы разбиваются на классы универсальности, члены которых имеют одинаковое критическое поведение.
-Это так, если разные системы живут на подмногообразиях в пространстве констант связи, которые пересекают одну и ту же критическую поверхность.
-Тогда критическая точка у них общая.
-
-\subsection{Ренормгруппа в непрерывных моделях}
-\label{sec:renormgroup-general}
-В непрерывных моделях перенормировка осуществляется в импульсном пространстве. Рассмотрим скалярное поле $\varphi(\vec x)$, где $\vec x\in \mathbb{R}^d$. Проведем преобразование Фурье
-\begin{equation}
-  \label{eq:64}
-  \varphi(\vec x)=\int \frac{d^d \vec k}{(2\pi)^d}\tilde \varphi(\vec k) e^{i\vec k\cdot \vec x}
-\end{equation}
-Функционал действия может быть переписан в виде, зависящем только от $\tilde\varphi$: $S[\varphi]\to S[\tilde\varphi]$. Например, для модели $\varphi^4$ \eqref{eq:16} получается
-\begin{multline}
-  \label{eq:65}
-  S[\varphi,r,u]=\int  \frac{d^d \vec k}{(2\pi)^d} \frac{1}{2} \tilde\varphi(-\vec k)\tilde\varphi(\vec k)(\vec k^2+r)+\\
-  \frac{1}{4}u\int  \frac{d^d \vec k_1}{(2\pi)^d} \frac{d^d \vec k_2}{(2\pi)^d} \frac{d^d \vec k_3}{(2\pi)^d} \tilde\varphi(-\vec k_1-\vec k_2 -\vec k_3)\tilde \varphi(\vec k_1)\tilde\varphi (\vec k_2)\tilde\varphi(\vec k_3).
-\end{multline}
-В общем случае функционал действия зависит от поля $\varphi$ и параметров $u_i$ в плотности Лагранжиана (констант связи).
-
-Квантовая теория поля всегда содержит расходящиеся интегралы, поэтому нужна регуляризация.
-Будем считать, что в качестве такой регуляризации используется обрезание по импульсам $\left|\vec k\right|<\Lambda$.
-После преобразования Фурье мера в функциональном интеграле переписывается как
-\begin{equation}
-  \label{eq:66}
-  [d\varphi]_{\Lambda}=\prod_x d\varphi(x)=\prod_{\left|\vec k\right|<\Lambda}d\tilde\varphi(\vec k)
-\end{equation}
-Теперь опишем перенормировку Вильсона-Каданова.
-Она проводится в два этапа.
-Сначала мы интегрируем по $\tilde\varphi(\vec k): \Lambda/s<\left|k\right|<\Lambda$.
-То есть мы исключаем быстрые моды, так как критическое поведение описывается медленными модами.
-$s$-масштабный фактор.
-В результате мы получаем новое обрезание $\Lambda/s$ и действие $S'[\varphi,\{u_i\}]$.
-\begin{equation}
-  \label{eq:67}
-  e^{-S'[\varphi,\{u_i\}]}=\int \prod_{\Lambda/s<\left|\vec k\right|<\Lambda}d\varphi(\vec k)e^{-S[\varphi,\{u_i\}]}
-\end{equation}
-Пока нас интересую только медленные моды, действие $S'$ эквивалентно $S$. Вторым шагом осуществим масштабное преобразование
-\begin{eqnarray}
-  \label{eq:68}
-  \vec k \to \vec k'=s \vec k\\
-  \vec x\to \vec x'=\vec x/s
-\end{eqnarray}
-При этом поле преобразуется так:
-\begin{eqnarray}
-  \label{eq:69}
-  \varphi(\vec x)\to \varphi'(\vec x/s)=s^{\Delta}\varphi (\vec x)\\
-  \tilde\varphi'(s\vec k)=s^{\Delta-d}\tilde\varphi (\vec k)
-\end{eqnarray}
-Здесь $\Delta$- скейлинговая размерность поля $\varphi$, она связана с индексом $\eta$: $\Delta=\eta/2$.
-Мера в функциональном интеграле при масштабном преобразовании умножится на константу.
-Теперь можно сравнить $S'$ и $S$, так как масштаб обрезания и там и там равен $\Lambda$ и те же степени свободы.
-Эти два действия описывают одинаковое поведение на больших расстояниях.
-Поэтому вид действия $S'$ должен быть тот же, что и у $S$, но с другими константами связи $u_i'$.
-\begin{equation}
-  \label{eq:70}
-  S'[\varphi,\{u_i\}]=S[\varphi,\{u_i'\}]
-\end{equation}
-Последовательным действием таких преборазований мы получаем кривую $u_i(s)$ в пространстве параметров лагранжиана.  Мы можем записать уравнение этой кривой как
-\begin{equation}
-  \label{eq:71}
-  \frac{du_i}{d(\ln s)}=\beta_i(\{u_i\})
-\end{equation}
-$\beta_i$ называется $\beta$-функцией параметра $u_i$. 
-Фиксированная точка $u_j^{*}$:
-\begin{equation}
-  \label{eq:72}
-  \beta_i(\{u^{*}_j\})=0
-\end{equation}
-Эта точка неподвижна относительно преобразований ренормгруппы. В фиксированной точке теория масштабно-инвариантна на квантовом уровне.
-
-\section{Лекция 4 }
-\label{sec:lecture-4}
-\subsection{Уравнение Каллана-Симанчика}
-
-Вообще говоря, квантовая теория поля может быть не масштабно-инвариантна из-за наличия размерных параметров на классическом уровне или возникающих при перенормировке. Действие
-\begin{equation}
-  \label{eq:73}
-  S=\int d^dx \mathcal{L}
-\end{equation}
-зависит от полей $\varphi$ и констант связи $\vec u=(u_1,\dots,u_n)$.
-Рассмотрим инфинитезимальное масштабное преобразование $\lambda=1+\omega$.
-При этом вариация $x_{\nu}$ будет $\delta_{\omega}x_{\nu}=\omega x_{\nu}$.
-Такое преобразование, в соответствии с предыдущей лекцией,  можно рассматривать как преобразование констант связи $\vec u\to \vec u'$.
-При наличии масштабной инвариантности $\vec u = \vec u'$.
-При инфинитезимальных преобразованиях $x\to x+dl x$ вариация плотности лагранжиана дается Нётеровским током:
-\begin{equation}
-  \label{eq:74}
-  \delta\mathcal{L}=\partial_{\mu}J^{\mu}dl
-\end{equation}
-\begin{equation}
-  \label{eq:75}
-  J^{\mu}=x_{\nu}T^{\mu\nu}
-\end{equation}
-Здесь $T^{\mu\nu}$ - тензор энергии-импульса.  Через $\Theta$ мы обозначим след тензора энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия
-\begin{equation}
-  \label{eq:87}
-  \delta S=dl \int d^d x \Theta(x)
-\end{equation}
-Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$. В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
-
-В классической теории вид преобразований полей при масштабных преобразованиях легко получаются из анализа размерностей.
-Напомним, что достаточно иметь одну единицу измерения - длины (или обратной длины).
-Если теория масштабно-инвариантна, то действие должно быть безразмерным.
-Канонические (классические) размерности полей легко определить из требования безразмерности слагаемых в функционале действия, если ввести соглашение, определяющее размерность координат или импульсов.
-
-Будем обозначать каноническую размерность произвольно величины $F$ через $d[F]$.
-Положим $d[p]=-d[x]=1$. Тогда $d[d^d x]=-d,\; d[\partial]=1$. Теперь легко найти размерности полей. Например, для модели $\varphi^4$
-\begin{equation}
-  \label{eq:83}
-  S[\varphi]=\int d^d x\left( -\frac{(\partial \varphi)^2}{2}-\frac{\mu \varphi^2}{2}-\frac{u\varphi^4}{24}+h\varphi\right),
-\end{equation}
-рассмотрим первое слагаемое. Оно должно быть безразмерным. При этом его размерность $d[\int d^d x (\partial \varphi)^2]=2d[\varphi]+2-d=0$. Отсюда $d[\varphi]=d/2-1$. Для общего действия
-\begin{equation}
-  \label{eq:84}
-  S[\varphi]=-\int d^d x\left( \frac{(\partial \varphi)^2}{2}+\sum_n u_n \frac{\varphi^n}{n!}\right)
-\end{equation}
-размерности констант связи следующие:
-\begin{equation}
-  \label{eq:85}
-  d[h=-u_1]=d/2+1,\quad d[\mu=u_2]=2,\quad d[g_4]=4-d,\quad d[g_6]=6-2d,\quad d[g_n]=n-\frac{d(n-2)}{2}
-\end{equation}
-При масштабных преобразованиях поля и константы связи ведут себя так:
-\begin{equation}
-  \label{eq:86}
-  \varphi'(x)=s^{-d[\varphi]}\varphi(x/s),\quad u_i'=s^{-d[u_i]}u_i
-\end{equation}
-
-Напомним, что
-\begin{equation}
-  \label{eq:76}
-  \beta_{i}(\vec u)=\frac{du_i}{d\ln s}
-\end{equation}
-Параметр ренормгруппы $s$ связан с параметром масштабного преобразования $l$ соотношением $l=\ln s$, при этом
-\begin{equation}
-  \label{eq:79}
-   \beta_{i}(\vec u)=\frac{du_i}{dl}
-\end{equation}
-Если в точке $u$ $\beta_i(\vec u)>0$, то $u_i(l)$ растет, $\beta_i (\vec u)<0$ - убывает.
-В фиксированной точке $u^*$ $\beta_i(\vec u^*)=0$.
-Пространство действий делится фиксированной точкой на регионы.
-Константы связи ``заперты'' в одном из этих регионов.
-Фиксированная точка может достигаться при $l\to \pm \infty$.
-Если $u(l)\to u^*$ при $l\to +\infty$, то такая точка называется инфракрасной, если $u(l)\to u^*$ при $l\to -\infty$, то ультрафиолетовой.
-Введем функции $\Phi_i$:
-\begin{equation}
-  \label{eq:77}
-  \Phi_i=\frac{\partial \mathcal{L}}{\partial u_i}
-\end{equation}
-Вариация $\delta \mathcal{L}$ дается их линейной комбинацией.
-\begin{equation}
-  \label{eq:78}
-  \Theta(x)=\frac{\partial \mathcal{L}}{\partial l}=\sum_i \frac{\partial \mathcal{L}}{\partial u_i}\frac{d u_i}{dl}=\sum_i\beta_i(\vec u)\Phi_i(\vec u)
-\end{equation}
-$\Theta=0$ тогда и только тогда, когда $\beta_i(\vec u)=0$, значит в фиксированной точке ренормгруппы есть масштабная инвариантность.
-
-Рассмотрим $N$-точечную корреляционную функцию --- среднее значение некоторого $N$-точечного локального оператора
-\begin{equation}
-  \label{eq:81}
-  \langle X\rangle =\langle A_1 (x_1)\dots A_N (x_N)\rangle
-\end{equation}
-
-Мы хотим получить уравнение для его преобразования под действием ренормгруппы. Такое уравнение называется уравнением Каллана-Симанчика.
-
-Вариация корреляционных функций при масштабных преобразованиях может описываться двумя способами.
-
-Во-первых, мы можем вычислить вариацию всех полей:
-\begin{multline}
-  \label{eq:82}
-  \delta \langle X\rangle=\delta \langle A_1(x_1)\dots A_N (x_N)\rangle = \delta \int {\cal D}\varphi A_1 \dots A_N e^{-S[\varphi]} = \\
-  \delta \int {\cal D} \varphi\; \left( \sum_k A_1 \dots \delta A_k \dots A_N e^{-S[\varphi]} -A_1\dots A_N e^{-S[\varphi]}\delta S\right)
-\end{multline}
-Вариация $A_k$ дается глобальной дилатацией координат и внутренней вариацией поля в соответствии с его канонической размерностью:
-\begin{equation}
-  \label{eq:88}
-  \delta A_k=dl (x^{\mu}_k\partial^k_{\mu}+d[A_k]) A_k
-\end{equation}
-Вариация действия определяется следом тензора энергии-импульса (\ref{eq:87}). Поэтому
-\begin{equation}
-  \label{eq:89}
-  \delta\langle X\rangle=dl \left(\sum_k (x_k^{\mu}\partial_{\mu}^k+d[A_k])\langle X\rangle-\int d^d y \Theta(y)\right)
-\end{equation}
-
-Другой способ вычисления состоит в вариации полей и действия по константам связи $u_i$:
-\begin{equation}
-  \label{eq:90}
-  \delta\langle X\rangle=dl\sum_i \beta_i(\vec u)\frac{\partial}{\partial u_i}\langle X\rangle,
-\end{equation}
-но
-\begin{equation}
-  \label{eq:91}
-  \frac{\partial}{\partial u_i}\langle X\rangle=\sum_k \langle A_1\dots \frac{\partial A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Phi_i(y)\rangle.
-\end{equation}
-Отсюда
-\begin{equation}
-  \label{eq:92}
-  \delta\langle X\rangle=dl \sum_i \sum_k\langle A_1\dots \frac{\partial A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Theta(y)\rangle
-\end{equation}
-Сравнивая это уравнение с (\ref{eq:89}) получаем уравнение Каллана-Симанчика:
-\begin{equation}
-  \label{eq:93}
-  \left[ \sum_k\left( x^{\mu}_k \frac{\partial}{\partial x^{\mu}_k}+\Gamma_k(\vec u)\right) -\sum_i \beta_i(\vec u)\frac{\partial }{\partial u_i}\right]\langle X\rangle=0,
-\end{equation}
-где $\Gamma_k$ - аномальная размерность поля $A_k(x_k)$, определяющаяся выражением
-\begin{equation}
-  \label{eq:94}
-  \Gamma_k A_k(x_k)=\left( d[A_k]+\sum_i \beta_i(\vec u) \frac{\partial }{\partial u_i}\right) A_k(x_k).
-\end{equation}
-В частности, для следа тензора энергии-импульса $\Gamma \Theta=2 \Theta$, то есть аномальная размерность равна классической.
-Это верно и для других компонент тензора энергии-импульса в силу Лоренц-инвариантности.
-
-\subsection{Ренормгруппа в двух измерениях}
-\label{sec:renormgroup-in-2d}
-
-Реноргрупповой анализ квантовой теории поля в двух измерениях дает следующий результат, известный как $c$-теорема Замолодчикова \cite{zamolodchikov1986irreversibility}.
-
-\begin{theorem}
-  Для любой унитарной квантовой теории поля в двух измерениях существует функция $c(\vec u)$ такая, что
-  \label{c-theorem}
-  \begin{itemize}
-  \item $c(\vec u)$ убывает, как функция параметра ренормгруппы
-    \begin{equation}
-      \label{eq:95}
-      \frac{dc}{dl}\leq 0
-    \end{equation}
-  \item $c(\vec u)$ стационарна в фиксированной точке $\vec u^*$ ренормгруппы, то есть
-    \begin{equation}
-      \label{eq:96}
-      \frac{dc({\vec u^*})}{dl}=0 \Leftrightarrow \beta_i(\vec u^*)=0
-    \end{equation}
-  \item 2-точечные корреляторы в фиксированной точке полностью определяются значением $c=c(\vec u^*)$.
-    Если ввести комплексные координаты $z=x_1+ix_2,\quad \bar z=x_1-ix_2$ и обозначить компоненты тензора энергии импульса через $T=T_{zz}$, $\bar T=T_{\bar z\bar z}$, $\Theta=T_{z\bar z}=T_{\bar z z}=T_{\mu\mu}=0$, то для корреляторов верно следующее выражение
-    \begin{eqnarray}
-      \label{eq:97}
-      \langle T(z,\bar z)T(0,0)\rangle=\frac{c/2}{z^4}\\
-      \langle \bar T(z,\bar z)\bar T(0,0)\rangle=\frac{c/2}{\bar z^4}\\
-      \langle T(z,\bar z) \bar T(0,0)\rangle=0
-    \end{eqnarray}
-    Число $c=\lim_{\vec u\to \vec u^*} c(\vec u)$ называется центральным зарядом. 
-  \end{itemize}
-\end{theorem}
-Для унитарных теорий из этой теоремы следует, что $c_{UV}\geq c_{IR}$.
-
-В фиксированной точке ренормгруппы имеет место масштабная инвариантность.
-Вместе с трансляционной и лоренц-инвариантностью она порождает конформную инвариантность, то есть инвариантность относительно преобразований, сохраняющих углы.
-
-\section{Лекция 5. Двумерная модель Изинга}
+\section{Лекция 2. Двумерная модель Изинга}
 \label{sec:lecture-5}
 
-Вернемся на некоторое время к модели Изинга в двух измерениях \eqref{eq:1}.
+Займемся решением модели Изинга в двух измерениях \eqref{eq:1}.
 Точного решения для модели с внешним полем до сих пор не найдено.
@@
 Теперь перейдем к точному решению модели Изинга.
-\section{Лекция 6. Решение Вдовиченко.}
+\section{Лекция 3. Решение Вдовиченко.}
 \label{sec:lecture-6}
@@
 Мы не будем его проделывать, так как в следующих лекциях мы легко сможем вычислить корреляторы из конформной теории поля.
+
+\section{Лекция 4}
+\label{sec:lecture-3}
+
+\subsection{Скейлинг или масштабная инвариантность}
+\label{sec:scaling}
+
+Гипотеза подобия связывает между собой критические индексы.
+Ее можно сформулировать так: плотность свободной энергии $f(t,h)=\frac{F}{N}$ около критической точки является однородной функцией $h$ и безразмерной температуры $t=\frac{T}{T_c}-1$.
+То есть существуют $a,b$:
+\begin{equation}
+  \label{eq:33}
+  f(\lambda^a t,\lambda^b h)=\lambda f(t,h)
+\end{equation}
+В следующих лекциях мы обоснуем эту гипотезу при помощи ренормгруппы.
+
+Покажем теперь, какие условия накладывает гипотеза подобия на критические индексы. Заметим, что $t^{-\frac{1}{a}}f$ инвариантна при преобразовании $t\to \lambda^a t, h\to \lambda^b h$. Введем
+\begin{equation}
+  \label{eq:34}
+  y=\frac{h}{t^{\frac{b}{a}}}
+\end{equation}
+Тогда
+\begin{equation}
+  \label{eq:35}
+  f(t,h)=t^{\frac{1}{a}}g(y).
+\end{equation}
+Для спонтанной намагниченности имеем
+\begin{equation}
+  \label{eq:36}
+  M=-\left.\frac{\partial f}{\partial h}\right|_{h=0}=t^{\frac{1-b}{a}}g'(0),
+\end{equation}
+а для  магнитной восприимчивости
+\begin{equation}
+  \label{eq:37}
+  \chi=\left.\frac{\partial^2 f}{\partial h^2}\right|_{h=0}=t^{\frac{1-2b}{a}}g''(0).
+\end{equation}
+Аналогично для удельной теплоемкости получаем
+\begin{equation}
+  \label{eq:38}
+  c=-T\left.\frac{\partial^2 f}{\partial T^2}\right|_{h=0}=-\frac{1}{T_c}t^{\frac{1}{a-2}}g''(0)
+\end{equation}
+В пределе $t\to 0$ $M\sim h^{\frac{1}{\delta}}$, поэтому $g'(y)\sim y^{\frac{1}{\delta}}$ при $y\to \infty$.
+А значит, если в критической точке намагниченность $M$ конечна и не равна нулю, должно выполняться равенство $1-b-\frac{b}{\delta}=0$.
+Подставляя выражение для $\delta$ через $b$ в (\ref{eq:36},\ref{eq:37},\ref{eq:38}), мы получаем связь критических индексов
+  \begin{eqnarray}
+    \label{eq:39}
+    \alpha=2-\frac{1}{a}\\
+    \beta=\frac{1-b}{a}\\
+    \gamma=-\frac{1-2b}{a}\\
+    \delta=\frac{b}{1-b}
+  \end{eqnarray}
+\subsection{Процедура Каданова}
+\label{sec:kadanoff-procedure}
+Теперь обоснуем гипотезу подобия в модели Изинга при помощи процедуры Каданова и свяжем индексы $a,b$ с $\nu,\eta$.
+Рассмотрим кубическую $d$-мерную модель Изинга.
+\begin{equation}
+  \label{eq:40}
+  H=-J\sum_{\left<ij\right>}\sigma_i \sigma_j-h\sum_i \sigma_i
+\end{equation}
+Разбиваем решетку на блоки со стороной в $r$ ячеек. Будем нумеровать блоки большими латинскими буквами $I,J$ и понимать под записью $i\in I$ перечисление вершин в $I$-том блоке.
+Сумма спинов в блоке принимает значения от $r^{-d}$ до $r^d$. Введем блочный спин
+\begin{equation}
+  \label{eq:41}
+  \Sigma_I=\frac{1}{R}\sum_{i\in I}\sigma_i
+\end{equation}
+$R$ - нормировочный множитель, который выбирается так, чтобы блочный спин мог принимать значения $\pm 1$. Если бы спины были всегда в одном направлении, то $R$ имел бы значение $r^d$.
+
+Мы предполагаем, что поведение вблизи критической точки описывается в терминах блочных спинов, так как корреляционная длина $\xi>>r$. Гамильтониан для блочных спинов имеет вид
+\begin{equation}
+  \label{eq:42}
+  H'=-J' \sum_{\left<IJ\right>} \Sigma_I \Sigma_J-h' \sum_I \Sigma_I
+\end{equation}
+Так как корреляционная длина для блоков
+\begin{equation}
+  \label{eq:43}
+  \xi'=\frac{\xi}{r},
+\end{equation}
+то из (\ref{eq:31}) для температуры имеем
+\begin{equation}
+  \label{eq:44}
+  t'=r^{\frac{1}{\nu}} t.
+\end{equation}
+Суммарная энергия взаимодействия со внешним полем должна оставаться неизменной, то есть
+\begin{equation}
+  \label{eq:45}
+  h\sum_i \sigma_i=h' \sum_I \Sigma_I=\frac{h'}{R}\sum_i \sigma_i\quad\Longrightarrow\quad h'= Rh
+\end{equation}
+Так как общая свободная энергия тоже не должна меняться, то свободная энергия на блок $\sim r^d f$, то есть
+\begin{equation}
+  \label{eq:46}
+  f(t',h')=r^d f(t,h)
+\end{equation}
+или
+\begin{equation}
+  \label{eq:47}
+  f(t,h)=r^{-d} f(r^{\frac{1}{\nu}} t, Rh)
+\end{equation}
+Осталось вычислить $R$ как функцию от $r$, чтобы оправдать гипотезу подобия. Смотрим на парный коррелятор в критической точке
+\begin{multline}
+  \label{eq:48}
+  \Gamma'(\vec n)=\left< \Sigma_I\Sigma_J\right>-\left< \Sigma_I\right>\left<\Sigma_J\right>=\frac{1}{R^2}\sum_{i\in I}\sum_{j\in J}\left(\left<\sigma_i \sigma_j\right>-\left<\sigma_i\right>\left<\sigma_j\right>\right) =\\
+  = \frac{r^{2d}}{R^2}\Gamma(r\vec n)=\frac{R^{-2}r^{2d}}{\left|r\vec n\right|^{d-2+\eta}}=\frac{R^{-2}r^{d+2-\eta}}{\left|\vec n\right|^{d-2+\eta}}
+\end{multline}
+Отсюда
+\begin{equation}
+  \label{eq:49}
+  R=r^{\frac{d+2-\eta}{2}}, \quad h'=r^{\frac{d+2-\eta}{2}}h
+\end{equation}
+Подставляя в (\ref{eq:33}) $r=\lambda^{\frac{1}{d}}$ получаем выражение для скейлинговых параметров $a,b$:
+\begin{eqnarray}
+  \label{eq:50}
+  a=\frac{1}{\nu d}\\
+  b=\frac{d+2-\eta}{2d}
+\end{eqnarray}
+Для критических индексов имеем
+\begin{eqnarray}
+  \label{eq:51}
+  \alpha=2-\nu d\\
+  \beta=\frac{1}{2}\nu (d-2+\eta)\\
+  \gamma=\nu (2-\eta)\\
+  \delta=\frac{d+2-\eta}{d-2+\eta}
+\end{eqnarray}
+
+\section{Лекция 5}
+\label{sec:lecture-3}
+В прошлой лекции мы обосновали гипотезу подобия при помощи рассмотрения блочных спинов и введения эффективного гамильтониана, имеющего ту же форму, но другие константы связи.
+Эта процедура является перенормировкой в координатном пространстве, она определяет отображение гамильтониана $H\to H'$.
+Последовательное применение такой процедуры порождает так называемую ренормгруппу.
+Строго говоря, ренормгруппа является не группой, полугруппой, так как у преобразования нет обратного, ведь при переходе к блокам большего размера мы теряем информацию.
+Опишем ренормгруппу для решеточных моделей.
+
+\subsection{Ренормгруппа в решеточных моделях}
+\label{sec:renormgroup-lattice-models}
+Рассматриваем решеточную модель, состоящую из $N$ спинов $\sigma_i$ на $d$-мерной решетке. Общий вид гамильтониана таких моделей
+\begin{equation}
+  \label{eq:55}
+  H(\vec J,[\sigma],N)=J_0 + J_1\sum_i \sigma_i +J_2\overset{(1)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j+J_3\overset{(2)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j + \dots
+\end{equation}
+Здесь мы явно указали на зависимость гамильтониана от констант связи, которые собраны в вектор $\vec J=(J_0,J_1,J_2,J_3,\dots)$.
+Сумма $\overset{(1)}{\sum_{\left<ij\right>}}$ - это сумма по ближайшим соседям, $\overset{(2)}{\sum_{\left<ij\right>}}$ - сумма по вершинам, разделенным двумя ребрами (через одного) и так далее.
+Статсумма
+\begin{equation}
+  \label{eq:56}
+  Z(\vec J,N)=\sum_{[\sigma]}e^{-H(\vec J,[\sigma],N)}
+\end{equation}
+Мы так переопределили константы связи, чтобы избавиться от множителя $\beta$.
+
+Теперь мы вводим блочные переменные с блоком со стороной в $r$ ячеек решетки, содержащим $r^d$ вершин.
+$\Sigma_I$ - блочные спины, $\xi_i$ - переменные внутри блока.
+В таких переменных статсумма переписывается так:
+\begin{equation}
+  \label{eq:57}
+  Z(\vec J,N)=\sum_{[\Sigma][\sigma]}e^{-H(\vec J,[\Sigma],[\sigma],N)}
+\end{equation}
+Если мы просуммируем по внутриблочным степеням свободы $\xi$, то получится перенормированный гамильтониан $H'(\vec J,[\Sigma],Nr^{-d})$.
+\begin{equation}
+  \label{eq:58}
+  e^{-H'(\vec J',[\Sigma],Nr^{-d})}=\sum_{[\xi]}e^{-H(\vec J,[\Sigma],[\xi],N)}
+\end{equation}
+Вблизи критической точки можно предполагать что у $H'$ такой же вид, как и у $H$, так как параметр порядка расходится и поведение определяется дальними корреляциями.
+Описания поведения системы в терминах $H'$ и $H$ эквивалентны, поэтому соответствующие выражения для статсуммы должны совпадать (с точностью до умножения на константу):
+\begin{equation}
+\label{eq:52}
+  Z(\vec J,N)=\sum_{[\Sigma]}e^{-H'(\vec J',[\Sigma],Nr^{-d})}=Z(\vec J',Nr^{-d})
+\end{equation}
+Удельная свободная энергия отображается как $f(\vec J)=r^{-d} f(\vec J')$.
+
+Отображение констант связи $\vec J\to\vec J'$ и порождает ренормгруппу. Будем его записывать как
+\begin{equation}
+  \label{eq:53}
+  \vec J'=T(\vec J)
+\end{equation}
+Последовательное применение таких преобразований порождает в пространстве констант связи некоторый набор точек, который называется траекторией ренормгруппы.
+
+На каждом шаге корреляционная длина уменьшается в $r$ раз, поэтому траектория уводит систему из окрестности критической точки.
+Но в самой критической точке корреляционная длина бесконечна, поэтому эта точка неподвижна относительно действия ренормгруппы.
+
+В общем случае критическое поведение наблюдается на некоторой критической поверхности в пространстве $\vec J$. Под действием ренормгруппы точки двигаются по ней. Стационарная точка
+\begin{equation}
+  \label{eq:54}
+  \vec J_c=T(\vec J_c)
+\end{equation}
+называется фиксированной точной ренормгруппы.
+
+Вообще говоря, преобразование $T$ нелинейно, однако в окрестности фиксированной точки его можно линеаризовать.
+Вводим переменную $\delta\vec J=\vec J-\vec J_c$ и раскладываем $T$ в ряд Тейлора по $\delta\vec J$.
+Тогда
+\begin{equation}
+  \label{eq:59}
+  \delta\vec J'=A\delta\vec J,
+\end{equation}
+где $A$ - матрица, $A_{ij}=\frac{\partial T_i}{\partial J_j}$.
+Мы можем диагонализовать матрицу $A$, ее собственные значения мы обозначим через $\lambda_i$, собственные векторы через $\vec u_i$.
+Тогда для точки в пространстве констант связи мы можем написать (в окрестности  критической точки):
+\begin{equation}
+  \label{eq:60}
+  \vec J=\vec J_c+\sum_i t_i \vec u_i
+\end{equation}
+Переменные $t_i$ под действием ренормгруппы преобразуются так:
+\begin{equation}
+  \label{eq:61}
+  t'_i=\lambda_i t_i=r^{y_i} t_i
+\end{equation}
+Здесь мы ввели обозначение $y_i$ для критических индексов. В примере из раздела \ref{sec:kadanoff-procedure} такими индексами были $a$ и $b$. 
+Для свободной энергии имеем
+\begin{equation}
+  \label{eq:62}
+  f(t_1,t_2,\dots)=r^{-d} f(r^{y_1}t_1,r^{y_2}t_2,\dots)
+\end{equation}
+Таким образом, критические индексы получаются из собственных значений линеаризованной ренормгруппы в фиксированной точки.
+
+Если часть собственных значений $\lambda_i$ положительна, а часть - отрицательная, то фиксированная точка называется гиперболической. 
+Критической поверхностью называются такие точки $\vec J$, что
+\begin{equation}
+  \label{eq:63}
+  \lim_{n\to \infty}T^n (\vec J)=\vec J_c
+\end{equation}
+Около точки $\vec J_c$ она представляет собой векторное пространство, натянутое на те векторы $\vec u_i$, для которых соответствующие собственные значения $\lambda_i<1$.
+
+Параметры $t_i$, которые соответствуют $\lambda_i>1$ называются релевантными, так как они растут под действием ренормгруппы.
+Параметры с $y_i<0 \; (\lambda_i<1)$ --- иррелевантные, с $y_i=0$ --- маргинальные.
+
+Существование критической поверхности объясняет универсальность критических индексов в разных моделях.
+Статистические системы разбиваются на классы универсальности, члены которых имеют одинаковое критическое поведение.
+Это так, если разные системы живут на подмногообразиях в пространстве констант связи, которые пересекают одну и ту же критическую поверхность.
+Тогда критическая точка у них общая.
+
+\subsection{Ренормгруппа в непрерывных моделях}
+\label{sec:renormgroup-general}
+В непрерывных моделях перенормировка осуществляется в импульсном пространстве. Рассмотрим скалярное поле $\varphi(\vec x)$, где $\vec x\in \mathbb{R}^d$. Проведем преобразование Фурье
+\begin{equation}
+  \label{eq:64}
+  \varphi(\vec x)=\int \frac{d^d \vec k}{(2\pi)^d}\tilde \varphi(\vec k) e^{i\vec k\cdot \vec x}
+\end{equation}
+Функционал действия может быть переписан в виде, зависящем только от $\tilde\varphi$: $S[\varphi]\to S[\tilde\varphi]$. Например, для модели $\varphi^4$ \eqref{eq:16} получается
+\begin{multline}
+  \label{eq:65}
+  S[\varphi,r,u]=\int  \frac{d^d \vec k}{(2\pi)^d} \frac{1}{2} \tilde\varphi(-\vec k)\tilde\varphi(\vec k)(\vec k^2+r)+\\
+  \frac{1}{4}u\int  \frac{d^d \vec k_1}{(2\pi)^d} \frac{d^d \vec k_2}{(2\pi)^d} \frac{d^d \vec k_3}{(2\pi)^d} \tilde\varphi(-\vec k_1-\vec k_2 -\vec k_3)\tilde \varphi(\vec k_1)\tilde\varphi (\vec k_2)\tilde\varphi(\vec k_3).
+\end{multline}
+В общем случае функционал действия зависит от поля $\varphi$ и параметров $u_i$ в плотности Лагранжиана (констант связи).
+
+Квантовая теория поля всегда содержит расходящиеся интегралы, поэтому нужна регуляризация.
+Будем считать, что в качестве такой регуляризации используется обрезание по импульсам $\left|\vec k\right|<\Lambda$.
+После преобразования Фурье мера в функциональном интеграле переписывается как
+\begin{equation}
+  \label{eq:66}
+  [d\varphi]_{\Lambda}=\prod_x d\varphi(x)=\prod_{\left|\vec k\right|<\Lambda}d\tilde\varphi(\vec k)
+\end{equation}
+Теперь опишем перенормировку Вильсона-Каданова.
+Она проводится в два этапа.
+Сначала мы интегрируем по $\tilde\varphi(\vec k): \Lambda/s<\left|k\right|<\Lambda$.
+То есть мы исключаем быстрые моды, так как критическое поведение описывается медленными модами.
+$s$-масштабный фактор.
+В результате мы получаем новое обрезание $\Lambda/s$ и действие $S'[\varphi,\{u_i\}]$.
+\begin{equation}
+  \label{eq:67}
+  e^{-S'[\varphi,\{u_i\}]}=\int \prod_{\Lambda/s<\left|\vec k\right|<\Lambda}d\varphi(\vec k)e^{-S[\varphi,\{u_i\}]}
+\end{equation}
+Пока нас интересую только медленные моды, действие $S'$ эквивалентно $S$. Вторым шагом осуществим масштабное преобразование
+\begin{eqnarray}
+  \label{eq:68}
+  \vec k \to \vec k'=s \vec k\\
+  \vec x\to \vec x'=\vec x/s
+\end{eqnarray}
+При этом поле преобразуется так:
+\begin{eqnarray}
+  \label{eq:69}
+  \varphi(\vec x)\to \varphi'(\vec x/s)=s^{\Delta}\varphi (\vec x)\\
+  \tilde\varphi'(s\vec k)=s^{\Delta-d}\tilde\varphi (\vec k)
+\end{eqnarray}
+Здесь $\Delta$- скейлинговая размерность поля $\varphi$, она связана с индексом $\eta$: $\Delta=\eta/2$.
+Мера в функциональном интеграле при масштабном преобразовании умножится на константу.
+Теперь можно сравнить $S'$ и $S$, так как масштаб обрезания и там и там равен $\Lambda$ и те же степени свободы.
+Эти два действия описывают одинаковое поведение на больших расстояниях.
+Поэтому вид действия $S'$ должен быть тот же, что и у $S$, но с другими константами связи $u_i'$.
+\begin{equation}
+  \label{eq:70}
+  S'[\varphi,\{u_i\}]=S[\varphi,\{u_i'\}]
+\end{equation}
+Последовательным действием таких преборазований мы получаем кривую $u_i(s)$ в пространстве параметров лагранжиана.  Мы можем записать уравнение этой кривой как
+\begin{equation}
+  \label{eq:71}
+  \frac{du_i}{d(\ln s)}=\beta_i(\{u_i\})
+\end{equation}
+$\beta_i$ называется $\beta$-функцией параметра $u_i$. 
+Фиксированная точка $u_j^{*}$:
+\begin{equation}
+  \label{eq:72}
+  \beta_i(\{u^{*}_j\})=0
+\end{equation}
+Эта точка неподвижна относительно преобразований ренормгруппы. В фиксированной точке теория масштабно-инвариантна на квантовом уровне.
+
+\section{Лекция 6 }
+\label{sec:lecture-4}
+\subsection{Уравнение Каллана-Симанчика}
+
+Вообще говоря, квантовая теория поля может быть не масштабно-инвариантна из-за наличия размерных параметров на классическом уровне или возникающих при перенормировке. Действие
+\begin{equation}
+  \label{eq:73}
+  S=\int d^dx \mathcal{L}
+\end{equation}
+зависит от полей $\varphi$ и констант связи $\vec u=(u_1,\dots,u_n)$.
+Рассмотрим инфинитезимальное масштабное преобразование $\lambda=1+\omega$.
+При этом вариация $x_{\nu}$ будет $\delta_{\omega}x_{\nu}=\omega x_{\nu}$.
+Такое преобразование, в соответствии с предыдущей лекцией,  можно рассматривать как преобразование констант связи $\vec u\to \vec u'$.
+При наличии масштабной инвариантности $\vec u = \vec u'$.
+При инфинитезимальных преобразованиях $x\to x+dl x$ вариация плотности лагранжиана дается Нётеровским током:
+\begin{equation}
+  \label{eq:74}
+  \delta\mathcal{L}=\partial_{\mu}J^{\mu}dl
+\end{equation}
+\begin{equation}
+  \label{eq:75}
+  J^{\mu}=x_{\nu}T^{\mu\nu}
+\end{equation}
+Здесь $T^{\mu\nu}$ - тензор энергии-импульса.  Через $\Theta$ мы обозначим след тензора энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия
+\begin{equation}
+  \label{eq:87}
+  \delta S=dl \int d^d x \Theta(x)
+\end{equation}
+Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$. В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
+
+В классической теории вид преобразований полей при масштабных преобразованиях легко получаются из анализа размерностей.
+Напомним, что достаточно иметь одну единицу измерения - длины (или обратной длины).
+Если теория масштабно-инвариантна, то действие должно быть безразмерным.
+Канонические (классические) размерности полей легко определить из требования безразмерности слагаемых в функционале действия, если ввести соглашение, определяющее размерность координат или импульсов.
+
+Будем обозначать каноническую размерность произвольно величины $F$ через $d[F]$.
+Положим $d[p]=-d[x]=1$. Тогда $d[d^d x]=-d,\; d[\partial]=1$. Теперь легко найти размерности полей. Например, для модели $\varphi^4$
+\begin{equation}
+  \label{eq:83}
+  S[\varphi]=\int d^d x\left( -\frac{(\partial \varphi)^2}{2}-\frac{\mu \varphi^2}{2}-\frac{u\varphi^4}{24}+h\varphi\right),
+\end{equation}
+рассмотрим первое слагаемое. Оно должно быть безразмерным. При этом его размерность $d[\int d^d x (\partial \varphi)^2]=2d[\varphi]+2-d=0$. Отсюда $d[\varphi]=d/2-1$. Для общего действия
+\begin{equation}
+  \label{eq:84}
+  S[\varphi]=-\int d^d x\left( \frac{(\partial \varphi)^2}{2}+\sum_n u_n \frac{\varphi^n}{n!}\right)
+\end{equation}
+размерности констант связи следующие:
+\begin{equation}
+  \label{eq:85}
+  d[h=-u_1]=d/2+1,\quad d[\mu=u_2]=2,\quad d[g_4]=4-d,\quad d[g_6]=6-2d,\quad d[g_n]=n-\frac{d(n-2)}{2}
+\end{equation}
+При масштабных преобразованиях поля и константы связи ведут себя так:
+\begin{equation}
+  \label{eq:86}
+  \varphi'(x)=s^{-d[\varphi]}\varphi(x/s),\quad u_i'=s^{-d[u_i]}u_i
+\end{equation}
+
+Напомним, что
+\begin{equation}
+  \label{eq:76}
+  \beta_{i}(\vec u)=\frac{du_i}{d\ln s}
+\end{equation}
+Параметр ренормгруппы $s$ связан с параметром масштабного преобразования $l$ соотношением $l=\ln s$, при этом
+\begin{equation}
+  \label{eq:79}
+   \beta_{i}(\vec u)=\frac{du_i}{dl}
+\end{equation}
+Если в точке $u$ $\beta_i(\vec u)>0$, то $u_i(l)$ растет, $\beta_i (\vec u)<0$ - убывает.
+В фиксированной точке $u^*$ $\beta_i(\vec u^*)=0$.
+Пространство действий делится фиксированной точкой на регионы.
+Константы связи ``заперты'' в одном из этих регионов.
+Фиксированная точка может достигаться при $l\to \pm \infty$.
+Если $u(l)\to u^*$ при $l\to +\infty$, то такая точка называется инфракрасной, если $u(l)\to u^*$ при $l\to -\infty$, то ультрафиолетовой.
+Введем функции $\Phi_i$:
+\begin{equation}
+  \label{eq:77}
+  \Phi_i=\frac{\partial \mathcal{L}}{\partial u_i}
+\end{equation}
+Вариация $\delta \mathcal{L}$ дается их линейной комбинацией.
+\begin{equation}
+  \label{eq:78}
+  \Theta(x)=\frac{\partial \mathcal{L}}{\partial l}=\sum_i \frac{\partial \mathcal{L}}{\partial u_i}\frac{d u_i}{dl}=\sum_i\beta_i(\vec u)\Phi_i(\vec u)
+\end{equation}
+$\Theta=0$ тогда и только тогда, когда $\beta_i(\vec u)=0$, значит в фиксированной точке ренормгруппы есть масштабная инвариантность.
+
+Рассмотрим $N$-точечную корреляционную функцию --- среднее значение некоторого $N$-точечного локального оператора
+\begin{equation}
+  \label{eq:81}
+  \langle X\rangle =\langle A_1 (x_1)\dots A_N (x_N)\rangle
+\end{equation}
+
+Мы хотим получить уравнение для его преобразования под действием ренормгруппы. Такое уравнение называется уравнением Каллана-Симанчика.
+
+Вариация корреляционных функций при масштабных преобразованиях может описываться двумя способами.
+
+Во-первых, мы можем вычислить вариацию всех полей:
+\begin{multline}
+  \label{eq:82}
+  \delta \langle X\rangle=\delta \langle A_1(x_1)\dots A_N (x_N)\rangle = \delta \int {\cal D}\varphi A_1 \dots A_N e^{-S[\varphi]} = \\
+  \delta \int {\cal D} \varphi\; \left( \sum_k A_1 \dots \delta A_k \dots A_N e^{-S[\varphi]} -A_1\dots A_N e^{-S[\varphi]}\delta S\right)
+\end{multline}
+Вариация $A_k$ дается глобальной дилатацией координат и внутренней вариацией поля в соответствии с его канонической размерностью:
+\begin{equation}
+  \label{eq:88}
+  \delta A_k=dl (x^{\mu}_k\partial^k_{\mu}+d[A_k]) A_k
+\end{equation}
+Вариация действия определяется следом тензора энергии-импульса (\ref{eq:87}). Поэтому
+\begin{equation}
+  \label{eq:89}
+  \delta\langle X\rangle=dl \left(\sum_k (x_k^{\mu}\partial_{\mu}^k+d[A_k])\langle X\rangle-\int d^d y \Theta(y)\right)
+\end{equation}
+
+Другой способ вычисления состоит в вариации полей и действия по константам связи $u_i$:
+\begin{equation}
+  \label{eq:90}
+  \delta\langle X\rangle=dl\sum_i \beta_i(\vec u)\frac{\partial}{\partial u_i}\langle X\rangle,
+\end{equation}
+но
+\begin{equation}
+  \label{eq:91}
+  \frac{\partial}{\partial u_i}\langle X\rangle=\sum_k \langle A_1\dots \frac{\partial A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Phi_i(y)\rangle.
+\end{equation}
+Отсюда
+\begin{equation}
+  \label{eq:92}
+  \delta\langle X\rangle=dl \sum_i \sum_k\langle A_1\dots \frac{\partial A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Theta(y)\rangle
+\end{equation}
+Сравнивая это уравнение с (\ref{eq:89}) получаем уравнение Каллана-Симанчика:
+\begin{equation}
+  \label{eq:93}
+  \left[ \sum_k\left( x^{\mu}_k \frac{\partial}{\partial x^{\mu}_k}+\Gamma_k(\vec u)\right) -\sum_i \beta_i(\vec u)\frac{\partial }{\partial u_i}\right]\langle X\rangle=0,
+\end{equation}
+где $\Gamma_k$ - аномальная размерность поля $A_k(x_k)$, определяющаяся выражением
+\begin{equation}
+  \label{eq:94}
+  \Gamma_k A_k(x_k)=\left( d[A_k]+\sum_i \beta_i(\vec u) \frac{\partial }{\partial u_i}\right) A_k(x_k).
+\end{equation}
+В частности, для следа тензора энергии-импульса $\Gamma \Theta=2 \Theta$, то есть аномальная размерность равна классической.
+Это верно и для других компонент тензора энергии-импульса в силу Лоренц-инвариантности.
+
+\subsection{Ренормгруппа в двух измерениях}
+\label{sec:renormgroup-in-2d}
+
+Реноргрупповой анализ квантовой теории поля в двух измерениях дает следующий результат, известный как $c$-теорема Замолодчикова \cite{zamolodchikov1986irreversibility}.
+
+\begin{theorem}
+  Для любой унитарной квантовой теории поля в двух измерениях существует функция $c(\vec u)$ такая, что
+  \label{c-theorem}
+  \begin{itemize}
+  \item $c(\vec u)$ убывает, как функция параметра ренормгруппы
+    \begin{equation}
+      \label{eq:95}
+      \frac{dc}{dl}\leq 0
+    \end{equation}
+  \item $c(\vec u)$ стационарна в фиксированной точке $\vec u^*$ ренормгруппы, то есть
+    \begin{equation}
+      \label{eq:96}
+      \frac{dc({\vec u^*})}{dl}=0 \Leftrightarrow \beta_i(\vec u^*)=0
+    \end{equation}
+  \item 2-точечные корреляторы в фиксированной точке полностью определяются значением $c=c(\vec u^*)$.
+    Если ввести комплексные координаты $z=x_1+ix_2,\quad \bar z=x_1-ix_2$ и обозначить компоненты тензора энергии импульса через $T=T_{zz}$, $\bar T=T_{\bar z\bar z}$, $\Theta=T_{z\bar z}=T_{\bar z z}=T_{\mu\mu}=0$, то для корреляторов верно следующее выражение
+    \begin{eqnarray}
+      \label{eq:97}
+      \langle T(z,\bar z)T(0,0)\rangle=\frac{c/2}{z^4}\\
+      \langle \bar T(z,\bar z)\bar T(0,0)\rangle=\frac{c/2}{\bar z^4}\\
+      \langle T(z,\bar z) \bar T(0,0)\rangle=0
+    \end{eqnarray}
+    Число $c=\lim_{\vec u\to \vec u^*} c(\vec u)$ называется центральным зарядом. 
+  \end{itemize}
+\end{theorem}
+Для унитарных теорий из этой теоремы следует, что $c_{UV}\geq c_{IR}$.
+
+В фиксированной точке ренормгруппы имеет место масштабная инвариантность.
+Вместе с трансляционной и лоренц-инвариантностью она порождает конформную инвариантность, то есть инвариантность относительно преобразований, сохраняющих углы.
+
 \section{Лекция 7. Конформная группа.}
@@
 
-Теперь опишем структуру модуля Верма со старшим весом $h$.
+Теперь опишем структуру модуля Верма со старшим весом $h$ (Таблица \ref{tab:verma}).
 
 \begin{table}[tbh]
-\label{tab:diagrams} \noindent \centering{\
+\label{tab:verma} \noindent \centering{\
 \begin{tabular}{|l|l|l|l|}

### 2011-12-21 GeneralOverview/Lectures/CFT-APTU-2011.tex
Some misprints corrected.

@@
 \author{Антон Назаров\\
-  \small{СПбГУ, физический факультет}\\
-  \small{кафедра физики высоких энергий и элементарных частиц}\\
+  \small{СПбГУ, физический факультет, кафедра физики высоких энергий и элементарных частиц;}\\
+  \small{математико-механический факультет, междисциплинарная лаборатория имени П.Л. Чебышева}\\
   \texttt{antonnaz@gmail.com}
 }
-\date{Осенний семестр 2010 года}
+\date{Осенний семестр 2011 года}
 
@@
   Текст представляет собой конспект лекций по квантовой теории поля в двух измерениях.
-Лекции читались в осеннем семестре 2010 года в Академическом университете для магистрантов 6 курса (группа теории конденсированного состояния).
+Лекции читались в осеннем семестре 2010 года и в осеннем семестре 2011 в Академическом университете для магистрантов 6 курса (группа теории конденсированного состояния).
 \end{abstract}
@@
   \end{itemize}
-\item Перенормировки, ренормгруппа
 \item Решение модели Изинга
@@
   \end{itemize}
+\item Перенормировки, ренормгруппа
 \item Конформная инвариантность
@@
 Решений со внешним полем и в большем числе измерений пока не известно.
-Недавнее достижение Станислава Смирнова, за которое он получил в этом году премию Филдса, непосредственно связано с темой наших лекций.
-В своих работах Станислав Смирнов впервые строго доказал наличие конформного предела в двумерной модели Изинга \cite{smirnov2007conformal,smirnov2006towards,smirnov2001critical}.
-Фазовые переходы в модели Изинга наблюдаются только в этом пределе, при конечных размерах системы никаких переходов нет.
+Недавнее достижение Станислава Смирнова, за которое он получил в 2010 году премию Филдса, непосредственно связано с темой наших лекций.
+В своих работах Станислав Смирнов впервые строго доказал наличие конформной инвариантности в критической точке двумерной модели Изинга \cite{smirnov2007conformal,smirnov2006towards,smirnov2001critical}.
+
+Фазовые переходы в модели Изинга наблюдаются только в термодинамическом пределе, при конечных размерах системы никаких переходов нет.
 
@@
 
-В критической точке параметр порядка системы стремится к бесконечности, кроме того, фазовый переход в дискретных моделях наблюдается только в термодинамическом пределе числа вершин стремящегося к бесконечности ($N\to \infty$).
+В критической точке параметр порядка системы стремится к бесконечности, кроме того, фазовый переход в дискретных моделях наблюдается только в пределе числа вершин стремящегося к бесконечности ($N\to \infty$).
+Такой предел называется термодинамическим.
 Поэтому при описании фазового перехода имеет смысл перейти от модели с дискретным пространством  к непрерывному $d$-мерному пространству.
@@
 При нулевой температуре ($\beta\to \infty$) мы получаем обычный производящий функционал в евклидовом времени, то есть теорию поля.
-При конечных температурах статсумма квантовой $d$-мерной системы напоминает статсумму $d+1$-мерной классической системы на полосе шириной $\beta$.
+При конечных температурах статсумма квантовой $d$-мерной системы соответствует статсумме $d+1$-мерной классической системы на полосе шириной $\beta$.
 
@@
 При переходах второго рода наблюдается скачок производных макроскопических термодинамических величин (теплоемкость, магнитная восприимчивость).
+Эта классификация несколько условна (см.
+\cite{ma2000modern,ma1980}), бывают и другие виды фазовых переходов, например, переход Костерлица-Таулесса \cite{0022-3719-6-7-010}.
 
@@
 \end{equation}
-При $T>T_c$ спонтанная намагниченность исчезает.
+При $T>T_c$ спонтанная намагниченность \eqref{eq:7} исчезает.
 При $T<T_c$ она не равна нулю и стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_c$.
-Это ферромагнитная фаза.
+Это упорядоченная ферромагнитная фаза.
 Около критической точки спонтанная намагниченность ведет себя как
@@
 
-При подходе к критической точке магнитная восприимчивость расходится
+При подходе к критической точке магнитная восприимчивость \eqref{eq:8} расходится
 \begin{equation}
@@
 \begin{array}{l}
-W_{l+1}(n,m,1)=W_l(n-1,m,1)+e^{-i\pi/4} W_l(n,m-1,2)+e^{i\pi/4}W_l(n,m-1,4)\\
-W_{l+1}(n,m,2)=e^{i\pi/4}W_l(n-1,m,1)+W_l(n,m-1,2)+e^{i\pi/4}W_l(n+1,m,3)\\
+W_{l+1}(n,m,1)=W_l(n-1,m,1)+e^{-i\pi/4} W_l(n,m-1,2)+e^{i\pi/4}W_l(n,m+1,4)\\
+W_{l+1}(n,m,2)=e^{i\pi/4}W_l(n-1,m,1)+W_l(n,m-1,2)+e^{-i\pi/4}W_l(n+1,m,3)\\
 W_{l+1}(n,m,3)=e^{i\pi/4}W_l(n,m-1,2)+W_l(n+1,m,3)+e^{-i\pi/4}W_l(n,m+1,4)\\
@@
   \label{eq:134}
-  f=-T \lim_{N\to \infty}\frac{Z_N}{N}=-T \lim_{N\to \infty} \left(\ln (2\ch^2 K)+\frac{1}{2N}\sum_p \ln D_p\right)
+  f=-T \lim_{N\to \infty}\frac{\ln Z_N}{N}=-T \lim_{N\to \infty} \left(\ln (2\ch^2 K)+\frac{1}{2N}\sum_p \ln D_p\right)
 \end{equation}
@@
   \label{eq:142}
-  f\approx g_1 (\epsilon)+c\epsilon^2 \ln(e)
+  f\approx g_1 (\epsilon)+c\epsilon^2 \ln(\epsilon)
 \end{equation}
@@
 
-Мы предполагаем, что поведение вблизи критической точки описывается в терминах блочных спинов, так как корреляционная длина $\xi>>r$. Гамильтониан для блочных спинов имеет вид
+Основной вклад в статсумму вблизи критической точки вносят большие кластеры, так как корреляционная длина $\xi>>r$.
+Поэтому мы предполагаем, что поведение вблизи критической точки описывается в терминах блочных спинов.
+Гамильтониан для блочных спинов имеет вид
 \begin{equation}
@@
 Последовательное применение такой процедуры порождает так называемую ренормгруппу.
-Строго говоря, ренормгруппа является не группой, полугруппой, так как у преобразования нет обратного, ведь при переходе к блокам большего размера мы теряем информацию.
+Строго говоря, ренормгруппа является не группой, а полугруппой, так как у преобразования нет обратного, ведь при переходе к блокам большего размера мы теряем информацию.
 Опишем ренормгруппу для решеточных моделей.
@@
 \end{equation}
-Здесь мы явно указали на зависимость гамильтониана от констант связи, которые собраны в вектор $\vec J=(J_0,J_1,J_2,J_3,\dots)$.
+Здесь мы явно указали зависимость гамильтониана от констант связи, которые собраны в вектор $\vec J=(J_0,J_1,J_2,J_3,\dots)$.
 Сумма $\overset{(1)}{\sum_{\left<ij\right>}}$ - это сумма по ближайшим соседям, $\overset{(2)}{\sum_{\left<ij\right>}}$ - сумма по вершинам, разделенным двумя ребрами (через одного) и так далее.
@@
 \end{equation}
-Удельная свободная энергия отображается как $f(\vec J)=r^{-d} f(\vec J')$.
+Удельная свободная энергия отображается так: $f(\vec J)=r^{-d} f(\vec J')$.
 
@@
 лекцию \ref{sec:kadanoff-procedure}) обосновало нам масштабную инвариантность модели Изинга.
-Сейчас мы обсудим, какие ограничения накладывает на теорию конформная инвариантность, а затем покажем, что в двух измерениях она следует из масштабной, трансляционной и вращательной инвариантностей.
+Сейчас мы обсудим, какие ограничения накладывает на теорию конформная инвариантность.
 
@@
 \end{equation}
-Сравним полученное равенство с результатом применения оператора $\partial^2$ к уравнению \eqref{eq:149}:
+Сравним полученное равенство с результатом применения оператора $\partial^{\rho}$ к уравнению \eqref{eq:149}:
 \begin{equation}
@@
   x'^{\mu}=x^{\mu}+a^{\mu}&\quad \mbox{--- трансляция}\\
-  x'{\mu}=\alpha x^{\mu} &\quad \mbox{--- растяжение}\\
+  x'^{\mu}=\alpha x^{\mu} &\quad \mbox{--- растяжение}\\
   x'^{\mu}=m^{\mu}_{\nu} x^{\nu} &\quad \mbox{--- поворот}\\
@@
   \label{eq:226}
-  \partial \epsilon=0\\
-  \bar \partial \bar \epsilon=0.
+ \bar \partial \epsilon=0\\
+  \partial \bar \epsilon=0.
 \end{eqnarray}
@@
 \end{eqnarray}
-Прежде чем мы начнем переписывать тождества в комплексных координатах обсудим следующий вспомогательный математический факт: для голоморфных (антиголоморфных) функций можно использовать следующее представление для $\delta$-функции:
+Прежде, чем мы начнем переписывать тождества в комплексных координатах, обсудим следующий вспомогательный математический факт: для голоморфных (антиголоморфных) функций можно использовать следующее представление для $\delta$-функции:
 \begin{equation}
@@
   2\pi \partial \langle T_{\bar z \bar z } X\rangle +2\pi \bar \partial \langle T_{z\bar z}X\rangle = -\sum_{i} \bar \partial \frac{1}{\bar z-w_{i}} \partial_{\bar w_{i}} \langle X \rangle\\
-  2 \langle T_{z\bar z} X 1\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) \Delta_{i} \langle X\rangle\\
-  -2 \langle T_{z\bar z} X 1\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) s_{i} \langle X\rangle\\
+  2 \langle T_{z\bar z} X\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) \Delta_{i} \langle X\rangle\\
+  -2 \langle T_{z\bar z} X\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) s_{i} \langle X\rangle\\
 \end{eqnarray}
@@
 \end{equation}
-Где $\xi$ --- корреляционная длина. $\xi^{-1}$ можно рассматривать как массу в теопии. В критической точке $\xi$ расходится и теория становится безмассовой.
+Где $\xi$ --- корреляционная длина. $\xi^{-1}$ можно рассматривать как массу в теории. В критической точке $\xi$ расходится и теория становится безмассовой.
 \begin{equation}
@@
 Это выражение не совсем точное, так как при вычислении $\varepsilon_{n}$ надо брать среднее по всем соседям, но сейчас нам это не очень важно.
-В любом случае коррелятор оператора энергии соответствует цетырехточечной функции.
-
-Мы знаем (см. Лекции \ref{sec:lecture-2}, \ref{sec:lecture-5}, \ref{sec:lecture-6}) значения критических индексов в модели Изинга --- $\eta=\frac{1}{4}, \nu=1$. Тогда для двухточечной функции
+В любом случае коррелятор оператора энергии соответствует четырехточечной функции.
+
+Мы знаем (см. Лекции \ref{sec:lecture-1}, \ref{sec:lecture-5}, \ref{sec:lecture-6}) значения критических индексов в модели Изинга --- $\eta=\frac{1}{4}, \nu=1$. Тогда для двухточечной функции
 \begin{equation}
@@
 \end{eqnarray}
-следовательно $\psi=\psi(x)$ и $\bar \psi=\bar \psi(\bar z)$.
+следовательно $\psi=\psi(z)$ и $\bar \psi=\bar \psi(\bar z)$.
 

### 2011-12-22 AffineLieAlgebras/Splints/paper2.tex
Some work on second paper on splints

--- 2011-12-13 AffineLieAlgebras/Splints/paper2.tex
@@
   {\small $^1$ Department of High-energy and elementary particle physics, SPb State University}\\
-  {\small 198904, Saint-Petersburg, Russia}\\
+  {\small 198904, Saint-Petersburg, Russia,}
   {\small e-mail: lyakh1507@nm.ru}\\
-  {\small$^{2}$ Chebyshev Laboratory,}\\
+  {\small$^{2}$ Chebyshev Laboratory,}
   {\small Department of Mathematics and Mechanics, SPb State University}\\
-  {\small 199178, Saint-Petersburg, Russia}\\
+  {\small 199178, Saint-Petersburg, Russia}
   {\small email: antonnaz@gmail.com}}
+\date{}
 \maketitle
@@
 splint properties drastically simplifies calculations of
-branching coefficients. We study affine extension of splint root system of simple Lie algebra.
+branching coefficients. We study affine extension of splint root system of simple Lie algebra and obtain relations on theta and branching functions.
 \end{abstract}
@@
 
-Consider Lie algebra $\gf$ and its irreducible modules $L^{\mu}_{\gf}$. 
-Splints of root systems were introduced by D.
-Richter in paper \cite{richter2008splints} to describe cases of drastic simplification of module reduction into the sum of subalgebra modules.
-In paper \cite{2011arXiv1111.6787L} we've proved that branching coefficients coincide with multiplicities (more details here).
+The term {\it splint} was introduced by D. Richter in \cite{richter2008splints} where the
+classification of splints for simple Lie algebras was obtained. The fan $\Gamma \subset \Delta$ was
+introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent properties of
+branching coefficients for maximal embeddings. Injection fan is an efficient tool to study branching
+rules. Later this construction was generalized to non-maximal embeddings and affine Lie algebras in
+\cite{2010arXiv1007.0318L, ilyin812pbc}. In paper \cite{2011arXiv1111.6787L} we have shown that the
+existence of a splint for a root system of a simple Lie algebra leads to simplifications in
+reduction procedures of a Lie algebra module to modules of a subalgebra. This effect is based on the
+injection fan and singular element properties of Lie algebra modules.
 
-In present note we generalize our analysis to affine extension of $\gf$.
-We consider affine Lie algebra $\gfh$ with the underlying simple finite-dimensional Lie algebra $\gf$.
-We assume that root system $\Delta_{\gf}$ admits splint $\Delta_{\gf}=\Delta_{\af_{1}}\cup \Delta_{\af_{2}}$.
-It is well-known \cite{kac1990idl} that irreducible $\gfh$-module can be decomposed into the sum of irreducible $\gf$-modules.
+In the present note we discuss possible applications of splint in
+a root system of simple Lie algebra related to representation
+theory of affine Lie algebras. We discuss the structure of
+injection fan for affine Lie algebras and show that it admits a
+decomposition similar to that used in \cite{2011arXiv1111.6787L}
+for simple Lie algebras. Such a decomposition leads to equations
+for theta-functions. We study graded branching of affine Lie
+algebra modules reduced to a finite-dimensional subalgebra and
+discuss consequences of splint in this case.
+
+\section{Splints and affine Lie algebras}
+\label{sec:definitions}
+
+Consider simple Lie algebra $\gf$ with a root system $\Delta$. Let
+$\af_{1}\subset \gf$ be its reductive subalgebra, such that
+$\Delta_{1}\subset\Delta$. Irreducible highest-weight modules of
+$\gf$ and $\af$ are denoted by $L^{\mu}$ and $L^{\nu}_{\af}$
+correspondingly. Weyl character formula for irreducible modules is
+$\mathrm{ch}L^{\mu}=\frac{\Psi^{(\mu)}}{\prod_{\alpha\in\Delta}(1-e^{-\alpha})}$,
+where $\Psi^{(\mu)}=\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}$
+is a singular element of the module and $W$ -- the Weyl group of
+$\gf$. Formal character of irreducible module admits a
+decomposition
 \begin{equation}
-  \label{eq:1}
-  L_{\gfh}^{\mu}=\bigoplus_{\nu=(\co{\nu},n,k)} b^{\mu}_{\co{\nu}}(n) L^{\co{\nu}}_{\gf}
+  \label{eq:4}
+  \mathrm{ch} L^{\mu}=\sum_{\nu\in P_{\af}} b^{\mu}_{\nu} \mathrm{ch} L^{\nu}_{\af},
 \end{equation}
-Then each of these $\gf$-modules in this decomposition admits decomposition to $\af_{1}$ modules with branching coefficients equal to weight multiplicities of $\af_{2}$ irreducible module \cite{2011arXiv1111.6787L}.
+where $P$, $P_{\af}$ are weight lattices of $\gf$ and $\af$. We
+want to study affine extension of this situation:
+$\gf\subset\gfh,\; \af\subset\afh$, $\afh\subset\gfh$,
+$\hat{\Delta}\subset\hat{\Delta}$ and
+$\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{\hat{\nu}}
+b^{\hat{\mu}}_{\hat{\nu}} \mathrm{ch} L^{\hat{\nu}}_{\afh}$. For
+weights of an affine Lie algebra $\gfh$ we have
+$\hat{\mu}=(\mu,k,n)$, where $\mu$ is a weight of $\gf$, $k$ --
+the level of the module and $n$ -- the grade of the weight
+$\hat{\mu}$
+
+\begin{Def}
+  Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a bijective map of
+  roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with vector composition law
+  in $\Delta_{1}$ and $\Delta$.
+\begin{equation*}
+\phi:\Delta_1 \longrightarrow \Delta, \quad \phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,\,\,\, \alpha,\beta \in \Delta_1
+\end{equation*}
+\end{Def}
+
+Note that the image $Im(\phi)$ must not inherit the root system properties except the addition rules
+equivalent to the addition rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and
+$\phi_2$ can splinter $\Delta$ when the latter can be presented as a disjoint union of images
+$Im(\phi_1)$ and $Im(\phi_2)$.
+
+$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
+\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
+_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
+\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+
+\begin{Def}
+  A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if there are two embeddings
+  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
+  \phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the disjoint union of the
+  images of $\phi _{1}$ and $\phi _{2}$ and (b) neither the rank of $\Delta _{1}$ nor the rank of
+  $\Delta _{2}$ exceeds the rank of $%
+  \Delta $.
+\end{Def}
+
+It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote
+this by $\Delta \approx (\Delta_1,\Delta_2)$. Each component $\Delta_1$ and $\Delta_2$ is a "stem''
+of the splint $%
+(\Delta_1,\Delta_2)$.
+
+We consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem. As shown in paper \cite{2011arXiv1111.6787L} the second stem $\Delta _{\frak{s}}:=\Delta
+_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product
+$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}$
+and it defines an injection fan $\Gamma _{\frak{a}%
+\hookrightarrow \frak{g}}$ \cite{lyakhovsky1996rra,ilyin812pbc,2010arXiv1007.0318L}.
+
+Since the singular element of a $\gf$-module $L^{\mu}$ can be
+written as $\Psi _{\frak{g}}^{\left( \mu \right) }=e^{-\rho }
+\sum_{w\in W_{\frak{a}}}\epsilon \left( w \right) w\circ \left(
+e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho
+_{\frak{s}}}\right)$  for branching coefficients we get the
+identity \cite{2011arXiv1111.6787L}:
 \begin{equation}
-  \label{eq:2}
-  L^{\co{\nu}}_{\gf} = \bigoplus b^{\mu}_{\af_{1}\co{\nu}}(n) L^{\co{\nu}}_{\gf}
+  \label{eq:9}
+b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}  
 \end{equation}
-We state that it is possible to reorganize weights in such a way that branching coefficients for the reduction $\gfh\downarrow \af_{1}$  are expressed in terms of weight multiplicities of $\hat\af_{2}$.
-\section{Main theorem}
-\label{sec:main-theorem}
-\begin{theorem}
-  Consider reduction of affine Lie algebra $\gfh$-module $L^{\mu}_{\gfh}$ to finite-dimensional subalgebra $\af_{1}$. Then for branching coefficients following relation holds:
+Here the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $, they have the
+same Dynkin numbers: $\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
+m_{k}\omega_{(\sfr) k} . \label{new h weight}$ So branching coefficients coincide with weight
+multiplicities of $\sfr$-modules.
+
+Now we consider affine extension of this setup, $\afh\subset\gfh$. Since $\mathrm{rank}\gf\leq
+\mathrm{rank} \af+\mathrm{rank}\sfr$ for Weyl denominators we get
+ \[
+\prod_{\alpha\in\hat{\Delta}^{+}_{1}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}\prod_{\beta\in\hat{\Delta}^{+}_{2}}(1-e^{\phi\circ \beta})^{\mathrm{mult}(\beta)}=\prod_{\gamma\in\hat{\Delta}^{+}}(1-e^{-\gamma})^{\mathrm{mult}(\gamma)}\prod_{n=0}^{\infty}(1-e^{-n\delta})^{\mathrm{rank}\af+\mathrm{rank}\sfr-\mathrm{rank}\gf}
+\]
+
+Using a specialization
+\cite{kac1988modular,kac1984infinite,kac1990idl} and the
+definition of Dedekind eta-function
+$\eta(\tau)=q^{1/24}\prod_{n=1}^{\infty}(1-q^{n})$, where
+$q=e^{2\pi i \tau}$ we can rewrite this identity as the relation
+imposed on theta-functions $\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in P_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$:
+\begin{multline}
+  \label{eq:5}
+  \eta(\tau)^{\mathrm{dim}(\af)}\prod_{\alpha\in\Delta_{1}^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z)}{\eta(\tau)} \eta(\tau)^{\mathrm{dim}(\sfr)}\prod_{\beta\in\Delta_{2}^{+}}\frac{\Theta^{(\hat A_{1})}_{\phi\circ \beta}(\tau,z))}{\eta(\tau)}=\\
+\eta(\tau)^{\mathrm{rank}(\af)+\mathrm{rank}(\sfr)-\mathrm{rank}(\gf)}
+\eta(\tau)^{\mathrm{dim}(\gf)}\prod_{\alpha\in\Delta^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z))}{\eta(\tau)}
+\end{multline}
+Here $z\in P_{\geq 0}\otimes \mathbb{C}$. Using Weyl denominator identity this relation can be
+rewritten as a non-trivial relation connecting theta-functions of algebras $\gfh,\hat\sfr,\afh$:
 \begin{equation}
-    \label{eq:3}
-    b^{\mu}_{\nu}=\sum_{?} m^{\nu}_{\hat\af_{2}}
+  \label{eq:6}
+  \left(\sum_{v\in W_{\af}}\epsilon(v) \Theta^{(\afh)}_{v\rho_{\af}}(\tau,z)\right)
+  \cdot \left(\sum_{u\in W_{\sfr}}\epsilon(u) \Theta^{(\hat{\sfr})}_{\phi\circ(u\rho_{\sfr})}(\tau,z)\right)= 
+  \left(\sum_{w\in W}\epsilon(w) \Theta^{(\gfh)}_{w\rho_{\gf}}(\tau,z)\right)
 \end{equation}
-\end{theorem}
-\begin{proof}
-  At first we use equation \eqref{eq:1}, then substitute to equation \eqref{eq:2}, reorganize weights and obtain the desired result. 
-\end{proof}
+%Now we can use Weyl denominator identity $e^{-\rho}\prod_{\alpha\in \hat{\Delta}^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}=\sum_{w\in \hat{W}}\det(w)e^{w\rho}$
 
-\section{Examples}
-\label{sec:examples}
-The most simple example is constructed starting with splint $\Delta_{A_{2}}=\Delta_{A_{1}\oplus A_{1}}\cup \Delta_{A_{1}}$.
+Now consider the branching of $\gfh$-module to $\gf$-modules. For
+formal characters we can write the following expression:
+\begin{equation}
+  \label{eq:8}
+\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{\nu}(n) \mathrm{ch} L^{\nu}_{\gf}.
+\end{equation}
+Rewriting this equation for weight multiplicities we get
+$m^{(\hat{\mu})}_{\hat{\nu}=(\nu,k,n)}=\sum_{\xi\in P}
+b^{(\hat{\mu})}_{\xi}(n) m^{(\xi)}_{\nu}$. We can introduce
+branching functions similarly to the case of branching for affine
+subalgebra \cite{kac1988modular,kac1990idl}:
+$b^{(\hat{\mu})}_{\nu}(q)=\sum_{n=0}^{\infty}
+b^{(\hat{\mu})}_{\nu}(n) q^{n}$.
+These branching functions are connected to $q$-dimension of module $\mathrm{dim}_{q}L^{\hat \mu}_{\gfh}=\sum_{n=0}^{\infty}q^{n}\sum_{\nu\in P} b^{(\hat \mu)}_{\nu}(n) \mathrm{dim }L^{\nu}_{\gf}=\sum_{\nu\in P}b^{(\hat\mu)}_{\nu}(q) \mathrm{dim} L^{\nu}_{\gf}$.
+It is well-known \cite{gannon2006moonshine} that $q$-dimension is a modular function for some $\Gamma\subset SL_{2}(\mathbb{Z})$, so branching functions $b^{(\hat \mu)}_{\nu}(q)$ have modular properties.
 
-Then we consider the case $\gfh=\hat B_{2}$.
+ For string functions of a module
+$L^{\hat{\mu}}$ we have
+\begin{equation}
+  \label{eq:7}
+   \sigma^{(\hat{\mu})}_{\nu}(q) = \sum_{\xi\in P} m^{(\xi)}_{\nu} b^{(\hat{\mu})}_{\xi}(q).
+\end{equation}
+
+Introduce an ordering of the set of weights $\xi$ as follows:
+attribute to a weight $(\rho,\xi)$ its product $(\rho,\xi)$ with
+the Weyl vector $\rho$. Then relation \eqref{eq:7} can be written
+in the matrix form $\sigma(q)=M b(q)$ or as an inverse relation
+$b(q)=M^{-1}\sigma(q)$. Here $\sigma(q)$ and $b(q)$ are infinite
+columns of string and branching functions. Matrix $M$ contains
+multiplicities of weights in $\gf$-modules similar to that of
+Table 1 in paper \cite{2010arXiv1001}. The inverse matrix $M^{-1}$
+encodes recurrent relations imposed weight multiplicities
+\cite{il2010folded}.
+
+Now consider the branching of $\gfh$-modules in $\af$-modules and
+assume the existence of a splint
+$\Delta^{+}_{\gf}=\Delta^{+}_{\af}\cup \phi(\Delta^{+}_{\sfr})$.
+We decompose $\gf$-modules in equation \eqref{eq:8} into
+$\af$-modules using property \eqref{eq:9}:
+\begin{multline}
+  \label{eq:10}
+  \mathrm{ch}L^{\hat{\mu}}_{\gfh}=
+\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P_{\af}} b^{(\hat{\mu})}_{(\gfh\downarrow\af)\nu}(n) \mathrm{ch} L^{\nu}_{\af}=
+\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} b^{(\nu)}_{(\gf\downarrow \af) \xi}\mathrm{ch} L^{\xi}_{\af}=\\
+=\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} M^{\widetilde{\nu}}_{  \widetilde{\nu}-\phi^{-1}( \nu-\xi )}\mathrm{ch} L^{\xi}_{\af}
+\end{multline}
+We see that the similar matrix relation holds for branching
+functions $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}
+b_{(\gfh\downarrow\gf)}(q)$ and we can write
+$\sigma(q)=M_{\af}\cdot b_{(\gfh\downarrow\af)}(q)$. So if we know
+branching coefficients for the embedding $\gf\subset\gfh$ (for
+example, see book \cite{kass1990ala}) we can easily obtain
+branching functions for the embedding $\af\subset \gfh$.
 \section*{Conclusion}
-\label{sec:conclusion}
-Further question is to generalize this analysis to affine sublagebras and apply the results on branching coefficients to the study of CFT coset models.
+\label{sec:conclusion} We have demonstrated that splint in affine
+Lie algebras leads to new relations between theta-functions and
+branching functions for branching to finite-dimensional
+subalgebras, which can be useful for computations. Further
+question is to generalize this analysis to affine subalgebras and
+to apply the results to branching in the study of CFT coset
+models.
+
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+Anton Nazarov thanks the Chebyshev Laboratory (Department of Mathematics and Mechanics,
+Saint-Petersburg State University) for support under the grant 11.G34.31.0026
+of the Government of Russian Federation.
 

### 2011-12-28 AffineLieAlgebras/Thesis/common.tex
Review of CFT fixed

@@
 % Общие разделы автореферата и диссертации
+
 \mkcommonsect{actuality}{Актуальность работы}{%
@@
 На защиту выносятся следующие основные результаты и положения:}{%
-Текст раздела
+\begin{itemize}
+\item Получены новые рекуррентные соотношения на коэффициенты ветвления представлений аффинных алгебр Ли на представления произвольных редуктивных подалгебр
+\item Показана связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда
+\item Показано, что наличие сплинта приводит к существенному упрощению при вычислении коэффициентов ветвления и ведет к новым соотношениям на функции ветвления
+\item Продемонстрирована роль алгебраических методов теории представлений аффинных алгебр Ли в изучении критического поведения в двумерных решеточных моделях
+\item Реализованы различные алгоритмы для вычислений в теории представлений конечномерных и аффинных алгебр Ли
+\end{itemize}
+
 }
@@
 \mkcommonsect{approbation}{Апробация работы}{%
-Текст раздела
+  Материалы диссертации докладывались на семинарах кафедры физики высоких энергий и элементарных частиц СПбГУ, на семинарах в лаборатории имени П.Л.
+Чебышева математико-механического факультета СПбГУ, на  международном семинаре молодых ученых ``Workshop on Advanced Computer Simulation Methods''  27 - 29 апреля 2009 (Санкт-Петербург),  на международных конференциях:  ``Модели квантовой теории поля (MQFT-2010)'' 18-22 октября 2010 (Санкт-Петербург), ``Supersymmetries and Quantum Symmetries - 2011'', 18-23 июля 2011 (Дубна), ``Quantum Theory and Symmetries (QTS-7)'', 7-13 августа 2011 (Прага).
 }
@@
 \mkcommonsect{struct}{Структура и объем диссертации}{%
-Текст раздела
+Диссертация состоит из шести глав.
+
+Глава \ref{cha:CFT} является вводной.
+В ней мы даем обзор конформной теории поля, моделей Весса-Зумино-Новикова-Виттена и coset-моделей.
+Мы приводим аксиоматическую формулировку конформной теории поля, а также обсуждаем БРСТ-подход к описанию калибровочных моделей Весса-Зумино-Новикова-Виттена, приводящий к реализации coset-конструкции.
+
+Основной проблемой данной диссертации является изучение редукции модулей аффинных и конечномерных алгебр Ли на модули подалгебр, вычисление коэффициентов ветвления.
+В главе \ref{cha:affine-lie-algebras} мы вводим основные понятия теории представлений аффинных алгебр Ли и выводим основное рекуррунтное соотношение на коэффициенты ветвления.
+
+В следующей главе \ref{cha:BGG} мы проясняем связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
+
+Глава \ref{cha:splints} посвящена сплинтам.
+
+В главе \ref{sec:SLE} мы описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
+
+Заключительная глава \ref{cha:computational-methods} представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли.
+
 }

### 2011-12-28 AffineLieAlgebras/Thesis/intro.tex
Work on CFT section (axiomatics) + wzw moved to chapter 1
Review of CFT fixed

@@
 % Актуальность работы
-\actualitysection
-\actualitytext
+
+Аффинные алгебры Ли были открыты Виктором Кацем \cite{kac1968simple} и Робертом Муди \cite{moody1968new} в 1967 году в результате отказа от требования положительной определенности матрицы Картана.
+Это требование определяет полупростые конечномерные алгебры Ли.
+Аффинные алгебры Ли отличаются тем, что матрица Картана, задающая коммутационные соотношения, лишь положительно полуопределена.
+Оказывается, что такие алгебры могут быть реализованы как центральные расширения алгебр петель, связанных с полупростыми алгебрами Ли.
+Такая особенность структуры аффинных алгебр Ли привела к тому, что они приобрели особое значение в физике после появления в 1984 году конформной теории поля \cite{belavin1984ics}.
+Ведь квантование теорий поля естественным образом приводит к центральным расширениям алгебр симметрии.
+Теория представлений аффинных алегбр Ли играет определяющую роль при изучении важных классов моделей конформной теории поля -- моделей Весса-Зумино-Новикова-Виттена и coset-моделей.
+
+% Методы, используемые для изучения аффинных алгебр Ли, тесно связаны с теорией представлений конечномерных алгебр Ли, широко используемой в различных разделах физики, в том числе в теории элементарных частиц.
+Большое число
+
+%\actualitysection
+%\actualitytext
 
 % Цель диссертационной работы
-\objectivesection
-\objectivetext
+% \objectivesection
+
+% \objectivetext
 
 % Научная новизна
-\noveltysection
-\noveltytext
+% \noveltysection
+% \noveltytext
 
 % Практическая ценность
-\valuesection
-\valuetext
+% \valuesection
+% \valuetext
 
@@
 \structtext
-Диссертация состоит из трех глав.
-В первой главе рассматривается теория представлений аффинных алгебр Ли.
-Обсуждаются проблемы построения представлений и вычисления правил ветвлений представлений алгебры на представления подалгебры.
-В разделе \ref{sec:branching}  выводятся рекуррентные соотношения для коэффициентов ветвления, в разделе \ref{sec:bgg} обсуждается связь ветвлений представлений с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
-Во второй главе рассматриваются практические алгоритмы для вычисления кратностей и коэффициентов ветвления и описывается пакет {\bf Affine.m} для системы компьютерной алгебры {\it Mathematica}, разработанный с использованием этих алгоритмов.
-В третьей главе рассмотрены приложения к моделям конформной теории поля.
 %%% Local Variables: 

### 2011-12-28 AffineLieAlgebras/Thesis/review.tex
Thesis partially structure cleaned, some translations in chapter 2.
Review of CFT fixed

@@
 
-Конформная теория поля возникла как инструмент для описания критического поведения в двумерных системах \cite{Polyakov:1970xd}.
-В двух измерениях такая теория обладает богатой симметрией, так что ее даже иногда называют точно решаемой \cite{belavin1984ics}.
-На самом деле существуют разнообразные классы моделей двумерной конформной теории поля и даже задача классификации всех таких моделей до конца не решена, несмотря на первоначальный оптимизм \cite{moore1989taming}.
+Двумерная конформная теория поля возникла в результате обобщения гипотезы конформной инвариантности критического поведения в двумерных системах \cite{Polyakov:1970xd}.
+Если использовать для описания критического поведения теорию поля, то такая теория должна обладать конформной инвариантностью.
 
-\section{Общие свойства моделей конформной теории поля}
+Глобальная конформная инвариантность в произвольном числе измерений ведет к важным физическим следствиям.
+Например, особый интерес в последнее время привлекла $N=4$ суперсимметричная модель Янга-Миллса.
+
+ Однако в случае двумерной теории важнейшую роль играет локальная конформная инвариантность.
+Такая теория обладает богатой симметрией, так что ее даже иногда называют точно решаемой \cite{belavin1984ics}.
+
+Конформное преобразование --- это преобразование, меняющее только масштаб у метрического тензора:
+\begin{equation}
+  \label{eq:10}
+  g'_{\mu\nu}(x')=\Lambda(x)g_{\mu\nu}(x)
+\end{equation}
+На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
+В двумерном случае существует бесконечное число локально-конформных преобразований $z\to w(z)$.
+Это легко видеть из условия конформности преобразований, так как в двумерном случае такое
+условие эквивалентно уравнению Коши-Римана для голоморфных функций ($\partial_{\bar z}w(z,\bar
+z)=0$).
+
+Таким образом, локально-конформные преобразования находятся в однозначном соответствии с множеством
+всех аналитических функций $w(z)$ на плоскости.
+
+Глобальные конформные преобразования имеют вид $w(z)=\frac{az+b}{cz+d},\; ad-bc=1$.
+
+Рассмотрим инфинитезимальные преобразования $w(z)=z+\epsilon(z),\quad \epsilon(z)=\sum_{-\infty}^{\infty}c_nz^{n+1}$. 
+Тогда для бесспинового поля $\phi(z,\bar z)$ верно следующее: $\phi'(z',\bar z')=\phi(z,\bar z)$,
+$\delta\phi=-\epsilon(z)\partial\phi-\bar \epsilon(\bar z)\bar \partial \phi=\sum_n(c_n L_n\phi+\bar
+c_n\bar L_n\phi)$, где $L_n=-z^{n+1}\partial_z,\quad \bar L_n=-\bar z^{n+1}\partial_{\bar z}$
+
+Мы видим, что в классической теории алгебра конформных преобразований --- это алгебра Витта, которая
+порождается генераторами $\{L_n, n\in \mathbb{Z}\}$ --- модами разложения оператора энергии-импульса $T$, с
+коммутационными соотношениями
+\begin{equation}
+  \label{eq:2}
+  [L_m,L_n]=(m-n)L_{m+n}
+\end{equation}
+При квантовании возникает конформная аномалия, что соответствует центральному расширению \eqref{eq:9} алгебры  (то
+есть появлению центрального заряда $c$). В коммутационные соотношения надо добавить член
+$\frac{c}{12}(m^3-m)\delta_{m+n,0}$. В результате получаем алгебру Вирасоро.
+
+Поля теории $\phi(z,\bar z)$ должны преобразовываться определенным образом при конформных преобразованиях.
+Оказывается, что все поля группируются в конформные семейства, в которых есть одно примарное поле
+\begin{equation}
+  \label{eq:3}
+  \begin{split}
+    \phi_{\Delta,\bar \Delta}(z,\bar z)\underset{
+      \genfrac{}{}{0pt}{}{z\to w(z)}
+        {\bar z \to \bar w(\bar z)}
+    }
+    {\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\left(\frac{d\bar w}{d\bar
+        z}\right)^{\bar\Delta}\phi_{\Delta,\bar \Delta}(w(z),\bar w(\bar z))\\
+    L_n \phi=0,\quad n>0\\
+    L_0 \phi=\Delta \phi\\
+  \end{split}
+\end{equation}
+$\Delta, \bar \Delta$ называются конформными размерностями поля.
+Все остальные поля называются вторичными и получаются из примарного действием операторов $L_{-n}$:
+\begin{equation}
+  \label{eq:67}
+  L_{-n_1}L_{-n_2}\dots \phi_{\Delta}
+\end{equation}
+Все поля в теории оказываются суммами произведений элементов мультиплетов алгебры Вирасоро.
+
+Алгебраические методы позволяют получать огромное количество точных результатов в двумерных конформных теориях поля.
+Существуют разнообразные классы моделей двумерной конформной теории поля и даже задача классификации всех таких моделей до конца не решена, несмотря на первоначальный оптимизм \cite{moore1989taming}.
+Конформная теория поля привлекла большое внимание также в благодаря своей связи с теорией струн.
+
+Вместе с тем доказательство соответствия между критическим поведением решеточных моделей и конформной теории поля остается серьезной проблемой.
+Здесь в последнее время получены новые результаты, связанные с использованием эволюции Шрамма-Левнера.
+Некоторые вопросы такого соответствия мы обсуждаем в главе \ref{sec:SLE}.
+
+Двумерная конформная теория поля выделяется как модель квантовой теории поля из-за того, что она может быть сформулирована аксиоматически.
+В данной главе мы приводим такую аксиоматическую формулировку в разделе \ref{sec:conformal-field-theory-general}, а затем рассматриваем важнейшие классы моделей конформной теории -- модели Весса-Зумино-Новикова-Виттена \ref{sec:WZNW-models} и coset-модели \ref{sec:coset-models-cft}.
+Эти модели обладают дополнительными симметриями, выражающимися на языке теории представлений аффинных алгебр Ли и являются естественным приложением математических результатов данной диссертации.
+
+В том случае, если в теории конечное число примарных полей, такая теория называется минимальной.
+Обычно соответствие между критическим поведением решеточных моделей и конформной теорией поля устанавливается именно для минимальных моделей \cite{bauer2004cfts,bauer2003sle,bauer2003conformal}.
+Проблема соответствия между решеточными моделями и coset-моделями конформной теории поля обсуждается в главе \ref{sec:SLE}.
+
+Кроме того, конформные теории классифицируются по значениям центрального заряда $c$. Теории с рациональным
+центральным зарядом называются рациональными. Считается, что все такие теории могут быть получены
+факторизацией так называемых моделей Весса-Зумино-Новикова-Виттена \cite{moore1989taming}.
+
+\section{Аксиоматическая формулировка конформной теории поля}
 \label{sec:conformal-field-theory-general}
 
-Двумерная конформная теория поля возникла при изучении моделей критического поведения в двумерных моделях и привлекла большое внимание благодаря новым идеям и своей связи с теорией струн.
-Двумерная конформная теория поля выделяется как модель квантовой теории поля из-за того, что она может быть сформулирована аксиоматически, например, следующим образом.
+Существуют различные подходы к аксиоматизации двумерной конформной теории поля. В общем случае нам
+не нужно знать действие, если мы полный знаем набор примарных полей и операторные разложения их
+произведений.
+
+В данном разделе мы приводим одну из возможных аксиоматических формулировок конформной теории поля, предложенную в работе \cite{felder1989structure} и изложенную в книге \cite{schottenloher2008mathematical}.
+Другие популярные подходы восходят к работам Сегала \cite{segal1987definition} или используют вертексные алгебры \cite{kac1998vertex}.
+
 Введем пространство $S(\mathbb{R}^{n})$ тест-функций $f:\mathbb{R}^{n}\to \mathbb{C}$.
@@
 
-\subsection{Напоминание про двумерную конформную теорию поля}
-\label{sec:CFT}
-
-Конформное преобразование --- это преобразование, меняющее только масштаб у метрического тензора:
-\begin{equation}
-  \label{eq:10}
-  g'_{\mu\nu}(x')=\Lambda(x)g_{\mu\nu}(x)
-\end{equation}
-
-Конформная теория поля --- это теория поля, обладающая инвариантностью относительно этих преобразований.
-
-В теории струн двумерная конформная теория поля описывает динамику на мировой поверхности, а в
-теории критических явлений --- фазовые переходы в двумерных системах.
-
-%% В $D$-мерном случае генераторы у таких преобразований следующие:
-%% \begin{align}
-%%   \label{eq:1}
-%%   & M_{\mu\nu} \equiv i(x_\mu\partial_\nu-x_\nu\partial_\mu) \,, \\
-%%   &P_\mu \equiv-i\partial_\mu \,, \\
-%%   &D \equiv-ix_\mu\partial^\mu \,, \\
-%%   &K_\mu \equiv i(x^2\partial_\mu-2x_\mu x_\nu\partial^\nu) \,,
-%% \end{align}
-%% 
-На двумерной мировой поверхности удобно ввести комплексные координаты $z,\bar{z}$. 
-В двумерном случае существует бесконечное число локально-конформных преобразований.
-Это легко можно увидеть из условия конформности преобразований, так как в двумерном случае это
-условие эквивалентно уравнению Коши-Римана для голоморфных функций ($\partial_{\bar z}w(z,\bar
-z)=0$).
-
-Таким образом локально-конформные преобразования находятся в однозначном соответствии с множеством
-всех аналитических функций $w(z)$ на плоскости.
-
-Глобальные конформные преобразования имеют вид $f(z)=\frac{az+b}{cz+d},\; ad-bc=1$.
-
-Рассмотрим инфинитезимальные преобразования $w(z)=z+\epsilon(z),\quad
-\epsilon(z)=\sum_{-\infty}^{\infty}c_nz^{n+1}$. 
-Тогда для бесспинового поля $\phi(z,\bar z)$ верно следующее: $\phi'(z',\bar z')=\phi(z,\bar z)$,
-$\delta\phi=-\epsilon(z)\partial\phi-\bar \epsilon(\bar z)\bar \partial \phi=\sum_n(c_n L_n\phi+\bar
-c_n\bar L_n\phi)$, где $L_n=-z^{n+1}\partial_z,\quad \bar L_n=-\bar z^{n+1}\partial_{\bar z}$
-
-Мы видим, что в классической теории алгебра конформных преобразований --- это алгебра Витта, которая
-порождается генераторами $\{L_n, n\in \mathbb{Z}\}$ --- модами разложения оператора энергии-импульса $T$, с
-коммутационными соотношениями
-\begin{equation}
-  \label{eq:2}
-  [L_m,L_n]=(m-n)L_{m+n}
-\end{equation}
-При квантовании возникает конформная аномалия, что соответствует центральному расширению \eqref{eq:9} алгебры  (то
-есть появлению центрального заряда $c$). В коммутационные соотношения надо добавить член
-$\frac{c}{12}(m^3-m)\delta_{m+n,0}$. В результате получаем алгебру Вирасоро.
-
-(Про тензор энергии-импульса:
-$x^{\mu}\to x^{\mu}+\epsilon^{\mu}\Rightarrow \delta S=\int d^2 x
-T^{\mu\nu}\partial_{\mu}\epsilon_{\nu}=
-\frac{1}{2}\int d^2 xT_{\mu}^{\mu}\partial_{\rho}\epsilon^{\rho}$
-В двумерной конформной теории поля тензор энергии-импульса бесследовый).
-
-Поля теории $\phi(z,\bar z)$ должны преобразовываться определенным образом при конформных преобразованиях.
-Оказывается, что все поля группируются в конформные семейства, в которых есть одно примарное поле
-\begin{equation}
-  \label{eq:3}
-  \begin{split}
-    \phi_{\Delta,\bar \Delta}(z,\bar z)\underset{
-      \genfrac{}{}{0pt}{}{z\to w(z)}
-        {\bar z \to \bar w(\bar z)}
-    }
-    {\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\left(\frac{d\bar w}{d\bar
-        z}\right)^{\bar\Delta}\phi_{\Delta,\bar \Delta}(w(z),\bar w(\bar z))\\
-    L_n \phi=0,\quad n>0\\
-    L_0 \phi=\Delta \phi\\
-  \end{split}
-\end{equation}
-$\Delta, \bar \Delta$ называются конформными размерностями поля.
-Все остальные поля называются вторичными и получаются из примарного действием операторов $L_{-n}$:
-\begin{equation}
-  \label{eq:67}
-  L_{-n_1}L_{-n_2}\dots \phi_{\Delta}
-\end{equation}
-Все поля в теории оказываются суммами произведений элементов мультиплетов алгебры Вирасоро.
-
-При некоторых дополнительных предположениях двумерную конформную теорию можно построить и решить
-полностью, если определен набор примарных полей и конформных размерностей.
-
-Существуют различные подходы к аксиоматизации двумерной конформной теории поля. В общем случае нам
-не нужно знать действие, если мы полный знаем набор примарных полей и операторные разложения их
-произведений.
-
-В том случае, если в теории конечное число примарных полей, такая теория называется минимальной.
-Кроме того, теории классифицируются по значениям центрального заряда $c$. Теории с рациональным
-центральным зарядом называются рациональными. Оказывается, что все такие теории могут быть получены
-факторизацией так называемых моделей Весса-Зумино-Новикова-Виттена.
-
-\subsection{WZW-модели}
-\label{sec:wzw}
-
 WZW-модели обладают дополнительной симметрией. Алгебра токов в них --- это алгебра Каца-Муди
@@
 
-Сейчас я поясню, что все это значит и как строятся такие модели.
+В данном разделе мы показываем, как такие модели можно строить путем квантования нелинейной сигма-модели с дополнительным членом Весса-Зумино.
 
@@
 
-(Нарисовать картинку штанов).
-
 В теории критического поведения конформная инвариантность имеет место только в критической точке,
@@
 
-%% Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
-%% Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
-%% выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
-%% вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
-%% обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
-%% параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
-%% Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
-%% параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
-%% статсумма дается следом оператора сдвига в степени $m$:
-%% \begin{equation}
-%%   \label{eq:6}
-%%   Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
-%% \end{equation}
-%% Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
-%% конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
-%% $H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
-%% $L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
-%% $P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
-%% можно записать в виде
-%% \begin{equation}
-%%   \label{eq:7}
-%%   \begin{split}
-%%       Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
-%%       L_0)\}\\
-%%       =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
-%%   \end{split}
-%% \end{equation}
-%% Или, если ввести $q=\exp 2\pi i \tau$
-%% \begin{equation}
-%%   \label{eq:2}
-%%   Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
-%% \end{equation}
-%% Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
-%% 
-%% Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
-%% эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
-%% 
+Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
+Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
+выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
+вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
+обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
+параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
+Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
+параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
+статсумма дается следом оператора сдвига в степени $m$:
+\begin{equation}
+  \label{eq:6}
+  Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
+\end{equation}
+Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
+конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
+$H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
+$L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
+$P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
+можно записать в виде
+\begin{equation}
+  \label{eq:7}
+  \begin{split}
+      Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
+      L_0)\}\\
+      =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
+  \end{split}
+\end{equation}
+Или, если ввести $q=\exp 2\pi i \tau$
+\begin{equation}
+  \label{eq:2}
+  Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
+\end{equation}
+Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
+
+Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
+эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
+
 Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
@@
 $\mathbb{C}$.
-%% 
-%% Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
-%% конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
-%% $SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
-%% \begin{equation}
-%%   \label{eq:99} A=
-%%   \begin{pmatrix} a & b\\ c & d
-%%   \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
-%% \end{equation}
-%% и матрицы $A$ и $-A$ действуют одинаково на $\tau$
-%% \begin{equation}
-%%   \label{eq:100} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
-%% \end{equation}
-%% $\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
-%% модулярной группой.
-%% 
+
+Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
+конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
+$SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
+\begin{equation}
+  \label{eq:99} A=
+  \begin{pmatrix} a & b\\ c & d
+  \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+\end{equation}
+и матрицы $A$ и $-A$ действуют одинаково на $\tau$
+\begin{equation}
+  \label{eq:100} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+\end{equation}
+$\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
+модулярной группой.
+
 Конформная теория поля задаётся примарными полями $\Phi_a$ с конформными размерностями $\Delta_a$.
@@
 \end{equation}
-Наша работа посвящена разработке общего метода редукции представлений аффинных алгебр Ли, поэтому
-случай конформных вложений --- лишь один из примеров применения нашего метода. Однако в этом случае
-физический смысл наиболее очевиден.
+Таким образом, редукция представлений аффинной алгебры на представления подалгебры, рассмотренная в главе \ref{cha:affine-lie-algebras}, приводит к построению модулярно-инвариантных статсумм методом конформных вложений.
+
+\section{Coset-модели конформной теории поля}
+\label{sec:coset-models-cft}
+
+Coset-конструкция для моделей конформной теории поля была предложена в работе \cite{Goddard198588}.
+Первоначально она была введена чисто алгебраически на языке генераторов, без обращения к действию и лагранжиану.
+Coset-модели задаются алгеброй Ли $\gf$ и ее подалгеброй $\af$.
+Обозначим через $J_{n}^{a}$ генераторы аффинной алгебры Ли $\gfh$, а через $\tilde{J}_{n}^{b}$ -- генераторы $\afh$, так что $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b} J^{a}_{n}$.
+Генераторы алгебры Вирасоро в coset-моделях даются разностями выражений Сугавары для ВЗНВ-моделей, соответствующих алгебрам  $\gf$ и $\af$:
+\begin{equation*}
+  L_{n}=L_{n}^{\gf}-L_{n}^{\af}
+\end{equation*}
+Коммутационные соотношения между генераторам алгебры Вирасоро и генераторами подалгебры  $\afh$ тривиальны
+\begin{equation}
+  \label{eq:26}
+  \left[L_{n},\tilde{J}^{b}_{m}\right]=0
+\end{equation}
+
+Coset-модели можно реализовать, как калибровочные модели Весса-Зумино-Новикова-Виттена, если добавить дополнительные калибровочные полями  $A, \bar{A}$, принимающие значения в алгебре Ли $\af\subset \gf$, в действие ВЗНВ-модели  \cite{gawdzki1988g}:
+\begin{multline}
+  \label{eq:38}
+      S(g,A)=S_{WZNW}(g)+\\
+      \frac{k}{4\pi}\int d^{2}z \left(\mathcal{K}(A, g^{-1}\bar \partial g)-\mathcal{K}(\bar A, (\partial g ) g^{-1})+\mathcal{K}(A,g^{-1}\bar A g)-\mathcal{K}(A,\bar A)\right)
+\end{multline}
+Полученная теория поля обладает калибровочной инвариантностью и ее квантование естественно проводить с использованием БРСТ-формализма \cite{hwang1993brst}.
+
+Токи в квантовой теории даются выражением
+\begin{equation}
+  \label{eq:39}
+  J_{(\gf,\af)}=-k\partial g g^{-1} -k g A g^{-1}
+\end{equation}
+
+Из тождеств Уорда можно получить равенство
+\begin{equation*}
+  \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{v}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
+\end{equation*}
+
+В coset-моделях поля нумеруются парами весов  $(\mu,\nu)$, где $\mu$ -- вес  $\gfh$, а $\nu$ -- вес $\afh$, соответственно.
+Но появляются правила отбора, так как функции ветвления для некоторых пар весов  $(\mu,\nu)$ исчезают.
+Кроме того, имеется избыточность, так как функции ветвления для различных пар $(\mu,\nu)$ могут совпадать \cite{fuchs1996resolution,schellekens1990field}.
+
+Итак, примарные поля нумеруются парами весов  $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ алгебры $\gfh$ и подалгебры $\afh$, такими, что соответствующие функции ветвления $b^{\mu}_{\nu}(q)\neq 0$.
+Некоторые пары эквивалентны.
+Эта эквивалентность дается действием так называемых ``простых токов'' $(J,\tilde{J})$, которые являются элементами группы внешних автоморфизмов  $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ алгебры $\gfh\times\afh$, где $B(G)$ -- это центр группы Ли $G$.
+Мы можем думать о простых токах как о примарных полях, тогда их действие на поля теории дается слиянием \cite{difrancesco1997cft}.
+Таким образом, примарные поля coset-моделей нумеруются классами эквивалентности пар весов  $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, где $(J,\tilde J)$ такие, что  конформные веса компонент равны:  $h_{J}-h_{\tilde{J}}=0$.
+
+Конформный вес примарного поля в coset-модели равен
+\begin{multline}
+  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
+  \left|\phi_{(\mu,\nu)}\right>=\\
+  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
+\end{multline}
+Из тождеств Уорда можно получить аналог уравнений Книжника-Замолодчикова для coset-моделей \cite{kogan1997knizhnik}:
+\begin{equation}
+  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
+  \label{eq:6}
+\end{equation}
 

### 2011-12-28 AffineLieAlgebras/Thesis/1.tex
Review of CFT fixed

@@
 \label{cha:affine-lie-algebras}
-Аффинные алгебры Ли - это естественное обобщение простых конечномерных алгебр Ли.
-Они возникают при изучении различных физических моделей, например, моделей Весса-Зумино-Новикова-Виттена в конформной теории поля и интегрируемых спиновых цепочек.
-
-\section{Введение}
-\label{sec:introduction}
 
@@
 Выводы к главе изложены в разделе \ref{sec:conclusion}.
-В следующей главе \ref{cha:computational-methods} описывается реализация алгоритма на языке {\it Mathematica} и приводятся дополнительные примеры вычислений.
+В следующей главе \ref{cha:BGG} мы показываем связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
+Реализация алгоритма на языке {\it Mathematica} и дополнительные примеры машинных вычислений описаны в главе  \ref{cha:computational-methods}.
 

### 2011-12-28 AffineLieAlgebras/Thesis/5.tex
Conclusion of the thesis removed, some work on the structure of chapters.

@@
 
-\section{Заключение}
+\section*{Выводы к шестой главе}
 \label{sec:conclusion}
@@
 
-\section{Описание пакета}
+\section*{Описание пакета}
 \label{package}
@@
 
-Содержимое пакета:
-\begin{verbatim}
-    Affine/                              Корневой каталог
-      demo/                               Демонстрации
-        demo.nb                                Демонстрационный файл
-        paper.nb                               Код, содержащийся в статье 
-      doc/                                 Каталог документации
-        figures/                             рисунки в статье
-          timing.pdf                           диаграмма, показывающая производительность
-          branching-timing.pdf                 ...  для коэффициентов ветвления
-          irrep-sum.pdf                        сумма неприводимых представлений B2
-          irrep-verma-pverma.pdf               неприводимое представлений, модуль Верма и обобщенный модуль Верма для B2
-          G2-irrep.pdf                         неприводимое представление G2
-          G2-pverma.pdf                        параболический модуль Верма для G2
-          tensor-product.pdf                   тензорное произведение модулей  A1
-        bibliography.bib                     Библиографическая база
-        paper.pdf                            Статья, описывающая пакет
-        paper.tex                            Исходный LaTeX-файл статьи
-        TODO.org                             Список доработок
-      src/                                 Каталог исходного кода
-        affine.m                             основной пакет
-      tests/                               Каталог тестов
-        tests.m                              тесты
-      README.markdown                    Инструкция по установке и использованию
-\end{verbatim}
+%%  Содержимое пакета:
+%%  \begin{verbatim}
+%%      Affine/                              Корневой каталог
+%%        demo/                               Демонстрации
+%%          demo.nb                                Демонстрационный файл
+%%          paper.nb                               Код, содержащийся в статье 
+%%        doc/                                 Каталог документации
+%%          figures/                             рисунки в статье
+%%            timing.pdf                           диаграмма, показывающая производительность
+%%            branching-timing.pdf                 ...  для коэффициентов ветвления
+%%            irrep-sum.pdf                        сумма неприводимых представлений B2
+%%            irrep-verma-pverma.pdf               неприводимое представлений, модуль Верма и обобщенный модуль Верма для B2
+%%            G2-irrep.pdf                         неприводимое представление G2
+%%            G2-pverma.pdf                        параболический модуль Верма для G2
+%%            tensor-product.pdf                   тензорное произведение модулей  A1
+%%          bibliography.bib                     Библиографическая база
+%%          paper.pdf                            Статья, описывающая пакет
+%%          paper.tex                            Исходный LaTeX-файл статьи
+%%          TODO.org                             Список доработок
+%%        src/                                 Каталог исходного кода
+%%          affine.m                             основной пакет
+%%        tests/                               Каталог тестов
+%%          tests.m                              тесты
+%%        README.markdown                    Инструкция по установке и использованию
+%%  \end{verbatim}
+%%
 
+%%  
 %% References

### 2011-12-28 AffineLieAlgebras/Thesis/2.tex
Conclusion of the thesis removed, some work on the structure of chapters.

--- 2011-09-28 AffineLieAlgebras/Thesis/2.tex
@@
-%% \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
-%% \newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
-%% \newcommand{\co}[1]{\stackrel{\circ }{#1}}
-%% \newcommand{\pia}{\pi_{\mathfrak{a}}}
-%% \newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
-%% \newcommand{\gf}{\mathfrak{g}}
-%% \newcommand{\af}{\mathfrak{a}}
-\newcommand{\bff}{\mathfrak{b}}
-%% \newcommand{\afb}{\mathfrak{a}_{\bot}}
-%% \newcommand{\hf}{\mathfrak{h}}
-\newcommand{\hfg}{\hf_{\gf}}
-%% \newcommand{\hfb}{\mathfrak{h}_{\bot}}
-%% \newcommand{\pf}{\mathfrak{p}}
-%% \newcommand{\aft}{\widetilde{\mathfrak{a}}}
+\chapter{Коэффициенты ветвления и обобщенная резольвента Бернштейна-Гельфанда-Гельфанда}
+\label{cha:BGG}
 
-\begin{abstract}
-%% Text of abstract
-In this paper we present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
-Algorithms are based on the properties of weights and Weyl symmetry.
-The most important problems for us are the ones, concerning computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition.
-These problems have numerous applications in physics and we provide some examples of these applications.
-The program is implemented in popular computer algebra system {\it Mathematica} and works with finite-dimensional and affine Lie algebras.
+Как мы показали в предыдущей главе, рекуррентные соотношения для коэффициентов ветвления основываются на определенном разложении сингулярного элемента.
+В данной главе мы показываем, что такое разложение может использоваться для построения параболических модулей Верма и получения обобщенных формул Вейля-Верма для характеров.
+Также мы демонстрируем, что ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и демонстрирует свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).
 
-% A submitted program is expected to be of benefit to other physicists or physical chemists, or be an exemplar of good programming practice, or illustrate new or novel programming techniques which are of importance to some branch of computational physics or physical chemistry.
-%
-% Acceptable program descriptions can take different forms.
-The following Long Write-Up structure is a suggested structure but it is not obligatory.
-Actual structure will depend on the length of the program, the extent to which the algorithms or software have already been described in literature, and the detail provided in the user manual.
+Резольвента для неприводимых модулей в терминах бесконечномерных модулей важна для теории интегрируемых спиновых цепочек \cite{derk1008}.
+В подходе  $\mathcal{Q}$-оператора Бакстера \cite{derk09} общие трансфер-матрицы, соответствующие (обобщенным) модулям Верма, факторизуются в произведение операторов Бакстера.
+Резольвента позволяет вычислить трансфер-матрицы для конечномерных вспомогательных пространств.
 
-%Your manuscript and figure sources should be submitted through the Elsevier Editorial System (EES) by using the online submission tool at \\
-% http://www.ees.elsevier.com/cpc.
+Чтобы продемонстрировать связь БГГ резольвенты с ветвлением мы используем рекурсивный подход, представленный в работе \cite
+{2010arXiv1007.0318L} (аналогичный подход для максимальных вложений использовался в работе \cite{ilyin812pbc}) и изложенный в главе \ref{cha:affine-lie-algebras}.
+Мы рассматриваем подалгебру $\af \hookrightarrow \gf$ вместе с $\afb$ -- ``ортогональным партнером'' $\af$ по отношению к форме Киллинга, а также подалгебру $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$, где $\frak{h}=\frak{\frak{h}_{\af}}\oplus
+\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. Для любой редуктивной подалгебры $\af$ алгебра $\afb\hookrightarrow \gf$ регулярна и редуктивна. Для интегрируемого модуля старшего веса $%
+L^{\left(\mu \right) }$ и ортогональной подалгебры  $\af_{\bot }$ мы рассматриваем сингулярный элемент $\Psi ^{\left( \mu \right) }$ (числитель в формуле Вейля для характеров $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
+\mu \right) }}{\Psi ^{\left( 0\right) }}$, см., например,  \cite
+{humphreys1997introduction}) и знаменатель Вейля $\Psi _{\af_{\bot
+  }}^{\left( 0\right) }$ для ортогонального партнера. В работе показано, что элемент  $\Psi _{\gf%
+}^{\left( \mu \right) }$ может быть разложен в комбинацию числителей Вейля $\Psi _{\af_{\bot }}^{\left( \nu \right) }$, где $\nu \in P_{%
+\mathfrak{a}_{\bot}}^{+}$. Это разложение дает возможность построить множество модулей старшего веса $L_{\afb}%
+^{\mu _{\afb}}$. В том случае, если вложение\ $\af%
+_{\bot }\hookrightarrow \gf$ \ удовлетворяет ``стандартным параболическим'' условиям, эти модули порождают параболические модули Верма $M_{\left(
+\afb \hookrightarrow \gf\right) }^{\mu _{%
+\afb}}$, так что исходный характер $ch\left(
+L^{\mu }\right) $ в итоге раскладывается в знакопеременную сумму таких модулей.
+С другой стороны, если параболическое условие нарушено, конструкция сохраняется и порождает разложение по отношению к набору обобщенных модулей Верма  $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
+\widetilde{\afb}}}$, где $%
+\widetilde{\frak{b}_{\perp }}$ уже не является подалгеброй в $\gf$, а оказывается сжатием $\widetilde{\afb}$.
 
-%In addition to the manuscript you must supply: the program source code; job control scripts, where applicable; a README file giving the names and a brief description of all the files that make up the package and clear instructions on the installation and execution of the program; sample input and output data for at least one comprehensive test run; and, where appropriate, a user manual.
-These should be sent, via email as a compressed archive file, to the CPC Program Librarian at cpc@qub.ac.uk.
+Некоторые общие свойства предложенного разложения формулируются в терминах  формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''.
+Использование этого инструмента позволило сформулировать простой и явный алгоритм для вычисления правил ветвления, подходящий для произвольной (максимальной или не максимальной) подалгебры в аффинной алгебре Ли \cite{2010arXiv1007.0318L}.
 
-\end{abstract}
+Возможные обобщения полученных результатов обсуждаются в Разделе \ref{sec:conclusions}.
 
-%%
-%% Start line numbering here if you want
-%%
-% \linenumbers
+\section{Ортогональная подалгебра и сингулярные элементы}
 
-% Computer program descriptions should contain the following
-% PROGRAM SUMMARY.
+\label{sec:recurr-form-branch}
 
-{\bf PROGRAM SUMMARY}%/NEW VERSION PROGRAM SUMMARY}
-  %Delete as appropriate.
+В этом разделе мы покажем, как рекуррентный подход к проблеме ветвления естественным образом приводит к представлению формального характера $\frak{g}$-модуля в виде комбинации характеров, соответствующих параболическим (обобщенным) модулям Верма.
+Рассмотрим редуктивную алгебру Ли  $\frak{g}$ и ее редуктивную подалгебру $\frak{a}\subset \frak{g}$.
+Пусть  $L^{\mu} $ -- интегрируемый модуль старшего веса алгебры  $\frak{g}$, $\mu \in P^{+}$.  Будем считать  $L^{\mu}$ вполне приводимым по отношению к подалгебре $\frak{a}$,
+\begin{equation*}
+L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
+\end{equation*}
+Это разложение может быть записано в терминах формальных характеров с использованием оператора проекции  $\pi _{\frak{a}}$ (на весовое пространство $\frak{h_{a}}^{\ast }$):
+\begin{equation}
+\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
+}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
+\label{branching1}
+\end{equation}
+Для модуля  $L^{\mu }$ существует БГГ резольвента (см. \cite
+{bernstein1976category,bernstein1975differential,bernstein1971structure} и
+\cite{humphreys2008representations}). Все члены фильтрующей последовательности представляются суммами модулей Верма со старшими весами $\nu$, сильно связанными с $\mu$:
+\begin{equation*}
+\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
+W\right\} .
+\end{equation*}
 
-\begin{small}
-\noindent
-{\em Manuscript Title:}{\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of finite-dimensional and affine Lie algebras                                       \\
-{\em Authors:}Anton Nazarov                                                \\
-{\em Program Title:}Affine.m                                          \\
-{\em Journal Reference:}                                      \\
-  %Leave blank, supplied by Elsevier.
-{\em Catalogue identifier:}                                   \\
-  %Leave blank, supplied by Elsevier.
-{\em Licensing provisions:}none                                   \\
-  %enter "none" if CPC non-profit use license is sufficient.
-{\em Programming language:}Mathematica                                   \\
-{\em Computer:}i386-i686, x86\textunderscore 64                                               \\
-  %Computer(s) for which program has been designed.
-{\em Operating system:} Linux, Windows, MacOS, Solaris                                       \\
-  %Operating system(s) for which program has been designed.
-{\em RAM:} 5-500 Mb                                              \\
-  %RAM in bytes required to execute program with typical data.
-%{\em Number of processors used:}                              \\
-  %If more than one processor.
-%{\em Supplementary material:}                                 \\
-  % Fill in if necessary, otherwise leave out.
-{\em Keywords:} Mathematica; Lie algebra; affine Lie algebra; Kac-Moody algebra; root system; weights; irreducible modules, CFT, Integrable systems\\
-  % Please give some freely chosen keywords that we can use in a
-  % cumulative keyword index.
-{\em Classification:} 5 Computer Algebra, 4.2 Other algebras and groups                                         \\
-  %Classify using CPC Program Library Subject Index, see (
-  % http://cpc.cs.qub.ac.uk/subjectIndex/SUBJECT_index.html)
-  %e.g. 4.4 Feynman diagrams, 5 Computer Algebra.
-%{\em External routines/libraries:}                            \\
-  % Fill in if necessary, otherwise leave out.
-%{\em Subprograms used:}                                       \\
-  %Fill in if necessary, otherwise leave out.
-%{\em Catalogue identifier of previous version:}*              \\
-  %Only required for a New Version summary, otherwise leave out.
-%{\em Journal reference of previous version:}*                  \\
-  %Only required for a New Version summary, otherwise leave out.
-%{\em Does the new version supersede the previous version?:}*   \\
-  %Only required for a New Version summary, otherwise leave out.
-{\em Nature of problem:}\\
-  %Describe the nature of the problem here.
-Representation theory of finite-dimensional Lie algebras has many applications in different branches of physics, including elementary particle physics, molecular physics, nuclear physics.
-Representations of affine Lie algebras appear in string theories and two-dimensional conformal field theory used for the description of critical phenomena in two-dimensional systems.
-Also Lie symmetries play major role in study of quantum integrable systems.
-   \\
-{\em Solution method:}\\
-  %Describe the method solution here.
-We work with weights and roots of finite-dimensional and affine Lie algebras and use Weyl symmetry extensively.
-Central problems which are the computations of weight multiplicities, branching and fusion coefficients are solved using one general recurrent algorithm based on generalization of Weyl character formula.
-We also offer alternative implementation based on Freudenthal multiplicity formula which can be faster in some cases.
-   \\
-%{\em Reasons for the new version:}*\\
-  %Only required for a New Version summary, otherwise leave out.
-%   \\
-%{\em Summary of revisions:}*\\
-  %Only required for a New Version summary, otherwise leave out.
-%   \\
-{\em Restrictions:}\\
-  %Describe any restrictions on the complexity of the problem here.
-Computational complexity grows fast  with the rank of algebra, so computations for algebra of rank greater than 8 are non practical.
-   \\
-{\em Unusual features:}\\
-  %Describe any unusual features of the program/problem here.
-We offer the possibility to use traditional mathematical notation for objects in representation theory of Lie algebras in computations if {\bf Affine.m} is used in {\it Mathematica} notebook interface.
-   \\
-%{\em Additional comments:}\\
-  %Provide any additional comments here.
-%   \\
-{\em Running time:}\\
-  %Give an indication of the typical running time here.
-From seconds to days depending on rank of algebra and complexity of representations.
-   \\
+\subsection{Ортогональная подалгебра}
 
-% \begin{thebibliography}{0}
-% \bibitem{1}Reference 1         % This list should only contain those items referenced in the
-% \bibitem{2}Reference 2         % Program Summary section.
-% \bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
-%                                % This list is different from the bibliography at the end of
-%                                % the Long Write-Up.
-% \end{thebibliography}
-% * Items marked with an asterisk are only required for new versions
-% of programs previously published in the CPC Program Library.\\
-\end{small}
+Пусть  $\frak{h}_{\frak{a}}$ -- подалгебра Картана в  $\mathfrak{g}$. Для  $\mathfrak{a}\hookrightarrow \frak{g}$ введем ``ортогонального партнера''  $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$.
 
-%% main text
-\section{Introduction}
-\label{intro}
-
-Representation theory of Lie algebras is of central importance for different areas of physics and mathematics.
-In physics Lie algebras are used to describe symmetries of quantum and classical systems.
-Computational methods in representation theory have a long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
-
-Most popular programs \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{fischbacher2002ilp}, \cite{coxweyl} are created to study representation theory of simple finite-dimensional Lie algebras.
-The main computational problems are the following:
-\begin{enumerate}
-\item Construction of root system which determine the properties of Lie algebra including its commutation relations.
-\item Weyl group traversal which is important due to Weyl symmetry of root system and characters of representations.
-\item Calculation of weight multiplicities, branching and fusion coefficients, which are essential for construction and study of representations.
-\end{enumerate}
-There are well-known algorithms for these tasks \cite{moody1982fast}, \cite{stembridge2001computational}, \cite{belinfante1989survey}, \cite{casselman1994machine}.
-The third problem is most computation-intensive.
-There are two different recurrent algorithms which are based on the Weyl character formula and the Freudenthal multiplicity formula.
-In this paper we analyze them both.
-
-Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and in a study of  integrable systems.
-But infinite-dimensional algebras are much harder to investigate and the number of available computer programs is much smaller in this case.
-
-Affine Lie algebras \cite{kac1990idl} constitute important and tractable class of infinite-dimensional Lie algebras.
-They are constructed as central extensions of loop algebras of (semi-simple) finite-dimensional Lie algebras and appear naturally in a study of Wess-Zumino-Witten and coset models in conformal field theory \cite{Walton:1999xc}, \cite{difrancesco1997cft}, \cite{Goddard198588}, \cite{Dunbar:1992gh}.
-
-The structure of affine Lie algebras allows to adapt for them computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
-The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of affine Lie algebras and representations was published in 1990.
-But we are not aware of software packages for popular computer algebra systems which can be used to extend these results.
-We address this issue and present {\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.
-We describe the features and limitations of the package in the present paper.
-We also provide representation-theoretical background of implemented algorithms and present examples of computations relevant to physical applications.
-
-The paper starts with an overview of Lie algebras and their representation theory (Sec.
-\ref{sec:theor-backgr}).
-Then we describe datastructures of {\bf Affine.m} used to present different objects related to Lie algebras and representations (Sec.
-\ref{sec:core-datastructures}) and discuss implemented algorithms (Sec.
-\ref{sec:comp-algor}).
-Next section consists of physically interesting examples (Sec.
-\ref{sec:examples}).
-The paper is concluded with the discussion of possible extensions and refinements (Sec.
-\ref{sec:conclusion}).
-
-\section{Theoretical background}
-\label{sec:theor-backgr}
-
-In this section we remind necessary definitions and present formulae used in computations.
-
-\subsection{Lie algebras of finite and affine types}
-\label{sec:lie-algebras-finite}
-
-{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it Lie bracket}.
-If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
-\begin{equation}
-  \label{eq:1}
-  [X^{i},X^{j}]=\sum_{k} C^{ij}_{k} X^{k}
-\end{equation}
-Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to commutator.
-{\it Semisimple} Lie algebra is a direct sum of simple Lie algebras.
-In the present paper we treat simple and semisimple Lie algebras.
-
-{\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
-We denote the elements of basis of $\hfg$ by $H^{i}$.
-
-Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
-{\it Weights} are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
-
-Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
-This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).
-
-{\it Loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
-\begin{equation}
-  \label{eq:6}
-  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
-\end{equation}
-Central extension leads to the appearance of an additional term
-\begin{equation}
-  \label{eq:7}
-   [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
-\end{equation}
-This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
-
-We do not treat twisted affine Lie algebras in the present paper.
-
-\subsection{Modules, weights and roots}
-\label{sec:weights-roots}
-
-Let $\gf$ be a inite-dimensional or an affine Lie algebra.
-
-Then $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
-\begin{equation}
-  \label{eq:2}
-  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
-\end{equation}
-Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms of the  vector space $V$ with the commutator as a bracket.
-
-For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by a special choice of basis $\{v_{j}\}$ in $V$:
-\begin{equation}
-  \label{eq:3}
-  H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
-\end{equation}
-Eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
-Vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
-The  weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
-The weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of the weight subspace.
-
-The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
-\begin{equation}
-  \label{eq:5}
-  E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
-\end{equation}
-Module structure can be encoded by the formal character of a module
-\begin{equation}
-  \label{eq:10}
-  \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
-\end{equation}
-Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
-A character can be specialized by taking its value on some element $\xi$ of $\hf$.
-
-Lie algebra is its own module with respect to a special kind of representation. The action that
-defines this representation is called adjoint and is given by the bracket $ad_{X} Y=[X,Y]$. 
-{\it Roots} are weights of the adjoint representation of $\gf$.
-They encode the commutation relations of algebra in the following way.
-Denote by $\Delta$ the set of roots.
-For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and the generators $E^{\alpha}, E^{-\alpha}$ such that
-\begin{align}
-  \label{eq:4}
-  &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
-  &\left[E^{\alpha},E^{\beta}\right]=
-  \begin{cases}
-    N_{\alpha,\beta} E^{\alpha+\beta}, & \mbox{if}\; \alpha+\beta\in \Delta\\
-    \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
-    0,&\mbox{otherwise}
-  \end{cases}
-\end{align}
-
-Given the root system $\Delta$ we can choose the set of positive roots.
-This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
-Elements of $-\Delta^{+}$ are called negative roots.
-
-A positive root is {\it simple} if it cannot be written as a sum of positive roots.
-The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis in $\hfg^{*}$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive simultaneously.
-In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
-By numbering simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
-Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
-$\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}).
-{\it Comarcs} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
-
-Although for affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
-The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.
-The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- the highest root of the algebra $\go$.
-Note that root multiplicity $\mathrm{mult}(\alpha)$ for an affine Lie algebra root can be greater than one.
-
-Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called the Borel subalgebra.
-
-{\it Parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
-It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
-{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .
-
-The {\it Weyl group} $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
-\begin{equation}
-  \label{eq:8}
-  s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
-\end{equation}
-Root system and characters of representation are invariant with respect to the Weyl group  action. Root system can be reconstructed from the set of simple roots by the Weyl group transformations.
-
-Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
-
-Consider an action of the element $s_{\alpha}s_{\alpha+\delta}$ of the Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ being a simple root of the underlying finite-dimensional Lie algebra $\gf$.
-Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
-So the Weyl group can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to roots of $\gf$.
-
-A Weyl group element can be presented as a product of elementary reflections in multiple ways.
-Number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$.
-We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for the parity of the number of Weyl reflections generating $w$.
-
-Fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
-It is called a {\it main Weyl chamber}.
-
-The {\it Cartan matrix} $A$ is defined by products of simple roots
-\begin{equation}
-  \label{eq:9}
-  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}
-\end{equation}
-and can be used for a compact description of Lie algebra commutation relations in the Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
-
-Form \eqref{eq:9} induces a basis dual  to the simple
-roots basis. It is called the {\it fundamental weights basis}. We denote
-its elements by $\omega_i$:
-\begin{equation}
-  \label{eq:20}
-  \langle\omega_i,\alpha_j\rangle=\frac{2(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
-\end{equation}
-For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
-For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
-Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
-
- The sum of fundamental weights $\rho=\sum_{i} \omega_{i}$ is called a {\it Weyl vector}. It is an important tool in representation theory.
-
-\subsection{Highest weight modules}
-\label{sec:high-weight-modul}
-
-We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e.
-if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
-
-Highest weight module $V^{\mu}$ contains a single highest weight $\mu$, all the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
-
-The most simple type of highest weight modules is the Verma module
-$M^{\mu}$. Its space can be defined as a module
-\begin{equation}
-  \label{eq:17}
-  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}),
-\end{equation}
-with respect to a multiplication in $U(\gf)$ and
-$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
-Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
-Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D^{\lambda}(\bff_{+})$.
-
-Weight multiplicities in Verma modules can be found by applying the Weyl
-character formula
-\begin{equation}
-  \label{eq:11}
-  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
-\end{equation}
-Here we have used the Weyl denominator identity
-\begin{equation}
-  \label{eq:12}
-  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
-\end{equation}
-and $\epsilon \left( w\right) :=\det \left( w\right)$ is equal to 
-the parity of the sequence of Weyl reflections generating $w$.
-
-Verma module $M^{\mu}$ has the unique maximal submodule and the
-unique nontrivial simple quotient $L^{\mu}$ which is an
-{\it irreducible highest weight module}.
-
-Irreducible highest weight modules have no non-trivial submodules. 
-The Weyl character formula for
-irreducible highest weight modules is
-\begin{equation}
-  \label{eq:13}
-  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
-\end{equation}
-Thus the character of an irreducible highest weight module can be
-seen as a combination of characters of Verma modules. ( This
-fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
-(\cite{bernstein1976category,bernstein1971structure}, see also
-\cite{humphreys2008representations}).)
-
-Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
-%% !!! \Delta_{p}?!
+Рассмотрим корневое подпространство  $\frak{h}_{\perp \frak{a}}^{\ast }$, ортогональное к $\frak{a}$,
 \begin{equation*}
-M_{I}^{\mu}=U\left( \gf\right)\otimes _{U\left( \pf_{I}\right) }L_{\pf_{I}}^{\mu}.
+\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
+h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} ,
 \end{equation*}
-Introduce a formal element $R_{I}:=\prod_{\alpha \in \Delta
-^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
-^{\mathrm{mult}(\alpha )}$. Then the character of a generalized
-Verma module can be written as
-\begin{equation}
-  \label{eq:18}
-  \mathrm{ch}M_{I}^{\mu}=\frac{1}{R_{I}}\mathrm{ch}L_{\pf_{I}}^{\mu }.
-\end{equation}
-
-%% Define external border of irreducible representation here
-
-We can use the Weyl character formula to obtain recurrent relations for weight multiplicities -- important tools for calculations \cite{il2010folded,kulish4sfa}.
-
-For irreducible highest-weight modules recurrent relations have the following form
-\begin{equation}
-\label{eq:14}
-m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
--\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
-(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
-\end{equation}
-Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side.
-In case of Verma module it is just $\delta_{\xi,\mu}$.
-For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
-
-Other recurrent formula can be obtained from a study of Casimir
-elements action on irreducible highest weight modules
-\cite{humphreys1997introduction}:
-\begin{equation}
-  \label{eq:15}
-  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
-\end{equation}
-It is called the Freudenthal multiplicity formula.
-Note that it is applicable only to irreducible modules.
-
-We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.
-
-Now consider an algebra $\gf$ and a reductive subalgebra
-$\af\subset \gf$. Simple roots $\beta_{i}$ of the subalgebra $\af$
-can be presented as linear combinations of $\gf$-algebra roots
-$\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j}
-\alpha_{j},\ j=1,\dots,r_{\af}$.
-
-Each irreducible $\gf$-module is also an $\af$-module, although
-$L^{\mu}_{\gf}$ is in general not irreducible as $\af$-module. 
-It can be
-decomposed into a direct sum of irreducible $\af$-modules:
-\begin{equation}
-  \label{eq:16}
-  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
-\end{equation}
-Coefficients in such a decomposition are called branching
-coefficients.
-
-It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. 
-This traditional approach has serious limitations especially in case of affine Lie algebras. We discuss them in the end of section \ref{sec:comp-algor}.
-
-Now we describe an alternative approach which is based on recurrent properties of branching coefficients. 
-But before we proceed to these recurrent relations we need several additional definitions.
-
-For a subalgebra $\af\subset \gf$ we introduce the subalgebra
-$\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
-orthogonal to $\hf_{\af}$,
-\begin{equation*}
-\hf_{\perp \af}^{\ast }:=\left\{ \eta \in \hf^{\ast }|\forall
-h\in \hf_{\af};\eta \left( h\right) =0\right\} ,
-\end{equation*}
-and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
-to roots of $\af$,
+и корни  $\frak{g}$ (соответственно, положительные корни),  ортогональные к $\frak{a}$,
 \begin{eqnarray}
-\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
-h\in \hf_{\af};\beta \left( h\right) =0\right\} ,
+\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
+h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
 \label{delta a ort} \\
-\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
-}^{+}|\forall h\in \hf_{\af};\beta ^{+}\left( h\right) =0\right\} .
+\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
+}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
 \notag
 \end{eqnarray}
-Let $W_{\afb}$ be a subgroup of $W$ generated by
-reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
-}}^{+}$. The subsystem $\Delta _{\afb}$ determines a 
-subalgebra $\afb$ with the Cartan subalgebra $\hf_{\af%
-_{\perp }}$.
-
-The Cartan subalgebra $\frak{h}$ can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
-\frak{h}_{\afb}\oplus \frak{h}_{\perp }$
-
-We also introduce the notations
+Обозначим символом  $W_{\frak{a}_{\perp }}$ подгруппу  $W$, порожденную отражениями  $w_{\beta }$ с корнями  $\beta \in \Delta_{\frak{a}_{\perp}}^{+}$.
+Корневая подсистема  $\Delta _{\frak{a}_{\perp }}$ определяет подалгебру  $\frak{a}_{\perp }$, имеющую подалгебру Картана $\frak{h}_{\frak{a}_{\perp }}$.
+Пусть
+\begin{equation*}
+\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
+}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
+h\right) =0\right\};
+\end{equation*}
+выделим в  $\frak{g}$  подалгебры
 \begin{eqnarray}
-\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp },
 \qquad
@@
 \end{eqnarray}
+Заметим, что  $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ в общем случае не является подалгеброй в $\mathfrak{g}$.
 
-For $\af$ and $\afb$ we consider the
-corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\af_{\perp
-}} $ and compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
-D}_{\afb}$ of the injection:
+Для подалгебр Картана имеет место разложение
 \begin{equation}
-\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho , \qquad
-\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
-_{\perp }}\rho .  \label{defect-ort}
+\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
+\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
+\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
+\frak{h}_{\frak{a}}.
 \end{equation}
+Рассмотрим векторы Вейля  $\rho _{\frak{a}}$ и $\rho _{\frak{a}_{\perp}} $, соответствующие  $\frak{a}$ и $\frak{a}_{\perp }$.
+Введем так называемые ``дефекты'' вложения  $\mathcal{D}_{\frak{a}}$ и $\mathcal{D}_{\frak{a}_{\perp }}$:
+\begin{equation}
+\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho , \qquad
+\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
+_{\perp }}\rho .  \label{defect ort}
+\end{equation}
+Для  $\mu \in P^{+}$ рассмотрим связанные веса  $\left\{\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ и их проекции на $h_{\frak{a}_{\perp }}^{\ast }$, дополнительно сдвинутые на вектор дефекта $-\mathcal{D}_{\frak{a}_{\perp }}$:
+\begin{equation*}
+\mu _{\frak{a}_{\perp }}\left( w\right) :=\pi _{\frak{a}_{\perp }}\left[
+w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad w\in W.
+\end{equation*}
 
-%%!!! Define P^+
-For $\mu \in P^{+}$ consider the linked weights $\left\{ \left(
-w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections
-to
-$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
-\mathcal{D}_{\afb}$:
-\begin{equation*}
-\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
-w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
-\end{equation*}
-Among the weights $\left\{ \mu _{\af_{\perp
-}}\left( w\right) |w\in W\right\} $ one can always choose those located in
-the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
-set of representatives $u$ for the classes $W/W_{\afb}$ such
-that
-
+Среди весов  $\left\{ \mu _{\frak{a}_{\perp
+}}\left( w\right) |w\in W\right\} $ всегда можно выбрать те, которые попадают в фундаментальную камеру $\overline{C_{\frak{a}_{\perp }}}$.
+Пусть $U$ -- множество представителей $u$ классов  $W/W_{\frak{a}_{\perp }}$, таких что
 \begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
-\overline{C_{\afb}}\right\} \quad .  \label{U-def}
+U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
+\overline{C_{\frak{a}_{\perp }}}\right\} \quad .  \label{U-def}
 \end{equation}
-Thus we can form the subsets:
+Тогда можно выделить подмножества:
 \begin{equation}
 \mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
-\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
+\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}%
 _{\perp }},\quad u\in U,  \label{mu-a}
 \end{equation}
-and
+и
 \begin{equation}
-\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
+\mu _{\frak{a}_{\perp }}\left( u\right) :=\pi _{\frak{a}_{\perp }}\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U.
 \label{mu-a-tilda}
@@
 
-Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
-since it is built on a subset of roots of the algebra $\mathfrak{g}$.
+Заметим, что подалгебра  $\mathfrak{a}_{\bot}$ по определению регулярна, так как она построена на подмножестве корней алгебры $\mathfrak{g}$.
 
-Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients.
-If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.
+Для интересующих нас модулей формула Вейля-Каца для  $\mathrm{ch}\left( L^{\mu }\right) $ может быть записана через сингулярные элементы \cite{humphreys1997introduction},
+\begin{equation*}
+\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
+)-\rho },
+\end{equation*}
+а именно:
+\begin{equation}
+\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
+^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
+\label{Weyl-Kac2}
+\end{equation}
+То же верно и для подмодулей $\mathrm{ch}\left( L_{\frak{a}}^{\nu
+}\right) $ в формуле (\ref{branching1})
+\begin{equation*}
+\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
+\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
+}^{\left( \nu \right) }}{R_{\frak{a}}},
+\end{equation*}
+где
+\begin{equation*}
+\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
+}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
+\end{equation*}
+Применяя формулу  (\ref{Weyl-Kac2}) к правилу ветвления  (\ref{branching1}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu
+\right) }$ и $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
+\begin{eqnarray}
+\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
+)-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
+(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
+\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
+\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
+mult}_{\frak{a}}(\beta )}},  \notag  \label{eq:4} \\
+\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
+&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
+}^{\left( \nu \right) }}{R_{\frak{a}}}.
+\end{eqnarray}
 
-Now we can use the Weyl character formula to write a
-recurrent relation \cite{2010arXiv1007.0318L} for signed branching
-coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
-injection $\af\hookrightarrow \gf$:
+\subsection{Разложение сингулярного элемента.}
+
+\label{subsec:decomp-sing-element}
+
+Теперь мы выполним разложение сингулярного элемента  $\Psi ^{\left(\mu \right) }$ на сингулярные элементы модулей ортогонального партнера:
+
+\begin{lemma}
+
+Пусть  $\frak{a}_{\bot }$ -- ортогональный партнер редуктивной подалгебры  $\frak{a}\hookrightarrow \frak{g}$ и $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$, $\widetilde{%
+\frak{a}_{\perp }}=\frak{a}_{\perp }\oplus \frak{h}_{\perp }$, $%
+\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$.
+
+Пусть $L^{\mu }$ -- интегрируемый модуль старшего веса  $\mu \in P^{+}$ и
+
+$\Psi ^{\left( \mu \right) }$\ -- сингулярный элемент $L^{\mu }$.
+
+Тогда элемент  $\Psi ^{\left( \mu \right) }$ может быть разложен в сумму по  $u\in U$ (см.
+(\ref{U-def})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
+$\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
+\begin{equation}
+\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\widetilde{%
+\mathfrak{a}}}\left( u\right) }\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) }.  \label{sing decomp main}
+\end{equation}
+\label{Psi-decomp-lemma}
+\end{lemma}
+
+\begin{proof}
+Пусть
+\[
+u(\mu +\rho )=\pi _{\left( \aft\right) }u(\mu +\rho )+\pi _{\left(
+\frak{a}_{\perp }\right) }u(\mu +\rho ),
+\]
+где $u\in U$. Для произвольного  $v\in W_{\frak{a}_{\bot }}$ рассмотрим сингулярный вес  $vu(\mu +\rho )-\rho $ и выполним разложение:
+\begin{equation}
+\begin{array}{lcl}
+vu(\mu +\rho )-\rho  & = & \pi _{\left( \frak{a}\right) }\left( u(\mu +\rho
+)\right) -\rho +\rho _{\frak{a}_{\perp }}
+\\
+&  & +\ v\left( \pi _{\left( \aft_{\perp }\right) }u(\mu
++\rho )-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{%
+\frak{a}_{\perp }} .
+\end{array}
+\label{sing-decomp-1}
+\end{equation}
+Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}), чтобы упростить первую строку в формуле (\ref{sing-decomp-1}):
+\[
+\begin{array}{r}
+\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
+\frak{a}_{\perp }}= \\
+\pi _{\left( \aft\right) }\left( u(\mu +\rho )\right) -\pi _{\aft%
+}\rho -\pi _{\af_{\bot }}\rho +\rho _{\frak{a}_{\bot }}= \\
+=\pi _{\left( \aft\right) }\left( u(\mu +\rho )-\rho \right) +\mathcal{D}%
+_{\frak{a}_{\bot }},
+\end{array}
+\]
+и вторую строку
+\[
+\begin{array}{c}
+v\left( \pi _{\left( \frak{a}_{\perp }\right) }u(\mu +\rho
+)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}%
+_{\perp }}= \\
+v\left( \pi _{\left( \frak{a}_{\bot }\right) }u(\mu +\rho )-%
+\mathcal{D}_{\frak{a}_{\bot }}-\pi _{\left( \frak{a}_{\bot }\right) }\rho
++\rho _{\frak{a}_{\bot }}\right)
+-\rho _{\frak{a}_{\bot }}= \\
+=v\left( \pi _{\left( \frak{a}_{\bot }\right) }\left[ u(\mu
++\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\bot }}+\rho _{\frak{a}_{\bot
+}}\right) -\rho _{\frak{a}_{\bot }}.
+\end{array}
+\]
+В результате получаем требуемое разложение сингулярного элемента $\Psi ^{\mu }$ на сингулярные элементы $\Psi_{\frak{a}_{\perp}}^{\eta}$ модулей $L_{\frak{a}_{\perp }}^{\eta }$ подалгебры $\frak{a}_{\perp }$:
+\begin{equation}
+\begin{array}{l}
+\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
+(v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
+=\sum_{u\in U}\epsilon (u)e^{\pi _{\aft}\left[ u(\mu +\rho )-\rho \right]
++\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
+(v)e^{v\left( \pi _{\left( \frak{a}_{\perp }\right) }\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}+\rho _{\frak{a}%
+_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
+=\sum_{u\in U}\;\epsilon (u)\Psi _{\af_{\perp }}^{\pi
+_{\left( \frak{a}_{\perp }\right) }\left[ u(\mu +\rho )-\rho
+\right] -\mathcal{D}_{\frak{a}_{\perp }}}e^{\pi _{\left( \aft\right) }%
+\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}.
+\end{array}
+\label{singular main}
+\end{equation}
+\end{proof}
+
+%\bigskip
+
+\begin{remark}
+Это соотношение можно рассматривать как обобщение формулы Вейля для сингулярного элемента $\Psi _{\frak{g}}^{\mu }$: векторы $\mu _{%
+\widetilde{\mathfrak{a}}}\left( u\right) $ играют роль сингулярных весов, в то время как множители  $\epsilon (u)$ расширены до $\epsilon
+(u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$.
+
+Действительно, при  $\frak{a=g}$ подалгебры  $\frak{a}_{\perp }$, и $\frak{h}_{\perp }$ тривиальны, $U=W$ и оригинальная формула Вейля восстанавливается, так как сингулярные элементы $\epsilon (u)\Psi _{\frak{a}_{\perp %
+}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\epsilon (u)$ становятся  тривиальными.
+
+В противоположном пределе, когда $\frak{a}=0$, $\Delta _{\frak{a}_{\perp }}=\Delta _{\frak{g}}$, $%
+\frak{h}_{\perp }^{\ast }=0$, $\frak{a}_{\perp }=\frak{g}$, $\mathcal{D}_{%
+\frak{a}_{\perp }}=0$ и $U=W/W_{\frak{a}_{\perp }}=e$, вновь приходим к выражению для  сингулярного элемента
+ $\Psi ^{\mu }$, теперь -- в результате тривиализации множества векторов $\mu _{\af}\left( e\right) =0$.
+\end{remark}
+
+\begin{remark}
+
+В работе \cite{2010arXiv1007.0318L} разложение, аналогичное формуле (\ref{singular main}), было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
 \begin{equation}
@@
 k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
+\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
 _{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
-\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right.  \\
-\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
+\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right.  \\
+\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
 }}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
@@
 \end{array}
-\label{recurrent-rel}
+\label{recurrent rel}
 \end{equation}
-The recursion is governed by the set $\Gamma _{\af\rightarrow \gf}$ called the injection fan. The latter is defined by the
-carrier set $\left\{ \xi \right\} _{\af\rightarrow \gf}$ for the
-coefficient function $s(\xi )$
+Рекурсия задается множеством  $\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}$, которое носит название веера вложения.
+Это множество определяется как носитель  $\left\{ \xi \right\}_{\frak{a}\rightarrow \frak{g}}$  коэффициентной функции $s(\xi )$
 \begin{equation*}
-\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}:=\left\{
-\xi \in P_{\widetilde{\af}}|s(\xi )\neq 0\right\}
+\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{g}}:=\left\{
+\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\},
 \end{equation*}
-appearing in the expansion
+возникающей в разложении 
 \begin{equation}
 \prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
-_{\widetilde{\af}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
-_{\af}(\pi _{\widetilde{\af}}\alpha )}=-\sum_{\gamma \in P_{%
-\widetilde{\af}}}s(\gamma )e^{-\gamma };\quad
+_{\widetilde{\frak{a}}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
+_{\frak{a}}(\pi _{\widetilde{\frak{a}}}\alpha )}=-\sum_{\gamma \in P_{%
+\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma }.\quad
 \end{equation}
-The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
-\right\} $ -- and the zero element is to be eliminated:
+Веса из множества $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
+g}}$ сдвигаются на $\gamma _{0}$ -- младший вектор в $\left\{ \xi
+\right\} $, и исключается нулевой элемент:
 \begin{equation}
-\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma
+\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}=\left\{ \xi -\gamma
 _{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
 \end{equation}
-Formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
 
-If the root system of $\afb$ is generated by some subset of $\gf$
-simple roots $\alpha_{1},\dots,\alpha_{r}$ then the recurrent
-relation (\ref{recurrent-rel}) is connected with the generalized
-Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules
-\cite{2011arXiv1102.1702L}.
+Рекуррентное соотношение (\ref{recurrent rel}) первоначально использовалось для описания ветвления интегрируемых модулей.
+Заметим, что существует важный класс модулей, которые также могут быть редуцированы при помощи веера вложения -- это модули Верма.
+\end{remark}
 
-Another particular case of this formula is connected with tensor
-product decompositions. Consider the tensor product of two
-irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$. It is also a
-$\gf$-module but not irreducible in general. So
+\subsection{Фомулы Вейля-Верма.}
+
+\begin{statement}
+%\bigskip
+Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характер интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) характеров параболических модулей Верма, распределенных по множеству весов $\mu _{\widetilde{\mathfrak{a}}}\left(
+u\right)$:
 \begin{equation}
-  \label{eq:19}
-  L^{\mu}\otimes L^{\nu}=\bigoplus_{\gamma} f^{\mu\nu}_{\gamma}L^{\gamma}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{%
+\widetilde{\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) },  \label{gen Weyl-Verma}
 \end{equation}
-The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion
-coefficients. The problem of computation of fusion coefficients is
-equivalent to branching problem for the diagonal subalgebra
-$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
+где  $U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
+\overline{C_{\frak{a}_{\perp }}}\right\} $ и $I$ -- такое подмножество в  $S$, что $\Delta _{I}^{+}$ эквивалентно $\Delta _{\frak{a}_{\perp }}^{+}$.
+\end{statement}
 
-In the case of affine Lie algebras $\gf, \af$  the multiplicities
-$m_{\nu}$ and the corresponding branching coefficients $b_{\nu}$
-can be regarded as the coefficients in power series decomposition
-of string and branching functions correspondingly:
-\begin{align}
-  \label{eq:21}
-  &\sigma_{\nu}(q)=\sum_{n=0}^{\infty} m_{\nu-n\delta} q^n, \quad \nu=\sum_j c_j \omega_j,\quad c_j\geq 0\\
-  & b_{\nu}(q)=\sum_{n=0}^{\infty} b_{\nu-n\delta} q^n,\quad  \nu=\sum_j c_j \omega_j, \quad c_j\geq 0
-\end{align}
-String and branching functions have  modular and analytic properties which are important for conformal field theory, especially in  coset models and the study of CFT on higher genus surfaces \cite{kac1988modular}, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}.
+%\bigskip
+\begin{proof}
+Подалгебра  $\mathfrak{a}_{\bot }$ регулярна и редуктивна по определению  (\ref{delta a ort}). Рассмотрим её знаменатель Вейля   $R_{\frak{a}_{\perp }}:=\prod_{\alpha \in \Delta _{\frak{a}%
+_{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}%
+\mathrm{\left( \alpha \right) }}$ и элемент  $R_{J}:=\prod_{\alpha \in
+\Delta ^{+}\setminus \Delta _{\frak{a}_{\perp }}^{+}}\left( 1-e^{-\alpha
+}\right) ^{\mathrm{mult}(\alpha )}$ как сомножители в $R$:
+\begin{equation*}
+R=R_{J}R_{\frak{a}_{\perp }}.
+\end{equation*}
+Согласно этой факторизации и разложению  (\ref{sing decomp main}) характер $\mathrm{ch}\left( L^{\mu }\right) $ можно переписать в виде
+\begin{eqnarray*}
+\mathrm{ch}\left( L^{\mu }\right) &=&\left( R_{J}\right) ^{-1}\left( R_{%
+\frak{a}_{\perp }}\right) ^{-1}\Psi ^{\mu }=\left( R_{J}\right)
+^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}}\left( u\right) }\epsilon
+(u)\left( R_{\frak{a}_{\perp }}\right) ^{-1}\Psi _{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) } \\
+&=&\left( R_{J}\right) ^{-1}\sum_{u\in U}\;e^{\mu _{\widetilde{\frak{a}}%
+}\left( u\right) }\epsilon (u)\mathrm{ch}\left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
+}}\left( u\right) }\right),
+\end{eqnarray*}
+где  $\left\{ L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left(
+u\right) }|u\in U\right\} $ -- множество конечномерных $\frak{a}%
+_{\perp }$-модулей со старшими весами   $\mu _{\frak{a}_{\perp }}\left(
+u\right) $.
+Нас интересуют нетривиальные подалгебры $\frak{a}$ и, соответственно, нетривиальные  $\frak{a}_{\perp }$ (случай тривиальной ортогональной подалгебры рассматривался выше в (см.
+Замечание 1)).
+Значит $r_{\frak{a}}\geq 1$ и $r_{\frak{a}%
+_{\perp }}<r$.
+Так как диаграмма Дынкина для любой регулярной подалгебры получается в результате исключения одной, двух или более вершин из расширенной диаграммы Дынкина алгебры, а расширенная диаграмма содержит не более одного зависимого корня (старший корень), множество корней $\Delta _{\frak{a}_{\perp }}^{+}$ всегда эквивалентно некоторому множеству $\Delta _{I}^{+}$, порожденному набором  простых корней $I\subset S $.
 
-{\bf Affine.m}  calculates weight multiplicities and branching coefficients for affine Lie algebras up to some finite grade.
-We present examples of computations in Sections \ref{sec:string-funct-affine}, \ref{sec:branch-funct-coset}.
-Now we proceed to the description of datastructures and algorithms implemented in {\bf Affine.m}.
+Следовательно мы можем (переопределяя множество  $\Delta ^{+}$) отождествить $\Delta _{\frak{a}_{\perp }}^{+}$ с подмножеством  $\Delta _{I}^{+}$, где $I\subset S$.
+В результате мы можем определить объекты, необходимые для построения обобщенных модулей Верма \cite{lepowsky1977generalization,humphreys2008representations}.
+У нас есть два множества корневых векторов $\left\{ x_{\xi }\in \frak{g}_{\xi }|\xi \in \Delta _{I}^{+}\right\}
+$ и $\left\{ x_{\eta }\in \frak{g}_{\eta }|\eta \in \Delta ^{+}\setminus
+\Delta _{I}^{+}\right\} $, и соответствующие нильпотентные подалгебры в  $\frak{n}%
+^{+}$:
+\begin{equation*}
+\frak{n}_{I}^{+}:=\sum_{\xi \in \Delta _{I}^{+}}\frak{g}_{\xi },\quad
+\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta ^{+}\setminus \Delta _{I}^{+}}\frak{g}%
+_{\eta }.
+\end{equation*}
+Первая подалгебра вместе со своей отрицательной копией  $\frak{n}%
+_{I}^{-} $ порождает простую подалгебру 
+\begin{equation*}
+\frak{s}_{I}=\frak{n}_{I}^{-}+\frak{h}_{I}+\frak{n}_{I}^{+}.
+\end{equation*}
+Мы расширяем ее оставшимися картановскими генераторами:
+\begin{equation*}
+\frak{l}_{I}=\frak{n}_{I}^{-}+\frak{h}+\frak{n}_{I}^{+}.
+\end{equation*}
+Полупрямое произведение  $\frak{l}_{I}$ и $\frak{u}_{I}^{+}$ дает параболическую подалгебру $\frak{p}_{I}\hookrightarrow \frak{g}$ :
+\begin{equation}
+\frak{p}_{I}=\frak{l}_{I}\vartriangleright \frak{u}_{I}^{+}.
+\label{paralolic subalg}
+\end{equation}
+Ее универсальная обертывающая $U\left( \frak{p}_{I}\right) $ является подалгеброй в  $%
+U\left( \frak{g}\right) $. Модули  $L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) }$ алгебры  $\frak{l}_{I}$ легко поднимаются до  $\frak{p}_{I}$-модулей при помощи тривиального действия нильрадикала $\frak{u}_{I}^{+}$.
+Последний стандартным образом индуцирует $U\left( \frak{g}\right) $-модули:
+\begin{equation*}
+M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=U\left( \frak{g}\right)
+\otimes _{U\left( \frak{p}_{I}\right) }L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) }.
+\end{equation*}
 
-\section{Core datastructures}
-\label{sec:core-datastructures} Having introduced necessary
-mathematical objects, problems and relations we now describe the
-related datastructures of {\bf Affine.m}. Although {\it
-Mathematica} is untyped language it is possible to create
-structured objects and do type checks with patterns
-\cite{shifrinmathematica}, \cite{maeder2000computer}.
-\subsection{Weights}
-\label{sec:weights}
-
-Weights are represented  by two data-structures: \lstinline{finiteWeight} for finite-dimensional Lie algebras and \lstinline{affineWeight}  for affine.
-
-Internally the finite weight is a \lstinline{List} with the
-\lstinline{Head} \lstinline{finiteWeight}, its components are the
-coordinates of the weight in the orthogonal Bourbaki  basis
-\cite{bourbaki2002lie}.
-
-Affine weight is an extension of a finite weight by supplying it
-with level and grade coordinates. There is a set of functions
-defined for finite and affine weights. The complete list can be
-found in  online help of the package. The most important
-are definitions of addition, multiplication by a number and a
-scalar product (bilinear form) for weights. These definitions
-allow to use traditional notation when working with {\bf
-Affine.m}:
-\begin{lstlisting}
-  w=makeFiniteWeight[{1,0,3}];
-  v=makeFiniteWeight[{3,2,1}];
-  2*w+v==makeFiniteWeight[{5,2,7}]
-  w.v==6
-\end{lstlisting}
-
-The use of orthogonal basis in the internal structure of weights allows us to work with weights without complete specification of root system which is useful for study of branching, since roots of the subalgebra can be specified by hand.
-
-\subsection{Root systems}
-\label{sec:root-systems}
-
-To specify an algebra of finite or affine type it is enough to fix
-its root system. Root systems are represented by two datatypes
-\lstinline{finiteRootSystem} and \lstinline{affineRootSystem}. The
-latter is an extension of the former. We offer several different
-constructors for these datastructures. It is possible to specify
-the set of simple roots explicitly, for example to study the
-subalgebra $B_2\subset B_4$ we can use the definition
-\begin{lstlisting}
-  b2b4=makeFiniteRootSystem[ { {1,-1,0,0}, {0,1,0,0} } ]
-\end{lstlisting}
-There are constructors for root systems of simple finite-dimensional Lie algebras:
-\begin{lstlisting}
-  b2=makeSimpleRootSystem[B,2]
-\end{lstlisting}
-We use typographic features of {\it Mathematica} frontend to offer mathematical notation for simple Lie algebras:
-
-\begin{lstlisting}[mathescape=true]
-  $B_2$ == makeFiniteRootSystem[ { {1, -1}, {0, 1} }]
-\end{lstlisting}
-
-Non-twisted affine root systems can be created as affine extensions of finte root systems, e.g.
-\begin{lstlisting}
-  b2affine = makeAffineExtension[b2]
-\end{lstlisting}
-In notebook interface this can be written simply as $\hat{B}_2$.
-
-Semisimple Lie algebras can be created as sums of simple:
-\begin{lstlisting}[mathescape=true]
-  $A_1\oplus A_1$ == finiteRootSystem[2, 2, {finiteWeight[2, {1, 0}], finiteWeight[2, {0, 1}]}]
-\end{lstlisting}
-%% The problem is here
-
-Predicate \lstinline{rootSystemQ} checks if the object is root systems of finite or affine type.
-
-List of simple roots is the property of root system so it is accessed as \lstinline{rs[simpleRoots]}.
-
-We have implemented several functions to get major properties of root systems. Weyl vector is given by the function \lstinline{rho[rs_?rootSystemQ]}:
-\begin{lstlisting}[label=list:1]
-  In[1]  =  rho[b2]
-  Out[1]  =  finiteWeight[2, {3/2, 1/2}]
-\end{lstlisting}
-Positive roots can be constructed with \lstinline{positiveRoots[rs_?rootSystemQ]}.
-For an affine Lie algebra this and related functions return the list up to fixed grade.
-This grade limit is set through the value of \lstinline{rs[gradeLimit]} which is equal to 10 by default.
-List of roots (up to \lstinline{gradeLimit}) is returned by \lstinline{roots[rs]}.
-Cartan matrix and fundamental weights are calculated by the functions \lstinline{cartanMatrix} and \lstinline{fundamentalWeights} correspondingly.
-
-It is possible to specify a weight of a Lie algebra by its Dynkin labels
-\begin{lstlisting}
-  weight[b2][1,2] == makeFiniteWeight[{2, 1}]
-\end{lstlisting}
-The function \lstinline{dynkinLabels[rs_?rootSystemQ][wg_?weightQ]} returns Dynkin labels of weight \lstinline{wg} in the root system \lstinline{rs}.
-
-Elements of Weyl group are specified by the set of indices of reflections, so the element  $w=s_{1}s_{2}s_{1}$ of the Weyl group of algebra $B_{2}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
-Then it can be applied to the weights:
-\begin{lstlisting}
-  w = weylGroupElement[b2][1,2,1];
-  w @ makeFiniteWeight[{1,0}] == makeFiniteWeight[{-1,0}]
-\end{lstlisting}
-
-Computation of lexicographically minimal form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching in {\it Mathematica}.
-In \cite{KallenShortlex} rewrite rules for simple finite dimensional and affine Lie algebras are presented as {\it Mathematica} patterns.
-Our presentation of Weyl group elements is compatible with the code of \cite{KallenShortlex}
-\begin{lstlisting}[mathescape=true]
-  In[1]  = $<<$A3reduce;
-           reduce[s[1,2,1,2,1,3,2,1,1]]
-  Out[1] = s[2, 3, 2]
-
-  In[2]  = (weylGroupElement[$A_{3}$] @@ reduce[s[1,2,1,2,1,3,2,1,1]]) @ weight[$A_{3}$][-1,-2,-1]
-  Out[2] = finiteWeight[4, {-2, 2, 1, -1}]
-
-  In[3]  = dynkinLabels[$A_{3}$][Out[2]]
-  Out[3] = {-4, 1, 2}
-\end{lstlisting}
-
-\subsection{Formal elements}
-\label{sec:formal-elements}
-
-We represent formal characters of representations by special structure \lstinline{formalElement}.
-This structure is a hash-table implemented with \lstinline{DownValues}.
-The keys are weights at the exponents and the values are the  corresponding multiplicities.
-\lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]!
-creates data-structure which represents the element $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ of the formal algebra $\mathcal{E}$.
-The operations in $\mathcal{E}$ are implemented for \lstinline{formalElement} data-type: formal elements can be added, multiplied by a number or by an exponent of a weight.
-There exists also a multiplication of formal elements but no division.
-\begin{lstlisting}[mathescape=true]
-  In[1]  = makeFormalElement[{makeFiniteWeight[{1,1}],makeFiniteWeight[{0,0}]},{1,2}] *
-             (2 * Exp[makeFiniteWeight[{1,0}]] *
-             makeFormalElement[{makeFiniteWeight[{1,1}],makeFiniteWeight[{0,0}]},{1,2}]);
-  In[2]  = In[1][weights]
-  Out[2] = {finiteWeight[2, {1, 0}], finiteWeight[2, {2, 1}], finiteWeight[2, {3, 2}]}
-
-  In[3]  = In[1][multiplicities]
-  Out[3] = {8, 8, 2}
-\end{lstlisting}
-
-\subsection{Modules}
-\label{sec:modules}
-
-{\bf Affine.m} can be used to study different kinds of modules, i.e.
-Verma modules, irreducible modules and parabolic Verma modules.
-We need datastructure \lstinline{module} to represent generic module of Lie algebra $\gf$.
-Module properties can be deduced from its set of singular weights using Weyl character formulae \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}.
-Set of singular weights can have Weyl symmetry.
-It can be a symmetry with respect to the Weyl group $W_{\gf}$ or with respect to some subalgebra $W_{\af}$ as in the case of parabolic Verma modules.
-Then it is possible to study only the main Weyl chamber $C_{\af}$.
-To use this symmetry generic constructor for \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],limit:10}.
-Here \lstinline{rs} is the root system of the Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is the root system corresponding to the Weyl group $W_{\af}$ which is the (anti-)symmetry of the set of singular weights.
-Parameter \lstinline{limit} limits computation for infinite-dimensional modules such as Verma or parabolic Verma.
-There are several specialized constructors for different types of highest weight modules:
-\begin{lstlisting}[mathescape=true]
-vm=makeVermaModule[$B_{2}$][{2,1}];
-pm=makeParabolicVermaModule[$B_{2}$][weight[$B_{2}$][2,1],{1}];
-im=makeIrreducibleModule[$B_{2}$][2,1];
-GraphicsRow[textPlot/@{im,vm,pm}]
-$\includegraphics[width=130mm]{figures/irrep-verma-pverma.pdf}$
-\end{lstlisting}
-
-As we already stated properties of a module are encoded by its singular element.
-Function \lstinline{singularElement[m_module]} returns singular element of a module as \lstinline{formalElement} datastructure.
-Character (up to \lstinline{limit} for (parabolic) Verma modules) is returned by the function \lstinline{character[m_module]}.
-Direct sum of modules is a module and we use natural notation
-\begin{lstlisting}[mathescape=true]
-im1=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
-im2=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][1,2]];
-textPlot[im1$\oplus$ im2]
-$\includegraphics[width=60mm]{figures/irrep-sum.pdf}$
-\end{lstlisting}
-
-The tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
-\begin{lstlisting}[mathescape=true]
-textPlot[makeIrreducibleModule[$A_{1}$][5]$\otimes$ makeIrreducibleModule[$A_{1}$][3]];
-$\includegraphics[width=60mm]{figures/tensor-product.pdf}$
-\end{lstlisting}
-\section{Computational algorithms}
-\label{sec:comp-algor}
-
-As we have already stated in section \ref{sec:high-weight-modul} there exist two recurrent relations which can be used to calculate weight multiplicities in irreducible modules.
-Both algorithms proceed in the following way to calculate weight multiplicities:
-\begin{enumerate}
-\item Create the list of weights in the main Weyl chamber by subtracting all possible combinations of simple roots from the highest weight (e.g.
-for finite-dimensional algebra subtract $\alpha_{1}$ from $\mu$ while inside $\bar C$, then subtract $\alpha_{2}$ from all the weights already obtained etc).
-\item Sort the list of weights by their product with the Weyl vector.
-\item Use a recurrent formula. If the weight required for recurrent computation is outside the main chamber use the Weyl symmetry.
-\end{enumerate}
-The difference in the performance of algorithms is in the number of previous values required to get the multiplicity of weight under consideration.
-For  the Weyl formula based recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in the Weyl group (if we are far from the boundary of representation diagram).
-When the Freudenthal formula \eqref{eq:15} is used number of previous values grows with the distance from the external border of representation.
-So the Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
-Note that the Freudenthal formula is valid for irreducible modules only, so it can not be used to study (generalized) Verma modules.
-
-We have made some experiments with our implementations of the Freudenthal formula and formula \eqref{eq:15} and have got Figure  \ref{fig:freudenthal-racah-times}, which depicts the dependence of the computation time on the number of weights in a module.
-
-\begin{figure}[h]
-  \noindent\centering{
-    \includegraphics[width=80mm]{figures/timing.pdf}
-  }
-  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{eq:14} (solid) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
-\label{fig:freudenthal-racah-times}
-
-\end{figure}
-
-In the calculation of branching coefficients the application of the Freudenthal formula requires a complete construction of formal characters of an algebra module and all the representations of a subalgebra.
-It is impractical when the rank of algebra and subalgebra are big, for example for maximal subalgebras.
-
-Alternative algorithm which was presented in the paper \cite{2010arXiv1007.0318L}  contains the following steps:
-
-\begin{enumerate}
-\item  Construct the root system $\Delta _{\af}$ for the embedding $%
-\af\rightarrow \frak{g}$.
-
-\item  Select all the positive roots $\alpha \in \Delta ^{+}$ orthogonal
-to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
-
-\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. Relation
- (\ref{eq:6}) defines the sign function
- $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
- $\gamma_0$ is to be subtracted to get the fan:
- $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}$.
-
-\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
-)-\rho ;\;w \in W\right\} $ of singular weights for the $\frak{g}$%
--module $L^{(\mu )}$.
-
-\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
-}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
-)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
-\af_{\perp }}}}\right\} $. Since the set $\Delta_{\afb }^{+}$ is fixed
-we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
-}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
-\af_{\perp }}}}$ (by computing its scalar product with the fundamental
-weights of $\afb^{+}$).
-
-\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
-calculate dimensions of the corresponding modules, $\mathrm{\dim }\left(
-L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
-}\left( u\right) }\right) $, using the Weyl dimension formula and construct
-the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
-
-\item  Calculate the anomalous branching coefficients using 
-recurrent relation (\ref{recurrent-rel}) and select among them those
-corresponding to the weights in the main Weyl
-chamber $\overline{C_{\af}}$.
-\end{enumerate}
-
-We can speed up the algorithm by
-one-time computation of the representatives of the conjugate classes $%
-W/W_{\afb }$.
-
-Consider the regular embedding $B_{2}\subset B_{4}$.
-In this case the fan consists of 24 elements.
-In order to decompose $B_{4}$ module we need to construct the subset of singular weights of the module which projects to the main Weyl chamber of the subalgebra $B_{2}$.
-The full set of singular weights consists of 384 elements.
-The required subset contains at most 48 elements.
-So the time for the construction of this required subset is negligible if the number of branching coefficients is greater than that.
-We may estimate the total number of required operations for the computation of branching coefficients as the product of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients and the number of elements in the fan.
-In the case of a direct algorithm we need to compute the multiplicities for each module in the decomposition, so the number of operations grows faster than the square of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients.
-
-To further illustrate this performance issue we include Figure \ref{fig:branching} where we show the time required for computations of branching coefficients for $B_{3}\subset B_{4}$.
-
-\begin{figure}[h]
-  \noindent\centering{
-   \includegraphics[width=100mm]{figures/branching-timing.pdf}
-  }
-  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{recurrent-rel} (solid) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
-  \label{fig:branching}
-\end{figure}
-
-\section{Examples}
-\label{sec:examples}
-In this section we present some examples of computations available with {\bf Affine.m} with the code required to produce these results.
-
-\subsection{Tensor product decompositon for finite-dimensional Lie algebras}
-\label{sec:tens-prod-decomp}
-
-Computation of fusion coefficients for the decomposition of tensor product of highest-weight modules to the direct sum of irreducible modules has numerous applications in physics.
-For example, we can consider the spin of a composite system such as an atom.
-Another interesting example is integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of a Lie algebra $\gf$ with a $\gf$-invariant Hamiltonian $H$, describing the nearest-neighbour spin-spin interaction.
-In order to solve such a system, i.e.
-to find eigenstates of the Hamiltonian, we need to decompose $L^{\otimes N}$ into the direct sum of irreducible $\gf$-modules of lower dimension and diagonalize the Hamiltonian on these modules.
-
-For fundamental representations of simple Lie algebras it is sometimes possible to get an analytic result describing the dependence of decomposition coefficients on $N$ (See \cite{LyakhovskyPostnova2011}).
-Our code provides numerical values and can be used to check this analytic results.
-
-Consider a tensor power of $B_{2}$ the first fundamental representation $\left(L^{[1,0]}\right)^{\otimes 4}$. Decomposition coefficients are just the branching
- coefficients for the tensor power module reduced to the diagonal subalgebra $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$. So the following code calculates these coefficients:
-\begin{lstlisting}[mathescape=true]
-fm = makeIrreducibleModule[$B_{2}$][1, 0];
-tp = ((fm$\otimes$ ]fm)$\otimes$ fm)$\otimes$]fm;
-subs = makeFiniteRootSystem[
-  {1/4*{1, -1, 1, -1, 1, -1, 1, -1}, 
-   1/4*{0, 1, 0, 1, 0, 1, 0, 1}}];
-bc = branching[tp, subs];
-{bc[#], dynkinLabels[subs][#]} & /@ bc[weights]
-\end{lstlisting}
-It produces a list of highest weights and tensor product decomposition coefficients:
-\begin{lstlisting}
-{{1, {4, 0}}, {3, {2, 2}}, {0, {3, 0}}, 
-{2, {0, 4}}, {3, {1, 2}}, {6, {2, 0}}, 
-{6, {0, 2}}, {1, {1, 0}}, {3, {0, 0}}}]
-\end{lstlisting}
-
-Returning to the problem of spin chain Hamiltonian diagonalization we can see that instead of diagonalizing operator in space of dimension $625$ we can diagonalize operators in the spaces of dimensions $55, 81, 30, 35, 35, 14, 10, 5, 1$.
-
-\subsection{Branching and parabolic Verma modules}
-\label{sec:branch-parab-verma}
-
-We illustrate the generalized BGG-resolution by the diagrams of $G_{2}$ parabolic Verma modules which appear in the decomposition of irreducible module $L^{[1,1]}_{G_{2}}$:
+Это  \textit{обобщенные модули Верма}  \cite{lepowsky1977generalization},
+порожденные старшими весами  $\mu _{\frak{a}%
+_{\perp }}\left( u\right) $. Как  $U\left( \frak{u}_{I}^{-}\right) $-модуль каждый  $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ изоморфен  $%
+U\left( \frak{u}_{I}^{-}\right) \otimes L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\right) }$ и его характер можно записать при помощи функции Костанта-Хекмана \cite{KostantHeckman1982}, соответствующей вложению ортогонального партнера $\frak{a}_{\perp
+}\hookrightarrow \frak{g}$:
+\begin{equation*}
+\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\mathcal{KH}_{%
+\frak{a}_{\perp }\hookrightarrow \frak{g}}\mathrm{ch}L_{\frak{a}_{\perp
+}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
+\end{equation*}
+Функция  $\mathcal{KH}_{\frak{a}_{\perp }\hookrightarrow \frak{%
+g}}$ генерируется знаменателем  $R_{I}$, так что последнее выражение можно переписать следующим образом
+\begin{equation*}
+\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\frac{1}{R_{I}}%
+\mathrm{ch}L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }.
+\end{equation*}
+Таким образом мы получили обобщенную формулу Вейля-Верма для характеров -- разложение  $\mathrm{ch}\left(
+L^{\mu }\right) $ на характеры обобщенных модулей Верма:
 \begin{equation}
@@
 u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
-u\right) }.  \label{char-in-gen-verma-mod}
+u\right) }.  \label{char in gen verma mod}
 \end{equation}
-The character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, characters of the generalized Verma modules in decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}.
-Characters in the upper row appear in \eqref{char-in-gen-verma-mod} with positive sign and in the lower row -- with negative.
+\end{proof}
 
-\begin{figure}[h]
+\begin{remark}
+Здесь обобщенная формула Вейля-Верма для характеров (называемая формулой переменного суммирования в книге \cite{humphreys2008representations}) имеет специальный вид: веса $\mu _{\aft}$ отличны от старших весов обобщенных модулей Верма $\mu _{\afb}$.
+Причина в том, что старший вес $M_{I}$-модуля не равен проекции его максимального веса на  $h^*_{\afb}$ (он должен быть дополнительно сдвинут на дефект).
+\end{remark}
+
+\begin{example}
+  Рассмотрим обобщенные модули Верма для вложения $A_{1}\hookrightarrow B_{2}$, где подалгебра  $\afb$ связана с корнем  $\alpha_{1}$ алгебры  $B_{2}$.
+Обобщенный модуль Верма $M^{\omega_{1}}_{I}$ со старшим весом   $\omega_{1}=e_{1}$ показан на Рисунке \ref{fig:B2_Verma_Decomp}.
+  \begin{figure}[h!bt]
   \noindent\centering{
-    \includegraphics[width=80mm]{figures/G2-irrep.pdf}
+   \includegraphics[width=120mm]{B2_Gen_Verma_Decomp}
   }
-  \caption{Character of the irreducible $G_{2}$-module $L^{[1,1]}$}
-  \label{branching-bgg}
-\end{figure}
-\begin{figure}[h]
-  \noindent\centering{
-    \includegraphics[width=150mm]{figures/G2-pverma.pdf}
+  \caption{Обобщенные модули Верма для регулярного вложения  $A_1$ в $B_2$. 
+    Простые корни $\alpha_1, \alpha_2$ алгебры $B_2$ показаны пунктирными стрелками.
+Простой корень  $\beta = \alpha_1+2\alpha_2$ алгебры $A_1$ изображен серым вектором.
+Разложение $L^{\omega_{1}}$ представлено набором контуров входящих в него обобщенных модулей Верма.
+Пунктирные контуры соответствуют положительным значениям  $\epsilon(u)$, а точечные -- отрицательным.
 }
-  \caption{Characters of $G_{2}$ generalized Verma modules appearing in the decomposition of $L^{[1,1]}$.
-Parabolic Verma modules in the upper row appear in the decomposition with a positive sign, in the lower row -- with a negative.}
-  \label{g2-pverma}
+
+ \label{fig:B2_Verma_Decomp}
 \end{figure}
 
-\subsection{String functions of affine Lie algebras and CFT models}
-\label{sec:string-funct-affine}
+\end{example}
 
-String functions can be used to present formal characters of affine Lie algebra highest weight representation.
-They have interesting analytic and modular properties \cite{kac1990idl,kac1988modular,kac1984infinite}.
+\begin{remark}
+Как доказано, например, в книге  \cite{humphreys2008representations} (см.
+утверждение 9.6), характеры обобщенных модулей Верма $M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ могут также описываться как линейные комбинации обычных модулей Верма алгебры $\frak{g}$:
+\begin{equation*}
+\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\sum_{w\in W_{%
+\frak{a}_{\perp }}}\epsilon \left( w\right) \mathrm{ch}M^{w\left( \mu _{%
+\frak{a}_{\perp }}\left( u\right) +\rho _{\frak{a}_{\perp }}\right) -\rho _{%
+\frak{a}_{\perp }}}
+\end{equation*}
+Подставляя это выражение в формулу (\ref{char in gen verma mod}) и используя определения  (\ref{mu-a},\ref{mu-a-tilda}) и (\ref{defect ort}), мы восстанавливаем стандартное разложение Вейля-Верма для характера:
+\begin{equation*}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{w\in W}\;\epsilon (u)\mathrm{ch}%
+M^{w\left( \mu +\rho \right) -\rho }.
+\end{equation*}
+\end{remark}
 
-{\bf Affine.m} produces power series decomposition for string functions.
-Consider an affine Lie algebra $\hat{sl(3)}=\hat A_{2}$ and its highest weight module $L^{(1,0,0)}$.
-To get the string functions we can use the code:
-\begin{lstlisting}[mathescape=true]
-stringFunctions[$\hat A_2$,{1,1,2}]
-{{0, 0, 4}, 
-  $2 q + 10 q^2 + 40 q^3 + 133 q^4 + 398 q^5 + 1084 q^6 + 2760 q^7 + 6632 q^8 + 15214 q^9 + 33508 q^{10}$}, 
-{{0, 3, 1}, 
-  $2 q + 12 q^2 + 49 q^3 + 166 q^4 + 494 q^5 + 1340 q^6 + 3387 q^7 + 8086 q^8 + 18415 q^9 + 40302 q^{10}$}, 
-{{1, 1, 2}, 
-  $1 + 6 q + 27 q^2 + 96 q^3 + 298 q^4 + 836 q^5 + 2173 q^6 + 5310 q^7 + 12341 q^8 + 27486 q^9 + 59029 q^{10}$}, 
-{{2, 2, 0}, 
-  $1 + 8 q + 35 q^2 + 124 q^3 + 379 q^4 + 1052 q^5 + 2700 q^6 + 6536 q^7 + 15047 q^8 + 33248 q^9 + 70877 q^{10}$}, 
-{{3, 0, 1}, 
-  $2 + 12 q + 49 q^2 + 166 q^3 + 494 q^4 + 1340 q^5 + 3387 q^6 + 8086 q^7 + 18415 q^8 + 40302 q^9 + 85226 q^{10}$}
-\end{lstlisting}
-Similarly for the affine Lie algebra $\hat G_{2}$ we get
-\begin{lstlisting}[mathescape=true]
-stringFunctions[$\hat G_2$,{1,1,0}]
-{{2, 0, 0}, 
-  $1 + 8 q + 37 q^2 + 138 q^3 + 431 q^4 + 1227 q^5 + 3208 q^6 + 7901 q^7$}, 
-{{0, 0, 1}, 
-  $3 q + 18 q^2 + 73 q^3 + 247 q^4 + 736 q^5 + 2000 q^6 + 5070 q^7$}, 
-{{1, 1, 0},
-  $1 + 7 q + 32 q^2 + 117 q^3 + 370 q^4 + 1055 q^5 + 2780 q^6 + 6880 q^7$}, 
-{{0, 2, 0}, 
-  $3 q + 15 q^2 + 63 q^3 + 210 q^4 + 633 q^5 + 1725 q^6 + 4407 q^7$}
-\end{lstlisting}
+\section{БГГ резольвента и ветвление}
+В работе \cite{lepowsky1977generalization} показано, что для модуля старшего веса $L^{\mu }$, где $\mu \in P^{+}$, последовательность (обобщенная БГГ резольвента)
+\begin{equation}
+0\rightarrow M_{r}^{I}\overset{\delta _{r}}{\rightarrow }M_{r-1}^{I}\overset{%
+\delta _{r-1}}{\rightarrow }\ldots \overset{\delta _{1}}{\rightarrow }%
+M_{0}^{I}\overset{\varepsilon }{\rightarrow }L^{\mu }\rightarrow 0,
+\label{resolution sequence}
+\end{equation}
+где
+\begin{equation}
+M_{k}^{I}=\bigoplus_{u\in U,\;\mathrm{length}\left( u\right)
+=k}M_{I}^{u\left( \mu +\rho \right) -\rho },\quad M_{0}^{I}=M_{I}^{\mu }
+\label{Verma elements sequence}
+\end{equation}
+является точной и формула (\ref{gen Weyl-Verma}%
+) следует из этого разложения.
 
-\subsection{Branching functions and coset models of conformal field theory}
-\label{sec:branch-funct-coset}
+\begin{figure}[h!bt]
+ \noindent\centering{
+   \includegraphics[width=140mm]{B2_Exact}}
+ \caption{Вложение $A_1\hookrightarrow B_2$ (см. Рисунок \ref{fig:B2_Verma_Decomp}). Ортогональный партнер, подалгебра $A_1$, соответствует корню $\alpha_1$.
+   Резольвента простого модуля $L^{\omega_1}$. Показана центральная часть точной последовательности
+   $0 \to Im(\delta_2) \to \left( e^{\mu _{\widetilde{%
+\frak{a}}}\left( e\right) }\mathrm{ch}M_{I}^{\pi _{\afb}\left[ \omega_1 \right] -%
+\mathcal{D}_{\afb} }=M^{\omega_1}_{I}\right) \to
+   L^{\omega_1}\to 0 $.  Здесь $\mu _{\widetilde{\frak{a}}}\left( e\right) =\pi _{\aft}\left[ \mu \right] + \mathcal{D}_{\afb}$.
+   }
+\end{figure}
 
-It is believed that most rational models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$.
-These models can be studied as gauge theories \cite{Hwang:1994yr, hwang1993brst}.
+\begin{statement}
+Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра  $\afb\hookrightarrow \frak{g}$ ортогональна редуктивной подалгебре $\frak{a}\hookrightarrow \frak{g}$.
+Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\afb$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к подалгебре $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}$ .
+\end{statement}
 
-Branching functions for an embedding $\af\subset\gf$ are the partition functions of CFT on the torus (see \cite{difrancesco1997cft}).
+\begin{proof}
+Положим
+\begin{equation*}
+\mathrm{ch}M_{I}^{u\left( \mu +\rho \right) -\rho }=e^{\mu _{\widetilde{%
+\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
+u\right) },\mathrm{ch}M_{I}^{\mu }=e^{\mu _{\widetilde{\frak{a}}}\left(
+e\right) }\mathrm{ch}M_{I}^{\pi _{\frak{a}_{\perp }}\left[ \mu \right] -%
+\mathcal{D}_{\frak{a}_{\perp }}},
+\end{equation*}
+где \ $\mu _{\widetilde{\frak{a}}}\left( u\right) ,\mu _{\frak{a}_{\perp
+}}\left( u\right) $ и $\mathcal{D}_{\frak{a}_{\perp }}$ заданы как в Лемме \ref{Psi-decomp-lemma}, $%
+u\in U$ определено формулой (\ref{U-def}). В результате получим элементы фильтрующей последовательности (\ref{resolution sequence}).
 
-As a first example we show how to construct branching functions for the embedding $\hat A_{1}\to \hat B_{2}$ up to the tenth grade:
-\begin{lstlisting}[mathescape=true]
-branchingFunctions[$\hat B_{2}$,makeAffineExtension[makeFiniteRootSystem[{{1, 1}}]], {1, 1, 1}]
+Рассмотрим множество $\left\{ \mu _{\frak{a}_{\perp }}\left( u\right) |u\in U\right\} $ как множество старших весов простых модулей $L_{\frak{a}%
+_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ и вычислим размерности этих модулей. Вместе с 
+$\left\{ \mu _{\widetilde{\mathfrak{a}}}\left( u\right) |u\in
+U\right\} $ мы получим набор сингулярных весов
+\begin{equation*}
+\left\{ \epsilon (u)\;
+e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }
+\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp
+}}\left( u\right) }\right) \right\} .
+\end{equation*}
+Ветвление  $L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu
+\in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$  определяется веером вложения  $\Gamma _{\frak{a}\rightarrow \frak{g}}$ и соотношением (\ref{recurrent rel}), которое дает нам коэффициенты  $k_{\xi
+}^{\left( \mu \right) }$, а значит определяет и  $b_{\nu }^{\left( \mu \right) }$, так как  $b_{\nu }^{\left( \mu \right) }=k_{\nu }^{\left( \mu
+\right) }$ при $\nu \in \overline{C_{\frak{a}}}$ .
+\end{proof}
 
- {{3, 0}, 
-  $2 + 14 q + 52 q^2 + 154 q^3 + 410 q^4 + 994 q^5 + 2248 q^6 + 4832 q^7 + 9934 q^8 + 19680 q^9 + 37802 q^{10}$},
- {{2, 1}, 
-  $4 + 20 q + 72 q^2 + 220 q^3 + 584 q^4 + 1424 q^5 + 3248 q^6 + 7012 q^7 + 14488 q^8 + 28844 q^9 + 55616 q^{10}$},
- {{0, 3}, 
-  $4 q + 20 q^2 + 68 q^3 + 200 q^4 + 516 q^5 + 1224 q^6 + 2736 q^7 + 5808 q^8 + 11820 q^9 + 23236 q^{10}$},
- {{1, 2}, 
-  $2 + 14 q + 54 q^2 + 168 q^3 + 462 q^4 + 1148 q^5 + 2656 q^6 + 5812 q^7 + 12130 q^8 + 24358 q^9 + 47328 q^{10}$}
-\end{lstlisting}
+\begin{corollary}
+Пусть  $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$ и  $\frak{a}\hookrightarrow \frak{g}$ -- редуктивная подалгебра $\frak{g}$.
+Пусть $\frak{a}_{\perp }$, ортогональный партнер для $\frak{a}$, эквивалентен  $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, и $\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ с $\frak{h=\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$.
+Пусть $L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }=\bigoplus\limits_{\nu \in P_{\widetilde{\frak{a}}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\widetilde{\frak{a}}}^{\nu }$ -- ветвление модуля $L^{\mu }$ относительно подалгебры $\widetilde{\frak{%
+a}}$. Тогда коэффициенты $b_{\nu }^{\left( \mu \right) }$ определяют обобщенную резольвенту (\ref{resolution sequence}) модуля $L^{\mu }$
+по отношению к  $\frak{a}_{\perp }$.
+\end{corollary}
 
-Another example demonstrates the computation of branching functions for the regular embedding $\hat B_{2}\subset \hat C_{3}$:
-\begin{lstlisting}[mathescape=true]
-sub=makeAffineExtension[parabolicSubalgebra[$C_{3}$][2,3]];
-branchingFunctions[$\hat C_{3}$,sub, {2, 0, 0, 0}]
+\begin{proof}
+Пусть $\alpha $ -- простой корень  $A_{1}$.
+Используем преобразования из группы Вейля чтобы перевести его в некоторый простой корень алгебры $\frak{g}$, например $\alpha _{1}$.
+Построим сингулярный элемент для модуля  $L_{\frak{g}\downarrow
+\widetilde{\frak{a}}}^{\mu }$, то есть  $\Psi _{\widetilde{\frak{a}}%
+}^{\left( L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }\right)
+}=\sum_{\nu \in P_{\widetilde{\frak{a}}}^{+},b_{\nu }^{\left( \mu \right)
+}>0}b_{\nu }^{\left( \mu \right) }\Psi _{\widetilde{\frak{a}}}^{\left( \nu
+\right) }$, и разложим его $\Psi _{\widetilde{\frak{a}}}^{\left( L_{\frak{%
+g}\downarrow \widetilde{\frak{a}}}^{\mu }\right) }=k_{\xi }^{\left( \mu
+\right) }e^{\xi }$. В нашем случае представители $u$ в рекуррентном соотношении (\ref{recurrent rel}) определяются весом $\xi $ однозначно:
+\begin{equation*}
+\epsilon (u\left( \xi \right) )\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{%
+\frak{a}_{\perp }}\left( u\left( \xi \right) \right) }\right) =-s\left(
+\gamma _{0}\right) k_{\xi }^{\left( \mu \right) }-\sum_{\gamma \in \Gamma _{%
+\widetilde{\frak{a}}\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right)
+k_{\xi +\gamma }^{\left( \mu \right) }.
+\end{equation*}
+Тогда
+\begin{equation*}
+\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\left(
+\xi \right) \right) }\right) =\left| s\left( \gamma _{0}\right) k_{\xi
+}^{\left( \mu \right) }+\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}%
+\rightarrow \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma
+}^{\left( \mu \right) }\right|
+\end{equation*}
+и
+\begin{equation*}
+\mu _{\frak{a}_{\perp }}\left( u\left( \xi \right) \right) =\frac{1}{2}%
+\left( \dim \left( L_{A_{1}}^{\mu \left( \xi \right) }\right) -1\right)
+\alpha _{1}
+\end{equation*}
+Таким образом, множество обобщенных модулей Верма  $e^{\xi +\mathcal{D}%
+_{\frak{a}_{\perp }}}\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
+u\left( \xi \right) \right) }$ полностью фиксировано:
+\begin{equation*}
+\left\{ e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }\mathrm{ch}%
+M_{I}^{\mu _{\frak{a}_{\perp }}\left( u\right) }|u\in U\right\} .
+\end{equation*}
+Упорядочивая эти модули по длине $u$, мы получаем компоненты (\ref{Verma elements sequence}) резольвенты (\ref{resolution sequence}).
+\end{proof}
 
-{{0, 1, 0}, 
-  $2 q - 20 q^3 + 24 q^4 + 82 q^5 - 320 q^6 + 108 q^7$}, 
-{{1, 0, 0}, 
-  $1 - q - 8 q^2 + 19 q^3 + 16 q^4 - 156 q^5 + 205 q^6 + 640 q^7$}, 
-{{0, 0, 1}, 
-  $q - 5 q^3 + 7 q^5$}
-\end{lstlisting}
+\section{Выводы к третьей главе}
 
-\section{Conclusion}
-\label{sec:conclusion}
-We have presented the package {\bf Affine.m} for computations in representation theory of finite-dimensional and affine Lie algebras.
-It can be used to study Weyl symmetry, root systems, irreducible, Verma and parabolic Verma modules of finite-dimensional and affine Lie algebras.
-In the present paper we have also discussed main ideas used for an implementation of the package and described most important notions of representation theory required to use {\bf Affine.m}.
+\label{sec:conclusions}
+В работе \cite{2010arXiv1007.0318L} было показано, что метод веера вложения работает также и для специальных вложений.
+Надо заметить, что  разложения Вейля-Верма также могут быть получены в этом случае.
+Резольвенты, соответствующие специальным подалгебрам, описывают соотношения между проекциями характера начального модуля и обобщенными модулями Верма со старшими весами в подпространстве $h^*$.
 
-We have demonstrated that recurrent approach based on the Weyl character formula is not only useful for calculations but also allows to establish connections with the (generalized) Bernstein-Bernstein-Gelfand resolution.
-
-Also we have presented examples of computations with this package connected with problems of physics and mathematics.
-
-In future versions of our software we are going to treat twisted affine Lie algebras, extended affine Lie algebras and provide more direct support for tensor product decompositions.
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-I thank V.D. Lyakhovsky and O.Postnova for discussions and helpful comments.
-
-The work is supported by the Chebyshev Laboratory
-(Department of Mathematics and Mechanics, Saint-Petersburg State
-University) under the grant 11.G34.31.0026 of the Government of the
-Russian Federation.
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-\appendix
-
-\section{Software package}
-\label{package}
-The package can be freely downloaded from \url{http://github.com/naa/Affine}. To get the development code use the command
-\begin{lstlisting}[language=bash]
- git clone git://github.com/naa/Affine.git
-\end{lstlisting}
-
-Contents of the package:
-\begin{verbatim}
-    Affine/                                root folder
-      demo/                                  demonstrations
-        demo.nb                                demo notebook
-        paper.nb                               code for the paper
-      doc/                                 documentation folder
-        figures/                             figures in paper 
-          timing.pdf                           diagram showing performance
-          branching-timing.pdf                 ...  for branching coefficients  
-          irrep-sum.pdf                        sum of B2 irreps
-          irrep-verma-pverma.pdf               irrep, Verma, (p)Verma for B2
-          G2-irrep.pdf                         irrep for G2
-          G2-pverma.pdf                        parabolic Verma for G2
-          tensor-product.pdf                   tensor product of A1-modules
-        bibliography.bib                     bibliographic database
-        paper.pdf                            present paper
-        paper.tex                            paper source
-        TODO.org                             list of issues
-      src/                                 source folder
-        affine.m                             main software package
-      tests/                               unit tests folder
-        tests.m                              unit tests
-      README.markdown                      installation and usage notes
-\end{verbatim}
-
-%% References
-%%
-%% Following citation commands can be used in the body text:
-%% Usage of \cite is as follows:
-%%   \cite{key}         ==>>  [#]
-%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
-%%
-
-%% References with bibTeX database:
-
-  %   \section*{References}
-  %   \label{sec:references}
-  %   
-  %   
-  %   \bibliography{bibliography}
-  %   \bibliographystyle{phcpc}
-  %   %\bibliographystyle{model1-num-names}
-  %   
-  %   
-  %   %% Authors are advised to submit their bibtex database files. They are
-  %   %% requested to list a bibtex style file in the manuscript if they do
-  %   %% not want to use elsarticle-num.bst.
-  %   
-  %   %% References without bibTeX database:
-  %   
-  %   % \begin{thebibliography}{00}
-  %   
-  %   %% \bibitem must have the following form:
-  %   %%   \bibitem{key}...
-  %   %%
-  %   
-  %   % \bibitem{}
-  %   
-  %   % \end{thebibliography}
-  %   
-  %   
-  %
+Рассмотрим ситуацию, когда выбор простых корней зафиксирован какими-то внешними факторами (возникающими, например, из требований физических приложений).
+В этом случае ортогональный партнер не может порождаться только простыми корнями.
+Элементы   $\frak{u}_{I}^{+}:=\sum_{\eta \in \Delta
+^{+}\setminus \Delta _{I}^{+}}\frak{g}_{\eta }$ не образуют подалгебру в  $%
+\mathfrak{g}$, так как некоторые не простые корни отсутствуют в  $\Delta ^{+}\setminus
+\Delta _{I}^{+}$. Важно отметить, что в этом случае формула Вейля-Верма по-прежнему существует. В ней обобщенные модули Верма соответствуют сжатиями \cite{Doebner1967Melsheimer} алгебры $%
+\frak{n}^{+}$ и соотношения Вейля-Верма описывают разложение пространства представления $L^{\mu}$ в набор обобщенных модулей Верма сжатой алгебры  $U\left(\frak{n}_c^{+}\right)$.
+Весовые векторы образованы базисом Пуанкаре-Биркгофа-Витта алгебр $U\left(\frak{n}_c^{+}\right)$ и
+$U\left( \mathfrak{a}_{\bot} \right)$. Чтобы рассмотреть такое пространство как  $%
+\mathfrak{g}$-модуль мы должны выполнить деформацию \cite
+{Nijenhuis1966Richardson} алгебры $\frak{n}_c^{+}$ (то есть восстановить первоначальный закон композиции).
+Пространство сохраняется, и после такой деформации генераторы начальной алгебры будут действовать на нем правильным образом.
 

### 2011-12-29 AffineLieAlgebras/Thesis/2.tex
First version sent to Vladimir Dmitrievich

@@
 {humphreys1997introduction}) и знаменатель Вейля $\Psi _{\af_{\bot
-  }}^{\left( 0\right) }$ для ортогонального партнера. В работе показано, что элемент  $\Psi _{\gf%
+  }}^{\left( 0\right) }$ для ортогонального партнера. Ниже мы показываем, что элемент  $\Psi _{\gf%
 }^{\left( \mu \right) }$ может быть разложен в комбинацию числителей Вейля $\Psi _{\af_{\bot }}^{\left( \nu \right) }$, где $\nu \in P_{%
@@
 \label{sec:conclusions}
-В работе \cite{2010arXiv1007.0318L} было показано, что метод веера вложения работает также и для специальных вложений.
+В главе \ref{cha:affine-lie-algebras}  было показано, что метод веера вложения работает также и для специальных вложений.
 Надо заметить, что  разложения Вейля-Верма также могут быть получены в этом случае.

### 2011-12-29 AffineLieAlgebras/Thesis/4.tex
Conclusion of the thesis removed, some work on the structure of chapters.
First version sent to Vladimir Dmitrievich

@@
 
-В разделе  \ref{sec:conclusion} мы обсуждаем возможность сравнения классификации операторов смены граничных условий, следующей из свойства мартингалов с общей классификацией операторов смены граничных условий в граничной конформной теории поля, связанной с D-бранными решениями \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,Maldacena:2001ky,felder1999geometry,alekseev1999d}.
+В разделе  \ref{sec:5-conclusion} мы обсуждаем возможность сравнения классификации операторов смены граничных условий, следующей из свойства мартингалов с общей классификацией операторов смены граничных условий в граничной конформной теории поля, связанной с D-бранными решениями \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,Maldacena:2001ky,felder1999geometry,alekseev1999d}.
 
@@
 
-\section{Заключение}
-\label{sec:conclusion}
+\section{Выводы к пятой главе}
+\label{sec:5-conclusion}
 

### 2011-12-29 AffineLieAlgebras/Thesis/5.tex
First version sent to Vladimir Dmitrievich

@@
   }
-  \caption{Время работы алгоритмов, основанных на применении формулы Фрейденталя \eqref{eq:15} (пунктиром)  и рекуррентного соотношения \eqref{recurrent-rel} (сплошная линия) с ростом числа весов в  $\bar C$ при вычислении коэффициентов ветвления для вложения $B_{3}\subset B_{4}$.}
+  \caption{Время работы алгоритмов, основанных на применении формулы Фрейденталя \eqref{eq:15} (пунктиром)  и рекуррентного соотношения \eqref{recurrent-relation} (сплошная линия) с ростом числа весов в  $\bar C$ при вычислении коэффициентов ветвления для вложения $B_{3}\subset B_{4}$.}
   \label{fig:branching}
@@
 \section*{Выводы к шестой главе}
-\label{sec:conclusion}
+\label{sec:6-conclusion}
 В данной главе мы представили пакет {\bf Affine.m} для вычислений в теории представлений конечномерных и аффинных алгебр Ли.

### 2011-12-29 AffineLieAlgebras/Thesis/3.tex
Conclusion of the thesis removed, some work on the structure of chapters.
First version sent to Vladimir Dmitrievich

@@
 Сплинты были классифицированы в работе \cite{richter2008splints}  (см.
-Приложение в работе) и первые три класса сплинтов в этой классификации инъективны.
+Приложение в конце главы) и первые три класса сплинтов в этой классификации инъективны.
 
@@
 
-\section{Заключение}
+\section{Выводы к четвертой главе}
 
-\label{sec:conclusions}
+\label{sec:4-conclusions}
 Мы продемонстрировали, что сплинт представляет собой очень эффективный инструмент для вычисления коэффициентов ветвления.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Приложение}
+\section*{Приложение}
 \label{sec:appendix}

### 2012-01-10 AffineLieAlgebras/Thesis/3.tex
Misprints fixed

@@
 \label{cha:splints}
-
-\section{Сплинты и ветвления}
-\label{sec:splints}
-
-%%\newtheorem{Def}{Definition}[section]
-%%\newtheorem{Cnj}[Def]{Conjecture}
-%%\newtheorem{Prop}[Def]{Property}
-%%\newtheorem{example}{Example}[section]
-%%
-%\input{tcilatex}
 
@@
 Мы показываем, что использование свойств сплинта  позволяет сильно упростить вычисление коэффициентов ветвления.
-
-\section{Введение}
-\label{sec:Introduction}
 
@@
 Мы демонстрируем, что (при выполнении определенных условий, описанных в разделе \ref{sec:stems and multiplicity functions}) сплинт является естественным инструментом для изучения свойств редукции  $\gf$-модулей по отношению к подалгебре $\af\longrightarrow\gf$.
-Используя этот инструмент мы получаем основной результат данной главы -- однозначное соответствие между кратностями весов неприводимых модулей сплинта и коэффициентов ветвления для редуцированного модуля $L^{\mu}_{\gf\downarrow \af}$
+Используя этот инструмент мы получаем основной результат данной главы -- однозначное соответствие между кратностями весов неприводимых модулей сплинта и коэффициентов ветвления для редуцированного модуля $L^{\mu}_{\gf\downarrow \af}$.
 
@@
 
+\section{Сплинты и соотношения для аффинных алгебр Ли}
+\label{sec:splints-affine}
+
+Splint of root system of simple Lie algebra appears naturally in
+the study of (regular) embeddings of reductive subalgebras. It can
+be used to derive branching rules. Application of
+splint properties drastically simplifies calculations of
+branching coefficients. We study affine extension of splint root system of simple Lie algebra and obtain relations on theta and branching functions.
+
+The term {\it splint} was introduced by D. Richter in \cite{richter2008splints} where the
+classification of splints for simple Lie algebras was obtained. The fan $\Gamma \subset \Delta$ was
+introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent properties of
+branching coefficients for maximal embeddings. Injection fan is an efficient tool to study branching
+rules. Later this construction was generalized to non-maximal embeddings and affine Lie algebras in
+\cite{2010arXiv1007.0318L, ilyin812pbc}. In paper \cite{2011arXiv1111.6787L} we have shown that the
+existence of a splint for a root system of a simple Lie algebra leads to simplifications in
+reduction procedures of a Lie algebra module to modules of a subalgebra. This effect is based on the
+injection fan and singular element properties of Lie algebra modules.
+
+In the present note we discuss possible applications of splint in
+a root system of simple Lie algebra related to representation
+theory of affine Lie algebras. We discuss the structure of
+injection fan for affine Lie algebras and show that it admits a
+decomposition similar to that used in \cite{2011arXiv1111.6787L}
+for simple Lie algebras. Such a decomposition leads to equations
+for theta-functions. We study graded branching of affine Lie
+algebra modules reduced to a finite-dimensional subalgebra and
+discuss consequences of splint in this case.
+
+\subsection{Splints and affine Lie algebras}
+\label{sec:definitions}
+
+Consider simple Lie algebra $\gf$ with a root system $\Delta$. Let
+$\af_{1}\subset \gf$ be its reductive subalgebra of the same rank, such that
+$\Delta_{\af}\equiv\Delta_{1}\subset\Delta$ and $Q_{\af}\subset Q$, where $Q$ is the root lattice. Irreducible highest-weight modules of
+$\gf$ and $\af$ are denoted by $L^{\mu}$ and $L^{\nu}_{\af}$
+correspondingly. Weyl character formula for irreducible modules is
+$\mathrm{ch}L^{\mu}=\frac{\Psi^{(\mu)}}{\prod_{\alpha\in\Delta}(1-e^{-\alpha})}$,
+where $\Psi^{(\mu)}=\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}$
+is a singular element of the module and $W$ -- the Weyl group of
+$\gf$. Formal character of irreducible module admits a
+decomposition
+\begin{equation}
+  \label{eq:4}
+  \mathrm{ch} L^{\mu}=\sum_{\nu\in P_{\af}} b^{\mu}_{\nu} \mathrm{ch} L^{\nu}_{\af},
+\end{equation}
+where $P$, $P_{\af}$ are weight lattices of $\gf$ and $\af$. We
+want to study affine extension of this situation:
+$\gf\subset\gfh,\; \af\subset\afh$, $\afh\subset\gfh$,
+$\hat{\Delta}\subset\hat{\Delta}$ and
+$\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{\hat{\nu}}
+b^{\hat{\mu}}_{\hat{\nu}} \mathrm{ch} L^{\hat{\nu}}_{\afh}$. For
+weights of an affine Lie algebra $\gfh$ we have
+$\hat{\mu}=(\mu,k,n)$, where $\mu$ is a weight of $\gf$, $k$ --
+the level of the module and $n$ -- the grade of the weight
+$\hat{\mu}$
+
+\begin{Def}
+  Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a bijective map of
+  roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with vector composition law
+  in $\Delta_{1}$ and $\Delta$.
+\begin{equation*}
+\phi:\Delta_1 \longrightarrow \Delta, \quad \phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,\,\,\, \alpha,\beta \in \Delta_1
+\end{equation*}
+\end{Def}
+
+Note that the image $Im(\phi)$ must not inherit the root system properties except the addition rules
+equivalent to the addition rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and
+$\phi_2$ can splinter $\Delta$ when the latter can be presented as a disjoint union of images
+$Im(\phi_1)$ and $Im(\phi_2)$.
+
+$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
+\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
+_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
+\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+
+\begin{Def}
+  A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if there are two embeddings
+  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
+  \phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the disjoint union of the
+  images of $\phi _{1}$ and $\phi _{2}$ and (b) neither the rank of $\Delta _{1}$ nor the rank of
+  $\Delta _{2}$ exceeds the rank of $%
+  \Delta $.
+\end{Def}
+
+It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote
+this by $\Delta \approx (\Delta_1,\Delta_2)$. Each component $\Delta_1$ and $\Delta_2$ is a "stem''
+of the splint.
+
+We consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem. As shown in paper \cite{2011arXiv1111.6787L} the second stem $\Delta _{\frak{s}}:=\Delta
+_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product
+$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}$
+and it defines an injection fan $\Gamma _{\frak{a}%
+\hookrightarrow \frak{g}}$ \cite{lyakhovsky1996rra,ilyin812pbc,2010arXiv1007.0318L}.
+
+Since the singular element of $L^{\mu}$ can be
+written as $\Psi _{\frak{g}}^{\left( \mu \right) }=e^{-\rho }
+\sum_{w\in W_{\frak{a}}}\epsilon \left( w \right) w\circ \left(
+e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho
+_{\frak{s}}}\right)$  for branching coefficients we get the
+identity \cite{2011arXiv1111.6787L}:
+\begin{equation}
+  \label{eq:9}
+b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}  
+\end{equation}
+Here the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $, they have the
+same Dynkin numbers: $\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
+m_{k}\omega_{(\sfr) k} . \label{new h weight}$ So branching coefficients coincide with weight
+multiplicities of $\sfr$-modules.
+
+Now we consider affine extension of this setup, $\afh\subset\gfh$. Since $\mathrm{rank}\gf\leq
+\mathrm{rank} \af+\mathrm{rank}\sfr$ for Weyl denominators we get
+ \[
+\prod_{\alpha\in\hat{\Delta}^{+}_{1}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}\prod_{\beta\in\hat{\Delta}^{+}_{2}}(1-e^{\phi\circ \beta})^{\mathrm{mult}(\beta)}=\prod_{\gamma\in\hat{\Delta}^{+}}(1-e^{-\gamma})^{\mathrm{mult}(\gamma)}\prod_{n=0}^{\infty}(1-e^{-n\delta})^{\mathrm{rank}\af+\mathrm{rank}\sfr-\mathrm{rank}\gf}
+\]
+
+Using a specialization
+\cite{kac1988modular,kac1984infinite,kac1990idl} and the
+definition of Dedekind eta-function
+$\eta(\tau)=q^{1/24}\prod_{n=1}^{\infty}(1-q^{n})$, where
+$q=e^{2\pi i \tau}$ we can rewrite this identity as the relation
+imposed on theta-functions $\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in Q_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$:
+\begin{multline}
+  \label{eq:5}
+  \eta(\tau)^{\mathrm{dim}(\af)}\prod_{\alpha\in\Delta_{1}^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z)}{\eta(\tau)} \eta(\tau)^{\mathrm{dim}(\sfr)}\prod_{\beta\in\Delta_{2}^{+}}\frac{\Theta^{(\hat A_{1})}_{\phi\circ \beta}(\tau,z))}{\eta(\tau)}=\\
+\eta(\tau)^{\mathrm{rank}(\af)+\mathrm{rank}(\sfr)-\mathrm{rank}(\gf)}
+\eta(\tau)^{\mathrm{dim}(\gf)}\prod_{\alpha\in\Delta^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z))}{\eta(\tau)}
+\end{multline}
+Here $z\in P_{\geq 0}\otimes \mathbb{C}$. Using Weyl denominator identity this relation can be
+rewritten as a non-trivial relation connecting theta-functions of algebras $\gfh,\hat\sfr,\afh$:
+\begin{equation}
+  \label{eq:6}
+  \left(\sum_{v\in W_{\af}}\epsilon(v) \Theta^{(\afh)}_{v\rho_{\af}}(\tau,z)\right)
+  \cdot \left(\sum_{u\in W_{\sfr}}\epsilon(u) \Theta^{(\hat{\sfr})}_{\phi\circ(u\rho_{\sfr})}(\tau,z)\right)= 
+  \left(\sum_{w\in W}\epsilon(w) \Theta^{(\gfh)}_{w\rho_{\gf}}(\tau,z)\right)
+\end{equation}
+%Now we can use Weyl denominator identity $e^{-\rho}\prod_{\alpha\in \hat{\Delta}^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}=\sum_{w\in \hat{W}}\det(w)e^{w\rho}$
+
+Now consider the branching of $\gfh$-module to $\gf$-modules. For
+formal characters we can write the following expression:
+\begin{equation}
+  \label{eq:8}
+\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{\nu}(n) \mathrm{ch} L^{\nu}_{\gf}.
+\end{equation}
+Rewriting this equation for weight multiplicities we get
+$m^{(\hat{\mu})}_{\hat{\nu}=(\nu,k,n)}=\sum_{\xi\in P}
+b^{(\hat{\mu})}_{\xi}(n) m^{(\xi)}_{\nu}$. We can introduce
+branching functions similarly to the case of branching for affine
+subalgebra \cite{kac1988modular,kac1990idl}:
+$b^{(\hat{\mu})}_{\nu}(q)=\sum_{n=0}^{\infty}
+b^{(\hat{\mu})}_{\nu}(n) q^{n}$.
+These branching functions are connected to $q$-dimension of module $\mathrm{dim}_{q}L^{\hat \mu}_{\gfh}=\sum_{n=0}^{\infty}q^{n}\sum_{\nu\in P} b^{(\hat \mu)}_{\nu}(n) \mathrm{dim }L^{\nu}_{\gf}=\sum_{\nu\in P}b^{(\hat\mu)}_{\nu}(q) \mathrm{dim} L^{\nu}_{\gf}$.
+It is well-known that $q$-dimension is a modular function for some $\Gamma\subset SL_{2}(\mathbb{Z})$  \cite{gannon2006moonshine}, so branching functions $b^{(\hat \mu)}_{\nu}(q)$ have modular properties.
+
+ For string functions of a module
+$L^{\hat{\mu}}$ we have
+\begin{equation}
+  \label{eq:7}
+   \sigma^{(\hat{\mu})}_{\nu}(q) = \sum_{\xi\in P} m^{(\xi)}_{\nu} b^{(\hat{\mu})}_{\xi}(q).
+\end{equation}
+
+Introduce an ordering of the set of weights $\xi$ as follows:
+attribute to a weight $(\rho,\xi)$ its product $(\rho,\xi)$ with
+the Weyl vector $\rho$. Then relation \eqref{eq:7} can be written
+in the matrix form $\sigma(q)=M b(q)$ or as an inverse relation
+$b(q)=M^{-1}\sigma(q)$. Here $\sigma(q)$ and $b(q)$ are infinite
+columns of string and branching functions. Matrix $M$ contains
+multiplicities of weights in $\gf$-modules similar to that of
+Table 1 in paper \cite{2010arXiv1001}. The inverse matrix $M^{-1}$
+encodes recurrent relations imposed weight multiplicities
+\cite{il2010folded}.
+
+Now consider the branching of $\gfh$-modules in $\af$-modules and
+assume the existence of a splint
+$\Delta^{+}_{\gf}=\Delta^{+}_{\af}\cup \phi(\Delta^{+}_{\sfr})$.
+We decompose $\gf$-modules in equation \eqref{eq:8} into
+$\af$-modules using property \eqref{eq:9}:
+\begin{multline}
+  \label{eq:10}
+  \mathrm{ch}L^{\hat{\mu}}_{\gfh}=
+\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P_{\af}} b^{(\hat{\mu})}_{(\gfh\downarrow\af)\nu}(n) \mathrm{ch} L^{\nu}_{\af}=
+\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} b^{(\nu)}_{(\gf\downarrow \af) \xi}\mathrm{ch} L^{\xi}_{\af}=\\
+=\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} M^{\widetilde{\nu}}_{  \widetilde{\nu}-\phi^{-1}( \nu-\xi )}\mathrm{ch} L^{\xi}_{\af}
+\end{multline}
+We see that the similar matrix relation holds for branching
+functions $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}\;
+b_{(\gfh\downarrow\gf)}(q)$ and we can write
+$\sigma(q)=M_{\af}\; b_{(\gfh\downarrow\af)}(q)$. So if we know
+branching coefficients for the embedding $\gf\subset\gfh$ (for
+example, see book \cite{kass1990ala}) we can easily obtain
+branching functions for the embedding $\af\subset \gfh$.
+\subsection*{Conclusion}
+\label{sec:conclusion} We have demonstrated that splint in affine
+Lie algebras leads to new relations between theta-functions and
+branching functions for branching to finite-dimensional
+subalgebras, which can be useful for computations. Further
+question is to generalize this analysis to affine subalgebras and
+to apply the results to branching in the study of CFT coset
+models.
+
 \section{Выводы к четвертой главе}

### 2012-01-10 AffineLieAlgebras/Thesis/common.tex
Misprints fixed

@@
 
-\topic{Бесконечномерные алгебры симметрии в моделях квантовой теории поля}
+\topic{Правила ветвления аффинных алгебр Ли и приложения в моделях конформной теории поля}
 
@@
 Материалы диссертации опубликованы в $8$ печатных работах, из них $3$ статьи в
-рецензируемых журналах~\citemy{2010arXiv1007.0318L,2010LyakhovskyNazarovTMF}, $2$ статьи в
-сборниках трудов конференций, 2 препринта и $1$ тезисы доклада.
+рецензируемых журналах~\citemy{2010arXiv1007.0318L,2010LyakhovskyNazarovTMF,2011arXiv1111.6787L}, $4$ статьи в
+сборниках тезисов и трудов конференций \cite{2011arXiv1112.4354N,2010LyakhovskyNazarovMQFT,Nazarov2008,NazarovACSM2009}, и в препринте \cite{2011arXiv1107.4681N}.
 }
@@
 
-Глава \ref{cha:splints} посвящена сплинтам.
+Глава \ref{cha:splints} посвящена сплинтам -- расщеплением корневой системы алгебры Ли в объединение образов корневых систем двух алгебр, не обязательно являющихся подалгебрами данной алгебры.
+Если одна из алгебр является подалгеброй, то сплинт приводит к резкому упрощению в вычислении коэффициентов ветвления -- они совпадают с кратностями весов в модуле другой алгебры.
+Основная часть главы посвящена доказательству этого факта.
+Кроме того, сплинт корневой системы простой конечномерной алгебры Ли приводит к возникновению новых соотношений на струнные функции и функции ветвления соответствующего аффинного расширения.
+Эти соотношения обсуждаются в разделе
 

### 2012-01-10 AffineLieAlgebras/Thesis/review.tex
Misprints fixed

@@
 Существуют разнообразные классы моделей двумерной конформной теории поля и даже задача классификации всех таких моделей до конца не решена, несмотря на первоначальный оптимизм \cite{moore1989taming}.
-Конформная теория поля привлекла большое внимание также в благодаря своей связи с теорией струн.
-
-Вместе с тем доказательство соответствия между критическим поведением решеточных моделей и конформной теории поля остается серьезной проблемой.
-Здесь в последнее время получены новые результаты, связанные с использованием эволюции Шрамма-Левнера.
-Некоторые вопросы такого соответствия мы обсуждаем в главе \ref{sec:SLE}.
+Конформная теория поля привлекла большое внимание также благодаря своей связи с теорией струн.
 
@@
 Обычно соответствие между критическим поведением решеточных моделей и конформной теорией поля устанавливается именно для минимальных моделей \cite{bauer2004cfts,bauer2003sle,bauer2003conformal}.
-Проблема соответствия между решеточными моделями и coset-моделями конформной теории поля обсуждается в главе \ref{sec:SLE}.
+Вместе с тем доказательство соответствия между критическим поведением решеточных моделей и конформной теории поля остается серьезной проблемой.
+Здесь в последнее время получены новые результаты, связанные с использованием эволюции Шрамма-Левнера.
+Некоторые вопросы такого соответствия мы обсуждаем в главе \ref{sec:SLE}.
+В ней мы обсуждаем соответствие между решеточными моделями и coset-моделями конформной теории поля.
 
@@
 центральным зарядом называются рациональными. Считается, что все такие теории могут быть получены
-факторизацией так называемых моделей Весса-Зумино-Новикова-Виттена \cite{moore1989taming}.
+факторизацией моделей Весса-Зумино-Новикова-Виттена \cite{moore1989taming}.
 
@@
 Обычно их понимают следующим образом.
-Пусть $\Omega\in\mathbb{H}$ -- вакуум, $n$-точечные корреляционные функции в квантовой теории поля обычно понимают, как
+Пусть $\Omega\in\mathbb{H}$ -- вакуум, тогда $n$-точечные корреляционные функции в квантовой теории поля даются выражением
 \begin{equation}
@@
 где $\varphi_{i_{k}}$ -- поля в теории.
-$n$-точечные корреляционные функции можно аналитически продолжить на пространство $M_{n}=\{(z_{1},\dots,z_{n})\in \mathbb{C}^{n}: z_{i}\neq z_{j},\; i\neq j\}$.
+Функции $G_{i_{1},\dots,i_{n}}$ можно аналитически продолжить на пространство $M_{n}=\{(z_{1},\dots,z_{n})\in \mathbb{C}^{n}: z_{i}\neq z_{j},\; i\neq j\}$.
 $M_{n}^{+}$ состоит из наборов, где $\mathrm{Re}\;z_{i}>0$ для любого $i$.
@@
 
-  Пусть $B_{0}$ -- индексное множество (счетное), последовательности произвольной длины $(i_{1},\dots,i_{n})\in B_{0}^{n}$ образуют пространство мультииндексов $i\in B$.
+  Пусть $B_{0}$ -- индексное множество (счетное).
+Последовательности произвольной длины $(i_{1},\dots,i_{n})\in B_{0}^{n}$ образуют пространство мультииндексов $i\in B$.
 Корреляционные функции $G_{i_{1},\dots, i_{n}}:M_{n}\to \mathbb{R}$ удовлетворяют следующим аксиомам.
@@
   (Аксиома локальности)
-  Для всех $(i_{1},\dots,i_{n})\in B_{0}^{n}$, $(z_{1},\dots, z_{n})\in M_{n}$ и $\pi\in S_{n}$ -- перестановок множества из $n$ элементов верно равенство
+  Для всех $(i_{1},\dots,i_{n})\in B_{0}^{n}$, $(z_{1},\dots, z_{n})\in M_{n}$ и $\pi\in S_{n}$ --- перестановок множества из $n$ элементов верно равенство
   \begin{equation}
@@
   Обозначим через $\Theta:\mathbb{C}\to\mathbb{C}$  отображение $z=t+i y\to \Theta(z)= -t+i y$.
-Тогда аксиома утверждает, что существует инволюция $\star:B_{0}\to B_{0}$, $\star^{2}=\mathrm{id}_{B_{0}}$, которая продолжается на $B$ ($i\to i^{*}$), и выполняются свойства
+Тогда аксиома утверждает, что существует инволюция $\star:B_{0}\to B_{0}$, $\star^{2}=\mathrm{id}_{B_{0}}$, которая продолжается на $B$ ($\star:i\to i^{*}$), и выполняются свойства
   \begin{enumerate}
@@
 \end{axiom}
-Эта аксиома позволяет восстановить гильбертово пространство $\mathbb{H}$, так как она дает положительную полу-определенную форму $H$ на $\underline{S}^{+}$.
-То есть мы можем определить $\mathbb{H}$ как пополнение $\underline{S}^{+}$ факторизованное по $\mathrm{ker}\; H$ с произведением \eqref{eq:54}.
+Эта аксиома позволяет восстановить гильбертово пространство $\mathbb{H}$, так как она дает положительную полуопределенную форму $H$ на $\underline{S}^{+}$.
+То есть мы можем определить $\mathbb{H}$ как пополнение $\underline{S}^{+}$ факторизованное по $\mathrm{ker}\, H$ с произведением \eqref{eq:54}.
 Мы можем построить и полевые операторы.
@@
 \end{theorem}
+Доказательство этой теоремы приведено в книге \cite{schottenloher2008mathematical}.
+
 Теперь добавим аксиомы, специфичные для конформной теории поля. Во-первых введем масштабную инвариантность.
@@
 Простейший класс конформных теория поля составляют минимальные модели, в которых число примарных полей конечно.
+Такие модели проще всего сопоставить с критическим поведением в решеточных моделях.
+Например, в работе \cite{belavin1984ics} было найдено соответствие между моделью Изинга и несколькими минимальными моделями конформной теории поля, в работе \cite{zamolodchikov1987representations} обсуждалось соответствие с моделью Поттса, а в работе \cite{zamolodchikov1987conformal} предложена модель конформной теории поля для вычисления многоточечных корреляционных функций в модели Ашкина-Теллера.
+Обзор этих результатов есть в книге \cite{difrancesco1997cft}.
+
+ Уже для модели Поттса приходится принимать во внимание не только алгебру Вирасоро, но и дополнительную дискретную симметрию $Z_{N}$.
+Более общие модели можно получить при изучении дополнительной бесконечномерной симметрии.
+Основной класс таких моделей -- это модели Весса-Зумино-Новикова-Виттена.
 
@@
 
-WZW-модели обладают дополнительной симметрией. Алгебра токов в них --- это алгебра Каца-Муди
+Модели Весса-Зумино-Новикова-Виттена обладают дополнительной симметрией. Алгебра токов в них --- это алгебра Каца-Муди
 (аффинная алгебра Ли $\mathfrak{g}$), полная киральная алгебра --- полупрямое произведение
-$Vir\ltimes \mathfrak{g}$, примарные поля преобразуются по неприводимым представлениям алгебры $\mathfrak{g}$.
+$Vir\ltimes \mathfrak{g}$, примарные поля классифицируются по неприводимым представлениям алгебры $\mathfrak{g}$.
 
-В данном разделе мы показываем, как такие модели можно строить путем квантования нелинейной сигма-модели с дополнительным членом Весса-Зумино.
+В данном разделе мы показываем, как такие модели можно строить путем квантования нелинейной сигма-модели с дополнительным членом Весса-Зумино следуя обзору \cite{Walton:1999xc} и книге \cite{difrancesco1997cft}.
 
-Модели Весса-Зумино-Виттена можно строить начиная со следующего действия:
+Модели Весса-Зумино-Новикова-Виттена можно строить начиная со следующего действия:
 \begin{equation}
@@
 \end{equation}
-Он определен на трехмерном многообразии $B$, ограниченном исходным двумерным пространством.
+Он определен на трехмерном многообразии $B$, ограниченном исходным двумерным пространством $S^{2}$.
 Через $\tilde{g}$ мы обозначили продолжение поля $g$ на $B$. Такое продолжение не единственно. В
@@
 контур в разных направлениях для голоморфной и антиголоморфной частей.
-Тогда вариация действия
+Тогда вариация действия примет вид
 \begin{equation}
@@
 \end{equation}
-Раскладывая токи
+Раскладывая токи по некоторому базису $t^{a}$ в алгебре Ли $\gf$
 \begin{equation}
@@
 \end{equation}
-Для токов из явного вида тока и формулы для преобразования $g$ имеем
+Из явного вида тока и формулы для преобразования $g$ имеем
 \begin{equation}
@@
 \end{equation}
-Если это подставить в тождество Уорда, то получаем операторное разложение для токов, которое имеет
-вид 
+Если это подставить в тождество Уорда, то получаем операторное разложение для токов:
 \begin{equation}
@@
   \label{eq:102}
-  T(z)=\frac{1}{2(k+h^v)}\sum_a N(J^a J^a)(z)
+  T(z)=\frac{1}{2(k+h^{\vee})}\sum_a :J^a J^a:(z)
 \end{equation}
-Здесь $h^v$ - дуальное число Кокстера. $h^v=\sum_i \alpha_i^v +1=\frac{1}{2}(\Theta,\Theta+2\rho)$,
+Здесь $h^{\vee}$ - дуальное число Кокстера. $h^{\vee}=\sum_i \alpha_i^{\vee} +1=\frac{1}{2}(\theta,\theta+2\rho)$,
 а нормальное упорядочение вводится следующим образом: 
@@
   \label{eq:12}
-  N(AB)(w)=\frac{1}{2\pi i}\oint\frac{dz}{z-w}A(z)B(w)
+  :AB:(w)=\frac{1}{2\pi i}\oint\frac{dz}{z-w}A(z)B(w)
 \end{equation}
@@
   \label{eq:91}
-  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:J^a_m J^a_{n-m}:
+  L_n=\frac{1}{2(k+h^{\vee})}\sum_a\sum_m:J^a_m J^a_{n-m}:
 \end{equation}
@@
     \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
-    c=\frac{k\;\mathrm{dim}g}{k+h^v}\\
+    c=\frac{k\;\mathrm{dim}g}{k+h^{\vee}}\\
     \left[L_n,J^a_m\right]=-mJ^a_{n+m}.
@@
 
-Примарными оказываются поля, которые преобразуются ковариантно под действием $G(z)\times G(\bar z)$,
+Примарными назваются поля, которые преобразуются ковариантно под действием $G(z)\times G(\bar z)$,
 как $g(z,\bar z)$. В терминах операторного разложения это свойство переформулируется следующим
@@
     \label{eq:94}
-    \phi_{\lambda}(0)=\left|\phi_{\lambda}\right>
+    \left|\phi_{\lambda}\right>=\lim_{z\to 0}\phi_{\lambda}(z)\left|0\right>
   \end{equation}
@@
   \label{eq:96}
-  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>
+  L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^{\vee})}\left|\phi_{\lambda}\right>
 \end{equation}
-Здесь использовано явное выражение для собственных значений квадратичного оператора Казимира.
+Здесь использовано явное выражение для собственных значений квадратичного оператора Казимира. То есть конформный вес примарного поля ВЗНВ-модели равен
+\begin{equation}
+  \label{eq:65}
+  h_{\lambda}=\frac{(\lambda,\lambda+2\rho)}{2(k+h^{\vee})}
+\end{equation}
 
@@
 голоморфный и антиголоморфный сектора.
+
+Уравнения Книжника-Замолодчикова
 
@@
 
-Конформная теория поля задаётся примарными полями $\Phi_a$ с конформными размерностями $\Delta_a$.
+Конформная теория поля задаётся примарными полями $\phi_a$ с конформными размерностями $h_a$.
 
@@
 
-Для WZW-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$. Тогда
+Для ВЗНВ-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$. Тогда
 \begin{equation}
@@
 Коэффициенты ветвления для вложения аффинной подалгебры Ли в аффинную алгебру можно использовать для
-построения модулярно-инвариантной статсуммы в соответствующей WZW-модели. Когда рассматривается
+построения модулярно-инвариантной статсуммы в соответствующей ВЗНВ-модели. Когда рассматривается
 теория на торе,  набор физически допустимых полей ограничен требованиями модулярной инвариантности.
@@
 Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует
-алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно. (Я сейчас поясню, что это
-значит).
+алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно.
 
-Представления алгебры можно рассматривать как сумму представлений подалгебры.
+Представления алгебры $\gf$ можно рассматривать как сумму представлений подалгебры $\af$.
 
@@
 и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится. То есть из
-диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый не диагональный инвариант для
+диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый недиагональный инвариант для
 подалгебры $\mathfrak{a}$. Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
@@
 \end{equation}
+Рассмотрим неприводимый модуль $L^{\mu}_{\gfh}$ как приводимый модуль подалгебры $\afh$: $L^{\mu}_{\gfh}=\bigoplus_{\nu}L^{\nu}_{\afh}$.
+В силу  равенства \eqref{eq:26} весовые векторы, соответствующие весам $L^{\mu}_{\gfh}$, сингулярным по отношению к действию $\afh$, будут образовывать модуль алгебры Вирасоро.
+Статсумма такой модели будет даваться функциями ветвления для вложения $\afh\to\gfh$ (См.
+раздел \ref{sec:coset-models} в главе \ref{cha:affine-lie-algebras}).
 
@@
 
+\section{Конформная теория поля на области с границей}
+\label{sec:boundary-cft}
+
+При изучении критических явлений большое применение находит формулировка конформной теории поля на области с границей.
+Это естественно как при описании реальных экспериментов, где система всегда имеет конечные размеры, так и при изучении критического поведения отдельных кластеров в решеточных моделях.
+Формулировка так называемой граничной конформной теории поля восходит к пионерским работам Карди \cite{cardy1984conformal,cardy1989boundary,cardy1986effect}.
+
 %%

### 2012-01-10 AffineLieAlgebras/Thesis/intro.tex
Misprints fixed

@@
 Аффинные алгебры Ли отличаются тем, что матрица Картана, задающая коммутационные соотношения, лишь положительно полуопределена.
-Оказывается, что такие алгебры могут быть реализованы как центральные расширения алгебр петель, связанных с полупростыми алгебрами Ли.
-Такая особенность структуры аффинных алгебр Ли привела к тому, что они приобрели особое значение в физике после появления в 1984 году конформной теории поля \cite{belavin1984ics}.
+Оказывается такие алгебры могут быть реализованы как центральные расширения алгебр петель, связанных с полупростыми алгебрами Ли.
+Эта особенность структуры аффинных алгебр Ли привела к тому, что они приобрели особое значение в физике после появления в 1984 году конформной теории поля \cite{belavin1984ics}.
 Ведь квантование теорий поля естественным образом приводит к центральным расширениям алгебр симметрии.
@@
 % Личный вклад автора
-\contribsection
-\contribtext
+%\contribsection
+%\contribtext
 

### 2012-01-12 AffineLieAlgebras/Thesis/4.tex
Misprints and labels

@@
 \begin{equation}
-  \label{eq:20}
+  \label{eq:120}
        d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}  
@@
   \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
-  \label{eq:1}
+  \label{eq:69}
 \end{equation}
@@
 Теперь нам нужно рассмотреть, как преобразуется конец следа эволюции Шрамма-Левнера  $\gamma_{t}$ при переходе от времени $t$ к $t+ dt$.
-Первый множитель в правой части уравнения  (\ref{eq:1}) дает нам
+Первый множитель в правой части уравнения  (\ref{eq:69}) дает нам
 \begin{equation*}
@@
 \begin{equation}
-  \label{eq:2}
+\label{eq:70}
   d\varphi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\varphi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\varphi_{\lambda_{i}}(w_{i}) 
@@
 \end{equation}
-Подставим формулу \eqref{eq:2} и получим уравнение
+Подставим формулу \eqref{eq:70} и получим уравнение
 \begin{equation}
@@
 Иногда предпочтительно использовать базис Шевалле или Картана-Вейля.
-Так что мы изменим условие нормировке дополнительного $\mathrm{dim}\gf$-мерного Броуновского движения \eqref{eq:5} на $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, и генератор преобразования поля  \eqref{eq:2} примет вид
+Так что мы изменим условие нормировке дополнительного $\mathrm{dim}\gf$-мерного Броуновского движения \eqref{eq:5} на $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, и генератор преобразования поля  \eqref{eq:70} примет вид
 \begin{equation*}

### 2012-01-12 AffineLieAlgebras/Thesis/review.tex
Misprints and labels

@@
 
-Уравнения Книжника-Замолодчикова
+Из тождества Уорда для токов \eqref{eq:87}, конструкции Сугавары \eqref{eq:102} и операторного разложения для тока и примарного поля \eqref{eq:84} нетрудно получить уравнение Книжника-Замолодчикова на корреляционные функции:
+\begin{equation}
+  \label{eq:66}
+  \left( \frac{\partial}{\partial z_i}+\sum_{j\neq i}^N \sum_a \frac{t^a_i t^a_j}{k+h^{\vee}}\frac{1}{z_i-z_j}\right) \lagle g (z_1,\bar z_1)\dots g(z_N,\bar z_N)\rangle
+\end{equation}
 
@@
 \begin{equation}
-  \label{eq:2}
+  \label{eq:71}
   Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
@@
 представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсумма на торе
-(\ref{eq:2}) может быть записана в виде
+(\ref{eq:71}) может быть записана в виде
 \begin{equation}
@@
 \begin{equation}
-  \label{eq:5} \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i
-\tau}
+  \label{eq:74}
+  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i\tau}
 \end{equation}
@@
 \begin{equation}
-  \label{eq:6} \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi}
+  \label{eq:76}\mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi}
 L_{\hat \lambda}\otimes L_{\hat \xi}
@@
 $\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$. В теории, связанной с  $\mathfrak{g}$
-с вакуумом $\left|\lambda\right>$ будут следующие состояния:
+с вакуумом $\left| 0\right>$, примарным полем $\phi_{\lambda}$ и состоянием старшего веса  $\left|\lambda\right>=\lim_{z\to 0} \phi_{\lambda}(z) \left|0\right>$ будут следующие состояния:
 \begin{equation}
@@
 энергии-импульса в общем случае это не так. Поэтому тензор энергии-импульса большей теории должен
-состоять только из генераторов $\tilde{J}$. Тогда $T_{\mathfrak{g}}=T_{\mathfrak{a}}\Rightarrow
-c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению
+состоять только из генераторов $\tilde{J}$. Тогда из $T_{\mathfrak{g}}=T_{\mathfrak{a}}$ следует $c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению
 \begin{equation}
   \label{eq:111}
-  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+a}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+h^{\vee}_{\gf}}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+h^{\vee}_{\af}}
 \end{equation}
@@
 
-Можно показать, что только для представлений уровня 1 это равенство удовлетворяется. То есть класс
+Можно показать, что это равенство удовлетворяется только для представлений уровня 1. То есть класс
 конформных вложений не слишком широк и существует полная их классификация. Кроме того, для
@@
 Существует теорема о том, что для конформного вложения  $\mathfrak{a}\subset\mathfrak{g}$ только
-конечное число коэффициентов ветвления отлично от нуля. Поэтому после того, как мы разложили все
+конечное число коэффициентов ветвления отлично от нуля \cite{kac1988modular,altschuler1990branching}. Поэтому после того, как мы разложили все
 представления $\mathfrak{g}$ мы подставляем результаты в выражение для статсуммы и получаем
@@
 \end{equation}
-Таким образом, редукция представлений аффинной алгебры на представления подалгебры, рассмотренная в главе \ref{cha:affine-lie-algebras}, приводит к построению модулярно-инвариантных статсумм методом конформных вложений.
+Таким образом, редукция представлений аффинной алгебры на представления подалгебры, рассмотренная в главе \ref{cha:affine-lie-algebras}, приводит к построению модулярно-инвариантных статсумм методом конформных вложений \cite{walton1989conformal}.
+Проблема конформных вложений также недавно рассматривалась в работе \cite{coquereaux2008conformal}.
+Мы приводим примеры таких вычислений в разделе \ref{sec:conformal-embeddings}.
 
@@
 \end{multline}
-Полученная теория поля обладает калибровочной инвариантностью и ее квантование естественно проводить с использованием БРСТ-формализма \cite{hwang1993brst}.
+Полученная теория поля обладает калибровочной $G\times G$-инвариантностью  и ее квантование естественно проводить с использованием БРСТ-формализма \cite{hwang1993brst}.
 
@@
 \begin{equation*}
-  \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{v}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
+  \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{\vee}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
 \end{equation*}
@@
   \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
-  \label{eq:6}
+  \label{eq:101}
 \end{equation}
+
+Из алгебраического определения coset-моделей следует, что функции ветвления для модулей аффинной алгебры $\gfh$ на модули подалгебры $\afh$ являются характерами конформных семейств.
+
+Все минимальные унитарные модели можно реализовать как coset-модели типа $\widehat{su(2)}_k/\widehat{u(1)}$ или $\widehat{su(2)_k\oplus su(2)_1}/\widehat{su(2)_{k+1}}$ (здесь нижний индекс указывает на уровень модулей старшего веса, соответствующих примарным полям).
 

### 2012-01-12 AffineLieAlgebras/Thesis/1.tex
First version sent to Vladimir Dmitrievich
Misprints and labels

@@
 
-Как было показано в разделе \ref{sec:modular-invariance}, проблема ветвления для аффинных алгебр Ли возникает в конформной теории поля, например, при построении модулярно-инвариантных статсумм  \cite{difrancesco1997cft}.
-Недавно проблема конформных вложений рассматривалась в работе \cite{coquereaux2008conformal}.
+В главе \ref{cha:CFT} мы показали, что для построения модулярно-инвариантных статсумм и в процессе изучения coset-моделей возникает проблема ветвления для аффинных алгебр Ли.
+В данной главе мы выводим рекуррентные соотношения на коэффициенты ветвления, которые являеются важнейшим инструментом данной диссертации.
+Эти соотношения получены нами в работе \cite{2010arXiv1007.0318L}.
 
@@
 секцию \ref{sec:algorithm}).
-В разделе \ref{sec:branching-examples} мы представляем различные примеры применения алгоритма для конечномерных \ref{sec:finite-dimens-lie} и аффинных алгебр Ли и обсуждаем их роль в моделях конформной теории поля \ref{sec:phys-appl}.
+В разделе \ref{sec:branching-examples} мы представляем различные примеры применения алгоритма для конечномерных (\ref{sec:finite-dimens-lie}) и аффинных алгебр Ли и обсуждаем их роль в моделях конформной теории поля (\ref{sec:phys-appl}).
 Выводы к главе изложены в разделе \ref{sec:conclusion}.
@@
 \label{sec:intro-simple-lie-algebras}
-
-{\it Алгебра Ли} $\gf$ -- это векторное пространство с билинейной операцией $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, которая называется  {\it скобкой Ли или коммутатором}.
-Если выбрать некоторый  $X_{i}$ в $\gf$, то коммутационные соотношения можно задать при помощи  {\it структурных констант} $C_{ijk}$:
+\begin{definition}
+{\it Алгебра Ли $\gf$} -- это векторное пространство с билинейной операцией $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, которая называется  {\it скобкой Ли или коммутатором}.
+Если выбрать некоторый базис  $X_{i}$ в $\gf$, то коммутационные соотношения можно задать при помощи  {\it структурных констант} $C_{ijk}$:
 \begin{equation}
@@
 
-Алгебра Ли называется {\it простой} если она не содержит нетривиальных идеалов относительно коммутатора.
-{\it Полупростая} алгебра Ли -- это прямая сумма простых алгебр Ли.
-В этой работе мы рассматриваем, в основном, простые и полупростые алгебры Ли.
+\end{definition}
+
+Алгебра Ли называется {\it простой} если она не содержит нетривиальных идеалов относительно коммутатора. {\it Полупростая} алгебра Ли -- это прямая сумма простых алгебр Ли.
 
@@
 \begin{definition}
+\label{def:1}
 Будем рассматривать алгебру Ли $\gf$ над полем $k=\mathbb{C},\mathbb{R}$.
@@
   \begin{multline}
-    \label{eq:1}
+    \label{eq:68}
     (dc) (X_{1},\dots, X_{n+1})=\sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} c([X_{s},X_{t}],X_{1},\dots,\hat X_{s},\dots,\hat X_{t},\dots X_{n+1})\\
@@
 \begin{equation}
-  \label{eq:2}
+  \label{eq:40}
   \dots\stackrel{d_{n}}{\longleftarrow} C^{n}(g;A)\stackrel{d_{n-1}}{\longleftarrow} C^{n-1}(\gf;A)\leftarrow \dots \leftarrow C^{1}(\gf;A) \stackrel{d_{0}}{\longleftarrow} C^{0}(\gf;A)\leftarrow 0
@@
   \begin{multline}
-    \label{eq:3}
+    \label{eq:98}
     \partial(a\otimes (X_{1}\wedge \dots \wedge X_{n})) =\\ \sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} a\otimes ([X_{s},X_{t}]\wedge X_{1} \wedge\dots\wedge\hat X_{s}\wedge \dots\wedge \hat X_{t}\wedge \dots\wedge X_{n+1})\\
@@
   \begin{equation}
-    \label{eq:4}
+    \label{eq:62}
     0\to k \to \tilde \gf\to \gf\to 0,
@@
 \end{definition}
-Заметим, что всякий 2-коцикл $c\in C^{2}(\gf;A)$ определяет центральное расширение $\gf$:
-\begin{equation}
-  \label{eq:5}
+Заметим, что всякий 2-коцикл $c\in C^{2}(\gf;A), \; dc=0$ определяет центральное расширение $\gf$:
+\begin{equation}
+  \label{eq:64}
   0\to k\stackrel{\lambda\to (0,\lambda)}{\longrightarrow}\tilde\gf=\gf\oplus k \stackrel{(X,\lambda)\to X}{\longrightarrow} \gf\to 0
@@
 \begin{equation}
-  \label{eq:6}
+  \label{eq:103}
   [(X,\lambda),(Y,\mu)]=([X,Y],c(X,Y))
 \end{equation}
-Тождество Якоби для такой скобки равносильно тому, что $c$-- 2-коцикл. Когомологичным коциклам отвечают эквивалентные расширения.
+Тождество Якоби для такой скобки равносильно тому, что $c$\; --- 2-коцикл. Когомологичным коциклам отвечают эквивалентные расширения.
 
@@
 \begin{equation}
-  \label{eq:7}
+  \label{eq:104}
   \begin{diagram}
@@
 
-Вернемся к алгебре Витта \eqref{eq:230}. Существует коцикл
-\begin{equation}
-  \label{eq:8}
+Для алгебры Витта \eqref{eq:2} существует коцикл
+\begin{equation}
+  \label{eq:105}
   c(l_{n},l_{m})=\frac{1}{12}(m^{3}-m)\delta_{-n,m}
@@
 \begin{eqnarray}
-  \label{eq:9}
+  \label{eq:106}
   [L_{n},c]=0\\
@@
 \begin{equation}
-  \label{eq:6}
+  \label{eq:108}
   [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
@@
 \begin{equation}
-  \label{eq:7}
+  \label{eq:112}
    [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
@@
 
-Пусть $\gf$ -- конечномерная или аффинная алгебра Ли.  $\gf$-модулем называется векторное пространство $V$ с билинейным отображением $\gf \times V\to V$, таким, что выполнено равенство
-\begin{equation}
-  \label{eq:2}
-  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
-\end{equation}
-Представление алгебры  $\gf$ на векторном пространстве $V$ называется гомоморфизм $\gf\to gl(V)$ из $\gf$ в алгебру Ли эндоморфизмов векторного пространства $V$, где скобка задана коммутатором.
+Пусть $\gf$ -- конечномерная или аффинная алгебра Ли. Мы ввели модули алгебры $\gf$ в определении \ref{def:1}. Широко используется альтернативный термин {\it представление}.
+
+%%    $\gf$-модулем называется векторное пространство $V$ с билинейным отображением $\gf \times V\to V$, таким, что выполнено равенство
+%%  \begin{equation}
+%%    \label{eq:2}
+%%    [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
+%%  \end{equation}
+\begin{definition}
+Представление алгебры  $\gf$ на векторном пространстве $V$ называется гомоморфизм $\gf\to gl(V)$ из $\gf$ в алгебру Ли эндоморфизмов векторного пространства $V$, где скобка задана коммутатором:
+\begin{equation}
+  \label{eq:113}
+  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{для}\; x,y\in \gf, v\in V  
+\end{equation}
+
+\end{definition}
 
@@
 \begin{equation}
-  \label{eq:3}
+  \label{eq:114}
   H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
@@
 \begin{equation}
-  \label{eq:5}
+  \label{eq:115}
   E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
@@
 \begin{equation}
-  \label{eq:10}
+  \label{eq:116}
   \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
@@
 \begin{align}
-  \label{eq:4}
+  \label{eq:63}
   &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
@@
 \begin{equation}
-  \label{eq:8}
+  \label{eq:117}
   s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
@@
 Рассмотрим действие элемента группы Вейля $s_{\alpha}s_{\alpha+\delta}$ аффинной алгебры Ли   $\hat\gf$, соответствующего простому корню  $\alpha$ конечномерной подалгебры Ли $\gf$.
-Из определения  \eqref{eq:8} легко видеть, что $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
+Из определения  \eqref{eq:117} легко видеть, что $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
 То есть группа Вейля для аффинной алгебры Ли может быть представлена как полупрямое произведение группы Вейля $W_{\gf}$ конечномерной подалгебры  $\gf$ и трансляций, соответствующих корням $\gf$.
@@
 Элемент группы Вейля можно представить как произведение простых отражений различными способами.
-Число простых отражений в кратчайшей последовательности, представляющей элемент$w\in W_{\gf}$ называется {\it длиной}  $w$ и обозначается $l(w)$.
+Число простых отражений в кратчайшей последовательности, представляющей элемент\; $w\in W_{\gf}$ называется {\it длиной}  $w$ и обозначается $l(w)$.
 Мы также используем обозначение $\epsilon(w)=(-1)^{l(w)}$ для четности числа отражений Вейля, порождающих $w$.
@@
 \begin{equation}
-  \label{eq:9}
+  \label{eq:118}
   A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}.
@@
 
-Форма, заданная матрицей Картана \eqref{eq:9} определяет базис, дуальный к базису простых корней.  Он называется  {\it базисом фундаментальных весов}. Мы обозначаем его элементы через $\omega_i$:
+Форма, заданная матрицей Картана \eqref{eq:118} определяет базис, дуальный к базису простых корней.  Он называется  {\it базисом фундаментальных весов}. Мы обозначаем его элементы через $\omega_i$:
 \begin{equation}
@@
 Для аффинной алгебры Ли есть дополнительный фундаментальный вес $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
-Другие фундаментальные веса равны $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, где $\co{\omega_i}$ -- это фундаментальные веса конечномерной подалгебры Ли $\gf$.
+Другие фундаментальные веса равны $\omega_i=a_i^{\vee} \omega_0 +\co{\omega_i}$, где $\co{\omega_i}$ -- это фундаментальные веса конечномерной подалгебры Ли $\gf$.
 
@@
 \begin{equation}
-  \label{eq:11}
+  \label{eq:122}
   \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
@@
 \begin{equation}
-  \label{eq:12}
-  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
-\end{equation}
-а $\epsilon \left( w\right) :=\det \left( w\right)$ равняется четности последовательности отражений Вейля, образующих $w$.
+  \label{eq:123}
+  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}.
+\end{equation}
+%% а $\epsilon \left( w\right) :=\det \left( w\right)$ равняется четности последовательности отражений Вейля, образующих $w$.
 
@@
 Неприводимые модули старшего веса не имеют нетривиальных подмодулей. 
-Формула Вейля для характеров неприводимых модулей старшего веса имеет вид
+Формула Вейля-Каца для характеров неприводимых модулей старшего веса имеет вид
 \begin{equation}
@@
 \af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
-}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\af}(\beta )}},  \label{eq:4} \\
+}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\af}(\beta )}},  \label{eq:124} \\
 \pi _{\af}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
@@
 
-Рассмотрим правую часть равенства (\ref{eq:4}).
+Рассмотрим правую часть равенства (\ref{eq:124}).
 Числитель описывает ветвление в терминах сингулярных элементов и, как элемент  $\mathcal{E}\left( \gf \right)$, допускает разложение в виде:
@@
 \begin{equation}
-%  \label{eq:20}
-  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}.
+  \label{eq:119}
+  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{для} \; \nu\in \bar{C}_{\mathfrak{a}}.
 \label{eq:21-1}
@@
 \begin{proof}
-Перепишем соотношение (\ref{eq:4}) для элемента $\frac{\Psi _{\gf}^{\mu }}{R_{\afb}}$ используя определение (\ref{eq:37})
+Перепишем соотношение (\ref{eq:124}) для элемента $\frac{\Psi _{\gf}^{\mu }}{R_{\afb}}$ используя определение (\ref{eq:37})
 для носителя $\Phi _{\af\subset \gf}$ ,
@@
 \subset \gf}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
-\af}.  \label{eq:17}
+\af}.  \label{eq:121}
 \end{equation}
@@
 В новом сингулярном элементе $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ кратности весов равны размерностям $\dim\left(L^{\mu _{\widetilde{\afb}}\left( u\right)}_{\left\{ \afb \right\}}\right)$ соответствующих  $\afb$-модулей, умноженным на значения $\epsilon (u)$.
-В результате старшие веса подмодулей $\af$ и их кратности удовлетворяют набору линейных соотношений (\ref{eq:17}).
+В результате старшие веса подмодулей $\af$ и их кратности удовлетворяют набору линейных соотношений (\ref{eq:121}).
 Эти свойства выполняются для любой редуктивной подалгебры $\af\rightarrow \gf$ и уравнения могут быть переписаны в виде рекуррентных соотношений, которые можно решать последовательно.

### 2012-01-12 AffineLieAlgebras/Thesis/3.tex
Mostly fighting with duplicate labels

@@
 \af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
-}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:4} \\
+}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:132} \\
 \frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\af%
@@
 \begin{equation}
-  \label{eq:4}
+  \label{eq:133}
   \mathrm{ch} L^{\mu}=\sum_{\nu\in P_{\af}} b^{\mu}_{\nu} \mathrm{ch} L^{\nu}_{\af},
@@
 \begin{equation}
-  \label{eq:9}
+  \label{eq:146}
 b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
@@
 \begin{multline}
-  \label{eq:5}
+  \label{eq:135}
   \eta(\tau)^{\mathrm{dim}(\af)}\prod_{\alpha\in\Delta_{1}^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z)}{\eta(\tau)} \eta(\tau)^{\mathrm{dim}(\sfr)}\prod_{\beta\in\Delta_{2}^{+}}\frac{\Theta^{(\hat A_{1})}_{\phi\circ \beta}(\tau,z))}{\eta(\tau)}=\\
@@
 \begin{equation}
-  \label{eq:6}
+  \label{eq:143}
   \left(\sum_{v\in W_{\af}}\epsilon(v) \Theta^{(\afh)}_{v\rho_{\af}}(\tau,z)\right)
@@
 \begin{equation}
-  \label{eq:7}
+  \label{eq:145}
    \sigma^{(\hat{\mu})}_{\nu}(q) = \sum_{\xi\in P} m^{(\xi)}_{\nu} b^{(\hat{\mu})}_{\xi}(q).
@@
 attribute to a weight $(\rho,\xi)$ its product $(\rho,\xi)$ with
-the Weyl vector $\rho$. Then relation \eqref{eq:7} can be written
+the Weyl vector $\rho$. Then relation \eqref{eq:145} can be written
 in the matrix form $\sigma(q)=M b(q)$ or as an inverse relation
@@
 We decompose $\gf$-modules in equation \eqref{eq:8} into
-$\af$-modules using property \eqref{eq:9}:
+$\af$-modules using property \eqref{eq:146}:
 \begin{multline}
-  \label{eq:10}
+  \label{eq:125}
   \mathrm{ch}L^{\hat{\mu}}_{\gfh}=

### 2012-01-12 AffineLieAlgebras/Thesis/4.tex
Mostly fighting with duplicate labels

@@
   \begin{equation}
-    \label{eq:87}
+    \label{eq:139}
     \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
@@
  \begin{equation}
-   \label{eq:3}
+   \label{eq:128}
    J^{a}(z)J^{b}(w)\sim \frac{k\delta_{ab}}{(z-w)^{2}}+\sum_{c}i f_{abc}\frac{J^{c}}{z-w},
@@
 
-Разложим токи на моды $J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n $, воспользуемся операторным разложением \eqref{eq:3} и получим коммутационные соотношения аффинной алгебры Ли $\gfh$:
+Разложим токи на моды $J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n $, воспользуемся операторным разложением \eqref{eq:128} и получим коммутационные соотношения аффинной алгебры Ли $\gfh$:
 \begin{equation*}
@@
 \begin{equation}
-  \label{eq:4}
+  \label{eq:134}
   L_n=\frac{1}{2(k+h^{\vee})}\left(\sum\limits_a\sum\limits_{m\leq -1}J^a_m J^a_{n-m}+\sum_{m\geq 0} J^{a}_{n-m}J^{a}_{m}\right), 
@@
   \begin{equation}
-    \label{eq:92}
+    \label{eq:141}
     \begin{aligned}
@@
 \end{eqnarray}
-Эти уравнения можно переписать как алгебраические соотношения, связывающие параметры случайного блуждания $\kappa, \tau$ с уровнем  $k$ представления аффинной алгебры Ли, если воспользоваться коммутационными соотношениями  \eqref{eq:92}.
+Эти уравнения можно переписать как алгебраические соотношения, связывающие параметры случайного блуждания $\kappa, \tau$ с уровнем  $k$ представления аффинной алгебры Ли, если воспользоваться коммутационными соотношениями  \eqref{eq:141}.
 Строгий анализ полученных алгебраических соотношений проведен в работе \cite{alekseev2010sle}.
@@
   \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
-  \label{eq:6}
+  \label{eq:144}
 \end{equation}
@@
   \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}\left(d \theta ^{a} t^{a}_{i}\right)\right)
-\label{eq:5}
+\label{eq:136}
 \end{equation}
@@
   \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0,
-\label{eq:9}
+\label{eq:147}
 \end{equation}
@@
   \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}J^{a}_{-1}J^{a}_{-1}\right)\right) \phi_{(\mu,\nu)}
-\label{eq:10}
+\label{eq:126}
 \end{equation}
@@
 
-Уравнение \eqref{eq:10} теперь имеет вид
+Уравнение \eqref{eq:126} теперь имеет вид
 \begin{equation}
-  \label{eq:11}
+  \label{eq:138}
   \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
@@
  \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{(\mu,\nu)},
-\label{eq:12}
+\label{eq:140}
 \end{equation}
@@
 
-Найдем решения уравнения  \eqref{eq:11}. Подействуем на  $\psi$ оператором $L_{2}$:
+Найдем решения уравнения  \eqref{eq:138}. Подействуем на  $\psi$ оператором $L_{2}$:
 \begin{equation}
@@
 Иногда предпочтительно использовать базис Шевалле или Картана-Вейля.
-Так что мы изменим условие нормировке дополнительного $\mathrm{dim}\gf$-мерного Броуновского движения \eqref{eq:5} на $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, и генератор преобразования поля  \eqref{eq:70} примет вид
+Так что мы изменим условие нормировке дополнительного $\mathrm{dim}\gf$-мерного Броуновского движения \eqref{eq:136} на $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, и генератор преобразования поля  \eqref{eq:70} примет вид
 \begin{equation*}
@@
   \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\mu,\nu)}
-\label{eq:30}
+\label{eq:131}
 \end{equation}
@@
 
-Действуя на уравнение \eqref{eq:30} операторами  $L_{2}$ и $L_{1}^{2}$ мы можем получить уравнения \eqref{eq:28} и \eqref{eq:17}.
+Действуя на уравнение \eqref{eq:131} операторами  $L_{2}$ и $L_{1}^{2}$ мы можем получить уравнения \eqref{eq:28} и \eqref{eq:17}.
 Чтобы получить дополнительные уравнения мы можем подействовать генераторами  $\tilde{J}^{b}_{1}$ алгебры $\afh$ и оператором $L_{1}$, аналогично том, как мы делали с оператором  $J^{3}_{1}$ при выводе уравнения \eqref{eq:29}.
 
-Чтобы упростить соотношения можно использовать обобщение уравнений Книжника-Замолодчикова \eqref{eq:6}, как было сделано для ВЗНВ-моделей в статье \cite{alekseev2010sle}.
+Чтобы упростить соотношения можно использовать обобщение уравнений Книжника-Замолодчикова \eqref{eq:144}, как было сделано для ВЗНВ-моделей в статье \cite{alekseev2010sle}.
 

### 2012-01-12 AffineLieAlgebras/Thesis/review.tex
Mostly fighting with duplicate labels

@@
 \end{equation}
-При квантовании возникает конформная аномалия, что соответствует центральному расширению \eqref{eq:9} алгебры  (то
+При квантовании возникает конформная аномалия, что соответствует центральному расширению \eqref{eq:62} алгебры  (то
 есть появлению центрального заряда $c$). В коммутационные соотношения надо добавить член
@@
   \label{eq:66}
-  \left( \frac{\partial}{\partial z_i}+\sum_{j\neq i}^N \sum_a \frac{t^a_i t^a_j}{k+h^{\vee}}\frac{1}{z_i-z_j}\right) \lagle g (z_1,\bar z_1)\dots g(z_N,\bar z_N)\rangle
+  \left( \frac{\partial}{\partial z_i}+\sum_{j\neq i}^N \sum_a \frac{t^a_i t^a_j}{k+h^{\vee}}\frac{1}{z_i-z_j}\right) \langle g (z_1,\bar z_1)\dots g(z_N,\bar z_N)\rangle
 \end{equation}
@@
 \begin{equation}
-  \label{eq:100} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+  \label{eq:137} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
 \end{equation}

### 2012-01-13 AffineLieAlgebras/Thesis/1.tex
Mostly fighting with duplicate labels
Duplicate labels

@@
 %%  \begin{equation}
-%%    \label{eq:2}
+%%    \label{eq:130}
 %%    [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
@@
 }(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
-)e^{-\gamma }  \label{eq:6}
+)e^{-\gamma }  \label{eq:142}
 \end{equation}
@@
   b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{для} \; \nu\in \bar{C}_{\mathfrak{a}}.
-\label{eq:21-1}
 \end{equation}
@@
 \item Построить множество $\Gamma _{\af\rightarrow \gf}$.
-Соотношение  (\ref{eq:6}) определяет знаковую функцию $s(\gamma)$ и множество $\Phi_{\af\subset \gf}$.
+Соотношение  (\ref{eq:142}) определяет знаковую функцию $s(\gamma)$ и множество $\Phi_{\af\subset \gf}$.
 Вычитание наименьшего веса $\gamma_0$ дает веер вложения (\ref{fan-defined}):
@@
 \begin{equation*}
-  \label{eq:26}
+  \label{eq:155}
  S_{B_2}=\{e_3-e_4,e_4\}.
@@
 \begin{equation}
-  \label{eq:34}
+  \label{eq:148}
    Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
@@
 Недиагональные модулярные инварианты этой модели могут быть построены из диагонального инварианта, если существует аффинная алгебра  $\mathfrak{g}$, такая, что $\af\subset\mathfrak{g}$.
-Тогда мы можем заменить характеры  $\mathfrak{g}$-модулей в диагональной модулярно-инвариантной статсумме (\ref{eq:34}) на разложения
+Тогда мы можем заменить характеры  $\mathfrak{g}$-модулей в диагональной модулярно-инвариантной статсумме (\ref{eq:148}) на разложения
 \begin{equation*}
@@
 \begin{equation}
-  \label{eq:36}
+  \label{eq:154}
    Z_{\af}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\af}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau).
@@
 \begin{equation*}
-  \label{eq:109}
+  \label{eq:151}
   X^{\alpha_1}_{-n_1}X^{\alpha_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
@@
 \begin{equation*}
-  \label{eq:110}
+  \label{eq:152}
   \tilde{X}^{\alpha'_1}_{-n_1}\tilde{X}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\af}(\lambda)\right>.
@@
 \begin{equation}
-  \label{eq:2}
+  \label{eq:127}
   T_{\mathfrak{g}}(z)=T_{\af}(z)
@@
 \begin{equation}
-  \label{eq:111}
+  \label{eq:153}
   \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\af}{x_ek+a}.
@@
 
-Можно показать, что решения уравнения (\ref{eq:111}) существуют только для уровня $k=1$ \cite{difrancesco1997cft}.
+Можно показать, что решения уравнения (\ref{eq:153}) существуют только для уровня $k=1$ \cite{difrancesco1997cft}.
 
@@
 
-Если рассмотреть соотношение (\ref{eq:111}) и асимптотику функций ветвления, то можно доказать теорему о конечной приводимости \cite{kac1988modular}.
+Если рассмотреть соотношение (\ref{eq:153}) и асимптотику функций ветвления, то можно доказать теорему о конечной приводимости \cite{kac1988modular}.
 Она утверждает, что для конформного вложения  $\af\longrightarrow\mathfrak{g}$ лишь конечное число коэффициентов ветвления отлично от нуля.
@@
 \end{equation*}
-При конформном вложении тензоры энергии-импульса  $T_{\mathfrak{g}}(z)$ и $T_{\af}(z)$ равны (см. (\ref{eq:2})).
+При конформном вложении тензоры энергии-импульса  $T_{\mathfrak{g}}(z)$ и $T_{\af}(z)$ равны (см. (\ref{eq:127})).
 

### 2012-01-13 AffineLieAlgebras/Thesis/4.tex
Duplicate labels

@@
       \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}=0
-\label{eq:8}
+\label{eq:150}
 \end{equation}
@@
   \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)
-\label{eq:18}
+\label{eq:159}
 \end{equation}
@@
 
-Воспользуемся формулой \eqref{eq:8} и получим следующее уравнение из условий для мартингала:
+Воспользуемся формулой \eqref{eq:150} и получим следующее уравнение из условий для мартингала:
 \begin{equation}
@@
 \begin{equation}
-  \label{eq:26}
+  \label{eq:156}
   \left[L_{n},\tilde{J}^{b}_{m}\right]=0
@@
 \end{equation}
-Подставляя это выражение в уравнение \eqref{eq:8} мы получаем условие мартингала
+Подставляя это выражение в уравнение \eqref{eq:150} мы получаем условие мартингала
 \begin{equation}
@@
 \begin{equation}
-  \label{eq:14}
+  \label{eq:160}
   c=\frac{2(k-1)}{k+2}
@@
 \begin{equation}
-  \label{eq:13}
+  \label{eq:158}
   L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{(\mu,\nu)}=0,
@@
 \begin{equation}
-  \label{eq:15}
+  \label{eq:161}
   L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{(\mu,\nu)}=0
@@
 \begin{equation}
-  \label{eq:17}
+  \label{eq:157}
   12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) +  \tau (C_{\mu}-\tilde{C}_{\nu})=0,
@@
 У нас есть три неэквивалентных поля, нумерующихся парами весов $su(2)$ и $u(1)$: $\phi_{(0,0)}, \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$.
-Уравнение \eqref{eq:29} тривиально для  $\phi_{(0,0)}$ и  $\phi_{(0,2)}$, так что уравнения  \eqref{eq:17}, \eqref{eq:28} непротиворечивы,  однако мы не знаем, как интерпретировать параметр  $\tau$ в контексте модели Изинга.
+Уравнение \eqref{eq:29} тривиально для  $\phi_{(0,0)}$ и  $\phi_{(0,2)}$, так что уравнения  \eqref{eq:157}, \eqref{eq:28} непротиворечивы,  однако мы не знаем, как интерпретировать параметр  $\tau$ в контексте модели Изинга.
 Для поля  $\phi_{(1,1)}$ не существует решений уравнений на  $\kappa,\tau$, так что не каждое примарное поле соответствует оператору смены граничного условия.
@@
 \end{equation*}
-Условие мартингала  \eqref{eq:8} запишется в виде
+Условие мартингала  \eqref{eq:150} запишется в виде
 \begin{equation*}
@@
 
-Действуя на уравнение \eqref{eq:131} операторами  $L_{2}$ и $L_{1}^{2}$ мы можем получить уравнения \eqref{eq:28} и \eqref{eq:17}.
+Действуя на уравнение \eqref{eq:131} операторами  $L_{2}$ и $L_{1}^{2}$ мы можем получить уравнения \eqref{eq:28} и \eqref{eq:157}.
 Чтобы получить дополнительные уравнения мы можем подействовать генераторами  $\tilde{J}^{b}_{1}$ алгебры $\afh$ и оператором $L_{1}$, аналогично том, как мы делали с оператором  $J^{3}_{1}$ при выводе уравнения \eqref{eq:29}.
@@
 Описание полей в coset-моделях нетривиально ввиду идентификации полей \cite{schellekens1990field} и необходимости в разрешении фиксированных точек \cite{Fuchs:1996dd,fuchs1996resolution}, которое не обсуждалась в данной главе.
-Эти тонкости могут усложнить решение уравнений  \eqref{eq:28}, \eqref{eq:17} и аналогов уравнения \eqref{eq:29}.
+Эти тонкости могут усложнить решение уравнений  \eqref{eq:28}, \eqref{eq:157} и аналогов уравнения \eqref{eq:29}.
 С другой стороны, использование уравнений Книжника-Замолодчикова  \cite{kogan1997knizhnik} для корреляционных функций в духе работы \cite{alekseev2010sle} приводит к матричным алгебраическим соотношениям, которые напоминают NIM-представления для граничных состояний \cite{ishikawa2003novel}.

### 2012-01-13 AffineLieAlgebras/Thesis/2.tex
Mostly fighting with duplicate labels
Duplicate labels

@@
 }^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
-\label{branching1}
+\label{branching12}
 \end{equation}
@@
 U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
-\overline{C_{\frak{a}_{\perp }}}\right\} \quad .  \label{U-def}
+\overline{C_{\frak{a}_{\perp }}}\right\} \quad .  \label{U-def1}
 \end{equation}
@@
 ^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
-\label{Weyl-Kac2}
+\label{Weyl-Kac21}
 \end{equation}
 То же верно и для подмодулей $\mathrm{ch}\left( L_{\frak{a}}^{\nu
-}\right) $ в формуле (\ref{branching1})
+}\right) $ в формуле (\ref{branching12})
 \begin{equation*}
@@
 \end{equation*}
-Применяя формулу  (\ref{Weyl-Kac2}) к правилу ветвления  (\ref{branching1}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu
+Применяя формулу  (\ref{Weyl-Kac21}) к правилу ветвления  (\ref{branching12}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu
 \right) }$ и $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
@@
 \frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
-mult}_{\frak{a}}(\beta )}},  \notag  \label{eq:4} \\
+mult}_{\frak{a}}(\beta )}},  \notag  \label{eq:132} \\
 \pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
@@
 Тогда элемент  $\Psi ^{\left( \mu \right) }$ может быть разложен в сумму по  $u\in U$ (см.
-(\ref{U-def})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
+(\ref{U-def1})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
 $\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
@@
 }}\left( u\right) $ и $\mathcal{D}_{\frak{a}_{\perp }}$ заданы как в Лемме \ref{Psi-decomp-lemma}, $%
-u\in U$ определено формулой (\ref{U-def}). В результате получим элементы фильтрующей последовательности (\ref{resolution sequence}).
+u\in U$ определено формулой (\ref{U-def1}). В результате получим элементы фильтрующей последовательности (\ref{resolution sequence}).
 

### 2012-01-13 AffineLieAlgebras/Thesis/3.tex
Duplicate labels

@@
 }^{+}}b_{\nu }^{(\mu )}ch\left( L_{\af}^{\nu }\right) .
-\label{branching1}
+\label{branching13}
 \end{equation}
@@
 ^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
-\label{Weyl-Kac2}
+\label{Weyl-Kac22}
 \end{equation}
-Это же верно и для подмодулей $\mathrm{ch}\left( L_{\af}^{\nu}\right) $ в уравнении (\ref{branching1})
+Это же верно и для подмодулей $\mathrm{ch}\left( L_{\af}^{\nu}\right) $ в уравнении (\ref{branching13})
 \[
@@
 
-Применяя формулу (\ref{Weyl-Kac2}) к правилам ветвления (\ref{branching1}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu\right) }$ и $\Psi _{\af}^{\left( \nu \right) }$ :
+Применяя формулу (\ref{Weyl-Kac22}) к правилам ветвления (\ref{branching13}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu\right) }$ и $\Psi _{\af}^{\left( \nu \right) }$ :
 \begin{eqnarray}
@@
 \begin{equation}
-  \label{eq:8}
+  \label{eq:149}
 \mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{\nu}(n) \mathrm{ch} L^{\nu}_{\gf}.
@@
 $\Delta^{+}_{\gf}=\Delta^{+}_{\af}\cup \phi(\Delta^{+}_{\sfr})$.
-We decompose $\gf$-modules in equation \eqref{eq:8} into
+We decompose $\gf$-modules in equation \eqref{eq:149} into
 $\af$-modules using property \eqref{eq:146}:

### 2012-01-14 AffineLieAlgebras/Thesis/4.tex
Equation numbering fixed (no duplicates)

@@
 Основная задача данной главы состоит в обобщении эволюции Шрамма-Левнера с дополнительным случайным блужданием на группе Ли на случай фактор-пространства  $G/A$ и в изучении связи с coset-конструкцией конформной теории поля.
-В разделе \ref{sec:coset-models} мы напоминаем некоторые детали coset-конструкции, вводим эволюцию Шрамма-Левнера на фактор-пространстве и связываем ее с конформной теорией поля.
+В разделе \ref{sec:coset-models-sle} мы напоминаем некоторые детали coset-конструкции, вводим эволюцию Шрамма-Левнера на фактор-пространстве и связываем ее с конформной теорией поля.
 По аналогии со случаем моделей Весса-Зумино-Новикова-Виттена мы получаем систему алгебраических уравнений на оператор смены граничного условия из условия на мартингал.
@@
 \begin{equation}
-\label{eq:19}
+\label{eq:166}
   \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
@@
 
-Стохастический процесс, который удовлетворяет уравнению \eqref{eq:19} называется {\it эволюцией Шрамма-Левнера} на верхней полуплоскости $\mathbb{H}$.
-Для нас будет удобнее использовать отображение $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, так что уравнение \eqref{eq:19} переписывается в виде
+Стохастический процесс, который удовлетворяет уравнению \eqref{eq:166} называется {\it эволюцией Шрамма-Левнера} на верхней полуплоскости $\mathbb{H}$.
+Для нас будет удобнее использовать отображение $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, так что уравнение \eqref{eq:166} переписывается в виде
 \begin{equation}
@@
 %% \mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
-\label{eq:21}
+\label{eq:162}
 \end{equation}
@@
 %% Here $\phi(z_{t})$ is a primary field corresponding to boundary condition changing operator.
-%% We've used the conformal map $g_{t}$ to get the expression on the whole plane in equation \eqref{eq:21}.
+%% We've used the conformal map $g_{t}$ to get the expression on the whole plane in equation \eqref{eq:162}.
 Мы рассматриваем теорию с границей, так что мы должны использовать модели граничной конформной теории поля и накладывать соответствующие граничные условия \cite{cardy1984conformal,cardy1989boundary,cardy1991bulk}.
@@
 Кроме того, у нас есть операторы смены граничного условия   $\phi$ на конце следа эволюции Шрамма-Левнера и на бесконечности.
-Воспользуемся конформным отображением   $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$, чтобы переписать выражение \eqref{eq:21} на верхней полуплоскости без разреза:
+Воспользуемся конформным отображением   $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$, чтобы переписать выражение \eqref{eq:162} на верхней полуплоскости без разреза:
 \begin{equation}
@@
   \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=    \mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t+dt}}\right], \quad d\mathbb{E}\left[ \prec\mathcal{O}\succ_{\gamma_{t}}\right]=0
-\label{eq:22}
+\label{eq:163}
 \end{equation}
@@
   \left( \sum_{i}\left[-\frac{2h_{i}}{w_{i}^{2}} +\frac{2}{w_{i}}\partial_{w_{i}}\right]+\frac{\kappa}{2}\sum_{i,j}\partial_{w_{i}} \partial_{w_{j}}\right)\mathcal{F}(\left\{z_{i}\right\})=0
-\label{eq:23}
+\label{eq:165}
 \end{equation}
@@
 \end{equation*}
-(См. \cite{difrancesco1997cft}). То есть мы можем переписать дифференциальное уравнение \eqref{eq:23} как алгебраическое уравнение на поле $\phi$, соответствующее оператору смены граничных условий:
+(См. \cite{difrancesco1997cft}). То есть мы можем переписать дифференциальное уравнение \eqref{eq:165} как алгебраическое уравнение на поле $\phi$, соответствующее оператору смены граничных условий:
 \begin{equation}
-  \label{eq:24}
+  \label{eq:168}
    \left<\left([L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi\right)(0)\; \varphi_{\lambda_{1}}\dots \varphi_{\lambda_{{2N}}}\right>=0.
@@
 \cite{belavin1984ics}, \cite{difrancesco1997cft}. 
-Равенство \eqref{eq:24} верно для произвольной наблюдаемой $\mathcal{O}$ и для произвольных примарных поле $\varphi_{\lambda_{i}}$, так что $\psi=[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ -- нулевое поле уровня два и $\psi(0)\left|0\right>$ -- нулевое состояние уровня два.
+Равенство \eqref{eq:168} верно для произвольной наблюдаемой $\mathcal{O}$ и для произвольных примарных поле $\varphi_{\lambda_{i}}$, так что $\psi=[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ -- нулевое поле уровня два и $\psi(0)\left|0\right>$ -- нулевое состояние уровня два.
 В минимальных унитарных моделях существует только два примарных поля, порождающих модули Верма алгебры Вирасоро с нулевыми состояниями на уровне два.
@@
 \begin{equation}
-  \label{eq:25}
+  \label{eq:164}
   c=\frac{k\;\mathrm{dim}\gf}{k+h^{\vee}}
@@
   \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0,
-  \label{eq:27}
+  \label{eq:167}
 \end{equation}
@@
 \section{Coset-модели}
-\label{sec:coset-models}
+\label{sec:coset-models-sle}
 Теперь мы обобщим анализ соответствия между эволюцией Шрамма-Левнера и конформной теорией поля на случай coset-моделей \cite{Goddard198588}.
@@
 \begin{equation}
-  \label{eq:28}
+  \label{eq:169}
   (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
@@
 \begin{equation}
-  \label{eq:29}
+  \label{eq:170}
   \left(-6  + \kappa +  \tau +  2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0} \phi_{(\mu,\nu)}=0
@@
 У нас есть три неэквивалентных поля, нумерующихся парами весов $su(2)$ и $u(1)$: $\phi_{(0,0)}, \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$.
-Уравнение \eqref{eq:29} тривиально для  $\phi_{(0,0)}$ и  $\phi_{(0,2)}$, так что уравнения  \eqref{eq:157}, \eqref{eq:28} непротиворечивы,  однако мы не знаем, как интерпретировать параметр  $\tau$ в контексте модели Изинга.
+Уравнение \eqref{eq:170} тривиально для  $\phi_{(0,0)}$ и  $\phi_{(0,2)}$, так что уравнения  \eqref{eq:157}, \eqref{eq:169} непротиворечивы,  однако мы не знаем, как интерпретировать параметр  $\tau$ в контексте модели Изинга.
 Для поля  $\phi_{(1,1)}$ не существует решений уравнений на  $\kappa,\tau$, так что не каждое примарное поле соответствует оператору смены граничного условия.
@@
 
-Действуя на уравнение \eqref{eq:131} операторами  $L_{2}$ и $L_{1}^{2}$ мы можем получить уравнения \eqref{eq:28} и \eqref{eq:157}.
-Чтобы получить дополнительные уравнения мы можем подействовать генераторами  $\tilde{J}^{b}_{1}$ алгебры $\afh$ и оператором $L_{1}$, аналогично том, как мы делали с оператором  $J^{3}_{1}$ при выводе уравнения \eqref{eq:29}.
+Действуя на уравнение \eqref{eq:131} операторами  $L_{2}$ и $L_{1}^{2}$ мы можем получить уравнения \eqref{eq:169} и \eqref{eq:157}.
+Чтобы получить дополнительные уравнения мы можем подействовать генераторами  $\tilde{J}^{b}_{1}$ алгебры $\afh$ и оператором $L_{1}$, аналогично том, как мы делали с оператором  $J^{3}_{1}$ при выводе уравнения \eqref{eq:170}.
 
@@
 Описание полей в coset-моделях нетривиально ввиду идентификации полей \cite{schellekens1990field} и необходимости в разрешении фиксированных точек \cite{Fuchs:1996dd,fuchs1996resolution}, которое не обсуждалась в данной главе.
-Эти тонкости могут усложнить решение уравнений  \eqref{eq:28}, \eqref{eq:157} и аналогов уравнения \eqref{eq:29}.
+Эти тонкости могут усложнить решение уравнений  \eqref{eq:169}, \eqref{eq:157} и аналогов уравнения \eqref{eq:170}.
 С другой стороны, использование уравнений Книжника-Замолодчикова  \cite{kogan1997knizhnik} для корреляционных функций в духе работы \cite{alekseev2010sle} приводит к матричным алгебраическим соотношениям, которые напоминают NIM-представления для граничных состояний \cite{ishikawa2003novel}.

### 2012-01-14 AffineLieAlgebras/Thesis/3.tex
Equation numbering fixed (no duplicates)

@@
 \af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
-}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:132} \\
+}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:171} \\
 \frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\af%
 }^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\af}^{\left( \nu \right) }}{R_{%
-\af}}.  \label{singular main}
+\af}}.  \label{singular-main}
 \end{eqnarray}
@@
 \end{array}
-\label{recurrent rel}
+\label{recurrent-rel}
 \end{equation}
@@
 h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
-\label{delta a ort}
+\label{delta-a-ort}
 \end{eqnarray}
@@
 \end{eqnarray}
-и $\pi$ -- оператор проекции. Если вложение максимально, то оператор проекции становится тривиальным и соотношение (\ref{recurrent rel}) упрощается:
+и $\pi$ -- оператор проекции. Если вложение максимально, то оператор проекции становится тривиальным и соотношение (\ref{recurrent-rel}) упрощается:
 \begin{equation}
@@
 
-Вернемся к соотношению  (\ref{singular main}) и домножим обе стороны на  $R_{\af}$:
+Вернемся к соотношению  (\ref{singular-main}) и домножим обе стороны на  $R_{\af}$:
 \begin{equation}
@@
 _{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product
-$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}$
+$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint-product}$
 and it defines an injection fan $\Gamma _{\frak{a}%
@@
 same Dynkin numbers: $\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
-m_{k}\omega_{(\sfr) k} . \label{new h weight}$ So branching coefficients coincide with weight
+m_{k}\omega_{(\sfr) k} . \label{new-h-weight}$ So branching coefficients coincide with weight
 multiplicities of $\sfr$-modules.
@@
 \subsection*{Conclusion}
-\label{sec:conclusion} We have demonstrated that splint in affine
+\label{sec:conclusion-four} We have demonstrated that splint in affine
 Lie algebras leads to new relations between theta-functions and

### 2012-01-14 AffineLieAlgebras/Thesis/5.tex
Equation numbering fixed (no duplicates)

@@
 Необходимые сведения из теории представлений приведены в главе \ref{cha:affine-lie-algebras}.
-Здесь мы начинаем с описания структур данных пакета  {\bf Affine.m}, использующихся для описания различных объектов теории представлений  (раздел \ref{sec:core-datastructures}), обсуждаем алгоритмы  (раздел \ref{sec:comp-algor}) и приводим примеры  (раздел \ref{sec:examples}).
+Здесь мы начинаем с описания структур данных пакета  {\bf Affine.m}, использующихся для описания различных объектов теории представлений  (раздел \ref{sec:core-datastructures}), обсуждаем алгоритмы  (раздел \ref{sec:comp-algor}) и приводим примеры  (раздел \ref{sec:examples-six}).
 
@@
 \section{Примеры}
-\label{sec:examples}
+\label{sec:examples-six}
 В этом разделе мы приводим примеры вычислений, проведенных с использованием {\bf Affine.m} и код, который для этого потребовался.

### 2012-01-14 AffineLieAlgebras/Thesis/4.tex
Misprints, translation of section on affine splints, reorganization of last chapter

@@
-%\chapter{Практические приложения}
-%\label{cha:applications}
+\chapter{Практические приложения}
+\label{cha:applications}
 
-\chapter{Эволюция Шрамма-Левнера и алгебраические свойства предельного перехода от решеточных моделей к конформной теории поля}
+В этой главе мы рассматриваем роль сингулярных элементов модулей аффинных алгебр Ли в приложениях к задачам конформной теории поля.
+Мы используем установленные в главах \ref{cha:affine-lie-algebras}, \ref{cha:BGG}, \ref{cha:splints} свойства для эффективных вычислений.
+
+\section{Роль сингулярных элементов coset-моделей в установлении соответствия между конформной теорией поля и критическим поведением в решеточных моделях}
+
+% и  Эволюция Шрамма-Левнера и алгебраические свойства предельного перехода от решеточных моделей к конформной теории поля}
 \label{sec:SLE}
+
+Алгебраические методы в конформной теории поля позволяют получать явные уравнения на корреляционные функции (например, уравнения Книжника-Замолодчикова \eqref{eq:66} в ВЗНВ-моделях и их аналоги в coset-моделях \eqref{eq:101}).
+Во многих случаях эти уравнения можно решить аналитически либо численно и получить конкретные значения для физических величин, например, для критических индексов.
+Таким образом конформная теория поля является мощным инструментом для описания критического поведения в решеточных моделях.
+
+Однако соответствие между решеточными моделями и конформной теорией поля, описывающей их критическое поведение, не так легко установить.
+В случае простых моделей (Изинга, Поттса, Ашкина-Теллера и т.д.) и минимальных моделей конформной теории поля такое соответствие первоначально устанавливалось путем сравнения центральных зарядов и конформных размерностей.
+Но соответствие корреляторов нуждается в строгом доказательстве.
+Один из инструментов изучения решеточных моделей -- эволюция Шрамма-Левнера -- позволяет в некоторых случаях доказать такое соответствие (см.
+\cite{duminil2011conformal,chelkak2009universality,smirnov2007towards,smirnov2001critical,Cardy:2005kh,bauer2004conformal,bauer2004sle,bauer2004cfts,bauer2003sle,friedrich2003conformal,bauer2002sle}).
+Класс моделей конформной теории поля, для которых получены такие результаты, в основном ограничивается минимальными унитарными моделями.
+
+Введение дополнительного случайного блуждания на группе позволяет построить стохастический аналоги для ВЗНВ-моделей \cite{bettelheim2005stochastic,Rasmussen:2004xr,alekseev2010sle}.
+В данном разделе мы обсуждаем обобщение этой конструкции на случай coset-моделей.
+В установлении соответствия между корреляторами в стохастических моделях и моделях конформной теории поля существенную роль играют сингулярные элементы, что связано со структурой модулей алгебры Вирасоро в ВЗНВ и coset-моделях (см.
+разделы \ref{sec:WZNW-models}\ref{sec:coset-models-cft}).
+К сожалению, пока не известно, пределами каких решеточных моделей могут являться такие стохастические конструкции.
 
@@
 
-\section{Введение}
+\subsection{Введение}
 Эволюция Шрамма-Левнера -- это стохастический процесс, который предложил Oded Schramm  \cite{schramm2000scaling} для описания скейлингового предела критических интерфейсов в двумерных статистических решеточных моделях.
@@
 Более общие модели конформной теории поля обладают дополнительными симметриями.
-Например, алгебры Каца-Муди возникают в моделях Весса-Зумино-Новикова-Виттена.
+Например,  в моделях Весса-Зумино-Новикова-Виттена возникают аффинные алгебры Ли.
 Чтобы реализовать такие симметрии при изучении эволюции Шрамма-Левнера нужно ввести дополнительное случайное блуждание на группе Ли \cite{bettelheim2005stochastic}, \cite{Rasmussen:2004xr}.
@@
 
-\section{Модели Весса-Зумино-Новикова-Виттена и эволюция Шрамма-Левнера}
+\subsection{Модели Весса-Зумино-Новикова-Виттена и эволюция Шрамма-Левнера}
 \label{sec:sle-wzw-models}
@@
 
-\section{Coset-модели}
+\subsection{Coset-модели и эволюция Шрамма-Левнера}
 \label{sec:coset-models-sle}
@@
 
-\section{Выводы к пятой главе}
+\subsection{О связи мартингалов coset-моделей с классификацией операторов смены граничного условия}
 \label{sec:5-conclusion}

### 2012-01-14 AffineLieAlgebras/Thesis/1.tex
Misprints, translation of section on affine splints, reorganization of last chapter

@@
 
-В формуле Вейля-Каца и числитель, и знаменатель могут рассматриваться как формальные элементы, содержащие сингулярные веса модулей Верма $V^{\xi}$ со старшими весами  $\xi=\mu$ и $\xi=0$ \cite{humphreys1997introduction}.
+В формуле Вейля-Каца \eqref{eq:13} и числитель, и знаменатель могут рассматриваться как формальные элементы, содержащие сингулярные веса модулей Верма $V^{\xi}$ со старшими весами  $\xi=\mu$ и $\xi=0$ \cite{humphreys1997introduction}.
 Мы связываем сингулярные элементы с соответствующими интегрируемыми модулями  $L^{\mu }$ и $L_{\af}^{\nu }$:
@@
 \end{eqnarray}
-Здесь $\Delta _{\af}^{+}$ -- множество положительных корней подалгебры $\af$ (без потери общности мы можем считать их векторами из положительного корневого пространства  $\hf^{\ast  +}$ of $\gf$).
+Здесь $\Delta _{\af}^{+}$ -- множество положительных корней подалгебры $\af$ (без потери общности мы можем считать их векторами из положительного корневого пространства  $\hf^{\ast  +}$ алгебры $\gf$).
 
@@
 \begin{equation}
-\hf=\frak{\hf_{\af}}\oplus \hf_{\af_{\perp }}\oplus
-\hf_{\perp }=\frak{\hf_{\widetilde{\af}}}\oplus \hf_{%
-\af_{\perp }}=\frak{\hf_{\widetilde{\af_{\perp }}}}\oplus
+\hf=\frak{\hf_{\af}}\oplus \hf_{\afb}\oplus
+\hf_{\perp }=\frak{\hf_{\widetilde{\af}}}\oplus \hf_{\afb}=\frak{\hf_{\widetilde{\afb}}}\oplus
 \hf_{\af}.
@@
 \label{defect-perp}
-\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi _{\af%
-_{\perp }}\circ\rho .
+\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi_{\afb}\rho .
 \end{equation}
@@
 
-Когда  $\gf$ и $\af$ конечномерные все регулярные вложения можно получить путем последовательного удаления вершин из расширенной диаграммы Дынкина алгебры $\gf$ (и  $\Delta_{\afb }^{+}=\emptyset $ если $\af$ максимальна).
+Когда  $\gf$ и $\af$ -- конечномерные, все регулярные вложения можно получить путем последовательного удаления вершин из расширенной диаграммы Дынкина алгебры $\gf$ (и  $\Delta_{\afb }^{+}=\emptyset $ если $\af$ максимальна).
 Если регулярное вложение для классических серий $A$, $C$ и $D$ зафиксировано таким образом, то диаграмма Дынкина для $\afb$ получается из расширенной диаграммы $\gf$ путем удаления поддиаграммы $\af$ и соседних вершин:
@@
 
-\begin{enumerate}
+\begin{enumerate}[(i)]
 \item Построить корневую систему $\Delta _{\af}$ для вложения $\af\rightarrow \gf$.
@@
 
-Можно ускорить работу алгоритмы путем однократного вычисления представителей классов смежности $W/W_{\afb }$.
+Можно ускорить работу алгоритма путем однократного вычисления представителей классов смежности $W/W_{\afb }$.
 
@@
   \centering
-  \includegraphics[width=100mm]{figure3}
+  \includegraphics[width=60mm]{figure3}
   \caption{Регулярное вложение  $B_2 \rightarrow B_4$ получается путем исключения вершины из диаграммы Дынкина. 
@@
 
-В ортогональном базисе $\left\{e_1,\dots,e_4\right\}$ простые и положительные алгебры $B_4$ равны
+В ортогональном базисе $\left\{e_1,\dots,e_4\right\}$ простые и положительные корни алгебры $B_4$ равны
 \begin{eqnarray*}
@@
   \label{eq:153}
-  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+g}=\frac{x_e k\; \mathrm{dim}\,\af}{x_ek+a}.
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+h^{\vee}_{\gf}}=\frac{x_e k\; \mathrm{dim}\,\af}{x_ek+h^{\vee}_{\af}}.
 \end{equation}
 Здесь $x_e$ -- так называемый ``индекс вложения'':
-$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$, где $\Theta$, $\Theta_{\mathfrak{a}}$ -- старшие корни алгебр
-$\mathfrak{g}$ и $\mathfrak{a}$, а  $g$ и $a$ -- соответствующие дуальные числа Кокстера.
+$x_e=\frac{\left|\pi_{\mathfrak{a}} \theta\right|^2}{\left|\theta_{\mathfrak{a}}\right|^2}$, где $\theta$, $\theta_{\mathfrak{a}}$ -- старшие корни алгебр
+$\mathfrak{g}$ и $\mathfrak{a}$, а  $h^{\vee}_{\gf}$ и $h^{\vee}_{\af}$ -- дуальные числа Кокстера.
 
@@
 В частности для неприводимых модулей уровня один мы получаем тривиальное ветвление:
-\begin{equation*}
+\begin{eqnarray*}
   \label{eq:44}
@@
    L^{(0,1;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(2;4;0)}.
-\end{equation*}
+\end{eqnarray*}
 
@@
 
-Coset-модели \cite{Goddard198588} тесно связанные с калибровочными ВЗНВ-моделям активно изучаются в теории струн, особенно в струнных моделях в пространстве анти де Ситтера
-\cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}. Характера в coset-моделях пропорциональны функциям ветвления.
+Coset-модели \cite{Goddard198588}, тесно связанные с калибровочными ВЗНВ-моделями, активно изучаются в теории струн, особенно в струнных моделях в пространстве анти де Ситтера
+\cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}. Характеры в coset-моделях пропорциональны функциям ветвления.
 \begin{equation}
@@
 
-Используя Определение (\ref{fan-definition}) мы получаем веер вложения $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
+Используя Определение \ref{fan-definition} мы получаем веер вложения $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
 Заметим, что наименьший вес веера $\gamma_0$ равен нулю и  $s\left( \gamma_0 \right)=-1$.
@@
     \chi^{(\omega_1)}_{0}(q) = & q^{\frac{5}{6}}\left(1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\right. \\
-    &\left. 222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\right),
+    &\left. 222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\right).
   \end{array}
@@
 
-\section{Выводы ко второй главе}
+\section{Заключение}
 \label{sec:conclusion}

### 2012-01-14 AffineLieAlgebras/Thesis/3.tex
Misprints, translation of section on affine splints, reorganization of last chapter

@@
 Используя этот инструмент мы получаем основной результат данной главы -- однозначное соответствие между кратностями весов неприводимых модулей сплинта и коэффициентов ветвления для редуцированного модуля $L^{\mu}_{\gf\downarrow \af}$.
+
+Затем мы обсуждаем аффинное расширение корневой системы допускающей сплинт и получаем новые соотношения, связывающие функции ветвления неприводимых модулей на модули конечномерных подалгебр (см.
+Раздел \ref{sec:splints-affine}).
 
@@
 
-\begin{Def}
+\begin{definition}
 Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$. Тогда отображение $\phi $ -- ``вложение''
@@
 для любой тройки $\alpha ,\beta ,\gamma \in P_{0}$, такой, что $\gamma =\alpha+\beta $.
-\end{Def}
+\end{definition}
 
@@
 
-\begin{Def}
+\begin{definition}
 Корневая система $\Delta$ ``расщепляется'' на  $(\Delta _{1},\Delta _{2})$, если существует два вложения  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ и $\phi _{2}:\Delta _{2}\hookrightarrow \Delta $, где (a) $\Delta $ -- несвязное объединение образов $\phi _{1}$ и $\phi _{2}$, и (b) ни ранг  $\Delta _{1}$, ни ранг  $\Delta _{2}$ не превосходит ранга $\Delta $.
-\end{Def}
+\end{definition}
 
@@
 
-\begin{Cnj}
+\begin{conjecture}
 Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением
@@
 \end{equation}
-\end{Cnj}
+\end{conjecture}
 
@@
 Рассмотрим любую пару ребер $\lambda _{i},\lambda _{j}$ и соответствующие веса $\mu +\rho $, $\mu +\rho +\lambda _{i}$ и $\mu +\rho +\lambda _{j}$.
-Применим отражение $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
+Применим отражение $s_{\alpha _{i}}$ (или $s_{\alpha _{j}}$),
 \begin{equation}
@@
 В разделе \ref{sec:appendix} мы показываем, что для каждого такого $\beta _{l}$ существует корень  $\alpha _{l}\in S_{\frak{c}}$, такой, что $\beta _{l}=\alpha _{l}+\beta _{k}$.
-Легко видеть, что в этом случае соответствующее ребро пересекает гиперплоскость, ограничивающую главную камеру Вейля$ \bar{C_{\af}}$ и ортогональную к корню $\alpha _{l}$,
+Легко видеть, что в этом случае соответствующее ребро пересекает гиперплоскость, ограничивающую главную камеру Вейля $\bar{C_{\af}}$ и ортогональную к корню $\alpha _{l}$,
 \begin{equation}
@@
 Следующим шагом построим полную  $W_{\sfr}$-орбиту элемента $\Phi _{\sfr}^{\left( \widetilde{\mu }\right) }$  в $P_{\sfr}$.
-Легко видеть, что его кообраз принадлежит  $\bar{C_{\af}}$ и что множество $\phi^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) \setminus \Phi _{\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ соответствует весам, принадлежащим границе$\bar{C_{\af}}$ (включая подмножество $\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\} $).
+Легко видеть, что его кообраз принадлежит  $\bar{C_{\af}}$ и что множество $\phi^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) \setminus \Phi _{\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ соответствует весам, принадлежащим границе $\bar{C_{\af}}$ (включая подмножество $\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\} $).
 То есть мы построили все формальные элементы с соответствующими знаковыми множителями, которые после сложения с  $\Phi _{\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ образуют диаграмму $\phi^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) $ в $\bar{C_{\af}}$.
@@
 Теперь вернемся к равенству (\ref{singular main-3}).
-Можно добавить к $\Phi _{\gf}^{\left( \mu \right) }$ пары формальных элементов, построенные выше, с противоположными знаками: $\epsilon \left( w\right)|_{w\in W_{\sfr}}$ and $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$.
+Можно добавить к $\Phi _{\gf}^{\left( \mu \right) }$ пары формальных элементов, построенные выше, с противоположными знаками: $\epsilon \left( w\right)|_{w\in W_{\sfr}}$  и  $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$.
 Припишем знаки $\epsilon \left( w\right) |_{w\in W_{\sfr}}$ элементам, веса которых попадут в главную камеру $\bar{C_{\af}}$.
-К соседним камерам $\bar{C_{\af}^{(l)}}$ относятся те же элементы, но  с противоположным знаком  (Эти камеры связаны с главной простыми отражениями $s_{\alpha _{l}}$, так что противоположные знаки $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$ здесь естественны).
+К соседним камерам $\bar{C}_{\af}^{(l)}$ относятся те же элементы, но  с противоположным знаком  (Эти камеры связаны с главной простыми отражениями $s_{\alpha _{l}}$, так что противоположные знаки $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$ здесь естественны).
 Можно повторить эту процедуру и получить дополнительные сингулярные веса в любой камере Вейля $\bar{C_{\af}^{(m)}}$, причем эти веса будут иметь знаки, противоположные знакам в соседних камерах.
@@
 
-Splint of root system of simple Lie algebra appears naturally in
-the study of (regular) embeddings of reductive subalgebras. It can
-be used to derive branching rules. Application of
-splint properties drastically simplifies calculations of
-branching coefficients. We study affine extension of splint root system of simple Lie algebra and obtain relations on theta and branching functions.
+Как мы показали в предыдущих разделах, сплинты корневых систем простых алгебр Ли возникают при изучении регулярных вложений редуктивных подалгебр.
+Сплинт может использоваться для вывода правил ветвления, его свойства сильно облегчают вычисления коэффициентов ветвления.
+В этом разделе мы используем свойства сплинта конечномерной алгебры Ли для получения новых соотношений на тета-функции и функции ветвления, связанные с аффинным расширением алгебры.
 
-The term {\it splint} was introduced by D. Richter in \cite{richter2008splints} where the
-classification of splints for simple Lie algebras was obtained. The fan $\Gamma \subset \Delta$ was
-introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent properties of
-branching coefficients for maximal embeddings. Injection fan is an efficient tool to study branching
-rules. Later this construction was generalized to non-maximal embeddings and affine Lie algebras in
-\cite{2010arXiv1007.0318L, ilyin812pbc}. In paper \cite{2011arXiv1111.6787L} we have shown that the
-existence of a splint for a root system of a simple Lie algebra leads to simplifications in
-reduction procedures of a Lie algebra module to modules of a subalgebra. This effect is based on the
-injection fan and singular element properties of Lie algebra modules.
+Веер вложения для аффинных алгебр Ли допускает разложение, аналогичное разложению веера для простых алгебр Ли, следующему из существования сплинта.
+Такое разложение приводит к соотношению на тета-функции.
+Затем мы рассматриваем градуированное ветвление модуля аффинной алгебры Ли на модули конечномерной подалгебры и получаем соотношения на функции ветвления.
 
-In the present note we discuss possible applications of splint in
-a root system of simple Lie algebra related to representation
-theory of affine Lie algebras. We discuss the structure of
-injection fan for affine Lie algebras and show that it admits a
-decomposition similar to that used in \cite{2011arXiv1111.6787L}
-for simple Lie algebras. Such a decomposition leads to equations
-for theta-functions. We study graded branching of affine Lie
-algebra modules reduced to a finite-dimensional subalgebra and
-discuss consequences of splint in this case.
-
-\subsection{Splints and affine Lie algebras}
-\label{sec:definitions}
-
-Consider simple Lie algebra $\gf$ with a root system $\Delta$. Let
-$\af_{1}\subset \gf$ be its reductive subalgebra of the same rank, such that
-$\Delta_{\af}\equiv\Delta_{1}\subset\Delta$ and $Q_{\af}\subset Q$, where $Q$ is the root lattice. Irreducible highest-weight modules of
-$\gf$ and $\af$ are denoted by $L^{\mu}$ and $L^{\nu}_{\af}$
-correspondingly. Weyl character formula for irreducible modules is
+Рассмотрим простую алгебры Ли $\gf$ с корневой системой $\Delta$. Пусть
+$\af_{1}\subset \gf$ --  ее редуктивная подалегебра того же ранга, такая, что
+$\Delta_{\af}\equiv\Delta_{1}\subset\Delta$ и $Q_{\af}\subset Q$, где $Q$ -- корневая решетка. Неприводимые модули старшего веса алгебр 
+$\gf$ и $\af$ мы обозначаем через $L^{\mu}$ и $L^{\nu}_{\af}$. Формула Вейля для характеров неприводимых модулей имеет вид
 $\mathrm{ch}L^{\mu}=\frac{\Psi^{(\mu)}}{\prod_{\alpha\in\Delta}(1-e^{-\alpha})}$,
-where $\Psi^{(\mu)}=\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}$
-is a singular element of the module and $W$ -- the Weyl group of
-$\gf$. Formal character of irreducible module admits a
-decomposition
+где  $\Psi^{(\mu)}=\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}$ -- сингулярный элемент модуля, а$W$ -- группа Вейля алгебры $\gf$. Формальный характер неприводимого модуля допускает разложение
 \begin{equation}
@@
 \end{equation}
-where $P$, $P_{\af}$ are weight lattices of $\gf$ and $\af$. We
-want to study affine extension of this situation:
+где $P$, $P_{\af}$ -- весовые решетки $\gf$ и $\af$. Мы хотим рассмотреть аффинное расширение данной конструкции:
 $\gf\subset\gfh,\; \af\subset\afh$, $\afh\subset\gfh$,
-$\hat{\Delta}\subset\hat{\Delta}$ and
+$\hat{\Delta}\subset\hat{\Delta}$ и
 $\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{\hat{\nu}}
-b^{\hat{\mu}}_{\hat{\nu}} \mathrm{ch} L^{\hat{\nu}}_{\afh}$. For
-weights of an affine Lie algebra $\gfh$ we have
-$\hat{\mu}=(\mu,k,n)$, where $\mu$ is a weight of $\gf$, $k$ --
-the level of the module and $n$ -- the grade of the weight
+b^{\hat{\mu}}_{\hat{\nu}} \mathrm{ch} L^{\hat{\nu}}_{\afh}$. Веса аффинной алгебры Ли $\gfh$ имеют вид
+$\hat{\mu}=(\mu,k,n)$, где $\mu$ -- вес алгебры $\gf$, $k$ -- уровень представления, а  $n$ -- грейд веса
 $\hat{\mu}$
 
-\begin{Def}
-  Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a bijective map of
-  roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with vector composition law
-  in $\Delta_{1}$ and $\Delta$.
-\begin{equation*}
-\phi:\Delta_1 \longrightarrow \Delta, \quad \phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,\,\,\, \alpha,\beta \in \Delta_1
-\end{equation*}
-\end{Def}
+%%  \begin{Def}
+%%    Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a bijective map of
+%%    roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with vector composition law
+%%    in $\Delta_{1}$ and $\Delta$.
+%%  \begin{equation*}
+%%  \phi:\Delta_1 \longrightarrow \Delta, \quad \phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,\,\,\, \alpha,\beta \in \Delta_1
+%%  \end{equation*}
+%%  \end{Def}
+%%  
+%%  Note that the image $Im(\phi)$ must not inherit the root system properties except the addition rules
+%%  equivalent to the addition rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and
+%%  $\phi_2$ can splinter $\Delta$ when the latter can be presented as a disjoint union of images
+%%  $Im(\phi_1)$ and $Im(\phi_2)$.
+%%  
+%%  $\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
+%%  \hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
+%%  _i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
+%%  \phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+%%  
+%%  \begin{Def}
+%%    A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if there are two embeddings
+%%    $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
+%%    \phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the disjoint union of the
+%%    images of $\phi _{1}$ and $\phi _{2}$ and (b) neither the rank of $\Delta _{1}$ nor the rank of
+%%    $\Delta _{2}$ exceeds the rank of $%
+%%    \Delta $.
+%%  \end{Def}
+%%  
+%%  It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote
+%%  this by $\Delta \approx (\Delta_1,\Delta_2)$. Each component $\Delta_1$ and $\Delta_2$ is a "stem''
+%%  of the splint.
+%%  
+%% We consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem.
 
-Note that the image $Im(\phi)$ must not inherit the root system properties except the addition rules
-equivalent to the addition rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and
-$\phi_2$ can splinter $\Delta$ when the latter can be presented as a disjoint union of images
-$Im(\phi_1)$ and $Im(\phi_2)$.
+Пусть $(\Delta_1,\Delta_2)$ -- сплинт корневой системы $\Delta$ алгебры $\gf$, причем $\Delta_1=\Delta_{\af}$ является корневой системой редуктивной подалгебры $\af$.
+Как было показано ранее, второй стебель $\Delta_{\frak{s}}:=\Delta_{2}=\Delta \setminus \Delta_{\af}$ можно переписать в виде произведения
+$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint-product}$, которое определяет веер вложения $\Gamma _{\frak{a}\hookrightarrow \frak{g}}$ \cite{lyakhovsky1996rra,ilyin812pbc,2010arXiv1007.0318L}.
 
-$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
-\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
-_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
-\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
-
-\begin{Def}
-  A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if there are two embeddings
-  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
-  \phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the disjoint union of the
-  images of $\phi _{1}$ and $\phi _{2}$ and (b) neither the rank of $\Delta _{1}$ nor the rank of
-  $\Delta _{2}$ exceeds the rank of $%
-  \Delta $.
-\end{Def}
-
-It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote
-this by $\Delta \approx (\Delta_1,\Delta_2)$. Each component $\Delta_1$ and $\Delta_2$ is a "stem''
-of the splint.
-
-We consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem. As shown in paper \cite{2011arXiv1111.6787L} the second stem $\Delta _{\frak{s}}:=\Delta
-_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product
-$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint-product}$
-and it defines an injection fan $\Gamma _{\frak{a}%
-\hookrightarrow \frak{g}}$ \cite{lyakhovsky1996rra,ilyin812pbc,2010arXiv1007.0318L}.
-
-Since the singular element of $L^{\mu}$ can be
-written as $\Psi _{\frak{g}}^{\left( \mu \right) }=e^{-\rho }
+Так как сингулярный элемент модуля $L^{\mu}$ можно переписать в виде $\Psi _{\frak{g}}^{\left( \mu \right) }=e^{-\rho }
 \sum_{w\in W_{\frak{a}}}\epsilon \left( w \right) w\circ \left(
 e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho
-_{\frak{s}}}\right)$  for branching coefficients we get the
-identity \cite{2011arXiv1111.6787L}:
+_{\frak{s}}}\right)$, для коэффициентов ветвления имеет место равенство \cite{2011arXiv1111.6787L}:
 \begin{equation}
@@
 \end{equation}
-Here the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $, they have the
-same Dynkin numbers: $\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
-m_{k}\omega_{(\sfr) k} . \label{new-h-weight}$ So branching coefficients coincide with weight
-multiplicities of $\sfr$-modules.
+Здесь старший вес $\widetilde{\mu }$ однозначно определяется весом $\mu $, так как они оба имеют одинаковые индексы Дынкина: $\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
+m_{k}\omega_{(\sfr) k} . \label{new-h-weight}$ То есть коэффициенты ветвления совпадают с кратностями весов в модулях алгебры $\sfr$.
 
-Now we consider affine extension of this setup, $\afh\subset\gfh$. Since $\mathrm{rank}\gf\leq
-\mathrm{rank} \af+\mathrm{rank}\sfr$ for Weyl denominators we get
- \[
-\prod_{\alpha\in\hat{\Delta}^{+}_{1}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}\prod_{\beta\in\hat{\Delta}^{+}_{2}}(1-e^{\phi\circ \beta})^{\mathrm{mult}(\beta)}=\prod_{\gamma\in\hat{\Delta}^{+}}(1-e^{-\gamma})^{\mathrm{mult}(\gamma)}\prod_{n=0}^{\infty}(1-e^{-n\delta})^{\mathrm{rank}\af+\mathrm{rank}\sfr-\mathrm{rank}\gf}
-\]
+Теперь рассмотрим аффинное расширение $\afh\subset\gfh$. Так как $\mathrm{rank}\gf\leq\mathrm{rank} \af+\mathrm{rank}\sfr$, для знаменателей Вейля мы получаем
+\begin{multline}
+  \label{eq:129}
+\prod_{\alpha\in\hat{\Delta}^{+}_{1}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}\prod_{\beta\in\hat{\Delta}^{+}_{2}}(1-e^{\phi\circ \beta})^{\mathrm{mult}(\beta)}=\\
+\prod_{\gamma\in\hat{\Delta}^{+}}(1-e^{-\gamma})^{\mathrm{mult}(\gamma)}\prod_{n=0}^{\infty}(1-e^{-n\delta})^{\mathrm{rank}\af+\mathrm{rank}\sfr-\mathrm{rank}\gf}
+\end{multline}
 
-Using a specialization
-\cite{kac1988modular,kac1984infinite,kac1990idl} and the
-definition of Dedekind eta-function
-$\eta(\tau)=q^{1/24}\prod_{n=1}^{\infty}(1-q^{n})$, where
-$q=e^{2\pi i \tau}$ we can rewrite this identity as the relation
-imposed on theta-functions $\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in Q_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$:
+Воспользуемя специализацией \cite{kac1988modular,kac1984infinite,kac1990idl} и определением $\eta$-функции Дедекинда
+$\eta(\tau)=q^{1/24}\prod_{n=1}^{\infty}(1-q^{n})$, где
+$q=e^{2\pi i \tau}$, чтбы переписать предыдущее равенство в виде соотношения на тета-функции $$\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in Q_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$$:
 \begin{multline}
@@
 \end{multline}
-Here $z\in P_{\geq 0}\otimes \mathbb{C}$. Using Weyl denominator identity this relation can be
-rewritten as a non-trivial relation connecting theta-functions of algebras $\gfh,\hat\sfr,\afh$:
+Здесь $z\in P_{\geq 0}\otimes \mathbb{C}$.
+При помощи тождества Вейля для знаменателей это равенство можно переписать как нетривиальное соотношение, связывающее тета-функции алгебр $\gfh,\hat\sfr,\afh$:
 \begin{equation}
@@
 
-Now consider the branching of $\gfh$-module to $\gf$-modules. For
-formal characters we can write the following expression:
+Теперь рассмотрим ветвление модуля алгебры $\gfh$ на модули подалгебры $\gf$. Для формальных характеров верно следующее выражение:
 \begin{equation}
@@
 \end{equation}
-Rewriting this equation for weight multiplicities we get
+Переписывая это уравнения для кратностей весов мы получаем
 $m^{(\hat{\mu})}_{\hat{\nu}=(\nu,k,n)}=\sum_{\xi\in P}
-b^{(\hat{\mu})}_{\xi}(n) m^{(\xi)}_{\nu}$. We can introduce
-branching functions similarly to the case of branching for affine
-subalgebra \cite{kac1988modular,kac1990idl}:
+b^{(\hat{\mu})}_{\xi}(n) m^{(\xi)}_{\nu}$. Теперь мы можем ввести функции ветвления аналогично случаю аффинной подалгебры \cite{kac1988modular,kac1990idl}:
 $b^{(\hat{\mu})}_{\nu}(q)=\sum_{n=0}^{\infty}
 b^{(\hat{\mu})}_{\nu}(n) q^{n}$.
-These branching functions are connected to $q$-dimension of module $\mathrm{dim}_{q}L^{\hat \mu}_{\gfh}=\sum_{n=0}^{\infty}q^{n}\sum_{\nu\in P} b^{(\hat \mu)}_{\nu}(n) \mathrm{dim }L^{\nu}_{\gf}=\sum_{\nu\in P}b^{(\hat\mu)}_{\nu}(q) \mathrm{dim} L^{\nu}_{\gf}$.
-It is well-known that $q$-dimension is a modular function for some $\Gamma\subset SL_{2}(\mathbb{Z})$  \cite{gannon2006moonshine}, so branching functions $b^{(\hat \mu)}_{\nu}(q)$ have modular properties.
+Эти функции ветвления связаны с  $q$-размерностью модуя $\mathrm{dim}_{q}L^{\hat \mu}_{\gfh}=\sum_{n=0}^{\infty}q^{n}\sum_{\nu\in P} b^{(\hat \mu)}_{\nu}(n) \mathrm{dim }L^{\nu}_{\gf}=\sum_{\nu\in P}b^{(\hat\mu)}_{\nu}(q) \mathrm{dim} L^{\nu}_{\gf}$.
+Известно, что  $q$-размерность является модулярной функцией по отношению к действию некоторой подгруппы $\Gamma\subset SL_{2}(\mathbb{Z})$  \cite{gannon2006moonshine}, так что функции ветвления  $b^{(\hat \mu)}_{\nu}(q)$ обладают модулярными свойствами.
 
- For string functions of a module
-$L^{\hat{\mu}}$ we have
+Для струнных функций модуля
+$L^{\hat{\mu}}$ верно соотношение
 \begin{equation}
@@
 
-Introduce an ordering of the set of weights $\xi$ as follows:
-attribute to a weight $(\rho,\xi)$ its product $(\rho,\xi)$ with
-the Weyl vector $\rho$. Then relation \eqref{eq:145} can be written
-in the matrix form $\sigma(q)=M b(q)$ or as an inverse relation
-$b(q)=M^{-1}\sigma(q)$. Here $\sigma(q)$ and $b(q)$ are infinite
-columns of string and branching functions. Matrix $M$ contains
-multiplicities of weights in $\gf$-modules similar to that of
-Table 1 in paper \cite{2010arXiv1001}. The inverse matrix $M^{-1}$
-encodes recurrent relations imposed weight multiplicities
+Введем порядок на множестве весов $\xi$ следующим образом:
+припишем весу  $\xi$ значение его скалярного произведения $(\rho,\xi)$ с вектором Вейля $\rho$ и упорядочим веса по этим значениям.
+Тогда соотношение \eqref{eq:145} можно переписать в матричном виде: $\sigma(q)=M b(q)$ и обратно,
+$b(q)=M^{-1}\sigma(q)$.
+Здесь  $\sigma(q)$ и  $b(q)$ -- бесконечные векторы струнных функций и функций ветвления.
+Матрица $M$ содержит кратности весов в  $\gf$-модулях, аналогично Таблице 1 в работе \cite{2010arXiv1001}.
+Обратная матрица $M^{-1}$ содержит рекуррентные соотношения на кратности весов
 \cite{il2010folded}.
 
-Now consider the branching of $\gfh$-modules in $\af$-modules and
-assume the existence of a splint
+Теперь рассмотрим ветвление модулей алгебры $\gfh$ на модули подалгебры $\af$ в предположении существовании сплинта
 $\Delta^{+}_{\gf}=\Delta^{+}_{\af}\cup \phi(\Delta^{+}_{\sfr})$.
-We decompose $\gf$-modules in equation \eqref{eq:149} into
-$\af$-modules using property \eqref{eq:146}:
+Разложим  $\gf$-модули в равенстве \eqref{eq:149} на 
+$\af$-модули используя свойство \eqref{eq:146}:
 \begin{multline}
@@
 \end{multline}
-We see that the similar matrix relation holds for branching
-functions $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}\;
-b_{(\gfh\downarrow\gf)}(q)$ and we can write
-$\sigma(q)=M_{\af}\; b_{(\gfh\downarrow\af)}(q)$. So if we know
-branching coefficients for the embedding $\gf\subset\gfh$ (for
-example, see book \cite{kass1990ala}) we can easily obtain
-branching functions for the embedding $\af\subset \gfh$.
-\subsection*{Conclusion}
-\label{sec:conclusion-four} We have demonstrated that splint in affine
-Lie algebras leads to new relations between theta-functions and
-branching functions for branching to finite-dimensional
-subalgebras, which can be useful for computations. Further
-question is to generalize this analysis to affine subalgebras and
-to apply the results to branching in the study of CFT coset
-models.
+ Мы видим, что аналогичное матричное соотношение выполняется для функций ветвления $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}\;
+b_{(\gfh\downarrow\gf)}(q)$ и мы можем написать
+$\sigma(q)=M_{\af}\; b_{(\gfh\downarrow\af)}(q)$.
+Так что если мы знаем коэффициенты ветвления для вложения $\gf\subset\gfh$ (см., например, книгу \cite{kass1990ala}) мы сразу получаем (градуированные) функции ветвления для вложения $\af\subset \gfh$.
 
-\section{Выводы к четвертой главе}
+\section{Заключение}
 
@@
 
+Также мы продемонстрировали, что сплинт для аффинных алгебр Ли ведет к новым соотношениям на тета-функции и функции ветвления для редукции на модули конечномерных подалгебр, что может быть полезно для вычислений.
+Возможно дальнейшее обобщение этого анализа на аффинные подалгебры и применение результатов изучению coset-моделей конформной теории поля.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Приложение}
+\begin{subappendices}
+\section{Приложение}
 \label{sec:appendix}
@@
 \end{itemize}
-
+\end{subappendices}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

### 2012-01-30 AffineLieAlgebras/Thesis/2.tex
Equation numbering fixed (no duplicates)

@@
 
-\label{subsec:decomp-sing-element}
+\label{subsec:decomp-sing-element-again}
 
@@
 \end{array}
-\label{sing-decomp-1}
+\label{sing-decomp-2}
 \end{equation}
-Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}), чтобы упростить первую строку в формуле (\ref{sing-decomp-1}):
+Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}), чтобы упростить первую строку в формуле (\ref{sing-decomp-2}):
 \[
@@
 
-В работе \cite{2010arXiv1007.0318L} разложение, аналогичное формуле (\ref{singular main}), было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
+В предыдущей главе (и в нашей работе \cite{2010arXiv1007.0318L}) разложение, аналогичное формуле (\ref{singular main}), было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
 \begin{equation}
@@
 Пусть  $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$ и  $\frak{a}\hookrightarrow \frak{g}$ -- редуктивная подалгебра $\frak{g}$.
-Пусть $\frak{a}_{\perp }$, ортогональный партнер для $\frak{a}$, эквивалентен  $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, и $\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ с $\frak{h=\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$.
+Пусть $\frak{a}_{\perp }$ -- ортогональный партнер для $\frak{a}$, -- эквивалентен  $A_{1}$, $\frak{a}_{\perp }\approx $ $A_{1}$, и $\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$ с $\frak{h=\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$.
 Пусть $L_{\frak{g}\downarrow \widetilde{\frak{a}}}^{\mu }=\bigoplus\limits_{\nu \in P_{\widetilde{\frak{a}}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\widetilde{\frak{a}}}^{\nu }$ -- ветвление модуля $L^{\mu }$ относительно подалгебры $\widetilde{\frak{%
@@
 
-\section{Выводы к третьей главе}
+\section{Заключение}
 

### 2012-01-30 AffineLieAlgebras/Thesis/5.tex

@@
-\chapter{Вычислительные методы для теории представлений аффинных алгебр Ли}
+\section{Вычислительные методы для теории представлений аффинных алгебр Ли}
 \label{cha:computational-methods}
 
-В данной главе мы описываем вычислительный пакет  {\bf Affine.m}, разработанный нами на основе идей и методов, изложенных в главах \ref{cha:affine-lie-algebras}, \ref{cha:BGG}.
+В данном разделе мы описываем вычислительный пакет  {\bf Affine.m}, разработанный нами на основе идей и методов, изложенных в главах \ref{cha:affine-lie-algebras}, \ref{cha:BGG}.
 Этот пакет для популярной системы компьютерной алгебры {\it Mathematica} может использоваться для вычислений в теории представлений конечномерных и аффинных алгебр Ли.
@@
 Существует два рекуррентных алгоритма, основывающихся на формуле Вейля для характеров и формуле Фрейденталя для кратностей.
-В данной главе мы их опишем.
+В данном разделе мы их опишем.
 
@@
 
-Чтобы исправить этот недостаток, нами был создан пакет {\bf Affine.m} для популярной системы  {\it Mathematica}.
-Возможности и ограничения этого пакета мы и описываем в этой главе.
-Кроме того, мы приводим некоторые примеры, связанные с физическими приложениями.
-
 Необходимые сведения из теории представлений приведены в главе \ref{cha:affine-lie-algebras}.
@@
 
-\section{Структуры данных}
+\subsection{Структуры данных}
 \label{sec:core-datastructures} 
 Хотя {\it Mathematica} -- нетипизированный язык программирования, в нем можно создавать структурированные объекты и проверять их типы используя сопоставление с шаблоном (pattern matching) \cite{shifrinmathematica}, \cite{maeder2000computer}.
-\subsection{Веса}
+\subsubsection{Веса}
 \label{sec:weights}
@@
 
-\subsection{Корневые системы}
+\subsubsection{Корневые системы}
 \label{sec:root-systems}
@@
 
-\subsection{Формальные элементы}
+\subsubsection{Формальные элементы}
 \label{sec:formal-elements}
@@
 
-\subsection{Модули}
+\subsubsection{Модули}
 \label{sec:modules}
@@
 \end{lstlisting}
-\section{Основные алгоритмы}
+\subsection{Основные алгоритмы}
 \label{sec:comp-algor}
@@
 
-\section{Примеры}
+\section{Примеры вычислений}
 \label{sec:examples-six}
@@
 
-\section*{Выводы к шестой главе}
+\section{Заключение}
 \label{sec:6-conclusion}
-В данной главе мы представили пакет {\bf Affine.m} для вычислений в теории представлений конечномерных и аффинных алгебр Ли.
+В данной главе мы использовали свойства сингулярных элементов для классификации операторов изменения граничных условий в coset-моделях конформной теории поля, соответствующих стохастическим моделям с эволюцией Шрамма-Левнера с дополнительным блужданием на факторпространстве $G/A$.
+
+Кроме того, в этой главе мы представили пакет {\bf Affine.m} для вычислений в теории представлений конечномерных и аффинных алгебр Ли.
 Он может использоваться для изучения групп Вейля, корневых систем, неприводимых модулей, модулей Верма и параболических модулей Верма конечномерных и аффинных алгебр Ли.
@@
 
-В следующих версиях программы мы планируем реализовать работу со скрученными аффинными алгебрами Ли, расширенными аффинными алгебрами и реализовать более полную поддержку вычислений коэффициентов разложения тензорных произведений.
+% В следующих версиях программы мы планируем реализовать работу со скрученными аффинными алгебрами Ли, расширенными аффинными алгебрами и реализовать более полную поддержку вычислений коэффициентов разложения тензорных произведений.
 
@@
 
-\section*{Описание пакета}
-\label{package}
-Пакет может быть бесплатно загружен с сайта \url{http://github.com/naa/Affine}. Чтобы получить разрабатываемую версию кода можно использовать систему управления версиями {\it git} и команду
-\begin{lstlisting}[language=bash]
- git clone git://github.com/naa/Affine.git
-\end{lstlisting}
-
+%%  \section*{Описание пакета}
+%%  \label{package}
+%%  Пакет может быть бесплатно загружен с сайта \url{http://github.com/naa/Affine}. Чтобы получить разрабатываемую версию кода можно использовать систему управления версиями {\it git} и команду
+%%  \begin{lstlisting}[language=bash]
+%%   git clone git://github.com/naa/Affine.git
+%%  \end{lstlisting}
+%%  
 %%  Содержимое пакета:

### 2012-01-31 AffineLieAlgebras/Thesis/talk.tex
Talk text written.

\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsthm} 
\usepackage{pb-diagram}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
\usepackage{epstopdf}
\usepackage{multicol}
\usepackage{cancel}

\usepackage{amsfonts}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newtheorem{theorem}{Theorem}
%% \newtheorem{acknowledgement}[theorem]{Acknowledgement}
%% \newtheorem{algorithm}[theorem]{Algorithm}
%% \newtheorem{axiom}[theorem]{Axiom}
%% \newtheorem{case}[theorem]{Case}
%% \newtheorem{claim}[theorem]{Claim}
%% \newtheorem{conclusion}[theorem]{Conclusion}
%% \newtheorem{condition}[theorem]{Condition}
%% \newtheorem{conjecture}[theorem]{Conjecture}
%% \newtheorem{mycorollary}[theorem]{Corollary}
%% \newtheorem{mycriterion}[theorem]{Criterion}
%% \newtheorem{mydefinition}[theorem]{Definition}
%% \newtheorem{myexample}[theorem]{Example}
%% \newtheorem{myexercise}[theorem]{Exercise}
%% \newtheorem{mynotation}[theorem]{Notation}
%% \newtheorem{myproblem}[theorem]{Problem}
%% \newtheorem{myproposition}[theorem]{Proposition}
%% \newtheorem{myremark}[theorem]{Remark}
%% \newtheorem{mysolution}[theorem]{Solution}
%% \newtheorem{mysummary}[theorem]{Summary}
%% \newenvironment{myproof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfg}{\hf_{\gf}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\sfr}{\mathfrak{s}}
%\pagestyle{plain}

\theoremstyle{definition} \newtheorem{Def}{Определение}
\newcommand{\tr}{\hat\triangleright} \newcommand{\trc}{\triangleright}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

\begin{document}
Здравствуйте! Меня зовут Антон Назаров, я из петербургского университета. Мой доклад называется ``Сингулярные элементы модулей аффинных алгебр Ли  в моделях конформной теории поля''. Он основан на тексте кандидатской диссертации. 
Сперва я расскажу про физическую мотивацию, напомню про WZNW и coset-модели, а потом буду говорить про наши результаты. У нас вышло несколько статей, которые доступны в виде препринтов. Что-то я уже рассказывал здесь летом на конференции SQS.

Модели Весса-Зумино-Новикова-Виттена выделяются из числа моделей двумерной конформной теории поля тем, что у них есть привычная формулировка на языке действия. Действие в модели имеет вид суммы. Первый член -- это просто нелинейная сигма-модель. Поле g живет на комплексной плоскости с бесконечностью (два-сфере) и принимает значение в простой компактной группе Ли. 
В самой нелинейной сигма-модели конформная инвариантность теряется при квантовании. Но конформная инвариантность восстанавливается за счет второго члена Весса-Зумино. Это топологический член, который определен на трехмерном многообразии, границей которого является наша два-сфера. Он строится из полей g с тильдой -- продолжений поля g. Естественно, такое продолжение не единственно, но если мы возьмем два разных продолжения, то мы получим три-сферу. Так как третья группа гомологий любой компактной конечномерной группы Ли равна Z, при целых k экспонента действия определена однозначно.

То есть у нас хорошая модель, в которой есть конформная инвариантность. Перейдем к комплексным переменным. У нас есть два сохраняющихся тока J и J бар. Заметим, что они принимают значения в алгебре Ли g, соответствующей группе G. Есть калибровочная инвариантность относительно таких преобразований. Соответствующие тождества Уорда имеют такой вид. Теперь если мы подставим сюда сами токи J и разложим их по генераторам и степеням z, то мы получим коммутационные соотношения аффинной алгебры g хат. 
Конформная инвариантность в двумерной теории поля связана с алгеброй Вирасоро. Здесь у нас алгебра Вирасоро реализуется с помощью конструкции Сугавары, то есть она вкладывается в универсальную обертывающую аффинной алгебры Ли.

Полная киральная алгебра -- это полупрямое произведение аффинной алгебры Ли и алгебры Вирасоро. Примарными по отношению к ней называются локальные поля, которые ведут себя как поле g и имеют операторное разложение такого вида. 
Примарные поля можно нумеровать старшими весами представлений g с крышкой. Их конформные веса даются следующим выражением. 
Состояния можно получать из соответствия между полями и состояниями. Тогда сингулярными векторами называются такие, что действие на них повышающих операторов равно нулю. Конечно, векторы старшего веса являются сингулярными, но не только они. Модули, которые получаются действием понижающих операторов, отщепляются. То есть корреляторы между с полями равны нулю. 
Теперь я напомню про coset-модели. Их можно формулировать как WZNW-модели с дополнительным чисто калибровочным полем, принимающим значение в (представлениях) подалгебры a алгебры g. Теперь у нас такие токи и для калибровочных полей выполняется такое равенство.  В результате интегрирования этого калибровочного поля мы избавляемся от степеней свободы, связанных с подалгеброй a. Здесь тоже есть конформная инвариантность и генераторы алгебры Вирасоро даются разностями выражений Сугавары соответствующих алгебрам g и a. 
Заметим, что генераторы алгебры a  с крышкой коммутируют с генераторами алгебры Вирасоро. Сразу можно заметить, что сингулярные по отношению к a с крышкой векторы образуют модули алгебры Вирасоро. Тогда функции ветвления оказываются характерами модулей алгебры Вирасоро. (Я здесь упростил некоторые детали).

В coset-моделях примарные поля нумеруются парами весов алгебр g и a, для которых функции ветвления не равны нулю. Некоторые пары эквивалентны. Соотношение эквивалентности дается умножением на так называемые простые токи, состоящие из g и a-компонент с равными конформными весами. Тогда конформный вес примарного поля дается разностью конформных весов для двух WZNW-моделей.

Теперь перейдем к изучению структуры сингулярных элементов. Именно сингулярные элементы определяют свойства модулей аффинных алгебр Ли. 
Простейший тип модулей -- это модули Верма. Их можно представить как произведение универсальной обертывающей алгебры и одномерного представления подалгебры Бореля. Тогда формальный характер можно записать вот в таком виде. Здесь мы воспользовались тождеством знаменателей. Заметим, что знаменатель у нас всегда одинаковый, а в числителе как-раз и стоит сингулярный элемент. Неприводимый модуль можно получить из модуля Верма факторизацией по максимальному подмодулю. Известная формула Вейля-Каца дает нам следующее выражение для характеров неприводимых модулей. Как ее можно интерпретировать: в числителе сингулярный элемент, а знаменатель тот же самый. Для неприводимых модулей сингулярный элемент дается сдвинутой орбитой группы Вейля. Эту формулу можно рассматривать как выражение характера неприводимого модуля через характеры модулей Верма вследствие резольвенты Бернштейна-Гельфанда-Гельфанда.

Теперь поговорим о разложениях сингулярных элементов. Рассмотрим аффинную или конечномерную алгебру g и ее редуктивную подалгебру a. Тогда мы можем разложить модули алгебры g на модули подалгебры a. Здесь я для определенности написал неприводимые модули, хотя мог бы рассматривать модули Верма. 
Для характеров я могу написать следующее разложение. Здесь пи - это проекция в алгебрах Картана, ее нужно добавить, если ранг a меньше ранга g. Проблема тут в том, чтобы найти коэффициенты этого разложения, которые называются коэффициентами ветвления. Можно считать в лоб - построить модуль g, потом последовательно строить вычитать модули a, но это неэффективно. 
Для этого мы хотим домножить на знаменатель, а потом ввести упорядочение. Но в случае немаксимальной подалгебры из-за проекции мы можем случайно домножить на ноль, поэтому нам нужен промежуточный шаг. Введем еще одну подалгебру b, которую мы также будем обозначать как a ортогональное. Эта подалгебра определяется набором корней g, ортогональных корневой системе a. Тогда у нас есть ``ортогональная пара подалгебр''. 
Еще введем такое обозначение для разностей векторов Вейля подалгебр и проекций вектора Вейля алгебры. 
Тогда верна следующая лемма о разложении сингулярного элемента. 
Здесь мы фактически построили модули Верма алгебры b из весов сингулярного элемента модуля g и собрали комбинации характеров модулей Верма в характеры неприводимых модулей. После проекции у нас от этих неприводимых модулей остаются только размерности. 
Теперь мы можем написать рекуррентное соотношение для сингулярных коэффициентов ветвления k. Эти сингулярные коэффициенты ветвления равны обычным внутри главной камеры Вейля. Рекурсия идет по множеству весов, которое получается из разложения знаменателя. В качестве начальных данных рекурсии выступают сингулярные веса с соответствующими размерностями. Заметим, что множество гамма нужно построить один раз для пары алгебр a и g.

Сейчас я покажу простой пример. Рассмотрим алгебру B2 (so(5)) и подалгебру A1 (so(3)), построенную на длинном корне. Вот сингулярный элемент модуля алгебры. Ортогональная подалгебра -- это тоже A1. Справа построены модули ортогональной подалгебры и указаны их размерности.
Дальше веер вложения строится из этих двух корней. После раскрытия скобок остается три элемента, выкидываем ноль, начинаем с этой двойки, получаем здесь два, тут один и все, вот оно, наше ветвление. 
Теперь аффинный пример. Возьмем аффинное расширение этого же примера. У нас получается вот такой веер и вот такой сингулярный элемент с соответствующими размерностями. В результате рекуррентного вычисления получается следующая картина. Смотрим в главную камеру Вейля, показанную черными линиями и видим наши коэффициенты ветвления. Можно их рассматривать как коэффициенты в разложении функций ветвления по степеням параметра q. 
Покажем связь нашего разложения с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда. Заметим, что ортогональная подалгебра по определению всегда регулярна. Можно считать, что она определяется подмножеством простых корней I. Возьмем сингулярный элемент и построим модули ортогональной подалгебры, аналогично прошлому примеру. Теперь подействуем на эти модули таким знаменателем. В результате мы получаем обобщенные или параболические модули Верма. 
Здесь я привел рисунок параболических модулей Верма, соответствующих нашему разложению модулей B2 на модули A1. Мы можем записать характер неприводимого модуля в виде чередующейся суммы характеров параболических модулей Верма. Здесь пунктиром я показал те модули, которые входят в сумму с положительным знаком, а точечками -- с отрицательным. 
Теперь я перейду к немного другому разложению сингулярных элементов, которое следует из разложения корневой системы, но не на ортогональные компоненты. Введем вложение корневых систем так, чтобы сохранялась сумма. Это вложение индуцирует вложение формальных алгебр. Заметим, что мы не требуем сохранения углов между корнями. 
Назовем сплинтом или расщеплением корневой системы ее разложение в объединение образов двух вложений, причем таких, что ранги прообразов не превышают ранга образа. Если одна из компонент расщепления является корневой системой подалгебры, то есть эта компонента вложена метрически, то вторая компонента определяет веер вложения. Веер вложения оказывается образом сингулярного элемента второй алгебры под действием phi. 
Оказывается, что в таком случае и сингулярный элемент модуля можно разложить в сумму образов сингулярных элементов модулей второй алгебры. При этом у этих модулей старший вес имеет те же индексы Дынкина. В результате коэффициенты ветвления модулей алгебры g на модули подалгебры a1 оказываются равны кратностям весов в модулях второй алгебры. При этом сами образы модулей оказываются деформированными, с неправильными углами. Посмотрите на картинку. В данном случае корневая система алгебры B2 раскладывается в объединение корневой системы подалгебры A1 и образа корневой системы алгебры A2 с ``неправильными'' углами. То есть вот такой модуль раскладывается с вот такими коэффициентами. Еще один красивый пример -- это алгебры G2 и разложение ее корневой системы на корневые системы двух алгебр A2. На рисунке пунктиром показаны соответствующие сингулярные элементы. Здесь -- коэффициенты ветвления. 
Есть классификация сплинтов, она не очень большая, но что интересно, включает случай, описывающийся базисом Гельфанда-Цетлина. 
Теперь рассмотрим аффинное расширение этой ситуации. Здесь у нас есть подобное разложение для знаменателей Вейля, но у нас разное количество чисто мнимых корней, поэтому полностью конечномерный случай не воспроизводится. Зато мы можем переписать разложение знаменателя в произведение в виде тождества, связывающего тета-функции, соответствующие трем разным алгебрам g, s и a. 
Рассмотрим ветвление модулей аффинной алгебры на модули конечномерной подалгебры. В этом случае мы можем завести функции ветвления. Коэффициенты ветвления для этого случая табулированы в книжке Касса, Муди и Патеры. 
Такие функции ветвления оказываются связаны с q-размерностью, то есть являются модулярными формами. 
Если мы введем порядок на множестве весов, то мы можем записать связь струнных функций с функциями ветвления в матричном виде. При этом матрица M содержит кратности весов в модулях g (по строчкам), а обратная матрица $M^{-1}$ -- рекуррентные соотношения, то есть коэффициенты веера $s(\Gamma)$. 
Теперь рассмотрим подалгебру a алгебры g и предположим, что есть сплинт, то есть корневая система g раскладывается в объединение корневой системы a и образа корневой системы s. 
Тогда мы можем записать характер через функции ветвление на модули a, а для них воспользоваться соотношением, следующим из существования сплинта. В результате мы связываем функции ветвления g с крышкой на g и g с крышкой на a.

То есть мы продемонстрировали возникновение сингулярных элементов модулей аффинных алгебр Ли в coset-моделях конформной теории поля. Показали, что сингулярные элементы определяют структуру модуля, а их разложение позволяет вычислять функции ветвления. 
Кроме того, мы продемонстрировали связь разложения сингулярных элементов с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда. Затем мы показали, что в случае существования расщепления коэффициенты ветвления совпадают с кратностями весов в модуле алгебры, которая не является подалгеброй g. 
Еще мы обсудили следствия сплинта для аффинных алгебр Ли.
\end{document}

### 2012-03-03 AffineLieAlgebras/Thesis/common.tex
Started second SLE paper. Some changes in thesis

@@
 Материалы диссертации опубликованы в $8$ печатных работах, из них $3$ статьи в
-рецензируемых журналах~\citemy{2010arXiv1007.0318L,2010LyakhovskyNazarovTMF,2011arXiv1111.6787L}, $4$ статьи в
+рецензируемых журналах~\citemy{2010arXiv1007.0318L,2011arXiv1102.1702L,2011arXiv1111.6787L}, $4$ статьи в
 сборниках тезисов и трудов конференций \cite{2011arXiv1112.4354N,2010LyakhovskyNazarovMQFT,Nazarov2008,NazarovACSM2009}, и в препринте \cite{2011arXiv1107.4681N}.
@@
 \mkcommonsect{contrib}{Личный вклад автора}{%
-Текст раздела
+
 }

### 2012-03-03 AffineLieAlgebras/Splints/paper.tex
Started second SLE paper. Some changes in thesis

@@
 
-In \cite{2010arXiv1007.0318L} it was proven that branching coefficients $%
-b_{\xi }^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
+In \cite{2010arXiv1007.0318L} it was proven that singular branching coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
 \hookrightarrow \frak{g}$ are subject to the set of recurrent relations:
@@
 \begin{array}{c}
-b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
 \sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
@@
 \left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
-}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
+}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
 }\right) .
@@
 \end{eqnarray}
-and $\pi$ is the projection operator. When an injection is maximal the
+and $\pi$ is the projection operator.
+Inside the main Weyl chamber $C_{\mathfrak{a}}$ singular branching coefficients coincide with branching coefficients: $ b_{\xi }^{\left( \mu \right) }=k_{\xi }^{\left( \mu \right) }\; \forall \xi\in C_{\mathfrak{a}}$.
+When an injection is maximal the
 projection becomes trivial and the relation (\ref{recurrent rel}) is
@@
 \begin{array}{c}
-b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
 \sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
@@
 \left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
-\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
+\gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right) }\right) .
 \end{array}
@@
 injective splints:
-\[
+\begin{equation}
+\label{eq:1}
 \begin{array}{cc||c|c}
@@
 \hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
-& C_{r}(r\geq 3) & D_{r} & \oplus ^{r}A_{1} \\ \hline
+(*)& C_{r}(r\geq 3) & \oplus ^{r}A_{1} &  D_{r} \\ \hline
 \hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
@@
 \end{array}
-\]
+\end{equation}
+
 Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\frak{s}})
@@
 weights.
+
+Note that in the case of $C_{r}$-series (marked with the star in table \eqref{eq:1}) metrical embedding $\Delta_{D_{r}}\to \Delta_{C_{r}}$ does not lead to the appearance of regular subalgebra $\mathfrak{a}$ (See \cite{dynkin1952semisimple}).
 
@@
 The next step is to construct the full $W_{\frak{s}}$-orbit $\Phi _{\frak{s}%
-}^{\left( \widetilde{\mu }\right) }$  in $P_{\frak{s}}$. It is easily seen
+}^{\left( \widetilde{\mu }\right) }$  in $P_{\frak{s}}$. It is necessary to check
 that its coimage belongs to $\bar{C_{\frak{a}}}$ and that the set $\phi
@@
 $\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{%
-\frak{c}}\right\} $). Thus we have constructed all the formal elements\ with
+\frak{c}}\right\} $). Provided this condition is valid we have constructed all the formal elements\ with
 the appropriate sign factors that after being added to $\Phi _{\frak{g}%
@@
 
-\item
-Type 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
-^{r}A_{1}}). $
-
-The situation in this case is eqivalent to the previous one and
-the additional edges are constructed similarly.
+%%  \item
+%%  Type 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus
+%%  ^{r}A_{1}}). $
+%%  
+%%  The situation in this case is eqivalent to the previous one and
+%%  the additional edges are constructed similarly.
 \item

### 2012-03-03 AffineLieAlgebras/Splints/paper2.tex
Started second SLE paper. Some changes in thesis

@@
 \documentclass[12pt]{article}
+ \textheight=24cm
+ \textwidth=16.5cm
+ \topmargin=-1.5cm
+ \oddsidemargin=-0.25cm
+
 \usepackage{amsfonts}
@@
 \usepackage[english]{babel}
-
-%TCIDATA{OutputFilter=Latex.dll}
-%TCIDATA{LastRevised=Mon Oct 10 18:16:16 2011}
-%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
-%TCIDATA{CSTFile=article.cst}
 
@@
 \newcommand{\hfg}{\hf_{\gf}}
-
-%\input{tcilatex}
 
@@
 Consider simple Lie algebra $\gf$ with a root system $\Delta$. Let
-$\af_{1}\subset \gf$ be its reductive subalgebra, such that
-$\Delta_{1}\subset\Delta$. Irreducible highest-weight modules of
+$\af_{1}\subset \gf$ be its reductive subalgebra of the same rank, such that
+$\Delta_{\af}\equiv\Delta_{1}\subset\Delta$ and $Q_{\af}\subset Q$, where $Q$ is the root lattice. Irreducible highest-weight modules of
 $\gf$ and $\af$ are denoted by $L^{\mu}$ and $L^{\nu}_{\af}$
@@
 this by $\Delta \approx (\Delta_1,\Delta_2)$. Each component $\Delta_1$ and $\Delta_2$ is a "stem''
-of the splint $%
-(\Delta_1,\Delta_2)$.
+of the splint.
 
@@
 
-Since the singular element of a $\gf$-module $L^{\mu}$ can be
+Since the singular element of $L^{\mu}$ can be
 written as $\Psi _{\frak{g}}^{\left( \mu \right) }=e^{-\rho }
@@
 $q=e^{2\pi i \tau}$ we can rewrite this identity as the relation
-imposed on theta-functions $\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in P_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$:
+imposed on theta-functions $\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in Q_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$:
 \begin{multline}
@@
 These branching functions are connected to $q$-dimension of module $\mathrm{dim}_{q}L^{\hat \mu}_{\gfh}=\sum_{n=0}^{\infty}q^{n}\sum_{\nu\in P} b^{(\hat \mu)}_{\nu}(n) \mathrm{dim }L^{\nu}_{\gf}=\sum_{\nu\in P}b^{(\hat\mu)}_{\nu}(q) \mathrm{dim} L^{\nu}_{\gf}$.
-It is well-known \cite{gannon2006moonshine} that $q$-dimension is a modular function for some $\Gamma\subset SL_{2}(\mathbb{Z})$, so branching functions $b^{(\hat \mu)}_{\nu}(q)$ have modular properties.
+It is well-known that $q$-dimension is a modular function for some $\Gamma\subset SL_{2}(\mathbb{Z})$  \cite{gannon2006moonshine}, so branching functions $b^{(\hat \mu)}_{\nu}(q)$ have modular properties.
 
@@
 We see that the similar matrix relation holds for branching
-functions $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}
+functions $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}\;
 b_{(\gfh\downarrow\gf)}(q)$ and we can write
-$\sigma(q)=M_{\af}\cdot b_{(\gfh\downarrow\af)}(q)$. So if we know
+$\sigma(q)=M_{\af}\; b_{(\gfh\downarrow\af)}(q)$. So if we know
 branching coefficients for the embedding $\gf\subset\gfh$ (for
@@
 
-%%
-%%
-%%  In the present paper we provide alternative proof of the main statement of paper [LN-2011-Splints] which uses graded commutative structure on vector space of universal enveloping algebra $U(n^{-})$.
-%%
-%%  Con
-%%  
-%%  
-%%  Consider decomposition of simple Lie algebra $\gf=\nfp\oplus \hf \oplus \nfm$.
-Verma module $M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+})$.
-$S(\nfm)=\{x_{1}\dots x_{l}:x_{i}\in\nfm\}_{l=0}^{\infty}$
-%%  \begin{theorem}
-%%    Fix some ordering $\alpha_{1},\dots,\alpha_{s}$ on the set of positive roots $\Delta^{+}$ and obtain the ordering on the basis $f_{1},\dots,f_{s}$ of $\nfm$.
-Then monomials $f_{1}^{n_{1}} \dots f_{s}^{n_{s}}$ form a basis in $U(\nfm)\sim M^{\lambda}$ and $U(\nfm)\sim \mathbb{Z}^{s}_{\geq 0}$.
-%%  \end{theorem}
-%%  \begin{statement}
-%%    Let $\Delta^{+}_{\gf}=\Delta^{+}_{\af_{1}}\cup \Delta^{+}_{\af_{2}}$ be a splint positive root system of simple Lie algebra $\gf$.
-Then $M^{\lambda}_{\gf}\sim M^{\lambda}_{\af_{1}}\oplus M^{\lambda}_{\af_{2}}$.
-%%    \begin{proof}
-%%      Basis of $M^{\lambda}_{\gf}$ is given by $f_{1}^{n_{1}}\dots f_{s_{1}}^{n_{s_{1}}} f_{s_{1}+1}^{n_{s_{1}+1}}\dots f_{s_{1}+s_{2}}^{n_{s_{1}+s_{2}}}$, where $f_{1},\dots, f_{s_{1}}\in \nfm_{\af_{1}}$ and $f_{s_{1}+1},\dots,f_{s_{1}+s_{2}}\in \nfm_{\af_{2}}$
-%%    \end{proof}
-%%  \end{statement}
-%%  Now consider irreducible $\gf$-module $L_{\gf}^{\mu}=M^{\mu}_{\gf}/I^{\mu}_{\gf}$t
-%%  
 \bibliography{bibliography}{}

### 2012-03-03 AffineLieAlgebras/Thesis/1.tex
Started second SLE paper. Some changes in thesis

@@
 
-Рассмотрим интегрируемый модуль $L^{\mu }$ алгебры $\gf$ со старшим весом  $\mu$ и пусть  $\af\subset\gf$ -- редуктивная подалгебра $\gf$. Модуль $L^{\mu}$ полностью приводим по отношению к $\af$.
+Рассмотрим интегрируемый модуль $L^{\mu }$ алгебры $\gf$ со старшим весом  $\mu$ и пусть  $\af\subset\gf$ -- редуктивная подалгебра $\gf$. Модуль $L^{\mu}$ вполне приводим по отношению к $\af$.
 \begin{equation*}
@@
 \end{equation}
-Упорядочение корней в  $\co{\Delta _{\af}}$ индуцирует натуральное упорядочение весов в $P_{\af}$. Обозначим через $\gamma_{0}$ наименьший вектор $\Phi _{\af\subset \gf}$. Множество
+Упорядочение корней в  $\co{\Delta _{\af}}$ индуцирует естественное упорядочение весов в $P_{\af}$. Обозначим через $\gamma_{0}$ наименьший вектор $\Phi _{\af\subset \gf}$. Множество
 \begin{equation}
@@
 \end{equation*}
-Эти выражения представляют собой факторизацию аномального элемента  $\Psi^{\mu}$ и мы видим, что они содержат комбинации сингулярных элементов $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ модулей $L_{\widetilde{\afb}}^{\eta }$ подалгебры  $\widetilde{\afb}$:
+Эти выражения обеспечивают факторизацию аномального элемента  $\Psi^{\mu}$ и мы видим, что они содержат комбинации сингулярных элементов $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ модулей $L_{\widetilde{\afb}}^{\eta }$ подалгебры  $\widetilde{\afb}$:
 \begin{equation*}

### 2012-03-17 AffineLieAlgebras/SLE/paper.tex
Some work on SLE paper

\documentclass[a4paper]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{multicol}
\usepackage{color}
\usepackage{graphicx}
\usepackage{hyperref}

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

\begin{document}

\title{SLE martingales in coset conformal field theory}
\author{Anton Nazarov}
\maketitle
\section{Introduction}
\label{sec:introduction}

Generalizing results of papers \cite{bettelheim2005stochastic,santachiara2008sle,alekseev2010sle} we
consider Schramm-Loewner evolution $SLE_{\kappa}$ with additional Brownian motion on coset space
$G/A$ characterised by parameter $\tau$ proposed in our paper \cite{2011arXiv1112.4354N}. We consider correlation functions in coset models of
conformal field theory which satisfy martingale conditions with respect to this stochastic process.
Since all minimal unitary models of conformal field theory can be obtained from coset construction
for certain choice of Lie group $G$ and subgroup $A$ \cite{difrancesco1997cft} these correlation functions correspond to SLE
observables appearing as the scaling limit of lattice observables. Trace of
Schramm-Loewner $\gamma_{t}$ evolution describes critical domain wall in lattice models.

 Consider upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$. We denote this slit domain by $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$. Conformal map from $\mathbb{H}_{t}$ to $\mathbb{H}$ is denoted by $g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ and satisfies stochastic differential equation \cite{schramm2000scaling}:
\begin{equation}
\label{eq:19}
  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
\end{equation}
where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.

For us it is more convenient to use map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
\begin{equation}
  \label{eq:20}
       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}  
\end{equation}

It is natural to study the problem in upper half-plane  and consider correlation
functions of boundary conformal field theory with boundary condition changing operators sitting at
the tip of SLE trace and at the infinity.

So we are to consider $N$-point boundary correlation functions on the upper half-plane of the form 
\begin{equation}
  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\}_{i=1}^{N})_{\mathbb{H}_{t}}=
\left<\varphi(z_{t}) \phi_{1}(z_{1},\bar z_{1}) \dots \phi_{n}(z_{n},\bar z_{n})
      \varphi(\infty)\right>,
    \label{eq:2}
\end{equation}
where $\phi_{i}$ are bulk primary fields and $\varphi(z_{t})$ is boundary condition changing operator. We assume conformal invariance of boundary conditions so boundary states satisfy Cardy conditions \cite{cardy1989boundary,cardy1986effect,cardy1984conformal}.

 We consider Schramm-Loewner evolution with additional Brownian motion on $G/A$-coset space \cite{2011arXiv1112.4354N}. Denote by $\mathcal{K}$ Killing form of Lie algebra $\gf$ corresponding to Lie group $G$ and by $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) the  generators of $\gf$-representation ($\af$-representation) corresponding to primary field $\phi_{i}$.
Primary fields in coset models are labeled by pairs $(\lambda,\eta)$ of weights $\gf$ and $\af$-representations. For each $\lambda$ possible values of $\eta$ are those which appear in decomposition of representation $L^{(\mu)}_{\gf}=\bigoplus_{\eta} H^{\lambda}_{\eta}\otimes L^{(\eta)}_{\af}$. Some pairs are equivalent, we discuss and use this equivalence relation later. 
We assume that boundary field $\varphi$ is also primary and labeled by weights $(\mu,\nu)$.

  We use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite expression \eqref{eq:2} in the whole upper half plane:

\begin{equation}
  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{i}} 
  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{\bar h_i}
  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
  \label{eq:1}
\end{equation}
We can extend the definition of $\mathcal{F}$ to the whole plane by doubling the number of fields $\phi_{i}$ \cite{cardy2004boundary,cardy1984conformal} and consider $w_{i},\bar w_{i}$ as independent variables. To simplify notation we will write $\mathcal{F}(\left\{w_{i}\right\}_{i=1}^{2N})$.

Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:2}) gives us
\begin{equation*}
  -\frac{2h_{i}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}.
\end{equation*}
We denote by $\mathcal{G}_{i}$ generator of infinitesimal transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$. Then normalization condition of additional $\dim\gf$-dimensional Brownian motion \eqref{eq:5} to $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation \eqref{eq:2} is
\begin{equation}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right).
\label{eq:3}
\end{equation}
 Ito formula  gives us the expression for the differential of $\mathcal{F}$, it should be zero due to martingale condition:
\begin{equation}
d \mathcal{F}_{\mathbb{H}_{t}}= \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}=0
\label{eq:8}
\end{equation}
Substitute definition \eqref{eq:3} and get 
\begin{equation}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0,
  \label{eq:4}
\end{equation}
where
\begin{equation*}
  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right);\quad \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}};\; \tilde{\mathcal{J}}^{b}_{{-n}}=-\sum_{i}\frac{\tilde{t}^{b}_{i}}{(w_{i}-z)^{n}}
\end{equation*}
This equation is equivalent to following algebraic condition on boundary state $\varphi(0)\left|0\right>$:
\begin{equation}
  \label{eq:7}
  <0|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\varphi(0)|0>=0
\end{equation}
Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that $|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\varphi(0)|0>$ is null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in coset theory
\begin{equation}
  \label{eq:18}
\begin{array}{l}
  L_{n}=L_{n}^{\gf}-L_{n}^{\af}\\
  \left[L_{n}^{\gf},J^{a}_{m}\right]=-m J^{a}_{n+m}\\
  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m}\\
  \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}
\end{array}
\end{equation}
 it is more convenient to act by $L_{2}^{\gf}$ and $\left(L_{1}^{\gf}\right)^{2}$. 
 Acting with $L_{2}^{\gf}$ we get
\begin{equation*}
  L_{2}^{\gf}\psi= \left(-8 L_{0}-c+ 3 \kappa L_{0}+\frac{1}{2}\tau (k \dim\gf-x_{e}k\dim\af)\right) \varphi_{(\mu,\nu)}=0
\end{equation*}
We use $L_{0} \varphi_{(\mu,\nu)}=h_{(\mu,\nu)} \varphi_{(\mu,\nu)}$ where conformal weight $h_{(\mu,\nu)}= \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k x_{e}+h^{\vee}_{\af})}\right)$ and central charge $c=\frac{k\dim \gf}{k+h^{\vee}_{\gf}}-\frac{x_{e}k\dim \af}{x_{e} k+h^{\vee}_{\af}}$ and get relation on $\kappa,\tau$:
\begin{equation}
  \label{eq:28} (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0
\end{equation}
Second relation appears as the result of $L_{1}^{\gf}$-action:
\begin{equation}
  \label{eq:21}
 -12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
(C_{\mu}-\tilde{C}_{\nu})=0,
\end{equation}
 where $C_{\mu}=(\mu,\mu+2\rho), \tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ is the eigenvalue of quadratic Casimir operators $\sum_{a}t^{a}t^{a}, \sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ of Lie algebras $\gf$ and $\af$.

From equations \eqref{eq:28},\eqref{eq:17} we immediately get $\kappa,\tau$ for each pair $(\mu,\nu)$ of $\gf$ and $\af$-weights.

It is also possible to consider coset theory as $G\times A$  gauge theory and impose constraints on physical states later (See \cite{hwang1993brst,kogan1997knizhnik,gawdzki1988g,figueroa89equivalence}). In this case second term in equation \eqref{eq:3} will include sum over $\gf$ and $\af$ generators and two parameters of Brownian motion $\tau_{\gf}$ and $\tau_{\af}$.

Coset  models are specified by Lie algebra
$\gf$ and its subalgebra $\af$. Denote by $J_{n}^{a}$ the generators of affine Lie algebra $\gfh$
and by $\tilde{J}_{n}^{b}$ the generators of $\afh$, so that $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b}
J^{a}_{n}$. 
Virasoro generators in coset models are given by the difference of Sugawara expressions
of $\gf$ and $\af$-WZNW models:
\begin{equation*} L_{n}=L_{n}^{\gf}-L_{n}^{\af}
\end{equation*}
 Commutation relations of Virasoro generators with generators of subalgebra $\afh$
are trivial
\begin{equation}
  \label{eq:26} \left[L_{n},\tilde{J}^{b}_{m}\right]=0
\end{equation}

Commutation relations between generators of $\gfh$ and Virasoro generators are now
\begin{equation}
  \label{eq:1}
  \left[ L_{n}, J_{m}^{a} \right] = [L_{n}^{\gf}-L_{n}^{\af},J_{m}^{a}]= 
\end{equation}

Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields
 $A,
\bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}.
 Then fields
are labeled by pairs of weights $(\mu,\nu)$, where $\mu$ is the weight of $\gfh$ and $\nu$ is the
weight of $\afh$ correspondingly. But there are selection rules, i.e. the branching functions for
certain pairs of weights $(\mu,\nu)$ vanish. There is also a redundancy, i.e. non-vanishing
branching functions for distinct pairs $(\mu,\nu)$ turn out to be identical
\cite{fuchs1996resolution,schellekens1990field}.

So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ of
algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$. Some
pairs are equivalent. This equivalence is given by the action of so called ``simple currents''
$(J,\tilde{J})$, which are certain elements of outer automorphisms group $\mathcal{O}(\gfh)\times
\mathcal{O}(\afh)\approx B(G)\times B(A)$ of $\gfh\times\afh$, where $B(G)$ is center of Lie group
G. We can think of simple currents as of primary fields and their action on fields of theory are
then given by fusion product \cite{difrancesco1997cft}. So primary fields of coset model are given
by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where
$(J,\tilde J)$ such that their conformal weights are equal: $h_{J}-h_{\tilde{J}}=0$.

Conformal weight of coset primary field is equal to
\begin{multline}
L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b
\tilde{J}^b_0 \tilde{J}^b_0 \right) \left|\phi_{(\mu,\nu)}\right>=\\
\left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
\end{multline} It is possible to obtain analogues of Knizhnik-Zamolodchikov equations for coset
models \cite{kogan1997knizhnik}:
\begin{equation} \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq
j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde
t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots
\phi_{N}(z_{N})\right>=0
  \label{eq:6}
\end{equation}

Let us introduce Schramm-Loewner evolution corresponding to coset models. The idea is to constrain
additional Brownian motion on group manifold to the factor space $G/A$.

To study SLE on $G/A$ factor space we restrict random walk on group manifold by the choice of basis
in $\gf$. Assume that generators $\{J^{a};\; a=1\dots \dim\gf\}$ are chosen in such way that
$\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\;
a=\dim\gf-\dim\af\dots \dim\gf\}$ are the generators of subalgebra
$\af\subset \gf$. Now we can consider $(\dim\gf-\dim\af)$-dimensional Brownian
motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \;
d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\dim\gf-\dim\af$.

Then for generator of field transformation we can write
\begin{equation} \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa}
d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\dim\gf-\dim\af}\left(d
\theta ^{a} t^{a}_{i}\right)\right)
\label{eq:5}
\end{equation}
 Substituting to equation \eqref{eq:8} we get martingale condition

\begin{equation} \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa
\mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\dim\gf-\dim\af}
\mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right) \mathcal{F}_{\mathbb{H}}=0
\label{eq:9}
\end{equation}

which can be rewritten as the requirement for
\begin{equation} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
\left(\sum_{a=1}^{\dim\gf-\dim\af}J^{a}_{-1}J^{a}_{-1}\right)\right)
\phi_{(\mu,\nu)}
\label{eq:10}
\end{equation}
 to be level two null-field.

 It is not always convenient to work with generators
orthogonal with respect to Killing form $\mathcal{K}$, sometimes it is preferable to use Chevalley
or Cartan-Weyl basis. So we change normalization condition of additional
$\dim\gf$-dimensional Brownian motion \eqref{eq:5} to $\mathbb{E}\left[d\theta^{a}\;
d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation
\eqref{eq:2} is
\begin{equation*} \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa}
d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d
\theta ^{a} t^{a}_{i}\right)\right).
\end{equation*}
 Martingale condition \eqref{eq:8} can be written as
\begin{equation*} \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa
\mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
\sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)
\mathcal{F}_{\mathbb{H}}=0.
\end{equation*}
 This equation can again be rewritten as the requirement for
\begin{equation} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
\left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
\phi_{(\mu,\nu)}
\label{eq:30}
\end{equation}
 to be level two null-field.

Acting with $L_{2}$ we get
\begin{equation*}
  L_{2}\psi= \left(-8 L_{0}+c/2+ 3 \kappa L_{0}+\frac{1}{2}\tau k \dim\gf\right)
\phi_{(\mu,\nu)}
\end{equation*}
\begin{equation}
  \label{eq:28} (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
\end{equation}

Now we act with $L_{1}^{2}$  and obtain
\begin{equation}
  \label{eq:17} 12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
(C_{\mu}-\tilde{C}_{\nu})=0,
\end{equation}
 where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator
$\sum_{a}t^{a}t^{a}$. We need to get one more equation since we
have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so
$L_{1}\psi=0$ and then $J_{1}^{a}L_{1}\psi=0,\; \tilde{J}_{1}^{b} L_{1}\psi=0$, so

\begin{equation}
L_{1} \psi=L_{1}\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
\left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
\phi_{(\mu,\nu)}
\end{equation}

\begin{equation*}
L_{1}\psi = \left(-6 L_{-1}+\kappa (2  L_{-1} L_{0}+L_{0}) + \tau \sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{0}\right)
\phi_{(\mu,\nu)}
\end{equation*}
\begin{equation*}
  L_{1}^{2}\psi= \left(-12 L_{0}+\kappa (4  L_{0}^{2}+2 L_{0}) + \tau \sum_{a=1}^{\dim\gf}J^{a}_{0}J^{a}_{0}\right)
\phi_{(\mu,\nu)}
\end{equation*}
\begin{equation*}
  J_{1}^{a}L_{1} \psi= \left(-6 J_{0}^{a}+\kappa (2  J_{0}^{a} L_{0}+J_{0}^{a}) + \tau
    \sum_{b=1}^{\dim\gf}\sum_{c=1}^{\dim\gf}i f^{abc}J^{c}_{0}J^{b}_{0}+k\tau J_{0}^{a}\right)
\phi_{(\mu,\nu)}
\end{equation*}

\begin{equation*}
  L_{2}\psi= \left(-8 L_{0}+c/2+ 3 \kappa L_{0}+\frac{1}{2}\tau k \dim\gf\right)
\phi_{(\mu,\nu)}
\end{equation*}

\begin{eqnarray*}
  (3\kappa-8) h_{(\mu,\nu)}+c/2+\frac{1}{2}\tau k \dim\gf=0\\
  -12 h_{(\mu,\nu)}+\kappa (4 h_{(\mu,\nu)}^{2}+2 h_{(\mu,\nu)}) +\tau C(\mu) =0\\
  (-6 +\kappa (2 h_{(\mu,\nu)}+1)+\tau
\end{eqnarray*}
\begin{equation}
  \label{eq:29} \left(-6 + \kappa + \tau + 2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0}
\phi_{(\mu,\nu)}=0
\end{equation}

Acting on \eqref{eq:30} with $L_{2}$ and $L_{1}^{2}$ we can obtain equations \eqref{eq:28} and
\eqref{eq:17}. To get more equations we can act by $\afh$-generators $\tilde{J}^{b}_{1}$ and $L_{1}$
similarly to what was done with $J^{3}_{1}$ to get equation \eqref{eq:29}.

To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov
equations \eqref{eq:6} as was done for WZNW-models in paper \cite{alekseev2010sle}.

Now consider simple example. Let $G=SU(2)$ and $A=U(1)$, and corresponding Lie algebras
$\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator
$J^{3}$, $\af\subset\gf$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.

 The equation \eqref{eq:10} is now
\begin{equation}
  \label{eq:11} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
\left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
\end{equation}
 If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\;
J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
\begin{equation} \psi= \left(-2
L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right)
\phi_{(\mu,\nu)}
\label{eq:12}
\end{equation}
 which is similar to the equations for parafermionic fields introduced in paper
\cite{santachiara2008sle}.

Central charge in this case is equal to
\begin{equation}
  \label{eq:14} c=\frac{2(k-1)}{k+2}
\end{equation}

Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
\begin{equation}
  \label{eq:13} L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{(\mu,\nu)}=0,
\end{equation}
 and obtain
\begin{equation}
  \label{eq:28} (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
\end{equation}
 Another equation can be obtained by action of $L_{1}^{2}$
\begin{equation}
  \label{eq:15} L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau
(J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{(\mu,\nu)}=0
\end{equation}
 Since
$J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$
we have
\begin{equation}
  \label{eq:17} 12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
(C_{\mu}-\tilde{C}_{\nu})=0,
\end{equation}
 where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator
$\sum_{a}t^{a}t^{a}$. For $u(1)$ it is just $\nu^{2}$. We need to get one more equation since we
have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so
$L_{1}\psi=0$ and then $J_{1}^{3}L_{1}\psi=0$, so
\begin{equation}
  \label{eq:29} \left(-6 + \kappa + \tau + 2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0}
\phi_{(\mu,\nu)}=0
\end{equation}

Turn to the case $k=2, \;c=1/2$ which corresponds to square lattice Ising model. We have three
non-equivalent fields numbered by the pairs of $su(2)$ and $u(1)$ weights, which are $\phi_{(0,0)},
\; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$. The
equation \eqref{eq:29} is trivial for $\phi_{(0,0)}$ and $\phi_{(0,2)}$, so the equations
\eqref{eq:17}, \eqref{eq:28} are consistent although we do not know how to interpret $\tau$ in
context of the Ising model. If we consider the field $\phi_{(1,1)}$ we have no solution for
$\kappa,\tau$, so we see that not every primary field corresponds to some boundary condition
changing operator.

\section{Algebraic equations}
\label{sec:algebraic-equations}

\section{Examples}
\label{sec:examples}

\section{Conclusion}
\label{sec:conclusion}

\bibliography{bibliography}{}
\bibliographystyle{utphys}

\end{document}

### 2012-03-17 AffineLieAlgebras/SLE/computations.m

@@ -85,3 +85,188 @@ Sum[f, {i, i   }] evaluates the sum   max  f
             . Sum[f, i] gives the indefinite sum \[Sum] f.
                                                    i
 
+
+kappa:=((8*h+c)*(cm-cn)-6*h*(k*dimg-k*xe*dima))/(3*h*(cm-cn)-h*(2h+1)*(k*dimg-k*xe*dima))
+
+tau:=12*h/(cm-cn)-2*h*(2*h+1)/(cm-cn)*kappa
+
+Simplify[{kappa,tau} /. {h->cm/(2*(k+hg))-cn/(2*(k*xe+ha)), c->k*dimg/(2*(k+hg))-k*xe*dima/(2*(k*xe+ha))}]/.{cn->1,k->2,dimg->3,dima->1,hg->2,ha->0,xe->1}/.{cm->4}
+
+
+
+Solve[{(3*kp-8)*h-c+tu*(k*dimg-xe*k*dima)==0,-12*h+2*kp*h*(2*h+1)+tu*(cm-cn)==0},{kp,tu}]/.{h->cm/(2*(k+hg))-cn/(2*(k*xe+ha)), c->k*dimg/(2*(k+hg))-k*xe*dima/(2*(k*xe+ha))}/.{cn->1,k->2,dimg->3,dima->1,hg->2,ha->0,xe->1}/.{cm->1}
+
+                          9
+Out[34]= {{kp -> 8, tu -> --}}
+                          16
+
+Syntax::sntxf: "(k*xe+ha))}/.{cn->1,k->2,dimg->3,dima->1,hg->2,ha->0,xe->1}/.{
+      cm->" cannot be followed by "}".
+
+                 92        29
+Out[31]= {{kp -> --, tu -> --}}
+                 11        88
+
+                            3
+Out[30]= {{kp -> 7, tu -> -(-)}}
+                            4
+
+                                                                          2
+                   -3 (-c - 8 h) - 48 h         2 (c - 10 h + 2 c h + 16 h )
+Out[29]= {{kp -> -(--------------------), tu -> ----------------------------}}
+                   -9 h + 8 h (1 + 2 h)                  -1 + 16 h
+
+                   -((cm - cn) (-c - 8 h)) - 12 h (dimg k - dima k xe)
+Out[28]= {{kp -> -(---------------------------------------------------), 
+                   -3 (cm - cn) h + 2 h (1 + 2 h) (dimg k - dima k xe)
+ 
+>     tu -> 
+ 
[…]

### 2012-04-02 AffineLieAlgebras/SLE/paper.tex
Abstract rewritten, paper reorganized.

@@
 \begin{document}
-
 \title{SLE martingales in coset conformal field theory}
@@
 \maketitle
+\begin{abstract}
+  The problem is to provide a way for the concurrent use of Scramm-Loewner evolution (SLE) and conformal field theory (CFT).
+Both SLE and CFT are popular instruments to study critical behavior of physical models in two dimensions, but they use different objects.
+While Scharmm-Loewner evolution has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory.
+In order to connect two approaches we consider CFT correlation functions which are martingales with respect to SLE.
+We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models.
+\end{abstract}
+
 \section{Introduction}
@@
 
-Generalizing results of papers \cite{bettelheim2005stochastic,santachiara2008sle,alekseev2010sle} we
+SLE describes critical behavior. It is convenient for strict mathematical proofs. For many lattice models  the convergence of  domain walls to SLE was proved.
+
+CFT on the other hand is formulated in terms of families of quantum fields which usually has no natural interpretation in microscopic terms.
+On the other hand CFT has efficient computational tools such as Virasoro symmetry, Knizhnik-Zamolodchikov equations, fusion algebra etc and provides numerous predictions, such as celebrated Cardy formula which gives crossing probability for critical percolation.
+
+Combination of these two approaches should be immensely powerful, so it is important to find objects which can be studied from both points of view.
+Correlation functions of CFT which are martingales with respect to Schramm-Loewner evolution are such objects.
+They are actively studied.
+
+We present new class of such observables.
+We consider correlation functions in coset conformal field theory which are martingales with respect to Schramm-Loewner evolution with additional random motion on factor of group $G$ by subgroup $A$.
+Using Knizhnik-Zamolodchikov equations we establish necessary and sufficient conditions on such functions and derive relations connecting parameters of SLE and CFT.
+We then check the consistency of these results with the earlier results obtained for parafermionic observables and general Cardy conditions on boundary states in conformal field theory.
+
+\section{Martingale conditions}
+\label{sec:mart-cond}
+
+We
 consider Schramm-Loewner evolution $SLE_{\kappa}$ with additional Brownian motion on coset space
@@
 We denote by $\mathcal{G}_{i}$ generator of infinitesimal transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$.
-Then normalization condition of additional $\dim\gf$-dimensional Brownian motion \eqref{eq:5} to $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation \eqref{eq:2} is
+We normalize additional $\dim\gf$-dimensional Brownian motion as $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation \eqref{eq:2} is equal to
 \begin{equation}
@@
 
-From equations \eqref{eq:28},\eqref{eq:17} we immediately get $\kappa,\tau$ for each pair $(\mu,\nu)$ of $\gf$ and $\af$-weights.
+From equations \eqref{eq:28},\eqref{eq:21} we immediately get $\kappa,\tau$ for each pair $(\mu,\nu)$ of $\gf$ and $\af$-weights.
+
+But correlation functions in coset conformal field theory must satisfy (generalized) Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} which are of the form
+\begin{equation}
+  \label{eq:16}
+ \left[ \frac{1}{2}\frac{\partial}{\partial w_{i}} +\sum_{j\neq i} \left( \frac{\sum_{a}t_{i}^{a}t_{j}^{a}}{k+h^{\vee}}-\frac{\sum_{b}\tilde t_{i}^{b}\tilde t_{j}^{b}}{x_{e}k+h_{\af}^{\vee}}\right) \right]\mathcal{F}_{\mathbb{H}}=0
+\end{equation}
+Rewrite the equation as
+\begin{equation}
+  \label{eq:22}
+  \left[ \frac{1}{2}\frac{\partial}{\partial w_{i}} +\sum_{j\neq i} \left( \frac{\sum_{a}t_{i}^{a}t_{j}^{a}}{k+h^{\vee}}-\frac{\sum_{b}\tilde t_{i}^{b}\tilde t_{j}^{b}}{x_{e}k+h_{\af}^{\vee}}\right) \right]\mathcal{F}_{\mathbb{H}}=0
+\end{equation}
+
+From this relations and equation \eqref{eq:8} we can write sufficient conditions for SLE martingale to be CFT correlation function:
+\begin{equation}
+  \label{eq:23}
+  M x = 0
+\end{equation}
 
@@
 
-Coset  models are specified by Lie algebra
-$\gf$ and its subalgebra $\af$. Denote by $J_{n}^{a}$ the generators of affine Lie algebra $\gfh$
-and by $\tilde{J}_{n}^{b}$ the generators of $\afh$, so that $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b}
-J^{a}_{n}$. 
-Virasoro generators in coset models are given by the difference of Sugawara expressions
-of $\gf$ and $\af$-WZNW models:
-\begin{equation*} L_{n}=L_{n}^{\gf}-L_{n}^{\af}
-\end{equation*}
- Commutation relations of Virasoro generators with generators of subalgebra $\afh$
-are trivial
-\begin{equation}
-  \label{eq:26} \left[L_{n},\tilde{J}^{b}_{m}\right]=0
-\end{equation}
+\subsection{Examples}
+\label{sec:examples-1}
 
-Commutation relations between generators of $\gfh$ and Virasoro generators are now
-\begin{equation}
-  \label{eq:1}
-  \left[ L_{n}, J_{m}^{a} \right] = [L_{n}^{\gf}-L_{n}^{\af},J_{m}^{a}]= 
-\end{equation}
+Minimal models $su(2)/u(1)$.
 
-Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields
- $A,
-\bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}.
- Then fields
-are labeled by pairs of weights $(\mu,\nu)$, where $\mu$ is the weight of $\gfh$ and $\nu$ is the
-weight of $\afh$ correspondingly. But there are selection rules, i.e. the branching functions for
-certain pairs of weights $(\mu,\nu)$ vanish. There is also a redundancy, i.e. non-vanishing
-branching functions for distinct pairs $(\mu,\nu)$ turn out to be identical
-\cite{fuchs1996resolution,schellekens1990field}.
+\section{Outlook}
+\label{sec:outlook}
 
-So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ of
-algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$. Some
-pairs are equivalent. This equivalence is given by the action of so called ``simple currents''
-$(J,\tilde{J})$, which are certain elements of outer automorphisms group $\mathcal{O}(\gfh)\times
-\mathcal{O}(\afh)\approx B(G)\times B(A)$ of $\gfh\times\afh$, where $B(G)$ is center of Lie group
-G. We can think of simple currents as of primary fields and their action on fields of theory are
-then given by fusion product \cite{difrancesco1997cft}. So primary fields of coset model are given
-by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where
-$(J,\tilde J)$ such that their conformal weights are equal: $h_{J}-h_{\tilde{J}}=0$.
-
-Conformal weight of coset primary field is equal to
-\begin{multline}
-L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b
-\tilde{J}^b_0 \tilde{J}^b_0 \right) \left|\phi_{(\mu,\nu)}\right>=\\
-\left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
-\end{multline} It is possible to obtain analogues of Knizhnik-Zamolodchikov equations for coset
-models \cite{kogan1997knizhnik}:
-\begin{equation} \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq
-j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde
-t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots
-\phi_{N}(z_{N})\right>=0
-  \label{eq:6}
-\end{equation}
-
-Let us introduce Schramm-Loewner evolution corresponding to coset models. The idea is to constrain
-additional Brownian motion on group manifold to the factor space $G/A$.
-
-To study SLE on $G/A$ factor space we restrict random walk on group manifold by the choice of basis
-in $\gf$. Assume that generators $\{J^{a};\; a=1\dots \dim\gf\}$ are chosen in such way that
-$\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\;
-a=\dim\gf-\dim\af\dots \dim\gf\}$ are the generators of subalgebra
-$\af\subset \gf$. Now we can consider $(\dim\gf-\dim\af)$-dimensional Brownian
-motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \;
-d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\dim\gf-\dim\af$.
-
-Then for generator of field transformation we can write
-\begin{equation} \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa}
-d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\dim\gf-\dim\af}\left(d
-\theta ^{a} t^{a}_{i}\right)\right)
-\label{eq:5}
-\end{equation}
- Substituting to equation \eqref{eq:8} we get martingale condition
-
-\begin{equation} \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa
-\mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\dim\gf-\dim\af}
-\mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right) \mathcal{F}_{\mathbb{H}}=0
-\label{eq:9}
-\end{equation}
-
-which can be rewritten as the requirement for
-\begin{equation} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
-\left(\sum_{a=1}^{\dim\gf-\dim\af}J^{a}_{-1}J^{a}_{-1}\right)\right)
-\phi_{(\mu,\nu)}
-\label{eq:10}
-\end{equation}
- to be level two null-field.
-
- It is not always convenient to work with generators
-orthogonal with respect to Killing form $\mathcal{K}$, sometimes it is preferable to use Chevalley
-or Cartan-Weyl basis. So we change normalization condition of additional
-$\dim\gf$-dimensional Brownian motion \eqref{eq:5} to $\mathbb{E}\left[d\theta^{a}\;
-d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation
-\eqref{eq:2} is
-\begin{equation*} \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa}
-d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d
-\theta ^{a} t^{a}_{i}\right)\right).
-\end{equation*}
- Martingale condition \eqref{eq:8} can be written as
-\begin{equation*} \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa
-\mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
-\sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)
-\mathcal{F}_{\mathbb{H}}=0.
-\end{equation*}
- This equation can again be rewritten as the requirement for
-\begin{equation} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
-\left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
-\phi_{(\mu,\nu)}
-\label{eq:30}
-\end{equation}
- to be level two null-field.
-
-Acting with $L_{2}$ we get
-\begin{equation*}
-  L_{2}\psi= \left(-8 L_{0}+c/2+ 3 \kappa L_{0}+\frac{1}{2}\tau k \dim\gf\right)
-\phi_{(\mu,\nu)}
-\end{equation*}
-\begin{equation}
-  \label{eq:28} (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
-\end{equation}
-
-Now we act with $L_{1}^{2}$  and obtain
-\begin{equation}
-  \label{eq:17} 12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
-(C_{\mu}-\tilde{C}_{\nu})=0,
-\end{equation}
- where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator
-$\sum_{a}t^{a}t^{a}$. We need to get one more equation since we
-have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so
-$L_{1}\psi=0$ and then $J_{1}^{a}L_{1}\psi=0,\; \tilde{J}_{1}^{b} L_{1}\psi=0$, so
-
-\begin{equation}
-L_{1} \psi=L_{1}\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
-\left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
-\phi_{(\mu,\nu)}
-\end{equation}
-
-\begin{equation*}
-L_{1}\psi = \left(-6 L_{-1}+\kappa (2  L_{-1} L_{0}+L_{0}) + \tau \sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{0}\right)
-\phi_{(\mu,\nu)}
-\end{equation*}
-\begin{equation*}
-  L_{1}^{2}\psi= \left(-12 L_{0}+\kappa (4  L_{0}^{2}+2 L_{0}) + \tau \sum_{a=1}^{\dim\gf}J^{a}_{0}J^{a}_{0}\right)
-\phi_{(\mu,\nu)}
-\end{equation*}
-\begin{equation*}
-  J_{1}^{a}L_{1} \psi= \left(-6 J_{0}^{a}+\kappa (2  J_{0}^{a} L_{0}+J_{0}^{a}) + \tau
-    \sum_{b=1}^{\dim\gf}\sum_{c=1}^{\dim\gf}i f^{abc}J^{c}_{0}J^{b}_{0}+k\tau J_{0}^{a}\right)
-\phi_{(\mu,\nu)}
-\end{equation*}
-
-\begin{equation*}
-  L_{2}\psi= \left(-8 L_{0}+c/2+ 3 \kappa L_{0}+\frac{1}{2}\tau k \dim\gf\right)
-\phi_{(\mu,\nu)}
-\end{equation*}
-
-\begin{eqnarray*}
-  (3\kappa-8) h_{(\mu,\nu)}+c/2+\frac{1}{2}\tau k \dim\gf=0\\
-  -12 h_{(\mu,\nu)}+\kappa (4 h_{(\mu,\nu)}^{2}+2 h_{(\mu,\nu)}) +\tau C(\mu) =0\\
-  (-6 +\kappa (2 h_{(\mu,\nu)}+1)+\tau
-\end{eqnarray*}
-\begin{equation}
-  \label{eq:29} \left(-6 + \kappa + \tau + 2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0}
-\phi_{(\mu,\nu)}=0
-\end{equation}
-
-Acting on \eqref{eq:30} with $L_{2}$ and $L_{1}^{2}$ we can obtain equations \eqref{eq:28} and
-\eqref{eq:17}. To get more equations we can act by $\afh$-generators $\tilde{J}^{b}_{1}$ and $L_{1}$
-similarly to what was done with $J^{3}_{1}$ to get equation \eqref{eq:29}.
-
-To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov
-equations \eqref{eq:6} as was done for WZNW-models in paper \cite{alekseev2010sle}.
-
-Now consider simple example. Let $G=SU(2)$ and $A=U(1)$, and corresponding Lie algebras
-$\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator
-$J^{3}$, $\af\subset\gf$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
-
- The equation \eqref{eq:10} is now
-\begin{equation}
-  \label{eq:11} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
-\left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
-\end{equation}
- If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\;
-J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
-\begin{equation} \psi= \left(-2
-L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right)
-\phi_{(\mu,\nu)}
-\label{eq:12}
-\end{equation}
- which is similar to the equations for parafermionic fields introduced in paper
-\cite{santachiara2008sle}.
-
-Central charge in this case is equal to
-\begin{equation}
-  \label{eq:14} c=\frac{2(k-1)}{k+2}
-\end{equation}
-
-Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
-\begin{equation}
-  \label{eq:13} L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{(\mu,\nu)}=0,
-\end{equation}
- and obtain
-\begin{equation}
-  \label{eq:28} (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
-\end{equation}
- Another equation can be obtained by action of $L_{1}^{2}$
-\begin{equation}
-  \label{eq:15} L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau
-(J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{(\mu,\nu)}=0
-\end{equation}
- Since
-$J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$
-we have
-\begin{equation}
-  \label{eq:17} 12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
-(C_{\mu}-\tilde{C}_{\nu})=0,
-\end{equation}
- where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator
-$\sum_{a}t^{a}t^{a}$. For $u(1)$ it is just $\nu^{2}$. We need to get one more equation since we
-have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so
-$L_{1}\psi=0$ and then $J_{1}^{3}L_{1}\psi=0$, so
-\begin{equation}
-  \label{eq:29} \left(-6 + \kappa + \tau + 2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0}
-\phi_{(\mu,\nu)}=0
-\end{equation}
-
-Turn to the case $k=2, \;c=1/2$ which corresponds to square lattice Ising model. We have three
-non-equivalent fields numbered by the pairs of $su(2)$ and $u(1)$ weights, which are $\phi_{(0,0)},
-\; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$. The
-equation \eqref{eq:29} is trivial for $\phi_{(0,0)}$ and $\phi_{(0,2)}$, so the equations
-\eqref{eq:17}, \eqref{eq:28} are consistent although we do not know how to interpret $\tau$ in
-context of the Ising model. If we consider the field $\phi_{(1,1)}$ we have no solution for
-$\kappa,\tau$, so we see that not every primary field corresponds to some boundary condition
-changing operator.
-
-\section{Algebraic equations}
-\label{sec:algebraic-equations}
-
-\section{Examples}
-\label{sec:examples}
+In excellent paper \cite{bettelheim2005stochastic} connection between WZNW-models and Schramm-Loewner evolution with additional Brownian motion on group manifold was established.
+This paper also stated a problem of the connection of SLE parameters for martingales in WZNW, coset and minimal models.
+Here we used the method to obtain necessary and sufficient conditions on SLE martingales proposed in paper \cite{alekseev2010sle}.
+This method allowed us to compare our results with parafermionic results of the papers \cite{santachiara2008sle,picco2008numerical}.
 
@@
 \label{sec:conclusion}
+
+%%  
+%%  
+%%  
+%%  Coset  models are specified by Lie algebra
+%%  $\gf$ and its subalgebra $\af$. Denote by $J_{n}^{a}$ the generators of affine Lie algebra $\gfh$
+%%  and by $\tilde{J}_{n}^{b}$ the generators of $\afh$, so that $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b}
+%%  J^{a}_{n}$. 
+%%  Virasoro generators in coset models are given by the difference of Sugawara expressions
+%%  of $\gf$ and $\af$-WZNW models:
+%%  \begin{equation*} L_{n}=L_{n}^{\gf}-L_{n}^{\af}
+%%  \end{equation*}
+%%   Commutation relations of Virasoro generators with generators of subalgebra $\afh$
+%%  are trivial
+%%  \begin{equation}
+%%    \label{eq:26} \left[L_{n},\tilde{J}^{b}_{m}\right]=0
+%%  \end{equation}
+%%  
+%%  Commutation relations between generators of $\gfh$ and Virasoro generators are now
+%%  \begin{equation}
+%%    \label{eq:1}
+%%    \left[ L_{n}, J_{m}^{a} \right] = [L_{n}^{\gf}-L_{n}^{\af},J_{m}^{a}]= 
+%%  \end{equation}
+%%  
+%%  Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields
+%%   $A,
+%%  \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}.
+%%   Then fields
+%%  are labeled by pairs of weights $(\mu,\nu)$, where $\mu$ is the weight of $\gfh$ and $\nu$ is the
+%%  weight of $\afh$ correspondingly. But there are selection rules, i.e. the branching functions for
+%%  certain pairs of weights $(\mu,\nu)$ vanish. There is also a redundancy, i.e. non-vanishing
+%%  branching functions for distinct pairs $(\mu,\nu)$ turn out to be identical
+%%  \cite{fuchs1996resolution,schellekens1990field}.
+%%  
+%%  So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ of
+%%  algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$. Some
+%%  pairs are equivalent. This equivalence is given by the action of so called ``simple currents''
+%%  $(J,\tilde{J})$, which are certain elements of outer automorphisms group $\mathcal{O}(\gfh)\times
+%%  \mathcal{O}(\afh)\approx B(G)\times B(A)$ of $\gfh\times\afh$, where $B(G)$ is center of Lie group
+%%  G. We can think of simple currents as of primary fields and their action on fields of theory are
+%%  then given by fusion product \cite{difrancesco1997cft}. So primary fields of coset model are given
+%%  by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where
+%%  $(J,\tilde J)$ such that their conformal weights are equal: $h_{J}-h_{\tilde{J}}=0$.
+%%  
+%%  Conformal weight of coset primary field is equal to
+%%  \begin{multline}
+%%  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b
+%%  \tilde{J}^b_0 \tilde{J}^b_0 \right) \left|\phi_{(\mu,\nu)}\right>=\\
+%%  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
+%%  \end{multline} It is possible to obtain analogues of Knizhnik-Zamolodchikov equations for coset
+%%  models \cite{kogan1997knizhnik}:
+%%  \begin{equation} \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq
+%%  j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde
+%%  t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots
+%%  \phi_{N}(z_{N})\right>=0
+%%    \label{eq:6}
+%%  \end{equation}
+%%  
+%%  Let us introduce Schramm-Loewner evolution corresponding to coset models. The idea is to constrain
+%%  additional Brownian motion on group manifold to the factor space $G/A$.
+%%  
+%%  
+%%  To study SLE on $G/A$ factor space we restrict random walk on group manifold by the choice of basis
+%%  in $\gf$. Assume that generators $\{J^{a};\; a=1\dots \dim\gf\}$ are chosen in such way that
+%%  $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\;
+%%  a=\dim\gf-\dim\af\dots \dim\gf\}$ are the generators of subalgebra
+%%  $\af\subset \gf$. Now we can consider $(\dim\gf-\dim\af)$-dimensional Brownian
+%%  motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \;
+%%  d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\dim\gf-\dim\af$.
+%%  
+%%  Then for generator of field transformation we can write
+%%  \begin{equation} \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa}
+%%  d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\dim\gf-\dim\af}\left(d
+%%  \theta ^{a} t^{a}_{i}\right)\right)
+%%  \label{eq:5}
+%%  \end{equation}
+%%   Substituting to equation \eqref{eq:8} we get martingale condition
+%%  
+%%  \begin{equation} \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa
+%%  \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\dim\gf-\dim\af}
+%%  \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right) \mathcal{F}_{\mathbb{H}}=0
+%%  \label{eq:9}
+%%  \end{equation}
+%%  
+%%  which can be rewritten as the requirement for
+%%  \begin{equation} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
+%%  \left(\sum_{a=1}^{\dim\gf-\dim\af}J^{a}_{-1}J^{a}_{-1}\right)\right)
+%%  \phi_{(\mu,\nu)}
+%%  \label{eq:10}
+%%  \end{equation}
+%%   to be level two null-field.
+%%  
+%%   It is not always convenient to work with generators
+%%  orthogonal with respect to Killing form $\mathcal{K}$, sometimes it is preferable to use Chevalley
+%%  or Cartan-Weyl basis. So we change normalization condition of additional
+%%  $\dim\gf$-dimensional Brownian motion \eqref{eq:5} to $\mathbb{E}\left[d\theta^{a}\;
+%%  d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation
+%%  \eqref{eq:2} is
+%%  \begin{equation*} \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa}
+%%  d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d
+%%  \theta ^{a} t^{a}_{i}\right)\right).
+%%  \end{equation*}
+%%   Martingale condition \eqref{eq:8} can be written as
+%%  \begin{equation*} \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa
+%%  \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
+%%  \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)
+%%  \mathcal{F}_{\mathbb{H}}=0.
+%%  \end{equation*}
+%%   This equation can again be rewritten as the requirement for
+%%  \begin{equation} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
+%%  \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
+%%  \phi_{(\mu,\nu)}
+%%  \label{eq:30}
+%%  \end{equation}
+%%   to be level two null-field.
+%%  
+%%  Acting with $L_{2}$ we get
+%%  \begin{equation*}
+%%    L_{2}\psi= \left(-8 L_{0}+c/2+ 3 \kappa L_{0}+\frac{1}{2}\tau k \dim\gf\right)
+%%  \phi_{(\mu,\nu)}
+%%  \end{equation*}
+%%  \begin{equation}
+%%    \label{eq:28} (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
+%%  \end{equation}
+%%  
+%%  Now we act with $L_{1}^{2}$  and obtain
+%%  \begin{equation}
+%%    \label{eq:17} 12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
+%%  (C_{\mu}-\tilde{C}_{\nu})=0,
+%%  \end{equation}
+%%   where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator
+%%  $\sum_{a}t^{a}t^{a}$. We need to get one more equation since we
+%%  have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so
+%%  $L_{1}\psi=0$ and then $J_{1}^{a}L_{1}\psi=0,\; \tilde{J}_{1}^{b} L_{1}\psi=0$, so
+%%  
+%%  \begin{equation}
+%%  L_{1} \psi=L_{1}\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
+%%  \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
+%%  \phi_{(\mu,\nu)}
+%%  \end{equation}
+%%  
+%%  \begin{equation*}
+%%  L_{1}\psi = \left(-6 L_{-1}+\kappa (2  L_{-1} L_{0}+L_{0}) + \tau \sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{0}\right)
+%%  \phi_{(\mu,\nu)}
+%%  \end{equation*}
+%%  \begin{equation*}
+%%    L_{1}^{2}\psi= \left(-12 L_{0}+\kappa (4  L_{0}^{2}+2 L_{0}) + \tau \sum_{a=1}^{\dim\gf}J^{a}_{0}J^{a}_{0}\right)
+%%  \phi_{(\mu,\nu)}
+%%  \end{equation*}
+%%  \begin{equation*}
+%%    J_{1}^{a}L_{1} \psi= \left(-6 J_{0}^{a}+\kappa (2  J_{0}^{a} L_{0}+J_{0}^{a}) + \tau
+%%      \sum_{b=1}^{\dim\gf}\sum_{c=1}^{\dim\gf}i f^{abc}J^{c}_{0}J^{b}_{0}+k\tau J_{0}^{a}\right)
+%%  \phi_{(\mu,\nu)}
+%%  \end{equation*}
+%%  
+%%  
+%%  \begin{equation*}
+%%    L_{2}\psi= \left(-8 L_{0}+c/2+ 3 \kappa L_{0}+\frac{1}{2}\tau k \dim\gf\right)
+%%  \phi_{(\mu,\nu)}
+%%  \end{equation*}
+%%  
+%%  \begin{eqnarray*}
+%%    (3\kappa-8) h_{(\mu,\nu)}+c/2+\frac{1}{2}\tau k \dim\gf=0\\
+%%    -12 h_{(\mu,\nu)}+\kappa (4 h_{(\mu,\nu)}^{2}+2 h_{(\mu,\nu)}) +\tau C(\mu) =0\\
+%%    (-6 +\kappa (2 h_{(\mu,\nu)}+1)+\tau
+%%  \end{eqnarray*}
+%%  \begin{equation}
+%%    \label{eq:29} \left(-6 + \kappa + \tau + 2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0}
+%%  \phi_{(\mu,\nu)}=0
+%%  \end{equation}
+%%  
+%%  Acting on \eqref{eq:30} with $L_{2}$ and $L_{1}^{2}$ we can obtain equations \eqref{eq:28} and
+%%  \eqref{eq:17}. To get more equations we can act by $\afh$-generators $\tilde{J}^{b}_{1}$ and $L_{1}$
+%%  similarly to what was done with $J^{3}_{1}$ to get equation \eqref{eq:29}.
+%%  
+%%  To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov
+%%  equations \eqref{eq:6} as was done for WZNW-models in paper \cite{alekseev2010sle}.
+%%  
+%%  
+%%  Now consider simple example. Let $G=SU(2)$ and $A=U(1)$, and corresponding Lie algebras
+%%  $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator
+%%  $J^{3}$, $\af\subset\gf$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
+%%  
+%%   The equation \eqref{eq:10} is now
+%%  \begin{equation}
+%%    \label{eq:11} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
+%%  \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
+%%  \end{equation}
+%%   If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\;
+%%  J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
+%%  \begin{equation} \psi= \left(-2
+%%  L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right)
+%%  \phi_{(\mu,\nu)}
+%%  \label{eq:12}
+%%  \end{equation}
+%%   which is similar to the equations for parafermionic fields introduced in paper
+%%  \cite{santachiara2008sle}.
+%%  
+%%  Central charge in this case is equal to
+%%  \begin{equation}
+%%    \label{eq:14} c=\frac{2(k-1)}{k+2}
+%%  \end{equation}
+%%  
+%%  Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
+%%  \begin{equation}
+%%    \label{eq:13} L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{(\mu,\nu)}=0,
+%%  \end{equation}
+%%   and obtain
+%%  \begin{equation}
+%%    \label{eq:28} (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
+%%  \end{equation}
+%%   Another equation can be obtained by action of $L_{1}^{2}$
+%%  \begin{equation}
+%%    \label{eq:15} L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau
+%%  (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{(\mu,\nu)}=0
+%%  \end{equation}
+%%   Since
+%%  $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$
+%%  we have
+%%  \begin{equation}
+%%    \label{eq:17} 12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
+%%  (C_{\mu}-\tilde{C}_{\nu})=0,
+%%  \end{equation}
+%%   where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator
+%%  $\sum_{a}t^{a}t^{a}$. For $u(1)$ it is just $\nu^{2}$. We need to get one more equation since we
+%%  have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so
+%%  $L_{1}\psi=0$ and then $J_{1}^{3}L_{1}\psi=0$, so
+%%  \begin{equation}
+%%    \label{eq:29} \left(-6 + \kappa + \tau + 2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0}
+%%  \phi_{(\mu,\nu)}=0
+%%  \end{equation}
+%%  
+%%  
+%%  Turn to the case $k=2, \;c=1/2$ which corresponds to square lattice Ising model. We have three
+%%  non-equivalent fields numbered by the pairs of $su(2)$ and $u(1)$ weights, which are $\phi_{(0,0)},
+%%  \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$. The
+%%  equation \eqref{eq:29} is trivial for $\phi_{(0,0)}$ and $\phi_{(0,2)}$, so the equations
+%%  \eqref{eq:17}, \eqref{eq:28} are consistent although we do not know how to interpret $\tau$ in
+%%  context of the Ising model. If we consider the field $\phi_{(1,1)}$ we have no solution for
+%%  $\kappa,\tau$, so we see that not every primary field corresponds to some boundary condition
+%%  changing operator.
+%%  
+%%  
+%%  \section{Algebraic equations}
+%%  \label{sec:algebraic-equations}
+%%  
+%%  \section{Examples}
+%%  \label{sec:examples}
+%%
 

### 2012-04-05 AffineLieAlgebras/SLE/paper.tex
JETP letter style applied.

@@
-\documentclass[a4paper]{article}
-\usepackage{amsmath,amssymb,amsthm}
-\usepackage{multicol}
-\usepackage{color}
-\usepackage{graphicx}
+\documentclass{jetpl}
+\twocolumn
+
+%%% article in English
+\lat
+
+%%% declaration of a new mathematical operator
+\DeclareMathOperator{\sign}{sign}
+
+%\usepackage{amsmath,amssymb,amsthm}
+%\usepackage{multicol}
+%\usepackage{color}
+%\usepackage{graphicx}
 \usepackage{hyperref}
@@
 \newtheorem{mynote}{Note}[section]
-\theoremstyle{definition}
+%\theoremstyle{definition}
 \newtheorem{definition}{Definition}
@@
 
-\theoremstyle{definition} \newtheorem{Def}{Definition}
+%\theoremstyle{definition} \newtheorem{Def}{Definition}
 \newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
@@
 
-\begin{document}
+%%% article title
 \title{SLE martingales in coset conformal field theory}
-\author{Anton Nazarov}
-\maketitle
-\begin{abstract}
+
+%%% article title - for colontitle (at the top of the page)
+\rtitle{SLE martingales in coset conformal field theory}
+
+%%% article title - for table of contents (usualy identical with \title)
+\sodtitle{SLE martingales in coset conformal field theory}
+
+%%% author(s) ( + e-mail)
+
+\author{Anton Nazarov$^{+*}$\/\thanks{e-mail: anton.nazarov@hep.phys.spbu.ru}}
+
+%%% author(s) - for colontitle (at the top of the page)
+\rauthor{Anton Nazarov}
+
+%%% author(s) - for table of contents
+\sodauthor{Nazarov}
+
+%%% author's address(es)
+\address{
+  $^+$ Department of High-Energy and Elementary Particle Physics, 
+  Faculty of Physics and\\ Chebyshev Laboratory,
+  Faculty of Mathematics and Mechanics, \\ SPb State University
+  198904, Saint-Petersburg, Russia}
+
+%%% dates of submition & resubmition (if submitted once, second argument is *)
+\dates{06 April 2012}{*}
+
+%%% abstract
+
+\abstract{
   The problem is to provide a way for the concurrent use of Scramm-Loewner evolution (SLE) and conformal field theory (CFT).
@@
 In order to connect two approaches we consider CFT correlation functions which are martingales with respect to SLE.
-We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models.
-\end{abstract}
+We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models.}
+
+%%% PACS numbers
+\PACS{05.50.+q, 11.25.Hf, 02.20.Sv}
+
+\begin{document}
+\maketitle
 
@@
 
-\begin{equation}
-  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{i}} 
+\begin{multline}
+  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\})_{\mathbb{H}_{t}}=\\
+  =\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{i}} 
   \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{\bar h_i}
@@
   \label{eq:1}
-\end{equation}
+\end{multline}
 We can extend the definition of $\mathcal{F}$ to the whole plane by doubling the number of fields $\phi_{i}$ \cite{cardy2004boundary,cardy1984conformal} and consider $w_{i},\bar w_{i}$ as independent variables.
@@
  Ito formula  gives us the expression for the differential of $\mathcal{F}$, it should be zero due to martingale condition:
-\begin{equation}
-d \mathcal{F}_{\mathbb{H}_{t}}= \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
-      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}=0
+\begin{multline}
+d \mathcal{F}_{\mathbb{H}_{t}}=\\ \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)
+\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
+      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}\\=0
 \label{eq:8}
-\end{equation}
+\end{multline}
 Substitute definition \eqref{eq:3} and get 
@@
 where
-\begin{equation*}
-  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right);\quad \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}};\; \tilde{\mathcal{J}}^{b}_{{-n}}=-\sum_{i}\frac{\tilde{t}^{b}_{i}}{(w_{i}-z)^{n}}
-\end{equation*}
+\begin{eqnarray*}
+  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right)\\ \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}};\; \tilde{\mathcal{J}}^{b}_{{-n}}=-\sum_{i}\frac{\tilde{t}^{b}_{i}}{(w_{i}-z)^{n}}
+\end{eqnarray*}
 This equation is equivalent to following algebraic condition on boundary state $\varphi(0)\left|0\right>$:
-\begin{equation}
+\begin{multline}
   \label{eq:7}
-  <0|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\varphi(0)|0>=0
-\end{equation}
-Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that $|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\varphi(0)|0>$ is null-state.
-Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$.
-Since in coset theory
+  \left<0\left|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})\right.\right.\\
+  \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
+\left.\varphi(0)|0\right>=0
+\end{multline}
+Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that 
+\begin{multline}
+|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
+\cdot\varphi(0)|0>
+\end{multline}
+is null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in coset theory
 \begin{equation}
   \label{eq:18}
-\begin{array}{l}
-  L_{n}=L_{n}^{\gf}-L_{n}^{\af}\\
-  \left[L_{n}^{\gf},J^{a}_{m}\right]=-m J^{a}_{n+m}\\
-  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m}\\
-  \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}
+\begin{array}{rl}
+  L_{n}=& L_{n}^{\gf}-L_{n}^{\af}\\
+  \left[L_{n}^{\gf},J^{a}_{m}\right]=& -m J^{a}_{n+m}\\
+  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=&-m\tilde{J}^{b}_{n+m}\\
+  \left[L_{n}^{\gf},L_{m}\right]=&[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=\\
+  & =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}
 \end{array}
@@
  where $C_{\mu}=(\mu,\mu+2\rho), \tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ is the eigenvalue of quadratic Casimir operators $\sum_{a}t^{a}t^{a}, \sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ of Lie algebras $\gf$ and $\af$.
+Relations \eqref{eq:28},\eqref{eq:21} are necessary conditions for CFT correlation functions to be SLE martingales.
 
@@
 
-Minimal models $su(2)/u(1)$.
+Minimal models $su(2)/u(1)$, $su(2)\oplus su(2)/su(2)$.
 
@@
 This method allowed us to compare our results with parafermionic results of the papers \cite{santachiara2008sle,picco2008numerical}.
+
+Coset structure of minimal models is manifest in field theory perturbed by external magnetic field \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
+This theory is supported by experimental data \cite{coldea2010quantum}.
+Relation between correlation functions in coset theory and SLE observables can be a starting point for the study of domain walls in lattice models away of critical point.
+Schramm-Loewner evolution was applied for the description of domain walls in Ising model with external field in recent paper \cite{stevenson2011domain}, although the perturbation was not compatible with affine field theory structure.
 

### 2012-04-13 AffineLieAlgebras/SLE/paper.tex
Some changes in wording in introduction. Acknowledgments added.

@@
 \abstract{
-  The problem is to provide a way for the concurrent use of Scramm-Loewner evolution (SLE) and conformal field theory (CFT).
+  In order to provide a way for the concurrent use of Schramm-Loewner evolution (SLE) and conformal field theory (CFT) we consider CFT correlation functions which are martingales with respect to SLE.
+We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models.
 Both SLE and CFT are popular instruments to study critical behavior of physical models in two dimensions, but they use different objects.
-While Scharmm-Loewner evolution has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory.
-In order to connect two approaches we consider CFT correlation functions which are martingales with respect to SLE.
-We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models.}
+While Scharmm-Loewner evolution has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory.}
 
@@
 
-SLE describes critical behavior. It is convenient for strict mathematical proofs. For many lattice models  the convergence of  domain walls to SLE was proved.
+Schramm-Loewner evolution \cite{schramm2000scaling} is a stochastic process used to study critical behavior \cite{Cardy:2005kh,rohde2005basic}.
+For many lattice models  the convergence of  domain walls to SLE traces was proved \cite{bauer20062d,schramm2006conformally}.
 
@@
 \label{sec:conclusion}
+
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+ I am grateful to A. Bytsko, K. Izyurov, D. Chelkak and R. Santachiara for the discussions on SLE and WZNW models. This work  is supported by
+the Chebyshev Laboratory (Department of Mathematics and Mechanics,
+Saint-Petersburg State University) under the grant 11.G34.31.0026
+of the Government of the Russian Federation.
 

### 2012-04-25 AffineLieAlgebras/SLE/paper.tex
Some changes in SLE paper. Added Smirnov-Makarov paper to bibliography.

@@
 \abstract{
-  In order to provide a way for the concurrent use of Schramm-Loewner evolution (SLE) and conformal field theory (CFT) we consider CFT correlation functions which are martingales with respect to SLE.
+  Scharmm-Loewner evolution (SLE) and conformal field theory (CFT) are popular instruments to study critical behavior of physical models in two dimensions, but they use different objects.
+While SLE  has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory.
+  To provide a way for the concurrent use of SLE and CFT we consider CFT correlation functions which are martingales with respect to SLE.
 We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models.
-Both SLE and CFT are popular instruments to study critical behavior of physical models in two dimensions, but they use different objects.
-While Scharmm-Loewner evolution has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory.}
+Coset models are connected with off-critical massive field theories and we discuss possible implications for SLE.}
 
@@
 
-Schramm-Loewner evolution \cite{schramm2000scaling} is a stochastic process used to study critical behavior \cite{Cardy:2005kh,rohde2005basic}.
-For many lattice models  the convergence of  domain walls to SLE traces was proved \cite{bauer20062d,schramm2006conformally}.
+Schramm-Loewner evolution \cite{schramm2000scaling} is a stochastic process satisfying stochastic differential equation (\ref{eq:19}).
+Solution of equation (\ref{eq:19}) can be seen as probability measure on random curves called SLE traces.
+SLE is  useful for the study of critical behavior \cite{Cardy:2005kh,rohde2005basic}, since for many lattice models  the convergence of  domain walls to SLE traces can be proved \cite{bauer20062d,schramm2006conformally}.
+Practical computations with SLE rely on Ito calculus.
 
-CFT on the other hand is formulated in terms of families of quantum fields which usually has no natural interpretation in microscopic terms.
-On the other hand CFT has efficient computational tools such as Virasoro symmetry, Knizhnik-Zamolodchikov equations, fusion algebra etc and provides numerous predictions, such as celebrated Cardy formula which gives crossing probability for critical percolation.
+Conformal field theory \cite{belavin1984ics} is formulated in terms of families of quantum fields which usually has no natural interpretation in microscopic terms.
+On the other hand CFT has efficient computational tools such as Virasoro symmetry, Knizhnik-Zamolodchikov equations, fusion algebra etc and provides numerous predictions, such as celebrated Cardy formula \cite{cardy1992critical,smirnov2001critical} which gives crossing probability for critical percolation.
 
 Combination of these two approaches should be immensely powerful, so it is important to find objects which can be studied from both points of view.
-Correlation functions of CFT which are martingales with respect to Schramm-Loewner evolution are such objects.
-They are actively studied.
+We consider correlation functions of CFT which are martingales with respect to Schramm-Loewner evolution are such objects.
 
-We present new class of such observables.
-We consider correlation functions in coset conformal field theory which are martingales with respect to Schramm-Loewner evolution with additional random motion on factor of group $G$ by subgroup $A$.
+We present new class of such observables in coset conformal field theory \cite{Goddard198588}.
+They are correlation functions in $G/A$-coset conformal field theory which are martingales with respect to Schramm-Loewner evolution with additional Brownian motion on factor-space of Lie group $G$ by subgroup $A$ \cite{2011arXiv1112.4354N}.
 Using Knizhnik-Zamolodchikov equations we establish necessary and sufficient conditions on such functions and derive relations connecting parameters of SLE and CFT.
-We then check the consistency of these results with the earlier results obtained for parafermionic observables and general Cardy conditions on boundary states in conformal field theory.
+We then check the consistency of these results with the earlier results obtained for parafermionic observables \cite{santachiara2008sle}.
+
+All minimal unitary models can be obtained by coset construction.
+This coset structure leads to specific off-critical behavior such as classification of massive excitations by affine Toda field theory \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
+In conclusion we discuss possible connections of these CFT perturbation with massive off-critical SLEs (which contain additional drift term  \cite{makarov2010off}).
 
@@
 
-We
-consider Schramm-Loewner evolution $SLE_{\kappa}$ with additional Brownian motion on coset space
-$G/A$ characterised by parameter $\tau$ proposed in our paper \cite{2011arXiv1112.4354N}. We consider correlation functions in coset models of
-conformal field theory which satisfy martingale conditions with respect to this stochastic process.
-Since all minimal unitary models of conformal field theory can be obtained from coset construction
-for certain choice of Lie group $G$ and subgroup $A$ \cite{difrancesco1997cft} these correlation functions correspond to SLE
-observables appearing as the scaling limit of lattice observables. Trace of
-Schramm-Loewner $\gamma_{t}$ evolution describes critical domain wall in lattice models.
-
- Consider upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$.
+%% We
+%% consider Schramm-Loewner evolution $SLE_{\kappa}$ with additional Brownian motion on coset space
+%% $G/A$ characterised by parameter $\tau$ proposed in our paper \cite{2011arXiv1112.4354N}. We consider correlation functions in coset models of
+%% conformal field theory which satisfy martingale conditions with respect to this stochastic process.
+%% Since all minimal unitary models of conformal field theory can be obtained from coset construction
+%% for certain choice of Lie group $G$ and subgroup $A$ \cite{difrancesco1997cft} these correlation functions correspond to SLE
+%% observables appearing as the scaling limit of lattice observables. Trace of
+%% Schramm-Loewner $\gamma_{t}$ evolution describes critical domain wall in lattice models.
+%% 
+ Consider some critical lattice model on the upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$.
 We denote this slit domain by $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$.
-Conformal map from $\mathbb{H}_{t}$ to $\mathbb{H}$ is denoted by $g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ and satisfies stochastic differential equation \cite{schramm2000scaling}:
+Assume that $\gamma_{t}$ satisfies restriction property and is conformally  invariant \cite{Cardy:2005kh}.
+Then  conformal map  $g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ satisfies stochastic differential equation \cite{schramm2000scaling}:
 \begin{equation}
@@
 
-It is natural to study the problem in upper half-plane  and consider correlation
-functions of boundary conformal field theory with boundary condition changing operators sitting at
-the tip of SLE trace and at the infinity.
-
-So we are to consider $N$-point boundary correlation functions on the upper half-plane of the form 
+Consider  $N$-point correlation function of boundary conformal field theory with boundary condition changing operators sitting at the tip of SLE trace and at the infinity:
 \begin{equation}
@@
 where $\phi_{i}$ are bulk primary fields and $\varphi(z_{t})$ is boundary condition changing operator.
-We assume conformal invariance of boundary conditions so boundary states satisfy Cardy conditions \cite{cardy1989boundary,cardy1986effect,cardy1984conformal}.
 
- We consider Schramm-Loewner evolution with additional Brownian motion on $G/A$-coset space \cite{2011arXiv1112.4354N}.
-Denote by $\mathcal{K}$ Killing form of Lie algebra $\gf$ corresponding to Lie group $G$ and by $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) the  generators of $\gf$-representation ($\af$-representation) corresponding to primary field $\phi_{i}$.
 Primary fields in coset models are labeled by pairs $(\lambda,\eta)$ of weights $\gf$ and $\af$-representations.
@@
   We use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite expression \eqref{eq:2} in the whole upper half plane:
-
 \begin{multline}
@@
 
+$G/A$-coset conformal field theory can be realized as WZNW-model with gauge group $G$ interacting with pure gauge field of gauge group $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
+So we have $G/A$ gauge symmetry and we add random gauge transformations to Schramm-Loewner evolution \cite{2011arXiv1112.4354N} similar to the case of WZNW-models \cite{bettelheim2005stochastic}.
+Denote by $\mathcal{K}$ Killing form of Lie algebra $\gf$ corresponding to Lie group $G$ and by $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) the  generators of $\gf$-representation ($\af$-representation) corresponding to primary field $\phi_{i}$.
+
 Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:2}) gives us
@@
 We denote by $\mathcal{G}_{i}$ generator of infinitesimal transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$.
-We normalize additional $\dim\gf$-dimensional Brownian motion as $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation \eqref{eq:2} is equal to
+We normalize additional $\dim\gf$-dimensional Brownian motion as $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation is equal to
 \begin{equation}
@@
 \end{equation}
- Ito formula  gives us the expression for the differential of $\mathcal{F}$, it should be zero due to martingale condition:
+ Ito formula  gives us the expression for the differential of $\mathcal{F}$ which should be zero due to martingale condition:
 \begin{multline}
@@
   \label{eq:18}
-\begin{array}{rl}
-  L_{n}=& L_{n}^{\gf}-L_{n}^{\af}\\
-  \left[L_{n}^{\gf},J^{a}_{m}\right]=& -m J^{a}_{n+m}\\
-  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=&-m\tilde{J}^{b}_{n+m}\\
-  \left[L_{n}^{\gf},L_{m}\right]=&[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=\\
-  & =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}
+\begin{array}{ll}
+  L_{n}= L_{n}^{\gf}-L_{n}^{\af} &\\
+  \left[L_{n}^{\gf},J^{a}_{m}\right]= -m J^{a}_{n+m}&\\
+  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m}&\\
+  \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=&\\
+  \quad =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}&
 \end{array}
@@
 
+\subsection{Examples}
+\label{sec:examples-1}
+
+Minimal models $su(2)/u(1)$, $su(2)\oplus su(2)/su(2)$.
+
+Consider standard coset realization of minimal models: $su(2)_{N}/u(1)_{N}$.
+Central charge is $c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2}$.
+Conformal weights of primary fields with Dynkin indeces $(k,l)$ are $h_{(k,l)}=\frac{k(k+2)}{4(N+2)}-\frac{l^{2}}{4N}$.
+$C_{\mu}=k(k+2)/2, C_{\nu}=l^{2}/2$
+For Ising model $N=2,c=1/2$, $h_{(2,0)}=1/2, h_{(1,1)}=1/16$.
+We get for $\varphi_{(2,0)}$: $3\kappa-9+4\tau =0, -3+\kappa+4\tau=0$, $\kappa=3, \tau=0$.
+For $\varphi_{(1,1)}$: $3\kappa-16+64\tau=0, -64+9\kappa + 64\tau=0$, $\kappa=16/3, \tau=0$.
+For $N=3, c=4/5$.
+Conformal weights $h_{(0,0)}=0$, $h_{(0,2)}=2/3$, $h_{(0,-2)}=2/3$, $h_{(1,3)}=2/5$, $h_{(1,1)}=1/15$, $h_{(1,-1)}=1/15$.
+Corresponding values of $\kappa,\tau$ are: $(208/25,242/225), (460/33,116/33),(260/53,28/477)$
+
+Now use another coset realization of minimal unitary models: $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$, $c=\frac{3N}{N+2}+1-\frac{3(N+1)}{N+3}=1-\frac{6}{(N+2)(N+3)}$
+
+three-state Potts model $\frac{\hat{su}(3)_{1}\oplus \hat{su}(3)_{1}}{\hat{su}(3)_{2}}$
+
 But correlation functions in coset conformal field theory must satisfy (generalized) Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} which are of the form
@@
 
-\subsection{Examples}
-\label{sec:examples-1}
-
-Minimal models $su(2)/u(1)$, $su(2)\oplus su(2)/su(2)$.
-
-\section{Outlook}
+\section{Conclusion and outlook}
 \label{sec:outlook}
@@
 This paper also stated a problem of the connection of SLE parameters for martingales in WZNW, coset and minimal models.
-Here we used the method to obtain necessary and sufficient conditions on SLE martingales proposed in paper \cite{alekseev2010sle}.
+In present letter we used the method to obtain necessary and sufficient conditions on SLE martingales proposed in paper \cite{alekseev2010sle}.
 This method allowed us to compare our results with parafermionic results of the papers \cite{santachiara2008sle,picco2008numerical}.
@@
 Relation between correlation functions in coset theory and SLE observables can be a starting point for the study of domain walls in lattice models away of critical point.
+
+Massive off-critical SLEs has additional drift term in driving Brownian motion \cite{makarov2010off}.
+
   Schramm-Loewner evolution was applied for the description of domain walls in Ising model with external field in recent paper \cite{stevenson2011domain}, although the perturbation was not compatible with affine field theory structure.
-
-\section{Conclusion}
-\label{sec:conclusion}
 

### 2012-04-25 AffineLieAlgebras/SLE/computations.m
Some changes in SLE paper. Added Smirnov-Makarov paper to bibliography.

@@ -270,3 +270,435 @@ Out[33]= 0
               6 - kp             6 (6 - kp)
 Out[32]= (1 + ------) (6 - kp) - ----------
                 kp                   kp
+
+
+
+h:=k*(k+2)/(4*(N+2))-l^2/(4*N);
+c:=(2*N-2)/(N+2);
+cm:=k*(k+2)/2; 
+cn:=l^2/2;
+
+eqns:={(3*kp-8)*h-c+t*2*N==0, -12*h+2*kp*h*(2*h+1)+t*(cm-cn)==0};
+
+soln=Solve[eqns,{kp,t}]
+
+soln/.{N->3,k->1,l->-1}
+
+                 260       28
+Out[25]= {{kp -> ---, t -> ---}}
+                 53        477
+
+
+Simplify[soln/.{k->0,l->1}]
+
+kp1:=4*(N+1)/(N+2);
+t1:=4*N^3/(N+2)^3;
+kp2:=4*(N+2)/(N+1);
+t2:=2^(-4/N)*N^3/((N+2)*(N+1));
+
+Table[{{i,j},soln,kp1,t1,kp2,t2}/.{N->4,k->i,l->j},{i,0,3},{j,0,3}]
+
+                                 1
+Power::infy: Infinite expression - encountered.
+                                 0
+
+Infinity::indet: Indeterminate expression 0 ComplexInfinity encountered.
+
+                                                1    10  32  24  16
+Out[75]= {{{{0, 0}, {{kp -> Indeterminate, t -> -}}, --, --, --, --}, 
+                                                8    3   27  5   15
+ 
+                       184       25     10  32  24  16
+>     {{0, 1}, {{kp -> ---, t -> ---}}, --, --, --, --}, 
+                       31        124    3   27  5   15
+ 
+                       52       4    10  32  24  16
+>     {{0, 2}, {{kp -> --, t -> -}}, --, --, --, --}, 
+                       7        7    3   27  5   15
+ 
+                       248       169    10  32  24  16
+>     {{0, 3}, {{kp -> ---, t -> ---}}, --, --, --, --}}, 
+                       23        92     3   27  5   15
+ 
+                       144       1     10  32  24  16
+>    {{{1, 0}, {{kp -> ---, t -> --}}, --, --, --, --}, 
+                       31        31    3   27  5   15
+ 
+                       24       3     10  32  24  16
+>     {{1, 1}, {{kp -> --, t -> --}}, --, --, --, --}, 
[…]

### 2012-04-26 AffineLieAlgebras/SLE/paper.tex
Some work on examples.

@@
 
+Let $\gf$ be (semisimple) Lie algebra of Lie group $G$ and $\af$ -- Lie algebra of subgroup $A\subset G$. Denote by $x_{e}$ index of embedding $\af\to\gf$.
+
 Primary fields in coset models are labeled by pairs $(\lambda,\eta)$ of weights $\gf$ and $\af$-representations.
@@
 \end{equation*}
-We use $L_{0} \varphi_{(\mu,\nu)}=h_{(\mu,\nu)} \varphi_{(\mu,\nu)}$ where conformal weight $h_{(\mu,\nu)}= \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k x_{e}+h^{\vee}_{\af})}\right)$ and central charge $c=\frac{k\dim \gf}{k+h^{\vee}_{\gf}}-\frac{x_{e}k\dim \af}{x_{e} k+h^{\vee}_{\af}}$ and get relation on $\kappa,\tau$:
+We use $L_{0} \varphi_{(\mu,\nu)}=h_{(\mu,\nu)} \varphi_{(\mu,\nu)}$, where conformal weight is $h_{(\mu,\nu)}= \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k x_{e}+h^{\vee}_{\af})}\right)$ and central charge is $c=\frac{k\dim \gf}{k+h^{\vee}_{\gf}}-\frac{x_{e}k\dim \af}{x_{e} k+h^{\vee}_{\af}}$ and get relation on $\kappa,\tau$:
 \begin{equation}
@@
 \label{sec:examples-1}
-
-Minimal models $su(2)/u(1)$, $su(2)\oplus su(2)/su(2)$.
-
-Consider standard coset realization of minimal models: $su(2)_{N}/u(1)_{N}$.
+As an example consider   $\frac{su(2)_{N}}{u(1)_{N}}$-coset models which are equivalent to $Z_{N}$-parafermions.
 Central charge is $c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2}$.
@@
 $C_{\mu}=k(k+2)/2, C_{\nu}=l^{2}/2$
-For Ising model $N=2,c=1/2$, $h_{(2,0)}=1/2, h_{(1,1)}=1/16$.
-We get for $\varphi_{(2,0)}$: $3\kappa-9+4\tau =0, -3+\kappa+4\tau=0$, $\kappa=3, \tau=0$.
-For $\varphi_{(1,1)}$: $3\kappa-16+64\tau=0, -64+9\kappa + 64\tau=0$, $\kappa=16/3, \tau=0$.
+Case  $N=2,c=1/2$ is Ising model, we have two non-trivial primary fields with conformal weights $h_{(2,0)}=1/2, h_{(1,1)}=1/16$.
+Substituting field $\varphi_{(2,0)}$ into equations (\ref{eq:28},\ref{eq:21}) we get $3\kappa-9+4\tau =0;\quad -3+\kappa+4\tau=0$.
+Then $\kappa=3, \tau=0$.
+For field $\varphi_{(1,1)}$ we obtain $3\kappa-16+64\tau=0,\quad -64+9\kappa + 64\tau=0$, $\kappa=16/3, \tau=0$.
+So we have no additional motion for Ising model and two possible values for SLE parameter $\kappa$,  coinciding with well-known results.
 For $N=3, c=4/5$.

### 2012-04-26 AffineLieAlgebras/SLE/paper.tex
Conclusion of SLE letter expanded with the discussion of massive SLEs.

@@
 %%% dates of submition & resubmition (if submitted once, second argument is *)
-\dates{06 April 2012}{*}
+\dates{26 April 2012}{*}
 
@@
   To provide a way for the concurrent use of SLE and CFT we consider CFT correlation functions which are martingales with respect to SLE.
-We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models.
-Coset models are connected with off-critical massive field theories and we discuss possible implications for SLE.}
+We establish connection between parameters of Schramm-Loewner evolution on coset space and algebraic data of coset conformal field theory.
+Then we check the consistency of our approach with the  behaviour of parafermionic and minimal models.
+Coset models can be connected to off-critical massive field theories and we discuss possible implications for SLE.}
 
@@
 They are correlation functions in $G/A$-coset conformal field theory which are martingales with respect to Schramm-Loewner evolution with additional Brownian motion on factor-space of Lie group $G$ by subgroup $A$ \cite{2011arXiv1112.4354N}.
-Using Knizhnik-Zamolodchikov equations we establish necessary and sufficient conditions on such functions and derive relations connecting parameters of SLE and CFT.
+We derive relations connecting parameters of SLE and CFT.
 We then check the consistency of these results with the earlier results obtained for parafermionic observables \cite{santachiara2008sle}.
@@
 \label{sec:examples-1}
-As an example consider   $\frac{su(2)_{N}}{u(1)_{N}}$-coset models which are equivalent to $Z_{N}$-parafermions.
+As an example consider  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset models which are equivalent to $Z_{N}$-parafermions.
 Central charge is $c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2}$.
 Conformal weights of primary fields with Dynkin indeces $(k,l)$ are $h_{(k,l)}=\frac{k(k+2)}{4(N+2)}-\frac{l^{2}}{4N}$.
-$C_{\mu}=k(k+2)/2, C_{\nu}=l^{2}/2$
-Case  $N=2,c=1/2$ is Ising model, we have two non-trivial primary fields with conformal weights $h_{(2,0)}=1/2, h_{(1,1)}=1/16$.
+% $C_{\mu}=k(k+2)/2, C_{\nu}=l^{2}/2$
+
+Case $N=2$, $c=\frac{1}{2}$ corresponds to Ising model, we have two non-trivial primary fields with conformal weights $h_{(2,0)}=1/2, h_{(1,1)}=1/16$.
 Substituting field $\varphi_{(2,0)}$ into equations (\ref{eq:28},\ref{eq:21}) we get $3\kappa-9+4\tau =0;\quad -3+\kappa+4\tau=0$.
@@
 So we have no additional motion for Ising model and two possible values for SLE parameter $\kappa$,  coinciding with well-known results.
-For $N=3, c=4/5$.
-Conformal weights $h_{(0,0)}=0$, $h_{(0,2)}=2/3$, $h_{(0,-2)}=2/3$, $h_{(1,3)}=2/5$, $h_{(1,1)}=1/15$, $h_{(1,-1)}=1/15$.
-Corresponding values of $\kappa,\tau$ are: $(208/25,242/225), (460/33,116/33),(260/53,28/477)$
 
-Now use another coset realization of minimal unitary models: $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$, $c=\frac{3N}{N+2}+1-\frac{3(N+1)}{N+3}=1-\frac{6}{(N+2)(N+3)}$
+For $N=3$ parafermionic model central charge is $c=\frac{4}{5}$.
+Conformal weights are $h_{(0,0)}=0$, $h_{(0,2)}=h_{(0,-2)}=\frac{2}{3}\; \mathrm{mod}\; 1$, $h_{(2,0)}=\frac{2}{5}$, $h_{(2,2)}=h_{(2,-2)}=\frac{1}{15}$.
+Corresponding values of $\kappa,\tau$ are: $(\frac{208}{25},\frac{242}{225}), (\frac{10}{3},0),(\frac{80}{19},\frac{14}{171})$.
+As was mentioned in \cite{santachiara2008sle} field $\varphi_{(2,0)}$ with conformal weight $h_{(2,0)}=\frac{2}{5}$ constitutes $Z_{3}$-singlet, so  additional random walk does not appear and $\tau=0$.
+The form of equations (\ref{eq:7}) is similar to that of \cite{santachiara2008sle}, but normalization of $\tau$ differs.
 
-three-state Potts model $\frac{\hat{su}(3)_{1}\oplus \hat{su}(3)_{1}}{\hat{su}(3)_{2}}$
+It is easy to see that for  $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset realization of minimal unitary models with $c=\frac{3N}{N+2}+1-\frac{3(N+1)}{N+3}=1-\frac{6}{(N+2)(N+3)}$ system of equations (\ref{eq:28},\ref{eq:21}) is always consistent for $\tau=0$ and we get standard connection between SLE-parameter $\kappa$ and central charge $c=\frac{(6-\kappa)(3\kappa-8)}{2\kappa}$.
 
-But correlation functions in coset conformal field theory must satisfy (generalized) Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} which are of the form
-\begin{equation}
-  \label{eq:16}
- \left[ \frac{1}{2}\frac{\partial}{\partial w_{i}} +\sum_{j\neq i} \left( \frac{\sum_{a}t_{i}^{a}t_{j}^{a}}{k+h^{\vee}}-\frac{\sum_{b}\tilde t_{i}^{b}\tilde t_{j}^{b}}{x_{e}k+h_{\af}^{\vee}}\right) \right]\mathcal{F}_{\mathbb{H}}=0
-\end{equation}
-Rewrite the equation as
-\begin{equation}
-  \label{eq:22}
-  \left[ \frac{1}{2}\frac{\partial}{\partial w_{i}} +\sum_{j\neq i} \left( \frac{\sum_{a}t_{i}^{a}t_{j}^{a}}{k+h^{\vee}}-\frac{\sum_{b}\tilde t_{i}^{b}\tilde t_{j}^{b}}{x_{e}k+h_{\af}^{\vee}}\right) \right]\mathcal{F}_{\mathbb{H}}=0
-\end{equation}
-
-From this relations and equation \eqref{eq:8} we can write sufficient conditions for SLE martingale to be CFT correlation function:
-\begin{equation}
-  \label{eq:23}
-  M x = 0
-\end{equation}
-
-It is also possible to consider coset theory as $G\times A$  gauge theory and impose constraints on physical states later (See \cite{hwang1993brst,kogan1997knizhnik,gawdzki1988g,figueroa89equivalence}).
+%% But correlation functions in coset conformal field theory must satisfy (generalized) Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} which are of the form
+%% \begin{equation}
+%%   \label{eq:16}
+%%  \left[ \frac{1}{2}\frac{\partial}{\partial w_{i}} +\sum_{j\neq i} \left( \frac{\sum_{a}t_{i}^{a}t_{j}^{a}}{k+h^{\vee}}-\frac{\sum_{b}\tilde t_{i}^{b}\tilde t_{j}^{b}}{x_{e}k+h_{\af}^{\vee}}\right) \right]\mathcal{F}_{\mathbb{H}}=0
+%% \end{equation}
+%% Rewrite the equation as
+%% \begin{equation}
+%%   \label{eq:22}
+%%   \left[ \frac{1}{2}\frac{\partial}{\partial w_{i}} +\sum_{j\neq i} \left( \frac{\sum_{a}t_{i}^{a}t_{j}^{a}}{k+h^{\vee}}-\frac{\sum_{b}\tilde t_{i}^{b}\tilde t_{j}^{b}}{x_{e}k+h_{\af}^{\vee}}\right) \right]\mathcal{F}_{\mathbb{H}}=0
+%% \end{equation}
+%% 
+%% From this relations and equation \eqref{eq:8} we can write sufficient conditions for SLE martingale to be CFT correlation function:
+%% \begin{equation}
+%%   \label{eq:23}
+%%   M x = 0
+%% \end{equation}
+%% 
+%% It is also possible to consider coset theory as $G\times A$  gauge theory and impose constraints on physical states later (See \cite{hwang1993brst,kogan1997knizhnik,gawdzki1988g,figueroa89equivalence}).
 In this case second term in equation \eqref{eq:3} will include sum over $\gf$ and $\af$ generators and two parameters of Brownian motion $\tau_{\gf}$ and $\tau_{\af}$.
-
+%% 
 \section{Conclusion and outlook}
@@
 
-Massive off-critical SLEs has additional drift term in driving Brownian motion \cite{makarov2010off}.
+Massive perturbations of $G/A$-coset theory are realized as affine Toda field theory and classified by simple roots of Lie algebra $\gf$.
 
-  Schramm-Loewner evolution was applied for the description of domain walls in Ising model with external field in recent paper \cite{stevenson2011domain}, although the perturbation was not compatible with affine field theory structure.
+Massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off}.
+Addition of drift term to (\ref{eq:20}) leads to appearance of new terms in martingale condition (\ref{eq:8}).
+
+On the other hand perturbation can be seen as the insertion of certain primary field in all correlation functions \cite{hollowood1989rational}.
+The question is whether the interaction of this primary field with the $\tau$-term of the equation (\ref{eq:4}) lead to the same contribution as the addition of massive drift to SLE.
+
+Domain walls in  Ising model perturbed by random Gaussian external were studied numerically using Schramm-Loewner evolution in recent paper \cite{stevenson2011domain}.
+Further task is to compare this results with massive perturbations.
 

### 2012-04-26 AffineLieAlgebras/SLE/computations.m

@@ -296,7 +296,544 @@ t1:=4*N^3/(N+2)^3;
 kp2:=4*(N+2)/(N+1);
 t2:=2^(-4/N)*N^3/((N+2)*(N+1));
 
-Table[{{i,j},soln,kp1,t1,kp2,t2}/.{N->4,k->i,l->j},{i,0,3},{j,0,3}]
+Table[{{i,j},h,soln,kp1,t1,kp2,t2}/.{N->3,k->2*i,l->2*j},{i,-1,1},{j,0,1}]
+
+                                 1
+Power::infy: Infinite expression - encountered.
+                                 0
+
+Infinity::indet: Indeterminate expression 0 ComplexInfinity encountered.
+
+                                 1
+Power::infy: Infinite expression - encountered.
+                                 0
+
+Infinity::indet: Indeterminate expression 0 ComplexInfinity encountered.
+
+                                                    2     16  108
+Out[52]= {{{{-1, 0}, 0, {{kp -> Indeterminate, t -> --}}, --, ---, 5, 
+                                                    15    5   125
+ 
+         27                  1           208       242    16  108
+>      -------}, {{-1, 1}, -(-), {{kp -> ---, t -> ---}}, --, ---, 5, 
+           1/3               3           25        225    5   125
+       40 2
+ 
+         27                                                2     16  108
+>      -------}}, {{{0, 0}, 0, {{kp -> Indeterminate, t -> --}}, --, ---, 5, 
+           1/3                                             15    5   125
+       40 2
+ 
+         27                 1           208       242    16  108       27
+>      -------}, {{0, 1}, -(-), {{kp -> ---, t -> ---}}, --, ---, 5, -------}}
+           1/3              3           25        225    5   125         1/3
+       40 2                                                          40 2
+ 
+                  2          10            16  108       27
+>     , {{{1, 0}, -, {{kp -> --, t -> 0}}, --, ---, 5, -------}, 
+                  5          3             5   125         1/3
+                                                       40 2
+ 
+               1           80       14     16  108       27
+>     {{1, 1}, --, {{kp -> --, t -> ---}}, --, ---, 5, -------}}}
+               15          19       171    5   125         1/3
+                                                       40 2
+
+h/.{N->3,k->2,l->-2}
+
+Simplify[Solve[cc-(6-k)*(3*k-8)/(2*k)==0,k]/.{cc->1-6/((N+1)*(N+2))}]/.{N->6}
+
+                7         32
[…]

### 2012-05-03 AffineLieAlgebras/SLE/paper.tex
Minor changes in text

@@
 \abstract{
-  Scharmm-Loewner evolution (SLE) and conformal field theory (CFT) are popular instruments to study critical behavior of physical models in two dimensions, but they use different objects.
+  Scharmm-Loewner evolution (SLE) and conformal field theory (CFT) are popular and widely used instruments to study critical behavior of two-dimensional models, but they use different objects.
 While SLE  has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory.
@@
 Then we check the consistency of our approach with the  behaviour of parafermionic and minimal models.
-Coset models can be connected to off-critical massive field theories and we discuss possible implications for SLE.}
+Coset models are connected with off-critical massive field theories and we discuss implications for SLE.}
 
@@
 Schramm-Loewner evolution \cite{schramm2000scaling} is a stochastic process satisfying stochastic differential equation (\ref{eq:19}).
-Solution of equation (\ref{eq:19}) can be seen as probability measure on random curves called SLE traces.
-SLE is  useful for the study of critical behavior \cite{Cardy:2005kh,rohde2005basic}, since for many lattice models  the convergence of  domain walls to SLE traces can be proved \cite{bauer20062d,schramm2006conformally}.
+Solution of the equation (\ref{eq:19}) can be seen as a probability measure on random curves (called SLE traces).
+SLE is useful for the study of critical behavior \cite{Cardy:2005kh,rohde2005basic}, since for many lattice models convergence of  domain walls to SLE traces can be proved \cite{bauer20062d,schramm2006conformally}.
 Practical computations with SLE rely on Ito calculus.
 
-Conformal field theory \cite{belavin1984ics} is formulated in terms of families of quantum fields which usually has no natural interpretation in microscopic terms.
-On the other hand CFT has efficient computational tools such as Virasoro symmetry, Knizhnik-Zamolodchikov equations, fusion algebra etc and provides numerous predictions, such as celebrated Cardy formula \cite{cardy1992critical,smirnov2001critical} which gives crossing probability for critical percolation.
+Conformal field theory \cite{belavin1984ics} is formulated in terms of families of quantum fields which usually has no direct microscopic interpretation.
+On the other hand, CFT has efficient computational tools such as Virasoro symmetry, Knizhnik-Zamolodchikov equations, fusion algebra etc and provides numerous predictions, such as celebrated Cardy formula \cite{cardy1992critical,smirnov2001critical} which gives crossing probability for critical percolation.
 
-Combination of these two approaches should be immensely powerful, so it is important to find objects which can be studied from both points of view.
-We consider correlation functions of CFT which are martingales with respect to Schramm-Loewner evolution are such objects.
+Combination of these two approaches is immensely powerful, so it is important to find objects which can be studied from both points of view.
 
-We present new class of such observables in coset conformal field theory \cite{Goddard198588}.
-They are correlation functions in $G/A$-coset conformal field theory which are martingales with respect to Schramm-Loewner evolution with additional Brownian motion on factor-space of Lie group $G$ by subgroup $A$ \cite{2011arXiv1112.4354N}.
+We present new class of such observables in coset conformal field theory  -- correlation functions which are martingales with respect to Schramm-Loewner evolution with additional Brownian motion on factor-space of Lie group $G$ by subgroup $A$ \cite{2011arXiv1112.4354N}.
 We derive relations connecting parameters of SLE and CFT.
-We then check the consistency of these results with the earlier results obtained for parafermionic observables \cite{santachiara2008sle}.
+We then check the consistency of these results with the earlier results  for parafermionic observables \cite{santachiara2008sle}.
 
 All minimal unitary models can be obtained by coset construction.
-This coset structure leads to specific off-critical behavior such as classification of massive excitations by affine Toda field theory \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
-In conclusion we discuss possible connections of these CFT perturbation with massive off-critical SLEs (which contain additional drift term  \cite{makarov2010off}).
+Coset structure leads to specific off-critical behavior.
+Massive excitations of coset CFTs are given by affine Toda field theories \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
+Recent experimental study confirming this result attracted a lot of attention \cite{coldea2010quantum}.
+In conclusion we discuss possible connections of massive CFT perturbations with  off-critical SLEs (containing additional drift term  \cite{makarov2010off}).
 
@@
 %% 
- Consider some critical lattice model on the upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$.
+ Consider some critical lattice model on the upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$ (domain wall up to some length $t$).
 We denote this slit domain by $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$.
@@
 \end{equation}
-where $\phi_{i}$ are bulk primary fields and $\varphi(z_{t})$ is boundary condition changing operator.
+where $\phi_{i}$ are bulk primary fields with conformal weights $h_i$ and $\varphi(z_{t})$ is a boundary condition changing operator.
 
@@
 
-Primary fields in coset models are labeled by pairs $(\lambda,\eta)$ of weights $\gf$ and $\af$-representations.
+Primary fields in coset models are labeled by pairs $(\lambda,\eta)$ of weights of $\gf$ and $\af$-representations.
 For each $\lambda$ possible values of $\eta$ are those which appear in decomposition of representation $L^{(\mu)}_{\gf}=\bigoplus_{\eta} H^{\lambda}_{\eta}\otimes L^{(\eta)}_{\af}$.
-Some pairs are equivalent, we discuss and use this equivalence relation later.
+(Some pairs are equivalent, see \cite{fuchs1996resolution,schellekens1990field}).
 We assume that boundary field $\varphi$ is also primary and labeled by weights $(\mu,\nu)$.
@@
 
-$G/A$-coset conformal field theory can be realized as WZNW-model with gauge group $G$ interacting with pure gauge field of gauge group $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
-So we have $G/A$ gauge symmetry and we add random gauge transformations to Schramm-Loewner evolution \cite{2011arXiv1112.4354N} similar to the case of WZNW-models \cite{bettelheim2005stochastic}.
+$G/A$-coset conformal field theory can be realized as WZNW-model (with gauge group $G$) interacting with pure gauge field of gauge group $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
+If we fix $A$-gauge we have $G/A$ gauge symmetry.
+Then we add random gauge transformations to Schramm-Loewner evolution \cite{2011arXiv1112.4354N} similar to the case of WZNW-models \cite{bettelheim2005stochastic}.
 Denote by $\mathcal{K}$ Killing form of Lie algebra $\gf$ corresponding to Lie group $G$ and by $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) the  generators of $\gf$-representation ($\af$-representation) corresponding to primary field $\phi_{i}$.
 
-Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:2}) gives us
+Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
 \begin{equation*}
@@
 \end{equation*}
-We denote by $\mathcal{G}_{i}$ generator of infinitesimal transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$.
+Denote by $\mathcal{G}_{i}$ generator of infinitesimal transformation of primary field $\phi_{i}$:\;$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$.
 We normalize additional $\dim\gf$-dimensional Brownian motion as $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation is equal to
@@
 \end{equation}
+So we have fixed $A$-gauge by allowing random walk only in direction orthogonal to subalgebra $\af$.
+
  Ito formula  gives us the expression for the differential of $\mathcal{F}$ which should be zero due to martingale condition:
@@
 \end{multline}
-is null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in coset theory
+is a null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in coset theory commutation relations of full chiral algebra are
 \begin{equation}
@@
   \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=&\\
-  \quad =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}&
+  \quad =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0},&
 \end{array}
 \end{equation}
- it is more convenient to act by $L_{2}^{\gf}$ and $\left(L_{1}^{\gf}\right)^{2}$. 
+ it is more convenient to act with $L_{2}^{\gf}$ and $\left(L_{1}^{\gf}\right)^{2}$. 
  Acting with $L_{2}^{\gf}$ we get
@@
 \end{equation}
- where $C_{\mu}=(\mu,\mu+2\rho), \tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ is the eigenvalue of quadratic Casimir operators $\sum_{a}t^{a}t^{a}, \sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ of Lie algebras $\gf$ and $\af$.
+ where $C_{\mu}=(\mu,\mu+2\rho)$ and $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ are the eigenvalues of quadratic Casimir operators $\sum_{a}t^{a}t^{a}$ and $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ of Lie algebras $\gf$ and $\af$.
 Relations \eqref{eq:28},\eqref{eq:21} are necessary conditions for CFT correlation functions to be SLE martingales.
@@
 \label{sec:examples-1}
-As an example consider  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset models which are equivalent to $Z_{N}$-parafermions.
+As an example consider  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset model which is equivalent to $Z_{N}$-parafermions.
 Central charge is $c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2}$.
@@
 For field $\varphi_{(1,1)}$ we obtain $3\kappa-16+64\tau=0,\quad -64+9\kappa + 64\tau=0$, $\kappa=16/3, \tau=0$.
-So we have no additional motion for Ising model and two possible values for SLE parameter $\kappa$,  coinciding with well-known results.
+So we have no additional motion for Ising model and two possible values for SLE parameter $\kappa$,  coinciding with well-known results \cite{schramm2006conformally}.
 
@@
 
-In excellent paper \cite{bettelheim2005stochastic} connection between WZNW-models and Schramm-Loewner evolution with additional Brownian motion on group manifold was established.
-This paper also stated a problem of the connection of SLE parameters for martingales in WZNW, coset and minimal models.
-In present letter we used the method to obtain necessary and sufficient conditions on SLE martingales proposed in paper \cite{alekseev2010sle}.
+In the excellent paper \cite{bettelheim2005stochastic} connection between WZNW-models and Schramm-Loewner evolution with additional Brownian motion on group manifold was established.
+The authors also stated a problem of the connection of SLE parameters for martingales in WZNW, coset and minimal models.
+In present letter we used the method to obtain necessary conditions on SLE martingales proposed in paper \cite{alekseev2010sle}.
 This method allowed us to compare our results with parafermionic results of the papers \cite{santachiara2008sle,picco2008numerical}.
@@
 Coset structure of minimal models is manifest in field theory perturbed by external magnetic field \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
-This theory is supported by experimental data \cite{coldea2010quantum}.
+This theory is supported by recent experimental data \cite{coldea2010quantum}.
 Relation between correlation functions in coset theory and SLE observables can be a starting point for the study of domain walls in lattice models away of critical point.

### 2012-05-08 AffineLieAlgebras/SLE/paper.tex
Minor addition
Notes from V.D. applied

@@
 Schramm-Loewner evolution \cite{schramm2000scaling} is a stochastic process satisfying stochastic differential equation (\ref{eq:19}).
-Solution of the equation (\ref{eq:19}) can be seen as a probability measure on random curves (called SLE traces).
-SLE is useful for the study of critical behavior \cite{Cardy:2005kh,rohde2005basic}, since for many lattice models convergence of  domain walls to SLE traces can be proved \cite{bauer20062d,schramm2006conformally}.
-Practical computations with SLE rely on Ito calculus.
+A solution of  equation (\ref{eq:19}) can be seen as  probability measure on random curves (called SLE traces).
+SLE is useful for the study of critical behavior \cite{Cardy:2005kh,rohde2005basic}, since for many lattice models the convergence of  domain walls to SLE traces can be proved \cite{bauer20062d,schramm2006conformally}.
+Practical computations with SLE rely on Ito calculus while proofs use discrete complex analysis \cite{duminil2011conformal}.
 
 Conformal field theory \cite{belavin1984ics} is formulated in terms of families of quantum fields which usually has no direct microscopic interpretation.
-On the other hand, CFT has efficient computational tools such as Virasoro symmetry, Knizhnik-Zamolodchikov equations, fusion algebra etc and provides numerous predictions, such as celebrated Cardy formula \cite{cardy1992critical,smirnov2001critical} which gives crossing probability for critical percolation.
+On the other hand CFT has efficient computational tools such as Virasoro symmetry, Knizhnik-Zamolodchikov equations, fusion algebra etc and provides numerous predictions, such as celebrated Cardy formula \cite{cardy1992critical,smirnov2001critical} which gives crossing probability for critical percolation.
 
@@
 
-We present new class of such observables in coset conformal field theory  -- correlation functions which are martingales with respect to Schramm-Loewner evolution with additional Brownian motion on factor-space of Lie group $G$ by subgroup $A$ \cite{2011arXiv1112.4354N}.
-We derive relations connecting parameters of SLE and CFT.
+We present a new class of such observables in coset conformal field theory  -- correlation functions which are martingales with respect to Schramm-Loewner evolution with additional Brownian motion on factor-space of Lie group $G$ by subgroup $A$ \cite{2011arXiv1112.4354N}.
+We derive relations connecting SLE and CFT parameters.
 We then check the consistency of these results with the earlier results  for parafermionic observables \cite{santachiara2008sle}.
@@
 
-For us it is more convenient to use map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
+For us it is convenient to use the map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
 \begin{equation}
@@
 \end{equation}
-where $\phi_{i}$ are bulk primary fields with conformal weights $h_i$ and $\varphi(z_{t})$ is a boundary condition changing operator.
+where $\phi_{i}$ are bulk primary fields with conformal weights $h_i$ and $\varphi(z_{t})$ is boundary condition changing operator.
 
-Let $\gf$ be (semisimple) Lie algebra of Lie group $G$ and $\af$ -- Lie algebra of subgroup $A\subset G$. Denote by $x_{e}$ index of embedding $\af\to\gf$.
+Let $\gf$ be a (semisimple) Lie algebra of a Lie group $G$ and $\af$ -- Lie algebra of a subgroup $A\subset G$. Denote by $x_{e}$ embedding index for $\af\to\gf$.
 
-Primary fields in coset models are labeled by pairs $(\lambda,\eta)$ of weights of $\gf$ and $\af$-representations.
-For each $\lambda$ possible values of $\eta$ are those which appear in decomposition of representation $L^{(\mu)}_{\gf}=\bigoplus_{\eta} H^{\lambda}_{\eta}\otimes L^{(\eta)}_{\af}$.
+Primary fields in coset models are labeled by pairs $(\lambda,\eta)$ of weights for $\gf$- and $\af$-representations.
+For each $\lambda$ the set of possible weights $\eta$ includes those which appear in the decomposition  $L^{(\mu)}_{\gf}=\bigoplus_{\eta} H^{\lambda}_{\eta}\otimes L^{(\eta)}_{\af}$.
 (Some pairs are equivalent, see \cite{fuchs1996resolution,schellekens1990field}).
-We assume that boundary field $\varphi$ is also primary and labeled by weights $(\mu,\nu)$.
+We assume that boundary field $\varphi$ is also primary and is labeled by weights $(\mu,\nu)$.
 
@@
 \end{multline}
-We can extend the definition of $\mathcal{F}$ to the whole plane by doubling the number of fields $\phi_{i}$ \cite{cardy2004boundary,cardy1984conformal} and consider $w_{i},\bar w_{i}$ as independent variables.
-To simplify notation we will write $\mathcal{F}(\left\{w_{i}\right\}_{i=1}^{2N})$.
+We can extend the definition of $\mathcal{F}$ to the whole plane by doubling the number of fields $\phi_{i}$ \cite{cardy2004boundary,cardy1984conformal} and by considering $w_{i},\bar w_{i}$ as independent variables.
+To simplify notations we will write $\mathcal{F}(\left\{w_{i}\right\}_{i=1}^{2N})$.
 
-$G/A$-coset conformal field theory can be realized as WZNW-model (with gauge group $G$) interacting with pure gauge field of gauge group $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
+$G/A$-coset conformal field theory can be realized as a WZNW-model (with gauge group $G$) interacting with pure gauge field of gauge group $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
 If we fix $A$-gauge we have $G/A$ gauge symmetry.
 Then we add random gauge transformations to Schramm-Loewner evolution \cite{2011arXiv1112.4354N} similar to the case of WZNW-models \cite{bettelheim2005stochastic}.
-Denote by $\mathcal{K}$ Killing form of Lie algebra $\gf$ corresponding to Lie group $G$ and by $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) the  generators of $\gf$-representation ($\af$-representation) corresponding to primary field $\phi_{i}$.
+Denote by $\mathcal{K}$ the Killing form of a Lie algebra $\gf$ corresponding to a Lie group $G$ and by $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) the  generators of $\gf$-representation ($\af$-representation) corresponding to the primary field $\phi_{i}$.
 
-Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in right-hand-side of equation (\ref{eq:1}) gives us
+Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in the right-hand-side of equation (\ref{eq:1}) gives us
 \begin{equation*}
@@
 \end{equation*}
-Denote by $\mathcal{G}_{i}$ generator of infinitesimal transformation of primary field $\phi_{i}$:\;$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$.
-We normalize additional $\dim\gf$-dimensional Brownian motion as $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation is equal to
+We denote by $\mathcal{G}_{i}$ the generator of infinitesimal transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$.
+We normalize additional $\left(\dim\gf\right)$-dimensional Brownian motion as $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
+The generator of field transformation is equal to
 \begin{equation}
@@
 
- Ito formula  gives us the expression for the differential of $\mathcal{F}$ which should be zero due to martingale condition:
+ Ito formula  gives us an expression for the differential of $\mathcal{F}$ which should be zero due to martingale condition:
 \begin{multline}
@@
 \end{multline}
-Substitute definition \eqref{eq:3} and get 
+Substituting  definition \eqref{eq:3} we get 
 \begin{equation}
@@
 \end{equation}
-where
+with
 \begin{eqnarray*}
-  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right)\\ \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}};\; \tilde{\mathcal{J}}^{b}_{{-n}}=-\sum_{i}\frac{\tilde{t}^{b}_{i}}{(w_{i}-z)^{n}}
+  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right),\\ \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}};\; \tilde{\mathcal{J}}^{b}_{{-n}}=-\sum_{i}\frac{\tilde{t}^{b}_{i}}{(w_{i}-z)^{n}}.
 \end{eqnarray*}
-This equation is equivalent to following algebraic condition on boundary state $\varphi(0)\left|0\right>$:
+This equation is equivalent to the following algebraic condition on the boundary state $\varphi(0)\left|0\right>$:
 \begin{multline}
@@
   \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
-\left.\varphi(0)|0\right>=0
+\left.\varphi(0)|0\right>=0.
 \end{multline}
@@
 \end{multline}
-is a null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in coset theory commutation relations of full chiral algebra are
+is a null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in a coset theory commutation relations of full chiral algebra are
 \begin{equation}
@@
 \begin{array}{ll}
-  L_{n}= L_{n}^{\gf}-L_{n}^{\af} &\\
-  \left[L_{n}^{\gf},J^{a}_{m}\right]= -m J^{a}_{n+m}&\\
-  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m}&\\
+  L_{n}= L_{n}^{\gf}-L_{n}^{\af}, &\\
+  \left[L_{n}^{\gf},J^{a}_{m}\right]= -m J^{a}_{n+m},&\\
+  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m},&\\
   \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=&\\
@@
  it is more convenient to act with $L_{2}^{\gf}$ and $\left(L_{1}^{\gf}\right)^{2}$. 
- Acting with $L_{2}^{\gf}$ we get
+ Applying $L_{2}^{\gf}$ we get
 \begin{equation*}
@@
 \end{equation*}
-We use $L_{0} \varphi_{(\mu,\nu)}=h_{(\mu,\nu)} \varphi_{(\mu,\nu)}$, where conformal weight is $h_{(\mu,\nu)}= \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k x_{e}+h^{\vee}_{\af})}\right)$ and central charge is $c=\frac{k\dim \gf}{k+h^{\vee}_{\gf}}-\frac{x_{e}k\dim \af}{x_{e} k+h^{\vee}_{\af}}$ and get relation on $\kappa,\tau$:
+We use $L_{0} \varphi_{(\mu,\nu)}=h_{(\mu,\nu)} \varphi_{(\mu,\nu)}$, with the conformal weight  $h_{(\mu,\nu)}= \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k x_{e}+h^{\vee}_{\af})}\right)$ and the central charge $c=\frac{k\dim \gf}{k+h^{\vee}_{\gf}}-\frac{x_{e}k\dim \af}{x_{e} k+h^{\vee}_{\af}}$.
+This leads to the relation on $\kappa,\tau$:
 \begin{equation}
-  \label{eq:28} (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0
+  \label{eq:28} (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0.
 \end{equation}
-Second relation appears as the result of $L_{1}^{\gf}$-action:
+The second relation appears as a result of the $L_{1}^{\gf}$-action:
 \begin{equation}
@@
 \end{equation}
- where $C_{\mu}=(\mu,\mu+2\rho)$ and $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ are the eigenvalues of quadratic Casimir operators $\sum_{a}t^{a}t^{a}$ and $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ of Lie algebras $\gf$ and $\af$.
-Relations \eqref{eq:28},\eqref{eq:21} are necessary conditions for CFT correlation functions to be SLE martingales.
+ where $C_{\mu}=(\mu,\mu+2\rho)$ and $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ are the eigenvalues of the quadratic Casimir operators $\sum_{a}t^{a}t^{a}$ and $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ of Lie algebras $\gf$ and $\af$.
+Relations \eqref{eq:28},\eqref{eq:21} are the necessary conditions for CFT correlation functions to be SLE martingales.
 
@@
 \label{sec:examples-1}
-As an example consider  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset model which is equivalent to $Z_{N}$-parafermions.
-Central charge is $c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2}$.
+As an example consider  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset models which are equivalent to $Z_{N}$-parafermions.
+The central charge is $c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2}$.
 Conformal weights of primary fields with Dynkin indeces $(k,l)$ are $h_{(k,l)}=\frac{k(k+2)}{4(N+2)}-\frac{l^{2}}{4N}$.
@@
 
-Case $N=2$, $c=\frac{1}{2}$ corresponds to Ising model, we have two non-trivial primary fields with conformal weights $h_{(2,0)}=1/2, h_{(1,1)}=1/16$.
-Substituting field $\varphi_{(2,0)}$ into equations (\ref{eq:28},\ref{eq:21}) we get $3\kappa-9+4\tau =0;\quad -3+\kappa+4\tau=0$.
-Then $\kappa=3, \tau=0$.
-For field $\varphi_{(1,1)}$ we obtain $3\kappa-16+64\tau=0,\quad -64+9\kappa + 64\tau=0$, $\kappa=16/3, \tau=0$.
-So we have no additional motion for Ising model and two possible values for SLE parameter $\kappa$,  coinciding with well-known results \cite{schramm2006conformally}.
+Case $N=2$, $c=\frac{1}{2}$ corresponds to the Ising model, we have two non-trivial primary fields with conformal weights $h_{(2,0)}=1/2, h_{(1,1)}=1/16$.
+Substituting the field $\varphi_{(2,0)}$ into equations (\ref{eq:28},\ref{eq:21}) we get: $3\kappa-9+4\tau =0;\quad -3+\kappa+4\tau=0$.
+The solution is $\kappa=3, \tau=0$.
+For the field $\varphi_{(1,1)}$ the relations are $3\kappa-16+64\tau=0,\quad -64+9\kappa + 64\tau=0$, $\kappa=16/3, \tau=0$.
+So we have no additional motion for the Ising model and two possible values for SLE parameter $\kappa$  coinciding with the well-known results \cite{schramm2006conformally}.
 
-For $N=3$ parafermionic model central charge is $c=\frac{4}{5}$.
+For $N=3$ the parafermionic model central charge is $c=\frac{4}{5}$.
 Conformal weights are $h_{(0,0)}=0$, $h_{(0,2)}=h_{(0,-2)}=\frac{2}{3}\; \mathrm{mod}\; 1$, $h_{(2,0)}=\frac{2}{5}$, $h_{(2,2)}=h_{(2,-2)}=\frac{1}{15}$.
-Corresponding values of $\kappa,\tau$ are: $(\frac{208}{25},\frac{242}{225}), (\frac{10}{3},0),(\frac{80}{19},\frac{14}{171})$.
-As was mentioned in \cite{santachiara2008sle} field $\varphi_{(2,0)}$ with conformal weight $h_{(2,0)}=\frac{2}{5}$ constitutes $Z_{3}$-singlet, so  additional random walk does not appear and $\tau=0$.
-The form of equations (\ref{eq:7}) is similar to that of \cite{santachiara2008sle}, but normalization of $\tau$ differs.
+The corresponding values of $\kappa,\tau$ are: $(\frac{208}{25},\frac{242}{225}), (\frac{10}{3},0),(\frac{80}{19},\frac{14}{171})$.
+As it  was mentioned in \cite{santachiara2008sle} the field $\varphi_{(2,0)}$ with the conformal weight $h_{(2,0)}=\frac{2}{5}$ constitutes the $Z_{3}$-singlet, so  an additional random walk does not appear and $\tau=0$.
+The form of equations (\ref{eq:7}) is similar to that of \cite{santachiara2008sle}, but the normalization of $\tau$ differs.
 
-It is easy to see that for  $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset realization of minimal unitary models with $c=\frac{3N}{N+2}+1-\frac{3(N+1)}{N+3}=1-\frac{6}{(N+2)(N+3)}$ system of equations (\ref{eq:28},\ref{eq:21}) is always consistent for $\tau=0$ and we get standard connection between SLE-parameter $\kappa$ and central charge $c=\frac{(6-\kappa)(3\kappa-8)}{2\kappa}$.
+It is easy to see that for the $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset realization of minimal unitary models with $c=\frac{3N}{N+2}+1-\frac{3(N+1)}{N+3}=1-\frac{6}{(N+2)(N+3)}$ the system of equations (\ref{eq:28},\ref{eq:21}) is always consistent for $\tau=0$ and we get a standard connection between the SLE-parameter $\kappa$ and the central charge $c=\frac{(6-\kappa)(3\kappa-8)}{2\kappa}$.
 
@@
 
-In the excellent paper \cite{bettelheim2005stochastic} connection between WZNW-models and Schramm-Loewner evolution with additional Brownian motion on group manifold was established.
-The authors also stated a problem of the connection of SLE parameters for martingales in WZNW, coset and minimal models.
-In present letter we used the method to obtain necessary conditions on SLE martingales proposed in paper \cite{alekseev2010sle}.
-This method allowed us to compare our results with parafermionic results of the papers \cite{santachiara2008sle,picco2008numerical}.
+In  \cite{bettelheim2005stochastic} a connection between WZNW-models and Schramm-Loewner evolution with additional Brownian motion on group manifold was established.
+The authors also stated a problem of a possible connection of SLE parameters for martingales in WZNW, coset and minimal models.
+In present letter we used the method proposed in \cite{alekseev2010sle} to obtain necessary conditions on SLE martingales.
+This method allowed us to compare our results with parafermionic results presented in \cite{santachiara2008sle,picco2008numerical}.
 
-Coset structure of minimal models is manifest in field theory perturbed by external magnetic field \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
-This theory is supported by recent experimental data \cite{coldea2010quantum}.
-Relation between correlation functions in coset theory and SLE observables can be a starting point for the study of domain walls in lattice models away of critical point.
+The coset structure of minimal models is manifest in field theory perturbed by an external magnetic field \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
+This theory is supported by experimental data \cite{coldea2010quantum}.
+Relations between correlation functions in coset theory and SLE observables can be a starting point in studies of domain walls in lattice models away from the  critical point.
 
-Massive perturbations of $G/A$-coset theory are realized as affine Toda field theory and classified by simple roots of Lie algebra $\gf$.
+Massive perturbations of $G/A$-coset theory are realized as an affine Toda field theory and are classified by simple roots of the Lie algebra $\gf$.
 
 Massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off}.
-Addition of drift term to (\ref{eq:20}) leads to appearance of new terms in martingale condition (\ref{eq:8}).
+Inclusion of a drift term in (\ref{eq:20}) leads to the  appearance of new terms in the martingale condition (\ref{eq:8}).
 
-On the other hand perturbation can be seen as the insertion of certain primary field in all correlation functions \cite{hollowood1989rational}.
-The question is whether the interaction of this primary field with the $\tau$-term of the equation (\ref{eq:4}) lead to the same contribution as the addition of massive drift to SLE.
+On the other hand the perturbation can be seen as an insertion of certain primary field in all the correlation functions \cite{hollowood1989rational}.
+The question is whether the interaction of this primary field with the $\tau$-term of the equation (\ref{eq:4}) leads to the same contribution as the addition of a massive drift to SLE.
 
-Domain walls in  Ising model perturbed by random Gaussian external were studied numerically using Schramm-Loewner evolution in recent paper \cite{stevenson2011domain}.
-Further task is to compare this results with massive perturbations.
+Domain walls in the Ising model perturbed by a random Gaussian external field were studied numerically using Schramm-Loewner evolution in a recent paper \cite{stevenson2011domain}.
+In the forthcoming studies we will compare this results with massive perturbations.
 
@@
 \label{sec:acknowledgements}
- I am grateful to A. Bytsko, K. Izyurov, D. Chelkak and R. Santachiara for the discussions on SLE and WZNW models. This work  is supported by
+ I am grateful to A.
+Bytsko, K.
+Izyurov, D.
+Chelkak and R.
+Santachiara for the discussions on SLE and WZNW models and to V.D.
+Lyakhovsky for careful reading of the present text.
+This work  is supported by
 the Chebyshev Laboratory (Department of Mathematics and Mechanics,

### 2012-05-08 AffineLieAlgebras/SLE/paper.tex
Added some formulas to SLE paper, minor changes in thesis preamble for proper use of eps2pdf.

@@
 
-$G/A$-coset conformal field theory can be realized as a WZNW-model (with gauge group $G$) interacting with pure gauge field of gauge group $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
+$G/A$-coset conformal field theory can be realized as a WZNW-model (with gauge group $G$) interacting with pure gauge fields of gauge group $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
+The action is written in terms of fields $\gamma:\mathbb{C}\to G$ and $\alpha,\bar\alpha:\mathbb{C}\to A$:
+\begin{multline}
+  \label{eq:24}
+      S_{G/A}(\gamma, \alpha)=-\frac{k}{8\pi}\int_{S^2} d^2x\; {\cal K} (\gamma^{-1}\partial^{\mu}\gamma,\gamma^{-1}\partial_{\mu}\gamma)-\\
+ - \frac{k }{24\pi} \int_{B}\epsilon_{ijk} {\cal K}\left(
+    \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^i},
+      \left[\tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^j}
+      \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^k}\right]\right) d^3y+\\
++
+      \frac{k}{4\pi}\int_{S^2} d^{2}z \left(\mathcal{K}(\alpha, \gamma^{-1}\bar \partial \gamma)-\mathcal{K}(\bar \alpha, (\partial \gamma ) \gamma^{-1})\right.\\
+      \left.+\mathcal{K}(\alpha,\gamma^{-1}\bar \alpha \gamma)-\mathcal{K}(\alpha,\bar \alpha)\right).
+\end{multline}
+Here we denote by $\mathcal{K}$ the Killing form of a Lie algebra $\gf$ corresponding to a Lie group $G$.
+
  If we fix $A$-gauge we have $G/A$ gauge symmetry.
 Then we add random gauge transformations to Schramm-Loewner evolution \cite{2011arXiv1112.4354N} similar to the case of WZNW-models \cite{bettelheim2005stochastic}.
-Denote by $\mathcal{K}$ the Killing form of a Lie algebra $\gf$ corresponding to a Lie group $G$ and by $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) the  generators of $\gf$-representation ($\af$-representation) corresponding to the primary field $\phi_{i}$.
+Denote by $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) the  generators of $\gf$-representation ($\af$-representation) corresponding to the primary field $\phi_{i}$.
 
@@
 
+It is possible to get the perturbed theory from the action \cite{bakas1996lagrangian,hollowood1995massive,park1994deformed}
+\begin{equation}
+  S_{\text{pert}}=S_{G/A}(\gamma,\alpha)-\frac{k\lambda}{2\pi}\int {\cal K} (\gamma T, \gamma^{-1} \bar T),
+\end{equation}
+where $T,\bar T\in \gf$ are specially chosen Lie algebra elements.
+
+For example consider  $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset realization of minimal unitary models.
+Then we get perturbation by $\phi_{(2,1)}$ primary field from the action
+\begin{equation}
+  S=S_{\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}} (\gamma_1,\gamma_2,\alpha,\bar \alpha) - \frac{k\lambda}{2\pi}\int Tr(\gamma_1^{-1} \gamma_2+\gamma_2^{-1}\gamma_1)
+\end{equation}
+
 Massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off}.
@@
 Santachiara for the discussions on SLE and WZNW models and to V.D.
-Lyakhovsky for careful reading of the present text.
+Lyakhovsky for the careful reading of the text.
 This work  is supported by

### 2012-05-10 AffineLieAlgebras/SLE/paper.tex
Added one paper to bibliography

@@
 \end{equation}
+This perturbation leads to insertion of perturbing operator in all correlation functions
 
-Massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off}.
+Massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off,bauer2009off}.
 Inclusion of a drift term in (\ref{eq:20}) leads to the  appearance of new terms in the martingale condition (\ref{eq:8}).

### 2012-05-12 AffineLieAlgebras/SLE/paper.tex
Added equation with the drift.
Preliminary version is completed,  comments removed. Ready to be sent to friends.

--- 2012-05-08 AffineLieAlgebras/SLE/paper.tex
@@
 
-\newtheorem{statement}{Statement}
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{lemma}{Lemma}
-\newtheorem{mynote}{Note}[section]
-%\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
 %%% dates of submition & resubmition (if submitted once, second argument is *)
-\dates{26 April 2012}{*}
+\dates{12 May 2012}{*}
 
@@
 
-%% We
-%% consider Schramm-Loewner evolution $SLE_{\kappa}$ with additional Brownian motion on coset space
-%% $G/A$ characterised by parameter $\tau$ proposed in our paper \cite{2011arXiv1112.4354N}. We consider correlation functions in coset models of
-%% conformal field theory which satisfy martingale conditions with respect to this stochastic process.
-%% Since all minimal unitary models of conformal field theory can be obtained from coset construction
-%% for certain choice of Lie group $G$ and subgroup $A$ \cite{difrancesco1997cft} these correlation functions correspond to SLE
-%% observables appearing as the scaling limit of lattice observables. Trace of
-%% Schramm-Loewner $\gamma_{t}$ evolution describes critical domain wall in lattice models.
-%% 
  Consider some critical lattice model on the upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$ (domain wall up to some length $t$).
@@
 Conformal weights of primary fields with Dynkin indeces $(k,l)$ are $h_{(k,l)}=\frac{k(k+2)}{4(N+2)}-\frac{l^{2}}{4N}$.
-% $C_{\mu}=k(k+2)/2, C_{\nu}=l^{2}/2$
 
@@
 
-%% But correlation functions in coset conformal field theory must satisfy (generalized) Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} which are of the form
-%% \begin{equation}
-%%   \label{eq:16}
-%%  \left[ \frac{1}{2}\frac{\partial}{\partial w_{i}} +\sum_{j\neq i} \left( \frac{\sum_{a}t_{i}^{a}t_{j}^{a}}{k+h^{\vee}}-\frac{\sum_{b}\tilde t_{i}^{b}\tilde t_{j}^{b}}{x_{e}k+h_{\af}^{\vee}}\right) \right]\mathcal{F}_{\mathbb{H}}=0
-%% \end{equation}
-%% Rewrite the equation as
-%% \begin{equation}
-%%   \label{eq:22}
-%%   \left[ \frac{1}{2}\frac{\partial}{\partial w_{i}} +\sum_{j\neq i} \left( \frac{\sum_{a}t_{i}^{a}t_{j}^{a}}{k+h^{\vee}}-\frac{\sum_{b}\tilde t_{i}^{b}\tilde t_{j}^{b}}{x_{e}k+h_{\af}^{\vee}}\right) \right]\mathcal{F}_{\mathbb{H}}=0
-%% \end{equation}
-%% 
-%% From this relations and equation \eqref{eq:8} we can write sufficient conditions for SLE martingale to be CFT correlation function:
-%% \begin{equation}
-%%   \label{eq:23}
-%%   M x = 0
-%% \end{equation}
-%% 
-%% It is also possible to consider coset theory as $G\times A$  gauge theory and impose constraints on physical states later (See \cite{hwang1993brst,kogan1997knizhnik,gawdzki1988g,figueroa89equivalence}).
-In this case second term in equation \eqref{eq:3} will include sum over $\gf$ and $\af$ generators and two parameters of Brownian motion $\tau_{\gf}$ and $\tau_{\af}$.
-%% 
 \section{Conclusion and outlook}
@@
 Massive perturbations of $G/A$-coset theory are realized as an affine Toda field theory and are classified by simple roots of the Lie algebra $\gf$.
-
-It is possible to get the perturbed theory from the action \cite{bakas1996lagrangian,hollowood1995massive,park1994deformed}
+Affine Toda field theory can be obtained by adding perturbation term to  the action (\ref{eq:24}):
 \begin{equation}
@@
 \end{equation}
-where $T,\bar T\in \gf$ are specially chosen Lie algebra elements.
+where $T,\bar T\in \gf$ are specially chosen Lie algebra elements \cite{bakas1996lagrangian,hollowood1995massive,park1994deformed}. 
+The perturbation leads to an insertion of certain primary field in all the correlation functions  \cite{hollowood1989rational}.
+It was shown that massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off,bauer2009off}.
+The question is whether the interaction of the perturbing primary field with the $\tau$-term of the equation (\ref{eq:4}) leads to the same contribution as the addition of a massive drift to SLE.
 
-For example consider  $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset realization of minimal unitary models.
-Then we get perturbation by $\phi_{(2,1)}$ primary field from the action
-\begin{equation}
-  S=S_{\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}} (\gamma_1,\gamma_2,\alpha,\bar \alpha) - \frac{k\lambda}{2\pi}\int Tr(\gamma_1^{-1} \gamma_2+\gamma_2^{-1}\gamma_1)
-\end{equation}
-
-Massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off}.
-Inclusion of a drift term in (\ref{eq:20}) leads to the  appearance of new terms in the martingale condition (\ref{eq:8}).
-
-On the other hand the perturbation can be seen as an insertion of certain primary field in all the correlation functions \cite{hollowood1989rational}.
-The question is whether the interaction of this primary field with the $\tau$-term of the equation (\ref{eq:4}) leads to the same contribution as the addition of a massive drift to SLE.
-
-Domain walls in the Ising model perturbed by a random Gaussian external field were studied numerically using Schramm-Loewner evolution in a recent paper \cite{stevenson2011domain}.
-In the forthcoming studies we will compare this results with massive perturbations.
+In the forthcoming studies we will address this question and compare  massive perturbations of coset models with the numerical studies of domain walls in the Ising model perturbed by a random Gaussian external field \cite{stevenson2011domain}.
 
@@
 
-%%  
-%%  
-%%  
-%%  Coset  models are specified by Lie algebra
-%%  $\gf$ and its subalgebra $\af$. Denote by $J_{n}^{a}$ the generators of affine Lie algebra $\gfh$
-%%  and by $\tilde{J}_{n}^{b}$ the generators of $\afh$, so that $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b}
-%%  J^{a}_{n}$. 
-%%  Virasoro generators in coset models are given by the difference of Sugawara expressions
-%%  of $\gf$ and $\af$-WZNW models:
-%%  \begin{equation*} L_{n}=L_{n}^{\gf}-L_{n}^{\af}
-%%  \end{equation*}
-%%   Commutation relations of Virasoro generators with generators of subalgebra $\afh$
-%%  are trivial
-%%  \begin{equation}
-%%    \label{eq:26} \left[L_{n},\tilde{J}^{b}_{m}\right]=0
-%%  \end{equation}
-%%  
-%%  Commutation relations between generators of $\gfh$ and Virasoro generators are now
-%%  \begin{equation}
-%%    \label{eq:1}
-%%    \left[ L_{n}, J_{m}^{a} \right] = [L_{n}^{\gf}-L_{n}^{\af},J_{m}^{a}]= 
-%%  \end{equation}
-%%  
-%%  Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields
-%%   $A,
-%%  \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}.
-%%   Then fields
-%%  are labeled by pairs of weights $(\mu,\nu)$, where $\mu$ is the weight of $\gfh$ and $\nu$ is the
-%%  weight of $\afh$ correspondingly. But there are selection rules, i.e. the branching functions for
-%%  certain pairs of weights $(\mu,\nu)$ vanish. There is also a redundancy, i.e. non-vanishing
-%%  branching functions for distinct pairs $(\mu,\nu)$ turn out to be identical
-%%  \cite{fuchs1996resolution,schellekens1990field}.
-%%  
-%%  So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ of
-%%  algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$. Some
-%%  pairs are equivalent. This equivalence is given by the action of so called ``simple currents''
-%%  $(J,\tilde{J})$, which are certain elements of outer automorphisms group $\mathcal{O}(\gfh)\times
-%%  \mathcal{O}(\afh)\approx B(G)\times B(A)$ of $\gfh\times\afh$, where $B(G)$ is center of Lie group
-%%  G. We can think of simple currents as of primary fields and their action on fields of theory are
-%%  then given by fusion product \cite{difrancesco1997cft}. So primary fields of coset model are given
-%%  by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where
-%%  $(J,\tilde J)$ such that their conformal weights are equal: $h_{J}-h_{\tilde{J}}=0$.
-%%  
-%%  Conformal weight of coset primary field is equal to
-%%  \begin{multline}
-%%  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b
-%%  \tilde{J}^b_0 \tilde{J}^b_0 \right) \left|\phi_{(\mu,\nu)}\right>=\\
-%%  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
-%%  \end{multline} It is possible to obtain analogues of Knizhnik-Zamolodchikov equations for coset
-%%  models \cite{kogan1997knizhnik}:
-%%  \begin{equation} \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq
-%%  j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde
-%%  t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots
-%%  \phi_{N}(z_{N})\right>=0
-%%    \label{eq:6}
-%%  \end{equation}
-%%  
-%%  Let us introduce Schramm-Loewner evolution corresponding to coset models. The idea is to constrain
-%%  additional Brownian motion on group manifold to the factor space $G/A$.
-%%  
-%%  
-%%  To study SLE on $G/A$ factor space we restrict random walk on group manifold by the choice of basis
-%%  in $\gf$. Assume that generators $\{J^{a};\; a=1\dots \dim\gf\}$ are chosen in such way that
-%%  $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\;
-%%  a=\dim\gf-\dim\af\dots \dim\gf\}$ are the generators of subalgebra
-%%  $\af\subset \gf$. Now we can consider $(\dim\gf-\dim\af)$-dimensional Brownian
-%%  motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \;
-%%  d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\dim\gf-\dim\af$.
-%%  
-%%  Then for generator of field transformation we can write
-%%  \begin{equation} \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa}
-%%  d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\dim\gf-\dim\af}\left(d
-%%  \theta ^{a} t^{a}_{i}\right)\right)
-%%  \label{eq:5}
-%%  \end{equation}
-%%   Substituting to equation \eqref{eq:8} we get martingale condition
-%%  
-%%  \begin{equation} \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa
-%%  \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\dim\gf-\dim\af}
-%%  \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right) \mathcal{F}_{\mathbb{H}}=0
-%%  \label{eq:9}
-%%  \end{equation}
-%%  
-%%  which can be rewritten as the requirement for
-%%  \begin{equation} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
-%%  \left(\sum_{a=1}^{\dim\gf-\dim\af}J^{a}_{-1}J^{a}_{-1}\right)\right)
-%%  \phi_{(\mu,\nu)}
-%%  \label{eq:10}
-%%  \end{equation}
-%%   to be level two null-field.
-%%  
-%%   It is not always convenient to work with generators
-%%  orthogonal with respect to Killing form $\mathcal{K}$, sometimes it is preferable to use Chevalley
-%%  or Cartan-Weyl basis. So we change normalization condition of additional
-%%  $\dim\gf$-dimensional Brownian motion \eqref{eq:5} to $\mathbb{E}\left[d\theta^{a}\;
-%%  d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation
-%%  \eqref{eq:2} is
-%%  \begin{equation*} \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa}
-%%  d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d
-%%  \theta ^{a} t^{a}_{i}\right)\right).
-%%  \end{equation*}
-%%   Martingale condition \eqref{eq:8} can be written as
-%%  \begin{equation*} \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa
-%%  \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
-%%  \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)
-%%  \mathcal{F}_{\mathbb{H}}=0.
-%%  \end{equation*}
-%%   This equation can again be rewritten as the requirement for
-%%  \begin{equation} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
-%%  \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
-%%  \phi_{(\mu,\nu)}
-%%  \label{eq:30}
-%%  \end{equation}
-%%   to be level two null-field.
-%%  
-%%  Acting with $L_{2}$ we get
-%%  \begin{equation*}
-%%    L_{2}\psi= \left(-8 L_{0}+c/2+ 3 \kappa L_{0}+\frac{1}{2}\tau k \dim\gf\right)
-%%  \phi_{(\mu,\nu)}
-%%  \end{equation*}
-%%  \begin{equation}
-%%    \label{eq:28} (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
-%%  \end{equation}
-%%  
-%%  Now we act with $L_{1}^{2}$  and obtain
-%%  \begin{equation}
-%%    \label{eq:17} 12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
-%%  (C_{\mu}-\tilde{C}_{\nu})=0,
-%%  \end{equation}
-%%   where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator
-%%  $\sum_{a}t^{a}t^{a}$. We need to get one more equation since we
-%%  have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so
-%%  $L_{1}\psi=0$ and then $J_{1}^{a}L_{1}\psi=0,\; \tilde{J}_{1}^{b} L_{1}\psi=0$, so
-%%  
-%%  \begin{equation}
-%%  L_{1} \psi=L_{1}\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
-%%  \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
-%%  \phi_{(\mu,\nu)}
-%%  \end{equation}
-%%  
-%%  \begin{equation*}
-%%  L_{1}\psi = \left(-6 L_{-1}+\kappa (2  L_{-1} L_{0}+L_{0}) + \tau \sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{0}\right)
-%%  \phi_{(\mu,\nu)}
-%%  \end{equation*}
-%%  \begin{equation*}
-%%    L_{1}^{2}\psi= \left(-12 L_{0}+\kappa (4  L_{0}^{2}+2 L_{0}) + \tau \sum_{a=1}^{\dim\gf}J^{a}_{0}J^{a}_{0}\right)
-%%  \phi_{(\mu,\nu)}
-%%  \end{equation*}
-%%  \begin{equation*}
-%%    J_{1}^{a}L_{1} \psi= \left(-6 J_{0}^{a}+\kappa (2  J_{0}^{a} L_{0}+J_{0}^{a}) + \tau
-%%      \sum_{b=1}^{\dim\gf}\sum_{c=1}^{\dim\gf}i f^{abc}J^{c}_{0}J^{b}_{0}+k\tau J_{0}^{a}\right)
-%%  \phi_{(\mu,\nu)}
-%%  \end{equation*}
-%%  
-%%  
-%%  \begin{equation*}
-%%    L_{2}\psi= \left(-8 L_{0}+c/2+ 3 \kappa L_{0}+\frac{1}{2}\tau k \dim\gf\right)
-%%  \phi_{(\mu,\nu)}
-%%  \end{equation*}
-%%  
-%%  \begin{eqnarray*}
-%%    (3\kappa-8) h_{(\mu,\nu)}+c/2+\frac{1}{2}\tau k \dim\gf=0\\
-%%    -12 h_{(\mu,\nu)}+\kappa (4 h_{(\mu,\nu)}^{2}+2 h_{(\mu,\nu)}) +\tau C(\mu) =0\\
-%%    (-6 +\kappa (2 h_{(\mu,\nu)}+1)+\tau
-%%  \end{eqnarray*}
-%%  \begin{equation}
-%%    \label{eq:29} \left(-6 + \kappa + \tau + 2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0}
-%%  \phi_{(\mu,\nu)}=0
-%%  \end{equation}
-%%  
-%%  Acting on \eqref{eq:30} with $L_{2}$ and $L_{1}^{2}$ we can obtain equations \eqref{eq:28} and
-%%  \eqref{eq:17}. To get more equations we can act by $\afh$-generators $\tilde{J}^{b}_{1}$ and $L_{1}$
-%%  similarly to what was done with $J^{3}_{1}$ to get equation \eqref{eq:29}.
-%%  
-%%  To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov
-%%  equations \eqref{eq:6} as was done for WZNW-models in paper \cite{alekseev2010sle}.
-%%  
-%%  
-%%  Now consider simple example. Let $G=SU(2)$ and $A=U(1)$, and corresponding Lie algebras
-%%  $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator
-%%  $J^{3}$, $\af\subset\gf$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
-%%  
-%%   The equation \eqref{eq:10} is now
-%%  \begin{equation}
-%%    \label{eq:11} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
-%%  \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
-%%  \end{equation}
-%%   If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\;
-%%  J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
-%%  \begin{equation} \psi= \left(-2
-%%  L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right)
-%%  \phi_{(\mu,\nu)}
-%%  \label{eq:12}
-%%  \end{equation}
-%%   which is similar to the equations for parafermionic fields introduced in paper
-%%  \cite{santachiara2008sle}.
-%%  
-%%  Central charge in this case is equal to
-%%  \begin{equation}
-%%    \label{eq:14} c=\frac{2(k-1)}{k+2}
-%%  \end{equation}
-%%  
-%%  Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
-%%  \begin{equation}
-%%    \label{eq:13} L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{(\mu,\nu)}=0,
-%%  \end{equation}
-%%   and obtain
-%%  \begin{equation}
-%%    \label{eq:28} (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
-%%  \end{equation}
-%%   Another equation can be obtained by action of $L_{1}^{2}$
-%%  \begin{equation}
-%%    \label{eq:15} L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau
-%%  (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{(\mu,\nu)}=0
-%%  \end{equation}
-%%   Since
-%%  $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$
-%%  we have
-%%  \begin{equation}
-%%    \label{eq:17} 12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
-%%  (C_{\mu}-\tilde{C}_{\nu})=0,
-%%  \end{equation}
-%%   where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator
-%%  $\sum_{a}t^{a}t^{a}$. For $u(1)$ it is just $\nu^{2}$. We need to get one more equation since we
-%%  have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so
-%%  $L_{1}\psi=0$ and then $J_{1}^{3}L_{1}\psi=0$, so
-%%  \begin{equation}
-%%    \label{eq:29} \left(-6 + \kappa + \tau + 2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0}
-%%  \phi_{(\mu,\nu)}=0
-%%  \end{equation}
-%%  
-%%  
-%%  Turn to the case $k=2, \;c=1/2$ which corresponds to square lattice Ising model. We have three
-%%  non-equivalent fields numbered by the pairs of $su(2)$ and $u(1)$ weights, which are $\phi_{(0,0)},
-%%  \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$. The
-%%  equation \eqref{eq:29} is trivial for $\phi_{(0,0)}$ and $\phi_{(0,2)}$, so the equations
-%%  \eqref{eq:17}, \eqref{eq:28} are consistent although we do not know how to interpret $\tau$ in
-%%  context of the Ising model. If we consider the field $\phi_{(1,1)}$ we have no solution for
-%%  $\kappa,\tau$, so we see that not every primary field corresponds to some boundary condition
-%%  changing operator.
-%%  
-%%  
-%%  \section{Algebraic equations}
-%%  \label{sec:algebraic-equations}
-%%  
-%%  \section{Examples}
-%%  \label{sec:examples}
-%%
-
 \bibliography{bibliography}{}

### 2012-05-17 AffineLieAlgebras/Thesis/1.tex
Some changes in thesis structure

@@
-\chapter{Рекуррентные соотношения для коэффициентов ветвления представлений аффинных алгебр Ли}
+\chapter{Разложение сингулярных элементов и рекуррентные соотношения для коэффициентов ветвления}
 \label{cha:affine-lie-algebras}
@@
 Реализация алгоритма на языке {\it Mathematica} и дополнительные примеры машинных вычислений описаны в главе  \ref{cha:computational-methods}.
-
-%%  \subsubsection{Notation}
-%%  \label{sec:notation}
-%%  
-%%  Consider affine Lie algebras $\gf$ and $\af$ with
-%%  underlying finite-dimensional subalgebras $\go$ and $%
-%%  \ao$ and an injection $\af\longrightarrow \frak{g%
-%%  }$ such that $\af$ is a reductive subalgebra $\frak{a\subset g}$ with
-%%  correlated root spaces: $\hf_{\af}^{\ast }\subset \hf_{\frak{g%
-%%  }}^{\ast }$ and $\hf_{\ao}^{\ast }\subset \frak{h%
-%%  }_{\go}^{\ast }$\
-%%  .
-%%  We use the following notations:
-%%  
-%%  $L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
-%%  of $\gf$ with the highest weight $\mu $\ ; (resp. integrable $\af$
-%%  -module with the highest weight $\nu $ );
-%%  
-%%  $r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\gf$ $%
-%%  \left( \mbox{resp. }\af\right) $ ;
-%%  
-%%  $\Delta $ $\left( \Delta _{\af}\right) $--- the root system; $\Delta
-%%  ^{+} $ $\left( \mbox{resp. }\Delta _{\af}^{+}\right) $--- the positive
-%%  root system (of $\gf$ and $\af$ respectively);
-%%  
-%%  $\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\af}\left(
-%%  \alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $\Delta
-%%  $ (resp. in $\left( \Delta _{\af}\right) $);
-%%  
-%%  $\co{\Delta}$ , $\left( \co{\Delta _{\af}}%
-%%  \right)$ --- the finite root system of the subalgebra $\co{%
-%%  \gf}$ (resp. $\co{\af}$);
-%%  
-%%  $\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\af}^{\nu }\right) $ --- the
-%%  weight diagram of $L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right)
-%%  $ ;
-%%  
-%%  $W$ , $\left( W_{\af}\right) $--- the corresponding Weyl group;
-%%  
-%%  $C$ , $\left( C_{\af}\right) $--- the fundamental Weyl chamber;
-%%  
-%%  $\bar{C}, \left(\bar{C_{\mathfrak{a}}}\right)$ --- the closure of the fundamental Weyl chamber;
-%%  
-%%  $\rho $\ , $\left( \rho _{\af}\right) $\ --- the Weyl vector;
-%%  
-%%  $\epsilon \left( w\right) :=\det \left( w\right) $ ;
-%%  
-%%  $\alpha _{i}$ , $\left( \beta _{j}\right) $ --- the $i
-%%  $-th (resp. $j$-th) basic root for $\gf$ $\left( \mbox{resp. }\af%
-%%  \right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
-%%  
-%%  $\delta $ --- the imaginary root of $\gf$ (and of $\af$ if any);
-%%  
-%%  $\alpha _{i}^{\vee }$ , $\left( \beta _{j}^{\vee
-%%  }\right) $--- the basic coroot for $\gf$ $\left( \mbox{resp. }\af%
-%%  \right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;
-%%  
-%%  $\co{\xi }$ , $\co{\xi _{\left( \af\right) }}$
-%%  --- the finite (classical) part of the weight $\xi \in P$ , $\left( \mbox{%
-%%  resp. }\xi _{\left( \af\right) }\in P_{\af}\right) $;
-%%  
-%%  $\lambda =\left( \co{\lambda };k;n\right) $ ---
-%%  decomposition of the affine weight $\lambda$ indicating the finite
-%%  part $\co{\lambda }$, the level $k$ and the grade $n$;
-%%  
-%%  $P$ $\left( \mbox{resp. } P_{\af}\right) $ \ --- the weight lattice;
-%%  
-%%  $m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
-%%  }\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mbox{%
-%%  resp. }\in P_{\af}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
-%%  L_{\af}^{\nu } $);
-%%  
-%%  $ch\left( L^{\mu }\right) $ $\left( \mbox{resp. }ch\left( L_{\af}^{\nu
-%%  }\right) \right) $--- the formal character of $L^{\mu }$ $\left( \mbox{resp. }%
-%%  L_{\af}^{\nu }\right) $;
-%%  
-%%  $ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
-%%  +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
-%%  \mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;
-%%  
-%%  $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
-%%  mult}\left( \alpha \right) }}\quad $
-%%  $\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
-%%  \af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
-%%  \left( \alpha \right) }}\right) $--- the Weyl denominator.
-%%  
-%%  
-%%  
-\section{Простые алгебры Ли, алгебра петель, центральные расширения и аффинные алгебры Ли}
-
-\label{sec:intro-simple-lie-algebras}
-\begin{definition}
-{\it Алгебра Ли $\gf$} -- это векторное пространство с билинейной операцией $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, которая называется  {\it скобкой Ли или коммутатором}.
-Если выбрать некоторый базис  $X_{i}$ в $\gf$, то коммутационные соотношения можно задать при помощи  {\it структурных констант} $C_{ijk}$:
-\begin{equation}
-  \label{eq:1}
-  [X^{i},X^{j}]=\sum_{k} C^{ij}_{k} X^{k}
-\end{equation}
-
-\end{definition}
-
-Алгебра Ли называется {\it простой} если она не содержит нетривиальных идеалов относительно коммутатора. {\it Полупростая} алгебра Ли -- это прямая сумма простых алгебр Ли.
-
-{\it Подалгеброй Картана}  $\hfg$ называется нильпотентная подалгебра алгебры $\gf$, совпадающая со своим нормализатором. Мы обозначаем элементы базиса в $\hfg$ через $H^{i}$.
-
-Форма Киллинга на  $\gf$ порождает невырожденную билинейную форму $(\cdot,\cdot)$ на подалгебре Картана $\hfg$, позволяющую идентифицировать $\hfg$ с подпространством дуального пространства  $\hfg^{*}$ линейных функционалов на $\hfg$.
-{\it Веса}  -- это элементы  $\hfg^{*}$, мы обозначаем их греческими буквами $\mu,\nu, \omega, \lambda\dots$
-
-Коммутационные соотношения  (\ref{eq:1}) можно записать в компактной форме, если выбрать базис специальным образом.
-Такой базис описывается корневой системой, которая определяется в разделе \ref{sec:weights-roots} (Смотри также \cite{humphreys1997introduction,humphreys1992reflection}).
-
-Чтобы определить аффинные алгебры нам нужно обсудить процедуру центрального расширения алгебры Ли.
-Напомним несколько определений (см \cite{fuks1986cohomology},\cite{fuks1984}, \cite{feigin1988}).
-\begin{definition}
-\label{def:1}
-Будем рассматривать алгебру Ли $\gf$ над полем $k=\mathbb{C},\mathbb{R}$.
-Векторное пространство $A$ над полем $k$ называется {\it модулем над $\gf$} или {\it $\gf$-модулем}, если задано билинейное отображение $\mu:\gf\times A\to A$, такое что $\mu([X,Y],a)=\mu(X,\mu(Y,a))-\mu(Y,\mu(X,a))$ для $X,Y\in \gf, a\in A$.
-Далее мы будем опускать символ $\mu$ и писать $X a= \mu(X,a)$.
-\end{definition}
-\begin{definition}
-  {\it $n$-мерная коцепь с коэффициентами в $A$} -- это кососимметричный $n$-линейный функционал на $\gf$ со значениями в $A$. Пространство $n$-коцепей $C^{n}(\gf;A)=\mathrm{Hom}(\wedge^{n}\gf;A)$.
-\end{definition}
-Заметим, что элементы $\gf$ действуют на $C^{n}(\gf;A)$.
-\begin{definition}
-  Внешний дифференциал $d=d_{n}:C^{n}(\gf;A)\to C^{n+1}(\gf;A)$ определяется формулой
-  \begin{multline}
-    \label{eq:68}
-    (dc) (X_{1},\dots, X_{n+1})=\sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} c([X_{s},X_{t}],X_{1},\dots,\hat X_{s},\dots,\hat X_{t},\dots X_{n+1})\\
-    +\sum_{1\leq s\leq n+1} (-1)^{s}X_{s} c(X_{1},\dots \hat X_{s},\dots X_{n+1})
-  \end{multline}
-\end{definition}
-Нетрудно проверить, что последовательность
-\begin{equation}
-  \label{eq:40}
-  \dots\stackrel{d_{n}}{\longleftarrow} C^{n}(g;A)\stackrel{d_{n-1}}{\longleftarrow} C^{n-1}(\gf;A)\leftarrow \dots \leftarrow C^{1}(\gf;A) \stackrel{d_{0}}{\longleftarrow} C^{0}(\gf;A)\leftarrow 0
-\end{equation}
-точна.Тогда $\{C^{n}(\gf;A),d_{n}\}=C^{*}(\gf;A)$ есть комплекс.
-\begin{definition}
-Соответствующие когомологии называются {\it когомологиями алгебры $\gf$ с коэффициентами в $A$} и обозначаются через $H^{n}(\gf;A)=\mathrm{Ker}\; d_{n}/\mathrm{Im}\; d_{n-1}$.
-
-\end{definition}
-Заметим, что поле $k$ может рассматриваться как тривиальный $\gf$-модуль. В этом случае второй член в формуле \eqref{eq:1} исчезает и используют сокращенные обозначения $C^{n}(\gf), H^{n}(\gf)$.
-\begin{definition}
-  Определим, заодно, и гомологии. Пространство $n$-мерных цепей $C_{n}(\gf;A)=A\otimes \wedge^{n}\gf$, дифференциал $\partial=\partial_{n}:C_{n}(\gf;A)\to C_{n-1}(\gf;A)$ определяется формулой
-  \begin{multline}
-    \label{eq:98}
-    \partial(a\otimes (X_{1}\wedge \dots \wedge X_{n})) =\\ \sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} a\otimes ([X_{s},X_{t}]\wedge X_{1} \wedge\dots\wedge\hat X_{s}\wedge \dots\wedge \hat X_{t}\wedge \dots\wedge X_{n+1})\\
-    +\sum_{1\leq s\leq n+1} (-1)^{s}(X_{s} a)\otimes (X_{1}\wedge\dots\wedge \hat X_{s}\wedge\dots\wedge X_{n+1})
-  \end{multline}
-  Аналогично определяется точная последовательность, комплекс и группа гомологий $H_{n}(\gf;A)$.
-\end{definition}
-\begin{definition}
-  {\it Одномерным центральным расширением алгебры $\gf$ } называется точная последовательность
-  \begin{equation}
-    \label{eq:62}
-    0\to k \to \tilde \gf\to \gf\to 0,
-  \end{equation}
-  такая что образ $k\to \tilde\gf$ содержится в центре $\tilde\gf$.
-\end{definition}
-Заметим, что всякий 2-коцикл $c\in C^{2}(\gf;A), \; dc=0$ определяет центральное расширение $\gf$:
-\begin{equation}
-  \label{eq:64}
-  0\to k\stackrel{\lambda\to (0,\lambda)}{\longrightarrow}\tilde\gf=\gf\oplus k \stackrel{(X,\lambda)\to X}{\longrightarrow} \gf\to 0
-\end{equation}
-Скобка Ли в алгебре $\tilde\gf$, которая равна $\gf\oplus k$ как векторное пространство, определяется равенством
-\begin{equation}
-  \label{eq:103}
-  [(X,\lambda),(Y,\mu)]=([X,Y],c(X,Y))
-\end{equation}
-Тождество Якоби для такой скобки равносильно тому, что $c$\; --- 2-коцикл. Когомологичным коциклам отвечают эквивалентные расширения.
-
-Два расширения $\tilde \gf$ и $\tilde{\tilde\gf}$ называются эквивалентными, если существует изоморфизм $I:\tilde\gf\to \tilde{\tilde \gf}$ такой, что диаграмма коммутирует:
-\begin{equation}
-  \label{eq:104}
-  \begin{diagram}
-    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \arrow{s,l}{id} \node{\tilde\gf}\arrow{s,l}{I} \arrow{e,t}{} \node{k}\arrow{s,r}{id} \arrow{e,t}{} \node{0}\\
-    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \node{\tilde{\tilde\gf}} \arrow{e,t}{} \node{k} \arrow{e,t}{} \node{0}
-  \end{diagram}
-\end{equation}
-%% \begin{exercise}
-%%  Построить изоморфизм $I$.   
-%% \end{exercise}
-
-Таким образом пространство $H^{2}(\gf)$ -- это множество классов 1-мерных центральных расширений $\gf$. Нуль в $H^{2}(\gf)$  соответствует тривиальному расширению.
-
-Для алгебры Витта \eqref{eq:2} существует коцикл
-\begin{equation}
-  \label{eq:105}
-  c(l_{n},l_{m})=\frac{1}{12}(m^{3}-m)\delta_{-n,m}
-\end{equation}
-%% \begin{exercise}
-%%   Проверить, что $c$ -- коцикл алгебры Витта. 
-%% \end{exercise}
-Соответствующее центральное расширение алгебры Витта называется алгеброй Вирасоро. Коммутационные соотношения этой алгебры имеют вид
-\begin{eqnarray}
-  \label{eq:106}
-  [L_{n},c]=0\\
-  \left[L_{n},L_{m}\right]=(n-m)L_{n+m} +\frac{c}{12} (m^{3}-m) \delta_{-n,m}
-\end{eqnarray}
-Можно показать, что $H^{2}(Witt)\cong \mathbb{C}$ и все нетривиальные коциклы пропорциональны $c$. 
-(Доказательство есть в \cite{fuks1986cohomology}, \cite{schottenloher2008mathematical}).
-
-{\it Алгебра петель} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, соответствующая полупростой алгебре Ли $\gf$, определяется коммутационными соотношениями
-\begin{equation}
-  \label{eq:108}
-  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
-\end{equation}
-Центральное расширение алгебры петель ведет к возникновению дополнительного члена
-\begin{equation}
-  \label{eq:112}
-   [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
-\end{equation}
-Эта алгебра $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ называется (не скрученной)  {\it аффинной алгеброй Ли} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
-
-\subsection{Модули, веса и корни}
-\label{sec:weights-roots}
-
-Пусть $\gf$ -- конечномерная или аффинная алгебра Ли. Мы ввели модули алгебры $\gf$ в определении \ref{def:1}. Широко используется альтернативный термин {\it представление}.
-
-%%    $\gf$-модулем называется векторное пространство $V$ с билинейным отображением $\gf \times V\to V$, таким, что выполнено равенство
-%%  \begin{equation}
-%%    \label{eq:130}
-%%    [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
-%%  \end{equation}
-\begin{definition}
-Представление алгебры  $\gf$ на векторном пространстве $V$ называется гомоморфизм $\gf\to gl(V)$ из $\gf$ в алгебру Ли эндоморфизмов векторного пространства $V$, где скобка задана коммутатором:
-\begin{equation}
-  \label{eq:113}
-  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{для}\; x,y\in \gf, v\in V  
-\end{equation}
-
-\end{definition}
-
-В произвольном представлении операторы, соответствующие генераторам подалгебры Картана $H^{i}$ можно одновременно диагонализовать путем специального выбора базиса
- $\{v_{j}\}$ в $V$:
-\begin{equation}
-  \label{eq:114}
-  H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
-\end{equation}
-Собственные значения $\nu^{i}_{j}$ генераторов Картана на элементе базиса $v_{j}$ определяют вес  $\nu_{j}\in \hfg^{*}$, такой, что $\nu_{j}(H^{i})=\nu_{j}^{i}$.
-Вектор $v\in V$ называется весовым вектором веса  $\lambda$, если $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
-Весовое подпространство состоит из всех весовых векторов $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
-Кратностью веса  $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ называется размерность весового подпространства.
-
-Структура модуля определяется набором весов, так как действие генераторов $E^{\alpha}$ на весовых векторах дается выражением
-\begin{equation}
-  \label{eq:115}
-  E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
-\end{equation}
-Структуру модуля можно записать в виде формального характера
-\begin{equation}
-  \label{eq:116}
-  \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
-\end{equation}
-Характер  $\mathrm{ch}V\in \mathcal{E}$ -- это элемент алгебры  $\mathcal{E}$, порожденной формальными экспонентами весов.
-Характер можно специализировать --- взять его значение на некотором элементе $\xi\in\hf$.
-
-Алгебра Ли является собственным модулем по отношению к специальному представлению, называющемуся присоединенном. Действие генераторов в этом представлении дается скобкой $ad_{X} Y=[X,Y]$. 
-{\it Корни} -- это веса присоединенного представления алгебры $\gf$.
-Они определяют коммутационные соотношения в алгебре следующим образом.
-Обозначим через $\Delta$ множество корней.
-Для каждого $\alpha\in \Delta$ существует корень  $-\alpha\in \Delta$ и генераторы $E^{\alpha}, E^{-\alpha}$, такие, что
-\begin{align}
-  \label{eq:63}
-  &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
-  &\left[E^{\alpha},E^{\beta}\right]=
-  \begin{cases}
-    N_{\alpha,\beta} E^{\alpha+\beta}, & \mbox{if}\; \alpha+\beta\in \Delta\\
-    \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
-    0,&\mbox{в остальных случаях}
-  \end{cases}
-\end{align}
-
-В корневой системе $\Delta$ можно выбрать множество положительных корней.
-Это подмножество  $\Delta^{+}\subset \Delta$, такое, что для любого корня $\alpha\in\Delta$ ровно один из корней $\alpha, -\alpha$ содержится $\Delta^{+}$ и для любых двух различных положительных корней $\alpha, \beta\in \Delta^{+}$, таких, что $\alpha+\beta\in \Delta$ их сумма тоже положительна $\alpha+\beta\in\Delta^{+}$.
-Элементы множества $-\Delta^{+}$ называются отрицательными корнями.
-
-Положительный корень называется {\it простым} если его нельзя представить в виде суммы положительных корней.
-Множество простых корней  $\Phi=\left\{\alpha_{i}\right\}$ является базисом в $\hfg^{*}$ и каждый корень может быть записан как сумма $\alpha=\sum_{i}n_{i}\alpha_{i}$, где все $n_{i}$ не отрицательны или не положительны одновременно.
-В случае конечномерной алгебры Ли  $\gf$ простые корни можно пронумеровать числами от  1 до ранга алгебры $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
-Такая нумерация порождает лексикографическое упорядочение корневой системы.
-Старший по отношению к этому упорядочению корень обозначается через $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, его координаты в базисе простых корней $a_i$ называются  {\it марками}.
-$\theta$ -- это старший вес присоединенного модуля (См.
-раздел \ref{sec:high-weight-modul}).
-{\it Ко-марками} называются числа, равные $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
-
-В аффинной алгебре Ли  $\hat\gf$ множество корней  $\Delta$ бесконечно, но набор простых корней  $\Phi$ конечен.
-Обозначим его элементы через $\alpha_{0},\dots \alpha_{r}$, где $r=\mathrm{rank}(\gf)$.
-Корни $\alpha_1,\dots, \alpha_r$ -- это корни соответствующей конечномерной алгебры Ли $\go$.
-Простой корень  $\alpha_0=\delta-\theta$ -- это разность  {\it мнимого корня} $\delta$ и $\theta$ -- старшего корня алгебры $\go$.
-Заметим, что кратность корня  $\mathrm{mult}(\alpha)$ в случае аффинной алгебры Ли может быть больше единицы.
-
-Подалгебра  $\bff_{+}\subset \gf$, порожденная генераторами $H^{i}, E^{\alpha}$, соответствующими положительным корням $\alpha\in \Delta^{+}$, называется подалгеброй Бореля.
-
-{\it Параболическая подалгебра}  $\pf_{I}\supset \bff_{+}$ содержит подалгебру Бореля и порождена некоторым подмножеством простых корней  $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
-Она образована подмножеством генераторов  $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
-{\it Регулярная подалгебра} $\af\subset\gf$ определяется корневой системой  $\Delta_{\af}$, множество простых корней которой  $\{\beta_{i}, i=1,\dots,r_{\af}\}$ является подмножеством множества $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ корней алгебры $\gf$.
-
- {\it Группа Вейля} $W_{\gf}$ порождается отражениями $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$, соответствующим простым корням $\{\alpha_{i}\}$:
-\begin{equation}
-  \label{eq:117}
-  s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
-\end{equation}
-Корневая система и характеры представлений инвариантны относительно действия группы Вейля.
-Корневая система может быть восстановлена из множества простых корней в результате применения вейлевских отражений.
-
-Группа Вейля конечна для конечномерных алгебр Ли и конечно порождена для аффинных алгебр Ли.
-
-Рассмотрим действие элемента группы Вейля $s_{\alpha}s_{\alpha+\delta}$ аффинной алгебры Ли   $\hat\gf$, соответствующего простому корню  $\alpha$ конечномерной подалгебры Ли $\gf$.
-Из определения  \eqref{eq:117} легко видеть, что $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
-То есть группа Вейля для аффинной алгебры Ли может быть представлена как полупрямое произведение группы Вейля $W_{\gf}$ конечномерной подалгебры  $\gf$ и трансляций, соответствующих корням $\gf$.
-
-Элемент группы Вейля можно представить как произведение простых отражений различными способами.
-Число простых отражений в кратчайшей последовательности, представляющей элемент\; $w\in W_{\gf}$ называется {\it длиной}  $w$ и обозначается $l(w)$.
-Мы также используем обозначение $\epsilon(w)=(-1)^{l(w)}$ для четности числа отражений Вейля, порождающих $w$.
-
-Фундаментальная область $\bar{C}$ для действия группы Вейля $W_{\gf}$ на $\hfg^{*}$ описывается условием $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ для всех простых корней $\alpha_{i}$.
-Ее называют {\it главной камерой Вейля}.
-
-{\it Матрица Картана} $A$ строится из произведений простых корней
-\begin{equation}
-  \label{eq:118}
-  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}.
-\end{equation}
-Она может использоваться для компактного описания алгебры Ли и ее коммутационных соотношений в базисе Шевалле \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
-
-Форма, заданная матрицей Картана \eqref{eq:118} определяет базис, дуальный к базису простых корней.  Он называется  {\it базисом фундаментальных весов}. Мы обозначаем его элементы через $\omega_i$:
-\begin{equation}
-  \label{eq:20}
-  \langle\omega_i,\alpha_j\rangle=\frac{2(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
-\end{equation}
-Для конечномерной алгебры Ли существует $r$ фундаментальных весов $\omega_{i}$, $i=1,\dots, r$.
-Для аффинной алгебры Ли есть дополнительный фундаментальный вес $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
-Другие фундаментальные веса равны $\omega_i=a_i^{\vee} \omega_0 +\co{\omega_i}$, где $\co{\omega_i}$ -- это фундаментальные веса конечномерной подалгебры Ли $\gf$.
-
-Сумма фундаментальных весов $\rho=\sum_{i} \omega_{i}$ называется {\it вектором Вейля} и играет большую роль в теории представлений.
-
-\subsection{Модули старшего веса}
-\label{sec:high-weight-modul}
-
-Мы рассматриваем конечно-порожденные  $\gf$-модули $V$, такие, что $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, где каждое подпространство $V_{\xi}$ конечномерно и существует конечный набор весов $\lambda_{1},\dots \lambda_{s}$, порождающий весовую систему модуля $V$.
-То есть, если $\mathrm{dim}V_{\xi}\neq 0$, то $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$, где $n_{k}\in \mathbb{Z}_{+}$ (См.
-\cite{humphreys2008representations}, \cite{carter2005lie}).
-
-Модули старшего веса содержат единственный старший вес $\mu$ и все остальные веса в них могут быть получены вычитанием линейных комбинаций простых корней $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
-
-Самый простой тип модулей старшего веса -- это модули Верма $M^{\mu}$. Модуль Верма можно определить, как пространство
-\begin{equation}
-  \label{eq:17}
-  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}),
-\end{equation}
-где действие $\gf$ дается умножением в $U(\gf)$, а
-$\underset{U(\bff_{+})}{\otimes}$ значит, что действие элементов $U(\bff_{+})$ ``проносится'' через левую часть тензорного произведения направо.
-Здесь $\bff_{+}$ -- подалгебры Бореля, а $D^{\mu}(\bff_{+})$ -- представление $\bff_{+}$, такое, что $D(E^{\alpha})=0,\; D(H)=\mu(H)$ для любого положительного корня $\alpha$.
-Элементы  $\gf$ действуют слева и мы должны прокоммутировать все элементы $\bff_{+}$ направо, чтобы они могли подействовать на пространстве $D^{\lambda}(\bff_{+})$.
-
-Кратности весов в модуле Верма можно определить из формулы Вейля для характеров
-\begin{equation}
-  \label{eq:122}
-  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
-\end{equation}
-Здесь мы воспользовались тождеством Вейля для знаменателей
-\begin{equation}
-  \label{eq:123}
-  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}.
-\end{equation}
-%% а $\epsilon \left( w\right) :=\det \left( w\right)$ равняется четности последовательности отражений Вейля, образующих $w$.
-
-У модуля Верма  $M^{\mu}$ есть единственный максимальный подмодуль и нетривиальный фактормодуль $L^{\mu}$ является 
-{\it неприводимым модулем старшего веса}.
-
-Неприводимые модули старшего веса не имеют нетривиальных подмодулей. 
-Формула Вейля-Каца для характеров неприводимых модулей старшего веса имеет вид
-\begin{equation}
-  \label{eq:13}
-  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
-\end{equation}
-То есть характер неприводимого модуля старшего веса можно рассматривать как комбинацию характеров модулей Верма.
-Этот факт следует из существования резольвенты Бернштейна-Гельфанда-Гельфанда \cite{bernstein1976category,bernstein1971structure}, см.
-также
-\cite{humphreys2008representations}.
-
-Конструкция обобщенного (или параболического) модуля Верма аналогична формуле (\ref{eq:17}), но представление подалгебры Бореля заменяется на представление параболической подалгебры $\pf_{I}\supset \bff_{+}$, определяющейся некоторым подмножеством  $\{\alpha_{I}\}$ простых корней $I\subset \{1,\dots, r\}$:
-%% !!! \Delta_{p}?!
-\begin{equation*}
-M_{I}^{\mu}=U\left( \gf\right)\otimes _{U\left( \pf_{I}\right) }L_{\pf_{I}}^{\mu}.
-\end{equation*}
-Введем формальный элемент $R_{I}:=\prod_{\alpha \in \Delta
-^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
-^{\mathrm{mult}(\alpha )}$. Тогда характер обобщенного модуля Верма можно записать в виде
-\begin{equation}
-  \label{eq:18}
-  \mathrm{ch}M_{I}^{\mu}=\frac{1}{R_{I}}\mathrm{ch}L_{\pf_{I}}^{\mu }.
-\end{equation}
-
-%% Define external border of irreducible representation here
-
-Формула Вейля для характеров может быть использована для получения рекуррентных соотношений на кратности весов. Эти соотношения важны для вычислений \cite{il2010folded,kulish4sfa}.
-
-Для неприводимых модулей старшего веса рекуррентные соотношения имеют вид
-\begin{equation}
-\label{eq:14}
-m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
--\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
-(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
-\end{equation}
-Формулы для модулей Верма и обобщенных модулей Верма отличаются только во вторым членом в правой части.
-В случае модулей Верма он равен $\delta_{\xi,\mu}$.
-Для обобщенного модуля Верма суммирование во втором члене в правой части равенства \eqref{eq:14} производится по элементам подгруппы Вейля порожденной отражениями, соответствующими корням $\{\alpha_{I}\}$.
-
-В разделе \ref{subsec:Construct-recurrent-rel} мы покажем, что для модулей старшего веса эти соотношения могут быть получены как частный случай рекуррентных соотношений на коэффициенты ветвления.
-
-Другая рекуррентная формула для кратностей может быть получена из рассмотрения действия элементов Казимира на неприводимых модулях старшего веса \cite{humphreys1997introduction}:
-\begin{equation}
-  \label{eq:15}
-  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
-\end{equation}
-Эта формула называется формулой Фрейденталя. Заметим, что она применима только для неприводимых модулей
-
-Применение рекуррентных соотношений \eqref{eq:14} и \eqref{eq:15} для вычисления кратностей весов обсуждается в разделе \ref{sec:comp-algor}.
 

### 2012-05-17 AffineLieAlgebras/Thesis/review.tex
Started second SLE paper. Some changes in thesis
Some changes in thesis structure

@@
 
-\chapter{Конформная теория поля}
+\chapter{Конформная теория поля и аффинные алгебры Ли}
 \label{cha:CFT}
@@
 
+\section{Простые алгебры Ли, алгебра петель, центральные расширения и аффинные алгебры Ли}
+
+\label{sec:intro-simple-lie-algebras}
+\begin{definition}
+{\it Алгебра Ли $\gf$} -- это векторное пространство с билинейной операцией $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, которая называется  {\it скобкой Ли или коммутатором}.
+Если выбрать некоторый базис  $X_{i}$ в $\gf$, то коммутационные соотношения можно задать при помощи  {\it структурных констант} $C_{ijk}$:
+\begin{equation}
+  \label{eq:1}
+  [X^{i},X^{j}]=\sum_{k} C^{ij}_{k} X^{k}
+\end{equation}
+
+\end{definition}
+
+Алгебра Ли называется {\it простой} если она не содержит нетривиальных идеалов относительно коммутатора. {\it Полупростая} алгебра Ли -- это прямая сумма простых алгебр Ли.
+
+{\it Подалгеброй Картана}  $\hfg$ называется нильпотентная подалгебра алгебры $\gf$, совпадающая со своим нормализатором. Мы обозначаем элементы базиса в $\hfg$ через $H^{i}$.
+
+Форма Киллинга на  $\gf$ порождает невырожденную билинейную форму $(\cdot,\cdot)$ на подалгебре Картана $\hfg$, позволяющую идентифицировать $\hfg$ с подпространством дуального пространства  $\hfg^{*}$ линейных функционалов на $\hfg$.
+{\it Веса}  -- это элементы  $\hfg^{*}$, мы обозначаем их греческими буквами $\mu,\nu, \omega, \lambda\dots$
+
+Коммутационные соотношения  (\ref{eq:1}) можно записать в компактной форме, если выбрать базис специальным образом.
+Такой базис описывается корневой системой, которая определяется в разделе \ref{sec:weights-roots} (Смотри также \cite{humphreys1997introduction,humphreys1992reflection}).
+
+Чтобы определить аффинные алгебры нам нужно обсудить процедуру центрального расширения алгебры Ли.
+Напомним несколько определений (см \cite{fuks1986cohomology},\cite{fuks1984}, \cite{feigin1988}).
+\begin{definition}
+\label{def:1}
+Будем рассматривать алгебру Ли $\gf$ над полем $k=\mathbb{C},\mathbb{R}$.
+Векторное пространство $A$ над полем $k$ называется {\it модулем над $\gf$} или {\it $\gf$-модулем}, если задано билинейное отображение $\mu:\gf\times A\to A$, такое что $\mu([X,Y],a)=\mu(X,\mu(Y,a))-\mu(Y,\mu(X,a))$ для $X,Y\in \gf, a\in A$.
+Далее мы будем опускать символ $\mu$ и писать $X a= \mu(X,a)$.
+\end{definition}
+\begin{definition}
+  {\it $n$-мерная коцепь с коэффициентами в $A$} -- это кососимметричный $n$-линейный функционал на $\gf$ со значениями в $A$. Пространство $n$-коцепей $C^{n}(\gf;A)=\mathrm{Hom}(\wedge^{n}\gf;A)$.
+\end{definition}
+Заметим, что элементы $\gf$ действуют на $C^{n}(\gf;A)$.
+\begin{definition}
+  Внешний дифференциал $d=d_{n}:C^{n}(\gf;A)\to C^{n+1}(\gf;A)$ определяется формулой
+  \begin{multline}
+    \label{eq:68}
+    (dc) (X_{1},\dots, X_{n+1})=\sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} c([X_{s},X_{t}],X_{1},\dots,\hat X_{s},\dots,\hat X_{t},\dots X_{n+1})\\
+    +\sum_{1\leq s\leq n+1} (-1)^{s}X_{s} c(X_{1},\dots \hat X_{s},\dots X_{n+1})
+  \end{multline}
+\end{definition}
+Нетрудно проверить, что последовательность
+\begin{equation}
+  \label{eq:40}
+  \dots\stackrel{d_{n}}{\longleftarrow} C^{n}(g;A)\stackrel{d_{n-1}}{\longleftarrow} C^{n-1}(\gf;A)\leftarrow \dots \leftarrow C^{1}(\gf;A) \stackrel{d_{0}}{\longleftarrow} C^{0}(\gf;A)\leftarrow 0
+\end{equation}
+точна.Тогда $\{C^{n}(\gf;A),d_{n}\}=C^{*}(\gf;A)$ есть комплекс.
+\begin{definition}
+Соответствующие когомологии называются {\it когомологиями алгебры $\gf$ с коэффициентами в $A$} и обозначаются через $H^{n}(\gf;A)=\mathrm{Ker}\; d_{n}/\mathrm{Im}\; d_{n-1}$.
+
+\end{definition}
+Заметим, что поле $k$ может рассматриваться как тривиальный $\gf$-модуль. В этом случае второй член в формуле \eqref{eq:1} исчезает и используют сокращенные обозначения $C^{n}(\gf), H^{n}(\gf)$.
+\begin{definition}
+  Определим, заодно, и гомологии. Пространство $n$-мерных цепей $C_{n}(\gf;A)=A\otimes \wedge^{n}\gf$, дифференциал $\partial=\partial_{n}:C_{n}(\gf;A)\to C_{n-1}(\gf;A)$ определяется формулой
+  \begin{multline}
+    \label{eq:98}
+    \partial(a\otimes (X_{1}\wedge \dots \wedge X_{n})) =\\ \sum_{1\leq s<t\leq n+1} (-1)^{s+t-1} a\otimes ([X_{s},X_{t}]\wedge X_{1} \wedge\dots\wedge\hat X_{s}\wedge \dots\wedge \hat X_{t}\wedge \dots\wedge X_{n+1})\\
+    +\sum_{1\leq s\leq n+1} (-1)^{s}(X_{s} a)\otimes (X_{1}\wedge\dots\wedge \hat X_{s}\wedge\dots\wedge X_{n+1})
+  \end{multline}
+  Аналогично определяется точная последовательность, комплекс и группа гомологий $H_{n}(\gf;A)$.
+\end{definition}
+\begin{definition}
+  {\it Одномерным центральным расширением алгебры $\gf$ } называется точная последовательность
+  \begin{equation}
+    \label{eq:62}
+    0\to k \to \tilde \gf\to \gf\to 0,
+  \end{equation}
+  такая что образ $k\to \tilde\gf$ содержится в центре $\tilde\gf$.
+\end{definition}
+Заметим, что всякий 2-коцикл $c\in C^{2}(\gf;A), \; dc=0$ определяет центральное расширение $\gf$:
+\begin{equation}
+  \label{eq:64}
+  0\to k\stackrel{\lambda\to (0,\lambda)}{\longrightarrow}\tilde\gf=\gf\oplus k \stackrel{(X,\lambda)\to X}{\longrightarrow} \gf\to 0
+\end{equation}
+Скобка Ли в алгебре $\tilde\gf$, которая равна $\gf\oplus k$ как векторное пространство, определяется равенством
+\begin{equation}
+  \label{eq:103}
+  [(X,\lambda),(Y,\mu)]=([X,Y],c(X,Y))
+\end{equation}
+Тождество Якоби для такой скобки равносильно тому, что $c$\; --- 2-коцикл. Когомологичным коциклам отвечают эквивалентные расширения.
+
+Два расширения $\tilde \gf$ и $\tilde{\tilde\gf}$ называются эквивалентными, если существует изоморфизм $I:\tilde\gf\to \tilde{\tilde \gf}$ такой, что диаграмма коммутирует:
+\begin{equation}
+  \label{eq:104}
+  \begin{diagram}
+    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \arrow{s,l}{id} \node{\tilde\gf}\arrow{s,l}{I} \arrow{e,t}{} \node{k}\arrow{s,r}{id} \arrow{e,t}{} \node{0}\\
+    \node 0 \arrow{e,t}{}  \node{\gf} \arrow{e,t}{} \node{\tilde{\tilde\gf}} \arrow{e,t}{} \node{k} \arrow{e,t}{} \node{0}
+  \end{diagram}
+\end{equation}
+%% \begin{exercise}
+%%  Построить изоморфизм $I$.   
+%% \end{exercise}
+
+Таким образом пространство $H^{2}(\gf)$ -- это множество классов 1-мерных центральных расширений $\gf$. Нуль в $H^{2}(\gf)$  соответствует тривиальному расширению.
+
+Для алгебры Витта \eqref{eq:2} существует коцикл
+\begin{equation}
+  \label{eq:105}
+  c(l_{n},l_{m})=\frac{1}{12}(m^{3}-m)\delta_{-n,m}
+\end{equation}
+%% \begin{exercise}
+%%   Проверить, что $c$ -- коцикл алгебры Витта. 
+%% \end{exercise}
+Соответствующее центральное расширение алгебры Витта называется алгеброй Вирасоро. Коммутационные соотношения этой алгебры имеют вид
+\begin{eqnarray}
+  \label{eq:106}
+  [L_{n},c]=0\\
+  \left[L_{n},L_{m}\right]=(n-m)L_{n+m} +\frac{c}{12} (m^{3}-m) \delta_{-n,m}
+\end{eqnarray}
+Можно показать, что $H^{2}(Witt)\cong \mathbb{C}$ и все нетривиальные коциклы пропорциональны $c$. 
+(Доказательство есть в \cite{fuks1986cohomology}, \cite{schottenloher2008mathematical}).
+
+{\it Алгебра петель} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, соответствующая полупростой алгебре Ли $\gf$, определяется коммутационными соотношениями
+\begin{equation}
+  \label{eq:108}
+  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
+\end{equation}
+Центральное расширение алгебры петель ведет к возникновению дополнительного члена
+\begin{equation}
+  \label{eq:112}
+   [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
+\end{equation}
+Эта алгебра $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ называется (не скрученной)  {\it аффинной алгеброй Ли} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
+
+\subsection{Модули, веса и корни}
+\label{sec:weights-roots}
+
+Пусть $\gf$ -- конечномерная или аффинная алгебра Ли. Мы ввели модули алгебры $\gf$ в определении \ref{def:1}. Широко используется альтернативный термин {\it представление}.
+
+%%    $\gf$-модулем называется векторное пространство $V$ с билинейным отображением $\gf \times V\to V$, таким, что выполнено равенство
+%%  \begin{equation}
+%%    \label{eq:130}
+%%    [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
+%%  \end{equation}
+\begin{definition}
+Представление алгебры  $\gf$ на векторном пространстве $V$ называется гомоморфизм $\gf\to gl(V)$ из $\gf$ в алгебру Ли эндоморфизмов векторного пространства $V$, где скобка задана коммутатором:
+\begin{equation}
+  \label{eq:113}
+  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{для}\; x,y\in \gf, v\in V  
+\end{equation}
+
+\end{definition}
+
+В произвольном представлении операторы, соответствующие генераторам подалгебры Картана $H^{i}$ можно одновременно диагонализовать путем специального выбора базиса
+ $\{v_{j}\}$ в $V$:
+\begin{equation}
+  \label{eq:114}
+  H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
+\end{equation}
+Собственные значения $\nu^{i}_{j}$ генераторов Картана на элементе базиса $v_{j}$ определяют вес  $\nu_{j}\in \hfg^{*}$, такой, что $\nu_{j}(H^{i})=\nu_{j}^{i}$.
+Вектор $v\in V$ называется весовым вектором веса  $\lambda$, если $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
+Весовое подпространство состоит из всех весовых векторов $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
+Кратностью веса  $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ называется размерность весового подпространства.
+
+Структура модуля определяется набором весов, так как действие генераторов $E^{\alpha}$ на весовых векторах дается выражением
+\begin{equation}
+  \label{eq:115}
+  E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
+\end{equation}
+Структуру модуля можно записать в виде формального характера
+\begin{equation}
+  \label{eq:116}
+  \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
+\end{equation}
+Характер  $\mathrm{ch}V\in \mathcal{E}$ -- это элемент алгебры  $\mathcal{E}$, порожденной формальными экспонентами весов.
+Характер можно специализировать --- взять его значение на некотором элементе $\xi\in\hf$.
+
+Алгебра Ли является собственным модулем по отношению к специальному представлению, называющемуся присоединенном. Действие генераторов в этом представлении дается скобкой $ad_{X} Y=[X,Y]$. 
+{\it Корни} -- это веса присоединенного представления алгебры $\gf$.
+Они определяют коммутационные соотношения в алгебре следующим образом.
+Обозначим через $\Delta$ множество корней.
+Для каждого $\alpha\in \Delta$ существует корень  $-\alpha\in \Delta$ и генераторы $E^{\alpha}, E^{-\alpha}$, такие, что
+\begin{align}
+  \label{eq:63}
+  &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
+  &\left[E^{\alpha},E^{\beta}\right]=
+  \begin{cases}
+    N_{\alpha,\beta} E^{\alpha+\beta}, & \mbox{if}\; \alpha+\beta\in \Delta\\
+    \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
+    0,&\mbox{в остальных случаях}
+  \end{cases}
+\end{align}
+
+В корневой системе $\Delta$ можно выбрать множество положительных корней.
+Это подмножество  $\Delta^{+}\subset \Delta$, такое, что для любого корня $\alpha\in\Delta$ ровно один из корней $\alpha, -\alpha$ содержится $\Delta^{+}$ и для любых двух различных положительных корней $\alpha, \beta\in \Delta^{+}$, таких, что $\alpha+\beta\in \Delta$ их сумма тоже положительна $\alpha+\beta\in\Delta^{+}$.
+Элементы множества $-\Delta^{+}$ называются отрицательными корнями.
+
+Положительный корень называется {\it простым} если его нельзя представить в виде суммы положительных корней.
+Множество простых корней  $\Phi=\left\{\alpha_{i}\right\}$ является базисом в $\hfg^{*}$ и каждый корень может быть записан как сумма $\alpha=\sum_{i}n_{i}\alpha_{i}$, где все $n_{i}$ не отрицательны или не положительны одновременно.
+В случае конечномерной алгебры Ли  $\gf$ простые корни можно пронумеровать числами от  1 до ранга алгебры $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
+Такая нумерация порождает лексикографическое упорядочение корневой системы.
+Старший по отношению к этому упорядочению корень обозначается через $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, его координаты в базисе простых корней $a_i$ называются  {\it марками}.
+$\theta$ -- это старший вес присоединенного модуля (См.
+раздел \ref{sec:high-weight-modul}).
+{\it Ко-марками} называются числа, равные $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
+
+В аффинной алгебре Ли  $\hat\gf$ множество корней  $\Delta$ бесконечно, но набор простых корней  $\Phi$ конечен.
+Обозначим его элементы через $\alpha_{0},\dots \alpha_{r}$, где $r=\mathrm{rank}(\gf)$.
+Корни $\alpha_1,\dots, \alpha_r$ -- это корни соответствующей конечномерной алгебры Ли $\go$.
+Простой корень  $\alpha_0=\delta-\theta$ -- это разность  {\it мнимого корня} $\delta$ и $\theta$ -- старшего корня алгебры $\go$.
+Заметим, что кратность корня  $\mathrm{mult}(\alpha)$ в случае аффинной алгебры Ли может быть больше единицы.
+
+Подалгебра  $\bff_{+}\subset \gf$, порожденная генераторами $H^{i}, E^{\alpha}$, соответствующими положительным корням $\alpha\in \Delta^{+}$, называется подалгеброй Бореля.
+
+{\it Параболическая подалгебра}  $\pf_{I}\supset \bff_{+}$ содержит подалгебру Бореля и порождена некоторым подмножеством простых корней  $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
+Она образована подмножеством генераторов  $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
+{\it Регулярная подалгебра} $\af\subset\gf$ определяется корневой системой  $\Delta_{\af}$, множество простых корней которой  $\{\beta_{i}, i=1,\dots,r_{\af}\}$ является подмножеством множества $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ корней алгебры $\gf$.
+
+ {\it Группа Вейля} $W_{\gf}$ порождается отражениями $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$, соответствующим простым корням $\{\alpha_{i}\}$:
+\begin{equation}
+  \label{eq:117}
+  s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
+\end{equation}
+Корневая система и характеры представлений инвариантны относительно действия группы Вейля.
+Корневая система может быть восстановлена из множества простых корней в результате применения вейлевских отражений.
+
+Группа Вейля конечна для конечномерных алгебр Ли и конечно порождена для аффинных алгебр Ли.
+
+Рассмотрим действие элемента группы Вейля $s_{\alpha}s_{\alpha+\delta}$ аффинной алгебры Ли   $\hat\gf$, соответствующего простому корню  $\alpha$ конечномерной подалгебры Ли $\gf$.
+Из определения  \eqref{eq:117} легко видеть, что $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
+То есть группа Вейля для аффинной алгебры Ли может быть представлена как полупрямое произведение группы Вейля $W_{\gf}$ конечномерной подалгебры  $\gf$ и трансляций, соответствующих корням $\gf$.
+
+Элемент группы Вейля можно представить как произведение простых отражений различными способами.
+Число простых отражений в кратчайшей последовательности, представляющей элемент\; $w\in W_{\gf}$ называется {\it длиной}  $w$ и обозначается $l(w)$.
+Мы также используем обозначение $\epsilon(w)=(-1)^{l(w)}$ для четности числа отражений Вейля, порождающих $w$.
+
+Фундаментальная область $\bar{C}$ для действия группы Вейля $W_{\gf}$ на $\hfg^{*}$ описывается условием $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ для всех простых корней $\alpha_{i}$.
+Ее называют {\it главной камерой Вейля}.
+
+{\it Матрица Картана} $A$ строится из произведений простых корней
+\begin{equation}
+  \label{eq:118}
+  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}.
+\end{equation}
+Она может использоваться для компактного описания алгебры Ли и ее коммутационных соотношений в базисе Шевалле \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
+
+Форма, заданная матрицей Картана \eqref{eq:118} определяет базис, дуальный к базису простых корней.  Он называется  {\it базисом фундаментальных весов}. Мы обозначаем его элементы через $\omega_i$:
+\begin{equation}
+  \label{eq:20}
+  \langle\omega_i,\alpha_j\rangle=\frac{2(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
+\end{equation}
+Для конечномерной алгебры Ли существует $r$ фундаментальных весов $\omega_{i}$, $i=1,\dots, r$.
+Для аффинной алгебры Ли есть дополнительный фундаментальный вес $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
+Другие фундаментальные веса равны $\omega_i=a_i^{\vee} \omega_0 +\co{\omega_i}$, где $\co{\omega_i}$ -- это фундаментальные веса конечномерной подалгебры Ли $\gf$.
+
+Сумма фундаментальных весов $\rho=\sum_{i} \omega_{i}$ называется {\it вектором Вейля} и играет большую роль в теории представлений.
+
+\subsection{Модули старшего веса}
+\label{sec:high-weight-modul}
+
+Мы рассматриваем конечно-порожденные  $\gf$-модули $V$, такие, что $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, где каждое подпространство $V_{\xi}$ конечномерно и существует конечный набор весов $\lambda_{1},\dots \lambda_{s}$, порождающий весовую систему модуля $V$.
+То есть, если $\mathrm{dim}V_{\xi}\neq 0$, то $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$, где $n_{k}\in \mathbb{Z}_{+}$ (См.
+\cite{humphreys2008representations}, \cite{carter2005lie}).
+
+Модули старшего веса содержат единственный старший вес $\mu$ и все остальные веса в них могут быть получены вычитанием линейных комбинаций простых корней $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
+
+Самый простой тип модулей старшего веса -- это модули Верма $M^{\mu}$. Модуль Верма можно определить, как пространство
+\begin{equation}
+  \label{eq:17}
+  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}),
+\end{equation}
+где действие $\gf$ дается умножением в $U(\gf)$, а
+$\underset{U(\bff_{+})}{\otimes}$ значит, что действие элементов $U(\bff_{+})$ ``проносится'' через левую часть тензорного произведения направо.
+Здесь $\bff_{+}$ -- подалгебры Бореля, а $D^{\mu}(\bff_{+})$ -- представление $\bff_{+}$, такое, что $D(E^{\alpha})=0,\; D(H)=\mu(H)$ для любого положительного корня $\alpha$.
+Элементы  $\gf$ действуют слева и мы должны прокоммутировать все элементы $\bff_{+}$ направо, чтобы они могли подействовать на пространстве $D^{\lambda}(\bff_{+})$.
+
+Кратности весов в модуле Верма можно определить из формулы Вейля для характеров
+\begin{equation}
+  \label{eq:122}
+  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
+\end{equation}
+Здесь мы воспользовались тождеством Вейля для знаменателей
+\begin{equation}
+  \label{eq:123}
+  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}.
+\end{equation}
+%% а $\epsilon \left( w\right) :=\det \left( w\right)$ равняется четности последовательности отражений Вейля, образующих $w$.
+
+У модуля Верма  $M^{\mu}$ есть единственный максимальный подмодуль и нетривиальный фактормодуль $L^{\mu}$ является 
+{\it неприводимым модулем старшего веса}.
+
+Неприводимые модули старшего веса не имеют нетривиальных подмодулей. 
+Формула Вейля-Каца для характеров неприводимых модулей старшего веса имеет вид
+\begin{equation}
+  \label{eq:13}
+  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
+\end{equation}
+То есть характер неприводимого модуля старшего веса можно рассматривать как комбинацию характеров модулей Верма.
+Этот факт следует из существования резольвенты Бернштейна-Гельфанда-Гельфанда \cite{bernstein1976category,bernstein1971structure}, см.
+также
+\cite{humphreys2008representations}.
+
+Конструкция обобщенного (или параболического) модуля Верма аналогична формуле (\ref{eq:17}), но представление подалгебры Бореля заменяется на представление параболической подалгебры $\pf_{I}\supset \bff_{+}$, определяющейся некоторым подмножеством  $\{\alpha_{I}\}$ простых корней $I\subset \{1,\dots, r\}$:
+%% !!! \Delta_{p}?!
+\begin{equation*}
+M_{I}^{\mu}=U\left( \gf\right)\otimes _{U\left( \pf_{I}\right) }L_{\pf_{I}}^{\mu}.
+\end{equation*}
+Введем формальный элемент $R_{I}:=\prod_{\alpha \in \Delta
+^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
+^{\mathrm{mult}(\alpha )}$. Тогда характер обобщенного модуля Верма можно записать в виде
+\begin{equation}
+  \label{eq:18}
+  \mathrm{ch}M_{I}^{\mu}=\frac{1}{R_{I}}\mathrm{ch}L_{\pf_{I}}^{\mu }.
+\end{equation}
+
+%% Define external border of irreducible representation here
+
+Формула Вейля для характеров может быть использована для получения рекуррентных соотношений на кратности весов. Эти соотношения важны для вычислений \cite{il2010folded,kulish4sfa}.
+
+Для неприводимых модулей старшего веса рекуррентные соотношения имеют вид
+\begin{equation}
+\label{eq:14}
+m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
+-\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
+(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.
+\end{equation}
+Формулы для модулей Верма и обобщенных модулей Верма отличаются только во вторым членом в правой части.
+В случае модулей Верма он равен $\delta_{\xi,\mu}$.
+Для обобщенного модуля Верма суммирование во втором члене в правой части равенства \eqref{eq:14} производится по элементам подгруппы Вейля порожденной отражениями, соответствующими корням $\{\alpha_{I}\}$.
+
+В разделе \ref{subsec:Construct-recurrent-rel} мы покажем, что для модулей старшего веса эти соотношения могут быть получены как частный случай рекуррентных соотношений на коэффициенты ветвления.
+
+Другая рекуррентная формула для кратностей может быть получена из рассмотрения действия элементов Казимира на неприводимых модулях старшего веса \cite{humphreys1997introduction}:
+\begin{equation}
+  \label{eq:15}
+  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
+\end{equation}
+Эта формула называется формулой Фрейденталя. Заметим, что она применима только для неприводимых модулей
+
+Применение рекуррентных соотношений \eqref{eq:14} и \eqref{eq:15} для вычисления кратностей весов обсуждается в разделе \ref{sec:comp-algor}.
+
 %%

### 2012-05-17 AffineLieAlgebras/Thesis/common.tex
Some changes in thesis structure

@@
 \begin{itemize}
-\item Получены новые рекуррентные соотношения на коэффициенты ветвления представлений аффинных алгебр Ли на представления произвольных редуктивных подалгебр
+\item Продемонстрирована роль сингулярных элементов в описании структуры модулей аффинных алгебр Ли 
+\item Из разложения сингулярных элементов получены новые рекуррентные соотношения на коэффициенты ветвления представлений аффинных алгебр Ли на представления произвольных редуктивных подалгебр
 \item Показана связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда
-\item Показано, что наличие сплинта приводит к существенному упрощению при вычислении коэффициентов ветвления и ведет к новым соотношениям на функции ветвления
-\item Продемонстрирована роль алгебраических методов теории представлений аффинных алгебр Ли в изучении критического поведения в двумерных решеточных моделях
+\item Выявлена связь расщепления корневой системы алгебры с разложением сингулярных элементов модулей алгебры в комбинацию сингулярных элементов модулей подалгебр
+\item Показано, что наличие расщепления приводит к существенному упрощению при вычислении коэффициентов ветвления и ведет к новым соотношениям на функции ветвления
+\item Предложено обобщение стохастического процесса Шрамма-Лёвнера на случай систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля
+\item Продемонстрирована роль сингулярных элементов в построении мартингалов стохастического процесса Шрамма-Лёвнера, то есть проиллюстрировано применение алгебраических методов теории представлений аффинных алгебр Ли в изучении критического поведения в двумерных решеточных моделях
 \item Реализованы различные алгоритмы для вычислений в теории представлений конечномерных и аффинных алгебр Ли
@@
 \mkcommonsect{pub}{Публикации.}{%
-Материалы диссертации опубликованы в $8$ печатных работах, из них $3$ статьи в
-рецензируемых журналах~\citemy{2010arXiv1007.0318L,2011arXiv1102.1702L,2011arXiv1111.6787L}, $4$ статьи в
-сборниках тезисов и трудов конференций \cite{2011arXiv1112.4354N,2010LyakhovskyNazarovMQFT,Nazarov2008,NazarovACSM2009}, и в препринте \cite{2011arXiv1107.4681N}.
+Материалы диссертации опубликованы в $10$ печатных работах, из них $4$ статьи в
+рецензируемых журналах~\citemy{2010arXiv1007.0318L,2011arXiv1102.1702L,2011arXiv1111.6787L,NazarovJETPletters}, $5$ статей в
+сборниках тезисов и трудов конференций \cite{2011arXiv1112.4354N,2010LyakhovskyNazarovMQFT,Nazarov2008,NazarovACSM2009,2012arXiv1204.1855L}, и в препринте \cite{2011arXiv1107.4681N}.
 }

### 2012-05-17 AffineLieAlgebras/Thesis/intro.tex
Some changes in thesis structure

@@
 
-Аффинные алгебры Ли были открыты Виктором Кацем \cite{kac1968simple} и Робертом Муди \cite{moody1968new} в 1967 году в результате отказа от требования положительной определенности матрицы Картана.
-Это требование определяет полупростые конечномерные алгебры Ли.
+Аффинные алгебры Ли были открыты Виктором Кацем \cite{kac1968simple} и Робертом Муди \cite{moody1968new} в 1967 году в результате отказа от требования положительной определенности матрицы Картана, определяющего полупростые конечномерные алгебры Ли.
 Аффинные алгебры Ли отличаются тем, что матрица Картана, задающая коммутационные соотношения, лишь положительно полуопределена.
-Оказывается такие алгебры могут быть реализованы как центральные расширения алгебр петель, связанных с полупростыми алгебрами Ли.
-Эта особенность структуры аффинных алгебр Ли привела к тому, что они приобрели особое значение в физике после появления в 1984 году конформной теории поля \cite{belavin1984ics}.
-Ведь квантование теорий поля естественным образом приводит к центральным расширениям алгебр симметрии.
+Такие алгебры могут быть реализованы как центральные расширения алгебр петель, связанных с полупростыми алгебрами Ли.
+После появления в 1984 году конформной теории поля \cite{belavin1984ics}, аффинные алгебры Ли приобрели большое значение в физике, так как квантование теорий поля естественным образом приводит к центральным расширениям алгебр симметрии.
 Теория представлений аффинных алегбр Ли играет определяющую роль при изучении важных классов моделей конформной теории поля -- моделей Весса-Зумино-Новикова-Виттена и coset-моделей.

### 2012-05-22 AffineLieAlgebras/Thesis/4.tex
Some work on thesis

@@
 
+\subsection{Интегрируемые возмущения конформной теории поля и массивная эволюция Шрамма-Лёвнера}
+\label{sec:massive-sle}
+
+\section{TODO}
+
+\abstract{
+  Scharmm-Loewner evolution (SLE) and conformal field theory (CFT) are popular and widely used instruments to study critical behavior of two-dimensional models, but they use different objects.
+While SLE  has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory.
+  To provide a way for the concurrent use of SLE and CFT we consider CFT correlation functions which are martingales with respect to SLE.
+We establish connection between parameters of Schramm-Loewner evolution on coset space and algebraic data of coset conformal field theory.
+Then we check the consistency of our approach with the  behaviour of parafermionic and minimal models.
+Coset models are connected with off-critical massive field theories and we discuss implications for SLE.}
+
+%%% PACS numbers
+%\PACS{05.50.+q, 11.25.Hf, 02.20.Sv}
+
+%\begin{document}
+%\maketitle
+
+\subsection{Introduction}
+\label{sec:introduction}
+
+Schramm-Loewner evolution \cite{schramm2000scaling} is a stochastic process satisfying stochastic differential equation (\ref{eq:19}).
+A solution of  equation (\ref{eq:19}) can be seen as  probability measure on random curves (called SLE traces).
+SLE is useful for the study of critical behavior \cite{Cardy:2005kh,rohde2005basic}, since for many lattice models the convergence of  domain walls to SLE traces can be proved \cite{bauer20062d,schramm2006conformally}.
+Practical computations with SLE rely on Ito calculus while proofs use discrete complex analysis \cite{duminil2011conformal}.
+
+Conformal field theory \cite{belavin1984ics} is formulated in terms of families of quantum fields which usually has no direct microscopic interpretation.
+On the other hand CFT has efficient computational tools such as Virasoro symmetry, Knizhnik-Zamolodchikov equations, fusion algebra etc and provides numerous predictions, such as celebrated Cardy formula \cite{cardy1992critical,smirnov2001critical} which gives crossing probability for critical percolation.
+
+Combination of these two approaches is immensely powerful, so it is important to find objects which can be studied from both points of view.
+
+We present a new class of such observables in coset conformal field theory  -- correlation functions which are martingales with respect to Schramm-Loewner evolution with additional Brownian motion on factor-space of Lie group $G$ by subgroup $A$ \cite{2011arXiv1112.4354N}.
+We derive relations connecting SLE and CFT parameters.
+We then check the consistency of these results with the earlier results  for parafermionic observables \cite{santachiara2008sle}.
+
+All minimal unitary models can be obtained by coset construction.
+Coset structure leads to specific off-critical behavior.
+Massive excitations of coset CFTs are given by affine Toda field theories \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
+Recent experimental study confirming this result attracted a lot of attention \cite{coldea2010quantum}.
+In conclusion we discuss possible connections of massive CFT perturbations with  off-critical SLEs (containing additional drift term  \cite{makarov2010off}).
+
+\subsection{Martingale conditions}
+\label{sec:mart-cond}
+
+ Consider some critical lattice model on the upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$ (domain wall up to some length $t$).
+We denote this slit domain by $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$.
+Assume that $\gamma_{t}$ satisfies restriction property and is conformally  invariant \cite{Cardy:2005kh}.
+Then  conformal map  $g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ satisfies stochastic differential equation \cite{schramm2000scaling}:
+\begin{equation}
+\label{eq:19}
+  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
+\end{equation}
+where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
+
+For us it is convenient to use the map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
+\begin{equation}
+  \label{eq:20}
+       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}  
+\end{equation}
+
+Consider  $N$-point correlation function of boundary conformal field theory with boundary condition changing operators sitting at the tip of SLE trace and at the infinity:
+\begin{equation}
+  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\}_{i=1}^{N})_{\mathbb{H}_{t}}=
+\left<\varphi(z_{t}) \phi_{1}(z_{1},\bar z_{1}) \dots \phi_{n}(z_{n},\bar z_{n})
+      \varphi(\infty)\right>,
+    \label{eq:2}
+\end{equation}
+where $\phi_{i}$ are bulk primary fields with conformal weights $h_i$ and $\varphi(z_{t})$ is boundary condition changing operator.
+
+Let $\gf$ be a (semisimple) Lie algebra of a Lie group $G$ and $\af$ -- Lie algebra of a subgroup $A\subset G$. Denote by $x_{e}$ embedding index for $\af\to\gf$.
+
+Primary fields in coset models are labeled by pairs $(\lambda,\eta)$ of weights for $\gf$- and $\af$-representations.
+For each $\lambda$ the set of possible weights $\eta$ includes those which appear in the decomposition  $L^{(\mu)}_{\gf}=\bigoplus_{\eta} H^{\lambda}_{\eta}\otimes L^{(\eta)}_{\af}$.
+(Some pairs are equivalent, see \cite{fuchs1996resolution,schellekens1990field}).
+We assume that boundary field $\varphi$ is also primary and is labeled by weights $(\mu,\nu)$.
+
+  We use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite expression \eqref{eq:2} in the whole upper half plane:
+\begin{multline}
+  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\})_{\mathbb{H}_{t}}=\\
+  =\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{i}} 
+  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{\bar h_i}
+  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
+  \label{eq:1}
+\end{multline}
+We can extend the definition of $\mathcal{F}$ to the whole plane by doubling the number of fields $\phi_{i}$ \cite{cardy2004boundary,cardy1984conformal} and by considering $w_{i},\bar w_{i}$ as independent variables.
+To simplify notations we will write $\mathcal{F}(\left\{w_{i}\right\}_{i=1}^{2N})$.
+
+$G/A$-coset conformal field theory can be realized as a WZNW-model (with gauge group $G$) interacting with pure gauge fields of gauge group $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
+The action is written in terms of fields $\gamma:\mathbb{C}\to G$ and $\alpha,\bar\alpha:\mathbb{C}\to A$:
+\begin{multline}
+  \label{eq:24}
+      S_{G/A}(\gamma, \alpha)=-\frac{k}{8\pi}\int_{S^2} d^2x\; {\cal K} (\gamma^{-1}\partial^{\mu}\gamma,\gamma^{-1}\partial_{\mu}\gamma)-\\
+ - \frac{k }{24\pi} \int_{B}\epsilon_{ijk} {\cal K}\left(
+    \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^i},
+      \left[\tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^j}
+      \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^k}\right]\right) d^3y+\\
++
+      \frac{k}{4\pi}\int_{S^2} d^{2}z \left(\mathcal{K}(\alpha, \gamma^{-1}\bar \partial \gamma)-\mathcal{K}(\bar \alpha, (\partial \gamma ) \gamma^{-1})\right.\\
+      \left.+\mathcal{K}(\alpha,\gamma^{-1}\bar \alpha \gamma)-\mathcal{K}(\alpha,\bar \alpha)\right).
+\end{multline}
+Here we denote by $\mathcal{K}$ the Killing form of a Lie algebra $\gf$ corresponding to a Lie group $G$.
+
+ If we fix $A$-gauge we have $G/A$ gauge symmetry.
+Then we add random gauge transformations to Schramm-Loewner evolution \cite{2011arXiv1112.4354N} similar to the case of WZNW-models \cite{bettelheim2005stochastic}.
+Denote by $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) the  generators of $\gf$-representation ($\af$-representation) corresponding to the primary field $\phi_{i}$.
+
+Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in the right-hand-side of equation (\ref{eq:1}) gives us
+\begin{equation*}
+  -\frac{2h_{i}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}.
+\end{equation*}
+We denote by $\mathcal{G}_{i}$ the generator of infinitesimal transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$.
+We normalize additional $\left(\dim\gf\right)$-dimensional Brownian motion as $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
+The generator of field transformation is equal to
+\begin{equation}
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right).
+\label{eq:3}
+\end{equation}
+So we have fixed $A$-gauge by allowing random walk only in direction orthogonal to subalgebra $\af$.
+
+ Ito formula  gives us an expression for the differential of $\mathcal{F}$ which should be zero due to martingale condition:
+\begin{multline}
+d \mathcal{F}_{\mathbb{H}_{t}}=\\ \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)
+\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
+      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}\\=0
+\label{eq:8}
+\end{multline}
+Substituting  definition \eqref{eq:3} we get 
+\begin{equation}
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
+      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0,
+  \label{eq:4}
+\end{equation}
+with
+\begin{eqnarray*}
+  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right),\\ \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}};\; \tilde{\mathcal{J}}^{b}_{{-n}}=-\sum_{i}\frac{\tilde{t}^{b}_{i}}{(w_{i}-z)^{n}}.
+\end{eqnarray*}
+This equation is equivalent to the following algebraic condition on the boundary state $\varphi(0)\left|0\right>$:
+\begin{multline}
+  \label{eq:7}
+  \left<0\left|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})\right.\right.\\
+  \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
+\left.\varphi(0)|0\right>=0.
+\end{multline}
+Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that 
+\begin{multline}
+|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
+\cdot\varphi(0)|0>
+\end{multline}
+is a null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in a coset theory commutation relations of full chiral algebra are
+\begin{equation}
+  \label{eq:18}
+\begin{array}{ll}
+  L_{n}= L_{n}^{\gf}-L_{n}^{\af}, &\\
+  \left[L_{n}^{\gf},J^{a}_{m}\right]= -m J^{a}_{n+m},&\\
+  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m},&\\
+  \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=&\\
+  \quad =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0},&
+\end{array}
+\end{equation}
+ it is more convenient to act with $L_{2}^{\gf}$ and $\left(L_{1}^{\gf}\right)^{2}$. 
+ Applying $L_{2}^{\gf}$ we get
+\begin{equation*}
+  L_{2}^{\gf}\psi= \left(-8 L_{0}-c+ 3 \kappa L_{0}+\frac{1}{2}\tau (k \dim\gf-x_{e}k\dim\af)\right) \varphi_{(\mu,\nu)}=0
+\end{equation*}
+We use $L_{0} \varphi_{(\mu,\nu)}=h_{(\mu,\nu)} \varphi_{(\mu,\nu)}$, with the conformal weight  $h_{(\mu,\nu)}= \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k x_{e}+h^{\vee}_{\af})}\right)$ and the central charge $c=\frac{k\dim \gf}{k+h^{\vee}_{\gf}}-\frac{x_{e}k\dim \af}{x_{e} k+h^{\vee}_{\af}}$.
+This leads to the relation on $\kappa,\tau$:
+\begin{equation}
+  \label{eq:28} (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0.
+\end{equation}
+The second relation appears as a result of the $L_{1}^{\gf}$-action:
+\begin{equation}
+  \label{eq:21}
+ -12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
+(C_{\mu}-\tilde{C}_{\nu})=0,
+\end{equation}
+ where $C_{\mu}=(\mu,\mu+2\rho)$ and $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ are the eigenvalues of the quadratic Casimir operators $\sum_{a}t^{a}t^{a}$ and $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ of Lie algebras $\gf$ and $\af$.
+Relations \eqref{eq:28},\eqref{eq:21} are the necessary conditions for CFT correlation functions to be SLE martingales.
+
+From equations \eqref{eq:28},\eqref{eq:21} we immediately get $\kappa,\tau$ for each pair $(\mu,\nu)$ of $\gf$ and $\af$-weights.
+
+\subsubsection{Examples}
+\label{sec:examples-1}
+As an example consider  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset models which are equivalent to $Z_{N}$-parafermions.
+The central charge is $c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2}$.
+Conformal weights of primary fields with Dynkin indeces $(k,l)$ are $h_{(k,l)}=\frac{k(k+2)}{4(N+2)}-\frac{l^{2}}{4N}$.
+
+Case $N=2$, $c=\frac{1}{2}$ corresponds to the Ising model, we have two non-trivial primary fields with conformal weights $h_{(2,0)}=1/2, h_{(1,1)}=1/16$.
+Substituting the field $\varphi_{(2,0)}$ into equations (\ref{eq:28},\ref{eq:21}) we get: $3\kappa-9+4\tau =0;\quad -3+\kappa+4\tau=0$.
+The solution is $\kappa=3, \tau=0$.
+For the field $\varphi_{(1,1)}$ the relations are $3\kappa-16+64\tau=0,\quad -64+9\kappa + 64\tau=0$, $\kappa=16/3, \tau=0$.
+So we have no additional motion for the Ising model and two possible values for SLE parameter $\kappa$  coinciding with the well-known results \cite{schramm2006conformally}.
+
+For $N=3$ the parafermionic model central charge is $c=\frac{4}{5}$.
+Conformal weights are $h_{(0,0)}=0$, $h_{(0,2)}=h_{(0,-2)}=\frac{2}{3}\; \mathrm{mod}\; 1$, $h_{(2,0)}=\frac{2}{5}$, $h_{(2,2)}=h_{(2,-2)}=\frac{1}{15}$.
+The corresponding values of $\kappa,\tau$ are: $(\frac{208}{25},\frac{242}{225}), (\frac{10}{3},0),(\frac{80}{19},\frac{14}{171})$.
+As it  was mentioned in \cite{santachiara2008sle} the field $\varphi_{(2,0)}$ with the conformal weight $h_{(2,0)}=\frac{2}{5}$ constitutes the $Z_{3}$-singlet, so  an additional random walk does not appear and $\tau=0$.
+The form of equations (\ref{eq:7}) is similar to that of \cite{santachiara2008sle}, but the normalization of $\tau$ differs.
+
+It is easy to see that for the $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset realization of minimal unitary models with $c=\frac{3N}{N+2}+1-\frac{3(N+1)}{N+3}=1-\frac{6}{(N+2)(N+3)}$ the system of equations (\ref{eq:28},\ref{eq:21}) is always consistent for $\tau=0$ and we get a standard connection between the SLE-parameter $\kappa$ and the central charge $c=\frac{(6-\kappa)(3\kappa-8)}{2\kappa}$.
+
+\subsection{Conclusion and outlook}
+\label{sec:outlook}
+
+In  \cite{bettelheim2005stochastic} a connection between WZNW-models and Schramm-Loewner evolution with additional Brownian motion on group manifold was established.
+The authors also stated a problem of a possible connection of SLE parameters for martingales in WZNW, coset and minimal models.
+In present letter we used the method proposed in \cite{alekseev2010sle} to obtain necessary conditions on SLE martingales.
+This method allowed us to compare our results with parafermionic results presented in \cite{santachiara2008sle,picco2008numerical}.
+
+The coset structure of minimal models is manifest in field theory perturbed by an external magnetic field \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
+This theory is supported by experimental data \cite{coldea2010quantum}.
+Relations between correlation functions in coset theory and SLE observables can be a starting point in studies of domain walls in lattice models away from the  critical point.
+
+Massive perturbations of $G/A$-coset theory are realized as an affine Toda field theory and are classified by simple roots of the Lie algebra $\gf$.
+Affine Toda field theory can be obtained by adding perturbation term to  the action (\ref{eq:24}):
+\begin{equation}
+  S_{\text{pert}}=S_{G/A}(\gamma,\alpha)-\frac{k\lambda}{2\pi}\int {\cal K} (\gamma T, \gamma^{-1} \bar T),
+\end{equation}
+where $T,\bar T\in \gf$ are specially chosen Lie algebra elements \cite{bakas1996lagrangian,hollowood1995massive,park1994deformed}. 
+The perturbation leads to an insertion of certain primary field in all the correlation functions  \cite{hollowood1989rational}.
+It was shown that massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off,bauer2009off}.
+The question is whether the interaction of the perturbing primary field with the $\tau$-term of the equation (\ref{eq:4}) leads to the same contribution as the addition of a massive drift to SLE.
+
+In the forthcoming studies we will address this question and compare  massive perturbations of coset models with the numerical studies of domain walls in the Ising model perturbed by a random Gaussian external field \cite{stevenson2011domain}.
+
 %%

### 2012-05-22 AffineLieAlgebras/Thesis/common.tex
Some work on thesis

@@
 
-В главе \ref{sec:SLE} мы описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
-
-Заключительная глава \ref{cha:computational-methods} представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли.
+Заключительная глава \ref{cha:applications} посвящена практическим приложениям результатов диссертации.
+В разделе \ref{sec:SLE} мы  описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
+Раздел \ref{cha:computational-methods} представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли и реализованного с использованием методов диссертации.
 

### 2012-05-22 AffineLieAlgebras/Thesis/review.tex
Some work on thesis

@@
 
-\chapter{Конформная теория поля и аффинные алгебры Ли}
+\chapter{Конформная теория поля и алгебры Ли}
 \label{cha:CFT}
 
-Двумерная конформная теория поля возникла в результате обобщения гипотезы конформной инвариантности критического поведения в двумерных системах \cite{Polyakov:1970xd}.
-Если использовать для описания критического поведения теорию поля, то такая теория должна обладать конформной инвариантностью.
+Двумерная конформная теория поля возникла в результате обобщения гипотезы о масштабной инвариантности критического поведения в двумерных системах \cite{Polyakov:1970xd}.
+Если использовать теорию поля для описания критического поведения, то такая теория должна обладать конформной инвариантностью.
 
@@
 В том случае, если в теории конечное число примарных полей, такая теория называется минимальной.
-Обычно соответствие между критическим поведением решеточных моделей и конформной теорией поля устанавливается именно для минимальных моделей \cite{bauer2004cfts,bauer2003sle,bauer2003conformal}.
-Вместе с тем доказательство соответствия между критическим поведением решеточных моделей и конформной теории поля остается серьезной проблемой.
-Здесь в последнее время получены новые результаты, связанные с использованием эволюции Шрамма-Левнера.
-Некоторые вопросы такого соответствия мы обсуждаем в главе \ref{sec:SLE}.
-В ней мы обсуждаем соответствие между решеточными моделями и coset-моделями конформной теории поля.
+Обычно соответствие между критическим поведением решеточных моделей и конформной теорией поля устанавливается именно для минимальных моделей \cite{belavin1984ics}.
+
+Строгое доказательство соответствия между критическим поведением решеточных моделей и конформной теории поля остается серьезной проблемой, но  в последнее время получены новые результаты, связанные с использованием  эволюции Шрамма-Лёвнера.
+Этот подход основывается на сопоставлении доменных стенок в решеточных моделях с траекториями случайного процесса, называющегося эволюцией Шрамма-Лёвнера \cite{schramm2000scaling}.
+Для простых моделей, типа модели Изинга, удается доказать, что некоторая наблюдаемая --  мартингал по отношению к эволюции Шрамма-Лёвнера, -- обладает конформной инвариантностью.
+Оказывается, что этого достаточно для доказательства конформной инвариантности критического поведения модели \cite{duminil2011conformal}.
+Такая техника сильно отличается от теоретико-полевого описания, поэтому актуальна проблема установления соответствия между эволюцией Шрамма-Лёвнера и конформной теорией поля \cite{bauer2002sle,bauer2003conformal,bauer2003sle,bauer2004cfts,bauer2004sle,bauer2004conformal}.
+В главе \ref{cha:applications} мы показываем, что алгебраические методы играют роль в установлении такого соответствия для ВЗНВ и coset-моделей конформной теории поля.
 
@@
 
-\subsection{Конформные вложения и модулярно-инвариантные статсуммы}
-\label{sec:modular-invariance}
-
-При изучении конформной теории поля на плоскости или на сфере 
-голоморфный и антиголоморфный сектора можно рассматривать независимо. 
-Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть
-определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать
-взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно) чтобы теория была определена на торе.
-
-В теории критического поведения конформная инвариантность имеет место только в критической точке,
-где голоморфный и антиголоморфный сектора расцеплены. Но вблизи критической точки эти сектора должны
-быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве
-параметров, то эта связь должна сохраняться и в критической точке. Физический спектр теории должен
-плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного
-сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической
-точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния. Здесь
-естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории
-на торе.
-
-Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
-Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
-выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
-вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
-обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
-параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
-Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
-параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
-статсумма дается следом оператора сдвига в степени $m$:
-\begin{equation}
-  \label{eq:6}
-  Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
-\end{equation}
-Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
-конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
-$H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
-$L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
-$P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
-можно записать в виде
-\begin{equation}
-  \label{eq:7}
-  \begin{split}
-      Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
-      L_0)\}\\
-      =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
-  \end{split}
-\end{equation}
-Или, если ввести $q=\exp 2\pi i \tau$
-\begin{equation}
-  \label{eq:71}
-  Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
-\end{equation}
-Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
-
-Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
-эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
-
-Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
-модулярной инвариантности статсуммы.
-
-При помощи конформных преобразований можно перейти к таким координатам, в которых соотношения
-эквивалентности для тора (граничные условия) записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
-$\mathbb{C}$.
-
-Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
-конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
-$SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
-\begin{equation}
-  \label{eq:99} A=
-  \begin{pmatrix} a & b\\ c & d
-  \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
-\end{equation}
-и матрицы $A$ и $-A$ действуют одинаково на $\tau$
-\begin{equation}
-  \label{eq:137} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
-\end{equation}
-$\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
-модулярной группой.
-
-Конформная теория поля задаётся примарными полями $\phi_a$ с конформными размерностями $h_a$.
-
-Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
-произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
-представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсумма на торе
-(\ref{eq:71}) может быть записана в виде
-\begin{equation}
-  \label{eq:9}
-    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
-\end{equation}
-где $\chi_j$ --- нормализованный характер представления $\mathcal{H}_j$,
-\begin{equation}
-  \label{eq:74}
-  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i\tau}
-\end{equation}
-
-Характеры переходят друг в друга при модулярных преобразованиях:
-\begin{equation}
-  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
-\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
-\end{equation}
-где $S$ и $T$ --- постоянные матрицы.
-
-Для ВЗНВ-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$. Тогда
-\begin{equation}
-  \label{eq:76}\mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi}
-L_{\hat \lambda}\otimes L_{\hat \xi}
-\end{equation}
-
-Коэффициенты ветвления для вложения аффинной подалгебры Ли в аффинную алгебру можно использовать для
-построения модулярно-инвариантной статсуммы в соответствующей ВЗНВ-модели. Когда рассматривается
-теория на торе,  набор физически допустимых полей ограничен требованиями модулярной инвариантности.
-
-Простейший модулярный инвариант можно записать следующим образом:
-\begin{equation}
-  \label{eq:34}
-   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
-\end{equation}
-Здесь суммирование ведется по всем конформным семействам (то есть по всем представлениям алгебры
-$\mathfrak{a}$).
-
-Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует
-алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно.
-
-Представления алгебры $\gf$ можно рассматривать как сумму представлений подалгебры $\af$.
-
-Если мы рассмотрим редукцию характеров аффинной алгебры
-\begin{equation}
-  \label{eq:8}
-   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
-  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
-\end{equation}
-и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится. То есть из
-диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый недиагональный инвариант для
-подалгебры $\mathfrak{a}$. Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
-ней конформная инвариантность.
-
-Пусть $J^{a_j}_{-n_j}$ и $\tilde{J}^{a'_j}_{-n_j}$ --- понижающие операторы алгебр  $\mathfrak{g}$ и
-$\mathfrak{a}\subset\mathfrak{g}$.  $\pi_{\mathfrak{a}}$ --- проекционный оператор
-$\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$. В теории, связанной с  $\mathfrak{g}$
-с вакуумом $\left| 0\right>$, примарным полем $\phi_{\lambda}$ и состоянием старшего веса  $\left|\lambda\right>=\lim_{z\to 0} \phi_{\lambda}(z) \left|0\right>$ будут следующие состояния:
-\begin{equation}
-  \label{eq:109}
-  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
-\end{equation}
-Вакуум $\mathfrak{g}$-инвариантен, то есть $J_0^a\left|0\right>=0$. При проекции на подалгебру
-$\mathfrak{a}$ состояния примут вид
-\begin{equation}
-  \label{eq:110}
-  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
-\end{equation}
-Из $\mathfrak{g}$-ивариантности вакуума следует его $\mathfrak{a}$-инвариантность, но для тензора
-энергии-импульса в общем случае это не так. Поэтому тензор энергии-импульса большей теории должен
-состоять только из генераторов $\tilde{J}$. Тогда из $T_{\mathfrak{g}}=T_{\mathfrak{a}}$ следует $c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению
-\begin{equation}
-  \label{eq:111}
-  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+h^{\vee}_{\gf}}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+h^{\vee}_{\af}}
-\end{equation}
-Здесь $x_e$ --- индекс вложения, а  $g$, $a$ --- дуальные числа Кокстера, которые характеризуют алгебры.
-
-Можно показать, что это равенство удовлетворяется только для представлений уровня 1. То есть класс
-конформных вложений не слишком широк и существует полная их классификация. Кроме того, для
-конформных вложений существуют специальные методы разложения представлений.
-
-Модулярная инвариантность статсуммы для полей, принадлежащих представлениям алгебры  $\mathfrak{g}$,
-сохраняется при проекции на подалгебру $\mathfrak{a}$. Если все представления $\mathfrak{g}$ в теории
-удовлетворяют описанным требованиям, то при проекции мы получаем конформную теорию поля.
-
-Существует теорема о том, что для конформного вложения  $\mathfrak{a}\subset\mathfrak{g}$ только
-конечное число коэффициентов ветвления отлично от нуля \cite{kac1988modular,altschuler1990branching}. Поэтому после того, как мы разложили все
-представления $\mathfrak{g}$ мы подставляем результаты в выражение для статсуммы и получаем
-модулярно-инвариантную статсумму для вложенной теории. Такая статсумма уже не будет иметь
-диагональный вид:
-\begin{equation}
-  \label{eq:36}
-   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
-\end{equation}
-Таким образом, редукция представлений аффинной алгебры на представления подалгебры, рассмотренная в главе \ref{cha:affine-lie-algebras}, приводит к построению модулярно-инвариантных статсумм методом конформных вложений \cite{walton1989conformal}.
-Проблема конформных вложений также недавно рассматривалась в работе \cite{coquereaux2008conformal}.
-Мы приводим примеры таких вычислений в разделе \ref{sec:conformal-embeddings}.
-
-\section{Coset-модели конформной теории поля}
-\label{sec:coset-models-cft}
-
-Coset-конструкция для моделей конформной теории поля была предложена в работе \cite{Goddard198588}.
-Первоначально она была введена чисто алгебраически на языке генераторов, без обращения к действию и лагранжиану.
-Coset-модели задаются алгеброй Ли $\gf$ и ее подалгеброй $\af$.
-Обозначим через $J_{n}^{a}$ генераторы аффинной алгебры Ли $\gfh$, а через $\tilde{J}_{n}^{b}$ -- генераторы $\afh$, так что $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b} J^{a}_{n}$.
-Генераторы алгебры Вирасоро в coset-моделях даются разностями выражений Сугавары для ВЗНВ-моделей, соответствующих алгебрам  $\gf$ и $\af$:
-\begin{equation*}
-  L_{n}=L_{n}^{\gf}-L_{n}^{\af}
-\end{equation*}
-Коммутационные соотношения между генераторам алгебры Вирасоро и генераторами подалгебры  $\afh$ тривиальны
-\begin{equation}
-  \label{eq:26}
-  \left[L_{n},\tilde{J}^{b}_{m}\right]=0
-\end{equation}
-Рассмотрим неприводимый модуль $L^{\mu}_{\gfh}$ как приводимый модуль подалгебры $\afh$: $L^{\mu}_{\gfh}=\bigoplus_{\nu}L^{\nu}_{\afh}$.
-В силу  равенства \eqref{eq:26} весовые векторы, соответствующие весам $L^{\mu}_{\gfh}$, сингулярным по отношению к действию $\afh$, будут образовывать модуль алгебры Вирасоро.
-Статсумма такой модели будет даваться функциями ветвления для вложения $\afh\to\gfh$ (См.
-раздел \ref{sec:coset-models} в главе \ref{cha:affine-lie-algebras}).
-
-Coset-модели можно реализовать, как калибровочные модели Весса-Зумино-Новикова-Виттена, если добавить дополнительные калибровочные полями  $A, \bar{A}$, принимающие значения в алгебре Ли $\af\subset \gf$, в действие ВЗНВ-модели  \cite{gawdzki1988g}:
-\begin{multline}
-  \label{eq:38}
-      S(g,A)=S_{WZNW}(g)+\\
-      \frac{k}{4\pi}\int d^{2}z \left(\mathcal{K}(A, g^{-1}\bar \partial g)-\mathcal{K}(\bar A, (\partial g ) g^{-1})+\mathcal{K}(A,g^{-1}\bar A g)-\mathcal{K}(A,\bar A)\right)
-\end{multline}
-Полученная теория поля обладает калибровочной $G\times G$-инвариантностью  и ее квантование естественно проводить с использованием БРСТ-формализма \cite{hwang1993brst}.
-
-Токи в квантовой теории даются выражением
-\begin{equation}
-  \label{eq:39}
-  J_{(\gf,\af)}=-k\partial g g^{-1} -k g A g^{-1}
-\end{equation}
-
-Из тождеств Уорда можно получить равенство
-\begin{equation*}
-  \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{\vee}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
-\end{equation*}
-
-В coset-моделях поля нумеруются парами весов  $(\mu,\nu)$, где $\mu$ -- вес  $\gfh$, а $\nu$ -- вес $\afh$, соответственно.
-Но появляются правила отбора, так как функции ветвления для некоторых пар весов  $(\mu,\nu)$ исчезают.
-Кроме того, имеется избыточность, так как функции ветвления для различных пар $(\mu,\nu)$ могут совпадать \cite{fuchs1996resolution,schellekens1990field}.
-
-Итак, примарные поля нумеруются парами весов  $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ алгебры $\gfh$ и подалгебры $\afh$, такими, что соответствующие функции ветвления $b^{\mu}_{\nu}(q)\neq 0$.
-Некоторые пары эквивалентны.
-Эта эквивалентность дается действием так называемых ``простых токов'' $(J,\tilde{J})$, которые являются элементами группы внешних автоморфизмов  $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ алгебры $\gfh\times\afh$, где $B(G)$ -- это центр группы Ли $G$.
-Мы можем думать о простых токах как о примарных полях, тогда их действие на поля теории дается слиянием \cite{difrancesco1997cft}.
-Таким образом, примарные поля coset-моделей нумеруются классами эквивалентности пар весов  $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, где $(J,\tilde J)$ такие, что  конформные веса компонент равны:  $h_{J}-h_{\tilde{J}}=0$.
-
-Конформный вес примарного поля в coset-модели равен
-\begin{multline}
-  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
-  \left|\phi_{(\mu,\nu)}\right>=\\
-  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
-\end{multline}
-Из тождеств Уорда можно получить аналог уравнений Книжника-Замолодчикова для coset-моделей \cite{kogan1997knizhnik}:
-\begin{equation}
-  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
-  \label{eq:101}
-\end{equation}
-
-Из алгебраического определения coset-моделей следует, что функции ветвления для модулей аффинной алгебры $\gfh$ на модули подалгебры $\afh$ являются характерами конформных семейств.
-
-Все минимальные унитарные модели можно реализовать как coset-модели типа $\widehat{su(2)}_k/\widehat{u(1)}$ или $\widehat{su(2)_k\oplus su(2)_1}/\widehat{su(2)_{k+1}}$ (здесь нижний индекс указывает на уровень модулей старшего веса, соответствующих примарным полям).
-
-\section{Конформная теория поля на области с границей}
-\label{sec:boundary-cft}
-
-При изучении критических явлений большое применение находит формулировка конформной теории поля на области с границей.
-Это естественно как при описании реальных экспериментов, где система всегда имеет конечные размеры, так и при изучении критического поведения отдельных кластеров в решеточных моделях.
-Формулировка так называемой граничной конформной теории поля восходит к пионерским работам Карди \cite{cardy1984conformal,cardy1989boundary,cardy1986effect}.
-
-\section{Простые алгебры Ли, алгебра петель, центральные расширения и аффинные алгебры Ли}
+Как мы видим, теория представлений аффинных алгебр Ли играет определяющую роль при изучении моделей Весса-Зумино-Новикова-Виттена. Для удобства приведем в следующем разделе основные определения.
+
+\subsection{Простые алгебры Ли, алгебра петель, центральные расширения и аффинные алгебры Ли}
 
@@
 
-\subsection{Модули, веса и корни}
+\subsubsection{Модули, веса и корни}
 \label{sec:weights-roots}
@@
 
-\subsection{Модули старшего веса}
+\subsubsection{Модули старшего веса}
 \label{sec:high-weight-modul}
@@
 
+\subsection{Конформные вложения и модулярно-инвариантные статсуммы}
+\label{sec:modular-invariance}
+
+При изучении конформной теории поля на плоскости или на сфере 
+голоморфный и антиголоморфный сектора можно рассматривать независимо. 
+Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть
+определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать
+взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно) чтобы теория была определена на торе.
+
+В теории критического поведения конформная инвариантность имеет место только в критической точке,
+где голоморфный и антиголоморфный сектора расцеплены. Но вблизи критической точки эти сектора должны
+быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве
+параметров, то эта связь должна сохраняться и в критической точке. Физический спектр теории должен
+плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного
+сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической
+точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния. Здесь
+естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории
+на торе.
+
+Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
+Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
+выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
+вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
+обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
+параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
+Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
+параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
+статсумма дается следом оператора сдвига в степени $m$:
+\begin{equation}
+  \label{eq:6}
+  Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
+\end{equation}
+Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
+конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
+$H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
+$L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
+$P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
+можно записать в виде
+\begin{equation}
+  \label{eq:7}
+  \begin{split}
+      Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
+      L_0)\}\\
+      =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
+  \end{split}
+\end{equation}
+Или, если ввести $q=\exp 2\pi i \tau$
+\begin{equation}
+  \label{eq:71}
+  Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
+\end{equation}
+Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
+
+Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
+эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
+
+Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
+модулярной инвариантности статсуммы.
+
+При помощи конформных преобразований можно перейти к таким координатам, в которых соотношения
+эквивалентности для тора (граничные условия) записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
+$\mathbb{C}$.
+
+Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
+конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
+$SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
+\begin{equation}
+  \label{eq:99} A=
+  \begin{pmatrix} a & b\\ c & d
+  \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+\end{equation}
+и матрицы $A$ и $-A$ действуют одинаково на $\tau$
+\begin{equation}
+  \label{eq:137} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+\end{equation}
+$\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
+модулярной группой.
+
+Конформная теория поля задаётся примарными полями $\phi_a$ с конформными размерностями $h_a$.
+
+Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
+произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
+представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсумма на торе
+(\ref{eq:71}) может быть записана в виде
+\begin{equation}
+  \label{eq:9}
+    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
+\end{equation}
+где $\chi_j$ --- нормализованный характер представления $\mathcal{H}_j$,
+\begin{equation}
+  \label{eq:74}
+  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i\tau}
+\end{equation}
+
+Характеры переходят друг в друга при модулярных преобразованиях:
+\begin{equation}
+  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
+\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
+\end{equation}
+где $S$ и $T$ --- постоянные матрицы.
+
+Для ВЗНВ-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$. Тогда
+\begin{equation}
+  \label{eq:76}\mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi}
+L_{\hat \lambda}\otimes L_{\hat \xi}
+\end{equation}
+
+Коэффициенты ветвления для вложения аффинной подалгебры Ли в аффинную алгебру можно использовать для
+построения модулярно-инвариантной статсуммы в соответствующей ВЗНВ-модели. Когда рассматривается
+теория на торе,  набор физически допустимых полей ограничен требованиями модулярной инвариантности.
+
+Простейший модулярный инвариант можно записать следующим образом:
+\begin{equation}
+  \label{eq:34}
+   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
+\end{equation}
+Здесь суммирование ведется по всем конформным семействам (то есть по всем представлениям алгебры
+$\mathfrak{a}$).
+
+Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует
+алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно.
+
+Представления алгебры $\gf$ можно рассматривать как сумму представлений подалгебры $\af$.
+
+Если мы рассмотрим редукцию характеров аффинной алгебры
+\begin{equation}
+  \label{eq:8}
+   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
+  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
+\end{equation}
+и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится. То есть из
+диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый недиагональный инвариант для
+подалгебры $\mathfrak{a}$. Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
+ней конформная инвариантность.
+
+Пусть $J^{a_j}_{-n_j}$ и $\tilde{J}^{a'_j}_{-n_j}$ --- понижающие операторы алгебр  $\mathfrak{g}$ и
+$\mathfrak{a}\subset\mathfrak{g}$.  $\pi_{\mathfrak{a}}$ --- проекционный оператор
+$\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$. В теории, связанной с  $\mathfrak{g}$
+с вакуумом $\left| 0\right>$, примарным полем $\phi_{\lambda}$ и состоянием старшего веса  $\left|\lambda\right>=\lim_{z\to 0} \phi_{\lambda}(z) \left|0\right>$ будут следующие состояния:
+\begin{equation}
+  \label{eq:109}
+  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+\end{equation}
+Вакуум $\mathfrak{g}$-инвариантен, то есть $J_0^a\left|0\right>=0$. При проекции на подалгебру
+$\mathfrak{a}$ состояния примут вид
+\begin{equation}
+  \label{eq:110}
+  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
+\end{equation}
+Из $\mathfrak{g}$-ивариантности вакуума следует его $\mathfrak{a}$-инвариантность, но для тензора
+энергии-импульса в общем случае это не так. Поэтому тензор энергии-импульса большей теории должен
+состоять только из генераторов $\tilde{J}$. Тогда из $T_{\mathfrak{g}}=T_{\mathfrak{a}}$ следует $c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению
+\begin{equation}
+  \label{eq:111}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+h^{\vee}_{\gf}}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+h^{\vee}_{\af}}
+\end{equation}
+Здесь $x_e$ --- индекс вложения, а  $g$, $a$ --- дуальные числа Кокстера, которые характеризуют алгебры.
+
+Можно показать, что это равенство удовлетворяется только для представлений уровня 1. То есть класс
+конформных вложений не слишком широк и существует полная их классификация. Кроме того, для
+конформных вложений существуют специальные методы разложения представлений.
+
+Модулярная инвариантность статсуммы для полей, принадлежащих представлениям алгебры  $\mathfrak{g}$,
+сохраняется при проекции на подалгебру $\mathfrak{a}$. Если все представления $\mathfrak{g}$ в теории
+удовлетворяют описанным требованиям, то при проекции мы получаем конформную теорию поля.
+
+Существует теорема о том, что для конформного вложения  $\mathfrak{a}\subset\mathfrak{g}$ только
+конечное число коэффициентов ветвления отлично от нуля \cite{kac1988modular,altschuler1990branching}. Поэтому после того, как мы разложили все
+представления $\mathfrak{g}$ мы подставляем результаты в выражение для статсуммы и получаем
+модулярно-инвариантную статсумму для вложенной теории. Такая статсумма уже не будет иметь
+диагональный вид:
+\begin{equation}
+  \label{eq:36}
+   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
+\end{equation}
+Таким образом, редукция представлений аффинной алгебры на представления подалгебры, рассмотренная в главе \ref{cha:affine-lie-algebras}, приводит к построению модулярно-инвариантных статсумм методом конформных вложений \cite{walton1989conformal}.
+Проблема конформных вложений также недавно рассматривалась в работе \cite{coquereaux2008conformal}.
+Мы приводим примеры таких вычислений в разделе \ref{sec:conformal-embeddings}.
+
+\section{Coset-модели конформной теории поля}
+\label{sec:coset-models-cft}
+
+Coset-конструкция для моделей конформной теории поля была предложена в работе \cite{Goddard198588}.
+Первоначально она была введена чисто алгебраически на языке генераторов, без обращения к действию и лагранжиану.
+Coset-модели задаются алгеброй Ли $\gf$ и ее подалгеброй $\af$.
+Обозначим через $J_{n}^{a}$ генераторы аффинной алгебры Ли $\gfh$, а через $\tilde{J}_{n}^{b}$ -- генераторы $\afh$, так что $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b} J^{a}_{n}$.
+Генераторы алгебры Вирасоро в coset-моделях даются разностями выражений Сугавары для ВЗНВ-моделей, соответствующих алгебрам  $\gf$ и $\af$:
+\begin{equation*}
+  L_{n}=L_{n}^{\gf}-L_{n}^{\af}
+\end{equation*}
+Коммутационные соотношения между генераторам алгебры Вирасоро и генераторами подалгебры  $\afh$ тривиальны
+\begin{equation}
+  \label{eq:26}
+  \left[L_{n},\tilde{J}^{b}_{m}\right]=0
+\end{equation}
+Рассмотрим неприводимый модуль $L^{\mu}_{\gfh}$ как приводимый модуль подалгебры $\afh$: $L^{\mu}_{\gfh}=\bigoplus_{\nu}L^{\nu}_{\afh}$.
+В силу  равенства \eqref{eq:26} весовые векторы, соответствующие весам $L^{\mu}_{\gfh}$, сингулярным по отношению к действию $\afh$, будут образовывать модуль алгебры Вирасоро.
+Статсумма такой модели будет даваться функциями ветвления для вложения $\afh\to\gfh$ (См.
+раздел \ref{sec:coset-models} в главе \ref{cha:affine-lie-algebras}).
+
+Coset-модели можно реализовать, как калибровочные модели Весса-Зумино-Новикова-Виттена, если добавить дополнительные калибровочные полями  $A, \bar{A}$, принимающие значения в алгебре Ли $\af\subset \gf$, в действие ВЗНВ-модели  \cite{gawdzki1988g}:
+\begin{multline}
+  \label{eq:38}
+      S(g,A)=S_{WZNW}(g)+\\
+      \frac{k}{4\pi}\int d^{2}z \left(\mathcal{K}(A, g^{-1}\bar \partial g)-\mathcal{K}(\bar A, (\partial g ) g^{-1})+\mathcal{K}(A,g^{-1}\bar A g)-\mathcal{K}(A,\bar A)\right)
+\end{multline}
+Полученная теория поля обладает калибровочной $G\times G$-инвариантностью  и ее квантование естественно проводить с использованием БРСТ-формализма \cite{hwang1993brst}.
+
+Токи в квантовой теории даются выражением
+\begin{equation}
+  \label{eq:39}
+  J_{(\gf,\af)}=-k\partial g g^{-1} -k g A g^{-1}
+\end{equation}
+
+Из тождеств Уорда можно получить равенство
+\begin{equation*}
+  \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{\vee}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
+\end{equation*}
+
+В coset-моделях поля нумеруются парами весов  $(\mu,\nu)$, где $\mu$ -- вес  $\gfh$, а $\nu$ -- вес $\afh$, соответственно.
+Но появляются правила отбора, так как функции ветвления для некоторых пар весов  $(\mu,\nu)$ исчезают.
+Кроме того, имеется избыточность, так как функции ветвления для различных пар $(\mu,\nu)$ могут совпадать \cite{fuchs1996resolution,schellekens1990field}.
+
+Итак, примарные поля нумеруются парами весов  $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ алгебры $\gfh$ и подалгебры $\afh$, такими, что соответствующие функции ветвления $b^{\mu}_{\nu}(q)\neq 0$.
+Некоторые пары эквивалентны.
+Эта эквивалентность дается действием так называемых ``простых токов'' $(J,\tilde{J})$, которые являются элементами группы внешних автоморфизмов  $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ алгебры $\gfh\times\afh$, где $B(G)$ -- это центр группы Ли $G$.
+Мы можем думать о простых токах как о примарных полях, тогда их действие на поля теории дается слиянием \cite{difrancesco1997cft}.
+Таким образом, примарные поля coset-моделей нумеруются классами эквивалентности пар весов  $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, где $(J,\tilde J)$ такие, что  конформные веса компонент равны:  $h_{J}-h_{\tilde{J}}=0$.
+
+Конформный вес примарного поля в coset-модели равен
+\begin{multline}
+  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
+  \left|\phi_{(\mu,\nu)}\right>=\\
+  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
+\end{multline}
+Из тождеств Уорда можно получить аналог уравнений Книжника-Замолодчикова для coset-моделей \cite{kogan1997knizhnik}:
+\begin{equation}
+  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
+  \label{eq:101}
+\end{equation}
+
+Из алгебраического определения coset-моделей следует, что функции ветвления для модулей аффинной алгебры $\gfh$ на модули подалгебры $\afh$ являются характерами конформных семейств.
+
+Все минимальные унитарные модели можно реализовать как coset-модели типа $\widehat{su(2)}_k/\widehat{u(1)}$ или $\widehat{su(2)_k\oplus su(2)_1}/\widehat{su(2)_{k+1}}$ (здесь нижний индекс указывает на уровень модулей старшего веса, соответствующих примарным полям).
+
+\section{Конформная теория поля на области с границей}
+\label{sec:boundary-cft}
+
+При изучении критических явлений большое применение находит формулировка конформной теории поля на области с границей.
+Это естественно как при описании реальных экспериментов, где система всегда имеет конечные размеры, так и при изучении критического поведения отдельных кластеров в решеточных моделях.
+Формулировка так называемой граничной конформной теории поля восходит к пионерским работам Карди \cite{cardy1984conformal,cardy1989boundary,cardy1986effect}.
+
+Рассмотрим теорию на верхней полуплоскости, которую мы обозначим через $\mathbb{H}$.
+
 %%

### 2012-05-23 AffineLieAlgebras/Thesis/review.tex
Some text on boundary cft started

@@
 
-Глобальные конформные преобразования имеют вид $w(z)=\frac{az+b}{cz+d},\; ad-bc=1$.
+Глобальные конформные преобразования имеют вид
+\begin{equation}
+  \label{eq:172}
+  w(z)=\frac{az+b}{cz+d},\; ad-bc=1ю
+\end{equation}
 
@@
 Рассмотрим теорию на верхней полуплоскости, которую мы обозначим через $\mathbb{H}$.
+Модель на верхней полуплоскости может быть конформно-инвариантной только если конформные преобразования сохраняют границу и граничные условия, то есть переводят вещественную ось в себя.
+Среди глобальных конформных преобразований (\ref{eq:172}) это те, у которых параметры $a,b,c$ вещественные, то есть глобальная конформная группа для полуплоскости содержит половину глобальных конформных преобразований плоскости.
+Аналогично среди инфинитезимальных преобразований $z\to z+\epsilon(z)$ подходят лишь те, для которых $\epsilon(\bar z)=\bar \epsilon(z)$.
+То есть голоморфный и антиголоморфный сектора не независимы.
+
+Вид преобразований примарных полей (\ref{eq:3}) дает следующие варианты конформно-инвариантных граничных условий:
+\begin{eqnarray}
+  \label{eq:173}
+ & \phi |_{\mathbb{R}}=0,\\
+ & \phi |_{\mathbb{R}}=\infty,\\
+ & \left. \frac{\partial \phi}{\partial n}\right|_{\mathbb{R}}=0
+\end{eqnarray}
 

### 2012-05-26 AffineLieAlgebras/Thesis/review.tex
Added one formula
More on boundary cft

@@
 \end{eqnarray}
+Конформное тождество Уорда показывает, как конформные преобразования действуют на корреляционные функции:
+\begin{equation}
+  \label{eq:174}
+  \delta_{\epsilon,\bar \epsilon} \left< X\right> = -\frac{1}{2\pi i} \oint_C dz \epsilon(z) \left< T(z) X\right> +\frac{1}{2\pi i}\oint_C d\bar z \bar \epsilon(\bar z) \left< \bar T(\bar z) X\right> 
+\end{equation}
+Теперь контур интегрирования $C$ должен лежать в  верхней полуплоскости, а  $\epsilon$ и $\bar \epsilon$ уже не являются независимыми, они комлексно сопряжены $\bar \epsilon=\epsilon^{*}$.
+Теория уже не распадается на независимые голоморфный и антиголоморфный сектора.
+Однако мы можем продолжить теорию на нижнюю полуплоскость, рассматривая зависимость от $\bar z_{i}$ на верхней полуплоскости как зависимость от $z_{i}^{*}=\bar z_{i}$ на нижней полуплоскости.
+Для этого мы добавим ``зеркальное отражение'' системы, то есть удвоим число полей в корреляторах.
+Если выполнено условие $T(z^{*})=\bar T(z), \bar T(z^{*})=T(z)$, то есть $\bar T=T$ на вещественной оси, мы можем продолжить контуры интегрирования в нижнюю полуплоскость.
+
+Это условие естественно, так как в координатах $x,y$ оно имеет вид $T_{xy}=0$, что соответствует отсутствию потока энергии через границу.
+
+Теперь мы можем переписать тождество Уорда следующим образом:
+\begin{equation}
+  \label{eq:172}
+  \delta_{\epsilon} \left< X\right> = -\frac{1}{2\pi i} \oint dz \epsilon(z) \left< T(z) X'\right>,
+\end{equation}
+где
+\begin{equation}
+  \label{eq:175}
+  X'=\phi_{h_{1}}(z_{1}) \bar \phi_{\bar h_{1}}(z_{1}^{*}) \dots \phi_{h_{n}}(z_{n}) \bar \phi_{\bar h_{n}}(z_{n}^{*}), 
+\end{equation}
+а $\phi_{h_{i}}(z_{i})$ -- голоморфная часть поля $\phi_{(h_{i},\bar h_{i}}(z_{i},\bar z_{i})$ и $\bar\phi_{\bar h_{i}}(z_{i}^{*})$ -- антиголоморфная часть после преобразования четности (отражения), то есть тоже голоморфное поле с голоморфной размерностью $\bar h_{i}$.
+Таким образом, коррелятор $\left<X\right>$ на верхней полуплоскости, как функция $2n$ переменных $z_{1},\bar z_{1},\dots,z_{n},\bar z_{n}$ удовлетворяет тем же дифференциальным уравнениям, что и коррелятор $\left< X'\right>$ на всей плоскости, рассматриваемый как функция $2n$ голоморфных переменных $z_{1},\dots z_{2n}$, где $z_{n+i}=z_{i}^{*}$.
 

### 2012-05-26 AffineLieAlgebras/Thesis/review.tex
Section on boundary CFT is completed, restructured section on SLE. Further translation is needed.

@@
 Однако мы можем продолжить теорию на нижнюю полуплоскость, рассматривая зависимость от $\bar z_{i}$ на верхней полуплоскости как зависимость от $z_{i}^{*}=\bar z_{i}$ на нижней полуплоскости.
-Для этого мы добавим ``зеркальное отражение'' системы, то есть удвоим число полей в корреляторах.
-Если выполнено условие $T(z^{*})=\bar T(z), \bar T(z^{*})=T(z)$, то есть $\bar T=T$ на вещественной оси, мы можем продолжить контуры интегрирования в нижнюю полуплоскость.
+Для этого мы добавим ``зеркальное отражение'' системы, то есть удвоим число полей в корреляторах, добавив их образы по отношению преобразованию четности.
+Если выполнено условие $T(z^{*})=\bar T(z), \bar T(z^{*})=T(z)$, то есть $\bar T=T$ на вещественной оси, мы можем продолжить контуры интегрирования в нижнюю полуплоскость (Смотри Рис.
+\ref{fig:ward}).
 
@@
 Таким образом, коррелятор $\left<X\right>$ на верхней полуплоскости, как функция $2n$ переменных $z_{1},\bar z_{1},\dots,z_{n},\bar z_{n}$ удовлетворяет тем же дифференциальным уравнениям, что и коррелятор $\left< X'\right>$ на всей плоскости, рассматриваемый как функция $2n$ голоморфных переменных $z_{1},\dots z_{2n}$, где $z_{n+i}=z_{i}^{*}$.
+
+\begin{figure}[h]
+ \centering
+  \includegraphics[width=100mm]{contours}  
+  \caption{Объединение контуров интегрирования в тождесте Уорда в граничной конформной теории поля}
+  \label{fig:ward}
+\end{figure}
+
+То есть если нас интересует $n$-точечная корреляционная функция в теории на верхней полуплоскости, мы можем рассматривать голоморфную часть $2n$-точечной функции на всей плоскости.
+Взаимодействие полей с границей симулируется путем рассмотрения взаимодействия полей с их зеркальными отражениями.
+
+Если мы хотим изучать теорию с неоднородными граничными условиями, мы можем сделать это введя так называемые граничные операторы.
+Рассмотрим, для примера, поле $\phi(z)$  с конформной размерностью $h$, заданное на верхней полуплоскости.
+При приближении к вещественной оси оно взаимодействует со своим зеркальным отражением и мы можем воспользоваться операторным разложением:
+\begin{equation}
+  \label{eq:176}
+  \phi(z)\phi(z^*)\approx \sum_i (z-z^*)^{(h_i -2h)}\varphi_B^{(i)}(x),
+\end{equation}
+где мы отбросили высшие члены и положили $x=\frac{z+z^*}{2}$, а поля $\varphi_B$ живут на границе.
+Операторы $\varphi_B^{(i)}$ можно рассматривать как операторы изменения граничных условий.
+Их классификация следует из требований модулярной инвариантности и дается формулой Верлинде (См.
+\cite{cardy1989boundary,difrancesco1997cft}).
+
+Аналогичные рассуждения можно провести для ВЗНВ- и coset-моделей на верхней полуплоскости \cite{gawedzki2002boundary},\cite{ishikawa2003novel}, \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,felder1999geometry,alekseev1999d}, \cite{mercat2001integrable}.
+
+В разделе \ref{sec:SLE} мы обсудим связь граничной конформной теории поля с решеточными моделями и стохастическими процессами.
 

### 2012-05-26 AffineLieAlgebras/Thesis/4.tex
Section on boundary CFT is completed, restructured section on SLE. Further translation is needed.

@@
 Мы опять используем конформное отображение  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ чтобы переписать формулу для наблюдаемых на всей верхней полуплоскости.
-\begin{equation*}
+\begin{equation}
   \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{\lambda_i}} 
@@
   \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
-\end{equation*}
+  \label{eq:177}
+\end{equation}
 
@@
 
-Coset-модели можно реализовать, как калибровочные модели Весса-Зумино-Новикова-Виттена, если добавить дополнительные калибровочные полями  $A, \bar{A}$, принимающие значения в алгебре Ли $\af\subset \gf$, в действие \cite{gawdzki1988g}.
-Теперь поля нумеруются парами весов  $(\mu,\nu)$, где $\mu$ -- вес  $\gfh$, а $\nu$ -- вес $\afh$, соответственно.
+Поля нумеруются парами весов  $(\mu,\nu)$, где $\mu$ -- вес  $\gfh$, а $\nu$ -- вес $\afh$, соответственно.
 Но появляются правила отбора, так как функции ветвления для некоторых пар весов  $(\mu,\nu)$ исчезают.
@@
 
-Теперь введем эволюцию Шрамма-Левнера, соответствующую coset-моделям.
-Суть конструкции состоит в ограничении дополнительного броуновского движения на групповом многообразии на фактор-пространство  $G/A$.
-
-Чтобы ограничить броуновское движение на фактор-пространство $G/A$ выберем базис в $\gf$ специальным образом.
-Потребуем, чтобы генераторы $\{J^{a};\; a=1\dots \mathrm{dim}\gf\}$ были выбраны так, что $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$, а $\{J^{a};\; a=\mathrm{dim}\gf-\mathrm{dim}\af\dots \mathrm{dim}\gf\}$ -- генераторы подалгебры $\af\subset \gf$.
-Теперь мы  можем ввести  $(\mathrm{dim}\gf-\mathrm{dim}\af)$-мерное Броуновское движение с генераторами $d\theta^{a}$, такими, что $\mathbb{E}(d\theta^{a} \; d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\mathrm{dim}\gf-\mathrm{dim}\af$.
-
-Тогда для генераторов преобразования полей можно написать
-\begin{equation}
-  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}\left(d \theta ^{a} t^{a}_{i}\right)\right)
-\label{eq:136}
-\end{equation}
-Подставляя это выражение в уравнение \eqref{eq:150} мы получаем условие мартингала
-\begin{equation}
-  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0,
-\label{eq:147}
-\end{equation}
-которое можно переписать как требование, чтобы поле
-\begin{equation}
-  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}J^{a}_{-1}J^{a}_{-1}\right)\right) \phi_{(\mu,\nu)}
-\label{eq:126}
-\end{equation}
-было нулевым полем уровня два.
-
-Рассмотрим простой пример.Пусть $G=SU(2)$ и $A=U(1)$, соответствующая алгебра Ли $\gf=\mathrm{su}(2)$ имеет генераторы $J^{1},J^{2},J^{3}$, а $\af=\mathrm{u}(1)$ -- генератор $J^{3}$, $\af\subset\gf$.
-Заметим, что $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
-%%We label weights by Dynkin labels, so $J^{3}_{0}\phi_{(\mu,\nu)}=\frac{\mu}{2} \phi_{(\mu,\nu)}$.
-
-Уравнение \eqref{eq:126} теперь имеет вид
-\begin{equation}
-  \label{eq:138}
-  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
-\end{equation}
-Если перейти к базису $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\; J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$, это уравнение будет переписано в виде
-\begin{equation}
- \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{(\mu,\nu)},
-\label{eq:140}
-\end{equation}
-аналогичном уравнениям для парафермионных полей, выведенным в статье  \cite{santachiara2008sle}.
-
-В данном примере центральный заряд равен
-\begin{equation}
-  \label{eq:160}
-  c=\frac{2(k-1)}{k+2}
-\end{equation}
-
-Найдем решения уравнения  \eqref{eq:138}. Подействуем на  $\psi$ оператором $L_{2}$:
-\begin{equation}
-  \label{eq:158}
-  L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{(\mu,\nu)}=0,
-\end{equation}
-и получим
-\begin{equation}
-  \label{eq:169}
-  (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
-\end{equation}
-Другое уравнение можно получить действием  $L_{1}^{2}$
-\begin{equation}
-  \label{eq:161}
-  L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{(\mu,\nu)}=0
-\end{equation}
-Так как $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$, мы получаем
-\begin{equation}
-  \label{eq:157}
-  12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) +  \tau (C_{\mu}-\tilde{C}_{\nu})=0,
-\end{equation}
-где $C_{\mu}=(\mu,\mu+2\rho)$ -- собственное значение квадратичного оператора Казимира $\sum_{a}t^{a}t^{a}$.
-Для $u(1)$ это просто $\nu^{2}$.
-Нам необходимо еще одно уравнение, так как у нас три неизвестных $\kappa,\tau,h_{(\mu,\nu)}$.
-Чтобы его получить, мы пользуемся тем, что $\psi$ -- сингулярный вектор, так что $L_{1}\psi=0$ и следовательно $J_{1}^{3}L_{1}\psi=0$, что дает уравнение
-\begin{equation}
-  \label{eq:170}
-  \left(-6  + \kappa +  \tau +  2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0} \phi_{(\mu,\nu)}=0
-\end{equation}
-
-Рассмотрим случай $k=2, \;c=1/2$, который соответствует модели Изинга на квадратной решетке.
-У нас есть три неэквивалентных поля, нумерующихся парами весов $su(2)$ и $u(1)$: $\phi_{(0,0)}, \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$.
-Уравнение \eqref{eq:170} тривиально для  $\phi_{(0,0)}$ и  $\phi_{(0,2)}$, так что уравнения  \eqref{eq:157}, \eqref{eq:169} непротиворечивы,  однако мы не знаем, как интерпретировать параметр  $\tau$ в контексте модели Изинга.
-Для поля  $\phi_{(1,1)}$ не существует решений уравнений на  $\kappa,\tau$, так что не каждое примарное поле соответствует оператору смены граничного условия.
-
-Теперь обобщим анализ на произвольную  coset-модель.
-Работать с генераторами, ортогональными по отношению к форме Киллинга $\mathcal{K}$, не всегда удобно.
-Иногда предпочтительно использовать базис Шевалле или Картана-Вейля.
-Так что мы изменим условие нормировке дополнительного $\mathrm{dim}\gf$-мерного Броуновского движения \eqref{eq:136} на $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, и генератор преобразования поля  \eqref{eq:70} примет вид
-\begin{equation*}
-  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right).
-\end{equation*}
-Условие мартингала  \eqref{eq:150} запишется в виде
-\begin{equation*}
-  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
-      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0.
-\end{equation*}
-Это уравнение снова может быть переписано, как требование чтобы поле
-\begin{equation}
-  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\mu,\nu)}
-\label{eq:131}
-\end{equation}
-было нулевым полем уровня два.
-
-Действуя на уравнение \eqref{eq:131} операторами  $L_{2}$ и $L_{1}^{2}$ мы можем получить уравнения \eqref{eq:169} и \eqref{eq:157}.
-Чтобы получить дополнительные уравнения мы можем подействовать генераторами  $\tilde{J}^{b}_{1}$ алгебры $\afh$ и оператором $L_{1}$, аналогично том, как мы делали с оператором  $J^{3}_{1}$ при выводе уравнения \eqref{eq:170}.
-
-Чтобы упростить соотношения можно использовать обобщение уравнений Книжника-Замолодчикова \eqref{eq:144}, как было сделано для ВЗНВ-моделей в статье \cite{alekseev2010sle}.
-
-\subsection{О связи мартингалов coset-моделей с классификацией операторов смены граничного условия}
-\label{sec:5-conclusion}
-
-Мы предложили способ обобщения эволюции Шрамма-Левнера для получения таких наблюдаемых, которые могут исследоваться методами конформной теории поля.
-Описание полей в coset-моделях нетривиально ввиду идентификации полей \cite{schellekens1990field} и необходимости в разрешении фиксированных точек \cite{Fuchs:1996dd,fuchs1996resolution}, которое не обсуждалась в данной главе.
-Эти тонкости могут усложнить решение уравнений  \eqref{eq:169}, \eqref{eq:157} и аналогов уравнения \eqref{eq:170}.
-С другой стороны, использование уравнений Книжника-Замолодчикова  \cite{kogan1997knizhnik} для корреляционных функций в духе работы \cite{alekseev2010sle} приводит к матричным алгебраическим соотношениям, которые напоминают NIM-представления для граничных состояний \cite{ishikawa2003novel}.
-Дальнейшее изучение этого предмета может выявить глубокую алгебраическую связь условия мартингала с классификацией граничных состояний.
-
-Физическая интерпретация решений условий мартингала не вполне ясна, но пока не найдена и решеточная интерпретация эволюции Шрамма-Левнера с дополнительным Броуновским движением на групповом многообразии \cite{bettelheim2005stochastic} и решеточная реализация ВЗНВ-моделей.
-Кажется, что эти вопросы тесно связаны.
-
-\subsection{Интегрируемые возмущения конформной теории поля и массивная эволюция Шрамма-Лёвнера}
-\label{sec:massive-sle}
-
-\section{TODO}
-
-\abstract{
-  Scharmm-Loewner evolution (SLE) and conformal field theory (CFT) are popular and widely used instruments to study critical behavior of two-dimensional models, but they use different objects.
-While SLE  has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory.
-  To provide a way for the concurrent use of SLE and CFT we consider CFT correlation functions which are martingales with respect to SLE.
-We establish connection between parameters of Schramm-Loewner evolution on coset space and algebraic data of coset conformal field theory.
-Then we check the consistency of our approach with the  behaviour of parafermionic and minimal models.
-Coset models are connected with off-critical massive field theories and we discuss implications for SLE.}
-
-%%% PACS numbers
-%\PACS{05.50.+q, 11.25.Hf, 02.20.Sv}
-
-%\begin{document}
-%\maketitle
-
-\subsection{Introduction}
-\label{sec:introduction}
-
-Schramm-Loewner evolution \cite{schramm2000scaling} is a stochastic process satisfying stochastic differential equation (\ref{eq:19}).
-A solution of  equation (\ref{eq:19}) can be seen as  probability measure on random curves (called SLE traces).
-SLE is useful for the study of critical behavior \cite{Cardy:2005kh,rohde2005basic}, since for many lattice models the convergence of  domain walls to SLE traces can be proved \cite{bauer20062d,schramm2006conformally}.
-Practical computations with SLE rely on Ito calculus while proofs use discrete complex analysis \cite{duminil2011conformal}.
-
-Conformal field theory \cite{belavin1984ics} is formulated in terms of families of quantum fields which usually has no direct microscopic interpretation.
-On the other hand CFT has efficient computational tools such as Virasoro symmetry, Knizhnik-Zamolodchikov equations, fusion algebra etc and provides numerous predictions, such as celebrated Cardy formula \cite{cardy1992critical,smirnov2001critical} which gives crossing probability for critical percolation.
-
-Combination of these two approaches is immensely powerful, so it is important to find objects which can be studied from both points of view.
-
-We present a new class of such observables in coset conformal field theory  -- correlation functions which are martingales with respect to Schramm-Loewner evolution with additional Brownian motion on factor-space of Lie group $G$ by subgroup $A$ \cite{2011arXiv1112.4354N}.
-We derive relations connecting SLE and CFT parameters.
-We then check the consistency of these results with the earlier results  for parafermionic observables \cite{santachiara2008sle}.
-
-All minimal unitary models can be obtained by coset construction.
-Coset structure leads to specific off-critical behavior.
-Massive excitations of coset CFTs are given by affine Toda field theories \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
-Recent experimental study confirming this result attracted a lot of attention \cite{coldea2010quantum}.
-In conclusion we discuss possible connections of massive CFT perturbations with  off-critical SLEs (containing additional drift term  \cite{makarov2010off}).
-
-\subsection{Martingale conditions}
-\label{sec:mart-cond}
-
- Consider some critical lattice model on the upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$ (domain wall up to some length $t$).
-We denote this slit domain by $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$.
-Assume that $\gamma_{t}$ satisfies restriction property and is conformally  invariant \cite{Cardy:2005kh}.
-Then  conformal map  $g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ satisfies stochastic differential equation \cite{schramm2000scaling}:
-\begin{equation}
-\label{eq:19}
-  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
-\end{equation}
-where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
-
-For us it is convenient to use the map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
-\begin{equation}
-  \label{eq:20}
-       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}  
-\end{equation}
-
-Consider  $N$-point correlation function of boundary conformal field theory with boundary condition changing operators sitting at the tip of SLE trace and at the infinity:
-\begin{equation}
-  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\}_{i=1}^{N})_{\mathbb{H}_{t}}=
-\left<\varphi(z_{t}) \phi_{1}(z_{1},\bar z_{1}) \dots \phi_{n}(z_{n},\bar z_{n})
-      \varphi(\infty)\right>,
-    \label{eq:2}
-\end{equation}
-where $\phi_{i}$ are bulk primary fields with conformal weights $h_i$ and $\varphi(z_{t})$ is boundary condition changing operator.
-
-Let $\gf$ be a (semisimple) Lie algebra of a Lie group $G$ and $\af$ -- Lie algebra of a subgroup $A\subset G$. Denote by $x_{e}$ embedding index for $\af\to\gf$.
-
-Primary fields in coset models are labeled by pairs $(\lambda,\eta)$ of weights for $\gf$- and $\af$-representations.
-For each $\lambda$ the set of possible weights $\eta$ includes those which appear in the decomposition  $L^{(\mu)}_{\gf}=\bigoplus_{\eta} H^{\lambda}_{\eta}\otimes L^{(\eta)}_{\af}$.
-(Some pairs are equivalent, see \cite{fuchs1996resolution,schellekens1990field}).
-We assume that boundary field $\varphi$ is also primary and is labeled by weights $(\mu,\nu)$.
-
-  We use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite expression \eqref{eq:2} in the whole upper half plane:
-\begin{multline}
-  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\})_{\mathbb{H}_{t}}=\\
-  =\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{i}} 
-  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{\bar h_i}
-  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
-  \label{eq:1}
-\end{multline}
-We can extend the definition of $\mathcal{F}$ to the whole plane by doubling the number of fields $\phi_{i}$ \cite{cardy2004boundary,cardy1984conformal} and by considering $w_{i},\bar w_{i}$ as independent variables.
-To simplify notations we will write $\mathcal{F}(\left\{w_{i}\right\}_{i=1}^{2N})$.
-
-$G/A$-coset conformal field theory can be realized as a WZNW-model (with gauge group $G$) interacting with pure gauge fields of gauge group $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
-The action is written in terms of fields $\gamma:\mathbb{C}\to G$ and $\alpha,\bar\alpha:\mathbb{C}\to A$:
+Как мы упоминали в главе \ref{cha:CFT}, $G/A$-coset модель конформной теории поля может быть реализована как ВЗНВ-модель (с калибровочной группой $G$), взаимодействующая с чисто калибровочными полями, с калибровочной группой $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
+Действие записывается через поля $\gamma:\mathbb{C}\to G$ and $\alpha,\bar\alpha:\mathbb{C}\to A$ следующим образом:
 \begin{multline}
@@
 \end{multline}
-Here we denote by $\mathcal{K}$ the Killing form of a Lie algebra $\gf$ corresponding to a Lie group $G$.
+Здесь через  $\mathcal{K}$ обозначена форма Киллинга в алгебре Ли $\gf$, соответствующей группе Ли $G$.
 
- If we fix $A$-gauge we have $G/A$ gauge symmetry.
-Then we add random gauge transformations to Schramm-Loewner evolution \cite{2011arXiv1112.4354N} similar to the case of WZNW-models \cite{bettelheim2005stochastic}.
-Denote by $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) the  generators of $\gf$-representation ($\af$-representation) corresponding to the primary field $\phi_{i}$.
+Если мы фиксируем  $A$-калибровку, у нас останется  $G/A$ калибровочная инвариантность.
+Значит мы должны добавить случайные калибровочные преобразования к эволюции Шрамма-Левнера, аналогично случаю ВЗНВ-моделей из предыдущего раздела (См.
+также \cite{bettelheim2005stochastic}).
+Обозначим через $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) генераторы представления алгебры $\gf$ (соответственно, представления $\af$), соответствующего примарному полю $\phi_{i}$.
 
-Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in the right-hand-side of equation (\ref{eq:1}) gives us
+Рассмотрим эволюцию следа SLE $\gamma_{t}$ с момента   $t$ до $t+ dt$.  Первый сомножитель в правой части уравнения (\ref{eq:177}) дает нам
 \begin{equation*}
@@
 \label{sec:examples-1}
+
+Рассмотрим простой пример.Пусть $G=SU(2)$ и $A=U(1)$, соответствующая алгебра Ли $\gf=\mathrm{su}(2)$ имеет генераторы $J^{1},J^{2},J^{3}$, а $\af=\mathrm{u}(1)$ -- генератор $J^{3}$, $\af\subset\gf$.
+Заметим, что $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
+%%We label weights by Dynkin labels, so $J^{3}_{0}\phi_{(\mu,\nu)}=\frac{\mu}{2} \phi_{(\mu,\nu)}$.
+
+Уравнение \eqref{eq:126} теперь имеет вид
+\begin{equation}
+  \label{eq:138}
+  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
+\end{equation}
+Если перейти к базису $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\; J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$, это уравнение будет переписано в виде
+\begin{equation}
+ \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{(\mu,\nu)},
+\label{eq:140}
+\end{equation}
+аналогичном уравнениям для парафермионных полей, выведенным в статье  \cite{santachiara2008sle}.
+
+В данном примере центральный заряд равен
+\begin{equation}
+  \label{eq:160}
+  c=\frac{2(k-1)}{k+2}
+\end{equation}
+
 As an example consider  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset models which are equivalent to $Z_{N}$-parafermions.
@@
 
-\subsection{Conclusion and outlook}
+\subsection{Coset-модели и интегрируемые деформации конформной теории поля}
 \label{sec:outlook}
@@
 
+\subsection{О связи мартингалов coset-моделей с классификацией операторов смены граничного условия}
+\label{sec:5-conclusion}
+
+Мы предложили способ обобщения эволюции Шрамма-Левнера для получения таких наблюдаемых, которые могут исследоваться методами конформной теории поля.
+Описание полей в coset-моделях нетривиально ввиду идентификации полей \cite{schellekens1990field} и необходимости в разрешении фиксированных точек \cite{Fuchs:1996dd,fuchs1996resolution}, которое не обсуждалась в данной главе.
+Эти тонкости могут усложнить решение уравнений  \eqref{eq:169}, \eqref{eq:157} и аналогов уравнения \eqref{eq:170}.
+С другой стороны, использование уравнений Книжника-Замолодчикова  \cite{kogan1997knizhnik} для корреляционных функций в духе работы \cite{alekseev2010sle} приводит к матричным алгебраическим соотношениям, которые напоминают NIM-представления для граничных состояний \cite{ishikawa2003novel}.
+Дальнейшее изучение этого предмета может выявить глубокую алгебраическую связь условия мартингала с классификацией граничных состояний.
+
+Физическая интерпретация решений условий мартингала не вполне ясна, но пока не найдена и решеточная интерпретация эволюции Шрамма-Левнера с дополнительным Броуновским движением на групповом многообразии \cite{bettelheim2005stochastic} и решеточная реализация ВЗНВ-моделей.
+Кажется, что эти вопросы тесно связаны.
+
 %%

### 2012-05-30 AffineLieAlgebras/Thesis/4.tex
Translation in last chapter is completed. Printed as a booklet

@@
 \begin{multline}
-  \label{eq:24}
+\label{eq:178}
       S_{G/A}(\gamma, \alpha)=-\frac{k}{8\pi}\int_{S^2} d^2x\; {\cal K} (\gamma^{-1}\partial^{\mu}\gamma,\gamma^{-1}\partial_{\mu}\gamma)-\\
@@
 \end{equation*}
-We denote by $\mathcal{G}_{i}$ the generator of infinitesimal transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$.
-We normalize additional $\left(\dim\gf\right)$-dimensional Brownian motion as $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
-The generator of field transformation is equal to
+Напомним, что через  $\mathcal{G}_{i}$ мы обозначили  генераторы инфинитезимальных преобразований примарных $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$.
+Нормируем дополнительное $\left(\dim\gf\right)$-мерное Броуновское движение следующим образом: $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
+Тогда генератор преобразования поля равен
 \begin{equation}
   \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right).
-\label{eq:3}
+\label{eq:179}
 \end{equation}
-So we have fixed $A$-gauge by allowing random walk only in direction orthogonal to subalgebra $\af$.
+То есть мы фиксировали  $A$-калибровку, разрешив случайное блуждание только в направлении, ортогональном подалгебре $\af$.
 
- Ito formula  gives us an expression for the differential of $\mathcal{F}$ which should be zero due to martingale condition:
+Формула Ито дает нам выражение для дифференциала $\mathcal{F}$, который равняется нулю в силу условия мартингала:
 \begin{multline}
@@
       \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}\\=0
-\label{eq:8}
+\label{eq:180}
 \end{multline}
-Substituting  definition \eqref{eq:3} we get 
+Подставляя определение \eqref{eq:179}, мы получаем
 \begin{equation}
@@
       \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0,
-  \label{eq:4}
+\label{eq:181}
 \end{equation}
-with
+где
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-This equation is equivalent to the following algebraic condition on the boundary state $\varphi(0)\left|0\right>$:
+Это равенство эквивалентно следующему алгебраическому условию на граничное состояние $\varphi(0)\left|0\right>$:
 \begin{multline}
-  \label{eq:7}
+\label{eq:182}
   \left<0\left|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})\right.\right.\\
@@
 \end{multline}
-Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that 
+Так как набор  $\{\phi_{i}\}$ состоит из произвольных примарных полей, мы заключаем, что 
 \begin{multline}
+\label{eq:126}
 |\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
@@
 \end{multline}
-is a null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in a coset theory commutation relations of full chiral algebra are
+является нулевым состоянием.
+Теперь мы можем подействовать на  $\psi$ повышающими операторами и получить уравнения на  $\kappa,\tau$.
+Так как в  coset-моделях коммутационные соотношения полной киральной алгебры даются выражением
 \begin{equation}
-  \label{eq:18}
+\label{eq:183}
 \begin{array}{ll}
@@
 \end{equation}
- it is more convenient to act with $L_{2}^{\gf}$ and $\left(L_{1}^{\gf}\right)^{2}$. 
- Applying $L_{2}^{\gf}$ we get
+для нас более удобно действовать операторами $L_{2}^{\gf}$ и $\left(L_{1}^{\gf}\right)^{2}$. 
+Применение оператора $L_{2}^{\gf}$ дает
 \begin{equation*}
@@
 \end{equation*}
-We use $L_{0} \varphi_{(\mu,\nu)}=h_{(\mu,\nu)} \varphi_{(\mu,\nu)}$, with the conformal weight  $h_{(\mu,\nu)}= \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k x_{e}+h^{\vee}_{\af})}\right)$ and the central charge $c=\frac{k\dim \gf}{k+h^{\vee}_{\gf}}-\frac{x_{e}k\dim \af}{x_{e} k+h^{\vee}_{\af}}$.
-This leads to the relation on $\kappa,\tau$:
+Здесь мы воспользовались тем, что $L_{0} \varphi_{(\mu,\nu)}=h_{(\mu,\nu)} \varphi_{(\mu,\nu)}$, с конформным весом  $h_{(\mu,\nu)}= \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k x_{e}+h^{\vee}_{\af})}\right)$, а центральный заряд равен $c=\frac{k\dim \gf}{k+h^{\vee}_{\gf}}-\frac{x_{e}k\dim \af}{x_{e} k+h^{\vee}_{\af}}$.
+В результате получаем соотношение на $\kappa,\tau$:
 \begin{equation}
-  \label{eq:28} (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0.
+ (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0.
+ \label{eq:184}
 \end{equation}
-The second relation appears as a result of the $L_{1}^{\gf}$-action:
+Второе уравнение получается в результате действия $L_{1}^{\gf}$:
 \begin{equation}
-  \label{eq:21}
+\label{eq:185}
  -12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
@@
 \end{equation}
- where $C_{\mu}=(\mu,\mu+2\rho)$ and $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ are the eigenvalues of the quadratic Casimir operators $\sum_{a}t^{a}t^{a}$ and $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ of Lie algebras $\gf$ and $\af$.
-Relations \eqref{eq:28},\eqref{eq:21} are the necessary conditions for CFT correlation functions to be SLE martingales.
+здесь $C_{\mu}=(\mu,\mu+2\rho)$ и $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ -- это собственные значения квадратичных операторов Казимира $\sum_{a}t^{a}t^{a}$ и $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ алгебр Ли $\gf$ и $\af$.
+Равенства \eqref{eq:183},\eqref{eq:185} представляют собой необходимые условия того, чтобы корреляционные функции в coset-модели конформной теории поля являлись мартингалами по отношению к эволюции Шрамма-Левнера.
 
-From equations \eqref{eq:28},\eqref{eq:21} we immediately get $\kappa,\tau$ for each pair $(\mu,\nu)$ of $\gf$ and $\af$-weights.
+Из уравнения  \eqref{eq:183},\eqref{eq:185} мы сразу получаем значения  $\kappa,\tau$ для каждой пары весов $(\mu,\nu)$ алгебр $\gf$ и $\af$.
 
-\subsubsection{Examples}
+\subsubsection{Примеры}
 \label{sec:examples-1}
@@
 Заметим, что $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
+Как известно,  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset модель эквивалентна  $Z_{N}$-парафермионам \cite{difrancesco1997cft}.
 %%We label weights by Dynkin labels, so $J^{3}_{0}\phi_{(\mu,\nu)}=\frac{\mu}{2} \phi_{(\mu,\nu)}$.
+Примарные поля нумеруются парами весов $(\mu,\nu)$, которые мы будем задавать индексами Дынкина $(k,l)$.
 
@@
   \label{eq:160}
-  c=\frac{2(k-1)}{k+2}
+  c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2},
 \end{equation}
+а конформный вес примарного поля с весами, заданными индексами Дынкина $(k,l)$,  равен $h_{(k,l)}=\frac{k(k+2)}{4(N+2)}-\frac{l^{2}}{4N}$.
 
-As an example consider  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset models which are equivalent to $Z_{N}$-parafermions.
-The central charge is $c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2}$.
-Conformal weights of primary fields with Dynkin indeces $(k,l)$ are $h_{(k,l)}=\frac{k(k+2)}{4(N+2)}-\frac{l^{2}}{4N}$.
+Случай  $N=2$, $c=\frac{1}{2}$ соответствует модели Изинга.
+В этом случае у нас есть два нетривиальных примарных поля с конформными весами $h_{(2,0)}=1/2, h_{(1,1)}=1/16$.
+Подставляя поле $\varphi_{(2,0)}$ в выражения (\ref{eq:183},\ref{eq:185}) мы получаем уравнения: $3\kappa-9+4\tau =0;\quad -3+\kappa+4\tau=0$ с решением $\kappa=3, \tau=0$.
+Для поля  $\varphi_{(1,1)}$ получаются соотношения $3\kappa-16+64\tau=0,\quad -64+9\kappa + 64\tau=0$ и значения параметров $\kappa=16/3, \tau=0$.
+То есть в случае модели Изинга нет необходимости в дополнительном случайном блуждании, а значения параметра эволюции Шрамма-Лёвнера $\kappa$ совпадают с известными результатами \cite{schramm2006conformally}.
 
-Case $N=2$, $c=\frac{1}{2}$ corresponds to the Ising model, we have two non-trivial primary fields with conformal weights $h_{(2,0)}=1/2, h_{(1,1)}=1/16$.
-Substituting the field $\varphi_{(2,0)}$ into equations (\ref{eq:28},\ref{eq:21}) we get: $3\kappa-9+4\tau =0;\quad -3+\kappa+4\tau=0$.
-The solution is $\kappa=3, \tau=0$.
-For the field $\varphi_{(1,1)}$ the relations are $3\kappa-16+64\tau=0,\quad -64+9\kappa + 64\tau=0$, $\kappa=16/3, \tau=0$.
-So we have no additional motion for the Ising model and two possible values for SLE parameter $\kappa$  coinciding with the well-known results \cite{schramm2006conformally}.
+При  $N=3$ центральный заряд парафермионной модели равен $c=\frac{4}{5}$.
+Конформные веса принимают значения $h_{(0,0)}=0$, $h_{(0,2)}=h_{(0,-2)}=\frac{2}{3}\; \mathrm{mod}\; 1$, $h_{(2,0)}=\frac{2}{5}$, $h_{(2,2)}=h_{(2,-2)}=\frac{1}{15}$.
+Соответствующие значения параметров  $\kappa,\tau$ равны: $(\frac{208}{25},\frac{242}{225}), (\frac{10}{3},0),(\frac{80}{19},\frac{14}{171})$.
+Как было указано в работе \cite{santachiara2008sle}, поле  $\varphi_{(2,0)}$ с конформным весом  $h_{(2,0)}=\frac{2}{5}$ образует  $Z_{3}$-синглет, так что дополнительное случайное блуждание не возникает и  $\tau=0$.
+Вид уравнения (\ref{eq:182}) аналогичен полученному в работе \cite{santachiara2008sle} для парафермионов, но нормировка параметра $\tau$ отличается.
 
-For $N=3$ the parafermionic model central charge is $c=\frac{4}{5}$.
-Conformal weights are $h_{(0,0)}=0$, $h_{(0,2)}=h_{(0,-2)}=\frac{2}{3}\; \mathrm{mod}\; 1$, $h_{(2,0)}=\frac{2}{5}$, $h_{(2,2)}=h_{(2,-2)}=\frac{1}{15}$.
-The corresponding values of $\kappa,\tau$ are: $(\frac{208}{25},\frac{242}{225}), (\frac{10}{3},0),(\frac{80}{19},\frac{14}{171})$.
-As it  was mentioned in \cite{santachiara2008sle} the field $\varphi_{(2,0)}$ with the conformal weight $h_{(2,0)}=\frac{2}{5}$ constitutes the $Z_{3}$-singlet, so  an additional random walk does not appear and $\tau=0$.
-The form of equations (\ref{eq:7}) is similar to that of \cite{santachiara2008sle}, but the normalization of $\tau$ differs.
-
-It is easy to see that for the $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset realization of minimal unitary models with $c=\frac{3N}{N+2}+1-\frac{3(N+1)}{N+3}=1-\frac{6}{(N+2)(N+3)}$ the system of equations (\ref{eq:28},\ref{eq:21}) is always consistent for $\tau=0$ and we get a standard connection between the SLE-parameter $\kappa$ and the central charge $c=\frac{(6-\kappa)(3\kappa-8)}{2\kappa}$.
+Легко видеть, что для реализации минимальных унитарных моделей в виде  $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset моделей с центральными зарядами $c=\frac{3N}{N+2}+1-\frac{3(N+1)}{N+3}=1-\frac{6}{(N+2)(N+3)}$ система уравнения (\ref{eq:183},\ref{eq:185}) всегда совместна при  $\tau=0$ и мы получаем стандартную для минимальных моделей связь между параметром эволюции Шрамма-Левнера $\kappa$ и центральным зарядом $c=\frac{(6-\kappa)(3\kappa-8)}{2\kappa}$.
 
@@
 
-In  \cite{bettelheim2005stochastic} a connection between WZNW-models and Schramm-Loewner evolution with additional Brownian motion on group manifold was established.
-The authors also stated a problem of a possible connection of SLE parameters for martingales in WZNW, coset and minimal models.
-In present letter we used the method proposed in \cite{alekseev2010sle} to obtain necessary conditions on SLE martingales.
-This method allowed us to compare our results with parafermionic results presented in \cite{santachiara2008sle,picco2008numerical}.
+Связь между  ВЗНВ-моделями и эволюцией Шрамма-Левнера с дополнительным броуновским движением на групповом многообразии была установлена в работе    \cite{bettelheim2005stochastic}.
+Авторы этой работы поставили задачу установления связи между параметрами эволюции Шрамма-Лёвнера для мартингалов в ВЗНВ, coset  и минимальных моделях конформной теории поля.
+Мы воспользовались методом, предложенным в работе \cite{alekseev2010sle} чтобы получить необходимые условия на мартингалы.
+Этот метод позволил нам сравнить наши результаты с результатами для парафермионов из работ \cite{santachiara2008sle,picco2008numerical}.
 
-The coset structure of minimal models is manifest in field theory perturbed by an external magnetic field \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
-This theory is supported by experimental data \cite{coldea2010quantum}.
-Relations between correlation functions in coset theory and SLE observables can be a starting point in studies of domain walls in lattice models away from the  critical point.
+Реализация минимальных моделей посредством  coset-конструкции полезна при рассмотрении теории, возмущенной внешним магнитным полем \cite{fateev1990conformal,eguchi1989deformations,hollowood1989rational}.
+Эта модель подтверждается экспериментальными данными недавней работы \cite{coldea2010quantum}.
+Соотношения между корреляционными функциями в  coset-модели и наблюдаемыми эволюции Шрамма-Лёвнера могут выступить стартовой точкой в изучении доменных стенок в решеточных моделях вдали от критической точки.
 
-Massive perturbations of $G/A$-coset theory are realized as an affine Toda field theory and are classified by simple roots of the Lie algebra $\gf$.
-Affine Toda field theory can be obtained by adding perturbation term to  the action (\ref{eq:24}):
+Массивные возмущения  $G/A$-coset модели могут быть реализованы как аффинная теория поля Тоды.
+Они классифицируются простыми корнями алгебры Ли $\gf$.
+Действие аффинной теории Тоды можно получить добавлением возмущающего члена в действие (\ref{eq:178}):
 \begin{equation}
@@
 \end{equation}
-where $T,\bar T\in \gf$ are specially chosen Lie algebra elements \cite{bakas1996lagrangian,hollowood1995massive,park1994deformed}. 
-The perturbation leads to an insertion of certain primary field in all the correlation functions  \cite{hollowood1989rational}.
-It was shown that massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off,bauer2009off}.
-The question is whether the interaction of the perturbing primary field with the $\tau$-term of the equation (\ref{eq:4}) leads to the same contribution as the addition of a massive drift to SLE.
+где $T,\bar T\in \gf$ -- специальным образом выбранные элементы алгебры Ли \cite{bakas1996lagrangian,hollowood1995massive,park1994deformed}.
+Такое возмущение ведет к вставке некоторого примарного поля во все корреляторы \cite{hollowood1989rational}.
+Недавно было показано, что массивная эволюция Шрамма-Лёвнера вне критической точки содержит дополнительный член в движущем броуновском движении, который соответствует сносу \cite{makarov2010off,bauer2009off}.
+Необходимо проверить, что взаимодействие возмущающего примарного поля с  $\tau$-членом уравнения (\ref{eq:181}) приводит к такому же вкладу, что и введение массивного сноса в эволюцию Шрамма-Лёвнера.
 
-In the forthcoming studies we will address this question and compare  massive perturbations of coset models with the numerical studies of domain walls in the Ising model perturbed by a random Gaussian external field \cite{stevenson2011domain}.
+В дальнейших исследованиях мы планируем ответить на данный вопрос и сравнить массивные возмущения coset-моделей с результатами численного изучения доменных стенок в модели Изинга, возмущенной случайным гауссовым полем \cite{stevenson2011domain}.
 
@@
 Описание полей в coset-моделях нетривиально ввиду идентификации полей \cite{schellekens1990field} и необходимости в разрешении фиксированных точек \cite{Fuchs:1996dd,fuchs1996resolution}, которое не обсуждалась в данной главе.
-Эти тонкости могут усложнить решение уравнений  \eqref{eq:169}, \eqref{eq:157} и аналогов уравнения \eqref{eq:170}.
+Эти тонкости могут усложнить решение уравнений  \eqref{eq:184}, \eqref{eq:185}.
 С другой стороны, использование уравнений Книжника-Замолодчикова  \cite{kogan1997knizhnik} для корреляционных функций в духе работы \cite{alekseev2010sle} приводит к матричным алгебраическим соотношениям, которые напоминают NIM-представления для граничных состояний \cite{ishikawa2003novel}.

### 2012-05-31 AffineLieAlgebras/Thesis/common.tex
Minor changes

@@
 Глава \ref{cha:CFT} является вводной.
-В ней мы даем обзор конформной теории поля, моделей Весса-Зумино-Новикова-Виттена и coset-моделей.
-Мы приводим аксиоматическую формулировку конформной теории поля, а также обсуждаем БРСТ-подход к описанию калибровочных моделей Весса-Зумино-Новикова-Виттена, приводящий к реализации coset-конструкции.
+В ней мы даем аксиоматическую формулировку конформной теории поля, описываем модели Весса-Зумино-Новикова-Виттена и coset-модели.
+Затем мы демонстрируем роль аффинных алгебр в описании этих моделей и приводим основные понятия теории представлений, использующиеся в диссертации.
+Кроме того, мы обсуждаем конформную теорию поля на области с границей, так как она оказывается связана со стохастическим описанием решеточных моделей.
 

### 2012-06-04 AffineLieAlgebras/Thesis/3.tex
Edits from paper version. Text duplication mostly fixed.

@@
 Сплинт можно использовать для получения правил ветвления.
-Мы показываем, что использование свойств сплинта  позволяет сильно упростить вычисление коэффициентов ветвления.
+Мы показываем, что использование свойств сплинта в сочетании с разложением сингулярного элемента позволяет сильно упростить вычисление коэффициентов ветвления.
 
@@
 
-Пусть $L^{\mu }$ -- вполне приводимый по отношению к  $\af$ модуль алгебры $\gf$,
-\[
-L_{\gf\downarrow \af}^{\mu }=\bigoplus\limits_{\nu \in P_{\af%
-}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
-\]
-\begin{equation}
-\pi _{\af}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\af%
-}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\af}^{\nu }\right) .
-\label{branching13}
-\end{equation}
-Для модулей, которые мы исследуем, формула Вейля для характеров $\mathrm{ch}\left(L^{\mu }\right) $ может быть записана через сингулярные элементы \cite{humphreys1997introduction}
-\[
-\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
-)-\rho },
-\]
-а именно,
-\begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
-^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
-\label{Weyl-Kac22}
-\end{equation}
-Это же верно и для подмодулей $\mathrm{ch}\left( L_{\af}^{\nu}\right) $ в уравнении (\ref{branching13})
-\[
-\mathrm{ch}\left( L_{\af}^{\nu }\right) =\frac{\Psi _{\af}^{\left(
-\nu \right) }}{\Psi _{\af}^{\left( 0\right) }}=\frac{\Psi _{\af%
-}^{\left( \nu \right) }}{R_{\af}},
-\]
-где
-\[
-\Psi _{\af}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\af%
-}}\epsilon (w)e^{w(\nu +\rho _{_{\af}})-\rho _{_{\af}}}.
-\]
-
-Применяя формулу (\ref{Weyl-Kac22}) к правилам ветвления (\ref{branching13}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu\right) }$ и $\Psi _{\af}^{\left( \nu \right) }$ :
-\begin{eqnarray}
-\frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho )-\rho }}{\prod_{\alpha \in
-\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu
-}^{(\mu )}\frac{\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{%
-\af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
-}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:171} \\
-\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\af%
-}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\af}^{\left( \nu \right) }}{R_{%
-\af}}.  \label{singular-main}
-\end{eqnarray}
-
-В работе \cite{2010arXiv1007.0318L} (см.
-главу \ref{cha:affine-lie-algebras}) было доказано, что коэффициенты ветвления $b_{\xi }^{\left(\mu\right)}$, отвечающие вложению $\af\hookrightarrow \gf$, удовлетворяют следующим рекуррентным соотношениям:
-\begin{equation}
-\begin{array}{c}
-b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\af_{\perp }}^{\mu _{\af%
-_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
-\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right. \\
-\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
-}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
-}\right) ,
-\end{array}
-\label{recurrent-rel}
-\end{equation}
-где $\afb$ -- подалгбера, задающаяся корнями  $\gf$, ортогональными ко всем корням $\af$ и $W_{\perp}$ -- подгруппа Вейля, соответствующая $\afb$,
-\begin{eqnarray}
-\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
-h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
-\label{delta-a-ort}
-\end{eqnarray}
-\begin{eqnarray}
-\widetilde{\af_{\perp }} :=\af_{\perp }\oplus \frak{h}_{\perp }
-\qquad \widetilde{\af} :=\af\oplus \frak{h}_{\perp }
-\end{eqnarray}
-и $\pi$ -- оператор проекции. Если вложение максимально, то оператор проекции становится тривиальным и соотношение (\ref{recurrent-rel}) упрощается:
-\begin{equation}
-\begin{array}{c}
-b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
-}+\right. \\
-\left. +\sum_{\gamma \in \Gamma _{\af\rightarrow \gf}}s\left(
-\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
-\end{array}
-\label{recurrent relation max}
-\end{equation}
-Рекурсия задается множеством  $\Gamma _{\af\rightarrow \gf}$, называющимся ``веер вложения''.
-Оно определяется как носитель $\left\{ \xi \right\} _{\af\rightarrow \gf}$ для коэффициентоной функции $s(\xi )$
-\[
-\left\{ \xi \right\} _{\af\rightarrow \gf}:=\left\{ \xi \in P_{%
-\af}|s(\xi )\neq 0\right\}
-\]
-возникающей в разложении
-\begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\af}^{+}}\left( 1-e^{
--\alpha }\right) =-\sum_{\gamma \in P_{\af}}s(\gamma )e^{-\gamma };\quad
-\label{product}
-\end{equation}
-
-Теперь мы приведем два определения, введенные в работе \cite{richter2008splints}
+Приведем два определения, введенные в работе \cite{richter2008splints}
 
 \begin{definition}
-Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$. Тогда отображение $\phi $ -- ``вложение''
+Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$. Рассмотрим отображение
 \begin{equation}
@@
 \Delta _{0}\hookrightarrow \Delta , \\
-P_{0}\hookrightarrow P,
+P_{0}\hookrightarrow P.
 \end{array}
@@
 \end{equation}
-если \newline
+Оно называется ``вложением'', если \newline
 \noindent (a) оно вкладывает $\Delta _{0}$ в $\Delta $, и \newline
@@
 
-В случае инъективного сплинта второй стебель $\Delta _{\sfr}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (\ref{product}) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$.
+В случае инъективного сплинта второй стебель $\Delta _{\sfr}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (аналогично формуле (\ref{eq:142})) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$.
 Обозначим через $\Delta_{\mathfrak{s}0}$ кообраз второго вложения $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$.
@@
 
-В случае инъективного сплинты мы можем сказать, что подалгебра $\af\hookrightarrow \gf$ расщепляется $\Delta$ (и назовем $\af$ ``расщепляющей подалгеброй'' алгебры $\gf$).
+В случае инъективного сплинта мы можем сказать, что подалгебра $\af\hookrightarrow \gf$ расщепляется $\Delta$ (и назовем $\af$ ``расщепляющей подалгеброй'' алгебры $\gf$).
 Сплинты были классифицированы в работе \cite{richter2008splints}  (см.
@@
 
-Вернемся к соотношению  (\ref{singular-main}) и домножим обе стороны на  $R_{\af}$:
+Вернемся к соотношению (\ref{eq:124}). В данном случае операция проекции тривиальна, поэтому после умножения обеих сторон на  $R_{\af}$ получаем:
 \begin{equation}
@@
 
-Для неприводимого модуля старшего веса $L_{\gf}^{\mu }$ сингулярный элемент $\Psi _{\gf}^{\left( \mu \right) }$ -- это элемент $\mathcal{E}$, соответствующий сдвинутой орбите группы веса $\left( \mu +\rho\right) \in P^{+}$, со знаковой функцией $\epsilon \left( w\right) $.
+Для неприводимого модуля старшего веса $L_{\gf}^{\mu }$ сингулярный элемент $\Psi _{\gf}^{\left( \mu \right) }$ -- это элемент $\mathcal{E}$, соответствующий сдвинутой орбите группы Вейля веса $\left( \mu +\rho\right) \in P^{+}$, со знаковой функцией $\epsilon \left( w\right) $.
 Удобно использовать также не сдвинутые сингулярные элементы
@@
 $\af_{1}\subset \gf$ --  ее редуктивная подалегебра того же ранга, такая, что
-$\Delta_{\af}\equiv\Delta_{1}\subset\Delta$ и $Q_{\af}\subset Q$, где $Q$ -- корневая решетка. Неприводимые модули старшего веса алгебр 
-$\gf$ и $\af$ мы обозначаем через $L^{\mu}$ и $L^{\nu}_{\af}$. Формула Вейля для характеров неприводимых модулей имеет вид
-$\mathrm{ch}L^{\mu}=\frac{\Psi^{(\mu)}}{\prod_{\alpha\in\Delta}(1-e^{-\alpha})}$,
-где  $\Psi^{(\mu)}=\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}$ -- сингулярный элемент модуля, а$W$ -- группа Вейля алгебры $\gf$. Формальный характер неприводимого модуля допускает разложение
-\begin{equation}
-  \label{eq:133}
-  \mathrm{ch} L^{\mu}=\sum_{\nu\in P_{\af}} b^{\mu}_{\nu} \mathrm{ch} L^{\nu}_{\af},
-\end{equation}
-где $P$, $P_{\af}$ -- весовые решетки $\gf$ и $\af$. Мы хотим рассмотреть аффинное расширение данной конструкции:
+$\Delta_{\af}\equiv\Delta_{1}\subset\Delta$ и $Q_{\af}\subset Q$, где $Q$ -- корневая решетка. Мы хотим рассмотреть аффинное расширение данной конструкции:
 $\gf\subset\gfh,\; \af\subset\afh$, $\afh\subset\gfh$,
@@
 \end{multline}
+Введем тета-функции \cite{kac1984infinite}:
+$$\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in Q_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}.$$
 
-Воспользуемя специализацией \cite{kac1988modular,kac1984infinite,kac1990idl} и определением $\eta$-функции Дедекинда
+Воспользуемся специализацией \cite{kac1988modular,kac1984infinite,kac1990idl} и определением $\eta$-функции Дедекинда
 $\eta(\tau)=q^{1/24}\prod_{n=1}^{\infty}(1-q^{n})$, где
-$q=e^{2\pi i \tau}$, чтбы переписать предыдущее равенство в виде соотношения на тета-функции $$\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in Q_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$$:
+$q=e^{2\pi i \tau}$, чтобы переписать предыдущее равенство в виде следующего соотношения на тета-функции:
+
 \begin{multline}

### 2012-06-04 AffineLieAlgebras/Thesis/1.tex
Edits from paper version. Text duplication mostly fixed.

@@
 
-В следующем разделе \ref{sec:intro-simple-lie-algebras} мы определяем аффинные алгебры Ли и приводим основные определения в теории представлений.
-Заодно мы фиксируем обозначения.
-Затем в разделе \ref{sec:branching} мы выводим формулы разложения, основывающиеся на аномальных коэффициентах ветвления и описываем алгоритм редукции интегрируемых модулей старшего веса $L_{\mathfrak{g}}$ по отношению к редуктивной подалгебре  $\mathfrak{a}\subset \mathfrak{g}$ (см.
-секцию \ref{sec:algorithm}).
+В разделе \ref{sec:branching} мы выводим формулы разложения, основывающиеся на аномальных коэффициентах ветвления и описываем алгоритм редукции интегрируемых модулей старшего веса $L_{\mathfrak{g}}$ по отношению к редуктивной подалгебре  $\mathfrak{a}\subset \mathfrak{g}$.
 В разделе \ref{sec:branching-examples} мы представляем различные примеры применения алгоритма для конечномерных (\ref{sec:finite-dimens-lie}) и аффинных алгебр Ли и обсуждаем их роль в моделях конформной теории поля (\ref{sec:phys-appl}).
@@
 В следующей главе \ref{cha:BGG} мы показываем связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
-Реализация алгоритма на языке {\it Mathematica} и дополнительные примеры машинных вычислений описаны в главе  \ref{cha:computational-methods}.
+Реализация алгоритма на языке {\it Mathematica} и дополнительные примеры машинных вычислений описаны в разделе \ref{cha:computational-methods} главы \ref{cha:applications}.
 
@@
 к $\af$,
-\begin{eqnarray*}
+\begin{eqnarray}
+\label{delta-a-ort}
 \Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\gf}|
@@
 }^{+}|\forall h \in \hf_{\af};  \beta^{+}\left(h \right)=0  \right\} .
-\end{eqnarray*}
+\end{eqnarray}
 Обозначим через $W_{\afb}$ подгруппу группы Вейля $W$, порожденную отражениями $w _{\beta }$, соответствующими корням $\beta \in \Delta _{\afb}^{+}$ .
@@
 \end{equation*}
+Кроме того, мы будем пользоваться аналогичным определением
+\begin{eqnarray}
+\label{eq:136}
+\mu _{\tilde \af}\left( u\right) :=\pi _{\tilde \af}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb},\\
+\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}.
+\end{eqnarray}
+
 Чтобы упростить вид соотношений мы будем опускать значок "$\circ$" при записи проекций весов.
@@
 
-Теперь покажем, что формула Вейля-Каца для характеров (в терминах сингулярных элементов) представляет собой частный случай более общего соотношения:
+Покажем, что формула Вейля-Каца для характеров (в терминах сингулярных элементов) представляет собой частный случай более общего соотношения:
 
@@
 \end{equation*}
-Эти выражения обеспечивают факторизацию аномального элемента  $\Psi^{\mu}$ и мы видим, что они содержат комбинации сингулярных элементов $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ модулей $L_{\widetilde{\afb}}^{\eta }$ подалгебры  $\widetilde{\afb}$:
+Эти выражения обеспечивают факторизацию сингулярного элемента  $\Psi^{\mu}$ и мы видим, что они содержат комбинации сингулярных элементов $\Psi _{\widetilde{\af_{\perp }}}^{\eta }$ модулей $L_{\widetilde{\afb}}^{\eta }$ подалгебры  $\widetilde{\afb}$:
 \begin{equation*}
@@
 \label{tab:diagrams} \noindent \centering{\
-\begin{tabular}{|l|l|l|l|}
+\begin{tabular}{|l|l|l|}
 \hline
-$\gf$ & Расширенная диаграмма $\gf$ & Диаграммы подалгебр $\af,\; \afb$ &  \\ \hline
+$\gf$ & Расширенная диаграмма $\gf$ & Диаграммы подалгебр $\af,\; \afb$   \\ \hline
 $A_n$ & \includegraphics{table1_1(l)} & \includegraphics{table1_1(r)}
-&  \\ \hline
+  \\ \hline
 $C_n$ & \includegraphics{table1_3(l)} & \includegraphics{table1_3(r)}
-&  \\ \hline
+  \\ \hline
 $D_n$ & \includegraphics{table1_4(l)} & \includegraphics{table1_4(r)}
-&  \\ \hline
+  \\ \hline
 \end{tabular}
@@
 
-\item Вычислить аномальные коэффициенты ветвления используя рекуррентное соотношение (\ref{recurrent-relation}) и выбрать среди них те, которые соответствуют весам в главной камере Вейля $\overline{C_{\af}}$.
+\item Вычислить сингулярные коэффициенты ветвления используя рекуррентное соотношение (\ref{recurrent-relation}) и выбрать среди них те, которые соответствуют весам в главной камере Вейля $\overline{C_{\af}}$.
 \end{enumerate}
@@
 $\mathrm{dim}(L^{\left[0,1,0,2\right]})=2772$.
-В данном случае дефект не тривиален, $\mathcal{D}_{\af_{\perp }}=-2\left( e_1 + e_2 \right)$, тогда как $\hf_{\bot}=0$. Среди сингулярных весов есть 
+В данном случае дефект не равен нулю, $\mathcal{D}_{\af_{\perp }}=-2\left( e_1 + e_2 \right)$, тогда как $\hf_{\bot}$ тривиальна. Среди сингулярных весов есть 
 48 векторов со свойством $\left\{ \mu _{\afb}\left( u\right) =\pi _{\af_{\perp }}\left[ u(\mu +\rho)-\rho \right] -\mathcal{D}_{\afb}\in \overline{C_{\afb}}\right\} $.

### 2012-06-04 AffineLieAlgebras/Thesis/2.tex
Edits from paper version. Text duplication mostly fixed.

@@
 L^{\left(\mu \right) }$ и ортогональной подалгебры  $\af_{\bot }$ мы рассматриваем сингулярный элемент $\Psi ^{\left( \mu \right) }$ (числитель в формуле Вейля для характеров $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
-\mu \right) }}{\Psi ^{\left( 0\right) }}$, см., например,  \cite
-{humphreys1997introduction}) и знаменатель Вейля $\Psi _{\af_{\bot
+\mu \right) }}{\Psi ^{\left( 0\right) }}$, см. раздел \ref{sec:high-weight-modul}) и знаменатель Вейля $\Psi _{\af_{\bot
   }}^{\left( 0\right) }$ для ортогонального партнера. Ниже мы показываем, что элемент  $\Psi _{\gf%
@@
 \widetilde{\frak{b}_{\perp }}$ уже не является подалгеброй в $\gf$, а оказывается сжатием $\widetilde{\afb}$.
-
-Некоторые общие свойства предложенного разложения формулируются в терминах  формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''.
-Использование этого инструмента позволило сформулировать простой и явный алгоритм для вычисления правил ветвления, подходящий для произвольной (максимальной или не максимальной) подалгебры в аффинной алгебре Ли \cite{2010arXiv1007.0318L}.
 
@@
 
-\subsection{Ортогональная подалгебра}
-
-Пусть  $\frak{h}_{\frak{a}}$ -- подалгебра Картана в  $\mathfrak{g}$. Для  $\mathfrak{a}\hookrightarrow \frak{g}$ введем ``ортогонального партнера''  $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$.
-
-Рассмотрим корневое подпространство  $\frak{h}_{\perp \frak{a}}^{\ast }$, ортогональное к $\frak{a}$,
-\begin{equation*}
-\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
-h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} ,
-\end{equation*}
-и корни  $\frak{g}$ (соответственно, положительные корни),  ортогональные к $\frak{a}$,
-\begin{eqnarray}
-\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
-h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
-\label{delta a ort} \\
-\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
-}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
-\notag
-\end{eqnarray}
-Обозначим символом  $W_{\frak{a}_{\perp }}$ подгруппу  $W$, порожденную отражениями  $w_{\beta }$ с корнями  $\beta \in \Delta_{\frak{a}_{\perp}}^{+}$.
-Корневая подсистема  $\Delta _{\frak{a}_{\perp }}$ определяет подалгебру  $\frak{a}_{\perp }$, имеющую подалгебру Картана $\frak{h}_{\frak{a}_{\perp }}$.
-Пусть
-\begin{equation*}
-\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
-}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
-h\right) =0\right\};
-\end{equation*}
-выделим в  $\frak{g}$  подалгебры
-\begin{eqnarray}
-\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp },
-\qquad
-\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
-\end{eqnarray}
-Заметим, что  $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ в общем случае не является подалгеброй в $\mathfrak{g}$.
-
-Для подалгебр Картана имеет место разложение
-\begin{equation}
-\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
-\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
-\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
-\frak{h}_{\frak{a}}.
-\end{equation}
-Рассмотрим векторы Вейля  $\rho _{\frak{a}}$ и $\rho _{\frak{a}_{\perp}} $, соответствующие  $\frak{a}$ и $\frak{a}_{\perp }$.
-Введем так называемые ``дефекты'' вложения  $\mathcal{D}_{\frak{a}}$ и $\mathcal{D}_{\frak{a}_{\perp }}$:
-\begin{equation}
-\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho , \qquad
-\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
-_{\perp }}\rho .  \label{defect ort}
-\end{equation}
-Для  $\mu \in P^{+}$ рассмотрим связанные веса  $\left\{\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ и их проекции на $h_{\frak{a}_{\perp }}^{\ast }$, дополнительно сдвинутые на вектор дефекта $-\mathcal{D}_{\frak{a}_{\perp }}$:
-\begin{equation*}
-\mu _{\frak{a}_{\perp }}\left( w\right) :=\pi _{\frak{a}_{\perp }}\left[
-w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad w\in W.
-\end{equation*}
-
-Среди весов  $\left\{ \mu _{\frak{a}_{\perp
-}}\left( w\right) |w\in W\right\} $ всегда можно выбрать те, которые попадают в фундаментальную камеру $\overline{C_{\frak{a}_{\perp }}}$.
-Пусть $U$ -- множество представителей $u$ классов  $W/W_{\frak{a}_{\perp }}$, таких что
-\begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
-\overline{C_{\frak{a}_{\perp }}}\right\} \quad .  \label{U-def1}
-\end{equation}
-Тогда можно выделить подмножества:
-\begin{equation}
-\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
-\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}%
-_{\perp }},\quad u\in U,  \label{mu-a}
-\end{equation}
-и
-\begin{equation}
-\mu _{\frak{a}_{\perp }}\left( u\right) :=\pi _{\frak{a}_{\perp }}\left[
-u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U.
-\label{mu-a-tilda}
-\end{equation}
-
+Воспользуемся введенным в главе \ref{cha:affine-lie-algebras} понятием ``ортогонального партнера''  $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$ для подалгебры   $\mathfrak{a}\hookrightarrow \frak{g}$.
 Заметим, что подалгебра  $\mathfrak{a}_{\bot}$ по определению регулярна, так как она построена на подмножестве корней алгебры $\mathfrak{g}$.
@@
 
-Теперь мы выполним разложение сингулярного элемента  $\Psi ^{\left(\mu \right) }$ на сингулярные элементы модулей ортогонального партнера:
+Теперь мы выполним разложение сингулярного элемента  $\Psi ^{\left(\mu \right) }$ на сингулярные элементы модулей ортогонального партнера.
+Это разложение в целом аналогично разложению в Лемме \ref{lemma}, однако в данном случае его составляющими являются сингулярные элементы ортогонального партнера $\afb$.
 
@@
 Тогда элемент  $\Psi ^{\left( \mu \right) }$ может быть разложен в сумму по  $u\in U$ (см.
-(\ref{U-def1})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
+(\ref{U-def})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
 $\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
@@
 \end{equation}
-Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect ort}), чтобы упростить первую строку в формуле (\ref{sing-decomp-2}):
+Используем дефект $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect-perp}), чтобы упростить первую строку в формуле (\ref{sing-decomp-2}):
 \[
@@
 
-В предыдущей главе (и в нашей работе \cite{2010arXiv1007.0318L}) разложение, аналогичное формуле (\ref{singular main}), было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
-\begin{equation}
-\begin{array}{c}
-k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
-\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
-_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
-\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right.  \\
-\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
-}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
-}\right) .
-\end{array}
-\label{recurrent rel}
-\end{equation}
-Рекурсия задается множеством  $\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}$, которое носит название веера вложения.
-Это множество определяется как носитель  $\left\{ \xi \right\}_{\frak{a}\rightarrow \frak{g}}$  коэффициентной функции $s(\xi )$
-\begin{equation*}
-\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{g}}:=\left\{
-\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\},
-\end{equation*}
-возникающей в разложении 
-\begin{equation}
-\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
-_{\widetilde{\frak{a}}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
-_{\frak{a}}(\pi _{\widetilde{\frak{a}}}\alpha )}=-\sum_{\gamma \in P_{%
-\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma }.\quad
-\end{equation}
-Веса из множества $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
-g}}$ сдвигаются на $\gamma _{0}$ -- младший вектор в $\left\{ \xi
-\right\} $, и исключается нулевой элемент:
-\begin{equation}
-\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}=\left\{ \xi -\gamma
-_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
-\end{equation}
+В предыдущей главе (и в нашей работе \cite{2010arXiv1007.0318L}) разложение, аналогичное формуле (\ref{singular main}), было использовано для построения рекуррентных соотношений (\ref{recurrent-relation}) для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$.
 
-Рекуррентное соотношение (\ref{recurrent rel}) первоначально использовалось для описания ветвления интегрируемых модулей.
+Рекуррентное соотношение (\ref{recurrent-relation}) первоначально использовалось для описания ветвления интегрируемых модулей.
 Заметим, что существует важный класс модулей, которые также могут быть редуцированы при помощи веера вложения -- это модули Верма.
@@
 \begin{proof}
-Подалгебра  $\mathfrak{a}_{\bot }$ регулярна и редуктивна по определению  (\ref{delta a ort}). Рассмотрим её знаменатель Вейля   $R_{\frak{a}_{\perp }}:=\prod_{\alpha \in \Delta _{\frak{a}%
+Подалгебра  $\mathfrak{a}_{\bot }$ регулярна и редуктивна по определению  (\ref{delta-a-ort}). Рассмотрим её знаменатель Вейля   $R_{\frak{a}_{\perp }}:=\prod_{\alpha \in \Delta _{\frak{a}%
 _{\perp }}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}%
@@
 \end{equation*}
-Подставляя это выражение в формулу (\ref{char in gen verma mod}) и используя определения  (\ref{mu-a},\ref{mu-a-tilda}) и (\ref{defect ort}), мы восстанавливаем стандартное разложение Вейля-Верма для характера:
+Подставляя это выражение в формулу (\ref{char in gen verma mod}) и используя определения  (\ref{eq:136}) и (\ref{defect-perp}), мы восстанавливаем стандартное разложение Вейля-Верма для характера:
 \begin{equation*}
@@
 \begin{statement}
-Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра  $\afb\hookrightarrow \frak{g}$ ортогональна редуктивной подалгебре $\frak{a}\hookrightarrow \frak{g}$.
-Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\afb$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к подалгебре $\frak{a}_{\perp }$, так и правила ветвления $L^{\mu }$ по отношению к $\frak{a}$ .
+Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра  $\afb\hookrightarrow \frak{g}$ является ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$.
+Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\afb$, так и правила ветвления $L^{\mu }$ по отношению к $\afb$, так и правила ветвления $L^{\mu }$ по отношению к $\af$ .
 \end{statement}
@@
 }}\left( u\right) $ и $\mathcal{D}_{\frak{a}_{\perp }}$ заданы как в Лемме \ref{Psi-decomp-lemma}, $%
-u\in U$ определено формулой (\ref{U-def1}). В результате получим элементы фильтрующей последовательности (\ref{resolution sequence}).
+u\in U$ определено формулой (\ref{U-def}). В результате получим элементы фильтрующей последовательности (\ref{resolution sequence}).
 
@@
 Ветвление  $L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu
-\in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$  определяется веером вложения  $\Gamma _{\frak{a}\rightarrow \frak{g}}$ и соотношением (\ref{recurrent rel}), которое дает нам коэффициенты  $k_{\xi
+\in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$  определяется веером вложения  $\Gamma _{\frak{a}\rightarrow \frak{g}}$ и соотношением (\ref{recurrent-relation}), которое дает нам коэффициенты  $k_{\xi
 }^{\left( \mu \right) }$, а значит определяет и  $b_{\nu }^{\left( \mu \right) }$, так как  $b_{\nu }^{\left( \mu \right) }=k_{\nu }^{\left( \mu
@@
 g}\downarrow \widetilde{\frak{a}}}^{\mu }\right) }=k_{\xi }^{\left( \mu
-\right) }e^{\xi }$. В нашем случае представители $u$ в рекуррентном соотношении (\ref{recurrent rel}) определяются весом $\xi $ однозначно:
+\right) }e^{\xi }$. В нашем случае представители $u$ в рекуррентном соотношении (\ref{recurrent-relation}) определяются весом $\xi $ однозначно:
 \begin{equation*}

### 2012-06-04 AffineLieAlgebras/Thesis/review.tex
Translation in last chapter is completed. Printed as a booklet
Minor changes
Edits from paper version. Text duplication mostly fixed.

@@
 
-\chapter{Конформная теория поля и алгебры Ли}
+\chapter{Конформная теория поля и аффинные алгебры Ли}
 \label{cha:CFT}
@@
   \begin{split}
-    \phi_{\Delta,\bar \Delta}(z,\bar z)\underset{
+    \phi_{h,\bar h}(z,\bar z)\underset{
       \genfrac{}{}{0pt}{}{z\to w(z)}
@@
     }
-    {\longrightarrow} \left(\frac{dw}{dz}\right)^{\Delta}\left(\frac{d\bar w}{d\bar
-        z}\right)^{\bar\Delta}\phi_{\Delta,\bar \Delta}(w(z),\bar w(\bar z))\\
+    {\longrightarrow} \left(\frac{dw}{dz}\right)^{h}\left(\frac{d\bar w}{d\bar
+        z}\right)^{\bar h}\phi_{h,\bar h}(w(z),\bar w(\bar z))\\
     L_n \phi=0,\quad n>0\\
-    L_0 \phi=\Delta \phi\\
+    L_0 \phi=h \phi\\
   \end{split}
 \end{equation}
-$\Delta, \bar \Delta$ называются конформными размерностями поля.
+$h, \bar h$ называются конформными весами поля.
 Все остальные поля называются вторичными и получаются из примарного действием операторов $L_{-n}$:
@@
   \label{eq:67}
-  L_{-n_1}L_{-n_2}\dots \phi_{\Delta}
+  L_{-n_1}L_{-n_2}\dots \phi_{h,\bar h}
 \end{equation}
@@
 Существуют разнообразные классы моделей двумерной конформной теории поля и даже задача классификации всех таких моделей до конца не решена, несмотря на первоначальный оптимизм \cite{moore1989taming}.
-Конформная теория поля привлекла большое внимание также благодаря своей связи с теорией струн.
+Помимо описания критических явлений, конформная теория поля привлекла большое внимание благодаря своей связи с теорией струн.
 
@@
 Такая техника сильно отличается от теоретико-полевого описания, поэтому актуальна проблема установления соответствия между эволюцией Шрамма-Лёвнера и конформной теорией поля \cite{bauer2002sle,bauer2003conformal,bauer2003sle,bauer2004cfts,bauer2004sle,bauer2004conformal}.
+
 В главе \ref{cha:applications} мы показываем, что алгебраические методы играют роль в установлении такого соответствия для ВЗНВ и coset-моделей конформной теории поля.
 
-Кроме того, конформные теории классифицируются по значениям центрального заряда $c$. Теории с рациональным
+Конформные теории классифицируются по значениям центрального заряда $c$. Теории с рациональным
 центральным зарядом называются рациональными. Считается, что все такие теории могут быть получены
@@
 Можно определять конформную теорию поля путем задания всех полей, как делается в подходе, предложенном в работе \cite{moore1989classical}.
-Мы воспользуемся определением из работы \cite{felder1989structure}, подробно изложенном в книге \cite{schottenloher2008mathematical}.
-Чтобы определить конформную теорию поля оказывается достаточно задать все корреляционные функции.
-Обычно их понимают следующим образом.
-Пусть $\Omega\in\mathbb{H}$ -- вакуум, тогда $n$-точечные корреляционные функции в квантовой теории поля даются выражением
+Однако мы воспользуемся определением из работы \cite{felder1989structure}, подробно изложенном в книге \cite{schottenloher2008mathematical}.
+В этом подходе теория определяется путем задания всех корреляционных функций.
+Преимущество такой аксиоматизации в более легком сопоставлении с решеточными моделями.
+
+Корреляционные функции обычно понимают следующим образом.   Пусть $\Omega\in\mathbb{H}$ -- вакуум, тогда $n$-точечные корреляционные функции в квантовой теории поля даются выражением
 \begin{equation}
@@
 
-\section{Модели Весса-Зумино-Новикова-Виттена и алгебры Ли}
+\section{Конформная теория поля на торе}
+\label{sec:nnn}
+
+При изучении конформной теории поля на плоскости или на сфере 
+голоморфный и антиголоморфный сектора можно рассматривать независимо. 
+Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть
+определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать
+взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно) чтобы теория была определена на торе.
+
+В теории критического поведения конформная инвариантность имеет место только в критической точке,
+где голоморфный и антиголоморфный сектора расцеплены. Но вблизи критической точки эти сектора должны
+быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве
+параметров, то эта связь должна сохраняться и в критической точке. Физический спектр теории должен
+плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного
+сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической
+точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния. Здесь
+естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории
+на торе.
+
+Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
+Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
+выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
+вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
+обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
+параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
+Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
+параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
+статсумма дается следом оператора сдвига в степени $m$:
+\begin{equation}
+  \label{eq:6}
+  Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
+\end{equation}
+Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
+конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
+$H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
+$L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
+$P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
+можно записать в виде
+\begin{equation}
+  \label{eq:7}
+  \begin{split}
+      Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
+      L_0)\}\\
+      =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
+  \end{split}
+\end{equation}
+Или, если ввести $q=\exp 2\pi i \tau$
+\begin{equation}
+  \label{eq:71}
+  Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
+\end{equation}
+Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
+
+Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
+эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
+
+Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
+модулярной инвариантности статсуммы.
+
+При помощи конформных преобразований можно перейти к таким координатам, в которых соотношения
+эквивалентности для тора (граничные условия) записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
+$\mathbb{C}$.
+
+Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
+конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
+$SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
+\begin{equation}
+  \label{eq:99} A=
+  \begin{pmatrix} a & b\\ c & d
+  \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
+\end{equation}
+и матрицы $A$ и $-A$ действуют одинаково на $\tau$
+\begin{equation}
+  \label{eq:137} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
+\end{equation}
+$\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
+модулярной группой.
+
+Конформная теория поля задаётся примарными полями $\phi_a$ с конформными размерностями $h_a$.
+
+Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
+произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
+представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсумма на торе
+(\ref{eq:71}) может быть записана в виде
+\begin{equation}
+  \label{eq:9}
+    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
+\end{equation}
+где $\chi_j$ --- нормализованный характер представления $\mathcal{H}_j$,
+\begin{equation}
+  \label{eq:74}
+  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i\tau}
+\end{equation}
+
+Характеры переходят друг в друга при модулярных преобразованиях:
+\begin{equation}
+  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
+\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
+\end{equation}
+где $S$ и $T$ --- постоянные матрицы.
+
+\section{Конформная теория поля на области с границей}
+\label{sec:boundary-cft}
+
+При изучении критических явлений большое применение находит формулировка конформной теории поля на области с границей.
+Это естественно как при описании реальных экспериментов, где система всегда имеет конечные размеры, так и при изучении критического поведения отдельных кластеров в решеточных моделях.
+Формулировка так называемой граничной конформной теории поля восходит к пионерским работам Карди \cite{cardy1984conformal,cardy1989boundary,cardy1986effect}.
+
+Рассмотрим теорию на верхней полуплоскости, которую мы обозначим через $\mathbb{H}$.
+Модель на верхней полуплоскости может быть конформно-инвариантной только если конформные преобразования сохраняют границу и граничные условия, то есть переводят вещественную ось в себя.
+Среди глобальных конформных преобразований (\ref{eq:172}) это те, у которых параметры $a,b,c$ вещественные, то есть глобальная конформная группа для полуплоскости содержит половину глобальных конформных преобразований плоскости.
+Аналогично среди инфинитезимальных преобразований $z\to z+\epsilon(z)$ подходят лишь те, для которых $\epsilon(\bar z)=\bar \epsilon(z)$.
+То есть голоморфный и антиголоморфный сектора не независимы.
+
+Вид преобразований примарных полей (\ref{eq:3}) дает следующие варианты конформно-инвариантных граничных условий:
+\begin{eqnarray}
+  \label{eq:173}
+ & \phi |_{\mathbb{R}}=0,\\
+ & \phi |_{\mathbb{R}}=\infty,\\
+ & \left. \frac{\partial \phi}{\partial n}\right|_{\mathbb{R}}=0
+\end{eqnarray}
+Конформное тождество Уорда показывает, как конформные преобразования действуют на корреляционные функции:
+\begin{equation}
+  \label{eq:174}
+  \delta_{\epsilon,\bar \epsilon} \left< X\right> = -\frac{1}{2\pi i} \oint_C dz \epsilon(z) \left< T(z) X\right> +\frac{1}{2\pi i}\oint_C d\bar z \bar \epsilon(\bar z) \left< \bar T(\bar z) X\right> 
+\end{equation}
+Теперь контур интегрирования $C$ должен лежать в  верхней полуплоскости, а  $\epsilon$ и $\bar \epsilon$ уже не являются независимыми, они комлексно сопряжены $\bar \epsilon=\epsilon^{*}$.
+Теория уже не распадается на независимые голоморфный и антиголоморфный сектора.
+Однако мы можем продолжить теорию на нижнюю полуплоскость, рассматривая зависимость от $\bar z_{i}$ на верхней полуплоскости как зависимость от $z_{i}^{*}=\bar z_{i}$ на нижней полуплоскости.
+Для этого мы добавим ``зеркальное отражение'' системы, то есть удвоим число полей в корреляторах, добавив их образы по отношению преобразованию четности.
+Если выполнено условие $T(z^{*})=\bar T(z), \bar T(z^{*})=T(z)$, то есть $\bar T=T$ на вещественной оси, мы можем продолжить контуры интегрирования в нижнюю полуплоскость (Смотри Рис.
+\ref{fig:ward}).
+
+Это условие естественно, так как в координатах $x,y$ оно имеет вид $T_{xy}=0$, что соответствует отсутствию потока энергии через границу.
+
+Теперь мы можем переписать тождество Уорда следующим образом:
+\begin{equation}
+  \label{eq:186}
+  \delta_{\epsilon} \left< X\right> = -\frac{1}{2\pi i} \oint dz \epsilon(z) \left< T(z) X'\right>,
+\end{equation}
+где
+\begin{equation}
+  \label{eq:175}
+  X'=\phi_{h_{1}}(z_{1}) \bar \phi_{\bar h_{1}}(z_{1}^{*}) \dots \phi_{h_{n}}(z_{n}) \bar \phi_{\bar h_{n}}(z_{n}^{*}), 
+\end{equation}
+а $\phi_{h_{i}}(z_{i})$ -- голоморфная часть поля $\phi_{(h_{i},\bar h_{i}}(z_{i},\bar z_{i})$ и $\bar\phi_{\bar h_{i}}(z_{i}^{*})$ -- антиголоморфная часть после преобразования четности (отражения), то есть тоже голоморфное поле с голоморфной размерностью $\bar h_{i}$.
+Таким образом, коррелятор $\left<X\right>$ на верхней полуплоскости, как функция $2n$ переменных $z_{1},\bar z_{1},\dots,z_{n},\bar z_{n}$ удовлетворяет тем же дифференциальным уравнениям, что и коррелятор $\left< X'\right>$ на всей плоскости, рассматриваемый как функция $2n$ голоморфных переменных $z_{1},\dots z_{2n}$, где $z_{n+i}=z_{i}^{*}$.
+
+\begin{figure}[h]
+ \centering
+  \includegraphics[height=50mm]{contours}  
+  \caption{Объединение контуров интегрирования в тождесте Уорда в граничной конформной теории поля}
+  \label{fig:ward}
+\end{figure}
+
+То есть если нас интересует $n$-точечная корреляционная функция в теории на верхней полуплоскости, мы можем рассматривать голоморфную часть $2n$-точечной функции на всей плоскости.
+Взаимодействие полей с границей симулируется путем рассмотрения взаимодействия полей с их зеркальными отражениями.
+
+Если мы хотим изучать теорию с неоднородными граничными условиями, мы можем сделать это введя так называемые граничные операторы.
+Рассмотрим, для примера, поле $\phi(z)$  с конформной размерностью $h$, заданное на верхней полуплоскости.
+При приближении к вещественной оси оно взаимодействует со своим зеркальным отражением и мы можем воспользоваться операторным разложением:
+\begin{equation}
+  \label{eq:176}
+  \phi(z)\phi(z^*)\approx \sum_i (z-z^*)^{(h_i -2h)}\varphi_B^{(i)}(x),
+\end{equation}
+где мы отбросили высшие члены и положили $x=\frac{z+z^*}{2}$, а поля $\varphi_B$ живут на границе.
+Операторы $\varphi_B^{(i)}$ можно рассматривать как операторы изменения граничных условий.
+Их классификация следует из требований модулярной инвариантности и дается формулой Верлинде (См.
+\cite{cardy1989boundary,difrancesco1997cft}).
+
+Аналогичные рассуждения можно провести для ВЗНВ- и coset-моделей на верхней полуплоскости \cite{gawedzki2002boundary},\cite{ishikawa2003novel}, \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,felder1999geometry,alekseev1999d}, \cite{mercat2001integrable}.
+
+В разделе \ref{sec:SLE} мы обсудим связь граничной конформной теории поля с решеточными моделями и стохастическими процессами.
+
+\section{Аффинные алгебры Ли в моделях Весса-Зумино-Новикова-Виттена }
 \label{sec:WZNW-models}
@@
 \end{equation}
-где $a^2>0$ - положительный параметр, $g(x)\in G$ - поле со значениями в группе $G$, которую мы
+где $a^2>0$ - положительный параметр, $g(x)\in G$ - поле со значениями в группе Ли $G$, которую мы
 будем считать полупростой. Действие задается на комплексной плоскости с бесконечностью, которая
-топологически эквивалентна 2-сфере.
+топологически эквивалентна 2-сфере. Взятие следа $Tr$ представляет собой матричную реализацию формы Киллинга ${\cal K}$ алгебры Ли $\gf$, соответствующей группе Ли $G$.
 
@@
 \begin{equation}
-  \label{eq:75} \Delta\Gamma= - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr'\left( \tilde
+  \label{eq:75} \Delta\Gamma= - \frac{i }{24\pi} \int_{S^3}\epsilon_{ijk} Tr\left( \tilde
 g^{-1}\frac{\partial \tilde g}{\partial y^i} \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
@@
   \label{eq:78}
-  (1+\frac{a^2 k}{4\pi})\partial_z(g^{-1}\partial_{\bar z}g)+(1-\frac{a^2 k}{4\pi})\partial_{\bar z}(g^{-1}\partial_z g)=0
+  \left(1+\frac{a^2 k}{4\pi}\right)\partial_z(g^{-1}\partial_{\bar z}g)+\left(1-\frac{a^2 k}{4\pi}\right)\partial_{\bar z}(g^{-1}\partial_z g)=0
 \end{equation}
@@
 \end{equation}
-Для токов
+Введем токи
 \begin{equation}
   \label{eq:72}
-  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
-\end{equation}
-
+  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g.
+\end{equation}
+Тогда уравнение (\ref{eq:79}) примет вид
 \begin{equation}
@@
 \end{equation}
- При инфинитезимальных преобразованиях $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ вариация
- $\delta_{\omega}g=\omega g$, а вариация действия
+ При инфинитезимальных преобразованиях $\Omega=1+\omega,\; \bar \Omega =1+\bar \omega$ вариация поля
+ $\delta_{\omega}g=\omega g$, а вариация действия дается равенством
  \begin{equation}
@@
 
-Примарные поля преобразуются  интегрируемыми конечномерными представлениями, а бесконечномерные и
-неинтегрируемые поля зануляют корреляционные функции.
+%Примарные поля преобразуются  интегрируемыми конечномерными представлениями, а бесконечномерные и
+%неинтегрируемые поля зануляют корреляционные функции.
 В WZW-моделях примарные поля
@@
 \end{equation}
+Решая эти уравнения, в принципе, можно найти все корреляционные функции.
 
@@
 
-Форма Киллинга на  $\gf$ порождает невырожденную билинейную форму $(\cdot,\cdot)$ на подалгебре Картана $\hfg$, позволяющую идентифицировать $\hfg$ с подпространством дуального пространства  $\hfg^{*}$ линейных функционалов на $\hfg$.
+Форма Киллинга ${\cal K}$ на  $\gf$ порождает невырожденную билинейную форму $(\cdot,\cdot)$ на подалгебре Картана $\hfg$, позволяющую идентифицировать $\hfg$ с подпространством дуального пространства  $\hfg^{*}$ линейных функционалов на $\hfg$.
 {\it Веса}  -- это элементы  $\hfg^{*}$, мы обозначаем их греческими буквами $\mu,\nu, \omega, \lambda\dots$
@@
   \label{eq:108}
-  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
+  [X^{i}t^{n},X^{j}t^{m}]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}
 \end{equation}
@@
 
-В произвольном представлении операторы, соответствующие генераторам подалгебры Картана $H^{i}$ можно одновременно диагонализовать путем специального выбора базиса
+В произвольном представлении операторы, соответствующие генераторам подалгебры Картана $H^{i}$, можно одновременно диагонализовать путем специального выбора базиса
  $\{v_{j}\}$ в $V$:
@@
 \end{equation}
+
 Структуру модуля можно записать в виде формального характера
@@
 
-В корневой системе $\Delta$ можно выбрать множество положительных корней.
+В корневой системе $\Delta$ можно выбрать множество {\it положительных корней}.
 Это подмножество  $\Delta^{+}\subset \Delta$, такое, что для любого корня $\alpha\in\Delta$ ровно один из корней $\alpha, -\alpha$ содержится $\Delta^{+}$ и для любых двух различных положительных корней $\alpha, \beta\in \Delta^{+}$, таких, что $\alpha+\beta\in \Delta$ их сумма тоже положительна $\alpha+\beta\in\Delta^{+}$.
 Элементы множества $-\Delta^{+}$ называются отрицательными корнями.
+
+{\it Сингулярным} называется вектор $v_{\lambda}$, такой что $E^{\alpha}v_{\lambda}=0,\; \forall \alpha\in \Delta^+$. Вес $\lambda$, отвечающий сингулярному вектору, также называется сингулярным.
 
@@
 раздел \ref{sec:high-weight-modul}).
-{\it Ко-марками} называются числа, равные $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
+{\it Ко-марками} называются числа $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
 
@@
 $\underset{U(\bff_{+})}{\otimes}$ значит, что действие элементов $U(\bff_{+})$ ``проносится'' через левую часть тензорного произведения направо.
-Здесь $\bff_{+}$ -- подалгебры Бореля, а $D^{\mu}(\bff_{+})$ -- представление $\bff_{+}$, такое, что $D(E^{\alpha})=0,\; D(H)=\mu(H)$ для любого положительного корня $\alpha$.
+Здесь $\bff_{+}$ -- подалгебра Бореля, а $D^{\mu}(\bff_{+})$ -- представление $\bff_{+}$, такое, что $D(E^{\alpha})=0,\; D(H)=\mu(H)$ для любого положительного корня $\alpha$.
 Элементы  $\gf$ действуют слева и мы должны прокоммутировать все элементы $\bff_{+}$ направо, чтобы они могли подействовать на пространстве $D^{\lambda}(\bff_{+})$.
@@
 
+Заметим, что в формулах Вейля для характеров (\ref{eq:122},\ref{eq:13},\ref{eq:18}) структура модулей определяется числителем.
+Формальный элемент, стоящий в числителе формулы Вейля, называется {\it сингулярным элементом}.
+В случае модулей Верма он задается старшим весом, а у неприводимых модулей и параболических модулей Верма является комбинацией формальных экспонент сингулярных весов.
+Разложение сингулярных элементов модулей старшего веса играет существенную роль в данной диссертации.
+
 Формула Вейля для характеров может быть использована для получения рекуррентных соотношений на кратности весов. Эти соотношения важны для вычислений \cite{il2010folded,kulish4sfa}.
@@
 
-При изучении конформной теории поля на плоскости или на сфере 
-голоморфный и антиголоморфный сектора можно рассматривать независимо. 
-Если мы говорим о применении конформной теории для описания поведения струн, то теория должна быть
-определена на римановых поверхностях большего рода ($h>0$), чтобы можно было описывать
-взаимодействия струн. Считается, что для этого необходимо (и, возможно, достаточно) чтобы теория была определена на торе.
-
-В теории критического поведения конформная инвариантность имеет место только в критической точке,
-где голоморфный и антиголоморфный сектора расцеплены. Но вблизи критической точки эти сектора должны
-быть связаны, и так как мы предполагаем плавный переход к критической точке в пространстве
-параметров, то эта связь должна сохраняться и в критической точке. Физический спектр теории должен
-плавно меняться, когда мы покидаем критическую точку, и связь голоморфного и антиголоморфного
-сектора вдали от критической точки должна приводить к ограничениям на набор состояний в критической
-точке. Этого можно достичь через геометрию, то есть накладывая граничные условия на состояния. Здесь
-естественно рассматривать периодические граничные условия, которые эквивалентны рассмотрению теории
-на торе.
-
-Наложим периодические граничные условия с периодами $\omega_1, \omega_2,\; \tau=\omega_2/\omega_1$. 
-Мы хотим вычислить статсумму для теории на торе через генераторы алгебры Вирасоро $L_0,\bar L_0$ и
-выяснить ее зависимость от параметра $\tau$. Пусть пространственное направление соответствует
-вещественной оси, а временное - мнимой. Пусть $\omega_1$ направлен вдоль вещественной оси. Через $H$
-обозначим гамильтониан, а через $P$ - общий импульс системы. Тогда оператор трансляции на $a$
-параллельно периоду $\omega_2$ имеет вид $\exp(-\frac{a}{|\omega_2|}(H \mathrm{Im} \omega_2-i P \mathrm{Re} \omega_2))$. 
-Если считать, что $a$ - расстояние в решетке, то такой сдвиг переводит нас с одного ряда на другой
-параллельно периоду $\omega_2$. Если полный период содержит $m$ ячеек решетки ($|\omega_2|=ma$), то
-статсумма дается следом оператора сдвига в степени $m$:
-\begin{equation}
-  \label{eq:6}
-  Z(\omega_1,\omega_2)=\mathrm{Tr} \exp-\{H \mathrm{Im} \omega_2-iP\mathrm{Re}\omega_2\}
-\end{equation}
-Операторы $H,P$ можно выразить через генераторы алгебры Вирасоро если рассмотреть тор как цилиндр
-конечной длины со склеенными концами. На цилиндре с длиной окружности $L$ гамильтониан
-$H=(2\pi/L)(L_0+\bar L_0-c/12)$. Константа добавлена, чтобы вакуумная энергия исчезала в пределе
-$L\to \infty$. Оператор импульса, который генерирует трансляции вокруг окружности, имеет вид
-$P=(2\pi i/L)(L_0-\bar L_0)$. Так как мы выбрали $\omega_1$ вещественным и равным $L$, статсумму
-можно записать в виде
-\begin{equation}
-  \label{eq:7}
-  \begin{split}
-      Z(\tau)=\mathrm{Tr}\exp \pi i \{(\tau-\bar \tau)(L_0+\bar L_0-c/12)+(\tau+\bar \tau)(L_0-\bar
-      L_0)\}\\
-      =\mathrm{Tr} \exp 2 \pi i \{\tau(L_0-c/24)-\bar\tau (\bar L_0-c/24)\}\\
-  \end{split}
-\end{equation}
-Или, если ввести $q=\exp 2\pi i \tau$
-\begin{equation}
-  \label{eq:71}
-  Z(\tau)=Tr \left (q^{L_0-c/24}\bar{q}^{\bar{L}_0-c/24}\right)
-\end{equation}
-Это выражение, на самом деле --- сумма характеров представлений алгебры Вирасоро (конформных семейств).
-
-Двумерный тор представляет собой фактор пространство $\mathbb{R}^2\approx \mathbb{C}$ по отношениям
-эквивалентности $z\sim z+w_1$ and $z\sim z+w_2$, где $w_1$ и $w_2$ не параллельны.
-
-Разные параметризации тора связаны модулярными преобразованиями, таким образом возникает требование
-модулярной инвариантности статсуммы.
-
-При помощи конформных преобразований можно перейти к таким координатам, в которых соотношения
-эквивалентности для тора (граничные условия) записываются в виде $z\sim z+1$ и $z\sim z+\tau$, где $\tau$ в верхней полуплоскости
-$\mathbb{C}$.
-
-Легко видеть, что $\tau$, $T(\tau)=\tau+1$ и $S(\tau)=-\frac{1}{\tau}$ описывают
-конформно-эквивалентные торы. Отображения $T$ и $S$ порождают группу
-$SL(2,\mathbb{Z})/\mathbb{Z}_2$, состоящую из матриц вида
-\begin{equation}
-  \label{eq:99} A=
-  \begin{pmatrix} a & b\\ c & d
-  \end{pmatrix} \quad\mbox{где}\; a,b,c,d\in\mathbb{Z},\quad ad-bc=1,
-\end{equation}
-и матрицы $A$ и $-A$ действуют одинаково на $\tau$
-\begin{equation}
-  \label{eq:137} \tau\to A\tau=\frac{a\tau+b}{c\tau+d}
-\end{equation}
-$\tau$ называется модулярным параметром, а группа $SL(2,\mathbb{Z})/\mathbb{Z}_2$ ---
-модулярной группой.
-
-Конформная теория поля задаётся примарными полями $\phi_a$ с конформными размерностями $h_a$.
-
-Примарные поля живут в пространствах $\mathcal{H}_{(i,j)}$, которые представляют собой тензорные
-произведения неприводимого представления $\mathcal{H}_j$ киральной алгебры и неприводимого
-представления $\bar{\mathcal{H}}_{\bar{j}}$ антикиральной алгебры. Тогда статсумма на торе
-(\ref{eq:71}) может быть записана в виде
-\begin{equation}
-  \label{eq:9}
-    Z(\tau)=\sum_{(j,\bar j)}\chi_j(q)\bar \chi_{\bar j}(\bar q)
-\end{equation}
-где $\chi_j$ --- нормализованный характер представления $\mathcal{H}_j$,
-\begin{equation}
-  \label{eq:74}
-  \chi_j(\tau)=Tr_{\mathcal{H}_j}(q^{L_0-\frac{c}{24}})\quad \mbox{где}\; q=e^{2\pi i\tau}
-\end{equation}
-
-Характеры переходят друг в друга при модулярных преобразованиях:
-\begin{equation}
-  \label{eq:107} \chi_j\left(-\frac{1}{\tau}\right)=\sum_k S_{jk}\chi_k(\tau)\quad \mbox{и}\quad
-\chi_j(\tau+1)=\sum_kT_{jk}\chi_k(\tau),
-\end{equation}
-где $S$ и $T$ --- постоянные матрицы.
-
-Для ВЗНВ-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$. Тогда
+Теперь рассмотрим модели Весса-Зумино-Новикова-Виттена на торе.
+Для ВЗНВ-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$.
+Тогда пространство полей представляет собой прямую сумму
 \begin{equation}
@@
 Можно показать, что это равенство удовлетворяется только для представлений уровня 1. То есть класс
-конформных вложений не слишком широк и существует полная их классификация. Кроме того, для
-конформных вложений существуют специальные методы разложения представлений.
+конформных вложений не слишком широк и существует полная их классификация \cite{difrancesco1997cft}. Кроме того, для
+конформных вложений существуют специальные методы разложения представлений \cite{altschuler1990branching}.
 
@@
 \end{equation}
+То есть в coset-моделях коммутационные соотношения полной киральной алгебры даются выражением
+\begin{equation}
+\label{eq:183}
+\begin{array}{ll}
+  L_{n}= L_{n}^{\gf}-L_{n}^{\af}, &\\
+  \left[L_{n}^{\gf},J^{a}_{m}\right]= -m J^{a}_{n+m},&\\
+  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m},&\\
+  \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=&\\
+  \quad =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}.&
+\end{array}
+\end{equation}
+
 Рассмотрим неприводимый модуль $L^{\mu}_{\gfh}$ как приводимый модуль подалгебры $\afh$: $L^{\mu}_{\gfh}=\bigoplus_{\nu}L^{\nu}_{\afh}$.
 В силу  равенства \eqref{eq:26} весовые векторы, соответствующие весам $L^{\mu}_{\gfh}$, сингулярным по отношению к действию $\afh$, будут образовывать модуль алгебры Вирасоро.
-Статсумма такой модели будет даваться функциями ветвления для вложения $\afh\to\gfh$ (См.
-раздел \ref{sec:coset-models} в главе \ref{cha:affine-lie-algebras}).
+Статсумма такой модели будет даваться функциями ветвления для вложения $\afh\to\gfh$.
+Проблемы вычисления функций ветвления для аффинных алгебр Ли мы рассматриваем в главе \ref{cha:affine-lie-algebras}.
 
@@
 
-\section{Конформная теория поля на области с границей}
-\label{sec:boundary-cft}
-
-При изучении критических явлений большое применение находит формулировка конформной теории поля на области с границей.
-Это естественно как при описании реальных экспериментов, где система всегда имеет конечные размеры, так и при изучении критического поведения отдельных кластеров в решеточных моделях.
-Формулировка так называемой граничной конформной теории поля восходит к пионерским работам Карди \cite{cardy1984conformal,cardy1989boundary,cardy1986effect}.
-
-Рассмотрим теорию на верхней полуплоскости, которую мы обозначим через $\mathbb{H}$.
-Модель на верхней полуплоскости может быть конформно-инвариантной только если конформные преобразования сохраняют границу и граничные условия, то есть переводят вещественную ось в себя.
-Среди глобальных конформных преобразований (\ref{eq:172}) это те, у которых параметры $a,b,c$ вещественные, то есть глобальная конформная группа для полуплоскости содержит половину глобальных конформных преобразований плоскости.
-Аналогично среди инфинитезимальных преобразований $z\to z+\epsilon(z)$ подходят лишь те, для которых $\epsilon(\bar z)=\bar \epsilon(z)$.
-То есть голоморфный и антиголоморфный сектора не независимы.
-
-Вид преобразований примарных полей (\ref{eq:3}) дает следующие варианты конформно-инвариантных граничных условий:
-\begin{eqnarray}
-  \label{eq:173}
- & \phi |_{\mathbb{R}}=0,\\
- & \phi |_{\mathbb{R}}=\infty,\\
- & \left. \frac{\partial \phi}{\partial n}\right|_{\mathbb{R}}=0
-\end{eqnarray}
-Конформное тождество Уорда показывает, как конформные преобразования действуют на корреляционные функции:
-\begin{equation}
-  \label{eq:174}
-  \delta_{\epsilon,\bar \epsilon} \left< X\right> = -\frac{1}{2\pi i} \oint_C dz \epsilon(z) \left< T(z) X\right> +\frac{1}{2\pi i}\oint_C d\bar z \bar \epsilon(\bar z) \left< \bar T(\bar z) X\right> 
-\end{equation}
-Теперь контур интегрирования $C$ должен лежать в  верхней полуплоскости, а  $\epsilon$ и $\bar \epsilon$ уже не являются независимыми, они комлексно сопряжены $\bar \epsilon=\epsilon^{*}$.
-Теория уже не распадается на независимые голоморфный и антиголоморфный сектора.
-Однако мы можем продолжить теорию на нижнюю полуплоскость, рассматривая зависимость от $\bar z_{i}$ на верхней полуплоскости как зависимость от $z_{i}^{*}=\bar z_{i}$ на нижней полуплоскости.
-Для этого мы добавим ``зеркальное отражение'' системы, то есть удвоим число полей в корреляторах, добавив их образы по отношению преобразованию четности.
-Если выполнено условие $T(z^{*})=\bar T(z), \bar T(z^{*})=T(z)$, то есть $\bar T=T$ на вещественной оси, мы можем продолжить контуры интегрирования в нижнюю полуплоскость (Смотри Рис.
-\ref{fig:ward}).
-
-Это условие естественно, так как в координатах $x,y$ оно имеет вид $T_{xy}=0$, что соответствует отсутствию потока энергии через границу.
-
-Теперь мы можем переписать тождество Уорда следующим образом:
-\begin{equation}
-  \label{eq:172}
-  \delta_{\epsilon} \left< X\right> = -\frac{1}{2\pi i} \oint dz \epsilon(z) \left< T(z) X'\right>,
-\end{equation}
-где
-\begin{equation}
-  \label{eq:175}
-  X'=\phi_{h_{1}}(z_{1}) \bar \phi_{\bar h_{1}}(z_{1}^{*}) \dots \phi_{h_{n}}(z_{n}) \bar \phi_{\bar h_{n}}(z_{n}^{*}), 
-\end{equation}
-а $\phi_{h_{i}}(z_{i})$ -- голоморфная часть поля $\phi_{(h_{i},\bar h_{i}}(z_{i},\bar z_{i})$ и $\bar\phi_{\bar h_{i}}(z_{i}^{*})$ -- антиголоморфная часть после преобразования четности (отражения), то есть тоже голоморфное поле с голоморфной размерностью $\bar h_{i}$.
-Таким образом, коррелятор $\left<X\right>$ на верхней полуплоскости, как функция $2n$ переменных $z_{1},\bar z_{1},\dots,z_{n},\bar z_{n}$ удовлетворяет тем же дифференциальным уравнениям, что и коррелятор $\left< X'\right>$ на всей плоскости, рассматриваемый как функция $2n$ голоморфных переменных $z_{1},\dots z_{2n}$, где $z_{n+i}=z_{i}^{*}$.
-
-\begin{figure}[h]
- \centering
-  \includegraphics[width=100mm]{contours}  
-  \caption{Объединение контуров интегрирования в тождесте Уорда в граничной конформной теории поля}
-  \label{fig:ward}
-\end{figure}
-
-То есть если нас интересует $n$-точечная корреляционная функция в теории на верхней полуплоскости, мы можем рассматривать голоморфную часть $2n$-точечной функции на всей плоскости.
-Взаимодействие полей с границей симулируется путем рассмотрения взаимодействия полей с их зеркальными отражениями.
-
-Если мы хотим изучать теорию с неоднородными граничными условиями, мы можем сделать это введя так называемые граничные операторы.
-Рассмотрим, для примера, поле $\phi(z)$  с конформной размерностью $h$, заданное на верхней полуплоскости.
-При приближении к вещественной оси оно взаимодействует со своим зеркальным отражением и мы можем воспользоваться операторным разложением:
-\begin{equation}
-  \label{eq:176}
-  \phi(z)\phi(z^*)\approx \sum_i (z-z^*)^{(h_i -2h)}\varphi_B^{(i)}(x),
-\end{equation}
-где мы отбросили высшие члены и положили $x=\frac{z+z^*}{2}$, а поля $\varphi_B$ живут на границе.
-Операторы $\varphi_B^{(i)}$ можно рассматривать как операторы изменения граничных условий.
-Их классификация следует из требований модулярной инвариантности и дается формулой Верлинде (См.
-\cite{cardy1989boundary,difrancesco1997cft}).
-
-Аналогичные рассуждения можно провести для ВЗНВ- и coset-моделей на верхней полуплоскости \cite{gawedzki2002boundary},\cite{ishikawa2003novel}, \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,felder1999geometry,alekseev1999d}, \cite{mercat2001integrable}.
-
-В разделе \ref{sec:SLE} мы обсудим связь граничной конформной теории поля с решеточными моделями и стохастическими процессами.
-
+\section{Заключение}
+\label{sec:review-conclusion}
+
+Мы описали двумерную конформную теорию поля и показали роль теории представлений аффинных алгебр Ли в изучении моделей Весса-Зумино-Новикова-Виттена и coset-моделей.
+В следующих главах мы используем разложение сингулярных элементов для описания свойств представлений и для вывода соотношений, позволяющих вычислять коэффициенты ветвления.
 %%

### 2012-06-04 AffineLieAlgebras/Thesis/4.tex
Edits from paper version. Text duplication mostly fixed.

@@
 
-\section{Роль сингулярных элементов coset-моделей в установлении соответствия между конформной теорией поля и критическим поведением в решеточных моделях}
+\section{Coset-модели и критическое поведение}
 
@@
 Класс моделей конформной теории поля, для которых получены такие результаты, в основном ограничивается минимальными унитарными моделями.
-
-Введение дополнительного случайного блуждания на группе позволяет построить стохастический аналоги для ВЗНВ-моделей \cite{bettelheim2005stochastic,Rasmussen:2004xr,alekseev2010sle}.
-В данном разделе мы обсуждаем обобщение этой конструкции на случай coset-моделей.
-В установлении соответствия между корреляторами в стохастических моделях и моделях конформной теории поля существенную роль играют сингулярные элементы, что связано со структурой модулей алгебры Вирасоро в ВЗНВ и coset-моделях (см.
-разделы \ref{sec:WZNW-models}\ref{sec:coset-models-cft}).
-К сожалению, пока не известно, пределами каких решеточных моделей могут являться такие стохастические конструкции.
-
-Эволюция Шрамма-Левнера появляется как скейлинговый предел интерфейсов в решеточных моделях в критической точке.
-Критическое поведение этих моделей можно описывать при помощи минимальных моделей конформной теории поля.
-Оказывается, что некоторые корреляционные функции в моделях конформной теории поля являются мартингалами по отношению к эволюции Шрамма-Левнера.
-В этой главе мы обобщаем эволюцию Шрамма-Левнера с дополнительным броуновским движением на группе Ли  $G$ на случай фактор-пространства $G/A$.
-Замет мы изучаем, как связано такое описание критического поведения с coset-моделями конформной теории поля.
-В качестве критерия согласованности мы используем тот факт, что минимальные модели могут быть реализованы как coset-модели при некотором выборе групп $G, A$.
 
@@
 Мы рассматриваем теорию с границей, так что мы должны использовать модели граничной конформной теории поля и накладывать соответствующие граничные условия \cite{cardy1984conformal,cardy1989boundary,cardy1991bulk}.
-В случае верхней полуплоскости корреляционные функции в граничной конформной теории поля могут быть переписаны как корреляционные функции для теории на всей плоскости, но с удвоенным числом полей.
+В случае верхней полуплоскости корреляционные функции в граничной конформной теории поля могут быть переписаны как корреляционные функции для теории на всей плоскости, но с удвоенным числом полей (см.
+раздел \ref{sec:boundary-cft}).
 
@@
 
-Мы предполагаем, что $\mathcal{F}$ содержит некоторый набор примарных полей  $\varphi_{\lambda_{i}}$ с конформными весами $h_{\lambda_{i}}$.
+Мы предполагаем, что $\mathcal{F}$ содержит некоторый набор примарных полей  $\varphi_{i}$ с конформными весами $h_{i}$.
 Так как мы рассматриваем граничную конформную теорию поля, мы должны добавить объемные поля в сопряженных точках  $\bar z_{i}$.
-Для дальнейшего использования в моделях Весса-Зумино-Новикова-Виттена мы обозначим конформные веса этих сопряженных полей через $h_{\lambda_{i}^{*}}$.
 Кроме того, у нас есть операторы смены граничного условия   $\phi$ на конце следа эволюции Шрамма-Левнера и на бесконечности.
@@
 \begin{equation*}
-  -\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{\lambda_{i}}}.
+  -\frac{2h_{\lambda_{i}}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}.
 \end{equation*}
@@
 \label{eq:70}
-  d\varphi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\varphi_{\lambda_{i}}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\varphi_{\lambda_{i}}(w_{i}) 
+  d\varphi_{i}(w_{i}) = \mathcal{G}_{i}\varphi_{i}(w_{i})=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}\varphi_{i}(w_{i}) 
 \end{equation}
@@
   \label{eq:168}
-   \left<\left([L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi\right)(0)\; \varphi_{\lambda_{1}}\dots \varphi_{\lambda_{{2N}}}\right>=0.
+   \left<\left([L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi\right)(0)\; \varphi_{1}\dots \varphi_{2N}\right>=0.
 \end{equation}
@@
 \cite{belavin1984ics}, \cite{difrancesco1997cft}. 
-Равенство \eqref{eq:168} верно для произвольной наблюдаемой $\mathcal{O}$ и для произвольных примарных поле $\varphi_{\lambda_{i}}$, так что $\psi=[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ -- нулевое поле уровня два и $\psi(0)\left|0\right>$ -- нулевое состояние уровня два.
+Равенство \eqref{eq:168} верно для произвольной наблюдаемой $\mathcal{O}$ и для произвольных примарных поле $\varphi_{i}$, так что $\psi=[L_{-2}-\frac{\kappa}{2}L_{-1}^{2}]\phi$ -- нулевое поле уровня два и $\psi(0)\left|0\right>$ -- нулевое состояние уровня два.
 В минимальных унитарных моделях существует только два примарных поля, порождающих модули Верма алгебры Вирасоро с нулевыми состояниями на уровне два.
-Это поля $\phi_{1,2}$ и $\phi_{2,1}$, так что $\phi\sim \phi_{1,2} \;\text{or}\; \phi_{2,1}$.
+Это поля $\phi_{1,2}$ и $\phi_{2,1}$, так что $\phi\sim \phi_{1,2} \;\text{или}\; \phi_{2,1}$.
 
@@
 Модели Весса-Зумино-Новикова-Виттена обладают симметрией Каца-Муди в дополнение к конформной инвариантности, приводящей к появлению алгебры Вирасоро.
-Сначала мы напомним свойства ВЗНВ-моделей \cite{difrancesco1997cft}, которые нужны для изучения мартингалов эволюции Шрамма-Левнера.
+Мы описали ВЗНВ-модели в разделе \ref{sec:WZNW-models}.
 
-Действие модели Весса-Зумино-Новикова-Виттена записывается в терминах отображения $g:\mathbb{C}\cup \{\infty\}\sim S^{2}\to G$ из комплексной плоскости с бесконечностью (сферы Римана) в некоторую (простую) группу Ли $G$:
-\begin{multline}
-  S=-\frac{k}{8\pi}\int d^2x\; \mathcal{K} (g^{-1}\partial^{\mu}g, g^{-1} \partial_{\mu}g)  
-  - \frac{k }{24\pi^{2}} \int_{B}\epsilon_{ijk} \mathcal{K}\left(
-    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i},\left[
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
-      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right]\right) d^3y
-\end{multline}
-Здесь $\mathcal{K}$ -- форма Киллинга на алгебре Ли  $\gf$ группы Ли $G$.
-Первый член -- это просто нелинейная сигма-модель, а второй записывается при помощи продолжения $\tilde{g}$ с два-сферы $S^{2}$ на трехмерное многообразие $B$, границей которого является два-сфера.
-Так как это продолжение не единственно, а экспонента действия должна быть определена однозначно, константа  $k$ должна быть целочисленной.
-
-Сохраняющиеся токи в этой модели даются выражениями:
-  \begin{eqnarray}
-    J(z)= -k \partial_zg g^{-1}
-    \bar J(\bar z)=k g^{-1}\partial_{\bar z}g
-  \end{eqnarray}
-
-Модель обладает калибровочной инвариантностью по отношению к преобразованиям
-  $g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)$, 
-здесь $\Omega,\;\bar \Omega \in G$ независимы. Из рассмотрения инфинитезимальных калибровочных преобразований  $\Omega=1+\omega$ получаем тождества Уорда
-  \begin{equation}
-    \label{eq:139}
-    \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
-    \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>,
-  \end{equation}
-из которых следует операторное разложение для токов:
- \begin{equation}
-   \label{eq:128}
-   J^{a}(z)J^{b}(w)\sim \frac{k\delta_{ab}}{(z-w)^{2}}+\sum_{c}i f_{abc}\frac{J^{c}}{z-w},
- \end{equation}
-здесь $f_{abc}$ -- структурные константы алгебры Ли $\gf$.
-
-Разложим токи на моды $J^a(z)=\sum\limits_{n\in \mathbb Z}z^{n-1}J^a_n $, воспользуемся операторным разложением \eqref{eq:128} и получим коммутационные соотношения аффинной алгебры Ли $\gfh$:
-\begin{equation*}
- \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}.  
-\end{equation*}
-
-Конформная инвариантность в этой модели следует из конструкции Сугавары, которая представляет собой способ вложения алгебры Вирасоро в универсальную обертывающую алгебры аффинной алгебры Ли $\gfh$ ($Vir\subset U(\gfh)$):
-\begin{equation}
-  \label{eq:134}
-  L_n=\frac{1}{2(k+h^{\vee})}\left(\sum\limits_a\sum\limits_{m\leq -1}J^a_m J^a_{n-m}+\sum_{m\geq 0} J^{a}_{n-m}J^{a}_{m}\right), 
-\end{equation}
-где $h^{\vee}$ -- дуальное число Кокстера алгебры Ли $\gf$. 
-Полная киральная алгебра модели представляет собой полупрямое произведение аффинной алгебры и алгебры Вирасоро $\gfh \ltimes Vir$ с коммутационными соотношениями
-  \begin{equation}
-    \label{eq:141}
-    \begin{aligned}
-      \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0} \\
-      \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
-      \left[L_n,J^a_m\right]=-mJ^a_{n+m}
-    \end{aligned}
-  \end{equation}
-Здесь центральный заряд  $c$ алгебры Вирасоро дается выражением
-\begin{equation}
-  \label{eq:164}
-  c=\frac{k\;\mathrm{dim}\gf}{k+h^{\vee}}
-\end{equation}
-В модели существует бесконечное число полей, примарных по отношению к действию алгебры Вирасоро, но они организованы в модули старшего веса аффинной алгебры Ли $\gfh$.
-Примарные поля полной киральной алгебры  $\phi_{\lambda}$ нумеруются старшими весами  $\gfh$-модулей.
-Покажем, как генераторы алгебры Вирасоро и аффинной алгебры Ли действуют на примарные поля:
-  \begin{equation*}
-    \begin{aligned}
-      & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>  \quad    J^a_n\left|\phi_{\lambda}\right>=0 \quad \text{для}\; n>0 \\
-      & L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^{\vee})}\left|\phi_{\lambda}\right>=h_{\lambda} \left|\phi_{\lambda}\right>,
-    \end{aligned}
-  \end{equation*}
-где $\rho$ -- вектор Вейля алгебры $\gf$.
-
-Теперь рассмотрим эволюцию Шрамма-Левнера в ВЗНВ-моделях. 
+Рассмотрим эволюцию Шрамма-Левнера в ВЗНВ-моделях. 
 Подобно минимальным моделям мы рассматриваем наблюдаемые
@@
   \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
-  \frac{\left<\phi_{\Lambda}(z_{t}) \phi_{\lambda_1}(z_{1}) \dots \phi_{\lambda_n}(z_{n}) \phi_{\lambda^{*}_1}(\bar z_{1}) \dots \phi_{\lambda^{*}_n}(\bar z_{n})
-      \phi_{\Lambda^{*}}(\infty)\right>}{\left<\phi_{\Lambda}(z_{t})\phi_{\Lambda^{*}}(\infty)\right>}
+  \frac{\left<\phi_{\Lambda}(z_{t}) \varphi_{\lambda_1}(z_{1}) \dots \varphi_{\lambda_n}(z_{n}) \varphi_{\lambda^{*}_1}(\bar z_{1}) \dots \varphi_{\lambda^{*}_n}(\bar z_{n})
+      \phi_{\Lambda^{*}}(\infty)\right>}{\left<\phi_{\Lambda}(z_{t})\phi_{\Lambda^{*}}(\infty)\right>},
 \end{equation*}
+где примарные объемные поля нумеруются весами $\lambda_i$.
+
 Мы опять используем конформное отображение  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ чтобы переписать формулу для наблюдаемых на всей верхней полуплоскости.
@@
 \begin{equation*}
-  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i}),
+  d\varphi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\varphi_{\lambda_{i}}(w_{i}),
 \end{equation*}
@@
 \end{eqnarray}
-Эти уравнения можно переписать как алгебраические соотношения, связывающие параметры случайного блуждания $\kappa, \tau$ с уровнем  $k$ представления аффинной алгебры Ли, если воспользоваться коммутационными соотношениями  \eqref{eq:141}.
+Эти уравнения можно переписать как алгебраические соотношения, связывающие параметры случайного блуждания $\kappa, \tau$ с уровнем  $k$ представления аффинной алгебры Ли, если воспользоваться коммутационными соотношениями  (\ref{eq:102}), (\ref{eq:90}).
 Строгий анализ полученных алгебраических соотношений проведен в работе \cite{alekseev2010sle}.
@@
 Такие модели задаются алгеброй Ли $\gf$ и ее подалгеброй $\af$.
-Обозначим через $J_{n}^{a}$ генераторы аффинной алгебры Ли $\gfh$, а через $\tilde{J}_{n}^{b}$ -- генераторы $\afh$, так что $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b} J^{a}_{n}$.
-Генераторы алгебры Вирасоро в coset-моделях даются разностями выражений Сугавары для ВЗНВ-моделей, соответствующих алгебрам  $\gf$ и $\af$:
-\begin{equation*}
-  L_{n}=L_{n}^{\gf}-L_{n}^{\af}
-\end{equation*}
-Коммутационные соотношения между генераторам алгебры Вирасоро и генераторами подалгебры  $\afh$ тривиальны
-\begin{equation}
-  \label{eq:156}
-  \left[L_{n},\tilde{J}^{b}_{m}\right]=0
-\end{equation}
-
-Поля нумеруются парами весов  $(\mu,\nu)$, где $\mu$ -- вес  $\gfh$, а $\nu$ -- вес $\afh$, соответственно.
-Но появляются правила отбора, так как функции ветвления для некоторых пар весов  $(\mu,\nu)$ исчезают.
-Кроме того, имеется избыточность, так как функции ветвления для различных пар $(\mu,\nu)$ могут совпадать \cite{fuchs1996resolution,schellekens1990field}.
-
-Итак, примарные поля нумеруются парами весов  $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ алгебры $\gfh$ и подалгебры $\afh$, такими, что соответствующие функции ветвления $b^{\mu}_{\nu}(q)\neq 0$.
-Некоторые пары эквивалентны.
-Эта эквивалентность дается действием так называемых ``простых токов'' $(J,\tilde{J})$, которые являются элементами группы внешних автоморфизмов  $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ алгебры $\gfh\times\afh$, где $B(G)$ -- это центр группы Ли $G$.
-Мы можем думать о простых токах как о примарных полях, тогда их действие на поля теории дается слиянием \cite{difrancesco1997cft}.
-Таким образом, примарные поля coset-моделей нумеруются классами эквивалентности пар весов  $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, где $(J,\tilde J)$ такие, что  конформные веса компонент равны:  $h_{J}-h_{\tilde{J}}=0$.
-
-Конформный вес примарного поля в coset-модели равен
-\begin{multline}
-  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
-  \left|\phi_{(\mu,\nu)}\right>=\\
-  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
-\end{multline}
-Можно получить аналог уравнений Книжника-Замолодчикова для coset-моделей \cite{kogan1997knizhnik}:
-\begin{equation}
-  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
-  \label{eq:144}
-\end{equation}
+Воспользуемся обозначениями, введенными в разделе \ref{sec:coset-models-cft}.
 
 Как мы упоминали в главе \ref{cha:CFT}, $G/A$-coset модель конформной теории поля может быть реализована как ВЗНВ-модель (с калибровочной группой $G$), взаимодействующая с чисто калибровочными полями, с калибровочной группой $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
-Действие записывается через поля $\gamma:\mathbb{C}\to G$ and $\alpha,\bar\alpha:\mathbb{C}\to A$ следующим образом:
+Действие записывается через поля $\gamma:\mathbb{C}\to G$ and $\alpha,\bar\alpha:\mathbb{C}\to A$ следующим образом (\ref{eq:38}):
 \begin{multline}
@@
 также \cite{bettelheim2005stochastic}).
-Обозначим через $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) генераторы представления алгебры $\gf$ (соответственно, представления $\af$), соответствующего примарному полю $\phi_{i}$.
+Обозначим через $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) генераторы представления алгебры $\gf$ (соответственно, представления $\af$), соответствующего примарному полю $\varphi_{i}$.
 
@@
 \end{equation*}
-Напомним, что через  $\mathcal{G}_{i}$ мы обозначили  генераторы инфинитезимальных преобразований примарных $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$.
+Напомним, что через  $\mathcal{G}_{i}$ мы обозначили  генераторы инфинитезимальных преобразований примарных $\varphi_{i}$:$d\varphi_{i}(w_{i}) = \mathcal{G}_{i}\varphi_{i}(w_{i})$.
 Нормируем дополнительное $\left(\dim\gf\right)$-мерное Броуновское движение следующим образом: $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
@@
 \begin{multline}
-d \mathcal{F}_{\mathbb{H}_{t}}=\\ \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)
+d \mathcal{F}_{\mathbb{H}_{t}}= \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)
 \left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
@@
 \end{eqnarray*}
-Это равенство эквивалентно следующему алгебраическому условию на граничное состояние $\varphi(0)\left|0\right>$:
+Это равенство эквивалентно следующему алгебраическому условию на граничное состояние $\phi(0)\left|0\right>$:
 \begin{multline}
 \label{eq:182}
-  \left<0\left|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})\right.\right.\\
+  \left<0\left|\phi(\infty)\varphi_{1}(w_{1})\dots\varphi_{2N}(w_{2N})\right.\right.\\
   \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
-\left.\varphi(0)|0\right>=0.
+\left.\phi(0)|0\right>=0.
 \end{multline}
@@
 \label{eq:126}
-|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
-\cdot\varphi(0)|0>
+|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
+\cdot\phi(0)|0>
 \end{multline}
@@
 Теперь мы можем подействовать на  $\psi$ повышающими операторами и получить уравнения на  $\kappa,\tau$.
-Так как в  coset-моделях коммутационные соотношения полной киральной алгебры даются выражением
-\begin{equation}
-\label{eq:183}
-\begin{array}{ll}
-  L_{n}= L_{n}^{\gf}-L_{n}^{\af}, &\\
-  \left[L_{n}^{\gf},J^{a}_{m}\right]= -m J^{a}_{n+m},&\\
-  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m},&\\
-  \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=&\\
-  \quad =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0},&
-\end{array}
-\end{equation}
-для нас более удобно действовать операторами $L_{2}^{\gf}$ и $\left(L_{1}^{\gf}\right)^{2}$. 
+Так как в  coset-моделях коммутационные соотношения полной киральной алгебры даются выражением (\ref{eq:183}), для нас более удобно действовать операторами $L_{2}^{\gf}$ и $\left(L_{1}^{\gf}\right)^{2}$.
 Применение оператора $L_{2}^{\gf}$ дает
@@
 
-Физическая интерпретация решений условий мартингала не вполне ясна, но пока не найдена и решеточная интерпретация эволюции Шрамма-Левнера с дополнительным Броуновским движением на групповом многообразии \cite{bettelheim2005stochastic} и решеточная реализация ВЗНВ-моделей.
-Кажется, что эти вопросы тесно связаны.
-
 %%

### 2012-06-04 AffineLieAlgebras/Thesis/1.tex
Some misprints fixed.

@@
 Вложение должно сохранять конформную инвариантность.
-Пусть $X^{\alpha_j}_{-n_j}$ и $\tilde{X}^{\alpha'_j}_{-n_j}$ -- понижающие операторы для алгебры $\mathfrak{g}$ и подалгебры $\af\subset\mathfrak{g}$ соответственно.
+Пусть $J^{\alpha_j}_{-n_j}$ и $\tilde{J}^{\alpha'_j}_{-n_j}$ -- понижающие операторы для алгебры $\mathfrak{g}$ и подалгебры $\af\subset\mathfrak{g}$ соответственно.
 Обозначим через $\pi_{\af}$ оператор проекции $\pi_{\af}:\mathfrak{g}\longrightarrow \af$.
@@
   \label{eq:151}
-  X^{\alpha_1}_{-n_1}X^{\alpha_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+  J^{\alpha_1}_{-n_1}J^{\alpha_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
 \end{equation*}
@@
   \label{eq:152}
-  \tilde{X}^{\alpha'_1}_{-n_1}\tilde{X}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\af}(\lambda)\right>.
+  \tilde{J}^{\alpha'_1}_{-n_1}\tilde{J}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\af}(\lambda)\right>.
 \end{equation*}
 Инвариантность вакуума под действием $\mathfrak{g}$ влечет его инвариантность относительно действия $\af$, но это неверно для тензора энергии-импульса.
-Необходимо, чтобы тензор энергии-импульса объемлющей теории содержал только генераторы $\tilde{X}$.
+Необходимо, чтобы тензор энергии-импульса объемлющей теории содержал только генераторы $\tilde{J}$.
 Тогда соотношение
@@
 \label{eq:48}
-  L_n=\frac{1}{2(k+h^v)}\sum_{\alpha}\sum_m:X^{\alpha}_m X^{\alpha}_{n-m}: \; .
+  L_n=\frac{1}{2(k+h^v)}\sum_{\alpha}\sum_m:J^{\alpha}_m J^{\alpha}_{n-m}: \; .
 \end{equation*}
@@
 В эти комбинации мы должны подставить генераторы подалгебры $\af$ выраженные через генераторы $\mathfrak{g}$ и получить тензор энергии-импульса $T_{\mathfrak{g}}$.
-Но если набор генераторов, связанных с  $\Delta_{\afb}$ не пуст, это не возможно, так как  $T_{\mathfrak{g}}$ содержит генераторы $X^{\alpha}_n$, где $\alpha\in \Delta_{\afb}$.
+Но если набор генераторов, связанных с  $\Delta_{\afb}$ не пуст, это не возможно, так как  $T_{\mathfrak{g}}$ содержит генераторы $J^{\alpha}_n$, где $\alpha\in \Delta_{\afb}$.
 \end{proof}
@@
 Это можно заметить сравнивая Рисунок \ref{fig:B2_A1} и Рисунок \ref{fig:AffineB2_A1_anom_proj}, на котором сингулярный элемент $\Psi ^{\left( \mu \right) }_{\left(  \widehat{A_1}, A_1 \right)}$ для аффинного вложения  $\hat{A_1}\to\hat{B_{2}}$  показан вплоть до двенадцатого грейда.
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=120mm]{figure12}
-  \caption{Сингулярный элемент $\Psi ^{\left( \omega_1 \right) }_{\left(  \widehat{A_1}, A_1 \right)}$ в базисе $\{\beta,\delta\}$.
-Размерности соответствующих  $\afb=A_1$-модулей со знаками  $\epsilon(u)$ представлены на рисунке.}
-  \label{fig:AffineB2_A1_anom_proj}
-\end{figure}
-
-\begin{figure}[h!bt]
-  \centering
-  \includegraphics[width=120mm]{figure13}
-  \caption{Сингулярные коэффициенты ветвления для вложения $\hat{A_1}\rightarrow \hat{B_2}$.
-Использован базис $\{\beta,\delta\}$.
-Границы главной камеры Вейля $\bar{C}_{\hat{A}_1}$ показаны черными линиями.
-Сингулярные коэффициенты ветвления внутри главной камеры Вейля равны коэффициентам ветвления для вложения $\hat{A_1}\rightarrow \hat{B_2}$.}
-  \label{fig:AffineB2_A1_branching}
-\end{figure}
-
 Кратности старших весов внутри главной камеры Вейля
@@
 \end{eqnarray*}
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=120mm]{figure12}
+  \caption{Сингулярный элемент $\Psi ^{\left( \omega_1 \right) }_{\left(  \widehat{A_1}, A_1 \right)}$ в базисе $\{\beta,\delta\}$.
+Размерности соответствующих  $\afb=A_1$-модулей со знаками  $\epsilon(u)$ представлены на рисунке.}
+  \label{fig:AffineB2_A1_anom_proj}
+\end{figure}
+
+\begin{figure}[tb]
+  \centering
+  \includegraphics[width=120mm]{figure13}
+  \caption{Сингулярные коэффициенты ветвления для вложения $\hat{A_1}\rightarrow \hat{B_2}$.
+Использован базис $\{\beta,\delta\}$.
+Границы главной камеры Вейля $\bar{C}_{\hat{A}_1}$ показаны черными линиями.
+Сингулярные коэффициенты ветвления внутри главной камеры Вейля равны коэффициентам ветвления для вложения $\hat{A_1}\rightarrow \hat{B_2}$.}
+  \label{fig:AffineB2_A1_branching}
+\end{figure}
+
 Этот результат можно представить в виде набора функций ветвления:

### 2012-06-10 AffineLieAlgebras/SLE/paper.tex
Sent improved version to JETP Letters.

@@
   \label{eq:20}
-       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}  
+       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}d\xi_{t}  
 \end{equation}
@@
 We normalize additional $\left(\dim\gf\right)$-dimensional Brownian motion as $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
+We also introduce the parameter $\tau$, which is the variance of this stochastic process.
 The generator of field transformation is equal to
@@
 
- Ito formula  gives us an expression for the differential of $\mathcal{F}$ which should be zero due to martingale condition:
+The differential of $\mathcal{F}$ should be zero due to martingale condition.
+Ito formula is used to calculate the differential \cite{alekseev2010sle}.
+We need to include second order terms in  $\mathcal{G}_{i}$ since they contain squares of Brownian motion differentials $d\xi_{t},\; d\theta^{a}$ with the expectation values proportional to $dt$ ($\mathbb{E}[d\xi_{t}^{2}]=dt$):
 \begin{multline}

### 2012-06-28 AffineLieAlgebras/Thesis/autoref.tex
Autoreferat started

\documentclass[14pt,autoref,href,facsimile
%,fixint=false
%,times
]{disser}

\usepackage[a4paper,nohead,includefoot,mag=1000,
            margin=2cm,footskip=1cm]{geometry}
\usepackage[T2A]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage[english,russian]{babel}
\usepackage{tabularx}
\ifpdf\usepackage{epstopdf}\fi

% Поддержка нескольких списков литературы в одном документе
\usepackage{multibib}
% Создание команд для цитирования собственных работ диссертанта
% в отдельном разделе. В данном случае ссылка будет иметь вид \citemy{...}.
\newcites{my}{Список публикаций}

% Путь к файлам с иллюстрациями
\graphicspath{{figures/}}

\begin{document}
% Включение файла с общим текстом диссертации и автореферата
% (текст титульного листа и характеристика работы).
\input{common}

\title{АВТОРЕФЕРАТ\\
диссертации на соискание ученой степени\\
кандидата физико-математических наук}

\maketitle

% Внутренняя сторона обложки
\noindent
\begin{center}
Работа выполнена на кафедре физики высоких энергий и элементарных частиц физического факультета Санкт-Петербургского государственного университета.
% \emph{название организации}.
\end{center}
\vskip1ex
\begin{tabularx}{\linewidth}{lp{1cm}X}
Научный руководитель:  & & \emph{доктор физико-математических наук}, \\
                       & & \emph{профессор}, \\
                       & & \emph{Ляховский Владимир Дмитриевич}
\\
Официальные оппоненты: & & \emph{доктор физико-математических наук}, \\
                       & & \emph{профессор}, \\
                       & & \emph{Кулиш Петр Петрович}\\
                       & & \emph{кандидат физико-математических наук}, \\
                       & & \emph{ученое звание}, \\
                       & & \emph{Мудров Андрей И}
\\
Ведущая организация:   & & \emph{Объединенный институт ядерных исследований}\\
\end{tabularx}

\vskip2ex\noindent
Защита состоится \datefield{} в \rule[0pt]{1cm}{0.5pt}\, часов
на заседании совета \emph{Д 212.232.24} по защите докторских и кандидатских диссертаций при \emph{Санкт-Петербургском государственном университете}, расположенном по адресу:
\emph{Санкт-Петербург, Средний пр. В.О., д. 41/43, ауд. 305}

\vskip1ex\noindent
С диссертацией можно ознакомиться в научной библиотеке
\emph{Санкт-Петербургского государственного университета}.

\vskip1ex\noindent
Автореферат разослан \datefield{}

\vskip2ex\noindent
%Отзывы и замечания по автореферату в двух экземплярах, заверенные
%печатью, просьба высылать по вышеуказанному адресу на имя ученого секретаря
%диссертационного совета.

\vfill\noindent
Ученый секретарь\\
диссертационного совета,\\
\emph{ученая степень}, \emph{ученое звание}%
\hfill
\makeatletter
% вставка файла, содержащего факсимиле ученого секретаря
\ifDis@facsimile
  \raisebox{-4pt}{\includegraphics[width=3cm]{sec-facsimile}}\hfill
\fi%
\makeatother%
\emph{фамилия и. о.}

\clearpage

\nsection{Общая характеристика работы}

% Актуальность работы
\actualitysection
\actualitytext

% Цель диссертационной работы
\objectivesection
\objectivetext

% Научная новизна
\noveltysection
\noveltytext

% Практическая значимость
\valuesection
\valuetext

% Результаты и положения, выносимые на защиту
\resultssection
\resultstext

% Апробация работы
\approbationsection
\approbationtext

% Публикации
\pubsection
\pubtext

% Личный вклад автора
\contribsection
\contribtext

% Структура и объем диссертации
\structsection
\structtext

\nsection{Содержание работы}

\textbf{Во Введении} обоснована актуальность диссертационной работы,
сформулирована цель и аргументирована научная новизна исследований, показана
практическая значимость полученных результатов, представлены выносимые на
защиту научные положения.

\textbf{В первой главе} ...

Содержание первой главы.

Результаты первой главы опубликованы в
работе~\citemy{Ivanov_1999_Journal_17_173}.

\textbf{Во второй главе} ...

Содержание второй главы.

Результаты второй главы опубликованы в
работе~\citemy{Petrov_2001_Journal_23_12321}.

\textbf{В третьей главе} ...

Содержание третьей главы.

Результаты третьей главы опубликованы в
работе~\citemy{Sidorov_2002_Journal_32_1531}.

\textbf{В Заключении}

% ----------------------------------------------------------------
\renewcommand\bibsection{\nsection{Список публикаций}}

% Префикс номеров ссылок на работы соискателя
\def\BibPrefix{A}
\bibliographystylemy{disser}
\bibliographymy{thesis}

\renewcommand\bibsection{\nsection{Цитированная литература}}

\def\BibPrefix{}
\bibliographystyle{disser}
\bibliography{thesis}
% ----------------------------------------------------------------

\end{document}

### 2012-07-16 AffineLieAlgebras/Thesis/common.tex
Edits from paper version. Text duplication mostly fixed.
Autoref bibliography added

@@
 рецензируемых журналах~\citemy{2010arXiv1007.0318L,2011arXiv1102.1702L,2011arXiv1111.6787L,NazarovJETPletters}, $5$ статей в
-сборниках тезисов и трудов конференций \cite{2011arXiv1112.4354N,2010LyakhovskyNazarovMQFT,Nazarov2008,NazarovACSM2009,2012arXiv1204.1855L}, и в препринте \cite{2011arXiv1107.4681N}.
+сборниках тезисов и трудов конференций \citemy{2011arXiv1112.4354N,2010LyakhovskyNazarovMQFT,Nazarov2008,NazarovACSM2009,2012arXiv1204.1855L}, и в препринте \citemy{2011arXiv1107.4681N}.
 }
@@
 Кроме того, сплинт корневой системы простой конечномерной алгебры Ли приводит к возникновению новых соотношений на струнные функции и функции ветвления соответствующего аффинного расширения.
-Эти соотношения обсуждаются в разделе
+Эти соотношения обсуждаются в разделе \ref{sec:splints-affine}.
 

### 2012-07-17 AffineLieAlgebras/Thesis/autoref.tex
Autoref bibliography added
More changes to autoreferat

@@
 % Практическая значимость
-\valuesection
-\valuetext
+%\valuesection
+%\valuetext
 
@@
 
-\nsection{Содержание работы}
+\contentsection
+\contenttext
 
-\textbf{Во Введении} обоснована актуальность диссертационной работы,
-сформулирована цель и аргументирована научная новизна исследований, показана
-практическая значимость полученных результатов, представлены выносимые на
-защиту научные положения.
-
-\textbf{В первой главе} ...
-
-Содержание первой главы.
-
-Результаты первой главы опубликованы в
-работе~\citemy{Ivanov_1999_Journal_17_173}.
-
-\textbf{Во второй главе} ...
-
-Содержание второй главы.
-
-Результаты второй главы опубликованы в
-работе~\citemy{Petrov_2001_Journal_23_12321}.
-
-\textbf{В третьей главе} ...
-
-Содержание третьей главы.
-
-Результаты третьей главы опубликованы в
-работе~\citemy{Sidorov_2002_Journal_32_1531}.
-
-\textbf{В Заключении}
-
+%%  \nsection{Содержание работы}
+%%  
+%%  \textbf{Во Введении} обоснована актуальность диссертационной работы,
+%%  сформулирована цель и аргументирована научная новизна исследований, показана
+%%  практическая значимость полученных результатов, представлены выносимые на
+%%  защиту научные положения.
+%%  
+%%  \textbf{В первой главе} ...
+%%  
+%%  Содержание первой главы.
+%%  
+%%  Результаты первой главы опубликованы в
+%%  работе~\cite{2010arXiv1007.0318L}
+%%  
+%%  \textbf{Во второй главе} ...
+%%  
+%%  Содержание второй главы.
+%%  
+%%  Результаты второй главы опубликованы в
+%%  работе~\citemy{Petrov_2001_Journal_23_12321}.
+%%  
+%%  \textbf{В третьей главе} ...
+%%  
+%%  Содержание третьей главы.
+%%  
+%%  Результаты третьей главы опубликованы в
+%%  работе~\citemy{Sidorov_2002_Journal_32_1531}.
+%%  
+%%  \textbf{В Заключении}
+%%  
 % ----------------------------------------------------------------
@@
 \bibliographystylemy{disser}
-\bibliographymy{thesis}
+\bibliographymy{bibliography}
 
@@
 \bibliographystyle{disser}
-\bibliography{thesis}
+\bibliography{bibliography}
 % ----------------------------------------------------------------

### 2012-07-17 AffineLieAlgebras/Thesis/common.tex
More changes to autoreferat

@@
 \mkcommonsect{actuality}{Актуальность работы}{%
- Проблема вычисления коэффициентов ветвления для представлений алгебр Ли стоит уже многие десятилетия.
-Она актуальна для различных физических приложений.
-Вместе с тем, в отличие от кратностей весов не существует особенно эффективных алгоритмов.
+  Почти тридцать лет конформная теория поля в двух измерениях привлекает огромное внимание исследователей \cite{belavin1984ics}.
+Эта теория используется для описания критического поведения в двумерных статистических системах.
+Благодаря наличию бесконечномерной алгебры симметрии двумерная конформная теория поля может быть сформулирована аксиоматически.
+Помимо математической красоты теория обладает огромной практической ценностью -- с ее использованием было получено множество результатов и численных предсказаний в изучении критического поведения в двумерных системах \cite{difrancesco1997cft,henkel1999conformal}.
+Методы двумерной конформной теории поля с успехом применяются также при изучении эффекта Кондо \cite{cox1998exotic,affleck1993exact} и дробного квантового эффекта Холла \cite{moore1991nonabelions}.
+
+Поиски строгого математического доказательства для предсказаний двумерной конформной теории поля \cite{cardy1992critical} в последние годы привели к большому количеству новых идей и результатов в дискретном комплексном анализе \cite{smirnov2001critical,duminil2011conformal,smirnov2010discrete}.
+
+Теория представлений бесконечномерных алгебр Ли играет определяющую роль в изучении моделей конформной теории поля.
+Помимо алгебры Вирасоро, наличие которой является определяющим для двумерной конформной теории поля, большую роль играют аффинные алгебры Ли.
+Изучение аффинных алгебр Ли было начато Виктором Кацем и Робертом Муди в 1960-х годах с попытки обобщения классификации простых конечномерных алгебр Ли на бесконечномерный случай \cite{kac1968simple,moody1968new}.
+Первоначально интерес к этим алгебрам был связан с модулярными свойствами характеров их модулей \cite{kac1984infinite,macdonald1971affine}.
+После возникновения двумерной конформной теории поля были предложены модели Весса-Зумино-Новикова-Виттена \cite{witten1984nab}, а затем и coset-модели \cite{Goddard198588}, в которых теория представлений аффинных алгебр Ли играет определяющую роль.
+
+Моделям Весса-Зумино-Новикова-Виттена и coset-моделям в последние десятилетия были посвящены тысячи работ.
+Большой интерес вызывает и теория представлений аффинных алгебр Ли.
+Вместе с тем, в теории представлений многие вопросы по-прежнему остаются не решенными.
+Например, проблема вычисления коэффициентов ветвления для представлений алгебр Ли стоит уже многие десятилетия.
+Она актуальна для различных физических приложений в coset-моделях конформной теории поля.
+Вместе с тем, в отличие от проблемы вычисления кратностей весов, для вычисления коэффициентов ветвления не существовало особенно эффективных алгоритмов.
 }
 
-\mkcommonsect{objective}{Цель диссертационной работы}{%
+\mkcommonsect{objective}{Цели и задачи работы}{%
  Разработка рекуррентного подхода к функциям ветвления аффинных алгебр Ли, его связь с проблемами теории представлений и его приложения в моделях конформной теории поля.
@@
 \mkcommonsect{struct}{Структура и объем диссертации}{%
-Диссертация состоит из шести глав.
+Диссертация состоит из введения и шести глав, содержит 157 страниц и 30 рисунков. Список литературы включает 151 наименование.
 
-Глава \ref{cha:CFT} является вводной.
+}
+
+\mkcommonsect{content}{Содержание работы}{%
+
+\textbf{Во Введении} обоснована актуальность диссертационной работы,
+сформулирована цель и аргументирована научная новизна исследований, показана
+практическая значимость полученных результатов, представлены выносимые на
+защиту научные положения.
+
+\textbf{Глава 1} носит обзорный характер.
 В ней мы даем аксиоматическую формулировку конформной теории поля, описываем модели Весса-Зумино-Новикова-Виттена и coset-модели.
@@
 Основной проблемой данной диссертации является изучение редукции модулей аффинных и конечномерных алгебр Ли на модули подалгебр, вычисление коэффициентов ветвления.
-В главе \ref{cha:affine-lie-algebras} мы вводим основные понятия теории представлений аффинных алгебр Ли и выводим основное рекуррунтное соотношение на коэффициенты ветвления.
 
-В следующей главе \ref{cha:BGG} мы проясняем связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
+\textbf{В главе 2} мы вводим основные понятия теории представлений аффинных алгебр Ли и выводим основное рекуррунтное соотношение на коэффициенты ветвления.
+Основные результаты данной главы опубликованы в работе \citemy{2010arXiv1007.0318L}.
 
-Глава \ref{cha:splints} посвящена сплинтам -- расщеплением корневой системы алгебры Ли в объединение образов корневых систем двух алгебр, не обязательно являющихся подалгебрами данной алгебры.
+В следующей \textbf{главе 3} мы проясняем связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
+Результаты третьей главы опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}
+
+\textbf{Глава 4} посвящена сплинтам -- расщеплением корневой системы алгебры Ли в объединение образов корневых систем двух алгебр, не обязательно являющихся подалгебрами данной алгебры.
 Если одна из алгебр является подалгеброй, то сплинт приводит к резкому упрощению в вычислении коэффициентов ветвления -- они совпадают с кратностями весов в модуле другой алгебры.
@@
 Кроме того, сплинт корневой системы простой конечномерной алгебры Ли приводит к возникновению новых соотношений на струнные функции и функции ветвления соответствующего аффинного расширения.
-Эти соотношения обсуждаются в разделе \ref{sec:splints-affine}.
+Эти соотношения обсуждаются в разделе 4.4.
+Данные результаты опубликованы в статьях \citemy{2011arXiv1111.6787L,2012arXiv1204.1855L}.
 
-Заключительная глава \ref{cha:applications} посвящена практическим приложениям результатов диссертации.
-В разделе \ref{sec:SLE} мы  описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
-Раздел \ref{cha:computational-methods} представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли и реализованного с использованием методов диссертации.
+Заключительная \textbf{глава 5} посвящена практическим приложениям результатов диссертации.
+В разделе 5.1 мы  описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
+Эти результаты были опубликованы нами в работах \citemy{NazarovJETPletters,2011arXiv1112.4354N}.
+Раздел 5.2 представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли и реализованного с использованием методов диссертации.
+Вычислительным методам посвящены наши работы \citemy{2011arXiv1107.4681N,NazarovACSM2009,Nazarov2008}.
 

### 2012-07-18 AffineLieAlgebras/Thesis/intro.tex
More changes to autoreferat
Macros and new commands are moved to separate file, some text is added to the authoreferat.

@@
 
-%\actualitysection
-%\actualitytext
+\actualitysection
+\actualitytext
 
 % Цель диссертационной работы
-% \objectivesection
-
-% \objectivetext
+ \objectivesection
+ \objectivetext
 
 % Научная новизна
-% \noveltysection
-% \noveltytext
+ \noveltysection
+ \noveltytext
 
 % Практическая ценность
-% \valuesection
-% \valuetext
+ \valuesection
+ \valuetext
 
@@
 % Личный вклад автора
-%\contribsection
-%\contribtext
+\contribsection
+\contribtext
 
@@
 \structtext
+
+% Краткое содержание работы
+%\contentsection
+%\contenttext
+
+Глава \ref{cha:CFT} носит обзорный характер.
+В ней мы даем аксиоматическую формулировку конформной теории поля, описываем модели Весса-Зумино-Новикова-Виттена и coset-модели.
+Затем мы демонстрируем роль аффинных алгебр в описании этих моделей и приводим основные понятия теории представлений, использующиеся в диссертации.
+Кроме того, мы обсуждаем конформную теорию поля на области с границей, так как она оказывается связана со стохастическим описанием решеточных моделей.
+
+Основной проблемой данной диссертации является изучение редукции модулей аффинных и конечномерных алгебр Ли на модули подалгебр, вычисление коэффициентов ветвления.
+
+В главе \ref{cha:affine-lie-algebras} мы показываем, что структура сингулярного элемента определяет свойства модуля алгебры Ли, доказываем лемму о разложении сингулярного элемента и выводим основное рекуррунтное соотношение на коэффициенты ветвления.
+Основные результаты данной главы опубликованы в работе \citemy{2010arXiv1007.0318L}.
+
+В следующей главе \ref{cha:BGG} мы проясняем связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
+Результаты третьей главы опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}
+
+Глава \ref{cha:splints} посвящена сплинтам -- расщеплением корневой системы алгебры Ли в объединение образов корневых систем двух алгебр, не обязательно являющихся подалгебрами данной алгебры.
+Если одна из алгебр является подалгеброй, то сплинт приводит к резкому упрощению в вычислении коэффициентов ветвления -- они совпадают с кратностями весов в модуле другой алгебры.
+Основная часть главы посвящена доказательству этого факта.
+Кроме того, сплинт корневой системы простой конечномерной алгебры Ли приводит к возникновению новых соотношений на струнные функции и функции ветвления соответствующего аффинного расширения.
+Эти соотношения обсуждаются в разделе \ref{sec:splints-affine}.
+Данные результаты опубликованы в статьях \citemy{2011arXiv1111.6787L,2012arXiv1204.1855L}.
+
+Заключительная глава \ref{cha:applications} посвящена практическим приложениям результатов диссертации.
+В разделе \ref{sec:SLE} мы  описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
+Эти результаты были опубликованы нами в работах \citemy{NazarovJETPletters,2011arXiv1112.4354N}.
+Раздел \ref{cha:computational-methods} представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли и реализованного с использованием методов диссертации.
+Вычислительным методам посвящены наши работы \citemy{2011arXiv1107.4681N,NazarovACSM2009,Nazarov2008}.
+
 %%% Local Variables: 

### 2012-07-18 AffineLieAlgebras/Thesis/common.tex
Macros and new commands are moved to separate file, some text is added to the authoreferat.

@@
 
-\mkcommonsect{content}{Содержание работы}{%
-
-\textbf{Во Введении} обоснована актуальность диссертационной работы,
-сформулирована цель и аргументирована научная новизна исследований, показана
-практическая значимость полученных результатов, представлены выносимые на
-защиту научные положения.
-
-\textbf{Глава 1} носит обзорный характер.
-В ней мы даем аксиоматическую формулировку конформной теории поля, описываем модели Весса-Зумино-Новикова-Виттена и coset-модели.
-Затем мы демонстрируем роль аффинных алгебр в описании этих моделей и приводим основные понятия теории представлений, использующиеся в диссертации.
-Кроме того, мы обсуждаем конформную теорию поля на области с границей, так как она оказывается связана со стохастическим описанием решеточных моделей.
-
-Основной проблемой данной диссертации является изучение редукции модулей аффинных и конечномерных алгебр Ли на модули подалгебр, вычисление коэффициентов ветвления.
-
-\textbf{В главе 2} мы вводим основные понятия теории представлений аффинных алгебр Ли и выводим основное рекуррунтное соотношение на коэффициенты ветвления.
-Основные результаты данной главы опубликованы в работе \citemy{2010arXiv1007.0318L}.
-
-В следующей \textbf{главе 3} мы проясняем связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
-Результаты третьей главы опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}
-
-\textbf{Глава 4} посвящена сплинтам -- расщеплением корневой системы алгебры Ли в объединение образов корневых систем двух алгебр, не обязательно являющихся подалгебрами данной алгебры.
-Если одна из алгебр является подалгеброй, то сплинт приводит к резкому упрощению в вычислении коэффициентов ветвления -- они совпадают с кратностями весов в модуле другой алгебры.
-Основная часть главы посвящена доказательству этого факта.
-Кроме того, сплинт корневой системы простой конечномерной алгебры Ли приводит к возникновению новых соотношений на струнные функции и функции ветвления соответствующего аффинного расширения.
-Эти соотношения обсуждаются в разделе 4.4.
-Данные результаты опубликованы в статьях \citemy{2011arXiv1111.6787L,2012arXiv1204.1855L}.
-
-Заключительная \textbf{глава 5} посвящена практическим приложениям результатов диссертации.
-В разделе 5.1 мы  описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
-Эти результаты были опубликованы нами в работах \citemy{NazarovJETPletters,2011arXiv1112.4354N}.
-Раздел 5.2 представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли и реализованного с использованием методов диссертации.
-Вычислительным методам посвящены наши работы \citemy{2011arXiv1107.4681N,NazarovACSM2009,Nazarov2008}.
-
-}
+%%  \mkcommonsect{content}{Содержание работы}{%
+%%  
+%%  }
 

### 2012-07-18 AffineLieAlgebras/Thesis/autoref.tex
Macros and new commands are moved to separate file, some text is added to the authoreferat.

@@
 \graphicspath{{figures/}}
+
+\input{macro}
 
@@
 
-\contentsection
-\contenttext
+% \contentsection
+% \contenttext
 
-%%  \nsection{Содержание работы}
+\nsection{Содержание работы}
+
+\textbf{Во Введении} обоснована актуальность диссертационной работы,
+сформулирована цель и аргументирована научная новизна исследований, показана
+практическая значимость полученных результатов, представлены выносимые на
+защиту научные положения.
+
+\textbf{Глава 1} носит обзорный характер.
+В ней мы даем аксиоматическую формулировку конформной теории поля, описываем модели Весса-Зумино-Новикова-Виттена и coset-модели.
+Затем мы демонстрируем роль аффинных алгебр в описании этих моделей и приводим основные понятия теории представлений, использующиеся в диссертации.
+Кроме того, мы обсуждаем конформную теорию поля на области с границей, так как она оказывается связана со стохастическим описанием решеточных моделей.
+
+\textbf{В главе 2} мы показываем, что структура сингулярного элемента определяет свойства модуля алгебры Ли, доказываем лемму о разложении сингулярного элемента и выводим основное рекуррунтное соотношение на коэффициенты ветвления.
+Основные результаты данной главы опубликованы в работе \citemy{2010arXiv1007.0318L}.
+
+Формула Вейля-Каца для формальных характеров интегрируемых модулей старшего веса конечномерных и аффинных алгебр Ли имеет вид
+\begin{equation}
+  \label{eq:1}
+  \mathrm{ch} V^{(\mu)} = \frac{\Psi^{(\mu)}}{R},
+\end{equation}
+где $\Psi^{(\mu)}$ -- сингулярный элемент модуля, а $R=\prod_{\alpha\in \Delta^+}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}$ -- знаменатель Вейля.
+Сингулярный элемент определяется набором сингулярных весов модуля и имеет разный вид для разных типов модулей старшего веса.
+Например, $\Psi^{(\mu)}=\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}$ для неприводимых модулей.
+Заметим, что знаменатель Вейля является универсальным объектом, характеризующим корневую систему алгебры Ли, а свойства модуля определяются сингулярным элементом.
+
+Процедура редукции состоит в разложении модуля алгебры Ли $\gf$ в сумму модулей некоторой подалгебры $\af$
+\begin{equation}
+  \label{eq:2}
+  L_{\gf\downarrow \af}^{\mu }=\bigoplus
+\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
+\end{equation}
+Используя оператор проекции  $\pi_{\af}$ (на весовое пространство $\hf_{\af}^*$), перепишем это разложение для формальных характеров:
+\begin{equation}
+\label{branching1}
+ \pi _{\af}\circ ch\left( L^{\mu }\right)
+ =\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu)}ch\left( L_{\af}^{\nu }\right) .
+\end{equation}
+Нас интересуют коэффициенты ветвления $b^{(\mu)}_{\nu}$.
+
+Для любой алгебры $\gf$ и подалгебры $\af\subset \gf$ можно построить  подалгебру $\afb$ такую, что 
+\begin{eqnarray}
+\label{delta-a-ort}
+\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\gf}|
+\forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} , \\
+\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
+}^{+}|\forall h \in \hf_{\af};  \beta^{+}\left(h \right)=0  \right\} .
+\end{eqnarray}
+Обозначим через $W_{\afb}$ подгруппу группы Вейля $W$, порожденную отражениями $w _{\beta }$, соответствующими корням $\beta \in \Delta _{\afb}^{+}$ .
+Подсистема  $\Delta _{\af_{\perp }}$ определяет подалгебру $\af_{\perp }$ с подалгеброй Картана $\hf_{\afb}$.
+
+Мы доказываем следующую лемму о разложении сингулярного элемента:
+\begin{lemma}
+\label{lemma}
+Пусть $\left( \af,\afb \right)$ -- ортогональная пара редуктивных подалгебр $\gf$ и  $\widetilde{\afb}=\afb\oplus \hf_{\perp }$, $\widetilde{\af}=\af\oplus\hf_{\perp }$ ,
+
+$L^{\mu }$ -- модуль старшего веса с сингулярным элементом $\Psi ^{\left(\mu \right)}$ ,
+
+$R_{\af_{\perp }}$ -- знаменатель Вейля для подалгебры $\af_{\perp }$.
+
+Тогда элемент  $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi _{\af}\left( \frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}\right) $ можно разложить в сумму по  $u\in U$ (см.
+(\ref{U-def})) сингулярных весов $e^{\mu _{\af}\left( u\right) }$ с коэффициентами $\epsilon (u)\mathrm{\dim}\left( L_{\widetilde{\afb}}^{\mu _{\widetilde{\afb}}\left( u\right) }\right) $:
+\begin{equation}
+\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\quad \pi _{\af}\left( \frac{\Psi^{\mu }}{R_{\af%
+_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }
+\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
+\widetilde{\af_{\perp }}}\left( u\right) }\right) e^{\mu _{\af}\left( u \right) }.
+\end{equation}
+\end{lemma}
+
+Используя эту лемму мы выводим следующее рекуррентное соотношение на сингулярные коэффициенты ветвления
+
+\begin{theorem}
+  Для сингулярных коэффициентов ветвления $k^{(\mu)}_{\nu}$ (\ref{eq:21}) выполняется соотношение
+  \begin{equation}
+    \label{recurrent-relation}
+    \begin{array}{c}
+      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+        \sum_{u\in U} \epsilon(u)\;
+        \dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
+        _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
+        \delta_{\xi-\gamma_0,\pi_{\af}(u(\mu+\rho)-\rho)}+ \right.\\
+      \left.
+        +\sum_{\gamma \in
+          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+          +\gamma }^{\left( \mu \right) }\right).
+    \end{array}
+  \end{equation}
+\end{theorem}
+
+Затем мы формулируем рекурсивный алгоритм и показываем, он позволяет эффективно вычислять коэффициенты ветвления для конечномерных и аффинных алгебр Ли.
+
+В следующей \textbf{главе 3} мы используем  разложение сингулярного элемента, чтобы показать связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
+Результаты третьей главы опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}
+
+\textbf{Глава 4} посвящена сплинтам -- расщеплением корневой системы алгебры Ли в объединение образов корневых систем двух алгебр, не обязательно являющихся подалгебрами данной алгебры.
+Если одна из алгебр является подалгеброй, то сплинт приводит к резкому упрощению в вычислении коэффициентов ветвления -- они совпадают с кратностями весов в модуле другой алгебры.
+Основная часть главы посвящена доказательству этого факта.
+Кроме того, сплинт корневой системы простой конечномерной алгебры Ли приводит к возникновению новых соотношений на струнные функции и функции ветвления соответствующего аффинного расширения.
+Эти соотношения обсуждаются в разделе 4.4.
+Данные результаты опубликованы в статьях \citemy{2011arXiv1111.6787L,2012arXiv1204.1855L}.
+
+Заключительная \textbf{глава 5} посвящена практическим приложениям результатов диссертации.
+В разделе 5.1 мы  описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
+Эти результаты были опубликованы нами в работах \citemy{NazarovJETPletters,2011arXiv1112.4354N}.
+Раздел 5.2 представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли и реализованного с использованием методов диссертации.
+Вычислительным методам посвящены наши работы \citemy{2011arXiv1107.4681N,NazarovACSM2009,Nazarov2008}.
+
 %%  

### 2012-07-19 AffineLieAlgebras/Thesis/autoref.tex
Some more changes in autoref

@@
 
-Используя эту лемму мы выводим следующее рекуррентное соотношение на сингулярные коэффициенты ветвления
+Теперь мы можем ввести ``веер вложения'', который необходим для формулировки рекуррентных соотношений:
+\begin{definition}
+\label{fan-definition} Рассмотрим произведение
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left( 1-e^{-\pi
+_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
+}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
+)e^{-\gamma }  \label{eq:142}
+\end{equation}
+и носитель $\Phi _{\af\subset \gf}\subset P_{\af}$ функции $s(\gamma )=\det \left( \gamma \right) $ :
+\begin{equation}
+\Phi _{\af\subset \gf}=\left\{ \gamma \in P_{\af}|s(\gamma
+)\neq 0\right\}   \label{eq:37}
+\end{equation}
+Упорядочение корней в  $\co{\Delta _{\af}}$ индуцирует естественное упорядочение весов в $P_{\af}$. Обозначим через $\gamma_{0}$ наименьший вектор $\Phi _{\af\subset \gf}$. Множество
+\begin{equation}
+\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \gf}\right\} \setminus \left\{ 0\right\}
+\label{fan-defined}
+\end{equation}
+называется  \textit{веером вложения}.
+\end{definition}
+Веер вложения универсален и зависит только от вложения $\af\to\gf$ и не зависит от модуля $L^{(\mu)}$.
+
+Числитель описывает ветвление в терминах сингулярных элементов и, как элемент  $\mathcal{E}\left( \gf \right)$, допускает разложение в виде:
+\begin{equation}
+  \label{eq:21}
+  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
+        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\af}}k_{\lambda
+  }^{\left( \mu \right) }e^{\lambda }.
+\end{equation}
+Здесь $k_{\lambda}^{\left( \mu \right) }$  -- целочисленные коэффициенты, их знаки зависят от длины элементов группы Вейля в 
+$\Psi _{\left( \af\right) }^{\left( \nu \right) }$. Важно заметить, что $k_{\lambda}^{\left( \mu \right) }$ совпадают с коэффициентами ветвления для всех весов $\nu$ в главной камере Вейля:
+\begin{equation}
+  \label{eq:119}
+  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{для} \; \nu\in \bar{C}_{\mathfrak{a}}.
+\end{equation}
+Мы называем коэффициенты $k_{\lambda}$ сингулярными коэффициентами ветвления
+(см. также \cite{ilyin812pbc}).
+
+Теперь мы можем сформулировать основную в этой главе теорему, которая позволит нам рекуррентно вычислять коэффициенты ветвления.
 
@@
 
-Затем мы формулируем рекурсивный алгоритм и показываем, он позволяет эффективно вычислять коэффициенты ветвления для конечномерных и аффинных алгебр Ли.
+Далее мы анализируем пары $(\af,\afb)$ для простых алгебр Ли.
+Оказывается, что для ``ортогональной пары'' $(\af,\afb)$, вообще говоря, $\af\oplus\afb\not\subset\gf $.
+В частности, для серии простых конечномерных алгебр $B_n$ существуют ``ортогональные пары'' подалгебр $(B_k,B_{n-k})$.
+
+На основании рекуррентного соотношения (\ref{recurrent-relation}) сформулирован следующий алгоритм вычисления коэффициентов ветвления:
+
+\begin{enumerate}[(i)]
+\item Построить корневую систему $\Delta _{\af}$ для вложения $\af\rightarrow \gf$.
+
+\item Выбрать все положительные корни $\alpha \in \Delta ^{+}$, ортогональные к  $\af$, то есть сформировать множество $\Delta_{\afb }^{+}$.
+
+\item Построить множество $\Gamma _{\af\rightarrow \gf}$.
+Соотношение  (\ref{eq:142}) определяет знаковую функцию $s(\gamma)$ и множество $\Phi_{\af\subset \gf}$.
+Вычитание наименьшего веса $\gamma_0$ дает веер вложения (\ref{fan-defined}):
+ $\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{\af\subset \gf}\right\} \setminus \left\{ 0\right\}$.
+
+\item Построить множество $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
+)-\rho ;\;w \in W\right\} $ сингулярных весов для  $\gf$-модуля $L^{(\mu )}$.
+
+\item Выбрать веса $\left\{ \mu _{\widetilde{\afb}}\left( w\right) =\pi _{\widetilde{\afb}}\left[ w(\mu +\rho
+)-\rho \right] -\mathcal{D}_{\afb}\in \overline{C_{\widetilde{\afb}}}\right\} $.
+Так как множество  $\Delta_{\afb }^{+}$ фиксировано, легко осуществить проверку принадлежности веса $\mu _{\widetilde{\afb}}\left( w\right) $ к главной камере Вейля $\overline{C_{\widetilde{\afb}}}$ (достаточно вычислить скалярные произведения с фундаментальными весами $\afb^{+}$).
+
+\item Для весов $\mu _{\widetilde{\afb}}\left( w\right) $ вычислить размерности соответствующих модулей, $\mathrm{\dim }\left(L_{\widetilde{\afb}}^{\mu _{\widetilde{\afb}}\left( u\right) }\right) $, используя формулу Вейля для размерностей.
+Затем построить сингулярный элемент $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
+
+\item Вычислить сингулярные коэффициенты ветвления используя рекуррентное соотношение (\ref{recurrent-relation}) и выбрать среди них те, которые соответствуют весам в главной камере Вейля $\overline{C_{\af}}$.
+\end{enumerate}
+
+Остальные разделы главы 2 содержат примеры вычислений с использованием предложенного алгоритма, а также описание роли функций ветвления в формулировке конформной теории поля на торе и в coset-моделях конформной теории поля.
 
 В следующей \textbf{главе 3} мы используем  разложение сингулярного элемента, чтобы показать связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
-Результаты третьей главы опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}
+Результаты третьей главы опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}.
+
+%%  3 Коэффициенты ветвления и обобщенная резольвента Бернштейна-Гельфанда-Гельфанда
+%%    3.1 Ортогональная подалгебра и сингулярные элементы
+%%      3.1.1 Разложение сингулярного элемента.
+%%      3.1.2 Фомулы Вейля-Верма.
+%%    3.2 БГГ резольвента и ветвление
+%%    3.3 Заключение
+
+Оказывается, что для полупростой конечномерной алгебры $\gf$  и полупростой конечномерной подалгебры $\af$ алгебра $\afb$, определенная в формуле (\ref{branching1}), является регулярной.
+Тогда отношение знаменателей Вейля порождает параболические модули Верма.
+
+%%     4 Сплинты корневых систем и функции ветвления
+%%       4.1 Вложения и сплинты
+%%       4.2 Как стебли определяют функции кратности
+%%       4.3 Примеры
+%%       4.4 Сплинты и соотношения для аффинных алгебр Ли
+%%       4.5 Заключение
+%%       4.6 Приложение
+%%     5 Практические приложения
+%%       5.1 Coset-модели и критическое поведение
+%%         5.1.1 Введение
+%%         5.1.2 Эволюция Шрамма-Левнера
+%%         5.1.3 Мартингалы эволюции Шрамма-Левнера и корреляционные функции в конформной теории поля
+%%         5.1.4 Модели Весса-Зумино-Новикова-Виттена и эволюция Шрамма-Левнера
+%%         5.1.5 Coset-модели и эволюция Шрамма-Левнера
+%%           5.1.5.1 Примеры
+%%         5.1.6 Coset-модели и интегрируемые деформации конформной теории поля
+%%         5.1.7 О связи мартингалов coset-моделей с классификацией операторов смены граничного условия
+%%       5.2 Вычислительные методы для теории представлений аффинных алгебр Ли
+%%         5.2.1 Структуры данных
+%%           5.2.1.1 Веса
+%%           5.2.1.2 Корневые системы
+%%           5.2.1.3 Формальные элементы
+%%           5.2.1.4 Модули
+%%         5.2.2 Основные алгоритмы
+%%       5.3 Примеры вычислений
+%%         5.3.1 Разложение тензорных произведений модулей конечномерных алгебр Ли на неприводимые
+%%         5.3.2 Ветвления и параболические модули Верма
+%%         5.3.3 Струнные функции аффинных алгебр Ли и модели конформной теории поля
+%%         5.3.4 Функции ветвления и coset-модели конформной теории поля
+%%       5.4 Заключение
+%%
 

### 2012-07-20 AffineLieAlgebras/Thesis/2.tex
Some duplication is removed from the chapter 3. Authoreferat completed

@@
 
-Для интересующих нас модулей формула Вейля-Каца для  $\mathrm{ch}\left( L^{\mu }\right) $ может быть записана через сингулярные элементы \cite{humphreys1997introduction},
-\begin{equation*}
-\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
-)-\rho },
-\end{equation*}
-а именно:
-\begin{equation}
-\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
-^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
-\label{Weyl-Kac21}
-\end{equation}
-То же верно и для подмодулей $\mathrm{ch}\left( L_{\frak{a}}^{\nu
-}\right) $ в формуле (\ref{branching12})
-\begin{equation*}
-\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
-\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
-}^{\left( \nu \right) }}{R_{\frak{a}}},
-\end{equation*}
-где
-\begin{equation*}
-\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
-}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
-\end{equation*}
-Применяя формулу  (\ref{Weyl-Kac21}) к правилу ветвления  (\ref{branching12}) мы получаем соотношение, связывающее сингулярные элементы $\Psi ^{\left( \mu
-\right) }$ и $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
-\begin{eqnarray}
-\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho
-)-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}%
-(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{%
-\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{\frak{a}})-\rho _{%
-\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}}^{+}}(1-e^{-\beta })^{\mathrm{%
-mult}_{\frak{a}}(\beta )}},  \notag  \label{eq:132} \\
-\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
-&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}%
-}^{\left( \nu \right) }}{R_{\frak{a}}}.
-\end{eqnarray}
-
 \subsection{Разложение сингулярного элемента.}
@@
 
-Теперь мы выполним разложение сингулярного элемента  $\Psi ^{\left(\mu \right) }$ на сингулярные элементы модулей ортогонального партнера.
+Выполним разложение сингулярного элемента  $\Psi ^{\left(\mu \right) }$ на сингулярные элементы модулей ортогонального партнера.
 Это разложение в целом аналогично разложению в Лемме \ref{lemma}, однако в данном случае его составляющими являются сингулярные элементы ортогонального партнера $\afb$.

### 2012-07-20 AffineLieAlgebras/Thesis/common.tex
Some duplication is removed from the chapter 3. Authoreferat completed

@@
 \mkcommonsect{actuality}{Актуальность работы}{%
+
   Почти тридцать лет конформная теория поля в двух измерениях привлекает огромное внимание исследователей \cite{belavin1984ics}.
@@
 \mkcommonsect{objective}{Цели и задачи работы}{%
+
  Разработка рекуррентного подхода к функциям ветвления аффинных алгебр Ли, его связь с проблемами теории представлений и его приложения в моделях конформной теории поля.
@@
 \mkcommonsect{novelty}{Научная новизна}{%
-  Предложен эффективный алгоритм для вычисления коэффициентов ветвления, показана его связь с резольвентой Бернштейна-Гельфанда-Гельфанда.
+
+  В диссертации впервые решены следующие задачи:
+  \begin{itemize}
+  \itemполучено эффективное рекуррентное соотношение для коэффициентов ветвления модулей аффинных и конечномерных алгебр Ли на модули не максимальных подалгебр.
+  \item Показано, что наличие расщепления приводит к существенному упрощению при вычислении коэффициентов ветвления.
+  \item Показана связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
+  \item Предложено обобщение стохастического процесса Шрамма-Лёвнера на случай систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля.
+  \end{itemize}
 }
@@
 \mkcommonsect{value}{Практическая значимость}{%
-  Результаты работы                                  
+
+  Предложен эффективный алгоритм для вычисления коэффициентов ветвления.
+Данный алгоритм реализован в пакете программ {\bf Affine.m}, который может быть использован для решения задач теории представлений конечномерных и аффинных алгебр Ли, возникающих в различных областях физики, начиная от изучения атомных и молекулярных спектров и заканчивая конформной теорией поля и интегрируемыми системами.
 }
@@
 \mkcommonsect{results}{%
+
 На защиту выносятся следующие основные результаты и положения:}{%
@@
 \mkcommonsect{approbation}{Апробация работы}{%
+
   Материалы диссертации докладывались на семинарах кафедры физики высоких энергий и элементарных частиц СПбГУ, на семинарах в лаборатории имени П.Л.
@@
 \mkcommonsect{pub}{Публикации.}{%
-Материалы диссертации опубликованы в $10$ печатных работах, из них $4$ статьи в
-рецензируемых журналах~\citemy{2010arXiv1007.0318L,2011arXiv1102.1702L,2011arXiv1111.6787L,NazarovJETPletters}, $5$ статей в
-сборниках тезисов и трудов конференций \citemy{2011arXiv1112.4354N,2010LyakhovskyNazarovMQFT,Nazarov2008,NazarovACSM2009,2012arXiv1204.1855L}, и в препринте \citemy{2011arXiv1107.4681N}.
+
+Материалы диссертации опубликованы в $10$ печатных работах, из них $5$ статей в
+рецензируемых журналах~\citemy{2010arXiv1007.0318L,2011arXiv1102.1702L,2011arXiv1111.6787L,NazarovJETPletters,2011arXiv1107.4681N}, $5$ статей в
+сборниках тезисов и трудов конференций \citemy{2011arXiv1112.4354N,2010LyakhovskyNazarovMQFT,Nazarov2008,NazarovACSM2009,2012arXiv1204.1855L}.
 }
@@
 \mkcommonsect{struct}{Структура и объем диссертации}{%
+
 Диссертация состоит из введения и шести глав, содержит 157 страниц и 30 рисунков. Список литературы включает 151 наименование.

### 2012-07-20 AffineLieAlgebras/Thesis/autoref.tex
Some duplication is removed from the chapter 3. Authoreferat completed

--- 2012-07-18 AffineLieAlgebras/Thesis/autoref.tex
@@
                        & & \emph{ученое звание}, \\
-                       & & \emph{Мудров Андрей И}
+                       & & \emph{Мудров Андрей Игоревич}
 \\
@@
 % Цель диссертационной работы
-\objectivesection
-\objectivetext
+%\objectivesection
+%\objectivetext
 
@@
 Для любой алгебры $\gf$ и подалгебры $\af\subset \gf$ можно построить  подалгебру $\afb$ такую, что 
-\begin{eqnarray}
+\begin{equation}
 \label{delta-a-ort}
-\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\gf}|
-\forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} , \\
-\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
-}^{+}|\forall h \in \hf_{\af};  \beta^{+}\left(h \right)=0  \right\} .
-\end{eqnarray}
+\Delta _{\af_{\perp }} :=\left\{ \beta \in \Delta _{\gf}|
+\forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} 
+\end{equation}
 Обозначим через $W_{\afb}$ подгруппу группы Вейля $W$, порожденную отражениями $w _{\beta }$, соответствующими корням $\beta \in \Delta _{\afb}^{+}$ .
 Подсистема  $\Delta _{\af_{\perp }}$ определяет подалгебру $\af_{\perp }$ с подалгеброй Картана $\hf_{\afb}$.
+Пусть
+$\hf_{\perp }^{\ast }:=\left\{ \eta \in \hf_{\perp \af}^{\ast
+}|\forall h \in \hf_{\af\oplus \af_{\perp}}; \eta \left( h \right)=0 \right\}$, тогда имеет место разложение подалгебры Картана $\hf=\frak{\hf_{\af}}\oplus \hf_{\afb}\oplus\hf_{\perp }$.
+
+Для подалгебр из ортогональной пары  $\left( \af,\afb\right) $ рассмотрим соответствующие векторы Вейля $\rho _{\af}$ и $\rho _{\af_{\perp }}$, и образуем так называемые  ''дефекты'' вложения $\mathcal{D}_{\af}$ и $\mathcal{D}_{\af_{\perp }}$ :
+\begin{equation}
+\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
+\end{equation}
+\begin{equation}
+\label{defect-perp}
+\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi_{\afb}\rho .
+\end{equation}
+
+Рассмотрим сингулярные веса  $\left\{\left( w(\mu +\rho )-\rho \right)|w  \in W \right\}$  модуля старшего веса  $L_{\gf}^{\mu }$ и их проекции на $h_{\widetilde{\af_{\perp }}}^{\ast }$ (дополнительно сдвинутые на дефект $-\mathcal{D}_{\af_{\perp }}$):
+\begin{equation*}
+\mu _{\widetilde{\af_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
+a}_{\perp }}}\circ\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp
+}},\quad w\in W.
+\end{equation*}
+Среди весов  $\left\{\mu _{\widetilde{\af_{\perp }}}\left( w\right)|w\in W\right\}$ выберем находящиеся в главной камере Вейля $\overline{C_{\widetilde{\afb}}}$ и обозначим через $U$ множество представителей $u$ классов смежности $W/W_{\af_{\perp }}$, таких что
+\begin{equation}
+U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
+\in \overline{C_{\widetilde{\af_{\perp }}}}\right\} \quad .
+\label{U-def}
+\end{equation}
+Для множества  $U$ введем веса
+\begin{equation*}
+\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho %
+\right] +\mathcal{D}_{\af_{\perp }}.
+\end{equation*}
+Кроме того, мы будем пользоваться аналогичным определением
+\begin{eqnarray}
+\label{eq:136}
+\mu _{\tilde \af}\left( u\right) :=\pi _{\tilde \af}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb},\\
+\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}.
+\end{eqnarray}
 
@@
 
-Используя эту лемму мы выводим следующее рекуррентное соотношение на сингулярные коэффициенты ветвления
+Теперь мы можем ввести ``веер вложения'', который необходим для формулировки рекуррентных соотношений:
+\begin{definition}
+\label{fan-definition} Рассмотрим произведение
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left( 1-e^{-\pi
+_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
+}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
+)e^{-\gamma }  \label{eq:142}
+\end{equation}
+и носитель $\Phi _{\af\subset \gf}\subset P_{\af}$ функции $s(\gamma )=\det \left( \gamma \right) $ :
+\begin{equation}
+\Phi _{\af\subset \gf}=\left\{ \gamma \in P_{\af}|s(\gamma
+)\neq 0\right\}   \label{eq:37}
+\end{equation}
+Упорядочение корней в  $\co{\Delta _{\af}}$ индуцирует естественное упорядочение весов в $P_{\af}$. Обозначим через $\gamma_{0}$ наименьший вектор $\Phi _{\af\subset \gf}$. Множество
+\begin{equation}
+\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \gf}\right\} \setminus \left\{ 0\right\}
+\label{fan-defined}
+\end{equation}
+называется  \textit{веером вложения}.
+\end{definition}
+Веер вложения универсален и зависит только от вложения $\af\to\gf$ и не зависит от модуля $L^{(\mu)}$.
+
+Введем сингулярные коэффициенты ветвления следующим образом:
+\begin{eqnarray}
+  \label{eq:3}
+  k^{(\mu)}_{\xi}=b^{(\mu)}_{\xi} \;\text{если}\; \xi\in \bar C_{\af}\\
+  k^{(\mu)}_{\xi}=\epsilon(w) b^{(\mu)}_{w(\xi+\rho_{af})-\rho_{\af}} \;\text{где}\; w\in W_{\af}:w(\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}
+\end{eqnarray}
+
+Теперь мы можем сформулировать основную теорему, которая позволит нам рекуррентно вычислять коэффициенты ветвления.
 
 \begin{theorem}
-  Для сингулярных коэффициентов ветвления $k^{(\mu)}_{\nu}$ (\ref{eq:21}) выполняется соотношение
+  Для сингулярных коэффициентов ветвления $k^{(\mu)}_{\nu}$ выполняется соотношение
   \begin{equation}
@@
 
-Затем мы формулируем рекурсивный алгоритм и показываем, он позволяет эффективно вычислять коэффициенты ветвления для конечномерных и аффинных алгебр Ли.
+Далее мы анализируем пары $(\af,\afb)$ для простых алгебр Ли.
+Оказывается, что для ``ортогональной пары'' $(\af,\afb)$, вообще говоря, $\af\oplus\afb\not\subset\gf $.
+В частности, для серии простых конечномерных алгебр $B_n$ существуют ``ортогональные пары'' подалгебр $(B_k,B_{n-k})$.
 
-В следующей \textbf{главе 3} мы используем  разложение сингулярного элемента, чтобы показать связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
-Результаты третьей главы опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}
+На основании рекуррентного соотношения (\ref{recurrent-relation}) сформулирован алгоритм вычисления коэффициентов ветвления.
+Остальные разделы главы 2 содержат примеры вычислений с использованием предложенного алгоритма, а также описание роли функций ветвления в формулировке конформной теории поля на торе и в coset-моделях конформной теории поля.
+
+\textbf{В главе 3} мы используем  разложение сингулярного элемента, чтобы показать связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
+Результаты третьей главы опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}.
+
+Оказывается, что для полупростой конечномерной алгебры $\gf$  и полупростой конечномерной подалгебры $\af$ алгебра $\afb$, определенная в формуле (\ref{branching1}), является регулярной.
+Отношение знаменателей Вейля порождает параболические модули Верма.
+Сингулярный элемент  $\Psi ^{\left( \mu \right) }$ может быть разложен в сумму по  $u\in U$ (см.
+(\ref{U-def})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
+$\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
+\begin{equation}
+\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\widetilde{%
+\mathfrak{a}}}\left( u\right) }\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) }.  \label{sing decomp main}
+\end{equation}
+Мы доказываем следующее утверждение, демонстрирующее, что разложение сингулярного элемента связано с разложением характера неприводимого модуля в комбинацию характеров обобщенных модулей Верма
+\begin{statement}
+%\bigskip
+Для ортогональной подалгебры  $\frak{a}_{\perp }$ в $\frak{g}$ (являющейся ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$) характер интегрируемого модуля старшего веса  $L^{\mu }$ может быть представлен в виде комбинации (с целочисленными коэффициентами) характеров параболических модулей Верма, распределенных по множеству весов $\mu _{\widetilde{\mathfrak{a}}}\left(
+u\right)$:
+\begin{equation}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{%
+\widetilde{\frak{a}}}\left( u\right) }\mathrm{ch}M_{I}^{\mu _{\frak{a}%
+_{\perp }}\left( u\right) },  \label{gen Weyl-Verma}
+\end{equation}
+где  $U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
+\overline{C_{\frak{a}_{\perp }}}\right\} $ и $I$ -- такое подмножество в  $S$, что $\Delta _{I}^{+}$ эквивалентно $\Delta _{\frak{a}_{\perp }}^{+}$.
+\end{statement}
+
+Связь редукции и (обобщенной) резольвенты Бернштейна-Гельфанда-Гельфанда дается следующим утверждением:
+\begin{statement}
+Пусть $L^{\mu }$ --  $\frak{g}$-модуль со старшим весом $\mu \in P^{+}$, и пусть регулярная подалгебра  $\afb\hookrightarrow \frak{g}$ является ортогональным партнером редуктивной подалгебры $\frak{a}\hookrightarrow \frak{g}$.
+Тогда разложение (\ref{sing decomp main}) определяет как обобщенную резольвенту $L^{\mu }$ по отношению к $\afb$, так и правила ветвления $L^{\mu }$ по отношению к $\afb$, так и правила ветвления $L^{\mu }$ по отношению к $\af$ .
+\end{statement}
 
@@
 
+\begin{definition}
+Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$. Рассмотрим отображение
+\begin{equation}
+\phi :\left\{
+\begin{array}{l}
+\Delta _{0}\hookrightarrow \Delta , \\
+P_{0}\hookrightarrow P.
+\end{array}
+\right.
+\end{equation}
+Оно называется ``вложением'', если \newline
+\noindent (a) оно вкладывает $\Delta _{0}$ в $\Delta $, и \newline
+\noindent (b) $\phi$ действует гомоморфно по отношению к группам сложения векторов в $P_{0}$ и $P$:
+\[
+\phi (\gamma )=\phi (\alpha )+\phi (\beta )
+\]
+для любой тройки $\alpha ,\beta ,\gamma \in P_{0}$, такой, что $\gamma =\alpha+\beta $.
+\end{definition}
+
+$\phi$ индуцирует вложение формальных алгебр: ${\mathcal{E}}_0\hookrightarrow \mathcal{E}$ и для образа ${\mathcal{E}}_i=\mathrm{Im}_{\phi}\left( {\mathcal{E}}_0\right)$ можно рассмотреть обратное отображение $\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+
+Заметим, что нужно различать два класса вложений: когда скалярное произведение (заданное формой Киллинга) в корневом пространстве $P_0$ инвариантно по отношению к  $\phi$ и когда оно не  $\phi$-инвариантно.
+Вложения первого класса называются ``метрическими'', второго -- ``неметрическими''.
+
+\begin{definition}
+Корневая система $\Delta$ ``расщепляется'' на  $(\Delta _{1},\Delta _{2})$, если существует два вложения  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ и $\phi _{2}:\Delta _{2}\hookrightarrow \Delta $, где (a) $\Delta $ -- несвязное объединение образов $\phi _{1}$ и $\phi _{2}$, и (b) ни ранг  $\Delta _{1}$, ни ранг  $\Delta _{2}$ не превосходит ранга $\Delta $.
+\end{definition}
+
+Эквивалентно, можно сказать, что  $(\Delta_1,\Delta_2)$  -- ``сплинт'' (расщепление)  $\Delta$ и мы можем обозначить его через $\Delta \approx (\Delta_1,\Delta_2)$.
+Каждая из компонент  $\Delta_1$ и $\Delta_2$ называется ``стеблем'' сплинта $(\Delta_1,\Delta_2)$.
+
+Чтобы показать связь веера вложения со сплинтом рассмотрим случай, когда один из стеблей $\Delta _{1}=\Delta _{\af}$  является подсистемой корневой системы.
+
+Сплинт $\Delta \approx (\Delta _{1},\Delta _{2})$ называется ``инъективным'', если $\Delta _{1}=\Delta _{\af}$, -- подсистема корневой системы $\Delta $, соответствующая регулярной редуктивной подалгебре $\af\hookrightarrow \gf$.
+
+В случае инъективного сплинта второй стебель $\Delta _{\sfr}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (аналогично формуле (\ref{eq:142})) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$.
+Обозначим через $\Delta_{\mathfrak{s}0}$ кообраз второго вложения $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$.
+Верна следующая гипотеза.
+
+\begin{conjecture}
+Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением
+\begin{equation}
+\prod_{\beta \in \Delta _{\sfr}^{+}}\left( 1-e^{-\beta }\right)
+=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
+\end{equation}
+\end{conjecture}
+
+В случае инъективного сплинта мы можем сказать, что подалгебра $\af\hookrightarrow \gf$ расщепляется $\Delta$ (и назовем $\af$ ``расщепляющей подалгеброй'' алгебры $\gf$).
+Сплинты были классифицированы в работе \cite{richter2008splints}  (см.
+Приложение в конце главы) и первые три класса сплинтов в этой классификации инъективны.
+
+\begin{Prop}
+\begin{equation}
+\frac{e^{\rho _{\gf}}}{\prod_{\beta \in \Delta _{\sfr%
+}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\sfr%
+}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\sfr}^{\widetilde{\mu }%
+}}M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
+\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}=\sum_{\nu \in P_{\af}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
+\label{singular main-4}
+\end{equation}
+Любой вес с ненулевой кратностью, входящий в правую часть равенства, равен одному из старших весов в разложении. Кратность $M_{\left( \sfr
+\right) \widetilde{\nu }}^{\widetilde{\mu }}$ веса  $\widetilde{\nu}\in \mathcal{N}_{\sfr}^{\widetilde{\mu }}$ определяет коэффициент ветвления  $b_{\nu }^{(\mu )}$ для старшего веса $\nu =\left( \mu-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
+\[
+b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}^{(\mu )}=M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}.
+\]
+\end{Prop}
+
 Заключительная \textbf{глава 5} посвящена практическим приложениям результатов диссертации.
+
  В разделе 5.1 мы  описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
 Эти результаты были опубликованы нами в работах \citemy{NazarovJETPletters,2011arXiv1112.4354N}.
-Раздел 5.2 представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли и реализованного с использованием методов диссертации.
+
+Стохастический процесс, который удовлетворяет уравнению 
+\begin{equation}
+\label{eq:166}
+  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
+\end{equation}
+называется {\it эволюцией Шрамма-Левнера} на верхней полуплоскости $\mathbb{H}$.
+Здесь $\xi_{t}$ -- Броуновское движение.
+Динамика конца  $z_{t}$ критической кривой $\gamma_{t}$ (конец следа эволюции Шрамма-Левнера) описывается уравнением $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
+Нам удобнее использовать отображение $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$.
+
+Мы обобщаем анализ соответствия между эволюцией Шрамма-Левнера и конформной теорией поля на случай coset-моделей \cite{Goddard198588}. Такие модели задаются алгеброй Ли $\gf$ и ее подалгеброй $\af$. 
+$G/A$-coset модель конформной теории поля может быть реализована как ВЗНВ-модель (с калибровочной группой $G$), взаимодействующая с чисто калибровочными полями, с калибровочной группой $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
+Действие записывается через поля $\gamma:\mathbb{C}\to G$ and $\alpha,\bar\alpha:\mathbb{C}\to A$:
+\begin{multline}
+\label{eq:178}
+      S_{G/A}(\gamma, \alpha)=\\
+-\frac{k}{8\pi}\int_{S^2} d^2x\; {\cal K} (\gamma^{-1}\partial^{\mu}\gamma,\gamma^{-1}\partial_{\mu}\gamma)-
+ \frac{k }{24\pi} \int_{B}\epsilon_{ijk} {\cal K}\left(
+    \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^i},
+      \left[\tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^j}
+      \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^k}\right]\right) d^3y+\\
++
+      \frac{k}{4\pi}\int_{S^2} d^{2}z \left(\mathcal{K}(\alpha, \gamma^{-1}\bar \partial \gamma)-\mathcal{K}(\bar \alpha, (\partial \gamma ) \gamma^{-1})\right.
+      \left.+\mathcal{K}(\alpha,\gamma^{-1}\bar \alpha \gamma)-\mathcal{K}(\alpha,\bar \alpha)\right).
+\end{multline}
+Здесь через  $\mathcal{K}$ обозначена форма Киллинга в алгебре Ли $\gf$, соответствующей группе Ли $G$.
+
+Если мы фиксируем  $A$-калибровку, у нас останется  $G/A$ калибровочная инвариантность.
+Значит мы должны добавить случайные калибровочные преобразования к эволюции Шрамма-Левнера, аналогично случаю ВЗНВ-моделей  (См.
+\cite{bettelheim2005stochastic}).
+Обозначим через $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) генераторы представления алгебры $\gf$ (соответственно, представления $\af$), соответствующего примарному полю $\varphi_{i}$.
+
+Теперь рассмотрим наблюдаемые в присутствии следа эволюции Шрамма-Левнера.
+Математическое ожидание решеточной наблюдаемой $\mathcal{O}$ на верхней полуплоскости можно вычислить как сумму ожиданий этой наблюдаемой в присутствии (конечной части) траектории эволюции Шрамма-Левнера  $\gamma_{t}$ вплоть до некоторого времени $t$, умноженных на вероятность этой траектории:
+\begin{equation*}
+  \prec \mathcal{O} \succ_{\mathbb{H}}=\mathbb{E}\left[\prec\mathcal{O}\succ_{\gamma_{t}}\right]=\sum_{\gamma_{t}} P\left[C_{\gamma_{t}}\right] \prec \mathcal{O} \succ_{\gamma_{t}}
+\end{equation*}
+Решеточная наблюдаемая  $\prec \mathcal{O} \succ_{\mathbb{H}}$ не зависит от  $t$, следовательно $\prec\mathcal{O}\succ_{\gamma_{t}}$ -- мартингал.
+Это должно выполняться и для ее непрерывного предела, дающегося комбинацией корреляционных функций в конформной теории поля \cite{bauer2003sle}:
+\begin{equation}
+  \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
+  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}
+%% =
+%%   \frac{\left<^{g_{t}}
+%% \mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
+\label{eq:162}
+\end{equation}
+Мы рассматриваем теорию с границей, так что мы должны использовать модели граничной конформной теории поля и накладывать соответствующие граничные условия.
+В случае верхней полуплоскости корреляционные функции в граничной конформной теории поля могут быть переписаны как корреляционные функции для теории на всей плоскости, но с удвоенным числом полей.
+
+Мы предполагаем, что $\mathcal{F}$ содержит некоторый набор примарных полей  $\varphi_{i}$ с конформными весами $h_{i}$.
+Так как мы рассматриваем граничную конформную теорию поля, мы должны добавить объемные поля в сопряженных точках  $\bar z_{i}$.
+Кроме того, у нас есть операторы смены граничного условия   $\phi$ на конце следа эволюции Шрамма-Левнера и на бесконечности.
+
+Рассмотрим, что происходит с наблюдаемыми при эволюции следа SLE $\gamma_{t}$ с момента   $t$ до $t+ dt$.
+
+Через  $\mathcal{G}_{i}$ мы обозначили  генераторы инфинитезимальных преобразований примарных $\varphi_{i}$:$d\varphi_{i}(w_{i}) = \mathcal{G}_{i}\varphi_{i}(w_{i})$.
+Нормируем дополнительное $\left(\dim\gf\right)$-мерное Броуновское движение следующим образом: $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
+Тогда генератор преобразования поля равен
+\begin{equation}
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right).
+\label{eq:179}
+\end{equation}
+То есть мы фиксировали  $A$-калибровку, разрешив случайное блуждание только в направлении, ортогональном подалгебре $\af$.
+
+Формула Ито, дает выражение для дифференциала $\mathcal{F}$, который равняется нулю в силу условия мартингала.
+Это равенство можно переписать в виде следующего алгебраического условия на граничное состояние $\phi(0)\left|0\right>$:
+\begin{multline}
+\label{eq:182}
+  \left<0\left|\phi(\infty)\varphi_{1}(w_{1})\dots\varphi_{2N}(w_{2N})\right.\right.\\
+  \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
+\left.\phi(0)|0\right>=0.
+\end{multline}
+Так как набор  $\{\phi_{i}\}$ состоит из произвольных примарных полей, мы заключаем, что 
+\begin{multline}
+\label{eq:126}
+|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
+\cdot\phi(0)|0>
+\end{multline}
+является нулевым состоянием, то есть соответствуют сингулярному весу в представлении алгебры Вирасоро.
+Действуя повышающими операторами мы получаем соотношения, связывающие параметры стохастического процесса и coset-модели конформной теории поля:
+\begin{equation}
+ (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0.
+ \label{eq:184}
+\end{equation}
+\begin{equation}
+\label{eq:185}
+ -12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
+(C_{\mu}-\tilde{C}_{\nu})=0,
+\end{equation}
+здесь $C_{\mu}=(\mu,\mu+2\rho)$ и $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ -- это собственные значения квадратичных операторов Казимира $\sum_{a}t^{a}t^{a}$ и $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ алгебр Ли $\gf$ и $\af$.
+Из уравнения  \eqref{eq:184},\eqref{eq:185} мы сразу получаем значения  $\kappa,\tau$ для каждой пары весов $(\mu,\nu)$ алгебр $\gf$ и $\af$.
+Для coset-реализаций минимальных и парафермионных моделей эти результаты совпадают с тем, что было ранее получено путем введения стохастического процесса с дополнительным дискретным случайным блужданием  \cite{santachiara2008sle}.
+
+Остальная часть главы представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли и реализованного с использованием методов диссертации.
 Вычислительным методам посвящены наши работы \citemy{2011arXiv1107.4681N,NazarovACSM2009,Nazarov2008}.

### 2012-07-24 AffineLieAlgebras/Thesis/1.tex
Some changes in autoreferat and thesis. I need to sort out numbering of remarks, theorems etc

@@
 Нас интересуют коэффициенты ветвления $b^{(\mu)}_{\nu}$.
-
 \subsubsection{Ортогональная подалгебра и веер вложения.}
@@
 Эффективность полученного алгоритма была продемонстрирована на различных примерах.
-В частности, мы рассмотрели построение модулярно-инвариантных статсумм в методе конформных вложений и coset-конструкцию моделей рациональной конформной теории поля.
-Эти конструкции полезны при изучении ВЗНВ-моделей, возникающих в контексте AdS/CFT соответствия \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km}.
-
+В частности, мы построили примеры модулярно-инвариантных статсумм методом конформных вложений и статсумм в coset-моделях рациональной конформной теории поля.
 Дальнейшее улучшение алгоритма может быть достигнуто при использовании техники сложенных вееров \cite{il2010folded}.
-Нужно отметить, что даже в случае струнных функций явное решение соответствующих рекуррентных соотношений представляет собой сложную проблему (см.
+% Нужно отметить, что даже в случае струнных функций явное решение соответствующих рекуррентных соотношений представляет собой сложную проблему (см.
 подробности в работе\cite{il2010folded}).

### 2012-07-24 AffineLieAlgebras/Thesis/common.tex
Some changes in autoreferat and thesis. I need to sort out numbering of remarks, theorems etc

@@
 
-  Почти тридцать лет конформная теория поля в двух измерениях привлекает огромное внимание исследователей \cite{belavin1984ics}.
+  Последние тридцать лет конформная теория поля в двух измерениях привлекает огромное внимание исследователей \cite{belavin1984ics}.
 Эта теория используется для описания критического поведения в двумерных статистических системах.
 Благодаря наличию бесконечномерной алгебры симметрии двумерная конформная теория поля может быть сформулирована аксиоматически.
-Помимо математической красоты теория обладает огромной практической ценностью -- с ее использованием было получено множество результатов и численных предсказаний в изучении критического поведения в двумерных системах \cite{difrancesco1997cft,henkel1999conformal}.
+Помимо математической красоты теория обладает огромной практической ценностью -- с ее использованием было получено большое количество результатов и численных предсказаний в изучении критического поведения в двумерных системах \cite{difrancesco1997cft,henkel1999conformal}.
 Методы двумерной конформной теории поля с успехом применяются также при изучении эффекта Кондо \cite{cox1998exotic,affleck1993exact} и дробного квантового эффекта Холла \cite{moore1991nonabelions}.
@@
 
-Теория представлений бесконечномерных алгебр Ли играет определяющую роль в изучении моделей конформной теории поля.
-Помимо алгебры Вирасоро, наличие которой является определяющим для двумерной конформной теории поля, большую роль играют аффинные алгебры Ли.
+Теория представлений бесконечномерных алгебр Ли является важным инструментом изучения моделей конформной теории поля.
+Помимо алгебры Вирасоро, наличие которой обязательно в двумерной конформной теории поля, большую роль играют аффинные алгебры Ли.
 Изучение аффинных алгебр Ли было начато Виктором Кацем и Робертом Муди в 1960-х годах с попытки обобщения классификации простых конечномерных алгебр Ли на бесконечномерный случай \cite{kac1968simple,moody1968new}.
@@
 Большой интерес вызывает и теория представлений аффинных алгебр Ли.
-Вместе с тем, в теории представлений многие вопросы по-прежнему остаются не решенными.
+Вместе с тем, в теории представлений многие вопросы по-прежнему не имеют простых решений.
 Например, проблема вычисления коэффициентов ветвления для представлений алгебр Ли стоит уже многие десятилетия.
@@
 
-\mkcommonsect{novelty}{Научная новизна}{%
+\mkcommonsect{novelty}{Научная новизна и практическая значимость}{%
 
@@
   \begin{itemize}
-  \itemполучено эффективное рекуррентное соотношение для коэффициентов ветвления модулей аффинных и конечномерных алгебр Ли на модули не максимальных подалгебр.
+  \item Получено эффективное рекуррентное соотношение для коэффициентов ветвления модулей аффинных и конечномерных алгебр Ли на модули не максимальных подалгебр.
   \item Показано, что наличие расщепления приводит к существенному упрощению при вычислении коэффициентов ветвления.
@@
   \end{itemize}
+  Алгоритм вычисления коэффициентов ветвления реализован в пакете  {\bf Affine.m} для популярной системы компьютерной алгебры {\it Mathematica}.
+Пакет {\bf Affine.m} может быть использован для решения задач теории представлений конечномерных и аффинных алгебр Ли, возникающих в различных областях физики, начиная от изучения атомных и молекулярных спектров и заканчивая конформной теорией поля и интегрируемыми системами.
 }
@@
 
-  Предложен эффективный алгоритм для вычисления коэффициентов ветвления.
-Данный алгоритм реализован в пакете программ {\bf Affine.m}, который может быть использован для решения задач теории представлений конечномерных и аффинных алгебр Ли, возникающих в различных областях физики, начиная от изучения атомных и молекулярных спектров и заканчивая конформной теорией поля и интегрируемыми системами.
 }
@@
 \item Предложено обобщение стохастического процесса Шрамма-Лёвнера на случай систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля
-\item Продемонстрирована роль сингулярных элементов в построении мартингалов стохастического процесса Шрамма-Лёвнера, то есть проиллюстрировано применение алгебраических методов теории представлений аффинных алгебр Ли в изучении критического поведения в двумерных решеточных моделях
-\item Реализованы различные алгоритмы для вычислений в теории представлений конечномерных и аффинных алгебр Ли
+%\item Продемонстрирована роль сингулярных элементов в построении мартингалов стохастического процесса Шрамма-Лёвнера, то есть проиллюстрировано применение алгебраических методов теории представлений аффинных алгебр Ли в изучении критического поведения в двумерных решеточных моделях
+\item Разработан пакет программ {\bf Affine.m}, реализующий различные алгоритмы для вычислений в теории представлений конечномерных и аффинных алгебр Ли
 \end{itemize}

### 2012-07-25 AffineLieAlgebras/Thesis/autoref.tex
Synopsis revised.

@@
 Затем мы демонстрируем роль аффинных алгебр в описании этих моделей и приводим основные понятия теории представлений, использующиеся в диссертации.
+Мы указываем на то, что основные свойства интегрируемых модулей старшего веса определяются структурой сингулярного элемента, что выражается в формуле Вейля-Каца для формальных характеров.
 Кроме того, мы обсуждаем конформную теорию поля на области с границей, так как она оказывается связана со стохастическим описанием решеточных моделей.
 
-\textbf{В главе 2} мы показываем, что структура сингулярного элемента определяет свойства модуля алгебры Ли, доказываем лемму о разложении сингулярного элемента и выводим основное рекуррунтное соотношение на коэффициенты ветвления.
+\textbf{В главе 2} мы выводим основное рекуррунтное соотношение на коэффициенты ветвления.
+Пользуясь тем, что структура сингулярного элемента определяет свойства модуля алгебры Ли, мы формулируем и доказываем лемму о разложении сингулярного элемента.
+Такое разложение определяет правила ветвления и позволяет сформулировать рекуррентную процедуру редукции.
 Основные результаты данной главы опубликованы в работе \citemy{2010arXiv1007.0318L}.
@@
 Например, $\Psi^{(\mu)}=\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}$ для неприводимых модулей.
-Заметим, что знаменатель Вейля является универсальным объектом, характеризующим корневую систему алгебры Ли, а свойства модуля определяются сингулярным элементом.
+Про этом знаменатель Вейля является универсальным объектом, характеризующим корневую систему алгебры Ли, а свойства модуля определяются сингулярным элементом.
 
@@
 
-Для любой алгебры $\gf$ и подалгебры $\af\subset \gf$ можно построить  подалгебру $\afb$ такую, что 
-\begin{equation}
-\label{delta-a-ort}
-\Delta _{\af_{\perp }} :=\left\{ \beta \in \Delta _{\gf}|
-\forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} 
-\end{equation}
+Для любой алгебры $\gf$ и подалгебры $\af\subset \gf$ можно построить  подалгебру $\afb$ такую, что $\Delta _{\af_{\perp }} =\left\{ \beta \in \Delta _{\gf}| \forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\}$.
+
 Обозначим через $W_{\afb}$ подгруппу группы Вейля $W$, порожденную отражениями $w _{\beta }$, соответствующими корням $\beta \in \Delta _{\afb}^{+}$ .
@@
 
-Для подалгебр из ортогональной пары  $\left( \af,\afb\right) $ рассмотрим соответствующие векторы Вейля $\rho _{\af}$ и $\rho _{\af_{\perp }}$, и образуем так называемые  ''дефекты'' вложения $\mathcal{D}_{\af}$ и $\mathcal{D}_{\af_{\perp }}$ :
-\begin{equation}
-\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
-\end{equation}
-\begin{equation}
-\label{defect-perp}
-\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi_{\afb}\rho .
-\end{equation}
+Для подалгебр из ортогональной пары  $\left( \af,\afb\right) $ рассмотрим соответствующие векторы Вейля $\rho _{\af}$ и $\rho _{\af_{\perp }}$, и образуем так называемые  ''дефекты'' вложения $\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho$, $\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi_{\afb}\rho$.
 
@@
 \end{equation*}
-Среди весов  $\left\{\mu _{\widetilde{\af_{\perp }}}\left( w\right)|w\in W\right\}$ выберем находящиеся в главной камере Вейля $\overline{C_{\widetilde{\afb}}}$ и обозначим через $U$ множество представителей $u$ классов смежности $W/W_{\af_{\perp }}$, таких что
-\begin{equation}
-U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
-\in \overline{C_{\widetilde{\af_{\perp }}}}\right\} \quad .
-\label{U-def}
-\end{equation}
-Для множества  $U$ введем веса
-\begin{equation*}
-\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho %
-\right] +\mathcal{D}_{\af_{\perp }}.
-\end{equation*}
-Кроме того, мы будем пользоваться аналогичным определением
-\begin{eqnarray}
-\label{eq:136}
-\mu _{\tilde \af}\left( u\right) :=\pi _{\tilde \af}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb},\\
-\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}.
-\end{eqnarray}
+Среди весов  $\left\{\mu _{\widetilde{\af_{\perp }}}\left( w\right)|w\in W\right\}$ выберем находящиеся в главной камере Вейля $\overline{C_{\widetilde{\afb}}}$.
+Множество $U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
+\in \overline{C_{\widetilde{\af_{\perp }}}}\right\}$ состоит из элементов группы Вейля, переводящих старший вес в главную камеру Вейля подалгебры $\tilde\afb$ (с учетом сдвига на $\rho$ и на дефект).
+Элементы $U$ являются представителями классов смежности $W/W_{\af_{\perp }}$.
+Каждому элементу  $U$ поставим в соответствие вес $\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}$.
+Аналогичным образом определим $\mu _{\tilde \af}\left( u\right) :=\pi _{\tilde \af}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}$ и $\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}$
 
@@
 
-Тогда элемент  $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi _{\af}\left( \frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}\right) $ можно разложить в сумму по  $u\in U$ (см.
-(\ref{U-def})) сингулярных весов $e^{\mu _{\af}\left( u\right) }$ с коэффициентами $\epsilon (u)\mathrm{\dim}\left( L_{\widetilde{\afb}}^{\mu _{\widetilde{\afb}}\left( u\right) }\right) $:
+Тогда элемент  $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi _{\af}\left( \frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}\right) $ можно разложить в сумму по  $u\in U$ сингулярных весов $e^{\mu _{\af}\left( u\right) }$ с коэффициентами $\epsilon (u)\mathrm{\dim}\left( L_{\widetilde{\afb}}^{\mu _{\widetilde{\afb}}\left( u\right) }\right) $:
 \begin{equation}
@@
 Введем сингулярные коэффициенты ветвления следующим образом:
-\begin{eqnarray}
+\begin{equation}
   \label{eq:3}
-  k^{(\mu)}_{\xi}=b^{(\mu)}_{\xi} \;\text{если}\; \xi\in \bar C_{\af}\\
-  k^{(\mu)}_{\xi}=\epsilon(w) b^{(\mu)}_{w(\xi+\rho_{af})-\rho_{\af}} \;\text{где}\; w\in W_{\af}:w(\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}
-\end{eqnarray}
+  \begin{array}{l}
+  k^{(\mu)}_{\xi}=b^{(\mu)}_{\xi} \quad\text{если}\quad \xi\in \bar C_{\af}\\
+  k^{(\mu)}_{\xi}=\epsilon(w) b^{(\mu)}_{w(\xi+\rho_{af})-\rho_{\af}} \quad\text{где}\; w\in W_{\af}:w(\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}.
+  \end{array}
+\end{equation}
 
@@
 Отношение знаменателей Вейля порождает параболические модули Верма.
-Сингулярный элемент  $\Psi ^{\left( \mu \right) }$ может быть разложен в сумму по  $u\in U$ (см.
-(\ref{U-def})) сингулярных элементов $\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$ с коэффициентами
-$\epsilon (u)e^{\mu _{\widetilde{\mathfrak{a}}}\left( u\right) }$:
+Сингулярный элемент  $\Psi ^{\left( \mu \right) }$ может быть разложен в сумму по  $u\in U$  сингулярных элементов $\Psi _{\afb}^{\mu _{\afb}\left( u\right) }$ с коэффициентами
+$\epsilon (u)e^{\mu _{\widetilde{\af}}\left( u\right) }$:
 \begin{equation}
@@
 Обозначим через $\Delta_{\mathfrak{s}0}$ кообраз второго вложения $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$.
-Верна следующая гипотеза.
+Верно следующее утверждение.
 
-\begin{conjecture}
+\begin{statement}
 Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением
@@
 \end{equation}
-\end{conjecture}
+\end{statement}
 
@@
 
+Если выполнено техническое требование на структуру сингулярного элемента, то верно следующее свойство:
 \begin{Prop}
@@
 $G/A$-coset модель конформной теории поля может быть реализована как ВЗНВ-модель (с калибровочной группой $G$), взаимодействующая с чисто калибровочными полями, с калибровочной группой $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
-Действие записывается через поля $\gamma:\mathbb{C}\to G$ and $\alpha,\bar\alpha:\mathbb{C}\to A$:
+Действие записывается через поля $\gamma:\mathbb{C}\to G$ и $\alpha,\bar\alpha:\mathbb{C}\to A$:
 \begin{multline}

### 2012-07-25 AffineLieAlgebras/Thesis/common.tex
Minor changes in intro
Synopsis revised.

@@
 
-  Последние тридцать лет конформная теория поля в двух измерениях привлекает огромное внимание исследователей \cite{belavin1984ics}.
+  Последние тридцать лет конформная теория поля в двух измерениях привлекает большое внимание исследователей \cite{belavin1984ics}.
 Эта теория используется для описания критического поведения в двумерных статистических системах.
@@
 
-Моделям Весса-Зумино-Новикова-Виттена и coset-моделям в последние десятилетия были посвящены тысячи работ.
+Моделям Весса-Зумино-Новикова-Виттена и coset-моделям  посвящены тысячи работ.
 Большой интерес вызывает и теория представлений аффинных алгебр Ли.
@@
 \mkcommonsect{value}{Практическая значимость}{%
-
 }

### 2012-07-25 AffineLieAlgebras/Thesis/review.tex
Some misprints fixed
Some changes in first chapter

@@
 
+\begin{definition}
+\label{def:singular-weight}
   {\it Сингулярным} называется вектор $v_{\lambda}$, такой что $E^{\alpha}v_{\lambda}=0,\; \forall \alpha\in \Delta^+$. Вес $\lambda$, отвечающий сингулярному вектору, также называется сингулярным. 
+\end{definition}
+В следующем разделе мы показываем, что структура модулей старшего веса определяется сингулярным элементом -- элементом алгебры, порожденной формальными экспонентами весов, который является линейной комбинацией экспонент сингулярных весов.
 
@@
 Формальный элемент, стоящий в числителе формулы Вейля, называется {\it сингулярным элементом}.
-В случае модулей Верма он задается старшим весом, а у неприводимых модулей и параболических модулей Верма является комбинацией формальных экспонент сингулярных весов.
+В случае модуля Верма сингулярный элемент задается старшим весом, а у неприводимых модулей и параболических модулей Верма является комбинацией формальных экспонент сингулярных весов.
 Разложение сингулярных элементов модулей старшего веса играет существенную роль в данной диссертации.
@@
 
-Применение рекуррентных соотношений \eqref{eq:14} и \eqref{eq:15} для вычисления кратностей весов обсуждается в разделе \ref{sec:comp-algor}.
+Практические аспекты применения рекуррентных соотношений \eqref{eq:14} и \eqref{eq:15} для вычисления кратностей весов обсуждаются в разделе \ref{sec:comp-algor}.
 

### 2012-07-26 AffineLieAlgebras/Thesis/1.tex
Added improvements from V.D.

@@
 В разделе \ref{sec:branching} мы выводим формулы разложения, основывающиеся на аномальных коэффициентах ветвления и описываем алгоритм редукции интегрируемых модулей старшего веса $L_{\mathfrak{g}}$ по отношению к редуктивной подалгебре  $\mathfrak{a}\subset \mathfrak{g}$.
-В разделе \ref{sec:branching-examples} мы представляем различные примеры применения алгоритма для конечномерных (\ref{sec:finite-dimens-lie}) и аффинных алгебр Ли и обсуждаем их роль в моделях конформной теории поля (\ref{sec:phys-appl}).
+В разделе \ref{sec:finite-dimens-lie}  мы представляем различные примеры вычисления коэффициентов ветвления для конечномерных алгебр Ли для пояснения работы алгоритма.
+Затем мы обсуждаем преимущества алгоритма (раздел \ref{sec:branching-algor-comparison}), после чего приводим вычисления коэффициентов ветвления, возникающие в моделях конформной теории поля (\ref{sec:phys-appl}).
 Выводы к главе изложены в разделе \ref{sec:conclusion}.
@@
 Один из инструментов в ней -- это множество весов $\Gamma_{\af\rightarrow \gf}$, называющееся веером вложения.
+Веер вложения  $\Gamma\subset \Delta$ был впервые введен в работе  \cite{lyakhovsky1996rra} как подмножество корневой системы, описывающее рекуррентные свойства коэффициентов ветвления для максимальных вложений.
+Веер вложения -- это эффективный инструмент для изучения правил ветвления.
+Позднее в работах \cite{2010arXiv1007.0318L, ilyin812pbc} эта конструкция была обобщена на не-максимальные вложения и бесконечномерные алгебры Ли.
 Так как мы рассматриваем общую ситуацию (где вложение не обязательно максимально) понятие веера вложения нуждается в уточнении:
@@
 \begin{remark}
-Это соотношение можно рассматривать как обобщение формулы Вейля для сингулярного элемента  $\Psi _{\gf}^{\mu }$: векторы  $\mu_{\af}\left(u\right)$ играют роль сингулярных весов, но вместо определителей $\epsilon (u)$ появляются произведения  $\epsilon(u)\mathrm{\dim }\left( L_{\widetilde{\afb}}^{\mu _{\widetilde{\afb}}\left(u\right) }\right).$ Действительно, при  $\frak{a=g}$ подалгебры  $\afb$ и $\hf_{\perp }$ тривиальны, $U=W$ , и исходная формула Вейля с легкостью восстанавливается.
+Это соотношение является обобщением формулы Вейля для сингулярного элемента  $\Psi _{\gf}^{\mu }$: векторы  $\mu_{\af}\left(u\right)$ играют роль сингулярных весов, но вместо определителей $\epsilon (u)$ появляются произведения  $\epsilon(u)\mathrm{\dim }\left( L_{\widetilde{\afb}}^{\mu _{\widetilde{\afb}}\left(u\right) }\right).$ Действительно, при  $\frak{a=g}$ подалгебры  $\afb$ и $\hf_{\perp }$ тривиальны, $U=W$ , и исходная формула Вейля с легкостью восстанавливается.
 \end{remark}
@@
 \begin{theorem}
+  \label{recurrent-relation-theorem}
   Для сингулярных коэффициентов ветвления $k^{(\mu)}_{\nu}$ (\ref{eq:21}) выполняется соотношение
@@
 
-\section{Примеры}
-\label{sec:branching-examples}
-
-\subsection{Ветвления модулей конечномерных алгебр Ли}
+\section{Примеры вычисления коэффициентов ветвления модулей конечномерных алгебр Ли}
 \label{sec:finite-dimens-lie}
@@
 \end{eqnarray*}
+
+\section{Преимущества рекуррентного алгоритма для коэффициентов ветвления}
+\label{sec:branching-algor-comparison}
+
+При вычислении коэффициентов ветвления использование формулы Фрейденталя требует полного построения формальных характеров представления алгебры и всех представлений подалгебры, входящих в его разложение.
+Такой подход становится непрактичным для большого ранга алгебры и подалгебры, например, при максимальных вложениях.
+
+Альтернативный алгоритм описан в разделе \ref{sec:algorithm}.
+Рассмотренный там же пример регулярного вложения \ref{sec:someth-high-dimens}  $B_{2}\subset B_{4}$ позволяет сделать следующее сравнение числа требующихся операций.
+В данном примере веер вложения состоит из 24 элементов.
+Для разложения модуля алгебры  $B_{4}$ необходимо построить подмножество сингулярных весов модуля, проектирующихся в главную камеру Вейля подалгебры $B_{2}$.
+Полное множество сингулярных весов состоит из 384 элементов, в главную камеру Вейля проектируется не более 48, так что время на построение этого множества пренебрежимо мало, если число коэффициентов ветвления более 48.
+Мы можем оценить сверху общее число операций для вычисления коэффициентов ветвления произведением числа весов в главной камере Вейля подалгебры с ненулевыми коэффициентами ветвления на число элементов веера вложения.
+С другой стороны, при использовании алгоритма, основанного на построении всех характеров при помощи формулы Фрейденталя мы должны вычислить кратности для каждого модуля в разложении, так что общее количество операций растет с ростом числа весов в представлении быстрее, чем квадрат числа весов в главной камере Вейля подалгебры с ненулевыми коэффициентами ветвления.
+
+Чтобы проиллюстрировать эту разницу в производительности алгоритмов, мы приводим Рисунок \ref{fig:branching}, на котором показано время, необходимое для вычисления коэффициентов ветвления для вложения $B_{3}\subset B_{4}$.
+
+\begin{figure}[h]
+  \noindent\centering{
+   \includegraphics[width=100mm]{figures/branching-timing}
+  }
+  \caption{Время работы алгоритмов, основанных на применении формулы Фрейденталя \eqref{eq:15} (пунктиром)  и рекуррентного соотношения \eqref{recurrent-relation} (сплошная линия) с ростом числа весов в  $\bar C$ при вычислении коэффициентов ветвления для вложения $B_{3}\subset B_{4}$.}
+  \label{fig:branching}
+\end{figure}
+
 %\newpage
-\subsection{Примеры приложений в конформной теории поля}
+\section{Примеры приложений в конформной теории поля}
 \label{sec:phys-appl}

### 2012-07-26 AffineLieAlgebras/Thesis/review.tex
Added improvements from V.D.

@@
 \end{equation}
-Эта формула называется формулой Фрейденталя. Заметим, что она применима только для неприводимых модулей
-
+Эта формула называется формулой Фрейденталя. Заметим, что она применима только для неприводимых модулей.
 Практические аспекты применения рекуррентных соотношений \eqref{eq:14} и \eqref{eq:15} для вычисления кратностей весов обсуждаются в разделе \ref{sec:comp-algor}.
 
-\subsection{Конформные вложения и модулярно-инвариантные статсуммы}
+Опишем теперь проблему редукции -- разложения модуля алгебры в сумму модулей подалгебры. Пусть $L^{\mu}$ -- модуль конечномерной или аффинной алгебры Ли $\gf$, а $\af\subset\gf$ -- подалгебра. Тогда 
+\begin{equation}
+  L_{\gf\downarrow \af}^{\mu }=\bigoplus
+\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
+\end{equation}
+Если ввести оператор проекции  $\pi_{\af}:\hf^{*}\to\hf_{\af}^*$ на весовое пространство подалгебры, то разложение модуля можно переписать как линейную комбинацию формальных характеров:
+\begin{equation}
+ \pi _{\af}\circ ch\left( L^{\mu }\right)
+ =\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu)}ch\left( L_{\af}^{\nu }\right) .
+\end{equation}
+При этом возникает задача вычисления  коэффициентов ветвления $b^{(\mu)}_{\nu}$.
+Заметим, что коэффициенты ветвления, в принципе, можно находить путем построения характера исходного модуля $L^{\mu}_{\gf}$ (что требует вычисления всех кратностей весов) и последовательного вычитания характеров модулей $L^{\nu}_{\af}$, входящих в разложение.
+Однако такое вычисление весьма трудоемко, поэтому в главе \ref{cha:affine-lie-algebras} мы выводим эффективное рекуррентное соотношение (Теорема \ref{recurrent-relation-theorem}), позволяющее вычислять коэффициенты ветвления без нахождения кратностей весов.
+Преимущества данного алгоритма обсуждаются в разделе \ref{sec:branching-algor-comparison}.
+
+Проблема редукции модулей конечномерных алгебр Ли возникает во многих областях физики, например, в физике элементарных частиц и спектроскопии.
+В следующих двух разделах мы показываем, как коэффициенты ветвления для аффинных алгебр Ли возникают при изучении моделей конформной теории поля.
+
+\subsection{Коэффициенты ветвления и модулярно-инвариантные статсуммы}
 \label{sec:modular-invariance}
@@
 В силу  равенства \eqref{eq:26} весовые векторы, соответствующие весам $L^{\mu}_{\gfh}$, сингулярным по отношению к действию $\afh$, будут образовывать модуль алгебры Вирасоро.
-Статсумма такой модели будет даваться функциями ветвления для вложения $\afh\to\gfh$.
+
+Статсумма этой модели будет даваться функциями ветвления для вложения $\afh\to\gfh$.
 Проблемы вычисления функций ветвления для аффинных алгебр Ли мы рассматриваем в главе \ref{cha:affine-lie-algebras}.
 
-Coset-модели можно реализовать, как калибровочные модели Весса-Зумино-Новикова-Виттена, если добавить дополнительные калибровочные полями  $A, \bar{A}$, принимающие значения в алгебре Ли $\af\subset \gf$, в действие ВЗНВ-модели  \cite{gawdzki1988g}:
+Coset-модели можно реализовать, как калибровочные модели Весса-Зумино-Новикова-Виттена, если добавить дополнительные калибровочные поля  $A, \bar{A}$, принимающие значения в алгебре Ли $\af\subset \gf$, в действие ВЗНВ-модели  \cite{gawdzki1988g}:
 \begin{multline}
@@
 Кроме того, имеется избыточность, так как функции ветвления для различных пар $(\mu,\nu)$ могут совпадать \cite{fuchs1996resolution,schellekens1990field}.
-
-Итак, примарные поля нумеруются парами весов  $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ алгебры $\gfh$ и подалгебры $\afh$, такими, что соответствующие функции ветвления $b^{\mu}_{\nu}(q)\neq 0$.
-Некоторые пары эквивалентны.
 Эта эквивалентность дается действием так называемых ``простых токов'' $(J,\tilde{J})$, которые являются элементами группы внешних автоморфизмов  $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ алгебры $\gfh\times\afh$, где $B(G)$ -- это центр группы Ли $G$.
@@
 Таким образом, примарные поля coset-моделей нумеруются классами эквивалентности пар весов  $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, где $(J,\tilde J)$ такие, что  конформные веса компонент равны:  $h_{J}-h_{\tilde{J}}=0$.
+
+Таким образом вычисление коэффициентов ветвления играет существенную роль в определении спектра coset-моделей конформной теории поля.
 
@@
 Мы описали двумерную конформную теорию поля и показали роль теории представлений аффинных алгебр Ли в изучении моделей Весса-Зумино-Новикова-Виттена и coset-моделей.
-В следующих главах мы используем разложение сингулярных элементов для описания свойств представлений и для вывода соотношений, позволяющих вычислять коэффициенты ветвления.
+Мы показали, что вычисление коэффициентов ветвления необходимо для построения модулярно-инвариантных статсумм ВЗНВ-моделей и для изучения coset-моделей.
+В следующей главе мы используем разложение сингулярных элементов для описания свойств представлений и для вывода соотношений, позволяющих вычислять коэффициенты ветвления.
+Кроме того, мы приведем различные примеры вычислений коэффициентов ветвления.
 %%

### 2012-07-26 AffineLieAlgebras/Thesis/3.tex
Some changes in autoreferat and thesis. I need to sort out numbering of remarks, theorems etc
Added improvements from V.D.

@@
 Richter в работе  \cite{richter2008splints}, где  были получены все сплинты для простых алгебр Ли.
-В работе так же упоминалось, что сплинт должен быть тесно связан с конструкцией веера вложения.
-Веер вложения  $\Gamma\subset \Delta$ был введен в работе  \cite{lyakhovsky1996rra} как подмножество корневой системы, описывающее рекуррентные свойства коэффициентов ветвления для максимальных вложений.
-Веер вложения -- это эффективный инструмент для изучения правил ветвления.
-Позднее в работах \cite{2010arXiv1007.0318L, ilyin812pbc} эта конструкция была обобщена на не-максимальные вложения и бесконечномерные алгебры Ли.
+В работе так же упоминалось, что сплинт должен быть тесно связан с конструкцией веера вложения, определенной в главе \ref{cha:affine-lie-algebras} (См.
+Определение \ref{fan-definition}).
 
@@
 
-Также мы продемонстрировали, что сплинт для аффинных алгебр Ли ведет к новым соотношениям на тета-функции и функции ветвления для редукции на модули конечномерных подалгебр, что может быть полезно для вычислений.
-Возможно дальнейшее обобщение этого анализа на аффинные подалгебры и применение результатов изучению coset-моделей конформной теории поля.
+Также мы продемонстрировали, что сплинт для аффинных алгебр Ли ведет к новым соотношениям на тета-функции и функции ветвления для редукции на модули конечномерных подалгебр, что сильно облегчает вычисления.
 

### 2012-07-26 AffineLieAlgebras/Thesis/5.tex
Edits from paper version. Text duplication mostly fixed.
Added improvements from V.D.

@@
 
-Необходимые сведения из теории представлений приведены в главе \ref{cha:affine-lie-algebras}.
+Необходимые сведения из теории представлений приведены в разделе \ref{sec:WZNW-models}.
 Здесь мы начинаем с описания структур данных пакета  {\bf Affine.m}, использующихся для описания различных объектов теории представлений  (раздел \ref{sec:core-datastructures}), обсуждаем алгоритмы  (раздел \ref{sec:comp-algor}) и приводим примеры  (раздел \ref{sec:examples-six}).
@@
 \end{lstlisting}
+
 \subsection{Основные алгоритмы}
 \label{sec:comp-algor}
+В пакете {\bf Affine.m} реализованы следующие основные алгоритмы:
+\begin{itemize}
+\item алгоритм построения элементов группы Вейля,
+\item алгоритм построения корневой системы,
+\item алгоритм вычисления кратностей весов в неприводимых модулях, основывающийся на формуле Фрейденталя (\ref{eq:14}),
+\item алгоритм вычисления кратностей весов в произвольных модулях, основывающийся на рекуррентной формуле (\ref{eq:15}),
+\item алгоритм вычисления коэффициентов ветвления путем полного построения модулей, входящих в разложение, по формуле Фрейденталя,
+\item алгоритм рекуррентного вычисления коэффициентов ветвления (См. Теорему \ref{recurrent-relation-theorem} и раздел \ref{sec:algorithm})
+\end{itemize}
 
-Существует два рекуррентных соотношения \eqref{eq:15}, \eqref{eq:14}, которые можно использовать для вычисления кратностей весов в неприводимых модулях. Оба алгоритма состоят из следующих шагов:
+Отметим, что существует два рекуррентных соотношения \eqref{eq:15}, \eqref{eq:14}, которые можно использовать для вычисления кратностей весов в неприводимых модулях.
+Мы реализовали два алгоритма  вычисления кратностей весов, так как каждый из них имеет свои достоинства и недостатки.
+Оба алгоритма состоят из следующих шагов:
 \begin{enumerate}
@@
 
-При вычислении коэффициентов ветвления использование формулы Фрейденталя требует полного построения формальных характеров представления алгебры и всех представлений подалгебры, входящих в его разложение.
-Такой подход становится непрактичным для большого ранга алгебры и подалгебры, например, при максимальных вложениях.
-
-Альтернативный алгоритм описан в разделе \ref{sec:algorithm}.
-Рассмотренный там же пример регулярного вложения \ref{sec:someth-high-dimens}  $B_{2}\subset B_{4}$ позволяет сделать следующее сравнение числа требующихся операций.
-В данном примере веер вложения состоит из 24 элементов.
-Для разложения модуля алгебры  $B_{4}$ необходимо построить подмножество сингулярных весов модуля, проектирующихся в главную камеру Вейля подалгебры $B_{2}$.
-Полное множество сингулярных весов состоит из 384 элементов, в главную камеру Вейля проектируется не более 48, так что время на построение этого множества пренебрежимо мало, если число коэффициентов ветвления более 48.
-Мы можем оценить сверху общее число операций для вычисления коэффициентов ветвления произведением числа весов в главной камере Вейля подалгебры с ненулевыми коэффициентами ветвления на число элементов веера вложения.
-С другой стороны, при использовании алгоритма, основанного на построении всех характеров при помощи формулы Фрейденталя мы должны вычислить кратности для каждого модуля в разложении, так что общее количество операций растет с ростом числа весов в представлении быстрее, чем квадрат числа весов в главной камере Вейля подалгебры с ненулевыми коэффициентами ветвления.
-
-Чтобы проиллюстрировать эту разницу в производительности алгоритмов, мы приводим Рисунок \ref{fig:branching}, на котором показано время, необходимое для вычисления коэффициентов ветвления для вложения $B_{3}\subset B_{4}$.
-
-\begin{figure}[h]
-  \noindent\centering{
-   \includegraphics[width=100mm]{figures/branching-timing}
-  }
-  \caption{Время работы алгоритмов, основанных на применении формулы Фрейденталя \eqref{eq:15} (пунктиром)  и рекуррентного соотношения \eqref{recurrent-relation} (сплошная линия) с ростом числа весов в  $\bar C$ при вычислении коэффициентов ветвления для вложения $B_{3}\subset B_{4}$.}
-  \label{fig:branching}
-\end{figure}
+Аналогично, коэффициенты ветвления могут быть вычислены с помощью рекуррентного алгоритма (см.
+раздел \ref{sec:algorithm}) или путем полного построения характеров по формуле Фрейденталя.
+Мы сравнили  производительность этих двух подходов в разделе \ref{sec:branching-algor-comparison}.
 
@@
 
-Мы показали, что рекуррентный подход, основанный на формуле Вейля для характеров полезен не только для вычислений, но и позволяет прояснить связь с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
-
 Также мы представили примеры вычислений с применением нашего пакета, полезных для различных физических и математических проблем.

### 2012-07-26 AffineLieAlgebras/Thesis/3.tex

@@
 В случае инъективного сплинта мы можем сказать, что подалгебра $\af\hookrightarrow \gf$ расщепляется $\Delta$ (и назовем $\af$ ``расщепляющей подалгеброй'' алгебры $\gf$).
-Сплинты были классифицированы в работе \cite{richter2008splints}  (см.
-Приложение в конце главы) и первые три класса сплинтов в этой классификации инъективны.
+Сплинты были классифицированы в работе \cite{richter2008splints}  и первые три класса сплинтов в этой классификации инъективны.
 
@@
 Ниже мы приводим часть таблицы сплинтов из работы \cite{richter2008splints}, соответствующую инъективным сплинтам:
-\[
+\begin{equation}
+  \label{eq:128}
   \begin{array}{cc||c|c}
@@
     \hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
-& C_{r}(r\geq 3) & D_{r} & \oplus ^{r}A_{1} \\ \hline
+    (*)& C_{r}(r\geq 3) & D_{r} & \oplus ^{r}A_{1} \\ \hline
     \hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
@@
   \end{array}
-\]
+\end{equation}
 
@@
 Такая добавка не меняет основных свойств ветвления, но позволяет использовать кратности весов $\sfr$-модулей без последующей проекции весов.
+
+Второй инъективный сплинт типа (ii), отмеченный звездочкой в таблице (\ref{eq:128}), не порождает дополнительного $\sfr$-модуля и ветвление в этом случае связано со сплинтом более сложным образом.
+Мы не рассматриваем здесь этот случай.
 
@@
 \end{equation}
-Следующим шагом построим полную  $W_{\sfr}$-орбиту элемента $\Phi _{\sfr}^{\left( \widetilde{\mu }\right) }$  в $P_{\sfr}$.
-Легко видеть, что его кообраз принадлежит  $\bar{C_{\af}}$ и что множество $\phi^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) \setminus \Phi _{\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ соответствует весам, принадлежащим границе $\bar{C_{\af}}$ (включая подмножество $\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\} $).
-То есть мы построили все формальные элементы с соответствующими знаковыми множителями, которые после сложения с  $\Phi _{\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ образуют диаграмму $\phi^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) $ в $\bar{C_{\af}}$.
-
-Теперь вернемся к равенству (\ref{singular main-3}).
+Следующим шагом необходимо проверить, что образ $\phi\left(\Phi^{(\tilde \mu)}_{\sfr}\right)$ содержится в $\bar C_{\af}$ и множество $\phi\left(\Phi^{(\tilde\mu)}_{\sfr}\right)\setminus \left.\Phi^{(\mu)}_{\gf}\right|_{\bar C_{\af}}$ соответствует весам на границе $\bar C_{\af}$ (включая подмножество $\left\{-e^{\mu+\rho-(m_l+1)\beta_l}|\; \beta_l\in S_{\frak{c}}\right\}$).
+Предположим, что это условие выполнено и вернемся к соотношению (\ref{singular main-3}).
 Можно добавить к $\Phi _{\gf}^{\left( \mu \right) }$ пары формальных элементов, построенные выше, с противоположными знаками: $\epsilon \left( w\right)|_{w\in W_{\sfr}}$  и  $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$.
@@
 \end{example}
+
+\section{Сплинты классических алгебр Ли}
+\label{sec:appendix}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Покажем, что для инъективного сплинта классической алгебры Ли выполняется следующее свойство:
+\begin{Prop}
+Пусть $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ -- инъективный сплинт с разложением множества простых корней  $S=S_{\frak{c}}\cup S_{\frak{d}}$, где $S_{\frak{c}}=S\cap S_{\af}$ и $S_{\frak{d}}=S\cap S_{\sfr}$.
+
+Тогда для каждого простого корня  $\beta \in S_{\sfr}$ существует пара корней  ( $\alpha $ ,$\beta ^{\prime }$), где $\alpha \in $ $S_{\frak{c}},\beta ^{\prime }\in S_{\sfr}$, такая, что $\alpha =\beta-\beta ^{\prime }$
+\end{Prop}
+\begin{itemize}
+\item
+Тип 1. $\Delta _{G_{2}}\approx (\Delta _{A_{2}},\Delta
+_{A_{2}}).$
+
+ \begin{figure}[h!bt]
+  \noindent\centering{
+   \includegraphics[width=100mm]{g2-roots}
+  }
+  \caption{Положительные корни $G_{2}$ и образование сингулярного элемента $\Phi^{(0)}_{\mathfrak{s}}$ в главной камере Вейля алгебры $\af=A_{2}$.}
+  \label{fig:g2-roots}
+\end{figure}
+Здесь оба стебля метрические и соответствующие корневые системы эквивалентны.
+На Рисунке \ref{fig:g2-roots} показана часть сингулярного элемента $\Phi_{G_{2}}^{\left( 0\right) }$.
+Границы  $\bar{C_{\frak{a}}}$ изображены пунктирными линиями, начинающимися в центре сингулярного элемента.
+Они содержат ребро $\lambda _{2}=-\alpha _{2}=-\beta _{2}$ и корни $-\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3}$ и $ -\beta _{3}$
+($\beta _{3}$ показан, как $\beta _{l}$).
+Для корня $\beta_{1}$ искомая пара -- это  $(\alpha _{1}, \beta _{2})$: $\alpha _{1}=\beta _{1}-\beta _{2}$.
+Ребро $\lambda _{2,3}^{\sfr}=\beta _{3}$ равно  $\lambda _{1}^{\frak{s}}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ и  $\sfr$-модуль получает индекс Дынкина $m_{1}$  и наследует второй индекс $m_{2}$.
+В этом частном случае  $m_{1}=m_{2}=0$.
+Общий случай с начальным модулем $L^{\mu }$, где $\mu =m_{1}\omega _{1}+m_{2}\omega _{2}$, может быть рассмотрен аналогично: необходимо найти ребро $\lambda _{2}=-\left(
+m_{2}+1\right) \beta _{2}$ и положить $\lambda_{1}^{\sfr}=-\left( m_{1}+1\right) \beta _{1}$, его конец принадлежит границе $\bar{C_{\af}}$.
+Отражение $s_{\beta_{2}} $ переводит $\beta _{1}$ в $\beta _{3}$ и соответствующее ребро
+$\lambda _{2,3}^{\sfr}=-\left( m_{1}+1\right) \beta _{3}$ имеет длину $\left( m_{1}+1\right) $.
+Теперь рассмотрим ребра $\lambda _{1}^{\sfr}$ (или $\lambda _{2,3}^{\sfr} $) и $\lambda _{1,3}^{\sfr}$ (или $\lambda _{2,3,1}^{\sfr}$), и обнаружим, что они принадлежат границе  $\bar{C_{\af}}$ и Вейлевская симметрия предсказывает, что $\lambda _{1,3}^{\sfr}=-\left( m_{2}+1\right)\beta _{3}$ ($\lambda _{2,3,1}^{\sfr}=-\left( m_{2}+1\right) \beta _{1}$) .
+Наконец, ребро $\lambda _{1,3,2}^{\sfr}=-\left(m_{1}+1\right) \beta _{2}$ замыкает многогранник.
+Его вершины соответствуют весам сингулярного элемента $\Phi _{\sfr}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{\sfr}}\varepsilon \left( w\right) e^{w\circ \left(
+\widetilde{\mu }+\rho_{\sfr}\right) }$ модуля $L_{\sfr}^{\left( \widetilde{\mu }\right) }$, где $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}\widetilde{\omega }_{2}$.
+Заметим, что в этом случае знаковые множители можно получить прямо в первоначальной весовой системе, так как стебли метрические.
+\item
+Тип 1. $\Delta _{F_{4}}\approx (\Delta _{D_{4}},\Delta_{D_{4}}).$
+
+Оба стебля здесь метрические и соответствующие корневые системы эквивалентны.
+Система $\Delta _{D_{4}}$ подалгебры $\frak{a=}D_{4}$ формируется множеством $\left\{ \pm e_{i}\pm e_{j}\right\} _{|i,j=1,\ldots 4,\; i\neq j}.$ Простые корни $S_{\frak{c}}$ -- это $\left\{e_{2}-e_{3},e_{3}-e_{4}\right\} $ и $S_{\frak{d}}=\left\{ e_{4},\frac{1}{2}\left(e_{1}-e_{2}-e_{3}-e_{4}\right) \right\} $.
+Для модуля $L^{\mu }$, где $\mu =\sum m_{k}\omega _{k}$ рассмотрим ребро $\lambda _{3}=-\left( m_{3}+1\right) e_{4}=-\left( m_{3}+1\right)
+\beta _{3}$.
+Построим ребро $\lambda _{2}^{\sfr}=-\left( \widetilde{m}_{2}+1\right) \beta _{2}$.
+Искомая пара корней -- это $\left(\alpha_{2}=e_{3}-e_{4},\beta _{3}\right) $.
+Пересечение  $\lambda _{2}^{\sfr}$ с  $\alpha _{2}$-границей камеры $\bar{C_{\af}}$ определяет длину $\lambda _{2}^{\sfr}=-\left( m_{2}+1\right) \beta _{2}$ и длины ребра $\lambda _{3,2}^{\sfr}$ равна длине $\lambda _{2}^{\sfr}$.
+Далее рассмотрим ребро $\lambda _{2}^{\sfr}=-\left( m_{2}+1\right) \beta _{2}$ и пару $\left( \alpha_{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $.
+Длина   $\lambda _{1}^{\sfr}$ становится равной $\lambda_{1}^{\sfr}=-\left( m_{1}+1\right) \beta _{1}$.
+Продолжаем эту процедуру, пока не замкнем многогранник.
+Ребра, направленные вдоль корней типа $\alpha_4$, $\alpha _{4}=\beta_{4}=$ $\frac{1}{2}\left( e_{1}-e_{2}-e_{3}-e_{4}\right) $, рассматриваются аналогично и, наконец, сингулярный элемент $\Phi_{\sfr}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{\sfr}}\varepsilon \left( w\right) e^{w\circ \left(\widetilde{\mu }+\rho _{\sfr}\right) }$ для модуля $L_{\sfr}^{\left( \widetilde{\mu }\right) }$, где
+$\widetilde{\mu }=\sum m_{k}\widetilde{\omega }_{k}$ возникает в камере $\bar{C_{\af}}$.
+\item
+Тип 2. $\Delta _{B_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus^{r}A_{1}}). $
+
+Оба стебля метрические.
+Вложения дается стеблем $\Delta_{D_{r}}$ с простыми корнями $S_{\af}=\left\{e_{1}-e_{2},e_{2}-e_{3},\ldots,e_{r-1}-e_{r},e_{r-1}+e_{r}\right\} $.
+Второй стебель соответствует прямой сумме алгебр $A_{1}$ с простыми корнями $S_{\sfr}=\left\{ e_{1},e_{2},\ldots ,e_{r-1},e_{r}\right\} $.
+Рассмотрим ребро $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ (здесь $\beta_{r}=e_{r}$) и ребро $\lambda _{r-1}=-\left(\widetilde{m}_{r-1}+1\right) \beta _{r-1}$, присоединенное к нему (здесь $\beta_{r-1}=e_{r-1}$).
+Соответствующая пара корней -- это $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta _{r-1}=e_{r-1}\right) $.
+Из условия пересечения определяется второе ребро $\lambda_{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ , оно ортогонально к  $\beta _{r}$, так что противоположное ребро имеет ту же длину.
+Индекс Дынкина $m_{r-1}$ теперь связан также с простым корнем $\beta _{r-1}$.
+Далее рассмотрим полученное ребро $\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ и $\lambda_{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$, чтобы определить индекс $\widetilde{m}_{r-2}=m_{r-2}$ и ребро $\lambda _{r-2}=-\left( m_{r-2}+1\right) \beta _{r-2}$, и так далее, пока все пары ребер не будут определены.
+Наконец, в $\bar{C}_{D_{r}}$ элемент $\Phi _{\oplus ^{r}A_{1}}^{\left(\widetilde{\mu }\right) }=\sum_{w\in W_{\oplus^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+\frac{1}{2}\sum e_{k}\right) }$ может быть построен для модуля
+$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$, где
+$\widetilde{\mu }=\sum m_{k}\frac{1}{2}e_{k}$.
+
+\item
+Тип 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus^{r}A_{1}}). $
+
+Ситуация в этом случае эквивалентна предыдущему и дополнительные ребра строятся аналогично.
+Однако в данном случае нарушено требование $\phi\left(\Phi^{(0)}_{\sfr}\right)\subset {\bar C_{\af}}^{(0)}$.
+Множество $\phi\left(\Phi^{(0)}_{\sfr}\right)$ включает веса из нескольких соседних камер Вейля $C_{\af}$.
+Разложение (\ref{singular main-3}) не может быть выполнено и инъективный сплинт $\Delta_{C_r}\approx (\Delta_{\oplus^r A_1}, \Delta_{D_r})$ не приводит к выполнению свойства (\ref{singular main-4}).
+
+\item
+Тип 3 $\Delta _{A_{r}}\approx (\Delta _{A_{r-1}\oplus u_{1}},\Delta _{\oplus ^{r}A_{1}}).$
+
+Здесь только первый стебель метрический и он определяет вложение с простыми корнями  $S_{\af}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots ,e_{r-1}-e_{r}\right\} $.
+Второй стебель, соответствующий прямой сумме  $r$ копий алгебры $A_{1}$, имеет простые корни $S_{\sfr}=\left\{
+e_{1}-e_{r+1},e_{2}-e_{r+1},\ldots ,e_{r}-e_{r+1}\right\} $. Рассмотрим ребро $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ с $\beta
+_{r}=e_{r}-e_{r+1}$ и $\lambda _{r-1}=-\left( \widetilde{m}_{r-1}+1\right) \beta _{r-1}$  с $\beta_{r-1}=e_{r-1}-e_{r+1}$ присоединенным к нему.
+Тогда соответствующая пара равна $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta_{r-1}=e_{r-1}-e_{r+1}\right)$.
+Пересечение с границей $\bar{C}_{A_{r-1}}$, ортогональной $\alpha _{r-1}$ определяет второе ребро $\lambda _{r-1}=-\left(m_{r-1}+1\right) \beta _{r-1}$.
+Индекс Дынкина $m_{r-1}$ должен использоваться для фундаментального веса  $\omega _{r-1}.$ Отражение  $s_{\beta _{r}}$ переводит $\lambda _{r-1}=-\left(m_{r-1}+1\right) \beta _{r-1}$ в $\lambda _{r,r-1}=-\left(m_{r-1}+1\right) \beta _{r-1}.$ Далее рассмотрим полученное ребро edge
+$\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ и $\lambda _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$ с  $\beta_{r-2}=e_{r-2}-e_{r+1} $ , чтобы получить индекс $\widetilde{m}_{r-2}=m_{r-2}$ и ребро $\lambda _{r-2}=-\left(m_{r-2}+1\right) \beta _{r-2}$, и так далее, пока не получим все пары ребер.
+Наконец, в  $\bar{C}_{D_{r}}$ элемент$\Phi _{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right)}=\sum_{w\in W_{\oplus^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+\widetilde{\rho }\right) }$ может быть построен для модуля $L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$, где $\widetilde{\mu }=\sum m_{k}\beta _{k}.$ Простейший случай $\Delta _{A_{2}}\approx (\Delta _{A_{1}\oplus u_{1}},\Delta_{A_{1}\oplus A_{1}})$ показан в примере \ref{example-1} и на Рисунке \ref{fig:a2_splint}.
+\item
+Тип 3 $\Delta _{B_{2}}\approx (\Delta _{A_{1}},\Delta _{A_{2}}).$
+
+Этот сплинт показан в примере \ref{example-2} и на Рисунке \ref{fig:b2_splint}, 
+$S_{A\_1}=\left\{ e_{1}-e_{2}\right\} $, $S_{A\_2}=\left\{e_{1},e_{2}\right\} $.
+Ребро $\lambda _{\alpha _{2}}=\lambda_{\beta _{2}}=-\left( m_{2}+1\right) \beta _{2}$ продолжается ребром $\lambda _{\beta _{1}}=-\left( \widetilde{m}_{1}+1\right) \beta_{1}$.
+Рассмотрим пару $\left(\alpha_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right)$.
+Конец ребра $\lambda _{\beta _{1}}$ должен указывать вес, инвариантный по отношению к отражению  $s_{\alpha _{1}}$.
+Его длина таким образом фиксирована: $\lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$ В кообразе второго стебля, то есть в корневой системе $\Delta_{A_{2}}$, отражение $s_{\beta _{2}}$ переводит $\lambda _{\beta _{1}}=-\left(m_{1}+1\right) \beta_{1}$ в $\lambda _{2,3}$, то есть это ребро имеет ту же длину в $\beta _{3}=e_{1}+e_{3}$, и $\lambda _{2,3}=-\left(m_{1}+1\right)\beta _{3}$ с $\beta_{3}=e_{1}+e_{3}$.
+Неприводимый  $\sfr$-модуль имеет старший вес $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}\widetilde{\omega }_{2}$.
+На Рисунке \ref{fig:b2_splint} мы видим детали этих соотношений и, в частности, случай, когда $L_{B_{2}}^{\left[ 3,2\right] }$ редуцируется на подалгебру $A_{1}\oplus u\left( 1\right) $ и соответствующие старшие веса (вместе с их кратностями) образуют диаграмму $\mathcal{N}_{A_2}^{\left[ 3,2\right] }$ .
+\end{itemize}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{subappendices}
-\section{Приложение}
-\label{sec:appendix}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Покажем, что для инъективного сплинта классической алгебры Ли выполняется следующее свойство:
-\begin{Prop}
-Пусть $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ -- инъективный сплинт с разложением множества простых корней  $S=S_{\frak{c}}\cup S_{\frak{d}}$, где $S_{\frak{c}}=S\cap S_{\af}$ и $S_{\frak{d}}=S\cap S_{\sfr}$.
-
-Тогда для каждого простого корня  $\beta \in S_{\sfr}$ существует пара корней  ( $\alpha $ ,$\beta ^{\prime }$), где $\alpha \in $ $S_{\frak{c}},\beta ^{\prime }\in S_{\sfr}$, такая, что $\alpha =\beta-\beta ^{\prime }$
-\end{Prop}
-\begin{itemize}
-\item
-Тип 1. $\Delta _{G_{2}}\approx (\Delta _{A_{2}},\Delta
-_{A_{2}}).$
-
- \begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=100mm]{g2-roots}
-  }
-  \caption{Положительные корни $G_{2}$ и образование сингулярного элемента $\Phi^{(0)}_{\mathfrak{s}}$ в главной камере Вейля алгебры $\af=A_{2}$.}
-  \label{fig:g2-roots}
-\end{figure}
-Здесь оба стебля метрические и соответствующие корневые системы эквивалентны.
-На Рисунке \ref{fig:g2-roots} показана часть сингулярного элемента $\Phi_{G_{2}}^{\left( 0\right) }$.
-Границы  $\bar{C_{\frak{a}}}$ изображены пунктирными линиями, начинающимися в центре сингулярного элемента.
-Они содержат ребро $\lambda _{2}=-\alpha _{2}=-\beta _{2}$ и корни $-\beta _{1}=-s_{\alpha _{2}}\circ \beta _{3}$ и $ -\beta _{3}$
-($\beta _{3}$ показан, как $\beta _{l}$).
-Для корня $\beta_{1}$ искомая пара -- это  $(\alpha _{1}, \beta _{2})$: $\alpha _{1}=\beta _{1}-\beta _{2}$.
-Ребро $\lambda _{2,3}^{\sfr}=\beta _{3}$ равно  $\lambda _{1}^{\frak{s}}=\beta _{1}=s_{\alpha _{2}}\circ \beta _{3}$ и  $\sfr$-модуль получает индекс Дынкина $m_{1}$  и наследует второй индекс $m_{2}$.
-В этом частном случае  $m_{1}=m_{2}=0$.
-Общий случай с начальным модулем $L^{\mu }$, где $\mu =m_{1}\omega _{1}+m_{2}\omega _{2}$, может быть рассмотрен аналогично: необходимо найти ребро $\lambda _{2}=-\left(
-m_{2}+1\right) \beta _{2}$ и положить $\lambda_{1}^{\sfr}=-\left( m_{1}+1\right) \beta _{1}$, его конец принадлежит границе $\bar{C_{\af}}$.
-Отражение $s_{\beta_{2}} $ переводит $\beta _{1}$ в $\beta _{3}$ и соответствующее ребро
-$\lambda _{2,3}^{\sfr}=-\left( m_{1}+1\right) \beta _{3}$ имеет длину $\left( m_{1}+1\right) $.
-Теперь рассмотрим ребра $\lambda _{1}^{\sfr}$ (или $\lambda _{2,3}^{\sfr} $) и $\lambda _{1,3}^{\sfr}$ (или $\lambda _{2,3,1}^{\sfr}$), и обнаружим, что они принадлежат границе  $\bar{C_{\af}}$ и Вейлевская симметрия предсказывает, что $\lambda _{1,3}^{\sfr}=-\left( m_{2}+1\right)\beta _{3}$ ($\lambda _{2,3,1}^{\sfr}=-\left( m_{2}+1\right) \beta _{1}$) .
-Наконец, ребро $\lambda _{1,3,2}^{\sfr}=-\left(m_{1}+1\right) \beta _{2}$ замыкает многогранник.
-Его вершины соответствуют весам сингулярного элемента $\Phi _{\sfr}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{\sfr}}\varepsilon \left( w\right) e^{w\circ \left(
-\widetilde{\mu }+\rho_{\sfr}\right) }$ модуля $L_{\sfr}^{\left( \widetilde{\mu }\right) }$, где $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}\widetilde{\omega }_{2}$.
-Заметим, что в этом случае знаковые множители можно получить прямо в первоначальной весовой системе, так как стебли метрические.
-\item
-Тип 1. $\Delta _{F_{4}}\approx (\Delta _{D_{4}},\Delta_{D_{4}}).$
-
-Оба стебля здесь метрические и соответствующие корневые системы эквивалентны.
-Система $\Delta _{D_{4}}$ подалгебры $\frak{a=}D_{4}$ формируется множеством $\left\{ \pm e_{i}\pm e_{j}\right\} _{|i,j=1,\ldots 4,\; i\neq j}.$ Простые корни $S_{\frak{c}}$ -- это $\left\{e_{2}-e_{3},e_{3}-e_{4}\right\} $ и $S_{\frak{d}}=\left\{ e_{4},\frac{1}{2}\left(e_{1}-e_{2}-e_{3}-e_{4}\right) \right\} $.
-Для модуля $L^{\mu }$, где $\mu =\sum m_{k}\omega _{k}$ рассмотрим ребро $\lambda _{3}=-\left( m_{3}+1\right) e_{4}=-\left( m_{3}+1\right)
-\beta _{3}$.
-Построим ребро $\lambda _{2}^{\sfr}=-\left( \widetilde{m}_{2}+1\right) \beta _{2}$.
-Искомая пара корней -- это $\left(\alpha_{2}=e_{3}-e_{4},\beta _{3}\right) $.
-Пересечение  $\lambda _{2}^{\sfr}$ с  $\alpha _{2}$-границей камеры $\bar{C_{\af}}$ определяет длину $\lambda _{2}^{\sfr}=-\left( m_{2}+1\right) \beta _{2}$ и длины ребра $\lambda _{3,2}^{\sfr}$ равна длине $\lambda _{2}^{\sfr}$.
-Далее рассмотрим ребро $\lambda _{2}^{\sfr}=-\left( m_{2}+1\right) \beta _{2}$ и пару $\left( \alpha_{1}=e_{2}-e_{3},\beta _{1}=e_{2}\right) $.
-Длина   $\lambda _{1}^{\sfr}$ становится равной $\lambda_{1}^{\sfr}=-\left( m_{1}+1\right) \beta _{1}$.
-Продолжаем эту процедуру, пока не замкнем многогранник.
-Ребра, направленные вдоль корней типа $\alpha_4$, $\alpha _{4}=\beta_{4}=$ $\frac{1}{2}\left( e_{1}-e_{2}-e_{3}-e_{4}\right) $, рассматриваются аналогично и, наконец, сингулярный элемент $\Phi_{\sfr}^{\left( \widetilde{\mu }\right) }=\sum_{w\in W_{\sfr}}\varepsilon \left( w\right) e^{w\circ \left(\widetilde{\mu }+\rho _{\sfr}\right) }$ для модуля $L_{\sfr}^{\left( \widetilde{\mu }\right) }$, где
-$\widetilde{\mu }=\sum m_{k}\widetilde{\omega }_{k}$ возникает в камере $\bar{C_{\af}}$.
-\item
-Тип 2. $\Delta _{B_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus^{r}A_{1}}). $
-
-Оба стебля метрические.
-Вложения дается стеблем $\Delta_{D_{r}}$ с простыми корнями $S_{\af}=\left\{e_{1}-e_{2},e_{2}-e_{3},\ldots,e_{r-1}-e_{r},e_{r-1}+e_{r}\right\} $.
-Второй стебель соответствует прямой сумме алгебр $A_{1}$ с простыми корнями $S_{\sfr}=\left\{ e_{1},e_{2},\ldots ,e_{r-1},e_{r}\right\} $.
-Рассмотрим ребро $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ (здесь $\beta_{r}=e_{r}$) и ребро $\lambda _{r-1}=-\left(\widetilde{m}_{r-1}+1\right) \beta _{r-1}$, присоединенное к нему (здесь $\beta_{r-1}=e_{r-1}$).
-Соответствующая пара корней -- это $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta _{r-1}=e_{r-1}\right) $.
-Из условия пересечения определяется второе ребро $\lambda_{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ , оно ортогонально к  $\beta _{r}$, так что противоположное ребро имеет ту же длину.
-Индекс Дынкина $m_{r-1}$ теперь связан также с простым корнем $\beta _{r-1}$.
-Далее рассмотрим полученное ребро $\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ и $\lambda_{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$, чтобы определить индекс $\widetilde{m}_{r-2}=m_{r-2}$ и ребро $\lambda _{r-2}=-\left( m_{r-2}+1\right) \beta _{r-2}$, и так далее, пока все пары ребер не будут определены.
-Наконец, в $\bar{C}_{D_{r}}$ элемент $\Phi _{\oplus ^{r}A_{1}}^{\left(\widetilde{\mu }\right) }=\sum_{w\in W_{\oplus^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+\frac{1}{2}\sum e_{k}\right) }$ может быть построен для модуля
-$L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$, где
-$\widetilde{\mu }=\sum m_{k}\frac{1}{2}e_{k}$.
-
-\item
-Тип 2. $\Delta _{C_{r}}\approx (\Delta _{D_{r}},\Delta _{\oplus^{r}A_{1}}). $
-
-Ситуация в этом случае эквивалентна предыдущему и дополнительные ребра строятся аналогично.
-
-\item
-Тип 3 $\Delta _{A_{r}}\approx (\Delta _{A_{r-1}\oplus u_{1}},\Delta _{\oplus ^{r}A_{1}}).$
-
-Здесь только первый стебель метрический и он определяет вложение с простыми корнями  $S_{\af}=\left\{ e_{1}-e_{2},e_{2}-e_{3},\ldots ,e_{r-1}-e_{r}\right\} $.
-Второй стебель, соответствующий прямой сумме  $r$ копий алгебры $A_{1}$, имеет простые корни $S_{\sfr}=\left\{
-e_{1}-e_{r+1},e_{2}-e_{r+1},\ldots ,e_{r}-e_{r+1}\right\} $. Рассмотрим ребро $\lambda _{r}=-\left( m_{r}+1\right) \beta _{r}$ с $\beta
-_{r}=e_{r}-e_{r+1}$ и $\lambda _{r-1}=-\left( \widetilde{m}_{r-1}+1\right) \beta _{r-1}$  с $\beta_{r-1}=e_{r-1}-e_{r+1}$ присоединенным к нему.
-Тогда соответствующая пара равна $\left( \alpha _{r-1}=e_{r-1}-e_{r},\beta_{r-1}=e_{r-1}-e_{r+1}\right)$.
-Пересечение с границей $\bar{C}_{A_{r-1}}$, ортогональной $\alpha _{r-1}$ определяет второе ребро $\lambda _{r-1}=-\left(m_{r-1}+1\right) \beta _{r-1}$.
-Индекс Дынкина $m_{r-1}$ должен использоваться для фундаментального веса  $\omega _{r-1}.$ Отражение  $s_{\beta _{r}}$ переводит $\lambda _{r-1}=-\left(m_{r-1}+1\right) \beta _{r-1}$ в $\lambda _{r,r-1}=-\left(m_{r-1}+1\right) \beta _{r-1}.$ Далее рассмотрим полученное ребро edge
-$\lambda _{r-1}=-\left( m_{r-1}+1\right) \beta _{r-1}$ и $\lambda _{r-2}=-\left( \widetilde{m}_{r-2}+1\right) \beta _{r-2}$ с  $\beta_{r-2}=e_{r-2}-e_{r+1} $ , чтобы получить индекс $\widetilde{m}_{r-2}=m_{r-2}$ и ребро $\lambda _{r-2}=-\left(m_{r-2}+1\right) \beta _{r-2}$, и так далее, пока не получим все пары ребер.
-Наконец, в  $\bar{C}_{D_{r}}$ элемент$\Phi _{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right)}=\sum_{w\in W_{\oplus^{r}A_{1}}}\varepsilon \left( w\right) e^{w\circ \left( \widetilde{\mu }+\widetilde{\rho }\right) }$ может быть построен для модуля $L_{\oplus ^{r}A_{1}}^{\left( \widetilde{\mu }\right) }$, где $\widetilde{\mu }=\sum m_{k}\beta _{k}.$ Простейший случай $\Delta _{A_{2}}\approx (\Delta _{A_{1}\oplus u_{1}},\Delta_{A_{1}\oplus A_{1}})$ показан в примере \ref{example-1} и на Рисунке \ref{fig:a2_splint}.
-\item
-Тип 3 $\Delta _{B_{2}}\approx (\Delta _{A_{1}},\Delta _{A_{2}}).$
-
-Этот сплинт показан в примере \ref{example-2} и на Рисунке \ref{fig:b2_splint}, 
-$S_{A\_1}=\left\{ e_{1}-e_{2}\right\} $, $S_{A\_2}=\left\{e_{1},e_{2}\right\} $.
-Ребро $\lambda _{\alpha _{2}}=\lambda_{\beta _{2}}=-\left( m_{2}+1\right) \beta _{2}$ продолжается ребром $\lambda _{\beta _{1}}=-\left( \widetilde{m}_{1}+1\right) \beta_{1}$.
-Рассмотрим пару $\left(\alpha_{1}=e_{1}-e_{2},\beta _{1}=e_{1}\right)$.
-Конец ребра $\lambda _{\beta _{1}}$ должен указывать вес, инвариантный по отношению к отражению  $s_{\alpha _{1}}$.
-Его длина таким образом фиксирована: $\lambda _{\beta _{1}}=-\left( m_{1}+1\right) \beta _{1}$ В кообразе второго стебля, то есть в корневой системе $\Delta_{A_{2}}$, отражение $s_{\beta _{2}}$ переводит $\lambda _{\beta _{1}}=-\left(m_{1}+1\right) \beta_{1}$ в $\lambda _{2,3}$, то есть это ребро имеет ту же длину в $\beta _{3}=e_{1}+e_{3}$, и $\lambda _{2,3}=-\left(m_{1}+1\right)\beta _{3}$ с $\beta_{3}=e_{1}+e_{3}$.
-Неприводимый  $\sfr$-модуль имеет старший вес $\widetilde{\mu }=m_{1}\widetilde{\omega }_{1}+m_{2}\widetilde{\omega }_{2}$.
-На Рисунке \ref{fig:b2_splint} мы видим детали этих соотношений и, в частности, случай, когда $L_{B_{2}}^{\left[ 3,2\right] }$ редуцируется на подалгебру $A_{1}\oplus u\left( 1\right) $ и соответствующие старшие веса (вместе с их кратностями) образуют диаграмму $\mathcal{N}_{A_2}^{\left[ 3,2\right] }$ .
-\end{itemize}
-\end{subappendices}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

### 2012-07-26 AffineLieAlgebras/Thesis/4.tex

@@
 
-\subsection{Введение}
 Эволюция Шрамма-Левнера -- это стохастический процесс, который предложил Oded Schramm  \cite{schramm2000scaling} для описания скейлингового предела критических интерфейсов в двумерных статистических решеточных моделях.
@@
 
-Более общие модели конформной теории поля обладают дополнительными симметриями.
-Например,  в моделях Весса-Зумино-Новикова-Виттена возникают аффинные алгебры Ли.
-Чтобы реализовать такие симметрии при изучении эволюции Шрамма-Левнера нужно ввести дополнительное случайное блуждание на группе Ли \cite{bettelheim2005stochastic}, \cite{Rasmussen:2004xr}.
+Как мы показали в главе \ref{cha:CFT}, более общие модели конформной теории поля обладают дополнительными симметриями.
+Так в моделях Весса-Зумино-Новикова-Виттена и в coset-моделях возникают аффинные алгебры Ли.
+Чтобы реализовать эти симметрии при изучении эволюции Шрамма-Левнера, нужно ввести дополнительное случайное блуждание на группе Ли \cite{bettelheim2005stochastic}, \cite{Rasmussen:2004xr}.
 Такое случайное блуждание определяется в разделе \ref{sec:sle-wzw-models}.
@@
 
-Основная задача данной главы состоит в обобщении эволюции Шрамма-Левнера с дополнительным случайным блужданием на группе Ли на случай фактор-пространства  $G/A$ и в изучении связи с coset-конструкцией конформной теории поля.
-В разделе \ref{sec:coset-models-sle} мы напоминаем некоторые детали coset-конструкции, вводим эволюцию Шрамма-Левнера на фактор-пространстве и связываем ее с конформной теорией поля.
+Мы обобщаем эволюцию Шрамма-Левнера с дополнительным случайным блужданием на группе Ли на случай фактор-пространства  $G/A$ и в изучении связи с coset-конструкцией конформной теории поля.
 По аналогии со случаем моделей Весса-Зумино-Новикова-Виттена мы получаем систему алгебраических уравнений на оператор смены граничного условия из условия на мартингал.
 При помощи coset-конструкции можно реализовать минимальные и парафермионные модели конформной теории поля (см.
-\cite{difrancesco1997cft}), так что мы можем сравнить наши уравнения на оператор смены граничных условий с результатами работы \cite{santachiara2008sle}.
+\cite{difrancesco1997cft}).
+Мы сравниваем наши уравнения на оператор смены граничных условий с результатами работы \cite{santachiara2008sle} и видим, что они совпадают.
+Кроме того, полученные нами значения параметров эволюции Шрамма-Лёвнера согласуются с результатами для минимальных моделей.
 
-В разделе  \ref{sec:5-conclusion} мы обсуждаем возможность сравнения классификации операторов смены граничных условий, следующей из свойства мартингалов с общей классификацией операторов смены граничных условий в граничной конформной теории поля, связанной с D-бранными решениями \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,Maldacena:2001ky,felder1999geometry,alekseev1999d}.
+%%  В разделе  \ref{sec:5-conclusion} мы обсуждаем возможность сравнения классификации операторов смены граничных условий, следующей из свойства мартингалов с общей классификацией операторов смены граничных условий в граничной конформной теории поля, связанной с D-бранными решениями \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,Maldacena:2001ky,felder1999geometry,alekseev1999d}.
+%%
 
@@
 Как мы упоминали в главе \ref{cha:CFT}, $G/A$-coset модель конформной теории поля может быть реализована как ВЗНВ-модель (с калибровочной группой $G$), взаимодействующая с чисто калибровочными полями, с калибровочной группой $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
-Действие записывается через поля $\gamma:\mathbb{C}\to G$ and $\alpha,\bar\alpha:\mathbb{C}\to A$ следующим образом (\ref{eq:38}):
-\begin{multline}
-\label{eq:178}
-      S_{G/A}(\gamma, \alpha)=-\frac{k}{8\pi}\int_{S^2} d^2x\; {\cal K} (\gamma^{-1}\partial^{\mu}\gamma,\gamma^{-1}\partial_{\mu}\gamma)-\\
- - \frac{k }{24\pi} \int_{B}\epsilon_{ijk} {\cal K}\left(
-    \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^i},
-      \left[\tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^j}
-      \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^k}\right]\right) d^3y+\\
-+
-      \frac{k}{4\pi}\int_{S^2} d^{2}z \left(\mathcal{K}(\alpha, \gamma^{-1}\bar \partial \gamma)-\mathcal{K}(\bar \alpha, (\partial \gamma ) \gamma^{-1})\right.\\
-      \left.+\mathcal{K}(\alpha,\gamma^{-1}\bar \alpha \gamma)-\mathcal{K}(\alpha,\bar \alpha)\right).
-\end{multline}
-Здесь через  $\mathcal{K}$ обозначена форма Киллинга в алгебре Ли $\gf$, соответствующей группе Ли $G$.
+Как было показано в главе \ref{cha:CFT}, действие записывается через поля  $g:\mathbb{C}\to G$ и $A,\bar A:\mathbb{C}\to \af$ (\ref{eq:38}).
+Здесь $\af$ -- алгебра Ли, соответствующая группе Ли $A$.
 
@@
 Они классифицируются простыми корнями алгебры Ли $\gf$.
-Действие аффинной теории Тоды можно получить добавлением возмущающего члена в действие (\ref{eq:178}):
+Действие аффинной теории Тоды можно получить добавлением возмущающего члена в действие (\ref{eq:38}):
 \begin{equation}
-  S_{\text{pert}}=S_{G/A}(\gamma,\alpha)-\frac{k\lambda}{2\pi}\int {\cal K} (\gamma T, \gamma^{-1} \bar T),
+  S_{\text{pert}}=S_{G/A}(g,A,\bar A)-\frac{k\lambda}{2\pi}\int {\cal K} (g T, g^{-1} \bar T),
 \end{equation}
@@
 
-\subsection{О связи мартингалов coset-моделей с классификацией операторов смены граничного условия}
-\label{sec:5-conclusion}
-
-Мы предложили способ обобщения эволюции Шрамма-Левнера для получения таких наблюдаемых, которые могут исследоваться методами конформной теории поля.
+%%  
+%%  \subsection{О связи мартингалов coset-моделей с классификацией операторов смены граничного условия}
+%%  \label{sec:5-conclusion}
+%%  
+%%  Мы предложили способ обобщения эволюции Шрамма-Левнера для получения таких наблюдаемых, которые могут исследоваться методами конформной теории поля.
 Описание полей в coset-моделях нетривиально ввиду идентификации полей \cite{schellekens1990field} и необходимости в разрешении фиксированных точек \cite{Fuchs:1996dd,fuchs1996resolution}, которое не обсуждалась в данной главе.
@@
 Дальнейшее изучение этого предмета может выявить глубокую алгебраическую связь условия мартингала с классификацией граничных состояний.
+%%
 

### 2012-07-26 AffineLieAlgebras/Thesis/2.tex

@@
 
-\section{Заключение}
-
-\label{sec:conclusions}
+\begin{remark}
 В главе \ref{cha:affine-lie-algebras}  было показано, что метод веера вложения работает также и для специальных вложений.
@@
 Пространство сохраняется, и после такой деформации генераторы начальной алгебры будут действовать на нем правильным образом.
+\end{remark}
+
+\section{Заключение}
+
+\label{sec:conclusions}
+
+Мы показали, что разложение сингулярного элемента, возникающее при редукции модулей, оказывается связано с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
+При этом веер вложения порождает параболические модули Верма.
+Результаты данной главы опубликованы в работах \cite{2010LyakhovskyNazarovMQFT,2011arXiv1102.1702L}.
 

### 2012-08-10 AffineLieAlgebras/Thesis/3.tex
From V.D.

@@
 \label{sec:4-conclusions}
-Мы продемонстрировали, что сплинт представляет собой очень эффективный инструмент для вычисления коэффициентов ветвления.
+
+Нами установлена непосредственная связь инъективного сплинта и ветвлений: доказано, что при условии включения образа $\phi(\Phi_{\sfr}^{(\tilde \mu)}$ в $\bar C_{\af}$ кратность веса вспомогательного модуля определяет коэффициент ветвления $b_{\nu}^{(\mu)}$.
+Далее мы продемонстрировали, что это свойство сплинта представляет очень эффективный инструмент для вычисления коэффициентов ветвления.
 В частности, инъективные сплинты дают возможность свести определение правил ветвления модулей старшего веса к вычислению кратностей весов для модуля с теми же индексами Дынкина алгебры Ли $\mathfrak{s}$.
 Эта алгебра $\mathfrak{s}$ не обязательно является подалгеброй в  $\gf$ , ее ранг $r_{\mathfrak{s}}=r$ совпадает с рангом $\gf$, но сома она ``проще'' чем  $\gf$, так как только подмножество корней корневой системы включено во второй ``стебель''  $\Delta_{\mathfrak{s}}$.
+В этом случае для вычислений коэффициентов ветвления можно применять не только общий алгоритм (раздел \label{sec:algorithm}), но и формулу Фрейденталя, позволяющую быстро вычислять кратности весов.
 

### 2012-08-10 AffineLieAlgebras/Thesis/review.tex
From V.D.

@@
     G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n},\bar z_{1},\dots, \bar z_{n})=\\
-\prod_{j=1}^{n}\left(\frac{dw(z_{j})}{dz}\right)^{h_{i_{j}}}\left(\overline{\frac{dw(z_{j})}{dz}}\right)^{\bar{h}_{i_{j}}} G_{i_{\pi(1)},\dots i_{\pi(n)}}(w_{1},\dots, w_{n},\bar w_{1},\dots,\bar w_{n}),
+\prod_{j=1}^{n}\left(\frac{dw(z_{j})}{dz}\right)^{h_{i_{j}}}\left(\overline{\frac{dw(z_{j})}{dz}}\right)^{\bar{h}_{i_{j}}} G_{i_1,\dots i_n}(w_{1},\dots, w_{n},\bar w_{1},\dots,\bar w_{n}),
   \end{multline}
@@
     \end{equation}
-  \item Обозначим через $\underline{S}^{+}$ пространство последовательности тест-функций $\underline{f}=(f_{i})_{i\in B}, f_{i}\in S^{+}_{n}$. Тогда
+  \item Обозначим через $\underline{S}^{+}$ пространство последовательностей тест-функций $\underline{f}=(f_{i})_{i\in B}, f_{i}\in S^{+}_{n}$. Тогда
     \begin{multline}
@@
 
-Пусть $\gf$ -- конечномерная или аффинная алгебра Ли. Мы ввели модули алгебры $\gf$ в определении \ref{def:1}. Широко используется альтернативный термин {\it представление}.
+Пусть $\gf$ -- конечномерная или аффинная алгебра Ли. Мы ввели модули алгебры $\gf$ в определении \ref{def:1}. Широко используется термин {\it представление}.
 
@@
 \begin{definition}
-Представление алгебры  $\gf$ на векторном пространстве $V$ называется гомоморфизм $\gf\to gl(V)$ из $\gf$ в алгебру Ли эндоморфизмов векторного пространства $V$, где скобка задана коммутатором:
+Представлением алгебры  $\gf$ на векторном пространстве $V$ называется гомоморфизм $\gf\to gl(V)$ из $\gf$ в алгебру Ли эндоморфизмов векторного пространства $V$, где скобка задана коммутатором:
 \begin{equation}
@@
  =\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu)}ch\left( L_{\af}^{\nu }\right) .
+ \label{eq:131}
 \end{equation}
@@
 
-Теперь рассмотрим модели Весса-Зумино-Новикова-Виттена на торе.
-Для ВЗНВ-моделей примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\mathfrak{g}$.
+Рассмотрим модель Весса-Зумино-Новикова-Виттена, соотвествующую алгебре $\af\subset \gf$ на торе.
+В этой модели примарные поля определяются старшими весами  $\hat \lambda, \hat \xi$ соответствующих представлений алгебры $\af$.
 Тогда пространство полей представляет собой прямую сумму
 \begin{equation}
-  \label{eq:76}\mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi}
+  \label{eq:76}\mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k),+}_{\af}} M_{\hat \lambda,\hat \xi}
 L_{\hat \lambda}\otimes L_{\hat \xi}
 \end{equation}
-
-Коэффициенты ветвления для вложения аффинной подалгебры Ли в аффинную алгебру можно использовать для
-построения модулярно-инвариантной статсуммы в соответствующей ВЗНВ-модели. Когда рассматривается
-теория на торе,  набор физически допустимых полей ограничен требованиями модулярной инвариантности.
-
-Простейший модулярный инвариант можно записать следующим образом:
-\begin{equation}
-  \label{eq:34}
+В теории на торе набор физически допустимых полей ограничен требованиями модулярной инвариантности.
+Коэффициенты ветвления для вложения аффинной подалгебры Ли $\af$ в аффинную алгебру $\gf$ можно использовать для
+построения модулярно-инвариантной статсуммы в соответствующей ВЗНВ-модели.
+
+Модулярная инвариантность статсуммы необходима для самосогласованности теории на торе и римановых поверхностях высшего рода, что важно для приложений конформной теории поля в теории струн и описании критического поведения.
+
+Простейшая модулярно-инвариантная статсумма имеет диагональный вид:
+\begin{equation}
+  \label{eq:148}
    Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
 \end{equation}
-Здесь суммирование ведется по всем конформным семействам (то есть по всем представлениям алгебры
-$\mathfrak{a}$).
-
-Другие модулярные инварианты в WZW-модели с алгеброй $\mathfrak{a}$ можно получить, если существует
-алгебра $\mathfrak{g}$, в которую $\mathfrak{a}$ вкладывается конформно.
-
-Представления алгебры $\gf$ можно рассматривать как сумму представлений подалгебры $\af$.
-
-Если мы рассмотрим редукцию характеров аффинной алгебры
-\begin{equation}
-  \label{eq:8}
-   \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
-  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
-\end{equation}
-и подставим разложение в формулу \eqref{eq:34}, то модулярная инвариантность сохранится. То есть из
-диагонального инварианта для алгебры $\mathfrak{g}$ мы получаем новый недиагональный инвариант для
-подалгебры $\mathfrak{a}$. Но возникает вопрос, будет ли теория, полученная таким образом, самосогласованной, сохранится ли в
-ней конформная инвариантность.
-
-Пусть $J^{a_j}_{-n_j}$ и $\tilde{J}^{a'_j}_{-n_j}$ --- понижающие операторы алгебр  $\mathfrak{g}$ и
-$\mathfrak{a}\subset\mathfrak{g}$.  $\pi_{\mathfrak{a}}$ --- проекционный оператор
-$\pi_{\mathfrak{a}}:\mathfrak{g}\longrightarrow \mathfrak{a}$. В теории, связанной с  $\mathfrak{g}$
-с вакуумом $\left| 0\right>$, примарным полем $\phi_{\lambda}$ и состоянием старшего веса  $\left|\lambda\right>=\lim_{z\to 0} \phi_{\lambda}(z) \left|0\right>$ будут следующие состояния:
-\begin{equation}
-  \label{eq:109}
-  J^{a_1}_{-n_1}J^{a_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
-\end{equation}
-Вакуум $\mathfrak{g}$-инвариантен, то есть $J_0^a\left|0\right>=0$. При проекции на подалгебру
-$\mathfrak{a}$ состояния примут вид
-\begin{equation}
-  \label{eq:110}
-  \tilde{J}^{a'_1}_{-n_1}\tilde{J}^{a'_2}_{-n_2}\dots\left|\pi_{\mathfrak{a}}(\lambda)\right>.
-\end{equation}
-Из $\mathfrak{g}$-ивариантности вакуума следует его $\mathfrak{a}$-инвариантность, но для тензора
-энергии-импульса в общем случае это не так. Поэтому тензор энергии-импульса большей теории должен
-состоять только из генераторов $\tilde{J}$. Тогда из $T_{\mathfrak{g}}=T_{\mathfrak{a}}$ следует $c(\mathfrak{g})=c(\mathfrak{a})$. Это приводит к уравнению
-\begin{equation}
-  \label{eq:111}
-  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+h^{\vee}_{\gf}}=\frac{x_e k\; \mathrm{dim}\,\mathfrak{a}}{x_ek+h^{\vee}_{\af}}
-\end{equation}
-Здесь $x_e$ --- индекс вложения, а  $g$, $a$ --- дуальные числа Кокстера, которые характеризуют алгебры.
-
-Можно показать, что это равенство удовлетворяется только для представлений уровня 1. То есть класс
-конформных вложений не слишком широк и существует полная их классификация \cite{difrancesco1997cft}. Кроме того, для
+Здесь суммирование ведется по множеству старших весов интегрируемых модулей в ВЗНВ-модели, а $\chi_{\mu}(\tau)$ -- это нормированные характеры (см. \cite{difrancesco1997cft}) этих модулей.
+
+Построение недиагональных модулярных инвариантов -- это нетривиальная проблема, хотя для некоторых моделей известна полная классификация модулярных инвариантов \cite{1994hepthGannon,1995JMPGannon}.
+
+Рассмотрим модель Весса-Зумино-Новикова-Виттена с аффинной алгеброй Ли $\af$.
+Недиагональные модулярные инварианты этой модели могут быть построены из диагонального инварианта, если существует аффинная алгебра  $\mathfrak{g}$, такая, что $\af\subset\mathfrak{g}$.
+Тогда мы можем заменить характеры  $\mathfrak{g}$-модулей в диагональной модулярно-инвариантной статсумме (\ref{eq:148}) на разложения
+\begin{equation*}
+  \label{eq:32}
+\sum_{\nu \in P^{+}_{\af}}b^{(\mu)}_{\nu} \chi_{\nu},
+\end{equation*}
+содержащие нормированные характеры $\chi_{\nu}$ соответствующих $\af$-модулей. В результате мы получим недиагональную модулярно-инвариантную статсумму для теории с алгеброй токов $\af$,
+\begin{equation}
+  \label{eq:154}
+   Z_{\af}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\af}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau).
+\end{equation}
+
+Эффективная процедура редукции существенна для этой конструкции.
+Вложение должно сохранять конформную инвариантность.
+Пусть $J^{\alpha_j}_{-n_j}$ и $\tilde{J}^{\alpha'_j}_{-n_j}$ -- понижающие операторы для алгебры $\mathfrak{g}$ и подалгебры $\af\subset\mathfrak{g}$ соответственно.
+Обозначим через $\pi_{\af}$ оператор проекции $\pi_{\af}:\mathfrak{g}\longrightarrow \af$.
+В теории, связанной с $\mathfrak{g}$ и вакуумом $\left|\lambda\right>$ состояния строятся как
+\begin{equation*}
+  \label{eq:151}
+  J^{\alpha_1}_{-n_1}J^{\alpha_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
+\end{equation*}
+А для подалгебры $\af$ соответствующие состояния имеют вид
+\begin{equation*}
+  \label{eq:152}
+  \tilde{J}^{\alpha'_1}_{-n_1}\tilde{J}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\af}(\lambda)\right>.
+\end{equation*}
+Инвариантность вакуума под действием $\mathfrak{g}$ влечет его инвариантность относительно действия $\af$, но это неверно для тензора энергии-импульса.
+Необходимо, чтобы тензор энергии-импульса объемлющей теории содержал только генераторы $\tilde{J}$.
+Тогда соотношение
+\begin{equation}
+  \label{eq:127}
+  T_{\mathfrak{g}}(z)=T_{\af}(z)
+\end{equation}
+ведет к равенству центральных зарядов
+\begin{equation*}
+  \label{eq:33}
+  c(\mathfrak{g})=c(\af)
+\end{equation*}
+и к уравнению
+\begin{equation}
+  \label{eq:153}
+  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+h^{\vee}_{\gf}}=\frac{x_e k\; \mathrm{dim}\,\af}{x_ek+h^{\vee}_{\af}}.
+\end{equation}
+Здесь $x_e$ -- так называемый ``индекс вложения'':
+$x_e=\frac{\left|\pi_{\mathfrak{a}} \theta\right|^2}{\left|\theta_{\mathfrak{a}}\right|^2}$, где $\theta$, $\theta_{\mathfrak{a}}$ -- старшие корни алгебр
+$\mathfrak{g}$ и $\mathfrak{a}$, а  $h^{\vee}_{\gf}$ и $h^{\vee}_{\af}$ -- дуальные числа Кокстера.
+
+Можно показать, что решения уравнения (\ref{eq:153}) существуют только для уровня $k=1$ \cite{difrancesco1997cft}.
+Полная классификация конформных вложения дана в работе \cite{schellekens1986conformal}.  Для
 конформных вложений существуют специальные методы разложения представлений \cite{altschuler1990branching}.
 
-Модулярная инвариантность статсуммы для полей, принадлежащих представлениям алгебры  $\mathfrak{g}$,
-сохраняется при проекции на подалгебру $\mathfrak{a}$. Если все представления $\mathfrak{g}$ в теории
-удовлетворяют описанным требованиям, то при проекции мы получаем конформную теорию поля.
-
-Существует теорема о том, что для конформного вложения  $\mathfrak{a}\subset\mathfrak{g}$ только
-конечное число коэффициентов ветвления отлично от нуля \cite{kac1988modular,altschuler1990branching}. Поэтому после того, как мы разложили все
-представления $\mathfrak{g}$ мы подставляем результаты в выражение для статсуммы и получаем
-модулярно-инвариантную статсумму для вложенной теории. Такая статсумма уже не будет иметь
-диагональный вид:
-\begin{equation}
-  \label{eq:36}
-   Z_{\mathfrak{a}}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\mathfrak{a}}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau)
-\end{equation}
+Если рассмотреть соотношение (\ref{eq:153}) и асимптотику функций ветвления, то можно доказать теорему о конечной приводимости \cite{kac1988modular}.
+Она утверждает, что для конформного вложения  $\af\longrightarrow\mathfrak{g}$ лишь конечное число коэффициентов ветвления отлично от нуля.
+
 Таким образом, редукция представлений аффинной алгебры на представления подалгебры, рассмотренная в главе \ref{cha:affine-lie-algebras}, приводит к построению модулярно-инвариантных статсумм методом конформных вложений \cite{walton1989conformal}.

### 2012-08-10 AffineLieAlgebras/Thesis/1.tex
From V.D.

@@
 
-Простейшая модулярно-инвариантная статсумма имеет диагональный вид:
-\begin{equation}
-  \label{eq:148}
-   Z(\tau)=\sum_{ \mu\in P^{+}_{\mathfrak{g}}} \chi_{\mu}(\tau)\bar \chi_{\mu}(\bar \tau)
-\end{equation}
-Здесь суммирование ведется по множеству старших весов интегрируемых модулей в ВЗНВ-модели, а $\chi_{\mu}(\tau)$ -- это нормированные характеры (см. \cite{difrancesco1997cft}) этих модулей.
-
-Построение недиагональных модулярных инвариантов -- это нетривиальная проблема, хотя для некоторых моделей известна полная классификация модулярных инвариантов \cite{1994hepthGannon,1995JMPGannon}.
-
-Рассмотрим модель Весса-Зумино-Новикова-Виттена с аффинной алгеброй Ли $\af$.
-Недиагональные модулярные инварианты этой модели могут быть построены из диагонального инварианта, если существует аффинная алгебра  $\mathfrak{g}$, такая, что $\af\subset\mathfrak{g}$.
-Тогда мы можем заменить характеры  $\mathfrak{g}$-модулей в диагональной модулярно-инвариантной статсумме (\ref{eq:148}) на разложения
-\begin{equation*}
-  \label{eq:32}
-\sum_{\nu \in P^{+}_{\af}}b^{(\mu)}_{\nu} \chi_{\nu},
-\end{equation*}
-содержащие нормированные характеры $\chi_{\nu}$ соответствующих $\af$-модулей. В результате мы получим недиагональную модулярно-инвариантную статсумму для теории с алгеброй токов $\af$,
-\begin{equation}
-  \label{eq:154}
-   Z_{\af}(\tau)=\sum_{ \nu,\lambda\in P^{+}_{\af}} \chi_{\nu}(\tau)M_{\nu\lambda}\bar \chi_{\lambda}(\bar \tau).
-\end{equation}
-
-Эффективная процедура редукции существенна для этой конструкции.
-Вложение должно сохранять конформную инвариантность.
-Пусть $J^{\alpha_j}_{-n_j}$ и $\tilde{J}^{\alpha'_j}_{-n_j}$ -- понижающие операторы для алгебры $\mathfrak{g}$ и подалгебры $\af\subset\mathfrak{g}$ соответственно.
-Обозначим через $\pi_{\af}$ оператор проекции $\pi_{\af}:\mathfrak{g}\longrightarrow \af$.
-В теории, связанной с $\mathfrak{g}$ и вакуумом $\left|\lambda\right>$ состояния строятся как
-\begin{equation*}
-  \label{eq:151}
-  J^{\alpha_1}_{-n_1}J^{\alpha_2}_{-n_2}\dots\left|\lambda\right>\quad n_1\geq n_2\geq \dots>0.
-\end{equation*}
-А для подалгебры $\af$ соответствующие состояния имеют вид
-\begin{equation*}
-  \label{eq:152}
-  \tilde{J}^{\alpha'_1}_{-n_1}\tilde{J}^{\alpha'_2}_{-n_2}\dots\left|\pi_{\af}(\lambda)\right>.
-\end{equation*}
-Инвариантность вакуума под действием $\mathfrak{g}$ влечет его инвариантность относительно действия $\af$, но это неверно для тензора энергии-импульса.
-Необходимо, чтобы тензор энергии-импульса объемлющей теории содержал только генераторы $\tilde{J}$.
-Тогда соотношение
-\begin{equation}
-  \label{eq:127}
-  T_{\mathfrak{g}}(z)=T_{\af}(z)
-\end{equation}
-ведет к равенству центральных зарядов
-\begin{equation*}
-  \label{eq:33}
-  c(\mathfrak{g})=c(\af)
-\end{equation*}
-и к уравнению
-\begin{equation}
-  \label{eq:153}
-  \frac{k\;\mathrm{dim}\,\mathfrak{g}}{k+h^{\vee}_{\gf}}=\frac{x_e k\; \mathrm{dim}\,\af}{x_ek+h^{\vee}_{\af}}.
-\end{equation}
-Здесь $x_e$ -- так называемый ``индекс вложения'':
-$x_e=\frac{\left|\pi_{\mathfrak{a}} \theta\right|^2}{\left|\theta_{\mathfrak{a}}\right|^2}$, где $\theta$, $\theta_{\mathfrak{a}}$ -- старшие корни алгебр
-$\mathfrak{g}$ и $\mathfrak{a}$, а  $h^{\vee}_{\gf}$ и $h^{\vee}_{\af}$ -- дуальные числа Кокстера.
-
-Можно показать, что решения уравнения (\ref{eq:153}) существуют только для уровня $k=1$ \cite{difrancesco1997cft}.
-
-Полная классификация конформных вложения дана в работе \cite{schellekens1986conformal}.
-
+Отметим, что случай конформных вложений довольно специфичен.
 Если рассмотреть соотношение (\ref{eq:153}) и асимптотику функций ветвления, то можно доказать теорему о конечной приводимости \cite{kac1988modular}.
 Она утверждает, что для конформного вложения  $\af\longrightarrow\mathfrak{g}$ лишь конечное число коэффициентов ветвления отлично от нуля.
+Кроме того, верно следующее замечание.
 
@@
 В эти комбинации мы должны подставить генераторы подалгебры $\af$ выраженные через генераторы $\mathfrak{g}$ и получить тензор энергии-импульса $T_{\mathfrak{g}}$.
-Но если набор генераторов, связанных с  $\Delta_{\afb}$ не пуст, это не возможно, так как  $T_{\mathfrak{g}}$ содержит генераторы $J^{\alpha}_n$, где $\alpha\in \Delta_{\afb}$.
+Но если набор генераторов, связанных с  $\Delta_{\afb}$ не пуст, это невозможно, так как  $T_{\mathfrak{g}}$ содержит генераторы $J^{\alpha}_n$, где $\alpha\in \Delta_{\afb}$.
 \end{proof}
@@
 \label{sec:spec-embedd-hata_1s}
-Рассмотрим следующие пример аффинной алгебры Ли $\gf$ и аффинной подалгебры $\af$:
-$\hat{A}_1 \rightarrow \hat{A}_2$ и вложение является аффинным расширением специального вложения $A_1 \rightarrow A_2$ с индексом вложения $x_e=4$.
+Рассмотрим следующий пример конформного вложения  аффинной подалгебры $\af$ в  аффинную алгебру Ли $\gf$.
+Вложение $\hat{A}_1 \rightarrow \hat{A}_2$ является аффинным расширением специального вложения $A_1 \rightarrow A_2$ с индексом вложения $x_e=4$.
 Так как мы должны рассматривать $\gf$-модули уровня один, соответствующие  $\af$-модули будут иметь уровень $\tilde{k}=kx_e=4$.

### 2012-08-10 AffineLieAlgebras/Thesis/intro.tex
Some duplication is removed from the chapter 3. Authoreferat completed
From V.D.

@@
 
-Аффинные алгебры Ли были открыты Виктором Кацем \cite{kac1968simple} и Робертом Муди \cite{moody1968new} в 1967 году в результате отказа от требования положительной определенности матрицы Картана, определяющего полупростые конечномерные алгебры Ли.
+%%Аффинные алгебры Ли были открыты Виктором Кацем \cite{kac1968simple} и Робертом Муди \cite{moody1968new} в 1967 году в результате отказа от требования положительной определенности матрицы Картана, определяющего полупростые конечномерные алгебры Ли.
 Аффинные алгебры Ли отличаются тем, что матрица Картана, задающая коммутационные соотношения, лишь положительно полуопределена.
@@
 Теория представлений аффинных алегбр Ли играет определяющую роль при изучении важных классов моделей конформной теории поля -- моделей Весса-Зумино-Новикова-Виттена и coset-моделей.
-
+%%
+%%
 % Методы, используемые для изучения аффинных алгебр Ли, тесно связаны с теорией представлений конечномерных алгебр Ли, широко используемой в различных разделах физики, в том числе в теории элементарных частиц.
@@
 % Цель диссертационной работы
- \objectivesection
- \objectivetext
+% \objectivesection
+% \objectivetext
 
@@
 % Практическая ценность
- \valuesection
- \valuetext
+% \valuesection
+% \valuetext
 
@@
 % Личный вклад автора
-\contribsection
-\contribtext
+% \contribsection
+% \contribtext
 

### 2012-08-16 AffineLieAlgebras/Thesis/common.tex
Some notes for conclusions

@@
   \item Получено эффективное рекуррентное соотношение для коэффициентов ветвления модулей аффинных и конечномерных алгебр Ли на модули не максимальных подалгебр.
-  \item Показано, что наличие расщепления приводит к существенному упрощению при вычислении коэффициентов ветвления.
-  \item Показана связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
-  \item Предложено обобщение стохастического процесса Шрамма-Лёвнера на случай систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля.
+Алгоритм вычисления коэффициентов ветвления реализован в пакете  {\bf Affine.m} для популярной системы компьютерной алгебры {\it Mathematica}.
+  \item Установлена прямая связь инъективного сплинта и ветвлений.
+Доказано, что при определенных условиях  кратности весов вспомогательного модуля иньективного сплинта совпадают с коэффициентами ветвления в редукции на вложенную подалгебру.
+Наличие расщепления приводит к существенному упрощению при вычислении коэффициентов ветвления.
+%  \item Показано, что наличие расщепления приводит к существенному упрощению при вычислении коэффициентов ветвления.
+  \item Исследована связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
+  \item Построена модель обобщеннного стохастического процесса Шрамма-Лёвнера для систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля.
   \end{itemize}
-  Алгоритм вычисления коэффициентов ветвления реализован в пакете  {\bf Affine.m} для популярной системы компьютерной алгебры {\it Mathematica}.
-Пакет {\bf Affine.m} может быть использован для решения задач теории представлений конечномерных и аффинных алгебр Ли, возникающих в различных областях физики, начиная от изучения атомных и молекулярных спектров и заканчивая конформной теорией поля и интегрируемыми системами.
+Отметим, что  пакет {\bf Affine.m} может быть использован для решения задач теории представлений конечномерных и аффинных алгебр Ли, возникающих в различных областях физики, начиная от изучения атомных и молекулярных спектров и заканчивая конформной теорией поля и интегрируемыми системами.
 }
@@
 \item Из разложения сингулярных элементов получены новые рекуррентные соотношения на коэффициенты ветвления представлений аффинных алгебр Ли на представления произвольных редуктивных подалгебр
-\item Показана связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда
+\item Исследована связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда
 \item Выявлена связь расщепления корневой системы алгебры с разложением сингулярных элементов модулей алгебры в комбинацию сингулярных элементов модулей подалгебр

### 2012-08-23 AffineLieAlgebras/Thesis/2.tex
Some changes in chapters 3 and 5

@@
 \afb}}$, так что исходный характер $ch\left(
-L^{\mu }\right) $ в итоге раскладывается в знакопеременную сумму таких модулей.
+L^{\mu }\right) $ в итоге раскладывается в знакопеременную сумму характеров таких модулей.
 С другой стороны, если параболическое условие нарушено, конструкция сохраняется и порождает разложение по отношению к набору обобщенных модулей Верма  $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
@@
 
-Возможные обобщения полученных результатов обсуждаются в Разделе \ref{sec:conclusions}.
+% Возможные обобщения полученных результатов обсуждаются в Разделе \ref{sec:conclusions}.
 
@@
 \label{sec:conclusions}
-
-Мы показали, что разложение сингулярного элемента, возникающее при редукции модулей, оказывается связано с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
-При этом веер вложения порождает параболические модули Верма.
+В этой главе мы исследовали связь ветвления и обобщенной резольвенты Бернштейна-Гельфанда-Гельфанда.
+Как было показано в предыдущей главе, для построения коэффициентов ветвления осуществляется разложение сингулярного элемента неприводимого модуля алгебры в линейную комбинацию сингулярных элементов модулей подалгебры.
+Мы показали, что действие веера вложения на компоненты этого разложения порождает обобщенные модули Верма.
+Эти модули образуют точную последовательность обобщенной резольвенты Бернштейна-Гельфанда-Гельфанда.
+Характер исходного неприводимого модуля выражается через характеры обобщенных модулей Верма посредством формулы Вейля-Верма.
+Коэффициенты в этой формуле равняются коэффициентам разложения сингулярного элемента.
+Таким образом, разложение сингулярного элемента определяет как коэффициенты ветвления, так и обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда. 
+Кроме того, мы показали, что в случае когда ортогональный партнер подалгебры является алгеброй $A_1$, коэффициенты ветвления  определяют обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда. 
  Результаты данной главы опубликованы в работах \cite{2010LyakhovskyNazarovMQFT,2011arXiv1102.1702L}.

### 2012-08-23 AffineLieAlgebras/Thesis/4.tex
Some changes in chapters 3 and 5

@@
 \begin{eqnarray}
+  L_{1}\left|\psi\right>=0\\
+  L_{2}\left|\psi\right>=0
+\end{eqnarray}
+В силу конструкции Сугавары (\ref{eq:91}) $  L_n=\frac{1}{2(k+h^{\vee})}\sum_a\sum_m:J^a_m J^a_{n-m}:$ это условие может быть выполнено только если $J^{a}_{n} \left|\psi\right>=0$
+\begin{eqnarray}
     J^{a}_{1} \left|\psi\right>=0\\
-  J^{a}_{2}\left|\psi\right>=0\\
-  L_{2}\left|\psi\right>=0\\
-  L_{1}\left|\psi\right>=0
+    J^{a}_{2}\left|\psi\right>=0.
 \end{eqnarray}
+
 Эти уравнения можно переписать как алгебраические соотношения, связывающие параметры случайного блуждания $\kappa, \tau$ с уровнем  $k$ представления аффинной алгебры Ли, если воспользоваться коммутационными соотношениями  (\ref{eq:102}), (\ref{eq:90}).

### 2012-08-29 AffineLieAlgebras/Thesis/4.tex
Some changes in chapter 5

--- 2012-07-26 AffineLieAlgebras/Thesis/4.tex
@@
 \end{equation}
-является нулевым состоянием уровня два и если на него подействовать повышающими операторами, мы должны получить ноль.
+является нулевым состоянием уровня два.
+Из того, что корреляторы примарных полей с полем $\psi$ равны нулю следует, что состояние $\left|\psi\right>$ содержится в инвариантном подмодуле модуля Верма аффинной алгебры $\gfh$, порожденного действием операторов $J^a_n$ на состояние $\phi_{\Lambda}$, отвечающее старшему весу $\Lambda$.
+Таким образом, условие мартингала относительно эволюции Шрамма-Левнера эквивалентно тому, что некоторый вектор не принадлежит неприводимому модулю аффинной алгебры, а содержится в максимальном инвариантном подмодуле модуля Верма.
+Как видно, например, из конструкции БГГ-резольвенты (см.
+главу \ref{cha:BGG}), инвариантные подмодули в модуле Верма тесно связаны со структурой сингулярного элемента неприводимого модуля.
+
+Если на состояние $\left|\psi\right>$ подействовать повышающими операторами, мы должны получить ноль.
 \begin{eqnarray}
+ \label{eq:34}
+ L_{1}\left|\psi\right>=0\\
+  L_{2}\left|\psi\right>=0
+\end{eqnarray}
+В силу конструкции Сугавары (\ref{eq:91}) $  L_n=\frac{1}{2(k+h^{\vee})}\sum_a\sum_m:J^a_m J^a_{n-m}:$ это условие может быть выполнено только если $J^{a}_{n} \left|\psi\right>=0$
+\begin{eqnarray}
+  \label{eq:36} 
   J^{a}_{1} \left|\psi\right>=0\\
-  J^{a}_{2}\left|\psi\right>=0\\
-  L_{2}\left|\psi\right>=0\\
-  L_{1}\left|\psi\right>=0
+  J^{a}_{2}\left|\psi\right>=0.
 \end{eqnarray}
 Эти уравнения можно переписать как алгебраические соотношения, связывающие параметры случайного блуждания $\kappa, \tau$ с уровнем  $k$ представления аффинной алгебры Ли, если воспользоваться коммутационными соотношениями  (\ref{eq:102}), (\ref{eq:90}).
-Строгий анализ полученных алгебраических соотношений проведен в работе \cite{alekseev2010sle}.
+Полный анализ таких алгебраических соотношений проведен в работе \cite{alekseev2010sle}.
+
+Однако мы воспользуемся другим подходом.
+Рассмотрим состояние $\left|\psi\right>$ с точки зрения конечномерной подалгебры $\gf\subset\gfh$.
+Все три слагаемых, действующих на состояние $\left|\phi_{\Lambda}\right>$ в формуле (\ref{eq:16}) с точки зрения подалгебры $\gf$ являются квадратичными операторами Казимира (пропорциональны $\sum_a J^a J^a$).
+Поэтому состояние $\left|\psi\right>$ отвечает весу $\Lambda-2\delta$.
+
+Сразу можно написать необходимое условие на уровень и старший вес $\Lambda$: вектор веса  $\Lambda-2\delta$ должен содержаться в модуле Верма $V^{\mu}$, старший вес которого $\mu$ является сингулярным для неприводимого модуля $L^{\Lambda}$.
+То есть должны существовать неотрицательные числа $a_0,\dots,a_r\in \mathbb{Z}_+$ ($r=\mathrm{rank}(\gf)$) и отражение Вейля $w\in W_{\gfh}$ такие, что $\Lambda-2\delta = w(\Lambda+\rho)-\rho-\sum_{k=0}^r a_k \alpha_k$.
+Вспомним, что группа Вейля аффинной алгебры Ли $\gfh$  представляет собой полупрямое произведение группы Вейля конечномерной алгебры $\gf$ и группы трансляций, порожденной простыми корнями $\alpha_1,\dots,\alpha_r$.
+Так как $\alpha_0 = \delta-\theta$ получаем, что $a_0=2$
+
+Рассмотрим некоторые примеры. 
+Простейший случай, когда выполняются условия (\ref{eq:34}),(\ref{eq:36}) -- это $\gfh = \hat{\mathfrak{su}}(2),\; \Lambda=\omega_1,\; k=1,\; \forall \kappa: \tau = 2-\kappa/2$.
 

### 2012-08-30 AffineLieAlgebras/Thesis/4.tex
Added some text on singular elements and Schramm-Loewner evolution.

@@
 
-Однако мы воспользуемся другим подходом.
-Рассмотрим состояние $\left|\psi\right>$ с точки зрения конечномерной подалгебры $\gf\subset\gfh$.
-Все три слагаемых, действующих на состояние $\left|\phi_{\Lambda}\right>$ в формуле (\ref{eq:16}) с точки зрения подалгебры $\gf$ являются квадратичными операторами Казимира (пропорциональны $\sum_a J^a J^a$).
+Мы продемонстрируем другой подход к анализу соотношения (\ref{eq:16}).
+С точки зрения конечномерной подалгебры $\gf\subset\gfh$ все три слагаемых, действующих на состояние $\left|\phi_{\Lambda}\right>$ в формуле (\ref{eq:16}), являются квадратичными операторами Казимира (пропорциональны $\sum_a J^a J^a$).
 Поэтому состояние $\left|\psi\right>$ отвечает весу $\Lambda-2\delta$.
 
-Сразу можно написать необходимое условие на уровень и старший вес $\Lambda$: вектор веса  $\Lambda-2\delta$ должен содержаться в модуле Верма $V^{\mu}$, старший вес которого $\mu$ является сингулярным для неприводимого модуля $L^{\Lambda}$.
-То есть должны существовать неотрицательные числа $a_0,\dots,a_r\in \mathbb{Z}_+$ ($r=\mathrm{rank}(\gf)$) и отражение Вейля $w\in W_{\gfh}$ такие, что $\Lambda-2\delta = w(\Lambda+\rho)-\rho-\sum_{k=0}^r a_k \alpha_k$.
-Вспомним, что группа Вейля аффинной алгебры Ли $\gfh$  представляет собой полупрямое произведение группы Вейля конечномерной алгебры $\gf$ и группы трансляций, порожденной простыми корнями $\alpha_1,\dots,\alpha_r$.
-Так как $\alpha_0 = \delta-\theta$ получаем, что $a_0=2$
+Из этого следует необходимое условие на уровень и старший вес $\Lambda$: вектор веса  $\Lambda-2\delta$ должен содержаться в модуле Верма $V^{\mu}_{\gfh}$, старший вес которого $\mu=w(\Lambda+\rho)-\rho$ является сингулярным для неприводимого модуля $L^{\Lambda}_{\gfh}$.
+То есть должны существовать неотрицательные числа $a_0,\dots,a_r\in \mathbb{Z}_+$ ($r=\mathrm{rank}(\gf)$)  такие, что
+\begin{equation}
+  \Lambda-2\delta = \mu-\sum_{k=0}^r a_k \alpha_k.
+\label{eq:109}
+\end{equation} 
+Рассмотрим сингулярные веса с минимальным грейдом, которые могут входить в правую часть уравнения (\ref{eq:109}).
+Во-первых, это сингулярные веса в нулевом грейде, которые совпадают с сингулярными весами неприводимого модуля $L^{\Lambda}$ конечномерной алгебры $\gf$.
+Так как $\alpha_0 = \delta-\theta$ получаем в этом случае, что $a_0=2$ и $\Lambda-\mu= 2\theta-\sum_{k=1}^r a_k \alpha_k, \; a_k\geq 0$.
+В случае алгебры $\gf=\mathfrak{su}(2)$ имеем $\Lambda=l\omega_1,\; \theta=2\omega_1,\; \rho=\omega_1,\; \mu=-(l+2)\omega_1$ и $2l+2=4-2a_1$.
+То есть $a_1=0$ и $l=1$, а поле $\phi_{\Lambda}$ имеет спин $\frac{1}{2}$.
+В случае алгебры $\gf=\mathfrak{su}(N)$ аналогичное рассуждение выполняется для каждого из индексов Дынкина, отличных от нуля.
+То есть равенство (\ref{eq:109}) может выполняться только если каждый из индексов Дынкина не более единицы.
 
-Рассмотрим некоторые примеры. 
-Простейший случай, когда выполняются условия (\ref{eq:34}),(\ref{eq:36}) -- это $\gfh = \hat{\mathfrak{su}}(2),\; \Lambda=\omega_1,\; k=1,\; \forall \kappa: \tau = 2-\kappa/2$.
+Вспомним, что группа Вейля аффинной алгебры Ли $\gfh$  представляет собой полупрямое произведение группы Вейля конечномерной алгебры $\gf$ и группы трансляций $T=\left\{t_{\alpha_k}\right\}$, порожденной простыми корнями $\alpha_1,\dots,\alpha_r$.
+Так как  $t_{\alpha}\lambda=\lambda+\frac{2(\lambda,\delta)}{(\alpha,\alpha)}\alpha-\left(\frac{(\alpha,\alpha)}{2} (\lambda,\delta)+(\lambda,\alpha)\right) \delta$, в случае длинного корня $\alpha:\; (\alpha,\alpha)=2$ при $k>2$ и $(\alpha,\lambda)\neq 0$ условие (\ref{eq:109}) не может выполняться для $\mu=t_{\alpha} w(\Lambda+\rho)-\rho, \; w\in W_{\gf}$ просто в силу того, что грейд в правой части меньше $-2$.
+
+Таким образом условие (\ref{eq:109}), характеризующее структуру сингулярного элемента представления аффинной алгебры Ли $\gfh$, исключает из рассмотрение большое количество примарных полей $\phi_{\Lambda}$.
+Вместе с тем это условие несколько слабее, чем необходимые условия, полученные в разделе 2 работы \cite{alekseev2010sle}.
 
@@
 Необходимо проверить, что взаимодействие возмущающего примарного поля с  $\tau$-членом уравнения (\ref{eq:181}) приводит к такому же вкладу, что и введение массивного сноса в эволюцию Шрамма-Лёвнера.
-
-В дальнейших исследованиях мы планируем ответить на данный вопрос и сравнить массивные возмущения coset-моделей с результатами численного изучения доменных стенок в модели Изинга, возмущенной случайным гауссовым полем \cite{stevenson2011domain}.
+Кроме того, требуется сравнить массивные возмущения coset-моделей с результатами численного изучения доменных стенок в модели Изинга, возмущенной случайным гауссовым полем \cite{stevenson2011domain}.
 

### 2012-08-30 AffineLieAlgebras/Thesis/5.tex
Added some text on singular elements and Schramm-Loewner evolution.

@@
 \label{sec:6-conclusion}
-В данной главе мы использовали свойства сингулярных элементов для классификации операторов изменения граничных условий в coset-моделях конформной теории поля, соответствующих стохастическим моделям с эволюцией Шрамма-Левнера с дополнительным блужданием на факторпространстве $G/A$.
+В данной главе мы исследовали классификацию операторов изменения граничных условий в моделях Весса-Зумино-Новикова-Виттена, соответствующих стохастическим моделям с эволюцией Шрамма-Левнера с дополнительным блужданием на группе Ли $G$ Мы показали, что условие для мартингала, определяющее классификацию операторов изменения граничных условий, задает ограничения на структуру сингулярных элементов представлений аффинной алгебры Ли, порожденных граничными состояниями.
+Изучение структуры сингулярных элементов существенно упрощает поиск операторов смены граничных условий, так как отсекается большое количество лишних вариантов.
+
+Кроме того, мы обобщили эволюцию Шрамма-Левнера путем введения дополнительного случайного блуждания на факторпространстве $G/A$.
+Наблюдаемые такого стохастического процесса описываются корреляторами в coset-моделях конформной теории поля.
+
+Мы показали, что наше обобщение эволюции Шрамма-Левнера путем добавления случайного блуждания на факторпространстве $G/A$ совместно с coset-реализацией минимальных моделей конформной теории поля.
 

### 2012-08-30 AffineLieAlgebras/Thesis/review.tex
Added some text on singular elements and Schramm-Loewner evolution.

@@
 Рассмотрим действие элемента группы Вейля $s_{\alpha}s_{\alpha+\delta}$ аффинной алгебры Ли   $\hat\gf$, соответствующего простому корню  $\alpha$ конечномерной подалгебры Ли $\gf$.
-Из определения  \eqref{eq:117} легко видеть, что $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
+Из определения  \eqref{eq:117} легко видеть, что $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2(\lambda,\delta)}{(\alpha,\alpha)}\alpha-\left(\frac{(\alpha,\alpha)}{2} (\lambda,\delta)+(\lambda,\alpha)\right) \delta$.
 То есть группа Вейля для аффинной алгебры Ли может быть представлена как полупрямое произведение группы Вейля $W_{\gf}$ конечномерной подалгебры  $\gf$ и трансляций, соответствующих корням $\gf$.

### 2012-08-31 AffineLieAlgebras/Thesis/5.tex
Autoreferat revised, conclusion for the whole thesis is written.

@@
 \label{sec:6-conclusion}
-В данной главе мы исследовали классификацию операторов изменения граничных условий в моделях Весса-Зумино-Новикова-Виттена, соответствующих стохастическим моделям с эволюцией Шрамма-Левнера с дополнительным блужданием на группе Ли $G$ Мы показали, что условие для мартингала, определяющее классификацию операторов изменения граничных условий, задает ограничения на структуру сингулярных элементов представлений аффинной алгебры Ли, порожденных граничными состояниями.
+В данной главе мы исследовали классификацию операторов изменения граничных условий в моделях Весса-Зумино-Новикова-Виттена, соответствующих стохастическим моделям с эволюцией Шрамма-Левнера с дополнительным блужданием на группе Ли $G$.
+Мы показали, что условие для мартингала, определяющее классификацию операторов изменения граничных условий, задает ограничения на структуру сингулярных элементов представлений аффинной алгебры Ли, порожденных граничными состояниями.
 Изучение структуры сингулярных элементов существенно упрощает поиск операторов смены граничных условий, так как отсекается большое количество лишних вариантов.

### 2012-08-31 AffineLieAlgebras/Thesis/3.tex
Autoreferat revised, conclusion for the whole thesis is written.

@@
 
-Нами установлена непосредственная связь инъективного сплинта и ветвлений: доказано, что при условии включения образа $\phi(\Phi_{\sfr}^{(\tilde \mu)}$ в $\bar C_{\af}$ кратность веса вспомогательного модуля определяет коэффициент ветвления $b_{\nu}^{(\mu)}$.
+Нами установлена непосредственная связь инъективного сплинта и ветвлений: доказано, что при условии включения образа $\phi(\Phi_{\sfr}^{(\tilde \mu)})$ в $\bar C_{\af}$ кратность веса вспомогательного модуля определяет коэффициент ветвления $b_{\nu}^{(\mu)}$.
 Далее мы продемонстрировали, что это свойство сплинта представляет очень эффективный инструмент для вычисления коэффициентов ветвления.
 В частности, инъективные сплинты дают возможность свести определение правил ветвления модулей старшего веса к вычислению кратностей весов для модуля с теми же индексами Дынкина алгебры Ли $\mathfrak{s}$.
-Эта алгебра $\mathfrak{s}$ не обязательно является подалгеброй в  $\gf$ , ее ранг $r_{\mathfrak{s}}=r$ совпадает с рангом $\gf$, но сома она ``проще'' чем  $\gf$, так как только подмножество корней корневой системы включено во второй ``стебель''  $\Delta_{\mathfrak{s}}$.
+Эта алгебра $\mathfrak{s}$ не обязательно является подалгеброй в  $\gf$ , ее ранг $r_{\mathfrak{s}}=r$ совпадает с рангом $\gf$, но сама она ``проще'' чем  $\gf$, так как только подмножество корней корневой системы включено во второй ``стебель''  $\Delta_{\mathfrak{s}}$.
 В этом случае для вычислений коэффициентов ветвления можно применять не только общий алгоритм (раздел \label{sec:algorithm}), но и формулу Фрейденталя, позволяющую быстро вычислять кратности весов.

### 2012-08-31 AffineLieAlgebras/Thesis/intro.tex
Autoreferat revised, conclusion for the whole thesis is written.

@@
 
-Основной проблемой данной диссертации является изучение редукции модулей аффинных и конечномерных алгебр Ли на модули подалгебр, вычисление коэффициентов ветвления.
+Мы описываем возникновение в конформной теории поля одной из основных проблем данной диссертации -- задачи редукции модулей аффинных и конечномерных алгебр Ли на модули подалгебр и вычисления коэффициентов ветвления.
 
@@
 
+В данной главе мы показываем, что
+
 В следующей главе \ref{cha:BGG} мы проясняем связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
+Разложение сингулярного элемента, предложенное в главе \ref{cha:affine-lie-algebras}, используется для построения параболических модулей Верма и получения обобщенных формул Вейля-Верма для характеров.
+Параболические модули Верма образуют обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда.
+То есть ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и демонстрирует свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).
 Результаты третьей главы опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}
@@
 
+В заключении мы кратко перечисляем основные теоретические результаты работы и их практические приложения.
 %%% Local Variables: 

### 2012-08-31 AffineLieAlgebras/Thesis/common.tex
Autoreferat revised, conclusion for the whole thesis is written.

@@
 
-Моделям Весса-Зумино-Новикова-Виттена и coset-моделям  посвящены тысячи работ.
-Большой интерес вызывает и теория представлений аффинных алгебр Ли.
-Вместе с тем, в теории представлений многие вопросы по-прежнему не имеют простых решений.
-Например, проблема вычисления коэффициентов ветвления для представлений алгебр Ли стоит уже многие десятилетия.
+Моделям Весса-Зумино-Новикова-Виттена, coset-моделям и теории представлений аффинных алгебр Ли  посвящены тысячи работ.
+Однако многие проблемы по-прежнему не имеют простых решений.
+Например, задача вычисления коэффициентов ветвления для представлений алгебр Ли стоит уже многие десятилетия.
 Она актуальна для различных физических приложений в coset-моделях конформной теории поля.
-Вместе с тем, в отличие от проблемы вычисления кратностей весов, для вычисления коэффициентов ветвления не существовало особенно эффективных алгоритмов.
+При этом, в отличие от проблемы вычисления кратностей весов, для вычисления коэффициентов ветвления не существовало особенно эффективных алгоритмов.
 }
@@
   \item Исследована связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
+Показано, что разложение сингулярного элемента определяет как коэффициенты ветвления, так и обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда, так как действие веера вложения на компоненты разложения порождает обобщенные модули Верма, которые образуют точную последовательность.
   \item Построена модель обобщеннного стохастического процесса Шрамма-Лёвнера для систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля.
@@
 \begin{itemize}
-\item Продемонстрирована роль сингулярных элементов в описании структуры модулей аффинных алгебр Ли 
+\item Продемонстрировано, что сингулярные элементы определяет структуру модулей аффинных алгебр Ли 
 \item Из разложения сингулярных элементов получены новые рекуррентные соотношения на коэффициенты ветвления представлений аффинных алгебр Ли на представления произвольных редуктивных подалгебр
@@
 \item Показано, что наличие расщепления приводит к существенному упрощению при вычислении коэффициентов ветвления и ведет к новым соотношениям на функции ветвления
-\item Предложено обобщение стохастического процесса Шрамма-Лёвнера на случай систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля
+\item Показано, что условие для мартингала, определяющее классификацию операторов изменения граничных условий в наблюдаемых стохастического процесса Шрамма-Лёвнера, задает ограничения на структуру сингулярных элементов представлений аффинной алгебры Ли, порожденных граничными состояниями.
+Изучение структуры сингулярных элементов существенно упрощает поиск операторов смены граничных условий, так как отсекается большое количество лишних вариантов.
+\item Построена модель обобщеннного стохастического процесса Шрамма-Лёвнера для систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля и показано, что такое обобщение совместно с coset-реализацией минимальных моделей.
 %\item Продемонстрирована роль сингулярных элементов в построении мартингалов стохастического процесса Шрамма-Лёвнера, то есть проиллюстрировано применение алгебраических методов теории представлений аффинных алгебр Ли в изучении критического поведения в двумерных решеточных моделях
@@
 
-Диссертация состоит из введения и шести глав, содержит 157 страниц и 30 рисунков. Список литературы включает 151 наименование.
+Диссертация состоит из введения и шести глав, содержит 160 страниц и 30 рисунков. Список литературы включает 151 наименование.
 

### 2012-08-31 AffineLieAlgebras/Thesis/concl.tex
Some notes for conclusions
Added some text on singular elements and Schramm-Loewner evolution.
Autoreferat revised, conclusion for the whole thesis is written.

--- 2011-11-10 AffineLieAlgebras/Thesis/review.tex
@@
-\review
+\conclusion
+\label{cha:conclusion}
+
+В данной диссертации были решены следующие задачи, возникающие в конформной теории поля и при изучении критических явлений.
+
+Во-первых, мы рассмотрели проблему разложения модуля аффинной алгебры Ли в прямую сумму модулей редуктивной подалгебры.
+Данная задача возникает в конформной теории поля при построении модулярно-инвариантных статсумм в ВЗНВ-моделях методом конформных вложений и статсумм в coset-моделях рациональной конформной теории поля.
+Мы показали, что техника веера вложения может использоваться для работы с произвольными редуктивными подалгебрами, как максимальными, так и не максимальными.
+Использование данной техники и разложение сингулярного элемента позволили нам вывести рекуррентные соотношения на коэффициенты ветвления, которые можно решать последовательно.
+Эти соотношения позволяют эффективно вычислять коэффициенты ветвления, что было продемонстрировано на различных примерах.
+
+Во-вторых  мы исследовали связь ветвления и обобщенной резольвенты Бернштейна-Гельфанда-Гельфанда.
+Мы показали, что действие веера вложения на компоненты разложения сингулярного элемента порождает обобщенные модули Верма.
+Эти модули образуют точную последовательность обобщенной резольвенты Бернштейна-Гельфанда-Гельфанда.
+Характер исходного неприводимого модуля выражается через характеры обобщенных модулей Верма посредством формулы Вейля-Верма.
+Коэффициенты в этой формуле равняются коэффициентам разложения сингулярного элемента.
+Таким образом, разложение сингулярного элемента определяет как коэффициенты ветвления, так и обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда. 
+Кроме того, мы показали, что в случае когда ортогональный партнер подалгебры является алгеброй $A_1$, коэффициенты ветвления  определяют обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда.
+
+Также нами была установлена связь инъективного сплинта и ветвлений.
+Для сплинта $\phi:\Delta^+_{\af}\cup \Delta^+_{\sfr}\to \Delta^+_{\gf}$ доказано, что при условии включения образа  $\phi(\Phi_{\sfr}^{(\tilde \mu)})$ сингулярного элемента вспомогательного модуля алгебры $\sfr$ в главную камеру Вейля  $\bar C_{\af}$ подалгебры $\af$ кратность веса вспомогательного модуля определяет коэффициент ветвления $b_{\nu}^{(\mu)}$.
+Это свойство сплинта представляет очень эффективный инструмент для вычисления коэффициентов ветвления, так как определение правил ветвления модулей старшего веса сводится к вычислению кратностей весов для модуля с теми же индексами Дынкина алгебры Ли $\mathfrak{s}$.
+В этом случае для вычислений коэффициентов ветвления можно применять не только общий алгоритм (раздел \label{sec:algorithm}), но и формулу Фрейденталя, позволяющую быстро вычислять кратности весов.
+Для вложений  $D_{r}\hookrightarrow B_{r}$ , $D_{r}\hookrightarrow C_{r}$ и $A_{r-1}\oplus u\left( 1\right) \hookrightarrow A_{r}$ существование сплинта ведет к появлению правил ветвления Гельфанда-Цейтлина: редукция свободна от множественности (все ненулевые коэффициенты ветвления равны 1).
+Кроме того, мы продемонстрировали, что сплинт для аффинных алгебр Ли ведет к новым соотношениям на тета-функции и функции ветвления для редукции на модули конечномерных подалгебр.
+
+Наконец, мы исследовали классификацию операторов изменения граничных условий в моделях Весса-Зумино-Новикова-Виттена, соответствующих стохастическим моделям с эволюцией Шрамма-Левнера с дополнительным блужданием на группе Ли $G$.
+Было показано, что условие для мартингала, определяющее классификацию операторов изменения граничных условий, задает ограничения на структуру сингулярных элементов представлений аффинной алгебры Ли, порожденных граничными состояниями.
+Изучение структуры сингулярных элементов существенно упрощает поиск операторов смены граничных условий, так как отсекается большое количество лишних вариантов.
+Далее мы обобщили эволюцию Шрамма-Левнера путем введения дополнительного случайного блуждания на факторпространстве $G/A$ и показали, что такое обобщение эволюции Шрамма-Левнера совместно с coset-реализацией минимальных моделей конформной теории поля.
+
+Полученные рекуррентные соотношения на коэффициенты ветвления и свойства сплинта были нами использованы при реализации пакета программ {\bf Affine.m}  для вычислений в теории представлений конечномерных и аффинных алгебр Ли.
+Этот пакет он может использоваться для изучения групп Вейля, корневых систем, неприводимых модулей, модулей Верма и параболических модулей Верма конечномерных и аффинных алгебр Ли.
+Большое число иллюстраций и вычислений в данной работе выполнены с использованием пакета  {\bf Affine.m}.
+Однако применения пакета не ограничиваются задачами, возникающими в конформной теории поля, он может быть полезен и при изучении интегрируемых систем, исследовании атомных и молекулярных спектров и в других областях физики, где используется теория представлений конечномерных и аффинных алгебр Ли.
+
+Теоретические идеи и методы данной работы могут быть в дальнейшем использованы при изучении представлений более широкого класса алгебр -- расширенных алгебр Каца-Муди.
+Кроме того, в теории критического поведения большой интерес вызывает задача описания нарушения конформной инвариантности при выходе из критической точки.
+При этом возникают квантовые теории поля типа аффинной теории Тоды, в которых алгебраическая структура частично сохраняется и теория представлений аффинных алгебр Ли остается важным инструментом.
+Кроме того, может быть расширена и область применения пакет {\bf Affine.m}, в частности, планируется улучшение интерфейса и непосредственная поддержка вычисления коэффициентов разложения тензорных произведений представлений на неприводимые.
 

### 2012-09-09 AffineLieAlgebras/Thesis/common.tex
Minor changes in common.tex and bibliography

@@
 \begin{itemize}
-\item Продемонстрировано, что сингулярные элементы определяет структуру модулей аффинных алгебр Ли 
-\item Из разложения сингулярных элементов получены новые рекуррентные соотношения на коэффициенты ветвления представлений аффинных алгебр Ли на представления произвольных редуктивных подалгебр
-\item Исследована связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда
-\item Выявлена связь расщепления корневой системы алгебры с разложением сингулярных элементов модулей алгебры в комбинацию сингулярных элементов модулей подалгебр
-\item Показано, что наличие расщепления приводит к существенному упрощению при вычислении коэффициентов ветвления и ведет к новым соотношениям на функции ветвления
+\item Получены новые рекуррентные соотношения на коэффициенты ветвления представлений аффинных алгебр Ли на представления произвольных редуктивных подалгебр, с использованием разложения сингулярных элементов
+\item Установлено, что разложение сингулярного элемента определяет как коэффициенты ветвления, так и обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда, так как действие веера вложения на компоненты разложения порождает обобщенные модули Верма, которые образуют точную последовательность
+\item  Доказано, что при определенных условиях  кратности весов вспомогательного модуля иньективного сплинта совпадают с коэффициентами ветвления в редукции на вложенную подалгебру.
+Наличие расщепления приводит к существенному упрощению при вычислении коэффициентов ветвления.
 \item Показано, что условие для мартингала, определяющее классификацию операторов изменения граничных условий в наблюдаемых стохастического процесса Шрамма-Лёвнера, задает ограничения на структуру сингулярных элементов представлений аффинной алгебры Ли, порожденных граничными состояниями.
-Изучение структуры сингулярных элементов существенно упрощает поиск операторов смены граничных условий, так как отсекается большое количество лишних вариантов.
-\item Построена модель обобщеннного стохастического процесса Шрамма-Лёвнера для систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля и показано, что такое обобщение совместно с coset-реализацией минимальных моделей.
+Изучение структуры сингулярных элементов существенно упрощает поиск операторов смены граничных условий.
+Построена модель обобщеннного стохастического процесса Шрамма-Лёвнера для систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля и показано, что такое обобщение совместно с coset-реализацией минимальных моделей.
 %\item Продемонстрирована роль сингулярных элементов в построении мартингалов стохастического процесса Шрамма-Лёвнера, то есть проиллюстрировано применение алгебраических методов теории представлений аффинных алгебр Ли в изучении критического поведения в двумерных решеточных моделях

### 2012-09-17 AffineLieAlgebras/Thesis/review.tex
PDF sent to reviewers

@@
   \begin{enumerate}
-  \item Для всех $j\in B_{0}$ отображения $\varphi_{j}:S^{+}\to \mathrm{End}(D)$ линейны, $\varphi_{j}$ -- полевые операторы, $\varphi_{j}(D)\subset D, \Omega\in D$ и вакуум $\Omega$ инвариантен относительно инвариантных представлений $U$ группы $E_{2}$.
+  \item Для всех $j\in B_{0}$ отображения $\varphi_{j}:S^{+}\to \mathrm{End}(D)$ линейны, $\varphi_{j}$ -- полевые операторы, $\varphi_{j}(D)\subset D, \Omega\in D$ и вакуум $\Omega$ инвариантен относительно унитарных представлений $U$ группы $E_{2}$.
   \item Поля $\varphi_{j}$ преобразуются ковариантно по отношению к представлению $U$, для $w\in E_{2}$:

### 2012-09-19 GeneralOverview/CFT-talk.tex
CFT talk added

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{graphicx}
\pagestyle{plain}
 \newtheorem{theorem}{Теорема}
\theoremstyle{definition} 
\newtheorem{Def}{Definition}
\newtheorem{axiom}{Аксиома}

\topmargin=-3.5cm
\oddsidemargin=-1.5cm
\evensidemargin=-1.5cm
\textwidth=19cm
\textheight=28cm

\title{Что такое конформная теория поля?}
\author{Антон Назаров\\ antonnaz@gmail.com}
\begin{document}
\maketitle

Здравствуйте!

Мой доклад называется ``Что такое конформная теория поля?'' и я сразу
отвечу на этот вопрос. Конформная теория поля -- это квантовая теория
поля, обладающая конформной инвариантностью.  Я объясню, что значат
эти слова, но сперва мотивация.

Рассмотрим нашу любимую модель Изинга. Это простая модель магнетика.
У нас есть квадратная решетка, в вершинах которой находятся спины
$\sigma$, принимающие значения $\pm 1$. Энергия конфигурации дается
суммой произведений ближайших соседей
$E[\sigma]=\sum_{\left<ij\right>} \sigma_i \sigma_j$, а вероятность
конфигурации равна экспоненте от минус бета на энергию
$P[\sigma]=\frac{1}{Z}e^{-\beta E[\sigma]}$. Нас интересуют локальные 
наблюдаемые -- средние значения функций от спинов в заданных узлах
$f(z_1,\dots,z_n)=\sum_{[\sigma]} f(\sigma(z_1),\dots,\sigma(z_n))
P[\sigma]$.

Так как в настоящем магнетике очень много узлов, а расстояние между
ними очень маленькое, возникает естественное желание перейти к
непрерывному описанию. Мы можем переписать энергию через разностные производные
$E[\sigma]=\sum_x \sum_y \left( \frac{(\sigma(x,y)-\sigma(x+\Delta
    x,y))^2}{\Delta x^2} + \frac{(\sigma(x,y)-\sigma(x,y+\Delta
    y))^2}{\Delta y^2}\right) +\mathrm{const}$
и перейти к пределу $\Delta x, \Delta y\to 0$. Тогда для энергии
получится выражение типа 
$E[\varphi]=\int dx dy \left( (\partial_x \varphi)^2+(\partial_y
  \varphi)^2\right)$

У нас получилась теория поля. Нам надо еще накладывать дополнительные
условия на поля, которые были бы аналогом того, что спины $\sigma=\pm
1$.  Наши наблюдаемые -- это корреляционные функции. Они должны быть
средними значениями по всем конфигурациям поля, поэтому теория поля
должна быть квантовой.

Мы знаем, что в критической точке корреляционные функции обладают
определенными свойствами по отношению к конформным преобразованиям.

Что же такое теория поля?

Напомню про классическую механику. Она появилась из наблюдений за
планетами, поэтому в ней есть точечные объекты с координатами
$p_i, q_i$  в $n$-мерном пространстве. Координаты удовлетворяют
дифференциальным уравнениям 
$\dot p_i = -\partial_{q_i} H(p,q,t)$, $\dot q_i = \partial_{p_i}
H(p,q,t)$,

Решения ищутся в классе каких-то хороших функций, например, гладких.

Теория поля -- это естественное обобщение классической механики, когда
речь идет не об отдельных точечных объектах, а о среде. Физики
смотрели на то, как железные опилки выстраиваются вокруг магнита и
видели картинки силовых линий, поэтому предположили, что существует
некоторое поле, которое их выстраивает.

Само поле должно удовлетворять каким-то уравнениям, например, $\vec
E=-\nabla \varphi$, $\Delta \varphi=4\pi \rho$. 
Так как мы хотим, чтобы у нас могли быть точечные заряды
$\rho=\delta(\vec x - \vec x_0)$, то мы не можем обойтись функциями,
приходится переходить к распределениям.
Пространство тест-функций Шварца мы будем обозначать через
$S(\mathbb{R}^n)=\{f:\mathbb{R}^n\to \mathbb{C}\}$, распределения --
это непрерывные функционалы $T:S(\mathbb{R}^n)\to \mathbb{C}$ на
пространстве тест-функций. Понятно, что для каждой измеримой функции
$g$ есть распределение $T_g (f) = \int_{\mathbb{R}^n} g(x) f(x) dx$.
Распределения можно дифференцировать $(\partial^{\alpha} T) (f) =
(-1)^{|\alpha|} T(\partial^{\alpha} f)$. Кроме того, любое
интересующее нас распределение можно представить в виде $T=\sum_{0\leq
  |\alpha| \leq n} \partial^{\alpha} T_{g_a}$.

Таким образом, классическая теория поля -- это наука о
распределениях, удовлетворяющих некоторым дифференциальным уравнениям
в частных производных.

Теперь слово ``квантовая''. В начале XX века обнаружилось, что у
микроскопических частиц не удается одновременно точно измерить
координату и импульс. Была предложена следующая конструкция --
состояние системы описывается некоторым вектором в гильбертовом
пространстве ${\cal H}$, а измерению координаты или импульса
соответствует действие операторами $\hat q_i, \hat p_i$. Эти операторы
не коммутируют $[\hat q, \hat p]=i \hbar$, поэтому собственное
состояние оператора координаты не может быть собственным состоянием
оператора импульса.

Подробнее мы обсуждали квантовую механику на учебном семинаре в
прошлом году, сейчас нам важно, что у нас появилось гильбертово
пространство состояний ${\cal H}$ и пространство операторов на нем
${\cal O}({\cal H})$.

Как совместить эту картину с теорией поля?

Естественно, заменить поля на операторнозначные распределения
$\varphi:S(\mathbb{C}^n)\to {\cal O}({\cal H})$. При этом нам нужно
потребовать выполнения следующих условий. В гильбертовом пространстве
состояний ${\cal H}$ должно быть плотное множество $D\subset {\cal
  H}$, такое что
\begin{itemize}
\item $\forall f\in S(\mathbb{C}^n), D\subset D_{\varphi(f)}$, где
  $D_{\varphi(f)}$ -- область определения $\varphi(f)$.
\item $f\to \varphi(f)|_D$ -- линейное отображение из
  $S(\mathbb{C}^n)$ в $\mathrm{End}(D)$
\item $\forall \nu\in D, \omega\in {\cal H}$ отображение $f\to
  \left<\omega, \varphi(f)(\nu)\right>$ -- непрерывное распределение
\end{itemize}
Кроме того, мы потребуем в ${\cal H}$ наличия выделенного состояния
$\Omega\in {\cal H}$ -- вакуума.

Путь $B_0$ -- счетное множество индексов, которые будут нумеровать
поля в теории. Мы будем пользоваться мультииндексами
$i=(i_1,\dots,i_n)\in B_0^n$, и множество мультииндексов обозначим
через $\{i\}=B$.

Мы хотим определить наблюдаемые -- корреляционные функции
$G_{i_1,\dots, i_n}(z_1,\dots,z_n)$, так что $$G_{i_1,\dots,
  i_n}(z_1,\dots,z_n)=\left<\Omega,\varphi_{i_1}(z_1)\dots
  \varphi_{i_n}(z_n)\Omega\right>.$$

Они будут жить на $M_n=\{(z_1,\dots,z_n): z_i\neq z_j\}$, еще мы будем
использовать $M_n^+: \mathrm{Re}z_i>0$. Введем последовательность
пространств тест-функций с ограниченным носителем $\{S_n^+: S_0^+=\mathbb{C}, S_n^+=\{f\in
  S(\mathbb{C}^n: \mathrm{supp}(f)\subset M_n^+\}$.

Теперь мы можем сформулировать нашу теорию в виде системы аксиом на
непрерывные полиномиально ограниченные функции $G_{i_1,\dots,
  i_n}:M_n\to \mathbb{C}$, $G_{\emptyset}=1$.
\begin{axiom}
  Локальность:   для всех $(i_{1},\dots,i_{n})\in B_{0}^{n}$,
  $(z_{1},\dots, z_{n})\in M_{n}$ и $\pi\in S_{n}$ --- перестановок
  множества из $n$ элементов верно равенство 
  $G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n})=G_{i_{\pi(1)},\dots i_{\pi(n)}}(z_{\pi(1)},\dots, z_{\pi(n)})$
\end{axiom}
\begin{axiom}
  Преобразования при движениях комплексной плоскости: 
рассмотрим группу движений двумерного пространства $E_{2}$,
генераторами которой являются повороты
$r_{\alpha}:\mathbb{C}\to\mathbb{C}, \; z\to e^{i\alpha}z,\; \alpha\in
\mathbb{R}$ и трансляции $t_{a}:\mathbb{C}\to\mathbb{C},\; z\to z+a,\;
a\in\mathbb{C}$, 
Тогда для любого индекса $i\in B_{0}$  существуют независимые конформные веса $h_{i},\bar h_{i}\in \mathbb{R}$, такие, что для всех преобразований $w\in E_{2}$
  $G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n},\bar z_{1},\dots, \bar z_{n})=
\prod_{j=1}^{n}\left(\frac{dw(z_{j})}{dz}\right)^{h_{i_{j}}}\left(\overline{\frac{dw(z_{j})}{dz}}\right)^{\bar{h}_{i_{j}}}
G_{i_1,\dots i_n}(w_{1},\dots, w_{n},\bar w_{1},\dots,\bar w_{n})$,
где $w_{i}=w(z_{i})$, а $s_{i}=h_{i}-\bar h_{i}, d_{i}=h_{i}+\bar
h_{i}$  -- конформный спин и скейлинговая размерность. 
\end{axiom}
\begin{axiom}
  Положительность по отношению к отражениям:
  Обозначим через $\Theta:\mathbb{C}\to\mathbb{C}$  отображение $z=t+i y\to \Theta(z)= -t+i y$. Тогда аксиома утверждает, что существует инволюция $\star:B_{0}\to B_{0}$, $\star^{2}=\mathrm{id}_{B_{0}}$, которая продолжается на $B$ ($\star:i\to i^{*}$), и выполняются свойства
  \begin{enumerate}
  \item Верно равенство $G_{i}(z)=G_{i^{*}}(\Theta(z))=G_{i^{*}}(-z^{*})$
  \item Обозначим через $\underline{S}^{+}$ пространство
    последовательностей тест-функций $\underline{f}=(f_{i})_{i\in B},
    f_{i}\in S^{+}_{n}$. Тогда неравенство
    $$\left<\underline{f},\underline{f}\right>=
      \sum_{i,j\in B}\sum_{n,m}\int_{M_{n+m}}G_{i^{*} j}(\Theta(z_{1}),\dots ,\Theta(z_{n}),w_{1},\dots,w_{m}) f_{i}(z)^{*}f_{j}(w) d^{n}z d^{m}w \geq 0,$$
      верно  $\forall \underline{f}\in \underline{S}^{+}$. 
  \end{enumerate}
\end{axiom}

Если эти аксиомы выполнены для системы функций $\{G_i\}$, то мы можем
восстановить гильбертово пространство ${\cal H}$. У нас есть
положительная полуопределенная форма на $\underline{S}^+$, тогда
${\cal H}$ -- это пополнение $\underline{S}^+$, факторизованное по
ядру этой формы.

Можно построить и поля $\varphi_j$ для всех $j\in B_0$. Для $f\in S^+,
\underline g\in \underline S^+, [\underline{g}]\in {\cal H}$ определим
$\varphi_j(f)([\underline{g}])=\left((\underline{g}\times
  f)_{i_1,\dots,i_{n+1}}\right)_{i\in B}$, где $(\underline{g}\times
f)_{i_1,\dots,i_{n+1}}(z_1,\dots, z_{n+1})=g_{i_1,\dots, i_m}
(z_1,\dots, z_n) f(z_{n+1}) \delta_{j,i_{n+1}}$.

Еще у нас есть вакуум $\Omega=[f]: f_{\emptyset}=1, f_i=0\; \forall
i\neq \emptyset$. Кроме того, на ${\cal H}$ у нас действует унитарное
представление $E_2$, а инвариантное относительно него подпространство
$D$ плотно.

Теорема определяет структуру двумерной евклидовой теории поля:
\begin{theorem}
  \begin{enumerate}
  \item 
    Для всех $j\in B_{0}$ отображения $\varphi_{j}:S^{+}\to
    \mathrm{End}(D)$ линейны, $\varphi_{j}$ -- полевые операторы,
    $\varphi_{j}(D)\subset D, \Omega\in D$ и вакуум $\Omega$
    инвариантен относительно унитарных представлений $U$ группы
    $E_{2}$. 
  \item Поля $\varphi_{j}$ преобразуются ковариантно по отношению к представлению $U$, для $w\in E_{2}$:
    $$U(w)\varphi_{j}(z)U(w)^{*}=\left(\frac{\partial w}{\partial z}\right)^{h_{j}}\varphi_{j}(w(z))$$
  \item Матричные коэффициенты $\left<\Omega|\varphi_{i_{1}}(z_{1})\dots \varphi_{i_{n}}(z_{n})|\Omega\right>$ представляются аналитическими функциями, которые при $\mathrm{Re}z_{n}>\dots>\mathrm{Re}z_{1}>0$ совпадают с корреляционными функциями
    $$\left<\Omega|\varphi_{i_{1}}(z_{1})\dots \varphi_{i_{n}}(z_{n})|\Omega\right>=G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n})$$
  \end{enumerate}
\end{theorem}
Кроме того, если рассмотреть корреляционные функции, зависящие от
двойного набора переменных $G_{i_1,\dots,i_n}(z_1,\dots, z_n,\bar
z_1,\dots,\bar z_n)$, они оказываются голоморфными на $M_n^>\times
M_n^>$, где $M_n^>=\{z\in M_n^+:\mathrm{Re}
z_n>\dots>\mathrm{Re}z_1>0\}$.

Чтобы получилась конформная теория поля нам осталось добавить
требование масштабной инвариантности. 
\begin{axiom}
  Корреляционная функция $G_{i}, i\in B$ преобразуется ковариантно при масштабных преобразованиях $w(z)=e^{\tau}z$, то есть
    $$G_{i_{1},\dots,i_{n}}(z_{1},\dots,z_{n})=\left(e^{\tau}\right)^{h_{1}+\dots+h_{n}+\bar{h}_{1}+\dots+\bar{h}_{n}} G_{i_{1},\dots,i_{n}}(e^{\tau} z_{1},\dots,e^{\tau} z_{n}),$$
  где $(z_{1},\dots,z_{n})\in M_{n},\quad h_{j}=h_{i_{j}}$
\end{axiom}

Заметим, что двух- и трех-точечные функции теперь полностью
определены:
$G_{ij}(z_1,z_2,\bar z_1, \bar z_2)=C_{ij} (z_1-z_2)^{-(h_i+h_j)}(\bar
z_1-\bar z_2)^{-(\bar h_i+\bar h_j)}$ и
$G_{ijk}=C_{ijk}z_{12}^{-h_1-h_2+h_3}
z_{23}^{-h_2-h_3+h_1}z_{13}^{-h_1-h_3+h_2} 
\bar z_{12}^{-\bar h_1-\bar h_2+\bar h_3} \bar z_{23}^{-\bar h_2-\bar
  h_3+\bar h_1}\bar z_{13}^{-\bar h_1-\bar h_3+\bar h_2}$, где
$C_{ij}, C_{ijk}\in \mathbb{C}$.

При таких предположениях теория не очень практичная -- мы ничего не
знаем про структуру гильбертова пространства ${\cal H}$ и поля
$\varphi_j$. Поэтому из физических предположений мы предполагаем
также, что среди полей есть четыре особенных поля -- компоненты
тензора энергии-импульса.

\begin{axiom}
  (Существование тензора энергии-импульса)
  Среди полей $\varphi_{i},\; i\in B_{0}$ есть четыре поля
  $T_{\mu\nu},\; \mu,\nu=0,1$, такие, что $T_{\mu\nu}=T_{\nu\mu},\quad
  T_{\mu\nu}^{*}=T_{\nu\mu}(\Theta(z)),\quad \partial_{0} T_{\mu
    0}+\partial_{1}T_{\mu 1}=0$, скейлинговая размерность поля
  $d(T_{\mu\nu})=h_{\mu\nu}+\bar{h}_{\mu\nu}=2$,  конформный спин $s(T_{00}-T_{11}\pm 2i T_{01})=\pm 2$. 
\end{axiom}
Можно показать, что $\mathrm{tr} T_{\mu\nu}=0$ и $T=T_{00}-i T_{01}$ не зависит от $\bar z$, то есть $\bar \partial T=0$. Операторы $L_{n}=\oint \frac{dz}{2\pi i} z^{n+1} T(z)$
удовлетворяют коммутационным соотношениям алгебры Вирасоро 
$$ [L_m,L_n]=(m-n)L_{m+n}+\frac{c}{12}(m^3-m)\delta_{m+n,0}.$$

Примарными будем называть поля $\varphi_{i}, i\in B_{0}$, такие, что
$[L_{n}, \varphi_{i}(z)]=z^{n+1}\partial
\varphi_{i}(z)+h_{i}(n+1)z^{n}\varphi_{i}(z)$,  $\forall n\in\mathbb{Z}$.

Для каждого примарного поля $\varphi_{i}$ можно определить конформное
семейство $[\varphi_{i}]$, состоящее из вторичных полей
$\varphi_{i}^{\alpha}(z)=L_{-\alpha_{1}}(z)\dots
L_{-\alpha_{n}}(z)\varphi_{i}(z)$, где $L_{-n}(z)=\frac{1}{2\pi
  i}\oint\frac{T(\xi)}{(\xi-z)^{n+1}} d\xi$. Заметим, что
$L_{n}(0)=L_{n}$ и корреляционные функции вторичных полей могут быть
выражены через корреляционные функции примарных.  Последняя аксиома
определяет операторное разложение:
\begin{axiom}
Корреляционные функции примарных полей  при $z_{i}\to z_{j}$ удовлетворяют уравнению:
$$\left<\Omega|\varphi_{i_{1}}(z_{1})\dots\varphi_{i}(z_{i})\dots \varphi_{j}(z_{j})\dots \varphi_{i_{n}}(z_{n})|\Omega\right>=$$
$$  \sum_{k\in B_{0}}C_{ijk} (z_{i}-z_{j})^{h_{k}-h_{i}-h_{j}} \left<\Omega|\varphi_{i_{1}}(z_{1})\dots\varphi_{k}(z_{k})\dots \varphi_{i_{n}}(z_{n})|\Omega\right>$$
$$  +\mbox{регулярные члены}$$
\end{axiom}

Если дополнительно предположить, что операторное разложение
ассоциативно (так называемый ``конформный бутстрап''),  то вся теория
определяется набором примарных полей $\varphi_{j}, j\in B_{0}$,  их
размерностями и коэффициентами операторного разложения $C_{ijk}$.

Поля разделились на модули алгебры Вирасоро. Каждому полю $\varphi_i$
соответствует состояние $\lim_{z\to 0}\varphi_i(z)\Omega$. Можно
считать, что гильбертово пространство состояний тоже раскладывается на
модули алгебры Вирасоро.

В модуле Верма может оказаться такое состояние $\left|\omega\right>$,
что $L_{n}\left|\omega\right>=0, \quad \forall  n>0$. Действие
понижающих операторов на такие состояния порождает  инвариантное
подпространство, то есть модуль Верма оказывается  приводимым. Такие
состояния обладают нулевой нормой и  исключаются. Их иногда называют
нулевыми состояниями (null-state).  Как искать  такие состояния?

На уровне один
$L_{1}\left(L_{-1}\left|h\right>\right)=0\Longrightarrow h=0$, то есть
все состояния, полученные из  вакуума понижающим оператором являются
нефизическими состояниями с нулевой нормой, как и должно быть.

На уровне два будем искать нулевое состояние в виде
$\left|\omega\right>=(L_{-2}+a L_{-1}^{2})\left| h \right> $. Из
$L_{1}\left|\omega\right>=0$ получаем
$$ 0=([L_{1},L_{-2}] +a [L_{1},L_{-1}^{2}])\left|h\right> = (3+2a(2h+1))L_{-1}\left|h\right>$$
То есть  $ a=-\frac{3}{2(2h+1)}$
Аналогично, действуя $L_{2}$ получаем условие $ c=2h\frac{5-8h}{2h+1}$

Так как состояние $(L_{-2}-\frac{3}{2(2h+1)}
L_{-1}^{2})\left|h\right>$ имеет нулевую норму, для корреляторов
получаем
 $$\left<(L_{-2}+aL_{1}^{2})\phi_{1}(w_{1}) \dots \phi_{n}(w_{n}) \right>=0.$$ 
Из определения $L_{n}$ можно переписать это условие в виде дифференциального уравнения:
$$\left[  a \frac{\partial^{2}}{\partial w_{1}^{2}} +\sum_{j\neq 1} \left(\frac{h_{j}}{(w_{1}-w_{j})^{2}}+\frac{1}{w_{1}-w_{j}} \frac{\partial}{\partial w_{j}}\right)\right] \left< \phi_{1}(w_{1}) \dots \phi_{n}(w_{n}) \right> =0$$

То есть мы получили дифференциальные уравнения на корреляционные функции.

Рассмотрим в качестве примера модель Изинга. Ей соответствует
конформная теория поля с тремя примарными полями
$\varphi_{1}: (0,0),\quad \varphi_{2}:
\left(\frac{1}{2},\frac{1}{2}\right),\quad
\varphi_{3}:\left(\frac{1}{16},\frac{1}{16}\right)$ и центральным
зарядом $1/2$. Заметим, что для поля спина $\sigma=\varphi_{3}$ с конформной
размерностью $h=1/16$ выполнено условие $  c=2h\frac{5-8h}{2h+1}$. То есть мы можем записать уравнение для корреляционных функций спинов. Рассмотрим четырехточечную функцию
   $$G^{(4)} =\langle \sigma(z_1,\bar z_1)\dots \sigma(z_4,\bar z_4)\rangle$$

Из требования конформной ковариантности для корреляционных функций можно переписать $G^{(4)}$ в виде
  $$G^{(4)} = \mathrm{const}\cdot \left(\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right)^{\frac{1}{8}} \overline{ \left(\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right)}^{\frac{1}{8}}F(x,\bar x),$$
где $x=\frac{z_{12}z_{34}}{z_{13}z_{24}}, z_{ij}=\left| z_{i}-z_{j}\right|$. Тогда дифференциальное уравнение на $F$ примет вид
 $$ \left( x(1-x) \frac{\partial^{2}}{\partial x^{2}} +(\frac{1}{2}-x)\frac{\partial}{\partial x}+\frac{1}{16}\right) F(x,\bar x)=0$$
и аналогично для $\bar x$.
Решение этого уравнения дается гипергеометрической функцией. В данном случае она упрощается до $f_{1,2}(x)=(1\pm \sqrt{1-x})^{\frac{1}{2}}$. Тогда  четырехточечную функцию можно записать в виде комбинации решений
$$  G^{(4)} =  \left|\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right|^{\frac{1}{4}}\sum_{i,j=1}^{2}a_{ij}f_{i}(x)f_{j}(\bar x)$$

Возвращаясь к физической системе мы должны положить $\bar x= x^{*}$, тогда из однозначности четырехточечной функции комбинация может быть только $a(|f_{1}(x)|^{2}+|f_{2}(x)|^{2})$. Из сравнения с операторным разложением для $\sigma(z)\sigma(w)$ нетрудно получить, что $a=1/2$.

В итоге для четырехточечной функции получается следующее выражение:
  $$G^{(4)} =\langle \sigma(z_1,\bar z_1)\dots \sigma(z_4,\bar z_4)\rangle = \frac{1}{2} \left|\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right|^{\frac{1}{4}}\left(\left|1+\sqrt{1-x}\right| + \left|1-\sqrt{1-x}\right|\right)$$

Таким образом конформная теория поля позволяет не только находить
критические индексы, но и получать явные выражения  для корреляционных
функций статистических моделей в критической  точке.

\end{document}

### 2012-09-19 AffineLieAlgebras/Thesis/autoref.tex
Some work on autoref

@@
 
-Мы обобщаем анализ соответствия между эволюцией Шрамма-Левнера и конформной теорией поля на случай coset-моделей \cite{Goddard198588}. Такие модели задаются алгеброй Ли $\gf$ и ее подалгеброй $\af$. 
-$G/A$-coset модель конформной теории поля может быть реализована как ВЗНВ-модель (с калибровочной группой $G$), взаимодействующая с чисто калибровочными полями, с калибровочной группой $A\subset G$ \cite{gawdzki1988g,figueroa89equivalence}.
+Мы обобщаем анализ соответствия между эволюцией Шрамма-Левнера и конформной теорией поля на случай coset-моделей. Такие модели задаются алгеброй Ли $\gf$ и ее подалгеброй $\af$. 
+$G/A$-coset модель конформной теории поля может быть реализована как ВЗНВ-модель (с калибровочной группой $G$), взаимодействующая с чисто калибровочными полями, с калибровочной группой $A\subset G$.
 Действие записывается через поля $\gamma:\mathbb{C}\to G$ и $\alpha,\bar\alpha:\mathbb{C}\to A$:

### 2012-09-20 AffineLieAlgebras/Thesis/autoref.tex
Autoref shortened

@@
 % Актуальность работы
-\actualitysection
-\actualitytext
+%\actualitysection
+%\actualitytext
+
+\textbf{Актуальность работы}
+
+  Последние тридцать лет конформная теория поля в двух измерениях привлекает большое внимание исследователей.
+Эта теория используется для описания критического поведения в двумерных статистических системах.
+Благодаря наличию бесконечномерной алгебры симметрии двумерная конформная теория поля может быть сформулирована аксиоматически.
+Помимо математической красоты теория обладает огромной практической ценностью -- с ее использованием было получено большое количество результатов и численных предсказаний в изучении критического поведения в двумерных системах.
+Методы двумерной конформной теории поля с успехом применяются также при изучении эффекта Кондо и дробного квантового эффекта Холла.
+
+Поиски строгого математического доказательства для предсказаний двумерной конформной теории поля в последние годы привели к большому количеству новых идей и результатов в дискретном комплексном анализе \cite{smirnov2001critical}.
+
+Теория представлений бесконечномерных алгебр Ли является важным инструментом изучения моделей конформной теории поля.
+Помимо алгебры Вирасоро, наличие которой обязательно в двумерной конформной теории поля, большую роль играют аффинные алгебры Ли.
+Изучение аффинных алгебр Ли было начато Виктором Кацем и Робертом Муди в 1960-х годах с попытки обобщения классификации простых конечномерных алгебр Ли на бесконечномерный случай \cite{kac1968simple,moody1968new}.
+Первоначально интерес к этим алгебрам был связан с модулярными свойствами характеров их модулей.
+После возникновения двумерной конформной теории поля были предложены модели Весса-Зумино-Новикова-Виттена, а затем и coset-модели, в которых теория представлений аффинных алгебр Ли играет определяющую роль.
+
+Моделям Весса-Зумино-Новикова-Виттена, coset-моделям и теории представлений аффинных алгебр Ли  посвящены тысячи работ.
+Однако многие проблемы по-прежнему не имеют простых решений.
+Например, задача вычисления коэффициентов ветвления для представлений алгебр Ли стоит уже многие десятилетия.
+Она актуальна для различных физических приложений в coset-моделях конформной теории поля.
+При этом, в отличие от проблемы вычисления кратностей весов, для вычисления коэффициентов ветвления не существовало особенно эффективных алгоритмов.
 
@@
 Мы указываем на то, что основные свойства интегрируемых модулей старшего веса определяются структурой сингулярного элемента, что выражается в формуле Вейля-Каца для формальных характеров.
-Кроме того, мы обсуждаем конформную теорию поля на области с границей, так как она оказывается связана со стохастическим описанием решеточных моделей.
+Мы обсуждаем конформную теорию поля на области с границей, так как она оказывается связана со стохастическим описанием решеточных моделей.
 
 \textbf{В главе 2} мы выводим основное рекуррунтное соотношение на коэффициенты ветвления.
-Пользуясь тем, что структура сингулярного элемента определяет свойства модуля алгебры Ли, мы формулируем и доказываем лемму о разложении сингулярного элемента.
-Такое разложение определяет правила ветвления и позволяет сформулировать рекуррентную процедуру редукции.
+Пользуясь тем, что структура сингулярного элемента определяет свойства модуля алгебры Ли, мы доказываем лемму о разложении сингулярного элемента.
+Это разложение определяет правила ветвления и позволяет сформулировать рекуррентную процедуру редукции.
 Основные результаты данной главы опубликованы в работе \citemy{2010arXiv1007.0318L}.
 
-Формула Вейля-Каца для формальных характеров интегрируемых модулей старшего веса конечномерных и аффинных алгебр Ли имеет вид
-\begin{equation}
-  \label{eq:1}
-  \mathrm{ch} V^{(\mu)} = \frac{\Psi^{(\mu)}}{R},
-\end{equation}
+Формула Вейля-Каца для формальных характеров интегрируемых модулей старшего веса конечномерных и аффинных алгебр Ли имеет вид $\mathrm{ch} V^{(\mu)} = \frac{\Psi^{(\mu)}}{R}$,
 где $\Psi^{(\mu)}$ -- сингулярный элемент модуля, а $R=\prod_{\alpha\in \Delta^+}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}$ -- знаменатель Вейля.
@@
 Например, $\Psi^{(\mu)}=\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}$ для неприводимых модулей.
-Про этом знаменатель Вейля является универсальным объектом, характеризующим корневую систему алгебры Ли, а свойства модуля определяются сингулярным элементом.
+Знаменатель  Вейля $R$ является универсальным объектом, характеризующим корневую систему алгебры Ли, а свойства модуля определяются сингулярным элементом.
 
-Процедура редукции состоит в разложении модуля алгебры Ли $\gf$ в сумму модулей некоторой подалгебры $\af$
-\begin{equation}
-  \label{eq:2}
-  L_{\gf\downarrow \af}^{\mu }=\bigoplus
-\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
-\end{equation}
+Процедура редукции состоит в разложении модуля алгебры Ли $\gf$ в сумму модулей некоторой подалгебры $\af$:
+$ L_{\gf\downarrow \af}^{\mu }=\bigoplus
+\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.$
+
 Используя оператор проекции  $\pi_{\af}$ (на весовое пространство $\hf_{\af}^*$), перепишем это разложение для формальных характеров: 
@@
 
-Для подалгебр из ортогональной пары  $\left( \af,\afb\right) $ рассмотрим соответствующие векторы Вейля $\rho _{\af}$ и $\rho _{\af_{\perp }}$, и образуем так называемые  ''дефекты'' вложения $\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho$, $\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi_{\afb}\rho$.
+Для подалгебр из ортогональной пары  $\left( \af,\afb\right) $ рассмотрим соответствующие векторы Вейля $\rho _{\af}$ и $\rho _{\af_{\perp }}$, и образуем так называемые  ``дефекты'' вложения $\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho$, $\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi_{\afb}\rho$.
 
@@
 Каждому элементу  $U$ поставим в соответствие вес $\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}$.
-Аналогичным образом определим $\mu _{\tilde \af}\left( u\right) :=\pi _{\tilde \af}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}$ и $\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}$
-
+Аналогичным образом определим $\mu _{\tilde \af}\left( u\right) :=\pi _{\tilde \af}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}$ и $\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\afb}$.
 Мы доказываем следующую лемму о разложении сингулярного элемента:
@@
 
-Теперь мы можем ввести ``веер вложения'', который необходим для формулировки рекуррентных соотношений:
+Введем ``веер вложения'', который необходим для формулировки рекуррентных соотношений:
 \begin{definition}
@@
 \end{equation}
-и носитель $\Phi _{\af\subset \gf}\subset P_{\af}$ функции $s(\gamma )=\det \left( \gamma \right) $ :
-\begin{equation}
+и носитель $\Phi _{\af\subset \gf}\subset P_{\af}$ функции $s(\gamma )=\det \left( \gamma \right) $ : \quad
+$
 \Phi _{\af\subset \gf}=\left\{ \gamma \in P_{\af}|s(\gamma
 )\neq 0\right\}   \label{eq:37}
-\end{equation}
+$
 Упорядочение корней в  $\co{\Delta _{\af}}$ индуцирует естественное упорядочение весов в $P_{\af}$. Обозначим через $\gamma_{0}$ наименьший вектор $\Phi _{\af\subset \gf}$. Множество
@@
 Введем сингулярные коэффициенты ветвления следующим образом:
-\begin{equation}
+\begin{equation*}
   \label{eq:3}
@@
 
-Оказывается, что для полупростой конечномерной алгебры $\gf$  и полупростой конечномерной подалгебры $\af$ алгебра $\afb$, определенная в формуле (\ref{branching1}), является регулярной.
+Для полупростой конечномерной алгебры $\gf$  и полупростой конечномерной подалгебры $\af$ алгебра $\afb$ является регулярной.
 Отношение знаменателей Вейля порождает параболические модули Верма.
@@
 \begin{definition}
-Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$. Рассмотрим отображение
-\begin{equation}
-\phi :\left\{
-\begin{array}{l}
-\Delta _{0}\hookrightarrow \Delta , \\
-P_{0}\hookrightarrow P.
-\end{array}
-\right.
-\end{equation}
+Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$. Рассмотрим отображение $\phi :\left\{
+\Delta _{0}\hookrightarrow \Delta , 
+P_{0}\hookrightarrow P
+\right\}.
+$
 Оно называется ``вложением'', если \newline
@@
 \noindent (b) $\phi$ действует гомоморфно по отношению к группам сложения векторов в $P_{0}$ и $P$:
-\[
+$
 \phi (\gamma )=\phi (\alpha )+\phi (\beta )
-\]
+$
 для любой тройки $\alpha ,\beta ,\gamma \in P_{0}$, такой, что $\gamma =\alpha+\beta $.
@@
 
-Эквивалентно, можно сказать, что  $(\Delta_1,\Delta_2)$  -- ``сплинт'' (расщепление)  $\Delta$ и мы можем обозначить его через $\Delta \approx (\Delta_1,\Delta_2)$.
+Можно сказать, что  $(\Delta_1,\Delta_2)$  -- ``сплинт'' (расщепление)  $\Delta$ и мы можем обозначить его через $\Delta \approx (\Delta_1,\Delta_2)$.
 Каждая из компонент  $\Delta_1$ и $\Delta_2$ называется ``стеблем'' сплинта $(\Delta_1,\Delta_2)$.
 
-Чтобы показать связь веера вложения со сплинтом рассмотрим случай, когда один из стеблей $\Delta _{1}=\Delta _{\af}$  является подсистемой корневой системы.
-
-Сплинт $\Delta \approx (\Delta _{1},\Delta _{2})$ называется ``инъективным'', если $\Delta _{1}=\Delta _{\af}$, -- подсистема корневой системы $\Delta $, соответствующая регулярной редуктивной подалгебре $\af\hookrightarrow \gf$.
-
+Чтобы показать связь веера вложения со сплинтом рассмотрим случай ``инъективного'' сплинта, когда один из стеблей $\Delta _{1}=\Delta _{\af}$  является подсистемой корневой системы, соответствующей регулярной редуктивной подалгебре $\af\hookrightarrow \gf$.
 В случае инъективного сплинта второй стебель $\Delta _{\sfr}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (аналогично формуле (\ref{eq:142})) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$.
@@
 \begin{statement}
-Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением
-\begin{equation}
+Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением\\
+$
 \prod_{\beta \in \Delta _{\sfr}^{+}}\left( 1-e^{-\beta }\right)
-=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
-\end{equation}
+=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }$
 \end{statement}
@@
 \begin{Prop}
-\begin{equation}
+Любой вес с ненулевой кратностью, входящий в правую часть равенства:
+\[
 \frac{e^{\rho _{\gf}}}{\prod_{\beta \in \Delta _{\sfr%
@@
 \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
-}=\sum_{\nu \in P_{\af}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
-\label{singular main-4}
-\end{equation}
-Любой вес с ненулевой кратностью, входящий в правую часть равенства, равен одному из старших весов в разложении. Кратность $M_{\left( \sfr
+}=\sum_{\nu \in P_{\af}^{++}}b_{\nu }^{(\mu )}e^{\nu },
+\]
+равен одному из старших весов в разложении. Кратность $M_{\left( \sfr
 \right) \widetilde{\nu }}^{\widetilde{\mu }}$ веса  $\widetilde{\nu}\in \mathcal{N}_{\sfr}^{\widetilde{\mu }}$ определяет коэффициент ветвления  $b_{\nu }^{(\mu )}$ для старшего веса $\nu =\left( \mu-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
@@
 Заключительная \textbf{глава 5} посвящена практическим приложениям результатов диссертации.
-
  В разделе 5.1 мы  описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
@@
 Стохастический процесс, который удовлетворяет уравнению 
-\begin{equation}
-\label{eq:166}
+$
   \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
-\end{equation}
+$
 называется {\it эволюцией Шрамма-Левнера} на верхней полуплоскости $\mathbb{H}$.
@@
 Если мы фиксируем  $A$-калибровку, у нас останется  $G/A$ калибровочная инвариантность.
-Значит мы должны добавить случайные калибровочные преобразования к эволюции Шрамма-Левнера, аналогично случаю ВЗНВ-моделей  (См.
-\cite{bettelheim2005stochastic}).
+Значит мы должны добавить случайные калибровочные преобразования к эволюции Шрамма-Левнера, аналогично случаю ВЗНВ-моделей.
 Обозначим через $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) генераторы представления алгебры $\gf$ (соответственно, представления $\af$), соответствующего примарному полю $\varphi_{i}$.
 
-Теперь рассмотрим наблюдаемые в присутствии следа эволюции Шрамма-Левнера.
+Рассмотрим наблюдаемые в присутствии следа эволюции Шрамма-Левнера.
 Математическое ожидание решеточной наблюдаемой $\mathcal{O}$ на верхней полуплоскости можно вычислить как сумму ожиданий этой наблюдаемой в присутствии (конечной части) траектории эволюции Шрамма-Левнера  $\gamma_{t}$ вплоть до некоторого времени $t$, умноженных на вероятность этой траектории:
@@
 Решеточная наблюдаемая  $\prec \mathcal{O} \succ_{\mathbb{H}}$ не зависит от  $t$, следовательно $\prec\mathcal{O}\succ_{\gamma_{t}}$ -- мартингал.
-Это должно выполняться и для ее непрерывного предела, дающегося комбинацией корреляционных функций в конформной теории поля \cite{bauer2003sle}:
+Это должно выполняться и для ее непрерывного предела, дающегося комбинацией корреляционных функций в конформной теории поля:
 \begin{equation}
@@
 Рассмотрим, что происходит с наблюдаемыми при эволюции следа SLE $\gamma_{t}$ с момента   $t$ до $t+ dt$. 
-
-Через  $\mathcal{G}_{i}$ мы обозначили  генераторы инфинитезимальных преобразований примарных $\varphi_{i}$:$d\varphi_{i}(w_{i}) = \mathcal{G}_{i}\varphi_{i}(w_{i})$.
+Через  $\mathcal{G}_{i}$ мы обозначили  генераторы инфинитезимальных преобразований примарных полей $\varphi_{i}$:$d\varphi_{i}(w_{i}) = \mathcal{G}_{i}\varphi_{i}(w_{i})$.
 Нормируем дополнительное $\left(\dim\gf\right)$-мерное Броуновское движение следующим образом: $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
@@
 
-Формула Ито, дает выражение для дифференциала $\mathcal{F}$, который равняется нулю в силу условия мартингала.
-Это равенство можно переписать в виде следующего алгебраического условия на граничное состояние $\phi(0)\left|0\right>$:
-\begin{multline}
-\label{eq:182}
-  \left<0\left|\phi(\infty)\varphi_{1}(w_{1})\dots\varphi_{2N}(w_{2N})\right.\right.\\
-  \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
-\left.\phi(0)|0\right>=0.
-\end{multline}
-Так как набор  $\{\phi_{i}\}$ состоит из произвольных примарных полей, мы заключаем, что 
+Формула Ито дает выражение для дифференциала $d\mathcal{F}$, который равняется нулю в силу условия мартингала.
+Это равенство можно переписать в виде дифференциального уравнения на корреляционные функции, которое эквивалентно   алгебраическому условия на граничное состояние $\phi(0)\left|0\right>$.
 \begin{multline}

### 2012-09-20 AffineLieAlgebras/Thesis/common.tex
Autoref shortened

@@
 
-  Последние тридцать лет конформная теория поля в двух измерениях привлекает большое внимание исследователей \cite{belavin1984ics}.
+  Последние тридцать лет конформная теория поля в двух измерениях привлекает большое внимание исследователей.
 Эта теория используется для описания критического поведения в двумерных статистических системах.
@@
 
-\mkcommonsect{novelty}{Научная новизна и практическая значимость}{%
-
+\mkcommonsect{novelty}{Научная новизна и практическая значимость.}{%
   В диссертации впервые решены следующие задачи:
@@
 
-\mkcommonsect{value}{Практическая значимость}{%
-}
+%\mkcommonsect{value}{Практическая значимость}{%
+%}
 
-\mkcommonsect{results}{%
-
-На защиту выносятся следующие основные результаты и положения:}{%
+\mkcommonsect{results}{На защиту выносятся следующие основные результаты и положения:}{%
 \begin{itemize}

### 2012-10-04 AffineLieAlgebras/Thesis/autoref.tex
Some changes

@@
 \input{macro}
+%\renewcommand{\thestatement}{}
 
@@
 \begin{center}
-Работа выполнена на кафедре физики высоких энергий и элементарных частиц физического факультета Санкт-Петербургского государственного университета.
+Работа выполнена в Санкт-Петербургском государственном университете.
 % \emph{название организации}.
@@
                        & & \emph{профессор}, \\
-                       & & \emph{Ляховский Владимир Дмитриевич}
-\\
-Официальные оппоненты: & & \emph{доктор физико-математических наук}, \\
-                       & & \emph{профессор}, \\
-                       & & \emph{Кулиш Петр Петрович}\\
-                       & & \emph{кандидат физико-математических наук}, \\
-                       & & \emph{ученое звание}, \\
-                       & & \emph{Мудров Андрей Игоревич}
+                       & & \emph{Ляховский Владимир Дмитриевич} \\
+Официальные оппоненты: & & \emph{Кулиш Петр Петрович}\\
+                       & & \emph{доктор физико-математических наук}, \\
+                       & & \emph{профессор},\\
+                       & & \emph{Санкт-Петербургское   отделение
+Математического   института   им.  В.А. Стеклова   РАН, главный научный сотрудник, заведующий 
+лаборатории математических проблем физики}; \\
+                       & & \emph{Мудров Андрей Игоревич} \\
+                       & & \emph{кандидат физико-математических наук, Университет Лестера (Великобритания), преподаватель} 
 \\
@@
 Защита состоится \datefield{} в \rule[0pt]{1cm}{0.5pt}\, часов
-на заседании совета \emph{Д 212.232.24} по защите докторских и кандидатских диссертаций при \emph{Санкт-Петербургском государственном университете}, расположенном по адресу:
-\emph{Санкт-Петербург, Средний пр. В.О., д. 41/43, ауд. 305}
+на заседании диссертационного совета \emph{Д 212.232.24}  при \emph{Санкт-Петербургском государственном университете} по адресу:
+\emph{199004, Санкт-Петербург, Средний пр. В.О., д. 41/43, ауд. 304}
 
 \vskip1ex\noindent
-С диссертацией можно ознакомиться в научной библиотеке
+С диссертацией можно ознакомиться в библиотеке
 \emph{Санкт-Петербургского государственного университета}.
 
-\vskip1ex\noindent
+%\vskip1ex
+\noindent
 Автореферат разослан \datefield{}
 
-\vskip2ex\noindent
+%\vskip2ex\noindent
 %Отзывы и замечания по автореферату в двух экземплярах, заверенные
@@
 
-\vfill\noindent
+\vfill
+\noindent
+\begin{minipage}
 Ученый секретарь\\
-диссертационного совета,\\
-\emph{ученая степень}, \emph{ученое звание}%
+диссертационного совета,%\\
+\end{minipage}
+%\emph{д.ф.-м.н.}%, \emph{ученое звание}%
 \hfill
@@
 \ifDis@facsimile
-  \raisebox{-4pt}{\includegraphics[width=3cm]{sec-facsimile}}\hfill
+  \raisebox{-4pt}{\includegraphics[width=3cm,height=1cm]{aksenova}}\hfill
 \fi%
 \makeatother%
-\emph{фамилия и. о.}
+\emph{Аксенова Е.В.}
 
@@
 Последние тридцать лет конформная теория поля в двух измерениях привлекает большое внимание исследователей.
-Эта теория используется для описания критического поведения в двумерных статистических системах.
+Конформная теория поля используется для описания критического поведения в двумерных статистических системах и  обладает большой практической ценностью -- с ее использованием было получено значительное количество результатов и численных предсказаний.
+Методы двумерной конформной теории поля с успехом применяются также при изучении эффекта Кондо и дробного квантового эффекта Холла.
 Благодаря наличию бесконечномерной алгебры симметрии двумерная конформная теория поля может быть сформулирована аксиоматически.
-Помимо математической красоты теория обладает огромной практической ценностью -- с ее использованием было получено большое количество результатов и численных предсказаний в изучении критического поведения в двумерных системах.
-Методы двумерной конформной теории поля с успехом применяются также при изучении эффекта Кондо и дробного квантового эффекта Холла.
 
@@
 
-\textbf{В главе 2} мы выводим основное рекуррунтное соотношение на коэффициенты ветвления.
-Пользуясь тем, что структура сингулярного элемента определяет свойства модуля алгебры Ли, мы доказываем лемму о разложении сингулярного элемента.
-Это разложение определяет правила ветвления и позволяет сформулировать рекуррентную процедуру редукции.
+\textbf{В главе 2} мы выводим основное рекуррентное соотношение на коэффициенты ветвления.
+Сначала мы доказываем лемму о разложении сингулярного элемента.
+Структура сингулярного элемента определяет свойства модуля алгебры Ли, поэтому разложение определяет правила ветвления и позволяет сформулировать рекуррентную процедуру редукции.
 Основные результаты данной главы опубликованы в работе \citemy{2010arXiv1007.0318L}.
@@
 \textbf{В главе 3} мы используем  разложение сингулярного элемента, чтобы показать связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
-Результаты третьей главы опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}.
+Данные результаты опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}.
 
@@
 \begin{definition}
-Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$. Рассмотрим отображение $\phi :\left\{
+Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$.Отображение $\phi :\left\{
 \Delta _{0}\hookrightarrow \Delta , 
@@
 \right\}.
-$
-Оно называется ``вложением'', если \newline
-\noindent (a) оно вкладывает $\Delta _{0}$ в $\Delta $, и \newline
-\noindent (b) $\phi$ действует гомоморфно по отношению к группам сложения векторов в $P_{0}$ и $P$:
+$ называется ``вложением'', если  $\phi$ вкладывает $\Delta _{0}$ в $\Delta $ и действует гомоморфно по отношению к группам сложения векторов в $P_{0}$ и $P$:
 $
@@
 
-$\phi$ индуцирует вложение формальных алгебр: ${\mathcal{E}}_0\hookrightarrow \mathcal{E}$ и для образа ${\mathcal{E}}_i=\mathrm{Im}_{\phi}\left( {\mathcal{E}}_0\right)$ можно рассмотреть обратное отображение $\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+Вложение $\phi$ индуцирует вложение формальных алгебр: ${\mathcal{E}}_0\hookrightarrow \mathcal{E}$ и для образа ${\mathcal{E}}_i=\mathrm{Im}_{\phi}\left( {\mathcal{E}}_0\right)$ можно рассмотреть обратное отображение $\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+Нужно различать два класса вложений: ``метрические'', если скалярное произведение (заданное формой Киллинга) в корневом пространстве $P_0$ инвариантно по отношению к  $\phi$ и ``неметрические'', если оно не  $\phi$-инвариантно.
 
-Заметим, что нужно различать два класса вложений: когда скалярное произведение (заданное формой Киллинга) в корневом пространстве $P_0$ инвариантно по отношению к  $\phi$ и когда оно не  $\phi$-инвариантно.
-Вложения первого класса называются ``метрическими'', второго -- ``неметрическими''.
-
-\begin{definition}
-Корневая система $\Delta$ ``расщепляется'' на  $(\Delta _{1},\Delta _{2})$, если существует два вложения  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ и $\phi _{2}:\Delta _{2}\hookrightarrow \Delta $, где (a) $\Delta $ -- несвязное объединение образов $\phi _{1}$ и $\phi _{2}$, и (b) ни ранг  $\Delta _{1}$, ни ранг  $\Delta _{2}$ не превосходит ранга $\Delta $.
-\end{definition}
-
+Будем говорить, что корневая система $\Delta$ ``расщепляется'' на  $(\Delta _{1},\Delta _{2})$, если существует два вложения  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ и $\phi _{2}:\Delta _{2}\hookrightarrow \Delta $, где (a) $\Delta $ -- несвязное объединение образов $\phi _{1}$ и $\phi _{2}$, и (b) ни ранг  $\Delta _{1}$, ни ранг  $\Delta _{2}$ не превосходит ранга $\Delta $.
 Можно сказать, что  $(\Delta_1,\Delta_2)$  -- ``сплинт'' (расщепление)  $\Delta$ и мы можем обозначить его через $\Delta \approx (\Delta_1,\Delta_2)$.
@@
 
-Чтобы показать связь веера вложения со сплинтом рассмотрим случай ``инъективного'' сплинта, когда один из стеблей $\Delta _{1}=\Delta _{\af}$  является подсистемой корневой системы, соответствующей регулярной редуктивной подалгебре $\af\hookrightarrow \gf$.
-В случае инъективного сплинта второй стебель $\Delta _{\sfr}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (аналогично формуле (\ref{eq:142})) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$.
+Покажем связь веера вложения и ``инъективного'' сплинта, когда один из стеблей $\Delta _{1}=\Delta _{\af}$  является подсистемой корневой системы, соответствующей регулярной редуктивной подалгебре $\af\hookrightarrow \gf$.
+В этом случае знаменатель Вейля, соотвествующий второму стебелю $\Delta _{\sfr}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$, может быть переписан в виде произведения (аналогично формуле (\ref{eq:142})) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$.
 Обозначим через $\Delta_{\mathfrak{s}0}$ кообраз второго вложения $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$.
@@
 
-В случае инъективного сплинта мы можем сказать, что подалгебра $\af\hookrightarrow \gf$ расщепляется $\Delta$ (и назовем $\af$ ``расщепляющей подалгеброй'' алгебры $\gf$).
+В случае инъективного сплинта мы можем сказать, что подалгебра $\af\hookrightarrow \gf$ расщепляет $\Delta$.
 Сплинты были классифицированы в работе \cite{richter2008splints}  (см.
 Приложение в конце главы) и первые три класса сплинтов в этой классификации инъективны.
-
 Если выполнено техническое требование на структуру сингулярного элемента, то верно следующее свойство:
@@
 \label{eq:178}
-      S_{G/A}(\gamma, \alpha)=\\
--\frac{k}{8\pi}\int_{S^2} d^2x\; {\cal K} (\gamma^{-1}\partial^{\mu}\gamma,\gamma^{-1}\partial_{\mu}\gamma)-
- \frac{k }{24\pi} \int_{B}\epsilon_{ijk} {\cal K}\left(
+      S=
+-\frac{k}{4\pi}\left[ \frac{1}{2} \int_{S^2} d^2x\; {\cal K} (\gamma^{-1}\partial^{\mu}\gamma,\gamma^{-1}\partial_{\mu}\gamma)-
+ \frac{1 }{6} \int_{B}\epsilon_{ijk} {\cal K}\left(
     \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^i},
       \left[\tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^j}
-      \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^k}\right]\right) d^3y+\\
-+
-      \frac{k}{4\pi}\int_{S^2} d^{2}z \left(\mathcal{K}(\alpha, \gamma^{-1}\bar \partial \gamma)-\mathcal{K}(\bar \alpha, (\partial \gamma ) \gamma^{-1})\right.
-      \left.+\mathcal{K}(\alpha,\gamma^{-1}\bar \alpha \gamma)-\mathcal{K}(\alpha,\bar \alpha)\right).
+      \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^k}\right]\right) d^3y+\right.\\
+\left.+
+ \int_{S^2} d^{2}z \left(\mathcal{K}(\alpha, \gamma^{-1}\bar \partial \gamma)-\mathcal{K}(\bar \alpha, (\partial \gamma ) \gamma^{-1})\right.
+      \left.+\mathcal{K}(\alpha,\gamma^{-1}\bar \alpha \gamma)-\mathcal{K}(\alpha,\bar \alpha)\right)\right].
 \end{multline}
-Здесь через  $\mathcal{K}$ обозначена форма Киллинга в алгебре Ли $\gf$, соответствующей группе Ли $G$.
-
-Если мы фиксируем  $A$-калибровку, у нас останется  $G/A$ калибровочная инвариантность.
-Значит мы должны добавить случайные калибровочные преобразования к эволюции Шрамма-Левнера, аналогично случаю ВЗНВ-моделей.
+Через  $\mathcal{K}$ обозначена форма Киллинга в алгебре Ли $\gf$, соответствующей группе Ли $G$.
+После фиксации  $A$-калибровки останется  $G/A$ калибровочная инвариантность.
+Поэтому мы должны добавить случайные калибровочные преобразования к эволюции Шрамма-Левнера.
 Обозначим через $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) генераторы представления алгебры $\gf$ (соответственно, представления $\af$), соответствующего примарному полю $\varphi_{i}$.
@@
 Это должно выполняться и для ее непрерывного предела, дающегося комбинацией корреляционных функций в конформной теории поля:
-\begin{equation}
+$
   \prec \mathcal{O} \succ_{\mathbb{H}_{t}}\to \mathcal{F}(\left\{z_{i}\right\})_{\mathbb{H}_{t}}=
-  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}
+  \frac{\left< \mathcal{O}(\{z_{i}\})\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}{\left<\phi(z_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}_{t}}}.
+$
 %% =
@@
 %% \mathcal{O}\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}{\left<\phi(\xi_{t})\phi^{\dagger}(\infty)\right>_{\mathbb{H}}}
-\label{eq:162}
-\end{equation}
-Мы рассматриваем теорию с границей, так что мы должны использовать модели граничной конформной теории поля и накладывать соответствующие граничные условия.
-В случае верхней полуплоскости корреляционные функции в граничной конформной теории поля могут быть переписаны как корреляционные функции для теории на всей плоскости, но с удвоенным числом полей.
+Мы предполагаем, что $\mathcal{F}$ содержит некоторый набор примарных полей  $\varphi_{i}$ с конформными весами $h_{i}$.
+Так как мы рассматриваем конформную теорию с границей, необходимо добавить объемные поля в сопряженных точках  $\bar z_{i}$.
+Операторы смены граничного условия   $\phi$ находятся на конце следа эволюции Шрамма-Левнера и на бесконечности.
 
-Мы предполагаем, что $\mathcal{F}$ содержит некоторый набор примарных полей  $\varphi_{i}$ с конформными весами $h_{i}$.
-Так как мы рассматриваем граничную конформную теорию поля, мы должны добавить объемные поля в сопряженных точках  $\bar z_{i}$.
-Кроме того, у нас есть операторы смены граничного условия   $\phi$ на конце следа эволюции Шрамма-Левнера и на бесконечности.
-
-Рассмотрим, что происходит с наблюдаемыми при эволюции следа SLE $\gamma_{t}$ с момента   $t$ до $t+ dt$. 
+Исследуем, что происходит с наблюдаемыми при эволюции следа SLE $\gamma_{t}$ с момента   $t$ до $t+ dt$. 
 Через  $\mathcal{G}_{i}$ мы обозначили  генераторы инфинитезимальных преобразований примарных полей $\varphi_{i}$:$d\varphi_{i}(w_{i}) = \mathcal{G}_{i}\varphi_{i}(w_{i})$.
 Нормируем дополнительное $\left(\dim\gf\right)$-мерное Броуновское движение следующим образом: $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
-Тогда генератор преобразования поля равен
-\begin{equation}
+Генератор преобразования поля равен
+$
   \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right).
-\label{eq:179}
-\end{equation}
-То есть мы фиксировали  $A$-калибровку, разрешив случайное блуждание только в направлении, ортогональном подалгебре $\af$.
+$ Мы фиксировали  $A$-калибровку, разрешив случайное блуждание только в направлении, ортогональном подалгебре $\af$.
 
 Формула Ито дает выражение для дифференциала $d\mathcal{F}$, который равняется нулю в силу условия мартингала.
-Это равенство можно переписать в виде дифференциального уравнения на корреляционные функции, которое эквивалентно   алгебраическому условия на граничное состояние $\phi(0)\left|0\right>$.
+Это равенство можно переписать в виде дифференциального уравнения на корреляционные функции, эквивалентное   алгебраическому условию на граничное состояние $\phi(0)\left|0\right>$.
 \begin{multline}
@@
 Действуя повышающими операторами мы получаем соотношения, связывающие параметры стохастического процесса и coset-модели конформной теории поля:
-\begin{equation}
- (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0.
- \label{eq:184}
-\end{equation}
-\begin{equation}
+\begin{eqnarray}
 \label{eq:185}
+ (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0\\
  -12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
 (C_{\mu}-\tilde{C}_{\nu})=0,
-\end{equation}
-здесь $C_{\mu}=(\mu,\mu+2\rho)$ и $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ -- это собственные значения квадратичных операторов Казимира $\sum_{a}t^{a}t^{a}$ и $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ алгебр Ли $\gf$ и $\af$.
-Из уравнения  \eqref{eq:184},\eqref{eq:185} мы сразу получаем значения  $\kappa,\tau$ для каждой пары весов $(\mu,\nu)$ алгебр $\gf$ и $\af$.
-Для coset-реализаций минимальных и парафермионных моделей эти результаты совпадают с тем, что было ранее получено путем введения стохастического процесса с дополнительным дискретным случайным блужданием  \cite{santachiara2008sle}.
+\end{eqnarray}
+здесь $C_{\mu}=(\mu,\mu+2\rho)$ и $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ -- собственные значения квадратичных операторов Казимира $\sum_{a}t^{a}t^{a}$ и $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ алгебр Ли $\gf$ и $\af$.
+Из уравнения \eqref{eq:185} мы сразу получаем значения  $\kappa,\tau$ для каждой пары весов $(\mu,\nu)$ алгебр $\gf$ и $\af$.
+Для coset-реализаций минимальных и парафермионных моделей эти результаты совпадают со значениями, полученными в работе \cite{santachiara2008sle} путем введения стохастического процесса с дополнительным дискретным случайным блужданием.
 
@@
 Вычислительным методам посвящены наши работы \citemy{2011arXiv1107.4681N,NazarovACSM2009,Nazarov2008}.
-
+\vspace{-0.5cm}
 %%  
@@
 \bibliographymy{bibliography}
-
+\vspace{-0.3cm}
 \renewcommand\bibsection{\nsection{Цитированная литература}}
-
+\vspace{-0.5cm}
 \def\BibPrefix{}

### 2012-10-04 AffineLieAlgebras/MQFT2012/presentation.tex
Presentation from MQFT2012 added

\documentclass[pdftex]{beamer} 
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsthm} 
\usepackage{pb-diagram}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{epstopdf}
\usepackage{multicol}
\usepackage{cancel}

\usepackage{amsfonts}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newtheorem{theorem}{Theorem}
%% \newtheorem{acknowledgement}[theorem]{Acknowledgement}
%% \newtheorem{algorithm}[theorem]{Algorithm}
%% \newtheorem{axiom}[theorem]{Axiom}
%% \newtheorem{case}[theorem]{Case}
%% \newtheorem{claim}[theorem]{Claim}
%% \newtheorem{conclusion}[theorem]{Conclusion}
%% \newtheorem{condition}[theorem]{Condition}
%% \newtheorem{conjecture}[theorem]{Conjecture}
%% \newtheorem{mycorollary}[theorem]{Corollary}
%% \newtheorem{mycriterion}[theorem]{Criterion}
%% \newtheorem{mydefinition}[theorem]{Definition}
%% \newtheorem{myexample}[theorem]{Example}
%% \newtheorem{myexercise}[theorem]{Exercise}
\newtheorem{mylemma}[theorem]{Lemma}
%% \newtheorem{mynotation}[theorem]{Notation}
%% \newtheorem{myproblem}[theorem]{Problem}
%% \newtheorem{myproposition}[theorem]{Proposition}
%% \newtheorem{myremark}[theorem]{Remark}
%% \newtheorem{mysolution}[theorem]{Solution}
%% \newtheorem{mysummary}[theorem]{Summary}
%% \newenvironment{myproof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfg}{\hf_{\gf}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\sfr}{\mathfrak{s}}
%\pagestyle{plain}

\theoremstyle{definition} \newtheorem{Def}{Definition}
\setbeamertemplate{caption}[empty]
\newcommand{\tr}{\hat\triangleright} \newcommand{\trc}{\triangleright}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

\usetheme{AnnArbor}
%\usetheme{Warsaw}

%% Модели Весса-Зумино-Новикова-Виттена и coset-модели -- это два важных
%% класса моделей двумерной конформной теории поля. Теория представления
%% аффинных алгебр Ли играет центральную роль при изучении таких моделей. 
%% Сингулярные векторы в модулях алгебры Ли аннигилируются повышающими
%% операторами. Набор этих векторов определяет структуры представления:
%% например, неприводимый модуль можно построить из модуля Верма путем
%% отщепления модулей Верма, соответствующих сингулярным векторам
%% (БГГ-резольвента). 
%% Мы рассмотрим структуру сингулярных элементов и свойства их разложения
%% по отношению к (аффинным) подалгебрам. Из этих свойств следуют
%% рекуррентные соотношения на коэффициенты ветвления и связь ветвления с
%% обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда. Мы также
%% покажем, что разложение сингулярных элементов определяет структуру
%% модулей алгебры Вирасоро в coset-моделях конформной теории поля.
%% 
\title[On singular elements in CFT]{On singular elements in conformal field theory}
\author[A. Nazarov]{A. Nazarov and V.D. Lyakhovsky\\\small{arXiv:1007.0318, 1111.6787, 1204.1855}}%\\\small{По материалам кандидатской диссертации\\ см. также arXiv:1007.0318, 1102.1702, 1107.4681, 1111.6787, 1112.4354 \\ научный руководитель В. Д. Ляховский}}

\institute[SPbSU]{
  Department of High Energy and Elementary Particle Physics\\
  faculty of physics\\
  St Petersburg State University\\
  198904, St Petersburg, Russia\\
  e-mail: anton.nazarov@hep.phys.spbu.ru
}

\date[MQFT 2012] % (optional, should be abbreviation of conference name)
{27.09.2012}
\begin{document}
\maketitle

\section{Introduction}

\begin{frame}
  \frametitle{Talk outline}
  We describe the structure of affine Lie algebra modules and its role in coset construction of conformal field theory models.
  \begin{itemize}
  \item WZNW and coset models of CFT
  \item Weyl-Kac formula and singular elements of algebra modules
  \item Singular element decomposition and branching
  \item Splints, theta functions and branching functions
  \end{itemize}

\end{frame}
\section{WZNW and coset-models of CFT }
\begin{frame}
  \frametitle{WZNW-action}
  \begin{equation}
    \label{eq:4}
    S=S_0+k\Gamma, \quad k\in \mathbb{Z}
  \end{equation}
Here $S_0$ is the action of non-linear sigma model:
\begin{equation}
  \label{eq:5}
  S_0=-\frac{k}{8\pi}\int_{S^2} d^2x\; Tr (\partial^{\mu}g^{-1}\partial_{\mu}g),\quad g(x):\mathbb{C}\cup \{\infty\}\sim S^{2}\to G 
\end{equation}

We need to add topological Wess-Zumino term:
\begin{equation}
  \label{eq:73}
\Gamma= - \frac{i }{24\pi} \int_{B}\epsilon_{ijk} Tr\left(
    \tilde g^{-1}\frac{\partial \tilde g}{\partial y^i}
      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^j}
      \tilde g^{-1}\frac{\partial \tilde g}{\partial y^k}\right) d^3y
\end{equation}
Here $\Gamma$ is defined on 3d manifold $B$, such that $\partial B = S^{2}$. $\tilde{g}$ is a continuation of $g$ to $B$.\\
$\pi_{3}(G)=\mathbb{Z} \Rightarrow k\in\mathbb{Z}, \; e^{-S[g]}$ is single-valued.

\end{frame}
\begin{frame}
  \frametitle{Affine Lie algebra}

  \begin{itemize}
  \item   The currents are 
    $J(z)= -k \partial_zg g^{-1}\quad \bar J(\bar z)=k g^{-1}\partial_{\bar z}g$

  \item We have gauge invariance $   g(z,\bar z)\to \Omega(z)g(z,\bar z)\bar \Omega^{-1}(\bar z)$,
    where $\Omega,\;\bar \Omega \in G$

  \item Ward identities for $\Omega=1+\omega$:
    \begin{equation*}
      \label{eq:87}
      \delta_{\omega,\bar \omega}\left< X \right>=-\frac{1}{2\pi i}\oint dz \sum\omega^a \left< J^a X\right>+
      \frac{1}{2\pi i} \oint d\bar z \sum \bar \omega^a \left< \bar J^a X\right>
    \end{equation*}
  \item  $J(z)=\sum_{a} J^{a}(z) t^{a}=\sum_{a} \sum _{n} J^{a}_{n} t^{a} z^{n-1} \Rightarrow$ commutation relations of affine Lie algebra $\gfh$: 
    \begin{equation*}
      \left[J^a_n,J^b_m\right]=\sum_c i f^{abc}J^c_{n+m}+kn\delta^{ab}\delta_{n+m,0}
    \end{equation*}
  \item Virasoro generators are given by Sugawara construction $  L_n=\frac{1}{2(k+h^v)}\sum\limits_a\sum\limits_m:J^a_m J^a_{n-m}: \Leftrightarrow Vir\subset U(\gfh)$.
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Primary fields}
  \begin{itemize}
  \item Full chiral algebra of the model is $\gfh \ltimes Vir$:
    \begin{equation}
      \label{eq:92}
      \begin{aligned}
        \left[L_n,L_m\right]=(n-m)L_{n+m}+\frac{c}{12}(n^3-n)\delta_{n+m,0}\\
        \left[L_n,J^a_m\right]=-mJ^a_{n+m}
      \end{aligned}
    \end{equation}
  \item $\left[L_{0},L_{m}\right]=-m L_{m},\quad \left[L_{0},J^{a}_{m}\right]=-m J^{a}_{m}$ \quad-- grading
  \item Primary fields are defined by operator product expansion $J_{\gf}^{a}(z)\phi_{i}(w)\sim \frac{-t^{a}_{i}\phi_{i}(w)}{z-w}$.
  \item Primary fields $\phi_{\lambda}$ correspond to highest weights of representations. Field-state correspondence: $\left|\lambda\right>=\lim_{z\to 0}\phi_{\lambda}(z)\left|\Omega\right>$:
    \begin{equation*}
      \begin{aligned}
        & J_0^a\left|\phi_{\lambda}\right>=-t^a_{\lambda}\left|\phi_{\lambda}\right>  \quad    J^a_n\left|\phi_{\lambda}\right>=0 \quad \mbox{for}\; n>0 \\
        & L_0\left|\phi_{\lambda}\right>=\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0\left|\phi_{\lambda}\right>=\frac{(\lambda,\lambda+2\rho)}{2(k+h^v)}\left|\phi_{\lambda}\right>=h_{\lambda} \left|\phi_{\lambda}\right>
      \end{aligned}
    \end{equation*}

  \item Singular vectors
$
    \begin{aligned}
      &J^a_n\left|v \right>=0 \quad \mbox{for}\; n>0 \\
      & J^{+}_{0} \left|v \right>=0
    \end{aligned}
    $
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Weyl-Kac character formula and singular elements}

Verma module
\begin{equation*}
 M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}) \quad \mbox{where} \quad     \gf=\mathfrak{n}_{+}\oplus \hf \oplus\mathfrak{n}_{-}, \bff_{+}=\mathfrak{n}_{+}\oplus \hf
\end{equation*}

$D^{\mu}(\bff_{+}): D(E^{\alpha})=0,\; D(H)=\mu(H)\quad \forall \alpha>0$.

\begin{equation*}
  \label{eq:11}
  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}, \quad \epsilon \left( w\right) :=\det \left( w\right)
\end{equation*}

$M^{\mu}$ has unique maximal submodule and unique non-trivial factormodule $L^{\mu}$ -- 
{\it irreducible highest weight module}. $L^{\mu}\sim U(\mathfrak{n}_{-})/<\Psi^{\mu}>$.

\begin{equation*}
  \label{eq:13}
  \mathrm{ch} L^{\mu}=\frac{\Psi^{\mu}}{R}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho} (\mbox{BGG})
\end{equation*}

\end{frame}

\begin{frame}
  \frametitle{Coset-construction and gauged WZNW-model}

  Let's add pure gauge fields  $A, \bar{A}$ with the values in subalgebra $\af\subset \gf$ to the action:
  \begin{multline*}
    S(g,A)=S_{WZNW}(g)+\\
    \frac{k}{4\pi}\int d^{2}z \left(Tr(A g^{-1}\bar \partial g)-Tr(\bar A (\partial g ) g^{-1})+Tr(A g^{-1}\bar A g)-Tr(A \bar A)\right)
  \end{multline*}

  The currents are
  \begin{equation*}
    J_{(\gf,\af)}=-k\partial g g^{-1} -k g A g^{-1}
  \end{equation*}

  Using Ward identities we obtain
  \begin{equation*}
    \left< A^{b}(z)\phi_{1}\dots \phi_{N}\right>=\frac{2}{k+2 h^{v}_{\af}}\sum_{k}\frac{\tilde{t}^{b}_{k}}{z-z_{k}}\left<\phi_{1}\dots \phi_{N}\right>
  \end{equation*}

%%  Commutation relations for current components are preserved.

  Algebraic structure is connected with  $\gfh, \afh: \afh\subset\gfh$.

  Virasoro generators are given by the difference of Sugawara expressions:
  \begin{equation*}
    L_{n}=L_{n}^{\gf}-L_{n}^{\af}
  \end{equation*}
\end{frame}

\begin{frame}
  \frametitle{Primary fields and singular elements}
%%   For  $\afh$ generators we have:
%%   \begin{equation*}
%%     \left[ L_{n}, \tilde{J}^{b}_{m}\right]=0 \quad\Longleftrightarrow\quad \tilde{J}^{b}_{m}\left| v \right>=0\Rightarrow \tilde{J}^{b}_{m}L_{n}\left| v \right>=0
%%   \end{equation*}
%%   Branching functions $b^{\mu}_{(\gfh\downarrow\afh) \nu}(q)$ are proportional to the characters of Virasoro algebra.
%% 
  Primary fields are labeled with pairs of weights $(\mu,\nu)\in \hf_{\gfh}^{*}\oplus \hf_{\afh}^{*}$ such that  $b^{\mu}_{\nu}(q)\neq 0$. Some pairs are equivalent. The equivalence is given by the  action of simple currents $(J,\tilde{J})$ such that $h_{J}-h_{\tilde{J}}=0$.

  Conformal weight of primary field is
  \begin{multline}
    L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^v)}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^v)}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
    \left|\phi_{\lambda}\right>=\\
    \left(\frac{(\mu,\mu+2\rho)}{2(k+h^v)}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^v)}\right)\left|\phi_{(\mu,\nu)}\right>
  \end{multline}

%%   \begin{equation*}
%%     \begin{diagram}
%%       \node{ \bigoplus_{(\mu,\nu)}L^{\mu}_{\gfh}\otimes L^{\nu}_{\afh}\equiv \bigoplus_{(\mu,\nu)} (U(\bff_{\gfh})\otimes U(\bff_{\afh})/ 
%%         <\Psi^{\mu}_{\gfh}\otimes \Psi^{\nu}_{\afh}>)} \arrow{e,t}{\afh\to\gfh}  \node{\bigoplus L_{\gfh}\equiv \bigoplus U(\bff_{\gfh})/<\Psi>}     \arrow{s,l}{/(J,\tilde J)}\\
%%       \node{\bigoplus V^{(\mu,\nu)}}\arrow{w,t}{\equiv} \node{\bigoplus L^{\nu}_{\afh}\times V^{(\mu,\nu)}}
%%     \end{diagram}
%%   \end{equation*}
%%   
  We can decompose $\gfh$ modules
  \begin{equation*}
    L^{\mu}_{\gfh}=\bigoplus_{\nu} L^{\nu}_{\afh}\otimes V^{(\mu,\nu)}
  \end{equation*}

%%  So $G/A$-coset theory is related to $\gf\oplus \bar{\af}$-theory.
\end{frame}

\section{Singular elements of affine Lie algebra modules}

\begin{frame}
  \frametitle{Singular element decomposition}
  We can rewrite the decomposition with characters
  \begin{equation*}
\pi _{\af}\left( \frac{\sum_{\omega \in W}\epsilon (\omega )e^{\omega (\mu +\rho )-\rho }}
  {\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{mult}(\alpha )}}\right) =
\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}
\frac{\sum_{\omega \in W_{\af}}\epsilon (\omega )e^{\omega (\nu +\rho _{\af})-\rho _{\af}}}
{\prod_{\beta \in \Delta _{\af}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\af}(\beta )}}.  
\end{equation*}

We need to compute branching coefficients. Let us multiply by denominator and rearrange sum as recurrent relation. \\

Consider roots orthogonal to $\Delta_{\af}$.

Let $\Delta^{+}_{\frak{b}}=\left\{\alpha\in \Delta^{+}_{\frak{g}}:\forall
\beta\in\Delta_{\af} ; \alpha\bot \beta\right\}$ -- subset of positive roots of $\gf$, orthogonal to root system of  $\af$.

Denote by  $W_{\frak{b}}$  subgroup of Weyl group $W$, generated by reflections  $\omega _{\beta }$, corresponding to roots $\beta \in \Delta
_{\frak{b}}^{+}$.

Subsystem $\Delta _{\frak{b}}$ determines subalgebra $\frak{b}=\afb\subset\gf$.
\end{frame}
\begin{frame}

$\af, \mathfrak{b}$ -- ``orthogonal pair'' of subalgebras $\gf$, $\bff$ is regular.

Cartan subalgebra is decomposed as 
$\frak{{h}=\frak{h}_{\af}+\frak{h}_{\bot}+\frak{h}_{\frak{b}}.}$

Introduce
\begin{eqnarray*}
\mathcal{D}_{\af} :=\rho_{\af}-\pi_{\af}\rho.\\
\mathcal{D}_{\frak{b}} :=\rho_{\frak{b}}-\pi_{\frak{b}}\rho.
\end{eqnarray*}
\begin{mylemma}
\label{lemma}
Let  $\widetilde{\afb}=\afb\oplus \hf_{\perp }$, $\widetilde{\af}=\af\oplus\hf_{\perp }$ ,

$L^{\mu }$ -- irreducible module with singular element $\Psi ^{\left(\mu \right)}$ ,

$R_{\af_{\perp }}$ -- Weyl denominator for subalgebra $\af_{\perp }$. $U\sim W/W_{\afb}$.

Then  $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi _{\af}\left( \frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}\right) $ can be present as the sum over  $u\in U$:
\begin{equation*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\quad \pi _{\af}\left( \frac{\Psi^{\mu }}{R_{\af%
_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }
\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
\widetilde{\af_{\perp }}}\left( u\right) }\right) e^{\mu _{\af}\left( u \right) }.
\end{equation*}
\end{mylemma}
\end{frame}
\begin{frame}
  \frametitle{Recurrent relations on branching coefficients}

\begin{eqnarray*}
k_{\xi }^{\left( \mu \right) } &=&-\frac{1}{s\left( \gamma _{0}\right) }%
\left( \sum_{u\in W/W_{\frak{b}}}\epsilon (u)\;\mathrm{dim}\left( L_{\mathfrak{b}}^{\pi
_{\left( \frak{b}\right) }\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{%
\frak{b}}}\right) \right.\\
&&\left.\delta _{\xi -\gamma _{0},\pi _{\left( \frak{a\oplus h}%
_{\perp}\right) }\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{b}%
}}+
%\right.
%\notag \\ &&
%\left. +
\sum_{\gamma \in \Gamma _{\afh\subset \gfh}}s\left( \gamma
+\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right) }\right) \text{.}
\end{eqnarray*}
The recursion is governed by the set $\Gamma _{\afh\subset \gfh}$ of weights $\left\{\xi\right\}$ in expansion
\begin{equation*}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\mathfrak{b} }^{+}}\left( 1-e^{-\pi
_{\afh}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\afh}(\pi _{\afh}\alpha )}=-\sum_{\gamma \in P_{\afh}}s(\gamma )e^{-\gamma }
\end{equation*}
We need to shift weights on  $\gamma _{0}$ -- minimal weight in  $\left\{ \xi\right\} $, and exclude zero element:
\begin{equation*}
\Gamma _{\afh\subset \gfh}=\left\{ \xi -\gamma
_{0}\right\} \setminus \left\{ 0\right\} .
\end{equation*}
\end{frame}
\section{Examples}
\begin{frame}
  \frametitle{Simple example: $A_{1}\subset B_{2}$}
  \begin{figure}[t]
    \vspace*{-0.5cm}
    \begin{multicols}{2}
      \hfill
      \includegraphics[width=60mm]{figures/figure1}
      \hfill
      \caption{Roots of $B_{2},A_{1}$ and $\Psi ^{\omega_1  }$}
      \hfill
      \vspace{5mm}
      \includegraphics[width=60mm]{figures/figure2}
      \caption{Orthogonal subalgebra $\mathfrak{b}$ and dimensions of  $\mathfrak{b}$-modules}
    \end{multicols}
  \end{figure}
\end{frame}
\subsection{Affine example}
\begin{frame}
  \begin{figure}[t]
    \vspace*{-0.5cm}
    \begin{multicols}{2}
      \hfill
      \includegraphics[width=60mm]{figures/figure10}
      \hfill
      \caption{$\Gamma_{\hat A_1\subset \hat B_2}$}
      \hfill
      \includegraphics[width=60mm]{figures/figure12}
      \caption{ $\pi_{\hat A_{1}}\left( \Psi ^{\omega_1  }_{\hat B_{2}}\right)$}
    \end{multicols}
  \end{figure}
  \begin{figure}[b]
    \vspace*{-1.3cm}
    \centering
      \includegraphics[width=100mm]{figures/figure13}
    \caption{Signed branching coefficients for $\hat A_1\subset \hat B_2$}
    \label{fig:2}
  \end{figure}
\end{frame}

\section{Splints and embeddings}
\begin{frame}
  \frametitle{Splints}
  \begin{Def}
$\phi $ -- ``embedding'' $\Delta_{0}\hookrightarrow \Delta$:
$\phi (\gamma )=\phi (\alpha )+\phi (\beta )\quad  \forall \alpha ,\beta ,\gamma \in P_{0}: \gamma =\alpha+\beta.$

\end{Def}
$\phi$ induces embedding of formal algebras: ${\mathcal{E}}_0\hookrightarrow \mathcal{E}$ and for ${\mathcal{E}}_i=\mathrm{Im}_{\phi}\left( {\mathcal{E}}_0\right)$ and $\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.

\begin{Def}
Root system $\Delta$ ``splints'' to  $(\Delta _{1},\Delta _{2})$ if there exist embeddings  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $\phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ -- disjoint union of images of $\phi _{1}$ and $\phi _{2}$, (b) rank of  $\Delta _{1}$ and rank  $\Delta _{2}$ is less or equal to rank of $\Delta $.
\end{Def}
Let $\Delta _{1}=\Delta _{\af}$. $\Delta _{\sfr}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ determines injection fan  $\Gamma _{\af\hookrightarrow \gf}$. 
$\prod_{\beta \in \Delta _{\sfr}^{+}}\left( 1-e^{-\beta }\right)
=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }$

$\Psi _{\gf}^{\left( \mu \right) }=e^{-\rho}\sum_{w\in W_{\af}}w\circ \left(
e^{\rho _{\af}}\phi_{2}\left(\Psi ^{\widetilde{\mu }+\rho _{\sfr}}\right)\right) \quad \mu=\sum m_{k}\omega ^{k},\;\widetilde{\mu }=\sum m_{k}\omega _{\sfr}^{k}$

\end{frame}
\begin{frame}
  \frametitle{Example}
  \vspace{-0.5cm}
\begin{figure}[h!bt]
  \hspace*{-1.2cm}

   \includegraphics[width=50mm]{figures/b2}
   \includegraphics[width=50mm]{figures/b2-a2-a1}
  \caption{Weights and multiplicities of  $L^{[3,2]}_{B_{2}}$ on the left. Short dash is a singular element contour. On the right is a decomposition of singular element $\Psi_{B_{2}}(L^{[3,2]}_{B_{2}})$ into sum of images of singular elements $\Psi_{A_{2}}(L^{[3,2]})$ (long dash).  $L^{[3,2]}_{A_{2}}$ multiplicities =  branching coefficients for  $L^{[3,2]}_{B_{2}\downarrow A_{1}\oplus u(1)}$.}

 \label{fig:b2_splint}
\end{figure}

\end{frame}

\subsection{$G_2$}
\begin{frame}

  \begin{figure}[h!bt]
  \noindent\centering{
   \includegraphics[width=65mm]{figures/g2}
  }

  \caption{Weyl group orbit  (long dash) for  $\Psi_{G_{2}}(L^{[3,2]})$ and its decomposition into sum of images of singular elements of   $A_{2}$ modules (short dash). Weight multiplicities of  $L^{[3,2]}_{A_{2}}$ coincide with branching coefficients $L^{[3,2]}_{G_{2}\downarrow A_{2}}$.}

 \label{fig:g2_splint}
\end{figure}

\end{frame}

\subsection{Affine Lie algebras}
\begin{frame}
Affine extension $\afh\subset\gfh$. Since $\mathrm{rank}\gf\leq\mathrm{rank} \af+\mathrm{rank}\sfr$ for Weyl denominators we have 
\begin{multline*}
\prod_{\alpha\in\hat{\Delta}^{+}_{1}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}\prod_{\beta\in\hat{\Delta}^{+}_{2}}(1-e^{\phi\circ \beta})^{\mathrm{mult}(\beta)}=\\
\prod_{\gamma\in\hat{\Delta}^{+}}(1-e^{-\gamma})^{\mathrm{mult}(\gamma)}\prod_{n=0}^{\infty}(1-e^{-n\delta})^{\mathrm{rank}\af+\mathrm{rank}\sfr-\mathrm{rank}\gf}
\end{multline*}
 $$\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in Q_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$$
Then we obtain relation on theta-functions of algebras $\gfh,\hat\sfr,\afh$:
\begin{multline*}
  \left(\sum_{v\in W_{\af}}\epsilon(v) \Theta^{(\afh)}_{v\rho_{\af}}(\tau,z)\right)
  \cdot \left(\sum_{u\in W_{\sfr}}\epsilon(u) \Theta^{(\hat{\sfr})}_{\phi\circ(u\rho_{\sfr})}(\tau,z)\right)= \\
  \left(\sum_{w\in W}\epsilon(w) \Theta^{(\gfh)}_{w\rho_{\gf}}(\tau,z)\right)
\end{multline*}
\end{frame}
\begin{frame}
  \frametitle{Branching to finite-dimensional subalgebras}

Consider branching of  $\gfh$-module to  $\gf$-modules
\begin{equation*}
  \label{eq:149}
\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{\nu}(n) \mathrm{ch} L^{\nu}_{\gf} \quad m^{(\hat{\mu})}_{\hat{\nu}=(\nu,k,n)}=\sum_{\xi\in P}
b^{(\hat{\mu})}_{\xi}(n) m^{(\xi)}_{\nu}
\end{equation*}
Introduce functions $b^{(\hat{\mu})}_{\nu}(q):=\sum_{n=0}^{\infty} b^{(\hat{\mu})}_{\nu}(n) q^{n}$, which are connected with  $q$-dimension \\ $\mathrm{dim}_{q}L^{\hat \mu}_{\gfh}=\sum_{n=0}^{\infty}q^{n}\sum_{\nu\in P} b^{(\hat \mu)}_{\nu}(n) \mathrm{dim }L^{\nu}_{\gf}=\sum_{\nu\in P}b^{(\hat\mu)}_{\nu}(q) \mathrm{dim} L^{\nu}_{\gf}$.

 $ \sigma^{(\hat{\mu})}_{\nu}(q) = \sum_{\xi\in P} m^{(\xi)}_{\nu} b^{(\hat{\mu})}_{\xi}(q)$.

Introduce the order on the set of the roots $\xi$:
assign to the weight   $\xi$ the value  $(\rho,\xi)$ and order weights using this values. Then  $$\sigma(q)=M b(q)\quad b(q)=M^{-1}\sigma(q)$$
  $\sigma(q)$ and  $b(q)$ are infinite vectors of string functions and branching functions. The matrix $M$ contains weight multiplicities of  $\gf$-modules. Inverse matrix $M^{-1}$ consists of recurrent relations on weight multiplicities.
\end{frame}
\begin{frame}
    \frametitle{Matrix relations for splints}
Consider branching of  $\gfh$-modules into  $\af$-modules when there exists a splint
$\Delta^{+}_{\gf}=\Delta^{+}_{\af}\cup \phi(\Delta^{+}_{\sfr})$.
Decompose  $\gf$-modules into 
$\af$-modules using splint properties:
\begin{multline}
  \label{eq:125}
  \mathrm{ch}L^{\hat{\mu}}_{\gfh}=
\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P_{\af}} b^{(\hat{\mu})}_{(\gfh\downarrow\af)\nu}(n) \mathrm{ch} L^{\nu}_{\af}=\\
\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} b^{(\nu)}_{(\gf\downarrow \af) \xi}\mathrm{ch} L^{\xi}_{\af}=\\
=\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} M^{\widetilde{\nu}}_{  \widetilde{\nu}-\phi^{-1}( \nu-\xi )}\mathrm{ch} L^{\xi}_{\af}
\end{multline}
Matrix relation holds for branching functions $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}\;
b_{(\gfh\downarrow\gf)}(q)$ and
$\sigma(q)=M_{\af}\; b_{(\gfh\downarrow\af)}(q)$.  If we know branching coefficients for the embedding $\gf\subset\gfh$ we immediately obtain (graded) branching functions for the embedding $\af\subset \gfh$.
\end{frame}

\section{Conclusion}

\begin{frame}
  \frametitle{Conclusion}
  \begin{itemize}
  \item Singular elements determine structure of modules
  \item Decomposition of singular element leads to relations on branching coefficients
  \item We can get different decompositions and new relations if we consider deformed root subsystems
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Thank you!}
\end{frame}

\end{document}

### 2012-10-04 AffineLieAlgebras/MQFT2012/talk.tex
Presentation from MQFT2012 added

\documentclass[a4paper]{article}

\begin{document}
Thank you. I am happy to be here. My talk is about representation theory of affine Lie algebras. I want to emphasize the role of singular elements in structure of irreducible modules. Here is the outline of my talk. At first I will remind you of Wess-Zumino-Novikov-Witten models and coset construction in two-dimensional conformal field theory. Then we will see the appearance of affine Lie algebras. I will remind you of Weyl-Kac formula and use singular element decomposition to introduce recurrent relation on branching coefficients. At last we introduce splints of root  systems and corresponding decompositions of singular elements and consider consequences for representation theory.

Wess-Zumino-Witten action has this form. The first term is the action of non-linear sigma model. It is written for the field on complex plane which takes values in some semisimple Lie group Gi. Conformal invariance is lost after the quantization, so we need to add topological term to cancel the anomaly. This Wess-Zumino term is written in term of continuation of field gi to 3-manifold B which is bounded by two-sphere. Such continuation is not unique and this expression is not single-valued but the exponent of it is if k is integral.

Conserved currents for this model are written here. After the introduction of complex variables z and z bar the sectors can be studied independently. We have gauge invariance, where omega and omega bar are independent. Ward identities for gauge transformations are here.

We do series expansion of the currents and substitute it to Ward identities. We obtain commutation relations of affine Lie algebra g hat. 
Virasoro generators are given by Sugawara construction, so Virasoro algebra is embedded into universal enveloping algebra of g hat.

We see that full chiral algebra of the model is semidirect product of affine Lie algebra and Virasoro algebra with this commutation relations. 
Note that we have grading here. L zero is essentially an energy operator.

All the fields are organised as families. Each family consists of primary field and its descendants. Primary fields are defined by this operator product expansion with currents. Primary fields are labelled by highest weights of affine Lie algebra representations. From field-state correspondence we see that these fields are also primary with respect to Virasoro generators and have these conformal dimensions.

Singular vectors in Hilbert space are those which are destroyed by all raising operators. Hilbert space consists of highest-weight modules of affine Lie algebra. Let us study the structure of these modules.

The simplest modules are Verma modules. If we introduce formal characters we see that characters of such modules has this form. The numerator consists of single exponent of highest weight and the denominator can be written as the product over positive roots or as the sum over Weyl group orbit. Verma module has unique maximal submodule and non-trivial factormodule is irreducible. We can think of it as of universal enveloping algebra of lowering operators modulo some ideal generated by singular element. 
It can be seen from Weyl-Kac character formula. Here psi is singular element and R is Weyl denominator. Also character of irreducible module can be presented as a combination of Verma module characters.

Let us now move to coset construction. We add interaction with pure gauge fields to the action. These fields take values in some subalgebra of algebra g. The currents now has two components. From Ward identities we see that we essentially have two Wess-Zumino-Novikov-Witten models. The generators of Virasoro algebra are given by the difference of Sugawara expression.

Primary fields are now labeled with pairs of weights mu and nu for algebras g and a. But some pairs are equivalent. The equivalence is given by action of so-called simple currents. Conformal weights of primary field are differences of conformal weights in Wess-Zumino-Witten models.

The modules of affine Lie algebra g hat can be decomposed as a sum of tensor product of subalgebra and Virasoro modules. So we need to study the branching rules to describe Virasoro modules.

We can rewrite the decomposition of modules as the decomposition of formal characters. Branching coefficients are dimensions of certain energy subspaces of Virasoro modules.

In order to compute branching coefficients we want to multiply by denominator, equate coefficients before the exponents and rearrange sum  as a recurrent relation. But we have technical difficulty - some components of denominator after projection can give us zero. We will isolate such roots.

Consider roots that are orthogonal to root system of subalgebra a. It can be seen that such roots form root system and determine subalgebra b which we call orthogonal to a. For such an orthogonal pair of subalgebras we can state following lemma. The singular element of algebra g module divided by the denominator of orthogonal subalgebra can be decomposed into the sum over equivalence classes of Weyl group and coefficients are equal to dimensions of orthogonal subalgebra modules.

Now we can write recurrent relation for signed branching coefficients. Here is a recurrent term and elements of our decomposition appear as initial data for the recursion. The recursion is governed by the certain set of weights which appear in the expansion of denominator. We call this set an injection fan. It is universal for all modules.

Now consider simple example. Here is root system of algebra B two. This is highest weight of module. Here are weights of singular element. Here is positive root system of algebra, here is root of subalgebra. Here is root of orthogonal subalgebra. Then we show the modules of orthogonal subalgebra and their dimensions. Calculate branching coefficients recurrently using this initial data.

Now consider affine extension. Here is injection fan and singular element with the dimensions of modules of orthogonal subalgebra. And here is result of recurrent computation.

Let us study another decomposition. We will use pair of algebras but one of them is not required to be subalgebra. Instead we will look at the root system of algebra as the union of images of two embeddings. These embeddings are not required to preserve the angles between the roots. We call this situation ``splint''. Let first component of splint be root system of some subalgebra a. Then we can clearly see that splint determine injection fan. We also has a decomposition of singular elements.

Then it is possible to show that branching coefficients coincide with weight multiplicities of modules of algebra s. Consider as an example Lie algebra B2. Its root system can be seen as the union of root system of A1 and root system of A2 with changed angles. We see that singular element can also be presented as combination of singular elements of A2 with changed angles. So when we calculate branching coefficients to A1 we see that they coincide with weight multiplicities of A2 modules.

\end{document}

### 2012-10-09 AffineLieAlgebras/Thesis/common.tex
<mmmm
Synopsis shortened to 16 pages

@@
 
-\topic{Правила ветвления аффинных алгебр Ли и приложения в моделях конформной теории поля}
+\topic{Правила ветвления аффинных алгебр Ли\\ и приложения в моделях конформной теории поля}
 
@@
 \mkcommonsect{objective}{Цели и задачи работы}{%
-
  Разработка рекуррентного подхода к функциям ветвления аффинных алгебр Ли, его связь с проблемами теории представлений и его приложения в моделях конформной теории поля.
@@
   В диссертации впервые решены следующие задачи:
-  \begin{itemize}
+  \begin{itemize}[topsep=0pt, itemsep=-1ex]
   \item Получено эффективное рекуррентное соотношение для коэффициентов ветвления модулей аффинных и конечномерных алгебр Ли на модули не максимальных подалгебр.
@@
 %  \item Показано, что наличие расщепления приводит к существенному упрощению при вычислении коэффициентов ветвления.
-  \item Исследована связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
-Показано, что разложение сингулярного элемента определяет как коэффициенты ветвления, так и обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда, так как действие веера вложения на компоненты разложения порождает обобщенные модули Верма, которые образуют точную последовательность.
-  \item Построена модель обобщеннного стохастического процесса Шрамма-Лёвнера для систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля.
+  \item Исследована связь процедуры редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда (БГГ).
+Показано, что разложение сингулярного элемента определяет как коэффициенты ветвления, так и обобщенную БГГ-резольвенту, так как действие веера вложения на компоненты разложения порождает обобщенные модули Верма, которые образуют точную последовательность.
+  \item Построена модель обобщенного стохастического процесса Шрамма-Лёвнера для систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля.
   \end{itemize}
@@
 
-\mkcommonsect{results}{На защиту выносятся следующие основные результаты и положения:}{%
-\begin{itemize}
+\mkcommonsect{results}{На защиту выносятся следующие результаты и положения:}{%
+\begin{itemize}[topsep=0pt, itemsep=-1ex]
 \item Получены новые рекуррентные соотношения на коэффициенты ветвления представлений аффинных алгебр Ли на представления произвольных редуктивных подалгебр, с использованием разложения сингулярных элементов
-\item Установлено, что разложение сингулярного элемента определяет как коэффициенты ветвления, так и обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда, так как действие веера вложения на компоненты разложения порождает обобщенные модули Верма, которые образуют точную последовательность
+\item Установлено, что разложение сингулярного элемента определяет как коэффициенты ветвления, так и обобщенную БГГ-резольвенту, так как действие веера вложения на компоненты разложения порождает обобщенные модули Верма, которые образуют точную последовательность
 \item  Доказано, что при определенных условиях  кратности весов вспомогательного модуля иньективного сплинта совпадают с коэффициентами ветвления в редукции на вложенную подалгебру.
@@
 \mkcommonsect{approbation}{Апробация работы}{%
+  Материалы диссертации докладывались на трех международных конференциях, а также на семинарах кафедры физики высоких энергий и элементарных частиц СПбГУ, на семинарах в лаборатории имени П.Л.
+Чебышева математико-механического факультета СПбГУ, на семинаре лаборатории теоретической физики ОИЯИ (Дубна).
 
-  Материалы диссертации докладывались на семинарах кафедры физики высоких энергий и элементарных частиц СПбГУ, на семинарах в лаборатории имени П.Л.
-Чебышева математико-механического факультета СПбГУ, на  международном семинаре молодых ученых ``Workshop on Advanced Computer Simulation Methods''  27 - 29 апреля 2009 (Санкт-Петербург),  на международных конференциях:  ``Модели квантовой теории поля (MQFT-2010)'' 18-22 октября 2010 (Санкт-Петербург), ``Supersymmetries and Quantum Symmetries - 2011'', 18-23 июля 2011 (Дубна), ``Quantum Theory and Symmetries (QTS-7)'', 7-13 августа 2011 (Прага).
+%  международном семинаре молодых ученых ``Workshop on Advanced Computer Simulation Methods''  27 - 29 апреля 2009 
+%(Санкт-Петербург),  на международных конференциях:  ``Модели квантовой теории поля (MQFT-2010)'' 18-22 октября 2010 
+%(Санкт-Петербург), ``Supersymmetries and Quantum Symmetries - 2011'', 18-23 июля 2011 (Дубна), ``Quantum Theory and 
+%Symmetries (QTS-7)'', 7-13 августа 2011 (Прага). 
 }
@@
 \mkcommonsect{pub}{Публикации.}{%
-
 Материалы диссертации опубликованы в $10$ печатных работах, из них $5$ статей в
@@
 
-\mkcommonsect{contrib}{Личный вклад автора}{%
-
+\mkcommonsect{contrib}{Личный вклад автора.}{%
+  Все основные результаты и выносимые на защиту положения получены автором самостоятельно.
+Личный вклад автора в работы с соавтором составляет $50$ процетнов, в работы без соавторов -- $100$ процентов.
 }
@@
 \mkcommonsect{struct}{Структура и объем диссертации}{%
-
 Диссертация состоит из введения и шести глав, содержит 160 страниц и 30 рисунков. Список литературы включает 151 наименование.

### 2012-10-09 AffineLieAlgebras/Thesis/autoref.tex
Synopsis shortened to 16 pages

@@
 \usepackage[a4paper,nohead,includefoot,mag=1000,
-            margin=2cm,footskip=1cm]{geometry}
+            margin=2cm,footskip=0.7cm]{geometry}
+\usepackage{enumitem}
 \usepackage[T2A]{fontenc}
@@
 \ifpdf\usepackage{epstopdf}\fi
-
 % Поддержка нескольких списков литературы в одном документе
@@
 \graphicspath{{figures/}}
-
+\setlength{\parskip}{0ex}
 \input{macro}
@@
 % (текст титульного листа и характеристика работы).
+
 \input{common}
@@
 \noindent
-\begin{minipage}
 Ученый секретарь\\
 диссертационного совета,%\\
-\end{minipage}
 %\emph{д.ф.-м.н.}%, \emph{ученое звание}%
@@
 
-\textbf{Актуальность работы}
-
+\textbf{Актуальность работы.}
 Последние тридцать лет конформная теория поля в двух измерениях привлекает большое внимание исследователей.
@@
 Изучение аффинных алгебр Ли было начато Виктором Кацем и Робертом Муди в 1960-х годах с попытки обобщения классификации простых конечномерных алгебр Ли на бесконечномерный случай \cite{kac1968simple,moody1968new}.
-Первоначально интерес к этим алгебрам был связан с модулярными свойствами характеров их модулей.
-После возникновения двумерной конформной теории поля были предложены модели Весса-Зумино-Новикова-Виттена, а затем и coset-модели, в которых теория представлений аффинных алгебр Ли играет определяющую роль.
+Интерес к этим алгебрам был связан с модулярными свойствами характеров их модулей.
+После возникновения двумерной конформной теории поля были предложены модели Весса-Зумино-Новикова-Виттена (ВЗНВ), а затем и coset-модели, в которых теория представлений аффинных алгебр Ли играет определяющую роль.
 
-Моделям Весса-Зумино-Новикова-Виттена, coset-моделям и теории представлений аффинных алгебр Ли  посвящены тысячи работ.
+ВЗНВ-моделям, coset-моделям и теории представлений аффинных алгебр Ли  посвящены тысячи работ.
 Однако многие проблемы по-прежнему не имеют простых решений.
-Например, задача вычисления коэффициентов ветвления для представлений алгебр Ли стоит уже многие десятилетия.
-Она актуальна для различных физических приложений в coset-моделях конформной теории поля.
-При этом, в отличие от проблемы вычисления кратностей весов, для вычисления коэффициентов ветвления не существовало особенно эффективных алгоритмов.
+Так, задача вычисления коэффициентов ветвления для представлений алгебр Ли стоит уже многие десятилетия.
+Она актуальна для физических приложений в coset-моделях конформной теории поля.
+Для вычисления коэффициентов ветвления, в отличие от проблемы нахождения кратностей весов, не существовало особенно эффективных алгоритмов.
 
@@
 % Результаты и положения, выносимые на защиту
+
 \resultssection
@@
 
+\vspace{-0.5cm}
 \nsection{Содержание работы}
-
+\vspace{-0.3cm}
 \textbf{Во Введении} обоснована актуальность диссертационной работы,
@@
 \textbf{Глава 1} носит обзорный характер.
-В ней мы даем аксиоматическую формулировку конформной теории поля, описываем модели Весса-Зумино-Новикова-Виттена и coset-модели.
-Затем мы демонстрируем роль аффинных алгебр в описании этих моделей и приводим основные понятия теории представлений, использующиеся в диссертации.
+В ней приводится аксиоматическая формулировка конформной теории поля, описываются ВЗНВ-модели и coset-модели.
+Затем демонстрируется роль аффинных алгебр в описании этих моделей и вводятся основные понятия теории представлений, использующиеся в диссертации.
 Мы указываем на то, что основные свойства интегрируемых модулей старшего веса определяются структурой сингулярного элемента, что выражается в формуле Вейля-Каца для формальных характеров.
@@
 
-\textbf{В главе 2} мы выводим основное рекуррентное соотношение на коэффициенты ветвления.
-Сначала мы доказываем лемму о разложении сингулярного элемента.
+\textbf{В главе 2} выводится основное рекуррентное соотношение на коэффициенты ветвления.
+Сначала доказывается лемма о разложении сингулярного элемента.
 Структура сингулярного элемента определяет свойства модуля алгебры Ли, поэтому разложение определяет правила ветвления и позволяет сформулировать рекуррентную процедуру редукции.
@@
 где $\Psi^{(\mu)}$ -- сингулярный элемент модуля, а $R=\prod_{\alpha\in \Delta^+}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}$ -- знаменатель Вейля.
+Здесь $\Delta^+$ -- множество положительных корней алгебры, а $\rho$ -- вектор Вейля.
 Сингулярный элемент определяется набором сингулярных весов модуля и имеет разный вид для разных типов модулей старшего веса.
-Например, $\Psi^{(\mu)}=\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}$ для неприводимых модулей.
+Например, $\Psi^{(\mu)}=\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}$ для неприводимых модулей ($W$ -- группа Вейля).
 Знаменатель  Вейля $R$ является универсальным объектом, характеризующим корневую систему алгебры Ли, а свойства модуля определяются сингулярным элементом.
@@
 Мы доказываем следующую лемму о разложении сингулярного элемента:
+\vspace{-0.3cm}
 \begin{lemma}
@@
 Пусть $\left( \af,\afb \right)$ -- ортогональная пара редуктивных подалгебр $\gf$ и  $\widetilde{\afb}=\afb\oplus \hf_{\perp }$, $\widetilde{\af}=\af\oplus\hf_{\perp }$ ,
-
 $L^{\mu }$ -- модуль старшего веса с сингулярным элементом $\Psi ^{\left(\mu \right)}$ ,
-
 $R_{\af_{\perp }}$ -- знаменатель Вейля для подалгебры $\af_{\perp }$.
-
 Тогда элемент  $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi _{\af}\left( \frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}\right) $ можно разложить в сумму по  $u\in U$ сингулярных весов $e^{\mu _{\af}\left( u\right) }$ с коэффициентами $\epsilon (u)\mathrm{\dim}\left( L_{\widetilde{\afb}}^{\mu _{\widetilde{\afb}}\left( u\right) }\right) $:
@@
 \end{lemma}
-
 Введем ``веер вложения'', который необходим для формулировки рекуррентных соотношений:
+\vspace{-0.5cm}
 \begin{definition}
@@
 $
-Упорядочение корней в  $\co{\Delta _{\af}}$ индуцирует естественное упорядочение весов в $P_{\af}$. Обозначим через $\gamma_{0}$ наименьший вектор $\Phi _{\af\subset \gf}$. Множество
-\begin{equation}
-\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
-\af\subset \gf}\right\} \setminus \left\{ 0\right\}
-\label{fan-defined}
-\end{equation}
+Упорядочение корней в  $\co{\Delta _{\af}}$ индуцирует естественное упорядочение весов в $P_{\af}$. Обозначим через $\gamma_{0}$ наименьший вектор $\Phi _{\af\subset \gf}$.
+
+Множество
+$\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \gf}\right\} \setminus \left\{ 0\right\}$
 называется  \textit{веером вложения}.
-\end{definition}
+\end{definition}\vspace{-0.3cm}
 Веер вложения универсален и зависит только от вложения $\af\to\gf$ и не зависит от модуля $L^{(\mu)}$.
@@
 
-Теперь мы можем сформулировать основную теорему, которая позволит нам рекуррентно вычислять коэффициенты ветвления.
-
+Теперь можно сформулировать основную теорему, которая позволяет рекуррентно вычислять коэффициенты ветвления.
+\vspace{-0.5cm}
 \begin{theorem}
@@
 \end{theorem}
-
 Далее мы анализируем пары $(\af,\afb)$ для простых алгебр Ли.
@@
 
-\textbf{В главе 3} мы используем  разложение сингулярного элемента, чтобы показать связь ветвления с (обобщенной) резольвентой Бернштейна-Гельфанда-Гельфанда.
+\textbf{В главе 3} мы используем  разложение сингулярного элемента, чтобы показать связь ветвления с (обобщенной) БГГ-резольвентой.
 Данные результаты опубликованы в работах \citemy{2011arXiv1102.1702L,2010LyakhovskyNazarovMQFT}.
@@
 Мы доказываем следующее утверждение, демонстрирующее, что разложение сингулярного элемента связано с разложением характера неприводимого модуля в комбинацию характеров обобщенных модулей Верма
+\vspace{-0.3cm}
 \begin{statement}
@@
 \end{statement}
-
-Связь редукции и (обобщенной) резольвенты Бернштейна-Гельфанда-Гельфанда дается следующим утверждением:
+\vspace{-0.3cm}
+Связь редукции и (обобщенной) резольвенты БГГ дается следующим утверждением:
+\vspace{-0.3cm}
 \begin{statement}
@@
 \end{statement}
-
+\vspace{-0.3cm}
 \textbf{Глава 4} посвящена сплинтам -- расщеплением корневой системы алгебры Ли в объединение образов корневых систем двух алгебр, не обязательно являющихся подалгебрами данной алгебры.
@@
 
+\vspace{-0.3cm}
 \begin{definition}
-Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$.Отображение $\phi :\left\{
+Пусть $\Delta _{0}$ и $\Delta$ -- корневые системы с соответствующими весовыми решетками $P_{0}$ и $P$. Отображение $\phi :\left\{
 \Delta _{0}\hookrightarrow \Delta , 
 P_{0}\hookrightarrow P
-\right\}.
+\right\}
 $ называется ``вложением'', если  $\phi$ вкладывает $\Delta _{0}$ в $\Delta $ и действует гомоморфно по отношению к группам сложения векторов в $P_{0}$ и $P$:
@@
 \end{definition}
-
+\vspace{-0.5cm}
 Вложение $\phi$ индуцирует вложение формальных алгебр: ${\mathcal{E}}_0\hookrightarrow \mathcal{E}$ и для образа ${\mathcal{E}}_i=\mathrm{Im}_{\phi}\left( {\mathcal{E}}_0\right)$ можно рассмотреть обратное отображение $\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
@@
 Верно следующее утверждение.
-
+\vspace{-0.3cm}
 \begin{statement}
@@
 \end{statement}
-
-В случае инъективного сплинта мы можем сказать, что подалгебра $\af\hookrightarrow \gf$ расщепляет $\Delta$.
+В случае инъективного сплинта можно сказать, что подалгебра $\af\hookrightarrow \gf$ расщепляет $\Delta$.
 Сплинты были классифицированы в работе \cite{richter2008splints}  (см.
@@
 Если выполнено техническое требование на структуру сингулярного элемента, то верно следующее свойство:
+\vspace{-0.3cm}
 \begin{Prop}
@@
 \end{Prop}
-
 Заключительная \textbf{глава 5} посвящена практическим приложениям результатов диссертации.
  В разделе 5.1 мы  описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
-Эти результаты были опубликованы нами в работах \citemy{NazarovJETPletters,2011arXiv1112.4354N}.
+Эти результаты были опубликованы в работах \citemy{NazarovJETPletters,2011arXiv1112.4354N}.
 
@@
 $
-называется {\it эволюцией Шрамма-Левнера} на верхней полуплоскости $\mathbb{H}$.
-Здесь $\xi_{t}$ -- Броуновское движение.
+называется {\it эволюцией Шрамма-Левнера} (SLE) на верхней полуплоскости $\mathbb{H}$.
+Здесь $\xi_{t}$ -- Броуновское движение, $\kappa$ -- параметр процесса.
 Динамика конца  $z_{t}$ критической кривой $\gamma_{t}$ (конец следа эволюции Шрамма-Левнера) описывается уравнением $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
@@
 После фиксации  $A$-калибровки останется  $G/A$ калибровочная инвариантность.
-Поэтому мы должны добавить случайные калибровочные преобразования к эволюции Шрамма-Левнера.
+Поэтому надо добавить случайные калибровочные преобразования к эволюции Шрамма-Левнера.
 Обозначим через $t^{a}_{i}$ ($\tilde{t}^{b}_{i}$) генераторы представления алгебры $\gf$ (соответственно, представления $\af$), соответствующего примарному полю $\varphi_{i}$.
@@
 Исследуем, что происходит с наблюдаемыми при эволюции следа SLE $\gamma_{t}$ с момента   $t$ до $t+ dt$. 
-Через  $\mathcal{G}_{i}$ мы обозначили  генераторы инфинитезимальных преобразований примарных полей $\varphi_{i}$:$d\varphi_{i}(w_{i}) = \mathcal{G}_{i}\varphi_{i}(w_{i})$.
+Пусть  $\mathcal{G}_{i}$ --  генераторы инфинитезимальных преобразований примарных полей $\varphi_{i}$:$d\varphi_{i}(w_{i}) = \mathcal{G}_{i}\varphi_{i}(w_{i})$.
 Нормируем дополнительное $\left(\dim\gf\right)$-мерное Броуновское движение следующим образом: $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$.
@@
 Действуя повышающими операторами мы получаем соотношения, связывающие параметры стохастического процесса и coset-модели конформной теории поля:
-\begin{eqnarray}
+\begin{equation}
 \label{eq:185}
+\begin{array}{l}
  (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0\\
@@
 (C_{\mu}-\tilde{C}_{\nu})=0,
-\end{eqnarray}
+\end{array}
+\end{equation}
 здесь $C_{\mu}=(\mu,\mu+2\rho)$ и $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ -- собственные значения квадратичных операторов Казимира $\sum_{a}t^{a}t^{a}$ и $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ алгебр Ли $\gf$ и $\af$.
 Из уравнения \eqref{eq:185} мы сразу получаем значения  $\kappa,\tau$ для каждой пары весов $(\mu,\nu)$ алгебр $\gf$ и $\af$.
-Для coset-реализаций минимальных и парафермионных моделей эти результаты совпадают со значениями, полученными в работе \cite{santachiara2008sle} путем введения стохастического процесса с дополнительным дискретным случайным блужданием.
+Для coset-реализаций минимальных и парафермионных моделей эти результаты совпадают со значениями, полученными в работе \cite{santachiara2008sle} путем введения стохастического процесса с дискретным случайным блужданием.
 
-Остальная часть главы представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли и реализованного с использованием методов диссертации.
-Вычислительным методам посвящены наши работы \citemy{2011arXiv1107.4681N,NazarovACSM2009,Nazarov2008}.
-\vspace{-0.5cm}
+Остальная часть главы представляет собой описание пакета {\bf Affine.m}, предназначенного для вычислений в теории представлений аффинных и конечномерных алгебр Ли и реализующего предложенные в диссертации методы.
+Вычислительным методам посвящены работы \citemy{2011arXiv1107.4681N,NazarovACSM2009,Nazarov2008}.
+\vspace{-0.7cm}
+%\thispage
 %%  
@@
 % ----------------------------------------------------------------
+\setlength{\parskip}{-0.5ex}
 \renewcommand\bibsection{\nsection{Список публикаций}}

### 2012-10-13 AffineLieAlgebras/MQFT2012/paper.tex
New paper on vertex operator algebras

--- 2012-03-03 AffineLieAlgebras/Splints/paper2.tex
@@
 \documentclass[12pt]{article}
- \textheight=24cm
- \textwidth=16.5cm
- \topmargin=-1.5cm
- \oddsidemargin=-0.25cm
-
 \usepackage{amsfonts}
@@
 \begin{document}
-\title{On affine extension of splint root systems}
+\title{On singular elements in conformal field theory. \\ Singular elements in vertex operator algebras}
 
@@
 \begin{abstract}
-Splint of root system of simple Lie algebra appears naturally in
-the study of (regular) embeddings of reductive subalgebras. It can
-be used to derive branching rules. Application of
-splint properties drastically simplifies calculations of
-branching coefficients. We study affine extension of splint root system of simple Lie algebra and obtain relations on theta and branching functions.
+  We consider singular elements of simple finite-dimensional and affine Lie algebra modules. We
+  construct corresponding vertex operator algebras. We consider decompositions of singular elements
+  connected with branching, splints and parabolic Verma modules and describe vertex counterparts. 
 \end{abstract}
@@
 \section{Introduction}
-\label{sec:introduction}
-
-The term {\it splint} was introduced by D. Richter in \cite{richter2008splints} where the
-classification of splints for simple Lie algebras was obtained. The fan $\Gamma \subset \Delta$ was
-introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent properties of
-branching coefficients for maximal embeddings. Injection fan is an efficient tool to study branching
-rules. Later this construction was generalized to non-maximal embeddings and affine Lie algebras in
-\cite{2010arXiv1007.0318L, ilyin812pbc}. In paper \cite{2011arXiv1111.6787L} we have shown that the
-existence of a splint for a root system of a simple Lie algebra leads to simplifications in
-reduction procedures of a Lie algebra module to modules of a subalgebra. This effect is based on the
-injection fan and singular element properties of Lie algebra modules.
-
-In the present note we discuss possible applications of splint in
-a root system of simple Lie algebra related to representation
-theory of affine Lie algebras. We discuss the structure of
-injection fan for affine Lie algebras and show that it admits a
-decomposition similar to that used in \cite{2011arXiv1111.6787L}
-for simple Lie algebras. Such a decomposition leads to equations
-for theta-functions. We study graded branching of affine Lie
-algebra modules reduced to a finite-dimensional subalgebra and
-discuss consequences of splint in this case.
-
-\section{Splints and affine Lie algebras}
-\label{sec:definitions}
-
-Consider simple Lie algebra $\gf$ with a root system $\Delta$. Let
-$\af_{1}\subset \gf$ be its reductive subalgebra of the same rank, such that
-$\Delta_{\af}\equiv\Delta_{1}\subset\Delta$ and $Q_{\af}\subset Q$, where $Q$ is the root lattice. Irreducible highest-weight modules of
-$\gf$ and $\af$ are denoted by $L^{\mu}$ and $L^{\nu}_{\af}$
-correspondingly. Weyl character formula for irreducible modules is
-$\mathrm{ch}L^{\mu}=\frac{\Psi^{(\mu)}}{\prod_{\alpha\in\Delta}(1-e^{-\alpha})}$,
-where $\Psi^{(\mu)}=\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}$
-is a singular element of the module and $W$ -- the Weyl group of
-$\gf$. Formal character of irreducible module admits a
-decomposition
-\begin{equation}
-  \label{eq:4}
-  \mathrm{ch} L^{\mu}=\sum_{\nu\in P_{\af}} b^{\mu}_{\nu} \mathrm{ch} L^{\nu}_{\af},
-\end{equation}
-where $P$, $P_{\af}$ are weight lattices of $\gf$ and $\af$. We
-want to study affine extension of this situation:
-$\gf\subset\gfh,\; \af\subset\afh$, $\afh\subset\gfh$,
-$\hat{\Delta}\subset\hat{\Delta}$ and
-$\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{\hat{\nu}}
-b^{\hat{\mu}}_{\hat{\nu}} \mathrm{ch} L^{\hat{\nu}}_{\afh}$. For
-weights of an affine Lie algebra $\gfh$ we have
-$\hat{\mu}=(\mu,k,n)$, where $\mu$ is a weight of $\gf$, $k$ --
-the level of the module and $n$ -- the grade of the weight
-$\hat{\mu}$
-
-\begin{Def}
-  Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a bijective map of
-  roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with vector composition law
-  in $\Delta_{1}$ and $\Delta$.
-\begin{equation*}
-\phi:\Delta_1 \longrightarrow \Delta, \quad \phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,\,\,\, \alpha,\beta \in \Delta_1
-\end{equation*}
-\end{Def}
-
-Note that the image $Im(\phi)$ must not inherit the root system properties except the addition rules
-equivalent to the addition rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and
-$\phi_2$ can splinter $\Delta$ when the latter can be presented as a disjoint union of images
-$Im(\phi_1)$ and $Im(\phi_2)$.
-
-$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
-\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
-_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
-\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
-
-\begin{Def}
-  A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if there are two embeddings
-  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
-  \phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the disjoint union of the
-  images of $\phi _{1}$ and $\phi _{2}$ and (b) neither the rank of $\Delta _{1}$ nor the rank of
-  $\Delta _{2}$ exceeds the rank of $%
-  \Delta $.
-\end{Def}
-
-It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote
-this by $\Delta \approx (\Delta_1,\Delta_2)$. Each component $\Delta_1$ and $\Delta_2$ is a "stem''
-of the splint.
-
-We consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem. As shown in paper \cite{2011arXiv1111.6787L} the second stem $\Delta _{\frak{s}}:=\Delta
-_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product
-$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}$
-and it defines an injection fan $\Gamma _{\frak{a}%
-\hookrightarrow \frak{g}}$ \cite{lyakhovsky1996rra,ilyin812pbc,2010arXiv1007.0318L}.
-
-Since the singular element of $L^{\mu}$ can be
-written as $\Psi _{\frak{g}}^{\left( \mu \right) }=e^{-\rho }
-\sum_{w\in W_{\frak{a}}}\epsilon \left( w \right) w\circ \left(
-e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho
-_{\frak{s}}}\right)$  for branching coefficients we get the
-identity \cite{2011arXiv1111.6787L}:
-\begin{equation}
-  \label{eq:9}
-b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
-}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}  
-\end{equation}
-Here the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $, they have the
-same Dynkin numbers: $\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
-m_{k}\omega_{(\sfr) k} . \label{new h weight}$ So branching coefficients coincide with weight
-multiplicities of $\sfr$-modules.
-
-Now we consider affine extension of this setup, $\afh\subset\gfh$. Since $\mathrm{rank}\gf\leq
-\mathrm{rank} \af+\mathrm{rank}\sfr$ for Weyl denominators we get
- \[
-\prod_{\alpha\in\hat{\Delta}^{+}_{1}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}\prod_{\beta\in\hat{\Delta}^{+}_{2}}(1-e^{\phi\circ \beta})^{\mathrm{mult}(\beta)}=\prod_{\gamma\in\hat{\Delta}^{+}}(1-e^{-\gamma})^{\mathrm{mult}(\gamma)}\prod_{n=0}^{\infty}(1-e^{-n\delta})^{\mathrm{rank}\af+\mathrm{rank}\sfr-\mathrm{rank}\gf}
-\]
-
-Using a specialization
-\cite{kac1988modular,kac1984infinite,kac1990idl} and the
-definition of Dedekind eta-function
-$\eta(\tau)=q^{1/24}\prod_{n=1}^{\infty}(1-q^{n})$, where
-$q=e^{2\pi i \tau}$ we can rewrite this identity as the relation
-imposed on theta-functions $\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in Q_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$:
-\begin{multline}
-  \label{eq:5}
-  \eta(\tau)^{\mathrm{dim}(\af)}\prod_{\alpha\in\Delta_{1}^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z)}{\eta(\tau)} \eta(\tau)^{\mathrm{dim}(\sfr)}\prod_{\beta\in\Delta_{2}^{+}}\frac{\Theta^{(\hat A_{1})}_{\phi\circ \beta}(\tau,z))}{\eta(\tau)}=\\
-\eta(\tau)^{\mathrm{rank}(\af)+\mathrm{rank}(\sfr)-\mathrm{rank}(\gf)}
-\eta(\tau)^{\mathrm{dim}(\gf)}\prod_{\alpha\in\Delta^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z))}{\eta(\tau)}
-\end{multline}
-Here $z\in P_{\geq 0}\otimes \mathbb{C}$. Using Weyl denominator identity this relation can be
-rewritten as a non-trivial relation connecting theta-functions of algebras $\gfh,\hat\sfr,\afh$:
-\begin{equation}
-  \label{eq:6}
-  \left(\sum_{v\in W_{\af}}\epsilon(v) \Theta^{(\afh)}_{v\rho_{\af}}(\tau,z)\right)
-  \cdot \left(\sum_{u\in W_{\sfr}}\epsilon(u) \Theta^{(\hat{\sfr})}_{\phi\circ(u\rho_{\sfr})}(\tau,z)\right)= 
-  \left(\sum_{w\in W}\epsilon(w) \Theta^{(\gfh)}_{w\rho_{\gf}}(\tau,z)\right)
-\end{equation}
-%Now we can use Weyl denominator identity $e^{-\rho}\prod_{\alpha\in \hat{\Delta}^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}=\sum_{w\in \hat{W}}\det(w)e^{w\rho}$
-
-Now consider the branching of $\gfh$-module to $\gf$-modules. For
-formal characters we can write the following expression:
-\begin{equation}
-  \label{eq:8}
-\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{\nu}(n) \mathrm{ch} L^{\nu}_{\gf}.
-\end{equation}
-Rewriting this equation for weight multiplicities we get
-$m^{(\hat{\mu})}_{\hat{\nu}=(\nu,k,n)}=\sum_{\xi\in P}
-b^{(\hat{\mu})}_{\xi}(n) m^{(\xi)}_{\nu}$. We can introduce
-branching functions similarly to the case of branching for affine
-subalgebra \cite{kac1988modular,kac1990idl}:
-$b^{(\hat{\mu})}_{\nu}(q)=\sum_{n=0}^{\infty}
-b^{(\hat{\mu})}_{\nu}(n) q^{n}$.
-These branching functions are connected to $q$-dimension of module $\mathrm{dim}_{q}L^{\hat \mu}_{\gfh}=\sum_{n=0}^{\infty}q^{n}\sum_{\nu\in P} b^{(\hat \mu)}_{\nu}(n) \mathrm{dim }L^{\nu}_{\gf}=\sum_{\nu\in P}b^{(\hat\mu)}_{\nu}(q) \mathrm{dim} L^{\nu}_{\gf}$.
-It is well-known that $q$-dimension is a modular function for some $\Gamma\subset SL_{2}(\mathbb{Z})$  \cite{gannon2006moonshine}, so branching functions $b^{(\hat \mu)}_{\nu}(q)$ have modular properties.
-
- For string functions of a module
-$L^{\hat{\mu}}$ we have
-\begin{equation}
-  \label{eq:7}
-   \sigma^{(\hat{\mu})}_{\nu}(q) = \sum_{\xi\in P} m^{(\xi)}_{\nu} b^{(\hat{\mu})}_{\xi}(q).
-\end{equation}
-
-Introduce an ordering of the set of weights $\xi$ as follows:
-attribute to a weight $(\rho,\xi)$ its product $(\rho,\xi)$ with
-the Weyl vector $\rho$. Then relation \eqref{eq:7} can be written
-in the matrix form $\sigma(q)=M b(q)$ or as an inverse relation
-$b(q)=M^{-1}\sigma(q)$. Here $\sigma(q)$ and $b(q)$ are infinite
-columns of string and branching functions. Matrix $M$ contains
-multiplicities of weights in $\gf$-modules similar to that of
-Table 1 in paper \cite{2010arXiv1001}. The inverse matrix $M^{-1}$
-encodes recurrent relations imposed weight multiplicities
-\cite{il2010folded}.
-
-Now consider the branching of $\gfh$-modules in $\af$-modules and
-assume the existence of a splint
-$\Delta^{+}_{\gf}=\Delta^{+}_{\af}\cup \phi(\Delta^{+}_{\sfr})$.
-We decompose $\gf$-modules in equation \eqref{eq:8} into
-$\af$-modules using property \eqref{eq:9}:
-\begin{multline}
-  \label{eq:10}
-  \mathrm{ch}L^{\hat{\mu}}_{\gfh}=
-\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P_{\af}} b^{(\hat{\mu})}_{(\gfh\downarrow\af)\nu}(n) \mathrm{ch} L^{\nu}_{\af}=
-\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} b^{(\nu)}_{(\gf\downarrow \af) \xi}\mathrm{ch} L^{\xi}_{\af}=\\
-=\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} M^{\widetilde{\nu}}_{  \widetilde{\nu}-\phi^{-1}( \nu-\xi )}\mathrm{ch} L^{\xi}_{\af}
-\end{multline}
-We see that the similar matrix relation holds for branching
-functions $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}\;
-b_{(\gfh\downarrow\gf)}(q)$ and we can write
-$\sigma(q)=M_{\af}\; b_{(\gfh\downarrow\af)}(q)$. So if we know
-branching coefficients for the embedding $\gf\subset\gfh$ (for
-example, see book \cite{kass1990ala}) we can easily obtain
-branching functions for the embedding $\af\subset \gfh$.
-\section*{Conclusion}
-\label{sec:conclusion} We have demonstrated that splint in affine
-Lie algebras leads to new relations between theta-functions and
-branching functions for branching to finite-dimensional
-subalgebras, which can be useful for computations. Further
-question is to generalize this analysis to affine subalgebras and
-to apply the results to branching in the study of CFT coset
-models.
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-Anton Nazarov thanks the Chebyshev Laboratory (Department of Mathematics and Mechanics,
-Saint-Petersburg State University) for support under the grant 11.G34.31.0026
-of the Government of Russian Federation.
-
-\bibliography{bibliography}{}
-\bibliographystyle{utphys}
-
+\begin{itemize}
+\item Singular element of simple Lie algebra irreducible module, VOA corresponding to that module.
+  What are the relations in VOA on singular vectors? Is there BGG-resolution?
+\item Affine Lie algebra, parabolic Verma modules?
+\item Splints?
+\item Coset vertex operator algebras and branching
+\end{itemize}
 \end{document}

### 2012-10-15 AffineLieAlgebras/Thesis/common.tex
Minor changes in synopsis, some misprints fixed.

@@
 Изучение структуры сингулярных элементов существенно упрощает поиск операторов смены граничных условий.
-Построена модель обобщеннного стохастического процесса Шрамма-Лёвнера для систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля и показано, что такое обобщение совместно с coset-реализацией минимальных моделей.
+Построена модель обобщенного стохастического процесса Шрамма-Лёвнера для систем с калибровочной инвариантностью, соответствующих coset-моделям конформной теории поля и показано, что такое обобщение совместно с coset-реализацией минимальных моделей.
 %\item Продемонстрирована роль сингулярных элементов в построении мартингалов стохастического процесса Шрамма-Лёвнера, то есть проиллюстрировано применение алгебраических методов теории представлений аффинных алгебр Ли в изучении критического поведения в двумерных решеточных моделях

### 2012-10-15 AffineLieAlgebras/Thesis/concl.tex
Minor changes in synopsis, some misprints fixed.

@@
 При этом возникают квантовые теории поля типа аффинной теории Тоды, в которых алгебраическая структура частично сохраняется и теория представлений аффинных алгебр Ли остается важным инструментом.
-Кроме того, может быть расширена и область применения пакет {\bf Affine.m}, в частности, планируется улучшение интерфейса и непосредственная поддержка вычисления коэффициентов разложения тензорных произведений представлений на неприводимые.
+Кроме того, может быть расширена и область применения пакета {\bf Affine.m}, в частности, планируется улучшение интерфейса и непосредственная поддержка вычисления коэффициентов разложения тензорных произведений представлений на неприводимые.
 

### 2012-10-19 AffineLieAlgebras/Thesis/autoref.tex
Minor changes in synopsis, some misprints fixed.
Minor autoref changes

@@
                        & & \emph{Санкт-Петербургское   отделение
-Математического   института   им.  В.А. Стеклова   РАН, главный научный сотрудник, заведующий 
+Математического   института   им.  В.А. Стеклова   РАН, заведующий 
 лаборатории математических проблем физики}; \\
@@
 диссертационного совета,%\\
-%\emph{д.ф.-м.н.}%, \emph{ученое звание}%
+ д.ф.-м.н.%, \emph{ученое звание}%
 \hfill
@@
 \nsection{Общая характеристика работы}
-
+\vspace{-0.5cm}
 % Актуальность работы
@@
 Подсистема  $\Delta _{\af_{\perp }}$ определяет подалгебру $\af_{\perp }$ с подалгеброй Картана $\hf_{\afb}$.
+
 Пусть
@@
 }|\forall h \in \hf_{\af\oplus \af_{\perp}}; \eta \left( h \right)=0 \right\}$, тогда имеет место разложение подалгебры Картана $\hf=\frak{\hf_{\af}}\oplus \hf_{\afb}\oplus\hf_{\perp }$.
-
 Для подалгебр из ортогональной пары  $\left( \af,\afb\right) $ рассмотрим соответствующие векторы Вейля $\rho _{\af}$ и $\rho _{\af_{\perp }}$, и образуем так называемые  ``дефекты'' вложения $\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho$, $\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi_{\afb}\rho$.
@@
 $
-Упорядочение корней в  $\co{\Delta _{\af}}$ индуцирует естественное упорядочение весов в $P_{\af}$. Обозначим через $\gamma_{0}$ наименьший вектор $\Phi _{\af\subset \gf}$.
+Упорядочение корней в  $\Delta _{\af}$ индуцирует естественное упорядочение весов в $P_{\af}$. Обозначим через $\gamma_{0}$ наименьший вектор $\Phi _{\af\subset \gf}$.
 
@@
 Заключительная \textbf{глава 5} посвящена практическим приложениям результатов диссертации.
- В разделе 5.1 мы  описываем применение алгебраических методов к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
-Эти результаты были опубликованы в работах \citemy{NazarovJETPletters,2011arXiv1112.4354N}.
+ В разделе 5.1 мы примененяем алгебраические методы к проблеме поиска соответствия между квантовополевым и решеточным описанием критического поведения.
+Результаты опубликованы в работах \citemy{NazarovJETPletters,2011arXiv1112.4354N}.
 
-Стохастический процесс, который удовлетворяет уравнению 
+Стохастический процесс, удовлетворяющий уравнению 
 $
@@
 \label{eq:178}
-      S=
--\frac{k}{4\pi}\left[ \frac{1}{2} \int_{S^2} d^2x\; {\cal K} (\gamma^{-1}\partial^{\mu}\gamma,\gamma^{-1}\partial_{\mu}\gamma)-
- \frac{1 }{6} \int_{B}\epsilon_{ijk} {\cal K}\left(
+\hspace{-0.5cm}      S=
+-\frac{k}{8\pi}\left[ \int_{S^2} d^2x\; {\cal K} (\gamma^{-1}\partial^{\mu}\gamma,\gamma^{-1}\partial_{\mu}\gamma)-
+ \frac{1 }{3} \int_{B}\epsilon_{ijk} {\cal K}\left(
     \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^i},
       \left[\tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^j}
-      \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^k}\right]\right) d^3y+\right.\\
+      \tilde \gamma^{-1}\frac{\partial \tilde \gamma}{\partial y^k}\right]\right) d^3y\right.\\
 \left.+
- \int_{S^2} d^{2}z \left(\mathcal{K}(\alpha, \gamma^{-1}\bar \partial \gamma)-\mathcal{K}(\bar \alpha, (\partial \gamma ) \gamma^{-1})\right.
+2 \int_{S^2} d^{2}z \left(\mathcal{K}(\alpha, \gamma^{-1}\bar \partial \gamma)-\mathcal{K}(\bar \alpha, (\partial \gamma ) \gamma^{-1})\right.
       \left.+\mathcal{K}(\alpha,\gamma^{-1}\bar \alpha \gamma)-\mathcal{K}(\alpha,\bar \alpha)\right)\right].

### 2012-10-19 GeneralOverview/Lectures/CFT-APTU-2011.tex
Some misprints fixed
Misprints
Minor autoref changes

@@
   \label{eq:9}
-  \Gamma(i-j)=\left<\sigma_i-\sigma_j\right>.
+  \Gamma(i-j)=\left<\sigma_i\sigma_j\right>.
 \end{equation}
@@
   \label{eq:120}
-  \Sigma=\sum_{s=0}^{\infty}\frac{1}{s!}\sum_{l_1\dots l_s=1}^{\infty} \kappa^{l_1+\dots+l_s}F^{(1)}_{l_1} \dots F^{(1)}_{l_s}=
-  \sum_{s=0}^{\infty}\frac{1}{s!}\left(\sum_{l=1}^{\infty} \kappa^{l}F^{(1)}_{l} \right)^s =\exp\left(-\sum_{l=1}^{\infty} \kappa^l F_l\right)
+  \Sigma=\sum_{s=0}^{\infty}\frac{(-1)^s}{s!}\sum_{l_1\dots l_s=1}^{\infty} \kappa^{l_1+\dots+l_s}F^{(1)}_{l_1} \dots F^{(1)}_{l_s}=
+  \sum_{s=0}^{\infty}\frac{(-1)^s}{s!}\left(\sum_{l=1}^{\infty} \kappa^{l}F^{(1)}_{l} \right)^s =\exp\left(-\sum_{l=1}^{\infty} \kappa^l F_l\right)
 \end{equation}
@@
   \label{eq:38}
-  c=-T\left.\frac{\partial^2 f}{\partial T^2}\right|_{h=0}=-\frac{1}{T_c}t^{\frac{1}{a-2}}g''(0)
+  c=-T\left.\frac{\partial^2 f}{\partial T^2}\right|_{h=0}=-\frac{1}{T_c}t^{\frac{1}{a}-2}g''(0)
 \end{equation}
@@
 \end{equation}
-$R$ - нормировочный множитель, который выбирается так, чтобы блочный спин мог принимать значения $\pm 1$. Если бы спины были всегда в одном направлении, то $R$ имел бы значение $r^d$.
+Здесь $R$ - некоторый нормировочный множитель, который мы скоро вычислим.
+% выбирается так, чтобы блочный спин мог принимать значения $\pm 1$. Если бы спины были всегда в одном направлении, то $R$ имел бы значение $r^d$.
 
@@
 \end{equation}
-Таким образом, критические индексы получаются из собственных значений линеаризованной ренормгруппы в фиксированной точки.
+Таким образом, критические индексы получаются из собственных значений линеаризованной ренормгруппы в фиксированной точке.
 
@@
   \label{eq:89}
-  \delta\langle X\rangle=dl \left(\sum_k (x_k^{\mu}\partial_{\mu}^k+d[A_k])\langle X\rangle-\int d^d y \Theta(y)\right)
+  \delta\langle X\rangle=dl \left(\sum_k (x_k^{\mu}\partial_{\mu}^k+d[A_k])\langle X\rangle-\int d^d y \langle\Theta(y)X\rangle\right)
 \end{equation}
@@
   e^{i x^{\rho}P_{\rho}}D e^{-i x^{\rho}P_{\rho}}=D+x^{\nu}P_{\nu}\\
-  e^{i x^{\rho}P_{\rho}}K_{\mu} e^{-i x^{\rho}P_{\rho}}=K_{\mu}+2x_{\mu}D -2 x^{\nu}L_{\mu\nu}+2x_{\mu}(x^{\nu}P_{\nu})-x^{2 P_{\mu}}
+  e^{i x^{\rho}P_{\rho}}K_{\mu} e^{-i x^{\rho}P_{\rho}}=K_{\mu}+2x_{\mu}D -2 x^{\nu}L_{\mu\nu}+2x_{\mu}(x^{\nu}P_{\nu})-x^{2} P_{\mu}
 \end{eqnarray}
@@
   \label{eq:189}
-  \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}=\frac{C_{12}(\gamma_{1}\gamma_{2})^{(\Delta_{1}+\Delta_{2})/2}}{\gamma_{1}^{\Delta_{1}}\gamma_{2}^{\Delta_{2}} \left|x_{1}-x_{2}\right|}.
+  \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}=\frac{C_{12}(\gamma_{1}\gamma_{2})^{(\Delta_{1}+\Delta_{2})/2}}{\gamma_{1}^{\Delta_{1}}\gamma_{2}^{\Delta_{2}} \left|x_{1}-x_{2}\right|^{\Delta_1+\Delta_2}}.
 \end{equation}
@@
   2\pi \partial \langle T_{\bar z z } X\rangle +2\pi \bar \partial \langle T_{zz}X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X \rangle\\
-  2\pi \partial \langle T_{\bar z \bar z } X\rangle +2\pi \bar \partial \langle T_{z\bar z}X\rangle = -\sum_{i} \bar \partial \frac{1}{\bar z-w_{i}} \partial_{\bar w_{i}} \langle X \rangle\\
+  2\pi \partial \langle T_{\bar z \bar z } X\rangle +2\pi \bar \partial \langle T_{z\bar z}X\rangle = -\sum_{i} \bar \partial \frac{1}{\bar z-\bar w_{i}} \partial_{\bar w_{i}} \langle X \rangle\\
   2 \langle T_{z\bar z} X\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) \Delta_{i} \langle X\rangle\\
-  -2 \langle T_{z\bar z} X\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) s_{i} \langle X\rangle\\
+  -2 \langle T_{z\bar z} X\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) s_{i} \langle X\rangle
 \end{eqnarray}
@@
   \label{eq:311}
-  a=-\frac{3}{2}(2h+1)
+  a=-\frac{3}{2(2h+1)}
 \end{equation}

### 2012-11-17 AffineLieAlgebras/MQFT2012/paper.tex
Minor changes
Definition of vertex operator algebra.
Started the paper

@@
 \section{Introduction}
+The notion of vertex operator algebra \cite{borcherds1986vertex} formalizes
+algebraic structure that underlies two-dimensional conformal field theory
+\cite{kac1998vertex,frenkel1988vertex}. Vertex algebras associated to
+representations of affine Lie algebras \cite{frenkel1992vertex} form an
+important class corresponding to Wess-Zumino-Novikov-Witten
+\cite{witten1984nab,Walton:1999xc} and coset models \cite{Goddard198588} of
+conformal field theory.
+
+We show that recurrent relations on branching coefficients for affine Lie
+algebra modules are related to the structure of Virasoro modules.
+
+We study singular elements of affine Lie algebra modules and establish the properties
+of
+
 \begin{itemize}
@@
 \end{itemize}
+
+\begin{Def}
+  Vertex algebra: $V$ -- vector space with identity $1$, endomorphism
+  $T:V\to V$ and linear multiplication map $Y:V\otimes V\to V((z)):
+  (a,b)\to Y(a,z)b=\sum_n a_n b z^{-n-1}$,
+  such that
+  \begin{itemize}
+  \item {\it Identity} $\forall a\in V, Y(1,z) a =a$ and $Y(a,z) 1 \in a+z V z$
+  \item {\it Translation} $T(1)=0$ and $\forall a,b\in V$:
+    $$Y(a,z)T b - T Y(a,z) b =
+    \frac{d}{dz} Y(a,z) b$$
+  \item {\it Four point function}. $\forall a,b,c\in V \exists
+    X(a,b,c;z,w)\in V[[z,w]][z^{-1},w^{-1},(z-w)^{-1}]: Y(a,z)Y(b,w)c,
+    Y(b,w)Y(a,z)c, Y(Y(a,z-w)b,w)c$ are expansions of $X(a,b,c;z,w)$
+    in $V((z))((w)), V((w))((z)), V((w))((z-w))$
+  \item {\it Grading} $V=\bigoplus_{n=0}^{\infty} V_n$
+  \item {\it Virasoro element} $\omega\in V_2: Y(w,z)=\sum_{n\in
+      \mathbb{Z}} L_n z^{-n-2}$ satisfies $\forall a\in V_n$ the
+      relations $L_0 a =n a$,
+      $Y(L_{-1}a,z)=\frac{d}{dz}Y(a,z)=[Y(a,z),T]$,
+      $[L_m,L_n]a=(m-n)L_{m+n} a + \delta_{m+n,0} \frac{m^3 -
+        m}{12}ca$, $c$ -- central charge.
+  \end{itemize}
+
+\end{Def}
+
+\bibliography{bibliography}{}
+\bibliographystyle{utphys}
+
 \end{document}

### 2012-11-27 AffineLieAlgebras/MQFT2012/paper.tex
Some work on thesis presentation and on paper about vertex operator algebras

--- 2012-10-13 AffineLieAlgebras/MQFT2012/paper.tex
@@
 \section{Introduction}
+The notion of vertex operator algebra \cite{borcherds1986vertex} formalizes algebraic structure that
+underlies two-dimensional conformal field theory \cite{kac1998vertex,frenkel1988vertex}. Vertex
+algebras associated to representations of affine Lie algebras \cite{frenkel1992vertex} form an
+important class corresponding to Wess-Zumino-Novikov-Witten \cite{witten1984nab,Walton:1999xc} and
+coset models \cite{Goddard198588} of conformal field theory. These vertex algebras are used to
+reveal modular properties of formal characters of affine Lie algebra modules \cite{zhu1996modular}.
+
+In present paper we consider vertex operator algebras corresponding to coset models of conformal
+field theory. Properties of these algebras are connected with the problem of reduction of affine Lie
+algebra module into the sum of affine Lie subalgebra modules.
+
+We demonstrate that recurrent relations on branching coefficients for affine Lie algebra modules are
+related to the structure of Virasoro modules. Our method is based upon the structure of singular
+elements of affine Lie algebra modules.
+
+\section{Vertex operator algebra for coset models}
+\label{sec:vert-oper-algebra}
+
+Recall the definition of vertex operator algebra \cite{borcherds1986vertex,kac1998vertex,frenkel2001vertex,frenkel1988vertex}.
+\begin{Def}
+  Vertex algebra is a  vector space $V$ with identity $1$, equipped with an endomorphism
+  $T:V\to V$ and a linear multiplication map $Y:V\otimes V\to V((z)):
+  (a,b)\to Y(a,z)b=\sum_n a_n b z^{-n-1}$,
+  such that following relations are satisfied:
+  \begin{itemize}
+  \item {\it Identity} $\forall a\in V, Y(1,z) a =a$ and $Y(a,z) 1 \in a+z V z$
+  \item {\it Translation} $T(1)=0$ and $\forall a,b\in V$:
+    $$Y(a,z)T b - T Y(a,z) b =
+    \frac{d}{dz} Y(a,z) b$$
+  \item {\it Four point function}. $\forall a,b,c\in V \exists
+    X(a,b,c;z,w)\in V[[z,w]][z^{-1},w^{-1},(z-w)^{-1}]: Y(a,z)Y(b,w)c,
+    Y(b,w)Y(a,z)c, Y(Y(a,z-w)b,w)c$ are expansions of $X(a,b,c;z,w)$
+    in $V((z))((w)), V((w))((z)), V((w))((z-w))$
+  \item {\it Grading} $V=\bigoplus_{n=0}^{\infty} V_n$
+  \item {\it Virasoro element} $\omega\in V_2: Y(w,z)=\sum_{n\in
+      \mathbb{Z}} L_n z^{-n-2}$ satisfies $\forall a\in V_n$ the
+      relations $L_0 a =n a$,
+      $Y(L_{-1}a,z)=\frac{d}{dz}Y(a,z)=[Y(a,z),T]$,
+      $[L_m,L_n]a=(m-n)L_{m+n} a + \delta_{m+n,0} \frac{m^3 -
+        m}{12}ca$, $c$ -- central charge.
+  \end{itemize}
+
+\end{Def}
+
+Consider affine Lie algebra $\gfh$, which is an affine extension of (semi)simple Lie algebra $\gf$.
+Let $\omega_{0},\dots,\omega_{r}$ be fundamental weights of $\gfh$. Then $L^{k\omega_{0}}_{\gfh}$ is vertex operator algebra and its irreducible modules are $L^{\mu}_{\gfh}$ such that $\mu<k$.
+
 \begin{itemize}
@@
 \end{itemize}
+
+\bibliography{bibliography}{}
+\bibliographystyle{utphys}
+
 \end{document}

### 2012-11-28 AffineLieAlgebras/MQFT2012/paper.tex
Some changes in presentation for defence and in vertex algebra paper.

@@
 
+In this case Virasoro element is  $\omega=\frac{1}{2(k+h^{\vee})}\sum_i u_i(-1) u_i(-1)$, where
+$u_i (i=1,\dots,\mathrm{dim}\gf)$  is an orthogonal basis in $\gfh$ w.r.t. Cartan-Killing form.
+
+Vertex operator algebra structure for coset models of conformal field theory is given by the following statements \cite{frenkel1992vertex}:
+\begin{statement}
+\label{thm:cosets}
+Let  $V=\bigoplus_{n=0}^{\infty} V_n$ -- vertex operator algebra such that $\mathrm{dim}V_0=1$ and $W\subset V$ is a subalgebra, denote by $\omega,\omega_1$ Virasoro elements of  $V$ and $W$ correspondingly.
+If the condition  $L_1\omega_1 =0$ is satisfied then $W'=\{b:
+  a(n)b=0 \forall n\geq 0, a\in W\}$ is vertex operator subalgebra of  $V$ with Virasoro element $\omega'=\omega-\omega_1$.
+\end{statement}
+Note that for $\af\subset\gf$ and $V=L^0_{(\gf)}k, W=L^0_{(\af)k}$ the algebra
+$W'$ is vertex operator algebra of  $G/A$-coset-model.
+
+The algebra  $W'$ is called {\it commutant} of $W$ and denoted as $\mathrm{Com}(W)\equiv W'$.
+\begin{statement}
+  If the conditions of previous statement are satisfied and  $Y(\omega_1,z)=\sum_n
+  L_{(1)n} z^{-n-2}$ then $\mathrm{Com}(W)=\{b: L_{(1)-1}b=0\}$. 
+\end{statement}
+
 \begin{itemize}

### 2012-12-05 AffineLieAlgebras/Thesis/talk-defence.tex
Talk text started

\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsthm} 
\usepackage{pb-diagram}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
\usepackage{epstopdf}
\usepackage{multicol}
\usepackage{cancel}

\usepackage{amsfonts}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newtheorem{theorem}{Theorem}
%% \newtheorem{acknowledgement}[theorem]{Acknowledgement}
%% \newtheorem{algorithm}[theorem]{Algorithm}
%% \newtheorem{axiom}[theorem]{Axiom}
%% \newtheorem{case}[theorem]{Case}
%% \newtheorem{claim}[theorem]{Claim}
%% \newtheorem{conclusion}[theorem]{Conclusion}
%% \newtheorem{condition}[theorem]{Condition}
%% \newtheorem{conjecture}[theorem]{Conjecture}
%% \newtheorem{mycorollary}[theorem]{Corollary}
%% \newtheorem{mycriterion}[theorem]{Criterion}
%% \newtheorem{mydefinition}[theorem]{Definition}
%% \newtheorem{myexample}[theorem]{Example}
%% \newtheorem{myexercise}[theorem]{Exercise}
%% \newtheorem{mynotation}[theorem]{Notation}
%% \newtheorem{myproblem}[theorem]{Problem}
%% \newtheorem{myproposition}[theorem]{Proposition}
%% \newtheorem{myremark}[theorem]{Remark}
%% \newtheorem{mysolution}[theorem]{Solution}
%% \newtheorem{mysummary}[theorem]{Summary}
%% \newenvironment{myproof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfg}{\hf_{\gf}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\sfr}{\mathfrak{s}}
%\pagestyle{plain}

\theoremstyle{definition} \newtheorem{Def}{Определение}
\newcommand{\tr}{\hat\triangleright} \newcommand{\trc}{\triangleright}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

\begin{document}

Спасибо! Добрый день! 
Моя диссертация называется ``Правила ветвления аффинных алгебр Ли и приложения в моделях конформной теории поля''.

Сперва о теме исследования. Конформная теория поля в двух измерениях появилась для описания критического поведения в двумерных решеточных моделях. Также двумерная конформная теория поля играет существенную роль в теории струн (если записать действие Полякова для релятивистской струны, а потом вычислить эффективное действие для полей на мировой поверхности, полученная теория будет конформной теорией поля).

Конформная теория поля интересна еще и тем, что она является точно решаемой, то есть корреляционные функции можно найти без использования теории возмущений. Конформная теория поля выделяется еще и как квантовая теория поля со взаимодействием, допускающая аксиоматическую формулировку.

Модели Весса-Зумино-Новикова-Виттена и coset-модели -- это два важных класса моделей конформной теории поля. Они реализуют рациональные модели конформной теории поля, то есть для любого рационального значения центрального заряда существует соответствующая ВЗНВ или coset-модель. В этих теориях имеется калибровочная инвариантность, которая сильно помогает в исследовании.

Наличие калибровочной инвариантности приводит к возникновению аффинных алгебр Ли. Аффинные алгебры Ли -- это важный класс бесконечномерных алгебр Ли, их теория представлений хорошо развита. Таким образом, у нас есть инструмент для исследования моделей конформной теории поля. Кроме того, аффинные алгебры Ли связаны с теорией специальных функций и модулярных форм, но на этих вопросах мы не будем сейчас останавливаться.

Задача редукции представления аффинной алгебры Ли на представления подалгебры возникает при изучении структуры пространства состояний в ВЗНВ и coset-моделях. 
Эта задача нетривиальна, ей давно занимаются, но окончательной формулы для коэффициентов ветвления пока не существует.

Теперь я перечислю основные результаты диссертации. В диссертации впервые решены следующие задачи: получено эффективное рекуррентное соотношение для вычисления коэффициентов ветвления; создан пакет для популярной системы символьных вычислений Mathematica, позволяющий решать различные задачи теории представлений аффинных и конечномерных алгебр Ли; показано, что разложение сингулярного элемента, которое использовалось для вывода рекуррентного соотношения, определяет как коэффициенты ветвления, так и обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда; установлена прямая связь расщепления корневой системы и ветвления, указано, при каких условиях кратности весов модуля вспомогательной алгебры совпадают с коэффициентами ветвления; предложено обобщение стохастического процесса Шрамма-Лёвнера на системы с калибровочной инвариантностью и исследованы требования на операторы, соответствующие изменению граничных условий в решеточных моделях.

Отмечу, что пакет Affine.m подходит для решения задач теории представлений в различных областях физики, от изучения спектров атомов и молекул и до конформной теории поля и квантовых интегрируемых систем.

Диссертации имеет следующую структуру. Первая глава носит обзорных характер и содержит основные понятия двумерной конформной теории поля и теории представлений аффинных алгебр Ли. 
Во второй главе вводится разложение сингулярного элементы и выводится рекуррентное соотношение на коэффициенты ветвления. Затем приводятся примеры применения рекуррентного соотношения для вычисления коэффициентов ветвления аффинных и конечномерных алгебр Ли и примеры приложений в моделях конформной теории поля. 
Третья глава посвящена исследованию связи ветвления и обобщенной резольвенты Бернштейна-Гельфанда-Гельфанда. Показано, что разложение сингулярного элемента, определяющее коэффициенты ветвления, приводит к построению обобщенных модулей Верма, образующих точную последовательность.
В четвертой главе рассматривается связь расщеплений корневых систем алгебр Ли с ветвлением. Показано, что при выполнении определенных условий на структуру сингулярного элемента, коэффициенты ветвления совпадают с кратностями весов в модуле вспомогательной алгебры. 
Пятая глава посвящена практическим приложениям. В первом разделе мы обсуждаем обобщение эволюции Шрамма-Лёвнера, использующейся для описания доменных стенок в решеточных моделях. Во втором разделе описывается компьютерная программа Affine.m.

Перейду теперь к содержанию и объяснению основных результатов диссертации.

Модели Весса-Зумино-Новикова-Виттена имеют следующее действие. Первый член -- это действие нелинейной сигма-модели. При его квантовании конформная инвариантность нарушается, поэтому требуется второй топологический член, который восстанавливает конформную симметрию. Действие записано для поля же, которое задано на комплексной плоскости и принимает значения в группе Ли же. Так как в действии содержатся производные же, то нас, на самом деле интересует не группа, а соответствующая алгебра Ли. В этой теории есть калибровочная инвариантность, которой соответствуют сохраняющиеся токи. Если разложить эти токи по степеням зет и по базису в алгебре ли, то компоненты этого разложения будут удовлетворять коммутационным соотношениям аффинной алгебры Ли. (Аффинная алгебра Ли -- это центральное расширение алгебры петель). 
Из конформной инвариантности следует, что алгебры Вирасоро, соответствующая конформным преобразованиям, содержится в универсальной обертывающей аффинной алгебры Ли. То есть ее генераторы можно представить в виде комбинаций генераторов аффинной алгебры. Пространство состояний теории раскладывается на представления аффинной алгебры Ли. 
Coset-модели являются обобщением моделей Весса-Зумино-Новикова-Виттена. Мы добавляем к действию взаимодействие с чисто калибровочным полем, принимающим значения в некоторой подалгебре а алгебры же. 
Конформная инвариантность сохраняется, выражения для генераторов алгебры Вирасоро -- разности выражений для алгебр же и а. 
Заметим, что векторы или состояния, которые сингулярны по отношению к аффинной подалгебре а, то есть зануляются понижающими операторами, образуют модули алгебры Вирасоро. Функции ветвления, которые определяются коэффициентами ветвления, -- это характеры этих модулей алгебры Вирасоро. То есть вычисляя коэффициенты ветвления мы исследуем структуру пространства состояний coset-модели. Примарные поля в coset-моделях нумеруются парами весов алгебры и подалгебры, для которых функция ветвления отлична от нуля, то есть существуют ненулевые коэффициенты ветвления.

Теперь несколько слов о модулях аффинных алгебр Ли, которые исследуются в данной работе. 
Во-первых, модули Верма. Это бесконечномерные модули с очень простой структурой, подобной конструкции пространства Фока - просто все состояния, которые получаются действием на вектор старшего веса операторами рождения.

У модуля Верма есть единственный максимальный подмодуль, если по нему факторизовать, то есть выкинуть входящие в него состояния, получится неприводимый модуль. Его структура может быть записана в виде формального характера, для которого верно такое выражение. Наверху стоит сингулярный элемент, содержащий набор сингулярных весов. Внизу -- знаменатель Вейля. Характер неприводимого модуля можно представить в виде комбинации характеров модулей Верма. 
Сингулярный элемент определяет основные свойства модуля.

Задача редукции ставится следующим образом. Пусть алгебра же и ее подалгебра а -- конечномерные или аффинные. Хотим разложить неприводимый модуль алгебры же на неприводимые модули алгебры а и вычислить коэффициенты этого разложения, то есть сколько раз каждый из неприводимых модулей входит в разложение.

Мы получили рекуррентное соотношение на эти коэффициенты. Сейчас я его объясню. 
Рассмотрим, например, модуль алгебры эс-о-пять. Здесь приведены кратности весов в нем и его сингулярные веса пунктиром. Рассмотрим подалгебру эс-о-три, построенную на этом корне. Оказывается, что существует вспомогательная подалгебра (в данном случае - тоже эс-о-три), все корни которой ортогональны корням исходной подалгебры. Размерности неприводимых модулей этой подалгебры, построенных в сингулярных весах, являются начальными данными для рекуррентного вычисления коэффициентов ветвления. Такие модули и их размерности изображены на третьем рисунке. Для вычисления размерностей сам модуль строить не нужно, поэтому построение начальных данных -- это очень простая процедура.

Рекуррентное соотношение имеет следующий вид: в него входят начальные точки - точки сингулярного элемента с размерностями. И сумма уже вычисленных коэффициентов ветвления, домноженных на соответствующие значения функции эсб которая вычисляется из разложения знаменателей Вейля. Она универсальна, то есть не зависит от того, какой модуль мы раскладываем, а только от того, какую алгебру и подалгебру мы рассматриваем.

Вот пример применения этой рекуррентной формулы для вычисления коэффициентов ветвления для аффинных алгебр Ли. Здесь алгебра -- это аффинное расширение алгебры эс-о-пять, а подалгебра -- аффинное расширение алгебры эс-о-три. Тут показан набор весов и значений функции эс, определяющих рекурсию, а вот здесь начальные данные. На последнем рисунке результат вычисления коэффициентов ветвления. Выделена главная камера Вейля.

Выводы ко второй главе состоят в том, что мы показали, что коэффициенты ветвления нужны для вычисления спектра возбуждений в моделях Весса-Зумино-Новикова-Виттена, функции ветвления дают статсумму для coset-моделей, мы получили новую рекуррентную формулу на коэффициенты ветвления, которая не требует лишних вычислений. В частности, не нужно строить модули, входящие в разложение. Вот на этом рисунке приведено время вычисления коэффициентов ветвления модулей эс-о-девять на модули эс-о-семь в зависимости от размерности модуля. Пунктиром - традиционный алгоритм, требующий построения модулей, входящих в разложение, сплошная -- наш рекуррентный алгоритм.

То есть мы продемонстрировали эффективность нашего алгоритма.

Перехожу к третьей главе, которая посвящена связи ветвления и обобщенной резольвенты Бернштейна-Гельфанда-Гельфанда.

\end{document}

### 2012-12-12 GeneralOverview/RepresentationTheory/RT-notes.tex
Started some notes on representation theory

\documentclass[12pt]{article}
\usepackage{amsfonts}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsthm}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[russian]{babel}
\usepackage[utf8]{inputenc}

\newtheorem{Def}{Определение}[section]
\newtheorem{theorem}{Теорема}
\newtheorem{statement}{Утверждение}
\newtheorem{Cnj}[Def]{Гипотеза}
\newtheorem{Prop}[Def]{Свойство}
\newtheorem{example}{Пример}[section]
\newtheorem{axiom}{Аксиома}

\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\nfp}{\mathfrak{n}^{+}}
\newcommand{\nfm}{\mathfrak{n}^{-}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\uf}{\mathfrak{u}}
\newcommand{\sfr}{\mathfrak{s}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}

\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\sfh}{\hat{\mathfrak{s}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\begin{document}
\title{Заметки по теории групп Ли, алгебр Ли и их представлений}

\maketitle

\begin{abstract}
  Здесь мы обсуждаем основные проблемы теории групп Ли, указываем на
  аналогию с теорией Галуа и приводим некоторые нерешенные задачи.
\end{abstract}

\section{Мотивация}
\begin{itemize}
\item Как появилась появилась теория групп Ли?
\item В чем состоит аналогия с теорией Галуа?
\item Какие задачи должна была решать теория непрерывных групп?
\item Какие задачи не смогла решить? Почему?
\item Какие задачи еще не решены?
\end{itemize}

\section{Теория групп Ли и теория Галуа}
\label{sec:galois}

Группы Галуа появились для решения полиномиальных (алгебраических)
уравнений, группы Ли -- для решения обыкновенных дифференциальных
уравнений.

Галуа ввел конечные группы для решения уравнений второй, третьей и
четвертой степени и доказательства неразрешимости уравнений пятой
степени. Речь идет о группах инвариантности уравнений.

Ли аналогично ввел непрерывные группы инвариантности дифференциальных
уравнений.

Группы делятся на простые и разрешимые. Разрешимые связаны с
интегрируемостью и упрощением обыкновенных дифференциальных уравнений.

Дифференциальные уравнения могут быть разрешены, если их группа
инвариантности разрешима.

Классические функции математической физики возникают как матричные
элементы представлений простых групп Ли.

\bibliography{bibliography}{}
\bibliographystyle{utphys}

\end{document}

### 2012-12-12 GeneralOverview/annotation.tex
Annonation added

\documentclass{article}
\usepackage[russian]{babel}
\usepackage[utf8]{inputenc}
\title{Конформная теория поля}
\author{Антон Назаров}
\date{13 сентября 2012}
\begin{document}
\maketitle
Конформная теория поля может быть сформулирована достаточно строго.
Этим она отличается от других моделей квантовой теории поля.

Мы кратко опишем переход от дискретных систем к непрерывным и от
классических к квантовым. Обсудим, как при этом возникают понятия
полей, состояний, корреляционных функций, операторного разложения.
Затем мы сформулируем аксиомы, которым должны удовлетворять
корреляционные функции и покажем, что по корреляционным функциям
восстанавливаются поля и гильбертово пространство состояний.

Из требования определенного поведения корреляционных функций при
конформных преобразованиях возникает алгебра Вирасоро. Поля в
конформной теории образуют модули алгебры Вирасоро. Из структуры
модулей следуют уравнения на корреляционные функции, которые, кстати,
совпадают с уравнениями на мартингалы эволюции Шрамма-Лёвнера.
\end{document}

### 2012-12-12 AffineLieAlgebras/Thesis/talk-defence.tex

@@
 \def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}
+
+\topmargin=-3.5cm
+%\oddsidemargin=-1.5cm
+%\evensidemargin=-1.5cm
+%\textwidth=19cm
+\textheight=28cm
 
@@
 Рекуррентное соотношение имеет следующий вид: в него входят начальные точки - точки сингулярного элемента с размерностями.
-И сумма уже вычисленных коэффициентов ветвления, домноженных на соответствующие значения функции эсб которая вычисляется из разложения знаменателей Вейля.
+И сумма уже вычисленных коэффициентов ветвления, домноженных на соответствующие значения функции эс, которая вычисляется из разложения знаменателей Вейля.
 Она универсальна, то есть не зависит от того, какой модуль мы раскладываем, а только от того, какую алгебру и подалгебру мы рассматриваем.
+Набор формальных экспонент весов гамма с коэффициентами эс от гамма называется веером вложения.
+
+Замечу, что если подалгебра -- это подалгебра Картана, то рекуррентное соотношение будет давать кратности весов в неприводимом модуле.
 
@@
 
+Зачем вообще нам нужно выражать характер неприводимого модуля через характеры модулей Верма?
+Ведь в случае конечномерных алгебр неприводимые модули конечномерны, а модули Верма -- нет?!
+Посмотрите на рисунок.
+Здесь изображен модуль Верма алгебры эс-о-пять.
+Видно, что его структура довольно проста.
+То есть идея состоит в исследовании модуля путем погружения его в модуль большой размерности, но имеющий простую структуру.
+
+Справа показан обобщенный или параболический модуль Верма той же алгебры.
+Он строится не из одного старшего веса, а из неприводимого модуля некоторой параболической подалгебры.
+В данном случае это подалгебра эс-о-три, построенная на вот этом корне.
+Характер обобщенного модуля Верма -- это отношение характера неприводимого модуля подалгебры к вееру вложения этой подалгебры.
+
+Как же использовать обобщенные модули Верма для изучения неприводимого модуля?
+Оказывается, что характер неприводимого модуля является комбинацией с разными знаками.
+Вот на этом рисунке это показано.
+Здесь вы видите набор обобщенных модулей Верма, комбинация характеров которых дает характер вот этого неприводимого модуля.
+Какие же обобщенные модули здесь изображены?
+Эти модули построены из тех неприводимых представлений вспомогательной подалгебры, размерности которых давали нам начальные данные для вычисления коэффициентов ветвления на вот эту подалгебру!
+Суммы таких модулей образуют точную последовательность обобщенной резольвенты. Здесь представлена центральная часть этой точной последовательности.
+
+Итак, по результатам данной главы можно сделать следующие выводы.
+Использование веера вложения приводит к построению параболических модулей Верма.
+Обобщенные модули Верма образуют точную последовательность обобщенной резольвенты Бернштейна-Гельфанда-Гельфанда.
+Кроме того, разложение сингулярного элемента, которое определяет коэффициенты ветвления, определяет и обобщенную резольвенту.
+Итак, мы установили связь ветвления и обобщенной БГГ-резольвенты.
+
+В четвертой главе рассматриваются сплинты или расщепления корневой системы.
+Чтобы объяснить понятие расщепления, я начну с простого примера.
+Рассмотрим корневую систему алгебры эс-о-пять.
+Она состоит из восьми корней.
+Если мы выкинем корни некоторой подалгебры эс-о-три, то у нас останется шесть корней, между которыми есть те же соотношения, что и в корневой системе алгебры эс-эль-три, хотя углы и длины корней другие.
+Оказывается, что если мы будем раскладывать неприводимый модуль эс-о-пять на модули эс-о-три, коэффициенты ветвления совпадут с кратностями весов эс-эль-три!
+Здесь приведено формальное определение расщепления.
+
+Из нашего рекуррентного соотношения, которое дает как коэффициенты ветвления, так и кратности весов, можно понять, почему происходит совпадение.
+В каких же случаях оно имеет место?
+Оказывается, что для этого должно быть выполнено следующее условие -- сингулярный элемент модуля алгебры должен представляться в виде комбинации образов сингулярных элементов вспомогательной алгебры, входящей в расщепление.
+Вот здесь перечислены все случаи для простых конечномерных алгебр Ли.
+В качестве еще одного примера я покажу сингулярный элемент, его разложение и коэффициенты ветвления для модуля алгебры же-два на модули подалгебры а-два. 
+Итак, выводы к четвертой главе.
+Мы проанализировали связь расщеплений с ветвлением, доказали, что расщепление приводит к совпадению коэффициентов ветвления с кратностями весов вспомогательной алгебры.
+Затем мы рассмотрели аффинные расширения конечномерных алгебр Ли с расщепляющейся корневой системой и получили для них новые соотношения на тета-функции и функции ветвления аффинных алгебр на конечномерные подалгебры.
+Однако эти соотношения не такие простые, как простое совпадение в случае конечномерных алгебр, поэтому я не привожу их в презентации.
+
+Пятая глава посвящена практическим приложениям.
+В первом разделе мы рассматриваем обобщение стохастического процесса Шрамма-Левнера.
+Стохастический процесс Шрамма-Левнера служит для описания критического поведения доменных стенок в решеточных моделях.
+Рассмотрим решеточную модель, например, модель Изинга, на верхней полуплоскости.
+Пусть заданы граничные условия.
+Например, на половине границы спины вверх, а на половине -- вниз.
+Тогда у нас будет доменная стенка.
+Мы можем параметризовать ее параметром т.
+Если мы сделаем разрез вдоль стенки, то область с разрезом можно отобразить на верхнюю полуплоскость конформным отображением.
+Оказывается, что в критической точке в термодинамическом пределе такое отображение удовлетворяет стохастическому дифференциальному уравнению.
+
+Можно рассмотреть решеточную наблюдаемую в присутствии доменной стенки.
+Среднее значение такой наблюдаемой складывается из суммы по всем траекториям средних значений в областях с разрезом.
+Так как само среднее значение не зависит от параметризации стенки, то приращение среднего значения в области со стенкой при росте стенки не должно зависеть от времени.
+Такая наблюдаемая называется мартингалом.
+
+Критическое поведение решеточной модели описывается конформной теории поля, поэтому наблюдаемой должна соответствовать корреляционная функция в конформной теории поля.
+Она содержит операторы смены граничного условия на конце стенки и на бесконечности.
+Мы можем прирастить стенку, а потом сделать отображение на всю полуплоскость.
+При этом входящие в корреляционную функцию поля преобразуются так.
+Из требования определенного поведения при росте доменной стенки получается уравнение на корреляционную функцию.
+Это уравнение можно переписать в виде алгебраического соотношения на оператор смены граничного условия.
+Так можно классифицировать операторы смены граничного условия.
+В работе предложено обобщение данной конструкции. Рассмотрим аналог coset-модели, где вместе с ростом стенки производится случайное калибровочное преобразование. 
+Для такого процесса тоже можно рассмотреть поведение наблюдаемых при росте стенки.
+Отсюда получается следующее условие на оператор смены граничного условия: такой вектор должен быть сингулярным.
+То есть перечислить возможные операторы смены граничного условия можно исследуя структуру сингулярных элементов в модулях аффинных алгебр Ли.
+Заметим, что все конформные теории поля, которые соответствуют решеточным моделям, можно получить coset-конструкцией.
+
+Второй раздел пятой главы посвящен описанию компьютерной программы аффайн-эм, которая использовалась для создания почти всех примеров и иллюстраций в данной презентации.
+Покажу еще пару примеров.
+Вот вычисление струнных функций для аффинной алгебры эс-эль-три.
+А вот модули алгебры эс-о-пять.
+
+Итак, в пятой главе было предложено обобщение эволюции Шрамма-Левнера, которое соответствует coset-моделям в конформной теории.
+Получены алгебраические соотношения на оператор смены граничных условий.
+Классификация таких операторов связана со структурой сингулярных элементов.
+Реализован пакет аффайн-эм для популярной системы символьных вычислений Математика.
+Этот пакет может быть полезен для решения различных задач.
+
+Еще раз перечислю основные результаты работы.
+
+Во-первых, получены новые рекуррентные соотношения на коэффициенты ветвления.
+
+Показана связь редукции с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда.
+
+Выявлена связь расщепления корневой системы алгебры с разложением сингулярных элементов модулей алгебры в комбинацию образов сингулярных элементов модулей вспомогательной алгебры.
+Показано, что наличие расщепления приводит к совпадению коэффициентов ветвления с кратностями весов и ведет к новым соотношениям на функции ветвления для аффинных алгебр Ли.
+
+Предложено обобщение стохастического процесса Шрамма-Левнера на случай coset-моделей.
+
+Реализован пакет аффайн-эм для вычислений в теории представлений.
+
+Вот список публикаций в рецензируемых журналах и список других публикаций и докладов.
+
+Спасибо большое за внимание!
+
 \end{document}

### 2012-12-15 AffineLieAlgebras/MQFT2012/paper.tex
Minor changes
Some work on vertex algebra paper

@@
 Consider affine Lie algebra $\gfh$, which is an affine extension of (semi)simple Lie algebra $\gf$.
-Let $\omega_{0},\dots,\omega_{r}$ be fundamental weights of $\gfh$. Then $L^{k\omega_{0}}_{\gfh}$ is vertex operator algebra and its irreducible modules are $L^{\mu}_{\gfh}$ such that $\mu<k$.
-
-In this case Virasoro element is  $\omega=\frac{1}{2(k+h^{\vee})}\sum_i u_i(-1) u_i(-1)$, where
-$u_i (i=1,\dots,\mathrm{dim}\gf)$  is an orthogonal basis in $\gfh$ w.r.t. Cartan-Killing form.
+Let $\omega_{0},\dots,\omega_{r}$ be fundamental weights of $\gfh$.
+Irreducible highest weight module $L^{k\omega_0}_{\gfh}$ of affine Lie algebra $\gfh$ can be endowed with the structure of Vertex operator algebra \cite{frenkel1992vertex}.
+Its irreducible modules are $L^{\mu}_{\gfh}$ such that $\mu<k$.
+Virasoro element in this case is given by the formula
+\begin{equation}
+  \label{eq:2}
+  \omega=\frac{1}{2(k+h^{\vee})}\sum_i u_i(-1) u_i(-1),
+\end{equation}
+where $u_i (i=1,\dots,\mathrm{dim}\gf)$  form an orthogonal basis in $\gfh$ with respect to Cartan-Killing form.
 
@@
 Note that for $\af\subset\gf$ and $V=L^0_{(\gf)}k, W=L^0_{(\af)k}$ the algebra
-$W'$ is vertex operator algebra of  $G/A$-coset-model.
+$W'$ is the vertex operator algebra of  $G/A$-coset-model.
 
@@
 
+Irreducible $V$-modules can be reduced into combination of tensor products of irreducible $W$- and $W'$-modules:
+\begin{equation}
+  \label{eq:1}
+  M_V=\bigoplus_{i\in I} (M^i_{W}\otimes M^i_{W'}),
+\end{equation}
+where $I$ is some index set.
+
+For coset models we can write this decomposition as
+\begin{equation}
+  \label{eq:3}
+  L^{\mu}_{\gfh}=\bigoplus_{\nu \in \pi({\cal N})} (M^{h(\mu,\nu),c}_{Vir} \otimes L^{\nu}_{\afh}),
+\end{equation}
+where the summation is over the projection of weight diagram of $L^{\mu}_{\gfh}$ to Cartan subalgebra of $\afh$. Central charge and conformal weights of Virasoro modules are equal to
+\begin{eqnarray}
+  \label{eq:4}
+    c=\frac{k\;\mathrm{dim}\gf}{k+h^{\vee}_{\gf}}-\frac{x_e k\;\mathrm{dim}\af}{x_e k+h^{\vee}_{\af}}\\
+    h(\mu,\nu)=\left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee}_{\gf})}\right)
+\end{eqnarray}
+(See pp. 837-840 (855-858 in file) of Di Francesco for a characterization of singular vectors of Virasoro modules for $su(2)$)
+
+Let $V=L$
+Branching functions coincide with characters of Virasoro modules. Virasoro characters can be written in terms of Virasoro Verma modules characters. 
+Recurrence relations on branching coefficients lead to recurrence relations on integer partitions numbers.
 \begin{itemize}

### 2013-01-30 AffineLieAlgebras/Splints/affine.tex
Started new text on splints for affine Lie algebras

--- 2012-03-03 AffineLieAlgebras/Splints/paper2.tex
@@
 \documentclass[12pt]{article}
- \textheight=24cm
- \textwidth=16.5cm
- \topmargin=-1.5cm
- \oddsidemargin=-0.25cm
-
+%% \textheight=24cm
+%% \textwidth=16.5cm
+%% \topmargin=-1.5cm
+%% \oddsidemargin=-0.25cm
+%%
 \usepackage{amsfonts}
@@
 
-The term {\it splint} was introduced by D. Richter in \cite{richter2008splints} where the
-classification of splints for simple Lie algebras was obtained. The fan $\Gamma \subset \Delta$ was
-introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent properties of
-branching coefficients for maximal embeddings. Injection fan is an efficient tool to study branching
-rules. Later this construction was generalized to non-maximal embeddings and affine Lie algebras in
-\cite{2010arXiv1007.0318L, ilyin812pbc}. In paper \cite{2011arXiv1111.6787L} we have shown that the
-existence of a splint for a root system of a simple Lie algebra leads to simplifications in
-reduction procedures of a Lie algebra module to modules of a subalgebra. This effect is based on the
-injection fan and singular element properties of Lie algebra modules.
+The equivalence of coset models $g_2/su(3)$ and $su(3)\times
+su(3)/su(3)$ is well-known for more then twenty years \cite{Dunbar:1992gh}. 
+They are also equivalent to $su(2)\times su(2)/su(2)$ coset model with
+non-diagonal modular invariant. In paper \cite{Dunbar:1992gh} the equivalence
+is derived from the coincidence of conformal weights and central
+charges in these models.
 
-In the present note we discuss possible applications of splint in
-a root system of simple Lie algebra related to representation
-theory of affine Lie algebras. We discuss the structure of
-injection fan for affine Lie algebras and show that it admits a
-decomposition similar to that used in \cite{2011arXiv1111.6787L}
-for simple Lie algebras. Such a decomposition leads to equations
-for theta-functions. We study graded branching of affine Lie
-algebra modules reduced to a finite-dimensional subalgebra and
-discuss consequences of splint in this case.
+Note that irreducible Virasoro modules are uniquely specified by central
+charge and conformal weights and characters
+of Virasoro modules are proportional to branching functions. So the branching
+coefficients for the affine Lie algebra embeddings $\hat A_2\to \hat G_2$ and
+$\hat A_2\to \hat A_2 \otimes \hat A_2$ should coincide.
 
-\section{Splints and affine Lie algebras}
-\label{sec:definitions}
+In present text we do not rely on properties of Virasoro algebra modules to
+establish this equality of branching functions. We use structure of affine Lie
+algebras.
 
-Consider simple Lie algebra $\gf$ with a root system $\Delta$. Let
-$\af_{1}\subset \gf$ be its reductive subalgebra of the same rank, such that
-$\Delta_{\af}\equiv\Delta_{1}\subset\Delta$ and $Q_{\af}\subset Q$, where $Q$ is the root lattice. Irreducible highest-weight modules of
-$\gf$ and $\af$ are denoted by $L^{\mu}$ and $L^{\nu}_{\af}$
-correspondingly. Weyl character formula for irreducible modules is
-$\mathrm{ch}L^{\mu}=\frac{\Psi^{(\mu)}}{\prod_{\alpha\in\Delta}(1-e^{-\alpha})}$,
-where $\Psi^{(\mu)}=\sum_{w\in W}\epsilon(w) e^{w(\mu+\rho)-\rho}$
-is a singular element of the module and $W$ -- the Weyl group of
-$\gf$. Formal character of irreducible module admits a
-decomposition
-\begin{equation}
-  \label{eq:4}
-  \mathrm{ch} L^{\mu}=\sum_{\nu\in P_{\af}} b^{\mu}_{\nu} \mathrm{ch} L^{\nu}_{\af},
-\end{equation}
-where $P$, $P_{\af}$ are weight lattices of $\gf$ and $\af$. We
-want to study affine extension of this situation:
-$\gf\subset\gfh,\; \af\subset\afh$, $\afh\subset\gfh$,
-$\hat{\Delta}\subset\hat{\Delta}$ and
-$\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{\hat{\nu}}
-b^{\hat{\mu}}_{\hat{\nu}} \mathrm{ch} L^{\hat{\nu}}_{\afh}$. For
-weights of an affine Lie algebra $\gfh$ we have
-$\hat{\mu}=(\mu,k,n)$, where $\mu$ is a weight of $\gf$, $k$ --
-the level of the module and $n$ -- the grade of the weight
-$\hat{\mu}$
+Now consider branching coefficients computation for the embedding
+$\hat{su(3)}\to \hat g_2$. Construct the injection
+fan. All the multipliers, corresponding to long and imaginary roots of
+$\hat g_2$ are reduced. So we are left with
+$\prod_{\alpha\in \Delta^+_{short} (g_2)}\prod_{n=1}^{\infty}
+(1-exp(-\alpha - n\delta))$
+We have Weyl denominator of affine $su(3)$ on short roots, but without
+purely imaginary roots.
 
-\begin{Def}
-  Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a bijective map of
-  roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with vector composition law
-  in $\Delta_{1}$ and $\Delta$.
-\begin{equation*}
-\phi:\Delta_1 \longrightarrow \Delta, \quad \phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,\,\,\, \alpha,\beta \in \Delta_1
-\end{equation*}
-\end{Def}
+To construct singular element we can present the Weyl group elements
+of $\hat g_2 as s_1\dots s_k t_{\lambda} s'_1\dots s'_l$,
+where $s_i$ are reflection w.r.t. long roots, $s'$ are reflections w.r.t.
+short roots and $t_{\lambda}$ are usual translations
+that change grade. The translation can be presented as a combination
+of translations on the short roots (?).
+So in each grade of singular element we have singular weights of $\hat
+A_2$ on short roots, additionally
+translated and reflected by Weyl group of $A_2$ on long roots.
 
-Note that the image $Im(\phi)$ must not inherit the root system properties except the addition rules
-equivalent to the addition rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and
-$\phi_2$ can splinter $\Delta$ when the latter can be presented as a disjoint union of images
-$Im(\phi_1)$ and $Im(\phi_2)$.
+This data allows us to compute branching coefficients.
 
-$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
-\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
-_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
-\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+Then we need to compare this picture with $su(3)\times su(3)/su(3)$
+model. The injection fan is similar to previous
+case, but we have the imaginary roots, since rank of algebra is 4 and
+rank of subalgebra is 2.
+In singular element we also have some additional translations. The
+question is, how do these translations compensate
+extra imaginary roots in calculation?
 
-\begin{Def}
-  A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if there are two embeddings
-  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
-  \phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the disjoint union of the
-  images of $\phi _{1}$ and $\phi _{2}$ and (b) neither the rank of $\Delta _{1}$ nor the rank of
-  $\Delta _{2}$ exceeds the rank of $%
-  \Delta $.
-\end{Def}
-
-It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote
-this by $\Delta \approx (\Delta_1,\Delta_2)$. Each component $\Delta_1$ and $\Delta_2$ is a "stem''
-of the splint.
-
-We consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem. As shown in paper \cite{2011arXiv1111.6787L} the second stem $\Delta _{\frak{s}}:=\Delta
-_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product
-$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}$
-and it defines an injection fan $\Gamma _{\frak{a}%
-\hookrightarrow \frak{g}}$ \cite{lyakhovsky1996rra,ilyin812pbc,2010arXiv1007.0318L}.
-
-Since the singular element of $L^{\mu}$ can be
-written as $\Psi _{\frak{g}}^{\left( \mu \right) }=e^{-\rho }
-\sum_{w\in W_{\frak{a}}}\epsilon \left( w \right) w\circ \left(
-e^{\rho _{\frak{a}}}\Psi ^{\widetilde{\mu }+\rho
-_{\frak{s}}}\right)$  for branching coefficients we get the
-identity \cite{2011arXiv1111.6787L}:
-\begin{equation}
-  \label{eq:9}
-b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
-}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}  
-\end{equation}
-Here the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $, they have the
-same Dynkin numbers: $\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
-m_{k}\omega_{(\sfr) k} . \label{new h weight}$ So branching coefficients coincide with weight
-multiplicities of $\sfr$-modules.
-
-Now we consider affine extension of this setup, $\afh\subset\gfh$. Since $\mathrm{rank}\gf\leq
-\mathrm{rank} \af+\mathrm{rank}\sfr$ for Weyl denominators we get
- \[
-\prod_{\alpha\in\hat{\Delta}^{+}_{1}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}\prod_{\beta\in\hat{\Delta}^{+}_{2}}(1-e^{\phi\circ \beta})^{\mathrm{mult}(\beta)}=\prod_{\gamma\in\hat{\Delta}^{+}}(1-e^{-\gamma})^{\mathrm{mult}(\gamma)}\prod_{n=0}^{\infty}(1-e^{-n\delta})^{\mathrm{rank}\af+\mathrm{rank}\sfr-\mathrm{rank}\gf}
-\]
-
-Using a specialization
-\cite{kac1988modular,kac1984infinite,kac1990idl} and the
-definition of Dedekind eta-function
-$\eta(\tau)=q^{1/24}\prod_{n=1}^{\infty}(1-q^{n})$, where
-$q=e^{2\pi i \tau}$ we can rewrite this identity as the relation
-imposed on theta-functions $\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in Q_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$:
-\begin{multline}
-  \label{eq:5}
-  \eta(\tau)^{\mathrm{dim}(\af)}\prod_{\alpha\in\Delta_{1}^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z)}{\eta(\tau)} \eta(\tau)^{\mathrm{dim}(\sfr)}\prod_{\beta\in\Delta_{2}^{+}}\frac{\Theta^{(\hat A_{1})}_{\phi\circ \beta}(\tau,z))}{\eta(\tau)}=\\
-\eta(\tau)^{\mathrm{rank}(\af)+\mathrm{rank}(\sfr)-\mathrm{rank}(\gf)}
-\eta(\tau)^{\mathrm{dim}(\gf)}\prod_{\alpha\in\Delta^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z))}{\eta(\tau)}
-\end{multline}
-Here $z\in P_{\geq 0}\otimes \mathbb{C}$. Using Weyl denominator identity this relation can be
-rewritten as a non-trivial relation connecting theta-functions of algebras $\gfh,\hat\sfr,\afh$:
-\begin{equation}
-  \label{eq:6}
-  \left(\sum_{v\in W_{\af}}\epsilon(v) \Theta^{(\afh)}_{v\rho_{\af}}(\tau,z)\right)
-  \cdot \left(\sum_{u\in W_{\sfr}}\epsilon(u) \Theta^{(\hat{\sfr})}_{\phi\circ(u\rho_{\sfr})}(\tau,z)\right)= 
-  \left(\sum_{w\in W}\epsilon(w) \Theta^{(\gfh)}_{w\rho_{\gf}}(\tau,z)\right)
-\end{equation}
-%Now we can use Weyl denominator identity $e^{-\rho}\prod_{\alpha\in \hat{\Delta}^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}=\sum_{w\in \hat{W}}\det(w)e^{w\rho}$
-
-Now consider the branching of $\gfh$-module to $\gf$-modules. For
-formal characters we can write the following expression:
-\begin{equation}
-  \label{eq:8}
-\mathrm{ch}L^{\hat{\mu}}_{\gfh}=\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{\nu}(n) \mathrm{ch} L^{\nu}_{\gf}.
-\end{equation}
-Rewriting this equation for weight multiplicities we get
-$m^{(\hat{\mu})}_{\hat{\nu}=(\nu,k,n)}=\sum_{\xi\in P}
-b^{(\hat{\mu})}_{\xi}(n) m^{(\xi)}_{\nu}$. We can introduce
-branching functions similarly to the case of branching for affine
-subalgebra \cite{kac1988modular,kac1990idl}:
-$b^{(\hat{\mu})}_{\nu}(q)=\sum_{n=0}^{\infty}
-b^{(\hat{\mu})}_{\nu}(n) q^{n}$.
-These branching functions are connected to $q$-dimension of module $\mathrm{dim}_{q}L^{\hat \mu}_{\gfh}=\sum_{n=0}^{\infty}q^{n}\sum_{\nu\in P} b^{(\hat \mu)}_{\nu}(n) \mathrm{dim }L^{\nu}_{\gf}=\sum_{\nu\in P}b^{(\hat\mu)}_{\nu}(q) \mathrm{dim} L^{\nu}_{\gf}$.
-It is well-known that $q$-dimension is a modular function for some $\Gamma\subset SL_{2}(\mathbb{Z})$  \cite{gannon2006moonshine}, so branching functions $b^{(\hat \mu)}_{\nu}(q)$ have modular properties.
-
- For string functions of a module
-$L^{\hat{\mu}}$ we have
-\begin{equation}
-  \label{eq:7}
-   \sigma^{(\hat{\mu})}_{\nu}(q) = \sum_{\xi\in P} m^{(\xi)}_{\nu} b^{(\hat{\mu})}_{\xi}(q).
-\end{equation}
-
-Introduce an ordering of the set of weights $\xi$ as follows:
-attribute to a weight $(\rho,\xi)$ its product $(\rho,\xi)$ with
-the Weyl vector $\rho$. Then relation \eqref{eq:7} can be written
-in the matrix form $\sigma(q)=M b(q)$ or as an inverse relation
-$b(q)=M^{-1}\sigma(q)$. Here $\sigma(q)$ and $b(q)$ are infinite
-columns of string and branching functions. Matrix $M$ contains
-multiplicities of weights in $\gf$-modules similar to that of
-Table 1 in paper \cite{2010arXiv1001}. The inverse matrix $M^{-1}$
-encodes recurrent relations imposed weight multiplicities
-\cite{il2010folded}.
-
-Now consider the branching of $\gfh$-modules in $\af$-modules and
-assume the existence of a splint
-$\Delta^{+}_{\gf}=\Delta^{+}_{\af}\cup \phi(\Delta^{+}_{\sfr})$.
-We decompose $\gf$-modules in equation \eqref{eq:8} into
-$\af$-modules using property \eqref{eq:9}:
-\begin{multline}
-  \label{eq:10}
-  \mathrm{ch}L^{\hat{\mu}}_{\gfh}=
-\sum_{n=0}^{\infty}e^{-n\delta} \sum_{\nu\in P_{\af}} b^{(\hat{\mu})}_{(\gfh\downarrow\af)\nu}(n) \mathrm{ch} L^{\nu}_{\af}=
-\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} b^{(\nu)}_{(\gf\downarrow \af) \xi}\mathrm{ch} L^{\xi}_{\af}=\\
-=\sum_{n=0}^{\infty} e^{-n\delta} \sum_{\nu\in P} b^{(\hat{\mu})}_{(\gfh\downarrow\gf )\nu}(n) \sum_{\xi\in P_{\af}} M^{\widetilde{\nu}}_{  \widetilde{\nu}-\phi^{-1}( \nu-\xi )}\mathrm{ch} L^{\xi}_{\af}
-\end{multline}
-We see that the similar matrix relation holds for branching
-functions $b_{(\gfh\downarrow\af)}(q)= M_{\sfr}\;
-b_{(\gfh\downarrow\gf)}(q)$ and we can write
-$\sigma(q)=M_{\af}\; b_{(\gfh\downarrow\af)}(q)$. So if we know
-branching coefficients for the embedding $\gf\subset\gfh$ (for
-example, see book \cite{kass1990ala}) we can easily obtain
-branching functions for the embedding $\af\subset \gfh$.
-\section*{Conclusion}
-\label{sec:conclusion} We have demonstrated that splint in affine
-Lie algebras leads to new relations between theta-functions and
-branching functions for branching to finite-dimensional
-subalgebras, which can be useful for computations. Further
-question is to generalize this analysis to affine subalgebras and
-to apply the results to branching in the study of CFT coset
-models.
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-Anton Nazarov thanks the Chebyshev Laboratory (Department of Mathematics and Mechanics,
-Saint-Petersburg State University) for support under the grant 11.G34.31.0026
-of the Government of Russian Federation.
+The case of non-diagonal modular invariants for $su(2)\times
+su(2)/su(2)$ model is also unclear for me.
 

### 2013-02-01 AffineLieAlgebras/Splints/affine.tex
Minor changes

@@
 
+\section{Branching coefficients, branching funcitons and characters}
+\label{sec:branch-coeff-branch}
+
+For affine Lie algebra $\gfh$ the specialized character can be computed as
+\begin{equation}
+  \label{eq:1}
+  \mathrm{ch}_{\mu} (\tau, \{z^i \}) = \mathrm{tr}\left( e^{2\pi i \tau L_0
+    +\frac{c}{24} - h_{\mu } + \sum_i z_i H^i_0} \right)= \mathrm{tr} \left(
+  q^{L_0 +c/24-h_{\mu}} \prod_i \omega_i^{H^i_0}\right)
+\end{equation}
+Here $H^i$ are the elements of the Cartan subalgera of $\gf$, $q=e^{2\pi i
+  \tau}$, $\omega_i = e^{2\pi i z_i}$, $h_{\mu} = \frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}$. 
+Virasoro character for conformal family of primary field $\varphi_{\mu}$ for Wess-Zumino-Novikov-Witten model with affine Lie
+algebra $\gfh$ is equal to restricted character multiplied by
+$q^{h_{\mu}-c/24}$:
+\begin{equation}
+  \label{eq:2}
+  \chi_{\mu} (\tau) = q^{h_{\mu}-c/24} \mathrm{ch} _\mu (\tau,0)
+\end{equation}
+
 Now consider branching coefficients computation for the embedding

### 2013-02-07 AffineLieAlgebras/Simons/talk.tex
Created folder for the talk at Simons Center

\documentclass[a4paper]{article}

\begin{document}
Hello!
It's a great pleasure for me to be here in Simons Center for geometry and physics. 
My talk is called 
\end{document}

### 2013-02-07 AffineLieAlgebras/Simons/talk.tex
Abstract added

@@
 \documentclass[a4paper]{article}
+The title is
+``Boundary condition changing operators and singular vectors Virasoro and
+affine Lie algebra modules''.
+
+Abstract:
+We consider the behaviour of CFT correlation functions with respect to
+Schramm-Loewner evolution with additional Brownian motion on gauge
+group. Using the analogy with lattice models we consider
+correlation functions that satisfy martingale conditions and contain
+boundary condition changing operators and primary fields.
+Martingale conditions can be rewritten as algebraic relations on
+boundary condition changing operators and interpreted from
+representation-theoretic point of view.
 

### 2013-02-08 AffineLieAlgebras/Simons/talk.tex
Minor changes

@@
 \documentclass[a4paper]{article}
-The title is
-``Boundary condition changing operators and singular vectors Virasoro and
-affine Lie algebra modules''.
 
-Abstract:
+\title{Boundary condition changing operators and singular vectors of Virasoro and
+affine Lie algebra modules}
+
+\author{Anton Nazarov}
+\begin{document}
+\maketitle
+\begin{abstract}
 We consider the behaviour of CFT correlation functions with respect to
@@
 representation-theoretic point of view.
+\end{abstract}
 
-\begin{document}
 Hello!
 It's a great pleasure for me to be here in Simons Center for geometry and physics. 
-My talk is called 
+My talk is called ``Boundary condition changing operators and singular vectors of Virasoro and
+affine Lie algebra modules''. 
 \end{document}

### 2013-02-09 AffineLieAlgebras/Simons/talk.tex
Some work on the talk

@@
 affine Lie algebra modules''.
+
+Consider some simple two-dimensional lattice model, for example, Ising
+model on hexagonal lattice. Let us study the behavior of domain walls.
+In order to do it we need to look at the model on the bounded domain.
+We take upper half-plane. Then impose boundary condition in such a way
+that we have a domain wall from zero to infinity.
+
+In critical model there is continuous limit. It is given by a solution
+of Schramm-Loewner stochastic differential equation. 
 \end{document}

### 2013-03-04 AffineLieAlgebras/Splints/affine.tex
Some text on affine splints

@@
 
+\section{Splints and affine root systems}
+\label{sec:splints-affine-root}
+
+\begin{Def}
+  Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a bijective map of
+  roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with vector composition law
+  in $\Delta_{1}$ and $\Delta$.
+\begin{equation*}
+\phi:\Delta_1 \longrightarrow \Delta, \quad \phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,\,\,\, \alpha,\beta \in \Delta_1
+\end{equation*}
+\end{Def}
+
+Note that the image $Im(\phi)$ must not inherit the root system properties except the addition rules
+equivalent to the addition rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and
+$\phi_2$ can splinter $\Delta$ when the latter can be presented as a disjoint union of images
+$Im(\phi_1)$ and $Im(\phi_2)$.
+
+$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
+\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
+_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
+\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.
+
+\begin{Def}
+  A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if there are two embeddings
+  $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
+  \phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the disjoint union of the
+  images of $\phi _{1}$ and $\phi _{2}$ and (b) neither the rank of $\Delta _{1}$ nor the rank of
+  $\Delta _{2}$ exceeds the rank of $%
+  \Delta $.
+\end{Def}
+
+It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$ and we shall denote
+this by $\Delta \approx (\Delta_1,\Delta_2)$. Each component $\Delta_1$ and $\Delta_2$ is a "stem''
+of the splint.
+
+We consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ is a root subsystem. As shown in paper \cite{2011arXiv1111.6787L} the second stem $\Delta _{\frak{s}}:=\Delta
+_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product
+$\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}$
+and it defines an injection fan $\Gamma _{\frak{a}%
+\hookrightarrow \frak{g}}$ \cite{lyakhovsky1996rra,ilyin812pbc,2010arXiv1007.0318L}.
+
+Using straightforward calculation we can easily obtain an identity on theta-functions
+
+definition of Dedekind eta-function
+$\eta(\tau)=q^{1/24}\prod_{n=1}^{\infty}(1-q^{n})$, where
+$q=e^{2\pi i \tau}$ we can rewrite this identity as the relation
+imposed on theta-functions $\Theta^{(\gfh)}_{\widehat{\lambda}=(\lambda,k,0)}(\tau,z)=\sum_{\xi\in Q_{\gf}+\frac{\lambda}{k}}e^{2\pi i k \left(\frac{1}{2} (\xi,\xi) \tau + (\xi,z)\right)}$:
+\begin{multline}
+  \label{eq:5}
+  \eta(\tau)^{\mathrm{dim}(\af)}\prod_{\alpha\in\Delta_{1}^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z)}{\eta(\tau)} \eta(\tau)^{\mathrm{dim}(\sfr)}\prod_{\beta\in\Delta_{2}^{+}}\frac{\Theta^{(\hat A_{1})}_{\phi\circ \beta}(\tau,z))}{\eta(\tau)}=\\
+\eta(\tau)^{\mathrm{rank}(\af)+\mathrm{rank}(\sfr)-\mathrm{rank}(\gf)}
+\eta(\tau)^{\mathrm{dim}(\gf)}\prod_{\alpha\in\Delta^{+}}\frac{\Theta^{(\hat A_{1})}_{\alpha}(\tau,z))}{\eta(\tau)}
+\end{multline}
+Here $z\in P_{\geq 0}\otimes \mathbb{C}$. Using Weyl denominator identity this relation can be
+rewritten as a non-trivial relation connecting theta-functions of algebras $\gfh,\hat\sfr,\afh$:
+\begin{equation}
+  \label{eq:6}
+  \left(\sum_{v\in W_{\af}}\epsilon(v) \Theta^{(\afh)}_{v\rho_{\af}}(\tau,z)\right)
+  \cdot \left(\sum_{u\in W_{\sfr}}\epsilon(u) \Theta^{(\hat{\sfr})}_{\phi\circ(u\rho_{\sfr})}(\tau,z)\right)= 
+  \left(\sum_{w\in W}\epsilon(w) \Theta^{(\gfh)}_{w\rho_{\gf}}(\tau,z)\right)
+\end{equation}
+
 \bibliography{bibliography}{}

### 2013-05-03 AffineLieAlgebras/Simons/talk.tex
Added some notes from Simons center visit

@@
 \documentclass[a4paper]{article}
+\usepackage{verbatim}
+\usepackage{amsmath,amssymb,amsthm}
+\newcommand{\gfh}{\hat{\mathfrak{g}}}
+\newcommand{\gf}{\mathfrak{g}}
+\newcommand{\af}{\mathfrak{a}}
 
@@
 
+\section{Title}
+\label{sec:title}
+
 Hello!
-It's a great pleasure for me to be here in Simons Center for geometry and physics. 
-My talk is called ``Boundary condition changing operators and singular vectors of Virasoro and
-affine Lie algebra modules''.
+
+It's a great pleasure for me to be here in Simons Center for geometry and physics. My name is Anton
+Nazarov. I am work in St. Petersburg state university and my talk is called ``Boundary condition
+changing operators and singular vectors of Virasoro and affine Lie algebra modules''.
+
+This talk is based upon my letter to JETP letters, some previous conference talks and my PhD thesis.
+
+\section{Plan of the talk}
+\label{sec:plan-talk}
+
+Plan of my talk is here. First of all I will remind you how to study martingales of Schramm-Loewner
+evolution using conformal field theory in two dimensions.
+
+Then I will talk of generalized Schramm-Loewner evolution with additional random gauge
+transformations. This process is connected with Wess-Zumino-Novikov-Witen models of conformal field
+theory.
+
+To generalize this study even further we will add the interaction with pure gauge field. Then gauge
+fixing reduces some degrees of freedom and we obtain coset models of conformal field theory and
+martingale conditions on certain class of observables in these models.
+
+I will discuss observables that can have natural interpretation as the limits of lattice
+observables. These observables contain boundary condition changing operators. Martingale condition
+can be written as an algebraic relation on boundary fields. So in Wess-Zumino-Witten and coset models
+we can use representation theory to interpret martingale condition.
 
@@
 of Schramm-Loewner stochastic differential equation.
+
+\section{Domain wall in Ising model}
+\label{sec:domain-wall-ising}
+
+I want to remind you of Schramm-Loewner evolution. Consider Ising model on triangular lattice on the
+upper half-plane  with the following boundary condition: Spins up on half of the boundary and down
+on another half. Then we have a domain boundary growing from zero. We can parametrize this growth
+with parameter $t$ and prove that in scaling limit in critical point it tends to SLE trace. 
+Consider curve up to some value of parameter $t_{I}$ and make a cut along it. Then conformal map
+$g_{t}$ maps the domain with the cut to the upper half plane. For Schramm-Loewner evolution this map
+satisfies following differential equation. It will be more convenient for me to write it another
+way. Solution of the equation gives us conformally-invariant probability measure on trajectories
+$\gamma_{t}$ in upper half-plane.
+
+\section{CFT description}
+\label{sec:cft-description}
+
+How can we describe this using conformal field theory? We can consider lattice observables in upper
+half plane. Expectation values of these observables can be obtained as an average of expectation
+values in domains with all possible cuts. For a finite lattice it can be written as a sum over all
+possible trajectories of average values of ${\cal O}$ in slit domains multiplied by probabilities of
+trajectories.
+
+But the expectation value of the observable in upper half-plane does not depend on parametrization
+of cuts, so the expectation value in slit domain should be a martingale with respect to growth of
+cut.
+
+Now we consider continuous limit in critical point. Expectation value of lattice observable is then
+given by correlation function of conformal field theory.
+
+Since we consider CFT with boundary we need to take into account boundary conditions. So we insert
+boundary condition changing operators at the tip of the trace and at the infinity. Using conformal
+map we can rewrite it on the whole half-plane.
+
+We also assume that limit of lattice observable is given by a product of primary fields in points
+$z_{1}, \dots, z_{n}$ or $w_{1},\dots,w_{n}$ after the conformal map.
+
+\section{SLE martingales}
+\label{sec:sle-martingales}
+
+Now I want to write martingale condition and analyze correlation functions that satisfy it.
+
+Use Ito formula for stochastic differential. First term here gives us this contribution, second term
+depends on primary fields $\varphi_{i}$. So the differential consists of powers of field
+transformation generators. For minimal models these generators are derivatives, so we obtain this
+differential equation on correlation function.
+
+We can rewrite this equation as algebraic relation on boundary condition changing operator. Then we
+can establish correspondence between SLE parameter $\kappa$ and CFT paramters $c$ and $h_{\phi}$.
+
+\section{SLE martingales-2}
+Let's generalize this analysis to non-minimal models. Consider Wess-Zumino-Novikov-Witten model. The
+action of this model is written for the field $\gamma$ that lives on complex plane with infinity and
+takes values in Lie group $G$ or its representation. The action consists of two termss. First term
+is the action of non-linear sigma model and the second term is topological. It is added to restore
+the conformal invariance after quantization. The model has gauge invariance and two conserved
+currents. Conformal invariance is manifest in independent conservation of holomorphic and
+antiholomorphic currents.
+
+We can use Ward identities to get commutation relation for the coefficients in power series
+expansion for the currents.
+\section{Primary fields}
+\label{sec:primary-fields}
+
+We see that coefficients in mode expansion of currents satisfy commutation relations for generators
+of affine Lie algebra $\gfh$. Sugawara construction gives us generators of Virasoro algebra in terms
+of affine Lie algebra generators.
+
+So Virasoro algebra is embedded into the universal enveloping algebra of affine Lie algebra. 
+Full chiral algebra is a semidirect product of Virasoro and affine Lie algebra with these
+commutation relations. Note that central charge is determined by the level of affine Lie algebra
+representation.
+
+Primary fields with respect to full chiral algebra are labeled by highest weights of affine Lie
+algebra representations. Conformal weight for primary field is given by this formula.
+
+\section{SLE and WZNW models}
+\label{sec:sle-wznw-models}
+
+Consider and observable in Wess-Zumino-Novikov-Witten model of the same form as in minimal models.
+
+Now we have an additional degree of freedom since we can do gauge transformations. We augment
+Schramm-Loewner evolution with random walk on the group $G$.
+
+This idea was proposed in papers by Gruzberg and Rassmussen.
+
+Now we add the differential of random gauge transform to field transformation generator. 
+Full generator look like this. Here the basis elements of Lie algebra representation and $d \Theta$
+are independent Brownian motions. We have new parameter $\tau$.
+
+\section{SLE martingales in WZNW-models}
+\label{sec:sle-martingales-wznw}
+
+Again we use Ito formula to obtain the differential equation on martingales.
+
+Here I use this notation for ${\cal L}_{-n}$ and ${\cal J}^{a}_{-n}$.
+
+The differential equation holds for all observables so for all combinations of primary fields in
+correlation function. Then it can be rewritten as an algebraic relation on boundary condition
+changing operator. ????
+
+Correlation function of arbitrary primary fields with this operator is zero. Then this state is
+level 2 null-state and action of raising operators on it is zero. So we obtain algebraic relations
+connecting $\kappa, \tau$ and $k, h_{\phi}$. In this way we get a classification of primary boundary
+condition changing operators which can sit at the tip of SLE trace.
+
+\section{Null states and singular weights of affine Lie algebra module}
+\label{sec:null-states-singular}
+
+Can we answer simple question: are there level two null states in a given affine Lie algebra Verma
+module? Yes, we can. All null states belong to Verma modules of singular weights.
+
+Consider Verma module of highest weight $\lambda$ and let $\lambda$ be integral dominant. Then the
+set of singular weights is $\{\omega (\lambda+\rho)-\rho\}$ for $\omega\in W_{\gfh}$.
+
+\section{Gauged WZNW-action and coset construction}
+\label{sec:gauged-wznw-action}
+
+We can generalize our analysis even further and consider coset models of conformal field theory.
+These models can be constructed by adding the interaction with pure gauge fields to
+Wess-Zumino-Novikov-Witten action. The fields $\alpha, \bar \alpha$ takes values in some subalgebra
+$\af$ of Lie algebra $\gf$.  So we have this action.
+
+Now the current has an additional term. If we fix gauge some degrees of freedom are restricted.
+
+Algebraic structure is determined by two algebras $\af\subset\gf$ and generators of Virasoro algebra
+are given by difference of Sugawara expressions.
+
+Note that affine subalgebra generators commute with Virasoro algebra.
+
+\section{Primary fields}
+\label{sec:primary-fields-1}
+
+In coset models we can label primary fields by pairs of weights. First weight is weight of algebra
+$\gfh$ and the second for subalgebra $\af$. Branching functions for these pairs must be non-trivial.
+Some pairs are equivalent but it is possible to take this equivalence into account.
+
+Conformal weight is equal to the difference of these expressions that are similar to conformal
+weights in Wess-Zumino-Novikov-Witten model.
+
+We also have an analogue of Knizhnik-Zamolodchikov equations that can be useful later.
+
+\section{SLE on coset space}
+\label{sec:sle-coset-space}
+
+Let me analyze the martingale condition in coset models. When I fix gauge in the model some degrees
+of freedom are frozen, so I allow only certain directions for additional random walk.
+
 \end{document}

### 2013-05-03 AffineLieAlgebras/Simons/sle-wzw-boundary.tex
Added some notes from Simons center visit

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}

\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\nfp}{\mathfrak{n}^{+}}
\newcommand{\nfm}{\mathfrak{n}^{-}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\uf}{\mathfrak{u}}
\newcommand{\sfr}{\mathfrak{s}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}

\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\sfh}{\hat{\mathfrak{s}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\begin{document}
\title{Schramm-Loewner evolution martingale equation and Cardy conditions in Wess-Zumino-Novikov-Witten models}

\maketitle

\begin{abstract}
  We can write martingale condition with respect to Schramm-Loewner evolution as an equation on
  boundary condition changing operator. This equation has discrete set of solutions, so we have a
  classification of boundary conditions producing SLE traces. On the other hand Cardy conditions
  provide full classification of conformally-invariant boundary conditions. We describe the
  intersection and difference of these two sets of solutions. 
\end{abstract}

Heroes: SLE with random gauge transforms, WZNW-model, classification of Cardy conditions solutions.

Story: WZNW-model connects parameters of SLE and random gauge transform, martingale condition leads
to classification of solutions. This classification is compared with Cardy conditions.

Consider Scharmm-Loewner evolution with additional random walk on simple Lie group $G$. It is a
stochastic process $(w_{t}, \Omega_{t}(z))$ in $\mathbb{C}\times G$ satisfying stochastic
differential equations $d w_{t}(z)=\frac{dt}{w_{t}(z)}-\sqrt{\kappa} d\xi_{t}$, $d \Omega_{t}(z) =
\frac{\sum_{a} t^{a} d\theta^{a}}{z-z_{0}}$

Consider Wess-Zumino-Novikov-Witten model on the upper half-plane.

 Correlation function of the form
$\left<\phi(0) \varphi_{1}(w_{1})\dots \varphi_{n}(w_{n}) \phi^{*}(\infty)\right>$ that is
martingale with to the stochastic process $(w_{t}(z), \Omega_{t}(z))$ $d w_{t}(z)=\frac{dt}{w_{t}(z)}-\sqrt{\kappa} d\xi_{t}$ if
and only if the state $L_{-2}+\frac{\kappa}{2} L_{-1}^{2} +\frac{\tau}{2}$

\end{document}

### 2013-05-03 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
Added some notes from Simons center visit

--- 2013-05-03 AffineLieAlgebras/Simons/sle-wzw-boundary.tex
@@
 \begin{document}
-\title{Schramm-Loewner evolution martingale equation and Cardy conditions in Wess-Zumino-Novikov-Witten models}
+\title{Schramm-Loewner evolution in tricritical Ising model}
 
@@
 
-\begin{abstract}
-  We can write martingale condition with respect to Schramm-Loewner evolution as an equation on
-  boundary condition changing operator. This equation has discrete set of solutions, so we have a
-  classification of boundary conditions producing SLE traces. On the other hand Cardy conditions
-  provide full classification of conformally-invariant boundary conditions. We describe the
-  intersection and difference of these two sets of solutions. 
-\end{abstract}
-
-Heroes: SLE with random gauge transforms, WZNW-model, classification of Cardy conditions solutions.
-
-Story: WZNW-model connects parameters of SLE and random gauge transform, martingale condition leads
-to classification of solutions. This classification is compared with Cardy conditions.
-
-Consider Scharmm-Loewner evolution with additional random walk on simple Lie group $G$. It is a
-stochastic process $(w_{t}, \Omega_{t}(z))$ in $\mathbb{C}\times G$ satisfying stochastic
-differential equations $d w_{t}(z)=\frac{dt}{w_{t}(z)}-\sqrt{\kappa} d\xi_{t}$, $d \Omega_{t}(z) =
-\frac{\sum_{a} t^{a} d\theta^{a}}{z-z_{0}}$
-
-Consider Wess-Zumino-Novikov-Witten model on the upper half-plane.
-
- Correlation function of the form
-$\left<\phi(0) \varphi_{1}(w_{1})\dots \varphi_{n}(w_{n}) \phi^{*}(\infty)\right>$ that is
-martingale with to the stochastic process $(w_{t}(z), \Omega_{t}(z))$ $d w_{t}(z)=\frac{dt}{w_{t}(z)}-\sqrt{\kappa} d\xi_{t}$ if
-and only if the state $L_{-2}+\frac{\kappa}{2} L_{-1}^{2} +\frac{\tau}{2}$
-
 \end{document}

### 2013-05-06 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
Some notes for tricritical Ising

@@
 
+Tricritical Ising: integrability (RSOS), supersymmetry (?), conformally-invariant boundary conditions, identification with CFT. 
+CFT with supersymmetry (additional generators and relations). 
+Boundary conditions, CFT primary fields and SLE. 
+SLE on superspace \cite{nagi2005stochastic,rasmussen2004stochastic} and BCFT for tricritical Ising (parameter correspondence).
+
+Proof: discrete holomorphicity and integrability. 
+(Loop description?)
+\bibliography{bibliography}{} 
+\bibliographystyle{utphys}
+
 \end{document}

### 2013-05-06 AffineLieAlgebras/Simons/tricritical.m

@@ -1,0 +1,34 @@
+c:=15/2-3*(k+1/k);
+
+Solve[c==7/10,{k}]
+
+               3         5
+Out[8]= {{k -> -}, {k -> -}}
+               5         3
+
+h:=(2-k)/(2*k);
+
+h/.Out[8]
+
+(6*k-3)/16/.Out[8]
+
+          3   7
+Out[12]= {--, --}
+          80  16
+
+          7  1
+Out[11]= {-, --}
+          6  10
+
+Syntax::sntxf: "h." cannot be followed by "/Out[8]".
+
+        15      1
+Out[6]= -- - 3 (- + k)
+        2       k
+
+Out[4]= True
+
+        15      1
+Out[2]= -- - 3 (- + k)
+        2       k
+

### 2013-05-27 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
Added some text from Chim

@@
 (Loop description?)
+
+\section{Tricritical Ising model: definition}
+\label{sec:tricr-ising-model}
+
+The 2-Dimensional tricritical Ising model is the simplest known statistical model to exhibit
+supersymmetry. This simple model has a long history of theoretical and experimental study.
+
+Several lattice realization of tricritical Ising model are possible. We consider the dilute Ising model and the $A_4$
+Restricted Solid-on-Solid (RSOS) model. The dilute Ising model has the classical Hamiltonian 
+\begin{equation}
+  \label{eq:1}
+  H = -\beta \sum_{<i,j>}\sigma_i\sigma_j - \mu \sum_{i}(\sigma_i)^2  
+\end{equation}
+where $i,j$ label the lattice sites, each of the variables $\sigma_i$
+takes three values $-1,0,1$ ($0$ represents the vacant site) and the
+first sum in (\ref{eq:1}) is made over nearest neighbor pairs. Concentration
+of the vacancies is controlled by the chemical potential $\mu$. The
+phase diagram of this system in coordinates of temperature $T$ and
+$e^{-\mu}$ is shown in Fig.~\ref{fig:phase-diagram}.
+
+\begin{figure}[h]
+  \centering{
+    \includegraphics[height=70mm]{fig1}
+    \caption{Phase diagram for the dilute Ising model}}
+  \label{fig:phase-diagram}
+\end{figure}
+
+ There are two phases
+separated by a line AB of phase transition. For low vacancies and low
+temperature, we have an ordered phase I with spontaneously broken $Z_2$
+symmetry. On the other side of the transition line we have a disordered
+phase II with unbroken symmetry. The point B is the usual critical point
+of the Ising model, and the solid segment BT corresponds to the second
+order transition belonging to the Ising model universality class. The
+dotted segment AT is a line of first order phase transition. The point T
+where the two critical segments joined smoothly is the tricritical point of the
+system. 
+%%  
+%%  This model belongs to the universality class of the
+%%  Landau-Ginzburg $\varphi^6$-theory at this tricritical point [23], so
+%%  the phase diagram could also be understood in terms
+%%  of the Landau-Ginzburg effective potential of this system [14].
+%%  This effective potential (specific free energy) is plotted
+%%  as the function of the order parameter ($<\sigma>$) of this system in Fig.2
+%%  for various regions of the phase diagram.
+%%  The ground state is degenerate in phase I,
+%%  while in phase II it is non-degenerate. There is only one vacuum
+%%  on the line BT, typical of a second order transition.
+%%  Note that along the first
+%%  order transition line AT, the vacuum is in fact three-fold degenerate.
+%%
+
+\section{Restricted solid on solid models}
+\label{sec:restr-solid-solid}
+
+The $A_4$ RSOS lattice realization of tricritical Ising models is constructed as follows.
+Consider a diagonal square lattice where the degree of
+freedom at each site can take on four values $l_i = 1, 2, 3, 4$.
+The value of $l_i$ is further constrained by the requirement
+$|l_i-l_j| = 1$ for nearest neighbor sites $i$ and $j$. We can say
+that possible spin values are labeled by nodes of $A_4$ Dynkin
+diagram and neighboring spins are labeled by connected nodes.
+
+There is a ferromagnetic next-nearest-neighbor interaction and a
+single-site interaction. The lattice can be divided into two sublattices
+I and II, where the values of $l_i$ are odd in one sublattice, and
+even in the other sublattice. There are three degenerate
+ground states as shown in Fig.~\ref{fig:vacua}.
+\begin{figure}[h]
+  \centering{
+    \includegraphics[width=90mm]{vacua}
+    \caption{Vacua for $A_4$ RSOS model}}
+  \label{fig:vacua}
+\end{figure}
+
+To make contact with the order parameter $<\sigma>$ of the Ising model
+with vacancies (\ref{eq:1}),  the ground states are labeled by $-1, 0$
+and $+1$ in Fig.~\ref{fig:vacua} \cite{chim1996boundary}.
+
+The Hamiltonian of the RSOS model is symmetric under
+the global $Z_2$ transform $l_i \to 5 - l_i$, which corresponds to the
+spin-reversal symmetry of the model (1). The three ground states will
+become identical in the bulk at the tricritical point. However the nature
+of the order parameter at the boundary will depend on the specific boundary
+condition. As shown in [2], the state $|\tilde{\Delta}_{(1,s)}\rangle$ corresponds
+to the
+boundary condition where all boundary degrees of freedom are fixed to the
+value $s$, this is illustrated in Fig.10.
+For the state $|\tilde{0}\rangle$, the boundary degrees of freedom are fixed to
+$1$, and hence the neighboring state must be in the state $2$. Thus in
+the continuum limit, the order parameter at the boundary will be in the $-1$
+vacuum, and we shall denote this boundary condition by $(-)$. The boundary
+state $|\tilde{1\over10}\rangle$ corresponds to fixing the the boundary degree
+of freedom to $2$, and the neighboring sites can be in either states $1$ or
+$3$. In this case the order parameter at the boundary may be in the $-1$ or
+$0$ vacuum. This boundary condition where the $-1$ and $0$ vacua are
+degenerate will be labeled $(-0)$.
+We can similarly associated $|\tilde{3\over5}\rangle$ with the boundary condition
+$(0+)$ where the $0$ and $+1$ vacua are degenerate at the boundary. In the
+same way, the boundary condition $(+)$ where the order parameter is fixed to
+the $+1$ vacuum will correspond to the boundary state $|\tilde{3\over2}\rangle$.
+One can regard $(-)$ and $(+)$ as ``fixed'' boundary conditions for the
+Ising model with vacancies (1).
+
+In the work of [30], they identified the boundary states
+$|\tilde{\Delta}_{(r,1)}>$ as the boundary condition where the boundary
+degrees of freedom are fixed to the value $r$, while the neighboring sites
+must be in the state $r+1$ (for $1\le{r}\le{3}$). For the boundary state
+$|\tilde{7\over16}\rangle$, this means that the boundary will be in state $2$
+and the neighboring sites will be in state $3$. This of course fixes
+the order parameter to be in the vacuum $0$ in the continuum limit, and
+we denote this the $(0)$ boundary condition. A few comments about this
+boundary condition is in order. Using the states in (17), the partition
+function of the model on the cylinder with boundaries at both ends can be
+computed. Let us define the modular parameter as $q \equiv e^{2\pi{i}\tau}$,
+where $\tau = {{iR}\over{2L}}$ on a cylinder of length $L$ and circumference
+$R$. The partition functions involving the boundary condition $(0)$ include
+$$Z_{(0)(0)}(q) = \chi_{0}(q) + \chi_{3\over2}(q), \eqno(18a)$$ and
+$$Z_{(-)(0)}(q) = \chi_{7\over16}(q). \eqno(18b)$$
+The result (18a) was conjectured earlier in [31] for the Tricritical Ising
+partition function with microscopic ``free'' boundary spins, and later
+confirmed
+by direct calculation [30] and numerically in [32, 33].
+Furthermore (18b) was also obtained in [33] by considering the partition
+function with ``mixed'' boundary condition, ie microscopic ``fixed'' and
+``free'' boundary conditions.
+Thus we concluded that the boundary condition $(0)$ is associated
+with the lattice Tricritical Ising model where the microscopic boundary spins
+are not constrained. Such lattice boundary conditions are often referred to
+in the literature as the ``free'' boundary condition, even in the conformal
+field theory.
+
+Lastly we consider the conformal boundary state $|\tilde{3\over80}\rangle$ which
+has not previously been identified. Note that it is dual to the boundary
+conditions $(-0)$ and $(0+)$, and we conjecture that it corresponds to the
+case where the boundary can exist in all three vacua. In other words, like
+in the bulk theory, the three vacua are also degenerate on the boundary. We
+shall call such boundary condition ``degenerate'' and label it as $(d)$.
+Since a great deal of ``fine-tuning'' of the boundary parameters are required
+to achieve three-fold degeneracy of the vacua, we expect the boundary
+condition $(d)$ to be unstable under perturbation by relevant boundary
+operators. This boundary condition carries the $3\over{80}$ representation of
+the Virasoro algebra, so the boundary operators that can appear along such
+a boundary is given by the Operator Product Expansion of the primary field
+$\Phi_{({3\over{80}})}$ with itself [18]. From the operator product
+$$\Phi_{({3\over{80}})}\Phi_{({3\over{80}})} = [\Phi_{(0)}] +
+[\Phi_{({1\over{10}})}] + [\Phi_{({3\over5})}] + [\Phi_{({3\over2})}],$$
+we see that two relevant boundary fields $\psi_{({3\over5})}$ and
+$\psi_{({1\over{10}})}$ can appear for this boundary condition. Perturbing by
+these relevant operators could generate renormalization group flow from the
+boundary condition $(d)$ down to a more ``stable'' boundary fixed point.
+To lend support for this speculation, we computed the boundary ground state
+degeneracy (the so-called ``$g$-factor'' [34])
+from the boundary states (17) and
+they are in order of decreasing magnitude
+$$g_{(d)} = \sqrt{2}\eta^2C; \quad g_{(-0)} = g_{(0+)} = \eta^2C,$$
+$$g_{(0)} = \sqrt{2}C; \quad \hbox{and} \quad g_{(-)} = g_{(+)} = C.$$
+The value of $g$ should decrease along renormalization group trajectories,
+and in this respect, $(d)$ would be the most ``unstable'' conformal boundary
+condition. Similar comments can be made about the two-fold degenerate
+boundary conditions $(-0)$ and $(0+)$ with the next-largest value of $g$.
+One can repeat the analysis for the associated boundary operator for these
+boundary conditions, and we found that they both admit the relevant boundary
+operator $\psi_{({3\over5})}$. Thus we expect that the perturbation of
+$(-0)$ and $(0+)$ by this operator would
+generate RG flow down to other conformal boundary conditions. This is studied
+in the next section.
+
+\section{Conformal field theory}
+\label{sec:conf-field-theory}
+
+At the tricritical point T, the system is described by the conformal field
+theory (CFT) with central charge $c={7\over10}$ \cite{friedan1985superconformal}. There are six irreducible
+representations of the Virasoro algebra, and the corresponding conformal
+dimensions $\Delta_{(r,s)}$ of the primary field $\phi_{(r,s)}$ are organized
+into a Kac table:
+\centerline{
+\vbox{
+\tabskip=0pt \offinterlineskip
+\def\hr{\noalign{\hrule}}
+\def\o{\over}
+\halign
+       {\vrule# & \hskip1em\hfil#\hskip1em&
+        \vrule# & \hskip1em\hfil#\hskip1em&
+        \vrule# & \hskip1em\hfil#\hskip1em&
+        \vrule# & \hskip1em\hfil#\hskip1em&
+        \vrule#\cr
+        \hr
+        height 14 pt &${3\o2}$ && ${3\o5}$ && ${1\o10}$ && $0$ &\cr
+        height 2 pt &\omit && \omit && \omit && \omit &\cr
+        \hr
+        height 14 pt &${7\o16}$ && ${3\o80}$ && ${3\o80}$ && ${7\o16}$ &\cr
+        height 2 pt &\omit && \omit && \omit && \omit &\cr
+        \hr
+        height 14 pt &${0}$ && ${1\o10}$ && ${3\o5}$ && ${3\o2}$ &\cr
+        height 2 pt &\omit && \omit && \omit && \omit &\cr
+        \hr}
+}}
+
+%% \centerline{{\bf Figure} 3}
+
+The fields in this theory can be classified
+according to their properties under the $Z_2$ spin-reversal transformation
+$\sigma \to -\sigma$ (this is a symmetry of the microscopic model (1)).
+In particular we have four even fields:
+the identity $I \equiv \Phi_{(0)}$, the leading
+energy density $\epsilon \equiv \Phi_{({1\over10})}$, the subleading
+energy (vacancy) density $\epsilon' \equiv \Phi_{({3\over5})}$
+and the irrelevant field $\epsilon'' \equiv \Phi_{({3\over2})}$.
+Here we use the short-hand notation $\Phi_{(\Delta)}$ for the scalar field
+$\Phi_{(\Delta,\bar\Delta)}$ with $\Delta=\bar\Delta$.
+There are two odd fields under spin-reversal: the leading spin field
+$\sigma \equiv \Phi_{({3\over80})}$, and the subleading spin field $\sigma'
+\equiv \Phi_{({7\over16})}$.
+
+In addition to the scalar fields, this conformal
+field theory also possesses
+fermion fields $G(z) \equiv \Phi_{({3\over2},0)}$ and $\bar{G}(\bar{z}) \equiv
+\Phi_{(0,{3\over2})}$. The currents $G(z)$ ($\bar{G}(\bar{z})$)
+together with the stress
+tensor $T(z)$ ($\bar{T}(\bar{z})$) generate the Neveu-Schwartz-Ramond algebra,
+hence this model exhibits superconformal symmetry. We can alternatively
+classify the fields in this CFT according to this extended symmetry. For
+example, in the Neveu-Schwartz sector of this CFT we have the superfield
+$$\bf\Phi_{({1\over10})}(z,\theta;\bar{z},\bar{\theta}) =
+\epsilon + \theta\bar\psi + \bar{\theta}\psi + \theta\bar{\theta}\epsilon',$$
+where $\psi \equiv \Phi_{({3\over5},{1\over10})}$, and $\bar\psi \equiv
+\Phi_{({1\over10},{3\over5})}$ are fermion and antifermion fields respectively.
+All the component fields of $\bf\Phi_{({1\over10})}$ are mutually local and,
+together with the identity operator $I$ and its descendants, they constitute
+the Neveu-Schwartz sector of this CFT. In this sector, Kramers-Wannier duality
+transformation
+acts as a second $Z_2$ symmetry under which $\bf\Phi_{({1\over10})} \to
+-\bf\Phi_{({1\over10})}$; $\theta \to -\theta$. More specifically, under
+duality
+transformation, the signs of $\epsilon, \psi$, and $\bar{G}$ are changed, while
+$I, \epsilon', \bar\psi$, and $G$ are unaltered.
+
+The spin fields $\sigma$ and $\sigma'$ provide the Ramond representation
+of the superconformal symmetry. The duality transformation converts them
+into the disorder fields $\mu$ and $\mu'$ respectively, where
+$\mu = G_{0}\sigma$, $\mu' = G_0\sigma'$. Here $G_0$ is the zero-mode
+of $G$ in the Ramond sector. Hence the Operator Product Algebras generated by
+$(I, \sigma, \sigma', \epsilon, \epsilon')$ and
+$(I, \mu, \mu', -\epsilon, \epsilon')$ are isomorphic under duality.
+In other words, the Tricritical Ising Model is a self-dual system.
+
 \bibliography{bibliography}{} 

### 2013-05-31 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
minor
Some text added

@@
 and $+1$ in Fig.~\ref{fig:vacua} \cite{chim1996boundary}.
+
+Bolzmann weights for RSOS models are defined as follows \cite{behrend2001integrable}. Consider
+graph ${\cal G}$ (Dynkin diagram $A_4$ for the tricritical Ising
+model). This graph has the adjacency matrix $G$. Let $2\cos\lambda$ be the
+highest eigenvalue of matrix $G$ and $\psi$ the corresponding eigenvector:
+\begin{equation}
+  \label{eq:2}
+  \sum_{b\in {\cal G}} G_{ab}\psi_b = 2\cos(\lambda) \psi_a
+\end{equation}
+By the Perron-Frobenius theorem $\psi_a \neq 0$ for all $a\in {\cal
+  G}$. 
+The parametrization for eigenvalue is connected with
+representation theory of Temperley-Lieb algebra ${\cal T}(L,\lambda)$,
+where $L\in \mathbb{Z}_+$ and $\lambda\in\mathbb{C}$, generated by the
+identity operator $I$ and generators $e_1,\dots, e_L$ satisfying
+\begin{equation}
+  \label{eq:3}
+  \begin{array}{l}
+    e_j^2 = 2\cos(\lambda) e_j\\
+    e_j e_k e_j = e_j, \quad |j-k|=1\\
+    e_j e_k = e_k e_j , \quad |j-k|>1
+  \end{array}
+\end{equation}
+For ${\cal G}, \lambda, \psi$ the generators of ${\cal T}(L,\lambda)$
+are given by matrices with rows and columns labeled by the paths in ${\cal G}^{L+2}$
+\begin{equation}
+  \label{eq:4}
+  \left(e_j\right)_{(a_0,\dots, a_{L+1}),(b_0,\dots,
+    b_{L+1})}=\frac{\psi^{1/2}_{a_j} \psi^{1/2}_{b_j}}{\psi_{a_{j-1}}}
+  \delta_{a_{j-1} a_{j+1}} \prod_{\substack{k=0\\k\neq j}}^{L+1}\delta_{a_k b_k}
+\end{equation}
+
+Bolzmann weights are given by the expression
+\begin{equation}
+  \label{eq:5}
+  W\left.\left(
+    \begin{array}{cc}
+      d & c\\
+      a & b
+    \end{array}\right| u \right)
+= s_1 (-u)\delta_{ac} + \frac{s_0 (u) \psi_a^{1/2}
+  \psi_c^{1/2}}{\psi_b} \delta_{bd},
+\end{equation}
+where
+  \begin{equation}
+    \label{eq:6}
+    s_r(u)=\frac{\sin(r\lambda+u)}{\sin\lambda},\quad \frac{\lambda}{\pi}\not\in\mathbb{Z}.
+%%      \left.s_r(u)\right|_{\frac{\lambda}{\pi}\in \mathbb{Z}} =
+%%      \lim_{\lambda'\to \lambda} \frac{\sin(r \lambda'
+%%        +(\lambda'-\lambda)u)}{\sin \lambda'}
+  \end{equation}
+We are interested in the case $A_4$, so $\lambda=0.62831853071796$ and
+isotropic case $u=\lambda/2$. Conformal point is
+$u=\xi_1=\xi_2=\lambda/2$. Then we have
+$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda}$.
 

### 2013-06-05 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
Minor changes,  calculations in Maxima added

@@
   \end{equation}
-We are interested in the case $A_4$, so $\lambda=0.62831853071796$ and
-isotropic case $u=\lambda/2$. Conformal point is
-$u=\xi_1=\xi_2=\lambda/2$. Then we have
-$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda}$.
+We are interested in the case $A_4$, so we have
+$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
+$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
+  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
+The isotropic case $u=\lambda/2$ with boundary parameters
+$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
+$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.
 

### 2013-06-08 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
Minor changes

@@
 
-Bolzmann weights are given by the expression
+Bolzmann  weights for the lattice faces are given by the expression
 \begin{equation}
@@
   \end{equation}
+
+Bulk weights satisfy Yang-Baxter equation \cite{behrend2001integrable}
+that leads to integrability of the model using transfer matrix
+approach.
+
   We are interested in the case $A_4$, so we have
@@
 $\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
-  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
+  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
 The isotropic case $u=\lambda/2$ with boundary parameters
@@
 $s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.
+
+Bolzmann weights for the lattice edges can differ from face weights.
+Choice of these weights corresponds to different boundary conditions.
+Conformally invariant boundary conditions for $A_4$ RSOS realization
+of the tricritical Ising model were identified in
+\cite{chim1996boundary}, boundary weights were listed in
+\cite{behrend2001integrable}.
+
+Behrend and Pearce use following labeling of boundary conditions for
+rank $g$ model:
+$\left\{(r,a)\ |\ r\in\{1,\dots,g-1\}, a\in {\cal G}\right\}$. For the
+$(1,a)$ boundary condition boundary weights are given by the equation
+\begin{equation}
+  \label{eq:8}
+  B^{1,a}\left.\left( c
+    \begin{array}{ll}
+      a & 1\\
+      a & 1
+    \end{array}\right| u, \xi \right)= \frac{s_0(\xi+u) s_1(\xi-u)
+  \psi^{1/2}_c } {s_0(2\xi) \psi_a^{1/2}}
+\end{equation}
+
+So in the $(1, a)$ boundary condition the state of every alternate
+boundary spin is fixed to be $a$, while each other boundary spin,
+with state $c$ adjacent to $a$ on ${\cal G}$, is associated with a
+weight proportional to $\psi_c^{1/2}$.
+
+These boundary weights satisfy the boundary Yang-Baxter equation.
+For the Ising and tricritical Ising models we limit ourselves with $r=1$
+boundary states.
+
+The weight of the spin configuration $C$ is equal to the product of
+face weights and boundary weights:
+\begin{equation}
+  \label{eq:7}
+  W(c)=\prod_{f\in \mathrm{faces}} W(f,C) \prod_{b\in \mathrm{boundary
+      faces}} B(b,C)
+\end{equation}
+
+\subsection{RSOS realization of Ising model}
+\label{sec:rsos-real-ising}
+
+For RSOS realization of Ising model we have:
+\begin{eqnarray}
+  \label{eq:10}
+  2 \cos\lambda = \sqrt{2}\\
+  \lambda=\frac{\pi}{4}\\
+  \psi = (1,\sqrt{2},1)
+\end{eqnarray}
+So we obtain Boltzmann weights:
+\begin{equation}
+  \label{eq:9}
+  \begin{array}{l}
+  W\left.\left(
+    \begin{array}{ll}
+      2 & 3\\
+      1 & 2
+    \end{array}\right| u \right) = \frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
+  W\left.\left(
+    \begin{array}{ll}
+      1 & 2\\
+      2 & 3
+    \end{array}\right| u
+\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
+  W\left.\left(
+    \begin{array}{ll}
+      2 & 1\\
+      3 & 2
+    \end{array}\right| u
+\right)=\frac{1}{\sqrt{2}}\frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
+  W\left.\left(
+    \begin{array}{ll}
+      3 & 2\\
+      2 & 1
+    \end{array}\right| u
+\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
+  W\left.\left(
+    \begin{array}{ll}
+      3 & 2\\
+      2 & 1
+    \end{array}\right| u
+\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
+\end{array}
+\end{equation}
 

### 2013-06-14 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
Some Mathematica code added

@@
   \label{eq:7}
-  W(c)=\prod_{f\in \mathrm{faces}} W(f,C) \prod_{b\in \mathrm{boundary
-      faces}} B(b,C)
+  W(c)=\prod_{f\in \mathrm{faces}} W(f,C) \prod_{b\in \mbox{\small{boundary
+      faces}}} B(b,C)
 \end{equation}
+
+\subsection{Mapping of RSOS and tricritical model}
+\label{sec:mapp-rsos-tricr}
+
+Weights for $A_4$ RSOS model are:
 
@@
 \end{eqnarray}
+Values on even sublattice sites are fixed to $2$ and odd sublattice
+values $1,3$ can be mapped to Ising spins $-1,+1$. Critical value for
+Ising model is $K_C=\frac{1}{2}\log (1+\sqrt{2})$.
+
 So we obtain Boltzmann weights:
@@
   \label{eq:9}
-  \begin{array}{l}
-  W\left.\left(
+  \begin{array}{lllll}
+    V_{-} &=& W\left.\left(
     \begin{array}{ll}
@@
       1 & 2
-    \end{array}\right| u \right) = \frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
-  W\left.\left(
-    \begin{array}{ll}
-      1 & 2\\
-      2 & 3
-    \end{array}\right| u
-\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
-  W\left.\left(
+    \end{array}\right| u \right) &=&   W\left.\left(
     \begin{array}{ll}
@@
     \end{array}\right| u
-\right)=\frac{1}{\sqrt{2}}\frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
-  W\left.\left(
+\right)=\frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
+H_{-}&=&W\left.\left(
+    \begin{array}{ll}
+      1 & 2\\
+      2 & 3
+    \end{array}\right| u\right) &=&  W\left.\left(
     \begin{array}{ll}
@@
 \right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
-  W\left.\left(
+
+V_{+}&=&W\left.\left(
+    \begin{array}{ll}
+      2 & 1\\
+      1 & 2
+    \end{array}\right| u
+\right)&=&   W\left.\left(
+    \begin{array}{ll}
+      2 & 3\\
+      3 & 2
+    \end{array}\right| u
+\right)= \frac{\sin\left( u\right) }{\sqrt{2}\,\sin\left(
+    \lambda\right) }-\frac{\sin\left( u-\lambda\right) }{\sin\left(
+    l\right) } = \sin(u)-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
+H_{+}&=&W\left.\left(
+    \begin{array}{ll}
+      1 & 2\\
+      2 & 1
+    \end{array}\right| u
+\right)&=&   W\left.\left(
     \begin{array}{ll}
       3 & 2\\
-      2 & 1
+      2 & 3
     \end{array}\right| u
-\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
+\right)= \frac{\sqrt{2}\sin\left( u\right) }{\sin\left(
+    \lambda\right) }-\frac{\sin\left( u-\lambda\right) }{\sin\left(
+    l\right) } = 2\sin(u)-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)
 \end{array}
 \end{equation}
+Here we have denoted by $V_{\pm}, H_{\pm}$ Boltzmann weights for
+vertical and horizontal adjacent spins with positive ($+$) or negative
+($-$) product. The case $u=\lambda/2=\frac{\pi}{8}$ is isotropic
+$\frac{V_+}{V_-}=\frac{H_+}{H_-}= 1+\sqrt{2}=e^{2 K_C}$.
+
+The crucial object in the proof of convergence of lattice correlations
+to correlation functions in critical limit is parafermionic observable
+of Smirnov, Hongler \cite{1202.2838v2}.
+
+It can be defined as follows: consider Ising configuration on a double cover of domain $\Omega$
+with singularity at $z$.
 

### 2013-06-14 AffineLieAlgebras/Simons/tricritical.m
Some Mathematica code added

@@ -60,3 +60,1103 @@ Solve::naqs: Sin[u] - Sqrt[2] Sin[-- + u]
                                     Pi
 Out[14]= Solve[Sin[u] - Sqrt[2] Sin[-- + u], u]
                                     4
+
+Solve[Sin[l+u]/Sin[l]==Sin[2*l-u]/Sin[2*l],u]
+
+Solve::ifun: Inverse functions are being used by Solve, so some solutions may
+     not be found; use Reduce for complete solution information.
+
+Out[17]= {{u -> 0}}
+
+Solve[Sin[l+u]/Sin[l]==Sin[3*l-u]/Sin[3*l],u]
+
+Solve::ifun: Inverse functions are being used by Solve, so some solutions may
+     not be found; use Reduce for complete solution information.
+
+Out[18]= {{u -> 0}}
+
+Solve[(1+v)/Sqrt[2]==Sin[u+Pi/4],u]
+
+Solve::ifun: Inverse functions are being used by Solve, so some solutions may
+     not be found; use Reduce for complete solution information.
+
+                               -Sqrt[2] - Sqrt[2] v
+                -Pi - 4 ArcSin[--------------------]
+                                        2
+Out[23]= {{u -> ------------------------------------}, 
+                                 4
+ 
+                          Sqrt[2] + Sqrt[2] v
+           -Pi + 4 ArcSin[-------------------]
+                                   2
+>    {u -> -----------------------------------}}
+                            4
+
+                                  Pi
+                  Sqrt[2] - 2 Sin[-- + u]
+                                  4
+Out[19]= {{v -> -(-----------------------)}}
+                          Sqrt[2]
+
+
+Solve[(1-v)/Sqrt[2]==Sin[Pi/4-u],u]
+
+Solve::ifun: Inverse functions are being used by Solve, so some solutions may
+     not be found; use Reduce for complete solution information.
+
+                              Sqrt[2] - Sqrt[2] v
[…]

### 2013-06-21 AffineLieAlgebras/Simons/paper.tex
Paper text on tricritical Ising started

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}

\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\nfp}{\mathfrak{n}^{+}}
\newcommand{\nfm}{\mathfrak{n}^{-}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\uf}{\mathfrak{u}}
\newcommand{\sfr}{\mathfrak{s}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}

\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\sfh}{\hat{\mathfrak{s}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\begin{document}
\title{Schramm-Loewner evolution in tricritical Ising model}
\author{Anton Nazarov}%% $^{1,2}$}

%% \address{
%%   $^1$ Department of High-Energy and Elementary Particle Physics, 
%%   Faculty of Physics, \\ SPb State University
%%   198904, Saint-Petersburg, Russia}
%% \address{
%%   $^{2}$ Chebyshev Laboratory,
%%   Faculty of Mathematics and Mechanics, \\ SPb State University
%%   199178, Saint-Petersburg, Russia\\
%% anton.nazarov@hep.phys.spbu.ru}
%% 
%% 
\maketitle

\begin{abstract}
  We consider restricted solid-on-solid realization of the tricritical Ising model on upper
  half-plane. We use conformally-invariant boundary conditions  and integrability of the model to
  show the coincidence of lattice interfaces to Schramm-Loewner evolution traces in critical point.
  We emphasize the similarity and differences with the Ising model. 
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Tricritical Ising model is the dilute Ising model in the tricritcal point.
The 2-Dimensional tricritical Ising model is the simplest known statistical model to exhibit
supersymmetry. This simple model has a long history of theoretical and experimental study.

Several lattice realization of tricritical Ising model are possible. We consider the dilute Ising model and the $A_4$
Restricted Solid-on-Solid (RSOS) model. The dilute Ising model is described by the Hamiltonian 
\begin{equation}
  \label{eq:1}
  H = -\beta \sum_{<i,j>}\sigma_i\sigma_j - \mu \sum_{i}(\sigma_i)^2  
\end{equation}
We overview the phase diagram and present restricted solid-on-solid realization of the model in
section \ref{sec:rsos-real-ising}. This model has the tricritical point $T$.

In recent
years theoretical progress in the study of critical behavior was connected with the description of
geometrical objects -- interfaces. It was achieved by the use of Scharmm-Loewner evolution. To study
the behavior of critical interfaces we consider the model on the bounded domain.

The behaviour of the model in critical
point is described by conformal field theory (CFT) with central charge $c=\frac{7}{10}$
\cite{friedan1985superconformal}.

Shramm-Loewner evolution is the stochastic differential equation that describes the growth of
conformally-invariant cut (some details here).

We use CFT data to establish the value of Schramm-Loewner evolution parameter $\kappa$. The relation
$c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}$ gives us possible values of $\kappa=\frac{16}{5},\; 5$.
The model is also simplest example of supersymmetric conformal field theory. Schramm-Loewner
evolution on superspace was introduced in \cite{nagi2005stochastic,rasmussen2004stochastic}. The
relationship between the central charge and SLE parameter in this case is
$c=\frac{15}{2}-3\left(\kappa+\frac{1}{\kappa}\right)$. It gives us
$\kappa=\frac{3}{5},\frac{5}{3}$. (? c different for different sectors? )

We consider the model on the domain with a boundary (upper half-plane). So we need to impose
conformally invariant boundary conditions. Boundary states satisfy Cardy conditions and were
classified by Chim \cite{chim1996boundary}. Conformal weights for the boundary fields are $h=0,\;
\frac{1}{10},\; \frac{3}{5},\; \frac{3}{2},\; \frac{3}{80},\; \frac{7}{16}$.

We review the Schramm-Loewner evolution and conformal field theory model for the tricritical Ising
model in section \ref{sec:conf-field-theory}.

The weights $h=\frac{1}{10},\; \frac{7}{16}$ satisfy the relationship between the parameter $\kappa$
and conformal weight of boundary condition changing operator in SLE martingale: $(3\kappa-8) h =c$.
If we consider SLE on a superspace we have the equation $h=\frac{6\kappa-3}{16}$ and get the weights
$h=\frac{7}{6}?, \frac{1}{10}$ in the Neveu-Schwartz sector and $h=\frac{3}{80}, \frac{7}{16}$ in
the Ramond-Ramond sector.

The classification of boundary states and SLE martingale condition suggests us the proper choice of
integrable boundary conditions in RSOS realization of the model. For example, the following boundary
satisfy it:
\begin{equation}
  \label{eq:2}
  \underline{\begin{array}{llllllllll}
    2 & & 2 & & 4 & & 4 & & 4\\
    &  3 & & 3 & & 3 & & 3 & &
  \end{array}}
\end{equation}
There is obviously an interface on double lattice delimiting $2$-s from $4$-s. We analyze the
boundary conditions in RSOS model and  introduce the interfaces in section
\ref{sec:bound-cond-interf}.

 Then we
select lattice observable that is martingale with respect to the interface growth.
This observable is a generalization of Smirnov-Hongler parafermionic observable []:
\begin{equation}
  \label{eq:3}
  f = \sum e^{-\mbox{winding}} e^{-Kl}
\end{equation}

In the section \ref{sec:discr-holom-observ} we show that this observable satisfy discrete s-holomorphicity
condition and is a solution of discrete boundary problem. In critical limit this gives us the
holomorphic function crucial for the proof of the convergence of the interface to SLE trace.

We list unsolved problems and future directions in conclusion \ref{sec:conclusion}.

\section{Statement of the main theorem}
\label{sec:results}

\section{RSOS realization of the Ising and tricritical Ising model}
\label{sec:rsos-real-ising}

\section{Conformal field theory and Scramm-Loewner evolution}
\label{sec:conf-field-theory}

\section{Boundary conditions and interfaces}
\label{sec:bound-cond-interf}

\section{Discrete holomorphic observable and proof of convergence}
\label{sec:discr-holom-observ}

\section{Conclusion}
\label{sec:conclusion}

\bibliography{bibliography}{} 
\bibliographystyle{utphys}

\end{document}

### 2013-06-24 AffineLieAlgebras/Simons/paper.tex
Paper outlined

@@
 \usepackage{graphicx}
+
+\newtheorem{theorem}{Theorem}
 
@@
 
-\section{Statement of the main theorem}
+\subsection{Statement of the main theorem}
 \label{sec:results}
 
+\begin{theorem}
+  For tricritical Ising model on upper half plane there exists s-holomorphic observable $f$ given by the
+  formula. It satisfies discrete boundary problem with boundary conditions. In the limit it
+  converges to analytic function. Correlation function of something $F$ can be calculated as $F=f+if$.
+\end{theorem}
 \section{RSOS realization of the Ising and tricritical Ising model}
 \label{sec:rsos-real-ising}
+
+Tricritical Ising model was introduced as a modification of the Ising model \cite{}. The model is
+the dilute Ising model with the Hamiltonian 
+\begin{equation}
+  \label{eq:1}
+  H = -\beta \sum_{<i,j>}\sigma_i\sigma_j - \mu \sum_{i}(\sigma_i)^2.
+\end{equation}
+Here $\mu$ is chemical potential of vacancies,
+if $\mu$ tends to zero we recover ordinary Ising model without vacant sites. We consider the model on some domain
+$\Omega$ in complex plane. The model has three vacuum states with the spins on all sites equal to
+$+1$, $-1$ and $0$. In tricritical point the vacuum is degenerate.
+
+(Phase diagram here)
+
+(In tricritical point this model is conformally-invariant and described by CFT)
+
+There is another lattice model in the same universality class. It is $A_4$ Restricted Solid-on-Solid
+(RSOS) model.
+
+In restricted solid-on-solid models spins on the sites take values labeled by the
+nodes of simply-laced Dynkin diagram. The values at the adjacent sites must be adjacent on the
+Dynkin diagram.
+
+The weight of the configuration $C$ is equal to the product of
+face weights and boundary weights:
+\begin{equation}
+  \label{eq:7}
+  W(c)=\prod_{f\in \mathrm{faces}} W(f,C) \prod_{b\in \mbox{\small{boundary
+      faces}}} B(b,C)
+\end{equation}
+
+Face weight is determined by the Perron-Frobenius
+eigenvector $\psi$ of the adjacency matrix $G$ of Dynkin diagram. Denote by $2\cos\lambda$ be the
+highest eigenvalue of $G$, then $\sum_{b\in {\cal G}} G_{ab}\psi_b = 2\cos(\lambda) \psi_a $ and 
+by the Perron-Frobenius theorem $\psi_a \neq 0$.
+
+Bolzmann weight for a face with vertex labels $a,b,c,d$ is given by the formula
+\begin{equation}
+  \label{eq:5}
+    W\left.\left(
+    \begin{array}{cc}
+      d & c\\
+      a & b
+    \end{array}\right| u \right)
+= s_1 (-u)\delta_{ac} + \frac{s_0 (u) \psi_a^{1/2}
+  \psi_c^{1/2}}{\psi_b} \delta_{bd},
+\end{equation}
+where
+  \begin{equation}
+    \label{eq:6}
+    s_r(u)=\frac{\sin(r\lambda+u)}{\sin\lambda},\quad \frac{\lambda}{\pi}\not\in\mathbb{Z}.
+  \end{equation}
+
+Bulk weights satisfy Yang-Baxter equation \cite{behrend2001integrable}
+that leads to integrability of the model using transfer matrix
+approach.
+
+Bolzmann weights for the lattice edges can differ from face weights.
+Choice of these weights corresponds to different boundary conditions.
+Conformally invariant boundary conditions for $A_4$ RSOS realization
+of the tricritical Ising model were identified in
+\cite{chim1996boundary}, boundary weights were listed in
+\cite{behrend2001integrable}.
+
+Behrend and Pearce use following labeling of boundary conditions for
+rank $g$ model:
+$\left\{(r,a)\ |\ r\in\{1,\dots,g-1\}, a\in {\cal G}\right\}$. For the
+$(1,a)$ boundary condition boundary weights are given by the equation
+\begin{equation}
+  \label{eq:8}
+  B^{1,a}\left.\left( c
+    \begin{array}{ll}
+      a & 1\\
+      a & 1
+    \end{array}\right| u, \xi \right)= \frac{s_0(\xi+u) s_1(\xi-u)
+  \psi^{1/2}_c } {s_0(2\xi) \psi_a^{1/2}}
+\end{equation}
+
+So in the $(1, a)$ boundary condition the state of every alternate
+boundary spin is fixed to be $a$, while each other boundary spin,
+with state $c$ adjacent to $a$ on ${\cal G}$, is associated with a
+weight proportional to $\psi_c^{1/2}$.
+
+These boundary weights satisfy the boundary Yang-Baxter equation.
+
+%%%%%%%%%%
+For the Ising and tricritical Ising models we limit ourselves with $r=1$
+boundary states. 
+%%%%%%%%%%
+
+Ising model is realized using $A_{3}$ diagram. If we enumerate the nodes by $1,2,3$ the sites with
+values $1$ and $3$ correspond to positive and negative spins and the sublattice with $2$-s is frozen
+and do not play any role.
+
+For RSOS realization of Ising model we have:
+\begin{eqnarray}
+  \label{eq:10}
+  2 \cos\lambda = \sqrt{2}\\
+  \lambda=\frac{\pi}{4}\\
+  \psi = (1,\sqrt{2},1)
+\end{eqnarray}
+Values on even sublattice sites are fixed to $2$ and odd sublattice
+values $1,3$ can be mapped to Ising spins $-1,+1$. Critical value for
+Ising model is $K_C=\frac{1}{2}\log (1+\sqrt{2})$.
+
+So we obtain Boltzmann weights:
+\begin{equation}
+  \label{eq:9}
+  \begin{array}{lllll}
+    V_{-} &=& W\left.\left(
+    \begin{array}{ll}
+      2 & 3\\
+      1 & 2
+    \end{array}\right| u \right) &=&   W\left.\left(
+    \begin{array}{ll}
+      2 & 1\\
+      3 & 2
+    \end{array}\right| u
+\right)=\frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
+H_{-}&=&W\left.\left(
+    \begin{array}{ll}
+      1 & 2\\
+      2 & 3
+    \end{array}\right| u\right) &=&  W\left.\left(
+    \begin{array}{ll}
+      3 & 2\\
+      2 & 1
+    \end{array}\right| u
+\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
+
+V_{+}&=&W\left.\left(
+    \begin{array}{ll}
+      2 & 1\\
+      1 & 2
+    \end{array}\right| u
+\right)&=&   W\left.\left(
+    \begin{array}{ll}
+      2 & 3\\
+      3 & 2
+    \end{array}\right| u
+\right)= \frac{\sin\left( u\right) }{\sqrt{2}\,\sin\left(
+    \lambda\right) }-\frac{\sin\left( u-\lambda\right) }{\sin\left(
+    l\right) } = \sin(u)-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
+H_{+}&=&W\left.\left(
+    \begin{array}{ll}
+      1 & 2\\
+      2 & 1
+    \end{array}\right| u
+\right)&=&   W\left.\left(
+    \begin{array}{ll}
+      3 & 2\\
+      2 & 3
+    \end{array}\right| u
+\right)= \frac{\sqrt{2}\sin\left( u\right) }{\sin\left(
+    \lambda\right) }-\frac{\sin\left( u-\lambda\right) }{\sin\left(
+    l\right) } = 2\sin(u)-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)
+\end{array}
+\end{equation}
+Here we have denoted by $V_{\pm}, H_{\pm}$ Boltzmann weights for
+vertical and horizontal adjacent spins with positive ($+$) or negative
+($-$) product. The case $u=\lambda/2=\frac{\pi}{8}$ is isotropic
+$\frac{V_+}{V_-}=\frac{H_+}{H_-}= 1+\sqrt{2}=e^{2 K_C}$.
+
+%% The crucial object in the proof of convergence of lattice correlations
+%% to correlation functions in critical limit is parafermionic observable
+%% of Smirnov, Hongler \cite{1202.2838v2}.
+%% 
+%% It can be defined as follows: consider Ising configuration on a double cover of domain $\Omega$
+%% with singularity at $z$. 
+%%
+
+  We are interested in the case $A_4$, so we have
+$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
+$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
+  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
+The isotropic case $u=\lambda/2$ with boundary parameters
+$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
+$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.
+
+\begin{itemize}
+\item Boltzmann weights for $A_{4}$
+\item Boundary weights ?
+\item Critical point, isotropicity
+\item Loop description (two types of loops, duality, similarity with dilute Ising model) 
+\end{itemize}
 
@@
 
+In recent
+years theoretical progress in the study of critical behavior was connected with the description of
+geometrical objects -- interfaces. It was achieved by the use of Scharmm-Loewner evolution. To study
+the behavior of critical interfaces we consider the model on the bounded domain.
+
+The behaviour of the model in critical
+point is described by conformal field theory (CFT) with central charge $c=\frac{7}{10}$
+\cite{friedan1985superconformal}.
+
+Shramm-Loewner evolution is the stochastic differential equation that describes the growth of
+conformally-invariant cut (some details here).
+
+We use CFT data to establish the value of Schramm-Loewner evolution parameter $\kappa$. The relation
+$c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}$ gives us possible values of $\kappa=\frac{16}{5},\; 5$.
+The model is also simplest example of supersymmetric conformal field theory. Schramm-Loewner
+evolution on superspace was introduced in \cite{nagi2005stochastic,rasmussen2004stochastic}. The
+relationship between the central charge and SLE parameter in this case is
+$c=\frac{15}{2}-3\left(\kappa+\frac{1}{\kappa}\right)$. It gives us
+$\kappa=\frac{3}{5},\frac{5}{3}$. (? c different for different sectors? )
+
+We consider the model on the domain with a boundary (upper half-plane). So we need to impose
+conformally invariant boundary conditions. Boundary states satisfy Cardy conditions and were
+classified by Chim \cite{chim1996boundary}. Conformal weights for the boundary fields are $h=0,\;
+\frac{1}{10},\; \frac{3}{5},\; \frac{3}{2},\; \frac{3}{80},\; \frac{7}{16}$.
+
+We review the Schramm-Loewner evolution and conformal field theory model for the tricritical Ising
+model in section \ref{sec:conf-field-theory}.
+
+The weights $h=\frac{1}{10},\; \frac{7}{16}$ satisfy the relationship between the parameter $\kappa$
+and conformal weight of boundary condition changing operator in SLE martingale: $(3\kappa-8) h =c$.
+If we consider SLE on a superspace we have the equation $h=\frac{6\kappa-3}{16}$ and get the weights
+$h=\frac{7}{6}?, \frac{1}{10}$ in the Neveu-Schwartz sector and $h=\frac{3}{80}, \frac{7}{16}$ in
+the Ramond-Ramond sector.
+
 \section{Boundary conditions and interfaces}
 \label{sec:bound-cond-interf}
+
+The classification of boundary states and SLE martingale condition suggests us the proper choice of
+integrable boundary conditions in RSOS realization of the model. For example, the following boundary
+satisfy it:
+\begin{equation}
+  \label{eq:2}
+  \underline{\begin{array}{llllllllll}
+    2 & & 2 & & 4 & & 4 & & 4\\
+    &  3 & & 3 & & 3 & & 3 & &
+  \end{array}}
+\end{equation}
+There is obviously an interface on double lattice delimiting $2$-s from $4$-s. We analyze the
+boundary conditions in RSOS model and  introduce the interfaces in section
+\ref{sec:bound-cond-interf}.
 
@@
 
+ Then we
+select lattice observable that is martingale with respect to the interface growth.
+This observable is a generalization of Smirnov-Hongler parafermionic observable []:
+\begin{equation}
+  \label{eq:3}
+  f = \sum e^{-\mbox{winding}} e^{-Kl}
+\end{equation}
+
+In the section \ref{sec:discr-holom-observ} we show that this observable satisfy discrete s-holomorphicity
+condition and is a solution of discrete boundary problem. In critical limit this gives us the
+holomorphic function crucial for the proof of the convergence of the interface to SLE trace.
+
 \section{Conclusion}
 \label{sec:conclusion}
+
+We list unsolved problems and future directions in conclusion \ref{sec:conclusion}.
 

### 2013-06-25 AffineLieAlgebras/Simons/paper.tex
Added some text and acknoledgements

@@
 
-Tricritical Ising model was introduced as a modification of the Ising model \cite{}. The model is
+Tricritical Ising model was introduced as a modification of the Ising model \cite{} (See Malte Henkel ``Conformal invariance and critical phenomena'' 430, 408). (pp 14, 221, 340).
+
+Blume-Capel model. Critical exponents [430]. Mathematica program for CFT: Lassig Mussardo CPC 66, 71 (1991) [423].
+
+ The model is
 the dilute Ising model with the Hamiltonian 
@@
 
+Bolzmann weights are
+\begin{equation}
+  \label{eq:4}
+    \begin{array}{lllll}
+    V_{-} &=& W\left.\left(
+    \begin{array}{ll}
+      2 & 3\\
+      1 & 2
+    \end{array}\right| u \right) &=&   W\left.\left(
+    \begin{array}{ll}
+      2 & 1\\
+      3 & 2
+    \end{array}\right| u
+\right)=\frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
+\end{equation}
+
 \begin{itemize}
@@
 
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+
+This research was started during my stay at Simons center for geometry and physics in Stony Brook
+university. I thank Simons foundation for the financial support during my stay, the organizers of
+the program ``Conformal geometry'' and Simons center staff for their hospitality. I also thank
+Christian Hagendorff(?) and Dmitry Chelkak for fruitful discussions.
+
+This work  is supported by
+the Chebyshev Laboratory (Department of Mathematics and Mechanics,
+Saint-Petersburg State University) under the grant 11.G34.31.0026
+of the Government of the Russian Federation and by the Dynasty foundation.
+
+I am grateful to my wife Alexandra for her constant support and care.
+
 \bibliography{bibliography}{} 

### 2013-06-26 AffineLieAlgebras/Simons/paper.tex
Some text added

@@
   4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
-The isotropic case $u=\lambda/2$ with boundary parameters
-$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
+
+For simplicity we consider only the isotropic case $u=\lambda/2$ with boundary parameters
+$u=\xi_1=\xi_2=\lambda/2$. This case in critical limit corresponds to the  conformal point. Then we have
 $s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.
 
-Bolzmann weights are
+There are 14 configurations with Bolzmann weights:
 \begin{equation}
-  \label{eq:4}
-    \begin{array}{lllll}
-    V_{-} &=& W\left.\left(
-    \begin{array}{ll}
-      2 & 3\\
+  \label{eq:12}
+  \begin{array}{l}
+    W\left(                                          
+        \begin{array}{cc}
+          2 & 1 \\
           1 & 2
-    \end{array}\right| u \right) &=&   W\left.\left(
-    \begin{array}{ll}
-      2 & 1\\
+        \end{array}
+      \right)=
+    W\left(
+        \begin{array}{cc}
+          3 & 4 \\
+          4 & 3
+        \end{array}
+      \right)=
+\frac{\sqrt{2+\frac{2}{\sqrt{5}}}
+      \left(3+\sqrt{5}\right) \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4}
+          \left(1+\sqrt{5}\right)\right)\right)}{1+\sqrt{5}}\\
+    W\left(                                      
+        \begin{array}{cc}
+          2 & 3 \\
+          1 & 2
+        \end{array}
+      \right)=
+    W\left(                                         
+        \begin{array}{cc}
+          3 & 2 \\
+          4 & 3
+        \end{array}
+      \right)=    W\left(                                         
+        \begin{array}{cc}
+          3 & 4 \\
+          2 & 3
+        \end{array}
+      \right)=    W\left(                                         
+        \begin{array}{cc}
+          2 & 1 \\
           3 & 2
-    \end{array}\right| u
-\right)=\frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
+        \end{array}
+      \right)=\frac{2 \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4}
+          \left(1+\sqrt{5}\right)\right)\right)}{\sqrt[4]{5}}\\
+    W\left(                                         
+        \begin{array}{cc}
+          1 & 2 \\
+          2 & 1
+        \end{array}
+      \right)= 
+      W\left(                                                  
+        \begin{array}{cc}
+          4 & 3 \\
+          3 & 4
+        \end{array}
+      \right)=\left(3+\sqrt{5}\right) \sqrt{\frac{1}{10}
+      \left(5+\sqrt{5}\right)} \sin
+    \left(\frac{1}{2}\cos^{-1}\left(\frac{1}{4}
+        \left(1+\sqrt{5}\right)\right)\right) \\  
+    W\left(                                       
+        \begin{array}{cc}
+          3 & 2 \\
+          2 & 1
+        \end{array}
+      \right)=
+    W\left(                                                       
+        \begin{array}{cc}
+          1 & 2 \\
+          2 & 3
+        \end{array}
+      \right)=    W\left(                                                      
+        \begin{array}{cc}
+          4 & 3 \\
+          3 & 2
+        \end{array}
+      \right)=
+    W\left(                                                        
+        \begin{array}{cc}
+          2 & 3 \\
+          3 & 4
+        \end{array}
+      \right)=\\
+    \quad\quad\quad\sqrt{2+\frac{2}{\sqrt{5}}} \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4} \left(1+\sqrt{5}\right)\right)\right)\\
+    W\left(
+        \begin{array}{cc}
+          3 & 2 \\
+          2 & 3
+        \end{array}
+      \right)=    W\left(
+        \begin{array}{cc}
+          2 & 3 \\
+          3 & 2
+        \end{array}
+      \right)=2 \sqrt{2+\frac{2}{\sqrt{5}}} \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4} \left(1+\sqrt{5}\right)\right)\right)\\
+
+  \end{array}
 \end{equation}
 
+We see the duality under the exchange $1\leftrightarrow 4, 2\leftrightarrow 3$.
+
+Boundary weights are in correspondence with the choice of boundary
+conditions. Possible integrable boundary conditions and boundary
+weights were identified in \cite{behrend2001integrable}.
+
+The $A_4$ RSOS model admits following loop description. Consider odd
+sublattice with values at sites equal to $1,3$ and draw loops around
+$4$s on it. Then consider even sublattice and draw loops around $1$s.
+The loops do not intersect. Loop picture characterizes configuration
+up to duality.
+
+Consider following boundary condition:
+\begin{equation}
+  \label{eq:13}
+  \underline{\begin{array}{llllllllll}
+    & 3 & & 1 &  & 3 & - & 3 & & \\
+    2 & & 2 &  & 2 & | & 4 & | & 2\\
+    & 1 & & 3 & - & 3 & & 3 &- & \\
+    2 & & 2 & | & 4 & & 4 & & 4\\
+    &  3 & & 3 &- & 3 &- & 3 &- &\dots
+  \end{array}}
+\end{equation}
+There is obviously an interface on double lattice delimiting $2$-s from $4$-s. We analyze the
+
 \begin{itemize}
-\item Boltzmann weights for $A_{4}$
 \item Boundary weights ?
-\item Critical point, isotropicity
 \item Loop description (two types of loops, duality, similarity with dilute Ising model) 

### 2013-06-27 AffineLieAlgebras/Simons/paper.tex
Some text on SLE and CFT (copy)

@@
 
-Tricritical Ising model was introduced as a modification of the Ising model \cite{} (See Malte Henkel ``Conformal invariance and critical phenomena'' 430, 408). (pp 14, 221, 340).
+Tricritical Ising model was introduced as a modification of the Ising
+model \cite{} (See Malte Henkel ``Conformal invariance and critical
+phenomena'' 430, 408). (pp 14, 221, 340).
 
@@
 \end{equation}
-There is obviously an interface on double lattice delimiting $2$-s from $4$-s. We analyze the
+There is obviously an interface on double lattice delimiting $2$-s
+from $4$-s. We need to prove conformal invariance of this interface.
 
@@
 
+Connection of interfaces in restricted solid-on-solid models with
+Schramm-Loewner evolution and conformal field theory was discussed in
+the paper \cite{cardy2007ade}, but no rigorous proof was given.
+
 In recent
 years theoretical progress in the study of critical behavior was connected with the description of
-geometrical objects -- interfaces. It was achieved by the use of Scharmm-Loewner evolution. To study
-the behavior of critical interfaces we consider the model on the bounded domain.
+geometrical objects -- interfaces. It was achieved by the use of
+Scharmm-Loewner evolution \cite{schramm2000scaling}, which is
+introduced as follows. 
+Consider some critical lattice model on the upper half-plane
+$\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$
+(domain wall up to some length $t$). We denote this slit domain by
+$\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$. Assume that
+$\gamma_{t}$ satisfies restriction property and is conformally
+invariant \cite{Cardy:2005kh}. Then conformal map
+$g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ satisfies stochastic differential
+equation \cite{schramm2000scaling}:
+\begin{equation}
+\label{eq:19}
+  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
+\end{equation}
+where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.
 
-The behaviour of the model in critical
+Sometimes it is more convenient to use the map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
+\begin{equation}
+  \label{eq:20}
+       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}d\xi_{t}  
+\end{equation}
+
+To establish the connection with conformal field theory one needs to
+consider $N$-point correlation function of boundary CFT with boundary
+condition changing operators $\varphi$ sitting at the tip of SLE trace
+$z_t$ and at the infinity:
+\begin{equation}
+  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\}_{i=1}^{N})_{\mathbb{H}_{t}}=
+\left<\varphi(z_{t}) \phi_{1}(z_{1},\bar z_{1}) \dots \phi_{n}(z_{n},\bar z_{n})
+      \varphi(\infty)\right>,
+    \label{eq:14}
+\end{equation}
+where $\phi_{i}$ are bulk primary fields with conformal weights $h_i$.
+Then use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite expression \eqref{eq:14} in the whole upper half plane:
+\begin{multline}
+  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\})_{\mathbb{H}_{t}}=\\
+  =\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{i}} 
+  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{\bar h_i}
+  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
+  \label{eq:4}
+\end{multline}
+To extend the definition of $\mathcal{F}$ to the whole plane we need
+to double the number of fields $\phi_{i}$
+\cite{cardy2004boundary,cardy1984conformal} and consider $w_{i},\bar
+w_{i}$ as independent variables. For simplicity we will write
+$\mathcal{F}(\left\{w_{i}\right\}_{i=1}^{2N})$.
+
+Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in the right-hand-side of equation (\ref{eq:1}) gives us
+\begin{equation*}
+  -\frac{2h_{i}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}.
+\end{equation*}
+We denote by $\mathcal{G}_{i}$ the generator of infinitesimal
+transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) =
+\mathcal{G}_{i}\phi_{i}(w_{i})$:
+ The generator of field transformation is equal to
+\begin{equation}
+  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}.
+  \label{eq:11}
+\end{equation}
+
+The differential of $\mathcal{F}$ should be zero due to martingale condition.
+Ito formula is used to calculate the differential.
+We need to include second order terms in  $\mathcal{G}_{i}$ since they contain squares of Brownian motion differential $d\xi_{t}$ with the expectation value proportional to $dt$ ($\mathbb{E}[d\xi_{t}^{2}]=dt$):
+\begin{multline}
+d \mathcal{F}_{\mathbb{H}_{t}}=\\ \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)
+\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
+      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}\\=0
+\label{eq:8}
+\end{multline}
+Substituting  definition \eqref{eq:11} we get 
+\begin{equation}
+  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}\right)        \mathcal{F}_{\mathbb{H}}=0,
+  \label{eq:4}
+\end{equation}
+with
+\begin{eqnarray*}
+  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right).
+\end{eqnarray*}
+This equation is equivalent to the algebraic condition on the boundary state $\varphi(0)\left|0\right>$:
+\begin{multline}
+  \label{eq:7}
+  \left<0\left|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})
+  \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}\right)
+\varphi(0)\right|0\right>=0.
+\end{multline}
+Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that 
+\begin{equation}
+|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}\right)
+\varphi(0)|0>
+\end{equation}
+is a null-state. Now act on $\psi$ by raising operators to get
+equations connecting  $\kappa$, central charge $c$ and conformal
+weight of boundary condition changing operator $h$.
+\begin{eqnarray}
+  \label{eq:15}
+  c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}\\
+  h=\frac{c}{3\kappa-8}
+\end{eqnarray}
+
+The behaviour of the dilute Ising and $A_4$ RSOS  models in tricritical
 point is described by conformal field theory (CFT) with central charge $c=\frac{7}{10}$
@@
 
-Shramm-Loewner evolution is the stochastic differential equation that describes the growth of
-conformally-invariant cut (some details here).
+We use CFT data to establish the value of Schramm-Loewner evolution parameter $\kappa$. The relation
+$c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}$ gives us possible values of
+$\kappa=\frac{16}{5},\; 5$. Boundary states satisfy Cardy conditions and were
+classified by Chim \cite{chim1996boundary}. Conformal weights for the boundary fields are $h=0,\;
+\frac{1}{10},\; \frac{3}{5},\; \frac{3}{2},\; \frac{3}{80},\;
+\frac{7}{16}$.
 
-We use CFT data to establish the value of Schramm-Loewner evolution parameter $\kappa$. The relation
-$c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}$ gives us possible values of $\kappa=\frac{16}{5},\; 5$.
+Substituting $c=7/10, \kappa=16/5, 5$ in equations (\ref{eq:15}) we
+obtain following possible values for conformal weight of boundary
+condition changing operator: $h=7/16,1/10$
+
 The model is also simplest example of supersymmetric conformal field theory. Schramm-Loewner
@@
 We consider the model on the domain with a boundary (upper half-plane). So we need to impose
-conformally invariant boundary conditions. Boundary states satisfy Cardy conditions and were
-classified by Chim \cite{chim1996boundary}. Conformal weights for the boundary fields are $h=0,\;
-\frac{1}{10},\; \frac{3}{5},\; \frac{3}{2},\; \frac{3}{80},\; \frac{7}{16}$.
+conformally invariant boundary conditions.
 

### 2013-06-27 AffineLieAlgebras/Simons/tricritical.m
Some calculations

@@ -501,662 +501,280 @@ Out[86]= W$179[#1, #2, #3, #4, ------] &
         
 Clear[W]
 
-Select[Flatten[Table[MatrixForm[{{d,c},{a,b}}]==w[a,b,c,d],{a,1,4},{b,1,4},{c,1,4},{d,1,4}]],#[[2]]=!=0&]
+Table[W[{{d,c},{a,b}}]==w[a,b,c,d],{a,1,4},{b,1,4},{c,1,4},{d,1,4}]
 
-Out[108]= {W[{{2, 1}, {1, 2}}] == 
+Out[104]= {{{{W[{{1, 1}, {1, 1}}] == 0., W[{{2, 1}, {1, 1}}] == 0., 
  
-                 1 + Sqrt[5]                        1 + Sqrt[5]
-          ArcCos[-----------]                ArcCos[-----------]
-                      4                                  4
-      Sin[-------------------]         2 Sin[-------------------]
-                   2                                  2
->     ------------------------ + --------------------------------------, 
-                            2                                        2
-               (1 + Sqrt[5])                            (1 + Sqrt[5])
-      Sqrt[1 - --------------]   (1 + Sqrt[5]) Sqrt[1 - --------------]
-                     16                                       16
+>       W[{{3, 1}, {1, 1}}] == 0., W[{{4, 1}, {1, 1}}] == 0.}, 
  
-                                                 2
->    W[{{2, 3}, {1, 2}}] == Sqrt[----------------------------------] 
-                                                                 2
-                                                    (1 + Sqrt[5])
-                                 (1 + Sqrt[5]) (1 - --------------)
-                                                          16
+>      {W[{{1, 2}, {1, 1}}] == 0., W[{{2, 2}, {1, 1}}] == 0., 
  
-                  1 + Sqrt[5]
-           ArcCos[-----------]
-                       4
->      Sin[-------------------], 
-                    2
+>       W[{{3, 2}, {1, 1}}] == 0., W[{{4, 2}, {1, 1}}] == 0.}, 
  
-                                       1 + Sqrt[5]
-                                ArcCos[-----------]
-                                            4
-                            Sin[-------------------]
-                                         2
->    W[{{1, 2}, {2, 1}}] == ------------------------ + 
-                                                  2
-                                     (1 + Sqrt[5])
-                            Sqrt[1 - --------------]
-                                           16
[…]

### 2013-07-09 AffineLieAlgebras/Simons/paper.tex
Added kappa=5, s=3/5
Cardy values added

@@
   formula. It satisfies discrete boundary problem with boundary conditions. In the limit it
-  converges to analytic function. Correlation function of something $F$ can be calculated as $F=f+if$.
+  converges to analytic function. Correlation function of something
+  $F$ can be calculated as $F=f+if$.
+
+  $f$ is defined on dual lattice. 
+  \begin{eqnarray}
+    \label{eq:17}
+    f=\sum_{C\in \mbox{conf}|\gamma:a\to z} W(C) e^{-i s \Theta}\\
+    s=3/5\\
+    \kappa=5
+  \end{eqnarray}
 \end{theorem}
@@
   We are interested in the case $A_4$, so we have
+$2\cos\lambda=\frac{1+\sqrt{5}}{2}$, $\lambda=\pi/5$, $\psi=\left[1,2\cos\lambda,2\cos\lambda,1\right]$.
 $2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
@@
       \right)=2 \sqrt{2+\frac{2}{\sqrt{5}}} \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4} \left(1+\sqrt{5}\right)\right)\right)\\
+
+  \end{array}
+\end{equation}
+
+\begin{equation}
+  \label{eq:12}
+  \begin{array}{l}
+    W\left(                                          
+        \begin{array}{cc}
+          2 & 1 \\
+          1 & 2
+        \end{array}
+      \right)=
+    W\left(
+        \begin{array}{cc}
+          3 & 4 \\
+          4 & 3
+        \end{array}
+      \right)=   W\left(                                         
+        \begin{array}{cc}
+          1 & 2 \\
+          2 & 1
+        \end{array}
+      \right)= \\
+      W\left(                                                  
+        \begin{array}{cc}
+          4 & 3 \\
+          3 & 4
+        \end{array}
+      \right)=\sqrt{\frac{2}{1+\sqrt{5}}}+\sqrt{\frac{1}{2}\left(1+\sqrt{5}\right)\\
+    W\left(                                      
+        \begin{array}{cc}
+          2 & 3 \\
+          1 & 2
+        \end{array}
+      \right)=
+    W\left(                                         
+        \begin{array}{cc}
+          3 & 2 \\
+          4 & 3
+        \end{array}
+      \right)=    W\left(                                         
+        \begin{array}{cc}
+          3 & 4 \\
+          2 & 3
+        \end{array}
+      \right)=    W\left(                                         
+        \begin{array}{cc}
+          2 & 1 \\
+          3 & 2
+        \end{array}
+      \right)=\\
+    W\left(                                       
+        \begin{array}{cc}
+          3 & 2 \\
+          2 & 1
+        \end{array}
+      \right)=
+    W\left(                                                       
+        \begin{array}{cc}
+          1 & 2 \\
+          2 & 3
+        \end{array}
+      \right)=    W\left(                                                      
+        \begin{array}{cc}
+          4 & 3 \\
+          3 & 2
+        \end{array}
+      \right)=
+    W\left(                                                        
+        \begin{array}{cc}
+          2 & 3 \\
+          3 & 4
+        \end{array}
+      \right)=
+\sqrt[4]{\frac{2}{1+\sqrt{5}}}\\
+    W\left(
+        \begin{array}{cc}
+          3 & 2 \\
+          2 & 3
+        \end{array}
+      \right)=    W\left(
+        \begin{array}{cc}
+          2 & 3 \\
+          3 & 2
+        \end{array}
+      \right)=2
 

### 2013-07-10 area-length/notes.tex
Area-length notes added

--- 2013-06-26 AffineLieAlgebras/Simons/paper.tex
@@
 \begin{document}
-\title{Schramm-Loewner evolution in tricritical Ising model}
+\title{Notes on area-length problem for CLE}
 \author{Anton Nazarov}%% $^{1,2}$}
 
-%% \address{
-%%   $^1$ Department of High-Energy and Elementary Particle Physics, 
-%%   Faculty of Physics, \\ SPb State University
-%%   198904, Saint-Petersburg, Russia}
-%% \address{
-%%   $^{2}$ Chebyshev Laboratory,
-%%   Faculty of Mathematics and Mechanics, \\ SPb State University
-%%   199178, Saint-Petersburg, Russia\\
-%% anton.nazarov@hep.phys.spbu.ru}
-%% 
-%% 
 \maketitle
@@
 \begin{abstract}
-  We consider restricted solid-on-solid realization of the tricritical Ising model on upper
-  half-plane. We use conformally-invariant boundary conditions  and integrability of the model to
-  show the coincidence of lattice interfaces to Schramm-Loewner evolution traces in critical point.
-  We emphasize the similarity and differences with the Ising model. 
+  Here I document staff related to my work on area-length problem.
 \end{abstract}
 
-\section{Introduction}
-\label{sec:introduction}
-
-Tricritical Ising model is the dilute Ising model in the tricritcal point.
-The 2-Dimensional tricritical Ising model is the simplest known statistical model to exhibit
-supersymmetry. This simple model has a long history of theoretical and experimental study.
-
-Several lattice realization of tricritical Ising model are possible. We consider the dilute Ising model and the $A_4$
-Restricted Solid-on-Solid (RSOS) model. The dilute Ising model is described by the Hamiltonian 
-\begin{equation}
-  \label{eq:1}
-  H = -\beta \sum_{<i,j>}\sigma_i\sigma_j - \mu \sum_{i}(\sigma_i)^2  
-\end{equation}
-We overview the phase diagram and present restricted solid-on-solid realization of the model in
-section \ref{sec:rsos-real-ising}. This model has the tricritical point $T$.
-
-In recent
-years theoretical progress in the study of critical behavior was connected with the description of
-geometrical objects -- interfaces. It was achieved by the use of Scharmm-Loewner evolution. To study
-the behavior of critical interfaces we consider the model on the bounded domain.
-
-The behaviour of the model in critical
-point is described by conformal field theory (CFT) with central charge $c=\frac{7}{10}$
-\cite{friedan1985superconformal}.
-
-Shramm-Loewner evolution is the stochastic differential equation that describes the growth of
-conformally-invariant cut (some details here).
-
-We use CFT data to establish the value of Schramm-Loewner evolution parameter $\kappa$. The relation
-$c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}$ gives us possible values of $\kappa=\frac{16}{5},\; 5$.
-The model is also simplest example of supersymmetric conformal field theory. Schramm-Loewner
-evolution on superspace was introduced in \cite{nagi2005stochastic,rasmussen2004stochastic}. The
-relationship between the central charge and SLE parameter in this case is
-$c=\frac{15}{2}-3\left(\kappa+\frac{1}{\kappa}\right)$. It gives us
-$\kappa=\frac{3}{5},\frac{5}{3}$. (? c different for different sectors? )
-
-We consider the model on the domain with a boundary (upper half-plane). So we need to impose
-conformally invariant boundary conditions. Boundary states satisfy Cardy conditions and were
-classified by Chim \cite{chim1996boundary}. Conformal weights for the boundary fields are $h=0,\;
-\frac{1}{10},\; \frac{3}{5},\; \frac{3}{2},\; \frac{3}{80},\; \frac{7}{16}$.
-
-We review the Schramm-Loewner evolution and conformal field theory model for the tricritical Ising
-model in section \ref{sec:conf-field-theory}.
-
-The weights $h=\frac{1}{10},\; \frac{7}{16}$ satisfy the relationship between the parameter $\kappa$
-and conformal weight of boundary condition changing operator in SLE martingale: $(3\kappa-8) h =c$.
-If we consider SLE on a superspace we have the equation $h=\frac{6\kappa-3}{16}$ and get the weights
-$h=\frac{7}{6}?, \frac{1}{10}$ in the Neveu-Schwartz sector and $h=\frac{3}{80}, \frac{7}{16}$ in
-the Ramond-Ramond sector.
-
-The classification of boundary states and SLE martingale condition suggests us the proper choice of
-integrable boundary conditions in RSOS realization of the model. For example, the following boundary
-satisfy it:
-\begin{equation}
-  \label{eq:2}
-  \underline{\begin{array}{llllllllll}
-    2 & & 2 & & 4 & & 4 & & 4\\
-    &  3 & & 3 & & 3 & & 3 & &
-  \end{array}}
-\end{equation}
-There is obviously an interface on double lattice delimiting $2$-s from $4$-s. We analyze the
-boundary conditions in RSOS model and  introduce the interfaces in section
-\ref{sec:bound-cond-interf}.
-
- Then we
-select lattice observable that is martingale with respect to the interface growth.
-This observable is a generalization of Smirnov-Hongler parafermionic observable []:
-\begin{equation}
-  \label{eq:3}
-  f = \sum e^{-\mbox{winding}} e^{-Kl}
-\end{equation}
-
-In the section \ref{sec:discr-holom-observ} we show that this observable satisfy discrete s-holomorphicity
-condition and is a solution of discrete boundary problem. In critical limit this gives us the
-holomorphic function crucial for the proof of the convergence of the interface to SLE trace.
-
-We list unsolved problems and future directions in conclusion \ref{sec:conclusion}.
-
-\subsection{Statement of the main theorem}
-\label{sec:results}
-
-\begin{theorem}
-  For tricritical Ising model on upper half plane there exists s-holomorphic observable $f$ given by the
-  formula. It satisfies discrete boundary problem with boundary conditions. In the limit it
-  converges to analytic function. Correlation function of something $F$ can be calculated as $F=f+if$.
-\end{theorem}
-\section{RSOS realization of the Ising and tricritical Ising model}
-\label{sec:rsos-real-ising}
-
-Tricritical Ising model was introduced as a modification of the Ising model \cite{} (See Malte Henkel ``Conformal invariance and critical phenomena'' 430, 408). (pp 14, 221, 340).
-
-Blume-Capel model. Critical exponents [430]. Mathematica program for CFT: Lassig Mussardo CPC 66, 71 (1991) [423].
-
- The model is
-the dilute Ising model with the Hamiltonian 
-\begin{equation}
-  \label{eq:1}
-  H = -\beta \sum_{<i,j>}\sigma_i\sigma_j - \mu \sum_{i}(\sigma_i)^2.
-\end{equation}
-Here $\mu$ is chemical potential of vacancies,
-if $\mu$ tends to zero we recover ordinary Ising model without vacant sites. We consider the model on some domain
-$\Omega$ in complex plane. The model has three vacuum states with the spins on all sites equal to
-$+1$, $-1$ and $0$. In tricritical point the vacuum is degenerate.
-
-(Phase diagram here)
-
-(In tricritical point this model is conformally-invariant and described by CFT)
-
-There is another lattice model in the same universality class. It is $A_4$ Restricted Solid-on-Solid
-(RSOS) model.
-
-In restricted solid-on-solid models spins on the sites take values labeled by the
-nodes of simply-laced Dynkin diagram. The values at the adjacent sites must be adjacent on the
-Dynkin diagram.
-
-The weight of the configuration $C$ is equal to the product of
-face weights and boundary weights:
-\begin{equation}
-  \label{eq:7}
-  W(c)=\prod_{f\in \mathrm{faces}} W(f,C) \prod_{b\in \mbox{\small{boundary
-      faces}}} B(b,C)
-\end{equation}
-
-Face weight is determined by the Perron-Frobenius
-eigenvector $\psi$ of the adjacency matrix $G$ of Dynkin diagram. Denote by $2\cos\lambda$ be the
-highest eigenvalue of $G$, then $\sum_{b\in {\cal G}} G_{ab}\psi_b = 2\cos(\lambda) \psi_a $ and 
-by the Perron-Frobenius theorem $\psi_a \neq 0$.
-
-Bolzmann weight for a face with vertex labels $a,b,c,d$ is given by the formula
-\begin{equation}
-  \label{eq:5}
-    W\left.\left(
-    \begin{array}{cc}
-      d & c\\
-      a & b
-    \end{array}\right| u \right)
-= s_1 (-u)\delta_{ac} + \frac{s_0 (u) \psi_a^{1/2}
-  \psi_c^{1/2}}{\psi_b} \delta_{bd},
-\end{equation}
-where
-  \begin{equation}
-    \label{eq:6}
-    s_r(u)=\frac{\sin(r\lambda+u)}{\sin\lambda},\quad \frac{\lambda}{\pi}\not\in\mathbb{Z}.
-  \end{equation}
-
-Bulk weights satisfy Yang-Baxter equation \cite{behrend2001integrable}
-that leads to integrability of the model using transfer matrix
-approach.
-
-Bolzmann weights for the lattice edges can differ from face weights.
-Choice of these weights corresponds to different boundary conditions.
-Conformally invariant boundary conditions for $A_4$ RSOS realization
-of the tricritical Ising model were identified in
-\cite{chim1996boundary}, boundary weights were listed in
-\cite{behrend2001integrable}.
-
-Behrend and Pearce use following labeling of boundary conditions for
-rank $g$ model:
-$\left\{(r,a)\ |\ r\in\{1,\dots,g-1\}, a\in {\cal G}\right\}$. For the
-$(1,a)$ boundary condition boundary weights are given by the equation
-\begin{equation}
-  \label{eq:8}
-  B^{1,a}\left.\left( c
-    \begin{array}{ll}
-      a & 1\\
-      a & 1
-    \end{array}\right| u, \xi \right)= \frac{s_0(\xi+u) s_1(\xi-u)
-  \psi^{1/2}_c } {s_0(2\xi) \psi_a^{1/2}}
-\end{equation}
-
-So in the $(1, a)$ boundary condition the state of every alternate
-boundary spin is fixed to be $a$, while each other boundary spin,
-with state $c$ adjacent to $a$ on ${\cal G}$, is associated with a
-weight proportional to $\psi_c^{1/2}$.
-
-These boundary weights satisfy the boundary Yang-Baxter equation.
-
-%%%%%%%%%%
-For the Ising and tricritical Ising models we limit ourselves with $r=1$
-boundary states. 
-%%%%%%%%%%
-
-Ising model is realized using $A_{3}$ diagram. If we enumerate the nodes by $1,2,3$ the sites with
-values $1$ and $3$ correspond to positive and negative spins and the sublattice with $2$-s is frozen
-and do not play any role.
-
-For RSOS realization of Ising model we have:
-\begin{eqnarray}
-  \label{eq:10}
-  2 \cos\lambda = \sqrt{2}\\
-  \lambda=\frac{\pi}{4}\\
-  \psi = (1,\sqrt{2},1)
-\end{eqnarray}
-Values on even sublattice sites are fixed to $2$ and odd sublattice
-values $1,3$ can be mapped to Ising spins $-1,+1$. Critical value for
-Ising model is $K_C=\frac{1}{2}\log (1+\sqrt{2})$.
-
-So we obtain Boltzmann weights:
-\begin{equation}
-  \label{eq:9}
-  \begin{array}{lllll}
-    V_{-} &=& W\left.\left(
-    \begin{array}{ll}
-      2 & 3\\
-      1 & 2
-    \end{array}\right| u \right) &=&   W\left.\left(
-    \begin{array}{ll}
-      2 & 1\\
-      3 & 2
-    \end{array}\right| u
-\right)=\frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
-H_{-}&=&W\left.\left(
-    \begin{array}{ll}
-      1 & 2\\
-      2 & 3
-    \end{array}\right| u\right) &=&  W\left.\left(
-    \begin{array}{ll}
-      3 & 2\\
-      2 & 1
-    \end{array}\right| u
-\right)=-\frac{\sin(u-\lambda)}{\sin(\lambda)}=-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
-
-V_{+}&=&W\left.\left(
-    \begin{array}{ll}
-      2 & 1\\
-      1 & 2
-    \end{array}\right| u
-\right)&=&   W\left.\left(
-    \begin{array}{ll}
-      2 & 3\\
-      3 & 2
-    \end{array}\right| u
-\right)= \frac{\sin\left( u\right) }{\sqrt{2}\,\sin\left(
-    \lambda\right) }-\frac{\sin\left( u-\lambda\right) }{\sin\left(
-    l\right) } = \sin(u)-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)\\
-H_{+}&=&W\left.\left(
-    \begin{array}{ll}
-      1 & 2\\
-      2 & 1
-    \end{array}\right| u
-\right)&=&   W\left.\left(
-    \begin{array}{ll}
-      3 & 2\\
-      2 & 3
-    \end{array}\right| u
-\right)= \frac{\sqrt{2}\sin\left( u\right) }{\sin\left(
-    \lambda\right) }-\frac{\sin\left( u-\lambda\right) }{\sin\left(
-    l\right) } = 2\sin(u)-\sqrt{2}\sin\left(u-\frac{\pi}{4}\right)
-\end{array}
-\end{equation}
-Here we have denoted by $V_{\pm}, H_{\pm}$ Boltzmann weights for
-vertical and horizontal adjacent spins with positive ($+$) or negative
-($-$) product. The case $u=\lambda/2=\frac{\pi}{8}$ is isotropic
-$\frac{V_+}{V_-}=\frac{H_+}{H_-}= 1+\sqrt{2}=e^{2 K_C}$.
-
-%% The crucial object in the proof of convergence of lattice correlations
-%% to correlation functions in critical limit is parafermionic observable
-%% of Smirnov, Hongler \cite{1202.2838v2}.
-%% 
-%% It can be defined as follows: consider Ising configuration on a double cover of domain $\Omega$
-%% with singularity at $z$. 
-%%
-
-  We are interested in the case $A_4$, so we have
-$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
-$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
-  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
-
-For simplicity we consider only the isotropic case $u=\lambda/2$ with boundary parameters
-$u=\xi_1=\xi_2=\lambda/2$. This case in critical limit corresponds to the  conformal point. Then we have
-$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.
-
-There are 14 configurations with Bolzmann weights:
-\begin{equation}
-  \label{eq:12}
-  \begin{array}{l}
-    W\left(                                          
-        \begin{array}{cc}
-          2 & 1 \\
-          1 & 2
-        \end{array}
-      \right)=
-    W\left(
-        \begin{array}{cc}
-          3 & 4 \\
-          4 & 3
-        \end{array}
-      \right)=
-\frac{\sqrt{2+\frac{2}{\sqrt{5}}}
-      \left(3+\sqrt{5}\right) \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4}
-          \left(1+\sqrt{5}\right)\right)\right)}{1+\sqrt{5}}\\
-    W\left(                                      
-        \begin{array}{cc}
-          2 & 3 \\
-          1 & 2
-        \end{array}
-      \right)=
-    W\left(                                         
-        \begin{array}{cc}
-          3 & 2 \\
-          4 & 3
-        \end{array}
-      \right)=    W\left(                                         
-        \begin{array}{cc}
-          3 & 4 \\
-          2 & 3
-        \end{array}
-      \right)=    W\left(                                         
-        \begin{array}{cc}
-          2 & 1 \\
-          3 & 2
-        \end{array}
-      \right)=\frac{2 \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4}
-          \left(1+\sqrt{5}\right)\right)\right)}{\sqrt[4]{5}}\\
-    W\left(                                         
-        \begin{array}{cc}
-          1 & 2 \\
-          2 & 1
-        \end{array}
-      \right)= 
-      W\left(                                                  
-        \begin{array}{cc}
-          4 & 3 \\
-          3 & 4
-        \end{array}
-      \right)=\left(3+\sqrt{5}\right) \sqrt{\frac{1}{10}
-      \left(5+\sqrt{5}\right)} \sin
-    \left(\frac{1}{2}\cos^{-1}\left(\frac{1}{4}
-        \left(1+\sqrt{5}\right)\right)\right) \\  
-    W\left(                                       
-        \begin{array}{cc}
-          3 & 2 \\
-          2 & 1
-        \end{array}
-      \right)=
-    W\left(                                                       
-        \begin{array}{cc}
-          1 & 2 \\
-          2 & 3
-        \end{array}
-      \right)=    W\left(                                                      
-        \begin{array}{cc}
-          4 & 3 \\
-          3 & 2
-        \end{array}
-      \right)=
-    W\left(                                                        
-        \begin{array}{cc}
-          2 & 3 \\
-          3 & 4
-        \end{array}
-      \right)=\\
-    \quad\quad\quad\sqrt{2+\frac{2}{\sqrt{5}}} \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4} \left(1+\sqrt{5}\right)\right)\right)\\
-    W\left(
-        \begin{array}{cc}
-          3 & 2 \\
-          2 & 3
-        \end{array}
-      \right)=    W\left(
-        \begin{array}{cc}
-          2 & 3 \\
-          3 & 2
-        \end{array}
-      \right)=2 \sqrt{2+\frac{2}{\sqrt{5}}} \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4} \left(1+\sqrt{5}\right)\right)\right)\\
-
-  \end{array}
-\end{equation}
-
-We see the duality under the exchange $1\leftrightarrow 4, 2\leftrightarrow 3$.
-
-Boundary weights are in correspondence with the choice of boundary
-conditions. Possible integrable boundary conditions and boundary
-weights were identified in \cite{behrend2001integrable}.
-
-The $A_4$ RSOS model admits following loop description. Consider odd
-sublattice with values at sites equal to $1,3$ and draw loops around
-$4$s on it. Then consider even sublattice and draw loops around $1$s.
-The loops do not intersect. Loop picture characterizes configuration
-up to duality.
-
-Consider following boundary condition:
-\begin{equation}
-  \label{eq:13}
-  \underline{\begin{array}{llllllllll}
-    & 3 & & 1 &  & 3 & - & 3 & & \\
-    2 & & 2 &  & 2 & | & 4 & | & 2\\
-    & 1 & & 3 & - & 3 & & 3 &- & \\
-    2 & & 2 & | & 4 & & 4 & & 4\\
-    &  3 & & 3 &- & 3 &- & 3 &- &\dots
-  \end{array}}
-\end{equation}
-There is obviously an interface on double lattice delimiting $2$-s from $4$-s. We analyze the
-
-\begin{itemize}
-\item Boundary weights ?
-\item Loop description (two types of loops, duality, similarity with dilute Ising model) 
-\end{itemize}
-
-\section{Conformal field theory and Scramm-Loewner evolution}
-\label{sec:conf-field-theory}
-
-In recent
-years theoretical progress in the study of critical behavior was connected with the description of
-geometrical objects -- interfaces. It was achieved by the use of Scharmm-Loewner evolution. To study
-the behavior of critical interfaces we consider the model on the bounded domain.
-
-The behaviour of the model in critical
-point is described by conformal field theory (CFT) with central charge $c=\frac{7}{10}$
-\cite{friedan1985superconformal}.
-
-Shramm-Loewner evolution is the stochastic differential equation that describes the growth of
-conformally-invariant cut (some details here).
-
-We use CFT data to establish the value of Schramm-Loewner evolution parameter $\kappa$. The relation
-$c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}$ gives us possible values of $\kappa=\frac{16}{5},\; 5$.
-The model is also simplest example of supersymmetric conformal field theory. Schramm-Loewner
-evolution on superspace was introduced in \cite{nagi2005stochastic,rasmussen2004stochastic}. The
-relationship between the central charge and SLE parameter in this case is
-$c=\frac{15}{2}-3\left(\kappa+\frac{1}{\kappa}\right)$. It gives us
-$\kappa=\frac{3}{5},\frac{5}{3}$. (? c different for different sectors? )
-
-We consider the model on the domain with a boundary (upper half-plane). So we need to impose
-conformally invariant boundary conditions. Boundary states satisfy Cardy conditions and were
-classified by Chim \cite{chim1996boundary}. Conformal weights for the boundary fields are $h=0,\;
-\frac{1}{10},\; \frac{3}{5},\; \frac{3}{2},\; \frac{3}{80},\; \frac{7}{16}$.
-
-We review the Schramm-Loewner evolution and conformal field theory model for the tricritical Ising
-model in section \ref{sec:conf-field-theory}.
-
-The weights $h=\frac{1}{10},\; \frac{7}{16}$ satisfy the relationship between the parameter $\kappa$
-and conformal weight of boundary condition changing operator in SLE martingale: $(3\kappa-8) h =c$.
-If we consider SLE on a superspace we have the equation $h=\frac{6\kappa-3}{16}$ and get the weights
-$h=\frac{7}{6}?, \frac{1}{10}$ in the Neveu-Schwartz sector and $h=\frac{3}{80}, \frac{7}{16}$ in
-the Ramond-Ramond sector.
-
-\section{Boundary conditions and interfaces}
-\label{sec:bound-cond-interf}
-
-The classification of boundary states and SLE martingale condition suggests us the proper choice of
-integrable boundary conditions in RSOS realization of the model. For example, the following boundary
-satisfy it:
-\begin{equation}
-  \label{eq:2}
-  \underline{\begin{array}{llllllllll}
-    2 & & 2 & & 4 & & 4 & & 4\\
-    &  3 & & 3 & & 3 & & 3 & &
-  \end{array}}
-\end{equation}
-There is obviously an interface on double lattice delimiting $2$-s from $4$-s. We analyze the
-boundary conditions in RSOS model and  introduce the interfaces in section
-\ref{sec:bound-cond-interf}.
-
-\section{Discrete holomorphic observable and proof of convergence}
-\label{sec:discr-holom-observ}
-
- Then we
-select lattice observable that is martingale with respect to the interface growth.
-This observable is a generalization of Smirnov-Hongler parafermionic observable []:
-\begin{equation}
-  \label{eq:3}
-  f = \sum e^{-\mbox{winding}} e^{-Kl}
-\end{equation}
-
-In the section \ref{sec:discr-holom-observ} we show that this observable satisfy discrete s-holomorphicity
-condition and is a solution of discrete boundary problem. In critical limit this gives us the
-holomorphic function crucial for the proof of the convergence of the interface to SLE trace.
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-We list unsolved problems and future directions in conclusion \ref{sec:conclusion}.
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-
-This research was started during my stay at Simons center for geometry and physics in Stony Brook
-university. I thank Simons foundation for the financial support during my stay, the organizers of
-the program ``Conformal geometry'' and Simons center staff for their hospitality. I also thank
-Christian Hagendorff(?) and Dmitry Chelkak for fruitful discussions.
-
-This work  is supported by
-the Chebyshev Laboratory (Department of Mathematics and Mechanics,
-Saint-Petersburg State University) under the grant 11.G34.31.0026
-of the Government of the Russian Federation and by the Dynasty foundation.
-
-I am grateful to my wife Alexandra for her constant support and care.
-
-\bibliography{bibliography}{} 
-\bibliographystyle{utphys}
-
 \end{document}

### 2013-07-10 AffineLieAlgebras/Simons/tricritical.m
Some computations

@@ -480,6 +480,31 @@ Clear[RSOSModel]
 
 w=RSOSModel[t]
 
+w[2,3,2,3]
+
+2*Sin[Pi/10]/Sin[Pi/5]
+
+[Calculating...]
+
+[Calculating...]
+
+             -1 + Sqrt[5]
+Out[274]= -------------------
+                 5   Sqrt[5]
+          2 Sqrt[- - -------]
+                 8      8
+
+                       1 + Sqrt[5]
+                ArcCos[-----------]
+                            4
+          2 Sin[-------------------]
+                         2
+Out[273]= --------------------------
+                                 2
+                    (1 + Sqrt[5])
+           Sqrt[1 - --------------]
+                          16
+
                                 lm$182
 Out[101]= W$182[#1, #2, #3, #4, ------] & 
                                   2
@@ -778,3 +803,2085 @@ Out[146]= --
           16
 
 Out[145]= k
+
+2^24
+
+Out[150]= 16777216
+
+Out[149]= 4096
+
+Out[148]= 18446744073709551616
+
+
+N[Pi]
+
+Out[152]= 3.14159
+
+Out[151]= Pi
+
+Cos[5*Pi/4]
+
+               1
+Out[153]= -(-------)
+            Sqrt[2]
+
+Cos[4*Pi/5]
+
+          -1 - Sqrt[5]
+Out[154]= ------------
+               4
+
+
+N[Sqrt[2*Sqrt[5]+2]]
+
+Out[158]= 2.54404
+
+?Conjugate
+
+Clear[P]
+
+P[theta_,z_]:=1/2*(z+Exp[2*I*theta]*Conjugate[z])
+
+al=Sqrt[2]-1
+
+Out[175]= -1 + Sqrt[2]
+
+
+P[-3*Pi/8,al^g*Exp[-I/2*ww]]
+
+                         g
+           (-1 + Sqrt[2])                  Conjugate[g]
+Out[181]= (--------------- + (-1 + Sqrt[2])             
+                I/2 ww
+               E
+ 
+         (-3 I)/4 Pi + I/2 Conjugate[ww]
+>       E                               ) / 2
+
+
+?Reduce
+
+Reduce[expr, vars] reduces the statement expr
+     by solving equations or inequalities for vars
+      and eliminating quantifiers. Reduce[expr, vars, dom]
+
[…]

### 2013-07-24 AffineLieAlgebras/Simons/paper.tex
Acknowledgements added

--- 2013-06-26 AffineLieAlgebras/Simons/paper.tex
@@
   4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
-
-For simplicity we consider only the isotropic case $u=\lambda/2$ with boundary parameters
-$u=\xi_1=\xi_2=\lambda/2$. This case in critical limit corresponds to the  conformal point. Then we have
+The isotropic case $u=\lambda/2$ with boundary parameters
+$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
 $s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.
 
-There are 14 configurations with Bolzmann weights:
-\begin{equation}
-  \label{eq:12}
-  \begin{array}{l}
-    W\left(                                          
-        \begin{array}{cc}
-          2 & 1 \\
-          1 & 2
-        \end{array}
-      \right)=
-    W\left(
-        \begin{array}{cc}
-          3 & 4 \\
-          4 & 3
-        \end{array}
-      \right)=
-\frac{\sqrt{2+\frac{2}{\sqrt{5}}}
-      \left(3+\sqrt{5}\right) \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4}
-          \left(1+\sqrt{5}\right)\right)\right)}{1+\sqrt{5}}\\
-    W\left(                                      
-        \begin{array}{cc}
-          2 & 3 \\
-          1 & 2
-        \end{array}
-      \right)=
-    W\left(                                         
-        \begin{array}{cc}
-          3 & 2 \\
-          4 & 3
-        \end{array}
-      \right)=    W\left(                                         
-        \begin{array}{cc}
-          3 & 4 \\
-          2 & 3
-        \end{array}
-      \right)=    W\left(                                         
-        \begin{array}{cc}
-          2 & 1 \\
-          3 & 2
-        \end{array}
-      \right)=\frac{2 \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4}
-          \left(1+\sqrt{5}\right)\right)\right)}{\sqrt[4]{5}}\\
-    W\left(                                         
-        \begin{array}{cc}
-          1 & 2 \\
-          2 & 1
-        \end{array}
-      \right)= 
-      W\left(                                                  
-        \begin{array}{cc}
-          4 & 3 \\
-          3 & 4
-        \end{array}
-      \right)=\left(3+\sqrt{5}\right) \sqrt{\frac{1}{10}
-      \left(5+\sqrt{5}\right)} \sin
-    \left(\frac{1}{2}\cos^{-1}\left(\frac{1}{4}
-        \left(1+\sqrt{5}\right)\right)\right) \\  
-    W\left(                                       
-        \begin{array}{cc}
-          3 & 2 \\
-          2 & 1
-        \end{array}
-      \right)=
-    W\left(                                                       
-        \begin{array}{cc}
-          1 & 2 \\
-          2 & 3
-        \end{array}
-      \right)=    W\left(                                                      
-        \begin{array}{cc}
-          4 & 3 \\
-          3 & 2
-        \end{array}
-      \right)=
-    W\left(                                                        
-        \begin{array}{cc}
-          2 & 3 \\
-          3 & 4
-        \end{array}
-      \right)=\\
-    \quad\quad\quad\sqrt{2+\frac{2}{\sqrt{5}}} \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4} \left(1+\sqrt{5}\right)\right)\right)\\
-    W\left(
-        \begin{array}{cc}
-          3 & 2 \\
-          2 & 3
-        \end{array}
-      \right)=    W\left(
-        \begin{array}{cc}
-          2 & 3 \\
-          3 & 2
-        \end{array}
-      \right)=2 \sqrt{2+\frac{2}{\sqrt{5}}} \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4} \left(1+\sqrt{5}\right)\right)\right)\\
-
-  \end{array}
-\end{equation}
-
-We see the duality under the exchange $1\leftrightarrow 4, 2\leftrightarrow 3$.
-
-Boundary weights are in correspondence with the choice of boundary
-conditions. Possible integrable boundary conditions and boundary
-weights were identified in \cite{behrend2001integrable}.
-
-The $A_4$ RSOS model admits following loop description. Consider odd
-sublattice with values at sites equal to $1,3$ and draw loops around
-$4$s on it. Then consider even sublattice and draw loops around $1$s.
-The loops do not intersect. Loop picture characterizes configuration
-up to duality.
-
-Consider following boundary condition:
-\begin{equation}
-  \label{eq:13}
-  \underline{\begin{array}{llllllllll}
-    & 3 & & 1 &  & 3 & - & 3 & & \\
-    2 & & 2 &  & 2 & | & 4 & | & 2\\
-    & 1 & & 3 & - & 3 & & 3 &- & \\
-    2 & & 2 & | & 4 & & 4 & & 4\\
-    &  3 & & 3 &- & 3 &- & 3 &- &\dots
-  \end{array}}
-\end{equation}
-There is obviously an interface on double lattice delimiting $2$-s from $4$-s. We analyze the
-
 \begin{itemize}
+\item Boltzmann weights for $A_{4}$
 \item Boundary weights ?
+\item Critical point, isotropicity
 \item Loop description (two types of loops, duality, similarity with dilute Ising model) 
@@
 years theoretical progress in the study of critical behavior was connected with the description of
-geometrical objects -- interfaces. It was achieved by the use of Scharmm-Loewner evolution. To study
-the behavior of critical interfaces we consider the model on the bounded domain.
+geometrical objects -- interfaces. It was achieved by the use of Scharmm-Loewner evolution \cite{schramm2000scaling}.
 
-The behaviour of the model in critical
+The behaviour of the dilute Ising model in tricritical
 point is described by conformal field theory (CFT) with central charge $c=\frac{7}{10}$
@@
 Shramm-Loewner evolution is the stochastic differential equation that describes the growth of
-conformally-invariant cut (some details here).
+conformally-invariant cut
+
+\begin{equation}
+  \label{eq:6}
+
+\end{equation}
 

### 2013-07-24 AffineLieAlgebras/Simons/paper.tex

--- 2013-07-09 AffineLieAlgebras/Simons/paper.tex
@@
   We are interested in the case $A_4$, so we have
+
+$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
+$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
+  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
+The isotropic case $u=\lambda/2$ with boundary parameters
+$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
+$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.
+
+\begin{itemize}
+\item Boltzmann weights for $A_{4}$
+\item Boundary weights ?
+\item Critical point, isotropicity
+
 $2\cos\lambda=\frac{1+\sqrt{5}}{2}$, $\lambda=\pi/5$, $\psi=\left[1,2\cos\lambda,2\cos\lambda,1\right]$.
@@
 
+In recent
+years theoretical progress in the study of critical behavior was connected with the description of
+geometrical objects -- interfaces. It was achieved by the use of Scharmm-Loewner evolution \cite{schramm2000scaling}.
+
+The behaviour of the dilute Ising model in tricritical
+point is described by conformal field theory (CFT) with central charge $c=\frac{7}{10}$
+\cite{friedan1985superconformal}.
+
+Shramm-Loewner evolution is the stochastic differential equation that describes the growth of
+conformally-invariant cut
+
+\begin{equation}
+  \label{eq:6}
+
+\end{equation}
+
+We use CFT data to establish the value of Schramm-Loewner evolution parameter $\kappa$. The relation
+$c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}$ gives us possible values of $\kappa=\frac{16}{5},\; 5$.
+
 Connection of interfaces in restricted solid-on-solid models with
@@
 We consider the model on the domain with a boundary (upper half-plane). So we need to impose
-conformally invariant boundary conditions.
+conformally invariant boundary conditions. Boundary states satisfy Cardy conditions and were
+classified by Chim \cite{chim1996boundary}. Conformal weights for the boundary fields are $h=0,\;
+\frac{1}{10},\; \frac{3}{5},\; \frac{3}{2},\; \frac{3}{80},\; \frac{7}{16}$.
 

### 2013-08-12 area-length/notes.tex
Some text
Sections and abstract are added

@@
   Here I document staff related to my work on area-length problem.
+
+  We consider the scaling limit of conformal loop ensemble. The ratio
+  of loop area to certain power of loop length exhibit universal
+  scaling behavior. Scaling function is proportional to Bessel's
+  function. We show it using fusion rules for degenerate field in
+  conformal field theory on a cone. 
 \end{abstract}
 
+\section{Introduction}
+\label{sec:introduction}
+
+Here we discuss the history of the problem and state our answer to it.
+
+\section{Scaling of random loops}
+\label{sec:scaling-random-loops}
+
+In this section we introduce scaling function for random loops.
+
+Consider rooted loops in $O(n)$ model. Let $N^r(L)$ be number of
+rooted loops with a given length.  By $N^r(L,A)$ we denote the number
+of loops of given length and area. $N^r(L)=\int_0^{\infty} N^r(L,A)
+dA$. Area weighted number of loops is denoted by $G^r(L,\mu)$. (Here
+$\mu$ is bulk coupling constant ?).
+\begin{equation}
+  \label{eq:2}
+  G^r(L,\mu)=\int e^{\mu A} N^r(L,A) dA
+\end{equation}
+
+\begin{equation}
+  \label{eq:1}
+  G^r (\mu,x) = \sum_{\mathrm{clusters}} N^r (L,A) x^L e^{-\mu A}
+\end{equation}
+
+The idea is to write $G$ as a correlation function in Liouville
+theory.
+
+\section{Scaling limit and CFT on a cone}
+\label{sec:scaling-limit-cft}
+
+Here we argue that scaling limit is connected with correlation
+functions of CFT on a cone. Then we introduce recurrence relations on
+the angle of the cone. We show that this recurrent relation is
+equivalent to fusion rules of degenerate field in CFT.
+
+\section{CFT fusion coefficients and Bessel's functions}
+\label{sec:cft-fusi-coeff}
+
+In this section we solve recurrent relation using fusion rules and
+show that scaling function is equal to Bessel's function.
+
+\section{Conclusion}
+\label{sec:conclusion}
+Some concluding remarks are here.
+
 \end{document}

### 2013-08-19 area-length/notes.tex
Bibliography added
Minor changes to area-length notes

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
 
@@
 
+Though several publications exist
+\cite{cardy2003exact,cardy2003crossover,cardy2001exact,cardy1994geometrical}
+on this problem and the answer is
+obtained from computer simulation \cite{richard2001scaling}, good understanding was not
+obtained.
+
 \section{Scaling of random loops}
@@
 
+Note that number of rooted loops of given area scales as the area to
+the power minus one.
+
+Define Hausdorff dimension as follows.
+\begin{definition}
+  {\it Hausdorff content} of the set $S$ is
+  \begin{equation}
+    \label{eq:3}
+    C^d_H = \mathrm{inf} \sum_i r_i^d,
+  \end{equation}
+  where $\{r_i\}$ are such that there exists cover of $S$ by balls of
+  radii $r_i>0$.
+
+  {\it Hausdorff dimension}
+  \begin{equation}
+    \label{eq:4}
+    d_H\equiv\mathrm{dim}_H(S) = \mathrm{inf}\{ d\geq 0: C^d_H(S)=0\}
+  \end{equation}
+\end{definition}
+
+Consider loop of length $L$. The radius of the loop is connected with
+the length as $L\sim R^{d_H}$. The area is related to radius $A\sim
+R^2$, so $A\sim L^{\frac{2}{d_H}$.
+(It is proved or almost proved in papers by Lawler).
+
+For CLE the connection of Hausdorff dimension and parameter $\kappa$
+is known:
+\begin{equation}
+  \label{eq:5}
+  d_H=1+\frac{\kappa}{8}
+\end{equation}
+
+($\nu^{-1}=d_H$ ????)
+
+At $x\to x_c$
+\begin{equation}
+  \label{eq:6}
+  G^r(\mu,x)= \mu^{\theta} F\left(\frac{x-x_c}{\mu^{\phi}}\right)
+\end{equation}
+
 \section{Scaling limit and CFT on a cone}
@@
 
+\bibliography{bibliography}{} 
+\bibliographystyle{utphys}
+
 \end{document}

### 2013-09-11 area-length/notes.tex
Minor changes

@@
 
+\subsection{$O(n)$ model}
+\label{sec:introduction-1}
+
+Partition function for $O(n)$ model is
+\begin{equation}
+  \label{eq:9}
+  Z_{O(n)} = \sum_{\mbox{loop conf}} x^{\mbox{total length}}
+  n^{\mbox{number of loops}}
+\end{equation}
+
 \section{Scaling of random loops}
@@
 the length as $L\sim R^{d_H}$. The area is related to radius $A\sim
-R^2$, so $A\sim L^{\frac{2}{d_H}$.
+R^2$, so $A\sim L^{\frac{2}{d_H}}$.
 (It is proved or almost proved in papers by Lawler).
@@
 
+Partition function is product over loops of different length
+\begin{equation}
+  \label{eq:10}
+  Z_{O(n)} = \sum_{\mbox{loop conf}} \prod_L x^{L N(L)} n^{N(L)} = \sum_{\mbox{loop conf}} \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)}
+\end{equation}
+
+We can rewrite $G^r(\mu,x)$ as the derivative of generating function
+\begin{equation}
+  \label{eq:7}
+  G^r(\mu,x)=\mu\partial_x \log Z(\mu,\mu_B)
+\end{equation}
+
+Here
+\begin{equation}
+  \label{eq:8}
+  Z(\mu,\mu_B) = \left< e^{-\mu A} \right> = \frac{\sum_{\mbox{loop conf}}
+  \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)} e^{-\mu A}}{\sum_{\mbox{loop conf}} \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)}}
+\end{equation}
+
 \section{Scaling limit and CFT on a cone}
@@
 equivalent to fusion rules of degenerate field in CFT.
+
+Boundary Liouville theory:
+\begin{equation}
+  \label{eq:12}
+  S=\oint_{S^{1}} \phi \mathcal{N} \phi |dw| + \oint_{S^{1}} \mu_{B} e^{b\phi} + \mu\int_{D} e^{2b\phi} dw d\bar{w}
+\end{equation}
+
+\begin{equation}
+  \label{eq:11}
+  G^{r}(\mu,\mu_{B}) = \mu \frac{\left<V_{\frac{b}{2}} B_{-\frac{1}{b}}\right>}{\left<V_{\frac{b}{2}}\right>}
+\end{equation}
 

### 2013-11-27 area-length/notes.tex
Minor changes

@@
 \end{equation}
+Critical point is $x=\frac{1}{\sqrt{2+\sqrt{2-n}}}$, the continuum
+limit in this point is described by minimal model $(p,p')$ with
+$n=-2\cos\left(\frac{\pi p}{p'}\right)$. $c=1-6\frac{(p-p')^2}{pp'}$, $b=$.
+
+Self-avoiding walk is obtained in the limit $n\to 0$. Then $c=0$ and
+we have logarithmic conformal field theory.
 
@@
 
-\section{Scaling limit and CFT on a cone}
-\label{sec:scaling-limit-cft}
+\section{Liouville theory}
+\label{sec:liouville-theory}
 
-Here we argue that scaling limit is connected with correlation
-functions of CFT on a cone. Then we introduce recurrence relations on
-the angle of the cone. We show that this recurrent relation is
-equivalent to fusion rules of degenerate field in CFT.
+Liouville theory, flat metric, asymptotic for field, Coulomb gas formalism.
+
+The action for Liouville theory on a surface $\Gamma$ in arbitrary world-sheet metric $g$ is
+\begin{equation}
+  \label{eq:13}
+  S=\frac{1}{4\pi} \int_{\Gamma} \sqrt{g} \left( g^{ab} \partial_{a}\varphi \partial_{b}\varphi + Q R \varphi +4\pi \mu e^{2b\varphi}\right) d^{2}x
+\end{equation}
+Classical equations of motion are
+\begin{equation}
+  \label{eq:16}
+  \Delta \varphi(x) = \frac{1}{2} \left(b+\frac{1}{b}\right) R (x) + 4\pi b e^{2 b \varphi}
+\end{equation}
+Here $\Delta$ is Laplace-Beltrami operator
+\begin{equation}
+  \label{eq:17}
+  \Delta=\frac{1}{\sqrt{g}}\partial_{\mu} \left(\sqrt{g} g^{\mu\nu} \partial_{\nu}\right)
+\end{equation}
+
+We can select locally flat metric $g^{ab}=\delta^{ab}$ on some sheet, then the action takes the form
+\begin{equation}
+  \label{eq:14}
+  S= \int d^{2}x \frac{1}{4\pi} (\partial_{a} \varphi)^{2}+\mu e^{2b\varphi}
+\end{equation}
+Since we rewrote the action in this form we need to take into account the curvature. We do it by
+supposing the existence of conical singularity at infinity.
+\begin{equation}
+  \label{eq:15}
+  \varphi(z)=-Q \log (z\bar z)+O(1) \quad z\to\infty
+\end{equation}
+The equations of motion take the from
+\begin{equation}
+  \label{eq:18}
+  \Delta \varphi = 4\pi b e^{2b\varphi}
+\end{equation}
+The background charge is connected with the parameter $b$ by equation
+\begin{equation}
+  \label{eq:20}
+  Q=b+\frac{1}{b}
+\end{equation}
+
+Liouville field theory is a conformal field theory with central charge
+\begin{equation}
+  \label{eq:19}
+  c=1+6\left(b+\frac{1}{b}\right)^{2}
+\end{equation}
+and primary fields are given by vertex operators $V_{\alpha}=e^{\alpha\varphi}$. But primary fields
+$V_{\alpha}$ and $V_{Q-\alpha}$ are to be identified. For $\alpha=\frac{Q}{2}+i P, P\in \mathbb{R}$
+fields $V_{\alpha}$ are non-local.
+
+Computation of correlation functions in Liouville field theory relies on screening operators and
+recurrent relations that appear from OPE for auxiliary correlation functions.
+\subsection{Coulomb gas representation and screening operators}
+\label{sec:coul-gas-repr}
+
+\subsection{Boundary Liouville theory}
+\label{sec:bound-liouv-theory}
 
@@
 \end{equation}
+
+In paper \cite{fateev2000boundary} following expression was obtained for one-point boundary
+correlation function
+\begin{equation}
+  \label{eq:22}
+  \left<V_{\alpha}(x)\right>=\frac{U(\alpha|\mu_{B})}{|z-\bar z|^{2\Delta_{\alpha}}}
+\end{equation}
+
+\begin{equation}
+  \label{eq:21}
+  U(\alpha)=\frac{2}{b}\left(\pi\mu\gamma( b^{2})\right)^{\frac{Q-2\alpha}{2b}} \Gamma(2b\alpha-b^{2})
+  \Gamma\left(\frac{2\alpha}{b}-\frac{1}{b^{2}}-1\right) \cosh (2\alpha-Q)\pi s
+\end{equation}
+where $s$ is determined from the equation
+\begin{equation}
+  \label{eq:23}
+  \cosh^{2} \pi b s=\frac{\mu_{B}^{2}}{\mu}\sin \pi b^{2}
+\end{equation}
+and $\gamma(x)=\frac{\Gamma(x)}{\Gamma(1-x)}$.
+
+This one point function is related to generating function of surfaces with a conic singularity of given length and area in
+two-dimensional gravity theory. 
+Partition function for  surfaces with a conic singularity of given length and area in
+two-dimensional gravity theory is denoted by $Z_{\alpha}(A,l)$. Canonical transformation gives us
+\begin{equation}
+  \label{eq:24}
+  W_{\alpha}(l,\mu)=\int_{0}^{\infty} \frac{dA}{A} e^{-\mu A}Z_{\alpha}(A,l)
+\end{equation}
+
+Note that number of surfaces of given area $A$ and length $l$ is given by a canonical ensemble
+(parameters $N$, $E$)
+\begin{equation}
+  \label{eq:25}
+  N(l,A) = \sum_{\mbox{surfaces}} \delta(\mbox{Area}-A)\delta(\mbox{Length}-l)
+\end{equation}
+\begin{equation}
+  \label{eq:26}
+  F=\log Z
+\end{equation}
+Using Legendre transformation ($f^{*}(p)=\sup_{x\in I} (xp - f(x))$ $x\to \mbox{tangent}$) we move
+to the description with bulk and boundary interaction constants. 
+\begin{equation}
+  \label{eq:27}
+  \min_{\mu}(F(\mu)-\mu A) = S = \log N(A) \quad \mbox{Enthropy}
+\end{equation}
+Thus we obtain grand canonical ensemble (number of particles is not fixed, $w_{n}=\frac{1}{Z}
+e^{\frac{-(E_{n}-\mu N)}{kT}}$)
+
+$Z(\mu_{B},\mu) = \sum_{\mbox{surfaces}} e^{-\mu_{B}l -\mu A}=\int D\varphi e^{-S[\varphi]}$
+\begin{equation}
+  \label{eq:28}
+  \int D\varphi = \int dA dl \int D\phi \quad \mbox{but} \quad \int D\phi = N(A,l)
+\end{equation}
+It is useful to note different definition of integration measure in \cite{fateev2000boundary}: $\int
+\frac{d A}{A}\frac{d l }{l} N(A,l)$
+\section{Scaling limit and CFT on a cone}
+\label{sec:scaling-limit-cft}
+
+Here we argue that scaling limit is connected with correlation
+functions of CFT on a cone. Then we introduce recurrence relations on
+the angle of the cone. We show that this recurrent relation is
+equivalent to fusion rules of degenerate field in CFT.
 

### 2013-11-30 area-length/notes.tex
Some changes

@@
 Liouville theory, flat metric, asymptotic for field, Coulomb gas formalism.
+\cite{nakayama2004liouville,ponsot2002boundary,teschner2001liouville,fateev2000boundary,teschner2000remarks,zamolodchikov1996conformal}
 
@@
 $V_{\alpha}$ and $V_{Q-\alpha}$ are to be identified. For $\alpha=\frac{Q}{2}+i P, P\in \mathbb{R}$
-fields $V_{\alpha}$ are non-local.
+fields $V_{\alpha}$ are non-local. Conformal dimension of primary field $V_{\alpha}$ is
+\begin{equation}
+  \label{eq:32}
+  \Delta_{\alpha}=\alpha(Q-\alpha)
+\end{equation}
+
+Fields $V_{-\frac{nb}{2}}, \; n\in \mathbb{N}$ are degenerate, correlation functions of these fields
+satisfy differential equations of order $n+1$.
 
@@
 \label{sec:coul-gas-repr}
+
+Calculation of correlation functions in Liouville field theory can be done as follows. 
+Consider correlation some function with operator $V_{-\frac{b}{2}}$, it satisfies second order
+differential equation:
+\begin{equation}
+  \label{eq:33}
+  \left(\frac{1}{b^{2}}\partial^{2}+T(z)\right)\left<V_{-\frac{b}{2}}(z) \dots \right>=0
+\end{equation}
+Now to find some correlation function $\left<V_{\alpha_{1}}(z_{1})\dots
+  V_{\alpha_{k}}(z_{k})\right>$ we consider auxiliary correlation function with additional
+operator $V_{-\frac{b}{2}}(z)$, find a solution to differential equation and fix the integration
+constants using fusion rules for field $V_{-\frac{b}{2}}$.
+
+It can be shown (add reference here? \cite{nakayama2004liouville},\cite{teschner2001liouville}) that 
+\begin{equation}
+  \label{eq:34}
+  V_{-\frac{b}{2}}\times V_{\alpha}= [V_{\alpha-\frac{b}{2}}]+[V_{\alpha+\frac{b}{2}}]
+\end{equation}
+We can introduce structure constants of this operator product expansion \cite{fateev2000boundary}
+\begin{equation}
+  \label{eq:35}
+   V_{-\frac{b}{2}} V_{\alpha}= C_{+}[V_{\alpha-\frac{b}{2}}]+C_{-}[V_{\alpha+\frac{b}{2}}]
+\end{equation}
+
+Why? $C_{+}=1$,
+\begin{multline}
+  \label{eq:36}
+  C_{-}=-\mu\int d^{2}x \left<V_{\alpha}(0)V_{-\frac{b}{2}}(1) e^{2b\varphi(x)}
+    V_{Q-\alpha-\frac{b}{2}}(\infty)\right>=\\
+  -\mu\frac{\pi\gamma(2b\alpha-1-b^{2})}{\gamma(-b^{2})\gamma(2b\alpha)},
+\end{multline}
+where
+\begin{equation}
+  \label{eq:37}
+  \gamma(x)=\frac{\Gamma(x)}{\Gamma(1-x)}
+\end{equation}
+
+To calculate two-point function
+$\left<V_{\alpha}(x)V_{\alpha}(0)\right>=\frac{D(\alpha)}{|x|^{2\Delta_{\alpha}}}$ we consider
+auxiliary three-point function
+\begin{equation}
+  \label{eq:38}
+  \left<V_{\alpha}(x_{1})V_{\alpha+\frac{b}{2}}(x_{2})V_{-\frac{b}{2}}(z)\right>
+\end{equation}
 
@@
 
+For the partition function of surfaces with given area $A$ and length $l$ and conical singularity
+with angle $a(\alpha)$ following expression is obtained:
+\begin{equation}
+  \label{eq:29}
+  Z_{\alpha}(A,l)=\frac{1}{b}\frac{\Gamma(2\alpha b
+    -b^{2})}{\Gamma\left(1+\frac{1}{b^{2}}-\frac{2\alpha}{b}\right)} \left(\frac{l\Gamma(b^{2})}{2
+      A}\right)^{\frac{(Q-2\alpha)}{b}} \exp\left(-\frac{l^{2}}{4 A \sin \pi b^{2}}\right)
+\end{equation}
+
+How is it connected with the equation \eqref{eq:21}?
+
 Note that number of surfaces of given area $A$ and length $l$ is given by a canonical ensemble
@@
 \frac{d A}{A}\frac{d l }{l} N(A,l)$
+
+\begin{multline}
+  \label{eq:30}
+  \left< 1 \right>_{\alpha}=\int \left< V_{\alpha}(z)\right> dz = \int dz \sum_{\mbox{surfaces with cone
+    }\alpha\mbox{ at }z} e^{-S[\mbox{surface}]}=\\
+  \int \frac{dl}{l} \int dz  \sum_{\mbox{surfaces with cone
+    }\alpha\mbox{ at }z \mbox{ of length }l}e^{-S[\mbox{surface}]}=\\
+  \int\frac{dl}{l} W_{a}(l) e^{-\mu_{B}l}
+\end{multline}
+
+\begin{multline}
+  \label{eq:31}
+  Z_{\alpha}(\mu,\mu_{B}) = \int \left< V_{\alpha}(z)\right> dz=\\\int D\varphi\int d^{2}z \exp\left(-\frac{1}{4\pi} \int d^{2}z
+    b(\nabla\varphi)^{2}-\mu_{B}\oint e^{b\varphi}dx -\mu\int d^{2}z e^{2b\varphi}\right.\\
+  \left.-\alpha\int
+  d^{2}w \varphi(w) \delta(z-w)\right)
+\end{multline}
+So we see that one point boundary correlation function gives us partition function for surfaces of
+given length and area.
+
 \section{Scaling limit and CFT on a cone}

### 2013-12-05 area-length/notes.tex
Some changes

@@
 \end{equation}
+
+Full form of the operator product expansion is
+\begin{equation}
+  \label{eq:39}
+  A(z)B(w)\underset{z\to w}{\longrightarrow} \sum_{C} \frac{f_{AB}^{C}}{(z-w)^{h_{A}+h_{B}-h_{C}}} C(w)
+\end{equation}
+
+We use auxiliary correlation function that can be computed using Coulomb gas picture. The
+computation relies on following ideas.
+
+\subsubsection{Coulomb gas picture. Free boson theory. Minimal models}
+\label{sec:free-boson-minimal-models}
+
+\begin{equation}
+  \label{eq:40}
+  S=\int d^{2}z b (\partial \varphi)^{2},\quad \left<\varphi(z,\bar z)\varphi(w,\bar
+    w)\right>=-\frac{1}{2b}\left(\ln (z-w) + \ln (\bar z - \bar w)\right)+const
+\end{equation}
+
+\begin{equation}
+  \label{eq:42}
+  T(z)=-\frac{1}{2}:\partial \varphi \partial \varphi:, \quad c=1
+\end{equation}
+In holomorphic sector primary fields are $\partial \varphi$ with $h=1$ and
+$V_{\alpha}(z)=e^{i \alpha \varphi(z)}$ with dimension $h_{\alpha}=\frac{\alpha^{2}}{2}$.
+
+Field $\varphi(z)$ is not purely holomorphic, it contains zero mode
+\begin{equation}
+  \label{eq:43}
+  \varphi(z)=\varphi_{0}-ia_{0}\ln z+\sum_{n\neq 0}\frac{1}{n}a_{n} z^{-n},\quad
+  [a_{n},a_{m}]=n\delta_{n+m,0}, \quad [\varphi_{0},a_{0}]=i
+\end{equation}
+But we can limit ourselves to chiral operators.
+
+If $\alpha_{1}+\dots+\alpha_{n}=0$ then 
+\begin{equation}
+  \label{eq:41}
+  \left<e^{\alpha_{1}\varphi}(z_{1})\dots e^{\alpha_{n}\varphi}(z_{n})\right> = \prod_{i<j}(z_{i}-z_{j})^{-\alpha_{i}\alpha_{j}}
+\end{equation}
+Since $\left< :e^{A_{1}}::e^{A_{2}}:\dots :A^{A_{n}}:\right> =
+\exp\sum_{i<j}\left<A_{i}A_{j}\right>$, we can take $A_{i}=\alpha_{i}\varphi(z_{i})$ and use the
+fact that $\left<A_{i}A_{j}\right>=\ln |z_{i}-z_{j}|^{-\alpha_{i}\alpha_{j}}$.
+
+Neutrality condition can be seen from the invariance of the action w.r.t. $\varphi\to\varphi+a$,
+then the correlator obtains factor $e^{\sum \alpha_{i}}$ which is 1 if $\sum \alpha_{i}=0$.
+
+Vacuum expectation value of operator with non-zero charge $\alpha$ should be zero.
+
+To obtain models with $c\neq 1$ one needs to introduce the background charge:
+\begin{equation}
+  \label{eq:44}
+  S=\frac{1}{8\pi} \int d^{2}x \sqrt{g} (\partial_{\mu}\varphi\partial^{\mu}\varphi+2\gamma\varphi R)
+\end{equation}
+Here $R$ is scalar curvature, $\gamma$ - constant.
+
+(Gauss-Bonnet theorem: $\int d^{2}x \sqrt{g} R = 8\pi(1-h)$, $h$-number of handles).
+
+After introducing interaction with the curvature Ward identities are changed and now neutrality
+condition is $\sum \alpha_{i}=2\alpha_{0}$, where $i\sqrt{2}\alpha_{0}=\gamma$. 
+Stress-energy tensor now takes the form
+\begin{equation}
+  \label{eq:45}
+  T_{\mu\nu}=T^{(0)}_{\mu\nu}-\frac{\gamma}{2\pi}\left(\partial_{\mu}\partial_{\nu}\varphi-\frac{1}{2}\eta_{\mu\nu}\partial^{\rho}\partial_{\rho}\varphi\right)
+\end{equation}
+and
+\begin{equation}
+  \label{eq:46}
+  T(z)=-\frac{1}{2}:\partial \varphi\partial\varphi:+i\sqrt{2}\alpha_{0}\partial^{2}\varphi
+\end{equation}
+If we calculate OPE of $T$ we see that $\partial\varphi$ is not primary any more \cite{difrancesco1997cft}:
+\begin{equation}
+  \label{eq:47}
+  T(z)\partial\varphi(w)\sim
+  \frac{i2\sqrt{2}\alpha_{0}}{(z-w)^{3}}+\frac{\partial\varphi(w)}{(z-w)^{2}} +\frac{\partial^{2}\varphi(w)}{z-w}
+\end{equation}
+Vertex operators are still primary, but conformal dimensions are now
+\begin{equation}
+  \label{eq:48}
+  h_{\alpha}=\alpha^{2}-2\alpha_{0}\alpha
+\end{equation}
+and central charge is
+\begin{equation}
+  \label{eq:49}
+  c=1-24\alpha_{0}^{2}
+\end{equation}
+The correlator \eqref{eq:41} is preserved. Now vertex operators $V_{\alpha}$ and
+$V_{2\alpha_{0}-\alpha}$ are equivalent, so two-point function
+$\left<V_{\alpha}(z)V_{\alpha}(w)\right>$  is not zero, but it should be represented as
+$\left<V_{\alpha}(z)V_{2\alpha_{0}-\alpha}(w)\right>=\frac{1}{(z-w)^{h_{\alpha}}}$.
+
+In general we insert non-local screening operator with zero conformal dimension but nonzero charge.
+If $\psi$ is primary field with $h_{\psi}=1$ its integral $  A=\oint dz \psi(z) $ is a nonlocal
+operator of conformal dimension zero (invariant under conformal mapping $z\to w$ 
+\begin{equation}
+  \label{eq:50}
+  A\to \oint dz \psi(z) \left(\frac{\partial w}{\partial z}\right)=\oint dw \psi(w)
+\end{equation}
+Then
+\begin{multline}
+  \label{eq:51}
+  [L_{n},A]=\oint dz [L_{n},\psi(z)]=\\\oint dz  (n+1) z^{n}\psi(z)+z^{n+1}\partial \psi(z)=\\
+  \oint dz \partial (z^{n+1}\psi (z))=0
+\end{multline}
+Screening operators are constructed from vertex operators
+\begin{equation}
+  \label{eq:52}
+  V_{\pm}=V_{\alpha_{\pm}}, \quad \alpha_{\pm}=\alpha_{0}\pm \sqrt{\alpha_{0}^{2}+1}, \quad
+  \alpha_{+}\alpha_{-}=-1,\quad \alpha_{+}+\alpha_{-}=2\alpha_{0}
+\end{equation}
+\begin{equation}
+  \label{eq:53}
+  Q_{\pm}=\oint dz V_{\pm}(z)=\oint dz e^{i\sqrt{2}\alpha_{\pm}\varphi(z)}
+\end{equation}
+Now for two-point function we can write
+\begin{equation}
+  \label{eq:54}
+  \left<V_{\alpha}(z)V_{\alpha}(w)Q_{-}^{m}Q_{+}^{n}\right>,
+\end{equation}
+with neutrality condition $2\alpha+n\alpha_{+}+m\alpha_{-}=2\alpha_{0}$,  so $2\alpha$ is an integer
+combination of $\alpha_{-}$ and $\alpha_{+}$.
+So we obtain Kac formula for conformal weights of fields in minimal models
+\begin{equation}
+  \label{eq:55}
+  \alpha_{r,s}=\frac{1}{2}(1-r)\alpha_{+}+\frac{1}{2}(1-s)\alpha_{-}\quad 
+  h_{r,s}(c)=\frac{1}{4}(r\alpha_{+}+s\alpha_{-})^{2}-\alpha_{0}^{2}
+\end{equation}
+
+If we calculate three-point function and require operator algebra to be closed we can obtain
+conditions on possible values of central charge or background charge $\alpha_{0}$.
+
+Computation of three-point function relies on following trick: find four-point function as a
+solution of differential equation following from null-vector condition and then recover structure
+constants for three-point function from the limit $z\to 0$, where $z$ is cross-ratio.
+
+Structure constants in three-point function are equal to fusion coefficients for corresponding
+fields, for example substitute fusion rule \eqref{eq:39} to three-point function
+
+  \begin{equation}
+    \label{eq:56}
+    \langle
+    \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{\Delta_{1}+\Delta_{2}-\Delta_{3}}
+      x_{23}^{\Delta_{2}+\Delta_{3}-\Delta_{1}}x_{13}^{\Delta_{3}+\Delta_{1}-\Delta_{2}}}.     
+  \end{equation}
+
+Assume that we know four-point function
+$\left<\varphi_{1}(z_{1})\varphi_{2}(z_{2})\varphi_{3}(z_{3})\varphi_{4}(z_{4})\right>$, then we
+take limits $z_{1}\to z_{2}$ and $z_{3}\to z_{4}$ and obtain product of structure constants
+$C_{12}^{r}C_{34}^{r}$ as a coefficient before $\frac{1}{z_{24}^{r}}$.
+
+To compute four-point function we use conformal invariance to send $z_{1}\to 0$, $z_{2}\to z$
+$z_{3}\to 1$ and $z_{4}\to \infty$:
+\begin{equation}
+  \label{eq:58}
+  \left<\varphi_{1}(z_{1})\varphi_{2}(z_{2})\varphi_{3}(z_{3})\varphi_{4}(z_{4})\right>=\left<
+    V_{r_{1},s_{1}}(z_{1}) V_{r_{2},s_{2}}(z_{2}) V_{r_{3},s_{3}}(z_{3}) V_{-r_{4},-s_{4}}(z_{4})
+    Q_{+}^{r} Q_{-}^{s}\right>,
+\end{equation}
+where neutrality condition gives us
+\begin{equation}
+  \label{eq:59}
+  \begin{array}{c}
+    r_{4}=r_{1}+r_{2}+r_{3}-2r-2\\
+    s_{4}=s_{1}+s_{2}+s_{3}-2s-2
+  \end{array}
+\end{equation}
+then 
+\begin{multline}
+  \label{eq:58}
+  \left<\varphi_{1}(0)\varphi_{2}(z)\varphi_{3}(1)\varphi_{4}(\infty)\right>=\left<
+    V_{r_{1},s_{1}}(0) V_{r_{2},s_{2}}(z) V_{r_{3},s_{3}}(1) V_{-r_{4},-s_{4}}(\infty)
+    Q_{+}^{r} Q_{-}^{s}\right>=\\
+  z^{\frac{1}{3}\sum h_{i}-h_{1}-h_{2}}(1-z)^{\frac{1}{3}\sum h_{i}-h_{2}-h_{3}} G(z)
+\end{multline}
+
+The simplest case is when $\varphi_{2}=\varphi_{(2,1)}$, then we need to compute integral
+\begin{multline}
+  \label{eq:60}
+  \left<
+    V_{r_{1},s_{1}}(0) V_{2,1}(z) V_{r_{3},s_{3}}(1) V_{-r_{4},-s_{4}}(\infty)
+    Q_{+}\right>=\\
+  \oint dw \left<     V_{r_{1},s_{1}}(0) V_{2,1}(z) V_{r_{3},s_{3}}(1) V_{-r_{4},-s_{4}}(\infty)
+    V_{+}(w)\right>=\\
+  z^{2\alpha_{2,1}\alpha_{r_{1},s_{1}}}  (1-z)^{2\alpha_{2,1}\alpha_{r_{3},s_{3}}} G(z)
+\end{multline}
+Substitute \eqref{eq:41} and in holomorphic sector we obtain
+\begin{equation}
+  \label{eq:61}
+  \oint dw w^{a}(w-1)^{b}(w-z)^{c},
+\end{equation}
+where
+\begin{equation}
+  \label{eq:62}
+  a=2\alpha_{+}\alpha_{r_{1},s_{1}},\quad b=2\alpha_{+}\alpha_{r_{3},s_{3}}, c=2\alpha_{+}\alpha_{2,1}
+\end{equation}
+
+The difficulty is in choice of integration contour, we need to choose two independent contours which
+will give us two independent solutions of differential equation \eqref{eq:33}.
+
+Two choices of contour \cite{difrancesco1997cft} give integrals
+\begin{equation}
+  \label{eq:63}
+  \begin{array}{ll}
+    I_{1}(a,b,c; z) &= \int_{1}^{\infty} dw w^{a} (w-1)^{b} (w-z)^{c}\\
+    I_{1}(a,b,c; z) &= \int_{0}^{z} dw w^{a} (1-w)^{b} (w-z)^{c}\\
+    &=z^{1+a+b+c}\int_{0}^{1}dw  w^{a}(1-w)^{b}(1-zw)^{c}
+  \end{array}
+\end{equation}
+These integrals can be calculated by power series expansion of terms with $z$, use of integral
+formula for beta-function 
+\begin{equation}
+  \label{eq:64}
+    B(x,y)=\frac{\Gamma(x)\Gamma(y)}{\Gamma(x+y)} = \int_{0}^{1} t^{x-1} (1-t)^{y-1} dt =
+    \int_{0}^{\infty} t^{x-1} (1+t)^{-x-y} dt
+  \end{equation}
+then convert power series to hypergeometric function definition using $\Gamma(t+1)=t\Gamma(t)$
+\begin{equation}  
+  F(\lambda,\mu,\nu; z)=\sum_{k=0}^{\infty}\frac{1}{k!}\frac{(\lambda)_{k}(\mu)_{k}}{(\nu)_{k}}
+  z^{k}, \;\mbox{where}\; (x)_{k}=x(x-1)\dots (x-k+1)
+\end{equation}
+Final result for conformal block is
+\begin{eqnarray}
+  \label{eq:65}
+  I_{1}(a,b,c;z)=\frac{\Gamma(-a-b-c-1)\Gamma(b+1)}{\Gamma(-a-c)} F(-c,-a-b-c-1,-a-c; z)\\
+  I_{2}(a,b,c;z)=z^{1+a+b+c}\frac{\Gamma(a+1)\Gamma(c+1)}{\Gamma(a+c+2)} F(-b,a+1,a+c+2; z)\\
+  G(z,\bar z)=\sum_{i,j=1,2}X_{ij} I_{i}(z) \bar I_{j}(\bar z)
+\end{eqnarray}
+Calculation of coefficients $X_{ij}$ can be made using monodromy properties of correlation function
+around singularities. It is equivalent to operator product expansion of primary fields. Functions
+$I_{1}, I_{2}$ are in correspondence with intermediate fields in OPE for pairs of primary fields in
+four-point function. Different ways to calculate using OPE correspond to different conformal blocks:
+\begin{equation}
+  \label{eq:66}
+  \mathcal{G}(z,\bar z) =
+  \left<\varphi_{1}(z_{1})\varphi_{2}(z_{2})\varphi_{3}(z_{3})\varphi_{4}(z_{4})\right> =
+  \sum_{r,s;\bar r, \bar s}\mathcal{F}_{r,s}(z) \bar{\mathcal{F}}_{\bar r,\bar s}(\bar z)
+\end{equation}
+where $\mathcal{F}_{r,s}$ corresponds to a field $\varphi_{(r,s)}$ in OPE
+\begin{equation}
+  \label{eq:67}
+  \varphi_{(r,s)}\in \varphi_{(r_{1},s_{1})}\times \varphi_{(r_{2},s_{2})}
+\end{equation}
+
+\subsubsection{Liouville theory}
+\label{sec:liouville-theory-1}
+
+Liouville theory is very similar to Coulomb gas picture for minimal models. Scalar curvature at
+infinity is $4\pi b$.
+
+Stress-energy tensor is
+\begin{equation}
+  \label{eq:68}
+  T(z)=-(\partial \varphi)^{2}+Q \partial^{2}\varphi
+\end{equation}
+Central charge is related to $Q$ by formula \eqref{eq:19}, similarly to minimal models
+\eqref{eq:49}.
+
+It can be shown (add reference here? \cite{nakayama2004liouville},\cite{teschner2001liouville}) that 
+\begin{equation}
+  \label{eq:34}
+  V_{-\frac{b}{2}}\times V_{\alpha}= [V_{\alpha-\frac{b}{2}}]+[V_{\alpha+\frac{b}{2}}]
+\end{equation}
+
 We can introduce structure constants of this operator product expansion \cite{fateev2000boundary}
@@
 
-Why? $C_{+}=1$,
+This structure constants are equal to constants in three-point functions and can be computed by
+screening integrals. For $C_{+}$ we have neutrality condition
+$\alpha-\frac{b}{2}+Q-\alpha+\frac{b}{2}=Q$, so we do not need screening integrals and $C_{+}=1$.
+For $C_{-}$ we screen by first order of Liouville interaction $-\mu\int e^{2b\varphi} d^{2}x$ 
+(Check here, it should be contour integral!!!): 
 \begin{multline}
@@
     V_{Q-\alpha-\frac{b}{2}}(\infty)\right>=\\
+  \int d^{2}x x^{2\alpha b} (x-1)^{-b^{2}}=\\
   -\mu\frac{\pi\gamma(2b\alpha-1-b^{2})}{\gamma(-b^{2})\gamma(2b\alpha)},

### 2013-12-05 area-length/notes.tex
More work on Liouville notes

@@
 \title{Notes on area-length problem for CLE}
-\author{Anton Nazarov}%% $^{1,2}$}
+%\author{Anton Nazarov}%% $^{1,2}$}
 
@@
 \begin{abstract}
-  Here I document staff related to my work on area-length problem.
+%  Here I document staff related to my work on area-length problem.
 
@@
 
+Complete results for four-point functions in minimal model with Coulomb gas representation are
+presented in paper \cite{dotsenko1985four}.
+
 \subsubsection{Liouville theory}
@@
 For $C_{-}$ we screen by first order of Liouville interaction $-\mu\int e^{2b\varphi} d^{2}x$ 
-(Check here, it should be contour integral!!!): 
+(Add notes from Zamolodchikov lectures p.131,141 \cite{zamolodchikovlectures}): 
 \begin{multline}
@@
 \end{equation}
+Then we consider two operator product expansions when $z\to x_{1}$ and when $z\to x_{2}$. In the
+first case only the term $C_{-} V_{\alpha+\frac{b}{2}}$ survives and we get
+$C_{-}D\left(\alpha+\frac{b}{2}\right)$. In the second case we get $C_{+}D(\alpha)$. Since $C_{+}=1$
+we get functional equation on $D$:
+\begin{equation}
+  \label{eq:57}
+  \frac{D\left(\alpha+\frac{b}{2}\right)}{D(\alpha)}=\frac{1}{C_{-}(\alpha)}
+\end{equation}
+The solution of this equation is
+\begin{equation}
+  \label{eq:69}
+  D(\alpha)=(\pi\mu\gamma(b^{2}))^{\frac{Q-2\alpha}{b}} \frac{\gamma(2b\alpha-b^{2})}{b^{2}\gamma\left(2-\frac{2\alpha}{b}+\frac{1}{b^{2}}\right)}
+\end{equation}
+
+Result for three-point function can be obtained in the same way by considering auxiliary four-point
+function that satisfy second order differential equation due to degeneracy of the field $V_{-\frac{b}{2}}$.
 
@@
 
+\subsection{Computation of one-point function}
+\label{sec:comp-one-point}
+
+To actually compute bulk one-point function \eqref{eq:22} in boundary Liouville field theory  we
+consider auxiliary bulk two-point function
+\begin{equation}
+  \label{eq:70}
+  G_{\alpha,-\frac{b}{2}}=\left<V_{\alpha}(x)V_{-\frac{b}{2}}(z)\right>
+\end{equation}
+Since we consider theory on upper half-plane, this two-point function satisfy the same equation as
+four-point function $\left<V_{\alpha}(x)V_{-\frac{b}{2}}(z)V_{\alpha}(\bar x)V_{-\frac{b}{2}}(\bar
+  z)\right>$ in the whole plane. (Zero mode?) 
+(Note: $\left<\phi(z,\bar z)\right>_{b}\sim\left<\phi(z)\phi(\bar z)\right>=\frac{1}{(z-\bar
+  z)^{2h}}$, then $\left<\phi(y)\right>\sim \frac{1}{y^{2h}}$)
+
+Since our four-point function satisfy second order ODE, it can be presented as a linear combination
+of two independent solutions -- conformal blocks. Change of variables allows to rewrite the equation
+as a hypergeometric equation, so conformal blocks are given by hypergeometric functions:
+\begin{equation}
+  \label{eq:71}
+  \mathcal{G}_{\pm}(x,z)=\frac{|x-\bar x|^{2\Delta_{\alpha}-2\Delta_{-\frac{b}{2}}}}{|z-\bar
+    x|^{4\Delta_{\alpha}}} \mathcal{F}_{\pm}(\eta),
+\end{equation}
+where $\Delta_{-\frac{b}{2}}=-\frac{1}{2}-\frac{3b^{2}}{4}$ and 
+\begin{equation}
+  \label{eq:72}
+  \eta=\frac{(z-x)(\bar z-\bar x)}{(z-\bar x)(\bar z - x)}
+\end{equation}
+\begin{eqnarray}
+  \label{eq:73}
+  F_{+}(\eta)=\eta^{\alpha b}(1-\eta)^{-\frac{b^{2}}{2}} F(2\alpha b -1-2b^{2},-b^{2},2\alpha
+  b-b^{2};\eta)\\
+  F_{-}(\eta)=\eta^{1+b^{2}-\alpha b}(1-\eta)^{-\frac{b^{2}}{2}} F(-b^{2},1-2\alpha b,2+b^{2}-2\alpha
+  b;\eta)
+\end{eqnarray}
+Coefficients before independent solutions $\mathcal{G}_{\pm}$ are fixed by substituting OPE
+\eqref{eq:35}:
+\begin{equation}
+  \label{eq:74}
+  G_{\alpha,-\frac{b}{2}}=C_{+}(\alpha) U\left(\alpha-\frac{b}{2}\right) \mathcal{G}_{+}(x,z)+
+  C_{-}(\alpha) U\left(\alpha+\frac{b}{2}\right) \mathcal{G}_{-}(x,z)
+\end{equation}
+Next we need to consider OPE when both operators $V_{\alpha}(x), V_{-\frac{b}{2}}(z)$ approach the
+boundary. 
 \section{Scaling limit and CFT on a cone}

### 2013-12-14 area-length/notes.tex
Minor changes

@@
 on this problem and the answer is
-obtained from computer simulation \cite{richard2001scaling}, good understanding was not
+obtained from computer simulation \cite{ richard2001scaling}, good understanding was not
 obtained.
+
+\subsection{Self-avoiding polygons}
+\label{sec:self-avoid-polyg}
+
+The model of self-avoiding polygons was numerically studied in the paper \cite{richard2001scaling}.
+Author consider polygons with generating function
+\begin{equation}
+  \label{eq:75}
+  G(x,q)=\sum_{m,n} p_{m,n} x^{m} q^{n},
+\end{equation}
+where $p_{m,n}$ is the number of polygons with perimeter $m$, enclosing an area $n$ passing through
+a given edge (or node). 
+Cardy \cite{cardy2001exact} use following definition for generating function of rooted loops, using
+$g=-\ln q$:
+\begin{equation}
+  \label{eq:76}
+  G^{(r)}(x,g)=\sum_{l,A} p_{l,A}^{(r)} x^{l} e^{-gA}
+\end{equation}
+Generating function for rooted polygons $G^{(r)}(x,g)$ is related to $G(x,g)$ by
+\begin{equation}
+  \label{eq:81}
+  G^{(r)}(x,g)=x \frac{d}{dx} G(x,g),
+\end{equation}
+because root can be chosen in $l$ ways.
+
+This model has critical point $(x_{c},0)$ and generating functions displays scaling behavior
+\begin{equation}
+  \label{eq:77}
+  G(x,g)\sim G(x,g)_{\mathrm{reg}}+g^{\theta} F\left((x_{c}-x)g^{-\phi}\right)
+\end{equation}
+Critical indices $\theta,\phi$ are related to conventional exponents $\nu,\alpha$:
+\begin{eqnarray}
+  \label{eq:78}
+  \phi=\frac{1}{2}\nu\\
+  \theta=\frac{1}{2}(1-\alpha) \nu
+\end{eqnarray}
+Hyperscaling hypothesis adds another relation
+\begin{equation}
+  \label{eq:79}
+  \alpha=2-2\nu
+\end{equation}
+Numerical results predict
+\begin{eqnarray}
+  \label{eq:80}
+  \nu=\frac{3}{4}\\
+  \theta=\frac{1}{3}\\
+  \phi=\frac{2}{3}
+\end{eqnarray}
+We want to find scaling function $F$.
 
@@
 \label{sec:introduction-1}
+
+Self-avoiding polygons can be thought as the limit $n\to 0$ of loops in $O(n)$ model.
 
@@
 limit in this point is described by minimal model $(p,p')$ with
-$n=-2\cos\left(\frac{\pi p}{p'}\right)$. $c=1-6\frac{(p-p')^2}{pp'}$, $b=$.
+$n=-2\cos\left(\frac{\pi p}{p'}\right)$. $c=1-6\frac{(p-p')^2}{pp'}$, $b=\sqrt{\frac{3}{2}}$.
 
@@
 
+Logarithmic CFT $\sim$ Liouville theory ???
+
 \section{Scaling of random loops}
 \label{sec:scaling-random-loops}
+
+Cardy \cite{cardy2001exact} argues that generating function $G^{(r)}$ for rooted self-avoiding loops is given by a derivative w.r.t. $x$
+of expectation value of $e^{-gA}$ (eq.6):
+\begin{equation}
+  \label{eq:82}
+  Z=\left<e^{-gA}\right>_{\mathrm{SAL}}=\left<e^{-\sqrt{g}\int J_{\lambda}A_{\lambda}d^{2}x}\right>_{\mathrm{SAL}.A}
+\end{equation}
+But reasoning is quite strange and unsound.
 
@@
 \end{equation}
+ Very strange.
 
@@
 \cite{nakayama2004liouville,ponsot2002boundary,teschner2001liouville,fateev2000boundary,teschner2000remarks,zamolodchikov1996conformal}
+
+Liouville theory describes internal metric of surface. It is possible to obtain length of boundary
+and area of surface with such a metric. To get the answer for flat loops we need to impose some
+condition on metric in the bulk. 
+It is
+\begin{equation}
+  \label{eq:83}
+  g^{ab}=\eta^{ab}
+\end{equation}
+where
+\begin{equation}
+  \label{eq:84}
+  g^{ab}=e^{2b\varphi} \eta^{ab}
+\end{equation}
+So the condition is
+\begin{equation}
+  \label{eq:85}
+  \varphi(x) = 0 
+\end{equation}
 
@@
 Coefficients before independent solutions $\mathcal{G}_{\pm}$ are fixed by substituting OPE
-\eqref{eq:35}:
+\eqref{eq:35} (substitute it to equation?):
 \begin{equation}
@@
 boundary.
+
+Bulk operator $V_{-\frac{b}{2}}$ near the boundary gives rise to two boundary families $B_{0}$ and
+$B_{-b}$. The fusion of $B_{0}=I$ to $V_{\alpha}$ is $\left<V_{\alpha}(x)
+  B_{0}(0)\right>=\frac{R(\alpha,0|\mu_{B})}{|z-\bar z|^{2\Delta_{\alpha}}}$, and the fusion of $V_{-\frac{b}{2}}$ 
 \section{Scaling limit and CFT on a cone}

### 2014-02-01 area-length/notes.tex
Some text on Liouville and triangulations

@@
 
-  We consider the scaling limit of conformal loop ensemble. The ratio
+  We consider conformal loop ensemble. The ratio
   of loop area to certain power of loop length exhibit universal
   scaling behavior. Scaling function is proportional to Bessel's
-  function. We show it using fusion rules for degenerate field in
-  conformal field theory on a cone. 
+  function. We show it using boundary Liouville field theory fusion rules for degenerate field.
 \end{abstract}
@@
 
-Here we discuss the history of the problem and state our answer to it.
+One can ask simple question: how many loops is there?
+
+To make this question more precise consider conformal loop ensemble \cite{sheffield2010conformal}. It is critical limit of
+lattice different models for different values of $\kappa$. Loops can be interpreted as a critical
+limits of domain walls in lattice models. 
+We are interested in distribution of loops by length and area.
 
@@
 
+Some results exist in literature for particular case of self-avoiding walks ($\kappa=\frac{8}{3}$). We start
+with the description of these results \ref{sec:self-avoid-polyg}, then show that general problem
+leads to Liouville field theory \ref{sec:scaling-random-loops} and obtain our result using Liouville
+field theory fusion rules \ref{sec:liouville-theory}.
+
 \subsection{Self-avoiding polygons}
@@
 The model of self-avoiding polygons was numerically studied in the paper \cite{richard2001scaling}.
-Author consider polygons with generating function
+The simplest case is the generating function for polygons of given length. It can be introduced as
+\begin{equation}
+  \label{eq:86}
+  G(x)=\sum_l p_l x^l,
+\end{equation}
+where  $p_l$ is the number of different polygons on square lattice of length $l$. Different are
+polygons that can not be superposed by a lattice translation.
+If we know generating function we can obtain number of polygons of given length differentiating
+w.r.t. $x$.
+
+We can also introduce generating function for polygons of given length and area:
 \begin{equation}
@@
 \end{equation}
-But reasoning is quite strange and unsound.
+But reasoning is quite strange and unsound. Due to the need to use $g$ for metric in later sections
+we will denote area coupling constant by $\mu$ and loop length coupling constant by $\mu_{B}=-\ln x$
+(boundary).
 
@@
 dA$. Area weighted number of loops is denoted by $G^r(L,\mu)$. (Here
-$\mu$ is bulk coupling constant ?).
+$\mu$ is bulk coupling constant ).
 \begin{equation}
@@
 
-($\nu^{-1}=d_H$ ????)
+($\nu^{-1}=d_H$)
 
@@
 \end{equation}
- Very strange.
 
@@
 condition on metric in the bulk.
-It is
-\begin{equation}
-  \label{eq:83}
-  g^{ab}=\eta^{ab}
-\end{equation}
-where
-\begin{equation}
-  \label{eq:84}
-  g^{ab}=e^{2b\varphi} \eta^{ab}
-\end{equation}
-So the condition is
-\begin{equation}
-  \label{eq:85}
-  \varphi(x) = 0 
-\end{equation}
 
-The action for Liouville theory on a surface $\Gamma$ in arbitrary world-sheet metric $g$ is
+The action for Liouville theory on a surface $\Gamma$ in arbitrary background metric $g$ is
 \begin{equation}
@@
 \end{equation}
+
+This theory gives internal metric $\tilde g^{ab}=e^{\varphi(x)}g^{ab}(x)$
+
 Classical equations of motion are
@@
   \label{eq:16}
-  \Delta \varphi(x) = \frac{1}{2} \left(b+\frac{1}{b}\right) R (x) + 4\pi b e^{2 b \varphi}
+  \Delta \varphi(x) = \frac{1}{2} \left(b+\frac{1}{b}\right) R (x) + 4\pi \mu e^{2 b \varphi}
 \end{equation}
@@
 \end{equation}
+
+Since
+\begin{equation}
+  \label{eq:93}
+  \sqrt{g}(R-\Delta \varphi)=\sqrt{\tilde g} \tilde R, 
+\end{equation}
+for metric $\tilde g= e^{2b\varphi} g$, equation of motion can be written as
+\begin{equation}
+  \label{eq:94}
+  \tilde R(x) + 4\pi \mu=0
+\end{equation}
+So classical configurations have constant curvature $-4\pi\mu$.
+
+In most cases it is possible to use flat background metric, but one needs to be careful with
+singularities. For example, consider a manifold with the topology of a sphere. We can use flat
+background metric but we need to introduce singularity at infinity \cite{zamolodchikovlectures}.
+
+In flat background metric $g: ds^{2}=dz d\bar z$ equations of motions are
+\begin{equation}
+  \label{eq:90}
+  4\partial\bar \partial \varphi = 4\pi\mu e^{2b\varphi}
+\end{equation}
+To solve it we consider auxiliary equation:
+\begin{equation}
+  \label{eq:91}
+  4\partial^{2} \psi + t\psi=0
+\end{equation}
+Function $t$ here is $zz$ component of energy-momentum tensor. Denote by $\psi$  vector
+$\psi=(\psi_{1},\psi_{2})$ of linearly independent solutions. Then solution of equation
+\eqref{eq:90} is given by the expression
+\begin{equation}
+  \label{eq:92}
+  \varphi=-\frac{1}{b} \log \left(\bar \psi(\bar z) \lambda \psi(z)\right),
+\end{equation}
+where $\lambda$ is some matrix that is invariant w.r.t. to the action of monodromy group around the
+singularity.
+
+\begin{equation}
+  \label{eq:89}
+  g=
+\end{equation}
+
+In theory with the action
+$$S=\frac{1}{4\pi} \int \sqrt{g}\left( \frac{1}{2} g^{\mu\nu} \partial_{\mu} \varphi \partial_{\nu}
+  \varphi + Q R\varphi + 4\pi\mu e^{2b\varphi}\right) d^{2}x,$$ 
+where $g$ is a background metric we need to assume some regularization procedure to define a
+functional integral, because we want to integrate over measure that does not depend upon metric.
+The idea is that the form of the action is the same but parameters are changed. 
+So now $\mu$ is not a classical cosmological constant and $\mu,b,Q$ are connected through
+consistency requirements for the theory. 
+The consistency requirement is background-independence. The action should not change when we choose
+another background metric and shift field $\varphi$ accordingly. 
+Let $\tilde g = e^{\sigma} g$, redefine $\varphi$ as $\tilde \varphi=\varphi + \frac{Q}{2}\sigma$,
+then all the terms with $\sigma$ are cancelled if we take into account contributions from matter
+partition function. But it is possible only if 
+$$Q=\frac{25-c_{M}}{6}$$. 
+To make exponential term background-independent we need to have $Q=\frac{1}{b}+b$.
+
+If we consider correlation functions of fields $V_{\alpha}=e^{2\alpha\varphi}$ and impose
+background-independence conditions we obtain relation on conformal weights
+$$\Delta_{\alpha}=\alpha(Q-\alpha)$$
+So for theory to be background-independent we need to have these relations.
+
+Conformal transformation $z\to w(z)$ can be presented as a change in background metric, so 
+$$\varphi(w,\bar w) = \varphi(z,\bar z) -\frac{Q}{2}\log \left|\frac{dw}{dz}\right|^{2}$$
+If we consider flat background metric, we need to have asymptotic $\varphi(z,\bar z)\sim -Q \log
+|z|^{2}$ at infinity to have smooth metric $e^{2b\varphi}$.
+
+Now if we consider flat theory with $\mu=0$ everything is good, but when we introduce the observable
+$e^{-\mu A}=e^{-\mu \int d^{2}x e^{2b\varphi}}$ we need to regularize exponential field, impose
+consistency conditions and we get ordinary Liouville theory as the result! 
+So Liouville theory seems to be unique in this way.
+
+My understanding is that averaging over flat configurations weighted by $e^{-\mu A}$ is equivalent
+to averaging over configurations with cosmological constant $\mu$ which introduces non-zero
+curvature of singularity at infinity in flat background.
+
+By the way, it is also written that they consider unnormalized correlation functions (without the
+division by $Z$) because there are difficulties with the definition of functional integral $\int
+D\varphi e^{-S[\varphi]}$. 
+So we need to impose some normalization on their results.
 
@@
 and primary fields are given by vertex operators $V_{\alpha}=e^{\alpha\varphi}$. But primary fields
-$V_{\alpha}$ and $V_{Q-\alpha}$ are to be identified. For $\alpha=\frac{Q}{2}+i P, P\in \mathbb{R}$
+$V_{\alpha}$ and $V_{Q-\alpha}$ are to be identified. 
+Reflection amplitudes are used for this identification:
+\begin{equation}
+  \label{eq:87}
+  V_{\alpha}(z,\bar z)=S(\alpha) V_{Q-\alpha}(z,\bar z),
+\end{equation}
+where
+\begin{equation}
+  \label{eq:88}
+  S(\alpha)=\frac{\left(\pi\mu\gamma(b^{2})\right)^{\frac{Q-2\alpha}{b}}}{b^{2}}
+  \frac{\gamma(2\alpha b -b^{2})}{\gamma\left(2-\frac{2\alpha}{b}+\frac{1}{b^{2}}\right)}
+\end{equation}
+
+For $\alpha=\frac{Q}{2}+i P, P\in \mathbb{R}$
 fields $V_{\alpha}$ are non-local. Conformal dimension of primary field $V_{\alpha}$ is
@@
 $B_{-b}$. The fusion of $B_{0}=I$ to $V_{\alpha}$ is $\left<V_{\alpha}(x)
-  B_{0}(0)\right>=\frac{R(\alpha,0|\mu_{B})}{|z-\bar z|^{2\Delta_{\alpha}}}$, and the fusion of $V_{-\frac{b}{2}}$ 
+  B_{0}(0)\right>=\frac{R(\alpha,0|\mu_{B})}{|z-\bar z|^{2\Delta_{\alpha}}}$, and the fusion of
+$V_{-\frac{b}{2}}$
+
+\section{Quantum gravity from random graphs}
+\label{sec:quantum-gravity-from}
+
+There is another approach to quantum gravity. Instead of field theory on a surface one can consider
+random discrete surfaces and statistical models on them. Random triangulations or quadrangulations
+of a surface can be represented by dual random graphs \cite{kazakov1986ising}.  The matter is
+introduced as a lattice statistical model on such random graph. Then computation of partition
+function (or correlation functions) for matter on random surface is equivalent to summation over
+random planar Feynman diagrams for certain matrix model.
+
+Using this approach Ivan Kostov was able to obtain disk partition function
+\cite{kostov2004boundary,kostov2003boundary}. His results are as follows.
+
+\begin{equation}
+  \label{eq:95}
+  W(\tau) = -\frac{M^{g}}{2\sin \pi g} \cosh g\tau,
+\end{equation}
+where parameters $M$, $\tau$ are defined by
+\begin{equation}
+  \label{eq:96}
+  \mu=\frac{1}{\pi} \frac{\Gamma\left(1-\frac{1}{g}\right)}{\Gamma\left(\frac{1}{g}\right)} M^{2}
+\end{equation}
+\begin{equation}
+  \label{eq:97}
+  \mu_{B}=\frac{\Gamma\left(1-\frac{1}{g}\right)}{\pi} M\cosh \tau
+\end{equation}
+
+Here $g=\frac{1}{b^{2}}$. The result \eqref{eq:95} is supposed to coincide with the results of
+\cite{fateev2000boundary} in the following sense:
+\begin{equation}
+  \label{eq:98}
+  \partial_{\mu} W = \partial_{\mu_{B}} U
+\end{equation}
+
 \section{Scaling limit and CFT on a cone}

### 2014-02-01 benjamin-ono/notes.tex
Bibliography and some notes on Benjamin-Ono equations

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{ esint }
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\nfp}{\mathfrak{n}^{+}}
\newcommand{\nfm}{\mathfrak{n}^{-}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\uf}{\mathfrak{u}}
\newcommand{\sfr}{\mathfrak{s}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}

\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\sfh}{\hat{\mathfrak{s}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\begin{document}
\title{Notes on non-abelian generalization of Benjamin-Ono equation}
%\author{Anton Nazarov}%% $^{1,2}$}

\maketitle

\begin{abstract}
Benjamin-Ono equation describes waves in deep ocean. This integrable equation is actively studied.
Connection with conformal field theory and quantum Hall liquid was discovered in these studies. 
We introduce non-abelian generalization of Benjamin-Ono equation and demonstrate the connection with
Wess-Zumino-Novikov-Witten and coset models of conformal field theory.
\end{abstract}

\section{Introduction: Benjamin-Ono equation}
\label{sec:introduction}

There are several 1+1-dimensional partial differential equations describing waves. First consider
Riemann equation on function $u(x,t)$:
\begin{equation}
  \label{eq:1}
  u_{t}+ u u_{x} =0
\end{equation}

This equation can be linearized by setting
\begin{equation}
  \label{eq:2}
  u=\bar u+u_{1} (x,t)
\end{equation}
and assuming $u_{1}$ to be small. Then we get chiral wave equation
\begin{equation}
  \label{eq:3}
  u_{t}+\bar u u_{x}+\dots=0
\end{equation}
Solution of Cauchy problem is given by a retarded function
\begin{equation}
  \label{eq:4}
  u(t,x)=u_{0}(x-\bar u t),
\end{equation}
where
\begin{equation}
  \label{eq:5}
  u(x,t=0)=u_{0}(x)
\end{equation}

Solution to Riemann equation can be formally written as
\begin{equation}
  \label{eq:6}
  u(t,x)=u_{0}(x-u(t,x)\cdot t)
\end{equation}
For bulged initial data this solution is unstable, shock waves are formed, then solution is multivalued and hydrodynamic
instability occurs. Concave initial data on the other hand is getting smoother over time.

Corrections to Riemann equation (\ref{eq:1}) dramatically change behavior of solutions. For example
dispersion term kills infinities. Equation with dispersion term $u_{xx}$
\begin{equation}
  \label{eq:7}
  u_{t}+u u_{x}+\nu u_{xx}=0
\end{equation}
is called Burgers equation. Here $\nu$ is liquid viscosity. 
The Hamiltonian
\begin{equation}
  \label{eq:8}
  H=\frac{1}{2} \int u^{2} dx
\end{equation}
is not conserved, so the dynamic is non-Hamiltonian. In the limit $\nu\to 0$ bulged initial data
tends over time to function with a step. It is so called ``weak solution'' of Riemann equation.

One way to obtain equation with conserved energy is to add third derivative:
\begin{equation}
  \label{eq:9}
  u_{t}+u u_{x}+u_{xxx}=0.
\end{equation}
This is famous KdV (Korteweg–de Vries) equation.

Now the Hamiltonian is
\begin{equation}
  \label{eq:10}
  H=\frac{1}{3}\int u^{2}+u u_{x} dx
\end{equation}
Soliton wave is given by the formula
\begin{equation}
  \label{eq:11}
  u_{s}(x-ct)=\frac{1}{\cosh^{2}(x-ct)}
\end{equation}
These waves exist in shallow water when depth is less then wave length.

Appearance of solitons is a distinct property of integrable equations, which are always Hamiltonian
since they have infinitely many conserved quantities
\begin{equation}
  \label{eq:12}
  \left\{ H_{n},H\right\} =0\quad \Leftrightarrow \quad\partial_{t} H_{n}=0
\end{equation}

One of these conserved quantities for KdV equation is soliton mass (Check this expression)
\begin{equation}
  \label{eq:13}
  I_{1}=\int \frac{1}{\cosh^{2}(x-ct)} dx
\end{equation}
It can take arbitrary values.

Solitons are separable, they are very stable and generate large time asymptotics in hydrodynamics.

Equations with even number of derivatives are non-Hamiltonian but we can amend it by making these
terms non-local. E.g.
\begin{equation}
  \label{eq:14}
  u_{t}+u u_{x}+u^{H}_{xx}=0,
\end{equation}
where $u^{H}$ is Hilbert transform
\begin{equation}
  \label{eq:15}
  u^{H}(x)=\frac{1}{\pi} \fint \frac{u(x')}{x-x'}dx' 
\end{equation}
This is Benjamin-Ono equation which describes waves on boundary between two liquids of different
densities in a deep ocean. Solitons for this equation have the form
\begin{equation}
  \label{eq:16}
  u(x,t)=f(x-ct)=\frac{1}{\pi} \frac{A}{(x-A t)^{2}+\frac{1}{A^{2}}}
\end{equation}
Here $A$ is wave velocity and $\frac{1}{A^{2}}$ is width of the wave. Very peculiarly in this
equation mass is quantized.
\begin{equation}
  \label{eq:17}
  I_{1}=\int u(x,t) dx =1\quad \partial_{t} I_{1}=0
\end{equation}
Many-soliton solution have integer mass. For equation with some coefficient $\beta$
\begin{equation}
  \label{eq:18}
   u_{t}+u u_{x}+\beta u^{H}_{xx}=0
\end{equation}
mass is $N\beta$, where $N\in \mathbb{Z}$. So we have quantization on classical level.

If the mass of initial data is not quantized, it decays into several solitons of integer mass moving
in one direction and non-integer mass noise which moves in the opposite direction.

\end{document}

### 2014-03-02 area-length/notes.tex
Minor changes
Uniformization theorem added to the notes, bibliography update, paper started
A lot of changes in this commit. I've added text on uniformization theorem, though it is not complete yet. I need to write about the connection with Liouville equation. Some mock up of a paper is also added, but it does not contain new material, just some text copied from notes.

@@
 Some results exist in literature for particular case of self-avoiding walks ($\kappa=\frac{8}{3}$). We start
-with the description of these results \ref{sec:self-avoid-polyg}, then show that general problem
-leads to Liouville field theory \ref{sec:scaling-random-loops} and obtain our result using Liouville
+with the description of these results \ref{sec:self-avoid-polyg} and show that general problem
+leads to Liouville field theory and obtain our result using Liouville
 field theory fusion rules \ref{sec:liouville-theory}.
@@
 
-\subsection{$O(n)$ model}
-\label{sec:introduction-1}
-
-Self-avoiding polygons can be thought as the limit $n\to 0$ of loops in $O(n)$ model.
-
-Partition function for $O(n)$ model is
-\begin{equation}
-  \label{eq:9}
-  Z_{O(n)} = \sum_{\mbox{loop conf}} x^{\mbox{total length}}
-  n^{\mbox{number of loops}}
-\end{equation}
-Critical point is $x=\frac{1}{\sqrt{2+\sqrt{2-n}}}$, the continuum
-limit in this point is described by minimal model $(p,p')$ with
-$n=-2\cos\left(\frac{\pi p}{p'}\right)$. $c=1-6\frac{(p-p')^2}{pp'}$, $b=\sqrt{\frac{3}{2}}$.
-
-Self-avoiding walk is obtained in the limit $n\to 0$. Then $c=0$ and
-we have logarithmic conformal field theory.
-
-Logarithmic CFT $\sim$ Liouville theory ???
-
-\section{Scaling of random loops}
-\label{sec:scaling-random-loops}
-
-Cardy \cite{cardy2001exact} argues that generating function $G^{(r)}$ for rooted self-avoiding loops is given by a derivative w.r.t. $x$
-of expectation value of $e^{-gA}$ (eq.6):
-\begin{equation}
-  \label{eq:82}
-  Z=\left<e^{-gA}\right>_{\mathrm{SAL}}=\left<e^{-\sqrt{g}\int J_{\lambda}A_{\lambda}d^{2}x}\right>_{\mathrm{SAL}.A}
-\end{equation}
-But reasoning is quite strange and unsound. Due to the need to use $g$ for metric in later sections
-we will denote area coupling constant by $\mu$ and loop length coupling constant by $\mu_{B}=-\ln x$
-(boundary).
-
-In this section we introduce scaling function for random loops.
-
-Consider rooted loops in $O(n)$ model. Let $N^r(L)$ be number of
-rooted loops with a given length.  By $N^r(L,A)$ we denote the number
-of loops of given length and area. $N^r(L)=\int_0^{\infty} N^r(L,A)
-dA$. Area weighted number of loops is denoted by $G^r(L,\mu)$. (Here
-$\mu$ is bulk coupling constant ).
-\begin{equation}
-  \label{eq:2}
-  G^r(L,\mu)=\int e^{\mu A} N^r(L,A) dA
-\end{equation}
-
-\begin{equation}
-  \label{eq:1}
-  G^r (\mu,x) = \sum_{\mathrm{clusters}} N^r (L,A) x^L e^{-\mu A}
-\end{equation}
-
-The idea is to write $G$ as a correlation function in Liouville
-theory.
-
-Note that number of rooted loops of given area scales as the area to
-the power minus one.
+Let us reformulate this problem a bit so that it could be generalized. Consider self-avoiding
+polygons of length not greater than $n$ on a square lattice. This implies uniform measure on
+polygons. The scaling limit of self-avoiding walk when lattice mesh size $a\to 0$ and length $l\to
+\infty$ is conjectured to be described by Schramm-Loewner evolution with parameter
+$\kappa=\frac{8}{3}$. Since we consider closed loops the limit is loops of conformal loop ensemble
+with $\kappa=\frac{8}{3}$.
+The natural question is how to generalize the definition of functions $G$ and $F$ to CLE with
+arbitrary value of $\kappa$?
+
+If we consider self-avoiding polygons of length up to $n$ the generating function $G_{n}(x)$ can be
+introduced as non-local observable. Denote by $N_{n}$ total number of polygons of length up to $n$.
+Since we have uniform measure, the probability for polygon to have length $l$ is
+$\frac{p_{l}}{N_{n}}$. Then the generating function $G_{n}(x)$ is the expectation value of $x^{l}=e^{-\mu_{B}l}$
+\begin{equation}
+  \label{eq:102}
+  G_{n}(x)=\sum_{l<n} p_{l} x^{l} = N_{n} \sum_{l<n} \frac{p_{l}}{N_{n}} x^{l} = N_{n}\mathbb{E}[x^{l}]
+\end{equation}
+Generating function for polygons of given area can be written in similar way as
+\begin{equation}
+  \label{eq:103}
+   G_{n}(x,\mu)=\sum_{l<n} p_{l,A} x^{l} e^{-\mu A} = N_{n} \sum_{l<n} \frac{p_{l,A}}{N_{n}} x^{l} =
+   N_{n}\mathbb{E}[x^{l} e^{-\mu A}]
+\end{equation}
+Note that the  observables $\mathbb{E}[e^{-\mu_{B}l}]$ ,$\mathbb{E}[e^{-\mu_{B}l -\mu A}]$ are
+non-local. So while the generalization from self-avoiding walk to arbitrary SLE is natural it is not
+clear how one can compute such observables.
+
+Local observables w.r.t. SLE can be described by correlation functions of boundary conformal field
+theory. So we need a theory which reproduces CFT in the limit $\mu,\mu_{B}\to 0$ and has non-local
+observables such as area and length.
+
+Liouville theory of two-dimensional gravity is a natural choice, but to see it we need to discuss
+some geometry first.
+
+Parameter $\kappa$ of SLE and CLE is connected with Hausdorff dimension of the curve.
 
@@
 
+Note that number of rooted loops of given area scales as the area to
+the power minus one.
+
+Let $N^r(L)$ be number of rooted loops with a given length. By $N^r(L,A)$ we denote the number of
+loops of given length and area. $N^r(L)=\int_0^{\infty} N^r(L,A) dA$. Area weighted number of loops
+is denoted by $G^r(L,\mu)$. (Here $\mu$ is bulk coupling constant ).
+\begin{equation}
+  \label{eq:2}
+  G^r(L,\mu)=\int e^{\mu A} N^r(L,A) dA
+\end{equation}
+
+\begin{equation}
+  \label{eq:1}
+  G^r (\mu,x) = \sum_{\mathrm{clusters}} N^r (L,A) x^L e^{-\mu A}
+\end{equation}
+
 At $x\to x_c$
@@
 
-Partition function is product over loops of different length
-\begin{equation}
-  \label{eq:10}
-  Z_{O(n)} = \sum_{\mbox{loop conf}} \prod_L x^{L N(L)} n^{N(L)} = \sum_{\mbox{loop conf}} \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)}
-\end{equation}
-
-We can rewrite $G^r(\mu,x)$ as the derivative of generating function
-\begin{equation}
-  \label{eq:7}
-  G^r(\mu,x)=\mu\partial_x \log Z(\mu,\mu_B)
-\end{equation}
-
-Here
-\begin{equation}
-  \label{eq:8}
-  Z(\mu,\mu_B) = \left< e^{-\mu A} \right> = \frac{\sum_{\mbox{loop conf}}
-  \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)} e^{-\mu A}}{\sum_{\mbox{loop conf}} \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)}}
-\end{equation}
+%% 
+%% \subsection{$O(n)$ model}
+%% \label{sec:introduction-1}
+%% 
+%% Self-avoiding polygons can be thought as the limit $n\to 0$ of loops in $O(n)$ model.
+%% 
+%% Partition function for $O(n)$ model is
+%% \begin{equation}
+%%   \label{eq:9}
+%%   Z_{O(n)} = \sum_{\mbox{loop conf}} x^{\mbox{total length}}
+%%   n^{\mbox{number of loops}}
+%% \end{equation}
+%% Critical point is $x=\frac{1}{\sqrt{2+\sqrt{2-n}}}$, the continuum
+%% limit in this point is described by minimal model $(p,p')$ with
+%% $n=-2\cos\left(\frac{\pi p}{p'}\right)$. $c=1-6\frac{(p-p')^2}{pp'}$, $b=\sqrt{\frac{3}{2}}$.
+%% 
+%% Self-avoiding walk is obtained in the limit $n\to 0$. Then $c=0$ and
+%% we have logarithmic conformal field theory. 
+%% 
+%% Logarithmic CFT $\sim$ Liouville theory ???
+%% 
+%% \section{Scaling of random loops}
+%% \label{sec:scaling-random-loops}
+%% 
+%% Cardy \cite{cardy2001exact} argues that generating function $G^{(r)}$ for rooted self-avoiding loops is given by a derivative w.r.t. $x$
+%% of expectation value of $e^{-gA}$ (eq.6):
+%% \begin{equation}
+%%   \label{eq:82}
+%%   Z=\left<e^{-gA}\right>_{\mathrm{SAL}}=\left<e^{-\sqrt{g}\int J_{\lambda}A_{\lambda}d^{2}x}\right>_{\mathrm{SAL}.A}
+%% \end{equation}
+%% But reasoning is quite strange and unsound. Due to the need to use $g$ for metric in later sections
+%% we will denote area coupling constant by $\mu$ and loop length coupling constant by $\mu_{B}=-\ln x$
+%% (boundary). 
+%% 
+%% 
+%% In this section we introduce scaling function for random loops. 
+%% 
+%% Consider rooted loops in $O(n)$ model.
+%% 
+%% The idea is to write $G$ as a correlation function in Liouville
+%% theory.
+%% 
+%% 
+%% Partition function is product over loops of different length
+%% \begin{equation}
+%%   \label{eq:10}
+%%   Z_{O(n)} = \sum_{\mbox{loop conf}} \prod_L x^{L N(L)} n^{N(L)} = \sum_{\mbox{loop conf}} \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)}
+%% \end{equation}
+%% 
+%% 
+%% We can rewrite $G^r(\mu,x)$ as the derivative of generating function
+%% \begin{equation}
+%%   \label{eq:7}
+%%   G^r(\mu,x)=\mu\partial_x \log Z(\mu,\mu_B)
+%% \end{equation}
+%% 
+%% Here
+%% \begin{equation}
+%%   \label{eq:8}
+%%   Z(\mu,\mu_B) = \left< e^{-\mu A} \right> = \frac{\sum_{\mbox{loop conf}}
+%%   \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)} e^{-\mu A}}{\sum_{\mbox{loop conf}} \prod_L\prod_A x^{L N(L,A)} n^{N(L,A)}}
+%% \end{equation}
+%% 
+%% 
+KPZ-scaling. ``Wrong branch'' for $\mu_{B}$?
 
@@
 
-Liouville theory, flat metric, asymptotic for field, Coulomb gas formalism.
-\cite{nakayama2004liouville,ponsot2002boundary,teschner2001liouville,fateev2000boundary,teschner2000remarks,zamolodchikov1996conformal}
-
-Liouville theory describes internal metric of surface. It is possible to obtain length of boundary
-and area of surface with such a metric. To get the answer for flat loops we need to impose some
-condition on metric in the bulk.
+%%  Liouville theory, flat metric, asymptotic for field, Coulomb gas formalism.
+%%  \cite{nakayama2004liouville,ponsot2002boundary,teschner2001liouville,fateev2000boundary,teschner2000remarks,zamolodchikov1996conformal} 
+%%  
+%%  Liouville theory describes internal metric of surface. It is possible to obtain length of boundary
+%%  and area of surface with such a metric. To get the answer for flat loops we need to impose some
+%%  condition on metric in the bulk. 
+%%
+
+In last 30 years great progress was made in study of quantum Liouville theory made in papers
+\cite{fateev2000boundary,zamolodchikov1996conformal,knizhnik1988fractal} and in study of matter on
+random discrete surfaces
+\cite{kazakov1986ising,duplantier1990geometrical,gaudin1989n,duplantier1988conformal}. These two
+approaches to two-dimensional quantum gravity are in agreement
+\cite{kostov2004boundary,kostov2003boundary}. In recent years strict mathematical definitions and proofs for some
+field-theoretic results were obtained \cite{duplantier2011liouville,garban2012quantum}. All these
+solid developments allow us to use Liouville theory as a theory of random surfaces and apply its
+methods to the geometry of random loops. Our approach is similar to the application of Liouville
+theory to harmonic measure problems \cite{duplantier2000conformally}.
+
+In present text we do not try to be mathematically strict and do not use the definition of Liouville
+measure from \cite{duplantier2011liouville} but we suppose that our result can be proven using
+methods of that paper.
+
+Before moving to quantum Liouville theory and scaling limit of generating functions of self-avoiding
+polygons we need to discuss the geometry of Riemann surfaces and polygons on complex plane and its
+connection with Liouville equation.
+
+\subsection{Uniformization of Riemann surfaces and Liouville equation}
+\label{sec:unif-riem-surf}
+
+The problem of uniformization of Riemann surfaces was of central importance in mathematics at the
+end of 19th -- beginning of 20th century. Great mathematicians such as Riemann, Klein and Poincare
+proposed different approaches to its solution and the uniformization theorem was finally proven by
+Koebe in 1907.
+
+\begin{definition}
+  A Riemann surface is a connected Hausdorff space $M$ (distinct points have disjoint neighbourhoods) together with a collection
+  of charts ${U_{\alpha} , z_{\alpha} }$ with the following properties:
+  \begin{itemize}
+  \item The $U_{\alpha}$ form an open covering of $M$ .
+  \item Each $z_{\alpha}$ is a homeomorphic mapping ($\exists$ continuous inverse) of $U_{\alpha}$ onto an open subset of the complex plane $\mathbb{C}$.
+  \item If $U_{\alpha}\cap  U_{\beta} \neq \emptyset$, then $f_{\alpha\beta} = z_{\beta}\circ  z_{\alpha}^{-1}$ is complex analytic on $z_{\alpha} (U_{\alpha} \cap U_{\beta} )$.
+  \end{itemize}  
+\end{definition}
+
+The statement of the theorem is 
+\begin{theorem}
+  Every simply connected Riemann surface is conformally equivalent to one of the three domains: the
+  open unit disk, the complex plane, or the Riemann sphere. In particular it admits a Riemannian
+  metric of constant curvature.
+\end{theorem}
+
+This classifies Riemannian surfaces as elliptic (positively curved -- rather, admitting a constant
+positively curved metric), parabolic (flat), and hyperbolic (negatively curved) according to their
+universal cover.
+
+Proof is based upon existence and properties of Green function for the surface $M$.
+
+ We can
+ compose each $z_{\alpha}$ with a Mobius transformation of the disk onto itself so that we can
+assume that for each coordinate disk $U_{\alpha}$ and each $p_{0}\in  U_{\alpha}$ there is a coordinate function
+$z$ with $z (p_{0} ) = 0$.
+
+     Suppose $M$ is a Riemann surface. Fix $p_{0}\in  M$ and let $z : U\to  \mathbb{D}$ be a coordinate
+function such that $z(p_{0} ) = 0$. Let $\mathcal{F}_{p_{0}}$ be the collection of subharmonic
+functions $v$ on $M \setminus p_{0}$ satisfying
+\begin{itemize}
+\item $v = 0$ on $M \setminus K$, for some compact $K\subset M$ with $K \neq M$, and
+\item $\limsup_{p\to p_{0}} (v(p) + log |z(p)|) < \infty$
+\end{itemize}
+
+Set
+\begin{equation}
+  \label{eq:104}
+  g_{M} (p, p_{0} ) = \sup\{v(p) : v\in \mathcal{F}_{p_{0}} \}
+\end{equation}
+
+Second condition does not depend on the choice of the coordinate function $z_{\alpha}$ , provided
+$z_{\alpha} (p_{0} ) = 0$. The collection $\mathcal{F}_{p_{0}}$ is a Perron family, so by Harnack's
+Theorem      $g_M (p, p_{0} )$ is either harmonic in  $M \setminus \{p_{0} \}$, or  is equal to $+\infty$  for
+all $p\in M \setminus \{p_{0} \}$.
+In the first case, $g_{M} (p, p_{0} )$ is called Green's function with pole (or logarithmic singularity)
+at $p_{0}$ . In the second case we say that Green's function does not exist.
+
+The Uniformization Theorem can be reformulated as follows (Koebe[1907]):
+
+\begin{theorem}
+  Suppose $M$ is a simply connected Riemann surface. If Green's function exists for $M$ , then there
+  is a one-to-one analytic map of $M$ onto $\mathbb{D}$. If $M$ is compact, then there is a
+  one-to-one analytic map of $M$ onto $\mathbb{C}^{*}$ . If $M$ is not compact and if Green's
+  function does not exist for $M$ , then there is a one-to-one analytic map of $M$ onto
+  $\mathbb{C}$.
+\end{theorem}
+
+Note that uniformization theorem does not give a construction of uniformization map.
+
+More modern formulation of uniformization principle operates with quotient of universal cover of
+Riemann surface by the action of some Fuchsian group. This group is monodromy group of Liouville
+equation (?)
+
+\subsection{Classical theory}
+\label{sec:classical-theory}
 
@@
 \end{equation}
+
+**** More on classical solutions here *****
+
+\subsection{Functional integral formulation}
+\label{sec:funct-integr-form}
+
+To have quantum theory of gravity we need to define somehow functional integral. It can symbolically
+written as
+\begin{equation}
+  \label{eq:101}
+  \int [\mathcal{D}\varphi] e^{-S[\varphi]}
+\end{equation}
+Actual definition is tricky, because we need to quantize metric $e^{2b\varphi}g^{\mu\nu}$ and this
+metric takes part not only in action for field $\varphi$, but also in action for matter field and
+even functional integral measure \cite{david1988conformal,distler1989conformal,polyakov1987gauge}.
 
@@
 functional integral, because we want to integrate over measure that does not depend upon metric.
+
 The idea is that the form of the action is the same but parameters are changed. 
@@
 satisfy differential equations of order $n+1$.
+
+\subsubsection{KPZ-scaling}
+\label{sec:kpz-scaling}
+
+Knizhnik-Polyakov-Zamolodchikov (KPZ \cite{knizhnik1988fractal}) scaling relation gives behavior of
+Liouville correlation functions w.r.t. to change in coupling constants $\mu, \mu_{B}$. This relation
+is easy to obtain. Consider reparametrisation $\varphi\to\varphi-\frac{1}{2b}\ln\mu$. The action
+$S[\mu,\mu_{B}]$ is then
+\begin{equation}
+  \label{eq:84}
+  S[\mu,\mu_{B}]=-\frac{1}{4\pi}\int d^{2}x \frac{1}{2b}QR\ln\mu+S\left[1,\frac{\mu_{B}}{\sqrt{\mu}}\right]
+\end{equation}
+Since
+\begin{equation}
+  \label{eq:85}
+  \int d^{2}x R =4\pi\chi,
+\end{equation}
+where $\chi=2-2\#handles-\#boundaries$ is Euler characteristic of the surface, we get
+\begin{equation}
+  \label{eq:99}
+    S[\mu,\mu_{B}]=-\frac{1}{2b}Q\chi\ln\mu+S\left[1,\frac{\mu_{B}}{\sqrt{\mu}}\right]
+\end{equation}
+Substitute it into functional integral for correlation function of arbitrary bulk and boundary
+vertex operators:
+\begin{equation}
+  \label{eq:100}
+  \langle V_{\alpha_{1}}(z_{1})\dots V_{\alpha_{n}}(z_{n}) B_{\beta_{1}}(x_{1})\dots B_{\beta_{m}}(x_{m})\rangle=
+\end{equation}
 
@@
 Here $g=\frac{1}{b^{2}}$. The result \eqref{eq:95} is supposed to coincide with the results of
-\cite{fateev2000boundary} in the following sense:
+\cite{fateev2000boundary} \eqref{eq:21} in the following sense:
 \begin{equation}
@@
   \partial_{\mu} W = \partial_{\mu_{B}} U
+\end{equation}
+for $\alpha=b$ (?)
+
+Substitute $  M^{2}=\mu\frac{\pi}{1}
+\frac{\Gamma\left(\frac{1}{g}\right)}{\Gamma\left(1-\frac{1}{g}\right)}$ to \eqref{eq:95}:
+\begin{equation}
+  \label{eq:83}
+  W(\tau) = -\frac{\left(\mu\frac{\pi}{1}
+\frac{\Gamma\left(\frac{1}{g}\right)}{\Gamma\left(1-\frac{1}{g}\right)}\right)^{g/2}}{2\sin \pi g} \cosh g\tau,
+\end{equation}
+
+and compare with \eqref{eq:21} for $\alpha=b$:
+
+\begin{equation}
+  U(b)=\frac{2}{b} \left(\pi\mu\gamma( b^{2})\right)^{\frac{-b+1/b}{2b}} \Gamma(b^{2})
+  \Gamma\left(1-\frac{1}{b^{2}}\right) \cosh (b-1/b)\pi s
+\end{equation}
+where $s$ is determined from the equation
+\begin{equation}
+  \cosh^{2} \pi b s=\frac{\mu_{B}^{2}}{\mu}\sin \pi b^{2}
 \end{equation}

### 2014-03-15 area-length/notes.tex
Some text on pinning operator and Hausdorff dimension

@@
 
-\subsection{Self-avoiding polygons}
+v\subsection{Self-avoiding polygons}
 \label{sec:self-avoid-polyg}
@@
 
+Using their numeric results, authors of the paper \cite{richard2001scaling} were able to come with
+the following scaling for rooted generating function:
+\begin{equation}
+  \label{eq:112}
+  G^{(r)}(\mu,\mu_B)\sim \mu^{\frac{1}{3}} \frac{\mathrm{Ai}'(s)}{\mathrm{Ai}(s)},\quad \mbox{where}\; s=\left(\frac{\mu_{B}^{2}}{\mu}\right)^{\phi}
+\end{equation}
+We want to get physical and geometrical understanding of this result and its generalization to
+different measures on closed curves.
+
 Let us reformulate this problem a bit so that it could be generalized. Consider self-avoiding
@@
 theory. So we need a theory which reproduces CFT in the limit $\mu,\mu_{B}\to 0$ and has non-local
-observables such as area and length.
+observables such as area and length. Note also that the parameter $\kappa$ is connected with the
+central charge of conformal field theory by the relation
+\begin{equation}
+  \label{eq:113}
+  c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}
+\end{equation}
 
@@
 the power minus one.
+
+Hausdorff dimension in CFT is calculated by the insertion of certain primary field called ``pinning
+operator'' \cite{bettelheim2005harmonic}. Expanded presentation can be found in the paper
+\cite{gruzberg2006stochastic}. The argument is as follows.
+
+Consider a closed curve. Harmonic measure of some part of the curve can be understood as a charge of
+that part if the curve is made of conducting material and its total charge is equal to one. 
+Closed curve can be covered by small circles of radius $r$ centered at points
+$z_{i}$. Consider one such circle. The curve divides the circle into two parts, inner and outer
+w.r.t. to curve. Outer part can be conformally mapped to the unit disk. Denote this map by $w(z)$.
+With the normalization such that one point is fixed and derivative at infinity is equal to one the
+moments of harmonic measure in small circle of radius $r$ scale as
+\begin{equation}
+  \label{eq:116}
+  \mu(r)\sim |w(r)|\sim r |w'(r)|
+\end{equation}
+So scaling of the moments of $\mu(r)$ are determined by scaling of $|w'(r)|$:
+\begin{equation}
+  \label{eq:117}
+  \prec |w'(r)|^{h}\succ \sim r^{\Delta(h)}, \quad r\to 0
+\end{equation}
+
+The moments of harmonic measure for the whole curve can be written as a sum over small circles:
+\begin{equation}
+  \label{eq:120}
+  M_{h}=\sum_{i=1}^{N} \mu(z_{i},r)^{h}
+\end{equation}
+
+In the limit $r\to 0$ number of circles grows and moments scale as
+\begin{equation}
+  \label{eq:121}
+  M_{h}\sim r^{\tau(h)}
+\end{equation}
+The function $\tau(h)$ is called multifractal spectrum. For simple curve $\tau(h)=h-1$, so anomalous
+exponents $\delta(h)$ are defined as $\delta(h)=\tau(h)-h+1$.
+
+Note that $M_{0}$ is a total number of circles and $\tau(0)=-d_{H}$ by definition of Hausdorff
+dimension. For $h=1$ the sum is equal to the total charge of the curve so it does not scale and
+$\tau(1)=0$.
+
+To calculate multifractal spectrum we need to average over the values at points $z_{i}$. One can
+assume the ergodicity and rewrite $M_{h}$ as
+\begin{equation}
+  \label{eq:122}
+  M_{h}=N \prec \mu(z,r)^{h}\succ
+\end{equation}
+for some point $z$. The total number of circles $N$ is equal to zeroth momentum $M_{0}$, so
+$M_{h}\sim r^{\tau(0)} \prec \mu(z,r)^{h}\succ$. Local multifractal spectrum $\tilde\tau(h)$ is
+defined as $ \prec \mu(z,r)^{h}\succ\sim r^{\tilde\tau(h)}$ and local anomalous exponents are
+$\Delta_{bulk}(h)=\tilde\tau(h) -h$.
+
+Following relations hold for multifractal spectrum and anomalous exponents:
+$\tilde\tau(h)=\tau(h)-\tau(0)$, $\Delta_{bulk}(h)=\delta(h)-\delta(0)$, $d_{H}=1+\Delta_{bulk}(1)$
+
+Multifractal spectrum and anomalous exponents were first obtained by Duplantier in paper
+\cite{duplantier2000conformally} using quantum gravity. The result is
+\begin{equation}
+  \label{eq:123}
+  \Delta_{bulk}(h)=-\frac{h}{2}+\left(\frac{1}{16}+\frac{1}{4\kappa}\right)
+  (\kappa-4+\sqrt{(\kappa-4)^{2}+16\kappa h})
+\end{equation}
+\begin{equation}
+  \label{eq:124}
+  \tau(h)=\frac{1}{2}(h-1) +\frac{25-c}{24}\left(\sqrt{\frac{24 h +1-c}{25-c}}-1\right), 
+\end{equation}
+where $c$ and $\kappa$ are connected by \eqref{eq:113}.
+
+So we have following result for Hausdorff dimension (eq \eqref{eq:5}):
+\begin{equation}
+  \label{eq:125}
+  d_{H}=1+\frac{\kappa}{8}
+\end{equation}
+
+The stochastic averages for (local) moments of harmonic measure are represented by different CFT
+correlation functions depending upon the position of point of interest. If we are interested in a
+bulk point lying on a curve, we need to put at this point a special operator. It is $\Psi_{10}$
+which has an interpretation as an operator that creates two lines coming from the point in the bulk.
+To see it one can consider circle of small radius $\varepsilon$ centered at $z$. Put some conformal
+boundary condition on one half of the circle and another condition on the rest of the circle. Then
+critical curve would join the points of change in boundary conditions. The expectation values of
+observables in this geometry are given by CFT correlation functions with two boundary condition
+changing operators inserted:
+\begin{equation}
+  \label{eq:119}
+  \left< \Psi_{12}(z')\Psi_{12}(z'')\right>
+\end{equation}
+where $|z'-z|\leq \varepsilon$ and $|z''-z|\leq \varepsilon$. The boundary condition changing
+operators in Coulomb gas picture can be presented as the vertex operators
+$V_{\alpha_{12}}=e^{i\sqrt{2}\alpha_{12}\varphi(z)}$. When $\varepsilon\to 0$ we can fuse this two
+operators to single operator $V_{2\alpha_{12}}$. Note that $\alpha_{12}=-\frac{1}{2}\alpha_{-}$
+\eqref{eq:55}, so $V_{2\alpha_{12}}\sim V_{-\alpha_{-}}\sim V_{\alpha_{+}}$ (?)
+
+The moments of harmonic measure are connected with the CFT correlation functions by
+\begin{equation}
+  \label{eq:118}
+  \left<O_{h}(r) \Psi_{10}(0)\Psi(\infty)\right>\sim r^{h'-2h}\prec |w'(r)|^{h}\succ
+\end{equation}
 
@@
 
+Let $D$ denote $\mathbb{C}$, $\mathbb{C}^{*}$ or $\mathbb{D}$.
+\begin{theorem}
+Every Riemann surface $M$ is conformally equivalent to the quotient $D/\Gamma$ with $\Gamma$  a freely acting
+discontinuous group of fractional transformations preserving $D$.
+\end{theorem}
+
+Let us consider the case of Riemann surfaces with universal covering $\mathbb{H}\sim \mathbb{D}$ and
+denote by $J_{H}$ the complex analytic covering $J_{H} : \mathbb{H}\to M$ . In this case $\Gamma$
+(the automorphism group of $J_{H}$ ) is a finitely generated Fuchsian 
+group $\Gamma\subset PSL(2,
+\mathbb{R}) = SL(2, \mathbb{R})/{I, -I}$ acting on $\mathbb{H}$ by linear fractional transformations
+\begin{equation}
+  \label{eq:106}
+  w\in \mathbb{H}\quad \gamma\cdot w=\frac{aw+b}{cw+d}\in\mathbb{H},\quad
+  \gamma=\begin{pmatrix} a & b\\ c & d\end{pmatrix} \in\Gamma\subset PSL(2,\mathbb{R})
+\end{equation}
+
+By the fixed point equation
+\begin{equation}
+  \label{eq:107}
+  w_{\pm}=\frac{a-d\pm\sqrt{(a+d)^{2}-4}}{2c}
+\end{equation}
+it follows that $\gamma\neq I$ can be classified according to the value of $|\mathrm{tr} \gamma|$:
+\begin{enumerate}
+\item Elliptic case: $|\mathrm{tr} \gamma|<2$, $\gamma$ has one fixed point on $\mathbb{H}$:
+  $w_{-}=\bar w_{+}\not\in\mathbb{R}$ and $M$ has branch point
+\item Parabolic case: $|\mathrm{tr}\gamma|=2$, $w_{-}=w_{+}\in\mathbb{R}$ and Riemann surface $M$
+  has a puncture.
+\item Hyperbolic case: $|\mathrm{tr}\gamma|>2$, Riemann surface has handles. 
+\end{enumerate}
+
+   A Riemann surface $M$ isomorphic to the quotient $\mathbb{H}/\Gamma$ has the Poincar\'e metric $\hat g$ as the
+unique metric with scalar curvature $R_{\hat g} = -1$ compatible with its complex structure. This
+implies the uniqueness of the solution of the Liouville equation on $M$. The Poincar\'e metric
+on $\mathbb{H}$ is
+\begin{equation}
+  \label{eq:108}
+  ds^{2}=\frac{|dw|^{2}}{(\Im w)^{2}}
+\end{equation}
+Note that $P SL(2, \mathbb{R})$ transformations are isometries of $\mathbb{H}$ endowed with the Poincar\'e metric.
+   An important property of $\Gamma$ is that it is isomorphic to the fundamental group $\pi_{1}(M)$.
+
+Substitute $w=J_{H}^{-1}(z)$ in \eqref{eq:108} and get Poincar\'e metric on $M$:
+\begin{equation}
+  \label{eq:109}
+  ds^{2}=2\hat g_{z\bar z}|dz|^{2}=e^{\varphi(z,\bar z)} |dz|^{2}=\frac{|J_{H}^{-1}(z)'|^{2}}{(\Im
+    J_{H}^{-1}(z))^{2}} |dz|^{2}
+\end{equation}
+
+The curvature in complex coordinates is given by
+\begin{equation}
+  \label{eq:110}
+  R_{\hat g}=-\hat g^{z\bar z}\partial \bar \partial \ln \hat g_{z\bar z}, \quad \hat g^{z\bar z}=2e^{-\varphi}
+\end{equation}
+The condition $R_{\hat g}=-1$ is equivalent to Liouville equation
+\begin{equation}
+  \label{eq:111}
+  \partial \bar \partial \varphi(z,\bar z)=\frac{1}{2} e^{\varphi(z,\bar z)}
+\end{equation}
+The field $\tilde\varphi=\varphi+\ln \mu, \; \mu>0$ defines a metric of constant curvature $-\mu$.
+
 \subsection{Classical theory}
@@
   \varphi + Q R\varphi + 4\pi\mu e^{2b\varphi}\right) d^{2}x,$$ 
-where $g$ is a background metric we need to assume some regularization procedure to define a
-functional integral, because we want to integrate over measure that does not depend upon metric.
-
-The idea is that the form of the action is the same but parameters are changed. 
+where $g$ is a background metric, we need to assume some regularization procedure to define a
+functional integral, because we want to integrate over measure that does not depend upon metric
+\begin{equation}
+  \label{eq:114}
+  ||\delta\varphi||^{2}=\int \sqrt{g} e^{\varphi(x)}(\delta\varphi)^{2} d^{2}x
+\end{equation}
+This measure is non-linear and non translation-invariant and we need to substitute it with the
+measure
+\begin{equation}
+  \label{eq:115}
+    ||\delta\varphi||^{2}=\int \sqrt{g}(\delta\varphi)^{2} d^{2}x,
+\end{equation}
+that is  w.r.t. to change $\varphi(x)\to \varphi(x) +C(x)$ for arbitrary fixed function $C(x)$.
+
+There is for now no way to do it, so 
+the idea is that the form of the action after regularization is the same but parameters are changed.
+The parameters are then obtained from consistency condition, which is background-independence of the
+theory.
+
 So now $\mu$ is not a classical cosmological constant and $\mu,b,Q$ are connected through
@@
 another background metric and shift field $\varphi$ accordingly. 
-Let $\tilde g = e^{\sigma} g$, redefine $\varphi$ as $\tilde \varphi=\varphi + \frac{Q}{2}\sigma$,
+Let $\tilde g = e^{\sigma} g$ and redefine $\varphi$ as $\tilde \varphi=\varphi +
+\frac{Q}{2}\sigma$.
+
+Consider first the case $\mu=0$.
 then all the terms with $\sigma$ are cancelled if we take into account contributions from matter
@@
 
+\section{Scaling of generating function for polygons}
+\label{sec:scal-gener-funct}
+
+The solution is
+\begin{equation}
+  \label{eq:105}
+  \left< V_{\alpha_{01}} B_{\beta_{10}}\right>
+\end{equation}
+
 \section{Conclusion}

### 2014-03-29 area-length/notes.tex
Pinning operator is written

@@
 which has an interpretation as an operator that creates two lines coming from the point in the bulk.
+
+Identification of this operator is based upon the model of compactified boson field. Level lines of
+such a field are critical curves described by Schramm-Loewner evolution. Vertex operators of the
+model are either ``electric'' or ``magnetic''. Magnetic operators are interpreted as discontinuities
+in field value.
+
+This interpretation is based on the following analogy. Consider $O(n)$ model on the domain
+$\mathcal{D}$ on the honeycomb lattice. It's configurations can be seen as the configurations of
+oriented loops with arbitrary orientation. Then each site has weight $e^{\pm i e_{0}\pi/6}$ if loop
+is turning right or left at the site. The parameter $e_{0}$ is connected with $n$ by $n=2\cos \pi
+e_{0}$. Then we need to introduce height function that will give us field in critical limit. Choose
+an arbitrary site of dual lattice as a reference point $H=0$ and increase or decrease $H$ by $\pi$
+when crossing loop depending upon its orientation.
+
+Since the choice of loop orientations is arbitrary field $H$ should be compactified $H\simeq
+H+2\pi$.
+ In critical limit this gives us free boson theory:
+\begin{equation}
+  \label{eq:126}
+  S=\frac{g}{4\pi} \int_{\mathcal{D}} d^{2}x (\nabla H)^{2} +\frac{i e_{0}}{2\pi}
+  \int_{\partial\mathcal{D}} dl KH +\frac{i e_{0}}{8\pi} \int_{\mathcal{D}} d^{2}x
+  RH+\lambda\int_{\mathcal{D}} d^{2}x V(H)
+\end{equation}
+Boundary loops has different weights. To take this into account we need to add second term to the
+action. Third term comes from the curvature of surface which can be realized microscopically by
+insertion of lattice faces with number of edges not equal to 6. The last term is locking potential
+which is needed for field compactification. In the limit $\lambda\to\infty$ field $H=k\pi$, so the
+potential is
+\begin{equation}
+  \label{eq:127}
+  V(H)=\sum_{k\in\mathbb{Z}\setminus \{0\}}v_{k}e^{2ikH}
+\end{equation}
+Each term in this expansion is vertex operator with scaling dimension $x_{k}=\frac{2}{g}k(k-e_{0})$,
+so for $e_{0}\in [0,1]$ the operator with $k=1$ is most relevant and it is strictly marginal if
+$x_{k}=2$, which is required for conformal invariance. This fixes us the parameter $g$:
+\begin{equation}
+  \label{eq:128}
+  e_{0}=1-g\quad n=-2\cos \pi g
+\end{equation}
+Dense phase is for $e_{0}\in [0,1], g\in [0,1]$ and dilute phase of $O(n)$ model corresponds to
+$e_{0}\in [-1,0], g\in [1,2]$.
+Now critical curves can be identified with the level lines of field $H$ and $g=\frac{4}{\kappa}$.
+
+Following notation is more conventional:
+$\varphi=\sqrt{2g}H$ with new coupling constant in action equal to $\frac{1}{2}$. Compactification
+radius for this choice is $\mathcal{R}=\sqrt{\frac{8}{\kappa}}$ and action reads
+\begin{equation}
+  \label{eq:129}
+  S[\varphi]=\frac{1}{8\pi}\int_{\mathcal{D}}d^{2}x ((\nabla \varphi)^{2} + i2\sqrt{2} \alpha_{0}
+  R\varphi)+i\frac{\sqrt{2}\alpha_{0}}{2\pi} \int_{\partial\mathcal{D}} dl
+  K\varphi+\int_{\mathcal{D}}d^{2}x e^{i\sqrt{2}\alpha_{+}\varphi}
+\end{equation}
+where $2\alpha_{0}=\frac{\sqrt{\kappa}}{2}e_{0}=\frac{\sqrt{\kappa}}{2}-\frac{2}{\sqrt{\kappa}}$,
+$\alpha_{\pm}=\alpha_{0}\pm\sqrt{\alpha_{0}^{2}+1}$, $\alpha_{+}=\frac{\sqrt{\kappa}}{2}$,
+$\alpha_{-}=-\frac{2}{\sqrt{\kappa}}$.
+
+Central charge of this theory is
+\begin{equation}
+  \label{eq:130}
+  c=1-24\alpha_{0}^{2}=1-3\frac{(\kappa-4)^{2}}{2\kappa}
+\end{equation}
+In computations of correlation functions the last term in action is treated perturbatively. Due to
+neutrality condition at most first order terms survive.
+
+We now describe theory on a full plane which has the following primary fields and local operators.
+
+By choosing coordinates we can make space locally flat with the curvature at infinity. Then instead
+of term with the curvature $R$ we get vertex operator $V_{-2\alpha_{0},-2\alpha_{0}}(\infty)$.
+
+We can decompose field $\varphi(z,\bar z)$ into holomorphic and antiholomorphic part and introduce a
+dual field $\tilde\varphi$ as
+\begin{equation}
+  \label{eq:131}
+  \varphi(z,\bar z)=\phi(z)+\bar\phi(\bar z),\quad \tilde\varphi=-i\phi(z)+i\bar\phi(z)
+\end{equation}
+
+Holomorphic and antiholomorphic vertex operators are
+\begin{equation}
+  \label{eq:132}
+  V_{\alpha}(z)=e^{i\sqrt{2}\alpha \phi(z)},\quad \bar V_{\bar\alpha}(\bar z)=e^{i\sqrt{2}\bar\alpha
+    \bar \phi(\bar z)}
+\end{equation}
+
+Full vertex operator is a product of them
+\begin{equation}
+  \label{eq:133}
+  V_{\alpha,\bar\alpha}(z,\bar z)=V_{\alpha}(z)\bar V_{\bar \alpha}(\bar z)
+\end{equation}
+There is another possible decomposition with physical interpretation of electric and magnetic operators:
+\begin{equation}
+  \label{eq:134}
+  \alpha=e+m\quad \bar\alpha=e-m
+\end{equation}
+\begin{equation}
+  \label{eq:135}
+  V_{e,0}(z,\bar z)=e^{i\sqrt{2} e\varphi(z,\bar z)},\quad   V_{0,m}(z,\bar z)=e^{-\sqrt{2} m\tilde\varphi(z,\bar z)}
+\end{equation}
+
+Conformal weights of these operators are 
+\begin{equation}
+  \label{eq:136}
+  h(\alpha)=\alpha(\alpha-2\alpha_{0})=(e+m)(e+m-2\alpha_{0})
+\end{equation}
+\begin{equation}
+  \label{eq:137}
+  \bar h(\bar\alpha)=\bar\alpha(\bar\alpha-2\alpha_{0})=(e-m)(e-m-2\alpha_{0})
+\end{equation}
+
+Spinless operators with $h=\bar h$ are possible when $\alpha=\bar\alpha$ or
+$\bar\alpha=2\alpha_{0}-\alpha$. These two cases correspond to pure electric operators with $m=0$ or
+magnetic operators with arbitrary $m$ and electric charge $e=\alpha_{0}$.
+
+The following notation is used in \cite{gruzberg2006stochastic} for spinless vertex operators:
+\begin{equation}
+  \label{eq:138}
+  V^{(\alpha)}=V_{\alpha,2\alpha_{0}-\alpha}=V_{\alpha}\bar V_{2\alpha_{0}-\alpha}
+\end{equation}
+
+Charges and conformal weights of degenerate fields from Kac table are
+\begin{equation}
+  \label{eq:139}
+  \alpha_{r,s}=\frac{1}{2}(1-r)\alpha_{+}+\frac{1}{2}(1-s)\alpha_{-},\quad h_{r,s}=\frac{(r\kappa-4s)^{2}-(\kappa-4)^{2}}{16\kappa}
+\end{equation}
+So holomorphic and full primary fields are denoted by $\psi_{r,s}(z)\sim V_{\alpha_{r,s}}(z)$ and
+$\psi_{r,s}(z,\bar z)\sim V^{(\alpha_{r,s})}(z,\bar z)$
+
+Theory on a domain with boundary is different, because we need to take into account boundary condition
+\begin{equation}
+  \label{eq:140}
+  \partial_{l}\varphi|_{\partial \mathcal{D}}=0.
+\end{equation}
+But we can map the domain $\mathcal{D}$ to upper half-plane $\mathbb{H}$, then we can take into
+account boundary conditions by analytic continuation to the whole plane and duplication of fields:
+\begin{equation}
+  \label{eq:141}
+  \bar\phi(\bar z)\to -\phi(z^{*})
+\end{equation}
+\begin{eqnarray}
+  \label{eq:142}
+  V_{e,0}\to e^{i\sqrt{2}e\phi(z)} e^{-i\sqrt{2} e \phi(z^{*})}\\
+  V_{0,m}\to e^{i\sqrt{2}m\phi(z)} e^{-i\sqrt{2} m \phi(z^{*})}
+\end{eqnarray}
+
+On the boundary vertex operators fuse with their images:
+\begin{equation}
+  \label{eq:144}
+    V_{e,m}(z,\bar z)\to V^{(2m)}(x) e^{i 2\sqrt{2}m \phi(x)}
+\end{equation}
+
+Critical curves are level lines of field $\varphi$, so by imposing boundary condition $\varphi=0$
+on one half of the boundary and $\varphi=\pi n R$ on another half we get $n$ curves growing from the
+origin. We now argue that curves are produced by a magnetic operator $V_{0,m}$ with properly chosen
+$m$.
+
+\begin{equation}
+  \label{eq:145}
+  V_{e,0}(z,\bar z)V_{0,m}(z',\bar z')=\left(\frac{z-z'}{\bar z-\bar z'}\right)^{2em}
+  V_{e+m}(z')\bar V_{e-m}(\bar z')+\dots=e^{4i em \arg(z-z')} V_{e+m}(z')\bar V_{e-m}(\bar z')+\dots
+\end{equation}
+So when electric operator goes around magnetic operator we get a field jump of $4\sqrt{2}\pi m$.
+Magnetic operator is vortex operator. So
+\begin{equation}
+  \label{eq:146}
+  m=\frac{\sqrt{2}}{8}nR = \frac{n}{2\sqrt{\kappa}}=-\frac{n}{4} \alpha_{-}
+\end{equation}
+Since we want curve-creating operator to be spinless we have $e=\alpha_{0}$ and
+$\alpha=\alpha_{0}-\frac{n}{4}\alpha_{-}=\alpha_{0,\frac{n}{2}}$. So our curve-creating operator is
+$\psi_{0,n/2}(z,\bar z)$ with conformal weight
+\begin{equation}
+  \label{eq:147}
+  h_{0,n/2}=\frac{4n^{2}-(\kappa-4)^{2}}{16\kappa}
+\end{equation}
+
+Pinning operator creates one curve passing through the point in the bulk, so it is $\psi_{0,1}$. Its
+conformal weight is
+\begin{equation}
+  \label{eq:148}
+  h_{0,1}=\frac{8-\kappa}{16},
+\end{equation}
+and Hausdorff dimension is
+\begin{equation}
+  \label{eq:149}
+  d_{H}=2-2h_{0,1}
+\end{equation}
+
 To see it one can consider circle of small radius $\varepsilon$ centered at $z$. Put some conformal

### 2014-04-01 area-length/notes.tex
Harmonic measure and SLE Hausdorff dimension is written

@@
 \end{equation}
-So scaling of the moments of $\mu(r)$ are determined by scaling of $|w'(r)|$:
+This scaling follows from electrostatic interpretation of harmonic measure, since $\mu(r)$ is charge
+inside the circle and by Gauss theorem it is equal to the flux of electric field through the
+boundary. Typical absolute value of electric field on the circle is $|w'(r)|$ and boundary length is
+$2\pi r$.
+
+So scaling of the moments of $\mu(r)$ is determined by scaling of $|w'(r)|$:
 \begin{equation}
@@
 Following relations hold for multifractal spectrum and anomalous exponents:
-$\tilde\tau(h)=\tau(h)-\tau(0)$, $\Delta_{bulk}(h)=\delta(h)-\delta(0)$, $d_{H}=1+\Delta_{bulk}(1)$
+$\tilde\tau(h)=\tau(h)-\tau(0)$, $\Delta_{bulk}(h)=\delta(h)-\delta(0)$. The most important for us
+here is the connection of Hausdorff dimension and local anomalous exponent 
+\begin{equation}
+  \label{eq:150}
+  d_{H}=1+\Delta_{bulk}(1)
+\end{equation}
 
@@
 
+Correlation functions in Coulomb gas picture are easily calculated:
+\begin{equation}
+  \label{eq:157}
+  \left< V_{\alpha_{1}}(z_{1})\dots
+    V_{\alpha_{n}}(z_{n})\right>=\prod_{i<j}(z_{i}-z_{j})^{2\alpha_{i}\alpha_{j}}, \quad \mbox{if}\quad \sum_{i}\alpha_{i}=2\alpha_{0}
+\end{equation}
+
 Full vertex operator is a product of them
@@
 \end{equation}
-and Hausdorff dimension is
+We want to show that Hausdorff dimension is
 \begin{equation}
@@
 
-To see it one can consider circle of small radius $\varepsilon$ centered at $z$. Put some conformal
-boundary condition on one half of the circle and another condition on the rest of the circle. Then
-critical curve would join the points of change in boundary conditions. The expectation values of
-observables in this geometry are given by CFT correlation functions with two boundary condition
-changing operators inserted:
-\begin{equation}
-  \label{eq:119}
-  \left< \Psi_{12}(z')\Psi_{12}(z'')\right>
-\end{equation}
-where $|z'-z|\leq \varepsilon$ and $|z''-z|\leq \varepsilon$. The boundary condition changing
-operators in Coulomb gas picture can be presented as the vertex operators
-$V_{\alpha_{12}}=e^{i\sqrt{2}\alpha_{12}\varphi(z)}$. When $\varepsilon\to 0$ we can fuse this two
-operators to single operator $V_{2\alpha_{12}}$. Note that $\alpha_{12}=-\frac{1}{2}\alpha_{-}$
-\eqref{eq:55}, so $V_{2\alpha_{12}}\sim V_{-\alpha_{-}}\sim V_{\alpha_{+}}$ (?)
-
-The moments of harmonic measure are connected with the CFT correlation functions by
-\begin{equation}
-  \label{eq:118}
-  \left<O_{h}(r) \Psi_{10}(0)\Psi(\infty)\right>\sim r^{h'-2h}\prec |w'(r)|^{h}\succ
-\end{equation}
+To do so we need to connect local anomalous scaling exponents with conformal weights of vertex
+operators. Local moments of harmonic measure $\mu(z,r)^{h}$ are connected with conformal maps.
+Consider conformal map $w$ of the exterior of critical curve $\gamma$ to upper half-plane or unit
+circle. Normalize this map such that $w(z)=z$ and $w(z'\to\infty)=z'+o(z')$. As we have seen the
+scaling of $w$ near $z$ is related to harmonic measure.
+
+The partition function $Z(0,L)$ of configurations that contain a closed curve passing through the
+points $0$ and $L$ is given by the correlator of two pinning operators $\psi_{0,1}$:
+\begin{equation}
+  \label{eq:151}
+  \frac{Z(0,L)}{Z}=\left<\psi_{0,1}(0)\psi_{0,1}(L)\right>,
+\end{equation}
+where $Z$ is partition function of all configurations.
+
+The partition function $Z(0,L)$ can be calculated as the product of partition functions inside and
+outside of the curve averaged over all possible curves:
+\begin{equation}
+  \label{eq:152}
+  Z(0,L)=\prec Z_{\gamma}^{\mathrm{int}} Z_{\gamma}^{\mathrm{ext}}\succ
+\end{equation}
+To get the moments of harmonic measure we need to insert some operator $\mathcal{O}(r)$ (product of
+operators), for charge neutrality we need to add another one at infinity $\mathcal{O}(\infty)$.
+Since we are interested in small $r<<L$ we can fuse $\mathcal{O}(\infty)$ with $\psi_{0,1}(L)$ into
+$\Psi(\infty)$. So we need to compute correlation function $\left<\psi_{0,1}(0) \mathcal{O}(r)
+  \Psi(\infty)\right>$. It can be done in two ways, directly and averaging
+$\left<\mathcal{O}(r)\mathcal{O}(\infty)\right>_{\gamma}$ over all curves:
+\begin{equation}
+  \label{eq:153}
+  \left<\psi_{0,1}(0) \mathcal{O}(r)\Psi(\infty)\right>= \prec
+  \left<\mathcal{O}(r)\mathcal{O}(\infty)\right>_{\gamma}^{\mathrm{ext}} Z_{\gamma}^{\mathrm{ext}} Z_{\gamma}^{\mathrm{int}}\succ
+\end{equation}
+The correlation function of operators $\mathcal{O}$ is statistically independent from other factors
+and has all the dependence on $r$. Apply to this correlation function conformal map $w$:
+\begin{equation}
+  \label{eq:154}
+  \left<\mathcal{O}(r)\mathcal{O}(\infty)\right>_{\gamma}^{\mathrm{ext}}=|w'(r)|^{h}\left<\mathcal{O}(w(r))\mathcal{O}(\infty)\right>,
+\end{equation}
+where $h$ is conformal weight of $\mathcal{O}$. So
+\begin{equation}
+  \label{eq:155}
+  \prec|w'(r)|^{h}\succ\sim\frac{ \left<\psi_{0,1}(0) \mathcal{O}(r)\Psi(\infty)\right>}{\left<\mathcal{O}(w(r))\mathcal{O}(\infty)\right>}
+\end{equation}
+
+To get Hausdorff dimension $d_{H}=1+\Delta(1)$ \eqref{eq:150} we need to insert operator
+$V_{\alpha(1)/2,\alpha(1)/2}$, since we consider system with boundary. Then it fuses with its image
+and produce vertex operator with conformal weight $h=1$. 
+\begin{equation}
+  \label{eq:156}
+  \prec|w'(r)|^{2h(\alpha(1)/2)}\succ\sim\frac{\left< V_{\alpha(1)/2}(z) V_{\alpha(1)/2}(z^{*}) \psi_{0,1}(0) \Psi(\infty)\right>}{\left<V_{\alpha(1)/2}(w(z)) V_{\alpha(1)/2}(w^{*}(z))\right>}
+\end{equation}
+
+Use the formula \eqref{eq:157} to calculate correlation functions on the right-hand side. The
+numerator gives us $r^{2\alpha_{0,1}\alpha(1)}$ for $z,z^{*}\to r,\; z-z^{*}\to 0$, the denominator
+$(w(z)-w^{*}(z))^{\alpha(1)^{2}/2}\sim (|z| |w'(z)|)^{\alpha(1)^{2}/2}$. So total power of $|w'(r)|$
+is 
+$2h(\alpha(1)/2)+\alpha(1)^{2}/2=\alpha(1)
+(\alpha(1)/2-2\alpha_{0})+\alpha(1)^{2}/2=\alpha(1)(\alpha(1)-2\alpha_{0})=1$, and total power of
+$r$ is $2\alpha_{0,1}\alpha(1)-\alpha(1)^{2}/2$
+\begin{equation}
+  \label{eq:158}
+  \prec |w'(r)|\succ \sim r^{\Delta(1)}=r^{2\alpha_{0,1}\alpha(1)-\alpha(1)^{2}/2}
+\end{equation}
+
+If we substitute $h_{0,1}=\frac{1}{2}-\frac{\kappa}{16}$ and
+$2\alpha_{0}=\frac{\sqrt{\kappa}}{2}-\frac{2}{\sqrt{\kappa}}$ we obtain $\Delta(1)=\frac{\kappa}{8}$.
+
+%%  To see it one can consider circle of small radius $\varepsilon$ centered at $z$. Put some conformal
+%%  boundary condition on one half of the circle and another condition on the rest of the circle. Then
+%%  critical curve would join the points of change in boundary conditions. The expectation values of
+%%  observables in this geometry are given by CFT correlation functions with two boundary condition
+%%  changing operators inserted:
+%%  \begin{equation}
+%%    \label{eq:119}
+%%    \left< \Psi_{12}(z')\Psi_{12}(z'')\right>
+%%  \end{equation}
+%%  where $|z'-z|\leq \varepsilon$ and $|z''-z|\leq \varepsilon$. The boundary condition changing
+%%  operators in Coulomb gas picture can be presented as the vertex operators
+%%  $V_{\alpha_{12}}=e^{i\sqrt{2}\alpha_{12}\varphi(z)}$. When $\varepsilon\to 0$ we can fuse this two
+%%  operators to single operator $V_{2\alpha_{12}}$. Note that $\alpha_{12}=-\frac{1}{2}\alpha_{-}$
+%%  \eqref{eq:55}, so $V_{2\alpha_{12}}\sim V_{-\alpha_{-}}\sim V_{\alpha_{+}}$ (?)
+%%  
+%%  
+%%  The moments of harmonic measure are connected with the CFT correlation functions by
+%%  \begin{equation}
+%%    \label{eq:118}
+%%    \left<O_{h}(r) \Psi_{10}(0)\Psi(\infty)\right>\sim r^{h'-2h}\prec |w'(r)|^{h}\succ
+%%  \end{equation}
+%%  
+%%  
+%%  
+%%  
+%%
 

### 2014-04-02 area-length/notes.tex
KPZ scaling written

@@
 
+\subsection{CFT and local SLE geometry}
+\label{sec:cft-local-sle}
+
 Local observables w.r.t. SLE can be described by correlation functions of boundary conformal field
@@
 
-Liouville theory of two-dimensional gravity is a natural choice, but to see it we need to discuss
-some geometry first.
+Liouville theory of two-dimensional gravity is a natural choice, but first we need to discuss
+how CFT is used to study local geometry of SLE curves.
 
@@
 
-Let $N^r(L)$ be number of rooted loops with a given length. By $N^r(L,A)$ we denote the number of
-loops of given length and area. $N^r(L)=\int_0^{\infty} N^r(L,A) dA$. Area weighted number of loops
-is denoted by $G^r(L,\mu)$. (Here $\mu$ is bulk coupling constant ).
-\begin{equation}
-  \label{eq:2}
-  G^r(L,\mu)=\int e^{\mu A} N^r(L,A) dA
-\end{equation}
-
-\begin{equation}
-  \label{eq:1}
-  G^r (\mu,x) = \sum_{\mathrm{clusters}} N^r (L,A) x^L e^{-\mu A}
-\end{equation}
-
-At $x\to x_c$
-\begin{equation}
-  \label{eq:6}
-  G^r(\mu,x)= \mu^{\theta} F\left(\frac{x-x_c}{\mu^{\phi}}\right)
-\end{equation}
+%%  Let $N^r(L)$ be number of rooted loops with a given length. By $N^r(L,A)$ we denote the number of
+%%  loops of given length and area. $N^r(L)=\int_0^{\infty} N^r(L,A) dA$. Area weighted number of loops
+%%  is denoted by $G^r(L,\mu)$. (Here $\mu$ is bulk coupling constant ).
+%%  \begin{equation}
+%%    \label{eq:2}
+%%    G^r(L,\mu)=\int e^{\mu A} N^r(L,A) dA
+%%  \end{equation}
+%%  
+%%  \begin{equation}
+%%    \label{eq:1}
+%%    G^r (\mu,x) = \sum_{\mathrm{clusters}} N^r (L,A) x^L e^{-\mu A}
+%%  \end{equation}
+%%  
+%%  At $x\to x_c$
+%%  \begin{equation}
+%%    \label{eq:6}
+%%    G^r(\mu,x)= \mu^{\theta} F\left(\frac{x-x_c}{\mu^{\phi}}\right)
+%%  \end{equation}
+%%
 
@@
 %%
+
+\subsection{Quantum gravity and global geometry of critical curves}
+\label{sec:quant-grav-glob}
+
+Theory of quantum gravity in two dimensions, implemented as a matter CFT coupled to Liouville field
+describes the behavior of statistical models in fluctuating geometry. 
+While usually configurations of  Liouville field are interpreted as random curved Riemann surfaces,
+we need to consider random flat shapes. So functional integral in our case is over different space
+of functions. The matter is implemented as a minimal model in Coulomb gas picture with matter field $\varphi$.
+
 KPZ-scaling. ``Wrong branch'' for $\mu_{B}$?
@@
 \end{equation}
-and primary fields are given by vertex operators $V_{\alpha}=e^{\alpha\varphi}$. But primary fields
+and primary fields are given by vertex operators $V_{\alpha}=e^{2\alpha\varphi}$. But primary fields
 $V_{\alpha}$ and $V_{Q-\alpha}$ are to be identified. 
@@
 Liouville correlation functions w.r.t. to change in coupling constants $\mu, \mu_{B}$. This relation
-is easy to obtain. Consider reparametrisation $\varphi\to\varphi-\frac{1}{2b}\ln\mu$. The action
+is easy to obtain. Consider reparametrisation $\varphi=\tilde\varphi-\frac{1}{2b}\ln\mu$. The action
 $S[\mu,\mu_{B}]$ is then
@@
 vertex operators:
-\begin{equation}
+\begin{multline}
   \label{eq:100}
-  \langle V_{\alpha_{1}}(z_{1})\dots V_{\alpha_{n}}(z_{n}) B_{\beta_{1}}(x_{1})\dots B_{\beta_{m}}(x_{m})\rangle=
-\end{equation}
+  \langle V_{\alpha_{1}}(z_{1})\dots V_{\alpha_{n}}(z_{n}) B_{\beta_{1}}(x_{1})\dots
+  B_{\beta_{m}}(x_{m})\rangle=\\
+  \int \mathcal{D}\tilde\varphi e^{2\alpha_{1}\tilde\varphi(z_{1}}\dots
+  e^{2\alpha_{n}\tilde\varphi(z_{n})} \mu^{-\frac{1}{b} \sum_{i}\alpha_{i}} 
+  e^{\beta_{1}\tilde\varphi(x_{1}}\dots
+  e^{\beta_{m}\tilde\varphi(x_{m})} \mu^{-\frac{1}{2b} \sum_{i}\beta_{i}} e^{-S[\tilde\varphi]}
+  \mu^{\frac{Q\chi}{2b}}\\
+  \sim \mu^{\frac{Q\chi-2\sum_{i}\alpha_{i}-\sum_{j}\beta_{j}}{2b}}
+\end{multline}
 

### 2014-04-03 area-length/notes.tex
Quantum gravity action and gravitational dressing for matter fields

@@
 we need to consider random flat shapes. So functional integral in our case is over different space
-of functions. The matter is implemented as a minimal model in Coulomb gas picture with matter field $\varphi$.
-
-KPZ-scaling. ``Wrong branch'' for $\mu_{B}$?
+of functions. The matter is implemented as a minimal model in Coulomb gas picture with matter field
+$\chi$.
+
+Full action of two-dimensional quantum gravity on world-sheet manifold $\mathcal{M}$ with boundary
+$\partial \mathcal{M}$ in background metric $\hat g$ is given by the formula \cite{kostov2004boundary}:
+\begin{multline}
+  \label{eq:160}
+  S[\chi,\varphi]=\int_{\mathcal{M}}\left(\frac{1}{4\pi}[(\nabla \varphi)^{2}+(\nabla
+    \chi)^{2}+(Q\varphi-ie_{0}\chi)\hat R]+\mu e^{2b\varphi}\right)d^{2}z +\\
+  +  \int_{\partial
+    \mathcal{M}}\left(\frac{1}{2\pi}(Q\varphi-ie_{0}\chi)\hat K + \mu_{B}e^{b\varphi}\right)dx+\mbox{ghosts}
+\end{multline}
+where $\hat R$ is curvature of background metric in the bulk, $\hat K$ -- curvature of background
+metric on the boundary, 
+\begin{equation}
+  \label{eq:161}
+  Q=\frac{1}{b}+b,\quad e_{0}=\frac{1}{b}-b
+\end{equation}
+and ghosts central charge is $-26$, so total central charge vanishes:
+\begin{equation}
+  \label{eq:162}
+  c_{tot}=c_{\varphi}+c_{\chi}+c_{\mathrm{ghosts}}=(1+6Q^{2})+(1-6e_{0}^{2})-26=0
+\end{equation}
+We can use conformal map to rewrite the action on the upper half-plane $\mathbb{H}$:
+\begin{equation}
+  \label{eq:159}
+  S[\varphi,\chi]=\int_{\mathbb{H}} d^{2}z \left(\frac{1}{4\pi}[(\nabla \varphi)^{2}+(\nabla
+    \chi)^{2}]+\mu e^{2b\varphi}\right) +\int_{-\infty}^{\infty} dx \mu_{B}e^{b\varphi} + \mbox{ghosts}
+\end{equation}
+where charges are now hidden in fields asymptotic at the infinity:
+\begin{equation}
+  \label{eq:163}
+  \varphi\sim Q\log|z|^{2},\quad \chi\sim-e_{0}\log|z|^{2}
+\end{equation}
+
+The partition function is defined as a functional integral over matter and Liouville field:
+\begin{equation}
+  \label{eq:164}
+  Z(\mu,\mu_{B})=\int \mathcal{D}\chi \mathcal{D}\varphi e^{-S[\chi,\varphi]}
+\end{equation}
+To define the measure one needs to fix the boundary conditions. Kostov et. al choose non-homogeneous
+Neumann boundary condition for the Liouville field:
+\begin{equation}
+  \label{eq:165}
+  i(\partial -\bar\partial)\varphi=4\pi\mu_{B}e^{b\varphi}
+\end{equation}
+
+There is a duality $b\to \frac{1}{b}$ in this theory. In particular, it is possible to choose
+boundary term as $e^{\frac{\varphi}{b}}$. This choice may be relevant to us since it corresponds to
+dual boundary cosmological constant $\tilde\mu_{B}$ which has scaling $\tilde\mu_{B}\sim
+\mu^{\frac{1}{2b^{2}}}$ and is related to fractal boundary.
+
+We want to consider configurations with fractal boundaries but flat bulk. So the difference is in
+space of functions $\varphi$ we are integrating over in \eqref{eq:164}.
+
+Note that self-avoiding walks is the model with $\kappa=\frac{8}{3}$, $c=0$,
+$e_{0}=\frac{1}{\sqrt{6}}$, $b=\sqrt{\frac{3}{2}}$ or $b=\sqrt{\frac{2}{3}}$. Since in paper
+\cite{kostov2004boundary} $b$ is assumed to be less than $1$, we will use
+\begin{equation}
+  \label{eq:166}
+  b=\sqrt{\frac{2}{3}}, \quad 0<b<1
+\end{equation}
+Matter theory is just a free boson, so primary fields are vertex electric and magnetic operators
+\eqref{eq:135} (with the change of notations $\alpha\to \sqrt{2} e$, $2\alpha_{0}\to  e_{0}$). In
+quantum gravity vertex operators are dressed by Liouville field
+\begin{equation}
+  \label{eq:167}
+  V_{e,\alpha}(z,\bar z)=e^{2ie\chi(z,\bar z)} e^{2\alpha\varphi(z,\bar z)}
+\end{equation}
+in such a way that conformal dimension $\Delta=1$:
+\begin{equation}
+  \label{eq:168}
+  e(e-e_{0})+\alpha(Q-\alpha)=1
+\end{equation}
+Similarly for magnetic (vortex) operators we have
+\begin{equation}
+  \label{eq:169}
+  \chi(z,\bar z)=\chi(z)+\bar\chi(\bar z),\quad \tilde\chi(z,\bar z)=\chi(z)-\bar\chi(\bar z)
+\end{equation}
+\begin{equation}
+  \label{eq:170}
+  V_{m,\alpha}(z,\bar z)=e^{2im\tilde\chi(z,\bar z)} e^{2\alpha\varphi(z,\bar z)}
+\end{equation}
+Since left and right conformal dimensions
+\begin{equation}
+  \label{eq:171}
+  \Delta_{m}=m(m-e_{0}), \quad \bar\Delta_{m}=m(m+e_{0})
+\end{equation}
+are not equal the field is not spinless. So we need to consider mixed operator $\mathcal{O}_{e,m}$
+with dimensions \eqref{eq:134}
+\begin{equation}
+  \label{eq:172}
+  \Delta_{e,m}=(e+m)(e+m-e_{0}), \quad \bar \Delta_{e,m}=(e-m)(e-m-e_{0})
+\end{equation}
+The spin $\Delta-\bar\Delta$ vanishes if $e=\frac{e_{0}}{2}$.
+\begin{equation}
+  \label{eq:173}
+  \Delta_{\frac{e_{0}}{2},m}=m^{2}-\frac{e_{0}^{2}}{4}
+\end{equation}
+
+Primary fields from Kac table with dimensions
+\begin{equation}
+  \label{eq:174}
+  \Delta_{rs}=\frac{1}{4}\left[\left(\frac{r}{b}-sb\right)^{2}-e_{0}^{2}\right]
+\end{equation}
+can be constructed as electric operators with charges
+\begin{equation}
+  \label{eq:175}
+  e_{rs}=\frac{1}{2}\left(e_{0}-\frac{r}{b}+sb\right)
+\end{equation}
+or as magnetic operators with electric charge $\frac{e_{0}}{2}$ and magnetic charge
+\begin{equation}
+  \label{eq:176}
+  m_{rs}=\frac{1}{2}\left(-\frac{r}{b}+sb\right)
+\end{equation}
 

### 2014-04-04 area-length/notes.tex
Gravitational dressings+one point function

@@
 \end{equation}
+Proper dressing corresponds to the choice of smaller value of $\alpha$ such that \eqref{eq:168}
+holds.
+
 Similarly for magnetic (vortex) operators we have
@@
 \end{equation}
+
+Pinning operator corresponds to $r=0, s=1$, so $m=\frac{b}{2}$ and
+$\Delta=\frac{b^{2}}{4}-\frac{e_{0}^{2}}{4}=\frac{1}{2}-\frac{b^{2}}{4}$.
+
+Dressing dimension $\alpha$ is $\frac{b}{2}$ or $\frac{1}{b}+\frac{b}{2}$, dimension of Liouville
+vertex operator is $\Delta_{01}^{L}=\alpha(Q-\alpha)=\frac{1}{2}+\frac{b^{2}}{4}=\frac{1}{2}d_{H}$.
+
+Matter field $\chi$ should satisfy some boundary condition. In Coulomb gas approach there are two
+possible choices -- Dirichlet 
+\begin{equation}
+  \label{eq:177}
+  (\partial+\bar \partial)\chi=0
+\end{equation}
+and Neumann
+\begin{equation}
+  \label{eq:178}
+  (\partial-\bar \partial)\chi=0  
+\end{equation}
+If we want to interpret critical curves as the level lines of matter field $\chi$ we need to impose
+Dirichlet conditions \eqref{eq:140}. Dirichlet condition means that field on the boundary has
+constant value $\chi_{B}$.
+
+Boundary matter fields are boundary condition changing operators between different boundary
+conditions. Neumann-Neumann operators are boundary vertex operators $B_{e}=e^{ie\chi(x)}$, with
+scaling dimension $\Delta^{B}_{e}=e(e-e_{0})$. Dirichlet-Dirichlet fields are boundary magnetic
+operators $\tilde B_{m}$ which introduce jump $\delta\chi=2\pi m$ of the boundary value of
+the field from $\chi_{B}$ to $\chi_{B}+\delta\chi_{B}=\chi_{B}+2\pi m n$. The dimension is
+$\Delta^{B}_{m}=m(m-e_{0})$. Unlike the bulk magnetic operator boundary operator does not have
+electric charge. Electric and magnetic charges for degenerate boundary operators are
+\begin{equation}
+  \label{eq:143}
+  e_{rs}=\frac{1}{2}\left( e_{0}-\frac{r}{b}+sb\right),\quad m_{rs}=\frac{1}{2}\left(e_{0}-\frac{r}{b}+sb\right)
+\end{equation}
+Dirichlet-Neumann and Neumann-Dirichlet operators are boundary twist operators.
+
+Wrong dressing of the identity boundary operator is $e^{\frac{\varphi}{b}}$. In this case
+$\mu_{B}\sim \mu^{\frac{1}{2b^{2}}}$ and boundary is fractal. 
+Two dressings are dual to each other, so if fractal boundary $\mu_{B}\sim \mu^{\frac{1}{2b^{2}}}$ corresponds to
+Dirichlet boundary condition, then simple boundary $\mu_{B}\sim \mu^{\frac{1}{2}}$ corresponds to
+Neumann boundary condition.
+
+For degenerate operator $0,1$ we have $m_{01}=\frac{1}{2}\left(e_{0}+b\right)=\frac{1}{2b}$,
+$\Delta^{B}_{m}=\frac{1}{2b}\left(\frac{1}{2b}-\frac{1}{b}+b\right)=\frac{1}{2}-\frac{1}{4b^{2}}$
+with dressing field $B_{\beta}=e^{\beta\varphi}$ with $\beta=\frac{1}{2b}$.
+
+The observables in two-dimensional quantum gravity are products of CFT correlation functions and
+correlation functions of dressed matter vertex operators. Coordinate-independent parts of these
+correlation functions are identified with restricted partition functions in microscopic models
+\cite{kostov2004boundary,kostov2003boundary}. Microscopic models for quantum gravity are integrable
+lattice models, such as Ising, Potts, $O(n)$ or SOS, considered on random lattices.
+
+Bulk one-point function
+\begin{equation}
+  \label{eq:179}
+  \left< V_{\alpha}(z,\bar z)\right>_{\sigma}=\frac{U_{\sigma}(\alpha)}{|z-\bar z|^{2\Delta_{\alpha}}}
+\end{equation}
+is given by the formula
+\begin{equation}
+  \label{eq:180}
+  U_{\sigma}(\alpha)=\frac{2}{b}\left(\pi\mu\gamma(b^{2})\right)^{\frac{Q-2\alpha}{2b}}
+  \Gamma(2b\alpha-b^{2})\Gamma\left(\frac{2\alpha}{b}-\frac{1}{b^{2}}-1\right) \cos[\pi(2\alpha-Q)(2\sigma-Q)]
+\end{equation}
+Microscopically this function is interpreted as the partition function of the loop gas on a
+punctured disk with a vertex operator $V_{\alpha}$ inserted at the puncture and Dirichlet boundary
+condition with the height $\sim \sigma$.
+
+Supposedly we need to change theory by measuring length not with $e^{b\varphi}$ or
+$e^{\frac{\varphi}{b}}$ but by insertion of gravitational dressing for pinning operator
+$B_{m_{01}}$, which is $e^{\frac{\varphi}{2b}}$.
 

### 2014-04-17 CFT/area-length/letter.tex

\documentclass[12pt]{article}
\usepackage[russian]{babel}
\usepackage[utf8x]{inputenc}
\begin{document}
Здравствуйте!
У меня тут есть одна идея, но я ее еще не совсем додумал. В общих чертах
она такая. Пусть мы ищем производящую функцию для многоугольников
заданной длины на квадратной решетке. Для начала возьмем решетку
конечного размера $L\times L$ с тороидальными граничными условиями. Тогда мы
хотим найти 
$$G(x)=\sum_l p_l x^l$$,
здесь $p_l$ - число различных многоугольников длины $l$. Различные - это
те, которые нельзя совместить трансляцией. (Вроде бы у Гутмана и Ричарда
именно так). 
Если на той же решетке рассмотреть конфигурации $O(n)$-модели, то
статсумма будет
$$Z_{O(n)}(x,n)=\sum_{\mathrm{conf}} x^l n^{\#\mathrm{loops}}$$
В пределе $n\to 0$ вклад дают только конфигурации из одной петли. Число
таких конфигураций длины $l$ - это $p_l$ умножить на число трансляций
$L^2$, если игнорировать конфигурации с петлями, намотанными на тор
(нелокальные).

То есть 
$$G(x)=\lim_{n\to 0} \frac{1}{L^2} Z_{O(n)}(x,n)$$. 
Производящая функция для петель с корнем дается производной по $x$, так
как корень у петли длины $l$ можно выбрать $l$ способами:
$$G^{(r)}(x)=\partial_x G(x) = \lim_{n\to 0} \frac{1}{L^2} \partial_x
Z_{O(n)} (x,n)$$.

Теперь перейдем к производящим функциям для петель с длиной и площадью:
$$G(x,\mu)=\sum_{l,A} p_{l,A} x^l e^{-\mu A}$$
$$G^{(r)}(x,\mu)=\partial_x G(x,\mu)$$
В $O(n)$-модели можно рассмотреть аналогичную наблюдаемую 
$$\langle e^{-\mu A} \rangle_{O(n)} = \frac{1}{Z_{O(n)} (x,n)}
\sum_{\mathrm{conf}} e^{-\mu A} x^l  n^{\#\mathrm{loops}}$$
Тогда интересующая нас производящая функция дается выражением
$$G(x,\mu)=\lim_{n\to 0} \frac{1}{L^2} Z_{O(n)}(x,n) \langle<e^{-\mu
A}\rangle_{O(n)}$$
Видимо в пределе $L\to \infty$ в окрестности критической точки $x_c$
надо как-то перенормировать бесконечный множитель
$\frac{Z_{O(n)}(x,n)}{L^2}$. 
Для производящей функции петель с корнем получается 
$$\partial_x \left( Z_{O(n)}(x,n) \langle<e^{-\mu
A}\rangle_{O(n)}\right) = \sum_{\mathrm{conf}} l x^l e^{-\mu A}
n^{\#\mathrm{loops}} = $$
$$Z_{O(n)}(x,n) \frac{1}{Z_{O(n)}(x,n)}
\sum_{\mathrm{conf}} l x^l e^{-\mu A} n^{\#\mathrm{loops}} =
Z_{O(n)}(x,n) \langle<e^{-\mu A}\rangle_{O(n)},$$
то есть 
$$G^{(r)}(x,\mu)=\lim_{n\to 0} \frac{1}{L^2} Z_{O(n)}(x,n) \langle<l
e^{-\mu A}\rangle_{O(n)}$$
Таким образом нам надо вычислять $\langle l e^{-\mu A}\rangle_{O(n)}$ в
окрестности критической точки.

В критической точке $O(n)$ модель описывается конформной теорией поля.
Для этой конформной теории поля можно использовать представление
кулоновского газа, чтобы записать действие. 
$$S^{*} [\varphi] = \in d^2 x (\partial \varphi)^2 + QR \varphi$$
Предел $n\to 0$ должен как-то получаться переходом к пределу по фоновому
заряду. Тут я пока не очень понимаю, что может происходить.
Нас интересует окрестность критической точки. Там теорию можно
представить как деформацию некоторым примарным полем $\Phi$:
$$S=S^{*} + \lambda \int d^2 x \Phi(x)$$
Но примарные поля в представлении кулоновского газа даются вершинными
операторами $e^{\alpha \varphi}$. То есть действие деформированной
теории принимает вид 
$$S=[\varphi] = \in d^2 x (\partial \varphi)^2 + QR \varphi+\lambda
e^{\alpha \varphi}$$,
практически действие теории Лиувилля (с точностью до связи $\lambda,
\alpha$ с зарядом $Q$). Но я пока не понимаю, какое именно примарное
поле соответствует деформации по $x$. Вроде бы если вес деформирующего
поля единица, то есть деформация маргинальная, то деформированная теория
хорошо перенормируется. Это соответствует $\alpha=2b$ при
$b=\sqrt{\frac{3}{2}}$, а при $\alpha=b$ выходит вес $-1$. Я не очень
хорошо знаю про деформации конформной теории поля и про то, какие
примарные поля соответствуют отходу от критической точки по каким
параметрам. Буду признателен за ссылку, у меня под рукой есть только
книжка Mussardo и оригинальная работа Замолодчикова про модель Изинга.

Наблюдаемые в деформированной теории записываются так:
$$\langle X \rangle_{\lambda} = \frac{\langle X \exp{\lambda \int d^2 x
e^{\alpha \varphi}}\rangle_0}{Z_{\lambda}}$$,
где 
$$Z_{\lambda}=\langle \exp{\lambda \int d^2 x e^{\alpha
\varphi}}\rangle_0$$
То есть в нашем случае получается что-то вроде 
$$\langle e^{-\mu A}\rangle_{\lambda} = \frac{\int D\varphi
e^{S^{*}[\varphi]} e^{-\mu A} e^{\lambda \int d^2 x e^{\alpha
\varphi}}}{\int D\varphi e^{S^{*}[\varphi]} e^{\lambda \int d^2 x
e^{\alpha \varphi}}}$$.
Не очень понятно, будет ли даваться площадь той же формулой $A=\int d^2
x e^{2b\varphi}$, что и в теории Лиувилля, но если так, то получается,
что интересующая нас величина дается отношением корреляторов некоторых
вершинных операторов. 
Аналогично для $$\langle l e^{-\mu A}\rangle_{\lambda}$$. 
То есть вроде бы понятно, откуда может получаться отношение функций Бесселя.

Остаются вопросы: какая именно деформация?
Правда ли, что получается теория Лиувилля?

\newpage
Aнтон, привет,

Я путешествую с севера на юг. Сейчас посередине в городе Hue, не знаю как написать по-русски. Завтра
буду в городе Hoi, тоже не знаю как написать.

Вот несколько комментариев по поводу Вашего письма.

1) Рассмотрим $О(n)$ модель. Она описывает CFT c $c<1$, где центральный заряд функция n. Случай $n=0$
соответствует SAW $c=0, \kappa=16/6$.
В этом и только в этом случае можно получить информацию об одной петле из ансамбля многих петель из
предела $n\to 0$.

Eсли же $c\neq 0$, этот трюк не помогает (по крайней мере, я не знаю как его обобщить, и думаю что
никак).
\\
2) FZZ предлагает другой способ. Рассматривать сразу только одну петлю (поверхность в их случае). Их
статсумма считает только одну поверхность, однако,
это, не вложенная (embedded) в 3-мерное или какое другое пространство). Нам нужна вложенная
поверхность в 2-мерное пространство. Разница, я думаю, только в переучете
эквивалентных поверхностей получающихся отображением полу-плоскости в себя.
\\
В этом способе мне не понятно как получается функция Бесселя в знаменателе. 
\\
3 ) Подход FZZ апеллирует к флуцтуируещей метрике $\sqrt g= e^{2b\phi}$. Напротив, $О(n)$ модель и CFT
описывается флуктуируещим Гауссовым полем $\varphi$. 
Разница между ними довольно тонкая. Мы можем обсудить её подробнее в январе. Пока что отмечу одну
важную деталь.
\\
Оба поля Гауссовы. Рассмотрим CFT и Лиувилль в на кривой поверхности (background metric). 
\\
CFT: $Action= \int 1/2 g^{mu\nu}\partial_\mu \varphi\partial_\nu\phi) dV+ i\alpha_0 \int R\varphi
dV$\\

Liouville: $Action= \int 1/2 g^{mu\nu}\partial_\mu \phi\partial_\nu\phi) dV+ \alpha_0 \int R\varphi
dV$\\

where $dV=\sqrt g d^2z$-- элемент объема.\\

Отметьте отсутствие $i$ во второй формуле. В CFT, второй член - фаза, в Лиувилле он действительный. 
Это не случайно. Поля имеют разный физ смысл.\\

Наверняка, Вы это хорошо понимаете.\\

Всего доброго,
П.

\end{document}

### 2014-04-17 CFT/area-length/paper.tex

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\nfp}{\mathfrak{n}^{+}}
\newcommand{\nfm}{\mathfrak{n}^{-}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\uf}{\mathfrak{u}}
\newcommand{\sfr}{\mathfrak{s}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}

\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\sfh}{\hat{\mathfrak{s}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\begin{document}
\title{Generating function for self-avoiding polygons and Liouville quantum gravity}
\author{Anton Nazarov, Pavel Weigmann}%% $^{1,2}$}

\maketitle

\begin{abstract}
  We show that scaling behaviour of generating function for self-avoiding polygons on conical
  surface is described by correlation function of Liouville quantum gravity
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Self-avoiding polygons are popular objects for numerical simulations. Use of advanced algorithms
allows to obtain very precise numeric results.

Guttman and coauthors \cite{richard2001scaling} were able to get numeric answer to the following
question: ``what is the distribution with respect to length and area of self-avoiding polygons?''
Moreover, they were able to fit numeric results with Airy function. There were several attempts to
explain this peculiar development theoretically (see
\cite{cardy2003crossover,cardy2003exact,cardy2001exact}), but they are not satisfactory from our
point of view.

In present paper we generalize the construction of self-avoiding polygons to arbitrary conformal
measure on closed curves. Then we show that distribution in area and length is given by certain
correlation function in two-dimensional Liouville theory of gravity. The paper is organized as
follows. In this section we describe the results of Guttman \cite{richard2001scaling}. Next we
introduce general conformal measure on closed discrete curves (sec. \ref{sec:meas-curv-renorm}).
Then we argue that scaling limit is described by Liouville field theory (sec.
\ref{sec:liouv-field-theory}) and conclude the paper with possible approach to strict proof of
present results (sec. \ref{sec:conclusion}).

Self-avoiding polygons in paper \cite{richard2001scaling} were generated using pivot algorithm.
Maximal length on square lattice was 66. Generating function for polygons of given length and area
is introduced as
\begin{equation}
  \label{eq:75}
  G(x,q)=\sum_{m,n} p_{m,n} x^{m} q^{n},
\end{equation}
where $p_{m,n}$ is the number of polygons with perimeter $m$, enclosing an area $n$ passing through
a given edge (or node).

Cardy \cite{cardy2001exact} use the following definition for generating function of rooted loops,
with $g=-\ln q$:
\begin{equation}
  \label{eq:76}
  G^{(r)}(x,g)=\sum_{l,A} p_{l,A}^{(r)} x^{l} e^{-gA}
\end{equation}
Generating function for rooted polygons $G^{(r)}(x,g)$ is related to $G(x,g)$ by
\begin{equation}
  \label{eq:81}
  G^{(r)}(x,g)=x \frac{d}{dx} G(x,g),
\end{equation}
because root can be chosen in $l$ ways.

This model has critical point $(x_{c},0)$ and generating functions displays scaling behavior
\begin{equation}
  \label{eq:77}
  G(x,g)\sim G(x,g)_{\mathrm{reg}}+g^{\theta} F\left((x_{c}-x)g^{-\phi}\right)
\end{equation}
Critical indices $\theta,\phi$ are related to conventional exponents $\nu,\alpha$:
\begin{eqnarray}
  \label{eq:78}
  \phi=\frac{1}{2}\nu\\
  \theta=\frac{1}{2}(1-\alpha) \nu
\end{eqnarray}
Hyperscaling hypothesis adds another relation
\begin{equation}
  \label{eq:79}
  \alpha=2-2\nu
\end{equation}
Numerical results predict
\begin{eqnarray}
  \label{eq:80}
  \nu=\frac{3}{4}\\
  \theta=\frac{1}{3}\\
  \phi=\frac{2}{3}
\end{eqnarray}
We want to find scaling function $F$.

For an arbitrary polygon $P$ on a square lattice $L_{a}$ with lattice spacing $a$ we can use
Schwarz–Christoffel mapping conformal map $z(w)$ from unit disk ${\cal D}$ to the interior of $P$.
Self-avoiding polygons can be seen as a probability measure on polygons and on some subset ${\cal
  Z}_{a}$ of conformal maps $z(w):{\cal D}\to \mathbb{C}$ from unit disk to regions on the complex
plane. Precisely we define ${\cal Z}_{a}$ as ${\cal Z}_{a}=\{z(w):{\cal D}\to \mathbb{C}\; |\;
z(\partial{\cal D}) - \mbox{polygon on }L_{a}\}$ and denote the measure on ${\cal Z}_{a}$ by $\mu_{SAP,a}$.

Length of polygon boundary is then given by 
\begin{equation}
  \label{eq:2}
  l(z)=\oint_{\partial{\cal D}} |z'(w)| dw
\end{equation}
and area by an integral
\begin{equation}
  \label{eq:3}
  A(z)=\int_{{\cal D}} |z'(w)| d^{2}w
\end{equation}

Generating function for rooted polygons of given length and area can be seen as an observable given by the formula
\begin{equation}
  \label{eq:1}
  G^{(r)}(\mu_{B},\mu)=\sum_{z\in{\cal Z}_{a}} e^{-\mu A(z)} e^{-\mu_{B} l(z)} d\mu_{SAP,a}(z)
\end{equation}
In the limit $a\to 0$ the set ${\cal Z}_{a}$ is dense in the space of conformal maps (analytic
functions on unit disk).

In experiment we have sum over polygons of limited length and finite lattice spacing. If length is
still finite but $a\to 0$ the subspace ${\cal Z}_{a}$ is dense in the Hardy space $H^{\infty}$.

Every simply-connected region on complex plane can be approximated by a polygon for sufficiently
small $a$.

We want to rewrite generating function as a functional integral over space of analytic functions on
unit disk:
\begin{equation}
  \label{eq:4}
   G^{(r)}(\mu_{B},\mu)=\int_{H^{\infty}({\cal D})} e^{-\mu A(z)} e^{-\mu_{B} l(z)} d\mu_{SAP}(z)
\end{equation}

In order to compute such an integral we need to write the measure explicitly. There are two
approaches to this measure. First we can use conformal map $z(w)$ and introduce weight (Lagrangian).
Second we can consider loop as an SLE trace and use that measure. Big problem that we do not address
here is to prove the equivalence of these approaches.

\section{Measure on curves and renormalization}
\label{sec:meas-curv-renorm}

We can use Bose field action to introduce measure. Field $\chi(w)=\ln |z'(w)|$
\begin{equation}
  \label{eq:5}
  S=\frac{g}{4\pi} \int_{{\cal D}}|\nabla \chi|^{2} +i\frac{e_{0}}{2\pi} \int_{\partial {\cal D}}
  R\chi
\end{equation}
To get rid of curvature  term one can rewrite this matter action on upper half-plane:
\begin{equation}
  \label{eq:7}
  S=\frac{g}{4\pi} \int_{\Im z\geq 0}(\nabla \chi)^{2} 
\end{equation}
We need to impose boundary condition instead of the curvature term: $\chi=-e_{0}\log (z\bar z)$ for
$z\to \infty$.

SLE measure on the curves is represented by conformal field theory with this action. Local
observables are given by correlation functions of boundary and bulk vertex operators built from the
field $\chi$. To produce the curve connecting two points on the boundary one needs to insert two
boundary condition changing operators. Then use conformal map to make boundary a circle of radius
$r$:
\begin{equation}
  \label{eq:9}
  z=i r \frac{w-i}{w+i}
\end{equation}
and take a limit $r\to 0$. In this limit two boundary condition changing operators fuse to one
``pinning'' operator \cite{bettelheim2005harmonic} and curve becomes closed.

While matter field $\chi$ is used to introduce measure on critical curves, we need another field
$\varphi$ to take into account area and length of closed curve.

To take into account weights of area and length we should add to the action two terms
\begin{equation}
  \label{eq:8}
  \tilde S=S + \mu \int_{\Im z\geq 0} e^{2\chi} + \mu_{B}\int_{-\infty}^{+\infty} e^{\chi}
\end{equation}

\begin{equation}
  \label{eq:6}
  A[\chi,\varphi]= \int_{\Im z\geq 0} d^{2}z \left(\frac{1}{4\pi} \left[(\nabla \varphi)^{2} +
      (\nabla \chi)^{2}\right] +\mu e^{2b\varphi}\right) +\int_{-\infty}^{+\infty}dx \mu_{B}e^{b\varphi}
\end{equation}

\section{Liouville field theory}
\label{sec:liouv-field-theory}

\section{Conclusion}
\label{sec:conclusion}

\bibliography{bibliography}{} 
\bibliographystyle{utphys}

\end{document}

### 2014-04-17 benjamin-ono/notes.tex

@@
 
+The equation can be quantized. Mass is then changed to $\beta-\hbar$, where $\beta=\beta' \hbar$ and
+$\beta-\hbar=(\beta'-1)\hbar$. (?)
+
+The Hamiltonian is
+\begin{equation}
+  \label{eq:19}
+  H=\frac{1}{2}\int \left(u^{2}+\frac{1}{3} u^{2} u^{H}_{x}\right) dx
+\end{equation}
+Now to quantize the equation we assume that function $u(x,t)$ is defined on the circle or radius
+$\frac{L}{2\pi}$. Then we can expand $u$ in modes
+\begin{equation}
+  \label{eq:20}
+  u(x)=\sum_{k} e^{i k x}a_{k}
+\end{equation}
+The coefficients $a_{k}$ satisfy commutation relation
+\begin{equation}
+  \label{eq:21}
+  \{a_{m},a_{n}\}=n\delta_{nm}
+\end{equation}
+
+Equation can be written in Hamiltonian form
+\begin{equation}
+  \label{eq:22}
+  u_{t}=\{H,u\},
+\end{equation}
+and
+\begin{equation}
+  \label{eq:23}
+  H=\sum_{k>0} a_{-k} L_{k},
+\end{equation}
+where
+\begin{equation}
+  \label{eq:24}
+  L_{k}=\sum_{n>0} a_{n+k} a_{n}+\beta\sum_{n>0} n a_{n+k}
+\end{equation}
+The functions $L_{k}$ satisfy commutation relations w.r.t. Poisson bracket of Virasoro algebra
+\begin{equation}
+  \label{eq:25}
+  \{L_{k},L_{l}\}=(k-l)L_{k+l}+\frac{c}{12} k(k^{2}-1) \delta_{k+l,0},
+\end{equation}
+where
+\begin{equation}
+  \label{eq:26}
+  c=-6\beta^{2}
+\end{equation}
+So this is Poisson-Lie realization of Virasoro algebra (classical Virasoro algebra).
+
+Quantization is straightforward:
+\begin{equation}
+  \label{eq:27}
+  [a_{m}, a_{n}]=\hbar n \delta_{nm}
+\end{equation}
+\begin{equation}
+  \label{eq:28}
+  H=\sum_{k>0}:a_{-k}L_{k}:
+\end{equation}
+An we obtain commutation relations of Virasoro algebra
+\begin{equation}
+  \label{eq:29}
+   [L_{k},L_{l}]=(k-l)L_{k+l}+\frac{c}{12} k(k^{2}-1) \delta_{k+l,0},
+\end{equation}
+but now central charge is different
+\begin{equation}
+  \label{eq:30}
+  c=1-6\left( \sqrt{\beta} -\frac{1}{\sqrt{\beta}}\right)^{2}
+\end{equation}
+
+Benjamin-Ono equation is also connected to random matrices. Steady state equation $u_{t}=0$ is
+equivalent to loop equation for Hermitian matrices.
+
+Quantization of solitons is somehow connected with conformal field theory. In fractional quantum
+Hall waves on the boundary are described by Benjamin-Ono equation \cite{?Wiegmann}.
+
+In conformal field theory Virasoro symmetry can be extended to Lie groups. For example, if
+$u=\partial_{x} \varphi$ and $e^{i\varphi}$ is position of a particle on a ring, then $u$ is
+particle displacement. Since
+\begin{equation}
+  \label{eq:31}
+  e^{i\varphi_{1}}e^{i\varphi_{2}}=e^{i(\varphi_{1}+\varphi_{2})}
+\end{equation}
+we deal with $U(1)$ group.
+
+The Benjamin-Ono equation for $\varphi$ is
+\begin{equation}
+  \label{eq:35}
+  \partial_{t} \varphi +\frac{1}{2} (\partial_{x}\varphi)^{2}+\partial_{x}^{2}\varphi^{H}=0
+\end{equation}
+
+Now consider $\varphi\in su(2)$. Then $g=e^{i\varphi}$ is Lie group element and
+\begin{equation}
+  \label{eq:32}
+  \hat u=-ig^{-1} \partial_{x} g\in su(2)
+\end{equation}
+is connection in line bundle. It is $su_{k}(2)$-current $\hat J$.
+\begin{equation}
+  \label{eq:33}
+  J(x)=\sum \hat J_{n} e^{inx}
+\end{equation}
+Elements $J_{n}$ generate Kac-Moody algebra
+\begin{equation}
+  \label{eq:34}
+  [J_{n},J_{m}]=(n-m)J_{n+m} + k n \delta_{n+m,0}
+\end{equation}
+
+The problem is to construct non-abelian extension of Benjamin-Ono equation.
+
+If $g\leftrightarrow e^{i\varphi}$, then $\partial_{x}\varphi\leftrightarrow g^{-1}\partial_{x}g=J$.
+Using (\ref{eq:35}) we can conjecture form of the generalized equation
+\begin{equation}
+  \label{eq:36}
+  \partial_{t}J+\partial_{x}[J\cdot J]+\dots=0
+\end{equation}
+Such equation is supposed to have solutions with quantized mass.
+
+Note also that Benjamin-Ono equation is a certain limit of intermediate long-wave equation (ILW).
+The term $u^{H}=\fint \frac{u}{x-x'}dx'$ is the limit $L\to\infty$ of
+\begin{equation}
+  \label{eq:37}
+  u^{H}=\fint u \coth \frac{x-x'}{L} dx'
+\end{equation}
+for $2L$-periodic ocean. Hilbert transform connects real and imaginary parts of complex function
+$(\Re f)^{H}\to \Im f$. For complex functions the equation should be like
+\begin{equation}
+  \label{eq:38}
+  f_{t}=f f_{z}+if_{zz}, \quad ix=z
+\end{equation}
+For $\varphi=\sum_{k}\frac{a_{k}}{k} e^{ikx}$ we have stress-energy tensor
+\begin{equation}
+  \label{eq:39}
+  T=\sum_{k}L_{k}z^{-k-2}=T_{xx}+T_{yy}-2i T_{xy}=(\partial \varphi)^{2} +i\alpha\partial^{2}\varphi,
+\end{equation}
+and
+\begin{equation}
+  \label{eq:40}
+  [a_{k},a_{n}]=\delta_{n+k,0},
+\end{equation}
+\begin{equation}
+  \label{eq:41}
+  L_{n}=\sum_{k}:a_{k}a_{n-k}:
+\end{equation}
+\begin{equation}
+  \label{eq:42}
+  H=\sum_{k}:a_{-k}L_{k}:
+\end{equation}
+
+Benjamin-Ono equation is equivalent to
+\begin{equation}
+  \label{eq:43}
+  \partial_{t}u=[H,u]
+\end{equation}
+But we have boundary condition $a^{\dagger}_{k}=a_{-k}$. For $su(2)$-generalization we have
+$a_{k}\to J_{k}, J=g \partial g$, but on the boundary we have coset $su(2)/u(1)\approx S^{2}$. And
+$J=J_{x}\sigma_{x}+J_{y}\sigma_{y}+J_{z}\sigma_{z}$ should be changed to $\sigma_{z}\cdot J$. So if
+we want to get Benjamin-Ono equation for spin waves we need to rewrite $H=\sum_{k}:J_{-k} L_{k}:$ on
+the boundary.  
 \end{document}

### 2014-04-17 CFT/area-length/notes.tex
Log update + Some text on flat surfaces

--- 2014-04-04 area-length/notes.tex
@@
 
+\section{Liouville theory for flat surfaces}
+\label{sec:liouv-theory-flat}
+
+Now we will introduce Liouville theory for flat surfaces. We want to study closed loops in complex
+plane. The interior of such a loop can be mapped to unit disk or upper half-plane. Since the loops
+are on a flat plane and disk is in complex plane too we do not need to consider metrics with
+non-zero curvature. But curvature on the boundary is non-zero. So we write the action in terms of
+flat background metric $\hat g_{\mu\nu}$ with $\hat R=0$, but we on the boundary curvature $\hat
+K\neq 0$.
+
+We assume background-independence in the following sense. If $\hat g$ is flat metric then
+$e^{\sigma}\hat g$ is also flat if $\Delta\sigma=0$ inside the domain $\mathcal{M}$. On the boundary
+$\sigma$ is $2\pi$-periodic function. (The space of functions ${\varphi}$ is Hardy space).
+
+Since the connection of parameters $b$, $Q$ and asymptotic of the fields $\chi, \varphi$ at infinity
+for the theory on the upper half-plane is established from background-independence, we do not yet
+know if $Q=b+\frac{1}{b}$. Also the choice of area and length terms $e^{2b\varphi}$ and
+$e^{b\varphi}$ is not fixed,  even in usual Liouville theory it is possible to write boundary length
+as $e^{\frac{\varphi}{b}}$ for fractal boundary with fractal dimension $2b^{2}$. So in our action we
+leave parameters $b,a,Q$ free:
+\begin{multline}
+\label{eq:181}
+  S[\chi,\varphi]=\int_{\mathcal{M}}\left(\frac{1}{4\pi}[(\nabla \varphi)^{2}+(\nabla
+    \chi)^{2}]+\mu e^{2b\varphi}\right)d^{2}z +\\
+  +  \int_{\partial
+    \mathcal{M}}\left(\frac{1}{2\pi}(Q\varphi-ie_{0}\chi)\hat K + \mu_{B}e^{a\varphi}\right)dx+\mbox{ghosts}
+\end{multline}
+Let $\mathcal{M}=\mathbb{D}$ and $g_{\mu\nu}=\delta_{\mu\nu}$. Then the action is
+\begin{equation}
+  \label{eq:182}
+   S[\chi,\varphi]=\int_{\mathbb{D}}\left(\frac{1}{4\pi}[(\nabla \varphi)^{2}+(\nabla
+    \chi)^{2}]+\mu e^{2b\varphi}\right)d^{2}z +
+    \int_{S^{1}} \left(\frac{1}{2\pi}(Q\varphi-ie_{0}\chi) + \mu_{B}e^{a\varphi}\right)dx+\mbox{ghosts}
+\end{equation}
+Let us change background metric to $\tilde g_{\mu\nu}=e^{\sigma}g_{\mu\nu}$, then the action is
+\begin{equation}
+  \label{eq:183}
+  S_{\tilde g}[\chi,\varphi]=\int_{\mathbb{D}} \left( \frac{1}{4\pi} e^{2\sigma}\left[ (\nabla
+      \varphi)^{2}+(\nabla \chi)^{2}\right] +\mu e^{2b\varphi}\right)d^{2}z +\int_{S^{1}} \left( \frac{1}{2\pi}
+\end{equation}
+
 \section{Liouville theory}

### 2014-11-30 AffineLieAlgebras/Splints/special-paper.tex
Paper on splints for special embeddings is commited to git
Some text is written mostly in introduction, tables are copied from the thesis of Polina, figure is for illustration only, bibliography is almost empty.

\documentclass{article}

\usepackage{amsfonts}
\usepackage{pb-diagram}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\usepackage{amsmath,amssymb,amsthm}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[english,russian]{babel}

\newtheorem{Def}{Definition}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{statement}{Statement}
\newtheorem{Cnj}[Def]{Conjecture}
\newtheorem{Prop}[Def]{Property}
\newtheorem{example}{Example}[section]

\begin{document}

\title{Splints of root systems for special Lie subalgebras} % Тут надо придумать хорошее название

\author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$, P.I.~Kakin$^{1}$\\
  {\small $^1$ Department of High-energy and elementary particle physics,}\\ {\small St Petersburg State University}\\
  {\small 198904, Saint-Petersburg, Russia,}\\
  {\small $^{2}$ e-mail: antonnaz@gmail.com}}
%%  {\small$^{2}$ Chebyshev Laboratory,}
%%  {\small Department of Mathematics and Mechanics, SPb State University}\\
%%  {\small 199178, Saint-Petersburg, Russia}}
\date{}
\maketitle

\begin{abstract}
  Splint of root system for simple Lie algebra appears naturally in studies of (regular) embeddings
  of reductive subalgebras. Splint can be used to construct branching rules. We consider special
  embedding of Lie subalgebra to Lie algebra. We classify projections of algebra root systems using
  extended Dynkin diagrams and single out the conditions of splint appearance and coincidence of
  branching coefficients with weight multiplicities.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

The notion of splint was introduced by David Richter in the paper \cite{richter2008splints}. Splint
is the decomposition of root system into disjoint union of images of two or more root systems.

Splint is defined as a decomposition of root system into disjoint union of images of two embeddings
of some other root systems. Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$
is a bijective map of roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with
vector composition law in $\Delta_{1}$ and $\Delta$.
\begin{equation*}
\phi:\Delta_1 \longrightarrow \Delta
\end{equation*}
\begin{equation*}
\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
\,\,\, \alpha,\beta \in \Delta_1
\end{equation*}

Note that the image $Im(\phi)$ is not required to inherit the root system
properties except the addition rules equivalent to the addition
rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
can splinter $\Delta$  when the latter can be presented 
as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.

Root system of regular subalgebra is contained in the root system of algebra so splint is useful in
computation of branching coefficients.

In the paper \cite{2011arXiv1111.6787L} it was proven that the existence of splint leads to the
coincidence of branching coefficients with weight multiplicities under certain conditions. 
\begin{Prop}
\begin{equation}
\frac{e^{\rho _{\frak{g}}}}{\prod_{\beta \in \Delta _{\frak{s}%
}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }%
}}M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
}=\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
\label{singular main-4}
\end{equation}
Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
highest weights in the decomposition. The multiplicity $M_{\left( \frak{s}%
\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
}\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ defines the branching
coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
\[
b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
}^{(\mu )}=M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}.
\]
\end{Prop}
%% Rewrite this property informally

In the present paper we consider special embeddings of Lie subalgebras into Lie algebra. In this
case root system of the subalgebra is not contained in the root system of the algebra. So the
original motivation for splints is not applicable. But we can consider the projection of root system
of algebra on the root space of the subalgebra. Such a projection is not a root system anymore, but
it satisfies milder conditions (Section \ref{sec:spec-embedd-proj}). It is possible to classify most
projections using Dynkin diagrams augmented with multiplicities. We then define splint for such
'weak' root systems and state the conditions of its appearance and implications for the calculation
of branching coefficients (Section \ref{sec:splints-spec-embedd}).

In conclusion \ref{sec:conclusion} we discuss the cases when the projection of the root system does
not fall into above mentioned classification.

\section{Special embeddings and projections of root system}
\label{sec:spec-embedd-proj}

The study of special embeddings was traces back to fundamental papers by Eugene Dynkin
\cite{dynkin1952semisimple,dynkin1952maximal}, he called such subalgebras ``S-subalgebras'' to
distinguish from regular or ``R-subalgebras'' that have root systems obtained by dropping some roots
of the algebra root system. While maximal regular subalgebras have complete classification, the case
of special subalgebras is more difficult.

Denote Lie algebra by $\mathfrak{g}$, we assume that it is simple. Let's denote a subalgebra by
$\mathfrak{a}$. To construct an embedding of special subalgebra $\mathfrak{a}\to \mathfrak{g}$ one
needs to consider some representation of $\mathfrak{a}$ of dimension $\mathrm{dim}\mathfrak{g}$ and
identify generators of $\mathfrak{a}$ with linear combinations of generators of $\mathfrak{g}$ in
the adjoint representation.

 Such subalgebras are constructed by considering
representation of the algebra to

Projection of $\mathfrak{g}$ root system to the root space of $\mathfrak{a}$ in many cases can be
encoded by augmented Dynkin diagram with simple root multiplicities not greater or equal than 1.
Number of roots in projection is equal to the number of roots in $\mathfrak{g}$ root system (We do
not consider the case of orthogonal roots here). The rank of augmented Dynkin diagram is the same as
the rank of subalgebra $\mathfrak{a}$. Having Lie algebra $\mathfrak{a}$ and augmented Dynkin
diagram of the same rank it should be possible to reconstruct the embedding $\mathfrak{a}\to
\mathfrak{g}$, though not always in a unique way.

(We have the dimension of representation of $\mathfrak{a}$ and projection of roots of
$\mathfrak{g}$. It's not enough since in general there are different non-equivalent representations
of $\mathfrak{a}$. But the number of simple root systems with given number of roots is finite, so
it's possible to check which one has given projection).

Classification of all splints for special embeddings of a given algebra $\mathfrak{a}$ is given by
the augmented Dynkin diagrams of the same rank. (!)

Case of diagrams with multiplicities is not particularly interesting since we have just multiple
copies of the same stem (?).

%Теоремы из Дынкина и их очевидные следствия:

\begin{theorem}\label{dyn0}
  If representation $\phi$ of algebra $g$ induces representation $\tilde\phi$ on subalgebra $a$ then
  the weight system of representation $\tilde\phi$ can be obtained from representation $\phi$ by
  orthogonal projection of the weight space of algebra $g$ on the weight space of subalgebra $a$

  \cite{dynkin1952maximal}. %(Требует проверки, так как сформулировано в туманных и устаревших терминах в обоих источниках: см. стр.374 в d1 в доказательстве теоремы 3.2 или стр.119 в d2 - теорема 0.11)
\end{theorem}

В приложении к присоединенному представлению эта теорема означает, что в ортогональной проекции
корневой системы алгебры $g$ на корневое пространство подалгебры $a$ содержится корневая система
подалгебры $a$. Более того, верна следующая теорема:

\begin{theorem}\label{dyn1}
Всякая специальная подалгебра $a$ полупростой алгебры $g$ целочисленна, то есть проекции корней алгебры $g$ при ортогональной проекции на корневое пространство алгебры $a$ являются линейными комбинациями с целочисленными коэффициентами простых корней алгебры $a$ \cite{dynkin1972semisimple,dynkin1952semisimple}. %(стр.397 в d1)
\end{theorem}

\begin{theorem}\label{dyn2}
  Пусть $a$ - полупростая подалгебра полупростой алгебры $g$. Генератор, соответствующий корню
  $\lambda$ подалгебры $a$, раскладывается по базису Картана алгебры $g$ в линейную комбинации
  генераторов, соответствующих корням алгебры $g$. При ортогональном проектировании корневого
  пространства алгебры $g$ на корневое пространство подалгебры $a$ корни алгебры $g$ из указанной
  линейной комбинации спроектируются в корень $\lambda$

  \cite{dynkin1972semisimple,dynkin1952semisimple}. %(Требует проверки, так как сформулировано в туманных и устаревших терминах, см. стр.378 в d1)
\end{theorem}

Обозначим проекцию корневой системы $\Delta$ алгебры $g$ через $\Delta'$. Согласно теоремам \ref
{dyn0} и \ref {dyn2}, $\Delta'$ будет состоять из корневой системы $\Delta_a$ и векторов - линейных
комбинаций корней из $\Delta_a$ с целочисленными коэффициентами. Более того, из теоремы \ref {dyn0}
следует, что $\Delta'$ будет содержать какие-то корни из $\Delta_a$ больше одного раза.
Действительно, если бы все генераторы подалгебры $a$ совпадали с какими-то генераторами алгебры $g$,
то корневую систему $\Delta_a$ можно было бы отождествить с частью корневой системы $\Delta$. То
есть подалгебра $a$ была бы регулярной. Значит, в подалгебре $a$ есть генераторы, равные линейной
комбинации генераторов алгебры $g$ по крайней мере с двумя коэффицентами, не равными нулю. Корни,
соответствующие генераторам из этой линейной комбинации с ненулевыми коэффициентами, спроектируются
в один и тот же корень подалгебры $a$. То есть, хотя бы одна пара корней подалгебры $a$ будет
входить в $\Delta'$ более одного раза.

Получается, что в результате проекции возникает объект $\Delta'$, в который метрически вложена
$\Delta_a$, и в котром есть кратные корни с коэффициентом кратности не равным единице.

Example here (something like $A_2\to D_{4}$)

\begin{figure}[h!bt]
  \noindent\centering{
   \includegraphics[width=80mm]{Special-A2-D4-all-2}
  }
  \caption{Projection of $D_{4}$ ($so(8)$)-root system onto root space of special subalgebra $A_{2}$
    ($su(3)$). Note that this roots system is $G_{2}$ but with non-trivial multiplicities. }
 \label{fig:d4-a2_splint}
\end{figure}

Relying on these theorems we can encode the projections of root system by Dynkin diagrams. We need
to allow simple roots to have non-trivial multiplicities.

Classification of special embeddings

\begin{theorem}\label{va1}
Вложения
\begin{itemize}
\item $so(n-1)\rightarrow so(n)$,
\item $so(n)\rightarrow su(n)$,
\item $su(n)\rightarrow sp(2n)$,
\item $su(n-1)\rightarrow su(n)$,
\item $sp(n)\rightarrow su(2n)$
\end{itemize} -- все максимальные специальные вложения класса $A$ простых алгебр в простые алгебры (некоторые вкладываемые алгебры просты с точностью до фактора $u(1)$);
вложения
\begin{itemize}
\item $so(n)\oplus so(m)\rightarrow so(n+m)$
\item $su(n)\oplus su(m)\rightarrow su(n+m)$
\item $sp(n)\oplus sp(m)\rightarrow sp(n+m)$
\item $so(n)\oplus so(m)\rightarrow so(nm)$
\item $su(n)\oplus su(m)\rightarrow su(nm)$
\item $so(n)\oplus sp(m)\rightarrow sp(nm)$
\item $sp(n)\oplus sp(m)\rightarrow so(4nm)$
\end{itemize} -- все максимальные специальные вложения класса $A$ полупростых алгебр в простые алгебры \cite {sp1}.
\end{theorem}

\begin{theorem}\label{va2}
Не существует максимальных вложений класса $B$ полупростых (но не простых) алгебр в простые классические алгебры Ли. Если же вложение класса $B$ в простую алгебру $g$ строится на представлении $d$ размерности $p$, то оно может быть максимальным, только если $d$ неприводимо и:
\begin{itemize}
\item $g=so(n)$, $d$ -  ортогональное представление, $n=p$,
\item $g=sp(n)$, $d$ -  симплектичное представление, $n=p/2$,
\item $g=su(n)$, $d$ -  не ортогональное и не симплектичное представление, $n=p$.
\cite {sp1}
\end{itemize}
\end{theorem}

Эта теорема позволяет в подавляющем большинстве случаев определять максимальность вложения, не строя его явно.\\

Максимальные вложения класса $B$ приведены в таблице \ref{max-embeddings-class-B} (ну или еще какая-то текстовая связка-объяснение таблицы).

\begin{table}[h]

\label{max-embeddings-class-B}
\caption{Максимальные вложения класса $B$ в алгебры $so(2n)$, $so(2n-1)$, $su(n)$, $sp(2n)$ для $n\le 20$ \cite {sp1}.}
\begin{tabular}[t]{|p{3em}|p{20em}|}
\hline
 $a$ & $g$\\
\hline
$ sp(2)$ & $so(10)$, $so(14)$, $sp(8)$, $sp(10)$, $sp(20)$, $so(20)$  \\
\hline
$ su(3)$ & $su(6)$, $so(8)$, $su(10)$, $su(15)$, $so(27)$  \\
\hline
$ su(4)$ & $so(15)$, $su(10)$, $su(20)$, $so(20)$  \\
\hline
$ sp(3)$ & $so(14)$, $sp(7)$, $su(21)$ \\
\hline
$ so(7)$ & $so(8)$, $so(21)$, $so(27)$ \\
\hline
$ su(5)$ & $su(10)$, $su(15)$, $so(24)$ \\
\hline
$ sp(4)$ & $so(27)$, $so(36)$ \\
\hline
$ so(8)$ & $so(28)$, $so(35)$ \\
\hline
$ so(9)$ & $so(36)$ \\
\hline
$ su(6)$ & $su(15)$, $sp(10)$, $so(35)$ \\
\hline
$ so(10)$ & $su(16)$ \\
\hline
$ so(12)$ & $sp(16)$ \\
\hline
$ G_2$ & $so(7)$, $so(14)$ \\
\hline
$ F_4$ & $so(26)$ \\
\hline
\end{tabular}

\end{table}

\section{Splints for special embeddings}
\label{sec:splints-spec-embedd}

\begin{table}[h]
\begin{tabular}[t]{|p{2em}|p{6em}|p{5em}|p{5em}|p{2em}|p{6em}|}
\hline
Тип & $s$ & $W_a\subset W_s$ & $W_s\subset W_a$ & $g_{inv} $ & Примеры \\
\hline
1 & корневая система & нет & да & есть  & $B_2\rightarrow D_3$, $G_2\rightarrow B_3$\\
\hline
2 & корневая система  & да & да & нет & $A_1\rightarrow A_1+A_1$ \\
\hline
3 & корневая система  & да & нет & есть & $A_1+A_1\rightarrow D_3$ \\
\hline
4 & не корневая система  & да & нет & есть & $A_1\rightarrow A_2$, $A_1\rightarrow B_3$\\
\hline
5 & не корневая система  & да & нет & нет  & $A_1\rightarrow B_2$\\
\hline
6 & \multicolumn{4}{|l|}{$W_a\not\subset W_s$ и $W_s\not\subset W_a$} & $B_2\rightarrow D_4$\\
\hline
\end{tabular}
\caption{Классы специальных сплинтов.}
\label {spsp}
\end{table}

\section*{Conclusion}
\label{sec:conclusion}

\bibliography{special-bibliography}{} 
\bibliographystyle{apalike}
%%  \bibitem{d1}
%%  {\it Е.Б.Дынкин}
%%  Полупростые подалгебры полупростых алгебр.
%%  // Тр. Моск. матем. об-ва, т.1, стр. 39-166 (1952)
%%  \bibitem{d2}
%%  {\it Е.Б.Дынкин}
%%  Максимальные подгруппы классических групп.
%%  // Труды Моск. матем. об-ва, т. 1 (1952)
%%  
%%  
\end{document}

### 2014-12-01 AffineLieAlgebras/Splints/special-presentation.tex
Presentation on special splints started

\documentclass[pdftex]{beamer}

\setbeamertemplate{navigation symbols}{} % выключить навигационную панльку
\setbeamertemplate{footline}[frame number] % нумерация страниц

\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{pb-diagram}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
\usepackage{epstopdf}
\usepackage{multicol}
\usepackage{cancel}
\usepackage{hyperref}
\usepackage{amsfonts}

\usepackage{listings}
\usepackage{textcomp}
\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
  %	backgroundcolor=\color{lbcolor},
  language=Mathematica,
  tabsize=2,
  rulecolor=,
  basicstyle=\scriptsize,
  upquote=true,
  % aboveskip={1.5\baselineskip},
  columns=fixed,
  showstringspaces=false,
  extendedchars=true,
  % breaklines=true,
  prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
  % frame=single,
  showtabs=false,
  showspaces=false,
  showstringspaces=false,
  identifierstyle=\ttfamily,
  keywordstyle=\color[rgb]{0,0,1},
  commentstyle=\color[rgb]{0.133,0.545,0.133},
  stringstyle=\color[rgb]{0.627,0.126,0.941},
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\newtheorem{Sl}{Corollary}
\newtheorem{Utv}{Proposition}
%% \newtheorem{acknowledgement}[theorem]{Acknowledgement}
%% \newtheorem{algorithm}[theorem]{Algorithm}
%% \newtheorem{axiom}[theorem]{Axiom}
%% \newtheorem{case}[theorem]{Case}
%% \newtheorem{claim}[theorem]{Claim}
%% \newtheorem{conclusion}[theorem]{Conclusion}
%% \newtheorem{condition}[theorem]{Condition}
%% \newtheorem{conjecture}[theorem]{Conjecture}
%% \newtheorem{mycorollary}[theorem]{Corollary}
%% \newtheorem{mycriterion}[theorem]{Criterion}
%% \newtheorem{mydefinition}[theorem]{Definition}
%% \newtheorem{myexample}[theorem]{Example}
%% \newtheorem{myexercise}[theorem]{Exercise}
\newtheorem{mylemma}[theorem]{Лемма}
%% \newtheorem{mynotation}[theorem]{Notation}
%% \newtheorem{myproblem}[theorem]{Problem}
%% \newtheorem{myproposition}[theorem]{Proposition}
%% \newtheorem{myremark}[theorem]{Remark}
%% \newtheorem{mysolution}[theorem]{Solution}
%% \newtheorem{mysummary}[theorem]{Summary}
%% \newenvironment{myproof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfg}{\hf_{\gf}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\sfr}{\mathfrak{s}}
% \pagestyle{plain}

\theoremstyle{definition} \newtheorem{Def}{Definition}
\setbeamertemplate{caption}[empty]
\newcommand{\tr}{\hat\triangleright} \newcommand{\trc}{\triangleright}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

\usetheme{AnnArbor}
%\usetheme{Warsaw}

\title[]{Splints of root systems for special Lie subalgebras}

\author[]{Polina Kakin, Vladimir Lyakhovsky, \underline{Anton Nazarov}}

\institute[]{
  Department of High Energy and Elementary Particle Physics\\
  Physical faculty\\
  SPSU\\
}

\date[Novozhilov's 90] % (optional, should be abbreviation of conference name)
{In Search of Fundamental Symmetries
	\\December 2014}
\begin{document}

%% Plan:
%% 1. Structure of irrep is defined by additive properties of root system (Verma module+singular element = Weyl formula)
%% 2. Non angle-preserving map, splint
%% 3. Classification of splints, statement
%% 4. Special embeddings
%% 5. Projection of root system: examples
%% 6. Classification, Dynkin diagrams with multiplicities
%% 7. Conclusion
%% 
\maketitle
\section{Introduction}
\begin{frame}
  \frametitle{Root systems and irreducible representations}
  \begin{itemize}
  \item Additive properties of root system determine Verma module
    \begin{equation*}
      M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+})=\{(E^{-\alpha_{1}})^{n_{1}}\dots (E^{-\alpha_{s}})^{n_{s}} \left|v_{\mu}\right>\}_{\alpha_{i}\in\Delta^{+}}^{n_{i}=0,1,\dots}
    \end{equation*}
    \begin{figure}[h]
      \center{\includegraphics[width=0.4\linewidth]{B2_Verma}}
    \vspace{-0.3cm}
      \caption{Verma module and root system of $B_{2} (so(5))$ Lie algebra} 
      \label{verma}
    \end{figure}
    \vspace{-0.3cm}
  \item Weyl formula: singular element and characters of Verma modules
    \begin{equation*}
      \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
    \end{equation*}

  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Splint of a root system}
  Idea: consider root systems up to non-angle-preserving maps $\iota:\tilde\Delta\to \Delta$, $\iota(\alpha)=\iota(\alpha_{1})+\iota(\alpha_{2})\Leftrightarrow \alpha=\alpha_{1}+\alpha_{2}$

    A root system $\Delta$ "splinters"{ }as $\left(\Delta_{\af},\Delta_{\sfr}\right)$ if there are two embeddings $\iota_1:\Delta_{\af}\hookrightarrow\Delta$ and $\iota_2:\Delta_{\sfr}\hookrightarrow\Delta$.      $\Delta_{\af}$, $\Delta_{\sfr}$ are the "stems"{ }of the splint.

% where $\left(a\right)$ $\Delta$ is a disjoint union of the images of $\iota_1$ and $\iota_2$ $\left(b\right)$ neither the rank of $\Delta_1$ nor the rank of $\Delta_2$ exceeds the rank of~$\Delta$.

    \begin{equation*}
      \begin{array}{cc||c|c}
        \hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
        _{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
        \\ \hline\hline
        \hbox{(1)} & G_{2} & A_{2} & A_{2} \\
        & F_{4} & D_{4} & D_{4} \\ 
        & B_{2} & D_{2} & D_{2} \\ \hline
        \hbox{(2)} & B_{r}(r\geq 3) & D_{r} & \oplus ^{r}A_{1} \\
        (*)& C_{r}(r\geq 3) & \oplus ^{r}A_{1} &  D_{r} \\ \hline
        \hbox{(3)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
        ^{r}A_{1} \\
        & B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
      \end{array}
  \label{tb2}
    \end{equation*}

    Reduction $\gf\downarrow \af$: \quad$\pi\left(\mathrm{ch}L^{\mu}_{\gf}\right)=\sum_{\nu} b^{(\mu)}_{\nu} \mathrm{ch}L^{\nu}_{\af}$
\end{frame}

\begin{frame}
  \frametitle{Branching coefficients $=$ weight multiplicities of $\mathfrak{s}$}

  \begin{figure}[h!bt]
  \noindent\centering{
   \includegraphics[width=40mm]{g2}
  }\vspace{-0.3cm}
  \caption{Weyl group orbit  (long dash) for  $\Psi_{G_{2}}(L^{[3,2]})$ and its decomposition into sum of images of singular elements of   $A_{2}$ modules (short dash). Weight multiplicities of  $L^{[3,2]}_{A_{2}}$ coincide with branching coefficients $L^{[3,2]}_{G_{2}\downarrow A_{2}}$.}
 \label{fig:g2_splint}
\end{figure}\vspace{-0.3cm}
  \begin{equation*}
    b_{(\mu-\iota (\tilde{\mu}-\tilde{\nu}))}^{(\mu)}=M_{\sfr (\tilde{\nu})}^{(\tilde{\mu})}, 
  \end{equation*}

 $M^{(\tilde\mu)}_{\sfr(\tilde\nu)}$ - the multiplicity of the weight $\tilde\nu$ in the module $L^{\tilde\mu}_{\sfr}$ of algebra $\sfr$,\\
 $\tilde\mu=\sum m_k \tilde\omega_k$,  $\tilde\omega_k$ - fundamental weights for $\sfr$, $m_k$ - Dynkin labels of $\mu$.
\end{frame}
\section{Special subalgebras}
\begin{frame}
  \frametitle{Splint in the case of special embedding}
  \begin{Def}
    Embedding $\af \rightarrow \gf $ of semisimple Lie algebras is called "special"{ }if a root system $ \Delta _ {\af} $ of algebra $ \af $ is not a subsystem of a root system $ \Delta _ {\gf} $ of algebra $ \gf $.
  \end{Def}
  Properties of special subalgebras \cite {d}
    \begin{itemize}
    \item Orthogonal projection of algebra $g$ onto root space of subalgebra $a$ contains a root system of subalgebra $a$ 
    \item Projections of the roots of algebra $g$ are linear combinations of the roots of subalgebra $a$ with integer coefficients.
    \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Orthogonal projection}
  \begin{itemize}
  \item $\Delta'$ is orthogonal projection of the root system $\Delta_g$ onto the root space of subalgebra $a$
    \begin{itemize}
    \item $\Delta'\supset\Delta_a$
    \item $\Delta'$ contains some roots of $\Delta_a$ more than once
    \end{itemize}

  \item $\Phi_g^{(\mu)'}$ is orthogonal projection of the singular element of algebra $g$ onto the root space of subalgebra $a$ 
  \item $V_{a\rightarrow g}$ is injection fan defined as follows:

    \begin {equation}
      V_{a\rightarrow g}=\prod_{\Delta'^{+}\setminus \Delta_a^{+}}
      (1- e^{-\lambda}).
    \end {equation}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Special splint}
  \begin{itemize}
  \item $\Delta'\approx\left(\Delta_a,\Delta_s\right)$ is a special splint
  \item $\Delta_s=\Delta' \backslash \Delta_a$ is a system of vectors
    \begin{itemize}
    \item if $\Delta_s$ is not a root system then singular element $\Phi_s$ is obtained by applying injection fan $V_{a\rightarrow g}$ to the branching coefficients $g\downarrow a$.
    \end{itemize}
  \item $W_s$ is a group of reflections in hyperplanes orthogonal to the vectors in $\Delta_s$
  \item $W_{inv}$ is a group of reflections in hyperplanes orthogonal to the roots from $\Delta_g$ that already lie in the root space of subalgebra $a$.
  \end{itemize}
\end{frame}

\section{Types of special splints}
\begin{frame}
  \frametitle{Special splints: $\Delta_s\subset\Delta_a$}
  \begin{Utv}
    If $\Delta'\approx\left(\Delta_a,\Delta_s\right)$ is a special splint and $\Delta_s\subset\Delta_a$ then:

    $$
    \Phi_g^{(\mu)'}=\sum_{w\in W_{inv}} \epsilon (w) w(1+\sigma_1+\dots)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\tilde{\rho_s}}\Phi_s^{(\tilde{\mu})}),
    $$
    \begin{itemize}
      \item where $\sigma_1+\dots$ are elements of the group $W_s$ that move $\Phi_s^{(\tilde{\mu})}$ to the next Weyl chamber of subalgebra $a$. The number of elements is equal to the number of the fundamental Weyl chamber of subalgebra $a$ one needs to fill the fundamental Weyl chamber of the group $W_{inv}$.

      \item The vector $\hat\mu+\hat\rho_g$ is vector of the highest lenght in the projection of the singular element $\Phi_g^{(\mu)'}$ with positive multiplicity.
      \end{itemize}
    \label{u3}
  \end{Utv}
\end{frame}

\begin{frame}
  \frametitle{Special splints: $\Delta_a\subset\Delta_s$}
  \begin{Utv}
    If $\Delta'\approx\left(\Delta_a,\Delta_s\right)$ is a special splint and $\Delta_a\subset\Delta_s$ while $W_{inv}\subset\Delta_a$ then:

    $$
    \Phi_g^{(\mu)'}=\sum_{w\in W_{inv}} \epsilon (w) w(1+\sigma_1+\dots)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\rho_s}\Phi_s^{(\tilde{\mu})});
    $$
    if there is no $W_{inv}$ or $W_{inv}\not\subset W_a$ then:
    $$
    \Phi_g^{(\mu)'}=(2-\sum_{w\in W_a} \epsilon (w) w)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\rho_s}\Phi_s^{(\tilde{\mu})}).
    $$
    \label{u2}
  \end{Utv}
\end{frame}

\begin{frame}
  \frametitle{Special splints and branching coefficients}
  \begin{Sl}
    If $\Phi_s^{(\tilde{\mu})}$ can be put in the fundamental Weyl chamber $\bar C_a$ of subalgebra $a$ then by applying injection fan to the singular element $\Phi_s^{(\tilde{\mu})}$ one obtains $M_{s (\tilde{\nu})}^{(\tilde{\mu})}=b_{(\mu-\tilde{\mu}+\tilde{\nu})}^{(\mu)}$. If $\Phi_s^{(\tilde{\mu})}$ can not be put in $\bar C_a$ then $b_{(\mu-\tilde{\mu}+\tilde{\nu})}^{(\mu)}=N_{(\tilde{\nu})}$ where $N_{(\tilde{\nu})}$ are as follows: $$V_{a\rightarrow g}^{-1}(1+\sigma_1+\dots)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\rho_s}\Phi_s^{(\tilde{\mu})}))=\sum_{\tilde{\nu}} N_{(\tilde{\nu})}e^{\tilde{\mu}}.$$
    In both cases $\tilde{\nu}\in\bar C_a$ and the fundamental Weyl chamber $\bar C_a$ begins in the point $\tilde{\mu}-\mu$.
    \label{u31}
  \end{Sl}

\end{frame}

\begin{frame}
  \frametitle{Types of special splints}
  \begin{table}[h]
    \begin{tabular}[t]{|p{1,5em}|p{5em}|p{5em}|p{5em}|p{2em}|p{6em}|}
      \hline
      Type & $s$ & $W_a\subset W_s$ & $W_s\subset W_a$ & $W_{inv} $ & Examples \\
      \hline
      1 & root system & no & yes & yes  & $B_2\rightarrow D_3$, $G_2\rightarrow B_3$\\
      \hline
      2 & root system & yes & yes & no & $A_1\rightarrow A_1+A_1$ \\
      \hline
      3 & root system & yes & yes & no & $A_1+A_1\rightarrow D_3$ \\
      \hline
      4 & not a root system & yes & no & yes & $A_1\rightarrow A_2$, $A_1\rightarrow B_3$\\
      \hline
      5 & not a root system & yes & no & no  & $A_1\rightarrow B_2$\\
      \hline
      6 & \multicolumn{4}{|l|}{$W_a\not\subset W_s$ and $W_s\not\subset W_a$} & $B_2\rightarrow D_4$\\
      \hline
    \end{tabular}
    \label {spsp}
  \end{table}

\end{frame}

\section{Examples}

\begin{frame}
  \frametitle{Splint for embedding $B_2\rightarrow D_3$ ($so(5)\rightarrow so(6)$)}

  \begin{figure}[h]
    \center{\includegraphics[width=0.4\linewidth]{drawing-1}}
    \caption{Splint $D_3\approx (B_2,A_1+A_1)$: projection of the singular element $\Phi_{D_3}^{([1,1,2])'}$ can be made from singular elements $\Phi_{A_1+A_1}^{([1,1])}$. Light-grey area is the fundamental Weyl chamber of subalgebra $B_2$.} 
    \label{ris3}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Splint for embedding $B_2\rightarrow D_3$ ($so(5)\rightarrow so(6)$)}

  \begin{figure}[h]
    \center{\includegraphics[width=0.4\linewidth]{drawing-3}}
    \caption{Injection fan applied to the singular element $\Phi_{A_1+A_1}^{([1,1])}$ yields branching coefficients that are equal to 1 which is in agreement with the Gelfand-Tzeytlin rule for branching for embeddings $so(2n-1)\rightarrow so(2n)$. }
    \label{ris5}
  \end{figure}

\end{frame}

\begin{frame}
  \frametitle{Splint for embedding $G_2\rightarrow B_3$ ($g(2)\rightarrow so(7)$)}

  \begin{figure}[h]
    \center{\includegraphics[width=0.5\linewidth]{drawing-4}}
    \caption{Splint $B_3\approx (G_2,A_2)$: projection of the singular element $\Phi_{B_3}^{([0,0,1])'}$ can be made from singular elements $\Phi_{A_2}^{([0,1])}$. Light-grey area is the fundamental Weyl chamber of subalgebra $G_2$.}
    \label{ris6}
  \end{figure}

\end{frame}

\begin{frame}
  \frametitle{Splint for embedding $A_1\rightarrow A_2$ ($so(3)\rightarrow su(3)$)}

  \begin{figure}[h]
    \center{\includegraphics[width=0.7\linewidth]{drawing-5}}
    \label {a5}
    \caption{Projection of the singular element $\Phi_{A_2}^{([1,1])'}$ can be made from two singular elements $\Phi_{BC_1}^{(\tilde{\mu})}$.}
  \end{figure}

\end{frame}

\begin{frame}
  \frametitle{Splint for embedding $A_1+A_1\rightarrow D_3$ ($so(4)\rightarrow so(6)$)}

  \begin{figure}[h]
    \center{\includegraphics[width=0.4\linewidth]{drawing-2}}
    \caption{Splint $D_3\approx (A_1+A_1,B_2)$: projection of the singular element $\Phi_{D_3}^{([1,1,2])'}$ can be made from singular elements $\Phi_{B_2}^{([1,2])}$ (one of then is marked with grey colour).}
    \label{ris4}
  \end{figure}

\end{frame}

\section{Conclusion}

\begin{frame}
  \frametitle{Conclusion}
  \begin{itemize}
  \item The concept of splint was generalised on the case of special embedding.
  \item Decomposition of the projection of the singular element of splintered algebra was found for both the case when one of the stems is not a root system and the case when it is.
  \item The way to simplify calculation of branching coefficients was found for the case when both stems are root systems.
  \item All special splints were arranged into types and some of the types were thoroughly studied.
  \item The definition of singular element for the vector system that is not a root system was suggested.
  \item Together with the newly defined injection fan it might serve as the base for representation theory of such systems.
  \item The type of special splints where neither of stems contains the other requires further research.
  \end{itemize}

\end{frame}

\begin{frame}
  \frametitle{References}
  \begin{thebibliography}{99}

  \bibitem{ln}
    {\it V.D.Lyakhovsky, A.A.Nazarov}
    Fan, splint and branching rules.
    // Зап. научн. сем. ПОМИ, т. 398, стр. 162–178 (2012)
    arXiv:1111.6787v2 (2011)

  \bibitem{b1}
    {\it V.D.Lyakhovsky, S.Melnikov, er al}
    Recursion relations and branching rules for simple Lie algebras.
    // Journal of Physics A-Mathematical and General 29, no. 5, p.1075-1088 (1996)

  \bibitem{b2}
    {\it V.D.Lyakhovsky, A.A.Nazarov}
    Recursive algorithm and branching for nonmaximal embeddings.
    // Journal of Physics A-Mathematical and General 44, no. 7 (2011)

  \bibitem{sp1}
    {\it D.V.Vasilevich, V.D.Lyakhovsky}
    Method of special embeddings for grand unification models.
    // Theoretical and Mathematical Physics, 66:3, p. 231–237 (1986)

  \bibitem{d}
    {\it Е.Б.Дынкин}
    Полупростые подалгебры полупростых алгебр.
    // Тр. Моск. матем. об-ва, т.1, стр. 39-166 (1952)

  \end{thebibliography}
\end{frame}

\begin{frame}[c]
  \begin{center}
    \Large{Thank you for attention!}    
  \end{center}

%%   \begin{figure}[h]
%%     \center{\includegraphics[width=0.65\linewidth]{IMG_1777}}
%% 
%%   \end{figure}
%%

\end{frame}

\end{document}

### 2014-12-17 AffineLieAlgebras/Splints/special-paper.tex
Multiplicity-free modules, bibliography, general structure

@@
 
+\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
+\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
+\newcommand{\co}[1]{\stackrel{\circ }{#1}}
+\newcommand{\pia}{\pi_{\mathfrak{a}}}
+\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
+\newcommand{\gf}{\mathfrak{g}}
+\newcommand{\gfh}{\hat{\mathfrak{g}}}
+\newcommand{\af}{\mathfrak{a}}
+\newcommand{\afh}{\hat{\mathfrak{a}}}
+\newcommand{\bff}{\mathfrak{b}}
+\newcommand{\afb}{\mathfrak{a}_{\bot}}
+\newcommand{\hf}{\mathfrak{h}}
+\newcommand{\hfg}{\hf_{\gf}}
+\newcommand{\hfa}{\hf_{\af}}
+\newcommand{\hfb}{\mathfrak{h}_{\bot}}
+\newcommand{\pf}{\mathfrak{p}}
+\newcommand{\aft}{\widetilde{\mathfrak{a}}}
+\newcommand{\sfr}{\mathfrak{s}}
+
 \begin{document}
@@
 \begin{abstract}
-  Splint of root system for simple Lie algebra appears naturally in studies of (regular) embeddings
-  of reductive subalgebras. Splint can be used to construct branching rules. We consider special
-  embedding of Lie subalgebra to Lie algebra. We classify projections of algebra root systems using
-  extended Dynkin diagrams and single out the conditions of splint appearance and coincidence of
-  branching coefficients with weight multiplicities.
+  Splint is a decomposition of root system into union of root systems. Splint of root system for
+  simple Lie algebra appears naturally in studies of (regular) embeddings of reductive subalgebras.
+  Splint can be used to construct branching rules. We consider special embedding of Lie subalgebra
+  to Lie algebra. We classify projections of algebra root systems using extended Dynkin diagrams and
+  single out the conditions of splint appearance and coincidence of branching coefficients with
+  weight multiplicities. While such a coincidence is not very common it is connected with Gelfand-Tsetlin basis. 
 \end{abstract}
@@
 The notion of splint was introduced by David Richter in the paper \cite{richter2008splints}. Splint
-is the decomposition of root system into disjoint union of images of two or more root systems.
-
-Splint is defined as a decomposition of root system into disjoint union of images of two embeddings
-of some other root systems. Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$
-is a bijective map of roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with
-vector composition law in $\Delta_{1}$ and $\Delta$.
+is the decomposition of root system into disjoint union of images of two or more embeddings of some
+other root systems. Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a
+bijective map of roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with vector
+composition law in $\Delta_{1}$ and $\Delta$.
 \begin{equation*}
@@
 In the paper \cite{2011arXiv1111.6787L} it was proven that the existence of splint leads to the
-coincidence of branching coefficients with weight multiplicities under certain conditions. 
+coincidence of branching coefficients with weight multiplicities under certain conditions. We denote
+Lie algebra by $\gf$ and consider it's subalgebra $\af$. If $\af$ is a regular subalgebra, its root
+system $\Delta_{\af}$ is contained in $\Delta_{\gf}$. Branching coefficients $b^{(\mu)}_{\nu}$
+appear in decomposition of irreducible representation $L^{\mu}_{\gf}$ of $\gf$ to the sum of
+irreducible representations of $\af$:
+\begin{equation}
+  \label{eq:1}
+  L^{\mu}_{\gf}=\bigoplus_{\nu} b^{(\mu)}_{\nu} L^{\nu}_{\af}
+\end{equation}
+
+Assume that root system $\Delta_{\gf}$ splinters as $\Delta_{\gf}=\Delta_{\af} \cup
+\phi(\Delta_{\sfr})$, where $\phi$ is an embedding of root system $\Delta_{\sfr}$ of some semisimple
+Lie algebra $\sfr$. Then branching coefficients $b^{(\mu)}_{\nu}$ for the reduction
+$L^{(\mu)}_{\gf}\downarrow \af$ coincide with weight multiplicities $m^{(\tilde \mu)}_{\nu}$ in
+$\sfr$-representations provided certain technical condition holds \cite{2011arXiv1111.6787L}.
+Highest weight $\tilde\mu$ of $\sfr$-representation is calculated from Dynkin labels of highest
+weight $\mu$ of $\gf$-module.
+
+In next section \ref{sec:splints-root-systems} we review the classification of splints for simple
+root systems and results for branching coefficients. Then we move to the study of special embeddings
+which is the main subject of the present paper. We consider special embeddings of Lie subalgebras
+into Lie algebra. In this case root system of the subalgebra is not contained in the root system of
+the algebra. So the original motivation for splints is not applicable. But we can consider the
+projection of root system of algebra on the root space of the subalgebra. Such a projection is not a
+root system anymore, but it satisfies milder conditions (Section \ref{sec:spec-embedd-proj}). It is
+possible to classify most projections using Dynkin diagrams augmented with multiplicities. We then
+define splint for such 'weak' root systems and state the conditions of its appearance and
+implications for the calculation of branching coefficients (Section \ref{sec:splints-spec-embedd}).
+
+Use of representation theory of the subalgebra allows us to classify all the splints for the projections
+of algebra root system. We also apply this method to metric splints and regular subalgebras and get
+a unified treatment. We obtain Gelfand-Tsetlin rules for regular and special embeddings this way.
+
+In conclusion \ref{sec:conclusion} we discuss the cases when the projection of the root system does
+not fall into above mentioned classification.
+
+\section{Splints of root systems and regular subalgebras}
+\label{sec:splints-root-systems}
+The notion of splint was introduced in the paper \cite{richter2008splints} and classification of
+splints for simple root systems was obtained there.
+
+Embedding $\phi$ of a root system $\Delta_1$ into a root system
+$\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
+subset of $\Delta$ that commutes with vector composition law in
+$\Delta_{1}$ and $\Delta$.
+\begin{equation*}
+\phi:\Delta_1 \longrightarrow \Delta
+\end{equation*}
+\begin{equation*}
+\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
+\,\,\, \alpha,\beta \in \Delta_1
+\end{equation*}
+
+Note that the image $Im(\phi)$ must not inherit the root system
+properties except the addition rules equivalent to the addition
+rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
+can splinter $\Delta$  when the latter can be presented 
+as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.
+
+The classification is shown in table
+
+Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
+\mathfrak{a}\hookrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
+is a
+reductive subalgebra $\mathfrak{a \subset g}$ with correlated root spaces: $%
+\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset \mathfrak{h}_{\mathfrak{g }%
+}^{\ast }$. Let $\mathfrak{a}^{\mathfrak{s}}$ be a semisimple summand of
+$\mathfrak{a}$,
+this means that $\mathfrak{a}=\mathfrak{a}^{\mathfrak{s}} \oplus \mathfrak{u}(1)\oplus %
+\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^{\mathfrak{s}}$
+to be a proper regular subalgebra and $\mathfrak{a}$ to be the
+maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed that is the rank
+$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
+
+Computation of branching coefficients relies on roots $\Delta_{\gf}\setminus \Delta_{\af}$
+\cite{2010arXiv1007.0318L} so splint  is naturally connected branching coefficients for regular
+subalgebra.
+
+Remember that only three types of splints are
+injective and thus are naturally connected with branching. Below we
+reproduce the part of the splints table from \cite{richter2008splints} corresponding to
+injective splints:
+\begin{equation}
+\label{eq:1}
+\begin{array}{cc||c|c}
+\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
+_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
+\\ \hline\hline
+\hbox{(i)} & G_{2} & A_{2} & A_{2} \\
+& F_{4} & D_{4} & D_{4} \\ \hline
+\hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
+(*)& C_{r}(r\geq 3) & \oplus ^{r}A_{1} &  D_{r} \\ \hline
+\hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
+^{r}A_{1} \\
+& B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
+\end{array}
+\end{equation}
+
+Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\frak{s}})
+$ of the simple root system $\Delta $. In the first two types both $\Delta _{%
+\frak{a}}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
+first type splints are equivalent and in the second are not. In the third
+type splints only $\Delta _{\frak{a}}$ is embedded metrically. The summands $%
+u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$. This does not change
+the principle properties of branching but makes it possible to use the
+multiplicities of $\frak{s}$ -modules without further projecting their
+weights.
+
+Note that in the case of $C_{r}$-series (marked with the star in table \eqref{eq:1}) metrical
+embedding $\Delta_{D_{r}}\to \Delta_{C_{r}}$ does not lead to the appearance of regular subalgebra
+$\mathfrak{a}$ (See \cite{dynkin1952semisimple}).
+
+In the paper \cite{2011arXiv1102.1702L} it was shown that
+
 \begin{Prop}
@@
 
-In the present paper we consider special embeddings of Lie subalgebras into Lie algebra. In this
-case root system of the subalgebra is not contained in the root system of the algebra. So the
-original motivation for splints is not applicable. But we can consider the projection of root system
-of algebra on the root space of the subalgebra. Such a projection is not a root system anymore, but
-it satisfies milder conditions (Section \ref{sec:spec-embedd-proj}). It is possible to classify most
-projections using Dynkin diagrams augmented with multiplicities. We then define splint for such
-'weak' root systems and state the conditions of its appearance and implications for the calculation
-of branching coefficients (Section \ref{sec:splints-spec-embedd}).
-
-In conclusion \ref{sec:conclusion} we discuss the cases when the projection of the root system does
-not fall into above mentioned classification.
-
 \section{Special embeddings and projections of root system}
@@
 distinguish from regular or ``R-subalgebras'' that have root systems obtained by dropping some roots
-of the algebra root system. While maximal regular subalgebras have complete classification, the case
-of special subalgebras is more difficult.
+of the algebra root system. While regular subalgebras are easy to construct by dropping nodes from
+extended Dynkin diagram of the algebra, the case of special subalgebras is more difficult. Complete
+classification for exceptional Lie algebras was obtained recently in \cite{minchenko2006semisimple}.
+The algorithm of construction of special subalgebras is available in GAP package but still requires
+manual intervention \cite{de2011constructing}.
 
-Denote Lie algebra by $\mathfrak{g}$, we assume that it is simple. Let's denote a subalgebra by
-$\mathfrak{a}$. To construct an embedding of special subalgebra $\mathfrak{a}\to \mathfrak{g}$ one
-needs to consider some representation of $\mathfrak{a}$ of dimension $\mathrm{dim}\mathfrak{g}$ and
-identify generators of $\mathfrak{a}$ with linear combinations of generators of $\mathfrak{g}$ in
-the adjoint representation.
+Assume that Lie algebra $\gf$ is simple. Let's denote a subalgebra by
+$\af$. We denote corresponding Cartan subalgebras by $\hfg$ and $\hfa$ and identify them with the dual
+spaces $\hfg^{*}$, $\hfa^{*}$ using Killing forms of $\gf$ and $\af$.
 
- Such subalgebras are constructed by considering
-representation of the algebra to
+To construct an embedding $\af\to\gf$ consider some representation $L^{\nu}_{\af}$ as a subspace of
+Lie algebra $\gf$. Then one needs to check that the generators of $\af$ then can be presented as
+linear combinations of generators of $\gf$. We can identify Cartan subalgebra $\hfa\subset \af$ with
+dual space $\hfa^{*}$ using Killing form. Then the root system $\Delta_{\gf}$ of $\gf$ can be
+projected to $\hfa^{*}$ using the expression of $\hfa$-generators through $\hfg$-generators.
 
-Projection of $\mathfrak{g}$ root system to the root space of $\mathfrak{a}$ in many cases can be
-encoded by augmented Dynkin diagram with simple root multiplicities not greater or equal than 1.
-Number of roots in projection is equal to the number of roots in $\mathfrak{g}$ root system (We do
-not consider the case of orthogonal roots here). The rank of augmented Dynkin diagram is the same as
-the rank of subalgebra $\mathfrak{a}$. Having Lie algebra $\mathfrak{a}$ and augmented Dynkin
-diagram of the same rank it should be possible to reconstruct the embedding $\mathfrak{a}\to
-\mathfrak{g}$, though not always in a unique way.
+%%  To reduce $\gf$-representations project $\gf$ root system to Cartan subalgebra of $\af$. 
+%% 
+%%  To construct an embedding of special subalgebra $\af\to \gf$ one
+%% needs to consider some representation of $\af$ of dimension $\mathrm{dim}\gf$ and
+%% identify generators of $\af$ with linear combinations of generators of $\gf$ in
+%% the adjoint representation. 
+%% 
+%%  Such subalgebras are constructed by considering
+%% representation of the algebra to
+%%
 
-(We have the dimension of representation of $\mathfrak{a}$ and projection of roots of
-$\mathfrak{g}$. It's not enough since in general there are different non-equivalent representations
-of $\mathfrak{a}$. But the number of simple root systems with given number of roots is finite, so
-it's possible to check which one has given projection).
+From classical papers \cite{dynkin1952semisimple,dynkin1952maximal} it is well known that the
+projection of $\gf$ root system $\Delta_{\gf}$ to $\hfa^{*}$ is a weight system of some
+finite-dimensional but not irreducible representation of $\af$. Moreover, roots of $\af$ are
+contained in this projection. We denote such a projection by
+\begin{equation}
+  \label{eq:2}
+  \Delta'=\pi_{\af}\left(\Delta_{\gf}\right)
+\end{equation}
 
-Classification of all splints for special embeddings of a given algebra $\mathfrak{a}$ is given by
-the augmented Dynkin diagrams of the same rank. (!)
-
-Case of diagrams with multiplicities is not particularly interesting since we have just multiple
-copies of the same stem (?).
+The system $\Delta'$ can be a root system but it can be not reduced and can contain some vectors
+with multiplicities greater then one.
 
 %Теоремы из Дынкина и их очевидные следствия:
+
+To
 
@@
 
+Applying this theorem
 В приложении к присоединенному представлению эта теорема означает, что в ортогональной проекции
@@
 
-Relying on these theorems we can encode the projections of root system by Dynkin diagrams. We need
-to allow simple roots to have non-trivial multiplicities.
-
-Classification of special embeddings
-
-\begin{theorem}\label{va1}
-Вложения
-\begin{itemize}
-\item $so(n-1)\rightarrow so(n)$,
-\item $so(n)\rightarrow su(n)$,
-\item $su(n)\rightarrow sp(2n)$,
-\item $su(n-1)\rightarrow su(n)$,
-\item $sp(n)\rightarrow su(2n)$
-\end{itemize} -- все максимальные специальные вложения класса $A$ простых алгебр в простые алгебры (некоторые вкладываемые алгебры просты с точностью до фактора $u(1)$);
-вложения
-\begin{itemize}
-\item $so(n)\oplus so(m)\rightarrow so(n+m)$
-\item $su(n)\oplus su(m)\rightarrow su(n+m)$
-\item $sp(n)\oplus sp(m)\rightarrow sp(n+m)$
-\item $so(n)\oplus so(m)\rightarrow so(nm)$
-\item $su(n)\oplus su(m)\rightarrow su(nm)$
-\item $so(n)\oplus sp(m)\rightarrow sp(nm)$
-\item $sp(n)\oplus sp(m)\rightarrow so(4nm)$
-\end{itemize} -- все максимальные специальные вложения класса $A$ полупростых алгебр в простые алгебры \cite {sp1}.
-\end{theorem}
-
-\begin{theorem}\label{va2}
-Не существует максимальных вложений класса $B$ полупростых (но не простых) алгебр в простые классические алгебры Ли.
-Если же вложение класса $B$ в простую алгебру $g$ строится на представлении $d$ размерности $p$, то оно может быть максимальным, только если $d$ неприводимо и:
-\begin{itemize}
-\item $g=so(n)$, $d$ -  ортогональное представление, $n=p$,
-\item $g=sp(n)$, $d$ -  симплектичное представление, $n=p/2$,
-\item $g=su(n)$, $d$ -  не ортогональное и не симплектичное представление, $n=p$.
-\cite {sp1}
-\end{itemize}
-\end{theorem}
-
-Эта теорема позволяет в подавляющем большинстве случаев определять максимальность вложения, не строя его явно.\\
-
-Максимальные вложения класса $B$ приведены в таблице \ref{max-embeddings-class-B} (ну или еще какая-то текстовая связка-объяснение таблицы).
-
-\begin{table}[h]
-
-\label{max-embeddings-class-B}
-\caption{Максимальные вложения класса $B$ в алгебры $so(2n)$, $so(2n-1)$, $su(n)$, $sp(2n)$ для $n\le 20$ \cite {sp1}.}
-\begin{tabular}[t]{|p{3em}|p{20em}|}
-\hline
- $a$ & $g$\\
-\hline
-$ sp(2)$ & $so(10)$, $so(14)$, $sp(8)$, $sp(10)$, $sp(20)$, $so(20)$  \\
-\hline
-$ su(3)$ & $su(6)$, $so(8)$, $su(10)$, $su(15)$, $so(27)$  \\
-\hline
-$ su(4)$ & $so(15)$, $su(10)$, $su(20)$, $so(20)$  \\
-\hline
-$ sp(3)$ & $so(14)$, $sp(7)$, $su(21)$ \\
-\hline
-$ so(7)$ & $so(8)$, $so(21)$, $so(27)$ \\
-\hline
-$ su(5)$ & $su(10)$, $su(15)$, $so(24)$ \\
-\hline
-$ sp(4)$ & $so(27)$, $so(36)$ \\
-\hline
-$ so(8)$ & $so(28)$, $so(35)$ \\
-\hline
-$ so(9)$ & $so(36)$ \\
-\hline
-$ su(6)$ & $su(15)$, $sp(10)$, $so(35)$ \\
-\hline
-$ so(10)$ & $su(16)$ \\
-\hline
-$ so(12)$ & $sp(16)$ \\
-\hline
-$ G_2$ & $so(7)$, $so(14)$ \\
-\hline
-$ F_4$ & $so(26)$ \\
-\hline
-\end{tabular}
-
-\end{table}
+%% Relying on these theorems we can encode the projections of root system by Dynkin diagrams. We need
+%% to allow simple roots to have non-trivial multiplicities. 
+%%
 
@@
 \label{sec:splints-spec-embedd}
+
+Since roots are weights of the adjoint representation, such a projection produces the weight diagram
+of $\af$-representation that contains adjoint representation of $\af$. After the subtraction of
+$\af$-root system $\Delta_{\af}$ from $\Delta'$ we obtain weight diagram of representation called
+``characteristic representation of subalgebra $\af$'' by Dynkin in the seminal paper
+\cite{dynkin1952semisimple}.
+
+We want to classify all the cases when branching coefficients coincide with weight multiplicities of
+some other algebra representations. Such a coincidence is possible when the projection $\Delta'$ of
+$\gf$ root system admits a splint $\Delta=\Delta_{\af}\cup \Delta_{\sfr}$. Projection of the root
+system $\Delta'$ coincides with the projection of weight diagram of the adjoint representation of
+algebra $\gf$ with the exception of zero weight. Adjoint representation of $\gf$ contains adjoint
+representation of $\af$ and can be decomposed as
+\begin{equation}
+  \label{eq:3}
+  \mathrm{ad}_{\gf}=\mathrm{ad}_{\af}\oplus M_{\af}^{\chi},
+\end{equation}
+where $M^{\chi}_{\af}$ is not necessary irreducible representation of $\af$ called
+``characteristic'' in \cite{dynkin1952semisimple}.
+
+Weight diagram of $M^{\chi}_{\af}$ coincides with root system $\Delta_{\sfr}$ with the exception of
+zero weight. So we need to find all the representations for all simple Lie algebras $\af$, such that
+their weight diagrams are root systems after the exclusion of zero weight.
+
+Multiplicity of zero weight in adjoint representation is equal to the rank of the algebra. So if
+$\mathrm{rank}\gf-\mathrm{rank}\af$, the representations in questions must be multiplicity-free.
+
+The simplest class of multiplicity-free representations is called ``strongly multiplicity free''
+\cite{lehrer2006strongly} and consists of multiplicity free representations with weight systems
+admitting strict ordering $\nu_{1}<\nu_{2} \Leftrightarrow \nu_{1}=\nu_{2}+n \alpha$, where $n\in
+\mathbb{N}, \alpha\in \Delta^{+}_{\af}$ and for all $\nu_{1},\nu_{2}$ either $\nu_{1}<\nu_{2}$ or
+$\nu_{2}<\nu_{1}$.
+
+The list of strongly multiplicity free representations consists of (first) fundamental representations
+for series $A_{r}, B_{r}, C_{r}$, exceptional Lie algebra $G_{2}$ (7-dimensional representation) and
+all $A_{1}$ representations.
+
+First fundamental representation of $B_{r}$ immediately gives us the splint $\Delta'=\pi_{B_{r}}\left(
+\Delta_{D_{r+1}}\right) = \Delta_{B_{r}}\cup \Delta_{A_{1}+\dots+A_{1}}$ corresponding to Gelfand-Tsetlin
+multiplicity-free branching for the embedding $so(2r+1)\to so(2r+2)$.
+
+Fundamental weights of the algebra $A_{r}$ are shorter than its roots, but the projections of $\gf$
+weights must be given by linear combinations of roots of special subalgebra $\af$ with integer
+coefficients, so the first class of strongly multiplicity free representations does not produce such
+projection.
+
+Nevertheless, the union of diagrams of two fundamental representations of $A_{2}$ with the root
+system of $A_{2}$ produces weight diagram of $G_{2}$. This case corresponds to splint
+$\Delta_{G_{2}}=\varphi_{1}( \Delta_{A_{2}})\cup \varphi_{2}(\Delta_{A_{2}})$ which is connected
+with regular subalgebra $A_{2}\subset G_{2}$ (see Section \ref{sec:splints-root-systems}).
+
+The complete classification of multiplicity-free irreducible representations was obtained in
+\cite{howe1995perspectives} (see also \cite{stembridge2003multiplicity}).
+
+What we really need is the classification of all the representations where multiplicities of all
+non-zero weights are equal to one. Fortunately, such a classification was obtained in
+\cite{plotkin1998visual}. It consists of multiplicity-free representations and adjoint
+representations of algebras $B_{r}$.
+
+ (Possibly, strongly multiplicity-free:
+).
+
+ Classification of strongly multiplicity-free representations is simple:
+$A_{n}$ first fundamental representation, $B_{n}$ first fundamental representation, $C_{n}$ first
+fundamental representation, $G_{2}$ first fundamental representation (7) and
+all irreducible $A_{1}$-representations.
+
+(See also https://projecteuclid.org/euclid.jmsj/1180135505 for multiplicity-free branching rules)
+
+Having obtained this classification we need to check which weight diagrams can be obtained as the
+projections of $\gf$ root system. It is the case for $B_{n}\to D_{n+1}$ or $A_{1}\oplus\dots\oplus
+A_{1}\to D_{n+1}$.
+
+Projection of $\gf$ root system to the root space of $\af$ in many cases can be
+encoded by augmented Dynkin diagram with simple root multiplicities not greater or equal than 1.
+Number of roots in projection is equal to the number of roots in $\gf$ root system (We do
+not consider the case of orthogonal roots here). The rank of augmented Dynkin diagram is the same as
+the rank of subalgebra $\af$. Having Lie algebra $\af$ and augmented Dynkin
+diagram of the same rank it should be possible to reconstruct the embedding $\af\to
+\gf$, though not always in a unique way.
+
+We must also account for the case of roots of parallel roots of different length. $BC_{1} $ is the
+simplest system with parallel roots, one of its two parallel is twice longer than another. Such a
+system appear in study of affine
+
+ The simplest
+system with parallel roots have roots of two different length and Such a systems
+appear  $BC_{1} $ and its generalization. (We have the dimension of representation of $\af$ and
+projection of roots of $\gf$. It's not enough since in general there are different non-equivalent
+representations of $\af$. But the number of simple root systems with given number of roots is
+finite, so it's possible to check which one has given projection).
+
+Classification of all splints for special embeddings of a given algebra $\af$ is given by
+the augmented Dynkin diagrams of the same rank. (!)
+
+Case of diagrams with multiplicities is not particularly interesting since we have just multiple
+copies of the same stem (?).
 

### 2014-12-17 AffineLieAlgebras/Splints/special-paper.tex
More work on multiplicity-free

@@
 some other algebra representations. Such a coincidence is possible when the projection $\Delta'$ of
-$\gf$ root system admits a splint $\Delta=\Delta_{\af}\cup \Delta_{\sfr}$. Projection of the root
-system $\Delta'$ coincides with the projection of weight diagram of the adjoint representation of
-algebra $\gf$ with the exception of zero weight. Adjoint representation of $\gf$ contains adjoint
+$\gf$ root system admits a splint $\Delta'=\varphi_{\af}(\Delta_{\af})\cup
+\varphi_{\sfr}(\Delta_{\sfr})$, where $\varphi_{\af}$ and $\varphi_{\sfr}$ are the embeddings of
+corresponding root systems. The embedding $\varphi_{\af}$ is metric and trivial. Projection of the
+root system $\Delta'$ coincides with the projection of weight diagram of the adjoint representation
+of algebra $\gf$ with the exception of zero weight. Adjoint representation of $\gf$ contains adjoint
 representation of $\af$ and can be decomposed as
@@
 
-First fundamental representation of $B_{r}$ immediately gives us the splint $\Delta'=\pi_{B_{r}}\left(
-\Delta_{D_{r+1}}\right) = \Delta_{B_{r}}\cup \Delta_{A_{1}+\dots+A_{1}}$ corresponding to Gelfand-Tsetlin
-multiplicity-free branching for the embedding $so(2r+1)\to so(2r+2)$.
-
 Fundamental weights of the algebra $A_{r}$ are shorter than its roots, but the projections of $\gf$
@@
 
+First fundamental representation of $B_{r}$ immediately gives us the splint $\Delta'=\pi_{B_{r}}\left(
+\Delta_{D_{r+1}}\right) = \Delta_{B_{r}}\cup \Delta_{A_{1}+\dots+A_{1}}$ corresponding to Gelfand-Tsetlin
+multiplicity-free branching for the embedding $so(2r+1)\to so(2r+2)$.
+
+First fundamental representation of $C_{r}$ -?
+
+Projection $\Delta'$ on the subalgebra $A_{1}$ is never multiplicity free, so $\Delta_{\sfr}$ always
+contain parallel roots. The simplest case is special embedding $A_{1}\to A_{2}$ where
+$\Delta_{\sfr}$ is the root system $BC_{1}$. Such systems do not correspond to semisimple Lie
+algebras, so we can not speak of a coincidence of branching coefficients for the reduction
+$\gf\downarrow \af$ with weight multiplicities of $\sfr$-representations.
+
+Weight diagram of of seven-dimensional representation of $G_{2}$ together with $G_{2}$ root system
+form the projection of root system $B_{3}$ which appears in special embedding of simple Lie algebra
+$G_{2}\to B_{3}$. Branching coefficients in this case coincide with weight multiplicities of
+representations of algebra $\sfr=A_{2}$ with image of root system consisting of short roots of
+$G_{2}$.
+
 The complete classification of multiplicity-free irreducible representations was obtained in
 \cite{howe1995perspectives} (see also \cite{stembridge2003multiplicity}).
+
+The weight $\mu$ is minuscule if $\left<\mu,\alpha^{\vee}\right>\leq 1$ for all $\alpha\in
+\Delta^{+}$.
+
+Classification of multiplicity-free irreducible highest weight modules $L^{\mu}$ in
+\cite{howe1995perspectives,stembridge2003multiplicity} consists of the following classes:
+\begin{itemize}
+\item (1) $\mu$ is minuscule,
+\item (2) $\mu$ is quasi-minuscule and Lie algebra has only one short simple root,
+\item (3) Lie algebra is $sp(6)$ and $\mu=\omega_{1}$, or
+\item (4) Lie algebra is $sl(n + 1)$ and  $\mu= m\omega_{1}$ or $\mu  = m\omega_{n}$ 
+\end{itemize}
+
+We see that case (1) contains strongly multiplicity free modules of series $A_{r}, B_{r}, C_{r}$ and
+exceptional Lie algebra $G_{2}$, strongly multiplicity free modules of $A_{1}$ are included in class
+(4).
 
@@
 \cite{plotkin1998visual}. It consists of multiplicity-free representations and adjoint
-representations of algebras $B_{r}$.
-
- (Possibly, strongly multiplicity-free:
-).
-
- Classification of strongly multiplicity-free representations is simple:
-$A_{n}$ first fundamental representation, $B_{n}$ first fundamental representation, $C_{n}$ first
-fundamental representation, $G_{2}$ first fundamental representation (7) and
-all irreducible $A_{1}$-representations.
+representations of algebras $B_{r}, C_{r}$ and $F_{4}$.
 

### 2014-12-19 AffineLieAlgebras/Splints/special-paper.tex
More on special splints

@@
 The weight $\mu$ is minuscule if $\left<\mu,\alpha^{\vee}\right>\leq 1$ for all $\alpha\in
-\Delta^{+}$.
+\Delta^{+}$. Equivalently, all the weights of the irreducible representation $L^{\mu}$ lie on Weyl
+group orbit of $\mu$.  Weight is quasi-minuscule if  $\left<\mu,\alpha^{\vee}\right>\leq 2$ for all $\alpha\in
+\Delta^{+}$, this means that all non-zero weights lie on single Weyl group orbit.
 
@@
 
-We see that case (1) contains strongly multiplicity free modules of series $A_{r}, B_{r}, C_{r}$ and
-exceptional Lie algebra $G_{2}$, strongly multiplicity free modules of $A_{1}$ are included in class
-(4).
+We see that case (1) contains strongly multiplicity free modules of series $A_{r}$ and exceptional
+Lie algebra $G_{2}$, class (2) contains strongly multiplicity free modules of $ B_{r}, C_{r}$ ,
+strongly multiplicity free modules of $A_{1}$ are included in class (4).
+
+(From wiki:http://en.wikipedia.org/wiki/Minuscule_representation)
+Each simple Lie algebra has a unique quasi-minuscule representation that is not minuscule, and the
+multiplicity of the zero weight is the number of short nodes of the Dynkin diagram.
+
+The minuscule representations are indexed by the weight lattice modulo the root lattice, or
+equivalently by irreducible representations of the center of the simply connected compact group. For
+the simple Lie algebras, the dimensions of the minuscule representations are given as follows.
+
+    An (n+1
+    k) for 0 ≤ k ≤ n (exterior powers of vector representation). Quasi-minuscule: n2+2n (adjoint)
+    Bn 1 (trivial), 2n (spin). Quasi-minuscule: 2n+1 (vector)
+    Cn 1 (trivial), 2n (vector). Quasi-minuscule: 2n2–n–1 if n>1
+    Dn 1 (trivial), 2n (vector), 2n−1 (half spin), 2n−1 (half spin). Quasi-minuscule: 2n2–n (adjoint)
+    E6 1 , 27, 27. Quasi-minuscule: 78 (adjoint)
+    E7 1, 56. Quasi-minuscule: 133 (adjoint)
+    E8 1. Quasi-minuscule: 248 (adjoint)
+    F4 1. Quasi-minuscule: 26
+    G2 1. Quasi-minuscule: 7
+
+We need to consider representations of class (4) only for $m=1,2$ since root system $\Delta_{\sfr}$
+can have roots of at most two different lengths. In the case $m=1$ we get strongly multiplicity free
+modules of $A_{r}$ which were discussed above. And for algebra $A_{2}$ and $m=2$ the weight diagram
+of representation $L^{2\omega_{1}}_{A_{2}}$ coincides with root system of exceptional Lie algebra
+$G_{2}$. This case appears in the special embedding $A_{2}\to B_{3}$. But for $A_{r}, r>2$ there are
+no root systems that coincide with weight diagram of $L^{2\omega_{1}}_{A_{r}}$.
 
@@
 \cite{plotkin1998visual}. It consists of multiplicity-free representations and adjoint
-representations of algebras $B_{r}, C_{r}$ and $F_{4}$.
+representations of algebras $B_{r}, C_{r}$ and $F_{4}$.  (? check with
+\cite{berenshtein1990multiplicity}).
 

### 2014-12-19 AffineLieAlgebras/Splints/special-presentation.tex
More on special splints

@@
 \usetheme{AnnArbor}
-%\usetheme{Warsaw}
+% \usetheme{Warsaw}
 
-\title[]{Splints of root systems for special Lie subalgebras}
+\title[Special splints]{Splints of root systems for special Lie subalgebras}
 
-\author[]{Polina Kakin, Vladimir Lyakhovsky, \underline{Anton Nazarov}}
+\author[Kakin, Lyakhovsky, Nazarov]{Polina Kakin, Vladimir Lyakhovsky, \underline{Anton Nazarov}}
 
-\institute[]{
+\institute[SPbSU]{
   Department of High Energy and Elementary Particle Physics\\
@@
   \end{Def}
+  To construct an embedding consider some representation $L^{\mu}_{\af}$ as a subspace of Lie algebra $\gf$.
+Get generators of $\af$ as linear combinations of generators of $\gf$.
+To reduce $\gf$-representations project $\gf$ root system to Cartan subalgebra of $\af$.
+
   Properties of special subalgebras \cite {d}
   \begin{itemize}
-    \item Orthogonal projection of algebra $g$ onto root space of subalgebra $a$ contains a root system of subalgebra $a$ 
-    \item Projections of the roots of algebra $g$ are linear combinations of the roots of subalgebra $a$ with integer coefficients.
+  \item Orthogonal projection of algebra $\gf$ onto root space of subalgebra $\af$ contains a root system of subalgebra $\af$ 
+  \item Projections of the roots of algebra $\gf$ are linear combinations of the roots of subalgebra $\af$ with integer coefficients.
   \end{itemize}
@@
 \begin{frame}
-  \frametitle{Orthogonal projection}
+  \frametitle{Orthogonal projection and splint}
   \begin{itemize}
-  \item $\Delta'$ is orthogonal projection of the root system $\Delta_g$ onto the root space of subalgebra $a$
+  \item $\Delta'$ is orthogonal projection of the root system $\Delta_{\gf}$ onto the root space of subalgebra $\af$
     \begin{itemize}
-    \item $\Delta'\supset\Delta_a$
-    \item $\Delta'$ contains some roots of $\Delta_a$ more than once
+    \item $\Delta'\supset\Delta_{\af}$
+    \item $\Delta'$ contains some roots of $\Delta_{\af}$ more than once
     \end{itemize}
-
-  \item $\Phi_g^{(\mu)'}$ is orthogonal projection of the singular element of algebra $g$ onto the root space of subalgebra $a$ 
-  \item $V_{a\rightarrow g}$ is injection fan defined as follows:
-
-    \begin {equation}
-      V_{a\rightarrow g}=\prod_{\Delta'^{+}\setminus \Delta_a^{+}}
-      (1- e^{-\lambda}).
-    \end {equation}
+  \item $\Phi_{\gf}^{(\mu)'}$ is orthogonal projection of the singular element of $\gf$-representation  onto the root space of subalgebra $\af$ 
+  \item $\Delta'\approx\left(\Delta_{\af},\Delta_{\sfr}\right)$ is a special splint
+  \item $\Delta_{\sfr}=\Delta' \backslash \Delta_{\af}$ is a system of vectors
+  \item $W_{\sfr}$ is a group of reflections in hyperplanes orthogonal to the vectors in $\Delta_{\sfr}$
+  \item $W_{inv}$ is a group of reflections in hyperplanes orthogonal to the roots from $\Delta_{\gf}$ that already lie in the root space of subalgebra $\af$.
   \end{itemize}
@@
 \begin{frame}
-  \frametitle{Special splint}
-  \begin{itemize}
-  \item $\Delta'\approx\left(\Delta_a,\Delta_s\right)$ is a special splint
-  \item $\Delta_s=\Delta' \backslash \Delta_a$ is a system of vectors
-    \begin{itemize}
-    \item if $\Delta_s$ is not a root system then singular element $\Phi_s$ is obtained by applying injection fan $V_{a\rightarrow g}$ to the branching coefficients $g\downarrow a$.
-    \end{itemize}
-  \item $W_s$ is a group of reflections in hyperplanes orthogonal to the vectors in $\Delta_s$
-  \item $W_{inv}$ is a group of reflections in hyperplanes orthogonal to the roots from $\Delta_g$ that already lie in the root space of subalgebra $a$.
-  \end{itemize}
+  \frametitle{Examples of root system projections}
+  \begin{multicols}{4}
+    \begin{figure}[h!tb]
+      \includegraphics[width=1.0\linewidth]{Special-A1-A1-A3}      
+      \caption{$A_1+A_1\to A_3$}
+      \label{fig:a1a1a3}
+    \end{figure}
+    \begin{figure}[h!tb]
+      \includegraphics[width=1.0\linewidth]{Special-A2-A5}      
+      \caption{$A_2\to A_5$}
+      \label{fig:a2a5}
+    \end{figure}
+    \begin{figure}[h!tb]
+      \includegraphics[width=1.0\linewidth]{Special-A2-D4}
+      \caption{$A_2\to D_4$}
+      \label{fig:a2d4}
+    \end{figure}
+    \begin{figure}[h!tb]
+      \includegraphics[width=1.0\linewidth]{Special-G2-B3}      
+      \caption{$G_2\to B_3$}
+      \label{fig:g2b3}
+    \end{figure}
+
+  \end{multicols}
+
 \end{frame}
@@
 \section{Types of special splints}
-\begin{frame}
-  \frametitle{Special splints: $\Delta_s\subset\Delta_a$}
-  \begin{Utv}
-    If $\Delta'\approx\left(\Delta_a,\Delta_s\right)$ is a special splint and $\Delta_s\subset\Delta_a$ then:
-
-    $$
-    \Phi_g^{(\mu)'}=\sum_{w\in W_{inv}} \epsilon (w) w(1+\sigma_1+\dots)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\tilde{\rho_s}}\Phi_s^{(\tilde{\mu})}),
-    $$
-    \begin{itemize}
-      \item where $\sigma_1+\dots$ are elements of the group $W_s$ that move $\Phi_s^{(\tilde{\mu})}$ to the next Weyl chamber of subalgebra $a$.
+%% \begin{frame}
+%%   \frametitle{Special splints: $\Delta_s\subset\Delta_a$}
+%%   \begin{Utv}
+%%     If $\Delta'\approx\left(\Delta_a,\Delta_s\right)$ is a special splint and $\Delta_s\subset\Delta_a$ then:
+%%     
+%%     $$
+%%     \Phi_g^{(\mu)'}=\sum_{w\in W_{inv}} \epsilon (w) w(1+\sigma_1+\dots)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\tilde{\rho_s}}\Phi_s^{(\tilde{\mu})}),
+%%     $$
+%%     \begin{itemize}
+%%     \item where $\sigma_1+\dots$ are elements of the group $W_s$ that move $\Phi_s^{(\tilde{\mu})}$ to the next Weyl chamber of subalgebra $a$.
 The number of elements is equal to the number of the fundamental Weyl chamber of subalgebra $a$ one needs to fill the fundamental Weyl chamber of the group $W_{inv}$.
-
-      \item The vector $\hat\mu+\hat\rho_g$ is vector of the highest lenght in the projection of the singular element $\Phi_g^{(\mu)'}$ with positive multiplicity.
-      \end{itemize}
-    \label{u3}
-  \end{Utv}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Special splints: $\Delta_a\subset\Delta_s$}
-  \begin{Utv}
-    If $\Delta'\approx\left(\Delta_a,\Delta_s\right)$ is a special splint and $\Delta_a\subset\Delta_s$ while $W_{inv}\subset\Delta_a$ then:
-
-    $$
-    \Phi_g^{(\mu)'}=\sum_{w\in W_{inv}} \epsilon (w) w(1+\sigma_1+\dots)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\rho_s}\Phi_s^{(\tilde{\mu})});
-    $$
-    if there is no $W_{inv}$ or $W_{inv}\not\subset W_a$ then:
-    $$
-    \Phi_g^{(\mu)'}=(2-\sum_{w\in W_a} \epsilon (w) w)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\rho_s}\Phi_s^{(\tilde{\mu})}).
-    $$
-    \label{u2}
-  \end{Utv}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Special splints and branching coefficients}
-  \begin{Sl}
-    If $\Phi_s^{(\tilde{\mu})}$ can be put in the fundamental Weyl chamber $\bar C_a$ of subalgebra $a$ then by applying injection fan to the singular element $\Phi_s^{(\tilde{\mu})}$ one obtains $M_{s (\tilde{\nu})}^{(\tilde{\mu})}=b_{(\mu-\tilde{\mu}+\tilde{\nu})}^{(\mu)}$.
-If $\Phi_s^{(\tilde{\mu})}$ can not be put in $\bar C_a$ then $b_{(\mu-\tilde{\mu}+\tilde{\nu})}^{(\mu)}=N_{(\tilde{\nu})}$ where $N_{(\tilde{\nu})}$ are as follows: $$V_{a\rightarrow g}^{-1}(1+\sigma_1+\dots)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\rho_s}\Phi_s^{(\tilde{\mu})}))=\sum_{\tilde{\nu}} N_{(\tilde{\nu})}e^{\tilde{\mu}}.$$
-    In both cases $\tilde{\nu}\in\bar C_a$ and the fundamental Weyl chamber $\bar C_a$ begins in the point $\tilde{\mu}-\mu$.
-    \label{u31}
-  \end{Sl}
-
-\end{frame}
+%%       
+%%     \item The vector $\hat\mu+\hat\rho_g$ is vector of the highest lenght in the projection of the singular element $\Phi_g^{(\mu)'}$ with positive multiplicity.
+%%     \end{itemize}
+%%     \label{u3}
+%%   \end{Utv}
+%% \end{frame}
+%% 
+%% \begin{frame}
+%%   \frametitle{Special splints: $\Delta_a\subset\Delta_s$}
+%%   \begin{Utv}
+%%     If $\Delta'\approx\left(\Delta_a,\Delta_s\right)$ is a special splint and $\Delta_a\subset\Delta_s$ while $W_{inv}\subset\Delta_a$ then:
+%%     
+%%     $$
+%%     \Phi_g^{(\mu)'}=\sum_{w\in W_{inv}} \epsilon (w) w(1+\sigma_1+\dots)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\rho_s}\Phi_s^{(\tilde{\mu})});
+%%     $$
+%%     if there is no $W_{inv}$ or $W_{inv}\not\subset W_a$ then:
+%%     $$
+%%     \Phi_g^{(\mu)'}=(2-\sum_{w\in W_a} \epsilon (w) w)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\rho_s}\Phi_s^{(\tilde{\mu})}).
+%%     $$
+%%     \label{u2}
+%%   \end{Utv}
+%% \end{frame}
+%%
 
@@
       \hline
-      Type & $s$ & $W_a\subset W_s$ & $W_s\subset W_a$ & $W_{inv} $ & Examples \\
+      Type & $s$ & $W_{\af}\subset W_{\sfr}$ & $W_{\sfr}\subset W_{\af}$ & $W_{inv} $ & Examples \\
       \hline
@@
       \hline
-      6 & \multicolumn{4}{|l|}{$W_a\not\subset W_s$ and $W_s\not\subset W_a$} & $B_2\rightarrow D_4$\\
+      6 & \multicolumn{4}{|l|}{$W_{\af}\not\subset W_{\sfr}$ and $W_{\sfr}\not\subset W_{\af}$} & $B_2\rightarrow D_4$\\
       \hline
@@
     \label {spsp}
+    In first three cases coincidence of branching coefficients with weight multiplicities of $\sfr$-representations takes place. 
   \end{table}
+\end{frame}
 
-\end{frame}
+%%   \begin{frame}
+%%     \frametitle{Special splints and branching coefficients}
+%%     \begin{Sl}
+%%       If $\Phi_s^{(\tilde{\mu})}$ can be put in the fundamental Weyl chamber $\bar C_a$ of subalgebra $a$ then by applying injection fan to the singular element $\Phi_s^{(\tilde{\mu})}$ one obtains $M_{s (\tilde{\nu})}^{(\tilde{\mu})}=b_{(\mu-\tilde{\mu}+\tilde{\nu})}^{(\mu)}$.
+If $\Phi_s^{(\tilde{\mu})}$ can not be put in $\bar C_a$ then $b_{(\mu-\tilde{\mu}+\tilde{\nu})}^{(\mu)}=N_{(\tilde{\nu})}$ where $N_{(\tilde{\nu})}$ are as follows: $$V_{a\rightarrow g}^{-1}(1+\sigma_1+\dots)(e^{\hat\mu+\hat\rho_g-\tilde{\mu}-\rho_s}\Phi_s^{(\tilde{\mu})}))=\sum_{\tilde{\nu}} N_{(\tilde{\nu})}e^{\tilde{\mu}}.$$
+%%       In both cases $\tilde{\nu}\in\bar C_a$ and the fundamental Weyl chamber $\bar C_a$ begins in the point $\tilde{\mu}-\mu$.
+%%       \label{u31}
+%%     \end{Sl}
+%% 
+%% 
+%%   \end{frame}
+%% 
+%%
 
@@
     \center{\includegraphics[width=0.4\linewidth]{drawing-2}}
-    \caption{Splint $D_3\approx (A_1+A_1,B_2)$: projection of the singular element $\Phi_{D_3}^{([1,1,2])'}$ can be made from singular elements $\Phi_{B_2}^{([1,2])}$ (one of then is marked with grey colour).}
+    \caption{Splint $D_3\approx (A_1+A_1,B_2)$: projection of the singular element $\Phi_{D_3}^{([1,1,2])'}$ can be made from singular elements $\Phi_{B_2}^{([1,2])}$ (one of them is marked with grey colour).}
     \label{ris4}
@@
 \begin{frame}
+  \frametitle{Towards classification of splints for special embeddings}
+  \begin{itemize}
+  \item Number of special embeddings is infinite: arbitrary algebra $\gf$, $\af$-representation
+  \item Splints are rare
+  \item We can use Dynkin diagrams with multiplicities for projections
+  \item Diagrams of the same rank as $\af$ should be considered, root multiplicities less or equal to 2
+  \end{itemize}
+\vspace{-0.3cm}
+  \begin{multicols}{4}
+    \begin{figure}[h!tb]
+      \includegraphics[width=1.0\linewidth]{Special-A1-A1-A3}      \\
+      \includegraphics[width=0.8\linewidth]{A1A1A3}      
+      \caption{$A_1+A_1\to A_3$}
+      \label{fig:a1a1a3}
+    \end{figure}
+    \begin{figure}[h!tb]
+      \includegraphics[width=1.0\linewidth]{Special-A2-A5}      \\
+      \includegraphics[width=0.8\linewidth]{A2A5}      \vspace{-0.3cm}
+      \caption{$A_2\to A_5$}
+      \label{fig:a2a5}
+    \end{figure}\par
+    \begin{figure}[h!tb]
+      \includegraphics[width=1.0\linewidth]{Special-A2-D4}\\
+      \includegraphics[width=0.8\linewidth]{A2D4}      
+      \caption{$A_2\to D_4$}
+      \label{fig:a2d4}
+    \end{figure}
+    \begin{figure}[h!tb]
+      \includegraphics[width=0.8\linewidth]{Special-G2-B3}      \\
+      \includegraphics[width=0.8\linewidth]{G2B3}      \vspace{-0.2cm}
+      \caption{$G_2\to B_3$}
+      \label{fig:g2b3}
+    \end{figure}
+
+  \end{multicols}
+
+\end{frame}
+\section{Conclusion}
+
+\begin{frame}
   \frametitle{Conclusion}
@@
   \item The concept of splint was generalised on the case of special embedding.
-  \item Decomposition of the projection of the singular element of splintered algebra was found for both the case when one of the stems is not a root system and the case when it is.
   \item The way to simplify calculation of branching coefficients was found for the case when both stems are root systems.
-  \item All special splints were arranged into types and some of the types were thoroughly studied.
-  \item The definition of singular element for the vector system that is not a root system was suggested.
-  \item Together with the newly defined injection fan it might serve as the base for representation theory of such systems.
-  \item The type of special splints where neither of stems contains the other requires further research.
+  \item Some generalization of Dynkin diagrams can be useful. 
   \end{itemize}

### 2014-12-19 AffineLieAlgebras/Splints/special-paper.tex
More on splints

@@
 
-(From wiki:http://en.wikipedia.org/wiki/Minuscule_representation)
+(From wiki:\url{http://en.wikipedia.org/wiki/Minuscule_representation})
 Each simple Lie algebra has a unique quasi-minuscule representation that is not minuscule, and the
@@
 \cite{plotkin1998visual}. It consists of multiplicity-free representations and adjoint
-representations of algebras $B_{r}, C_{r}$ and $F_{4}$.  (? check with
+representations of algebras $A_{r}, B_{r}, C_{r}$ and $F_{4}$.  (? check with
 \cite{berenshtein1990multiplicity}).
 
+For adjoint representation of algebra $A_{r}$ we see that projection $\Delta'$ of root system
+$\Delta_{\gf}$ should consist of roots of subalgebra $\af=A_{r}$ with multiplicity 2. This is the
+case for $\gf=A_{r+1}$, so for the special embedding $A_{r}\to A_{r+1} (su(r+1)\to su(r+2))$ we get
+a splint.
+
 (See also https://projecteuclid.org/euclid.jmsj/1180135505 for multiplicity-free branching rules)
+%% 
+%% Having obtained this classification we need to check which weight diagrams can be obtained as the
+%% projections of $\gf$ root system. It is the case for $B_{n}\to D_{n+1}$ or $A_{1}\oplus\dots\oplus
+%% A_{1}\to D_{n+1}$.
+%% 
+%% 
+%% 
+%% Projection of $\gf$ root system to the root space of $\af$ in many cases can be
+%% encoded by augmented Dynkin diagram with simple root multiplicities not greater or equal than 1.
+%% Number of roots in projection is equal to the number of roots in $\gf$ root system (We do
+%% not consider the case of orthogonal roots here). The rank of augmented Dynkin diagram is the same as
+%% the rank of subalgebra $\af$. Having Lie algebra $\af$ and augmented Dynkin
+%% diagram of the same rank it should be possible to reconstruct the embedding $\af\to
+%% \gf$, though not always in a unique way. 
+%% 
+%% We must also account for the case of roots of parallel roots of different length. $BC_{1} $ is the
+%% simplest system with parallel roots, one of its two parallel is twice longer than another. Such a
+%% system appear in study of affine 
+%% 
+%% 
+%%  The simplest
+%% system with parallel roots have roots of two different length and Such a systems
+%% appear  $BC_{1} $ and its generalization. (We have the dimension of representation of $\af$ and
+%% projection of roots of $\gf$. It's not enough since in general there are different non-equivalent
+%% representations of $\af$. But the number of simple root systems with given number of roots is
+%% finite, so it's possible to check which one has given projection).
+%% 
+%% Classification of all splints for special embeddings of a given algebra $\af$ is given by
+%% the augmented Dynkin diagrams of the same rank. (!)
+%% 
+%% Case of diagrams with multiplicities is not particularly interesting since we have just multiple
+%% copies of the same stem (?).
+%%
 
-Having obtained this classification we need to check which weight diagrams can be obtained as the
-projections of $\gf$ root system. It is the case for $B_{n}\to D_{n+1}$ or $A_{1}\oplus\dots\oplus
-A_{1}\to D_{n+1}$.
-
-Projection of $\gf$ root system to the root space of $\af$ in many cases can be
-encoded by augmented Dynkin diagram with simple root multiplicities not greater or equal than 1.
-Number of roots in projection is equal to the number of roots in $\gf$ root system (We do
-not consider the case of orthogonal roots here). The rank of augmented Dynkin diagram is the same as
-the rank of subalgebra $\af$. Having Lie algebra $\af$ and augmented Dynkin
-diagram of the same rank it should be possible to reconstruct the embedding $\af\to
-\gf$, though not always in a unique way.
-
-We must also account for the case of roots of parallel roots of different length. $BC_{1} $ is the
-simplest system with parallel roots, one of its two parallel is twice longer than another. Such a
-system appear in study of affine
-
- The simplest
-system with parallel roots have roots of two different length and Such a systems
-appear  $BC_{1} $ and its generalization. (We have the dimension of representation of $\af$ and
-projection of roots of $\gf$. It's not enough since in general there are different non-equivalent
-representations of $\af$. But the number of simple root systems with given number of roots is
-finite, so it's possible to check which one has given projection).
-
-Classification of all splints for special embeddings of a given algebra $\af$ is given by
-the augmented Dynkin diagrams of the same rank. (!)
-
-Case of diagrams with multiplicities is not particularly interesting since we have just multiple
-copies of the same stem (?).
+Having obtained the complete classification of splints of projections of root system for special
+embeddings, we need to check when such splints lead to the coincidence of branching coefficients
+with weight multiplicities in modules of algebra $\sfr$. This depends on the decomposition of
+projection of singular element $\pi_{\af}\left(\Psi^{\mu}_{\gf}\right)$ into the combination of
+singular elements of subalgebra $\sfr$. Relation between Weyl groups of $\af$ and $\sfr$ is crucial
+here.
 
@@
 
+As the result we see that branching coefficients coincide with weight multiplicities for
+the embeddings $something\to something$ and do not coincide for $something else\to something else$.
+
 \section*{Conclusion}
 \label{sec:conclusion}
+
+Computation of branching coefficients is important for different physical models with symmetry
+breaking. This computation is drastically simplified if branching coefficients coincide with weight
+multiplicities, since efficient Freudental formula can be used \cite{moody1982fast}. Classification
+of splints for regular and special embeddings gives us all the cases when this coincidence takes
+place. Aside from computational importance, this coincidence is very interesting from
+representation-theoretic point of view, because it follows from new unexpected connection between
+different simple Lie algebras.
 

### 2015-01-08 AffineLieAlgebras/Splints/special-paper.tex
Classification of special splints is completed

@@
 as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.
+
+Why one would consider non angle-preserving maps of root systems? Additive properties of root system
+determine the structure of Verma module:
+    \begin{equation*}
+      M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+})=\{(E^{-\alpha_{1}})^{n_{1}}\dots (E^{-\alpha_{s}})^{n_{s}} \left|v_{\mu}\right>\}_{\alpha_{i}\in\Delta^{+}}^{n_{i}=0,1,\dots}
+    \end{equation*}
+Here $\bff_{+}$ is the Borel subalgebra and $D^{\mu}$ its one-dimensional representation. 
+Weyl character formula expresses character of irreducible representation as a combination of
+characters of Verma modules: 
+\begin{equation*}
+  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \varepsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\varepsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \varepsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
+\end{equation*}
+Here the sum is over elements of Weyl group and their actions $w\triangleright \mu
+=w(\mu+\rho)-\rho$ depend on angles between roots. But we can rewrite Weyl character formula
+representing Weyl group elements as the products of reflections $s_{\alpha}, \alpha \in S$ in
+hyperplanes orthogonal to simple roots: $w=s_{\alpha_{1}}\cdot s_{\alpha_{2}}\dots$. Reflections act
+on root system by permutations, so the composition of such an action with embedding $\phi$ is easily
+obtained. The orbit of Weyl groups action $w\triangleright \mu, w\in W$ can be constructed by
+subtractions of roots from the highest weight $\mu$. Let's denote Dynkin labels of $\mu$ by
+$(\mu_{1},\dots \mu_{r})$. Then $\mu-\mu_{1}\alpha_{1}, \mu-\mu_{2}\alpha_{2},\dots,
+\mu-\mu_{r}\alpha_{r}, \alpha_{i}\in S$ are the points of the orbit that can be obtained by
+elementary reflections $s_{\alpha_{i}}, \alpha_{i}\in S$. Next set of points that are obtained by
+two consecutive reflections $s_{\alpha_{i}}\cdot s_{\alpha_{j}}\triangleright\mu$ are obtained as
+the subtraction $\mu-\mu_{i}\alpha_{i}-\mu_{j} (s_{\alpha_{i}}\alpha_{j})$. Continuing this way we
+construct the image of singular element $\Psi=\sum_{w\in W} \varepsilon(w) e^{w(\mu+\rho)-\rho}$
+after the embedding $\phi$ \cite{2011arXiv1111.6787L}. The multiplicities in the character of Verma
+module are unchanged by the embedding since they are determined by additive properties of the roots.
+So we see that weight multiplicities of irreducible modules are also preserved by the embedding.
 
@@
 \hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
-_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
+_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\sfr}\hspace{0.25in}
 \\ \hline\hline
@@
 
-Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\frak{s}})
+Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\sfr})
 $ of the simple root system $\Delta $. In the first two types both $\Delta _{%
-\frak{a}}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
+\frak{a}}$ and $\Delta _{\sfr}$ are embedded metrically. Stems in the
 first type splints are equivalent and in the second are not. In the third
@@
 the principle properties of branching but makes it possible to use the
-multiplicities of $\frak{s}$ -modules without further projecting their
+multiplicities of $\sfr$ -modules without further projecting their
 weights.
@@
 \begin{equation}
-\frac{e^{\rho _{\frak{g}}}}{\prod_{\beta \in \Delta _{\frak{s}%
-}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\frak{s}%
-}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }%
-}}M_{\left( \frak{s}\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
+\frac{e^{\rho _{\gf}}}{\prod_{\beta \in \Delta _{\sfr%
+}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\sfr%
+}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\sfr}^{\widetilde{\mu }%
+}}M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
 \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
@@
 \end{equation}
+
+Actually:
+\begin{equation}
+\frac{e^{\rho _{\frak{a}}-\rho _{\gf}}}{\prod_{\beta \in \Delta _{\sfr%
+}^{+}}(1-e^{-\beta })}\left( \Phi ^{\mu }_{\gf}\right) = \frac{e^{\rho _{\frak{a}}-\rho _{\gf}}}{\prod_{\beta \in \Delta _{\sfr%
+}^{+}}(1-e^{-\beta })}\left( e^{\mu +\rho _{\gf}}\phi\left( e^{-\widetilde{\mu }}\Psi^{\widetilde{\mu }}_{\sfr}\right)\right) = 
+\end{equation}
+
+\begin{equation}
+= e^{\rho _{\frak{a}}+\mu-\phi\left(\widetilde{\mu }\right)}\phi\left(ch L_s^{\widetilde{\mu }}\right) = e^{\rho _{\frak{a}}+\mu-\phi\left(\widetilde{\mu }\right)}\sum_{\widetilde{\nu }\in \mathcal{N}_{\sfr}^{\widetilde{\mu }%
+}}M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
+\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)} =\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}\Phi_a^{\left(\nu\right)}.
+\end{equation}
+
 Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
-highest weights in the decomposition. The multiplicity $M_{\left( \frak{s}%
+highest weights in the decomposition. The multiplicity $M_{\left( \sfr%
 \right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
-}\in \mathcal{N}_{\frak{s}}^{\widetilde{\mu }}$ defines the branching
+}\in \mathcal{N}_{\sfr}^{\widetilde{\mu }}$ defines the branching
 coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
@@
 projection of $\gf$ root system $\Delta_{\gf}$ to $\hfa^{*}$ is a weight system of some
-finite-dimensional but not irreducible representation of $\af$. Moreover, roots of $\af$ are
-contained in this projection. We denote such a projection by
+finite-dimensional but not irreducible representation of $\af$.  We denote such a projection by
 \begin{equation}
   \label{eq:2}
-  \Delta'=\pi_{\af}\left(\Delta_{\gf}\right)
+  \Delta'=\pia\left(\Delta_{\gf}\right)
 \end{equation}
@@
 
-To
+Several theorems from \cite{dynkin1952semisimple} are useful to us.
 
 \begin{theorem}\label{dyn0}
-  If representation $\phi$ of algebra $g$ induces representation $\tilde\phi$ on subalgebra $a$ then
+  If representation $\phi$ of algebra $\gf$ induces representation $\tilde\phi$ on subalgebra $\af$ then
   the weight system of representation $\tilde\phi$ can be obtained from representation $\phi$ by
-  orthogonal projection of the weight space of algebra $g$ on the weight space of subalgebra $a$
+  orthogonal projection of the weight space of algebra $\gf$ on the weight space of subalgebra $\af$
 
@@
 
-Applying this theorem
-В приложении к присоединенному представлению эта теорема означает, что в ортогональной проекции
-корневой системы алгебры $g$ на корневое пространство подалгебры $a$ содержится корневая система
-подалгебры $a$. Более того, верна следующая теорема:
+Applying this theorem to the adjoint representation of $\gf$ we see that the roots of $\af$ are
+contained in the projection $\Delta'$ of root system $\Delta_{\gf}$.
 
+Moreover, the following theorems hold. 
 \begin{theorem}\label{dyn1}
-Всякая специальная подалгебра $a$ полупростой алгебры $g$ целочисленна, то есть проекции корней алгебры $g$ при ортогональной проекции на корневое пространство алгебры $a$ являются линейными комбинациями с целочисленными коэффициентами простых корней алгебры $a$ \cite{dynkin1972semisimple,dynkin1952semisimple}.
-%(стр.397 в d1)
+  Every special subalgebra $\af$ of semisimple Lie algebra $\gf$ is integer, i.e. projections of
+  roots of $\gf$ to $\hfa^{*}$ are linear combinations of simple roots of $\af$ with integer
+  coefficients \cite{dynkin1952semisimple}
 \end{theorem}
@@
 \begin{theorem}\label{dyn2}
-  Пусть $a$ - полупростая подалгебра полупростой алгебры $g$. Генератор, соответствующий корню
-  $\lambda$ подалгебры $a$, раскладывается по базису Картана алгебры $g$ в линейную комбинации
-  генераторов, соответствующих корням алгебры $g$. При ортогональном проектировании корневого
-  пространства алгебры $g$ на корневое пространство подалгебры $a$ корни алгебры $g$ из указанной
-  линейной комбинации спроектируются в корень $\lambda$
-
-  \cite{dynkin1972semisimple,dynkin1952semisimple}. %(Требует проверки, так как сформулировано в туманных и устаревших терминах, см. стр.378 в d1)
+  If $\af$  is semisimple subalgebra of semisimple Lie algebra $\gf$ and generator $e_{\alpha}$ corresponding to
+  a root $\alpha$ of subalgebra $\af$ is presented as a linear combination $e_{\alpha}=\sum_{\beta}
+  e_{\beta}$ of $\gf$-generators
+  corresponding to roots $\beta$ of $\gf$, then the roots $\beta$ are projected into $\alpha$,
+  $\pia(\beta)=\alpha$. 
+  \cite{dynkin1972semisimple,dynkin1952semisimple}. 
 \end{theorem}
 
-Обозначим проекцию корневой системы $\Delta$ алгебры $g$ через $\Delta'$. Согласно теоремам \ref
-{dyn0} и \ref {dyn2}, $\Delta'$ будет состоять из корневой системы $\Delta_a$ и векторов - линейных
-комбинаций корней из $\Delta_a$ с целочисленными коэффициентами. Более того, из теоремы \ref {dyn0}
-следует, что $\Delta'$ будет содержать какие-то корни из $\Delta_a$ больше одного раза.
-Действительно, если бы все генераторы подалгебры $a$ совпадали с какими-то генераторами алгебры $g$,
-то корневую систему $\Delta_a$ можно было бы отождествить с частью корневой системы $\Delta$. То
-есть подалгебра $a$ была бы регулярной. Значит, в подалгебре $a$ есть генераторы, равные линейной
-комбинации генераторов алгебры $g$ по крайней мере с двумя коэффицентами, не равными нулю. Корни,
-соответствующие генераторам из этой линейной комбинации с ненулевыми коэффициентами, спроектируются
-в один и тот же корень подалгебры $a$. То есть, хотя бы одна пара корней подалгебры $a$ будет
-входить в $\Delta'$ более одного раза.
+From these theorems we see that the root system $\Delta_{\af}$ is metrically embedded (in the sense
+of splint) into the projection $\Delta'$. Moreover, the multiplicities of some roots
+$\alpha\in\Delta_{\af}$ in this projection $\Delta'$ are greater than one.
 
-Получается, что в результате проекции возникает объект $\Delta'$, в который метрически вложена
-$\Delta_a$, и в котром есть кратные корни с коэффициентом кратности не равным единице.
-
-Example here (something like $A_2\to D_{4}$)
+As an example we present a projection $\Delta'$ of root system $D_{4}$ to root system of special
+subalgebra $A_{2}$ (Fig. \ref{fig:d4-a2_splint}).
 
@@
 \varphi_{\sfr}(\Delta_{\sfr})$, where $\varphi_{\af}$ and $\varphi_{\sfr}$ are the embeddings of
-corresponding root systems. The embedding $\varphi_{\af}$ is metric and trivial. Projection of the
-root system $\Delta'$ coincides with the projection of weight diagram of the adjoint representation
-of algebra $\gf$ with the exception of zero weight. Adjoint representation of $\gf$ contains adjoint
-representation of $\af$ and can be decomposed as
+corresponding root systems. The embedding $\varphi_{\af}$ is metric and trivial. Moreover, the
+projection of singular element $\pia\left(\Psi^{\mu}\right)$ should admit a decomposition into
+linear combination of singular elements of irreducible representations of $\sfr$:
+\begin{equation}
+  \label{eq:4}
+  \pia\left(\Psi^{\mu}_{\gf}\right)=\sum_{\nu} \Psi^{\nu}_{\sfr}.
+\end{equation}
+First we classify all the splints
+of the projection of root system into union of simple root systems for special embeddings, and then
+discuss the decomposition of singular elements.
+
+Projection of the root system $\Delta'$ coincides with the projection of weight diagram of the
+adjoint representation of algebra $\gf$ with the exception of zero weight. Adjoint representation of
+$\gf$ contains adjoint representation of $\af$ and can be decomposed as
 \begin{equation}
@@
 zero weight. So we need to find all the representations for all simple Lie algebras $\af$, such that
-their weight diagrams are root systems after the exclusion of zero weight.
+their weight diagrams are root systems after the exclusion of zero weight. In order to do so we must
+note, that all the weights of $M^{\chi}_{\af}$ should have length not less than length of shortest
+root of $\af$, since $\af$ is an integer subalgebra of $\gf$ \ref{dyn1}. Moreover, $M^{\chi}_{\af}$
+should contain weights of at most two different lengths.
+
+If root system $\Delta_{\gf}$ contains roots $\alpha: \alpha\perp \beta,\; \forall \beta\in
+\Delta_{\af}$ orthogonal to root system of the subalgebra, one cannot proceed with the decomposition
+of singular element \eqref{eq:4}. The elements $e^{\nu}$ of $\pia\left(\Psi^{\mu}_{\gf}\right)$
+should be augmented with the dimensions of representations of algebra $\afb$ spanned by generators
+corresponding to orthogonal roots \cite{2010arXiv1007.0318L}. Then there will be non-trivial
+multiplicities in the right hand side of \eqref{eq:4} and no coincidence of branching coefficients
+with weight multiplicities of $\sfr$-representations. One can write more cumbersome relation between
+multiplicities and branching coefficients, but it is out of scope for the present paper.
 
 Multiplicity of zero weight in adjoint representation is equal to the rank of the algebra. So if
-$\mathrm{rank}\gf-\mathrm{rank}\af$, the representations in questions must be multiplicity-free.
+$\mathrm{rank}\gf-\mathrm{rank}\af=1$, the representation in question $M^{\chi}_{\af}$ must be
+multiplicity-free. If $\mathrm{rank}\gf-\mathrm{rank}\af>1$ only zero weight can have non-trivial
+multiplicities.
 
@@
 \Delta_{D_{r+1}}\right) = \Delta_{B_{r}}\cup \Delta_{A_{1}+\dots+A_{1}}$ corresponding to Gelfand-Tsetlin
-multiplicity-free branching for the embedding $so(2r+1)\to so(2r+2)$.
+multiplicity-free branching for the embedding $\mathfrak{so}(2r+1)\to \mathfrak{so}(2r+2)$.
 
-First fundamental representation of $C_{r}$ -?
+The length of the first fundamental weight of  $C_{r}$ is less than length of its short root, so
+this case can not correspond to integer subalgebra.
 
-Projection $\Delta'$ on the subalgebra $A_{1}$ is never multiplicity free, so $\Delta_{\sfr}$ always
-contain parallel roots. The simplest case is special embedding $A_{1}\to A_{2}$ where
-$\Delta_{\sfr}$ is the root system $BC_{1}$. Such systems do not correspond to semisimple Lie
-algebras, so we can not speak of a coincidence of branching coefficients for the reduction
-$\gf\downarrow \af$ with weight multiplicities of $\sfr$-representations.
+If there are vectors of different length in the projection $\Delta'$ on the subalgebra $A_{1}$, such a
+projection is not multiplicity free, and $\Delta_{\sfr}$ contains parallel roots. The simplest case
+is the special embedding $A_{1}\to A_{2}$ with index 4 where $\Delta_{\sfr}$ is the root system
+$BC_{1}$. Such systems do not correspond to semisimple Lie algebras, so we can not speak of a
+coincidence of branching coefficients for the reduction $\gf\downarrow \af$ with weight
+multiplicities of $\sfr$-representations.
 
+%% The only case of the projection $\Delta'$ to $A_{1}$ with root multiplicities not greater than 2 is
+%% special embedding $A_{1}\to A_{2}$ with index 1 given by 
+%% 
 Weight diagram of of seven-dimensional representation of $G_{2}$ together with $G_{2}$ root system
@@
 The complete classification of multiplicity-free irreducible representations was obtained in
-\cite{howe1995perspectives} (see also \cite{stembridge2003multiplicity}).
+\cite{howe1995perspectives} (see also \cite{stembridge2003multiplicity}). It consists of minuscule
+and quasi-minuscule representations.
 
 The weight $\mu$ is minuscule if $\left<\mu,\alpha^{\vee}\right>\leq 1$ for all $\alpha\in
-\Delta^{+}$. Equivalently, all the weights of the irreducible representation $L^{\mu}$ lie on Weyl
-group orbit of $\mu$.  Weight is quasi-minuscule if  $\left<\mu,\alpha^{\vee}\right>\leq 2$ for all $\alpha\in
-\Delta^{+}$, this means that all non-zero weights lie on single Weyl group orbit.
+\Delta^{+}$ and all the weights of the irreducible representation $L^{\mu}$ lie on Weyl
+group orbit of $\mu$. Weight is quasi-minuscule if $\left<\mu,\alpha^{\vee}\right>\leq 2$ for all
+$\alpha\in \Delta^{+}$ and all non-zero weights lie on single Weyl group orbit.
+
+Minuscule representations are well-studied and very useful in computations of e.g. tensor products
+\cite{stembridge2003multiplicity,stembridge2001computational}. The minuscule representations are
+indexed by the weight lattice modulo the root lattice. There is a unique quasi-minuscule
+representation that is not minuscule for each simple Lie algebra. The multiplicity of the zero 
+weight in quasi-minuscule representation is the number of short nodes of the Dynkin diagram.
+
+List of minuscule representations consists of tensor powers of vector
+representation for the series $A_{r}$; spin representations for the series
+$B_{r}$; vector representations for $C_{r}$; vector, and two half-spin for $D_{r}$; two
+27-dimensional representations for $E_{6}$ and 56-dimensional representation of $E_{7}$.
+
+Quasi-minuscule representations that are not minuscule are: adjoint representation of $A_{r}$,
+vector representation for $B_{r}$, $2r^{2}-r-1$-dimensional representation for $C_{r}$, adjoint
+representations for $D_{r}, E_{6}, E_{7}, E_{8}$, 26-dimensional representation for $F_{4}$ and
+7-dimensional of $G_{2}$.
+
+%% 
+%%     An (n+1
+%%     k) for 0 ≤ k ≤ n (exterior powers of vector representation). Quasi-minuscule: n2+2n (adjoint)
+%%     Bn 1 (trivial), 2n (spin). Quasi-minuscule: 2n+1 (vector)
+%%     Cn 1 (trivial), 2n (vector). Quasi-minuscule: 2n2–n–1 if n>1
+%%     Dn 1 (trivial), 2n (vector), 2n−1 (half spin), 2n−1 (half spin). Quasi-minuscule: 2n2–n (adjoint)
+%%     E6 1 , 27, 27. Quasi-minuscule: 78 (adjoint)
+%%     E7 1, 56. Quasi-minuscule: 133 (adjoint)
+%%     E8 1. Quasi-minuscule: 248 (adjoint)
+%%     F4 1. Quasi-minuscule: 26
+%%     G2 1. Quasi-minuscule: 7
+%% 
+%%
 
@@
 \item (2) $\mu$ is quasi-minuscule and Lie algebra has only one short simple root,
-\item (3) Lie algebra is $sp(6)$ and $\mu=\omega_{1}$, or
-\item (4) Lie algebra is $sl(n + 1)$ and  $\mu= m\omega_{1}$ or $\mu  = m\omega_{n}$ 
+\item (3) Lie algebra is $\mathfrak{sp}(6)$ and $\mu=\omega_{1}$, or
+\item (4) Lie algebra is $\mathfrak{sl}(n + 1)$ and  $\mu= m\omega_{1}$ or $\mu  = m\omega_{n}$ 
 \end{itemize}
@@
 
-(From wiki:\url{http://en.wikipedia.org/wiki/Minuscule_representation})
-Each simple Lie algebra has a unique quasi-minuscule representation that is not minuscule, and the
-multiplicity of the zero weight is the number of short nodes of the Dynkin diagram.
+We do not need to consider minuscule representations for simply-laced Lie algebras, since in this
+case length of the weights of representation $M^{\chi}_{\af}$ is less than length of $\af$ roots,
+that contradicts to $\af$ being an integer subalgebra. For the series $B_{r}$ we have already
+discussed minuscule spin representation, since it is strongly multiplicity free. The last case in
+(1) is the vector representation for $C_{r}$. It is $2r$-dimensional, but the length of its highest weight $\omega_{1}$ is less
+than length of the short root of algebra $C_{r}$. So it can not be a characteristic representation
+for the special subalgebra.
 
-The minuscule representations are indexed by the weight lattice modulo the root lattice, or
-equivalently by irreducible representations of the center of the simply connected compact group. For
-the simple Lie algebras, the dimensions of the minuscule representations are given as follows.
+%% , so with the dimension of the
+%% adjoint representation we get $2r+2r^{2}=2r(r+1)$ which is exactly the dimension of the adjoint
+%% representation for the algebra $D_{r+1}$.  
+%% But there is no such embedding (?).
+%% 
+Case (2) consists of the series $B_{r}$ and exceptional root system $G_{2}$. The embedding $G_{2}\to
+B_{3}$ was already discussed. 
+For the series $B_{r}$ we the dimension of the adjoint representation
+is $2r^{2}+r$ and of quasi-minuscule representation it is $2r+1$, so the dimension of the algebra
+$\gf$ should be $(r+1)(2r+1)$ with the $\mathrm{rank}\gf=r+1$. The only solution is $\gf=D_{r+1}$
+and we have already seen that this case corresponds to strongly multiplicity free module and
+Gelfand-Tsetlin basis.
 
-    An (n+1
-    k) for 0 ≤ k ≤ n (exterior powers of vector representation). Quasi-minuscule: n2+2n (adjoint)
-    Bn 1 (trivial), 2n (spin). Quasi-minuscule: 2n+1 (vector)
-    Cn 1 (trivial), 2n (vector). Quasi-minuscule: 2n2–n–1 if n>1
-    Dn 1 (trivial), 2n (vector), 2n−1 (half spin), 2n−1 (half spin). Quasi-minuscule: 2n2–n (adjoint)
-    E6 1 , 27, 27. Quasi-minuscule: 78 (adjoint)
-    E7 1, 56. Quasi-minuscule: 133 (adjoint)
-    E8 1. Quasi-minuscule: 248 (adjoint)
-    F4 1. Quasi-minuscule: 26
-    G2 1. Quasi-minuscule: 7
+In case (3) the diagram of the representation contains weights with the length smaller than the
+length of short root, so it cannot be a projection of $\Delta_{\gf}$ to an integer subalgebra.
 
@@
 
-What we really need is the classification of all the representations where multiplicities of all
-non-zero weights are equal to one. Fortunately, such a classification was obtained in
+So far we've considered all the cases when $\mathrm{rank}\gf-\mathrm{rank}\af=1$. To complete our
+classification of splints we need the classification of all the representations where multiplicities
+of all non-zero weights are equal to one. Fortunately, such a classification was obtained in
 \cite{plotkin1998visual}. It consists of multiplicity-free representations and adjoint
-representations of algebras $A_{r}, B_{r}, C_{r}$ and $F_{4}$.  (? check with
-\cite{berenshtein1990multiplicity}).
+representations of algebras $A_{r}, B_{r}, C_{r}$, $F_{4}$ and $G_{2}$.
 
-For adjoint representation of algebra $A_{r}$ we see that projection $\Delta'$ of root system
-$\Delta_{\gf}$ should consist of roots of subalgebra $\af=A_{r}$ with multiplicity 2. This is the
-case for $\gf=A_{r+1}$, so for the special embedding $A_{r}\to A_{r+1} (su(r+1)\to su(r+2))$ we get
-a splint.
+In order to have the embedding $\af\to \gf$ such that The adjoint representation of $\gf$ is
+decomposed into two adjoint representations of $\af$ (and possibly several trivial
+representations) we need to satisfy following conditions:
+\begin{itemize}
+\item Denote by $n_{\gf}$ the total number of roots in $\Delta_{\gf}$ and the projection $\Delta'$.
+  Then it is
+  \begin{equation}
+    \label{eq:5}
+    n_{\gf}=2n_{\af}
+  \end{equation}
+\item Denote rank of $\gf$ by shorthand notation $r_{\gf}$. Then the dimension
+  \begin{equation}
+    \label{eq:6}
+    \mathrm{dim}\gf=n_{\gf}+r_{\gf}\geq 2\mathrm{dim}\af=2n_{\af}+2r_{\af}
+  \end{equation}
 
-(See also https://projecteuclid.org/euclid.jmsj/1180135505 for multiplicity-free branching rules)
+\end{itemize}
+
+% (? check with \cite{berenshtein1990multiplicity}).
+
+For the adjoint representation of algebra $A_{r}$ we see that projection $\Delta'$ of root system
+$\Delta_{\gf}$ should consist of roots of subalgebra $\af=A_{r}$ with multiplicity 2. The total
+number of roots for $A_{r}$ is $r(r+1)$, so $\Delta'$ and $\Delta_{\gf}$ contain $2r(r+1)$ roots,
+since there are no roots orthogonal to $\Delta_{\af}$. There are two for possible solutions for
+$\gf$: $D_{r+1}$ and $G_{2}$ for $r=2$. But the dimension of $D_{r+1}$ is $(r+1)(2r+1)$ while the
+dimension of $A_{r}$ is $r(r+2)$ and $2\mathrm{dim}A_{r}>\mathrm{dim}D_{r+1}$, so the adjoint
+representation of $D_{r+1}$ cannot be decomposed as twice the adjoint representation of $A_{r}$.
+There is no corresponding embedding $A_{r}\to D_{r+1}$ and no splint. We see that conditions
+\eqref{eq:5}\eqref{eq:6} do not hold.
+
+In order to have the embedding $B_{r}\to \gf$ such that the adjoint representation of $\gf$ is
+decomposed into two adjoint representations of $B_{r}$. It is straightforward to check that there is
+no solutions for $\gf$ satisfying the \eqref{eq:5}\eqref{eq:6} for the series $A$, $B$, $C$,
+$D$ and all exceptional simple Lie algebras.
+
+Since the number of roots of root system $C_{r}$ is the same as for $B_{r}$ and we need to check the
+same cases, we see that there is embedding for $C_{r}$ too.
+
+The adjoint representation of $G_{2}$ gives us the algebra $D_{4}$ as the solution of the
+constraints \eqref{eq:5}\eqref{eq:6}. The embedding $G_{2}\to D_{4}$ exists, since there are
+embeddings $G_{2}\to B_{3}$ and $B_{3}\to D_{4}$.
+
+For the adjoint representation of $F_{4}$ there is no solution that satisfies conditions
+\eqref{eq:5}\eqref{eq:6}.
+
+%% This is the
+%% case for $\gf=A_{r+1}$, so for the special embedding $A_{r}\to A_{r+1} (su(r+1)\to su(r+2))$ we get
+%% a splint. 
+%% 
+%% (See also https://projecteuclid.org/euclid.jmsj/1180135505 for multiplicity-free branching rules)
 %% 
@@
 
+The complete classification of splints for special embeddings $\Delta'=\pia(\Delta_{\gf})
+\equiv \Delta_{\af}\cup \Delta_{\sfr}$ where $\gf, \af$ are simple and $\sfr$ is semisimple is:
+\begin{itemize}
+\item $B_{n}\to D_{n+1}$
+\item $G_{2}\to B_{3}$
+\item $G_{2}\to D_{4}$
+\end{itemize}
+
 Having obtained the complete classification of splints of projections of root system for special
-embeddings, we need to check when such splints lead to the coincidence of branching coefficients
+embeddings, we need to check whether such splints lead to the coincidence of branching coefficients
 with weight multiplicities in modules of algebra $\sfr$. This depends on the decomposition of
-projection of singular element $\pi_{\af}\left(\Psi^{\mu}_{\gf}\right)$ into the combination of
+projection of singular element $\pia\left(\Psi^{\mu}_{\gf}\right)$ into the combination of
 singular elements of subalgebra $\sfr$. Relation between Weyl groups of $\af$ and $\sfr$ is crucial

### 2015-01-21 AffineLieAlgebras/Splints/special-paper.tex
Preprint published

@@
 \usepackage[utf8x]{inputenc}
-\usepackage[english,russian]{babel}
+\usepackage[english]{babel}
 
@@
 
-Note that the image $Im(\phi)$ is not required to inherit the root system
-properties except the addition rules equivalent to the addition
-rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
-can splinter $\Delta$  when the latter can be presented 
-as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.
+Note that the image $Im(\phi)$ is not required to inherit the root system properties except the
+addition rules equivalent to the addition rules in $\Delta_{1}$ (for pre-images). If an embedding
+$\phi$ preserves the angles between the roots it is called ``metric''. Two embeddings $\phi_1$ and
+$\phi_2$ can splinter $\Delta$ when the latter can be presented as a disjoint union of images
+$Im(\phi_1)$ and $Im(\phi_2)$.
 
@@
     \end{equation*}
-Here $\bff_{+}$ is the Borel subalgebra and $D^{\mu}$ its one-dimensional representation. 
+Here $\bff_{+}$ is the Borel subalgebra of $\gf$, $D^{\mu}$ its one-dimensional representation,
+$\left|v_{\mu}\right>$ is the highest weight vector and $E^{-\alpha_{j}}$ are lowering operators
+that are in correspondence with positive roots $\alpha_{j}\in \Delta^{+}$. 
 Weyl character formula expresses character of irreducible representation as a combination of
@@
 \end{equation*}
-Here the sum is over elements of Weyl group and their actions $w\triangleright \mu
+Here the sum is over elements of the Weyl group and their actions $w\triangleright \mu
 =w(\mu+\rho)-\rho$ depend on angles between roots. But we can rewrite Weyl character formula
@@
 on root system by permutations, so the composition of such an action with embedding $\phi$ is easily
-obtained. The orbit of Weyl groups action $w\triangleright \mu, w\in W$ can be constructed by
+obtained. The orbit of Weyl groups action $w\triangleright \mu, w\in W$, can be constructed by
 subtractions of roots from the highest weight $\mu$. Let's denote Dynkin labels of $\mu$ by
 $(\mu_{1},\dots \mu_{r})$. Then $\mu-\mu_{1}\alpha_{1}, \mu-\mu_{2}\alpha_{2},\dots,
-\mu-\mu_{r}\alpha_{r}, \alpha_{i}\in S$ are the points of the orbit that can be obtained by
+\mu-\mu_{r}\alpha_{r}, \alpha_{i}\in S$, are the points of the orbit that can be obtained by
 elementary reflections $s_{\alpha_{i}}, \alpha_{i}\in S$. Next set of points that are obtained by
@@
 Lie algebra $\sfr$. Then branching coefficients $b^{(\mu)}_{\nu}$ for the reduction
-$L^{(\mu)}_{\gf}\downarrow \af$ coincide with weight multiplicities $m^{(\tilde \mu)}_{\nu}$ in
+$L^{(\mu)}_{\gf\downarrow \af}$ coincide with weight multiplicities $m^{(\tilde \mu)}_{\nu}$ in
 $\sfr$-representations provided certain technical condition holds \cite{2011arXiv1111.6787L}.
@@
 
-In next section \ref{sec:splints-root-systems} we review the classification of splints for simple
+In the next section \ref{sec:splints-root-systems} we review the classification of splints for simple
 root systems and results for branching coefficients. Then we move to the study of special embeddings
 which is the main subject of the present paper. We consider special embeddings of Lie subalgebras
-into Lie algebra. In this case root system of the subalgebra is not contained in the root system of
+into a Lie algebra. In this case root system of the subalgebra is not contained in the root system of
 the algebra. So the original motivation for splints is not applicable. But we can consider the
-projection of root system of algebra on the root space of the subalgebra. Such a projection is not a
+projection of root system of the algebra on the root space of the subalgebra. Such a projection is not a
 root system anymore, but it satisfies milder conditions (Section \ref{sec:spec-embedd-proj}). It is
@@
 In conclusion \ref{sec:conclusion} we discuss the cases when the projection of the root system does
-not fall into above mentioned classification.
+not fall into the classification mentioned above.
 
@@
 \label{sec:splints-root-systems}
-The notion of splint was introduced in the paper \cite{richter2008splints} and classification of
-splints for simple root systems was obtained there.
+The notion and classification of
+splints for simple root systems were introduced in the paper \cite{richter2008splints}.
 
-Embedding $\phi$ of a root system $\Delta_1$ into a root system
-$\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
-subset of $\Delta$ that commutes with vector composition law in
-$\Delta_{1}$ and $\Delta$.
-\begin{equation*}
-\phi:\Delta_1 \longrightarrow \Delta
-\end{equation*}
-\begin{equation*}
-\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
-\,\,\, \alpha,\beta \in \Delta_1
-\end{equation*}
-
-Note that the image $Im(\phi)$ must not inherit the root system
-properties except the addition rules equivalent to the addition
-rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
-can splinter $\Delta$  when the latter can be presented 
-as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.
-
-The classification is shown in table
-
+%% Embedding $\phi$ of a root system $\Delta_1$ into a root system
+%% $\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
+%% subset of $\Delta$ that commutes with vector composition law in
+%% $\Delta_{1}$ and $\Delta$.
+%% \begin{equation*}
+%% \phi:\Delta_1 \longrightarrow \Delta
+%% \end{equation*}
+%% \begin{equation*}
+%% \phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
+%% \,\,\, \alpha,\beta \in \Delta_1
+%% \end{equation*}
+%% 
+%% Note that the image $Im(\phi)$ must not inherit the root system
+%% properties except the addition rules equivalent to the addition
+%% rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
+%% can splinter $\Delta$  when the latter can be presented 
+%% as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.   
+%% 
+%% The classification is shown in table
+%% 
 Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
@@
 Computation of branching coefficients relies on roots $\Delta_{\gf}\setminus \Delta_{\af}$
-\cite{2010arXiv1007.0318L} so splint  is naturally connected branching coefficients for regular
+\cite{2010arXiv1007.0318L} so splint  is naturally connected to branching coefficients for regular
 subalgebra.
 
-Remember that only three types of splints are
-injective and thus are naturally connected with branching. Below we
-reproduce the part of the splints table from \cite{richter2008splints} corresponding to
-injective splints:
+Only three types of splints are
+injective and thus are naturally connected to branching \cite{richter2008splints}:
 \begin{equation}
@@
 \begin{Prop}
+There is a decomposition of a singular element of the algebra $\gf$ into singular elements of the subalgebra $\sfr$:
 \begin{equation}
-\frac{e^{\rho _{\gf}}}{\prod_{\beta \in \Delta _{\sfr%
-}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\sfr%
-}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\sfr}^{\widetilde{\mu }%
-}}M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
-\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
-}=\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
-\label{singular main-4}
+ \Phi ^{\mu }_{\gf} = \sum_{w\in W_{\frak{a}}}\epsilon\left( w\right)w\left( e^{\mu +\rho _{\gf}}\phi\left( e^{-\widetilde{\mu }}\Psi^{\widetilde{\mu }}_{\sfr}\right)\right),
 \end{equation}
-
-Actually:
+where $\epsilon\left( w\right)$ is a determinant of the element $w$ of the Weyl group $W_{\af}$ of
+the subalgebra $\af$. The action of Weyl group on the weights is extended to the algebra of formal
+exponents by the rule $w\left(e^{\nu}\right)=e^{w\nu}, w\in W$. Hence, the multiplicity $M_{\left(
+      \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight $\widetilde{\nu }$ from the
+  weight diagram of the algebra $\sfr$ with the highest weight $\tilde\mu$ defines the branching
+  coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu -\phi \left(
+      \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
 \begin{equation}
-\frac{e^{\rho _{\frak{a}}-\rho _{\gf}}}{\prod_{\beta \in \Delta _{\sfr%
-}^{+}}(1-e^{-\beta })}\left( \Phi ^{\mu }_{\gf}\right) = \frac{e^{\rho _{\frak{a}}-\rho _{\gf}}}{\prod_{\beta \in \Delta _{\sfr%
-}^{+}}(1-e^{-\beta })}\left( e^{\mu +\rho _{\gf}}\phi\left( e^{-\widetilde{\mu }}\Psi^{\widetilde{\mu }}_{\sfr}\right)\right) = 
-\end{equation}
-
-\begin{equation}
-= e^{\rho _{\frak{a}}+\mu-\phi\left(\widetilde{\mu }\right)}\phi\left(ch L_s^{\widetilde{\mu }}\right) = e^{\rho _{\frak{a}}+\mu-\phi\left(\widetilde{\mu }\right)}\sum_{\widetilde{\nu }\in \mathcal{N}_{\sfr}^{\widetilde{\mu }%
-}}M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
-\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)} =\sum_{\nu \in P_{\frak{a}}^{++}}b_{\nu }^{(\mu )}\Phi_a^{\left(\nu\right)}.
-\end{equation}
-
-Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
-highest weights in the decomposition. The multiplicity $M_{\left( \sfr%
-\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
-}\in \mathcal{N}_{\sfr}^{\widetilde{\mu }}$ defines the branching
-coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
--\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
-\[
 b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
 }^{(\mu )}=M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}. 
-\]
+\label{bran1}
+\end{equation}
 \end{Prop} 
@@
 
-The study of special embeddings was traces back to fundamental papers by Eugene Dynkin
-\cite{dynkin1952semisimple,dynkin1952maximal}, he called such subalgebras ``S-subalgebras'' to
+The study of specialy embedded subalgebras traces back to fundamental papers by Eugene Dynkin
+\cite{dynkin1952semisimple,dynkin1952maximal} where he called such subalgebras ``S-subalgebras'' to
 distinguish from regular or ``R-subalgebras'' that have root systems obtained by dropping some roots
-of the algebra root system. While regular subalgebras are easy to construct by dropping nodes from
-extended Dynkin diagram of the algebra, the case of special subalgebras is more difficult. Complete
+of the algebra root system. Thus regular subalgebras are easy to construct by dropping nodes from
+extended Dynkin diagram of the algebra, while the case of special subalgebras is more difficult. Complete
 classification for exceptional Lie algebras was obtained recently in \cite{minchenko2006semisimple}.
-The algorithm of construction of special subalgebras is available in GAP package but still requires
+The algorithm of the special subalgebras construction is available in GAP package but still requires
 manual intervention \cite{de2011constructing}.
@@
 To construct an embedding $\af\to\gf$ consider some representation $L^{\nu}_{\af}$ as a subspace of
-Lie algebra $\gf$. Then one needs to check that the generators of $\af$ then can be presented as
+Lie algebra $\gf$. Then one needs to check that the generators of $\af$ can be presented as
 linear combinations of generators of $\gf$. We can identify Cartan subalgebra $\hfa\subset \af$ with
@@
 
-From classical papers \cite{dynkin1952semisimple,dynkin1952maximal} it is well known that the
-projection of $\gf$ root system $\Delta_{\gf}$ to $\hfa^{*}$ is a weight system of some
-finite-dimensional but not irreducible representation of $\af$.  We denote such a projection by
+This projection is described in the classical papers \cite{dynkin1952semisimple,dynkin1952maximal} by the following theorem:
+
+\begin{theorem}\label{dyn0}
+  If a representation $L^{\mu}_{\gf}$ of the algebra $\gf$ induces a representation
+  $L^{\tilde\mu}_{\af}$ on the subalgebra $\af$ then the weight system of $L^{\tilde\mu}_{\af}$ can
+  be obtained from $L^{\mu}_{\gf}$ by an orthogonal projection of $\hfg^{*}$ on $\hfa^{*}$.
+
+  \cite{dynkin1952maximal}. 
+\end{theorem}
+
+In relation to the adjoint representation of $\gf$ this theorem means that the projection of the root system $\Delta_{\gf}$ to $\hfa^{*}$ is a weight system of some
+finite-dimensional but not irreducible representation of $\af$. Moreover this reducible representation contains the adjoint representation of $\af$. And if we denote such a projection by
 \begin{equation}
   \label{eq:2}
-  \Delta'=\pia\left(\Delta_{\gf}\right)
+  \Delta'=\pia\left(\Delta_{\gf}\right),
 \end{equation}
+then the roots of $\af$ will be contained in $\Delta'$. Thus the system $\Delta'$ can be a root
+system but it might not be reduced and might contain some vectors with multiplicities greater than
+one.
 
-The system $\Delta'$ can be a root system but it can be not reduced and can contain some vectors
-with multiplicities greater then one.
+The following theorems \cite{dynkin1952semisimple} also concern the properties of $\Delta'$.
 
-%Теоремы из Дынкина и их очевидные следствия:
-
-Several theorems from \cite{dynkin1952semisimple} are useful to us.
-
-\begin{theorem}\label{dyn0}
-  If representation $\phi$ of algebra $\gf$ induces representation $\tilde\phi$ on subalgebra $\af$ then
-  the weight system of representation $\tilde\phi$ can be obtained from representation $\phi$ by
-  orthogonal projection of the weight space of algebra $\gf$ on the weight space of subalgebra $\af$
-
-  \cite{dynkin1952maximal}.
-%(Требует проверки, так как сформулировано в туманных и устаревших терминах в обоих источниках: см.
-стр.374 в d1 в доказательстве теоремы 3.2 или стр.119 в d2 - теорема 0.11)
-\end{theorem}
-
-Applying this theorem to the adjoint representation of $\gf$ we see that the roots of $\af$ are
-contained in the projection $\Delta'$ of root system $\Delta_{\gf}$.
-
-Moreover, the following theorems hold. 
 \begin{theorem}\label{dyn1}
-  Every special subalgebra $\af$ of semisimple Lie algebra $\gf$ is integer, i.e. projections of
+  Every special subalgebra $\af$ of a semisimple Lie algebra $\gf$ is integer, i.e. the projections of
   roots of $\gf$ to $\hfa^{*}$ are linear combinations of simple roots of $\af$ with integer
@@
 \begin{theorem}\label{dyn2}
-  If $\af$  is semisimple subalgebra of semisimple Lie algebra $\gf$ and generator $e_{\alpha}$ corresponding to
-  a root $\alpha$ of subalgebra $\af$ is presented as a linear combination $e_{\alpha}=\sum_{\beta}
+  If $\af$  is a semisimple subalgebra of a semisimple Lie algebra $\gf$ and the generator $e_{\alpha}$ corresponding to
+  the root $\alpha$ of $\af$ is presented as a linear combination $e_{\alpha}=\sum_{\beta}
   e_{\beta}$ of $\gf$-generators
-  corresponding to roots $\beta$ of $\gf$, then the roots $\beta$ are projected into $\alpha$,
+  corresponding to the roots $\beta$ of $\gf$, then the roots $\beta$ are projected into $\alpha$,
   $\pia(\beta)=\alpha$. 
@@
 
-As an example we present a projection $\Delta'$ of root system $D_{4}$ to root system of special
+As an example we present a projection $\Delta'$ of the root system of $D_{4}$ to the root system of the special
 subalgebra $A_{2}$ (Fig. \ref{fig:d4-a2_splint}).
@@
   }
-  \caption{Projection of $D_{4}$ ($so(8)$)-root system onto root space of special subalgebra $A_{2}$
+  \caption{Projection of $D_{4}$ ($so(8)$)-root system onto the root space of the special subalgebra $A_{2}$
     ($su(3)$). Note that this roots system is $G_{2}$ but with non-trivial multiplicities. }
@@
 
-Since roots are weights of the adjoint representation, such a projection produces the weight diagram
-of $\af$-representation that contains adjoint representation of $\af$. After the subtraction of
-$\af$-root system $\Delta_{\af}$ from $\Delta'$ we obtain weight diagram of representation called
-``characteristic representation of subalgebra $\af$'' by Dynkin in the seminal paper
-\cite{dynkin1952semisimple}.
+%Since roots are weights of the adjoint representation, such a projection produces the weight diagram
+%of $\af$-representation that contains adjoint representation of $\af$.
+%After the subtraction of
+%$\af$-root system $\Delta_{\af}$ from $\Delta'$ we obtain the weight diagram of representation called
+%``characteristic representation of subalgebra $\af$'' by Dynkin in the seminal paper
+%\cite{dynkin1952semisimple}.
 
@@
 corresponding root systems. The embedding $\varphi_{\af}$ is metric and trivial. Moreover, the
-projection of singular element $\pia\left(\Psi^{\mu}\right)$ should admit a decomposition into
+projection of singular element $\pia\left(\Psi^{\mu}_{\gf}\right)$ should admit a decomposition into
 linear combination of singular elements of irreducible representations of $\sfr$:
@@
   \label{eq:4}
-  \pia\left(\Psi^{\mu}_{\gf}\right)=\sum_{\nu} \Psi^{\nu}_{\sfr}.
+  \pia\left(\Psi^{\mu}_{\gf}\right)=\sum_{\nu} \varkappa_{\nu}e^{\nu}\Psi^{\tilde\mu}_{\sfr},
 \end{equation}
-First we classify all the splints
-of the projection of root system into union of simple root systems for special embeddings, and then
-discuss the decomposition of singular elements.
+with integer coefficients $\varkappa_{\nu}$, where the sum is over the set of weights $\nu$ that
+will be determined later. First we classify all the splints of the projection of a root system into
+a union of simple root systems for special embeddings, and then discuss the decomposition of singular
+elements.
 
-Projection of the root system $\Delta'$ coincides with the projection of weight diagram of the
-adjoint representation of algebra $\gf$ with the exception of zero weight. Adjoint representation of
+Projection of the $\gf$ root system $\Delta'$ coincides with the projection of the weight diagram of the
+adjoint representation of algebra $\gf$ with the exception of zero weight. The adjoint representation of
 $\gf$ contains adjoint representation of $\af$ and can be decomposed as
@@
 
-Weight diagram of $M^{\chi}_{\af}$ coincides with root system $\Delta_{\sfr}$ with the exception of
+The weight diagram of $M^{\chi}_{\af}$ coincides with the root system $\Delta_{\sfr}$ with the exception of
 zero weight. So we need to find all the representations for all simple Lie algebras $\af$, such that
@@
 
-If root system $\Delta_{\gf}$ contains roots $\alpha: \alpha\perp \beta,\; \forall \beta\in
-\Delta_{\af}$ orthogonal to root system of the subalgebra, one cannot proceed with the decomposition
+If the root system $\Delta_{\gf}$ contains roots $\alpha: \alpha\perp \beta,\; \forall \beta\in
+\Delta_{\af},$ orthogonal to the root system of the subalgebra, one cannot proceed with the decomposition
 of singular element \eqref{eq:4}. The elements $e^{\nu}$ of $\pia\left(\Psi^{\mu}_{\gf}\right)$
@@
 
-Multiplicity of zero weight in adjoint representation is equal to the rank of the algebra. So if
+The multiplicity of zero weight in the adjoint representation is equal to the rank of the algebra. So if
 $\mathrm{rank}\gf-\mathrm{rank}\af=1$, the representation in question $M^{\chi}_{\af}$ must be
@@
 Fundamental weights of the algebra $A_{r}$ are shorter than its roots, but the projections of $\gf$
-weights must be given by linear combinations of roots of special subalgebra $\af$ with integer
-coefficients, so the first class of strongly multiplicity free representations does not produce such
+weights must be given by linear combinations of the roots of the  special subalgebra $\af$ with integer
+coefficients, so the first class of strongly multiplicity free representations does not produce such a
 projection.
@@
 \Delta_{D_{r+1}}\right) = \Delta_{B_{r}}\cup \Delta_{A_{1}+\dots+A_{1}}$ corresponding to Gelfand-Tsetlin
-multiplicity-free branching for the embedding $\mathfrak{so}(2r+1)\to \mathfrak{so}(2r+2)$.
+multiplicity-free branching for the special embedding $\mathfrak{so}(2r+1)\to \mathfrak{so}(2r+2)$.
 
-The length of the first fundamental weight of  $C_{r}$ is less than length of its short root, so
-this case can not correspond to integer subalgebra.
+The length of the first fundamental weight of  $C_{r}$ is less than the length of its short root, so
+this case can not correspond to an integer subalgebra.
 
@@
 %% 
-Weight diagram of of seven-dimensional representation of $G_{2}$ together with $G_{2}$ root system
-form the projection of root system $B_{3}$ which appears in special embedding of simple Lie algebra
+The weight diagram of the seven-dimensional representation of $G_{2}$ together with $G_{2}$ root system
+form the projection of the root system $B_{3}$ which corresponds to special embedding 
 $G_{2}\to B_{3}$. Branching coefficients in this case coincide with weight multiplicities of
@@
 The weight $\mu$ is minuscule if $\left<\mu,\alpha^{\vee}\right>\leq 1$ for all $\alpha\in
-\Delta^{+}$ and all the weights of the irreducible representation $L^{\mu}$ lie on Weyl
-group orbit of $\mu$. Weight is quasi-minuscule if $\left<\mu,\alpha^{\vee}\right>\leq 2$ for all
-$\alpha\in \Delta^{+}$ and all non-zero weights lie on single Weyl group orbit.
+\Delta^{+}$ and all the weights of the irreducible representation $L^{\mu}$ lie on the Weyl
+group orbit of $\mu$. A weight is quasi-minuscule if $\left<\mu,\alpha^{\vee}\right>\leq 2$ for all
+$\alpha\in \Delta^{+}$ and all non-zero weights lie on the single Weyl group orbit.
 
@@
 representation for the series $A_{r}$; spin representations for the series
-$B_{r}$; vector representations for $C_{r}$; vector, and two half-spin for $D_{r}$; two
+$B_{r}$; vector representations for $C_{r}$; vector and two half-spin for $D_{r}$; two
 27-dimensional representations for $E_{6}$ and 56-dimensional representation of $E_{7}$.
@@
 We see that case (1) contains strongly multiplicity free modules of series $A_{r}$ and exceptional
-Lie algebra $G_{2}$, class (2) contains strongly multiplicity free modules of $ B_{r}, C_{r}$ ,
+Lie algebra $G_{2}$, class (2) contains strongly multiplicity free modules of $ B_{r}$ and $C_{r}$ ,
 strongly multiplicity free modules of $A_{1}$ are included in class (4).
@@
 (1) is the vector representation for $C_{r}$. It is $2r$-dimensional, but the length of its highest weight $\omega_{1}$ is less
-than length of the short root of algebra $C_{r}$. So it can not be a characteristic representation
+than the length of the short root of algebra $C_{r}$. So it can not be a characteristic representation
 for the special subalgebra.
@@
 %% 
-Case (2) consists of the series $B_{r}$ and exceptional root system $G_{2}$. The embedding $G_{2}\to
+Case (2) consists of the series $B_{r}$ and the exceptional root system $G_{2}$. The embedding $G_{2}\to
 B_{3}$ was already discussed. 
-For the series $B_{r}$ we the dimension of the adjoint representation
+ The dimension of the adjoint representation for the series $B_{r}$
 is $2r^{2}+r$ and of quasi-minuscule representation it is $2r+1$, so the dimension of the algebra
@@
 
-We need to consider representations of class (4) only for $m=1,2$ since root system $\Delta_{\sfr}$
+We need to consider representations of class (4) only for $m=1,2$ since the root system $\Delta_{\sfr}$
 can have roots of at most two different lengths. In the case $m=1$ we get strongly multiplicity free
 modules of $A_{r}$ which were discussed above. And for algebra $A_{2}$ and $m=2$ the weight diagram
-of representation $L^{2\omega_{1}}_{A_{2}}$ coincides with root system of exceptional Lie algebra
+of representation $L^{2\omega_{1}}_{A_{2}}$ coincides with the root system of exceptional Lie algebra
 $G_{2}$. This case appears in the special embedding $A_{2}\to B_{3}$. But for $A_{r}, r>2$ there are
@@
 
-In order to have the embedding $\af\to \gf$ such that The adjoint representation of $\gf$ is
+In order to have the embedding $\af\to \gf$ such that the adjoint representation of $\gf$ is
 decomposed into two adjoint representations of $\af$ (and possibly several trivial
@@
 \item Denote by $n_{\gf}$ the total number of roots in $\Delta_{\gf}$ and the projection $\Delta'$.
-  Then it is
+  Then
   \begin{equation}
     \label{eq:5}
-    n_{\gf}=2n_{\af}
+    n_{\gf}=2n_{\af}.
   \end{equation}
@@
 
-For the adjoint representation of algebra $A_{r}$ we see that projection $\Delta'$ of root system
+For the adjoint representation of algebra $A_{r}$ we see that the projection $\Delta'$ of the root system
 $\Delta_{\gf}$ should consist of roots of subalgebra $\af=A_{r}$ with multiplicity 2. The total
 number of roots for $A_{r}$ is $r(r+1)$, so $\Delta'$ and $\Delta_{\gf}$ contain $2r(r+1)$ roots,
-since there are no roots orthogonal to $\Delta_{\af}$. There are two for possible solutions for
+since there are no roots orthogonal to $\Delta_{\af}$. There are two possible solutions for
 $\gf$: $D_{r+1}$ and $G_{2}$ for $r=2$. But the dimension of $D_{r+1}$ is $(r+1)(2r+1)$ while the
@@
 
-In order to have the embedding $B_{r}\to \gf$ such that the adjoint representation of $\gf$ is
+Let's consider the embedding $B_{r}\to \gf$ such that the adjoint representation of $\gf$ is
 decomposed into two adjoint representations of $B_{r}$. It is straightforward to check that there is
@@
 Since the number of roots of root system $C_{r}$ is the same as for $B_{r}$ and we need to check the
-same cases, we see that there is embedding for $C_{r}$ too.
+same cases, we see that there is no embedding for $C_{r}$ too.
 
@@
 constraints \eqref{eq:5}\eqref{eq:6}. The embedding $G_{2}\to D_{4}$ exists, since there are
-embeddings $G_{2}\to B_{3}$ and $B_{3}\to D_{4}$.
+embeddings $G_{2}\to B_{3}$ and $B_{3}\to D_{4}$, but the decomposition of adjoint representation of
+$D_{4}$ is different: $ \mathrm{ad}_{D_{4}}=\mathrm{ad}_{G_{2}}\oplus 2 L^{\omega_{1}}_{G_{2}}$. So
+this case does not produce splint for the projection $\Delta'$.
 
@@
 \item $G_{2}\to B_{3}$
-\item $G_{2}\to D_{4}$
+%\item $G_{2}\to D_{4}$
 \end{itemize}
 
-Having obtained the complete classification of splints of projections of root system for special
-embeddings, we need to check whether such splints lead to the coincidence of branching coefficients
-with weight multiplicities in modules of algebra $\sfr$. This depends on the decomposition of
-projection of singular element $\pia\left(\Psi^{\mu}_{\gf}\right)$ into the combination of
-singular elements of subalgebra $\sfr$. Relation between Weyl groups of $\af$ and $\sfr$ is crucial
-here.
+Note that in the splints for special embeddings there is no case where $\Delta_{\sfr}$ is embedded
+non-metrically which is a direct result of our exhaustive classification of suitable characteristic
+representations of the subalgebra $\af$.
 
-\begin{table}[h]
-\begin{tabular}[t]{|p{2em}|p{6em}|p{5em}|p{5em}|p{2em}|p{6em}|}
+Having obtained the complete classification of splints of the projections of
+the root systems for special embeddings, we need to check whether such splints lead
+to the coincidence of branching coefficients with weight multiplicities in modules of
+the algebra $\sfr$.
+
+Let's consider the first case - the embedding $B_{n}\to D_{n+1}$. The root system of $D_{n+1}$ has
+exactly two simple roots that are different from the simple roots of $B_{n}$. In the notation of
+\cite{bourbaki2002lie} they are $\alpha_{n}=e_n-e_{n+1}$ and $\alpha_{n+1}=e_n+e_{n+1}$ while
+$\alpha_n^{B_n}=e_n$. This difference leads to the crucial difference in the Weyl groups of the
+algebras: while $W_{B_{n}}$ is a semidirect product of the group of permutation $e_{i} \to e_{j}$
+and the group of the change of sign $e_{i}\to (\pm 1)_{i}e_{i}$, $W_{D_{n+1}}$ is the same but for
+the additional condition on the group of the change of sign: $\prod_{i} (\pm)_{i}=1.$ Since the
+projection of $D_{n+1}$ on $B_{n}$ acts as
+$(e_1,e_2,\dots,e_{n},e_{n+1})\to(e_1,e_2,\dots,e_{n},0)$, the singular element
+$\Phi^{(\mu)}_{D_{n+1}}$ which is the orbit of $W_{D_{n+1}}$ will become a composition of the orbits
+of $W_{B_{n}}$ after the projection.
+
+Indeed, if $\mu+\rho_{D_{n+1}}=(a_1,a_2,\dots,a_{n+1})$ in the standart basis
+$(e_1,e_2,\dots,e_{n+1})$, then the Weyl group $W_{D_{n+1}}$ will act on it by permutating $a_i$ and
+changing their signs. After the projection the last coefficient in every element will be cut. Among
+these elements will be groups in which all elements will have the same set of $a_i$ standing in
+arbitrary order and having an arbitrary sign. These groups will be similar to the orbits of the Weyl
+group $W_{B_{n}}$ but for the singular miltiplicity. A singular miltiplicity is a determinant
+$\varepsilon (w)$ of the element $w$ of the Weyl group. Because of the additional condition on the
+Weyl group $W_{D_{n+1}}$ the change of the signs of $a_i$ doesn't change the singular multiplicity.
+That's not true for the Weyl group $W_{B_{n}}$, thus exactly half of the elements of each newly
+formed orbit $\tilde\Phi^{\tilde\nu}_{B_n}$ of $W_{B_{n}}$ will have the wrong singular
+multiplicity. Moreover, these orbits can be rewritten in the following form:
+
+\begin{equation}
+\tilde\Phi^{\tilde\nu}_{B_n}=\sum_{w\in W_{D_n}} \varepsilon(w) (1+s_{e_n})w e^{\tilde\nu+\rho_{B_n}}.
+\end{equation}
+
+This decomposition is possible because the orbit of the Weyl group of $D_n$ coincides with the half
+of $\tilde\Phi^{\tilde\nu}_{B_n}$ that has correct singular multiplicities and other half can be
+obtained by the action of the element $s_{e_n}$ of $W_{B_{n}}$.
+
+Thus, the projection $(\Phi^{(\mu)}_{D_{n+1}})'$ consists of $(n+1)$ quasi-orbits (with ``wrong'' signs) of the Weyl group
+$W_{B_{n}}$. It means that there are $(n+1)$ weights in the fundamental Weyl chamber $\bar C_{B_n}$
+of $B_n$. It can be easily shown that these weights are $(a_1,a_2,\dots,a_{n})$ and weights obtained
+from $(a_1,a_2,\dots,a_{n})$ by consequent subtraction of $\mu_i e_i$ starting with $\mu_n e_n$,
+where $\mu_i$ is Dynkin labels of $\mu$ plus $1$. As it turns out, if one were to add to this set
+the required weights with corresponding singular multiplicities to construct the singular element of
+$\sfr=A_1+A_1+\dots+A_1$ as was done in the Introduction of this paper, all additional weight would
+lie on the boundaries of the fundamental Weyl chamber $\bar C_{B_n}$. This fact is easily proved by
+observing that the action of one of $s_{\alpha_i^{B_n}}$ on the weights doesn't change those
+weigths. Thus, the projection $(\Phi^{\mu}_{D_{n+1}})'$ can be viewed as a quasi-orbit of the
+singular element of $\sfr$:
+
+\begin{equation}
+\Phi^{[\mu_1,\mu_2,\dots,\mu_{n+1}]}_{D_{n+1}}=\sum_{w\in W_{D_n}} \varepsilon(w) (1+s_{e_n})w (e^{\mu'+\rho_{D_{n+1}}'-\tilde\mu}\Psi^{[\mu_1,\mu_2,\dots,\mu_{n}]}_{\sfr}),
+\end{equation}
+where $\tilde\mu=[\mu_1,\mu_2,\dots,\mu_{n}]$. This decomposition yields the branching rules similar to (\ref{bran1}):
+
+\begin{equation}
+b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
+}^{[\mu_1,\mu_2,\dots,\mu_{n+1}]}=M_{\left( \sfr\right) \widetilde{\nu }}^{[\mu_1,\mu_2,\dots,\mu_{n}]}, 
+\label{bran1}
+\end{equation}
+which is in total agreement with the Gelfand-Tsetlin branching rules as the weights of the representations of $\sfr=A_1+A_1+\dots+A_1$ are always equal to one (see Fig.\ref{ris1} and Fig.\ref{ris2}).
+
+\begin{figure}[h]
+\begin{center}
+\begin{minipage}[h]{0.5\linewidth}
+\includegraphics[width=0.95\linewidth]{drawing-1}
+\caption{Splint $D_3= B_2\cup A_1+A_1$: projection of the singular element $\Phi_{D_3}^{[1,1,2]}$ can be made from singular elements $\Phi_{A_1+A_1}^{[1,1]}$.
+Light-grey area is the fundamental Weyl chamber of subalgebra $B_2$.}
+\label{ris1} 
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.47\linewidth}
+\includegraphics[width=0.9\linewidth,viewport=0 0 157 157,clip]{drawing-3}
+\caption{Injection fan applied to the singular element $\Phi_{A_1+A_1}^{[1,1]}$ yields branching coefficients that are equal to 1.}
+\label{ris2}
+\end{minipage}
+\end{center}
+\end{figure}
+
+Careful examination of the embedding $G_{2}\to B_{3}$ leads to exactly the  same conclusion.
+
+So far we only considered special splints where both embedded systems are root systems. However, it
+is possible to study the splints where it is not the case. Such splints obviously can not serve to
+simplify calculation of the branching rules but one may use the properties of special embeddings and
+the projections to creat a perepesentation theory for the systems that are not root systems.
+
+As the result we see that branching coefficients coincide with weight multiplicities for the splints
+in the following table:
+\begin{equation}
+\label{eq:1}
+\begin{array}{cc||c|c}
+\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
+_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\sfr}\hspace{0.25in}
+\\ \hline\hline
+\hbox{(i)} & G_{2} & A_{2} & A_{2} \\
+& F_{4} & D_{4} & D_{4} \\ 
+\hbox{(*)} & B_{3} & G_{2} & A_{2}  \\
+\hbox{(*)} & D_{r+1} & B_{r} & \oplus ^{r}A_{1}  \\
 \hline
-Тип & $s$ & $W_a\subset W_s$ & $W_s\subset W_a$ & $g_{inv} $ & Примеры \\
-\hline
-1 & корневая система & нет & да & есть  & $B_2\rightarrow D_3$, $G_2\rightarrow B_3$\\
-\hline
-2 & корневая система  & да & да & нет & $A_1\rightarrow A_1+A_1$ \\
-\hline
-3 & корневая система  & да & нет & есть & $A_1+A_1\rightarrow D_3$ \\
-\hline
-4 & не корневая система  & да & нет & есть & $A_1\rightarrow A_2$, $A_1\rightarrow B_3$\\
-\hline
-5 & не корневая система  & да & нет & нет  & $A_1\rightarrow B_2$\\
-\hline
-6 & \multicolumn{4}{|l|}{$W_a\not\subset W_s$ и $W_s\not\subset W_a$} & $B_2\rightarrow D_4$\\
-\hline
-\end{tabular}
-\caption{Классы специальных сплинтов.}
-\label {spsp}
-\end{table}
-
-As the result we see that branching coefficients coincide with weight multiplicities for
-the embeddings $something\to something$ and do not coincide for $something else\to something else$.
+\hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
+\hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
+^{r}A_{1} \\
+& B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
+\end{array}
+\end{equation} 
+here the splints marked with (*) are special splints.
 
@@
 different simple Lie algebras.
+
+There exist special embeddings of semisimple Lie-algebras into simple Lie-algebras. For such
+embeddings the procedure of finding splints that allow to calculate branching coefficient is similar
+to the one conducted above. While the results of the procedure are not presented in this paper they
+can be obtained with little difficulty.
 

### 2015-02-10 AffineLieAlgebras/Splints/special-paper.tex
JPhysA submission 21.01.2015

@@
-\documentclass{article}
+\documentclass[12pt]{iopart}
 
-\usepackage{amsfonts}
+%\usepackage{amsfonts}
 \usepackage{pb-diagram}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\usepackage{amsmath,amssymb,amsthm}
+\usepackage{iopams,setstack}
 \usepackage{multicol}
@@
 
-\title{Splints of root systems for special Lie subalgebras} % Тут надо придумать хорошее название
+\ftc{Splints of root systems for special Lie subalgebras}
 
-\author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$, P.I.~Kakin$^{1}$\\
-  {\small $^1$ Department of High-energy and elementary particle physics,}\\ {\small St Petersburg State University}\\
-  {\small 198904, Saint-Petersburg, Russia,}\\
-  {\small $^{2}$ e-mail: antonnaz@gmail.com}}
-%%  {\small$^{2}$ Chebyshev Laboratory,}
-%%  {\small Department of Mathematics and Mechanics, SPb State University}\\
-%%  {\small 199178, Saint-Petersburg, Russia}}
-\date{}
-\maketitle
+\author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$, P.I.~Kakin$^{1}$}
+\address{ $^1$ Department of High-energy and elementary particle physics,  St Petersburg State University, 198904, Saint-Petersburg, Russia}
+\ead{ $^{2}$ e-mail: antonnaz@gmail.com}
 
 \begin{abstract}
-  Splint is a decomposition of root system into union of root systems. Splint of root system for
-  simple Lie algebra appears naturally in studies of (regular) embeddings of reductive subalgebras.
-  Splint can be used to construct branching rules. We consider special embedding of Lie subalgebra
-  to Lie algebra. We classify projections of algebra root systems using extended Dynkin diagrams and
+  Splint is a decomposition of root system into a union of root systems. Splint of root system for a
+  simple Lie algebra appears naturally in the studies of (regular) embeddings of reductive
+  subalgebras. Splint can be used to construct branching rules. We consider a special embedding of a
+  Lie subalgebra into a simple Lie algebra. We classify the projections of algebra root systems and
   single out the conditions of splint appearance and coincidence of branching coefficients with
-  weight multiplicities. While such a coincidence is not very common it is connected with Gelfand-Tsetlin basis. 
+  weight multiplicities. While such a coincidence is not very common it is connected with
+  Gelfand-Tsetlin basis.
+
+\noindent{\it Keywords\/}: Lie algebra, special subalgebra, branching, weight multiplicity, splint
 \end{abstract}
+
+\submitto{\jpa}
 
@@
 The notion of splint was introduced by David Richter in the paper \cite{richter2008splints}. Splint
-is the decomposition of root system into disjoint union of images of two or more embeddings of some
-other root systems. Embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a
-bijective map of roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with vector
+is a decomposition of a root system into a disjoint union of the images of two or more embeddings of some
+other root systems. An embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a
+bijective map of roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with the vector
 composition law in $\Delta_{1}$ and $\Delta$.
@@
 
-Why one would consider non angle-preserving maps of root systems? Additive properties of root system
-determine the structure of Verma module:
+Why one would consider non angle-preserving maps of root systems? Additive properties of the root system
+determine the structure of the Verma module:
     \begin{equation*}
@@
     \end{equation*}
-Here $\bff_{+}$ is the Borel subalgebra of $\gf$, $D^{\mu}$ its one-dimensional representation,
+Here $\bff_{+}$ is the Borel subalgebra of $\gf$, $D^{\mu}$ is its one-dimensional representation,
 $\left|v_{\mu}\right>$ is the highest weight vector and $E^{-\alpha_{j}}$ are lowering operators
 that are in correspondence with positive roots $\alpha_{j}\in \Delta^{+}$. 
-Weyl character formula expresses character of irreducible representation as a combination of
-characters of Verma modules: 
+The Weyl character formula expresses a character of an irreducible representation as a combination of
+the characters of the Verma modules: 
 \begin{equation*}
@@
 Here the sum is over elements of the Weyl group and their actions $w\triangleright \mu
-=w(\mu+\rho)-\rho$ depend on angles between roots. But we can rewrite Weyl character formula
-representing Weyl group elements as the products of reflections $s_{\alpha}, \alpha \in S$ in
-hyperplanes orthogonal to simple roots: $w=s_{\alpha_{1}}\cdot s_{\alpha_{2}}\dots$. Reflections act
-on root system by permutations, so the composition of such an action with embedding $\phi$ is easily
-obtained. The orbit of Weyl groups action $w\triangleright \mu, w\in W$, can be constructed by
-subtractions of roots from the highest weight $\mu$. Let's denote Dynkin labels of $\mu$ by
+=w(\mu+\rho)-\rho$ depend on angles between roots. But we can rewrite the Weyl character formula
+representing the Weyl group elements as the products of the reflections $s_{\alpha}, \alpha \in S$ in
+the hyperplanes orthogonal to the simple roots: $w=s_{\alpha_{1}}\cdot s_{\alpha_{2}}\dots$. The reflections act
+on the root system by permutations, so the composition of such an action with the embedding $\phi$ is easily
+obtained. The orbit of the Weyl group action $w\triangleright \mu, w\in W$, can be constructed by
+subtractions of roots from the highest weight $\mu$. Let's denote the Dynkin labels of $\mu$ by
 $(\mu_{1},\dots \mu_{r})$. Then $\mu-\mu_{1}\alpha_{1}, \mu-\mu_{2}\alpha_{2},\dots,
 \mu-\mu_{r}\alpha_{r}, \alpha_{i}\in S$, are the points of the orbit that can be obtained by
-elementary reflections $s_{\alpha_{i}}, \alpha_{i}\in S$. Next set of points that are obtained by
+the elementary reflections $s_{\alpha_{i}}, \alpha_{i}\in S$. The next set of points that are obtained by
 two consecutive reflections $s_{\alpha_{i}}\cdot s_{\alpha_{j}}\triangleright\mu$ are obtained as
 the subtraction $\mu-\mu_{i}\alpha_{i}-\mu_{j} (s_{\alpha_{i}}\alpha_{j})$. Continuing this way we
-construct the image of singular element $\Psi=\sum_{w\in W} \varepsilon(w) e^{w(\mu+\rho)-\rho}$
-after the embedding $\phi$ \cite{2011arXiv1111.6787L}. The multiplicities in the character of Verma
-module are unchanged by the embedding since they are determined by additive properties of the roots.
-So we see that weight multiplicities of irreducible modules are also preserved by the embedding.
+construct the image of the singular element $\Psi=\sum_{w\in W} \varepsilon(w) e^{w(\mu+\rho)-\rho}$
+after the embedding $\phi$ \cite{2011arXiv1111.6787L}. The multiplicities in the character of the Verma
+module are unchanged by the embedding since they are determined by the additive properties of the roots.
+So we see that the weight multiplicities of irreducible modules are also preserved by the embedding.
 
-Root system of regular subalgebra is contained in the root system of algebra so splint is useful in
+The root system of the regular subalgebra is contained in the root system of the algebra so the splint is useful in the
 computation of branching coefficients.
@@
 In the paper \cite{2011arXiv1111.6787L} it was proven that the existence of splint leads to the
-coincidence of branching coefficients with weight multiplicities under certain conditions. We denote
+coincidence of branching coefficients with weight multiplicities under certain conditions. We denote a
 Lie algebra by $\gf$ and consider it's subalgebra $\af$. If $\af$ is a regular subalgebra, its root
 system $\Delta_{\af}$ is contained in $\Delta_{\gf}$. Branching coefficients $b^{(\mu)}_{\nu}$
-appear in decomposition of irreducible representation $L^{\mu}_{\gf}$ of $\gf$ to the sum of
+appear in the decomposition of an irreducible representation $L^{\mu}_{\gf}$ of $\gf$ to the sum of
 irreducible representations of $\af$:
@@
 
-Assume that root system $\Delta_{\gf}$ splinters as $\Delta_{\gf}=\Delta_{\af} \cup
-\phi(\Delta_{\sfr})$, where $\phi$ is an embedding of root system $\Delta_{\sfr}$ of some semisimple
+Assume that the root system $\Delta_{\gf}$ splinters as $\Delta_{\gf}=\Delta_{\af} \cup
+\phi(\Delta_{\sfr})$, where $\phi$ is an embedding of a root system $\Delta_{\sfr}$ of some semisimple
 Lie algebra $\sfr$. Then branching coefficients $b^{(\mu)}_{\nu}$ for the reduction
-$L^{(\mu)}_{\gf\downarrow \af}$ coincide with weight multiplicities $m^{(\tilde \mu)}_{\nu}$ in
-$\sfr$-representations provided certain technical condition holds \cite{2011arXiv1111.6787L}.
-Highest weight $\tilde\mu$ of $\sfr$-representation is calculated from Dynkin labels of highest
-weight $\mu$ of $\gf$-module.
+$L^{(\mu)}_{\gf\downarrow \af}$ coincide with the weight multiplicities $m^{(\tilde \mu)}_{\nu}$ in the $\sfr$-representations provided certain technical condition holds \cite{2011arXiv1111.6787L}.
+The highest weight $\tilde\mu$ of the $\sfr$-representation is calculated from the Dynkin labels of the highest
+weight $\mu$ of the $\gf$-module.
 
 In the next section \ref{sec:splints-root-systems} we review the classification of splints for simple
-root systems and results for branching coefficients. Then we move to the study of special embeddings
+root systems and the results for branching coefficients. Then we move to the study of special embeddings
 which is the main subject of the present paper. We consider special embeddings of Lie subalgebras
-into a Lie algebra. In this case root system of the subalgebra is not contained in the root system of
+into a Lie algebra. In this case the root system of the subalgebra is not contained in the root system of
 the algebra. So the original motivation for splints is not applicable. But we can consider the
-projection of root system of the algebra on the root space of the subalgebra. Such a projection is not a
+projection of the root system of the algebra on the root space of the subalgebra. Such a projection is not a
 root system anymore, but it satisfies milder conditions (Section \ref{sec:spec-embedd-proj}). It is
-possible to classify most projections using Dynkin diagrams augmented with multiplicities. We then
-define splint for such 'weak' root systems and state the conditions of its appearance and
-implications for the calculation of branching coefficients (Section \ref{sec:splints-spec-embedd}).
+possible to classify the splints of the projection using the fact that the adjoint representation of the algebra is decomposed into the direct sum of representations of the subalgebra.
+We show that if there is a splint then branching coefficients coincide with weight multiplicities of representations of another Lie algebra (Section \ref{sec:splints-spec-embedd}).
+Thus in this case branching coefficients are very easy to compute.
 
-Use of representation theory of the subalgebra allows us to classify all the splints for the projections
-of algebra root system. We also apply this method to metric splints and regular subalgebras and get
-a unified treatment. We obtain Gelfand-Tsetlin rules for regular and special embeddings this way.
+The use of representation theory of the subalgebra allows us to classify all the splints for the projections
+of the algebra root system. We also apply this method to metric splints and regular subalgebras and get
+a unified treatment. We obtain the Gelfand-Tsetlin rules for regular and special embeddings this way.
 
@@
 \label{sec:splints-root-systems}
-The notion and classification of
+The notion and the classification of
 splints for simple root systems were introduced in the paper \cite{richter2008splints}.
 
-%% Embedding $\phi$ of a root system $\Delta_1$ into a root system
-%% $\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
-%% subset of $\Delta$ that commutes with vector composition law in
-%% $\Delta_{1}$ and $\Delta$.
-%% \begin{equation*}
-%% \phi:\Delta_1 \longrightarrow \Delta
-%% \end{equation*}
-%% \begin{equation*}
-%% \phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
-%% \,\,\, \alpha,\beta \in \Delta_1
-%% \end{equation*}
-%% 
-%% Note that the image $Im(\phi)$ must not inherit the root system
-%% properties except the addition rules equivalent to the addition
-%% rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
-%% can splinter $\Delta$  when the latter can be presented 
-%% as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.   
-%% 
-%% The classification is shown in table
-%% 
 Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
@@
 to be a proper regular subalgebra and $\mathfrak{a}$ to be the
-maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed that is the rank
-$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.
+maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed, so that the rank
+$r$ of $\af$ is equal to that of $\mathfrak{g}$.
 
-Computation of branching coefficients relies on roots $\Delta_{\gf}\setminus \Delta_{\af}$
+The computation of branching coefficients relies on the roots $\Delta_{\gf}\setminus \Delta_{\af}$
 \cite{2010arXiv1007.0318L} so splint  is naturally connected to branching coefficients for regular
-subalgebra.
+subalgebras.
 
@@
 \begin{equation}
-\label{eq:1}
+\label{tab:1}
 \begin{array}{cc||c|c}
@@
 
-Note that in the case of $C_{r}$-series (marked with the star in table \eqref{eq:1}) metrical
-embedding $\Delta_{D_{r}}\to \Delta_{C_{r}}$ does not lead to the appearance of regular subalgebra
+Note that in the case of $C_{r}$-series (marked with the star in table \ref{tab:1}) the metrical
+embedding $\Delta_{D_{r}}\to \Delta_{C_{r}}$ does not lead to the appearance of the regular subalgebra
 $\mathfrak{a}$ (See \cite{dynkin1952semisimple}).
@@
 where $\epsilon\left( w\right)$ is a determinant of the element $w$ of the Weyl group $W_{\af}$ of
-the subalgebra $\af$. The action of Weyl group on the weights is extended to the algebra of formal
+the subalgebra $\af$. The action of the Weyl group on the weights is extended to the algebra of formal
 exponents by the rule $w\left(e^{\nu}\right)=e^{w\nu}, w\in W$. Hence, the multiplicity $M_{\left(
@@
 
-The study of specialy embedded subalgebras traces back to fundamental papers by Eugene Dynkin
+The study of specialy embedded subalgebras traces back to the fundamental papers by Eugene Dynkin
 \cite{dynkin1952semisimple,dynkin1952maximal} where he called such subalgebras ``S-subalgebras'' to
@@
 of the algebra root system. Thus regular subalgebras are easy to construct by dropping nodes from
-extended Dynkin diagram of the algebra, while the case of special subalgebras is more difficult. Complete
+the extended Dynkin diagram of the algebra, while the case of special subalgebras is more difficult. The complete
 classification for exceptional Lie algebras was obtained recently in \cite{minchenko2006semisimple}.
 The algorithm of the special subalgebras construction is available in GAP package but still requires
-manual intervention \cite{de2011constructing}.
+a manual intervention \cite{de2011constructing}.
 
-Assume that Lie algebra $\gf$ is simple. Let's denote a subalgebra by
+Assume that the Lie algebra $\gf$ is simple. Let's denote a subalgebra by
 $\af$. We denote corresponding Cartan subalgebras by $\hfg$ and $\hfa$ and identify them with the dual
-spaces $\hfg^{*}$, $\hfa^{*}$ using Killing forms of $\gf$ and $\af$.
+spaces $\hfg^{*}$, $\hfa^{*}$ using the Killing forms of $\gf$ and $\af$.
 
@@
 Lie algebra $\gf$. Then one needs to check that the generators of $\af$ can be presented as
-linear combinations of generators of $\gf$. We can identify Cartan subalgebra $\hfa\subset \af$ with
-dual space $\hfa^{*}$ using Killing form. Then the root system $\Delta_{\gf}$ of $\gf$ can be
+linear combinations of generators of $\gf$. We can identify the Cartan subalgebra $\hfa\subset \af$ with
+the dual space $\hfa^{*}$ using the Killing form. Then the root system $\Delta_{\gf}$ of $\gf$ can be
 projected to $\hfa^{*}$ using the expression of $\hfa$-generators through $\hfg$-generators.
@@
   Every special subalgebra $\af$ of a semisimple Lie algebra $\gf$ is integer, i.e. the projections of
-  roots of $\gf$ to $\hfa^{*}$ are linear combinations of simple roots of $\af$ with integer
+  the roots of $\gf$ to $\hfa^{*}$ are linear combinations of the simple roots of $\af$ with integer
   coefficients \cite{dynkin1952semisimple}
@@
   \noindent\centering{
-   \includegraphics[width=80mm]{Special-A2-D4-all-2}
+   \includegraphics[width=40mm]{Special-A2-D4-all-2}
   }
   \caption{Projection of $D_{4}$ ($so(8)$)-root system onto the root space of the special subalgebra $A_{2}$
-    ($su(3)$). Note that this roots system is $G_{2}$ but with non-trivial multiplicities. }
+    ($su(3)$). Note that this root system is $G_{2}$ but with non-trivial multiplicities. }
  \label{fig:d4-a2_splint}
@@
 some other algebra representations. Such a coincidence is possible when the projection $\Delta'$ of
-$\gf$ root system admits a splint $\Delta'=\varphi_{\af}(\Delta_{\af})\cup
+the $\gf$ root system admits a splint $\Delta'=\varphi_{\af}(\Delta_{\af})\cup
 \varphi_{\sfr}(\Delta_{\sfr})$, where $\varphi_{\af}$ and $\varphi_{\sfr}$ are the embeddings of
-corresponding root systems. The embedding $\varphi_{\af}$ is metric and trivial. Moreover, the
-projection of singular element $\pia\left(\Psi^{\mu}_{\gf}\right)$ should admit a decomposition into
-linear combination of singular elements of irreducible representations of $\sfr$:
+the corresponding root systems. The embedding $\varphi_{\af}$ is metric and trivial. Moreover, the
+projection of the singular element $\pia\left(\Psi^{\mu}_{\gf}\right)$ should admit a decomposition into
+a linear combination of singular elements of irreducible representations of $\sfr$:
 \begin{equation}
@@
 with integer coefficients $\varkappa_{\nu}$, where the sum is over the set of weights $\nu$ that
-will be determined later. First we classify all the splints of the projection of a root system into
+will be determined later.
+Such a decomposition of the singular element is very similar to the branching of Weyl group orbits considered in the papers \cite{larouche2011branching,larouche2009branching}.
+First we classify all the splints of the projection of a root system into
 a union of simple root systems for special embeddings, and then discuss the decomposition of singular
@@
 Projection of the $\gf$ root system $\Delta'$ coincides with the projection of the weight diagram of the
-adjoint representation of algebra $\gf$ with the exception of zero weight. The adjoint representation of
-$\gf$ contains adjoint representation of $\af$ and can be decomposed as
+adjoint representation of the algebra $\gf$ with the exception of zero weight. The adjoint representation of
+$\gf$ contains the adjoint representation of $\af$ and can be decomposed as
 \begin{equation}
@@
 their weight diagrams are root systems after the exclusion of zero weight. In order to do so we must
-note, that all the weights of $M^{\chi}_{\af}$ should have length not less than length of shortest
+note, that all the weights of $M^{\chi}_{\af}$ should have a length not less than the length of the shortest
 root of $\af$, since $\af$ is an integer subalgebra of $\gf$ \ref{dyn1}. Moreover, $M^{\chi}_{\af}$
@@
 \Delta_{\af},$ orthogonal to the root system of the subalgebra, one cannot proceed with the decomposition
-of singular element \eqref{eq:4}. The elements $e^{\nu}$ of $\pia\left(\Psi^{\mu}_{\gf}\right)$
-should be augmented with the dimensions of representations of algebra $\afb$ spanned by generators
-corresponding to orthogonal roots \cite{2010arXiv1007.0318L}. Then there will be non-trivial
-multiplicities in the right hand side of \eqref{eq:4} and no coincidence of branching coefficients
-with weight multiplicities of $\sfr$-representations. One can write more cumbersome relation between
-multiplicities and branching coefficients, but it is out of scope for the present paper.
+of the singular element \ref{eq:4}. The elements $e^{\nu}$ of $\pia\left(\Psi^{\mu}_{\gf}\right)$
+should be augmented with the dimensions of representations of the algebra $\afb$ spanned by generators
+corresponding to the orthogonal roots \cite{2010arXiv1007.0318L}. Then there will be non-trivial
+multiplicities in the right hand side of \ref{eq:4} and no coincidence of branching coefficients
+with the weight multiplicities of $\sfr$-representations. One can write more cumbersome relation between
+the multiplicities and branching coefficients, but it is out of scope for the present paper.
 
@@
 The list of strongly multiplicity free representations consists of (first) fundamental representations
-for series $A_{r}, B_{r}, C_{r}$, exceptional Lie algebra $G_{2}$ (7-dimensional representation) and
+for the series $A_{r}, B_{r}, C_{r}$, the exceptional Lie algebra $G_{2}$ (7-dimensional representation) and
 all $A_{1}$ representations.
@@
 
-Nevertheless, the union of diagrams of two fundamental representations of $A_{2}$ with the root
-system of $A_{2}$ produces weight diagram of $G_{2}$. This case corresponds to splint
+Nevertheless, the union of diagrams of the two fundamental representations of $A_{2}$ with the root
+system of $A_{2}$ produces a weight diagram of $G_{2}$. This case corresponds to splint
 $\Delta_{G_{2}}=\varphi_{1}( \Delta_{A_{2}})\cup \varphi_{2}(\Delta_{A_{2}})$ which is connected
-with regular subalgebra $A_{2}\subset G_{2}$ (see Section \ref{sec:splints-root-systems}).
+with the regular subalgebra $A_{2}\subset G_{2}$ (see Section \ref{sec:splints-root-systems}).
 
-First fundamental representation of $B_{r}$ immediately gives us the splint $\Delta'=\pi_{B_{r}}\left(
-\Delta_{D_{r+1}}\right) = \Delta_{B_{r}}\cup \Delta_{A_{1}+\dots+A_{1}}$ corresponding to Gelfand-Tsetlin
+The first fundamental representation of $B_{r}$ immediately gives us the splint $\Delta'=\pi_{B_{r}}\left(
+\Delta_{D_{r+1}}\right) = \Delta_{B_{r}}\cup \Delta_{A_{1}+\dots+A_{1}}$ corresponding to the Gelfand-Tsetlin
 multiplicity-free branching for the special embedding $\mathfrak{so}(2r+1)\to \mathfrak{so}(2r+2)$.
@@
 
-If there are vectors of different length in the projection $\Delta'$ on the subalgebra $A_{1}$, such a
+If there are vectors of a different length in the projection $\Delta'$ on the subalgebra $A_{1}$, such a
 projection is not multiplicity free, and $\Delta_{\sfr}$ contains parallel roots. The simplest case
@@
 %% 
-The weight diagram of the seven-dimensional representation of $G_{2}$ together with $G_{2}$ root system
-form the projection of the root system $B_{3}$ which corresponds to special embedding 
-$G_{2}\to B_{3}$. Branching coefficients in this case coincide with weight multiplicities of
-representations of algebra $\sfr=A_{2}$ with image of root system consisting of short roots of
+The weight diagram of the seven-dimensional representation of $G_{2}$ together with the $G_{2}$ root system
+form the projection of the root system $B_{3}$ which corresponds to the special embedding 
+$G_{2}\to B_{3}$. The branching coefficients in this case coincide with the weight multiplicities of
+representations of algebra $\sfr=A_{2}$ with the image of the root system consisting of the short roots of
 $G_{2}$.
@@
 
-Minuscule representations are well-studied and very useful in computations of e.g. tensor products
+Minuscule representations are well-studied and very useful in the computations of e.g. tensor products
 \cite{stembridge2003multiplicity,stembridge2001computational}. The minuscule representations are
@@
 representation that is not minuscule for each simple Lie algebra. The multiplicity of the zero 
-weight in quasi-minuscule representation is the number of short nodes of the Dynkin diagram.
+weight in quasi-minuscule representation is the number of the short nodes of the Dynkin diagram.
 
-List of minuscule representations consists of tensor powers of vector
+The list of the minuscule representations consists of tensor powers of the vector
 representation for the series $A_{r}$; spin representations for the series
 $B_{r}$; vector representations for $C_{r}$; vector and two half-spin for $D_{r}$; two
-27-dimensional representations for $E_{6}$ and 56-dimensional representation of $E_{7}$.
+27-dimensional representations for $E_{6}$ and the 56-dimensional representation of $E_{7}$.
 
-Quasi-minuscule representations that are not minuscule are: adjoint representation of $A_{r}$,
-vector representation for $B_{r}$, $2r^{2}-r-1$-dimensional representation for $C_{r}$, adjoint
-representations for $D_{r}, E_{6}, E_{7}, E_{8}$, 26-dimensional representation for $F_{4}$ and
-7-dimensional of $G_{2}$.
+Quasi-minuscule representations that are not minuscule are: the adjoint representation of $A_{r}$,
+the vector representation for $B_{r}$, the $2r^{2}-r-1$-dimensional representation for $C_{r}$, the adjoint
+representations for $D_{r}, E_{6}, E_{7}, E_{8}$, the 26-dimensional representation for $F_{4}$ and
+the 7-dimensional of $G_{2}$.
 
@@
 
-Classification of multiplicity-free irreducible highest weight modules $L^{\mu}$ in
+The classification of the multiplicity-free irreducible highest weight modules $L^{\mu}$ in
 \cite{howe1995perspectives,stembridge2003multiplicity} consists of the following classes:
@@
 
-We see that case (1) contains strongly multiplicity free modules of series $A_{r}$ and exceptional
-Lie algebra $G_{2}$, class (2) contains strongly multiplicity free modules of $ B_{r}$ and $C_{r}$ ,
-strongly multiplicity free modules of $A_{1}$ are included in class (4).
+We see that the case (1) contains strongly multiplicity free modules of the series $A_{r}$ and the exceptional
+Lie algebra $G_{2}$, the class (2) contains strongly multiplicity free modules of $ B_{r}$ and $C_{r}$ ,
+strongly multiplicity free modules of $A_{1}$ are included in the class (4).
 
-We do not need to consider minuscule representations for simply-laced Lie algebras, since in this
-case length of the weights of representation $M^{\chi}_{\af}$ is less than length of $\af$ roots,
+We do not need to consider the minuscule representations for the simply-laced Lie algebras, since in this
+case the length of the weights of the representation $M^{\chi}_{\af}$ is less than the length of the $\af$ roots,
 that contradicts to $\af$ being an integer subalgebra. For the series $B_{r}$ we have already
-discussed minuscule spin representation, since it is strongly multiplicity free. The last case in
+discussed the minuscule spin representation, since it is strongly multiplicity free. The last case in
 (1) is the vector representation for $C_{r}$. It is $2r$-dimensional, but the length of its highest weight $\omega_{1}$ is less
@@
 %% 
-Case (2) consists of the series $B_{r}$ and the exceptional root system $G_{2}$. The embedding $G_{2}\to
+The case (2) consists of the series $B_{r}$ and the exceptional root system $G_{2}$. The embedding $G_{2}\to
 B_{3}$ was already discussed. 
  The dimension of the adjoint representation for the series $B_{r}$
-is $2r^{2}+r$ and of quasi-minuscule representation it is $2r+1$, so the dimension of the algebra
+is $2r^{2}+r$ and of the quasi-minuscule representation it is $2r+1$, so the dimension of the algebra
 $\gf$ should be $(r+1)(2r+1)$ with the $\mathrm{rank}\gf=r+1$. The only solution is $\gf=D_{r+1}$
-and we have already seen that this case corresponds to strongly multiplicity free module and
-Gelfand-Tsetlin basis.
+and we have already seen that this case corresponds to the strongly multiplicity free module and
+the Gelfand-Tsetlin basis.
 
-In case (3) the diagram of the representation contains weights with the length smaller than the
-length of short root, so it cannot be a projection of $\Delta_{\gf}$ to an integer subalgebra.
+In the case (3) the diagram of the representation contains weights with the length smaller than the
+length of the short root, so it cannot be a projection of $\Delta_{\gf}$ to an integer subalgebra.
 
-We need to consider representations of class (4) only for $m=1,2$ since the root system $\Delta_{\sfr}$
+We need to consider representations of the class (4) only for $m=1,2$ since the root system $\Delta_{\sfr}$
 can have roots of at most two different lengths. In the case $m=1$ we get strongly multiplicity free
 modules of $A_{r}$ which were discussed above. And for algebra $A_{2}$ and $m=2$ the weight diagram
-of representation $L^{2\omega_{1}}_{A_{2}}$ coincides with the root system of exceptional Lie algebra
+of the representation $L^{2\omega_{1}}_{A_{2}}$ coincides with the root system of the exceptional Lie algebra
 $G_{2}$. This case appears in the special embedding $A_{2}\to B_{3}$. But for $A_{r}, r>2$ there are
-no root systems that coincide with weight diagram of $L^{2\omega_{1}}_{A_{r}}$.
+no root systems that coincide with the weight diagram of $L^{2\omega_{1}}_{A_{r}}$.
 
@@
 decomposed into two adjoint representations of $\af$ (and possibly several trivial
-representations) we need to satisfy following conditions:
+representations) we need to satisfy the following conditions:
 \begin{itemize}
@@
 For the adjoint representation of algebra $A_{r}$ we see that the projection $\Delta'$ of the root system
-$\Delta_{\gf}$ should consist of roots of subalgebra $\af=A_{r}$ with multiplicity 2. The total
-number of roots for $A_{r}$ is $r(r+1)$, so $\Delta'$ and $\Delta_{\gf}$ contain $2r(r+1)$ roots,
+$\Delta_{\gf}$ should consist of roots of the subalgebra $\af=A_{r}$ with the multiplicity 2. The total
+number of the roots for $A_{r}$ is $r(r+1)$, so $\Delta'$ and $\Delta_{\gf}$ contain $2r(r+1)$ roots,
 since there are no roots orthogonal to $\Delta_{\af}$. There are two possible solutions for
@@
 representation of $D_{r+1}$ cannot be decomposed as twice the adjoint representation of $A_{r}$.
-There is no corresponding embedding $A_{r}\to D_{r+1}$ and no splint. We see that conditions
-\eqref{eq:5}\eqref{eq:6} do not hold.
+There is no corresponding embedding $A_{r}\to D_{r+1}$ and no splint. We see that the conditions
+\ref{eq:5}\ref{eq:6} do not hold.
 
@@
 decomposed into two adjoint representations of $B_{r}$. It is straightforward to check that there is
-no solutions for $\gf$ satisfying the \eqref{eq:5}\eqref{eq:6} for the series $A$, $B$, $C$,
+no solutions for $\gf$ satisfying the \ref{eq:5}\ref{eq:6} for the series $A$, $B$, $C$,
 $D$ and all exceptional simple Lie algebras.
 
-Since the number of roots of root system $C_{r}$ is the same as for $B_{r}$ and we need to check the
+Since the number of roots of the root system $C_{r}$ is the same as for $B_{r}$ and we need to check the
 same cases, we see that there is no embedding for $C_{r}$ too.
@@
 The adjoint representation of $G_{2}$ gives us the algebra $D_{4}$ as the solution of the
-constraints \eqref{eq:5}\eqref{eq:6}. The embedding $G_{2}\to D_{4}$ exists, since there are
-embeddings $G_{2}\to B_{3}$ and $B_{3}\to D_{4}$, but the decomposition of adjoint representation of
+constraints \ref{eq:5}\ref{eq:6}. The embedding $G_{2}\to D_{4}$ exists, since there are
+embeddings $G_{2}\to B_{3}$ and $B_{3}\to D_{4}$, but the decomposition of the adjoint representation of
 $D_{4}$ is different: $ \mathrm{ad}_{D_{4}}=\mathrm{ad}_{G_{2}}\oplus 2 L^{\omega_{1}}_{G_{2}}$. So
@@
 For the adjoint representation of $F_{4}$ there is no solution that satisfies conditions
-\eqref{eq:5}\eqref{eq:6}.
+\ref{eq:5}\ref{eq:6}.
 
@@
 $(e_1,e_2,\dots,e_{n+1})$, then the Weyl group $W_{D_{n+1}}$ will act on it by permutating $a_i$ and
-changing their signs. After the projection the last coefficient in every element will be cut. Among
+changing their signs. After the projection the last coefficient in the every element will be cut. Among
 these elements will be groups in which all elements will have the same set of $a_i$ standing in
@@
 from $(a_1,a_2,\dots,a_{n})$ by consequent subtraction of $\mu_i e_i$ starting with $\mu_n e_n$,
-where $\mu_i$ is Dynkin labels of $\mu$ plus $1$. As it turns out, if one were to add to this set
-the required weights with corresponding singular multiplicities to construct the singular element of
-$\sfr=A_1+A_1+\dots+A_1$ as was done in the Introduction of this paper, all additional weight would
+where $\mu_i$ is the Dynkin labels of $\mu$ plus $1$. As it turns out, if one were to add to this set
+the required weights with the corresponding singular multiplicities to construct the singular element of
+$\sfr=A_1+A_1+\dots+A_1$ as was done in the Introduction of this paper, all additional weights would
 lie on the boundaries of the fundamental Weyl chamber $\bar C_{B_n}$. This fact is easily proved by
@@
 }^{[\mu_1,\mu_2,\dots,\mu_{n+1}]}=M_{\left( \sfr\right) \widetilde{\nu }}^{[\mu_1,\mu_2,\dots,\mu_{n}]}, 
-\label{bran1}
+\label{bran11}
 \end{equation}
@@
 \includegraphics[width=0.95\linewidth]{drawing-1}
-\caption{Splint $D_3= B_2\cup A_1+A_1$: projection of the singular element $\Phi_{D_3}^{[1,1,2]}$ can be made from singular elements $\Phi_{A_1+A_1}^{[1,1]}$.
+\caption{Splint $D_3= B_2\cup A_1+A_1$: the projection of the singular element $\Phi_{D_3}^{[1,1,2]}$ can be made from singular elements $\Phi_{A_1+A_1}^{[1,1]}$.
 Light-grey area is the fundamental Weyl chamber of subalgebra $B_2$.}
@@
 \includegraphics[width=0.9\linewidth,viewport=0 0 157 157,clip]{drawing-3}
-\caption{Injection fan applied to the singular element $\Phi_{A_1+A_1}^{[1,1]}$ yields branching coefficients that are equal to 1.}
+\caption{The injection fan applied to the singular element $\Phi_{A_1+A_1}^{[1,1]}$ yields branching coefficients that are equal to 1.}
 \label{ris2}
@@
 
-Careful examination of the embedding $G_{2}\to B_{3}$ leads to exactly the  same conclusion.
+A careful examination of the embedding $G_{2}\to B_{3}$ leads to exactly the same conclusion.
 
@@
 simplify calculation of the branching rules but one may use the properties of special embeddings and
-the projections to creat a perepesentation theory for the systems that are not root systems.
+the projections to creat a repesentation theory for the systems that are not root systems.
 
@@
 \begin{equation}
-\label{eq:1}
+\label{tab:2}
 \begin{array}{cc||c|c}
@@
 
-Computation of branching coefficients is important for different physical models with symmetry
+The computation of branching coefficients is important for different physical models with a symmetry
 breaking. This computation is drastically simplified if branching coefficients coincide with weight
-multiplicities, since efficient Freudental formula can be used \cite{moody1982fast}. Classification
+multiplicities, since efficient Freudental formula can be used \cite{moody1982fast}. The classification
 of splints for regular and special embeddings gives us all the cases when this coincidence takes
 place. Aside from computational importance, this coincidence is very interesting from
-representation-theoretic point of view, because it follows from new unexpected connection between
+representation-theoretic point of view, because it follows from the new unexpected connection between
 different simple Lie algebras.
 
-There exist special embeddings of semisimple Lie-algebras into simple Lie-algebras. For such
+There exist special embeddings of semisimple Lie algebras into simple Lie algebras. For such
 embeddings the procedure of finding splints that allow to calculate branching coefficient is similar
@@
 \bibliography{special-bibliography}{} 
-\bibliographystyle{apalike}
-%%  \bibitem{d1}
-%%  {\it Е.Б.Дынкин}
-%%  Полупростые подалгебры полупростых алгебр.
-%%  // Тр. Моск. матем. об-ва, т.1, стр. 39-166 (1952)
-%%  \bibitem{d2}
-%%  {\it Е.Б.Дынкин}
-%%  Максимальные подгруппы классических групп.
-%%  // Труды Моск. матем. об-ва, т. 1 (1952)
-%%  
-%%  
+\bibliographystyle{iopart-num}
+
 \end{document}

### 2015-03-21 AffineLieAlgebras/Splints/special-paper.tex
Submitted to TMPh on February 2015

@@
-\documentclass[12pt]{iopart}
+\documentclass[12pt]{article}
 
-%\usepackage{amsfonts}
+\baselineskip=20pt
+\hsize=340pt
+\vsize=490pt
+
+\usepackage{amssymb}
+
+\usepackage{color,graphicx}
+
+\usepackage{amsmath}
+
+\usepackage{amsmath,amssymb,amsthm}
 \usepackage{pb-diagram}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\usepackage{iopams,setstack}
 \usepackage{multicol}
@@
 
-\ftc{Splints of root systems for special Lie subalgebras}
+\title{Splints of root systems for special Lie subalgebras}
 
-\author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$, P.I.~Kakin$^{1}$}
-\address{ $^1$ Department of High-energy and elementary particle physics,  St Petersburg State University, 198904, Saint-Petersburg, Russia}
-\ead{ $^{2}$ e-mail: antonnaz@gmail.com}
+\author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$, P.I.~Kakin$^{1}$\\
+  {\small $^1$ Department of High-energy and elementary particle physics,}\\ {\small St Petersburg State University}\\
+  {\small 198904, Saint-Petersburg, Russia,}\\
+  {\small $^{2}$ e-mail: antonnaz@gmail.com}}
+%\date{}
+%\address{ $^1$ Department of High-energy and elementary particle physics,  St Petersburg State University, 198904, Saint-Petersburg, Russia}
+%\address{ $^{2}$ e-mail: anton.nazarov@hep.phys.spbu.ru}
+
+\maketitle
 
@@
 \end{abstract}
-
-\submitto{\jpa}
 
@@
 weight $\mu$ of the $\gf$-module.
-
-In the next section \ref{sec:splints-root-systems} we review the classification of splints for simple
-root systems and the results for branching coefficients. Then we move to the study of special embeddings
-which is the main subject of the present paper. We consider special embeddings of Lie subalgebras
-into a Lie algebra. In this case the root system of the subalgebra is not contained in the root system of
-the algebra. So the original motivation for splints is not applicable. But we can consider the
-projection of the root system of the algebra on the root space of the subalgebra. Such a projection is not a
-root system anymore, but it satisfies milder conditions (Section \ref{sec:spec-embedd-proj}). It is
-possible to classify the splints of the projection using the fact that the adjoint representation of the algebra is decomposed into the direct sum of representations of the subalgebra.
-We show that if there is a splint then branching coefficients coincide with weight multiplicities of representations of another Lie algebra (Section \ref{sec:splints-spec-embedd}).
-Thus in this case branching coefficients are very easy to compute.
-
-The use of representation theory of the subalgebra allows us to classify all the splints for the projections
-of the algebra root system. We also apply this method to metric splints and regular subalgebras and get
-a unified treatment. We obtain the Gelfand-Tsetlin rules for regular and special embeddings this way.
-
-In conclusion \ref{sec:conclusion} we discuss the cases when the projection of the root system does
-not fall into the classification mentioned above.
-
-\section{Splints of root systems and regular subalgebras}
-\label{sec:splints-root-systems}
-The notion and the classification of
-splints for simple root systems were introduced in the paper \cite{richter2008splints}.
-
-Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
-\mathfrak{a}\hookrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
-is a
-reductive subalgebra $\mathfrak{a \subset g}$ with correlated root spaces: $%
-\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset \mathfrak{h}_{\mathfrak{g }%
-}^{\ast }$. Let $\mathfrak{a}^{\mathfrak{s}}$ be a semisimple summand of
-$\mathfrak{a}$,
-this means that $\mathfrak{a}=\mathfrak{a}^{\mathfrak{s}} \oplus \mathfrak{u}(1)\oplus %
-\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^{\mathfrak{s}}$
-to be a proper regular subalgebra and $\mathfrak{a}$ to be the
-maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed, so that the rank
-$r$ of $\af$ is equal to that of $\mathfrak{g}$.
-
-The computation of branching coefficients relies on the roots $\Delta_{\gf}\setminus \Delta_{\af}$
-\cite{2010arXiv1007.0318L} so splint  is naturally connected to branching coefficients for regular
-subalgebras.
-
-Only three types of splints are
-injective and thus are naturally connected to branching \cite{richter2008splints}:
-\begin{equation}
-\label{tab:1}
-\begin{array}{cc||c|c}
-\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
-_{\frak{a}}\hspace{0.25in} & \hspace{0.25in}\Delta _{\sfr}\hspace{0.25in}
-\\ \hline\hline
-\hbox{(i)} & G_{2} & A_{2} & A_{2} \\
-& F_{4} & D_{4} & D_{4} \\ \hline
-\hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
-(*)& C_{r}(r\geq 3) & \oplus ^{r}A_{1} &  D_{r} \\ \hline
-\hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
-^{r}A_{1} \\
-& B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
-\end{array}
-\end{equation}
-
-Each row in the table gives a splint $(\Delta _{\frak{a}},\Delta _{\sfr})
-$ of the simple root system $\Delta $. In the first two types both $\Delta _{%
-\frak{a}}$ and $\Delta _{\sfr}$ are embedded metrically. Stems in the
-first type splints are equivalent and in the second are not. In the third
-type splints only $\Delta _{\frak{a}}$ is embedded metrically. The summands $%
-u\left( 1\right) $ are added to keep $r_{\frak{a}}=r$. This does not change
-the principle properties of branching but makes it possible to use the
-multiplicities of $\sfr$ -modules without further projecting their
-weights.
-
-Note that in the case of $C_{r}$-series (marked with the star in table \ref{tab:1}) the metrical
-embedding $\Delta_{D_{r}}\to \Delta_{C_{r}}$ does not lead to the appearance of the regular subalgebra
-$\mathfrak{a}$ (See \cite{dynkin1952semisimple}).
-
-In the paper \cite{2011arXiv1102.1702L} it was shown that
-
-\begin{Prop}
-There is a decomposition of a singular element of the algebra $\gf$ into singular elements of the subalgebra $\sfr$:
+The proof of the coincidence of the branching coefficients with the weight multiplicities of
+$\sfr$-module is based upon the decomposition of singular element of the algebra $\gf$ into singular
+elements for $\sfr$:
 \begin{equation}
@@
 \end{equation}
-\end{Prop} 
-%% Rewrite this property informally
+
+We use similar approach to study special embeddings. We consider special embeddings of Lie
+subalgebras into a Lie algebra. In this case the root system of the subalgebra is not contained in
+the root system of the algebra. So the original motivation for splints is not applicable. But we can
+consider the projection of the root system of the algebra on the root space of the subalgebra. Such
+a projection is not a root system anymore, but it satisfies milder conditions (Section
+\ref{sec:spec-embedd-proj}). It is possible to classify the splints of the projection using the fact
+that the adjoint representation of the algebra is decomposed into the direct sum of representations
+of the subalgebra. We show that if there is a splint then branching coefficients coincide with
+weight multiplicities of representations of another Lie algebra (Section
+\ref{sec:splints-spec-embedd}). Thus in this case branching coefficients are very easy to compute.
+
+The use of representation theory of the subalgebra allows us to classify all the splints for the projections
+of the algebra root system. We also apply this method to metric splints and regular subalgebras and get
+a unified treatment. We obtain the Gelfand-Tsetlin rules for regular and special embeddings this way.
+
+In conclusion \ref{sec:conclusion} we discuss the cases when the projection of the root system does
+not fall into the classification mentioned above.
 
@@
 
-As an example we present a projection $\Delta'$ of the root system of $D_{4}$ to the root system of the special
-subalgebra $A_{2}$ (Fig. \ref{fig:d4-a2_splint}).
-
-\begin{figure}[h!bt]
-  \noindent\centering{
-   \includegraphics[width=40mm]{Special-A2-D4-all-2}
-  }
-  \caption{Projection of $D_{4}$ ($so(8)$)-root system onto the root space of the special subalgebra $A_{2}$
-    ($su(3)$). Note that this root system is $G_{2}$ but with non-trivial multiplicities. }
- \label{fig:d4-a2_splint}
-\end{figure}
+For example the projection of the root system of $D_{4}$($so(8)$) to the root system of the special
+subalgebra $A_{2}$($su(3)$) coincides with the root system $G_{2}$, but the short roots have the multiplicity $3$.
 
@@
 $\Delta_{G_{2}}=\varphi_{1}( \Delta_{A_{2}})\cup \varphi_{2}(\Delta_{A_{2}})$ which is connected
-with the regular subalgebra $A_{2}\subset G_{2}$ (see Section \ref{sec:splints-root-systems}).
+with the regular subalgebra $A_{2}\subset G_{2}$ (see \cite{2011arXiv1111.6787L}).
 
@@
 
-\section*{Conclusion}
+\section{Conclusion}
 \label{sec:conclusion}
@@
 \bibliography{special-bibliography}{} 
-\bibliographystyle{iopart-num}
+\bibliographystyle{utphys}
 

### 2015-03-21 AffineLieAlgebras/Splints/special-paper-ru.tex
Russian translation started

--- 2015-03-21 AffineLieAlgebras/Splints/special-paper.tex
@@
 \usepackage[utf8x]{inputenc}
-\usepackage[english]{babel}
+\usepackage[english,russian]{babel}
 
@@
 
-\title{Splints of root systems for special Lie subalgebras}
+\title{Сплинты корневых систем для специальных подалгебр Ли}
 
-\author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$, P.I.~Kakin$^{1}$\\
-  {\small $^1$ Department of High-energy and elementary particle physics,}\\ {\small St Petersburg State University}\\
-  {\small 198904, Saint-Petersburg, Russia,}\\
+\author{В.Д.~Ляховский$^1$, А.А.~Назаров$^{1,2}$, П.И.~Какинь$^{1}$\\
+  {\small $^1$ Кафедра физики высоких энергий и элементарных частиц,}\\ {\small Санкт-Петербургский государственный университет}\\
+  {\small 198904, Санкт-Петербург, Россия}\\
   {\small $^{2}$ e-mail: antonnaz@gmail.com}}
@@
 \begin{abstract}
-  Splint is a decomposition of root system into a union of root systems. Splint of root system for a
-  simple Lie algebra appears naturally in the studies of (regular) embeddings of reductive
-  subalgebras. Splint can be used to construct branching rules. We consider a special embedding of a
-  Lie subalgebra into a simple Lie algebra. We classify the projections of algebra root systems and
-  single out the conditions of splint appearance and coincidence of branching coefficients with
-  weight multiplicities. While such a coincidence is not very common it is connected with
-  Gelfand-Tsetlin basis.
+  Расщепление или сплинт -- это разложение корневой системы в объединение нескольких корневых
+  систем. Сплинт возникает при изучении (регулярных) вложений редуктивных подалгебр. Его можно
+  использовать для построения правил ветвления представлений. Мы рассматриваем специальное вложения
+  подалгебры Ли в простые алгебры Ли, классифицируем проекции корневых систем алгебр и выводим
+  условия возникновения сплинта и совпадения коэффициентов ветвления с кратностями весов. Хотя
+  такое совпадение происходит не слишком часто, оно оказывается связано с базисом Гельфанда-Цетлина.
 
-\noindent{\it Keywords\/}: Lie algebra, special subalgebra, branching, weight multiplicity, splint
+\noindent{\it Keywords\/}: Алгебра Ли, специальная подалгебра, ветвление, кратность весов, сплинт
 \end{abstract}
 
-\section{Introduction}
+\section{Введение}
 \label{sec:introduction}
 
-The notion of splint was introduced by David Richter in the paper \cite{richter2008splints}. Splint
-is a decomposition of a root system into a disjoint union of the images of two or more embeddings of some
-other root systems. An embedding $\phi$ of a root system $\Delta_1$ into a root system $\Delta$ is a
-bijective map of roots of $\Delta_{1}$ to a (proper) subset of $\Delta$ that commutes with the vector
-composition law in $\Delta_{1}$ and $\Delta$.
+Понятие сплинта (расщепления) было предложено Дэвидом Рихтером в работе \cite{richter2008splints}.
+Сплинт -- это разложение корневой системы в объединение образов двух или более вложений других
+корневых систем. Вложением  $\phi$ корневой системы $\Delta_1$ в корневую систему  system $\Delta$
+называется биективное отображение корней $\Delta_{1}$ в (собственное) подмножество  $\Delta$,
+коммутирующее с  законом сложения векторов в $\Delta_{1}$ и $\Delta$.
 \begin{equation*}
@@
 
-Note that the image $Im(\phi)$ is not required to inherit the root system properties except the
-addition rules equivalent to the addition rules in $\Delta_{1}$ (for pre-images). If an embedding
-$\phi$ preserves the angles between the roots it is called ``metric''. Two embeddings $\phi_1$ and
-$\phi_2$ can splinter $\Delta$ when the latter can be presented as a disjoint union of images
-$Im(\phi_1)$ and $Im(\phi_2)$.
+Заметим, что мы не требуем от образа $Im(\phi)$ сохранения свойств корневой системы за исключением
+совпадения правил сложения с правилами сложения в $\Delta_{1}$ (для прообразов). Если вложение
+$\phi$ сохраняет углы между корнями, то оно называется ``метрическим''. Два вложения $\phi_1$ и
+$\phi_2$ расщепляют корневую систему $\Delta$, если последняя может быть представлена в виде
+дизъюнктного образов $Im(\phi_1)$ и $Im(\phi_2)$.
 
-Why one would consider non angle-preserving maps of root systems? Additive properties of the root system
-determine the structure of the Verma module:
+Чем же интересны отображения корневых систем, не сохраняющие углов между корнями? Аддитивные
+свойства корневой системы определяют структуру модуля Верма:
     \begin{equation*}
@@
     \end{equation*}
-Here $\bff_{+}$ is the Borel subalgebra of $\gf$, $D^{\mu}$ is its one-dimensional representation,
-$\left|v_{\mu}\right>$ is the highest weight vector and $E^{-\alpha_{j}}$ are lowering operators
-that are in correspondence with positive roots $\alpha_{j}\in \Delta^{+}$. 
-The Weyl character formula expresses a character of an irreducible representation as a combination of
-the characters of the Verma modules: 
+Здесь $\bff_{+}$ -- подалгебра Бореля алгебры $\gf$, $D^{\mu}$ -- одномерное представление
+подалгебры Бореля, $\left|v_{\mu}\right>$ -- вектор старшего веса, а  $E^{-\alpha_{j}}$ --
+понижающие операторы, соответствующие положительным корням $\alpha_{j}\in \Delta^{+}$. 
+Формула Вейля для характеров выражает характер неприводимого представления в виде комбинации характеров
+модулей Верма: 
 \begin{equation*}
@@
 \end{equation*}
-Here the sum is over elements of the Weyl group and their actions $w\triangleright \mu
-=w(\mu+\rho)-\rho$ depend on angles between roots. But we can rewrite the Weyl character formula
-representing the Weyl group elements as the products of the reflections $s_{\alpha}, \alpha \in S$ in
-the hyperplanes orthogonal to the simple roots: $w=s_{\alpha_{1}}\cdot s_{\alpha_{2}}\dots$. The reflections act
-on the root system by permutations, so the composition of such an action with the embedding $\phi$ is easily
-obtained. The orbit of the Weyl group action $w\triangleright \mu, w\in W$, can be constructed by
-subtractions of roots from the highest weight $\mu$. Let's denote the Dynkin labels of $\mu$ by
-$(\mu_{1},\dots \mu_{r})$. Then $\mu-\mu_{1}\alpha_{1}, \mu-\mu_{2}\alpha_{2},\dots,
-\mu-\mu_{r}\alpha_{r}, \alpha_{i}\in S$, are the points of the orbit that can be obtained by
-the elementary reflections $s_{\alpha_{i}}, \alpha_{i}\in S$. The next set of points that are obtained by
-two consecutive reflections $s_{\alpha_{i}}\cdot s_{\alpha_{j}}\triangleright\mu$ are obtained as
-the subtraction $\mu-\mu_{i}\alpha_{i}-\mu_{j} (s_{\alpha_{i}}\alpha_{j})$. Continuing this way we
-construct the image of the singular element $\Psi=\sum_{w\in W} \varepsilon(w) e^{w(\mu+\rho)-\rho}$
-after the embedding $\phi$ \cite{2011arXiv1111.6787L}. The multiplicities in the character of the Verma
-module are unchanged by the embedding since they are determined by the additive properties of the roots.
-So we see that the weight multiplicities of irreducible modules are also preserved by the embedding.
+Здесь суммирование ведется по элементам группы Вейля, действие которых $w\triangleright \mu
+=w(\mu+\rho)-\rho$ зависит от углов между корнями. Но формулу Вейля для характеров можно переписать,
+представив элементы группы Вейля в виде произведений отражений $s_{\alpha}, \alpha \in S$ в
+гиперплоскостях, ортогональных простым корням: $w=s_{\alpha_{1}}\cdot s_{\alpha_{2}}\dots$.
+Отражения действуют на корневую систему перестановками, так что композицию такого действия с
+вложением $\phi$ нетрудно вычислить. Орбиту группы Вейля $w\triangleright \mu, w\in W$ можно
+построить последовательными вычитаниями корней из старшего веса $\mu$. Для этого обозначим индексы
+Дынкина веса $\mu$ через $(\mu_{1},\dots \mu_{r})$. Тогда $\mu-\mu_{1}\alpha_{1},
+\mu-\mu_{2}\alpha_{2},\dots, \mu-\mu_{r}\alpha_{r}, \alpha_{i}\in S$ -- это веса орбиты, которые
+получаются из старшего веса $\mu$ элементарными отражениями $s_{\alpha_{i}}, \alpha_{i}\in S$.
+Следующий набор точек орбиты, получаемых последовательным применением двух отражений
+$s_{\alpha_{i}}\cdot s_{\alpha_{j}}\triangleright\mu$, можно построить путем вычитания
+$\mu-\mu_{i}\alpha_{i}-\mu_{j} (s_{\alpha_{i}}\alpha_{j})$. Продолжая данную процедуру, мы построим
+образ сингулярного элемента $\Psi=\sum_{w\in W} \varepsilon(w) e^{w(\mu+\rho)-\rho}$ под действием
+вложения $\phi$ \cite{2011arXiv1111.6787L}. Кратности в характере модуля Верма не меняются при
+вложении, так как они определяются аддитивными свойствами корней. Соответственно, при вложении
+сохраняются и кратности в неприводимых модулях.
 
-The root system of the regular subalgebra is contained in the root system of the algebra so the splint is useful in the
-computation of branching coefficients.
+Корневая система регулярной подалгебры содержится в корневой системе алгебры, так что сплинт
+возникает при вычислении коэффициентов ветвления.
 
-In the paper \cite{2011arXiv1111.6787L} it was proven that the existence of splint leads to the
-coincidence of branching coefficients with weight multiplicities under certain conditions. We denote a
-Lie algebra by $\gf$ and consider it's subalgebra $\af$. If $\af$ is a regular subalgebra, its root
-system $\Delta_{\af}$ is contained in $\Delta_{\gf}$. Branching coefficients $b^{(\mu)}_{\nu}$
-appear in the decomposition of an irreducible representation $L^{\mu}_{\gf}$ of $\gf$ to the sum of
-irreducible representations of $\af$:
+В работе  \cite{2011arXiv1111.6787L} было показано, что существование сплинта ведет к совпадению
+коэффициентов ветвления с кратностями весов при выполнении некоторых дополнительных условий.
+Обозначим алгебру Ли через $\gf$ и рассмотрим ее подалгебру $\af$. Если подалгебра  $\af$ регулярна,
+то ее корневая система  $\Delta_{\af}$ содержится в $\Delta_{\gf}$. Коэффициенты ветвления $b^{(\mu)}_{\nu}$
+появляются при разложении неприводимого представления  $L^{\mu}_{\gf}$ алгебры $\gf$ в сумму
+неприводимых представлений подалгебры $\af$:
 \begin{equation}
@@
 
-Assume that the root system $\Delta_{\gf}$ splinters as $\Delta_{\gf}=\Delta_{\af} \cup
-\phi(\Delta_{\sfr})$, where $\phi$ is an embedding of a root system $\Delta_{\sfr}$ of some semisimple
-Lie algebra $\sfr$. Then branching coefficients $b^{(\mu)}_{\nu}$ for the reduction
-$L^{(\mu)}_{\gf\downarrow \af}$ coincide with the weight multiplicities $m^{(\tilde \mu)}_{\nu}$ in the $\sfr$-representations provided certain technical condition holds \cite{2011arXiv1111.6787L}.
-The highest weight $\tilde\mu$ of the $\sfr$-representation is calculated from the Dynkin labels of the highest
-weight $\mu$ of the $\gf$-module.
-The proof of the coincidence of the branching coefficients with the weight multiplicities of
-$\sfr$-module is based upon the decomposition of singular element of the algebra $\gf$ into singular
-elements for $\sfr$:
+Предположим, что корневая система $\Delta_{\gf}$ расщепляется как  $\Delta_{\gf}=\Delta_{\af} \cup
+\phi(\Delta_{\sfr})$, где  $\phi$ -- вложение корневой системы $\Delta_{\sfr}$ некоторой полупростой
+алгебры Ли $\sfr$. Тогда коэффициенты ветвления $b^{(\mu)}_{\nu}$ при редукции
+$L^{(\mu)}_{\gf\downarrow \af}$ совпадают с кратностями весов  $m^{(\tilde \mu)}_{\nu}$ в
+представлениях  $\sfr$ при выполнении определенного технического условия \cite{2011arXiv1111.6787L}.
+Старший вес  $\tilde\mu$ представления $\sfr$ вычисляется по индексам Дынкина старшего веса  $\mu$
+модуля алгебры $\gf$. Доказательство равенства коэффициентов ветвления с кратностями весов
+представлений $\sfr$ основывается на разложении сингулярного элемента алгебры  $\gf$ в комбинацию
+сингулярных элементов $\sfr$:
 \begin{equation}
@@
 \end{equation}
-where $\epsilon\left( w\right)$ is a determinant of the element $w$ of the Weyl group $W_{\af}$ of
-the subalgebra $\af$. The action of the Weyl group on the weights is extended to the algebra of formal
-exponents by the rule $w\left(e^{\nu}\right)=e^{w\nu}, w\in W$. Hence, the multiplicity $M_{\left(
-      \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight $\widetilde{\nu }$ from the
-  weight diagram of the algebra $\sfr$ with the highest weight $\tilde\mu$ defines the branching
-  coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu -\phi \left(
-      \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
+где $\epsilon\left( w\right)$ -- определитель элемента $w$ группы Вейля $W_{\af}$ подалгебры $\af$.
+Действие группы Вейля на весах продолжается на алгебры формальных экспонент по правилу
+$w\left(e^{\nu}\right)=e^{w\nu}, w\in W$. Отсюда кратность $M_{\left( \sfr\right) \widetilde{\nu
+  }}^{\widetilde{\mu }}$ веса $\widetilde{\nu }$ из весовой диаграммы представления алгебры $\sfr$
+со старшим весом $\tilde\mu$ определят коэффициент ветвления $b_{\nu }^{(\mu )}$ для старшего веса
+$\nu =\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
 \begin{equation}
@@
 
-We use similar approach to study special embeddings. We consider special embeddings of Lie
-subalgebras into a Lie algebra. In this case the root system of the subalgebra is not contained in
-the root system of the algebra. So the original motivation for splints is not applicable. But we can
-consider the projection of the root system of the algebra on the root space of the subalgebra. Such
-a projection is not a root system anymore, but it satisfies milder conditions (Section
-\ref{sec:spec-embedd-proj}). It is possible to classify the splints of the projection using the fact
-that the adjoint representation of the algebra is decomposed into the direct sum of representations
-of the subalgebra. We show that if there is a splint then branching coefficients coincide with
-weight multiplicities of representations of another Lie algebra (Section
-\ref{sec:splints-spec-embedd}). Thus in this case branching coefficients are very easy to compute.
+В данной работе мы воспользуемся похожим подходом для изучения специальных вложений. Мы
+рассматриваем специальные вложения подалгебр Ли в алгебру Ли. В таком случае корневая система
+подалгебры на содержится в корневой системе алгебры и первоначальная мотивация для введения сплинта
+не применима. Но мы можем рассмотреть проекцию корневой системы алгебры на корневое пространство
+подалгебры. Результат такой проекции уже не будет корневой системой, однако он будет удовлетворять
+более мягким условиям (см Раздел \ref{sec:spec-embedd-proj}). Оказывается, что сплинты проекций
+корневых систем можно классифицировать, используя разложение присоединенного представления алгебры
+в прямую сумму представлений подалгебры. Мы показываем, что при наличии такого сплинта коэффициенты
+ветвления совпадают с кратностями весов в представлениях другой алгебры Ли (Раздел
+\ref{sec:splints-spec-embedd}). А значит, в этом случае коэффициенты ветвления очень легко вычислить.
 
-The use of representation theory of the subalgebra allows us to classify all the splints for the projections
-of the algebra root system. We also apply this method to metric splints and regular subalgebras and get
-a unified treatment. We obtain the Gelfand-Tsetlin rules for regular and special embeddings this way.
+Мы используем теорию представлений подалгебры для классификации всех сплинтов для проекции корневой
+системы алгебры. Однако метод универсален и мы применяем его и к метрическим сплинтам и регулярным
+подалгебрам. В результате мы получаем правила Гельфанда-Цетлина для регулярных и специальных
+вложений.
 
-In conclusion \ref{sec:conclusion} we discuss the cases when the projection of the root system does
-not fall into the classification mentioned above.
+В заключении \ref{sec:conclusion} мы обсуждаем случаи, которые не укладываются в упомянутую выше
+классификацию.
 
-\section{Special embeddings and projections of root system}
+\section{Специальные вложения и проекции корневой системы}
 \label{sec:spec-embedd-proj}
@@
 
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+
+We thank the organizers of the conference ``In Search of Fundamental Symmetries'' where some results
+of this work were presented.
+
+P.I. Kakin would like to acknowledge Saint Petersburg State University for the research grant
+11.38.185.2014.
+
 \bibliography{special-bibliography}{} 

### 2015-03-23 AffineLieAlgebras/Splints/special-paper-ru.tex
More translation

@@
 
-The study of specialy embedded subalgebras traces back to the fundamental papers by Eugene Dynkin
-\cite{dynkin1952semisimple,dynkin1952maximal} where he called such subalgebras ``S-subalgebras'' to
-distinguish from regular or ``R-subalgebras'' that have root systems obtained by dropping some roots
-of the algebra root system. Thus regular subalgebras are easy to construct by dropping nodes from
-the extended Dynkin diagram of the algebra, while the case of special subalgebras is more difficult. The complete
-classification for exceptional Lie algebras was obtained recently in \cite{minchenko2006semisimple}.
-The algorithm of the special subalgebras construction is available in GAP package but still requires
-a manual intervention \cite{de2011constructing}.
+Специальные вложения подалгебр детально рассматривались в фундаментальных работах Евгения
+Борисовича Дынкина \cite{dynkin1952semisimple,dynkin1952maximal}, где для них использовалось
+название ``S-подалгебры'' чтобы отличить от регулярных или ``R-подалгебр'', полученных путем
+исключения некоторых корней из корневой системы алгебры. Все регулярные подалгебры нетрудно построить
+путем исключения вершин из расширенной диаграммы Дынкина для алгебры, но для специальных подалгебр
+такого простого метода нет. Полная классификация для исключительных алгебр Ли была построена недавно
+в работе \cite{minchenko2006semisimple}. Алгоритм построения специальных подалгебр реализован в виде
+пакета для системы GAP, но построение все равно требует участия человека \cite{de2011constructing}.
 
-Assume that the Lie algebra $\gf$ is simple. Let's denote a subalgebra by
-$\af$. We denote corresponding Cartan subalgebras by $\hfg$ and $\hfa$ and identify them with the dual
-spaces $\hfg^{*}$, $\hfa^{*}$ using the Killing forms of $\gf$ and $\af$.
+Будем предполагать, что алгебра Ли $\gf$ простая. Обозначим подалгебру через $\af$. Соответствующие
+подалгебры Картана будем обозначать через $\hfg$ и $\hfa$, и отождествим их с дуальными
+пространствами $\hfg^{*}$, $\hfa^{*}$ используя формы Киллинга алгебр  $\gf$ и $\af$.
 
-To construct an embedding $\af\to\gf$ consider some representation $L^{\nu}_{\af}$ as a subspace of
-Lie algebra $\gf$. Then one needs to check that the generators of $\af$ can be presented as
-linear combinations of generators of $\gf$. We can identify the Cartan subalgebra $\hfa\subset \af$ with
-the dual space $\hfa^{*}$ using the Killing form. Then the root system $\Delta_{\gf}$ of $\gf$ can be
-projected to $\hfa^{*}$ using the expression of $\hfa$-generators through $\hfg$-generators.
+Для построения вложения  $\af\to\gf$ надо отождествить некоторое представление  $L^{\nu}_{\af}$ с
+подпространством в алгебре Ли $\gf$. Затем необходимо проверить, что генераторы  $\af$ могут быть
+представлены в виде линейных комбинаций генераторов  $\gf$. После отождествления подалгебры Картана
+$\hfa\subset \af$ с дуальным пространством $\hfa^{*}$ при помощи формы Киллинга, корневую систему
+$\Delta_{\gf}$ алгебры $\gf$ можно спроектировать на  $\hfa^{*}$ используя выражение
+генераторов подалгебры $\hfa$ через генераторы  $\hfg$.
 
@@
 
-This projection is described in the classical papers \cite{dynkin1952semisimple,dynkin1952maximal} by the following theorem:
+Свойства этой проекции описаны в классических работах  \cite{dynkin1952semisimple,dynkin1952maximal} в
+следующих теоремах:
 
 \begin{theorem}\label{dyn0}
-  If a representation $L^{\mu}_{\gf}$ of the algebra $\gf$ induces a representation
-  $L^{\tilde\mu}_{\af}$ on the subalgebra $\af$ then the weight system of $L^{\tilde\mu}_{\af}$ can
-  be obtained from $L^{\mu}_{\gf}$ by an orthogonal projection of $\hfg^{*}$ on $\hfa^{*}$.
-
+  Если представление  $L^{\mu}_{\gf}$ алгебры $\gf$ индуцирует представление $L^{\tilde\mu}_{\af}$
+  подалегбры $\af$, то весовая диаграмма $L^{\tilde\mu}_{\af}$ получается из диаграммы
+  $L^{\mu}_{\gf}$ ортогональной проекцией $\hfg^{*}$ на $\hfa^{*}$.
   \cite{dynkin1952maximal}. 
@@
 
-In relation to the adjoint representation of $\gf$ this theorem means that the projection of the root system $\Delta_{\gf}$ to $\hfa^{*}$ is a weight system of some
-finite-dimensional but not irreducible representation of $\af$. Moreover this reducible representation contains the adjoint representation of $\af$. And if we denote such a projection by
+Применяя эту теорему к присоединенному представлению  $\gf$, видим, что проекция корневой
+системы  $\Delta_{\gf}$ на $\hfa^{*}$ оказывается весовой системой некоторого конечномерного но не
+обязательно неприводимого представления $\af$. Более того, это приводимое представление должно
+содержать присоединенное представление $\af$. Если обозначить проекцию корневой системы через
 \begin{equation}
@@
 \end{equation}
-then the roots of $\af$ will be contained in $\Delta'$. Thus the system $\Delta'$ can be a root
-system but it might not be reduced and might contain some vectors with multiplicities greater than
-one.
+то все корни $\af$ будут содержаться в $\Delta'$. То есть система  $\Delta'$ может быть корневой
+системой, но она не обязательно является приведенной и может содержать некоторые векторы с
+кратностью больше единицы.
 
-The following theorems \cite{dynkin1952semisimple} also concern the properties of $\Delta'$.
+Следующие теоремы \cite{dynkin1952semisimple} также описывают свойства  $\Delta'$.
 
 \begin{theorem}\label{dyn1}
-  Every special subalgebra $\af$ of a semisimple Lie algebra $\gf$ is integer, i.e. the projections of
-  the roots of $\gf$ to $\hfa^{*}$ are linear combinations of the simple roots of $\af$ with integer
-  coefficients \cite{dynkin1952semisimple}
+  Каждая специальная подалгебра  $\af$ полупростой алгебры Ли  $\gf$ -- целочисленная, то есть
+  проекции корней  $\gf$ на $\hfa^{*}$ являются линейными комбинациями простых корней  $\af$ с
+  целочисленными коэффициентами \cite{dynkin1952semisimple}
 \end{theorem}
@@
 \begin{theorem}\label{dyn2}
-  If $\af$  is a semisimple subalgebra of a semisimple Lie algebra $\gf$ and the generator $e_{\alpha}$ corresponding to
-  the root $\alpha$ of $\af$ is presented as a linear combination $e_{\alpha}=\sum_{\beta}
-  e_{\beta}$ of $\gf$-generators
-  corresponding to the roots $\beta$ of $\gf$, then the roots $\beta$ are projected into $\alpha$,
+  Если $\af$  -- полупростая подалгебра полупростой алгебры Ли $\gf$ и генератор $e_{\alpha}$,
+  соответствующий корню $\alpha$ алгебры $\af$, представляется в виде линейной комбинации  $e_{\alpha}=\sum_{\beta}
+  e_{\beta}$ генераторов $\gf$ соответствующих корням  $\beta$ алгебры $\gf$, тогда все эти корни
+  $\beta$ проектируются в  $\alpha$,
   $\pia(\beta)=\alpha$. 
@@
 
-From these theorems we see that the root system $\Delta_{\af}$ is metrically embedded (in the sense
-of splint) into the projection $\Delta'$. Moreover, the multiplicities of some roots
-$\alpha\in\Delta_{\af}$ in this projection $\Delta'$ are greater than one.
+Из этих теорем мы видим, что  корневая система $\Delta_{\af}$ вложена метрически (в смысле
+определения сплинта) в проекцию  $\Delta'$. Более того, кратности некоторых корней 
+$\alpha\in\Delta_{\af}$ в этой проекции  $\Delta'$ больше единицы.
 
-For example the projection of the root system of $D_{4}$($so(8)$) to the root system of the special
-subalgebra $A_{2}$($su(3)$) coincides with the root system $G_{2}$, but the short roots have the multiplicity $3$.
+Например, проекция корневой системы $D_{4}$($so(8)$) на корневую систему специальной подалгебры
+$A_{2}$($su(3)$) совпадает с корневой системой $G_{2}$, но кратность коротких корней равна $3$.
 
@@
 
-\section{Splints for special embeddings}
+\section{Сплинты для специальных вложений}
 \label{sec:splints-spec-embedd}
@@
 
-We want to classify all the cases when branching coefficients coincide with weight multiplicities of
-some other algebra representations. Such a coincidence is possible when the projection $\Delta'$ of
-the $\gf$ root system admits a splint $\Delta'=\varphi_{\af}(\Delta_{\af})\cup
-\varphi_{\sfr}(\Delta_{\sfr})$, where $\varphi_{\af}$ and $\varphi_{\sfr}$ are the embeddings of
-the corresponding root systems. The embedding $\varphi_{\af}$ is metric and trivial. Moreover, the
-projection of the singular element $\pia\left(\Psi^{\mu}_{\gf}\right)$ should admit a decomposition into
-a linear combination of singular elements of irreducible representations of $\sfr$:
+Мы хотим перечислить все случаи совпадения коэффициентов ветвления с кратностями весов в
+представлении некоторой другой алгебры. Такое совпадение возможно, если проекция $\Delta'$ корневой
+системы алгебры $\gf$ допускает сплинт $\Delta'=\varphi_{\af}(\Delta_{\af})\cup
+\varphi_{\sfr}(\Delta_{\sfr})$, где  $\varphi_{\af}$ и $\varphi_{\sfr}$ -- вложения соответствующих
+корневых систем. Вложение  $\varphi_{\af}$ метрическое и тривиальное. Кроме этого, проекция
+сингулярного элемента  $\pia\left(\Psi^{\mu}_{\gf}\right)$ должна раскладываться в линейную
+комбинацию сингулярных элементов неприводимых представлений $\sfr$:
 \begin{equation}
@@
 \end{equation}
-with integer coefficients $\varkappa_{\nu}$, where the sum is over the set of weights $\nu$ that
-will be determined later.
-Such a decomposition of the singular element is very similar to the branching of Weyl group orbits considered in the papers \cite{larouche2011branching,larouche2009branching}.
-First we classify all the splints of the projection of a root system into
-a union of simple root systems for special embeddings, and then discuss the decomposition of singular
-elements.
+с целыми коэффициентами  $\varkappa_{\nu}$, где  множество весов  $\nu$, по которому ведется
+суммирование, будет определено ниже. Это разложение сингулярного элемента очень похоже на ветвления
+орбит группы Вейля, рассмотренные в работах  \cite{larouche2011branching,larouche2009branching}.
+Сперва мы перечислим все расщепления проекций корневой системы в объединение простых корневых систем
+при специальных вложениях, а затем обсудим разложение сингулярного элемента.
 
-Projection of the $\gf$ root system $\Delta'$ coincides with the projection of the weight diagram of the
-adjoint representation of the algebra $\gf$ with the exception of zero weight. The adjoint representation of
-$\gf$ contains the adjoint representation of $\af$ and can be decomposed as
+Проекция  $\Delta'$ корневой системы  $\gf$ совпадает с проекцией весовой диаграммы присоединенного
+представления алгебры  $\gf$, за исключением нулевого веса. Присоединенное представление  $\gf$
+содержит присоединенное представление  $\af$ и раскладывается в прямую сумму
 \begin{equation}
@@
 \end{equation}
-where $M^{\chi}_{\af}$ is not necessary irreducible representation of $\af$ called
-``characteristic'' in \cite{dynkin1952semisimple}.
+где  $M^{\chi}_{\af}$ -- не обязательно неприводимое представление $\af$, названное 
+``характеристическим'' в работе \cite{dynkin1952semisimple}.
 
-The weight diagram of $M^{\chi}_{\af}$ coincides with the root system $\Delta_{\sfr}$ with the exception of
-zero weight. So we need to find all the representations for all simple Lie algebras $\af$, such that
-their weight diagrams are root systems after the exclusion of zero weight. In order to do so we must
-note, that all the weights of $M^{\chi}_{\af}$ should have a length not less than the length of the shortest
-root of $\af$, since $\af$ is an integer subalgebra of $\gf$ \ref{dyn1}. Moreover, $M^{\chi}_{\af}$
-should contain weights of at most two different lengths.
+Весовая диаграмма $M^{\chi}_{\af}$ совпадает с корневой системой  $\Delta_{\sfr}$, за исключением
+нулевого веса. То есть нам достаточно найти все представления для всех простых алгебр Ли $\af$
+такие, что их весовая диаграмма совпадает с некоторой корневой системой после исключения нулевого
+веса. Во-первых, заметим, что все веса  $M^{\chi}_{\af}$ должны быть  не меньшей длины чем
+кратчайший корень $\af$, так как $\af$ -- целочисленная подалгебра $\gf$ \ref{dyn1}. Во-вторых,
+$M^{\chi}_{\af}$ должна содержать веса не более, чем двух разных длин.
 
-If the root system $\Delta_{\gf}$ contains roots $\alpha: \alpha\perp \beta,\; \forall \beta\in
-\Delta_{\af},$ orthogonal to the root system of the subalgebra, one cannot proceed with the decomposition
-of the singular element \ref{eq:4}. The elements $e^{\nu}$ of $\pia\left(\Psi^{\mu}_{\gf}\right)$
-should be augmented with the dimensions of representations of the algebra $\afb$ spanned by generators
-corresponding to the orthogonal roots \cite{2010arXiv1007.0318L}. Then there will be non-trivial
-multiplicities in the right hand side of \ref{eq:4} and no coincidence of branching coefficients
-with the weight multiplicities of $\sfr$-representations. One can write more cumbersome relation between
-the multiplicities and branching coefficients, but it is out of scope for the present paper.
+Если в корневой системе  $\Delta_{\gf}$ есть корни $\alpha: \alpha\perp \beta,\; \forall \beta\in
+\Delta_{\af},$ ортогональные корневой системе подалгебры, то сингулярный элемент не допускает
+разложения \ref{eq:4}.  В этом случае элементы формальной алгебры $e^{\nu}$ проекции
+$\pia\left(\Psi^{\mu}_{\gf}\right)$ надо снабдить размерностями представлений алгебры $\afb$,
+порожденной генераторами, соответствующими ортогональным корням \cite{2010arXiv1007.0318L}. Тогда
+правая часть разложения  \ref{eq:4} будет содержать нетривиальные кратности и совпадение
+коэффициентов ветвления с кратностями весов в представлениях  $\sfr$ не будет иметь места. В
+этом случае можно вывести более сложное соотношение между кратностями весов и коэффициентами
+ветвления, но этот вывод лежит за рамками данной работы.
 
-The multiplicity of zero weight in the adjoint representation is equal to the rank of the algebra. So if
-$\mathrm{rank}\gf-\mathrm{rank}\af=1$, the representation in question $M^{\chi}_{\af}$ must be
-multiplicity-free. If $\mathrm{rank}\gf-\mathrm{rank}\af>1$ only zero weight can have non-trivial
-multiplicities.
+Кратность нулевого веса в присоединенном представлении равна рангу алгебры. Так что при 
+$\mathrm{rank}\gf-\mathrm{rank}\af=1$, характеристическое представление  $M^{\chi}_{\af}$ должно
+быть свободно от нетривиальных кратностей.  При $\mathrm{rank}\gf-\mathrm{rank}\af>1$ только нулевой
+вес может иметь нетривиальную кратность.
 
-The simplest class of multiplicity-free representations is called ``strongly multiplicity free''
-\cite{lehrer2006strongly} and consists of multiplicity free representations with weight systems
-admitting strict ordering $\nu_{1}<\nu_{2} \Leftrightarrow \nu_{1}=\nu_{2}+n \alpha$, where $n\in
-\mathbb{N}, \alpha\in \Delta^{+}_{\af}$ and for all $\nu_{1},\nu_{2}$ either $\nu_{1}<\nu_{2}$ or
+Простейшие свободные от кратностей представления называется ``строго свободными от кратностей''
+ (``strongly multiplicity free'') \cite{lehrer2006strongly} и представляют собой представления с
+ весовыми системами, допускающими строгое упорядочение $\nu_{1}<\nu_{2} \Leftrightarrow
+ \nu_{1}=\nu_{2}+n \alpha$, где $n\in
+\mathbb{N}, \alpha\in \Delta^{+}_{\af}$ и для всех $\nu_{1},\nu_{2}$ либо $\nu_{1}<\nu_{2}$, либо
 $\nu_{2}<\nu_{1}$.
 
-The list of strongly multiplicity free representations consists of (first) fundamental representations
-for the series $A_{r}, B_{r}, C_{r}$, the exceptional Lie algebra $G_{2}$ (7-dimensional representation) and
-all $A_{1}$ representations.
+Список строго свободных от кратностей представлений состоит из (первых) фундаментальных
+представлений в сериях $A_{r}, B_{r}, C_{r}$, представления исключительной алгебры Ли $G_{2}$
+(7-мерного) и всех представлений $A_{1}$.
 
-Fundamental weights of the algebra $A_{r}$ are shorter than its roots, but the projections of $\gf$
-weights must be given by linear combinations of the roots of the  special subalgebra $\af$ with integer
-coefficients, so the first class of strongly multiplicity free representations does not produce such a
-projection.
+Фундаментальные веса алгебры $A_{r}$ короче, чем ее корни, но проекции весов $\gf$ должны даваться
+линейными комбинациями корней специальной подалгебры  $\af$ с целыми коэффициентами, так что первый
+класс строго свободных от кратностей представлений не порождает проекции корневой системы,
+допускающей расщепление.
 
-Nevertheless, the union of diagrams of the two fundamental representations of $A_{2}$ with the root
-system of $A_{2}$ produces a weight diagram of $G_{2}$. This case corresponds to splint
-$\Delta_{G_{2}}=\varphi_{1}( \Delta_{A_{2}})\cup \varphi_{2}(\Delta_{A_{2}})$ which is connected
-with the regular subalgebra $A_{2}\subset G_{2}$ (see \cite{2011arXiv1111.6787L}).
+Тем не менее, объединение диаграмм двух фундаментальных представлений  $A_{2}$ с корневой системой
+$A_{2}$ образует корневую систему $G_{2}$. Этот случай соответствуют сплинту
+$\Delta_{G_{2}}=\varphi_{1}( \Delta_{A_{2}})\cup \varphi_{2}(\Delta_{A_{2}})$, связанному с
+регулярной подалгеброй $A_{2}\subset G_{2}$ (подробнее см. \cite{2011arXiv1111.6787L}).
 
-The first fundamental representation of $B_{r}$ immediately gives us the splint $\Delta'=\pi_{B_{r}}\left(
-\Delta_{D_{r+1}}\right) = \Delta_{B_{r}}\cup \Delta_{A_{1}+\dots+A_{1}}$ corresponding to the Gelfand-Tsetlin
-multiplicity-free branching for the special embedding $\mathfrak{so}(2r+1)\to \mathfrak{so}(2r+2)$.
+Первое фундаментальное представление  $B_{r}$ немедленно дает сплинт $\Delta'=\pi_{B_{r}}\left(
+\Delta_{D_{r+1}}\right) = \Delta_{B_{r}}\cup \Delta_{A_{1}+\dots+A_{1}}$, соответствующий правилу
+ветвления Гельфанда-Цетлина с тривиальными коэффициентами для специального вложения
+$\mathfrak{so}(2r+1)\to \mathfrak{so}(2r+2)$.
 
-The length of the first fundamental weight of  $C_{r}$ is less than the length of its short root, so
-this case can not correspond to an integer subalgebra.
+Длина первого фундаментального веса алгебры   $C_{r}$ меньше, чем длина ее короткого корня, так что
+этот случай не может порождать сплинт для целочисленной подалгебры.
 
-If there are vectors of a different length in the projection $\Delta'$ on the subalgebra $A_{1}$, such a
-projection is not multiplicity free, and $\Delta_{\sfr}$ contains parallel roots. The simplest case
-is the special embedding $A_{1}\to A_{2}$ with index 4 where $\Delta_{\sfr}$ is the root system
-$BC_{1}$. Such systems do not correspond to semisimple Lie algebras, so we can not speak of a
-coincidence of branching coefficients for the reduction $\gf\downarrow \af$ with weight
-multiplicities of $\sfr$-representations.
+Далее, если в проекции  $\Delta'$ на подалгебру  $A_{1}$ есть векторы разной длины, то в такой
+проекции есть нетривиальные кратности и система $\Delta_{\sfr}$ должна содержать сонаправленные
+корни. Простейший пример -- это специальное вложение $A_{1}\to A_{2}$ с индексом 4, где
+$\Delta_{\sfr}$ -- это корневая система $BC_{1}$. Такие системы не соответствуют полупростым
+алгебрам Ли, так что мы не можем говорить о совпадении коэффициентов ветвления для редукции
+$\gf\downarrow \af$ с кратностями весов в представлениях $\sfr$.
 
@@
 %%
-The weight diagram of the seven-dimensional representation of $G_{2}$ together with the $G_{2}$ root system
-form the projection of the root system $B_{3}$ which corresponds to the special embedding 
-$G_{2}\to B_{3}$. The branching coefficients in this case coincide with the weight multiplicities of
-representations of algebra $\sfr=A_{2}$ with the image of the root system consisting of the short roots of
-$G_{2}$.
 
-The complete classification of multiplicity-free irreducible representations was obtained in
-\cite{howe1995perspectives} (see also \cite{stembridge2003multiplicity}). It consists of minuscule
-and quasi-minuscule representations.
+Наконец, весовая диаграмма семимерного представления $G_{2}$ вместе с корневой системой $G_{2}$
+образует проекцию корневой системы $B_{3}$, возникающую при специальном вложении $G_{2}\to B_{3}$.
+Коэффициенты ветвления в этом случае совпадают с кратностями весов в представлениях алгебры $G_{2}$.
 
-The weight $\mu$ is minuscule if $\left<\mu,\alpha^{\vee}\right>\leq 1$ for all $\alpha\in
-\Delta^{+}$ and all the weights of the irreducible representation $L^{\mu}$ lie on the Weyl
-group orbit of $\mu$. A weight is quasi-minuscule if $\left<\mu,\alpha^{\vee}\right>\leq 2$ for all
-$\alpha\in \Delta^{+}$ and all non-zero weights lie on the single Weyl group orbit.
+Полная классификация представлений, свободных от кратностей, получена в работе
+\cite{howe1995perspectives} (см. также \cite{stembridge2003multiplicity}). Она состоит из
+микровесовых и квазимикровесовых представлений.
 
-Minuscule representations are well-studied and very useful in the computations of e.g. tensor products
-\cite{stembridge2003multiplicity,stembridge2001computational}. The minuscule representations are
-indexed by the weight lattice modulo the root lattice. There is a unique quasi-minuscule
-representation that is not minuscule for each simple Lie algebra. The multiplicity of the zero 
-weight in quasi-minuscule representation is the number of the short nodes of the Dynkin diagram.
+Вес  $\mu$ называется микровесом, если  $\left<\mu,\alpha^{\vee}\right>\leq 1$ для всех $\alpha\in
+\Delta^{+}$ и все веса неприводимого представления  $L^{\mu}$ лежат на той же орбите группы Вейля,
+что и $\mu$. Вес называется квазимикровесом, если $\left<\mu,\alpha^{\vee}\right>\leq 2$ для всех
+$\alpha\in \Delta^{+}$ и все ненулевые веса представления лежат на одной орбите группы Вейля.
 
-The list of the minuscule representations consists of tensor powers of the vector
-representation for the series $A_{r}$; spin representations for the series
-$B_{r}$; vector representations for $C_{r}$; vector and two half-spin for $D_{r}$; two
-27-dimensional representations for $E_{6}$ and the 56-dimensional representation of $E_{7}$.
+Микровесовые представления хорошо изучены и очень полезны при вычислениях, например, тензорных произведений
+\cite{stembridge2003multiplicity,stembridge2001computational}. Микровесовые представления нумеруются
+элементами весовой решетки, факторизованной по корневой решетке. Для каждой простой алгебры Ли
+существует единственное квазимикровесовое представление, не являющееся микровесовым.  Кратность
+нулевого веса в квазимикровесовом представлении равна числу коротких вершин в диаграмме Дынкина.
 
-Quasi-minuscule representations that are not minuscule are: the adjoint representation of $A_{r}$,
-the vector representation for $B_{r}$, the $2r^{2}-r-1$-dimensional representation for $C_{r}$, the adjoint
-representations for $D_{r}, E_{6}, E_{7}, E_{8}$, the 26-dimensional representation for $F_{4}$ and
-the 7-dimensional of $G_{2}$.
+Полный список микровесовых представлений состоит из тензорных степеней векторного представления
+алгебр серии $A_{r}$; спинорных представлений алгебр серии $B_{r}$; векторных представлений $C_{r}$;
+векторных и полуспиновых представлений $D_{r}$; двух 
+27-мерных представлений алгебры $E_{6}$ и  56-мерного представления $E_{7}$.
+
+Квазимикровесовые представления, не являющиеся микровесовыми -- это присоединенное представление
+$A_{r}$, векторное представление $B_{r}$, представление размерности $2r^{2}-r-1$ алгебры $C_{r}$,
+присоединенные представления алгебр $D_{r}, E_{6}, E_{7}, E_{8}$, 26-мерное представление $F_{4}$ и
+7-мерное представление $G_{2}$.
 
@@
 
-The classification of the multiplicity-free irreducible highest weight modules $L^{\mu}$ in
-\cite{howe1995perspectives,stembridge2003multiplicity} consists of the following classes:
+Классификация неприводимых представлений  $L^{\mu}$, свободных от кратностей, в работе
+\cite{howe1995perspectives,stembridge2003multiplicity} состоит из следующих классов:
 \begin{itemize}
-\item (1) $\mu$ is minuscule,
-\item (2) $\mu$ is quasi-minuscule and Lie algebra has only one short simple root,
-\item (3) Lie algebra is $\mathfrak{sp}(6)$ and $\mu=\omega_{1}$, or
-\item (4) Lie algebra is $\mathfrak{sl}(n + 1)$ and  $\mu= m\omega_{1}$ or $\mu  = m\omega_{n}$ 
+\item (1) $\mu$ -- микровес
+\item (2) $\mu$ -- квазимикровес и в алгебре Ли только один короткий простой корень,
+\item (3) алгебра Ли $\mathfrak{sp}(6)$ и $\mu=\omega_{1}$, и
+\item (4) алгебра Ли $\mathfrak{sl}(n + 1)$ и  $\mu= m\omega_{1}$ или $\mu  = m\omega_{n}$ 
 \end{itemize}
 
-We see that the case (1) contains strongly multiplicity free modules of the series $A_{r}$ and the exceptional
-Lie algebra $G_{2}$, the class (2) contains strongly multiplicity free modules of $ B_{r}$ and $C_{r}$ ,
-strongly multiplicity free modules of $A_{1}$ are included in the class (4).
+Как видно, класс (1) содержит строго свободные от кратностей представления серии  $A_{r}$ и
+исключительной алгебры Ли $G_{2}$, класс  (2) содержит строго свободные от кратностей представления
+$ B_{r}$ и $C_{r}$ , а строго свободные от кратностей представления $A_{1}$ входят в класс (4).
 
-We do not need to consider the minuscule representations for the simply-laced Lie algebras, since in this
-case the length of the weights of the representation $M^{\chi}_{\af}$ is less than the length of the $\af$ roots,
-that contradicts to $\af$ being an integer subalgebra. For the series $B_{r}$ we have already
-discussed the minuscule spin representation, since it is strongly multiplicity free. The last case in
-(1) is the vector representation for $C_{r}$. It is $2r$-dimensional, but the length of its highest weight $\omega_{1}$ is less
-than the length of the short root of algebra $C_{r}$. So it can not be a characteristic representation
-for the special subalgebra.
+Нам не надо рассматривать микровесовые представления алгебр $A$, $D$, $E$, так как в этом случае
+длина весов представления  $M^{\chi}_{\af}$ меньше длины корней подалгебры  $\af$, что противоречит
+целочисленности подалгебры  $\af$. Микровесовые спиновые представления алгебры серии $B_{r}$ уже
+обсуждались, так как они являются строго свободными от кратностей. Последний случай в классе (1) --
+это векторное представление  $C_{r}$. Оно  $2r$-мерно, но длина старшего веса $\omega_{1}$ меньше
+длины короткого корня алгебры $C_{r}$, так что это представление не может быть характеристическим
+для специальной подалгебры.
 
@@
 %%
-The case (2) consists of the series $B_{r}$ and the exceptional root system $G_{2}$. The embedding $G_{2}\to
-B_{3}$ was already discussed. 
- The dimension of the adjoint representation for the series $B_{r}$
-is $2r^{2}+r$ and of the quasi-minuscule representation it is $2r+1$, so the dimension of the algebra
-$\gf$ should be $(r+1)(2r+1)$ with the $\mathrm{rank}\gf=r+1$. The only solution is $\gf=D_{r+1}$
-and we have already seen that this case corresponds to the strongly multiplicity free module and
-the Gelfand-Tsetlin basis.
 
-In the case (3) the diagram of the representation contains weights with the length smaller than the
-length of the short root, so it cannot be a projection of $\Delta_{\gf}$ to an integer subalgebra.
+Класс (2) состоит из серии  $B_{r}$ и исключительной корневой системы $G_{2}$. Вложение  $G_{2}\to
+B_{3}$ уже описано выше. Размерность присоединенного представления для серии $B_{r}$ равна
+$2r^{2}+r$, а размерность квазимикровесового представления равна $2r+1$, таким образом размерность
+алгебры 
+$\gf$ должна быть $(r+1)(2r+1)$ при ранге $\mathrm{rank}\gf=r+1$. Единственное решение,
+удовлетворяющее этим условиям -- это  $\gf=D_{r+1}$ и мы уже видели, что этот случай соответствует
+строго свободным от кратностей представлениям и базису Гельфанда-Цетлина.
 
-We need to consider representations of the class (4) only for $m=1,2$ since the root system $\Delta_{\sfr}$
-can have roots of at most two different lengths. In the case $m=1$ we get strongly multiplicity free
-modules of $A_{r}$ which were discussed above. And for algebra $A_{2}$ and $m=2$ the weight diagram
-of the representation $L^{2\omega_{1}}_{A_{2}}$ coincides with the root system of the exceptional Lie algebra
-$G_{2}$. This case appears in the special embedding $A_{2}\to B_{3}$. But for $A_{r}, r>2$ there are
-no root systems that coincide with the weight diagram of $L^{2\omega_{1}}_{A_{r}}$.
+В классе  (3) диаграмма представления содержит веса с длиной меньше длины короткого корня, так что
+она не может быть проекцией  $\Delta_{\gf}$ на целочисленную подалгебру.
 
-So far we've considered all the cases when $\mathrm{rank}\gf-\mathrm{rank}\af=1$. To complete our
-classification of splints we need the classification of all the representations where multiplicities
-of all non-zero weights are equal to one. Fortunately, such a classification was obtained in
-\cite{plotkin1998visual}. It consists of multiplicity-free representations and adjoint
-representations of algebras $A_{r}, B_{r}, C_{r}$, $F_{4}$ and $G_{2}$.
+Нам следует рассмотреть представления класса  (4) только при $m=1,2$, так как корневая система
+$\Delta_{\sfr}$ может содержать корни не более чем двух разных длин. В случае case $m=1$ мы снова
+получаем строго свободные от кратностей модули $A_{r}$, которые уже обсуждались выше. А для алгебры
+$A_{2}$ и $m=2$ весовая диаграмма представления $L^{2\omega_{1}}_{A_{2}}$ совпадает с корневой
+системой исключительной алгебры Ли
+$G_{2}$. Этот случай возникает в специальном вложении  $A_{2}\to B_{3}$. Для $A_{r}, r>2$ не
+существует корневых систем, которые совпадают с весовой диаграммой $L^{2\omega_{1}}_{A_{r}}$.
 
-In order to have the embedding $\af\to \gf$ such that the adjoint representation of $\gf$ is
-decomposed into two adjoint representations of $\af$ (and possibly several trivial
-representations) we need to satisfy the following conditions:
+Мы рассмотрели все случаи, когда $\mathrm{rank}\gf-\mathrm{rank}\af=1$. Чтобы завершить нашу
+классификацию сплинтов, нам нужна классификация всех представлений, в которых кратности ненулевых
+весов равны единице. Такая классификация была представлена в работе
+\cite{plotkin1998visual}. Она состоит из свободных от кратностей представлений и присоединенных
+представлений алгебр  $A_{r}, B_{r}, C_{r}$, $F_{4}$ и $G_{2}$.
+
+Чтобы существовало вложение $\af\to \gf$, такое что присоединенное представление  $\gf$
+раскладывается в два присоединенных представления $\af$ (и, возможно, несколько тривиальных
+представлений), должны быть выполнены следующие условия:
 \begin{itemize}
-\item Denote by $n_{\gf}$ the total number of roots in $\Delta_{\gf}$ and the projection $\Delta'$.
-  Then
+\item Обозначим через $n_{\gf}$ общее число корней в  $\Delta_{\gf}$ и проекции $\Delta'$.
+  Тогда
   \begin{equation}
@@
   \end{equation}
-\item Denote rank of $\gf$ by shorthand notation $r_{\gf}$. Then the dimension
+\item Обозначим ранг $\gf$ для краткости через $r_{\gf}$. Тогда размерность
   \begin{equation}

### 2015-03-23 AffineLieAlgebras/Splints/special-paper-ru.tex
Russian translation completed

@@
 
-Специальные вложения подалгебр детально рассматривались в фундаментальных работах Евгения
-Борисовича Дынкина \cite{dynkin1952semisimple,dynkin1952maximal}, где для них использовалось
+Специальные вложения подалгебр детально рассматривались в фундаментальных работах Евгения Борисовича Дынкина \cite{dynkin1952semisimple,dynkin1952maximal}, где для них использовалось
 название ``S-подалгебры'' чтобы отличить от регулярных или ``R-подалгебр'', полученных путем
@@
 
-For the adjoint representation of algebra $A_{r}$ we see that the projection $\Delta'$ of the root system
-$\Delta_{\gf}$ should consist of roots of the subalgebra $\af=A_{r}$ with the multiplicity 2. The total
-number of the roots for $A_{r}$ is $r(r+1)$, so $\Delta'$ and $\Delta_{\gf}$ contain $2r(r+1)$ roots,
-since there are no roots orthogonal to $\Delta_{\af}$. There are two possible solutions for
-$\gf$: $D_{r+1}$ and $G_{2}$ for $r=2$. But the dimension of $D_{r+1}$ is $(r+1)(2r+1)$ while the
-dimension of $A_{r}$ is $r(r+2)$ and $2\mathrm{dim}A_{r}>\mathrm{dim}D_{r+1}$, so the adjoint
-representation of $D_{r+1}$ cannot be decomposed as twice the adjoint representation of $A_{r}$.
-There is no corresponding embedding $A_{r}\to D_{r+1}$ and no splint. We see that the conditions
-\ref{eq:5}\ref{eq:6} do not hold.
+Рассмотрим присоединенное представление алгебры $A_{r}$. Мы видим, что проекция $\Delta'$ корневой
+системы $\Delta_{\gf}$ должна состоять из корней подалгебры $\af=A_{r}$ с кратностью 2. Общее число
+корней в $A_{r}$ равно $r(r+1)$, так что $\Delta'$ и $\Delta_{\gf}$ содержат по $2r(r+1)$ корней,
+так как нет корней, ортогональных $\Delta_{\af}$. Отсюда существует два варианта решения для алгебры
+$\gf$: $D_{r+1}$ и $G_{2}$ при $r=2$. Но размерность $D_{r+1}$ равна $(r+1)(2r+1)$, тогда как
+размерность $A_{r}$ равна $r(r+2)$ и $2\mathrm{dim}A_{r}>\mathrm{dim}D_{r+1}$, так что
+присоединенное представление $D_{r+1}$ не может быть разложено в сумму двух копий присоединенного
+представления $A_{r}$. А значит, нет и соответствующего вложения $A_{r}\to D_{r+1}$ и сплинта.
+Условия \ref{eq:5},\ref{eq:6} не выполняются.
 
-Let's consider the embedding $B_{r}\to \gf$ such that the adjoint representation of $\gf$ is
-decomposed into two adjoint representations of $B_{r}$. It is straightforward to check that there is
-no solutions for $\gf$ satisfying the \ref{eq:5}\ref{eq:6} for the series $A$, $B$, $C$,
-$D$ and all exceptional simple Lie algebras.
+Теперь перейдем к вложению $B_{r}\to \gf$, такому что присоединенное представление $\gf$
+раскладывается в сумму двух копий присоединенного представления $B_{r}$. Легко проверить перебором,
+что подходящего решения для $\gf$, удовлетворяющего условиям \ref{eq:5}\ref{eq:6}, не существует в
+сериях $A$, $B$, $C$, $D$, не подходят и все исключительные простые алгебры Ли.
 
-Since the number of roots of the root system $C_{r}$ is the same as for $B_{r}$ and we need to check the
-same cases, we see that there is no embedding for $C_{r}$ too.
+Так как число корней корневой системы  $C_{r}$ такое же, как и в $B_{r}$ и нам нужно проверять те же
+случаи, мы видим, что для  $C_{r}$ тоже нет подходящего вложения.
 
-The adjoint representation of $G_{2}$ gives us the algebra $D_{4}$ as the solution of the
-constraints \ref{eq:5}\ref{eq:6}. The embedding $G_{2}\to D_{4}$ exists, since there are
-embeddings $G_{2}\to B_{3}$ and $B_{3}\to D_{4}$, but the decomposition of the adjoint representation of
-$D_{4}$ is different: $ \mathrm{ad}_{D_{4}}=\mathrm{ad}_{G_{2}}\oplus 2 L^{\omega_{1}}_{G_{2}}$. So
-this case does not produce splint for the projection $\Delta'$.
+Присоединенное представление алгебры $G_{2}$ дает нам алгебру  $D_{4}$ в качестве решения условий
+\ref{eq:5},\ref{eq:6}. Вложение  $G_{2}\to D_{4}$ существует, так как есть вложения $G_{2}\to B_{3}$
+и $B_{3}\to D_{4}$, но разложение присоединенного представления $D_{4}$ другое: $
+\mathrm{ad}_{D_{4}}=\mathrm{ad}_{G_{2}}\oplus 2 L^{\omega_{1}}_{G_{2}}$. То есть и этот случай не
+приводит к возникновению сплинта для проекции $\Delta'$.
 
-For the adjoint representation of $F_{4}$ there is no solution that satisfies conditions
-\ref{eq:5}\ref{eq:6}.
+Для присоединенного представления  $F_{4}$ решений, удовлетворяющих соотношениям
+\ref{eq:5},\ref{eq:6} не существует.
 
@@
 
-The complete classification of splints for special embeddings $\Delta'=\pia(\Delta_{\gf})
-\equiv \Delta_{\af}\cup \Delta_{\sfr}$ where $\gf, \af$ are simple and $\sfr$ is semisimple is:
+Итак, полная классификация сплинтов для специальных вложений $\Delta'=\pia(\Delta_{\gf})
+\equiv \Delta_{\af}\cup \Delta_{\sfr}$, где  $\gf, \af$ -- простые, а  $\sfr$ -- полупростая алгебра
+Ли имеет следующий вид:
 \begin{itemize}
@@
 
-Note that in the splints for special embeddings there is no case where $\Delta_{\sfr}$ is embedded
-non-metrically which is a direct result of our exhaustive classification of suitable characteristic
-representations of the subalgebra $\af$.
+Заметим, что среди сплинтов для специальных вложений нет случаев, когда $\Delta_{\sfr}$ вложена не
+метрически. Это результат нашей исчерпывающей классификации подходящих характеристических
+представлений подалгебры $\af$.
 
-Having obtained the complete classification of splints of the projections of
-the root systems for special embeddings, we need to check whether such splints lead
-to the coincidence of branching coefficients with weight multiplicities in modules of
-the algebra $\sfr$.
+После получения полной классификации сплинтов проекций корневых систем при специальных вложениях,
+необходимо проверить совпадение коэффициентов ветвления с кратностями весов в модулях алгебры $\sfr$.
 
-Let's consider the first case - the embedding $B_{n}\to D_{n+1}$. The root system of $D_{n+1}$ has
-exactly two simple roots that are different from the simple roots of $B_{n}$. In the notation of
-\cite{bourbaki2002lie} they are $\alpha_{n}=e_n-e_{n+1}$ and $\alpha_{n+1}=e_n+e_{n+1}$ while
-$\alpha_n^{B_n}=e_n$. This difference leads to the crucial difference in the Weyl groups of the
-algebras: while $W_{B_{n}}$ is a semidirect product of the group of permutation $e_{i} \to e_{j}$
-and the group of the change of sign $e_{i}\to (\pm 1)_{i}e_{i}$, $W_{D_{n+1}}$ is the same but for
-the additional condition on the group of the change of sign: $\prod_{i} (\pm)_{i}=1.$ Since the
-projection of $D_{n+1}$ on $B_{n}$ acts as
-$(e_1,e_2,\dots,e_{n},e_{n+1})\to(e_1,e_2,\dots,e_{n},0)$, the singular element
-$\Phi^{(\mu)}_{D_{n+1}}$ which is the orbit of $W_{D_{n+1}}$ will become a composition of the orbits
-of $W_{B_{n}}$ after the projection.
+Рассмотрим первый случай -- вложение $B_{n}\to D_{n+1}$. Корневая система $D_{n+1}$ содержит в
+точности два простых корня, не входящих в число простых корней подалгебры $B_{n}$. В обозначениях Бурбаки
+\cite{bourbaki2002lie} это простые корни $\alpha_{n}=e_n-e_{n+1}$ и $\alpha_{n+1}=e_n+e_{n+1}$, а
+$\alpha_n^{B_n}=e_n$. Такое отличие приводит к критическому различию в группах Вейля этих алгебр:
+группа $W_{B_{n}}$ представляет собой полупрямое произведение группы перестановок $e_{i} \to e_{j}$
+и группы смен знаков $e_{i}\to (\pm 1)_{i}e_{i}$, а группа $W_{D_{n+1}}$ отличается тем, что на
+операции смены знаков наложено дополнительное условие: $\prod_{i} (\pm)_{i}=1.$ Так как проекция
+$D_{n+1}$ на $B_{n}$ действует как
+$(e_1,e_2,\dots,e_{n},e_{n+1})\to(e_1,e_2,\dots,e_{n},0)$, сингулярный элемент
+$\Phi^{(\mu)}_{D_{n+1}}$, представляющий собой орбиту $W_{D_{n+1}}$, раскладывается в комбинацию
+орбит  $W_{B_{n}}$ после проекции.
 
-Indeed, if $\mu+\rho_{D_{n+1}}=(a_1,a_2,\dots,a_{n+1})$ in the standart basis
-$(e_1,e_2,\dots,e_{n+1})$, then the Weyl group $W_{D_{n+1}}$ will act on it by permutating $a_i$ and
-changing their signs. After the projection the last coefficient in the every element will be cut. Among
-these elements will be groups in which all elements will have the same set of $a_i$ standing in
-arbitrary order and having an arbitrary sign. These groups will be similar to the orbits of the Weyl
-group $W_{B_{n}}$ but for the singular miltiplicity. A singular miltiplicity is a determinant
-$\varepsilon (w)$ of the element $w$ of the Weyl group. Because of the additional condition on the
-Weyl group $W_{D_{n+1}}$ the change of the signs of $a_i$ doesn't change the singular multiplicity.
-That's not true for the Weyl group $W_{B_{n}}$, thus exactly half of the elements of each newly
-formed orbit $\tilde\Phi^{\tilde\nu}_{B_n}$ of $W_{B_{n}}$ will have the wrong singular
-multiplicity. Moreover, these orbits can be rewritten in the following form:
+А именно, если $\mu+\rho_{D_{n+1}}=(a_1,a_2,\dots,a_{n+1})$ в стандартном базисе
+$(e_1,e_2,\dots,e_{n+1})$, то группа Вейля $W_{D_{n+1}}$ действует на него перестановкой координат
+$a_i$ и сменой их знаков. После проектирования последняя координата каждого веса в орбите должна быть
+отброшена. Среди элементов орбиты будут подмножества, в которых все элементы имеют один и тот же
+набор координат $a_i$, но стоящих в произвольном порядке и имеющих произвольные знаки. Эти
+подмножества похожи на орбиты группы Вейля $W_{B_{n}}$, но с сингулярными кратностями. Сингулярная
+кратность -- это детерминант
+$\varepsilon (w)$ элемента  $w$ группы Вейля. В силу дополнительного условия в группе Вейля
+$W_{D_{n+1}}$ смена знаков  $a_i$ не меняет сингулярной кратности. Однако это не выполняется в
+группе Вейля $W_{B_{n}}$, а значит ровно половина элементов в каждой новопостроенной орбите
+$\tilde\Phi^{\tilde\nu}_{B_n}$ группы $W_{B_{n}}$ будет с неправильной сингулярной кратностью. Более
+того, эти орбиты можно переписать в следующем виде:
 
@@
 \end{equation}
+Это разложение возможно потому, что орбита группы Вейля $D_n$ совпадает с той половиной
+$\tilde\Phi^{\tilde\nu}_{B_n}$, у которой сингулярные кратности правильные, а вторая половина
+получается действием элемента $s_{e_n}$ группы $W_{B_{n}}$.
 
-This decomposition is possible because the orbit of the Weyl group of $D_n$ coincides with the half
-of $\tilde\Phi^{\tilde\nu}_{B_n}$ that has correct singular multiplicities and other half can be
-obtained by the action of the element $s_{e_n}$ of $W_{B_{n}}$.
-
-Thus, the projection $(\Phi^{(\mu)}_{D_{n+1}})'$ consists of $(n+1)$ quasi-orbits (with ``wrong'' signs) of the Weyl group
-$W_{B_{n}}$. It means that there are $(n+1)$ weights in the fundamental Weyl chamber $\bar C_{B_n}$
-of $B_n$. It can be easily shown that these weights are $(a_1,a_2,\dots,a_{n})$ and weights obtained
-from $(a_1,a_2,\dots,a_{n})$ by consequent subtraction of $\mu_i e_i$ starting with $\mu_n e_n$,
-where $\mu_i$ is the Dynkin labels of $\mu$ plus $1$. As it turns out, if one were to add to this set
-the required weights with the corresponding singular multiplicities to construct the singular element of
-$\sfr=A_1+A_1+\dots+A_1$ as was done in the Introduction of this paper, all additional weights would
-lie on the boundaries of the fundamental Weyl chamber $\bar C_{B_n}$. This fact is easily proved by
-observing that the action of one of $s_{\alpha_i^{B_n}}$ on the weights doesn't change those
-weigths. Thus, the projection $(\Phi^{\mu}_{D_{n+1}})'$ can be viewed as a quasi-orbit of the
-singular element of $\sfr$:
+Итак, проекция $(\Phi^{(\mu)}_{D_{n+1}})'$ состоит из  $(n+1)$ квази-орбиты (с  ``неправильными''
+знаками) группы Вейля$W_{B_{n}}$. Значит, в главной камере Вейля  $\bar C_{B_n}$ алгебры
+$B_n$ содержится
+$(n+1)$ вес.  Легко проверить, что это старший вес  $(a_1,a_2,\dots,a_{n})$ и веса, получающиеся из
+него последовательными вычитаниями $\mu_i e_i$, начиная с $\mu_n e_n$, где  $\mu_i$ -- индексы
+Дынкина  $\mu$ плюс $1$. Оказывается, что при дополнении этого множества  весами с
+соответствующими сингулярными кратностями до восстановления сингулярного элемента
+$\sfr=A_1+A_1+\dots+A_1$, как было сделано во введении, все дополнительные веса будут лежать на
+границе главной камеры Вейля $\bar C_{B_n}$. Этот факт легко доказать, если заметить, что действие
+одного из отражений of $s_{\alpha_i^{B_n}}$ на веса не меняет их. Итак, проекция
+$(\Phi^{\mu}_{D_{n+1}})'$ может рассматриваться как квази-орбита сингулярного элемента $\sfr$:
 
@@
 \end{equation}
-where $\tilde\mu=[\mu_1,\mu_2,\dots,\mu_{n}]$. This decomposition yields the branching rules similar to (\ref{bran1}):
+где $\tilde\mu=[\mu_1,\mu_2,\dots,\mu_{n}]$. Это порождает  правила ветвления, аналогичные соотношению (\ref{bran1}):
 
@@
 \end{equation}
-which is in total agreement with the Gelfand-Tsetlin branching rules as the weights of the representations of $\sfr=A_1+A_1+\dots+A_1$ are always equal to one (see Fig.\ref{ris1} and Fig.\ref{ris2}).
+что полностью соответствует правилам ветвления Гельфанда-Цетлина, так как кратности весов в
+представлениях  $\sfr=A_1+A_1+\dots+A_1$ всегда равны единице (см Рис.\ref{ris1} и Рис.\ref{ris2}).
 
@@
 \includegraphics[width=0.95\linewidth]{drawing-1}
-\caption{Splint $D_3= B_2\cup A_1+A_1$: the projection of the singular element $\Phi_{D_3}^{[1,1,2]}$ can be made from singular elements $\Phi_{A_1+A_1}^{[1,1]}$.
-Light-grey area is the fundamental Weyl chamber of subalgebra $B_2$.}
+\caption{Сплинт $D_3= B_2\cup A_1+A_1$: проекция сингулярного элемента  $\Phi_{D_3}^{[1,1,2]}$ может
+  быть построена из сингулярных элементова $\Phi_{A_1+A_1}^{[1,1]}$. Светло-серая область -- это
+  главная камера Вейля подалгебры $B_2$.} 
 \label{ris1} 
@@
 \includegraphics[width=0.9\linewidth,viewport=0 0 157 157,clip]{drawing-3}
-\caption{The injection fan applied to the singular element $\Phi_{A_1+A_1}^{[1,1]}$ yields branching coefficients that are equal to 1.}
+\caption{Веер вложения, примененный к сингулярному элементу $\Phi_{A_1+A_1}^{[1,1]}$, дает
+  коэффициенты ветвления, равные  1.}
 \label{ris2}
@@
 
-A careful examination of the embedding $G_{2}\to B_{3}$ leads to exactly the same conclusion.
+Аналогичное детальное рассмотрение вложения $G_{2}\to B_{3}$ дает такой же результат.
 
-So far we only considered special splints where both embedded systems are root systems. However, it
-is possible to study the splints where it is not the case. Such splints obviously can not serve to
-simplify calculation of the branching rules but one may use the properties of special embeddings and
-the projections to creat a repesentation theory for the systems that are not root systems.
+Мы рассмотрели случаи сплинтов для специальных вложений, в которых вложенные системы являются
+корневыми. Однако можно изучать сплинты и тогда, когда это не выполняется. Такие сплинты нельзя
+использовать для построения правил ветвления, но можно надеяться использовать свойства специальных
+вложений и проекций, чтобы построить теорию представлений для систем векторов, не являющихся
+корневыми системами.
 
-As the result we see that branching coefficients coincide with weight multiplicities for the splints
-in the following table:
+В результате мы видим, что коэффициенты ветвления совпадают с кратностями весов для сплинтов из
+следующей таблицы:
 \begin{equation}
@@
 \end{equation} 
-here the splints marked with (*) are special splints.
+Здесь звездочкой (*) отмечены сплинты, возникающие в специальных вложениях.
 
-\section{Conclusion}
+\section{Заключение}
 \label{sec:conclusion}
 
-The computation of branching coefficients is important for different physical models with a symmetry
-breaking. This computation is drastically simplified if branching coefficients coincide with weight
-multiplicities, since efficient Freudental formula can be used \cite{moody1982fast}. The classification
-of splints for regular and special embeddings gives us all the cases when this coincidence takes
-place. Aside from computational importance, this coincidence is very interesting from
-representation-theoretic point of view, because it follows from the new unexpected connection between
-different simple Lie algebras.
+Вычисление коэффициентов ветвление требуется в различных физических моделях с нарушением симметрии.
+Такое вычисление радикально упрощается, если коэффициенты ветвления совпадают с кратностями весов,
+так как для них можно использовать эффективную формулу Фрейденталя
+\cite{moody1982fast}.Классификация сплинтов для регулярных и специальных вложений дает нам все
+случаи такого совпадения. Помимо облегчения вычислений это совпадение интересно с точки зрения
+теории представлений, так как оно указывает на новую и неожиданную связь между различными алгебрами Ли.
 
-There exist special embeddings of semisimple Lie algebras into simple Lie algebras. For such
-embeddings the procedure of finding splints that allow to calculate branching coefficient is similar
-to the one conducted above. While the results of the procedure are not presented in this paper they
-can be obtained with little difficulty.
+Существуют также специальные вложения полупростых алгебр Ли в простые алгебры Ли. Для таких вложений
+процедура нахождения сплинтов, позволяющих вычислять коэффициенты ветвления, аналогична
+рассмотренной выше. Хотя мы не приводим результаты этой процедуры, их нетрудно получить.
 
-\section*{Acknowledgements}
+\section*{Благодарности}
 \label{sec:acknowledgements}
 
-We thank the organizers of the conference ``In Search of Fundamental Symmetries'' where some results
-of this work were presented.
+Мы благодарим организаторов конференции ``In Search of Fundamental Symmetries'', где были
+представлены некоторые результаты данной работы.
 
-P.I. Kakin would like to acknowledge Saint Petersburg State University for the research grant
-11.38.185.2014.
+П.И. Какинь выражает благодарность СПБГУ за финансовую поддержку в рамках исследовательского гранта  11.38.185.2014.
 

### 2015-03-23 AffineLieAlgebras/Splints/special-paper-ru.tex
Russian bibliography fixed

@@
 
-Специальные вложения подалгебр детально рассматривались в фундаментальных работах Евгения Борисовича Дынкина \cite{dynkin1952semisimple,dynkin1952maximal}, где для них использовалось
+Специальные вложения подалгебр детально рассматривались в фундаментальных работах Евгения Борисовича Дынкина \cite{dynkin1952semisimpleru,dynkin1952maximalru}, где для них использовалось
 название ``S-подалгебры'' чтобы отличить от регулярных или ``R-подалгебр'', полученных путем
@@
 
-Свойства этой проекции описаны в классических работах  \cite{dynkin1952semisimple,dynkin1952maximal} в
+Свойства этой проекции описаны в классических работах  \cite{dynkin1952semisimpleru,dynkin1952maximalru} в
 следующих теоремах:
@@
   $L^{\mu}_{\gf}$ ортогональной проекцией $\hfg^{*}$ на $\hfa^{*}$.
-  \cite{dynkin1952maximal}. 
+  \cite{dynkin1952maximalru}. 
 \end{theorem}
@@
 
-Следующие теоремы \cite{dynkin1952semisimple} также описывают свойства  $\Delta'$.
+Следующие теоремы \cite{dynkin1952semisimpleru} также описывают свойства  $\Delta'$.
 
@@
   проекции корней  $\gf$ на $\hfa^{*}$ являются линейными комбинациями простых корней  $\af$ с
-  целочисленными коэффициентами \cite{dynkin1952semisimple}
+  целочисленными коэффициентами \cite{dynkin1952semisimpleru}
 \end{theorem}
@@
   $\pia(\beta)=\alpha$. 
-  \cite{dynkin1972semisimple,dynkin1952semisimple}. 
+  \cite{dynkin1972semisimple,dynkin1952semisimpleru}. 
 \end{theorem}
@@
 %``characteristic representation of subalgebra $\af$'' by Dynkin in the seminal paper
-%\cite{dynkin1952semisimple}.
+%\cite{dynkin1952semisimpleru}.
 
@@
 где  $M^{\chi}_{\af}$ -- не обязательно неприводимое представление $\af$, названное 
-``характеристическим'' в работе \cite{dynkin1952semisimple}.
+``характеристическим'' в работе \cite{dynkin1952semisimpleru}.
 

### 2015-03-24 AffineLieAlgebras/Splints/special-paper-ru.tex
Grammar fix

@@
 Сплинт -- это разложение корневой системы в объединение образов двух или более вложений других
-корневых систем. Вложением  $\phi$ корневой системы $\Delta_1$ в корневую систему  system $\Delta$
+корневых систем. Вложением  $\phi$ корневой системы $\Delta_1$ в корневую систему $\Delta$
 называется биективное отображение корней $\Delta_{1}$ в (собственное) подмножество  $\Delta$,
@@
 
-Заметим, что мы не требуем от образа $Im(\phi)$ сохранения свойств корневой системы за исключением
-совпадения правил сложения с правилами сложения в $\Delta_{1}$ (для прообразов). Если вложение
+Заметим, что мы не требуем от образа $Im(\phi)$ сохранения каких-либо свойств корневой системы за исключением аддитивных:  
+правила сложения в $Im(\phi)$ совпадают с правилами сложения в $\Delta_{1}$. Если вложение
 $\phi$ сохраняет углы между корнями, то оно называется ``метрическим''. Два вложения $\phi_1$ и
 $\phi_2$ расщепляют корневую систему $\Delta$, если последняя может быть представлена в виде
-дизъюнктного образов $Im(\phi_1)$ и $Im(\phi_2)$.
+дизъюнктного объединения образов $Im(\phi_1)$ и $Im(\phi_2)$.
 
@@
 рассматриваем специальные вложения подалгебр Ли в алгебру Ли. В таком случае корневая система
-подалгебры на содержится в корневой системе алгебры и первоначальная мотивация для введения сплинта
+подалгебры не содержится в корневой системе алгебры, и первоначальная мотивация для введения сплинта
 не применима. Но мы можем рассмотреть проекцию корневой системы алгебры на корневое пространство
 подалгебры. Результат такой проекции уже не будет корневой системой, однако он будет удовлетворять
-более мягким условиям (см Раздел \ref{sec:spec-embedd-proj}). Оказывается, что сплинты проекций
+более мягким условиям (см. Раздел \ref{sec:spec-embedd-proj}). Оказывается, что сплинты проекций
 корневых систем можно классифицировать, используя разложение присоединенного представления алгебры
 в прямую сумму представлений подалгебры. Мы показываем, что при наличии такого сплинта коэффициенты
-ветвления совпадают с кратностями весов в представлениях другой алгебры Ли (Раздел
+ветвления совпадают с кратностями весов в представлениях другой алгебры Ли (см. Раздел
 \ref{sec:splints-spec-embedd}). А значит, в этом случае коэффициенты ветвления очень легко вычислить.
@@
 
-В заключении \ref{sec:conclusion} мы обсуждаем случаи, которые не укладываются в упомянутую выше
+В заключении (см. Раздел \ref{sec:conclusion}) мы обсуждаем случаи, которые не укладываются в упомянутую выше
 классификацию.
@@
 Специальные вложения подалгебр детально рассматривались в фундаментальных работах Евгения Борисовича Дынкина \cite{dynkin1952semisimpleru,dynkin1952maximalru}, где для них использовалось
-название ``S-подалгебры'' чтобы отличить от регулярных или ``R-подалгебр'', полученных путем
+название ``S-подалгебры'', чтобы отличить от регулярных или ``R-подалгебр'', полученных путем
 исключения некоторых корней из корневой системы алгебры. Все регулярные подалгебры нетрудно построить
@@
 подалгебры Картана будем обозначать через $\hfg$ и $\hfa$, и отождествим их с дуальными
-пространствами $\hfg^{*}$, $\hfa^{*}$ используя формы Киллинга алгебр  $\gf$ и $\af$.
+пространствами $\hfg^{*}$, $\hfa^{*}$, используя формы Киллинга алгебр  $\gf$ и $\af$.
 
@@
 Применяя эту теорему к присоединенному представлению  $\gf$, видим, что проекция корневой
-системы  $\Delta_{\gf}$ на $\hfa^{*}$ оказывается весовой системой некоторого конечномерного но не
+системы  $\Delta_{\gf}$ на $\hfa^{*}$ оказывается весовой системой некоторого конечномерного, но не
 обязательно неприводимого представления $\af$. Более того, это приводимое представление должно
@@
   соответствующий корню $\alpha$ алгебры $\af$, представляется в виде линейной комбинации  $e_{\alpha}=\sum_{\beta}
-  e_{\beta}$ генераторов $\gf$ соответствующих корням  $\beta$ алгебры $\gf$, тогда все эти корни
+  e_{\beta}$ генераторов $\gf$, соответствующих корням  $\beta$ алгебры $\gf$, тогда все эти корни
   $\beta$ проектируются в  $\alpha$,
@@
 такие, что их весовая диаграмма совпадает с некоторой корневой системой после исключения нулевого
-веса. Во-первых, заметим, что все веса  $M^{\chi}_{\af}$ должны быть  не меньшей длины чем
-кратчайший корень $\af$, так как $\af$ -- целочисленная подалгебра $\gf$ \ref{dyn1}. Во-вторых,
+веса. Во-первых, заметим, что все веса  $M^{\chi}_{\af}$ должны быть  не меньшей длины, чем
+кратчайший корень $\af$, так как $\af$ -- целочисленная подалгебра $\gf$ [\ref{dyn1}]. Во-вторых,
 $M^{\chi}_{\af}$ должна содержать веса не более, чем двух разных длин.
@@
 \Delta_{\af},$ ортогональные корневой системе подалгебры, то сингулярный элемент не допускает
-разложения \ref{eq:4}.  В этом случае элементы формальной алгебры $e^{\nu}$ проекции
+разложения (\ref{eq:4}).  В этом случае элементы формальной алгебры $e^{\nu}$ проекции
 $\pia\left(\Psi^{\mu}_{\gf}\right)$ надо снабдить размерностями представлений алгебры $\afb$,
 порожденной генераторами, соответствующими ортогональным корням \cite{2010arXiv1007.0318L}. Тогда
-правая часть разложения  \ref{eq:4} будет содержать нетривиальные кратности и совпадение
+правая часть разложения (\ref{eq:4}) будет содержать нетривиальные кратности, и совпадение
 коэффициентов ветвления с кратностями весов в представлениях  $\sfr$ не будет иметь места. В
@@
 \begin{itemize}
-\item (1) $\mu$ -- микровес
-\item (2) $\mu$ -- квазимикровес и в алгебре Ли только один короткий простой корень,
-\item (3) алгебра Ли $\mathfrak{sp}(6)$ и $\mu=\omega_{1}$, и
+\item (1) $\mu$ -- микровес,
+\item (2) $\mu$ -- квазимикровес, и в алгебре Ли только один короткий простой корень,
+\item (3) алгебра Ли $\mathfrak{sp}(6)$ и $\mu=\omega_{1}$,
 \item (4) алгебра Ли $\mathfrak{sl}(n + 1)$ и  $\mu= m\omega_{1}$ или $\mu  = m\omega_{n}$ 
@@
 Нам следует рассмотреть представления класса  (4) только при $m=1,2$, так как корневая система
-$\Delta_{\sfr}$ может содержать корни не более чем двух разных длин. В случае case $m=1$ мы снова
+$\Delta_{\sfr}$ может содержать корни не более чем двух разных длин. В случае $m=1$ мы снова
 получаем строго свободные от кратностей модули $A_{r}$, которые уже обсуждались выше. А для алгебры
@@
 представления $A_{r}$. А значит, нет и соответствующего вложения $A_{r}\to D_{r+1}$ и сплинта.
-Условия \ref{eq:5},\ref{eq:6} не выполняются.
+Условия \ref{eq:5} и \ref{eq:6} не выполняются.
 
@@
 раскладывается в сумму двух копий присоединенного представления $B_{r}$. Легко проверить перебором,
-что подходящего решения для $\gf$, удовлетворяющего условиям \ref{eq:5}\ref{eq:6}, не существует в
-сериях $A$, $B$, $C$, $D$, не подходят и все исключительные простые алгебры Ли.
+что подходящего решения для $\gf$, удовлетворяющего условиям \ref{eq:5} и \ref{eq:6}, не существует в
+сериях $A$, $B$, $C$, $D$; не подходят и все исключительные простые алгебры Ли.
 
-Так как число корней корневой системы  $C_{r}$ такое же, как и в $B_{r}$ и нам нужно проверять те же
+Так как число корней корневой системы  $C_{r}$ такое же, как и в $B_{r}$, и нам нужно проверять те же
 случаи, мы видим, что для $C_{r}$ тоже нет подходящего вложения.
@@
 Присоединенное представление алгебры $G_{2}$ дает нам алгебру  $D_{4}$ в качестве решения условий
-\ref{eq:5},\ref{eq:6}. Вложение  $G_{2}\to D_{4}$ существует, так как есть вложения $G_{2}\to B_{3}$
+\ref{eq:5}, \ref{eq:6}. Вложение  $G_{2}\to D_{4}$ существует, так как есть вложения $G_{2}\to B_{3}$
 и $B_{3}\to D_{4}$, но разложение присоединенного представления $D_{4}$ другое: $
@@
 
-После получения полной классификации сплинтов проекций корневых систем при специальных вложениях,
+После получения полной классификации сплинтов проекций корневых систем при специальных вложениях
 необходимо проверить совпадение коэффициентов ветвления с кратностями весов в модулях алгебры $\sfr$.
@@
 Дынкина  $\mu$ плюс $1$. Оказывается, что при дополнении этого множества  весами с
-соответствующими сингулярными кратностями до восстановления сингулярного элемента
+соответствующими сингулярными кратностями до восстановления сингулярного элемента алгебры
 $\sfr=A_1+A_1+\dots+A_1$, как было сделано во введении, все дополнительные веса будут лежать на
@@
 одного из отражений of $s_{\alpha_i^{B_n}}$ на веса не меняет их. Итак, проекция
-$(\Phi^{\mu}_{D_{n+1}})'$ может рассматриваться как квази-орбита сингулярного элемента $\sfr$:
+$(\Phi^{\mu}_{D_{n+1}})'$ может рассматриваться как квази-орбита сингулярного элемента алгебры $\sfr$:
 
@@
 что полностью соответствует правилам ветвления Гельфанда-Цетлина, так как кратности весов в
-представлениях  $\sfr=A_1+A_1+\dots+A_1$ всегда равны единице (см Рис.\ref{ris1} и Рис.\ref{ris2}).
+представлениях алгебры $\sfr=A_1+A_1+\dots+A_1$ всегда равны единице (см. Рис.\ref{ris1} и Рис.\ref{ris2}).
 
@@
 случаи такого совпадения. Помимо облегчения вычислений это совпадение интересно с точки зрения
-теории представлений, так как оно указывает на новую и неожиданную связь между различными алгебрами Ли.
+теории представлений, так как оно указывает на новую и неожиданную связь между различными алгебрами
+Ли.
 

### 2015-08-03 AffineLieAlgebras/TensorProducts/notes.tex
Update of special-splints paper, started paper on graded tensor products, some notes and older talks added too

\documentclass[12pt]{article}

\usepackage{latexsym,amsmath,amssymb}
%\usepackage{amsfonts}
\usepackage{pb-diagram}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%\usepackage{setstack}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}

\usepackage{ucs} \usepackage[utf8x]{inputenc}
\usepackage[english,russian]{babel}

\newtheorem{Def}{Definition}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{statement}{Statement}
\newtheorem{Cnj}[Def]{Conjecture}
\newtheorem{Prop}[Def]{Property}
\newtheorem{example}{Example}[section]

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfg}{\hf_{\gf}}
\newcommand{\hfa}{\hf_{\af}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\sfr}{\mathfrak{s}}

\newcommand{\cR}{\check{R}}

%%%%%%%%%% Young tableaux %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newdimen\tableauside\tableauside=1.0ex
\newdimen\tableaurule\tableaurule=0.4pt
\newdimen\tableaustep
\def\phantomhrule#1{\hbox{\vbox to0pt{\hrule height\tableaurule width#1\vss}}}
\def\phantomvrule#1{\vbox{\hbox to0pt{\vrule width\tableaurule height#1\hss}}}
\def\sqr{\vbox{%
  \phantomhrule\tableaustep
  \hbox{\phantomvrule\tableaustep\kern\tableaustep\phantomvrule\tableaustep}%
  \hbox{\vbox{\phantomhrule\tableauside}\kern-\tableaurule}}}
\def\squares#1{\hbox{\count0=#1\noindent\loop\sqr
  \advance\count0 by-1 \ifnum\count0>0\repeat}}
\def\tableau#1{\vcenter{\offinterlineskip
  \tableaustep=\tableauside\advance\tableaustep by-\tableaurule
  \kern\normallineskip\hbox
    {\kern\normallineskip\vbox
      {\gettableau#1 0 }%
     \kern\normallineskip\kern\tableaurule}%
  \kern\normallineskip\kern\tableaurule}}
\def\gettableau#1 {\ifnum#1=0\let\next=\null\else
  \squares{#1}\let\next=\gettableau\fi\next}

\begin{document}

\title{Заметки про квантовые группы, интегрируемые системы и все такое}

%% \author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$, O.V.~Postnova$^{1}$}
%% \address{ $^1$ Department of High-energy and elementary particle physics,  St Petersburg State University, 198904, Saint-Petersburg, Russia}
%% \ead{ $^{2}$ e-mail: antonnaz@gmail.com}
%%

\begin{abstract}

  We show the connection of formulae for tensor product multiplicities with cluster algebras. 
  \noindent{\it Keywords\/}: Lie algebra, tensor product, multiplicity, cluster algebra, grading
\end{abstract}

\section{Introduction}
\label{sec:introduction}
\cite{di2013quantum}
\bibliography{bibliography}{} 
\bibliographystyle{iopart-num}

\subsection{Алгебры Хопфа}
\label{sec:hopf}
\begin{Def}
  {\it Алгебра Хопфа $(H,\mu,1_H,\Delta,\epsilon,S)$} - это
  векторное пространство$H$ над полем $k$, наделенное
  структурой алгебры с умножением $\mu:H\otimes H\to H$ и
  единицей $1_H$, коалгебры с коумножением $\Delta:H\to
  H\otimes H$ и коединицей $\epsilon:H\to k$, а так же
  антиподом $S$ - линейным отображением $S:H\to H$. Причем все
  эти структуры должны быть согласованы друг с другом.

  чтобы следующие диаграммы были коммутативны:
  \[
  \begin{diagram}
    \node{H\otimes H} \arrow{e,t}{\mu}
    \arrow{s,r}{\Delta\otimes \Delta} \node{H}
    \arrow{e,t}{\Delta}
    \node{H\otimes H} \\
    \node{H\otimes H\otimes H\otimes H}
    \arrow[2]{e,t}{id\otimes \tau\otimes id}
    \node[2]{H\otimes H\otimes H\otimes H}
    \arrow{n,r}{\mu\otimes \mu}
  \end{diagram}
  \]
  \[
  \begin{diagram}
    \node{H} \arrow{e,t}{\epsilon} \node{k} \node{k}
    \arrow{e,r}{\eta} \arrow{se,r}{\eta\otimes\eta}
    \node{H}\\
    \node{H\otimes H} \arrow{n,r}{\mu}
    \arrow{ne,r}{\epsilon\otimes\epsilon} \node[3]{H\otimes
      H} \arrow{n,r}{\Delta}
  \end{diagram}
  \]
  \[
  \begin{diagram}
    \node{H} \arrow{e,t}{\epsilon} \arrow{s,r}{\Delta}
    \node{k} \arrow{e,t}{\eta}
    \node{H}\\
    \node{H\otimes H} \arrow[2]{e,t}{id\otimes S,\ S\otimes
      id} \node[2]{H\otimes H} \arrow{n,r}{\mu}
  \end{diagram}
  \]
  , где $\eta$ - отображение $k\to H,\quad \eta(a)=a\ 1_{H}$

  Подробное определение есть, например, в книге Маджида
  \cite{Majid}.
\end{Def}
Универсальную обертывающую алгебру $U(g)$ любой алгебры Ли $g$ можно наделить структурой
(тривиальной) алгебры Хопфа следующим образом: $\Delta(f)=f\otimes 1 + 1 \otimes f,\
\epsilon(f)=0,\ S(f)=-f,\ f\in g$

На векторных пространствах алгебры Хопфа действуют так же, как
и обычные алгебры. Однако если векторное пространство само
наделено структурой алгебры, то действие алгебры Хопфа должно
быть согласовано со структурой алгебры на векторном
пространстве, чтобы оно могло называться модуль-алгеброй.
\begin{Def}
  \label{ModuleAlgebra}
  {\it $H$-модуль-алгеброй} называется алгебра $A$, на которой
  действие алгебры Хопфа $H$ согласовано с алгебраической
  структурой:
  \begin{eqnarray}
    h\triangleright (a\cdot b) = \sum (h_{(1)}\triangleright a) \cdot (h_{(2)}\triangleright b) \\
    h\triangleright 1 = \epsilon(h)1
  \end{eqnarray} 
  , где $a,b\in A,\ h\in H,\ \Delta(h)=\sum h_{(1)}\otimes
  h_{(2)}$

  Наглядно определение можно представить следующими
  диаграммами:
  \[
  \begin{diagram}
    \node{H\otimes A \otimes A} \arrow{e,t}{\cdot}
    \arrow{s,r}{\Delta\otimes id\otimes id} \node{H\otimes A}
    \arrow{e,t}{\triangleright} \node{A} \node{A\otimes A}
    \arrow{w,t}{\cdot}
    \\
    \node{H\otimes H \otimes A \otimes A} \arrow[3]{e,t}{id
      \otimes \tau \otimes id} \node[3]{H\otimes A \otimes H
      \otimes A} \arrow{n,l}{\triangleright \otimes
      \triangleright}
  \end{diagram}
  \]

  \[
  \begin{diagram}
    \node{H} \arrow{e,t}{\epsilon} \arrow{s,l}{\eta} \node{k}
    \arrow{e,t}{\eta} \node{A}
    \\
    \node{H\otimes A} \arrow{ene,r}{\triangleright}
  \end{diagram}
  \]

\end{Def}

Если $H$ действует на пространствах $V$ и $W$, то на тензорном
произведении $V\otimes W$ действие $h\in H$ дается формулой
\begin{equation}
  \label{HopfAlgebraActionOnTensorProduct}
  h\triangleright (v\otimes w) = \sum (h_{(1)}\triangleright v) \otimes (h_{(2)} \triangleright w)
\end{equation}
, где $\Delta(h)=\sum h_{(1)}\otimes h_{(2)}$

\subsection{$U_q(\mathfrak{sl}_2)$}
\label{sec:u_q_sl_2}

\subsection{Yangians}
\label{sec:yangians}

For any finite-dimensional semisimple Lie algebra $\af$, Drinfeld defined an infinite-dimensional
Hopf algebra $Y(\af)$, called the Yangian of $\af$. This Hopf algebra is a deformation
of the universal enveloping algebra $U(\af[z])$ of the Lie algebra of polynomial loops
of $\af$ given by explicit generators and relations. The relations can be encoded by identities
involving a rational $R$-matrix. Replacing it with a trigonometric $R$-matrix, one
arrives at affine quantum groups, defined in the same paper of Drinfeld.

In the case of the $\mathfrak{gl}_{N}$, the Yangian admits a simpler description in terms of a single ``ternary'' (or ``RTT'') relation on the matrix generators due to Faddeev and coauthors. 
The Yangian $Y(\mathfrak{gl}_{N})$ is defined to be the algebra generated by elements $t_{ij}^{(p)}$ with $1 \leq i, j \leq N$ and $p \geq 0$, subject to the relations:

\begin{equation}
  \label{eq:1}
 [t_{ij}^{(p+1)}, t_{kl}^{(q)}] -  [t_{ij}^{(p)}, t_{kl}^{(q+1)}]= -(t_{kj}^{(p)}t_{il}^{(q)} - t_{kj}^{(q)} t_{il}^{(p)}).
\end{equation}

Defining $t_{ij}^{(-1)}=\delta_{ij}$, setting $ T(z) = \sum_{p\ge -1} t_{ij}^{(p)} z^{-p+1}$

and introducing the $R$-matrix $R(z) = I + z^{-1} P$ on $\mathbb{C}^{N}\otimes \mathbb{C}^{N}$,
where $P$ is the operator permuting the tensor factors, the above relations can be written more
simply as the ternary relation:

$\displaystyle{ R_{12}(z-w) T_{1}(z)T_{2}(w) = T_{2}(w) T_{1}(z) R_{12}(z-w).}$

The Yangian becomes a Hopf algebra with comultiplication $\Delta$, counit $\epsilon$ and antipode $S$ given by
\begin{equation}
  \label{eq:2}
  (\Delta \otimes \mathrm{id})T(z)=T_{12}(z)T_{13}(z), \,\, (\varepsilon\otimes \mathrm{id})T(z)= I, \,\, (s\otimes \mathrm{id})T(z)=T(z)^{-1}.
\end{equation}

At special values of the spectral parameter $(z-w) $, the $R$-matrix degenerates to a rank one
projection. This can be used to define the quantum determinant of $T(z) $, which generates the
center of the Yangian.

The {\it twisted Yangian} $Y^{-}(\mathfrak{gl}_{2N})$, introduced by G. I. Olshansky, is the sub-Hopf algebra generated by the coefficients of

$\displaystyle{ S(z)=T(z)\sigma T(-z),}$

where $\sigma$ is the involution of $\mathfrak{gl}_{2N}$ given by

$\displaystyle{\sigma(E_{ij}) = (-1)^{i+j}E_{2N-j+1,2N-i+1}.}$
Quantum determinant is the center of Yangian.

\section{Yangians and their representations}

\subsection{Yangians}

\subsubsection{Definition of $Y(\gf)$: algebra and co-algebra}

Let the simple Lie algebra $\gf$  be generated\footnote{To avoid
becoming mired in detail, we have used anti-Hermitian generators
(hence no `$i$'), and, more importantly, compactness (hence an
inner product proportional to $\delta_{ab}$, so that we won't have
to distinguish `up' from `down' indices).} by $\{I_a\}$,
$a=1,\ldots,$dim$\,\gf$, with structure constants $f_{abc}$,
\begin{equation}\label{Y1}\left[ I_a , I_b \right] = f_{abc} I_c \,,\end{equation}
 and (trivial) coproduct\footnote{The enveloping algebra $U\gf$ of $\gf$
consists of (powers, polynomials and) series in the $I_a$ subject
to the Lie bracket, regarded as a commutator.} $\Delta:
U\gf\rightarrow U\gf\otimes U\gf$, \begin{equation}\label{Y1del}
 \Delta(I_a) = I_a \otimes 1
+ 1 \otimes I_a \,. \end{equation}
 For those new to it, the
coproduct is a generalization of the usual rule for addition of
spin. As such, the principal constraints on $\Delta$ are that it
be coassociative, \begin{equation}\label{coassoc} (\Delta\otimes
1)\Delta(x)=(1\otimes\Delta)\Delta(x)\end{equation} for all $x\in\gf$ (so that
the action of $x$ on a 3-particle state is unique), and that it
 be a homomorphism, \begin{equation}\label{hom} \Delta([x,y])=[\Delta(x),\Delta(y)]
  \end{equation} for all $x,y\in\gf$ (so that multiparticle states carry
 representations of the symmetry algebra). As we shall see below,
 there are non-trivial ways in which this can be achieved.

The Yangian \cite{drinf1,drinf2} $Y(\gf)$ is the enveloping algebra
generated by these and a second set of generators $\{J_a\}$, in
the adjoint representation of $\gf$ so that \begin{equation}\label{Y2} \left[
I_a , J_b \right] =   f_{abc} J_c \,, \end{equation} but with a non-trivial
coproduct \begin{equation}\label{Y2del} \Delta:Y(\gf)\rightarrow Y(\gf)\otimes
Y(\gf)\,,\qquad \Delta(J_a) = J_a \otimes 1 + 1 \otimes J_a +
{\alpha\over 2}f_{abc} I_c \otimes I_b\, \end{equation} for a parameter
$\alpha\in{\mathbb C}$. Note that (\ref{coassoc},\,\ref{hom}) hold
for all the $I_a,J_a$.

The commutator $[J_{a},J_{b}]$ is not fully specified, but is
constrained by the requirement that $\Delta$ be a homomorphism (as
explained in the next subsection): \begin{equation}\label{Y3}
[J_a,[J_b,I_c]]-[I_a,[J_b,J_c]] = \alpha^2
a_{abcdeg}\{I_d,I_e,I_g\} \,, \end{equation} where \begin{equation}
 a_{abcdeg}={1\over{24}}
 f_{adi} f_{bej}f_{cgk}f_{ijk}
 \hspace{0.1in},\hspace{0.15in}\{x_1,x_2,x_3\}=
 \sum_{i\neq j\neq k}x_{i}x_{j}x_{k} \,,
\end{equation} and \begin{equation}\label{Y4} [[J_a,J_b],[I_l,J_m]] +
[[J_l,J_m],[I_a,J_b]] = \alpha^2 \left( a_{abcdeg}f_{lmc} +
a_{lmcdeg}f_{abc} \right) \left\{ I_d,I_e,J_g \right\} \,. \end{equation} For
$\gf=a_1$,  (\ref{Y3}) is trivial, while for $\gf\neq a_1$,
(\ref{Y3}) implies (\ref{Y4}), which is thus
redundant\footnote{Throughout these lectures, we write specific
$\gf$ as $a_n={\mathfrak{su}}_{n+1}$, $b_n={\mathfrak{so}}_{2n+1}$,
$c_n={\mathfrak{sp}}_n$, $d_n={\mathfrak{so}}_{2n}$, along with
$e_6,e_7,e_8,f_4,g_2$.}.

In the original sense of the word `quantum' in `quantum group',
the parameter $\alpha$ is proportional to $\hbar$: it measures the
deformation of the `auxiliary' Lie algebra required to make the
quantum inverse scattering method work. In the next lecture, by
contrast, we shall see $Y(\gf)$ appearing explicitly as a charge
algebra, with $\alpha=1$ and $\hbar$ making a conventional
appearance on the right-hand side of each commutator.

Finally, there are also other structures on which we place less
emphasis but which make $Y(\gf)$ a Hopf algebra and which we give
for completeness: a co-unit \begin{equation} \epsilon: Y(\gf)\rightarrow
{\mathbb C}\,,\qquad \epsilon (I_a)=0,\quad\epsilon(J_a)=0\end{equation}
(physically a one-dimensional vacuum representation, trivial for
$Y(\gf)$), and an antipode \begin{equation} \label{antipode}s:Y(\gf)\rightarrow
Y(\gf)\,,\qquad s(I_a)=-I_a,\quad s(J_a)=-J_a+{1\over 2}f_{abc}I_c
I_b\,,\end{equation} an anti-automorphism (and physically a
$PT$-transformation).

\subsubsection{Drinfeld's `terrific' relation}

 Drinfeld
called the relations (\ref{Y3}) and (\ref{Y4}) `terrific'
\cite{drinf2}, and it is worth explaining their origin and
significance further (see also \cite{gron}). First, the left-hand
side of (\ref{Y3}) is a little more intuitive if we instead write
it as \begin{equation}\label{Y3'} [J_a,[J_b,I_c]]-[I_a,[J_b,J_c]] =
f_{d(ab}[J_{c)},J_d], \end{equation} where $(abc)$ means `the sum of $abc$
and cycles thereof'. One way of viewing $Y(\gf)$ is as a
deformation of the polynomial algebra $\gf[z]$: if $\alpha=0$, then
the algebra reduces to that of $I_a$ and $J_a\equiv z I_a$,
whereupon (\ref{Y3}) is just the Jacobi identity
$f_{d(ab}f_{c)de}=0$. So a natural way to think about $Y(\gf)$ is
as a graded algebra, in which $I_a$ has grade zero and $J_a$ and
$\alpha$ each grade one, and (\ref{Y3}) and (\ref{Y4}) are viewed
as constraints on the construction of higher-grade elements. For
example, suppose we define a grade-two element \begin{equation} K_a \equiv
{1\over c_A} f_{abc}[J_c,J_b] \qquad{\rm (where\;\;}
f_{abc}f_{dcb}=c_A \delta_{ad}\;). \end{equation} Then if we write\begin{equation}
[J_b,J_c]=f_{bcd}K_d + X_{bc}\,, \end{equation} (\ref{Y3}) fixes $X_{bc}$:
for suppose not, that there exists another possible $X'_{bc}$.
Then, setting $Y_{bc}=X'_{bc}-X_{bc}$, (\ref{Y3}) implies that
$f_{d(ab}Y_{c)d}=0$, and thus (equivalent to the statement
 that the second cohomology $H^2(\gf)=0$) that $Y_{cd}=f_{cde}Z_e$
 for some $Z_e$. But then
$c_A Z_a = f_{abc} f_{cbd}Z_d = f_{abc}Y_{cb}=c_A(K_a-K_a)=0$, so
$Z_a=0$ and so $X'_{bc}=X_{bc}$.

The origin of (\ref{Y3}) lies in first postulating $\Delta(J_a)$
in (\ref{Y2del}) and then requiring that this be a homomorphism.
To see this, first let $u_{ab}$ be such that $u_{ab}=-u_{ba}$ and
\begin{equation}\label{u1} u_{ab} [ I_a,I_b ] = 0 \,. \end{equation} Now compute \begin{equation}
u_{ab}\left(\Delta \left( [J_{a},J_{b}] \right) - 1\otimes
[J_a,J_b] - [J_a,J_b] \otimes 1 \right) \,. \end{equation} The parts of this
expression involving $J$ disappear because of (\ref{u1}), whilst
the remainder is
\begin{equation}gin{equation}\label{u2}
{1\over 2}u_{ab}f_{ade}f_{bgh}f_{dgk} \left( I_k \otimes I_e I_h +
I_e I_h\otimes I_k \right) \,.
\end{equation}
Because of (\ref{u1}), or $f_{abc}u_{ab}=0$, we may write \begin{equation}
u_{ab}= v_{dea} f_{deb} - v_{deb} f_{dea}   \end{equation} (equivalent to the
second homology $H_2(\gf)=0$). Requiring $\Delta$ to be a
homomorphism for all $v$, and using the Jacobi identity twice, we
obtain (\ref{Y3}).

\subsubsection{The $R$-matrix}

$Y(\gf)$ is closely related to the Yang-Baxter equation, which has
a rich literature in its own right (see \cite{jimbo}). A nice way
to see this, of which we give a sketch here, is to define a new
object, the monodromy matrix, \begin{equation} T(\lambda) \equiv \exp\left(
-{1\over \lambda}t^aI_a + {1\over \lambda^2}t^aJ_a-{1\over
\lambda^3}t^aK_a+\ldots\right), \end{equation} where $\lambda\in{\mathbb C}$
is a new, `spectral' parameter. The $\ldots$ denote higher terms,
of an appropriate-grade element constructed by repeated
commutation of $J$s, and the $t^a$ are a second set of generators
of $\gf$ (commuting with $Y(\gf)$), to be thought of as matrices
(perhaps in the defining representation of $\gf$, where this
exists) with elements $t^a_{ij}$. Thus, overall, $T$ is a matrix,
with entries which are elements of $Y(\gf)$.

The significance of $T$ lies in the fact that \begin{equation}\label{Tdel}
\Delta(T_{ij}(\lambda))=T_{ik}(\lambda) \otimes
T_{kj}(\lambda)\,.\end{equation} The first few terms are easily checked using
(\ref{Y1del},\,\ref{Y2del}): at order $\lambda^{-2}$, for example,
the non-trivial terms in the $\Delta(J_a)$ on the left are matched
on the right not only with the order-$\lambda^{-2}$ terms in each
exponential but also with the cross-terms from multiplying the
order-$\lambda^{-1}$ term in each $T$.

Now, $Y(\gf)$ has an (outer) automorphism \begin{equation}\label{auto}
L_\mu\,:\quad I_a\mapsto I_a\,,\qquad J_a\mapsto J_a+\mu I_a
\qquad(\mu\in{\mathbb C})\end{equation} (equivalent to $z\mapsto z+\mu$ in
the polynomial algebra if $\alpha=0$), whose action on $T$ is \begin{equation}
T(\lambda)\mapsto T(\lambda+\mu)\,.\end{equation} Let us consider the
intertwiners $\cR$, which are required to satisfy \begin{equation}\label{R}
\cR(\nu-\mu)\,. \;L_\mu\!\times\! L_\nu\left(\Delta(x)\right)
=L_\nu\!\times\! L_\mu\left(\Delta(x)\right) .\,\cR(\nu-\mu)\end{equation}
for any $x\in Y(\gf)$. (Strictly, we should only take
representations of this, and our intertwiner, conventionally
written $\cR$, and then an `$R$-matrix', is often written
$\cR={\bf P}R$ where ${\bf P}$ permutes the two module elements in
the tensor product---but we wish to defer all discussion of
representations to the next section.)

Thus \begin{equation} \label{RTT}\cR(\nu-\mu)\, T_{ik}(\mu)\otimes T_{kj}(\nu)
= T_{ik}(\nu)\otimes T_{kj}(\mu) \,\cR(\nu-\mu)\,.\end{equation}  There are
then two maps \begin{equation} T_{ik}(\mu)\otimes T_{kl}(\nu)\otimes
T_{lj}(\lambda) \mapsto T_{ik}(\lambda)\otimes T_{kl}(\nu)\otimes
T_{lj}(\mu)\,,\end{equation} and their equivalence \begin{equation}\label{YBE}
\cR(\lambda-\nu)\otimes 1\,.\, 1\otimes \cR(\lambda-\mu)\,.\,
\cR(\nu-\mu)\otimes 1 = 1\otimes\cR(\nu-\mu)\,.\,
\cR(\lambda-\mu)\otimes 1\,.\,1\otimes \cR(\lambda-\nu)\end{equation} is the
Yang-Baxter equation (YBE), illustrated schematically in fig.1.

This equation is familiar from 1+1D $S$-matrix theory, where it is
the condition for consistent factorization of the multiparticle
$S$-matrix into two-particle factors.
\begin{figure}[htb]
\hspace{32mm} \setlength{\unitlength}{1mm}
\begin{picture}(120,30)(15,15)
\put(8,-6){\line(1,3){17}} \put(98,-6){\line(1,3){17}}
\put(44,-6){\line(-2,3){34}} \put(114,-6){\line(-2,3){34}}
\put(-3,-2){\line(5,3){43}} \put(127,38){\line(-5,-3){43}}
\put(60,20){\makebox(0,0){=}}
\put(19,5){\makebox(0,0){\footnotesize $\cR(\nu\!-\!\mu)$}}
\put(37,16){\makebox(0,0){\footnotesize$\cR(\lambda\!-\!\mu)$}}
\put(28,31){\makebox(0,0){\footnotesize$\cR(\lambda\!-\!\nu)$}}
\put(111,10){\makebox(0,0){\footnotesize$\cR(\lambda\!-\!\nu)$}}
\put(88,21){\makebox(0,0){\footnotesize$\cR(\lambda\!-\!\mu)$}}
\put(116,25){\makebox(0,0){\footnotesize$\cR(\nu\!-\!\mu)$}}
\end{picture}\vspace{20mm}
\caption{The Yang-Baxter equation}
\end{figure}
Each line in the figure will carry a representation of $Y(\gf)$.
The simplest case, in which this is ${\mathbb C}^2$, yielded the
first solution of this equation, due to Yang \cite{Yang},
\begin{equation}\label{firstR}
\cR(\mu) = \left(\begin{array}{cccc} 1+\mu &  0 & 0 & 0\\
                      0 & 1 & \mu & 0\\
                       0& \mu & 1 & 0\\
                  0  &0 & 0& 1+\mu
\end{array}\right) \,.
\end{equation} $Y({\frak sl}_2)$ can be built from it, and it was in honour
of this that Drinfeld named the Yangian.

 A theorem of Belavin and Drinfeld \cite{beldr} is that
(subject to certain technical conditions) as
$\mu\rightarrow\infty$ all YBE solutions which are rational
functions of $\mu$ (and we shall see that this is so for the
Yangian $\cR(\mu)$ in the next section) are of the asymptotic form
\begin{equation} \cR(\mu) = {\bf P}\left( 1\otimes 1 + {1\over \mu} I_a\otimes
I_a + {\cal O}(\mu^{-2})\right),\end{equation} This leads not only to the
uniqueness of $Y(\gf)$, but also to the possibility of
rediscovering much about Lie algebras and their representations
purely by studying YBE solutions \cite{cher2}.

\subsection{Representations of Yangians}

Since $Y(\gf)\supset \gf$, and representations (`reps') of $Y(\gf)$
will also be reps of $\gf$, the representation theory of $\gf$ is a
good starting point. Recall that, for a Lie algebra $\gf$ of rank
$r$, there are $r$ distinguished, `fundamental' irreducible
representations (`irreps'). The story is similar for $Y(\gf)$,
which also has $r$ fundamental (and finite-dimensional) irreps
\cite{gron,drinf88}.

However, a rep which is  $Y(\gf)$-irreducible may be
$\gf$-reducible, and this is typically the case for the fundamental
irreps of $Y(\gf)$, whose $\gf$-components are the corresponding
fundamental irrep of $\gf$ and (generally) some others. These
decompositions appeared incrementally in the literature
\cite{ogiev86,chari91,KR}; for a full enumeration for simply-laced
$\gf$ see \cite{kleber96}.

\subsubsection{$Y(\gf)$-reps which are $\gf$-irreps}

The simplest situation is clearly when a $\gf$-irrep is extensible
to a $Y(\gf)$-irrep, and there are no other components. Drinfeld
enumerated the cases for which this occurs \cite{drinf1}. Starting
from an irrep $\rho$ of $\gf$, he constructed a rep $\tilde{\rho}$
of $Y(\gf)$ by setting
\begin{equation}\label{rep}
\tilde\rho(I_a) = \rho(I_a) \,, \qquad \tilde\rho(J_a) = 0 \,.
\end{equation}
Now, although $\tilde\rho$ is clearly consistent with
(\ref{Y1},\,\ref{Y2}), it is not, in general, consistent with
(\ref{Y3}) (we specialize here to $\gf\neq a_1$, and so do not
consider (\ref{Y4}) separately). Consistency is only possible for
irreps in which the right hand side of (\ref{Y3}) vanishes. This
is the case for the following irreps.

 Let $n_i$ be the coefficient of the simple
root ${\alpha}_i\in{\mathbb R}^r$ ($i=1,\ldots,r$) in the
expansion of the highest root ${\alpha}_{\rm max}$ of $\gf$, and
let $k_i = ({\alpha}_{\rm max},{\alpha}_{\rm
max})/({\alpha}_i,{\alpha}_i)$. Let the corresponding fundamental
weight be ${\omega}_i$. The irrep of $\gf$ with highest weight
${\Omega}$ may then be extended to an irrep of $Y(\gf)$ using
(\ref{rep}) for \begin{equation}
\begin{array}{rcl}
 & (i) & {\Omega}={\omega}_i \quad {\rm when } \quad
 n_i=k_i\\[0.2in]

 {\rm and} & (ii) &
  {\Omega}=t{\omega}_i\quad {\rm when }
 \quad n_i=1
 \qquad (t\in{\mathbb Z}).\end{array}\label{irreps} \end{equation}
These include all the fundamental irreps of $a_n$ and $c_n$, and
the vector and spinor irreps of $b_n$ and $d_n$. Only for one
algebra, $e_8$, is there no such rep.

A sketch of the proof of this is as follows. First, we need to
know the $\gf$-rep $X$ in which the right-hand side of (\ref{Y3})
acts. Since the $J_a$ form an adjoint representation of $\gf$, it
is clear from (\ref{Y3'}) that the left-hand side of (\ref{Y3}) is
contained in $\Lambda^2(\gf)$, the antisymmetric part of $\gf\otimes
\gf$. Further (and, as we saw above, equivalent to $H^2(\gf)=0$),
\begin{equation} f_{d(ab}u_{c)d}=0 \hspace{0.2in} \Rightarrow \hspace{0.2in}
u_{ab} = f_{abc}v_c \,, \end{equation} so that $X\oplus \gf=\Lambda^2(\gf)$,
and it turns out that $X$ is irreducible for all $\gf$. The image
of the right-hand side of (\ref{Y3}) in $End(V)$ is zero if
$X\otimes V\not\supset V$  by the Wigner-Eckhart theorem. Knowing
$X$, Drinfeld was then able to find the $V$, listed above, for
which this is true.

\subsubsection{The $Y(\gf)$-rep $\gf\oplus{\mathbb C}$}

The more general case, in which the $Y(\gf)$-irrep is
$\gf$-reducible, is much harder. Indeed, the only explicitly known
such rep is again due to Drinfeld, with $V=\gf\oplus{\mathbb C}$
(that is, {\em adjoint}$\oplus${\em singlet}). (Note that there
can be no rep of $Y(\gf)$ based on the adjoint rep of $\gf$ alone,
since $X \subset \gf\otimes \gf$.) The action of $Y(\gf)$ is
\begin{eqnarray}
\nonumber \rho(I_a) x = [I_a,x] &  & \rho(J_a) x = <x,I_a> \\
\label{gplusC}\label{adj} \rho(I_a) \lambda = 0 &  & \rho(J_a)
\lambda = d \lambda I_a
\end{eqnarray}
on $(x,\lambda) \in \gf \oplus {\mathbb C}$, where $<,>$ is an
inner product on $\gf$, and $d \in {\mathbb C}$  is dependent on
$\gf$ and on the choice of inner product. In fact, it is rather
intriguing that, for the exceptional algebras, $d$ depends only on
dim$\,\gf$, and that there is a uniform formula for the whole of
the exceptional series $a_2,g_2,d_4,f_4,e_6,e_7,e_8$, including
its classical elements. This, alongside the appearance of $X$ in
\cite{deligne,cvitanovic} and the unified $\cR$-matrix structure
of \cite{westbury}, suggests that it might be interesting to
investigate the connection between Yangians and the `magic square'
construction of the exceptional $\gf$.

\subsubsection{The tensor product graph}\label{TPG}

There are no explicit constructions of $Y(\gf)$ actions on more
general $\gf$-reducible $Y(\gf)$-irreps. However, we can construct
tensor products of the reps above, and some conclusions may be
drawn. Let us denote $\gf$-reps with upper-case letters
$V,W,\ldots$, and $L_\mu\left(Y(\gf)\right)$-reps ({\em i.e.\
}acted on by the automorphism (\ref{auto}), and thus carrying a
parameter $\mu$) with lower-case letters $v(\mu),w(\mu),\ldots$.
The essential point which will emerge is this: suppose we first
decompose $v(\mu)$ into $\gf$-irreps; of course we then know the
action of the $I_a$ on each. But we also know that the $J_a$ act
in the adjoint rep, and this limits the $\gf$-irreps between which
it may have non-trivial action.

Suppose we wish to construct the tensor product $u(\mu/2)\otimes
u(-\mu/2)$ where $u=U$ is an irrep $\rho$ of the form
(\ref{irreps}). The action on $U$ is \begin{equation}\label{irreps2}
\tilde\rho^{u(\pm \mu/2)}(I_a) = \rho(I_a) \,, \qquad
\tilde\rho^{u(\pm \mu/2)}(J_a) = \pm {\mu\over 2}\rho(I_a) \,, \end{equation}
 so that the action on the tensor product,
constructed using the coproduct (\ref{Y1del},\,\ref{Y2del}), is
\begin{eqnarray} \tilde\rho^{u(\mu/2)\otimes u(-\mu/2)}(I_a) & = &\quad
\rho(I_a)\otimes 1
+ 1 \otimes \rho(I_a)\label{act1}\\[0.1in]
\tilde\rho^{u(\mu/2)\otimes u(-\mu/2)}(J_a) & = & -{\mu\over
2}\left(
 1 \otimes \rho(I_a) - \rho(I_a)\otimes 1\right) + {1\over 4}
\left[\rho\otimes\rho(C),1\otimes \rho(I_a) - \rho(I_a)\otimes
1\right],\qquad\quad\label{act2}\end{eqnarray} where we have used the fact
that \begin{equation} {1\over 2} f_{abc} I_c\otimes I_b = {1\over 4} \left[ C,
1\otimes I_a-I_a\otimes 1\right]\,,\qquad {\rm with} \quad C\equiv
I_d\otimes I_d\,.\end{equation} It is clear from (\ref{act2}) that the $J_a$
act in the adjoint rep of (and which we shall write as) $\gf$, and
that they reverse parity. Further, \begin{equation} C={1\over 2}
\left(\Delta(I_d)^2 - I_d I_d\otimes 1 - 1 \otimes I_d
I_d\right)\,,\end{equation} so that $C$ takes the numerical value ${1\over
2}\left(C_2(W)-2C_2(U)\right)$ on a component $W$ of $U\otimes U$,
where $C_2=I_dI_d$ is the quadratic Casimir operator of $\gf$. Thus
the action of $J_a$ from $W$ to $W'$ may be non-trivial only if
$W'\subset \gf\otimes W$, if $W'$ and $W$ have opposite parity, and
if $\mu\neq {1\over 4} \left(C_2(W')-C_2(W)\right)$ (for if this
last equality is satisfied the right-hand side of (\ref{act2})
vanishes). However, the action from $W'$ to $W$ will not then
vanish -- and the $Y(\gf)$-rep $u(\mu/2)\otimes u(-\mu/2)$,
irreducible for general $\mu$, will be reducible, but not fully
reducible.

Let us look at an example, with $U=\tableau{1}$ the vector rep of
$SO(N)$. Then \begin{equation}\tableau{1}\otimes \tableau{1} = \tableau{2}
\oplus \tableau{1 1} \oplus 1\,,\end{equation} where we have denoted by
$\tableau{2}$ the traceless rank-two symmetric tensor, by
$\tableau{1 1}$ the rank-two antisymmetric tensor (the adjoint),
and by $1$ the one-dimensional representation. The $Y(\gf)$ action
on $u(\mu/2)\otimes u(-\mu/2)$ is most easily described by forming
these components into a graph, \begin{equation} \tableau{2}
\;\stackrel{1}{\longrightarrow}\; \tableau{1 1}
\;\stackrel{N/2-1}{\longrightarrow}\; 1\,,\end{equation} with a directed edge
from $W$ to $W'$ labelled with ${1\over
4}\left(C_2(W)-C_2(W')\right)$. We see that this is general
irreducible, but, at $\mu=\pm 1$, for example, is reducible (and
note also that both these possibilities, $\tableau{2}$ and
$\tableau{1 1}\,\oplus 1$, are irreps described earlier, in
(\ref{irreps}) and (\ref{gplusC}) respectively). This `tensor
product graph' (TPG) method \cite{TPG} is generally applicable
provided $U\otimes U$ (or indeed $U\otimes V$, with $V\neq U$) has
no multiplicities.

Via (\ref{R}), it also enables us to determine $\cR(\mu)$, which,
since it commutes with $\tilde\rho(I_a)$, (\ref{act1}), must be of
the form \begin{equation} \cR(\mu) = \sum_{W \subset U \otimes U} \tau_W(\mu)
P_W \end{equation} (where $P_W$ is the projector onto $W\subset U\otimes U$).
Then its commutation with $\tilde\rho(J_a)$, (\ref{act2}), implies
that, for each pair $W,W'$ of connected nodes of the TPG,
\begin{equation}\label{taus} \tau_{W'} = {\delta-\mu\over \delta+\mu}\,
\tau_W\,,\qquad{\rm where} \quad\delta = {1\over 4}\left(
C_2(W)-C_2(W')\right)\,.\end{equation} For the admissible $U$ of (\ref{rep}),
this system of equations proves to be consistent and determines
$\cR(\mu)$ up to an overall scalar factor; while for all other $U$
the equations are inconsistent. In our $SO(N)$ example above, the
$\cR(\mu)$ is that found in \cite{zams}. We also see that the
$\cR(\mu)$ constructed this way are rational in $\mu$, justifying
to some extent the claim at the end of the last section.

The above technique, applied to solutions of the YBE (the $\cR$),
is known as the `fusion procedure' \cite{KSR}, and may be used
even if the TPG fails. For example: suppose we wish, in the above
example, to calculate the $\cR$ acting in $W\otimes W$ where
$W=\tableau{1 1}\oplus 1$. Now $W\otimes W$ has various
multiplicities, and the TPG fails, but we can use the fact that
$u(1/2)\otimes u(-1/2)$ is reducible --- that $\cR(-1)$ does not
contain $P_{\tableau{2}}$ --- to construct $\cR$ on $W\otimes
W\subset U^{\otimes 4}$; it is \begin{equation}\label{R4} \cR(-1)\otimes
\cR(-1)\,.\, 1\otimes \cR(\mu-1)\otimes 1\,.\, \cR(\mu)\otimes
\cR(\mu)\,.\, 1\otimes \cR(\mu+1)\otimes 1\,.\end{equation} The essential
point is that the YBE allows the $\cR(-1)\otimes\cR(-1)$ term,
similar to the projector onto $(\tableau{1 1}\oplus 1)^{\otimes
2}\subset \tableau{1}^{\otimes 4}$, to be moved through to the
right of this expression, which can therefore consistently be
restricted to act on $W\otimes W$. (Incidentally, the resulting
$\cR$ \cite{mack91} can also be calculated directly \cite{chari91}
from the $Y(\gf)$ action (\ref{gplusC}) on $\gf\oplus{\mathbb C}$.)

\subsection{Yangians and Dorey's rule}

As promised, we finish with an aspect of the representation theory
which is rather nicer for $Y(\gf)$ than for $\gf$.

We denote by $V_i$ the $i$th fundamental $\gf$-irrep, with highest
weight $\omega_i$, and by $v_i(\mu)$ the $i$th fundamental
$L_\mu(Y(\gf))$-irrep, which, we recall, has $V_i$ as its `top'
component\footnote{That is, `top' according to a partial ordering
of highest weights in terms of the fundamental weights.}.

\subsubsection{Tensor products of fundamental $\gf$-irreps}

For representations of $\gf$, the Clebsch-Gordan decomposition
tells us when $V_i\otimes V_j \supset \bar{V}_k$, or, better to
say, when \begin{equation} V_i \otimes V_j \otimes V_k \supset 1\label{CG}\end{equation}
(where we again denote the one-dimensional rep as $1$). The
solutions to this were characterized in terms of weights in a
longstanding conjecture \cite{PRV}, proved relatively recently
\cite{kumar}. When specialized to the fundamental reps this states
that (\ref{CG}) holds if there exists an element $\sigma$ in the
Weyl group (of transformations of the root lattice generated by
the reflections $w_i$ through planes perpendicular to the simple
roots) $W$ of $\gf$ such that the dominant weight\footnote{A
dominant weight is one whose coefficients, when it is expressed in
terms of the simple weights, are all positive. They are also,
therefore, the highest weights.} conjugate to $-\omega_j-\sigma
\omega_k$ is $\omega_i$.

\subsubsection{Dorey's rule}\label{Dorey's rule}

A rule due to Dorey \cite{dorey}, and shown by Braden
\cite{braden} to be a restricted case of the above, was originally
discovered in the context of purely elastic scattering theories
(PESTs, indeed) in 1+1D integrable models, where it described
particle fusings (and thereby $S$-matrix pole structure and
perturbative three-point couplings in affine Toda field theory, at
least when $\gf$ is simply-laced \cite{BCDS}). It states that a
fusing $ijk$ occurs iff there exist integers $r$ and $s$ such that
\begin{equation} \omega_i + c^r \omega_j + c^s \omega_k=0\,,\label{dorey}\end{equation}
where $c=\prod_{i=1}^rw_i$ is a Coxeter element of the Weyl group.
(The ordering of the simple roots does not matter.) The simplest
case in which (\ref{dorey}) is satisfied but (\ref{CG}) is not is
the self-coupling of the second fundamental rep (the rank-two
antisymmetric tensor) of $d_5$.

Coxeter elements have many nice properties which make
(\ref{dorey}) more attractive than (\ref{CG}). Their action
partitions the roots of $\gf$ into $r$ orbits, each of size $h$,
where $h$ is the Coxeter number of $\gf$ (which therefore satisfies
$r(h+1)=$dim$\,\gf$). Further, $c$ acts very simply on $r$ planes
through the root lattice, in each of which it is a rotation by
$s\pi/h$, where $s$ is an exponent of $\gf$. In PESTs this yields a
beautiful\footnote{To be convinced of this one only need look at
the illustrations in \cite{coxeter}.} geometric interpretation of
the conservation in three-point couplings of a set of local
charges, with spins equal to the exponents: instead of $r$
conservation equations, one has a single equation in ${\mathbb
R}^r$, projected onto $r$ planes \cite{dorey}.

\subsubsection{Tensor products of fundamental $Y(\gf)$-irreps}

Various results from integrable models suggested that Dorey's rule
might apply to the fusion of fundamental $Y(\gf)$ reps
\cite{nankai}, and it was proved in 1995 \cite{chari95} that there
exist $\mu,\nu,\lambda$ such that \begin{equation} v_i(\mu)\otimes v_j(\nu)
\otimes v_k(\lambda) \supset 1\,,\label{CGY}\end{equation} precisely when
(\ref{dorey}) holds --- the values of  $\mu,\nu,\lambda$ are
related to the angles of the rotations described in the last
paragraph. (This is strictly true only for simply-laced $\gf$; for
nonsimply-laced $\gf$ there is a correspondence, but it is much
more subtle.) The proof, however, was case-by-case, and it is an
open question whether there is a more natural way to access the
hidden geometry of Yangian representations.

\subsection{Some further reading}

An alternative way to present the Yangian story is to begin with
(\ref{RTT})\footnote{Albeit with `quantum' and `auxiliary' spaces
exchanging roles --- see sect.\ref{qq}.} and an explicit
$R$-matrix and proceed from there to construct
$Y({\mathfrak{gl}}_n)$ and, via an appropriate `quantum
determinant', $Y({\mathfrak{sl}}_n)$ (see \cite{molev} and
references therein). Drinfeld also provided another realization of
$Y(\gf)$ in \cite{drinf87}, analogous to a Cartan-Weyl basis, which
is often used to study $Y(\gf)$ representation theory, and a set of
polynomials in correspondence with (finite-dimensional) $Y(\gf)$
reps which can be used to classify them (allowing one, for
example, to deduce the existence of the fundamental $Y(\gf)$ irreps
discussed in this chapter). For connections between these two
approaches see \cite{crampe}; for that between $Y(\gf)$ and the
Bethe ansatz see \cite{KR,KS}; for that with Hecke algebras see
\cite{cher,drinf86}; for that with separation-of-variables
techniques see \cite{skly}. We noted earlier that $Y(\gf)$ may be
thought of as a deformation of a polynomial algebra, with
parameter $z$: the analogue of the full loop algebra, with powers
of $z^{-1}$ as well, is the `quantum double' of $Y(\gf)$
\cite{Ydouble1,Ydouble2}. Super-Yangians have their origins in
\cite{nazsuper}; some representations were studied in
\cite{RBZhang}. Finally, $Y(\gf)$ can also be obtained in the
$q\rightarrow 1$ limit of a $q$-deformed untwisted affine algebra
$U_q(\hat{g})$ in the `spin gradation' (equivalent for
simply-laced $\gf$ to the principal gradation), as remarked in
\cite{drinf1,CPbook} and detailed for $\gf=a_1$ in \cite{BL2} -- we
give further details in an appendix. Indeed, the structure of the
representation ring of $U_q(\hat{g})$, for $q$ not a root of
unity, is the same as that of $Y(\gf)$.

\section{Y-,T- and Q-systems}
\label{sec:y-t-q}

\section{Kirillov-Reshetikhin formula}
\label{sec:kirill-resh-form}

\section{Graded tensor product decomposition and cluster algebras }
\label{sec:grad-tens-prod}

Klimyk's formula: \url{http://mathoverflow.net/questions/85593/decompose-tensor-product-of-type-g-2-lie-algebras}

\section{AdS/CFT}
\label{sec:adscft}

\end{document}

### 2015-08-03 AffineLieAlgebras/TensorProducts/paper.tex
Update of special-splints paper, started paper on graded tensor products, some notes and older talks added too

\documentclass[12pt]{iopart}

%\usepackage{amsfonts}
\usepackage{pb-diagram}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\usepackage{iopams,setstack}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}

\newtheorem{Def}{Definition}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{statement}{Statement}
\newtheorem{Cnj}[Def]{Conjecture}
\newtheorem{Prop}[Def]{Property}
\newtheorem{example}{Example}[section]

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfg}{\hf_{\gf}}
\newcommand{\hfa}{\hf_{\af}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\sfr}{\mathfrak{s}}

\begin{document}

\ftc{Recurrent formulae for graded tensor product multiplicities and cluster algebras}

\author{V.D.~Lyakhovsky$^1$, A.A.~Nazarov$^{1,2}$, O.V.~Postnova$^{1}$, A..~Komisartchuk$^{1}$}
\address{ $^1$ Department of High-energy and elementary particle physics,  St Petersburg State University, 198904, Saint-Petersburg, Russia}
\ead{ $^{2}$ e-mail: antonnaz@gmail.com}

\begin{abstract}

We show the connection of formulae for tensor product multiplicities with cluster algebras. 
\noindent{\it Keywords\/}: Lie algebra, tensor product, multiplicity, cluster algebra, grading
\end{abstract}

\submitto{\jpa}

\section{Introduction}
\label{sec:introduction}

Feigin-Loktev construction of graded tensor product of finite-dimensional representations of simple
Lie algebras was recently interpreted from the point of view of cluster algebras theory. This
construction of graded tensor product is rooted in the fusion product of conformal field theory.
Cluster algebra interpretation produces the generalization of Kirillov-Reshetikhin formula for
tensor product decomposition coefficients to the graded case. Kirillov-Reshetikhin formula is the
fermionic formula and follows from Bethe ansatz equations. On the other hand tensor product
decomposition can be calculated recursively with something like so-called Klimyk rule which relies
on the Weyl character formula. So far there is no such simple method for graded tensor product. In
the present paper we provide a recurrent relations for the graded tensor product decomposition
coefficients and compare recurrent computations with the Kirillov-Reshetikhin formula. Note that
recurrent approach is not limited to any specific class of modules and is more general.

\begin{itemize}
\item Di Francesco-Kedem's paper
\item Feigin-Loktev tensor product.

  Let $\gf$ be a semisimple Lie algebra and b $L^{\mu}_{\gf}$ denote its finite-dimensional
  irreducible module with highest weight $\mu$. Feigin and Loktev considered more general cyclic
  modules but we limit ourselves with irreducible modules here. First step is to define a filtration
  on the tensor product of the irreducible modules $V=L^{\mu_{1}}\otimes\dots \otimes L^{\mu_{n}}$.
  Consider the current algebra $\gf[[t]]$ of $\gf$-valued complex polynomials with generators
  $X[n]=X\otimes t^{n}$ where $X\in \gf$. For $z\in\mathbb{C}$ we can define the action of $X[n]\in
  \gf[[t]]$ on $v\in L^{\mu}_{\gf}$ by $X[n]\cdot v = z^{n}X v$. Take complex vector
  $(z_{1},\dots,z_{n})$ then we have the action of $\gf[[t]]$ on $V=L^{\mu_{1}}\otimes\dots \otimes
  L^{\mu_{n}}$ by the rule
  \begin{equation}
    \label{eq:1}
    X[m](v_{1}\otimes \dots\otimes v_{n})=\sum_{i=1}^{n} z_{i}^{m}
    v_{1}\otimes\dots\otimes X v_{i}\otimes\dots\otimes v_{n}.    
  \end{equation}

 In the paper \cite{feigin1999generalized} it was shown that the module $V$ of $\gf[[t]]$ is
 generated by the action of lowering operators on the tensor product of highest weight vectors
 $v_{1}\otimes\dots \otimes v_{n}$. The algebra $\gf[[t]]$ is graded by the degree of polynomial
 and the algebra $U(\gf[[t]])$ is also graded. Then we have the induced filtration on $V$:
 \begin{equation}
   \label{eq:2}
   F^{i}V=U^{\leq i}(\gf[[t]])v_{1}\otimes\dots\otimes v_{n}.
 \end{equation}
 Note that $F^{0}V$ is the irreducible $\gf$-submodule corresponding to the highest weight in the
 tensor product decomposition
 \begin{equation}
   \label{eq:3}
   L^{\mu_{1}}\otimes\dots \otimes L^{\mu_{n}}=L^{\nu_{1}}\oplus\dots\oplus L^{\nu_{k}}
 \end{equation}

\item Fusion product of Virasoro modules, fusion in WZW models and Feigin-Loktev tensor product 
\item KR-formula
\item Weyl character formula and formulas for tensor product
\item Weyl character formula for graded tensor product
\item Computations: examples, performance
\item Cluster algebra perspective
\end{itemize}

\cite{di2013quantum} 
\bibliography{cluster}{} 
\bibliographystyle{iopart-num}

\end{document}

### 2015-08-03 AffineLieAlgebras/Thesis/talk2.tex
Update of special-splints paper, started paper on graded tensor products, some notes and older talks added too

\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}

\begin{document}
Здравствуйте! Сегодня я представляю свою диссертацию ``Правила ветвления аффинных алгебр Ли и приложения в моделях конформной теории поля''. Диссертация выполнена на нашей кафедре. 
Сначала я скажу о структуре диссертации. Диссертация состоит из пяти глав. Первая глава является обзорной и дает физическую мотивацию. В ней я рассказываю про конформную теорию поля в двух измерениях и о том, как в ней возникают аффинные алгебры Ли. 
Вторая глава посвящена проблемрекуррентный представления аффинной алгебры в сумму представлений подалгебры. В этой главе выведены рекуррентные соотношения на коэффициенты ветвления. 
В третьей главе показано, как процедура редукции связана с обобщенной резольвентой Бернштейна-Гельфанда-Гельфанда. 
В четвертой глав обсуждаются расщепления корневых систем простых алгебр Ли и следствия для теории представлений. Также рассматривается проблема ветвления представлений аффинной алгебры Ли на представления конечномерной подалгебры. 
Заключительная пятая глава посвящена более прикладным вещам - связи coset-моделей конформной теории поля со стохастическими процессами и компьютерной программе Affine.m 
В своем докладе я буду следовать структуре диссертации. Начну с напоминания про модели Весса-Зумино-Новикова-Виттена. Я про них уже как-то рассказывал на семинаре, но это было два года назад. 
Итак, эти модели отличаются от многих других моделей конформной теории поля тем, что их можно формулировать в терминах действия. Первый член в действии представляет собой действие нелинейной сигма модели. Поле g(x) живет на плоскости с бесконечностью и принимает значения в полупростой группе Ли G. В такой модели конформная инвариантность теряется при квантовании. Поэтому мы должны добавить топологический члена Весса-Зумино. Этот член записывается через продолжение поля на трехмерное многообразие. Мы можем думать, что наша двумерная сфера ограничивает шар, на котором задано поле g с тильдой. Такое продолжение не единственно. Так как третья группа гомологий представляет собой целые числа, то экспонента от действия определена однозначно и теория корректная. 
Перейдем к комплексным координатам z и z бар на плоскости. В теории есть сохраняющиеся токи J и J бар. Они принимают значения в конечномерной алгебре Ли g, соответствующей группе G.  То есть мы можем рассматривать голоморфный и антиголоморфный сектора независимо. Помимо конформной инвариантности у нас есть еще и калибровочная инвариантность с такими преобразованиями. Омега и омега с чертой независимы. 
Записываем тождества Уорда для таких преобразований. Если разложить токи по степеням z и генераторам алгебры Ли и подставить в тождество Уорда, мы обнаруживаем, что коэффициенты удовлетворяют коммутационным соотношениям аффинной алгебры Ли.
В конформной теории у нас должна быть алгебра Вирасоро, которая возникает при рассмотрении локальных конформных преобразований. Здесь генераторы этой алгебры можно реализовать в виде комбинаций генераторов аффинной алгебры Ли. Это так называемая конструкция Сугавары. 
Полная киральная алгебра представляет собой полупрямое произведение аффинной алгебры Ли и алгебры Вирасоро. 
Теперь мы можем ввести понятие примарного поля по отношению к полной киральной алгебре. Тогда примарные поля нумеруются старшими весами представлений аффинной алгебры Ли, действие на них понижающих операторов порождает семейства вторичных полей. 
Сингулярными называются векторы, которые зануляются повышающими операторами. Соответствующие им веса тоже называются сингулярными. 
То есть мы увидели, что аффинные алгебры Ли играют большую роль в моделях Весса-Зумино-Новикова-Виттена. 
Теперь к проблеме редукции. Самая прозрачная конструкция - это калибровочная ВЗНВ-модель. То есть мы добавляем взаимодействие с чисто калибровочным полем со значениями в некоторой подалгебре a алгебры g. В результате фиксации калибровки соответствующие степени свободы исчезают и остается coset-модель. 
В ней такие токи и тождества Уорда. Генераторы алгебры Вирасоро даются разностями выражений для алгебр g и a. Аналогично и для конформных размерностей и центральных зарядов. 
Заметим, что по отношению к генераторам подалгебры все векторы оказываются сингулярными. Функции ветвления пропорциональны характерам модулей алгебры Вирасоро. В coset-моделях примарные поля нумеруются парами весов - алгебры и подалгебры. Некоторые пары эквивалентны. То есть в coset-моделях нам нужно знать правила ветвления для модулей. 
Перейдем теперь ко второй главе диссертации, в которой выводятся новые рекуррентные соотношения на коэффициенты ветвления. Заметим, что для различных типов модулей алгебр Ли верны примерно аналогичные формулы Вейля для характеров. В числителе стоит сингулярный элемент, состоящий из экспонент сингулярных весов со знаками, а в знаменателе - произведение скобок, отвечающих положительным корням. В случае модулей Верма в числителе всего один член. Для неприводимых модулей верна такая формула. Заметим также, что характер неприводимого модуля может быть выражен в виде комбинации характеров модулей Верма. Это следствие существования резольвенты Бернштейна-Гельфанда-Гельфанда, которую мы обсуждаем в главе 3. 
Чтобы получить формулу для коэффициентов ветвления мы воспользуемся разложением сингулярного элемента. То есть мы хотим домножить формулу разложения характера алгебры в сумму характеров подалгебры на знаменатель. Но тут можно случайно домножить на ноль, если некоторые корни проектируются в ноль. Выделим их отдельно. Оказывается, что они порождают подалгебру, которую мы называем ортогональным партнером. 
Действуя знаменателем на сингулярный элемент алгебры g и проектируя мы получаем следующее разложение, включающее размерности модулей ортогонального партнера. 
Теперь мы можем домножить на дельта делить на дельта а и сравнить коэффициенты при одинаковых экспонентах. В результате получается рекуррентное соотношение на коэффициенты ветвления. 
Это соотношение новое, оно эффективно, так как для вычисления коэффициентов ветвления нам не нужно строить ни самого модуля, ни модулей подалгебры, в сумму которых он раскладывается. 
Продемонстрируем на примере, как все это работает. Вот сингулярный элемент фундаментального представления алгебры B2. Хотим раскладывать на модули подалгебры A1. Размерности вот таких модулей ортогональной алгебры А1 войдут в формулу. 
Теперь аффинное расширение. Вот веер вложения - отношение знаменателей Вейля алгебры и подалгебры, деленное на знаменатель Вейля ортогонального партнера. Вот проекция сингулярного элемента. Ставя веер в каждую точку рекуррентно вычисляем коэффициенты ветвления. При этом можно ограничиться главной камерой Вейля. 
Выводы к главе 2. Коэффициенты ветвления нужны для вычисления спектра на торе. Функции ветвления дают статсумму в coset-моделях. 
Мы вывели совершенно новую формулу для коэффициентов ветвления и продемонстрировали ее эффективность. Посмотрите на этот рисунок, здесь показано время работы программы в зависимости от необходимого числа коэффициентов ветвления. 
Теперь переходим к главе 3. 
В этой главе мы исследуем связь ветвления и обобщенной резольвенты Бернштейна-Гельфанда-Гельфанда. Пусть у нас то же, что и в предыдущей главе, но при разложении представления мы не делаем проекции. Тогда действие знаменателя ортогонального партнера на сингулярный элемент даст нам набор его неприводимых модулей. Когда мы на них подействуем веером, мы получим так параболические модули Верма. Эти модули входят в точную последовательность. На этой иллюстрации показана ее центральная часть. Эта глава относительно короткая, вот ее выводы. 
В четвертой главе мы исследуем понятие расщепления или сплинта корневой системы, введенное Дэвидом Рихтером в 2008 году. Мы будем рассматривать вложения корневых систем, при которых могут не сохраняться углы между корнями, а лишь аддитивные свойства. 
Мы будем говорить, что корневая система расщепляется, если есть два вложения двух других корневых систем. И она оказывается объединением образов этих вложений. 
Все расщепления для простых конечномерных алгебры Ли были классифицированы в работе Рихтера. 
Посмотрим, что происходит с ветвлением при наличии сплинта. 
Пусть есть алгебры g, ее регулярная подалгебра a и алгебра s. И пусть есть вложение корневой системы s в корневую систему g. То есть корневая система g представляет собой объединение корневой системы a и образа корневой системы s.
Тогда веер вложения определяется корневой системой s. Более того, сингулярный элемент представления алгебры g может быть разложен в комбинацию образов сингулярных элементов модулей алгебры s. Тогда коэффициенты ветвления совпадают с кратностями весов в представлении алгебры s. 
Продемонстрирую пару простых примеров. Рассмотрим алгебру B2 и подалгебру A1. Сингулярный элемент разложился в комбинацию образов сингулярных элементов алгебры A2. Коэффициенты ветвления совпадают с кратностями. Аналогично для алгебры G2. 
Теперь мы можем рассмотреть аффинное расширение расщепленной корневой системы. В этом случае веер вложения уже не получается - не хватает мнимых корней. То есть коэффициенты ветвления уже не совпадают с кратностями. Зато мы можем получить связь тета-функций аффинных алгебр a, s и g. 
Еще мы можем рассмотреть градуированное ветвление модуля аффинной алгебры Ли на модули конечномерной подалгебры. В этом случае мы можем ввести градуированные функции ветвления. Для этих функций в случае существования сплинта можно написать матричные соотношения. 
Введем порядок на множестве корней. 
Тогда мы можем записать кратности весов в матрицу M. Потом мы воспользуемся существованием сплинта и напишем матричное соотношение на функции ветвления. 
Выводы к четвертой главе. 
Мы проанализировали связь сплинта с веером вложения, показали, что расщепление определяет веер вложения. 
Определили, в каких случаях расщепление приводит к совпадению коэффициентов ветвления с кратностями весов. 
Получили новые соотношения на тета-функции и градуированные функции ветвления. 
Теперь я перехожу к пятой главе, которая посвящена более прикладным вещам. Первая тема здесь - это связь конформной теории поля и эволюции Шрамма-Левнера. Эволюция Шрамма-Левнера - это стохастический процесс. 
\end{document}

### 2015-08-03 AffineLieAlgebras/Simons/cardy.m

@@ -1,5 +1,7 @@
 t={{0,1,0,0},{1,0,1,0},{0,1,0,1},{0,0,1,0}};
 
+[Calculating...]
+
 RSOSModel[adjMatrix__List]:=
 	  Module[{es,ev,lm,W},
 		 es=Sort[Transpose[Eigensystem[adjMatrix]],#1[[1]]>#2[[1]]&][[1]];
@@ -11,6 +13,10 @@ RSOSModel[adjMatrix__List]:=
 		 W[#1,#2,#3,#4,lm/2]&]
 
 w=RSOSModel[t]
+
+                             lm$81
+Out[3]= W$81[#1, #2, #3, #4, -----] & 
+                               2
 
 w1=RSOSModel[{{0,1,0},{1,0,1},{0,1,0}}]
 
@@ -633,6 +639,277 @@ Out[101]= -------------------
 proj[x_,u_]:=1/2*(x+ Conjugate[x]*u^2/Abs[u]^2)
 
 Simplify[proj[1,Exp[-3*Pi*I/8]]-proj[(Sqrt[2]-1)*Exp[-Pi*I/4],Exp[-3*Pi*I/8]]]
+
+Simplify[proj[1,Exp[-3*Pi*I/4*s]]-proj[(Exp[2*J]*Exp[-mu]+1-Exp[-mu])*Exp[-Pi*I/2*s],Exp[-3*Pi*I/4*s]]]
+
+NSolve[N[Simplify[proj[1,Exp[-3*Pi*I/4*s]]-proj[(1/0.15*0.593+1-0.593)*Exp[-Pi*I/2*s],Exp[-3*Pi*I/4*s]]]]==0,{s}]
+
+Solve[proj[1,x^3]-proj[(1/0.15*0.593+1-0.593)*x^2,x^3]==0,x]
+
+N[Exp[-Pi*I*s/4]/.{s->1/10}]
+
+Out[30]= 0.996917 - 0.0784591 I
+
+Out[29]= 0.891007 - 0.45399 I
+
+
+N[proj[1,x^3]-proj[(1/0.15*0.593+1-0.593)*x^2,x^3]/.{x->Exp[-Pi*I*s/4]/.{s->7/16}}]
+
+Out[33]= -1.84632 + 3.0804 I
+
+Out[32]= -0.58329 + 3.68275 I
+
+Out[31]= -3.28128 + 0.787767 I
+    
[…]

### 2015-08-03 GeneralOverview/Lectures/CFT-APTU-2015.tex
Lecture notes "Group theory methods in QFT 2014" added, CFT2015 added

--- 2012-10-19 GeneralOverview/Lectures/CFT-APTU-2011.tex
@@
 
-\topmargin=-3.5cm
-\oddsidemargin=-1.5cm
-\evensidemargin=-1.5cm
-\textwidth=19cm
-\textheight=28cm
-
+%% \topmargin=-3.5cm
+%% \oddsidemargin=-1.5cm
+%% \evensidemargin=-1.5cm
+%% \textwidth=19cm
+%% \textheight=28cm
+%% 
 \title{Конформная теория поля и критические явления\\
@@
   \small{СПбГУ, физический факультет, кафедра физики высоких энергий и элементарных частиц;}\\
-  \small{математико-механический факультет, междисциплинарная лаборатория имени П.Л. Чебышева}\\
   \texttt{antonnaz@gmail.com}
 }
-\date{Осенний семестр 2011 года}
+\date{Весенний семестр 2015 года}
 
@@
 \begin{abstract}
-  Текст представляет собой конспект лекций по квантовой теории поля в двух измерениях.
-Лекции читались в осеннем семестре 2010 года и в осеннем семестре 2011 в Академическом университете для магистрантов 6 курса (группа теории конденсированного состояния).
+  Текст представляет собой конспект лекций по конформной теории поля в двух измерениях. Лекции
+  читались в осеннем семестре 2010, 2011 и 2012 года и в весеннем семестре 2015 в Академическом университете для
+  магистрантов 6 курса (группа теории конденсированного состояния).
 \end{abstract}
@@
   \item Примарные и вторичные поля
-  \item Минимальные модели
+  \item Классификация минимальных моделей
+  \item Представление кулоновского газа для минимальных моделей
+  \item Уравнения на корреляционные функции в минимальных моделях
+  \item Модели с дополнительной симметрией
+  \item Модели Весса-Зумино-Новикова-Виттена
+  \item Алгебры Каца-Муди
+  \item $Z_{N}$-парафермионы
+  \item Поправки от конечного размера системы и теория с границей
+
   \end{itemize}
@@
 \label{sec:literature}
-В \ref{sec:lecture-1} лекции  мы опираемся на вводные главы книги \cite{difrancesco1997cft}.
-Мы уделяем большое внимание использованию математического аппарата квантовой теории поля в моделях статистической физики.
-При этом мы пользуемся знакомством слушателей с функциональным интегралом.
-Последовательное изложение техники функционального интеграла в статистической физике можно найти в книге А.Н.
-Васильева \cite{vasiliev1976}.
-
-Лекции \ref{sec:lecture-5}, \ref{sec:lecture-6} посвящены  точному решению модели Изинга в двух измерениях.
-Подробно решение  модели Изинга в двух измерениях рассмотрено в книге  \cite{belavin2001lect}, на материале которой и основано изложение в данных лекциях.
-
-В следующих лекциях \ref{sec:lecture-3}, \ref{sec:lecture-4} мы обсуждаем применение ренормгруппы к описанию критического поведения, более подробно и достаточно педагогически этот вопрос рассматривается в книге \cite{ma1980} (\cite{ma2000modern}).
-Исчерпывающую информацию содержит моногорафия \cite{vasiliev1998} (английский вариант \cite{Vasilev:1027193}).
-Лекция \ref{sec:lecture-4} основана на вводной главе обзора \cite{Ravanini:2000st}.
-
-Изложение конформной теории поля в двух измерениях опирается на оригинальную статью \cite{belavin1984ics}, книгу \cite{difrancesco1997cft}, обзор \cite{zamolodchikov1989rus,zamolodchikov1989conformal}, недавно переизданный в виде книги.
-В последних лекциях \ref{sec:lecture-10}, \ref{sec:lecture-11}, \ref{sec:lecture-12} использовались также материалы из обзора \cite{Ginsparg:1988ui}, хотя логика изложения ближе к книге \cite{difrancesco1997cft}.
-Некоторые алгебраические сведения о представлениях алгебры Вирасоро  могут быть найдены в книге \cite{golod2001}.
-
-Дополнительные сведения о приложениях конформной теории поля и ее связи с теорией суперструн можно найти в подробных лекциях \cite{springerlink:10.1134/S1063778810050108} и обзорах \cite{Walton:1999xc}, \cite{gaberdiel2000icf}.
+В \ref{sec:lecture-1} лекции мы опираемся на вводные главы книги \cite{difrancesco1997cft}. Мы
+уделяем большое внимание использованию математического аппарата квантовой теории поля в моделях
+статистической физики. При этом мы пользуемся знакомством слушателей с функциональным интегралом.
+Последовательное изложение техники функционального интеграла в статистической физике можно найти в
+книге А.Н. Васильева \cite{vasiliev1976}.
+
+Лекции \ref{sec:lecture-5}, \ref{sec:lecture-6} посвящены точному решению модели Изинга в двух
+измерениях. Подробно решение модели Изинга в двух измерениях рассмотрено в книге
+\cite{belavin2001lect}, на материале которой и основано изложение в данных лекциях.
+
+В следующих лекциях \ref{sec:lecture-3}, \ref{sec:lecture-4} мы обсуждаем применение ренормгруппы к
+описанию критического поведения, более подробно и достаточно педагогически этот вопрос
+рассматривается в книге \cite{ma1980} (\cite{ma2000modern}). Исчерпывающую информацию содержит
+моногорафия \cite{vasiliev1998} (английский вариант \cite{Vasilev:1027193}). Лекция
+\ref{sec:lecture-4} основана на вводной главе обзора \cite{Ravanini:2000st}.
+
+Изложение конформной теории поля в двух измерениях опирается на оригинальную статью
+\cite{belavin1984ics}, книгу \cite{difrancesco1997cft}, обзор
+\cite{zamolodchikov1989rus,zamolodchikov1989conformal}, недавно переизданный в виде книги. В
+последних лекциях \ref{sec:lecture-10}, \ref{sec:lecture-11}, \ref{sec:lecture-12} использовались
+также материалы из обзора \cite{Ginsparg:1988ui}, хотя логика изложения ближе к книге
+\cite{difrancesco1997cft}. Некоторые алгебраические сведения о представлениях алгебры Вирасоро могут
+быть найдены в книге \cite{golod2001}.
+
+Дополнительные сведения о приложениях конформной теории поля и ее связи с теорией суперструн можно
+найти в подробных лекциях \cite{springerlink:10.1134/S1063778810050108} и обзорах
+\cite{Walton:1999xc}, \cite{gaberdiel2000icf}.
 
@@
 
-Во-первых, они существуют в природе. Например, критическое поведение на поверхности металлов напоминает поведение модели Изинга в двух измерениях \cite{campuzano1985110}.
-
-Во-вторых, в двух измерениях даже в простых моделях есть фазовые переходы.
-Это не так, например,  в одномерной модели Изинга.
-В простых двумерных моделях можно вычислить критические индексы и изучать поведение системы при фазовых переходах.
-
-Гипотеза универсальности утверждает, что все системы в критической точке разбиваются на небольшое число классов.
-Системы из одного класса ведут себя одинаково, имеют одинаковые критические индексы.
-Благодаря гипотезе универсальности существует лишь небольшое число типов критического поведения, поэтому значения индексов, вычисленные теоретически в простых моделях соответствуют гораздо более сложным реальным системам.
-
-В критической точке наблюдается масштабная инвариантность, что ведет к конформной инвариантности \cite{Polyakov:1970xd}.
-В двух измерениях конформная инвариантность дает очень много сведений о системе, так как алгебра конформных преобразований бесконечномерна.
-В результате поведение системы может быть описано строго математически методами двумерной конформной теории поля.
-
-Двумерная конформная теория поля имеет и другое применение, не связанное с описанием фазовых переходов --- это теория струн, которая считается перспективным кандидатом на роль квантовой теории гравитации.
-
-В данных лекциях мы займемся проблемой описания фазовых переходов в двумерных системах.
-Основной для нас будет двумерная модель Изинга.
-Мы обсудим обоснование гипотез подобия и универсальности в рамках ренормгруппового подхода, покажем наличие конформной инвариантности в критической точке и продемонстрируем на примере применение конформной теории поля для вычисления критических индексов и корреляторов.
+Во-первых, они существуют в природе. Например, критическое поведение на поверхности металлов
+напоминает поведение модели Изинга в двух измерениях \cite{campuzano1985110}.
+
+Во-вторых, в двух измерениях даже в простых моделях есть критическая точка. Это не так, например, в
+одномерной модели Изинга. В простых двумерных моделях можно вычислить критические индексы и изучать
+поведение системы при фазовых переходах.
+
+Гипотеза универсальности утверждает, что все системы в критической точке разбиваются на небольшое
+число классов. Системы из одного класса ведут себя одинаково, имеют одинаковые критические индексы.
+Благодаря гипотезе универсальности существует лишь небольшое число типов критического поведения,
+поэтому значения индексов, вычисленные теоретически в простых моделях соответствуют гораздо более
+сложным реальным системам.
+
+В критической точке наблюдается масштабная инвариантность, что ведет к конформной инвариантности
+\cite{Polyakov:1970xd}. В двух измерениях конформная инвариантность дает очень много сведений о
+системе, так как алгебра конформных преобразований бесконечномерна. В результате поведение системы
+может быть описано строго математически методами двумерной конформной теории поля.
+
+Двумерная конформная теория поля имеет и другое применение, не связанное с описанием фазовых
+переходов --- это теория струн, которая считается перспективным кандидатом на роль квантовой теории
+гравитации.
+
+В данных лекциях мы займемся проблемой описания фазовых переходов в двумерных системах. Основной для
+нас будет двумерная модель Изинга. Мы обсудим обоснование гипотез подобия и универсальности в рамках
+ренормгруппового подхода, покажем наличие конформной инвариантности в критической точке и
+продемонстрируем на примере применение конформной теории поля для вычисления критических индексов и
+корреляторов.
 
@@
 
-Мы рассматриваем статистические системы.
-Все макроскопические характеристики таких систем вычисляются из статсуммы, которая связана с микроскопическим описанием системы.
-Для больцмановского распределения вероятность системы находиться в состоянии с номером $i$ с энергией $E_i$
+Мы рассматриваем статистические системы. Все макроскопические характеристики таких систем
+вычисляются из статсуммы, которая связана с микроскопическим описанием системы. Для больцмановского
+распределения вероятность системы находиться в состоянии с номером $i$ с энергией $E_i$
 \begin{equation}
@@
 \end{equation}
-Мы используем систему единиц, в которой постоянная Больцмана равна единице $k_B=1$, введем $\beta=\frac{1}{T}$. Статсумма:
+Мы используем систему единиц, в которой постоянная Больцмана равна единице $k_B=1$, введем
+$\beta=\frac{1}{T}$. Статсумма:
 \begin{equation}
@@
 \end{equation}
-Таким образом статсумма является производящей функцией всех термодинамических величин. Вычисление статсуммы в реальных системах --- это сложная задача.
-Макроскопическое описание имеет смысл только в термодинамическом пределе, когда число частиц стремится к бесконечности $N\to \infty$.
-
-Двумерная модель Изинга --- это простейшая модель магнетика.
-Она формулируется на решетке, которую мы будем, для простоты, считать прямоугольной.
-Вершины решетки нумеруются латинскими индексами $i,j$.
-В вершинах решетки находятся частицы со спинами $\sigma_j$ равными $\pm 1$ (вверх или вниз).
-Взаимодействуют только ближайшие соседи, константу взаимодействия обозначим через $J$.
-Для энергии системы имеем
+Таким образом статсумма является производящей функцией всех термодинамических величин. Вычисление
+статсуммы в реальных системах --- это сложная задача. Макроскопическое описание имеет смысл только в
+термодинамическом пределе, когда число частиц стремится к бесконечности $N\to \infty$.
+
+Двумерная модель Изинга --- это простейшая модель магнетика. Она формулируется на решетке, которую
+мы будем, для простоты, считать прямоугольной. Вершины решетки нумеруются латинскими индексами
+$i,j$. В вершинах решетки находятся частицы со спинами $\sigma_j$ равными $\pm 1$ (вверх или вниз).
+Взаимодействуют только ближайшие соседи, константу взаимодействия обозначим через $J$. Для энергии
+системы имеем
 \begin{equation}
@@
 \end{equation}
-Суммирование в первом члене ведется только по парам ближайших соседей, второй член --- это взаимодействие со внешним полем $h$.
-Пусть система состоит из $N$ вершин. Она имеет $2^N$ различных конфигураций. Случай $J>0$ соответствует ферромагнетику, $J<0$ --- антиферромагнетику. 
-При $h=0$ низшее энергетическое состояние двукратно вырождено --- это состояние, в котором все спины направлены вверх или вниз.
-
-Существует несколько точных решений двумерной модели Изинга в отсутствие внешнего поля.
-Решений со внешним полем и в большем числе измерений пока не известно.
-Недавнее достижение Станислава Смирнова, за которое он получил в 2010 году премию Филдса, непосредственно связано с темой наших лекций.
-В своих работах Станислав Смирнов впервые строго доказал наличие конформной инвариантности в критической точке двумерной модели Изинга \cite{smirnov2007conformal,smirnov2006towards,smirnov2001critical}.
-
-Фазовые переходы в модели Изинга наблюдаются только в термодинамическом пределе, при конечных размерах системы никаких переходов нет.
+Суммирование в первом члене ведется только по парам ближайших соседей, второй член --- это
+взаимодействие со внешним полем $h$. Пусть система состоит из $N$ вершин. Она имеет $2^N$ различных
+конфигураций. Случай $J>0$ соответствует ферромагнетику, $J<0$ --- антиферромагнетику. При $h=0$
+низшее энергетическое состояние двукратно вырождено --- это состояние, в котором все спины
+направлены вверх или вниз.
+
+Существует несколько точных решений двумерной модели Изинга в отсутствие внешнего поля. Решений со
+внешним полем и в большем числе измерений пока не известно. Недавнее достижение Станислава Смирнова,
+за которое он получил в 2010 году премию Филдса, непосредственно связано с темой наших лекций. В
+своих работах Станислав Смирнов впервые строго доказал наличие конформной инвариантности в
+критической точке двумерной модели Изинга
+\cite{smirnov2007conformal,smirnov2006towards,smirnov2001critical}.
+
+Фазовые переходы в модели Изинга наблюдаются только в термодинамическом пределе, при конечных
+размерах системы никаких переходов нет.
 
@@
 \end{equation}
-Здесь мы ввели обозначение $\sigma_{\mathrm{tot}}=\sum_i \sigma_i$. Видно, что магнитная восприимчивость пропорциональна дисперсии полного спина. Введем парную корреляционную функцию
+Здесь мы ввели обозначение $\sigma_{\mathrm{tot}}=\sum_i \sigma_i$. Видно, что магнитная
+восприимчивость пропорциональна дисперсии полного спина. Введем парную корреляционную функцию
 \begin{equation}
@@
 \end{equation}
-Из-за вращательной и трансляционной инвариантности $\Gamma$ зависит только от расстояния между вершинами $\left|i-j\right|$. Связная корреляционная функция
+Из-за вращательной и трансляционной инвариантности $\Gamma$ зависит только от расстояния между
+вершинами $\left|i-j\right|$. Связная корреляционная функция
 \begin{equation}
@@
 \end{equation}
-То есть магнитная восприимчивость --- это мера статистической когерентности системы, она растет с ростом зависимости спинов между собой.
+То есть магнитная восприимчивость --- это мера статистической когерентности системы, она растет с
+ростом зависимости спинов между собой.
 
@@
 
-Распределение Больцмана инвариантно относительно сдвига энергии на константу, поэтому можно переписать гамильтониан в более удобном для обобщения виде:
+Распределение Больцмана инвариантно относительно сдвига энергии на константу, поэтому можно
+переписать гамильтониан в более удобном для обобщения виде:
 \begin{equation}
@@
 
-Другой класс дискретных моделей отличается более существенно.
-Если в модели Изинга переменные (спины) живут в вершинах, а энергия --- на ребрах, то в вершинных моделях все наоборот.
-В качестве переменных берутся направленные ребра (стрелки), а энергия в вершине зависит от числа входящих и выходящих из нее стрелок.
-Пусть ребра, входящие в вершину имеют значения $0,1$ в зависимости от направления стрелки.
-Тогда энергия вершины обозначается через $R_{\alpha\mu}^{\beta\nu},\; \alpha,\beta,\mu,\nu=0,1$.
-Бывает 16 таких членов.
-В зависимости от того, сколько из них не равны нулю, выделяют 6-вершинную и 8-вершинную модели.
-8-вершинная модель --- ненулевой вклад только когда входит четное число стрелок (0 входит, 4 выходит; 4 входит, 0 выходит; 6 способов выбрать две входящие стрелки -- итого 8 отличных от нуля членов $R_{\alpha\mu}^{\beta\nu}$).
-
-Другой класс статистических моделей --- это модели с непрерывными степенями свободы. Например, заменим спины $\sigma_i$ в \eqref{eq:1} на единичные вектора в $m$-мерном пространстве $\vec n_i$.
+Другой класс дискретных моделей отличается более существенно. Если в модели Изинга переменные
+(спины) живут в вершинах, а энергия --- на ребрах, то в вершинных моделях все наоборот. В качестве
+переменных берутся направленные ребра (стрелки), а энергия в вершине зависит от числа входящих и
+выходящих из нее стрелок. Пусть ребра, входящие в вершину имеют значения $0,1$ в зависимости от
+направления стрелки. Тогда энергия вершины обозначается через $R_{\alpha\mu}^{\beta\nu},\;
+\alpha,\beta,\mu,\nu=0,1$. Бывает 16 таких членов. В зависимости от того, сколько из них не равны
+нулю, выделяют 6-вершинную и 8-вершинную модели. 8-вершинная модель --- ненулевой вклад только когда
+входит четное число стрелок (0 входит, 4 выходит; 4 входит, 0 выходит; 6 способов выбрать две
+входящие стрелки -- итого 8 отличных от нуля членов $R_{\alpha\mu}^{\beta\nu}$).
+
+Еще один класс статистических моделей --- это модели с непрерывными степенями свободы. Например,
+заменим спины $\sigma_i$ в \eqref{eq:1} на единичные вектора в $m$-мерном пространстве $\vec n_i$.
 \begin{equation}
@@
 
-В критической точке параметр порядка системы стремится к бесконечности, кроме того, фазовый переход в дискретных моделях наблюдается только в пределе числа вершин стремящегося к бесконечности ($N\to \infty$).
-Такой предел называется термодинамическим.
-Поэтому при описании фазового перехода имеет смысл перейти от модели с дискретным пространством  к непрерывному $d$-мерному пространству.
-В дальнейшем $d$ будет равно двум, но сейчас мы пишем в самом общем виде, чтобы указать аналогию с теорией поля.
-При переходе к непрерывному пространству гамильтониан \eqref{eq:13} принимает вид
+В критической точке наблюдается корреляция спинов на больших расстояниях, кроме того, фазовый переход
+в дискретных моделях наблюдается только в пределе числа вершин стремящегося к бесконечности ($N\to
+\infty$). Такой предел называется термодинамическим. Поэтому при описании фазового перехода имеет
+смысл перейти от модели с дискретным пространством к непрерывному $d$-мерному пространству. В
+дальнейшем $d$ будет равно двум, но сейчас мы пишем в самом общем виде, чтобы указать аналогию с
+теорией поля. При переходе к непрерывному пространству гамильтониан \eqref{eq:13} принимает вид
 \begin{equation}
@@
 \end{equation}
-Здесь подразумевается суммирование по повторяющимся индексам.
-(Легко понять обратный переход, если заменить производные разностями по ближайшим соседям, а потом отбросить в энергии постоянный член $J\sum_i \left|\vec n_i\right|^2=JN$).
-Условие $\vec n^2(x)=1$ сложно использовать, поэтому мы заменим его на другое аналогичное.
-Первый вариант такой замены --- это наложить требование $\frac{1}{V}\int d^dx\; \vec n^2=1$.
-В результате получается так называемая сферическая модель.
-Другая возможность --- добавить в гамильтониан \eqref{eq:15} потенциал $V(\left|\vec n\right|)$ с минимумом в $\left|\vec n\right|=1$ и устремить константу связи к бесконечности.
-Простейший вид такого потенциала --- $V(\left|\vec n\right|)=a\vec n^2+b\left(\vec n^2\right)^2$.
-Добавим его в гамильтониан и изменим нормировку $\vec n$ так, чтобы константа $J$ ушла.
-Получим
+Здесь подразумевается суммирование по повторяющимся индексам. (Легко понять обратный переход, если
+заменить производные разностями по ближайшим соседям, а потом отбросить в энергии постоянный член
+$J\sum_i \left|\vec n_i\right|^2=JN$).
+
+Условие $\vec n^2(x)=1$ сложно использовать, поэтому мы заменим его на другое аналогичное. Первый
+вариант такой замены --- это наложить требование $\frac{1}{V}\int d^dx\; \vec n^2=1$. В результате
+получается так называемая сферическая модель. Другая возможность --- добавить в гамильтониан
+\eqref{eq:15} потенциал $V(\left|\vec n\right|)$ с минимумом в $\left|\vec n\right|=1$ и устремить
+константу связи к бесконечности. Простейший вид такого потенциала --- $V(\left|\vec n\right|)=a\vec
+n^2+b\left(\vec n^2\right)^2$. Добавим его в гамильтониан и изменим нормировку $\vec n$ так, чтобы
+константа $J$ ушла. Получим
 \begin{equation}
@@
 \end{equation}
-Если у $\vec n$ всего одна компонента $\varphi$, то мы получаем скалярную модели $\varphi^4$. Если $u=0$, то такая модель называется Гауссовой и допускает точное решение.
+Если у $\vec n$ всего одна компонента $\varphi$, то мы получаем скалярную модели $\varphi^4$. Если
+$u=0$, то такая модель называется Гауссовой и допускает точное решение. 
 \begin{equation}
@@
 \end{equation}
-Статсумма --- это сумма $e^{-\beta E[\varphi]}$ по всем конфигурациям поля $\varphi$, то есть она записывается при помощи функционального интеграла:
+Статсумма --- это сумма $e^{-\beta E[\varphi]}$ по всем конфигурациям поля $\varphi$, то есть она
+записывается при помощи функционального интеграла: 
 \begin{equation}
@@
 \end{equation}
-В гауссовой модели функциональный интеграл имеет гауссовский вид, поэтому он хорошо определен и легко вычисляется.
-Значит можно вычислить статсумму и все корреляционные функции.
-Величины в модели $\varphi^4$ можно получать по теории возмущений вокруг решения гауссовой модели.
-Это и есть вычисление функционального интеграла как суммы по фейнмановским диаграммам.
+В гауссовой модели функциональный интеграл имеет гауссовский вид, поэтому он хорошо определен и
+легко вычисляется. Значит можно вычислить статсумму и все корреляционные функции. Величины в модели
+$\varphi^4$ можно получать по теории возмущений вокруг решения гауссовой модели. Это и есть
+вычисление функционального интеграла как суммы по фейнмановским диаграммам.
 
@@
 \end{equation}
-$e^{-\beta H}$ похоже на оператор эволюции $e^{-i H t}$, то есть его тоже можно записать через функциональный интеграл.
-Покажем, как это делается на примере системы с одной степенью свободы.
-В этом случае ядро оператора плотности имеет вид
+$e^{-\beta H}$ похоже на оператор эволюции $e^{-i H t}$, то есть его тоже можно записать через
+функциональный интеграл. Покажем, как это делается на примере системы с одной степенью свободы. В
+этом случае ядро оператора плотности имеет вид 
 \begin{equation}
@@
 \end{equation}
-Вспомним, что в квантовой механике оператор эволюции имеет вид $U(t)=e^{-i H t}$, а его ядро --- амплитуда перехода из состояния $\left|x_i\right>$ в $\left<x_f\right|$ дается интегралом по траекториям
+Вспомним, что в квантовой механике оператор эволюции имеет вид $U(t)=e^{-i H t}$, а его ядро ---
+амплитуда перехода из состояния $\left|x_i\right>$ в $\left<x_f\right|$ дается интегралом по
+траекториям 
 \begin{equation}
@@
 \end{equation}
-Заменой $t\to i\tau, \; \tau\in [0,\beta]$ (виковским поворотом) переходим к евклидову действию $S[x(t)]\to iS_E[x(\tau)]$. Для ядра оператора плотности получаем
+Заменой $t\to i\tau, \; \tau\in [0,\beta]$ (виковским поворотом) переходим к евклидову действию
+$S[x(t)]\to iS_E[x(\tau)]$. Для ядра оператора плотности получаем 
 \begin{equation}
@@
 \end{equation}
-Здесь мы предположили, что $A$ зависит только от $x$, то есть $\left<y\right| A\left|x\right>=A(x)\delta(x-y)$.
-Мы видим, что значение $A$ дается функциональным интегралом, но $A$ вычисляется в точке $\tau=0$.
-
-Обобщение на систему с континуумом степеней свободы и многочастичные функции естественно.
-Статсумма квантовой системы получается из обычного интеграла по траекториям путем викова поворота и ограничения евклидова времени на конечный промежуток $[0,\beta]$.
-При нулевой температуре ($\beta\to \infty$) мы получаем обычный производящий функционал в евклидовом времени, то есть теорию поля.
-При конечных температурах статсумма квантовой $d$-мерной системы соответствует статсумме $d+1$-мерной классической системы на полосе шириной $\beta$.
+Здесь мы предположили, что $A$ зависит только от $x$, то есть $\left<y\right|
+A\left|x\right>=A(x)\delta(x-y)$. Мы видим, что значение $A$ дается функциональным интегралом, но
+$A$ вычисляется в точке $\tau=0$.
+
+Обобщение на систему с континуумом степеней свободы и многочастичные функции естественно. Статсумма
+квантовой системы получается из обычного интеграла по траекториям путем викова поворота и
+ограничения евклидова времени на конечный промежуток $[0,\beta]$. При нулевой температуре ($\beta\to
+\infty$) мы получаем обычный производящий функционал в евклидовом времени, то есть теорию поля. При
+конечных температурах статсумма квантовой $d$-мерной системы соответствует статсумме $d+1$-мерной
+классической системы на полосе шириной $\beta$.
 
@@
 
-Классическое уравнение движения получается из принципа экстремальности действия (равенства нулю вариации действия).
+Классическое уравнение движения получается из принципа экстремальности действия (равенства нулю
+вариации действия).
 
@@
 \end{equation}
-поля тоже преобразуются, то есть у них не только меняется аргумент, но и само поле. Тип поля (скалярное, векторное, спинорное) -- это вид такого преобразования.
+поля тоже преобразуются, то есть у них не только меняется аргумент, но и само поле. Тип поля
+(скалярное, векторное, спинорное) -- это вид такого преобразования. 
 \begin{equation}
@@
 Теперь рассмотрим инфинитезимальные преобразования.
-Если действие инвариантно относительно каких-либо преобразований, то говорят, что в теории есть симметрия.
-В этом случае действие должно быть стационарно по отношению к инфинитезимальным преобразованиям.
+Если действие инвариантно относительно каких-либо преобразований, то говорят, что в теории есть
+симметрия. В этом случае действие должно быть стационарно по отношению к инфинитезимальным
+преобразованиям.
 
@@
 Примеры генераторов:
-Если мы предположим, что поле $\varphi$ -- такое поле, которое не меняется при конформных преобразованиях, то есть $F(\varphi)=\varphi$, то мы получим следующий вид для генераторов:
+Если мы предположим, что поле $\varphi$ -- такое поле, которое не меняется при конформных
+преобразованиях, то есть $F(\varphi)=\varphi$, то мы получим следующий вид для генераторов: 
 \begin{eqnarray}
@@
 \end{eqnarray}
-Если же при поворотах поле преобразуется $\varphi'(x')=\Lambda\varphi(x)$, то при инфинитезимальных преобразованиях $\varphi'(x')=\varphi(x)-\frac{i}{2}\omega_{\mu\nu}S^{\mu\nu}$ и генератор принимает вид
+Если же при поворотах поле преобразуется $\varphi'(x')=\Lambda\varphi(x)$, то при инфинитезимальных
+преобразованиях $\varphi'(x')=\varphi(x)-\frac{i}{2}\omega_{\mu\nu}S^{\mu\nu}$ и генератор принимает
+вид 
 \begin{equation*}
@@
 \end{equation*}
-$j^{\mu}_{a}$ называется нетеровским током, соответствующим данной симметрии. 
+$j^{\mu}_{a}$ называется нётеровским током, соответствующим данной симметрии. 
 Если $\delta_{\omega} S=0$, то
@@
 
- Рассмотрим инфинитезимальное масштабное преобразование $\lambda=1+\omega$.
-При этом вариация $x_{\nu}$ будет $\delta_{\omega}x_{\nu}=\omega x_{\nu}$.
-При инфинитезимальных преобразованиях $x\to x+dl x$ вариация плотности лагранжиана дается Нётеровским током:
+ Рассмотрим инфинитезимальное масштабное преобразование $\lambda=1+\omega$. При этом вариация
+ $x_{\nu}$ будет $\delta_{\omega}x_{\nu}=\omega x_{\nu}$.  При инфинитезимальных преобразованиях
+ $x\to x+dl x$ вариация плотности лагранжиана дается Нётеровским током: 
 \begin{equation}
@@
 \end{equation}
-Здесь $T^{\mu\nu}$ - тензор энергии-импульса.  Через $\Theta$ мы обозначим след тензора энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия
+Здесь $T^{\mu\nu}$ - тензор энергии-импульса.  Через $\Theta$ мы обозначим след тензора
+энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия 
 \begin{equation}
@@
 \end{equation}
-Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$. В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
+Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$. В
+масштабно-инвариантной теории тензор энергии-импульса бесследовый.
 
@@
 
-Фазовые переходы характеризуются скачком в макроскопических характеристиках системы.
-При переходах первого рода скачком меняется внутренняя энергия (например, при переходе жидкость-газ).
-При переходах второго рода наблюдается скачок производных макроскопических термодинамических величин (теплоемкость, магнитная восприимчивость).
-Эта классификация несколько условна (см.
-\cite{ma2000modern,ma1980}), бывают и другие виды фазовых переходов, например, переход Костерлица-Таулесса \cite{0022-3719-6-7-010}.
-
-Строго говоря, фазовые переходы бывают только в термодинамическом пределе.
-Это легко понять для систем типа модели Изинга в нулевом поле, где энергия любой конфигурации кратна энергетическому масштабу $\epsilon=-J$, а статсумма представляет собой полином от $z=e^{-\beta\epsilon}$.
-В модели Изинга наибольшая энергия $E=2N\epsilon$, $Z$- полином степени $2N$ от $z$ с единичными коэффициентами.
-Корни этого полинома лежат вне положительной вещественной оси и комплексно сопряжены.
-Сингулярности свободной энергии или ее производных могут быть только в корнях, которые находятся вне физической области при $N<\infty$.
-При $N\to \infty$ число корней становится бесконечным, они лежат на дугах, которые могут касаться положительной вещественной оси.
-В этих точках поведение термодинамических величин и становится сингулярным.
+Фазовые переходы характеризуются скачком в макроскопических характеристиках системы. При переходах
+первого рода скачком меняется внутренняя энергия (например, при переходе жидкость-газ). При
+переходах второго рода наблюдается скачок производных макроскопических термодинамических величин
+(теплоемкость, магнитная восприимчивость).  Эта классификация несколько условна (см.
+\cite{ma2000modern,ma1980}), бывают и другие виды фазовых переходов, например, переход
+Костерлица-Таулесса \cite{0022-3719-6-7-010}.
+
+Строго говоря, фазовые переходы бывают только в термодинамическом пределе. Это легко понять для
+систем типа модели Изинга в нулевом поле, где энергия любой конфигурации кратна энергетическому
+масштабу $\epsilon=-J$, а статсумма представляет собой полином от $z=e^{-\beta\epsilon}$. В модели
+Изинга наибольшая энергия $E=2N\epsilon$, $Z$- полином степени $2N$ от $z$ с единичными
+коэффициентами. Корни этого полинома лежат вне положительной вещественной оси и комплексно
+сопряжены. Сингулярности свободной энергии или ее производных могут быть только в корнях, которые
+находятся вне физической области при $N<\infty$. При $N\to \infty$ число корней становится
+бесконечным, они лежат на дугах, которые могут касаться положительной вещественной оси. В этих
+точках поведение термодинамических величин и становится сингулярным.
 
@@
 \end{equation}
-При $T>T_c$ спонтанная намагниченность \eqref{eq:7} исчезает.
-При $T<T_c$ она не равна нулю и стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_c$.
-Это упорядоченная ферромагнитная фаза.
-Около критической точки спонтанная намагниченность ведет себя как
+При $T>T_c$ спонтанная намагниченность \eqref{eq:7} исчезает. При $T<T_c$ она не равна нулю и
+стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_c$. Это упорядоченная ферромагнитная фаза. Около
+критической точки спонтанная намагниченность ведет себя как 
 \begin{equation}
@@
 \end{equation}
-Вдали от критической точки корреляторы $\Gamma_c(i)$ убывают экспоненциально с расстоянием. Характерная длина убывания $\xi$ называется корреляционной длиной
+Вдали от критической точки корреляторы $\Gamma_c(i)$ убывают экспоненциально с расстоянием.
+Характерная длина убывания $\xi$ называется корреляционной длиной 
 \begin{equation}
@@
 
-Около критической точки система состоит из доменов разной намагниченности.
-Существуют домены всевозможных размеров от шага решетки до корреляционной длины $\xi$.
-Свободная энергия $F$ получает вклады от доменных стенок.
-Сингулярное поведение возникает из-за вкладов доменов большого размера, оно определяется флуктуациями и не может быть правильно учтено в теории среднего поля.
-Вблизи критической температуры $\xi$ больше физических размеров системы.
-Свободная энергия перестает зависеть от $\xi$.
+Около критической точки система состоит из доменов разной намагниченности. Существуют домены
+всевозможных размеров от шага решетки до корреляционной длины $\xi$. Свободная энергия $F$ получает
+вклады от доменных стенок. Сингулярное поведение возникает из-за вкладов доменов большого размера,
+оно определяется флуктуациями и не может быть правильно учтено в теории среднего поля. Вблизи
+критической температуры $\xi$ больше физических размеров системы. Свободная энергия перестает
+зависеть от $\xi$.
 
@@
 \end{equation}
-Поведение термодинамических величин определяется критическими индексами. Перечислим их вместе со значениями в двумерной модели Изинга. Эти значения получены из точных решений модели.
+Поведение термодинамических величин определяется критическими индексами. Перечислим их вместе со
+значениями в двумерной модели Изинга. Эти значения получены из точных решений модели. 
 \begin{table}[h!tb]
@@
 
-Заметим, что систему можно описывать классической статистической механикой (обычной квантовой теорией поля с неограниченным временем) когда корреляционная длина больше характерной длины волны де Бройля.
-Если характерная скорость $v$ (скорость света, скорость Ферми или скорость какого-либо возбуждения), то $\lambda_T=\frac{v\hbar}{k_B T}\sim \beta$.
-То есть классическая статистика применима при больших температурах или вблизи критической точки, если $T_c\neq 0$.
+Заметим, что систему можно описывать классической статистической механикой (обычной квантовой
+теорией поля с неограниченным временем) когда корреляционная длина больше характерной длины волны де
+Бройля. Если характерная скорость $v$ (скорость света, скорость Ферми или скорость какого-либо
+возбуждения), то $\lambda_T=\frac{v\hbar}{k_B T}\sim \beta$. То есть классическая статистика
+применима при больших температурах или вблизи критической точки. %, если $T_c\neq 0$.
 
@@
 
-Займемся решением модели Изинга в двух измерениях \eqref{eq:1}.
-Точного решения для модели с внешним полем до сих пор не найдено.
-Решение же для $h=0$ впервые было получено Онзагером в 1944 году.
-В этой и следующей лекциях излагается решение Вдовиченко, как наиболее короткое и простое.
-Изложение взято из книги \cite{belavin2001lect}.
+Займемся решением модели Изинга в двух измерениях \eqref{eq:1}. Точного решения для модели с внешним
+полем до сих пор не найдено. Решение же для $h=0$ впервые было получено Онзагером в 1944 году. В
+этой и следующей лекциях излагается решение Вдовиченко, как наиболее короткое и простое. Изложение
+взято из книги \cite{belavin2001lect}. 
 Энергия системы в отсутствие внешнего поля дается выражением
@@
 \end{equation}
-Будем считать, что в наша решетка $\mathcal{L}$ состоит из $N=mn$ узлов.
-Обозначим через $M$ число пар $\left<i,j\right>$.
-$M=2N-n-m$.
-Для простоты будем накладывать тороидальные граничные условия.
-Тогда $M=2N$.
-Введем {\it дуальную решетку $\mathcal{L}^*$}, вершинами которой будут центры граней исходной решетки.
+Будем считать, что в наша решетка $\mathcal{L}$ состоит из $N=mn$ узлов. Обозначим через $M$ число
+пар $\left<i,j\right>$. $M=2N-n-m$. Для простоты будем накладывать тороидальные граничные условия.
+Тогда $M=2N$. Введем {\it дуальную решетку $\mathcal{L}^*$}, вершинами которой будут центры граней
+исходной решетки.  
 Нам удобно будет использовать действие в следующем виде:
@@
 \item Основное состояние, все спины направлены в одну сторону, $X[\sigma]=1$
-\item Все спины в одну сторону, один в противоположную.
-Такому состоянию можно сопоставить контур на дуальной решетке вокруг этого спина.
-Тогда каждая сторона контура даст вклад $e^{-2K}$ в $X[\sigma]$.
+\item Все спины в одну сторону, один в противоположную. Такому состоянию можно сопоставить контур на
+  дуальной решетке вокруг этого спина. Тогда каждая сторона контура даст вклад $e^{-2K}$ в
+  $X[\sigma]$. 
   \begin{equation}
@@
   \end{equation}
-\item Два спина направлены в противоположную сторону, здесь есть два варианта контура на дуально решетке - если спины рядом, то его длина равна шести, если не рядом - то восьми.
-То есть вклады $\left(e^{-2K}\right)^6$ и $\left(e^{-2K}\right)^8$.
+\item Два спина направлены в противоположную сторону, здесь есть два варианта контура на дуально
+  решетке - если спины рядом, то его длина равна шести, если не рядом - то восьми. То есть вклады
+  $\left(e^{-2K}\right)^6$ и $\left(e^{-2K}\right)^8$. 
 \item И так далее.
 \end{itemize}
-В итоге мы можем записать все вклады $X[\sigma]$ в виде суммы по всевозможным замкнутым контурам на дуальной решетке. Если ввести обозначение
+В итоге мы можем записать все вклады $X[\sigma]$ в виде суммы по всевозможным замкнутым контурам на
+дуальной решетке. Если ввести обозначение 
 \begin{equation}
@@
 \end{equation}
-Здесь $l[c]$ --- длина контура $c$ на дуальной решетке, соответствующего состоянию $\sigma$. Тогда для $Z$ получаем
+Здесь $l[c]$ --- длина контура $c$ на дуальной решетке, соответствующего состоянию $\sigma$. Тогда
+для $Z$ получаем 
 \begin{equation}
@@
 \end{equation}
-Такое выражение называется низкотемпературным разложением, так как оно хорошо сходится при малых температурах ($K>>1$).
-
-Чтобы получить высокотемпературное разложение, воспользуемся тем, что $e^{K\sigma_i\sigma_j}=\ch K+\sigma_i\sigma_j\sh K=\ch K \left(1+\sigma_i\sigma_j \th K\right)$.
-Тогда статсумма записывается в виде
+Такое выражение называется низкотемпературным разложением, так как оно хорошо сходится при малых
+температурах ($K>>1$).
+
+Чтобы получить высокотемпературное разложение, воспользуемся тем, что $e^{K\sigma_i\sigma_j}=\ch
+K+\sigma_i\sigma_j\sh K=\ch K \left(1+\sigma_i\sigma_j \th K\right)$. Тогда статсумма записывается в
+виде 
 \begin{equation}
@@
 \end{equation}
-Будем раскрывать скобки в произведении, сопоставляя каждому множителю $\sigma_i\sigma_j \th K$ ребро на решетке $\mathcal{L}$, соединяющее вершины $i,j$.
-Заметим, что вклад непрерывного пути, соединяющего вершины $i$ и $k$ пропорционален $(\sigma_i \sigma_{i+1}) (\sigma_{i+1}\sigma_{i+2}) (\sigma_{i+2}\sigma_{i+3})\dots (\sigma_{k-1}\sigma_k)=\sigma_{i}\sigma_k$, где мы пронумеровали вершины вдоль пути.
-То есть вклад от незамкнутого пути дается его концами, а вклад от замкнутого контура всегда равен 1.
-Тогда произведение запишется в виде
+Будем раскрывать скобки в произведении, сопоставляя каждому множителю $\sigma_i\sigma_j \th K$ ребро
+на решетке $\mathcal{L}$, соединяющее вершины $i,j$. Заметим, что вклад непрерывного пути,
+соединяющего вершины $i$ и $k$ пропорционален $(\sigma_i \sigma_{i+1}) (\sigma_{i+1}\sigma_{i+2})
+(\sigma_{i+2}\sigma_{i+3})\dots (\sigma_{k-1}\sigma_k)=\sigma_{i}\sigma_k$, где мы пронумеровали
+вершины вдоль пути. То есть вклад от незамкнутого пути дается его концами, а вклад от замкнутого
+контура всегда равен 1.  Тогда произведение запишется в виде 
 \begin{equation}
@@
 где $a_k$ дается суммой по всем контурам $c$ (не обязательно замкнутым или односвязным) длины $k$. 
-Чтобы вычислить статсумму, нам надо просуммировать такие выражения по всем возможным конфигурациям спинов.
-Заметим, что для любого незамкнутого контура и любой конфигурации найдется другая конфигурация, куда вклад этого контура входит с противоположным знаком (так как спины направлены в другую сторону).
-А вклад замкнутого контура равен $\th^{l[c]}K$ в любой конфигурации, то есть входит в статсумму $2^N$ раз.
-В результате получаем высокотемпературное разложение статсуммы в виде суммы по всем замкнутым контурам на решетке $\mathcal{L}$:
+Чтобы вычислить статсумму, нам надо просуммировать такие выражения по всем возможным конфигурациям
+спинов. Заметим, что для любого незамкнутого контура и любой конфигурации найдется другая
+конфигурация, куда вклад этого контура входит с противоположным знаком (так как спины направлены в
+другую сторону). А вклад замкнутого контура равен $\th^{l[c]}K$ в любой конфигурации, то есть входит
+в статсумму $2^N$ раз. В результате получаем высокотемпературное разложение статсуммы в виде суммы
+по всем замкнутым контурам на решетке $\mathcal{L}$: 
 \begin{equation}
@@
 \end{equation}
-Решетки $\mathcal{L}$ и $\mathcal{L}^*$ отличаются только на границе, поэтому в термодинамическом пределе $M/N\to 2$ и выражения для удельной свободной энергии из высокотемпературного и низкотемпературного разложений должны совпадать.
-Если ввести функцию $\Phi(\kappa)=\lim_{N\to \infty}\frac{1}{N} \ln \left(\sum_c \kappa^{l[c]}\right)$, то свободная энергия запишется в высокотемпературном и низкотемпературном разложениях следующим образом:
+Решетки $\mathcal{L}$ и $\mathcal{L}^*$ отличаются только на границе, поэтому в термодинамическом
+пределе $M/N\to 2$ и выражения для удельной свободной энергии из высокотемпературного и
+низкотемпературного разложений должны совпадать. Если ввести функцию $\Phi(\kappa)=\lim_{N\to
+  \infty}\frac{1}{N} \ln \left(\sum_c \kappa^{l[c]}\right)$, то свободная энергия запишется в
+высокотемпературном и низкотемпературном разложениях следующим образом: 
 \begin{equation}
@@
 \end{equation}
-Это и есть соотношение дуальности {\it Крамерса-Ванье}.
-Если ввести $K^*$ так, что $\th K^*=e^{-2K}$ или $\sh 2K^* \sh 2K=1$, то соотношение дуальности будет связывать теорию при температуре $K$ и $K^*$:
+Это и есть соотношение дуальности {\it Крамерса-Ванье}. Если ввести $K^*$ так, что $\th K^*=e^{-2K}$
+или $\sh 2K^* \sh 2K=1$, то соотношение дуальности будет связывать теорию при температуре $K$ и
+$K^*$: 
 \begin{equation}
@@
 \end{equation}
-Рассмотрим теперь поведение теории в критической точке $K_c$.
-В ней свободная энергия $f(K_c)$ не аналитична.
-Тогда $f$ должна быть не аналитична и при $K^*=K_c$.
-Если предположить, что критическая точка единственна, то мы можем найти ее из требования $K=K^*$, то есть $2K=\ln(2\ch^2 K)$ или
+Рассмотрим теперь поведение теории в критической точке $K_c$. В ней свободная энергия $f(K_c)$ не
+аналитична. Тогда $f$ должна быть не аналитична и при $K^*=K_c$. Если предположить, что критическая
+точка единственна, то мы можем найти ее из требования $K=K^*$, то есть $2K=\ln(2\ch^2 K)$ или 
 \begin{equation}
@@
 Теперь перейдем к точному решению модели Изинга.
-\section{Лекция 3. Решение Вдовиченко.}
+
+\subsection{Решение Вдовиченко.}
 \label{sec:lecture-6}
-Суть состоит в сведении вычисления статсуммы в высокотемпературном разложении к решению некоторого рекуррентного соотношения.
-Это соотношение записывается в матричном виде и его решение дается следом матрицы, который можно вычислить после преобразования Фурье.
-
-Заметим, что суммирование по замкнутым контурам обозначает, что в каждой вершине сходится четное число ребер.
-Поэтому мы можем перейти от суммирования по замкнутым контурам к суммированию по ``траекториям чернильной точки'' --- замкнутым путям, состоящим из компонент, которые можно нарисовать, не отрывая ручку от бумаги.
-При этом в случае контура с самопересечениями существует несколько способов нарисовать его.
-Например, ``восьмерку'' можно представить как два пути, путь без самопересечения и путь с самопересечением (Смотри рисунок \ref{fig:ising-1}).
+Суть состоит в сведении вычисления статсуммы в высокотемпературном разложении к решению некоторого
+рекуррентного соотношения. Это соотношение записывается в матричном виде и его решение дается следом
+матрицы, который можно вычислить после преобразования Фурье.
+
+Заметим, что суммирование по замкнутым контурам обозначает, что в каждой вершине сходится четное
+число ребер. Поэтому мы можем перейти от суммирования по замкнутым контурам к суммированию по
+``траекториям чернильной точки'' --- замкнутым путям, состоящим из компонент, которые можно
+нарисовать, не отрывая ручку от бумаги. При этом в случае контура с самопересечениями существует
+несколько способов нарисовать его. Например, ``восьмерку'' можно представить как два пути, путь без
+самопересечения и путь с самопересечением (Смотри рисунок \ref{fig:ising-1}). 
 \begin{figure}[h!tb]
@@
 \end{figure}
-Поэтому такие вклады надо брать с множителем $(-1)^{\nu(\Gamma)}$, где $\nu(\Gamma)$ - число самопересечений пути $\Gamma$.
+Поэтому такие вклады надо брать с множителем $(-1)^{\nu(\Gamma)}$, где $\nu(\Gamma)$ - число
+самопересечений пути $\Gamma$. 
 Статсумма в высокотемпературном разложении \eqref{eq:108} дается выражением 
@@
 \end{equation}
-Воспользуемся следующим утверждением, доказательство которого оставляется в качестве упражнения.
-Для любой связной замкнутой петли на плоскости с $\nu$ самоперечечениями и полным углом поворота $2\pi(n+1)$ (при ее обходе) верно равенство
+Воспользуемся следующим утверждением, доказательство которого оставляется в качестве упражнения. Для
+любой связной замкнутой петли на плоскости с $\nu$ самоперечечениями и полным углом поворота
+$2\pi(n+1)$ (при ее обходе) верно равенство 
 \begin{equation}
@@
 
-\section{Лекция 4}
+\section{Лекция 3}
 \label{sec:lecture-3}
@@
 
-\section{Лекция 5}
-\label{sec:lecture-3}
-В прошлой лекции мы обосновали гипотезу подобия при помощи рассмотрения блочных спинов и введения эффективного гамильтониана, имеющего ту же форму, но другие константы связи.
+\subsection{Ренормгруппа в решеточных моделях}
+\label{sec:renormgroup-lattice-models}
+Мы обосновали гипотезу подобия при помощи рассмотрения блочных спинов и введения эффективного гамильтониана, имеющего ту же форму, но другие константы связи.
 Эта процедура является перенормировкой в координатном пространстве, она определяет отображение гамильтониана $H\to H'$.
@@
 
-\subsection{Ренормгруппа в решеточных моделях}
-\label{sec:renormgroup-lattice-models}
 Рассматриваем решеточную модель, состоящую из $N$ спинов $\sigma_i$ на $d$-мерной решетке. Общий вид гамильтониана таких моделей
@@
 
-\section{Лекция 6 }
-\label{sec:lecture-4}
 \subsection{Уравнение Каллана-Симанчика}
@@
 
-В фиксированной точке ренормгруппы имеет место масштабная инвариантность.
-Вместе с трансляционной и лоренц-инвариантностью она порождает конформную инвариантность, то есть инвариантность относительно преобразований, сохраняющих углы.
-
-\section{Лекция 7. Конформная группа.}
-\label{sec:lecture-7}
-
-Построение Каданова-Вильсона (см.
-лекцию \ref{sec:kadanoff-procedure}) обосновало нам масштабную инвариантность модели Изинга.
-Сейчас мы обсудим, какие ограничения накладывает на теорию конформная инвариантность.
-
-Сперва рассмотрим конформную группу в произвольном числе измерений $d$.
-Метрический тензор обозначим через $g_{\mu\nu},\; \mu,\nu=1,\dots,d$.
-Конформными называются преобразования $x\to x'$, сохраняющие метрический тензор с точностью до масштаба:
+В фиксированной точке ренормгруппы имеет место масштабная инвариантность. Вместе с трансляционной и
+лоренц-инвариантностью она порождает конформную инвариантность, то есть инвариантность относительно
+преобразований, сохраняющих углы. 
+\newpage
+\section{Лекция 4. Конформная группа.}
+\label{sec:lecture-4}
+
+Построение Каданова-Вильсона (см. лекцию \ref{sec:kadanoff-procedure}) обосновало нам масштабную
+инвариантность модели Изинга. Сейчас мы обсудим, какие ограничения накладывает на теорию конформная
+инвариантность.
+
+Сперва рассмотрим конформную группу в произвольном числе измерений $d$. Метрический тензор обозначим
+через $g_{\mu\nu},\; \mu,\nu=1,\dots,d$. Конформными называются преобразования $x\to x'$,
+сохраняющие метрический тензор с точностью до масштаба: 
 \begin{equation}
@@
 \end{equation}
-Заметим, что группа Пуанкаре является подгруппой конформной группы с $\Lambda(x)=1$, а также что конформные преобразования сохраняют углы.
+Заметим, что группа Пуанкаре является подгруппой конформной группы с $\Lambda(x)=1$, а также что
+конформные преобразования сохраняют углы.
 
@@
   \label{eq:145}
-  g'_{\mu\nu}=\frac{\partial x^{\alpha}}{\partial x'^{\mu}}\frac{\partial x^{\beta}}{\partial x'^{\nu}} g_{\alpha\beta}=(\delta^{\alpha}_{\mu}-\partial_{\mu}\epsilon^{\alpha})(\delta^{\beta}_{\nu}-\partial_{\nu} \epsilon^{\beta})g_{\alpha\beta}=g_{\mu\nu}-(\partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu})
+  g'_{\mu\nu}=\frac{\partial x^{\alpha}}{\partial x'^{\mu}}\frac{\partial x^{\beta}}{\partial
+    x'^{\nu}}
+  g_{\alpha\beta}=(\delta^{\alpha}_{\mu}-\partial_{\mu}\epsilon^{\alpha})(\delta^{\beta}_{\nu}-\partial_{\nu}
+  \epsilon^{\beta})g_{\alpha\beta}=g_{\mu\nu}-(\partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu}) 
 \end{equation}
@@
 \end{equation}
-Для простоты рассмотрим преобразования, действующие на плоскую метрику $g_{\mu\nu}(x)=\eta_{\mu\nu}$, кроме того, с учетом приложений к статистической физике, будем работать в евклидовом пространстве, а не в пространстве Минковского.
-Так что $\eta=\mathrm{diag}(1,1,\dots,1),\quad \eta_{\mu\nu}=\delta_{\mu\nu}$.
-В этом случае условие \eqref{eq:147} перепишется в простом виде
+Для простоты рассмотрим преобразования, действующие на плоскую метрику
+$g_{\mu\nu}(x)=\eta_{\mu\nu}$, кроме того, с учетом приложений к статистической физике, будем
+работать в евклидовом пространстве, а не в пространстве Минковского. Так что
+$\eta=\mathrm{diag}(1,1,\dots,1),\quad \eta_{\mu\nu}=\delta_{\mu\nu}$. В этом случае условие
+\eqref{eq:147} перепишется в простом виде 
 \begin{equation}
@@
 \end{equation}
-Сравним полученное равенство с результатом применения оператора $\partial^{\rho}$ к уравнению \eqref{eq:149}:
+Сравним полученное равенство с результатом применения оператора $\partial^{\rho}$ к уравнению
+\eqref{eq:149}: 
 \begin{equation}
@@
 \end{equation}
-Сразу можно отметить, что при $d=1$ любое гладкое преобразование будет конформным. Рассмотрим случай $d\geq 3$. Функция $f(x)$ должна иметь вид
+Сразу можно отметить, что при $d=1$ любое гладкое преобразование будет конформным. Рассмотрим случай
+$d\geq 3$. Функция $f(x)$ должна иметь вид 
 \begin{equation}
@@
 \end{equation}
-Так как равенства \eqref{eq:147}, \eqref{eq:148}, \eqref{eq:150} должны выполняться для любых $x^{\mu}$, то мономы в $\epsilon$ можно рассматривать независимо.
-На $a_{\mu}$ не возникает никаких ограничений.
-Этот член соответствует трансляциям.
-Теперь подставляем линейный член в \eqref{eq:147}, \eqref{eq:148} и получаем условие
+Так как равенства \eqref{eq:147}, \eqref{eq:148}, \eqref{eq:150} должны выполняться для любых
+$x^{\mu}$, то мономы в $\epsilon$ можно рассматривать независимо. На $a_{\mu}$ не возникает никаких
+ограничений. Этот член соответствует трансляциям. Теперь подставляем линейный член в \eqref{eq:147},
+\eqref{eq:148} и получаем условие 
 \begin{equation}
@@
 Первый член соответствует масштабному преобразованию, а второй - повороту. 
-В результате подстановки квадратичного члена $\epsilon$ в \eqref{eq:148}, \eqref{eq:150} получаем следующее условие на $c_{\mu\nu\rho}$:
+В результате подстановки квадратичного члена $\epsilon$ в \eqref{eq:148}, \eqref{eq:150} получаем
+следующее условие на $c_{\mu\nu\rho}$: 
 \begin{equation}
@@
 где $\eta_{ab}=\mathrm{diag}(-1,1,\dots,1)$. Видно, что мы получили алгебру $so(d+1,1)$. В случае пространства Минковского была бы $so(d,2)$.
-\section{Лекция 8}
-\label{sec:lecture-8}
 
@@
 
-Обсудим, какой вид могут иметь простейшие инварианты --- $N$-точечные функции $\Gamma(x_1,\dots,x_N)$.
-В силу трансляционной инвариантности они могут зависеть только от модуля разности $|\vec x_i-\vec x_j|$.
-Масштабная инвариантность может сохраняться только отношениями
+Обсудим, какой вид могут иметь простейшие инварианты --- $N$-точечные функции
+$\Gamma(x_1,\dots,x_N)$. В силу трансляционной инвариантности они могут зависеть только от модуля
+разности $|\vec x_i-\vec x_j|$.  Масштабная инвариантность может сохраняться только отношениями 
 \begin{equation}
@@
 
-Покажем теперь, как преобразуются поля при конформных преобразованиях.
-Для этого используем метод индуцированных представлений, который можно легко объяснить на примере алгебры Пуанкаре.
-Сначала рассматриваем подалгебру, которая оставляет точку $x=0$ неподвижной.
-Это алгебра группы Лоренца или группы вращений в случае евклидова пространства.
-На поля в точке $x=0$ она действует своими матричными представлениями:
+Покажем теперь, как преобразуются поля при конформных преобразованиях. Для этого используем метод
+индуцированных представлений, который можно легко объяснить на примере алгебры Пуанкаре. Сначала
+рассматриваем подалгебру, которая оставляет точку $x=0$ неподвижной. Это алгебра группы Лоренца или
+группы вращений в случае евклидова пространства. На поля в точке $x=0$ она действует своими
+матричными представлениями: 
 \begin{equation}
@@
 \end{multline}
-Для полной конформной группы подгруппа стабильности точки $x=0$ порождается поворотами, растяжениями и специальными конформными преобразованиями.
-Обозначим представление генераторов через $S_{\mu\nu}, \tilde \Delta, k_{\mu}$ соответственно.
-Они порождают матричное представление усеченной алгебры с коммутационными соотношениями
+Для полной конформной группы подгруппа стабильности точки $x=0$ порождается поворотами, растяжениями
+и специальными конформными преобразованиями. Обозначим представление генераторов через $S_{\mu\nu},
+\tilde \Delta, k_{\mu}$ соответственно. Они порождают матричное представление усеченной алгебры с
+коммутационными соотношениями 
 \begin{eqnarray}
@@
 \end{eqnarray}
-Если требовать, чтобы поле $\Phi(x)$ преобразовывалось по неприводимому представлению группы Лоренца, то по лемме Шура любая матрица, коммутирующая со всеми генераторами $S_{\mu\nu}$ пропорциональна единичной.
+Если требовать, чтобы поле $\Phi(x)$ преобразовывалось по неприводимому представлению группы
+Лоренца, то по лемме Шура любая матрица, коммутирующая со всеми генераторами $S_{\mu\nu}$
+пропорциональна единичной.   
 \begin{mynote}
@@
 
-То есть $\tilde \Delta\propto I$ и $k_{\mu}=0$.
-Тогда $\tilde \Delta =-i \Delta I$, где $\Delta$ -- скейлинговая размерность поля $\Phi$, $\Phi'(\lambda x)=\lambda^{-\Delta}\Phi(x)$.
-Закон преобразования бесспинового поля $\varphi$ при конечных конформных преобразованиях
+То есть $\tilde \Delta\propto I$ и $k_{\mu}=0$. Тогда $\tilde \Delta =-i \Delta I$, где $\Delta$ --
+скейлинговая размерность поля $\Phi$, $\Phi'(\lambda x)=\lambda^{-\Delta}\Phi(x)$. Закон
+преобразования бесспинового поля $\varphi$ при конечных конформных преобразованиях 
 \begin{eqnarray}
@@
 \end{equation}
-где мы использовали равенства \eqref{eq:147}, \eqref{eq:148}.
-То есть бесследовость тензора энергии-импульса ведет к конформной инвариантности классической теории поля.
-В классической теории поля при наличии трансляционной, вращательной и масштабной инвариантности  тензор энергии-импульса часто можно переопределить так, чтобы он был бесследовым.
-То есть конформная инвариантность следует из трансляционной, вращательной и масштабной.
-В случае двумерной квантовой теории поля общего доказательства нет, но конформная инвариантность наблюдается во множестве моделей.
-
-\section{Лекция 9}
-\label{sec:lecture-9}
+где мы использовали равенства \eqref{eq:147}, \eqref{eq:148}. То есть бесследовость тензора
+энергии-импульса ведет к конформной инвариантности классической теории поля. В классической теории
+поля при наличии трансляционной, вращательной и масштабной инвариантности  тензор энергии-импульса
+часто можно переопределить так, чтобы он был бесследовым. То есть конформная инвариантность следует
+из трансляционной, вращательной и масштабной. В случае двумерной квантовой теории поля общего
+доказательства нет, но конформная инвариантность наблюдается во множестве моделей.
+
+\section{Лекция 5}
+\label{sec:lecture-5}
 
@@
 \end{equation}
-Отсюда сразу получаем, сто
+Отсюда сразу получаем, что
 \begin{equation}
@@
 \end{equation}
-Из четырех точек уже можно собрать инварианты \eqref{eq:175}, поэтому из требований конформной инвариантности для четырехточечной функции можно написать только
+Из четырех точек уже можно собрать инварианты \eqref{eq:175}, поэтому из требований конформной
+инвариантности для четырехточечной функции можно написать только 
 \begin{equation}
@@
 
-Напомним, о чем идет речь. В произвольной теории поля с полями $\Phi(x)$ инфинитезимальное преобразование может быть записано при помощи генераторов
+Напомним, о чем идет речь. В произвольной теории поля с полями $\Phi(x)$ инфинитезимальное
+преобразование может быть записано при помощи генераторов 
 \begin{equation}
@@
 \end{equation}
-Сделаем замену переменных $\Phi\to \Phi'$ в функциональном интеграле. При этом можно предполагать, что ``мера интегрирования'' не меняется $\mathcal{D}\Phi'=\mathcal{D}\Phi$ \cite{difrancesco1997cft}:
+Сделаем замену переменных $\Phi\to \Phi'$ в функциональном интеграле. При этом можно предполагать,
+что ``мера интегрирования'' не меняется $\mathcal{D}\Phi'=\mathcal{D}\Phi$
+\cite{difrancesco1997cft}: 
 \begin{equation}
@@
 \end{equation}
-Рассмотрим некоторые примеры, которые понадобятся нам для конформной теории. Мы используем полученный нами явный вид генераторов \eqref{eq:169}.
+Рассмотрим некоторые примеры, которые понадобятся нам для конформной теории. Мы используем
+полученный нами явный вид генераторов \eqref{eq:169}.
 
@@
 \end{equation}
-Теперь рассмотрим вращения. Если тензор энергии-импульса симметризован (это можно сделать в большинстве случаев), то отвечающий вращениям ток дается выражением
+Теперь рассмотрим вращения. Если тензор энергии-импульса симметризован (это можно сделать в
+большинстве случаев), то отвечающий вращениям ток дается выражением 
 \begin{equation}
@@
 \end{equation}
-Тензор энергии-импульса в квантовой теории симметричен в корреляционных функциях, если его положение не совпадает с положениями других полей в корреляторе.
-
-Наконец, для масштабных преобразований ток имеет вид $T^{\mu}_{\nu}x^{\nu}$, действие генератора дается выражением \eqref{eq:181} и тождества Уорда выглядят так:
+Тензор энергии-импульса в квантовой теории симметричен в корреляционных функциях, если его положение
+не совпадает с положениями других полей в корреляторе.
+
+Наконец, для масштабных преобразований ток имеет вид $T^{\mu}_{\nu}x^{\nu}$, действие генератора
+дается выражением \eqref{eq:181} и тождества Уорда выглядят так: 
 \begin{equation}
@@
 
-В некоторых теориях из масштабной, вращательной и трансляционной инвариантности автоматически следует конформная инвариантность.
-Как мы знаем, конформная инвариантность соответствует бесследовости тензора энергии-импульса.
-Общего доказательства конформной инвариантности для масштабно-, трансляционно- и вращательно-инвариантных теорий не существует даже для двумерного случая, однако мы можем показать, что вакуумное среднее квадрата следа тензора энергии-импульса в этом случае равно нулю.
+В некоторых теориях из масштабной, вращательной и трансляционной инвариантности автоматически
+следует конформная инвариантность. Как мы знаем, конформная инвариантность соответствует
+бесследовости тензора энергии-импульса. Общего доказательства конформной инвариантности для
+масштабно-, трансляционно- и вращательно-инвариантных теорий не существует даже для двумерного
+случая, однако мы можем показать, что вакуумное среднее квадрата следа тензора энергии-импульса в
+этом случае равно нулю.
 
@@
 \end{equation}
-Если в теории сохраняется четность, то $S_{\mu\nu\rho\sigma}(x)=S_{\rho\sigma\mu\nu}(x)$.
-В силу масштабной инвариантности $T_{\mu\nu}$ имеет скейлинговую размерность 2, так как является плотностью.
-Следовательно функция Швингера при масштабных преобразованиях ведет себя так:
+Если в теории сохраняется четность, то $S_{\mu\nu\rho\sigma}(x)=S_{\rho\sigma\mu\nu}(x)$. В силу
+масштабной инвариантности $T_{\mu\nu}$ имеет скейлинговую размерность 2, так как является
+плотностью. Следовательно функция Швингера при масштабных преобразованиях ведет себя так: 
 \begin{equation}
@@
 \end{equation}
-при любых значениях $x$. В частности $\langle T^{\mu}_{\mu}(0)\rangle=0$, то есть у оператора следа тензора энергии-импульса нулевое матожидание и среднеквадратичное отклонение в основном состоянии.
-
-\section{Лекция 10. Конформная инвариантность в двумерной теории.}
-\label{sec:lecture-10}
-
-В лекции \ref{sec:lecture-7} мы получили общее условие на вид инфинитезимальных конформных преобразований:
+при любых значениях $x$. В частности $\langle T^{\mu}_{\mu}(0)\rangle=0$, то есть у оператора следа
+тензора энергии-импульса нулевое матожидание и среднеквадратичное отклонение в основном состоянии.
+
+\section{Лекция 6. Конформная инвариантность в двумерной теории.}
+\label{sec:lecture-6}
+
+В лекции \ref{sec:lecture-4} мы получили общее условие на вид инфинитезимальных конформных преобразований:
 \begin{equation}
@@
 \end{equation}
-Теперь у нас $d=2$, $\mu,\nu=0,1$ и $\eta_{\mu\nu}=\delta_{\mu\nu}$, так как мы работаем в евклидовой теории. Расписывая компоненты уравнения \eqref{eq:223}, получаем
+Теперь у нас $d=2$, $\mu,\nu=0,1$ и $\eta_{\mu\nu}=\delta_{\mu\nu}$, так как мы работаем в
+евклидовой теории. Расписывая компоненты уравнения \eqref{eq:223}, получаем 
 \begin{eqnarray}
@@
 \end{eqnarray}
-Решениями будут любые голоморфные и антиголоморфные функции: $\epsilon=\epsilon(z)$ -- голоморфная функция и $\bar \epsilon=\bar \epsilon(\bar z)$ -- антиголоморфная.
-Таким образом мы видим, что алгебра локальных конформных преобразований в двумерном случае оказывается бесконечномерной алгеброй преобразований
+Решениями будут любые голоморфные и антиголоморфные функции: $\epsilon=\epsilon(z)$ -- голоморфная
+функция и $\bar \epsilon=\bar \epsilon(\bar z)$ -- антиголоморфная. Таким образом мы видим, что
+алгебра локальных конформных преобразований в двумерном случае оказывается бесконечномерной алгеброй
+преобразований 
 \begin{eqnarray}
@@
 \end{eqnarray}
-Мы видим, что алгебра распадается в прямую сумму $\mathcal{A} \oplus \bar{\mathcal{A}}$, каждая компонента --- это алгебра Витта (Witt algebra).
-Оказывается удобно продолжить теорию на случай независимых $z,\bar z$.
-Тогда теория распадется на два независимых сектора.
-Условие же $z^{*}=\bar z$ можно наложить в самом конце.
-Такая процедура соответствует комплексному продолжению всех функций от $x_{0},x_{1}$ на $x_{0},x_{1}\in \mathbb{C}^{2}$.
-Заметим, что вещественная плоскость сохраняется подалгеброй, натянутой на генераторы $l_{n}+\bar l_{n}$ и $i(l_{n}-\bar l_{n})$.
+Мы видим, что алгебра распадается в прямую сумму $\mathcal{A} \oplus \bar{\mathcal{A}}$, каждая
+компонента --- это алгебра Витта (Witt algebra). Оказывается удобно продолжить теорию на случай
+независимых $z,\bar z$. Тогда теория распадется на два независимых сектора. Условие же $z^{*}=\bar
+z$ можно наложить в самом конце. 
+Такая процедура соответствует комплексному продолжению всех функций
+от $x_{0},x_{1}$ на $x_{0},x_{1}\in \mathbb{C}^{2}$. Заметим, что вещественная плоскость сохраняется
+подалгеброй, натянутой на генераторы $l_{n}+\bar l_{n}$ и $i(l_{n}-\bar l_{n})$.
 
@@
 
-Глобальными называются те преобразования, которые определены на всей сфере Римана $S^{2}=\mathbb{C}^{2}\cup \{\infty\}$.
-Понятно, что это может быть только при $n\geq -1$.
-Кроме того, чтобы рассмотреть окрестность точки $z=\infty$ можно сделать преобразование координат $z=-\frac{1}{w}$.
-Тогда
+Глобальными называются те преобразования, которые определены на всей сфере Римана
+$S^{2}=\mathbb{C}^{2}\cup \{\infty\}$. Понятно, что это может быть только при $n\geq -1$. Кроме
+того, чтобы рассмотреть окрестность точки $z=\infty$ можно сделать преобразование координат
+$z=-\frac{1}{w}$. Тогда 
 \begin{equation}
@@
 \end{equation}
-Это выражение должно быть хорошо определено при $w\to 0$, то есть $n\leq 1$.
-Значит глобальные конформные преобразования генерируются $l_{\pm 1},l_{0},\bar l_{\pm 1},\bar l_{0}$.
-Заметим, что генераторы $l_{-1},\bar l_{-1}$ порождают трансляции, $i(l_{0}-\bar l_{0})$ -- вращения, $l_{0}+\bar l_{0}$ -- масштабные преобразования.
+Это выражение должно быть хорошо определено при $w\to 0$, то есть $n\leq 1$. Значит глобальные
+конформные преобразования генерируются $l_{\pm 1},l_{0},\bar l_{\pm 1},\bar l_{0}$. Заметим, что
+генераторы $l_{-1},\bar l_{-1}$ порождают трансляции, $i(l_{0}-\bar l_{0})$ -- вращения, $l_{0}+\bar
+l_{0}$ -- масштабные преобразования. 
 Конечные глобальные преобразования имеют вид 
@@
   c & d
-\end{pmatrix}$, то ясно, что мы имеем дело с группой $SL_{2}(\mathbb{C})/Z_{2}\approx SO(3,1)$.
-Факторизация по $Z_{2}$ соответствует тому, что изменение знака у $a,b,c,d$ разом не меняет преобразования.
-Эта группа называется также группой проективных конформных преобразований.
+\end{pmatrix}$, 
+то ясно, что мы имеем дело с группой $SL_{2}(\mathbb{C})/Z_{2}\approx SO(3,1)$. Факторизация по
+$Z_{2}$ соответствует тому, что изменение знака у $a,b,c,d$ разом не меняет преобразования. Эта
+группа называется также группой проективных конформных преобразований.
 
@@
 
-Глобальные конформные преобразования образуют группу, локальные же преобразования не обратимы, поэтому по отношению к ним говорят только об алгебре.
-
-Глобальные преобразования полезны для описания физических состояний.
-Допустим, мы работаем в базисе собственных состояний операторов $l_{0}, \bar l_{0}$, соответствующие собственные значения $h,\bar h$ -- независимые, вещественные, называются конформными весами или голоморфной и антиголоморфной размерностями.
-Так как $l_{0}+\bar l_{0}$ -- генератор дилатации, то скейлинговая размерность $\Delta=h+\bar h$, а поскольку $i(l_{0}-\bar l_{0})$ порождает вращения, то спин $s=h-\bar h$.
+Глобальные конформные преобразования образуют группу, локальные же преобразования не обратимы,
+поэтому по отношению к ним говорят только об алгебре.
+
+Глобальные преобразования полезны для описания физических состояний. Допустим, мы работаем в базисе
+собственных состояний операторов $l_{0}, \bar l_{0}$, соответствующие собственные значения $h,\bar
+h$ -- независимые, вещественные, называются конформными весами или голоморфной и антиголоморфной
+размерностями. Так как $l_{0}+\bar l_{0}$ -- генератор дилатации, то скейлинговая размерность
+$\Delta=h+\bar h$, а поскольку $i(l_{0}-\bar l_{0})$ порождает вращения, то спин $s=h-\bar h$.
 
@@
 \end{eqnarray}
-Прежде, чем мы начнем переписывать тождества в комплексных координатах, обсудим следующий вспомогательный математический факт: для голоморфных (антиголоморфных) функций можно использовать следующее представление для $\delta$-функции:
+Прежде, чем мы начнем переписывать тождества в комплексных координатах, обсудим следующий
+вспомогательный математический факт: для голоморфных (антиголоморфных) функций можно использовать
+следующее представление для $\delta$-функции: 
 \begin{equation}
@@
 
-\section{Лекция 11}
-\label{sec:lecture-11}
+\section{Лекция 7}
+\label{sec:lecture-7}
 
@@
 
-\section{Лекция 12}
-\label{sec:lecture-12}
+\section{Лекция 8. Уравнения на корреляционные функции в минимальных моделях}
+\label{sec:lecture-7}
+  \begin{itemize}
+  \item Конформный предел модели Изинга
+  \item Свободный фермион
+  \item Выражение для четырехточечной функции в модели Изинга
+  \end{itemize}
 
@@
 
-Рассмотрим теорию с центральным зарядом $c=\frac{1}{2}$, $\bar c=c$ и примарными полями с конформными размерностями
+Рассмотрим теорию с центральным зарядом $c=\frac{1}{2}$, $\bar c=c$ и примарными полями с
+конформными размерностями
 \begin{equation}
@@
 
-Мы знаем (см. Лекции \ref{sec:lecture-1}, \ref{sec:lecture-5}, \ref{sec:lecture-6}) значения критических индексов в модели Изинга --- $\eta=\frac{1}{4}, \nu=1$. Тогда для двухточечной функции
+Мы знаем (см. Лекции \ref{sec:lecture-1}, \ref{sec:lecture-2}, \ref{sec:lecture-3}) значения критических индексов в модели Изинга --- $\eta=\frac{1}{4}, \nu=1$. Тогда для двухточечной функции
 \begin{equation}
@@
 
-\section{Лекция 13. Уравнения на корреляционные функции в минимальных моделях}
-\label{sec:lecture-13}
-
-Чтобы окончательно зафиксировать структуру двумерной конформной теории поля введем два дополнительных предположения.
-Во-первых, мы предполагаем, что локальные поля образуют алгебру $\mathcal{A}$ по отношению к операторному разложению \eqref{eq:248}\eqref{eq:249}.
+\subsection{Уравнения на корреляционные функции в минимальных моделях}
+\label{sec:null-fields}
+
+Чтобы окончательно зафиксировать структуру двумерной конформной теории поля введем два
+дополнительных предположения. Во-первых, мы предполагаем, что локальные поля образуют алгебру
+$\mathcal{A}$ по отношению к операторному разложению \eqref{eq:248}\eqref{eq:249}.
 
@@
 
+\section{Лекция 9. Классификация минимальных моделей}
+\label{sec:lecture-7}
+
+  \begin{itemize}
+  \item Детерминант Каца
+  \item Значения центрального заряда и соответствие с решеточными моделями
+  \end{itemize}
+
+Charges and conformal weights of degenerate fields from Kac table are
+\begin{equation}
+  \label{eq:139}
+  \alpha_{r,s}=\frac{1}{2}(1-r)\alpha_{+}+\frac{1}{2}(1-s)\alpha_{-},\quad h_{r,s}=\frac{(r\kappa-4s)^{2}-(\kappa-4)^{2}}{16\kappa}
+\end{equation}
+So holomorphic and full primary fields are denoted by $\psi_{r,s}(z)\sim V_{\alpha_{r,s}}(z)$ and
+$\psi_{r,s}(z,\bar z)\sim V^{(\alpha_{r,s})}(z,\bar z)$
+
+\section{Лекция 10. Представление кулоновского газа для минимальных моделей}
+\label{sec:lecture-8}
+
+\subsection{Coulomb gas representation and screening operators}
+\label{sec:coul-gas-repr}
+
+Calculation of correlation functions in Liouville field theory can be done as follows. 
+Consider correlation some function with operator $V_{-\frac{b}{2}}$, it satisfies second order
+differential equation:
+\begin{equation}
+  \label{eq:33}
+  \left(\frac{1}{b^{2}}\partial^{2}+T(z)\right)\left<V_{-\frac{b}{2}}(z) \dots \right>=0
+\end{equation}
+Now to find some correlation function $\left<V_{\alpha_{1}}(z_{1})\dots
+  V_{\alpha_{k}}(z_{k})\right>$ we consider auxiliary correlation function with additional
+operator $V_{-\frac{b}{2}}(z)$, find a solution to differential equation and fix the integration
+constants using fusion rules for field $V_{-\frac{b}{2}}$.
+
+It can be shown (add reference here? \cite{nakayama2004liouville},\cite{teschner2001liouville}) that 
+\begin{equation}
+  \label{eq:34}
+  V_{-\frac{b}{2}}\times V_{\alpha}= [V_{\alpha-\frac{b}{2}}]+[V_{\alpha+\frac{b}{2}}]
+\end{equation}
+
+Full form of the operator product expansion is
+\begin{equation}
+  \label{eq:39}
+  A(z)B(w)\underset{z\to w}{\longrightarrow} \sum_{C} \frac{f_{AB}^{C}}{(z-w)^{h_{A}+h_{B}-h_{C}}} C(w)
+\end{equation}
+
+We use auxiliary correlation function that can be computed using Coulomb gas picture. The
+computation relies on following ideas.
+
+\subsubsection{Coulomb gas picture. Free boson theory. Minimal models}
+\label{sec:free-boson-minimal-models}
+
+\begin{equation}
+  \label{eq:40}
+  S=\int d^{2}z b (\partial \varphi)^{2},\quad \left<\varphi(z,\bar z)\varphi(w,\bar
+    w)\right>=-\frac{1}{2b}\left(\ln (z-w) + \ln (\bar z - \bar w)\right)+const
+\end{equation}
+
+\begin{equation}
+  \label{eq:42}
+  T(z)=-\frac{1}{2}:\partial \varphi \partial \varphi:, \quad c=1
+\end{equation}
+In holomorphic sector primary fields are $\partial \varphi$ with $h=1$ and
+$V_{\alpha}(z)=e^{i \alpha \varphi(z)}$ with dimension $h_{\alpha}=\frac{\alpha^{2}}{2}$.
+
+Field $\varphi(z)$ is not purely holomorphic, it contains zero mode
+\begin{equation}
+  \label{eq:43}
+  \varphi(z)=\varphi_{0}-ia_{0}\ln z+\sum_{n\neq 0}\frac{1}{n}a_{n} z^{-n},\quad
+  [a_{n},a_{m}]=n\delta_{n+m,0}, \quad [\varphi_{0},a_{0}]=i
+\end{equation}
+But we can limit ourselves to chiral operators.
+
+If $\alpha_{1}+\dots+\alpha_{n}=0$ then 
+\begin{equation}
+  \label{eq:41}
+  \left<e^{\alpha_{1}\varphi}(z_{1})\dots e^{\alpha_{n}\varphi}(z_{n})\right> = \prod_{i<j}(z_{i}-z_{j})^{-\alpha_{i}\alpha_{j}}
+\end{equation}
+Since $\left< :e^{A_{1}}::e^{A_{2}}:\dots :A^{A_{n}}:\right> =
+\exp\sum_{i<j}\left<A_{i}A_{j}\right>$, we can take $A_{i}=\alpha_{i}\varphi(z_{i})$ and use the
+fact that $\left<A_{i}A_{j}\right>=\ln |z_{i}-z_{j}|^{-\alpha_{i}\alpha_{j}}$.
+
+Neutrality condition can be seen from the invariance of the action w.r.t. $\varphi\to\varphi+a$,
+then the correlator obtains factor $e^{\sum \alpha_{i}}$ which is 1 if $\sum \alpha_{i}=0$.
+
+Vacuum expectation value of operator with non-zero charge $\alpha$ should be zero.
+
+To obtain models with $c\neq 1$ one needs to introduce the background charge:
+\begin{equation}
+  \label{eq:44}
+  S=\frac{1}{8\pi} \int d^{2}x \sqrt{g} (\partial_{\mu}\varphi\partial^{\mu}\varphi+2\gamma\varphi R)
+\end{equation}
+Here $R$ is scalar curvature, $\gamma$ - constant.
+
+(Gauss-Bonnet theorem: $\int d^{2}x \sqrt{g} R = 8\pi(1-h)$, $h$-number of handles).
+
+After introducing interaction with the curvature Ward identities are changed and now neutrality
+condition is $\sum \alpha_{i}=2\alpha_{0}$, where $i\sqrt{2}\alpha_{0}=\gamma$. 
+Stress-energy tensor now takes the form
+\begin{equation}
+  \label{eq:45}
+  T_{\mu\nu}=T^{(0)}_{\mu\nu}-\frac{\gamma}{2\pi}\left(\partial_{\mu}\partial_{\nu}\varphi-\frac{1}{2}\eta_{\mu\nu}\partial^{\rho}\partial_{\rho}\varphi\right)
+\end{equation}
+and
+\begin{equation}
+  \label{eq:46}
+  T(z)=-\frac{1}{2}:\partial \varphi\partial\varphi:+i\sqrt{2}\alpha_{0}\partial^{2}\varphi
+\end{equation}
+If we calculate OPE of $T$ we see that $\partial\varphi$ is not primary any more \cite{difrancesco1997cft}:
+\begin{equation}
+  \label{eq:47}
+  T(z)\partial\varphi(w)\sim
+  \frac{i2\sqrt{2}\alpha_{0}}{(z-w)^{3}}+\frac{\partial\varphi(w)}{(z-w)^{2}} +\frac{\partial^{2}\varphi(w)}{z-w}
+\end{equation}
+Vertex operators are still primary, but conformal dimensions are now
+\begin{equation}
+  \label{eq:48}
+  h_{\alpha}=\alpha^{2}-2\alpha_{0}\alpha
+\end{equation}
+and central charge is
+\begin{equation}
+  \label{eq:49}
+  c=1-24\alpha_{0}^{2}
+\end{equation}
+The correlator \eqref{eq:41} is preserved. Now vertex operators $V_{\alpha}$ and
+$V_{2\alpha_{0}-\alpha}$ are equivalent, so two-point function
+$\left<V_{\alpha}(z)V_{\alpha}(w)\right>$  is not zero, but it should be represented as
+$\left<V_{\alpha}(z)V_{2\alpha_{0}-\alpha}(w)\right>=\frac{1}{(z-w)^{h_{\alpha}}}$.
+
+In general we insert non-local screening operator with zero conformal dimension but nonzero charge.
+If $\psi$ is primary field with $h_{\psi}=1$ its integral $  A=\oint dz \psi(z) $ is a nonlocal
+operator of conformal dimension zero (invariant under conformal mapping $z\to w$ 
+\begin{equation}
+  \label{eq:50}
+  A\to \oint dz \psi(z) \left(\frac{\partial w}{\partial z}\right)=\oint dw \psi(w)
+\end{equation}
+Then
+\begin{multline}
+  \label{eq:51}
+  [L_{n},A]=\oint dz [L_{n},\psi(z)]=\\\oint dz  (n+1) z^{n}\psi(z)+z^{n+1}\partial \psi(z)=\\
+  \oint dz \partial (z^{n+1}\psi (z))=0
+\end{multline}
+Screening operators are constructed from vertex operators
+\begin{equation}
+  \label{eq:52}
+  V_{\pm}=V_{\alpha_{\pm}}, \quad \alpha_{\pm}=\alpha_{0}\pm \sqrt{\alpha_{0}^{2}+1}, \quad
+  \alpha_{+}\alpha_{-}=-1,\quad \alpha_{+}+\alpha_{-}=2\alpha_{0}
+\end{equation}
+\begin{equation}
+  \label{eq:53}
+  Q_{\pm}=\oint dz V_{\pm}(z)=\oint dz e^{i\sqrt{2}\alpha_{\pm}\varphi(z)}
+\end{equation}
+Now for two-point function we can write
+\begin{equation}
+  \label{eq:54}
+  \left<V_{\alpha}(z)V_{\alpha}(w)Q_{-}^{m}Q_{+}^{n}\right>,
+\end{equation}
+with neutrality condition $2\alpha+n\alpha_{+}+m\alpha_{-}=2\alpha_{0}$,  so $2\alpha$ is an integer
+combination of $\alpha_{-}$ and $\alpha_{+}$.
+So we obtain Kac formula for conformal weights of fields in minimal models
+\begin{equation}
+  \label{eq:55}
+  \alpha_{r,s}=\frac{1}{2}(1-r)\alpha_{+}+\frac{1}{2}(1-s)\alpha_{-}\quad 
+  h_{r,s}(c)=\frac{1}{4}(r\alpha_{+}+s\alpha_{-})^{2}-\alpha_{0}^{2}
+\end{equation}
+
+If we calculate three-point function and require operator algebra to be closed we can obtain
+conditions on possible values of central charge or background charge $\alpha_{0}$.
+
+Computation of three-point function relies on following trick: find four-point function as a
+solution of differential equation following from null-vector condition and then recover structure
+constants for three-point function from the limit $z\to 0$, where $z$ is cross-ratio.
+
+Structure constants in three-point function are equal to fusion coefficients for corresponding
+fields, for example substitute fusion rule \eqref{eq:39} to three-point function
+
+  \begin{equation}
+    \label{eq:56}
+    \langle
+    \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{\Delta_{1}+\Delta_{2}-\Delta_{3}}
+      x_{23}^{\Delta_{2}+\Delta_{3}-\Delta_{1}}x_{13}^{\Delta_{3}+\Delta_{1}-\Delta_{2}}}.     
+  \end{equation}
+
+Assume that we know four-point function
+$\left<\varphi_{1}(z_{1})\varphi_{2}(z_{2})\varphi_{3}(z_{3})\varphi_{4}(z_{4})\right>$, then we
+take limits $z_{1}\to z_{2}$ and $z_{3}\to z_{4}$ and obtain product of structure constants
+$C_{12}^{r}C_{34}^{r}$ as a coefficient before $\frac{1}{z_{24}^{r}}$.
+
+To compute four-point function we use conformal invariance to send $z_{1}\to 0$, $z_{2}\to z$
+$z_{3}\to 1$ and $z_{4}\to \infty$:
+\begin{equation}
+  \label{eq:58}
+  \left<\varphi_{1}(z_{1})\varphi_{2}(z_{2})\varphi_{3}(z_{3})\varphi_{4}(z_{4})\right>=\left<
+    V_{r_{1},s_{1}}(z_{1}) V_{r_{2},s_{2}}(z_{2}) V_{r_{3},s_{3}}(z_{3}) V_{-r_{4},-s_{4}}(z_{4})
+    Q_{+}^{r} Q_{-}^{s}\right>,
+\end{equation}
+where neutrality condition gives us
+\begin{equation}
+  \label{eq:59}
+  \begin{array}{c}
+    r_{4}=r_{1}+r_{2}+r_{3}-2r-2\\
+    s_{4}=s_{1}+s_{2}+s_{3}-2s-2
+  \end{array}
+\end{equation}
+then 
+\begin{multline}
+  \label{eq:58}
+  \left<\varphi_{1}(0)\varphi_{2}(z)\varphi_{3}(1)\varphi_{4}(\infty)\right>=\left<
+    V_{r_{1},s_{1}}(0) V_{r_{2},s_{2}}(z) V_{r_{3},s_{3}}(1) V_{-r_{4},-s_{4}}(\infty)
+    Q_{+}^{r} Q_{-}^{s}\right>=\\
+  z^{\frac{1}{3}\sum h_{i}-h_{1}-h_{2}}(1-z)^{\frac{1}{3}\sum h_{i}-h_{2}-h_{3}} G(z)
+\end{multline}
+
+The simplest case is when $\varphi_{2}=\varphi_{(2,1)}$, then we need to compute integral
+\begin{multline}
+  \label{eq:60}
+  \left<
+    V_{r_{1},s_{1}}(0) V_{2,1}(z) V_{r_{3},s_{3}}(1) V_{-r_{4},-s_{4}}(\infty)
+    Q_{+}\right>=\\
+  \oint dw \left<     V_{r_{1},s_{1}}(0) V_{2,1}(z) V_{r_{3},s_{3}}(1) V_{-r_{4},-s_{4}}(\infty)
+    V_{+}(w)\right>=\\
+  z^{2\alpha_{2,1}\alpha_{r_{1},s_{1}}}  (1-z)^{2\alpha_{2,1}\alpha_{r_{3},s_{3}}} G(z)
+\end{multline}
+Substitute \eqref{eq:41} and in holomorphic sector we obtain
+\begin{equation}
+  \label{eq:61}
+  \oint dw w^{a}(w-1)^{b}(w-z)^{c},
+\end{equation}
+where
+\begin{equation}
+  \label{eq:62}
+  a=2\alpha_{+}\alpha_{r_{1},s_{1}},\quad b=2\alpha_{+}\alpha_{r_{3},s_{3}}, c=2\alpha_{+}\alpha_{2,1}
+\end{equation}
+
+The difficulty is in choice of integration contour, we need to choose two independent contours which
+will give us two independent solutions of differential equation \eqref{eq:33}.
+
+Two choices of contour \cite{difrancesco1997cft} give integrals
+\begin{equation}
+  \label{eq:63}
+  \begin{array}{ll}
+    I_{1}(a,b,c; z) &= \int_{1}^{\infty} dw w^{a} (w-1)^{b} (w-z)^{c}\\
+    I_{1}(a,b,c; z) &= \int_{0}^{z} dw w^{a} (1-w)^{b} (w-z)^{c}\\
+    &=z^{1+a+b+c}\int_{0}^{1}dw  w^{a}(1-w)^{b}(1-zw)^{c}
+  \end{array}
+\end{equation}
+These integrals can be calculated by power series expansion of terms with $z$, use of integral
+formula for beta-function 
+\begin{equation}
+  \label{eq:64}
+    B(x,y)=\frac{\Gamma(x)\Gamma(y)}{\Gamma(x+y)} = \int_{0}^{1} t^{x-1} (1-t)^{y-1} dt =
+    \int_{0}^{\infty} t^{x-1} (1+t)^{-x-y} dt
+  \end{equation}
+then convert power series to hypergeometric function definition using $\Gamma(t+1)=t\Gamma(t)$
+\begin{equation}  
+  F(\lambda,\mu,\nu; z)=\sum_{k=0}^{\infty}\frac{1}{k!}\frac{(\lambda)_{k}(\mu)_{k}}{(\nu)_{k}}
+  z^{k}, \;\mbox{where}\; (x)_{k}=x(x-1)\dots (x-k+1)
+\end{equation}
+Final result for conformal block is
+\begin{eqnarray}
+  \label{eq:65}
+  I_{1}(a,b,c;z)=\frac{\Gamma(-a-b-c-1)\Gamma(b+1)}{\Gamma(-a-c)} F(-c,-a-b-c-1,-a-c; z)\\
+  I_{2}(a,b,c;z)=z^{1+a+b+c}\frac{\Gamma(a+1)\Gamma(c+1)}{\Gamma(a+c+2)} F(-b,a+1,a+c+2; z)\\
+  G(z,\bar z)=\sum_{i,j=1,2}X_{ij} I_{i}(z) \bar I_{j}(\bar z)
+\end{eqnarray}
+Calculation of coefficients $X_{ij}$ can be made using monodromy properties of correlation function
+around singularities. It is equivalent to operator product expansion of primary fields. Functions
+$I_{1}, I_{2}$ are in correspondence with intermediate fields in OPE for pairs of primary fields in
+four-point function. Different ways to calculate using OPE correspond to different conformal blocks:
+\begin{equation}
+  \label{eq:66}
+  \mathcal{G}(z,\bar z) =
+  \left<\varphi_{1}(z_{1})\varphi_{2}(z_{2})\varphi_{3}(z_{3})\varphi_{4}(z_{4})\right> =
+  \sum_{r,s;\bar r, \bar s}\mathcal{F}_{r,s}(z) \bar{\mathcal{F}}_{\bar r,\bar s}(\bar z)
+\end{equation}
+where $\mathcal{F}_{r,s}$ corresponds to a field $\varphi_{(r,s)}$ in OPE
+\begin{equation}
+  \label{eq:67}
+  \varphi_{(r,s)}\in \varphi_{(r_{1},s_{1})}\times \varphi_{(r_{2},s_{2})}
+\end{equation}
+
+Complete results for four-point functions in minimal model with Coulomb gas representation are
+presented in paper \cite{dotsenko1985four}.
+
+\section{ Лекция 11. Модели с дополнительной симметрией}
+  \begin{itemize}
+  \item Модели Весса-Зумино-Новикова-Виттена
+  \item Алгебры Каца-Муди
+  \item $Z_{N}$-парафермионы
+  \end{itemize}
+\section{Лекция 12. Конформная теория поля, теория Лиувилля и теория струн}
+
+\section{ Лекция 13. Поправки от конечного размера системы и теория с границей}
+
 \section{Заключение}

### 2015-08-03 GeneralOverview/Lectures/groups2014.tex
Lecture notes "Group theory methods in QFT 2014" added, CFT2015 added

\documentclass[a4paper,12pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}
\usepackage{ucs}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{pb-diagram}
\usepackage{multicol}
\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
\pagestyle{plain}

%\usepackage{verbatim} 
\newenvironment{comment}
{\par\noindent{\bf TODO}\\}
{\\\hfill$\scriptstyle\blacksquare$\par}

\newtheorem{statement}{Statement}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{corollary}{Corollary}[theorem]
\theoremstyle{definition}
\newtheorem{mynote}{Замечание}[section]
\theoremstyle{definition}
\newtheorem{definition}{Определение}
\theoremstyle{definition}
\newtheorem{exercise}{Упражнение}
\newtheorem{example}{Пример}

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}

%% \topmargin=-3.5cm
%% \oddsidemargin=-1.5cm
%% \evensidemargin=-1.5cm
%% \textwidth=19cm
%% \textheight=28cm
%% 
\title{Методы теории групп в квантовой теории поля\\
\small{Кафедра физики высоких энергий и элементарных частиц СПбГУ}
}
\author{Антон Назаров\\
  \small{СПбГУ, физический факультет, кафедра физики высоких энергий и элементарных частиц;}\\
  \texttt{antonnaz@gmail.com}
}
\date{Осенний семестр 2014 года}

\begin{document}
\maketitle
\thispagestyle{empty}
\begin{abstract}
  Текст представляет собой конспект лекций курса ``Методы теории групп в квантовой теории поля'' (Теория представлений-2). Лекции читались в осеннем семестре 2014 года в СПбГУ для магистрантов 5 курса (кафедра физики высоких энергий и элементарных частиц). 
\end{abstract}
\tableofcontents

\section{Лекция 1}
\label{sec:lecture-1}

\subsection{Программа курса}
\label{sec:program}
\begin{enumerate}
\item Представления группы Лоренца
\item Метод индуцированных представлений, представления группы Пуанкаре
\item Алгебраический анализ представлений
\item Представления групп Ли
\item Метод орбит, геометрическое квантование
\end{enumerate}

\subsection{Литература}
\bibliographystyle{gost780}
\bibliography{groups}{}

Книга автора курса: \cite{book:10358}, \cite{book:1244385}, книга, с подробным разъяснением
материала первой части курса: \cite{book:855864}, подробный двухтомник для физиков:
\cite{book:130300,book:130301}, хорошая обзорная книга, охватывающая дополнительные разделы:
\cite{book:872634}.

\subsection{Группы и Представления групп}
\label{sec:intro}

\begin{equation}
  \label{eq:1}
  (U\psi,U\varphi)=(\psi,\varphi)
\end{equation}
$U$ -- унитарный линейный оператор. Если же $ (U\psi,U\varphi)=(\psi,\varphi)^{*}$, то $U$ --
антиунитарный, антилинейный.

Пусть $T_{1},T_{2}$ -- преобразования, тогда или
\begin{equation}
  \label{eq:2}
  U(T_{2})U(T_{1})=U(T_{2}T_{1})
\end{equation}
или
\begin{equation}
  \label{eq:2}
  U(T_{2})U(T_{1})=e^{i\varphi(T_{1},T_{2})} U(T_{2}T_{1}).
\end{equation}
Во втором случае представление называется проективным.

Пусть $G$ -- группа, элемент $g\in G$. Обозначим через $D(G,V)$ представление группы $G$ линейными
операторами в линейном пространстве $V$, $D(g)\in GL(V)$. Действие группы на каком-то множестве,
не являющемся линейным пространством будем называть ``реализацией''.

\begin{definition}
  {\it Топологическая группа} -- группа, являющаяся топологическим пространством. 
\end{definition}
\begin{definition}
  {\it Группа Ли} -- группа, являющаяся гладким (аналитическим) многообразием
\end{definition}

{\it Определяющим} называется представление, использующееся для задания группы.

Рассмотрим множество $M$ и отображение $g\in G\to O(g)\in Aut(M)$, т.ч. $O(g_{1}g_{2}^{-1})=O(g_{1})
O^{-1}(g_{2})$. Тогда для функций $f\in Fun(M,k)$, где $k$ -- поле, $k=\mathbb{R}, \mathbb{C}$ --
характеристики 0 (характеристика $p$ -- числа по модулю простого числа $p$), отображения
\begin{equation}
  \label{eq:3}
  \begin{array}{l}
  f(\cdot)\to f(\cdot\; g)\\
  f(\cdot)\to f(g\; \cdot)    
  \end{array}
\end{equation}
задают представления $G$. 
\begin{exercise}
  Проверить, что это действительно представление
\end{exercise}

Пусть $V_{1},V_{2}$ -- линейные пространства и существует отображение $\zeta$:
\begin{equation}
  \label{eq:4}
    \begin{diagram}
    \node{V_{1}}\arrow{s,r}{D_{1}} \arrow{e,t}{\zeta} \node{V_{2}}\arrow{s,r}{D_{2}}\\
    \node{V_{1}}\arrow{e,t}{\zeta} \node{V_{2}}
  \end{diagram}
\end{equation}
Если диаграмма коммутативна, то есть $\forall g, v$ верно $D_{2}(g)\zeta v=\zeta D_{1}(g) v$, тогда
$\zeta$ называется сплетающим оператором представлений $D_{1}, D_{2}$. Если существует обратное
отображение $\zeta^{-1}$, то $\zeta D_{1} \zeta^{-1}=D_{2}$ и представления $D_{1}$ и $D_{2}$
эквивалентны.

\begin{definition}
  {\it Категория} $C$ состоит из объектов категории $Ob(C)$ и отображений -- морфизмов $f\in
  Hom(C)$, $f:a\to b$. Морфизмы должны быть определена композиция $f\cdot g$ и для любого $a\in
  Ob(C)$ должно существовать тождественное отображение $1_{a}:a\to a$, причем $1_{b}\cdot f=f\cdot
  1_{a}$.
\end{definition}

Представления группы образуют категорию, а сплетающие операторы являются морфизмами в ней.

Прямая сумма представлений $D_{1}, D_{2}$:
\begin{equation}
  \label{eq:5}
  \begin{pmatrix}
    D_{1}(g) & 0 \\
    0 & D_{2}(g)
  \end{pmatrix} 
  \begin{pmatrix}
    v_{1}\\ v_{2}
  \end{pmatrix}
\end{equation}
Если
\begin{equation}
  \label{eq:6}
  D(g)=
  \begin{pmatrix}
    D_{1}(g) & C(g) \\
    0 & D_{2}(g)
  \end{pmatrix} 
  \begin{pmatrix}
    v_{1}\\ v_{2}
  \end{pmatrix},
\end{equation}
то $V_{2}$ является инвариантным подпространством, $D_{2}$ -- подпредставлением $D$, а
$D_{\downarrow V_{2}}=D_{2}$ -- ограничение представления $D$ на $V_{2}$. Представление $D$
называется приводимым, так как есть инвариантное подпространство. В случае топологических групп
инвариантное подпространство должно быть замкнутым. Если дополнение инвариантного подпространства
инвариантно, то представление называется вполне приводимым и $D=D_{1}\oplus \dots\oplus D_{n}$ (в
случае конечномерных представлений).

\begin{theorem}
  Всякое унитарное представление вполне приводимо
\end{theorem}

Какие задачи нужно уметь решать в теории представлений:
\begin{enumerate}
\item Находить спектр унитарных представлений группы
\item Раскладывать представления на неприводимые
\item Раскладывать представления группы на представления подгруппы
  $H\subset G,\quad D_{G\downarrow H}=D_{1}(H)\oplus \dots D_{n}(H)$
\item Строить индуцированные представления $D_{H\uparrow G}$
\item Раскладывать тензорное произведение на неприводимые
  $D_{1}\otimes D_{2}=D_{1}'\oplus\dots \oplus D_{n}'$, в теории поля такое разложение описывает
  возможные каналы распада после столкновения двух частиц. 
\end{enumerate}
\begin{definition}
  Алгебра Ли $\gf$ группы Ли $G$ -- это касательное пространство к групповому многообразию. В
  алгебре Ли определена скобка $[\;,\;]$, экспоненциальное отображение задает локальные координаты
  на группе в окрестности единицы: $X\in \gf, \; e^{tX}\in G$, $t$ -- координаты. 
\end{definition}
\begin{definition}
  Присоединенное представление группы $G$ -- это представление на алгебре Ли $\gf$, для $g\in G, \;
  X\in \gf$ задающееся формулой
  \begin{equation}
    \label{eq:7}
    Ad_{g} X=\left.\frac{d}{dt}g e^{tX} g^{-1}\right|_{t=0}
  \end{equation}

\end{definition}

\begin{exercise}
  Проверить, что это -- представление
\end{exercise}

Введем на алгебре $\gf$ скалярное произведение, тогда $\gf^{*}$ -- пространство линейных
функционалов над $\gf$, -- можно отождествить с $\gf$: $(v,\cdot)\equiv v^{*}$. Соответственно,
можно определить коприсоединенное представление по правилу
\begin{equation}
  \label{eq:8}
  (Ad^{*} Y,X)=(Y,Ad^{-1}X)
\end{equation}

\begin{theorem}
  Унитарные представления группы $G$ находятся в однозначном соответствии с орбитами
  коприсоединенного представления $\gf^{*}/G$.
\end{theorem}

\begin{example}
  $G=\mathbb{R}^{n}$ -- группа Ли, $\gf=(\mathbb{R}^{n},[\;,\;]=0)$; орбиты -- точки в
  $\mathbb{R}^{n}$. Пусть $g_{1}\in G,\quad r\in \mathbb{R}^{n}$, тогда
  $D^{r}(g_{1})=e^{i(r,g_{1})}$. Существует представление $\tilde D(g_{1}): e^{i(r,g')}\to
  e^{i(r,g'-g_{1})}$. 
Левое действие $G$ на функциях $f:\mathbb{R}^{n}\to k,\quad D:f(\cdot)\to
  f(g^{-1}\cdot)$ раскладывается на неприводимые представления вида $\tilde D$, что соответствует
  разложению функции $f$ в ряд Фурье. Спектр представлений -- это орбиты коприсоединенного
  представления, то есть каждая точка пространства $\mathbb{R}^{n}$ задает неприводимое представление.
\end{example}

\subsubsection{Индуцированные представления}
\label{sec:induced-reps}

Рассмотрим $f\in Fun(G,k)$. По отношению к действию тривиальной подгруппы ${e}\subset G$ все функции
инвариантны.

Пусть $H\subset G,\; h\in H, g\in G$, рассмотрим функции $f:G\to V$, для которых выполняется
$f(gh)=D(h^{-1})\cdot f(g),\; D(h^{-1})\in D(H,V)$. Назовем пространство таких функций $f\in
Fun(G,H,V)$. Наша задача по $Fun(G,H,V)$ восстанавливать представление группы $G$.

Обозначим через $D^{L}(g)\cdot f=f(g^{-1}\cdot)$ левый сдвиг, а через  $D^{R}(g)\cdot f=f(\cdot
g^{-1})$ -- правый. Тогда
\begin{equation}
  \label{eq:9}
  D^{L}(g)f(g'h)=f(g^{-1}g' h)=D(h^{-1}) f(g^{-1} g')=D(h^{-1})D^{L}(g)f(g')
\end{equation}

Покажем, что $Fun(G,H,V)$ инвариантно по отношению к $D^{L}$. Действие $D^{L}$ на $Fun(G,H,V)$ --
индуцированное представление $D_{H\uparrow G}$. Введем классы эквивалентности $H\backslash
G=\{H\}\cdot g_{x}$, $G/H=\{g_{x}\{H\}\}=X$, $x$ -- класс, $g_{x}$ -- представитель класса.
Рассмотрим функции на классах $\varphi(x)=f(g_{x})$, $f(g\cdot g_{x}h)=D(h^{-1})f(g_{x})$. То есть
если мы определим действие на факторпространстве $D(H)$ на $\varphi$ на $X$, то затем его можно
поднять до представления всей группы.

\section{Лекция 2}
\label{sec:lecture-2}

От функций на группе переходим к функциям на классах смежности. 
\end{document}

### 2015-08-18 GeneralOverview/Lectures/Integrability2015.tex
Started lectures on CFT and integrability

--- 2012-10-19 GeneralOverview/Lectures/CFT-APTU-2011.tex
@@
 
-%\usepackage{verbatim} 
+% \usepackage{verbatim} 
 \newenvironment{comment}
@@
 
-\topmargin=-3.5cm
-\oddsidemargin=-1.5cm
-\evensidemargin=-1.5cm
-\textwidth=19cm
-\textheight=28cm
-
-\title{Конформная теория поля и критические явления\\
-\small{Академический университет, кафедра теоретической физики}
+\title{Конформная инвариантность и интегрируемость в теории поля\\
+  \small{СПбГУ, физический факультет университет, кафедра ФВЭиЭЧ}
 }
 \author{Антон Назаров\\
-  \small{СПбГУ, физический факультет, кафедра физики высоких энергий и элементарных частиц;}\\
-  \small{математико-механический факультет, междисциплинарная лаборатория имени П.Л. Чебышева}\\
+  \small{СПбГУ, физический факультет,}\\
+  \small{ кафедра физики высоких энергий и элементарных частиц;}\\
   \texttt{antonnaz@gmail.com}
 }
-\date{Осенний семестр 2011 года}
+\date{Осенний семестр 2015 года}
+
+\def\barr{\left(\begin{array}}
+\def\earr{\end{array}\right)}
+\def\beq#1{\begin{equation}\label{#1}}
+\def\eeq{\end{equation}}
+\def\ber#1{\begin{eqnarray}\label{#1} &&\nqq}%   left alignment
+\def\eer{\end{eqnarray}}
+
+\newcommand{\bear}[1]{\begin{eqnarray}\label{#1}}
+\newcommand{\ear}{\end{eqnarray}}
+
+\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
+\catcode`\@=11 \@addtoreset{equation}{section}\catcode`\@=12
+\newcommand{\N}{ {\mathbb N} }
+\newcommand{\R}{ {\mathbb R} }
+\newcommand{\SL}{\mathop{\rm sl}\nolimits}
+\newcommand{\SO}{\mathop{\rm so}\nolimits}
+\newcommand{\SP}{\mathop{\rm sp}\nolimits}
+\newcommand{\ts}{\textstyle}
+\newcommand{\ds}{\displaystyle}
+\newcommand{\fn}{\footnote}
+\newcommand{\fnm}{\footnotemark}
+\newcommand{\fnt}{\footnotetext}
 
@@
 \begin{abstract}
-  Текст представляет собой конспект лекций по квантовой теории поля в двух измерениях.
-Лекции читались в осеннем семестре 2010 года и в осеннем семестре 2011 в Академическом университете для магистрантов 6 курса (группа теории конденсированного состояния).
+  Программа курса
 \end{abstract}
@@
 
+\section{Программа курса}
+\label{sec:program}
+
+  \begin{itemize}
+  \item  Скейлинг и конформная инвариантность, критическое поведение, ренормгруппа
+  \item Напоминание про классические статистические модели, связь с теорией поля, квантовые
+    статистические модели, симметрии, теорему Нётер
+  \item Классические интегрируемые системы, L-M пара
+  \item Глобальная конформная инвариантность в произвольном числе измерений
+  \item Тождества Уорда для конформных преобразований
+  \item Двухточечная и трехточечная функции
+  \item Общий вид четырехточечной функции в конформной теории, формфактор, конформные блоки
+  \item Конформная инвариантность в двух измерениях
+  \item Локальная конформная инвариантность
+  \item Алгебра Вирасоро.
+  \item Конформный бутстрап
+  \item Правила слияния, алгебра
+  \item Интегрируемость и интегриуемые деформации двумерной конформной теории поля
+  \item Способ получать интегрируемые системы: анзац Бете
+  \item Конформная инвариантность и конформный бутстрап в теории поля с размерностью больше двух
+  \item Конформная инвариантность в теории Янга-Миллса
+  \item N=4 SYM: конформная инвариантность и другие симметрии
+  \item аномальные размерности в N=4 SYM и интегрируемость
+  \item интегрируемость и AdS/CFT соответствие
+  \end{itemize}
+
 \section{Лекция 1}
-\label{sec:lecture-1}
-
-\subsection{Программа курса}
-\label{sec:program}
-\begin{enumerate}
-\item Введение.
+\label{sec:-1}
+
   \begin{itemize}
-  \item Двумерные модели
-  \item Фазовые переходы, критические индексы
-  \item Универсальность
-  \item Методы квантовой теории поля в статистической физике
+  \item Программа курса
+  \item Литература
+  \item Скейлинг и конформная инвариантность, критическое поведение, ренормгруппа
+  \item Напоминание про классические статистические модели, связь с теорией поля, квантовые
+    статистические модели, симметрии, теорему Нётер
+  \item Классический интегрируемые системы, L-M пара
   \end{itemize}
-\item Решение модели Изинга
-  \begin{itemize}
-  \item Интегрируемость
-  \item Подход Каданова
-  \end{itemize}
-\item Перенормировки, ренормгруппа
-\item Конформная инвариантность
-  \begin{itemize}
-  \item Глобальная конформная инвариантность
-  \item Ограничения на корреляционные функции
-  \item Локальная конформная инвариантность в двух измерениях
-  \item Алгебра Витта и алгебра Вирасоро.
-  \end{itemize}
-\item Конформная теория поля
-  \begin{itemize}
-  \item Примарные и вторичные поля
-  \item Минимальные модели
-  \end{itemize}
-\end{enumerate}
 
@@
 \label{sec:literature}
-В \ref{sec:lecture-1} лекции  мы опираемся на вводные главы книги \cite{difrancesco1997cft}.
-Мы уделяем большое внимание использованию математического аппарата квантовой теории поля в моделях статистической физики.
-При этом мы пользуемся знакомством слушателей с функциональным интегралом.
-Последовательное изложение техники функционального интеграла в статистической физике можно найти в книге А.Н.
-Васильева \cite{vasiliev1976}.
-
-Лекции \ref{sec:lecture-5}, \ref{sec:lecture-6} посвящены  точному решению модели Изинга в двух измерениях.
-Подробно решение  модели Изинга в двух измерениях рассмотрено в книге  \cite{belavin2001lect}, на материале которой и основано изложение в данных лекциях.
-
-В следующих лекциях \ref{sec:lecture-3}, \ref{sec:lecture-4} мы обсуждаем применение ренормгруппы к описанию критического поведения, более подробно и достаточно педагогически этот вопрос рассматривается в книге \cite{ma1980} (\cite{ma2000modern}).
-Исчерпывающую информацию содержит моногорафия \cite{vasiliev1998} (английский вариант \cite{Vasilev:1027193}).
-Лекция \ref{sec:lecture-4} основана на вводной главе обзора \cite{Ravanini:2000st}.
-
-Изложение конформной теории поля в двух измерениях опирается на оригинальную статью \cite{belavin1984ics}, книгу \cite{difrancesco1997cft}, обзор \cite{zamolodchikov1989rus,zamolodchikov1989conformal}, недавно переизданный в виде книги.
-В последних лекциях \ref{sec:lecture-10}, \ref{sec:lecture-11}, \ref{sec:lecture-12} использовались также материалы из обзора \cite{Ginsparg:1988ui}, хотя логика изложения ближе к книге \cite{difrancesco1997cft}.
-Некоторые алгебраические сведения о представлениях алгебры Вирасоро  могут быть найдены в книге \cite{golod2001}.
-
-Дополнительные сведения о приложениях конформной теории поля и ее связи с теорией суперструн можно найти в подробных лекциях \cite{springerlink:10.1134/S1063778810050108} и обзорах \cite{Walton:1999xc}, \cite{gaberdiel2000icf}.
+
+По двумерной конформной теории поля есть толстая книга \cite{difrancesco1997cft}, первые лекции
+следуют ей. Дополнительно можно посмотреть лекции Гинспарга \cite{Ginsparg:1988ui} и книгу
+Замолодчиковых \cite{zamolodchikov1989rus,zamolodchikov1989conformal}. Более кратко основные моменты
+описаны в основополагающей статье \cite{belavin1984ics}. Некоторые алгебраические сведения о
+представлениях алгебры Вирасоро могут быть найдены в книге \cite{golod2001}.
+
+Кое-что об интегрируемых моделях, в том числе, о решении модели Изинга в двух измерениях, можно
+почитать в лекциях Белавина \cite{belavin2001lect}.
+
+Применение ренормгруппы к описанию критического поведения подробно и достаточно педагогически
+рассматривается в книге \cite{ma1980} (\cite{ma2000modern}). Исчерпывающую информацию содержит
+моногорафия \cite{vasiliev1998} (английский вариант \cite{Vasilev:1027193}).
+
+Интегрируемым деформациям двумерной конформной теории поля посвящены лекции Ravanini
+\cite{Ravanini:2000st}.
+
+Дополнительные сведения о приложениях конформной теории поля и ее связи с теорией суперструн можно
+найти в подробных лекциях \cite{springerlink:10.1134/S1063778810050108} и обзорах
+\cite{Walton:1999xc}, \cite{gaberdiel2000icf}.
+
+Анзац Бете рассмотрен в лекциях \cite{faddeev1996algebraic}.
+
+Обзор применения интегрируемых систем в соответствии между N=4 теорий суперсимметричной теорией
+Янга-Миллса (N=4 SYM) и теорией суперструн типа IIB содержится в коллективной работе \cite{ReviewAdSCFT}.
 
@@
 
-Заметим, что систему можно описывать классической статистической механикой (обычной квантовой теорией поля с неограниченным временем) когда корреляционная длина больше характерной длины волны де Бройля.
-Если характерная скорость $v$ (скорость света, скорость Ферми или скорость какого-либо возбуждения), то $\lambda_T=\frac{v\hbar}{k_B T}\sim \beta$.
-То есть классическая статистика применима при больших температурах или вблизи критической точки, если $T_c\neq 0$.
-
-\section{Лекция 2. Двумерная модель Изинга}
-\label{sec:lecture-5}
-
-Займемся решением модели Изинга в двух измерениях \eqref{eq:1}.
-Точного решения для модели с внешним полем до сих пор не найдено.
-Решение же для $h=0$ впервые было получено Онзагером в 1944 году.
-В этой и следующей лекциях излагается решение Вдовиченко, как наиболее короткое и простое.
-Изложение взято из книги \cite{belavin2001lect}.
-Энергия системы в отсутствие внешнего поля дается выражением
-\begin{equation}
-  \label{eq:98}
-  E[\sigma]=-J\sum_{\left<i,j\right>}\sigma_i \sigma_j .
-\end{equation}
-Введем обозначение
-\begin{equation}
-  \label{eq:99}
-  K=J/T.
-\end{equation}
-Статсумма имеет вид
-\begin{equation}
-  \label{eq:100}
-  Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}\sigma_i\sigma_j}
-\end{equation}
-Будем считать, что в наша решетка $\mathcal{L}$ состоит из $N=mn$ узлов.
-Обозначим через $M$ число пар $\left<i,j\right>$.
-$M=2N-n-m$.
-Для простоты будем накладывать тороидальные граничные условия.
-Тогда $M=2N$.
-Введем {\it дуальную решетку $\mathcal{L}^*$}, вершинами которой будут центры граней исходной решетки.
-Нам удобно будет использовать действие в следующем виде:
-\begin{equation}
-  \label{eq:101}
-  Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1+1)}=e^{KM} \sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
-\end{equation}
-
-\subsection{Низкотемпературное и высокотемпературное разложение}
-\label{sec:low-high-temp}
-
-Обозначим выражения, входящие в сумму в последнем уравнении, через $X[\sigma]$:
-\begin{equation}
-  \label{eq:102}
-  X[\sigma]=e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
-\end{equation}
-Заметим, что все состояния можно упорядочить следующим образом:
+Заметим, что систему можно описывать классической статистической механикой (обычной квантовой
+теорией поля с неограниченным временем) когда корреляционная длина больше характерной длины волны де
+Бройля. Если характерная скорость $v$ (скорость света, скорость Ферми или скорость какого-либо
+возбуждения), то $\lambda_T=\frac{v\hbar}{k_B T}\sim \beta$. То есть классическая статистика
+применима при больших температурах или вблизи критической точки. %, если $T_c\neq 0$.
+
+\subsection{Лекция 1. Что такое интегрируемая система?}
+
+Гамильтонова система в $\R^{2n}(p,q)$.\\
+$H = H(p,q)$ - гамильтониан.
+\bear{canon_var}
+\dot{p}_{i} = - \frac{\partial H}{\partial q_{i}}, \quad \dot{q}_{i} = \frac{\partial H}{\partial p_{i}}, \quad i=1,\ldots,n.
+\ear
+\bear{F}
+\dot{F} = \sum^{n}_{i=1} \frac{\partial F}{\partial p_{i}}\dot{p}_{i} + \sum^{n}_{i=1} \frac{\partial F}{\partial q_{i}}\dot{q}_{i} = \sum^{n}_{i=1}\Bigl(\frac{\partial F}{\partial p_{i}}\left( - \frac{H}{\partial q_{i}}\right) + \frac{\partial{F}}{\partial q_{i}}\frac{\partial H}{\partial p_{i}} \Bigr)
+\ear
+Скобка Пуассона определена как:
+\bear{Pois_br}
+\{H,F\} = -\{F,H\}.
+\ear
+Для скобки выполняется тождество Якоби
+\bear{Yakobi_eq}
+\{\{F,H\},G\} + \{\{H,G\},F\} + \{\{G,F\},H\} =0.
+\ear
+$F$ - интеграл движения системы (\ref{canon_var}), если $\{F,H\} \equiv 0$.\\
+$\dot{F} \equiv 0$ - закон сохранения.\\
+
+\textit{Пример.} $\{H,H\}$ = -\{H,H\} = 0 - энергия.\\
+
+Тождество Якоби $\rightarrow$ теорема Пуассона: скобка двух интегралов - интеграл. Интегралы образуют алгебру Ли относительно скобки.\\
+
+Принцип Нетер : интеграл $\leftrightarrow$  симметрия системы.\\
+поток $p^{'}_{i} = -\displaystyle\frac{\partial F}{\partial q_{i}}$, $q^{'}_{i} = \displaystyle\frac{\partial F}{\partial p_{i}}$, $q^{'}_{i} = \displaystyle\frac{\partial q_{i}}{d \tau}$ коммутирует с (\ref{canon_var}).\\
+
+\textit{Определение:}\\
+Гамильтонова система называется интегрируемой по Лиувиллю, если у нее есть $n$ $\left( = \frac 12 \dim \R^{2n} \right)$ независимых интегралов в инволюции (т.е.
+$\{F_{i}, F_{j}\} =0$, для $\forall i,j$).\\
+
+\textit{Пример.} Задача Кеплера
+\[H = \frac12 |p|^{2} - \frac{k}{|q|},\quad p,q \in \R^{3}.\]
+
+Цепочка Тоды (М. Тода $1967$) -  $n$ частиц на прямой
+\bear{Toda_ham}
+H = \frac12 \sum^{n}_{i=1}p^{2}_{i} + \sum^{n-1}_{i=1}e^{q_{i} - q_{i+1}},
+\ear
+где $U(q) = \displaystyle{\sum^{n-1}_{i=1}e^{q_{i} - q_{i+1}}}$ - потенциальная энергия.\\
+Конечная цепочка Тоды: $q_{i} = -\infty$, $q_{n+1} = +\infty$.\\
+Случай $q_{n+1} = q_{1}$ мы не рассматриваем.\\
+
+Введем новые переменные:
+\bear{Flaschka_var}
+a_{j} = -\frac12 p_{j},\quad b_{k} = \frac12 e^{\frac 12 (q_{k} - q_{k+1})}, \quad k = 1,\ldots,n-1,\quad j = 1,\ldots n.
+\ear \textbf{Flasсhka, 1974}.\\
+Тогда уравнения движения
+\bear{eq_motion}
+\dot{q}_{j} =  p_{j}, \quad \dot{p}_{j} = -\frac{\partial U}{\partial q_{j}} = e^{q_{j-1} - q_{j}} - e^{q_{j} - q_{j+1}}
+\ear
+перепишутся как
+\bear{eq_motion_new}
+\dot{a}_{j} = 2(b^{2}_{j} - b^{2}_{j-1}), \quad \dot{b}_{k} = b_{k}(a_{k+1} - a_{k}).
+\ear
+Представление Лакса для цепочки Тоды (Flashka, Мананов 1974):\\
+(\ref{eq_motion_new}) $\Longleftrightarrow$ $\dot{L} = [B, L]$, где
+\bear{matrices}
+B =
+\left( \begin{array}{cccc}
+a_{1}& b_{1} &\ldots & 0\\
+b_{1}& a_{2} &\ddots & \vdots\\
+\vdots & \ddots &\ddots & b_{n-1}\\
+0& \ldots & b_{n-1}  & a_{n}
+\end{array}
+\right), \quad
+L =
+\left( \begin{array}{cccc}
+0 & b_{1} &\ldots & 0\\
+- b_{1} & 0 &\ddots & \vdots\\
+\vdots & \ddots &\ddots & b_{n-1}\\
+0 & \ldots & -b_{n-1}  & 0
+\end{array}
+\right),
+\ear
+Если $b_{i}>0 $, то матрица $B$ - матрица Якоби.\\
+Упражнение: проверить.
+\[[B,L] = BL - LB.\]
+
+\textit{Предложение.}\\
+
+Поток $\dot{L} = [B,L]$ сохраняет спектр  (набор собственных чисел) матрицы $L$
+и, наоборот, изоспектральная деформация $L \rightarrow C(t)LC^{-1}(t)$ описывается $\dot{L} = [B,L]$ для подходящей $B = B(t)$.\\
+
+\textit{Доказательство:}\\
+$C(t)$ - решение уравнения $\dot{C}(t) =  B(t)C(t)$  с начальным условием $C(0) = I$.\\
+$X = C^{-1}(t)L(t)C(t)$,\\
+$\dot{X} = \dot{(C^{-1})}LC + C^{-1}\dot{L}C + C^{-1}L\dot{C} = $
+
+\[\circledast \dot{\left(C^{-1}C\right)} = \dot{C^{-1}}C + C^{-1}\dot{C} = 0 \quad  \Rightarrow \dot{\left(C^{-1}\right)}  = -C^{-1}\dot{C}C^{-1} \circledast\]
+
+$= -C^{-1}\underbrace{\dot{C}C^{-1}}_{B}LC + C^{-1}\dot{L}C + C^{-1}L\underbrace{\dot{C}C^{-1}}_{B}C = C^{-1}\left(\dot{L} + LB -BL\right)C = $\\
+$C^{-1}\underbrace{\left(\dot{L} - [B,L]\right)}_{0}C = 0$ $\Rightarrow$ $\dot{x} = 0$ $\rightarrow$ $L = C(t)L_{0}C^{-1}(t)$, где $L_{0} = const$.\\
+\[\det{(L - \lambda E)} = \det{\left(CL_{0}C^{-1} - \lambda C C^{-1}\right)} = \det{C(L_{0} - \lambda E)C^{-1}} = \det{L_{0} - \lambda E} \]
+- не зависит от  $t$.\\
+
+\textit{Следствие:}\\
+
+$F_{k} = \frac{1}{k} tr{L}^{k}$, при $k=1,2, \ldots, n$, являются интегралами движения цепочки Тоды,\\
+$F_{k} = \displaystyle{frac{1}{k}\sum^{n}_{i=1}\lambda^{k}_{i}}$ - сохраняется.\\
+$F_{1} = a_{1} + \ldots + a_{n} = -\displaystyle\frac12 (p_{1} + \ldots + p_{n})$, где $(p_{1} + \ldots + p_{n})$ - полный импульс.\\
+$F_{2} = \frac12 tr L^{2} = \displaystyle{\frac12 \left(\sum^{n}_{i=1} a^{2}_{i} + \sum^{n-1}_{j=1}b^{k}_{j}\right)} = \displaystyle{\frac12 \left( \frac14 \sum^{n}_{i=1}p^{2}_{i} + 2 \sum^{n-1}_{j=1}\frac14 e^{q_{j} - q_{j+1}}\right)} = \frac14 M$.\\
+$F_{3} = \frac13 L^{3}$,\\
+$F_{4} = \ldots $  - не имеет естественной механической интерпретации.\\
+
+\textit{Теорема.}
+\bear{inv_int}
+\{F_{i},F_{j}\}\equiv 0,
+\ear
+то есть цепочка Тоды интегрируема по Лиувиллю.\\
+
+\textit{Лемма 1.}\\
+
+Матрицы Якоби имеют простой (невырожденный) спектр (собственные значения различны)
+\[\left(L - \lambda E\right)x = 0 \quad \exists !x \quad \Leftrightarrow \qquad\Bigl\{
+                                                                    \begin{array}{ll}
+                                                                      (a_{1} -\lambda)x_{1} + b_{1}x_{1} = 0 \textrm{,} & \Rightarrow x_{2}\textrm{;} \\
+                                                                      b_{1}x_{1} + (a_{2} - \lambda)x_{2} + b_{2}x_{3} = 0 \textrm{,} & \Rightarrow x_{3}\textrm{.}
+                                                                    \end{array} 
+\]
+$x_{2}\ldots x_{n}$ задано однозначно при данном $x_{1}$.\\
+Нормируем собственный вектор $(L - \lambda E)x = 0$, $(x,x) = 1$ и положим $x_{0}$ и $x_{n+1} = 0$.\\
+
+\textit{Лемма 2.}
+
+\bear{lemma2}
+\frac{\partial \lambda}{\partial a_{k}} = x^{2}_{k}, \qquad \frac{\partial \lambda}{\partial b_{j}} = 2x_{j}x_{j+1}.
+\ear
+
+\textit{Доказательство:}\\
+
+Проварьируем $(L - \lambda E)x = 0$:\\
+\[(\delta L - \delta \lambda E)x + (L - \lambda E)\delta x = 0.\]
+Умножим скалярно на $x$ :
+\[\left((\delta L - \delta \lambda E)x,x\right) + \left((L-\lambda E)\delta x,x \right) = 0\]
+\[\left((\delta L - \delta \lambda E)x,x\right) + \left(\delta x, (L-\lambda E)x \right) = 0\]
+$\left(\delta L x,x\right) = \delta \lambda \underbrace{(x,x)}_{1} = \delta \lambda$ $\Rightarrow$ $\delta\lambda = (\delta L x,x)$ $\Rightarrow$ (\ref{lemma2}).\\
+
+Скобка Пуассона в переменных Flaschka.
+\[\{F,G\} = \frac 14 \sum \left(b_{j}\frac{\partial F}{\partial b_{j}} - b_{j-1}\frac{\partial F}{\partial b_{j-1}}\right)\frac{\partial G}{\partial a_{j}} - \ldots (F\leftrightarrow G)\]
+$\lambda$, $\mu$ - два собственных числа $L$, а $x$, $y$ - соответствующие  нормированные собственные вектора.
+\[\{\lambda, \mu\} = \frac 12  \sum^{n}_{j=1}\left(b_{j}x_{j}x_{j+1} - b_{j-1}x_{j-1}x_{j}\right)y^{2}_{j} - (x\leftrightarrow y) =\]
+\[\frac12 \sum^{n}_{j=1} \left(b_{j}(x_{j+1}y_{j} - y_{j+1}x_{j}) + b_{j-1}(x_{j}y_{j-1} - x_{j-1}y_{j}) \right) x_{j}y_{j},\]
+где $W(x,y) = b_{j}(x_{j+1}y_{j} - y_{j+1}x_{j}) $ - дискретный Вронскиан.
+Получим систему разностных дифференциальных уравнений:
+\bear{sys_eqs}\Bigl\{
+    \begin{array}{ll}
+      b_{j-1}x_{j-1} + (a_{j} - \lambda)x_{j} + b_{j}x_{j+1} = 0 \textrm{,} & \Leftarrow (L-\lambda E)x =0\textrm{;} \\
+      b_{j-1}y_{j-1} + (a_{j} - \mu)y_{j} + b_{j}y_{j+1} = 0 \textrm{,} & \Leftarrow (L-\mu E)x =0 \textrm{.}
+    \end{array}
+\ear
+Домножим первое уравнение системы (\ref{sys_eqs}) на $y_{i}$, а второе - на $x_{j}$ и вычтем второе из первого, получим:\\
+$W_{j} - W_{j-1} = (\lambda - \mu)x_{j}y_{j}$, $\lambda = \mu$ $\Rightarrow$ $W_{j} = W_{j-1} = const$.\\
+\[\Rightarrow \{\lambda, \mu\} = \frac 12 \sum^{n}_{j=1} \left(W_{j} + W_{j-1}\right)\left(W_{j}  - W_{j-1}\right) = \frac{1}{2(\lambda - \mu)}\sum^{n}_{j=1}\left(W^{2}_{j} - W^{2}_{j-1}\right) =0.\]
+$\Rightarrow$ $\{F_{k}, F_{l}\} \equiv 0$ $\Rightarrow$  интегрируемость цепочки Тоды.\\
+
+\subsection{Лекция 2.}
+\bear{LP}
+\dot{L} = [B,L]
+\ear
+
+\bear{matrice_L}
+B =
+\left( \begin{array}{cccc}
+a_{1}& b_{1} &\ldots & 0\\
+b_{1}& a_{2} &\ddots & \vdots\\
+\vdots & \ddots &\ddots & b_{n-1}\\
+0& \ldots & b_{n-1}  & a_{n}
+\end{array}
+\right)  - \textrm{матрица Якоби при} b_{i}>0.
+\ear
+
+\textit{Метод обратной задачи (рассеяния).}\\
+
+Идея: Начальные данные $p(0)$ $q(0)$ $\longrightarrow$ $p(t),q(t)$\\
+спектральная задача для $L$ $\longrightarrow$ $\longleftarrow$ обратная спектральная задача\\
+спектральные данные при $t = 0$ $\longrightarrow$ спектральные данные в момент $t$\\
+простая  эволюция спектральных данных.\\
+
+Спектральные данные матриц Якоби.\\
+
+$\lambda_{1},\ldots ,\lambda_{n}$ - спектр $L$, $Lx=\lambda x$, собственные значения нормированных $x$.\\
+Дополнительные спектральные данные - первые компоненты собственных векторов $\xi_{1},\ldots,\xi_{n}>0$.\\
+Матрица $C = \left(
+               \begin{array}{ccc}
+                 \xi_{1} & \ldots & \xi_{n} \\
+                 \ldots & \ldots & \ldots \\
+                 \ldots & \ldots & \ldots \\
+               \end{array}
+             \right)$ - ортогональная (и самосопряженная ?).\\
+
+\[\Rightarrow\quad \xi^{2}_{1} + \ldots + \xi^{2}_{n} = 1,\quad \xi_{i} >0.\]
+
+\bear{Spectr}
+Spec = \{(\lambda,\xi): \quad \lambda_{1}<\lambda_{2}<\ldots<\lambda_{n} \quad \xi^{2}_{1} + \ldots + \xi^{2}_{n} = 1, \xi_{i} >0\}
+\ear
+
+\textit{Теорема.}\\
+
+$S : L(a,b) \rightarrow (\lambda, \xi)$ задает диффеоморфизм  (взаимно однозначное гладкое отображение) между матрицей Якоби и множеством Spec.\\
+
+Обратная задача заключается в восстановлении $L(a,b)$ по $(\lambda, \xi)$.\\
+Есть два решения. \textbf{Мозер 1974}.\\
+
+Функцию Вейля и цепные дроби. Идея восходит к Стильтьетсу.\\
+В резольвенту $R(z) = (zE-L)^{-1}$ и её первый диагональный элемент \\$W(z) = \left(\left(z E- L \right)^{-1} e_{1}, e_{1}\right)$ -  функция Вейля, где $e_{1} = \left(
+                                                                                                                                                     \begin{array}{c}
+                                                                                                                                                       1 \\
+                                                                                                                                                       0 \\
+                                                                                                                                                       \vdots \\
+                                                                                                                                                       0 \\
+                                                                                                                                                     \end{array}
+                                                                                                                                                   \right)$.\\
+\textit{Лемма 1.}
+\bear{Lemma_W}
+W(z) = \sum^{n}_{i=1}\frac {\xi^{2}_{i}}{z - \lambda_{i}}
+\ear
+\textit{Доказательство.}\\
+$LC = C\Lambda$, $\Lambda = \left(
+                                   \begin{array}{ccc}
+                                     \lambda_{1} & \ldots & 0 \\
+                                     \vdots & \vdots & \vdots \\
+                                     0 & \ldots & \lambda_{n} \\
+                                   \end{array}
+                                 \right)$, $C = \left(
+                                             \begin{array}{ccc}
+                                               \xi_{1} & \ldots & \xi_{1} \\
+                                               \vdots & \vdots & \vdots \\
+                                               \ldots & \ldots & \ldots \\
+                                             \end{array}
+                                           \right)$, $C^{T} = C^{-1} = \left(
+                                             \begin{array}{ccc}
+                                               \xi_{1} & \ldots & \ldots \\
+                                               \vdots & \vdots & \vdots \\
+                                               \xi_{n} & \ldots & \ldots \\
+                                             \end{array}
+                                           \right)$,  $L = C\Lambda C^{-1}$.\\
+
+\[W(z) = \left( \left(zCC^{-1}- C\Lambda C^{-1}\right)^{-1}e_{1},e_{1}\right) = \left(C\left( zE- \Lambda\right)^{-1}C^{-1}e_{1},e_{1}\right) =\]
+
+\[= \left(\left(zE- \Lambda\right)^{-1}C^{T}e_{1},C^{T} e_{1}\right) = \sum^{n}_{i=1} \frac{\xi^{2}_{i}}{z- \lambda_{i}}.\]
+
+Так как $(zE - \Lambda)^{-1} = \left(\begin{array}{ccc} (z -\lambda_{1})^{-1} & \ldots & 0 \\
+                                     \vdots & \ddots & \vdots \\
+                                     0 & \ldots & (z -\lambda_{n})^{-1} \\
+\end{array} \right).$\\
+\\
+\textit{Лемма 2. Цепная дробь.}\\
+\bear{fraction}
+W(z) = \frac{1}{z - a_{1} -
+\displaystyle\frac{b^{2}_{1}}{z - a_{2} -
+\displaystyle\frac{b^{2}_{2}}{
+\displaystyle\frac{\cdots}{\displaystyle{\cdots -\frac{b^{2}_{n-1}}{z-a_{n}}}}}}},
+\ear
+здесь $a_{i}$, $b_{j}$ - те же, что и в $L(a,b)$.
+если есть решение для $\xi$ и $\lambda$, то оно находится из этой формулы.\\
+
+\textit{Доказательство.}\\
+
+\bear{Delta_Z}
+\Delta_{j}(z) = \det{\left(\begin{array}{cccc}
+z - a_{j+1}& -b_{j+1} &\ldots & 0\\
+-b_{j+1}& \ddots &\ddots & \vdots\\
+\vdots & \ddots &\ddots & -b_{n-1}\\
+0& \ldots & -b_{n-1}  & z - a_{n}
+\end{array} 
+\right),}
+\ear
+где $j=1,\ldots, n-1$, $\Delta_{n}:=1$, $\Delta_{1} = 0$.\\
+
+Рекуррентное соотношение:
+\[\Delta_{j-1}(z) = (z-a_{j})\Delta_{j}(z) - b^{2}_{j}\Delta_{j+1}(z), \qquad W=\frac{\Delta_{1}}{\Delta_{0}} = \frac{1}{\frac{\Delta_{0}}{\Delta_{1}}}.\]
+\[\displaystyle\frac{\Delta_{j-1}(z)}{\Delta_{j-1}(z)} = z - a_{j} - \displaystyle\frac{b^{2}_{j}}{\Bigl(\frac{\Delta_{j}}{\Delta_{j+1}}\Bigr)}.\]
+(\ref{Delta_Z}) показывает связь цепочки Тоды с ортогональными многочленами и процессом  ортогонализации Грама-Шмидта.\\
+Ортогональные многочлены - результат ортогонализации Грама-Шмидтаю базиса $1$, $z$, $z^{2}$, $\ldots$  по отношению к скалярному произведению
+$\langle f,g \rangle = l(f,g)$.\\
+\[p_{0} = 1, \quad p_{1}(z), \ldots, \quad \langle p_{i},p_{j}\rangle = 0, \quad i\neq j.\]
+Обычно $\langle f,g,\rangle = \int {f(x),g(x)}d\mu(x)$, $\langle x f,g \rangle = \langle f,x g \rangle$.\\
+Ортогональные многочлены удовлетворяют рекуррентному соотношению: 
+\[zp_{i} = p_{i+1} + \alpha_{i}p_{i} + \beta_{i}p_{i-1},\]
+где $\alpha_{i} = \displaystyle\frac{\langle z p_{i}, p_{i}\rangle}{\langle p_{i}, p_{i} \rangle}$, $\beta_{i} = \displaystyle\frac{|p_{i}|^{2}}{|p_{i-1}|^{2}}$.\\
+
+Действительно, $zp_{i} = p_{i+1} + \alpha_{i}p_{i} + \beta_{i}p_{i-1} + \gamma_{i}p_{i-2} + \ldots$\\
+
+Утверждается, что $\gamma_{i} = \delta_{i} = \ldots = 0$\\
+\[\gamma_{i} \langle p_{i-2}, p_{i-2}\rangle = \langle z p_{i}, p_{i-2}\rangle = \langle p_{i}, z p_{i-2}\rangle =0\]
+\[\langle z p_{i}, p_{i}\rangle = \alpha_{i}\langle p_{i},p_{i}\rangle\]
+\[\langle z \underbrace{p_{i}}_{\beta_{i}\langle p_{i-1},p_{i-1}\rangle},p_{i-1}\rangle = \langle p_{i}, zp_{i-1}\rangle = \langle p_{i},p_{i}\rangle   = |p_{i}|^{2}\]
+
+Пусть теперь $(\lambda,\xi) \in Spec$, пространство $V = \R[z] \mod \prod (z - \lambda_{i})$ со скалярным произведением
+$\langle f,g \rangle = \displaystyle\sum^{n}_{i=1}f(\lambda_{i})g(\lambda_{j}) \xi^{2}_{i}$ - интеграл по дискретной мере\\
+Г.-Ш. $P_{0} = 1$, $P_{1},\ldots,P_{n_1}$, $P_{n} = \displaystyle\prod^{n}_{i=1}(z-\lambda_{i}) =0$\\
+
+\textit{Предложение.} \\
+\bear{def_a_b}
+a_{i+1} = \displaystyle\frac{\langle zp_{i},p_{i}\rangle}{\langle p_{i},p_{i} \rangle},\quad b_{j} = \frac{P_{j}}{P_{j-1}},
+\ear 
+где $i=0,\ldots,n-1$, $j=1,\ldots,n-1$, дает решение обратной задачи $(\lambda, \xi)$ $\rightarrow$ $L(z,b)$.\\
+
+\textit{Доказательство.}\\
+
+\textit{Лемма.}\\
+Пусть $a$, $b$ определены (\ref{def_a_b}), тогда $\Rightarrow$ $P_{k} = \det{\left( \begin{array}{cccc}
+z - a_{1}& -b_{1} &\ldots & 0\\
+b_{1}& \ddots &\ddots & \vdots\\
+\vdots & \ddots &\ddots & -b_{k-1}\\
+0& \ldots & -b_{k-1}  & z-a_{k}
+\end{array}\right)} = D_{k}$, \\
+действительно, $D_{a}$ удовлетворяют тому же рекуррентному соотношению
+\[D_{k+1} = (z - a_{k+1})D_{k} - b^{2}_{k}D_{k-1}\]
+из разложения по последнему столбцу с теми же начальными условиями $D_{0} = P_{0} = 1$, $D_{1} = P_{1} = z -a_{1}$.
+В частности,
+\[D_{n} = \det{\left(zE - L\right)} = \prod(z - \lambda_{i}) = P_{n}\]
+$\Rightarrow$ $\lambda_{1},\ldots, \lambda_{k}$  - собственные числа $L(a,b)$.\\
+
+Дополнительный спектр.\\
+
+Нормированные ортогональные многочлены $Q_{i} = \displaystyle\frac{P_{i}}{|P_{i}|} = \left(b_{1}\ldots b_{i}\right)^{-1}P_{i}$.\\
+Рекуррентное соотношение
+\bear{req_pol}
+\frac{b_{i+1}}{b_{i+1}}\frac{P_{i+1}}{b_{1}\ldots b_{i}} + \frac{(a_{i+1} -z)P_{i}}{b_{1}\ldots b_{i}} + \frac{b^{2}_{i}P_{i-1}}{b_{1}\ldots b_{i}} \equiv 0,
+\ear
+учитывая, что $\displaystyle\frac{P_{i+1}}{b_{1}\ldots b_{i}b_{i+1}} = Q_{i+1}$, $\displaystyle\frac{P_{i}}{b_{1}\ldots b_{i}} = Q_{i}$, $\displaystyle\frac{P_{i-1}}{b_{1}\ldots b_{i}} = Q_{i-1}$,
+перепишем  (\ref{req_pol})  как
+\bear{repol2}
+b_{i+1}Q_{i+1} + \left(a_{i+1} -z\right)Q_{i} + b_{i}Q_{i-1} \equiv 0.
+\ear
+Подставим $z= \lambda_{k}$:
+\bear{rec_pol3}
+b_{i+1}Q_{i+1}(\lambda_{k}) + (a_{i+1} - \lambda_{k})Q_{i}(\lambda_{k}) + b_{i}Q_{i-1}(\lambda_{k}) = 0.
+\ear
+$\Rightarrow$ вектор $v_{k} = \xi_{k}\left(Q_{0}(\lambda_{k}),Q_{1}(\lambda_{k}),\ldots,Q_{n-1}(\lambda_{k})\right)$ является собственным нормированным вектором для
+$\lambda = \lambda_{k}$ для $L(a,b)$.
+\bear{Q0}
+Q_{0}(z) =  \frac{1}{\xi^{2}_{1} + \ldots + \xi^{2}_{n}} =1, \qquad v_{k} = (\xi_{k},*,\ldots,*),
+\ear
+то есть $\xi_{k}$ являются первыми компонентами собственного вектора.
+
+\section{Лекция 2}
+\label{sec:-2}
+
+ Лекция 2. Скейлинг в критических моделях
   \begin{itemize}
-\item Основное состояние, все спины направлены в одну сторону, $X[\sigma]=1$
-\item Все спины в одну сторону, один в противоположную.
-Такому состоянию можно сопоставить контур на дуальной решетке вокруг этого спина.
-Тогда каждая сторона контура даст вклад $e^{-2K}$ в $X[\sigma]$.
-  \begin{equation}
-    \label{eq:103}
-    X[\sigma]=\left(e^{-2K}\right)^4
-  \end{equation}
-\item Два спина направлены в противоположную сторону, здесь есть два варианта контура на дуально решетке - если спины рядом, то его длина равна шести, если не рядом - то восьми.
-То есть вклады $\left(e^{-2K}\right)^6$ и $\left(e^{-2K}\right)^8$.
-\item И так далее.
+  \item Процедура Каданова (?)
+  \item Ренормгруппа в решеточных моделях
+  \item Ренормгруппа в непрерывных моделях
+  \item Уравнение Каллана-Симанчика
+  \item Ренормгруппа в двух измерениях
   \end{itemize}
-В итоге мы можем записать все вклады $X[\sigma]$ в виде суммы по всевозможным замкнутым контурам на дуальной решетке. Если ввести обозначение
-\begin{equation}
-  \label{eq:104}
-  \kappa=e^{-2K},
-\end{equation}
-то
-\begin{equation}
-  \label{eq:105}
-  X[\sigma]=\kappa^{l[c]}.
-\end{equation}
-Здесь $l[c]$ --- длина контура $c$ на дуальной решетке, соответствующего состоянию $\sigma$. Тогда для $Z$ получаем
-\begin{equation}
-  \label{eq:106}
-  Z=e^{MK}\sum_c \kappa^{l[c]}. 
-\end{equation}
-Такое выражение называется низкотемпературным разложением, так как оно хорошо сходится при малых температурах ($K>>1$).
-
-Чтобы получить высокотемпературное разложение, воспользуемся тем, что $e^{K\sigma_i\sigma_j}=\ch K+\sigma_i\sigma_j\sh K=\ch K \left(1+\sigma_i\sigma_j \th K\right)$.
-Тогда статсумма записывается в виде
-\begin{equation}
-  \label{eq:80}
-  Z=(\ch K)^M\sum_{[\sigma]}\prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)
-\end{equation}
-Будем раскрывать скобки в произведении, сопоставляя каждому множителю $\sigma_i\sigma_j \th K$ ребро на решетке $\mathcal{L}$, соединяющее вершины $i,j$.
-Заметим, что вклад непрерывного пути, соединяющего вершины $i$ и $k$ пропорционален $(\sigma_i \sigma_{i+1}) (\sigma_{i+1}\sigma_{i+2}) (\sigma_{i+2}\sigma_{i+3})\dots (\sigma_{k-1}\sigma_k)=\sigma_{i}\sigma_k$, где мы пронумеровали вершины вдоль пути.
-То есть вклад от незамкнутого пути дается его концами, а вклад от замкнутого контура всегда равен 1.
-Тогда произведение запишется в виде
-\begin{equation}
-  \label{eq:107}
-  \prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)=1+a_1 \th K +a_2 \th^2 K+\dots,
-\end{equation}
-где $a_k$ дается суммой по всем контурам $c$ (не обязательно замкнутым или односвязным) длины $k$.
-Чтобы вычислить статсумму, нам надо просуммировать такие выражения по всем возможным конфигурациям спинов.
-Заметим, что для любого незамкнутого контура и любой конфигурации найдется другая конфигурация, куда вклад этого контура входит с противоположным знаком (так как спины направлены в другую сторону).
-А вклад замкнутого контура равен $\th^{l[c]}K$ в любой конфигурации, то есть входит в статсумму $2^N$ раз.
-В результате получаем высокотемпературное разложение статсуммы в виде суммы по всем замкнутым контурам на решетке $\mathcal{L}$:
-\begin{equation}
-  \label{eq:108}
-  Z=(\ch K)^M 2^N \sum_c (\th K)^{l[c]}=(\ch K)^M 2^N \sum_c \kappa^{l[c]}.
-\end{equation}
-Здесь мы ввели обозначение $\kappa=\th K$. Это разложение хорошо сходится при $K<<1$.
-
-\subsection{Дуальность Крамерса-Ванье}
-\label{sec:duality}
-
-У нас есть два точных разложения для статсуммы. Сравним их в термодинамическом пределе.
-\begin{equation}
-  \label{eq:109}
-  f=-\lim_{N\to \infty}\frac{\ln Z_N}{N}.
-\end{equation}
-Решетки $\mathcal{L}$ и $\mathcal{L}^*$ отличаются только на границе, поэтому в термодинамическом пределе $M/N\to 2$ и выражения для удельной свободной энергии из высокотемпературного и низкотемпературного разложений должны совпадать.
-Если ввести функцию $\Phi(\kappa)=\lim_{N\to \infty}\frac{1}{N} \ln \left(\sum_c \kappa^{l[c]}\right)$, то свободная энергия запишется в высокотемпературном и низкотемпературном разложениях следующим образом:
-\begin{equation}
-  \label{eq:110}
-  -f(K)=2K+\Phi(e^{-2K})=\ln(2\ch^2 K)+\Phi(\th K)
-\end{equation}
-Это и есть соотношение дуальности {\it Крамерса-Ванье}.
-Если ввести $K^*$ так, что $\th K^*=e^{-2K}$ или $\sh 2K^* \sh 2K=1$, то соотношение дуальности будет связывать теорию при температуре $K$ и $K^*$:
-\begin{equation}
-  \label{eq:111}
-  f(K^*)=f(K)+2K-\ln(2\ch^2 K^*).
-\end{equation}
-Рассмотрим теперь поведение теории в критической точке $K_c$.
-В ней свободная энергия $f(K_c)$ не аналитична.
-Тогда $f$ должна быть не аналитична и при $K^*=K_c$.
-Если предположить, что критическая точка единственна, то мы можем найти ее из требования $K=K^*$, то есть $2K=\ln(2\ch^2 K)$ или
-\begin{equation}
-  \label{eq:112}
-  \sh^2 2K_c=1.
-\end{equation}
-Теперь перейдем к точному решению модели Изинга.
-\section{Лекция 3. Решение Вдовиченко.}
-\label{sec:lecture-6}
-Суть состоит в сведении вычисления статсуммы в высокотемпературном разложении к решению некоторого рекуррентного соотношения.
-Это соотношение записывается в матричном виде и его решение дается следом матрицы, который можно вычислить после преобразования Фурье.
-
-Заметим, что суммирование по замкнутым контурам обозначает, что в каждой вершине сходится четное число ребер.
-Поэтому мы можем перейти от суммирования по замкнутым контурам к суммированию по ``траекториям чернильной точки'' --- замкнутым путям, состоящим из компонент, которые можно нарисовать, не отрывая ручку от бумаги.
-При этом в случае контура с самопересечениями существует несколько способов нарисовать его.
-Например, ``восьмерку'' можно представить как два пути, путь без самопересечения и путь с самопересечением (Смотри рисунок \ref{fig:ising-1}).
-\begin{figure}[h!tb]
-  \centering
-    \includegraphics[width=80mm]{ising1}
-  \caption{Переход от контуров к замкнутым путям}
-  \label{fig:ising-1}
-\end{figure}
-Поэтому такие вклады надо брать с множителем $(-1)^{\nu(\Gamma)}$, где $\nu(\Gamma)$ - число самопересечений пути $\Gamma$.
-Статсумма в высокотемпературном разложении \eqref{eq:108} дается выражением
-\begin{equation}
-  \label{eq:113}
-  Z=(\ch K)^M 2^N\sum_c \kappa^{l[c]}.
-\end{equation}
-Обозначим сумму через $\Sigma=\sum_c \kappa^{l[c]}$. Перепишем её через сумму по путям
-\begin{equation}
-  \label{eq:114}
-  \Sigma=\sum_{\Gamma}(-1)^{\nu(\Gamma)} \kappa^{l[\Gamma]}
-\end{equation}
-Воспользуемся следующим утверждением, доказательство которого оставляется в качестве упражнения.
-Для любой связной замкнутой петли на плоскости с $\nu$ самоперечечениями и полным углом поворота $2\pi(n+1)$ (при ее обходе) верно равенство
-\begin{equation}
-  \label{eq:115}
-  (-1)^{\nu}=(-1)^n.
-\end{equation}
-Сопоставим каждому узлу в пути $\Gamma$ с углом поворота $\varphi$ в нем ($0,\pm \pi/2$) множитель $e^{\frac{i\varphi}{2}}$.
-Тогда после обхода петли полный множитель будет равен $(-1)^{\nu+1}$.
-Для несвязного пути, состоящего из $s$ компонент --- $(-1)^{m+s}$, где $m=\sum \nu$.
-То есть если ввести для пути $\Gamma$ общий множитель $s(\Gamma)$, то $\Sigma$ можно переписать в виде
-\begin{equation}
-  \label{eq:116}
-  \Sigma=\sum_{\Gamma}(-1)^{s(\Gamma)}\prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}\kappa^{l[\Gamma]}
-\end{equation}
-Обозначим через $F^{(1)}_l$ сумму по всем однокомпонентным петлям длины $l$, через $F^{(2)}_l$ --- двухкомпонентным и так далее.
-\begin{equation}
-  \label{eq:117}
-  F^{(1)}_l=\sum_{\Gamma:l[\Gamma]=l} \prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}.
-\end{equation}
-Тогда $F_l^{(2)}$ можно вычислить через $F^{(1)}$:
-\begin{equation}
-  \label{eq:118}
-  F^{(2)}_l=\frac{1}{2!}\sum_{l_1,l_2:l_1+l_2=l} F^{(1)}_{l_1} F^{(1)}_{l_2}
-\end{equation}
-Аналогично
-\begin{equation}
-  \label{eq:119}
-  F^{(s)}_l=\frac{1}{s!}\sum_{l_1,\dots l_s:l_1+\dots+l_s=l} F^{(1)}_{l_1}\dots F^{(1)}_{l_s}
-\end{equation}
-Теперь мы можем выразить $\Sigma$ через $F^{(1)}$:
-\begin{equation}
-  \label{eq:120}
-  \Sigma=\sum_{s=0}^{\infty}\frac{(-1)^s}{s!}\sum_{l_1\dots l_s=1}^{\infty} \kappa^{l_1+\dots+l_s}F^{(1)}_{l_1} \dots F^{(1)}_{l_s}=
-  \sum_{s=0}^{\infty}\frac{(-1)^s}{s!}\left(\sum_{l=1}^{\infty} \kappa^{l}F^{(1)}_{l} \right)^s =\exp\left(-\sum_{l=1}^{\infty} \kappa^l F_l\right)
-\end{equation}
-Петли с числом узлов больше $N$ не дают вклада, так как содержат повторяющиеся ребра и поэтому сократятся (Смотри рисунок \ref{fig:ising-2}).
-\begin{figure}[h!tb]
-  \centering
-  \includegraphics[width=40mm]{ising2}
-  \caption{Сокращение путей с повторяющимися ребрами}
-  \label{fig:ising-2}
-\end{figure}
-Наша задача свелась к вычислению $F_l$.
-Рассмотрим произвольную вершину с координатами $(n,m)$.
-Пронумеруем направления выхода из нее индексом $\nu=1,2,3,4$ против часовой стрелки.
-Обозначим через $W_l (n,m,\nu|n_0,m_0,\nu_0)$ сумму по всем путям длины $l$, соединяющим вершины $(n_0,m_0)$ и $(n,m)$.
-Первый шаг пути в направлении $\nu_0$.
-Учитываются множители $e^{\frac{i\varphi}{2}}$ начиная с узла, следующего за $(n_0,m_0)$ и заканчивая узлом $(n,m)$.
-Последний шаг пути не должен быть в направлении, противоположном $\nu$.
-Тогда $F_l$ можно записать как сумму $W_l(n,m,\nu|n,m,\nu)$ по всем вершинам решетки.
-Каждая петля при этом будет учтена $2l$ раз, так как у нее $l$ возможных вершин начала и два возможных направления.
-\begin{equation}
-  \label{eq:121}
-  F_l=\frac{1}{2l}\sum_{(n,m)\in \mathcal{L}} \sum_{\nu=1,2,3,4} W_l(n,m,\nu|n,m,\nu)
-\end{equation}
-Если мы зафиксируем начальную вершину путей $(n_0,m_0,\nu_0)$, то сумму по путям длины $l+1$ можно выразить через сумму по путям длины $l$.
-В вершину $(n,m,1)$ пути могут входить с направлений $2,3,4$, то есть последний шаг может быть из вершины $(n-1,m)$ в направлении $1$, из вершины $(n,m-1)$ в направлении $2$ и из вершины $(n,m-1)$ в направлении $4$.
-Аналогично для других направлений. Тогда
-\begin{equation}
-  \label{eq:122}
-\begin{array}{l}
-W_{l+1}(n,m,1)=W_l(n-1,m,1)+e^{-i\pi/4} W_l(n,m-1,2)+e^{i\pi/4}W_l(n,m+1,4)\\
-W_{l+1}(n,m,2)=e^{i\pi/4}W_l(n-1,m,1)+W_l(n,m-1,2)+e^{-i\pi/4}W_l(n+1,m,3)\\
-W_{l+1}(n,m,3)=e^{i\pi/4}W_l(n,m-1,2)+W_l(n+1,m,3)+e^{-i\pi/4}W_l(n,m+1,4)\\
-W_{l+1}(n,m,4)=e^{-i\pi/4}W_l(n-1,m,1)+e^{i\pi/4}W_l(n+1,m,3)+W_l(n,m+1,4)\\
-\end{array}
-\end{equation}
-Эти рекуррентные соотношения можно переписать в матричном виде, если ввести матрицу коэффициентов $\Lambda$:
-\begin{equation}
-  \label{eq:124}
-  W_{l+1}(n,m,\nu)=\sum_{p,q,\mu}\Lambda(n,m,\nu|t,u,\mu) W_l(t,u,\mu)
-\end{equation}
-Если вершины $(t,u)$ и $(n,m)$ не являются соседними, то $\Lambda(n,m,\nu|p,q,\mu)=0$.
-Матрица $\Lambda$ не зависит от начала пути.
-$W_{l+1}=\Lambda W_l$, поэтому мы $F_l$ дается следом $l$-той степени $\Lambda$:
-\begin{equation}
-  \label{eq:125}
-  F_l=\frac{1}{2l}\mathrm{Tr} W_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l W_0
-\end{equation}
-Но матрица $W_0=I$ (единичной матрице), поэтому
-\begin{equation}
-  \label{eq:126}
-  F_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l =\frac{1}{2l} \sum_k (\lambda_k)^l,
-\end{equation}
-где $\lambda_k$ - собственные значения матрицы $\Lambda$. Подставим выражение \eqref{eq:126} в формулу \eqref{eq:120}:
-\begin{multline}
-  \label{eq:127}
-  \Sigma=\exp\left(-\sum_{l=0}^{\infty} \frac{\kappa^l}{2l}\mathrm{Tr}\Lambda^l\right)=\exp\left(-\frac{1}{2}\sum_k \sum_{l=0}^{\infty} \frac{(\kappa\lambda_k)^l}{l}\right)=\\
-  \exp\left(\frac{1}{2}\sum_k \ln(1-\kappa\lambda_k)\right)=\prod_k(1-\kappa\lambda_k)^{1/2}=(\det(I-\kappa\Lambda))^{1/2}
-\end{multline}
-Чтобы вычислить детерминант сделаем дискретное преобразование Фурье:
-\begin{equation}
-  \label{eq:128}
-  W_{l}(n,m,\nu)=\sum_{p_1,p_2} \tilde{W}_l(p_1,p_2,\nu) e^{\frac{2\pi i (p_1n+p_2m)}{\sqrt N}}
-\end{equation}
-В импульсном представлении матрица $\Lambda$ будет иметь блочно-диагональный вид
-\begin{equation}
-  \label{eq:129}
-  \Lambda(p_1,p_2,\mu|q_1,q_2,\nu)=\delta_{p,q}\Lambda_p (\mu,\nu),
-\end{equation}
-где
-\begin{equation}
-  \label{eq:130}
-  \Lambda_p(\mu,\nu)=
-  \begin{pmatrix}
-    e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\
-    0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i p_2}{\sqrt N}}
-  \end{pmatrix}
-\end{equation}
-Матрица $I-\kappa\Lambda$ тоже имеет блочный вид с блоками
-\begin{equation}
-  \label{eq:131}
-  \begin{pmatrix}
-    1-\kappa e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\
-    0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1- \kappa e^{-\frac{2\pi i p_2}{\sqrt N}}
-  \end{pmatrix}.
-\end{equation}
-В результате вычисления детерминанта получаем
-\begin{eqnarray}
-  \label{eq:132}
-  \Sigma=\prod_{p_1,p_2} D^{1/2}_{p}\\
-  D_p=(1+\kappa^2)^2 -2\kappa (1-\kappa^2)\left( \cos \frac{2\pi p_1}{\sqrt N} +\cos \frac{2\pi p_2}{\sqrt N}\right)
-\end{eqnarray}
-В результате выражение для статсуммы имеет вид
-\begin{equation}
-  \label{eq:133}
-  Z_N=(2\ch^2 K)^N \prod_{p_1,p_2}D_p^{1/2}.
-\end{equation}
-Исследуем критическое поведение. Вычислим для этого удельную свободную энергию:
-\begin{equation}
-  \label{eq:134}
-  f=-T \lim_{N\to \infty}\frac{\ln Z_N}{N}=-T \lim_{N\to \infty} \left(\ln (2\ch^2 K)+\frac{1}{2N}\sum_p \ln D_p\right)
-\end{equation}
-В термодинамическом пределе $N\to \infty$ значения импульса покрывают всю ось, поэтому сумма переходит в интеграл. Мы сделаем замену переменных
-\begin{eqnarray}
-  \label{eq:135}
-  w_1=\frac{2\pi p_1}{\sqrt N}\quad  w_2=\frac{2\pi p_2}{\sqrt N},\quad w_{1,2}\in [0;2\pi]\\
-  dp_1 dp_2=\frac{N}{(2\pi)^2} dw_1 dw_2
-\end{eqnarray}
-Вспомним, что $\kappa=\th K$, поэтому
-\begin{equation}
-  \label{eq:136}
-  -\ln(2\ch^2 K)=\ln\left(\frac{1-\kappa^2}{2}\right)
-\end{equation}
-Нам будет удобно переписать $D_p$  в виде
-\begin{equation}
-  \label{eq:137}
-  D_p=(\kappa^2+2\kappa -1)^2 +4\kappa (1-\kappa^2) \left(\sin^2 \frac{w_1}{2} +\sin^2 \frac{w_2}{2}\right)
-\end{equation}
-Тогда свободная энергия дается интегралом
-\begin{multline}
-  \label{eq:138}
-  f=T\ln\left(\frac{1-\kappa^2}{2}\right)-\\
-  -\frac{T}{8\pi^2}\int_0^{2\pi}\int_0^{2\pi}\ln\left((\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)\right) dw_1 \;dw_2
-\end{multline}
-В критической точке должна быть расходимость.
-Интеграл может иметь особую точку только при $(\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)=0$.
-Это выражение имеет минимум при $w_1=w_2=0$.
-Тогда при $\kappa^2+2\kappa-1=0$ интеграл расходится, что соответствует критической точке.
-\begin{equation}
-  \label{eq:139}
-  \kappa_c=\sqrt 2 -1
-\end{equation}
-В критической точке основной вклад в интеграл дает окрестность $w_1=w_2=0$, введем
-\begin{equation}
-  \label{eq:140}
-  \epsilon=\kappa-\kappa_c
-\end{equation}
-Тогда около критической точки свободная энергия ведет себя как
-\begin{equation}
-  \label{eq:141}
-  f=g(\epsilon)-\frac{T}{8\pi^2}\int_{0}^{2\pi}\int_0^{2\pi}\ln \left( c\epsilon^2 +A(\epsilon)(w_1^2+w_2^2)\right)dw_1\;dw_2.
-\end{equation}
-Здесь $g(\epsilon), A(\epsilon)$ - регулярные функции. Если взять интеграл, то
-\begin{equation}
-  \label{eq:142}
-  f\approx g_1 (\epsilon)+c\epsilon^2 \ln(\epsilon)
-\end{equation}
-Тогда для теплоемкости имеем
-\begin{equation}
-  \label{eq:143}
-  c\propto \ln|T-T_c|
-\end{equation}
-То есть мы подтвердили, что критический индекс $\alpha=0$ (см.
-таблицу \ref{tab:diagrams}).
-Вычисление других критических индексов также возможно, но сопряжено с техническими трудностями.
-Мы не будем его проделывать, так как в следующих лекциях мы легко сможем вычислить корреляторы из конформной теории поля.
-
-\section{Лекция 4}
-\label{sec:lecture-3}
 
@@
 
-В фиксированной точке ренормгруппы имеет место масштабная инвариантность.
-Вместе с трансляционной и лоренц-инвариантностью она порождает конформную инвариантность, то есть инвариантность относительно преобразований, сохраняющих углы.
-
-\section{Лекция 7. Конформная группа.}
-\label{sec:lecture-7}
-
-Построение Каданова-Вильсона (см.
-лекцию \ref{sec:kadanoff-procedure}) обосновало нам масштабную инвариантность модели Изинга.
-Сейчас мы обсудим, какие ограничения накладывает на теорию конформная инвариантность.
-
-Сперва рассмотрим конформную группу в произвольном числе измерений $d$.
-Метрический тензор обозначим через $g_{\mu\nu},\; \mu,\nu=1,\dots,d$.
-Конформными называются преобразования $x\to x'$, сохраняющие метрический тензор с точностью до масштаба:
+В фиксированной точке ренормгруппы имеет место масштабная инвариантность. Вместе с трансляционной и
+лоренц-инвариантностью она порождает конформную инвариантность, то есть инвариантность относительно
+преобразований, сохраняющих углы.
+
+\section{Лекция 3}
+\label{sec:-3}
+
+  \begin{itemize}
+  \item Конформная группа.
+  \item Инварианты конформных преобразований
+  \item Явный вид конформных преобразований полей в $d\geq 3$.
+  \end{itemize}
+
+Построение Каданова-Вильсона (см. лекцию \ref{sec:kadanoff-procedure}) обосновало нам масштабную
+инвариантность модели Изинга. Сейчас мы обсудим, какие ограничения накладывает на теорию конформная
+инвариантность.
+
+Сперва рассмотрим конформную группу в произвольном числе измерений $d$. Метрический тензор обозначим
+через $g_{\mu\nu},\; \mu,\nu=1,\dots,d$. Конформными называются преобразования $x\to x'$,
+сохраняющие метрический тензор с точностью до масштаба: 
 \begin{equation}
@@
 \end{equation}
-где мы использовали равенства \eqref{eq:147}, \eqref{eq:148}.
-То есть бесследовость тензора энергии-импульса ведет к конформной инвариантности классической теории поля.
-В классической теории поля при наличии трансляционной, вращательной и масштабной инвариантности  тензор энергии-импульса часто можно переопределить так, чтобы он был бесследовым.
-То есть конформная инвариантность следует из трансляционной, вращательной и масштабной.
-В случае двумерной квантовой теории поля общего доказательства нет, но конформная инвариантность наблюдается во множестве моделей.
-
-\section{Лекция 9}
-\label{sec:lecture-9}
+где мы использовали равенства \eqref{eq:147}, \eqref{eq:148}. То есть бесследовость тензора
+энергии-импульса ведет к конформной инвариантности классической теории поля. В классической теории
+поля при наличии трансляционной, вращательной и масштабной инвариантности  тензор энергии-импульса
+часто можно переопределить так, чтобы он был бесследовым. То есть конформная инвариантность следует
+из трансляционной, вращательной и масштабной. В случае двумерной квантовой теории поля общего
+доказательства нет, но конформная инвариантность наблюдается во множестве моделей.
+
+\section{Лекция 4}
+\label{sec:-4}
+
+  \begin{itemize}
+  \item Корреляторы квазипримарных полей
+  \item Тождества Уорда
+  \end{itemize}
 
@@
 \end{equation}
-при любых значениях $x$. В частности $\langle T^{\mu}_{\mu}(0)\rangle=0$, то есть у оператора следа тензора энергии-импульса нулевое матожидание и среднеквадратичное отклонение в основном состоянии.
-
-\section{Лекция 10. Конформная инвариантность в двумерной теории.}
-\label{sec:lecture-10}
-
-В лекции \ref{sec:lecture-7} мы получили общее условие на вид инфинитезимальных конформных преобразований:
+при любых значениях $x$. В частности $\langle T^{\mu}_{\mu}(0)\rangle=0$, то есть у оператора следа
+тензора энергии-импульса нулевое матожидание и среднеквадратичное отклонение в основном состоянии.
+
+\section{Лекция 5}
+\label{sec:-5}
+
+  \begin{itemize}
+  \item Конформная инвариантность в двумерной теории.
+  \item Глобальные конформные преобразования
+  \item Тождества Уорда в двумерной конформной теории
+  \end{itemize}
+
+В лекции \ref{sec:lecture-4} мы получили общее условие на вид инфинитезимальных конформных преобразований:
 \begin{equation}
@@
 
-\section{Лекция 11}
-\label{sec:lecture-11}
+\section{Лекция 6}
+\label{sec:-6}
+
+  \begin{itemize}
+  \item Алгебраическая конструкция двумерной конформной теории поля
+  \item Алгебра локальных полей. Операторное разложение
+  \item Свободный бозон
+  \item Центральный заряд. Алгебра Вирасоро
+  \end{itemize}
 
@@
 
-\section{Лекция 12}
-\label{sec:lecture-12}
-
-\subsection{Конформный предел модели Изинга}
-\label{sec:ising-conformal-limit}
-
-Рассмотрим теорию с центральным зарядом $c=\frac{1}{2}$, $\bar c=c$ и примарными полями с конформными размерностями
-\begin{equation}
-  \label{eq:276}
-  \Phi_{1}: (0,0),\quad \Phi_{2}: \left(\frac{1}{2},\frac{1}{2}\right),\quad \Phi_{3}\left(\frac{1}{16},\frac{1}{16}\right)
-\end{equation}
-Первое из этих полей соответствует единичному оператору.
-
-В модели Изинга $\sigma$ -- параметр порядка. $\langle\sigma\rangle=0$ при большой температуре и $\langle \sigma\rangle\neq 0$ при малой. Как мы знаем,
-\begin{equation}
-  \label{eq:277}
-  \langle \sigma_{n} \sigma_{0}\rangle\sim e^{-\frac{|n|}{\xi}}
-\end{equation}
-Где $\xi$ --- корреляционная длина. $\xi^{-1}$ можно рассматривать как массу в теории. В критической точке $\xi$ расходится и теория становится безмассовой.
-\begin{equation}
-  \label{eq:278}
-  \langle\sigma_{n}\sigma_{0}\rangle\sim\frac{1}{|n|^{d-2+\eta}}
-\end{equation}
-Для оператора энергии верно
-\begin{equation}
-  \label{eq:279}
-  \langle \varepsilon_{n} \varepsilon_{0}\rangle \sim \langle\sigma_{n}\sigma_{n+1}\sigma_{0}\sigma_{1}\rangle\sim\frac{1}{|n|^{\frac{2d-2}{\nu}}}
-\end{equation}
-Это выражение не совсем точное, так как при вычислении $\varepsilon_{n}$ надо брать среднее по всем соседям, но сейчас нам это не очень важно.
-В любом случае коррелятор оператора энергии соответствует четырехточечной функции.
-
-Мы знаем (см. Лекции \ref{sec:lecture-1}, \ref{sec:lecture-5}, \ref{sec:lecture-6}) значения критических индексов в модели Изинга --- $\eta=\frac{1}{4}, \nu=1$. Тогда для двухточечной функции
-\begin{equation}
-  \label{eq:280}
-  \langle \sigma_{n} \sigma_{0} \rangle\sim \frac{1}{|n|^{\frac{1}{4}}} \sim\frac{1}{r^{2\Delta_{\sigma}}},
-\end{equation}
-так как мы помним, что двухточечная функция ведет себя как $\langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle=\frac{C_{12}}{r_{12}^{\Delta_{1}+\Delta_{2}}}$.
-Отсюда $\Delta_{\sigma}=h_{\sigma}+\bar h_{\sigma}=\frac{1}{8}$, $s_{\sigma}=h_{\sigma}-\bar h_{\sigma}=0$, то есть поле $\Phi_{3}$ соответствует спину в модели Изинга.
-
-Для оператора энергии мы видим, что
-\begin{equation}
-  \label{eq:281}
-  \langle\varepsilon_{n}\varepsilon_{0}\rangle\sim \frac{1}{|n|^{2\Delta_{\varepsilon}}},
-\end{equation}
-$\nu=1$, $d-1/\nu=1=\Delta_{\varepsilon}=h_{\varepsilon}+\bar h_{\varepsilon}$, то есть $h_{\varepsilon}=\frac{1}{2}$ и поле $\Phi_{2}$ соответствует оператору энергии в модели Изинга.
-
-\subsection{Свободный фермион}
-\label{sec:free-fermion}
-
-Заметим, что другая простая физическая система с центральным зарядом $(c,\bar c)=\left(\frac{1}{2},\frac{1}{2}\right)$ --- это свободный фермион. Его действие
-\begin{equation}
-  \label{eq:282}
-  S=\frac{1}{2} g \int d^{2}x\Psi^{+}\gamma^{0}\gamma^{\mu}\partial_{\mu}\Psi,
-\end{equation}
-где
-\begin{equation}
-  \label{eq:283}
-  \Psi=
-  \begin{pmatrix}
-    \psi\\ \bar \psi
-  \end{pmatrix}
-\end{equation}
-и для гамма-матриц выполняется
-\begin{equation}
-  \label{eq:284}
-  \gamma^{\mu}\gamma^{n}+\gamma^{\nu}\gamma^{\mu}=2\eta^{\mu\nu},\quad \gamma^{0}=
-  \begin{pmatrix}
-    0 & 1\\
-    1 & 0
-  \end{pmatrix}, \quad
-  \gamma^{1}=
-  \begin{pmatrix}
-    0 & -i\\
-    i & 0
-  \end{pmatrix}
-\end{equation}
-Вводим комплексные координаты \eqref{eq:225} и получаем
-\begin{equation}
-  \label{eq:285}
-  \gamma^{0}(\gamma^{0}\partial_{0}+\gamma^{1}\partial_{1})=2
-  \begin{pmatrix}
-    \bar \partial & 0\\
-    0 & \partial
-  \end{pmatrix}
-\end{equation}
-Тогда действие в компонентах \eqref{eq:283} будет
-\begin{equation}
-  \label{eq:286}
-  S=g\int d^{2}x (\bar \psi \partial \bar \psi + \psi\bar \partial \psi)
-\end{equation}
-Классические уравнения движения
-\begin{eqnarray}
-  \label{eq:287}
-  \partial \bar \psi=0\\
-  \bar \partial \psi=0, 
-\end{eqnarray}
-следовательно $\psi=\psi(z)$ и $\bar \psi=\bar \psi(\bar z)$.
-
-Мы хотим вычислить двухточечные корреляционные функции (пропагаторы).
-Они имеют вид $\langle \psi_i(x)\psi_j(x)\rangle, i,j=1,2$ (в координатах $x_1,x_2$).
-Для этого перепишем действие в матричном виде
-\begin{equation}
-  \label{eq:288}
-  S=\frac{1}{2}\int d^2x d^2 y \psi_i (x) A_{ij}(x,y) \psi_j(y),
-\end{equation}
-где мы ввели ядро
-\begin{equation}
-  \label{eq:289}
-  A_{ij}(x,y)=g \delta(x-y) (\gamma^0 \gamma^{\mu})_{ij} \partial_{\mu}.
-\end{equation}
- Корреляторы можно собрать в матрицу $K_{ij}(x,y)=\langle \psi_i(x)\psi_j(y)\rangle$. Если вычислить гауссов функциональный интеграл, то получается, что
- \begin{equation}
-   \label{eq:290}
-   K_{ij}(x,y)=\left(A^{-1}\right)_{ij}(x,y).
- \end{equation}
-То есть $K$ удовлетворяет следующему уравнению:
-\begin{equation}
-  \label{eq:291}
-  g \delta (x-y) (\gamma^0 \gamma^{\mu})_{ik} \frac{\partial}{\partial x^{\mu}} K_{kj}(x,y)=\delta(x-y)\delta_{ij}
-\end{equation}
-В наших комплексных координатах это уравнение имеет очень простой вид
-\begin{equation}
-  \label{eq:292}
-  2g
-  \begin{pmatrix}
-    \bar \partial & 0\\
-    0 & \partial
-  \end{pmatrix}
-  \begin{pmatrix}
-    \langle \psi(z,\bar z) \psi(w,\bar w) \rangle & \langle\psi(z,\bar z)\bar \psi(w,\bar w) \rangle \\
-    \langle \bar \psi(z,\bar z) \psi(w,\bar w) \rangle & \langle\bar\psi(z,\bar z)\bar \psi(w,\bar w) \rangle \\    
-  \end{pmatrix}=
-  \frac{1}{\pi}
-  \begin{pmatrix}
-    \bar \partial\frac{1}{z-w} & 0\\
-    0 & \partial \frac{1}{\bar z-\bar w}
-  \end{pmatrix}
-\end{equation}
-Решением этого уравнения будут
-\begin{eqnarray}
-  \label{eq:293}
-  \langle \psi(z,\bar z) \psi(w,\bar w) \rangle=\frac{1}{2\pi g} \frac{1}{z-w}\\
-  \langle\bar\psi(z,\bar z) \bar \psi(w,\bar w) \rangle =\frac{1}{2\pi g} \frac{1}{\bar z-\bar w}\\
-  \langle\psi(z,\bar z) \bar \psi(w,\bar w) \rangle =0
-\end{eqnarray}
-Если их продифференцировать, получаем
-\begin{eqnarray}
-  \label{eq:294}
-  \langle \partial_z \psi(z,\bar z) \psi(w,\bar w) \rangle=-\frac{1}{2\pi g} \frac{1}{(z-w)^2}\\
-  \langle \partial_z \psi(z,\bar z) \partial_w \psi(w,\bar w) \rangle=-\frac{1}{\pi g} \frac{1}{(z-w)^3}
-\end{eqnarray}
-То есть имеет место операторное разложение
-\begin{equation}
-  \label{eq:295}
-  \psi(z)\psi(w)\sim \frac{1}{2\pi g} \frac{1}{z-w}
-\end{equation}
-Для компонент тензора энергии-импульса имеем
-\begin{eqnarray}
-  \label{eq:296}
-  T^{\bar z\bar z} =2g\psi\partial \psi\\
-  T^{ z z} =2g\bar \psi\bar\partial \bar \psi\\
-  T^{ z\bar z} =-2g\psi\bar\partial \psi\neq 0
-\end{eqnarray}
-Однако $T^{z\bar z}$ исчезает на классических траекториях, то есть теория является конформной.
-Вводим привычное обозначение и квантуем:
-\begin{equation}
-  \label{eq:297}
-  T(z)=-2\pi T_{zz}=-\pi g :\psi(z) \partial \psi(z):=-\pi g\lim_{w\to z}(\psi(z)\partial \psi(w) -\langle\psi(z) \partial \psi(w)\rangle)
-\end{equation}
-Используем теорему Вика и вычисляем операторное разложение
-\begin{equation}
-  \label{eq:298}
-  T(z) \psi(w)=-\pi g:\psi(z)\partial \psi(z) :\psi(w) \sim \frac{1}{2}\frac{\partial \psi(z)}{z-w} +\frac{1}{2}\frac{\psi(z)}{(z-w)^2} \sim \frac{\frac{1}{2} \psi(w)}{(z-w)^2} +\frac{\partial \psi(w)}{z-w}
-\end{equation}
-Мы видим, что у фермионного поля $\psi$ конформная размерность $h=\frac{1}{2}$.
-
-Теперь аналогично вычисляем операторное разложение $T$ с собой:
-\begin{equation}
-  \label{eq:299}
-  T(z)T(w)=\pi^2 g^2 :\psi(z)\partial \psi(z)::\psi(w)\partial \psi(w): \sim \frac{\frac{1}{4}}{(z-w)^4} +\frac{2T(w)}{(z-w)^2} +\frac{\partial T(w)}{z-w}
-\end{equation}
-Мы видим, что центральный заряд в теории свободного фермиона $c=\frac{1}{2}$.
-
-\section{Лекция 13. Уравнения на корреляционные функции в минимальных моделях}
-\label{sec:lecture-13}
-
-Чтобы окончательно зафиксировать структуру двумерной конформной теории поля введем два дополнительных предположения.
-Во-первых, мы предполагаем, что локальные поля образуют алгебру $\mathcal{A}$ по отношению к операторному разложению \eqref{eq:248}\eqref{eq:249}.
+\section{Лекция 7}
+\label{sec:-7}
+
+  \begin{itemize}
+  \item Классификация минимальных моделей
+  \item Детерминант Каца
+  \item Значения центрального заряда и соответствие с решеточными моделями
+  \end{itemize}
+
+\subsection{Уравнения на корреляционные функции в минимальных моделях}
+\label{sec:null-fields}
+
+Чтобы окончательно зафиксировать структуру двумерной конформной теории поля введем два
+дополнительных предположения. Во-первых, мы предполагаем, что локальные поля образуют алгебру
+$\mathcal{A}$ по отношению к операторному разложению \eqref{eq:248}\eqref{eq:249}.
 
@@
 
-\section{Заключение}
-\label{sec:conclusion}
-
-С момента своего создания в 1984 году двумерная конформная теория поля бурно развивалась и новые результаты не вошли в данный курс.
-В качестве обзора можно предложить книги \cite{difrancesco1997cft}, \cite{schottenloher2008mathematical}.
-Большое развитие получили и решеточные модели, в том числе и строгие математические методы, не связанные напрямую с конформной теорией поля.
-В частности, много приложений нашла эволюция Шрамма-Левнера \cite{schramm2000scaling}, при помощи которой удалось строго показать конформную инвариантность некоторых критических моделей \cite{chelkak2009universality,smirnov2001critical}.
-Надеюсь, что данный курс лекций послужит введением в эти области исследований.
-
-\bibliography{CFT-APTU-2011}{}
+  \begin{itemize}
+  \item Детерминант Каца
+  \item Значения центрального заряда и соответствие с решеточными моделями
+  \end{itemize}
+
+Charges and conformal weights of degenerate fields from Kac table are
+\begin{equation}
+  \label{eq:139}
+  \alpha_{r,s}=\frac{1}{2}(1-r)\alpha_{+}+\frac{1}{2}(1-s)\alpha_{-},\quad h_{r,s}=\frac{(r\kappa-4s)^{2}-(\kappa-4)^{2}}{16\kappa}
+\end{equation}
+So holomorphic and full primary fields are denoted by $\psi_{r,s}(z)\sim V_{\alpha_{r,s}}(z)$ and
+$\psi_{r,s}(z,\bar z)\sim V^{(\alpha_{r,s})}(z,\bar z)$
+
+\section{Лекция 8}
+\label{sec:-8}
+
+  \begin{itemize}
+  \item Интегрируемость и интегриуемые деформации двумерной конформной теории поля
+  \end{itemize}
+
+\section{Лекция 9}
+  \begin{itemize}
+  \item Способ получать интегрируемые системы: анзац Бете
+  \end{itemize}
+\section{Лекция 10}
+  \begin{itemize}
+  \item Анзац Бете: спектр
+  \end{itemize}
+
+\section{Лекция 11}
+  \begin{itemize}
+  \item  Конформная инвариантность и конформный бутстрап в теории поля с размерностью больше двух
+  \end{itemize}
+
+\section{Лекция 12}
+  \begin{itemize}
+  \item Конформная инвариантность в теории Янга-Миллса
+  \end{itemize}
+\section{Лекция 13}
+  \begin{itemize}
+  \item N=4 SYM: конформная инвариантность и другие симметрии
+  \end{itemize}
+\section{Лекция 14}
+  \begin{itemize}
+  \item аномальные размерности в N=4 SYM и интегрируемость
+  \end{itemize}
+
+\section{Лекция 15}
+  \begin{itemize}
+  \item интегрируемость и AdS/CFT соответствие
+  \end{itemize}
+
+\bibliography{integrability}{}
 \bibliographystyle{utphys}

### 2015-10-03 GeneralOverview/Lectures/Integrability2015.tex
Lecture 1 reorganized to match actual lecture

@@
 
-\section{Лекция 1}
+\section{Лекция 1.  11 сентября 2015}
 \label{sec:-1}
@@
   \item Литература
-  \item Скейлинг и конформная инвариантность, критическое поведение, ренормгруппа
-  \item Напоминание про классические статистические модели, связь с теорией поля, квантовые
-    статистические модели, симметрии, теорему Нётер
-  \item Классический интегрируемые системы, L-M пара
+  \item Критические явления
+  \item Решение Вдовиченко двумерной модели Изинга
   \end{itemize}
@@
 ростом зависимости спинов между собой.
+
+\subsection{Критические явления}
+\label{sec:critical-phenomena}
+
+Фазовые переходы характеризуются скачком в макроскопических характеристиках системы. При переходах
+первого рода скачком меняется внутренняя энергия (например, при переходе жидкость-газ). При
+переходах второго рода наблюдается скачок производных макроскопических термодинамических величин
+(теплоемкость, магнитная восприимчивость).  Эта классификация несколько условна (см.
+\cite{ma2000modern,ma1980}), бывают и другие виды фазовых переходов, например, переход
+Костерлица-Таулесса \cite{0022-3719-6-7-010}.
+
+Строго говоря, фазовые переходы бывают только в термодинамическом пределе. Это легко понять для
+систем типа модели Изинга в нулевом поле, где энергия любой конфигурации кратна энергетическому
+масштабу $\epsilon=-J$, а статсумма представляет собой полином от $z=e^{-\beta\epsilon}$. В модели
+Изинга наибольшая энергия $E=2N\epsilon$, $Z$- полином степени $2N$ от $z$ с единичными
+коэффициентами. Корни этого полинома лежат вне положительной вещественной оси и комплексно
+сопряжены. Сингулярности свободной энергии или ее производных могут быть только в корнях, которые
+находятся вне физической области при $N<\infty$. При $N\to \infty$ число корней становится
+бесконечным, они лежат на дугах, которые могут касаться положительной вещественной оси. В этих
+точках поведение термодинамических величин и становится сингулярным.
+
+Нас будут интересовать переходы второго рода. Именно в них имеет место конформная инвариантность. 
+Перечислим основные результаты для модели Изинга в двух измерениях.
+
+Здесь есть один фазовый переход при конечной температуре. 
+Критическая температура
+\begin{equation}
+  \label{eq:27}
+  T_c:\quad \sh \frac{2J}{T_c}=1
+\end{equation}
+При $T>T_c$ спонтанная намагниченность \eqref{eq:7} исчезает. При $T<T_c$ она не равна нулю и
+стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_c$. Это упорядоченная ферромагнитная фаза. Около
+критической точки спонтанная намагниченность ведет себя как 
+\begin{equation}
+  \label{eq:28}
+  M\sim \left|T_c-T\right|^{\frac{1}{8}}
+\end{equation}
+Направление намагниченности определяется тем, куда было направлено внешнее поле до того, как его устремили к $0$.
+
+При подходе к критической точке магнитная восприимчивость \eqref{eq:8} расходится
+\begin{equation}
+  \label{eq:29}
+  \chi=\frac{\partial M}{\partial h}\sim \left|T-T_c \right|^{-\frac{7}{4}}.
+\end{equation}
+Вдали от критической точки корреляторы $\Gamma_c(i)$ убывают экспоненциально с расстоянием.
+Характерная длина убывания $\xi$ называется корреляционной длиной 
+\begin{equation}
+  \label{eq:30}
+  \left<\sigma_i\sigma_j\right>_c\sim e^{-\frac{\left|i-j\right|}{\xi(T)}}\quad \left|i-j\right|>>1.
+\end{equation}
+При $T\to T_c$ корреляционная длина расходится
+\begin{equation}
+  \label{eq:31}
+  \xi(T)\sim \frac{1}{\left|T-T_c\right|}.
+\end{equation}
+Такое поведение характеризует переходы второго рода и наблюдается в критических точках фазовой диаграммы.
+
+Около критической точки система состоит из доменов разной намагниченности. Существуют домены
+всевозможных размеров от шага решетки до корреляционной длины $\xi$. Свободная энергия $F$ получает
+вклады от доменных стенок. Сингулярное поведение возникает из-за вкладов доменов большого размера,
+оно определяется флуктуациями и не может быть правильно учтено в теории среднего поля. Вблизи
+критической температуры $\xi$ больше физических размеров системы. Свободная энергия перестает
+зависеть от $\xi$.
+
+Парная корреляционная функция ведет себя как
+\begin{equation}
+  \label{eq:32}
+  \Gamma(\vec n)\sim \frac{1}{\left|\vec n\right|^{d-2+\eta}}
+\end{equation}
+Поведение термодинамических величин определяется критическими индексами. Перечислим их вместе со
+значениями в двумерной модели Изинга. Эти значения получены из точных решений модели. 
+\begin{table}[h!tb]
+\label{tab:diagrams}
+\noindent  \centering{
+\begin{tabular}{|l|l|l|}
+  \hline
+  Критический  & Термодинамическая & Значение индекса в \\
+  индекс &  величина  & двумерной модели Изинга\\
+  \hline
+  $\alpha$ & $C\sim \frac{1}{\left|T-T_c\right|^{\alpha}}$ & $0$\\
+  $\beta$ & $M\sim \left|T-T_c\right|^{\beta}$ & $\frac{1}{8}$\\
+  $\gamma$ & $\chi\sim \frac{1}{\left|T-T_c\right|^{\gamma}}$ & $\frac{7}{4}$\\
+  $\delta$ & $M\sim h^{\frac{1}{\delta}}$ & $15$ \\
+  $\nu$ & $\xi\sim \frac{1}{\left|T-T_c\right|^{\nu}}$ & $1$\\
+  $\eta$ & $\Gamma(\vec n)\sim \left|\vec n\right|^{2-d-\eta}$ & $\frac{1}{4}$\\
+  \hline
+\end{tabular}
+\caption{Критические индексы и их значения в модели Изинга в 2 измерениях}
+}
+\end{table}
+
+Заметим, что систему можно описывать классической статистической механикой (обычной квантовой
+теорией поля с неограниченным временем) когда корреляционная длина больше характерной длины волны де
+Бройля. Если характерная скорость $v$ (скорость света, скорость Ферми или скорость какого-либо
+возбуждения), то $\lambda_T=\frac{v\hbar}{k_B T}\sim \beta$. То есть классическая статистика
+применима при больших температурах или вблизи критической точки. %, если $T_c\neq 0$.
+
+\subsection{Двумерная модель Изинга}
+\label{sec:ising2d}
+
+Займемся решением модели Изинга в двух измерениях \eqref{eq:1}. Точного решения для модели с внешним
+полем до сих пор не найдено. Решение же для $h=0$ впервые было получено Онзагером в 1944 году. В
+этой и следующей лекциях излагается решение Вдовиченко, как наиболее короткое и простое. Изложение
+взято из книги \cite{belavin2001lect}. 
+Энергия системы в отсутствие внешнего поля дается выражением
+\begin{equation}
+  \label{eq:98}
+  E[\sigma]=-J\sum_{\left<i,j\right>}\sigma_i \sigma_j .
+\end{equation}
+Введем обозначение
+\begin{equation}
+  \label{eq:99}
+  K=J/T.
+\end{equation}
+Статсумма имеет вид
+\begin{equation}
+  \label{eq:100}
+  Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}\sigma_i\sigma_j}
+\end{equation}
+Будем считать, что в наша решетка $\mathcal{L}$ состоит из $N=mn$ узлов. Обозначим через $M$ число
+пар $\left<i,j\right>$. $M=2N-n-m$. Для простоты будем накладывать тороидальные граничные условия.
+Тогда $M=2N$. Введем {\it дуальную решетку $\mathcal{L}^*$}, вершинами которой будут центры граней
+исходной решетки.  
+Нам удобно будет использовать действие в следующем виде:
+\begin{equation}
+  \label{eq:101}
+  Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1+1)}=e^{KM} \sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
+\end{equation}
+
+\subsubsection{Низкотемпературное и высокотемпературное разложение}
+\label{sec:low-high-temp}
+
+Обозначим выражения, входящие в сумму в последнем уравнении, через $X[\sigma]$: 
+\begin{equation}
+  \label{eq:102}
+  X[\sigma]=e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
+\end{equation}
+Заметим, что все состояния можно упорядочить следующим образом:
+\begin{itemize}
+\item Основное состояние, все спины направлены в одну сторону, $X[\sigma]=1$
+\item Все спины в одну сторону, один в противоположную. Такому состоянию можно сопоставить контур на
+  дуальной решетке вокруг этого спина. Тогда каждая сторона контура даст вклад $e^{-2K}$ в
+  $X[\sigma]$. 
+  \begin{equation}
+    \label{eq:103}
+    X[\sigma]=\left(e^{-2K}\right)^4
+  \end{equation}
+\item Два спина направлены в противоположную сторону, здесь есть два варианта контура на дуально
+  решетке - если спины рядом, то его длина равна шести, если не рядом - то восьми. То есть вклады
+  $\left(e^{-2K}\right)^6$ и $\left(e^{-2K}\right)^8$. 
+\item И так далее.
+\end{itemize}
+В итоге мы можем записать все вклады $X[\sigma]$ в виде суммы по всевозможным замкнутым контурам на
+дуальной решетке. Если ввести обозначение 
+\begin{equation}
+  \label{eq:104}
+  \kappa=e^{-2K},
+\end{equation}
+то
+\begin{equation}
+  \label{eq:105}
+  X[\sigma]=\kappa^{l[c]}.
+\end{equation}
+Здесь $l[c]$ --- длина контура $c$ на дуальной решетке, соответствующего состоянию $\sigma$. Тогда
+для $Z$ получаем 
+\begin{equation}
+  \label{eq:106}
+  Z=e^{MK}\sum_c \kappa^{l[c]}. 
+\end{equation}
+Такое выражение называется низкотемпературным разложением, так как оно хорошо сходится при малых
+температурах ($K>>1$).
+
+Чтобы получить высокотемпературное разложение, воспользуемся тем, что $e^{K\sigma_i\sigma_j}=\ch
+K+\sigma_i\sigma_j\sh K=\ch K \left(1+\sigma_i\sigma_j \th K\right)$. Тогда статсумма записывается в
+виде 
+\begin{equation}
+  \label{eq:80}
+  Z=(\ch K)^M\sum_{[\sigma]}\prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)
+\end{equation}
+Будем раскрывать скобки в произведении, сопоставляя каждому множителю $\sigma_i\sigma_j \th K$ ребро
+на решетке $\mathcal{L}$, соединяющее вершины $i,j$. Заметим, что вклад непрерывного пути,
+соединяющего вершины $i$ и $k$ пропорционален $(\sigma_i \sigma_{i+1}) (\sigma_{i+1}\sigma_{i+2})
+(\sigma_{i+2}\sigma_{i+3})\dots (\sigma_{k-1}\sigma_k)=\sigma_{i}\sigma_k$, где мы пронумеровали
+вершины вдоль пути. То есть вклад от незамкнутого пути дается его концами, а вклад от замкнутого
+контура всегда равен 1.  Тогда произведение запишется в виде 
+\begin{equation}
+  \label{eq:107}
+  \prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)=1+a_1 \th K +a_2 \th^2 K+\dots,
+\end{equation}
+где $a_k$ дается суммой по всем контурам $c$ (не обязательно замкнутым или односвязным) длины $k$. 
+Чтобы вычислить статсумму, нам надо просуммировать такие выражения по всем возможным конфигурациям
+спинов. Заметим, что для любого незамкнутого контура и любой конфигурации найдется другая
+конфигурация, куда вклад этого контура входит с противоположным знаком (так как спины направлены в
+другую сторону). А вклад замкнутого контура равен $\th^{l[c]}K$ в любой конфигурации, то есть входит
+в статсумму $2^N$ раз. В результате получаем высокотемпературное разложение статсуммы в виде суммы
+по всем замкнутым контурам на решетке $\mathcal{L}$: 
+\begin{equation}
+  \label{eq:108}
+  Z=(\ch K)^M 2^N \sum_c (\th K)^{l[c]}=(\ch K)^M 2^N \sum_c \kappa^{l[c]}.
+\end{equation}
+Здесь мы ввели обозначение $\kappa=\th K$. Это разложение хорошо сходится при $K<<1$.
+
+\subsubsection{Дуальность Крамерса-Ванье}
+\label{sec:duality}
+
+У нас есть два точных разложения для статсуммы. Сравним их в термодинамическом пределе.
+\begin{equation}
+  \label{eq:109}
+  f=-\lim_{N\to \infty}\frac{\ln Z_N}{N}.
+\end{equation}
+Решетки $\mathcal{L}$ и $\mathcal{L}^*$ отличаются только на границе, поэтому в термодинамическом
+пределе $M/N\to 2$ и выражения для удельной свободной энергии из высокотемпературного и
+низкотемпературного разложений должны совпадать. Если ввести функцию $\Phi(\kappa)=\lim_{N\to
+  \infty}\frac{1}{N} \ln \left(\sum_c \kappa^{l[c]}\right)$, то свободная энергия запишется в
+высокотемпературном и низкотемпературном разложениях следующим образом: 
+\begin{equation}
+  \label{eq:110}
+  -f(K)=2K+\Phi(e^{-2K})=\ln(2\ch^2 K)+\Phi(\th K)
+\end{equation}
+Это и есть соотношение дуальности {\it Крамерса-Ванье}. Если ввести $K^*$ так, что $\th K^*=e^{-2K}$
+или $\sh 2K^* \sh 2K=1$, то соотношение дуальности будет связывать теорию при температуре $K$ и
+$K^*$: 
+\begin{equation}
+  \label{eq:111}
+  f(K^*)=f(K)+2K-\ln(2\ch^2 K^*).
+\end{equation}
+Рассмотрим теперь поведение теории в критической точке $K_c$. В ней свободная энергия $f(K_c)$ не
+аналитична. Тогда $f$ должна быть не аналитична и при $K^*=K_c$. Если предположить, что критическая
+точка единственна, то мы можем найти ее из требования $K=K^*$, то есть $2K=\ln(2\ch^2 K)$ или 
+\begin{equation}
+  \label{eq:112}
+  \sh^2 2K_c=1.
+\end{equation}
+Теперь перейдем к точному решению модели Изинга.
+
+\subsubsection{Решение Вдовиченко.}
+\label{sec:ising-solution}
+Суть состоит в сведении вычисления статсуммы в высокотемпературном разложении к решению некоторого
+рекуррентного соотношения. Это соотношение записывается в матричном виде и его решение дается следом
+матрицы, который можно вычислить после преобразования Фурье.
+
+Заметим, что суммирование по замкнутым контурам обозначает, что в каждой вершине сходится четное
+число ребер. Поэтому мы можем перейти от суммирования по замкнутым контурам к суммированию по
+``траекториям чернильной точки'' --- замкнутым путям, состоящим из компонент, которые можно
+нарисовать, не отрывая ручку от бумаги. При этом в случае контура с самопересечениями существует
+несколько способов нарисовать его. Например, ``восьмерку'' можно представить как два пути, путь без
+самопересечения и путь с самопересечением (Смотри рисунок \ref{fig:ising-1}). 
+\begin{figure}[h!tb]
+  \centering
+    \includegraphics[width=80mm]{ising1}
+  \caption{Переход от контуров к замкнутым путям}
+  \label{fig:ising-1}
+\end{figure}
+Поэтому такие вклады надо брать с множителем $(-1)^{\nu(\Gamma)}$, где $\nu(\Gamma)$ - число
+самопересечений пути $\Gamma$. 
+Статсумма в высокотемпературном разложении \eqref{eq:108} дается выражением 
+\begin{equation}
+  \label{eq:113}
+  Z=(\ch K)^M 2^N\sum_c \kappa^{l[c]}.
+\end{equation}
+Обозначим сумму через $\Sigma=\sum_c \kappa^{l[c]}$. Перепишем её через сумму по путям 
+\begin{equation}
+  \label{eq:114}
+  \Sigma=\sum_{\Gamma}(-1)^{\nu(\Gamma)} \kappa^{l[\Gamma]}
+\end{equation}
+Воспользуемся следующим утверждением, доказательство которого оставляется в качестве упражнения. Для
+любой связной замкнутой петли на плоскости с $\nu$ самоперечечениями и полным углом поворота
+$2\pi(n+1)$ (при ее обходе) верно равенство 
+\begin{equation}
+  \label{eq:115}
+  (-1)^{\nu}=(-1)^n.
+\end{equation}
+Сопоставим каждому узлу в пути $\Gamma$ с углом поворота $\varphi$ в нем ($0,\pm \pi/2$) множитель $e^{\frac{i\varphi}{2}}$.
+Тогда после обхода петли полный множитель будет равен $(-1)^{\nu+1}$.
+Для несвязного пути, состоящего из $s$ компонент --- $(-1)^{m+s}$, где $m=\sum \nu$.
+То есть если ввести для пути $\Gamma$ общий множитель $s(\Gamma)$, то $\Sigma$ можно переписать в виде
+\begin{equation}
+  \label{eq:116}
+  \Sigma=\sum_{\Gamma}(-1)^{s(\Gamma)}\prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}\kappa^{l[\Gamma]}
+\end{equation}
+Обозначим через $F^{(1)}_l$ сумму по всем однокомпонентным петлям длины $l$, через $F^{(2)}_l$ --- двухкомпонентным и так далее.
+\begin{equation}
+  \label{eq:117}
+  F^{(1)}_l=\sum_{\Gamma:l[\Gamma]=l} \prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}.
+\end{equation}
+Тогда $F_l^{(2)}$ можно вычислить через $F^{(1)}$:
+\begin{equation}
+  \label{eq:118}
+  F^{(2)}_l=\frac{1}{2!}\sum_{l_1,l_2:l_1+l_2=l} F^{(1)}_{l_1} F^{(1)}_{l_2}
+\end{equation}
+Аналогично
+\begin{equation}
+  \label{eq:119}
+  F^{(s)}_l=\frac{1}{s!}\sum_{l_1,\dots l_s:l_1+\dots+l_s=l} F^{(1)}_{l_1}\dots F^{(1)}_{l_s}
+\end{equation}
+Теперь мы можем выразить $\Sigma$ через $F^{(1)}$:
+\begin{equation}
+  \label{eq:120}
+  \Sigma=\sum_{s=0}^{\infty}\frac{(-1)^s}{s!}\sum_{l_1\dots l_s=1}^{\infty} \kappa^{l_1+\dots+l_s}F^{(1)}_{l_1} \dots F^{(1)}_{l_s}=
+  \sum_{s=0}^{\infty}\frac{(-1)^s}{s!}\left(\sum_{l=1}^{\infty} \kappa^{l}F^{(1)}_{l} \right)^s =\exp\left(-\sum_{l=1}^{\infty} \kappa^l F_l\right)
+\end{equation}
+Петли с числом узлов больше $N$ не дают вклада, так как содержат повторяющиеся ребра и поэтому сократятся (Смотри рисунок \ref{fig:ising-2}).
+\begin{figure}[h!tb]
+  \centering
+  \includegraphics[width=40mm]{ising2}
+  \caption{Сокращение путей с повторяющимися ребрами}
+  \label{fig:ising-2}
+\end{figure}
+Наша задача свелась к вычислению $F_l$.
+Рассмотрим произвольную вершину с координатами $(n,m)$.
+Пронумеруем направления выхода из нее индексом $\nu=1,2,3,4$ против часовой стрелки.
+Обозначим через $W_l (n,m,\nu|n_0,m_0,\nu_0)$ сумму по всем путям длины $l$, соединяющим вершины $(n_0,m_0)$ и $(n,m)$.
+Первый шаг пути в направлении $\nu_0$.
+Учитываются множители $e^{\frac{i\varphi}{2}}$ начиная с узла, следующего за $(n_0,m_0)$ и заканчивая узлом $(n,m)$.
+Последний шаг пути не должен быть в направлении, противоположном $\nu$.
+Тогда $F_l$ можно записать как сумму $W_l(n,m,\nu|n,m,\nu)$ по всем вершинам решетки.
+Каждая петля при этом будет учтена $2l$ раз, так как у нее $l$ возможных вершин начала и два возможных направления.
+\begin{equation}
+  \label{eq:121}
+  F_l=\frac{1}{2l}\sum_{(n,m)\in \mathcal{L}} \sum_{\nu=1,2,3,4} W_l(n,m,\nu|n,m,\nu)
+\end{equation}
+Если мы зафиксируем начальную вершину путей $(n_0,m_0,\nu_0)$, то сумму по путям длины $l+1$ можно выразить через сумму по путям длины $l$.
+В вершину $(n,m,1)$ пути могут входить с направлений $2,3,4$, то есть последний шаг может быть из вершины $(n-1,m)$ в направлении $1$, из вершины $(n,m-1)$ в направлении $2$ и из вершины $(n,m-1)$ в направлении $4$.
+Аналогично для других направлений. Тогда
+\begin{equation}
+  \label{eq:122}
+\begin{array}{l}
+W_{l+1}(n,m,1)=W_l(n-1,m,1)+e^{-i\pi/4} W_l(n,m-1,2)+e^{i\pi/4}W_l(n,m+1,4)\\
+W_{l+1}(n,m,2)=e^{i\pi/4}W_l(n-1,m,1)+W_l(n,m-1,2)+e^{-i\pi/4}W_l(n+1,m,3)\\
+W_{l+1}(n,m,3)=e^{i\pi/4}W_l(n,m-1,2)+W_l(n+1,m,3)+e^{-i\pi/4}W_l(n,m+1,4)\\
+W_{l+1}(n,m,4)=e^{-i\pi/4}W_l(n-1,m,1)+e^{i\pi/4}W_l(n+1,m,3)+W_l(n,m+1,4)\\
+\end{array}
+\end{equation}
+Эти рекуррентные соотношения можно переписать в матричном виде, если ввести матрицу коэффициентов $\Lambda$:
+\begin{equation}
+  \label{eq:124}
+  W_{l+1}(n,m,\nu)=\sum_{p,q,\mu}\Lambda(n,m,\nu|t,u,\mu) W_l(t,u,\mu)
+\end{equation}
+Если вершины $(t,u)$ и $(n,m)$ не являются соседними, то $\Lambda(n,m,\nu|p,q,\mu)=0$.
+Матрица $\Lambda$ не зависит от начала пути.
+$W_{l+1}=\Lambda W_l$, поэтому мы $F_l$ дается следом $l$-той степени $\Lambda$:
+\begin{equation}
+  \label{eq:125}
+  F_l=\frac{1}{2l}\mathrm{Tr} W_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l W_0
+\end{equation}
+Но матрица $W_0=I$ (единичной матрице), поэтому
+\begin{equation}
+  \label{eq:126}
+  F_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l =\frac{1}{2l} \sum_k (\lambda_k)^l,
+\end{equation}
+где $\lambda_k$ - собственные значения матрицы $\Lambda$. Подставим выражение \eqref{eq:126} в формулу \eqref{eq:120}:
+\begin{multline}
+  \label{eq:127}
+  \Sigma=\exp\left(-\sum_{l=0}^{\infty} \frac{\kappa^l}{2l}\mathrm{Tr}\Lambda^l\right)=\exp\left(-\frac{1}{2}\sum_k \sum_{l=0}^{\infty} \frac{(\kappa\lambda_k)^l}{l}\right)=\\
+  \exp\left(\frac{1}{2}\sum_k \ln(1-\kappa\lambda_k)\right)=\prod_k(1-\kappa\lambda_k)^{1/2}=(\det(I-\kappa\Lambda))^{1/2}
+\end{multline}
+Чтобы вычислить детерминант сделаем дискретное преобразование Фурье:
+\begin{equation}
+  \label{eq:128}
+  W_{l}(n,m,\nu)=\sum_{p_1,p_2} \tilde{W}_l(p_1,p_2,\nu) e^{\frac{2\pi i (p_1n+p_2m)}{\sqrt N}}
+\end{equation}
+В импульсном представлении матрица $\Lambda$ будет иметь блочно-диагональный вид
+\begin{equation}
+  \label{eq:129}
+  \Lambda(p_1,p_2,\mu|q_1,q_2,\nu)=\delta_{p,q}\Lambda_p (\mu,\nu),
+\end{equation}
+где
+\begin{equation}
+  \label{eq:130}
+  \Lambda_p(\mu,\nu)=
+  \begin{pmatrix}
+    e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\
+    e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\
+    0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
+    e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i p_2}{\sqrt N}}
+  \end{pmatrix}
+\end{equation}
+Матрица $I-\kappa\Lambda$ тоже имеет блочный вид с блоками
+\begin{equation}
+  \label{eq:131}
+  \begin{pmatrix}
+    1-\kappa e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\
+    e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\
+    0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
+    e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1- \kappa e^{-\frac{2\pi i p_2}{\sqrt N}}
+  \end{pmatrix}.
+\end{equation}
+В результате вычисления детерминанта получаем
+\begin{eqnarray}
+  \label{eq:132}
+  \Sigma=\prod_{p_1,p_2} D^{1/2}_{p}\\
+  D_p=(1+\kappa^2)^2 -2\kappa (1-\kappa^2)\left( \cos \frac{2\pi p_1}{\sqrt N} +\cos \frac{2\pi p_2}{\sqrt N}\right)
+\end{eqnarray}
+В результате выражение для статсуммы имеет вид
+\begin{equation}
+  \label{eq:133}
+  Z_N=(2\ch^2 K)^N \prod_{p_1,p_2}D_p^{1/2}.
+\end{equation}
+Исследуем критическое поведение. Вычислим для этого удельную свободную энергию:
+\begin{equation}
+  \label{eq:134}
+  f=-T \lim_{N\to \infty}\frac{\ln Z_N}{N}=-T \lim_{N\to \infty} \left(\ln (2\ch^2 K)+\frac{1}{2N}\sum_p \ln D_p\right)
+\end{equation}
+В термодинамическом пределе $N\to \infty$ значения импульса покрывают всю ось, поэтому сумма переходит в интеграл. Мы сделаем замену переменных
+\begin{eqnarray}
+  \label{eq:135}
+  w_1=\frac{2\pi p_1}{\sqrt N}\quad  w_2=\frac{2\pi p_2}{\sqrt N},\quad w_{1,2}\in [0;2\pi]\\
+  dp_1 dp_2=\frac{N}{(2\pi)^2} dw_1 dw_2
+\end{eqnarray}
+Вспомним, что $\kappa=\th K$, поэтому
+\begin{equation}
+  \label{eq:136}
+  -\ln(2\ch^2 K)=\ln\left(\frac{1-\kappa^2}{2}\right)
+\end{equation}
+Нам будет удобно переписать $D_p$  в виде
+\begin{equation}
+  \label{eq:137}
+  D_p=(\kappa^2+2\kappa -1)^2 +4\kappa (1-\kappa^2) \left(\sin^2 \frac{w_1}{2} +\sin^2 \frac{w_2}{2}\right)
+\end{equation}
+Тогда свободная энергия дается интегралом
+\begin{multline}
+  \label{eq:138}
+  f=T\ln\left(\frac{1-\kappa^2}{2}\right)-\\
+  -\frac{T}{8\pi^2}\int_0^{2\pi}\int_0^{2\pi}\ln\left((\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)\right) dw_1 \;dw_2
+\end{multline}
+В критической точке должна быть расходимость.
+Интеграл может иметь особую точку только при $(\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)=0$.
+Это выражение имеет минимум при $w_1=w_2=0$.
+Тогда при $\kappa^2+2\kappa-1=0$ интеграл расходится, что соответствует критической точке.
+\begin{equation}
+  \label{eq:139}
+  \kappa_c=\sqrt 2 -1
+\end{equation}
+В критической точке основной вклад в интеграл дает окрестность $w_1=w_2=0$, введем
+\begin{equation}
+  \label{eq:140}
+  \epsilon=\kappa-\kappa_c
+\end{equation}
+Тогда около критической точки свободная энергия ведет себя как
+\begin{equation}
+  \label{eq:141}
+  f=g(\epsilon)-\frac{T}{8\pi^2}\int_{0}^{2\pi}\int_0^{2\pi}\ln \left( c\epsilon^2 +A(\epsilon)(w_1^2+w_2^2)\right)dw_1\;dw_2.
+\end{equation}
+Здесь $g(\epsilon), A(\epsilon)$ - регулярные функции. Если взять интеграл, то
+\begin{equation}
+  \label{eq:142}
+  f\approx g_1 (\epsilon)+c\epsilon^2 \ln(\epsilon)
+\end{equation}
+Тогда для теплоемкости имеем
+\begin{equation}
+  \label{eq:143}
+  c\propto \ln|T-T_c|
+\end{equation}
+То есть мы подтвердили, что критический индекс $\alpha=0$ (см.
+таблицу \ref{tab:diagrams}).
+Вычисление других критических индексов также возможно, но сопряжено с техническими трудностями.
+Мы не будем его проделывать, так как в следующих лекциях мы легко сможем вычислить корреляторы из конформной теории поля.
+
+\subsection{Лекция 1. Что такое интегрируемая система?}
+
+Гамильтонова система в $\R^{2n}(p,q)$.\\
+$H = H(p,q)$ - гамильтониан.
+\bear{canon_var}
+\dot{p}_{i} = - \frac{\partial H}{\partial q_{i}}, \quad \dot{q}_{i} = \frac{\partial H}{\partial p_{i}}, \quad i=1,\ldots,n.
+\ear
+\bear{F}
+\dot{F} = \sum^{n}_{i=1} \frac{\partial F}{\partial p_{i}}\dot{p}_{i} + \sum^{n}_{i=1} \frac{\partial F}{\partial q_{i}}\dot{q}_{i} = \sum^{n}_{i=1}\Bigl(\frac{\partial F}{\partial p_{i}}\left( - \frac{H}{\partial q_{i}}\right) + \frac{\partial{F}}{\partial q_{i}}\frac{\partial H}{\partial p_{i}} \Bigr)
+\ear
+Скобка Пуассона определена как:
+\bear{Pois_br}
+\{H,F\} = -\{F,H\}.
+\ear
+Для скобки выполняется тождество Якоби
+\bear{Yakobi_eq}
+\{\{F,H\},G\} + \{\{H,G\},F\} + \{\{G,F\},H\} =0.
+\ear
+$F$ - интеграл движения системы (\ref{canon_var}), если $\{F,H\} \equiv 0$.\\
+$\dot{F} \equiv 0$ - закон сохранения.\\
+
+\textit{Пример.} $\{H,H\}$ = -\{H,H\} = 0 - энергия.\\
+
+Тождество Якоби $\rightarrow$ теорема Пуассона: скобка двух интегралов - интеграл. Интегралы образуют алгебру Ли относительно скобки.\\
+
+Принцип Нетер : интеграл $\leftrightarrow$  симметрия системы.\\
+поток $p^{'}_{i} = -\displaystyle\frac{\partial F}{\partial q_{i}}$, $q^{'}_{i} = \displaystyle\frac{\partial F}{\partial p_{i}}$, $q^{'}_{i} = \displaystyle\frac{\partial q_{i}}{d \tau}$ коммутирует с (\ref{canon_var}).\\
+
+\textit{Определение:}\\
+Гамильтонова система называется интегрируемой по Лиувиллю, если у нее есть $n$ $\left( = \frac 12 \dim \R^{2n} \right)$ независимых интегралов в инволюции (т.е.
+$\{F_{i}, F_{j}\} =0$, для $\forall i,j$).\\
+
+\textit{Пример.} Задача Кеплера
+\[H = \frac12 |p|^{2} - \frac{k}{|q|},\quad p,q \in \R^{3}.\]
+
+Цепочка Тоды (М. Тода $1967$) -  $n$ частиц на прямой
+\bear{Toda_ham}
+H = \frac12 \sum^{n}_{i=1}p^{2}_{i} + \sum^{n-1}_{i=1}e^{q_{i} - q_{i+1}},
+\ear
+где $U(q) = \displaystyle{\sum^{n-1}_{i=1}e^{q_{i} - q_{i+1}}}$ - потенциальная энергия.\\
+Конечная цепочка Тоды: $q_{i} = -\infty$, $q_{n+1} = +\infty$.\\
+Случай $q_{n+1} = q_{1}$ мы не рассматриваем.\\
+
+Введем новые переменные:
+\bear{Flaschka_var}
+a_{j} = -\frac12 p_{j},\quad b_{k} = \frac12 e^{\frac 12 (q_{k} - q_{k+1})}, \quad k = 1,\ldots,n-1,\quad j = 1,\ldots n.
+\ear \textbf{Flasсhka, 1974}.\\
+Тогда уравнения движения
+\bear{eq_motion}
+\dot{q}_{j} =  p_{j}, \quad \dot{p}_{j} = -\frac{\partial U}{\partial q_{j}} = e^{q_{j-1} - q_{j}} - e^{q_{j} - q_{j+1}}
+\ear
+перепишутся как
+\bear{eq_motion_new}
+\dot{a}_{j} = 2(b^{2}_{j} - b^{2}_{j-1}), \quad \dot{b}_{k} = b_{k}(a_{k+1} - a_{k}).
+\ear
+Представление Лакса для цепочки Тоды (Flashka, Мананов 1974):\\
+(\ref{eq_motion_new}) $\Longleftrightarrow$ $\dot{L} = [B, L]$, где
+\bear{matrices}
+B =
+\left( \begin{array}{cccc}
+a_{1}& b_{1} &\ldots & 0\\
+b_{1}& a_{2} &\ddots & \vdots\\
+\vdots & \ddots &\ddots & b_{n-1}\\
+0& \ldots & b_{n-1}  & a_{n}
+\end{array}
+\right), \quad
+L =
+\left( \begin{array}{cccc}
+0 & b_{1} &\ldots & 0\\
+- b_{1} & 0 &\ddots & \vdots\\
+\vdots & \ddots &\ddots & b_{n-1}\\
+0 & \ldots & -b_{n-1}  & 0
+\end{array}
+\right),
+\ear
+Если $b_{i}>0 $, то матрица $B$ - матрица Якоби.\\
+Упражнение: проверить.
+\[[B,L] = BL - LB.\]
+
+\textit{Предложение.}\\
+
+Поток $\dot{L} = [B,L]$ сохраняет спектр  (набор собственных чисел) матрицы $L$
+и, наоборот, изоспектральная деформация $L \rightarrow C(t)LC^{-1}(t)$ описывается $\dot{L} = [B,L]$ для подходящей $B = B(t)$.\\
+
+\textit{Доказательство:}\\
+$C(t)$ - решение уравнения $\dot{C}(t) =  B(t)C(t)$  с начальным условием $C(0) = I$.\\
+$X = C^{-1}(t)L(t)C(t)$,\\
+$\dot{X} = \dot{(C^{-1})}LC + C^{-1}\dot{L}C + C^{-1}L\dot{C} = $
+
+\[\circledast \dot{\left(C^{-1}C\right)} = \dot{C^{-1}}C + C^{-1}\dot{C} = 0 \quad  \Rightarrow \dot{\left(C^{-1}\right)}  = -C^{-1}\dot{C}C^{-1} \circledast\]
+
+$= -C^{-1}\underbrace{\dot{C}C^{-1}}_{B}LC + C^{-1}\dot{L}C + C^{-1}L\underbrace{\dot{C}C^{-1}}_{B}C = C^{-1}\left(\dot{L} + LB -BL\right)C = $\\
+$C^{-1}\underbrace{\left(\dot{L} - [B,L]\right)}_{0}C = 0$ $\Rightarrow$ $\dot{x} = 0$ $\rightarrow$ $L = C(t)L_{0}C^{-1}(t)$, где $L_{0} = const$.\\
+\[\det{(L - \lambda E)} = \det{\left(CL_{0}C^{-1} - \lambda C C^{-1}\right)} = \det{C(L_{0} - \lambda E)C^{-1}} = \det{L_{0} - \lambda E} \]
+- не зависит от  $t$.\\
+
+\textit{Следствие:}\\
+
+$F_{k} = \frac{1}{k} tr{L}^{k}$, при $k=1,2, \ldots, n$, являются интегралами движения цепочки Тоды,\\
+$F_{k} = \displaystyle{frac{1}{k}\sum^{n}_{i=1}\lambda^{k}_{i}}$ - сохраняется.\\
+$F_{1} = a_{1} + \ldots + a_{n} = -\displaystyle\frac12 (p_{1} + \ldots + p_{n})$, где $(p_{1} + \ldots + p_{n})$ - полный импульс.\\
+$F_{2} = \frac12 tr L^{2} = \displaystyle{\frac12 \left(\sum^{n}_{i=1} a^{2}_{i} + \sum^{n-1}_{j=1}b^{k}_{j}\right)} = \displaystyle{\frac12 \left( \frac14 \sum^{n}_{i=1}p^{2}_{i} + 2 \sum^{n-1}_{j=1}\frac14 e^{q_{j} - q_{j+1}}\right)} = \frac14 M$.\\
+$F_{3} = \frac13 L^{3}$,\\
+$F_{4} = \ldots $  - не имеет естественной механической интерпретации.\\
+
+\textit{Теорема.}
+\bear{inv_int}
+\{F_{i},F_{j}\}\equiv 0,
+\ear
+то есть цепочка Тоды интегрируема по Лиувиллю.\\
+
+\textit{Лемма 1.}\\
+
+Матрицы Якоби имеют простой (невырожденный) спектр (собственные значения различны)
+\[\left(L - \lambda E\right)x = 0 \quad \exists !x \quad \Leftrightarrow \qquad\Bigl\{
+                                                                    \begin{array}{ll}
+                                                                      (a_{1} -\lambda)x_{1} + b_{1}x_{1} = 0 \textrm{,} & \Rightarrow x_{2}\textrm{;} \\
+                                                                      b_{1}x_{1} + (a_{2} - \lambda)x_{2} + b_{2}x_{3} = 0 \textrm{,} & \Rightarrow x_{3}\textrm{.}
+                                                                    \end{array} 
+\]
+$x_{2}\ldots x_{n}$ задано однозначно при данном $x_{1}$.\\
+Нормируем собственный вектор $(L - \lambda E)x = 0$, $(x,x) = 1$ и положим $x_{0}$ и $x_{n+1} = 0$.\\
+
+\textit{Лемма 2.}
+
+\bear{lemma2}
+\frac{\partial \lambda}{\partial a_{k}} = x^{2}_{k}, \qquad \frac{\partial \lambda}{\partial b_{j}} = 2x_{j}x_{j+1}.
+\ear
+
+\textit{Доказательство:}\\
+
+Проварьируем $(L - \lambda E)x = 0$:\\
+\[(\delta L - \delta \lambda E)x + (L - \lambda E)\delta x = 0.\]
+Умножим скалярно на $x$ :
+\[\left((\delta L - \delta \lambda E)x,x\right) + \left((L-\lambda E)\delta x,x \right) = 0\]
+\[\left((\delta L - \delta \lambda E)x,x\right) + \left(\delta x, (L-\lambda E)x \right) = 0\]
+$\left(\delta L x,x\right) = \delta \lambda \underbrace{(x,x)}_{1} = \delta \lambda$ $\Rightarrow$ $\delta\lambda = (\delta L x,x)$ $\Rightarrow$ (\ref{lemma2}).\\
+
+Скобка Пуассона в переменных Flaschka.
+\[\{F,G\} = \frac 14 \sum \left(b_{j}\frac{\partial F}{\partial b_{j}} - b_{j-1}\frac{\partial F}{\partial b_{j-1}}\right)\frac{\partial G}{\partial a_{j}} - \ldots (F\leftrightarrow G)\]
+$\lambda$, $\mu$ - два собственных числа $L$, а $x$, $y$ - соответствующие  нормированные собственные вектора.
+\[\{\lambda, \mu\} = \frac 12  \sum^{n}_{j=1}\left(b_{j}x_{j}x_{j+1} - b_{j-1}x_{j-1}x_{j}\right)y^{2}_{j} - (x\leftrightarrow y) =\]
+\[\frac12 \sum^{n}_{j=1} \left(b_{j}(x_{j+1}y_{j} - y_{j+1}x_{j}) + b_{j-1}(x_{j}y_{j-1} - x_{j-1}y_{j}) \right) x_{j}y_{j},\]
+где $W(x,y) = b_{j}(x_{j+1}y_{j} - y_{j+1}x_{j}) $ - дискретный Вронскиан.
+Получим систему разностных дифференциальных уравнений:
+\bear{sys_eqs}\Bigl\{
+    \begin{array}{ll}
+      b_{j-1}x_{j-1} + (a_{j} - \lambda)x_{j} + b_{j}x_{j+1} = 0 \textrm{,} & \Leftarrow (L-\lambda E)x =0\textrm{;} \\
+      b_{j-1}y_{j-1} + (a_{j} - \mu)y_{j} + b_{j}y_{j+1} = 0 \textrm{,} & \Leftarrow (L-\mu E)x =0 \textrm{.}
+    \end{array}
+\ear
+Домножим первое уравнение системы (\ref{sys_eqs}) на $y_{i}$, а второе - на $x_{j}$ и вычтем второе из первого, получим:\\
+$W_{j} - W_{j-1} = (\lambda - \mu)x_{j}y_{j}$, $\lambda = \mu$ $\Rightarrow$ $W_{j} = W_{j-1} = const$.\\
+\[\Rightarrow \{\lambda, \mu\} = \frac 12 \sum^{n}_{j=1} \left(W_{j} + W_{j-1}\right)\left(W_{j}  - W_{j-1}\right) = \frac{1}{2(\lambda - \mu)}\sum^{n}_{j=1}\left(W^{2}_{j} - W^{2}_{j-1}\right) =0.\]
+$\Rightarrow$ $\{F_{k}, F_{l}\} \equiv 0$ $\Rightarrow$  интегрируемость цепочки Тоды.\\
+
+\subsection{Лекция 2.}
+\bear{LP}
+\dot{L} = [B,L]
+\ear
+
+\bear{matrice_L}
+B =
+\left( \begin{array}{cccc}
+a_{1}& b_{1} &\ldots & 0\\
+b_{1}& a_{2} &\ddots & \vdots\\
+\vdots & \ddots &\ddots & b_{n-1}\\
+0& \ldots & b_{n-1}  & a_{n}
+\end{array}
+\right)  - \textrm{матрица Якоби при} b_{i}>0.
+\ear
+
+\textit{Метод обратной задачи (рассеяния).}\\
+
+Идея: Начальные данные $p(0)$ $q(0)$ $\longrightarrow$ $p(t),q(t)$\\
+спектральная задача для $L$ $\longrightarrow$ $\longleftarrow$ обратная спектральная задача\\
+спектральные данные при $t = 0$ $\longrightarrow$ спектральные данные в момент $t$\\
+простая  эволюция спектральных данных.\\
+
+Спектральные данные матриц Якоби.\\
+
+$\lambda_{1},\ldots ,\lambda_{n}$ - спектр $L$, $Lx=\lambda x$, собственные значения нормированных $x$.\\
+Дополнительные спектральные данные - первые компоненты собственных векторов $\xi_{1},\ldots,\xi_{n}>0$.\\
+Матрица $C = \left(
+               \begin{array}{ccc}
+                 \xi_{1} & \ldots & \xi_{n} \\
+                 \ldots & \ldots & \ldots \\
+                 \ldots & \ldots & \ldots \\
+               \end{array}
+             \right)$ - ортогональная (и самосопряженная ?).\\
+
+\[\Rightarrow\quad \xi^{2}_{1} + \ldots + \xi^{2}_{n} = 1,\quad \xi_{i} >0.\]
+
+\bear{Spectr}
+Spec = \{(\lambda,\xi): \quad \lambda_{1}<\lambda_{2}<\ldots<\lambda_{n} \quad \xi^{2}_{1} + \ldots + \xi^{2}_{n} = 1, \xi_{i} >0\}
+\ear
+
+\textit{Теорема.}\\
+
+$S : L(a,b) \rightarrow (\lambda, \xi)$ задает диффеоморфизм  (взаимно однозначное гладкое отображение) между матрицей Якоби и множеством Spec.\\
+
+Обратная задача заключается в восстановлении $L(a,b)$ по $(\lambda, \xi)$.\\
+Есть два решения. \textbf{Мозер 1974}.\\
+
+Функцию Вейля и цепные дроби. Идея восходит к Стильтьетсу.\\
+В резольвенту $R(z) = (zE-L)^{-1}$ и её первый диагональный элемент \\$W(z) = \left(\left(z E- L \right)^{-1} e_{1}, e_{1}\right)$ -  функция Вейля, где $e_{1} = \left(
+                                                                                                                                                     \begin{array}{c}
+                                                                                                                                                       1 \\
+                                                                                                                                                       0 \\
+                                                                                                                                                       \vdots \\
+                                                                                                                                                       0 \\
+                                                                                                                                                     \end{array}
+                                                                                                                                                   \right)$.\\
+\textit{Лемма 1.}
+\bear{Lemma_W}
+W(z) = \sum^{n}_{i=1}\frac {\xi^{2}_{i}}{z - \lambda_{i}}
+\ear
+\textit{Доказательство.}\\
+$LC = C\Lambda$, $\Lambda = \left(
+                                   \begin{array}{ccc}
+                                     \lambda_{1} & \ldots & 0 \\
+                                     \vdots & \vdots & \vdots \\
+                                     0 & \ldots & \lambda_{n} \\
+                                   \end{array}
+                                 \right)$, $C = \left(
+                                             \begin{array}{ccc}
+                                               \xi_{1} & \ldots & \xi_{1} \\
+                                               \vdots & \vdots & \vdots \\
+                                               \ldots & \ldots & \ldots \\
+                                             \end{array}
+                                           \right)$, $C^{T} = C^{-1} = \left(
+                                             \begin{array}{ccc}
+                                               \xi_{1} & \ldots & \ldots \\
+                                               \vdots & \vdots & \vdots \\
+                                               \xi_{n} & \ldots & \ldots \\
+                                             \end{array}
+                                           \right)$,  $L = C\Lambda C^{-1}$.\\
+
+\[W(z) = \left( \left(zCC^{-1}- C\Lambda C^{-1}\right)^{-1}e_{1},e_{1}\right) = \left(C\left( zE- \Lambda\right)^{-1}C^{-1}e_{1},e_{1}\right) =\]
+
+\[= \left(\left(zE- \Lambda\right)^{-1}C^{T}e_{1},C^{T} e_{1}\right) = \sum^{n}_{i=1} \frac{\xi^{2}_{i}}{z- \lambda_{i}}.\]
+
+Так как $(zE - \Lambda)^{-1} = \left(\begin{array}{ccc} (z -\lambda_{1})^{-1} & \ldots & 0 \\
+                                     \vdots & \ddots & \vdots \\
+                                     0 & \ldots & (z -\lambda_{n})^{-1} \\
+\end{array} \right).$\\
+\\
+\textit{Лемма 2. Цепная дробь.}\\
+\bear{fraction}
+W(z) = \frac{1}{z - a_{1} -
+\displaystyle\frac{b^{2}_{1}}{z - a_{2} -
+\displaystyle\frac{b^{2}_{2}}{
+\displaystyle\frac{\cdots}{\displaystyle{\cdots -\frac{b^{2}_{n-1}}{z-a_{n}}}}}}},
+\ear
+здесь $a_{i}$, $b_{j}$ - те же, что и в $L(a,b)$.
+если есть решение для $\xi$ и $\lambda$, то оно находится из этой формулы.\\
+
+\textit{Доказательство.}\\
+
+\bear{Delta_Z}
+\Delta_{j}(z) = \det{\left(\begin{array}{cccc}
+z - a_{j+1}& -b_{j+1} &\ldots & 0\\
+-b_{j+1}& \ddots &\ddots & \vdots\\
+\vdots & \ddots &\ddots & -b_{n-1}\\
+0& \ldots & -b_{n-1}  & z - a_{n}
+\end{array} 
+\right),}
+\ear
+где $j=1,\ldots, n-1$, $\Delta_{n}:=1$, $\Delta_{1} = 0$.\\
+
+Рекуррентное соотношение:
+\[\Delta_{j-1}(z) = (z-a_{j})\Delta_{j}(z) - b^{2}_{j}\Delta_{j+1}(z), \qquad W=\frac{\Delta_{1}}{\Delta_{0}} = \frac{1}{\frac{\Delta_{0}}{\Delta_{1}}}.\]
+\[\displaystyle\frac{\Delta_{j-1}(z)}{\Delta_{j-1}(z)} = z - a_{j} - \displaystyle\frac{b^{2}_{j}}{\Bigl(\frac{\Delta_{j}}{\Delta_{j+1}}\Bigr)}.\]
+(\ref{Delta_Z}) показывает связь цепочки Тоды с ортогональными многочленами и процессом  ортогонализации Грама-Шмидта.\\
+Ортогональные многочлены - результат ортогонализации Грама-Шмидтаю базиса $1$, $z$, $z^{2}$, $\ldots$  по отношению к скалярному произведению
+$\langle f,g \rangle = l(f,g)$.\\
+\[p_{0} = 1, \quad p_{1}(z), \ldots, \quad \langle p_{i},p_{j}\rangle = 0, \quad i\neq j.\]
+Обычно $\langle f,g,\rangle = \int {f(x),g(x)}d\mu(x)$, $\langle x f,g \rangle = \langle f,x g \rangle$.\\
+Ортогональные многочлены удовлетворяют рекуррентному соотношению: 
+\[zp_{i} = p_{i+1} + \alpha_{i}p_{i} + \beta_{i}p_{i-1},\]
+где $\alpha_{i} = \displaystyle\frac{\langle z p_{i}, p_{i}\rangle}{\langle p_{i}, p_{i} \rangle}$, $\beta_{i} = \displaystyle\frac{|p_{i}|^{2}}{|p_{i-1}|^{2}}$.\\
+
+Действительно, $zp_{i} = p_{i+1} + \alpha_{i}p_{i} + \beta_{i}p_{i-1} + \gamma_{i}p_{i-2} + \ldots$\\
+
+Утверждается, что $\gamma_{i} = \delta_{i} = \ldots = 0$\\
+\[\gamma_{i} \langle p_{i-2}, p_{i-2}\rangle = \langle z p_{i}, p_{i-2}\rangle = \langle p_{i}, z p_{i-2}\rangle =0\]
+\[\langle z p_{i}, p_{i}\rangle = \alpha_{i}\langle p_{i},p_{i}\rangle\]
+\[\langle z \underbrace{p_{i}}_{\beta_{i}\langle p_{i-1},p_{i-1}\rangle},p_{i-1}\rangle = \langle p_{i}, zp_{i-1}\rangle = \langle p_{i},p_{i}\rangle   = |p_{i}|^{2}\]
+
+Пусть теперь $(\lambda,\xi) \in Spec$, пространство $V = \R[z] \mod \prod (z - \lambda_{i})$ со скалярным произведением
+$\langle f,g \rangle = \displaystyle\sum^{n}_{i=1}f(\lambda_{i})g(\lambda_{j}) \xi^{2}_{i}$ - интеграл по дискретной мере\\
+Г.-Ш. $P_{0} = 1$, $P_{1},\ldots,P_{n_1}$, $P_{n} = \displaystyle\prod^{n}_{i=1}(z-\lambda_{i}) =0$\\
+
+\textit{Предложение.} \\
+\bear{def_a_b}
+a_{i+1} = \displaystyle\frac{\langle zp_{i},p_{i}\rangle}{\langle p_{i},p_{i} \rangle},\quad b_{j} = \frac{P_{j}}{P_{j-1}},
+\ear 
+где $i=0,\ldots,n-1$, $j=1,\ldots,n-1$, дает решение обратной задачи $(\lambda, \xi)$ $\rightarrow$ $L(z,b)$.\\
+
+\textit{Доказательство.}\\
+
+\textit{Лемма.}\\
+Пусть $a$, $b$ определены (\ref{def_a_b}), тогда $\Rightarrow$ $P_{k} = \det{\left( \begin{array}{cccc}
+z - a_{1}& -b_{1} &\ldots & 0\\
+b_{1}& \ddots &\ddots & \vdots\\
+\vdots & \ddots &\ddots & -b_{k-1}\\
+0& \ldots & -b_{k-1}  & z-a_{k}
+\end{array}\right)} = D_{k}$, \\
+действительно, $D_{a}$ удовлетворяют тому же рекуррентному соотношению
+\[D_{k+1} = (z - a_{k+1})D_{k} - b^{2}_{k}D_{k-1}\]
+из разложения по последнему столбцу с теми же начальными условиями $D_{0} = P_{0} = 1$, $D_{1} = P_{1} = z -a_{1}$.
+В частности,
+\[D_{n} = \det{\left(zE - L\right)} = \prod(z - \lambda_{i}) = P_{n}\]
+$\Rightarrow$ $\lambda_{1},\ldots, \lambda_{k}$  - собственные числа $L(a,b)$.\\
+
+Дополнительный спектр.\\
+
+Нормированные ортогональные многочлены $Q_{i} = \displaystyle\frac{P_{i}}{|P_{i}|} = \left(b_{1}\ldots b_{i}\right)^{-1}P_{i}$.\\
+Рекуррентное соотношение
+\bear{req_pol}
+\frac{b_{i+1}}{b_{i+1}}\frac{P_{i+1}}{b_{1}\ldots b_{i}} + \frac{(a_{i+1} -z)P_{i}}{b_{1}\ldots b_{i}} + \frac{b^{2}_{i}P_{i-1}}{b_{1}\ldots b_{i}} \equiv 0,
+\ear
+учитывая, что $\displaystyle\frac{P_{i+1}}{b_{1}\ldots b_{i}b_{i+1}} = Q_{i+1}$, $\displaystyle\frac{P_{i}}{b_{1}\ldots b_{i}} = Q_{i}$, $\displaystyle\frac{P_{i-1}}{b_{1}\ldots b_{i}} = Q_{i-1}$,
+перепишем  (\ref{req_pol})  как
+\bear{repol2}
+b_{i+1}Q_{i+1} + \left(a_{i+1} -z\right)Q_{i} + b_{i}Q_{i-1} \equiv 0.
+\ear
+Подставим $z= \lambda_{k}$:
+\bear{rec_pol3}
+b_{i+1}Q_{i+1}(\lambda_{k}) + (a_{i+1} - \lambda_{k})Q_{i}(\lambda_{k}) + b_{i}Q_{i-1}(\lambda_{k}) = 0.
+\ear
+$\Rightarrow$ вектор $v_{k} = \xi_{k}\left(Q_{0}(\lambda_{k}),Q_{1}(\lambda_{k}),\ldots,Q_{n-1}(\lambda_{k})\right)$ является собственным нормированным вектором для
+$\lambda = \lambda_{k}$ для $L(a,b)$.
+\bear{Q0}
+Q_{0}(z) =  \frac{1}{\xi^{2}_{1} + \ldots + \xi^{2}_{n}} =1, \qquad v_{k} = (\xi_{k},*,\ldots,*),
+\ear
+то есть $\xi_{k}$ являются первыми компонентами собственного вектора.
+
+\section{Лекция 2}
+\label{sec:-2}
+
+ Лекция 2. Скейлинг в критических моделях
+  \begin{itemize}
+  \item Процедура Каданова (?)
+  \item Ренормгруппа в решеточных моделях
+  \item Ренормгруппа в непрерывных моделях
+  \item Уравнение Каллана-Симанчика
+  \item Ренормгруппа в двух измерениях
+  \end{itemize}
 
@@
 
-\subsection{Критические явления}
-\label{sec:critical-phenomena}
-
-Фазовые переходы характеризуются скачком в макроскопических характеристиках системы. При переходах
-первого рода скачком меняется внутренняя энергия (например, при переходе жидкость-газ). При
-переходах второго рода наблюдается скачок производных макроскопических термодинамических величин
-(теплоемкость, магнитная восприимчивость).  Эта классификация несколько условна (см.
-\cite{ma2000modern,ma1980}), бывают и другие виды фазовых переходов, например, переход
-Костерлица-Таулесса \cite{0022-3719-6-7-010}.
-
-Строго говоря, фазовые переходы бывают только в термодинамическом пределе. Это легко понять для
-систем типа модели Изинга в нулевом поле, где энергия любой конфигурации кратна энергетическому
-масштабу $\epsilon=-J$, а статсумма представляет собой полином от $z=e^{-\beta\epsilon}$. В модели
-Изинга наибольшая энергия $E=2N\epsilon$, $Z$- полином степени $2N$ от $z$ с единичными
-коэффициентами. Корни этого полинома лежат вне положительной вещественной оси и комплексно
-сопряжены. Сингулярности свободной энергии или ее производных могут быть только в корнях, которые
-находятся вне физической области при $N<\infty$. При $N\to \infty$ число корней становится
-бесконечным, они лежат на дугах, которые могут касаться положительной вещественной оси. В этих
-точках поведение термодинамических величин и становится сингулярным.
-
-Нас будут интересовать переходы второго рода. Именно в них имеет место конформная инвариантность. 
-Перечислим основные результаты для модели Изинга в двух измерениях.
-
-Здесь есть один фазовый переход при конечной температуре. 
-Критическая температура
-\begin{equation}
-  \label{eq:27}
-  T_c:\quad \sh \frac{2J}{T_c}=1
-\end{equation}
-При $T>T_c$ спонтанная намагниченность \eqref{eq:7} исчезает. При $T<T_c$ она не равна нулю и
-стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_c$. Это упорядоченная ферромагнитная фаза. Около
-критической точки спонтанная намагниченность ведет себя как 
-\begin{equation}
-  \label{eq:28}
-  M\sim \left|T_c-T\right|^{\frac{1}{8}}
-\end{equation}
-Направление намагниченности определяется тем, куда было направлено внешнее поле до того, как его устремили к $0$.
-
-При подходе к критической точке магнитная восприимчивость \eqref{eq:8} расходится
-\begin{equation}
-  \label{eq:29}
-  \chi=\frac{\partial M}{\partial h}\sim \left|T-T_c \right|^{-\frac{7}{4}}.
-\end{equation}
-Вдали от критической точки корреляторы $\Gamma_c(i)$ убывают экспоненциально с расстоянием.
-Характерная длина убывания $\xi$ называется корреляционной длиной 
-\begin{equation}
-  \label{eq:30}
-  \left<\sigma_i\sigma_j\right>_c\sim e^{-\frac{\left|i-j\right|}{\xi(T)}}\quad \left|i-j\right|>>1.
-\end{equation}
-При $T\to T_c$ корреляционная длина расходится
-\begin{equation}
-  \label{eq:31}
-  \xi(T)\sim \frac{1}{\left|T-T_c\right|}.
-\end{equation}
-Такое поведение характеризует переходы второго рода и наблюдается в критических точках фазовой диаграммы.
-
-Около критической точки система состоит из доменов разной намагниченности. Существуют домены
-всевозможных размеров от шага решетки до корреляционной длины $\xi$. Свободная энергия $F$ получает
-вклады от доменных стенок. Сингулярное поведение возникает из-за вкладов доменов большого размера,
-оно определяется флуктуациями и не может быть правильно учтено в теории среднего поля. Вблизи
-критической температуры $\xi$ больше физических размеров системы. Свободная энергия перестает
-зависеть от $\xi$.
-
-Парная корреляционная функция ведет себя как
-\begin{equation}
-  \label{eq:32}
-  \Gamma(\vec n)\sim \frac{1}{\left|\vec n\right|^{d-2+\eta}}
-\end{equation}
-Поведение термодинамических величин определяется критическими индексами. Перечислим их вместе со
-значениями в двумерной модели Изинга. Эти значения получены из точных решений модели. 
-\begin{table}[h!tb]
-\label{tab:diagrams}
-\noindent  \centering{
-\begin{tabular}{|l|l|l|}
-  \hline
-  Критический  & Термодинамическая & Значение индекса в \\
-  индекс &  величина  & двумерной модели Изинга\\
-  \hline
-  $\alpha$ & $C\sim \frac{1}{\left|T-T_c\right|^{\alpha}}$ & $0$\\
-  $\beta$ & $M\sim \left|T-T_c\right|^{\beta}$ & $\frac{1}{8}$\\
-  $\gamma$ & $\chi\sim \frac{1}{\left|T-T_c\right|^{\gamma}}$ & $\frac{7}{4}$\\
-  $\delta$ & $M\sim h^{\frac{1}{\delta}}$ & $15$ \\
-  $\nu$ & $\xi\sim \frac{1}{\left|T-T_c\right|^{\nu}}$ & $1$\\
-  $\eta$ & $\Gamma(\vec n)\sim \left|\vec n\right|^{2-d-\eta}$ & $\frac{1}{4}$\\
-  \hline
-\end{tabular}
-\caption{Критические индексы и их значения в модели Изинга в 2 измерениях}
-}
-\end{table}
-
-Заметим, что систему можно описывать классической статистической механикой (обычной квантовой
-теорией поля с неограниченным временем) когда корреляционная длина больше характерной длины волны де
-Бройля. Если характерная скорость $v$ (скорость света, скорость Ферми или скорость какого-либо
-возбуждения), то $\lambda_T=\frac{v\hbar}{k_B T}\sim \beta$. То есть классическая статистика
-применима при больших температурах или вблизи критической точки. %, если $T_c\neq 0$.
-
-\subsection{Лекция 1. Что такое интегрируемая система?}
-
-Гамильтонова система в $\R^{2n}(p,q)$.\\
-$H = H(p,q)$ - гамильтониан.
-\bear{canon_var}
-\dot{p}_{i} = - \frac{\partial H}{\partial q_{i}}, \quad \dot{q}_{i} = \frac{\partial H}{\partial p_{i}}, \quad i=1,\ldots,n.
-\ear
-\bear{F}
-\dot{F} = \sum^{n}_{i=1} \frac{\partial F}{\partial p_{i}}\dot{p}_{i} + \sum^{n}_{i=1} \frac{\partial F}{\partial q_{i}}\dot{q}_{i} = \sum^{n}_{i=1}\Bigl(\frac{\partial F}{\partial p_{i}}\left( - \frac{H}{\partial q_{i}}\right) + \frac{\partial{F}}{\partial q_{i}}\frac{\partial H}{\partial p_{i}} \Bigr)
-\ear
-Скобка Пуассона определена как:
-\bear{Pois_br}
-\{H,F\} = -\{F,H\}.
-\ear
-Для скобки выполняется тождество Якоби
-\bear{Yakobi_eq}
-\{\{F,H\},G\} + \{\{H,G\},F\} + \{\{G,F\},H\} =0.
-\ear
-$F$ - интеграл движения системы (\ref{canon_var}), если $\{F,H\} \equiv 0$.\\
-$\dot{F} \equiv 0$ - закон сохранения.\\
-
-\textit{Пример.} $\{H,H\}$ = -\{H,H\} = 0 - энергия.\\
-
-Тождество Якоби $\rightarrow$ теорема Пуассона: скобка двух интегралов - интеграл. Интегралы образуют алгебру Ли относительно скобки.\\
-
-Принцип Нетер : интеграл $\leftrightarrow$  симметрия системы.\\
-поток $p^{'}_{i} = -\displaystyle\frac{\partial F}{\partial q_{i}}$, $q^{'}_{i} = \displaystyle\frac{\partial F}{\partial p_{i}}$, $q^{'}_{i} = \displaystyle\frac{\partial q_{i}}{d \tau}$ коммутирует с (\ref{canon_var}).\\
-
-\textit{Определение:}\\
-Гамильтонова система называется интегрируемой по Лиувиллю, если у нее есть $n$ $\left( = \frac 12 \dim \R^{2n} \right)$ независимых интегралов в инволюции (т.е.
-$\{F_{i}, F_{j}\} =0$, для $\forall i,j$).\\
-
-\textit{Пример.} Задача Кеплера
-\[H = \frac12 |p|^{2} - \frac{k}{|q|},\quad p,q \in \R^{3}.\]
-
-Цепочка Тоды (М. Тода $1967$) -  $n$ частиц на прямой
-\bear{Toda_ham}
-H = \frac12 \sum^{n}_{i=1}p^{2}_{i} + \sum^{n-1}_{i=1}e^{q_{i} - q_{i+1}},
-\ear
-где $U(q) = \displaystyle{\sum^{n-1}_{i=1}e^{q_{i} - q_{i+1}}}$ - потенциальная энергия.\\
-Конечная цепочка Тоды: $q_{i} = -\infty$, $q_{n+1} = +\infty$.\\
-Случай $q_{n+1} = q_{1}$ мы не рассматриваем.\\
-
-Введем новые переменные:
-\bear{Flaschka_var}
-a_{j} = -\frac12 p_{j},\quad b_{k} = \frac12 e^{\frac 12 (q_{k} - q_{k+1})}, \quad k = 1,\ldots,n-1,\quad j = 1,\ldots n.
-\ear \textbf{Flasсhka, 1974}.\\
-Тогда уравнения движения
-\bear{eq_motion}
-\dot{q}_{j} =  p_{j}, \quad \dot{p}_{j} = -\frac{\partial U}{\partial q_{j}} = e^{q_{j-1} - q_{j}} - e^{q_{j} - q_{j+1}}
-\ear
-перепишутся как
-\bear{eq_motion_new}
-\dot{a}_{j} = 2(b^{2}_{j} - b^{2}_{j-1}), \quad \dot{b}_{k} = b_{k}(a_{k+1} - a_{k}).
-\ear
-Представление Лакса для цепочки Тоды (Flashka, Мананов 1974):\\
-(\ref{eq_motion_new}) $\Longleftrightarrow$ $\dot{L} = [B, L]$, где
-\bear{matrices}
-B =
-\left( \begin{array}{cccc}
-a_{1}& b_{1} &\ldots & 0\\
-b_{1}& a_{2} &\ddots & \vdots\\
-\vdots & \ddots &\ddots & b_{n-1}\\
-0& \ldots & b_{n-1}  & a_{n}
-\end{array}
-\right), \quad
-L =
-\left( \begin{array}{cccc}
-0 & b_{1} &\ldots & 0\\
-- b_{1} & 0 &\ddots & \vdots\\
-\vdots & \ddots &\ddots & b_{n-1}\\
-0 & \ldots & -b_{n-1}  & 0
-\end{array}
-\right),
-\ear
-Если $b_{i}>0 $, то матрица $B$ - матрица Якоби.\\
-Упражнение: проверить.
-\[[B,L] = BL - LB.\]
-
-\textit{Предложение.}\\
-
-Поток $\dot{L} = [B,L]$ сохраняет спектр  (набор собственных чисел) матрицы $L$
-и, наоборот, изоспектральная деформация $L \rightarrow C(t)LC^{-1}(t)$ описывается $\dot{L} = [B,L]$ для подходящей $B = B(t)$.\\
-
-\textit{Доказательство:}\\
-$C(t)$ - решение уравнения $\dot{C}(t) =  B(t)C(t)$  с начальным условием $C(0) = I$.\\
-$X = C^{-1}(t)L(t)C(t)$,\\
-$\dot{X} = \dot{(C^{-1})}LC + C^{-1}\dot{L}C + C^{-1}L\dot{C} = $
-
-\[\circledast \dot{\left(C^{-1}C\right)} = \dot{C^{-1}}C + C^{-1}\dot{C} = 0 \quad  \Rightarrow \dot{\left(C^{-1}\right)}  = -C^{-1}\dot{C}C^{-1} \circledast\]
-
-$= -C^{-1}\underbrace{\dot{C}C^{-1}}_{B}LC + C^{-1}\dot{L}C + C^{-1}L\underbrace{\dot{C}C^{-1}}_{B}C = C^{-1}\left(\dot{L} + LB -BL\right)C = $\\
-$C^{-1}\underbrace{\left(\dot{L} - [B,L]\right)}_{0}C = 0$ $\Rightarrow$ $\dot{x} = 0$ $\rightarrow$ $L = C(t)L_{0}C^{-1}(t)$, где $L_{0} = const$.\\
-\[\det{(L - \lambda E)} = \det{\left(CL_{0}C^{-1} - \lambda C C^{-1}\right)} = \det{C(L_{0} - \lambda E)C^{-1}} = \det{L_{0} - \lambda E} \]
-- не зависит от  $t$.\\
-
-\textit{Следствие:}\\
-
-$F_{k} = \frac{1}{k} tr{L}^{k}$, при $k=1,2, \ldots, n$, являются интегралами движения цепочки Тоды,\\
-$F_{k} = \displaystyle{frac{1}{k}\sum^{n}_{i=1}\lambda^{k}_{i}}$ - сохраняется.\\
-$F_{1} = a_{1} + \ldots + a_{n} = -\displaystyle\frac12 (p_{1} + \ldots + p_{n})$, где $(p_{1} + \ldots + p_{n})$ - полный импульс.\\
-$F_{2} = \frac12 tr L^{2} = \displaystyle{\frac12 \left(\sum^{n}_{i=1} a^{2}_{i} + \sum^{n-1}_{j=1}b^{k}_{j}\right)} = \displaystyle{\frac12 \left( \frac14 \sum^{n}_{i=1}p^{2}_{i} + 2 \sum^{n-1}_{j=1}\frac14 e^{q_{j} - q_{j+1}}\right)} = \frac14 M$.\\
-$F_{3} = \frac13 L^{3}$,\\
-$F_{4} = \ldots $  - не имеет естественной механической интерпретации.\\
-
-\textit{Теорема.}
-\bear{inv_int}
-\{F_{i},F_{j}\}\equiv 0,
-\ear
-то есть цепочка Тоды интегрируема по Лиувиллю.\\
-
-\textit{Лемма 1.}\\
-
-Матрицы Якоби имеют простой (невырожденный) спектр (собственные значения различны)
-\[\left(L - \lambda E\right)x = 0 \quad \exists !x \quad \Leftrightarrow \qquad\Bigl\{
-                                                                    \begin{array}{ll}
-                                                                      (a_{1} -\lambda)x_{1} + b_{1}x_{1} = 0 \textrm{,} & \Rightarrow x_{2}\textrm{;} \\
-                                                                      b_{1}x_{1} + (a_{2} - \lambda)x_{2} + b_{2}x_{3} = 0 \textrm{,} & \Rightarrow x_{3}\textrm{.}
-                                                                    \end{array} 
-\]
-$x_{2}\ldots x_{n}$ задано однозначно при данном $x_{1}$.\\
-Нормируем собственный вектор $(L - \lambda E)x = 0$, $(x,x) = 1$ и положим $x_{0}$ и $x_{n+1} = 0$.\\
-
-\textit{Лемма 2.}
-
-\bear{lemma2}
-\frac{\partial \lambda}{\partial a_{k}} = x^{2}_{k}, \qquad \frac{\partial \lambda}{\partial b_{j}} = 2x_{j}x_{j+1}.
-\ear
-
-\textit{Доказательство:}\\
-
-Проварьируем $(L - \lambda E)x = 0$:\\
-\[(\delta L - \delta \lambda E)x + (L - \lambda E)\delta x = 0.\]
-Умножим скалярно на $x$ :
-\[\left((\delta L - \delta \lambda E)x,x\right) + \left((L-\lambda E)\delta x,x \right) = 0\]
-\[\left((\delta L - \delta \lambda E)x,x\right) + \left(\delta x, (L-\lambda E)x \right) = 0\]
-$\left(\delta L x,x\right) = \delta \lambda \underbrace{(x,x)}_{1} = \delta \lambda$ $\Rightarrow$ $\delta\lambda = (\delta L x,x)$ $\Rightarrow$ (\ref{lemma2}).\\
-
-Скобка Пуассона в переменных Flaschka.
-\[\{F,G\} = \frac 14 \sum \left(b_{j}\frac{\partial F}{\partial b_{j}} - b_{j-1}\frac{\partial F}{\partial b_{j-1}}\right)\frac{\partial G}{\partial a_{j}} - \ldots (F\leftrightarrow G)\]
-$\lambda$, $\mu$ - два собственных числа $L$, а $x$, $y$ - соответствующие  нормированные собственные вектора.
-\[\{\lambda, \mu\} = \frac 12  \sum^{n}_{j=1}\left(b_{j}x_{j}x_{j+1} - b_{j-1}x_{j-1}x_{j}\right)y^{2}_{j} - (x\leftrightarrow y) =\]
-\[\frac12 \sum^{n}_{j=1} \left(b_{j}(x_{j+1}y_{j} - y_{j+1}x_{j}) + b_{j-1}(x_{j}y_{j-1} - x_{j-1}y_{j}) \right) x_{j}y_{j},\]
-где $W(x,y) = b_{j}(x_{j+1}y_{j} - y_{j+1}x_{j}) $ - дискретный Вронскиан.
-Получим систему разностных дифференциальных уравнений:
-\bear{sys_eqs}\Bigl\{
-    \begin{array}{ll}
-      b_{j-1}x_{j-1} + (a_{j} - \lambda)x_{j} + b_{j}x_{j+1} = 0 \textrm{,} & \Leftarrow (L-\lambda E)x =0\textrm{;} \\
-      b_{j-1}y_{j-1} + (a_{j} - \mu)y_{j} + b_{j}y_{j+1} = 0 \textrm{,} & \Leftarrow (L-\mu E)x =0 \textrm{.}
-    \end{array}
-\ear
-Домножим первое уравнение системы (\ref{sys_eqs}) на $y_{i}$, а второе - на $x_{j}$ и вычтем второе из первого, получим:\\
-$W_{j} - W_{j-1} = (\lambda - \mu)x_{j}y_{j}$, $\lambda = \mu$ $\Rightarrow$ $W_{j} = W_{j-1} = const$.\\
-\[\Rightarrow \{\lambda, \mu\} = \frac 12 \sum^{n}_{j=1} \left(W_{j} + W_{j-1}\right)\left(W_{j}  - W_{j-1}\right) = \frac{1}{2(\lambda - \mu)}\sum^{n}_{j=1}\left(W^{2}_{j} - W^{2}_{j-1}\right) =0.\]
-$\Rightarrow$ $\{F_{k}, F_{l}\} \equiv 0$ $\Rightarrow$  интегрируемость цепочки Тоды.\\
-
-\subsection{Лекция 2.}
-\bear{LP}
-\dot{L} = [B,L]
-\ear
-
-\bear{matrice_L}
-B =
-\left( \begin{array}{cccc}
-a_{1}& b_{1} &\ldots & 0\\
-b_{1}& a_{2} &\ddots & \vdots\\
-\vdots & \ddots &\ddots & b_{n-1}\\
-0& \ldots & b_{n-1}  & a_{n}
-\end{array}
-\right)  - \textrm{матрица Якоби при} b_{i}>0.
-\ear
-
-\textit{Метод обратной задачи (рассеяния).}\\
-
-Идея: Начальные данные $p(0)$ $q(0)$ $\longrightarrow$ $p(t),q(t)$\\
-спектральная задача для $L$ $\longrightarrow$ $\longleftarrow$ обратная спектральная задача\\
-спектральные данные при $t = 0$ $\longrightarrow$ спектральные данные в момент $t$\\
-простая  эволюция спектральных данных.\\
-
-Спектральные данные матриц Якоби.\\
-
-$\lambda_{1},\ldots ,\lambda_{n}$ - спектр $L$, $Lx=\lambda x$, собственные значения нормированных $x$.\\
-Дополнительные спектральные данные - первые компоненты собственных векторов $\xi_{1},\ldots,\xi_{n}>0$.\\
-Матрица $C = \left(
-               \begin{array}{ccc}
-                 \xi_{1} & \ldots & \xi_{n} \\
-                 \ldots & \ldots & \ldots \\
-                 \ldots & \ldots & \ldots \\
-               \end{array}
-             \right)$ - ортогональная (и самосопряженная ?).\\
-
-\[\Rightarrow\quad \xi^{2}_{1} + \ldots + \xi^{2}_{n} = 1,\quad \xi_{i} >0.\]
-
-\bear{Spectr}
-Spec = \{(\lambda,\xi): \quad \lambda_{1}<\lambda_{2}<\ldots<\lambda_{n} \quad \xi^{2}_{1} + \ldots + \xi^{2}_{n} = 1, \xi_{i} >0\}
-\ear
-
-\textit{Теорема.}\\
-
-$S : L(a,b) \rightarrow (\lambda, \xi)$ задает диффеоморфизм  (взаимно однозначное гладкое отображение) между матрицей Якоби и множеством Spec.\\
-
-Обратная задача заключается в восстановлении $L(a,b)$ по $(\lambda, \xi)$.\\
-Есть два решения. \textbf{Мозер 1974}.\\
-
-Функцию Вейля и цепные дроби. Идея восходит к Стильтьетсу.\\
-В резольвенту $R(z) = (zE-L)^{-1}$ и её первый диагональный элемент \\$W(z) = \left(\left(z E- L \right)^{-1} e_{1}, e_{1}\right)$ -  функция Вейля, где $e_{1} = \left(
-                                                                                                                                                     \begin{array}{c}
-                                                                                                                                                       1 \\
-                                                                                                                                                       0 \\
-                                                                                                                                                       \vdots \\
-                                                                                                                                                       0 \\
-                                                                                                                                                     \end{array}
-                                                                                                                                                   \right)$.\\
-\textit{Лемма 1.}
-\bear{Lemma_W}
-W(z) = \sum^{n}_{i=1}\frac {\xi^{2}_{i}}{z - \lambda_{i}}
-\ear
-\textit{Доказательство.}\\
-$LC = C\Lambda$, $\Lambda = \left(
-                                   \begin{array}{ccc}
-                                     \lambda_{1} & \ldots & 0 \\
-                                     \vdots & \vdots & \vdots \\
-                                     0 & \ldots & \lambda_{n} \\
-                                   \end{array}
-                                 \right)$, $C = \left(
-                                             \begin{array}{ccc}
-                                               \xi_{1} & \ldots & \xi_{1} \\
-                                               \vdots & \vdots & \vdots \\
-                                               \ldots & \ldots & \ldots \\
-                                             \end{array}
-                                           \right)$, $C^{T} = C^{-1} = \left(
-                                             \begin{array}{ccc}
-                                               \xi_{1} & \ldots & \ldots \\
-                                               \vdots & \vdots & \vdots \\
-                                               \xi_{n} & \ldots & \ldots \\
-                                             \end{array}
-                                           \right)$,  $L = C\Lambda C^{-1}$.\\
-
-\[W(z) = \left( \left(zCC^{-1}- C\Lambda C^{-1}\right)^{-1}e_{1},e_{1}\right) = \left(C\left( zE- \Lambda\right)^{-1}C^{-1}e_{1},e_{1}\right) =\]
-
-\[= \left(\left(zE- \Lambda\right)^{-1}C^{T}e_{1},C^{T} e_{1}\right) = \sum^{n}_{i=1} \frac{\xi^{2}_{i}}{z- \lambda_{i}}.\]
-
-Так как $(zE - \Lambda)^{-1} = \left(\begin{array}{ccc} (z -\lambda_{1})^{-1} & \ldots & 0 \\
-                                     \vdots & \ddots & \vdots \\
-                                     0 & \ldots & (z -\lambda_{n})^{-1} \\
-\end{array} \right).$\\
-\\
-\textit{Лемма 2. Цепная дробь.}\\
-\bear{fraction}
-W(z) = \frac{1}{z - a_{1} -
-\displaystyle\frac{b^{2}_{1}}{z - a_{2} -
-\displaystyle\frac{b^{2}_{2}}{
-\displaystyle\frac{\cdots}{\displaystyle{\cdots -\frac{b^{2}_{n-1}}{z-a_{n}}}}}}},
-\ear
-здесь $a_{i}$, $b_{j}$ - те же, что и в $L(a,b)$.
-если есть решение для $\xi$ и $\lambda$, то оно находится из этой формулы.\\
-
-\textit{Доказательство.}\\
-
-\bear{Delta_Z}
-\Delta_{j}(z) = \det{\left(\begin{array}{cccc}
-z - a_{j+1}& -b_{j+1} &\ldots & 0\\
--b_{j+1}& \ddots &\ddots & \vdots\\
-\vdots & \ddots &\ddots & -b_{n-1}\\
-0& \ldots & -b_{n-1}  & z - a_{n}
-\end{array} 
-\right),}
-\ear
-где $j=1,\ldots, n-1$, $\Delta_{n}:=1$, $\Delta_{1} = 0$.\\
-
-Рекуррентное соотношение:
-\[\Delta_{j-1}(z) = (z-a_{j})\Delta_{j}(z) - b^{2}_{j}\Delta_{j+1}(z), \qquad W=\frac{\Delta_{1}}{\Delta_{0}} = \frac{1}{\frac{\Delta_{0}}{\Delta_{1}}}.\]
-\[\displaystyle\frac{\Delta_{j-1}(z)}{\Delta_{j-1}(z)} = z - a_{j} - \displaystyle\frac{b^{2}_{j}}{\Bigl(\frac{\Delta_{j}}{\Delta_{j+1}}\Bigr)}.\]
-(\ref{Delta_Z}) показывает связь цепочки Тоды с ортогональными многочленами и процессом  ортогонализации Грама-Шмидта.\\
-Ортогональные многочлены - результат ортогонализации Грама-Шмидтаю базиса $1$, $z$, $z^{2}$, $\ldots$  по отношению к скалярному произведению
-$\langle f,g \rangle = l(f,g)$.\\
-\[p_{0} = 1, \quad p_{1}(z), \ldots, \quad \langle p_{i},p_{j}\rangle = 0, \quad i\neq j.\]
-Обычно $\langle f,g,\rangle = \int {f(x),g(x)}d\mu(x)$, $\langle x f,g \rangle = \langle f,x g \rangle$.\\
-Ортогональные многочлены удовлетворяют рекуррентному соотношению: 
-\[zp_{i} = p_{i+1} + \alpha_{i}p_{i} + \beta_{i}p_{i-1},\]
-где $\alpha_{i} = \displaystyle\frac{\langle z p_{i}, p_{i}\rangle}{\langle p_{i}, p_{i} \rangle}$, $\beta_{i} = \displaystyle\frac{|p_{i}|^{2}}{|p_{i-1}|^{2}}$.\\
-
-Действительно, $zp_{i} = p_{i+1} + \alpha_{i}p_{i} + \beta_{i}p_{i-1} + \gamma_{i}p_{i-2} + \ldots$\\
-
-Утверждается, что $\gamma_{i} = \delta_{i} = \ldots = 0$\\
-\[\gamma_{i} \langle p_{i-2}, p_{i-2}\rangle = \langle z p_{i}, p_{i-2}\rangle = \langle p_{i}, z p_{i-2}\rangle =0\]
-\[\langle z p_{i}, p_{i}\rangle = \alpha_{i}\langle p_{i},p_{i}\rangle\]
-\[\langle z \underbrace{p_{i}}_{\beta_{i}\langle p_{i-1},p_{i-1}\rangle},p_{i-1}\rangle = \langle p_{i}, zp_{i-1}\rangle = \langle p_{i},p_{i}\rangle   = |p_{i}|^{2}\]
-
-Пусть теперь $(\lambda,\xi) \in Spec$, пространство $V = \R[z] \mod \prod (z - \lambda_{i})$ со скалярным произведением
-$\langle f,g \rangle = \displaystyle\sum^{n}_{i=1}f(\lambda_{i})g(\lambda_{j}) \xi^{2}_{i}$ - интеграл по дискретной мере\\
-Г.-Ш. $P_{0} = 1$, $P_{1},\ldots,P_{n_1}$, $P_{n} = \displaystyle\prod^{n}_{i=1}(z-\lambda_{i}) =0$\\
-
-\textit{Предложение.} \\
-\bear{def_a_b}
-a_{i+1} = \displaystyle\frac{\langle zp_{i},p_{i}\rangle}{\langle p_{i},p_{i} \rangle},\quad b_{j} = \frac{P_{j}}{P_{j-1}},
-\ear 
-где $i=0,\ldots,n-1$, $j=1,\ldots,n-1$, дает решение обратной задачи $(\lambda, \xi)$ $\rightarrow$ $L(z,b)$.\\
-
-\textit{Доказательство.}\\
-
-\textit{Лемма.}\\
-Пусть $a$, $b$ определены (\ref{def_a_b}), тогда $\Rightarrow$ $P_{k} = \det{\left( \begin{array}{cccc}
-z - a_{1}& -b_{1} &\ldots & 0\\
-b_{1}& \ddots &\ddots & \vdots\\
-\vdots & \ddots &\ddots & -b_{k-1}\\
-0& \ldots & -b_{k-1}  & z-a_{k}
-\end{array}\right)} = D_{k}$, \\
-действительно, $D_{a}$ удовлетворяют тому же рекуррентному соотношению
-\[D_{k+1} = (z - a_{k+1})D_{k} - b^{2}_{k}D_{k-1}\]
-из разложения по последнему столбцу с теми же начальными условиями $D_{0} = P_{0} = 1$, $D_{1} = P_{1} = z -a_{1}$.
-В частности,
-\[D_{n} = \det{\left(zE - L\right)} = \prod(z - \lambda_{i}) = P_{n}\]
-$\Rightarrow$ $\lambda_{1},\ldots, \lambda_{k}$  - собственные числа $L(a,b)$.\\
-
-Дополнительный спектр.\\
-
-Нормированные ортогональные многочлены $Q_{i} = \displaystyle\frac{P_{i}}{|P_{i}|} = \left(b_{1}\ldots b_{i}\right)^{-1}P_{i}$.\\
-Рекуррентное соотношение
-\bear{req_pol}
-\frac{b_{i+1}}{b_{i+1}}\frac{P_{i+1}}{b_{1}\ldots b_{i}} + \frac{(a_{i+1} -z)P_{i}}{b_{1}\ldots b_{i}} + \frac{b^{2}_{i}P_{i-1}}{b_{1}\ldots b_{i}} \equiv 0,
-\ear
-учитывая, что $\displaystyle\frac{P_{i+1}}{b_{1}\ldots b_{i}b_{i+1}} = Q_{i+1}$, $\displaystyle\frac{P_{i}}{b_{1}\ldots b_{i}} = Q_{i}$, $\displaystyle\frac{P_{i-1}}{b_{1}\ldots b_{i}} = Q_{i-1}$,
-перепишем  (\ref{req_pol})  как
-\bear{repol2}
-b_{i+1}Q_{i+1} + \left(a_{i+1} -z\right)Q_{i} + b_{i}Q_{i-1} \equiv 0.
-\ear
-Подставим $z= \lambda_{k}$:
-\bear{rec_pol3}
-b_{i+1}Q_{i+1}(\lambda_{k}) + (a_{i+1} - \lambda_{k})Q_{i}(\lambda_{k}) + b_{i}Q_{i-1}(\lambda_{k}) = 0.
-\ear
-$\Rightarrow$ вектор $v_{k} = \xi_{k}\left(Q_{0}(\lambda_{k}),Q_{1}(\lambda_{k}),\ldots,Q_{n-1}(\lambda_{k})\right)$ является собственным нормированным вектором для
-$\lambda = \lambda_{k}$ для $L(a,b)$.
-\bear{Q0}
-Q_{0}(z) =  \frac{1}{\xi^{2}_{1} + \ldots + \xi^{2}_{n}} =1, \qquad v_{k} = (\xi_{k},*,\ldots,*),
-\ear
-то есть $\xi_{k}$ являются первыми компонентами собственного вектора.
-
-\section{Лекция 2}
-\label{sec:-2}
-
- Лекция 2. Скейлинг в критических моделях
-  \begin{itemize}
-  \item Процедура Каданова (?)
-  \item Ренормгруппа в решеточных моделях
-  \item Ренормгруппа в непрерывных моделях
-  \item Уравнение Каллана-Симанчика
-  \item Ренормгруппа в двух измерениях
-  \end{itemize}
-
 \subsection{Скейлинг или масштабная инвариантность}

### 2015-10-04 GeneralOverview/Lectures/Integrability2015.tex
Lectures 1-3 as given, started to prepare Lecture 4

@@
 
-\subsection{Лекция 1. Что такое интегрируемая система?}
-
-Гамильтонова система в $\R^{2n}(p,q)$.\\
-$H = H(p,q)$ - гамильтониан.
-\bear{canon_var}
-\dot{p}_{i} = - \frac{\partial H}{\partial q_{i}}, \quad \dot{q}_{i} = \frac{\partial H}{\partial p_{i}}, \quad i=1,\ldots,n.
-\ear
-\bear{F}
-\dot{F} = \sum^{n}_{i=1} \frac{\partial F}{\partial p_{i}}\dot{p}_{i} + \sum^{n}_{i=1} \frac{\partial F}{\partial q_{i}}\dot{q}_{i} = \sum^{n}_{i=1}\Bigl(\frac{\partial F}{\partial p_{i}}\left( - \frac{H}{\partial q_{i}}\right) + \frac{\partial{F}}{\partial q_{i}}\frac{\partial H}{\partial p_{i}} \Bigr)
-\ear
-Скобка Пуассона определена как:
-\bear{Pois_br}
-\{H,F\} = -\{F,H\}.
-\ear
-Для скобки выполняется тождество Якоби
-\bear{Yakobi_eq}
-\{\{F,H\},G\} + \{\{H,G\},F\} + \{\{G,F\},H\} =0.
-\ear
-$F$ - интеграл движения системы (\ref{canon_var}), если $\{F,H\} \equiv 0$.\\
-$\dot{F} \equiv 0$ - закон сохранения.\\
-
-\textit{Пример.} $\{H,H\}$ = -\{H,H\} = 0 - энергия.\\
-
-Тождество Якоби $\rightarrow$ теорема Пуассона: скобка двух интегралов - интеграл. Интегралы образуют алгебру Ли относительно скобки.\\
-
-Принцип Нетер : интеграл $\leftrightarrow$  симметрия системы.\\
-поток $p^{'}_{i} = -\displaystyle\frac{\partial F}{\partial q_{i}}$, $q^{'}_{i} = \displaystyle\frac{\partial F}{\partial p_{i}}$, $q^{'}_{i} = \displaystyle\frac{\partial q_{i}}{d \tau}$ коммутирует с (\ref{canon_var}).\\
-
-\textit{Определение:}\\
-Гамильтонова система называется интегрируемой по Лиувиллю, если у нее есть $n$ $\left( = \frac 12 \dim \R^{2n} \right)$ независимых интегралов в инволюции (т.е.
-$\{F_{i}, F_{j}\} =0$, для $\forall i,j$).\\
-
-\textit{Пример.} Задача Кеплера
-\[H = \frac12 |p|^{2} - \frac{k}{|q|},\quad p,q \in \R^{3}.\]
-
-Цепочка Тоды (М. Тода $1967$) -  $n$ частиц на прямой
-\bear{Toda_ham}
-H = \frac12 \sum^{n}_{i=1}p^{2}_{i} + \sum^{n-1}_{i=1}e^{q_{i} - q_{i+1}},
-\ear
-где $U(q) = \displaystyle{\sum^{n-1}_{i=1}e^{q_{i} - q_{i+1}}}$ - потенциальная энергия.\\
-Конечная цепочка Тоды: $q_{i} = -\infty$, $q_{n+1} = +\infty$.\\
-Случай $q_{n+1} = q_{1}$ мы не рассматриваем.\\
-
-Введем новые переменные:
-\bear{Flaschka_var}
-a_{j} = -\frac12 p_{j},\quad b_{k} = \frac12 e^{\frac 12 (q_{k} - q_{k+1})}, \quad k = 1,\ldots,n-1,\quad j = 1,\ldots n.
-\ear \textbf{Flasсhka, 1974}.\\
-Тогда уравнения движения
-\bear{eq_motion}
-\dot{q}_{j} =  p_{j}, \quad \dot{p}_{j} = -\frac{\partial U}{\partial q_{j}} = e^{q_{j-1} - q_{j}} - e^{q_{j} - q_{j+1}}
-\ear
-перепишутся как
-\bear{eq_motion_new}
-\dot{a}_{j} = 2(b^{2}_{j} - b^{2}_{j-1}), \quad \dot{b}_{k} = b_{k}(a_{k+1} - a_{k}).
-\ear
-Представление Лакса для цепочки Тоды (Flashka, Мананов 1974):\\
-(\ref{eq_motion_new}) $\Longleftrightarrow$ $\dot{L} = [B, L]$, где
-\bear{matrices}
-B =
-\left( \begin{array}{cccc}
-a_{1}& b_{1} &\ldots & 0\\
-b_{1}& a_{2} &\ddots & \vdots\\
-\vdots & \ddots &\ddots & b_{n-1}\\
-0& \ldots & b_{n-1}  & a_{n}
-\end{array}
-\right), \quad
-L =
-\left( \begin{array}{cccc}
-0 & b_{1} &\ldots & 0\\
-- b_{1} & 0 &\ddots & \vdots\\
-\vdots & \ddots &\ddots & b_{n-1}\\
-0 & \ldots & -b_{n-1}  & 0
-\end{array}
-\right),
-\ear
-Если $b_{i}>0 $, то матрица $B$ - матрица Якоби.\\
-Упражнение: проверить.
-\[[B,L] = BL - LB.\]
-
-\textit{Предложение.}\\
-
-Поток $\dot{L} = [B,L]$ сохраняет спектр  (набор собственных чисел) матрицы $L$
-и, наоборот, изоспектральная деформация $L \rightarrow C(t)LC^{-1}(t)$ описывается $\dot{L} = [B,L]$ для подходящей $B = B(t)$.\\
-
-\textit{Доказательство:}\\
-$C(t)$ - решение уравнения $\dot{C}(t) =  B(t)C(t)$  с начальным условием $C(0) = I$.\\
-$X = C^{-1}(t)L(t)C(t)$,\\
-$\dot{X} = \dot{(C^{-1})}LC + C^{-1}\dot{L}C + C^{-1}L\dot{C} = $
-
-\[\circledast \dot{\left(C^{-1}C\right)} = \dot{C^{-1}}C + C^{-1}\dot{C} = 0 \quad  \Rightarrow \dot{\left(C^{-1}\right)}  = -C^{-1}\dot{C}C^{-1} \circledast\]
-
-$= -C^{-1}\underbrace{\dot{C}C^{-1}}_{B}LC + C^{-1}\dot{L}C + C^{-1}L\underbrace{\dot{C}C^{-1}}_{B}C = C^{-1}\left(\dot{L} + LB -BL\right)C = $\\
-$C^{-1}\underbrace{\left(\dot{L} - [B,L]\right)}_{0}C = 0$ $\Rightarrow$ $\dot{x} = 0$ $\rightarrow$ $L = C(t)L_{0}C^{-1}(t)$, где $L_{0} = const$.\\
-\[\det{(L - \lambda E)} = \det{\left(CL_{0}C^{-1} - \lambda C C^{-1}\right)} = \det{C(L_{0} - \lambda E)C^{-1}} = \det{L_{0} - \lambda E} \]
-- не зависит от  $t$.\\
-
-\textit{Следствие:}\\
-
-$F_{k} = \frac{1}{k} tr{L}^{k}$, при $k=1,2, \ldots, n$, являются интегралами движения цепочки Тоды,\\
-$F_{k} = \displaystyle{frac{1}{k}\sum^{n}_{i=1}\lambda^{k}_{i}}$ - сохраняется.\\
-$F_{1} = a_{1} + \ldots + a_{n} = -\displaystyle\frac12 (p_{1} + \ldots + p_{n})$, где $(p_{1} + \ldots + p_{n})$ - полный импульс.\\
-$F_{2} = \frac12 tr L^{2} = \displaystyle{\frac12 \left(\sum^{n}_{i=1} a^{2}_{i} + \sum^{n-1}_{j=1}b^{k}_{j}\right)} = \displaystyle{\frac12 \left( \frac14 \sum^{n}_{i=1}p^{2}_{i} + 2 \sum^{n-1}_{j=1}\frac14 e^{q_{j} - q_{j+1}}\right)} = \frac14 M$.\\
-$F_{3} = \frac13 L^{3}$,\\
-$F_{4} = \ldots $  - не имеет естественной механической интерпретации.\\
-
-\textit{Теорема.}
-\bear{inv_int}
-\{F_{i},F_{j}\}\equiv 0,
-\ear
-то есть цепочка Тоды интегрируема по Лиувиллю.\\
-
-\textit{Лемма 1.}\\
-
-Матрицы Якоби имеют простой (невырожденный) спектр (собственные значения различны)
-\[\left(L - \lambda E\right)x = 0 \quad \exists !x \quad \Leftrightarrow \qquad\Bigl\{
-                                                                    \begin{array}{ll}
-                                                                      (a_{1} -\lambda)x_{1} + b_{1}x_{1} = 0 \textrm{,} & \Rightarrow x_{2}\textrm{;} \\
-                                                                      b_{1}x_{1} + (a_{2} - \lambda)x_{2} + b_{2}x_{3} = 0 \textrm{,} & \Rightarrow x_{3}\textrm{.}
-                                                                    \end{array} 
-\]
-$x_{2}\ldots x_{n}$ задано однозначно при данном $x_{1}$.\\
-Нормируем собственный вектор $(L - \lambda E)x = 0$, $(x,x) = 1$ и положим $x_{0}$ и $x_{n+1} = 0$.\\
-
-\textit{Лемма 2.}
-
-\bear{lemma2}
-\frac{\partial \lambda}{\partial a_{k}} = x^{2}_{k}, \qquad \frac{\partial \lambda}{\partial b_{j}} = 2x_{j}x_{j+1}.
-\ear
-
-\textit{Доказательство:}\\
-
-Проварьируем $(L - \lambda E)x = 0$:\\
-\[(\delta L - \delta \lambda E)x + (L - \lambda E)\delta x = 0.\]
-Умножим скалярно на $x$ :
-\[\left((\delta L - \delta \lambda E)x,x\right) + \left((L-\lambda E)\delta x,x \right) = 0\]
-\[\left((\delta L - \delta \lambda E)x,x\right) + \left(\delta x, (L-\lambda E)x \right) = 0\]
-$\left(\delta L x,x\right) = \delta \lambda \underbrace{(x,x)}_{1} = \delta \lambda$ $\Rightarrow$ $\delta\lambda = (\delta L x,x)$ $\Rightarrow$ (\ref{lemma2}).\\
-
-Скобка Пуассона в переменных Flaschka.
-\[\{F,G\} = \frac 14 \sum \left(b_{j}\frac{\partial F}{\partial b_{j}} - b_{j-1}\frac{\partial F}{\partial b_{j-1}}\right)\frac{\partial G}{\partial a_{j}} - \ldots (F\leftrightarrow G)\]
-$\lambda$, $\mu$ - два собственных числа $L$, а $x$, $y$ - соответствующие  нормированные собственные вектора.
-\[\{\lambda, \mu\} = \frac 12  \sum^{n}_{j=1}\left(b_{j}x_{j}x_{j+1} - b_{j-1}x_{j-1}x_{j}\right)y^{2}_{j} - (x\leftrightarrow y) =\]
-\[\frac12 \sum^{n}_{j=1} \left(b_{j}(x_{j+1}y_{j} - y_{j+1}x_{j}) + b_{j-1}(x_{j}y_{j-1} - x_{j-1}y_{j}) \right) x_{j}y_{j},\]
-где $W(x,y) = b_{j}(x_{j+1}y_{j} - y_{j+1}x_{j}) $ - дискретный Вронскиан.
-Получим систему разностных дифференциальных уравнений:
-\bear{sys_eqs}\Bigl\{
-    \begin{array}{ll}
-      b_{j-1}x_{j-1} + (a_{j} - \lambda)x_{j} + b_{j}x_{j+1} = 0 \textrm{,} & \Leftarrow (L-\lambda E)x =0\textrm{;} \\
-      b_{j-1}y_{j-1} + (a_{j} - \mu)y_{j} + b_{j}y_{j+1} = 0 \textrm{,} & \Leftarrow (L-\mu E)x =0 \textrm{.}
-    \end{array}
-\ear
-Домножим первое уравнение системы (\ref{sys_eqs}) на $y_{i}$, а второе - на $x_{j}$ и вычтем второе из первого, получим:\\
-$W_{j} - W_{j-1} = (\lambda - \mu)x_{j}y_{j}$, $\lambda = \mu$ $\Rightarrow$ $W_{j} = W_{j-1} = const$.\\
-\[\Rightarrow \{\lambda, \mu\} = \frac 12 \sum^{n}_{j=1} \left(W_{j} + W_{j-1}\right)\left(W_{j}  - W_{j-1}\right) = \frac{1}{2(\lambda - \mu)}\sum^{n}_{j=1}\left(W^{2}_{j} - W^{2}_{j-1}\right) =0.\]
-$\Rightarrow$ $\{F_{k}, F_{l}\} \equiv 0$ $\Rightarrow$  интегрируемость цепочки Тоды.\\
-
-\subsection{Лекция 2.}
-\bear{LP}
-\dot{L} = [B,L]
-\ear
-
-\bear{matrice_L}
-B =
-\left( \begin{array}{cccc}
-a_{1}& b_{1} &\ldots & 0\\
-b_{1}& a_{2} &\ddots & \vdots\\
-\vdots & \ddots &\ddots & b_{n-1}\\
-0& \ldots & b_{n-1}  & a_{n}
-\end{array}
-\right)  - \textrm{матрица Якоби при} b_{i}>0.
-\ear
-
-\textit{Метод обратной задачи (рассеяния).}\\
-
-Идея: Начальные данные $p(0)$ $q(0)$ $\longrightarrow$ $p(t),q(t)$\\
-спектральная задача для $L$ $\longrightarrow$ $\longleftarrow$ обратная спектральная задача\\
-спектральные данные при $t = 0$ $\longrightarrow$ спектральные данные в момент $t$\\
-простая  эволюция спектральных данных.\\
-
-Спектральные данные матриц Якоби.\\
-
-$\lambda_{1},\ldots ,\lambda_{n}$ - спектр $L$, $Lx=\lambda x$, собственные значения нормированных $x$.\\
-Дополнительные спектральные данные - первые компоненты собственных векторов $\xi_{1},\ldots,\xi_{n}>0$.\\
-Матрица $C = \left(
-               \begin{array}{ccc}
-                 \xi_{1} & \ldots & \xi_{n} \\
-                 \ldots & \ldots & \ldots \\
-                 \ldots & \ldots & \ldots \\
-               \end{array}
-             \right)$ - ортогональная (и самосопряженная ?).\\
-
-\[\Rightarrow\quad \xi^{2}_{1} + \ldots + \xi^{2}_{n} = 1,\quad \xi_{i} >0.\]
-
-\bear{Spectr}
-Spec = \{(\lambda,\xi): \quad \lambda_{1}<\lambda_{2}<\ldots<\lambda_{n} \quad \xi^{2}_{1} + \ldots + \xi^{2}_{n} = 1, \xi_{i} >0\}
-\ear
-
-\textit{Теорема.}\\
-
-$S : L(a,b) \rightarrow (\lambda, \xi)$ задает диффеоморфизм  (взаимно однозначное гладкое отображение) между матрицей Якоби и множеством Spec.\\
-
-Обратная задача заключается в восстановлении $L(a,b)$ по $(\lambda, \xi)$.\\
-Есть два решения. \textbf{Мозер 1974}.\\
-
-Функцию Вейля и цепные дроби. Идея восходит к Стильтьетсу.\\
-В резольвенту $R(z) = (zE-L)^{-1}$ и её первый диагональный элемент \\$W(z) = \left(\left(z E- L \right)^{-1} e_{1}, e_{1}\right)$ -  функция Вейля, где $e_{1} = \left(
-                                                                                                                                                     \begin{array}{c}
-                                                                                                                                                       1 \\
-                                                                                                                                                       0 \\
-                                                                                                                                                       \vdots \\
-                                                                                                                                                       0 \\
-                                                                                                                                                     \end{array}
-                                                                                                                                                   \right)$.\\
-\textit{Лемма 1.}
-\bear{Lemma_W}
-W(z) = \sum^{n}_{i=1}\frac {\xi^{2}_{i}}{z - \lambda_{i}}
-\ear
-\textit{Доказательство.}\\
-$LC = C\Lambda$, $\Lambda = \left(
-                                   \begin{array}{ccc}
-                                     \lambda_{1} & \ldots & 0 \\
-                                     \vdots & \vdots & \vdots \\
-                                     0 & \ldots & \lambda_{n} \\
-                                   \end{array}
-                                 \right)$, $C = \left(
-                                             \begin{array}{ccc}
-                                               \xi_{1} & \ldots & \xi_{1} \\
-                                               \vdots & \vdots & \vdots \\
-                                               \ldots & \ldots & \ldots \\
-                                             \end{array}
-                                           \right)$, $C^{T} = C^{-1} = \left(
-                                             \begin{array}{ccc}
-                                               \xi_{1} & \ldots & \ldots \\
-                                               \vdots & \vdots & \vdots \\
-                                               \xi_{n} & \ldots & \ldots \\
-                                             \end{array}
-                                           \right)$,  $L = C\Lambda C^{-1}$.\\
-
-\[W(z) = \left( \left(zCC^{-1}- C\Lambda C^{-1}\right)^{-1}e_{1},e_{1}\right) = \left(C\left( zE- \Lambda\right)^{-1}C^{-1}e_{1},e_{1}\right) =\]
-
-\[= \left(\left(zE- \Lambda\right)^{-1}C^{T}e_{1},C^{T} e_{1}\right) = \sum^{n}_{i=1} \frac{\xi^{2}_{i}}{z- \lambda_{i}}.\]
-
-Так как $(zE - \Lambda)^{-1} = \left(\begin{array}{ccc} (z -\lambda_{1})^{-1} & \ldots & 0 \\
-                                     \vdots & \ddots & \vdots \\
-                                     0 & \ldots & (z -\lambda_{n})^{-1} \\
-\end{array} \right).$\\
-\\
-\textit{Лемма 2. Цепная дробь.}\\
-\bear{fraction}
-W(z) = \frac{1}{z - a_{1} -
-\displaystyle\frac{b^{2}_{1}}{z - a_{2} -
-\displaystyle\frac{b^{2}_{2}}{
-\displaystyle\frac{\cdots}{\displaystyle{\cdots -\frac{b^{2}_{n-1}}{z-a_{n}}}}}}},
-\ear
-здесь $a_{i}$, $b_{j}$ - те же, что и в $L(a,b)$.
-если есть решение для $\xi$ и $\lambda$, то оно находится из этой формулы.\\
-
-\textit{Доказательство.}\\
-
-\bear{Delta_Z}
-\Delta_{j}(z) = \det{\left(\begin{array}{cccc}
-z - a_{j+1}& -b_{j+1} &\ldots & 0\\
--b_{j+1}& \ddots &\ddots & \vdots\\
-\vdots & \ddots &\ddots & -b_{n-1}\\
-0& \ldots & -b_{n-1}  & z - a_{n}
-\end{array} 
-\right),}
-\ear
-где $j=1,\ldots, n-1$, $\Delta_{n}:=1$, $\Delta_{1} = 0$.\\
-
-Рекуррентное соотношение:
-\[\Delta_{j-1}(z) = (z-a_{j})\Delta_{j}(z) - b^{2}_{j}\Delta_{j+1}(z), \qquad W=\frac{\Delta_{1}}{\Delta_{0}} = \frac{1}{\frac{\Delta_{0}}{\Delta_{1}}}.\]
-\[\displaystyle\frac{\Delta_{j-1}(z)}{\Delta_{j-1}(z)} = z - a_{j} - \displaystyle\frac{b^{2}_{j}}{\Bigl(\frac{\Delta_{j}}{\Delta_{j+1}}\Bigr)}.\]
-(\ref{Delta_Z}) показывает связь цепочки Тоды с ортогональными многочленами и процессом  ортогонализации Грама-Шмидта.\\
-Ортогональные многочлены - результат ортогонализации Грама-Шмидтаю базиса $1$, $z$, $z^{2}$, $\ldots$  по отношению к скалярному произведению
-$\langle f,g \rangle = l(f,g)$.\\
-\[p_{0} = 1, \quad p_{1}(z), \ldots, \quad \langle p_{i},p_{j}\rangle = 0, \quad i\neq j.\]
-Обычно $\langle f,g,\rangle = \int {f(x),g(x)}d\mu(x)$, $\langle x f,g \rangle = \langle f,x g \rangle$.\\
-Ортогональные многочлены удовлетворяют рекуррентному соотношению: 
-\[zp_{i} = p_{i+1} + \alpha_{i}p_{i} + \beta_{i}p_{i-1},\]
-где $\alpha_{i} = \displaystyle\frac{\langle z p_{i}, p_{i}\rangle}{\langle p_{i}, p_{i} \rangle}$, $\beta_{i} = \displaystyle\frac{|p_{i}|^{2}}{|p_{i-1}|^{2}}$.\\
-
-Действительно, $zp_{i} = p_{i+1} + \alpha_{i}p_{i} + \beta_{i}p_{i-1} + \gamma_{i}p_{i-2} + \ldots$\\
-
-Утверждается, что $\gamma_{i} = \delta_{i} = \ldots = 0$\\
-\[\gamma_{i} \langle p_{i-2}, p_{i-2}\rangle = \langle z p_{i}, p_{i-2}\rangle = \langle p_{i}, z p_{i-2}\rangle =0\]
-\[\langle z p_{i}, p_{i}\rangle = \alpha_{i}\langle p_{i},p_{i}\rangle\]
-\[\langle z \underbrace{p_{i}}_{\beta_{i}\langle p_{i-1},p_{i-1}\rangle},p_{i-1}\rangle = \langle p_{i}, zp_{i-1}\rangle = \langle p_{i},p_{i}\rangle   = |p_{i}|^{2}\]
-
-Пусть теперь $(\lambda,\xi) \in Spec$, пространство $V = \R[z] \mod \prod (z - \lambda_{i})$ со скалярным произведением
-$\langle f,g \rangle = \displaystyle\sum^{n}_{i=1}f(\lambda_{i})g(\lambda_{j}) \xi^{2}_{i}$ - интеграл по дискретной мере\\
-Г.-Ш. $P_{0} = 1$, $P_{1},\ldots,P_{n_1}$, $P_{n} = \displaystyle\prod^{n}_{i=1}(z-\lambda_{i}) =0$\\
-
-\textit{Предложение.} \\
-\bear{def_a_b}
-a_{i+1} = \displaystyle\frac{\langle zp_{i},p_{i}\rangle}{\langle p_{i},p_{i} \rangle},\quad b_{j} = \frac{P_{j}}{P_{j-1}},
-\ear 
-где $i=0,\ldots,n-1$, $j=1,\ldots,n-1$, дает решение обратной задачи $(\lambda, \xi)$ $\rightarrow$ $L(z,b)$.\\
-
-\textit{Доказательство.}\\
-
-\textit{Лемма.}\\
-Пусть $a$, $b$ определены (\ref{def_a_b}), тогда $\Rightarrow$ $P_{k} = \det{\left( \begin{array}{cccc}
-z - a_{1}& -b_{1} &\ldots & 0\\
-b_{1}& \ddots &\ddots & \vdots\\
-\vdots & \ddots &\ddots & -b_{k-1}\\
-0& \ldots & -b_{k-1}  & z-a_{k}
-\end{array}\right)} = D_{k}$, \\
-действительно, $D_{a}$ удовлетворяют тому же рекуррентному соотношению
-\[D_{k+1} = (z - a_{k+1})D_{k} - b^{2}_{k}D_{k-1}\]
-из разложения по последнему столбцу с теми же начальными условиями $D_{0} = P_{0} = 1$, $D_{1} = P_{1} = z -a_{1}$.
-В частности,
-\[D_{n} = \det{\left(zE - L\right)} = \prod(z - \lambda_{i}) = P_{n}\]
-$\Rightarrow$ $\lambda_{1},\ldots, \lambda_{k}$  - собственные числа $L(a,b)$.\\
-
-Дополнительный спектр.\\
-
-Нормированные ортогональные многочлены $Q_{i} = \displaystyle\frac{P_{i}}{|P_{i}|} = \left(b_{1}\ldots b_{i}\right)^{-1}P_{i}$.\\
-Рекуррентное соотношение
-\bear{req_pol}
-\frac{b_{i+1}}{b_{i+1}}\frac{P_{i+1}}{b_{1}\ldots b_{i}} + \frac{(a_{i+1} -z)P_{i}}{b_{1}\ldots b_{i}} + \frac{b^{2}_{i}P_{i-1}}{b_{1}\ldots b_{i}} \equiv 0,
-\ear
-учитывая, что $\displaystyle\frac{P_{i+1}}{b_{1}\ldots b_{i}b_{i+1}} = Q_{i+1}$, $\displaystyle\frac{P_{i}}{b_{1}\ldots b_{i}} = Q_{i}$, $\displaystyle\frac{P_{i-1}}{b_{1}\ldots b_{i}} = Q_{i-1}$,
-перепишем  (\ref{req_pol})  как
-\bear{repol2}
-b_{i+1}Q_{i+1} + \left(a_{i+1} -z\right)Q_{i} + b_{i}Q_{i-1} \equiv 0.
-\ear
-Подставим $z= \lambda_{k}$:
-\bear{rec_pol3}
-b_{i+1}Q_{i+1}(\lambda_{k}) + (a_{i+1} - \lambda_{k})Q_{i}(\lambda_{k}) + b_{i}Q_{i-1}(\lambda_{k}) = 0.
-\ear
-$\Rightarrow$ вектор $v_{k} = \xi_{k}\left(Q_{0}(\lambda_{k}),Q_{1}(\lambda_{k}),\ldots,Q_{n-1}(\lambda_{k})\right)$ является собственным нормированным вектором для
-$\lambda = \lambda_{k}$ для $L(a,b)$.
-\bear{Q0}
-Q_{0}(z) =  \frac{1}{\xi^{2}_{1} + \ldots + \xi^{2}_{n}} =1, \qquad v_{k} = (\xi_{k},*,\ldots,*),
-\ear
-то есть $\xi_{k}$ являются первыми компонентами собственного вектора.
-
-\section{Лекция 2}
+\section{Лекция 2. 18 сентября 2015}
 \label{sec:-2}
@@
   \begin{itemize}
-  \item Процедура Каданова (?)
+  \item Процедура Каданова (кратко на лекции, подробно в конспекте)
   \item Ренормгруппа в решеточных моделях
@@
   \item Уравнение Каллана-Симанчика
-  \item Ренормгруппа в двух измерениях
+  \item Ренормгруппа в двух измерениях (только в конспекте)
   \end{itemize}
@@
 
-\section{Лекция 3}
+\section{Лекция 3. 2 октября 2015}
 \label{sec:-3}
@@
   \item Явный вид конформных преобразований полей в $d\geq 3$.
+  \item Тождества Уорда для конформных преобразований
+  \item Конформные преобразования в случае двух измерений
   \end{itemize}
@@
   \left[K_{\mu},P_{\nu}\right]=2i (\eta_{\mu\nu}D - L_{\mu\nu})\\
-  \left[K_{\rho},L_{\mu\nu}\right]=i(\eta_{\rho\mu}P_{\nu}-\eta_{\rho\nu}P_{\mu})\\
+  \left[P_{\rho},L_{\mu\nu}\right]=i(\eta_{\rho\mu}P_{\nu}-\eta_{\rho\nu}P_{\mu})\\
+  \left[K_{\rho},L_{\mu\nu}\right]=i(\eta_{\rho\mu}K_{\nu}-\eta_{\rho\nu}K_{\mu})\\
  \left[L_{\mu\nu},L_{\rho\sigma}\right]=i(\eta_{\nu\rho}L_{\mu\sigma}+\eta_{\mu\sigma}L_{\nu\rho}-\eta_{\mu\rho}L_{\nu\sigma}-\eta_{\nu\sigma}L_{\mu\rho})
@@
 
-\section{Лекция 4}
-\label{sec:-4}
-
-  \begin{itemize}
-  \item Корреляторы квазипримарных полей
-  \item Тождества Уорда
-  \end{itemize}
-
 \subsection{Корреляторы квазипримарных полей}
@@
 \label{sec:tracelessness}
+Материал этого раздела не обсуждался на лекции.
 
@@
 
-\section{Лекция 5}
-\label{sec:-5}
-
-  \begin{itemize}
-  \item Конформная инвариантность в двумерной теории.
-  \item Глобальные конформные преобразования
-  \item Тождества Уорда в двумерной конформной теории
-  \end{itemize}
-
-В лекции \ref{sec:lecture-4} мы получили общее условие на вид инфинитезимальных конформных преобразований:
+В начале лекции мы получили общее условие на вид инфинитезимальных конформных преобразований:
 \begin{equation}
@@
 
-\section{Лекция 6}
+\section{Лекция 4. 9 октября 2015}
 \label{sec:-6}
@@
   \item Центральный заряд. Алгебра Вирасоро
+  \item Классификация минимальных моделей
+  \item Детерминант Каца
+  \item Значения центрального заряда и соответствие с решеточными моделями
   \end{itemize}
@@
 {\it Минимальными} называются теории с конечным числом примарных полей. Чтобы полностью задать такую теорию нужно определить примарные поля и их конформные размерности.
-
-\section{Лекция 7}
-\label{sec:-7}
-
-  \begin{itemize}
-  \item Классификация минимальных моделей
-  \item Детерминант Каца
-  \item Значения центрального заряда и соответствие с решеточными моделями
-  \end{itemize}
 

### 2018-11-24 AffineLieAlgebras/MQFT2018/paper.tex
Paper started

\documentclass{article}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[T1,T2A]{fontenc}
\usepackage[russian,english]{babel}

\usepackage{amsmath,amssymb,amsthm,amsfonts}

\newtheorem{Def}{Definition}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{statement}{Statement}
\newtheorem{Cnj}[Def]{Conjecture}
\newtheorem{Prop}[Def]{Property}
\newtheorem{example}{Example}[section]

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\nf}{\mathfrak{g}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\slnn}{\mathfrak{sl}_{n}}
\newcommand{\sln}[1]{\mathfrak{sl}_{#1}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfg}{\hf_{\gf}}
\newcommand{\hfa}{\hf_{\af}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\sfr}{\mathfrak{s}}
%\newcommand{\dim}{\mathrm{dim} }

\begin{document}
\title{Finite-size scaling of free energy in dimer model on hexagonal domain}

\author{A.A.~Nazarov$^{1}$\\
{\small
  $^{1}$Department of Physics, St. Petersburg State University,} \\
{\small  Ulyanovskaya 1, 198504 St.~Petersburg, Russia}\\
%\small{$^{2}$}\\
%\small{$^{3}$}\\
\small{email:antonnaz@gmail.com}
}
\date{}
\maketitle

\begin{abstract}
    We consider dimer model on a hexagonal lattice. This model can be seen as a ``pile of cubes in the
  corner''. The partition function is given by the determinant of Kasteleyn matrix. We use the
  expression for the partition function to derive the scaling behavior of free energy in the limit
  of lattice mesh tending to zero and temperature tending to infinity. We discuss the connection of
  the expansion coefficients to the geometry of the domain.
\end{abstract}

\section*{Introduction}
\label{sec:introduction}
The dimer model appeared as a very simplified model of solutions \cite{Fowler-1937}. The molecules
are represented by the rigid tiles on a lattice. The partition function was computed on various
lattices and with different boundary conditions \cite{doi:10.1080/14786436108243366,
  P.W-1961,kenyon2009lectures}.

Dimer models are the integrable lattice models of statistical physics that are under an active
theoretical~\cite{zj2000,ferrari} and numerical
investigation~\cite{ks2018}. Particular dimer model appears for certain choice
of parameters in the well-known six-vertex model  \cite{pronko2017thesis}. Dimer models are
closely related to the theory of alternating matrices \cite{elkies1992alternating1,elkies1992alternating2}

Specifically, the well-known limit shape phenomenon~\cite{vershik1977kerov} was discovered for dimer
model~\cite{kenyon2006dimers} and a connection with the theory of random matrices was
established~\cite{johansson2002non}.

Study of dimer models on various lattices and domains leads to interesting connections with the
geometry of curved manifolds and with spectra of discrete and continuous Dirac and Laplace operators
\cite{kenyon2002laplacian,kenyon2000asymptotic}. Scaling limit of dimer model is proven to be
described by a Gaussian free-field theory \cite{kenyon2001dominos}, but finite-size corrections were
not considered previously. These corrections are important to close the gap between numerical
simulations and theoretical results.

We consider a particular case of the dimer model on a hexagonal domain of hexagonal lattice, that
can be seen as a ``pile of cubes in the corner''. The energy of configuration is the total number of
cubes. For this particular case we use an exact combinatorial formula for the partition function to
derive the expressions for scaling limit of free energy and first three terms of the finite-size
corrections. We show that the first term is identically zero. The second term has a universal part
that is given by the Euler constant and a geometry-dependent part that is written explicitly in
elementary functions. The third term which encapsulates logarithmic dependence on the mesh size is
also shown to be universal.

We than compare these results with our previous numeric simulations \cite{belov2018finite}. 
\section{Model definition}
\label{sec:model-definition}
The configurations of the dimer model are perfect matchings (sets of non-touching edges, covering
all the vertices) on some graph ${\cal G}$ with some choice of weights $\omega(e)$ on the edges. The
model is solvable on the bipartite graphs, i.e. the partition function can be computed if the
weights are introduced in such a way that each face with 0 mod 4 edges there is an odd number of
negative edge weights and each face with 2 mod 4 edges has an even number of of negative edge
weights. Then the signs of the edge weights form a so-called ``Kasteleyn orientation''on graph, the
weighting is called ``Kasteleyn weighting'' \cite{kenyon2001dominos,kenyon2009lectures}.

For a bipartite graph ${\cal G}$, color the vertices black and white in such a way that all the
vertices adjacent to the black one are white. Denote by $W$,$B$ the sets of white and black
vertices and by $w,b$ the elements of these sets.

The weights can be encoded as the ``Kasteleyn matrix'' -- weighted, signed adjacency matrix ${\cal K}$ with
the matrix elements ${\cal K}(w,b)$ equal to the weight of the edge $w\to b$: ${\cal K}(w,b)=\omega(w\to b)$.

Then the partition function is equal to the absolute value of the determinant of the Kasteleyn
matrix\cite{P.W-1961,doi:10.1080/14786436108243366}: 
\begin{equation}
  \label{eq:15}
  Z=\sum_{\mathrm{conf}}\prod_{e\in \mathrm{conf}}w(e)=|\det {\cal K}|
\end{equation}

Kasteleyn matrix defines a discrete Dirac operator $D$, in vertex $v$ we have:
\begin{equation}
  \label{eq:16}
  (Df)(v)=\sum_{u}{\cal K}(v,u) f(u)
\end{equation}

Kenyon \cite{kenyon2002laplacian,kenyon2000asymptotic} and others \cite{sridhar2015asymptotic}
considered asymptotics of the determinants of the discrete Dirac and Laplace operators, the problem
that, as can be seen from the above, is very close to the scaling of the free energy. But the finite
size corrections to the free energy scaling were not computed.

We consider coverings of the hexagonal domain on the hexagonal lattice consisting of the subsets of
lattice edges such that every vertex is the endpoint of exactly one edge.

We can draw a rhombus on a dual lattice around each edge in the configuration. The picture of
``cubes in the corner'' presented in the Fig.~\ref{dhf} is obtained. Let us write on the top of each
uppermost cube the height of its column of cubes. Looking at this picture from the top, we obtain a
height function defined on the rectangular domain of the square lattice.

\begin{figure}[htbp]
\center{\scalebox{0.4}{\includegraphics{loz.eps}}}
\caption{\label{dhf}A configuration of dimers on the hexagonal lattice and a corresponding picture
  of ``cubes in the corner''.}
\end{figure}

Let us define the sizes $M$, $N$, and $K$ of the sides of the hexagon.
The above description can be formalized by
%set of configurations of the model can be defined all possible ways to write
setting the non-negative numbers up to $K$ in the boxes of the rectangular $M\times N$ table so that a value in
each box is not greater than values in the adjacent upper and left boxes
\begin{equation}
  \label{eq:1}
  h_{ij}\leq h_{i-1,j},\quad h_{ij}\leq h_{i,j-1}.
\end{equation}

The weight of a particular configuration is given by the exponent of the volume of all cubes or by a
sum of the height function values:
\begin{equation*}
  \label{eq:10}
  E[conf]=\sum_{i,j} h_{ij}=\mathrm{Volume}
\end{equation*}
We set Boltzman constant equal to 1, then the partition function is 
\begin{equation*}
  \label{eq:14}
  Z=\sum_{conf} e^{-\frac{E[conf]}{T}}=\sum_{conf}q^{\mathrm{Vol}[conf]}, 
\end{equation*}
where $q=\exp\left(-1/T\right)$ .

For this particular case, the partition function is given by the classical Macmahon combinatorial
formula~\cite{vuletic2009generalization}
\begin{equation}
  \label{eq:12}
   Z[M,N,K,q]=\prod_{i=1}^{M}\prod_{j=1}^{N}\prod_{k=1}^{K}\frac{1-q^{i+j+k-1}}{1-q^{i+j+k-2}}
\end{equation}

MacMahon formula is obtained for the following definition of the Kasteleyn matrix. Embed the
hexagonal lattice in the complex plane $\mathbb{C}$ in such a way that some edges are parallel to
the real line. Then take
\begin{eqnarray}
  \label{eq:18}
  {\cal K}(w,b)=q^{\Re w+\Im w} \quad \mathrm{if}\quad \Im w=\Im b\\
  {\cal K}(w,b)=1 \quad \mathrm{if}\quad \Im w\neq\Im b
\end{eqnarray}

The scaling limit is achieved on the infinite lattice as $T\to\infty$. To study the scaling behavior
using Monte-Carlo simulations on the finite lattices we will consider temperatures proportional to
the lattice size and, then, extrapolate them to infinity.

%  \frametitle{Kasteleyn matrix and Dirac operator}
%%  Consider infinite-dimensional graded algebra, e.g. $\gf[[t]]$ or $\hat\gf$

%  \frametitle{Free energy scaling}
The   free energy per site is defined as$^{*}$
\footnote{For convenience we omit the factor $\frac{1}{T}$ in the usual definition of the free energy.}
\begin{equation*}
  \label{eq:17}
  % \frac{f}{T}
  f=-\frac{1}{V}\ln Z(M,N,K,q)
\end{equation*}
Here $V$ is the number of vertices, it is twice the number of dimers and twice the number of  cube faces:
\begin{equation*}
  \label{eq:19}
  V=2(MN+NK+MK)
\end{equation*}

%!!!! Kenyon uses $V=\#Dimers$.

We are interested in the scaling limit, combined with the thermodynamic limit, when
$ T\to \infty, \quad M,N,K\to \infty$, such that ratios
$\frac{M}{T}=a,\quad \frac{N}{T}=b, \quad \frac{K}{T}=c$ remain fixed. In what follows we use
$\varepsilon=\frac{1}{T}$, which can be seen as the scale of the model, e.g. mesh size.

In the next section we compute the asymptotic expansion of the free energy $f$ in $\varepsilon$ and
derive $\varepsilon$-independent closed expressions for the first several coefficients in this
expansion.

\section{The computation of the free energy asymptotic expansion}
\label{sec:free-energy-scaling}
First we substitute MacMahon formula \eqref{eq:12} into the free energy definition \eqref{eq:17} and
obtain
\begin{equation}
  \label{eq:20}
    %-\frac{f}{T}
    f=-\frac{1}{V}\ln Z =- \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}
  \ln\left(\frac{1-e^{-\varepsilon (i+j+k)} e^{\varepsilon}}{1-e^{-\varepsilon (i+j+k)} e^{2\varepsilon}}\right)
\end{equation}
Expanding the exponents $e^{\varepsilon}, e^{2\varepsilon}$ and logarithms in powers of $\varepsilon$ we obtain

%%series and split the
%%logarithm of product into the sum of logarithms. Thus we get:
%%\begin{multline}
%%  \label{eq:2}
%%   -\frac{f}{T}= \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}\left\{
%%    \ln\left(1-\frac{1}{e^{\varepsilon(i+j+k)}-1}\sum_{l=1}^{\infty} \frac{\varepsilon^{l}}{l!}\right)-\right.\\
%%  -\left.\ln\left(1-\frac{1}{e^{\varepsilon(i+j+k)}-1}\sum_{l=1}^{\infty} \frac{2^{l}\varepsilon^{l}}{l!}\right)\right\}
%%\end{multline}
%%Then expand the logarithms up to $\varepsilon^{3}$:
\begin{multline}
  \label{eq:4}
  %\frac{f}{T}
  f=- \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}\left\{
    g(i\varepsilon,j\varepsilon,k\varepsilon)+
    \frac{3}{2}\varepsilon\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}\right]\right.\\
  \left.+\frac{7}{6}\varepsilon^{2}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3 g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}+
      2 g(i\varepsilon,j\varepsilon,k\varepsilon)^{3}\right]\right\}  + \mathcal{O}(\varepsilon^{3})
\end{multline}

Here and below we will use the notation:
%Denote by $g$ the expression that will appear multiple times:
\begin{equation}
  \label{eq:5}
  g(x,y,z)=\frac{1}{e^{x+y+z}-1}
\end{equation}

This expression looks like a combination of Riemann sums for some integrals. Note that these sums
are finite, but some of the corresponding integrals are divergent.

%%But we need to obtain
%%corrections in $\varepsilon$ to the integrals as $\varepsilon\to 0$.
%%
%%We can use the following approximation formula for integral of some function $\tilde{f}$ to take
%%care of the corrections:

Let $G$ be an analytic function in the cube $[0,a]\times[0,b]\times[0,c]$, then
\begin{multline}
  \label{eq:21}
  \int_{0}^{a} \int_{0}^{b}\int_{0}^{c}G(x,y,z) dx\; dy\;
  dz\approx\sum_{i=1}^{M}\sum_{j=1}^{N}\sum_{k=1}^{K}\left\{\varepsilon^{3}G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)-\right.\\
  \left.-\left[\frac{\varepsilon^{4}}{2}\left((\partial_{x}+\partial_{y}+\partial_{z})G\right)(i\varepsilon,j\varepsilon,k\varepsilon)\right]+\right.\\
  \left.\varepsilon^{5}\left(\frac{1}{6}(\partial_{x}^{2}+\partial_{y}^{2}+\partial_{z}^{2})+\frac{1}{4}(\partial_{x}\partial_{y}+\partial_{x}\partial_{z}+\partial_{y}\partial_{z})\right)G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)
  \right\}+\mathcal{O}(\varepsilon^{6})
\end{multline}
This formula can be easily derived by dividing the volume of integration into cubes with side
$\varepsilon$ and substituting Taylor series for $G$ into integrals.

We can use this formula to approximate sums by integrals. Similar formula can be written for a
function of two variables and double sums. We will not need higher order terms, but will use the
approximation:
\begin{equation}
\label{eq:8}
  \sum_{j=1}^{N}\sum_{k=1}^{K}\varepsilon^{2}G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)\approx \int_{0}^{b}\int_{0}^{c}G(i\varepsilon,y,z) dy\; dz+\mathcal{O}(\varepsilon^{3}))
\end{equation}

%Now we can apply the integral representation.

Note that
\begin{equation}
  \label{eq:6}
  \begin{array}{c}
    \partial_{x}g(x,y,z)=-g(x,y,z)-g(x,y,z)^{2}\\
    \partial_{x}^{2}g(x,y,z)=g(x,y,z)+3g(x,y,z)^{2}+2g(x,y,z)^{3}
  \end{array}
\end{equation}

Taking this into account and using the relation \eqref{eq:21} to express the triple sum
$ \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}    g(i\varepsilon,j\varepsilon,k\varepsilon)$
in \eqref{eq:4} as the integral plus corrections, we obtain
\begin{multline}
\label{eq:23}
  \frac{f}{T}=-\frac{1}{ab+bc+ca}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{dx dy dz}{e^{x+y+z}-1}+\right.\\
  \left.+\sum_{i=1}^{M}\sum_{j=1}^{N}\sum_{k=1}^{K}\frac{\varepsilon^{5}}{12}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3
      g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}+2
      g(i\varepsilon,j\varepsilon,k\varepsilon)^{3}\right]\right\}
\end{multline}
Due to the equations \eqref{eq:6}, the corrections are of the same form as the higher order terms in
$\varepsilon$. The linear in $\varepsilon$ term in \eqref{eq:4} is cancelled by three partial
derivatives in \eqref{eq:21}. The coefficient of the quadratic term is changed by the addition of
second derivatives from \eqref{eq:21} to $\frac{1}{12}$.

There is no singularity in the sum, but
$\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{dx dy dz}{(\exp(x+y+z)-1)^{3}}$ diverges
logarithmically. So we can not just apply the integral representation~\eqref{eq:21} directly.

We apply the formula \eqref{eq:8} to the internal sums in the triple sum, since there is no
singularity in $\frac{1}{\left((\exp(i\varepsilon+j\varepsilon+k\varepsilon)-1\right)^{3}}$ for
$i\neq 0$:

\begin{equation}
  \label{eq:9}
\sum_{i=1}^{M}\left(\sum_{j=1}^{N}\sum_{k=1}^{K}\frac{\varepsilon^{5}}{12}
      \frac{e^{2(i\varepsilon+j\varepsilon+k\varepsilon)}+e^{i\varepsilon+j\varepsilon+k\varepsilon}}{\left(e^{i\varepsilon+j\varepsilon+k\varepsilon}-1\right)^{3}}  \right)\approx
    \frac{\varepsilon^{3}}{12}\sum_{i=1}^{M} \int_{0}^{b}\int_{0}^{c}
      \left(\frac{e^{2(i\varepsilon+y+z)}+e^{i\varepsilon+y+z}}{\left(e^{i\varepsilon+y+z}-1\right)^{3}}\right) dy dz+\mathcal{O}(\varepsilon^{3})
\end{equation}

The double integral can be taken explicitly, so we obtain
\begin{equation}
  \label{eq:11}
  \frac{\varepsilon^{3}}{12}\sum_{i=1}^{M}\left(     \frac{1}{e^{b+c+i\varepsilon}-1}+
  \frac{1}{1-e^{b+i\varepsilon}}+\frac{1}{1-e^{c+i\varepsilon}}+\frac{1}{e^{i\varepsilon}-1}\right)
\end{equation}

The function $\frac{1}{e^{x}-1}$ has a divergence, so we can not apply integral approximation directly. We first need to 
subtract and add $\frac{1}{i\varepsilon}$. The sum over $i$ of this term can be approximated using Euler formula:
  \begin{equation}
    \label{eq:24}
    \sum_{i=1}^{M}\frac{1}{i}=\frac{1}{M}\sum_{i=1}^{M}\frac{1}{i/M}=\int_{\frac{1}{M}}^{1}\frac{dx}{x}+\gamma+O(\varepsilon)=-\ln\varepsilon+\ln a+\gamma+O(\varepsilon)
  \end{equation}
Thus we get the integral
\begin{multline}
  \label{eq:13}
    \frac{\varepsilon^{3}}{12}\left[\sum_{i=1}^{M}\left(     \frac{1}{e^{b+c+i\varepsilon}-1}+
      \frac{1}{1-e^{b+i\varepsilon}}+\frac{1}{1-e^{c+i\varepsilon}}+\frac{1}{e^{i\varepsilon}-1}-\frac{1}{i\varepsilon}\right)-\ln\varepsilon+\ln a+\gamma+\mathcal{O}(\varepsilon^{3})\right]\approx\\
   \frac{\varepsilon^{2}}{12}\left[\int_{0}^{a}\left(     \frac{1}{e^{b+c+x}-1}+
      \frac{1}{1-e^{b+x}}+\frac{1}{1-e^{c+x}}+\frac{1}{e^{x}-1}-\frac{1}{x}\right)dx-\ln\varepsilon+\ln a+\gamma\right]+\mathcal{O}(\varepsilon^{3})    
\end{multline}
The integral is now taken explicitly, it is equal to
\begin{multline}
  \label{eq:22}
     \frac{\varepsilon^{2}}{12}\left[\int_{0}^{a}\left(     \frac{1}{e^{b+c+x}-1}+
         \frac{1}{1-e^{b+x}}+\frac{1}{1-e^{c+x}}+\frac{1}{e^{x}-1}-\frac{1}{x}\right)dx-\ln\varepsilon+\ln a+\gamma\right]=\\
     \frac{\varepsilon^{2}}{12}\left[\ln \left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{a (e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\ln\varepsilon+\ln a+\gamma\right]
\end{multline}

%%Substituting this approximation and using integral representation for the quadratic
%%  term in $\varepsilon$, we obtain for the free energy:
%%  \begin{multline*}
%%    \frac{f}{T}=-\frac{1}{ab+bc+ca}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{dx dy dz}{e^{x+y+z}-1}+\right.\\
%%    \left.+\frac{\varepsilon^{2}}{12}\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}
%%      \left(\frac{e^{2(x+y+z)}+e^{x+y+z}}{\left(e^{x+y+z}-1\right)^{3}}-\frac{1}{bc}\frac{1}{x}\right)dx dy dz+\right.\\
%%    \left.+\frac{\varepsilon^{2}}{12}(\ln a-\gamma)+\frac{\varepsilon^{2}}{12}\ln \varepsilon\right\}    
%%  \end{multline*}
%%The integral can be taken explicitly, it is equal to
%%\begin{multline}
%%  \label{eq:7}
%%  \int_{0}^{a} \int_{0}^{b}\int_{0}^{c}
%%  \left(\frac{e^{2(x+y+z)}+e^{x+y+z}}{\left(e^{x+y+z}-1\right)^{3}}-\frac{1}{bc}\frac{1}{x}\right)dx~dy~dz=\\
%%  =\ln \left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{a (e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)=\\
%%  =\ln \left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right) -\ln a.
%%\end{multline}

The term $\ln a$ is cancelled by the  and symmetry between $a,b,c$ is restored.
Substituting this approximation into the expression \eqref{eq:23} we obtain 
 the final expression:
\begin{multline}
  \label{eq:3}
  \frac{f}{T}=-\frac{1}{ab+bc+ca}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{dx dy dz}{e^{x+y+z}-1}+\right.\\
  \left.+\frac{\varepsilon^{2}}{12}\left[\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-
      \gamma\right]+\frac{\varepsilon^{2}}{12}\ln \varepsilon\right\} +\mathcal{O}(\varepsilon^{3})
\end{multline}

The coefficient of the logarithmic term is connected to the central charge of the theory. In the
paper \cite{cardy1988finite} it was shown, that this coefficient is $\frac{1}{6}c$. The scaling
behavior of dimer model is described by free fermion theory with $c=\frac{1}{2}$.

  \begin{figure}[h!tb]
    \includegraphics{exact-vs-expansion.pdf}
    \caption{Plot of the expression \eqref{eq:3} for $\varepsilon=\frac{1}{15}\dots\frac{1}{2}$, $a=3,b=2,c=1$
      exact values. Note that difference between exact and approximate values decreases with
      $\varepsilon$.}
  \end{figure}

%%\section{Scaling in the non-uniform model}
%%\label{sec:scaling-non-uniform}
%%
%%Consider a skew 3D partition with the partition function
%%\begin{equation}
%%  \label{eq:25}
%%  Z({q_{t}},\lambda)=\sum_{\lambda(t)}\prod_{t\in\mathbb{Z}}q_{t}^{|\lambda(t)|}
%%\end{equation}
%%
\section*{Conclusion}
\label{sec:conclusion}

  \begin{itemize}
  \item This free energy scaling formula is in agreement with numerical computations
  \item There are Monte-Carlo simulation results that support this scaling
  \item Form of our formula is similar to the asymptotics of discrete Dirac operator obtained by Kenyon
  \end{itemize}

\section*{Acknowledgments}
\label{sec:acknowledgements}
We are grateful to professor Nikolai Reshetikhin for his guidance in this work.
We are thankful to the organizers and participants of the conference MQFT-2018.

This research is supported by RFBR grant No. 18-01-00916.
The calculations were carried out using the facilities of the SPbU Resource Center ``Computational Center of SPbU''.

\bibliographystyle{utphys}
\bibliography{listing,bibliography,dimers}{} 
\end{document}

### 2018-11-24 AffineLieAlgebras/Simons/paper.tex
Minor
Various changes

@@
 \item Critical point, isotropicity
+\end{itemize}
 
@@
         \end{array}
-      \right)=\sqrt{\frac{2}{1+\sqrt{5}}}+\sqrt{\frac{1}{2}\left(1+\sqrt{5}\right)\\
+      \right)=\sqrt{\frac{2}{1+\sqrt{5}}}+\sqrt{\frac{1}{2}\left(1+\sqrt{5}\right)}\\
     W\left(                                      
@@
   \label{eq:6}
-
+  1
 \end{equation}
@@
 
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-
-This research was started during my stay at Simons center for geometry and physics in Stony Brook
-university. I thank Simons foundation for the financial support during my stay, the organizers of
-the program ``Conformal geometry'' and Simons center staff for their hospitality. I also thank
-Christian Hagendorff(?) and Dmitry Chelkak for fruitful discussions.
-
-This work  is supported by
-the Chebyshev Laboratory (Department of Mathematics and Mechanics,
-Saint-Petersburg State University) under the grant 11.G34.31.0026
-of the Government of the Russian Federation and by the Dynasty foundation.
-
-I am grateful to my wife Alexandra for her constant support and care.
+%%  
+%%  \section*{Acknowledgements}
+%%  \label{sec:acknowledgements}
+%%  
+%%  This research was started during my stay at Simons center for geometry and physics in Stony Brook
+%%  university. I thank Simons foundation for the financial support during my stay, the organizers of
+%%  the program ``Conformal geometry'' and Simons center staff for their hospitality. I also thank
+%%  Christian Hagendorff(?) and Dmitry Chelkak for fruitful discussions. 
+%%  
+%%  This work  is supported by
+%%  the Chebyshev Laboratory (Department of Mathematics and Mechanics,
+%%  Saint-Petersburg State University) under the grant 11.G34.31.0026
+%%  of the Government of the Russian Federation and by the Dynasty foundation. 
+%%  
+%%
 

### 2018-11-24 AffineLieAlgebras/TensorProducts/paper.tex
Various changes

@@
 
-\ftc{Recurrent formulae for graded tensor product multiplicities and cluster algebras}
+\ftc{Feigin-Loktev fusion product and formulas for graded tensor product multiplicities}
 
@@
 \begin{abstract}
-
-We show the connection of formulae for tensor product multiplicities with cluster algebras. 
+  Feigin-Loktev fusion product appeared from the study of operator algebra of conformal field
+  theory. It generalizes tensor product of representations of simple Lie algebras by introducing
+  grading. Graded product multiplicities are generalized Kostka polynomials. We start with the
+  fermionic formulae for these multiplicities and derive closed explicit expressions that do not
+  contain summation over integer partitions. We present closed formulas for graded tensor product
+  multiplicities for the fundamental representations of simple Lie algebras of small rank. These
+  formulas can be regarded as q-analogue of multinomial coefficients. 
 \noindent{\it Keywords\/}: Lie algebra, tensor product, multiplicity, cluster algebra, grading
@@
 recurrent approach is not limited to any specific class of modules and is more general.
+
+In certain cases fusion modules are Weyl or Demazure modules of the current algebra
+\cite{chari2001weyl,chari2006weyl,chari2014modules,chari2015demazure}. Then formulas for graded
+tensor product multiplicities are known (see \cite{chari2006weyl,chari2015demazure}). Some of these
+cases involve non-symmetric Macdonald polynomials \cite{0803.1146v1}.
 
@@
    \label{eq:2}
-   F^{i}V=U^{\leq i}(\gf[[t]])v_{1}\otimes\dots\otimes v_{n}.
+   F^{i}V=U^{\leq i}(\gf[[t]])v_{1}\otimes\dots\otimes v_{n},\quad F^{0}V\subset F^{1}V\subset\dots
  \end{equation}
+
+One can show that the number of graded components $F_{j}=F^{j}V/F^{j-1}V$ is finite.
+
  Note that $F^{0}V$ is the irreducible $\gf$-submodule corresponding to the highest weight in the
@@
 
+Having defined the filtration on $V$ one can introduce ``graded tensor product decomposition
+coefficients'' or Hilbert polynomials by the formula
+\begin{equation}
+  \label{eq:4}
+  M^{\mu_{1},\dots \mu_{n}}_{\lambda}(t)=\sum_{k\geq 0}t^{k} \mathrm{dim}\mathrm{Hom}_{\gf} (F_{k},L^{\lambda})
+\end{equation}
+
+If we set $t=1$ these coefficients coincide with tensor product decomposition coefficients:
+\begin{equation}
+  \label{eq:5}
+  M^{\mu_{1},\dots,\mu_{n}}_{\lambda}(1)=  M^{\mu_{1},\dots,\mu_{n}}_{\lambda}
+\end{equation}
+
+ \begin{example}
+   Consider tensor powers of fundamental representation of $sl_{2}$.
+
+ \end{example}
+
+Tensor product as affine Lie algebra module:
+
+Klimyk rule:
+\begin{equation}
+  \label{eq:6}
+  \mathrm{ch}L^{\mu}\cdot\mathrm{ch}L^{\nu}=\sum_{\xi\in \mbox{weights}L^{\nu}}\mathrm{ch} L^{\mu+\xi}
+\end{equation}
+
 \item Fusion product of Virasoro modules, fusion in WZW models and Feigin-Loktev tensor product
-\item KR-formula
+
+\item Use generalized Kirillov-Reshetikhin formula:\\
+    Tensor product of $n_{a,j}$ modules with highest weight $j\omega_{a}$
+    \begin{equation}
+      \label{eq:3}
+      M^{(\bf{n})}_{\lambda}(t)=\sum_{\{m_{a,j}\}}t^{\sum_{a,b,i,j}m_{a,j}C_{\gf}^{ab}\mathrm{min}(i,j)m_{b,j}}\prod_{a,j}\left[\begin{array}{c}p_{a,j}+m_{a,j}\\ m_{a,j}\end{array}\right]_{t},
+      \end{equation}
+      where $C_{\gf}$ -- Cartan matrix,  the sum is restricted:
+      \begin{equation}
+        \label{eq:6}
+        \sum_{a,j}j\omega_{a}(n_{a,j}-\sum_{b}C^{ab}m_{b,j})=\lambda
+      \end{equation}
+      \begin{equation}
+        \label{eq:7}
+        p_{a,j}=\sum_{j}\mathrm{min}(i,j) n_{a,j}-\sum_{b}\mathrm{min}(i,j)m_{b,j}
+      \end{equation}
+     $\left[\begin{array}{c}n\\ k\end{array}\right]_{t}=\frac{(n!)_{t}}{(k!)_{t}((n-k)!)_{t}}$, $(n)_{t}=1+t+\dots t^{n-1}$.
+
 \item Weyl character formula and formulas for tensor product
@@
 
+\section{Simple example}
+\label{sec:simple-example}
+
+Let's remind the properties of $q$-binomial coefficients
+(http://mathworld.wolfram.com/q-BinomialCoefficient.html). Recurrent relation for binomial coefficients
+\begin{equation}
+  \label{eq:7}
+  \left(\begin{array}{c}n\\ k\end{array}\right)=\left(\begin{array}{c}n-1\\
+      k-1\end{array}\right)+\left(\begin{array}{c}n-1\\ k\end{array}\right) 
+\end{equation}
+is easy to prove:
+\begin{equation}
+  \label{eq:8}
+  \frac{n!}{k!(n-k)!}=\frac{(n-1)!}{(k-1)!(n-k)!}+\frac{(n-1)!}{k!(n-k-1)!}
+\end{equation}
+Multiply by $k!(n-k)!/(n-1)!$:
+\begin{equation}
+  \label{eq:9}
+  n=k+(n-k)
+\end{equation}
+
+Similarly for $q$-binomials we should get
+\begin{equation}
+  \label{eq:10}
+  (n)_{q}=(k)_{q}+(n-k)_{q},
+\end{equation}
+but this is not the case, so we need to multiply $(n-k)_{q}$ by $q^{k}$. The resulting recurrent
+relation is
+\begin{equation}
+  \label{eq:11}
+  \left[\begin{array}{c}n\\ k\end{array}\right]_{q}=\left[\begin{array}{c}n-1\\ k-1\end{array}\right]_{q}+q^{k}\left[\begin{array}{c}n-1\\ k\end{array}\right]_{q}
+\end{equation}
+
+For $sl_{2}$ tensor product decomposition coefficients we have
+\begin{equation}
+  \label{eq:12}
+  M^{n}_{k}(t)=\left[\begin{array}{c}n\\ k\end{array}\right]_{t}-\left[\begin{array}{c}n\\ k-1\end{array}\right]_{t}
+\end{equation}
+\begin{equation}
+  \label{eq:13}
+  M^{n}_{k}(t)=M^{n-1}_{k-1}(t)+t^{k-1}M^{n-1}_{k}+(t-1)t^{k-1}\left[\begin{array}{c}n-1\\ k\end{array}\right]_{t}
+\end{equation}
+
+$sl_2$ case here
+Формула Кириллова-Решетихина дает кратность неприводимого представления со старшим весом $\lambda$ в
+тензорном произведении  $n_{a,j}$ представлений со старшими весами $j\omega_{a}$, где $\omega_{a}$
+-- фундаментальный вес с номером $a=1\dots \mathrm{rank}\gf$. 
+\begin{equation}
+  \label{eq:3}
+  M^{(\bf{n})}_{\lambda}(t)=\sum_{\{m_{a,j}\}}t^{\sum_{a,b,i,j}m_{a,j}C_{\gf}^{ab}\mathrm{min}(i,j)m_{b,j}}\prod_{a,j}\left[\begin{array}{c}p_{a,j}+m_{a,j}\\ m_{a,j}\end{array}\right]_{t},
+\end{equation}
+здесь $C_{\gf}$ -- матрица Картана, а сумма ограничена условиями
+\begin{equation}
+  \label{eq:6}
+  \sum_{a,j}j\omega_{a}(n_{a,j}-\sum_{b}C^{ab}m_{b,j})=\lambda
+\end{equation}
+\begin{equation}
+  \label{eq:7}
+  p_{a,i}=\sum_{j}\mathrm{min}(i,j) \left(n_{a,j}-\sum_{b}C^{ab}m_{b,j}\right)
+\end{equation}
+$\left[\begin{array}{c}n\\ k\end{array}\right]_{t}=\frac{(n!)_{t}}{(k!)_{t}((n-k)!)_{t}}$, $(n)_{t}=1+t+\dots t^{n-1}$.
+
+Сперва рассмотрим простейший пример, $\gf=sl_{2}$, $t=1$. Формула Кириллова-Решетихина будет иметь вид
+\begin{equation}
+  \label{eq:1}
+  M_{\lambda}^{(n_{1},n_{2},\dots)}=\sum_{m_{j}}\prod_{j}\left(
+    \begin{array}{c}
+      p_{j}+m_{j}\\
+      m_{j}
+    \end{array}\right),
+\end{equation}
+\begin{equation}
+  \label{eq:2}
+  \sum_{j}j\omega (n_{j}-2m_{j})=\lambda
+\end{equation}
+\begin{equation}
+  \label{eq:4}
+  p_{j}=\sum_{i}\min(i,j)(n_{i}-2m_{i})\geq 0
+\end{equation}
+Попробуем вычислить что-нибудь по этой формуле. Например, кратность представления со старшим весом
+$1$ (индекс Дынкина) в произведении пяти фундаментальных представлений. $n_{1}=5, n_{2}=n_{3}=\dots=0$
+\begin{equation}
+  \label{eq:5}
+  (n_{1}-2m_{1})+2(-2m_{2})+3(-m_{3})+\dots=1
+\end{equation}
+\begin{equation}
+  \label{eq:9}
+  m_{j}\geq 0
+\end{equation}
+\begin{equation}
+  \label{eq:8}
+    (5-2m_{1})+2(-2m_{2})+3(-m_{3})+\dots=1
+\end{equation}
+Решения: $m_{1}=2, m_{j}=0$, $m_{1}=0, m_{2}=1$. 
+Для $p_{j}$ имеем в первом случае $p_{1}=1$, во втором $p_{1}=5-2=3$,$p_{2}= 5+2\cdot (-2)=1$ в итоге кратность
+\begin{equation}
+  \label{eq:10}
+   M_{1}^{(5)}=\left(
+    \begin{array}{c}
+      1+2\\
+      2
+    \end{array}\right)+
+\left(\begin{array}{c}
+      1+1\\
+      1
+    \end{array}\right)=5
+\end{equation}
+
+\section{Proof}
+\label{sec:proof}
+$sl_{3}, so_{5}$ here
+  \begin{itemize}
+  \item $t$-deformation for the tensor product formula for $\mathfrak{sl}_{2}$:
+    \begin{equation}
+      \label{eq:8}
+      m^{\otimes n}_{l}(t)=\left[\begin{array}{c}n-l\\n\end{array}\right]_{t}-      \left[\begin{array}{c}n-l-1\\n\end{array}\right]_{t}
+    \end{equation}
+  \item  $t$-deformation for the tensor product formula for $\mathfrak{sl}_{3}$:
+    \begin{equation}
+      \label{eq:9}
+      \begin{array}{l}
+      M^{n}_{p_{1},p_{2}}(t)=(n,p_{1},p_{2})_{t}-(n,p_{1}-1,p_{2})_{t}+(n,p_{1}-2,p_{2}-1)_{t}\\-(n,p_{1},p_{2}-1)_{t}+(n,p_{1}-1,p_{2}-2)_{t}-(n,p_{1}-2,p_{2}-2)_{t},        
+      \end{array}
+    \end{equation}
+    where $(n,p_{1},p_{2})_{t}=\frac{(n!)_{t}}{(p_{2}!)_{t}((n-p_{1})!)_{t}((p_{1}-p_{2})!)_{t}}$
+  \end{itemize}
+
+Compare to Kirillov-Reshetikhin formula:
+
+Рассмотрим теперь алгебру $sl_{3}$. Матрица Картана
+\begin{equation}
+  \label{eq:11}
+  C=\left(\begin{array}{cc}
+      2 & -1\\
+      -1 & 2
+    \end{array}\right)
+\end{equation}
+Вычислим кратность представления со старшим весом с индексами Дынкина $(1,2)$ в произведении пяти
+фундаментальных представлений $L^{\omega_{1}}$. $n_{1,1}=5, n_{ij}=0$. Уравнения на $m_{aj}$:
+\begin{eqnarray}
+  \label{eq:12}
+  (5-2m_{1,1}+m_{2,1})+2(-2m_{12}+m_{22})+3(-2m_{13}+m_{23})+4(-2m_{14}+m_{24})+\dots=1\\
+  (m_{1,1}-2m_{2,1})+2(m_{12}-2m_{22})+3(m_{13}-2m_{23})+4(m_{14}-2m_{24})+\dots=2
+\end{eqnarray}
+сложим:
+\begin{equation}
+  \label{eq:13}
+  (5-m_{1,1}-m_{2,1})-2(m_{12}+m_{22})-3(m_{13}+m_{23})-4(m_{14}+m_{24})+\dots=3
+\end{equation}
+или
+\begin{equation}
+  \label{eq:14}
+    -(m_{1,1}+m_{2,1})-2(m_{12}+m_{22})-3(m_{13}+m_{23})-4(m_{14}+m_{24})+\dots=-2
+\end{equation}
+решения:
+$m_{11}=2, m_{ij}=0$, $m_{12}=1, m_{ij}=0$
+Вычислим $p_{ij}$. 
+\begin{eqnarray}
+  \label{eq:15}
+  p_{11}=(n_{11}-2m_{11}+m_{21})+(-2m_{12}+m_{22})+\dots\\
+  p_{21}=(m_{11}-2m_{21})+(m_{12}-2m_{22})+\dots\\
+  p_{12}=(n_{11}-2m_{11}+m_{21})+2(-2m_{12}+m_{22})+\dots\\
+  p_{22}=(m_{11}-2m_{21})+2(m_{12}-2m_{22})+\dots
+\end{eqnarray}
+В первом случае $p_{11}=1$, а остальные не нужны. Во втором $p_{11}=3, p_{21}=1, p_{12}=1,
+p_{22}=2$, из которых нужно только $p_{12}$. Подставляем в формулу Кириллова-Решетихина:
+\begin{equation}
+  \label{eq:16}
+    M_{(2,1)}^{(5)}=\left(
+    \begin{array}{c}
+      1+2\\
+      2
+    \end{array}\right)+
+\left(\begin{array}{c}
+      1+1\\
+      1
+    \end{array}\right)=5
+\end{equation}
+Что совпадает с разложением тензорного произведения другими способами.
+
+Заметим, что здесь, как и в случае $sl_{2}$, при поиске решений надо учитывать те $m_{ij}$, для
+которых $n_{ij}=0$.
+
+\section*{Conlusion}
+\label{sec:conlusion}
+
+\begin{equation}
+  \label{eq:17}
+  \sum_{\nu=j}^{q-1} t^{(q-\nu)(q-\nu-1)} C_{q-j}^{\nu-j} C_{l-q-1}^{q-\nu-1} = 
+  \sum_{\nu=j}^{q-1} t^{(q-\nu)(q-\nu-1)} C_{q-j}^{q-\nu} C_{l-q-1}^{q-\nu-1} 
+\end{equation}
+обозначим $q-1-\nu$ через $k$, тогда $\nu=q-1-k$, суммирование идет по $k=0\dots q-j-1$ и мы имеем
+\begin{equation}
+  \label{eq:18}
+  \sum_{k=0}^{q-j-1} t^{(k+1)k} C_{q-j}^{k+1} C_{l-q-1}^{k} =   \sum_{k=0}^{q-j-1} t^{(k+1)k} C_{q-j}^{q-j-1-k} C_{l-q-1}^{k} = C_{l-j-1}^{q-j-1},
+\end{equation}
+где в последнем равенстве использовано тождество Ва
 \cite{di2013quantum}
+
+Recurrent relation for fusion modules characters is here \cite{di2015difference}
 \bibliography{cluster}{} 

### 2018-11-24 CFT/central-charge/paper.tex
Various changes

\documentclass[aps,prl,reprint]{revtex4-1}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
%\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}2
\usepackage[russian]{babel}
\usepackage[utf8]{inputenc}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\nfp}{\mathfrak{n}^{+}}
\newcommand{\nfm}{\mathfrak{n}^{-}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\uf}{\mathfrak{u}}
\newcommand{\sfr}{\mathfrak{s}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}

\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\sfh}{\hat{\mathfrak{s}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\begin{document}
\title{Determination of CFT central charge from computer simulations using Wang-Landau algorithm}
\author{Pavel Belov}
\affiliation{Saint-Petersburg state university}
\author{Anton Nazarov}
\affiliation{Saint-Petersburg state university}
\author{Alexander Sorokin}
\affiliation{Saint-Petersburg Nuclear Physics Institute}

\begin{abstract}
  We propose a new way to determine a central charge of conformal field theory models corresponding
  to the 2d lattice models. The idea is to use Wang-Landau algorithm to determine free energy of the
  lattice model on the torus and then calculate central charge from free energy scaling w.r.t. torus
  radii. In this way central charge is directly obtained with a good precision while fit of data is
  relatively easy. We illustrate the method using Ising, tricritical Ising (Blume-Capel), Potts and
  site-diluted Ising models.
\end{abstract}

\maketitle

\section{Introduction}
\label{sec:introduction}

Quantum field theory is an excellent framework to understand the influence of geometry on the
systems behavior in solid state physics. This is especially true in case of critical behavior of
two-dimensional systems, where conformal invariance plays crucial role.

Conformal field theory in two dimensions is especially powerful since it possess an
infinite-dimensional Virasoro symmetry. The Hilbert space is a union of Virasoro algebra modules. If
the number of these modules is finite the theory is called a minimal model of CFT. Conformal field
theories have small number of parameters -- central charge and conformal weights of primary fields.
It is possible to compute analytically or numerically a lot of observables such as multi-point
correlation functions. Also it is possible to study a lot of different boundary conditions, behavior
in different geometries and various perturbations of conformal field theories. All these properties
make CFT very useful for the description of various experiments and numerical simulations. But the
problem is that often there are no suitable counterparts to the CFT fields in the lattice models or
experiments. So it is apriori not known which CFT describes the critical behavior of a given lattice
model. The most important task is to find value of CFT central charge. Several methods were proposed
by different authors \cite{feiguin2007interacting}, \cite{bastiaansen1998monte},
\cite{lauwers1991estimation} (?). First of these methods is only applicable to the one-dimensional
integrable models and the second requires careful simulations and precise multi-parametric numerical
fitting of conformal weights. We propose more direct approach based on the newer Wang-Landau
simulation algorithm \cite{wang2001efficient}.

\section{Theory}
\label{sec:theory}

Wang-Landau algorithm simulates the energy distribution $\rho(E)=e^{g(E)}$. Energy range is split
in some number of intervals (which can coincide with the number of discrete energies). The algorithm starts with random
lattice configuration, empty array of logarithms of energy densities $g(E_{1}),\dots,g(E_{n})$,
empty visitation histogram $h(E_{1}),\dots,h(E_{n})$ and some initial value (usually
1) of constant $a$. Then one lattice site and new value of
lattice variable at this site are chosen at
random. New state with the changed value at site is accepted with the probability
$e^{g(E_{new})-g(E_{old})}$, visitation number $h(E)$ is increased by 1 and $g(E)$ is increased by
$a$. This procedure is repeated until the visitation histogram is relatively flat. Then the value of
$a$ is divided by 2, the histogram is emptied and next step of algorithm begins. Usually about 20-30
such steps are done in simulations. Having the energy distribution $\rho(E)$ the partition function
is given by
\begin{equation}
  \label{eq:8}
  Z=\sum_{E_{i}} \rho(E_{i}) e^{-\frac{E_{i}}{T}}
\end{equation}

Availability of the partition function in simulations is the crucial difference between Wang-Landau and
other Monte-Carlo methods, such as Metropolis or Wolf algorithms. Having the partition function we
can consider free energy density
\begin{equation}
  \label{eq:10}
  f(T)=-\frac{T}{Volume}\log Z(T)
\end{equation}
In conformal field theory there is a well-known relation connecting free energy on an infinite
cylinder of circumference $N$ with the free energy on a plane (see, for example
\cite{difrancesco1997cft}, Chapter 5):
\begin{equation}
  \label{eq:11}
  f_{cyl}(N)=f_{plane}-\frac{\pi c}{6 N^{2}}.
\end{equation}
Central charge appears in this relation so it could be used to extract central charge value from the
simulation data. In order to do so we simulate a model on a torus of circumferences $N$ and $M$
to obtain free energy density $f_{tor}(N,M)$. Then we extrapolate free energy value when $M\to\infty$
to get free energy on a cylinder $f_{cyl}(N)=\lim_{M\to\infty} f_{tor}(N,M)$. Central charge can be
obtained by fitting $f_{cyl}(N)$ data into the equation~\eqref{eq:11}.

For this program to work we need to study the behavior  of $f_{tor}(N,M)$ when $M\to\infty$.
To do so we consider CFT partition function on the torus of circumferences $M$ and $N$.
  Bastiaansen and Knops \cite{bastiaansen1998monte} had to consider a skewed torus since at
that time there was no Monte-Carlo method for the free energy computation, but for us straight torus is
enough. Modular parameter of the torus is given by the quotient of two periods:
\begin{equation}
  \label{eq:2}
  \tau=i\frac{M}{N}
\end{equation}
In the usual CFT quantization one needs to chose time direction. We take it to be along the
period $M$ of the torus. The Hamiltonian is the generator of time translation and is given by a sum
of Virasoro generators $L_{0}, \bar L_{0}$:
\begin{equation}
  \label{eq:3}
  H=\frac{2\pi}{N} (L_{0}+\bar L_{0})-\frac{\pi c}{6 N},
\end{equation}
the additional term with the central charge $c$ appears from the conformal mapping from plane.

We can consider the exponent of the Hamiltonian as a row-to-row transfer matrix. Then translating
from row to row along the time direction $M$ times we get a partition function  on the torus
\begin{equation}
  \label{eq:1}
  Z=\sum_{j} \left<j\right|e^{-M H} \left|j\right>
\end{equation}
The sum here is over the states in Hilbert space. 
The Hilbert space of a conformal field theory is a direct sum of Virasoro algebra modules $V_{i}$ generated
by primary fields $\varphi_{i}$ and parametrised by conformal weights $h_{i}, \bar h_{i}$. Conformal
field theory always contains the identity operator with the conformal weight $h_{0}=0$. The
conformal weights of primary fields are between zero and one:  $0\leq h_{i},\bar h_{\bar i}\leq 1$. We can
choose the basis of Virasoro eigenstates $\left|h_{i}+m_{i},\bar h_{i}+\bar m_{i}\right>$, where
$m_{i},\bar m_{i}$ are positive integers:
\begin{equation}
  \label{eq:4}
  \begin{array}{l}
    L_{0}\left|h_{i}+m_{i},\bar h_{i}+\bar m_{i}\right>=(h_{i}+m_{i})\left|h_{i}+m_{i},\bar h_{i}+\bar
    m_{i}\right>\\
  \bar L_{0}\left|h_{i}+m_{i},\bar h_{i}+\bar m_{i}\right>=(\bar h_{i}+\bar m_{i})\left|h_{i}+m_{i},\bar h_{i}+\bar
    m_{i}\right>    
  \end{array}
\end{equation}

It is customary to use the parameter $q=\exp(2\pi i \tau)$.  In our case of straight torus the parameter $q$ is real, $q=\bar q=e^{-\frac{2\pi M}{N}}$.
Then for the partition function we get
\begin{multline}
  \label{eq:5}
  \frac{Z(q)}{Z_{0}}=q^{-\frac{c}{24}} \bar q^{-\frac{c}{24}}\sum_{j} n_{j} q^{h_{j}+m_{j}}\bar q^{\bar h_{j}+\bar
    m_{j}}=\\=\sum_{i,\bar i} {\cal M}_{i,\bar i}\chi_{i}(q) \bar\chi_{\bar i}(\bar q),
\end{multline}
where $j$ runs over all states and $i, \bar i$ run over primary states,
$\chi_{i}(q)=q^{h_{i}-\frac{c}{24}}\sum_{n\geq 0}d_{i}(n)q^{n}$ is the character of the Virasoro algebra module, $n_{j}$ the multiplicity of
the secondary state and ${\cal M}_{i,\bar i}$ is the multiplicity of the representation $V_{i}\otimes\bar
V_{\bar i}$. The partition function is defined up to normalization $Z_{0}$ that is interpreted as a
partition function on a plane. The multiplicities $\mathcal{M}_{i,\bar i}$ are constrained by  the
modular invariance of the partition function.  We do not need to know them and we also can obtain
conformal weights $h_{i}$ from the simulation data due to the following considerations. First it is important to note that CFT always contains the
identity field with $h_{0}=\bar h_{0}=0$ with the multiplicity $\mathcal{M}_{0,0}=1$.

The partition function in conformal field theory does not depend on temperature since CFT is
applicable only in thermodynamic limit in critical point. To connect CFT computation with the
simulation data we need to insert critical temperature in the expression for the free energy
$  f(N,M)=-\frac{T_{c}}{MN}\log Z(q)$. Let's denote by $f_{0}$ the limit
$\lim_{N\to\infty,M\to\infty}f(N,M)$, this term corresponds to the partition function on the plane.
Then we have
\begin{multline}
  \label{eq:13}
  f(N,M)=f_{0} - \frac{T_{c}\pi c}{6
    N^{2}}\\-\frac{T_{c}}{MN}\log\left[1+\sum_{i\neq 0,\bar i\neq 0} \mathcal{M}_{i,\bar i} q^{h_{i}+\bar h_{\bar
        i}} \left(\sum_{n\geq 0} d_{i}(n) q^{n}\right)\left(\sum_{m\geq 0} d_{\bar i}(m)
      q^{m}\right)\right.\\ +\left.\sum_{n\geq 1}d_{0,0}(n)q^{n}\right]
\end{multline}
One in the last logarithm is due to the identity field and we've moved the  contributions from the  secondary states of
the identity field $\sum_{n\geq 1}d_{0,0}(n)q^{n}$ to the right. Note that if $M\geq N$ the
parameter $q=e^{-\frac{2\pi M}{N}}$ is very small, so we can expand the logarithm holding only
leading contributions with $q^{h_{i}}$:
\begin{multline}
  \label{eq:14}
  f(N,M)=f_{0} - \frac{T_{c}\pi c}{6
    N^{2}}-\frac{T_{c}}{MN}\left[\sum_{i\neq 0,\bar i\neq 0} \mathcal{M}_{i,\bar i} q^{h_{i}+\bar h_{\bar i}} \right].
\end{multline}
If $M>N$ the third term is much smaller than the second one, so in principle we can use measures for
$f(N,M)$ for $M>>N$ (e.g. $M=10 N$) as values of $f(N)$. As the measure of inaccuracy we can take
the difference between $f(N, M)$ and $f(N, M-N)$.

From  the exact value of CFT partition
function for the Ising model on the torus we see that this gives reasonable precision.
CFT partition function for the critical Ising model on the torus is given by the formula
\begin{equation}
  \label{eq:15}
  Z_{Ising}(q)=\frac{1}{2}\left(\left|\frac{\theta_{2}(0|\tau)}{\eta(\tau)}\right|+\left|\frac{\theta_{3}(0|\tau)}{\eta(\tau)}\right|+\left|\frac{\theta_{4}(0|\tau)}{\eta(\tau)}\right|\right),
\end{equation}
where $\theta_{2},\theta_{3},\theta_{4}$ are Jacobi theta functions. Computing $f(N,M)$ numerically from this
expression it is easy to see that there is no difference in 8 digits after dot between $f(N,10 N)$
and $f(N)$.

On other hand fitting with the just the smallest conformal weight $h+\bar h$ also gives very good
precision. One can even extract conformal weights $h_{i}$ from such a fit.

If it is not known what conformal field theory describes critical behavior of the model
under consideration one can also take mean value between fits with $h_{min}=0$ and $h_{min}=1$ . We
show the difference in precision for all three methods in the following table. The value for $f(10)$
is obtained in three ways from the same simulation data for $f(10,n\cdot 10)$, where we took
$n=1\dots 10$ and used 25-steps Wang-Landau algorithm with flatness level $0.8$. 
\begin{equation}
  \label{eq:16}
  \begin{array}{c||c|c|c}
    \mbox{method} & f(10,100) & \mbox{fit}\; h+\bar h=\frac{1}{8} & \mbox{mean of fits} \;0,1\\
    \hline
    f(10) & 2.11568 & 2.11577 & 2.115 \\
    \mbox{inaccuracy} & 0.00009 & 0.00009 & 0.002
  \end{array}
\end{equation}
Taking into account the measure of inaccuracy for all three methods we obtain following values for
central charge. We used the following set of $N$-values:
$N=5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,24,30,40$.

\begin{equation}
  \label{eq:17}
  \begin{array}{c||c|c|c}
    \mbox{method} & f(10,100) & \mbox{fit}\; h+\bar h=\frac{1}{8} & \mbox{mean of fits} \;0,1\\
    \hline
    c &  0.507\pm 0.001 & 0.506\pm 0.001 & 0.46\pm 0.06 
  \end{array}
\end{equation}
Note that we have not estimated the imprecision from the finite lattice size. If we use only bigger
lattices with $N\geq 15$  from the same data set,  we get a bit different results for central
charge: $c=0.509\pm 0.002, c=0.505\pm 0.002, c=0.46\pm 0.13$. We see that the inaccuracy from using
the finite lattices is of the same order as the difference between first and second methods.

In the next section we present detailed results of our simulations of different lattice models.

\section{Simulation}
\label{sec:simulation}

We did the
simulation as follows. First we simulated the system on the lattices with periodic boundary
conditions for different values of $M/N$ and different values of circumference $N$. The partition
function and free energy are available in simulations subject to proper normalization. We used the
fact that for lattice models vacuum degeneracy is known to normalize the partition function. Then we
fit the dependence on $M/N$ of our data for free energy with the decreasing exponent $-b e^{-a
  \frac{M}{N}}$ to account for the third and other terms in formula \eqref{eq:7}. In the limit
$\frac{M}{N}\to\infty$ only first two terms survive, so with this fit we have obtained limit values
of $f(N)$. Now from the fit with $\frac{1}{N^{2}}$ we determine the value of central charge $c$.

Let us illustrate our method on the simplest example of the Ising model. The vacuum is twice
degenerate so we normalize the obtained energy distribution  ...

Pics here

q-state Potts

Tricritical Ising

Site-diluted Ising model

In recent study \cite{najafi2016monte} of the domain wall geometry of site-dilute Ising model it was
suggested that the central charge of the theory depends on dilution parameter $p$. We see in our
simulations that to the contrary the central charge is universal.

\section*{Conclusion}
\label{sec:conclusion}

\bibliography{listing}{} 
\bibliographystyle{apsrev4-1}

\end{document}

### 2018-11-24 GeneralOverview/Lectures/Integrability2015.tex
Various changes

@@
-\documentclass[a4paper,12pt]{article}
-\usepackage[utf8x]{inputenc}
-\usepackage[russian]{babel}
-\usepackage{ucs}
-\usepackage[unicode,verbose]{hyperref}
-\usepackage{amsmath,amssymb,amsthm}
-\usepackage{mathtools}
-\usepackage{pb-diagram}
-\usepackage{multicol}
-\usepackage{cmap}
-\usepackage{color}
-\usepackage{graphicx}
-\pagestyle{plain}
-
-% \usepackage{verbatim} 
-\newenvironment{comment}
-{\par\noindent{\bf TODO}\\}
+\documentclass[a4paper,12pt]{article} \usepackage[utf8x]{inputenc} \usepackage[russian]{babel}
+\usepackage{ucs} \usepackage[unicode,verbose]{hyperref} \usepackage{amsmath,amssymb,amsthm}
+\usepackage{mathtools} \usepackage{pb-diagram} \usepackage{multicol} \usepackage{cmap}
+\usepackage{color} \usepackage{graphicx} \pagestyle{plain}
+
+% \usepackage{verbatim} \newenvironment{comment} {\par\noindent{\bf TODO}\\}
 {\\\hfill$\scriptstyle\blacksquare$\par}
 
-\newtheorem{statement}{Statement}
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\theoremstyle{definition}
-\newtheorem{corollary}{Corollary}[theorem]
-\theoremstyle{definition}
-\newtheorem{mynote}{Замечание}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
-\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
-\newcommand{\co}[1]{\stackrel{\circ }{#1}}
-\newcommand{\pia}{\pi_{\mathfrak{a}}}
-\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
-\newcommand{\af}{\mathfrak{a}}
-\newcommand{\afb}{\mathfrak{a}_{\bot}}
-
-\title{Конформная инвариантность и интегрируемость в теории поля\\
-  \small{СПбГУ, физический факультет университет, кафедра ФВЭиЭЧ}
-}
-\author{Антон Назаров\\
-  \small{СПбГУ, физический факультет,}\\
-  \small{ кафедра физики высоких энергий и элементарных частиц;}\\
-  \texttt{antonnaz@gmail.com}
-}
-\date{Осенний семестр 2015 года}
-
-\def\barr{\left(\begin{array}}
-\def\earr{\end{array}\right)}
-\def\beq#1{\begin{equation}\label{#1}}
-\def\eeq{\end{equation}}
-\def\ber#1{\begin{eqnarray}\label{#1} &&\nqq}%   left alignment
+\newtheorem{statement}{Statement} \newtheorem{lemma}{Lemma} \newtheorem{theorem}{Theorem}
+\theoremstyle{definition} \newtheorem{corollary}{Corollary}[theorem] \theoremstyle{definition}
+\newtheorem{mynote}{Замечание}[section] \theoremstyle{definition}
+\newtheorem{definition}{Definition} \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
+\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}} \newcommand{\co}[1]{\stackrel{\circ }{#1}}
+\newcommand{\pia}{\pi_{\mathfrak{a}}} \newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
+\newcommand{\af}{\mathfrak{a}} \newcommand{\afb}{\mathfrak{a}_{\bot}}
+
+\title{Конформная инвариантность и интегрируемость в теории поля\\ \small{СПбГУ, физический
+факультет университет, кафедра ФВЭиЭЧ} } \author{Антон Назаров\\ \small{СПбГУ, физический
+факультет,}\\ \small{ кафедра физики высоких энергий и элементарных частиц;}\\
+\texttt{antonnaz@gmail.com} } \date{Осенний семестр 2015 года}
+
+\def\barr{\left(\begin{array}} \def\earr{\end{array}\right)} \def\beq#1{\begin{equation}\label{#1}}
+\def\eeq{\end{equation}} \def\ber#1{\begin{eqnarray}\label{#1} &&\nqq}% left alignment
 \def\eer{\end{eqnarray}}
 
-\newcommand{\bear}[1]{\begin{eqnarray}\label{#1}}
-\newcommand{\ear}{\end{eqnarray}}
-
-\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
-\catcode`\@=11 \@addtoreset{equation}{section}\catcode`\@=12
-\newcommand{\N}{ {\mathbb N} }
-\newcommand{\R}{ {\mathbb R} }
-\newcommand{\SL}{\mathop{\rm sl}\nolimits}
-\newcommand{\SO}{\mathop{\rm so}\nolimits}
-\newcommand{\SP}{\mathop{\rm sp}\nolimits}
-\newcommand{\ts}{\textstyle}
-\newcommand{\ds}{\displaystyle}
-\newcommand{\fn}{\footnote}
-\newcommand{\fnm}{\footnotemark}
+\newcommand{\bear}[1]{\begin{eqnarray}\label{#1}} \newcommand{\ear}{\end{eqnarray}}
+
+\renewcommand{\theequation}{\arabic{section}.\arabic{equation}} \catcode`\@=11
+\@addtoreset{equation}{section}\catcode`\@=12 \newcommand{\N}{ {\mathbb N} } \newcommand{\R}{
+{\mathbb R} } \newcommand{\SL}{\mathop{\rm sl}\nolimits} \newcommand{\SO}{\mathop{\rm so}\nolimits}
+\newcommand{\SP}{\mathop{\rm sp}\nolimits} \newcommand{\ts}{\textstyle}
+\newcommand{\ds}{\displaystyle} \newcommand{\fn}{\footnote} \newcommand{\fnm}{\footnotemark}
 \newcommand{\fnt}{\footnotetext}
@@
 \begin{document}
-\maketitle
-\thispagestyle{empty}
-\begin{abstract}
-  Программа курса
+\maketitle \thispagestyle{empty}
+\begin{abstract} Программа курса
 \end{abstract}
@@
 Обзор применения интегрируемых систем в соответствии между N=4 теорий суперсимметричной теорией
-Янга-Миллса (N=4 SYM) и теорией суперструн типа IIB содержится в коллективной работе \cite{ReviewAdSCFT}.
+Янга-Миллса (N=4 SYM) и теорией суперструн типа IIB содержится в коллективной работе
+\cite{ReviewAdSCFT}.
 
 \subsection{Введение}
-\label{sec:intro}
-Чем интересны двумерные системы?
+\label{sec:intro} Чем интересны двумерные системы?
 
@@
 \begin{equation}
-  \label{eq:2}
-  P_i=\frac{1}{Z}e^{-\beta E_i}, \quad \beta=\frac{1}{T}
-\end{equation}
-Мы используем систему единиц, в которой постоянная Больцмана равна единице $k_B=1$, введем
-$\beta=\frac{1}{T}$. Статсумма:
-\begin{equation}
-  \label{eq:3}
-  Z=\sum_i e^{-\beta E_i}.
-\end{equation}
-Свободная энергия
-\begin{equation}
-  \label{eq:4}
-  F=-T\ln Z
-\end{equation}
-Внутренняя энергия
-\begin{equation}
-  \label{eq:5}
-  U=-\frac{1}{Z}\frac{\partial Z}{\partial \beta}=-T^2 \frac{\partial}{\partial T}\left(\frac{F}{T}\right)
-\end{equation}
-Телоемкость равна производной внутренней энергии по температуре при заданном объеме
-\begin{equation}
-  \label{eq:6}
-  C=\left(\frac{\partial U}{\partial T}\right)_V=-T\frac{\partial^2 F}{\partial T^2}
-\end{equation}
-Таким образом статсумма является производящей функцией всех термодинамических величин. Вычисление
-статсуммы в реальных системах --- это сложная задача. Макроскопическое описание имеет смысл только в
-термодинамическом пределе, когда число частиц стремится к бесконечности $N\to \infty$.
+  \label{eq:2} P_i=\frac{1}{Z}e^{-\beta E_i}, \quad \beta=\frac{1}{T}
+\end{equation} Мы используем систему единиц, в которой постоянная Больцмана равна единице $k_B=1$,
+введем $\beta=\frac{1}{T}$. Статсумма:
+\begin{equation}
+  \label{eq:3} Z=\sum_i e^{-\beta E_i}.
+\end{equation} Свободная энергия
+\begin{equation}
+  \label{eq:4} F=-T\ln Z
+\end{equation} Внутренняя энергия
+\begin{equation}
+  \label{eq:5} U=-\frac{1}{Z}\frac{\partial Z}{\partial \beta}=-T^2 \frac{\partial}{\partial
+T}\left(\frac{F}{T}\right)
+\end{equation} Телоемкость равна производной внутренней энергии по температуре при заданном объеме
+\begin{equation}
+  \label{eq:6} C=\left(\frac{\partial U}{\partial T}\right)_V=-T\frac{\partial^2 F}{\partial T^2}
+\end{equation} Таким образом статсумма является производящей функцией всех термодинамических
+величин. Вычисление статсуммы в реальных системах --- это сложная задача. Макроскопическое описание
+имеет смысл только в термодинамическом пределе, когда число частиц стремится к бесконечности $N\to
+\infty$.
 
@@
 \begin{equation}
-  \label{eq:1}
-  E=J\sum_{\left<i,j\right>} \sigma_i\cdot \sigma_j-h\sum_i \sigma_i
-\end{equation}
-Суммирование в первом члене ведется только по парам ближайших соседей, второй член --- это
-взаимодействие со внешним полем $h$. Пусть система состоит из $N$ вершин. Она имеет $2^N$ различных
-конфигураций. Случай $J>0$ соответствует ферромагнетику, $J<0$ --- антиферромагнетику. При $h=0$
-низшее энергетическое состояние двукратно вырождено --- это состояние, в котором все спины
+  \label{eq:1} E=J\sum_{\left<i,j\right>} \sigma_i\cdot \sigma_j-h\sum_i \sigma_i
+\end{equation} Суммирование в первом члене ведется только по парам ближайших соседей, второй член
+--- это взаимодействие со внешним полем $h$. Пусть система состоит из $N$ вершин. Она имеет $2^N$
+различных конфигураций. Случай $J>0$ соответствует ферромагнетику, $J<0$ --- антиферромагнетику. При
+$h=0$ низшее энергетическое состояние двукратно вырождено --- это состояние, в котором все спины
 направлены вверх или вниз.
@@
 
-При исследовании магнетиков нас интересуют следующие термодинамически величины.
-Намагниченность, которая равна среднему значению спина по всем конфигурациям $[\sigma]$:
+При исследовании магнетиков нас интересуют следующие термодинамически величины. Намагниченность,
+которая равна среднему значению спина по всем конфигурациям $[\sigma]$:
 \begin{equation}
   \label{eq:7}
-  M=\left<\sigma_j\right>=\frac{1}{NZ}\sum_{[\sigma]}\left(\sum_i\sigma_i\right)e^{-\beta E[\sigma]}=-\frac{1}{N}\frac{\partial F}{\partial h}.
-\end{equation}
-Намагниченность является параметром порядка --- в упорядоченной (анти)ферромагнитной фазе она отлична от нуля.
+M=\left<\sigma_j\right>=\frac{1}{NZ}\sum_{[\sigma]}\left(\sum_i\sigma_i\right)e^{-\beta
+E[\sigma]}=-\frac{1}{N}\frac{\partial F}{\partial h}.
+\end{equation} Намагниченность является параметром порядка --- в упорядоченной (анти)ферромагнитной
+фазе она отлична от нуля.
 
@@
 \begin{equation}
-  \label{eq:8}
-  \chi=\left.\frac{\partial M}{\partial h}\right|_{h=0}=\frac{1}{N}\frac{\partial}{\partial h}\left(\frac{1}{Z}\sum_{[\sigma]}\left(\sum_i \sigma_i\right)e^{-\beta E[\sigma]}\right)=\frac{1}{NT}\left(\left<\sigma_{\mathrm{tot}}^2\right>-\left<\sigma_{\mathrm{tot}}\right>^2\right)
-\end{equation}
-Здесь мы ввели обозначение $\sigma_{\mathrm{tot}}=\sum_i \sigma_i$. Видно, что магнитная
-восприимчивость пропорциональна дисперсии полного спина. Введем парную корреляционную функцию
-\begin{equation}
-  \label{eq:9}
-  \Gamma(i-j)=\left<\sigma_i\sigma_j\right>.
-\end{equation}
-Из-за вращательной и трансляционной инвариантности $\Gamma$ зависит только от расстояния между
-вершинами $\left|i-j\right|$. Связная корреляционная функция
+  \label{eq:8} \chi=\left.\frac{\partial M}{\partial
+h}\right|_{h=0}=\frac{1}{N}\frac{\partial}{\partial h}\left(\frac{1}{Z}\sum_{[\sigma]}\left(\sum_i
+\sigma_i\right)e^{-\beta
+E[\sigma]}\right)=\frac{1}{NT}\left(\left<\sigma_{\mathrm{tot}}^2\right>-\left<\sigma_{\mathrm{tot}}\right>^2\right)
+\end{equation} Здесь мы ввели обозначение $\sigma_{\mathrm{tot}}=\sum_i \sigma_i$. Видно, что
+магнитная восприимчивость пропорциональна дисперсии полного спина. Введем парную корреляционную
+функцию
+\begin{equation}
+  \label{eq:9} \Gamma(i-j)=\left<\sigma_i\sigma_j\right>.
+\end{equation} Из-за вращательной и трансляционной инвариантности $\Gamma$ зависит только от
+расстояния между вершинами $\left|i-j\right|$. Связная корреляционная функция
 \begin{equation}
@@
 \Gamma_c(i-j)=\left<\sigma_i-\sigma_j\right>_c=\left<\sigma_i\sigma_j\right>-\left<\sigma_i\right>\left<\sigma_j\right>.
-\end{equation}
-Можно показать, что
-\begin{equation}
-  \label{eq:11}
-  \chi=\beta\sum_i\Gamma(i)_c.
-\end{equation}
-То есть магнитная восприимчивость --- это мера статистической когерентности системы, она растет с
-ростом зависимости спинов между собой.
+\end{equation} Можно показать, что
+\begin{equation}
+  \label{eq:11} \chi=\beta\sum_i\Gamma(i)_c.
+\end{equation} То есть магнитная восприимчивость --- это мера статистической когерентности системы,
+она растет с ростом зависимости спинов между собой.
 
@@
 
-Здесь есть один фазовый переход при конечной температуре. 
-Критическая температура
-\begin{equation}
-  \label{eq:27}
-  T_c:\quad \sh \frac{2J}{T_c}=1
-\end{equation}
-При $T>T_c$ спонтанная намагниченность \eqref{eq:7} исчезает. При $T<T_c$ она не равна нулю и
-стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_c$. Это упорядоченная ферромагнитная фаза. Около
-критической точки спонтанная намагниченность ведет себя как 
-\begin{equation}
-  \label{eq:28}
-  M\sim \left|T_c-T\right|^{\frac{1}{8}}
-\end{equation}
-Направление намагниченности определяется тем, куда было направлено внешнее поле до того, как его устремили к $0$.
+Здесь есть один фазовый переход при конечной температуре. Критическая температура
+\begin{equation}
+  \label{eq:27} T_c:\quad \sh \frac{2J}{T_c}=1
+\end{equation} При $T>T_c$ спонтанная намагниченность \eqref{eq:7} исчезает. При $T<T_c$ она не
+равна нулю и стремится к $1$ при $T\to 0$ и к $0$ при $T\to T_c$. Это упорядоченная ферромагнитная
+фаза. Около критической точки спонтанная намагниченность ведет себя как
+\begin{equation}
+  \label{eq:28} M\sim \left|T_c-T\right|^{\frac{1}{8}}
+\end{equation} Направление намагниченности определяется тем, куда было направлено внешнее поле до
+того, как его устремили к $0$.
 
@@
 \begin{equation}
-  \label{eq:29}
-  \chi=\frac{\partial M}{\partial h}\sim \left|T-T_c \right|^{-\frac{7}{4}}.
-\end{equation}
-Вдали от критической точки корреляторы $\Gamma_c(i)$ убывают экспоненциально с расстоянием.
-Характерная длина убывания $\xi$ называется корреляционной длиной 
-\begin{equation}
-  \label{eq:30}
-  \left<\sigma_i\sigma_j\right>_c\sim e^{-\frac{\left|i-j\right|}{\xi(T)}}\quad \left|i-j\right|>>1.
-\end{equation}
-При $T\to T_c$ корреляционная длина расходится
-\begin{equation}
-  \label{eq:31}
-  \xi(T)\sim \frac{1}{\left|T-T_c\right|}.
-\end{equation}
-Такое поведение характеризует переходы второго рода и наблюдается в критических точках фазовой диаграммы.
+  \label{eq:29} \chi=\frac{\partial M}{\partial h}\sim \left|T-T_c \right|^{-\frac{7}{4}}.
+\end{equation} Вдали от критической точки корреляторы $\Gamma_c(i)$ убывают экспоненциально с
+расстоянием. Характерная длина убывания $\xi$ называется корреляционной длиной
+\begin{equation}
+  \label{eq:30} \left<\sigma_i\sigma_j\right>_c\sim e^{-\frac{\left|i-j\right|}{\xi(T)}}\quad
+\left|i-j\right|>>1.
+\end{equation} При $T\to T_c$ корреляционная длина расходится
+\begin{equation}
+  \label{eq:31} \xi(T)\sim \frac{1}{\left|T-T_c\right|}.
+\end{equation} Такое поведение характеризует переходы второго рода и наблюдается в критических
+точках фазовой диаграммы.
 
@@
 \begin{equation}
-  \label{eq:32}
-  \Gamma(\vec n)\sim \frac{1}{\left|\vec n\right|^{d-2+\eta}}
-\end{equation}
-Поведение термодинамических величин определяется критическими индексами. Перечислим их вместе со
-значениями в двумерной модели Изинга. Эти значения получены из точных решений модели. 
+  \label{eq:32} \Gamma(\vec n)\sim \frac{1}{\left|\vec n\right|^{d-2+\eta}}
+\end{equation} Поведение термодинамических величин определяется критическими индексами. Перечислим
+их вместе со значениями в двумерной модели Изинга. Эти значения получены из точных решений модели.
 \begin{table}[h!tb]
@@
 \noindent \centering{
-\begin{tabular}{|l|l|l|}
-  \hline
-  Критический  & Термодинамическая & Значение индекса в \\
-  индекс &  величина  & двумерной модели Изинга\\
-  \hline
-  $\alpha$ & $C\sim \frac{1}{\left|T-T_c\right|^{\alpha}}$ & $0$\\
-  $\beta$ & $M\sim \left|T-T_c\right|^{\beta}$ & $\frac{1}{8}$\\
-  $\gamma$ & $\chi\sim \frac{1}{\left|T-T_c\right|^{\gamma}}$ & $\frac{7}{4}$\\
-  $\delta$ & $M\sim h^{\frac{1}{\delta}}$ & $15$ \\
-  $\nu$ & $\xi\sim \frac{1}{\left|T-T_c\right|^{\nu}}$ & $1$\\
-  $\eta$ & $\Gamma(\vec n)\sim \left|\vec n\right|^{2-d-\eta}$ & $\frac{1}{4}$\\
-  \hline
+\begin{tabular}{|l|l|l|} \hline Критический & Термодинамическая & Значение индекса в \\ индекс &
+величина & двумерной модели Изинга\\ \hline $\alpha$ & $C\sim \frac{1}{\left|T-T_c\right|^{\alpha}}$
+& $0$\\ $\beta$ & $M\sim \left|T-T_c\right|^{\beta}$ & $\frac{1}{8}$\\ $\gamma$ & $\chi\sim
+\frac{1}{\left|T-T_c\right|^{\gamma}}$ & $\frac{7}{4}$\\ $\delta$ & $M\sim h^{\frac{1}{\delta}}$ &
+$15$ \\ $\nu$ & $\xi\sim \frac{1}{\left|T-T_c\right|^{\nu}}$ & $1$\\ $\eta$ & $\Gamma(\vec n)\sim
+\left|\vec n\right|^{2-d-\eta}$ & $\frac{1}{4}$\\ \hline
 \end{tabular}
-\caption{Критические индексы и их значения в модели Изинга в 2 измерениях}
-}
+\caption{Критические индексы и их значения в модели Изинга в 2 измерениях} }
 \end{table}
@@
 этой и следующей лекциях излагается решение Вдовиченко, как наиболее короткое и простое. Изложение
-взято из книги \cite{belavin2001lect}. 
-Энергия системы в отсутствие внешнего поля дается выражением
-\begin{equation}
-  \label{eq:98}
-  E[\sigma]=-J\sum_{\left<i,j\right>}\sigma_i \sigma_j .
-\end{equation}
-Введем обозначение
-\begin{equation}
-  \label{eq:99}
-  K=J/T.
-\end{equation}
-Статсумма имеет вид
-\begin{equation}
-  \label{eq:100}
-  Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}\sigma_i\sigma_j}
-\end{equation}
-Будем считать, что в наша решетка $\mathcal{L}$ состоит из $N=mn$ узлов. Обозначим через $M$ число
-пар $\left<i,j\right>$. $M=2N-n-m$. Для простоты будем накладывать тороидальные граничные условия.
-Тогда $M=2N$. Введем {\it дуальную решетку $\mathcal{L}^*$}, вершинами которой будут центры граней
-исходной решетки.  
-Нам удобно будет использовать действие в следующем виде:
-\begin{equation}
-  \label{eq:101}
-  Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1+1)}=e^{KM} \sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
+взято из книги \cite{belavin2001lect}. Энергия системы в отсутствие внешнего поля дается выражением
+\begin{equation}
+  \label{eq:98} E[\sigma]=-J\sum_{\left<i,j\right>}\sigma_i \sigma_j .
+\end{equation} Введем обозначение
+\begin{equation}
+  \label{eq:99} K=J/T.
+\end{equation} Статсумма имеет вид
+\begin{equation}
+  \label{eq:100} Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}\sigma_i\sigma_j}
+\end{equation} Будем считать, что в наша решетка $\mathcal{L}$ состоит из $N=mn$ узлов. Обозначим
+через $M$ число пар $\left<i,j\right>$. $M=2N-n-m$. Для простоты будем накладывать тороидальные
+граничные условия. Тогда $M=2N$. Введем {\it дуальную решетку $\mathcal{L}^*$}, вершинами которой
+будут центры граней исходной решетки. Нам удобно будет использовать действие в следующем виде:
+\begin{equation}
+  \label{eq:101} Z=\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1+1)}=e^{KM}
+\sum_{[\sigma]}e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
 \end{equation}
@@
 \begin{equation}
-  \label{eq:102}
-  X[\sigma]=e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
-\end{equation}
-Заметим, что все состояния можно упорядочить следующим образом:
+  \label{eq:102} X[\sigma]=e^{K\sum_{\left<i,j\right>}(\sigma_i\sigma_j-1)}.
+\end{equation} Заметим, что все состояния можно упорядочить следующим образом:
 \begin{itemize}
@@
   \begin{equation}
-    \label{eq:103}
-    X[\sigma]=\left(e^{-2K}\right)^4
+    \label{eq:103} X[\sigma]=\left(e^{-2K}\right)^4
   \end{equation}
@@
 \item И так далее.
-\end{itemize}
-В итоге мы можем записать все вклады $X[\sigma]$ в виде суммы по всевозможным замкнутым контурам на
-дуальной решетке. Если ввести обозначение 
-\begin{equation}
-  \label{eq:104}
-  \kappa=e^{-2K},
-\end{equation}
-то
-\begin{equation}
-  \label{eq:105}
-  X[\sigma]=\kappa^{l[c]}.
-\end{equation}
-Здесь $l[c]$ --- длина контура $c$ на дуальной решетке, соответствующего состоянию $\sigma$. Тогда
-для $Z$ получаем 
-\begin{equation}
-  \label{eq:106}
-  Z=e^{MK}\sum_c \kappa^{l[c]}. 
-\end{equation}
-Такое выражение называется низкотемпературным разложением, так как оно хорошо сходится при малых
-температурах ($K>>1$).
+\end{itemize} В итоге мы можем записать все вклады $X[\sigma]$ в виде суммы по всевозможным
+замкнутым контурам на дуальной решетке. Если ввести обозначение
+\begin{equation}
+  \label{eq:104} \kappa=e^{-2K},
+\end{equation} то
+\begin{equation}
+  \label{eq:105} X[\sigma]=\kappa^{l[c]}.
+\end{equation} Здесь $l[c]$ --- длина контура $c$ на дуальной решетке, соответствующего состоянию
+$\sigma$. Тогда для $Z$ получаем
+\begin{equation}
+  \label{eq:106} Z=e^{MK}\sum_c \kappa^{l[c]}.
+\end{equation} Такое выражение называется низкотемпературным разложением, так как оно хорошо
+сходится при малых температурах ($K>>1$).
 
@@
 \begin{equation}
-  \label{eq:80}
-  Z=(\ch K)^M\sum_{[\sigma]}\prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)
-\end{equation}
-Будем раскрывать скобки в произведении, сопоставляя каждому множителю $\sigma_i\sigma_j \th K$ ребро
-на решетке $\mathcal{L}$, соединяющее вершины $i,j$. Заметим, что вклад непрерывного пути,
-соединяющего вершины $i$ и $k$ пропорционален $(\sigma_i \sigma_{i+1}) (\sigma_{i+1}\sigma_{i+2})
-(\sigma_{i+2}\sigma_{i+3})\dots (\sigma_{k-1}\sigma_k)=\sigma_{i}\sigma_k$, где мы пронумеровали
-вершины вдоль пути. То есть вклад от незамкнутого пути дается его концами, а вклад от замкнутого
-контура всегда равен 1.  Тогда произведение запишется в виде 
-\begin{equation}
-  \label{eq:107}
-  \prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)=1+a_1 \th K +a_2 \th^2 K+\dots,
-\end{equation}
-где $a_k$ дается суммой по всем контурам $c$ (не обязательно замкнутым или односвязным) длины $k$. 
-Чтобы вычислить статсумму, нам надо просуммировать такие выражения по всем возможным конфигурациям
-спинов. Заметим, что для любого незамкнутого контура и любой конфигурации найдется другая
-конфигурация, куда вклад этого контура входит с противоположным знаком (так как спины направлены в
-другую сторону). А вклад замкнутого контура равен $\th^{l[c]}K$ в любой конфигурации, то есть входит
-в статсумму $2^N$ раз. В результате получаем высокотемпературное разложение статсуммы в виде суммы
-по всем замкнутым контурам на решетке $\mathcal{L}$: 
-\begin{equation}
-  \label{eq:108}
-  Z=(\ch K)^M 2^N \sum_c (\th K)^{l[c]}=(\ch K)^M 2^N \sum_c \kappa^{l[c]}.
-\end{equation}
-Здесь мы ввели обозначение $\kappa=\th K$. Это разложение хорошо сходится при $K<<1$.
+  \label{eq:80} Z=(\ch K)^M\sum_{[\sigma]}\prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th
+K\right)
+\end{equation} Будем раскрывать скобки в произведении, сопоставляя каждому множителю
+$\sigma_i\sigma_j \th K$ ребро на решетке $\mathcal{L}$, соединяющее вершины $i,j$. Заметим, что
+вклад непрерывного пути, соединяющего вершины $i$ и $k$ пропорционален $(\sigma_i \sigma_{i+1})
+(\sigma_{i+1}\sigma_{i+2}) (\sigma_{i+2}\sigma_{i+3})\dots
+(\sigma_{k-1}\sigma_k)=\sigma_{i}\sigma_k$, где мы пронумеровали вершины вдоль пути. То есть вклад
+от незамкнутого пути дается его концами, а вклад от замкнутого контура всегда равен 1. Тогда
+произведение запишется в виде
+\begin{equation}
+  \label{eq:107} \prod_{\left<i,j\right>}\left(1+\sigma_i \sigma_j \th K\right)=1+a_1 \th K +a_2
+\th^2 K+\dots,
+\end{equation} где $a_k$ дается суммой по всем контурам $c$ (не обязательно замкнутым или
+односвязным) длины $k$. Чтобы вычислить статсумму, нам надо просуммировать такие выражения по всем
+возможным конфигурациям спинов. Заметим, что для любого незамкнутого контура и любой конфигурации
+найдется другая конфигурация, куда вклад этого контура входит с противоположным знаком (так как
+спины направлены в другую сторону). А вклад замкнутого контура равен $\th^{l[c]}K$ в любой
+конфигурации, то есть входит в статсумму $2^N$ раз. В результате получаем высокотемпературное
+разложение статсуммы в виде суммы по всем замкнутым контурам на решетке $\mathcal{L}$:
+\begin{equation}
+  \label{eq:108} Z=(\ch K)^M 2^N \sum_c (\th K)^{l[c]}=(\ch K)^M 2^N \sum_c \kappa^{l[c]}.
+\end{equation} Здесь мы ввели обозначение $\kappa=\th K$. Это разложение хорошо сходится при $K<<1$.
 
@@
 \begin{equation}
-  \label{eq:109}
-  f=-\lim_{N\to \infty}\frac{\ln Z_N}{N}.
-\end{equation}
-Решетки $\mathcal{L}$ и $\mathcal{L}^*$ отличаются только на границе, поэтому в термодинамическом
-пределе $M/N\to 2$ и выражения для удельной свободной энергии из высокотемпературного и
-низкотемпературного разложений должны совпадать. Если ввести функцию $\Phi(\kappa)=\lim_{N\to
-  \infty}\frac{1}{N} \ln \left(\sum_c \kappa^{l[c]}\right)$, то свободная энергия запишется в
-высокотемпературном и низкотемпературном разложениях следующим образом: 
-\begin{equation}
-  \label{eq:110}
-  -f(K)=2K+\Phi(e^{-2K})=\ln(2\ch^2 K)+\Phi(\th K)
-\end{equation}
-Это и есть соотношение дуальности {\it Крамерса-Ванье}. Если ввести $K^*$ так, что $\th K^*=e^{-2K}$
-или $\sh 2K^* \sh 2K=1$, то соотношение дуальности будет связывать теорию при температуре $K$ и
-$K^*$: 
-\begin{equation}
-  \label{eq:111}
-  f(K^*)=f(K)+2K-\ln(2\ch^2 K^*).
-\end{equation}
-Рассмотрим теперь поведение теории в критической точке $K_c$. В ней свободная энергия $f(K_c)$ не
-аналитична. Тогда $f$ должна быть не аналитична и при $K^*=K_c$. Если предположить, что критическая
-точка единственна, то мы можем найти ее из требования $K=K^*$, то есть $2K=\ln(2\ch^2 K)$ или 
-\begin{equation}
-  \label{eq:112}
-  \sh^2 2K_c=1.
-\end{equation}
-Теперь перейдем к точному решению модели Изинга.
+  \label{eq:109} f=-\lim_{N\to \infty}\frac{\ln Z_N}{N}.
+\end{equation} Решетки $\mathcal{L}$ и $\mathcal{L}^*$ отличаются только на границе, поэтому в
+термодинамическом пределе $M/N\to 2$ и выражения для удельной свободной энергии из
+высокотемпературного и низкотемпературного разложений должны совпадать. Если ввести функцию
+$\Phi(\kappa)=\lim_{N\to \infty}\frac{1}{N} \ln \left(\sum_c \kappa^{l[c]}\right)$, то свободная
+энергия запишется в высокотемпературном и низкотемпературном разложениях следующим образом:
+\begin{equation}
+  \label{eq:110} -f(K)=2K+\Phi(e^{-2K})=\ln(2\ch^2 K)+\Phi(\th K)
+\end{equation} Это и есть соотношение дуальности {\it Крамерса-Ванье}. Если ввести $K^*$ так, что
+$\th K^*=e^{-2K}$ или $\sh 2K^* \sh 2K=1$, то соотношение дуальности будет связывать теорию при
+температуре $K$ и $K^*$:
+\begin{equation}
+  \label{eq:111} f(K^*)=f(K)+2K-\ln(2\ch^2 K^*).
+\end{equation} Рассмотрим теперь поведение теории в критической точке $K_c$. В ней свободная энергия
+$f(K_c)$ не аналитична. Тогда $f$ должна быть не аналитична и при $K^*=K_c$. Если предположить, что
+критическая точка единственна, то мы можем найти ее из требования $K=K^*$, то есть $2K=\ln(2\ch^2
+K)$ или
+\begin{equation}
+  \label{eq:112} \sh^2 2K_c=1.
+\end{equation} Теперь перейдем к точному решению модели Изинга.
 
 \subsubsection{Решение Вдовиченко.}
-\label{sec:ising-solution}
-Суть состоит в сведении вычисления статсуммы в высокотемпературном разложении к решению некоторого
-рекуррентного соотношения. Это соотношение записывается в матричном виде и его решение дается следом
-матрицы, который можно вычислить после преобразования Фурье.
+\label{sec:ising-solution} Суть состоит в сведении вычисления статсуммы в высокотемпературном
+разложении к решению некоторого рекуррентного соотношения. Это соотношение записывается в матричном
+виде и его решение дается следом матрицы, который можно вычислить после преобразования Фурье.
 
@@
 самопересечения и путь с самопересечением (Смотри рисунок \ref{fig:ising-1}).
-\begin{figure}[h!tb]
-  \centering
+\begin{figure}[h!tb] \centering
     \includegraphics[width=80mm]{ising1}
@@
   \label{fig:ising-1}
-\end{figure}
-Поэтому такие вклады надо брать с множителем $(-1)^{\nu(\Gamma)}$, где $\nu(\Gamma)$ - число
-самопересечений пути $\Gamma$. 
-Статсумма в высокотемпературном разложении \eqref{eq:108} дается выражением 
-\begin{equation}
-  \label{eq:113}
-  Z=(\ch K)^M 2^N\sum_c \kappa^{l[c]}.
-\end{equation}
-Обозначим сумму через $\Sigma=\sum_c \kappa^{l[c]}$. Перепишем её через сумму по путям 
-\begin{equation}
-  \label{eq:114}
-  \Sigma=\sum_{\Gamma}(-1)^{\nu(\Gamma)} \kappa^{l[\Gamma]}
-\end{equation}
-Воспользуемся следующим утверждением, доказательство которого оставляется в качестве упражнения. Для
-любой связной замкнутой петли на плоскости с $\nu$ самоперечечениями и полным углом поворота
-$2\pi(n+1)$ (при ее обходе) верно равенство 
-\begin{equation}
-  \label{eq:115}
-  (-1)^{\nu}=(-1)^n.
-\end{equation}
-Сопоставим каждому узлу в пути $\Gamma$ с углом поворота $\varphi$ в нем ($0,\pm \pi/2$) множитель $e^{\frac{i\varphi}{2}}$.
-Тогда после обхода петли полный множитель будет равен $(-1)^{\nu+1}$.
-Для несвязного пути, состоящего из $s$ компонент --- $(-1)^{m+s}$, где $m=\sum \nu$.
-То есть если ввести для пути $\Gamma$ общий множитель $s(\Gamma)$, то $\Sigma$ можно переписать в виде
-\begin{equation}
-  \label{eq:116}
-  \Sigma=\sum_{\Gamma}(-1)^{s(\Gamma)}\prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}\kappa^{l[\Gamma]}
-\end{equation}
-Обозначим через $F^{(1)}_l$ сумму по всем однокомпонентным петлям длины $l$, через $F^{(2)}_l$ --- двухкомпонентным и так далее.
-\begin{equation}
-  \label{eq:117}
-  F^{(1)}_l=\sum_{\Gamma:l[\Gamma]=l} \prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}.
-\end{equation}
-Тогда $F_l^{(2)}$ можно вычислить через $F^{(1)}$:
-\begin{equation}
-  \label{eq:118}
-  F^{(2)}_l=\frac{1}{2!}\sum_{l_1,l_2:l_1+l_2=l} F^{(1)}_{l_1} F^{(1)}_{l_2}
-\end{equation}
-Аналогично
-\begin{equation}
-  \label{eq:119}
-  F^{(s)}_l=\frac{1}{s!}\sum_{l_1,\dots l_s:l_1+\dots+l_s=l} F^{(1)}_{l_1}\dots F^{(1)}_{l_s}
-\end{equation}
-Теперь мы можем выразить $\Sigma$ через $F^{(1)}$:
-\begin{equation}
-  \label{eq:120}
-  \Sigma=\sum_{s=0}^{\infty}\frac{(-1)^s}{s!}\sum_{l_1\dots l_s=1}^{\infty} \kappa^{l_1+\dots+l_s}F^{(1)}_{l_1} \dots F^{(1)}_{l_s}=
-  \sum_{s=0}^{\infty}\frac{(-1)^s}{s!}\left(\sum_{l=1}^{\infty} \kappa^{l}F^{(1)}_{l} \right)^s =\exp\left(-\sum_{l=1}^{\infty} \kappa^l F_l\right)
-\end{equation}
-Петли с числом узлов больше $N$ не дают вклада, так как содержат повторяющиеся ребра и поэтому сократятся (Смотри рисунок \ref{fig:ising-2}).
-\begin{figure}[h!tb]
-  \centering
+\end{figure} Поэтому такие вклады надо брать с множителем $(-1)^{\nu(\Gamma)}$, где $\nu(\Gamma)$ -
+число самопересечений пути $\Gamma$. Статсумма в высокотемпературном разложении \eqref{eq:108}
+дается выражением
+\begin{equation}
+  \label{eq:113} Z=(\ch K)^M 2^N\sum_c \kappa^{l[c]}.
+\end{equation} Обозначим сумму через $\Sigma=\sum_c \kappa^{l[c]}$. Перепишем её через сумму по
+путям
+\begin{equation}
+  \label{eq:114} \Sigma=\sum_{\Gamma}(-1)^{\nu(\Gamma)} \kappa^{l[\Gamma]}
+\end{equation} Воспользуемся следующим утверждением, доказательство которого оставляется в качестве
+упражнения. Для любой связной замкнутой петли на плоскости с $\nu$ самоперечечениями и полным углом
+поворота $2\pi(n+1)$ (при ее обходе) верно равенство
+\begin{equation}
+  \label{eq:115} (-1)^{\nu}=(-1)^n.
+\end{equation} Сопоставим каждому узлу в пути $\Gamma$ с углом поворота $\varphi$ в нем ($0,\pm
+\pi/2$) множитель $e^{\frac{i\varphi}{2}}$. Тогда после обхода петли полный множитель будет равен
+$(-1)^{\nu+1}$. Для несвязного пути, состоящего из $s$ компонент --- $(-1)^{m+s}$, где $m=\sum \nu$.
+То есть если ввести для пути $\Gamma$ общий множитель $s(\Gamma)$, то $\Sigma$ можно переписать в
+виде
+\begin{equation}
+  \label{eq:116} \Sigma=\sum_{\Gamma}(-1)^{s(\Gamma)}\prod_{j\in \Gamma}
+e^{\frac{i\varphi_j}{2}}\kappa^{l[\Gamma]}
+\end{equation} Обозначим через $F^{(1)}_l$ сумму по всем однокомпонентным петлям длины $l$, через
+$F^{(2)}_l$ --- двухкомпонентным и так далее.
+\begin{equation}
+  \label{eq:117} F^{(1)}_l=\sum_{\Gamma:l[\Gamma]=l} \prod_{j\in \Gamma} e^{\frac{i\varphi_j}{2}}.
+\end{equation} Тогда $F_l^{(2)}$ можно вычислить через $F^{(1)}$:
+\begin{equation}
+  \label{eq:118} F^{(2)}_l=\frac{1}{2!}\sum_{l_1,l_2:l_1+l_2=l} F^{(1)}_{l_1} F^{(1)}_{l_2}
+\end{equation} Аналогично
+\begin{equation}
+  \label{eq:119} F^{(s)}_l=\frac{1}{s!}\sum_{l_1,\dots l_s:l_1+\dots+l_s=l} F^{(1)}_{l_1}\dots
+F^{(1)}_{l_s}
+\end{equation} Теперь мы можем выразить $\Sigma$ через $F^{(1)}$:
+\begin{equation}
+  \label{eq:120} \Sigma=\sum_{s=0}^{\infty}\frac{(-1)^s}{s!}\sum_{l_1\dots l_s=1}^{\infty}
+\kappa^{l_1+\dots+l_s}F^{(1)}_{l_1} \dots F^{(1)}_{l_s}=
+\sum_{s=0}^{\infty}\frac{(-1)^s}{s!}\left(\sum_{l=1}^{\infty} \kappa^{l}F^{(1)}_{l} \right)^s
+=\exp\left(-\sum_{l=1}^{\infty} \kappa^l F_l\right)
+\end{equation} Петли с числом узлов больше $N$ не дают вклада, так как содержат повторяющиеся ребра
+и поэтому сократятся (Смотри рисунок \ref{fig:ising-2}).
+\begin{figure}[h!tb] \centering
   \includegraphics[width=40mm]{ising2}
@@
   \label{fig:ising-2}
-\end{figure}
-Наша задача свелась к вычислению $F_l$.
-Рассмотрим произвольную вершину с координатами $(n,m)$.
-Пронумеруем направления выхода из нее индексом $\nu=1,2,3,4$ против часовой стрелки.
-Обозначим через $W_l (n,m,\nu|n_0,m_0,\nu_0)$ сумму по всем путям длины $l$, соединяющим вершины $(n_0,m_0)$ и $(n,m)$.
-Первый шаг пути в направлении $\nu_0$.
-Учитываются множители $e^{\frac{i\varphi}{2}}$ начиная с узла, следующего за $(n_0,m_0)$ и заканчивая узлом $(n,m)$.
-Последний шаг пути не должен быть в направлении, противоположном $\nu$.
-Тогда $F_l$ можно записать как сумму $W_l(n,m,\nu|n,m,\nu)$ по всем вершинам решетки.
-Каждая петля при этом будет учтена $2l$ раз, так как у нее $l$ возможных вершин начала и два возможных направления.
-\begin{equation}
-  \label{eq:121}
-  F_l=\frac{1}{2l}\sum_{(n,m)\in \mathcal{L}} \sum_{\nu=1,2,3,4} W_l(n,m,\nu|n,m,\nu)
-\end{equation}
-Если мы зафиксируем начальную вершину путей $(n_0,m_0,\nu_0)$, то сумму по путям длины $l+1$ можно выразить через сумму по путям длины $l$.
-В вершину $(n,m,1)$ пути могут входить с направлений $2,3,4$, то есть последний шаг может быть из вершины $(n-1,m)$ в направлении $1$, из вершины $(n,m-1)$ в направлении $2$ и из вершины $(n,m-1)$ в направлении $4$.
-Аналогично для других направлений. Тогда
+\end{figure} Наша задача свелась к вычислению $F_l$. Рассмотрим произвольную вершину с координатами
+$(n,m)$. Пронумеруем направления выхода из нее индексом $\nu=1,2,3,4$ против часовой стрелки.
+Обозначим через $W_l (n,m,\nu|n_0,m_0,\nu_0)$ сумму по всем путям длины $l$, соединяющим вершины
+$(n_0,m_0)$ и $(n,m)$. Первый шаг пути в направлении $\nu_0$. Учитываются множители
+$e^{\frac{i\varphi}{2}}$ начиная с узла, следующего за $(n_0,m_0)$ и заканчивая узлом $(n,m)$.
+Последний шаг пути не должен быть в направлении, противоположном $\nu$. Тогда $F_l$ можно записать
+как сумму $W_l(n,m,\nu|n,m,\nu)$ по всем вершинам решетки. Каждая петля при этом будет учтена $2l$
+раз, так как у нее $l$ возможных вершин начала и два возможных направления.
+\begin{equation}
+  \label{eq:121} F_l=\frac{1}{2l}\sum_{(n,m)\in \mathcal{L}} \sum_{\nu=1,2,3,4} W_l(n,m,\nu|n,m,\nu)
+\end{equation} Если мы зафиксируем начальную вершину путей $(n_0,m_0,\nu_0)$, то сумму по путям
+длины $l+1$ можно выразить через сумму по путям длины $l$. В вершину $(n,m,1)$ пути могут входить с
+направлений $2,3,4$, то есть последний шаг может быть из вершины $(n-1,m)$ в направлении $1$, из
+вершины $(n,m-1)$ в направлении $2$ и из вершины $(n,m-1)$ в направлении $4$. Аналогично для других
+направлений. Тогда
 \begin{equation}
   \label{eq:122}
-\begin{array}{l}
-W_{l+1}(n,m,1)=W_l(n-1,m,1)+e^{-i\pi/4} W_l(n,m-1,2)+e^{i\pi/4}W_l(n,m+1,4)\\
+\begin{array}{l} W_{l+1}(n,m,1)=W_l(n-1,m,1)+e^{-i\pi/4} W_l(n,m-1,2)+e^{i\pi/4}W_l(n,m+1,4)\\
 W_{l+1}(n,m,2)=e^{i\pi/4}W_l(n-1,m,1)+W_l(n,m-1,2)+e^{-i\pi/4}W_l(n+1,m,3)\\
@@
 \end{array}
-\end{equation}
-Эти рекуррентные соотношения можно переписать в матричном виде, если ввести матрицу коэффициентов $\Lambda$:
-\begin{equation}
-  \label{eq:124}
-  W_{l+1}(n,m,\nu)=\sum_{p,q,\mu}\Lambda(n,m,\nu|t,u,\mu) W_l(t,u,\mu)
-\end{equation}
-Если вершины $(t,u)$ и $(n,m)$ не являются соседними, то $\Lambda(n,m,\nu|p,q,\mu)=0$.
-Матрица $\Lambda$ не зависит от начала пути.
-$W_{l+1}=\Lambda W_l$, поэтому мы $F_l$ дается следом $l$-той степени $\Lambda$:
-\begin{equation}
-  \label{eq:125}
-  F_l=\frac{1}{2l}\mathrm{Tr} W_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l W_0
-\end{equation}
-Но матрица $W_0=I$ (единичной матрице), поэтому
-\begin{equation}
-  \label{eq:126}
-  F_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l =\frac{1}{2l} \sum_k (\lambda_k)^l,
-\end{equation}
-где $\lambda_k$ - собственные значения матрицы $\Lambda$. Подставим выражение \eqref{eq:126} в формулу \eqref{eq:120}:
+\end{equation} Эти рекуррентные соотношения можно переписать в матричном виде, если ввести матрицу
+коэффициентов $\Lambda$:
+\begin{equation}
+  \label{eq:124} W_{l+1}(n,m,\nu)=\sum_{p,q,\mu}\Lambda(n,m,\nu|t,u,\mu) W_l(t,u,\mu)
+\end{equation} Если вершины $(t,u)$ и $(n,m)$ не являются соседними, то
+$\Lambda(n,m,\nu|p,q,\mu)=0$. Матрица $\Lambda$ не зависит от начала пути. $W_{l+1}=\Lambda W_l$,
+поэтому мы $F_l$ дается следом $l$-той степени $\Lambda$:
+\begin{equation}
+  \label{eq:125} F_l=\frac{1}{2l}\mathrm{Tr} W_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l W_0
+\end{equation} Но матрица $W_0=I$ (единичной матрице), поэтому
+\begin{equation}
+  \label{eq:126} F_l=\frac{1}{2l}\mathrm{Tr} \Lambda^l =\frac{1}{2l} \sum_k (\lambda_k)^l,
+\end{equation} где $\lambda_k$ - собственные значения матрицы $\Lambda$. Подставим выражение
+\eqref{eq:126} в формулу \eqref{eq:120}:
 \begin{multline}
-  \label{eq:127}
-  \Sigma=\exp\left(-\sum_{l=0}^{\infty} \frac{\kappa^l}{2l}\mathrm{Tr}\Lambda^l\right)=\exp\left(-\frac{1}{2}\sum_k \sum_{l=0}^{\infty} \frac{(\kappa\lambda_k)^l}{l}\right)=\\
-  \exp\left(\frac{1}{2}\sum_k \ln(1-\kappa\lambda_k)\right)=\prod_k(1-\kappa\lambda_k)^{1/2}=(\det(I-\kappa\Lambda))^{1/2}
-\end{multline}
-Чтобы вычислить детерминант сделаем дискретное преобразование Фурье:
-\begin{equation}
-  \label{eq:128}
-  W_{l}(n,m,\nu)=\sum_{p_1,p_2} \tilde{W}_l(p_1,p_2,\nu) e^{\frac{2\pi i (p_1n+p_2m)}{\sqrt N}}
-\end{equation}
-В импульсном представлении матрица $\Lambda$ будет иметь блочно-диагональный вид
-\begin{equation}
-  \label{eq:129}
-  \Lambda(p_1,p_2,\mu|q_1,q_2,\nu)=\delta_{p,q}\Lambda_p (\mu,\nu),
-\end{equation}
-где
-\begin{equation}
-  \label{eq:130}
-  \Lambda_p(\mu,\nu)=
-  \begin{pmatrix}
-    e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\
-    0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i p_2}{\sqrt N}}
+  \label{eq:127} \Sigma=\exp\left(-\sum_{l=0}^{\infty}
+\frac{\kappa^l}{2l}\mathrm{Tr}\Lambda^l\right)=\exp\left(-\frac{1}{2}\sum_k \sum_{l=0}^{\infty}
+\frac{(\kappa\lambda_k)^l}{l}\right)=\\ \exp\left(\frac{1}{2}\sum_k
+\ln(1-\kappa\lambda_k)\right)=\prod_k(1-\kappa\lambda_k)^{1/2}=(\det(I-\kappa\Lambda))^{1/2}
+\end{multline} Чтобы вычислить детерминант сделаем дискретное преобразование Фурье:
+\begin{equation}
+  \label{eq:128} W_{l}(n,m,\nu)=\sum_{p_1,p_2} \tilde{W}_l(p_1,p_2,\nu) e^{\frac{2\pi i
+(p_1n+p_2m)}{\sqrt N}}
+\end{equation} В импульсном представлении матрица $\Lambda$ будет иметь блочно-диагональный вид
+\begin{equation}
+  \label{eq:129} \Lambda(p_1,p_2,\mu|q_1,q_2,\nu)=\delta_{p,q}\Lambda_p (\mu,\nu),
+\end{equation} где
+\begin{equation}
+  \label{eq:130} \Lambda_p(\mu,\nu)=
+  \begin{pmatrix} e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}}
+e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\ e^{\frac{2\pi i
+p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}}
+e^{-\frac{i\pi}{4}} & 0 \\ 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i
+p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\ e^{\frac{2\pi i p_1}{\sqrt
+N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & e^{-\frac{2\pi i
+p_2}{\sqrt N}}
   \end{pmatrix}
-\end{equation}
-Матрица $I-\kappa\Lambda$ тоже имеет блочный вид с блоками
+\end{equation} Матрица $I-\kappa\Lambda$ тоже имеет блочный вид с блоками
 \begin{equation}
   \label{eq:131}
-  \begin{pmatrix}
-    1-\kappa e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\
-    0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
-    e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1- \kappa e^{-\frac{2\pi i p_2}{\sqrt N}}
+  \begin{pmatrix} 1-\kappa e^{\frac{2\pi i p_1}{\sqrt N}} & e^{\frac{2\pi i p_2}{\sqrt N}}
+e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} \\ e^{\frac{2\pi i
+p_1}{\sqrt N}} e^{\frac{i\pi}{4}} & 1-\kappa e^{\frac{2\pi i p_2}{\sqrt N}} & e^{-\frac{2\pi i
+p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 \\ 0 & e^{\frac{2\pi i p_2}{\sqrt N}} e^{\frac{i\pi}{4}} &
+1-\kappa e^{-\frac{2\pi i p_1}{\sqrt N}} & e^{-\frac{2\pi i p_2}{\sqrt N}} e^{-\frac{i\pi}{4}} \\
+e^{\frac{2\pi i p_1}{\sqrt N}} e^{-\frac{i\pi}{4}} & 0 & e^{\frac{2\pi i p_1}{\sqrt N}}
+e^{\frac{i\pi}{4}} & 1- \kappa e^{-\frac{2\pi i p_2}{\sqrt N}}
   \end{pmatrix}.
-\end{equation}
-В результате вычисления детерминанта получаем
-\begin{eqnarray}
-  \label{eq:132}
-  \Sigma=\prod_{p_1,p_2} D^{1/2}_{p}\\
-  D_p=(1+\kappa^2)^2 -2\kappa (1-\kappa^2)\left( \cos \frac{2\pi p_1}{\sqrt N} +\cos \frac{2\pi p_2}{\sqrt N}\right)
-\end{eqnarray}
-В результате выражение для статсуммы имеет вид
-\begin{equation}
-  \label{eq:133}
-  Z_N=(2\ch^2 K)^N \prod_{p_1,p_2}D_p^{1/2}.
-\end{equation}
-Исследуем критическое поведение. Вычислим для этого удельную свободную энергию:
-\begin{equation}
-  \label{eq:134}
-  f=-T \lim_{N\to \infty}\frac{\ln Z_N}{N}=-T \lim_{N\to \infty} \left(\ln (2\ch^2 K)+\frac{1}{2N}\sum_p \ln D_p\right)
-\end{equation}
-В термодинамическом пределе $N\to \infty$ значения импульса покрывают всю ось, поэтому сумма переходит в интеграл. Мы сделаем замену переменных
-\begin{eqnarray}
-  \label{eq:135}
-  w_1=\frac{2\pi p_1}{\sqrt N}\quad  w_2=\frac{2\pi p_2}{\sqrt N},\quad w_{1,2}\in [0;2\pi]\\
-  dp_1 dp_2=\frac{N}{(2\pi)^2} dw_1 dw_2
-\end{eqnarray}
-Вспомним, что $\kappa=\th K$, поэтому
-\begin{equation}
-  \label{eq:136}
-  -\ln(2\ch^2 K)=\ln\left(\frac{1-\kappa^2}{2}\right)
-\end{equation}
-Нам будет удобно переписать $D_p$  в виде
-\begin{equation}
-  \label{eq:137}
-  D_p=(\kappa^2+2\kappa -1)^2 +4\kappa (1-\kappa^2) \left(\sin^2 \frac{w_1}{2} +\sin^2 \frac{w_2}{2}\right)
-\end{equation}
-Тогда свободная энергия дается интегралом
+\end{equation} В результате вычисления детерминанта получаем
+\begin{eqnarray}
+  \label{eq:132} \Sigma=\prod_{p_1,p_2} D^{1/2}_{p}\\ D_p=(1+\kappa^2)^2 -2\kappa (1-\kappa^2)\left(
+\cos \frac{2\pi p_1}{\sqrt N} +\cos \frac{2\pi p_2}{\sqrt N}\right)
+\end{eqnarray} В результате выражение для статсуммы имеет вид
+\begin{equation}
+  \label{eq:133} Z_N=(2\ch^2 K)^N \prod_{p_1,p_2}D_p^{1/2}.
+\end{equation} Исследуем критическое поведение. Вычислим для этого удельную свободную энергию:
+\begin{equation}
+  \label{eq:134} f=-T \lim_{N\to \infty}\frac{\ln Z_N}{N}=-T \lim_{N\to \infty} \left(\ln (2\ch^2
+K)+\frac{1}{2N}\sum_p \ln D_p\right)
+\end{equation} В термодинамическом пределе $N\to \infty$ значения импульса покрывают всю ось,
+поэтому сумма переходит в интеграл. Мы сделаем замену переменных
+\begin{eqnarray}
+  \label{eq:135} w_1=\frac{2\pi p_1}{\sqrt N}\quad w_2=\frac{2\pi p_2}{\sqrt N},\quad w_{1,2}\in
+[0;2\pi]\\ dp_1 dp_2=\frac{N}{(2\pi)^2} dw_1 dw_2
+\end{eqnarray} Вспомним, что $\kappa=\th K$, поэтому
+\begin{equation}
+  \label{eq:136} -\ln(2\ch^2 K)=\ln\left(\frac{1-\kappa^2}{2}\right)
+\end{equation} Нам будет удобно переписать $D_p$ в виде
+\begin{equation}
+  \label{eq:137} D_p=(\kappa^2+2\kappa -1)^2 +4\kappa (1-\kappa^2) \left(\sin^2 \frac{w_1}{2}
++\sin^2 \frac{w_2}{2}\right)
+\end{equation} Тогда свободная энергия дается интегралом
 \begin{multline}
-  \label{eq:138}
-  f=T\ln\left(\frac{1-\kappa^2}{2}\right)-\\
-  -\frac{T}{8\pi^2}\int_0^{2\pi}\int_0^{2\pi}\ln\left((\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)\right) dw_1 \;dw_2
-\end{multline}
-В критической точке должна быть расходимость.
-Интеграл может иметь особую точку только при $(\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)=0$.
-Это выражение имеет минимум при $w_1=w_2=0$.
-Тогда при $\kappa^2+2\kappa-1=0$ интеграл расходится, что соответствует критической точке.
-\begin{equation}
-  \label{eq:139}
-  \kappa_c=\sqrt 2 -1
-\end{equation}
-В критической точке основной вклад в интеграл дает окрестность $w_1=w_2=0$, введем
-\begin{equation}
-  \label{eq:140}
-  \epsilon=\kappa-\kappa_c
-\end{equation}
-Тогда около критической точки свободная энергия ведет себя как
-\begin{equation}
-  \label{eq:141}
-  f=g(\epsilon)-\frac{T}{8\pi^2}\int_{0}^{2\pi}\int_0^{2\pi}\ln \left( c\epsilon^2 +A(\epsilon)(w_1^2+w_2^2)\right)dw_1\;dw_2.
-\end{equation}
-Здесь $g(\epsilon), A(\epsilon)$ - регулярные функции. Если взять интеграл, то
-\begin{equation}
-  \label{eq:142}
-  f\approx g_1 (\epsilon)+c\epsilon^2 \ln(\epsilon)
-\end{equation}
-Тогда для теплоемкости имеем
-\begin{equation}
-  \label{eq:143}
-  c\propto \ln|T-T_c|
-\end{equation}
-То есть мы подтвердили, что критический индекс $\alpha=0$ (см.
-таблицу \ref{tab:diagrams}).
-Вычисление других критических индексов также возможно, но сопряжено с техническими трудностями.
-Мы не будем его проделывать, так как в следующих лекциях мы легко сможем вычислить корреляторы из конформной теории поля.
+  \label{eq:138} f=T\ln\left(\frac{1-\kappa^2}{2}\right)-\\
+-\frac{T}{8\pi^2}\int_0^{2\pi}\int_0^{2\pi}\ln\left((\kappa^2 +2\kappa-1)^2 +4\kappa
+(1-\kappa^2)\left(\sin^2 \frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)\right) dw_1 \;dw_2
+\end{multline} В критической точке должна быть расходимость. Интеграл может иметь особую точку
+только при $(\kappa^2 +2\kappa-1)^2 +4\kappa (1-\kappa^2)\left(\sin^2
+\frac{w_1}{2}+\sin^2\frac{w_2}{2}\right)=0$. Это выражение имеет минимум при $w_1=w_2=0$. Тогда при
+$\kappa^2+2\kappa-1=0$ интеграл расходится, что соответствует критической точке.
+\begin{equation}
+  \label{eq:139} \kappa_c=\sqrt 2 -1
+\end{equation} В критической точке основной вклад в интеграл дает окрестность $w_1=w_2=0$, введем
+\begin{equation}
+  \label{eq:140} \epsilon=\kappa-\kappa_c
+\end{equation} Тогда около критической точки свободная энергия ведет себя как
+\begin{equation}
+  \label{eq:141} f=g(\epsilon)-\frac{T}{8\pi^2}\int_{0}^{2\pi}\int_0^{2\pi}\ln \left( c\epsilon^2
++A(\epsilon)(w_1^2+w_2^2)\right)dw_1\;dw_2.
+\end{equation} Здесь $g(\epsilon), A(\epsilon)$ - регулярные функции. Если взять интеграл, то
+\begin{equation}
+  \label{eq:142} f\approx g_1 (\epsilon)+c\epsilon^2 \ln(\epsilon)
+\end{equation} Тогда для теплоемкости имеем
+\begin{equation}
+  \label{eq:143} c\propto \ln|T-T_c|
+\end{equation} То есть мы подтвердили, что критический индекс $\alpha=0$ (см. таблицу
+\ref{tab:diagrams}). Вычисление других критических индексов также возможно, но сопряжено с
+техническими трудностями. Мы не будем его проделывать, так как в следующих лекциях мы легко сможем
+вычислить корреляторы из конформной теории поля.
 
@@
   \label{eq:12}
-  \begin{array}{l}
-    \sigma_i\sigma_j=2\delta_{\sigma_i\sigma_j}-1\\
+  \begin{array}{l} \sigma_i\sigma_j=2\delta_{\sigma_i\sigma_j}-1\\
 E[\sigma]=-2J\sum_{\left<ij\right>}\delta_{\sigma_i\sigma_j}-h\sum_i \sigma_i
   \end{array}
-\end{equation}
-Обсудим некоторые обобщения модели Изинга и проиллюстрируем сходство статистической механики с теорией поля.
-
-Если $\sigma_i$ может принимать значения не $-1,1$, а $1,2\dots,q$, то мы получаем модель Поттса с $q$ состояниями.
-Подобным образом получаются и модели Ашкина-Теллера \cite{difrancesco1997cft}.
+\end{equation} Обсудим некоторые обобщения модели Изинга и проиллюстрируем сходство статистической
+механики с теорией поля.
+
+Если $\sigma_i$ может принимать значения не $-1,1$, а $1,2\dots,q$, то мы получаем модель Поттса с
+$q$ состояниями. Подобным образом получаются и модели Ашкина-Теллера \cite{difrancesco1997cft}.
 
@@
 \begin{equation}
-  \label{eq:14}
-  \left|\vec n\right|^2=1
-\end{equation}
-В результате получим гамильтониан
-\begin{equation}
-  \label{eq:13}
-  E[\vec n]=J\sum_{\left<ij\right>}\vec n_i\cdot \vec n_j-\sum_i \vec h\cdot \vec n_i
-\end{equation}
-Это гамильтониан классической $O(m)$-модели Гейзенберга.
-
-В критической точке наблюдается корреляция спинов на больших расстояниях, кроме того, фазовый переход
-в дискретных моделях наблюдается только в пределе числа вершин стремящегося к бесконечности ($N\to
-\infty$). Такой предел называется термодинамическим. Поэтому при описании фазового перехода имеет
-смысл перейти от модели с дискретным пространством к непрерывному $d$-мерному пространству. В
+  \label{eq:14} \left|\vec n\right|^2=1
+\end{equation} В результате получим гамильтониан
+\begin{equation}
+  \label{eq:13} E[\vec n]=J\sum_{\left<ij\right>}\vec n_i\cdot \vec n_j-\sum_i \vec h\cdot \vec n_i
+\end{equation} Это гамильтониан классической $O(m)$-модели Гейзенберга.
+
+В критической точке наблюдается корреляция спинов на больших расстояниях, кроме того, фазовый
+переход в дискретных моделях наблюдается только в пределе числа вершин стремящегося к бесконечности
+($N\to \infty$). Такой предел называется термодинамическим. Поэтому при описании фазового перехода
+имеет смысл перейти от модели с дискретным пространством к непрерывному $d$-мерному пространству. В
 дальнейшем $d$ будет равно двум, но сейчас мы пишем в самом общем виде, чтобы указать аналогию с
@@
 \begin{equation}
-  \label{eq:15}
-  E[\vec n]=\int d^d x \left(J\partial_kn_i\partial_k  n_i-h_i\cdot n_i\right)
-\end{equation}
-Здесь подразумевается суммирование по повторяющимся индексам. (Легко понять обратный переход, если
-заменить производные разностями по ближайшим соседям, а потом отбросить в энергии постоянный член
-$J\sum_i \left|\vec n_i\right|^2=JN$).
+  \label{eq:15} E[\vec n]=\int d^d x \left(J\partial_kn_i\partial_k n_i-h_i\cdot n_i\right)
+\end{equation} Здесь подразумевается суммирование по повторяющимся индексам. (Легко понять обратный
+переход, если заменить производные разностями по ближайшим соседям, а потом отбросить в энергии
+постоянный член $J\sum_i \left|\vec n_i\right|^2=JN$).
 
@@
 \begin{equation}
-  \label{eq:16}
-  E[\vec n]=\int d^d x \left(\frac{1}{2}\partial_k n_i\cdot \partial_k n_i-\frac{1}{2}\mu^2 \vec n^2+\frac{1}{4}u\left(\vec n^2\right)^2\right)
-\end{equation}
-Если у $\vec n$ всего одна компонента $\varphi$, то мы получаем скалярную модели $\varphi^4$. Если
-$u=0$, то такая модель называется Гауссовой и допускает точное решение. 
-\begin{equation}
-  \label{eq:17}
-  E[\varphi]=\int d^d x (\frac{1}{2}(\nabla \varphi)^2+\frac{1}{2}\mu^2 \varphi^2)
-\end{equation}
-Статсумма --- это сумма $e^{-\beta E[\varphi]}$ по всем конфигурациям поля $\varphi$, то есть она
-записывается при помощи функционального интеграла: 
-\begin{equation}
-  \label{eq:18}
-  Z=\int \mathcal{D}\varphi e^{-\beta E[\varphi]}
-\end{equation}
-В гауссовой модели функциональный интеграл имеет гауссовский вид, поэтому он хорошо определен и
-легко вычисляется. Значит можно вычислить статсумму и все корреляционные функции. Величины в модели
-$\varphi^4$ можно получать по теории возмущений вокруг решения гауссовой модели. Это и есть
-вычисление функционального интеграла как суммы по фейнмановским диаграммам.
+  \label{eq:16} E[\vec n]=\int d^d x \left(\frac{1}{2}\partial_k n_i\cdot \partial_k
+n_i-\frac{1}{2}\mu^2 \vec n^2+\frac{1}{4}u\left(\vec n^2\right)^2\right)
+\end{equation} Если у $\vec n$ всего одна компонента $\varphi$, то мы получаем скалярную модели
+$\varphi^4$. Если $u=0$, то такая модель называется Гауссовой и допускает точное решение.
+\begin{equation}
+  \label{eq:17} E[\varphi]=\int d^d x (\frac{1}{2}(\nabla \varphi)^2+\frac{1}{2}\mu^2 \varphi^2)
+\end{equation} Статсумма --- это сумма $e^{-\beta E[\varphi]}$ по всем конфигурациям поля $\varphi$,
+то есть она записывается при помощи функционального интеграла:
+\begin{equation}
+  \label{eq:18} Z=\int \mathcal{D}\varphi e^{-\beta E[\varphi]}
+\end{equation} В гауссовой модели функциональный интеграл имеет гауссовский вид, поэтому он хорошо
+определен и легко вычисляется. Значит можно вычислить статсумму и все корреляционные функции.
+Величины в модели $\varphi^4$ можно получать по теории возмущений вокруг решения гауссовой модели.
+Это и есть вычисление функционального интеграла как суммы по фейнмановским диаграммам.
 
@@
 \begin{equation}
-  \label{eq:19}
-  \rho=e^{-\beta H}
-\end{equation}
-Статсумма дается суммой по собственным состояниям гамильтониана или следом матрицы плотности:
-\begin{equation}
-  \label{eq:20}
-  Z=\sum_n e^{-\beta E_n}=\mathrm{Tr} \rho
-\end{equation}
-Значение физической величины определим как среднее по состояниям:
-\begin{equation}
-  \label{eq:21}
-  \left< A\right>=\sum_n \left< n\right| e^{-\beta H}A\left| n \right>=\mathrm{Tr}(\rho A)
-\end{equation}
-$e^{-\beta H}$ похоже на оператор эволюции $e^{-i H t}$, то есть его тоже можно записать через
-функциональный интеграл. Покажем, как это делается на примере системы с одной степенью свободы. В
-этом случае ядро оператора плотности имеет вид 
-\begin{equation}
-  \label{eq:22}
-  \rho(x_f,x_i)=\left<x_f\right|e^{-\beta H} \left|x_i\right>
-\end{equation}
-Вспомним, что в квантовой механике оператор эволюции имеет вид $U(t)=e^{-i H t}$, а его ядро ---
-амплитуда перехода из состояния $\left|x_i\right>$ в $\left<x_f\right|$ дается интегралом по
-траекториям 
-\begin{equation}
-  \label{eq:23}
-  \left<x_f\right| U(t)\left| x_i\right>=\int_{(x_i,0)}^{(x_f,t)} [dx] e^{i S[x]}
-\end{equation}
-Заменой $t\to i\tau, \; \tau\in [0,\beta]$ (виковским поворотом) переходим к евклидову действию
-$S[x(t)]\to iS_E[x(\tau)]$. Для ядра оператора плотности получаем 
-\begin{equation}
-  \label{eq:24}
-  \rho(x_f,x_i)=\int_{(x_i,0)}^{(x_f,\beta)} [dx] e^{-S_E[x]}
-\end{equation}
-Статсумма
-\begin{equation}
-  \label{eq:25}
-  Z=\int dx \rho(x,x)=\int [dx] e^{-S_E[x]}
-\end{equation}
-Среднее значение $A$
+  \label{eq:19} \rho=e^{-\beta H}
+\end{equation} Статсумма дается суммой по собственным состояниям гамильтониана или следом матрицы
+плотности:
+\begin{equation}
+  \label{eq:20} Z=\sum_n e^{-\beta E_n}=\mathrm{Tr} \rho
+\end{equation} Значение физической величины определим как среднее по состояниям:
+\begin{equation}
+  \label{eq:21} \left< A\right>=\sum_n \left< n\right| e^{-\beta H}A\left| n
+\right>=\mathrm{Tr}(\rho A)
+\end{equation} $e^{-\beta H}$ похоже на оператор эволюции $e^{-i H t}$, то есть его тоже можно
+записать через функциональный интеграл. Покажем, как это делается на примере системы с одной
+степенью свободы. В этом случае ядро оператора плотности имеет вид
+\begin{equation}
+  \label{eq:22} \rho(x_f,x_i)=\left<x_f\right|e^{-\beta H} \left|x_i\right>
+\end{equation} Вспомним, что в квантовой механике оператор эволюции имеет вид $U(t)=e^{-i H t}$, а
+его ядро --- амплитуда перехода из состояния $\left|x_i\right>$ в $\left<x_f\right|$ дается
+интегралом по траекториям
+\begin{equation}
+  \label{eq:23} \left<x_f\right| U(t)\left| x_i\right>=\int_{(x_i,0)}^{(x_f,t)} [dx] e^{i S[x]}
+\end{equation} Заменой $t\to i\tau, \; \tau\in [0,\beta]$ (виковским поворотом) переходим к
+евклидову действию $S[x(t)]\to iS_E[x(\tau)]$. Для ядра оператора плотности получаем
+\begin{equation}
+  \label{eq:24} \rho(x_f,x_i)=\int_{(x_i,0)}^{(x_f,\beta)} [dx] e^{-S_E[x]}
+\end{equation} Статсумма
+\begin{equation}
+  \label{eq:25} Z=\int dx \rho(x,x)=\int [dx] e^{-S_E[x]}
+\end{equation} Среднее значение $A$
 \begin{equation}
   \label{eq:26}
-  \begin{array}{l}
-    \left<A\right>=\frac{1}{Z}\int dx \left<x\right|\rho A\left|x\right>=\frac{1}{Z}\int dx\; dy \left<x\right|\rho\left|y\right>\left<y\right|A\left|x\right>=    \\
-    =\frac{1}{Z}\int dx\; dy \int_{(x,0)}^{(y,\beta)} [dx] \left<y\right| A\left| x\right> e^{-S_E[x]}=\frac{1}{Z}\int dx\; dy\int_{(x,0)}^{(y,\beta)} [dx] A(x) \delta(x-y) e^{-S_E[x]}=\\
-    =\frac{1}{Z}\int [dx] A(x(0))e^{-S_E[x]}
+  \begin{array}{l} \left<A\right>=\frac{1}{Z}\int dx \left<x\right|\rho
+A\left|x\right>=\frac{1}{Z}\int dx\; dy
+\left<x\right|\rho\left|y\right>\left<y\right|A\left|x\right>= \\ =\frac{1}{Z}\int dx\; dy
+\int_{(x,0)}^{(y,\beta)} [dx] \left<y\right| A\left| x\right> e^{-S_E[x]}=\frac{1}{Z}\int dx\;
+dy\int_{(x,0)}^{(y,\beta)} [dx] A(x) \delta(x-y) e^{-S_E[x]}=\\ =\frac{1}{Z}\int [dx]
+A(x(0))e^{-S_E[x]}
   \end{array}
-\end{equation}
-Здесь мы предположили, что $A$ зависит только от $x$, то есть $\left<y\right|
+\end{equation} Здесь мы предположили, что $A$ зависит только от $x$, то есть $\left<y\right|
 A\left|x\right>=A(x)\delta(x-y)$. Мы видим, что значение $A$ дается функциональным интегралом, но
@@
 \subsection*{Классическая и квантовая теория поля}
-\label{sec:qft}
-Напоминание про теорию поля.
+\label{sec:qft} Напоминание про теорию поля.
 
@@
  Действие
-\begin{equation}
-  S=\int d^dx \mathcal{L}
-\end{equation}
-зависит от полей $\varphi$ и констант связи $\vec u=(u_1,\dots,u_n)$.
-Например:
-\begin{equation}
-  S[\varphi]=\int d^d x\left( -\frac{(\partial \varphi)^2}{2}-\frac{\mu \varphi^2}{2}-\frac{u\varphi^4}{24}+h\varphi\right),
+\begin{equation} S=\int d^dx \mathcal{L}
+\end{equation} зависит от полей $\varphi$ и констант связи $\vec u=(u_1,\dots,u_n)$. Например:
+\begin{equation} S[\varphi]=\int d^d x\left( -\frac{(\partial \varphi)^2}{2}-\frac{\mu
+\varphi^2}{2}-\frac{u\varphi^4}{24}+h\varphi\right),
 \end{equation}
@@
 \begin{equation}
-  \label{eq:303}
-  x\to x'
+  \label{eq:303} x\to x'
+\end{equation} поля тоже преобразуются, то есть у них не только меняется аргумент, но и само поле.
+Тип поля (скалярное, векторное, спинорное) -- это вид такого преобразования.
+\begin{equation}
+  \label{eq:304} \varphi(x)\to \varphi'(x')=F(\varphi(x))
 \end{equation}
-поля тоже преобразуются, то есть у них не только меняется аргумент, но и само поле. Тип поля
-(скалярное, векторное, спинорное) -- это вид такого преобразования. 
-\begin{equation}
-  \label{eq:304}
-  \varphi(x)\to \varphi'(x')=F(\varphi(x))
+
+При этом действие тоже преобразуется:
+\begin{equation}
+  \label{eq:305} S'=\int d^{d}x' \mathcal{L}(\varphi'(x'),\partial_{\mu} \varphi'(x'))=\int d^{d}x
+\left|\frac{\partial x'}{\partial x}\right| \mathcal{L}(F(\varphi(x)),\frac{\partial
+x^{\nu}}{\partial x'^{\mu}} \partial_{\nu}F(\varphi(x)))
+\end{equation} {\bf Примеры.}
+
+Трансляции:
+
+\begin{equation*}
+  \label{eq:306} x'^{\mu}=x^{\mu}+a^{\mu},\quad \varphi'(x+a)=\varphi(x),\quad S'=S
+\end{equation*}
+
+Поворот (преобразования Лоренца):
+\begin{equation*} x'^{\mu}=m^{\mu}_{\nu} x^{\nu}, \quad \varphi'(m x)=\Lambda \varphi(x),\quad
+\Lambda \mbox{--представление группы}
+\end{equation*}
+
+Теперь рассмотрим инфинитезимальные преобразования. Если действие инвариантно относительно
+каких-либо преобразований, то говорят, что в теории есть симметрия. В этом случае действие должно
+быть стационарно по отношению к инфинитезимальным преобразованиям.
+
+\begin{equation}
+  \label{eq:165} x'^{\mu}=x^{\mu}+\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}
+\end{equation} ($\omega_{a}$ -- бесконечно малые параметры).
+
+Наше поле преобразуется так:
+\begin{equation}
+  \label{eq:166} \varphi'(x')=\varphi(x)+\omega_a \frac{\delta F}{\delta \omega_a} (x).
+\end{equation} Генератор преобразования определяется следующим равенством:
+\begin{equation}
+  \label{eq:167} \delta_{\omega} \varphi(x)=\varphi'(x)-\varphi(x)\equiv -i\omega_a G_a \varphi(x)
+\end{equation} (здесь нет суммирования по $a$). Действие генератора на поле:
+\begin{equation}
+  \label{eq:168} iG_a \varphi=\frac{\delta
+x^{\mu}}{\delta\omega_a} \partial_{\mu}\varphi-\frac{\delta F}{\delta \omega_a}
 \end{equation}
 
-При этом действие тоже преобразуется:
-\begin{equation}
-  \label{eq:305}
-  S'=\int d^{d}x' \mathcal{L}(\varphi'(x'),\partial_{\mu} \varphi'(x'))=\int d^{d}x \left|\frac{\partial x'}{\partial x}\right| \mathcal{L}(F(\varphi(x)),\frac{\partial x^{\nu}}{\partial x'^{\mu}} \partial_{\nu}F(\varphi(x)))
-\end{equation}
-{\bf Примеры.}
-
-Трансляции:
-
-\begin{equation*}
-  \label{eq:306}
-  x'^{\mu}=x^{\mu}+a^{\mu},\quad \varphi'(x+a)=\varphi(x),\quad S'=S
-\end{equation*}
-
-Поворот (преобразования Лоренца):
-\begin{equation*}
-  x'^{\mu}=m^{\mu}_{\nu} x^{\nu}, \quad \varphi'(m x)=\Lambda \varphi(x),\quad \Lambda \mbox{--представление группы} 
-\end{equation*}
-
-Теперь рассмотрим инфинитезимальные преобразования.
-Если действие инвариантно относительно каких-либо преобразований, то говорят, что в теории есть
-симметрия. В этом случае действие должно быть стационарно по отношению к инфинитезимальным
-преобразованиям.
-
-\begin{equation}
-  \label{eq:165}
-  x'^{\mu}=x^{\mu}+\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}
-\end{equation}
-($\omega_{a}$ -- бесконечно малые параметры).
-
-Наше поле преобразуется так:
-\begin{equation}
-  \label{eq:166}
-  \varphi'(x')=\varphi(x)+\omega_a \frac{\delta F}{\delta \omega_a} (x).
-\end{equation}
-Генератор преобразования определяется следующим равенством:
-\begin{equation}
-  \label{eq:167}
-  \delta_{\omega} \varphi(x)=\varphi'(x)-\varphi(x)\equiv -i\omega_a G_a \varphi(x)
-\end{equation}
-(здесь нет суммирования по $a$). Действие генератора на поле:
-\begin{equation}
-  \label{eq:168}
-  iG_a \varphi=\frac{\delta x^{\mu}}{\delta\omega_a} \partial_{\mu}\varphi-\frac{\delta F}{\delta \omega_a}
-\end{equation}
-
-Примеры генераторов:
-Если мы предположим, что поле $\varphi$ -- такое поле, которое не меняется при конформных
-преобразованиях, то есть $F(\varphi)=\varphi$, то мы получим следующий вид для генераторов: 
-\begin{eqnarray}
-  \label{eq:169}
-  \mbox{трансляция}  & x'^{\mu}=x^{\mu}+\omega^{\mu}& \quad P_{\mu}=-i\partial_{\mu}\\
-  \mbox{поворот} & x'^{\mu}=x^{\mu}+\omega^{\mu}_{\nu}x^{\nu} & \quad L_{\mu\nu}=i(x_{\mu}\partial_{\nu}-x_{\nu}\partial{\mu})
-\end{eqnarray}
-Если же при поворотах поле преобразуется $\varphi'(x')=\Lambda\varphi(x)$, то при инфинитезимальных
-преобразованиях $\varphi'(x')=\varphi(x)-\frac{i}{2}\omega_{\mu\nu}S^{\mu\nu}$ и генератор принимает
-вид 
-\begin{equation*}
-  L_{\mu\nu}=i(x_{\mu}\partial_{\nu}-x_{\nu}\partial{\mu})+S_{\mu\nu}
+Примеры генераторов: Если мы предположим, что поле $\varphi$ -- такое поле, которое не меняется при
+конформных преобразованиях, то есть $F(\varphi)=\varphi$, то мы получим следующий вид для
+генераторов:
+\begin{eqnarray}
+  \label{eq:169} \mbox{трансляция} & x'^{\mu}=x^{\mu}+\omega^{\mu}& \quad P_{\mu}=-i\partial_{\mu}\\
+\mbox{поворот} & x'^{\mu}=x^{\mu}+\omega^{\mu}_{\nu}x^{\nu} & \quad
+L_{\mu\nu}=i(x_{\mu}\partial_{\nu}-x_{\nu}\partial{\mu})
+\end{eqnarray} Если же при поворотах поле преобразуется $\varphi'(x')=\Lambda\varphi(x)$, то при
+инфинитезимальных преобразованиях $\varphi'(x')=\varphi(x)-\frac{i}{2}\omega_{\mu\nu}S^{\mu\nu}$ и
+генератор принимает вид
+\begin{equation*} L_{\mu\nu}=i(x_{\mu}\partial_{\nu}-x_{\nu}\partial{\mu})+S_{\mu\nu}
 \end{equation*}
@@
 Якобиан такого преобразования
-\begin{eqnarray*}
-  \frac{\partial x'^{\nu}}{\partial x^{\mu}} = \delta^{\mu}_{\nu}+\partial_{\mu}\left(\omega_a \frac{\delta x^{\nu}}{\delta \omega_a}\right)\\
-  \frac{\partial x^{\nu}}{\partial x'^{\mu}} = \delta^{\mu}_{\nu}-\partial_{\mu}\left(\omega_a \frac{\delta x^{\nu}}{\delta \omega_a}\right)
+\begin{eqnarray*} \frac{\partial x'^{\nu}}{\partial x^{\mu}} =
+\delta^{\mu}_{\nu}+\partial_{\mu}\left(\omega_a \frac{\delta x^{\nu}}{\delta \omega_a}\right)\\
+\frac{\partial x^{\nu}}{\partial x'^{\mu}} = \delta^{\mu}_{\nu}-\partial_{\mu}\left(\omega_a
+\frac{\delta x^{\nu}}{\delta \omega_a}\right)
 \end{eqnarray*}
-\begin{equation*}
-  \left|\frac{\partial x'^{\nu}}{\partial x^{\mu}}\right| = 1+\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)
-\end{equation*}
-Вариация действия
-\begin{multline*}
-  0=\delta_{\omega} S=\int \mathcal{L}(\varphi',\partial_{\mu}\varphi',x'^{\mu})dx'-\int \mathcal{L}(\varphi,\partial_{\mu}\varphi,x)dx=\\
-  \int d^{d}x\left[ \left( 1+\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)\right) \mathcal{L} \left(\varphi+\delta_{\omega}\varphi,
+\begin{equation*} \left|\frac{\partial x'^{\nu}}{\partial x^{\mu}}\right| =
+1+\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)
+\end{equation*} Вариация действия
+\begin{multline*} 0=\delta_{\omega} S=\int
+\mathcal{L}(\varphi',\partial_{\mu}\varphi',x'^{\mu})dx'-\int
+\mathcal{L}(\varphi,\partial_{\mu}\varphi,x)dx=\\ \int d^{d}x\left[ \left(
+1+\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)\right) \mathcal{L}
+\left(\varphi+\delta_{\omega}\varphi,
     \partial_{\mu}\varphi+\partial_{\mu}\delta_{\omega}\varphi\right)\right]-\mathcal{L}(\varphi,\partial_{\mu}\varphi)=
 \end{multline*}
-\begin{multline*}
-      \int d^{d}x\left( \frac{\partial \mathcal{L}}{\partial \varphi} \delta_{\omega}\varphi +\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\partial_{\mu}\varphi +\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)\mathcal{L}\right)
-\end{multline*}
-Первые два члена переписываются с использованием уравнений Эйлера-Лагранжа и интегрирования по частям:
+\begin{multline*} \int d^{d}x\left( \frac{\partial \mathcal{L}}{\partial \varphi}
+\delta_{\omega}\varphi +\frac{\partial
+\mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\partial_{\mu}\varphi
++\partial_{\mu}\left(\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}\right)\mathcal{L}\right)
+\end{multline*} Первые два члена переписываются с использованием уравнений Эйлера-Лагранжа и
+интегрирования по частям:
 \begin{equation*}
-  \partial_{\mu}\left(\frac{\partial \mathcal{L}}{\partial (\partial_{\mu}\varphi)}\right)\delta_{\omega}\varphi+\frac{\partial \mathcal{L}}{\partial (\partial_{\mu}\varphi)}\delta_{\omega}\partial_{\mu}\varphi=
-    \partial_{\mu}\left(\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\varphi\right)
-\end{equation*}
-В итоге имеем:
-\begin{equation*}
-  0=\int d^{d}x \partial_{\mu}\left(\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\varphi +\delta^{\mu}_{\nu}\mathcal{L} \frac{\delta x^{\nu}}{\delta \omega_{a}}\right)
-\end{equation*}
-Если подставить явный вид вариации поля и ввести обозначение
-\begin{equation*}
-  j^{\mu}_{a}=\left(\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\partial_{\nu}\varphi -\delta^{\mu}_{\nu}\mathcal{L}\right) \frac{\delta x^{\nu}}{\delta \omega_{a}}-\frac{\partial \mathcal{L}}{\partial(\partial_{\mu}\varphi)}\frac{\delta F}{\delta w_{a}},
-\end{equation*}
-то для вариации действия выходит:
-\begin{equation*}
-  \delta_{\omega}S=-\int d^{d}x j^{\mu}_{a}\partial_{\mu}\omega_{a}
-\end{equation*}
-$j^{\mu}_{a}$ называется нётеровским током, соответствующим данной симметрии. 
-Если $\delta_{\omega} S=0$, то
+  \partial_{\mu}\left(\frac{\partial \mathcal{L}}{\partial
+(\partial_{\mu}\varphi)}\right)\delta_{\omega}\varphi+\frac{\partial \mathcal{L}}{\partial
+(\partial_{\mu}\varphi)}\delta_{\omega}\partial_{\mu}\varphi=
+    \partial_{\mu}\left(\frac{\partial
+\mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\varphi\right)
+\end{equation*} В итоге имеем:
+\begin{equation*} 0=\int d^{d}x \partial_{\mu}\left(\frac{\partial
+\mathcal{L}}{\partial(\partial_{\mu}\varphi)}\delta_{\omega}\varphi +\delta^{\mu}_{\nu}\mathcal{L}
+\frac{\delta x^{\nu}}{\delta \omega_{a}}\right)
+\end{equation*} Если подставить явный вид вариации поля и ввести обозначение
+\begin{equation*} j^{\mu}_{a}=\left(\frac{\partial
+\mathcal{L}}{\partial(\partial_{\mu}\varphi)}\partial_{\nu}\varphi
+-\delta^{\mu}_{\nu}\mathcal{L}\right) \frac{\delta x^{\nu}}{\delta \omega_{a}}-\frac{\partial
+\mathcal{L}}{\partial(\partial_{\mu}\varphi)}\frac{\delta F}{\delta w_{a}},
+\end{equation*} то для вариации действия выходит:
+\begin{equation*} \delta_{\omega}S=-\int d^{d}x j^{\mu}_{a}\partial_{\mu}\omega_{a}
+\end{equation*} $j^{\mu}_{a}$ называется нётеровским током, соответствующим данной симметрии. Если
+$\delta_{\omega} S=0$, то
 \begin{equation*}
   \partial_{\mu}j^{\mu}_{a}=0
+\end{equation*} Сохраняющийся заряд:
+\begin{equation*} Q_{a}=\int d^{d-1}x\; j^{0}_{a}
 \end{equation*}
-Сохраняющийся заряд:
-\begin{equation*}
-  Q_{a}=\int d^{d-1}x\; j^{0}_{a}
-\end{equation*}
 
  Рассмотрим инфинитезимальное масштабное преобразование $\lambda=1+\omega$. При этом вариация
- $x_{\nu}$ будет $\delta_{\omega}x_{\nu}=\omega x_{\nu}$.  При инфинитезимальных преобразованиях
- $x\to x+dl x$ вариация плотности лагранжиана дается Нётеровским током: 
-\begin{equation}
-  \label{eq:74}
-  \delta\mathcal{L}=\partial_{\mu}J^{\mu}dl
+$x_{\nu}$ будет $\delta_{\omega}x_{\nu}=\omega x_{\nu}$. При инфинитезимальных преобразованиях $x\to
+x+dl x$ вариация плотности лагранжиана дается Нётеровским током:
+\begin{equation}
+  \label{eq:74} \delta\mathcal{L}=\partial_{\mu}J^{\mu}dl
 \end{equation}
 \begin{equation}
-  \label{eq:75}
-  J^{\mu}=x_{\nu}T^{\mu\nu}
-\end{equation}
-Здесь $T^{\mu\nu}$ - тензор энергии-импульса.  Через $\Theta$ мы обозначим след тензора
-энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия 
-\begin{equation}
-  \label{eq:87}
-  \delta S=dl \int d^d x \Theta(x)
-\end{equation}
-Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$. В
-масштабно-инвариантной теории тензор энергии-импульса бесследовый.
+  \label{eq:75} J^{\mu}=x_{\nu}T^{\mu\nu}
+\end{equation} Здесь $T^{\mu\nu}$ - тензор энергии-импульса. Через $\Theta$ мы обозначим след
+тензора энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия
+\begin{equation}
+  \label{eq:87} \delta S=dl \int d^d x \Theta(x)
+\end{equation} Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$.
+В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
 
@@
 
-Гипотеза подобия связывает между собой критические индексы.
-Ее можно сформулировать так: плотность свободной энергии $f(t,h)=\frac{F}{N}$ около критической точки является однородной функцией $h$ и безразмерной температуры $t=\frac{T}{T_c}-1$.
-То есть существуют $a,b$:
-\begin{equation}
-  \label{eq:33}
-  f(\lambda^a t,\lambda^b h)=\lambda f(t,h)
-\end{equation}
-В следующих лекциях мы обоснуем эту гипотезу при помощи ренормгруппы.
-
-Покажем теперь, какие условия накладывает гипотеза подобия на критические индексы. Заметим, что $t^{-\frac{1}{a}}f$ инвариантна при преобразовании $t\to \lambda^a t, h\to \lambda^b h$. Введем
-\begin{equation}
-  \label{eq:34}
-  y=\frac{h}{t^{\frac{b}{a}}}
-\end{equation}
-Тогда
-\begin{equation}
-  \label{eq:35}
-  f(t,h)=t^{\frac{1}{a}}g(y).
-\end{equation}
-Для спонтанной намагниченности имеем
-\begin{equation}
-  \label{eq:36}
-  M=-\left.\frac{\partial f}{\partial h}\right|_{h=0}=t^{\frac{1-b}{a}}g'(0),
-\end{equation}
-а для  магнитной восприимчивости
-\begin{equation}
-  \label{eq:37}
-  \chi=\left.\frac{\partial^2 f}{\partial h^2}\right|_{h=0}=t^{\frac{1-2b}{a}}g''(0).
-\end{equation}
-Аналогично для удельной теплоемкости получаем
-\begin{equation}
-  \label{eq:38}
-  c=-T\left.\frac{\partial^2 f}{\partial T^2}\right|_{h=0}=-\frac{1}{T_c}t^{\frac{1}{a}-2}g''(0)
-\end{equation}
-В пределе $t\to 0$ $M\sim h^{\frac{1}{\delta}}$, поэтому $g'(y)\sim y^{\frac{1}{\delta}}$ при $y\to \infty$.
-А значит, если в критической точке намагниченность $M$ конечна и не равна нулю, должно выполняться равенство $1-b-\frac{b}{\delta}=0$.
-Подставляя выражение для $\delta$ через $b$ в (\ref{eq:36},\ref{eq:37},\ref{eq:38}), мы получаем связь критических индексов
-  \begin{eqnarray}
-    \label{eq:39}
-    \alpha=2-\frac{1}{a}\\
-    \beta=\frac{1-b}{a}\\
-    \gamma=-\frac{1-2b}{a}\\
+Гипотеза подобия связывает между собой критические индексы. Ее можно сформулировать так: плотность
+свободной энергии $f(t,h)=\frac{F}{N}$ около критической точки является однородной функцией $h$ и
+безразмерной температуры $t=\frac{T}{T_c}-1$. То есть существуют $a,b$:
+\begin{equation}
+  \label{eq:33} f(\lambda^a t,\lambda^b h)=\lambda f(t,h)
+\end{equation} В следующих лекциях мы обоснуем эту гипотезу при помощи ренормгруппы.
+
+Покажем теперь, какие условия накладывает гипотеза подобия на критические индексы. Заметим, что
+$t^{-\frac{1}{a}}f$ инвариантна при преобразовании $t\to \lambda^a t, h\to \lambda^b h$. Введем
+\begin{equation}
+  \label{eq:34} y=\frac{h}{t^{\frac{b}{a}}}
+\end{equation} Тогда
+\begin{equation}
+  \label{eq:35} f(t,h)=t^{\frac{1}{a}}g(y).
+\end{equation} Для спонтанной намагниченности имеем
+\begin{equation}
+  \label{eq:36} M=-\left.\frac{\partial f}{\partial h}\right|_{h=0}=t^{\frac{1-b}{a}}g'(0),
+\end{equation} а для магнитной восприимчивости
+\begin{equation}
+  \label{eq:37} \chi=\left.\frac{\partial^2 f}{\partial h^2}\right|_{h=0}=t^{\frac{1-2b}{a}}g''(0).
+\end{equation} Аналогично для удельной теплоемкости получаем
+\begin{equation}
+  \label{eq:38} c=-T\left.\frac{\partial^2 f}{\partial
+T^2}\right|_{h=0}=-\frac{1}{T_c}t^{\frac{1}{a}-2}g''(0)
+\end{equation} В пределе $t\to 0$ $M\sim h^{\frac{1}{\delta}}$, поэтому $g'(y)\sim
+y^{\frac{1}{\delta}}$ при $y\to \infty$. А значит, если в критической точке намагниченность $M$
+конечна и не равна нулю, должно выполняться равенство $1-b-\frac{b}{\delta}=0$. Подставляя выражение
+для $\delta$ через $b$ в (\ref{eq:36},\ref{eq:37},\ref{eq:38}), мы получаем связь критических
+индексов
+  \begin{eqnarray}
+    \label{eq:39} \alpha=2-\frac{1}{a}\\ \beta=\frac{1-b}{a}\\ \gamma=-\frac{1-2b}{a}\\
 \delta=\frac{b}{1-b}
@@
 \subsection{Процедура Каданова}
-\label{sec:kadanoff-procedure}
-Теперь обоснуем гипотезу подобия в модели Изинга при помощи процедуры Каданова и свяжем индексы $a,b$ с $\nu,\eta$.
-Рассмотрим кубическую $d$-мерную модель Изинга.
-\begin{equation}
-  \label{eq:40}
-  H=-J\sum_{\left<ij\right>}\sigma_i \sigma_j-h\sum_i \sigma_i
-\end{equation}
-Разбиваем решетку на блоки со стороной в $r$ ячеек. Будем нумеровать блоки большими латинскими буквами $I,J$ и понимать под записью $i\in I$ перечисление вершин в $I$-том блоке.
-Сумма спинов в блоке принимает значения от $r^{-d}$ до $r^d$. Введем блочный спин
-\begin{equation}
-  \label{eq:41}
-  \Sigma_I=\frac{1}{R}\sum_{i\in I}\sigma_i
-\end{equation}
-Здесь $R$ - некоторый нормировочный множитель, который мы скоро вычислим.
-% выбирается так, чтобы блочный спин мог принимать значения $\pm 1$. Если бы спины были всегда в одном направлении, то $R$ имел бы значение $r^d$.
-
-Основной вклад в статсумму вблизи критической точки вносят большие кластеры, так как корреляционная длина $\xi>>r$.
-Поэтому мы предполагаем, что поведение вблизи критической точки описывается в терминах блочных спинов.
-Гамильтониан для блочных спинов имеет вид
-\begin{equation}
-  \label{eq:42}
-  H'=-J' \sum_{\left<IJ\right>} \Sigma_I \Sigma_J-h' \sum_I \Sigma_I
-\end{equation}
-Так как корреляционная длина для блоков
-\begin{equation}
-  \label{eq:43}
-  \xi'=\frac{\xi}{r},
-\end{equation}
-то из (\ref{eq:31}) для температуры имеем
-\begin{equation}
-  \label{eq:44}
-  t'=r^{\frac{1}{\nu}} t.
-\end{equation}
-Суммарная энергия взаимодействия со внешним полем должна оставаться неизменной, то есть
-\begin{equation}
-  \label{eq:45}
-  h\sum_i \sigma_i=h' \sum_I \Sigma_I=\frac{h'}{R}\sum_i \sigma_i\quad\Longrightarrow\quad h'= Rh
-\end{equation}
-Так как общая свободная энергия тоже не должна меняться, то свободная энергия на блок $\sim r^d f$, то есть
-\begin{equation}
-  \label{eq:46}
-  f(t',h')=r^d f(t,h)
-\end{equation}
-или
-\begin{equation}
-  \label{eq:47}
-  f(t,h)=r^{-d} f(r^{\frac{1}{\nu}} t, Rh)
-\end{equation}
-Осталось вычислить $R$ как функцию от $r$, чтобы оправдать гипотезу подобия. Смотрим на парный коррелятор в критической точке
+\label{sec:kadanoff-procedure} Теперь обоснуем гипотезу подобия в модели Изинга при помощи процедуры
+Каданова и свяжем индексы $a,b$ с $\nu,\eta$. Рассмотрим кубическую $d$-мерную модель Изинга.
+\begin{equation}
+  \label{eq:40} H=-J\sum_{\left<ij\right>}\sigma_i \sigma_j-h\sum_i \sigma_i
+\end{equation} Разбиваем решетку на блоки со стороной в $r$ ячеек. Будем нумеровать блоки большими
+латинскими буквами $I,J$ и понимать под записью $i\in I$ перечисление вершин в $I$-том блоке. Сумма
+спинов в блоке принимает значения от $r^{-d}$ до $r^d$. Введем блочный спин
+\begin{equation}
+  \label{eq:41} \Sigma_I=\frac{1}{R}\sum_{i\in I}\sigma_i
+\end{equation} Здесь $R$ - некоторый нормировочный множитель, который мы скоро вычислим. %
+выбирается так, чтобы блочный спин мог принимать значения $\pm 1$. Если бы спины были всегда в одном
+направлении, то $R$ имел бы значение $r^d$.
+
+Основной вклад в статсумму вблизи критической точки вносят большие кластеры, так как корреляционная
+длина $\xi>>r$. Поэтому мы предполагаем, что поведение вблизи критической точки описывается в
+терминах блочных спинов. Гамильтониан для блочных спинов имеет вид
+\begin{equation}
+  \label{eq:42} H'=-J' \sum_{\left<IJ\right>} \Sigma_I \Sigma_J-h' \sum_I \Sigma_I
+\end{equation} Так как корреляционная длина для блоков
+\begin{equation}
+  \label{eq:43} \xi'=\frac{\xi}{r},
+\end{equation} то из (\ref{eq:31}) для температуры имеем
+\begin{equation}
+  \label{eq:44} t'=r^{\frac{1}{\nu}} t.
+\end{equation} Суммарная энергия взаимодействия со внешним полем должна оставаться неизменной, то
+есть
+\begin{equation}
+  \label{eq:45} h\sum_i \sigma_i=h' \sum_I \Sigma_I=\frac{h'}{R}\sum_i
+\sigma_i\quad\Longrightarrow\quad h'= Rh
+\end{equation} Так как общая свободная энергия тоже не должна меняться, то свободная энергия на блок
+$\sim r^d f$, то есть
+\begin{equation}
+  \label{eq:46} f(t',h')=r^d f(t,h)
+\end{equation} или
+\begin{equation}
+  \label{eq:47} f(t,h)=r^{-d} f(r^{\frac{1}{\nu}} t, Rh)
+\end{equation} Осталось вычислить $R$ как функцию от $r$, чтобы оправдать гипотезу подобия. Смотрим
+на парный коррелятор в критической точке
 \begin{multline}
-  \label{eq:48}
-  \Gamma'(\vec n)=\left< \Sigma_I\Sigma_J\right>-\left< \Sigma_I\right>\left<\Sigma_J\right>=\frac{1}{R^2}\sum_{i\in I}\sum_{j\in J}\left(\left<\sigma_i \sigma_j\right>-\left<\sigma_i\right>\left<\sigma_j\right>\right) =\\
-  = \frac{r^{2d}}{R^2}\Gamma(r\vec n)=\frac{R^{-2}r^{2d}}{\left|r\vec n\right|^{d-2+\eta}}=\frac{R^{-2}r^{d+2-\eta}}{\left|\vec n\right|^{d-2+\eta}}
-\end{multline}
-Отсюда
-\begin{equation}
-  \label{eq:49}
-  R=r^{\frac{d+2-\eta}{2}}, \quad h'=r^{\frac{d+2-\eta}{2}}h
-\end{equation}
-Подставляя в (\ref{eq:33}) $r=\lambda^{\frac{1}{d}}$ получаем выражение для скейлинговых параметров $a,b$:
-\begin{eqnarray}
-  \label{eq:50}
-  a=\frac{1}{\nu d}\\
-  b=\frac{d+2-\eta}{2d}
-\end{eqnarray}
-Для критических индексов имеем
-\begin{eqnarray}
-  \label{eq:51}
-  \alpha=2-\nu d\\
-  \beta=\frac{1}{2}\nu (d-2+\eta)\\
-  \gamma=\nu (2-\eta)\\
+  \label{eq:48} \Gamma'(\vec n)=\left< \Sigma_I\Sigma_J\right>-\left<
+\Sigma_I\right>\left<\Sigma_J\right>=\frac{1}{R^2}\sum_{i\in I}\sum_{j\in J}\left(\left<\sigma_i
+\sigma_j\right>-\left<\sigma_i\right>\left<\sigma_j\right>\right) =\\ =
+\frac{r^{2d}}{R^2}\Gamma(r\vec n)=\frac{R^{-2}r^{2d}}{\left|r\vec
+n\right|^{d-2+\eta}}=\frac{R^{-2}r^{d+2-\eta}}{\left|\vec n\right|^{d-2+\eta}}
+\end{multline} Отсюда
+\begin{equation}
+  \label{eq:49} R=r^{\frac{d+2-\eta}{2}}, \quad h'=r^{\frac{d+2-\eta}{2}}h
+\end{equation} Подставляя в (\ref{eq:33}) $r=\lambda^{\frac{1}{d}}$ получаем выражение для
+скейлинговых параметров $a,b$:
+\begin{eqnarray}
+  \label{eq:50} a=\frac{1}{\nu d}\\ b=\frac{d+2-\eta}{2d}
+\end{eqnarray} Для критических индексов имеем
+\begin{eqnarray}
+  \label{eq:51} \alpha=2-\nu d\\ \beta=\frac{1}{2}\nu (d-2+\eta)\\ \gamma=\nu (2-\eta)\\
 \delta=\frac{d+2-\eta}{d-2+\eta}
@@
 \subsection{Ренормгруппа в решеточных моделях}
-\label{sec:renormgroup-lattice-models}
-Мы обосновали гипотезу подобия при помощи рассмотрения блочных спинов и введения эффективного гамильтониана, имеющего ту же форму, но другие константы связи.
-Эта процедура является перенормировкой в координатном пространстве, она определяет отображение гамильтониана $H\to H'$.
-Последовательное применение такой процедуры порождает так называемую ренормгруппу.
-Строго говоря, ренормгруппа является не группой, а полугруппой, так как у преобразования нет обратного, ведь при переходе к блокам большего размера мы теряем информацию.
+\label{sec:renormgroup-lattice-models} Мы обосновали гипотезу подобия при помощи рассмотрения
+блочных спинов и введения эффективного гамильтониана, имеющего ту же форму, но другие константы
+связи. Эта процедура является перенормировкой в координатном пространстве, она определяет
+отображение гамильтониана $H\to H'$. Последовательное применение такой процедуры порождает так
+называемую ренормгруппу. Строго говоря, ренормгруппа является не группой, а полугруппой, так как у
+преобразования нет обратного, ведь при переходе к блокам большего размера мы теряем информацию.
 Опишем ренормгруппу для решеточных моделей.
 
-Рассматриваем решеточную модель, состоящую из $N$ спинов $\sigma_i$ на $d$-мерной решетке. Общий вид гамильтониана таких моделей
-\begin{equation}
-  \label{eq:55}
-  H(\vec J,[\sigma],N)=J_0 + J_1\sum_i \sigma_i +J_2\overset{(1)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j+J_3\overset{(2)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j + \dots
+Рассматриваем решеточную модель, состоящую из $N$ спинов $\sigma_i$ на $d$-мерной решетке. Общий вид
+гамильтониана таких моделей
+\begin{equation}
+  \label{eq:55} H(\vec J,[\sigma],N)=J_0 + J_1\sum_i \sigma_i
++J_2\overset{(1)}{\sum_{\left<ij\right>}}\sigma_i
+\sigma_j+J_3\overset{(2)}{\sum_{\left<ij\right>}}\sigma_i \sigma_j + \dots
+\end{equation} Здесь мы явно указали зависимость гамильтониана от констант связи, которые собраны в
+вектор $\vec J=(J_0,J_1,J_2,J_3,\dots)$. Сумма $\overset{(1)}{\sum_{\left<ij\right>}}$ - это сумма
+по ближайшим соседям, $\overset{(2)}{\sum_{\left<ij\right>}}$ - сумма по вершинам, разделенным двумя
+ребрами (через одного) и так далее. Статсумма
+\begin{equation}
+  \label{eq:56} Z(\vec J,N)=\sum_{[\sigma]}e^{-H(\vec J,[\sigma],N)}
+\end{equation} Мы так переопределили константы связи, чтобы избавиться от множителя $\beta$.
+
+Теперь мы вводим блочные переменные с блоком со стороной в $r$ ячеек решетки, содержащим $r^d$
+вершин. $\Sigma_I$ - блочные спины, $\xi_i$ - переменные внутри блока. В таких переменных статсумма
+переписывается так:
+\begin{equation}
+  \label{eq:57} Z(\vec J,N)=\sum_{[\Sigma][\sigma]}e^{-H(\vec J,[\Sigma],[\sigma],N)}
+\end{equation} Если мы просуммируем по внутриблочным степеням свободы $\xi$, то получится
+перенормированный гамильтониан $H'(\vec J,[\Sigma],Nr^{-d})$.
+\begin{equation}
+  \label{eq:58} e^{-H'(\vec J',[\Sigma],Nr^{-d})}=\sum_{[\xi]}e^{-H(\vec J,[\Sigma],[\xi],N)}
+\end{equation} Вблизи критической точки можно предполагать что у $H'$ такой же вид, как и у $H$, так
+как параметр порядка расходится и поведение определяется дальними корреляциями. Описания поведения
+системы в терминах $H'$ и $H$ эквивалентны, поэтому соответствующие выражения для статсуммы должны
+совпадать (с точностью до умножения на константу):
+\begin{equation}
+\label{eq:52} Z(\vec J,N)=\sum_{[\Sigma]}e^{-H'(\vec J',[\Sigma],Nr^{-d})}=Z(\vec J',Nr^{-d})
+\end{equation} Удельная свободная энергия отображается так: $f(\vec J)=r^{-d} f(\vec J')$.
+
+Отображение констант связи $\vec J\to\vec J'$ и порождает ренормгруппу. Будем его записывать как
+\begin{equation}
+  \label{eq:53} \vec J'=T(\vec J)
+\end{equation} Последовательное применение таких преобразований порождает в пространстве констант
+связи некоторый набор точек, который называется траекторией ренормгруппы.
+
+На каждом шаге корреляционная длина уменьшается в $r$ раз, поэтому траектория уводит систему из
+окрестности критической точки. Но в самой критической точке корреляционная длина бесконечна, поэтому
+эта точка неподвижна относительно действия ренормгруппы.
+
+В общем случае критическое поведение наблюдается на некоторой критической поверхности в пространстве
+$\vec J$. Под действием ренормгруппы точки двигаются по ней. Стационарная точка
+\begin{equation}
+  \label{eq:54} \vec J_c=T(\vec J_c)
+\end{equation} называется фиксированной точной ренормгруппы.
+
+Вообще говоря, преобразование $T$ нелинейно, однако в окрестности фиксированной точки его можно
+линеаризовать. Вводим переменную $\delta\vec J=\vec J-\vec J_c$ и раскладываем $T$ в ряд Тейлора по
+$\delta\vec J$. Тогда
+\begin{equation}
+  \label{eq:59} \delta\vec J'=A\delta\vec J,
+\end{equation} где $A$ - матрица, $A_{ij}=\frac{\partial T_i}{\partial J_j}$. Мы можем
+диагонализовать матрицу $A$, ее собственные значения мы обозначим через $\lambda_i$, собственные
+векторы через $\vec u_i$. Тогда для точки в пространстве констант связи мы можем написать (в
+окрестности критической точки):
+\begin{equation}
+  \label{eq:60} \vec J=\vec J_c+\sum_i t_i \vec u_i
+\end{equation} Переменные $t_i$ под действием ренормгруппы преобразуются так:
+\begin{equation}
+  \label{eq:61} t'_i=\lambda_i t_i=r^{y_i} t_i
+\end{equation} Здесь мы ввели обозначение $y_i$ для критических индексов. В примере из раздела
+\ref{sec:kadanoff-procedure} такими индексами были $a$ и $b$. Для свободной энергии имеем
+\begin{equation}
+  \label{eq:62} f(t_1,t_2,\dots)=r^{-d} f(r^{y_1}t_1,r^{y_2}t_2,\dots)
+\end{equation} Таким образом, критические индексы получаются из собственных значений линеаризованной
+ренормгруппы в фиксированной точке.
+
+Если часть собственных значений $\lambda_i$ положительна, а часть - отрицательная, то фиксированная
+точка называется гиперболической. Критической поверхностью называются такие точки $\vec J$, что
+\begin{equation}
+  \label{eq:63} \lim_{n\to \infty}T^n (\vec J)=\vec J_c
+\end{equation} Около точки $\vec J_c$ она представляет собой векторное пространство, натянутое на те
+векторы $\vec u_i$, для которых соответствующие собственные значения $\lambda_i<1$.
+
+Параметры $t_i$, которые соответствуют $\lambda_i>1$ называются релевантными, так как они растут под
+действием ренормгруппы. Параметры с $y_i<0 \; (\lambda_i<1)$ --- иррелевантные, с $y_i=0$ ---
+маргинальные.
+
+Существование критической поверхности объясняет универсальность критических индексов в разных
+моделях. Статистические системы разбиваются на классы универсальности, члены которых имеют
+одинаковое критическое поведение. Это так, если разные системы живут на подмногообразиях в
+пространстве констант связи, которые пересекают одну и ту же критическую поверхность. Тогда
+критическая точка у них общая.
+
+\subsection{Ренормгруппа в непрерывных моделях}
+\label{sec:renormgroup-general} В непрерывных моделях перенормировка осуществляется в импульсном
+пространстве. Рассмотрим скалярное поле $\varphi(\vec x)$, где $\vec x\in \mathbb{R}^d$. Проведем
+преобразование Фурье
+\begin{equation}
+  \label{eq:64} \varphi(\vec x)=\int \frac{d^d \vec k}{(2\pi)^d}\tilde \varphi(\vec k) e^{i\vec
+k\cdot \vec x}
+\end{equation} Функционал действия может быть переписан в виде, зависящем только от $\tilde\varphi$:
+$S[\varphi]\to S[\tilde\varphi]$. Например, для модели $\varphi^4$ \eqref{eq:16} получается
+\begin{multline}
+  \label{eq:65} S[\varphi,r,u]=\int \frac{d^d \vec k}{(2\pi)^d} \frac{1}{2} \tilde\varphi(-\vec
+k)\tilde\varphi(\vec k)(\vec k^2+r)+\\ \frac{1}{4}u\int \frac{d^d \vec k_1}{(2\pi)^d} \frac{d^d \vec
+k_2}{(2\pi)^d} \frac{d^d \vec k_3}{(2\pi)^d} \tilde\varphi(-\vec k_1-\vec k_2 -\vec k_3)\tilde
+\varphi(\vec k_1)\tilde\varphi (\vec k_2)\tilde\varphi(\vec k_3).
+\end{multline} В общем случае функционал действия зависит от поля $\varphi$ и параметров $u_i$ в
+плотности Лагранжиана (констант связи).
+
+Квантовая теория поля всегда содержит расходящиеся интегралы, поэтому нужна регуляризация. Будем
+считать, что в качестве такой регуляризации используется обрезание по импульсам $\left|\vec
+k\right|<\Lambda$. После преобразования Фурье мера в функциональном интеграле переписывается как
+\begin{equation}
+  \label{eq:66} [d\varphi]_{\Lambda}=\prod_x d\varphi(x)=\prod_{\left|\vec
+k\right|<\Lambda}d\tilde\varphi(\vec k)
+\end{equation} Теперь опишем перенормировку Вильсона-Каданова. Она проводится в два этапа. Сначала
+мы интегрируем по $\tilde\varphi(\vec k): \Lambda/s<\left|k\right|<\Lambda$. То есть мы исключаем
+быстрые моды, так как критическое поведение описывается медленными модами. $s$-масштабный фактор. В
+результате мы получаем новое обрезание $\Lambda/s$ и действие $S'[\varphi,\{u_i\}]$.
+\begin{equation}
+  \label{eq:67} e^{-S'[\varphi,\{u_i\}]}=\int \prod_{\Lambda/s<\left|\vec
+k\right|<\Lambda}d\varphi(\vec k)e^{-S[\varphi,\{u_i\}]}
+\end{equation} Пока нас интересую только медленные моды, действие $S'$ эквивалентно $S$. Вторым
+шагом осуществим масштабное преобразование
+\begin{eqnarray}
+  \label{eq:68} \vec k \to \vec k'=s \vec k\\ \vec x\to \vec x'=\vec x/s
+\end{eqnarray} При этом поле преобразуется так:
+\begin{eqnarray}
+  \label{eq:69} \varphi(\vec x)\to \varphi'(\vec x/s)=s^{\Delta}\varphi (\vec x)\\
+\tilde\varphi'(s\vec k)=s^{\Delta-d}\tilde\varphi (\vec k)
+\end{eqnarray} Здесь $\Delta$- скейлинговая размерность поля $\varphi$, она связана с индексом
+$\eta$: $\Delta=\eta/2$. Мера в функциональном интеграле при масштабном преобразовании умножится на
+константу. Теперь можно сравнить $S'$ и $S$, так как масштаб обрезания и там и там равен $\Lambda$ и
+те же степени свободы. Эти два действия описывают одинаковое поведение на больших расстояниях.
+Поэтому вид действия $S'$ должен быть тот же, что и у $S$, но с другими константами связи $u_i'$.
+\begin{equation}
+  \label{eq:70} S'[\varphi,\{u_i\}]=S[\varphi,\{u_i'\}]
+\end{equation} Последовательным действием таких преборазований мы получаем кривую $u_i(s)$ в
+пространстве параметров лагранжиана. Мы можем записать уравнение этой кривой как
+\begin{equation}
+  \label{eq:71} \frac{du_i}{d(\ln s)}=\beta_i(\{u_i\})
+\end{equation} $\beta_i$ называется $\beta$-функцией параметра $u_i$. Фиксированная точка $u_j^{*}$:
+\begin{equation}
+  \label{eq:72} \beta_i(\{u^{*}_j\})=0
+\end{equation} Эта точка неподвижна относительно преобразований ренормгруппы. В фиксированной точке
+теория масштабно-инвариантна на квантовом уровне.
+
+\subsection{Уравнение Каллана-Симанчика}
+
+Вообще говоря, квантовая теория поля может быть не масштабно-инвариантна из-за наличия размерных
+параметров на классическом уровне или возникающих при перенормировке. Действие
+\begin{equation}
+  \label{eq:73} S=\int d^dx \mathcal{L}
+\end{equation} зависит от полей $\varphi$ и констант связи $\vec u=(u_1,\dots,u_n)$. Рассмотрим
+инфинитезимальное масштабное преобразование $\lambda=1+\omega$. При этом вариация $x_{\nu}$ будет
+$\delta_{\omega}x_{\nu}=\omega x_{\nu}$. Такое преобразование, в соответствии с предыдущей лекцией,
+можно рассматривать как преобразование констант связи $\vec u\to \vec u'$. При наличии масштабной
+инвариантности $\vec u = \vec u'$. При инфинитезимальных преобразованиях $x\to x+dl x$ вариация
+плотности лагранжиана дается Нётеровским током:
+\begin{equation}
+  \label{eq:74} \delta\mathcal{L}=\partial_{\mu}J^{\mu}dl
 \end{equation}
-Здесь мы явно указали зависимость гамильтониана от констант связи, которые собраны в вектор $\vec J=(J_0,J_1,J_2,J_3,\dots)$.
-Сумма $\overset{(1)}{\sum_{\left<ij\right>}}$ - это сумма по ближайшим соседям, $\overset{(2)}{\sum_{\left<ij\right>}}$ - сумма по вершинам, разделенным двумя ребрами (через одного) и так далее.
-Статсумма
-\begin{equation}
-  \label{eq:56}
-  Z(\vec J,N)=\sum_{[\sigma]}e^{-H(\vec J,[\sigma],N)}
+\begin{equation}
+  \label{eq:75} J^{\mu}=x_{\nu}T^{\mu\nu}
+\end{equation} Здесь $T^{\mu\nu}$ - тензор энергии-импульса. Через $\Theta$ мы обозначим след
+тензора энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия
+\begin{equation}
+  \label{eq:87} \delta S=dl \int d^d x \Theta(x)
+\end{equation} Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$.
+В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
+
+В классической теории вид преобразований полей при масштабных преобразованиях легко получаются из
+анализа размерностей. Напомним, что достаточно иметь одну единицу измерения - длины (или обратной
+длины). Если теория масштабно-инвариантна, то действие должно быть безразмерным. Канонические
+(классические) размерности полей легко определить из требования безразмерности слагаемых в
+функционале действия, если ввести соглашение, определяющее размерность координат или импульсов.
+
+Будем обозначать каноническую размерность произвольно величины $F$ через $d[F]$. Положим
+$d[p]=-d[x]=1$. Тогда $d[d^d x]=-d,\; d[\partial]=1$. Теперь легко найти размерности полей.
+Например, для модели $\varphi^4$
+\begin{equation}
+  \label{eq:83} S[\varphi]=\int d^d x\left( -\frac{(\partial \varphi)^2}{2}-\frac{\mu
+\varphi^2}{2}-\frac{u\varphi^4}{24}+h\varphi\right),
+\end{equation} рассмотрим первое слагаемое. Оно должно быть безразмерным. При этом его размерность
+$d[\int d^d x (\partial \varphi)^2]=2d[\varphi]+2-d=0$. Отсюда $d[\varphi]=d/2-1$. Для общего
+действия
+\begin{equation}
+  \label{eq:84} S[\varphi]=-\int d^d x\left( \frac{(\partial \varphi)^2}{2}+\sum_n u_n
+\frac{\varphi^n}{n!}\right)
+\end{equation} размерности констант связи следующие:
+\begin{equation}
+  \label{eq:85} d[h=-u_1]=d/2+1,\quad d[\mu=u_2]=2,\quad d[g_4]=4-d,\quad d[g_6]=6-2d,\quad
+d[g_n]=n-\frac{d(n-2)}{2}
+\end{equation} При масштабных преобразованиях поля и константы связи ведут себя так:
+\begin{equation}
+  \label{eq:86} \varphi'(x)=s^{-d[\varphi]}\varphi(x/s),\quad u_i'=s^{-d[u_i]}u_i
 \end{equation}
-Мы так переопределили константы связи, чтобы избавиться от множителя $\beta$.
-
-Теперь мы вводим блочные переменные с блоком со стороной в $r$ ячеек решетки, содержащим $r^d$ вершин.
-$\Sigma_I$ - блочные спины, $\xi_i$ - переменные внутри блока.
-В таких переменных статсумма переписывается так:
-\begin{equation}
-  \label{eq:57}
-  Z(\vec J,N)=\sum_{[\Sigma][\sigma]}e^{-H(\vec J,[\Sigma],[\sigma],N)}
+
+Напомним, что
+\begin{equation}
+  \label{eq:76} \beta_{i}(\vec u)=\frac{du_i}{d\ln s}
+\end{equation} Параметр ренормгруппы $s$ связан с параметром масштабного преобразования $l$
+соотношением $l=\ln s$, при этом
+\begin{equation}
+  \label{eq:79} \beta_{i}(\vec u)=\frac{du_i}{dl}
+\end{equation} Если в точке $u$ $\beta_i(\vec u)>0$, то $u_i(l)$ растет, $\beta_i (\vec u)<0$ -
+убывает. В фиксированной точке $u^*$ $\beta_i(\vec u^*)=0$. Пространство действий делится
+фиксированной точкой на регионы. Константы связи ``заперты'' в одном из этих регионов. Фиксированная
+точка может достигаться при $l\to \pm \infty$. Если $u(l)\to u^*$ при $l\to +\infty$, то такая точка
+называется инфракрасной, если $u(l)\to u^*$ при $l\to -\infty$, то ультрафиолетовой. Введем функции
+$\Phi_i$:
+\begin{equation}
+  \label{eq:77} \Phi_i=\frac{\partial \mathcal{L}}{\partial u_i}
+\end{equation} Вариация $\delta \mathcal{L}$ дается их линейной комбинацией.
+\begin{equation}
+  \label{eq:78} \Theta(x)=\frac{\partial \mathcal{L}}{\partial l}=\sum_i \frac{\partial
+\mathcal{L}}{\partial u_i}\frac{d u_i}{dl}=\sum_i\beta_i(\vec u)\Phi_i(\vec u)
+\end{equation} $\Theta=0$ тогда и только тогда, когда $\beta_i(\vec u)=0$, значит в фиксированной
+точке ренормгруппы есть масштабная инвариантность.
+
+Рассмотрим $N$-точечную корреляционную функцию --- среднее значение некоторого $N$-точечного
+локального оператора
+\begin{equation}
+  \label{eq:81} \langle X\rangle =\langle A_1 (x_1)\dots A_N (x_N)\rangle
 \end{equation}
-Если мы просуммируем по внутриблочным степеням свободы $\xi$, то получится перенормированный гамильтониан $H'(\vec J,[\Sigma],Nr^{-d})$.
-\begin{equation}
-  \label{eq:58}
-  e^{-H'(\vec J',[\Sigma],Nr^{-d})}=\sum_{[\xi]}e^{-H(\vec J,[\Sigma],[\xi],N)}
-\end{equation}
-Вблизи критической точки можно предполагать что у $H'$ такой же вид, как и у $H$, так как параметр порядка расходится и поведение определяется дальними корреляциями.
-Описания поведения системы в терминах $H'$ и $H$ эквивалентны, поэтому соответствующие выражения для статсуммы должны совпадать (с точностью до умножения на константу):
-\begin{equation}
-\label{eq:52}
-  Z(\vec J,N)=\sum_{[\Sigma]}e^{-H'(\vec J',[\Sigma],Nr^{-d})}=Z(\vec J',Nr^{-d})
-\end{equation}
-Удельная свободная энергия отображается так: $f(\vec J)=r^{-d} f(\vec J')$.
-
-Отображение констант связи $\vec J\to\vec J'$ и порождает ренормгруппу. Будем его записывать как
-\begin{equation}
-  \label{eq:53}
-  \vec J'=T(\vec J)
-\end{equation}
-Последовательное применение таких преобразований порождает в пространстве констант связи некоторый набор точек, который называется траекторией ренормгруппы.
-
-На каждом шаге корреляционная длина уменьшается в $r$ раз, поэтому траектория уводит систему из окрестности критической точки.
-Но в самой критической точке корреляционная длина бесконечна, поэтому эта точка неподвижна относительно действия ренормгруппы.
-
-В общем случае критическое поведение наблюдается на некоторой критической поверхности в пространстве $\vec J$. Под действием ренормгруппы точки двигаются по ней. Стационарная точка
-\begin{equation}
-  \label{eq:54}
-  \vec J_c=T(\vec J_c)
-\end{equation}
-называется фиксированной точной ренормгруппы.
-
-Вообще говоря, преобразование $T$ нелинейно, однако в окрестности фиксированной точки его можно линеаризовать.
-Вводим переменную $\delta\vec J=\vec J-\vec J_c$ и раскладываем $T$ в ряд Тейлора по $\delta\vec J$.
-Тогда
-\begin{equation}
-  \label{eq:59}
-  \delta\vec J'=A\delta\vec J,
-\end{equation}
-где $A$ - матрица, $A_{ij}=\frac{\partial T_i}{\partial J_j}$.
-Мы можем диагонализовать матрицу $A$, ее собственные значения мы обозначим через $\lambda_i$, собственные векторы через $\vec u_i$.
-Тогда для точки в пространстве констант связи мы можем написать (в окрестности  критической точки):
-\begin{equation}
-  \label{eq:60}
-  \vec J=\vec J_c+\sum_i t_i \vec u_i
-\end{equation}
-Переменные $t_i$ под действием ренормгруппы преобразуются так:
-\begin{equation}
-  \label{eq:61}
-  t'_i=\lambda_i t_i=r^{y_i} t_i
-\end{equation}
-Здесь мы ввели обозначение $y_i$ для критических индексов. В примере из раздела \ref{sec:kadanoff-procedure} такими индексами были $a$ и $b$. 
-Для свободной энергии имеем
-\begin{equation}
-  \label{eq:62}
-  f(t_1,t_2,\dots)=r^{-d} f(r^{y_1}t_1,r^{y_2}t_2,\dots)
-\end{equation}
-Таким образом, критические индексы получаются из собственных значений линеаризованной ренормгруппы в фиксированной точке.
-
-Если часть собственных значений $\lambda_i$ положительна, а часть - отрицательная, то фиксированная точка называется гиперболической. 
-Критической поверхностью называются такие точки $\vec J$, что
-\begin{equation}
-  \label{eq:63}
-  \lim_{n\to \infty}T^n (\vec J)=\vec J_c
-\end{equation}
-Около точки $\vec J_c$ она представляет собой векторное пространство, натянутое на те векторы $\vec u_i$, для которых соответствующие собственные значения $\lambda_i<1$.
-
-Параметры $t_i$, которые соответствуют $\lambda_i>1$ называются релевантными, так как они растут под действием ренормгруппы.
-Параметры с $y_i<0 \; (\lambda_i<1)$ --- иррелевантные, с $y_i=0$ --- маргинальные.
-
-Существование критической поверхности объясняет универсальность критических индексов в разных моделях.
-Статистические системы разбиваются на классы универсальности, члены которых имеют одинаковое критическое поведение.
-Это так, если разные системы живут на подмногообразиях в пространстве констант связи, которые пересекают одну и ту же критическую поверхность.
-Тогда критическая точка у них общая.
-
-\subsection{Ренормгруппа в непрерывных моделях}
-\label{sec:renormgroup-general}
-В непрерывных моделях перенормировка осуществляется в импульсном пространстве. Рассмотрим скалярное поле $\varphi(\vec x)$, где $\vec x\in \mathbb{R}^d$. Проведем преобразование Фурье
-\begin{equation}
-  \label{eq:64}
-  \varphi(\vec x)=\int \frac{d^d \vec k}{(2\pi)^d}\tilde \varphi(\vec k) e^{i\vec k\cdot \vec x}
-\end{equation}
-Функционал действия может быть переписан в виде, зависящем только от $\tilde\varphi$: $S[\varphi]\to S[\tilde\varphi]$. Например, для модели $\varphi^4$ \eqref{eq:16} получается
-\begin{multline}
-  \label{eq:65}
-  S[\varphi,r,u]=\int  \frac{d^d \vec k}{(2\pi)^d} \frac{1}{2} \tilde\varphi(-\vec k)\tilde\varphi(\vec k)(\vec k^2+r)+\\
-  \frac{1}{4}u\int  \frac{d^d \vec k_1}{(2\pi)^d} \frac{d^d \vec k_2}{(2\pi)^d} \frac{d^d \vec k_3}{(2\pi)^d} \tilde\varphi(-\vec k_1-\vec k_2 -\vec k_3)\tilde \varphi(\vec k_1)\tilde\varphi (\vec k_2)\tilde\varphi(\vec k_3).
-\end{multline}
-В общем случае функционал действия зависит от поля $\varphi$ и параметров $u_i$ в плотности Лагранжиана (констант связи).
-
-Квантовая теория поля всегда содержит расходящиеся интегралы, поэтому нужна регуляризация.
-Будем считать, что в качестве такой регуляризации используется обрезание по импульсам $\left|\vec k\right|<\Lambda$.
-После преобразования Фурье мера в функциональном интеграле переписывается как
-\begin{equation}
-  \label{eq:66}
-  [d\varphi]_{\Lambda}=\prod_x d\varphi(x)=\prod_{\left|\vec k\right|<\Lambda}d\tilde\varphi(\vec k)
-\end{equation}
-Теперь опишем перенормировку Вильсона-Каданова.
-Она проводится в два этапа.
-Сначала мы интегрируем по $\tilde\varphi(\vec k): \Lambda/s<\left|k\right|<\Lambda$.
-То есть мы исключаем быстрые моды, так как критическое поведение описывается медленными модами.
-$s$-масштабный фактор.
-В результате мы получаем новое обрезание $\Lambda/s$ и действие $S'[\varphi,\{u_i\}]$.
-\begin{equation}
-  \label{eq:67}
-  e^{-S'[\varphi,\{u_i\}]}=\int \prod_{\Lambda/s<\left|\vec k\right|<\Lambda}d\varphi(\vec k)e^{-S[\varphi,\{u_i\}]}
-\end{equation}
-Пока нас интересую только медленные моды, действие $S'$ эквивалентно $S$. Вторым шагом осуществим масштабное преобразование
-\begin{eqnarray}
-  \label{eq:68}
-  \vec k \to \vec k'=s \vec k\\
-  \vec x\to \vec x'=\vec x/s
-\end{eqnarray}
-При этом поле преобразуется так:
-\begin{eqnarray}
-  \label{eq:69}
-  \varphi(\vec x)\to \varphi'(\vec x/s)=s^{\Delta}\varphi (\vec x)\\
-  \tilde\varphi'(s\vec k)=s^{\Delta-d}\tilde\varphi (\vec k)
-\end{eqnarray}
-Здесь $\Delta$- скейлинговая размерность поля $\varphi$, она связана с индексом $\eta$: $\Delta=\eta/2$.
-Мера в функциональном интеграле при масштабном преобразовании умножится на константу.
-Теперь можно сравнить $S'$ и $S$, так как масштаб обрезания и там и там равен $\Lambda$ и те же степени свободы.
-Эти два действия описывают одинаковое поведение на больших расстояниях.
-Поэтому вид действия $S'$ должен быть тот же, что и у $S$, но с другими константами связи $u_i'$.
-\begin{equation}
-  \label{eq:70}
-  S'[\varphi,\{u_i\}]=S[\varphi,\{u_i'\}]
-\end{equation}
-Последовательным действием таких преборазований мы получаем кривую $u_i(s)$ в пространстве параметров лагранжиана.  Мы можем записать уравнение этой кривой как
-\begin{equation}
-  \label{eq:71}
-  \frac{du_i}{d(\ln s)}=\beta_i(\{u_i\})
-\end{equation}
-$\beta_i$ называется $\beta$-функцией параметра $u_i$. 
-Фиксированная точка $u_j^{*}$:
-\begin{equation}
-  \label{eq:72}
-  \beta_i(\{u^{*}_j\})=0
-\end{equation}
-Эта точка неподвижна относительно преобразований ренормгруппы. В фиксированной точке теория масштабно-инвариантна на квантовом уровне.
-
-\subsection{Уравнение Каллана-Симанчика}
-
-Вообще говоря, квантовая теория поля может быть не масштабно-инвариантна из-за наличия размерных параметров на классическом уровне или возникающих при перенормировке. Действие
-\begin{equation}
-  \label{eq:73}
-  S=\int d^dx \mathcal{L}
-\end{equation}
-зависит от полей $\varphi$ и констант связи $\vec u=(u_1,\dots,u_n)$.
-Рассмотрим инфинитезимальное масштабное преобразование $\lambda=1+\omega$.
-При этом вариация $x_{\nu}$ будет $\delta_{\omega}x_{\nu}=\omega x_{\nu}$.
-Такое преобразование, в соответствии с предыдущей лекцией,  можно рассматривать как преобразование констант связи $\vec u\to \vec u'$.
-При наличии масштабной инвариантности $\vec u = \vec u'$.
-При инфинитезимальных преобразованиях $x\to x+dl x$ вариация плотности лагранжиана дается Нётеровским током:
-\begin{equation}
-  \label{eq:74}
-  \delta\mathcal{L}=\partial_{\mu}J^{\mu}dl
-\end{equation}
-\begin{equation}
-  \label{eq:75}
-  J^{\mu}=x_{\nu}T^{\mu\nu}
-\end{equation}
-Здесь $T^{\mu\nu}$ - тензор энергии-импульса.  Через $\Theta$ мы обозначим след тензора энергии-импульса $\Theta=\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}$. Он задает вариацию действия
-\begin{equation}
-  \label{eq:87}
-  \delta S=dl \int d^d x \Theta(x)
-\end{equation}
-Если теория масштабно-инвариантна, то $\partial_{\mu}J^{\mu}=T_{\mu}^{\mu}=\Theta=0$. В масштабно-инвариантной теории тензор энергии-импульса бесследовый.
-
-В классической теории вид преобразований полей при масштабных преобразованиях легко получаются из анализа размерностей.
-Напомним, что достаточно иметь одну единицу измерения - длины (или обратной длины).
-Если теория масштабно-инвариантна, то действие должно быть безразмерным.
-Канонические (классические) размерности полей легко определить из требования безразмерности слагаемых в функционале действия, если ввести соглашение, определяющее размерность координат или импульсов.
-
-Будем обозначать каноническую размерность произвольно величины $F$ через $d[F]$.
-Положим $d[p]=-d[x]=1$. Тогда $d[d^d x]=-d,\; d[\partial]=1$. Теперь легко найти размерности полей. Например, для модели $\varphi^4$
-\begin{equation}
-  \label{eq:83}
-  S[\varphi]=\int d^d x\left( -\frac{(\partial \varphi)^2}{2}-\frac{\mu \varphi^2}{2}-\frac{u\varphi^4}{24}+h\varphi\right),
-\end{equation}
-рассмотрим первое слагаемое. Оно должно быть безразмерным. При этом его размерность $d[\int d^d x (\partial \varphi)^2]=2d[\varphi]+2-d=0$. Отсюда $d[\varphi]=d/2-1$. Для общего действия
-\begin{equation}
-  \label{eq:84}
-  S[\varphi]=-\int d^d x\left( \frac{(\partial \varphi)^2}{2}+\sum_n u_n \frac{\varphi^n}{n!}\right)
-\end{equation}
-размерности констант связи следующие:
-\begin{equation}
-  \label{eq:85}
-  d[h=-u_1]=d/2+1,\quad d[\mu=u_2]=2,\quad d[g_4]=4-d,\quad d[g_6]=6-2d,\quad d[g_n]=n-\frac{d(n-2)}{2}
-\end{equation}
-При масштабных преобразованиях поля и константы связи ведут себя так:
-\begin{equation}
-  \label{eq:86}
-  \varphi'(x)=s^{-d[\varphi]}\varphi(x/s),\quad u_i'=s^{-d[u_i]}u_i
-\end{equation}
-
-Напомним, что
-\begin{equation}
-  \label{eq:76}
-  \beta_{i}(\vec u)=\frac{du_i}{d\ln s}
-\end{equation}
-Параметр ренормгруппы $s$ связан с параметром масштабного преобразования $l$ соотношением $l=\ln s$, при этом
-\begin{equation}
-  \label{eq:79}
-   \beta_{i}(\vec u)=\frac{du_i}{dl}
-\end{equation}
-Если в точке $u$ $\beta_i(\vec u)>0$, то $u_i(l)$ растет, $\beta_i (\vec u)<0$ - убывает.
-В фиксированной точке $u^*$ $\beta_i(\vec u^*)=0$.
-Пространство действий делится фиксированной точкой на регионы.
-Константы связи ``заперты'' в одном из этих регионов.
-Фиксированная точка может достигаться при $l\to \pm \infty$.
-Если $u(l)\to u^*$ при $l\to +\infty$, то такая точка называется инфракрасной, если $u(l)\to u^*$ при $l\to -\infty$, то ультрафиолетовой.
-Введем функции $\Phi_i$:
-\begin{equation}
-  \label{eq:77}
-  \Phi_i=\frac{\partial \mathcal{L}}{\partial u_i}
-\end{equation}
-Вариация $\delta \mathcal{L}$ дается их линейной комбинацией.
-\begin{equation}
-  \label{eq:78}
-  \Theta(x)=\frac{\partial \mathcal{L}}{\partial l}=\sum_i \frac{\partial \mathcal{L}}{\partial u_i}\frac{d u_i}{dl}=\sum_i\beta_i(\vec u)\Phi_i(\vec u)
-\end{equation}
-$\Theta=0$ тогда и только тогда, когда $\beta_i(\vec u)=0$, значит в фиксированной точке ренормгруппы есть масштабная инвариантность.
-
-Рассмотрим $N$-точечную корреляционную функцию --- среднее значение некоторого $N$-точечного локального оператора
-\begin{equation}
-  \label{eq:81}
-  \langle X\rangle =\langle A_1 (x_1)\dots A_N (x_N)\rangle
-\end{equation}
-
-Мы хотим получить уравнение для его преобразования под действием ренормгруппы. Такое уравнение называется уравнением Каллана-Симанчика.
+
+Мы хотим получить уравнение для его преобразования под действием ренормгруппы. Такое уравнение
+называется уравнением Каллана-Симанчика.
 
@@
 \begin{multline}
-  \label{eq:82}
-  \delta \langle X\rangle=\delta \langle A_1(x_1)\dots A_N (x_N)\rangle = \delta \int {\cal D}\varphi A_1 \dots A_N e^{-S[\varphi]} = \\
-  \delta \int {\cal D} \varphi\; \left( \sum_k A_1 \dots \delta A_k \dots A_N e^{-S[\varphi]} -A_1\dots A_N e^{-S[\varphi]}\delta S\right)
-\end{multline}
-Вариация $A_k$ дается глобальной дилатацией координат и внутренней вариацией поля в соответствии с его канонической размерностью:
-\begin{equation}
-  \label{eq:88}
-  \delta A_k=dl (x^{\mu}_k\partial^k_{\mu}+d[A_k]) A_k
+  \label{eq:82} \delta \langle X\rangle=\delta \langle A_1(x_1)\dots A_N (x_N)\rangle = \delta \int
+{\cal D}\varphi A_1 \dots A_N e^{-S[\varphi]} = \\ \delta \int {\cal D} \varphi\; \left( \sum_k A_1
+\dots \delta A_k \dots A_N e^{-S[\varphi]} -A_1\dots A_N e^{-S[\varphi]}\delta S\right)
+\end{multline} Вариация $A_k$ дается глобальной дилатацией координат и внутренней вариацией поля в
+соответствии с его канонической размерностью:
+\begin{equation}
+  \label{eq:88} \delta A_k=dl (x^{\mu}_k\partial^k_{\mu}+d[A_k]) A_k
+\end{equation} Вариация действия определяется следом тензора энергии-импульса (\ref{eq:87}). Поэтому
+\begin{equation}
+  \label{eq:89} \delta\langle X\rangle=dl \left(\sum_k (x_k^{\mu}\partial_{\mu}^k+d[A_k])\langle
+X\rangle-\int d^d y \langle\Theta(y)X\rangle\right)
 \end{equation}
-Вариация действия определяется следом тензора энергии-импульса (\ref{eq:87}). Поэтому
-\begin{equation}
-  \label{eq:89}
-  \delta\langle X\rangle=dl \left(\sum_k (x_k^{\mu}\partial_{\mu}^k+d[A_k])\langle X\rangle-\int d^d y \langle\Theta(y)X\rangle\right)
-\end{equation}
 
@@
 \begin{equation}
-  \label{eq:90}
-  \delta\langle X\rangle=dl\sum_i \beta_i(\vec u)\frac{\partial}{\partial u_i}\langle X\rangle,
-\end{equation}
-но
-\begin{equation}
-  \label{eq:91}
-  \frac{\partial}{\partial u_i}\langle X\rangle=\sum_k \langle A_1\dots \frac{\partial A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Phi_i(y)\rangle.
-\end{equation}
-Отсюда
-\begin{equation}
-  \label{eq:92}
-  \delta\langle X\rangle=dl \sum_i \sum_k\langle A_1\dots \frac{\partial A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Theta(y)\rangle
-\end{equation}
-Сравнивая это уравнение с (\ref{eq:89}) получаем уравнение Каллана-Симанчика:
-\begin{equation}
-  \label{eq:93}
-  \left[ \sum_k\left( x^{\mu}_k \frac{\partial}{\partial x^{\mu}_k}+\Gamma_k(\vec u)\right) -\sum_i \beta_i(\vec u)\frac{\partial }{\partial u_i}\right]\langle X\rangle=0,
-\end{equation}
-где $\Gamma_k$ - аномальная размерность поля $A_k(x_k)$, определяющаяся выражением
-\begin{equation}
-  \label{eq:94}
-  \Gamma_k A_k(x_k)=\left( d[A_k]+\sum_i \beta_i(\vec u) \frac{\partial }{\partial u_i}\right) A_k(x_k).
-\end{equation}
-В частности, для следа тензора энергии-импульса $\Gamma \Theta=2 \Theta$, то есть аномальная размерность равна классической.
-Это верно и для других компонент тензора энергии-импульса в силу Лоренц-инвариантности.
+  \label{eq:90} \delta\langle X\rangle=dl\sum_i \beta_i(\vec u)\frac{\partial}{\partial u_i}\langle
+X\rangle,
+\end{equation} но
+\begin{equation}
+  \label{eq:91} \frac{\partial}{\partial u_i}\langle X\rangle=\sum_k \langle A_1\dots \frac{\partial
+A_k}{\partial u_i}\dots A_N\rangle-\int d^d y \langle X \Phi_i(y)\rangle.
+\end{equation} Отсюда
+\begin{equation}
+  \label{eq:92} \delta\langle X\rangle=dl \sum_i \sum_k\langle A_1\dots \frac{\partial A_k}{\partial
+u_i}\dots A_N\rangle-\int d^d y \langle X \Theta(y)\rangle
+\end{equation} Сравнивая это уравнение с (\ref{eq:89}) получаем уравнение Каллана-Симанчика:
+\begin{equation}
+  \label{eq:93} \left[ \sum_k\left( x^{\mu}_k \frac{\partial}{\partial x^{\mu}_k}+\Gamma_k(\vec
+u)\right) -\sum_i \beta_i(\vec u)\frac{\partial }{\partial u_i}\right]\langle X\rangle=0,
+\end{equation} где $\Gamma_k$ - аномальная размерность поля $A_k(x_k)$, определяющаяся выражением
+\begin{equation}
+  \label{eq:94} \Gamma_k A_k(x_k)=\left( d[A_k]+\sum_i \beta_i(\vec u) \frac{\partial }{\partial
+u_i}\right) A_k(x_k).
+\end{equation} В частности, для следа тензора энергии-импульса $\Gamma \Theta=2 \Theta$, то есть
+аномальная размерность равна классической. Это верно и для других компонент тензора энергии-импульса
+в силу Лоренц-инвариантности.
 
@@
 
-Реноргрупповой анализ квантовой теории поля в двух измерениях дает следующий результат, известный как $c$-теорема Замолодчикова \cite{zamolodchikov1986irreversibility}.
-
-\begin{theorem}
-  Для любой унитарной квантовой теории поля в двух измерениях существует функция $c(\vec u)$ такая, что
+Реноргрупповой анализ квантовой теории поля в двух измерениях дает следующий результат, известный
+как $c$-теорема Замолодчикова \cite{zamolodchikov1986irreversibility}.
+
+\begin{theorem} Для любой унитарной квантовой теории поля в двух измерениях существует функция
+$c(\vec u)$ такая, что
   \label{c-theorem}
@@
     \begin{equation}
-      \label{eq:95}
-      \frac{dc}{dl}\leq 0
+      \label{eq:95} \frac{dc}{dl}\leq 0
     \end{equation}
@@
     \begin{equation}
-      \label{eq:96}
-      \frac{dc({\vec u^*})}{dl}=0 \Leftrightarrow \beta_i(\vec u^*)=0
+      \label{eq:96} \frac{dc({\vec u^*})}{dl}=0 \Leftrightarrow \beta_i(\vec u^*)=0
     \end{equation}
-  \item 2-точечные корреляторы в фиксированной точке полностью определяются значением $c=c(\vec u^*)$.
-    Если ввести комплексные координаты $z=x_1+ix_2,\quad \bar z=x_1-ix_2$ и обозначить компоненты тензора энергии импульса через $T=T_{zz}$, $\bar T=T_{\bar z\bar z}$, $\Theta=T_{z\bar z}=T_{\bar z z}=T_{\mu\mu}=0$, то для корреляторов верно следующее выражение
-    \begin{eqnarray}
-      \label{eq:97}
-      \langle T(z,\bar z)T(0,0)\rangle=\frac{c/2}{z^4}\\
-      \langle \bar T(z,\bar z)\bar T(0,0)\rangle=\frac{c/2}{\bar z^4}\\
-      \langle T(z,\bar z) \bar T(0,0)\rangle=0
-    \end{eqnarray}
-    Число $c=\lim_{\vec u\to \vec u^*} c(\vec u)$ называется центральным зарядом. 
+  \item 2-точечные корреляторы в фиксированной точке полностью определяются значением $c=c(\vec
+u^*)$. Если ввести комплексные координаты $z=x_1+ix_2,\quad \bar z=x_1-ix_2$ и обозначить компоненты
+тензора энергии импульса через $T=T_{zz}$, $\bar T=T_{\bar z\bar z}$, $\Theta=T_{z\bar z}=T_{\bar z
+z}=T_{\mu\mu}=0$, то для корреляторов верно следующее выражение
+    \begin{eqnarray}
+      \label{eq:97} \langle T(z,\bar z)T(0,0)\rangle=\frac{c/2}{z^4}\\ \langle \bar T(z,\bar z)\bar
+T(0,0)\rangle=\frac{c/2}{\bar z^4}\\ \langle T(z,\bar z) \bar T(0,0)\rangle=0
+    \end{eqnarray} Число $c=\lim_{\vec u\to \vec u^*} c(\vec u)$ называется центральным зарядом.
   \end{itemize}
-\end{theorem}
-Для унитарных теорий из этой теоремы следует, что $c_{UV}\geq c_{IR}$.
+\end{theorem} Для унитарных теорий из этой теоремы следует, что $c_{UV}\geq c_{IR}$.
 
@@
 \begin{equation}
-  \label{eq:123}
-  g'_{\mu\nu}(x')=\Lambda(x) g_{\mu\nu}(x).
-\end{equation}
-Заметим, что группа Пуанкаре является подгруппой конформной группы с $\Lambda(x)=1$, а также что
-конформные преобразования сохраняют углы.
+  \label{eq:123} g'_{\mu\nu}(x')=\Lambda(x) g_{\mu\nu}(x).
+\end{equation} Заметим, что группа Пуанкаре является подгруппой конформной группы с $\Lambda(x)=1$,
+а также что конформные преобразования сохраняют углы.
 
@@
 \begin{equation}
-  \label{eq:144}
-  x^{\mu}\to x'^{\mu}=x^{\mu}+\epsilon^{\mu}.
-\end{equation}
-Метрический тензор преобразуется следующим образом:
-\begin{equation}
-  \label{eq:145}
-  g'_{\mu\nu}=\frac{\partial x^{\alpha}}{\partial x'^{\mu}}\frac{\partial x^{\beta}}{\partial
-    x'^{\nu}}
+  \label{eq:144} x^{\mu}\to x'^{\mu}=x^{\mu}+\epsilon^{\mu}.
+\end{equation} Метрический тензор преобразуется следующим образом:
+\begin{equation}
+  \label{eq:145} g'_{\mu\nu}=\frac{\partial x^{\alpha}}{\partial x'^{\mu}}\frac{\partial
+x^{\beta}}{\partial x'^{\nu}}
 g_{\alpha\beta}=(\delta^{\alpha}_{\mu}-\partial_{\mu}\epsilon^{\alpha})(\delta^{\beta}_{\nu}-\partial_{\nu}
 \epsilon^{\beta})g_{\alpha\beta}=g_{\mu\nu}-(\partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu})
-\end{equation}
-Перепишем условие (\ref{eq:123})в таком виде:
-\begin{equation}
-  \label{eq:146}
-  g'_{\mu\nu}(x')=g_{\mu\nu}(x)-f(x)g_{\mu\nu}(x)
-\end{equation}
-Отсюда вытекает условие на вид преобразований:
+\end{equation} Перепишем условие (\ref{eq:123})в таком виде:
+\begin{equation}
+  \label{eq:146} g'_{\mu\nu}(x')=g_{\mu\nu}(x)-f(x)g_{\mu\nu}(x)
+\end{equation} Отсюда вытекает условие на вид преобразований:
 \begin{equation}
@@
   \partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu}=f(x)g_{\mu\nu}(x).
-\end{equation}
-Для простоты рассмотрим преобразования, действующие на плоскую метрику
+\end{equation} Для простоты рассмотрим преобразования, действующие на плоскую метрику
 $g_{\mu\nu}(x)=\eta_{\mu\nu}$, кроме того, с учетом приложений к статистической физике, будем
@@
 \begin{equation}
-  \label{eq:148}
-  f(x)=\frac{2}{d}\partial_{\rho}\epsilon^{\rho}.
+  \label{eq:148} f(x)=\frac{2}{d}\partial_{\rho}\epsilon^{\rho}.
+\end{equation} Теперь подставим $g_{\mu\nu}=\eta_{\mu\nu}$ в уравнение \eqref{eq:147} и
+продиффернцируем:
+\begin{equation}
+  \label{eq:149}
+  \partial_{\rho} \partial_{\mu}\epsilon_{\nu}+\partial_{\rho}\partial_{\nu}\epsilon_{\mu}=\eta_{\mu\nu}\partial_{\rho}
+f.
+\end{equation} Переставим два раза значки и скомбинируем три уравнения в одно:
+\begin{equation}
+  \label{eq:150} 2\partial_{\mu}\partial_{\nu}\epsilon_{\rho}=\eta_{\mu\rho}\partial_{\nu}
+f+\eta_{\nu\rho}\partial_{\mu}f-\eta_{\mu\nu}\partial_{\rho}f
+\end{equation} Свернем это уравнение с $\eta^{\mu\nu}$ и получим
+\begin{equation}
+  \label{eq:151} 2\partial^2 \epsilon_{\rho}=(2-d)\partial_{\rho}f
+\end{equation} Теперь продифференцируем его по $x^{\nu}$ и поменяем значок $\rho$ на $\mu$:
+\begin{equation}
+  \label{eq:152} 2\partial^2 \partial_{\nu} \epsilon_{\mu}=(2-d)\partial_{\mu}\partial_{\nu} f
+\end{equation} Сравним полученное равенство с результатом применения оператора $\partial^{\rho}$ к
+уравнению \eqref{eq:149}:
+\begin{equation}
+  \label{eq:153}
+  \partial^2 \partial_{\mu}\epsilon_{\nu}+\partial^2 \partial_{\nu}\epsilon_{\mu}=\eta_{\mu\nu}\partial^2
+f
+\end{equation} Из равенств \eqref{eq:152}, \eqref{eq:153} следует, что
+\begin{equation}
+  \label{eq:154} (2-d)\partial_{\mu}\partial_{\nu}f=\eta_{\mu\nu}\partial^2 f.
+\end{equation} Свернув с $\eta^{\mu\nu}$ получим
+\begin{equation}
+  \label{eq:155} (d-1)\partial^2 f =0.
+\end{equation} Сразу можно отметить, что при $d=1$ любое гладкое преобразование будет конформным.
+Рассмотрим случай $d\geq 3$. Функция $f(x)$ должна иметь вид
+\begin{equation}
+  \label{eq:156} f(x)=A+B_{\mu}x^{\mu}.
+\end{equation} Тогда из \eqref{eq:148} получаем для $\epsilon$
+\begin{equation}
+  \label{eq:157} \epsilon_{\mu}=a_{\mu}+b_{\mu\nu}x^{\nu} +c_{\mu\nu\rho}x^{\nu}x^{\rho},\quad
+c_{\mu\nu\rho}=c_{\mu\rho\nu}
+\end{equation} Так как равенства \eqref{eq:147}, \eqref{eq:148}, \eqref{eq:150} должны выполняться
+для любых $x^{\mu}$, то мономы в $\epsilon$ можно рассматривать независимо. На $a_{\mu}$ не
+возникает никаких ограничений. Этот член соответствует трансляциям. Теперь подставляем линейный член
+в \eqref{eq:147}, \eqref{eq:148} и получаем условие
+\begin{equation}
+  \label{eq:158} b_{\mu\nu}+b_{\nu\mu}=\frac{2}{d}b^{\lambda}_{\lambda}\eta_{\mu\nu}
+\end{equation} То есть $b_{\mu\nu}$ можно записать в виде
+\begin{equation}
+  \label{eq:159} b_{\mu\nu}=\alpha \eta_{\mu\nu} +m_{\mu\nu},\quad m_{\mu\nu}=-m_{\nu\mu}
+\end{equation} Первый член соответствует масштабному преобразованию, а второй - повороту. В
+результате подстановки квадратичного члена $\epsilon$ в \eqref{eq:148}, \eqref{eq:150} получаем
+следующее условие на $c_{\mu\nu\rho}$:
+\begin{equation}
+  \label{eq:160} c_{\mu\nu\rho}=\eta_{\mu\rho} h_{\nu} +\eta_{\mu\nu}h_{\rho}-\eta_{\nu\rho}h_{\mu},
+\quad h_{\mu}=\frac{1}{d} c^{\alpha}_{\alpha\mu}
+\end{equation} Ему соответствует преобразование
+\begin{equation}
+  \label{eq:161} x'^{\mu}=x^{\mu}+2 (x^{\nu}h_{\nu})x^{\mu} -h^{\mu} x^{\nu}x_{\nu}
+\end{equation} Такое преобразование называется специальным конформным преобразованием. Это
+преобразование можно естественно интерпретировать, если переписать в виде
+\begin{equation}
+  \label{eq:162} \frac{x'^{\mu}}{x'^2}=\frac{x^{\mu}}{x^2}-h^{\mu}.
+\end{equation} Видно, что специальное конформное преобразование --- это инверсия, трансляция и
+обратная инверсия.
+
+Соответствующие конченые конформные преобразования имеют вид
+\begin{eqnarray}
+  \label{eq:163} x'^{\mu}=x^{\mu}+a^{\mu}&\quad \mbox{--- трансляция}\\ x'^{\mu}=\alpha x^{\mu}
+&\quad \mbox{--- растяжение}\\ x'^{\mu}=m^{\mu}_{\nu} x^{\nu} &\quad \mbox{--- поворот}\\
+x'^{\mu}=\frac{x^{\mu}-h^{\mu}x^2}{1-2h_{\mu}x^{\mu}+h^2 x^2} & \quad \begin{array}{c}\mbox{---
+специальное конформное}\\ \mbox{ преобразование}\end{array}
+\end{eqnarray}
+
+Теперь выпишем вид генераторов конформных преобразований для скалярного поля. Напомним, что при
+произвольном конечном преобразовании скалярное поле преобразуется как
+\begin{equation}
+  \label{eq:164} \Phi'(x')=F(\Phi(x)).
+\end{equation} При соответствующем инфинитезимальном преобразовании
+\begin{equation}
+  \label{eq:165} x'^{\mu}=x^{\mu}+\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}
+\end{equation} скалярное поле преобразуется так:
+\begin{equation}
+  \label{eq:166} \Phi'(x')=\Phi(x)+\omega_a \frac{\delta F}{\delta \omega_a} (x).
+\end{equation} Генератор преобразования определяется следующим равенством:
+\begin{equation}
+  \label{eq:167} \delta_{\omega} \Phi(x)=\Phi'(x)-\Phi(x)\equiv -i\omega_a G_a \Phi(x)
+\end{equation} (здесь нет суммирования по $a$). Из \eqref{eq:166} получаем действие генератора на
+скалярное поле:
+\begin{equation}
+  \label{eq:168} iG_a \Phi=\frac{\delta x^{\mu}}{\delta\omega_a} \partial_{\mu}\Phi-\frac{\delta
+F}{\delta \omega_a}
 \end{equation}
-Теперь подставим $g_{\mu\nu}=\eta_{\mu\nu}$ в уравнение \eqref{eq:147} и продиффернцируем:
-\begin{equation}
-  \label{eq:149}
-  \partial_{\rho} \partial_{\mu}\epsilon_{\nu}+\partial_{\rho}\partial_{\nu}\epsilon_{\mu}=\eta_{\mu\nu}\partial_{\rho} f.
-\end{equation}
-Переставим два раза значки и скомбинируем три уравнения в одно:
-\begin{equation}
-  \label{eq:150}
-  2\partial_{\mu}\partial_{\nu}\epsilon_{\rho}=\eta_{\mu\rho}\partial_{\nu} f+\eta_{\nu\rho}\partial_{\mu}f-\eta_{\mu\nu}\partial_{\rho}f
-\end{equation}
-Свернем это уравнение с $\eta^{\mu\nu}$ и получим
-\begin{equation}
-  \label{eq:151}
-  2\partial^2 \epsilon_{\rho}=(2-d)\partial_{\rho}f
-\end{equation}
-Теперь продифференцируем его по $x^{\nu}$ и поменяем значок $\rho$ на $\mu$:
-\begin{equation}
-  \label{eq:152}
-  2\partial^2 \partial_{\nu} \epsilon_{\mu}=(2-d)\partial_{\mu}\partial_{\nu} f
-\end{equation}
-Сравним полученное равенство с результатом применения оператора $\partial^{\rho}$ к уравнению
-\eqref{eq:149}: 
-\begin{equation}
-  \label{eq:153}
-  \partial^2 \partial_{\mu}\epsilon_{\nu}+\partial^2 \partial_{\nu}\epsilon_{\mu}=\eta_{\mu\nu}\partial^2 f
-\end{equation}
-Из равенств \eqref{eq:152}, \eqref{eq:153} следует, что
-\begin{equation}
-  \label{eq:154}
-  (2-d)\partial_{\mu}\partial_{\nu}f=\eta_{\mu\nu}\partial^2 f.
-\end{equation}
-Свернув с $\eta^{\mu\nu}$ получим
-\begin{equation}
-  \label{eq:155}
-  (d-1)\partial^2 f =0.
-\end{equation}
-Сразу можно отметить, что при $d=1$ любое гладкое преобразование будет конформным. Рассмотрим случай
-$d\geq 3$. Функция $f(x)$ должна иметь вид 
-\begin{equation}
-  \label{eq:156}
-  f(x)=A+B_{\mu}x^{\mu}.
-\end{equation}
-Тогда из \eqref{eq:148} получаем для $\epsilon$
-\begin{equation}
-  \label{eq:157}
-  \epsilon_{\mu}=a_{\mu}+b_{\mu\nu}x^{\nu} +c_{\mu\nu\rho}x^{\nu}x^{\rho},\quad c_{\mu\nu\rho}=c_{\mu\rho\nu}
-\end{equation}
-Так как равенства \eqref{eq:147}, \eqref{eq:148}, \eqref{eq:150} должны выполняться для любых
-$x^{\mu}$, то мономы в $\epsilon$ можно рассматривать независимо. На $a_{\mu}$ не возникает никаких
-ограничений. Этот член соответствует трансляциям. Теперь подставляем линейный член в \eqref{eq:147},
-\eqref{eq:148} и получаем условие 
-\begin{equation}
-  \label{eq:158}
-  b_{\mu\nu}+b_{\nu\mu}=\frac{2}{d}b^{\lambda}_{\lambda}\eta_{\mu\nu}
-\end{equation}
-То есть $b_{\mu\nu}$ можно записать в виде
-\begin{equation}
-  \label{eq:159}
-  b_{\mu\nu}=\alpha \eta_{\mu\nu} +m_{\mu\nu},\quad m_{\mu\nu}=-m_{\nu\mu}
-\end{equation}
-Первый член соответствует масштабному преобразованию, а второй - повороту. 
-В результате подстановки квадратичного члена $\epsilon$ в \eqref{eq:148}, \eqref{eq:150} получаем
-следующее условие на $c_{\mu\nu\rho}$: 
-\begin{equation}
-  \label{eq:160}
-  c_{\mu\nu\rho}=\eta_{\mu\rho} h_{\nu} +\eta_{\mu\nu}h_{\rho}-\eta_{\nu\rho}h_{\mu}, \quad h_{\mu}=\frac{1}{d} c^{\alpha}_{\alpha\mu}
-\end{equation}
-Ему соответствует преобразование
-\begin{equation}
-  \label{eq:161}
-  x'^{\mu}=x^{\mu}+2 (x^{\nu}h_{\nu})x^{\mu} -h^{\mu} x^{\nu}x_{\nu}
-\end{equation}
-Такое преобразование называется специальным конформным преобразованием.
-Это преобразование можно естественно интерпретировать, если переписать в виде
-\begin{equation}
-  \label{eq:162}
-  \frac{x'^{\mu}}{x'^2}=\frac{x^{\mu}}{x^2}-h^{\mu}.
-\end{equation}
-Видно, что специальное конформное преобразование --- это инверсия, трансляция и обратная инверсия.
-
-Соответствующие конченые конформные преобразования имеют вид
-\begin{eqnarray}
-  \label{eq:163}
-  x'^{\mu}=x^{\mu}+a^{\mu}&\quad \mbox{--- трансляция}\\
-  x'^{\mu}=\alpha x^{\mu} &\quad \mbox{--- растяжение}\\
-  x'^{\mu}=m^{\mu}_{\nu} x^{\nu} &\quad \mbox{--- поворот}\\
-  x'^{\mu}=\frac{x^{\mu}-h^{\mu}x^2}{1-2h_{\mu}x^{\mu}+h^2 x^2}  & \quad \begin{array}{c}\mbox{--- специальное конформное}\\ \mbox{ преобразование}\end{array}
-\end{eqnarray}
-
-Теперь выпишем вид генераторов конформных преобразований для скалярного поля. 
-Напомним, что при произвольном конечном преобразовании скалярное поле преобразуется как
-\begin{equation}
-  \label{eq:164}
-  \Phi'(x')=F(\Phi(x)).
-\end{equation}
-При соответствующем инфинитезимальном преобразовании
-\begin{equation}
-  \label{eq:165}
-  x'^{\mu}=x^{\mu}+\omega_a \frac{\delta x^{\mu}}{\delta \omega_a}
-\end{equation}
-скалярное поле преобразуется так:
-\begin{equation}
-  \label{eq:166}
-  \Phi'(x')=\Phi(x)+\omega_a \frac{\delta F}{\delta \omega_a} (x).
-\end{equation}
-Генератор преобразования определяется следующим равенством:
-\begin{equation}
-  \label{eq:167}
-  \delta_{\omega} \Phi(x)=\Phi'(x)-\Phi(x)\equiv -i\omega_a G_a \Phi(x)
-\end{equation}
-(здесь нет суммирования по $a$). Из \eqref{eq:166} получаем действие генератора на скалярное поле:
-\begin{equation}
-  \label{eq:168}
-  iG_a \Phi=\frac{\delta x^{\mu}}{\delta\omega_a} \partial_{\mu}\Phi-\frac{\delta F}{\delta \omega_a}
-\end{equation}
-
-Если мы предположим, что поле $\Phi$ такое поле, которое не меняется при конформных преобразованиях, то есть $F(\Phi)=\Phi$, то мы получим следующий вид для генераторов:
-\begin{eqnarray}
-  \label{eq:169}
-  \mbox{трансляция} & \quad P_{\mu}=-i\partial_{\mu}\\
-  \mbox{поворот} & \quad L_{\mu\nu}=i(x_{\mu}\partial_{\nu}-x_{\nu}\partial{\mu})\\
-  \mbox{растяжение}& \quad D=-ix^{\mu}\partial_{\mu}\\
-  \begin{array}{r}
-  \mbox{специальное конформное}    \\
-  \mbox{преобразование}
-  \end{array}
-  & \quad K_{\mu}=-i(2x_{\mu}x^{\nu}\partial_{\nu}-x^2\partial_{\mu})
-\end{eqnarray}
-Отсюда легко найти коммутационные соотношения алгебры конформных преобразований в случае $d\geq 3$:
-\begin{eqnarray}
-  \label{eq:170}
-  \left[D,P_{\mu}\right]=i P_{\mu}\\
-  \left[D,K_{\mu}\right]=-i K_{\mu}\\
+
+Если мы предположим, что поле $\Phi$ такое поле, которое не меняется при конформных преобразованиях,
+то есть $F(\Phi)=\Phi$, то мы получим следующий вид для генераторов:
+\begin{eqnarray}
+  \label{eq:169} \mbox{трансляция} & \quad P_{\mu}=-i\partial_{\mu}\\ \mbox{поворот} & \quad
+L_{\mu\nu}=i(x_{\mu}\partial_{\nu}-x_{\nu}\partial{\mu})\\ \mbox{растяжение}& \quad
+D=-ix^{\mu}\partial_{\mu}\\
+  \begin{array}{r} \mbox{специальное конформное} \\ \mbox{преобразование}
+  \end{array} & \quad K_{\mu}=-i(2x_{\mu}x^{\nu}\partial_{\nu}-x^2\partial_{\mu})
+\end{eqnarray} Отсюда легко найти коммутационные соотношения алгебры конформных преобразований в
+случае $d\geq 3$:
+\begin{eqnarray}
+  \label{eq:170} \left[D,P_{\mu}\right]=i P_{\mu}\\ \left[D,K_{\mu}\right]=-i K_{\mu}\\
 \left[K_{\mu},P_{\nu}\right]=2i (\eta_{\mu\nu}D - L_{\mu\nu})\\
@@
 \left[L_{\mu\nu},L_{\rho\sigma}\right]=i(\eta_{\nu\rho}L_{\mu\sigma}+\eta_{\mu\sigma}L_{\nu\rho}-\eta_{\mu\rho}L_{\nu\sigma}-\eta_{\nu\sigma}L_{\mu\rho})
-\end{eqnarray}
-Остальные коммутаторы равны нулю.
-Чтобы понять, о какой алгебре идет речь, переопределим генераторы следующим образом. Введем генераторы $J_{ab}, \; a,b=-1,0,\dots,d, J_{ab}=-J_{ba}$:
-\begin{eqnarray}
-  \label{eq:171}
-  J_{\mu\nu}=L_{\mu\nu}\\
-  J_{-1,0}=D\\
-  J_{-1,\mu}=\frac{1}{2}(P_{\mu}-K_{\mu})\\
+\end{eqnarray} Остальные коммутаторы равны нулю. Чтобы понять, о какой алгебре идет речь,
+переопределим генераторы следующим образом. Введем генераторы $J_{ab}, \; a,b=-1,0,\dots,d,
+J_{ab}=-J_{ba}$:
+\begin{eqnarray}
+  \label{eq:171} J_{\mu\nu}=L_{\mu\nu}\\ J_{-1,0}=D\\ J_{-1,\mu}=\frac{1}{2}(P_{\mu}-K_{\mu})\\
 J_{0,\mu}=\frac{1}{2}(P_{\mu}+K_{\mu})
-\end{eqnarray}
-Коммутационные соотношения для таких генераторов запишутся в виде
+\end{eqnarray} Коммутационные соотношения для таких генераторов запишутся в виде
 \begin{equation}
@@
 \left[J_{ab},J_{cd}\right]=i(\eta_{ad}J_{bc}+\eta_{bc}J_{ad}-\eta_{ac}J_{bd}-\eta_{bd}J_{ac}),
-\end{equation}
-где $\eta_{ab}=\mathrm{diag}(-1,1,\dots,1)$. Видно, что мы получили алгебру $so(d+1,1)$. В случае пространства Минковского была бы $so(d,2)$.
+\end{equation} где $\eta_{ab}=\mathrm{diag}(-1,1,\dots,1)$. Видно, что мы получили алгебру
+$so(d+1,1)$. В случае пространства Минковского была бы $so(d,2)$.
 
@@
 \begin{equation}
-  \label{eq:173}
-  \frac{|\vec x_i-\vec x_j|}{|\vec x_k -\vec x_l|}
-\end{equation}
-Но при специальных конформных преобразованиях
-\begin{equation}
-  \label{eq:174}
-  |\vec x'_i-\vec x'_j|=\frac{|\vec x_i-\vec x_j|}{(1-2(\vec h,\vec x_i)+h^2x_i^2)^{1/2} (1-2(\vec h,\vec x_j)+h^2 x_j^2)^{1/2}}
-\end{equation}
-Поэтому не обойтись двумя или тремя точками и простейшие инварианты имеют вид
-\begin{eqnarray}
-  \label{eq:175}
-  \frac{|\vec x_1-\vec x_2||\vec x_3-\vec x_4|}{|\vec x_1-\vec x_3||\vec x_{2}-\vec x_{4}|}\\
-  \frac{|\vec x_1-\vec x_2||\vec x_3-\vec x_4|}{|\vec x_2-\vec x_3||\vec x_{1}-\vec x_{4}|}
-\end{eqnarray}
-Всего $N(N-3)/2$ вариантов для $N$ точек.
+  \label{eq:173} \frac{|\vec x_i-\vec x_j|}{|\vec x_k -\vec x_l|}
+\end{equation} Но при специальных конформных преобразованиях
+\begin{equation}
+  \label{eq:174} |\vec x'_i-\vec x'_j|=\frac{|\vec x_i-\vec x_j|}{(1-2(\vec h,\vec
+x_i)+h^2x_i^2)^{1/2} (1-2(\vec h,\vec x_j)+h^2 x_j^2)^{1/2}}
+\end{equation} Поэтому не обойтись двумя или тремя точками и простейшие инварианты имеют вид
+\begin{eqnarray}
+  \label{eq:175} \frac{|\vec x_1-\vec x_2||\vec x_3-\vec x_4|}{|\vec x_1-\vec x_3||\vec x_{2}-\vec
+x_{4}|}\\ \frac{|\vec x_1-\vec x_2||\vec x_3-\vec x_4|}{|\vec x_2-\vec x_3||\vec x_{1}-\vec x_{4}|}
+\end{eqnarray} Всего $N(N-3)/2$ вариантов для $N$ точек.
 
@@
 \begin{equation}
-  \label{eq:176}
-  L_{\mu\nu}\Phi(0)=S_{\mu\nu}\Phi(0)
-\end{equation}
-Затем мы пользуемся коммутационными соотношениями алгебры Пуанкаре и формулой Хаусдорфа
-\begin{equation}
-  \label{eq:177}
-  e^{-A}B e^{A}=B+[B,A]+\frac{1}{2!}[[B,A],A]+\frac{1}{3!}[[[B,A],A],A]+\dots
-\end{equation}
-чтобы вычислить результат переноса в точку $x$:
+  \label{eq:176} L_{\mu\nu}\Phi(0)=S_{\mu\nu}\Phi(0)
+\end{equation} Затем мы пользуемся коммутационными соотношениями алгебры Пуанкаре и формулой
+Хаусдорфа
+\begin{equation}
+  \label{eq:177} e^{-A}B e^{A}=B+[B,A]+\frac{1}{2!}[[B,A],A]+\frac{1}{3!}[[[B,A],A],A]+\dots
+\end{equation} чтобы вычислить результат переноса в точку $x$:
 \begin{multline}
-  \label{eq:178}
-  L_{\mu\nu}\Phi(x)=e^{ix^{\rho}P_{\rho}}L_{\mu\nu}e^{-i x^{\rho}P_{\rho}}\Phi(x)=\\
+  \label{eq:178} L_{\mu\nu}\Phi(x)=e^{ix^{\rho}P_{\rho}}L_{\mu\nu}e^{-i x^{\rho}P_{\rho}}\Phi(x)=\\
 (S_{\mu\nu}-x_{\mu}P_{\nu}+x_{\nu}P_{\mu})\Phi(x)=\\
 i(x_{\mu}\partial_{\nu}-x_{\nu}\partial_{\mu})\Phi(x)+S_{\mu\nu}\Phi(x)
-\end{multline}
-Для полной конформной группы подгруппа стабильности точки $x=0$ порождается поворотами, растяжениями
-и специальными конформными преобразованиями. Обозначим представление генераторов через $S_{\mu\nu},
-\tilde \Delta, k_{\mu}$ соответственно. Они порождают матричное представление усеченной алгебры с
-коммутационными соотношениями 
-\begin{eqnarray}
-  \label{eq:179}
-  \left[\tilde\Delta,S_{\mu\nu}\right]=0\\
-  \left[\tilde \Delta,k_{\mu}\right]=-i k_{\mu}\\
-  \left[k_{\mu},k_{\nu}\right]=0\\
+\end{multline} Для полной конформной группы подгруппа стабильности точки $x=0$ порождается
+поворотами, растяжениями и специальными конформными преобразованиями. Обозначим представление
+генераторов через $S_{\mu\nu}, \tilde \Delta, k_{\mu}$ соответственно. Они порождают матричное
+представление усеченной алгебры с коммутационными соотношениями
+\begin{eqnarray}
+  \label{eq:179} \left[\tilde\Delta,S_{\mu\nu}\right]=0\\ \left[\tilde \Delta,k_{\mu}\right]=-i
+k_{\mu}\\ \left[k_{\mu},k_{\nu}\right]=0\\
 \left[k_{\rho},S_{\mu\nu}\right]=i(\eta_{\rho\mu}k_{\nu}-\eta_{\rho\nu}k_{\mu})\\
 \left[S_{\mu\nu},S_{\rho\sigma}\right]=i(\eta_{\nu\rho}S_{\mu\sigma}+\eta_{\mu\sigma}S_{\nu\rho}-\eta_{\mu\rho}S_{\nu\sigma}-\eta_{\nu\sigma}S_{\mu\rho})
-\end{eqnarray}
-Трансляция генераторов дилатации и специальных конформных преобразований дается равенствами
-\begin{eqnarray}
-  \label{eq:180}
-  e^{i x^{\rho}P_{\rho}}D e^{-i x^{\rho}P_{\rho}}=D+x^{\nu}P_{\nu}\\
-  e^{i x^{\rho}P_{\rho}}K_{\mu} e^{-i x^{\rho}P_{\rho}}=K_{\mu}+2x_{\mu}D -2 x^{\nu}L_{\mu\nu}+2x_{\mu}(x^{\nu}P_{\nu})-x^{2} P_{\mu}
-\end{eqnarray}
-В результате действие этих генераторов на поле имеет вид
-\begin{eqnarray}
-  \label{eq:181}
-  D\Phi(x)=(-ix^{\nu}\partial_{\nu}+\tilde \Delta)\Phi(x)\\
-  K_{\mu}\Phi(x)=(k_{\mu}+2x_{\mu}\tilde\Delta -x^{\nu}S_{\mu\nu}-2ix_{\mu}x^{\nu}\partial_{\nu}+ix^{2} \partial_{\mu})\Phi(x)
-\end{eqnarray}
-Если требовать, чтобы поле $\Phi(x)$ преобразовывалось по неприводимому представлению группы
-Лоренца, то по лемме Шура любая матрица, коммутирующая со всеми генераторами $S_{\mu\nu}$
+\end{eqnarray} Трансляция генераторов дилатации и специальных конформных преобразований дается
+равенствами
+\begin{eqnarray}
+  \label{eq:180} e^{i x^{\rho}P_{\rho}}D e^{-i x^{\rho}P_{\rho}}=D+x^{\nu}P_{\nu}\\ e^{i
+x^{\rho}P_{\rho}}K_{\mu} e^{-i x^{\rho}P_{\rho}}=K_{\mu}+2x_{\mu}D -2
+x^{\nu}L_{\mu\nu}+2x_{\mu}(x^{\nu}P_{\nu})-x^{2} P_{\mu}
+\end{eqnarray} В результате действие этих генераторов на поле имеет вид
+\begin{eqnarray}
+  \label{eq:181} D\Phi(x)=(-ix^{\nu}\partial_{\nu}+\tilde \Delta)\Phi(x)\\
+K_{\mu}\Phi(x)=(k_{\mu}+2x_{\mu}\tilde\Delta
+-x^{\nu}S_{\mu\nu}-2ix_{\mu}x^{\nu}\partial_{\nu}+ix^{2} \partial_{\mu})\Phi(x)
+\end{eqnarray} Если требовать, чтобы поле $\Phi(x)$ преобразовывалось по неприводимому представлению
+группы Лоренца, то по лемме Шура любая матрица, коммутирующая со всеми генераторами $S_{\mu\nu}$
 пропорциональна единичной.
@@
 
-  {\it Лемма Шура}.
-Оператор, сплетающий неприводимые конечномерные представления группы Ли либо нулевой, либо обратим.
-Эта лемма доказывается в любом учебнике по теории групп Ли, например \cite{golod2001}.
-
-  {\it Следствие}. Оператор $B$, коммутирующий со всеми операторами конечномерного неприводимого представления, кратен единичному.
-
-  {\it Доказательство}: рассмотрим оператор $B-\lambda I$, он тоже коммутирует со всеми операторами представления.
-Возьмем $\lambda=\lambda_1$, являющееся решением уравнения $\det (B-\lambda I)=0$.
-Тогда оператор $B-\lambda I$ вырожден, и по лемме Шура равен нулю.
-Следовательно $B\propto I$.
+  {\it Лемма Шура}. Оператор, сплетающий неприводимые конечномерные представления группы Ли либо
+нулевой, либо обратим. Эта лемма доказывается в любом учебнике по теории групп Ли, например
+\cite{golod2001}.
+
+  {\it Следствие}. Оператор $B$, коммутирующий со всеми операторами конечномерного неприводимого
+представления, кратен единичному.
+
+  {\it Доказательство}: рассмотрим оператор $B-\lambda I$, он тоже коммутирует со всеми операторами
+представления. Возьмем $\lambda=\lambda_1$, являющееся решением уравнения $\det (B-\lambda I)=0$.
+Тогда оператор $B-\lambda I$ вырожден, и по лемме Шура равен нулю. Следовательно $B\propto I$.
 \end{mynote}
@@
 \begin{eqnarray}
-  \label{eq:182}
-  x\to x'\\
-  \varphi(x)\to \varphi'(x')=\left|\frac{\partial x'}{\partial x}\right|^{-\Delta/d}\varphi(x)\\
-  \left|\frac{\partial x'}{\partial x}\right|=\Lambda(x)^{-d/2}    \quad\mbox{--- якобиан преобразования}
-\end{eqnarray}
-Поля, которые так преобразуются, называются {\it квазипримарными}.
-
-Заметим, что  вариация действия при конформных преобразованиях определяется тензором энергии импульса:
-\begin{equation}
-  \label{eq:183}
-  \delta S=\int d^{d}x T^{\mu\nu}\partial_{\mu}\epsilon_{\nu}=\frac{1}{2} \int d^{d}x T^{\mu\nu}(\partial_{\mu}\epsilon_{\nu}-\partial_{\nu}\epsilon_{\mu})=\frac{1}{d}\int d^{d}x T^{\mu}_{\mu}\partial_{\rho}\epsilon^{\rho},
-\end{equation}
-где мы использовали равенства \eqref{eq:147}, \eqref{eq:148}. То есть бесследовость тензора
-энергии-импульса ведет к конформной инвариантности классической теории поля. В классической теории
-поля при наличии трансляционной, вращательной и масштабной инвариантности  тензор энергии-импульса
-часто можно переопределить так, чтобы он был бесследовым. То есть конформная инвариантность следует
-из трансляционной, вращательной и масштабной. В случае двумерной квантовой теории поля общего
-доказательства нет, но конформная инвариантность наблюдается во множестве моделей.
+  \label{eq:182} x\to x'\\ \varphi(x)\to \varphi'(x')=\left|\frac{\partial x'}{\partial
+x}\right|^{-\Delta/d}\varphi(x)\\ \left|\frac{\partial x'}{\partial x}\right|=\Lambda(x)^{-d/2}
+\quad\mbox{--- якобиан преобразования}
+\end{eqnarray} Поля, которые так преобразуются, называются {\it квазипримарными}.
+
+Заметим, что вариация действия при конформных преобразованиях определяется тензором энергии
+импульса:
+\begin{equation}
+  \label{eq:183} \delta S=\int d^{d}x T^{\mu\nu}\partial_{\mu}\epsilon_{\nu}=\frac{1}{2} \int d^{d}x
+T^{\mu\nu}(\partial_{\mu}\epsilon_{\nu}-\partial_{\nu}\epsilon_{\mu})=\frac{1}{d}\int d^{d}x
+T^{\mu}_{\mu}\partial_{\rho}\epsilon^{\rho},
+\end{equation} где мы использовали равенства \eqref{eq:147}, \eqref{eq:148}. То есть бесследовость
+тензора энергии-импульса ведет к конформной инвариантности классической теории поля. В классической
+теории поля при наличии трансляционной, вращательной и масштабной инвариантности тензор
+энергии-импульса часто можно переопределить так, чтобы он был бесследовым. То есть конформная
+инвариантность следует из трансляционной, вращательной и масштабной. В случае двумерной квантовой
+теории поля общего доказательства нет, но конформная инвариантность наблюдается во множестве
+моделей.
 
@@
 \begin{equation}
-  \label{eq:184}
-  \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = \frac{1}{Z} \int \mathcal{D} \Phi \varphi_{1}(x_{1})\varphi_{2}(x_{2}) e^{-S[\Phi]}
+  \label{eq:184} \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = \frac{1}{Z} \int \mathcal{D}
+\Phi \varphi_{1}(x_{1})\varphi_{2}(x_{2}) e^{-S[\Phi]}
+\end{equation} Мы знаем, как преобразуется поле при конформных преобразованиях \eqref{eq:182},
+поэтому коррелятор должен вести себя так:
+\begin{equation}
+  \label{eq:185} \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\rangle = \left|\frac{\partial
+x'_{1}}{\partial x_{1}}\right|^{\frac{\Delta_{1}}{d}}\left| \frac{\partial x'_{2}}{\partial
+x_{2}}\right|^{\frac{\Delta_{1}}{d}} \langle \varphi_{1}(x'_{1})\varphi_{2}(x'_{2})\rangle .
+\end{equation} Из требования инвариантности коррелятора при поворотах и трансляциях получаем, что
+коррелятор может зависеть только от модуля разности $\left|x_{1}-x_{2}\right|$:
+\begin{equation}
+  \label{eq:186} \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = f(\left|x_{1}-x_{2}\right|)
+\end{equation} При масштабных преобразованиях $x\to \lambda x$ из \eqref{eq:185} получаем
+\begin{equation}
+  \label{eq:187} \langle \varphi_{1}(x_{1})
+\varphi_{2}(x_{2})\rangle=\lambda^{\Delta_{1}+\Delta_{2}} \langle \varphi_{1}(\lambda x_{1})
+\varphi_{2}(\lambda x_{2})\rangle .
+\end{equation} То есть мы видим, что $ \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle$ -
+однородная функция, $f(x)=\lambda^{\Delta_{1}+\Delta_{2}} f(\lambda x)$. Отсюда
+\begin{equation}
+  \label{eq:188} \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle =
+\frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}.
+\end{equation} Однако мы ещё не воспользовались инвариантностью коррелятора относительно специальных
+конформных преобразований. Подставим явный вид преобразований $\left|x_{1}-x_{2}\right|$ из
+\eqref{eq:174} и введем обозначение $\gamma_{i}=\left(1-2(h,x_{i})+h^{2}x_{i}^{2}\right)$, тогда
+\begin{equation}
+  \label{eq:189}
+\frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}=\frac{C_{12}(\gamma_{1}\gamma_{2})^{(\Delta_{1}+\Delta_{2})/2}}{\gamma_{1}^{\Delta_{1}}\gamma_{2}^{\Delta_{2}}
+\left|x_{1}-x_{2}\right|^{\Delta_1+\Delta_2}}.
+\end{equation} Это равенство может выполняться только при $\Delta_{1}=\Delta_{2}$. В итоге для
+коррелятора
+\begin{equation}
+  \label{eq:190} \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle =
+   \begin{cases} \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{2\Delta_{1}}} & \Delta_{1}=\Delta_{2}\\ 0 &
+\Delta_{1}\neq \Delta_{2}
+   \end{cases}
+\end{equation} Вспомним, что для парной корреляционной функции мы вводили критический индекс $\eta$:
+$\Gamma(\vec n)\sim |\vec n|^{2-d-\eta}$. То есть для коррелятора квазипримарых полей
+\begin{equation}
+  \label{eq:191} \eta=2\Delta +2 -d.
 \end{equation}
-Мы знаем, как преобразуется поле при конформных преобразованиях \eqref{eq:182}, поэтому коррелятор должен вести себя так:
-\begin{equation}
-  \label{eq:185}
-  \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\rangle = \left|\frac{\partial x'_{1}}{\partial x_{1}}\right|^{\frac{\Delta_{1}}{d}}\left| \frac{\partial x'_{2}}{\partial x_{2}}\right|^{\frac{\Delta_{1}}{d}} \langle \varphi_{1}(x'_{1})\varphi_{2}(x'_{2})\rangle .
-\end{equation}
-Из требования инвариантности коррелятора при поворотах и трансляциях получаем, что коррелятор может зависеть только от модуля разности $\left|x_{1}-x_{2}\right|$:
-\begin{equation}
-  \label{eq:186}
-  \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = f(\left|x_{1}-x_{2}\right|)
-\end{equation}
-При масштабных преобразованиях $x\to \lambda x$ из \eqref{eq:185} получаем
-\begin{equation}
-  \label{eq:187}
-   \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle=\lambda^{\Delta_{1}+\Delta_{2}}  \langle \varphi_{1}(\lambda x_{1}) \varphi_{2}(\lambda x_{2})\rangle .
-\end{equation}
-То есть мы видим, что $ \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle$ - однородная функция, $f(x)=\lambda^{\Delta_{1}+\Delta_{2}} f(\lambda x)$. Отсюда
-\begin{equation}
-  \label{eq:188}
-   \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle = \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}.
-\end{equation}
-Однако мы ещё не воспользовались инвариантностью коррелятора относительно специальных конформных преобразований.
-Подставим явный вид преобразований $\left|x_{1}-x_{2}\right|$ из \eqref{eq:174} и введем обозначение $\gamma_{i}=\left(1-2(h,x_{i})+h^{2}x_{i}^{2}\right)$, тогда
-\begin{equation}
-  \label{eq:189}
-  \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{\Delta_{1}+\Delta_{2}}}=\frac{C_{12}(\gamma_{1}\gamma_{2})^{(\Delta_{1}+\Delta_{2})/2}}{\gamma_{1}^{\Delta_{1}}\gamma_{2}^{\Delta_{2}} \left|x_{1}-x_{2}\right|^{\Delta_1+\Delta_2}}.
-\end{equation}
-Это равенство может выполняться только при $\Delta_{1}=\Delta_{2}$. В итоге для коррелятора
-\begin{equation}
-  \label{eq:190}
-   \langle \varphi_{1}(x_{1}) \varphi_{2}(x_{2})\rangle =
-   \begin{cases}
-     \frac{C_{12}}{\left|x_{1}-x_{2}\right|^{2\Delta_{1}}} & \Delta_{1}=\Delta_{2}\\
-     0 & \Delta_{1}\neq \Delta_{2}
-   \end{cases}
-\end{equation}
-Вспомним, что для парной корреляционной функции мы вводили критический индекс $\eta$: $\Gamma(\vec n)\sim |\vec n|^{2-d-\eta}$. То есть для коррелятора квазипримарых полей
-\begin{equation}
-  \label{eq:191}
-  \eta=2\Delta +2 -d.
-\end{equation}
-
-Аналогичный анализ можно провести для трехточечных функций. Из требований трансляционной и вращательной инвариантности имеем
-\begin{equation}
-  \label{eq:192}
-  \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}},\quad a+b+c=\Delta_{1}+\Delta_{2}+\Delta_{3}.
-\end{equation}
-Здесь введено обозначение $x_{ij}=|x_{i}-x_{j}|$.
-Из требования инвариантности при специальных конформных преобразованиях получаем
-\begin{equation}
-  \label{eq:193}
-  \frac{C^{abc}_{123}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}}=\frac{C^{abc}_{123}}{\gamma_{1}^{\Delta_{1}}\gamma_{2}^{\Delta_{2}}\gamma_{3}^{\Delta_{3}}}\frac{(\gamma_{1}\gamma_{2})^{a/2}(\gamma_{2}\gamma_{3})^{b/2}(\gamma_{1}\gamma_{3})^{c/2}}{x_{12}^{a} x_{23}^{b}x_{13}^{c}}
-\end{equation}
-Это равенство может выполняться только при
+
+Аналогичный анализ можно провести для трехточечных функций. Из требований трансляционной и
+вращательной инвариантности имеем
+\begin{equation}
+  \label{eq:192} \langle
+\varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{a}
+x_{23}^{b}x_{13}^{c}},\quad a+b+c=\Delta_{1}+\Delta_{2}+\Delta_{3}.
+\end{equation} Здесь введено обозначение $x_{ij}=|x_{i}-x_{j}|$. Из требования инвариантности при
+специальных конформных преобразованиях получаем
+\begin{equation}
+  \label{eq:193} \frac{C^{abc}_{123}}{x_{12}^{a}
+x_{23}^{b}x_{13}^{c}}=\frac{C^{abc}_{123}}{\gamma_{1}^{\Delta_{1}}\gamma_{2}^{\Delta_{2}}\gamma_{3}^{\Delta_{3}}}\frac{(\gamma_{1}\gamma_{2})^{a/2}(\gamma_{2}\gamma_{3})^{b/2}(\gamma_{1}\gamma_{3})^{c/2}}{x_{12}^{a}
+x_{23}^{b}x_{13}^{c}}
+\end{equation} Это равенство может выполняться только при
 \begin{equation}
   \label{eq:194}
-  \begin{array}{l}
-    a+c=2\Delta_{1}\\
-    a+b=2\Delta_{2}\\
-    b+c=2\Delta_{3}
+  \begin{array}{l} a+c=2\Delta_{1}\\ a+b=2\Delta_{2}\\ b+c=2\Delta_{3}
   \end{array}
-\end{equation}
-Отсюда сразу получаем, что
+\end{equation} Отсюда сразу получаем, что
 \begin{equation}
   \label{eq:195}
-  \begin{array}{l}
-    a=\Delta_{1}+\Delta_{2}-\Delta_{3}\\
-    b=\Delta_{2}+\Delta_{3}-\Delta_{1}\\
+  \begin{array}{l} a=\Delta_{1}+\Delta_{2}-\Delta_{3}\\ b=\Delta_{2}+\Delta_{3}-\Delta_{1}\\
 c=\Delta_{3}+\Delta_{1}-\Delta_{2}.
   \end{array}
-\end{equation}
-В итоге для трехточечных функций имеем:
-\begin{equation}
-  \label{eq:196}
-   \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{\Delta_{1}+\Delta_{2}-\Delta_{3}} x_{23}^{\Delta_{2}+\Delta_{3}-\Delta_{1}}x_{13}^{\Delta_{3}+\Delta_{1}-\Delta_{2}}}.
-\end{equation}
-Из четырех точек уже можно собрать инварианты \eqref{eq:175}, поэтому из требований конформной
-инвариантности для четырехточечной функции можно написать только 
-\begin{equation}
-  \label{eq:197}
-  \langle \varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\varphi_{4}(x_{4})\rangle=f\left(\frac{x_{12}x_{34}}{x_{13}x_{24}}; \frac{x_{12}x_{34}}{x_{23}x_{14}}\right) \prod_{i<j}^{4}x_{ij}^{\Delta/3-\Delta_{i}-\Delta_{j}},\quad \Delta=\sum_{i=1}^{4}\Delta_{i}.
+\end{equation} В итоге для трехточечных функций имеем:
+\begin{equation}
+  \label{eq:196} \langle
+\varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\rangle=\frac{C^{abc}_{123}}{x_{12}^{\Delta_{1}+\Delta_{2}-\Delta_{3}}
+x_{23}^{\Delta_{2}+\Delta_{3}-\Delta_{1}}x_{13}^{\Delta_{3}+\Delta_{1}-\Delta_{2}}}.
+\end{equation} Из четырех точек уже можно собрать инварианты \eqref{eq:175}, поэтому из требований
+конформной инвариантности для четырехточечной функции можно написать только
+\begin{equation}
+  \label{eq:197} \langle
+\varphi_{1}(x_{1})\varphi_{2}(x_{2})\varphi_{3}(x_{3})\varphi_{4}(x_{4})\rangle=f\left(\frac{x_{12}x_{34}}{x_{13}x_{24}};
+\frac{x_{12}x_{34}}{x_{23}x_{14}}\right)
+\prod_{i<j}^{4}x_{ij}^{\Delta/3-\Delta_{i}-\Delta_{j}},\quad \Delta=\sum_{i=1}^{4}\Delta_{i}.
 \end{equation}
@@
 \begin{equation}
-  \label{eq:198}
-  \Phi'(x)=\Phi(x)-i\omega_{a} G_{a} \Phi(x)
+  \label{eq:198} \Phi'(x)=\Phi(x)-i\omega_{a} G_{a} \Phi(x)
+\end{equation} Вариация действия вычисляется через ток, соответствующий данному преобразовании:
+\begin{equation}
+  \label{eq:199} j^{\mu}_{a}=\left(\frac{\partial \mathcal{L} }{\partial
+(\partial_{\mu}\Phi)} \partial_{\nu}\Phi -\delta^{\mu}_{\nu}\mathcal{L}\right) \frac{\delta
+x^{\nu}}{\delta \omega_{a}} - \frac{\partial \mathcal{L} }{\partial (\partial_{\mu}
+\Phi)}\frac{\delta F}{\delta \omega_{a}}
 \end{equation}
-Вариация действия вычисляется через ток, соответствующий данному преобразовании:
-\begin{equation}
-  \label{eq:199}
-  j^{\mu}_{a}=\left(\frac{\partial \mathcal{L} }{\partial (\partial_{\mu}\Phi)} \partial_{\nu}\Phi -\delta^{\mu}_{\nu}\mathcal{L}\right) \frac{\delta x^{\nu}}{\delta \omega_{a}} - \frac{\partial \mathcal{L} }{\partial (\partial_{\mu} \Phi)}\frac{\delta F}{\delta \omega_{a}}
-\end{equation}
-\begin{equation}
-  \label{eq:200}
-  \delta S =\int d^{d}x \partial_{\mu}j^{\mu}_{a} \omega_{a}
-\end{equation}
-Обозначим через $X$ произведение локальных полей, входящих в коррелятор
-\begin{equation}
-  \label{eq:201}
-  X=\Phi(x_{1})\dots \Phi(x_{n}).
-\end{equation}
-Коррелятор дается функциональным интегралом
-\begin{equation}
-  \label{eq:202}
-  \langle X\rangle = \frac{1}{Z}\int \mathcal{D} \Phi X e^{-S[\Phi]}
-\end{equation}
-Сделаем замену переменных $\Phi\to \Phi'$ в функциональном интеграле. При этом можно предполагать,
-что ``мера интегрирования'' не меняется $\mathcal{D}\Phi'=\mathcal{D}\Phi$
+\begin{equation}
+  \label{eq:200} \delta S =\int d^{d}x \partial_{\mu}j^{\mu}_{a} \omega_{a}
+\end{equation} Обозначим через $X$ произведение локальных полей, входящих в коррелятор
+\begin{equation}
+  \label{eq:201} X=\Phi(x_{1})\dots \Phi(x_{n}).
+\end{equation} Коррелятор дается функциональным интегралом
+\begin{equation}
+  \label{eq:202} \langle X\rangle = \frac{1}{Z}\int \mathcal{D} \Phi X e^{-S[\Phi]}
+\end{equation} Сделаем замену переменных $\Phi\to \Phi'$ в функциональном интеграле. При этом можно
+предполагать, что ``мера интегрирования'' не меняется $\mathcal{D}\Phi'=\mathcal{D}\Phi$
 \cite{difrancesco1997cft}:
 \begin{equation}
-  \label{eq:203}
-  \langle X\rangle = \frac{1}{Z} \int \mathcal{D} \Phi' (X+\delta X)e^{-S[\Phi]-\int d^{d}x \partial_{\mu}j^{\mu}_{a}\omega_{a}(x)}
-\end{equation}
-Раскладываем выражение в ряд до первого порядка по $\omega_{a}(x)$:
-\begin{equation}
-  \label{eq:204}
-  \langle X\rangle=\frac{1}{Z} \left( \int \mathcal{D} \Phi X e^{-S[\Phi]}+\int \mathcal{D} \Phi \delta X e^{-S[\Phi]} -\int \mathcal{D}\Phi \int d^{d}x \partial_{\mu}j^{\mu}_{a}\omega_{a}(x) X e^{-S[\Phi]}\right)
-\end{equation}
-В результате имеем
-\begin{equation}
-  \label{eq:205}
-  \langle \delta X\rangle=\int d^{d}x \partial_{\mu}\langle j^{\mu}_{a}(x) X\rangle \omega_{a}(x)
-\end{equation}
-С другой стороны, мы можем вычислить $\langle\delta X\rangle$ используя \eqref{eq:198}:
+  \label{eq:203} \langle X\rangle = \frac{1}{Z} \int \mathcal{D} \Phi' (X+\delta X)e^{-S[\Phi]-\int
+d^{d}x \partial_{\mu}j^{\mu}_{a}\omega_{a}(x)}
+\end{equation} Раскладываем выражение в ряд до первого порядка по $\omega_{a}(x)$:
+\begin{equation}
+  \label{eq:204} \langle X\rangle=\frac{1}{Z} \left( \int \mathcal{D} \Phi X e^{-S[\Phi]}+\int
+\mathcal{D} \Phi \delta X e^{-S[\Phi]} -\int \mathcal{D}\Phi \int
+d^{d}x \partial_{\mu}j^{\mu}_{a}\omega_{a}(x) X e^{-S[\Phi]}\right)
+\end{equation} В результате имеем
+\begin{equation}
+  \label{eq:205} \langle \delta X\rangle=\int d^{d}x \partial_{\mu}\langle j^{\mu}_{a}(x) X\rangle
+\omega_{a}(x)
+\end{equation} С другой стороны, мы можем вычислить $\langle\delta X\rangle$ используя
+\eqref{eq:198}:
 \begin{multline}
-  \label{eq:206}
-  \langle\delta X\rangle=-i\sum_{i=1}^{n}\langle \Phi(x_{1})\dots G_{a} \Phi(x_{i}) \dots \Phi(x_{n})\rangle \omega_{a}(x_{i})=\\
-  -i \int d^{d}x \omega_{a}(x) \sum_{i=1}^{n} \langle \Phi(x_{1}) \dots G_{a} \Phi(x_{i}) \dots \Phi(x_{n})\rangle \delta (x-x_{i})
-\end{multline}
-Окончательно общий вид тождеств Уорда выглядит следующим образом:
+  \label{eq:206} \langle\delta X\rangle=-i\sum_{i=1}^{n}\langle \Phi(x_{1})\dots G_{a} \Phi(x_{i})
+\dots \Phi(x_{n})\rangle \omega_{a}(x_{i})=\\ -i \int d^{d}x \omega_{a}(x) \sum_{i=1}^{n} \langle
+\Phi(x_{1}) \dots G_{a} \Phi(x_{i}) \dots \Phi(x_{n})\rangle \delta (x-x_{i})
+\end{multline} Окончательно общий вид тождеств Уорда выглядит следующим образом:
 \begin{equation}
   \label{eq:207}
-  \partial_{\mu}\langle j^{\mu}_{a}\Phi(x_{1}) \dots \Phi(x_{n})\rangle=-i\sum_{i=1}^{n}\delta (x-x_{i}) \langle\Phi(x_{1})\dots G_{a} \Phi(x_{i})\dots \Phi(x_{n})\rangle
-\end{equation}
-Рассмотрим некоторые примеры, которые понадобятся нам для конформной теории. Мы используем
-полученный нами явный вид генераторов \eqref{eq:169}.
+  \partial_{\mu}\langle j^{\mu}_{a}\Phi(x_{1}) \dots \Phi(x_{n})\rangle=-i\sum_{i=1}^{n}\delta
+(x-x_{i}) \langle\Phi(x_{1})\dots G_{a} \Phi(x_{i})\dots \Phi(x_{n})\rangle
+\end{equation} Рассмотрим некоторые примеры, которые понадобятся нам для конформной теории. Мы
+используем полученный нами явный вид генераторов \eqref{eq:169}.
 
@@
   \label{eq:208}
-  \partial_{\mu}\langle T^{\mu}_{\nu} X\rangle =-i \sum_{i} \delta(x-x_{i}) \frac{\partial}{\partial x_{i}^{\nu}} \langle X \rangle
-\end{equation}
-Теперь рассмотрим вращения. Если тензор энергии-импульса симметризован (это можно сделать в
-большинстве случаев), то отвечающий вращениям ток дается выражением 
-\begin{equation}
-  \label{eq:209}
-  j^{\mu\nu\rho}=T^{\mu\nu}x^{\rho}-T^{\mu\rho}x^{\nu}.
-\end{equation}
-Тогда тождество Уорда может быть записано в виде
+  \partial_{\mu}\langle T^{\mu}_{\nu} X\rangle =-i \sum_{i} \delta(x-x_{i}) \frac{\partial}{\partial
+x_{i}^{\nu}} \langle X \rangle
+\end{equation} Теперь рассмотрим вращения. Если тензор энергии-импульса симметризован (это можно
+сделать в большинстве случаев), то отвечающий вращениям ток дается выражением
+\begin{equation}
+  \label{eq:209} j^{\mu\nu\rho}=T^{\mu\nu}x^{\rho}-T^{\mu\rho}x^{\nu}.
+\end{equation} Тогда тождество Уорда может быть записано в виде
 \begin{equation}
   \label{eq:210}
-  \partial_{\mu}\langle (T^{\mu\nu}x^{\rho}-T^{\mu\rho}x^{\nu}) X\rangle=\sum_{i }\delta(x-x_{i}) \left( (x^{\nu}_{i}\partial^{\rho}_{i}-x^{\rho}_{i}\partial^{\nu}_{i})\langle X\rangle-i S^{\nu\rho}_{i}\langle X\rangle\right).
-\end{equation}
-Его можно упростить с использованием тождества для трансляций \eqref{eq:208}:
-\begin{equation}
-  \label{eq:211}
-  \langle (T^{\rho\nu}-T^{\nu\rho}) X\rangle=-i \sum_{i} \delta(x-x_{i}) S^{\nu\rho}_{i}\langle X\rangle.
-\end{equation}
-Тензор энергии-импульса в квантовой теории симметричен в корреляционных функциях, если его положение
-не совпадает с положениями других полей в корреляторе.
+  \partial_{\mu}\langle (T^{\mu\nu}x^{\rho}-T^{\mu\rho}x^{\nu}) X\rangle=\sum_{i }\delta(x-x_{i})
+\left( (x^{\nu}_{i}\partial^{\rho}_{i}-x^{\rho}_{i}\partial^{\nu}_{i})\langle X\rangle-i
+S^{\nu\rho}_{i}\langle X\rangle\right).
+\end{equation} Его можно упростить с использованием тождества для трансляций \eqref{eq:208}:
+\begin{equation}
+  \label{eq:211} \langle (T^{\rho\nu}-T^{\nu\rho}) X\rangle=-i \sum_{i} \delta(x-x_{i})
+S^{\nu\rho}_{i}\langle X\rangle.
+\end{equation} Тензор энергии-импульса в квантовой теории симметричен в корреляционных функциях,
+если его положение не совпадает с положениями других полей в корреляторе.
 
@@
   \label{eq:212}
-  \partial_{\mu}\langle T^{\mu}_{\nu} x^{\nu} X\rangle=-\sum_{i} \delta(x-x_{i}) \left( x^{\nu}_{i}\frac{\partial}{\partial x^{\nu}_{i}} \langle X\rangle+\Delta_{i} \langle X\rangle\right) 
+  \partial_{\mu}\langle T^{\mu}_{\nu} x^{\nu} X\rangle=-\sum_{i} \delta(x-x_{i}) \left(
+x^{\nu}_{i}\frac{\partial}{\partial x^{\nu}_{i}} \langle X\rangle+\Delta_{i} \langle X\rangle\right)
+\end{equation} Его тоже можно упростить:
+\begin{equation}
+  \label{eq:213} \langle T^{\mu}_{\mu} X \rangle = -i \sum_{i} \delta(x-x_{i}) \Delta_{i}\langle
+X\rangle
 \end{equation}
-Его тоже можно упростить:
-\begin{equation}
-  \label{eq:213}
-  \langle T^{\mu}_{\mu} X \rangle = -i \sum_{i} \delta(x-x_{i}) \Delta_{i}\langle X\rangle
-\end{equation}
 
 \subsection{О бесследовости тензора энергии-импульса.}
-\label{sec:tracelessness}
-Материал этого раздела не обсуждался на лекции.
+\label{sec:tracelessness} Материал этого раздела не обсуждался на лекции.
 
@@
 \begin{equation}
-  \label{eq:214}
-  S_{\mu\nu\rho\sigma}=\langle T_{\mu\nu}(x) T_{\rho\sigma}(0)\rangle.
-\end{equation}
-Из симметричности тензора энергии-импульса
-\begin{equation}
-  \label{eq:215}
-  S_{\mu\nu\rho\sigma}=S_{\nu\mu\rho\sigma}=S_{\mu\nu\sigma\rho}=S_{\nu\mu\sigma\rho}
-\end{equation}
-Теперь воспользуемся трансляционной инвариантностью:
-\begin{equation}
-  \label{eq:216}
-  S_{\mu\nu\rho\sigma}=\langle T_{\mu\nu}(0)T_{\rho\sigma}(-x)\rangle =\langle T_{\rho\sigma}(-x) T_{\mu\nu}(0)\rangle = S_{\rho\sigma\mu\nu}(-x).
-\end{equation}
-Если в теории сохраняется четность, то $S_{\mu\nu\rho\sigma}(x)=S_{\rho\sigma\mu\nu}(x)$. В силу
-масштабной инвариантности $T_{\mu\nu}$ имеет скейлинговую размерность 2, так как является
-плотностью. Следовательно функция Швингера при масштабных преобразованиях ведет себя так: 
-\begin{equation}
-  \label{eq:217}
-  S_{\mu\nu\rho\sigma}(\lambda x)=\lambda^{-4} S_{\mu\nu\rho\sigma}(x)
-\end{equation}
-Теперь можно записать общий вид функции Швингера:
+  \label{eq:214} S_{\mu\nu\rho\sigma}=\langle T_{\mu\nu}(x) T_{\rho\sigma}(0)\rangle.
+\end{equation} Из симметричности тензора энергии-импульса
+\begin{equation}
+  \label{eq:215} S_{\mu\nu\rho\sigma}=S_{\nu\mu\rho\sigma}=S_{\mu\nu\sigma\rho}=S_{\nu\mu\sigma\rho}
+\end{equation} Теперь воспользуемся трансляционной инвариантностью:
+\begin{equation}
+  \label{eq:216} S_{\mu\nu\rho\sigma}=\langle T_{\mu\nu}(0)T_{\rho\sigma}(-x)\rangle =\langle
+T_{\rho\sigma}(-x) T_{\mu\nu}(0)\rangle = S_{\rho\sigma\mu\nu}(-x).
+\end{equation} Если в теории сохраняется четность, то
+$S_{\mu\nu\rho\sigma}(x)=S_{\rho\sigma\mu\nu}(x)$. В силу масштабной инвариантности $T_{\mu\nu}$
+имеет скейлинговую размерность 2, так как является плотностью. Следовательно функция Швингера при
+масштабных преобразованиях ведет себя так:
+\begin{equation}
+  \label{eq:217} S_{\mu\nu\rho\sigma}(\lambda x)=\lambda^{-4} S_{\mu\nu\rho\sigma}(x)
+\end{equation} Теперь можно записать общий вид функции Швингера:
 \begin{multline}
-  \label{eq:218}
-  S_{\mu\nu\rho\sigma}(x)=(x^{2})^{-4} \left( A_{1}g_{\mu\nu} g_{\rho\sigma} (x^{2})^{2} + A_{2} (g_{\mu\rho}g_{\nu\sigma}\right. +\\
-  \left. g_{\mu\sigma}g_{\nu\rho}) (x^{2})^{2} +A_{3} (g_{\mu\nu} x_{\rho}x_{\sigma} +g_{\rho\sigma}x_{\mu}x_{\nu})x^{2} +A_{4} x_{\mu}x_{\nu}x_{\rho}x_{\sigma}\right)
-\end{multline}
-Кроме того, у нас имеется закон сохранения $\partial^{\mu} T_{\mu\nu}=0$, поэтому
+  \label{eq:218} S_{\mu\nu\rho\sigma}(x)=(x^{2})^{-4} \left( A_{1}g_{\mu\nu} g_{\rho\sigma}
+(x^{2})^{2} + A_{2} (g_{\mu\rho}g_{\nu\sigma}\right. +\\ \left. g_{\mu\sigma}g_{\nu\rho})
+(x^{2})^{2} +A_{3} (g_{\mu\nu} x_{\rho}x_{\sigma} +g_{\rho\sigma}x_{\mu}x_{\nu})x^{2} +A_{4}
+x_{\mu}x_{\nu}x_{\rho}x_{\sigma}\right)
+\end{multline} Кроме того, у нас имеется закон сохранения $\partial^{\mu} T_{\mu\nu}=0$, поэтому
 \begin{multline}
   \label{eq:219}
-  \partial^{\mu}  S_{\mu\nu\rho\sigma}(x)=-(x^{2})^{-4} \left( 3(A_{4}+2 A_{3}) x_{\nu}x_{\rho}x_{\sigma}\right. +\\
-  \left. (4 A_{1}+3 A_{3}) g_{\rho\sigma} x_{\nu} x^{2} +(4 A_{2} - A_{3}) (g_{\rho\nu}x_{\sigma}+g_{\nu\sigma}x_{\rho}) x^{2}\right)=0
-\end{multline}
-Это равенство может выполняться для любого $x$ только если все коэффициенты в скобках равны нулю. То есть
-\begin{eqnarray}
-  \label{eq:220}
-  A_{1}=3 A\\
-  A_{2}=-A\\
-  A_{3}=-4 A\\
-  A_{4}=8 A
-\end{eqnarray}
-Окончательно получаем для функции Швингера
+  \partial^{\mu} S_{\mu\nu\rho\sigma}(x)=-(x^{2})^{-4} \left( 3(A_{4}+2 A_{3})
+x_{\nu}x_{\rho}x_{\sigma}\right. +\\ \left. (4 A_{1}+3 A_{3}) g_{\rho\sigma} x_{\nu} x^{2} +(4 A_{2}
+- A_{3}) (g_{\rho\nu}x_{\sigma}+g_{\nu\sigma}x_{\rho}) x^{2}\right)=0
+\end{multline} Это равенство может выполняться для любого $x$ только если все коэффициенты в скобках
+равны нулю. То есть
+\begin{eqnarray}
+  \label{eq:220} A_{1}=3 A\\ A_{2}=-A\\ A_{3}=-4 A\\ A_{4}=8 A
+\end{eqnarray} Окончательно получаем для функции Швингера
 \begin{multline}
-  \label{eq:221}
-  S_{\mu\nu\rho\sigma}(x)=\frac{A}{(x^{2})^{4}} \left( (3g_{\mu\nu} g_{\rho\sigma}-g_{\mu\rho}g_{\nu\sigma}-g_{\mu\sigma}g_{\nu\rho}) (x^{2})^{2} 
-  \right. \\
-  \left.-4 x^{2} (g_{\mu\nu} x_{\rho}x_{\sigma} +g_{\rho\sigma}x_{\mu}x_{\nu}) +8 x_{\mu}x_{\nu}x_{\rho}x_{\sigma}\right)
-\end{multline}
-Теперь прямой подстановкой можно проверить, что
-\begin{equation}
-  \label{eq:222}
-  S^{\mu\sigma}_{\mu\sigma}=\langle T^{\mu}_{\mu}(x) T^{\sigma}_{\sigma}(0)\rangle=0
-\end{equation}
-при любых значениях $x$. В частности $\langle T^{\mu}_{\mu}(0)\rangle=0$, то есть у оператора следа
-тензора энергии-импульса нулевое матожидание и среднеквадратичное отклонение в основном состоянии.
+  \label{eq:221} S_{\mu\nu\rho\sigma}(x)=\frac{A}{(x^{2})^{4}} \left( (3g_{\mu\nu}
+g_{\rho\sigma}-g_{\mu\rho}g_{\nu\sigma}-g_{\mu\sigma}g_{\nu\rho}) (x^{2})^{2} \right. \\ \left.-4
+x^{2} (g_{\mu\nu} x_{\rho}x_{\sigma} +g_{\rho\sigma}x_{\mu}x_{\nu}) +8
+x_{\mu}x_{\nu}x_{\rho}x_{\sigma}\right)
+\end{multline} Теперь прямой подстановкой можно проверить, что
+\begin{equation}
+  \label{eq:222} S^{\mu\sigma}_{\mu\sigma}=\langle T^{\mu}_{\mu}(x) T^{\sigma}_{\sigma}(0)\rangle=0
+\end{equation} при любых значениях $x$. В частности $\langle T^{\mu}_{\mu}(0)\rangle=0$, то есть у
+оператора следа тензора энергии-импульса нулевое матожидание и среднеквадратичное отклонение в
+основном состоянии.
 
@@
   \label{eq:223}
-  \partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu}=\frac{2}{d} \partial_{\rho}\epsilon^{\rho} \eta_{\mu\nu}.
-\end{equation}
-Теперь у нас $d=2$, $\mu,\nu=0,1$ и $\eta_{\mu\nu}=\delta_{\mu\nu}$, так как мы работаем в
-евклидовой теории. Расписывая компоненты уравнения \eqref{eq:223}, получаем 
+  \partial_{\mu}\epsilon_{\nu}+\partial_{\nu}\epsilon_{\mu}=\frac{2}{d} \partial_{\rho}\epsilon^{\rho}
+\eta_{\mu\nu}.
+\end{equation} Теперь у нас $d=2$, $\mu,\nu=0,1$ и $\eta_{\mu\nu}=\delta_{\mu\nu}$, так как мы
+работаем в евклидовой теории. Расписывая компоненты уравнения \eqref{eq:223}, получаем
 \begin{eqnarray}
   \label{eq:224}
-  \partial_{0} \epsilon_{1}+ \partial_{1}\epsilon_{0}=0& \Rightarrow & \quad\partial_{0} \epsilon_{1}=- \partial_{1}\epsilon_{0}\\
-  2\partial_{0}\epsilon_{0}=\partial_{0}\epsilon_{0}+\partial_{1}\epsilon_{1}& \Rightarrow& \quad \partial_{0} \epsilon_{0}= \partial_{1}\epsilon_{1}
-\end{eqnarray}
-То есть мы получили уравнения Коши-Римана. Введем комплексные координаты
-\begin{eqnarray}
-  \label{eq:225}
-  z=x_{0}+i x_{1}\\
-  \bar z = x_{0}-i x_{1}\\
-  \partial = \partial_{z}=\frac{1}{2}(\partial_{0}-i\partial_{1}) \\
-  \bar \partial=\partial_{\bar z}=\frac{1}{2} (\partial_{0}+i \partial_{1})\\
-  \epsilon=\epsilon_{0}+i \epsilon_{1}\\
-  \bar \epsilon=\epsilon_{0}-i \epsilon_{1}, 
-\end{eqnarray}
-тогда уравнения \eqref{eq:224} можно переписать в виде
-\begin{eqnarray}
-  \label{eq:226}
- \bar \partial \epsilon=0\\
+  \partial_{0} \epsilon_{1}+ \partial_{1}\epsilon_{0}=0& \Rightarrow & \quad\partial_{0}
+\epsilon_{1}=- \partial_{1}\epsilon_{0}\\
+2\partial_{0}\epsilon_{0}=\partial_{0}\epsilon_{0}+\partial_{1}\epsilon_{1}& \Rightarrow&
+\quad \partial_{0} \epsilon_{0}= \partial_{1}\epsilon_{1}
+\end{eqnarray} То есть мы получили уравнения Коши-Римана. Введем комплексные координаты
+\begin{eqnarray}
+  \label{eq:225} z=x_{0}+i x_{1}\\ \bar z = x_{0}-i x_{1}\\
+  \partial = \partial_{z}=\frac{1}{2}(\partial_{0}-i\partial_{1}) \\ \bar \partial=\partial_{\bar
+z}=\frac{1}{2} (\partial_{0}+i \partial_{1})\\ \epsilon=\epsilon_{0}+i \epsilon_{1}\\ \bar
+\epsilon=\epsilon_{0}-i \epsilon_{1},
+\end{eqnarray} тогда уравнения \eqref{eq:224} можно переписать в виде
+\begin{eqnarray}
+  \label{eq:226} \bar \partial \epsilon=0\\
   \partial \bar \epsilon=0.
-\end{eqnarray}
-Решениями будут любые голоморфные и антиголоморфные функции: $\epsilon=\epsilon(z)$ -- голоморфная
-функция и $\bar \epsilon=\bar \epsilon(\bar z)$ -- антиголоморфная. Таким образом мы видим, что
-алгебра локальных конформных преобразований в двумерном случае оказывается бесконечномерной алгеброй
-преобразований 
-\begin{eqnarray}
-  \label{eq:227}
-  z\to f(z)\\
-  \bar z \to \bar f(\bar z)
-\end{eqnarray}
-Введем в алгебре конформых преобразований следующий базис:
-\begin{eqnarray}
-  \label{eq:228}
-  z'=z+\epsilon_{n}(z)\\
-  \bar z'=\bar z+\bar \epsilon_{n}(\bar z)\\
-  \epsilon_{n}(z)= -z^{n+1}\\
-  \bar \epsilon_{n}(\bar z)=-\bar z^{n+1}
-\end{eqnarray}
-Тогда соответствующие генераторы будут равны
-\begin{eqnarray}
-  \label{eq:229}
-  l_{n}=-z^{n+1}\partial\\
-  \bar l_{n}=-\bar z^{n+1}\bar \partial 
-\end{eqnarray}
-Легко видеть, что коммутационные соотношения имеют вид
-\begin{eqnarray}
-  \label{eq:230}
-  \left[l_{m},l_{n}\right]=(m-n) l_{m+n}\\
-  \left[\bar l_{m},\bar l_{n}\right]=(m-n) \bar l_{m+n}\\  
-  \left[l_{n},\bar l_{m}\right]=0
-\end{eqnarray}
-Мы видим, что алгебра распадается в прямую сумму $\mathcal{A} \oplus \bar{\mathcal{A}}$, каждая
-компонента --- это алгебра Витта (Witt algebra). Оказывается удобно продолжить теорию на случай
-независимых $z,\bar z$. Тогда теория распадется на два независимых сектора. Условие же $z^{*}=\bar
-z$ можно наложить в самом конце. 
-Такая процедура соответствует комплексному продолжению всех функций
-от $x_{0},x_{1}$ на $x_{0},x_{1}\in \mathbb{C}^{2}$. Заметим, что вещественная плоскость сохраняется
-подалгеброй, натянутой на генераторы $l_{n}+\bar l_{n}$ и $i(l_{n}-\bar l_{n})$.
+\end{eqnarray} Решениями будут любые голоморфные и антиголоморфные функции: $\epsilon=\epsilon(z)$
+-- голоморфная функция и $\bar \epsilon=\bar \epsilon(\bar z)$ -- антиголоморфная. Таким образом мы
+видим, что алгебра локальных конформных преобразований в двумерном случае оказывается
+бесконечномерной алгеброй преобразований
+\begin{eqnarray}
+  \label{eq:227} z\to f(z)\\ \bar z \to \bar f(\bar z)
+\end{eqnarray} Введем в алгебре конформых преобразований следующий базис:
+\begin{eqnarray}
+  \label{eq:228} z'=z+\epsilon_{n}(z)\\ \bar z'=\bar z+\bar \epsilon_{n}(\bar z)\\ \epsilon_{n}(z)=
+-z^{n+1}\\ \bar \epsilon_{n}(\bar z)=-\bar z^{n+1}
+\end{eqnarray} Тогда соответствующие генераторы будут равны
+\begin{eqnarray}
+  \label{eq:229} l_{n}=-z^{n+1}\partial\\ \bar l_{n}=-\bar z^{n+1}\bar \partial
+\end{eqnarray} Легко видеть, что коммутационные соотношения имеют вид
+\begin{eqnarray}
+  \label{eq:230} \left[l_{m},l_{n}\right]=(m-n) l_{m+n}\\ \left[\bar l_{m},\bar l_{n}\right]=(m-n)
+\bar l_{m+n}\\ \left[l_{n},\bar l_{m}\right]=0
+\end{eqnarray} Мы видим, что алгебра распадается в прямую сумму $\mathcal{A} \oplus
+\bar{\mathcal{A}}$, каждая компонента --- это алгебра Витта (Witt algebra). Оказывается удобно
+продолжить теорию на случай независимых $z,\bar z$. Тогда теория распадется на два независимых
+сектора. Условие же $z^{*}=\bar z$ можно наложить в самом конце. Такая процедура соответствует
+комплексному продолжению всех функций от $x_{0},x_{1}$ на $x_{0},x_{1}\in \mathbb{C}^{2}$. Заметим,
+что вещественная плоскость сохраняется подалгеброй, натянутой на генераторы $l_{n}+\bar l_{n}$ и
+$i(l_{n}-\bar l_{n})$.
 
@@
 \begin{equation}
-  \label{eq:231}
-  l_{n}=-z^{n+1}\partial = - \left(-\frac{1}{w}\right)^{n+1}\left(\frac{\partial z}{\partial w}\right) \partial_{w}=-\left(-\frac{1}{w}\right)^{n-1}\partial_{w}.
-\end{equation}
-Это выражение должно быть хорошо определено при $w\to 0$, то есть $n\leq 1$. Значит глобальные
-конформные преобразования генерируются $l_{\pm 1},l_{0},\bar l_{\pm 1},\bar l_{0}$. Заметим, что
-генераторы $l_{-1},\bar l_{-1}$ порождают трансляции, $i(l_{0}-\bar l_{0})$ -- вращения, $l_{0}+\bar
-l_{0}$ -- масштабные преобразования. 
-Конечные глобальные преобразования имеют вид 
-\begin{equation}
-  \label{eq:232}
-  z\to \frac{az+b}{cz+d}, \quad ad-bc=1,\quad a,b,c,d\in \mathbb{C}
-\end{equation}
-(И аналогично для $\bar z$).
-Если собрать коэффициенты $a,b,c,d$ в матрицу $A=
-\begin{pmatrix}
-  a & b\\
-  c & d
-\end{pmatrix}$, 
-то ясно, что мы имеем дело с группой $SL_{2}(\mathbb{C})/Z_{2}\approx SO(3,1)$. Факторизация по
-$Z_{2}$ соответствует тому, что изменение знака у $a,b,c,d$ разом не меняет преобразования. Эта
-группа называется также группой проективных конформных преобразований.
+  \label{eq:231} l_{n}=-z^{n+1}\partial = - \left(-\frac{1}{w}\right)^{n+1}\left(\frac{\partial
+z}{\partial w}\right) \partial_{w}=-\left(-\frac{1}{w}\right)^{n-1}\partial_{w}.
+\end{equation} Это выражение должно быть хорошо определено при $w\to 0$, то есть $n\leq 1$. Значит
+глобальные конформные преобразования генерируются $l_{\pm 1},l_{0},\bar l_{\pm 1},\bar l_{0}$.
+Заметим, что генераторы $l_{-1},\bar l_{-1}$ порождают трансляции, $i(l_{0}-\bar l_{0})$ --
+вращения, $l_{0}+\bar l_{0}$ -- масштабные преобразования. Конечные глобальные преобразования имеют
+вид
+\begin{equation}
+  \label{eq:232} z\to \frac{az+b}{cz+d}, \quad ad-bc=1,\quad a,b,c,d\in \mathbb{C}
+\end{equation} (И аналогично для $\bar z$). Если собрать коэффициенты $a,b,c,d$ в матрицу $A=
+\begin{pmatrix} a & b\\ c & d
+\end{pmatrix}$, то ясно, что мы имеем дело с группой $SL_{2}(\mathbb{C})/Z_{2}\approx SO(3,1)$.
+Факторизация по $Z_{2}$ соответствует тому, что изменение знака у $a,b,c,d$ разом не меняет
+преобразования. Эта группа называется также группой проективных конформных преобразований.
 
@@
 \begin{eqnarray}
-  \label{eq:233}
-  &\mbox{трансляции} \quad x\to x+a, B=a^{0}+i a^{1},\quad &
-  \begin{pmatrix}
-    1 & B\\
-    0 & 1
-  \end{pmatrix}\\
-  &\mbox{вращения}\quad &
-  \begin{pmatrix}
-    e^{i \Theta/2} & 0\\
-    0 & e^{-i \Theta/2}
-  \end{pmatrix}\\
-  & \mbox{дилатации}\quad &
-  \begin{pmatrix}
-    \lambda & 0\\
-    0 & \lambda^{-1}
-  \end{pmatrix}\\
-  &\begin{array}{r}
-  \mbox{специальные конформные}    \\
-  \mbox{преобразования}
-  \end{array} 
-  \quad
-  C=h_{0}-i h_{1}\quad &
-  \begin{pmatrix}
-    1 & 0\\
-    C & 1
+  \label{eq:233} &\mbox{трансляции} \quad x\to x+a, B=a^{0}+i a^{1},\quad &
+  \begin{pmatrix} 1 & B\\ 0 & 1
+  \end{pmatrix}\\ &\mbox{вращения}\quad &
+  \begin{pmatrix} e^{i \Theta/2} & 0\\ 0 & e^{-i \Theta/2}
+  \end{pmatrix}\\ & \mbox{дилатации}\quad &
+  \begin{pmatrix} \lambda & 0\\ 0 & \lambda^{-1}
+  \end{pmatrix}\\ &\begin{array}{r} \mbox{специальные конформные} \\ \mbox{преобразования}
+  \end{array} \quad C=h_{0}-i h_{1}\quad &
+  \begin{pmatrix} 1 & 0\\ C & 1
   \end{pmatrix}
@@
 
-Квазипримарное поле $\varphi(z,\bar z)$ \eqref{eq:182} со спином $s$ при преобразованиях $z\to w(z), \bar z\to \bar w(\bar z)$ преобразуется так:
-\begin{equation}
-  \label{eq:234}
-  \varphi'(w,\bar w)=\left( \frac{d w}{d z}\right)^{-h}\left( \frac{d \bar w}{d \bar z}\right)^{-\bar h} \varphi(z,\bar z)
-\end{equation}
-Вариация квазипримарного поля при инфинитезимальных преобразованиях $w=z+\epsilon, \bar w =\bar z +\bar \epsilon$ имеет вид
-\begin{equation}
-  \label{eq:235}
-  \delta_{\epsilon,\bar \epsilon} \varphi=\varphi'(z,\bar z)-\varphi(z,\bar z)=-(h\varphi \partial \epsilon +\epsilon \partial \varphi) - (\bar h \varphi\bar \partial \bar \epsilon+\bar \epsilon \bar \partial \varphi)
-\end{equation}
-Если поле ведет себя так не только при глобальных, но и при локальных преобразованиях, то оно называется {\it примарным}.
+Квазипримарное поле $\varphi(z,\bar z)$ \eqref{eq:182} со спином $s$ при преобразованиях $z\to w(z),
+\bar z\to \bar w(\bar z)$ преобразуется так:
+\begin{equation}
+  \label{eq:234} \varphi'(w,\bar w)=\left( \frac{d w}{d z}\right)^{-h}\left( \frac{d \bar w}{d \bar
+z}\right)^{-\bar h} \varphi(z,\bar z)
+\end{equation} Вариация квазипримарного поля при инфинитезимальных преобразованиях $w=z+\epsilon,
+\bar w =\bar z +\bar \epsilon$ имеет вид
+\begin{equation}
+  \label{eq:235} \delta_{\epsilon,\bar \epsilon} \varphi=\varphi'(z,\bar z)-\varphi(z,\bar
+z)=-(h\varphi \partial \epsilon +\epsilon \partial \varphi) - (\bar h \varphi\bar \partial \bar
+\epsilon+\bar \epsilon \bar \partial \varphi)
+\end{equation} Если поле ведет себя так не только при глобальных, но и при локальных
+преобразованиях, то оно называется {\it примарным}.
 
 \subsection{Тождества Уорда в двумерной конформной теории}
-\label{sec:ward-2d-cft}
-В прошлой лекции мы получили общий вид тождеств Уорда для трансляций, поворотов и масштабных преобразований. Выпишем их здесь.
+\label{sec:ward-2d-cft} В прошлой лекции мы получили общий вид тождеств Уорда для трансляций,
+поворотов и масштабных преобразований. Выпишем их здесь.
 \begin{eqnarray}
   \label{eq:236}
-  \partial_{\mu}\langle T^{\mu}_{\nu} X\rangle = -\sum_{i} \delta(x-x_{i}) \partial_{\nu}^{(i)}\langle X\rangle\\
-  \langle (T^{\mu\nu}-T^{\nu\mu}) X\rangle =i\sum_{i}\delta(x-x_{i}) S^{\mu\nu}_{(i)}\langle X\rangle\\
-  \langle T^{\mu}_{\mu} X\rangle=-\sum_{i}\delta(x-x_{i}) \Delta_{(i)} \langle X\rangle
-\end{eqnarray}
-Прежде, чем мы начнем переписывать тождества в комплексных координатах, обсудим следующий
-вспомогательный математический факт: для голоморфных (антиголоморфных) функций можно использовать
-следующее представление для $\delta$-функции: 
-\begin{equation}
-  \label{eq:237}
-  \delta(x)=\frac{1}{\pi} \bar \partial \frac{1}{z} = \frac{1}{\pi}\partial \frac{1}{\bar z}
-\end{equation}
-Заметим, что
-\begin{equation}
-  \label{eq:238}
-  \int_{M} d^{2}x \partial_{\mu}F^{\mu}=\int_{\partial M} d\xi_{\mu} F^{\mu}=\frac{1}{2i} \oint_{\partial M} (-dz F^{\bar z}+d\bar z F^{z})
-\end{equation}
-Для голоморфной функции
-\begin{equation}
-  \label{eq:239}
-  \frac{1}{\pi}\int_{M} d^{2}x \bar \partial\left( \frac{f(z)}{z}\right)=\frac{1}{2\pi i} \int_{\partial M} dz \frac{f(z)}{z}=f(0)=\int_{M} d^{2}x \delta(x) f(z)
-\end{equation}
-Теперь перепишем тождества Уорда \eqref{eq:236} в комплексных координатах:
-\begin{eqnarray}
-  \label{eq:240}
-  2\pi \partial \langle T_{\bar z z } X\rangle +2\pi \bar \partial \langle T_{zz}X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X \rangle\\
-  2\pi \partial \langle T_{\bar z \bar z } X\rangle +2\pi \bar \partial \langle T_{z\bar z}X\rangle = -\sum_{i} \bar \partial \frac{1}{\bar z-\bar w_{i}} \partial_{\bar w_{i}} \langle X \rangle\\
-  2 \langle T_{z\bar z} X\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) \Delta_{i} \langle X\rangle\\
-  -2 \langle T_{z\bar z} X\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) s_{i} \langle X\rangle
-\end{eqnarray}
-Если сложить и вычесть два последних равенства и вспомнить определение $h, \bar h$, то получим
-\begin{eqnarray}
-  \label{eq:241}
-  2\pi \langle T_{\bar z z} X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}} h_{i} \langle X\rangle\\
-  2\pi \langle T_{z \bar z} X\rangle = -\sum_{i}  \partial \frac{1}{\bar z-\bar w_{i}} \bar h_{i} \langle X\rangle
-\end{eqnarray}
-Введем обозачения
-\begin{eqnarray}
-  \label{eq:242}
-  T=-2\pi T_{zz}\\
-  \bar T = -2 \pi T_{\bar z \bar z},
-\end{eqnarray}
-и подставим уравнения \eqref{eq:241} в первые два уравнения \eqref{eq:240}:
-\begin{eqnarray}
-  \label{eq:243}
-  \bar \partial \left( \langle T X\rangle -\sum_{i} \left( \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X\rangle + \frac{h_{i}}{(z-w_{i})^{2}} \langle X\rangle \right) \right) =0\\
-  \partial \left( \langle \bar T X\rangle -\sum_{i} \left( \frac{1}{\bar z-\bar w_{i}} \partial_{\bar w_{i}} \langle X\rangle + \frac{\bar h_{i}}{(\bar z-\bar w_{i})^{2}} \langle X\rangle \right) \right) =0
-\end{eqnarray}
-То есть выражения в скобках (анти)голоморфны. Следовательно
-\begin{equation}
-  \label{eq:244}
-  \langle T X\rangle =\sum_{i} \left( \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X\rangle + \frac{h_{i}}{(z-w_{i})^{2}} \langle X\rangle \right) +\mbox{регулярные члены}
-\end{equation}
-Это пример операторного разложения, которое мы будем обсуждать далее.
+  \partial_{\mu}\langle T^{\mu}_{\nu} X\rangle = -\sum_{i}
+\delta(x-x_{i}) \partial_{\nu}^{(i)}\langle X\rangle\\ \langle (T^{\mu\nu}-T^{\nu\mu}) X\rangle
+=i\sum_{i}\delta(x-x_{i}) S^{\mu\nu}_{(i)}\langle X\rangle\\ \langle T^{\mu}_{\mu}
+X\rangle=-\sum_{i}\delta(x-x_{i}) \Delta_{(i)} \langle X\rangle
+\end{eqnarray} Прежде, чем мы начнем переписывать тождества в комплексных координатах, обсудим
+следующий вспомогательный математический факт: для голоморфных (антиголоморфных) функций можно
+использовать следующее представление для $\delta$-функции:
+\begin{equation}
+  \label{eq:237} \delta(x)=\frac{1}{\pi} \bar \partial \frac{1}{z} = \frac{1}{\pi}\partial
+\frac{1}{\bar z}
+\end{equation} Заметим, что
+\begin{equation}
+  \label{eq:238} \int_{M} d^{2}x \partial_{\mu}F^{\mu}=\int_{\partial M} d\xi_{\mu}
+F^{\mu}=\frac{1}{2i} \oint_{\partial M} (-dz F^{\bar z}+d\bar z F^{z})
+\end{equation} Для голоморфной функции
+\begin{equation}
+  \label{eq:239} \frac{1}{\pi}\int_{M} d^{2}x \bar \partial\left(
+\frac{f(z)}{z}\right)=\frac{1}{2\pi i} \int_{\partial M} dz \frac{f(z)}{z}=f(0)=\int_{M} d^{2}x
+\delta(x) f(z)
+\end{equation} Теперь перепишем тождества Уорда \eqref{eq:236} в комплексных координатах:
+\begin{eqnarray}
+  \label{eq:240} 2\pi \partial \langle T_{\bar z z } X\rangle +2\pi \bar \partial \langle
+T_{zz}X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}} \partial_{w_{i}} \langle X \rangle\\
+2\pi \partial \langle T_{\bar z \bar z } X\rangle +2\pi \bar \partial \langle T_{z\bar z}X\rangle =
+-\sum_{i} \bar \partial \frac{1}{\bar z-\bar w_{i}} \partial_{\bar w_{i}} \langle X \rangle\\ 2
+\langle T_{z\bar z} X\rangle +2 \langle T_{\bar z z }X\rangle =- \sum_{i}\delta(x-x_{i}) \Delta_{i}
+\langle X\rangle\\ -2 \langle T_{z\bar z} X\rangle +2 \langle T_{\bar z z }X\rangle =-
+\sum_{i}\delta(x-x_{i}) s_{i} \langle X\rangle
+\end{eqnarray} Если сложить и вычесть два последних равенства и вспомнить определение $h, \bar h$,
+то получим
+\begin{eqnarray}
+  \label{eq:241} 2\pi \langle T_{\bar z z} X\rangle = -\sum_{i} \bar \partial \frac{1}{z-w_{i}}
+h_{i} \langle X\rangle\\ 2\pi \langle T_{z \bar z} X\rangle = -\sum_{i} \partial \frac{1}{\bar
+z-\bar w_{i}} \bar h_{i} \langle X\rangle
+\end{eqnarray} Введем обозачения
+\begin{eqnarray}
+  \label{eq:242} T=-2\pi T_{zz}\\ \bar T = -2 \pi T_{\bar z \bar z},
+\end{eqnarray} и подставим уравнения \eqref{eq:241} в первые два уравнения \eqref{eq:240}:
+\begin{eqnarray}
+  \label{eq:243} \bar \partial \left( \langle T X\rangle -\sum_{i} \left(
+\frac{1}{z-w_{i}} \partial_{w_{i}} \langle X\rangle + \frac{h_{i}}{(z-w_{i})^{2}} \langle X\rangle
+\right) \right) =0\\
+  \partial \left( \langle \bar T X\rangle -\sum_{i} \left( \frac{1}{\bar z-\bar
+w_{i}} \partial_{\bar w_{i}} \langle X\rangle + \frac{\bar h_{i}}{(\bar z-\bar w_{i})^{2}} \langle
+X\rangle \right) \right) =0
+\end{eqnarray} То есть выражения в скобках (анти)голоморфны. Следовательно
+\begin{equation}
+  \label{eq:244} \langle T X\rangle =\sum_{i} \left( \frac{1}{z-w_{i}} \partial_{w_{i}} \langle
+X\rangle + \frac{h_{i}}{(z-w_{i})^{2}} \langle X\rangle \right) +\mbox{регулярные члены}
+\end{equation} Это пример операторного разложения, которое мы будем обсуждать далее.
 
@@
 \begin{equation}
-  \label{eq:245}
-  \delta_{\epsilon}\langle X\rangle =\int_{M} d^{2}x \partial_{\mu} \langle T^{\mu\nu}(x)\epsilon_{\nu}(x) X \rangle
-\end{equation}
-В комплексных координатах она перепишется так:
-\begin{equation}
-  \label{eq:246}
-  \delta_{\epsilon,\bar \epsilon} \langle X\rangle = \frac{1}{2\pi i} \oint_{C} dz \epsilon(z) \langle T(z) X\rangle +\frac{1}{2\pi i} \oint_{C}  d\bar z \bar \epsilon(\bar z) \langle \bar T(\bar z) X\rangle
-\end{equation}
-Здесь интеграл берется по контуру, внутри которого находятся все аргументы $X$.
+  \label{eq:245} \delta_{\epsilon}\langle X\rangle =\int_{M} d^{2}x \partial_{\mu} \langle
+T^{\mu\nu}(x)\epsilon_{\nu}(x) X \rangle
+\end{equation} В комплексных координатах она перепишется так:
+\begin{equation}
+  \label{eq:246} \delta_{\epsilon,\bar \epsilon} \langle X\rangle = \frac{1}{2\pi i} \oint_{C} dz
+\epsilon(z) \langle T(z) X\rangle +\frac{1}{2\pi i} \oint_{C} d\bar z \bar \epsilon(\bar z) \langle
+\bar T(\bar z) X\rangle
+\end{equation} Здесь интеграл берется по контуру, внутри которого находятся все аргументы $X$.
 Вообще говоря, это выражение для вариации верно для коррелятора любых полей, не только примарных.
 
-Применимость тождеств Уорда основывается на регулярности тензора энергии-импульса.
-Он должен быть везде хорошо определен.
-В частности, $T(0)$ должен быть конечен.
-Кроме того, если вычислить вариацию постоянного поля в точке $z=\infty$:
-\begin{equation}
-  \label{eq:247}
-  \delta_{\epsilon} \langle 1\rangle =-\frac{1}{2\pi i} \oint_{C}dz \epsilon(z) \langle T(z)\rangle =0
-\end{equation}
-где контур обходит точку $\infty$. Для специальных конформных преобразований $\epsilon(z)\sim z^{2}$, поэтому $T(z)\sim z^{-4},\quad z\to \infty$.
+Применимость тождеств Уорда основывается на регулярности тензора энергии-импульса. Он должен быть
+везде хорошо определен. В частности, $T(0)$ должен быть конечен. Кроме того, если вычислить вариацию
+постоянного поля в точке $z=\infty$:
+\begin{equation}
+  \label{eq:247} \delta_{\epsilon} \langle 1\rangle =-\frac{1}{2\pi i} \oint_{C}dz \epsilon(z)
+\langle T(z)\rangle =0
+\end{equation} где контур обходит точку $\infty$. Для специальных конформных преобразований
+$\epsilon(z)\sim z^{2}$, поэтому $T(z)\sim z^{-4},\quad z\to \infty$.
 
@@
 
-В набор локальных полей теории входят не только те поля, которые входят в плотность лагранжиана, но и их производные, произведения и так далее.
-Мы предполагаем, что набор локальных полей $A$ является полным, то есть существует некий базис $\{ A_{j}\}$, по которому можно разложить любое поле. Локальные поля образуют линейное пространство.
+В набор локальных полей теории входят не только те поля, которые входят в плотность лагранжиана, но
+и их производные, произведения и так далее. Мы предполагаем, что набор локальных полей $A$ является
+полным, то есть существует некий базис $\{ A_{j}\}$, по которому можно разложить любое поле.
+Локальные поля образуют линейное пространство.
 
@@
 \begin{equation}
-  \label{eq:248}
-  A_{i}(x)A_{j}(y) =\sum_{k} C^{k}_{ij} (x,y) A_{k}(y),
-\end{equation}
-здесь $C_{ij}^{k}(x,y)$ -- функция. Равенство \eqref{eq:248} надо понимать в смысле корреляционных функций
-\begin{equation}
-  \label{eq:249}
-  \langle A_{i}(x) A_{j}(y) X\rangle = \sum_{k} C^{k}_{ij} (x,y) \langle A_{k}(y) X\rangle.
-\end{equation}
-Тогда набор локальных полей образует алгебру.
+  \label{eq:248} A_{i}(x)A_{j}(y) =\sum_{k} C^{k}_{ij} (x,y) A_{k}(y),
+\end{equation} здесь $C_{ij}^{k}(x,y)$ -- функция. Равенство \eqref{eq:248} надо понимать в смысле
+корреляционных функций
+\begin{equation}
+  \label{eq:249} \langle A_{i}(x) A_{j}(y) X\rangle = \sum_{k} C^{k}_{ij} (x,y) \langle A_{k}(y)
+X\rangle.
+\end{equation} Тогда набор локальных полей образует алгебру.
 
@@
 \begin{equation}
-  \label{eq:250}
-  \langle A_{1}(x_{1}) A_{2}(x_{2}) A_{3}(x_{3}) A_{4}(x_{4}) \rangle =\sum_{k,l} C^{k}_{12} (x_{1}-x_{2}) D_{kl}(x_{2}-x_{4}) C^{l}_{34}(x_{3}-x_{4}) 
-\end{equation}
-Здесь мы воспользовались трансляционной инвариантностью, а также ввели обозначение для пропагатора
-\begin{equation}
-  \label{eq:251}
-  \langle A_{i}(x_{i}) A_{j}(x_{j}) \rangle =D_{ij}(x_{i}-x_{j}).
-\end{equation}
-Однако операторным разложением можно воспользоваться и в другом порядке, тогда для четырехточечной функции получим:
-\begin{equation}
-  \label{eq:252}
-  \langle A_{1}(x_{1}) A_{2}(x_{2}) A_{3}(x_{3}) A_{4}(x_{4}) \rangle =\sum_{k,l} C^{k}_{13} (x_{1}-x_{3}) D_{kl}(x_{3}-x_{4}) C^{l}_{24}(x_{2}-x_{4})   
-\end{equation}
-Приравняв правые части уравнений \eqref{eq:252},\eqref{eq:250} можно получить систему уравнений на коэффициенты $C^{k}_{ij}$.
-Если решить эти уравнения, то в принципе можно вычислять любые корреляторы, если известен набор полей и их конформных размерностей.
-Такой подход называется конформным бутстрапом.
-
-Корреляционные функции имеют особенности при совпадении положений полей. Именно характер этих особенностей важен при описании критического поведения (критические индексы и т.п.).
-Для произведения $T$ и примарного поля $\varphi$ с конформными размерностями $h,\bar h$ имеет место операторное разложение \eqref{eq:244}:
-\begin{eqnarray}
-  \label{eq:253}
-  T(z) \varphi(w,\bar w)\sim \frac{h}{(z-w)^{2}} \varphi(w,\bar w)+\frac{1}{z-w} \partial_{w} \varphi(w,\bar w)\\
-  \bar T(\bar z) \varphi(w,\bar w)\sim \frac{\bar h}{(\bar z-\bar w)^{2}} \varphi(w,\bar w)+\frac{1}{\bar z-\bar w} \partial_{\bar w} \varphi(w,\bar w)  
+  \label{eq:250} \langle A_{1}(x_{1}) A_{2}(x_{2}) A_{3}(x_{3}) A_{4}(x_{4}) \rangle =\sum_{k,l}
+C^{k}_{12} (x_{1}-x_{2}) D_{kl}(x_{2}-x_{4}) C^{l}_{34}(x_{3}-x_{4})
+\end{equation} Здесь мы воспользовались трансляционной инвариантностью, а также ввели обозначение
+для пропагатора
+\begin{equation}
+  \label{eq:251} \langle A_{i}(x_{i}) A_{j}(x_{j}) \rangle =D_{ij}(x_{i}-x_{j}).
+\end{equation} Однако операторным разложением можно воспользоваться и в другом порядке, тогда для
+четырехточечной функции получим:
+\begin{equation}
+  \label{eq:252} \langle A_{1}(x_{1}) A_{2}(x_{2}) A_{3}(x_{3}) A_{4}(x_{4}) \rangle =\sum_{k,l}
+C^{k}_{13} (x_{1}-x_{3}) D_{kl}(x_{3}-x_{4}) C^{l}_{24}(x_{2}-x_{4})
+\end{equation} Приравняв правые части уравнений \eqref{eq:252},\eqref{eq:250} можно получить систему
+уравнений на коэффициенты $C^{k}_{ij}$. Если решить эти уравнения, то в принципе можно вычислять
+любые корреляторы, если известен набор полей и их конформных размерностей. Такой подход называется
+конформным бутстрапом.
+
+Корреляционные функции имеют особенности при совпадении положений полей. Именно характер этих
+особенностей важен при описании критического поведения (критические индексы и т.п.). Для
+произведения $T$ и примарного поля $\varphi$ с конформными размерностями $h,\bar h$ имеет место
+операторное разложение \eqref{eq:244}:
+\begin{eqnarray}
+  \label{eq:253} T(z) \varphi(w,\bar w)\sim \frac{h}{(z-w)^{2}} \varphi(w,\bar
+w)+\frac{1}{z-w} \partial_{w} \varphi(w,\bar w)\\ \bar T(\bar z) \varphi(w,\bar w)\sim \frac{\bar
+h}{(\bar z-\bar w)^{2}} \varphi(w,\bar w)+\frac{1}{\bar z-\bar w} \partial_{\bar w} \varphi(w,\bar
+w)
 \end{eqnarray}
@@
 
-В качестве примера конформной теории рассмотрим свободное бозонное поле $\varphi$. Действие имеет вид
-\begin{equation}
-  \label{eq:254}
-  S=\frac{1}{2} g \int d^{2}x \partial_{\mu}\varphi \partial^{\mu}\varphi,
-\end{equation}
-а пропагатор дается равенством
-\begin{equation}
-  \label{eq:255}
-  \langle\varphi(x) \varphi(y)\rangle =-\frac{1}{4\pi g} \ln (x-y)^{2}+\text{const}
-\end{equation}
-В комплексных координатах пропагатор запишется следующим образом:
-\begin{equation}
-  \label{eq:256}
-  \langle \varphi(z,\bar z) \varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \left( \ln(z-w) + \ln(\bar z -\bar w)\right) +\text{const}
-\end{equation}
-Дифференцируя получаем
-\begin{eqnarray}
-  \label{eq:257}
-  \langle\partial_{z} \varphi(z,\bar z) \partial_{w}\varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \frac{1}{(z-w)^{2}}\\
-  \langle\partial_{\bar z} \varphi(z,\bar z) \partial_{\bar w}\varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \frac{1}{(\bar z-\bar w)^{2}}  
-\end{eqnarray}
-То есть имеет место операторное разложение полей $\partial \varphi$:
+В качестве примера конформной теории рассмотрим свободное бозонное поле $\varphi$. Действие имеет
+вид
+\begin{equation}
+  \label{eq:254} S=\frac{1}{2} g \int d^{2}x \partial_{\mu}\varphi \partial^{\mu}\varphi,
+\end{equation} а пропагатор дается равенством
+\begin{equation}
+  \label{eq:255} \langle\varphi(x) \varphi(y)\rangle =-\frac{1}{4\pi g} \ln (x-y)^{2}+\text{const}
+\end{equation} В комплексных координатах пропагатор запишется следующим образом:
+\begin{equation}
+  \label{eq:256} \langle \varphi(z,\bar z) \varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \left(
+\ln(z-w) + \ln(\bar z -\bar w)\right) +\text{const}
+\end{equation} Дифференцируя получаем
+\begin{eqnarray}
+  \label{eq:257} \langle\partial_{z} \varphi(z,\bar z) \partial_{w}\varphi(w,\bar w)\rangle
+=-\frac{1}{4\pi g} \frac{1}{(z-w)^{2}}\\ \langle\partial_{\bar z} \varphi(z,\bar z) \partial_{\bar
+w}\varphi(w,\bar w)\rangle =-\frac{1}{4\pi g} \frac{1}{(\bar z-\bar w)^{2}}
+\end{eqnarray} То есть имеет место операторное разложение полей $\partial \varphi$:
 \begin{equation}
@@
 \begin{equation}
-  \label{eq:258}
-  T_{\mu\nu}=g \left(\partial_{\mu}\varphi \partial_{\nu} \varphi -\frac{1}{2} \eta_{\mu\nu}\partial_{\rho}\varphi \partial^{\rho} \varphi \right)
-\end{equation}
-После квантования получаем для оператора $T(z)$ следующее выражение:
-\begin{equation}
-  \label{eq:260}
-  T(z) =-2\pi g :\partial \varphi \partial \varphi : =-2\pi g \lim_{w\to z} \left(\partial \varphi(z) \partial \varphi(w) -\langle\partial \varphi(z) \partial \varphi(w)\rangle\right)
-\end{equation}
-Теперь мы можем вычислить операторное разложение тензора энергии-импульса и локального поля $\partial \varphi$:
-\begin{equation}
-  \label{eq:261}
-  T(z)\partial \varphi(w)=-2\pi g :\partial \varphi(z) \partial \varphi(z): \partial \varphi(w) \sim -4\pi g:\partial \varphi(z)  \partial \overbracket{ \varphi(z): \partial \varphi } (w) \sim \frac{\partial \varphi (z)}{(z-w)^{2}}
-\end{equation}
-Для вычисления мы использовали теорему Вика (см. \cite{vasiliev1998}, \cite{difrancesco1997cft}). Раскладывая в ряд по $(z-w)$ получаем окончательно для сингулярной части операторного разложения
-\begin{equation}
-  \label{eq:262}
-  T(z) \partial \varphi(w) \sim \frac{\partial \varphi(w) }{(z-w)^{2}} +\frac{\partial_{w}^{2} \varphi(w)}{z-w}
-\end{equation}
-Теперь мы видим, что поле $\partial \varphi$ -- примарное, с конформной размерностью $h=1$.
+  \label{eq:258} T_{\mu\nu}=g \left(\partial_{\mu}\varphi \partial_{\nu} \varphi -\frac{1}{2}
+\eta_{\mu\nu}\partial_{\rho}\varphi \partial^{\rho} \varphi \right)
+\end{equation} После квантования получаем для оператора $T(z)$ следующее выражение:
+\begin{equation}
+  \label{eq:260} T(z) =-2\pi g :\partial \varphi \partial \varphi : =-2\pi g \lim_{w\to z}
+\left(\partial \varphi(z) \partial \varphi(w) -\langle\partial \varphi(z) \partial
+\varphi(w)\rangle\right)
+\end{equation} Теперь мы можем вычислить операторное разложение тензора энергии-импульса и
+локального поля $\partial \varphi$:
+\begin{equation}
+  \label{eq:261} T(z)\partial \varphi(w)=-2\pi g :\partial \varphi(z) \partial \varphi(z): \partial
+\varphi(w) \sim -4\pi g:\partial \varphi(z) \partial \overbracket{ \varphi(z): \partial \varphi }
+(w) \sim \frac{\partial \varphi (z)}{(z-w)^{2}}
+\end{equation} Для вычисления мы использовали теорему Вика (см. \cite{vasiliev1998},
+\cite{difrancesco1997cft}). Раскладывая в ряд по $(z-w)$ получаем окончательно для сингулярной части
+операторного разложения
+\begin{equation}
+  \label{eq:262} T(z) \partial \varphi(w) \sim \frac{\partial \varphi(w) }{(z-w)^{2}}
++\frac{\partial_{w}^{2} \varphi(w)}{z-w}
+\end{equation} Теперь мы видим, что поле $\partial \varphi$ -- примарное, с конформной размерностью
+$h=1$.
 
@@
 \begin{multline}
-  \label{eq:263}
-  T(z) T(w) =4 \pi^{2}g^{2}:\partial \varphi(z) \partial \varphi(z): :\partial \varphi(w)\partial \varphi(w): \\
-  \sim \frac{1/2}{(z-w)^{4}} -\frac{4\pi g:\partial \varphi(z) \partial \varphi(w):}{(z-w)^{2}} \\
-  \sim \frac{1/2}{(z-w)^{4}}+ \frac{2T(w)}{(z-w)^{2}} +\frac{\partial T(w)}{z-w}
+  \label{eq:263} T(z) T(w) =4 \pi^{2}g^{2}:\partial \varphi(z) \partial \varphi(z): :\partial
+\varphi(w)\partial \varphi(w): \\ \sim \frac{1/2}{(z-w)^{4}} -\frac{4\pi g:\partial
+\varphi(z) \partial \varphi(w):}{(z-w)^{2}} \\ \sim \frac{1/2}{(z-w)^{4}}+ \frac{2T(w)}{(z-w)^{2}}
++\frac{\partial T(w)}{z-w}
 \end{multline}
@@
 
-В силу обсуждения после формулы \eqref{eq:247}, ренормгруппового анализа \ref{c-theorem} и вычисления функции Швингера  \eqref{eq:221} мы имеем следующий общий вид операторного разложения для $T(z)T(w)$:
-\begin{equation}
-  \label{eq:264}
-  T(z)T(w) \sim \frac{c/2}{(z-w)^{4}}+ \frac{2T(w)}{(z-w)^{2}} +\frac{\partial T(w)}{z-w}
-\end{equation}
-Здесь $c$ -- параметр теории, называемый центральным зарядом.
-Он зависит от физической природы теории и не определяется из соображений конформной инвариантности.
-В теории свободного бозона $c=1$, для фермиона $c=1/2$.
-Член $\frac{c/2}{(z-w)^{4}}$ называется аномальным.
+В силу обсуждения после формулы \eqref{eq:247}, ренормгруппового анализа \ref{c-theorem} и
+вычисления функции Швингера \eqref{eq:221} мы имеем следующий общий вид операторного разложения для
+$T(z)T(w)$:
+\begin{equation}
+  \label{eq:264} T(z)T(w) \sim \frac{c/2}{(z-w)^{4}}+ \frac{2T(w)}{(z-w)^{2}} +\frac{\partial
+T(w)}{z-w}
+\end{equation} Здесь $c$ -- параметр теории, называемый центральным зарядом. Он зависит от
+физической природы теории и не определяется из соображений конформной инвариантности. В теории
+свободного бозона $c=1$, для фермиона $c=1/2$. Член $\frac{c/2}{(z-w)^{4}}$ называется аномальным.
 Если этого члена нет, то $T$--квазипримарное поле c $h=2$.
@@
 \begin{equation}
-  \label{eq:265}
-  A=\frac{c}{4\pi^{2}}
-\end{equation}
-Покажем, как преобразуется тензор энергии-импульса при конформных преобразованиях. Используем формулу \eqref{eq:246}:
+  \label{eq:265} A=\frac{c}{4\pi^{2}}
+\end{equation} Покажем, как преобразуется тензор энергии-импульса при конформных преобразованиях.
+Используем формулу \eqref{eq:246}:
 \begin{multline}
-  \label{eq:266}
-  \delta_{\epsilon} T(w) =-\frac{1}{2\pi i} \oint_{C} dz \epsilon(z) T(z) T(w) =-\frac{1}{12} c \partial_{w}^{3}\epsilon(w) -2 T(w) \partial_{w} \epsilon(w) -\epsilon(w) \partial_{w}T(w) 
-\end{multline}
-Соответствующее конечное преобразование $z\to w(z)$ имеет вид
-\begin{eqnarray}
-  \label{eq:267}
-  T\to T'(w) =\left(\frac{dw}{dz}\right)^{-2} \left(T(z) -\frac{c}{12} \left\{ w,z\right\}\right)\\
-  \left\{ w,z\right\}=\frac{\left(\frac{d^{3}w}{dz^{3}}\right) } {\frac{dw}{dz}} -\frac{3}{2}\left(\frac{\frac{d^{2}w}{dz^{2}}}{\frac{dw}{dz}}\right)^{2}
-\end{eqnarray}
-В качестве упражнения предлагаем проверить это выражение обратным переходом к инфинитезимальному преобразованию.
+  \label{eq:266} \delta_{\epsilon} T(w) =-\frac{1}{2\pi i} \oint_{C} dz \epsilon(z) T(z) T(w)
+=-\frac{1}{12} c \partial_{w}^{3}\epsilon(w) -2 T(w) \partial_{w} \epsilon(w)
+-\epsilon(w) \partial_{w}T(w)
+\end{multline} Соответствующее конечное преобразование $z\to w(z)$ имеет вид
+\begin{eqnarray}
+  \label{eq:267} T\to T'(w) =\left(\frac{dw}{dz}\right)^{-2} \left(T(z) -\frac{c}{12} \left\{
+w,z\right\}\right)\\ \left\{ w,z\right\}=\frac{\left(\frac{d^{3}w}{dz^{3}}\right) } {\frac{dw}{dz}}
+-\frac{3}{2}\left(\frac{\frac{d^{2}w}{dz^{2}}}{\frac{dw}{dz}}\right)^{2}
+\end{eqnarray} В качестве упражнения предлагаем проверить это выражение обратным переходом к
+инфинитезимальному преобразованию.
 
@@
 \begin{eqnarray}
-  \label{eq:268}
-  T(z)=\sum_{n\in \mathbb{z}}z^{-n-2}L_{n}\\
-  T(z)=\sum_{n\in \mathbb{z}}\bar z^{-n-2}\bar L_{n}
-\end{eqnarray}
-При масштабном преобразовании $z\to z/\lambda$ оператор $T(z)\to \lambda^{2}T(z/\lambda)$, соответственно компоненты $L_{-n}\to \lambda^{n}L_{-n}$.
-\begin{equation}
-  \label{eq:269}
-  L_{n}=\oint \frac{dz}{2\pi i} z^{n+1} T(z)
-\end{equation}
-Выведем коммутационные соотношения для операторов $L_{n}$:
-\begin{equation}
-  \label{eq:270}
-  [L_{n},L_{m}]=\left( \oint \frac{dz}{2\pi i}\oint \frac{dw}{2\pi i}-\oint \frac{dw}{2\pi i}\oint \frac{dz}{2\pi i}\right) z^{n+1} T(z)w^{m+1}T(w)
-\end{equation}
-Используем операторное разложение \eqref{eq:264}:
+  \label{eq:268} T(z)=\sum_{n\in \mathbb{z}}z^{-n-2}L_{n}\\ T(z)=\sum_{n\in \mathbb{z}}\bar
+z^{-n-2}\bar L_{n}
+\end{eqnarray} При масштабном преобразовании $z\to z/\lambda$ оператор $T(z)\to
+\lambda^{2}T(z/\lambda)$, соответственно компоненты $L_{-n}\to \lambda^{n}L_{-n}$.
+\begin{equation}
+  \label{eq:269} L_{n}=\oint \frac{dz}{2\pi i} z^{n+1} T(z)
+\end{equation} Выведем коммутационные соотношения для операторов $L_{n}$:
+\begin{equation}
+  \label{eq:270} [L_{n},L_{m}]=\left( \oint \frac{dz}{2\pi i}\oint \frac{dw}{2\pi i}-\oint
+\frac{dw}{2\pi i}\oint \frac{dz}{2\pi i}\right) z^{n+1} T(z)w^{m+1}T(w)
+\end{equation} Используем операторное разложение \eqref{eq:264}:
 \begin{multline}
-  \label{eq:271}
-  [L_{n},L_{m}]=\oint \frac{dz}{2\pi i} \oint \frac{dw}{2\pi i} z^{n+1} w^{m+1}\left( \frac{c/2}{(z-w)^{4}} +\frac{2T(w)}{(z-w)^{2}}+\frac{\partial T(w) }{z-w} +\mbox{рег. члены}\right) =\\
-  \oint \frac{dw}{2\pi i} \left(\frac{c}{12} (n+1)n(n-1)w^{n-2}w^{m+1} + 2(n+1)w^{n}w^{m+1}T(w)+w^{n+1}w^{m+1}\partial T(w)\right)
-\end{multline}
-Интегрируем последний член по частям, внеинтегральный член зануляется, а под интегралом остается $(n-m)w^{n+m+1}T(w)$:
-\begin{equation}
-  \label{eq:272}
-    [L_{n},L_{m}]=\oint \frac{dw}{2\pi i} \left(\frac{c}{12} (n+1)n(n-1)w^{m+n-1}+ (n-m)w^{n+m+1}T(w)\right)
-\end{equation}
-Используя определение \eqref{eq:269} и вычисляя вычет подинтегрального выражения при $n=-m$, в итоге получаем коммутационное соотношение
-\begin{equation}
-  \label{eq:273}
-    [L_{n},L_{m}]=(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}
-\end{equation}
-Это коммутационные соотношения алгебры Вирасоро.
-
-Легко показать, что в результате действия оператора $L_{-n}$ на поле $\varphi$  с конформной размерностью $(h,\bar h)$ получается поле с размерностью $(h-n,\bar h)$.
-Все поля в теории разбиваются на конформные семейства, соответствующие примарным полям:
-\begin{equation}
-  \label{eq:274}
-  [\varphi]=\{L_{-n_{1}}L_{-n_{2}}\dots L_{-n_{N}}\bar L_{-m_{1}}\dots \bar L_{-m_{M}}\varphi\}
-\end{equation}
-Вычисление корреляторов вторичных полей сводится к корреляторам примарных. Алгебра локальных полей оказывается прямой суммой конформных семейств
-\begin{equation}
-  \label{eq:275}
-  \mathcal{A} =\bigoplus_{\alpha}[\varphi_{\alpha}]
-\end{equation}
-{\it Минимальными} называются теории с конечным числом примарных полей. Чтобы полностью задать такую теорию нужно определить примарные поля и их конформные размерности.
+  \label{eq:271} [L_{n},L_{m}]=\oint \frac{dz}{2\pi i} \oint \frac{dw}{2\pi i} z^{n+1} w^{m+1}\left(
+\frac{c/2}{(z-w)^{4}} +\frac{2T(w)}{(z-w)^{2}}+\frac{\partial T(w) }{z-w} +\mbox{рег. члены}\right)
+=\\ \oint \frac{dw}{2\pi i} \left(\frac{c}{12} (n+1)n(n-1)w^{n-2}w^{m+1} +
+2(n+1)w^{n}w^{m+1}T(w)+w^{n+1}w^{m+1}\partial T(w)\right)
+\end{multline} Интегрируем последний член по частям, внеинтегральный член зануляется, а под
+интегралом остается $(n-m)w^{n+m+1}T(w)$:
+\begin{equation}
+  \label{eq:272} [L_{n},L_{m}]=\oint \frac{dw}{2\pi i} \left(\frac{c}{12} (n+1)n(n-1)w^{m+n-1}+
+(n-m)w^{n+m+1}T(w)\right)
+\end{equation} Используя определение \eqref{eq:269} и вычисляя вычет подинтегрального выражения при
+$n=-m$, в итоге получаем коммутационное соотношение
+\begin{equation}
+  \label{eq:273} [L_{n},L_{m}]=(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0}
+\end{equation} Это коммутационные соотношения алгебры Вирасоро.
+
+Легко показать, что в результате действия оператора $L_{-n}$ на поле $\varphi$ с конформной
+размерностью $(h,\bar h)$ получается поле с размерностью $(h-n,\bar h)$. Все поля в теории
+разбиваются на конформные семейства, соответствующие примарным полям:
+\begin{equation}
+  \label{eq:274} [\varphi]=\{L_{-n_{1}}L_{-n_{2}}\dots L_{-n_{N}}\bar L_{-m_{1}}\dots \bar
+L_{-m_{M}}\varphi\}
+\end{equation} Вычисление корреляторов вторичных полей сводится к корреляторам примарных. Алгебра
+локальных полей оказывается прямой суммой конформных семейств
+\begin{equation}
+  \label{eq:275} \mathcal{A} =\bigoplus_{\alpha}[\varphi_{\alpha}]
+\end{equation} {\it Минимальными} называются теории с конечным числом примарных полей. Чтобы
+полностью задать такую теорию нужно определить примарные поля и их конформные размерности.
 
@@
 
-Ненулевые операторные разложения между членами конформных семейств определяются разложениями примарных полей. Поэтому можно писать сразу для семейств
-\begin{equation}
-  \label{eq:300}
-  [\varphi_i][\varphi_j]=\sum_k C_{ijk} [\varphi_k]
+Ненулевые операторные разложения между членами конформных семейств определяются разложениями
+примарных полей. Поэтому можно писать сразу для семейств
+\begin{equation}
+  \label{eq:300} [\varphi_i][\varphi_j]=\sum_k C_{ijk} [\varphi_k]
 \end{equation}
 
-При этом в минимальных моделях, где число примарных полей конечно, сумма \eqref{eq:300} оказывается конечной.
-Например, в модели Изинга у нас есть три семейства $[1], [\sigma], [\varepsilon]$. Из наличия симметрий ($\sigma\to - \sigma$ и $\varepsilon\to -\varepsilon$ (дуальность Крамерса-Ванье)) имеем:
-\begin{eqnarray}
-  \label{eq:301}
-  \left[\sigma\right]\left[\sigma\right]=1+\left[\varepsilon\right]\\
+При этом в минимальных моделях, где число примарных полей конечно, сумма \eqref{eq:300} оказывается
+конечной. Например, в модели Изинга у нас есть три семейства $[1], [\sigma], [\varepsilon]$. Из
+наличия симметрий ($\sigma\to - \sigma$ и $\varepsilon\to -\varepsilon$ (дуальность Крамерса-Ванье))
+имеем:
+\begin{eqnarray}
+  \label{eq:301} \left[\sigma\right]\left[\sigma\right]=1+\left[\varepsilon\right]\\
 \left[\sigma\right]\left[\varepsilon\right]=\left[\sigma\right]\\
@@
 
-Кроме того, потребуем, чтобы все состояния в гильбертовом пространстве порождались полями из алгебры локальных полей $\mathcal{A}$ из вакуума (state-field correspondence):
-\begin{equation}
-  \label{eq:307}
-  \forall \left| a\right> \in \mathbb{H}\quad \exists \varphi\in\mathcal{A}:\quad \lim_{z\to 0}\varphi(z)\left|0\right>=\left|a\right>
-\end{equation}
-Для примарного поля $\varphi$ с размерностью $h$ соответствующее состояние будем обозначать через $\left|h\right>$. 
-Из определения \eqref{eq:307} и операторного разложения \eqref{eq:253} легко видеть, что $L_{0}\left|h\right>=h\left|h\right>$.
-Заметим, что $L_{0} L_{n}\left|h\right> = L_{n} L_{0}\left|h\right> + [L_{0},L_{n}]\left|h\right> = (h-n) L_{n}\left|h\right>$. 
-Гамильтониан $H=L_{0}+\bar L_{0}$ должен иметь спектр, ограниченный снизу, поэтому для любого состояния $\left|h\right>$ должно существовать $n>0$, такое что $L_{n}\left|h\right> =0 $.
-Так как все состояния порождаются полями, а все поля получаются из примарных действием понижающих операторов $L_{-n}$, то все состояния должны разбиваться на модули старшего веса алгебры Вирасоро -- так называемые модули Верма.
-В минимальных моделях число таких модулей конечно.
-
-Рассмотрим действие $L_{n}$ на состояние $\left|h\right>$ и получим ограничение на значения конформного веса. Возьмем свертку с сопряженным состоянием $\left<h\right|$, $L^{+}_{m}=L_{-m}$:
-\begin{equation}
-  \label{eq:308}
-  \left<h\right|L^{+}_{-n}L_{n}\left|h\right>=\left<h\right| [L_{n},L_{-n}]\left|h\right> = \left(2nh +\frac{c}{12}(n^{3}-n)\right) \left<h|h\right>
-\end{equation}
-Норма состояний должна быть положительна.
-Устремим $n$ к бесконечности.
-Отсюда сразу получаем ограничение $c\geq 0$.
-Если положить $n=1$, то $h\geq 0$.
-При $h=0$ имеем $L_{1}\left|0\right>=0$, то есть вакуум $sl_{2}$-инвариантен, так как комбинации генераторов $L_{0,\pm_{1}}$ образуют подалгебру $sl_{2}$.
+Кроме того, потребуем, чтобы все состояния в гильбертовом пространстве порождались полями из алгебры
+локальных полей $\mathcal{A}$ из вакуума (state-field correspondence):
+\begin{equation}
+  \label{eq:307} \forall \left| a\right> \in \mathbb{H}\quad \exists \varphi\in\mathcal{A}:\quad
+\lim_{z\to 0}\varphi(z)\left|0\right>=\left|a\right>
+\end{equation} Для примарного поля $\varphi$ с размерностью $h$ соответствующее состояние будем
+обозначать через $\left|h\right>$. Из определения \eqref{eq:307} и операторного разложения
+\eqref{eq:253} легко видеть, что $L_{0}\left|h\right>=h\left|h\right>$. Заметим, что $L_{0}
+L_{n}\left|h\right> = L_{n} L_{0}\left|h\right> + [L_{0},L_{n}]\left|h\right> = (h-n)
+L_{n}\left|h\right>$. Гамильтониан $H=L_{0}+\bar L_{0}$ должен иметь спектр, ограниченный снизу,
+поэтому для любого состояния $\left|h\right>$ должно существовать $n>0$, такое что
+$L_{n}\left|h\right> =0 $. Так как все состояния порождаются полями, а все поля получаются из
+примарных действием понижающих операторов $L_{-n}$, то все состояния должны разбиваться на модули
+старшего веса алгебры Вирасоро -- так называемые модули Верма. В минимальных моделях число таких
+модулей конечно.
+
+Рассмотрим действие $L_{n}$ на состояние $\left|h\right>$ и получим ограничение на значения
+конформного веса. Возьмем свертку с сопряженным состоянием $\left<h\right|$, $L^{+}_{m}=L_{-m}$:
+\begin{equation}
+  \label{eq:308} \left<h\right|L^{+}_{-n}L_{n}\left|h\right>=\left<h\right|
+[L_{n},L_{-n}]\left|h\right> = \left(2nh +\frac{c}{12}(n^{3}-n)\right) \left<h|h\right>
+\end{equation} Норма состояний должна быть положительна. Устремим $n$ к бесконечности. Отсюда сразу
+получаем ограничение $c\geq 0$. Если положить $n=1$, то $h\geq 0$. При $h=0$ имеем
+$L_{1}\left|0\right>=0$, то есть вакуум $sl_{2}$-инвариантен, так как комбинации генераторов
+$L_{0,\pm_{1}}$ образуют подалгебру $sl_{2}$.
 
@@
 \label{tab:verma} \noindent \centering{\
-\begin{tabular}{|l|l|l|l|}
-\hline
-уровень & конформный вес & поле & состояние   \\ \hline
-0 & h & $\varphi$ & $\left|h\right>$  \\
-1 & h+1 & $L_{-1}\varphi$ & $L_{-1}\left|h\right>$  \\
-2 & h+2 & $L_{-2}\varphi$, $L_{-1}^{2}\varphi$ & $L_{-2}\left|h\right>$, $L_{-1}^{2}\left|h\right>$  \\
-3 & h+3 & $L_{-3}\varphi$,$L_{-1}L_{-2}\varphi$, $L_{-1}^{3}\varphi$ & $L_{-3}\left|h\right>$, $L_{-1}L_{-2}\left|h\right>$, $L_{-1}^{3}\left|h\right>$  \\
-\dots & \dots & \dots & \dots  \\
-N & h+N & $P(N)$ полей & $P(N)$ состояний  \\ \hline
-\end{tabular}
-}
+\begin{tabular}{|l|l|l|l|} \hline уровень & конформный вес & поле & состояние \\ \hline 0 & h &
+$\varphi$ & $\left|h\right>$ \\ 1 & h+1 & $L_{-1}\varphi$ & $L_{-1}\left|h\right>$ \\ 2 & h+2 &
+$L_{-2}\varphi$, $L_{-1}^{2}\varphi$ & $L_{-2}\left|h\right>$, $L_{-1}^{2}\left|h\right>$ \\ 3 & h+3
+& $L_{-3}\varphi$,$L_{-1}L_{-2}\varphi$, $L_{-1}^{3}\varphi$ & $L_{-3}\left|h\right>$,
+$L_{-1}L_{-2}\left|h\right>$, $L_{-1}^{3}\left|h\right>$ \\ \dots & \dots & \dots & \dots \\ N & h+N
+& $P(N)$ полей & $P(N)$ состояний \\ \hline
+\end{tabular} }
 \caption{Структура модуля Верма}
@@
 \begin{equation}
-  \label{eq:309}
-  \frac{1}{\prod_{n=1}^{\infty} (1-q^{n})} = \sum_{n=0}^{\infty} P(n) q^{n}
+  \label{eq:309} \frac{1}{\prod_{n=1}^{\infty} (1-q^{n})} = \sum_{n=0}^{\infty} P(n) q^{n}
 \end{equation}
 
-В модуле Верма может оказаться такое состояние $\left|\omega\right>$, что $L_{n}\left|\omega\right>=0, \quad \forall n>0$.
-Действие понижающих операторов на такие состояния порождает инвариантное подпространство, то есть модуль Верма оказывается приводимым.
-Такие состояния обладают нулевой нормой и исключаются.
-Их иногда называют нулевыми состояниями (null-state).
-Как искать такие состояния?
-
-На уровне один  $L_{1}\left(L_{-1}\left|h\right>\right)=0\Longrightarrow h=0$, то есть все состояния, полученные из вакуума понижающим оператором являются нефизическими состояниями с нулевой нормой, как и должно быть.
-
-На уровне два будем искать нулевое состояние в виде $\left|\omega\right>=(L_{-2}+a L_{-1}^{2})\left| h \right> $. Из $L_{1}\left|\omega\right>=0$ получаем
-\begin{equation}
-  \label{eq:310}
-  0=([L_{1},L_{-2}] +a [L_{1},L_{-1}^{2}])\left|h\right> = (3+2a(2h+1))L_{-1}\left|h\right>
+В модуле Верма может оказаться такое состояние $\left|\omega\right>$, что
+$L_{n}\left|\omega\right>=0, \quad \forall n>0$. Действие понижающих операторов на такие состояния
+порождает инвариантное подпространство, то есть модуль Верма оказывается приводимым. Такие состояния
+обладают нулевой нормой и исключаются. Их иногда называют нулевыми состояниями (null-state). Как
+искать такие состояния?
+
+На уровне один $L_{1}\left(L_{-1}\left|h\right>\right)=0\Longrightarrow h=0$, то есть все состояния,
+полученные из вакуума понижающим оператором являются нефизическими состояниями с нулевой нормой, как
+и должно быть.
+
+На уровне два будем искать нулевое состояние в виде $\left|\omega\right>=(L_{-2}+a L_{-1}^{2})\left|
+h \right> $. Из $L_{1}\left|\omega\right>=0$ получаем
+\begin{equation}
+  \label{eq:310} 0=([L_{1},L_{-2}] +a [L_{1},L_{-1}^{2}])\left|h\right> =
+(3+2a(2h+1))L_{-1}\left|h\right>
+\end{equation} То есть
+\begin{equation}
+  \label{eq:311} a=-\frac{3}{2(2h+1)}
+\end{equation} Аналогично, действуя $L_{2}$ получаем условие
+\begin{equation}
+  \label{eq:312} c=2h\frac{5-8h}{2h+1}
+\end{equation} Так как состояние $(L_{-2}-\frac{3}{2(2h+1)} L_{-1}^{2})\left|h\right>$ имеет нулевую
+норму, для корреляторов получаем $\left<(L_{-2}+aL_{1}^{2})\phi_{1}(w_{1}) \dots \phi_{n}(w_{n})
+\right>=0$. Используем тождества Уорда \eqref{eq:243}, \eqref{eq:244} и определение $L_{n}$
+\eqref{eq:269} и перепишем это условие в виде дифференциального уравнения:
+\begin{equation}
+  \label{eq:313} \left[ a \frac{\partial^{2}}{\partial w_{1}^{2}} +\sum_{j\neq 1}
+\left(\frac{h_{j}}{(w_{1}-w_{j})^{2}}+\frac{1}{w_{1}-w_{j}} \frac{\partial}{\partial
+w_{j}}\right)\right] \left< \phi_{1}(w_{1}) \dots \phi_{n}(w_{n}) \right> =0
+\end{equation} То есть мы получили дифференциальные уравнения на корреляционные функции.
+
+Рассмотрим в качестве примера модель Изинга. Ей соответствует конформная теория поля с тремя
+примарными полями \eqref{eq:276} и центральным зарядом $1/2$. Заметим, что для поля спина $\Phi_{3}$
+с конформной размерностью $h=1/16$ выполнено условие \eqref{eq:312}. То есть мы можем записать
+уравнение \eqref{eq:313} для корреляционных функций спинов. Рассмотрим для примера четырехточечную
+функцию
+\begin{equation}
+  \label{eq:314} G^{(4)} =\langle \sigma(z_1,\bar z_1)\dots \sigma(z_4,\bar z_4)\rangle
+\end{equation} Из лекции \ref{sec:lecture-9} и формулы \eqref{eq:197} можно переписать $G^{(4)}$ в
+виде
+\begin{equation}
+  \label{eq:315} G^{(4)} = \mathrm{const}\cdot \left(\frac{z_{13}z_{24}}{z_{12}
+z_{23}z_{34}z_{41}}\right)^{\frac{1}{8}} \overline{ \left(\frac{z_{13}z_{24}}{z_{12}
+z_{23}z_{34}z_{41}}\right)}^{\frac{1}{8}}F(x,\bar x),
+\end{equation} где $x=\frac{z_{12}z_{34}}{z_{13}z_{24}}, z_{ij}=\left| z_{i}-z_{j}\right|$. Тогда
+дифференциальное уравнение на $F$ примет вид
+\begin{equation}
+  \label{eq:316} \left( x(1-x) \frac{\partial^{2}}{\partial x^{2}}
++(\frac{1}{2}-x)\frac{\partial}{\partial x}+\frac{1}{16}\right) F(x,\bar x)=0
+\end{equation} и аналогично для $\bar x$. Решение этого уравнения дается гипергеометрической
+функцией. В данном случае она упрощается до $f_{1,2}(x)=(1\pm \sqrt{1-x})^{\frac{1}{2}}$. Тогда
+четырехточечную функцию можно записать в виде комбинации решений
+\begin{equation}
+  \label{eq:317} G^{(4)} = \left|\frac{z_{13}z_{24}}{z_{12}
+z_{23}z_{34}z_{41}}\right|^{\frac{1}{4}}\sum_{i,j=1}^{2}a_{ij}f_{i}(x)f_{j}(\bar x)
+\end{equation} Возвращаясь к физической системе мы должны положить $\bar x= x^{*}$, тогда из
+однозначности четырехточечной функции комбинация может быть только
+$a(|f_{1}(x)|^{2}+|f_{2}(x)|^{2})$. Из сравнения с операторным разложением для $\sigma(z)\sigma(w)$
+нетрудно получить, что $a=1/2$.
+
+В итоге для четырехточечной функции получается следующее выражение:
+\begin{equation}
+  \label{eq:302} G^{(4)} =\langle \sigma(z_1,\bar z_1)\dots \sigma(z_4,\bar z_4)\rangle =
+\frac{1}{2} \left|\frac{z_{13}z_{24}}{z_{12}
+z_{23}z_{34}z_{41}}\right|^{\frac{1}{4}}\left(\left|1+\sqrt{1-x}\right| +
+\left|1-\sqrt{1-x}\right|\right)
 \end{equation}
-То есть
-\begin{equation}
-  \label{eq:311}
-  a=-\frac{3}{2(2h+1)}
-\end{equation}
-Аналогично, действуя $L_{2}$ получаем условие
-\begin{equation}
-  \label{eq:312}
-  c=2h\frac{5-8h}{2h+1}
-\end{equation}
-Так как состояние $(L_{-2}-\frac{3}{2(2h+1)} L_{-1}^{2})\left|h\right>$ имеет нулевую норму, для корреляторов получаем $\left<(L_{-2}+aL_{1}^{2})\phi_{1}(w_{1}) \dots \phi_{n}(w_{n}) \right>=0$. 
-Используем тождества Уорда \eqref{eq:243}, \eqref{eq:244} и определение $L_{n}$ \eqref{eq:269} и перепишем это условие в виде дифференциального уравнения:
-\begin{equation}
-  \label{eq:313}
-\left[  a \frac{\partial^{2}}{\partial w_{1}^{2}} +\sum_{j\neq 1} \left(\frac{h_{j}}{(w_{1}-w_{j})^{2}}+\frac{1}{w_{1}-w_{j}} \frac{\partial}{\partial w_{j}}\right)\right] \left< \phi_{1}(w_{1}) \dots \phi_{n}(w_{n}) \right> =0
-\end{equation}
-То есть мы получили дифференциальные уравнения на корреляционные функции.
-
-Рассмотрим в качестве примера модель Изинга.
-Ей соответствует конформная теория поля с тремя примарными полями \eqref{eq:276} и центральным зарядом $1/2$.
-Заметим, что для поля спина $\Phi_{3}$ с конформной размерностью $h=1/16$ выполнено условие \eqref{eq:312}.
-То есть мы можем записать уравнение \eqref{eq:313} для корреляционных функций спинов.
-Рассмотрим для примера четырехточечную функцию
-\begin{equation}
-  \label{eq:314}
-   G^{(4)} =\langle \sigma(z_1,\bar z_1)\dots \sigma(z_4,\bar z_4)\rangle
-\end{equation}
-Из лекции \ref{sec:lecture-9} и формулы \eqref{eq:197} можно переписать $G^{(4)}$ в виде
-\begin{equation}
-  \label{eq:315}
-   G^{(4)} = \mathrm{const}\cdot \left(\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right)^{\frac{1}{8}} \overline{ \left(\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right)}^{\frac{1}{8}}F(x,\bar x),
-\end{equation}
-где $x=\frac{z_{12}z_{34}}{z_{13}z_{24}}, z_{ij}=\left| z_{i}-z_{j}\right|$. Тогда дифференциальное уравнение на $F$ примет вид
-\begin{equation}
-  \label{eq:316}
-  \left( x(1-x) \frac{\partial^{2}}{\partial x^{2}} +(\frac{1}{2}-x)\frac{\partial}{\partial x}+\frac{1}{16}\right) F(x,\bar x)=0
-\end{equation}
-и аналогично для $\bar x$.
-Решение этого уравнения дается гипергеометрической функцией.
-В данном случае она упрощается до $f_{1,2}(x)=(1\pm \sqrt{1-x})^{\frac{1}{2}}$.
-Тогда  четырехточечную функцию можно записать в виде комбинации решений
-\begin{equation}
-  \label{eq:317}
-  G^{(4)} =  \left|\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right|^{\frac{1}{4}}\sum_{i,j=1}^{2}a_{ij}f_{i}(x)f_{j}(\bar x)
-\end{equation}
-Возвращаясь к физической системе мы должны положить $\bar x= x^{*}$, тогда из однозначности четырехточечной функции комбинация может быть только $a(|f_{1}(x)|^{2}+|f_{2}(x)|^{2})$.
-Из сравнения с операторным разложением для $\sigma(z)\sigma(w)$ нетрудно получить, что $a=1/2$.
-
-В итоге для четырехточечной функции получается следующее выражение:
-\begin{equation}
-  \label{eq:302}
-  G^{(4)} =\langle \sigma(z_1,\bar z_1)\dots \sigma(z_4,\bar z_4)\rangle = \frac{1}{2} \left|\frac{z_{13}z_{24}}{z_{12} z_{23}z_{34}z_{41}}\right|^{\frac{1}{4}}\left(\left|1+\sqrt{1-x}\right| + \left|1-\sqrt{1-x}\right|\right)
-\end{equation}
-
-Таким образом конформная теория поля позволяет не только находить критические индексы, но и получать явные выражения для корреляционных функций статистических моделей в критической точке.
+
+Таким образом конформная теория поля позволяет не только находить критические индексы, но и получать
+явные выражения для корреляционных функций статистических моделей в критической точке.
 
@@
 \begin{equation}
-  \label{eq:139}
-  \alpha_{r,s}=\frac{1}{2}(1-r)\alpha_{+}+\frac{1}{2}(1-s)\alpha_{-},\quad h_{r,s}=\frac{(r\kappa-4s)^{2}-(\kappa-4)^{2}}{16\kappa}
-\end{equation}
-So holomorphic and full primary fields are denoted by $\psi_{r,s}(z)\sim V_{\alpha_{r,s}}(z)$ and
-$\psi_{r,s}(z,\bar z)\sim V^{(\alpha_{r,s})}(z,\bar z)$
+  \label{eq:139} \alpha_{r,s}=\frac{1}{2}(1-r)\alpha_{+}+\frac{1}{2}(1-s)\alpha_{-},\quad
+h_{r,s}=\frac{(r\kappa-4s)^{2}-(\kappa-4)^{2}}{16\kappa}
+\end{equation} So holomorphic and full primary fields are denoted by $\psi_{r,s}(z)\sim
+V_{\alpha_{r,s}}(z)$ and $\psi_{r,s}(z,\bar z)\sim V^{(\alpha_{r,s})}(z,\bar z)$
 
@@
 
-\bibliography{integrability}{}
-\bibliographystyle{utphys}
+\bibliography{integrability}{} \bibliographystyle{utphys}
 

### 2018-11-25 AffineLieAlgebras/MQFT2018/paper.tex
MQFT2018 paper completed

@@
 
+\newcommand{\Li}{\mathrm{Li}}
+\newcommand{\dx}{\mathrm{dx}~}
+\newcommand{\dy}{\mathrm{dy}~}
+\newcommand{\dz}{\mathrm{dz}}
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
   \label{eq:14}
-  Z=\sum_{conf} e^{-\frac{E[conf]}{T}}=\sum_{conf}q^{\mathrm{Vol}[conf]}, 
+  Z=\sum_{conf} e^{-\frac{E[conf]}{T}}=\sum_{conf}q^{\mathrm{Volume}[conf]}, 
 \end{equation*}
@@
 
-The scaling limit is achieved on the infinite lattice as $T\to\infty$. To study the scaling behavior
-using Monte-Carlo simulations on the finite lattices we will consider temperatures proportional to
-the lattice size and, then, extrapolate them to infinity.
-
+%% The scaling limit is achieved on the infinite lattice as $T\to\infty$. To study the scaling behavior
+%% using Monte-Carlo simulations on the finite lattices one can consider temperatures proportional to
+%% the lattice size and, then, extrapolate them to infinity.
+%%   
 %  \frametitle{Kasteleyn matrix and Dirac operator}
@@
   \label{eq:21}
-  \int_{0}^{a} \int_{0}^{b}\int_{0}^{c}G(x,y,z) dx\; dy\;
-  dz\approx\sum_{i=1}^{M}\sum_{j=1}^{N}\sum_{k=1}^{K}\left\{\varepsilon^{3}G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)-\right.\\
+  \int_{0}^{a} \int_{0}^{b}\int_{0}^{c}G(x,y,z) \dx\; \dy\;
+  \dz\approx\sum_{i=1}^{M}\sum_{j=1}^{N}\sum_{k=1}^{K}\left\{\varepsilon^{3}G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)-\right.\\
   \left.-\left[\frac{\varepsilon^{4}}{2}\left((\partial_{x}+\partial_{y}+\partial_{z})G\right)(i\varepsilon,j\varepsilon,k\varepsilon)\right]+\right.\\
@@
 \label{eq:8}
-  \sum_{j=1}^{N}\sum_{k=1}^{K}\varepsilon^{2}G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)\approx \int_{0}^{b}\int_{0}^{c}G(i\varepsilon,y,z) dy\; dz+\mathcal{O}(\varepsilon^{3}))
+  \sum_{j=1}^{N}\sum_{k=1}^{K}\varepsilon^{2}G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)\approx \int_{0}^{b}\int_{0}^{c}G(i\varepsilon,y,z) \dy\; \dz+\mathcal{O}(\varepsilon^{3}))
 \end{equation}
@@
 \label{eq:23}
-  \frac{f}{T}=-\frac{1}{ab+bc+ca}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{dx dy dz}{e^{x+y+z}-1}+\right.\\
+ f=-\frac{1}{2(ab+bc+ca)}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1}+\right.\\
   \left.+\sum_{i=1}^{M}\sum_{j=1}^{N}\sum_{k=1}^{K}\frac{\varepsilon^{5}}{12}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3
@@
 There is no singularity in the sum, but
-$\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{dx dy dz}{(\exp(x+y+z)-1)^{3}}$ diverges
+$\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{(\exp(x+y+z)-1)^{3}}$ diverges
 logarithmically. So we can not just apply the integral representation~\eqref{eq:21} directly.
@@
     \frac{\varepsilon^{3}}{12}\sum_{i=1}^{M} \int_{0}^{b}\int_{0}^{c}
-      \left(\frac{e^{2(i\varepsilon+y+z)}+e^{i\varepsilon+y+z}}{\left(e^{i\varepsilon+y+z}-1\right)^{3}}\right) dy dz+\mathcal{O}(\varepsilon^{3})
+      \left(\frac{e^{2(i\varepsilon+y+z)}+e^{i\varepsilon+y+z}}{\left(e^{i\varepsilon+y+z}-1\right)^{3}}\right) \dy \dz+\mathcal{O}(\varepsilon^{3})
 \end{equation}
@@
     \label{eq:24}
-    \sum_{i=1}^{M}\frac{1}{i}=\frac{1}{M}\sum_{i=1}^{M}\frac{1}{i/M}=\int_{\frac{1}{M}}^{1}\frac{dx}{x}+\gamma+O(\varepsilon)=-\ln\varepsilon+\ln a+\gamma+O(\varepsilon)
+    \sum_{i=1}^{M}\frac{1}{i}=\frac{1}{M}\sum_{i=1}^{M}\frac{1}{i/M}=\int_{\frac{1}{M}}^{1}\frac{\dx}{x}+\gamma+O(\varepsilon)=-\ln\varepsilon+\ln a+\gamma+O(\varepsilon)
   \end{equation}
@@
    \frac{\varepsilon^{2}}{12}\left[\int_{0}^{a}\left(     \frac{1}{e^{b+c+x}-1}+
-      \frac{1}{1-e^{b+x}}+\frac{1}{1-e^{c+x}}+\frac{1}{e^{x}-1}-\frac{1}{x}\right)dx-\ln\varepsilon+\ln a+\gamma\right]+\mathcal{O}(\varepsilon^{3})    
+      \frac{1}{1-e^{b+x}}+\frac{1}{1-e^{c+x}}+\frac{1}{e^{x}-1}-\frac{1}{x}\right)\dx-\ln\varepsilon+\ln a+\gamma\right]+\mathcal{O}(\varepsilon^{3})    
 \end{multline}
@@
      \frac{\varepsilon^{2}}{12}\left[\int_{0}^{a}\left(     \frac{1}{e^{b+c+x}-1}+
-         \frac{1}{1-e^{b+x}}+\frac{1}{1-e^{c+x}}+\frac{1}{e^{x}-1}-\frac{1}{x}\right)dx-\ln\varepsilon+\ln a+\gamma\right]=\\
+         \frac{1}{1-e^{b+x}}+\frac{1}{1-e^{c+x}}+\frac{1}{e^{x}-1}-\frac{1}{x}\right)\dx-\ln\varepsilon+\ln a+\gamma\right]=\\
      \frac{\varepsilon^{2}}{12}\left[\ln \left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{a (e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\ln\varepsilon+\ln a+\gamma\right]
@@
 %%  \begin{multline*}
-%%    \frac{f}{T}=-\frac{1}{ab+bc+ca}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{dx dy dz}{e^{x+y+z}-1}+\right.\\
+%%    \frac{f}{T}=-\frac{1}{ab+bc+ca}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1}+\right.\\
 %%    \left.+\frac{\varepsilon^{2}}{12}\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}
-%%      \left(\frac{e^{2(x+y+z)}+e^{x+y+z}}{\left(e^{x+y+z}-1\right)^{3}}-\frac{1}{bc}\frac{1}{x}\right)dx dy dz+\right.\\
+%%      \left(\frac{e^{2(x+y+z)}+e^{x+y+z}}{\left(e^{x+y+z}-1\right)^{3}}-\frac{1}{bc}\frac{1}{x}\right)\dx \dy \dz+\right.\\
 %%    \left.+\frac{\varepsilon^{2}}{12}(\ln a-\gamma)+\frac{\varepsilon^{2}}{12}\ln \varepsilon\right\}    
@@
 %%  \int_{0}^{a} \int_{0}^{b}\int_{0}^{c}
-%%  \left(\frac{e^{2(x+y+z)}+e^{x+y+z}}{\left(e^{x+y+z}-1\right)^{3}}-\frac{1}{bc}\frac{1}{x}\right)dx~dy~dz=\\
+%%  \left(\frac{e^{2(x+y+z)}+e^{x+y+z}}{\left(e^{x+y+z}-1\right)^{3}}-\frac{1}{bc}\frac{1}{x}\right)\dx~\dy~\dz=\\
 %%  =\ln \left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{a (e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)=\\
@@
   \label{eq:3}
-  \frac{f}{T}=-\frac{1}{ab+bc+ca}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{dx dy dz}{e^{x+y+z}-1}+\right.\\
+ f=-\frac{1}{2(ab+bc+ca)}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1}+\right.\\
   \left.+\frac{\varepsilon^{2}}{12}\left[\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-
@@
 
-The coefficient of the logarithmic term is connected to the central charge of the theory. In the
-paper \cite{cardy1988finite} it was shown, that this coefficient is $\frac{1}{6}c$. The scaling
-behavior of dimer model is described by free fermion theory with $c=\frac{1}{2}$.
+\section{Physical meaning of the expansion coefficients}
+\label{sec:accur-expans-phys}
 
-  \begin{figure}[h!tb]
-    \includegraphics{exact-vs-expansion.pdf}
-    \caption{Plot of the expression \eqref{eq:3} for $\varepsilon=\frac{1}{15}\dots\frac{1}{2}$, $a=3,b=2,c=1$
-      exact values. Note that difference between exact and approximate values decreases with
-      $\varepsilon$.}
-  \end{figure}
+The expansion  (\ref{eq:3}) can be written as
+\begin{equation}
+  \label{eq:26}
+  f=f_{0}+f_{1}\varepsilon + f_{2}\varepsilon^{2} +f_{3}\varepsilon^{2}\ln\varepsilon,
+\end{equation}
+where the coefficients are
+\begin{equation}
+  \label{eq:27}
+  f_{0}=-\frac{1}{2(ab+bc+ca)}\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1},
+\end{equation}
+\begin{equation}
+  \label{eq:28}
+  f_{1}=0,
+\end{equation}
+\begin{equation}
+  \label{eq:29}
+  f_{2}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12}\left[\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-
+    \gamma\right],
+\end{equation}
+and
+\begin{equation}
+  \label{eq:30}
+  f_{3}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12}
+\end{equation}
+In the scaling limit $\varepsilon\to 0$ so called ``limit shape phenomenon''~\cite{kenyon2006dimers}
+appears in the dimer model. The areas around the corners of the domain are ``frozen'' with height
+function values being fixed. An analytical ``Arctic curve'' delimits frozen regions from the region
+where the behavior is described by the effective free field theory
+\cite{kenyon2009lectures,kenyon2008height,kenyon2006dimers}.
 
+The behavior (\ref{eq:26}) of the logarithm of the partition function is generic in two-dimensional
+models \cite{cardy1988finite}.
+
+First two terms $f_{0}$ and $f_{1}$ are interpreted as a bulk and
+boundary free energies in the corresponding field theory. Since we have $f_{1}=0$, we can conclude
+that boundary tension is zero.
+The value of the first term $f_{0}$ can be rewritten using polylogarithm functions as
+\begin{multline}
+  \label{eq:34}
+  f_{0}=\frac{1}{2(ab+bc+ca)}\left[abc + \Li_{3}(e^{a})+\Li_{3}(e^{b})+\Li_{3}(e^{c})-
+    \Li_{3}(e^{a+b})\right.\\
+  \left.-\Li_{3}(e^{b+c})-    \Li_{3}(e^{a+c})+    \Li_{3}(e^{a+b+c})-\zeta(3)\right]
+\end{multline}
+
+The third term $f_{2}$ depends only on the shape of the domain through $a,b,c$ with a universal
+contribution that is equal to the Euler constant $\gamma$. We conjecture that Euler constant will
+appear even for a different choice of Kasteleyn weighting. In the future work we will consider
+coordinate dependent values of $q$, as was done in the paper \cite{okounkov2007random}.
+
+The term proportional to the logarithm of the scale $\varepsilon$ is also universal
+\cite{cardy1988finite} and should appear in all two-dimensional theories with boundary. In the paper
+\cite{cardy1988finite} it was argued that on a manifold of a characteristic length $L$ with a smooth
+boundary such a term must have the following form:
+\begin{equation}
+  \label{eq:31}
+  \delta F = -\frac{1}{6}{\bf c} \chi \ln L,
+\end{equation}
+where ${\bf c}$ is central charge of the effective field theory and $\chi$ is the Euler characteristic of
+the manifold
+\begin{equation}
+  \label{eq:32}
+  \chi=2-2 h-b,
+\end{equation}
+where $h$ is the number of handles and $b$ is the number of boundaries.
+
+Since the non-frozen domain is delimited by a smooth boundary, we have $\chi=1$ and
+\begin{equation}
+  \label{eq:33}
+  f_{3}=\frac{1}{2(ab+bc+ca)} \frac{{\bf c}}{6},
+\end{equation}
+which suggests the value of central charge ${\bf c}=\frac{1}{2}$. This value is in agreement with the
+identification of the dimer model with free fermions in the paper \cite{dijkgraaf2009dimer}.
+
+%% In the table we present the results of computations of free energy for the case $a=b=c=1$ and
+%% various values of $\varepsilon$ using an exact formula and expansion (\ref{eq:3}). In the third column
+%% difference is presented. We see that the difference decays faster than $\varepsilon^{3}$. The expansion
+%% (\ref{eq:3}) has good precision for comparison with Monte-Carlo simulation results such as presented
+%% in
+%% \cite{belov2018finite}. 
+%% 
+%% \begin{table}[htpb]
+%% \begin{center}
+%% \begin{tabular}{c|ccc}
+%%   $\varepsilon$&Exact value of $f$&$f$ from expansion (\ref{eq:3})&Difference\\
+%%   \hline
+%%   0.2 & 0.06734815 & 0.06559065 & 0.00175751\\
+%%   0.1 & 0.06689788 & 0.06681834 & 0.00007954\\
+%%   0.05 & 0.06721738 & 0.06719747 & 0.00001992\\
+%%   0.02 & 0.06732867 & 0.06732549 & $3.18791\cdot 10^{-6}$\\
+%%   0.01 & 0.06734815 & 0.06734736 & $7.97026 \cdot 10^{-7}$
+%%   0.005 & 0.06735375 & 0.06735355 & $1.99259 \cdot 10^{-7}$
+%% \end{tabular}
+%% \caption{Values of the free energy for $a=b=c=1$ computed by the exact formula (\ref{eq:20}) and an
+%%   approximate formula (\ref{eq:3}). The difference decays faster than $\varepsilon^{3}$.
+%% }
+%% \label{tttt1}
+%% \end{center}
+%% \end{table}
+%% 
+%%
+
+%%   \begin{figure}[h!tb]
+%% 
+%%     \includegraphics{exact-vs-expansion.pdf}
+%%     \caption{Plot of the expression \eqref{eq:3} for $\varepsilon=\frac{1}{15}\dots\frac{1}{2}$, $a=3,b=2,c=1$
+%%       exact values. Note that difference between exact and approximate values decreases with
+%%       $\varepsilon$.}
+%%   \end{figure}
+%% 
 %%\section{Scaling in the non-uniform model}
@@
 %%
-\section*{Conclusion}
+\section*{Conclusion and outlook}
 \label{sec:conclusion}
 
-  \begin{itemize}
-  \item This free energy scaling formula is in agreement with numerical computations
-  \item There are Monte-Carlo simulation results that support this scaling
-  \item Form of our formula is similar to the asymptotics of discrete Dirac operator obtained by Kenyon
-  \end{itemize}
+In the present paper we computed the asymptotic expansion of the free energy in the dimer model on a
+hexagonal domain of the hexagonal lattice. We've discussed the physical meaning of the expansion
+coefficients and argued that our results support the identification of the scaling behavior of the
+dimer model with the free-fermion field theory.
+
+In further work we will show the connection of the expansion coefficients with the spectral
+properties of Dirac operator on the non-frozen domain and study the universality of the presented
+expressions by considering the model with the non-uniform Kasteleyn weighting with $q$ depending on
+the coordinate.
 
@@
 \label{sec:acknowledgements}
-We are grateful to professor Nikolai Reshetikhin for his guidance in this work.
-We are thankful to the organizers and participants of the conference MQFT-2018.
+I am grateful to professor Nikolai Reshetikhin for his guidance in this work. I thank Pavel Belov
+for useful discussions and general support.
+
+I thank the organizers and participants of the conference MQFT-2018 for the opportunity
+to present our results and useful discussions.
 
 This research is supported by RFBR grant No. 18-01-00916.
-The calculations were carried out using the facilities of the SPbU Resource Center ``Computational Center of SPbU''.
+%The calculations were carried out using the facilities of the SPbU Resource Center ``Computational Center of SPbU''.
 

### 2018-11-26 AffineLieAlgebras/MQFT2018/paper.tex
Submitted to TMPh

@@
 \newcommand{\dz}{\mathrm{dz}}
-\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
-\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
-\newcommand{\co}[1]{\stackrel{\circ }{#1}}
-\newcommand{\pia}{\pi_{\mathfrak{a}}}
-\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
-\newcommand{\gf}{\mathfrak{g}}
-\newcommand{\nf}{\mathfrak{g}}
-\newcommand{\gfh}{\hat{\mathfrak{g}}}
-\newcommand{\af}{\mathfrak{a}}
-\newcommand{\afh}{\hat{\mathfrak{a}}}
-\newcommand{\bff}{\mathfrak{b}}
-\newcommand{\slnn}{\mathfrak{sl}_{n}}
-\newcommand{\sln}[1]{\mathfrak{sl}_{#1}}
-\newcommand{\afb}{\mathfrak{a}_{\bot}}
-\newcommand{\hf}{\mathfrak{h}}
-\newcommand{\hfg}{\hf_{\gf}}
-\newcommand{\hfa}{\hf_{\af}}
-\newcommand{\hfb}{\mathfrak{h}_{\bot}}
-\newcommand{\pf}{\mathfrak{p}}
-\newcommand{\aft}{\widetilde{\mathfrak{a}}}
-\newcommand{\sfr}{\mathfrak{s}}
-%\newcommand{\dim}{\mathrm{dim} }
 
 \begin{document}
-\title{Finite-size scaling of free energy in dimer model on hexagonal domain}
+\title{Finite-size scaling of free energy in the dimer model on a hexagonal domain}
 
@@
 {\small  Ulyanovskaya 1, 198504 St.~Petersburg, Russia}\\
-%\small{$^{2}$}\\
-%\small{$^{3}$}\\
 \small{email:antonnaz@gmail.com}
@@
   We consider dimer model on a hexagonal lattice. This model can be seen as a ``pile of cubes in the
-  corner''. The partition function is given by the determinant of Kasteleyn matrix. We use the
-  expression for the partition function to derive the scaling behavior of free energy in the limit
-  of lattice mesh tending to zero and temperature tending to infinity. We discuss the connection of
-  the expansion coefficients to the geometry of the domain.
+  corner''. The energy of configuration is given by the volume of the pile and the partition
+  function is computed by the classical MacMahon formula or, more formally, by the determinant of
+  Kasteleyn matrix. We use the expression for the partition function to derive the scaling behavior
+  of free energy in the limit of lattice mesh tending to zero and temperature tending to infinity.
+  We discuss the universality and physical meaning of expansion coefficients.
 \end{abstract}
@@
 that is given by the Euler constant and a geometry-dependent part that is written explicitly in
-elementary functions. The third term which encapsulates logarithmic dependence on the mesh size is
-also shown to be universal.
+terms of elementary functions. The third term which encapsulates logarithmic dependence on the mesh
+size is connected with the central charge of the effective field theory.
 
-We than compare these results with our previous numeric simulations \cite{belov2018finite}. 
+This result is supported by numeric simulations presented in our previous publication
+\cite{belov2018finite}.
+
 \section{Model definition}
@@
 model is solvable on the bipartite graphs, i.e. the partition function can be computed if the
-weights are introduced in such a way that each face with 0 mod 4 edges there is an odd number of
-negative edge weights and each face with 2 mod 4 edges has an even number of of negative edge
-weights. Then the signs of the edge weights form a so-called ``Kasteleyn orientation''on graph, the
-weighting is called ``Kasteleyn weighting'' \cite{kenyon2001dominos,kenyon2009lectures}.
+weights are introduced in such a way that for each face bounded by 0 mod 4 edges there is an odd
+number of negative edge weights and each face with 2 mod 4 edges has an even number of of negative
+edge weights. Then the signs of the edge weights form a so-called ``Kasteleyn orientation''on graph,
+the weighting is called ``Kasteleyn weighting'' \cite{kenyon2001dominos,kenyon2009lectures}.
 
 For a bipartite graph ${\cal G}$, color the vertices black and white in such a way that all the
-vertices adjacent to the black one are white. Denote by $W$,$B$ the sets of white and black
-vertices and by $w,b$ the elements of these sets.
+vertices adjacent to the black one are white. Denote by $B, W$ the sets of black and white
+vertices and by $b,w$ the elements of these sets.
 
@@
 
-Kasteleyn matrix defines a discrete Dirac operator $D$, in vertex $v$ we have:
+Kasteleyn matrix defines a discrete Dirac operator $D$, the action of $D$ on a function $f$ defined
+on vertices is given by:
 \begin{equation}
@@
 hexagonal lattice in the complex plane $\mathbb{C}$ in such a way that some edges are parallel to
-the real line. Then take
+the real line with and corresponding vertices have coordinates with integer real and imaginary
+parts. Then take
 \begin{eqnarray}
@@
 
-%% The scaling limit is achieved on the infinite lattice as $T\to\infty$. To study the scaling behavior
-%% using Monte-Carlo simulations on the finite lattices one can consider temperatures proportional to
-%% the lattice size and, then, extrapolate them to infinity.
-%%   
-%  \frametitle{Kasteleyn matrix and Dirac operator}
-%%  Consider infinite-dimensional graded algebra, e.g. $\gf[[t]]$ or $\hat\gf$
-
-%  \frametitle{Free energy scaling}
 The   free energy per site is defined as$^{*}$
@@
 
-%!!!! Kenyon uses $V=\#Dimers$.
-
-We are interested in the scaling limit, combined with the thermodynamic limit, when
-$ T\to \infty, \quad M,N,K\to \infty$, such that ratios
-$\frac{M}{T}=a,\quad \frac{N}{T}=b, \quad \frac{K}{T}=c$ remain fixed. In what follows we use
-$\varepsilon=\frac{1}{T}$, which can be seen as the scale of the model, e.g. mesh size.
+We are interested in the scaling limit, combined with the thermodynamic limit, when $ T\to \infty,$
+and $M,N,K\to \infty$, such that ratios $\frac{M}{T}=a,\quad \frac{N}{T}=b, \quad \frac{K}{T}=c$
+remain fixed. In what follows we use $\varepsilon=\frac{1}{T}$, which can be seen as the scale of
+the model, e.g. mesh size.
 
@@
 
-%%series and split the
-%%logarithm of product into the sum of logarithms. Thus we get:
-%%\begin{multline}
-%%  \label{eq:2}
-%%   -\frac{f}{T}= \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}\left\{
-%%    \ln\left(1-\frac{1}{e^{\varepsilon(i+j+k)}-1}\sum_{l=1}^{\infty} \frac{\varepsilon^{l}}{l!}\right)-\right.\\
-%%  -\left.\ln\left(1-\frac{1}{e^{\varepsilon(i+j+k)}-1}\sum_{l=1}^{\infty} \frac{2^{l}\varepsilon^{l}}{l!}\right)\right\}
-%%\end{multline}
-%%Then expand the logarithms up to $\varepsilon^{3}$:
 \begin{multline}
@@
 Here and below we will use the notation:
-%Denote by $g$ the expression that will appear multiple times:
 \begin{equation}
@@
 are finite, but some of the corresponding integrals are divergent.
-
-%%But we need to obtain
-%%corrections in $\varepsilon$ to the integrals as $\varepsilon\to 0$.
-%%
-%%We can use the following approximation formula for integral of some function $\tilde{f}$ to take
-%%care of the corrections:
 
@@
 \end{equation}
-
-%Now we can apply the integral representation.
 
@@
 
-%%Substituting this approximation and using integral representation for the quadratic
-%%  term in $\varepsilon$, we obtain for the free energy:
-%%  \begin{multline*}
-%%    \frac{f}{T}=-\frac{1}{ab+bc+ca}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1}+\right.\\
-%%    \left.+\frac{\varepsilon^{2}}{12}\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}
-%%      \left(\frac{e^{2(x+y+z)}+e^{x+y+z}}{\left(e^{x+y+z}-1\right)^{3}}-\frac{1}{bc}\frac{1}{x}\right)\dx \dy \dz+\right.\\
-%%    \left.+\frac{\varepsilon^{2}}{12}(\ln a-\gamma)+\frac{\varepsilon^{2}}{12}\ln \varepsilon\right\}    
-%%  \end{multline*}
-%%The integral can be taken explicitly, it is equal to
-%%\begin{multline}
-%%  \label{eq:7}
-%%  \int_{0}^{a} \int_{0}^{b}\int_{0}^{c}
-%%  \left(\frac{e^{2(x+y+z)}+e^{x+y+z}}{\left(e^{x+y+z}-1\right)^{3}}-\frac{1}{bc}\frac{1}{x}\right)\dx~\dy~\dz=\\
-%%  =\ln \left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{a (e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)=\\
-%%  =\ln \left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right) -\ln a.
-%%\end{multline}
-
 The term $\ln a$ is cancelled by the  and symmetry between $a,b,c$ is restored.
@@
 \end{equation}
+In the paper \cite{belov2018finite} we have presented results of Monte Carlo simulations using
+Metropolis and Wang-Landau algorithms that support the form of expansion (\ref{eq:26}). In
+particular we got $f_{1}=0.04\pm 0.04$ which is consistent with $f_{1}=0$.
+
 In the scaling limit $\varepsilon\to 0$ so called ``limit shape phenomenon''~\cite{kenyon2006dimers}
@@
 \end{multline}
+Here Riemann zeta function appears as a particular value of polylogarithm $\Li_{3}(1)=\zeta(3)$.
 
@@
 contribution that is equal to the Euler constant $\gamma$. We conjecture that Euler constant will
-appear even for a different choice of Kasteleyn weighting. In the future work we will consider
-coordinate dependent values of $q$, as was done in the paper \cite{okounkov2007random}.
+appear even for a different choice of Kasteleyn weighting, due to the treatment of logarithmic
+divergency. In the future work we will consider coordinate dependent values of $q$ and more complex
+geometries, as was done in the paper \cite{okounkov2007random}, to check this suggestion.
 
@@
 
-%% In the table we present the results of computations of free energy for the case $a=b=c=1$ and
-%% various values of $\varepsilon$ using an exact formula and expansion (\ref{eq:3}). In the third column
-%% difference is presented. We see that the difference decays faster than $\varepsilon^{3}$. The expansion
-%% (\ref{eq:3}) has good precision for comparison with Monte-Carlo simulation results such as presented
-%% in
-%% \cite{belov2018finite}. 
-%% 
-%% \begin{table}[htpb]
-%% \begin{center}
-%% \begin{tabular}{c|ccc}
-%%   $\varepsilon$&Exact value of $f$&$f$ from expansion (\ref{eq:3})&Difference\\
-%%   \hline
-%%   0.2 & 0.06734815 & 0.06559065 & 0.00175751\\
-%%   0.1 & 0.06689788 & 0.06681834 & 0.00007954\\
-%%   0.05 & 0.06721738 & 0.06719747 & 0.00001992\\
-%%   0.02 & 0.06732867 & 0.06732549 & $3.18791\cdot 10^{-6}$\\
-%%   0.01 & 0.06734815 & 0.06734736 & $7.97026 \cdot 10^{-7}$
-%%   0.005 & 0.06735375 & 0.06735355 & $1.99259 \cdot 10^{-7}$
-%% \end{tabular}
-%% \caption{Values of the free energy for $a=b=c=1$ computed by the exact formula (\ref{eq:20}) and an
-%%   approximate formula (\ref{eq:3}). The difference decays faster than $\varepsilon^{3}$.
-%% }
-%% \label{tttt1}
-%% \end{center}
-%% \end{table}
-%% 
-%%
-
-%%   \begin{figure}[h!tb]
-%% 
-%%     \includegraphics{exact-vs-expansion.pdf}
-%%     \caption{Plot of the expression \eqref{eq:3} for $\varepsilon=\frac{1}{15}\dots\frac{1}{2}$, $a=3,b=2,c=1$
-%%       exact values. Note that difference between exact and approximate values decreases with
-%%       $\varepsilon$.}
-%%   \end{figure}
-%% 
-%%\section{Scaling in the non-uniform model}
-%%\label{sec:scaling-non-uniform}
-%%
-%%Consider a skew 3D partition with the partition function
-%%\begin{equation}
-%%  \label{eq:25}
-%%  Z({q_{t}},\lambda)=\sum_{\lambda(t)}\prod_{t\in\mathbb{Z}}q_{t}^{|\lambda(t)|}
-%%\end{equation}
-%%
 \section*{Conclusion and outlook}
@@
 properties of Dirac operator on the non-frozen domain and study the universality of the presented
-expressions by considering the model with the non-uniform Kasteleyn weighting with $q$ depending on
-the coordinate.
+expressions by considering the model on more generic domain geometries with the non-uniform
+Kasteleyn weighting with $q$ depending on the coordinate.
 
@@
 This research is supported by RFBR grant No. 18-01-00916.
-%The calculations were carried out using the facilities of the SPbU Resource Center ``Computational Center of SPbU''.
 

### 2019-02-23 AffineLieAlgebras/MQFT2018/paper.tex
TMPh submitted version

@@
 \label{sec:introduction}
-The dimer model appeared as a very simplified model of solutions \cite{Fowler-1937}. The molecules
-are represented by the rigid tiles on a lattice. The partition function was computed on various
-lattices and with different boundary conditions \cite{doi:10.1080/14786436108243366,
-  P.W-1961,kenyon2009lectures}.
+The dimer model appeared in attempt to extend a statistical theory of perfect solutions in chemistry
+to the case of liquid mixtures with molecules of two very distinct sizes \cite{Fowler-1937}. The
+molecules were represented by the rigid tiles on a lattice and the number of tilings was
+approximately estimated. But an exact computation was not accessible at the time.
 
-Dimer models are the integrable lattice models of statistical physics that are under an active
-theoretical~\cite{zj2000,ferrari} and numerical
-investigation~\cite{ks2018}. Particular dimer model appears for certain choice
-of parameters in the well-known six-vertex model  \cite{pronko2017thesis}. Dimer models are
-closely related to the theory of alternating matrices \cite{elkies1992alternating1,elkies1992alternating2}
+In 1961, Kasteleyn \cite{P.W-1961}, Temperley and Fisher \cite{doi:10.1080/14786436108243366}
+represented the partition function of the dimer model as a Pfaffian of the signed adjacency matrix
+(``Kasteleyn matrix'') thus allowing the computation of the number of tilings and of free energy scaling limit.
+This result was very elegantly used by Fisher to solve Ising model \cite{fisher1966dimer} and by Fan
+and Wu \cite{Fan-1970} to compute free energy for a certain case of eight-vertex model.
 
-Specifically, the well-known limit shape phenomenon~\cite{vershik1977kerov} was discovered for dimer
-model~\cite{kenyon2006dimers} and a connection with the theory of random matrices was
-established~\cite{johansson2002non}.
+Further studies of dimer models revealed the connection to the theory of alternating matrices
+\cite{elkies1992alternating1,elkies1992alternating2}. Later, the well-known limit shape
+phenomenon~\cite{vershik1977kerov} was discovered for dimer models. First, the ``Arctic circle''
+theorem was proven for domino tilings of the domain in the form of ``Aztec diamond''
+~\cite{1998math......1068J}. Then similar result was obtained for a hexagonal domain on the
+hexagonal lattice~\cite{cohn1998shape}. Soon the connection of these results with the theory of
+random matrices was established~\cite{johansson2002non}. The papers
+\cite{kenyon2006dimers,kenyon2009lectures} present a detailed exposition of the limit shape
+phenomenon in the dimer models.
 
-Study of dimer models on various lattices and domains leads to interesting connections with the
+Dimer models are the integrable lattice models of statistical physics that are now under an active
+theoretical~\cite{zj2000,ferrari} and numerical investigation~\cite{ks2018}. Computation of
+correlation functions is a common problem for all vertex models \cite{colomo2012approach} as well as
+for dimer models. Another problem of great interest is the study of limit shapes in various cases
+\cite{borodin2010q,di2018tangent}.
+
+Configurations of dimer model on a hexagonal lattice are in one-to-one correspondence with the
+configurations of five-vertex model that appears for certain choice of parameters in the well-known
+six-vertex model \cite{kapitonov2012weighted,kapitonov2008five}.
+
+Study of dimer models on various lattices and domains led to interesting connections with the
 geometry of curved manifolds and with spectra of discrete and continuous Dirac and Laplace operators
@@
 derive the expressions for scaling limit of free energy and first three terms of the finite-size
-corrections. We show that the first term is identically zero. The second term has a universal part
-that is given by the Euler constant and a geometry-dependent part that is written explicitly in
-terms of elementary functions. The third term which encapsulates logarithmic dependence on the mesh
-size is connected with the central charge of the effective field theory.
+corrections. We show that the first term is identically zero. The second term is geometry-dependent
+and is written explicitly in terms of elementary functions. The third term which encapsulates
+logarithmic dependence on the mesh size is connected with the central charge of the effective field
+theory.
 
 This result is supported by numeric simulations presented in our previous publication
-\cite{belov2018finite}.
+\cite{1742-6596-1135-1-012024}.
 
@@
 \end{equation*}
-We set Boltzman constant equal to 1, then the partition function is 
+We set Boltzman constant equal to 1 and choose system of units in such a way that there is no
+coupling constant in the expression for energy. Then the partition function is
 \begin{equation*}
@@
 remain fixed. In what follows we use $\varepsilon=\frac{1}{T}$, which can be seen as the scale of
-the model, e.g. mesh size.
+the model, e.g. mesh size due to our choice of the system of units.
 
@@
   f=- \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}\left\{
-    g(i\varepsilon,j\varepsilon,k\varepsilon)+
-    \frac{3}{2}\varepsilon\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}\right]\right.\\
-  \left.+\frac{7}{6}\varepsilon^{2}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3 g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}+
-      2 g(i\varepsilon,j\varepsilon,k\varepsilon)^{3}\right]\right\}  + \mathcal{O}(\varepsilon^{3})
+    \varepsilon g(i\varepsilon,j\varepsilon,k\varepsilon)+
+    \frac{3}{2}\varepsilon^{2}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}\right]\right.\\
+  \left.+\frac{7}{6}\varepsilon^{3}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3 g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}+
+      2 g(i\varepsilon,j\varepsilon,k\varepsilon)^{3}\right]\right\}  + \mathcal{O}(\varepsilon^{4})
 \end{multline}
+%% Wrong power of $\varepsilon$ below!!
 
@@
 Taking this into account and using the relation \eqref{eq:21} to express the triple sum
-$ \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}    g(i\varepsilon,j\varepsilon,k\varepsilon)$
+$ \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}    \varepsilon g(i\varepsilon,j\varepsilon,k\varepsilon)$
 in \eqref{eq:4} as the integral plus corrections, we obtain
@@
   \end{equation}
-Thus we get the integral
+Thus we get the integral %%!!!!!
 \begin{multline}
@@
   \label{eq:26}
-  f=f_{0}+f_{1}\varepsilon + f_{2}\varepsilon^{2} +f_{3}\varepsilon^{2}\ln\varepsilon,
+  f=f_{0}+f_{1}\varepsilon +f_{2}\varepsilon^{2}\ln\varepsilon+ f_{3}\varepsilon^{2},
 \end{equation}
@@
 \begin{equation}
-  \label{eq:29}
-  f_{2}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12}\left[\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-
-    \gamma\right],
+  \label{eq:30}
+  f_{2}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12},
 \end{equation}
@@
 \begin{equation}
-  \label{eq:30}
-  f_{3}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12}
+  \label{eq:29}
+  f_{3}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12}\left[\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-
+    \gamma\right].
 \end{equation}
-In the paper \cite{belov2018finite} we have presented results of Monte Carlo simulations using
+
+In the paper \cite{1742-6596-1135-1-012024} we have presented results of Monte Carlo simulations using
 Metropolis and Wang-Landau algorithms that support the form of expansion (\ref{eq:26}). In
@@
 
-In the scaling limit $\varepsilon\to 0$ so called ``limit shape phenomenon''~\cite{kenyon2006dimers}
+In the scaling limit $\varepsilon\to 0$ so called ``limit shape phenomenon''~\cite{1998math......1068J,cohn1998shape}
 appears in the dimer model. The areas around the corners of the domain are ``frozen'' with height
@@
 
-The third term $f_{2}$ depends only on the shape of the domain through $a,b,c$ with a universal
-contribution that is equal to the Euler constant $\gamma$. We conjecture that Euler constant will
-appear even for a different choice of Kasteleyn weighting, due to the treatment of logarithmic
-divergency. In the future work we will consider coordinate dependent values of $q$ and more complex
-geometries, as was done in the paper \cite{okounkov2007random}, to check this suggestion.
-
 The term proportional to the logarithm of the scale $\varepsilon$ is also universal
@@
 
-Since the non-frozen domain is delimited by a smooth boundary, we have $\chi=1$ and
+Since the non-frozen domain is delimited by a smooth boundary, we have $\chi=1$ and we interpret
+$2(ab+bc+ca)$ as a volume of the domain, thus
 \begin{equation}
   \label{eq:33}
-  f_{3}=\frac{1}{2(ab+bc+ca)} \frac{{\bf c}}{6},
+  \delta F = \left(2(ab+bc+ca)\right) f_{2}\ln\varepsilon,
 \end{equation}
-which suggests the value of central charge ${\bf c}=\frac{1}{2}$. This value is in agreement with the
-identification of the dimer model with free fermions in the paper \cite{dijkgraaf2009dimer}.
+which together with formula \eqref{eq:30} suggests the value of central charge
+${\bf c}=\frac{1}{2}$. This value is in agreement with the identification of the dimer model with
+free fermions in the paper \cite{dijkgraaf2009dimer}.
+
+The last term $f_{3}$ depends only on the shape of the domain through $a,b,c$ with a universal
+contribution that is equal to the Euler constant $\gamma$. We conjecture that Euler constant will
+appear even for a different choice of Kasteleyn weighting, due to the treatment of logarithmic
+divergency. In the future work we will consider coordinate dependent values of $q$ and more complex
+geometries, as was done in the paper \cite{okounkov2007random}, to check this suggestion.
 

### 2019-03-31 AffineLieAlgebras/MQFT2018/paper.tex
First attempt to fix the result

@@
 \end{equation}
-Expanding the exponents $e^{\varepsilon}, e^{2\varepsilon}$ and logarithms in powers of $\varepsilon$ we obtain
-
-\begin{multline}
-  \label{eq:4}
-  %\frac{f}{T}
-  f=- \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}\left\{
-    \varepsilon g(i\varepsilon,j\varepsilon,k\varepsilon)+
-    \frac{3}{2}\varepsilon^{2}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}\right]\right.\\
-  \left.+\frac{7}{6}\varepsilon^{3}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3 g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}+
-      2 g(i\varepsilon,j\varepsilon,k\varepsilon)^{3}\right]\right\}  + \mathcal{O}(\varepsilon^{4})
-\end{multline}
-%% Wrong power of $\varepsilon$ below!!
-
 Here and below we will use the notation:
@@
 
+Omitting the arguments of $g(i\varepsilon,j\varepsilon,k\varepsilon)$ we thus can rewrite the free energy as
+\begin{equation}
+  \label{eq:2}
+  f=-\frac{1}{V}\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \left[\ln\left(1+g-g e^{\varepsilon}\right)-\ln\left(1+g-g e^{2\varepsilon}\right)\right]
+\end{equation}
+We have $V=2(MN+MK+NK)=2(ab+bc+ca)\varepsilon^{-2}$ and $g\sim \varepsilon^{-1}$ as
+$\varepsilon\to 0$. Let us rewrite the logarithms as a series in $\varepsilon, g$:
+\begin{equation}
+  \label{eq:25}
+  f=-\frac{1}{2(ab+bc+ca)}\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \varepsilon^{2}
+  \left[-\sum_{l=1}^{\infty}\frac{1}{l}\left(\sum_{m=1}^{\infty}\frac{g\varepsilon^{m}}{m!}\right)^{l}+
+    \sum_{l=1}^{\infty}\frac{1}{l}\left(\sum_{m=1}^{\infty}\frac{2^{m} g\varepsilon^{m}}{m!}\right)^{l}\right]
+\end{equation}
+We are interested in the leading contributions in $\varepsilon$. Since $g\sim \varepsilon^{-1}$,
+they come from the terms $g^{l}\varepsilon^{l}$ in the square brackets. The coefficients before
+these terms are $\frac{2^{l}-1}{l}$:
+\begin{equation}
+  \label{eq:36}
+  f\approx-\frac{1}{2(ab+bc+ca)}\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \varepsilon^{2} \left[g+\sum_{l=2}^{\infty}\frac{2^{l}-1}{l}g^{l}\varepsilon^{l}\right]
+\end{equation}
+We separated the first term since it plays a major role in the following computations.
+
+%% Since $g\sim \varepsilon^{-1}$, the first two terms in $\varepsilon$ are
+%% \begin{multline}
+%% \label{eq:35}
+%%   %\frac{f}{T}
+%%   f\approx-\frac{1}{2(ab+bc+ca)} \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K}\left\{
+%%     \varepsilon^{3} g(i\varepsilon,j\varepsilon,k\varepsilon)+
+%%     \frac{3}{2}\varepsilon^{4}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}\right]\right\}\\
+%%   +\mathcal{O}(\varepsilon^{2})
+%% \end{multline}
+%% Contribution of the order $\varepsilon^{2}$ come from the terms $g^{l}\varepsilon^{l}$ from the square brackets of the equation \eqref{eq:25}.
+The coefficients before these terms are $\frac{2^{l}-1}{l}$
+%% 
+%% 
+%% \begin{multline}
+%%   \label{eq:4}
+%%   %\frac{f}{T}
+%%   f=- \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}\left\{
+%%     \varepsilon g(i\varepsilon,j\varepsilon,k\varepsilon)+
+%%     \frac{3}{2}\varepsilon^{2}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}\right]\right.\\
+%%   \left.+\frac{7}{6}\varepsilon^{3}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3 g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}+
+%%       2 g(i\varepsilon,j\varepsilon,k\varepsilon)^{3}\right]\right\}  + \mathcal{O}(\varepsilon^{4})
+%% \end{multline}
+%% %% Wrong power of $\varepsilon$ below!!
+%% 
+%% 
 This expression looks like a combination of Riemann sums for some integrals. Note that these sums
-are finite, but some of the corresponding integrals are divergent.
+are finite for each $l$, but some of the corresponding integrals are divergent.
 

### 2019-03-31 AffineLieAlgebras/MQFT2018/paper.tex
New proof

@@
 
-\author{A.A.~Nazarov$^{1}$\\
+\author{A.A.~Nazarov$^{1,2}$, S.A.~Paston$^{1}$\\
 {\small
@@
 {\small  Ulyanovskaya 1, 198504 St.~Petersburg, Russia}\\
-\small{email:antonnaz@gmail.com}
+\small{$^{2}$email:antonnaz@gmail.com}
 }
@@
 Here $V$ is the number of vertices, it is twice the number of dimers and twice the number of  cube faces:
-\begin{equation*}
+\begin{equation}
   \label{eq:19}
-  V=2(MN+NK+MK)
-\end{equation*}
+  V=2(MN+NK+MK)=2(ab+bc+ca) \varepsilon^{-2}
+\end{equation}
 
@@
 obtain
-\begin{equation}
+\begin{multline}
   \label{eq:20}
     %-\frac{f}{T}
-    f=-\frac{1}{V}\ln Z =- \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}
-  \ln\left(\frac{1-e^{-\varepsilon (i+j+k)} e^{\varepsilon}}{1-e^{-\varepsilon (i+j+k)} e^{2\varepsilon}}\right)
+    f=-\frac{1}{V}\ln Z =\\=- \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}\left[
+  \ln\left(1-e^{-\varepsilon (i+j+k-3)} e^{-2\varepsilon}\right) -\ln\left(1-e^{-\varepsilon
+      (i+j+k-3)} e^{-\varepsilon}\right)\right] 
+\end{multline}
+We need to notice that for a finite $\varepsilon$ and each value of $i,j,k$ the logarithms have the
+form $\ln(1-x)$, where $0<x<1$. Thus we can represent the logarithms as a power series of $x$ and
+obtain
+\begin{equation}
+  \label{eq:7}
+  f=-\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K}\sum_{n=1}^{\infty}
+  \frac{1}{V}\frac{1}{n}\left[-e^{-n\varepsilon (i+j+k-3)} e^{-2n\varepsilon}+e^{-n\varepsilon
+      (i+j+k-3)} e^{-n\varepsilon}\right] 
 \end{equation}
+Here we have an absolutely convergent series, so we can change the order of summation and rewrite
+the free energy as
+\begin{equation}
+  \label{eq:37}
+  f=-\sum_{n=1}^{\infty}
+  \frac{1}{V}\frac{1}{n}e^{-n\varepsilon}\left(1-e^{-n\varepsilon}\right)\sum_{i=1}^{M}
+  \sum_{j=1}^{N} \sum_{k=1}^{K}e^{-n\varepsilon (i+j+k-3)} 
+\end{equation}
+The triple sum factorizes into the product of three sums of the type $\sum_{i=1}^{M}e^{-n\varepsilon
+  i}$, that are just the
+ sums of geometric progression. So we have $\sum_{i=1}^{M}e^{-n\varepsilon
+  i}=\frac{1-e^{-Mn\varepsilon}}{1-e^{-n\varepsilon}}$, and obtain
+\begin{equation}
+  \label{eq:38}
+  f=-\sum_{n=1}^{\infty}
+  \frac{1}{V}\frac{1}{n}\frac{e^{-n\varepsilon}}{\left(1-e^{-n\varepsilon}\right)^{2}}
+  \left(1-e^{-na}\right)\left(1-e^{-nb}\right)\left(1-e^{-nb}\right) 
+\end{equation}
+Denote by $\chi(z)$ the function
+\begin{equation}
+  \label{eq:39}
+  \chi(z)=e^{-z}\left(\frac{z}{1-e^{-z}}\right)^{2}, 
+\end{equation}
+and by $H_{n}$ the product of $\varepsilon$-independent exponents
+\begin{equation}
+  \label{eq:40}
+  H_{n}=\left(1-e^{-na}\right)\left(1-e^{-nb}\right)\left(1-e^{-nb}\right).
+\end{equation}
+
+Using the definition of the volume \eqref{eq:19} the free energy is written as
+\begin{equation}
+  \label{eq:41}
+  f=-\frac{1}{2(ab+bc+ca)} \sum _{n=1}^{\infty} \frac{\chi(n\varepsilon)}{n^{3}} H_{n}
+\end{equation}
+We are interested in the scaling behavior in $\varepsilon$ when $\varepsilon\to 0$. The function $f$
+is regular in $\varepsilon$ for $\varepsilon>0$. So we need to
+compute  $\left.f\right|_{\varepsilon\to 0}$ and the derivatives $\left.\frac{\partial f}{\partial
+  \varepsilon}\right|_{\varepsilon\to 0}$, $\left.\frac{\partial^{2} f}{\partial
+    \varepsilon^{2}}\right|_{\varepsilon\to 0}$. In general, the behavior of the form
+$f=f_{0}+f_{1}\varepsilon+f_{2} \varepsilon^{2}\ln \varepsilon+f_{3}\varepsilon^{2}$ is expected in
+two-dimensional critical systems \cite{cardy1988finite}.
+
 Here and below we will use the notation:

### 2019-04-04 AffineLieAlgebras/MQFT2018/paper.tex
New version of computation is mostly completed

@@
 
+The function $\chi(z)$ is smooth in 0, even and has the following Taylor series:
+\begin{equation}
+  \label{eq:45}
+  \chi(z)=1 - \frac{z^2}{12} + \frac{z^4}{240}+\mathcal{O}(z^{6})
+\end{equation}
+
 Using the definition of the volume \eqref{eq:19} the free energy is written as
@@
   \varepsilon}\right|_{\varepsilon\to 0}$, $\left.\frac{\partial^{2} f}{\partial
-    \varepsilon^{2}}\right|_{\varepsilon\to 0}$. In general, the behavior of the form
+  \varepsilon^{2}}\right|_{\varepsilon\to 0}$.
+
+For $\left.f\right|_{\varepsilon\to 0}$ we have $\chi(0)=1$ and the sum $\sum_{n=1}^{\infty}
+\frac{H_{n}}{n^{3}}$ is just a sum of  polylogarithms
+$\mathrm{Li}_{s}(z)=\sum_{n=1}^{\infty}\frac{z^{n}}{n^{s}}$ of third order:
+\begin{equation}
+  \label{eq:42}
+  \left.f\right|_{\varepsilon\to 0} =\frac{1}{2(ab+bc+ca)}\left[\Li_{3}(e^{-a})+\Li_{3}(e^{-b})+\Li_{3}(e^{-c})-
+    \Li_{3}(e^{-a-b})\right.\\
+  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right]
+\end{equation}
+The derivative of the function $\chi(z)$ is zero, $\chi'(0)=0$, and the series
+$\sum_{n=1}^{\infty} \frac{\chi'(n\varepsilon)}{n^{2}}H_{n}$ are convergent for a finite
+$\varepsilon$, thus we have for a derivative
+\begin{equation}
+  \label{eq:43}
+\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}=0
+\end{equation}
+
+Now let us compute the second derivative
+\begin{equation}
+  \label{eq:44}
+\frac{\partial^{2} f}{\partial
+  \varepsilon^{2}}=-\frac{1}{2(ab+bc+ca)} \sum _{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n} H_{n}.  
+\end{equation}
+Second derivative of $\chi$ is finite $\chi''(0)=-\frac{1}{6}$. But there is a difficulty with the
+limit $\varepsilon\to 0$ in this expression due to the poor convergence of the series. Let us
+rewrite the second derivative as a sum of two series:
+\begin{equation}
+  \label{eq:46}
+\frac{\partial^{2} f}{\partial
+  \varepsilon^{2}}=-\frac{1}{2(ab+bc+ca)} \left(\sum _{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n}+
+  \sum_{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n}(H_{n}-1)\right).    
+\end{equation}
+The second sum is now convergent, since $H_{n}-1$ decays exponentially in $n$. It can be presented
+as a combinations of series for logarithms:
+\begin{multline}
+  \label{eq:47}
+  \chi''(0)\sum_{n=1}^{\infty} \frac{H_{n}-1}{n}=\\=\chi''(0)\sum_{n=1}^{\infty}\frac{1}{n}\left(-e^{-a
+      n-b n-c n}+e^{-a n-b n}+e^{-a n-c n}+e^{-b n-c n} - e^{-a n}-e^{-b n}-e^{-c n}\right)=\\
+  =\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)
+%%  =\frac{1}{6} \left(-\log \left(1-e^{-a-b-c}\right)+\log
+%%   \left(1-e^{-a-b}\right)+\log
+%%   \left(1-e^{-a-c}\right)+\log
+%%   \left(1-e^{-b-c}\right)-\log
+%%   \left(1-e^{-a}\right)-\log
+%%   \left(1-e^{-b}\right)-\log
+%%   \left(1-e^{-c}\right)\right)
+\end{multline}
+
+First sum in the expression \eqref{eq:46} can be expressed as follows. First, consider second
+derivative of $\chi(z)$, separate an exponent and denote what is left by $\xi(z)$:
+\begin{equation}
+  \label{eq:48}
+  \chi''(z)=e^{-z}\frac{e^{2 z} \left(z^2+4 e^z
+   \left(z^2-1\right)+e^{2 z} \left(z^2-4
+   z+2\right)+4
+   z+2\right)}{\left(e^z-1\right)^4}=e^{-z}\xi(z)
+\end{equation}
+The sum is then rewritten
+\begin{equation}
+  \label{eq:49}
+  \sum _{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n}=
+  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(n\varepsilon) =
+  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(0)+  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}   
+\end{equation}
+The first term is series for the logarithm $\ln\left(1-e^{-\varepsilon}}\right)\approx \ln
+\varepsilon$,
+the second term can approximated by the integral:
+\begin{equation}
+  \label{eq:50}
+  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}\approx
+  \int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
+\end{equation}
+
+Thus we arrive to the following asymptotic behavior of the free energy:
+
+In general, the behavior of the form
 $f=f_{0}+f_{1}\varepsilon+f_{2} \varepsilon^{2}\ln \varepsilon+f_{3}\varepsilon^{2}$ is expected in

### 2019-04-04 AffineLieAlgebras/MQFT2018/paper.tex
New computation is completed, numeric section started

@@
 $\mathrm{Li}_{s}(z)=\sum_{n=1}^{\infty}\frac{z^{n}}{n^{s}}$ of third order:
-\begin{equation}
+\begin{multline}
   \label{eq:42}
@@
   \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right]
-\end{equation}
+\end{multline}
+Here Riemann zeta function appears as a particular value of polylogarithm $\Li_{3}(1)=\zeta(3)$.
+
 The derivative of the function $\chi(z)$ is zero, $\chi'(0)=0$, and the series
@@
 \end{equation}
-The first term is series for the logarithm $\ln\left(1-e^{-\varepsilon}}\right)\approx \ln
+The first term is series for the logarithm $\ln\left(1-e^{-\varepsilon}\right)\approx \ln
 \varepsilon$,
@@
 \end{equation}
+\begin{equation}
+  \label{eq:51}
+  \frac{\partial^{2} f}{\partial
+  \varepsilon^{2}}\approx-\frac{1}{2(ab+bc+ca)}
+\left[\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{6}\ln \varepsilon+\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz\right]
+\end{equation}
+Since we have logarithmic term in the second derivative, we have the behavior of free energy of the form
+\begin{equation}
+  \label{eq:26}
+  f\approx f_{0}+f_{1}\varepsilon +f_{2}\varepsilon^{2}\ln\varepsilon+ f_{3}\varepsilon^{2}+\mathcal{O}(\varepsilon^{3}),
+\end{equation}
+as expected in general in two-dimensional critical systems \cite{cardy1988finite}. Taking the
+derivatives of such expression by $\varepsilon$, we get $f_{0}=f(0)$,
+$f_{1}=\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}$,
+$\frac{\partial^{2} f}{\partial \varepsilon^{2}}=f_{2}(2\ln\varepsilon+3)+f_{3}$.
 
-Thus we arrive to the following asymptotic behavior of the free energy:
-
-In general, the behavior of the form
-$f=f_{0}+f_{1}\varepsilon+f_{2} \varepsilon^{2}\ln \varepsilon+f_{3}\varepsilon^{2}$ is expected in
-two-dimensional critical systems \cite{cardy1988finite}.
-
-Here and below we will use the notation:
-\begin{equation}
-  \label{eq:5}
-  g(x,y,z)=\frac{1}{e^{x+y+z}-1}
-\end{equation}
-
-Omitting the arguments of $g(i\varepsilon,j\varepsilon,k\varepsilon)$ we thus can rewrite the free energy as
-\begin{equation}
-  \label{eq:2}
-  f=-\frac{1}{V}\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \left[\ln\left(1+g-g e^{\varepsilon}\right)-\ln\left(1+g-g e^{2\varepsilon}\right)\right]
-\end{equation}
-We have $V=2(MN+MK+NK)=2(ab+bc+ca)\varepsilon^{-2}$ and $g\sim \varepsilon^{-1}$ as
-$\varepsilon\to 0$. Let us rewrite the logarithms as a series in $\varepsilon, g$:
-\begin{equation}
-  \label{eq:25}
-  f=-\frac{1}{2(ab+bc+ca)}\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \varepsilon^{2}
-  \left[-\sum_{l=1}^{\infty}\frac{1}{l}\left(\sum_{m=1}^{\infty}\frac{g\varepsilon^{m}}{m!}\right)^{l}+
-    \sum_{l=1}^{\infty}\frac{1}{l}\left(\sum_{m=1}^{\infty}\frac{2^{m} g\varepsilon^{m}}{m!}\right)^{l}\right]
-\end{equation}
-We are interested in the leading contributions in $\varepsilon$. Since $g\sim \varepsilon^{-1}$,
-they come from the terms $g^{l}\varepsilon^{l}$ in the square brackets. The coefficients before
-these terms are $\frac{2^{l}-1}{l}$:
-\begin{equation}
-  \label{eq:36}
-  f\approx-\frac{1}{2(ab+bc+ca)}\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \varepsilon^{2} \left[g+\sum_{l=2}^{\infty}\frac{2^{l}-1}{l}g^{l}\varepsilon^{l}\right]
-\end{equation}
-We separated the first term since it plays a major role in the following computations.
-
-%% Since $g\sim \varepsilon^{-1}$, the first two terms in $\varepsilon$ are
-%% \begin{multline}
-%% \label{eq:35}
-%%   %\frac{f}{T}
-%%   f\approx-\frac{1}{2(ab+bc+ca)} \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K}\left\{
-%%     \varepsilon^{3} g(i\varepsilon,j\varepsilon,k\varepsilon)+
-%%     \frac{3}{2}\varepsilon^{4}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}\right]\right\}\\
-%%   +\mathcal{O}(\varepsilon^{2})
-%% \end{multline}
-%% Contribution of the order $\varepsilon^{2}$ come from the terms $g^{l}\varepsilon^{l}$ from the square brackets of the equation \eqref{eq:25}.
-The coefficients before these terms are $\frac{2^{l}-1}{l}$
-%% 
-%% 
-%% \begin{multline}
-%%   \label{eq:4}
-%%   %\frac{f}{T}
-%%   f=- \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}\left\{
-%%     \varepsilon g(i\varepsilon,j\varepsilon,k\varepsilon)+
-%%     \frac{3}{2}\varepsilon^{2}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}\right]\right.\\
-%%   \left.+\frac{7}{6}\varepsilon^{3}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3 g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}+
-%%       2 g(i\varepsilon,j\varepsilon,k\varepsilon)^{3}\right]\right\}  + \mathcal{O}(\varepsilon^{4})
-%% \end{multline}
-%% %% Wrong power of $\varepsilon$ below!!
-%% 
-%% 
-This expression looks like a combination of Riemann sums for some integrals. Note that these sums
-are finite for each $l$, but some of the corresponding integrals are divergent.
-
-Let $G$ be an analytic function in the cube $[0,a]\times[0,b]\times[0,c]$, then
+Thus we have the coefficients
 \begin{multline}
-  \label{eq:21}
-  \int_{0}^{a} \int_{0}^{b}\int_{0}^{c}G(x,y,z) \dx\; \dy\;
-  \dz\approx\sum_{i=1}^{M}\sum_{j=1}^{N}\sum_{k=1}^{K}\left\{\varepsilon^{3}G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)-\right.\\
-  \left.-\left[\frac{\varepsilon^{4}}{2}\left((\partial_{x}+\partial_{y}+\partial_{z})G\right)(i\varepsilon,j\varepsilon,k\varepsilon)\right]+\right.\\
-  \left.\varepsilon^{5}\left(\frac{1}{6}(\partial_{x}^{2}+\partial_{y}^{2}+\partial_{z}^{2})+\frac{1}{4}(\partial_{x}\partial_{y}+\partial_{x}\partial_{z}+\partial_{y}\partial_{z})\right)G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)
-  \right\}+\mathcal{O}(\varepsilon^{6})
-\end{multline}
-This formula can be easily derived by dividing the volume of integration into cubes with side
-$\varepsilon$ and substituting Taylor series for $G$ into integrals.
-
-We can use this formula to approximate sums by integrals. Similar formula can be written for a
-function of two variables and double sums. We will not need higher order terms, but will use the
-approximation:
-\begin{equation}
-\label{eq:8}
-  \sum_{j=1}^{N}\sum_{k=1}^{K}\varepsilon^{2}G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)\approx \int_{0}^{b}\int_{0}^{c}G(i\varepsilon,y,z) \dy\; \dz+\mathcal{O}(\varepsilon^{3}))
-\end{equation}
-
-Note that
-\begin{equation}
-  \label{eq:6}
-  \begin{array}{c}
-    \partial_{x}g(x,y,z)=-g(x,y,z)-g(x,y,z)^{2}\\
-    \partial_{x}^{2}g(x,y,z)=g(x,y,z)+3g(x,y,z)^{2}+2g(x,y,z)^{3}
-  \end{array}
-\end{equation}
-
-Taking this into account and using the relation \eqref{eq:21} to express the triple sum
-$ \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}    \varepsilon g(i\varepsilon,j\varepsilon,k\varepsilon)$
-in \eqref{eq:4} as the integral plus corrections, we obtain
-\begin{multline}
-\label{eq:23}
- f=-\frac{1}{2(ab+bc+ca)}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1}+\right.\\
-  \left.+\sum_{i=1}^{M}\sum_{j=1}^{N}\sum_{k=1}^{K}\frac{\varepsilon^{5}}{12}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3
-      g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}+2
-      g(i\varepsilon,j\varepsilon,k\varepsilon)^{3}\right]\right\}
-\end{multline}
-Due to the equations \eqref{eq:6}, the corrections are of the same form as the higher order terms in
-$\varepsilon$. The linear in $\varepsilon$ term in \eqref{eq:4} is cancelled by three partial
-derivatives in \eqref{eq:21}. The coefficient of the quadratic term is changed by the addition of
-second derivatives from \eqref{eq:21} to $\frac{1}{12}$.
-
-There is no singularity in the sum, but
-$\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{(\exp(x+y+z)-1)^{3}}$ diverges
-logarithmically. So we can not just apply the integral representation~\eqref{eq:21} directly.
-
-We apply the formula \eqref{eq:8} to the internal sums in the triple sum, since there is no
-singularity in $\frac{1}{\left((\exp(i\varepsilon+j\varepsilon+k\varepsilon)-1\right)^{3}}$ for
-$i\neq 0$:
-
-\begin{equation}
-  \label{eq:9}
-\sum_{i=1}^{M}\left(\sum_{j=1}^{N}\sum_{k=1}^{K}\frac{\varepsilon^{5}}{12}
-      \frac{e^{2(i\varepsilon+j\varepsilon+k\varepsilon)}+e^{i\varepsilon+j\varepsilon+k\varepsilon}}{\left(e^{i\varepsilon+j\varepsilon+k\varepsilon}-1\right)^{3}}  \right)\approx
-    \frac{\varepsilon^{3}}{12}\sum_{i=1}^{M} \int_{0}^{b}\int_{0}^{c}
-      \left(\frac{e^{2(i\varepsilon+y+z)}+e^{i\varepsilon+y+z}}{\left(e^{i\varepsilon+y+z}-1\right)^{3}}\right) \dy \dz+\mathcal{O}(\varepsilon^{3})
-\end{equation}
-
-The double integral can be taken explicitly, so we obtain
-\begin{equation}
-  \label{eq:11}
-  \frac{\varepsilon^{3}}{12}\sum_{i=1}^{M}\left(     \frac{1}{e^{b+c+i\varepsilon}-1}+
-  \frac{1}{1-e^{b+i\varepsilon}}+\frac{1}{1-e^{c+i\varepsilon}}+\frac{1}{e^{i\varepsilon}-1}\right)
-\end{equation}
-
-The function $\frac{1}{e^{x}-1}$ has a divergence, so we can not apply integral approximation directly. We first need to 
-subtract and add $\frac{1}{i\varepsilon}$. The sum over $i$ of this term can be approximated using Euler formula:
-\begin{equation}
-    \label{eq:24}
-    \sum_{i=1}^{M}\frac{1}{i}=\frac{1}{M}\sum_{i=1}^{M}\frac{1}{i/M}=\int_{\frac{1}{M}}^{1}\frac{\dx}{x}+\gamma+O(\varepsilon)=-\ln\varepsilon+\ln a+\gamma+O(\varepsilon)
-  \end{equation}
-Thus we get the integral %%!!!!!
-\begin{multline}
-  \label{eq:13}
-    \frac{\varepsilon^{3}}{12}\left[\sum_{i=1}^{M}\left(     \frac{1}{e^{b+c+i\varepsilon}-1}+
-      \frac{1}{1-e^{b+i\varepsilon}}+\frac{1}{1-e^{c+i\varepsilon}}+\frac{1}{e^{i\varepsilon}-1}-\frac{1}{i\varepsilon}\right)-\ln\varepsilon+\ln a+\gamma+\mathcal{O}(\varepsilon^{3})\right]\approx\\
-   \frac{\varepsilon^{2}}{12}\left[\int_{0}^{a}\left(     \frac{1}{e^{b+c+x}-1}+
-      \frac{1}{1-e^{b+x}}+\frac{1}{1-e^{c+x}}+\frac{1}{e^{x}-1}-\frac{1}{x}\right)\dx-\ln\varepsilon+\ln a+\gamma\right]+\mathcal{O}(\varepsilon^{3})    
-\end{multline}
-The integral is now taken explicitly, it is equal to
-\begin{multline}
-  \label{eq:22}
-     \frac{\varepsilon^{2}}{12}\left[\int_{0}^{a}\left(     \frac{1}{e^{b+c+x}-1}+
-         \frac{1}{1-e^{b+x}}+\frac{1}{1-e^{c+x}}+\frac{1}{e^{x}-1}-\frac{1}{x}\right)\dx-\ln\varepsilon+\ln a+\gamma\right]=\\
-     \frac{\varepsilon^{2}}{12}\left[\ln \left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{a (e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\ln\varepsilon+\ln a+\gamma\right]
+  \label{eq:27}
+  f_{0}=\frac{1}{2(ab+bc+ca)}\left[\Li_{3}(e^{-a})+\Li_{3}(e^{-b})+\Li_{3}(e^{-c})-
+    \Li_{3}(e^{-a-b})\right.\\
+  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right]
 \end{multline}
 
-The term $\ln a$ is cancelled by the  and symmetry between $a,b,c$ is restored.
-Substituting this approximation into the expression \eqref{eq:23} we obtain 
- the final expression:
-\begin{multline}
-  \label{eq:3}
- f=-\frac{1}{2(ab+bc+ca)}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1}+\right.\\
-  \left.+\frac{\varepsilon^{2}}{12}\left[\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-
-      \gamma\right]+\frac{\varepsilon^{2}}{12}\ln \varepsilon\right\} +\mathcal{O}(\varepsilon^{3})
-\end{multline}
-
-\section{Physical meaning of the expansion coefficients}
-\label{sec:accur-expans-phys}
-
-The expansion  (\ref{eq:3}) can be written as
-\begin{equation}
-  \label{eq:26}
-  f=f_{0}+f_{1}\varepsilon +f_{2}\varepsilon^{2}\ln\varepsilon+ f_{3}\varepsilon^{2},
-\end{equation}
-where the coefficients are
-\begin{equation}
-  \label{eq:27}
-  f_{0}=-\frac{1}{2(ab+bc+ca)}\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1},
-\end{equation}
 \begin{equation}
@@
   \label{eq:29}
-  f_{3}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12}\left[\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-
-    \gamma\right].
+  f_{3}=-\frac{1}{2(ab+bc+ca)}\left[\frac{1}{12}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{8}+ \frac{1}{2}\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
+    \right].
 \end{equation}
+
+\section{Physical meaning of the expansion coefficients}
+\label{sec:accur-expans-phys}
 
@@
 The value of the first term $f_{0}$ can be rewritten using polylogarithm functions as
-\begin{multline}
-  \label{eq:34}
-  f_{0}=\frac{1}{2(ab+bc+ca)}\left[abc + \Li_{3}(e^{a})+\Li_{3}(e^{b})+\Li_{3}(e^{c})-
-    \Li_{3}(e^{a+b})\right.\\
-  \left.-\Li_{3}(e^{b+c})-    \Li_{3}(e^{a+c})+    \Li_{3}(e^{a+b+c})-\zeta(3)\right]
-\end{multline}
-Here Riemann zeta function appears as a particular value of polylogarithm $\Li_{3}(1)=\zeta(3)$.
 
@@
 The last term $f_{3}$ depends only on the shape of the domain through $a,b,c$ with a universal
-contribution that is equal to the Euler constant $\gamma$. We conjecture that Euler constant will
-appear even for a different choice of Kasteleyn weighting, due to the treatment of logarithmic
-divergency. In the future work we will consider coordinate dependent values of $q$ and more complex
-geometries, as was done in the paper \cite{okounkov2007random}, to check this suggestion.
+contribution that is equal to the integral of a function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$. We conjecture
+this constant will appear even for a different choice of Kasteleyn weighting, due to the treatment
+of logarithmic divergency. In the future work we will consider coordinate dependent values of $q$
+and more complex geometries, as was done in the paper \cite{okounkov2007random}, to check this
+suggestion.
+
+\section{Numeric checks}
+\label{sec:numeric-checks}
 

### 2019-04-08 AffineLieAlgebras/MQFT2018/paper.tex
Text almost completed, only skew partition case left

@@
 \end{equation}
-The triple sum factorizes into the product of three sums of the type $\sum_{i=1}^{M}e^{-n\varepsilon
+The triple sum factorizes into the product of three sums of the type $\sum_{i=0}^{M-1}e^{-n\varepsilon
   i}$, that are just the
- sums of geometric progression. So we have $\sum_{i=1}^{M}e^{-n\varepsilon
+ sums of geometric progression. So we have $\sum_{i=0}^{M-1}e^{-n\varepsilon
   i}=\frac{1-e^{-Mn\varepsilon}}{1-e^{-n\varepsilon}}$, and obtain
@@
 \label{sec:numeric-checks}
+To check our result \eqref{eq:26} numerically, we first need to evaluate the integral in $f_{3}$.
+The function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$ is smooth and but some care is required when taking the
+limit $z\to 0$ numerically. Evaluating the integral numerically with Mathematica we get
+\begin{equation}
+  \label{eq:2}
+  \int_{0}^{\infty}e^{-z}\frac{\xi(z)-\xi(0)}{z} dz = -0.08084228607897521
+\end{equation}
+
+The asymptotic expansion \eqref{eq:26} gives very good approximation for free energy. In Figure
+\ref{fig:approx-acc} we present exact and approximate values for $f$ and, on the right panel,
+demonstrate that inaccuracy is actually $\mathcal{O}(\varepsilon^{4})$.
+
+\begin{figure}[htbp]
+  \includegraphics[scale=0.9]{exact-vs-approximation}
+  \includegraphics{error-1}
+  \caption{\label{fig:approx-acc} {\it On the left:} Dependence of free energy on $1/\varepsilon$,
+    top -- $a=b=c=1$, bottom -- $a=3, b=2, c=1$. Exact values are shown by solid dots.
+    Approximations with formula \eqref{eq:26} are shown as blue dashed and red dotted lines. {\it On
+      the right:} Dependence of approximation inaccuracy on $\varepsilon$, solid line is fit by $b\varepsilon^{4}$.}
+\end{figure}
+
+\section{Generalization to other domains and particular cases}
+\label{sec:gener-other-doma}
+
+Consider the case of cubes in the box of infinite height. In this case $K=\infty$ and $M,N$ are
+finite. Now the hexagonal domain of dimer configurations has side of infinite length and total
+number of dimers is infinite, so it is more natural to set the volume of the system $V=MN$.
+
+Putting $K=\infty$ in the partition function, we see that all terms with $k$ are cancelled and we have
+\begin{equation}
+  \label{eq:3}
+  Z[M,N,q]=\prod_{i=1}^{M}\prod_{j=1}^{N}\frac{1}{1-q^{i+j-1}}
+\end{equation}
+
+The computation of free energy is almost exactly the same as in finite box case. We expand the
+logarithm in the free energy and then factorize the sum:
+\begin{multline}
+  \label{eq:4}
+  f=-\frac{1}{MN}\sum_{i=1}^{M}\sum_{j=1}^{N}\ln\left(1-e^{-\varepsilon(i+j-2)}e^{-\varepsilon}\right)=\\
+  =\sum_{n=1}^{\infty}\frac{\varepsilon^{2}}{ab}\frac{1}{n}e^{-n\varepsilon}\left(\sum_{i=1}^{M}e^{-n\varepsilon(i-1)}\right)
+  \left(\sum_{j=1}^{N}e^{-n\varepsilon(j-1)}\right)
+\end{multline}
+Computing the sums of geometric progressions we obtain almost the same expression as \eqref{eq:38},
+except that $H_{n}$ now has two multipliers $H_{n} =\left(1-e^{-na}\right)\left(1-e^{-nb}\right)$:
+\begin{equation}
+  \label{eq:5}
+  f=-\frac{1}{ab} \sum_{n=1}^{\infty}\frac{\chi(n\varepsilon)}{n^{3}} H_{n}.
+\end{equation}
+The function $\chi{z}$ is the same \eqref{eq:39}.
+
+Doing the same computations as in section \ref{sec:free-energy-scaling}, we obtain following results
+for the coefficients $f_{0}, f_{1}, f_{2}, f_{3}$:
+\begin{equation}
+  \label{eq:6}
+  f_{0}=\frac{1}{ab}\left[\Li_{3}(e^{-a})+\Li_{3}(e^{-b})-
+    \Li_{3}(e^{-a-b})-\zeta(3)\right]
+\end{equation}
+\begin{equation}
+  \label{eq:8}
+  f_{0}=0
+\end{equation}
+\begin{equation}
+  \label{eq:9}
+  f_{2}=\frac{1}{ab}\frac{1}{12}
+\end{equation}
+\begin{equation}
+  \label{eq:11}
+  f_{3}=-\frac{1}{ab}\left[\frac{1}{12}\ln\left(\frac{(e^{a}-1)(e^{b}-1)}{(e^{a+b}-1)}\right)-\frac{1}{8}+ \frac{1}{2}\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
+    \right].
+\end{equation}
+
+Again in the Fig. \ref{fig:approx-acc-2d} we see good numerical agreement between the asymptotic
+expansion \eqref{eq:26} and the exact formula \eqref{eq:4}.
+
+\begin{figure}[htbp]
+  \includegraphics[scale=0.8]{exact-vs-approximation-2d}
+  \includegraphics[scale=0.9]{error-2d}
+  \caption{\label{fig:approx-acc-2d} {\it On the left:} Dependence of free energy on $1/\varepsilon$
+    in the infinite height box,
+    top -- $a=b=1$, bottom -- $a=2, b=1$. Exact values are shown by solid dots.
+    Approximations with formula \eqref{eq:26} are shown as blue dashed and red dotted lines. {\it On
+      the right:} Dependence of approximation inaccuracy on $\varepsilon$, solid line is fit by $b\varepsilon^{4}$.}
+\end{figure}
 

### 2019-05-12 AffineLieAlgebras/MQFT2018/paper.tex
Non-uniform case started

@@
   \label{eq:40}
-  H_{n}=\left(1-e^{-na}\right)\left(1-e^{-nb}\right)\left(1-e^{-nb}\right).
+  H_{n}=\left(1-e^{-na}\right)\left(1-e^{-nb}\right)\left(1-e^{-nc}\right).
 \end{equation}
@@
 The second sum is now convergent, since $H_{n}-1$ decays exponentially in $n$. It can be presented
-as a combinations of series for logarithms:
+as a combination of series for logarithms:
 \begin{multline}
@@
 \end{equation}
-The function $\chi{z}$ is the same \eqref{eq:39}.
+The function $\chi(z)=e^{-z}\left(\frac{z}{1-e^{-z}}\right)^{2}$ is the same as in \eqref{eq:39}.
 
@@
 
+Let us consider the generalization to the case when $q$ depends upon the coordinate. It's usually
+done by varying $q$ on diagonal slices numbered by $t$. We need proper setup to consider the scaling
+limit. Let $\varphi(t)$ be a continuous bounded smooth function for $t\in\left[-a,b\right]$. Denote by
+$q_{i}=e^{-\varepsilon \varphi\left(i\varepsilon\right)}$ for $i=(-M+1)\dots N-1$. We index diagonal slices in
+such a way, that top left corner of the $M\times N$ box has index $N-M$, top right corner -- $N$,
+bottom left -- $-M$ and bottom right -- $0$. (See Fig. \ref{fig:box-t-coords} ). The slices with the
+indexes $N$ and $-M$ are empty so we set $q_{N}=q_{-M}=0$. There can be at most $N+M-1$ non-empty
+slices.
+
+\begin{figure}[htbp]
+  \includegraphics[scale=0.5]{box-t-coords}
+  \caption{\label{fig:box-t-coords} Coordinates of slices.}
+\end{figure}
+
+The partition function for this and more general case of arbitrary inner shape of the box was
+presented in the paper \cite{okounkov2007random}. In this case it contains products of weights
+$q_{i}$ for slices with negative and positive indexes:
+\begin{equation}
+  \label{eq:13}
+  Z=\prod_{i=0}^{N-1}\prod_{j=0}^{M-1} \frac{1}{1-q_{N-M}^{-1}\left(\prod_{k=0}^{i}q_{N-M-k}\right)\left(\prod_{l=0}^{j}q_{N-M+l}\right)}
+\end{equation}
+(see Theorem 2 in \cite{okounkov2007random}).
+If we set $q_{i}=q$, we recover formula \eqref{eq:3}.
+
+Now let us again consider free energy dependence on $\varepsilon$:
+\begin{equation}
+  \label{eq:21}
+  f=-\frac{\varepsilon^{2}}{ab}\sum_{i=0}^{N-1}\sum_{j=0}^{M-1}\ln
+  \left(1-e^{\varepsilon \varphi(b-a)}e^{-\varepsilon\sum_{k=0}^{i}\varphi\left(b-a-k\varepsilon\right)}
+    e^{-\varepsilon\sum_{l=0}^{j}\varphi\left(b-a+l\varepsilon\right)} \right)
+\end{equation}
+Expand the logarithm, change the order of summation and rewrite the free energy in the same way as
+we did before:
+\begin{equation}
+  \label{eq:22}
+   f=\sum_{n=1}^{\infty}\frac{\varepsilon^{2}}{ab}\frac{1}{n}e^{n\varepsilon
+     \varphi(b-a)}\sum_{i=0}^{N-1}\sum_{j=0}^{M-1} e^{-n\varepsilon\sum_{k=0}^{i}\varphi\left(b-a-k\varepsilon\right)}
+    e^{-n\varepsilon\sum_{l=0}^{j}\varphi\left(b-a+l\varepsilon\right)}
+\end{equation}
+Now we again can factorize double sum into product of two sums:
+\begin{equation}
+  \label{eq:23}
+    f=\sum_{n=1}^{\infty}\frac{\varepsilon^{2}}{ab}\frac{1}{n}e^{-n\varepsilon
+     \varphi(b-a)}\left(1+\sum_{i=1}^{N-1}
+     e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\right)
+   \left(1+\sum_{j=1}^{M-1}e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\right)
+\end{equation}
+Note that for $\varphi(t)\equiv 1$ we recover formula \eqref{eq:4}. 
+%%  
+%%  If we assume that $\varphi(b-a)\neq 0$, we can again obtain function $\chi(z)$:
+%%  \begin{multline}
+%%    \label{eq:24}
+%%     f=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{\chi\left(n\varepsilon\varphi(b-a)\right)}{n^{3}}\left(1-e^{-n\varepsilon
+%%         \varphi(b-a)}\right)^{2}\frac{1}{\varphi^{2}(b-a)}\cdot\\
+%%     \cdot\left(1+\sum_{i=1}^{N-1}
+%%       e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\right)
+%%     \left(1+\sum_{j=1}^{M-1}e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\right)  
+%%  \end{multline}
+%%
+
+We need to separate contributions of different orders in $\varepsilon$ and keep only the terms up to
+$\varepsilon^{2}$. To do so we expand the exponent
+\begin{equation}
+  \label{eq:35}
+e^{-n\varepsilon\varphi(b-a)}\approx
+1-n\varepsilon\varphi(b-a)+\frac{1}{2}n^{2}\varepsilon^{2}\varphi^{2}(b-a)+\mathcal{O}(\varepsilon^{3})  ,
+\end{equation}
+and approximate the sums by integrals using Euler-Maclaurin formula.
+
+The sum $\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)$ can be approximated using
+Euler-Maclaurin formula:
+\begin{multline}
+  \label{eq:25}
+  \varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)=\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx
+  +\frac{\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)+\\
+  +\frac{1}{12}\varepsilon^{2}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)+\mathcal{O}(\varepsilon^{3})
+\end{multline}
+
+Substituting into the exponent and expanding we get:
+\begin{multline}
+  \label{eq:34}
+  e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\approx e^{-n\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx
+  -n\frac{\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)
+  -n\frac{1}{12}\varepsilon^{2}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)}\approx\\
+\approx e^{-n\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx}\left[1-\frac{n\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)+\right.\\\left.
+  +\varepsilon^{2}\left(\frac{n^{2}}{8} \left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)^{2}-\frac{n}{12}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)\right)+\mathcal{O}(\varepsilon^{3})\right]
+\end{multline}
+Similarly, the expression for the second exponent is
+\begin{multline}
+  \label{eq:36}
+ e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\approx e^{-n\int_{0}^{j\varepsilon}\varphi(b-a+x)\dx}\left[1-\frac{n\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a+j\varepsilon)\right)+\right.\\\left.
+  +\varepsilon^{2}\left(\frac{n^{2}}{8} \left(\varphi(b-a)+\varphi(b-a+j\varepsilon)\right)^{2}-\frac{n}{12}\left(\varphi'(b-a+j\varepsilon)-\varphi'(b-a)\right)\right)+\mathcal{O}(\varepsilon^{3})\right]
+\end{multline}
+
+Now we need to substitute this expansion and formula \eqref{eq:35} into our formula for free energy
+\eqref{eq:23}.
+
 \section*{Conclusion and outlook}

### 2019-05-20 AffineLieAlgebras/MQFT2018/paper.tex
Non-uniform case typed from the notes

@@
 
-\section{Generalization to other domains and particular cases}
+\section{Box of infinite height}
 \label{sec:gener-other-doma}
@@
 
-Let us consider the generalization to the case when $q$ depends upon the coordinate. It's usually
+\section{Box of infinite height with coordinate-dependent weight}
+\label{sec:box-infinite-height}
+
+Now let us consider the generalization to the case when $q$ depends upon the coordinate. It's usually
 done by varying $q$ on diagonal slices numbered by $t$. We need proper setup to consider the scaling
@@
     f=\sum_{n=1}^{\infty}\frac{\varepsilon^{2}}{ab}\frac{1}{n}e^{-n\varepsilon
-     \varphi(b-a)}\left(1+\sum_{i=1}^{N-1}
+     \varphi(b-a)}\left(\sum_{i=0}^{N-1}
      e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\right)
-   \left(1+\sum_{j=1}^{M-1}e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\right)
+   \left(\sum_{j=0}^{M-1}e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\right),
  \end{equation}
-Note that for $\varphi(t)\equiv 1$ we recover formula \eqref{eq:4}. 
+where we assume that $\sum_{k=1}^{0}\varphi(b-a-k\varepsilon)=0$ and
+$\sum_{l=1}^{0}\varphi(b-a+l\varepsilon)=0$. Note that for $\varphi(t)\equiv 1$ we recover formula
+\eqref{eq:4}.
+
+Introduce following notations:
+\begin{equation}
+  \label{eq:52}
+  r_{\mp}(i\varepsilon)\equiv\varepsilon\sum_{k=1}^{i}\varphi(b-a\mp k\varepsilon)
+\end{equation}
+The functions $r_{\mp}$ can be approximated using Euler-Maclaurin formula as:
+\begin{equation}
+  \label{eq:53}
+  r_{\mp}(x)\approx\int_{0}^{x}\varphi(b-a\mp y) \dy +\frac{\varepsilon}{2}\left(\varphi(b-a\mp
+    x)-\varphi(b-a)\right)\mp \frac{\varepsilon^{2}}{12}\left(\varphi'(b-a\mp x)-\varphi'(b-a)\right)
+\end{equation}
+Denote by $\Psi$ the following functions:
+\begin{equation}
+  \label{eq:54}
+  \Psi^{\mp}_{n}(x)\equiv e^{-nr_{\mp}(x)}-e^{-nxr_{\mp}'(0)}
+\end{equation}
+With these notations we can write the free energy as
+\begin{multline}
+  \label{eq:55}
+  f=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n}e^{-n\varepsilon\varphi(b-a)}\left[\varepsilon^{2}\sum_{i=0}^{N-1}e^{-n\varepsilon
+    i r_{-}'(0)}\sum_{j=0}^{M-1}e^{-n\varepsilon j
+    r_{+}'(0)}+\varepsilon\sum_{i=0}^{N-1}e^{-n\varepsilon i
+    r_{-}'(0)}\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon)+\right.\\
+\left. +\varepsilon\sum_{i=0}^{N-1}\Psi^{-}_{n}(i\varepsilon) \cdot\varepsilon\sum_{j=0}^{M-1}e^{-n\varepsilon
+  j r_{+}'(0)}+\varepsilon\sum_{i=0}^{N-1}\Psi^{-}_{n}(i\varepsilon)
+\cdot\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon)\right]=\\
+=f^{(0)}+f^{+}+f^{-}+f^{\times}
+\end{multline}
+The first term $f^{(0)}$ can be computed explicitly as
+\begin{equation}
+  \label{eq:56}
+  f^{(0)}=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n} e^{-n\varepsilon
+    \varphi(b-a)}\varepsilon^{2}\frac{\left(1-e^{-n b r_{-}'(0)}\right)\left(1-e^{-n a
+        r_{+}'(0)}\right)}{\left(1-e^{-n\varepsilon r_{-}'(0)}\right)\left(1-e^{-n\varepsilon r_{+}'(0)}\right)}
+\end{equation}
+
+Denote by $H_{n}(\varepsilon)$ the numerator of this expression:
+\begin{equation}
+  \label{eq:57}
+  H_{n}(\varepsilon)=\left(1-e^{-n b r_{-}'(0)}\right)\left(1-e^{-n a r_{+}'(0)}\right)
+\end{equation}
+Note that
+\begin{equation}
+  \label{eq:58}
+  r_{\mp}'(0)=\varphi(b-a)\mp \frac{\varepsilon}{2} \varphi'(b-a)+\frac{\varepsilon^{2}}{12} \varphi''(b-a)+\mathcal{O}(\varepsilon^{3})
+\end{equation}
+can be rewritten as
+\begin{equation}
+  \label{eq:59}
+  r_{\mp}'(0)=\varphi(b-a)\left(1+\alpha_{\mp}(\varepsilon)\right), 
+\end{equation}
+where
+\begin{equation}
+  \label{eq:60}
+  \alpha_{\mp}(\varepsilon)=\mp
+  \frac{\varepsilon}{2}\frac{\varphi'(b-a)}{\varphi(b-a)}+\frac{\varepsilon^{2}}{12} \frac{\varphi''(b-a)}{\varphi(b-a)}+\mathcal{O}(\varepsilon^{3})
+\end{equation}
+
+Now for $f^{(0)}$ we have
+\begin{equation}
+  \label{eq:61}
+  f^{(0)}=\frac{1}{ab}\sum_{n=1}^{\infty} \frac{\tilde{\chi}\left(n\varepsilon
+      \varphi(b-a),\varepsilon\right) }{n^{3}\varphi(b-a)^{2}},
+\end{equation}
+where $\tilde{\chi}(z,\varepsilon)$  is defined as
+\begin{equation}
+  \label{eq:62}
+  \tilde{\chi}(z,\varepsilon)\equiv \frac{z^{2} e^{-z}
+    H_{n}(\varepsilon)}{\left(1-e^{-z\left(1+\alpha_{-}(\varepsilon)\right)}\right)
+    \left(1-e^{-z\left(1+\alpha_{+}(\varepsilon)\right)}\right)} 
+\end{equation}
+It is important to include $H_{n}(\varepsilon)$ since $H_{n}(\varepsilon)$ contains decaying
+exponents in $n$.
+
+Taking the derivatives of $f^{(0)}$ in $\varepsilon$ we get
+\begin{multline}
+  \label{eq:63}
+  \left(\frac{d}{d\varepsilon}\right)^{2} f^{(0)}=\frac{1}{ab\varphi(b-a)} \sum_{n=1}^{\infty}
+  \frac{1}{n^{3}}\left[
+    \left.\tilde{\chi}''_{\varepsilon\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+
+    2n\varphi(b-a)\left.\tilde{\chi}''_{z\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+\right.\\\left.
+      n^{2}\left(\varphi(b-a)\right)^{2}\tilde{\chi}''_{zz}\left(n\varepsilon\varphi(b-a),\varepsilon\right)  \right]+
+    \mathcal{O}(\varepsilon \ln \varepsilon)=\\
+    =\frac{1}{ab\varphi(b-a)}\left[\sum_{n=1}^{\infty} \frac{1}{n^{3}}
+      \tilde{\chi}''_{\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\tilde{\chi}''_{z\varepsilon}(0,0)\right]+
+    \\
+    +\frac{1}{ab}\sum_{n=1}^{\infty}\frac{H_{n}}{n}\chi''\left(n\varepsilon\varphi(b-a)\right)+\mathcal{O}(\varepsilon\ln \varepsilon),
+\end{multline}
+where
+\begin{equation}
+  \label{eq:64}
+  \chi(z)=\frac{z^{2} e^{-z}}{\left(1-e^{-z}\right)^{2}}
+\end{equation}
+and
+\begin{equation}
+  \label{eq:65}
+  H_{n}=\left(1-e^{-nb\varphi(b-a)}\right) \left(1-e^{-na\varphi(b-a)}\right)
+\end{equation}
+
+The last sum in the last line of the equation \eqref{eq:63} is the same as in the section
+\ref{sec:gener-other-doma}, thus we can compute it:
+\begin{equation}
+  \label{eq:66}
+  \frac{1}{ab}\sum_{n=1}^{\infty}\frac{H_{n}}{n}\chi''\left(n\varepsilon \varphi(b-a)\right)=
+  \frac{1}{ab}\left(\frac{1}{6}\ln \varepsilon +\frac{1}{6}\ln \varphi(b-a)+ \int_{0}^{\infty}
+    e^{-z}q(z) \dz+\chi''(0)\sum_{n=1}^{\infty}\frac{H_{n}-1}{n}\right),
+\end{equation}
+where $q(z)$ was defined in the equation
+
+Now we need to consider other terms in the expression \eqref{eq:55}. For $f^{+}$ we have
+\begin{equation}
+  \label{eq:67}
+  f^{+}=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n} e^{-n\varepsilon\varphi(b-a)} \varepsilon
+  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon)
+\end{equation}
+The sum over $j$ can be approximated by an integral using Euler-Maclaurin formula as
+\begin{equation}
+  \label{eq:68}
+  \varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon) = \int_{0}^{a}\Psi^{+}_{n}(x) \dx -
+  \frac{\varepsilon}{2}\left(\Psi^{+}_{n}(a)-\Psi^{+}_{n}(0)\right)+
+  \frac{\varepsilon^{2}}{12}\left(\Psi^{+'}_{n}(a)-\Psi^{+}_{n}(0)\right)+
+  \mathcal{O}\left(\varepsilon^{m}\Psi^{+(m-1)}_{n}\right)
+\end{equation}
+Since
+$\Psi_{n}(x)=e^{-nr'(0)x}\left(e^{-n\left(r(x)-xr'(0)\right)}-1\right)=e^{-nxr'(0)}\left(e^{-nx^{2}\zeta(x)}-1\right)$
+we see that $\Psi_{n}(0)=0$ and $\Psi_{n}'(0)=0$.
+Than in the limit $n\to\infty$ we have
+\begin{equation}
+  \label{eq:69}
+  \int_{0}^{c}\Psi_{n}(x)
+  \dx \xrightarrow[n\to\infty]{}\int_{0}^{c}e^{-nxr'(0)}\left(-nx^{2}\zeta(x)+\dots\right)\sim \frac{1}{n^{2}}
+\end{equation}
+The derivatives of $\Psi$ behave as $\Psi_{n}^{(m)}(0)\sim n^{m-1}$ so the contribution from
+$\varepsilon^{m}\Psi_{n}^{(m-1)}(0)$ to $f^{+}$ gives us
+\begin{equation}
+  \label{eq:70}
+  \sum_{n=1}^{\infty} \frac{1}{n} e^{-n\varepsilon\varphi(b-a)}
+  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}} \varepsilon^{m+1}\Psi_{n}^{(m-1)}(0)\sim
+  \sum_{n=1}^{\infty} \frac{1}{n^{4}} e^{-n\varepsilon\varphi(b-a)}
+  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}} (\varepsilon n )^{m+1}
+\end{equation}
+For the second derivative in $\varepsilon$ we thus see that main contribution behaves as
+$\sum_{n=1}\frac{1}{n^{2}}e^{-n\varepsilon\varphi(b-a)}
+  (n\varepsilon)^{m+1}\xrightarrow[\varepsilon\to 0]{}0$
+if $m\geq 3$. For the terms with $m=0,1,2$ we need to
+take the limit $\varepsilon\to 0$. Doing so, we obtain
+\begin{equation}
+  \label{eq:71}
+  \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{+}\right|_{\varepsilon=0} =
+  \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
+  e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}
+  \left(\varphi\int_{0}^{a} \Psi_{n}^{+}(x) \dx -\varepsilon^{2} \Psi_{n}^{+}(a) +\varepsilon^{3}\Psi^{+'}_{n}(0)\right)\right|_{\varepsilon=0}
+\end{equation}
+
+The contribution of $f^{-}$ is computed in exactly the same way:
+\begin{equation}
+  \label{eq:72}
+  \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{-}\right|_{\varepsilon=0} =
+  \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
+  e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nar_{+}'(0)}}{1-e^{-n\varepsilon r_{+}'(0)}}
+  \left(\varphi\int_{0}^{b} \Psi_{n}^{-}(x) \dx -\varepsilon^{2} \Psi_{n}^{-}(a) +\varepsilon^{3}\Psi^{-'}_{n}(0)\right)\right|_{\varepsilon=0}
+\end{equation}
+At last, we need to consider $f^{\times}$. In this term we can just take a limit $\varepsilon\to 0$
+and obtain
+\begin{multline}
+  \label{eq:73}
+  \left.\left(\frac{d}{d\varepsilon}\right)^{2}
+    f^{\times}\right|_{\varepsilon=0}=\left.\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n}
+  \left(\frac{d}{d\varepsilon^{2}}\right)^{2}\left(\int_{0}^{b}\Psi^{-}_{n}(x)\dx
+    -\frac{\varepsilon}{2}\Psi^{-}_{n}(b)+\frac{\varepsilon^{2}}{12}\Psi^{-'}_{n}(b)\right)\cdot\right.\\
+\cdot\left.\left(\int_{0}^{a}\Psi^{+}_{n}(x)\dx-\frac{\varepsilon}{2}\Psi^{+}_{n}(a)+
+    \frac{\varepsilon^{2}}{12}\Psi^{+}_{n}(a)\right)\right|_{\varepsilon=0} 
+\end{multline}
+This expression is easily computed explicitly, but is too cumbersome to present it here. 
 %%  

### 2019-06-12 AffineLieAlgebras/MQFT2018/paper.tex
More work on non-uniform case

@@
 
+\newtheorem{lemma}{Lemma}
 \newtheorem{Def}{Definition}[section]
@@
 \newcommand{\dx}{\mathrm{dx}~}
+\newcommand{\dxb}{\mathrm{d\bar x}~}
 \newcommand{\dy}{\mathrm{dy}~}
@@
   \label{eq:8}
-  f_{0}=0
+  f_{1}=0
 \end{equation}
@@
 \end{equation}
-Expand the logarithm, change the order of summation and rewrite the free energy in the same way as
-we did before:
+
+The terms $f_{0}$  in the asymptotic expansion \eqref{eq:26} can be easily obtained from
+this expression. To do so we need to approximate the sums by the integrals, using
+$\sum_{k=0}^{i}\varepsilon\varphi(b-a-k\varepsilon)\approx
+\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx$%%!!!!! Write more here
+and similar approximation for the outer sums:
+\begin{multline}
+  \label{eq:74}
+  f_{0}=-\frac{1}{ab}\int_{0}^{b}\int_{0}^{a}\ln
+  \left(1-e^{-\int_{0}^{y}\varphi\left(b-a-x\right)\dx}
+    e^{-\int_{0}^{z}\varphi\left(b-a+\bar x\right)\dxb} \right)\dz\dy=\\
+  =-\frac{1}{ab}\int_{0}^{b}\int_{0}^{a}\ln
+  \left(1-e^{-\int_{-y}^{z}\varphi\left(b-a+x\right)\dx} \right)\dz\dy
+\end{multline}
+Substituting in this expression $\varphi(x)\equiv 1$ we immediately get formula \eqref{eq:6}, since
+polylogarithms are integrals of logarithms. Although the logarithm has a divergency in the point
+$y=z=0$, it disappears after double integration.
+
+To compute the term $f_{1}$ we can use the following simple Lemma:
+\begin{lemma}
+  For an integrable function $f$ and smooth analytic function $\varphi$ the sum is approximated by
+  an integral with corrections  of order $\mathcal{o}(\varepsilon)$:
+  \begin{equation}
+    \label{eq:75}
+    \sum_{i=0}^{M}\sum_{j=0}^{N}\varepsilon^{2}f\left(\varepsilon\sum_{k=-i}^{j}\varphi(k\varepsilon)\right)=
+    \int_{0}^{a}\int_{0}^{b}f\left(\int_{-y}^{z}\varphi(x)\dx\right)\dz\dy+o(\varepsilon)
+  \end{equation}
+
+\end{lemma}
+
+To derive the expressions for higher order terms of the expansion \eqref{eq:26} we need to expand
+the logarithm, change the order of summation and rewrite the free energy in the same way as we did
+before:
 \begin{equation}

### 2019-06-13 AffineLieAlgebras/MQFT2018/paper.tex
All the terms in non-uniform case are written
Now we need to summarize the computations to get the final answer.

@@
 \begin{lemma}
-  For an integrable function $f$ and smooth analytic function $\varphi$ the sum is approximated by
-  an integral with corrections  of order $\mathcal{o}(\varepsilon)$:
+  Let $a=M\varepsilon$ and $b=N\varepsilon$.
+  For an integrable almost everywhere analytic function $f$ and analytic function $\varphi$ the sum is approximated by
+  an integral with the corrections  of order $o(\varepsilon)$:
   \begin{equation}
     \label{eq:75}
-    \sum_{i=0}^{M}\sum_{j=0}^{N}\varepsilon^{2}f\left(\varepsilon\sum_{k=-i}^{j}\varphi(k\varepsilon)\right)=
-    \int_{0}^{a}\int_{0}^{b}f\left(\int_{-y}^{z}\varphi(x)\dx\right)\dz\dy+o(\varepsilon)
+    \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}f\left(\varepsilon\sum_{k=-i}^{j}\varphi(k\varepsilon)\right)=
+    \int_{0}^{a}\int_{0}^{b}f\left(\int_{-y}^{z}\varphi(x)\dx\right)\dz\;\dy+o(\varepsilon)
+  \end{equation}
+\begin{proof}
+  Use Euler-Maclaurin formula to approximate the sums by the integrals with corrections. It is
+  enough to consider linear in $\varepsilon$ terms. First use
+  it for the sum in the argument of function $f$:
+  \begin{equation}
+    \label{eq:76}
+    \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}f\left(\varepsilon\sum_{k=-i}^{j}\varphi(k\varepsilon)\right)=
+    \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}f\left(\int_{-i\varepsilon}^{j\varepsilon}\varphi(x)\dx+\frac{\varepsilon}{2}\left(\varphi(j\varepsilon)-\varphi(-i\varepsilon)\right)+\mathcal{O}(\varepsilon^{2})\right)\dz\dy
+  \end{equation}
+  For a double sum the following simple analogue of Euler-Maclaurin formula can be used. 
+Let $G$ be an analytic function in the rectangle $[0,a]\times[0,b]$, then
+\begin{equation}
+  \label{eq:77}
+  \int_{0}^{a} \int_{0}^{b}G(y,z) \dz\; \dy\;
+  \approx\sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\left\{\varepsilon^{2}G\left(i\varepsilon,j\varepsilon\right)+
+    \frac{\varepsilon^{3}}{2}\left((\partial_{y}+\partial_{z})G\right)(i\varepsilon,j\varepsilon)\right\}+o(\varepsilon^{2})
+\end{equation}
+This formula can be easily derived by dividing the volume of integration into squares with side
+$\varepsilon$ and substituting Taylor series for $G$ into integrals.
+
+Denote by $G_{\varepsilon}(y,z)$ the function of two arguments that appear in the double sum in \eqref{eq:76}:
+\begin{equation}
+  \label{eq:78}
+  G_{\varepsilon}(y,z)=f\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right)
+\end{equation}
+Use formula \eqref{eq:77} to express the double sum in \eqref{eq:76} as the integral plus correction:
+\begin{equation}
+  \label{eq:79}
+  \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}G_{\varepsilon}(i\varepsilon,j\varepsilon)=\int_{0}^{a}\int_{0}^{b}
+  G_{\varepsilon}(y,z)\dz\;\dy-
+  \frac{\varepsilon^{3}}{2}
+  \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\left((\partial_{y}+\partial_{z})G_{\varepsilon}\right)(i\varepsilon,j\varepsilon)+o(\varepsilon^{3}) 
+\end{equation}
+Now expand the function $G_{\varepsilon}(y,z)$ under integral into Taylor series in $\varepsilon$:
+\begin{equation}
+  \label{eq:80}
+  \int_{0}^{a}\int_{0}^{b}G_{\varepsilon}(y,z)\dz\;\dy=
+  \int_{0}^{a}\int_{0}^{b}G_{0}(y,z)\dz\;\dy+\int_{0}^{a}\int_{0}^{b}\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))\cdot f'\left(\int_{-y}^{z}\varphi(x)\dx\right)\dz\;\dy+o(\varepsilon)
+\end{equation}
+On the other hand, the derivatives of $G_{\varepsilon}$ in $y,z$ are computed as
+\begin{eqnarray}
+  \label{eq:81}
+  \partial_{z}G_{\varepsilon}(y,z)=f'\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right)\varphi(z)+o(\varepsilon)\\
+  \partial_{y}G_{\varepsilon}(y,z)=-f'\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right)\varphi(-y)+o(\varepsilon)
+\end{eqnarray}
+Substituting equations \eqref{eq:80},\eqref{eq:81} into \eqref{eq:79} and using formula
+\eqref{eq:77} to change the double sum of the derivatives of $G_{\varepsilon}$ into double integral,
+we see that the linear correction in $\varepsilon$ is cancelled.
+
+\end{proof}
+\end{lemma}
+
+Using this lemma for our free energy density $f$, which is analytic and $\varphi$ which is smooth,
+we instantly see that 
+\begin{equation}
+  \label{eq:82}
+  f_{1}=0  
 \end{equation}
 
-\end{lemma}
+Next terms in the asymptotic expansion require more care, since we need to single out the
+contribution of the order $\varepsilon^{2}\ln\varepsilon$.
 
-To derive the expressions for higher order terms of the expansion \eqref{eq:26} we need to expand
-the logarithm, change the order of summation and rewrite the free energy in the same way as we did
-before:
+Thus, to derive the expressions for higher order terms of the expansion \eqref{eq:26} we need to
+expand the logarithm, change the order of summation and rewrite the free energy in the same way as
+we did before:
 \begin{equation}
@@
 \end{equation}
-Denote by $\Psi$ the following functions:
+Denote by $\Psi_{n}^{\mp}$ the following functions:
 \begin{equation}
   \label{eq:54}
-  \Psi^{\mp}_{n}(x)\equiv e^{-nr_{\mp}(x)}-e^{-nxr_{\mp}'(0)}
+  \Psi^{\mp}_{n}(x)\equiv e^{-nr_{\mp}(x)}-e^{-nxr_{\mp}'(0)}.
 \end{equation}
+These functions are analytic in $\varepsilon$, moreover, the higher derivatives of $\Psi^{\mp}_{n}$
+grow in $n$ not too rapidly. Thus, the sums of the series written in terms of these functions and
+their derivatives converge, as we will see below.
+
 With these notations we can write the free energy as
@@
 Since
-$\Psi_{n}(x)=e^{-nr'(0)x}\left(e^{-n\left(r(x)-xr'(0)\right)}-1\right)=e^{-nxr'(0)}\left(e^{-nx^{2}\zeta(x)}-1\right)$
+\begin{equation}
+  \label{eq:83}
+\Psi_{n}(x)=e^{-nr'(0)x}\left(e^{-n\left(r(x)-xr'(0)\right)}-1\right)=e^{-nxr'(0)}\left(e^{-nx^{2}\zeta(x)}-1\right)  
+\end{equation}
 we see that $\Psi_{n}(0)=0$ and $\Psi_{n}'(0)=0$.
@@
 \end{equation}
-The derivatives of $\Psi$ behave as $\Psi_{n}^{(m)}(0)\sim n^{m-1}$ so the contribution from
+The derivatives of $\Psi$ behave as $\Psi_{n}^{(m)}(0)\sim n^{m-1}$, since the derivatives should
+fall on the bracket in the expression \eqref{eq:83} for the value to be non-zero, and then extra
+power of $x$ is produced, which in turn should be differentiated. So the contribution from
 $\varepsilon^{m}\Psi_{n}^{(m-1)}(0)$ to $f^{+}$ gives us
@@
   e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}
-  \left(\varphi\int_{0}^{a} \Psi_{n}^{+}(x) \dx -\varepsilon^{2} \Psi_{n}^{+}(a) +\varepsilon^{3}\Psi^{+'}_{n}(0)\right)\right|_{\varepsilon=0}
+  \left(\varepsilon\int_{0}^{a} \Psi_{n}^{+}(x) \dx -\varepsilon^{2} \Psi_{n}^{+}(a) +\varepsilon^{3}\Psi^{+'}_{n}(0)\right)\right|_{\varepsilon=0}
 \end{equation}
+Note that $\frac{\varepsilon}{1-\exp(-n\varepsilon r'_{-}(0))}$ is analytic in $\varepsilon$. 
+The derivative can be computed explicitly, but the expression is too long to present it here.
 
@@
   e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nar_{+}'(0)}}{1-e^{-n\varepsilon r_{+}'(0)}}
-  \left(\varphi\int_{0}^{b} \Psi_{n}^{-}(x) \dx -\varepsilon^{2} \Psi_{n}^{-}(a) +\varepsilon^{3}\Psi^{-'}_{n}(0)\right)\right|_{\varepsilon=0}
+ \left(\varepsilon\int_{0}^{b} \Psi_{n}^{-}(x) \dx -\varepsilon^{2} \Psi_{n}^{-}(a) +\varepsilon^{3}\Psi^{-'}_{n}(0)\right)\right|_{\varepsilon=0}
 \end{equation}
@@
 \end{multline}
-This expression is easily computed explicitly, but is too cumbersome to present it here. 
+Again, this expression is easily computed explicitly, but is too cumbersome to present it here. 
 %%  
@@
 
-We need to separate contributions of different orders in $\varepsilon$ and keep only the terms up to
-$\varepsilon^{2}$. To do so we expand the exponent
-\begin{equation}
-  \label{eq:35}
-e^{-n\varepsilon\varphi(b-a)}\approx
-1-n\varepsilon\varphi(b-a)+\frac{1}{2}n^{2}\varepsilon^{2}\varphi^{2}(b-a)+\mathcal{O}(\varepsilon^{3})  ,
-\end{equation}
-and approximate the sums by integrals using Euler-Maclaurin formula.
-
-The sum $\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)$ can be approximated using
-Euler-Maclaurin formula:
-\begin{multline}
-  \label{eq:25}
-  \varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)=\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx
-  +\frac{\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)+\\
-  +\frac{1}{12}\varepsilon^{2}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)+\mathcal{O}(\varepsilon^{3})
-\end{multline}
-
-Substituting into the exponent and expanding we get:
-\begin{multline}
-  \label{eq:34}
-  e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\approx e^{-n\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx
-  -n\frac{\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)
-  -n\frac{1}{12}\varepsilon^{2}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)}\approx\\
-\approx e^{-n\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx}\left[1-\frac{n\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)+\right.\\\left.
-  +\varepsilon^{2}\left(\frac{n^{2}}{8} \left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)^{2}-\frac{n}{12}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)\right)+\mathcal{O}(\varepsilon^{3})\right]
-\end{multline}
-Similarly, the expression for the second exponent is
-\begin{multline}
-  \label{eq:36}
- e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\approx e^{-n\int_{0}^{j\varepsilon}\varphi(b-a+x)\dx}\left[1-\frac{n\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a+j\varepsilon)\right)+\right.\\\left.
-  +\varepsilon^{2}\left(\frac{n^{2}}{8} \left(\varphi(b-a)+\varphi(b-a+j\varepsilon)\right)^{2}-\frac{n}{12}\left(\varphi'(b-a+j\varepsilon)-\varphi'(b-a)\right)\right)+\mathcal{O}(\varepsilon^{3})\right]
-\end{multline}
-
-Now we need to substitute this expansion and formula \eqref{eq:35} into our formula for free energy
-\eqref{eq:23}.
+%% We need to separate contributions of different orders in $\varepsilon$ and keep only the terms up to
+%% $\varepsilon^{2}$. To do so we expand the exponent
+%% \begin{equation}
+%%   \label{eq:35}
+%% e^{-n\varepsilon\varphi(b-a)}\approx
+%% 1-n\varepsilon\varphi(b-a)+\frac{1}{2}n^{2}\varepsilon^{2}\varphi^{2}(b-a)+\mathcal{O}(\varepsilon^{3})  ,
+%% \end{equation}
+%% and approximate the sums by integrals using Euler-Maclaurin formula.
+%% 
+%% The sum $\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)$ can be approximated using
+%% Euler-Maclaurin formula:
+%% \begin{multline}
+%%   \label{eq:25}
+%%   \varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)=\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx
+%%   +\frac{\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)+\\
+%%   +\frac{1}{12}\varepsilon^{2}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)+\mathcal{O}(\varepsilon^{3})
+%% \end{multline}
+%% 
+%% Substituting into the exponent and expanding we get:
+%% \begin{multline}
+%%   \label{eq:34}
+%%   e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\approx e^{-n\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx
+%%   -n\frac{\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)
+%%   -n\frac{1}{12}\varepsilon^{2}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)}\approx\\
+%% \approx e^{-n\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx}\left[1-\frac{n\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)+\right.\\\left.
+%%   +\varepsilon^{2}\left(\frac{n^{2}}{8} \left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)^{2}-\frac{n}{12}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)\right)+\mathcal{O}(\varepsilon^{3})\right]
+%% \end{multline}
+%% Similarly, the expression for the second exponent is
+%% \begin{multline}
+%%   \label{eq:36}
+%%  e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\approx e^{-n\int_{0}^{j\varepsilon}\varphi(b-a+x)\dx}\left[1-\frac{n\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a+j\varepsilon)\right)+\right.\\\left.
+%%   +\varepsilon^{2}\left(\frac{n^{2}}{8} \left(\varphi(b-a)+\varphi(b-a+j\varepsilon)\right)^{2}-\frac{n}{12}\left(\varphi'(b-a+j\varepsilon)-\varphi'(b-a)\right)\right)+\mathcal{O}(\varepsilon^{3})\right]
+%% \end{multline}
+%% 
+%% Now we need to substitute this expansion and formula \eqref{eq:35} into our formula for free energy
+%% \eqref{eq:23}. 
+%%
 

### 2019-06-14 AffineLieAlgebras/MQFT2018/paper.tex
Numeric check subsection in non-uniform section added

@@
 The first term is series for the logarithm $\ln\left(1-e^{-\varepsilon}\right)\approx \ln
-\varepsilon$,
-the second term can approximated by the integral:
+\varepsilon$. 
+Denote by $Q(z)$ the difference of the function $\xi$ value in $z$ and zero, divided by z:
+\begin{equation}
+  \label{eq:85}
+  Q(z)=\frac{\xi(z)-\xi(0)}{z}.
+\end{equation}
+The function $Q(z)$ is analytic in $z$.
+
+Then the second term can approximated by the integral:
 \begin{equation}
   \label{eq:50}
-  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}\approx
-  \int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
+  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}Q(n\varepsilon)=\varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}\approx
+  \int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz=\int_{0}^{\infty}e^{-z}Q(z)\dz
 \end{equation}
@@
   \label{eq:29}
-  f_{3}=-\frac{1}{2(ab+bc+ca)}\left[\frac{1}{12}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{8}+ \frac{1}{2}\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
+  f_{3}=-\frac{1}{2(ab+bc+ca)}\left[\frac{1}{12}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{8}+ \frac{1}{2}\int_{0}^{\infty} e^{-z}Q(z) dz
     \right].
@@
   \label{eq:2}
-  \int_{0}^{\infty}e^{-z}\frac{\xi(z)-\xi(0)}{z} dz = -0.08084228607897521
+  \int_{0}^{\infty}e^{-z}Q(z)\dz=\int_{0}^{\infty}e^{-z}\frac{\xi(z)-\xi(0)}{z} dz = -0.080842%0.08084228607897521
 \end{equation}
@@
     =\frac{1}{ab\varphi(b-a)}\left[\sum_{n=1}^{\infty} \frac{1}{n^{3}}
-      \tilde{\chi}''_{\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\tilde{\chi}''_{z\varepsilon}(0,0)\right]+
+      \tilde{\chi}''_{\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\frac{1}{n^{2}}\tilde{\chi}''_{z\varepsilon}(0,0)\right]+
     \\
@@
 \end{multline}
-where
+where the function $\chi(z)$ is the same as in the equation \eqref{eq:39}
 \begin{equation}
@@
 \ref{sec:gener-other-doma}, thus we can compute it:
-\begin{equation}
+\begin{multline}
   \label{eq:66}
@@
   \frac{1}{ab}\left(\frac{1}{6}\ln \varepsilon +\frac{1}{6}\ln \varphi(b-a)+ \int_{0}^{\infty}
-    e^{-z}q(z) \dz+\chi''(0)\sum_{n=1}^{\infty}\frac{H_{n}-1}{n}\right),
+    e^{-z}Q(z) \dz+\chi''(0)\sum_{n=1}^{\infty}\frac{H_{n}-1}{n}\right)=\\
+  =\frac{1}{ab}\left(\frac{1}{6}\ln \varepsilon +\frac{1}{6}\ln \varphi(b-a)+ \int_{0}^{\infty}
+    e^{-z}Q(z) \dz+\frac{1}{6}\ln\left(\frac{\left(1-e^{a\varphi(b-a)}\right)\left(1-e^{a\varphi(b-a)}\right)}{1-e^{(a+b)\varphi(b-a)}}\right)\right),
+\end{multline}
+where $Q(z)$ was defined in the equation \eqref{eq:85}.
+
+Thus the contribution of $f^{(0)}$ to the asymptotic expansion \eqref{eq:26} consists of the term 
+\begin{equation}
+  \label{eq:87}
+f^{(0)}_{3}=\frac{1}{ab\varphi(b-a)}\left[\sum_{n=1}^{\infty} \frac{1}{n^{3}}
+  \tilde{\chi}''_{\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\frac{1}{n^{2}}\tilde{\chi}''_{z\varepsilon}(0,0)\right],
 \end{equation}
-where $q(z)$ was defined in the equation
+that is cumbersome but does not depend on $\varepsilon$ and can be computed explicitly and the
+expression \eqref{eq:66}, which gives us logarithmic behavior in $\varepsilon$.
 
@@
   \label{eq:71}
-  \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{+}\right|_{\varepsilon=0} =
+  f^{+}_{3}\equiv\left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{+}\right|_{\varepsilon=0} =
   \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
@@
   \label{eq:72}
-  \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{-}\right|_{\varepsilon=0} =
+   f^{-}_{3}\equiv \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{-}\right|_{\varepsilon=0} =
   \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
@@
   \label{eq:73}
-  \left.\left(\frac{d}{d\varepsilon}\right)^{2}
+   f^{\times}_{3}\equiv \left.\left(\frac{d}{d\varepsilon}\right)^{2}
     f^{\times}\right|_{\varepsilon=0}=\left.\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n}
@@
 Again, this expression is easily computed explicitly, but is too cumbersome to present it here.
+
+At last we can write the asymptotic expansion coefficients in the present case:
+\begin{equation}
+  \label{eq:84}
+  f_{0}= -\frac{1}{ab}\int_{0}^{b}\int_{0}^{a}\ln
+  \left(1-e^{-\int_{-y}^{z}\varphi\left(b-a+x\right)\dx} \right)\dz\dy
+\end{equation}
+\begin{equation}
+  \label{eq:88}
+  f_{1}=0
+\end{equation}
+\begin{equation}
+  \label{eq:89}
+  f_{2}=\frac{1}{ab}\frac{1}{12}    
+\end{equation}
+\begin{multline}
+  \label{eq:90}
+  f_{3}=f^{(0)}_{3}+f^{+}_{3}+f^{-}_{3}+f^{\times}_{3}+
+  \frac{1}{ab}\frac{1}{12}\ln\left(\frac{\varphi(b-a)\left(1-e^{a\varphi(b-a)}\right)\left(1-e^{a\varphi(b-a)}\right)}{1-e^{(a+b)\varphi(b-a)}}\right)+\\
+  +\frac{1}{ab}\left(\frac{1}{8} +\frac{1}{2} \int_{0}^{\infty}
+    e^{-z}q(z) \dz\right),
+\end{multline}
+Here in the first line we have the contributions that depend on the choice of the weight function
+$\varphi$ and in the second line -- the universal contribution that appears in the case
+$\varphi\equiv 1$ and in the box of finite height.
+
+\subsection{Numerical checks}
+\label{sec:numerical-checks-nonuniform}
+Here we present results of comparison of numerical values of the expansion coefficients
+$f_{0},f_{1},f_{2},f_{3}$ that were obtained from analytical formulas
+\eqref{eq:84},\eqref{eq:88},\eqref{eq:89},\eqref{eq:90} using Mathematica computer algebra system
+with the results of fitting exact numeric values of free energy for $\frac{1}{\varepsilon}=2\dots
+200$
+by the formula $f=f_{0}+
+f_{1}\varepsilon+
+f_{2}\varepsilon^{2}\ln\varepsilon+f_{3}\varepsilon^{2}+f_{4}\varepsilon^{3}+f_{5}\varepsilon^{4}$.
+
+In the table we present results for various functions $\varphi(z)$ and values of $a,b$.
+\begin{table}[htpb]
+\begin{center}
+\begin{tabular}{c|cccccc}
+  & $\varphi(z)$ & $a,b$ & $f_{0}$ &  $f_{1}$ &  $12ab f_{2}$ &  $f_{3}$ \\
+ \hline
+ analytic & $\frac{1}{3}(2+\cos(z))$ & 1,3 & $0.472206688$ & $0$ & $1$&$-0.043883000$\\
+ numeric & $\frac{1}{3}(2+\cos(z))$ & 1,3 &  $0.472206693$ & $0.000000730$ & $1.000730689$&$-0.043827958$\\
+  \hline
+ analytic & $\frac{1}{3}(2+\cos(z))$ & 2,3 & $0.235922467$ & $0$ & $1$&$-0.030398000$\\
+ numeric & $\frac{1}{3}(2+\cos(z))$ & 2,3 &  $0.235922467$ & $0.000000044$ & $1.000088528$&$-0.030394694$\\
+\hline                                                
+ analytic & $a+z/2$ & 1,3 & $0.097288596$ & $0$ & $1$&$-0.033688300$\\
+ numeric & $a+z/2$ & 1,3 &  $0.097288593$ & $0.000000848$ & $1.000848267$&$-0.033624441$\\
+\hline                                                
+ analytic & $a+z/2$ & 2,3 & $0.032804447$ & $0$ & $1$&$-0.015094000$\\
+ numeric & $a+z/2$ & 2,3 &  $0.032804447$ & $-0.000000002$ & $0.999996808$&$-0.015094162$\\
+\end{tabular}
+\caption{Values of the fitted parameters and analytically computed expansion coefficients for
+  various weight functions $\varphi$ and values of $a,b$.
+}
+\label{tttt1}
+\end{center}
+\end{table}
+
+We see very good coincidence between values, obtained numerically and analytically.
+
 %%  
@@
 
-In further work we will show the connection of the expansion coefficients with the spectral
-properties of Dirac operator on the non-frozen domain and study the universality of the presented
-expressions by considering the model on more generic domain geometries with the non-uniform
-Kasteleyn weighting with $q$ depending on the coordinate.
+In further work we will study the connection of the expansion coefficients with the spectral
+properties of Dirac operator on the non-frozen domain and study the universality of our results. We
+will also further discuss the description of the model by boundary conformal field theory.
 
@@
 \label{sec:acknowledgements}
-I am grateful to professor Nikolai Reshetikhin for his guidance in this work. I thank Pavel Belov
+We are grateful to professor Nikolai Reshetikhin for his attention to this work. We thank Pavel Belov
 for useful discussions and general support.
 
-I thank the organizers and participants of the conference MQFT-2018 for the opportunity
+We thank the organizers and participants of the conference MQFT-2018 for the opportunity
 to present our results and useful discussions.

### 2019-07-06 AffineLieAlgebras/MQFT2018/paper.tex
Before rewriting central charge section

@@
 \label{sec:introduction}
-The dimer model appeared in attempt to extend a statistical theory of perfect solutions in chemistry
-to the case of liquid mixtures with molecules of two very distinct sizes \cite{Fowler-1937}. The
-molecules were represented by the rigid tiles on a lattice and the number of tilings was
-approximately estimated. But an exact computation was not accessible at the time.
+The dimer model appeared in 1937 in an attempt to extend a statistical theory of perfect solutions
+in chemistry to the case of liquid mixtures with molecules of two very distinct sizes
+\cite{Fowler-1937}. The molecules were represented by the rigid tiles on a lattice and the number of
+tilings was approximately estimated. But an exact computation was not accessible at the time.
 
@@
 We consider a particular case of the dimer model on a hexagonal domain of hexagonal lattice, that
-can be seen as a ``pile of cubes in the corner''. The energy of configuration is the total number of
-cubes. For this particular case we use an exact combinatorial formula for the partition function to
-derive the expressions for scaling limit of free energy and first three terms of the finite-size
-corrections. We show that the first term is identically zero. The second term is geometry-dependent
-and is written explicitly in terms of elementary functions. The third term which encapsulates
-logarithmic dependence on the mesh size is connected with the central charge of the effective field
-theory.
-
-This result is supported by numeric simulations presented in our previous publication
-\cite{1742-6596-1135-1-012024}.
+can be seen as a ``pile of cubes in the corner of the box''. The energy of configuration is the
+total number of cubes. For this particular case we use an exact combinatorial formula for the
+partition function to derive the expressions for scaling limit of free energy and first three terms
+of the finite-size corrections. We show that the first term is identically zero. The second term
+which encapsulates logarithmic dependence on the mesh size is connected with the central charge of
+the effective field theory and with the geometry of limit shape. The third term is
+geometry-dependent and is written explicitly in terms of elementary functions.
+
+We then consider the box of infinite height and the case of coordinate-dependent Boltzmann weights.
+In these cases we are also able to write explicit expressions for finite-size corrections. We
+demonstrate the universality of the logarithmic term.
+
+Our results are supported by numeric checks and Monte-Carlo simulations presented in our previous
+publication \cite{1742-6596-1135-1-012024}.
 
@@
   \label{eq:15}
-  Z=\sum_{\mathrm{conf}}\prod_{e\in \mathrm{conf}}w(e)=|\det {\cal K}|
+  Z=\sum_{\mathrm{conf}}\prod_{e\in \mathrm{conf}}w(e)=|\det {\cal K}|.
 \end{equation}
@@
   \label{eq:16}
-  (Df)(v)=\sum_{u}{\cal K}(v,u) f(u)
+  (Df)(v)=\sum_{u}{\cal K}(v,u) f(u).
 \end{equation}
@@
   \label{eq:12}
-   Z[M,N,K,q]=\prod_{i=1}^{M}\prod_{j=1}^{N}\prod_{k=1}^{K}\frac{1-q^{i+j+k-1}}{1-q^{i+j+k-2}}
+   Z[M,N,K,q]=\prod_{i=1}^{M}\prod_{j=1}^{N}\prod_{k=1}^{K}\frac{1-q^{i+j+k-1}}{1-q^{i+j+k-2}}.
 \end{equation}
@@
   {\cal K}(w,b)=q^{\Re w+\Im w} \quad \mathrm{if}\quad \Im w=\Im b\\
-  {\cal K}(w,b)=1 \quad \mathrm{if}\quad \Im w\neq\Im b
+  {\cal K}(w,b)=1 \quad \mathrm{if}\quad \Im w\neq\Im b.
 \end{eqnarray}
@@
   % \frac{f}{T}
-  f=-\frac{1}{V}\ln Z(M,N,K,q)
+  f=-\frac{1}{V}\ln Z(M,N,K,q).
 \end{equation*}
@@
   \label{eq:19}
-  V=2(MN+NK+MK)=2(ab+bc+ca) \varepsilon^{-2}
+  V=2(MN+NK+MK)=2(ab+bc+ca) \varepsilon^{-2}.
 \end{equation}
@@
   \ln\left(1-e^{-\varepsilon (i+j+k-3)} e^{-2\varepsilon}\right) -\ln\left(1-e^{-\varepsilon
-      (i+j+k-3)} e^{-\varepsilon}\right)\right] 
+      (i+j+k-3)} e^{-\varepsilon}\right)\right].
 \end{multline}
@@
   \frac{1}{V}\frac{1}{n}\left[-e^{-n\varepsilon (i+j+k-3)} e^{-2n\varepsilon}+e^{-n\varepsilon
-      (i+j+k-3)} e^{-n\varepsilon}\right] 
+      (i+j+k-3)} e^{-n\varepsilon}\right]. 
 \end{equation}
@@
   \frac{1}{V}\frac{1}{n}e^{-n\varepsilon}\left(1-e^{-n\varepsilon}\right)\sum_{i=1}^{M}
-  \sum_{j=1}^{N} \sum_{k=1}^{K}e^{-n\varepsilon (i+j+k-3)} 
+  \sum_{j=1}^{N} \sum_{k=1}^{K}e^{-n\varepsilon (i+j+k-3)} .
 \end{equation}
@@
   \frac{1}{V}\frac{1}{n}\frac{e^{-n\varepsilon}}{\left(1-e^{-n\varepsilon}\right)^{2}}
-  \left(1-e^{-na}\right)\left(1-e^{-nb}\right)\left(1-e^{-nb}\right) 
+  \left(1-e^{-na}\right)\left(1-e^{-nb}\right)\left(1-e^{-nb}\right).
 \end{equation}
@@
   \label{eq:45}
-  \chi(z)=1 - \frac{z^2}{12} + \frac{z^4}{240}+\mathcal{O}(z^{6})
+  \chi(z)=1 - \frac{z^2}{12} + \frac{z^4}{240}+\mathcal{O}(z^{6}).
 \end{equation}
@@
   \label{eq:41}
-  f=-\frac{1}{2(ab+bc+ca)} \sum _{n=1}^{\infty} \frac{\chi(n\varepsilon)}{n^{3}} H_{n}
+  f=-\frac{1}{2(ab+bc+ca)} \sum _{n=1}^{\infty} \frac{\chi(n\varepsilon)}{n^{3}} H_{n}.
 \end{equation}
@@
     \Li_{3}(e^{-a-b})\right.\\
-  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right]
+  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right].
 \end{multline}
@@
   \label{eq:43}
-\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}=0
+\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}=0.
 \end{equation}
@@
       n-b n-c n}+e^{-a n-b n}+e^{-a n-c n}+e^{-b n-c n} - e^{-a n}-e^{-b n}-e^{-c n}\right)=\\
-  =\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)
+  =\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right).
 %%  =\frac{1}{6} \left(-\log \left(1-e^{-a-b-c}\right)+\log
@@
    z+2\right)+4
-   z+2\right)}{\left(e^z-1\right)^4}=e^{-z}\xi(z)
+   z+2\right)}{\left(e^z-1\right)^4}=e^{-z}\xi(z).
 \end{equation}
@@
   \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(n\varepsilon) =
-  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(0)+  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}   
+  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(0)+  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}.
 \end{equation}
@@
   \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}Q(n\varepsilon)=\varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}\approx
-  \int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz=\int_{0}^{\infty}e^{-z}Q(z)\dz
+  \int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz=\int_{0}^{\infty}e^{-z}Q(z)\dz.
 \end{equation}
@@
   \varepsilon^{2}}\approx-\frac{1}{2(ab+bc+ca)}
-\left[\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{6}\ln \varepsilon+\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz\right]
+\left[\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{6}\ln \varepsilon+\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz\right].
 \end{equation}
@@
     \Li_{3}(e^{-a-b})\right.\\
-  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right]
+  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right],
 \end{multline}
-
 \begin{equation}
@@
 The last term $f_{3}$ depends only on the shape of the domain through $a,b,c$ with a universal
-contribution that is equal to the integral of a function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$. We conjecture
-this constant will appear even for a different choice of Kasteleyn weighting, due to the treatment
-of logarithmic divergency. In the future work we will consider coordinate dependent values of $q$
-and more complex geometries, as was done in the paper \cite{okounkov2007random}, to check this
-suggestion.
+contribution that is equal to the integral of a function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$. In the
+next sections we show that this constant appear even for a different choice of Kasteleyn weighting,
+due to the treatment of logarithmic divergency. In the last section work we consider coordinate
+dependent values of $q$ and more complex geometries can be treated similarly as was done in the
+paper \cite{okounkov2007random}.
 
@@
   \label{eq:2}
-  \int_{0}^{\infty}e^{-z}Q(z)\dz=\int_{0}^{\infty}e^{-z}\frac{\xi(z)-\xi(0)}{z} dz = -0.080842%0.08084228607897521
+  \int_{0}^{\infty}e^{-z}Q(z)\dz=\int_{0}^{\infty}e^{-z}\frac{\xi(z)-\xi(0)}{z} dz = -0.080842.%0.08084228607897521
 \end{equation}
@@
   \label{eq:3}
-  Z[M,N,q]=\prod_{i=1}^{M}\prod_{j=1}^{N}\frac{1}{1-q^{i+j-1}}
+  Z[M,N,q]=\prod_{i=1}^{M}\prod_{j=1}^{N}\frac{1}{1-q^{i+j-1}}.
 \end{equation}
@@
   =\sum_{n=1}^{\infty}\frac{\varepsilon^{2}}{ab}\frac{1}{n}e^{-n\varepsilon}\left(\sum_{i=1}^{M}e^{-n\varepsilon(i-1)}\right)
-  \left(\sum_{j=1}^{N}e^{-n\varepsilon(j-1)}\right)
+  \left(\sum_{j=1}^{N}e^{-n\varepsilon(j-1)}\right).
 \end{multline}
@@
   f_{0}=\frac{1}{ab}\left[\Li_{3}(e^{-a})+\Li_{3}(e^{-b})-
-    \Li_{3}(e^{-a-b})-\zeta(3)\right]
+    \Li_{3}(e^{-a-b})-\zeta(3)\right],
 \end{equation}
@@
   \label{eq:8}
-  f_{1}=0
+  f_{1}=0,
 \end{equation}
@@
   \label{eq:9}
-  f_{2}=\frac{1}{ab}\frac{1}{12}
+  f_{2}=\frac{1}{ab}\frac{1}{12},
 \end{equation}
@@
   \label{eq:13}
-  Z=\prod_{i=0}^{N-1}\prod_{j=0}^{M-1} \frac{1}{1-q_{N-M}^{-1}\left(\prod_{k=0}^{i}q_{N-M-k}\right)\left(\prod_{l=0}^{j}q_{N-M+l}\right)}
+  Z=\prod_{i=0}^{N-1}\prod_{j=0}^{M-1} \frac{1}{1-q_{N-M}^{-1}\left(\prod_{k=0}^{i}q_{N-M-k}\right)\left(\prod_{l=0}^{j}q_{N-M+l}\right)}.
 \end{equation}
@@
   \left(1-e^{\varepsilon \varphi(b-a)}e^{-\varepsilon\sum_{k=0}^{i}\varphi\left(b-a-k\varepsilon\right)}
-    e^{-\varepsilon\sum_{l=0}^{j}\varphi\left(b-a+l\varepsilon\right)} \right)
+    e^{-\varepsilon\sum_{l=0}^{j}\varphi\left(b-a+l\varepsilon\right)} \right).
 \end{equation}
@@
   =-\frac{1}{ab}\int_{0}^{b}\int_{0}^{a}\ln
-  \left(1-e^{-\int_{-y}^{z}\varphi\left(b-a+x\right)\dx} \right)\dz\dy
+  \left(1-e^{-\int_{-y}^{z}\varphi\left(b-a+x\right)\dx} \right)\dz\dy.
 \end{multline}
@@
     \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}f\left(\varepsilon\sum_{k=-i}^{j}\varphi(k\varepsilon)\right)=
-    \int_{0}^{a}\int_{0}^{b}f\left(\int_{-y}^{z}\varphi(x)\dx\right)\dz\;\dy+o(\varepsilon)
+    \int_{0}^{a}\int_{0}^{b}f\left(\int_{-y}^{z}\varphi(x)\dx\right)\dz\;\dy+o(\varepsilon).
   \end{equation}
@@
     \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}f\left(\varepsilon\sum_{k=-i}^{j}\varphi(k\varepsilon)\right)=
-    \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}f\left(\int_{-i\varepsilon}^{j\varepsilon}\varphi(x)\dx+\frac{\varepsilon}{2}\left(\varphi(j\varepsilon)-\varphi(-i\varepsilon)\right)+\mathcal{O}(\varepsilon^{2})\right)\dz\dy
+    \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}f\left(\int_{-i\varepsilon}^{j\varepsilon}\varphi(x)\dx+\frac{\varepsilon}{2}\left(\varphi(j\varepsilon)-\varphi(-i\varepsilon)\right)+\mathcal{O}(\varepsilon^{2})\right).
   \end{equation}
@@
   \approx\sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\left\{\varepsilon^{2}G\left(i\varepsilon,j\varepsilon\right)+
-    \frac{\varepsilon^{3}}{2}\left((\partial_{y}+\partial_{z})G\right)(i\varepsilon,j\varepsilon)\right\}+o(\varepsilon^{2})
+    \frac{\varepsilon^{3}}{2}\left((\partial_{y}+\partial_{z})G\right)(i\varepsilon,j\varepsilon)\right\}+o(\varepsilon^{2}).
 \end{equation}
@@
   \label{eq:78}
-  G_{\varepsilon}(y,z)=f\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right)
+  G_{\varepsilon}(y,z)=f\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right).
 \end{equation}
@@
   \frac{\varepsilon^{3}}{2}
-  \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\left((\partial_{y}+\partial_{z})G_{\varepsilon}\right)(i\varepsilon,j\varepsilon)+o(\varepsilon^{3}) 
+  \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\left((\partial_{y}+\partial_{z})G_{\varepsilon}\right)(i\varepsilon,j\varepsilon)+o(\varepsilon^{3}).
 \end{equation}
@@
   \int_{0}^{a}\int_{0}^{b}G_{\varepsilon}(y,z)\dz\;\dy=
-  \int_{0}^{a}\int_{0}^{b}G_{0}(y,z)\dz\;\dy+\int_{0}^{a}\int_{0}^{b}\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))\cdot f'\left(\int_{-y}^{z}\varphi(x)\dx\right)\dz\;\dy+o(\varepsilon)
+  \int_{0}^{a}\int_{0}^{b}G_{0}(y,z)\dz\;\dy+\int_{0}^{a}\int_{0}^{b}\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))\cdot
+  f'\left(\int_{-y}^{z}\varphi(x)\dx\right)\dz\;\dy+o(\varepsilon). 
 \end{equation}
@@
   \partial_{z}G_{\varepsilon}(y,z)=f'\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right)\varphi(z)+o(\varepsilon)\\ 
-  \partial_{y}G_{\varepsilon}(y,z)=-f'\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right)\varphi(-y)+o(\varepsilon)
+  \partial_{y}G_{\varepsilon}(y,z)=-f'\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right)\varphi(-y)+o(\varepsilon).
 \end{eqnarray}
@@
   \label{eq:82}
-  f_{1}=0  
+  f_{1}=0.
 \end{equation}
@@
      \varphi(b-a)}\sum_{i=0}^{N-1}\sum_{j=0}^{M-1} e^{-n\varepsilon\sum_{k=0}^{i}\varphi\left(b-a-k\varepsilon\right)}
-    e^{-n\varepsilon\sum_{l=0}^{j}\varphi\left(b-a+l\varepsilon\right)}
+    e^{-n\varepsilon\sum_{l=0}^{j}\varphi\left(b-a+l\varepsilon\right)}.
 \end{equation}
@@
   \label{eq:52}
-  r_{\mp}(i\varepsilon)\equiv\varepsilon\sum_{k=1}^{i}\varphi(b-a\mp k\varepsilon)
+  r_{\mp}(i\varepsilon)\equiv\varepsilon\sum_{k=1}^{i}\varphi(b-a\mp k\varepsilon).
 \end{equation}
@@
   r_{\mp}(x)\approx\int_{0}^{x}\varphi(b-a\mp y) \dy +\frac{\varepsilon}{2}\left(\varphi(b-a\mp
-    x)-\varphi(b-a)\right)\mp \frac{\varepsilon^{2}}{12}\left(\varphi'(b-a\mp x)-\varphi'(b-a)\right)
+    x)-\varphi(b-a)\right)\mp \frac{\varepsilon^{2}}{12}\left(\varphi'(b-a\mp x)-\varphi'(b-a)\right).
 \end{equation}
@@
 \cdot\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon)\right]=\\
-=f^{(0)}+f^{+}+f^{-}+f^{\times}
+=f^{(0)}+f^{+}+f^{-}+f^{\times}.
 \end{multline}
@@
     \varphi(b-a)}\varepsilon^{2}\frac{\left(1-e^{-n b r_{-}'(0)}\right)\left(1-e^{-n a
-        r_{+}'(0)}\right)}{\left(1-e^{-n\varepsilon r_{-}'(0)}\right)\left(1-e^{-n\varepsilon r_{+}'(0)}\right)}
+        r_{+}'(0)}\right)}{\left(1-e^{-n\varepsilon r_{-}'(0)}\right)\left(1-e^{-n\varepsilon r_{+}'(0)}\right)}.
 \end{equation}
@@
   \label{eq:57}
-  H_{n}(\varepsilon)=\left(1-e^{-n b r_{-}'(0)}\right)\left(1-e^{-n a r_{+}'(0)}\right)
+  H_{n}(\varepsilon)=\left(1-e^{-n b r_{-}'(0)}\right)\left(1-e^{-n a r_{+}'(0)}\right).
 \end{equation}
@@
   \label{eq:58}
-  r_{\mp}'(0)=\varphi(b-a)\mp \frac{\varepsilon}{2} \varphi'(b-a)+\frac{\varepsilon^{2}}{12} \varphi''(b-a)+\mathcal{O}(\varepsilon^{3})
+  r_{\mp}'(0)=\varphi(b-a)\mp \frac{\varepsilon}{2} \varphi'(b-a)+\frac{\varepsilon^{2}}{12} \varphi''(b-a)+\mathcal{O}(\varepsilon^{3}).
 \end{equation}
@@
   \alpha_{\mp}(\varepsilon)=\mp
-  \frac{\varepsilon}{2}\frac{\varphi'(b-a)}{\varphi(b-a)}+\frac{\varepsilon^{2}}{12} \frac{\varphi''(b-a)}{\varphi(b-a)}+\mathcal{O}(\varepsilon^{3})
+  \frac{\varepsilon}{2}\frac{\varphi'(b-a)}{\varphi(b-a)}+\frac{\varepsilon^{2}}{12} \frac{\varphi''(b-a)}{\varphi(b-a)}+\mathcal{O}(\varepsilon^{3}).
 \end{equation}
@@
   \label{eq:61}
-  f^{(0)}=\frac{1}{ab}\sum_{n=1}^{\infty} \frac{\tilde{\chi}\left(n\varepsilon
+  f^{(0)}=\frac{1}{ab}\sum_{n=1}^{\infty} \frac{\tilde{\chi}_{n}\left(n\varepsilon
       \varphi(b-a),\varepsilon\right) }{n^{3}\varphi(b-a)^{2}},
 \end{equation}
-where $\tilde{\chi}(z,\varepsilon)$  is defined as
+where $\tilde{\chi}_{n}(z,\varepsilon)$  is defined as
 \begin{equation}
   \label{eq:62}
-  \tilde{\chi}(z,\varepsilon)\equiv \frac{z^{2} e^{-z}
+  \tilde{\chi}_{n}(z,\varepsilon)\equiv \frac{z^{2} e^{-z}
     H_{n}(\varepsilon)}{\left(1-e^{-z\left(1+\alpha_{-}(\varepsilon)\right)}\right)
-    \left(1-e^{-z\left(1+\alpha_{+}(\varepsilon)\right)}\right)} 
-\end{equation}
-It is important to include $H_{n}(\varepsilon)$ since $H_{n}(\varepsilon)$ contains decaying
+    \left(1-e^{-z\left(1+\alpha_{+}(\varepsilon)\right)}\right)}.
+\end{equation}
+It is important to include $H_{n}(\varepsilon)$, since $H_{n}(\varepsilon)$ contains decaying
 exponents in $n$.
@@
   \frac{1}{n^{3}}\left[
-    \left.\tilde{\chi}''_{\varepsilon\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+
-    2n\varphi(b-a)\left.\tilde{\chi}''_{z\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+\right.\\\left.
-      n^{2}\left(\varphi(b-a)\right)^{2}\tilde{\chi}''_{zz}\left(n\varepsilon\varphi(b-a),\varepsilon\right)  \right]+
+    \left.\tilde{\chi}''_{n,\varepsilon\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+
+    2n\varphi(b-a)\left.\tilde{\chi}''_{n,z\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+\right.\\\left.
+      n^{2}\left(\varphi(b-a)\right)^{2}\tilde{\chi}''_{n,zz}\left(n\varepsilon\varphi(b-a),\varepsilon\right)  \right]+
     \mathcal{O}(\varepsilon \ln \varepsilon)=\\
     =\frac{1}{ab\varphi(b-a)}\left[\sum_{n=1}^{\infty} \frac{1}{n^{3}}
-      \tilde{\chi}''_{\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\frac{1}{n^{2}}\tilde{\chi}''_{z\varepsilon}(0,0)\right]+
+      \tilde{\chi}''_{n,\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\frac{1}{n^{2}}\tilde{\chi}''_{n,z\varepsilon}(0,0)\right]+
     \\
@@
   \label{eq:65}
-  H_{n}=\left(1-e^{-nb\varphi(b-a)}\right) \left(1-e^{-na\varphi(b-a)}\right)
+  H_{n}=\left(1-e^{-nb\varphi(b-a)}\right) \left(1-e^{-na\varphi(b-a)}\right).
 \end{equation}
@@
 f^{(0)}_{3}=\frac{1}{ab\varphi(b-a)}\left[\sum_{n=1}^{\infty} \frac{1}{n^{3}}
-  \tilde{\chi}''_{\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\frac{1}{n^{2}}\tilde{\chi}''_{z\varepsilon}(0,0)\right],
+  \tilde{\chi}''_{n,\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\frac{1}{n^{2}}\tilde{\chi}''_{n,z\varepsilon}(0,0)\right],
 \end{equation}
@@
   f^{+}=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n} e^{-n\varepsilon\varphi(b-a)} \varepsilon
-  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon)
+  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon).
 \end{equation}
@@
   \frac{\varepsilon^{2}}{12}\left(\Psi^{+'}_{n}(a)-\Psi^{+}_{n}(0)\right)+
-  \mathcal{O}\left(\varepsilon^{m}\Psi^{+(m-1)}_{n}\right)
-\end{equation}
-Since
+  \mathcal{O}\left(\varepsilon^{m}\Psi^{+(m-1)}_{n}\right).
+\end{equation}
+Since $r(x)$ is an analytic function and $r(0)=0$ we can write $r(x)=xr'(0)+x^{2}\zeta(x)$, so 
 \begin{equation}
@@
 \end{equation}
-we see that $\Psi_{n}(0)=0$ and $\Psi_{n}'(0)=0$.
+and we see that $\Psi_{n}(0)=0$ and $\Psi_{n}'(0)=0$.
 Than in the limit $n\to\infty$ we have
@@
   \int_{0}^{c}\Psi_{n}(x)
-  \dx \xrightarrow[n\to\infty]{}\int_{0}^{c}e^{-nxr'(0)}\left(-nx^{2}\zeta(x)+\dots\right)\sim \frac{1}{n^{2}}
+  \dx \xrightarrow[n\to\infty]{}\int_{0}^{c}e^{-nxr'(0)}\left(-nx^{2}\zeta(x)+\dots\right)\dx\sim \frac{1}{n^{2}}.
 \end{equation}
@@
   \sum_{n=1}^{\infty} \frac{1}{n^{4}} e^{-n\varepsilon\varphi(b-a)}
-  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}} (\varepsilon n )^{m+1}
+  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}} (\varepsilon n )^{m+1}.
 \end{equation}
@@
   e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}
-  \left(\varepsilon\int_{0}^{a} \Psi_{n}^{+}(x) \dx -\varepsilon^{2} \Psi_{n}^{+}(a) +\varepsilon^{3}\Psi^{+'}_{n}(0)\right)\right|_{\varepsilon=0}
+  \varepsilon\left(\int_{0}^{a} \Psi_{n}^{+}(x) \dx -\varepsilon \Psi_{n}^{+}(a) +\varepsilon^{2}\Psi^{+'}_{n}(0)\right)\right|_{\varepsilon=0}.
 \end{equation}
@@
   e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nar_{+}'(0)}}{1-e^{-n\varepsilon r_{+}'(0)}}
- \left(\varepsilon\int_{0}^{b} \Psi_{n}^{-}(x) \dx -\varepsilon^{2} \Psi_{n}^{-}(a) +\varepsilon^{3}\Psi^{-'}_{n}(0)\right)\right|_{\varepsilon=0}
-\end{equation}
-At last, we need to consider $f^{\times}$. In this term we can just take a limit $\varepsilon\to 0$
-and obtain
+ \varepsilon\left(\int_{0}^{b} \Psi_{n}^{-}(x) \dx -\varepsilon \Psi_{n}^{-}(a) +\varepsilon^{2}\Psi^{-'}_{n}(0)\right)\right|_{\varepsilon=0}.
+\end{equation}
+At last, we need to consider
+$f^{\times}=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n}e^{-n\varepsilon\varphi(b-a)}\varepsilon\sum_{i=0}^{N-1}\Psi_{n}^{-}(i\varepsilon)
+\sum_{j=0}^{M-1}\Psi_{n}^{+}(j\varepsilon)$. Analyzing the contributions of the derivatives
+$\Psi_{n}^{(m)}(0)$, similarly to the discussion before the formula \eqref{eq:70}, we see that
+$\varepsilon^{m}\Psi_{n}^{(m-1)}(0)\sim \frac{1}{n^{2}}$. Thus
+\[\sum_{n=1}^{\infty}\frac{1}{n}e^{-n\varepsilon\varphi(b-a)}\frac{1}{n^{2}}\varepsilon^{m}\Psi_{n}^{(m-1)}(0)\sim
+\sum_{n=1}^{\infty}\frac{1}{n^{5}}e^{-n\varepsilon\varphi(b-a)}(\varepsilon n)^{m},\] and these terms
+give zero contribution after the derivative $\left(\frac{d}{d\varepsilon}\right)^{2}$ for
+$\varepsilon\to 0 $ and $m\geq 3$. The same holds for all the contributions with the derivatives of
+$\Psi$ in the both sums. In the terms with $m<3$ we can just take a double derivative over
+$\varepsilon$ and limit $\varepsilon\to 0$ and obtain
 \begin{multline}
@@
 \cdot\left.\left(\int_{0}^{a}\Psi^{+}_{n}(x)\dx-\frac{\varepsilon}{2}\Psi^{+}_{n}(a)+
-    \frac{\varepsilon^{2}}{12}\Psi^{+}_{n}(a)\right)\right|_{\varepsilon=0} 
+    \frac{\varepsilon^{2}}{12}\Psi^{+}_{n}(a)\right)\right|_{\varepsilon=0}.
 \end{multline}
@@
   f_{0}= -\frac{1}{ab}\int_{0}^{b}\int_{0}^{a}\ln
-  \left(1-e^{-\int_{-y}^{z}\varphi\left(b-a+x\right)\dx} \right)\dz\dy
+  \left(1-e^{-\int_{-y}^{z}\varphi\left(b-a+x\right)\dx} \right)\dz\dy,
 \end{equation}
@@
   \label{eq:88}
-  f_{1}=0
+  f_{1}=0,
 \end{equation}
@@
 \end{equation}
+and
 \begin{multline}
@@
 \end{multline}
-Here in the first line we have the contributions that depend on the choice of the weight function
+where in the first line we have the contributions that depend on the choice of the weight function
 $\varphi$ and in the second line -- the universal contribution that appears in the case
@@
  \hline
- analytic & $\frac{1}{3}(2+\cos(z))$ & 1,3 & $0.472206688$ & $0$ & $1$&$-0.043883000$\\
- numeric & $\frac{1}{3}(2+\cos(z))$ & 1,3 &  $0.472206693$ & $0.000000730$ & $1.000730689$&$-0.043827958$\\
+ analytic & $(2+\cos(z))/3$ & 1,3 & $0.472206688$ & $0$ & $1$&$-0.043883000$\\
+ numeric & $(2+\cos(z))/3$ & 1,3 &  $0.472206693$ & $0.000000730$ & $1.000730689$&$-0.043827958$\\
   \hline
- analytic & $\frac{1}{3}(2+\cos(z))$ & 2,3 & $0.235922467$ & $0$ & $1$&$-0.030398000$\\
- numeric & $\frac{1}{3}(2+\cos(z))$ & 2,3 &  $0.235922467$ & $0.000000044$ & $1.000088528$&$-0.030394694$\\
+ analytic & $(2+\cos(z))/3$ & 2,3 & $0.235922467$ & $0$ & $1$&$-0.030398000$\\
+ numeric & $(2+\cos(z))/3$ & 2,3 &  $0.235922467$ & $0.000000044$ & $1.000088528$&$-0.030394694$\\
 \hline                                                
@@
 We are grateful to professor Nikolai Reshetikhin for his attention to this work. We thank Pavel Belov
-for useful discussions and general support.
+for useful discussions and general support. We thank Mikhail Vyazovsky for pointing out a mistake in
+the first version of the paper.
 

### 2019-08-03 AffineLieAlgebras/MQFT2018/paper.tex
New version in the arXiv

@@
 \usepackage{amsmath,amssymb,amsthm,amsfonts}
+%\synctex=1
 
@@
 
-We consider a particular case of the dimer model on a hexagonal domain of hexagonal lattice, that
-can be seen as a ``pile of cubes in the corner of the box''. The energy of configuration is the
-total number of cubes. For this particular case we use an exact combinatorial formula for the
-partition function to derive the expressions for scaling limit of free energy and first three terms
-of the finite-size corrections. We show that the first term is identically zero. The second term
-which encapsulates logarithmic dependence on the mesh size is connected with the central charge of
-the effective field theory and with the geometry of limit shape. The third term is
-geometry-dependent and is written explicitly in terms of elementary functions.
-
-We then consider the box of infinite height and the case of coordinate-dependent Boltzmann weights.
-In these cases we are also able to write explicit expressions for finite-size corrections. We
-demonstrate the universality of the logarithmic term.
-
-Our results are supported by numeric checks and Monte-Carlo simulations presented in our previous
-publication \cite{1742-6596-1135-1-012024}.
+We consider a particular case of the dimer model on a hexagonal domain
+of hexagonal lattice, that can be seen as a ``pile of cubes in the
+corner of the box''. The energy of configuration is the total number
+of cubes. For this particular case we use an exact combinatorial
+formula for the partition function to derive the expressions for
+scaling limit of free energy and first three terms of the finite-size
+corrections. We show that the first term is identically zero. The
+second term which encapsulates logarithmic dependence on the mesh size
+is connected with the central charge of the effective field theory and
+with the geometry of limit shape. The third term has a
+geometry-dependent contribution that is written explicitly in terms of
+elementary functions and a universal contribution, which is constant
+in all the cases that we consider.
+
+We then consider the box of infinite height and the case of
+coordinate-dependent Boltzmann weights. In these cases we are also
+able to write explicit expressions for finite-size corrections. We
+demonstrate the universality of the logarithmic term and the constant
+contribution to the third term.
+
+Our results are supported by numeric checks and Monte-Carlo
+simulations presented in our previous publication
+\cite{1742-6596-1135-1-012024}.
 
@@
 number of negative edge weights and each face with 2 mod 4 edges has an even number of of negative
-edge weights. Then the signs of the edge weights form a so-called ``Kasteleyn orientation''on graph,
+edge weights. Then the signs of the edge weights form a so-called ``Kasteleyn orientation'' on graph,
 the weighting is called ``Kasteleyn weighting'' \cite{kenyon2001dominos,kenyon2009lectures}.
@@
 \end{equation*}
-We set Boltzman constant equal to 1 and choose system of units in such a way that there is no
+We set Boltzmann constant equal to 1 and choose system of units in such a way that there is no
 coupling constant in the expression for energy. Then the partition function is
@@
 
-\section{Physical meaning of the expansion coefficients}
+\section{Limit shape and physical meaning of the expansion coefficients}
 \label{sec:accur-expans-phys}
@@
 
-In the scaling limit $\varepsilon\to 0$ so called ``limit shape phenomenon''~\cite{1998math......1068J,cohn1998shape}
-appears in the dimer model. The areas around the corners of the domain are ``frozen'' with height
-function values being fixed. An analytical ``Arctic curve'' delimits frozen regions from the region
-where the behavior is described by the effective free field theory
-\cite{kenyon2009lectures,kenyon2008height,kenyon2006dimers}.
-
-The behavior (\ref{eq:26}) of the logarithm of the partition function is generic in two-dimensional
+The dimers in the scaling limit are in general described by a
+free-fermion theory \cite{dijkgraaf2009dimer}, but on a hexagonal
+lattice (and on the graphs that admit Kasteleyn orientation) the model
+is reformulated in terms of height function, that can be seen as a
+bosonization of the theory \cite{gogolin2004bosonization}.
+
+In the scaling limit $\varepsilon\to 0$ so called ``limit shape
+phenomenon''~\cite{1998math......1068J,cohn1998shape} appears in the
+dimer model. The areas around the corners of the domain are ``frozen''
+with height function values being fixed. An analytical ``Arctic
+curve'' delimits frozen regions from the region where the behavior is
+described by the effective free field theory
+\cite{kenyon2009lectures,kenyon2008height,kenyon2006dimers}. Moreover,
+the height function in the scaling limit tends to certain analytical
+surface and fluctuations around this ``limit shape'' are described by
+a gaussian free field theory in a curved background of ``limit
+shape''. A confomal map can be used to send the internal region of the
+``Arctic curve'' onto the upper half-plane.
+
+The scaling behavior (\ref{eq:26}) of the logarithm of the partition function is generic in two-dimensional
 models \cite{cardy1988finite}.
 
-First two terms $f_{0}$ and $f_{1}$ are interpreted as a bulk and
-boundary free energies in the corresponding field theory. Since we have $f_{1}=0$, we can conclude
-that boundary tension is zero.
-The value of the first term $f_{0}$ can be rewritten using polylogarithm functions as
+Thus we can interpret first two terms $f_{0}$ and $f_{1}$ as a bulk
+and boundary free energies in the corresponding field theory. The term
+$f_1$ corresponds to the contribution of the ``limit shape''. Since we
+have a deterministic frozen boundary, we naturally have $f_{1}=0$.
+%The value of the first term $f_{0}$ can be rewritten using polylogarithm functions as
 
@@
 \cite{cardy1988finite} and should appear in all two-dimensional theories with boundary. In the paper
-\cite{cardy1988finite} it was argued that on a manifold of a characteristic length $L$ with a smooth
+\cite{cardy1988finite} Cardy and Peschel argued that on a smooth manifold of a characteristic length $L$ with a smooth
 boundary such a term must have the following form:
@@
 \end{equation}
-where ${\bf c}$ is central charge of the effective field theory and $\chi$ is the Euler characteristic of
-the manifold
-\begin{equation}
-  \label{eq:32}
-  \chi=2-2 h-b,
-\end{equation}
-where $h$ is the number of handles and $b$ is the number of boundaries.
-
-Since the non-frozen domain is delimited by a smooth boundary, we have $\chi=1$ and we interpret
-$2(ab+bc+ca)$ as a volume of the domain, thus
+where ${\bf c}$ is central charge of the effective field theory and
+$\chi$ is the Euler characteristic of the manifold $\chi=2-2 h-b$,
+where $h$ is the number of handles and $b$ is the number of
+boundaries. Naive use of the formula \eqref{eq:31} with our result
+$\delta F=\frac{1}{12}$ would give ${\bf c}=\frac{1}{2}$, but it is
+not correct, since we need to consider the field theory in the curved
+background.
+
+In the case of a corner singularity on the boundary with the angle
+$\Theta$ the logarithmic contribution to the free energy is changed to
+\begin{equation}
+  \label{eq:86}
+  \delta F = \frac{{\bf c}}{24}\left(\frac{\Theta}{\pi}-\frac{\pi}{\Theta}\right) \ln L.
+\end{equation}
+This formula was recently used by N. Allegra \cite{allegra2015exact} to show that the central charge
+in the dimer model on the square lattice with a corner monomer is ${\bf c}=1$, contrary to some
+previous claims of ${\bf c}=-2$.
+
+In the case of manifold with conic singularity with the semi-angle
+$\Theta$, the logarithmic contribution presented in \cite{cardy1988finite} is:
+\begin{equation}
+  \label{eq:91}
+  \delta F = \frac{{\bf c}}{24}\left(\frac{\Theta}{\pi}-\frac{4\pi}{\Theta}\right) \ln L.
+\end{equation}
+
+In our case we interpret $2(ab+bc+ca)$ as a volume of the domain, thus
 \begin{equation}
   \label{eq:33}
-  \delta F = \left(2(ab+bc+ca)\right) f_{2}\ln\varepsilon,
-\end{equation}
-which together with formula \eqref{eq:30} suggests the value of central charge
-${\bf c}=\frac{1}{2}$. This value is in agreement with the identification of the dimer model with
-free fermions in the paper \cite{dijkgraaf2009dimer}.
-
-The last term $f_{3}$ depends only on the shape of the domain through $a,b,c$ with a universal
-contribution that is equal to the integral of a function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$. In the
-next sections we show that this constant appear even for a different choice of Kasteleyn weighting,
-due to the treatment of logarithmic divergency. In the last section work we consider coordinate
-dependent values of $q$ and more complex geometries can be treated similarly as was done in the
-paper \cite{okounkov2007random}.
+  \delta F = \left(2(ab+bc+ca)\right) f_{2}\ln\varepsilon.
+\end{equation}
+
+Using Cardy-Peschel formulas, presented above, $\delta F$ can be
+computed from value of the central charge for Gaussian free field
+${\bf c}=1$, the curvature of metric, induced by the limit shape and
+conformal map from the internal region of the ``Arctic curve'' to the
+upper half-plane. Such a computation can be used to check our result
+on $f_2$ but is quite lengthy and will be presented in a separate
+publication.
+
+The last term $f_{3}$ depends only on the shape of the domain through
+$a,b,c$ with a universal contribution that is equal to the integral of
+a function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$. In the next sections we
+show that this constant appears due to the treatment of logarithmic
+divergency even for the coordinate-dependent Boltzmann weights.
 
@@
 take the limit $\varepsilon\to 0$. Doing so, we obtain
-\begin{equation}
+\begin{multline}
   \label{eq:71}
-  f^{+}_{3}\equiv\left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{+}\right|_{\varepsilon=0} =
+  f^{+}_{3}\equiv\left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{+}\right|_{\varepsilon=0} =\\
   \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
@@
   \varepsilon\left(\int_{0}^{a} \Psi_{n}^{+}(x) \dx -\varepsilon \Psi_{n}^{+}(a) +\varepsilon^{2}\Psi^{+'}_{n}(0)\right)\right|_{\varepsilon=0}.
-\end{equation}
+\end{multline}
 Note that $\frac{\varepsilon}{1-\exp(-n\varepsilon r'_{-}(0))}$ is analytic in $\varepsilon$. 
@@
 The contribution of $f^{-}$ is computed in exactly the same way:
-\begin{equation}
+\begin{multline}
   \label{eq:72}
-   f^{-}_{3}\equiv \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{-}\right|_{\varepsilon=0} =
+   f^{-}_{3}\equiv \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{-}\right|_{\varepsilon=0} =\\
   \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
@@
  \varepsilon\left(\int_{0}^{b} \Psi_{n}^{-}(x) \dx -\varepsilon \Psi_{n}^{-}(a) +\varepsilon^{2}\Psi^{-'}_{n}(0)\right)\right|_{\varepsilon=0}.
-\end{equation}
+\end{multline}
 At last, we need to consider
@@
 
-In the present paper we computed the asymptotic expansion of the free energy in the dimer model on a
-hexagonal domain of the hexagonal lattice. We've discussed the physical meaning of the expansion
-coefficients and argued that our results support the identification of the scaling behavior of the
-dimer model with the free-fermion field theory.
-
-In further work we will study the connection of the expansion coefficients with the spectral
-properties of Dirac operator on the non-frozen domain and study the universality of our results. We
-will also further discuss the description of the model by boundary conformal field theory.
+In the present paper we computed the asymptotic expansion of the free
+energy in the dimer model on a hexagonal domain of the hexagonal
+lattice, on a hexagon with a side of infinite length and in the model
+with coordinate-dependent Boltzmann weights. We presented numerical
+results supporting our computations. We've discussed the physical
+meaning of the expansion coefficients and argued that our results
+support the identification of the scaling behavior of the dimer model
+with the Gaussian free field theory.
+
+In further work we will study the connection of the expansion
+coefficients with the spectral properties of Dirac operator on the
+non-frozen domain and study the universality of our results. We will
+also present the computations of the logarithmic correction to the free
+energy from the geometry of the ``limit shape''.
 
@@
 \label{sec:acknowledgements}
-We are grateful to professor Nikolai Reshetikhin for his attention to this work. We thank Pavel Belov
-for useful discussions and general support. We thank Mikhail Vyazovsky for pointing out a mistake in
-the first version of the paper.
-
-We thank the organizers and participants of the conference MQFT-2018 for the opportunity
-to present our results and useful discussions.
+We are grateful to professor Nikolai Reshetikhin for his attention to
+this work. We thank Pavel Belov for useful discussions and general
+support. We thank Mikhail Vyazovsky for pointing out a mistake in the
+first version of the paper. We thank Istvan Prause for the reference
+\cite{allegra2015exact} and Vadim Gorin for a discussion on geometry
+of the limit shape.
+
+We thank the organizers and participants of the conference MQFT-2018
+for the opportunity to present our results and useful discussions.
 

### 2019-08-03 AffineLieAlgebras/MQFT2018/paper.tex
Abstract fix

@@
 \begin{abstract}
-  We consider dimer model on a hexagonal lattice. This model can be seen as a ``pile of cubes in the
-  corner''. The energy of configuration is given by the volume of the pile and the partition
-  function is computed by the classical MacMahon formula or, more formally, by the determinant of
-  Kasteleyn matrix. We use the expression for the partition function to derive the scaling behavior
-  of free energy in the limit of lattice mesh tending to zero and temperature tending to infinity.
-  We discuss the universality and physical meaning of expansion coefficients.
+  We consider dimer model on a hexagonal lattice. This model can be
+  seen as a ``pile of cubes in the box''. The energy of configuration
+  is given by the volume of the pile and the partition function is
+  computed by the classical MacMahon formula or, more formally, by the
+  determinant of Kasteleyn matrix. We use the expression for the
+  partition function to derive the scaling behavior of free energy in
+  the limit of lattice mesh tending to zero and temperature tending to
+  infinity. We consider the cases of finite hexagonal domain, of
+  infinite height box and coordinate-dependent Boltzmann weights. We
+  obtain asymptotic expansion of free energy and discuss the
+  universality and physical meaning of the expansion coefficients.
 \end{abstract}
@@
 \begin{figure}[htbp]
-\center{\scalebox{0.4}{\includegraphics{loz.eps}}}
+\center{\scalebox{0.4}{\includegraphics{loz}}}
 \caption{\label{dhf}A configuration of dimers on the hexagonal lattice and a corresponding picture

### 2019-12-01 AffineLieAlgebras/MQFT2018/paper.tex
misprint fixed, version rejected in JPhysA

@@
 $f_{1}=\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}$,
-$\frac{\partial^{2} f}{\partial \varepsilon^{2}}=f_{2}(2\ln\varepsilon+3)+f_{3}$.
+$\frac{\partial^{2} f}{\partial \varepsilon^{2}}=f_{2}(2\ln\varepsilon+3)+2f_{3}$.
 

### 2019-12-10 AffineLieAlgebras/MQFT2018/paper.tex
Text on central charge in Introduction is rewritten

@@
 \cite{kenyon2002laplacian,kenyon2000asymptotic}. Scaling limit of dimer model is proven to be
-described by a Gaussian free-field theory \cite{kenyon2001dominos}, but finite-size corrections were
-not considered previously. These corrections are important to close the gap between numerical
-simulations and theoretical results.
+described by a Gaussian free-field theory \cite{kenyon2001dominos}, but finite-size corrections to
+the scaling of free energy were previously considered mostly in the absence of the limit shape
+\cite{Sh_Izmailian_2019,izmailian2016finite,izmailian2011dimer,izmailian2007non,izmailian2005logarithmic}.
+
+Finite size corrections are important to close the gap between numerical simulations and
+theoretical results. Moreover, they can be used to choose the proper field-theoretic description of
+the scaling limit. For example, logarithmic term is supposed to be universal and dependent on the
+value of central charge ${\bf c}$ of conformal field theory \cite{cardy1988finite}.
+
+Computation of finite-size corrections to the scaling of free energy in dimer model on a rectangular
+region on the square lattice led to a series of publications and even controversy about the proper CFT
+description of the scaling limit, when some publications claimed ${\bf c}=-2$, while others -- ${\bf c}=1$. 
+\cite{allegra2015exact,morin2016integrability,Sh_Izmailian_2019,izmailian2016finite,izmailian2005logarithmic}. 
+Note that in this case limit shape does not appear due to the choice of boundary conditions.
+
+The case of limit shape is even more complicated. While the fluctuations the limit shape can be
+computed from the variational minimization problem for surface tension and fluctuations are
+described by the Gaussian Free Field, the behavior on the boundary of the frozen region is not well
+understood. Surface tension becomes singular near the boundary of frozen domain, thus boundary
+contribution to the logarithmic correction to free energy scaling cannot be easily obtained from
+field-theoretic point of view. Because of this, the computation of finite size corrections from the
+exact solution of the model, especially of the logarithmic term, is very interesting.
 
@@
 This formula was recently used by N. Allegra \cite{allegra2015exact} to show that the central charge
-in the dimer model on the square lattice with a corner monomer is ${\bf c}=1$, contrary to some
-previous claims of ${\bf c}=-2$.
+in the height-function description of the dimer model on the square lattice with a corner monomer is
+${\bf c}=1$, contrary to some previous claims of ${\bf c}=-2$ \cite{morin2016integrability}.
 
@@
 
-Using Cardy-Peschel formulas, presented above, $\delta F$ can be
-computed from value of the central charge for Gaussian free field
-${\bf c}=1$, the curvature of metric, induced by the limit shape and
-conformal map from the internal region of the ``Arctic curve'' to the
-upper half-plane. Such a computation can be used to check our result
-on $f_2$ but is quite lengthy and will be presented in a separate
-publication.
+Using Cardy-Peschel formulas, presented above, it should be possible to compute $\delta F$ from
+value of the central charge for Gaussian free field ${\bf c}=1$, the curvature of metric, induced by
+the limit shape and conformal map from the internal region of the ``Arctic curve'' to the upper
+half-plane.
+But the metric is singular near the boundary of the internal region and singularities are not
+explicitly studied yet \cite{Astala}. Thus our result for value of $f_2$ should be useful in such a
+study, which we will attempt to do in a separate publication.
 
@@
 
-In the present paper we computed the asymptotic expansion of the free
-energy in the dimer model on a hexagonal domain of the hexagonal
-lattice, on a hexagon with a side of infinite length and in the model
-with coordinate-dependent Boltzmann weights. We presented numerical
-results supporting our computations. We've discussed the physical
-meaning of the expansion coefficients and argued that our results
-support the identification of the scaling behavior of the dimer model
-with the Gaussian free field theory.
-
-In further work we will study the connection of the expansion
-coefficients with the spectral properties of Dirac operator on the
-non-frozen domain and study the universality of our results. We will
-also present the computations of the logarithmic correction to the free
-energy from the geometry of the ``limit shape''.
+In the present paper we computed the asymptotic expansion of the free energy in the dimer model on a
+hexagonal domain of the hexagonal lattice, on a hexagon with a side of infinite length and in the
+model with coordinate-dependent Boltzmann weights. We presented numerical results supporting our
+computations. We've discussed the physical meaning of the expansion coefficients and argued that our
+results support the universal character of the logarithmic correction and can be used to study the
+behavior on the boundary of frozen region.
+
+In further work we will study the connection of the expansion coefficients with the spectral
+properties of Dirac operator on the non-frozen domain and study the universality of our results. We
+will also present the computations of the logarithmic correction to the free energy from the
+geometry of the ``limit shape''.
 

### 2020-01-04 AffineLieAlgebras/MQFT2018/paper.tex
Before applying Reshetikhin notes

@@
 
-Finite size corrections are important to close the gap between numerical simulations and
+Finite-size corrections are important to fill the gap between numerical simulations and
 theoretical results. Moreover, they can be used to choose the proper field-theoretic description of
-the scaling limit. For example, logarithmic term is supposed to be universal and dependent on the
-value of central charge ${\bf c}$ of conformal field theory \cite{cardy1988finite}.
-
-Computation of finite-size corrections to the scaling of free energy in dimer model on a rectangular
-region on the square lattice led to a series of publications and even controversy about the proper CFT
-description of the scaling limit, when some publications claimed ${\bf c}=-2$, while others -- ${\bf c}=1$. 
+the scaling limit. For example, the logarithmic term is supposed to be universal and dependent on a
+value of the central charge ${\bf c}$ of conformal field theory \cite{cardy1988finite}.
+
+Computation of finite-size corrections to the scaling of free energy in the dimer model on a rectangular
+region of the square lattice led to a series of publications and even controversy about the proper CFT
+description of the scaling limit. Some publications claimed ${\bf c}=-2$, while others -- ${\bf c}=1$ 
 \cite{allegra2015exact,morin2016integrability,Sh_Izmailian_2019,izmailian2016finite,izmailian2005logarithmic}. 
-Note that in this case limit shape does not appear due to the choice of boundary conditions.
-
-The case of limit shape is even more complicated. While the fluctuations the limit shape can be
-computed from the variational minimization problem for surface tension and fluctuations are
-described by the Gaussian Free Field, the behavior on the boundary of the frozen region is not well
-understood. Surface tension becomes singular near the boundary of frozen domain, thus boundary
-contribution to the logarithmic correction to free energy scaling cannot be easily obtained from
-field-theoretic point of view. Because of this, the computation of finite size corrections from the
-exact solution of the model, especially of the logarithmic term, is very interesting.
+Note that in this case the limit shape does not appear due to the choice of boundary conditions.
+
+The case of the limit shape is even more complicated. While the limit shape can be computed from the
+variational minimization problem for surface tension \cite{kenyon2007limit,kenyon2006dimers} and
+fluctuations are described by the Gaussian Free Field
+\cite{kenyon2001dominos,kenyon2008height,kenyon2009lectures}, the behavior on the boundary of the
+frozen region is not well understood. Surface tension becomes singular near the boundary of the frozen
+domain \cite{kenyon2007limit}, thus boundary contribution to the logarithmic correction to free
+energy scaling cannot be easily obtained from field-theoretic point of view. As a result, the
+computation of finite-size corrections from the exact solution of the model, especially of the
+logarithmic term, is important.
 
@@
 \begin{figure}[htbp]
-\center{\scalebox{0.4}{\includegraphics{loz}}}
+\center{\scalebox{0.4}{\includegraphics{my-loz}}}
 \caption{\label{dhf}A configuration of dimers on the hexagonal lattice and a corresponding picture
@@
 the limit shape and conformal map from the internal region of the ``Arctic curve'' to the upper
-half-plane.
-But the metric is singular near the boundary of the internal region and singularities are not
-explicitly studied yet \cite{Astala}. Thus our result for value of $f_2$ should be useful in such a
-study, which we will attempt to do in a separate publication.
+half-plane. But the metric is singular near the boundary of the internal region
+\cite{kenyon2007limit} and the contribution of singularities to the logarithmic correction is not
+explicitly studied yet. Thus our result for value of $f_2$ should be useful in such a study, which
+we will attempt to do in a separate publication.
 

### 2020-02-22 AffineLieAlgebras/MQFT2018/paper.tex
Before referee report

@@
 \begin{abstract}
-  We consider dimer model on a hexagonal lattice. This model can be
-  seen as a ``pile of cubes in the box''. The energy of configuration
-  is given by the volume of the pile and the partition function is
-  computed by the classical MacMahon formula or, more formally, by the
-  determinant of Kasteleyn matrix. We use the expression for the
-  partition function to derive the scaling behavior of free energy in
-  the limit of lattice mesh tending to zero and temperature tending to
-  infinity. We consider the cases of finite hexagonal domain, of
-  infinite height box and coordinate-dependent Boltzmann weights. We
-  obtain asymptotic expansion of free energy and discuss the
-  universality and physical meaning of the expansion coefficients.
+  We consider the dimer model on a hexagonal lattice. A model can be seen as a ``pile of cubes in
+  the box''. The energy of configuration is given by the volume of the pile. The partition function
+  is computed by the classical MacMahon formula or by the determinant of the Kasteleyn matrix. We
+  use MacMahon formula to derive the scaling behavior of free energy in the limit when the lattice
+  spacing goes to zero and temperature goes to infinity. We consider the cases of a finite hexagonal
+  domain, the case when one side of the hexagonal box is infinite and the case when Boltzmann
+  weights are inhomogeneous. We obtain asymptotic expansion of free energy, that is known as finite
+  size corrections, and discuss the universality and physical meaning of the expansion coefficients.
 \end{abstract}
@@
 represented the partition function of the dimer model as a Pfaffian of the signed adjacency matrix
-(``Kasteleyn matrix'') thus allowing the computation of the number of tilings and of free energy scaling limit.
+(``Kasteleyn matrix'') thus allowing the computation of the number of tilings and of the free energy
+in the scaling limit.
 This result was very elegantly used by Fisher to solve Ising model \cite{fisher1966dimer} and by Fan
-and Wu \cite{Fan-1970} to compute free energy for a certain case of eight-vertex model.
-
-Further studies of dimer models revealed the connection to the theory of alternating matrices
-\cite{elkies1992alternating1,elkies1992alternating2}. Later, the well-known limit shape
+and Wu \cite{Fan-1970} to compute the free energy for a certain case of the eight-vertex model.
+
+Further studies of dimer models revealed the connection to the theory of alternating sign matrices
+\cite{elkies1992alternating1,elkies1992alternating2}. Later, the limit shape
 phenomenon~\cite{vershik1977kerov} was discovered for dimer models. First, the ``Arctic circle''
 theorem was proven for domino tilings of the domain in the form of ``Aztec diamond''
-~\cite{1998math......1068J}. Then similar result was obtained for a hexagonal domain on the
+~\cite{1998math......1068J}. Then a similar result was obtained for a hexagonal domain on the
 hexagonal lattice~\cite{cohn1998shape}. Soon the connection of these results with the theory of
@@
 \cite{kenyon2006dimers,kenyon2009lectures} present a detailed exposition of the limit shape
-phenomenon in the dimer models.
-
-Dimer models are the integrable lattice models of statistical physics that are now under an active
+phenomenon in the dimer models. The study of limit shapes remains an important problem
+\cite{borodin2010q,di2018tangent}.
+
+Dimer models are now under an active
 theoretical~\cite{zj2000,ferrari} and numerical investigation~\cite{ks2018}. Computation of
-correlation functions is a common problem for all vertex models \cite{colomo2012approach} as well as
-for dimer models. Another problem of great interest is the study of limit shapes in various cases
-\cite{borodin2010q,di2018tangent}.
-
-Configurations of dimer model on a hexagonal lattice are in one-to-one correspondence with the
-configurations of five-vertex model that appears for certain choice of parameters in the well-known
-six-vertex model \cite{kapitonov2012weighted,kapitonov2008five}.
+correlation functions is an important problem in vertex models \cite{colomo2012approach} and in dimer models.
+
+Dimer configurations on a hexagonal lattice are in one-to-one correspondence with configurations of
+the five-vertex model that appears for certain choice of parameters in the six-vertex model
+\cite{kapitonov2012weighted,kapitonov2008five}.
 
@@
 \cite{kenyon2002laplacian,kenyon2000asymptotic}. Scaling limit of dimer model is proven to be
-described by a Gaussian free-field theory \cite{kenyon2001dominos}, but finite-size corrections to
+described by a Gaussian free-field theory \cite{kenyon2001dominos}, which is also conformal, but finite-size corrections to
 the scaling of free energy were previously considered mostly in the absence of the limit shape
@@
 
-Finite-size corrections are important to fill the gap between numerical simulations and
-theoretical results. Moreover, they can be used to choose the proper field-theoretic description of
-the scaling limit. For example, the logarithmic term is supposed to be universal and dependent on a
-value of the central charge ${\bf c}$ of conformal field theory \cite{cardy1988finite}.
-
-Computation of finite-size corrections to the scaling of free energy in the dimer model on a rectangular
-region of the square lattice led to a series of publications and even controversy about the proper CFT
-description of the scaling limit. Some publications claimed ${\bf c}=-2$, while others -- ${\bf c}=1$ 
+In general, finite-size corrections to free energy in the critical
+systems with a characteristic length $\varepsilon$ are supposed to
+have the form
+\begin{equation*}
+  f\approx f_{0}+f_{1}\varepsilon +f_{2}\varepsilon^{2}\ln\varepsilon+ f_{3}\varepsilon^{2}+\mathcal{O}(\varepsilon^{3}),
+\end{equation*}
+according to the paper by Cardy and Peschel \cite{cardy1988finite}.
+The coefficients can be used to choose the proper field-theoretic
+description of the scaling limit. For example, the logarithmic term is
+supposed to be universal and dependent on a value of the central
+charge ${\bf c}$ of conformal field theory.
+
+Computation of finite-size corrections to the scaling of free energy
+in the dimer model on a rectangular region of the square lattice led
+to a series of publications and even controversy about the proper CFT
+description of the scaling limit. Some publications claimed
+${\bf c}=-2$\cite{Rasmussen_2012}, while others -- ${\bf c}=1$
 \cite{allegra2015exact,morin2016integrability,Sh_Izmailian_2019,izmailian2016finite,izmailian2005logarithmic}.
-Note that in this case the limit shape does not appear due to the choice of boundary conditions.
-
-The case of the limit shape is even more complicated. While the limit shape can be computed from the
-variational minimization problem for surface tension \cite{kenyon2007limit,kenyon2006dimers} and
+Note that in this case the limit shape does not appear due to the
+choice of boundary conditions.
+
+The case of the limit shape is even more complicated. While the limit
+shape can be computed from the variational minimization problem for
+surface tension \cite{kenyon2007limit,kenyon2006dimers} and
 fluctuations are described by the Gaussian Free Field
-\cite{kenyon2001dominos,kenyon2008height,kenyon2009lectures}, the behavior on the boundary of the
-frozen region is not well understood. Surface tension becomes singular near the boundary of the frozen
-domain \cite{kenyon2007limit}, thus boundary contribution to the logarithmic correction to free
-energy scaling cannot be easily obtained from field-theoretic point of view. As a result, the
-computation of finite-size corrections from the exact solution of the model, especially of the
-logarithmic term, is important.
+\cite{kenyon2001dominos,kenyon2008height,kenyon2009lectures}, the
+behavior of the field near the boundary of the frozen region is not
+easy to understand. Surface tension becomes singular near the boundary
+of the frozen domain \cite{kenyon2007limit}, thus boundary
+contribution to the logarithmic correction to free energy scaling
+cannot be easily obtained from field-theoretic point of view. As a
+result, the computation of finite-size corrections from the exact
+solution of the model, especially of the logarithmic term, is
+important.
 

### 2020-04-08 AffineLieAlgebras/MQFT2018/paper.tex
Accepted to TMPh

@@
 \label{sec:model-definition}
-The configurations of the dimer model are perfect matchings (sets of non-touching edges, covering
-all the vertices) on some graph ${\cal G}$ with some choice of weights $\omega(e)$ on the edges. The
-model is solvable on the bipartite graphs, i.e. the partition function can be computed if the
-weights are introduced in such a way that for each face bounded by 0 mod 4 edges there is an odd
-number of negative edge weights and each face with 2 mod 4 edges has an even number of of negative
-edge weights. Then the signs of the edge weights form a so-called ``Kasteleyn orientation'' on graph,
-the weighting is called ``Kasteleyn weighting'' \cite{kenyon2001dominos,kenyon2009lectures}.
+The configurations of the dimer model are perfect matchings (sets of
+non-touching edges, covering all the vertices) on some graph
+${\cal G}$. Boltzmann weight of a configuration is given by the
+product of edge weights $\omega(e)$ for some choice of edge weights. The
+partition function is given by the sum of Boltzmann weights over all
+configurations: $Z=\sum_{\mathrm{conf}}\prod_{e\in\mathrm{conf}}\omega(e).$
+
+We consider dimer model on a hexagonal lattice. There are three
+possible directions of the edges. First we consider the following
+choice of Bolzmann weights. Take positive number $q$ and embed the
+hexagonal lattice in the complex plane $\mathbb{C}$ in such a way that
+some edges $e$ are parallel to the real line and corresponding
+vertices $w,b$ have coordinates with half-integer imaginary part (See left pane of the Fig.~\ref{dhf}). Then take
+\begin{equation}
+  \label{eq:18}
+  \begin{array}{lll}
+ \omega(e_{w\to b})=q^{\Im w}&  \mathrm{if} & \Im w=\Im b\\
+  \omega(e_{w\to b})=1 & \mathrm{if}& \Im w\neq\Im b.
+  \end{array}
+\end{equation}
+
+In the section \ref{sec:box-infinite-height} we will consider the case when $q=q(\Re w)$ is an arbitrary smooth function of the real part of coordinate.
+
+In general the model is solvable on the bipartite graphs, i.e.
+the partition function can be computed if the weights are introduced
+in such a way that for each face bounded by 0 mod 4 edges there is an
+odd number of negative edge weights and each face with 2 mod 4 edges
+has an even number of of negative edge weights. Then the signs of the
+edge weights form a so-called ``Kasteleyn orientation'' on graph, the
+weighting is called ``Kasteleyn weighting''
+\cite{kenyon2001dominos,kenyon2009lectures}.
 
@@
 uppermost cube the height of its column of cubes. Looking at this picture from the top, we obtain a
-height function defined on the rectangular domain of the square lattice.
+height function that is defined on the rectangular domain of the square lattice.
 
@@
 \center{\scalebox{0.4}{\includegraphics{my-loz}}}
-\caption{\label{dhf}A configuration of dimers on the hexagonal lattice and a corresponding picture
-  of ``cubes in the corner''.}
+\caption{\label{dhf}On the left: a configuration of dimers on the hexagonal lattice and the choice of coordinates for the definition of weights (\ref{eq:18}). On the right: corresponding picture
+  of ``cubes in the corner'' for the height function $h$.}
 \end{figure}
@@
 Let us define the sizes $M$, $N$, and $K$ of the sides of the hexagon.
-The above description can be formalized by
+The above description of height function can be formalized by
 %set of configurations of the model can be defined all possible ways to write
@@
 
-MacMahon formula is obtained for the following definition of the Kasteleyn matrix. Embed the
-hexagonal lattice in the complex plane $\mathbb{C}$ in such a way that some edges are parallel to
-the real line with and corresponding vertices have coordinates with integer real and imaginary
-parts. Then take
-\begin{eqnarray}
-  \label{eq:18}
-  {\cal K}(w,b)=q^{\Re w+\Im w} \quad \mathrm{if}\quad \Im w=\Im b\\
-  {\cal K}(w,b)=1 \quad \mathrm{if}\quad \Im w\neq\Im b.
-\end{eqnarray}
-
 The   free energy per site is defined as$^{*}$
@@
 To check our result \eqref{eq:26} numerically, we first need to evaluate the integral in $f_{3}$.
-The function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$ is smooth and but some care is required when taking the
+The function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$ is smooth and continuous, but some care is required when taking the
 limit $z\to 0$ numerically. Evaluating the integral numerically with Mathematica we get
@@
 expansion \eqref{eq:26} and the exact formula \eqref{eq:4}.
+
+Since a hexagon with an infinite side is similar to an infinite strip,
+it is natural to compare our result with the results for finite size
+corrections to the scaling of free energy for dimer model on a square
+lattice on a strip, cylinder and Möbius strip. These results were
+recently nicely summarized in the paper \cite{izmailian2017finite} and
+further investigated in the paper \cite{Sh_Izmailian_2019}. There the
+following general expansion for the free energy on $M\times N$ square
+lattice was presented ($S=M\times N$ here):
+\begin{equation}
+  \label{eq:32}
+  f=f_{\mathrm{bulk}}+\frac{2}{M}f_{s1}+\frac{2}{N}f_{s2}
+  +f_{\mathrm{corn}}\frac{\ln S}{S} +\frac{1}{S} (f_{\mathrm{univ}}+f_{\mathrm{nonuniv}})
+\end{equation}
+In particular, on a strip the bulk term is
+$f_{\mathrm{bulk}}=\frac{G}{\pi}$, where $G$ is the Catalan constant,
+surface free energy is nonzero, $f_{s1}=-\frac{1}{4}\ln(1+\sqrt{2})$ 
+and the coefficient of $\frac{1}{S}$ is equal to $\frac{\pi}{24}$. In
+the case of cylinder and  Möbius strip logarithmic term also appears.
+
+Comparing our results (\ref{eq:6}), (\ref{eq:8}), (\ref{eq:9}),
+(\ref{eq:11}) with these expressions, we see that behavior on
+hexagonal lattice in the presence of limit shape is different. In
+particular, bulk term $f_{0}$ depends on the geometric parameters $a$
+and $b$, boundary is
+tension free, so no boundary term $f_{1}$ is zero, and geometric
+parameters of the domain appear again in the coefficient of
+$\varepsilon^{2}$.
 

### 2020-04-08 AffineLieAlgebras/MQFT2018/paper-ru.tex
Russian version added

\documentclass{article}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[T1,T2A]{fontenc}
\usepackage[english,russian]{babel}

\usepackage{amsmath,amssymb,amsthm,amsfonts}
%\synctex=1

\newtheorem{lemma}{Лемма}
\newtheorem{Def}{Definition}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{statement}{Statement}
\newtheorem{Cnj}[Def]{Conjecture}
\newtheorem{Prop}[Def]{Property}
\newtheorem{example}{Example}[section]

\newcommand{\Li}{\mathrm{Li}}
\newcommand{\dx}{\mathrm{dx}~}
\newcommand{\dxb}{\mathrm{d\bar x}~}
\newcommand{\dy}{\mathrm{dy}~}
\newcommand{\dz}{\mathrm{dz}}

\begin{document}
\title{Поправки конечного размера к скейлингу свободной энергии в модели димеров на шестиугольной области}

\author{А.А.~Назаров$^{1,2}$, С.А.~Пастон$^{1}$\\
{\small
  $^{1}$Санкт-Петербургский государственный университет,}\\{\small физический факультет, }\\{\small кафедра физики высоких энергий и элементарных частиц,} \\
{\small 198504, Россия, Санкт-Петербург, Ульяновская ул. 1}\\
\small{$^{2}$email:antonnaz@gmail.com}
}
\date{}
\maketitle
\begin{abstract}
  Мы рассматриваем модель димеров на шестиугольной решетке. Эту
  модель можно представить в виде ``кучи кубиков в углу коробки''.
  Энергия конфигурации дается суммарным объемом кубиков. Статсумма
  модели вычисляется по классической формуле Макмагона или как
  детерминант матрицы Кастелейна. Мы используем формулу Макмагона и
  выводим скейлинговое поведение свободной энергии в пределе, когда
  шаг решетки стремится к нулю, а температура стремится к
  бесконечности. Мы рассматриваем случай конечной шестиугольной
  области, случай, когда длина одной из сторон шестиугольника
  стремится к бесконечности и случай неоднородных весов Больцмана. В
  работе получено асимптотическое разложение свободной энергии,
  которое обычно называется ``поправками конечного размера''. Мы
  обсуждаем универсальность и физический смысл коэффициентов этого
  разложения.
\end{abstract}

\section*{Введение}
\label{sec:introduction}

Модель димеров была введена в 1937 году при попытке расширить статистическую теорию идеальных
растворов в химии на случай жидких смесей с молекулами двух сильно отличающихся размеров
\cite{Fowler-1937}. Молекулы представлялись жесткими ребрами на решетке, в работе было приближенно
оценено количество покрытий решетки не соприкасающимися ребрами. Но точное вычисление авторам
осуществить не удалось.

В 1961 году Кастелейн \cite{P.W-1961}, а также Темперли и Фишер \cite{doi:10.1080/14786436108243366}
представили статсумму модели димеров в виде пфаффиана матрицы смежности со знаками (``матрицы
Кастелейна''), что позволило вычислить количество покрытий и свободную энергию в скейлинговом
пределе. Этот результат использовался Фишером для элегантного решения модели Изинга
\cite{fisher1966dimer}, а также Фаном и Ву \cite{Fan-1970} для вычисления свободной энергии для
специального случая восьмивершинной модели.

Дальнейшие исследования модели димеров выявили связь с теорией знакопеременных матриц
\cite{elkies1992alternating1,elkies1992alternating2}. Позднее, явление предельной
формы~\cite{vershik1977kerov} было открыто в моделях димеров. Во-первых, была доказана теорема об
``арктическом круге'' для покрытий области типа ``ацтекский брильянт'' костяшками
домино~\cite{1998math......1068J}. Затем подобный результат был получен для шестиугольной области на
шестиугольной решетке~\cite{cohn1998shape}. Вскоре была установлена связь этих результатов с
теорией случайных матриц~\cite{johansson2002non}. В работах
\cite{kenyon2006dimers,kenyon2009lectures} приведено подробное описание явления предельной формы в
моделях димеров. Изучение предельных форм остается важной задачей \cite{borodin2010q,di2018tangent}.

Модели димеров продолжают активно изучаться как теоретическими~\cite{zj2000,ferrari}, так и
численными методами~\cite{ks2018}. Вычисление корреляционных функций -- важная задача в вершинных
моделях  \cite{colomo2012approach} и в моделях димеров.

Конфигурации димеров на шестиугольной решетке находятся во взаимно однозначном соответствии с
конфигурациями пятивершинной модели, которая возникает при определенном выборе параметров в
шестивершинной модели \cite{kapitonov2012weighted,kapitonov2008five}.

При изучении модели димеров на различных решетках были обнаружены интересные взаимосвязи с
геометрией искривленных многообразий и со спектром дискретных и непрерывных операторов Дирака и
Лапласа \cite{kenyon2002laplacian,kenyon2000asymptotic}. Доказано, что скейлинговый предел модели
димеров описывается свободной гауссовой теорией поля \cite{kenyon2001dominos}, которая также
является конформной, но поправки конечного размера к скейлингу в основном до сих пор рассматривались
в отсутствии предельной формы
\cite{Sh_Izmailian_2019,izmailian2016finite,izmailian2011dimer,izmailian2007non,izmailian2005logarithmic}.

В общем, поправки конечного размера к свободной энергии в критических системах с характерной длиной
$\varepsilon$ должны иметь вид
\begin{equation*}
  f\approx f_{0}+f_{1}\varepsilon +f_{2}\varepsilon^{2}\ln\varepsilon+ f_{3}\varepsilon^{2}+\mathcal{O}(\varepsilon^{3}),
\end{equation*}
согласно аргументам, изложенным в работе Карди и Пешеля \cite{cardy1988finite}. Коэффициенты могут
использоваться для выбора подходящего теоретико-полевого описания скейлингового предела. Например,
логарифмический член считается универсальным и зависящим от значения центрального заряда конформной
теории поля ${\bf c}$.

Вычисление поправок конечного размера к скейлингу свободной энергии в модели димеров на
прямоугольной области квадратной решетки вызвало серию публикаций и научную дискуссию о правильной
конформной теории поля для описании скейлингового предела. В некоторых работах утверждалось, что
${\bf c}=-2$\cite{Rasmussen_2012}, в других -- ${\bf c}=1$
\cite{allegra2015exact,morin2016integrability,Sh_Izmailian_2019,izmailian2016finite,izmailian2005logarithmic}.
Заметим, что в этом случае явление предельной формы не возникает из-за выбора граничных условий.

В случае присутствия предельной формы все еще сложнее. Хотя предельная форма может быть вычислена из
вариационной минимизационной проблемы для поверхностного натяжения
\cite{kenyon2007limit,kenyon2006dimers}, а флуктуации описываются гауссовским свободным полем
\cite{kenyon2001dominos,kenyon2008height,kenyon2009lectures}, поведение поля около границы
замороженной области описать сложно. Поверхностное натяжение становится сингулярным около границы
замороженной области \cite{kenyon2007limit}, поэтому граничный вклад в логарифмическую поправку к
скейлингу свободной энергии нельзя легко получить с точки зрения теории поля. В результате,
вычисление поправок конечного размера из точного решения модели, в особенности, логарифмического
вклада, становится важной задачей.

Мы рассматриваем особый случай модели димеров на шестиугольной области шестиугольной решетки,
который можно представить в виде ``кучи кубиков в углу коробки''. Энергия конфигурации дается общим
числом кубиков. Для этого случая мы используем точную комбинаторную формулу для статсуммы и выводим
выражения для скейлингового предела свободной энергии и трех первых членов в поправках конечного
размера. Мы показываем, что первый член тождественно равен нулю. Второй член, который включает
логарифмическую зависимость от шага решетки, связан с центральным зарядом эффективной теории поля и
с геометрией предельной формы. Третий член содержит вклад, зависящий от геометрии, который явно
записывается в элементарных функциях, и универсальный вклад, постоянный во всех рассмотренных нами
случаях модели димеров.

Затем мы рассматриваем случай коробки бесконечной высоты и случай весов Больцмана, зависящих от
координаты. В этих случаях мы также выводим явные выражения для поправок конечных размеров. Мы
демонстрируем универсальность логарифмического члена и постоянного вклада в третий член разложения.

Наши результаты подтверждаются численной проверкой и результатами симуляций методом Монте-Карло,
представленными в нашей предыдущей публикации \cite{1742-6596-1135-1-012024}.

\section{Определение модели}
\label{sec:model-definition}

Конфигурации модели димеров -- это максимальные паросочетания (множества несоприкасающихся ребер,
покрывающие все вершины) на некотором графе ${\cal G}$. Больцмановский вес конфигурации дается
произведением весов ребер  $\omega(e)$, которые выбраны каким-то образом. Статсумма равна сумме
весов Больцмана по всем конфигурациям: $Z=\sum_{\mathrm{conf}}\prod_{e\in\mathrm{conf}}\omega(e).$

Мы рассматриваем модель димеров на шестиугольной решетке. У ребер три возможных направления. Сперва
мы рассматриваем следующий выбор весов Больцмана. Для положительного числа $q$ вложим шестиугольную
решетку в комплексную плоскость $\mathbb{C}$ так, чтобы некоторые ребра были параллельны
вещественной оси, а соответствующие вершины  $w,b$ имели координаты с целой или полуцелой мнимой
частью (См. левую часть Рис.~\ref{dhf}). Затем возьмем 
\begin{equation}
  \label{eq:18}
  \begin{array}{lll}
 \omega(e_{w\to b})=q^{\Im w},&  \mbox{если} & \Im w=\Im b\\
  \omega(e_{w\to b})=1, & \mbox{если}& \Im w\neq\Im b.
  \end{array}
\end{equation}

В разделе  \ref{sec:box-infinite-height} мы также рассмотрим случай, когда  $q=q(\Re w)$  --
произвольная гладкая функция вещественной части координаты.

В целом, модель точно решаема на двудольных графах, то есть статсумма может быть вычислена, если
веса введены таким образом, что для каждой грани, ограниченной 0 по модулю 4 ребер, число
отрицательных весов ребер нечетно, а у грани с 2 по модулю 4 ребрами, число отрицательных весов
ребер четное. Тогда знаки весов ребер образуют так называемую ``ориентацию Кастелейна'' на графе, а
выбор весов называется ``взвешиванием Кастелейна'' \cite{kenyon2001dominos,kenyon2009lectures}.

В двудольном графе ${\cal G}$ раскрасим вершины в черный и белый так, чтобы все вершины, смежные с черными,
были белыми. Обозначим множества черных и белых вершин  $B, W$, а элементы этих множеств --  $b,w$.

Веса можно записать в виде ``матрицы Кастелейна''  ${\cal K}$ -- взвешенной матрицы смежности со
знаком, в которой матричный элемент  ${\cal K}(w,b)$ равен весу ребра  $w\to b$: ${\cal
  K}(w,b)=\omega(w\to b)$.

Тогда статсумма равна абсолютному значению детерминанта матрицы Кастелейна~\cite{P.W-1961,doi:10.1080/14786436108243366}: 
\begin{equation}
  \label{eq:15}
  Z=\sum_{\mathrm{conf}}\prod_{e\in \mathrm{conf}}w(e)=|\det {\cal K}|.
\end{equation}

Матрица Кастелейна определяет дискретный оператор Дирака  $D$, где действие  $D$ на функцию $f$,
заданную на вершинах, дается формулой:
\begin{equation}
  \label{eq:16}
  (Df)(v)=\sum_{u}{\cal K}(v,u) f(u).
\end{equation}
Кенион \cite{kenyon2002laplacian,kenyon2000asymptotic} и другие  \cite{sridhar2015asymptotic}
рассматривали асимптотику детерминантов дискретных операторов Дирака и Лапласа, то есть, как мы
можем видеть, задачу, очень близкую к скейлингу свободной энергии. Но поправки конечного размера к
скейлингу свободной энергии в этих работах вычислены не были.

Мы рассматриваем покрытия шестиугольной области на шестиугольной решетке, состоящие из подмножеств
ребер решетки, таких что каждая вершина является концом ровно одного ребра.

Можно нарисовать ромб на двойственной решетке вокруг каждого ребра конфигурации. Тогда получится
изображение ``кубиков в углу'', показанное на Рис.~\ref{dhf}. Запишем на верхней стороне каждого
верхнего кубика высоту соответствующей колонки из кубиков. Если мы посмотрим на этот рисунок сверху,
то мы увидим функцию высоты, определенную в прямоугольной области квадратной решетки.

\begin{figure}[htbp]
\center{\scalebox{0.4}{\includegraphics{my-loz}}}
\caption{\label{dhf}Слева: конфигурация димеров на шестиугольной решетке и выбор координат для
  определения весов  (\ref{eq:18}). Справа: соответствующая картина ``кубиков в углу коробки'' для
  функции высоты $h$.}
\end{figure}

Обозначим длины сторон шестиугольной области через $M$, $N$, и $K$. 
Вышеприведенное описание функции высоты можно сделать более строгим, если поставить неотрицательные
числа не превосходящие  $K$ в ячейки прямоугольной таблицы размером  $M\times N$ таким образом, что
значение в любой ячейке не превосходит значений в  ячейках, находящихся слева и сверху от нее:
\begin{equation}
  \label{eq:1}
  h_{ij}\leq h_{i-1,j},\quad h_{ij}\leq h_{i,j-1}.
\end{equation}

Вес каждой конфигурации дается экспонентой объема всех кубиков или, что то же самое, суммы значений
функции высоты:  
\begin{equation*}
  \label{eq:10}
  E[conf]=\sum_{i,j} h_{ij}=\mathrm{Volume}
\end{equation*}
Мы полагаем постоянную Больцмана равной единице и выбираем систему единиц таким образом, что в
выражение для энергии не входит константа связи. Тогда статсумма равна
\begin{equation*}
  \label{eq:14}
  Z=\sum_{conf} e^{-\frac{E[conf]}{T}}=\sum_{conf}q^{\mathrm{Volume}[conf]}, 
\end{equation*}
где $q=\exp\left(-1/T\right)$ .

В данном случае, статсумму можно записать в виде классической комбинаторной формулы Макмагона
~\cite{vuletic2009generalization}
\begin{equation}
  \label{eq:12}
   Z[M,N,K,q]=\prod_{i=1}^{M}\prod_{j=1}^{N}\prod_{k=1}^{K}\frac{1-q^{i+j+k-1}}{1-q^{i+j+k-2}}.
\end{equation}

Удельная свободная энергия определим, как$^{*}$
\footnote{Для удобства мы опускаем множитель  $\frac{1}{T}$ в обычном определении свободной энергии.}
\begin{equation*}
  \label{eq:17}
  % \frac{f}{T}
  f=-\frac{1}{V}\ln Z(M,N,K,q).
\end{equation*}
Здесь $V$ -- это количество вершин, оно вдвое больше числа димеров и вдвое больше числа граней
кубиков:
\begin{equation}
  \label{eq:19}
  V=2(MN+NK+MK)=2(ab+bc+ca) \varepsilon^{-2}.
\end{equation}

Мы будем рассматривать скейлинговый предел, одновременно с термодинамическим пределом, в котором
$T\to \infty,$ и  $M,N,K\to \infty$ так, что отношения $\frac{M}{T}=a,\quad \frac{N}{T}=b, \quad
\frac{K}{T}=c$ остаются постоянными.  Далее мы используем величину $\varepsilon=\frac{1}{T}$,
которую можно рассматривать в качестве характерного размера модели, например, шага решетки при нашем
выборе системы единиц.

В следующем разделе мы вычислим асимптотическое разложение свободной энергии $f$ по $\varepsilon$ и
выведем независимые от  $\varepsilon$ явные выражения для первых коэффициентов этого разложения.

\section{Вычисление асимптотического разложения свободной энергии}
\label{sec:free-energy-scaling}
Начнем с подстановки формулы Макмагона \eqref{eq:12} в определение свободной энергии \eqref{eq:17} и получим
\begin{multline}
  \label{eq:20}
    %-\frac{f}{T}
    f=-\frac{1}{V}\ln Z =\\=- \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}\left[
  \ln\left(1-e^{-\varepsilon (i+j+k-3)} e^{-2\varepsilon}\right) -\ln\left(1-e^{-\varepsilon
      (i+j+k-3)} e^{-\varepsilon}\right)\right].
\end{multline}
Надо заметить, что для конечного  $\varepsilon$ и каждого значения  $i,j,k$ логарифмы имеют вид
$\ln(1-x)$, где $0<x<1$. То есть мы можем представить логарифмы в виде степенных рядов по $x$ и получить
\begin{equation}
  \label{eq:7}
  f=-\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K}\sum_{n=1}^{\infty}
  \frac{1}{V}\frac{1}{n}\left[-e^{-n\varepsilon (i+j+k-3)} e^{-2n\varepsilon}+e^{-n\varepsilon
      (i+j+k-3)} e^{-n\varepsilon}\right]. 
\end{equation}
Здесь ряд сходится абсолютно, поэтому мы можем поменять порядок суммирования и переписать свободную
энергию в виде
\begin{equation}
  \label{eq:37}
  f=-\sum_{n=1}^{\infty}
  \frac{1}{V}\frac{1}{n}e^{-n\varepsilon}\left(1-e^{-n\varepsilon}\right)\sum_{i=1}^{M}
  \sum_{j=1}^{N} \sum_{k=1}^{K}e^{-n\varepsilon (i+j+k-3)} .
\end{equation}
Тройная сумма теперь факторизуется в произведение трех сумм типа  $\sum_{i=0}^{M-1}e^{-n\varepsilon
  i}$, которые оказываются суммами геометрических прогрессий. Поэтому  $\sum_{i=0}^{M-1}e^{-n\varepsilon
  i}=\frac{1-e^{-Mn\varepsilon}}{1-e^{-n\varepsilon}}$, и мы получаем
\begin{equation}
  \label{eq:38}
  f=-\sum_{n=1}^{\infty}
  \frac{1}{V}\frac{1}{n}\frac{e^{-n\varepsilon}}{\left(1-e^{-n\varepsilon}\right)^{2}}
  \left(1-e^{-na}\right)\left(1-e^{-nb}\right)\left(1-e^{-nb}\right).
\end{equation}
Обозначим через  $\chi(z)$ функцию
\begin{equation}
  \label{eq:39}
  \chi(z)=e^{-z}\left(\frac{z}{1-e^{-z}}\right)^{2}, 
\end{equation}
а через  $H_{n}$ произведение независящих от $\varepsilon$ экспонент
\begin{equation}
  \label{eq:40}
  H_{n}=\left(1-e^{-na}\right)\left(1-e^{-nb}\right)\left(1-e^{-nc}\right).
\end{equation}

Функция  $\chi(z)$ гладкая в 0, четная и имеет следующее разложение в ряд Тейлора:
\begin{equation}
  \label{eq:45}
  \chi(z)=1 - \frac{z^2}{12} + \frac{z^4}{240}+\mathcal{O}(z^{6}).
\end{equation}

Воспользуемся определением объема \eqref{eq:19} и запишем свободную энергию в виде
\begin{equation}
  \label{eq:41}
  f=-\frac{1}{2(ab+bc+ca)} \sum _{n=1}^{\infty} \frac{\chi(n\varepsilon)}{n^{3}} H_{n}.
\end{equation}
Мы интересуемся скейлинговым поведением по  $\varepsilon$, когда $\varepsilon\to 0$. Функция  $f$
регулярна по  $\varepsilon$ при $\varepsilon>0$. Поэтому нам необходимо вычислить
$\left.f\right|_{\varepsilon\to 0}$ и производные  $\left.\frac{\partial f}{\partial
  \varepsilon}\right|_{\varepsilon\to 0}$, $\left.\frac{\partial^{2} f}{\partial
  \varepsilon^{2}}\right|_{\varepsilon\to 0}$.

Для $\left.f\right|_{\varepsilon\to 0}$ мы видим, что $\chi(0)=1$, а сумма $\sum_{n=1}^{\infty}
\frac{H_{n}}{n^{3}}$ представляет собой сумму полилогарифмов
$\mathrm{Li}_{s}(z)=\sum_{n=1}^{\infty}\frac{z^{n}}{n^{s}}$ третьего порядка:
\begin{multline}
  \label{eq:42}
  \left.f\right|_{\varepsilon\to 0} =\frac{1}{2(ab+bc+ca)}\left[\Li_{3}(e^{-a})+\Li_{3}(e^{-b})+\Li_{3}(e^{-c})-
    \Li_{3}(e^{-a-b})\right.\\
  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right].
\end{multline}
Здесь дзета-функция Римана возникает, как значение полилогарифма $\Li_{3}(1)=\zeta(3)$.

Прозиводная функции $\chi(z)$ равна нулю, $\chi'(0)=0$, а ряды
$\sum_{n=1}^{\infty} \frac{\chi'(n\varepsilon)}{n^{2}}H_{n}$ сходятся при конечных значениях
$\varepsilon$, поэтому мы получаем для производной
\begin{equation}
  \label{eq:43}
\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}=0.
\end{equation}

Теперь вычислим вторую производную
\begin{equation}
  \label{eq:44}
\frac{\partial^{2} f}{\partial
  \varepsilon^{2}}=-\frac{1}{2(ab+bc+ca)} \sum _{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n} H_{n}.  
\end{equation}
Вторая производная  $\chi$ конечна,  $\chi''(0)=-\frac{1}{6}$. Но при переходе к пределу
$\varepsilon\to 0$ в этом выражении возникает сложность из-за плохой сходимости ряда. Перепишем
вторую производную в виде суммы двух рядов:
\begin{equation}
  \label{eq:46}
\frac{\partial^{2} f}{\partial
  \varepsilon^{2}}=-\frac{1}{2(ab+bc+ca)} \left(\sum _{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n}+
  \sum_{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n}(H_{n}-1)\right).    
\end{equation}
Вторая сумма теперь сходится, так как  $H_{n}-1$ экспоненциально убывает по $n$. Ее можно записать в
виде комбинации рядов для логарифмов:
\begin{multline}
  \label{eq:47}
  \chi''(0)\sum_{n=1}^{\infty} \frac{H_{n}-1}{n}=\\=\chi''(0)\sum_{n=1}^{\infty}\frac{1}{n}\left(-e^{-a
      n-b n-c n}+e^{-a n-b n}+e^{-a n-c n}+e^{-b n-c n} - e^{-a n}-e^{-b n}-e^{-c n}\right)=\\
  =\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right).
%%  =\frac{1}{6} \left(-\log \left(1-e^{-a-b-c}\right)+\log
%%   \left(1-e^{-a-b}\right)+\log
%%   \left(1-e^{-a-c}\right)+\log
%%   \left(1-e^{-b-c}\right)-\log
%%   \left(1-e^{-a}\right)-\log
%%   \left(1-e^{-b}\right)-\log
%%   \left(1-e^{-c}\right)\right)
\end{multline}

Первую сумму в формуле  \eqref{eq:46} можно выразить следующим образом. Во-первых, рассмотрим вторую
производную функции $\chi(z)$, выделим экспоненту и обозначим то, что осталось, через $\xi(z)$:
\begin{equation}
  \label{eq:48}
  \chi''(z)=e^{-z}\frac{e^{2 z} \left(z^2+4 e^z
   \left(z^2-1\right)+e^{2 z} \left(z^2-4
   z+2\right)+4
   z+2\right)}{\left(e^z-1\right)^4}=e^{-z}\xi(z).
\end{equation}
Сумму теперь можно переписать в виде
\begin{equation}
  \label{eq:49}
  \sum _{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n}=
  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(n\varepsilon) =
  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(0)+  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}.
\end{equation}
Первый член -- это ряд для логарифма $\ln\left(1-e^{-\varepsilon}\right)\approx \ln
\varepsilon$. Обозначим через  $Q(z)$ разность значений функции $\xi$ в $z$ и в нуле, деленную на $z$:
\begin{equation}
  \label{eq:85}
  Q(z)=\frac{\xi(z)-\xi(0)}{z}.
\end{equation}
Тогда функция  $Q(z)$ будет аналитической по $z$.

В результате вторая сумма может быть приближена интегралом:
\begin{equation}
  \label{eq:50}
  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}Q(n\varepsilon)=\varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}\approx
  \int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz=\int_{0}^{\infty}e^{-z}Q(z)\dz.
\end{equation}
\begin{equation}
  \label{eq:51}
  \frac{\partial^{2} f}{\partial
  \varepsilon^{2}}\approx-\frac{1}{2(ab+bc+ca)}
\left[\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{6}\ln \varepsilon+\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz\right].
\end{equation}
Так как во вторую производную входит логарифмический член, мы получаем следующее поведение свободной энергии
\begin{equation}
  \label{eq:26}
  f\approx f_{0}+f_{1}\varepsilon +f_{2}\varepsilon^{2}\ln\varepsilon+ f_{3}\varepsilon^{2}+\mathcal{O}(\varepsilon^{3}),
\end{equation}
как и ожидается в двумерных критических системах  \cite{cardy1988finite}. После взятия производных
от этого выражения по  $\varepsilon$, мы видим, что
$f_{0}=f(0)$,$f_{1}=\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}$,
$\frac{\partial^{2} f}{\partial \varepsilon^{2}}=f_{2}(2\ln\varepsilon+3)+2f_{3}$.

Таким образом мы получаем коэффициенты
\begin{multline}
  \label{eq:27}
  f_{0}=\frac{1}{2(ab+bc+ca)}\left[\Li_{3}(e^{-a})+\Li_{3}(e^{-b})+\Li_{3}(e^{-c})-
    \Li_{3}(e^{-a-b})\right.\\
  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right],
\end{multline}
\begin{equation}
  \label{eq:28}
  f_{1}=0,
\end{equation}
\begin{equation}
  \label{eq:30}
  f_{2}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12},
\end{equation}
и
\begin{equation}
  \label{eq:29}
  f_{3}=-\frac{1}{2(ab+bc+ca)}\left[\frac{1}{12}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{8}+ \frac{1}{2}\int_{0}^{\infty} e^{-z}Q(z) dz
    \right].
\end{equation}

\section{Предельная форма и физический смысл коэффициентов разложения}
\label{sec:accur-expans-phys}

В работе  \cite{1742-6596-1135-1-012024} мы представили результаты симуляции методами Монте-Карло,
использующими алгоритмы Метрополиса и Вонга-Ландау, которые подтверждают вид разложения
(\ref{eq:26}). В частности, мы получили $f_{1}=0.04\pm 0.04$, что согласуется со значением $f_{1}=0$.

Димеры в скейлиноговом пределе в целом описываются теорией свободных фермионов
\cite{dijkgraaf2009dimer}, но на шестиугольной решетке (и на графах, допускающих существование
ориентации Кастелейна) модель переформулируется через функцию высоты, что можно рассматривать, как
бозонизацию теории \cite{gogolin2004bosonization}.

В скейлинговом пределе $\varepsilon\to 0$ в модели димеров возникает так называемая ``предельная форма''
~\cite{1998math......1068J,cohn1998shape}. Окрестности углов области ``заморожены'', значения
функции высоты на них фиксированы. Аналитическая ``арктическая кривая'' отделяет замороженные
области от области, где поведение описывается эффективной свободной теорией поля
\cite{kenyon2009lectures,kenyon2008height,kenyon2006dimers}. Более того, функция высоты в
скейлиноговом пределе стремится к определенной аналитической поверхности, а флуктуации вокруг этой
``предельной формы'' описываются свободной гауссовской теорией поля в искривленной фоновой метрике,
заданной ``предельной формой''. Можно использовать конформное отображение, чтобы перевести
внутренность ``арктической кривой'' в верхнюю полуплоскость.

Скейлиноговое поведение (\ref{eq:26}) логарифма статсуммы имеет вид, характерный для двумерных
моделей \cite{cardy1988finite}.

Поэтому мы можем рассматривать первые два члена $f_{0}$ и $f_{1}$ как объемную и граничную свободную
энергию в соответствующей теории поля. Член $f_1$ отвечает вкладу ``предельной формы''. Так как у
нас детерминистическая замороженная граница, мы естественно видим, что $f_{1}=0$.
%The value of the first term $f_{0}$ can be rewritten using polylogarithm functions as

Член, пропорциональный логарифму характерной длины $\varepsilon$ также универсален
\cite{cardy1988finite} и должен возникать во всех двумерных теориях с границей. В статье
\cite{cardy1988finite} Карди и Пешель утверждают, что на гладком многообразии с характерной длиной
$L$ и с гладкой границей этот член должен иметь следующий вид:
\begin{equation}
  \label{eq:31}
  \delta F = -\frac{1}{6}{\bf c} \chi \ln L,
\end{equation}
где  ${\bf c}$ -- центральный заряд эффективной теории поля, а $\chi$ -- эйлерова характеристика
многообразия  $\chi=2-2 h-b$, где  $h$ -- количество ручек, а  $b$ -- число границ. Наивное
применение формулы  \eqref{eq:31} к нашему результату $\delta F=\frac{1}{12}$ дало бы ${\bf
  c}=\frac{1}{2}$, но это некорректно, так как мы должны рассматривать теорию поля в искривленной
фоновой метрике.

В случае наличия угловой сингулярности с углом $\Theta$ на границе, логарифмический вклад в
свободную энергию превращается в 
\begin{equation}
  \label{eq:86}
  \delta F = \frac{{\bf c}}{24}\left(\frac{\Theta}{\pi}-\frac{\pi}{\Theta}\right) \ln L.
\end{equation}
Эта формула недавно использовалась в работе Н. Аллегра \cite{allegra2015exact}, чтобы показать, что
центральный заряд при описании модели димеров в терминах функции высоты на квадратной решетке с
мономером в углу равняется единице ${\bf c}=1$, вопреки предыдущим работам, утверждавшим, что ${\bf
  c}=-2$ \cite{morin2016integrability}.

В случае многообразия с конической сингулярностью с полу-углом $\Theta$, логарифмический вклад,
приведенный в работе \cite{cardy1988finite}, равен
\begin{equation}
  \label{eq:91}
  \delta F = \frac{{\bf c}}{24}\left(\frac{\Theta}{\pi}-\frac{4\pi}{\Theta}\right) \ln L.
\end{equation}

В нашем случае мы рассматриваем $2(ab+bc+ca)$ в качестве объема области, то есть
\begin{equation}
  \label{eq:33}
  \delta F = \left(2(ab+bc+ca)\right) f_{2}\ln\varepsilon.
\end{equation}

Применяя описанные выше формулы Карди и Пешеля, должно быть возможно вычислить  $\delta F$ через
значение центрального заряда для гауссовой свободной теории поля ${\bf c}=1$, кривизну метрики,
индуцированной предельной формой и конформное отображение из внутренней области ``арктической
кривой'' в верхнюю полуплоскость. Но метрика становится сингулярной у границы внутренней области
\cite{kenyon2007limit}, и вклад сингулярностей в логарифмическую поправку еще не изучен. Поэтому наш
результат для  $f_2$ должен быть полезен для такого исследования, которое мы постараемся представить
в отдельной публикации.

Последний член $f_{3}$ зависит только от формы области через $a,b,c$, с универсальным вкладом,
который равен интегралу функции  $e^{-z}\frac{\xi(z)-\xi(0)}{z}$. В следующих разделах мы покажем,
что эта константа возникает при устранении логарифмической расходимости даже для весов Больцмана,
зависящих от координаты.

\section{Численная проверка}
\label{sec:numeric-checks}
Для численной проверки нашего результата \eqref{eq:26} нам нужно вычислить интеграл в  $f_{3}$.
Функция  $e^{-z}\frac{\xi(z)-\xi(0)}{z}$ непрерывная и гладкая, но при численном вычислении предела
$z\to 0$ требуется осторожность. Вычисляя интеграл численно при помощи Mathematica, мы получаем
\begin{equation}
  \label{eq:2}
  \int_{0}^{\infty}e^{-z}Q(z)\dz=\int_{0}^{\infty}e^{-z}\frac{\xi(z)-\xi(0)}{z} dz = -0.080842.%0.08084228607897521
\end{equation}

Асимптотическое разложение \eqref{eq:26} дает очень хорошее приближение для свободной энергии. На
Рис.~\ref{fig:approx-acc} мы показываем точные и приближенные значения для $f$, а на правой
панели демонстрируем, что невязка аппроксимации ведет себя как  $\mathcal{O}(\varepsilon^{4})$.

\begin{figure}[htbp]
  \includegraphics[scale=0.9]{exact-vs-approximation}
  \includegraphics{error-1}
  \caption{\label{fig:approx-acc} {\it Слева:} Зависимость свободной энергии от  $1/\varepsilon$,
    вверху -- $a=b=c=1$, внизу -- $a=3, b=2, c=1$. Точные значения обозначены черными точками.
    Приближение по формуле  \eqref{eq:26} изображено голубой и красной пунктирными линиями.  {\it
      Справа:} Зависимость невязки аппроксимации от $\varepsilon$, сплошная линия -- приближение
    функцией $b\varepsilon^{4}$.}
\end{figure}

\section{Коробка бесконечной высоты}
\label{sec:gener-other-doma}

Рассмотрим случай кубиков в коробке бесконечной высоты. В этом случае $K=\infty$, а  $M,N$ --
конечны. Теперь шестиугольная область конфигураций димеров имеет сторону бесконечной длины, и общее
число димеров бесконечно, поэтому более естественно полагать объем системы равным $V=MN$.

Положив $K=\infty$ в статсумме, мы видим, что все члены с  $k$ сокращаются и остается 
\begin{equation}
  \label{eq:3}
  Z[M,N,q]=\prod_{i=1}^{M}\prod_{j=1}^{N}\frac{1}{1-q^{i+j-1}}.
\end{equation}

Вычисление свободной энергии практически полностью повторяет вычисление в случае коробки конечной
высоты. Мы раскладываем логарифм в выражении для свободной энергии, а затем факторизуем сумму:
\begin{multline}
  \label{eq:4}
  f=-\frac{1}{MN}\sum_{i=1}^{M}\sum_{j=1}^{N}\ln\left(1-e^{-\varepsilon(i+j-2)}e^{-\varepsilon}\right)=\\
  =\sum_{n=1}^{\infty}\frac{\varepsilon^{2}}{ab}\frac{1}{n}e^{-n\varepsilon}\left(\sum_{i=1}^{M}e^{-n\varepsilon(i-1)}\right)
  \left(\sum_{j=1}^{N}e^{-n\varepsilon(j-1)}\right).
\end{multline}
Вычисляя суммы геометрических прогрессий, мы получаем почти такие же выражения, как в формуле
\eqref{eq:38}, за исключением того, что $H_{n}$ теперь содержит только два множителя $H_{n}
=\left(1-e^{-na}\right)\left(1-e^{-nb}\right)$: 
\begin{equation}
  \label{eq:5}
  f=-\frac{1}{ab} \sum_{n=1}^{\infty}\frac{\chi(n\varepsilon)}{n^{3}} H_{n}.
\end{equation}
Функция  $\chi(z)=e^{-z}\left(\frac{z}{1-e^{-z}}\right)^{2}$ та же, что и в формуле \eqref{eq:39}.

Повторяя вычисления из раздела  \ref{sec:free-energy-scaling}, мы получаем следующие результаты для
коэффициентов $f_{0}, f_{1}, f_{2}, f_{3}$: 
\begin{equation}
  \label{eq:6}
  f_{0}=\frac{1}{ab}\left[\Li_{3}(e^{-a})+\Li_{3}(e^{-b})-
    \Li_{3}(e^{-a-b})-\zeta(3)\right],
\end{equation}
\begin{equation}
  \label{eq:8}
  f_{1}=0,
\end{equation}
\begin{equation}
  \label{eq:9}
  f_{2}=\frac{1}{ab}\frac{1}{12},
\end{equation}
\begin{equation}
  \label{eq:11}
  f_{3}=-\frac{1}{ab}\left[\frac{1}{12}\ln\left(\frac{(e^{a}-1)(e^{b}-1)}{(e^{a+b}-1)}\right)-\frac{1}{8}+ \frac{1}{2}\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
    \right].
\end{equation}

В этом случае мы так же видим на Рис.~\ref{fig:approx-acc-2d} хорошее численное совпадение
асимптотического разложения \eqref{eq:26} и точной формулы  \eqref{eq:4}.

Так как шестиугольник с бесконечной стороной похож на бесконечную полосу, естественно сравнить наш
результат с результатами для поправок конечного размера к скейлингу свободной энергии в модели
димеров на квадратной решетке на полосе, цилиндре и полосе, замкнутой в ленту Мёбиуса. Такие
результаты были недавно собраны вместе в работе \cite{izmailian2017finite}, а в работе
\cite{Sh_Izmailian_2019} был проведен их дальнейший анализ. В этих работах предложено следующее
общее выражение для разложения свободной энергии на квадратной решетке размером $M\times N$ (здесь
$S=M\times N$ ): 
\begin{equation}
  \label{eq:32}
  f=f_{\mathrm{bulk}}+\frac{2}{M}f_{s1}+\frac{2}{N}f_{s2}
  +f_{\mathrm{corn}}\frac{\ln S}{S} +\frac{1}{S} (f_{\mathrm{univ}}+f_{\mathrm{nonuniv}})
\end{equation}
В частности, на полосе объемный член $f_{\mathrm{bulk}}=\frac{G}{\pi}$, где  $G$ -- константа
Каталана, поверхностная свободная энергия отлична от нуля $f_{s1}=-\frac{1}{4}\ln(1+\sqrt{2})$, а
коэффициент перед  $\frac{1}{S}$ равен  $\frac{\pi}{24}$. В случае цилиндра и полосы Мёбиуса
логарифмический член также присутствует.

Сравнивая наши результаты \eqref{eq:6}, \eqref{eq:8}, \eqref{eq:9}, \eqref{eq:11} с этими
выражениями, мы видим, что поведение на шестиугольной решетке в присутствии предельной формы
отличается. В частности, объемный член $f_{0}$ зависит от геометрических параметров $a$ и  $b$,
граница свободна от натяжения, так что граничный член $f_{1}$ равен нулю, и геометрические параметры
области также входят и в коэффициент при $\varepsilon^{2}$.

\begin{figure}[htbp]
  \includegraphics[scale=0.8]{exact-vs-approximation-2d}
  \includegraphics[scale=0.9]{error-2d}
  \caption{\label{fig:approx-acc-2d} {\it Слева:} Зависимость свободной энергии от  $1/\varepsilon$
    в коробке бесконечной высоты, вверху при $a=b=1$, внизу -- $a=2, b=1$. Точные значения показаны
    черными точками. Приближения при помощи формулы \eqref{eq:26} изображены синей и красной
    пунктирными линиями. {\it Справа:} Зависимость невязки аппроксимации от  $\varepsilon$, сплошная
    линия -- приближение функцией $b\varepsilon^{4}$.}
\end{figure}

\section{Коробка бесконечной высоты с весами Больцмана, зависящими от координаты}
\label{sec:box-infinite-height}

Рассмотрим теперь обобщение на случай, когда  $q$ зависит от координаты. Обычно полагают, что  $q$
принимает различные значения на диагоналях, которые нумеруются координатой $t$. Нам нужно ввести
некоторые обозначения, чтобы можно было рассматривать скейлинговый предел. Пусть  $\varphi(t)$ --
непрерывная ограниченная гладкая функция при  $t\in\left[-a,b\right]$. Введем обозначение
$q_{i}=e^{-\varepsilon \varphi\left(i\varepsilon\right)}$ при $i=(-M+1)\dots N-1$. Мы нумеруем
диагонали таким образом, что левый верхний угол прямоугольника $M\times N$ имеет номер $N-M$, правый
верхний -- $N$, левый нижний -- $-M$, а правый нижний -- $0$. (См. Рис. \ref{fig:box-t-coords}).
Диагонали с индексами  $N$ и $-M$ имеют нулевую длину, поэтому мы можем положить $q_{N}=q_{-M}=0$.
Всего у нас не более $N+M-1$ непустой диагонали.

\begin{figure}[htbp]
  \includegraphics[scale=0.5]{box-t-coords}
  \caption{\label{fig:box-t-coords} Координаты диагоналей.}
\end{figure}

Статсумма для этого и более общего случая произвольной формы внутренней границы коробки была
вычислена в работе  \cite{okounkov2007random}. В нашем случае она содержит произведения весов
$q_{i}$ для диагоналей с отрицательными и положительными номерами:
\begin{equation}
  \label{eq:13}
  Z=\prod_{i=0}^{N-1}\prod_{j=0}^{M-1} \frac{1}{1-q_{N-M}^{-1}\left(\prod_{k=0}^{i}q_{N-M-k}\right)\left(\prod_{l=0}^{j}q_{N-M+l}\right)}.
\end{equation}
(См. Теорему 2 в \cite{okounkov2007random}).
Если мы положим  $q_{i}=q$,  мы восстановим формулу \eqref{eq:3}.

Опять рассмотрим зависимость свободной энергии от $\varepsilon$:
\begin{equation}
  \label{eq:21}
  f=-\frac{\varepsilon^{2}}{ab}\sum_{i=0}^{N-1}\sum_{j=0}^{M-1}\ln
  \left(1-e^{\varepsilon \varphi(b-a)}e^{-\varepsilon\sum_{k=0}^{i}\varphi\left(b-a-k\varepsilon\right)}
    e^{-\varepsilon\sum_{l=0}^{j}\varphi\left(b-a+l\varepsilon\right)} \right).
\end{equation}

Член  $f_{0}$ в асимптотическом разложении  \eqref{eq:26} легко можно получить из этого выражения.
Для этого нам нужно приблизить суммы интегралами, воспользовавшись формулой
$\sum_{k=0}^{i}\varepsilon\varphi(b-a-k\varepsilon)\approx
\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx$%%!!!!! Write more here
и аналогичными приближениями для других сумм:
\begin{multline}
  \label{eq:74}
  f_{0}=-\frac{1}{ab}\int_{0}^{b}\int_{0}^{a}\ln
  \left(1-e^{-\int_{0}^{y}\varphi\left(b-a-x\right)\dx}
    e^{-\int_{0}^{z}\varphi\left(b-a+\bar x\right)\dxb} \right)\dz\dy=\\
  =-\frac{1}{ab}\int_{0}^{b}\int_{0}^{a}\ln
  \left(1-e^{-\int_{-y}^{z}\varphi\left(b-a+x\right)\dx} \right)\dz\dy.
\end{multline}
Подставим в это выражение  $\varphi(x)\equiv 1$, мы немедленно получаем формулу \eqref{eq:6}, так
как полилогарифмы являются интегралами логарифмов. Хоть логарифм и расходится в точке $y=z=0$, эта
расходимость исчезает после двойного интегрирования.

Для вычисления члена $f_{1}$ мы воспользуемся следующей простой леммой:
\begin{lemma}
  Пусть  $a=M\varepsilon$ и $b=N\varepsilon$.
  Для интегрируемой почти всюду аналитической функции  $f$ и аналитической функции $\varphi$ сумма
  может быть приближена интегралом с поправками порядка $o(\varepsilon)$:
  \begin{equation}
    \label{eq:75}
    \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}f\left(\varepsilon\sum_{k=-i}^{j}\varphi(k\varepsilon)\right)=
    \int_{0}^{a}\int_{0}^{b}f\left(\int_{-y}^{z}\varphi(x)\dx\right)\dz\;\dy+o(\varepsilon).
  \end{equation}
  \begin{proof}
    Воспользуемся формулой Эйлера-Маклорена для приближения сумм интегралами с поправками.
    Достаточно рассмотреть линейные по $\varepsilon$ члены. Сперва используем формулу для первой
    суммы в аргументе функции $f$:
  \begin{equation}
    \label{eq:76}
    \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}f\left(\varepsilon\sum_{k=-i}^{j}\varphi(k\varepsilon)\right)=
    \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}f\left(\int_{-i\varepsilon}^{j\varepsilon}\varphi(x)\dx+\frac{\varepsilon}{2}\left(\varphi(j\varepsilon)-\varphi(-i\varepsilon)\right)+\mathcal{O}(\varepsilon^{2})\right).
  \end{equation}
  Для двойной суммы можно использовать следующий простой аналог формулы Эйлера-Маклорена. Пусть $G$
  -- аналитическая функция на прямоугольнике  $[0,a]\times[0,b]$, тогда
\begin{equation}
  \label{eq:77}
  \int_{0}^{a} \int_{0}^{b}G(y,z) \dz\; \dy\;
  \approx\sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\left\{\varepsilon^{2}G\left(i\varepsilon,j\varepsilon\right)+
    \frac{\varepsilon^{3}}{2}\left((\partial_{y}+\partial_{z})G\right)(i\varepsilon,j\varepsilon)\right\}+o(\varepsilon^{2}).
\end{equation}
Эта формула элементарно выводится путем разбиения области интегрирования на квадратики со стороной
$\varepsilon$ и подстановки рядов Тейлора для  $G$ в интегралы.

Обозначим через $G_{\varepsilon}(y,z)$ функцию двух аргументов, входящую в двойную сумму в \eqref{eq:76}:
\begin{equation}
  \label{eq:78}
  G_{\varepsilon}(y,z)=f\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right).
\end{equation}
Используем формулу \eqref{eq:77}, чтобы выразить двойную сумму в формуле \eqref{eq:76} через
интеграл и поправку:
\begin{equation}
  \label{eq:79}
  \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\varepsilon^{2}G_{\varepsilon}(i\varepsilon,j\varepsilon)=\int_{0}^{a}\int_{0}^{b}
  G_{\varepsilon}(y,z)\dz\;\dy-
  \frac{\varepsilon^{3}}{2}
  \sum_{i=0}^{M-1}\sum_{j=0}^{N-1}\left((\partial_{y}+\partial_{z})G_{\varepsilon}\right)(i\varepsilon,j\varepsilon)+o(\varepsilon^{3}).
\end{equation}
Теперь разложим функцию $G_{\varepsilon}(y,z)$ под интегралом в ряд Тейлора по $\varepsilon$:
\begin{equation}
  \label{eq:80}
  \int_{0}^{a}\int_{0}^{b}G_{\varepsilon}(y,z)\dz\;\dy=
  \int_{0}^{a}\int_{0}^{b}G_{0}(y,z)\dz\;\dy+\int_{0}^{a}\int_{0}^{b}\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))\cdot
  f'\left(\int_{-y}^{z}\varphi(x)\dx\right)\dz\;\dy+o(\varepsilon). 
\end{equation}
С другой стороны, производные  $G_{\varepsilon}$ по  $y,z$ вычисляются как
\begin{eqnarray}
  \label{eq:81}
  \partial_{z}G_{\varepsilon}(y,z)=f'\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right)\varphi(z)+o(\varepsilon)\\ 
  \partial_{y}G_{\varepsilon}(y,z)=-f'\left(\int_{-y}^{z}\varphi(x)\dx+\frac{\varepsilon}{2}(\varphi(z)-\varphi(-y))+o(\varepsilon)\right)\varphi(-y)+o(\varepsilon).
\end{eqnarray}
Подставляя равенства  \eqref{eq:80},\eqref{eq:81} в  \eqref{eq:79} и используя формулу \eqref{eq:77}
для замены двойной суммы производных  $G_{\varepsilon}$ на двойной интеграл, мы видим, что линейные
поправки по  $\varepsilon$ сокращаются. 
\end{proof}
\end{lemma}

Воспользуемся леммой для нашей удельной свободной энергии $f$, которая является аналитической
функцией, и для нашей гладкой функции  $\varphi$. Мы немедленно получаем, что
\begin{equation}
  \label{eq:82}
  f_{1}=0.
\end{equation}

Следующие члены асимптотического разложения требуют больших усилий, так как мы должны выделить вклад
порядка $\varepsilon^{2}\ln\varepsilon$.

Поэтому для вывода выражений для высших порядков в разложении \eqref{eq:26} нам нужно разложить
логарифм, поменять порядок суммирования и переписать свободную энергию таким же образом, как мы
делали это ранее:
\begin{equation}
  \label{eq:22}
   f=\sum_{n=1}^{\infty}\frac{\varepsilon^{2}}{ab}\frac{1}{n}e^{n\varepsilon
     \varphi(b-a)}\sum_{i=0}^{N-1}\sum_{j=0}^{M-1} e^{-n\varepsilon\sum_{k=0}^{i}\varphi\left(b-a-k\varepsilon\right)}
    e^{-n\varepsilon\sum_{l=0}^{j}\varphi\left(b-a+l\varepsilon\right)}.
  \end{equation}
Мы снова факторизуем двойную сумму в произведение двух сумм:  
\begin{equation}
  \label{eq:23}
    f=\sum_{n=1}^{\infty}\frac{\varepsilon^{2}}{ab}\frac{1}{n}e^{-n\varepsilon
     \varphi(b-a)}\left(\sum_{i=0}^{N-1}
     e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\right)
   \left(\sum_{j=0}^{M-1}e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\right),
 \end{equation}
 где мы полагаем, что $\sum_{k=1}^{0}\varphi(b-a-k\varepsilon)=0$ и
$\sum_{l=1}^{0}\varphi(b-a+l\varepsilon)=0$. Заметим, что при  $\varphi(t)\equiv 1$ мы восстановим формулу
\eqref{eq:4}.

Введем следующие обозначения:
\begin{equation}
  \label{eq:52}
  r_{\mp}(i\varepsilon)\equiv\varepsilon\sum_{k=1}^{i}\varphi(b-a\mp k\varepsilon).
\end{equation}
Функции  $r_{\mp}$ могут быть приближены по формуле Эйлера-Маклорена следующим образом:
\begin{equation}
  \label{eq:53}
  r_{\mp}(x)\approx\int_{0}^{x}\varphi(b-a\mp y) \dy +\frac{\varepsilon}{2}\left(\varphi(b-a\mp
    x)-\varphi(b-a)\right)\mp \frac{\varepsilon^{2}}{12}\left(\varphi'(b-a\mp x)-\varphi'(b-a)\right).
\end{equation}
Обозначим через $\Psi_{n}^{\mp}$ следующие функции:
\begin{equation}
  \label{eq:54}
  \Psi^{\mp}_{n}(x)\equiv e^{-nr_{\mp}(x)}-e^{-nxr_{\mp}'(0)}.
\end{equation}
Эти функции аналитичны по  $\varepsilon$, кроме того, высшие производные  $\Psi^{\mp}_{n}$ растут по
$n$ не слишком быстро. Поэтому суммы рядов, записанных через эти функции и их производные, сходятся,
как мы увидим далее.

С такими обозначениями мы можем записать свободную энергию в виде
\begin{multline}
  \label{eq:55}
  f=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n}e^{-n\varepsilon\varphi(b-a)}\left[\varepsilon^{2}\sum_{i=0}^{N-1}e^{-n\varepsilon
    i r_{-}'(0)}\sum_{j=0}^{M-1}e^{-n\varepsilon j
    r_{+}'(0)}+\varepsilon\sum_{i=0}^{N-1}e^{-n\varepsilon i
    r_{-}'(0)}\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon)+\right.\\
\left. +\varepsilon\sum_{i=0}^{N-1}\Psi^{-}_{n}(i\varepsilon) \cdot\varepsilon\sum_{j=0}^{M-1}e^{-n\varepsilon
  j r_{+}'(0)}+\varepsilon\sum_{i=0}^{N-1}\Psi^{-}_{n}(i\varepsilon)
\cdot\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon)\right]=\\
=f^{(0)}+f^{+}+f^{-}+f^{\times}.
\end{multline}
Первый член $f^{(0)}$ можно явно вычислить:
\begin{equation}
  \label{eq:56}
  f^{(0)}=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n} e^{-n\varepsilon
    \varphi(b-a)}\varepsilon^{2}\frac{\left(1-e^{-n b r_{-}'(0)}\right)\left(1-e^{-n a
        r_{+}'(0)}\right)}{\left(1-e^{-n\varepsilon r_{-}'(0)}\right)\left(1-e^{-n\varepsilon r_{+}'(0)}\right)}.
\end{equation}

Обозначим числитель этого выражения $H_{n}(\varepsilon)$:
\begin{equation}
  \label{eq:57}
  H_{n}(\varepsilon)=\left(1-e^{-n b r_{-}'(0)}\right)\left(1-e^{-n a r_{+}'(0)}\right).
\end{equation}
Заметим, что
\begin{equation}
  \label{eq:58}
  r_{\mp}'(0)=\varphi(b-a)\mp \frac{\varepsilon}{2} \varphi'(b-a)+\frac{\varepsilon^{2}}{12} \varphi''(b-a)+\mathcal{O}(\varepsilon^{3}).
\end{equation}
можно переписать в виде
\begin{equation}
  \label{eq:59}
  r_{\mp}'(0)=\varphi(b-a)\left(1+\alpha_{\mp}(\varepsilon)\right), 
\end{equation}
где
\begin{equation}
  \label{eq:60}
  \alpha_{\mp}(\varepsilon)=\mp
  \frac{\varepsilon}{2}\frac{\varphi'(b-a)}{\varphi(b-a)}+\frac{\varepsilon^{2}}{12} \frac{\varphi''(b-a)}{\varphi(b-a)}+\mathcal{O}(\varepsilon^{3}).
\end{equation}

Теперь для $f^{(0)}$ у нас получается
\begin{equation}
  \label{eq:61}
  f^{(0)}=\frac{1}{ab}\sum_{n=1}^{\infty} \frac{\tilde{\chi}_{n}\left(n\varepsilon
      \varphi(b-a),\varepsilon\right) }{n^{3}\varphi(b-a)^{2}},
\end{equation}
где $\tilde{\chi}_{n}(z,\varepsilon)$ определена как
\begin{equation}
  \label{eq:62}
  \tilde{\chi}_{n}(z,\varepsilon)\equiv \frac{z^{2} e^{-z}
    H_{n}(\varepsilon)}{\left(1-e^{-z\left(1+\alpha_{-}(\varepsilon)\right)}\right)
    \left(1-e^{-z\left(1+\alpha_{+}(\varepsilon)\right)}\right)}.
\end{equation}
Важно включить сюда $H_{n}(\varepsilon)$, так как $H_{n}(\varepsilon)$ содержит убывающие экспоненты
по $n$.

Вычисляя производные  $f^{(0)}$ по $\varepsilon$, мы получаем
\begin{multline}
  \label{eq:63}
  \left(\frac{d}{d\varepsilon}\right)^{2} f^{(0)}=\frac{1}{ab\varphi(b-a)} \sum_{n=1}^{\infty}
  \frac{1}{n^{3}}\left[
    \left.\tilde{\chi}''_{n,\varepsilon\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+
    2n\varphi(b-a)\left.\tilde{\chi}''_{n,z\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+\right.\\\left.
      n^{2}\left(\varphi(b-a)\right)^{2}\tilde{\chi}''_{n,zz}\left(n\varepsilon\varphi(b-a),\varepsilon\right)  \right]+
    \mathcal{O}(\varepsilon \ln \varepsilon)=\\
    =\frac{1}{ab\varphi(b-a)}\left[\sum_{n=1}^{\infty} \frac{1}{n^{3}}
      \tilde{\chi}''_{n,\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\frac{1}{n^{2}}\tilde{\chi}''_{n,z\varepsilon}(0,0)\right]+
    \\
    +\frac{1}{ab}\sum_{n=1}^{\infty}\frac{H_{n}}{n}\chi''\left(n\varepsilon\varphi(b-a)\right)+\mathcal{O}(\varepsilon\ln \varepsilon),
\end{multline}
где функция  $\chi(z)$ та же, что и в равенстве \eqref{eq:39}
\begin{equation}
  \label{eq:64}
  \chi(z)=\frac{z^{2} e^{-z}}{\left(1-e^{-z}\right)^{2}}
\end{equation}
и
\begin{equation}
  \label{eq:65}
  H_{n}=\left(1-e^{-nb\varphi(b-a)}\right) \left(1-e^{-na\varphi(b-a)}\right).
\end{equation}

Последняя сумма в последней строке равенства \eqref{eq:63} такая же, как и в разделе
\ref{sec:gener-other-doma}, поэтому ее можно вычислить
\begin{multline}
  \label{eq:66}
  \frac{1}{ab}\sum_{n=1}^{\infty}\frac{H_{n}}{n}\chi''\left(n\varepsilon \varphi(b-a)\right)=
  \frac{1}{ab}\left(\frac{1}{6}\ln \varepsilon +\frac{1}{6}\ln \varphi(b-a)+ \int_{0}^{\infty}
    e^{-z}Q(z) \dz+\chi''(0)\sum_{n=1}^{\infty}\frac{H_{n}-1}{n}\right)=\\
  =\frac{1}{ab}\left(\frac{1}{6}\ln \varepsilon +\frac{1}{6}\ln \varphi(b-a)+ \int_{0}^{\infty}
    e^{-z}Q(z) \dz+\frac{1}{6}\ln\left(\frac{\left(1-e^{a\varphi(b-a)}\right)\left(1-e^{a\varphi(b-a)}\right)}{1-e^{(a+b)\varphi(b-a)}}\right)\right),
\end{multline}
где $Q(z)$ было определено в формуле \eqref{eq:85}.

В итоге вклад $f^{(0)}$ в асимптотическое разложение \eqref{eq:26} дается членом
\begin{equation}
  \label{eq:87}
f^{(0)}_{3}=\frac{1}{ab\varphi(b-a)}\left[\sum_{n=1}^{\infty} \frac{1}{n^{3}}
  \tilde{\chi}''_{n,\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\frac{1}{n^{2}}\tilde{\chi}''_{n,z\varepsilon}(0,0)\right],
\end{equation}
который имеет сложный вид, но не зависит от  $\varepsilon$ и может быть выписан явно, и выражением
\eqref{eq:66}, которое дает логарифмическое поведение по $\varepsilon$.

Теперь мы должны рассмотреть другие члены в выражении \eqref{eq:55}. Для $f^{+}$ получаем
\begin{equation}
  \label{eq:67}
  f^{+}=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n} e^{-n\varepsilon\varphi(b-a)} \varepsilon
  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon).
\end{equation}
Сумма по $j$ может быть приближена интегралом с помощью формулы Эйлера-Маклорена
\begin{equation}
  \label{eq:68}
  \varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon) = \int_{0}^{a}\Psi^{+}_{n}(x) \dx -
  \frac{\varepsilon}{2}\left(\Psi^{+}_{n}(a)-\Psi^{+}_{n}(0)\right)+
  \frac{\varepsilon^{2}}{12}\left(\Psi^{+'}_{n}(a)-\Psi^{+}_{n}(0)\right)+
  \mathcal{O}\left(\varepsilon^{m}\Psi^{+(m-1)}_{n}\right).
\end{equation}
Так как функция $r(x)$ аналитическая и  $r(0)=0$, мы можем написать $r(x)=xr'(0)+x^{2}\zeta(x)$, поэтому
\begin{equation}
  \label{eq:83}
\Psi_{n}(x)=e^{-nr'(0)x}\left(e^{-n\left(r(x)-xr'(0)\right)}-1\right)=e^{-nxr'(0)}\left(e^{-nx^{2}\zeta(x)}-1\right)  
\end{equation}
и мы видим, что $\Psi_{n}(0)=0$ и $\Psi_{n}'(0)=0$.
Тогда в пределе $n\to\infty$ мы получаем
\begin{equation}
  \label{eq:69}
  \int_{0}^{c}\Psi_{n}(x)
  \dx \xrightarrow[n\to\infty]{}\int_{0}^{c}e^{-nxr'(0)}\left(-nx^{2}\zeta(x)+\dots\right)\dx\sim \frac{1}{n^{2}}.
\end{equation}
Производные  $\Psi$ ведут себя как  $\Psi_{n}^{(m)}(0)\sim n^{m-1}$, так как мы должны
дифференцировать выражение в скобках в формуле \eqref{eq:83}, чтобы получить ненулевое значение, а
тогда возникает дополнительная степень  $x$, которую тоже нужно дифференцировать. Поэтому вклад от
$\varepsilon^{m}\Psi_{n}^{(m-1)}(0)$ в $f^{+}$ дает
\begin{equation}
  \label{eq:70}
  \sum_{n=1}^{\infty} \frac{1}{n} e^{-n\varepsilon\varphi(b-a)}
  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}} \varepsilon^{m+1}\Psi_{n}^{(m-1)}(0)\sim
  \sum_{n=1}^{\infty} \frac{1}{n^{4}} e^{-n\varepsilon\varphi(b-a)}
  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}} (\varepsilon n )^{m+1}.
\end{equation}
Для второй производной по  $\varepsilon$ мы получаем, что основной вклад ведет себя как
$\sum_{n=1}\frac{1}{n^{2}}e^{-n\varepsilon\varphi(b-a)}
  (n\varepsilon)^{m+1}\xrightarrow[\varepsilon\to 0]{}0,$
если $m\geq 3$. Для членов с  $m=0,1,2$ нам нужно вычислить предел при $\varepsilon\to 0$. После
этого вычисления мы получаем:
\begin{multline}
  \label{eq:71}
  f^{+}_{3}\equiv\left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{+}\right|_{\varepsilon=0} =\\
  \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
  e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}
  \varepsilon\left(\int_{0}^{a} \Psi_{n}^{+}(x) \dx -\varepsilon \Psi_{n}^{+}(a) +\varepsilon^{2}\Psi^{+'}_{n}(0)\right)\right|_{\varepsilon=0}.
\end{multline}
Заметим, что  $\frac{\varepsilon}{1-\exp(-n\varepsilon r'_{-}(0))}$ аналитическая по $\varepsilon$.
Производные можно вычислить явно, но выражения получаются слишком громоздкими, поэтому мы их не приводим.

Вклад от $f^{-}$ можно вычислить точно таким же образом:
\begin{multline}
  \label{eq:72}
   f^{-}_{3}\equiv \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{-}\right|_{\varepsilon=0} =\\
  \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
  e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nar_{+}'(0)}}{1-e^{-n\varepsilon r_{+}'(0)}}
 \varepsilon\left(\int_{0}^{b} \Psi_{n}^{-}(x) \dx -\varepsilon \Psi_{n}^{-}(a) +\varepsilon^{2}\Psi^{-'}_{n}(0)\right)\right|_{\varepsilon=0}.
\end{multline}
Наконец, мы должны рассмотреть
$f^{\times}=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n}e^{-n\varepsilon\varphi(b-a)}\varepsilon\sum_{i=0}^{N-1}\Psi_{n}^{-}(i\varepsilon)
\sum_{j=0}^{M-1}\Psi_{n}^{+}(j\varepsilon)$. Изучая вклады производных
$\Psi_{n}^{(m)}(0)$ аналогично соображениям перед формулой \eqref{eq:70}, мы видим, что
$\varepsilon^{m}\Psi_{n}^{(m-1)}(0)\sim \frac{1}{n^{2}}$. То есть
\[\sum_{n=1}^{\infty}\frac{1}{n}e^{-n\varepsilon\varphi(b-a)}\frac{1}{n^{2}}\varepsilon^{m}\Psi_{n}^{(m-1)}(0)\sim
\sum_{n=1}^{\infty}\frac{1}{n^{5}}e^{-n\varepsilon\varphi(b-a)}(\varepsilon n)^{m},\] и эти члены
дают нулевой вклад после дифференцирования  $\left(\frac{d}{d\varepsilon}\right)^{2}$ при
$\varepsilon\to 0 $ и $m\geq 3$. Это же верно для всех вкладов с производными 
$\Psi$ в обеих суммах. В членах с  $m<3$ мы можем просто вычислить вторую производную по
$\varepsilon$ и предел $\varepsilon\to 0$ и получаем
\begin{multline}
  \label{eq:73}
   f^{\times}_{3}\equiv \left.\left(\frac{d}{d\varepsilon}\right)^{2}
    f^{\times}\right|_{\varepsilon=0}=\left.\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n}
  \left(\frac{d}{d\varepsilon^{2}}\right)^{2}\left(\int_{0}^{b}\Psi^{-}_{n}(x)\dx
    -\frac{\varepsilon}{2}\Psi^{-}_{n}(b)+\frac{\varepsilon^{2}}{12}\Psi^{-'}_{n}(b)\right)\cdot\right.\\
\cdot\left.\left(\int_{0}^{a}\Psi^{+}_{n}(x)\dx-\frac{\varepsilon}{2}\Psi^{+}_{n}(a)+
    \frac{\varepsilon^{2}}{12}\Psi^{+}_{n}(a)\right)\right|_{\varepsilon=0}.
\end{multline}
Это выражение тоже может быть вычислено явно, но слишком громоздко, поэтому мы его не приводим.

Наконец, мы можем выписать коэффициенты асимптотического разложения в данном случае:
\begin{equation}
  \label{eq:84}
  f_{0}= -\frac{1}{ab}\int_{0}^{b}\int_{0}^{a}\ln
  \left(1-e^{-\int_{-y}^{z}\varphi\left(b-a+x\right)\dx} \right)\dz\dy,
\end{equation}
\begin{equation}
  \label{eq:88}
  f_{1}=0,
\end{equation}
\begin{equation}
  \label{eq:89}
  f_{2}=\frac{1}{ab}\frac{1}{12}
\end{equation}
и
\begin{multline}
  \label{eq:90}
  f_{3}=f^{(0)}_{3}+f^{+}_{3}+f^{-}_{3}+f^{\times}_{3}+
  \frac{1}{ab}\frac{1}{12}\ln\left(\frac{\varphi(b-a)\left(1-e^{a\varphi(b-a)}\right)\left(1-e^{a\varphi(b-a)}\right)}{1-e^{(a+b)\varphi(b-a)}}\right)+\\
  +\frac{1}{ab}\left(\frac{1}{8} +\frac{1}{2} \int_{0}^{\infty}
    e^{-z}q(z) \dz\right),
\end{multline}
где в первую строку мы включили  вклады, которые зависят от выбора весовой функции
$\varphi$, а во вторую -- универсальный вклад, который появляется также при
$\varphi\equiv 1$ и в случае коробке конечной высоты.

\subsection{Численная проверка}
\label{sec:numerical-checks-nonuniform}
Здесь мы приводим результаты  сравнения численных значений коэффициентов разложения
$f_{0},f_{1},f_{2},f_{3}$, которые были получены из аналитических выражений
\eqref{eq:84},\eqref{eq:88},\eqref{eq:89},\eqref{eq:90} при помощи системы компьютерной алгебры
Mathematica, с результатами аппроксимации точных численных значений свободной энергии для
 $\frac{1}{\varepsilon}=2\dots 200$
по формуле $f=f_{0}+
f_{1}\varepsilon+
f_{2}\varepsilon^{2}\ln\varepsilon+f_{3}\varepsilon^{2}+f_{4}\varepsilon^{3}+f_{5}\varepsilon^{4}$.

В таблице мы приводим результаты для различных функций  $\varphi(z)$ и значений $a,b$.
\begin{table}[htpb]
\begin{center}
\begin{tabular}{c|cccccc}
  & $\varphi(z)$ & $a,b$ & $f_{0}$ &  $f_{1}$ &  $12ab f_{2}$ &  $f_{3}$ \\
 \hline
 analytic & $(2+\cos(z))/3$ & 1,3 & $0.472206688$ & $0$ & $1$&$-0.043883000$\\
 numeric & $(2+\cos(z))/3$ & 1,3 &  $0.472206693$ & $0.000000730$ & $1.000730689$&$-0.043827958$\\
  \hline
 analytic & $(2+\cos(z))/3$ & 2,3 & $0.235922467$ & $0$ & $1$&$-0.030398000$\\
 numeric & $(2+\cos(z))/3$ & 2,3 &  $0.235922467$ & $0.000000044$ & $1.000088528$&$-0.030394694$\\
\hline                                                
 analytic & $a+z/2$ & 1,3 & $0.097288596$ & $0$ & $1$&$-0.033688300$\\
 numeric & $a+z/2$ & 1,3 &  $0.097288593$ & $0.000000848$ & $1.000848267$&$-0.033624441$\\
\hline                                                
 analytic & $a+z/2$ & 2,3 & $0.032804447$ & $0$ & $1$&$-0.015094000$\\
 numeric & $a+z/2$ & 2,3 &  $0.032804447$ & $-0.000000002$ & $0.999996808$&$-0.015094162$\\
\end{tabular}
\caption{Значения параметров аппроксимации и аналитически вычисленных коэффициентов разложения для
  различных весовых функций $\varphi$ и значений $a,b$.
}
\label{tttt1}
\end{center}
\end{table}

Мы видим хорошее совпадение значений, полученных численно и аналитически.

%%  
%%  If we assume that $\varphi(b-a)\neq 0$, we can again obtain function $\chi(z)$:
%%  \begin{multline}
%%    \label{eq:24}
%%     f=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{\chi\left(n\varepsilon\varphi(b-a)\right)}{n^{3}}\left(1-e^{-n\varepsilon
%%         \varphi(b-a)}\right)^{2}\frac{1}{\varphi^{2}(b-a)}\cdot\\
%%     \cdot\left(1+\sum_{i=1}^{N-1}
%%       e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\right)
%%     \left(1+\sum_{j=1}^{M-1}e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\right)  
%%  \end{multline}
%%

%% We need to separate contributions of different orders in $\varepsilon$ and keep only the terms up to
%% $\varepsilon^{2}$. To do so we expand the exponent
%% \begin{equation}
%%   \label{eq:35}
%% e^{-n\varepsilon\varphi(b-a)}\approx
%% 1-n\varepsilon\varphi(b-a)+\frac{1}{2}n^{2}\varepsilon^{2}\varphi^{2}(b-a)+\mathcal{O}(\varepsilon^{3})  ,
%% \end{equation}
%% and approximate the sums by integrals using Euler-Maclaurin formula.
%% 
%% The sum $\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)$ can be approximated using
%% Euler-Maclaurin formula:
%% \begin{multline}
%%   \label{eq:25}
%%   \varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)=\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx
%%   +\frac{\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)+\\
%%   +\frac{1}{12}\varepsilon^{2}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)+\mathcal{O}(\varepsilon^{3})
%% \end{multline}
%% 
%% Substituting into the exponent and expanding we get:
%% \begin{multline}
%%   \label{eq:34}
%%   e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\approx e^{-n\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx
%%   -n\frac{\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)
%%   -n\frac{1}{12}\varepsilon^{2}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)}\approx\\
%% \approx e^{-n\int_{0}^{i\varepsilon}\varphi(b-a-x)\dx}\left[1-\frac{n\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)+\right.\\\left.
%%   +\varepsilon^{2}\left(\frac{n^{2}}{8} \left(\varphi(b-a)+\varphi(b-a-i\varepsilon)\right)^{2}-\frac{n}{12}\left(\varphi'(b-a-i\varepsilon)-\varphi'(b-a)\right)\right)+\mathcal{O}(\varepsilon^{3})\right]
%% \end{multline}
%% Similarly, the expression for the second exponent is
%% \begin{multline}
%%   \label{eq:36}
%%  e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\approx e^{-n\int_{0}^{j\varepsilon}\varphi(b-a+x)\dx}\left[1-\frac{n\varepsilon}{2}\left(\varphi(b-a)+\varphi(b-a+j\varepsilon)\right)+\right.\\\left.
%%   +\varepsilon^{2}\left(\frac{n^{2}}{8} \left(\varphi(b-a)+\varphi(b-a+j\varepsilon)\right)^{2}-\frac{n}{12}\left(\varphi'(b-a+j\varepsilon)-\varphi'(b-a)\right)\right)+\mathcal{O}(\varepsilon^{3})\right]  
%% \end{multline}
%% 
%% Now we need to substitute this expansion and formula \eqref{eq:35} into our formula for free energy
%% \eqref{eq:23}. 
%%

\section*{Выводы и перспективы}
\label{sec:conclusion}

В данной работе мы вычислили асимптотическое разложение свободной энергии в модели димеров на
шестиугольной области шестиугольной решетки, на шестиугольнике со стороной бесконечной длины и для
модели с весами Больцмана, зависящими от координаты. Мы представили численные результаты,
подтверждающие наши вычисления. Мы обсудили физический смысл коэффициентов разложения и показали,
что наши результаты подтверждают универсальный характер логарифмической поправки и могут
использоваться для изучения поведения на границе замороженной области.

В дальнейшем мы изучим связь коэффициентов разложения со спектральными свойствами оператора Дирака
на не замороженной области и исследуем универсальность наших результатов. Мы также представим
вычисление логарифмической поправки к свободной энергии через геометрию ``предельной формы''.

\section*{Благодарности}
\label{sec:acknowledgements}
Мы благодарим профессора Н.Ю. Решетихина за его внимание к этой работе. Мы благодарим П.А. Белова за
полезные дискуссии и поддержку. Мы благодарим М.И. Вязовского за указание на ошибку в первой версии
этой статьи. Мы благодарим Иствана Праусе за ссылку
\cite{allegra2015exact} и Вадима Горина за обсуждение предельной формы.

Мы благодарим организаторов и участников конференции МКТП-2018 за возможность представить наши
результаты и полезные обсуждения.

Исследование поддержано РФФИ, грант № 18-01-00916.

\bibliographystyle{utphys}
\bibliography{listing,bibliography,dimers}{} 
\end{document}
